### 2016-08-30 LaTeX/Turnover.tex
latex folder

\documentclass[12pt]{article}
%\documentclass{nature}

% Including pdf figures
\usepackage{graphicx}
\usepackage{pdfpages}
%really place a figure in a location
\usepackage{float}
%Overrun caption
\usepackage[CaptionAfterwards]{fltpage}
% Math stuff
\usepackage{amsmath}
% Bibliographies
\usepackage[numbers]{natbib}
\bibpunct{(}{)}{,}{a}{}{;}

\usepackage[font={scriptsize}]{caption}

\usepackage{lineno} %gives line numbers with \lineno command

\usepackage{setspace}
\onehalfspace

\begin{document}

\title{Gametic Selection, Sex Ratio Bias, and Transitions Between Sex Determination Systems}
\author{Michael F Scott$*^1$ and Matthew M Osmond$*^2$, and Sarah P Otto$^2$}
\date{}
\maketitle
\noindent
$*$ These authors contributed equally to this work

\noindent
$^1$ Department of Botany, University of British Columbia, \#3529 - 6270 University Boulevard, Vancouver, BC, Canada V6T 1Z4

\noindent
$^2$ Department of Zoology, University of British Columbia, \#4200 - 6270 University Boulevard, Vancouver, BC, Canada V6T 1Z4

\noindent
email: mfscott@biodiversity.ubc.ca, mmosmond@zoology.ubc.ca

\noindent
Contributions:

\newpage

\begin{abstract}
Sex determination systems are remarkably dynamic; many studied taxa display transitions of sex-determining genes between chromosomes or the evolution of new sex-determining systems. 
%Predominant theories in which new sex-determining systems are favoured by selection involve sex ratio selection or fitness differences between sexes (e.g., sexually antagonistic selection). 
Here, we utilize population genetic models to study the spread of novel sex-determining systems where we also include 
%a period of selection during the haploid stage produced by one sex, e.g., pollen or sperm competition. 
haploid gametic selection, e.g., pollen or sperm competition.
Haploid selected loci experience a form of sex-specific selection (because gametic competition occurs predominantly among haploids produced by males) and can also cause sex ratios at birth to become biased (because sex ratios are determined by the fertilization success of X- versus Y-bearing pollen/sperm). 
We find that the evolution of sex determination systems where mothers determine sex at birth (e.g., environmental sex determination where sex is determined at birth) is influenced by classic Fisherian sex ratio selection. {\color{red}(Maybe not true???)}
However, notably, we find that the spread of new genetic sex determination systems is not affected by sex ratio biases that are caused by gametic selection because sex ratios become biased after parental provisioning has occurred (even if pollen/sperm competition occurs within the mother). 
In addition, we find that linkage of an ancestral sex chromosome to a locus under haploid selection can favour transitions between male and female heterogamety (e.g., XY to ZW), which is not the case for any forms of diploid sex specific selection (e.g., sexually antagonistic selection).
During these transitions, new sex-determining alleles spread despite breaking up favourable associations that build up between ancestral sex-determining loci and selected loci, reducing population mean fitness. 
Furthermore, a period of selection among haploids can favour the stable maintenance of polymorphic sex determination systems. 
Thus, our models offer several new insights to be explored as information about sex determination in non-model taxa accumulates.

%[Approx 320 words]
\end{abstract}

\newpage

\section*{Introduction}

Animals and angiosperms exhibit extremely diverse sex determination systems, reviewed in \citet{Bull:1983vi,Charlesworth:2010it,Beukeboom:2014vb,Bachtrog:2014bx}. 
Among species with genetic sex determination of diploid sexes, some taxa have heterogametic males (XY) and homogametic females (XX), including %non-monotreme? 
mammals and most dioecious plants \citep{Ming:2011iy}; whereas other taxa have homogametic males (ZZ) and heterogametic females (ZW), including Lepidoptera and birds. 
Within several taxa, the chromosome that harbours the master sex-determining region changes. 
For example, transitions of the master sex-determining gene between chromosomes or the evolution of new master sex-determining genes have occurred in Salmonids \citep{Li:2011fm,Yano:2012di}, Diptera \citep{Vicoso:2015hf}, and \textit{Oryzias} \citep{Myosho:2012fv}.
%Presentation at evolution found neo sex chromosome in birds, doesn't seem to be published or bioRxiv yet (consider pers com.), title: A previously unknown neo-sex chromosome mediates plumage divergence and speciation in hybridizing birds Jason Sardell; Elizabeth Cooper; J. Albert C. Uy
In addition, many gonochoric/dioecious clades with genetic sex determination exhibit transitions between male (XY) and female (ZW) heterogamety, including eight of 26 teleost fish families \citep{Mank:2006bt}, true fruit flies \citep[Tephritids,][]{Vicoso:2015hf}, amphibians \citep{Hillis:1990gu}, the angiosperm genus \textit{Silene} \citep{Slancarova:2013dq}, Coleoptera and Hemiptera \citep[][plate 2]{Beukeboom:2014vb}.
Indeed, in some cases, both male and female heterogametic sex determination systems can be found the same species, including cichlid species \citep{Ser:2010iq} and \textit{Rana rugosa} \citep{Ogata:2007jm}.

\noindent
Depending on the prominence of transitions to ESD in the manuscript include something like (currently quoted):

``Transitions have repeatedly occurred between environmental sex determination and genotypic sex determination, as exemplified by the distribution of temperature sex determination among reptiles: either temperature or genes provide the initial trigger in closely related species (Ewert and Nelson 1991; Pokorna and Kratochvil 2009; Ezaz et al. 2009) or even conspecific populations (Pen et al. 2010). Similar situations are found in fishes (e.g., Conover and Heins 1978a).''

\noindent
We have results where polygenic sex determination is sometimes stable:

``Polygenic sex determination has been reported in many plants (e.g. Shannon \& Holsinger 2007), fishes (Vandeputte et al. 2007; Ser et al. 2010; Liew et al. 2012), crustaceans (e.g. Battaglia 1958; Battaglia \& Malesani 1959; Voordouw
\& Anholt 2002), bivalves (Haley 1977; Saavedra et al. 1997), gastropods (Yusa 2007a,b), and polychaetes (Bacci 1965, 1978; Premoli et al. 1996).''

%For example, closely related species in the Medaka lineage (cite Takenhana et al. 2008) and Tilapiinae (cite Lee et al 2004, Cnaani et al 2008), citations in Beukeboom.

\noindent
Description of sex ratio adjustment and sexual antagonism theories:

Predominant theories in which new sex determination systems are favoured by selection involve fitness differences between sexes (e.g., sexually antagonistic selection) or sex ratio selection.
\citet{vanDoorn:2007eu,vanDoorn:2010hu} show that new sex determination loci can be favoured if they arise in close linkage with a locus that experiences sexual antagonism. 
For example, linkage allows favourable associations to build up between a male-beneficial allele and a neo-Y chromosome. 
Such associations can favour a new master sex-determining gene on a new chromosome \citep{vanDoorn:2007eu} and can also favour a transition between male and female heterogamety \citep[e.g., a ZW to XY transition,][]{vanDoorn:2010hu}.
However, any sexually-antagonistic loci that are linked to the ancestral sex-determination locus will develop similar, favourable associations and select against the spread of a new sex-determination system.

Sex ratio selection might be a particularly important force driving transitions between sex-determining systems \citep[Chapter 7]{Beukeboom:2014vb}. 
For example, feminizing mutations may invade when female biased sex ratios are favoured due to interdemic selection (Wilson and Colwell 1981, Vuilleumier et al. 2007 CITE) or local mate competition (Hamilton 1967, Reinhold 1996, Werren and Taylor 1984, Pen et al. 2010 CITE). 
In other situations, sex ratio selection may favour transitions in order to restore equal sex ratios. 
For example, \citet{Kozielska:2010vm} consider systems in which the ancestral sex chromosomes experience meiotic drive (e.g., driving X or Y chromosomes are inherited disproportionately often), which leads to biased sex ratios. They find that new, unlinked sex-determining loci (masculinizing or feminizing mutations) can then spread, restoring an even sex ratio.

For example, new sex-determining systems (particularly transitions between male and female heterogamety) can be favoured in order to restore equal sex ratios in populations that have a sex ratio bias \citep{Bull:1983vi,Kozielska:2010vm,Ubeda:2015fx}.

Sex ratios can also become biased due to meiotic drive;
in a classic paper, \citet{Hamilton:1967ts} showed that X- or Y-linked alleles that experience meiotic drive will bias sex ratios. 
He assumed that driving alleles are under directional selection and spread to fixation but such alleles can also be maintained at intermediate frequencies by selection \citep{Feldman:1989gm,Holman:2015en}. 
When sex ratios are biased, other loci are expected to evolve to restore equal sex ratios. 
Indeed, alleles that negate the effect of sex-linked meiotic drivers and restore equal sex ratios have been identified \citep{Stalker:1961th,Smith:1975ft}. 
A similar process occurs with cytoplasmic male sterility alleles (that cause biased sex ratios) and nuclear `restorer' genotypes \citep{Frank:1989vl}.

When sex ratio bias occurs due to haploid selection, a natural class of sex ratio `restorers' exist because haploid selection often occurs in a context that is determined by the diploid parents. 
For example, the intensity of pollen competition can be manipulated by altering style length \citep{Travers:2001,Lankinen:2001gc,Ruane:2009vt}, delaying stigma receptivity \citep{Galen:1986wq,Lankinen:2011if} and/or delaying pollen tube growth in the pistil \citep{Herrero:2003jf}. 
Where the X and Y have fixed fitness differences, \citet{Hough:2013uo} demonstrated that mothers should generally evolve to balance sex ratios by reducing the intensity of haploid competition. 
However, reducing competition among haploids also reduces the potential for harmful deleterious mutations to be purged. 
When deleterious mutations are included, the optimal intensity of haploid selection can reflect a balance between maximizing offspring fitness and equalizing sex ratios.

As part of a collaborative project \citep{Otto:2015va}, I considered the evolution of the haploid `selective arena' in cases where the X chromosome harbours a polymorphism that affects haploid fitness. 
Mothers again primarily evolve to restore equal sex ratios.
However, modifying haploid selection also affects the X-linked genotypes that are inherited by offspring. 
Specifically, increasing the intensity of haploid selection increases the proportion of daughters (all progeny of X-bearing sperm/pollen are female) that inherit the allele with high haploid fitness. 
If this allele has high fitness in daughters, mothers can be selected to increase the intensity of haploid selection; otherwise, decreased selection among haploids is favoured.
Thus, because altering haploid selection intensity affects the alleles that are inherited by daughters, mothers can favour slightly biased sex ratios. 
In addition, I found that stronger sex ratio biases can be favoured by paternal manipulations of the haploid `selective arena' because fathers are strongly selected to maximize their own siring success (above selection to equalize the sex ratio).

It is not clear how the spread of new sex determination systems would be influenced by the combination of sex ratio biases and favourable associations between haploid selected loci and sex-determining regions.

We add haploid selection (and justification, see below)
\\
Mention Hough study for sex ratio adjustment here or in discussion? Also discuss the fact that, in terms of recombination suppression, haploid selection among male gametes generates selection pressure similar to that of male specific selection. 
\\
What will be the result: where there is sex biases and sex-specific selection

{\color{blue}
FROM PREVIOUS PAPER:

To the extent that pollen and sperm success reflects differences in their haploid genotypes, selection among these gametes/gametophytes is qualitatively distinct from selection among diploid males. 
That is, diploids cannot be assigned fitness values that also account for the fitness of their haploid gametes \cite{Immler:2012tl}. 
In plants, selection among haploid male gametophytes is thought to be pervasive \cite{SKOGSMYR:2002ce,Moore:2011jt,Marshall:2016fe}; in \textit{Arabidopsis}, 60-70\% of all genes are expressed during the haploid phase \cite{Borg:2009jpa}, and pollen expressed genes exhibit stronger signatures of purifying selection and positive selection \cite{Arunkumar:2013iq,Gossmann:2014dua}.
For agricultural breeding, pollen has been exposed to a variety of selection pressures \textit{in vivo} and \textit{in vitro}, including temperature \cite{Hedhly:2004iv,Clarke:2004ir}, herbicides \cite{Frascaroli:2001ee}, metals \cite{Searcy:1985vt}, water stress \cite{Ravikumar:2003uo}, and pathogens \cite{Ravikumar:2012ej}, resulting in an increased frequency of resistant genotypes among the diploid sporophytic offspring. 
In animals, expression during the haploid sperm stage is traditionally thought to be suppressed \cite{Hecht:1998hz}, although recent evidence suggests that the extent and selective importance of postmeiotic gene expression may be underestimated \cite{Zheng:2001fi,JOSEPH:2004haa,Vibranovski:2010et,Immler:2014im}. 
}

Here, suggest that the canonical view (no haploid expression in animals, genome highly chromatinized in sperm and not expressed) might be based on model organisms, such as mice, where sperm is sufficiently short-lived that transcripts provisioned during spermatogenesis may be sufficient without further haploid transcription (although note that the Vibranovski lab results are in mice showing some transcription does occur). 
In broadcast spawning animal species (e.g., corals, many fish) and species where sperm typically requires greater longevity, expression of the haploid genotype may be required (Immler paper indicates this, but not that strongly - as I remember). 
We can use this suggestion in discussion to speculate in what species the processes we study might be looked for (i.e.., animals with multiple matings, broadcast spawning and/or long-lived sperm and outcrossing/non-pollen-limited plants).

{\color{blue} 
\noindent FROM PREVIOUS PAPER:

The maintenance of polymorphism at loci that experience sex specific selection in both haploid and diploid phases was considered by Immler et al. \cite{Immler:2012tl}, demonstrating that polymorphisms can be maintained by sexually antagonistic selection or overdominance as well as by conflicting selection pressures in haploids and diploids (haploid-diploid conflict or ploidally antagonistic selection) or a combination of these selective regimes.

}

\textcolor{red}{NOTE RE: DRIVE. I expect drive (that occurs specifically in one sex, e.g., during spermatogenesis) to behave almost exactly like haploid selection. That is, I think that a XY-linked driver that is maintained by selection (e.g., because it causes sterility when homozygous, which is common in known drive systems) will only favour invasion of a more tightly linked neo-Y (worsening sex ratio biases) and could favour invasion of a neo-W. This may run counter to generic expectations from new sex chromosome systems evolving to balance the sex ratio. So, do you think it would significantly enhance the paper to model drive explicitly or just discuss it as being similar???}

\linenumbers
\modulolinenumbers[2]

\section*{Discussion}

{\color{blue}
FROM THESIS:
Generally, any sex-linked gene that harbours genetic variation in haploid fitness should cause sex ratios to become biased. 
Sex ratio bias caused by pollen competition has previously been discussed in the context of Y-linked deleterious mutations, which are thought to build up after recombination suppression evolves \citep{Lloyd:1974tz,Stehlik:2005ul}. 
Sex ratios can also become biased due to meiotic drive;
in a classic paper, \citet{Hamilton:1967ts} showed that X- or Y-linked alleles that experience meiotic drive will bias sex ratios. 
He assumed that driving alleles are under directional selection and spread to fixation but such alleles can also be maintained at intermediate frequencies by selection \citep{Feldman:1989gm,Holman:2015en}. 
When sex ratios are biased, other loci are expected to evolve to restore equal sex ratios. 
Indeed, alleles that negate the effect of sex-linked meiotic drivers and restore equal sex ratios have been identified \citep{Stalker:1961th,Smith:1975ft}. 
A similar process occurs with cytoplasmic male sterility alleles (that cause biased sex ratios) and nuclear `restorer' genotypes \citep{Frank:1989vl}.

When sex ratio bias occurs due to haploid selection, a natural class of sex ratio `restorers' exist because haploid selection often occurs in a context that is determined by the diploid parents. 
For example, the intensity of pollen competition can be manipulated by altering style length \citep{Travers:2001,Lankinen:2001gc,Ruane:2009vt}, delaying stigma receptivity \citep{Galen:1986wq,Lankinen:2011if} and/or delaying pollen tube growth in the pistil \citep{Herrero:2003jf}. 
Where the X and Y have fixed fitness differences, \citet{Hough:2013uo} demonstrated that mothers should generally evolve to balance sex ratios by reducing the intensity of haploid competition. 
However, reducing competition among haploids also reduces the potential for harmful deleterious mutations to be purged. 
When deleterious mutations are included, the optimal intensity of haploid selection can reflect a balance between maximizing offspring fitness and equalizing sex ratios.

As part of a collaborative project \citep{Otto:2015va}, I considered the evolution of the haploid `selective arena' in cases where the X chromosome harbours a polymorphism that affects haploid fitness. 
Mothers again primarily evolve to restore equal sex ratios.
However, modifying haploid selection also affects the X-linked genotypes that are inherited by offspring. 
Specifically, increasing the intensity of haploid selection increases the proportion of daughters (all progeny of X-bearing sperm/pollen are female) that inherit the allele with high haploid fitness. 
If this allele has high fitness in daughters, mothers can be selected to increase the intensity of haploid selection; otherwise, decreased selection among haploids is favoured.
Thus, because altering haploid selection intensity affects the alleles that are inherited by daughters, mothers can favour slightly biased sex ratios. 
In addition, I found that stronger sex ratio biases can be favoured by paternal manipulations of the haploid `selective arena' because fathers are strongly selected to maximize their own siring success (above selection to equalize the sex ratio).

Several aspects of the relationship between haploid selection (e.g., pollen or sperm competition) and sex ratios remain to be explored. 
For example, new sex-determining systems (particularly transitions between male and female heterogamety) can be favoured in order to restore equal sex ratios in populations that have a sex ratio bias \citep{Bull:1983vi,Kozielska:2010vm,Ubeda:2015fx}.
Based on the results of Chapter \ref{ch:sexchromosomes}, we would expect that sex ratio biases would occur via associations between sex-determining loci and loci that experience haploid selection. 
However, these associations should also select against transitions between sex-determining systems, as has been found with sexually antagonistic selection \citep{vanDoorn:2007eu,vanDoorn:2010hu}. 
It is not clear how the spread of new sex determination systems would be influenced by the combination of sex ratio biases and favourable associations between haploid selected loci and sex-determining regions. 
Finally, \citet{Hamilton:1967ts} pointed out that biased sex ratios can affect population size because the number of offspring in each generation is typically determined by the number of females. 
Population density can, in turn, affect the intensity of pollen/sperm competition in future generations because fewer males are available to donate pollen/sperm in a particular area. 
Thus, a feedback could occur between population densities and haploid selection, which has not yet been investigated. 
}

\bibliographystyle{amnatnat.bst}
\bibliography{sex_chromosomes.bib}

\end{document}

### 2016-08-30 PNAS_Style/PNASTWOS.TEX
playing with indices

%% PNAStwoS.tex
%% Sample file to use for PNAS articles prepared in LaTeX
%% For two column PNAS articles
%% Version: Apr 15, 2008

%% BASIC CLASS FILE
\documentclass{pnastwo}

%% ADDITIONAL OPTIONAL STYLE FILES
%\usepackage[dvips]{graphicx}
%\usepackage{pnastwoF}
%\usepackage{amssymb,amsfonts,amsmath}

%% OPTIONAL MACRO DEFINITIONS
\def\s{\sigma}

% Including math features
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{graphicx}

%%%%%%%%%%%%
%% For PNAS Only:
\url{www.pnas.org/cgi/doi/10.1073/pnas.0709640104}
\copyrightyear{2008}
\issuedate{Issue Date}
\volume{Volume}
\issuenumber{Issue Number}
%\setcounter{page}{2687} %Set page number here if desired
%%%%%%%%%%%%

\begin{document}

\title{Almost sharp fronts for the surface geostrophic equation}

\author{Roberta Graff\affil{1}{University of Cambridge, Cambridge,
United Kingdom},
Javier de Ruiz Garcia\affil{2}{Universidad de Murcia, Bioquimica y Biologia
Molecular, Murcia, Spain},
\and
Franklin Sonnery\affil{2}{}}

\contributor{Submitted to Proceedings of the National Academy of Sciences
of the United States of America}

\maketitle

\begin{article}
\begin{abstract}
We use heat kernels or eigenfunctions of the Laplacian to construct
local coordinates on large classes of Euclidean domains and Riemannian
manifolds (not necessarily smooth, e.g. with $\mathcal{C}^\alpha$
metric). These coordinates are bi-Lipschitz on large neighborhoods of
the domain or manifold, with  constants controlling the distortion and
the size of the neighborhoods that depend only on natural geometric
properties of the domain or manifold. The proof of these results relies
on novel estimates, from above and below, for the heat kernel and its
gradient, as well as for the eigenfunctions of the Laplacian and their
gradient, that hold in the non-smooth category, and are stable with
respect to perturbations within this category. Finally, these coordinate
systems are intrinsic and efficiently computable, and are of value in
applications. 
\end{abstract}

\keywords{monolayer | structure | x-ray reflectivity | molecular electronics}

\abbreviations{SAM, self-assembled monolayer; OTS,
octadecyltrichlorosilane}

\dropcap{I}n this article we study the evolution of ``almost-sharp'' fronts
for the surface quasi-geostrophic equation. This 2-D active scalar
equation reads for the surface quasi-geostrophic equation. 
\begin{equation}
\mfrac{D \theta}{Dt}=\mfrac{\pr \theta}{\pr t} + u\cdot \nabla
\theta=0 \label{qg1}
\end{equation}
where,
\begin{equation}
 u=(u_1,u_2)=(-\mfrac{\pr \psi}{\pr y},\mfrac{\pr \psi}{\pr
x})\label{qg2} \end{equation}
and,
\begin{equation} (-\triangle)^{\f12}\psi=\theta \, ,\label{qg3} \end{equation}
For simplicity we are considering fronts on the cylinder, i.e. we
take $(x,y)$ in $\mathbb{R}/_{\displaystyle{\mathbb{Z}}}\times
\mathbb{R}$. In this setting we define $-\triangle^{-\f12}$ that
comes from inverting the third equation by convolution with the
kernel. To avoid irrelevant considerations at $\infty$ we
will take $\eta$ to be compactly supported
\[
\mfrac{\chi(u,v)}{(u^2+v^2)^{\f12}}+\eta(u,v)
\]
where $\chi (x,y)\ \epsilon\ C^{\infty}_{0},\,\,
\chi(x,y)=1 \hspace{8pt} \mbox{in} \hspace{5pt} |x-y|\leq r \,\,
\mbox{and}\,\, supp \chi$ is contained in $  \{|x-y|\leq R\} $
with $0<r<R<\frac{1}{2}$. Also $ \eta\ \epsilon\ C^{\infty}_0$,
$\eta(0,0)=0 $.

The main mathematical interest in the quasi-geostrophic equation
lies in its strong similarities with the 3-Euler equations. These
results were first proved by Constantin, Majda and Tabak, see
\cite{1}, \cite{2} and \cite{3} for more details. There
are several other research lines for this equation, both
theoretical and numerical. See  \cite{4}, \cite{5}, and
\cite{6}.
The question
about the regularity of the solutions for QG  remains as an open
problem.

Recently one of the authors has obtained the equation for the
evolution of sharp fronts (in the periodic setting), proving its
local well-posedness for that equation. (see \cite{ZhaZha} and
\cite{TSL} for more details). This is a problem in contour
dynamics. Contour dynamics for other fluid equations has been
studied extensively.

\section{Analysis of almost sharp fronts}
We begin our analysis on almost sharp fronts for the
quasi-geostrophic equation recalling the notion of weak solution.

For these solutions we have the following

\begin{definition}
A bounded function $\theta$ is a weak solution of QG if for any
$\phi\,\epsilon\,
C_0^{\infty}(\fdb\times\mathbb{R}\times[0,\vep])$ we have
\begin{eqnarray}
&&  \int_{\mathbb{R}^+\times\fd\times\mathbb{R}} \hspace{-25pt}
 \theta(x,y,t)\, \pr_t \phi
\,(x,y,t) dy dx dt+\nonumber\\
  & +&\int_{\mathbb{R}^+\times\fd\times\mathbb{R}}
\hspace{-26pt} \theta\,(x,y,t) u(x,y,t)\cdot\nabla\phi\,(x,y,t)
dydxdt = 0 \label{weaksol} \end{eqnarray}
where $u$ is determined by equations \eqref{qg2} and \eqref{qg3}.
\end{definition}

\subsection{Data Sources}
We are interested in studying the evolution of almost sharp fronts
for the QG equation. These are weak solutions of the equation with
large gradient ($\sim \displaystyle{ \inlinefrac{1}{\delta}}$, where $2
\delta$ is the thickness of the transition layer for $\theta$).

\section{Discussion}
\subsection{Cylindrical Case}
We are going to consider the cylindrical case here. We consider a
transition layer of thickness smaller than $2\delta$ in which
 $\theta$ changes from 0 to 1. (see Figure \ref{afoto}).That means we are considering $\theta$  of the form
\[
\theta  = 1   \mbox{ if }\quad  y\geq \varphi(x,t)+\delta
\]
\[
\theta \mbox{ bounded} \mbox{ if }\quad |\varphi(x,t)-y|\leq\delta
\]
\be \theta = 0  \mbox{ if }\quad  y\leq \varphi(x,t)-\delta
\label{theta} \ee
where $\varphi$ is a smooth periodic function and
$0<\delta<\frac{1}{2}$.

%For these solutions we have the following

\begin{theorem}
If the active scalar $\theta$ is as in \eqref{theta} and satisfies
the equation \eqref{weaksol}, then $\varphi$ satisfies the
equation
\begin{eqnarray}
\mfrac{\pr \varphi}{\pr t}(x,t)&=&\hspace{-2pt}\dst
\int_{\fd}\mfrac{\mfrac{\pr \varphi}{\pr x}(x,t)-\mfrac{\pr
\varphi}{\pr
u}(u,t)}{[(x-u)^{2}+(\varphi(x,t)-\varphi(u,t))^{2}]^{\f12}}\nonumber\\
&&
\chi(x-u,\varphi(x,t)-\varphi(u,t)) du \hspace{3pt} +
\nonumber\\
&+&\dst \int_{\fd} \Big{[}\mfrac{\pr \varphi} {\pr
x}(x,t)-\mfrac{\pr \varphi}{\pr u} (u,t)\Big{]}
\nonumber\\&&
\eta(x-u,\varphi(x,t)-\varphi(u,t)) du + Error
\end{eqnarray}
with $|Error|\leq C\, \delta | log\delta| $ where $C$ depends only
on $\|\theta\|_{L^{\infty}}$ and $\|
\nabla\varphi\|_{L^{\infty}}$.
\end{theorem}

\begin{remark}
Note that equation \eqref{theta} specifies  the function $\varphi$
up to an error of order $\delta$. Theorem 1 provides an evolution
equation for the function $\varphi$ up to an error of order
$\delta |log \delta|$.
\end{remark}

In order to analyze the evolution of the ``almost-sharp'' front we
substitute the above expression for $\theta$ in the definition of
a weak solution (see \eqref{weaksol}). We use the notation $X =O(
Y)$ to indicate that $|X|\leq C |Y|$ where the constant $C$
depends only on $\|\theta\|_{L^{\infty}}$, $\|
\nabla\varphi\|_{L^{\infty}}$ and $\|\phi\|_{C^1}$, where $\phi$
is a test function appearing in Definition 1.

We consider the 3 different regions defined by the form on
$\theta$. Since $\theta=0$ in the region I the contribution from
that region is 0, i.e.
\[
  \int_{I\times \mathbb{R}}
 \theta(x,y,t)\, \pr_t \phi
\,(x,y,t) dy dx dt+  \]
\[
   +\int_{I\times \mathbb{R}}
 \theta\,(x,y,t) u(x,y,t)\cdot\nabla\phi\,(x,y,t) dydxdt = 0
\]

As for the region II
\[
\int_{II\times \mathbb{R}} \theta (x,y,t) \pr_t\phi (x,y,t)dx dy
dt = O(\delta)
\]
since $\theta$ is bounded and hence $O(1)$, and the area of the
region II is $O(\delta)$. As for the second term
\[
\int_{II\times \mathbb{R}} u \theta \nabla \phi dx dy dt =
O(\delta log(\delta))
\]

To see this, we fix $t$. We must estimate
\[
\int_{\mathbb{R}^2} u\cdot(\mathbb{1}_{II}\theta\nabla\phi) dx dy
\]
We are left to estimate the terms
\[
\int_{III\times \mathbb{R}} \theta \pr_t\phi dx dy
dt+\int_{III\times \mathbb{R}} \theta u_f\cdot \nabla \phi dx dy
dt=:A+B
\]

\subsection{Observations}
The following observations can be made form the numerical experiments
described in this section, and are consistent with the results
of more extensive experimentation performed by the authors:
\begin{itemize}
\item The CPU times in Tables 1--3 are compatible with the estimates in
formulae {\bf 14}, {\bf 16}, and {\bf 23}.
\item
The precision produced by each of Algorithms {\bf I} and {\bf II}
is similar to that provided by formula {\bf 3}, even when
$\omega_{k+1}$ is close to the machine precision.
\end{itemize}

\begin{materials}
\section{Digital RNA SNP Analysis} A real-time PCR assay was designed
to amplify {\it PLAC4} mRNA, with the two SNP alleles being discriminated
by TaqMan probes. {\it PLAC4} mRNA concentrations were quantified in
extracted RNA samples followed by dilutions to approximately one target
template molecule of either type (i.e., either allele) per well.
Details are given in the {\it SI Materials and Methods}.

\section{Digital RCD Analysis} Extracted DNA was quantified by
spectrophotometry (NanoDrop Technologies, Wilmington, DE) and diluted to a
concentration of 
approximately one target template from either chr21 or ch1 per well.
\end{materials}

\appendix[Estimating the Spectral Norm of a Matrix]
In this appendix we describe a method for the estimation of the spectral norm
of matrix $A$. The method does not require access to the individual
entries of $A$; it requires only applications of $A$ and $A$* to vectors.
It is a version of the classical power method. Its probabilistic
analysis summarized below was introduced fairly recently in refs. 13
and 14. This appendix is included here for completeness.

\appendix
This is an example of an appendix without a title.

\begin{acknowledgments}
This work was partially supported by 
Spanish Ministry of Science and Technology Grant BFM2002-02042 (to D.C. and
J.L.R.) and by National Science Foundation Grand DMS-0245242 (to C.F.).
\end{acknowledgments}

\begin{thebibliography}{10}
\bibitem{BN}
M.~Belkin and P.~Niyogi, {\em Using manifold structure for partially
  labelled classification}, Advances in NIPS, 15 (2003).

\bibitem{BBG:EmbeddingRiemannianManifoldHeatKernel}
P.~B\'erard, G.~Besson, and S.~Gallot, {\em Embedding {R}iemannian
  manifolds by their heat kernel}, Geom. and Fun. Anal., 4 (1994),
  pp.~374--398.

\bibitem{CLAcha1}
R.R.~Coifman and S.~Lafon, {\em Diffusion maps}, Appl. Comp. Harm. Anal.,
  21 (2006), pp.~5--30.

\bibitem{DiffusionPNAS}
R.R.~Coifman, S.~Lafon, A.~Lee, M.~Maggioni, B.~Nadler, F.~Warner, and
  S.~Zucker, {\em Geometric diffusions as a tool for harmonic analysis and
  structure definition of data. {P}art {I}: Diffusion maps}, Proc. of Nat.
  Acad. Sci.,  (2005), pp.~7426--7431.

\bibitem{Clementi:LowDimensionaFreeEnergyLandscapesProteinFolding}
P.~Das, M.~Moll, H.~Stamati, L.~Kavraki, and C.~Clementi, {\em
  Low-dimensional, free-energy landscapes of protein-folding reactions by
  nonlinear dimensionality reduction}, P.N.A.S., 103 (2006), pp.~9885--9890.

\bibitem{DoGri}
D.~Donoho and C.~Grimes, {\em Hessian eigenmaps: new locally linear
  embedding techniques for high-dimensional data}, Proceedings of the National
  Academy of Sciences, 100 (2003), pp.~5591--5596.

\bibitem{DoGri:WhenDoesIsoMap}
D.~L. Donoho and C.~Grimes, {\em When does isomap recover natural
  parameterization of families of articulated images?}, Tech. Report Tech. Rep.
  2002-27, Department of Statistics, Stanford University, August 2002.

\bibitem{GruterWidman:GreenFunction}
M.~Gr\"uter and K.-O. Widman, {\em The {G}reen function for uniformly
  elliptic equations}, Man. Math., 37 (1982), pp.~303--342.

\bibitem{Simon:NeumannEssentialSpectrum}
R.~Hempel, L.~Seco, and B.~Simon, {\em The essential spectrum of neumann
  laplacians on some bounded singular domains}, 1991.

\bibitem{1}
Kadison, R.\ V.\ and Singer, I.\ M.\ (1959)
Extensions of pure states, {\it Amer.\ J.\ Math.\ \bf
81}, 383-400.

\bibitem{2}
Anderson, J.\ (1981) A conjecture concerning the pure states of
$B(H)$ and a related theorem. in {\it Topics in Modern Operator
Theory}, Birkha\"user, pp.\ 27-43.

\bibitem{3}
Anderson, J.\ (1979) Extreme points in sets of
positive linear maps on $B(H)$. {\it J.\ Funct.\
Anal.\
\bf 31}, 195-217.

\bibitem{4}
Anderson, J.\ (1979) Pathology in the Calkin algebra. {\it J.\
Operator Theory \bf 2}, 159-167.

\bibitem{5}
Johnson, B.\ E.\ and Parrott, S.\ K.\ (1972) Operators commuting
with a von Neumann algebra modulo the set of compact operators.
{\it J.\ Funct.\ Anal.\ \bf 11}, 39-61.

\bibitem{6}
Akemann, C.\ and Weaver, N.\ (2004) Consistency of a
counterexample to Naimark's problem. {\it Proc.\ Nat.\ Acad.\
Sci.\ USA \bf 101}, 7522-7525.

\bibitem{TSL}
J.~Tenenbaum, V.~de~Silva, and J.~Langford, {\em A global geometric
  framework for nonlinear dimensionality reduction}, Science, 290 (2000),
  pp.~2319--2323.

\bibitem{ZhaZha}
Z.~Zhang and H.~Zha, {\em Principal manifolds and nonlinear dimension
  reduction via local tangent space alignement}, Tech. Report CSE-02-019,
  Department of computer science and engineering, Pennsylvania State
  University, 2002.
\end{thebibliography}
\end{article}

\begin{figure}
\centerline{\includegraphics[width=.4\textwidth]{figsamp.eps}}
\caption{LKB1 phosphorylates Thr-172 of AMPK$\alpha$ \textit{in vitro}
and activates its kinase activity.}\label{afoto}
\end{figure}

\begin{figure*}[ht]
\begin{center}
\centerline{\includegraphics[width=.7\textwidth]{figsamp.eps}}
\caption{LKB1 phosphorylates Thr-172 of AMPK$\alpha$ \textit{in vitro}
and activates its kinase activity.}\label{afoto2}
\end{center}
\end{figure*}

\begin{table}[h]
\caption{Repeat length of longer allele by age of onset class.
This is what happens when the text continues.}
\begin{tabular}{@{\vrule height 10.5pt depth4pt  width0pt}lrcccc}
&\multicolumn5c{Repeat length}\\
\noalign{\vskip-11pt}
Age of onset,\\
\cline{2-6}
\vrule depth 6pt width 0pt years&\multicolumn1c{\it n}&Mean&SD&Range&Median\\
\hline
Juvenile, 2$-$20&40&60.15& 9.32&43$-$86&60\\
Typical, 21$-$50&377&45.72&2.97&40$-$58&45\\
Late, $>$50&26&41.85&1.56&40$-$45&42\tablenote{The no. of wells for all samples was 384. Genotypes were
determined by mass spectrometric assay. The $m_t$ value indicates the
average number of wells positive for the over represented allele.}
\\
\hline
\end{tabular}
\end{table}

\begin{table*}[ht]
\caption{Summary of the experimental results}
\begin{tabular*}{\hsize}
{@{\extracolsep{\fill}}rrrrrrrrrrrrr}
\multicolumn{3}{l}{Parameters}&
\multicolumn{5}{c}{Averaged Results}&
\multicolumn{5}{c}{Comparisons}\cr
\hline
\multicolumn1c{$n$}&\multicolumn1c{$S^*_{MAX}$}&
\multicolumn1c{$t_1$}&\multicolumn1c{\ $r_1$}&
\multicolumn1c{\ $m_1$}&\multicolumn1c{$t_2$}&
\multicolumn1c{$r_2$}&\multicolumn1c{$m_2$}
&\multicolumn1c{$t_{lb}$}&\multicolumn1c{\ \ $t_1/t_2$}&
$r_1/r_2$&$m_1/m_2$&
$t_1/t_{lb}$\cr
\hline
10\tablenote{Stanford Synchrotron Radiation Laboratory (Stanford University,
Stanford, CA)}&1\quad &4&.0007&4&4&.0020&4&4&1.000&.333&1.000&1.000\cr
10\tablenote{$R_{\rm FREE}=R$ factor for the $\sim 5$\% of the randomly
chosen unique ref\/lections not used in the ref\/inement.}&5\quad &50&.0008&8&50&.0020&12&49&.999&.417&.698&1.020\cr
100\tablenote{Calculated for all observed data}&20\quad &2840975&.0423&95&2871117&.1083&521&---&
.990&.390&.182&---\ \ \cr
\hline
\end{tabular*}
\end{table*}

\end{document}

### 2016-08-30 PNAS_Style/SexChromosomes_PNAS.tex
playing with indices

\documentclass{pnastwo}

% Including pdf figures
\usepackage{graphicx}

% Including math features
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{graphicx}

% Including male & female symbols
\usepackage{wasysym}

%referencing SupMat
\usepackage{xr}
\externaldocument{SupMat}

% Including pdf figures
\usepackage{graphicx}
\usepackage{pdfpages}
% Math stuff
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}

% Bibliographies
%\usepackage[]{natbib}
%\bibpunct{[}{]}{,}{n}{}{;} 
%Fonts
%\usepackage[comma,sort&compress]{natbib}

\usepackage{lineno} %gives line numbers with \lineno command

\usepackage{setspace}
%\onehalfspace

\DeclareMathOperator{\Var}{Var}
\DeclareMathOperator{\Cov}{Cov}

\renewcommand{\bibitfont}{\fontsize{6pt}{9pt} \bibfont\slshape}

% Formats equations as (#)
% \renewcommand{\eqref}[1]{\textup{{\normalfont(\ref{#1}}\normalfont)}}

% Formats equations as bold #
\renewcommand{\eqref}[1]{\textup{\bf{\ref{#1}}}}

%%% font setup in order to make the article printable
%\usepackage{mathptmx}
%\usepackage{helvet}
%\renewcommand\bibfont{\fontsize{6pt}{9pt}\bfseries\sffamily}
%\renewcommand{\bibitfont}{\bibfont\slshape}
%\renewcommand{\bibbffont}{\bibfont}
%%%

\renewcommand{\bibitfont}{\fontsize{6pt}{9pt} \bibfont\slshape}

%------------------------------------------------
% DO NOT EDIT THIS SECTION
%------------------------------------------------

%% For PNAS Only:
\url{www.pnas.org/cgi/doi/10.1073/pnas.0709640104}
\copyrightyear{2008}
\issuedate{Issue Date}
\volume{Volume}
\issuenumber{Issue Number}

%----------------------------------------------------------------------------------------

\begin{document}

\title{The Role of Pollen and Sperm Competition in Sex Chromosome Evolution}
\author{
Michael F Scott\affil{1}{University of British Columbia, Vancouver BC, Canada}\affil{2}{corresponding author: mfscott@biodiversity.ubc.ca},
\and
Sarah P.~Otto\affil{1}{}}

%\maketitle

\significancetext{
%[120 word max] 
One feature that characterizes many sex chromosome systems is that, along most of the length, there is no recombination with the opposite sex chromosome.
The typical explanation for this phenomenon entails differences in selection between the sexes. 
However, selection during the haploid phase of males and females can also be strikingly divergent, with male-derived pollen/sperm experiencing particularly intense competition. 
We show that competition between pollen/sperm can favour extreme suppression of recombination between sex chromosomes. 
Extremely suppressed recombination allows strong associations between pollen/sperm beneficial alleles and the male-determining region (Y or Z), which results in biased sex ratios in XY systems. 
Thus, we provide predictions about the rate of sex chromosome evolution and genomic location of pollen/sperm expressed genes.
}

\maketitle

\begin{article}

\noindent
%$^1$ Department of Botany, University of British Columbia, \#3529 - 6270 University Boulevard, Vancouver, BC, Canada V6T 1Z4

\noindent
%$^2$ Department of Zoology, University of British Columbia, \#4200 - 6270 University Boulevard, Vancouver, BC, Canada V6T 1Z4

\noindent
%email: mfscott@biodiversity.ubc.ca.

\noindent
%Contributions: MFS designed and analyzed the models and wrote the manuscript. 
%SPO assisted with model analysis and edited the manuscript.

%\newpage

%\linenumbers
%\modulolinenumbers[2]

\begin{abstract}
To date, research on the evolution of sex chromosomes has focused on sexually antagonistic selection, which has been shown to be a potent driver of the strata and reduced recombination that characterize many sex chromosomes
In this study, we expand our view of the forces driving sex chromosome evolution by considering also selection among haploids, which is likely to occur predominantly among male gametes in angiosperms and animals, i.e., during pollen or sperm competition.
We find that suppressed recombination is favoured on the sex chromosomes, even without selective differences between male and female diploids.
Reduced recombination is favoured because it creates a stronger association between haploid beneficial alleles and the male determining region (Y or Z), which experiences haploid selection most often. 
Similarly, reduced recombination creates linkage between alleles selected against in the haploid stage and the female determining region (X or W).
In XY systems, these associations also result in biased sex ratios at birth.
% ploidally antagonistic selection, in which an allele can be beneficial during the haploid phase and deleterious during the diploid phase. 
%Therefore, conflicts between haploid and diploid phases can be partially resolved by linking genes that are selected in both haploid and diploid phases with sex chromosomes. 
Overall, we predict that whether and how fast recombination suppression evolves on the sex chromosomes can depend on the degree of haploid competition, not just on selective differences between the diploid sexes.
Based on our models, sex chromosomes should become enriched for genes that experience haploid selection, as is expected for genes that experience sexually antagonistic selection.
Thus, we generate a number of promising predictions that can be evaluated in emerging sex chromosome systems. 
\end{abstract}

\keywords{recombination evolution|sex chromosomes|sperm competition|pollen competition|haploid selection|modifier model|evolutionary theory} % When adding keywords, separate each term with a straight line: |

%\newpage

\section*{Introduction}

In organisms with diploid genetic sex determination, recombination is typically suppressed between the X and Y chromosomes or Z and W chromosomes. 
Suppressed recombination appears to begin near the sex-determining region (SDR) and then expand to include larger segments of each sex chromosome \cite{Bergero:2007kr,Nam:2008ko,Lemaitre:2009ij,Wang:2012,Charlesworth:2013}. 
In the absence of recombination, the sex-limited chromosome (Y or W) accumulates deleterious mutations (including gene losses) within the non-recombining region and `genetic degeneration' occurs \cite{Rice:1996ke,Charlesworth:2000cc,Bachtrog:2006ed,Marais:2008hm}.
Thus, the selective forces driving reduced recombination on sex chromosomes are fundamental to our understanding of sex chromosome evolution.

%In plants, recombination suppression is thought to occur during the establishment of the sex-determining region \cite{Charlesworth:2005cx,Charlesworth:2013,Charlesworth:2015dj}. 
%In particular, when separate sexes evolve from hermaphroditism, mutations to suppress both the male and female functions are required. 
%Reduced recombination between such loci is then favoured to avoid the production of offspring that are both male sterile and female sterile \cite{Nei:1969tb,Charlesworth:1978ut}.
%Here, we focus on the evolution of recombination between sex chromosomes after a sex-determining region has been established.

Typically, selective differences between males and females have been evoked to explain the suppression of recombination around established sex-determining regions \cite{Fisher:1931jo,Bull:1983vi, Rice:1987hs}. 
Charlesworth and Charlesworth \cite{Charlesworth:1980} showed that loci where males and females differ in equilibrium allele frequency due to selection (for example, sexually antagonistic selection) should evolve complete linkage with the sex-determining locus via translocations or fusions. 
More recently, Lenormand \cite{Lenormand:2003ug} demonstrated that sex differences in allele frequencies at equilibrium are not required in order to favour reduced recombination with the sex-determining region.
%, rather that there must be a difference in selection on alleles when found in males and females. 
In fact, recombination suppression can evolve around the sex-determining region even if selection favours the same allele in both sexes as long as that allele is favoured more strongly in one sex than the other.  
In essence, these studies have demonstrated that suppressors of recombination can be favoured because they strengthen the association between the sex in which an allele is favoured and the chromosome that is present in that sex more often, e.g., between male beneficial alleles and the Y or Z and between female beneficial alleles and the X or W  \cite{Otto:2011ua}.

While differences in selection between the diploid sexes has attracted the most theoretical and empirical attention, haploid gametes/gametophytes produced by males and females typically differ in the potential for selection because competition among pollen and sperm is particularly intense \cite{Mulcahy:1996ha,Bernasconi:2004dk,JOSEPH:2004haa}. 
To the extent that pollen and sperm success reflects differences in their haploid genotypes, selection among these gametes/gametophytes is qualitatively distinct from selection among diploid males. 
That is, diploids cannot be assigned fitness values that also account for the fitness of their haploid gametes \cite{Immler:2012tl}. 
In plants, selection among haploid male gametophytes is thought to be pervasive \cite{SKOGSMYR:2002ce,Moore:2011jt,Marshall:2016fe}; in \textit{Arabidopsis}, 60-70\% of all genes are expressed during the haploid phase \cite{Borg:2009jpa}, and pollen expressed genes exhibit stronger signatures of purifying selection and positive selection \cite{Arunkumar:2013iq,Gossmann:2014dua}.
For agricultural breeding, pollen has been exposed to a variety of selection pressures \textit{in vivo} and \textit{in vitro}, including temperature \cite{Hedhly:2004iv,Clarke:2004ir}, herbicides \cite{Frascaroli:2001ee}, metals \cite{Searcy:1985vt}, water stress \cite{Ravikumar:2003uo}, and pathogens \cite{Ravikumar:2012ej}, resulting in an increased frequency of resistant genotypes among the diploid sporophytic offspring. 
In animals, expression during the haploid sperm stage is traditionally thought to be suppressed \cite{Hecht:1998hz}, although recent evidence suggests that the extent and selective importance of postmeiotic gene expression may be underestimated \cite{Zheng:2001fi,JOSEPH:2004haa,Vibranovski:2010et,Immler:2014im}.

The maintenance of polymorphism at loci that experience sex specific selection in both haploid and diploid phases was considered by Immler et al. \cite{Immler:2012tl}, demonstrating that polymorphisms can be maintained by sexually antagonistic selection or overdominance as well as by conflicting selection pressures in haploids and diploids (haploid-diploid conflict or ploidally antagonistic selection) or a combination of these selective regimes.  
In this study, we include selection during the male haploid phase (sperm or pollen competition) in models for the evolution of recombination with the sex-determining region (XY or ZW).

\section{Model Background}

Recombination evolution on sex chromosomes is usually modelled by considering a locus under selection, the sex-determining region, and another locus that modifies the recombination rate between them, where modifiers include inversions, fusions, hotspot changes, and changes to genes involved in double strand breaks and recombination repair.
%, which is typically assumed not to have any direct fitness effect. 
Thus, a general model includes three loci and the recombination rates between them, which is typically too complex to interpret without further simplifying assumptions \cite{Otto:2007tv}. 
Lenormand \cite{Lenormand:2003ug} assumed that the recombination rates between these loci are large relative to selection, such that the linkage disequilibrium between loci equilibrates on a faster timescale than changes in allele frequencies (a `quasi-linkage equilibrium' approximation). 
This analysis is most appropriate for selected loci that are far from the sex-determining region on sex chromosomes and when modifiers of recombination are weak and loosely linked (e.g., autosomal modifiers of recombination machinery). 
Secondly, Charlesworth and Charlesworth \cite{Charlesworth:1980} assumed that the selected locus is initially autosomal and then considered fusions with (or translocations to) the sex-determining region, where their analysis assumed these rearrangements became closely linked to the selected locus. 
Their model also corresponds to modifications on sex chromosomes (e.g., inversions) that change the recombination rate with the sex-determining region from a very high to a very low level. 
Finally, Otto \cite{Otto:2014jf} considered modifiers of recombination between the sex-determining region and selected loci when the linkage between them is initially very tight.

Here, we study recombination evolution in a manner akin to Charlesworth and Charlesworth \cite{Charlesworth:1980} and Otto \cite{Otto:2014jf} except that we include a period of selection among haploid male gametes/gametophytes. 
The model of Lenormand \cite{Lenormand:2003ug} is very general and allows a period of haploid selection (assuming weak linkage); he recognizes but does not discuss the potential of such sex-specific haploid selection to favour suppressed recombination on sex chromosomes. 
Here, our goal is to complete the set of recombination evolution analyses that include a period of haploid pollen/sperm competition and explicitly describe why loci that experience haploid selection can drive the evolution of reduced recombination near sex-determining regions. 
Models where haploid selected loci and the sex-determining region can become tightly linked are particularly significant because sex in an XY sex determination system is determined by the chromosome carried by the successful pollen/sperm (after haploid selection). 
Thus, strong associations between haploid selected alleles and the sex-determining region (that can build up when linkage is tight) will cause diploid sex ratios to become biased, figure 1.

\section*{Model}

%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Consider replacing $w_{i}$ with $v_{i}$ throughout.
% Consider also $w_{i}^{m}$

We consider a modifier model in which the recombination rate between a locus under selection (selected locus, \textbf{A}, with alleles $A$ and $a$) and the sex-determining region (SDR) depends on the genotype at the modifier locus (\textbf{M}, with alleles $M$ and $m$). 
In our model, male haploid gametes/gametophytes experience selection according to their genotype at the \textbf{A} locus (see table \ref{tab:fitnesstable}) before random mating with female gametes/gametophytes. 
The resulting zygotes develop as males or females depending on their genotype at the sex-determining region. 
Diploid genetic sex determination systems are either male heterogametic (females XX and males XY) or female heterogametic (females ZW and males ZZ). 
There are therefore two asymmetries in the model, the sex in which haploid selection occurs and the sex which is heterogametic. 
%and our model also describes systems in which haploid selection occurs only among female gametes, with a corresponding change of male/female labelling. 
For simplicity, we primarily describe XY sex determination with male gametophytic selection (pollen/sperm competition), although we also present results for ZW sex determination and male gametophytic selection.

After a period of selection among diploid males and females (table \ref{tab:fitnesstable}), meiosis with recombination occurs to produce haploid gamete/gametophytes. 
Because females are homozygous at the SDR (with XY sex determination), the only recombination event of consequence in females is between the \textbf{A} and \textbf{M} locus, which occurs at rate $R_{f}$. 
In males, recombination similarly occurs between the selected locus \textbf{A} and the modifier locus \textbf{M} at rate $R_{m}$. 
Recombination can also occur between the SDR and the \textbf{A} locus in males, this recombination rate is controlled by the modifier locus and is given by $r_{ij}$, where $ij$ is the genotype at the \textbf{M} locus ($MM$, $Mm$, or $mm$), allowing this recombination rate to evolve.  
Double recombination events in males occur at rate $\chi_{ij}$, such that any ordering of the loci or type of modifier (genic, inversion, fusion) can be modelled with appropriate choices of $\chi_{ij}$, $r_{ij}$, and $R_{m}$. 
We track the frequencies of $MA$, $Ma$, $mA$ and $ma$ genotypes among female eggs/ovules, male X-bearing sperm/pollen, and male Y-bearing sperm/pollen separately to allow sex-specific allele frequencies and disequilibria. 
The recursion equations describing the change in genotype frequencies after a single generation of this life cycle are provided in the Sup. Mat.

In our first analysis, we assume that selection is weak relative to the initial recombination rate ($r_{MM}$), such that allele frequency differences between males and females are small.
We then evaluate the spread of modifiers of recombination ($m$) that cause recombination rates to become very small (assuming $r_{Mm}$, $\chi_{Mm}$, and $R_{m}$ are all small). 
These modifiers could be translocations or fusions from autosomes to sex chromosomes or, if the selected locus (\textbf{A}) begins on the sex chromosome, inversions or expansions of the non-recombining region.
We assume that chromosomes are still able to disjoin regularly from their homologs during meiosis.

In our second analysis, following Otto \cite{Otto:2014jf}, we assume that the \textbf{A} locus begins at equilibrium and in tight linkage with the SDR ($r_{MM}$ and $\chi$ are on the order of a small term, $\epsilon$). 
We then consider whether any modifiers can invade that increase this recombination rate slightly (where the change in recombination rate, $r_{Mm}-r_{MM}$, is on the order of $\epsilon$). 
The recombination rate between the modifier locus and these sex chromosome loci ($R_{f}$ and $R_{m}$) is not constrained. 
This analysis focuses on the final stages of sex chromosome evolution, asking when complete recombination is favoured or not. 
%Considering sexually antagonistic selection without haploid selection, \citet{Otto:2014jf} showed that there are some conditions (particularly overdominance in males) under which a small amount of recombination between the SDR and a selected locus can be favoured.

\begin{figure}[t]     
 \includegraphics[width= 0.8 \linewidth]{Figures/sexRatioPlot.pdf} 
 \caption{
\textbf{The sex ratio at birth is biased by linkage between an XY sex-determining region (SDR) and a locus that experiences haploid selection during pollen/sperm competition (\textbf{A}).}
Here, we assume that the population is fixed for a particular modifier of recombination such that all individuals have the same recombination rate, $r$. We then allow the \textbf{A} locus to reach an equilibrium frequency and calculate the birth sex ratio.
Alleles with high fitness during pollen/sperm competition typically become associated with the Y, causing sex ratios to become male-biased (solid and dashed lines). 
However, female biased sex ratios can arise if the haploid-beneficial allele is also strongly female-beneficial, causing it to become associated with the X (dotted line). 
The parameters used in this plot are: 
solid line 
($w_{ij}^{m}=w_{ij}^{f}=w_{ij}$, $w_{aa}=1$, $w_{Aa}=0.97$, $w_{AA}=0.91$, $w_{a}=0.9$, $w_{A}=1$) 
dashed line 
($w_{ij}^{m}=w_{ij}^{f}=w_{ij}$, $w_{aa}=1$, $w_{Aa}=1.12$, $w_{AA}=1.24$, $w_{a}=0.8$, $w_{A}=1$), 
dotted line 
($w_{aa}^{m}=1$, $w_{Aa}^{m}=0.94$, $w_{AA}^{m}=0.8$, 
$w_{aa}^{f}=1$, $w_{Aa}^{f}=1.14$, $w_{AA}^{f}=1.2$ , $w_{a}=0.9$, $w_{A}=1$).
 }
 \label{fig:sexRatio} 
\end{figure}

\section*{Results}

%\subsection*{Fusions, Translocations and Other Large Effect Modifiers Bringing \textbf{A} into Tight Linkage with the SDR}

Considering a population originally fixed for the $M$ allele at the modifier locus, the frequency of the $A$ allele among X-bearing eggs/ovules, X-bearing sperm/pollen, and Y-bearing sperm/pollen is given by $p_{Xf}$, $p_{Xm}$, and $p_{Ym}$ respectively.
The spread of rare mutants that change the recombination rate can be evaluated using the leading eigenvalue, $\lambda$, of the system described by equations (A1c), (A1d), (A2c), (A2d), (A3c), and (A3d).

Complete suppressors of recombination ($r_{Mm}=0$) that are closely linked to the \textbf{A} locus ($R_{f}=R_{m}=\chi=0$) experience the strongest selective force.  
These modifiers can bring either the $A$ or the $a$ allele into tight linkage with either the X or Y chromosome. 
Thus, the invasion of these mutants can be evaluated separately and is given by $\lambda_{ij}$, where $ij$ is the haplotype at the newly linked SDR and \textbf{A} loci.

The spread of modifiers that create tight linkage between the Y and $A$ allele is given by

\begin{equation}
\lambda_{YA}=
\bar{w}_{YA}^{m}/\bar{w}^{m}
\label{eq:Yinv}
\end{equation}

\noindent
where $\bar{w}_{YA}^{m}$ is the marginal fitness of Y$A$ haplotypes and $\bar{w}^{m}$ is the mean fitness of males, see table \ref{tab:marginalFitnesses}.
Such modifiers will spread if $\lambda_{YA}>1$, which is true when $\bar{w}_{YA}^{m}>\bar{w}^{m}$.

Invasion of modifiers that create a strong linkage between the X and $a$ allele is determined by the largest solution to the characteristic polynomial \eqref{eq:Xcharpoly}.
For such modifiers, the leading eigenvalue $\lambda_{Xa}$ is greater than one if

\begin{equation}
\bar{w}_{Xa}^{mat,f}/\bar{w}^{f}+(\bar{w}_{Xa}^{mat,m}/\bar{w}^{m})(\bar{w}_{Xa}^{pat,f}/\bar{w}^{f}) >
2
\label{eq:XAinvconds}
\end{equation}

\noindent
where $\bar{w}^{f}$ is the mean fitness of females and $\bar{w}_{Xa}^{i,j}$ indicates the marginal fitness of X$a$ haplotypes when inherited from the mother ($i=mat$) or father ($i=pat$) and found in offspring of sex $j$
This condition demonstrates that the newly formed sex chromosome is able to invade if its marginal fitness is higher than average (once appropriately weighted across carriers of maternal and paternal copies). 
However, we have not yet considered constraints on the initial frequency of the $A$ allele.

Next, we will consider the case where the \textbf{A} locus is initially at an intermediate frequency maintained by selection.
Polymorphisms can be maintained by a combination of sexually antagonistic selection, ploidally antagonistic selection, and/or overdominance \cite{Immler:2012tl}.
We then write $\lambda_{YA}$ in terms of the difference in fitness between haploid genotypes ($\delta_{H}=w_{A}-w_{a}$) and the difference in equilibrium allele frequency between Y-bearing pollen/sperm and ovules/eggs ($\delta=\hat{p}_{Ym}-\hat{p}_{Xf}$) where the caret indicates an equilibrium frequency. 
%In order to solve for the initial frequencies of the $A$ allele, we assume that linkage is initially loose between the SDR and \textbf{A} locus ($r_{MM}=1/2$, where the $M$ allele is initially fixed), such that segregation in males is random and $\hat{p}_{Xm}=\hat{p}_{Ym}=\hat{p}_{m}$ where the caret indicates an equilibrium frequency. 
We can then write equation \eqref{eq:Yinv}, for the invasion of modifiers that bring the $A$ allele into tight linkage with the Y chromosome, as

\begin{equation}
\lambda_{YA}=
1+\frac{r_{MM} w_{Aa}^{m}}{\hat{p}_{Ym} \bar{w}^{m}}\left(\delta +V_{m}\delta_{H}/\bar{w}_{H}  \right)
\label{eq:YinvEquil}
\end{equation}

\noindent
where $V_{m}=\hat{p}_{Ym} (1-\hat{p}_{Ym} )$ is the variance among Y-bearing pollen/sperm and $\bar{w}_{H}=(\hat{p}_{Ym} w_{A}+(1-\hat{p}_{Ym})w_{a})$ is the mean fitness of haploid male gametes/gametophytes.
If there is no selection among haploid genotypes ($w_{A}=w_{a}$), equation \eqref{eq:YinvEquil} is equivalent to equation (A3) in Charlesworth and Charlesworth \cite{Charlesworth:1980}, in which case these tightly linked Y$A$ haplotypes invade if the $A$ allele is more common in males than females ($\hat{p}_{m}-\hat{p}_{Xf}>0$), as expected if the $A$ allele is beneficial in males with sexually antagonistic selection. 
Here we also find an additional term, demonstrating that tight linkge is also favoured when the $A$ allele is beneficial during haploid selection ($w_{A}>w_{a}$), even in the absence of frequency differences between males and females ($\hat{p}_{Ym}=\hat{p}_{Xf}$), i.e., even when there is no difference in selection between diploid males and females.

Here, in order to solve \eqref{eq:Xcharpoly} for $\lambda_{Xa}$, we will assume that linkage is initially loose between the SDR and \textbf{A} locus ($r_{MM}=1/2$), such that segregation in males is random and $\hat{p}_{Xm}=\hat{p}_{Ym}=\hat{p}_{m}$.
In the Sup. Mat we present equivalent results for cases where we do not assume that recombination is initially free ($r_{MM}<1/2$).
We will further assume that selection is weak, such that the difference in frequency between $A$ alleles in males and females ($\delta=\hat{p}_{m}-\hat{p}_{Xf}$) and the difference in fitness between haploid genotypes ($\delta_{H}=w_{A}-w_{a}$) are small ($\delta$ and $\delta_{H}$ of order $\epsilon^2$). 
Ignoring terms of order $\epsilon^3$ and higher

\begin{equation}
\lambda_{Xa} =
1+\frac{1}{3}\frac{w_{Aa}^{m}}{2 (1-\hat{p}_{m}) \bar{w}^{m}}\left( \delta +V_{m}\delta_{H} \right)
.
\label{eq:XinvEquil}
\end{equation}

\noindent
Thus, the same conditions that favour linkage between the Y and the $A$ allele, favour linkage between the X and the $a$ allele. Specifically, when the $a$ allele is more common in females ($\delta>0$, e.g., $a$ is a female beneficial allele) and when the $A$ allele is favoured during haploid competition ($\delta_{H}>0$). 
In the special case where there is no difference in selection between male and female diploids ($w_{ij}^m=w_{ij}^f=w_{ij}$), we can find an exact expression for $\lambda_{XA}$ by solving for $\hat{p}_{m}$ and $\hat{p}_{Xf}$ without assuming that selection is weak, which confirms the expectation from \eqref{eq:XinvEquil} that linkage between the X chromosome and alleles deleterious in haploid pollen/sperm is favoured by selection, see Sup. Mat.

It may not be intuitively obvious why an association with the allele that is less fit during haploid selection should be favoured. 
This result comes from the fact that the $a$ allele is initially maintained at an equilibrium frequency when loosely linked to the SDR. 
At equilibrium, selection against $a$ in haploid male gametes/gametophytes must be balanced by selection in favour of $A$ in female and/or male diploids.
However, the X chromosome is found in males less often than an autosomal or loosely linked locus and therefore experiences haploid selection less frequently. 
Thus linkage between the $a$ locus and the X is favoured because it allows the $a$ allele to experience haploid selection less often. 
Similarly, equation \eqref{eq:YinvEquil} indicates that linkage between the Y, which experiences haploid selection most often, and a haploid beneficial allele is favoured.

%Especially given the classic result of \textit{Hamilton, 1967} that, even if the $a$ allele is only favoured in male haploid gametes/gametophytes (n.b., \textit{Hamilton, 1967} considers male-specific drive, rather than haploid selection), it can spread on the X chromosome.

As with previous analyses \cite{Charlesworth:1980,Charlesworth:1999kd,Lenormand:2003ug}, we find that the strength of selection in favour of recombination modifiers is strongest on Y chromosomes because these are always found in only one sex whereas the X will sometimes be found in males and sometimes in females. 
In particular, \eqref{eq:YinvEquil} and \eqref{eq:XinvEquil} differ by a factor of $1/3$ once we account for the difference between the probability of linkage arising with the $A$ allele, $p_{m}$, or the $a$ allele, $(1-p_{m})$. 
However, mutations causing linkage with the Y (e.g., fusions) should also arise at a lower rate because there are three times as many X chromosomes as Y chromosomes in the population, such that the overall establishment rate of recombination modifiers is the same on the X and Y \cite{Pennell:2015im}.

The tight linkage case considered above is the best case scenario for generating selection in favour of recombination suppressors. 
%Charlesworth and Charlesworth \cite{Charlesworth:1980} suggest that the tight linkage case considered above may be the best case scenario for generating selection in favour of recombination suppressors. 
For a few parameters, Charlesworth and Charlesworth \cite{Charlesworth:1980} find numerically that recombination suppressors spread, but at lower rates, if $R_{m}$ and $R_{f}$ are larger. 
Here, we find analytical results by assuming the recombination rates between the \textbf{A} locus, the \textbf{M} locus, and the SDR are small ($\chi$, $R_{m}$ and $R_{f}$ or order $\epsilon^3$). 
Neglecting terms of order $\epsilon^4$ and higher, the growth rate of such mutants ($\lambda\tilde{_{ij}}$) is.

\begin{subequations}
\begin{equation}
\begin{split}
\lambda\tilde{_{YA}} \approx&
\lambda_{YA}-
\frac{(1-\hat{p}_{m})w_{Aa}^{m}R_{m}}{\bar{w}^{m}}-\chi_{Mm}
\end{split}
\label{eq:Yinvr}
\end{equation}
\begin{equation}
\begin{split}
\lambda\tilde{_{Xa}} \approx
\lambda_{Xa}
%1+\frac{1}{3}
%\frac{w_{Aa}^{m}}{2 (1-\hat{p}_{m}) \bar{w}^{m}}\left( \delta +\hat{p}_{m} (1-\hat{p}_{m} )\delta_{H} \right) \\
%&
-\frac{\hat{p}_{m}}{3}\left(\frac{2w_{Aa}^{f}R_{f}}{\bar{w}^{f}} +\frac{w_{Aa}^{m}R_{m}}{\bar{w}^{m}} \right)-\frac{\chi_{Mm}}{3}
\end{split}
\label{eq:Xinv}
\end{equation}
\label{eq:XYinv}
\end{subequations}

\noindent
where $\lambda_{ij}$ corresponds to the tight linkage results \eqref{eq:YinvEquil} and \eqref{eq:XinvEquil}.
The additional terms in \eqref{eq:XYinv} illustrate that the spread of linked haplotypes is slowed when the alternative \textbf{A} allele recombines onto the modifier and SDR background (recombination rate $R_{m}$ or $R_{f}$) or when the modifier recombines onto the opposite sex chromosome (which occurs at rate $\chi_{Mm}$ in males). 
%This confirms the expectation from Charlesworth and Charlesworth \cite{Charlesworth:1980} that selection in favour of recombination suppression is strongest when linkage is tight. 
In figure \ref{fig:fusions}, we track the spread of a recombination modifier where $R_{m}, R_{f}, \chi, r_{Mm} \neq 0$, such that both  \textbf{M} alleles and both \textbf{A} alleles can recombine onto both sex chromosomes. As predicted from equation \eqref{eq:XYinv}, a recombination suppressor increases in frequency and the X and Y chromosomes become associated with the $a$ and $A$ alleles, respectively.

\begin{figure}
 \includegraphics[width= 0.8 \linewidth]{Figures/fusion.pdf} 
 \caption{
 \textbf{A modifier that reduces the recombination rate between the \textbf{A} locus and the SDR can spread to fixation despite causing sex ratios to become biased.} Here, we iterate the recursion equations \ref{eq:recXf}, \ref{eq:recXm}, \ref{eq:recY} to track the change of genotype frequencies among X-bearing female haploids ($X_{i}^{f}$), X-bearing male haploids ($X_{i}^{m}$), and Y-bearing male haploids ($Y_{i}^{m}$), respectively. 
 Across this plot, X-bearing haploids in males and females have very similar haplotype frequencies so we plot $X_{i}^{m}$ only.
 We assume that the population initially has loose linkage between the \textbf{A} locus and the SDR ($r_{MM}=0.5$, where $M$ is initially fixed) and allow allele frequencies to reach a polymorphic equilibrium. 
 We then introduce a modifier allele $m$ that reduces the recombination rate between \textbf{A} locus and the SDR ($r_{Mm}=r_{mm}=0.01$); in generation 0, $m$ is at frequency $0.01$ and in linkage equilibrium with $M$.
 We assume that the \textbf{M} locus lies between the \textbf{A} locus and the SDR such that $\chi_{ij}=(r_{ij}-R_{m})/(1-2R_{m})$, where $R_{m}=R_{f}=0.005$.
Fitness parameters are as in the solid line in figure \ref{fig:sexRatio}. That is, there are no differences in selection between diploid sexes and selection is ploidally antagonistic with $A$ favoured by haploid selection, thus $\hat{p}_{Xf}=\hat{p}_{Xm}=\hat{p}_{Ym}$ initially, see Sup. Mat. 
Lines show the frequencies of the $A$ allele (dashed), the $a$ allele (dotted) the recombination suppression mutant, $m$ (solid).
Due to continuing recombination between the \textbf{A} locus, \textbf{M} locus, and the SDR, a particular haplotype does not fix on the Y chromosome, as is the case when $r_{ij} = 0$ (see Sup. Mat.). 
However, after recombination has evolved to a lower level, the haploid beneficial allele ($A$, dashed lines) becomes more common on the Y and less common on the X.
}
 \label{fig:fusions} 
\end{figure}

We derive equivalent results for ZW sex chromosome systems (where males are ZZ and females are ZW) with a period of haploid selection among male gametes/gametophytes.
We again consider invasion of a modifier that creates tight linkage between the \textbf{A} locus and the \textbf{M} locus ($r_{Mm}$, $\chi$, $R_{m}$ and $R_{f}$ of order $\epsilon^3$) in a population in which linkage is initially loose between the SDR and \textbf{A} locus ($r_{MM}=1/2$).
Here, we present $\lambda_{Wa}$ and $\lambda_{ZA}$ under the same assumptions as \eqref{eq:XYinv}, where the difference in frequency of the $A$ allele between males and females and the difference in fitness between haploid genotypes are small ($\delta=\hat{p}_{Zm}-\hat{p}_{Wf}$ where $\delta$ and $\delta_{H}$ are of order $\epsilon^2$), yielding

\begin{subequations}
\begin{equation}
\begin{split}
\lambda\tilde{_{Wa}} \approx&
1+\frac{r_{MM}w_{Aa}^{f}}{(1-\hat{p}_{f}) \bar{w}^{f}}\left(\delta+V_{f}\delta_{H} \right)%\\
%&
-
\frac{\hat{p}_{f}w_{Aa}^{f}R_{f}}{\bar{w}^{f}}-\chi_{Mm}
\end{split}
\end{equation}
\begin{equation}
\begin{split}
\lambda\tilde{_{ZA}} \approx&
1+\frac{1}{3}
\frac{w_{Aa}^{f}}{2 \hat{p}_{f} \bar{w}^{f}}\left( \delta +V_{f}\delta_{H} \right) \\
&-\frac{(1-\hat{p}_{f})}{3}\left(\frac{2w_{Aa}^{m}R_{m}}{\bar{w}^{m}} +\frac{w_{Aa}^{f}R_{f}}{\bar{w}^{f}} \right)-\frac{\chi_{Mm}}{3}
\end{split}
\end{equation}
\label{eq:ZWinvEquil}
\end{subequations}

\noindent
where we discard terms of $O(\epsilon^4)$. 
$\lambda_{ZA}$ and $\lambda_{Wa}$ show that, when the $A$ allele is more common in males ($\delta>0$), linkage between the male Z chromosome and the $A$ allele and linkage between the female specific W chromosome and the $a$ allele are both favoured. 
In addition, linkage is favoured between the Z and the allele favoured during haploid selection ($A$ if $\delta_{H}>0$) and between the female specific W chromosome and the allele with low haploid fitness ($a$ if $\delta_{H}>0$).

%After this modifier is established, the \textbf{A} locus is effectively sex-linked and the Y haplotype becomes fixed for the $a$ allele ($p_{Ym}=0$ is stable), as explored in the next section along with the X-bearing haplotypes.

Finally, we evaluate the evolution of recombination during the final stages of sex chromosome evolution by considering the evolution of small amounts of recombination around the sex-determining region. 
Considering diploid selection alone, Otto \cite{Otto:2014jf} demonstrated that a small amount of recombination can be maintained by selection. 
Due to the asymmetrical inheritance pattern of sex chromosomes, an allele that is fixed on a Y chromosome (e.g., the $A$ allele) can also be favoured on the X during selection in females, even if the X is fixed for the alternative allele (e.g., the $a$ allele). 
With diploid selection only, this requires that the X-specific allele ($a$) is favoured during selection on the X in males, which only occurs when selection in males is overdominant.
Assuming, for example, that the Y is originally fixed for the $A$ allele, recombination with the sex-determining region produces X$A$ and Y$a$ haplotypes in pollen or sperm. 
Although Y$a$ haplotypes always have low fitness, X$A$ haplotypes can experience a short term advantage because they next experience selection in females and selection in females can favour the $A$ allele.
For a subset of parameters, the cost of producing low fitness sons can be outweighed by this transient fitness advantage in daughters, allowing modifiers of recombination that increase recombination to invade if sufficiently loosely linked to the sex-determining region, for further discussion see \cite{Otto:2014jf}.
Here, we perform a similar analysis in which there is also a period of selection among male haploids.

We find that mutants that increase the recombination rate are not typically favoured by selection. 
In particular, when the modifier locus is tightly linked to the \textbf{A} locus ($R_{f} \approx 0$), only mutants that suppress recombination can spread.
In addition, if the allele that is fixed on the Y (e.g., $A$) is favoured by selection on the X in males ($w_{AA}^{m}>w_{Aa}^{m}$) but not during selection among haploids ($w_{a}>w_{A}$) increased recombination is never favoured. 
However, if these conditions are not met there are some parameters under which increased recombination is favoured by selection (figure \ref{fig:combined}).

Assuming that the $A$ allele is initially fixed on the Y, increased recombination is favoured when the cost of producing Y$a$ pollen/sperm is be outweighed by selection in favour of X$A$ pollen/sperm.
%One might not expect selection to favour X$A$ haplotypes because an $A$ allele on an average X background should either have the same fitness as an $a$ allele (when a polymorphism is maintained on the X) or lower fitness (when $A$ is fixed on the X). 
%However, an X$A$ haplotype created by recombination in males is found in a male haploid (pollen or sperm), not on an average X background (which is weighted across X-bearing male sperm/pollen and female eggs/ovules). 
If $R_{f}$ and $R_{m}$ are small, the modifier remains linked to the haplotypes it creates (X$A$ and Y$a$), which always leads to a net long term disadvantage. 
When $R_{f}$ and $R_{m}$ are sufficiently large (e.g., autosomal modifiers), a modifier that increases recombination can gain a short term benefit from being found on X$A$ pollen/sperm before recombining onto a different background. 
X$A$ pollen or sperm can have a short term advantage if they have high fitness during haploid competition and/or high fitness in female diploids (all X-bearing pollen/sperm will form female diploids). 
Increased recombination is only consistent with X$A$ being favoured during haploid selection and/or selection in females, see Sup. Mat. 
For most parameters with or without haploid selection, X$A$ pollen/sperm either have no fitness advantage or have a transient fitness advantage that is outweighed by the cost of producing low-fitness Y$a$ pollen/sperm. 
Thus, increased recombination does not usually evolve. 
However, with selection among haploids, it is possible for a small amount of recombination to be favoured under a less restrictive set of selective regimes in diploids, including overdominance, sexually antagonistic selection and ploidally antagonistic selection.

\section*{Discussion}

Even in predominantly diploid organisms such as animals and angiosperms, there is considerable potential for selection among haploid male gametes (sperm/pollen). 
Here, we demonstrate that linkage between the diploid sex-determining region (XY or ZW) and a locus that experiences haploid selection is typically favoured by selection. 
Thus, along with selective differences between diploid sexes, selection among haploids could be a potent driver of recombination suppression on sex chromosomes.

%Following \citet{Charlesworth:1980}, we considered extreme recombination modifiers that bring an initially loosely linked polymorphic locus into tight linkage with the sex-determining region. 
%We find that alleles favoured during haploid selection should become linked to the male sex chromosome (Y or Z), which experiences haploid selection most often, and that alleles disfavoured during haploid selection should become linked to the Z or W chromosome, which experiences haploid selection least often. 
%Indeed, the analysis of \citet{Lenormand:2003ug}, which assumes recombination rates are large relative to selection and modified by a small amount, also shows that reduced recombination is favoured when haploid selection occurs in one sex, even for loci not maintained at a polymorphic equilibrium by selection, (e.g., during the spread of beneficial mutations).

In ZW sex determination systems, the sex ratio among diploids is unaffected by selection among male haploids. 
However, in XY sex determination systems, the number of males and females in each generation depends on the frequency of X and Y gametes after haploid selection. 
Despite this, we find that selection on recombination modifiers is not primarily driven by balancing the sex ratio of diploids.
In fact, the evolution of recombination suppression should lead to Y-bearing gametes/gametophytes that have high fitness during haploid selection.
Thus, we predict that sex ratios at birth can become male biased in the early stages of sex chromosome evolution.

Biased flowering sex ratios, especially male-biased sex ratios, are common among dioecious plants \cite{Field:2013cc}.
However, in \textit{Rumex}, more intense pollen competition appears to result in more female biased sex-ratios among the progeny \cite{Conn:1981uw,Stehlik:2006to,Field:2012fd}. 
This phenomenon may reflect the accumulation of deleterious mutations on the Y-chromosome following recombination suppression \cite{Lloyd:1974tz,Stehlik:2005ul}, as suggested by the prevalence of female sex ratio bias in species with heteromorphic rather than homomorphic sex chromosomes \cite{Field:2013cc}. 
Thus, the net effect of experimentally manipulating the intensity of haploid selection may depend on the stage of sex chromosome degeneration, as well as the alleles associated with the Y. 
The increasing availability of sex-linked markers should allow sexes to be identified before reproductive maturity in plants, thus allowing changes in the sex ratio to be directly evaluated across haploid and diploid phases in species with differing degrees of Y chromosome degeneration.

The emergence of both haploid expression profiles \cite{JOSEPH:2004haa,Borg:2009jpa} and a larger number of sex chromosome systems \cite{Ming:2011iy,Charlesworth:2013,Charlesworth:2015dj,Bachtrog:2014bx,Vicoso:2015hf} provides an excellent opportunity to evaluate whether sex chromosomes are enriched for genes selected during the haploid phase, as predicted by our models. 
If possible, a stronger signal of association with sex-determining regions should occur among loci explicitly shown to exhibit variation in haploid competitive ability \cite{Travers:2001vx} or loci where mutants affect fitness in both haploid and diploid phases \cite{Muralla:2011ks}. 
Finally, we predict that the strength of haploid competition partly determines whether and how fast recombination suppression evolves.
Evaluating a related hypothesis, Lenormand and Duthiel \cite{Lenormand:2005vb} correlate heterochiasmy (differences in autosomal recombination between sexes) with the degree of sex specific haploid selection, using outcrossing rate as a proxy for male haploid selection. 
We would predict a similar pattern for recombination suppression around sex-determining regions. 
Estimates of pollen limitation could also be used as proxy for the intensity of haploid competition \cite{Vamosi:2006hi,Friedman:2009eg}.

As in a previous analysis by Otto \cite{Otto:2014jf}, we find that a small amount of recombination can be selectively maintained around the sex-determining region. 
Otto \cite{Otto:2014jf} considered only diploid selection and found that overdominance in males was required for recombination to be selectively maintained. 
Here, we include a period of selection among haploids and find that increased recombination can be favoured with various forms of selection among diploids, including sexually antagonistic selection and ploidally antagonistic selection (figure \ref{fig:combined}), as long as the allele fixed on the Y is favoured in haploids and/or females. 
However, increased recombination is never favoured when modifiers of recombination act locally, such that they are also closely linked to the sex-determining region. 
Therefore, while these dynamics may influence the maintenance of small amounts of recombination around sex-determining regions when polymorphisms with the right form of selection arise (e.g., within the coloured regions in figure \ref{fig:combined}), suppressed recombination will be favoured in most circumstances.

%In our models, and in most models for the evolution of recombination, modifiers of recombination are assumed not to have direct effects on fitness. 
%However, fusions and other chromosomal rearrangements can alter the number and position (acrocentric or metacentric) of active centromeres, which can lead to biased segregation during meiosis \cite{Wyttenbach:1998uj,PardoManueldeVillena:2001gn,PardoManueldeVillena:2001ti,Yoshida:2012cz}. 
%This meiotic drive either creates direct selection for or against these extreme recombination modifiers, which could overwhelm the selective consequences of recombination modification. 
%This is one reason why the rate of fusions with sex chromosomes may not primarily reflect the benefits of reduced recombination \cite{Pennell:2015im}.

%Mention: UV sex chromosomes

%In addition to loci with polymorphisms maintained by sexually antagonistic selection, loci with polymorphisms maintained by heterozygote advantage have been shown to evolve linkage with the sex-determining region if there is inbreeding \cite{Charlesworth:1999kd}. 
%Because the heterogametic sex is heterozygous at the sex-determining region (XY or ZW), linkage with this region preserves heterozygosity in the face of inbreeding.

%Also Grossen study, "recombination in sex reversed individuals evolves towards zero in the presence of sexually antagonistic selection but towards a positive value when deleterious mutations were present as well. Given that the fitness effects of deleterious mutations were multiplicative and equal in the two sexes, deterministic models would predict no change in recombination, leading Grossen et al. (2012) to conclude that stochastic effects were responsible for the maintenance of recombination in their simulations (i.e. Muller's Ratchet and related Hill-Robertson effects)."

%In addition to the evolution of recombination suppression on sex chromosomes, sexually antagonistic selection has been implicated in the transition of genetic sex-determining systems between chromosomes. 
%In particular, a new male determining locus can spread if it arises in linkage with a locus experiencing sexually antagonistic selection \cite{vanDoorn:2007eu}. 
%Our results suggest a promising mechanism for future investigation, in which new male determination loci can arise close to loci experiencing haploid selection.

Meiotic drive is not exactly equivalent to a period of haploid selection. In particular, meiotic drive can only occur in heterozygotes and often involves an interaction with a separate susceptible/resistant locus \cite{Bull:1983vi}.
However, meiotic drive is also usually sex specific, either acting during spermatogenesis in males or polar body formation in females. 
In this respect, we expect loci experiencing meiotic drive to behave similarly to those experiencing haploid selection. 
In particular, we predict that selection should favour linkage between alleles favoured by drive and the sex chromosome for the sex in which drive occurs (e.g., with the Y or Z when drive occurs during spermatogenesis). 
Despite theoretical interest in related topics \cite{Feldman:1989gm,Haig:2010em,Brandvain:2012hh,Patten:2014tn,Rydzewski:2016csa}, such as the evolution of recombination between an X chromosome that experiences drive and another selected locus \cite{Feldman:1989gm,Rydzewski:2016csa}, this process has yet to be explicitly modelled and is worthy of future exploration. 
%Although it should be noted that meiotic drivers may be more common on sex chromosomes for other reasons \cite{Hurst:1991uh}, for example, because meiotic drive often occurs via interactions with a susceptible allele on the homologous chromosome, divergence between sex chromosomes may provide a particularly large source of suitable targets for drive \cite{Burt:2006}. 
%Finally, Ubeda et al. \cite{Ubeda:2015fx} demonstrate that new male determining alleles can be favoured when linked to a locus that experiences drive in males, transitioning between environmental and genetic sex determination systems. Again, we would also expect new genetic sex determination loci to be favoured in systems with environmental sex determination if they arise near loci that experience selection in male gametophytes. 
%Overall, these results suggest that we can expand our view of sex chromosome evolution to incorporate sex specific haploid selection and meiotic drive as well as sex specific selection in diploids.

Overall, as well as providing several predictions, our model offers a new perspective on drivers of sex chromosome evolution. 
Traditionally, sex differences in selection are thought to provide the raw material driving recombination suppression on sex chromosomes.
%A traditional view would conclude that the strength of sex differences in selection can determine how fast recombination suppression evolves on sex chromosomes. 
However, even where diploid sexes exhibit very few morphological or ecological differences, the selective environment of their haploid gametes may be very divergent.
We have shown that this condition - differences in fitness among pollen or sperm - should also favour suppressed recombination. 
Consequently, our view of sex chromosome evolution is expanded to incorporate the degree of sex specific selection in haploids along with that in diploids.

%Note on ploidally-antagonistic selection, drop? (agricultural breeding moved to intro.)
%We find that recombination suppression can evolve even when there is no difference in selection between diploid sexes, in which case polymorphisms can be maintained by overdominance or ploidally-antagonistic selection (Appendix 1).
%Intralocus haploid-diploid conflict requires that genes under selection in the haploid phase are also selected in the diploid phase. 
%Of the genes expressed during male gametophyte (pollen) development, approximately 90\% are also expressed in the diploid sporophytic stage \cite{Borg:2009jpa}.
%For agricultural breeding, pollen has been exposed to a variety of selection pressures in vivo and in vitro, including temperature \cite{Hedhly:2004iv,Clarke:2004ir}, herbicides \cite{Frascaroli:2001ee}, metals \cite{Searcy:1985vt}, water stress \cite{Ravikumar:2003uo}, and pathogens \cite{Ravikumar:2012ej}, resulting in an increased frequency of resistant genotypes among the diploid sporophytic offspring, such that systematic changes in these environments between haploid and diploid stages could lead to antagonistic selection. 
%In a common environment, \citet{Travers:2001vx} show that an allele at the phophoglucoisomerase locus in \textit{Clarkia unguiculata} is favoured during pollen competition but causes reduced seed production by diploid sporophytes. 
%While selection may most often act in the same direction in both phases, we focus on loci that experience antagonism because alleles can be maintained at high frequencies and thus account for substantial genetic variation that is sustained for long time periods.

\subsection*{Acknowledgements}

Funding for this project was provided by the University of British Columbia and by a Natural Sciences and Engineering Research Council of Canada grant to SPO.

%\bibliographystyle{pnas}
%\bibliography{Sex_Chromosomes.bib}

\input{bibliography_manual.tex}

\end{article}

\end{document}

### 2016-08-30 PNAS_Style/SupMat.tex
playing with indices

%\documentclass[12pt]{article}
\documentclass{pnastwo}

%\def\E {\mbox{E}}
%\def\ex {\mbox{e}}
%\def\partiald {\mbox{d}}
%\def\V {\mbox{Var}}
%\def\C {\mbox{Cov}}
%\def\se {\sigma_{\eps}}
%\def\half {\textstyle\frac{1}{2}}
%\def\quart {\textstyle\frac{1}{4}}
%\def\eight {\textstyle\frac{1}{8}}
%\def\sqrttwo {\textstyle\frac{1}{\sqrt{2}}}
%\newcommand{\eps}{\mbox{\large $\varepsilon$}}
%\newcommand{\ah}{\makebox[0pt][l]{$^a$}}
%\renewcommand{\baselinestretch}{1.325}
%\parskip 6pt plus 3pt minus 2pt
%%\special{papersize=8.25in,11.5in}
%\pagestyle{plain}
%\oddsidemargin 0pt
%\evensidemargin 0pt
%\textwidth 6.5in
%\textheight 9.1in

% Including line numbers
%\usepackage{lineno}

% Including pdf figures
\usepackage{graphicx}

% Including math features
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{graphicx}

% Bibliographies
\usepackage[]{natbib}
\bibpunct{(}{)}{,}{a}{}{;}

% Including male & female symbols
\usepackage{wasysym}

\usepackage{xr}
\externaldocument{SexChromosomes_PNAS}

%\usepackage{cite}
%\usepackage[round]{natbib}
%\usepackage{/Users/otto/Library/TeXmenu/amnat} 
%\bibliographystyle{cbe}

\usepackage{color} 
\newcommand{\red}[1]{\textcolor{red}{#1}}
\newcommand{\green}[1]{\textcolor{green}{#1}}
\newcommand{\blue}[1]{\textcolor{blue}{#1}}

% Formats equations as (#)
% \renewcommand{\eqref}[1]{\textup{{\normalfont(\ref{#1}}\normalfont)}}

% Formats equations as bold #
\renewcommand{\eqref}[1]{\textup{\bf{\ref{#1}}}}

%%% font setup in order to make the article printable
%\usepackage{mathptmx}
%\usepackage{helvet}
%\renewcommand\bibfont{\fontsize{6pt}{9pt}\bfseries\sffamily}
%\renewcommand{\bibitfont}{\bibfont\slshape}
%\renewcommand{\bibbffont}{\bibfont}
%%%

\renewcommand{\bibitfont}{\fontsize{6pt}{9pt} \bibfont\slshape}

%------------------------------------------------
% DO NOT EDIT THIS SECTION
%------------------------------------------------

%% For PNAS Only:
\url{www.pnas.org/cgi/doi/10.1073/pnas.0709640104}
\copyrightyear{2008}
\issuedate{Issue Date}
\volume{Volume}
\issuenumber{Issue Number}

%----------------------------------------------------------------------------------------

\begin{document}

\markright{Recombination evolution \hspace{2.3in} Scott \& Otto}
\section{Recursion Equations}
\label{app:recurs}
% Starts equation numbers from 0 again and adds S to tag
\setcounter{equation}{0}
\renewcommand{\theequation}{S.\arabic{equation}}
\renewcommand{\thefigure}{S.\arabic{figure}}
\renewcommand{\thetable}{S.\arabic{table}}

In each generation we census the genotype frequencies in male and female haploids before haploid selection, e.g., sperm/pollen and eggs/ovules. Before haploid selection, the frequency of X-bearing male and female haploids are given by $X_{i}^{m}$ and $X_{i}^{f}$ and the frequency of Y-bearing haploids is given by $Y_{i}^{m}$ where the index $i$ specifies genotypes $MA$, $Ma$, $mA$, and $ma$. 
Selection then occurs among male haploids according to the \textbf{A} locus allele, $k$, carried by individuals with genotype $i$.
Assuming that the fraction of X-bearing haploids produced by males is $f$, the genotype frequencies after haploid selection are $X_{i}^{m,s}=f w_{k}X_{i}^{m}/\bar{w}_{H}$ and $Y_{i}^{m,s}=(1-f) w_{k}Y_{i}^{m}/\bar{w}_{H}$, where $\bar{w}_{H}=\sum_{i=1}^{4}f w_{k}X_{i}^{m}+(1-f)w_{k}Y_{i}^{m}$ is the mean fitness of male haploids. Random mating then occurs between gametes to produce diploid females with genotype $ij$ at frequency $x_{ij}=X_{i}^{f}X_{j}^{m,s}$ and diploid males at frequency $y_{ij}=X_{i}^{f}Y_{j}^{m,s}$. 
In females, individuals with genotype $ij$ are equivalent to those with genotype $ji$. 
For simplicity we denote the frequency of genotype $ij$ in females to the average of these frequencies, $x_{ij}=(X_{i}^{f}X_{j}^{m,s}+X_{j}^{f}X_{i}^{m,s})/2$.
Note that the sex ratio before diploid selection depends both on the production of X-bearing haploids by fathers ($f$) and on haploid selection ($w_{k}$).
However, $f$ does not enter into any results, indicating that the main force driving recombination evolution is not to balance the current sex ratio.

\begin{table}[ht]
\centering
\smallskip
\caption{Fitness of different genotypes.}
\begin{tabular}{l c c c c c}
\hline\hline
  Genotype & $A$ & $a$ & $AA$ & $Aa$ & $aa$ \\ [0.5ex] \hline
  Fitness in males & $w_{A}$ & $w_{a}$ & $w_{AA}^{m}$ & $w_{Aa}^{m}$ & $w_{aa}^{m}$ \\
  Fitness in females & 1 & 1 & $w_{AA}^{f}$ & $w_{Aa}^{f}$ & $w_{aa}^{f}$\\
  \hline \hline
  \label{tab:fitnesstable}
 \end{tabular}
\end{table}

\begin{table}[ht]
\centering
\smallskip
\caption{Marginal fitnesses of Y$\mathbf{A}$ and X$\mathbf{a}$ haplotypes}
\begin{tabular}{l l}
\hline\hline
  $\bar{w}_{YA}^{m}$ & $=(w_{A}(p_{Xf}w_{AA}^f+(1-p_{Xf}) w_{Aa}^f))$ \\
  $\bar{w}_{Xa}^{mat,m}$ & $=p_{Ym}w_{A}w_{Aa}^m+(1-p_{Ym})w_{a}w_{aa}^m$ \\
  $\bar{w}_{Xa}^{pat,f}$ & $=p_{Xf}w_{a}w_{Aa}^f+(1-p_{Xf})w_{a}w_{aa}^f$ \\
  $\bar{w}_{Xa}^{mat,f}$ & $=p_{Xm}w_{A}w_{Aa}^f+(1-p_{Xm})w_{a}w_{aa}^f$\\
  \hline \hline
  \label{tab:marginalFitnesses}
 \end{tabular}
\end{table}

Selection among diploids then occurs according to the diploid genotype at the \textbf{A} locus, $k$, for an individual of type $ij$ (see Table \ref{tab:fitnesstable}). The diploid frequencies after selection are given by $x_{ij}^{s}=w_{k}^{f} x_{ij}/\bar{w}^{f}$ in females and $y_{ij}^{s}=w_{k}^{m}  y_{ij}/\bar{w}^{m}$ in males, where $\bar{w}^{f}= \sum_{i=1}^{4}\sum_{j=1}^{4}w_{k}^{f}x_{ij}$ and $\bar{w}^{m}= \sum_{i=1}^{4}\sum_{j=1}^{4}w_{k}^{m}y_{ij}$ are the mean fitnesses of females and males, respectively. 
Finally, these diploids undergo meiosis to produce the next generation. The haplotype frequencies in the next generation of eggs/ovules is given by:

\begin{subequations}
\begin{equation}
X_{MA}^{f'}=\left( \sum_{j=1}^{4} x_{1j}^{s} \right) - R_{f}(x_{14}^{s}-x_{23}^{s})
\end{equation}
\begin{equation}
X_{Ma}^{f'}=\left( \sum_{j=1}^{4} x_{2j}^{s} \right) + R_{f}(x_{14}^{s}-x_{23}^{s})
\end{equation}
\begin{equation}
X_{mA}^{f'}=\left( \sum_{j=1}^{4} x_{3j}^{s} \right) + R_{f}(x_{14}^{s}-x_{23}^{s})
\end{equation}
\begin{equation}
X_{ma}^{f'}=\left( \sum_{j=1}^{4} x_{4j}^{s} \right) - R_{f}(x_{14}^{s}-x_{23}^{s})
\end{equation}
\label{eq:recXf}
\end{subequations}

\noindent
which only involve the recombination rate between the \textbf{A} locus and the \textbf{M} locus in females ($R_{f}$). 
In males, recombination between the SDR and the \textbf{A} locus or the \textbf{M} also affects the frequencies of haplotypes produced. 
The frequency of haplotypes among X-bearing sperm/pollen (before haploid selection) in the next generation are given by

\begin{subequations}
\begin{equation}
\begin{split}
X_{MA}^{m'}=&\left( \sum_{j=1}^{4} y_{1j}^{s} \right) - r_{MM}(y_{12}^{s}-y_{21}^{s})\\
&- (R_{m}+r_{Mm}-2\chi)(y_{13}^{s}-y_{31}^{s})-(R_{m}+r_{Mm}-\chi)y_{14}^{s}\\
&+(r_{Mm}-\chi)y_{41}^{s}+\chi \ y_{23}^{s}+(r_{Mm}-\chi)y_{32}^{s}
\end{split}
\end{equation}
%
\begin{equation}
\begin{split}
X_{Ma}^{m'}=&\left( \sum_{j=1}^{4} y_{2j}^{s} \right) - r_{MM}(y_{21}^{s}-y_{12}^{s})\\
&- (R_{m}+r_{Mm}-2\chi)(y_{24}^{s}-y_{42}^{s})-(R_{m}+r_{Mm}-\chi)y_{23}^{s}\\
&+(r_{Mm}-\chi)y_{32}^{s}+\chi \ y_{14}^{s}+(r_{Mm}-\chi)y_{41}^{s}
\end{split}
\end{equation}
%
\begin{equation}
\begin{split}
X_{mA}^{m'}=&\left( \sum_{j=1}^{4} y_{3j}^{s} \right) - r_{mm}(y_{34}^{s}-y_{43}^{s})\\
&- (R_{m}+r_{Mm}-2\chi)(y_{31}^{s}-y_{13}^{s})-(R_{m}+r_{Mm}-\chi)y_{32}^{s}\\
&+(r_{Mm}-\chi)y_{23}^{s}+\chi \ y_{41}^{s}+(r_{Mm}-\chi)y_{14}^{s}
\end{split}
\end{equation}
%
\begin{equation}
\begin{split}
X_{ma}^{m'}=&\left( \sum_{j=1}^{4} y_{4j}^{s} \right) - r_{mm}(y_{43}^{s}-y_{34}^{s})\\
&- (R_{m}+r_{Mm}-2\chi)(y_{42}^{s}-y_{24}^{s})-(R_{m}+r_{Mm}-\chi)y_{41}^{s}\\
&+(r_{Mm}-\chi)y_{14}^{s}+\chi \ y_{32}^{s}+(r_{Mm}-\chi)y_{23}^{s}
\end{split}
\end{equation}
\label{eq:recXm}
\end{subequations}

\noindent
and the frequencies of Y-bearing sperm/pollen haplotypes (before haploid selection) are given by

\begin{subequations}
\begin{equation}
\begin{split}
Y_{MA}^{m'}=&\left( \sum_{j=1}^{4} y_{1j}^{s} \right) - r_{MM}(y_{21}^{s}-y_{12}^{s})\\
&- (R_{m}+r_{Mm}-2\chi)(y_{31}^{s}-y_{13}^{s})-(R_{m}+r_{Mm}-\chi)y_{41}^{s}\\
&+(r_{Mm}-\chi)y_{14}^{s}+\chi \ y_{32}^{s}+(r_{Mm}-\chi)y_{23}^{s}
\end{split}
\end{equation}
%
\begin{equation}
\begin{split}
Y_{Ma}^{m'}=&\left( \sum_{j=1}^{4} y_{2j}^{s} \right) - r_{MM}(y_{12}^{s}-y_{21}^{s})\\
&- (R_{m}+r_{Mm}-2\chi)(y_{42}^{s}-y_{24}^{s})-(R_{m}+r_{Mm}-\chi)y_{32}^{s}\\
&+(r_{Mm}-\chi)y_{23}^{s}+\chi \ y_{41}^{s}+(r_{Mm}-\chi)y_{14}^{s}
\end{split}
\end{equation}
%
\begin{equation}
\begin{split}
Y_{mA}^{m'}=&\left( \sum_{j=1}^{4} y_{3j}^{s} \right) - r_{mm}(y_{43}^{s}-y_{34}^{s})\\
&- (R_{m}+r_{Mm}-2\chi)(y_{13}^{s}-y_{31}^{s})-(R_{m}+r_{Mm}-\chi)y_{23}^{s}\\
&+(r_{Mm}-\chi)y_{32}^{s}+\chi \ y_{14}^{s}+(r_{Mm}-\chi)y_{41}^{s}
\end{split}
\end{equation}
%
\begin{equation}
\begin{split}
Y_{ma}^{m'}=&\left( \sum_{j=1}^{4} y_{4j}^{s} \right) - r_{mm}(y_{34}^{s}-y_{43}^{s})\\
&- (R_{m}+r_{Mm}-2\chi)(y_{24}^{s}-y_{42}^{s})-(R_{m}+r_{Mm}-\chi)y_{14}^{s}\\
&+(r_{Mm}-\chi)y_{41}^{s}+\chi \ y_{23}^{s}+(r_{Mm}-\chi)y_{32}^{s}
\end{split}
\end{equation}
\label{eq:recY}
\end{subequations}

\section{Invasion of recombination modifiers}

%In the main text, we consider selected loci that are initially loosely linked to the SDR such that $\hat{p}_{Xm}=\hat{p}_{Ym}$. 
Invasion of modifiers that create a strong linkage between the X and $a$ allele is determined by the largest solution to the characteristic polynomial

\begin{equation}
\begin{split}
{\lambda_{Xa}}^2- \lambda_{Xa} \bar{w}_{Xa}^{mat,f} /\bar{w}^{f}- (\bar{w}_{Xa}^{pat,f}/\bar{w}^{f})(\bar{w}_{Xa}^{mat,m}/\bar{w}^{m})=0
.
\end{split}
\label{eq:Xcharpoly}
\end{equation}

\noindent
This can be solved for $\lambda_{Xa}$ if we assume that the selected locus is initially loosely linked to the SDR ($r_{MM}$) and that there are no sex differences in selection ($w_{ij}^m=w_{ij}^f=w_{ij}$). 
The equilibrium frequency of the $A$ allele when maintained at a polymorphic equilibrium by selection is then

\begin{equation}
\hat{p}_{Xm}=\hat{p}_{Ym}=\hat{p}_{Xf}=
\frac{2 w_{a} w_{aa}- w_{Aa}(w_{A}+w_{a})}{2\left(w_{A}(w_{AA}-w_{Aa})+w_{a}(w_{aa}-w_{Aa})\right)}
.
\label{eq:PASpolyeq}
\end{equation}

\noindent
This equilibrium is valid and stable when

\begin{equation}
\begin{split}
w_{Aa}(w_{A}+w_{a})&>2w_{A} w_{AA} \text{ and}\\
w_{Aa}(w_{A}+w_{a})&>2w_{a} w_{aa}
.
\end{split}
\label{eq:PASstability}
\end{equation}

\noindent
Therefore, a polymorphism can be maintained either if there is heterozygote advantage in diploids ($w_{Aa}>w_{aa}$ and $w_{Aa}>w_{AA}$) or if there is antagonistic selection between haploids and diploids (e.g., $w_{A}>w_{a}$ and $w_{aa}>w_{Aa}>w_{AA}$) or a combination of both \citep{Immler:2012tl}.

After this equilibrium is reached, the invasion of a modifier that brings the $A$ allele into linkage with the Y is given by

\begin{equation}
\lambda_{YA}=
1+
\frac{(w_{A}-w_{a})w_{Aa}(w_{A}+w_{a})(w_{Aa}(w_{A}+w_{a})-2w_{AA}w_{A})}
{(w_{A}+w_{a})({w_{Aa}}^2(w_{A}+w_{a})^2-4w_{A}w_{AA}w_{a}w_{aa})}
,
\label{eq:YinvPAS}
\end{equation}

\noindent
where $\lambda_{YA}>1$ indicates that the modifier increases in frequency. 
Given that a polymorphism at the \textbf{A} locus is initially stable (conditions \ref{eq:PASstability} are met) the sign of $\lambda_{YA}-1$ depends on the sign of $w_{A}-w_{a}$. 
That is, modifiers that bring the allele favoured in haploids (e.g., $A$ when $w_{A}>w_{a}$) into tight linkage with the Y will spread.

Similarly, condition \eqref{eq:XAinvconds} for the invasion of modifiers that bring the $a$ allele into tight linkage with the X chromosome is satisfied if

\begin{equation}
\frac{(w_{A}-w_{a})w_{Aa}(w_{A}+w_{a})(w_{Aa}(w_{A}+w_{a})-2w_{AA}w_{A})}
{2(w_{A}+w_{a})({w_{Aa}}(w_{A}+w_{a})-w_{A}w_{AA}-w_{a}w_{aa})}>0,
\label{eq:XinvcondsPAS}
\end{equation}

\noindent
which requires $w_{A}>w_{a}$, given that conditions \eqref{eq:PASstability} are met. These results indicate that recombination modifiers invade if they bring the X into tight linkage with the allele that is less fit during haploid selection, even without the weak selection assumptions in equation \eqref{eq:XinvEquil} and without sex differences in selection in the diploid phase.

In the main text and above, we consider the invasion of recombination suppressors that bring the $a$ allele into tight linkage with the X when the \textbf{A} locus is initially loosely linked to the SDR ($r_{MM}=1/2$) such that $\hat{p}_{Xm}=\hat{p}_{Ym}$. 
Here, we consider cases where $r_{MM}<1/2$ and define the difference in the frequency of the $A$ allele between X- and Y-bearing pollen/sperm as $\delta_{XY}=\hat{p}_{Ym}-\hat{p}_{Xm}$. 
We assume that selection is weak relative to recombination such that $\delta$, $\delta_{XY}$, and $\delta_{H}$ are all small (of order $\epsilon^2$). 
Invasion is then given by

\begin{equation}
\lambda_{Xa}' =
\lambda_{Xa}\left(1-(1-2\ r_{MM})(3+2 w_{Aa}^{f}/\bar{w}^{f})\right)
+\frac{w_{Aa}^{f}\delta_{XY}}{3\bar{w}^{f}}
\label{eq:XaprimeEq}
\end{equation}

\noindent
Under the conditions where $\lambda_{Xa}>1$, we would expect that the $a$ allele is associated with the X such that $\delta_{XY}<0$. 
Thus, \eqref{eq:XaprimeEq} indicates that selection in favour of modifiers that suppress recombination is less strong when $r_{MM}<1/2$ ($\lambda_{Xa}'<\lambda_{Xa}$), in which case intralocus conflicts are initially partially resolved by reduced recombination.

%\newpage

\section{Invasion of Modifiers That Increase Recombination from an Initially Low Level}

%Here, we will assume that the selected locus, \textbf{A}, is between the SDR and modifier locus, \textbf{M} such that $\chi=r_{ij} R_{M}$ without interference. 
We consider a population in which linkage is tight between the \textbf{A} locus and the SDR ($r_{MM}$ is of order $\epsilon$, where the $M$ allele is initially fixed). 
%and then evaluate the spread of a rare mutant at the modifier locus that increases the recombination between \textbf{A} and the SDR by a small amount ($r_{Mm}-r_{MM}$ is of order $epsilon$). 
Recombination has no effect if the \textbf{A} locus is fixed for one allele, we therefore focus on the five equilibria that maintain both $A$ and $a$ alleles, of which four are given to leading order by:

\begin{equation*}
\begin{split}
(A)\ \ \ &\hat{p}_{Ym}=0,\ \hat{p}_{Xf}=\frac{\alpha}{\alpha+\beta},\  \hat{p}_{Xm}=\frac{w_{Aa}^{m} \alpha}{w_{Aa}^{m}\alpha+w_{aa}^{m}\beta}\\
(A')\ \ \ &\hat{p}_{Ym}=1,\ \hat{p}_{Xf}=1-\frac{\alpha'}{\alpha'+\beta'},\  \hat{p}_{Xm}=1-\frac{w_{Aa}^{m} \alpha'}{w_{Aa}^{m}\alpha'+w_{aa}^{m}\beta'}\\
(B)\ \ \ &\hat{p}_{Ym}=0,\ \hat{p}_{Xf}=1,\ \hat{p}_{Xm}=1\\
(B')\ \ \ &\hat{p}_{Ym}=1,\ \hat{p}_{Xf}=0,\ \hat{p}_{Xm}=0\\
\end{split}
\end{equation*}
\begin{equation*}
\begin{split}
\alpha=&w_{Aa}^{f} (w_{aa}^{m}w_{a}+w_{Aa}^{m}w_{A})-2w_{aa}^{f}w_{aa}^{m}w_{a}\\
\alpha '=&w_{Aa}^{f} (w_{AA}^{m}w_{A}+w_{Aa}^{m}w_{a})-2w_{AA}^{f}w_{AA}^{m}w_{A}\\
\beta=&w_{Aa}^{f} (w_{aa}^{m}w_{a}+w_{Aa}^{m}w_{A})-2w_{AA}^{f}w_{Aa}^{m}w_{A}\\
\beta '=&w_{Aa}^{f} (w_{AA}^{m}w_{A}+w_{Aa}^{m}w_{a})-2w_{aa}^{f}w_{Aa}^{m}w_{a}\\
\end{split}
\end{equation*}

\noindent
A fifth equilibrium $(C)$ also exists where $A$ is present at an intermediate frequency on the Y chromosome ($0<\hat{p}_{Y}<1$). However, equilibrium $(C)$ is never locally stable when $r_{MM} \approx 0$ and is therefore not considered further. 
Thus, the Y can either be fixed for the $a$ allele (equilibria $A$ and $B$) or the $A$ allele (equilibria $A'$ and $B'$).
The X chromosome can then either be polymorphic (equilibria $A$ and $A'$) or fixed for the alternative allele (equilibria $B$ and $B'$).
Since equilibria $(A)$ and $(B)$ are equivalent to equilibria $(A')$ and $(B')$ with the labelling of $A$ and $a$ alleles interchanged, we discuss only equilibria $(A')$ and $(B')$, in which the Y$A$ haplotype is favoured (as in the previous section), without loss of generality.

We next calculate when $(A')$ and $(B')$ are locally stable for $r_{MM}=0$. According to the `small parameter theory' \citep{Karlin:1972ab,Karlin:1972dq}, these stability properties are unaffected by small amounts of recombination between the SDR and \textbf{A} locus, although equilibrium frequencies may be slightly altered. 
For the $A$ allele to be stably fixed on the Y requires that $\bar{w}_{YA}^{m}>\bar{w}_{Ya}^{m}$, where the marginal fitnesses of Y$A$ and Y$a$ haplotypes are $\bar{w}_{YA}^{m}$ (as above) and $\bar{w}_{Ya}^{m}=w_{Aa}^{m}p_{Xf} + w_{aa}^{m}(1-p_{Xf})$, respectively.
Substituting $\hat{p}_{Xf}$ from above, fixation of the $A$ allele on the Y requires that $\gamma_{i}>0$ where $\gamma_{(A')}=w_{A}(w_{Aa}^{m} \alpha'+w_{AA}^{m} \beta')-w_{a}(w_{aa}^{m} \alpha'+w_{Aa}^{m} \beta')$ for equilibrium $(A')$ and $\gamma_{(B')}=w_{Aa}^{m}w_{A}-w_{aa}^{m}w_{a}$ for equilibrium $(B')$.
Stability of a polymorphism on the X chromosome (equilibrium $A'$) further requires that $\alpha' >0$ and $\beta' >0$. 
Fixation of the $a$ allele on the X (equilibrium $B'$) is mutually exclusive with $(A')$ and requires that $\beta'<0$. 
We will assume that these conditions are met such that population has reached a stable equilibrium at the \textbf{A} locus when considering evolution at the modifier locus.

To consider recombination rate evolution, we evaluate whether a mutant allele, $m$, can invade if it modifies the recombination rate between \textbf{A} and the SDR by a small amount ($|r_{mm}-r_{MM}|$ and $|r_{Mm}-r_{MM}|$ are of order $\epsilon$). 
As above, we use the leading eigenvalue, $\lambda$, from a local stability analysis to evaluate the spread of a rare mutant modifier, where now $\lambda_{i}$ determines invasion into a population at equilibrium $i$. 
Firstly, because stability of equilibrium $(A')$ requires that $\alpha '>0$ and $\beta '>0$ and all fitnesses must be non-negative, we can define the following series of $\kappa$ terms, which must be positive when $(A')$ is locally stable.

\begin{equation*}
\begin{split}
\kappa_{1} &=w_{aa}^{f}\alpha '+w_{Aa}^{f}\beta '\\
\kappa_{2} &=w_{Aa}^{f} \alpha '+w_{AA}^{f} \beta '\\
\kappa_{3}&=w_{Aa}^{m} \alpha '+w_{AA}^{m}\beta '\\
\kappa_{4}&=w_{aa}^{f} \alpha '+w_{AA}^{f} \beta '\\
\kappa_{5}&=w_{Aa}^{m}w_{a}+w_{AA}^{m}w_{A}\\
\kappa_{6}&=w_{Aa}^{m}w_{a}w_{AA}^{m}w_{A} \\
\kappa_{7}&=w_{aa}^{f}w_{Aa}^{m}w_{a}  \alpha ' + w_{AA}^{f}w_{AA}^{m}w_{A}  \beta '\\
\kappa_{8}&=w_{aa}^{m}\alpha ' \alpha '+2w_{Aa}^{m} \alpha ' \beta '+w_{AA}^{m} \beta ' \beta '\\
\kappa_{9}&=w_{Aa}^{m}w_{a} \alpha '+w_{AA}^{m}w_{A} \beta ' \\
\kappa_{10}&=w_{Aa}^{f}\kappa_{9}+2 \kappa_{6}\kappa_{4}/\kappa_{5}
\end{split}
\end{equation*}

\noindent
These are useful in determining the magnitude of $\lambda_{(A')}$, which determines invasion of modifiers and is given by

\begin{equation}
\lambda_{(A')}=1+(r_{Mm}-r_{MM}) \frac{w_{Aa}^{m}\alpha ' K_{1}}{w_{a}R_{m}(w_{aa}^{m} \alpha '+w_{Aa}^{m} \beta ')K_{2}}
\end{equation}

\noindent
where we neglect terms of order $\epsilon^2$ and higher and $K_{2}$ is strictly positive,

\begin{equation*}
\begin{split}
K_{2}=& R_{f} 2w_{Aa}^{f}\kappa_{3}\kappa_{5} (\alpha '+\beta ')\kappa_{10}
+R_{f}R_{m} w_{Aa}^{m}w_{AA}^{m}2w_{a}w_{A}K_{3}\kappa_{3}\kappa_{4}/\kappa_{5}\\
&+ R_{m} w_{Aa}^{m}w_{AA}^{m}(1-2R_{f})\big(w_{a} \beta ' \kappa_{1}(2w_{AA}^{m}w_{A}\kappa_{2}+\kappa_{10})
+w_{A}\alpha ' \kappa_{2}(2w_{Aa}^{m}w_{a}\kappa_{1}+\kappa_{10})\big)\\
\end{split}
\end{equation*}

\noindent
such that $\lambda_{(A')}>1$ if and only if $(r_{Mm}-r_{MM})K_{1}>0$, where

\begin{equation*}
\begin{split}
K_{1}=&-(1-2R_{f})R_{m} \gamma_{(A')} \kappa_{1}\kappa_{2}\kappa_{6}-R_{m}R_{f}\gamma_{(A')} \kappa_{4} \kappa_{6} \big(\kappa_{7}/\kappa_{5} +  w_{Aa}^{f} (\alpha '+\beta ')/2\big)\\
&-R_{f}\gamma_{(A')} w_{Aa}^{f}w_{a}\kappa_{1}\kappa_{3}\kappa_{5}\\
&+R_{f} w_{Aa}^{f}w_{Aa}^{m}(\gamma_{(A')}\alpha '+R_{m}w_{a}\kappa_{8})\big( 
(w_{Aa}^{m}-w_{AA}^{m})w_{a}w_{A}  \kappa_{4}
+(w_{A}-w_{a})w_{Aa}^{f}  \kappa_{5}(\alpha '+\beta ')/2  \big)\\
%
%\frac{w_{aa}^{f} \alpha '+w_{AA}^{f} \beta '}{w_{AA}^{m} w_{A}+w_{Aa}^{m} w_{a}}\right)\\
%FAa MAa (Maa PXa +  MAa PXA) ((MAA (factorA)^2 + (2 MAa factorA + Maa factorB) factorB) 
%        (FAa factorM (PXA - PXa) + 
 %    factorI (Maa - MAa) PXa PXA) PYA)
\end{split}
\end{equation*}

\noindent
Modifiers that increase recombination ($r_{Mm}-r_{MM}>0$) therefore only spread if $K_{1}>0$. 
Only the last term of $K_{1}$ can be positive, and this term can only be positive if either $w_{Aa}^{m}>w_{AA}^{m}$ or $w_{A}>w_{a}$.
Thus, for increased recombination to be favoured by selection ($K_{1}>0$), heterozygous males must be more fit that males homozygous for the allele fixed on the Y and/or the allele fixed on the Y must be favoured during haploid selection. 
Since the $A$ allele is fixed on the Y, $w_{Aa}^{m}>w_{AA}^{m}$ implies that X chromosomes bearing the $a$ allele are favoured during selection in males. 
If a polymorphism is maintained on the X (equilibrium $A'$), counter-selection must favour the $A$ allele during haploid selection and/or selection in females when $w_{Aa}^{m}>w_{AA}^{m}$. 
In addition, when linkage between the modifier locus and the selected locus is tight (at least in females, $R_{f}=0$), $K_{1}$ is always negative and increased recombination is never favoured.

We next consider the invasion of a recombination modifier into a population at equilibrium $(B')$. Local stability of this equilibrium requires that $(-\beta ')>0$ and $\gamma_{(B')}>0$. 
Ignoring terms of order $\epsilon^2$ and higher,

\begin{equation*}
\lambda_{(B')}=1+ \frac{(r_{Mm}-r_{MM})K_{4}}{4(\gamma_{(B')}+R_{m}w_{aa}^{m}w_{a})((-\beta ')+w_{Aa}^{f}(R_{f}w_{Aa}^{m}w_{a}+R_{m}w_{AA}^{m}w_{A}(1-R_{f}))}
\end{equation*}

\noindent
where

\begin{equation*}
\begin{split}
K_{4}=&-2\gamma_{(B')}(-\beta ')-(2R_{f}+R_{m}(1-R_{f}))w_{Aa}^{f}w_{AA}^{m}w_{A}\gamma_{(B')}\\
&-R_{m}(-\beta ')w_{aa}^{m}w_{a}\\
&+R_{f}(w_{A}-w_{a})w_{Aa}^{f}w_{Aa}^{m}(2 \gamma_{(B')}+R_{m}w_{aa}^{m}w_{a})\\
&+R_{f}R_{m}(w_{Aa}^{m}-w_{AA}^{m})w_{Aa}^{f}w_{Aa}^{m}w_{a}w_{A}
\end{split}
\end{equation*}

\noindent
Therefore $\lambda_{(B')}>1$ if and only if $(r_{Mm}-r_{MM})K_{4}>0$. 
The only terms in $K_{4}$ that can be positive again involve the factors $(w_{A}-w_{a})$ and $(w_{Aa}^{m}-w_{AA}^{m})$, such that either $w_{Aa}^{m}>w_{AA}^{m}$ or $w_{a}>w_{A}$ are again necessary (but not sufficient) conditions for the invasion of modifiers that increase recombination.

Finally, we re-write the condition $K_{4}>0$ to obtain

\begin{equation}
\begin{split}
w_{aa}^{f}<&w_{Aa}^{f}\left(1
-\gamma_{(B')}R_{f}(2-R_{m})R_{m})
-\gamma_{(B')}(w_{Aa}^{m}-w_{AA}^{m})K_{5}
+(w_{A}-w_{a})K_{6}\right)/K_{7}
\end{split}
\label{eq:FAAcond}
\end{equation}

\noindent
where the following terms are positive

\begin{equation*}
\begin{split}
K_{5}=&(1-R_{f})(2 \gamma_{(B')}(1-R_{m})+R_{m}w_{Aa}^{m}w_{a})/w_{Aa}^{m}\\
K_{6}=&(R_{f}R_{m}w_{A}{w_{Aa}^{m}}^2+(w_{AA}^{m}(1-R_{f})+R_{f}w_{Aa}^{m})(2 \gamma_{(B')}(1-R_{m})+w_{Aa}^{m}w_{A}R_{m}))\\
K_{7}=&4 \gamma_{(B')}+2 w_{aa}^{m}w_{a}R_{m}
\end{split}
\end{equation*}

\noindent
Thus, if haploid selection favours the $A$ allele, then condition \eqref{eq:FAAcond} can be met whether selection among diploid females favours allele $A$ or $a$ ($w_{aa}^{f}<w_{Aa}^{f}$ or $w_{aa}^{f}>w_{Aa}^{f}$). 
However, if haploid selection favours the $a$ allele ($w_{a}>w_{A}$), the evolution of increased recombination requires that $w_{Aa}^{m}>w_{AA}^{m}$ (see above), and equation \eqref{eq:FAAcond} shows that selection must favour the $A$ allele during selection in females ($w_{aa}^{f}<w_{Aa}^{f}$). 
Thus, increased recombination is only favoured if the $A$ allele is favoured during selection in females ($w_{aa}^{f}<w_{Aa}^{f}$) and/or the $A$ allele is favoured during haploid selection ($w_{A}>w_{a}$).
Only under these conditions is it possible for recombination between the X$A$ and Y$a$ to produce X$A$ gametes that are favoured over the short term (in daughters and/or gametes/gametophytes, respectively).

One might not expect selection to favour X$A$ haplotypes because an $A$ allele on an average X background should either have the same fitness as an $a$ allele (when a polymorphism is maintained, equilibrium $A'$) or lower fitness (when $A$ is fixed, equilibrium $B'$). 
However, an X$A$ haplotype created by recombination in males is found in a male haploid (pollen or sperm), not on an average X background (which is weighted across X-bearing male sperm/pollen and female eggs/ovules). 
Increased recombination does not evolve if $R_{f}$ and $R_{m}$ are small because the modifier remains linked to the haplotypes it creates, which will eventually be found on all backgrounds. 
However, when $R_{f}$ and $R_{m}$ are sufficiently large, modifiers that increase recombination can gain a transient fitness advantage.
X$A$ pollen/sperm haplotypes can gain a transient fitness advantage during haploid selection and/or selection in females. The evolution of increased recombination is only consistent with this form of selection.

%If $R_{f}$ and $R_{m}$ are small, the modifier remains linked to the haplotypes it creates (X$A$ and Y$a$), which always leads to a net long term disadvantage. 
%When $R_{f}$ and $R_{m}$ are sufficiently large (e.g., autosomal modifiers), a modifier that increases recombination can gain a short term benefit from being found on X$A$ male haploid before recombining onto a different background.

%Typically, mutants that increase the recombination rate are not favoured by selection. 
%In particular, when the modifier locus is tightly linked to the \textbf{A} locus ($R_{f} \approx 0$), only mutants that suppress recombination can spread.
%In addition, if the allele that is fixed on the Y ($A$ for equilibria $A'$ and $B'$) is favoured by selection on the X in males ($w_{AA}^{m}>w_{Aa}^{m}$) but not during selection among haploids ($w_{a}>w_{A}$) increased recombination is never favoured. 
%However, if these conditions are not met there are some parameters under which increased recombination is favoured by selection (figure \ref{fig:combined}).

%To interpret these conditions we consider the haplotypes created by recombination between the SDR and \textbf{A} locus in males. 
%Assuming that the $A$ allele is initially fixed on the Y, the only recombination events of consequence will create Y$a$-bearing and X$A$-bearing pollen or sperm (before haploid selection). 
%Y$a$ haplotypes must be selected against because $A$ is fixed on the Y such that $\bar{w}_{YA}^{m}>\bar{w}_{Ya}^{m}$.
%Therefore, for recombination to be favoured, the cost of producing Y$a$ haplotypes must be outweighed by selection in favour of X$A$ haplotypes. 
%One might not expect selection to favour X$A$ haplotypes because an $A$ allele on an average X background should either have the same fitness as an $a$ allele (when a polymorphism is maintained, equilibrium $A'$) or lower fitness (when $A$ is fixed, equilibrium $B'$). 
%However, an X$A$ haplotype created by recombination in males is found in a male haploid (pollen or sperm), not on an average X background (which is weighted across X-bearing male sperm/pollen and female eggs/ovules).

%If $R_{f}$ and $R_{m}$ are small, the modifier remains linked to the haplotypes it creates (X$A$ and Y$a$), which always leads to a net long term disadvantage. 
%When $R_{f}$ and $R_{m}$ are sufficiently large (e.g., autosomal modifiers), a modifier that increases recombination can gain a short term benefit from being found on X$A$ male haploid before recombining onto a different background. 
%X$A$ pollen or sperm can have a short term advantage if they have high fitness during haploid competition and/or high fitness in female diploids because all X-bearing gametes will form female diploids. 
%Increased recombination is only consistent with X$A$ being favoured during haploid selection and/or selection in females, see Appendix \ref{app:modinv}.

\begin{figure}[h!] 
\begin{minipage}[b]{0.75 \linewidth}
 \includegraphics[width= \linewidth]{Figures/combined.pdf} 
\end{minipage}\hfill
\begin{minipage}[b]{0.25 \linewidth}
 \caption[Selection can favour increased recombination between the sex-determining region (SDR) and a selected locus that is closely linked]{
 Selection can favour increased recombination between the sex-determining region (SDR) and a selected locus that is closely linked ($r_{ij} \approx 0$), even when selection in males is not overdominant. 
 Coloured regions show where increased recombination is favoured in a population at equilibrium $(A)$ in blue, $(B)$ in green, $(A')$ in red, and $(B')$ in orange. 
 Since this model is symmetrical, red/orange regions can be exchanged with blue/green regions if the labelling of $A$ and $a$ alleles is switched. 
 Across columns we vary the fitness of $a$-bearing haploids relative to the $A$-bearing haploids ($w_{A}=1$). Grey lines show the fitness of heterozygous diploids $w_{ij}^{k}=1$.
 In the first row, there are no differences in selection between male and female diploids ($w_{ij}^{f}=w_{ij}^{m}=w_{ij}$), where $w_{aa}$ and $w_{AA}$ are varied along the x and y axes, respectively. 
 As haploid selection becomes stronger, increased recombination can evolve with weaker overdominance in diploids and also with ploidally antagonistic selection ($w_{aa}>1>w_{AA}$).
 In the second and third rows, we consider sex differences in selection, where $w_{aa}^{m}$ and $w_{AA}^{m}$ are varied along the x and y axes ($w_{Aa}^{m}=1$).
 In the second row, where selection in females is overdominant ($w_{AA}^{f}=0.75$, $w_{Aa}^{f}=1$, $w_{aa}^{f}=0.75$), increased recombination can be favoured when selection is directional (or underdominant) in males and haploid selection is moderately strong. 
 In the third row, selection favours the $A$ allele in females ($w_{AA}^{f}=1.05$, $w_{Aa}^{f}=1$, $w_{aa}^{f}=0.75$) and increased recombination can also be favoured with sexually antagonistic selection ($w_{AA}^{m}<1<w_{aa}^{m}$).
 For this plot, we assume that the modifier of recombination is unlinked ($R_{f}=R_{m}=1/2$).
}
 \label{fig:combined} 
\end{minipage}
\end{figure}

\bibliographystyle{amnatnat.bst}
\bibliography{Sex_chromosomes.bib}

%\end{article}

\end{document}

### 2016-08-30 PNAS_Style/bibliography_manual.tex
playing with indices

\begin{thebibliography}{20}

\bibitem{Bergero:2007kr}
Bergero R, Forrest A, Kamau E, Charlesworth D
 (2007) {Evolutionary strata on the X chromosomes of the dioecious
  plant \textit{Silene latifolia}: evidence from new sex-linked genes}.
 \textit{Genetics} 175:1945--1954.

\bibitem{Nam:2008ko}
Nam K, Ellegren H
 (2008) {The chicken (\textit{Gallus gallus}) Z chromosome contains at
  least three nonlinear evolutionary strata}.
 \textit{Genetics} 180:1131--1136.

\bibitem{Lemaitre:2009ij}
Lemaitre C, {et~al.}
 (2009) {Footprints of inversions at present and past pseudoautosomal
  boundaries in human sex chromosomes}.
 \textit{Genome Biology and Evolution} 1:56--66.

\bibitem{Wang:2012}
Wang J, {et~al.}
 (2012) {Sequencing papaya X and Yh chromosomes reveals molecular
  basis of incipient sex chromosome evolution.}
 \textit{Proceedings of the National Academy of Sciences}
  109:13710--13715.

\bibitem{Charlesworth:2013}
Charlesworth D
 (2013) {Plant sex chromosome evolution.}
 \textit{Journal of Experimental Botany} 64:405--420.

\bibitem{Rice:1996ke}
Rice WR
 (1996) {Evolution of the Y Sex Chromosome in Animals}.
 \textit{BioScience} 46:331--343.

\bibitem{Charlesworth:2000cc}
Charlesworth B, Charlesworth D
 (2000) {The degeneration of Y chromosomes.}
 \textit{Philosophical transactions of the Royal Society of London.
  Series B, Biological sciences} 355:1563--1572.

\bibitem{Bachtrog:2006ed}
Bachtrog D
 (2006) {A dynamic view of sex chromosome evolution.}
 \textit{Current opinion in genetics {\&} development} 16:578--585.

\bibitem{Marais:2008hm}
Marais GAB, {et~al.}
 (2008) {Evidence for degeneration of the Y chromosome in the
  dioecious plant \textit{Silene latifolia}}.
 \textit{Current Biology} 18:545--549.

\bibitem{Fisher:1931jo}
Fisher R
 (1931) {The evolution of dominance}.
 \textit{Biological Reviews} 6:363.

\bibitem{Bull:1983vi}
Bull JJ
 (1983) \textit{{Evolution of sex determining mechanisms.}}
 (The Benjamin Cummings Publishing Company).

\bibitem{Rice:1987hs}
Rice WR
 (1987) {The accumulation of sexually antagonistic genes as a
  selective agent promoting the evolution of reduced recombination between
  primitive sex chromosomes}.
 \textit{Evolution} 41:911.

\bibitem{Charlesworth:1980}
Charlesworth D, Charlesworth B
 (1980) {Sex differences in fitness and selection for centric fusions
  between sex-chromosomes and autosomes}.
 \textit{Genetical Research} 35:205--214.

\bibitem{Lenormand:2003ug}
Lenormand T
 (2003) {The evolution of sex dimorphism in recombination.}
 \textit{Genetics} 163:811--822.

\bibitem{Otto:2011ua}
Otto SP, Pannell JR, Peichel CL, Ashman TL
 (2011) {About PAR: the distinct evolutionary dynamics of the
  pseudoautosomal region}.
 \textit{Trends in Genetics} 27:358--367.

\bibitem{Mulcahy:1996ha}
Mulcahy DL, Sari-Gorla M, Mulcahy GB
 (1996) {Pollen selection - past, present and future}.
 \textit{Sexual Plant Reproduction} 9:353--356.

\bibitem{Bernasconi:2004dk}
Bernasconi G
 (2004) {Evolutionary ecology of the prezygotic stage}.
 \textit{Science} 303:971--975.

\bibitem{JOSEPH:2004haa}
Joseph S, Kirkpatrick M
 (2004) {Haploid selection in animals}.
 \textit{Trends in Ecology {\&} Evolution} 19:592--597.

\bibitem{Immler:2012tl}
Immler S, Arnqvist G, Otto SP
 (2012) {Ploidally antagonistic selection maintains stable genetic
  polymorphism}.
 \textit{Evolution} 66:55--65.

\bibitem{SKOGSMYR:2002ce}
Skogsmyr I, Lankinen A
 (2002) {Sexual selection: an evolutionary force in plants?}
 \textit{Biological Reviews} 77:537--562.

\bibitem{Moore:2011jt}
Moore JC, Pannell JR
 (2011) {Sexual selection in plants}.
 \textit{Current Biology} 21:R176--R182.

\bibitem{Marshall:2016fe}
Marshall DL, Evans AS
 (2016) {Can selection on a male mating character result in
  evolutionary change? A selection experiment on California wild radish,
  \textit{Raphanus sativus}}.
 \textit{American journal of botany} 103:553--567.

\bibitem{Borg:2009jpa}
Borg M, Brownfield L, Twell D
 (2009) {Male gametophyte development: a molecular perspective}.
 \textit{Journal of Experimental Botany} 60:1465--1478.

\bibitem{Arunkumar:2013iq}
Arunkumar R, Josephs EB, Williamson RJ, Wright SI
 (2013) {Pollen-specific, but not sperm-specific, genes show stronger
  purifying selection and higher rates of positive selection than sporophytic
  genes in \textit{Capsella grandiflora}}.
 \textit{Molecular biology and evolution} 30:2475--2486.

\bibitem{Gossmann:2014dua}
Gossmann TI, Schmid MW, Grossniklaus U, Schmid KJ
 (2014) {Selection-driven evolution of sex-biased genes Is consistent
  with sexual selection in \textit{Arabidopsis thaliana}}.
 \textit{Molecular biology and evolution} 31:574--583.

\bibitem{Hedhly:2004iv}
Hedhly A, Hormaza JI, Herrero M
 (2004) {Effect of temperature on pollen tube kinetics and dynamics in
  sweet cherry, \textit{Prunus avium} (Rosaceae).}
 \textit{American journal of botany} 91:558--564.

\bibitem{Clarke:2004ir}
Clarke HJ, Khan TN, Siddique KHM
 (2004) {Pollen selection for chilling tolerance at hybridisation
  leads to improved chickpea cultivars}.
 \textit{Euphytica} 139:65--74.

\bibitem{Frascaroli:2001ee}
Frascaroli E, Songstad DD
 (2001) {Pollen genotype selection for a simply inherited qualitative
  factor determining resistance to chlorsulfuron in maize}.
 \textit{Theoretical and Applied Genetics} 102:342--346.

\bibitem{Searcy:1985vt}
Searcy KB, Mulcahy DL
 (1985) {Pollen selection and the gametophytic expression of metal
  tolerance in \textit{Silene dioica} (Caryophyllaceae) and \textit{Mimulus
  guttatus} (Scrophulariaceae)}.
 \textit{American journal of botany} 72:1700--1706.

\bibitem{Ravikumar:2003uo}
Ravikumar RL, Patil BS, Salimath PM
 (2003) {Drought tolerance in sorghum by pollen selection using
  osmotic stress}.
 \textit{Euphytica} 133:371--376.

\bibitem{Ravikumar:2012ej}
Ravikumar RL, Chaitra GN, Choukimath AM, Soregaon CD
 (2012) {Gametophytic selection for wilt resistance and its impact on
  the segregation of wilt resistance alleles in chickpea (\textit{Cicer
  arietinum} L.)}.
 \textit{Euphytica} 189:173--181.

\bibitem{Hecht:1998hz}
Hecht NB
 (1998) {Molecular mechanisms of male germ cell differentiation}.
 \textit{Bioessays} 20:555--561.

\bibitem{Zheng:2001fi}
Zheng Y, Deng X, Martin-DeLeon PA
 (2001) {Lack of sharing of Spam1 (Ph-20) among mouse spermatids and
  transmission ratio distortion}.
 \textit{Biology of Reproduction} 64:1730--1738.

\bibitem{Vibranovski:2010et}
Vibranovski MD, Chalopin DS, Lopes HF, Long M, Karr TL
 (2010) {Direct evidence for postmeiotic transcription during
  \textit{Drosophila melanogaster} spermatogenesis}.
 \textit{Genetics} 186:431--433.

\bibitem{Immler:2014im}
Immler S, Hotzy C, Alavioon G, Petersson E, Arnqvist G
 (2014) {Sperm variation within a single ejaculate affects offspring
  development in Atlantic salmon}.
 \textit{Biology letters} 10:20131040.

\bibitem{Otto:2007tv}
Otto SP, Day T
 (2007) \textit{{A biologist's guide to mathematical modeling in ecology
  and evolution}}
 (Princeton University Pres, Princeton, NJ).

\bibitem{Otto:2014jf}
Otto SP
 (2014) {Selective maintenance of recombination between the sex
  chromosomes.}
 \textit{Journal of Evolutionary Biology} 27:1431--1442.

 \bibitem{Charlesworth:1999kd}
B~Charlesworth and J~D Wall. (1999)
{Inbreeding, heterozygote advantage and the evolution of neo-X and
  neo-Y sex chromosomes}.
\textit{Proceedings of the Royal Society B: Biological Sciences},
  266(1414):51--56.

 \bibitem{Pennell:2015im}
Matthew~W Pennell, Mark Kirkpatrick, Sarah~P Otto, Jana~C Vamosi, Catherine~L
  Peichel, Nicole Valenzuela, and Jun Kitano.
(2014) {Y fuse? Sex chromosome fusions in fishes and reptiles}.
\textit{PLOS Genetics}, 11(5):e1005237.

\bibitem{Field:2013cc}
Field DL, Pickup M, Barrett SCH
 (2013) {Comparative analyses of sex-ratio variation in dioecious
  flowering plants.}
 \textit{Evolution} 67:661--672.

\bibitem{Conn:1981uw}
Conn JS, Blum U
 (1981) {Sex ratio of \textit{Rumex hastatulus}: the effect of
  environmental factors and certation}.
 \textit{Evolution} 35:1108--1116.

\bibitem{Stehlik:2006to}
Stehlik I, Barrett SCH
 (2006) {Pollination intensity influences sex ratios in dioecious
  Rumex nivalis, a wind-pollinated plant.}
 \textit{Evolution} 60:1207--1214.

\bibitem{Field:2012fd}
Field DL, Pickup M, Barrett SCH
 (2012) {The influence of pollination intensity on fertilization
  success, progeny sex ratio, and fitness in a wind-pollinated, dioecious
  plant}.
 \textit{International Journal of Plant Sciences} 173:184--191.

\bibitem{Lloyd:1974tz}
Lloyd DG
 (1974) \textit{{Female-predominant sex ratios in angiosperms}}
 (Heredity) Vol.{}~32.

\bibitem{Stehlik:2005ul}
Stehlik I, Barrett S
 (2005) {Mechanisms governing sex-ratio variation in dioecious
  \textit{Rumex nivalis}}.
 \textit{Evolution} 59:814--825.

\bibitem{Ming:2011iy}
Ming R, Bendahmane A, Renner SS
 (2011) {Sex chromosomes in land plants}.
 \textit{dx.doi.org} 62:485--514.

\bibitem{Charlesworth:2015dj}
Charlesworth D
 (2015) {Plant contributions to our understanding of sex chromosome
  evolution}.
 \textit{The New phytologist} 208:52--65.

\bibitem{Bachtrog:2014bx}
Bachtrog D, {et~al.}
 (2014) {Sex determination: why so many ways of doing it?}
 \textit{PLoS Biol} 12:e1001899.

\bibitem{Vicoso:2015hf}
Vicoso B, Bachtrog D
 (2015) {Numerous transitions of sex chromosomes in Diptera.}
 \textit{PLoS Biol} 13:e1002078.

\bibitem{Travers:2001vx}
Travers SE, Mazer SJ
 (2001) {Trade-offs between male and female reproduction associated
  with allozyme variation in phosphoglucoisomerase in an annual plant
  (\textit{Clarkia unguiculata}: Onagraceae).}
 \textit{Evolution} 55:2421--2428.

\bibitem{Muralla:2011ks}
Muralla R, Lloyd J, Meinke D
 (2011) {Molecular Foundations of Reproductive Lethality in
  Arabidopsis thaliana}.
 \textit{PLoS ONE} 6:e28398.

\bibitem{Lenormand:2005vb}
Lenormand T, Dutheil J
 (2005) {Recombination difference between sexes: a role for haploid
  selection}.
 \textit{PLoS Biol} 3:e63.

\bibitem{Vamosi:2006hi}
Vamosi JC, {et~al.}
 (2006) {Pollination decays in biodiversity hotspots.}
 \textit{Proceedings of the National Academy of Sciences of the United
  States of America} 103:956--961.

\bibitem{Friedman:2009eg}
Friedman J, Barrett SCH
 (2009) {Wind of change: new insights on the ecology and evolution of
  pollination and mating in wind-pollinated plants}.
 \textit{Annals of Botany} 103:1515--1527.

\bibitem{Feldman:1989gm}
Feldman MW, Otto SP
 (1989) {More on recombination and selection in the modifier theory of
  sex-ratio distortion}.
 \textit{Theoretical Population Biology} 35:207--225.

\bibitem{Haig:2010em}
Haig D
 (2010) {Games in tetrads: segregation, recombination, and meiotic
  drive.}
 \textit{The American Naturalist} 176:404--413.

\bibitem{Brandvain:2012hh}
Brandvain Y, Coop G
 (2012) {Scrambling eggs: meiotic drive and the evolution of female
  recombination rates}.
 \textit{Genetics} 190:709--723.

\bibitem{Patten:2014tn}
Patten MM
 (2014) {Meiotic drive influences the outcome of sexually antagonistic
  selection at a linked locus}.
 \textit{Journal of Evolutionary Biology} 27:2360--2370.

\bibitem{Rydzewski:2016csa}
Rydzewski WT, Carioscia SA, Li{\'e}vano G, Lynch VD, Patten MM
 (2016) {Sexual antagonism and meiotic drive cause stable linkage
  disequilibrium and favour reduced recombination on the X chromosome}.
 \textit{Journal of Evolutionary Biology} 29:1247--1256.

\bibitem{Ubeda:2015fx}
{\'U}beda F, Patten MM, Wild G
 (2015) {On the origin of sex chromosomes from meiotic drive.}
 \textit{Proceedings of the Royal Society B: Biological Sciences}
  282:20141932.

\end{thebibliography}

### 2016-08-30 PNAS_Style/bibliography_manuel.tex
playing with indices

\begin{thebibliography}{63}
\providecommand{\natexlab}[1]{#1}
\providecommand{\url}[1]{\texttt{#1}}
\expandafter\ifx\csname urlstyle\endcsname\relax
  \providecommand{\doi}[1]{doi: #1}\else
  \providecommand{\doi}{doi: \begingroup \urlstyle{rm}\Url}\fi

\bibitem[Bergero et~al.(2007)Bergero, Forrest, Kamau, and
  Charlesworth]{Bergero:2007kr}
R~Bergero, A~Forrest, E~Kamau, and D~Charlesworth.
\newblock {Evolutionary strata on the X chromosomes of the dioecious plant
  \emph{Silene latifolia}: evidence from new sex-linked genes}.
\newblock \emph{Genetics}, 175\penalty0 (4):\penalty0 1945--1954, February
  2007.

\bibitem[Nam and Ellegren(2008)]{Nam:2008ko}
K~Nam and H~Ellegren.
\newblock {The chicken (\emph{Gallus gallus}) Z chromosome contains at least
  three nonlinear evolutionary strata}.
\newblock \emph{Genetics}, 180\penalty0 (2):\penalty0 1131--1136, September
  2008.

\bibitem[Lemaitre et~al.(2009)Lemaitre, Braga, Gautier, Sagot, Tannier, and
  Marais]{Lemaitre:2009ij}
C~Lemaitre, M~D~V Braga, C~Gautier, M~F Sagot, E~Tannier, and G~A~B Marais.
\newblock {Footprints of inversions at present and past pseudoautosomal
  boundaries in human sex chromosomes}.
\newblock \emph{Genome Biology and Evolution}, 1\penalty0 (0):\penalty0 56--66,
  April 2009.

\bibitem[Wang et~al.(2012)Wang, Na, Yu, Gschwend, Han, Zeng, Aryal, VanBuren,
  Murray, Zhang, Navajas-P{\'e}rez, Feltus, Lemke, Tong, Chen, Wai, Singh,
  Wang, Min, Alam, Charlesworth, Moore, Jiang, Paterson, and Ming]{Wang:2012}
Jianping Wang, Jong-Kuk Na, Qingyi Yu, Andrea~R Gschwend, Jennifer Han,
  Fanchang Zeng, Rishi Aryal, Robert VanBuren, Jan~E Murray, Wenli Zhang,
  Rafael Navajas-P{\'e}rez, F~Alex Feltus, Cornelia Lemke, Eric~J Tong, Cuixia
  Chen, Ching~Man Wai, Ratnesh Singh, Ming-Li Wang, Xiang~Jia Min, Maqsudul
  Alam, Deborah Charlesworth, Paul~H Moore, Jiming Jiang, Andrew~H Paterson,
  and Ray Ming.
\newblock {Sequencing papaya X and Yh chromosomes reveals molecular basis of
  incipient sex chromosome evolution.}
\newblock \emph{Proceedings of the National Academy of Sciences}, 109\penalty0
  (34):\penalty0 13710--13715, August 2012.

\bibitem[Charlesworth(2013)]{Charlesworth:2013}
Deborah Charlesworth.
\newblock {Plant sex chromosome evolution.}
\newblock \emph{Journal of Experimental Botany}, 64\penalty0 (2):\penalty0
  405--420, January 2013.

\bibitem[Rice(1996)]{Rice:1996ke}
William~R Rice.
\newblock {Evolution of the Y Sex Chromosome in Animals}.
\newblock \emph{BioScience}, 46\penalty0 (5):\penalty0 331--343, May 1996.

\bibitem[Charlesworth and Charlesworth(2000)]{Charlesworth:2000cc}
B~Charlesworth and D~Charlesworth.
\newblock {The degeneration of Y chromosomes.}
\newblock \emph{Philosophical transactions of the Royal Society of London.
  Series B, Biological sciences}, 355\penalty0 (1403):\penalty0 1563--1572,
  November 2000.

\bibitem[Bachtrog(2006)]{Bachtrog:2006ed}
Doris Bachtrog.
\newblock {A dynamic view of sex chromosome evolution.}
\newblock \emph{Current opinion in genetics {\&} development}, 16\penalty0
  (6):\penalty0 578--585, December 2006.

\bibitem[Marais et~al.(2008)Marais, Nicolas, Bergero, Chambrier, Kejnovsky,
  Mon{\'e}ger, Hobza, Widmer, and Charlesworth]{Marais:2008hm}
Gabriel A~B Marais, Michael Nicolas, Roberta Bergero, Pierre Chambrier, Eduard
  Kejnovsky, Fran{\c c}oise Mon{\'e}ger, Roman Hobza, Alex Widmer, and Deborah
  Charlesworth.
\newblock {Evidence for degeneration of the Y chromosome in the dioecious plant
  \emph{Silene latifolia}}.
\newblock \emph{Current Biology}, 18\penalty0 (7):\penalty0 545--549, April
  2008.

\bibitem[Charlesworth et~al.(2005)Charlesworth, Charlesworth, and
  Marais]{Charlesworth:2005cx}
D~Charlesworth, B~Charlesworth, and G~Marais.
\newblock {Steps in the evolution of heteromorphic sex chromosomes}.
\newblock \emph{Heredity}, 95\penalty0 (2):\penalty0 118--128, May 2005.

\bibitem[Charlesworth(2015)]{Charlesworth:2015dj}
Deborah Charlesworth.
\newblock {Plant contributions to our understanding of sex chromosome
  evolution}.
\newblock \emph{The New phytologist}, 208\penalty0 (1):\penalty0 52--65, 2015.

\bibitem[Nei(1969)]{Nei:1969tb}
Masatoshi Nei.
\newblock {Linkage modification and sex difference in recombination}.
\newblock \emph{Genetics}, 63\penalty0 (3):\penalty0 681--699, November 1969.

\bibitem[Charlesworth and Charlesworth(1978)]{Charlesworth:1978ut}
B~Charlesworth and D~Charlesworth.
\newblock {A model for the evolution of dioecy and gynodioecy}.
\newblock \emph{American Naturalist}, 122\penalty0 (988):\penalty0 975--997,
  1978.

\bibitem[Fisher(1931)]{Fisher:1931jo}
R~Fisher.
\newblock {The evolution of dominance}.
\newblock \emph{Biological Reviews}, 6\penalty0 (4):\penalty0 363, October
  1931.

\bibitem[Bull(1983)]{Bull:1983vi}
J~J Bull.
\newblock \emph{{Evolution of sex determining mechanisms.}}
\newblock The Benjamin/Cummings Publishing Company, Inc., 1983.

\bibitem[Rice(1987)]{Rice:1987hs}
William~R Rice.
\newblock {The accumulation of sexually antagonistic genes as a selective agent
  promoting the evolution of reduced recombination between primitive sex
  chromosomes}.
\newblock \emph{Evolution}, 41\penalty0 (4):\penalty0 911, July 1987.

\bibitem[Charlesworth and Charlesworth(1980)]{Charlesworth:1980}
D~Charlesworth and B~Charlesworth.
\newblock {Sex differences in fitness and selection for centric fusions between
  sex-chromosomes and autosomes}.
\newblock \emph{Genetical Research}, 35\penalty0 (02):\penalty0 205--214, 1980.

\bibitem[Lenormand(2003)]{Lenormand:2003ug}
Thomas Lenormand.
\newblock {The evolution of sex dimorphism in recombination.}
\newblock \emph{Genetics}, 163\penalty0 (2):\penalty0 811--822, 2003.

\bibitem[Otto et~al.(2011)Otto, Pannell, Peichel, and Ashman]{Otto:2011ua}
S~P Otto, J~R Pannell, C~L Peichel, and T-L Ashman.
\newblock {About PAR: the distinct evolutionary dynamics of the pseudoautosomal
  region}.
\newblock \emph{Trends in Genetics}, 27\penalty0 (9):\penalty0 358--367, 2011.

\bibitem[Mulcahy et~al.(1996)Mulcahy, Sari-Gorla, and Mulcahy]{Mulcahy:1996ha}
David~L Mulcahy, Mirella Sari-Gorla, and Gabriella~Bergamini Mulcahy.
\newblock {Pollen selection - past, present and future}.
\newblock \emph{Sexual Plant Reproduction}, 9\penalty0 (6):\penalty0 353--356,
  November 1996.

\bibitem[Bernasconi(2004)]{Bernasconi:2004dk}
G~Bernasconi.
\newblock {Evolutionary ecology of the prezygotic stage}.
\newblock \emph{Science}, 303\penalty0 (5660):\penalty0 971--975, February
  2004.

\bibitem[Joseph and Kirkpatrick(2004)]{JOSEPH:2004haa}
S~Joseph and Mark Kirkpatrick.
\newblock {Haploid selection in animals}.
\newblock \emph{Trends in Ecology {\&} Evolution}, 19\penalty0 (11):\penalty0
  592--597, November 2004.

\bibitem[Immler et~al.(2012)Immler, Arnqvist, and Otto]{Immler:2012tl}
S~Immler, G~Arnqvist, and S~P Otto.
\newblock {Ploidally antagonistic selection maintains stable genetic
  polymorphism}.
\newblock \emph{Evolution}, 66\penalty0 (1):\penalty0 55--65, 2012.

\bibitem[Skogsmyr and Lankinen(2002)]{SKOGSMYR:2002ce}
I~Skogsmyr and A~Lankinen.
\newblock {Sexual selection: an evolutionary force in plants?}
\newblock \emph{Biological Reviews}, 77\penalty0 (4):\penalty0 537--562,
  November 2002.

\bibitem[Moore and Pannell(2011)]{Moore:2011jt}
Jamie~C Moore and John~R Pannell.
\newblock {Sexual selection in plants}.
\newblock \emph{Current Biology}, 21\penalty0 (5):\penalty0 R176--R182, March
  2011.

\bibitem[Marshall and Evans(2016)]{Marshall:2016fe}
D~L Marshall and A~S Evans.
\newblock {Can selection on a male mating character result in evolutionary
  change? A selection experiment on California wild radish, \emph{Raphanus
  sativus}}.
\newblock \emph{American journal of botany}, 103\penalty0 (3):\penalty0
  553--567, March 2016.

\bibitem[Borg et~al.(2009)Borg, Brownfield, and Twell]{Borg:2009jpa}
M~Borg, L~Brownfield, and D~Twell.
\newblock {Male gametophyte development: a molecular perspective}.
\newblock \emph{Journal of Experimental Botany}, 60\penalty0 (5):\penalty0
  1465--1478, January 2009.

\bibitem[Arunkumar et~al.(2013)Arunkumar, Josephs, Williamson, and
  Wright]{Arunkumar:2013iq}
R~Arunkumar, E~B Josephs, R~J Williamson, and S~I Wright.
\newblock {Pollen-specific, but not sperm-specific, genes show stronger
  purifying selection and higher rates of positive selection than sporophytic
  genes in \emph{Capsella grandiflora}}.
\newblock \emph{Molecular biology and evolution}, 30\penalty0 (11):\penalty0
  2475--2486, October 2013.

\bibitem[Gossmann et~al.(2014)Gossmann, Schmid, Grossniklaus, and
  Schmid]{Gossmann:2014dua}
T~I Gossmann, M~W Schmid, U~Grossniklaus, and K~J Schmid.
\newblock {Selection-driven evolution of sex-biased genes Is consistent with
  sexual selection in \emph{Arabidopsis thaliana}}.
\newblock \emph{Molecular biology and evolution}, 31\penalty0 (3):\penalty0
  574--583, February 2014.

\bibitem[Hedhly et~al.(2004)Hedhly, Hormaza, and Herrero]{Hedhly:2004iv}
A~Hedhly, J~I Hormaza, and M~Herrero.
\newblock {Effect of temperature on pollen tube kinetics and dynamics in sweet
  cherry, \emph{Prunus avium} (Rosaceae).}
\newblock \emph{American journal of botany}, 91\penalty0 (4):\penalty0
  558--564, April 2004.

\bibitem[Clarke et~al.(2004)Clarke, Khan, and Siddique]{Clarke:2004ir}
Heather~J Clarke, Tanveer~N Khan, and Kadambot H~M Siddique.
\newblock {Pollen selection for chilling tolerance at hybridisation leads to
  improved chickpea cultivars}.
\newblock \emph{Euphytica}, 139\penalty0 (1):\penalty0 65--74, 2004.

\bibitem[Frascaroli and Songstad(2001)]{Frascaroli:2001ee}
E~Frascaroli and D~D Songstad.
\newblock {Pollen genotype selection for a simply inherited qualitative factor
  determining resistance to chlorsulfuron in maize}.
\newblock \emph{Theoretical and Applied Genetics}, 102\penalty0 (2-3):\penalty0
  342--346, February 2001.

\bibitem[Searcy and Mulcahy(1985)]{Searcy:1985vt}
K~B Searcy and D~L Mulcahy.
\newblock {Pollen selection and the gametophytic expression of metal tolerance
  in \emph{Silene dioica} (Caryophyllaceae) and \emph{Mimulus guttatus}
  (Scrophulariaceae)}.
\newblock \emph{American journal of botany}, 72\penalty0 (11):\penalty0
  1700--1706, 1985.

\bibitem[Ravikumar et~al.(2003)Ravikumar, Patil, and
  Salimath]{Ravikumar:2003uo}
R~L Ravikumar, B~S Patil, and P~M Salimath.
\newblock {Drought tolerance in sorghum by pollen selection using osmotic
  stress}.
\newblock \emph{Euphytica}, 133:\penalty0 371--376, 2003.

\bibitem[Ravikumar et~al.(2012)Ravikumar, Chaitra, Choukimath, and
  Soregaon]{Ravikumar:2012ej}
R~L Ravikumar, G~N Chaitra, Anilkumar~M Choukimath, and C~D Soregaon.
\newblock {Gametophytic selection for wilt resistance and its impact on the
  segregation of wilt resistance alleles in chickpea (\emph{Cicer arietinum}
  L.)}.
\newblock \emph{Euphytica}, 189\penalty0 (2):\penalty0 173--181, July 2012.

\bibitem[Hecht(1998)]{Hecht:1998hz}
Norman~B Hecht.
\newblock {Molecular mechanisms of male germ cell differentiation}.
\newblock \emph{Bioessays}, 20\penalty0 (7):\penalty0 555--561, December 1998.

\bibitem[Zheng et~al.(2001)Zheng, Deng, and Martin-DeLeon]{Zheng:2001fi}
Y~Zheng, X~Deng, and P~A Martin-DeLeon.
\newblock {Lack of sharing of Spam1 (Ph-20) among mouse spermatids and
  transmission ratio distortion}.
\newblock \emph{Biology of Reproduction}, 64\penalty0 (6):\penalty0 1730--1738,
  June 2001.

\bibitem[Vibranovski et~al.(2010)Vibranovski, Chalopin, Lopes, Long, and
  Karr]{Vibranovski:2010et}
M~D Vibranovski, D~S Chalopin, H~F Lopes, M~Long, and T~L Karr.
\newblock {Direct evidence for postmeiotic transcription during
  \emph{Drosophila melanogaster} spermatogenesis}.
\newblock \emph{Genetics}, 186\penalty0 (1):\penalty0 431--433, September 2010.

\bibitem[Immler et~al.(2014)Immler, Hotzy, Alavioon, Petersson, and
  Arnqvist]{Immler:2014im}
S~Immler, C~Hotzy, G~Alavioon, E~Petersson, and G~Arnqvist.
\newblock {Sperm variation within a single ejaculate affects offspring
  development in Atlantic salmon}.
\newblock \emph{Biology letters}, 10\penalty0 (2):\penalty0 20131040, February
  2014.

\bibitem[Otto and Day(2007)]{Otto:2007tv}
S~P Otto and T~Day.
\newblock \emph{{A biologist's guide to mathematical modeling in ecology and
  evolution}}.
\newblock Princeton University Pres, Princeton, NJ, 2007.

\bibitem[Otto(2014)]{Otto:2014jf}
S~P Otto.
\newblock {Selective maintenance of recombination between the sex chromosomes.}
\newblock \emph{Journal of Evolutionary Biology}, 27\penalty0 (7):\penalty0
  1431--1442, July 2014.

\bibitem[Charlesworth and Wall(1999)]{Charlesworth:1999kd}
B~Charlesworth and J~D Wall.
\newblock {Inbreeding, heterozygote advantage and the evolution of neo-X and
  neo-Y sex chromosomes}.
\newblock \emph{Proceedings of the Royal Society B: Biological Sciences},
  266\penalty0 (1414):\penalty0 51--56, January 1999.

\bibitem[Pennell et~al.(2015)Pennell, Kirkpatrick, Otto, Vamosi, Peichel,
  Valenzuela, and Kitano]{Pennell:2015im}
Matthew~W Pennell, Mark Kirkpatrick, Sarah~P Otto, Jana~C Vamosi, Catherine~L
  Peichel, Nicole Valenzuela, and Jun Kitano.
\newblock {Y fuse? Sex chromosome fusions in fishes and reptiles}.
\newblock \emph{PLOS Genetics}, 11\penalty0 (5):\penalty0 e1005237, May 2015.

\bibitem[Karlin and McGregor(1972{\natexlab{a}})]{Karlin:1972ab}
Samuel Karlin and James McGregor.
\newblock {Application of method of small parameters to multi-niche population
  genetic models}.
\newblock \emph{Theoretical Population Biology}, 3\penalty0 (2):\penalty0
  186--209, June 1972{\natexlab{a}}.

\bibitem[Karlin and McGregor(1972{\natexlab{b}})]{Karlin:1972dq}
Samuel Karlin and James McGregor.
\newblock {Polymorphisms for genetic and ecological systems with weak
  coupling}.
\newblock \emph{Theoretical Population Biology}, 3\penalty0 (2):\penalty0
  210--238, June 1972{\natexlab{b}}.

\bibitem[Field et~al.(2013)Field, Pickup, and Barrett]{Field:2013cc}
David~L Field, Melinda Pickup, and Spencer C~H Barrett.
\newblock {Comparative analyses of sex-ratio variation in dioecious flowering
  plants.}
\newblock \emph{Evolution}, 67\penalty0 (3):\penalty0 661--672, March 2013.

\bibitem[Conn and Blum(1981)]{Conn:1981uw}
J~S Conn and Udo Blum.
\newblock {Sex ratio of \emph{Rumex hastatulus}: the effect of environmental
  factors and certation}.
\newblock \emph{Evolution}, 35\penalty0 (6):\penalty0 1108--1116, 1981.

\bibitem[Stehlik and Barrett(2006)]{Stehlik:2006to}
Ivana Stehlik and Spencer C~H Barrett.
\newblock {Pollination intensity influences sex ratios in dioecious Rumex
  nivalis, a wind-pollinated plant.}
\newblock \emph{Evolution}, 60\penalty0 (6):\penalty0 1207--1214, June 2006.

\bibitem[Field et~al.(2012)Field, Pickup, and Barrett]{Field:2012fd}
David~L Field, Melinda Pickup, and Spencer C~H Barrett.
\newblock {The influence of pollination intensity on fertilization success,
  progeny sex ratio, and fitness in a wind-pollinated, dioecious plant}.
\newblock \emph{International Journal of Plant Sciences}, 173\penalty0
  (2):\penalty0 184--191, February 2012.

\bibitem[Lloyd(1974)]{Lloyd:1974tz}
D~G Lloyd.
\newblock \emph{{Female-predominant sex ratios in angiosperms}}, volume~32.
\newblock Heredity, 1974.

\bibitem[Stehlik and Barrett(2005)]{Stehlik:2005ul}
I~Stehlik and SCH Barrett.
\newblock {Mechanisms governing sex-ratio variation in dioecious \emph{Rumex
  nivalis}}.
\newblock \emph{Evolution}, 59\penalty0 (4):\penalty0 814--825, 2005.

\bibitem[Ming et~al.(2011)Ming, Bendahmane, and Renner]{Ming:2011iy}
Ray Ming, Abdelhafid Bendahmane, and Susanne~S Renner.
\newblock {Sex chromosomes in land plants}.
\newblock \emph{dx.doi.org}, 62\penalty0 (1):\penalty0 485--514, June 2011.

\bibitem[Bachtrog et~al.(2014)Bachtrog, Mank, Peichel, Kirkpatrick, Otto,
  Ashman, Hahn, Kitano, Mayrose, Ming, Perrin, Ross, Valenzuela, Vamosi, and
  {Tree of Sex Consortium}]{Bachtrog:2014bx}
Doris Bachtrog, Judith~E Mank, Catherine~L Peichel, Mark Kirkpatrick, Sarah~P
  Otto, Tia-Lynn Ashman, Matthew~W Hahn, Jun Kitano, Itay Mayrose, Ray Ming,
  Nicolas Perrin, Laura Ross, Nicole Valenzuela, Jana~C Vamosi, and {Tree of
  Sex Consortium}.
\newblock {Sex determination: why so many ways of doing it?}
\newblock \emph{PLoS Biol}, 12\penalty0 (7):\penalty0 e1001899, July 2014.

\bibitem[Vicoso and Bachtrog(2015)]{Vicoso:2015hf}
Beatriz Vicoso and Doris Bachtrog.
\newblock {Numerous transitions of sex chromosomes in Diptera.}
\newblock \emph{PLoS Biol}, 13\penalty0 (4):\penalty0 e1002078, April 2015.

\bibitem[Travers and Mazer(2001)]{Travers:2001vx}
S~E Travers and S~J Mazer.
\newblock {Trade-offs between male and female reproduction associated with
  allozyme variation in phosphoglucoisomerase in an annual plant (\emph{Clarkia
  unguiculata}: Onagraceae).}
\newblock \emph{Evolution}, 55\penalty0 (12):\penalty0 2421--2428, December
  2001.

\bibitem[Lenormand and Dutheil(2005)]{Lenormand:2005vb}
T~Lenormand and J~Dutheil.
\newblock {Recombination difference between sexes: a role for haploid
  selection}.
\newblock \emph{PLoS Biol}, 3\penalty0 (3):\penalty0 e63, 2005.

\bibitem[van Doorn and Kirkpatrick(2007)]{vanDoorn:2007eu}
G~S van Doorn and Mark Kirkpatrick.
\newblock {Turnover of sex chromosomes induced by sexual conflict.}
\newblock \emph{Nature}, 449\penalty0 (7164):\penalty0 909--912, October 2007.

\bibitem[Feldman and Otto(1989)]{Feldman:1989gm}
Marcus~W Feldman and Sarah~P Otto.
\newblock {More on recombination and selection in the modifier theory of
  sex-ratio distortion}.
\newblock \emph{Theoretical Population Biology}, 35\penalty0 (2):\penalty0
  207--225, April 1989.

\bibitem[Haig(2010)]{Haig:2010em}
David Haig.
\newblock {Games in tetrads: segregation, recombination, and meiotic drive.}
\newblock \emph{The American Naturalist}, 176\penalty0 (4):\penalty0 404--413,
  October 2010.

\bibitem[Brandvain and Coop(2012)]{Brandvain:2012hh}
Y~Brandvain and G~Coop.
\newblock {Scrambling eggs: meiotic drive and the evolution of female
  recombination rates}.
\newblock \emph{Genetics}, 190\penalty0 (2):\penalty0 709--723, February 2012.

\bibitem[Patten(2014)]{Patten:2014tn}
M~M Patten.
\newblock {Meiotic drive influences the outcome of sexually antagonistic
  selection at a linked locus}.
\newblock \emph{Journal of Evolutionary Biology}, 27:\penalty0 2360--2370,
  2014.

\bibitem[Rydzewski et~al.(2016)Rydzewski, Carioscia, Li{\'e}vano, Lynch, and
  Patten]{Rydzewski:2016csa}
William~T Rydzewski, Sara~A Carioscia, Gabriela Li{\'e}vano, Victoria~D Lynch,
  and Manus~M Patten.
\newblock {Sexual antagonism and meiotic drive cause stable linkage
  disequilibrium and favour reduced recombination on the X chromosome}.
\newblock \emph{Journal of Evolutionary Biology}, 29\penalty0 (6):\penalty0
  1247--1256, March 2016.

\bibitem[{\'U}beda et~al.(2015){\'U}beda, Patten, and Wild]{Ubeda:2015fx}
Francisco {\'U}beda, Manus~M Patten, and Geoff Wild.
\newblock {On the origin of sex chromosomes from meiotic drive.}
\newblock \emph{Proceedings of the Royal Society B: Biological Sciences},
  282\penalty0 (1798):\penalty0 20141932, January 2015.

\end{thebibliography}

### 2016-08-30 LaTeX/Turnover.tex
removed some notes from LaTeX file

@@
 
-Animals and angiosperms exhibit extremely diverse sex determination systems, reviewed in \citet{Bull:1983vi,Charlesworth:2010it,Beukeboom:2014vb,Bachtrog:2014bx}. 
+%CHECK THROUGHOUT: use of sex-determination SYSTEMS versus MECHANISMS.
+
+Animals and angiosperms exhibit extremely diverse sex determination systems, as reviewed by \citet{Bull:1983vi,Charlesworth:2010it,Beukeboom:2014vb,Bachtrog:2014bx}. 
 Among species with genetic sex determination of diploid sexes, some taxa have heterogametic males (XY) and homogametic females (XX), including %non-monotreme? 
@@
 Albert C.
-Uy
+Uy.
+I wonder if this is actually a fusion event though?
 In addition, many gonochoric/dioecious clades with genetic sex determination exhibit transitions between male (XY) and female (ZW) heterogamety, including eight of 26 teleost fish families \citep{Mank:2006bt}, true fruit flies \citep[Tephritids,][]{Vicoso:2015hf}, amphibians \citep{Hillis:1990gu}, the angiosperm genus \textit{Silene} \citep{Slancarova:2013dq}, Coleoptera and Hemiptera \citep[][plate 2]{Beukeboom:2014vb}.
@@
 \noindent
-We have results where polygenic sex determination is sometimes stable:
+We have results where polygenic sex determination is sometimes stable, may be worth mentioning:
 
@@
 \& Anholt 2002), bivalves (Haley 1977; Saavedra et al. 1997), gastropods (Yusa 2007a,b), and polychaetes (Bacci 1965, 1978; Premoli et al. 1996).''
+From Vuilleumier et al. 2007:
+``Polymorphism for sex-determining genes within oramong populations has been reported in many speciesincluding houseflies, midges, woodlice, platyfish, cichlidfish, and frogs (Gordon, 1944; Kallman, 1970; Thomp-son, 1971; Macdonald, 1978; Bull, 1983; Rigaud et al., 1997; Caubet et al., 2000; Lande et al., 2001; Ogataet al., 2003; Lee et al., 2004; Mank et al., 2006).
+
+%NOTE: ``Bull & Charnov (1977) hypothesized that a new sex-determining gene can rapidly increase and become fixedin a population if it is linked to a gene with high adaptivevalue, and finally cause a change of the heterogametic sex.'' The Bull and Charnov paper is also the one in which the set of neutral equilibria between XY and ZW are identified (where sex ratios are equal)
+%NOTE: Vuilleumier et al. 2007 also find polymorphic sex determination can be stable.
 
@@
 \noindent
-Description of sex ratio adjustment and sexual antagonism theories:
+\textcolor{red}{Brief description of sex ratio adjustment and sexual antagonism theories:}
 
@@
 Sex ratio selection might be a particularly important force driving transitions between sex-determining systems \citep[Chapter 7]{Beukeboom:2014vb}. 
-For example, feminizing mutations may invade when female biased sex ratios are favoured due to interdemic selection (Wilson and Colwell 1981, Vuilleumier et al.
-2007 CITE) or local mate competition (Hamilton 1967, Reinhold 1996, Werren and Taylor 1984, Pen et al.
-2010 CITE).
+For example, feminizing mutations may invade when female biased sex ratios are favoured due to interdemic selection \citep{Wilson:1981vm,Vuillleumier:2007bh}.
+In other cases, flexible sex determination systems may be favoured in order to exploit environmental conditions that are optimal for males or females, creating locally biased sex ratios \citep{Charnov:1977tx,Werren:1984tl,Pen:2010kk}.
 In other situations, sex ratio selection may favour transitions in order to restore equal sex ratios. 
@@
 
-For example, new sex-determining systems (particularly transitions between male and female heterogamety) can be favoured in order to restore equal sex ratios in populations that have a sex ratio bias \citep{Bull:1983vi,Kozielska:2010vm,Ubeda:2015fx}.
+\noindent
+\textcolor{red}{We add haploid selection:}
 
-Sex ratios can also become biased due to meiotic drive;
-in a classic paper, \citet{Hamilton:1967ts} showed that X- or Y-linked alleles that experience meiotic drive will bias sex ratios. 
-He assumed that driving alleles are under directional selection and spread to fixation but such alleles can also be maintained at intermediate frequencies by selection \citep{Feldman:1989gm,Holman:2015en}.
-When sex ratios are biased, other loci are expected to evolve to restore equal sex ratios. 
-Indeed, alleles that negate the effect of sex-linked meiotic drivers and restore equal sex ratios have been identified \citep{Stalker:1961th,Smith:1975ft}. 
-A similar process occurs with cytoplasmic male sterility alleles (that cause biased sex ratios) and nuclear `restorer' genotypes \citep{Frank:1989vl}.
-
-When sex ratio bias occurs due to haploid selection, a natural class of sex ratio `restorers' exist because haploid selection often occurs in a context that is determined by the diploid parents. 
-For example, the intensity of pollen competition can be manipulated by altering style length \citep{Travers:2001,Lankinen:2001gc,Ruane:2009vt}, delaying stigma receptivity \citep{Galen:1986wq,Lankinen:2011if} and/or delaying pollen tube growth in the pistil \citep{Herrero:2003jf}.
-Where the X and Y have fixed fitness differences, \citet{Hough:2013uo} demonstrated that mothers should generally evolve to balance sex ratios by reducing the intensity of haploid competition. 
-However, reducing competition among haploids also reduces the potential for harmful deleterious mutations to be purged. 
-When deleterious mutations are included, the optimal intensity of haploid selection can reflect a balance between maximizing offspring fitness and equalizing sex ratios.
-
-As part of a collaborative project \citep{Otto:2015va}, I considered the evolution of the haploid `selective arena' in cases where the X chromosome harbours a polymorphism that affects haploid fitness.
-Mothers again primarily evolve to restore equal sex ratios.
-However, modifying haploid selection also affects the X-linked genotypes that are inherited by offspring. 
-Specifically, increasing the intensity of haploid selection increases the proportion of daughters (all progeny of X-bearing sperm/pollen are female) that inherit the allele with high haploid fitness. 
-If this allele has high fitness in daughters, mothers can be selected to increase the intensity of haploid selection; otherwise, decreased selection among haploids is favoured.
-Thus, because altering haploid selection intensity affects the alleles that are inherited by daughters, mothers can favour slightly biased sex ratios. 
-In addition, I found that stronger sex ratio biases can be favoured by paternal manipulations of the haploid `selective arena' because fathers are strongly selected to maximize their own siring success (above selection to equalize the sex ratio).
-
-It is not clear how the spread of new sex determination systems would be influenced by the combination of sex ratio biases and favourable associations between haploid selected loci and sex-determining regions.
-
-We add haploid selection (and justification, see below)
-\\
-Mention Hough study for sex ratio adjustment here or in discussion?
-Also discuss the fact that, in terms of recombination suppression, haploid selection among male gametes generates selection pressure similar to that of male specific selection.
-\\
-What will be the result: where there is sex biases and sex-specific selection
-
+Here, we use mathematical models to find the conditions under which new sex determination systems are favoured by selection where we include a period of selection among haploid gametes/gametophytes. 
 {\color{blue}
 FROM PREVIOUS PAPER:
-
-To the extent that pollen and sperm success reflects differences in their haploid genotypes, selection among these gametes/gametophytes is qualitatively distinct from selection among diploid males. 
-That is, diploids cannot be assigned fitness values that also account for the fitness of their haploid gametes \cite{Immler:2012tl}. 
 In plants, selection among haploid male gametophytes is thought to be pervasive \cite{SKOGSMYR:2002ce,Moore:2011jt,Marshall:2016fe}; in \textit{Arabidopsis}, 60-70\% of all genes are expressed during the haploid phase \cite{Borg:2009jpa}, and pollen expressed genes exhibit stronger signatures of purifying selection and positive selection \cite{Arunkumar:2013iq,Gossmann:2014dua}.
@@
 
+We add haploid selection (and justification, see below)
+\\
+Also discuss the fact that, in terms of recombination suppression, haploid selection among male gametes generates selection pressure similar to that of male specific selection. 
+\\
+What will be the result: where there is sex biases and sex-specific selection
+
 \textcolor{red}{NOTE RE: DRIVE.
@@
 
+DRAFT (improve): In \citet{Ubeda:2015fx}, the new sex determining locus spreads because it arises in linkage with a locus that experiences drive.
+They assume that drive occurs predominantly in one sex, e.g., during spermatogenesis or a 'killer' sperm.
+A driving allele is maintained at an intermediate frequency by selection, e.g., because it causes male sterility when homozygous (because all male sperm are killed).
+Y chromosomes that arise in linkage with the driving allele spread because they allow drive to occur more often, thus genetic sex determination with a sex ratio bias evolves.
+Thus \citet{Ubeda:2015fx} also find that genetic sex determiners can invade, despite causing sex ratios to become biased. 
+Finally, they show that autosomal 'restorers' that negate the effects of meiotic drive can invade and restore an equal sex ratio. 
+When sex ratio bias occurs due to haploid selection, a natural class of sex ratio `restorers' exist because haploid selection often occurs in a context that is determined by the diploid parents. 
+For example, the intensity of pollen competition can be manipulated by altering style length \citep{Travers:2001,Lankinen:2001gc,Ruane:2009vt}, delaying stigma receptivity \citep{Galen:1986wq,Lankinen:2011if} and/or delaying pollen tube growth in the pistil \citep{Herrero:2003jf}.
+Where the X and Y have fitness differences, \citet{Hough:2013uo} and \citet{Otto:2015va} demonstrated that mothers should generally evolve to balance sex ratios by reducing the intensity of haploid competition.
+
+{\color{blue}
+FROM THESIS:
+However, reducing competition among haploids also reduces the potential for harmful deleterious mutations to be purged. 
+When deleterious mutations are included, the optimal intensity of haploid selection can reflect a balance between maximizing offspring fitness and equalizing sex ratios.
+
+As part of a collaborative project \citep{Otto:2015va}, I considered the evolution of the haploid `selective arena' in cases where the X chromosome harbours a polymorphism that affects haploid fitness.
+Mothers again primarily evolve to restore equal sex ratios.
+However, modifying haploid selection also affects the X-linked genotypes that are inherited by offspring. 
+Specifically, increasing the intensity of haploid selection increases the proportion of daughters (all progeny of X-bearing sperm/pollen are female) that inherit the allele with high haploid fitness. 
+If this allele has high fitness in daughters, mothers can be selected to increase the intensity of haploid selection; otherwise, decreased selection among haploids is favoured.
+Thus, because altering haploid selection intensity affects the alleles that are inherited by daughters, mothers can favour slightly biased sex ratios. 
+In addition, I found that stronger sex ratio biases can be favoured by paternal manipulations of the haploid `selective arena' because fathers are strongly selected to maximize their own siring success (above selection to equalize the sex ratio).
+
+}
+
 {\color{blue}
@@
 A similar process occurs with cytoplasmic male sterility alleles (that cause biased sex ratios) and nuclear `restorer' genotypes \citep{Frank:1989vl}.
-
-When sex ratio bias occurs due to haploid selection, a natural class of sex ratio `restorers' exist because haploid selection often occurs in a context that is determined by the diploid parents. 
-For example, the intensity of pollen competition can be manipulated by altering style length \citep{Travers:2001,Lankinen:2001gc,Ruane:2009vt}, delaying stigma receptivity \citep{Galen:1986wq,Lankinen:2011if} and/or delaying pollen tube growth in the pistil \citep{Herrero:2003jf}.
-Where the X and Y have fixed fitness differences, \citet{Hough:2013uo} demonstrated that mothers should generally evolve to balance sex ratios by reducing the intensity of haploid competition. 
-However, reducing competition among haploids also reduces the potential for harmful deleterious mutations to be purged. 
-When deleterious mutations are included, the optimal intensity of haploid selection can reflect a balance between maximizing offspring fitness and equalizing sex ratios.
-
-As part of a collaborative project \citep{Otto:2015va}, I considered the evolution of the haploid `selective arena' in cases where the X chromosome harbours a polymorphism that affects haploid fitness.
-Mothers again primarily evolve to restore equal sex ratios.
-However, modifying haploid selection also affects the X-linked genotypes that are inherited by offspring. 
-Specifically, increasing the intensity of haploid selection increases the proportion of daughters (all progeny of X-bearing sperm/pollen are female) that inherit the allele with high haploid fitness. 
-If this allele has high fitness in daughters, mothers can be selected to increase the intensity of haploid selection; otherwise, decreased selection among haploids is favoured.
-Thus, because altering haploid selection intensity affects the alleles that are inherited by daughters, mothers can favour slightly biased sex ratios. 
-In addition, I found that stronger sex ratio biases can be favoured by paternal manipulations of the haploid `selective arena' because fathers are strongly selected to maximize their own siring success (above selection to equalize the sex ratio).
 

### 2016-08-30 LaTeX/Turnover.tex
Intro improved, not yet finished

@@
 I wonder if this is actually a fusion event though?
-In addition, many gonochoric/dioecious clades with genetic sex determination exhibit transitions between male (XY) and female (ZW) heterogamety, including eight of 26 teleost fish families \citep{Mank:2006bt}, true fruit flies \citep[Tephritids,][]{Vicoso:2015hf}, amphibians \citep{Hillis:1990gu}, the angiosperm genus \textit{Silene} \citep{Slancarova:2013dq}, Coleoptera and Hemiptera \citep[][plate 2]{Beukeboom:2014vb}.
-Indeed, in some cases, both male and female heterogametic sex determination systems can be found the same species, including cichlid species \citep{Ser:2010iq} and \textit{Rana rugosa} \citep{Ogata:2007jm}.
-
-\noindent
-Depending on the prominence of transitions to ESD in the manuscript include something like (currently quoted):
-
-``Transitions have repeatedly occurred between environmental sex determination and genotypic sex determination, as exemplified by the distribution of temperature sex determination among reptiles: either temperature or genes provide the initial trigger in closely related species (Ewert and Nelson 1991; Pokorna and Kratochvil 2009; Ezaz et al.
-2009) or even conspecific populations (Pen et al.
-2010).
-Similar situations are found in fishes (e.g., Conover and Heins 1978a).''
-
-\noindent
-We have results where polygenic sex determination is sometimes stable, may be worth mentioning:
-
-``Polygenic sex determination has been reported in many plants (e.g.
-Shannon \& Holsinger 2007), fishes (Vandeputte et al.
-2007; Ser et al.
-2010; Liew et al.
-2012), crustaceans (e.g.
-Battaglia 1958; Battaglia \& Malesani 1959; Voordouw
-\& Anholt 2002), bivalves (Haley 1977; Saavedra et al. 1997), gastropods (Yusa 2007a,b), and polychaetes (Bacci 1965, 1978; Premoli et al. 1996).''
-From Vuilleumier et al. 2007:
-``Polymorphism for sex-determining genes within oramong populations has been reported in many speciesincluding houseflies, midges, woodlice, platyfish, cichlidfish, and frogs (Gordon, 1944; Kallman, 1970; Thomp-son, 1971; Macdonald, 1978; Bull, 1983; Rigaud et al., 1997; Caubet et al., 2000; Lande et al., 2001; Ogataet al., 2003; Lee et al., 2004; Mank et al., 2006).
+In addition, many gonochoric/dioecious clades with genetic sex determination exhibit transitions between male (XY) and female (ZW) heterogamety, including lizards \citep{Ezaz:2009tk}, eight of 26 teleost fish families \citep{Mank:2006bt}, true fruit flies \citep[Tephritids,][]{Vicoso:2015hf}, amphibians \citep{Hillis:1990gu}, the angiosperm genus \textit{Silene} \citep{Slancarova:2013dq}, Coleoptera and Hemiptera \citep[][plate 2]{Beukeboom:2014vb}.
+Indeed, in some cases, both male and female heterogametic sex determination systems can be found the same species, as exhibited by some cichlid species \citep{Ser:2010iq} and \textit{Rana rugosa} \citep{Ogata:2007jm}.
+In addition, multiple transitions have occurred between genetic and environmental sex determination systems, e.g., in reptiles and fishes \citep{Conover:1987in,Mank:2006bt,Pokorna:2009ui,Ezaz:2009tk,Pen:2010kk,Holleley:2015hc}.
 
@@
 
-\noindent
-\textcolor{red}{Brief description of sex ratio adjustment and sexual antagonism theories:}
+%\textcolor{red}{Brief description of sex ratio adjustment and sexual antagonism theories:}
 
@@
 
-Sex ratio selection might be a particularly important force driving transitions between sex-determining systems \citep[Chapter 7]{Beukeboom:2014vb}. 
-For example, feminizing mutations may invade when female biased sex ratios are favoured due to interdemic selection \citep{Wilson:1981vm,Vuillleumier:2007bh}.
-In other cases, flexible sex determination systems may be favoured in order to exploit environmental conditions that are optimal for males or females, creating locally biased sex ratios \citep{Charnov:1977tx,Werren:1984tl,Pen:2010kk}.
+It has been suggested that sex ratio selection could be a particularly important force driving transitions between sex-determining systems \citep[Chapter 7]{Beukeboom:2014vb}. 
+For example, flexible sex determination systems may be favoured in order to exploit local environmental conditions that are optimal for males or females, which creates locally biased sex ratios \citep{Charnov:1977tx,Werren:1984tl,Pen:2010kk}.
+In addition, feminizing mutations may invade when female biased sex ratios are favoured due to selection among demes \citep{Wilson:1981vm,Vuillleumier:2007bh}. 
 In other situations, sex ratio selection may favour transitions in order to restore equal sex ratios. 
-For example, \citet{Kozielska:2010vm} consider systems in which the ancestral sex chromosomes experience meiotic drive (e.g., driving X or Y chromosomes are inherited disproportionately often), which leads to biased sex ratios.
-They find that new, unlinked sex-determining loci (masculinizing or feminizing mutations) can then spread, restoring an even sex ratio.
+For example, \citet{Kozielska:2010vm} consider systems in which the ancestral sex chromosomes experience meiotic drive (e.g., where driving X or Y chromosomes are inherited disproportionately often), which causes sex ratios to become biased \citep{Hamilton:1967ts}.
+They find that new, unlinked sex-determining loci (masculinizing or feminizing mutations, i.e., neo-Y or neo-W loci) can then spread, restoring an even sex ratio.
 
-\noindent
-\textcolor{red}{We add haploid selection:}
+%\textcolor{red}{We add haploid selection:}
 
 Here, we use mathematical models to find the conditions under which new sex determination systems are favoured by selection where we include a period of selection among haploid gametes/gametophytes. 
-{\color{blue}
-FROM PREVIOUS PAPER:
-In plants, selection among haploid male gametophytes is thought to be pervasive \cite{SKOGSMYR:2002ce,Moore:2011jt,Marshall:2016fe}; in \textit{Arabidopsis}, 60-70\% of all genes are expressed during the haploid phase \cite{Borg:2009jpa}, and pollen expressed genes exhibit stronger signatures of purifying selection and positive selection \cite{Arunkumar:2013iq,Gossmann:2014dua}.
-For agricultural breeding, pollen has been exposed to a variety of selection pressures \textit{in vivo} and \textit{in vitro}, including temperature \cite{Hedhly:2004iv,Clarke:2004ir}, herbicides \cite{Frascaroli:2001ee}, metals \cite{Searcy:1985vt}, water stress \cite{Ravikumar:2003uo}, and pathogens \cite{Ravikumar:2012ej}, resulting in an increased frequency of resistant genotypes among the diploid sporophytic offspring.
-In animals, expression during the haploid sperm stage is traditionally thought to be suppressed \cite{Hecht:1998hz}, although recent evidence suggests that the extent and selective importance of postmeiotic gene expression may be underestimated \cite{Zheng:2001fi,JOSEPH:2004haa,Vibranovski:2010et,Immler:2014im}.
-}
+Selection among haploid genotypes is thought to occur primarily among pollen/sperm, which can compete whenever there are more pollen/sperm than required for fertilization \citep{Mulcahy:1996ha,JOSEPH:2004haa}.
+Haploid selection may be particularly common in plants, in which 60-70\% of all genes are expressed in the male gametophyte and these genes exhibit stronger signatures of selection than random genes \citep{Borg:2009jpa,Arunkumar:2013iq,Gossmann:2014dua}.
+In addition, artificial selection pressures applied to male gametophytes cause the frequency of resistant alleles to increase \citep[e.g.,][]{Hormaza:1996cv,Ravikumar:2003uo,Hedhly:2004iv,Clarke:2004ir}.
+A smaller (but non-negligible) proportion of genes are thought to be expressed and selected in animal sperm, although precise estimates are uncertain \citep{Zheng:2001fi,JOSEPH:2004haa,Vibranovski:2010et}.
 
-Here, suggest that the canonical view (no haploid expression in animals, genome highly chromatinized in sperm and not expressed) might be based on model organisms, such as mice, where sperm is sufficiently short-lived that transcripts provisioned during spermatogenesis may be sufficient without further haploid transcription (although note that the Vibranovski lab results are in mice showing some transcription does occur).
-In broadcast spawning animal species (e.g., corals, many fish) and species where sperm typically requires greater longevity, expression of the haploid genotype may be required (Immler paper indicates this, but not that strongly - as I remember).
-We can use this suggestion in discussion to speculate in what species the processes we study might be looked for (i.e.., animals with multiple matings, broadcast spawning and/or long-lived sperm and outcrossing/non-pollen-limited plants).
+%Also discuss the fact that, in terms of recombination suppression, haploid selection among male gametes generates selection pressure similar to that of male specific selection. 
+%And sex ratio bias
 
-{\color{blue} 
-\noindent FROM PREVIOUS PAPER:
-
-The maintenance of polymorphism at loci that experience sex specific selection in both haploid and diploid phases was considered by Immler et al.
-\cite{Immler:2012tl}, demonstrating that polymorphisms can be maintained by sexually antagonistic selection or overdominance as well as by conflicting selection pressures in haploids and diploids (haploid-diploid conflict or ploidally antagonistic selection) or a combination of these selective regimes.
-
-}
-
-We add haploid selection (and justification, see below)
-\\
-Also discuss the fact that, in terms of recombination suppression, haploid selection among male gametes generates selection pressure similar to that of male specific selection. 
-\\
-What will be the result: where there is sex biases and sex-specific selection
+%What will be the result: where there is sex biases and sex-specific selection
 
@@
 So, do you think it would significantly enhance the paper to model drive explicitly or just discuss it as being similar???}
+
+{\color{blue} 
+FOR RESULTS?
+
+FROM PREVIOUS PAPER:
+The maintenance of polymorphism at loci that experience sex specific selection in both haploid and diploid phases was considered by Immler et al.
+\cite{Immler:2012tl}, demonstrating that polymorphisms can be maintained by sexually antagonistic selection or overdominance as well as by conflicting selection pressures in haploids and diploids (haploid-diploid conflict or ploidally antagonistic selection) or a combination of these selective regimes.
+}
 
@@
 Finally, they show that autosomal 'restorers' that negate the effects of meiotic drive can invade and restore an equal sex ratio. 
+OTHER RESTORERS.
+\textcolor{blue}{Indeed, alleles that negate the effect of sex-linked meiotic drivers and restore equal sex ratios have been identified \citep{Stalker:1961th,Smith:1975ft}. 
+A similar process occurs with cytoplasmic male sterility alleles (that cause biased sex ratios) and nuclear `restorer' genotypes \citep{Frank:1989vl}. 
+}
 When sex ratio bias occurs due to haploid selection, a natural class of sex ratio `restorers' exist because haploid selection often occurs in a context that is determined by the diploid parents. 
@@
 
+\textcolor{red}{\noindent Discuss patterns that might be looked for:}
+
+In broadcast spawning animal species (e.g., corals, many fish) and species where sperm typically requires greater longevity, haploid selection may be stronger because transcripts shared during spermatogenesis may become depleted \citep{Immler:2014im}.
+\textcolor{red}{also, mating systems (e.g., fewer alleles are available during haploid competition in monogamous species), selfing rates, and estimates of pollen limitation could be used as indicators of the intensity of haploid selection}
+
+\noindent
+We have results where polygenic sex determination is sometimes stable, may be worth mentioning:
+
+``Polygenic sex determination has been reported in many plants (e.g.
+Shannon \& Holsinger 2007), fishes (Vandeputte et al.
+2007; Ser et al.
+2010; Liew et al.
+2012), crustaceans (e.g.
+Battaglia 1958; Battaglia \& Malesani 1959; Voordouw
+\& Anholt 2002), bivalves (Haley 1977; Saavedra et al. 1997), gastropods (Yusa 2007a,b), and polychaetes (Bacci 1965, 1978; Premoli et al. 1996).''
+From Vuilleumier et al. 2007:
+``Polymorphism for sex-determining genes within oramong populations has been reported in many speciesincluding houseflies, midges, woodlice, platyfish, cichlidfish, and frogs (Gordon, 1944; Kallman, 1970; Thomp-son, 1971; Macdonald, 1978; Bull, 1983; Rigaud et al., 1997; Caubet et al., 2000; Lande et al., 2001; Ogataet al., 2003; Lee et al., 2004; Mank et al., 2006).
+
 {\color{blue}
-FROM THESIS:
-Generally, any sex-linked gene that harbours genetic variation in haploid fitness should cause sex ratios to become biased. 
-Sex ratio bias caused by pollen competition has previously been discussed in the context of Y-linked deleterious mutations, which are thought to build up after recombination suppression evolves \citep{Lloyd:1974tz,Stehlik:2005ul}.
-Sex ratios can also become biased due to meiotic drive;
-in a classic paper, \citet{Hamilton:1967ts} showed that X- or Y-linked alleles that experience meiotic drive will bias sex ratios. 
-He assumed that driving alleles are under directional selection and spread to fixation but such alleles can also be maintained at intermediate frequencies by selection \citep{Feldman:1989gm,Holman:2015en}.
-When sex ratios are biased, other loci are expected to evolve to restore equal sex ratios. 
-Indeed, alleles that negate the effect of sex-linked meiotic drivers and restore equal sex ratios have been identified \citep{Stalker:1961th,Smith:1975ft}. 
-A similar process occurs with cytoplasmic male sterility alleles (that cause biased sex ratios) and nuclear `restorer' genotypes \citep{Frank:1989vl}.
-
 Several aspects of the relationship between haploid selection (e.g., pollen or sperm competition) and sex ratios remain to be explored. 

### 2016-08-30 LaTeX/Turnover.tex
started results section

--- 2016-08-30 LaTeX/Turnover.tex
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Model}
+%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%genetic system
+We will consider a three locus model.
+Locus \textbf{X} is the ancestral sex-determining region (SDR), with alleles $X$ and $Y$ (or $Z$ and $W$).
+Locus \textbf{A} is a region under selection, with alleles $A$ and $a$.
+And locus \textbf{M} is a novel sex-determining region, with alleles $M$ and $m$.
+With genotype $MM$ at locus \textbf{M}, the sex of a zygote is determined by the genotype at locus \textbf{X} ($XX$ become females and $XY$ males, or $ZW$ become females and $ZZ$ males).
+With at least one $m$ allele at locus \textbf{M}, a zygote develops as a female with probability $k$ and as a male with probability $1-k$.
+With $k=0$, the novel sex determiner is a masculinizer (e.g., a neo-Y chromosome) and with $k=1$ the novel sex determiner is a feminizer (e.g, a neo-W chromosome).
+With intermediate $k$, locus \textbf{M} is interpreted as an environmental sex-determining region.
+
+%life-cycle
+The life-cycle begins with haploid gametes/gametophytes experiencing selection that depends on their allele at the \textbf{A} locus.
+Gametes/gametophytes from males then mate randomly with gametes/gametophytes from females.
+The resulting zygotes develop as males or females, depending on their genotypes at the \textbf{X} and \textbf{M} loci.
+There is then a period of diploid selection that again depends on genotypes at the \textbf{A} locus, followed by meiosis with recombination. 
+Recombination occurs between loci \textbf{X} and \textbf{A} with probability $r$, between loci \textbf{A} and \textbf{M} with probability $R$, and between loci \textbf{X} and \textbf{M} with probability $\chi$.
+%is chi really the prob of rec in our recursion equations?
+Any order of the loci can be modelled with appropriate choices of $r$, $R$, and $\chi$.
+We track the frequency of haploid genotypes produced by each sex from one generation to the next (recursion equations in Sup.\ Mat.).
+
+%what were going to do, briefly
+With allele $M$ fixed at the \textbf{M} locus, sex is determined by locus \textbf{X} and an equilibrium is reached at locus \textbf{A}.
+%where, importantly, locus \textbf{A} can be stably polymorphic.
+%the dynamics can be described by the frequency of $A$ in gametes/gametophytes from the homogametic sex and the frequencies of $A$ in the two types of gametes/gametophytes from the heterogametic sex.
+We then examine the ability of a rare, novel sex-determiner $m$ to increase in frequency at this equilibrium.
+Numerical simulations are used to examine when an invading mutation goes to fixation.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Results}
+%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%resident equilibrium
+With allele $M$ fixed, we follow the dynamics of the frequency of $A$ in gametes/gametophytes from the homogametic sex (e.g., in eggs from an XX female, $p_{Xf}$) and the frequencies of $A$ in the two types of gametes/gametophytes from the heterogametic sex (e.g., in sperm from an XY male that are X-bearing, $p_{Xm}$, and Y-bearing, $p_{Ym}$).
+Assuming selection is weak relative to recombination, the differences in the frequencies of $A$ in each type of gamete/gametophyte are small, and we can solve for the mean frequency of $A$ across all types ($p_A$) as well as the difference in the frequencies of $A$ between two of the three types, to first order in selection.
+Linear stability analysis can then be used to determine the stability of this equilibrium.
+Without haploid selection this reduces to the results of \citep{vanDoorn:2010hu}.
+
+%external stability/turnover
+
 \linenumbers

### 2016-08-30 LaTeX/Turnover.tex
Intro first draft completed

@@
 Predominant theories in which new sex determination systems are favoured by selection involve fitness differences between sexes (e.g., sexually antagonistic selection) or sex ratio selection.
+%\citet{Bull:1977wt} shows that direct selection on new sex determination loci can allow them to spread and switch between male and female heterogamety. 
 \citet{vanDoorn:2007eu,vanDoorn:2010hu} show that new sex determination loci can be favoured if they arise in close linkage with a locus that experiences sexual antagonism. 
@@
 
-%Also discuss the fact that, in terms of recombination suppression, haploid selection among male gametes generates selection pressure similar to that of male specific selection. 
-%And sex ratio bias
+There are various ways in which a period of haploid selection could influence transitions between sex determination systems. 
+Firstly, if we assume that haploid selection at any particular locus predominantly occurs in one sex (e.g., pollen/sperm competition), then such loci experience a form of sex-specific selection. 
+In this respect, we might expect that haploid selection might affect transitions between sex determination systems in a similar manner to sex-specific diploid selection \citep[as explored by][]{vanDoorn:2007eu,vanDoorn:2010hu}.
+That is, new masculizing mutations (neo-Y chromosomes) could be favoured via linkage associations with alleles that are beneficial in pollen/sperm. 
+However, sex ratios can also become biased if there is linkage between the sex-determining region and a locus that harbours genetic variation in haploid fitness. 
+For example, differences in fitness between X- and Y-bearing pollen tubes can cause the sex ratio among seeds to become biased when there is pollen competition \citep{Lloyd:1974tz,Conn:1981uw,Stehlik:2005ul,Stehlik:2006to,Field:2012fd,Field:2013cc}.
+It is not immediately clear how the spread of new sex determination systems would be influenced by the combination of sex ratio biases and favourable associations between haploid selected loci and sex-determining regions.
 
-%What will be the result: where there is sex biases and sex-specific selection
+Surprisingly, our models show that haploid selection influences the evolution of new sex determination systems in a way that is distinct from both diploid sex-specific selection and sex ratio selection.
+We find that new genetic sex determination systems are not affected by any sex ratio biases caused by associations between sex-determining regions and haploid selected loci. 
+In addition, we find that associations that build up between an ancestral sex-determining locus and a haploid-selected locus can favour transitions between male and female heterogamety (e.g., a neo-Z/neo-W locus spreads in an ancestrally XY system), despite the fact that these ancestral associations were built up by selection.
+This does not occur in models that do not include haploid selection.
 
@@
 {\color{blue}
-Several aspects of the relationship between haploid selection (e.g., pollen or sperm competition) and sex ratios remain to be explored. 
-For example, new sex-determining systems (particularly transitions between male and female heterogamety) can be favoured in order to restore equal sex ratios in populations that have a sex ratio bias \citep{Bull:1983vi,Kozielska:2010vm,Ubeda:2015fx}.
-Based on the results of Chapter \ref{ch:sexchromosomes}, we would expect that sex ratio biases would occur via associations between sex-determining loci and loci that experience haploid selection. 
-However, these associations should also select against transitions between sex-determining systems, as has been found with sexually antagonistic selection \citep{vanDoorn:2007eu,vanDoorn:2010hu}. 
-It is not clear how the spread of new sex determination systems would be influenced by the combination of sex ratio biases and favourable associations between haploid selected loci and sex-determining regions.
+(Check with Jim Bull that it's ok before including this speculation:)
 Finally, \citet{Hamilton:1967ts} pointed out that biased sex ratios can affect population size because the number of offspring in each generation is typically determined by the number of females. 

### 2016-08-31 LaTeX/Turnover.tex
intro draft completed

@@
 
+Brief results summary.
+
 DRAFT (improve): In \citet{Ubeda:2015fx}, the new sex determining locus spreads because it arises in linkage with a locus that experiences drive.
@@
 From Vuilleumier et al. 2007:
-``Polymorphism for sex-determining genes within oramong populations has been reported in many speciesincluding houseflies, midges, woodlice, platyfish, cichlidfish, and frogs (Gordon, 1944; Kallman, 1970; Thomp-son, 1971; Macdonald, 1978; Bull, 1983; Rigaud et al., 1997; Caubet et al., 2000; Lande et al., 2001; Ogataet al., 2003; Lee et al., 2004; Mank et al., 2006).
+``Polymorphism for sex-determining genes within or among populations has been reported in many species including houseflies, midges, woodlice, platyfish, cichlid fish, and frogs (Gordon, 1944; Kallman, 1970; Thomp-son, 1971; Macdonald, 1978; Bull, 1983; Rigaud et al., 1997; Caubet et al., 2000; Lande et al., 2001; Ogataet al., 2003; Lee et al., 2004; Mank et al., 2006).''
 

### 2016-08-31 LaTeX/Turnover.tex
lambdas added

--- 2016-08-30 LaTeX/Turnover.tex
@@
 %life-cycle
-The life-cycle begins with haploid gametes/gametophytes experiencing selection that depends on their allele at the \textbf{A} locus.
+The life-cycle begins with competition between haploid gametes/gametophytes within each sex, where selection depends on the sex of the diploid they came from and their allele at the \textbf{A} locus.
 Gametes/gametophytes from males then mate randomly with gametes/gametophytes from females.
 The resulting zygotes develop as males or females, depending on their genotypes at the \textbf{X} and \textbf{M} loci.
-There is then a period of diploid selection that again depends on genotypes at the \textbf{A} locus, followed by meiosis with recombination. 
+Diploids then compete with others of the same sex, where selection depends on the sex of the individual and its genotype at the \textbf{A} locus.
+This is followed by meiosis with recombination. 
 Recombination occurs between loci \textbf{X} and \textbf{A} with probability $r$, between loci \textbf{A} and \textbf{M} with probability $R$, and between loci \textbf{X} and \textbf{M} with probability $\chi$.
@@
 
-%resident equilibrium
+\subsection*{Resident equilibrium and stability}
 With allele $M$ fixed, we follow the dynamics of the frequency of $A$ in gametes/gametophytes from the homogametic sex (e.g., in eggs from an XX female, $p_{Xf}$) and the frequencies of $A$ in the two types of gametes/gametophytes from the heterogametic sex (e.g., in sperm from an XY male that are X-bearing, $p_{Xm}$, and Y-bearing, $p_{Ym}$).
@@
 Linear stability analysis can then be used to determine the stability of this equilibrium.
-Without haploid selection this reduces to the results of \citep{vanDoorn:2010hu}.
+With no haploid selection and $k=0$ (neo-$Y$ invading a $ZW$ system) or $k=1$ (neo-$W$ invading an $XY$ system), our results reduce to those of \cite{vanDoorn:2010hu}.
 
-%external stability/turnover
+\subsection*{Sex chromosome turnover}
+The spread of a rare mutant $m$ at the \textbf{M} locus in such a population is determined by the leading eigenvalue, $\lambda$, of the system described by the equations for the next generation frequency of haploid genotypes with the mutation.
+%, evaluated at the above equilibrium.
+Below we present the results for invasion into an $XY$ system assuming equal dominance coefficients in the two sexes, no competition among gametes/gametophytes from females, and linear arrangement \textbf{X}\textbf{A}\textbf{M}.
+Equivalent results for invasions into a $ZW$ system are given in the Sup.\ Mat.
+
+\subsubsection*{Neo-$Y$}
+
+The growth rate of a rare, dominant neo-$Y$ region ($k=0$) is
+\begin{equation}
+\lambda_{Y,XY} = 1 + V_A \frac{(r - R)}{r R} \frac{s_f^2}{\left( s_f + s_m \right)^2} t_m^2,
+\end{equation}
+where $V_A = p_A(1-p_A)$ is the variance at the \textbf{A} locus, $s_f$ and $s_m$ are the respective selection coefficients for $A$ in diploid females and males, and $t_m$ is the selection coefficient for $A$ in gametes/gametophytes from males.
+The neo-Y can therefore invade whenever it is in tighter linkage with the selected locus than the ancestral sex-determining locus, $r>R$, provided locus \textbf{A} is polymorphic ($V_A>0$) and there is selection among females ($s_f\neq0$) and gametes/gametophytes from males ($t_m\neq0$).
+%write in general form without weak selection
+
+\subsubsection*{Neo-$W$}
+
+The growth rate of a rare, dominant neo-$W$ region ($k=1$) is
+\begin{equation}
+\lambda_{W,XY} = 1 + V_A \frac{s_f \left( (2 r (1-R) +R) s_f + (1- 2r) R s_m \right)}{2 r R \left( s_f + s_m \right)^2} t_m^2.
+\end{equation}
+In this case, even when the novel sex-determining locus is in looser linkage with the selected locus than is the ancestral sex-determining locus, $r<R$, a novel sex-determiner can invade.
+For example, with $R=1/2$ the neo-W invades if there is some linkage between the ancestral sex-determining and selected loci ($r<1/2$), there is selection among gametes/gametophytes in males ($t_m\neq0$), and there is selection for or against $A$ in both males and females ($s_m s_f >0$) that is stronger in females than in males ($|s_f| > |s_m|$).
+%write in general form without weak selection
+
+\subsubsection*{Neo-ESD}
+
+The growth rate of a rare, dominant neo-ESD region that produces males or females with equal probability ($k=1/2$) is
+\begin{equation}
+\lambda_{ESD,XY} = 1 + \frac{(\lambda_{Y,XY} - 1) + (\lambda_{W,XY} -1)}{4} \Big|_{R=1/2}
+%V_A \frac{r}{1-2r}  \frac{s_{f} \left( s_m - 3 s_f\right) }{8 \left( s_{f} + s_{m} \right)^2} t_{m}^2.
+\end{equation}
+Thus the $k=1/2$ case gets half of the advantages of a neo-$W$ and half that of a neo-$Y$.  
+Recombination between the selected locus and the novel sex-determining locus, $R$, doesn't enter into the $k=1/2$ results because sex is essentially randomized each generation, %as if the novel sex-determiner were on an unlinked site that half the time acts as a neo-$W$ and half the time as a neo-$Y$.
+preventing associations from building up between allele $A$ and sex.  
+%write in general form without weak selection
 

### 2016-09-04 LaTeX/Turnover.tex
working on general formulation for all

@@
 %genetic system
-We will consider a three locus model.
+We consider a three locus model.
 Locus \textbf{X} is the ancestral sex-determining region (SDR), with alleles $X$ and $Y$ (or $Z$ and $W$).
@@
 %life-cycle
-The life-cycle begins with competition between haploid gametes/gametophytes within each sex, where selection depends on the sex of the diploid they came from and their allele at the \textbf{A} locus.
+The life-cycle begins with competition between haploid gametes/gametophytes from each sex, where selection depends on the sex of the diploid they came from and their allele at the \textbf{A} locus.
 Gametes/gametophytes from males then mate randomly with gametes/gametophytes from females.
 The resulting zygotes develop as males or females, depending on their genotypes at the \textbf{X} and \textbf{M} loci.
-Diploids then compete with others of the same sex, where selection depends on the sex of the individual and its genotype at the \textbf{A} locus.
+Diploids compete with others of the same sex, where selection depends on the sex of the individual and its genotype at the \textbf{A} locus.
 This is followed by meiosis with recombination. 
@@
 %the dynamics can be described by the frequency of $A$ in gametes/gametophytes from the homogametic sex and the frequencies of $A$ in the two types of gametes/gametophytes from the heterogametic sex.
-We then examine the ability of a rare, novel sex-determiner $m$ to increase in frequency at this equilibrium.
+We then examine the ability of a rare, novel sex-determiner, $m$, to increase in frequency from this equilibrium.
 Numerical simulations are used to examine when an invading mutation goes to fixation.

### 2016-09-05 LaTeX/Turnover.tex
deriving non-weak selection invasion criteria

@@
 
-The growth rate of a rare, dominant neo-$Y$ region ($k=0$) is
+%write in general form without weak selection
+Without assuming weak selection, a rare, dominant neo-$Y$ ($k=0$) will invade when the average invasion fitness of $XAy$ and $Yay$ haplotypes is greater than one, $(\lambda_A + \lambda_a)/2 >1$ (where $\lambda_i$ are the two eigenvalues when $R=r=0$).
+When the average invasion fitness of the haplotypes is less than one the neo-$Y$ does not invade.
+Otherwise neo-$Y$ invasion requires
 \begin{equation}
-\lambda_{Y,XY} = 1 + V_A \frac{(r - R)}{r R} \frac{s_f^2}{\left( s_f + s_m \right)^2} t_m^2,
+r R \left[ \frac{p_{Xf} w_{m,a}}{\lambda_a - 1} + \frac{(1 - p_{Xf}) w_{m,A}}{\lambda_A - 1} \right] w_{m,Aa} < \nu_m
+\end{equation}
+where $w_{m,i}$ is the relative viability fitness of males depending on their genotype at the \textbf{A} locus (with $i\in\{AA,Aa,aa\}$), and 
+$\nu_m = 
+  p_{Xf} p_{Ym} w_{a,m} w_{AA,m} +
+  p_{Xf} (1-p_{Ym}) w_{a,m} w_{Aa,m} +
+  (1-p_{Xf}) p_{Ym} w_{a,m} w_{Aa,m} +
+  (1-p_{Xf}) (1-p_{Ym}) w_{a, m} w_{aa,m}$
+is the mean relative fitness of resident males.
+Neo-$Y$ invasion therefore occurs for any recombination rates, $r$ and $R$, when the term inside the square brackets is negative.
+This occurs when the net flow of recombinants is from the less fit haplotype to the more fit.
+Assuming $\lambda_A>1$ and $\lambda_a<1$ without loss of generality, this is $(1 - p_{Xf}) w_{m,A} (\lambda_a -1) < p_{Xf} w_{m,a} (\lambda_A -1)$.
+When the net flow of recombinants is from the more fit haplotype to the less fit, neo-$Y$ invasion can still occur when the rates of recombination are small enough.
+
+%weak selection
+Assuming weak selection, we can solve for the invasion fitness of the neo-$Y$ more directly, giving
+\begin{equation}
+\lambda_{Y,XY} \approx 1 + V_A \frac{(r - R)}{r R} \frac{s_f^2}{\left( s_f + s_m \right)^2} t_m^2,
 \end{equation}
 where $V_A = p_A(1-p_A)$ is the variance at the \textbf{A} locus, $s_f$ and $s_m$ are the respective selection coefficients for $A$ in diploid females and males, and $t_m$ is the selection coefficient for $A$ in gametes/gametophytes from males.
-The neo-Y can therefore invade whenever it is in tighter linkage with the selected locus than the ancestral sex-determining locus, $r>R$, provided locus \textbf{A} is polymorphic ($V_A>0$) and there is selection among females ($s_f\neq0$) and gametes/gametophytes from males ($t_m\neq0$).
-%write in general form without weak selection
+The neo-$Y$ can therefore invade whenever it is in tighter linkage with the selected locus than the ancestral sex-determining locus, $r>R$, provided locus \textbf{A} is polymorphic ($V_A>0$) and there is selection among females ($s_f\neq0$) and gametes/gametophytes from males ($t_m\neq0$).
 
@@
 
-The growth rate of a rare, dominant neo-$W$ region ($k=1$) is
+%write in general form without weak selection
+Without assuming weak selection, a rare, dominant neo-$W$ ($k=1$) will invade when the average invasion fitness of $XAW$ and $XaW$ haplotypes is greater than one, $(\lambda_A + \lambda_a)/2 > 1$ (the two eigenvalues when $R=0$).
+When the average invasion fitness of the haplotypes is less than one the neo-$W$ does not invade.
+Otherwise neo-$W$ invasion requires
 \begin{equation}
-\lambda_{W,XY} = 1 + V_A \frac{s_f \left( (2 r (1-R) +R) s_f + (1- 2r) R s_m \right)}{2 r R \left( s_f + s_m \right)^2} t_m^2.
+R \left[ \frac{\bar{p}_m w_{m,A}}{\lambda_a - 1} + \frac{(1 - \bar{p}_m) w_{m,a}}{\lambda_A - 1} \right] w_{f,Aa} < \nu_f
+\end{equation}
+where $\bar{p}_m = (p_{Ym}+p_{Xm}) / 2$ is the mean frequency of $A$ in gametes/gametophytes from males, $w_{f,i}$ is the relative viability fitness of females depending on their genotype at the \textbf{A} locus (with $i\in\{AA,Aa,aa\}$), and
+$\nu_f = 
+  p_{Xf} p_{Xm} w_{a,m} w_{AA,f} +
+  p_{Xf} (1-p_{Xm}) w_{a,m} w_{Aa,f} +
+  (1-p_{Xf}) p_{Xm} w_{a,m} w_{Aa,f} +
+  (1-p_{Xf}) (1-p_{Xm}) w_{a, m} w_{aa,f}$
+is the mean relative fitness of resident females. 
+The rate of recombination between the \textbf{X} and \textbf{A} loci, $r$, does not explicitly appear (in contrast to the neo-$W$ case) because females are homozygous at the \textbf{X} locus with an $XY$ system.
+Neo-$W$ invasion therefore occurs with any recombination rate, $R$, when the term inside the square brackets is negative.
+This occurs when the net flow of recombinants is from the less fit haplotype to the more fit.
+Assuming $\lambda_A>1$ and $\lambda_a<1$ without loss of generality, this is $(1 - \bar{p}_m) w_{m,a} (\lambda_a -1) < \bar{p}_m w_{m,A} (\lambda_A -1)$.
+When the net flow of recombinants is from the more fit haplotype to the less fit, neo-$W$ invasion can still occur when the rate of recombination is small enough.
+
+%weak selection
+Assuming weak selection, we can solve for the invasion fitness of the neo-$W$ more directly, giving
+\begin{equation}
+\lambda_{W,XY} \approx 1 + V_A \frac{s_f \left( (2 r (1-R) +R) s_f + (1- 2r) R s_m \right)}{2 r R \left( s_f + s_m \right)^2} t_m^2.
 \end{equation}
 In this case, even when the novel sex-determining locus is in looser linkage with the selected locus than is the ancestral sex-determining locus, $r<R$, a novel sex-determiner can invade.
-For example, with $R=1/2$ the neo-W invades if there is some linkage between the ancestral sex-determining and selected loci ($r<1/2$), there is selection among gametes/gametophytes in males ($t_m\neq0$), and there is selection for or against $A$ in both males and females ($s_m s_f >0$) that is stronger in females than in males ($|s_f| > |s_m|$).
-%write in general form without weak selection
+For example, with $R=1/2$ the neo-$W$ invades if there is some linkage between the ancestral sex-determining and selected loci ($r<1/2$), there is selection among gametes/gametophytes in males ($t_m\neq0$), and there is selection for or against $A$ in both males and females ($s_m s_f >0$) that is stronger in females than in males ($|s_f| > |s_m|$).
 
@@
 \begin{equation}
-\lambda_{ESD,XY} = 1 + \frac{(\lambda_{Y,XY} - 1) + (\lambda_{W,XY} -1)}{4} \Big|_{R=1/2}
+\lambda_{ESD,XY} \approx 1 + \frac{(\lambda_{Y,XY} - 1) + (\lambda_{W,XY} -1)}{4} \Big|_{R=1/2}
 %V_A \frac{r}{1-2r}  \frac{s_{f} \left( s_m - 3 s_f\right) }{8 \left( s_{f} + s_{m} \right)^2} t_{m}^2.

### 2016-09-06 LaTeX/Turnover.tex
general solutions for W and Y invasions finished

--- 2016-09-04 LaTeX/Turnover.tex
@@
 Linear stability analysis can then be used to determine the stability of this equilibrium.
-With no haploid selection and $k=0$ (neo-$Y$ invading a $ZW$ system) or $k=1$ (neo-$W$ invading an $XY$ system), our results reduce to those of \cite{vanDoorn:2010hu}.
+With no haploid selection our results reduce to those of \cite{vanDoorn:2010hu} when $k=0$ (neo-$Y$ invading a $ZW$ system) or when $k=1$ (neo-$W$ invading an $XY$ system).
 
@@
 %, evaluated at the above equilibrium.
-Below we present the results for invasion into an $XY$ system assuming equal dominance coefficients in the two sexes, no competition among gametes/gametophytes from females, and linear arrangement \textbf{X}\textbf{A}\textbf{M}.
+Below we present the results for invasion into an $XY$ system assuming no competition among gametes/gametophytes from females, and linear arrangement \textbf{X}\textbf{A}\textbf{M}.
+%equal dominance coefficients in the two sexes,
 Equivalent results for invasions into a $ZW$ system are given in the Sup.\ Mat.
@@
 
-The growth rate of a rare, dominant neo-$Y$ region ($k=0$) is
+%write in general form without weak selection
+A rare, dominant neo-$Y$ ($k=0$) is always expected to invade the ancestral $XY$ system when the average growth rate of mutant haplotypes ($XAm$ and $Yam$) is positive, $(g_A + g_a)/2 > 0$ (growth rate is unaffected by the allele at the \textbf{X} locus, but recombination between it and the other loci can still destroy the haplotype).
+%($g_i = where $\lambda_i$ are the two eigenvalues when $R=r=0$; the \textbf{X} locus does not affect the dynamics).
+Defining $g_i^*$ as the growth rate of $Xm$ and $Ym$ haplotypes when on an $A$ ($i=A$) or $a$ background ($i=a$), then $g_i^* < g_i$, and if the $Xm$ and $Ym$ haplotypes decline on both \textbf{A} backgrounds ($g_i^* < 0 \; \forall \; i$) the neo-$Y$ does not invade.
+Otherwise, the $Xm$ and $Ym$ haplotypes grow on one \textbf{A} background and decline on the other and neo-$Y$ invasion requires
 \begin{equation}
-\lambda_{Y,XY} = 1 + V_A \frac{(r - R)}{r R} \frac{s_f^2}{\left( s_f + s_m \right)^2} t_m^2,
+r R \left[ \frac{p_{Xf} w_{m,a}}{g_a^*} + \frac{(1 - p_{Xf}) w_{m,A}}{g_A^*} \right] w_{m,Aa} < \nu_m,
+\end{equation}
+where $w_{m,i}$ is the relative viability fitness of males depending on their haploid or diploid genotype at the \textbf{A} locus (with $i\in\{A,a,AA,Aa,aa\}$) and
+$\nu_m = 
+  p_{Xf} p_{Ym} w_{a,m} w_{AA,m} +
+  p_{Xf} (1-p_{Ym}) w_{a,m} w_{Aa,m} +
+  (1-p_{Xf}) p_{Ym} w_{a,m} w_{Aa,m} +
+  (1-p_{Xf}) (1-p_{Ym}) w_{a, m} w_{aa,m}$
+is the mean relative fitness of resident males.
+%and $g_j^*$ is the growth rate of $Xm$ and $Ym$ haplotypes when on an $A$ ($j=A$)  or $a$ background ($j=a$).
+Neo-$Y$ invasion therefore occurs for any recombination rates, $r$ and $R$, when the net flow of double recombinants is from the less fit to the more fit \textbf{A} background (making the term inside the square brackets negative).
+%Assuming $g_A^* > 0$ and $g_a^* < 0$ without loss of generality, this is $-(1 - p_{Xf}) w_{m,A} g_a^* < p_{Xf} w_{m,a} g_A^*$.
+When the net flow of double recombinants is from the more fit to the less fit haplotype, neo-$Y$ invasion can still occur when the rates of recombination are small enough.
+
+%weak selection
+Assuming weak selection, we can solve for the invasion fitness of the neo-$Y$ explicitly, giving
+\begin{equation}
+\lambda_{Y,XY} \approx 1 + V_A \frac{(r - R)}{r R} \frac{s_f^2}{\left( s_f + s_m \right)^2} t_m^2,
 \end{equation}
 where $V_A = p_A(1-p_A)$ is the variance at the \textbf{A} locus, $s_f$ and $s_m$ are the respective selection coefficients for $A$ in diploid females and males, and $t_m$ is the selection coefficient for $A$ in gametes/gametophytes from males.
-The neo-Y can therefore invade whenever it is in tighter linkage with the selected locus than the ancestral sex-determining locus, $r>R$, provided locus \textbf{A} is polymorphic ($V_A>0$) and there is selection among females ($s_f\neq0$) and gametes/gametophytes from males ($t_m\neq0$).
-%write in general form without weak selection
+The neo-$Y$ can therefore invade whenever it is in tighter linkage with the selected locus than the ancestral sex-determining locus, $r>R$, provided locus \textbf{A} is polymorphic ($V_A>0$) and there is selection among both females ($s_f\neq0$) and gametes/gametophytes from males ($t_m\neq0$).
 
@@
 
-The growth rate of a rare, dominant neo-$W$ region ($k=1$) is
+%write in general form without weak selection
+Similarly, a rare, dominant neo-$W$ ($k=1$) will invade the ancestral $XY$ system whenever the average growth rate of $XAm$ and $Xam$ haplotypes is positive, $(g_A + g_a) / 2 > 1$. 
+When the growth rates of mutant haplotypes without recombination ($R=0$) are negative, $g_i^* < 0 \; \forall \; i \in \{A,a\}$, where $g_i < g_i^*$, the neo-$W$ does not invade.
+Otherwise neo-$W$ invasion requires
 \begin{equation}
-\lambda_{W,XY} = 1 + V_A \frac{s_f \left( (2 r (1-R) +R) s_f + (1- 2r) R s_m \right)}{2 r R \left( s_f + s_m \right)^2} t_m^2.
+R \left[ \frac{\bar{p}_m w_{m,A}}{g_a^*} + \frac{(1 - \bar{p}_m) w_{m,a}}{g_A^*} \right] w_{f,Aa} < \nu_f
+\end{equation}
+where $\bar{p}_m = (p_{Ym}+p_{Xm}) / 2$ is the mean frequency of $A$ in gametes/gametophytes from males, $w_{f,i}$ is the relative viability fitness of females depending on their diploid genotype at the \textbf{A} locus (with $i\in\{AA,Aa,aa\}$), and
+$\nu_f = 
+  p_{Xf} p_{Xm} w_{a,m} w_{AA,f} +
+  p_{Xf} (1-p_{Xm}) w_{a,m} w_{Aa,f} +
+  (1-p_{Xf}) p_{Xm} w_{a,m} w_{Aa,f} +
+  (1-p_{Xf}) (1-p_{Xm}) w_{a, m} w_{aa,f}$
+is the mean relative fitness of resident females. 
+%The rate of recombination between the \textbf{X} and \textbf{A} loci, $r$, does not explicitly appear because females are homozygous at the \textbf{X} locus with an ancestral $XY$ system.
+As in the case of the neo-$Y$, neo-$W$ invasion therefore occurs with any recombination rate, $R$, when the net flow of recombinants is from the less fit to the more fit haplotype.
+%Assuming $g_A^*>0$ and $g_a^*<0$ without loss of generality, this is $(1 - \bar{p}_m) w_{m,a} g_a^*< \bar{p}_m w_{m,A} g_A^*$.
+And when the net flow of recombinants is from the more fit to the less fit  haplotype, neo-$W$ invasion can still occur when the rate of recombination is small enough.
+
+%weak selection
+Assuming weak selection, we can solve for the invasion fitness of the neo-$W$ explicitly, giving
+\begin{equation}
+\lambda_{W,XY} \approx 1 + V_A \frac{s_f \left( (2 r (1-R) +R) s_f + (1- 2r) R s_m \right)}{2 r R \left( s_f + s_m \right)^2} t_m^2.
 \end{equation}
 In this case, even when the novel sex-determining locus is in looser linkage with the selected locus than is the ancestral sex-determining locus, $r<R$, a novel sex-determiner can invade.
-For example, with $R=1/2$ the neo-W invades if there is some linkage between the ancestral sex-determining and selected loci ($r<1/2$), there is selection among gametes/gametophytes in males ($t_m\neq0$), and there is selection for or against $A$ in both males and females ($s_m s_f >0$) that is stronger in females than in males ($|s_f| > |s_m|$).
-%write in general form without weak selection
+For example, with $R=1/2$ the neo-$W$ invades if there is any linkage between the ancestral sex-determining and selected loci ($r<1/2$), there is selection among gametes/gametophytes in males ($t_m\neq0$), and there is selection for or against $A$ in both males and females ($s_m s_f >0$) that is stronger in females than in males ($|s_f| > |s_m|$).
 
@@
 \begin{equation}
-\lambda_{ESD,XY} = 1 + \frac{(\lambda_{Y,XY} - 1) + (\lambda_{W,XY} -1)}{4} \Big|_{R=1/2}
+\lambda_{ESD,XY} \approx 1 + \frac{(\lambda_{Y,XY} - 1) + (\lambda_{W,XY} -1)}{4} \Big|_{R=1/2}
 %V_A \frac{r}{1-2r}  \frac{s_{f} \left( s_m - 3 s_f\right) }{8 \left( s_{f} + s_{m} \right)^2} t_{m}^2.
 \end{equation}
-Thus the $k=1/2$ case gets half of the advantages of a neo-$W$ and half that of a neo-$Y$.  
+Thus the $k=1/2$ case gets half of the advantages of a neo-$W$ and half that of a neo-$Y$ (BUT WHY THE 4?).  
 Recombination between the selected locus and the novel sex-determining locus, $R$, doesn't enter into the $k=1/2$ results because sex is essentially randomized each generation, %as if the novel sex-determiner were on an unlinked site that half the time acts as a neo-$W$ and half the time as a neo-$Y$.

### 2016-09-06 LaTeX/Turnover.tex
working on maternal ESD results

@@
 With $k=0$, the novel sex determiner is a masculinizer (e.g., a neo-Y chromosome) and with $k=1$ the novel sex determiner is a feminizer (e.g, a neo-W chromosome).
-With intermediate $k$, locus \textbf{M} is interpreted as an environmental sex-determining region.
+With intermediate $k$, locus \textbf{M} is interpreted as an offspring controlled environmental sex-determining region.
+Finally, we also analyze a model of maternally-controlled environmental sex-determination, where mothers with at least one $m$ allele produce daughters with probability $k$.
 
@@
 Gametes/gametophytes from males then mate randomly with gametes/gametophytes from females.
-The resulting zygotes develop as males or females, depending on their genotypes at the \textbf{X} and \textbf{M} loci.
+The resulting zygotes develop as males or females, depending on their genotypes at the \textbf{X} and \textbf{M} loci (or the \textbf{M} genotype of their mother).
 Diploids compete with others of the same sex, where selection depends on the sex of the individual and its genotype at the \textbf{A} locus.
@@
 %, evaluated at the above equilibrium.
-Below we present the results for invasion into an $XY$ system assuming no competition among gametes/gametophytes from females, and linear arrangement \textbf{X}\textbf{A}\textbf{M}.
+Below we present the results for invasion into an $XY$ system assuming no competition among gametes/gametophytes from females and linear arrangement \textbf{X}\textbf{A}\textbf{M}.
 %equal dominance coefficients in the two sexes,
@@
 \begin{equation}
-\lambda_{Y,XY} \approx 1 + V_A \frac{(r - R)}{r R} \frac{s_f^2}{\left( s_f + s_m \right)^2} t_m^2,
+\lambda_{Y,XY} \approx 1 + V_A \frac{(r - R)s_f}{r R} \frac{s_f}{\left( s_f + s_m \right)^2} t_m^2,
 \end{equation}
-where $V_A = p_A(1-p_A)$ is the variance at the \textbf{A} locus, $s_f$ and $s_m$ are the respective selection coefficients for $A$ in diploid females and males, and $t_m$ is the selection coefficient for $A$ in gametes/gametophytes from males.
+where $V_A = p_A(1-p_A)$ is the variance at the \textbf{A} locus, $s_f$ and $s_m$ are the respective selection coefficients for $A$ in diploid females and males, $t_m$ is the selection coefficient for $A$ in gametes/gametophytes from males, and we've assumed equal dominance coefficients in the two sexes.
 The neo-$Y$ can therefore invade whenever it is in tighter linkage with the selected locus than the ancestral sex-determining locus, $r>R$, provided locus \textbf{A} is polymorphic ($V_A>0$) and there is selection among both females ($s_f\neq0$) and gametes/gametophytes from males ($t_m\neq0$).
@@
 \begin{equation}
-\lambda_{W,XY} \approx 1 + V_A \frac{s_f \left( (2 r (1-R) +R) s_f + (1- 2r) R s_m \right)}{2 r R \left( s_f + s_m \right)^2} t_m^2.
+\lambda_{W,XY} \approx 1 + V_A \frac{(2r(1-R)-R) s_f + (1-2r)R s_m }{2 r R} \frac{s_f}{ \left( s_f + s_m \right)^2} t_m^2,
 \end{equation}
+where we've once again assumed equal dominance coefficients in the two sexes.
 In this case, even when the novel sex-determining locus is in looser linkage with the selected locus than is the ancestral sex-determining locus, $r<R$, a novel sex-determiner can invade.
@@
 
-\subsubsection*{Neo-ESD}
+\subsubsection*{Offspring-controlled neo-ESD}
 
-The growth rate of a rare, dominant neo-ESD region that produces males or females with equal probability ($k=1/2$) is
+The growth rate of a rare, dominant offspring-controlled neo-ESD region that produces males or females with equal probability ($k=1/2$) is
 \begin{equation}
-\lambda_{ESD,XY} \approx 1 + \frac{(\lambda_{Y,XY} - 1) + (\lambda_{W,XY} -1)}{4} \Big|_{R=1/2}
+\lambda_{ESD,XY} \approx 1 + \frac{1}{2}\frac{(\lambda_{Y,XY} - 1) + (\lambda_{W,XY} -1)}{2} \Big|_{R=1/2}
 %V_A \frac{r}{1-2r}  \frac{s_{f} \left( s_m - 3 s_f\right) }{8 \left( s_{f} + s_{m} \right)^2} t_{m}^2.
 \end{equation}
-Thus the $k=1/2$ case gets half of the advantages of a neo-$W$ and half that of a neo-$Y$ (BUT WHY THE 4?).  
+Thus with $k=1/2$ the neo-ESD gets half of the advantages of a neo-$W$ and half that of a neo-$Y$, but only has an effect one half of the time (the other half of the time it produces the same sex as the ancestral system would have).
 Recombination between the selected locus and the novel sex-determining locus, $R$, doesn't enter into the $k=1/2$ results because sex is essentially randomized each generation, %as if the novel sex-determiner were on an unlinked site that half the time acts as a neo-$W$ and half the time as a neo-$Y$.
 preventing associations from building up between allele $A$ and sex.
-%write in general form without weak selection
+
+\subsubsection*{Maternally-controlled neo-ESD}
+
+For all $k$ that we explore, the invasion fitness can be written
+
+\begin{equation}
+\lambda \approx 1 + V_A C_k B,
+\end{equation}
+where
+%\begin{equation}
+%V_A = \frac{- \left[ t_m + h (s_{f}+s_{m}) \right] \left[ t_m + (1-h) (s_{f}+s_{m}) \right]}{(1-2h)^2(s_{f}+s_{m})^2}
+%\end{equation}
+%is the variance in $A$ ($V_A>0$ when the polymorphic resident equilibrium is stable), 
+%with $h$ the dominance coefficient (equal in both sexes), 
+\begin{equation}
+B = \frac{s_f}{2r R(s_{f}+s_{m})^2} t_m^2
+\end{equation}
+and $C_k$ is a term that depends on $k$:
+
+%k=0
+\begin{equation}
+C_0 = 
+\end{equation}
+
+%k=1
+\begin{equation}
+C_1 = - \left[ (2r(1-R)-R) s_f + (1-2r)R s_m \right]
+\end{equation}
+
+%k=1/2
+\begin{equation}
+C_{1/2} = 
+\end{equation}
+
+In the case of $k=1$ the maternal and offspring controlled results are the same (which makes sense because we are here concerned only with the passage of mutations through females).
 

### 2016-09-07 LaTeX/Turnover.tex
cleaning up maternal ESD results

@@
 %, evaluated at the above equilibrium.
-Below we present the results for invasion into an $XY$ system assuming no competition among gametes/gametophytes from females and linear arrangement \textbf{X}\textbf{A}\textbf{M}.
+Below we present the results for invasion into an $XY$ system assuming no competition among gametes/gametophytes from females and linear arrangement \textbf{X}\textbf{A}\textbf{M} (SAY SOMETHING HERE ABOUT OTHER ARRANGEMENTS).
 %equal dominance coefficients in the two sexes,
-Equivalent results for invasions into a $ZW$ system are given in the Sup.\ Mat.
+Equivalent results for invasions into a $ZW$ system can be derived by consistently switching the roles of males and females \citep{vanDoorn:2010hu}.
 
@@
 \begin{equation}
-\lambda_{Y,XY} \approx 1 + V_A \frac{(r - R)s_f}{r R} \frac{s_f}{\left( s_f + s_m \right)^2} t_m^2,
+\lambda_{Y,XY} \approx 1 + V_A S_A (r - R)s_f,
 \end{equation}
-where $V_A = p_A(1-p_A)$ is the variance at the \textbf{A} locus, $s_f$ and $s_m$ are the respective selection coefficients for $A$ in diploid females and males, $t_m$ is the selection coefficient for $A$ in gametes/gametophytes from males, and we've assumed equal dominance coefficients in the two sexes.
+where $V_A = p_A(1-p_A)$ is the variance at the \textbf{A} locus, $S_A = s_f/ \left[ r R \left( s_f + s_m \right)^2 t_m^2 \right]$ (INTERPRETATION), $s_f$ and $s_m$ are the respective selection coefficients for $A$ in diploid females and males, $t_m$ is the selection coefficient for $A$ in gametes/gametophytes from males, and we've assumed equal dominance coefficients in the two sexes.
 The neo-$Y$ can therefore invade whenever it is in tighter linkage with the selected locus than the ancestral sex-determining locus, $r>R$, provided locus \textbf{A} is polymorphic ($V_A>0$) and there is selection among both females ($s_f\neq0$) and gametes/gametophytes from males ($t_m\neq0$).
@@
 \begin{equation}
-\lambda_{W,XY} \approx 1 + V_A \frac{(2r(1-R)-R) s_f + (1-2r)R s_m }{2 r R} \frac{s_f}{ \left( s_f + s_m \right)^2} t_m^2,
+\lambda_{W,XY} \approx 1 + V_A S_A \frac{(2r(1-R)-R) s_f + (1-2r)R s_m }{2},
 \end{equation}
@@
 \begin{equation}
-\lambda \approx 1 + V_A C_k B,
+\lambda \approx 1 + V_A S_A C_k,
 \end{equation}
@@
 %with $h$ the dominance coefficient (equal in both sexes), 
-\begin{equation}
-B = \frac{s_f}{2r R(s_{f}+s_{m})^2} t_m^2
-\end{equation}
-and $C_k$ is a term that depends on $k$:
+$C_k$ is a term that depends on $k$:
 
@@
 \begin{equation}
-C_0 = 
+C_0 = big \; ugly \; term
 \end{equation}
@@
 \begin{equation}
-C_1 = - \left[ (2r(1-R)-R) s_f + (1-2r)R s_m \right]
+C_1 = \frac{\left[ (2r(1-R)-R) s_f + (1-2r)R s_m \right]}{2}
 \end{equation}
@@
 \begin{equation}
-C_{1/2} = 
+C_{1/2} = even \; bigger, \; uglier \; term
 \end{equation}
 
-In the case of $k=1$ the maternal and offspring controlled results are the same (which makes sense because we are here concerned only with the passage of mutations through females).
+In the case of $k=1$ the maternal- and offspring-controlled results are the same since mutation is then only concerned with the passage of mutations through females.
+However, with $k\neq0$ the mutant dynamics differ.
 

### 2016-09-15 LaTeX/Turnover.tex
maternal case solved?

--- 2016-09-06 LaTeX/Turnover.tex
@@
 \subsection*{Resident equilibrium and stability}
-With allele $M$ fixed, we follow the dynamics of the frequency of $A$ in gametes/gametophytes from the homogametic sex (e.g., in eggs from an XX female, $p_{Xf}$) and the frequencies of $A$ in the two types of gametes/gametophytes from the heterogametic sex (e.g., in sperm from an XY male that are X-bearing, $p_{Xm}$, and Y-bearing, $p_{Ym}$).
+With allele $M$ fixed, we follow the dynamics of the frequency of $A$ in gametes/gametophytes from the homogametic sex (e.g., in eggs from an XX female, $p^f_X$) and the frequencies of $A$ in the two types of gametes/gametophytes from the heterogametic sex (e.g., in sperm from an XY male that are X-bearing, $p^m_X$, and Y-bearing, $p^m_Y$).
 Assuming selection is weak relative to recombination, the differences in the frequencies of $A$ in each type of gamete/gametophyte are small, and we can solve for the mean frequency of $A$ across all types ($p_A$) as well as the difference in the frequencies of $A$ between two of the three types, to first order in selection.
@@
 Below we present the results for invasion into an $XY$ system assuming no competition among gametes/gametophytes from females and linear arrangement \textbf{X}\textbf{A}\textbf{M}.
+%(SAY SOMETHING HERE ABOUT OTHER ARRANGEMENTS?).
 %equal dominance coefficients in the two sexes,
-Equivalent results for invasions into a $ZW$ system are given in the Sup.\ Mat.
+Equivalent results for invasions into a $ZW$ system can be derived by consistently switching the roles of males and females \citep{vanDoorn:2010hu}.
 
-\subsubsection*{Neo-$Y$}
+%\subsubsection*{Neo-$Y$}
+%
+%%write in general form without weak selection
+%A rare, dominant neo-$Y$ ($k=0$) is always expected to invade the ancestral $XY$ system when the average growth rate of mutant haplotypes ($Am$ and $am$) is positive, $(g_A + g_a)/2 > 0$.
+%($g_i = where $\lambda_i$ are the two eigenvalues when $R=r=0$; the \textbf{X} locus does not affect the dynamics).
+%When the growth rates of the mutant haplotypes without recombination ($R=0$) are negative, $g_i^* < 0 \; \forall \; i \in \{A,a\}$, where $g_i < g_i^*$, the neo-$Y$ does not invade.
+%Otherwise, the mutant allele increases in frequency on one \textbf{A} background and declines on the other and neo-$Y$ invasion requires
+%\begin{equation}
+%R \left[ \frac{p^f_X w_{m,a}}{g_A^*} + \frac{(1 - p^f_X) w_{m,A}}{g_a^*} \right] w_{m,Aa} < \nu_m,
+%\end{equation}
+%where $w_{m,i}$ is the relative viability fitness of males depending on their haploid or diploid genotype at the \textbf{A} locus (with $i\in\{A,a,AA,Aa,aa\}$) and
+%$\nu_m = 
+%  p^f_X p_{Ym} w^m_{a} w^m_{AA} +
+%  p^f_X (1-p_{Ym}) w^m_{a} w^m_{AA} +
+%  (1-p^f_X) p_{Ym} w^m_{a} w^m_{AA} +
+%  (1-p^f_X) (1-p_{Ym}) w^m_a w^m_{AA}$
+%is the mean relative fitness of resident males.
+%%and $g_j^*$ is the growth rate of $X^m$ and $Ym$ haplotypes when on an $A$ ($j=A$)  or $a$ background ($j=a$).
+%Neo-$Y$ invasion therefore occurs for any recombination rate, $R$, when the net flow of double recombinants is from the less fit to the more fit \textbf{A} background (making the term inside the square brackets negative).
+%%Assuming $g_A^* > 0$ and $g_a^* < 0$ without loss of generality, this is $-(1 - p^f_X) w_{m,A} g_a^* < p^f_X w_{m,a} g_A^*$.
+%When the net flow of double recombinants is from the more fit to the less fit haplotype, neo-$Y$ invasion can still occur when the rate of recombination is small enough.
+%
+%%weak selection
+%Assuming weak selection, we can solve for the invasion fitness of the neo-$Y$ explicitly, giving
+%\begin{equation}
+%\lambda_{Y,XY} \approx 1 + V_A S_A (r - R)s^f,
+%\end{equation}
+%where $V_A = p_A(1-p_A)$ is the variance at the \textbf{A} locus, $S_A = s^f/ \left[ r R \left( s^f + s^m \right)^2 t_m^2 \right]$ (INTERPRETATION), $s^f$ and $s^m$ are the respective selection coefficients for $A$ in diploid females and males, $t_m$ is the selection coefficient for $A$ in gametes/gametophytes from males, and we've assumed equal dominance coefficients in the two sexes.
+%The neo-$Y$ can therefore invade whenever it is in tighter linkage with the selected locus than the ancestral sex-determining locus, $r>R$, provided locus \textbf{A} is polymorphic ($V_A>0$) and there is selection among both females ($s^f\neq0$) and gametes/gametophytes from males ($t_m\neq0$).
+%
+%\subsubsection*{Neo-$W$}
+%
+%%write in general form without weak selection
+%Similarly, a rare, dominant neo-$W$ ($k=1$) will invade the ancestral $XY$ system whenever the average growth rate of $XAm$ and $Xam$ haplotypes is positive, $(g_A + g_a) / 2 > 1$. 
+%When the growth rates of the mutant haplotypes without recombination ($R=0$) are negative, $g_i^* < 0 \; \forall \; i \in \{A,a\}$, where $g_i < g_i^*$, the neo-$W$ does not invade.
+%Otherwise neo-$W$ invasion requires
+%\begin{equation}
+%R \left[ \frac{\bar{p}_m w_{m,A}}{g_a^*} + \frac{(1 - \bar{p}_m) w_{m,a}}{g_A^*} \right] w_{f,Aa} < \nu_f
+%\end{equation}
+%where $\bar{p}_m = (p_{Ym}+p^m_X) / 2$ is the mean frequency of $A$ in gametes/gametophytes from males, $w_{f,i}$ is the relative viability fitness of females depending on their diploid genotype at the \textbf{A} locus (with $i\in\{AA,Aa,aa\}$), and
+%$\nu_f = 
+%  p^f_X p^m_X w^m_{a} w_{AA,f} +
+%  p^f_X (1-p^m_X) w^m_{a} w_{Aa,f} +
+%  (1-p^f_X) p^m_X w^m_{a} w_{Aa,f} +
+%  (1-p^f_X) (1-p^m_X) w^m_a w_{aa,f}$
+%is the mean relative fitness of resident females. 
+%%The rate of recombination between the \textbf{X} and \textbf{A} loci, $r$, does not explicitly appear because females are homozygous at the \textbf{X} locus with an ancestral $XY$ system.
+%As in the case of the neo-$Y$, neo-$W$ invasion therefore occurs with any recombination rate, $R$, when the net flow of recombinants is from the less fit to the more fit haplotype.
+%%Assuming $g_A^*>0$ and $g_a^*<0$ without loss of generality, this is $(1 - \bar{p}_m) w_{m,a} g_a^*< \bar{p}_m w_{m,A} g_A^*$.
+%And when the net flow of recombinants is from the more fit to the less fit  haplotype, neo-$W$ invasion can still occur when the rate of recombination is small enough.
+%
+%%weak selection
+%Assuming weak selection, we can solve for the invasion fitness of the neo-$W$ explicitly, giving
+%\begin{equation}
+%\lambda_{W,XY} \approx 1 + V_A S_A \frac{(2r(1-R)-R) s^f + (1-2r)R s^m }{2},
+%\end{equation}
+%where we've once again assumed equal dominance coefficients in the two sexes.
+%In this case, even when the novel sex-determining locus is in looser linkage with the selected locus than is the ancestral sex-determining locus, $r<R$, a novel sex-determiner can invade.
+%For example, with $R=1/2$ the neo-$W$ invades if there is any linkage between the ancestral sex-determining and selected loci ($r<1/2$), there is selection among gametes/gametophytes in males ($t_m\neq0$), and there is selection for or against $A$ in both males and females ($s^m s^f >0$) that is stronger in females than in males ($|s^f| > |s^m|$).
+
+\subsubsection*{Neo-$Y$ and neo-$W$}
 
 %write in general form without weak selection
-A rare, dominant neo-$Y$ ($k=0$) is always expected to invade the ancestral $XY$ system when the average growth rate of mutant haplotypes ($XAm$ and $Yam$) is positive, $(g_A + g_a)/2 > 0$ (growth rate is unaffected by the allele at the \textbf{X} locus, but recombination between it and the other loci can still destroy the haplotype).
+A rare, dominant neo-$Y$ ($k=0$) or neo-$W$ ($k=1$) is always expected to invade an ancestral $XY$ system when the average growth rate of the mutant haplotypes ($Am$ and $am$) is positive, $(g_A + g_a)/2 > 0$.
 %($g_i = where $\lambda_i$ are the two eigenvalues when $R=r=0$; the \textbf{X} locus does not affect the dynamics).
-Defining $g_i^*$ as the growth rate of $Xm$ and $Ym$ haplotypes when on an $A$ ($i=A$) or $a$ background ($i=a$), then $g_i^* < g_i$, and if the $Xm$ and $Ym$ haplotypes decline on both \textbf{A} backgrounds ($g_i^* < 0 \; \forall \; i$) the neo-$Y$ does not invade.
-Otherwise, the $Xm$ and $Ym$ haplotypes grow on one \textbf{A} background and decline on the other and neo-$Y$ invasion requires
-\begin{equation}
-r R \left[ \frac{p_{Xf} w_{m,a}}{g_a^*} + \frac{(1 - p_{Xf}) w_{m,A}}{g_A^*} \right] w_{m,Aa} < \nu_m,
+When the growth rates of the mutant haplotypes without recombination ($R=0$) are negative, $g_i^* < 0 \; \forall \; i \in \{A,a\}$, where $g_i < g_i^*$, the new sex-determining allele does not invade.
+
+Otherwise, the new sex-determining allele increases in frequency on one \textbf{A} background and declines on the other and invasion requires
+\begin{equation}\label{eq:neoYR}
+R \left[ \frac{p^f_X w^m_a}{g_A^*} + \frac{(1 - p^f_X) w^m_A}{g_a^*} \right] w^m_{Aa} < \nu^m,
 \end{equation}
-where $w_{m,i}$ is the relative viability fitness of males depending on their haploid or diploid genotype at the \textbf{A} locus (with $i\in\{A,a,AA,Aa,aa\}$) and
-$\nu_m = 
-  p_{Xf} p_{Ym} w_{a,m} w_{AA,m} +
-  p_{Xf} (1-p_{Ym}) w_{a,m} w_{Aa,m} +
-  (1-p_{Xf}) p_{Ym} w_{a,m} w_{Aa,m} +
-  (1-p_{Xf}) (1-p_{Ym}) w_{a, m} w_{aa,m}$
-is the mean relative fitness of resident males.
-%and $g_j^*$ is the growth rate of $Xm$ and $Ym$ haplotypes when on an $A$ ($j=A$)  or $a$ background ($j=a$).
-Neo-$Y$ invasion therefore occurs for any recombination rates, $r$ and $R$, when the net flow of double recombinants is from the less fit to the more fit \textbf{A} background (making the term inside the square brackets negative).
-%Assuming $g_A^* > 0$ and $g_a^* < 0$ without loss of generality, this is $-(1 - p_{Xf}) w_{m,A} g_a^* < p_{Xf} w_{m,a} g_A^*$.
-When the net flow of double recombinants is from the more fit to the less fit haplotype, neo-$Y$ invasion can still occur when the rates of recombination are small enough.
+for the neo-$Y$, and 
+\begin{equation}\label{eq:neoWR}
+R \left[  \frac{(1 - \bar{p}^m) w^m_{a}}{g_A^*} + \frac{\bar{p}^m w^m_{A}}{g_a^*} \right] w^f_{Aa} < \nu^f
+\end{equation}
+for the neo-$W$.
+Here $\bar{p}^m = (p^m_X+p^m_Y)/2$ is the average frequency of $A$ in males, $w^i_{j}$ is the relative viability fitness of sex $i\in\{m,f\}$ depending on their haploid or diploid genotype at the \textbf{A} locus (with $j\in\{A,a,AA,Aa,aa\}$) and
+$\nu^i = 
+  p^f_X p^m_{\textbf{X}^i} w^m_{a} w^i_{AA} +
+  p^f_X (1-p^m_{\textbf{X}^i}) w^m_{a} w^i_{Aa} +
+  (1-p^f_X) p^m_{\textbf{X}^i} w^m_{a} w^i_{Aa} +
+  (1-p^f_X) (1-p^m_{\textbf{X}^i}) w^m_a w^i_{aa}$,
+with $\textbf{X}^m = Y$ and $\textbf{X}^f = X$, is the mean relative fitness of resident individuals of sex $i$.
+%and $g_j^*$ is the growth rate of $X^m$ and $Ym$ haplotypes when on an $A$ ($j=A$)  or $a$ background ($j=a$).
+
+The new sex-determining allele is therefore expected to invade for any recombination rate, $R$, when the net flow of double recombinants is from the less fit to the more fit \textbf{A} background (making the term inside the square brackets negative).
+%Assuming $g_A^* > 0$ and $g_a^* < 0$ without loss of generality, this is $-(1 - p^f_X) w_{m,A} g_a^* < p^f_X w_{m,a} g_A^*$.
+When the net flow of double recombinants is from the more fit to the less fit haplotype, the new sex-determining allele can still invade when the rate of recombination between it and the selected locus is small enough.
 
 %weak selection
-Assuming weak selection, we can solve for the invasion fitness of the neo-$Y$ explicitly, giving
+Assuming weak selection, we can solve for the invasion fitness of the new sex -determining alleles explicitly, giving
 \begin{equation}
-\lambda_{Y,XY} \approx 1 + V_A \frac{(r - R)s_f}{r R} \frac{s_f}{\left( s_f + s_m \right)^2} t_m^2,
+\lambda_{m,XY} \approx 1 + V_A S_A C_m,
 \end{equation}
-where $V_A = p_A(1-p_A)$ is the variance at the \textbf{A} locus, $s_f$ and $s_m$ are the respective selection coefficients for $A$ in diploid females and males, $t_m$ is the selection coefficient for $A$ in gametes/gametophytes from males, and we've assumed equal dominance coefficients in the two sexes.
-The neo-$Y$ can therefore invade whenever it is in tighter linkage with the selected locus than the ancestral sex-determining locus, $r>R$, provided locus \textbf{A} is polymorphic ($V_A>0$) and there is selection among both females ($s_f\neq0$) and gametes/gametophytes from males ($t_m\neq0$).
+where $V_A = p_A(1-p_A)$ is the variance at the \textbf{A} locus, $S_A = s^f (t^m)^2 / \left[ r R \left( s^f + s^m \right)^2 \right]$ (INTERPRETATION?), $s^f$ and $s^m$ are the respective selection coefficients for $A$ in diploid females and males, $t^m$ is the selection coefficient for $A$ in gametes/gametophytes from males, and we've assumed equal dominance coefficients in the two sexes.
 
-\subsubsection*{Neo-$W$}
+For the neo-$Y$ we have $C_Y = (r - R)s^f $.
+The neo-$Y$ can therefore invade whenever it is in tighter linkage with the selected locus than the ancestral sex-determining locus, $r>R$, provided locus \textbf{A} is polymorphic ($V_A>0$) and there is selection among both females ($s^f\neq0$) and gametes/gametophytes from males ($t^m\neq0$).
 
-%write in general form without weak selection
-Similarly, a rare, dominant neo-$W$ ($k=1$) will invade the ancestral $XY$ system whenever the average growth rate of $XAm$ and $Xam$ haplotypes is positive, $(g_A + g_a) / 2 > 1$. 
-When the growth rates of mutant haplotypes without recombination ($R=0$) are negative, $g_i^* < 0 \; \forall \; i \in \{A,a\}$, where $g_i < g_i^*$, the neo-$W$ does not invade.
-Otherwise neo-$W$ invasion requires
-\begin{equation}
-R \left[ \frac{\bar{p}_m w_{m,A}}{g_a^*} + \frac{(1 - \bar{p}_m) w_{m,a}}{g_A^*} \right] w_{f,Aa} < \nu_f
-\end{equation}
-where $\bar{p}_m = (p_{Ym}+p_{Xm}) / 2$ is the mean frequency of $A$ in gametes/gametophytes from males, $w_{f,i}$ is the relative viability fitness of females depending on their diploid genotype at the \textbf{A} locus (with $i\in\{AA,Aa,aa\}$), and
-$\nu_f = 
-  p_{Xf} p_{Xm} w_{a,m} w_{AA,f} +
-  p_{Xf} (1-p_{Xm}) w_{a,m} w_{Aa,f} +
-  (1-p_{Xf}) p_{Xm} w_{a,m} w_{Aa,f} +
-  (1-p_{Xf}) (1-p_{Xm}) w_{a, m} w_{aa,f}$
-is the mean relative fitness of resident females. 
-%The rate of recombination between the \textbf{X} and \textbf{A} loci, $r$, does not explicitly appear because females are homozygous at the \textbf{X} locus with an ancestral $XY$ system.
-As in the case of the neo-$Y$, neo-$W$ invasion therefore occurs with any recombination rate, $R$, when the net flow of recombinants is from the less fit to the more fit haplotype.
-%Assuming $g_A^*>0$ and $g_a^*<0$ without loss of generality, this is $(1 - \bar{p}_m) w_{m,a} g_a^*< \bar{p}_m w_{m,A} g_A^*$.
-And when the net flow of recombinants is from the more fit to the less fit  haplotype, neo-$W$ invasion can still occur when the rate of recombination is small enough.
+For the neo-$W$ we have $C_W = [(2r(1-R)-R) s^f + (1-2r)R s^m]/2$.
+In this case, even when the novel sex-determining locus is in looser linkage with the selected locus than is the ancestral sex-determining locus, $r<R$, a neo-$W$ can invade.
+For example, with $R=1/2$ the neo-$W$ invades if there is any linkage between the ancestral sex-determining and selected loci ($r<1/2$), there is selection among gametes/gametophytes in males ($t^m\neq0$), and there is selection for or against $A$ in both males and females ($s^m s^f >0$) that is stronger in females than in males ($|s^f| > |s^m|$).
 
-%weak selection
-Assuming weak selection, we can solve for the invasion fitness of the neo-$W$ explicitly, giving
-\begin{equation}
-\lambda_{W,XY} \approx 1 + V_A \frac{(2r(1-R)-R) s_f + (1-2r)R s_m }{2 r R} \frac{s_f}{ \left( s_f + s_m \right)^2} t_m^2,
-\end{equation}
-where we've once again assumed equal dominance coefficients in the two sexes.
-In this case, even when the novel sex-determining locus is in looser linkage with the selected locus than is the ancestral sex-determining locus, $r<R$, a novel sex-determiner can invade.
-For example, with $R=1/2$ the neo-$W$ invades if there is any linkage between the ancestral sex-determining and selected loci ($r<1/2$), there is selection among gametes/gametophytes in males ($t_m\neq0$), and there is selection for or against $A$ in both males and females ($s_m s_f >0$) that is stronger in females than in males ($|s_f| > |s_m|$).
+%\subsubsection*{Neo-$W$}
+%
+%%write in general form without weak selection
+%Similarly, a rare, dominant neo-$W$ ($k=1$) will invade the ancestral $XY$ system whenever the average growth rate of $XAm$ and $Xam$ haplotypes is positive, $(g_A + g_a) / 2 > 1$. 
+%When the growth rates of the mutant haplotypes without recombination ($R=0$) are negative, $g_i^* < 0 \; \forall \; i \in \{A,a\}$, where $g_i < g_i^*$, the neo-$W$ does not invade.
+%Otherwise neo-$W$ invasion requires
+%\begin{equation}
+%R \left[ \frac{\bar{p}_m w_{m,A}}{g_a^*} + \frac{(1 - \bar{p}_m) w_{m,a}}{g_A^*} \right] w_{f,Aa} < \nu_f
+%\end{equation}
+%where $\bar{p}_m = (p_{Ym}+p^m_X) / 2$ is the mean frequency of $A$ in gametes/gametophytes from males, $w_{f,i}$ is the relative viability fitness of females depending on their diploid genotype at the \textbf{A} locus (with $i\in\{AA,Aa,aa\}$), and
+%$\nu_f = 
+%  p^f_X p^m_X w^m_{a} w_{AA,f} +
+%  p^f_X (1-p^m_X) w^m_{a} w_{Aa,f} +
+%  (1-p^f_X) p^m_X w^m_{a} w_{Aa,f} +
+%  (1-p^f_X) (1-p^m_X) w^m_a w_{aa,f}$
+%is the mean relative fitness of resident females. 
+%%The rate of recombination between the \textbf{X} and \textbf{A} loci, $r$, does not explicitly appear because females are homozygous at the \textbf{X} locus with an ancestral $XY$ system.
+%As in the case of the neo-$Y$, neo-$W$ invasion therefore occurs with any recombination rate, $R$, when the net flow of recombinants is from the less fit to the more fit haplotype.
+%%Assuming $g_A^*>0$ and $g_a^*<0$ without loss of generality, this is $(1 - \bar{p}_m) w_{m,a} g_a^*< \bar{p}_m w_{m,A} g_A^*$.
+%And when the net flow of recombinants is from the more fit to the less fit  haplotype, neo-$W$ invasion can still occur when the rate of recombination is small enough.
+%
+%%weak selection
+%Assuming weak selection, we can solve for the invasion fitness of the neo-$W$ explicitly, giving
+%\begin{equation}
+%\lambda_{W,XY} \approx 1 + V_A S_A \frac{(2r(1-R)-R) s^f + (1-2r)R s^m }{2},
+%\end{equation}
+%where we've once again assumed equal dominance coefficients in the two sexes.
+%In this case, even when the novel sex-determining locus is in looser linkage with the selected locus than is the ancestral sex-determining locus, $r<R$, a novel sex-determiner can invade.
+%For example, with $R=1/2$ the neo-$W$ invades if there is any linkage between the ancestral sex-determining and selected loci ($r<1/2$), there is selection among gametes/gametophytes in males ($t_m\neq0$), and there is selection for or against $A$ in both males and females ($s^m s^f >0$) that is stronger in females than in males ($|s^f| > |s^m|$).
 
@@
 \lambda_{ESD,XY} \approx 1 + \frac{1}{2}\frac{(\lambda_{Y,XY} - 1) + (\lambda_{W,XY} -1)}{2} \Big|_{R=1/2}
-%V_A \frac{r}{1-2r}  \frac{s_{f} \left( s_m - 3 s_f\right) }{8 \left( s_{f} + s_{m} \right)^2} t_{m}^2.
+%V_A \frac{r}{1-2r}  \frac{s_{f} \left( s^m - 3 s^f\right) }{8 \left( s_{f} + s_{m} \right)^2} t_{m}^2.
 \end{equation}
@@
 
-For all $k$ that we explore, the invasion fitness can be written
-
+One might think that when the sex of a zygote is under the control of its mother, there would be strong selection to balance the sex ratio among zygotes. 
+However, we find that, as with offspring control, assuming weak selection the invasion fitness of a sex-determiner that is maternally controlled can be written
 \begin{equation}
-\lambda \approx 1 + V_A C_k B,
+\lambda_{k,XY} \approx 1 + V_A S_A C_k,
 \end{equation}
@@
 %with $h$ the dominance coefficient (equal in both sexes), 
-\begin{equation}
-B = \frac{s_f}{2r R(s_{f}+s_{m})^2} t_m^2
-\end{equation}
-and $C_k$ is a term that depends on $k$:
-
-%k=0
-\begin{equation}
-C_0 = 
-\end{equation}
-
-%k=1
-\begin{equation}
-C_1 = - \left[ (2r(1-R)-R) s_f + (1-2r)R s_m \right]
-\end{equation}
-
-%k=1/2
-\begin{equation}
-C_{1/2} = 
-\end{equation}
-
-In the case of $k=1$ the maternal and offspring controlled results are the same (which makes sense because we are here concerned only with the passage of mutations through females).
+$C_k$ is a term that depends on $k$.
+%
+%%k=0
+%\begin{equation}
+%C_0 = big \; ugly \; term
+%\end{equation}
+%
+%%k=1
+%\begin{equation}
+%C_1 = \frac{\left[ (2r(1-R)-R) s^f + (1-2r)R s^m \right]}{2}
+%\end{equation}
+%
+%%k=1/2
+%\begin{equation}
+%C_{1/2} = even \; bigger, \; uglier \; term
+%\end{equation}
+%
+%When $k=1$ the maternal- and offspring-controlled results are the same, $C_1 = C_W$, since the mutation remains in females (and hence mutant daughters always have mutant mothers).
+%However, with $k\neq1$ the results with maternal control differ from those with offspring control.
+Of particular interest is $k=1/2$ (i.e., when the mother perfectly balances the sex ratio of her offspring).
+When both recombination rates are small we have $C_{1/2} \approx R(s^m - s^f)/8 = \lim_{r \rightarrow 0} C_W/4$.
+This implies that, at least under tight linkage, maternal ESD can invade whenever a neo-$W$ can.
 

### 2016-09-15 LaTeX/Turnover.tex
fixed male female inequality

@@
 \end{equation}
-where $V_A = p_A(1-p_A)$ is the variance at the \textbf{A} locus, $S_A = s^f (t^m)^2 / \left[ r R \left( s^f + s^m \right)^2 \right]$ (INTERPRETATION?), $s^f$ and $s^m$ are the respective selection coefficients for $A$ in diploid females and males, $t^m$ is the selection coefficient for $A$ in gametes/gametophytes from males, and we've assumed equal dominance coefficients in the two sexes.
+where $V_A = p_A(1-p_A)$ is the variance at the \textbf{A} locus, $S_A = s^f (t^m)^2 / \left[ r R \left( s^f + s^m \right)^2 \right]$ (\textcolor{red}{INTERPRETATION?
+LOSE THE R?}), $s^f$ and $s^m$ are the respective selection coefficients for $A$ in diploid females and males, $t^m$ is the selection coefficient for $A$ in gametes/gametophytes from males, and we've assumed equal dominance coefficients in the two sexes.
 
@@
 In this case, even when the novel sex-determining locus is in looser linkage with the selected locus than is the ancestral sex-determining locus, $r<R$, a neo-$W$ can invade.
-For example, with $R=1/2$ the neo-$W$ invades if there is any linkage between the ancestral sex-determining and selected loci ($r<1/2$), there is selection among gametes/gametophytes in males ($t^m\neq0$), and there is selection for or against $A$ in both males and females ($s^m s^f >0$) that is stronger in females than in males ($|s^f| > |s^m|$).
+For example, with $R=1/2$ the neo-$W$ invades if there is any linkage between the ancestral sex-determining and selected loci ($r<1/2$), there is selection among gametes/gametophytes in males ($t^m\neq0$), and there is selection for or against $A$ in both males and females ($s^m s^f >0$) that is stronger in males than in females ($|s^m| > |s^f|$).
 
@@
 When both recombination rates are small we have $C_{1/2} \approx R(s^m - s^f)/8 = \lim_{r \rightarrow 0} C_W/4$.
-This implies that, at least under tight linkage, maternal ESD can invade whenever a neo-$W$ can.
+This implies that, at least under tight linkage, the invasion of maternal ESD is independent of $R$ (because $S_A\propto R^{-1}$) and can invade whenever a neo-$W$ can.
 

### 2016-09-25 LaTeX/Turnover.tex
comparing to Kirk

@@
 The life-cycle begins with competition between haploid gametes/gametophytes from each sex, where selection depends on the sex of the diploid they came from and their allele at the \textbf{A} locus.
-Gametes/gametophytes from males then mate randomly with gametes/gametophytes from females.
-The resulting zygotes develop as males or females, depending on their genotypes at the \textbf{X} and \textbf{M} loci (or the \textbf{M} genotype of their mother).
+Gametes/gametophytes from males then pair randomly with gametes/gametophytes from females.
+The resulting zygotes develop as males or females, depending on their genotypes at the \textbf{X} and \textbf{M} loci (or the \textbf{M} genotype of their mother in the case of maternal control).
 Diploids compete with others of the same sex, where selection depends on the sex of the individual and its genotype at the \textbf{A} locus.
@@
 Linear stability analysis can then be used to determine the stability of this equilibrium.
-With no haploid selection our results reduce to those of \cite{vanDoorn:2010hu} when $k=0$ (neo-$Y$ invading a $ZW$ system) or when $k=1$ (neo-$W$ invading an $XY$ system).
+With no haploid selection our results reduce to those of \cite{vanDoorn:2007eu}. %when $k=0$ (neo-$Y$ invading a $ZW$ system) or when $k=1$ (neo-$W$ invading an $XY$ system) (\textcolor{red}{CHECK}).
+However, with haploid selection a stable polymorphism at locus \textbf{A} no longer requires sexually antagonistic selection, as it can also be achieved by ploidally-antagonistic selection.
 
@@
 Below we present the results for invasion into an $XY$ system assuming no competition among gametes/gametophytes from females and linear arrangement \textbf{X}\textbf{A}\textbf{M}.
+%(i.e., $\chi = r R$).
 %(SAY SOMETHING HERE ABOUT OTHER ARRANGEMENTS?).
@@
 
-Otherwise, the new sex-determining allele increases in frequency on one \textbf{A} background and declines on the other and invasion requires
+Otherwise, the new sex-determining allele increases in frequency on one \textbf{A} background and declines on the other, and invasion requires
 \begin{equation}\label{eq:neoYR}
@@
 for the neo-$W$.
-Here $\bar{p}^m = (p^m_X+p^m_Y)/2$ is the average frequency of $A$ in males, $w^i_{j}$ is the relative viability fitness of sex $i\in\{m,f\}$ depending on their haploid or diploid genotype at the \textbf{A} locus (with $j\in\{A,a,AA,Aa,aa\}$) and
+Here $\bar{p}^m = (p^m_X+p^m_Y)/2$ is the average frequency of $A$ in gametophytes produced by males, $w^i_{j}$ is the relative viability fitness of sex $i\in\{m,f\}$ depending on their haploid or diploid genotype at the \textbf{A} locus (with $j\in\{A,a,AA,Aa,aa\}$) and
 $\nu^i = 
@@
 
-The new sex-determining allele is therefore expected to invade for any recombination rate, $R$, when the net flow of double recombinants is from the less fit to the more fit \textbf{A} background (making the term inside the square brackets negative).
+The new sex-determining allele is therefore expected to invade for any recombination rate, $R$, when the net flow of double recombinants is from the less fit to the more fit \textbf{A} background (making the terms inside the square brackets in Equations \ref{eq:neoYR} and \ref{eq:neoWR} negative).
 %Assuming $g_A^* > 0$ and $g_a^* < 0$ without loss of generality, this is $-(1 - p^f_X) w_{m,A} g_a^* < p^f_X w_{m,a} g_A^*$.
-When the net flow of double recombinants is from the more fit to the less fit haplotype, the new sex-determining allele can still invade when the rate of recombination between it and the selected locus is small enough.
+When the net flow of double recombinants is from the more fit to the less fit haplotype, the new sex-determining allele can still invade when the rate of recombination between it and the selected locus, $R$, is small enough.
 
 %weak selection
-Assuming weak selection, we can solve for the invasion fitness of the new sex -determining alleles explicitly, giving
+Assuming weak selection, we can solve for the invasion fitness of the new sex-determining allele, $m$, into the ancestral $XY$ system explicitly, giving
 \begin{equation}
@@
 \end{equation}
-where $V_A = p_A(1-p_A)$ is the variance at the \textbf{A} locus, $S_A = s^f (t^m)^2 / \left[ r R \left( s^f + s^m \right)^2 \right]$ (\textcolor{red}{INTERPRETATION?
-LOSE THE R?}), $s^f$ and $s^m$ are the respective selection coefficients for $A$ in diploid females and males, $t^m$ is the selection coefficient for $A$ in gametes/gametophytes from males, and we've assumed equal dominance coefficients in the two sexes.
+where $V_A = p_A(1-p_A)$ is the variance at the \textbf{A} locus, $S_A = s^f (t^m)^2 / \left[ r R \left( s^f + s^m \right)^2 \right]$ (\textcolor{red}{INTERPRETATION?}), $s^f$ and $s^m$ are the respective selection coefficients for $A$ in diploid females and males, $t^m$ is the selection coefficient for $A$ in gametes/gametophytes from males, and we've assumed equal dominance coefficients in the two sexes.
 
@@
 The neo-$Y$ can therefore invade whenever it is in tighter linkage with the selected locus than the ancestral sex-determining locus, $r>R$, provided locus \textbf{A} is polymorphic ($V_A>0$) and there is selection among both females ($s^f\neq0$) and gametes/gametophytes from males ($t^m\neq0$).
+This differs from \cite{vanDoorn:2007eu}
 
 For the neo-$W$ we have $C_W = [(2r(1-R)-R) s^f + (1-2r)R s^m]/2$.
-In this case, even when the novel sex-determining locus is in looser linkage with the selected locus than is the ancestral sex-determining locus, $r<R$, a neo-$W$ can invade.
+In this case, even when the novel sex-determining locus is in looser linkage with the selected locus than the ancestral sex-determining locus is, $r<R$, a neo-$W$ can invade.
 For example, with $R=1/2$ the neo-$W$ invades if there is any linkage between the ancestral sex-determining and selected loci ($r<1/2$), there is selection among gametes/gametophytes in males ($t^m\neq0$), and there is selection for or against $A$ in both males and females ($s^m s^f >0$) that is stronger in males than in females ($|s^m| > |s^f|$).
@@
 
-One might think that when the sex of a zygote is under the control of its mother, there would be strong selection to balance the sex ratio among zygotes. 
+One might think that when the sex of zygotes is under the control of mothers, there would be strong selection to balance the sex ratio among zygotes. 
 However, we find that, as with offspring control, assuming weak selection the invasion fitness of a sex-determiner that is maternally controlled can be written

### 2016-09-26 LaTeX/Turnover.tex
comparison to Kirk complete

@@
 The neo-$Y$ can therefore invade whenever it is in tighter linkage with the selected locus than the ancestral sex-determining locus, $r>R$, provided locus \textbf{A} is polymorphic ($V_A>0$) and there is selection among both females ($s^f\neq0$) and gametes/gametophytes from males ($t^m\neq0$).
-This differs from \cite{vanDoorn:2007eu}
+This reduces to the weak linkage results of \cite{vanDoorn:2007eu} when we do not assume equal dominance coefficients in the two sexes, there is no haploid selection, and there is free recombination between locus \textbf{A} and one of the sex-determining regions.
 
@@
 For example, with $R=1/2$ the neo-$W$ invades if there is any linkage between the ancestral sex-determining and selected loci ($r<1/2$), there is selection among gametes/gametophytes in males ($t^m\neq0$), and there is selection for or against $A$ in both males and females ($s^m s^f >0$) that is stronger in males than in females ($|s^m| > |s^f|$).
+This reduces to the weak linkage results of \cite[][Equation 3]{vanDoorn:2010hu} when we do not assume equal dominance coefficients in the two sexes and there is no haploid selection.
 

### 2016-11-08 LaTeX/Turnover.tex
adding drive to TeX file

--- 2016-09-25 LaTeX/Turnover.tex
@@
 %Predominant theories in which new sex-determining systems are favoured by selection involve sex ratio selection or fitness differences between sexes (e.g., sexually antagonistic selection). 
-Here, we utilize population genetic models to study the spread of novel sex-determining systems where we also include 
+Here, we utilize population genetic models to study the spread of novel sex-determining systems when there is
+%where we also include 
 %a period of selection during the haploid stage produced by one sex, e.g., pollen or sperm competition. 
 haploid gametic selection, e.g., pollen or sperm competition.
-Haploid selected loci experience a form of sex-specific selection (because gametic competition occurs predominantly among haploids produced by males) and can also cause sex ratios at birth to become biased (because sex ratios are determined by the fertilization success of X- versus Y-bearing pollen/sperm).
+Haploid selected loci experience a form of sex-specific selection (because gametic competition occurs predominantly among haploids produced by males) and can cause sex ratios at birth to become biased (because sex ratios are determined by the fertilization success of X- versus Y-bearing pollen/sperm).
 We find that the evolution of sex determination systems where mothers determine sex at birth (e.g., environmental sex determination where sex is determined at birth) is influenced by classic Fisherian sex ratio selection.
@@
 Diploids compete with others of the same sex, where selection depends on the sex of the individual and its genotype at the \textbf{A} locus.
-This is followed by meiosis with recombination. 
+This is followed by meiosis with recombination and sex-specific meiotic drive. 
 Recombination occurs between loci \textbf{X} and \textbf{A} with probability $r$, between loci \textbf{A} and \textbf{M} with probability $R$, and between loci \textbf{X} and \textbf{M} with probability $\chi$.
@@
 Any order of the loci can be modelled with appropriate choices of $r$, $R$, and $\chi$.
+We model meiotic drive at the viability locus only; individuals of sex $i$ who are heterozygous at the \textbf{A} locus produce haploids bearing allele $A$ with probability $\alpha^i$.
 We track the frequency of haploid genotypes produced by each sex from one generation to the next (recursion equations in Sup.\ Mat.).
@@
 \subsection*{Resident equilibrium and stability}
-With allele $M$ fixed, we follow the dynamics of the frequency of $A$ in gametes/gametophytes from the homogametic sex (e.g., in eggs from an XX female, $p^f_X$) and the frequencies of $A$ in the two types of gametes/gametophytes from the heterogametic sex (e.g., in sperm from an XY male that are X-bearing, $p^m_X$, and Y-bearing, $p^m_Y$).
-Assuming selection is weak relative to recombination, the differences in the frequencies of $A$ in each type of gamete/gametophyte are small, and we can solve for the mean frequency of $A$ across all types ($p_A$) as well as the difference in the frequencies of $A$ between two of the three types, to first order in selection.
+With allele $M$ fixed, we follow the dynamics of the frequency of $A$ in gametes/gametophytes from the homogametic sex (e.g., in eggs from an XX female, $p^f_X$), the frequencies of $A$ in the two types of gametes/gametophytes from the heterogametic sex (e.g., in sperm from an XY male that are X-bearing, $p^m_X$, and Y-bearing, $p^m_Y$), and the frequencies of the sex-determining factors in gametes/gametophytes from the heterogametic sex (e.g., the frequency of Y in sperm, $q$).
+Assuming selection and meiotic drive are weak relative to recombination, the differences in the frequencies of $A$ in each type of gamete/gametophyte are small, as is the bias in the sex-determining factor from the heterogametic sex, and we can solve for the mean frequency of $A$ across all types ($p_A$), the difference in the frequencies of $A$ between two of the three types, and the bias in the frequency of the sex-determining factor, to first order in selection.
 Linear stability analysis can then be used to determine the stability of this equilibrium.
-With no haploid selection our results reduce to those of \cite{vanDoorn:2007eu}. %when $k=0$ (neo-$Y$ invading a $ZW$ system) or when $k=1$ (neo-$W$ invading an $XY$ system) (\textcolor{red}{CHECK}).
-However, with haploid selection a stable polymorphism at locus \textbf{A} no longer requires sexually antagonistic selection, as it can also be achieved by ploidally-antagonistic selection.
+Without haploid selection or meiotic drive our results reduce to those of \cite{vanDoorn:2007eu}.
+%when $k=0$ (neo-$Y$ invading a $ZW$ system) or when $k=1$ (neo-$W$ invading an $XY$ system) (\textcolor{red}{CHECK}).
+However, with haploid selection or meiotic drive a stable polymorphism at locus \textbf{A} no longer requires sexually antagonistic selection.
+%, as it can also be achieved by ploidally-antagonistic selection.
 
@@
 %, evaluated at the above equilibrium.
-Below we present the results for invasion into an $XY$ system assuming no competition among gametes/gametophytes from females and linear arrangement \textbf{X}\textbf{A}\textbf{M}.
+Below we present the results for invasion into an $XY$ system assuming no competition among gametes/gametophytes from females, no meiotic drive in females, and linear arrangement \textbf{X}\textbf{A}\textbf{M}.
 %(i.e., $\chi = r R$).
@@
 \begin{equation}\label{eq:neoYR}
-R \left[ \frac{p^f_X w^m_a}{g_A^*} + \frac{(1 - p^f_X) w^m_A}{g_a^*} \right] w^m_{Aa} < \nu^m,
+R \left[ \frac{p^f_X w^m_a (1-\alpha^m)}{g_A^*} + \frac{(1 - p^f_X) w^m_A \alpha^m}{g_a^*} \right] w^m_{Aa} < \nu^m,
 \end{equation}
@@
 %and $g_j^*$ is the growth rate of $X^m$ and $Ym$ haplotypes when on an $A$ ($j=A$)  or $a$ background ($j=a$).
+Although male meiotic drive does not explicitly appear in Equation \ref{eq:neoWR}, it does affect the average frequency of $A$ in gametes/gametophytes from males, $\bar{p}^m$, and thus can play a role in neo-W invasion.
 
-The new sex-determining allele is therefore expected to invade for any recombination rate, $R$, when the net flow of double recombinants is from the less fit to the more fit \textbf{A} background (making the terms inside the square brackets in Equations \ref{eq:neoYR} and \ref{eq:neoWR} negative).
+Equations \eqref{eq:neoYR} and \eqref{eq:neoWR} show that the new sex-determining allele is expected to invade for any recombination rate, $R$, when the net flow of double recombinants is from the less fit to the more fit \textbf{A} background (making the terms inside the square brackets in Equations \ref{eq:neoYR} and \ref{eq:neoWR} negative).
 %Assuming $g_A^* > 0$ and $g_a^* < 0$ without loss of generality, this is $-(1 - p^f_X) w_{m,A} g_a^* < p^f_X w_{m,a} g_A^*$.
@@
 %weak selection
-Assuming weak selection, we can solve for the invasion fitness of the new sex-determining allele, $m$, into the ancestral $XY$ system explicitly, giving
+Assuming weak selection and meiotic drive, we can explicitly solve for the invasion fitness of the new sex-determining allele, $m$, into the ancestral $XY$ system, giving
 \begin{equation}
@@
 \end{equation}
-where $V_A = p_A(1-p_A)$ is the variance at the \textbf{A} locus, $S_A = s^f (t^m)^2 / \left[ r R \left( s^f + s^m \right)^2 \right]$ (\textcolor{red}{INTERPRETATION?}), $s^f$ and $s^m$ are the respective selection coefficients for $A$ in diploid females and males, $t^m$ is the selection coefficient for $A$ in gametes/gametophytes from males, and we've assumed equal dominance coefficients in the two sexes.
+where $V_A = p_A(1-p_A)$ is the variance at the \textbf{A} locus.
+We will consider haploid selection and meiotic drive separately.
+With haploid selection and no drive we have $S_A = s^f (t^m)^2 / \left[ r R \left( s^f + s^m \right)^2 \right]$, where $s^f$ and $s^m$ are the respective selection coefficients for $A$ in diploid females and males, $t^m$ is the selection coefficient for $A$ in gametes/gametophytes from males, and we've assumed equal dominance coefficients in the two sexes.
+With drive and no haploid selection we replace $t^m$ with $\alpha^m-1/2$.
 
-For the neo-$Y$ we have $C_Y = (r - R)s^f $.
-The neo-$Y$ can therefore invade whenever it is in tighter linkage with the selected locus than the ancestral sex-determining locus, $r>R$, provided locus \textbf{A} is polymorphic ($V_A>0$) and there is selection among both females ($s^f\neq0$) and gametes/gametophytes from males ($t^m\neq0$).
-This differs from \cite{vanDoorn:2007eu}
+For the neo-$Y$ we have $C_Y = (r - R)s^f $ with haploid selection and $C_Y = 4(r - R)s^f $ with drive.
+The neo-$Y$ can therefore invade whenever it is in tighter linkage with the selected locus than the ancestral sex-determining locus, $r>R$, provided locus \textbf{A} is polymorphic ($V_A>0$), there is diploid selection in females ($s^f\neq0$), and there is either haploid selection in gametes/gametophytes from males ($t^m\neq0$) or meiotic drive in males ($\alpha^m\neq1/2$).
+This reduces to the weak-linkage results of \cite{vanDoorn:2007eu} when we do not assume equal dominance coefficients in the two sexes, there is no haploid selection or meiotic drive, and there is free recombination between locus \textbf{A} and one of the sex-determining regions.
 
-For the neo-$W$ we have $C_W = [(2r(1-R)-R) s^f + (1-2r)R s^m]/2$.
+For the neo-$W$ we have $C_W = [(2r(1-R)-R) s^f + (1-2r)R s^m]/2$ with haploid selection and $C_W = 4[r(1-2R) s^f + (1-2r)R s^m]/2$ with drive.
 In this case, even when the novel sex-determining locus is in looser linkage with the selected locus than the ancestral sex-determining locus is, $r<R$, a neo-$W$ can invade.
-For example, with $R=1/2$ the neo-$W$ invades if there is any linkage between the ancestral sex-determining and selected loci ($r<1/2$), there is selection among gametes/gametophytes in males ($t^m\neq0$), and there is selection for or against $A$ in both males and females ($s^m s^f >0$) that is stronger in males than in females ($|s^m| > |s^f|$).
+For example, $R=1/2$ the neo-$W$ invades if there is any linkage between the ancestral sex-determining and selected loci ($r<1/2$), there is selection among gametes/gametophytes in males ($t^m\neq0$), and there is selection for or against $A$ in both males and females ($s^m s^f >0$) that is stronger in males than in females ($|s^m| > |s^f|$).
+With meiotic drive and $R=1/2$, all that is required for neo-W invasion is $r<1/2$ and $s^m s^f >0$.
+Our results reduce to the weak-linkage results of \cite[][Equation 3]{vanDoorn:2010hu} when we do not assume equal dominance coefficients in the two sexes and there is no haploid selection or meiotic drive.
 

### 2016-12-20 LaTeX/Turnover.tex
Figures 1 and 2 added

@@
 \usepackage{graphicx}
+\graphicspath{ {../Plots/} }
 \usepackage{pdfpages}
@@
 \newpage
+\linenumbers
+\modulolinenumbers[2]
 
@@
 %Predominant theories in which new sex-determining systems are favoured by selection involve sex ratio selection or fitness differences between sexes (e.g., sexually antagonistic selection). 
-Here, we utilize population genetic models to study the spread of novel sex-determining systems when there is
+Here, we utilize population genetic models to study the spread of novel sex-determining systems in the presence of
 %where we also include 
@@
 Haploid selected loci experience a form of sex-specific selection (because gametic competition occurs predominantly among haploids produced by males) and can cause sex ratios at birth to become biased (because sex ratios are determined by the fertilization success of X- versus Y-bearing pollen/sperm).
-We find that the evolution of sex determination systems where mothers determine sex at birth (e.g., environmental sex determination where sex is determined at birth) is influenced by classic Fisherian sex ratio selection.
+%We find that the evolution of sex determination systems where mothers determine sex at birth (e.g., environmental sex determination where sex is determined at birth) is influenced by classic Fisherian sex ratio selection.
 {\color{red}(Maybe not true???)}
-However, notably, we find that the spread of new genetic sex determination systems is not affected by sex ratio biases that are caused by gametic selection because sex ratios become biased after parental provisioning has occurred (even if pollen/sperm competition occurs within the mother).
+%However, notably, we find that the spread of new genetic sex determination systems is not affected by sex ratio biases that are caused by gametic selection because sex ratios become biased after parental provisioning has occurred (even if pollen/sperm competition occurs within the mother).
+Notably, we find that the spread of new genetic sex determination systems is not affected by sex ratio biases that are caused by gametic selection because sex ratios become biased after parental provisioning has occurred (even if pollen/sperm competition occurs within the mother).
 In addition, we find that linkage of an ancestral sex chromosome to a locus under haploid selection can favour transitions between male and female heterogamety (e.g., XY to ZW), which is not the case for any forms of diploid sex specific selection (e.g., sexually antagonistic selection).
@@
 
-Animals and angiosperms exhibit extremely diverse sex determination systems, as reviewed by \citet{Bull:1983vi,Charlesworth:2010it,Beukeboom:2014vb,Bachtrog:2014bx}. 
+Animals and angiosperms exhibit extremely diverse sex determination systems \citep[reviewed in][]{Bull:1983vi,Charlesworth:2010it,Beukeboom:2014vb,Bachtrog:2014bx}. 
 Among species with genetic sex determination of diploid sexes, some taxa have heterogametic males (XY) and homogametic females (XX), including %non-monotreme? 
@@
 In addition, many gonochoric/dioecious clades with genetic sex determination exhibit transitions between male (XY) and female (ZW) heterogamety, including lizards \citep{Ezaz:2009tk}, eight of 26 teleost fish families \citep{Mank:2006bt}, true fruit flies \citep[Tephritids,][]{Vicoso:2015hf}, amphibians \citep{Hillis:1990gu}, the angiosperm genus \textit{Silene} \citep{Slancarova:2013dq}, Coleoptera and Hemiptera \citep[][plate 2]{Beukeboom:2014vb}.
-Indeed, in some cases, both male and female heterogametic sex determination systems can be found the same species, as exhibited by some cichlid species \citep{Ser:2010iq} and \textit{Rana rugosa} \citep{Ogata:2007jm}.
+Indeed, in some cases, both male and female heterogametic sex determination systems can be found in the same species, as exhibited by some cichlid species \citep{Ser:2010iq} and \textit{Rana rugosa} \citep{Ogata:2007jm}.
 In addition, multiple transitions have occurred between genetic and environmental sex determination systems, e.g., in reptiles and fishes \citep{Conover:1987in,Mank:2006bt,Pokorna:2009ui,Ezaz:2009tk,Pen:2010kk,Holleley:2015hc}.
@@
 
-Here, we use mathematical models to find the conditions under which new sex determination systems are favoured by selection where we include a period of selection among haploid gametes/gametophytes. 
+Here, we use mathematical models to find the conditions under which new sex determination systems are favoured by selection when there is a period of selection among haploid gametes/gametophytes. 
 Selection among haploid genotypes is thought to occur primarily among pollen/sperm, which can compete whenever there are more pollen/sperm than required for fertilization \citep{Mulcahy:1996ha,JOSEPH:2004haa}.
@@
 A smaller (but non-negligible) proportion of genes are thought to be expressed and selected in animal sperm, although precise estimates are uncertain \citep{Zheng:2001fi,JOSEPH:2004haa,Vibranovski:2010et}.
+\textcolor{red}{add something about meiotic drive here?}
 
@@
 We consider a three locus model.
-Locus \textbf{X} is the ancestral sex-determining region (SDR), with alleles $X$ and $Y$ (or $Z$ and $W$).
+Locus \textbf{X} is the ancestral sex-determining region, with alleles $X$ and $Y$ (or $Z$ and $W$).
 Locus \textbf{A} is a region under selection, with alleles $A$ and $a$.
 And locus \textbf{M} is a novel sex-determining region, with alleles $M$ and $m$.
-With genotype $MM$ at locus \textbf{M}, the sex of a zygote is determined by the genotype at locus \textbf{X} ($XX$ become females and $XY$ males, or $ZW$ become females and $ZZ$ males).
+With genotype $MM$ at locus \textbf{M}, the sex of a zygote is determined by the genotype at locus \textbf{X} ($XX$ become females and $XY$ become males, or $ZW$ become females and $ZZ$ become males).
 With at least one $m$ allele at locus \textbf{M}, a zygote develops as a female with probability $k$ and as a male with probability $1-k$.
@@
 With intermediate $k$, locus \textbf{M} is interpreted as an offspring controlled environmental sex-determining region.
-Finally, we also analyze a model of maternally-controlled environmental sex-determination, where mothers with at least one $m$ allele produce daughters with probability $k$.
+Finally, we also analyze a model of maternally-controlled environmental sex-determination (ESD), where mothers with at least one $m$ allele produce daughters with probability $k$.
 
 %life-cycle
-The life-cycle begins with competition between haploid gametes/gametophytes from each sex, where selection depends on the sex of the diploid they came from and their allele at the \textbf{A} locus.
-Gametes/gametophytes from males then pair randomly with gametes/gametophytes from females.
+The life-cycle begins with competition between haploid gametes/gametophytes (hereafter gametes) from each sex, where selection depends on the sex of the diploid they came from and their allele at the \textbf{A} locus.
+Gametes from males then pair randomly with gametes from females.
 The resulting zygotes develop as males or females, depending on their genotypes at the \textbf{X} and \textbf{M} loci (or the \textbf{M} genotype of their mother in the case of maternal control).
@@
 \subsection*{Resident equilibrium and stability}
-With allele $M$ fixed, we follow the dynamics of the frequency of $A$ in gametes/gametophytes from the homogametic sex (e.g., in eggs from an XX female, $p^f_X$), the frequencies of $A$ in the two types of gametes/gametophytes from the heterogametic sex (e.g., in sperm from an XY male that are X-bearing, $p^m_X$, and Y-bearing, $p^m_Y$), and the frequencies of the sex-determining factors in gametes/gametophytes from the heterogametic sex (e.g., the frequency of Y in sperm, $q$).
-Assuming selection and meiotic drive are weak relative to recombination, the differences in the frequencies of $A$ in each type of gamete/gametophyte are small, as is the bias in the sex-determining factor from the heterogametic sex, and we can solve for the mean frequency of $A$ across all types ($p_A$), the difference in the frequencies of $A$ between two of the three types, and the bias in the frequency of the sex-determining factor, to first order in selection.
+With allele $M$ fixed, we follow the dynamics of the frequency of $A$ in gametes from the homogametic sex (e.g., in eggs from an XX female, $p^f_X$), the frequencies of $A$ in the two types of gametes from the heterogametic sex (e.g., in sperm from an XY male that are X-bearing, $p^m_X$, and Y-bearing, $p^m_Y$), and the frequencies of the sex-determining factors in gametes from the heterogametic sex (e.g., the frequency of Y in sperm, $q$).
+Assuming selection and meiotic drive are weak relative to recombination, the differences in the frequencies of $A$ in each type of gamete are small, as is the bias in the sex-determining factor from the heterogametic sex, and we can solve for the mean frequency of $A$ across all types ($p_A$), the difference in the frequencies of $A$ between two of the three types, and the bias in the frequency of the sex-determining factor, to first order in selection.
 Linear stability analysis can then be used to determine the stability of this equilibrium.
@@
 %, evaluated at the above equilibrium.
-Below we present the results for invasion into an $XY$ system assuming no competition among gametes/gametophytes from females, no meiotic drive in females, and linear arrangement \textbf{X}\textbf{A}\textbf{M}.
+Below we present the results for invasion into an $XY$ system assuming no competition among gametes from females, no meiotic drive in females, and linear arrangement \textbf{X}\textbf{A}\textbf{M}.
 %(i.e., $\chi = r R$).
@@
 for the neo-$W$.
-Here $\bar{p}^m = (p^m_X+p^m_Y)/2$ is the average frequency of $A$ in gametophytes produced by males, $w^i_{j}$ is the relative viability fitness of sex $i\in\{m,f\}$ depending on their haploid or diploid genotype at the \textbf{A} locus (with $j\in\{A,a,AA,Aa,aa\}$) and
+Here $\bar{p}^m = (p^m_X+p^m_Y)/2$ is the average frequency of $A$ in gametes produced by males, $w^i_{j}$ is the relative viability fitness of sex $i\in\{m,f\}$ depending on their haploid or diploid genotype at the \textbf{A} locus (with $j\in\{A,a,AA,Aa,aa\}$) and
 $\nu^i = 
@@
 %and $g_j^*$ is the growth rate of $X^m$ and $Ym$ haplotypes when on an $A$ ($j=A$)  or $a$ background ($j=a$).
-Although male meiotic drive does not explicitly appear in Equation \ref{eq:neoWR}, it does affect the average frequency of $A$ in gametes/gametophytes from males, $\bar{p}^m$, and thus can play a role in neo-W invasion.
+Although male meiotic drive does not explicitly appear in Equation \ref{eq:neoWR}, it does affect the average frequency of $A$ in gametes from males, $\bar{p}^m$, and thus can play a role in neo-W invasion.
 
@@
 We will consider haploid selection and meiotic drive separately.
-With haploid selection and no drive we have $S_A = s^f (t^m)^2 / \left[ r R \left( s^f + s^m \right)^2 \right]$, where $s^f$ and $s^m$ are the respective selection coefficients for $A$ in diploid females and males, $t^m$ is the selection coefficient for $A$ in gametes/gametophytes from males, and we've assumed equal dominance coefficients in the two sexes.
+With haploid selection and no drive we have $S_A = s^f (t^m)^2 / \left[ r R \left( s^f + s^m \right)^2 \right]$, where $s^f$ and $s^m$ are the respective selection coefficients for $A$ in diploid females and males, $t^m$ is the selection coefficient for $A$ in gametes from males, and we've assumed equal dominance coefficients in the two sexes.
 With drive and no haploid selection we replace $t^m$ with $\alpha^m-1/2$.
@@
 For the neo-$Y$ we have $C_Y = (r - R)s^f $ with haploid selection and $C_Y = 4(r - R)s^f $ with drive.
-The neo-$Y$ can therefore invade whenever it is in tighter linkage with the selected locus than the ancestral sex-determining locus, $r>R$, provided locus \textbf{A} is polymorphic ($V_A>0$), there is diploid selection in females ($s^f\neq0$), and there is either haploid selection in gametes/gametophytes from males ($t^m\neq0$) or meiotic drive in males ($\alpha^m\neq1/2$).
+The neo-$Y$ can therefore invade whenever it is in tighter linkage with the selected locus than the ancestral sex-determining locus, $r>R$, provided locus \textbf{A} is polymorphic ($V_A>0$), there is diploid selection in females ($s^f\neq0$), and there is either haploid selection between gametes from males ($t^m\neq0$) or meiotic drive in males ($\alpha^m\neq1/2$).
 This reduces to the weak-linkage results of \cite{vanDoorn:2007eu} when we do not assume equal dominance coefficients in the two sexes, there is no haploid selection or meiotic drive, and there is free recombination between locus \textbf{A} and one of the sex-determining regions.
@@
 For the neo-$W$ we have $C_W = [(2r(1-R)-R) s^f + (1-2r)R s^m]/2$ with haploid selection and $C_W = 4[r(1-2R) s^f + (1-2r)R s^m]/2$ with drive.
-In this case, even when the novel sex-determining locus is in looser linkage with the selected locus than the ancestral sex-determining locus is, $r<R$, a neo-$W$ can invade.
-For example, $R=1/2$ the neo-$W$ invades if there is any linkage between the ancestral sex-determining and selected loci ($r<1/2$), there is selection among gametes/gametophytes in males ($t^m\neq0$), and there is selection for or against $A$ in both males and females ($s^m s^f >0$) that is stronger in males than in females ($|s^m| > |s^f|$).
+In this case, even when the novel sex-determining locus is in looser linkage with the selected locus than the ancestral sex-determining locus is, $r<R$, a neo-$W$ can invade (Figure \ref{fig:Winvasion}).
+For example, $R=1/2$ the neo-$W$ invades if there is any linkage between the ancestral sex-determining and selected loci ($r<1/2$), there is selection among gametes in males ($t^m\neq0$), and there is selection for or against $A$ in both males and females ($s^m s^f >0$) that is stronger in males than in females ($|s^m| > |s^f|$).
 With meiotic drive and $R=1/2$, all that is required for neo-W invasion is $r<1/2$ and $s^m s^f >0$.
@@
 One might think that when the sex of zygotes is under the control of mothers, there would be strong selection to balance the sex ratio among zygotes. 
-However, we find that, as with offspring control, assuming weak selection the invasion fitness of a sex-determiner that is maternally controlled can be written
+However, we find that, as with offspring control, when assuming weak selection the invasion fitness of a sex-determiner that is maternally controlled can be written
 \begin{equation}
@@
 Of particular interest is $k=1/2$ (i.e., when the mother perfectly balances the sex ratio of her offspring).
-When both recombination rates are small we have $C_{1/2} \approx R(s^m - s^f)/8 = \lim_{r \rightarrow 0} C_W/4$.
-This implies that, at least under tight linkage, the invasion of maternal ESD is independent of $R$ (because $S_A\propto R^{-1}$) and can invade whenever a neo-$W$ can.
-
-\linenumbers
-\modulolinenumbers[2]
+When both recombination rates are small we have $C_{1/2} \approx R(s^m - s^f)/8 = \lim_{r \rightarrow 0} C_1/4$.
+This implies that, at least under tight linkage, the invasion of maternally-controlled ESD is independent of $R$ (because $S_A\propto R^{-1}$) and can invade whenever a neo-$W$ can.
 
@@
 
+\section*{Figures}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.5\linewidth]{FreqWLowR}\\
+\includegraphics[width=0.5\linewidth]{SexRatioLowR}\\
+\includegraphics[width=0.5\linewidth]{MeanDipFitLowR}
+\caption{
+A neo-$W$ invades an ancestrally $XY$ system and fixes (\textbf{A}) despite biasing the sex ratio (\textbf{B}) and decreasing mean diploid viability fitness (\textbf{C}).
+Parameters: $k=1$, $s^f = 0.05$, $s^m = 0.15$, $h^f = h^m = 0.7$, $t^f = 0$, $t^m = -0.1$, $\alpha^m = \alpha^f = 1/2$, $r=0.01$, $R=0.05$.
+}
+\label{fig:WinvasionLowR}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.5\linewidth]{FreqWHighR}\\
+\includegraphics[width=0.5\linewidth]{SexRatioHighR}\\
+\includegraphics[width=0.5\linewidth]{MeanDipFitHighR}
+\caption{
+A neo-$W$ invades an ancestrally $XY$ system (\textbf{A}) despite biasing the sex ratio (\textbf{B}) and decreasing mean diploid viability fitness (\textbf{C}).
+The neo-$W$ does not fix, producing a polymorphic sex-determination system.
+Parameters as in Figure \ref{fig:WinvasionLowR} but with $R=0.5$.
+}
+\label{fig:WinvasionHighR}
+\end{figure}
+
 \end{document}

### 2016-12-21 LaTeX/Turnover.tex
makin' plots

@@
 We find that new genetic sex determination systems are not affected by any sex ratio biases caused by associations between sex-determining regions and haploid selected loci. 
-In addition, we find that associations that build up between an ancestral sex-determining locus and a haploid-selected locus can favour transitions between male and female heterogamety (e.g., a neo-Z/neo-W locus spreads in an ancestrally XY system), despite the fact that these ancestral associations were built up by selection.
+In addition, we find that associations that build up between an ancestral sex-determining locus and a haploid-selected locus can favour transitions between male and female heterogamety (e.g., a neo-W allele arising at a previously autosomal locus spreads in an ancestrally XY system), despite the fact that these ancestral associations were built up by selection.
 This does not occur in models that do not include haploid selection.
@@
 With at least one $m$ allele at locus \textbf{M}, a zygote develops as a female with probability $k$ and as a male with probability $1-k$.
-With $k=0$, the novel sex determiner is a masculinizer (e.g., a neo-Y chromosome) and with $k=1$ the novel sex determiner is a feminizer (e.g, a neo-W chromosome).
+With $k=0$, the novel sex determiner is a masculinizer (i.e., a neo-Y) and with $k=1$ the novel sex determiner is a feminizer (i.e., a neo-W).
 With intermediate $k$, locus \textbf{M} is interpreted as an offspring controlled environmental sex-determining region.
@@
 Gametes from males then pair randomly with gametes from females.
-The resulting zygotes develop as males or females, depending on their genotypes at the \textbf{X} and \textbf{M} loci (or the \textbf{M} genotype of their mother in the case of maternal control).
+The resulting zygotes develop as males or females, depending on their genotypes at the \textbf{X} and \textbf{M} loci (and the \textbf{M} genotype of their mother in the case of maternal control).
 Diploids compete with others of the same sex, where selection depends on the sex of the individual and its genotype at the \textbf{A} locus.
@@
 %, evaluated at the above equilibrium.
-Below we present the results for invasion into an $XY$ system assuming no competition among gametes from females, no meiotic drive in females, and linear arrangement \textbf{X}\textbf{A}\textbf{M}.
+Below we present the analytic results for invasion into an $XY$ system assuming no competition among gametes from females, no meiotic drive in females, and linear arrangement \textbf{X}\textbf{A}\textbf{M}.
 %(i.e., $\chi = r R$).
@@
 %equal dominance coefficients in the two sexes,
-Equivalent results for invasions into a $ZW$ system can be derived by consistently switching the roles of males and females \citep{vanDoorn:2010hu}.
+Equivalent results for invasions into a $ZW$ system are derived by consistently switching the roles of males and females. %\citep{vanDoorn:2010hu}.
 
@@
 for the neo-$W$.
-Here $\bar{p}^m = (p^m_X+p^m_Y)/2$ is the average frequency of $A$ in gametes produced by males, $w^i_{j}$ is the relative viability fitness of sex $i\in\{m,f\}$ depending on their haploid or diploid genotype at the \textbf{A} locus (with $j\in\{A,a,AA,Aa,aa\}$) and
+Here $\bar{p}^m = (1-q) p^m_X+ q p^m_Y$ is the average frequency of $A$ in gametes produced by males, $w^i_{j}$ is the relative viability fitness of sex $i\in\{m,f\}$ depending on their haploid or diploid genotype at the \textbf{A} locus (with $j\in\{A,a,AA,Aa,aa\}$) and
 $\nu^i = 
@@
 We will consider haploid selection and meiotic drive separately.
-With haploid selection and no drive we have $S_A = s^f (t^m)^2 / \left[ r R \left( s^f + s^m \right)^2 \right]$, where $s^f$ and $s^m$ are the respective selection coefficients for $A$ in diploid females and males, $t^m$ is the selection coefficient for $A$ in gametes from males, and we've assumed equal dominance coefficients in the two sexes.
-With drive and no haploid selection we replace $t^m$ with $\alpha^m-1/2$.
+With haploid selection and no drive we have $S_A = s^f (t^m)^2 / \left[ r R \left( s^f + s^m \right)^2 \right]$, where $s^f$ and $s^m$ are the respective selection coefficients for $A$ in diploid females and males, $t^m$ is the selection coefficient for $A$ in gametes from males, and we've assumed equal dominance coefficients in the two sexes ($h^f = h^m$).
+With drive and no haploid selection one replaces $t^m$ with $\alpha^m-1/2$.
 
@@
 The neo-$Y$ can therefore invade whenever it is in tighter linkage with the selected locus than the ancestral sex-determining locus, $r>R$, provided locus \textbf{A} is polymorphic ($V_A>0$), there is diploid selection in females ($s^f\neq0$), and there is either haploid selection between gametes from males ($t^m\neq0$) or meiotic drive in males ($\alpha^m\neq1/2$).
-This reduces to the weak-linkage results of \cite{vanDoorn:2007eu} when we do not assume equal dominance coefficients in the two sexes, there is no haploid selection or meiotic drive, and there is free recombination between locus \textbf{A} and one of the sex-determining regions.
+This is similar to the conclusion reached concerning sexual-antagonistic selection in \cite{vanDoorn:2007eu} and reduces to their weak-linkage results exactly when we do not assume equal dominance coefficients in the two sexes, there is no haploid selection or meiotic drive, and there is free recombination between locus \textbf{A} and one of the sex-determining regions.
 
 For the neo-$W$ we have $C_W = [(2r(1-R)-R) s^f + (1-2r)R s^m]/2$ with haploid selection and $C_W = 4[r(1-2R) s^f + (1-2r)R s^m]/2$ with drive.
-In this case, even when the novel sex-determining locus is in looser linkage with the selected locus than the ancestral sex-determining locus is, $r<R$, a neo-$W$ can invade (Figure \ref{fig:Winvasion}).
-For example, $R=1/2$ the neo-$W$ invades if there is any linkage between the ancestral sex-determining and selected loci ($r<1/2$), there is selection among gametes in males ($t^m\neq0$), and there is selection for or against $A$ in both males and females ($s^m s^f >0$) that is stronger in males than in females ($|s^m| > |s^f|$).
+In this case, even when the novel sex-determining locus is in looser linkage with the selected locus than the ancestral sex-determining locus is, $r<R$, a neo-$W$ can invade (Figures \ref{fig:WinvasionLowR} -- \ref{fig:InvasionVsCentiMorgans}).
+This does not occur in models with only sexually-antagonistic selection \citep{vanDoorn:2010hu}.
+For example, with $R=1/2$ the neo-$W$ invades if there is any linkage between the ancestral sex-determining and selected loci ($r<1/2$), there is selection among gametes in males ($t^m\neq0$), and there is selection for or against $A$ in both males and females ($s^m s^f >0$) that is stronger in males than in females ($|s^m| > |s^f|$).
 With meiotic drive and $R=1/2$, all that is required for neo-W invasion is $r<1/2$ and $s^m s^f >0$.
@@
 One might think that when the sex of zygotes is under the control of mothers, there would be strong selection to balance the sex ratio among zygotes. 
-However, we find that, as with offspring control, when assuming weak selection the invasion fitness of a sex-determiner that is maternally controlled can be written
+However, we find that, as with offspring control, under weak selection the invasion fitness of a sex-determiner that is maternally controlled can be written
 \begin{equation}
@@
 When both recombination rates are small we have $C_{1/2} \approx R(s^m - s^f)/8 = \lim_{r \rightarrow 0} C_1/4$.
-This implies that, at least under tight linkage, the invasion of maternally-controlled ESD is independent of $R$ (because $S_A\propto R^{-1}$) and can invade whenever a neo-$W$ can.
+This implies that, at least under tight linkage, the invasion of maternally-controlled ESD is independent of $R$ (because $S_A\propto R^{-1}$) and can invade whenever a neo-$W$ can (which can invade even when it biases the sex ratio further; Figures \ref{fig:WinvasionLowR} -- \ref{fig:WinvasionHighR}).
 
@@
 Where the X and Y have fitness differences, \citet{Hough:2013uo} and \citet{Otto:2015va} demonstrated that mothers should generally evolve to balance sex ratios by reducing the intensity of haploid competition.
+
+{\color{red}{Despite the fact that sex ratio restorers can evolve, we find that sex chromosome turnover occurs regardless of sex ratio bias (Figure 3).}}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%W invades XY and fixes
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}
@@
 \caption{
-A neo-$W$ invades an ancestrally $XY$ system and fixes (\textbf{A}) despite biasing the sex ratio (\textbf{B}) and decreasing mean diploid viability fitness (\textbf{C}).
+Haploid selection allows a neo-$W$ to invade an ancestral $XY$ system and fix (\textbf{A}) despite temporarily biasing the sex ratio further (\textbf{B}) and decreasing mean diploid viability fitness (\textbf{C}).
+Complete turnover between genetic sex-determination systems occurs despite the neo-$W$ being less tightly linked to the selected locus than the ancestral sex-determining locus is, $R>r$.
 Parameters: $k=1$, $s^f = 0.05$, $s^m = 0.15$, $h^f = h^m = 0.7$, $t^f = 0$, $t^m = -0.1$, $\alpha^m = \alpha^f = 1/2$, $r=0.01$, $R=0.05$.
@@
 \end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%W invades XY but does not fix
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}
@@
 \caption{
-A neo-$W$ invades an ancestrally $XY$ system (\textbf{A}) despite biasing the sex ratio (\textbf{B}) and decreasing mean diploid viability fitness (\textbf{C}).
-The neo-$W$ does not fix, producing a polymorphic sex-determination system.
+Haploid selection allows a completely unlinked neo-$W$ to invade an ancestral $XY$ system (\textbf{A}) despite further biasing the sex ratio (\textbf{B}) and decreasing mean diploid viability fitness (\textbf{C}).
+The neo-$W$ does not fix (although variation at the \textbf{A} locus is maintained, $V_A>0$), resulting in a polymorphic sex-determination system.
 Parameters as in Figure \ref{fig:WinvasionLowR} but with $R=0.5$.
@@
 \end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%W invades for all rates of recombination with selected locus
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\begin{figure}
+%\centering
+%\includegraphics[width=0.5\linewidth]{InvasionVsRecombination}
+%\caption{
+%A neo-$W$ invades an ancestral $XY$ system with haploid selection regardless of how tightly it is linked to the selected locus. 
+%Parameters as in Figure \ref{fig:WinvasionLowR}.
+%}
+%\label{fig:InvasionVsRecombination}
+%\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%W invasion versus position of selected locus
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering
+\includegraphics[width=0.5\linewidth]{InvasionVsCentiMorgans}
+\caption{
+Haploid selection allows a neo-$W$ to invade an ancestral $XY$ system regardless of how tightly it and the ancestral sex-determining locus are linked to the selected locus. 
+The ancestral sex-determining locus is located at -0.05 and the novel sex-determining locus is located at 0.05, such that the probability of a cross-over between them is $\approx0.1$.
+The x-axis gives the position of the locus under haploid selection.
+We used Haldane's map function \citep[Equation 3 in ][]{Haldane1919} to convert from map distance (centiMorgans) to the probability of a cross-over event. 
+Parameters as in Figure \ref{fig:WinvasionLowR}.
+}
+\label{fig:InvasionVsCentiMorgans}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Y invades ZW and fixes (counter example to Kozi explanation)
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering
+\includegraphics[width=0.5\linewidth]{FreqWCounterKozi}\\
+\includegraphics[width=0.5\linewidth]{SexRatioCounterKozi}\\
+%\includegraphics[width=0.5\linewidth]{MeanDipFitCounterKozi}
+\caption{
+Meiotic drive allows a neo-$Y$ to invade an ancestral $ZW$ system and fix (\textbf{A}) despite temporarily biasing the sex ratio (\textbf{B}).
+%and decreasing mean diploid viability fitness (\textbf{C}).
+Parameters: $k=0$, $s^f = s^m = t^f = t^m = 0$, $\alpha^m = 0.4$, $\alpha^f = 1/2$, $r=0$, $R=0$.
+}
+\label{fig:CounterKozi}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2016-12-21 LaTeX/Turnover.tex
code for chromosome position plot done

@@
 \centering
-\includegraphics[width=0.5\linewidth]{InvasionVsCentiMorgans}
+%\includegraphics[width=0.5\linewidth]{InvasionVsCentiMorgans}
+\includegraphics[width=0.5\linewidth]{InvasionVsCentiMorgansAllOrders}
 \caption{
 Haploid selection allows a neo-$W$ to invade an ancestral $XY$ system regardless of how tightly it and the ancestral sex-determining locus are linked to the selected locus. 
-The ancestral sex-determining locus is located at -0.05 and the novel sex-determining locus is located at 0.05, such that the probability of a cross-over between them is $\approx0.1$.
+The ancestral sex-determining locus is located at -0.05 and the novel sex-determining locus is located at 0.05 (corresponding to the peaks of invasion fitness), such that the probability of a cross-over between them is $\approx0.1$.
 The x-axis gives the position of the locus under haploid selection.

### 2017-01-04 LaTeX/Turnover.tex
nothing

--- 2016-12-20 LaTeX/Turnover.tex
@@
 \usepackage{graphicx}
-\graphicspath{ {../Plots/} }
 \usepackage{pdfpages}
@@
 \newpage
-\linenumbers
-\modulolinenumbers[2]
 
@@
 %Predominant theories in which new sex-determining systems are favoured by selection involve sex ratio selection or fitness differences between sexes (e.g., sexually antagonistic selection). 
-Here, we utilize population genetic models to study the spread of novel sex-determining systems in the presence of
-%where we also include 
+Here, we utilize population genetic models to study the spread of novel sex-determiners in systems with 
 %a period of selection during the haploid stage produced by one sex, e.g., pollen or sperm competition. 
 haploid gametic selection, e.g., pollen or sperm competition.
-Haploid selected loci experience a form of sex-specific selection (because gametic competition occurs predominantly among haploids produced by males) and can cause sex ratios at birth to become biased (because sex ratios are determined by the fertilization success of X- versus Y-bearing pollen/sperm).
-%We find that the evolution of sex determination systems where mothers determine sex at birth (e.g., environmental sex determination where sex is determined at birth) is influenced by classic Fisherian sex ratio selection.
+Haploid selected loci experience a form of sex-specific selection (because gametic competition occurs predominantly among haploids produced by males) and can also cause sex ratios at birth to become biased (because sex ratios are determined by the fertilization success of X- versus Y-bearing pollen/sperm).
+We find that the evolution of sex determination systems where mothers determine sex at birth (e.g., environmental sex determination where sex is determined at birth) is influenced by classic Fisherian sex ratio selection.
 {\color{red}(Maybe not true???)}
-%However, notably, we find that the spread of new genetic sex determination systems is not affected by sex ratio biases that are caused by gametic selection because sex ratios become biased after parental provisioning has occurred (even if pollen/sperm competition occurs within the mother).
-Notably, we find that the spread of new genetic sex determination systems is not affected by sex ratio biases that are caused by gametic selection because sex ratios become biased after parental provisioning has occurred (even if pollen/sperm competition occurs within the mother).
+However, notably, we find that the spread of new genetic sex determination systems is not affected by sex ratio biases that are caused by gametic selection because sex ratios become biased after parental provisioning has occurred (even if pollen/sperm competition occurs within the mother).
 In addition, we find that linkage of an ancestral sex chromosome to a locus under haploid selection can favour transitions between male and female heterogamety (e.g., XY to ZW), which is not the case for any forms of diploid sex specific selection (e.g., sexually antagonistic selection).
@@
 
-Animals and angiosperms exhibit extremely diverse sex determination systems \citep[reviewed in][]{Bull:1983vi,Charlesworth:2010it,Beukeboom:2014vb,Bachtrog:2014bx}. 
+Animals and angiosperms exhibit extremely diverse sex determination systems, as reviewed by \citet{Bull:1983vi,Charlesworth:2010it,Beukeboom:2014vb,Bachtrog:2014bx}. 
 Among species with genetic sex determination of diploid sexes, some taxa have heterogametic males (XY) and homogametic females (XX), including %non-monotreme? 
@@
 In addition, many gonochoric/dioecious clades with genetic sex determination exhibit transitions between male (XY) and female (ZW) heterogamety, including lizards \citep{Ezaz:2009tk}, eight of 26 teleost fish families \citep{Mank:2006bt}, true fruit flies \citep[Tephritids,][]{Vicoso:2015hf}, amphibians \citep{Hillis:1990gu}, the angiosperm genus \textit{Silene} \citep{Slancarova:2013dq}, Coleoptera and Hemiptera \citep[][plate 2]{Beukeboom:2014vb}.
-Indeed, in some cases, both male and female heterogametic sex determination systems can be found in the same species, as exhibited by some cichlid species \citep{Ser:2010iq} and \textit{Rana rugosa} \citep{Ogata:2007jm}.
+Indeed, in some cases, both male and female heterogametic sex determination systems can be found the same species, as exhibited by some cichlid species \citep{Ser:2010iq} and \textit{Rana rugosa} \citep{Ogata:2007jm}.
 In addition, multiple transitions have occurred between genetic and environmental sex determination systems, e.g., in reptiles and fishes \citep{Conover:1987in,Mank:2006bt,Pokorna:2009ui,Ezaz:2009tk,Pen:2010kk,Holleley:2015hc}.
@@
 
-Here, we use mathematical models to find the conditions under which new sex determination systems are favoured by selection when there is a period of selection among haploid gametes/gametophytes. 
+Here, we use mathematical models to find the conditions under which new sex determination systems are favoured by selection where we include a period of selection among haploid gametes/gametophytes. 
 Selection among haploid genotypes is thought to occur primarily among pollen/sperm, which can compete whenever there are more pollen/sperm than required for fertilization \citep{Mulcahy:1996ha,JOSEPH:2004haa}.
@@
 A smaller (but non-negligible) proportion of genes are thought to be expressed and selected in animal sperm, although precise estimates are uncertain \citep{Zheng:2001fi,JOSEPH:2004haa,Vibranovski:2010et}.
-\textcolor{red}{add something about meiotic drive here?}
+\textcolor{red}{add something about drive}
 
@@
 %genetic system
-We consider a three locus model.
-Locus \textbf{X} is the ancestral sex-determining region, with alleles $X$ and $Y$ (or $Z$ and $W$).
+We will consider a three locus model.
+Locus \textbf{X} is the ancestral sex-determining region (SDR), with alleles $X$ and $Y$ (or $Z$ and $W$).
 Locus \textbf{A} is a region under selection, with alleles $A$ and $a$.
 And locus \textbf{M} is a novel sex-determining region, with alleles $M$ and $m$.
-With genotype $MM$ at locus \textbf{M}, the sex of a zygote is determined by the genotype at locus \textbf{X} ($XX$ become females and $XY$ become males, or $ZW$ become females and $ZZ$ become males).
+With genotype $MM$ at locus \textbf{M}, the sex of a zygote is determined by the genotype at locus \textbf{X} ($XX$ become females and $XY$ males, or $ZW$ become females and $ZZ$ males).
 With at least one $m$ allele at locus \textbf{M}, a zygote develops as a female with probability $k$ and as a male with probability $1-k$.
 With $k=0$, the novel sex determiner is a masculinizer (e.g., a neo-Y chromosome) and with $k=1$ the novel sex determiner is a feminizer (e.g, a neo-W chromosome).
-With intermediate $k$, locus \textbf{M} is interpreted as an offspring controlled environmental sex-determining region.
-Finally, we also analyze a model of maternally-controlled environmental sex-determination (ESD), where mothers with at least one $m$ allele produce daughters with probability $k$.
+With intermediate $k$, locus \textbf{M} is interpreted as an environmental sex-determining region.
 
 %life-cycle
-The life-cycle begins with competition between haploid gametes/gametophytes (hereafter gametes) from each sex, where selection depends on the sex of the diploid they came from and their allele at the \textbf{A} locus.
-Gametes from males then pair randomly with gametes from females.
-The resulting zygotes develop as males or females, depending on their genotypes at the \textbf{X} and \textbf{M} loci (or the \textbf{M} genotype of their mother in the case of maternal control).
-Diploids compete with others of the same sex, where selection depends on the sex of the individual and its genotype at the \textbf{A} locus.
-This is followed by meiosis with recombination and sex-specific meiotic drive. 
+The life-cycle begins with competition between haploid gametes/gametophytes within each sex, where selection depends on the sex of the diploid they came from and their allele at the \textbf{A} locus.
+Gametes/gametophytes from males then mate randomly with gametes/gametophytes from females.
+The resulting zygotes develop as males or females, depending on their genotypes at the \textbf{X} and \textbf{M} loci.
+Diploids then compete with others of the same sex, where selection depends on the sex of the individual and its genotype at the \textbf{A} locus.
+This is followed by meiosis with recombination. 
 Recombination occurs between loci \textbf{X} and \textbf{A} with probability $r$, between loci \textbf{A} and \textbf{M} with probability $R$, and between loci \textbf{X} and \textbf{M} with probability $\chi$.
@@
 Any order of the loci can be modelled with appropriate choices of $r$, $R$, and $\chi$.
-We model meiotic drive at the viability locus only; individuals of sex $i$ who are heterozygous at the \textbf{A} locus produce haploids bearing allele $A$ with probability $\alpha^i$.
 We track the frequency of haploid genotypes produced by each sex from one generation to the next (recursion equations in Sup.\ Mat.).
@@
 %the dynamics can be described by the frequency of $A$ in gametes/gametophytes from the homogametic sex and the frequencies of $A$ in the two types of gametes/gametophytes from the heterogametic sex.
-We then examine the ability of a rare, novel sex-determiner, $m$, to increase in frequency from this equilibrium.
+We then examine the ability of a rare, novel sex-determiner $m$ to increase in frequency at this equilibrium.
 Numerical simulations are used to examine when an invading mutation goes to fixation.
@@
 \subsection*{Resident equilibrium and stability}
-With allele $M$ fixed, we follow the dynamics of the frequency of $A$ in gametes from the homogametic sex (e.g., in eggs from an XX female, $p^f_X$), the frequencies of $A$ in the two types of gametes from the heterogametic sex (e.g., in sperm from an XY male that are X-bearing, $p^m_X$, and Y-bearing, $p^m_Y$), and the frequencies of the sex-determining factors in gametes from the heterogametic sex (e.g., the frequency of Y in sperm, $q$).
-Assuming selection and meiotic drive are weak relative to recombination, the differences in the frequencies of $A$ in each type of gamete are small, as is the bias in the sex-determining factor from the heterogametic sex, and we can solve for the mean frequency of $A$ across all types ($p_A$), the difference in the frequencies of $A$ between two of the three types, and the bias in the frequency of the sex-determining factor, to first order in selection.
+With allele $M$ fixed, we follow the dynamics of the frequency of $A$ in gametes/gametophytes from the homogametic sex (e.g., in eggs from an XX female, $p_{Xf}$) and the frequencies of $A$ in the two types of gametes/gametophytes from the heterogametic sex (e.g., in sperm from an XY male that are X-bearing, $p_{Xm}$, and Y-bearing, $p_{Ym}$).
+Assuming selection is weak relative to recombination, the differences in the frequencies of $A$ in each type of gamete/gametophyte are small, and we can solve for the mean frequency of $A$ across all types ($p_A$) as well as the difference in the frequencies of $A$ between two of the three types, to first order in selection.
 Linear stability analysis can then be used to determine the stability of this equilibrium.
-Without haploid selection or meiotic drive our results reduce to those of \cite{vanDoorn:2007eu}.
-%when $k=0$ (neo-$Y$ invading a $ZW$ system) or when $k=1$ (neo-$W$ invading an $XY$ system) (\textcolor{red}{CHECK}).
-However, with haploid selection or meiotic drive a stable polymorphism at locus \textbf{A} no longer requires sexually antagonistic selection.
-%, as it can also be achieved by ploidally-antagonistic selection.
+With no haploid selection and $k=0$ (neo-$Y$ invading a $ZW$ system) or $k=1$ (neo-$W$ invading an $XY$ system), our results reduce to those of \cite{vanDoorn:2010hu}.
 
@@
 %, evaluated at the above equilibrium.
-Below we present the results for invasion into an $XY$ system assuming no competition among gametes from females, no meiotic drive in females, and linear arrangement \textbf{X}\textbf{A}\textbf{M}.
-%(i.e., $\chi = r R$).
-%(SAY SOMETHING HERE ABOUT OTHER ARRANGEMENTS?).
-%equal dominance coefficients in the two sexes,
-Equivalent results for invasions into a $ZW$ system can be derived by consistently switching the roles of males and females \citep{vanDoorn:2010hu}.
+Below we present the results for invasion into an $XY$ system assuming equal dominance coefficients in the two sexes, no competition among gametes/gametophytes from females, and linear arrangement \textbf{X}\textbf{A}\textbf{M}.
+Equivalent results for invasions into a $ZW$ system are given in the Sup.\ Mat.
 
-%\subsubsection*{Neo-$Y$}
-%
-%%write in general form without weak selection
-%A rare, dominant neo-$Y$ ($k=0$) is always expected to invade the ancestral $XY$ system when the average growth rate of mutant haplotypes ($Am$ and $am$) is positive, $(g_A + g_a)/2 > 0$.
-%($g_i = where $\lambda_i$ are the two eigenvalues when $R=r=0$; the \textbf{X} locus does not affect the dynamics).
-%When the growth rates of the mutant haplotypes without recombination ($R=0$) are negative, $g_i^* < 0 \; \forall \; i \in \{A,a\}$, where $g_i < g_i^*$, the neo-$Y$ does not invade.
-%Otherwise, the mutant allele increases in frequency on one \textbf{A} background and declines on the other and neo-$Y$ invasion requires
-%\begin{equation}
-%R \left[ \frac{p^f_X w_{m,a}}{g_A^*} + \frac{(1 - p^f_X) w_{m,A}}{g_a^*} \right] w_{m,Aa} < \nu_m,
-%\end{equation}
-%where $w_{m,i}$ is the relative viability fitness of males depending on their haploid or diploid genotype at the \textbf{A} locus (with $i\in\{A,a,AA,Aa,aa\}$) and
-%$\nu_m = 
-%  p^f_X p_{Ym} w^m_{a} w^m_{AA} +
-%  p^f_X (1-p_{Ym}) w^m_{a} w^m_{AA} +
-%  (1-p^f_X) p_{Ym} w^m_{a} w^m_{AA} +
-%  (1-p^f_X) (1-p_{Ym}) w^m_a w^m_{AA}$
-%is the mean relative fitness of resident males.
-%%and $g_j^*$ is the growth rate of $X^m$ and $Ym$ haplotypes when on an $A$ ($j=A$)  or $a$ background ($j=a$).
-%Neo-$Y$ invasion therefore occurs for any recombination rate, $R$, when the net flow of double recombinants is from the less fit to the more fit \textbf{A} background (making the term inside the square brackets negative).
-%%Assuming $g_A^* > 0$ and $g_a^* < 0$ without loss of generality, this is $-(1 - p^f_X) w_{m,A} g_a^* < p^f_X w_{m,a} g_A^*$.
-%When the net flow of double recombinants is from the more fit to the less fit haplotype, neo-$Y$ invasion can still occur when the rate of recombination is small enough.
-%
-%%weak selection
-%Assuming weak selection, we can solve for the invasion fitness of the neo-$Y$ explicitly, giving
-%\begin{equation}
-%\lambda_{Y,XY} \approx 1 + V_A S_A (r - R)s^f,
-%\end{equation}
-%where $V_A = p_A(1-p_A)$ is the variance at the \textbf{A} locus, $S_A = s^f/ \left[ r R \left( s^f + s^m \right)^2 t_m^2 \right]$ (INTERPRETATION), $s^f$ and $s^m$ are the respective selection coefficients for $A$ in diploid females and males, $t_m$ is the selection coefficient for $A$ in gametes/gametophytes from males, and we've assumed equal dominance coefficients in the two sexes.
-%The neo-$Y$ can therefore invade whenever it is in tighter linkage with the selected locus than the ancestral sex-determining locus, $r>R$, provided locus \textbf{A} is polymorphic ($V_A>0$) and there is selection among both females ($s^f\neq0$) and gametes/gametophytes from males ($t_m\neq0$).
-%
-%\subsubsection*{Neo-$W$}
-%
-%%write in general form without weak selection
-%Similarly, a rare, dominant neo-$W$ ($k=1$) will invade the ancestral $XY$ system whenever the average growth rate of $XAm$ and $Xam$ haplotypes is positive, $(g_A + g_a) / 2 > 1$. 
-%When the growth rates of the mutant haplotypes without recombination ($R=0$) are negative, $g_i^* < 0 \; \forall \; i \in \{A,a\}$, where $g_i < g_i^*$, the neo-$W$ does not invade.
-%Otherwise neo-$W$ invasion requires
-%\begin{equation}
-%R \left[ \frac{\bar{p}_m w_{m,A}}{g_a^*} + \frac{(1 - \bar{p}_m) w_{m,a}}{g_A^*} \right] w_{f,Aa} < \nu_f
-%\end{equation}
-%where $\bar{p}_m = (p_{Ym}+p^m_X) / 2$ is the mean frequency of $A$ in gametes/gametophytes from males, $w_{f,i}$ is the relative viability fitness of females depending on their diploid genotype at the \textbf{A} locus (with $i\in\{AA,Aa,aa\}$), and
-%$\nu_f = 
-%  p^f_X p^m_X w^m_{a} w_{AA,f} +
-%  p^f_X (1-p^m_X) w^m_{a} w_{Aa,f} +
-%  (1-p^f_X) p^m_X w^m_{a} w_{Aa,f} +
-%  (1-p^f_X) (1-p^m_X) w^m_a w_{aa,f}$
-%is the mean relative fitness of resident females. 
-%%The rate of recombination between the \textbf{X} and \textbf{A} loci, $r$, does not explicitly appear because females are homozygous at the \textbf{X} locus with an ancestral $XY$ system.
-%As in the case of the neo-$Y$, neo-$W$ invasion therefore occurs with any recombination rate, $R$, when the net flow of recombinants is from the less fit to the more fit haplotype.
-%%Assuming $g_A^*>0$ and $g_a^*<0$ without loss of generality, this is $(1 - \bar{p}_m) w_{m,a} g_a^*< \bar{p}_m w_{m,A} g_A^*$.
-%And when the net flow of recombinants is from the more fit to the less fit  haplotype, neo-$W$ invasion can still occur when the rate of recombination is small enough.
-%
-%%weak selection
-%Assuming weak selection, we can solve for the invasion fitness of the neo-$W$ explicitly, giving
-%\begin{equation}
-%\lambda_{W,XY} \approx 1 + V_A S_A \frac{(2r(1-R)-R) s^f + (1-2r)R s^m }{2},
-%\end{equation}
-%where we've once again assumed equal dominance coefficients in the two sexes.
-%In this case, even when the novel sex-determining locus is in looser linkage with the selected locus than is the ancestral sex-determining locus, $r<R$, a novel sex-determiner can invade.
-%For example, with $R=1/2$ the neo-$W$ invades if there is any linkage between the ancestral sex-determining and selected loci ($r<1/2$), there is selection among gametes/gametophytes in males ($t_m\neq0$), and there is selection for or against $A$ in both males and females ($s^m s^f >0$) that is stronger in females than in males ($|s^f| > |s^m|$).
+\subsubsection*{Neo-$Y$}
 
-\subsubsection*{Neo-$Y$ and neo-$W$}
+The growth rate of a rare, dominant neo-$Y$ region ($k=0$) is
+\begin{equation}
+\lambda_{Y,XY} = 1 + V_A \frac{(r - R)}{r R} \frac{s_f^2}{\left( s_f + s_m \right)^2} t_m^2,
+\end{equation}
+where $V_A = p_A(1-p_A)$ is the variance at the \textbf{A} locus, $s_f$ and $s_m$ are the respective selection coefficients for $A$ in diploid females and males, and $t_m$ is the selection coefficient for $A$ in gametes/gametophytes from males.
+The neo-Y can therefore invade whenever it is in tighter linkage with the selected locus than is the ancestral sex-determining locus, $r>R$, provided locus \textbf{A} is polymorphic ($V_A>0$) and there is selection among both females ($s_f\neq0$) and gametes/gametophytes from males ($t_m\neq0$).
+%write in general form without weak selection
 
+\subsubsection*{Neo-$W$}
+
+The growth rate of a rare, dominant neo-$W$ region ($k=1$) is
+\begin{equation}
+\lambda_{W,XY} = 1 + V_A \frac{s_f \left( (2 r (1-R) +R) s_f + (1- 2r) R s_m \right)}{2 r R \left( s_f + s_m \right)^2} t_m^2.
+\end{equation}
+In this case, even when the novel sex-determining locus is in looser linkage with the selected locus than is the ancestral sex-determining locus, $r<R$, a novel sex-determiner can invade.
+For example, with $R=1/2$ the neo-W invades if there is some linkage between the ancestral sex-determining and selected loci ($r<1/2$), there is selection among gametes/gametophytes in males ($t_m\neq0$), and there is selection for or against $A$ in both males and females ($s_m s_f >0$) that is stronger in females than in males ($|s_f| > |s_m|$).
 %write in general form without weak selection
-A rare, dominant neo-$Y$ ($k=0$) or neo-$W$ ($k=1$) is always expected to invade an ancestral $XY$ system when the average growth rate of the mutant haplotypes ($Am$ and $am$) is positive, $(g_A + g_a)/2 > 0$.
-%($g_i = where $\lambda_i$ are the two eigenvalues when $R=r=0$; the \textbf{X} locus does not affect the dynamics).
-When the growth rates of the mutant haplotypes without recombination ($R=0$) are negative, $g_i^* < 0 \; \forall \; i \in \{A,a\}$, where $g_i < g_i^*$, the new sex-determining allele does not invade.
 
-Otherwise, the new sex-determining allele increases in frequency on one \textbf{A} background and declines on the other, and invasion requires
-\begin{equation}\label{eq:neoYR}
-R \left[ \frac{p^f_X w^m_a (1-\alpha^m)}{g_A^*} + \frac{(1 - p^f_X) w^m_A \alpha^m}{g_a^*} \right] w^m_{Aa} < \nu^m,
+\subsubsection*{Neo-ESD}
+
+The growth rate of a rare, dominant neo-ESD region that produces males or females with equal probability ($k=1/2$) is
+\begin{equation}
+\lambda_{ESD,XY} = 1 + \frac{(\lambda_{Y,XY} - 1) + (\lambda_{W,XY} -1)}{4} \Big|_{R=1/2}
+%V_A \frac{r}{1-2r}  \frac{s_{f} \left( s_m - 3 s_f\right) }{8 \left( s_{f} + s_{m} \right)^2} t_{m}^2.
 \end{equation}
-for the neo-$Y$, and 
-\begin{equation}\label{eq:neoWR}
-R \left[  \frac{(1 - \bar{p}^m) w^m_{a}}{g_A^*} + \frac{\bar{p}^m w^m_{A}}{g_a^*} \right] w^f_{Aa} < \nu^f
-\end{equation}
-for the neo-$W$.
-Here $\bar{p}^m = (p^m_X+p^m_Y)/2$ is the average frequency of $A$ in gametes produced by males, $w^i_{j}$ is the relative viability fitness of sex $i\in\{m,f\}$ depending on their haploid or diploid genotype at the \textbf{A} locus (with $j\in\{A,a,AA,Aa,aa\}$) and
-$\nu^i = 
-  p^f_X p^m_{\textbf{X}^i} w^m_{a} w^i_{AA} +
-  p^f_X (1-p^m_{\textbf{X}^i}) w^m_{a} w^i_{Aa} +
-  (1-p^f_X) p^m_{\textbf{X}^i} w^m_{a} w^i_{Aa} +
-  (1-p^f_X) (1-p^m_{\textbf{X}^i}) w^m_a w^i_{aa}$,
-with $\textbf{X}^m = Y$ and $\textbf{X}^f = X$, is the mean relative fitness of resident individuals of sex $i$.
-%and $g_j^*$ is the growth rate of $X^m$ and $Ym$ haplotypes when on an $A$ ($j=A$)  or $a$ background ($j=a$).
-Although male meiotic drive does not explicitly appear in Equation \ref{eq:neoWR}, it does affect the average frequency of $A$ in gametes from males, $\bar{p}^m$, and thus can play a role in neo-W invasion.
-
-Equations \eqref{eq:neoYR} and \eqref{eq:neoWR} show that the new sex-determining allele is expected to invade for any recombination rate, $R$, when the net flow of double recombinants is from the less fit to the more fit \textbf{A} background (making the terms inside the square brackets in Equations \ref{eq:neoYR} and \ref{eq:neoWR} negative).
-%Assuming $g_A^* > 0$ and $g_a^* < 0$ without loss of generality, this is $-(1 - p^f_X) w_{m,A} g_a^* < p^f_X w_{m,a} g_A^*$.
-When the net flow of double recombinants is from the more fit to the less fit haplotype, the new sex-determining allele can still invade when the rate of recombination between it and the selected locus, $R$, is small enough.
-
-%weak selection
-Assuming weak selection and meiotic drive, we can explicitly solve for the invasion fitness of the new sex-determining allele, $m$, into the ancestral $XY$ system, giving
-\begin{equation}
-\lambda_{m,XY} \approx 1 + V_A S_A C_m,
-\end{equation}
-where $V_A = p_A(1-p_A)$ is the variance at the \textbf{A} locus.
-We will consider haploid selection and meiotic drive separately.
-With haploid selection and no drive we have $S_A = s^f (t^m)^2 / \left[ r R \left( s^f + s^m \right)^2 \right]$, where $s^f$ and $s^m$ are the respective selection coefficients for $A$ in diploid females and males, $t^m$ is the selection coefficient for $A$ in gametes from males, and we've assumed equal dominance coefficients in the two sexes.
-With drive and no haploid selection we replace $t^m$ with $\alpha^m-1/2$.
-
-For the neo-$Y$ we have $C_Y = (r - R)s^f $ with haploid selection and $C_Y = 4(r - R)s^f $ with drive.
-The neo-$Y$ can therefore invade whenever it is in tighter linkage with the selected locus than the ancestral sex-determining locus, $r>R$, provided locus \textbf{A} is polymorphic ($V_A>0$), there is diploid selection in females ($s^f\neq0$), and there is either haploid selection between gametes from males ($t^m\neq0$) or meiotic drive in males ($\alpha^m\neq1/2$).
-This reduces to the weak-linkage results of \cite{vanDoorn:2007eu} when we do not assume equal dominance coefficients in the two sexes, there is no haploid selection or meiotic drive, and there is free recombination between locus \textbf{A} and one of the sex-determining regions.
-
-For the neo-$W$ we have $C_W = [(2r(1-R)-R) s^f + (1-2r)R s^m]/2$ with haploid selection and $C_W = 4[r(1-2R) s^f + (1-2r)R s^m]/2$ with drive.
-In this case, even when the novel sex-determining locus is in looser linkage with the selected locus than the ancestral sex-determining locus is, $r<R$, a neo-$W$ can invade (Figure \ref{fig:Winvasion}).
-For example, $R=1/2$ the neo-$W$ invades if there is any linkage between the ancestral sex-determining and selected loci ($r<1/2$), there is selection among gametes in males ($t^m\neq0$), and there is selection for or against $A$ in both males and females ($s^m s^f >0$) that is stronger in males than in females ($|s^m| > |s^f|$).
-With meiotic drive and $R=1/2$, all that is required for neo-W invasion is $r<1/2$ and $s^m s^f >0$.
-Our results reduce to the weak-linkage results of \cite[][Equation 3]{vanDoorn:2010hu} when we do not assume equal dominance coefficients in the two sexes and there is no haploid selection or meiotic drive.
-
-%\subsubsection*{Neo-$W$}
-%
-%%write in general form without weak selection
-%Similarly, a rare, dominant neo-$W$ ($k=1$) will invade the ancestral $XY$ system whenever the average growth rate of $XAm$ and $Xam$ haplotypes is positive, $(g_A + g_a) / 2 > 1$. 
-%When the growth rates of the mutant haplotypes without recombination ($R=0$) are negative, $g_i^* < 0 \; \forall \; i \in \{A,a\}$, where $g_i < g_i^*$, the neo-$W$ does not invade.
-%Otherwise neo-$W$ invasion requires
-%\begin{equation}
-%R \left[ \frac{\bar{p}_m w_{m,A}}{g_a^*} + \frac{(1 - \bar{p}_m) w_{m,a}}{g_A^*} \right] w_{f,Aa} < \nu_f
-%\end{equation}
-%where $\bar{p}_m = (p_{Ym}+p^m_X) / 2$ is the mean frequency of $A$ in gametes/gametophytes from males, $w_{f,i}$ is the relative viability fitness of females depending on their diploid genotype at the \textbf{A} locus (with $i\in\{AA,Aa,aa\}$), and
-%$\nu_f = 
-%  p^f_X p^m_X w^m_{a} w_{AA,f} +
-%  p^f_X (1-p^m_X) w^m_{a} w_{Aa,f} +
-%  (1-p^f_X) p^m_X w^m_{a} w_{Aa,f} +
-%  (1-p^f_X) (1-p^m_X) w^m_a w_{aa,f}$
-%is the mean relative fitness of resident females. 
-%%The rate of recombination between the \textbf{X} and \textbf{A} loci, $r$, does not explicitly appear because females are homozygous at the \textbf{X} locus with an ancestral $XY$ system.
-%As in the case of the neo-$Y$, neo-$W$ invasion therefore occurs with any recombination rate, $R$, when the net flow of recombinants is from the less fit to the more fit haplotype.
-%%Assuming $g_A^*>0$ and $g_a^*<0$ without loss of generality, this is $(1 - \bar{p}_m) w_{m,a} g_a^*< \bar{p}_m w_{m,A} g_A^*$.
-%And when the net flow of recombinants is from the more fit to the less fit  haplotype, neo-$W$ invasion can still occur when the rate of recombination is small enough.
-%
-%%weak selection
-%Assuming weak selection, we can solve for the invasion fitness of the neo-$W$ explicitly, giving
-%\begin{equation}
-%\lambda_{W,XY} \approx 1 + V_A S_A \frac{(2r(1-R)-R) s^f + (1-2r)R s^m }{2},
-%\end{equation}
-%where we've once again assumed equal dominance coefficients in the two sexes.
-%In this case, even when the novel sex-determining locus is in looser linkage with the selected locus than is the ancestral sex-determining locus, $r<R$, a novel sex-determiner can invade.
-%For example, with $R=1/2$ the neo-$W$ invades if there is any linkage between the ancestral sex-determining and selected loci ($r<1/2$), there is selection among gametes/gametophytes in males ($t_m\neq0$), and there is selection for or against $A$ in both males and females ($s^m s^f >0$) that is stronger in females than in males ($|s^f| > |s^m|$).
-
-\subsubsection*{Offspring-controlled neo-ESD}
-
-The growth rate of a rare, dominant offspring-controlled neo-ESD region that produces males or females with equal probability ($k=1/2$) is
-\begin{equation}
-\lambda_{ESD,XY} \approx 1 + \frac{1}{2}\frac{(\lambda_{Y,XY} - 1) + (\lambda_{W,XY} -1)}{2} \Big|_{R=1/2}
-%V_A \frac{r}{1-2r}  \frac{s_{f} \left( s^m - 3 s^f\right) }{8 \left( s_{f} + s_{m} \right)^2} t_{m}^2.
-\end{equation}
-Thus with $k=1/2$ the neo-ESD gets half of the advantages of a neo-$W$ and half that of a neo-$Y$, but only has an effect one half of the time (the other half of the time it produces the same sex as the ancestral system would have).
+Thus the $k=1/2$ case gets half of the advantages of a neo-$W$ and half that of a neo-$Y$.  
 Recombination between the selected locus and the novel sex-determining locus, $R$, doesn't enter into the $k=1/2$ results because sex is essentially randomized each generation, %as if the novel sex-determiner were on an unlinked site that half the time acts as a neo-$W$ and half the time as a neo-$Y$.
 preventing associations from building up between allele $A$ and sex.  
+%write in general form without weak selection
 
-\subsubsection*{Maternally-controlled neo-ESD}
-
-One might think that when the sex of zygotes is under the control of mothers, there would be strong selection to balance the sex ratio among zygotes. 
-However, we find that, as with offspring control, when assuming weak selection the invasion fitness of a sex-determiner that is maternally controlled can be written
-\begin{equation}
-\lambda_{k,XY} \approx 1 + V_A S_A C_k,
-\end{equation}
-where
-%\begin{equation}
-%V_A = \frac{- \left[ t_m + h (s_{f}+s_{m}) \right] \left[ t_m + (1-h) (s_{f}+s_{m}) \right]}{(1-2h)^2(s_{f}+s_{m})^2}
-%\end{equation}
-%is the variance in $A$ ($V_A>0$ when the polymorphic resident equilibrium is stable), 
-%with $h$ the dominance coefficient (equal in both sexes), 
-$C_k$ is a term that depends on $k$.
-%
-%%k=0
-%\begin{equation}
-%C_0 = big \; ugly \; term
-%\end{equation}
-%
-%%k=1
-%\begin{equation}
-%C_1 = \frac{\left[ (2r(1-R)-R) s^f + (1-2r)R s^m \right]}{2}
-%\end{equation}
-%
-%%k=1/2
-%\begin{equation}
-%C_{1/2} = even \; bigger, \; uglier \; term
-%\end{equation}
-%
-%When $k=1$ the maternal- and offspring-controlled results are the same, $C_1 = C_W$, since the mutation remains in females (and hence mutant daughters always have mutant mothers).
-%However, with $k\neq1$ the results with maternal control differ from those with offspring control.
-Of particular interest is $k=1/2$ (i.e., when the mother perfectly balances the sex ratio of her offspring).
-When both recombination rates are small we have $C_{1/2} \approx R(s^m - s^f)/8 = \lim_{r \rightarrow 0} C_1/4$.
-This implies that, at least under tight linkage, the invasion of maternally-controlled ESD is independent of $R$ (because $S_A\propto R^{-1}$) and can invade whenever a neo-$W$ can.
+\linenumbers
+\modulolinenumbers[2]
 
@@
 
-\section*{Figures}
-
-\begin{figure}
-\centering
-\includegraphics[width=0.5\linewidth]{FreqWLowR}\\
-\includegraphics[width=0.5\linewidth]{SexRatioLowR}\\
-\includegraphics[width=0.5\linewidth]{MeanDipFitLowR}
-\caption{
-A neo-$W$ invades an ancestrally $XY$ system and fixes (\textbf{A}) despite biasing the sex ratio (\textbf{B}) and decreasing mean diploid viability fitness (\textbf{C}).
-Parameters: $k=1$, $s^f = 0.05$, $s^m = 0.15$, $h^f = h^m = 0.7$, $t^f = 0$, $t^m = -0.1$, $\alpha^m = \alpha^f = 1/2$, $r=0.01$, $R=0.05$.
-}
-\label{fig:WinvasionLowR}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=0.5\linewidth]{FreqWHighR}\\
-\includegraphics[width=0.5\linewidth]{SexRatioHighR}\\
-\includegraphics[width=0.5\linewidth]{MeanDipFitHighR}
-\caption{
-A neo-$W$ invades an ancestrally $XY$ system (\textbf{A}) despite biasing the sex ratio (\textbf{B}) and decreasing mean diploid viability fitness (\textbf{C}).
-The neo-$W$ does not fix, producing a polymorphic sex-determination system.
-Parameters as in Figure \ref{fig:WinvasionLowR} but with $R=0.5$.
-}
-\label{fig:WinvasionHighR}
-\end{figure}
-
 \end{document}

### 2017-01-17 LaTeX/Turnover.tex
added beautiful appendix and updated model section up to characteristic polynomial.

--- 2016-12-21 LaTeX/Turnover.tex
@@
 %Predominant theories in which new sex-determining systems are favoured by selection involve sex ratio selection or fitness differences between sexes (e.g., sexually antagonistic selection). 
-Here, we utilize population genetic models to study the spread of novel sex-determining systems in the presence of
-%where we also include 
+Here, we utilize population genetic models to study the spread of novel sex-determiners in systems with 
 %a period of selection during the haploid stage produced by one sex, e.g., pollen or sperm competition. 
@@
 %genetic system
-We consider a three locus model.
+We consider the transition between an ancestral and novel sex determination systems using a three locus model.
 Locus \textbf{X} is the ancestral sex-determining region, with alleles $X$ and $Y$ (or $Z$ and $W$).
-Locus \textbf{A} is a region under selection, with alleles $A$ and $a$.
-And locus \textbf{M} is a novel sex-determining region, with alleles $M$ and $m$.
-With genotype $MM$ at locus \textbf{M}, the sex of a zygote is determined by the genotype at locus \textbf{X} ($XX$ become females and $XY$ become males, or $ZW$ become females and $ZZ$ become males).
-With at least one $m$ allele at locus \textbf{M}, a zygote develops as a female with probability $k$ and as a male with probability $1-k$.
-With $k=0$, the novel sex determiner is a masculinizer (i.e., a neo-Y) and with $k=1$ the novel sex determiner is a feminizer (i.e., a neo-W).
-With intermediate $k$, locus \textbf{M} is interpreted as an offspring controlled environmental sex-determining region.
+Locus \textbf{A} is a locus under selection, with alleles $A$ and $a$.
+Locus \textbf{M} is a novel sex-determining region, at which the null allele ($M$) is initially fixed in the population such that sex of zygotes is determined by the genotype at the ancestral sex-determining region, \textbf{X} ($XX$ become females and $XY$ become males, or $ZW$ become females and $ZZ$ become males).
+To evaluate the evolution of new sex-determination systems, we consider the invasion, fixation, maintenance, and/or loss of novel sex-determining alleles ($m$) at the \textbf{M} locus. 
+%We only do invasion analytically though (is this sentence still ok?)
+We assume that the \textbf{M} locus is dominant over the \textbf{X} locus such that zygotes with at least one $m$ allele at locus \textbf{M}, a zygote develops as a female with probability $k$ and as a male with probability $1-k$, regardless of the \textbf{X} locus genotype.
+With $k=0$, the $m$ allele is a masculinizer (i.e., a neo-Y) and with $k=1$ the $m$ allele is a feminizer (i.e., a neo-W).
+With intermediate $k$, the $m$ allele confers environmental sex determination such that zygotes develop as females in a proportion ($k$) of the environments they experience. 
 Finally, we also analyze a model of maternally-controlled environmental sex-determination (ESD), where mothers with at least one $m$ allele produce daughters with probability $k$.
@@
 %life-cycle
-The life-cycle begins with competition between haploid gametes/gametophytes (hereafter gametes) from each sex, where selection depends on the sex of the diploid they came from and their allele at the \textbf{A} locus.
-Gametes from males then pair randomly with gametes from females.
-The resulting zygotes develop as males or females, depending on their genotypes at the \textbf{X} and \textbf{M} loci (and the \textbf{M} genotype of their mother in the case of maternal control).
-Diploids compete with others of the same sex, where selection depends on the sex of the individual and its genotype at the \textbf{A} locus.
-This is followed by meiosis with recombination and sex-specific meiotic drive. 
+In each generation, we census the genotype frequencies in male and female gametes/gametophytes (hereafter gametes) before haploid competition (recursion equations in Sup.\ Mat.). 
+First, competition occurs among male gametes (sperm/pollen competition) and among female gametes (egg/ovule competition). 
+Selection during haploid competition depends on the \textbf{A} locus genotype, fitnesses are $w_{A}^m$ and $w_{a}^m$ for male gametes and $w_{A}^f$ and $w_{a}^f$ for female gametes, see table \ref{tab:fitnesstable}.
+Random mating then occurs between male and female gametes.
+The resulting zygotes develop as males or females, depending on their genotypes at the \textbf{X} and \textbf{M} loci (and the \textbf{M} genotype of their mother in the case of maternal control) as described above.
+Diploid males and females then experience selection, male fitness is given by $w_{h}^{m}$ and female fitness by $w_{h}^{f}$, where $h$ is the genotype at the \textbf{A} locus ($h \in AA, Aa, aa$).  
+%Diploids compete with others of the same sex, where selection depends on the sex of the individual and its genotype at the \textbf{A} locus.
+The next generation of gametes are then produced by meiosis, during which recombination and sex-specific meiotic drive can occur. 
 Recombination occurs between loci \textbf{X} and \textbf{A} with probability $r$, between loci \textbf{A} and \textbf{M} with probability $R$, and between loci \textbf{X} and \textbf{M} with probability $\chi$.
-%is chi really the prob of rec in our recursion equations?
-Any order of the loci can be modelled with appropriate choices of $r$, $R$, and $\chi$.
-We model meiotic drive at the viability locus only; individuals of sex $i$ who are heterozygous at the \textbf{A} locus produce haploids bearing allele $A$ with probability $\alpha^i$.
-We track the frequency of haploid genotypes produced by each sex from one generation to the next (recursion equations in Sup.\ Mat.).
+Therefore, any order of the loci can be modelled with appropriate choices of $r$, $R$, and $\chi$ (see Table \ref{tab:chisubstitutions}). 
+Males/females that are heterozygous at the \textbf{A} locus experience meiotic drive; $Aa$ heterozgotes of sex $d$ produce gametes bearing allele $A$ with probability $\alpha^d$. 
+Thus, the \textbf{A} locus experience sex-specific haploid competition, diploid selection and/or meiotic drive.
 
+\begin{table}[ht]
+\centering
+\smallskip
+\caption{Fitness of different genotypes in sex $d$}
+\begin{tabular}{l c }
+\hline\hline
+  Genotype & Fitness \\ [0.5ex] \hline
+  Haploid Competition & \\
+  A & $w_{A}^d = 1+t^d$ \\
+  a & $w_{a}^d = 1$ \\
+  Diploid Selection & \\
+  AA & $w_{AA}^d = 1+ s^d$ \\
+  Aa & $w_{Aa}^d = 1+h^k s^d$ \\
+  aa & $w_{aa}^d = 1$ \\
+  \hline \hline
+  \label{tab:fitnesstable}
+ \end{tabular}
+\end{table}
+
+%Info moved above
 %what were going to do, briefly
-With allele $M$ fixed at the \textbf{M} locus, sex is determined by locus \textbf{X} and an equilibrium is reached at locus \textbf{A}.
+%With allele $M$ fixed at the \textbf{M} locus, sex is determined by locus \textbf{X} and an equilibrium is reached at locus \textbf{A}.
 %where, importantly, locus \textbf{A} can be stably polymorphic.
 %the dynamics can be described by the frequency of $A$ in gametes/gametophytes from the homogametic sex and the frequencies of $A$ in the two types of gametes/gametophytes from the heterogametic sex.
-We then examine the ability of a rare, novel sex-determiner, $m$, to increase in frequency from this equilibrium.
-Numerical simulations are used to examine when an invading mutation goes to fixation.
+%We then examine the ability of a rare, novel sex-determiner, $m$, to increase in frequency from this equilibrium.
+%Numerical simulations are used to examine when an invading mutation goes to fixation.
 
@@
 
+The only asymmetry between males and females in our model is that, under the ancestral sex determination system, males develop with genotype $XY$ (or $ZZ$) and females with genotype $XX$ (or $ZW$). 
+Therefore, without loss of generality, we primarily present results for ancestral $XY$ sex determination. 
+Ancestral $ZW$ sex determination can be considered by changing the notation such that $X$ becomes $Z$, $Y$ becomes $W$ and the labelling of male and female selection terms are reversed.
+
+%I think this should be moved below because we have some 'results' where we don't assume weak selection but we only have the equilibrium calculated analytically for weak selection. 
 \subsection*{Resident equilibrium and stability}
-With allele $M$ fixed, we follow the dynamics of the frequency of $A$ in gametes from the homogametic sex (e.g., in eggs from an XX female, $p^f_X$), the frequencies of $A$ in the two types of gametes from the heterogametic sex (e.g., in sperm from an XY male that are X-bearing, $p^m_X$, and Y-bearing, $p^m_Y$), and the frequencies of the sex-determining factors in gametes from the heterogametic sex (e.g., the frequency of Y in sperm, $q$).
-Assuming selection and meiotic drive are weak relative to recombination, the differences in the frequencies of $A$ in each type of gamete are small, as is the bias in the sex-determining factor from the heterogametic sex, and we can solve for the mean frequency of $A$ across all types ($p_A$), the difference in the frequencies of $A$ between two of the three types, and the bias in the frequency of the sex-determining factor, to first order in selection.
-Linear stability analysis can then be used to determine the stability of this equilibrium.
-Without haploid selection or meiotic drive our results reduce to those of \cite{vanDoorn:2007eu}.
+In the resident population (allele $M$ fixed), we follow the frequency of $A$ in female gametes (eggs) from an XX female, $p^f_X$, and in X-bearing, $p^m_X$, and Y-bearing, $p^m_Y$, male gametes (sperm).
+We also track the total frequency of Y-bearing male gametes (sperm), $q$, which may deviate from $1/2$ due to meiotic drive in males.
+
+Various forms of selection can maintain a polymorphism at the \textbf{A} locus, including sexually antagonistic selection, overdominance and conflicts between diploid selection and selection upon haploid genotypes \citep[ploidally antagonistic selection,][]{Immler:2012tl} or a combination of these selective regimes.
+Here, we assume that selection and meiotic drive are weak relative to recombination ($s^k$ and $t^k$ of order $\epsilon$ and $\alpha^k=1/2+\alpha_{\Delta}^k$, where $\alpha_{\Delta}^k$ is of order $\epsilon$).
+The maintenance of a polymorphism at the \textbf{A} locus then requires that
+
+\begin{equation}
+\begin{split}
+0&<-((1-h^f)s^f +(1-h^m) s^m + t^f +t^m + 2\alpha_{\Delta}^f+2\alpha_{\Delta}^m)\\
+%
+0&<(h^f s^f +h^m s^m + t^f +t^m + 2\alpha_{\Delta}^f+2\alpha_{\Delta}^m).
+\end{split}
+\end{equation}
+
+Given that a polymorphism is maintained at the \textbf{A} locus by selection, with weak selection and drive, to leading order, the frequencies of $A$ in each type of gamete are the same ($\hat{p}^f_X=\hat{p}^m_X=\hat{p}^m_Y=\bar{p}$) and given by
+
+\begin{equation}
+\bar{p}=\frac{h^f s^f + h^m s^m +t^f+t^m+2\alpha_{\Delta}^f+2\alpha_{\Delta}^m}
+{(2h^f-1)s^f+(2h^m-1)s^m}
++O(\epsilon)
+.
+\label{eq:pAve}
+\end{equation}
+
+\noindent
+Differences in frequency between gamete types are of order $\epsilon$ to leading order and given by
+
+\begin{equation}
+\begin{split}
+\hat{p}^m_X-\hat{p}^f_X&=V_{A}\big{(}C^m - C^f \big{)}
++O(\epsilon^2)\\
+%
+\hat{p}^m_Y-\hat{p}^f_X&=V_{A}\big{(}C^m - C^f+(1-2r)(t^m-t^f)\big{)}/2r
++O(\epsilon^2)\\
+%
+\hat{p}^m_Y-\hat{p}^m_X&=V_{A}\big{(}C^m - C^f+(t^m-t^f)\big{)}(1-2r)/2r
++O(\epsilon^2)
+\end{split}
+\end{equation}
+
+\noindent
+where $V_{A}=\bar{p}(1-\bar{p})$ is the variance in the frequency of $A$ and $C^d=(\bar{p}+(1-2\bar{p})h^d) s^d +2\alpha_{\Delta}^d$. 
+The frequency of Y among male gametes is proportional to the difference in $A$ allele frequency on X- and Y-bearing male gametes, $q=\alpha_{\Delta}^m(\hat{p}^m_Y-\hat{p}^m_X)+O(\epsilon^3)$.
+Without haploid competition or drive ($\alpha_{\Delta}^d=t^d=0$), these results reduce to those of \citet{vanDoorn:2007eu}.
+
+% the differences in the frequencies of $A$ in each type of gamete are small, as is the bias in the sex-determining factor from the heterogametic sex, and we can solve for the mean frequency of $A$ across all types ($p_A$), the difference in the frequencies of $A$ between two of the three types, and the bias in the frequency of the sex-determining factor, to first order in selection.
+%Linear stability analysis can then be used to determine the stability of this equilibrium.
+%Without haploid selection or meiotic drive our results reduce to those of \cite{vanDoorn:2007eu}.
 %when $k=0$ (neo-$Y$ invading a $ZW$ system) or when $k=1$ (neo-$W$ invading an $XY$ system) (\textcolor{red}{CHECK}).
-However, with haploid selection or meiotic drive a stable polymorphism at locus \textbf{A} no longer requires sexually antagonistic selection.
+%However, with haploid selection or meiotic drive a stable polymorphism at locus \textbf{A} no longer requires sexually antagonistic selection.
 %, as it can also be achieved by ploidally-antagonistic selection.
@@
 \subsection*{Sex chromosome turnover}
-The spread of a rare mutant $m$ at the \textbf{M} locus in such a population is determined by the leading eigenvalue, $\lambda$, of the system described by the equations for the next generation frequency of haploid genotypes with the mutation.
+The evolution of a new sex determination system requires that a rare mutant, $m$, at the novel sex-determining locus  increases in frequency when rare. 
+The spread of a rare mutant $m$ at the \textbf{M} locus is determined by the leading eigenvalue, $\lambda$, of the system described by the equations for the next generation frequency of haploid genotypes with the mutation, (\ref{eq:recursions}c), (\ref{eq:recursions}d), (\ref{eq:recursions}g), (\ref{eq:recursions}h).
 %, evaluated at the above equilibrium.
-Below we present the analytic results for invasion into an $XY$ system assuming no competition among gametes from females, no meiotic drive in females, and linear arrangement \textbf{X}\textbf{A}\textbf{M}.
+%Here, we assume loci are arranged in the order \textbf{X}\textbf{A}\textbf{M} (i.e., $\chi=(1-r)R+(1-R)r$). 
+%Invasion is numerically evaluated for different locus arrangements in figure \ref{fig:InvasionVsCentiMorgans}, with qualitatively similar results.
 %(i.e., $\chi = r R$).
@@
 %equal dominance coefficients in the two sexes,
-Equivalent results for invasions into a $ZW$ system are derived by consistently switching the roles of males and females. %\citep{vanDoorn:2010hu}.
 
-%\subsubsection*{Neo-$Y$}
+\subsubsection*{Neo-$Y$}
+
+Invasion of a rare, dominant neo-$Y$ ($k=0$) is determined by the largest eigenvalue that solves the characteristic polynomial
+
+\begin{equation}
+a \lambda^2+ b \lambda + c =0
+\label{eq:charpoly_neoY}
+\end{equation}
+
 %
@@
 
+%<<<<<<< HEAD
+%\subsubsection*{Neo-$Y$}
+%
+%The growth rate of a rare, dominant neo-$Y$ region ($k=0$) is
+%\begin{equation}
+%\lambda_{Y,XY} = 1 + V_A \frac{(r - R)}{r R} \frac{s_f^2}{\left( s_f + s_m \right)^2} t_m^2,
+%\end{equation}
+%where $V_A = p_A(1-p_A)$ is the variance at the \textbf{A} locus, $s_f$ and $s_m$ are the respective selection coefficients for $A$ in diploid females and males, and $t_m$ is the selection coefficient for $A$ in gametes/gametophytes from males.
+%The neo-Y can therefore invade whenever it is in tighter linkage with the selected locus than is the ancestral sex-determining locus, $r>R$, provided locus \textbf{A} is polymorphic ($V_A>0$) and there is selection among both females ($s_f\neq0$) and gametes/gametophytes from males ($t_m\neq0$).
+%=======
+%>>>>>>> c89cd9e1d25a76e5bffdd1ee7574884f24c08070
 %write in general form without weak selection
@@
 
+\newpage
 \section*{Figures}
@@
 
+\setcounter{equation}{0}
+\renewcommand{\theequation}{S.\arabic{equation}}
+\setcounter{figure}{0}
+\renewcommand{\thefigure}{S.\arabic{figure}}
+\setcounter{table}{0}
+\renewcommand{\thetable}{S.\arabic{table}}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+
+\section*{Appendix}
+
+\subsection*{Recursion Equations}
+\label{app:recurs}
+
+In each generation we census the genotype frequencies in male and female gametes/gametophytes (hereafter, gametes) before haploid competition. 
+Before haploid competition, the frequencies of X-bearing male and female gametes are given by $X_{i}^{m}$ and $X_{i}^{f}$ and the frequencies of Y-bearing gametes are given by $Y_{i}^{m}$ and $Y_{i}^{f}$ where the index $i$ specifies genotypes $MA=1$, $Ma=2$, $mA=3$, and $ma=4$.
+Competition then occurs among gametes of the same sex (e.g., among eggs and among sperm separately) according to the \textbf{A} locus allele, $g$ ($g\in A$, $a$, see Table \ref{tab:fitnesstable}), carried by individuals with genotype $i$.
+The genotype frequencies after haploid competition are $X_{i}^{d,s}= w_{g}X_{i}^{d}/\bar{w}_{H}^{d}$ and $Y_{i}^{d,s}= w_{g}Y_{i}^{d}/\bar{w}_{H}^{d}$, where $\bar{w}_{H}^{d}=\sum_{i=1}^{4} w_{g}X_{i}^{d}+w_{g}Y_{i}^{d}$ is the mean fitness of male ($d=m$) or female ($d=f$) gametes.
+Random mating then occurs between gametes to produce diploid zygotes with genotype $ij$ at the \textbf{A} and \textbf{M} loci, such that $XX$ zygotes are denoted $xx_{ij}$, $XY$ zygotes are $xy_{ij}$, and $YY$ zygotes are $yy_{ij}$.
+In $XX$ and $YY$ zygotes, individuals with genotype $ij$ are equivalent to those with genotype $ji$. 
+For simplicity, we denote the frequency of genotype $ij$ in $XX$ and $YY$ zygotes to the average of these frequencies, $xx_{ij}=(X_{i}^{f,s}X_{j}^{m,s}+X_{j}^{f,s}X_{i}^{m,s})/2$ and $yy_{ij}=(Y_{i}^{f,s}Y_{j}^{m,s}+Y_{j}^{f,s}Y_{i}^{m,s})/2$.
+
+Denoting the \textbf{M} locus genotype by $b$ ($b\in MM$, $Mm$, $mm$) and the \textbf{X} locus genotype by $c$ ($c\in XX$, $XY$, $YY$), zygotes develop as females with probability $k_{bc}$. 
+Therefore, the frequencies of $XX$ females are given by $xx_{ij}^{f}=k_{bc}xx_{ij}$, $XY$ females are given by $xy_{ij}^{f}=k_{bc}xy_{ij}$, and $YY$ females are given by $yy_{ij}^{f}=k_{bc}xy_{ij}$. 
+Similarly, $XX$ male frequencies are $xx_{ij}^{m}=(1-k_{bc})xx_{ij}$, $XY$ male frequencies are $xy_{ij}^{m}=(1-k_{bc})xy_{ij}$, and $YY$ males frequencies are $yy_{ij}^{m}=(1-k_{bc})xy_{ij}$.
+This notation allows both the ancestral and novel sex-determining regions to determine zygotic sex according to an $XY$ system, a $ZW$ system, or an environmental sex-determining system. 
+In addition, we can consider any dominance relationship between the two sex-determining loci. 
+Typically, we assume that the ancestral sex-determining system (\textbf{X} locus) is $XY$ ($k_{MMXX}=1$ and $k_{MMXY}=k_{MMYY}=0$) and recessive to a dominant novel sex-determining locus, \textbf{M} ($k_{Mmc}=k_{mmc}=k$).
+
+Selection among diploids then occurs according to the diploid genotype at the \textbf{A} locus, $h$, for an individual of type $ij$ ($h \in AA$, $Aa$, $aa$, see Table \ref{tab:fitnesstable}). 
+The diploid frequencies after selection in sex $d$ are given by $xx_{ij}^{d,s}=w_{h}^{d} xx_{ij}/\bar{w}^{d}$, $xy_{ij}^{d,s}=w_{h}^{d} xy_{ij}/\bar{w}^{d}$, and $yy_{ij}^{d,s}=w_{h}^{d} yy_{ij}/\bar{w}^{d}$, where $\bar{w}^{d}= \sum_{i=1}^{4}\sum_{j=1}^{4}w_{h}^{d}xx_{ij}+w_{h}^{d}xy_{ij}+w_{h}^{d}yy_{ij}$ is the mean fitness of individuals of sex $d$.
+
+Finally, these diploids undergo meiosis to produce the next generation of gametes. 
+Recombination and sex-specific meiotic drive occur during meiosis.
+%We can also assume that recombination is sex specific and/or affected by the M locus - but generally we don't so I just describe $R=R_{f}=R, r_{MM,d}=r_{Mm,d}=r_{mm,d}=r, \chi_{m}=\chi_{f}=\chi$.
+Here, we allow the relative locations of the SDR, \textbf{A}, and \textbf{M} loci to be generic by using three parameters to describe the recombination rates between them.
+$R$ is the recombination rate between the \textbf{A} locus and the \textbf{M} locus, $\chi$ is the recombination rate between the \textbf{M} locus and the \textbf{X} locus, and $r$ is the recombination rate between the \textbf{A} locus and the \textbf{X} locus.
+Table \ref{tab:chisubstitutions} gives substitutions for $\chi$ for defined relative locus locations.
+During meiosis in sex $d$, meiotic drive occurs such that, in $Aa$ heterozygotes, a fraction $\alpha_{d}$ of gametes produced carry the $A$ allele and $(1-\alpha^d)$ carry the $a$ allele.
+
+\begin{table}[ht]
+\centering
+\smallskip
+\caption{$\chi$ substitutions for different loci orders (assuming no interference)}
+\begin{tabular}{l l}
+\hline\hline
+  Order of loci &   \\ [0.5ex] \hline
+  SDR-A-M & $\chi=R(1-r)+r(1-R)$  \\
+  SDR-M-A & $\chi=(r-R)/(1-2R)$ \\
+  A-SDR-M & $\chi=(R-r)/(1-2r)$ \\
+  \hline \hline
+  \label{tab:chisubstitutions}
+ \end{tabular}
+\end{table}
+
+Among gametes from sex $d$ (sperm/pollen when $d=m$, eggs/ovules when $d=f$), the frequency of haplotypes (before haploid competition) in the next generation are given by
+
+\begin{subequations}
+\begin{equation}
+\begin{split}
+X_{MA}^{d'}=&xx_{11}^{d,s}+xx_{13}^{d,s}/2+(xx_{12}^{d,s}+xx_{14}^{d,s})\alpha^d\\
+&-R(xx_{14}^{d,s}-xx_{23}^{d,s}) \alpha^d\\
+&+(xy_{11}^{d,s}+xy_{13}^{d,s})/2+(xy_{12}^{d,s}+xy_{14}^{d,s})\alpha^d\\
+&- r(xy_{12}^{d,s}-xy_{21}^{d,s})\alpha^d - \chi(xy_{13}^{d,s}-xy_{31}^{d,s})/2\\
+&+\big{\{}-(R+r+\chi)xy_{14}^{d,s} +(r+\chi-R)xy_{41}^{d,s}\\
+&+(R+r-\chi) xy_{23}^{d,s}+(R+\chi-r)xy_{32}^{d,s}\big{\}}\alpha^d/2
+\end{split}
+\end{equation}
+%
+\begin{equation}
+\begin{split}
+X_{Ma}^{d'}=&xx_{22}^{d,s}+xx_{24}^{d,s}/2+(xx_{12}^{d,s}+xx_{23}^{d,s})\alpha^d\\
+&-R(xx_{23}^{d,s}-xx_{14}^{d,s}) \alpha^d\\
+&(xy_{22}^{d,s}+xy_{24}^{d,s})/2+(xy_{21}^{d,s}+xy_{23}^{d,s})(1-\alpha^d)\\
+&- r(xy_{21}^{d,s}-xy_{12}^{d,s})(1-\alpha^d) - \chi(xy_{24}^{d,s}-xy_{42}^{d,s})/2\\
+&+\big{\{}-(R+r+\chi)xy_{23}^{d,s}+(r+\chi-R)xy_{32}^{d,s}\\
+&+(R+r-\chi) xy_{14}^{d,s}+(R+\chi-r)xy_{41}^{d,s}\big{\}}(1-\alpha^d)/2
+\end{split}
+\end{equation}
+%
+\begin{equation}
+\begin{split}
+X_{mA}^{d'}=&xx_{33}^{d,s}+xx_{13}^{d,s}/2+(xx_{23}^{d,s}+xx_{34}^{d,s})\alpha^d\\
+&-R(xx_{23}^{d,s}-xx_{14}^{d,s}) \alpha^d\\
+&(xy_{33}^{d,s}+xy_{31}^{d,s})/2+(xy_{32}^{d,s}+xy_{34}^{d,s})\alpha^d\\
+&- r(xy_{34}^{d,s}-xy_{43}^{d,s}) \alpha^d - \chi(xy_{31}^{d,s}-xy_{13}^{d,s})/2\\
+&+\big{\{}-(R+r+\chi)xy_{32}^{d,s} +(r+\chi-R)xy_{23}^{d,s}\\
+&+(R+r-\chi) xy_{41}^{d,s}+(R+\chi-r)xy_{14}^{d,s}\big{\}} \alpha^d/2
+\end{split}
+\end{equation}
+%
+\begin{equation}
+\begin{split}
+X_{ma}^{d'}=&xx_{44}^{d,s}+xx_{34}^{d,s}/2+(xx_{14}^{d,s}+xx_{24}^{d,s})\alpha^d\\
+&-R(xx_{14}^{d,s}-xx_{23}^{d,s}) \alpha^d\\
+&(xy_{44}^{d,s}+xy_{42}^{d,s})/2+(xy_{41}^{d,s}+xy_{43}^{d,s})(1-\alpha^d)\\
+&- r(xy_{43}^{d,s}-xy_{34}^{d,s})(1-\alpha^d) - \chi(xy_{42}^{d,s}-xy_{24}^{d,s})/2\\
+&+\big{\{}-(R+r+\chi)xy_{41}^{d,s}+(r+\chi-R)xy_{14}^{d,s}\\
+&+(R+r-\chi) xy_{32}^{d,s}+(R+\chi-r)xy_{23}^{d,s}\big{\}}(1-\alpha^d)/2
+\end{split}
+\end{equation}
+%%%%%%%%%%%%%%%%%%%
+%
+\begin{equation}
+\begin{split}
+Y_{MA}^{d'}=&yy_{11}^{d,s}+yy_{13}^{d,s}/2+(yy_{12}^{d,s}+yy_{14}^{d,s})\alpha^d\\
+&-R(yy_{14}^{d,s}-yy_{23}^{d,s}) \alpha^d\\
+&(xy_{11}^{d,s}+xy_{31}^{d,s})/2+(xy_{21}^{d,s}+xy_{41}^{d,s})\alpha^d\\
+&- r(xy_{21}^{d,s}-xy_{12}^{d,s})\alpha^d - \chi(xy_{31}^{d,s}-xy_{13}^{d,s})/2\\
+&+\big{\{} - (R+r+\chi)xy_{41}^{d,s} + (r+\chi-R)xy_{14}^{d,s}\\
+& + (R+r-\chi)xy_{32}^{d,s} + (R+\chi-r) xy_{23}^{d,s}\big{\}}\alpha^d/2
+\end{split}
+\end{equation}
+%
+\begin{equation}
+\begin{split}
+Y_{Ma}^{d'}=&yy_{22}^{d,s}+yy_{24}^{d,s}/2+(yy_{12}^{d,s}+yy_{23}^{d,s})\alpha^d\\
+&-R(yy_{23}^{d,s}-yy_{14}^{d,s}) \alpha^d\\
+&(xy_{22}^{d,s}+xy_{42}^{d,s})/2+(xy_{12}^{d,s}+xy_{32}^{d,s})(1-\alpha^d)\\
+&- r(xy_{12}^{d,s}-xy_{21}^{d,s})(1-\alpha^d) - \chi(xy_{42}^{d,s}-xy_{24}^{d,s})/2\\
+&+\big{\{}-(R+r+\chi)xy_{32}^{d,s} +(r+\chi-R) xy_{23}^{d,s}\\
+&+(R+r-\chi)xy_{41}^{d,s}+(R+\chi-r)xy_{14}^{d,s}\big{\}}(1-\alpha^d)/2
+\end{split}
+\end{equation}
+%
+\begin{equation}
+\begin{split}
+Y_{mA}^{d'}=&yy_{33}^{d,s}+yy_{13}^{d,s}/2+(yy_{23}^{d,s}+yy_{34}^{d,s})\alpha^d\\
+&-R(yy_{23}^{d,s}-yy_{14}^{d,s}) \alpha^d\\
+&(xy_{33}^{d,s}+xy_{13}^{d,s})/2+(xy_{23}^{d,s}+xy_{43}^{d,s})\alpha^d\\
+&- r(xy_{43}^{d,s}-xy_{34}^{d,s})\alpha^d - \chi(xy_{13}^{d,s}-xy_{31}^{d,s})/2\\
+&+\big{\{}-(R+r+\chi)xy_{23}^{d,s} +(r+\chi-R)xy_{32}^{d,s}\\
+&+(R+r-\chi) xy_{14}^{d,s} + (R+\chi-r) xy_{41}^{d,s}\big{\}}\alpha^d/2
+\end{split}
+\end{equation}
+%
+\begin{equation}
+\begin{split}
+Y_{ma}^{d'}=&yy_{44}^{d,s}+yy_{34}^{d,s}/2+(yy_{14}^{d,s}+yy_{24}^{d,s})\alpha^d\\
+&-R(yy_{14}^{d,s}-yy_{23}^{d,s}) \alpha^d\\
+&(xy_{44}^{d,s}+xy_{24}^{d,s})/2+(xy_{14}^{d,s}+xy_{34}^{d,s})(1-\alpha^d)\\
+&- r(xy_{34}^{d,s}-xy_{43}^{d,s})(1-\alpha^d) - \chi(xy_{24}^{d,s}-xy_{42}^{d,s})/2\\
+&+\big{\{}-(R+r+\chi) xy_{14}^{d,s} + (r+\chi-R)xy_{41}^{d,s}\\
+&+(R+r-\chi) xy_{23}^{d,s} + (R+\chi-r) xy_{32}^{d,s}\big{\}}(1-\alpha^d)/2
+\end{split}
+\end{equation}
+\label{eq:recursions}
+\end{subequations}
+
+\noindent
+The full system is therefore described by 16 recurrence equations (three loci, each with two alleles, and two gamete sexes yields 16 combinations). 
+However, some diploid types are not produced under a given sex determination system. 
+For example, with the $M$ allele fixed and ancestral $XY$ sex determination, there are no $XX$ males, $XY$ females, or $YY$ females ($xx_{11}^{m}$, $xx_{12}^{m}$, $xx_{22}^m$, $xy_{11}^{f}$, $xy_{12}^{f}$, $xy_{22}^f$, $yy_{11}^{f}$, $yy_{12}^{f}$, and $yy_{22}^f$ are all 0).
+In this case, the system only involves six recursion equations because there is only one \textbf{M} locus allele and no Y-bearing female gametes. 
+This six-equation system yields equilibrium \eqref{eq:pAve}. 
+Within this resident population (when $m$ is absent) we describe frequencies among different gamete types, which are given by $X_{MA}^{f}=p_{Xf}$, $X_{Ma}^{f}=(1-p_{Xf})$, $X_{MA}^{m}=(1-q)p_{Xm}$, $X_{Ma}^{m}=(1-q)(1-p_{Xm})$, $Y_{MA}^{m}=q p_{Ym}$, and $Y_{Ma}^{m}=q(1-p_{Ym})$.
+
 \end{document}

### 2017-01-19 LaTeX/Turnover.tex
additions to model, Results, Discussion and added awesome Appendix

@@
 The evolution of a new sex determination system requires that a rare mutant, $m$, at the novel sex-determining locus  increases in frequency when rare. 
-The spread of a rare mutant $m$ at the \textbf{M} locus is determined by the leading eigenvalue, $\lambda$, of the system described by the equations for the next generation frequency of haploid genotypes with the mutation, (\ref{eq:recursions}c), (\ref{eq:recursions}d), (\ref{eq:recursions}g), (\ref{eq:recursions}h).
+The spread of a rare mutant $m$ at the \textbf{M} locus is determined by the leading eigenvalue, $\lambda$, of the system described by the next generation frequency of eggs and sperm carrying the mutation, (\ref{eq:recursions}c), (\ref{eq:recursions}d), (\ref{eq:recursions}g), (\ref{eq:recursions}h), which is an eight equation system.
 %, evaluated at the above equilibrium.
-%Here, we assume loci are arranged in the order \textbf{X}\textbf{A}\textbf{M} (i.e., $\chi=(1-r)R+(1-R)r$). 
-%Invasion is numerically evaluated for different locus arrangements in figure \ref{fig:InvasionVsCentiMorgans}, with qualitatively similar results.
-%(i.e., $\chi = r R$).
-%(SAY SOMETHING HERE ABOUT OTHER ARRANGEMENTS?).
-%equal dominance coefficients in the two sexes,
-
-\subsubsection*{Neo-$Y$}
-
-Invasion of a rare, dominant neo-$Y$ ($k=0$) is determined by the largest eigenvalue that solves the characteristic polynomial
+%Thus, the system describing the change in frequency of the $m$ allele consists of eight recursion equations. 
+Dominant neo-Y chromosomes (when $k=0$) or neo-W chromosomes (when $k=1$) are only found in male diploids (neo-Y) or female diploids (neo-W) such that their long term growth rate depends only on the change in frequency of $m$-bearing gametes produced by males (for a neo-Y) or by females (for a neo-W).
+Furthermore, if the $m$ allele is fully dominant over the ancestral sex-determining system, phenotypes are not affected by the genotype at the ancestral sex-determining region (\textbf{X} locus). 
+Therefore, the invasion of rare mutant neo-Y or neo-W chromosomes can be described by a simpler, two equation system, the largest eigenvalue of which solves the characteristic polynomial
 
 \begin{equation}
-a \lambda^2+ b \lambda + c =0
+\lambda^2+ b \lambda + c =0
 \label{eq:charpoly_neoY}
 \end{equation}
+
+\noindent
+where $b$ is the average of the growth rates of the two haplotypes that carry the $m$ allele ($mA$ and $ma$), $b=(\lambda_{mA}^{m}+\lambda_{ma}^{m})/2$, and $c$ also involves the fitness of $m$ alleles when they recombine onto the other \textbf{A} background in a heterozygote, $c=\lambda_{mA}\lambda_{ma}+\rho_{mA}\rho_{ma}$.
+
+\begin{table}[ht]
+\centering
+\smallskip
+\caption{Parameters determining invasion (equation \ref{eq:charpoly_neoY}) for neo-Y or neo-W chromosomes}
+\begin{tabular}{l}
+\hline\hline
+   \noalign{\vskip 0.5ex}
+   neo-Y ($k=0$) \\ [0.5ex] \hline \noalign{\vskip 1ex}
+  $\lambda_{mA}=\{p_{Xf} w_{A}^{f} w_{A}^{m} w_{AA}^{m}+(1-p_{Xf}) w_{a}^{f} w_{A}^{m} w_{Aa}^{m}\alpha^m(1-R)\}/ \bar{w}_{H}^{f} \bar{w}_{H}^{m} \bar{w}^m$ \\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\lambda_{ma}=\{(1-p_{Xf}) w_{a}^{f} w_{a}^{m} w_{aa}^{m}+p_{Xf} w_{A}^{f} w_{a}^{m} w_{Aa}^{m}(1-\alpha^m)(1-R)\}/ \bar{w}_{H}^{f} \bar{w}_{H}^{m} \bar{w}^m $ \\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\rho_{mA}=R \{(1-p_{Xf}) w_{a}^{f} w_{A}^{m} w_{Aa}^{m} (1-\alpha_{m})\}/ \bar{w}_{H}^{f} \bar{w}_{H}^{m} \bar{w}^m $\\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\rho_{ma}=R\{p_{Xf} w_{A}^{f} w_{a}^{m} w_{Aa}^{m} \alpha_{m}\}/ \bar{w}_{H}^{f} \bar{w}_{H}^{m} \bar{w}^m$\\ [1ex] \hline 
+  \noalign{\vskip 0.5ex}
+  neo-W ($k=1$) \\ [0.5ex] \hline \noalign{\vskip 1ex}
+  $\lambda_{mA}=\{\bar{p}_{m} w_{A}^{m} w_{A}^{f} w_{AA}^{f}+(1-\bar{p}_{m}) w_{a}^{m} w_{A}^{f} w_{Aa}^{f}\alpha^f(1-R)\}/ \bar{w}_{H}^{f} \bar{w}_{H}^{m} \bar{w}^f$ \\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\lambda_{ma}=\{(1-\bar{p}_{m}) w_{a}^{m} w_{a}^{f} w_{aa}^{f}+\bar{p}_{m} w_{A}^{m} w_{a}^{f} w_{Aa}^{f}(1-\alpha^f)(1-R)\}/ \bar{w}_{H}^{f} \bar{w}_{H}^{m} \bar{w}^f $ \\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\rho_{mA}=R \{(1-\bar{p}_{m}) w_{a}^{m} w_{A}^{f} w_{Aa}^{f} (1-\alpha_{f})\}/ \bar{w}_{H}^{f} \bar{w}_{H}^{m} \bar{w}^f $\\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\rho_{ma}=R\{\bar{p}_{m} w_{A}^{m} w_{a}^{f} w_{Aa}^{f} \alpha_{f}\}/ \bar{w}_{H}^{f} \bar{w}_{H}^{m} \bar{w}^f$\\ [1ex] 
+  \hline \hline
+  \label{tab:haplotype_growth}
+ \end{tabular}
+\end{table}
 
@@
 
+Fisherian sex ratio selection follows from the fact that, for a given locus, half of the genetic material is inherited from a male, and half from a female. 
+Thus, if the population sex ratio is biased towards females, the average per-individual contribution of genetic material to the next generation from males is greater than the contribution from females (and vice versa for male-biased sex ratios).
+Therefore, an autosomal mutation that increases investment in males will spread via the higher per-individual contributions made by males. 
+In other words, the success of a non-sex-determining, autosomal mutant depends, in equal parts, on the contributions made by both males and females to the next generation.
+However, the mutations we consider here, neo-sex-determining alleles, do not follow the same inheritance rules. 
+For example, invasion of a dominant neo-Y depends on the number of neo-Y alleles contributed to the next generation by males only (equation \ref{eq:charpoly_neoY} and Table \ref{tab:haplotype_growth}) because neo-Y alleles will only be found in males.
+
+Sex ratio biases caused by haploid competition or meiotic drive have been shown to exert selection on various modifiers, which evolve to restore an equal sex ratio.
+
 {\color{blue}
@@
 \textcolor{red}{\noindent Discuss patterns that might be looked for:}
+
+Taken at face value, our results indicate that transitions in heterogametey (XY to ZW or vice versa) are more likely to be favoured by selection if there is selection upon both haploid and diploid genotypes rather than diploid selection alone.
 
@@
 $R$ is the recombination rate between the \textbf{A} locus and the \textbf{M} locus, $\chi$ is the recombination rate between the \textbf{M} locus and the \textbf{X} locus, and $r$ is the recombination rate between the \textbf{A} locus and the \textbf{X} locus.
-Table \ref{tab:chisubstitutions} gives substitutions for $\chi$ for defined relative locus locations.
+Table \ref{tab:chisubstitutions} gives substitutions for $\chi$ for defined relative locations of these loci.
 During meiosis in sex $d$, meiotic drive occurs such that, in $Aa$ heterozygotes, a fraction $\alpha_{d}$ of gametes produced carry the $A$ allele and $(1-\alpha^d)$ carry the $a$ allele.

### 2017-01-19 LaTeX/Turnover.tex
Adding extra results parts

@@
 \bibpunct{(}{)}{,}{a}{}{;}
+
+\usepackage[flushleft]{threeparttable}
 
@@
 %We only do invasion analytically though (is this sentence still ok?)
-We assume that the \textbf{M} locus is dominant over the \textbf{X} locus such that zygotes with at least one $m$ allele at locus \textbf{M}, a zygote develops as a female with probability $k$ and as a male with probability $1-k$, regardless of the \textbf{X} locus genotype.
+We assume that the \textbf{M} locus is dominant over the \textbf{X} locus such that zygotes with at least one $m$ allele develop as females with probability $k$ and as males with probability $1-k$, regardless of the \textbf{X} locus genotype.
 With $k=0$, the $m$ allele is a masculinizer (i.e., a neo-Y) and with $k=1$ the $m$ allele is a feminizer (i.e., a neo-W).
@@
 %life-cycle
-In each generation, we census the genotype frequencies in male and female gametes/gametophytes (hereafter gametes) before haploid competition (recursion equations in Sup.\ Mat.). 
+In each generation, we census the genotype frequencies in male and female gametes/gametophytes (hereafter gametes) before haploid competition (see Sup.\ Mat. for recursion equations). 
 First, competition occurs among male gametes (sperm/pollen competition) and among female gametes (egg/ovule competition). 
@@
 Males/females that are heterozygous at the \textbf{A} locus experience meiotic drive; $Aa$ heterozgotes of sex $d$ produce gametes bearing allele $A$ with probability $\alpha^d$. 
-Thus, the \textbf{A} locus experience sex-specific haploid competition, diploid selection and/or meiotic drive.
+Thus, the \textbf{A} locus can experience sex-specific haploid competition, diploid selection and/or meiotic drive.
 
@@
 \hline\hline
-  Genotype & Fitness \\ [0.5ex] \hline
-  Haploid Competition & \\
+  Genotype & Fitness during haploid competition \\ [0.5ex] \hline
   A & $w_{A}^d = 1+t^d$ \\
-  a & $w_{a}^d = 1$ \\
-  Diploid Selection & \\
+  a & $w_{a}^d = 1$ \\ [0.5ex] \hline
+  Genotype & Fitness during diploid selection \\ [0.5ex] \hline
   AA & $w_{AA}^d = 1+ s^d$ \\
   Aa & $w_{Aa}^d = 1+h^k s^d$ \\
-  aa & $w_{aa}^d = 1$ \\
+  aa & $w_{aa}^d = 1$ \\ [0.5ex] \hline
+  Genotype & Tranmission during meiosis in $Aa$ heterozygotes \\ [0.5ex] \hline
+  A & $\alpha^d=1/2+\alpha_{\Delta}^{d}$ \\
+  a & $(1-\alpha^d)=1/2-\alpha_{\Delta}^{d}$ \\
   \hline \hline
@@
 Various forms of selection can maintain a polymorphism at the \textbf{A} locus, including sexually antagonistic selection, overdominance and conflicts between diploid selection and selection upon haploid genotypes \citep[ploidally antagonistic selection,][]{Immler:2012tl} or a combination of these selective regimes.
-Here, we assume that selection and meiotic drive are weak relative to recombination ($s^k$ and $t^k$ of order $\epsilon$ and $\alpha^k=1/2+\alpha_{\Delta}^k$, where $\alpha_{\Delta}^k$ is of order $\epsilon$).
+Here, we assume that selection and meiotic drive are weak relative to recombination ($s^k$, $t^k$, $\alpha_{\Delta}^k$ of order $\epsilon$). 
 The maintenance of a polymorphism at the \textbf{A} locus then requires that
@@
 \end{split}
+\label{eq:freq_diffs}
 \end{equation}
@@
 where $V_{A}=\bar{p}(1-\bar{p})$ is the variance in the frequency of $A$ and $C^d=(\bar{p}+(1-2\bar{p})h^d) s^d +2\alpha_{\Delta}^d$. 
-The frequency of Y among male gametes is proportional to the difference in $A$ allele frequency on X- and Y-bearing male gametes, $q=\alpha_{\Delta}^m(\hat{p}^m_Y-\hat{p}^m_X)+O(\epsilon^3)$.
+The frequency of Y among male gametes is proportional to the difference in $A$ allele frequency on X- and Y-bearing male gametes, $q=1/2+\alpha_{\Delta}^m(\hat{p}^m_Y-\hat{p}^m_X)+O(\epsilon^3)$.
 Without haploid competition or drive ($\alpha_{\Delta}^d=t^d=0$), these results reduce to those of \citet{vanDoorn:2007eu}.
@@
 %Thus, the system describing the change in frequency of the $m$ allele consists of eight recursion equations. 
-Dominant neo-Y chromosomes (when $k=0$) or neo-W chromosomes (when $k=1$) are only found in male diploids (neo-Y) or female diploids (neo-W) such that their long term growth rate depends only on the change in frequency of $m$-bearing gametes produced by males (for a neo-Y) or by females (for a neo-W).
+Dominant neo-Y chromosomes (when $k=0$) or neo-W chromosomes (when $k=1$) are only found in male diploids (neo-Y) or female diploids (neo-W) such that their growth rate ultimately depends only on the change in frequency of $m$-bearing gametes produced by males (for a neo-Y) or by females (for a neo-W).
 Furthermore, if the $m$ allele is fully dominant over the ancestral sex-determining system, phenotypes are not affected by the genotype at the ancestral sex-determining region (\textbf{X} locus). 
@@
 \noindent
-where $b$ is the average of the growth rates of the two haplotypes that carry the $m$ allele ($mA$ and $ma$), $b=(\lambda_{mA}^{m}+\lambda_{ma}^{m})/2$, and $c$ also involves the fitness of $m$ alleles when they recombine onto the other \textbf{A} background in a heterozygote, $c=\lambda_{mA}\lambda_{ma}+\rho_{mA}\rho_{ma}$.
+where $b$ is the average of the growth rates of the two haplotypes that carry the $m$ allele ($mA$ and $ma$), $b=(\lambda_{mA}^{m}+\lambda_{ma}^{m})/2$, and $c$ also involves the fitness of $m$ alleles when they recombine onto the other \textbf{A} background in a heterozygote, $c=\lambda_{mA}\lambda_{ma}+\rho_{mA}\rho_{ma}$, see table \ref{tab:haplotype_growth}.
 
-\begin{table}[ht]
+\begin{threeparttable}[ht]
 \centering
@@
    neo-Y ($k=0$) \\ [0.5ex] \hline \noalign{\vskip 1ex}
-  $\lambda_{mA}=\{p_{Xf} w_{A}^{f} w_{A}^{m} w_{AA}^{m}+(1-p_{Xf}) w_{a}^{f} w_{A}^{m} w_{Aa}^{m}\alpha^m(1-R)\}/ \bar{w}_{H}^{f} \bar{w}_{H}^{m} \bar{w}^m$ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\lambda_{ma}=\{(1-p_{Xf}) w_{a}^{f} w_{a}^{m} w_{aa}^{m}+p_{Xf} w_{A}^{f} w_{a}^{m} w_{Aa}^{m}(1-\alpha^m)(1-R)\}/ \bar{w}_{H}^{f} \bar{w}_{H}^{m} \bar{w}^m $ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\rho_{mA}=R \{(1-p_{Xf}) w_{a}^{f} w_{A}^{m} w_{Aa}^{m} (1-\alpha_{m})\}/ \bar{w}_{H}^{f} \bar{w}_{H}^{m} \bar{w}^m $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\rho_{ma}=R\{p_{Xf} w_{A}^{f} w_{a}^{m} w_{Aa}^{m} \alpha_{m}\}/ \bar{w}_{H}^{f} \bar{w}_{H}^{m} \bar{w}^m$\\ [1ex] \hline 
+  $\lambda_{mA}=\{p_{X}^{f} w_{A}^{f} w_{A}^{m} w_{AA}^{m}+(1-p_{X}^{f}) w_{a}^{f} w_{A}^{m} w_{Aa}^{m}\alpha^m(1-R)\}/ \bar{w}_{H}^{f} \bar{w}_{H}^{m} \bar{w}^m$ \\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\lambda_{ma}=\{(1-p_{X}^{f}) w_{a}^{f} w_{a}^{m} w_{aa}^{m}+p_{X}^{f} w_{A}^{f} w_{a}^{m} w_{Aa}^{m}(1-\alpha^m)(1-R)\}/ \bar{w}_{H}^{f} \bar{w}_{H}^{m} \bar{w}^m $ \\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\rho_{mA}=R \{(1-p_{X}^{f}) w_{a}^{f} w_{A}^{m} w_{Aa}^{m} (1-\alpha_{m})\}/ \bar{w}_{H}^{f} \bar{w}_{H}^{m} \bar{w}^m $\\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\rho_{ma}=R\{p_{X}^{f} w_{A}^{f} w_{a}^{m} w_{Aa}^{m} \alpha_{m}\}/ \bar{w}_{H}^{f} \bar{w}_{H}^{m} \bar{w}^m$\\ [1ex] \hline 
   \noalign{\vskip 0.5ex}
-  neo-W ($k=1$) \\ [0.5ex] \hline \noalign{\vskip 1ex}
-  $\lambda_{mA}=\{\bar{p}_{m} w_{A}^{m} w_{A}^{f} w_{AA}^{f}+(1-\bar{p}_{m}) w_{a}^{m} w_{A}^{f} w_{Aa}^{f}\alpha^f(1-R)\}/ \bar{w}_{H}^{f} \bar{w}_{H}^{m} \bar{w}^f$ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\lambda_{ma}=\{(1-\bar{p}_{m}) w_{a}^{m} w_{a}^{f} w_{aa}^{f}+\bar{p}_{m} w_{A}^{m} w_{a}^{f} w_{Aa}^{f}(1-\alpha^f)(1-R)\}/ \bar{w}_{H}^{f} \bar{w}_{H}^{m} \bar{w}^f $ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\rho_{mA}=R \{(1-\bar{p}_{m}) w_{a}^{m} w_{A}^{f} w_{Aa}^{f} (1-\alpha_{f})\}/ \bar{w}_{H}^{f} \bar{w}_{H}^{m} \bar{w}^f $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\rho_{ma}=R\{\bar{p}_{m} w_{A}^{m} w_{a}^{f} w_{Aa}^{f} \alpha_{f}\}/ \bar{w}_{H}^{f} \bar{w}_{H}^{m} \bar{w}^f$\\ [1ex] 
+  neo-W ($k=1$) \** \\ [0.5ex] \hline \noalign{\vskip 1ex}
+  $\lambda_{mA}=\{\bar{p}^{m} w_{A}^{m} w_{A}^{f} w_{AA}^{f}+(1-\bar{p}^{m}) w_{a}^{m} w_{A}^{f} w_{Aa}^{f}\alpha^f(1-R)\}/ \bar{w}_{H}^{f} \bar{w}_{H}^{m} \bar{w}^f$ \\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\lambda_{ma}=\{(1-\bar{p}^{m}) w_{a}^{m} w_{a}^{f} w_{aa}^{f}+\bar{p}^{m} w_{A}^{m} w_{a}^{f} w_{Aa}^{f}(1-\alpha^f)(1-R)\}/ \bar{w}_{H}^{f} \bar{w}_{H}^{m} \bar{w}^f $ \\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\rho_{mA}=R \{(1-\bar{p}^{m}) w_{a}^{m} w_{A}^{f} w_{Aa}^{f} (1-\alpha_{f})\}/ \bar{w}_{H}^{f} \bar{w}_{H}^{m} \bar{w}^f $\\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\rho_{ma}=R\{\bar{p}^{m} w_{A}^{m} w_{a}^{f} w_{Aa}^{f} \alpha_{f}\}/ \bar{w}_{H}^{f} \bar{w}_{H}^{m} \bar{w}^f$\\ [1ex] 
   \hline \hline 
+   \end{tabular}
+      \begin{tablenotes}
+      \scriptsize
+      \item \** $\bar{p}^{m}=p_{Y}^{m}q+p_{X}^{m}(1-q)$ is the average frequency of the $A$ allele among X- and Y-bearing male gametes (pollen/sperm). 
+    \end{tablenotes}
   \label{tab:haplotype_growth}
- \end{tabular}
-\end{table}
+\end{threeparttable}
+
+Equation \eqref{eq:charpoly_neoY} and table \ref{tab:haplotype_growth} illustrate a number of key points about the invasion of neo-Y and neo-W mutations. 
+For a neo-Y, invasion depends on the relative \textcolor{red}{(is this right, is relative fitness divided by mean fitness or difference from 1???)} fitness of $A$-bearing and $a$-bearing male gametes (i.e., in sperm only, not eggs).
+The fitness of male gametes partly depends on the allele carried by the female gamete that they mate with (e.g., $A$ with probability $p_{X}^{f} w_{A}^{f}/\bar{w}_{H}^{f}$).
+Similarly, invasion of a neo-W depends on the relative fitness of $A$-bearing and $a$-bearing female gametes. 
+However, in the case of a neo-W, the allele carried by the male gamete that they mate with can come from either an X-bearing or a Y-bearing sperm (e.g., $A$ with probability $\bar{p}^{m} w_{A}^{m}/\bar{w}_{H}^{m}$, where $\bar{p}^{m}=p_{Y}^{m}q+p_{X}^{m}(1-q)$).
+In either case, the zygote will then develop as a female due to the presence of a neo-W.
+By contrast, females that do not carry the neo-W, only result from matings with X-bearing sperm (e.g., matings with $A$-bearing sperm occur with probability $\bar{p}_{X}^{m} w_{A}^{m}/\bar{w}_{H}^{m}$).
+If the \textbf{A} locus is initially linked to the ancestral sex-determining locus, \textbf{X}, (i.e., $r<1/2$) the frequency of the $A$ allele among X- and Y-bearing sperm can differ (equation \ref{eq:freq_diffs}).
+Thus, eggs with and without a neo-W differ in the frequency of alleles they obtain from mating with male gametes.
+
+Previous research suggests, when the ancestral sex-determining locus is linked to a locus that experiences haploid selection (e.g., meiotic drive), a new, unlinked sex-determining locus can invade in order to restore equal sex ratios \citep{Kozielska:2010vm}.
+Our model provides a good opportunity to determine whether Fisherian sex ratio selection provides a useful explanation for the evolution of new sex-determining loci in other contexts. 
+Consider, for example, the case where the \textbf{A} locus is linked to the ancestral-SDR ($r<1/2$) and experiences meiotic drive in males only (e.g., during spermatogenesis but not during oogenesis, $\alpha^m \neq 1/2$, $\alpha^f=1/2$).
+We will also disregard haploid competition ($t^f=t^m=0$) such that zygotic sex ratios can only be biased by meiotic drive in males. 
+In this case, the zygotic sex ratio can be initially biased only if the ancestral sex-determining system is XY. 
+If the ancestral sex-determining system is ZW, the zygotic sex ratio will be 1:1 because diploid sex is determined by the proportion of Z-bearing versus W-bearing eggs (and meiosis in females is fair).
+Thus, if the zygotic sex ratio is crucial to the evolution of new genetic sex-determining systems, invasion into ZW and XY systems will be distinct. 
+However, we find that invasion of new homogametic systems (XY to XY, or ZW to ZW) and heterogametic systems (XY to ZW or ZY to XY) occur under the same conditions. 
+That is, $\lambda_{XY,XY}=\lambda_{ZW,ZW}$ and $\lambda_{XY,ZW}=\lambda_{ZW,XY}$, where $\lambda_{i,j}$ indicates the growth rate of a new mutant giving sex-determining system $j$ in a population in which sex is ancestrally determined by system $i$.
+
+We are particularly concerned with whether or not a rare neo-sex-determining region increases in frequency, which occurs when the largest eigenvalue, $\lambda$, that solves \eqref{eq:charpoly_neoY} is greater than one.
+If the average change in frequency of the two haplotypes that carry the $m$ allele ($Am$ and $am$) is positive, invasion will always occur (if $\left\{(\lambda_{mA}-1)+ (\lambda_{ma}-1) \right\}/2>0$, $\lambda>1$).
+If neither haplotype increases in frequency ($\lambda_{mA}, \lambda_{ma} < 1$ \textcolor{red}{is this notation valid?}), the $m$ allele will not invade. 
+Otherwise, the new sex-determining allele increases in frequency on one \textbf{A} background and declines on the other, and invasion requires
+\begin{equation}\label{eq:neoYR}
+R \left[ 
+\frac{p^f_X w^m_a (1-\alpha^m)}{(\lambda_{mA}-1)\bar{w}_{H}^{m}} + 
+\frac{(1 - p^f_X) w^m_A \alpha^m \bar{w}_{H}^{m}}{(\lambda_{ma}-1)\bar{w}_{H}^{m}} \right] 
+\frac{w^m_{Aa}}{\bar{w}^m} < 1,
+\end{equation}
+
+\noindent
+for the neo-$Y$, and
+
+\noindent
+\begin{equation}\label{eq:neoWR}
+R \left[  
+\frac{(1 - \bar{p}^m) w^m_{a}}{(\lambda_{mA}-1)\bar{w}_{H}^{m}} + 
+\frac{\bar{p}^m w^m_{A}}{(\lambda_{ma}-1)\bar{w}_{H}^{m}} \right] 
+\frac{w^f_{Aa}}{\bar{w}^f} < 1
+\end{equation}
+
+\noindent
+for the neo-$W$.
+
+Equations \eqref{eq:neoYR} and \eqref{eq:neoWR} show that the new sex-determining allele is expected to invade for any recombination rate, $R$, when the net flow of double recombinants is from the less fit to the more fit \textbf{A} background (making the terms inside the square brackets in Equations \ref{eq:neoYR} and \ref{eq:neoWR} negative).
+%Assuming $g_A^* > 0$ and $g_a^* < 0$ without loss of generality, this is $-(1 - p^f_X) w_{m,A} g_a^* < p^f_X w_{m,a} g_A^*$.
+When the net flow of double recombinants is from the more fit to the less fit haplotype, the new sex-determining allele can still invade when the rate of recombination between it and the selected locus, $R$, is small enough.
 
@@
 %write in general form without weak selection
-A rare, dominant neo-$Y$ ($k=0$) or neo-$W$ ($k=1$) is always expected to invade an ancestral $XY$ system when the average growth rate of the mutant haplotypes ($Am$ and $am$) is positive, $(g_A + g_a)/2 > 0$.
+%A rare, dominant neo-$Y$ ($k=0$) or neo-$W$ ($k=1$) is always expected to invade an ancestral $XY$ system when the average growth rate of the mutant haplotypes ($Am$ and $am$) is positive, $(g_A + g_a)/2 > 0$.
 %($g_i = where $\lambda_i$ are the two eigenvalues when $R=r=0$; the \textbf{X} locus does not affect the dynamics).
-When the growth rates of the mutant haplotypes without recombination ($R=0$) are negative, $g_i^* < 0 \; \forall \; i \in \{A,a\}$, where $g_i < g_i^*$, the new sex-determining allele does not invade.
+%When the growth rates of the mutant haplotypes without recombination ($R=0$) are negative, $g_i^* < 0 \; \forall \; i \in \{A,a\}$, where $g_i < g_i^*$, the new sex-determining allele does not invade.
 
-Otherwise, the new sex-determining allele increases in frequency on one \textbf{A} background and declines on the other, and invasion requires
-\begin{equation}\label{eq:neoYR}
-R \left[ \frac{p^f_X w^m_a (1-\alpha^m)}{g_A^*} + \frac{(1 - p^f_X) w^m_A \alpha^m}{g_a^*} \right] w^m_{Aa} < \nu^m,
-\end{equation}
-for the neo-$Y$, and 
-\begin{equation}\label{eq:neoWR}
-R \left[  \frac{(1 - \bar{p}^m) w^m_{a}}{g_A^*} + \frac{\bar{p}^m w^m_{A}}{g_a^*} \right] w^f_{Aa} < \nu^f
-\end{equation}
-for the neo-$W$.
-Here $\bar{p}^m = (1-q) p^m_X+ q p^m_Y$ is the average frequency of $A$ in gametes produced by males, $w^i_{j}$ is the relative viability fitness of sex $i\in\{m,f\}$ depending on their haploid or diploid genotype at the \textbf{A} locus (with $j\in\{A,a,AA,Aa,aa\}$) and
-$\nu^i = 
-  p^f_X p^m_{\textbf{X}^i} w^m_{a} w^i_{AA} +
-  p^f_X (1-p^m_{\textbf{X}^i}) w^m_{a} w^i_{Aa} +
-  (1-p^f_X) p^m_{\textbf{X}^i} w^m_{a} w^i_{Aa} +
-  (1-p^f_X) (1-p^m_{\textbf{X}^i}) w^m_a w^i_{aa}$,
-with $\textbf{X}^m = Y$ and $\textbf{X}^f = X$, is the mean relative fitness of resident individuals of sex $i$.
+%Otherwise, the new sex-determining allele increases in frequency on one \textbf{A} background and declines on the other, and invasion requires
+%\begin{equation}\label{eq:neoYR}
+%R \left[ \frac{p^f_X w^m_a (1-\alpha^m)}{g_A^*} + \frac{(1 - p^f_X) w^m_A \alpha^m}{g_a^*} \right] w^m_{Aa} < \nu^m,
+%\end{equation}
+%for the neo-$Y$, and 
+%\begin{equation}\label{eq:neoWR}
+%R \left[  \frac{(1 - \bar{p}^m) w^m_{a}}{g_A^*} + \frac{\bar{p}^m w^m_{A}}{g_a^*} \right] w^f_{Aa} < \nu^f
+%\end{equation}
+%for the neo-$W$.
+%Here $\bar{p}^m = (1-q) p^m_X+ q p^m_Y$ is the average frequency of $A$ in gametes produced by males, $w^i_{j}$ is the relative viability fitness of sex $i\in\{m,f\}$ depending on their haploid or diploid genotype at the \textbf{A} locus (with $j\in\{A,a,AA,Aa,aa\}$) and
+%$\nu^i = 
+%  p^f_X p^m_{\textbf{X}^i} w^m_{a} w^i_{AA} +
+%  p^f_X (1-p^m_{\textbf{X}^i}) w^m_{a} w^i_{Aa} +
+%  (1-p^f_X) p^m_{\textbf{X}^i} w^m_{a} w^i_{Aa} +
+%  (1-p^f_X) (1-p^m_{\textbf{X}^i}) w^m_a w^i_{aa}$,
+%with $\textbf{X}^m = Y$ and $\textbf{X}^f = X$, is the mean relative fitness of resident individuals of sex $i$.
 %and $g_j^*$ is the growth rate of $X^m$ and $Ym$ haplotypes when on an $A$ ($j=A$)  or $a$ background ($j=a$).
-Although male meiotic drive does not explicitly appear in Equation \ref{eq:neoWR}, it does affect the average frequency of $A$ in gametes from males, $\bar{p}^m$, and thus can play a role in neo-W invasion.
+%Although male meiotic drive does not explicitly appear in Equation \ref{eq:neoWR}, it does affect the average frequency of $A$ in gametes from males, $\bar{p}^m$, and thus can play a role in neo-W invasion.
 
@@
 
+Fisherian sex ratio selection follows from the fact that, for a given locus, half of the genetic material is inherited from a male, and half from a female. 
+Thus, if the population sex ratio is biased towards females, the average per-individual contribution of genetic material to the next generation from males is greater than the contribution from females (and vice versa for male-biased sex ratios).
+Therefore, an autosomal mutation that increases investment in males will spread via the higher per-individual contributions made by males. 
+In other words, the success of a non-sex-determining, autosomal mutant depends, in equal parts, on the contributions made by both males and females to the next generation.
+However, the mutations we consider here, neo-sex-determining alleles, do not follow the same inheritance rules. 
+For example, invasion of a dominant neo-Y depends on the number of neo-Y alleles contributed to the next generation by males only (equation \ref{eq:charpoly_neoY} and Table \ref{tab:haplotype_growth}) because neo-Y alleles will only be found in males.
+
+Sex ratio biases caused by haploid competition or meiotic drive have been shown to exert selection on various modifiers, which evolve to restore an equal sex ratio.
+
 DRAFT (improve): In \citet{Ubeda:2015fx}, the new sex determining locus spreads because it arises in linkage with a locus that experiences drive.
@@
 {\color{red}{Despite the fact that sex ratio restorers can evolve, we find that sex chromosome turnover occurs regardless of sex ratio bias (Figure 3).}}
-
-Fisherian sex ratio selection follows from the fact that, for a given locus, half of the genetic material is inherited from a male, and half from a female. 
-Thus, if the population sex ratio is biased towards females, the average per-individual contribution of genetic material to the next generation from males is greater than the contribution from females (and vice versa for male-biased sex ratios).
-Therefore, an autosomal mutation that increases investment in males will spread via the higher per-individual contributions made by males. 
-In other words, the success of a non-sex-determining, autosomal mutant depends, in equal parts, on the contributions made by both males and females to the next generation.
-However, the mutations we consider here, neo-sex-determining alleles, do not follow the same inheritance rules. 
-For example, invasion of a dominant neo-Y depends on the number of neo-Y alleles contributed to the next generation by males only (equation \ref{eq:charpoly_neoY} and Table \ref{tab:haplotype_growth}) because neo-Y alleles will only be found in males.
-
-Sex ratio biases caused by haploid competition or meiotic drive have been shown to exert selection on various modifiers, which evolve to restore an equal sex ratio.
 

### 2017-01-20 LaTeX/Turnover.tex
Added to the results section, re-wrote invasion conditions with weak selection in a new form that shows invasion under more general conditions.

@@
   Genotype & Tranmission during meiosis in $Aa$ heterozygotes \\ [0.5ex] \hline
-  A & $\alpha^d=1/2+\alpha_{\Delta}^{d}$ \\
-  a & $(1-\alpha^d)=1/2-\alpha_{\Delta}^{d}$ \\
+  A & $\alpha^d=1/2+\alpha_{\Delta}^{d}/2$ \\
+  a & $(1-\alpha^d)=1/2-\alpha_{\Delta}^{d}/2$ \\
   \hline \hline
@@
 \begin{split}
-0&<-((1-h^f)s^f +(1-h^m) s^m + t^f +t^m + 2\alpha_{\Delta}^f+2\alpha_{\Delta}^m)\\
+0&<-((1-h^f)s^f +(1-h^m) s^m + t^f +t^m + \alpha_{\Delta}^f+\alpha_{\Delta}^m)\\
 %
-0&<(h^f s^f +h^m s^m + t^f +t^m + 2\alpha_{\Delta}^f+2\alpha_{\Delta}^m).
+0&<(h^f s^f +h^m s^m + t^f +t^m + \alpha_{\Delta}^f+\alpha_{\Delta}^m).
 \end{split}
 \end{equation}
+
+\noindent
+which indicates that a polymorphism is maintained under various selective regimes. 
+In particular special cases, e.g., no sex-differences in selection or meiotic drive ($s^m=s^f$, $h^m=h^f$, and $\alpha^m=\alpha^f=1/2$), equilibrium allele frequency and stability can be calculated analytically without assuming weak selection.
+%Here, we focus on the case where selection is weak relative to recombination so that we make fewer assumptions about the form of selection.
 
@@
 \begin{equation}
-\bar{p}=\frac{h^f s^f + h^m s^m +t^f+t^m+2\alpha_{\Delta}^f+2\alpha_{\Delta}^m}
+\bar{p}=\frac{h^f s^f + h^m s^m +t^f+t^m+\alpha_{\Delta}^f+\alpha_{\Delta}^m}
 {(2h^f-1)s^f+(2h^m-1)s^m}
@@
 \begin{split}
-\hat{p}^m_X-\hat{p}^f_X&=V_{A}\big{(}C^m - C^f \big{)}
+\hat{p}^m_X-\hat{p}^f_X&=V_{A}\big{(}D^m - D^f +\alpha_{\Delta}^m-\alpha_{\Delta}^f \big{)}
 +O(\epsilon^2)\\
 %
-\hat{p}^m_Y-\hat{p}^f_X&=V_{A}\big{(}C^m - C^f+(1-2r)(t^m-t^f)\big{)}/2r
+\hat{p}^m_Y-\hat{p}^f_X&=V_{A}\big{(}D^m - D^f+\alpha_{\Delta}^m-\alpha_{\Delta}^f+(1-2r)(t^m-t^f)\big{)}/2r
 +O(\epsilon^2)\\
 %
-\hat{p}^m_Y-\hat{p}^m_X&=V_{A}\big{(}C^m - C^f+(t^m-t^f)\big{)}(1-2r)/2r
+\hat{p}^m_Y-\hat{p}^m_X&=V_{A}\big{(}D^m - D^f+\alpha_{\Delta}^m-\alpha_{\Delta}^f+t^m-t^f\big{)}(1-2r)/2r
 +O(\epsilon^2)
@@
 \noindent
-where $V_{A}=\bar{p}(1-\bar{p})$ is the variance in the frequency of $A$ and $C^d=(\bar{p}+(1-2\bar{p})h^d) s^d +2\alpha_{\Delta}^d$. 
-The frequency of Y among male gametes is proportional to the difference in $A$ allele frequency on X- and Y-bearing male gametes, $q=1/2+\alpha_{\Delta}^m(\hat{p}^m_Y-\hat{p}^m_X)+O(\epsilon^3)$.
+where $V_{A}=\bar{p}(1-\bar{p})$ is the variance in the frequency of $A$ and $D^d=\big{(} \bar{p}s^d+(1-\bar{p})h^d s^d\big{)} -\big{(} \bar{p}h^d s^d+(1-\bar{p}) \big{)}$ corresponds to the difference in fitness between $A$ and $a$ alleles in diploids of sex $d$ ($\bar{p}$ is the leading-order probability of mating with an $A$-bearing gamete from the opposite sex).
+The frequency of Y among male gametes is depends upon the difference in $A$ allele frequency on X- and Y-bearing male gametes and the strength of meiotic drive in favour of the $A$ allele, $q=1/2+\alpha_{\Delta}^m(\hat{p}^m_Y-\hat{p}^m_X)/2+O(\epsilon^3)$.
 Without haploid competition or drive ($\alpha_{\Delta}^d=t^d=0$), these results reduce to those of \citet{vanDoorn:2007eu}.
@@
 Furthermore, if the $m$ allele is fully dominant over the ancestral sex-determining system, phenotypes are not affected by the genotype at the ancestral sex-determining region (\textbf{X} locus). 
-Therefore, the invasion of rare mutant neo-Y or neo-W chromosomes can be described by a simpler, two equation system, the largest eigenvalue of which solves the characteristic polynomial
+Therefore, the invasion of rare mutant neo-Y or neo-W chromosomes can be simplified and given by the largest eigenvalue that solves the quadratic characteristic polynomial
 
@@
 If the \textbf{A} locus is initially linked to the ancestral sex-determining locus, \textbf{X}, (i.e., $r<1/2$) the frequency of the $A$ allele among X- and Y-bearing sperm can differ (equation \ref{eq:freq_diffs}).
-Thus, eggs with and without a neo-W differ in the frequency of alleles they obtain from mating with male gametes.
-
-Previous research suggests, when the ancestral sex-determining locus is linked to a locus that experiences haploid selection (e.g., meiotic drive), a new, unlinked sex-determining locus can invade in order to restore equal sex ratios \citep{Kozielska:2010vm}.
-Our model provides a good opportunity to determine whether Fisherian sex ratio selection provides a useful explanation for the evolution of new sex-determining loci in other contexts. 
-Consider, for example, the case where the \textbf{A} locus is linked to the ancestral-SDR ($r<1/2$) and experiences meiotic drive in males only (e.g., during spermatogenesis but not during oogenesis, $\alpha^m \neq 1/2$, $\alpha^f=1/2$).
-We will also disregard haploid competition ($t^f=t^m=0$) such that zygotic sex ratios can only be biased by meiotic drive in males. 
-In this case, the zygotic sex ratio can be initially biased only if the ancestral sex-determining system is XY. 
-If the ancestral sex-determining system is ZW, the zygotic sex ratio will be 1:1 because diploid sex is determined by the proportion of Z-bearing versus W-bearing eggs (and meiosis in females is fair).
-Thus, if the zygotic sex ratio is crucial to the evolution of new genetic sex-determining systems, invasion into ZW and XY systems will be distinct. 
-However, we find that invasion of new homogametic systems (XY to XY, or ZW to ZW) and heterogametic systems (XY to ZW or ZY to XY) occur under the same conditions. 
-That is, $\lambda_{XY,XY}=\lambda_{ZW,ZW}$ and $\lambda_{XY,ZW}=\lambda_{ZW,XY}$, where $\lambda_{i,j}$ indicates the growth rate of a new mutant giving sex-determining system $j$ in a population in which sex is ancestrally determined by system $i$.
+Thus, eggs with and without a neo-W differ in the frequency of $A$ alleles they obtain from mating with male gametes.
 
@@
 \noindent
+\textcolor{red}{FIX THESE EQUATIONS...}
 for the neo-$W$.
+Equations \eqref{eq:neoYR} and \eqref{eq:neoWR} show that the new sex-determining allele, $m$, is expected to invade for any recombination rate, $R$, when the net flow of recombinants is from the less fit (smaller $\lambda_{mi}$) to the more fit \textbf{A} background (making the terms inside the square brackets in Equations \ref{eq:neoYR} and \ref{eq:neoWR} negative).
+\textcolor{red}{Q: is it definitely possible to have negative square brackets for a equilibria maintained by selection?}
+%Assuming $g_A^* > 0$ and $g_a^* < 0$ without loss of generality, this is $-(1 - p^f_X) w_{m,A} g_a^* < p^f_X w_{m,a} g_A^*$.
+When the net flow of recombinants is from the more fit to the less fit haplotype, the new sex-determining allele can still invade when the rate of recombination between it and the selected locus, $R$, is small enough.
+\textcolor{red}{Q:Is it the case that sometimes the square brackets are positive and invasion occurs for $R=1/2$?
+In which case it might be better to have slightly different phrasing here.}
 
-Equations \eqref{eq:neoYR} and \eqref{eq:neoWR} show that the new sex-determining allele is expected to invade for any recombination rate, $R$, when the net flow of double recombinants is from the less fit to the more fit \textbf{A} background (making the terms inside the square brackets in Equations \ref{eq:neoYR} and \ref{eq:neoWR} negative).
-%Assuming $g_A^* > 0$ and $g_a^* < 0$ without loss of generality, this is $-(1 - p^f_X) w_{m,A} g_a^* < p^f_X w_{m,a} g_A^*$.
-When the net flow of double recombinants is from the more fit to the less fit haplotype, the new sex-determining allele can still invade when the rate of recombination between it and the selected locus, $R$, is small enough.
+%weak selection
+We can explicitly determine the conditions under which invasion occurs if we assume that the $A$ allele reaches an equilibrium frequency under the ancestral sex-determination system before the neo-sex-determination system ($m$) arises.
+The equilibrium  frequency of $A$ on different ancestral backgrounds ($\hat{p}^m_Y$, $\hat{p}^m_X$, and $\hat{p}^f_X$) is given by equations \eqref{eq:pAve} and \eqref{eq:freq_diffs} where we assume selection and meiotic drive are weak relative to recombination ($s^k$, $t^k$, $\alpha_{\Delta}^k$ of order $\epsilon$).
+Under weak selection, we denote the leading eigenvalue describing the invasion of a neo-Y ($k=0$) and a neo-W ($k=0$) into an ancestrally XY system by $\lambda_{Y',XY}$ and $\lambda_{W',XY}$, respectively, which are given by
+
+\begin{equation}
+\lambda_{Y',XY} =1+ \frac{V_{A} \left( r-R \right)(S_{A})^2 }{r R}+O\left(\epsilon^3 \right) 
+\label{eq:lambda_neoY}
+\end{equation}
+
+\noindent 
+and
+
+\begin{equation}
+\lambda_{W',XY} =\lambda_{Y',XY}+\left(2\alpha_{\Delta}^m-2\alpha_{\Delta}^f+t^m-t^f \right) \left( \hat{p}^m_Y-\hat{p}^m_X \right)
++O\left(\epsilon^3 \right) \\
+\label{eq:lambda_neoW}
+\end{equation}
+
+\noindent
+where $V_{A}=\bar{p}(1-\bar{p})$ is the variance in the frequency of $A$ and $S_{A}=(D^m +\alpha_{\Delta}^m+t^m) - (D^f+\alpha_{\Delta}^f+t^f)$ is the difference in fitness in males versus females for the $A$ allele against the $a$ allele across diploid selection, haploid competition, and meiosis.
+
+\textcolor{red}{It may seem counterintuitive that, if the $A$ allele is more common on the ancestral-Y than the ancestral-X, and only favoured during haploid selection in males}
+
+\textcolor{red}{although our predictions also perform well when recombination is small, see figure \ref{fig:WinvasionLowR}.
+We would have to add a line showing what invasion fitness the weak selection approximation would give and add dots to this figure (dots that are currently connected by a line), as in (vD\&K, 2010) }
+
+%Sex ratios
+\textcolor{red}{Add figure w/ drive that explains this.}
+Previous research suggests, when the ancestral sex-determining locus is linked to a locus that experiences haploid selection (e.g., meiotic drive), a new, unlinked sex-determining locus can invade in order to restore equal sex ratios \citep{Kozielska:2010vm}.
+Our model provides a good opportunity to determine whether Fisherian sex ratio selection provides a useful explanation for the evolution of new sex-determining loci in other contexts. 
+Consider, for example, the case where the \textbf{A} locus is linked to the ancestral-SDR ($r<1/2$) and experiences meiotic drive in males only (e.g., during spermatogenesis but not during oogenesis, $\alpha^m \neq 1/2$, $\alpha^f=1/2$).
+We will also disregard haploid competition ($t^f=t^m=0$) such that zygotic sex ratios can only be biased by meiotic drive in males. 
+In this case, the zygotic sex ratio can be initially biased only if the ancestral sex-determining system is XY. 
+If the ancestral sex-determining system is ZW, the zygotic sex ratio will be 1:1 because diploid sex is determined by the proportion of Z-bearing versus W-bearing eggs (and meiosis in females is fair).
+Thus, if the zygotic sex ratio is crucial to the evolution of new genetic sex-determining systems, invasion into ZW and XY systems will be distinct. 
+However, we find that invasion of new homogametic systems (XY to XY, or ZW to ZW) and heterogametic systems (XY to ZW or ZY to XY) occur under the same conditions. 
+That is, $\lambda_{Y',XY}=\lambda_{W',ZW}$ and $\lambda_{Y',ZW}=\lambda_{W',XY}$.
 
@@
 
-\subsubsection*{Neo-$Y$ and neo-$W$}
+%\subsubsection*{Neo-$Y$ and neo-$W$}
 
@@
 
-Equations \eqref{eq:neoYR} and \eqref{eq:neoWR} show that the new sex-determining allele is expected to invade for any recombination rate, $R$, when the net flow of double recombinants is from the less fit to the more fit \textbf{A} background (making the terms inside the square brackets in Equations \ref{eq:neoYR} and \ref{eq:neoWR} negative).
+%Equations \eqref{eq:neoYR} and \eqref{eq:neoWR} show that the new sex-determining allele is expected to invade for any recombination rate, $R$, when the net flow of double recombinants is from the less fit to the more fit \textbf{A} background (making the terms inside the square brackets in Equations \ref{eq:neoYR} and \ref{eq:neoWR} negative).
 %Assuming $g_A^* > 0$ and $g_a^* < 0$ without loss of generality, this is $-(1 - p^f_X) w_{m,A} g_a^* < p^f_X w_{m,a} g_A^*$.
-When the net flow of double recombinants is from the more fit to the less fit haplotype, the new sex-determining allele can still invade when the rate of recombination between it and the selected locus, $R$, is small enough.
+%When the net flow of double recombinants is from the more fit to the less fit haplotype, the new sex-determining allele can still invade when the rate of recombination between it and the selected locus, $R$, is small enough.
 
 %weak selection
-Assuming weak selection and meiotic drive, we can explicitly solve for the invasion fitness of the new sex-determining allele, $m$, into the ancestral $XY$ system, giving
-\begin{equation}
-\lambda_{m,XY} \approx 1 + V_A S_A C_m,
-\end{equation}
-where $V_A = p_A(1-p_A)$ is the variance at the \textbf{A} locus.
-We will consider haploid selection and meiotic drive separately.
-With haploid selection and no drive we have $S_A = s^f (t^m)^2 / \left[ r R \left( s^f + s^m \right)^2 \right]$, where $s^f$ and $s^m$ are the respective selection coefficients for $A$ in diploid females and males, $t^m$ is the selection coefficient for $A$ in gametes from males, and we've assumed equal dominance coefficients in the two sexes ($h^f = h^m$).
-With drive and no haploid selection one replaces $t^m$ with $\alpha^m-1/2$.
+%Assuming weak selection and meiotic drive, we can explicitly solve for the invasion fitness of the new sex-determining allele, $m$, into the ancestral $XY$ system, giving
+%\begin{equation}
+%\lambda_{m,XY} \approx 1 + V_A S_A C_m,
+%\end{equation}
+%where $V_A = p_A(1-p_A)$ is the variance at the \textbf{A} locus.
+%We will consider haploid selection and meiotic drive separately.
+%With haploid selection and no drive we have $S_A = s^f (t^m)^2 / \left[ r R \left( s^f + s^m \right)^2 \right]$, where $s^f$ and $s^m$ are the respective selection coefficients for $A$ in diploid females and males, $t^m$ is the selection coefficient for $A$ in gametes from males, and we've assumed equal dominance coefficients in the two sexes ($h^f = h^m$).
+%With drive and no haploid selection one replaces $t^m$ with $\alpha^m-1/2$.
 
-For the neo-$Y$ we have $C_Y = (r - R)s^f $ with haploid selection and $C_Y = 4(r - R)s^f $ with drive.
-The neo-$Y$ can therefore invade whenever it is in tighter linkage with the selected locus than the ancestral sex-determining locus, $r>R$, provided locus \textbf{A} is polymorphic ($V_A>0$), there is diploid selection in females ($s^f\neq0$), and there is either haploid selection between gametes from males ($t^m\neq0$) or meiotic drive in males ($\alpha^m\neq1/2$).
-This is similar to the conclusion reached concerning sexual-antagonistic selection in \cite{vanDoorn:2007eu} and reduces to their weak-linkage results exactly when we do not assume equal dominance coefficients in the two sexes, there is no haploid selection or meiotic drive, and there is free recombination between locus \textbf{A} and one of the sex-determining regions.
+%For the neo-$Y$ we have $C_Y = (r - R)s^f $ with haploid selection and $C_Y = 4(r - R)s^f $ with drive.
+%The neo-$Y$ can therefore invade whenever it is in tighter linkage with the selected locus than the ancestral sex-determining locus, $r>R$, provided locus \textbf{A} is polymorphic ($V_A>0$), there is diploid selection in females ($s^f\neq0$), and there is either haploid selection between gametes from males ($t^m\neq0$) or meiotic drive in males ($\alpha^m\neq1/2$).
+%This is similar to the conclusion reached concerning sexual-antagonistic selection in \cite{vanDoorn:2007eu} and reduces to their weak-linkage results exactly when we do not assume equal dominance coefficients in the two sexes, there is no haploid selection or meiotic drive, and there is free recombination between locus \textbf{A} and one of the sex-determining regions.
 
-For the neo-$W$ we have $C_W = [(2r(1-R)-R) s^f + (1-2r)R s^m]/2$ with haploid selection and $C_W = 4[r(1-2R) s^f + (1-2r)R s^m]/2$ with drive.
-In this case, even when the novel sex-determining locus is in looser linkage with the selected locus than the ancestral sex-determining locus is, $r<R$, a neo-$W$ can invade (Figures \ref{fig:WinvasionLowR} -- \ref{fig:InvasionVsCentiMorgans}).
-This does not occur in models with only sexually-antagonistic selection \citep{vanDoorn:2010hu}.
-For example, with $R=1/2$ the neo-$W$ invades if there is any linkage between the ancestral sex-determining and selected loci ($r<1/2$), there is selection among gametes in males ($t^m\neq0$), and there is selection for or against $A$ in both males and females ($s^m s^f >0$) that is stronger in males than in females ($|s^m| > |s^f|$).
-With meiotic drive and $R=1/2$, all that is required for neo-W invasion is $r<1/2$ and $s^m s^f >0$.
-Our results reduce to the weak-linkage results of \cite[][Equation 3]{vanDoorn:2010hu} when we do not assume equal dominance coefficients in the two sexes and there is no haploid selection or meiotic drive.
+%For the neo-$W$ we have $C_W = [(2r(1-R)-R) s^f + (1-2r)R s^m]/2$ with haploid selection and $C_W = 4[r(1-2R) s^f + (1-2r)R s^m]/2$ with drive.
+%In this case, even when the novel sex-determining locus is in looser linkage with the selected locus than the ancestral sex-determining locus is, $r<R$, a neo-$W$ can invade (Figures \ref{fig:WinvasionLowR} -- \ref{fig:InvasionVsCentiMorgans}).
+%This does not occur in models with only sexually-antagonistic selection \citep{vanDoorn:2010hu}.
+%For example, with $R=1/2$ the neo-$W$ invades if there is any linkage between the ancestral sex-determining and selected loci ($r<1/2$), there is selection among gametes in males ($t^m\neq0$), and there is selection for or against $A$ in both males and females ($s^m s^f >0$) that is stronger in males than in females ($|s^m| > |s^f|$).
+%With meiotic drive and $R=1/2$, all that is required for neo-W invasion is $r<1/2$ and $s^m s^f >0$.
+%Our results reduce to the weak-linkage results of \cite[][Equation 3]{vanDoorn:2010hu} when we do not assume equal dominance coefficients in the two sexes and there is no haploid selection or meiotic drive.
 
@@
 %V_A \frac{r}{1-2r}  \frac{s_{f} \left( s^m - 3 s^f\right) }{8 \left( s_{f} + s_{m} \right)^2} t_{m}^2.
+\label{eq:lambda_ESD}
 \end{equation}
@@
 preventing associations from building up between allele $A$ and sex.
+
+Depends 50\% on its fitness relative to non-mutant males and 50\% on its fitness relative to non-mutant females.
 
@@
 
-Fisherian sex ratio selection follows from the fact that, for a given locus, half of the genetic material is inherited from a male, and half from a female. 
+Fisherian sex ratio selection follows from the fact that, for an autosomal locus, half of the genetic material is inherited from a male, and half from a female. 
 Thus, if the population sex ratio is biased towards females, the average per-individual contribution of genetic material to the next generation from males is greater than the contribution from females (and vice versa for male-biased sex ratios).
-Therefore, an autosomal mutation that increases investment in males will spread via the higher per-individual contributions made by males. 
-In other words, the success of a non-sex-determining, autosomal mutant depends, in equal parts, on the contributions made by both males and females to the next generation.
-However, the mutations we consider here, neo-sex-determining alleles, do not follow the same inheritance rules. 
-For example, invasion of a dominant neo-Y depends on the number of neo-Y alleles contributed to the next generation by males only (equation \ref{eq:charpoly_neoY} and Table \ref{tab:haplotype_growth}) because neo-Y alleles will only be found in males.
-
-Sex ratio biases caused by haploid competition or meiotic drive have been shown to exert selection on various modifiers, which evolve to restore an equal sex ratio.
+Therefore, a mutant that increases investment in males will spread via the higher per-individual contributions made by males. 
+That is, under Fisherian sex ratio selection, the success of a mutant relative to the non-mutant depends, in equal parts, on the contributions made by males and females to the next generation. 
+An implicit assumption of Fisherian sex ratio selection is that the mutant allele is autosomal and has the same inheritance pattern as the non-mutant allele. 
+The mutations we consider here, neo-sex-determining alleles, break this assumption. 
+For example, the success of neo-Y mutations depends only on the number of alleles contributed by males (equation \ref{eq:charpoly_neoY} and Table \ref{tab:haplotype_growth}). 
+Even mutants that are equally likely to be found in males or females, such as an environmental sex determination mutation (equation \ref{eq:lambda_ESD}), are not strictly autosomal if they determine sex.
+Thus, despite the fact that sex ratio biases caused by haploid competition or meiotic drive have been shown to exert selection on various modifiers \citep{Stalker:1961th,Smith:1975ft,Frank:1989vl,Hough:2013uo,Ubeda:2015fx, Otto:2015va}, we do not find evidence that Fisherian sex ratio selection acting upon neo-sex-determination systems (e.g., see figure \textcolor{red}{REF}).
 
@@
 Finally, they show that autosomal 'restorers' that negate the effects of meiotic drive can invade and restore an equal sex ratio.
-OTHER RESTORERS.
-\textcolor{blue}{Indeed, alleles that negate the effect of sex-linked meiotic drivers and restore equal sex ratios have been identified \citep{Stalker:1961th,Smith:1975ft}. 
-A similar process occurs with cytoplasmic male sterility alleles (that cause biased sex ratios) and nuclear `restorer' genotypes \citep{Frank:1989vl}. 
-}
-When sex ratio bias occurs due to haploid selection, a natural class of sex ratio `restorers' exist because haploid selection often occurs in a context that is determined by the diploid parents. 
-For example, the intensity of pollen competition can be manipulated by altering style length \citep{Travers:2001,Lankinen:2001gc,Ruane:2009vt}, delaying stigma receptivity \citep{Galen:1986wq,Lankinen:2011if} and/or delaying pollen tube growth in the pistil \citep{Herrero:2003jf}.
-Where the X and Y have fitness differences, \citet{Hough:2013uo} and \citet{Otto:2015va} demonstrated that mothers should generally evolve to balance sex ratios by reducing the intensity of haploid competition.
 
-{\color{red}{Despite the fact that sex ratio restorers can evolve, we find that sex chromosome turnover occurs regardless of sex ratio bias (Figure 3).}}
-
-{\color{blue}
-FROM THESIS:
-However, reducing competition among haploids also reduces the potential for harmful deleterious mutations to be purged. 
-When deleterious mutations are included, the optimal intensity of haploid selection can reflect a balance between maximizing offspring fitness and equalizing sex ratios.
-
-As part of a collaborative project \citep{Otto:2015va}, I considered the evolution of the haploid `selective arena' in cases where the X chromosome harbours a polymorphism that affects haploid fitness.
-Mothers again primarily evolve to restore equal sex ratios.
-However, modifying haploid selection also affects the X-linked genotypes that are inherited by offspring. 
-Specifically, increasing the intensity of haploid selection increases the proportion of daughters (all progeny of X-bearing sperm/pollen are female) that inherit the allele with high haploid fitness. 
-If this allele has high fitness in daughters, mothers can be selected to increase the intensity of haploid selection; otherwise, decreased selection among haploids is favoured.
-Thus, because altering haploid selection intensity affects the alleles that are inherited by daughters, mothers can favour slightly biased sex ratios. 
-In addition, I found that stronger sex ratio biases can be favoured by paternal manipulations of the haploid `selective arena' because fathers are strongly selected to maximize their own siring success (above selection to equalize the sex ratio).
-
-}
+We only consider selection at the \textbf{A} locus, the sex-determining regions do not experience direct selection except via their associations with sex and \textbf{A} locus alleles. 
+However, in some cases, there may be significant degeneration around the sex-limited allele (Y or W) in the ancestral sex determining region.
+That is, recessive deleterious mutations and/or deletions may fix around the Y or W allele \citealt{Rice:1996ke,Charlesworth:2000cc,Bachtrog:2006ed,Marais:2008hm}).
+Degenerated Y could prevent fixation, this was studied by vD\&K 2010, which is why we didn't do it. 
+They note that YY lethality can prevent neo-W (and Y) fixing but that even very small amounts of recombination between X and Y can complete the process.
 
@@
 ``Polymorphism for sex-determining genes within or among populations has been reported in many species including houseflies, midges, woodlice, platyfish, cichlid fish, and frogs (Gordon, 1944; Kallman, 1970; Thomp-son, 1971; Macdonald, 1978; Bull, 1983; Rigaud et al., 1997; Caubet et al., 2000; Lande et al., 2001; Ogataet al., 2003; Lee et al., 2004; Mank et al., 2006).''
+
+We caution that our model of meiotic drive is very simple, involving a single locus with two alleles. 
+Many meiotic drive systems involve an interaction with another locus at which alleles may `suppress' the action of meiotic drive. 
+Furthermore, in some cases, a driving allele may act by killing any gametes that carry a `target' allele at another locus, in which case the total number of gametes produced will be reduced (here, we assume total gamete number is not affected by drive).
+
+Mix pollen competition and sex-ratio affects in here?
+Kokko paper addresses some of these issues, but not related to sex-determination. 
+These feedbacks between population densities and meiotic drive or haploid competition for different sexual/mating systems deserve further attention.
+
+Here, we have not considered any population size dynamics
 

### 2017-01-21 LaTeX/Turnover.tex
minor grammar on first reading

@@
 \title{Gametic Selection, Sex Ratio Bias, and Transitions Between Sex Determination Systems}
-\author{Michael F Scott$*^1$ and Matthew M Osmond$*^2$, and Sarah P Otto$^2$}
+\author{Michael F Scott$^{*1}$ and Matthew M Osmond$^{*2}$, and Sarah P Otto$^2$}
 \date{}
@@
 \begin{abstract}
-Sex determination systems are remarkably dynamic; many studied taxa display transitions of sex-determining genes between chromosomes or the evolution of new sex-determining systems. 
+Sex determination systems are remarkably dynamic; many studied taxa display transitions between sex-determining genes across chromosomes or the evolution of new sex-determining systems. 
 %Predominant theories in which new sex-determining systems are favoured by selection involve sex ratio selection or fitness differences between sexes (e.g., sexually antagonistic selection). 
@@
 haploid gametic selection, e.g., pollen or sperm competition.
-Haploid selected loci experience a form of sex-specific selection (because gametic competition occurs predominantly among haploids produced by males) and can cause sex ratios at birth to become biased (because sex ratios are determined by the fertilization success of X- versus Y-bearing pollen/sperm).
+Haploid selected loci experience a form of sex-specific selection when gametic competition occurs predominantly among haploids produced by one sex (e.g.,  pollen competition).
+This can cause sex ratios at birth to become biased as sex ratios are determined by the fertilization success of X- versus Y-bearing pollen/sperm (or Z- versus W-bearing eggs). 
 %We find that the evolution of sex determination systems where mothers determine sex at birth (e.g., environmental sex determination where sex is determined at birth) is influenced by classic Fisherian sex ratio selection.
@@
 %However, notably, we find that the spread of new genetic sex determination systems is not affected by sex ratio biases that are caused by gametic selection because sex ratios become biased after parental provisioning has occurred (even if pollen/sperm competition occurs within the mother).
-Notably, we find that the spread of new genetic sex determination systems is not affected by sex ratio biases that are caused by gametic selection because sex ratios become biased after parental provisioning has occurred (even if pollen/sperm competition occurs within the mother).
+Notably, we find that the spread of new genetic sex determination systems is not affected by sex ratio biases that are caused by gametic selection because sex ratios become biased after parental provisioning has occurred, even if pollen/sperm competition occurs within the mother (e.g., pollen competition in stigma).
 In addition, we find that linkage of an ancestral sex chromosome to a locus under haploid selection can favour transitions between male and female heterogamety (e.g., XY to ZW), which is not the case for any forms of diploid sex specific selection (e.g., sexually antagonistic selection).
@@
 A smaller (but non-negligible) proportion of genes are thought to be expressed and selected in animal sperm, although precise estimates are uncertain \citep{Zheng:2001fi,JOSEPH:2004haa,Vibranovski:2010et}.
-\textcolor{red}{add something about meiotic drive here?}
+%\textcolor{red}{add something about meiotic drive here?}
 
@@
 %genetic system
-We consider the transition between an ancestral and novel sex determination systems using a three locus model.
+We consider the transition between ancestral and novel sex determination systems using a three locus model.
 Locus \textbf{X} is the ancestral sex-determining region, with alleles $X$ and $Y$ (or $Z$ and $W$).
@@
 In the resident population (allele $M$ fixed), we follow the frequency of $A$ in female gametes (eggs) from an XX female, $p^f_X$, and in X-bearing, $p^m_X$, and Y-bearing, $p^m_Y$, male gametes (sperm).
-We also track the total frequency of Y-bearing male gametes (sperm), $q$, which may deviate from $1/2$ due to meiotic drive in males.
+We also track the total frequency of Y-bearing male gametes, $q$, which may deviate from $1/2$ due to meiotic drive in males.
 
 Various forms of selection can maintain a polymorphism at the \textbf{A} locus, including sexually antagonistic selection, overdominance and conflicts between diploid selection and selection upon haploid genotypes \citep[ploidally antagonistic selection,][]{Immler:2012tl} or a combination of these selective regimes.
+In particular special cases, e.g., no sex-differences in selection or meiotic drive ($s^m=s^f$, $h^m=h^f$, and $\alpha^m=\alpha^f=1/2$), equilibrium allele frequency and stability can be calculated analytically without assuming weak selection.
 Here, we assume that selection and meiotic drive are weak relative to recombination ($s^k$, $t^k$, $\alpha_{\Delta}^k$ of order $\epsilon$). 
@@
 which indicates that a polymorphism is maintained under various selective regimes. 
-In particular special cases, e.g., no sex-differences in selection or meiotic drive ($s^m=s^f$, $h^m=h^f$, and $\alpha^m=\alpha^f=1/2$), equilibrium allele frequency and stability can be calculated analytically without assuming weak selection.
+%In particular special cases, e.g., no sex-differences in selection or meiotic drive ($s^m=s^f$, $h^m=h^f$, and $\alpha^m=\alpha^f=1/2$), equilibrium allele frequency and stability can be calculated analytically without assuming weak selection.
 %Here, we focus on the case where selection is weak relative to recombination so that we make fewer assumptions about the form of selection.
@@
 where $V_{A}=\bar{p}(1-\bar{p})$ is the variance in the frequency of $A$ and $D^d=\big{(} \bar{p}s^d+(1-\bar{p})h^d s^d\big{)} -\big{(} \bar{p}h^d s^d+(1-\bar{p}) \big{)}$ corresponds to the difference in fitness between $A$ and $a$ alleles in diploids of sex $d$ ($\bar{p}$ is the leading-order probability of mating with an $A$-bearing gamete from the opposite sex).
-The frequency of Y among male gametes is depends upon the difference in $A$ allele frequency on X- and Y-bearing male gametes and the strength of meiotic drive in favour of the $A$ allele, $q=1/2+\alpha_{\Delta}^m(\hat{p}^m_Y-\hat{p}^m_X)/2+O(\epsilon^3)$.
+The frequency of Y among male gametes depends upon the difference in $A$ allele frequency on X- and Y-bearing male gametes and the strength of meiotic drive in favour of the $A$ allele, $q=1/2+\alpha_{\Delta}^m(\hat{p}^m_Y-\hat{p}^m_X)/2+O(\epsilon^3)$.
 Without haploid competition or drive ($\alpha_{\Delta}^d=t^d=0$), these results reduce to those of \citet{vanDoorn:2007eu}.

### 2017-01-23 LaTeX/Turnover.tex
Added new figures

--- 2017-01-20 LaTeX/Turnover.tex
@@
 %However, notably, we find that the spread of new genetic sex determination systems is not affected by sex ratio biases that are caused by gametic selection because sex ratios become biased after parental provisioning has occurred (even if pollen/sperm competition occurs within the mother).
-Notably, we find that the spread of new genetic sex determination systems is not affected by sex ratio biases that are caused by gametic selection because sex ratios become biased after parental provisioning has occurred (even if pollen/sperm competition occurs within the mother).
+Notably, we find that the spread of new genetic sex determination systems is not affected by sex ratio biases that are caused by haploid competition or meiotic drive. 
 In addition, we find that linkage of an ancestral sex chromosome to a locus under haploid selection can favour transitions between male and female heterogamety (e.g., XY to ZW), which is not the case for any forms of diploid sex specific selection (e.g., sexually antagonistic selection).
@@
 which indicates that a polymorphism is maintained under various selective regimes. 
-In particular special cases, e.g., no sex-differences in selection or meiotic drive ($s^m=s^f$, $h^m=h^f$, and $\alpha^m=\alpha^f=1/2$), equilibrium allele frequency and stability can be calculated analytically without assuming weak selection.
-%Here, we focus on the case where selection is weak relative to recombination so that we make fewer assumptions about the form of selection.
+In particular special cases, e.g., no sex-differences in selection or meiotic drive ($s^m=s^f$, $h^m=h^f$, and $\alpha^m=\alpha^f=1/2$), the equilibrium allele frequency and stability can be calculated analytically without assuming weak selection.
+However, here, we focus on weak selection and make fewer fitness assumptions.
 
@@
 where $V_{A}=\bar{p}(1-\bar{p})$ is the variance in the frequency of $A$ and $D^d=\big{(} \bar{p}s^d+(1-\bar{p})h^d s^d\big{)} -\big{(} \bar{p}h^d s^d+(1-\bar{p}) \big{)}$ corresponds to the difference in fitness between $A$ and $a$ alleles in diploids of sex $d$ ($\bar{p}$ is the leading-order probability of mating with an $A$-bearing gamete from the opposite sex).
-The frequency of Y among male gametes is depends upon the difference in $A$ allele frequency on X- and Y-bearing male gametes and the strength of meiotic drive in favour of the $A$ allele, $q=1/2+\alpha_{\Delta}^m(\hat{p}^m_Y-\hat{p}^m_X)/2+O(\epsilon^3)$.
+The frequency of Y among male gametes depends upon the difference in $A$ allele frequency on X- and Y-bearing male gametes and the strength of meiotic drive in favour of the $A$ allele in males, $q=1/2+\alpha_{\Delta}^m(\hat{p}^m_Y-\hat{p}^m_X)/2+O(\epsilon^3)$.
 Without haploid competition or drive ($\alpha_{\Delta}^d=t^d=0$), these results reduce to those of \citet{vanDoorn:2007eu}.
@@
 %Sex ratios
-\textcolor{red}{Add figure w/ drive that explains this.}
 Previous research suggests, when the ancestral sex-determining locus is linked to a locus that experiences haploid selection (e.g., meiotic drive), a new, unlinked sex-determining locus can invade in order to restore equal sex ratios \citep{Kozielska:2010vm}.
@@
 That is, $\lambda_{Y',XY}=\lambda_{W',ZW}$ and $\lambda_{Y',ZW}=\lambda_{W',XY}$. 
+\textcolor{red}{Add figure w/ drive, showing sex ratio to explain this.}
 
@@
 \section*{Figures}
+\newpage
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Heterogametic transitions with/without sex ratio change
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{Combination_Turnover}\\
+\caption{
+\textcolor{red}{Could add titles to the columns/rows: neo-W for row 1, neo-Y for row 3, $r=0.5$, $R=0.05$ for column 1 and $r=0.05$, $R=0.5$ for column 2.
+\& possibly adjust padding (too much whitespace?).
+Matt - could you uncomment the line legends in the Mathematica file (function not included in my Mathematica version).}
+}
+\label{fig:Combination_Turnover}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Chromosomal Positions
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{Combination_Centimorgan}\\
+\caption{
+\textcolor{red}{A sexual antagonism (no haploid selection), B drive (no haploid competition), equal selection in sexes ($s^f=s^m$), C \& D Pollen/Sperm competition only (no drive).
+C allele favoured in pollen/sperm competition selected against less in males ($t<0$, $s^f, s^m >0$, $s^f<s^f$).
+D allele favoured in pollen/sperm competition selected against more in males than females ($t<0$, $s^f, s^m >0$, $s^f>s^f$).
+I suspect that panel C has a region where no equilibrium is maintained (CHECK!
+Maybe include different parameters here).
+Currently use different parameters for B than using in figure \ref{fig:Combination_Turnover} (selection/drive twice as strong in turnover figure)}
+}
+\label{fig:Combination_Centimorgans}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\includegraphics[width=0.5\linewidth]{FreqWLowR}\\
-\includegraphics[width=0.5\linewidth]{SexRatioLowR}\\
-\includegraphics[width=0.5\linewidth]{MeanDipFitLowR}
-\caption{
-Haploid selection allows a neo-$W$ to invade an ancestral $XY$ system and fix (\textbf{A}) despite temporarily biasing the sex ratio further (\textbf{B}) and decreasing mean diploid viability fitness (\textbf{C}).
-Complete turnover between genetic sex-determination systems occurs despite the neo-$W$ being less tightly linked to the selected locus than the ancestral sex-determining locus is, $R>r$.
-Parameters: $k=1$, $s^f = 0.05$, $s^m = 0.15$, $h^f = h^m = 0.7$, $t^f = 0$, $t^m = -0.1$, $\alpha^m = \alpha^f = 1/2$, $r=0.01$, $R=0.05$.
-}
-\label{fig:WinvasionLowR}
-\end{figure}
+%\begin{figure}
+%\centering
+%\includegraphics[width=0.5\linewidth]{FreqWLowR}\\
+%\includegraphics[width=0.5\linewidth]{SexRatioLowR}\\
+%\includegraphics[width=0.5\linewidth]{MeanDipFitLowR}
+%\caption{
+%Haploid selection allows a neo-$W$ to invade an ancestral $XY$ system and fix (\textbf{A}) despite temporarily biasing the sex ratio further (\textbf{B}) and decreasing mean diploid viability fitness (\textbf{C}).
+%Complete turnover between genetic sex-determination systems occurs despite the neo-$W$ being less tightly linked to the selected locus than the ancestral sex-determining locus is, $R>r$.
+%Parameters: $k=1$, $s^f = 0.05$, $s^m = 0.15$, $h^f = h^m = 0.7$, $t^f = 0$, $t^m = -0.1$, $\alpha^m = \alpha^f = 1/2$, $r=0.01$, $R=0.05$.
+%}
+%\label{fig:WinvasionLowR}
+%\end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\includegraphics[width=0.5\linewidth]{FreqWHighR}\\
-\includegraphics[width=0.5\linewidth]{SexRatioHighR}\\
-\includegraphics[width=0.5\linewidth]{MeanDipFitHighR}
-\caption{
-Haploid selection allows a completely unlinked neo-$W$ to invade an ancestral $XY$ system (\textbf{A}) despite further biasing the sex ratio (\textbf{B}) and decreasing mean diploid viability fitness (\textbf{C}).
-The neo-$W$ does not fix (although variation at the \textbf{A} locus is maintained, $V_A>0$), resulting in a polymorphic sex-determination system.
-Parameters as in Figure \ref{fig:WinvasionLowR} but with $R=0.5$.
-}
-\label{fig:WinvasionHighR}
-\end{figure}
+%\begin{figure}
+%\centering
+%\includegraphics[width=0.5\linewidth]{FreqWHighR}\\
+%\includegraphics[width=0.5\linewidth]{SexRatioHighR}\\
+%\includegraphics[width=0.5\linewidth]{MeanDipFitHighR}
+%\caption{
+%Haploid selection allows a completely unlinked neo-$W$ to invade an ancestral $XY$ system (\textbf{A}) despite further biasing the sex ratio (\textbf{B}) and decreasing mean diploid viability fitness (\textbf{C}).
+%The neo-$W$ does not fix (although variation at the \textbf{A} locus is maintained, $V_A>0$), resulting in a polymorphic sex-determination system.
+%Parameters as in Figure \ref{fig:WinvasionLowR} but with $R=0.5$.
+%}
+%\label{fig:WinvasionHighR}
+%\end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
+%\begin{figure}
+%\centering
 %\includegraphics[width=0.5\linewidth]{InvasionVsCentiMorgans}
-\includegraphics[width=0.5\linewidth]{InvasionVsCentiMorgansAllOrders}
-\caption{
-Haploid selection allows a neo-$W$ to invade an ancestral $XY$ system regardless of how tightly it and the ancestral sex-determining locus are linked to the selected locus. 
-The ancestral sex-determining locus is located at -0.05 and the novel sex-determining locus is located at 0.05 (corresponding to the peaks of invasion fitness), such that the probability of a cross-over between them is $\approx0.1$.
-The x-axis gives the position of the locus under haploid selection.
-We used Haldane's map function \citep[Equation 3 in ][]{Haldane1919} to convert from map distance (centiMorgans) to the probability of a cross-over event. 
-Parameters as in Figure \ref{fig:WinvasionLowR}.
-}
-\label{fig:InvasionVsCentiMorgans}
-\end{figure}
+%\includegraphics[width=0.5\linewidth]{InvasionVsCentiMorgansAllOrders}
+%\caption{
+%Haploid selection allows a neo-$W$ to invade an ancestral $XY$ system regardless of how tightly it and the ancestral sex-determining locus are linked to the selected locus. 
+%The ancestral sex-determining locus is located at -0.05 and the novel sex-determining locus is located at 0.05 (corresponding to the peaks of invasion fitness), such that the probability of a cross-over between them is $\approx0.1$.
+%The x-axis gives the position of the locus under haploid selection.
+%We used Haldane's map function \citep[Equation 3 in ][]{Haldane1919} to convert from map distance (centiMorgans) to the probability of a cross-over event. 
+%Parameters as in Figure \ref{fig:WinvasionLowR}.
+%}
+%\label{fig:InvasionVsCentiMorgans}
+%\end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\includegraphics[width=0.5\linewidth]{FreqWCounterKozi}\\
-\includegraphics[width=0.5\linewidth]{SexRatioCounterKozi}\\
+%\begin{figure}
+%\centering
+%\includegraphics[width=0.5\linewidth]{FreqWCounterKozi}\\
+%\includegraphics[width=0.5\linewidth]{SexRatioCounterKozi}\\
 %\includegraphics[width=0.5\linewidth]{MeanDipFitCounterKozi}
-\caption{
-Meiotic drive allows a neo-$Y$ to invade an ancestral $ZW$ system and fix (\textbf{A}) despite temporarily biasing the sex ratio (\textbf{B}).
+%\caption{
+%Meiotic drive allows a neo-$Y$ to invade an ancestral $ZW$ system and fix (\textbf{A}) despite temporarily biasing the sex ratio (\textbf{B}).
 %and decreasing mean diploid viability fitness (\textbf{C}).
-Parameters: $k=0$, $s^f = s^m = t^f = t^m = 0$, $\alpha^m = 0.4$, $\alpha^f = 1/2$, $r=0$, $R=0$.
-}
-\label{fig:CounterKozi}
-\end{figure}
+%Parameters: $k=0$, $s^f = s^m = t^f = t^m = 0$, $\alpha^m = 0.4$, $\alpha^f = 1/2$, $r=0$, $R=0$.
+%}
+%\label{fig:CounterKozi}
+%\end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+\newpage
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Changes in mean fitness
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{Combination_MeanFit}\\
+\caption{
+\textcolor{red}{Could add titles to the columns/rows: neo-W for row 1, neo-Y for row 3, $r=0.5$, $R=0.05$ for column 1 and $r=0.05$, $R=0.5$ for column 2.
+\& possibly adjust padding (too much whitespace?).
+Matt - could you uncomment the line legends in the Mathematica file (function not included in my Mathematica version).}
+}
+\label{fig:Combination_MeanFit}
+\end{figure}
+
 \end{document}

### 2017-01-23 LaTeX/Turnover.tex
special cases results

@@
 In particular special cases, e.g., no sex-differences in selection or meiotic drive ($s^m=s^f$, $h^m=h^f$, and $\alpha^m=\alpha^f=1/2$), the equilibrium allele frequency and stability can be calculated analytically without assuming weak selection.
-However, here, we focus on weak selection and make fewer fitness assumptions.
+However, here, we focus on weak selection in order to make fewer assumptions about fitnesses.
 
@@
 
-We are particularly concerned with whether or not a rare neo-sex-determining region increases in frequency, which occurs when the largest eigenvalue, $\lambda$, that solves \eqref{eq:charpoly_neoY} is greater than one.
+We are particularly concerned with whether or not a rare neo-sex-determining allele increases in frequency, which occurs when the largest eigenvalue, $\lambda$, that solves \eqref{eq:charpoly_neoY} is greater than one.
 If the average change in frequency of the two haplotypes that carry the $m$ allele ($Am$ and $am$) is positive, invasion will always occur (if $\left\{(\lambda_{mA}-1)+ (\lambda_{ma}-1) \right\}/2>0$, $\lambda>1$).
@@
 
-\textcolor{red}{It may seem counterintuitive that, if the $A$ allele is more common on the ancestral-Y than the ancestral-X, and only favoured during haploid selection in males}
+The neo-sex-determining allele $m$ will spread if $\lambda_{m,XY}>1$. 
+Equation \eqref{eq:lambda_neoY} demonstrates that a neo-Y will invade if and only if it is more closely linked to the selected locus than the ancestral sex-determining region (i.e., if $R<r$, note that $V_{A}$ and $(S_{A})^2$ are strictly positive).
+This result echoes that of \citet{vanDoorn:2007eu}, who considered diploid selection only and also found that homogametic transitions (XY to XY or ZW to ZW) can occur when the neo-sex-determining locus is more closely linked to a locus under sexually-antagonistic selection.
+%Because tighter linkage between the sex-determining region and a selected locus evolves during these transitions, stronger associations between selected alleles and diploid sexes can build up by selection (e.g., between male-beneficial alleles and the male-determining allele, Y).%, increasing diploid mean fitness (Figure \ref{fig:Combination_MeanFit}).
 
-\textcolor{red}{although our predictions also perform well when recombination is small, see figure \ref{fig:WinvasionLowR}.
+If there is no selection upon haploid genotypes ($t^d=\alpha^d_{\Delta}=0$), as considered by \citet{vanDoorn:2010hu}, the spread of a neo-W is equivalent to the spread of a neo-Y ($\lambda_{W',XY}=\lambda_{Y',XY}$) such that heterogametic transitions (XY to ZW or ZW to XY) can also occur only if the neo-sex-determining region is more closely linked to a locus under selection ($R<r$).
+However, if there is any haploid selection, the additional term in equation \eqref{eq:lambda_neoW} can be positive, which can allow invasion ($\lambda_{W',XY}>1$) even when the neo-sex-determining region is less closely linked to the selected locus ($R>r$).
+These transitions are unusual because, when $R>r$, associations that build up by selection between sex and alleles will be weakened. 
+Therefore, mean fitness can decrease, see Figure \ref{fig:Combination_MeanFit}.
+
+We find that neo-W alleles can invade for a large number of selective regimes. 
+To clarify the parameter space under which $\lambda_{W',XY}>1$, we consider several special cases. 
+Firstly, if the \textbf{A} locus is unlinked to the ancestral sex-determining region ($r=1/2$), a more closely linked neo-W ($R<1/2$) can always invade because $\left( \hat{p}^m_Y-\hat{p}^m_X \right)=0$ such that the second term in \eqref{eq:lambda_neoW} disappears and invasion depends on the sign of $(r-R)$.
+Indeed, invasion typically occurs when the neo-W is more closely linked to the selected locus than the ancestral sex-determining region, Figure \ref{fig:Combination_Centimorgans}.
+Secondly, we can simplify cases where $R>r$ using the special case where $R=1/2$ and $r<1/2$. 
+In table \ref{tab:specialcases} we give the conditions where invasion occurs where we further assume that haploid selection only occurs during one phase in one sex (e.g., during male meiosis only) and equal dominance, $h^f=h^m$.
+Where there is no haploid competition and meiotic drive in one sex only, an unlinked neo-W can invade as long as the same allele is favoured in male and female diploid selection ($s^f s^m>0$, see Figure \ref{fig:Combination_Centimorgans}B), which is 50\% of the parameter space.
+Where there is no meiotic drive and haploid competition occurs in one sex only, an unlinked neo-W can invade as long as the same allele is favoured in male and female diploid selection and there are sex differences in selection of one type ($-s^f(s^f-s^m)>0$, see Figure \ref{fig:Combination_Centimorgans}C,D), which is 25\% of the parameter space.
+These special cases indicate that neo-W invasion when $R>r$ can occur for a relatively large fraction of parameter space.
+
+\begin{table}[ht]
+\centering
+\smallskip
+\caption{Invasion conditions for unlinked neo-W ($R=1/2$, $r<1/2$) with one form of haploid selection only}
+\begin{tabular}{l c }
+\hline\hline
+  Assumptions & neo-W spreads ($\lambda_{W',XY}>1$) if \\ [0.5ex] \hline
+%  $r=1/2$, $R<1/2$ & Always \\ [0.5ex] \hline
+%  $r<1/2$, $R=1/2$ &  \\ [0.5ex] \hline
+  $h^m=h^f$, $t^f=t^m=\alpha^f_{\Delta}=0$ & $s^f s^m>0$ \\
+  $h^m=h^f$, $t^f=t^m=\alpha^m_{\Delta}=0$ & $s^f s^m>0$ \\
+  $h^m=h^f$, $t^f=\alpha^f_{\Delta}=\alpha^m_{\Delta}=0$ & $-s^f(s^f-s^m)>0$ \\
+  $h^m=h^f$, $t^m=\alpha^f_{\Delta}=\alpha^m_{\Delta}=0$ & $-s^f(s^f-s^m)>0$ \\
+  \hline \hline
+  \label{tab:specialcases}
+ \end{tabular}
+\end{table}
+
+%If we further assume equal dominance ($h^f=h^m$) and that haploid selection only occurs during male meiosis ($t^f=t^m=\alpha^f_{\Delta}=0$), or female meiosis ($t^f=t^m=\alpha^m_{\Delta}=0$), neo-W invasion occurs when $s^f s^m>0$, Figure \ref{fig:Combination_Centimorgans}B.
+%That is, when the same allele is favoured by selection in both males and females (it may remain polymorphic via counter selection during meiotic drive).
+
+%\textcolor{red}{It may seem counterintuitive that, if the $A$ allele is more common on the ancestral-Y than the ancestral-X, and only favoured during haploid selection in males}
+
+%\textcolor{red}{although our predictions also perform well when recombination is small, see figure \ref{fig:WinvasionLowR}.
 We would have to add a line showing what invasion fitness the weak selection approximation would give and add dots to this figure (dots that are currently connected by a line), as in (vD\&K, 2010) }
@@
 %Sex ratios
-Previous research suggests, when the ancestral sex-determining locus is linked to a locus that experiences haploid selection (e.g., meiotic drive), a new, unlinked sex-determining locus can invade in order to restore equal sex ratios \citep{Kozielska:2010vm}.
+Previous research suggests, when the ancestral sex-determining locus is linked to a locus that experiences haploid selection (e.g., meiotic drive), a new, unlinked sex-determining locus invades in order to restore equal sex ratios \citep{Kozielska:2010vm}.
 Our model provides a good opportunity to determine whether Fisherian sex ratio selection provides a useful explanation for the evolution of new sex-determining loci in other contexts. 
@@
 We will also disregard haploid competition ($t^f=t^m=0$) such that zygotic sex ratios can only be biased by meiotic drive in males. 
-In this case, the zygotic sex ratio can be initially biased only if the ancestral sex-determining system is XY. 
-If the ancestral sex-determining system is ZW, the zygotic sex ratio will be 1:1 because diploid sex is determined by the proportion of Z-bearing versus W-bearing eggs (and meiosis in females is fair).
+In this case, the zygotic sex ratio can be initially biased only if the ancestral sex-determining system is XY (Figure \ref{fig:Combination_Turnover}B). 
+If the ancestral sex-determining system is ZW, the zygotic sex ratio will be 1:1 because diploid sex is determined by the proportion of Z-bearing versus W-bearing eggs (and meiosis in females is fair, Figure \ref{fig:Combination_Turnover}D).
 Thus, if the zygotic sex ratio is crucial to the evolution of new genetic sex-determining systems, invasion into ZW and XY systems will be distinct. 
-However, we find that invasion of new homogametic systems (XY to XY, or ZW to ZW) and heterogametic systems (XY to ZW or ZY to XY) occur under the same conditions. 
-That is, $\lambda_{Y',XY}=\lambda_{W',ZW}$ and $\lambda_{Y',ZW}=\lambda_{W',XY}$. 
-\textcolor{red}{Add figure w/ drive, showing sex ratio to explain this.}
+However, we find that invasion by a homogametic neo-sex-determining allele (XY to XY, or ZW to ZW) or by a heterogametic neo-sex-determining allele (XY to ZW or ZY to XY) occur under the same conditions.
+That is, we can show that $\lambda_{Y',XY}=\lambda_{W',ZW}$ and $\lambda_{Y',ZW}=\lambda_{W',XY}$, for a numerical example, compare Figure \ref{fig:Combination_Turnover}A,B to Figure \ref{fig:Combination_Turnover}C,D.
 
@@
 Even mutants that are equally likely to be found in males or females, such as an environmental sex determination mutation (equation \ref{eq:lambda_ESD}), are not strictly autosomal if they determine sex.
-Thus, despite the fact that sex ratio biases caused by haploid competition or meiotic drive have been shown to exert selection on various modifiers \citep{Stalker:1961th,Smith:1975ft,Frank:1989vl,Hough:2013uo,Ubeda:2015fx, Otto:2015va}, we do not find evidence that Fisherian sex ratio selection acting upon neo-sex-determination systems (e.g., see figure \textcolor{red}{REF}).
+Thus, despite the fact that sex ratio biases caused by haploid competition or meiotic drive have been shown to exert selection on various autosomal modifiers \citep{Stalker:1961th,Smith:1975ft,Frank:1989vl,Hough:2013uo,Ubeda:2015fx, Otto:2015va}, we do not find evidence that Fisherian sex ratio selection acting upon neo-sex-determination systems (e.g., see Figure \ref{fig:Combination_Turnover}).
 
@@
 \caption{
-\textcolor{red}{Could add titles to the columns/rows: neo-W for row 1, neo-Y for row 3, $r=0.5$, $R=0.05$ for column 1 and $r=0.05$, $R=0.5$ for column 2.
-\& possibly adjust padding (too much whitespace?).
+Heterogametic transitions from XY to ZW sex determination (neo-W frequency shown by black lines, panels A and B) or from ZW to XY (neo-Y frequency shown by black lines, panels C and D) occurs similarly regardless of sex ratio biases present before (B versus D) or after (C versus A, dashed lines show male frequency).
+During the invasion of a neo-ZW sex determination system (A and B), the ancestral Y fixes in both males and females (blue and red lines). 
+Similarly, the ancestral W allele fixes in males and females (blue and red lines) during a ZW to XY transition. 
+In this plot, there is no haploid competition ($t^f=t^m=0$) and meiotic drive occurs during male meiosis only ($\alpha^f_{\Delta}=0$, $\alpha^d_{\Delta}=-1/5$).
+Therefore, sex ratio biases can only arise when the \textbf{A} locus is linked to an XY sex-determining locus.
+In panels A and C, the neo-sex-determining locus is more closely linked to the \textbf{A} locus than the ancestral sex-detemining region ($r=1/2$, $R=1/20$) such that a neo-Y can caused biased sex ratios (panel C).
+Unlike with diploid selection alone, when there is haploid selection (in this case meiotic drive), neo-sex-determining loci that are less closely linked to the \textbf{A} locus can also spread (panels B and D, $r=1/20$, $R=1/2$), see equation \eqref{eq:lambda_neoW} and Figure \ref{fig:Combination_Centimorgans}B.
+These transitions are unusual because linkage generally allows favourable associations to arise via selection and the new sex determination systems in B and D have looser linkage. 
+Thus, diploid mean fitness decreases over the course of the transitions in B and D, see Figure \ref{fig:Combination_MeanFit}.
+However, the mean fitness of females increases during the spread of dominant neo-W alleles and the mean fitness of males increases during the spread of dominant neo-Y alleles, Figure \ref{fig:Combination_MeanFit}.
+In this plot there are no sex differences in selection and an equilirbium is maintained because selection in diploids opposes meiotic drive, $s^f =s^m = 1/5$, $h^f = h^m = 7/10$.
+\textcolor{red}{Aethetic adjustments: Could add titles to the columns/rows: neo-W for row 1, neo-Y for row 3, $r=0.5$, $R=0.05$ for column 1 and $r=0.05$, $R=0.5$ for column 2.
+Could adjust padding (too much whitespace where there is no axis label).
+It also seems could increase ratio of font size relative to plot size to make figure more compact.
+Could make sex ratio biases more extreme by reducing the $r$ in A and C and reducing $R$ in B and D.
 Matt - could you uncomment the line legends in the Mathematica file (function not included in my Mathematica version).}

### 2017-01-24 LaTeX/Turnover.tex
sex symbols, notes in table 2

@@
 \usepackage{amsmath}
+\usepackage{stix}
 % Bibliographies
@@
 \begin{abstract}
-Sex determination systems are remarkably dynamic; many studied taxa display transitions of sex-determining genes between chromosomes or the evolution of new sex-determining systems. 
+Sex determination systems are remarkably dynamic; many studied taxa display transitions of sex-determining genes between chromosomes or the evolution of entirely new sex-determining systems. 
 %Predominant theories in which new sex-determining systems are favoured by selection involve sex ratio selection or fitness differences between sexes (e.g., sexually antagonistic selection). 
@@
 In each generation, we census the genotype frequencies in male and female gametes/gametophytes (hereafter gametes) before haploid competition (see Sup.\ Mat. for recursion equations). 
-First, competition occurs among male gametes (sperm/pollen competition) and among female gametes (egg/ovule competition). 
-Selection during haploid competition depends on the \textbf{A} locus genotype, fitnesses are $w_{A}^m$ and $w_{a}^m$ for male gametes and $w_{A}^f$ and $w_{a}^f$ for female gametes, see table \ref{tab:fitnesstable}.
+First, competition occurs among male gametes (sperm/pollen competition) and among female gametes (egg/ovule competition) separately. 
+Selection during haploid competition depends on the \textbf{A} locus genotype, relative fitnesses are given by $w_A^\Hermaphrodite$ and $w_a^\Hermaphrodite$ ($\Hermaphrodite \in \{\female,\male\}$; see table \ref{tab:fitnesstable}).
+%$w_{A}^\male$ and $w_{a}^\male$ for male gametes and $w_{A}^\female$ and $w_{a}^\female$ for female gametes, see table \ref{tab:fitnesstable}.
 Random mating then occurs between male and female gametes.
 The resulting zygotes develop as males or females, depending on their genotypes at the \textbf{X} and \textbf{M} loci (and the \textbf{M} genotype of their mother in the case of maternal control) as described above.
-Diploid males and females then experience selection, male fitness is given by $w_{h}^{m}$ and female fitness by $w_{h}^{f}$, where $h$ is the genotype at the \textbf{A} locus ($h \in AA, Aa, aa$).  
+Diploid males and females then experience selection, relative fitnesses are given by $w_{g}^{\male}$ in males and $w_{g}^{\female}$ in females, where $g$ is the diploid genotype at the \textbf{A} locus ($g \in \{AA, Aa, aa\}$).
 %Diploids compete with others of the same sex, where selection depends on the sex of the individual and its genotype at the \textbf{A} locus.
@@
 Therefore, any order of the loci can be modelled with appropriate choices of $r$, $R$, and $\chi$ (see Table \ref{tab:chisubstitutions}). 
-Males/females that are heterozygous at the \textbf{A} locus experience meiotic drive; $Aa$ heterozgotes of sex $d$ produce gametes bearing allele $A$ with probability $\alpha^d$. 
+Males/females that are heterozygous at the \textbf{A} locus experience meiotic drive; $Aa$ heterozgotes of sex $\Hermaphrodite$ produce gametes bearing allele $A$ with probability $\alpha^\Hermaphrodite$.
 Thus, the \textbf{A} locus can experience sex-specific haploid competition, diploid selection and/or meiotic drive.
@@
 \smallskip
-\caption{Fitness of different genotypes in sex $d$}
+\caption{Relative fitness of different genotypes in sex $\Hermaphrodite \in \{\female,\male\}$}
 \begin{tabular}{l c }
 \hline\hline
-  Genotype & Fitness during haploid competition \\ [0.5ex] \hline
-  A & $w_{A}^d = 1+t^d$ \\
-  a & $w_{a}^d = 1$ \\ [0.5ex] \hline
-  Genotype & Fitness during diploid selection \\ [0.5ex] \hline
-  AA & $w_{AA}^d = 1+ s^d$ \\
-  Aa & $w_{Aa}^d = 1+h^k s^d$ \\
-  aa & $w_{aa}^d = 1$ \\ [0.5ex] \hline
+  Genotype & Relative fitness during haploid competition \\ [0.5ex] \hline
+  A & $w_{A}^\Hermaphrodite = 1+t^\Hermaphrodite$ \\
+  a & $w_{a}^\Hermaphrodite = 1$ \\ [0.5ex] \hline
+  Genotype & Relative fitness during diploid selection \\ [0.5ex] \hline
+  AA & $w_{AA}^\Hermaphrodite = 1+ s^\Hermaphrodite$ \\
+  Aa & $w_{Aa}^\Hermaphrodite = 1+h^\Hermaphrodite s^\Hermaphrodite$ \\
+  aa & $w_{aa}^\Hermaphrodite = 1$ \\ [0.5ex] \hline
   Genotype & Tranmission during meiosis in $Aa$ heterozygotes \\ [0.5ex] \hline
-  A & $\alpha^d=1/2+\alpha_{\Delta}^{d}/2$ \\
-  a & $(1-\alpha^d)=1/2-\alpha_{\Delta}^{d}/2$ \\
+  A & $\alpha^\Hermaphrodite=1/2+\alpha_{\Delta}^{\Hermaphrodite}/2$ \\
+  a & $(1-\alpha^\Hermaphrodite)=1/2-\alpha_{\Delta}^{\Hermaphrodite}/2$ \\
   \hline \hline
@@
 \subsection*{Resident equilibrium and stability}
-In the resident population (allele $M$ fixed), we follow the frequency of $A$ in female gametes (eggs) from an XX female, $p^f_X$, and in X-bearing, $p^m_X$, and Y-bearing, $p^m_Y$, male gametes (sperm).
-We also track the total frequency of Y-bearing male gametes (sperm), $q$, which may deviate from $1/2$ due to meiotic drive in males.
+In the resident population (allele $M$ fixed), we follow the frequency of $A$ in female gametes (eggs) from an XX female, $p^\female_X$, and in X-bearing, $p^\male_X$, and Y-bearing, $p^\male_Y$, male gametes (sperm).
+We also track the total frequency of Y-bearing male gametes, $q$, which may deviate from $1/2$ due to meiotic drive in males.
 
 Various forms of selection can maintain a polymorphism at the \textbf{A} locus, including sexually antagonistic selection, overdominance and conflicts between diploid selection and selection upon haploid genotypes \citep[ploidally antagonistic selection,][]{Immler:2012tl} or a combination of these selective regimes.
-Here, we assume that selection and meiotic drive are weak relative to recombination ($s^k$, $t^k$, $\alpha_{\Delta}^k$ of order $\epsilon$). 
+Here, we assume that selection and meiotic drive are weak relative to recombination ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon$). 
 The maintenance of a polymorphism at the \textbf{A} locus then requires that
@@
 \begin{split}
-0&<-((1-h^f)s^f +(1-h^m) s^m + t^f +t^m + \alpha_{\Delta}^f+\alpha_{\Delta}^m)\\
-%
-0&<(h^f s^f +h^m s^m + t^f +t^m + \alpha_{\Delta}^f+\alpha_{\Delta}^m).
+0&<-((1-h^\female)s^\female +(1-h^\male) s^\male + t^\female +t^\male + \alpha_{\Delta}^\female+\alpha_{\Delta}^\male)\\
+%
+0&<(h^\female s^\female +h^\male s^\male + t^\female +t^\male + \alpha_{\Delta}^\female+\alpha_{\Delta}^\male).
 \end{split}
@@
 which indicates that a polymorphism is maintained under various selective regimes. 
-In particular special cases, e.g., no sex-differences in selection or meiotic drive ($s^m=s^f$, $h^m=h^f$, and $\alpha^m=\alpha^f=1/2$), the equilibrium allele frequency and stability can be calculated analytically without assuming weak selection.
+In particular special cases, e.g., no sex-differences in selection or meiotic drive ($s^\male=s^\female$, $h^\male=h^\female$, and $\alpha^\male=\alpha^\female=1/2$), the equilibrium allele frequency and stability can be calculated analytically without assuming weak selection.
 However, here, we focus on weak selection in order to make fewer assumptions about fitnesses.
 
-Given that a polymorphism is maintained at the \textbf{A} locus by selection, with weak selection and drive, to leading order, the frequencies of $A$ in each type of gamete are the same ($\hat{p}^f_X=\hat{p}^m_X=\hat{p}^m_Y=\bar{p}$) and given by
-
-\begin{equation}
-\bar{p}=\frac{h^f s^f + h^m s^m +t^f+t^m+\alpha_{\Delta}^f+\alpha_{\Delta}^m}
-{(2h^f-1)s^f+(2h^m-1)s^m}
+Given that a polymorphism is maintained at the \textbf{A} locus by selection, with weak selection and drive, to leading order, the frequencies of $A$ in each type of gamete are the same ($\hat{p}^\female_X=\hat{p}^\male_X=\hat{p}^\male_Y=\bar{p}$) and given by
+
+\begin{equation}
+\bar{p}=\frac{h^\female s^\female + h^\male s^\male +t^\female+t^\male+\alpha_{\Delta}^\female+\alpha_{\Delta}^\male}
+{(2h^\female-1)s^\female+(2h^\male-1)s^\male}
 +O(\epsilon)
@@
 \begin{split}
-\hat{p}^m_X-\hat{p}^f_X&=V_{A}\big{(}D^m - D^f +\alpha_{\Delta}^m-\alpha_{\Delta}^f \big{)}
+\hat{p}^\male_X-\hat{p}^\female_X&=V_{A}\big{(}D^\male - D^\female +\alpha_{\Delta}^\male-\alpha_{\Delta}^\female \big{)}
 +O(\epsilon^2)\\
 %
-\hat{p}^m_Y-\hat{p}^f_X&=V_{A}\big{(}D^m - D^f+\alpha_{\Delta}^m-\alpha_{\Delta}^f+(1-2r)(t^m-t^f)\big{)}/2r
+\hat{p}^\male_Y-\hat{p}^\female_X&=V_{A}\big{(}D^\male - D^\female+\alpha_{\Delta}^\male-\alpha_{\Delta}^\female+(1-2r)(t^\male-t^\female)\big{)}/2r
 +O(\epsilon^2)\\
 %
-\hat{p}^m_Y-\hat{p}^m_X&=V_{A}\big{(}D^m - D^f+\alpha_{\Delta}^m-\alpha_{\Delta}^f+t^m-t^f\big{)}(1-2r)/2r
+\hat{p}^\male_Y-\hat{p}^\male_X&=V_{A}\big{(}D^\male - D^\female+\alpha_{\Delta}^\male-\alpha_{\Delta}^\female+t^\male-t^\female\big{)}(1-2r)/2r
 +O(\epsilon^2)
@@
 \noindent
-where $V_{A}=\bar{p}(1-\bar{p})$ is the variance in the frequency of $A$ and $D^d=\big{(} \bar{p}s^d+(1-\bar{p})h^d s^d\big{)} -\big{(} \bar{p}h^d s^d+(1-\bar{p}) \big{)}$ corresponds to the difference in fitness between $A$ and $a$ alleles in diploids of sex $d$ ($\bar{p}$ is the leading-order probability of mating with an $A$-bearing gamete from the opposite sex).
-The frequency of Y among male gametes depends upon the difference in $A$ allele frequency on X- and Y-bearing male gametes and the strength of meiotic drive in favour of the $A$ allele in males, $q=1/2+\alpha_{\Delta}^m(\hat{p}^m_Y-\hat{p}^m_X)/2+O(\epsilon^3)$.
-Without haploid competition or drive ($\alpha_{\Delta}^d=t^d=0$), these results reduce to those of \citet{vanDoorn:2007eu}.
+where $V_{A}=\bar{p}(1-\bar{p})$ is the variance in the frequency of $A$ and $D^\Hermaphrodite=\big{(} \bar{p}s^\Hermaphrodite+(1-\bar{p})h^\Hermaphrodite s^\Hermaphrodite\big{)} -\big{(} \bar{p}h^\Hermaphrodite s^\Hermaphrodite+(1-\bar{p}) \big{)}$ corresponds to the difference in fitness between $A$ and $a$ alleles in diploids of sex $\Hermaphrodite \in \{\female,\male\}$ ($\bar{p}$ is the leading-order probability of mating with an $A$-bearing gamete from the opposite sex).
+The frequency of Y among male gametes depends upon the difference in $A$ allele frequency on X- and Y-bearing male gametes and the strength of meiotic drive in favour of the $A$ allele in males, $q=1/2+\alpha_{\Delta}^\male(\hat{p}^\male_Y-\hat{p}^\male_X)/2+O(\epsilon^3)$.
+Without haploid competition or drive ($\alpha_{\Delta}^\Hermaphrodite=t^\Hermaphrodite=0$), these results reduce to those of \citet{vanDoorn:2007eu}.
 
@@
 \noindent
-where $b$ is the average of the growth rates of the two haplotypes that carry the $m$ allele ($mA$ and $ma$), $b=(\lambda_{mA}^{m}+\lambda_{ma}^{m})/2$, and $c$ also involves the fitness of $m$ alleles when they recombine onto the other \textbf{A} background in a heterozygote, $c=\lambda_{mA}\lambda_{ma}+\rho_{mA}\rho_{ma}$, see table \ref{tab:haplotype_growth}.
+where $b$ is the average of the growth rates of the two haplotypes that carry the $m$ allele ($mA$ and $ma$), $b=(\lambda_{mA}+\lambda_{ma})/2$, and $c$ also involves the fitness of $m$ alleles when they recombine onto the other \textbf{A} background in a heterozygote, $c=\lambda_{mA}\lambda_{ma}+\rho_{mA}\rho_{ma}$ (see table \ref{tab:haplotype_growth}).
 
@@
    neo-Y ($k=0$) \\ [0.5ex] \hline \noalign{\vskip 1ex}
-  $\lambda_{mA}=\{p_{X}^{f} w_{A}^{f} w_{A}^{m} w_{AA}^{m}+(1-p_{X}^{f}) w_{a}^{f} w_{A}^{m} w_{Aa}^{m}\alpha^m(1-R)\}/ \bar{w}_{H}^{f} \bar{w}_{H}^{m} \bar{w}^m$ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\lambda_{ma}=\{(1-p_{X}^{f}) w_{a}^{f} w_{a}^{m} w_{aa}^{m}+p_{X}^{f} w_{A}^{f} w_{a}^{m} w_{Aa}^{m}(1-\alpha^m)(1-R)\}/ \bar{w}_{H}^{f} \bar{w}_{H}^{m} \bar{w}^m $ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\rho_{mA}=R \{(1-p_{X}^{f}) w_{a}^{f} w_{A}^{m} w_{Aa}^{m} (1-\alpha_{m})\}/ \bar{w}_{H}^{f} \bar{w}_{H}^{m} \bar{w}^m $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\rho_{ma}=R\{p_{X}^{f} w_{A}^{f} w_{a}^{m} w_{Aa}^{m} \alpha_{m}\}/ \bar{w}_{H}^{f} \bar{w}_{H}^{m} \bar{w}^m$\\ [1ex] \hline 
+  $\lambda_{mA}=\{p_{X}^{\female} w_{A}^{\female} w_{A}^{\male} w_{AA}^{\male}+(1-p_{X}^{\female}) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male}\alpha^\male(1-R)\}/ \{ \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\male$ \} \\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\lambda_{ma}=\{(1-p_{X}^{\female}) w_{a}^{\female} w_{a}^{\male} w_{aa}^{\male}+p_{X}^{\female} w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male}(1-\alpha^\male)(1-R)\}/ \{ \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\male \}$ \\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\rho_{mA}=R \{(1-p_{X}^{\female}) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} (1-\alpha_{m})\}/ \{ \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\male \} $\\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\rho_{ma}=R\{p_{X}^{\female} w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male} \alpha_{m}\}/ \{ \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\male \}$\\ [1ex] \hline 
   \noalign{\vskip 0.5ex}
-  neo-W ($k=1$) \** \\ [0.5ex] \hline \noalign{\vskip 1ex}
-  $\lambda_{mA}=\{\bar{p}^{m} w_{A}^{m} w_{A}^{f} w_{AA}^{f}+(1-\bar{p}^{m}) w_{a}^{m} w_{A}^{f} w_{Aa}^{f}\alpha^f(1-R)\}/ \bar{w}_{H}^{f} \bar{w}_{H}^{m} \bar{w}^f$ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\lambda_{ma}=\{(1-\bar{p}^{m}) w_{a}^{m} w_{a}^{f} w_{aa}^{f}+\bar{p}^{m} w_{A}^{m} w_{a}^{f} w_{Aa}^{f}(1-\alpha^f)(1-R)\}/ \bar{w}_{H}^{f} \bar{w}_{H}^{m} \bar{w}^f $ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\rho_{mA}=R \{(1-\bar{p}^{m}) w_{a}^{m} w_{A}^{f} w_{Aa}^{f} (1-\alpha_{f})\}/ \bar{w}_{H}^{f} \bar{w}_{H}^{m} \bar{w}^f $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\rho_{ma}=R\{\bar{p}^{m} w_{A}^{m} w_{a}^{f} w_{Aa}^{f} \alpha_{f}\}/ \bar{w}_{H}^{f} \bar{w}_{H}^{m} \bar{w}^f$\\ [1ex] 
+  neo-W ($k=1$) \\ [0.5ex] \hline \noalign{\vskip 1ex}
+  $\lambda_{mA}=\{\bar{p}^{\male} w_{A}^{\male} w_{A}^{\female} w_{AA}^{\female}+(1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female}\alpha^\female(1-R)\}/ \{ \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\female \}$ \\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\lambda_{ma}=\{(1-\bar{p}^{\male}) w_{a}^{\male} w_{a}^{\female} w_{aa}^{\female}+\bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female}(1-\alpha^\female)(1-R)\}/ \{\bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\female \}$ \\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\rho_{mA}=R \{(1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female} (1-\alpha_{f})\}/ \{\bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\female \} $\\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\rho_{ma}=R\{\bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female} \alpha_{f}\}/ \{\bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\female \}$\\ [1ex] 
   \hline \hline 
@@
       \scriptsize
-      \item \** $\bar{p}^{m}=p_{Y}^{m}q+p_{X}^{m}(1-q)$ is the average frequency of the $A$ allele among X- and Y-bearing male gametes (pollen/sperm). 
+      \item $\bar{p}^{\male}=p_{Y}^{\male}q+p_{X}^{\male}(1-q)$ is the average frequency of the $A$ allele among X- and Y-bearing male gametes 
+      \item $\bar{w}_H^\female = p_X^\female w_A^\female + (1-p_X^\female) w_a^\female$ is the mean fitness of female gametes
+      \item $\bar{w}_H^\male = \bar{p}^{\male} w_A^\male + (1-\bar{p}^{\male}) w_a^\male$ is the mean fitness of male gametes
+       \item $\bar{w}^\female = \{ p_X^\female w_A^\female (1-q) p_X^\male w_A^\male w_{AA}^\female + (1 - p_X^\female) w_a^\female (1-q) p_X^\male w_A^\male w_{Aa}^\female + p_X^\female w_A^\female (1-q) (1 - p_X^\male) w_a^\male w_{Aa}^\female + (1-p_X^\female) w_a^\female (1-q) (1 - p_X^\male) w_a^\male w_{aa}^\female \} / \{ \bar{w}_H^\female \bar{w}_H^\male\}$ is the mean fitness of females
+       \item $\bar{w}^\male = \{ p_X^\female w_A^\female q p_Y^\male w_A^\male w_{AA}^\male + (1 - p_X^\female) w_a^\female q p_Y^\male w_A^\male w_{Aa}^\male + p_X^\female w_A^\female q (1 - p_Y^\male) w_a^\male w_{Aa}^\male + (1-p_X^\female) w_a^\female q (1 - p_Y^\male) w_a^\male w_{aa}^\male \} / \{ \bar{w}_H^\male \bar{w}_H^\male\}$ is the mean fitness of males
     \end{tablenotes}
@@
 For a neo-Y, invasion depends on the relative \textcolor{red}{(is this right, is relative fitness divided by mean fitness or difference from 1???)} fitness of $A$-bearing and $a$-bearing male gametes (i.e., in sperm only, not eggs).
-The fitness of male gametes partly depends on the allele carried by the female gamete that they mate with (e.g., $A$ with probability $p_{X}^{f} w_{A}^{f}/\bar{w}_{H}^{f}$).
+The fitness of male gametes partly depends on the allele carried by the female gamete that they mate with (e.g., $A$ with probability $p_{X}^{\female} w_{A}^{\female}/\bar{w}_{H}^{\female}$).
 Similarly, invasion of a neo-W depends on the relative fitness of $A$-bearing and $a$-bearing female gametes. 
-However, in the case of a neo-W, the allele carried by the male gamete that they mate with can come from either an X-bearing or a Y-bearing sperm (e.g., $A$ with probability $\bar{p}^{m} w_{A}^{m}/\bar{w}_{H}^{m}$, where $\bar{p}^{m}=p_{Y}^{m}q+p_{X}^{m}(1-q)$).
+However, in the case of a neo-W, the allele carried by the male gamete that they mate with can come from either an X-bearing or a Y-bearing sperm (e.g., $A$ with probability $\bar{p}^{\male} w_{A}^{\male}/\bar{w}_{H}^{\male}$, where $\bar{p}^{\male}=p_{Y}^{\male}q+p_{X}^{\male}(1-q)$).
 In either case, the zygote will then develop as a female due to the presence of a neo-W.
-By contrast, females that do not carry the neo-W, only result from matings with X-bearing sperm (e.g., matings with $A$-bearing sperm occur with probability $\bar{p}_{X}^{m} w_{A}^{m}/\bar{w}_{H}^{m}$).
+By contrast, females that do not carry the neo-W, only result from matings with X-bearing sperm (e.g., matings with $A$-bearing sperm occur with probability $\bar{p}_{X}^{\male} w_{A}^{\male}/\bar{w}_{H}^{\male}$).
 If the \textbf{A} locus is initially linked to the ancestral sex-determining locus, \textbf{X}, (i.e., $r<1/2$) the frequency of the $A$ allele among X- and Y-bearing sperm can differ (equation \ref{eq:freq_diffs}).
@@
 R \left[ 
-\frac{p^f_X w^m_a (1-\alpha^m)}{(\lambda_{mA}-1)\bar{w}_{H}^{m}} + 
-\frac{(1 - p^f_X) w^m_A \alpha^m \bar{w}_{H}^{m}}{(\lambda_{ma}-1)\bar{w}_{H}^{m}} \right] 
-\frac{w^m_{Aa}}{\bar{w}^m} < 1,
+\frac{p^\female_X w^\male_a (1-\alpha^\male)}{(\lambda_{mA}-1)\bar{w}_{H}^{\male}} + 
+\frac{(1 - p^\female_X) w^\male_A \alpha^\male \bar{w}_{H}^{\male}}{(\lambda_{ma}-1)\bar{w}_{H}^{\male}} \right] 
+\frac{w^\male_{Aa}}{\bar{w}^\male} < 1,
 \end{equation}
@@
 R \left[  
-\frac{(1 - \bar{p}^m) w^m_{a}}{(\lambda_{mA}-1)\bar{w}_{H}^{m}} + 
-\frac{\bar{p}^m w^m_{A}}{(\lambda_{ma}-1)\bar{w}_{H}^{m}} \right] 
-\frac{w^f_{Aa}}{\bar{w}^f} < 1
+\frac{(1 - \bar{p}^\male) w^\male_{a}}{(\lambda_{mA}-1)\bar{w}_{H}^{\male}} + 
+\frac{\bar{p}^\male w^\male_{A}}{(\lambda_{ma}-1)\bar{w}_{H}^{\male}} \right] 
+\frac{w^\female_{Aa}}{\bar{w}^\female} < 1
 \end{equation}
@@
 \textcolor{red}{Q: is it definitely possible to have negative square brackets for a equilibria maintained by selection?}
-%Assuming $g_A^* > 0$ and $g_a^* < 0$ without loss of generality, this is $-(1 - p^f_X) w_{m,A} g_a^* < p^f_X w_{m,a} g_A^*$.
+%Assuming $g_A^* > 0$ and $g_a^* < 0$ without loss of generality, this is $-(1 - p^\female_X) w_{m,A} g_a^* < p^\female_X w_{m,a} g_A^*$.
 When the net flow of recombinants is from the more fit to the less fit haplotype, the new sex-determining allele can still invade when the rate of recombination between it and the selected locus, $R$, is small enough.
@@
 We can explicitly determine the conditions under which invasion occurs if we assume that the $A$ allele reaches an equilibrium frequency under the ancestral sex-determination system before the neo-sex-determination system ($m$) arises.
-The equilibrium  frequency of $A$ on different ancestral backgrounds ($\hat{p}^m_Y$, $\hat{p}^m_X$, and $\hat{p}^f_X$) is given by equations \eqref{eq:pAve} and \eqref{eq:freq_diffs} where we assume selection and meiotic drive are weak relative to recombination ($s^k$, $t^k$, $\alpha_{\Delta}^k$ of order $\epsilon$).
+The equilibrium  frequency of $A$ on different ancestral backgrounds ($\hat{p}^\male_Y$, $\hat{p}^\male_X$, and $\hat{p}^\female_X$) is given by equations \eqref{eq:pAve} and \eqref{eq:freq_diffs} where we assume selection and meiotic drive are weak relative to recombination ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon$).
 Under weak selection, we denote the leading eigenvalue describing the invasion of a neo-Y ($k=0$) and a neo-W ($k=0$) into an ancestrally XY system by $\lambda_{Y',XY}$ and $\lambda_{W',XY}$, respectively, which are given by
@@
 \begin{equation}
-\lambda_{W',XY} =\lambda_{Y',XY}+\left(2\alpha_{\Delta}^m-2\alpha_{\Delta}^f+t^m-t^f \right) \left( \hat{p}^m_Y-\hat{p}^m_X \right)
+\lambda_{W',XY} =\lambda_{Y',XY}+\left(2\alpha_{\Delta}^\male-2\alpha_{\Delta}^\female+t^\male-t^\female \right) \left( \hat{p}^\male_Y-\hat{p}^\male_X \right)
 +O\left(\epsilon^3 \right) \\
@@
 \noindent
-where $V_{A}=\bar{p}(1-\bar{p})$ is the variance in the frequency of $A$ and $S_{A}=(D^m +\alpha_{\Delta}^m+t^m) - (D^f+\alpha_{\Delta}^f+t^f)$ is the difference in fitness in males versus females for the $A$ allele against the $a$ allele across diploid selection, haploid competition, and meiosis.
+where $V_{A}=\bar{p}(1-\bar{p})$ is the variance in the frequency of $A$ and $S_{A}=(D^\male +\alpha_{\Delta}^\male+t^\male) - (D^\female+\alpha_{\Delta}^\female+t^\female)$ is the difference in fitness in males versus females for the $A$ allele against the $a$ allele across diploid selection, haploid competition, and meiosis.
 
@@
 
-If there is no selection upon haploid genotypes ($t^d=\alpha^d_{\Delta}=0$), as considered by \citet{vanDoorn:2010hu}, the spread of a neo-W is equivalent to the spread of a neo-Y ($\lambda_{W',XY}=\lambda_{Y',XY}$) such that heterogametic transitions (XY to ZW or ZW to XY) can also occur only if the neo-sex-determining region is more closely linked to a locus under selection ($R<r$).
+If there is no selection upon haploid genotypes ($t^\Hermaphrodite=\alpha^\Hermaphrodite_{\Delta}=0$), as considered by \citet{vanDoorn:2010hu}, the spread of a neo-W is equivalent to the spread of a neo-Y ($\lambda_{W',XY}=\lambda_{Y',XY}$) such that heterogametic transitions (XY to ZW or ZW to XY) can also occur only if the neo-sex-determining region is more closely linked to a locus under selection ($R<r$).
 However, if there is any haploid selection, the additional term in equation \eqref{eq:lambda_neoW} can be positive, which can allow invasion ($\lambda_{W',XY}>1$) even when the neo-sex-determining region is less closely linked to the selected locus ($R>r$).
@@
 To clarify the parameter space under which $\lambda_{W',XY}>1$, we consider several special cases. 
-Firstly, if the \textbf{A} locus is unlinked to the ancestral sex-determining region ($r=1/2$), a more closely linked neo-W ($R<1/2$) can always invade because $\left( \hat{p}^m_Y-\hat{p}^m_X \right)=0$ such that the second term in \eqref{eq:lambda_neoW} disappears and invasion depends on the sign of $(r-R)$.
+Firstly, if the \textbf{A} locus is unlinked to the ancestral sex-determining region ($r=1/2$), a more closely linked neo-W ($R<1/2$) can always invade because $\left( \hat{p}^\male_Y-\hat{p}^\male_X \right)=0$ such that the second term in \eqref{eq:lambda_neoW} disappears and invasion depends on the sign of $(r-R)$.
 Indeed, invasion typically occurs when the neo-W is more closely linked to the selected locus than the ancestral sex-determining region, Figure \ref{fig:Combination_Centimorgans}.
 Secondly, we can simplify cases where $R>r$ using the special case where $R=1/2$ and $r<1/2$. 
-In table \ref{tab:specialcases} we give the conditions where invasion occurs where we further assume that haploid selection only occurs during one phase in one sex (e.g., during male meiosis only) and equal dominance, $h^f=h^m$.
-Where there is no haploid competition and meiotic drive in one sex only, an unlinked neo-W can invade as long as the same allele is favoured in male and female diploid selection ($s^f s^m>0$, see Figure \ref{fig:Combination_Centimorgans}B), which is 50\% of the parameter space.
-Where there is no meiotic drive and haploid competition occurs in one sex only, an unlinked neo-W can invade as long as the same allele is favoured in male and female diploid selection and there are sex differences in selection of one type ($-s^f(s^f-s^m)>0$, see Figure \ref{fig:Combination_Centimorgans}C,D), which is 25\% of the parameter space.
+In table \ref{tab:specialcases} we give the conditions where invasion occurs where we further assume that haploid selection only occurs during one phase in one sex (e.g., during male meiosis only) and equal dominance, $h^\female=h^\male$.
+Where there is no haploid competition and meiotic drive in one sex only, an unlinked neo-W can invade as long as the same allele is favoured in male and female diploid selection ($s^\female s^\male>0$, see Figure \ref{fig:Combination_Centimorgans}B), which is 50\% of the parameter space.
+Where there is no meiotic drive and haploid competition occurs in one sex only, an unlinked neo-W can invade as long as the same allele is favoured in male and female diploid selection and there are sex differences in selection of one type ($-s^\female(s^\female-s^\male)>0$, see Figure \ref{fig:Combination_Centimorgans}C,D), which is 25\% of the parameter space.
 These special cases indicate that neo-W invasion when $R>r$ can occur for a relatively large fraction of parameter space.
@@
 %  $r<1/2$, $R=1/2$ &  \\ [0.5ex] \hline
-  $h^m=h^f$, $t^f=t^m=\alpha^f_{\Delta}=0$ & $s^f s^m>0$ \\
-  $h^m=h^f$, $t^f=t^m=\alpha^m_{\Delta}=0$ & $s^f s^m>0$ \\
-  $h^m=h^f$, $t^f=\alpha^f_{\Delta}=\alpha^m_{\Delta}=0$ & $-s^f(s^f-s^m)>0$ \\
-  $h^m=h^f$, $t^m=\alpha^f_{\Delta}=\alpha^m_{\Delta}=0$ & $-s^f(s^f-s^m)>0$ \\
+  $h^\male=h^\female$, $t^\female=t^\male=\alpha^\female_{\Delta}=0$ & $s^\female s^\male>0$ \\
+  $h^\male=h^\female$, $t^\female=t^\male=\alpha^\male_{\Delta}=0$ & $s^\female s^\male>0$ \\
+  $h^\male=h^\female$, $t^\female=\alpha^\female_{\Delta}=\alpha^\male_{\Delta}=0$ & $-s^\female(s^\female-s^\male)>0$ \\
+  $h^\male=h^\female$, $t^\male=\alpha^\female_{\Delta}=\alpha^\male_{\Delta}=0$ & $-s^\female(s^\female-s^\male)>0$ \\
   \hline \hline
@@
 
-%If we further assume equal dominance ($h^f=h^m$) and that haploid selection only occurs during male meiosis ($t^f=t^m=\alpha^f_{\Delta}=0$), or female meiosis ($t^f=t^m=\alpha^m_{\Delta}=0$), neo-W invasion occurs when $s^f s^m>0$, Figure \ref{fig:Combination_Centimorgans}B.
+%If we further assume equal dominance ($h^\female=h^\male$) and that haploid selection only occurs during male meiosis ($t^\female=t^\male=\alpha^\female_{\Delta}=0$), or female meiosis ($t^\female=t^\male=\alpha^\male_{\Delta}=0$), neo-W invasion occurs when $s^\female s^\male>0$, Figure \ref{fig:Combination_Centimorgans}B.
 %That is, when the same allele is favoured by selection in both males and females (it may remain polymorphic via counter selection during meiotic drive).
@@
 Our model provides a good opportunity to determine whether Fisherian sex ratio selection provides a useful explanation for the evolution of new sex-determining loci in other contexts. 
-Consider, for example, the case where the \textbf{A} locus is linked to the ancestral-SDR ($r<1/2$) and experiences meiotic drive in males only (e.g., during spermatogenesis but not during oogenesis, $\alpha^m \neq 1/2$, $\alpha^f=1/2$).
-We will also disregard haploid competition ($t^f=t^m=0$) such that zygotic sex ratios can only be biased by meiotic drive in males. 
+Consider, for example, the case where the \textbf{A} locus is linked to the ancestral-SDR ($r<1/2$) and experiences meiotic drive in males only (e.g., during spermatogenesis but not during oogenesis, $\alpha^\male \neq 1/2$, $\alpha^\female=1/2$).
+We will also disregard haploid competition ($t^\female=t^\male=0$) such that zygotic sex ratios can only be biased by meiotic drive in males. 
 In this case, the zygotic sex ratio can be initially biased only if the ancestral sex-determining system is XY (Figure \ref{fig:Combination_Turnover}B). 
@@
 %\begin{equation}
-%R \left[ \frac{p^f_X w_{m,a}}{g_A^*} + \frac{(1 - p^f_X) w_{m,A}}{g_a^*} \right] w_{m,Aa} < \nu_m,
+%R \left[ \frac{p^\female_X w_{m,a}}{g_A^*} + \frac{(1 - p^\female_X) w_{m,A}}{g_a^*} \right] w_{m,Aa} < \nu_m,
 %\end{equation}
@@
 %$\nu_m = 
-%  p^f_X p_{Ym} w^m_{a} w^m_{AA} +
-%  p^f_X (1-p_{Ym}) w^m_{a} w^m_{AA} +
-%  (1-p^f_X) p_{Ym} w^m_{a} w^m_{AA} +
-%  (1-p^f_X) (1-p_{Ym}) w^m_a w^m_{AA}$
+%  p^\female_X p_{Ym} w^\male_{a} w^\male_{AA} +
+%  p^\female_X (1-p_{Ym}) w^\male_{a} w^\male_{AA} +
+%  (1-p^\female_X) p_{Ym} w^\male_{a} w^\male_{AA} +
+%  (1-p^\female_X) (1-p_{Ym}) w^\male_a w^\male_{AA}$
 %is the mean relative fitness of resident males.
-%%and $g_j^*$ is the growth rate of $X^m$ and $Ym$ haplotypes when on an $A$ ($j=A$)  or $a$ background ($j=a$).
+%%and $g_j^*$ is the growth rate of $X^\male$ and $Ym$ haplotypes when on an $A$ ($j=A$)  or $a$ background ($j=a$).
 %Neo-$Y$ invasion therefore occurs for any recombination rate, $R$, when the net flow of double recombinants is from the less fit to the more fit \textbf{A} background (making the term inside the square brackets negative).
-%%Assuming $g_A^* > 0$ and $g_a^* < 0$ without loss of generality, this is $-(1 - p^f_X) w_{m,A} g_a^* < p^f_X w_{m,a} g_A^*$.
+%%Assuming $g_A^* > 0$ and $g_a^* < 0$ without loss of generality, this is $-(1 - p^\female_X) w_{m,A} g_a^* < p^\female_X w_{m,a} g_A^*$.
 %When the net flow of double recombinants is from the more fit to the less fit haplotype, neo-$Y$ invasion can still occur when the rate of recombination is small enough.
@@
 %\begin{equation}
-%\lambda_{Y,XY} \approx 1 + V_A S_A (r - R)s^f,
-%\end{equation}
-%where $V_A = p_A(1-p_A)$ is the variance at the \textbf{A} locus, $S_A = s^f/ \left[ r R \left( s^f + s^m \right)^2 t_m^2 \right]$ (INTERPRETATION), $s^f$ and $s^m$ are the respective selection coefficients for $A$ in diploid females and males, $t_m$ is the selection coefficient for $A$ in gametes/gametophytes from males, and we've assumed equal dominance coefficients in the two sexes.
-%The neo-$Y$ can therefore invade whenever it is in tighter linkage with the selected locus than the ancestral sex-determining locus, $r>R$, provided locus \textbf{A} is polymorphic ($V_A>0$) and there is selection among both females ($s^f\neq0$) and gametes/gametophytes from males ($t_m\neq0$).
+%\lambda_{Y,XY} \approx 1 + V_A S_A (r - R)s^\female,
+%\end{equation}
+%where $V_A = p_A(1-p_A)$ is the variance at the \textbf{A} locus, $S_A = s^\female/ \left[ r R \left( s^\female + s^\male \right)^2 t_m^2 \right]$ (INTERPRETATION), $s^\female$ and $s^\male$ are the respective selection coefficients for $A$ in diploid females and males, $t_m$ is the selection coefficient for $A$ in gametes/gametophytes from males, and we've assumed equal dominance coefficients in the two sexes.
+%The neo-$Y$ can therefore invade whenever it is in tighter linkage with the selected locus than the ancestral sex-determining locus, $r>R$, provided locus \textbf{A} is polymorphic ($V_A>0$) and there is selection among both females ($s^\female\neq0$) and gametes/gametophytes from males ($t_m\neq0$).
 %
@@
 %\end{equation}
-%where $\bar{p}_m = (p_{Ym}+p^m_X) / 2$ is the mean frequency of $A$ in gametes/gametophytes from males, $w_{f,i}$ is the relative viability fitness of females depending on their diploid genotype at the \textbf{A} locus (with $i\in\{AA,Aa,aa\}$), and
+%where $\bar{p}_m = (p_{Ym}+p^\male_X) / 2$ is the mean frequency of $A$ in gametes/gametophytes from males, $w_{f,i}$ is the relative viability fitness of females depending on their diploid genotype at the \textbf{A} locus (with $i\in\{AA,Aa,aa\}$), and
 %$\nu_f = 
-%  p^f_X p^m_X w^m_{a} w_{AA,f} +
-%  p^f_X (1-p^m_X) w^m_{a} w_{Aa,f} +
-%  (1-p^f_X) p^m_X w^m_{a} w_{Aa,f} +
-%  (1-p^f_X) (1-p^m_X) w^m_a w_{aa,f}$
+%  p^\female_X p^\male_X w^\male_{a} w_{AA,f} +
+%  p^\female_X (1-p^\male_X) w^\male_{a} w_{Aa,f} +
+%  (1-p^\female_X) p^\male_X w^\male_{a} w_{Aa,f} +
+%  (1-p^\female_X) (1-p^\male_X) w^\male_a w_{aa,f}$
 %is the mean relative fitness of resident females. 
@@
 %\begin{equation}
-%\lambda_{W,XY} \approx 1 + V_A S_A \frac{(2r(1-R)-R) s^f + (1-2r)R s^m }{2},
+%\lambda_{W,XY} \approx 1 + V_A S_A \frac{(2r(1-R)-R) s^\female + (1-2r)R s^\male }{2},
 %\end{equation}
@@
 %In this case, even when the novel sex-determining locus is in looser linkage with the selected locus than is the ancestral sex-determining locus, $r<R$, a novel sex-determiner can invade.
-%For example, with $R=1/2$ the neo-$W$ invades if there is any linkage between the ancestral sex-determining and selected loci ($r<1/2$), there is selection among gametes/gametophytes in males ($t_m\neq0$), and there is selection for or against $A$ in both males and females ($s^m s^f >0$) that is stronger in females than in males ($|s^f| > |s^m|$).
+%For example, with $R=1/2$ the neo-$W$ invades if there is any linkage between the ancestral sex-determining and selected loci ($r<1/2$), there is selection among gametes/gametophytes in males ($t_m\neq0$), and there is selection for or against $A$ in both males and females ($s^\male s^\female >0$) that is stronger in females than in males ($|s^\female| > |s^\male|$).
 
@@
 %\begin{equation}\label{eq:neoYR}
-%R \left[ \frac{p^f_X w^m_a (1-\alpha^m)}{g_A^*} + \frac{(1 - p^f_X) w^m_A \alpha^m}{g_a^*} \right] w^m_{Aa} < \nu^m,
+%R \left[ \frac{p^\female_X w^\male_a (1-\alpha^\male)}{g_A^*} + \frac{(1 - p^\female_X) w^\male_A \alpha^\male}{g_a^*} \right] w^\male_{Aa} < \nu^\male,
 %\end{equation}
@@
 %\begin{equation}\label{eq:neoWR}
-%R \left[  \frac{(1 - \bar{p}^m) w^m_{a}}{g_A^*} + \frac{\bar{p}^m w^m_{A}}{g_a^*} \right] w^f_{Aa} < \nu^f
+%R \left[  \frac{(1 - \bar{p}^\male) w^\male_{a}}{g_A^*} + \frac{\bar{p}^\male w^\male_{A}}{g_a^*} \right] w^\female_{Aa} < \nu^\female
 %\end{equation}
 %for the neo-$W$.
-%Here $\bar{p}^m = (1-q) p^m_X+ q p^m_Y$ is the average frequency of $A$ in gametes produced by males, $w^i_{j}$ is the relative viability fitness of sex $i\in\{m,f\}$ depending on their haploid or diploid genotype at the \textbf{A} locus (with $j\in\{A,a,AA,Aa,aa\}$) and
+%Here $\bar{p}^\male = (1-q) p^\male_X+ q p^\male_Y$ is the average frequency of $A$ in gametes produced by males, $w^i_{j}$ is the relative viability fitness of sex $i\in\{m,f\}$ depending on their haploid or diploid genotype at the \textbf{A} locus (with $j\in\{A,a,AA,Aa,aa\}$) and
 %$\nu^i = 
-%  p^f_X p^m_{\textbf{X}^i} w^m_{a} w^i_{AA} +
-%  p^f_X (1-p^m_{\textbf{X}^i}) w^m_{a} w^i_{Aa} +
-%  (1-p^f_X) p^m_{\textbf{X}^i} w^m_{a} w^i_{Aa} +
-%  (1-p^f_X) (1-p^m_{\textbf{X}^i}) w^m_a w^i_{aa}$,
-%with $\textbf{X}^m = Y$ and $\textbf{X}^f = X$, is the mean relative fitness of resident individuals of sex $i$.
-%and $g_j^*$ is the growth rate of $X^m$ and $Ym$ haplotypes when on an $A$ ($j=A$)  or $a$ background ($j=a$).
-%Although male meiotic drive does not explicitly appear in Equation \ref{eq:neoWR}, it does affect the average frequency of $A$ in gametes from males, $\bar{p}^m$, and thus can play a role in neo-W invasion.
+%  p^\female_X p^\male_{\textbf{X}^i} w^\male_{a} w^i_{AA} +
+%  p^\female_X (1-p^\male_{\textbf{X}^i}) w^\male_{a} w^i_{Aa} +
+%  (1-p^\female_X) p^\male_{\textbf{X}^i} w^\male_{a} w^i_{Aa} +
+%  (1-p^\female_X) (1-p^\male_{\textbf{X}^i}) w^\male_a w^i_{aa}$,
+%with $\textbf{X}^\male = Y$ and $\textbf{X}^\female = X$, is the mean relative fitness of resident individuals of sex $i$.
+%and $g_j^*$ is the growth rate of $X^\male$ and $Ym$ haplotypes when on an $A$ ($j=A$)  or $a$ background ($j=a$).
+%Although male meiotic drive does not explicitly appear in Equation \ref{eq:neoWR}, it does affect the average frequency of $A$ in gametes from males, $\bar{p}^\male$, and thus can play a role in neo-W invasion.
 
 %Equations \eqref{eq:neoYR} and \eqref{eq:neoWR} show that the new sex-determining allele is expected to invade for any recombination rate, $R$, when the net flow of double recombinants is from the less fit to the more fit \textbf{A} background (making the terms inside the square brackets in Equations \ref{eq:neoYR} and \ref{eq:neoWR} negative).
-%Assuming $g_A^* > 0$ and $g_a^* < 0$ without loss of generality, this is $-(1 - p^f_X) w_{m,A} g_a^* < p^f_X w_{m,a} g_A^*$.
+%Assuming $g_A^* > 0$ and $g_a^* < 0$ without loss of generality, this is $-(1 - p^\female_X) w_{m,A} g_a^* < p^\female_X w_{m,a} g_A^*$.
 %When the net flow of double recombinants is from the more fit to the less fit haplotype, the new sex-determining allele can still invade when the rate of recombination between it and the selected locus, $R$, is small enough.
@@
 %We will consider haploid selection and meiotic drive separately.
-%With haploid selection and no drive we have $S_A = s^f (t^m)^2 / \left[ r R \left( s^f + s^m \right)^2 \right]$, where $s^f$ and $s^m$ are the respective selection coefficients for $A$ in diploid females and males, $t^m$ is the selection coefficient for $A$ in gametes from males, and we've assumed equal dominance coefficients in the two sexes ($h^f = h^m$).
-%With drive and no haploid selection one replaces $t^m$ with $\alpha^m-1/2$.
-
-%For the neo-$Y$ we have $C_Y = (r - R)s^f $ with haploid selection and $C_Y = 4(r - R)s^f $ with drive.
-%The neo-$Y$ can therefore invade whenever it is in tighter linkage with the selected locus than the ancestral sex-determining locus, $r>R$, provided locus \textbf{A} is polymorphic ($V_A>0$), there is diploid selection in females ($s^f\neq0$), and there is either haploid selection between gametes from males ($t^m\neq0$) or meiotic drive in males ($\alpha^m\neq1/2$).
+%With haploid selection and no drive we have $S_A = s^\female (t^\male)^2 / \left[ r R \left( s^\female + s^\male \right)^2 \right]$, where $s^\female$ and $s^\male$ are the respective selection coefficients for $A$ in diploid females and males, $t^\male$ is the selection coefficient for $A$ in gametes from males, and we've assumed equal dominance coefficients in the two sexes ($h^\female = h^\male$).
+%With drive and no haploid selection one replaces $t^\male$ with $\alpha^\male-1/2$.
+
+%For the neo-$Y$ we have $C_Y = (r - R)s^\female $ with haploid selection and $C_Y = 4(r - R)s^\female $ with drive.
+%The neo-$Y$ can therefore invade whenever it is in tighter linkage with the selected locus than the ancestral sex-determining locus, $r>R$, provided locus \textbf{A} is polymorphic ($V_A>0$), there is diploid selection in females ($s^\female\neq0$), and there is either haploid selection between gametes from males ($t^\male\neq0$) or meiotic drive in males ($\alpha^\male\neq1/2$).
 %This is similar to the conclusion reached concerning sexual-antagonistic selection in \cite{vanDoorn:2007eu} and reduces to their weak-linkage results exactly when we do not assume equal dominance coefficients in the two sexes, there is no haploid selection or meiotic drive, and there is free recombination between locus \textbf{A} and one of the sex-determining regions.
 
-%For the neo-$W$ we have $C_W = [(2r(1-R)-R) s^f + (1-2r)R s^m]/2$ with haploid selection and $C_W = 4[r(1-2R) s^f + (1-2r)R s^m]/2$ with drive.
+%For the neo-$W$ we have $C_W = [(2r(1-R)-R) s^\female + (1-2r)R s^\male]/2$ with haploid selection and $C_W = 4[r(1-2R) s^\female + (1-2r)R s^\male]/2$ with drive.
 %In this case, even when the novel sex-determining locus is in looser linkage with the selected locus than the ancestral sex-determining locus is, $r<R$, a neo-$W$ can invade (Figures \ref{fig:WinvasionLowR} -- \ref{fig:InvasionVsCentiMorgans}).
 %This does not occur in models with only sexually-antagonistic selection \citep{vanDoorn:2010hu}.
-%For example, with $R=1/2$ the neo-$W$ invades if there is any linkage between the ancestral sex-determining and selected loci ($r<1/2$), there is selection among gametes in males ($t^m\neq0$), and there is selection for or against $A$ in both males and females ($s^m s^f >0$) that is stronger in males than in females ($|s^m| > |s^f|$).
-%With meiotic drive and $R=1/2$, all that is required for neo-W invasion is $r<1/2$ and $s^m s^f >0$.
+%For example, with $R=1/2$ the neo-$W$ invades if there is any linkage between the ancestral sex-determining and selected loci ($r<1/2$), there is selection among gametes in males ($t^\male\neq0$), and there is selection for or against $A$ in both males and females ($s^\male s^\female >0$) that is stronger in males than in females ($|s^\male| > |s^\female|$).
+%With meiotic drive and $R=1/2$, all that is required for neo-W invasion is $r<1/2$ and $s^\male s^\female >0$.
 %Our results reduce to the weak-linkage results of \cite[][Equation 3]{vanDoorn:2010hu} when we do not assume equal dominance coefficients in the two sexes and there is no haploid selection or meiotic drive.
@@
 \lambda_{ESD,XY} \approx 1 + \frac{1}{2}\frac{(\lambda_{Y,XY} - 1) + (\lambda_{W,XY} -1)}{2} \Big|_{R=1/2}
-%V_A \frac{r}{1-2r}  \frac{s_{f} \left( s^m - 3 s^f\right) }{8 \left( s_{f} + s_{m} \right)^2} t_{m}^2.
+%V_A \frac{r}{1-2r}  \frac{s_{f} \left( s^\male - 3 s^\female\right) }{8 \left( s_{f} + s_{m} \right)^2} t_{m}^2.
 \label{eq:lambda_ESD}
@@
 %\begin{equation}
-%C_1 = \frac{\left[ (2r(1-R)-R) s^f + (1-2r)R s^m \right]}{2}
+%C_1 = \frac{\left[ (2r(1-R)-R) s^\female + (1-2r)R s^\male \right]}{2}
 %\end{equation}
@@
 Of particular interest is $k=1/2$ (i.e., when the mother perfectly balances the sex ratio of her offspring).
-When both recombination rates are small we have $C_{1/2} \approx R(s^m - s^f)/8 = \lim_{r \rightarrow 0} C_1/4$.
+When both recombination rates are small we have $C_{1/2} \approx R(s^\male - s^\female)/8 = \lim_{r \rightarrow 0} C_1/4$.
 This implies that, at least under tight linkage, the invasion of maternally-controlled ESD is independent of $R$ (because $S_A\propto R^{-1}$) and can invade whenever a neo-$W$ can (which can invade even when it biases the sex ratio further; Figures \ref{fig:WinvasionLowR} -- \ref{fig:WinvasionHighR}).
@@
 Similarly, the ancestral W allele fixes in males and females (blue and red lines) during a ZW to XY transition. 
-In this plot, there is no haploid competition ($t^f=t^m=0$) and meiotic drive occurs during male meiosis only ($\alpha^f_{\Delta}=0$, $\alpha^d_{\Delta}=-1/5$).
+In this plot, there is no haploid competition ($t^\female=t^\male=0$) and meiotic drive occurs during male meiosis only ($\alpha^\female_{\Delta}=0$, $\alpha^\Hermaphrodite_{\Delta}=-1/5$).
 Therefore, sex ratio biases can only arise when the \textbf{A} locus is linked to an XY sex-determining locus.
@@
 However, the mean fitness of females increases during the spread of dominant neo-W alleles and the mean fitness of males increases during the spread of dominant neo-Y alleles, Figure \ref{fig:Combination_MeanFit}.
-In this plot there are no sex differences in selection and an equilirbium is maintained because selection in diploids opposes meiotic drive, $s^f =s^m = 1/5$, $h^f = h^m = 7/10$.
+In this plot there are no sex differences in selection and an equilirbium is maintained because selection in diploids opposes meiotic drive, $s^\female =s^\male = 1/5$, $h^\female = h^\male = 7/10$.
 \textcolor{red}{Aethetic adjustments: Could add titles to the columns/rows: neo-W for row 1, neo-Y for row 3, $r=0.5$, $R=0.05$ for column 1 and $r=0.05$, $R=0.5$ for column 2.
@@
 \caption{
-\textcolor{red}{A sexual antagonism (no haploid selection), B drive (no haploid competition), equal selection in sexes ($s^f=s^m$), C \& D Pollen/Sperm competition only (no drive).
-C allele favoured in pollen/sperm competition selected against less in males ($t<0$, $s^f, s^m >0$, $s^f<s^f$).
-D allele favoured in pollen/sperm competition selected against more in males than females ($t<0$, $s^f, s^m >0$, $s^f>s^f$).
+\textcolor{red}{A sexual antagonism (no haploid selection), B drive (no haploid competition), equal selection in sexes ($s^\female=s^\male$), C \& D Pollen/Sperm competition only (no drive).
+C allele favoured in pollen/sperm competition selected against less in males ($t<0$, $s^\female, s^\male >0$, $s^\female<s^\female$).
+D allele favoured in pollen/sperm competition selected against more in males than females ($t<0$, $s^\female, s^\male >0$, $s^\female>s^\female$).
 I suspect that panel C has a region where no equilibrium is maintained (CHECK!
@@
 %Complete turnover between genetic sex-determination systems occurs despite the neo-$W$ being less tightly linked to the selected locus than the ancestral sex-determining locus is, $R>r$.
-%Parameters: $k=1$, $s^f = 0.05$, $s^m = 0.15$, $h^f = h^m = 0.7$, $t^f = 0$, $t^m = -0.1$, $\alpha^m = \alpha^f = 1/2$, $r=0.01$, $R=0.05$.
+%Parameters: $k=1$, $s^\female = 0.05$, $s^\male = 0.15$, $h^\female = h^\male = 0.7$, $t^\female = 0$, $t^\male = -0.1$, $\alpha^\male = \alpha^\female = 1/2$, $r=0.01$, $R=0.05$.
 %}
@@
 %and decreasing mean diploid viability fitness (\textbf{C}).
-%Parameters: $k=0$, $s^f = s^m = t^f = t^m = 0$, $\alpha^m = 0.4$, $\alpha^f = 1/2$, $r=0$, $R=0$.
+%Parameters: $k=0$, $s^\female = s^\male = t^\female = t^\male = 0$, $\alpha^\male = 0.4$, $\alpha^\female = 1/2$, $r=0$, $R=0$.
 %}
@@
 In each generation we census the genotype frequencies in male and female gametes/gametophytes (hereafter, gametes) before haploid competition. 
-Before haploid competition, the frequencies of X-bearing male and female gametes are given by $X_{i}^{m}$ and $X_{i}^{f}$ and the frequencies of Y-bearing gametes are given by $Y_{i}^{m}$ and $Y_{i}^{f}$ where the index $i$ specifies genotypes $MA=1$, $Ma=2$, $mA=3$, and $ma=4$.
+Before haploid competition, the frequencies of X-bearing male and female gametes are given by $X_{i}^{\male}$ and $X_{i}^{\female}$ and the frequencies of Y-bearing gametes are given by $Y_{i}^{\male}$ and $Y_{i}^{\female}$ where the index $i$ specifies genotypes $MA=1$, $Ma=2$, $mA=3$, and $ma=4$.
 Competition then occurs among gametes of the same sex (e.g., among eggs and among sperm separately) according to the \textbf{A} locus allele, $g$ ($g\in A$, $a$, see Table \ref{tab:fitnesstable}), carried by individuals with genotype $i$.
-The genotype frequencies after haploid competition are $X_{i}^{d,s}= w_{g}X_{i}^{d}/\bar{w}_{H}^{d}$ and $Y_{i}^{d,s}= w_{g}Y_{i}^{d}/\bar{w}_{H}^{d}$, where $\bar{w}_{H}^{d}=\sum_{i=1}^{4} w_{g}X_{i}^{d}+w_{g}Y_{i}^{d}$ is the mean fitness of male ($d=m$) or female ($d=f$) gametes.
+The genotype frequencies after haploid competition are $X_{i}^{\Hermaphrodite,s}= w_{g}X_{i}^{\Hermaphrodite}/\bar{w}_{H}^{\Hermaphrodite}$ and $Y_{i}^{\Hermaphrodite,s}= w_{g}Y_{i}^{\Hermaphrodite}/\bar{w}_{H}^{\Hermaphrodite}$, where $\bar{w}_{H}^{\Hermaphrodite}=\sum_{i=1}^{4} w_{g}X_{i}^{\Hermaphrodite}+w_{g}Y_{i}^{\Hermaphrodite}$ is the mean fitness of male ($\Hermaphrodite=\male$) or female ($\Hermaphrodite=\female$) gametes.
 Random mating then occurs between gametes to produce diploid zygotes with genotype $ij$ at the \textbf{A} and \textbf{M} loci, such that $XX$ zygotes are denoted $xx_{ij}$, $XY$ zygotes are $xy_{ij}$, and $YY$ zygotes are $yy_{ij}$.
 In $XX$ and $YY$ zygotes, individuals with genotype $ij$ are equivalent to those with genotype $ji$. 
-For simplicity, we denote the frequency of genotype $ij$ in $XX$ and $YY$ zygotes to the average of these frequencies, $xx_{ij}=(X_{i}^{f,s}X_{j}^{m,s}+X_{j}^{f,s}X_{i}^{m,s})/2$ and $yy_{ij}=(Y_{i}^{f,s}Y_{j}^{m,s}+Y_{j}^{f,s}Y_{i}^{m,s})/2$.
+For simplicity, we denote the frequency of genotype $ij$ in $XX$ and $YY$ zygotes to the average of these frequencies, $xx_{ij}=(X_{i}^{\female,s}X_{j}^{\male,s}+X_{j}^{\female,s}X_{i}^{\male,s})/2$ and $yy_{ij}=(Y_{i}^{\female,s}Y_{j}^{\male,s}+Y_{j}^{\female,s}Y_{i}^{\male,s})/2$.
 
 Denoting the \textbf{M} locus genotype by $b$ ($b\in MM$, $Mm$, $mm$) and the \textbf{X} locus genotype by $c$ ($c\in XX$, $XY$, $YY$), zygotes develop as females with probability $k_{bc}$. 
-Therefore, the frequencies of $XX$ females are given by $xx_{ij}^{f}=k_{bc}xx_{ij}$, $XY$ females are given by $xy_{ij}^{f}=k_{bc}xy_{ij}$, and $YY$ females are given by $yy_{ij}^{f}=k_{bc}xy_{ij}$. 
-Similarly, $XX$ male frequencies are $xx_{ij}^{m}=(1-k_{bc})xx_{ij}$, $XY$ male frequencies are $xy_{ij}^{m}=(1-k_{bc})xy_{ij}$, and $YY$ males frequencies are $yy_{ij}^{m}=(1-k_{bc})xy_{ij}$.
+Therefore, the frequencies of $XX$ females are given by $xx_{ij}^{\female}=k_{bc}xx_{ij}$, $XY$ females are given by $xy_{ij}^{\female}=k_{bc}xy_{ij}$, and $YY$ females are given by $yy_{ij}^{\female}=k_{bc}xy_{ij}$.
+Similarly, $XX$ male frequencies are $xx_{ij}^{\male}=(1-k_{bc})xx_{ij}$, $XY$ male frequencies are $xy_{ij}^{\male}=(1-k_{bc})xy_{ij}$, and $YY$ males frequencies are $yy_{ij}^{\male}=(1-k_{bc})xy_{ij}$.
 This notation allows both the ancestral and novel sex-determining regions to determine zygotic sex according to an $XY$ system, a $ZW$ system, or an environmental sex-determining system. 
@@
 Selection among diploids then occurs according to the diploid genotype at the \textbf{A} locus, $h$, for an individual of type $ij$ ($h \in AA$, $Aa$, $aa$, see Table \ref{tab:fitnesstable}). 
-The diploid frequencies after selection in sex $d$ are given by $xx_{ij}^{d,s}=w_{h}^{d} xx_{ij}/\bar{w}^{d}$, $xy_{ij}^{d,s}=w_{h}^{d} xy_{ij}/\bar{w}^{d}$, and $yy_{ij}^{d,s}=w_{h}^{d} yy_{ij}/\bar{w}^{d}$, where $\bar{w}^{d}= \sum_{i=1}^{4}\sum_{j=1}^{4}w_{h}^{d}xx_{ij}+w_{h}^{d}xy_{ij}+w_{h}^{d}yy_{ij}$ is the mean fitness of individuals of sex $d$.
+The diploid frequencies after selection in sex $d$ are given by $xx_{ij}^{\Hermaphrodite,s}=w_{h}^{\Hermaphrodite} xx_{ij}/\bar{w}^{\Hermaphrodite}$, $xy_{ij}^{\Hermaphrodite,s}=w_{h}^{\Hermaphrodite} xy_{ij}/\bar{w}^{\Hermaphrodite}$, and $yy_{ij}^{\Hermaphrodite,s}=w_{h}^{\Hermaphrodite} yy_{ij}/\bar{w}^{\Hermaphrodite}$, where $\bar{w}^{\Hermaphrodite}= \sum_{i=1}^{4}\sum_{j=1}^{4}w_{h}^{\Hermaphrodite}xx_{ij}+w_{h}^{\Hermaphrodite}xy_{ij}+w_{h}^{\Hermaphrodite}yy_{ij}$ is the mean fitness of individuals of sex $d$.
 
@@
 Table \ref{tab:chisubstitutions} gives substitutions for $\chi$ for defined relative locations of these loci.
-During meiosis in sex $d$, meiotic drive occurs such that, in $Aa$ heterozygotes, a fraction $\alpha_{d}$ of gametes produced carry the $A$ allele and $(1-\alpha^d)$ carry the $a$ allele.
+During meiosis in sex $d$, meiotic drive occurs such that, in $Aa$ heterozygotes, a fraction $\alpha_{d}$ of gametes produced carry the $A$ allele and $(1-\alpha^\Hermaphrodite)$ carry the $a$ allele.
 
@@
 
-Among gametes from sex $d$ (sperm/pollen when $d=m$, eggs/ovules when $d=f$), the frequency of haplotypes (before haploid competition) in the next generation are given by
+Among gametes from sex $\Hermaphrodite$ (sperm/pollen when $\Hermaphrodite=\male$, eggs/ovules when $\Hermaphrodite=\female$), the frequency of haplotypes (before haploid competition) in the next generation are given by
 
@@
 \begin{split}
-X_{MA}^{d'}=&xx_{11}^{d,s}+xx_{13}^{d,s}/2+(xx_{12}^{d,s}+xx_{14}^{d,s})\alpha^d\\
-&-R(xx_{14}^{d,s}-xx_{23}^{d,s}) \alpha^d\\
-&+(xy_{11}^{d,s}+xy_{13}^{d,s})/2+(xy_{12}^{d,s}+xy_{14}^{d,s})\alpha^d\\
-&- r(xy_{12}^{d,s}-xy_{21}^{d,s})\alpha^d - \chi(xy_{13}^{d,s}-xy_{31}^{d,s})/2\\
-&+\big{\{}-(R+r+\chi)xy_{14}^{d,s} +(r+\chi-R)xy_{41}^{d,s}\\
-&+(R+r-\chi) xy_{23}^{d,s}+(R+\chi-r)xy_{32}^{d,s}\big{\}}\alpha^d/2
+X_{MA}^{{\Hermaphrodite}'}=&xx_{11}^{\Hermaphrodite,s}+xx_{13}^{\Hermaphrodite,s}/2+(xx_{12}^{\Hermaphrodite,s}+xx_{14}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
+&-R(xx_{14}^{\Hermaphrodite,s}-xx_{23}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
+&+(xy_{11}^{\Hermaphrodite,s}+xy_{13}^{\Hermaphrodite,s})/2+(xy_{12}^{\Hermaphrodite,s}+xy_{14}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
+&- r(xy_{12}^{\Hermaphrodite,s}-xy_{21}^{\Hermaphrodite,s})\alpha^\Hermaphrodite - \chi(xy_{13}^{\Hermaphrodite,s}-xy_{31}^{\Hermaphrodite,s})/2\\
+&+\big{\{}-(R+r+\chi)xy_{14}^{\Hermaphrodite,s} +(r+\chi-R)xy_{41}^{\Hermaphrodite,s}\\
+&+(R+r-\chi) xy_{23}^{\Hermaphrodite,s}+(R+\chi-r)xy_{32}^{\Hermaphrodite,s}\big{\}}\alpha^\Hermaphrodite/2
 \end{split}
@@
 \begin{split}
-X_{Ma}^{d'}=&xx_{22}^{d,s}+xx_{24}^{d,s}/2+(xx_{12}^{d,s}+xx_{23}^{d,s})\alpha^d\\
-&-R(xx_{23}^{d,s}-xx_{14}^{d,s}) \alpha^d\\
-&(xy_{22}^{d,s}+xy_{24}^{d,s})/2+(xy_{21}^{d,s}+xy_{23}^{d,s})(1-\alpha^d)\\
-&- r(xy_{21}^{d,s}-xy_{12}^{d,s})(1-\alpha^d) - \chi(xy_{24}^{d,s}-xy_{42}^{d,s})/2\\
-&+\big{\{}-(R+r+\chi)xy_{23}^{d,s}+(r+\chi-R)xy_{32}^{d,s}\\
-&+(R+r-\chi) xy_{14}^{d,s}+(R+\chi-r)xy_{41}^{d,s}\big{\}}(1-\alpha^d)/2
+X_{Ma}^{{\Hermaphrodite}'}=&xx_{22}^{\Hermaphrodite,s}+xx_{24}^{\Hermaphrodite,s}/2+(xx_{12}^{\Hermaphrodite,s}+xx_{23}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
+&-R(xx_{23}^{\Hermaphrodite,s}-xx_{14}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
+&(xy_{22}^{\Hermaphrodite,s}+xy_{24}^{\Hermaphrodite,s})/2+(xy_{21}^{\Hermaphrodite,s}+xy_{23}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite)\\
+&- r(xy_{21}^{\Hermaphrodite,s}-xy_{12}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite) - \chi(xy_{24}^{\Hermaphrodite,s}-xy_{42}^{\Hermaphrodite,s})/2\\
+&+\big{\{}-(R+r+\chi)xy_{23}^{\Hermaphrodite,s}+(r+\chi-R)xy_{32}^{\Hermaphrodite,s}\\
+&+(R+r-\chi) xy_{14}^{\Hermaphrodite,s}+(R+\chi-r)xy_{41}^{\Hermaphrodite,s}\big{\}}(1-\alpha^\Hermaphrodite)/2
 \end{split}
@@
 \begin{split}
-X_{mA}^{d'}=&xx_{33}^{d,s}+xx_{13}^{d,s}/2+(xx_{23}^{d,s}+xx_{34}^{d,s})\alpha^d\\
-&-R(xx_{23}^{d,s}-xx_{14}^{d,s}) \alpha^d\\
-&(xy_{33}^{d,s}+xy_{31}^{d,s})/2+(xy_{32}^{d,s}+xy_{34}^{d,s})\alpha^d\\
-&- r(xy_{34}^{d,s}-xy_{43}^{d,s}) \alpha^d - \chi(xy_{31}^{d,s}-xy_{13}^{d,s})/2\\
-&+\big{\{}-(R+r+\chi)xy_{32}^{d,s} +(r+\chi-R)xy_{23}^{d,s}\\
-&+(R+r-\chi) xy_{41}^{d,s}+(R+\chi-r)xy_{14}^{d,s}\big{\}} \alpha^d/2
+X_{mA}^{{\Hermaphrodite}'}=&xx_{33}^{\Hermaphrodite,s}+xx_{13}^{\Hermaphrodite,s}/2+(xx_{23}^{\Hermaphrodite,s}+xx_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
+&-R(xx_{23}^{\Hermaphrodite,s}-xx_{14}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
+&(xy_{33}^{\Hermaphrodite,s}+xy_{31}^{\Hermaphrodite,s})/2+(xy_{32}^{\Hermaphrodite,s}+xy_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
+&- r(xy_{34}^{\Hermaphrodite,s}-xy_{43}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite - \chi(xy_{31}^{\Hermaphrodite,s}-xy_{13}^{\Hermaphrodite,s})/2\\
+&+\big{\{}-(R+r+\chi)xy_{32}^{\Hermaphrodite,s} +(r+\chi-R)xy_{23}^{\Hermaphrodite,s}\\
+&+(R+r-\chi) xy_{41}^{\Hermaphrodite,s}+(R+\chi-r)xy_{14}^{\Hermaphrodite,s}\big{\}} \alpha^\Hermaphrodite/2
 \end{split}
@@
 \begin{split}
-X_{ma}^{d'}=&xx_{44}^{d,s}+xx_{34}^{d,s}/2+(xx_{14}^{d,s}+xx_{24}^{d,s})\alpha^d\\
-&-R(xx_{14}^{d,s}-xx_{23}^{d,s}) \alpha^d\\
-&(xy_{44}^{d,s}+xy_{42}^{d,s})/2+(xy_{41}^{d,s}+xy_{43}^{d,s})(1-\alpha^d)\\
-&- r(xy_{43}^{d,s}-xy_{34}^{d,s})(1-\alpha^d) - \chi(xy_{42}^{d,s}-xy_{24}^{d,s})/2\\
-&+\big{\{}-(R+r+\chi)xy_{41}^{d,s}+(r+\chi-R)xy_{14}^{d,s}\\
-&+(R+r-\chi) xy_{32}^{d,s}+(R+\chi-r)xy_{23}^{d,s}\big{\}}(1-\alpha^d)/2
+X_{ma}^{{\Hermaphrodite}'}=&xx_{44}^{\Hermaphrodite,s}+xx_{34}^{\Hermaphrodite,s}/2+(xx_{14}^{\Hermaphrodite,s}+xx_{24}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
+&-R(xx_{14}^{\Hermaphrodite,s}-xx_{23}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
+&(xy_{44}^{\Hermaphrodite,s}+xy_{42}^{\Hermaphrodite,s})/2+(xy_{41}^{\Hermaphrodite,s}+xy_{43}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite)\\
+&- r(xy_{43}^{\Hermaphrodite,s}-xy_{34}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite) - \chi(xy_{42}^{\Hermaphrodite,s}-xy_{24}^{\Hermaphrodite,s})/2\\
+&+\big{\{}-(R+r+\chi)xy_{41}^{\Hermaphrodite,s}+(r+\chi-R)xy_{14}^{\Hermaphrodite,s}\\
+&+(R+r-\chi) xy_{32}^{\Hermaphrodite,s}+(R+\chi-r)xy_{23}^{\Hermaphrodite,s}\big{\}}(1-\alpha^\Hermaphrodite)/2
 \end{split}
@@
 \begin{split}
-Y_{MA}^{d'}=&yy_{11}^{d,s}+yy_{13}^{d,s}/2+(yy_{12}^{d,s}+yy_{14}^{d,s})\alpha^d\\
-&-R(yy_{14}^{d,s}-yy_{23}^{d,s}) \alpha^d\\
-&(xy_{11}^{d,s}+xy_{31}^{d,s})/2+(xy_{21}^{d,s}+xy_{41}^{d,s})\alpha^d\\
-&- r(xy_{21}^{d,s}-xy_{12}^{d,s})\alpha^d - \chi(xy_{31}^{d,s}-xy_{13}^{d,s})/2\\
-&+\big{\{} - (R+r+\chi)xy_{41}^{d,s} + (r+\chi-R)xy_{14}^{d,s}\\
-& + (R+r-\chi)xy_{32}^{d,s} + (R+\chi-r) xy_{23}^{d,s}\big{\}}\alpha^d/2
+Y_{MA}^{{\Hermaphrodite}'}=&yy_{11}^{\Hermaphrodite,s}+yy_{13}^{\Hermaphrodite,s}/2+(yy_{12}^{\Hermaphrodite,s}+yy_{14}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
+&-R(yy_{14}^{\Hermaphrodite,s}-yy_{23}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
+&(xy_{11}^{\Hermaphrodite,s}+xy_{31}^{\Hermaphrodite,s})/2+(xy_{21}^{\Hermaphrodite,s}+xy_{41}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
+&- r(xy_{21}^{\Hermaphrodite,s}-xy_{12}^{\Hermaphrodite,s})\alpha^\Hermaphrodite - \chi(xy_{31}^{\Hermaphrodite,s}-xy_{13}^{\Hermaphrodite,s})/2\\
+&+\big{\{} - (R+r+\chi)xy_{41}^{\Hermaphrodite,s} + (r+\chi-R)xy_{14}^{\Hermaphrodite,s}\\
+& + (R+r-\chi)xy_{32}^{\Hermaphrodite,s} + (R+\chi-r) xy_{23}^{\Hermaphrodite,s}\big{\}}\alpha^\Hermaphrodite/2
 \end{split}
@@
 \begin{split}
-Y_{Ma}^{d'}=&yy_{22}^{d,s}+yy_{24}^{d,s}/2+(yy_{12}^{d,s}+yy_{23}^{d,s})\alpha^d\\
-&-R(yy_{23}^{d,s}-yy_{14}^{d,s}) \alpha^d\\
-&(xy_{22}^{d,s}+xy_{42}^{d,s})/2+(xy_{12}^{d,s}+xy_{32}^{d,s})(1-\alpha^d)\\
-&- r(xy_{12}^{d,s}-xy_{21}^{d,s})(1-\alpha^d) - \chi(xy_{42}^{d,s}-xy_{24}^{d,s})/2\\
-&+\big{\{}-(R+r+\chi)xy_{32}^{d,s} +(r+\chi-R) xy_{23}^{d,s}\\
-&+(R+r-\chi)xy_{41}^{d,s}+(R+\chi-r)xy_{14}^{d,s}\big{\}}(1-\alpha^d)/2
+Y_{Ma}^{{\Hermaphrodite}'}=&yy_{22}^{\Hermaphrodite,s}+yy_{24}^{\Hermaphrodite,s}/2+(yy_{12}^{\Hermaphrodite,s}+yy_{23}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
+&-R(yy_{23}^{\Hermaphrodite,s}-yy_{14}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
+&(xy_{22}^{\Hermaphrodite,s}+xy_{42}^{\Hermaphrodite,s})/2+(xy_{12}^{\Hermaphrodite,s}+xy_{32}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite)\\
+&- r(xy_{12}^{\Hermaphrodite,s}-xy_{21}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite) - \chi(xy_{42}^{\Hermaphrodite,s}-xy_{24}^{\Hermaphrodite,s})/2\\
+&+\big{\{}-(R+r+\chi)xy_{32}^{\Hermaphrodite,s} +(r+\chi-R) xy_{23}^{\Hermaphrodite,s}\\
+&+(R+r-\chi)xy_{41}^{\Hermaphrodite,s}+(R+\chi-r)xy_{14}^{\Hermaphrodite,s}\big{\}}(1-\alpha^\Hermaphrodite)/2
 \end{split}
@@
 \begin{split}
-Y_{mA}^{d'}=&yy_{33}^{d,s}+yy_{13}^{d,s}/2+(yy_{23}^{d,s}+yy_{34}^{d,s})\alpha^d\\
-&-R(yy_{23}^{d,s}-yy_{14}^{d,s}) \alpha^d\\
-&(xy_{33}^{d,s}+xy_{13}^{d,s})/2+(xy_{23}^{d,s}+xy_{43}^{d,s})\alpha^d\\
-&- r(xy_{43}^{d,s}-xy_{34}^{d,s})\alpha^d - \chi(xy_{13}^{d,s}-xy_{31}^{d,s})/2\\
-&+\big{\{}-(R+r+\chi)xy_{23}^{d,s} +(r+\chi-R)xy_{32}^{d,s}\\
-&+(R+r-\chi) xy_{14}^{d,s} + (R+\chi-r) xy_{41}^{d,s}\big{\}}\alpha^d/2
+Y_{mA}^{{\Hermaphrodite}'}=&yy_{33}^{\Hermaphrodite,s}+yy_{13}^{\Hermaphrodite,s}/2+(yy_{23}^{\Hermaphrodite,s}+yy_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
+&-R(yy_{23}^{\Hermaphrodite,s}-yy_{14}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
+&(xy_{33}^{\Hermaphrodite,s}+xy_{13}^{\Hermaphrodite,s})/2+(xy_{23}^{\Hermaphrodite,s}+xy_{43}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
+&- r(xy_{43}^{\Hermaphrodite,s}-xy_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite - \chi(xy_{13}^{\Hermaphrodite,s}-xy_{31}^{\Hermaphrodite,s})/2\\
+&+\big{\{}-(R+r+\chi)xy_{23}^{\Hermaphrodite,s} +(r+\chi-R)xy_{32}^{\Hermaphrodite,s}\\
+&+(R+r-\chi) xy_{14}^{\Hermaphrodite,s} + (R+\chi-r) xy_{41}^{\Hermaphrodite,s}\big{\}}\alpha^\Hermaphrodite/2
 \end{split}
@@
 \begin{split}
-Y_{ma}^{d'}=&yy_{44}^{d,s}+yy_{34}^{d,s}/2+(yy_{14}^{d,s}+yy_{24}^{d,s})\alpha^d\\
-&-R(yy_{14}^{d,s}-yy_{23}^{d,s}) \alpha^d\\
-&(xy_{44}^{d,s}+xy_{24}^{d,s})/2+(xy_{14}^{d,s}+xy_{34}^{d,s})(1-\alpha^d)\\
-&- r(xy_{34}^{d,s}-xy_{43}^{d,s})(1-\alpha^d) - \chi(xy_{24}^{d,s}-xy_{42}^{d,s})/2\\
-&+\big{\{}-(R+r+\chi) xy_{14}^{d,s} + (r+\chi-R)xy_{41}^{d,s}\\
-&+(R+r-\chi) xy_{23}^{d,s} + (R+\chi-r) xy_{32}^{d,s}\big{\}}(1-\alpha^d)/2
+Y_{ma}^{{\Hermaphrodite}'}=&yy_{44}^{\Hermaphrodite,s}+yy_{34}^{\Hermaphrodite,s}/2+(yy_{14}^{\Hermaphrodite,s}+yy_{24}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
+&-R(yy_{14}^{\Hermaphrodite,s}-yy_{23}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
+&(xy_{44}^{\Hermaphrodite,s}+xy_{24}^{\Hermaphrodite,s})/2+(xy_{14}^{\Hermaphrodite,s}+xy_{34}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite)\\
+&- r(xy_{34}^{\Hermaphrodite,s}-xy_{43}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite) - \chi(xy_{24}^{\Hermaphrodite,s}-xy_{42}^{\Hermaphrodite,s})/2\\
+&+\big{\{}-(R+r+\chi) xy_{14}^{\Hermaphrodite,s} + (r+\chi-R)xy_{41}^{\Hermaphrodite,s}\\
+&+(R+r-\chi) xy_{23}^{\Hermaphrodite,s} + (R+\chi-r) xy_{32}^{\Hermaphrodite,s}\big{\}}(1-\alpha^\Hermaphrodite)/2
 \end{split}
@@
 However, some diploid types are not produced under a given sex determination system. 
-For example, with the $M$ allele fixed and ancestral $XY$ sex determination, there are no $XX$ males, $XY$ females, or $YY$ females ($xx_{11}^{m}$, $xx_{12}^{m}$, $xx_{22}^m$, $xy_{11}^{f}$, $xy_{12}^{f}$, $xy_{22}^f$, $yy_{11}^{f}$, $yy_{12}^{f}$, and $yy_{22}^f$ are all 0).
+For example, with the $M$ allele fixed and ancestral $XY$ sex determination, there are no $XX$ males, $XY$ females, or $YY$ females ($xx_{11}^{\male}$, $xx_{12}^{\male}$, $xx_{22}^\male$, $xy_{11}^{\female}$, $xy_{12}^{\female}$, $xy_{22}^\female$, $yy_{11}^{\female}$, $yy_{12}^{\female}$, and $yy_{22}^\female$ are all 0).
 In this case, the system only involves six recursion equations because there is only one \textbf{M} locus allele and no Y-bearing female gametes. 
 This six-equation system yields equilibrium \eqref{eq:pAve}. 
-Within this resident population (when $m$ is absent) we describe frequencies among different gamete types, which are given by $X_{MA}^{f}=p_{Xf}$, $X_{Ma}^{f}=(1-p_{Xf})$, $X_{MA}^{m}=(1-q)p_{Xm}$, $X_{Ma}^{m}=(1-q)(1-p_{Xm})$, $Y_{MA}^{m}=q p_{Ym}$, and $Y_{Ma}^{m}=q(1-p_{Ym})$.
+Within this resident population (when $m$ is absent) we describe frequencies among different gamete types, which are given by $X_{MA}^{\female}=p_{Xf}$, $X_{Ma}^{\female}=(1-p_{Xf})$, $X_{MA}^{\male}=(1-q)p_{Xm}$, $X_{Ma}^{\male}=(1-q)(1-p_{Xm})$, $Y_{MA}^{\male}=q p_{Ym}$, and $Y_{Ma}^{\male}=q(1-p_{Ym})$.
 

### 2017-01-28 LaTeX/Turnover.tex

@@
 
-\title{Gametic Selection, Sex Ratio Bias, and Transitions Between Sex Determination Systems}
+\title{Gametic Selection, Meiotic Drive, Sex Ratio Bias, and Transitions Between Sex Determination Systems}
 \author{Michael F Scott$*^1$ and Matthew M Osmond$*^2$, and Sarah P Otto$^2$}
@@
 Sex determination systems are remarkably dynamic; many studied taxa display transitions of sex-determining genes between chromosomes or the evolution of entirely new sex-determining systems. 
-%Predominant theories in which new sex-determining systems are favoured by selection involve sex ratio selection or fitness differences between sexes (e.g., sexually antagonistic selection). 
-Here, we utilize population genetic models to study the spread of novel sex-determiners in systems with 
-%a period of selection during the haploid stage produced by one sex, e.g., pollen or sperm competition. 
-haploid gametic selection, e.g., pollen or sperm competition.
-Haploid selected loci experience a form of sex-specific selection (because gametic competition occurs predominantly among haploids produced by males) and can cause sex ratios at birth to become biased (because sex ratios are determined by the fertilization success of X- versus Y-bearing pollen/sperm).
-%We find that the evolution of sex determination systems where mothers determine sex at birth (e.g., environmental sex determination where sex is determined at birth) is influenced by classic Fisherian sex ratio selection.
-{\color{red}(Maybe not true???)}
-%However, notably, we find that the spread of new genetic sex determination systems is not affected by sex ratio biases that are caused by gametic selection because sex ratios become biased after parental provisioning has occurred (even if pollen/sperm competition occurs within the mother).
-Notably, we find that the spread of new genetic sex determination systems is not affected by sex ratio biases that are caused by haploid competition or meiotic drive. 
-In addition, we find that linkage of an ancestral sex chromosome to a locus under haploid selection can favour transitions between male and female heterogamety (e.g., XY to ZW), which is not the case for any forms of diploid sex specific selection (e.g., sexually antagonistic selection).
-During these transitions, new sex-determining alleles spread despite breaking up favourable associations that build up between ancestral sex-determining loci and selected loci, reducing population mean fitness.
+Predominant theories in which new sex-determining systems are favoured by selection involve sex ratio selection or sex-specific selection (e.g., sexually antagonistic selection). 
+Here, we utilize population genetic models to study the spread of novel sex-determiners when there is a period of sex-specific haploid selection. 
+Many loci experience selection on their haploid genotypes during gametic competition (e.g., pollen/sperm competition) or meiosis (i.e., meiotic drive). 
+Haploid selected loci typically experience a form of sex-specific selection because meiotic drive and/or gametic competition occurs predominantly in one sex or the other. 
+In addition, haploid selection can cause the zygotic sex ratio to become biased because sex ratios are determined by the fertilization success of X- versus Y-bearing pollen/sperm. 
+Notably, we find that the spread of new genetic sex determination systems is not affected by sex ratio biases that are caused by haploid selection. 
+In addition, we find that, with haploid selection, transitions between male and female heterogamety (XY to ZW or ZW to XY) can occur despite breaking up favourable associations the between ancestral sex-determining locus and selected loci.
+These transitions occur because an unlinked neo-Y (neo-W) can have higher fitness in males (females), even if the population mean fitness is reduced. 
+Such transitions are not possible with diploid selection alone, in which case tighter linkage increases the fitness of both males and females. 
 Furthermore, a period of selection among haploids can favour the stable maintenance of polymorphic sex determination systems. 
 Thus, our models offer several new insights to be explored as information about sex determination in non-model taxa accumulates.
-
-%[Approx 320 words]
 \end{abstract}
@@
 
+%Mine Brandvain & coop for citations, and mention their paper (recombination modifiers drive). Has lots of citations for male/female specific drivers. 
 %CHECK THROUGHOUT: use of sex-determination SYSTEMS versus MECHANISMS.
@@
 
-Brief results summary.
+If there is genetic variation maintained by sexually-antagonistic selection, new sex-determining systems can evolve. 
+In particular, transitions to new sex-determining systems can occur when new sex-determining regions are more closely linked to a sexually antagonistic locus.
+Here, we show that, genetic variation at loci that experience haploid selection can also generate selection in favour of new sex-determining systems. 
+Closer linkage can again favour transitions to new sex-determining systems. 
+However, with haploid selection, heterogametic transitions (XY to ZW or ZW to XY) can also occur when the new sex-determining region is less closely linked to the locus under selection.
 
@@
 Within this resident population (when $m$ is absent) we describe frequencies among different gamete types, which are given by $X_{MA}^{\female}=p_{Xf}$, $X_{Ma}^{\female}=(1-p_{Xf})$, $X_{MA}^{\male}=(1-q)p_{Xm}$, $X_{Ma}^{\male}=(1-q)(1-p_{Xm})$, $Y_{MA}^{\male}=q p_{Ym}$, and $Y_{Ma}^{\male}=q(1-p_{Ym})$.
+In this resident population, the mean fitnesses are given in table \ref{tab:meanfitnesses}.
+
+\begin{table}[ht]
+\centering
+\smallskip
+\caption{mean fitnesses in resident ($M$ fixed, XY sex determination) }
+\begin{tabular}{l l }
+\hline\hline
+  Sex \& Life Cycle Stage & Mean Fitness \\ [0.5ex] \hline  \noalign{\vskip 0.5ex}
+  female gametes ($\bar{w}_H^\female$) & 
+  $p_X^\female w_A^\female + (1-p_X^\female) w_a^\female$ \\ [0.5ex] \hline  \noalign{\vskip 0.5ex}
+  male gametes ($\bar{w}_H^\male$) & 
+  $\bar{p}^{\male} w_A^\male + (1-\bar{p}^{\male}) w_a^\male$ \\ [0.5ex] \hline  \noalign{\vskip 0.5ex}
+  females ($\bar{w}^\female$) & 
+  $\begin{array}{l}  \{ p_X^\female w_A^\female (1-q) p_X^\male w_A^\male w_{AA}^\female + \\
+  (1 - p_X^\female) w_a^\female (1-q) p_X^\male w_A^\male w_{Aa}^\female + \\
+  p_X^\female w_A^\female (1-q) (1 - p_X^\male) w_a^\male w_{Aa}^\female + \\
+  (1-p_X^\female) w_a^\female (1-q) (1 - p_X^\male) w_a^\male w_{aa}^\female \} / \{ \bar{w}_H^\female \bar{w}_H^\male\}
+  \end{array} 
+  $ \\ [0.5ex] \hline  \noalign{\vskip 0.5ex}
+  males ($\bar{w}^\male$) & 
+  $\begin{array}{l} \{ p_X^\female w_A^\female q p_Y^\male w_A^\male w_{AA}^\male + \\
+  (1 - p_X^\female) w_a^\female q p_Y^\male w_A^\male w_{Aa}^\male + \\
+  p_X^\female w_A^\female q (1 - p_Y^\male) w_a^\male w_{Aa}^\male + \\
+  (1-p_X^\female) w_a^\female q (1 - p_Y^\male) w_a^\male w_{aa}^\male \} / \{ \bar{w}_H^\male \bar{w}_H^\male\} 
+  \end{array}
+  $ \\ [0.5ex]  \noalign{\vskip 0.5ex}
+  \hline \hline
+  \label{tab:meanfitnesses}
+ \end{tabular}
+\end{table}
 

### 2017-01-31 LaTeX/Turnover.tex
paragraph added to discussion, some mentions of drive added to intro/abstract

@@
 
+Linkage between a locus that experiences haploid selection and a sex-determining region causes zygotic sex ratios to become biased \textcolor{red}{(REFERENCES)}, which we might then expect to exert sex ratio selection upon new modifiers.
 Fisherian sex ratio selection follows from the fact that, for an autosomal locus, half of the genetic material is inherited from a male, and half from a female. 
@@
 Even mutants that are equally likely to be found in males or females, such as an environmental sex determination mutation (equation \ref{eq:lambda_ESD}), are not strictly autosomal if they determine sex.
-Thus, despite the fact that sex ratio biases caused by haploid competition or meiotic drive have been shown to exert selection on various autosomal modifiers \citep{Stalker:1961th,Smith:1975ft,Frank:1989vl,Hough:2013uo,Ubeda:2015fx, Otto:2015va}, we do not find evidence that Fisherian sex ratio selection acting upon neo-sex-determination systems (e.g., see Figure \ref{fig:Combination_Turnover}).
+Thus, despite the fact that sex ratio biases caused by haploid competition or meiotic drive have been shown to exert selection on various autosomal modifiers \citep{Stalker:1961th,Smith:1975ft,Frank:1989vl,Hough:2013uo,Ubeda:2015fx, Otto:2015va}, we do not find evidence of Fisherian sex ratio selection acting upon neo-sex-determination systems (e.g., see Figure \ref{fig:Combination_Turnover}).
 

### 2017-01-31 LaTeX/Turnover.tex
added paragraph to discussion

--- 2017-01-28 LaTeX/Turnover.tex
@@
 
-%Mine Brandvain & coop for citations, and mention their paper (recombination modifiers drive). Has lots of citations for male/female specific drivers. 
 %CHECK THROUGHOUT: use of sex-determination SYSTEMS versus MECHANISMS.
@@
 %\textcolor{red}{We add haploid selection:}
-
-Here, we use mathematical models to find the conditions under which new sex determination systems are favoured by selection when there is a period of selection among haploid gametes/gametophytes. 
-Selection among haploid genotypes is thought to occur primarily among pollen/sperm, which can compete whenever there are more pollen/sperm than required for fertilization \citep{Mulcahy:1996ha,JOSEPH:2004haa}.
-Haploid selection may be particularly common in plants, in which 60-70\% of all genes are expressed in the male gametophyte and these genes exhibit stronger signatures of selection than random genes \citep{Borg:2009jpa,Arunkumar:2013iq,Gossmann:2014dua}.
+Here, we use mathematical models to find the conditions under which new sex determination systems are favoured when loci experience haploid selection. 
+Haploid genotypes at many loci experience selection during gamete competition and/or meiotic drive \citep{Mulcahy:1996ha,JOSEPH:2004haa}.
+Competition among gametes/gametophytes (e.g., sperm/pollen competition) is distinct from meiotic drive because drive only occurs among heterozygotes whereas gametes from homozygous parents can participate in gamete competition.
+We use the term `haploid selection' to encompass both proceses. 
+Meiotic drive refers to the biased (non-mendelian) segregation of genotypes during gamete production and is almost always sex-specific, e.g., occurring either during the production of male or female gametes only \textcolor{red}{(Ubeda and Haig, 2005; Lindholm et al.
+2016)}.
+Because there are typically more pollen/sperm than required for fertilization, haploid competition is also typically sex specific, occurring primarily among male gametes.
+Haploid competition may be particularly common in plants, in which 60-70\% of all genes are expressed in the male gametophyte and these genes exhibit stronger signatures of selection than random genes \citep{Borg:2009jpa,Arunkumar:2013iq,Gossmann:2014dua}.
 In addition, artificial selection pressures applied to male gametophytes cause the frequency of resistant alleles to increase \citep[e.g.,][]{Hormaza:1996cv,Ravikumar:2003uo,Hedhly:2004iv,Clarke:2004ir}.
-A smaller (but non-negligible) proportion of genes are thought to be expressed and selected in animal sperm, although precise estimates are uncertain \citep{Zheng:2001fi,JOSEPH:2004haa,Vibranovski:2010et}.
-\textcolor{red}{add something about meiotic drive here?}
+A smaller (but non-negligible) proportion of genes are thought to be expressed and selected during competition in animal sperm, although precise estimates are uncertain \citep{Zheng:2001fi,JOSEPH:2004haa,Vibranovski:2010et}.
 
 There are various ways in which a period of haploid selection could influence transitions between sex determination systems. 
-Firstly, if we assume that haploid selection at any particular locus predominantly occurs in one sex (e.g., pollen/sperm competition), then such loci experience a form of sex-specific selection. 
+Firstly, if we assume that haploid selection at any particular locus predominantly occurs in one sex (e.g., meiotic drive during spermatogenesis or pollen/sperm competition), then such loci experience a form of sex-specific selection.
 In this respect, we might expect that haploid selection might affect transitions between sex determination systems in a similar manner to sex-specific diploid selection \citep[as explored by][]{vanDoorn:2007eu,vanDoorn:2010hu}.
-That is, new masculizing mutations (neo-Y chromosomes) could be favoured via linkage associations with alleles that are beneficial in pollen/sperm. 
-However, sex ratios can also become biased if there is linkage between the sex-determining region and a locus that harbours genetic variation in haploid fitness. 
-For example, differences in fitness between X- and Y-bearing pollen tubes can cause the sex ratio among seeds to become biased when there is pollen competition \citep{Lloyd:1974tz,Conn:1981uw,Stehlik:2005ul,Stehlik:2006to,Field:2012fd,Field:2013cc}.
-It is not immediately clear how the spread of new sex determination systems would be influenced by the combination of sex ratio biases and favourable associations between haploid selected loci and sex-determining regions.
+That is, new masculizing mutations (neo-Y chromosomes) could be favoured via linkage associations with alleles that are beneficial in the male haploid stage. 
+However, sex ratios can also become biased by linkage between the sex-determining region and a locus that harbours genetic variation in haploid fitness. 
+For example, there are several known cases of sex ratio bias caused by sex-linked meiotic drive alleles \citep[][, Chapter 3]{Burt:2006} or selection among X- and Y-bearing pollen \citep{Lloyd:1974tz,Conn:1981uw,Stehlik:2005ul,Stehlik:2006to,Field:2012fd,Field:2013cc}.
+It is not immediately clear how the spread of new sex determination systems would be influenced by the combination of sex ratio biases and associations between haploid selected loci and sex-determining regions.
 
@@
 This does not occur in models that do not include haploid selection.
-
-\textcolor{red}{NOTE RE: DRIVE.
-I expect drive (that occurs specifically in one sex, e.g., during spermatogenesis) to behave almost exactly like haploid selection.
-That is, I think that a XY-linked driver that is maintained by selection (e.g., because it causes sterility when homozygous, which is common in known drive systems) will only favour invasion of a more tightly linked neo-Y (worsening sex ratio biases) and could favour invasion of a neo-W.
-This may run counter to generic expectations from new sex chromosome systems evolving to balance the sex ratio.
-So, do you think it would significantly enhance the paper to model drive explicitly or just discuss it as being similar???}
-
-{\color{blue} 
-FOR RESULTS?
-
-FROM PREVIOUS PAPER:
-The maintenance of polymorphism at loci that experience sex specific selection in both haploid and diploid phases was considered by Immler et al.
-\cite{Immler:2012tl}, demonstrating that polymorphisms can be maintained by sexually antagonistic selection or overdominance as well as by conflicting selection pressures in haploids and diploids (haploid-diploid conflict or ploidally antagonistic selection) or a combination of these selective regimes.
-}
 
@@
 Where there is no meiotic drive and haploid competition occurs in one sex only, an unlinked neo-W can invade as long as the same allele is favoured in male and female diploid selection and there are sex differences in selection of one type ($-s^\female(s^\female-s^\male)>0$, see Figure \ref{fig:Combination_Centimorgans}C,D), which is 25\% of the parameter space.
-These special cases indicate that neo-W invasion when $R>r$ can occur for a relatively large fraction of parameter space.
+These special cases indicate that neo-W invasion can occur for a relatively large fraction of parameter space, even if $R>r$.
 
@@
 If there is genetic variation maintained by sexually-antagonistic selection, new sex-determining systems can evolve. 
-In particular, transitions to new sex-determining systems can occur when new sex-determining regions are more closely linked to a sexually antagonistic locus.
-Here, we show that, genetic variation at loci that experience haploid selection can also generate selection in favour of new sex-determining systems. 
-Closer linkage can again favour transitions to new sex-determining systems. 
+In particular, transitions to new sex-determining systems can occur when new sex-determining regions are more closely linked to a sexually-antagonistic locus.
+Here, we show that genetic variation at loci that experience haploid selection can also generate selection in favour of new sex-determining systems. 
+Closer linkage can again favour new sex-determining alleles. 
 However, with haploid selection, heterogametic transitions (XY to ZW or ZW to XY) can also occur when the new sex-determining region is less closely linked to the locus under selection.
+
+Neo-W (neo-Y) alleles invade when their fitness in females (males) is greater than the mean fitness of females (males) under the ancestral sex determination system.
+With sexually antagonistic selection (between diploid sexes) only, linkage between a selected locus and the sex-determining region strengthens associations between male beneficial alleles and the male-determining allele (Y or Z) and between female beneficial alleles and the female-determining allele (X or W).
+Thus, the mean fitness of both males and females increases with closer linkage to the sex-determining region. 
+Therefore, new sex-determining alleles only invade if they are more closely linked than the ancestral sex-determining region. 
+However, if there is haploid selection on loci linked to an XY (ZW) sex-determining region, there are equilibria for which the mean fitness of females (males) or males is lower than it would be without sex-linkage, allowing unlinked neo-W (neo-Y) alleles to invade, see figure \ref{fig:Combination_MeanFit}.
 
@@
 
-DRAFT (improve): In \citet{Ubeda:2015fx}, the new sex determining locus spreads because it arises in linkage with a locus that experiences drive.
+%DRAFT (improve): In \citet{Ubeda:2015fx}, the new sex determining locus spreads because it arises in linkage with a locus that experiences drive.
 They assume that drive occurs predominantly in one sex, e.g., during spermatogenesis or a 'killer' sperm.
@@
 Y chromosomes that arise in linkage with the driving allele spread because they allow drive to occur more often, thus genetic sex determination with a sex ratio bias evolves.
-Thus \citet{Ubeda:2015fx} also find that genetic sex determiners can invade, despite causing sex ratios to become biased. 
-Finally, they show that autosomal 'restorers' that negate the effects of meiotic drive can invade and restore an equal sex ratio.
+%Thus \citet{Ubeda:2015fx} also find that genetic sex determiners can invade, despite causing sex ratios to become biased. 
+%Finally, they show that autosomal 'restorers' that negate the effects of meiotic drive can invade and restore an equal sex ratio.
 
@@
 
+Evolutionary events, such as the transition between one sex-determination system and another, are generally difficult to observe directly. 
+One observation would be the presence of sexually antagonistic variation linked to neo-sex chromosomes - example from cichlids (debated, i believe). 
+Our model could be examined in a similar manner, although we find that genes that experience haploid selection that are near either the neo- or ancestral-sex-determining locus could have been involved in favouring a transition between sex-determining systems.
+
+A complementary method of investigating evolutionary transitions is via comparative methods. 
 Taken at face value, our results indicate that transitions in heterogametey (XY to ZW or vice versa) are more likely to be favoured by selection if there is selection upon both haploid and diploid genotypes rather than diploid selection alone.

### 2017-02-01 LaTeX/Turnover.tex
matt got to eqn 5 and 6 in text

@@
 
-\subsection*{Sex chromosome turnover}
-The evolution of a new sex determination system requires that a rare mutant, $m$, at the novel sex-determining locus  increases in frequency when rare. 
+\subsection*{Turnover between sex-determination systems} 
+The evolution of a new sex determination system requires that a rare mutant allele, $m$, at the novel sex-determining locus  increases in frequency when rare. 
 The spread of a rare mutant $m$ at the \textbf{M} locus is determined by the leading eigenvalue, $\lambda$, of the system described by the next generation frequency of eggs and sperm carrying the mutation, (\ref{eq:recursions}c), (\ref{eq:recursions}d), (\ref{eq:recursions}g), (\ref{eq:recursions}h), which is an eight equation system.
@@
 %Thus, the system describing the change in frequency of the $m$ allele consists of eight recursion equations. 
-Dominant neo-Y chromosomes (when $k=0$) or neo-W chromosomes (when $k=1$) are only found in male diploids (neo-Y) or female diploids (neo-W) such that their growth rate ultimately depends only on the change in frequency of $m$-bearing gametes produced by males (for a neo-Y) or by females (for a neo-W).
+Dominant neo-Y (when $k=0$) or neo-W alleles (when $k=1$) are only found in male diploids (neo-Y) or female diploids (neo-W) such that their growth rate ultimately depends only on the change in frequency of $m$-bearing gametes produced by males (for a neo-Y) or by females (for a neo-W).
 Furthermore, if the $m$ allele is fully dominant over the ancestral sex-determining system, phenotypes are not affected by the genotype at the ancestral sex-determining region (\textbf{X} locus). 
-Therefore, the invasion of rare mutant neo-Y or neo-W chromosomes can be simplified and given by the largest eigenvalue that solves the quadratic characteristic polynomial
+Therefore, the invasion of rare mutant neo-Y or neo-W alleles can be simplified and given by the largest eigenvalue that solves the quadratic characteristic polynomial
 
@@
 \smallskip
-\caption{Parameters determining invasion (equation \ref{eq:charpoly_neoY}) for neo-Y or neo-W chromosomes}
+\caption{Parameters determining invasion (equation \ref{eq:charpoly_neoY}) for neo-Y or neo-W alleles}
 \begin{tabular}{l}
@@
    neo-Y ($k=0$) \\ [0.5ex] \hline \noalign{\vskip 1ex}
-  $\lambda_{mA}=\{p_{X}^{\female} w_{A}^{\female} w_{A}^{\male} w_{AA}^{\male}+(1-p_{X}^{\female}) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male}\alpha^\male(1-R)\}/ \{ \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\male$ \} \\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\lambda_{mA}=\{p_{X}^{\female} w_{A}^{\female} w_{A}^{\male} w_{AA}^{\male}+(1-p_{X}^{\female}) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male}\alpha^\male(1-R)\}/ \{ \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\male\} $\\ [0.5ex] \noalign{\vskip 0.5ex}
   $\lambda_{ma}=\{(1-p_{X}^{\female}) w_{a}^{\female} w_{a}^{\male} w_{aa}^{\male}+p_{X}^{\female} w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male}(1-\alpha^\male)(1-R)\}/ \{ \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\male \}$ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\rho_{mA}=R \{(1-p_{X}^{\female}) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} (1-\alpha_{m})\}/ \{ \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\male \} $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\rho_{ma}=R\{p_{X}^{\female} w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male} \alpha_{m}\}/ \{ \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\male \}$\\ [1ex] \hline 
+  $\rho_{mA}=R (1-p_{X}^{\female}) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} (1-\alpha^{\male})/ \{ \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\male \} $\\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\rho_{ma}=R p_{X}^{\female} w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male} \alpha^{\male}/ \{ \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\male \}$\\ [1ex] \hline 
   \noalign{\vskip 0.5ex}
@@
   $\lambda_{ma}=\{(1-\bar{p}^{\male}) w_{a}^{\male} w_{a}^{\female} w_{aa}^{\female}+\bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female}(1-\alpha^\female)(1-R)\}/ \{\bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\female \}$ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\rho_{mA}=R \{(1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female} (1-\alpha_{f})\}/ \{\bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\female \} $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\rho_{ma}=R\{\bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female} \alpha_{f}\}/ \{\bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\female \}$\\ [1ex] 
+  $\rho_{mA}=R (1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female} (1-\alpha^{\female})/ \{\bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\female \} $\\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\rho_{ma}=R\bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female} \alpha^{\female}/ \{\bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\female \}$\\ [1ex] 
   \hline \hline 
@@
       \item $\bar{p}^{\male}=p_{Y}^{\male}q+p_{X}^{\male}(1-q)$ is the average frequency of the $A$ allele among X- and Y-bearing male gametes 
-      \item $\bar{w}_H^\female = p_X^\female w_A^\female + (1-p_X^\female) w_a^\female$ is the mean fitness of female gametes
-      \item $\bar{w}_H^\male = \bar{p}^{\male} w_A^\male + (1-\bar{p}^{\male}) w_a^\male$ is the mean fitness of male gametes
-       \item $\bar{w}^\female = \{ p_X^\female w_A^\female (1-q) p_X^\male w_A^\male w_{AA}^\female + (1 - p_X^\female) w_a^\female (1-q) p_X^\male w_A^\male w_{Aa}^\female + p_X^\female w_A^\female (1-q) (1 - p_X^\male) w_a^\male w_{Aa}^\female + (1-p_X^\female) w_a^\female (1-q) (1 - p_X^\male) w_a^\male w_{aa}^\female \} / \{ \bar{w}_H^\female \bar{w}_H^\male\}$ is the mean fitness of females
-       \item $\bar{w}^\male = \{ p_X^\female w_A^\female q p_Y^\male w_A^\male w_{AA}^\male + (1 - p_X^\female) w_a^\female q p_Y^\male w_A^\male w_{Aa}^\male + p_X^\female w_A^\female q (1 - p_Y^\male) w_a^\male w_{Aa}^\male + (1-p_X^\female) w_a^\female q (1 - p_Y^\male) w_a^\male w_{aa}^\male \} / \{ \bar{w}_H^\male \bar{w}_H^\male\}$ is the mean fitness of males
+      \item $\bar{w}_H^\female = p_X^\female w_A^\female + (1-p_X^\female) w_a^\female$ is the mean fitness of female gametes during haploid competition
+      \item $\bar{w}_H^\male = \bar{p}^{\male} w_A^\male + (1-\bar{p}^{\male}) w_a^\male$ is the mean fitness of male gametes during haploid competition
+       \item $\bar{w}^\female = \{ p_X^\female w_A^\female (1-q) p_X^\male w_A^\male w_{AA}^\female + (1 - p_X^\female) w_a^\female (1-q) p_X^\male w_A^\male w_{Aa}^\female + p_X^\female w_A^\female (1-q) (1 - p_X^\male) w_a^\male w_{Aa}^\female + (1-p_X^\female) w_a^\female (1-q) (1 - p_X^\male) w_a^\male w_{aa}^\female \} / \{ \bar{w}_H^\female \bar{w}_H^\male\}$ is the mean fitness of females during diploid competition
+       \item $\bar{w}^\male = \{ p_X^\female w_A^\female q p_Y^\male w_A^\male w_{AA}^\male + (1 - p_X^\female) w_a^\female q p_Y^\male w_A^\male w_{Aa}^\male + p_X^\female w_A^\female q (1 - p_Y^\male) w_a^\male w_{Aa}^\male + (1-p_X^\female) w_a^\female q (1 - p_Y^\male) w_a^\male w_{aa}^\male \} / \{ \bar{w}_H^\male \bar{w}_H^\male\}$ is the mean fitness of males during diploid competition
     \end{tablenotes}
@@
 Equation \eqref{eq:charpoly_neoY} and table \ref{tab:haplotype_growth} illustrate a number of key points about the invasion of neo-Y and neo-W mutations. 
-For a neo-Y, invasion depends on the relative \textcolor{red}{(is this right, is relative fitness divided by mean fitness or difference from 1???)} fitness of $A$-bearing and $a$-bearing male gametes (i.e., in sperm only, not eggs).
-The fitness of male gametes partly depends on the allele carried by the female gamete that they mate with (e.g., $A$ with probability $p_{X}^{\female} w_{A}^{\female}/\bar{w}_{H}^{\female}$).
-Similarly, invasion of a neo-W depends on the relative fitness of $A$-bearing and $a$-bearing female gametes. 
-However, in the case of a neo-W, the allele carried by the male gamete that they mate with can come from either an X-bearing or a Y-bearing sperm (e.g., $A$ with probability $\bar{p}^{\male} w_{A}^{\male}/\bar{w}_{H}^{\male}$, where $\bar{p}^{\male}=p_{Y}^{\male}q+p_{X}^{\male}(1-q)$).
+For a neo-Y, invasion depends on the relative lifetime fitness of $A$-bearing and $a$-bearing male gametes (i.e., in sperm only). 
+The lifetime fitness of male gametes partly depends on the allele carried by the female gamete that they mate with (e.g., $A$ with probability $p_{X}^{\female} w_{A}^{\female}/\bar{w}_{H}^{\female}$).
+Similarly, invasion of a neo-W depends on the relative lifetime fitness of $A$-bearing and $a$-bearing female gametes (i.e., in eggs only). 
+However, in the case of a neo-W, the allele carried by the male gamete that they mate with can come from either an X-bearing or a Y-bearing sperm (e.g., $A$ with probability $\bar{p}^{\male} w_{A}^{\male}/\bar{w}_{H}^{\male}$).
 In either case, the zygote will then develop as a female due to the presence of a neo-W. 
-By contrast, females that do not carry the neo-W, only result from matings with X-bearing sperm (e.g., matings with $A$-bearing sperm occur with probability $\bar{p}_{X}^{\male} w_{A}^{\male}/\bar{w}_{H}^{\male}$).
+By contrast, females that do not carry the neo-W only result from matings with X-bearing sperm (e.g., matings with $A$-bearing sperm occur with probability $\bar{p}_{X}^{\male} w_{A}^{\male}/\bar{w}_{H}^{\male}$).
 If the \textbf{A} locus is initially linked to the ancestral sex-determining locus, \textbf{X}, (i.e., $r<1/2$) the frequency of the $A$ allele among X- and Y-bearing sperm can differ (equation \ref{eq:freq_diffs}).
@@
 We are particularly concerned with whether or not a rare neo-sex-determining allele increases in frequency, which occurs when the largest eigenvalue, $\lambda$, that solves \eqref{eq:charpoly_neoY} is greater than one.
-If the average change in frequency of the two haplotypes that carry the $m$ allele ($Am$ and $am$) is positive, invasion will always occur (if $\left\{(\lambda_{mA}-1)+ (\lambda_{ma}-1) \right\}/2>0$, $\lambda>1$).
-If neither haplotype increases in frequency ($\lambda_{mA}, \lambda_{ma} < 1$ \textcolor{red}{is this notation valid?}), the $m$ allele will not invade. 
+If the average change in frequency of the two haplotypes that carry the $m$ allele ($Am$ and $am$) is positive, invasion will always occur (if $\left\{(\lambda_{mA}-1)+ (\lambda_{ma}-1) \right\}/2 > 0$, $\lambda > 1$).
+If neither haplotype increases in frequency ($\lambda_{mA}, \lambda_{ma} < 1$), the $m$ allele will not invade. 
 Otherwise, the new sex-determining allele increases in frequency on one \textbf{A} background and declines on the other, and invasion requires
@@
 R \left[ 
-\frac{p^\female_X w^\male_a (1-\alpha^\male)}{(\lambda_{mA}-1)\bar{w}_{H}^{\male}} + 
-\frac{(1 - p^\female_X) w^\male_A \alpha^\male \bar{w}_{H}^{\male}}{(\lambda_{ma}-1)\bar{w}_{H}^{\male}} \right] 
+\frac{p^\female_X w^\female_A w^\male_a (1-\alpha^\male)}{ \bar{w}^\female_H \bar{w}^\male_H (\lambda_{mA}-1)} + 
+\frac{(1 - p^\female_X) w^\female_a w^\male_A \alpha^\male}{ \bar{w}^\female_H \bar{w}^\male_H (\lambda_{ma}-1)} \right] 
 \frac{w^\male_{Aa}}{\bar{w}^\male} < 1,
@@
 R \left[ 
-\frac{(1 - \bar{p}^\male) w^\male_{a}}{(\lambda_{mA}-1)\bar{w}_{H}^{\male}} + 
-\frac{\bar{p}^\male w^\male_{A}}{(\lambda_{ma}-1)\bar{w}_{H}^{\male}} \right] 
-\frac{w^\female_{Aa}}{\bar{w}^\female} < 1
-\end{equation}
-
-\noindent
-\textcolor{red}{FIX THESE EQUATIONS...}
+\frac{\bar{p}^\male w^\male_A w^\female_a (1-\alpha^\female)}{ \bar{w}^\male_H \bar{w}^\female_H (\lambda_{mA}-1)} + 
+\frac{(1 - \bar{p}^\male) w^\male_a w^\female_A \alpha^\female}{ \bar{w}^\male_H \bar{w}^\female_H (\lambda_{ma}-1)} \right] 
+\frac{w^\male_{Aa}}{\bar{w}^\male} < 1,
+\end{equation}
+
+\noindent
+\textcolor{red}{FIX THESE EQUATIONS... i changed them a little, is this okay now? (mmo)}
 for the neo-$W$.
@@
 \begin{equation}
-\lambda_{ESD,XY} \approx 1 + \frac{1}{2}\frac{(\lambda_{Y,XY} - 1) + (\lambda_{W,XY} -1)}{2} \Big|_{R=1/2}
+\lambda_{ESD} \approx 1 + \frac{1}{2}\frac{(\lambda_{Y,XY} - 1) + (\lambda_{W,XY} -1)}{2} \Big|_{R=1/2},
 %V_A \frac{r}{1-2r}  \frac{s_{f} \left( s^\male - 3 s^\female\right) }{8 \left( s_{f} + s_{m} \right)^2} t_{m}^2.
@@
 \end{equation}
+which is the same for invasion into an ancestrally XY or ZW system.
 Thus with $k=1/2$ the neo-ESD gets half of the advantages of a neo-$W$ and half that of a neo-$Y$, but only has an effect one half of the time (the other half of the time it produces the same sex as the ancestral system would have).

### 2017-02-01 LaTeX/Turnover.tex
discussion reorganised

--- 2017-01-31 LaTeX/Turnover.tex
@@
 Here, we utilize population genetic models to study the spread of novel sex-determiners when there is a period of sex-specific haploid selection. 
-Many loci experience selection on their haploid genotypes during gametic competition (e.g., pollen/sperm competition) or meiosis (i.e., meiotic drive). 
-Haploid selected loci typically experience a form of sex-specific selection because meiotic drive and/or gametic competition occurs predominantly in one sex or the other. 
-In addition, haploid selection can cause the zygotic sex ratio to become biased because sex ratios are determined by the fertilization success of X- versus Y-bearing pollen/sperm. 
+Many loci experience sex-specific selection on their haploid genotypes during gametic competition (e.g., pollen/sperm competition) or meiosis (i.e., meiotic drive); selective processes that typically occur in one sex or the other.
+%Haploid selected loci typically experience a form of sex-specific selection because meiotic drive and/or gametic competition occurs predominantly in one sex or the other. 
+In addition, haploid selection can cause the zygotic sex ratio to become biased because sex ratios are determined by the production and fertilization success of X- versus Y-bearing pollen/sperm. 
 Notably, we find that the spread of new genetic sex determination systems is not affected by sex ratio biases that are caused by haploid selection. 
@@
 Haploid genotypes at many loci experience selection during gamete competition and/or meiotic drive \citep{Mulcahy:1996ha,JOSEPH:2004haa}.
-Competition among gametes/gametophytes (e.g., sperm/pollen competition) is distinct from meiotic drive because drive only occurs among heterozygotes whereas gametes from homozygous parents can participate in gamete competition.
-We use the term `haploid selection' to encompass both proceses. 
-Meiotic drive refers to the biased (non-mendelian) segregation of genotypes during gamete production and is almost always sex-specific, e.g., occurring either during the production of male or female gametes only \textcolor{red}{(Ubeda and Haig, 2005; Lindholm et al.
-2016)}.
-Because there are typically more pollen/sperm than required for fertilization, haploid competition is also typically sex specific, occurring primarily among male gametes.
+We use the term `meiotic drive' to refer to the biased (non-medelian) segregation of genotypes during gamete production and the term `gametic competition' to refer to selection upon haploid genotypes within a gamete/gametophyte pool; the term `haploid selection' encompasses both processes.
+Meiotic drive generally occurs either during the production of male or female gametes only \textcolor{red}{(Ubeda and Haig, 2005; Lindholm et al. 2016)}. 
+Because there are typically more pollen/sperm than required for fertilization, gametic competition is also typically sex specific, occurring primarily among male gametes.
 Haploid competition may be particularly common in plants, in which 60-70\% of all genes are expressed in the male gametophyte and these genes exhibit stronger signatures of selection than random genes \citep{Borg:2009jpa,Arunkumar:2013iq,Gossmann:2014dua}.
@@
 There are various ways in which a period of haploid selection could influence transitions between sex determination systems. 
-Firstly, if we assume that haploid selection at any particular locus predominantly occurs in one sex (e.g., meiotic drive during spermatogenesis or pollen/sperm competition), then such loci experience a form of sex-specific selection.
+Firstly, if we assume that haploid selection at any particular locus predominantly occurs in one sex (e.g., meiotic drive during spermatogenesis), then such loci experience a form of sex-specific selection.
 In this respect, we might expect that haploid selection might affect transitions between sex determination systems in a similar manner to sex-specific diploid selection \citep[as explored by][]{vanDoorn:2007eu,vanDoorn:2010hu}.
-That is, new masculizing mutations (neo-Y chromosomes) could be favoured via linkage associations with alleles that are beneficial in the male haploid stage. 
+That is, new masculizing mutations (neo-Y chromosomes) could be favoured via associations with alleles that are beneficial in the male haploid stage. 
 However, sex ratios can also become biased by linkage between the sex-determining region and a locus that harbours genetic variation in haploid fitness. 
@@
 %$w_{A}^\male$ and $w_{a}^\male$ for male gametes and $w_{A}^\female$ and $w_{a}^\female$ for female gametes, see table \ref{tab:fitnesstable}.
+We assume that all gametes compete for fertilization during haploid competition, which is not the case for monogamous mating systems where gametes from only one mating partner are present. 
+Haploid competition in monogamous mating systems is equivalent to meiotic drive in our model, which only alters the frequency of gametes produced by heterozygotes. 
 Random mating then occurs between male and female gametes.
@@
 
-If there is genetic variation maintained by sexually-antagonistic selection, new sex-determining systems can evolve. 
-In particular, transitions to new sex-determining systems can occur when new sex-determining regions are more closely linked to a sexually-antagonistic locus.
-Here, we show that genetic variation at loci that experience haploid selection can also generate selection in favour of new sex-determining systems. 
-Closer linkage can again favour new sex-determining alleles. 
-However, with haploid selection, heterogametic transitions (XY to ZW or ZW to XY) can also occur when the new sex-determining region is less closely linked to the locus under selection.
-
-Neo-W (neo-Y) alleles invade when their fitness in females (males) is greater than the mean fitness of females (males) under the ancestral sex determination system.
-With sexually antagonistic selection (between diploid sexes) only, linkage between a selected locus and the sex-determining region strengthens associations between male beneficial alleles and the male-determining allele (Y or Z) and between female beneficial alleles and the female-determining allele (X or W).
-Thus, the mean fitness of both males and females increases with closer linkage to the sex-determining region. 
-Therefore, new sex-determining alleles only invade if they are more closely linked than the ancestral sex-determining region. 
-However, if there is haploid selection on loci linked to an XY (ZW) sex-determining region, there are equilibria for which the mean fitness of females (males) or males is lower than it would be without sex-linkage, allowing unlinked neo-W (neo-Y) alleles to invade, see figure \ref{fig:Combination_MeanFit}.
-
+One might expect Fisherian sex ratio selection to influence the spread of new sex-determining systems because linkage between haploid selected loci and sex-determining regions cause biased zygotic sex ratios \citep{Hamilton:1967ts,Burt:2006,Field:2012fd,Field:2013cc}.
 Fisherian sex ratio selection follows from the fact that, for an autosomal locus, half of the genetic material is inherited from a male, and half from a female. 
@@
 Even mutants that are equally likely to be found in males or females, such as an environmental sex determination mutation (equation \ref{eq:lambda_ESD}), are not strictly autosomal if they determine sex.
-Thus, despite the fact that sex ratio biases caused by haploid competition or meiotic drive have been shown to exert selection on various autosomal modifiers \citep{Stalker:1961th,Smith:1975ft,Frank:1989vl,Hough:2013uo,Ubeda:2015fx, Otto:2015va}, we do not find evidence that Fisherian sex ratio selection acting upon neo-sex-determination systems (e.g., see Figure \ref{fig:Combination_Turnover}).
+Thus, despite the fact that sex ratio biases caused by haploid competition or meiotic drive have been shown to exert selection on various autosomal modifiers \citep{Stalker:1961th,Smith:1975ft,Frank:1989vl,Hough:2013uo,Ubeda:2015fx, Otto:2015va}, we do not find evidence of Fisherian sex ratio selection acting upon neo-sex-determination systems (e.g., see Figure \ref{fig:Combination_Turnover} and \citealt{Ubeda:2015fx}, in which a neo-Y invades despite biasing sex ratios).
+
+It has previously been demonstrated that new sex-determining systems can evolve if there is genetic variation maintained by sexually-antagonistic selection \citep{vanDoorn:2007eu,vanDoorn:2010hu}. 
+In particular, transitions to new sex-determining systems can occur when new sex-determining regions are more closely linked to a sexually-antagonistic locus.
+Our results show that genetic variation at loci that experience haploid selection can also generate selection in favour of new sex-determining systems. 
+New sex-determining allleles are again favoured if they are more closely linked with a locus under haploid selection.
+However, with haploid selection, heterogametic transitions (XY to ZW or ZW to XY) can also occur when the new sex-determining region is less closely linked to the locus under selection.
+
+Neo-W (neo-Y) alleles invade when their fitness in females (males) is greater than the mean fitness of females (males) under the ancestral sex determination system.
+With sexually antagonistic selection (between diploid sexes) only, linkage between a selected locus and the sex-determining region strengthens associations between male beneficial alleles and the male-determining allele (Y or Z) and between female beneficial alleles and the female-determining allele (X or W).
+Thus, the mean fitness of both males and females increases with closer linkage to the sex-determining region. 
+Therefore, new sex-determining alleles only invade if they are more closely linked than the ancestral sex-determining region. 
+However, if there is haploid selection on loci linked to an XY (ZW) sex-determining region, polymorphisms can be maintained at which the mean fitness of females (males) or males is lower than it would be without sex-linkage, allowing unlinked neo-W (neo-Y) alleles to invade, see figure \ref{fig:Combination_MeanFit}.
 
@@
 
-We only consider selection at the \textbf{A} locus, the sex-determining regions do not experience direct selection except via their associations with sex and \textbf{A} locus alleles. 
-However, in some cases, there may be significant degeneration around the sex-limited allele (Y or W) in the ancestral sex determining region.
-That is, recessive deleterious mutations and/or deletions may fix around the Y or W allele \citealt{Rice:1996ke,Charlesworth:2000cc,Bachtrog:2006ed,Marais:2008hm}).
-Degenerated Y could prevent fixation, this was studied by vD\&K 2010, which is why we didn't do it. 
-They note that YY lethality can prevent neo-W (and Y) fixing but that even very small amounts of recombination between X and Y can complete the process.
+We only consider selection at the \textbf{A} locus, i.e., sex-determining alleles are not directly selected except via their associations with sex and \textbf{A} locus alleles. 
+However, in some cases, there may be significant degeneration around the sex-limited allele (Y or W) in the ancestral sex determining region because recessive deleterious mutations and/or deletions may fix around the Y or W allele \citealt{Rice:1996ke,Charlesworth:2000cc,Bachtrog:2006ed,Marais:2008hm}).
+During heterogametic transitions (XY to ZW or ZW to XY), the formally sex-limited allele fixes (Figure \ref{fig:Combination_Turnover}) such that all individuals have YY or WW genotypes. 
+Any recessive deleterious alleles linked to the Y or W will therefore be revealed to selection during a heterogametic transition. 
+This phenomenon was studied by \citet{vanDoorn:2010hu}, who found that degeneration can prevent fixation of a neo-W or a neo-Y allele, leading to a mixed sex determination system where the ancestral- and neo- sex-determining loci are both polymorphic.
+However, they noted that very rare recombination events around the ancestral sex-determining region can allow these heterogametic transitions to complete.
+
+Our model of meiotic drive is very simple, involving a single locus with two alleles. 
+However, many meiotic drive systems involve an interaction with another locus at which alleles may `suppress' the action of meiotic drive. 
+Furthermore, in some cases, a driving allele may act by killing any gametes that carry a `target' allele at another locus, in which case the total number of gametes produced will be reduced (here, we assume total gamete number is not affected by drive).
+
+Mix pollen competition and sex-ratio affects in here?
+Kokko paper addresses some of these issues, but not related to sex-determination. 
+These feedbacks between population densities and meiotic drive or haploid competition for different sexual/mating systems deserve further attention.
+
+Here, we have not considered any population size dynamics
+
+Finally, \citet{Hamilton:1967ts} pointed out that biased sex ratios can affect population size because the number of offspring in each generation is typically determined by the number of females. 
+Population density can, in turn, affect the intensity of pollen/sperm competition in future generations because fewer males are available to donate pollen/sperm in a particular area. 
+Thus, a feedback could occur between population densities and haploid selection, which has not yet been investigated.
 
@@
 ``Polymorphism for sex-determining genes within or among populations has been reported in many species including houseflies, midges, woodlice, platyfish, cichlid fish, and frogs (Gordon, 1944; Kallman, 1970; Thomp-son, 1971; Macdonald, 1978; Bull, 1983; Rigaud et al., 1997; Caubet et al., 2000; Lande et al., 2001; Ogataet al., 2003; Lee et al., 2004; Mank et al., 2006).''
-
-We caution that our model of meiotic drive is very simple, involving a single locus with two alleles. 
-Many meiotic drive systems involve an interaction with another locus at which alleles may `suppress' the action of meiotic drive. 
-Furthermore, in some cases, a driving allele may act by killing any gametes that carry a `target' allele at another locus, in which case the total number of gametes produced will be reduced (here, we assume total gamete number is not affected by drive).
-
-Mix pollen competition and sex-ratio affects in here?
-Kokko paper addresses some of these issues, but not related to sex-determination. 
-These feedbacks between population densities and meiotic drive or haploid competition for different sexual/mating systems deserve further attention.
-
-Here, we have not considered any population size dynamics
-
-{\color{blue}
-(Check with Jim Bull that it's ok before including this speculation:)
-Finally, \citet{Hamilton:1967ts} pointed out that biased sex ratios can affect population size because the number of offspring in each generation is typically determined by the number of females. 
-Population density can, in turn, affect the intensity of pollen/sperm competition in future generations because fewer males are available to donate pollen/sperm in a particular area. 
-Thus, a feedback could occur between population densities and haploid selection, which has not yet been investigated. 
-}
+Also check Kallman (1984) -from vD\&K, 2010.
+
+From vD\&K 2010:
+``We noted in the Introduction that several recently derived sex chromosomes are known with genes that appear to be targets of sex-antagonistic selection (Kallman 1973; Wada et al.
+1998; Lande et al.
+2001; Lindholm and Breden 2002; Streelman et al.
+2003; Fernandez and Morris 2008; Kitano et al.
+2009; Roberts et al.
+2009).
+These observations are certainly consistent with the hypothesis that sex-antagonistic selection was responsible for the establishment of a new sex-determining system, but a proper test of our hypothesis would require data to rule out the plausible alternative that the sex-antagonistic alleles accumulated secondarily, after the new sex chromosomes invaded.
+Indeed, linkage to sex chromosomes is favorable to the maintenance of sex-antagonistic variation (Rice 1987).
+The required data may soon become available through comparative genomic studies on species that recently underwent a heterogamety transition and their close relatives.
+The presence of sex-antagonistic variation at the same genomic location in closely related species that have the ancestral sex-determining system would support the view that sex-antagonistic variation predated the origin of the derived sex chromosomes and caused the invasion of a new sex-determination system.
+''
+
+Note that, ploidally-antagonistic selection does not suffer from the proviso that it is easier to maintain polymorphisms close to the SDR.
+vD\&K also suggest that this build up of sex-antagonistic polymorphisms may help to stabilize the ancestral sex-determining system, which would not be the case with haploid selection.
 

### 2017-02-01 LaTeX/Turnover.tex

--- 2017-02-01 LaTeX/Turnover.tex
@@
 
-If there is genetic variation maintained by sexually-antagonistic selection, new sex-determining systems can evolve. 
-In particular, transitions to new sex-determining systems can occur when new sex-determining regions are more closely linked to a sexually-antagonistic locus.
-Here, we show that genetic variation at loci that experience haploid selection can also generate selection in favour of new sex-determining systems. 
-Closer linkage can again favour new sex-determining alleles. 
-However, with haploid selection, heterogametic transitions (XY to ZW or ZW to XY) can also occur when the new sex-determining region is less closely linked to the locus under selection.
-
-Neo-W (neo-Y) alleles invade when their fitness in females (males) is greater than the mean fitness of females (males) under the ancestral sex determination system.
-With sexually antagonistic selection (between diploid sexes) only, linkage between a selected locus and the sex-determining region strengthens associations between male beneficial alleles and the male-determining allele (Y or Z) and between female beneficial alleles and the female-determining allele (X or W).
-Thus, the mean fitness of both males and females increases with closer linkage to the sex-determining region. 
-Therefore, new sex-determining alleles only invade if they are more closely linked than the ancestral sex-determining region. 
-However, if there is haploid selection on loci linked to an XY (ZW) sex-determining region, there are equilibria for which the mean fitness of females (males) or males is lower than it would be without sex-linkage, allowing unlinked neo-W (neo-Y) alleles to invade, see figure \ref{fig:Combination_MeanFit}.
-
-Linkage between a locus that experiences haploid selection and a sex-determining region causes zygotic sex ratios to become biased \textcolor{red}{(REFERENCES)}, which we might then expect to exert sex ratio selection upon new modifiers.
+One might expect Fisherian sex ratio selection to influence the spread of new sex-determining systems because linkage between haploid selected loci and sex-determining regions cause biased zygotic sex ratios \citep{Hamilton:1967ts,Burt:2006,Field:2012fd,Field:2013cc}.
 Fisherian sex ratio selection follows from the fact that, for an autosomal locus, half of the genetic material is inherited from a male, and half from a female. 
@@
 Even mutants that are equally likely to be found in males or females, such as an environmental sex determination mutation (equation \ref{eq:lambda_ESD}), are not strictly autosomal if they determine sex.
-Thus, despite the fact that sex ratio biases caused by haploid competition or meiotic drive have been shown to exert selection on various autosomal modifiers \citep{Stalker:1961th,Smith:1975ft,Frank:1989vl,Hough:2013uo,Ubeda:2015fx, Otto:2015va}, we do not find evidence of Fisherian sex ratio selection acting upon neo-sex-determination systems (e.g., see Figure \ref{fig:Combination_Turnover}).
+Thus, despite the fact that sex ratio biases caused by haploid competition or meiotic drive have been shown to exert selection on various autosomal modifiers \citep{Stalker:1961th,Smith:1975ft,Frank:1989vl,Hough:2013uo,Ubeda:2015fx, Otto:2015va}, we do not find evidence of Fisherian sex ratio selection acting upon neo-sex-determination systems (e.g., see Figure \ref{fig:Combination_Turnover} and \citealt{Ubeda:2015fx}, in which a neo-Y invades despite biasing sex ratios).
+
+It has previously been demonstrated that new sex-determining systems can evolve if there is genetic variation maintained by sexually-antagonistic selection \citep{vanDoorn:2007eu,vanDoorn:2010hu}. 
+In particular, transitions to new sex-determining systems can occur when new sex-determining regions are more closely linked to a sexually-antagonistic locus.
+Our results show that genetic variation at loci that experience haploid selection can also generate selection in favour of new sex-determining systems. 
+New sex-determining allleles are again favoured if they are more closely linked with a locus under haploid selection.
+However, with haploid selection, heterogametic transitions (XY to ZW or ZW to XY) can also occur when the new sex-determining region is less closely linked to the locus under selection.
+
+Neo-W (neo-Y) alleles invade when their fitness in females (males) is greater than the mean fitness of females (males) under the ancestral sex determination system.
+With sexually antagonistic selection (between diploid sexes) only, linkage between a selected locus and the sex-determining region strengthens associations between male beneficial alleles and the male-determining allele (Y or Z) and between female beneficial alleles and the female-determining allele (X or W).
+Thus, the mean fitness of both males and females increases with closer linkage to the sex-determining region. 
+Therefore, new sex-determining alleles only invade if they are more closely linked than the ancestral sex-determining region. 
+However, if there is haploid selection on loci linked to an XY (ZW) sex-determining region, polymorphisms can be maintained at which the mean fitness of females (males) or males is lower than it would be without sex-linkage, allowing unlinked neo-W (neo-Y) alleles to invade, see figure \ref{fig:Combination_MeanFit}.
 

### 2017-02-01 LaTeX/Turnover.tex
discussion, getting closer...

@@
 Because there are typically more pollen/sperm than required for fertilization, gametic competition is also typically sex specific, occurring primarily among male gametes.
-Haploid competition may be particularly common in plants, in which 60-70\% of all genes are expressed in the male gametophyte and these genes exhibit stronger signatures of selection than random genes \citep{Borg:2009jpa,Arunkumar:2013iq,Gossmann:2014dua}.
+Gametic competition may be particularly common in plants, in which 60-70\% of all genes are expressed in the male gametophyte and these genes exhibit stronger signatures of selection than random genes \citep{Borg:2009jpa,Arunkumar:2013iq,Gossmann:2014dua}.
 In addition, artificial selection pressures applied to male gametophytes cause the frequency of resistant alleles to increase \citep[e.g.,][]{Hormaza:1996cv,Ravikumar:2003uo,Hedhly:2004iv,Clarke:2004ir}.
@@
 %We only do invasion analytically though (is this sentence still ok?)
-We assume that the \textbf{M} locus is dominant over the \textbf{X} locus such that zygotes with at least one $m$ allele develop as females with probability $k$ and as males with probability $1-k$, regardless of the \textbf{X} locus genotype.
+We assume that the \textbf{M} locus is epistatically dominant over the \textbf{X} locus such that zygotes with at least one $m$ allele develop as females with probability $k$ and as males with probability $1-k$, regardless of the \textbf{X} locus genotype.
 With $k=0$, the $m$ allele is a masculinizer (i.e., a neo-Y) and with $k=1$ the $m$ allele is a feminizer (i.e., a neo-W).
@@
 %life-cycle
-In each generation, we census the genotype frequencies in male and female gametes/gametophytes (hereafter gametes) before haploid competition (see Sup.\ Mat. for recursion equations). 
+In each generation, we census the genotype frequencies in male and female gametes/gametophytes (hereafter gametes) before gametic competition (see Sup.\ Mat. for recursion equations). 
 First, competition occurs among male gametes (sperm/pollen competition) and among female gametes (egg/ovule competition) separately. 
-Selection during haploid competition depends on the \textbf{A} locus genotype, relative fitnesses are given by $w_A^\Hermaphrodite$ and $w_a^\Hermaphrodite$ ($\Hermaphrodite \in \{\female,\male\}$; see table \ref{tab:fitnesstable}).
+Selection during gametic competition depends on the \textbf{A} locus genotype, relative fitnesses are given by $w_A^\Hermaphrodite$ and $w_a^\Hermaphrodite$ ($\Hermaphrodite \in \{\female,\male\}$; see table \ref{tab:fitnesstable}).
 %$w_{A}^\male$ and $w_{a}^\male$ for male gametes and $w_{A}^\female$ and $w_{a}^\female$ for female gametes, see table \ref{tab:fitnesstable}.
-We assume that all gametes compete for fertilization during haploid competition, which is not the case for monogamous mating systems where gametes from only one mating partner are present. 
-Haploid competition in monogamous mating systems is equivalent to meiotic drive in our model, which only alters the frequency of gametes produced by heterozygotes. 
-Random mating then occurs between male and female gametes.
+We assume that all gametes compete for fertilization during gametic competition, which is not the case for monogamous mating systems where gametes from only one mating partner are present. 
+Gametic competition in monogamous mating systems is equivalent to meiotic drive in our model, which only alters the frequency of gametes produced by heterozygotes. 
+After gametic competition, random mating occurs between male and female gametes.
 The resulting zygotes develop as males or females, depending on their genotypes at the \textbf{X} and \textbf{M} loci (and the \textbf{M} genotype of their mother in the case of maternal control) as described above.
@@
 Males/females that are heterozygous at the \textbf{A} locus experience meiotic drive; $Aa$ heterozgotes of sex $\Hermaphrodite$ produce gametes bearing allele $A$ with probability $\alpha^\Hermaphrodite$.
-Thus, the \textbf{A} locus can experience sex-specific haploid competition, diploid selection and/or meiotic drive.
+Thus, the \textbf{A} locus can experience sex-specific gametic competition, diploid selection and/or meiotic drive.
 
@@
 \hline\hline
-  Genotype & Relative fitness during haploid competition \\ [0.5ex] \hline
+  Genotype & Relative fitness during gametic competition \\ [0.5ex] \hline
   A & $w_{A}^\Hermaphrodite = 1+t^\Hermaphrodite$ \\
@@
 The frequency of Y among male gametes depends upon the difference in $A$ allele frequency on X- and Y-bearing male gametes and the strength of meiotic drive in favour of the $A$ allele in males, $q=1/2+\alpha_{\Delta}^\male(\hat{p}^\male_Y-\hat{p}^\male_X)/2+O(\epsilon^3)$.
-Without haploid competition or drive ($\alpha_{\Delta}^\Hermaphrodite=t^\Hermaphrodite=0$), these results reduce to those of \citet{vanDoorn:2007eu}.
+Without gametic competition or drive ($\alpha_{\Delta}^\Hermaphrodite=t^\Hermaphrodite=0$), these results reduce to those of \citet{vanDoorn:2007eu}.
 
@@
       \item $\bar{p}^{\male}=p_{Y}^{\male}q+p_{X}^{\male}(1-q)$ is the average frequency of the $A$ allele among X- and Y-bearing male gametes 
-      \item $\bar{w}_H^\female = p_X^\female w_A^\female + (1-p_X^\female) w_a^\female$ is the mean fitness of female gametes during haploid competition
-      \item $\bar{w}_H^\male = \bar{p}^{\male} w_A^\male + (1-\bar{p}^{\male}) w_a^\male$ is the mean fitness of male gametes during haploid competition
-       \item $\bar{w}^\female = \{ p_X^\female w_A^\female (1-q) p_X^\male w_A^\male w_{AA}^\female + (1 - p_X^\female) w_a^\female (1-q) p_X^\male w_A^\male w_{Aa}^\female + p_X^\female w_A^\female (1-q) (1 - p_X^\male) w_a^\male w_{Aa}^\female + (1-p_X^\female) w_a^\female (1-q) (1 - p_X^\male) w_a^\male w_{aa}^\female \} / \{ \bar{w}_H^\female \bar{w}_H^\male\}$ is the mean fitness of females during diploid competition
-       \item $\bar{w}^\male = \{ p_X^\female w_A^\female q p_Y^\male w_A^\male w_{AA}^\male + (1 - p_X^\female) w_a^\female q p_Y^\male w_A^\male w_{Aa}^\male + p_X^\female w_A^\female q (1 - p_Y^\male) w_a^\male w_{Aa}^\male + (1-p_X^\female) w_a^\female q (1 - p_Y^\male) w_a^\male w_{aa}^\male \} / \{ \bar{w}_H^\male \bar{w}_H^\male\}$ is the mean fitness of males during diploid competition
+      \item see Table \ref{tab:meanfitnesses} for mean fitnesses.
+%      \item $\bar{w}_H^\female = p_X^\female w_A^\female + (1-p_X^\female) w_a^\female$ is the mean fitness of female gametes during gametic competition
+%      \item $\bar{w}_H^\male = \bar{p}^{\male} w_A^\male + (1-\bar{p}^{\male}) w_a^\male$ is the mean fitness of male gametes during gametic competition
+%       \item $\bar{w}^\female = \{ p_X^\female w_A^\female (1-q) p_X^\male w_A^\male w_{AA}^\female + (1 - p_X^\female) w_a^\female (1-q) p_X^\male w_A^\male w_{Aa}^\female + p_X^\female w_A^\female (1-q) (1 - p_X^\male) w_a^\male w_{Aa}^\female + (1-p_X^\female) w_a^\female (1-q) (1 - p_X^\male) w_a^\male w_{aa}^\female \} / \{ \bar{w}_H^\female \bar{w}_H^\male\}$ is the mean fitness of females during diploid competition
+%       \item $\bar{w}^\male = \{ p_X^\female w_A^\female q p_Y^\male w_A^\male w_{AA}^\male + (1 - p_X^\female) w_a^\female q p_Y^\male w_A^\male w_{Aa}^\male + p_X^\female w_A^\female q (1 - p_Y^\male) w_a^\male w_{Aa}^\male + (1-p_X^\female) w_a^\female q (1 - p_Y^\male) w_a^\male w_{aa}^\male \} / \{ \bar{w}_H^\male \bar{w}_H^\male\}$ is the mean fitness of males during diploid competition
     \end{tablenotes}
@@
 \noindent
-where $V_{A}=\bar{p}(1-\bar{p})$ is the variance in the frequency of $A$ and $S_{A}=(D^\male +\alpha_{\Delta}^\male+t^\male) - (D^\female+\alpha_{\Delta}^\female+t^\female)$ is the difference in fitness in males versus females for the $A$ allele against the $a$ allele across diploid selection, haploid competition, and meiosis.
+where $V_{A}=\bar{p}(1-\bar{p})$ is the variance in the frequency of $A$ and $S_{A}=(D^\male +\alpha_{\Delta}^\male+t^\male) - (D^\female+\alpha_{\Delta}^\female+t^\female)$ is the difference in fitness in males versus females for the $A$ allele against the $a$ allele across diploid selection, gametic competition, and meiosis.
 
@@
 In table \ref{tab:specialcases} we give the conditions where invasion occurs where we further assume that haploid selection only occurs during one phase in one sex (e.g., during male meiosis only) and equal dominance, $h^\female=h^\male$.
-Where there is no haploid competition and meiotic drive in one sex only, an unlinked neo-W can invade as long as the same allele is favoured in male and female diploid selection ($s^\female s^\male>0$, see Figure \ref{fig:Combination_Centimorgans}B), which is 50\% of the parameter space.
-Where there is no meiotic drive and haploid competition occurs in one sex only, an unlinked neo-W can invade as long as the same allele is favoured in male and female diploid selection and there are sex differences in selection of one type ($-s^\female(s^\female-s^\male)>0$, see Figure \ref{fig:Combination_Centimorgans}C,D), which is 25\% of the parameter space.
+Where there is no gametic competition and meiotic drive in one sex only, an unlinked neo-W can invade as long as the same allele is favoured in male and female diploid selection ($s^\female s^\male>0$, see Figure \ref{fig:Combination_Centimorgans}B), which is 50\% of the parameter space.
+Where there is no meiotic drive and gametic competition occurs in one sex only, an unlinked neo-W can invade as long as the same allele is favoured in male and female diploid selection and there are sex differences in selection of one type ($-s^\female(s^\female-s^\male)>0$, see Figure \ref{fig:Combination_Centimorgans}C,D), which is 25\% of the parameter space.
 These special cases indicate that neo-W invasion can occur for a relatively large fraction of parameter space, even if $R>r$.
@@
 Consider, for example, the case where the \textbf{A} locus is linked to the ancestral-SDR ($r<1/2$) and experiences meiotic drive in males only (e.g., during spermatogenesis but not during oogenesis, $\alpha^\male \neq 1/2$, $\alpha^\female=1/2$).
-We will also disregard haploid competition ($t^\female=t^\male=0$) such that zygotic sex ratios can only be biased by meiotic drive in males. 
+We will also disregard gametic competition ($t^\female=t^\male=0$) such that zygotic sex ratios can only be biased by meiotic drive in males. 
 In this case, the zygotic sex ratio can be initially biased only if the ancestral sex-determining system is XY (Figure \ref{fig:Combination_Turnover}B). 
@@
 Even mutants that are equally likely to be found in males or females, such as an environmental sex determination mutation (equation \ref{eq:lambda_ESD}), are not strictly autosomal if they determine sex.
-Thus, despite the fact that sex ratio biases caused by haploid competition or meiotic drive have been shown to exert selection on various autosomal modifiers \citep{Stalker:1961th,Smith:1975ft,Frank:1989vl,Hough:2013uo,Ubeda:2015fx, Otto:2015va}, we do not find evidence of Fisherian sex ratio selection acting upon neo-sex-determination systems (e.g., see Figure \ref{fig:Combination_Turnover} and \citealt{Ubeda:2015fx}, in which a neo-Y invades despite biasing sex ratios).
+Thus, despite the fact that sex ratio biases caused by gametic competition or meiotic drive have been shown to exert selection on various autosomal modifiers \citep{Stalker:1961th,Smith:1975ft,Frank:1989vl,Hough:2013uo,Ubeda:2015fx, Otto:2015va}, we do not find evidence of Fisherian sex ratio selection acting upon neo-sex-determination systems (e.g., see Figure \ref{fig:Combination_Turnover} and \citealt{Ubeda:2015fx}, in which a neo-Y invades despite biasing sex ratios).
 
@@
 
-We only consider selection at the \textbf{A} locus, i.e., sex-determining alleles are not directly selected except via their associations with sex and \textbf{A} locus alleles. 
+We assume that sex-determining alleles do not experience direct selection except via their associations with sex and alleles at a selected locus. 
 However, in some cases, there may be significant degeneration around the sex-limited allele (Y or W) in the ancestral sex determining region because recessive deleterious mutations and/or deletions may fix around the Y or W allele \citealt{Rice:1996ke,Charlesworth:2000cc,Bachtrog:2006ed,Marais:2008hm}).
-During heterogametic transitions (XY to ZW or ZW to XY), the formally sex-limited allele fixes (Figure \ref{fig:Combination_Turnover}) such that all individuals have YY or WW genotypes. 
+During heterogametic transitions (XY to ZW or ZW to XY), the formally sex-limited allele fixes such that all individuals have YY or WW genotypes (Figure \ref{fig:Combination_Turnover}). 
 Any recessive deleterious alleles linked to the Y or W will therefore be revealed to selection during a heterogametic transition. 
@@
 Our model of meiotic drive is very simple, involving a single locus with two alleles. 
-However, many meiotic drive systems involve an interaction with another locus at which alleles may `suppress' the action of meiotic drive. 
-Furthermore, in some cases, a driving allele may act by killing any gametes that carry a `target' allele at another locus, in which case the total number of gametes produced will be reduced (here, we assume total gamete number is not affected by drive).
-
-Mix pollen competition and sex-ratio affects in here?
-Kokko paper addresses some of these issues, but not related to sex-determination. 
-These feedbacks between population densities and meiotic drive or haploid competition for different sexual/mating systems deserve further attention.
-
-Here, we have not considered any population size dynamics
-
-Finally, \citet{Hamilton:1967ts} pointed out that biased sex ratios can affect population size because the number of offspring in each generation is typically determined by the number of females. 
-Population density can, in turn, affect the intensity of pollen/sperm competition in future generations because fewer males are available to donate pollen/sperm in a particular area. 
-Thus, a feedback could occur between population densities and haploid selection, which has not yet been investigated.
-
-\textcolor{red}{\noindent Discuss patterns that might be looked for:}
-
-Evolutionary events, such as the transition between one sex-determination system and another, are generally difficult to observe directly. 
-One observation would be the presence of sexually antagonistic variation linked to neo-sex chromosomes - example from cichlids (debated, i believe). 
-Our model could be examined in a similar manner, although we find that genes that experience haploid selection that are near either the neo- or ancestral-sex-determining locus could have been involved in favouring a transition between sex-determining systems.
-
-A complementary method of investigating evolutionary transitions is via comparative methods. 
+However, many meiotic drive systems involve an interaction with another locus at which alleles may `suppress' the action of meiotic drive \citep{Burt:2006} \textcolor{red}{(Lindholm et al. 2016)}. 
+Thus, the dynamics of meiotic drive alleles can be heavily dependent on the interaction between two loci and the recombination rate between them, which in turn can be affected by sex-linkage if there is reduced recombination between sex chromosomes \textcolor{red}{(Hurst and Pomiankowski, 1991)}.
+Furthermore, in some cases, a driving allele may act by killing any gametes that carry a `target' allele at another locus, in which case there is a two-locus drive system and the total number of gametes produced can be reduced by meiotic drive (here, we assume that the total gamete number is not affected by drive).
+Thus, the number of mates competing for fertilization (mating system) can further affect the frequency of a meiotic drive allele \textcolor{red}{Holman et al., 2015)}. 
+Finally, the intensity of pollen/sperm competition under a particular mating system can depend on the density of males available to donate pollen/sperm, which can depend on the sex ratio and population size \textcolor{red}{(Taylor and Jaenike, 2002)}.
+Here, we do not consider feedbacks between sex ratios and the intensity of haploid selection. 
+It remains to be investigated how the evolution of new sex-determining mechanisms could be influenced by ecological feedbacks under different mating systems and by two-locus meiotic drive.
+
+The hypotheses presented here can be investigated in a similar manner to the idea that transitions between sex-determining systems are favoured by linkage to sexually antagonistic variation. 
+In the case of sexually antagonistic variation, one supporting observation is that genes that appear to experience sexually-antagonistic selection have been found on recently derived sex chromosomes \textcolor{red}{CHECK (Kallman 1973; Wada et al.
+1998; Lande et al.
+2001; Lindholm and Breden 2002; Streelman et al.
+2003; Fernandez and Morris 2008; Kitano et al.
+2009; Roberts et al.
+2009)}.
+However, it is possible that sexually antagonistic variation accumulated after sex chromosome transitions because linkage with the sex-determining regions allows sexually antagonistic selection to maintain polymorphisms under a larger parameter space \textcolor{red}{(Rice, 1987, Jordan and Charlesworth, 2010-ish)}.
+We note that linkage with sex chromosomes is not, a priori, more permissive to the maintainence of ploidally antagonistic variation \citep{Immler:2012tl}.
+Secondly, we note that new sex-determination systems can be favoured if either the ancestral sex-determining region or the new sex-determining region are linked to loci under haploid selection. 
+Therefore, the presence of haploid selected loci around ancestral- or new- sex-determining regions could support their role in sex chromosome turnover. 
+%It would be particularly informative if selection were evaluated in closely related clades
+
+\textcolor{red}{\noindent Do we have any cool examples?
+Meiotic drive alleles certainly more common on the sex chromosomes - although there are other explanations: (1) Divergence between X and Y provides a ready supply of target alleles for meiotic drive.
+(2) sex-linked meiotic drive has a more obvious phenotype to detect, sex ratio bias.}
+
 Taken at face value, our results indicate that transitions in heterogametey (XY to ZW or vice versa) are more likely to be favoured by selection if there is selection upon both haploid and diploid genotypes rather than diploid selection alone.
+Thus,
 
 In broadcast spawning animal species (e.g., corals, many fish) and species where sperm typically requires greater longevity, haploid selection may be stronger because transcripts shared during spermatogenesis may become depleted \citep{Immler:2014im}.
-\textcolor{red}{also, mating systems (e.g., fewer alleles are available during haploid competition in monogamous species), selfing rates, and estimates of pollen limitation could be used as indicators of the intensity of haploid selection}
+\textcolor{red}{also, mating systems (e.g., fewer alleles are available during gametic competition in monogamous species), selfing rates, and estimates of pollen limitation could be used as indicators of the intensity of haploid selection}
 
@@
 
-From vD\&K 2010:
-``We noted in the Introduction that several recently derived sex chromosomes are known with genes that appear to be targets of sex-antagonistic selection (Kallman 1973; Wada et al.
-1998; Lande et al.
-2001; Lindholm and Breden 2002; Streelman et al.
-2003; Fernandez and Morris 2008; Kitano et al.
-2009; Roberts et al.
-2009).
-These observations are certainly consistent with the hypothesis that sex-antagonistic selection was responsible for the establishment of a new sex-determining system, but a proper test of our hypothesis would require data to rule out the plausible alternative that the sex-antagonistic alleles accumulated secondarily, after the new sex chromosomes invaded.
-Indeed, linkage to sex chromosomes is favorable to the maintenance of sex-antagonistic variation (Rice 1987).
-The required data may soon become available through comparative genomic studies on species that recently underwent a heterogamety transition and their close relatives.
-The presence of sex-antagonistic variation at the same genomic location in closely related species that have the ancestral sex-determining system would support the view that sex-antagonistic variation predated the origin of the derived sex chromosomes and caused the invasion of a new sex-determination system.
-''
-
-Note that, ploidally-antagonistic selection does not suffer from the proviso that it is easier to maintain polymorphisms close to the SDR.
 vD\&K also suggest that this build up of sex-antagonistic polymorphisms may help to stabilize the ancestral sex-determining system, which would not be the case with haploid selection.
@@
 Similarly, the ancestral W allele fixes in males and females (blue and red lines) during a ZW to XY transition. 
-In this plot, there is no haploid competition ($t^\female=t^\male=0$) and meiotic drive occurs during male meiosis only ($\alpha^\female_{\Delta}=0$, $\alpha^\Hermaphrodite_{\Delta}=-1/5$).
+In this plot, there is no gametic competition ($t^\female=t^\male=0$) and meiotic drive occurs during male meiosis only ($\alpha^\female_{\Delta}=0$, $\alpha^\Hermaphrodite_{\Delta}=-1/5$).
 Therefore, sex ratio biases can only arise when the \textbf{A} locus is linked to an XY sex-determining locus.
@@
 \caption{
-\textcolor{red}{A sexual antagonism (no haploid selection), B drive (no haploid competition), equal selection in sexes ($s^\female=s^\male$), C \& D Pollen/Sperm competition only (no drive).
+\textcolor{red}{A sexual antagonism (no haploid selection), B drive (no gametic competition), equal selection in sexes ($s^\female=s^\male$), C \& D Pollen/Sperm competition only (no drive).
 C allele favoured in pollen/sperm competition selected against less in males ($t<0$, $s^\female, s^\male >0$, $s^\female<s^\female$).
@@
 
-In each generation we census the genotype frequencies in male and female gametes/gametophytes (hereafter, gametes) before haploid competition. 
-Before haploid competition, the frequencies of X-bearing male and female gametes are given by $X_{i}^{\male}$ and $X_{i}^{\female}$ and the frequencies of Y-bearing gametes are given by $Y_{i}^{\male}$ and $Y_{i}^{\female}$ where the index $i$ specifies genotypes $MA=1$, $Ma=2$, $mA=3$, and $ma=4$.
+In each generation we census the genotype frequencies in male and female gametes/gametophytes (hereafter, gametes) before gametic competition. 
+Before gametic competition, the frequencies of X-bearing male and female gametes are given by $X_{i}^{\male}$ and $X_{i}^{\female}$ and the frequencies of Y-bearing gametes are given by $Y_{i}^{\male}$ and $Y_{i}^{\female}$ where the index $i$ specifies genotypes $MA=1$, $Ma=2$, $mA=3$, and $ma=4$.
 Competition then occurs among gametes of the same sex (e.g., among eggs and among sperm separately) according to the \textbf{A} locus allele, $g$ ($g\in A$, $a$, see Table \ref{tab:fitnesstable}), carried by individuals with genotype $i$.
-The genotype frequencies after haploid competition are $X_{i}^{\Hermaphrodite,s}= w_{g}X_{i}^{\Hermaphrodite}/\bar{w}_{H}^{\Hermaphrodite}$ and $Y_{i}^{\Hermaphrodite,s}= w_{g}Y_{i}^{\Hermaphrodite}/\bar{w}_{H}^{\Hermaphrodite}$, where $\bar{w}_{H}^{\Hermaphrodite}=\sum_{i=1}^{4} w_{g}X_{i}^{\Hermaphrodite}+w_{g}Y_{i}^{\Hermaphrodite}$ is the mean fitness of male ($\Hermaphrodite=\male$) or female ($\Hermaphrodite=\female$) gametes.
+The genotype frequencies after gametic competition are $X_{i}^{\Hermaphrodite,s}= w_{g}X_{i}^{\Hermaphrodite}/\bar{w}_{H}^{\Hermaphrodite}$ and $Y_{i}^{\Hermaphrodite,s}= w_{g}Y_{i}^{\Hermaphrodite}/\bar{w}_{H}^{\Hermaphrodite}$, where $\bar{w}_{H}^{\Hermaphrodite}=\sum_{i=1}^{4} w_{g}X_{i}^{\Hermaphrodite}+w_{g}Y_{i}^{\Hermaphrodite}$ is the mean fitness of male ($\Hermaphrodite=\male$) or female ($\Hermaphrodite=\female$) gametes.
 Random mating then occurs between gametes to produce diploid zygotes with genotype $ij$ at the \textbf{A} and \textbf{M} loci, such that $XX$ zygotes are denoted $xx_{ij}$, $XY$ zygotes are $xy_{ij}$, and $YY$ zygotes are $yy_{ij}$.
@@
 This notation allows both the ancestral and novel sex-determining regions to determine zygotic sex according to an $XY$ system, a $ZW$ system, or an environmental sex-determining system. 
-In addition, we can consider any dominance relationship between the two sex-determining loci. 
-Typically, we assume that the ancestral sex-determining system (\textbf{X} locus) is $XY$ ($k_{MMXX}=1$ and $k_{MMXY}=k_{MMYY}=0$) and recessive to a dominant novel sex-determining locus, \textbf{M} ($k_{Mmc}=k_{mmc}=k$).
+In addition, we can consider any epistatic dominance relationship between the two sex-determining loci. 
+Typically, we assume that the ancestral sex-determining system (\textbf{X} locus) is $XY$ ($k_{MMXX}=1$ and $k_{MMXY}=k_{MMYY}=0$) and epistatically recessive to a dominant novel sex-determining locus, \textbf{M} ($k_{Mmc}=k_{mmc}=k$).
 
@@
 
-Among gametes from sex $\Hermaphrodite$ (sperm/pollen when $\Hermaphrodite=\male$, eggs/ovules when $\Hermaphrodite=\female$), the frequency of haplotypes (before haploid competition) in the next generation are given by
+Among gametes from sex $\Hermaphrodite$ (sperm/pollen when $\Hermaphrodite=\male$, eggs/ovules when $\Hermaphrodite=\female$), the frequency of haplotypes (before gametic competition) in the next generation are given by
 

### 2017-02-01 LaTeX/Turnover.tex

@@
 Where there is no gametic competition and meiotic drive in one sex only, an unlinked neo-W can invade as long as the same allele is favoured in male and female diploid selection ($s^\female s^\male>0$, see Figure \ref{fig:Combination_Centimorgans}B), which is 50\% of the parameter space.
-Where there is no meiotic drive and gametic competition occurs in one sex only, an unlinked neo-W can invade as long as the same allele is favoured in male and female diploid selection and there are sex differences in selection of one type ($-s^\female(s^\female-s^\male)>0$, see Figure \ref{fig:Combination_Centimorgans}C,D), which is 25\% of the parameter space.
+Where there is no meiotic drive and gametic competition occurs in one sex only, an unlinked neo-W can invade as long as the same allele is favoured in male and female diploid selection and there are sex differences in selection of one type ($s^\female(s^\male-s^\female)>0$, see Figure \ref{fig:Combination_Centimorgans}C,D), which is 25\% of the parameter space.
 These special cases indicate that neo-W invasion can occur for a relatively large fraction of parameter space, even if $R>r$.
@@
   $h^\male=h^\female$, $t^\female=t^\male=\alpha^\male_{\Delta}=0$ & $s^\female s^\male>0$ \\
-  $h^\male=h^\female$, $t^\female=\alpha^\female_{\Delta}=\alpha^\male_{\Delta}=0$ & $-s^\female(s^\female-s^\male)>0$ \\
-  $h^\male=h^\female$, $t^\male=\alpha^\female_{\Delta}=\alpha^\male_{\Delta}=0$ & $-s^\female(s^\female-s^\male)>0$ \\
+  $h^\male=h^\female$, $t^\female=\alpha^\female_{\Delta}=\alpha^\male_{\Delta}=0$ & $s^\female(s^\male-s^\female)>0$ \\
+  $h^\male=h^\female$, $t^\male=\alpha^\female_{\Delta}=\alpha^\male_{\Delta}=0$ & $s^\male(s^\female-s^\male)>0$ \\
   \hline \hline

### 2017-02-02 LaTeX/Turnover.tex
updating nb
removed need for comparison subs, ran most of maternal control again

@@
 
-%I think this should be moved below because we have some 'results' where we don't assume weak selection but we only have the equilibrium calculated analytically for weak selection. 
-\subsection*{Resident equilibrium and stability}
-In the resident population (allele $M$ fixed), we follow the frequency of $A$ in female gametes (eggs) from an XX female, $p^\female_X$, and in X-bearing, $p^\male_X$, and Y-bearing, $p^\male_Y$, male gametes (sperm).
-We also track the total frequency of Y-bearing male gametes, $q$, which may deviate from $1/2$ due to meiotic drive in males.
-
-Various forms of selection can maintain a polymorphism at the \textbf{A} locus, including sexually antagonistic selection, overdominance and conflicts between diploid selection and selection upon haploid genotypes \citep[ploidally antagonistic selection,][]{Immler:2012tl} or a combination of these selective regimes.
-Here, we assume that selection and meiotic drive are weak relative to recombination ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon$). 
-The maintenance of a polymorphism at the \textbf{A} locus then requires that
-
-\begin{equation}
-\begin{split}
-0&<-((1-h^\female)s^\female +(1-h^\male) s^\male + t^\female +t^\male + \alpha_{\Delta}^\female+\alpha_{\Delta}^\male)\\
-%
-0&<(h^\female s^\female +h^\male s^\male + t^\female +t^\male + \alpha_{\Delta}^\female+\alpha_{\Delta}^\male).
-\end{split}
-\end{equation}
-
-\noindent
-which indicates that a polymorphism is maintained under various selective regimes. 
-In particular special cases, e.g., no sex-differences in selection or meiotic drive ($s^\male=s^\female$, $h^\male=h^\female$, and $\alpha^\male=\alpha^\female=1/2$), the equilibrium allele frequency and stability can be calculated analytically without assuming weak selection.
-However, here, we focus on weak selection in order to make fewer assumptions about fitnesses.
-
-Given that a polymorphism is maintained at the \textbf{A} locus by selection, with weak selection and drive, to leading order, the frequencies of $A$ in each type of gamete are the same ($\hat{p}^\female_X=\hat{p}^\male_X=\hat{p}^\male_Y=\bar{p}$) and given by
-
-\begin{equation}
-\bar{p}=\frac{h^\female s^\female + h^\male s^\male +t^\female+t^\male+\alpha_{\Delta}^\female+\alpha_{\Delta}^\male}
-{(2h^\female-1)s^\female+(2h^\male-1)s^\male}
-+O(\epsilon)
-.
-\label{eq:pAve}
-\end{equation}
-
-\noindent
-Differences in frequency between gamete types are of order $\epsilon$ to leading order and given by
-
-\begin{equation}
-\begin{split}
-\hat{p}^\male_X-\hat{p}^\female_X&=V_{A}\big{(}D^\male - D^\female +\alpha_{\Delta}^\male-\alpha_{\Delta}^\female \big{)}
-+O(\epsilon^2)\\
-%
-\hat{p}^\male_Y-\hat{p}^\female_X&=V_{A}\big{(}D^\male - D^\female+\alpha_{\Delta}^\male-\alpha_{\Delta}^\female+(1-2r)(t^\male-t^\female)\big{)}/2r
-+O(\epsilon^2)\\
-%
-\hat{p}^\male_Y-\hat{p}^\male_X&=V_{A}\big{(}D^\male - D^\female+\alpha_{\Delta}^\male-\alpha_{\Delta}^\female+t^\male-t^\female\big{)}(1-2r)/2r
-+O(\epsilon^2)
-\end{split}
-\label{eq:freq_diffs}
-\end{equation}
-
-\noindent
-where $V_{A}=\bar{p}(1-\bar{p})$ is the variance in the frequency of $A$ and $D^\Hermaphrodite=\big{(} \bar{p}s^\Hermaphrodite+(1-\bar{p})h^\Hermaphrodite s^\Hermaphrodite\big{)} -\big{(} \bar{p}h^\Hermaphrodite s^\Hermaphrodite+(1-\bar{p}) \big{)}$ corresponds to the difference in fitness between $A$ and $a$ alleles in diploids of sex $\Hermaphrodite \in \{\female,\male\}$ ($\bar{p}$ is the leading-order probability of mating with an $A$-bearing gamete from the opposite sex).
-The frequency of Y among male gametes depends upon the difference in $A$ allele frequency on X- and Y-bearing male gametes and the strength of meiotic drive in favour of the $A$ allele in males, $q=1/2+\alpha_{\Delta}^\male(\hat{p}^\male_Y-\hat{p}^\male_X)/2+O(\epsilon^3)$.
-Without gametic competition or drive ($\alpha_{\Delta}^\Hermaphrodite=t^\Hermaphrodite=0$), these results reduce to those of \citet{vanDoorn:2007eu}.
-
-% the differences in the frequencies of $A$ in each type of gamete are small, as is the bias in the sex-determining factor from the heterogametic sex, and we can solve for the mean frequency of $A$ across all types ($p_A$), the difference in the frequencies of $A$ between two of the three types, and the bias in the frequency of the sex-determining factor, to first order in selection.
-%Linear stability analysis can then be used to determine the stability of this equilibrium.
-%Without haploid selection or meiotic drive our results reduce to those of \cite{vanDoorn:2007eu}.
-%when $k=0$ (neo-$Y$ invading a $ZW$ system) or when $k=1$ (neo-$W$ invading an $XY$ system) (\textcolor{red}{CHECK}).
-%However, with haploid selection or meiotic drive a stable polymorphism at locus \textbf{A} no longer requires sexually antagonistic selection.
-%, as it can also be achieved by ploidally-antagonistic selection.
-
 \subsection*{Turnover between sex-determination systems} 
@@
 Therefore, the invasion of rare mutant neo-Y or neo-W alleles can be simplified and given by the largest eigenvalue that solves the quadratic characteristic polynomial
-
-\begin{equation}
-\lambda^2+ b \lambda + c =0
-\label{eq:charpoly_neoY}
-\end{equation}
-
-\noindent
+$\lambda^2+ b \lambda + c =0$,
+%\begin{equation}
+%\lambda^2+ b \lambda + c =0
+%\label{eq:charpoly_neoY}
+%\end{equation}
+%
+%\noindent
 where $b$ is the average of the growth rates of the two haplotypes that carry the $m$ allele ($mA$ and $ma$), $b=(\lambda_{mA}+\lambda_{ma})/2$, and $c$ also involves the fitness of $m$ alleles when they recombine onto the other \textbf{A} background in a heterozygote, $c=\lambda_{mA}\lambda_{ma}+\rho_{mA}\rho_{ma}$ (see table \ref{tab:haplotype_growth}).
@@
 \smallskip
-\caption{Parameters determining invasion (equation \ref{eq:charpoly_neoY}) for neo-Y or neo-W alleles}
+%\caption{Parameters determining invasion (equation \ref{eq:charpoly_neoY}) for neo-Y or neo-W alleles}
+\caption{Parameters determining invasion for neo-Y or neo-W alleles}
 \begin{tabular}{l}
@@
 \end{threeparttable}
-
-Equation \eqref{eq:charpoly_neoY} and table \ref{tab:haplotype_growth} illustrate a number of key points about the invasion of neo-Y and neo-W mutations. 
-For a neo-Y, invasion depends on the relative lifetime fitness of $A$-bearing and $a$-bearing male gametes (i.e., in sperm only). 
+\\
+
+Table \ref{tab:haplotype_growth} illustrates a number of key points about the invasion of neo-Y and neo-W mutations. 
+For a neo-Y, invasion depends on the relative lifetime fitness of $A$-bearing and $a$-bearing male gametes (i.e., sperm only). 
 The lifetime fitness of male gametes partly depends on the allele carried by the female gamete that they mate with (e.g., $A$ with probability $p_{X}^{\female} w_{A}^{\female}/\bar{w}_{H}^{\female}$).
-Similarly, invasion of a neo-W depends on the relative lifetime fitness of $A$-bearing and $a$-bearing female gametes (i.e., in eggs only). 
+Similarly, invasion of a neo-W depends on the relative lifetime fitness of $A$-bearing and $a$-bearing female gametes (i.e., eggs only). 
 However, in the case of a neo-W, the allele carried by the male gamete that they mate with can come from either an X-bearing or a Y-bearing sperm (e.g., $A$ with probability $\bar{p}^{\male} w_{A}^{\male}/\bar{w}_{H}^{\male}$).
@@
 
-We are particularly concerned with whether or not a rare neo-sex-determining allele increases in frequency, which occurs when the largest eigenvalue, $\lambda$, that solves \eqref{eq:charpoly_neoY} is greater than one.
-If the average change in frequency of the two haplotypes that carry the $m$ allele ($Am$ and $am$) is positive, invasion will always occur (if $\left\{(\lambda_{mA}-1)+ (\lambda_{ma}-1) \right\}/2 > 0$, $\lambda > 1$).
+We are particularly concerned with whether or not a rare neo-sex-determining allele increases in frequency, which occurs when the largest eigenvalue, $\lambda$, is greater than one. 
+If the average change in frequency of the two haplotypes that carry the $m$ allele ($Am$ and $am$) is positive, invasion will always occur (i.e., if $\left\{(\lambda_{mA}-1)+ (\lambda_{ma}-1) \right\}/2 > 0$ then $\lambda > 1$).
 If neither haplotype increases in frequency ($\lambda_{mA}, \lambda_{ma} < 1$), the $m$ allele will not invade. 
@@
 \frac{p^\female_X w^\female_A w^\male_a (1-\alpha^\male)}{ \bar{w}^\female_H \bar{w}^\male_H (\lambda_{mA}-1)} + 
-\frac{(1 - p^\female_X) w^\female_a w^\male_A \alpha^\male}{ \bar{w}^\female_H \bar{w}^\male_H (\lambda_{ma}-1)} \right] 
+%p^\female_X \frac{w^\female_A}{\bar{w}^\female_H} \frac{w^\male_a(1-\alpha^\male)}{\bar{w}^\male_H} \frac{1}{\lambda_{mA}-1} + 
+\frac{(1 - p^\female_X) w^\female_a w^\male_A \alpha^\male}{ \bar{w}^\female_H \bar{w}^\male_H (\lambda_{ma}-1)} 
+\right] 
 \frac{w^\male_{Aa}}{\bar{w}^\male} < 1,
@@
 \frac{\bar{p}^\male w^\male_A w^\female_a (1-\alpha^\female)}{ \bar{w}^\male_H \bar{w}^\female_H (\lambda_{mA}-1)} + 
-\frac{(1 - \bar{p}^\male) w^\male_a w^\female_A \alpha^\female}{ \bar{w}^\male_H \bar{w}^\female_H (\lambda_{ma}-1)} \right] 
+\frac{(1 - \bar{p}^\male) w^\male_a w^\female_A \alpha^\female}{ \bar{w}^\male_H \bar{w}^\female_H (\lambda_{ma}-1)} 
+\right] 
 \frac{w^\male_{Aa}}{\bar{w}^\male} < 1,
@@
 \noindent
-\textcolor{red}{FIX THESE EQUATIONS... i changed them a little, is this okay now? (mmo)}
 for the neo-$W$.
@@
 However, if there is any haploid selection, the additional term in equation \eqref{eq:lambda_neoW} can be positive, which can allow invasion ($\lambda_{W',XY}>1$) even when the neo-sex-determining region is less closely linked to the selected locus ($R>r$).
-These transitions are unusual because, when $R>r$, associations that build up by selection between sex and alleles will be weakened. 
-Therefore, mean fitness can decrease, see Figure \ref{fig:Combination_MeanFit}.
+These transitions are unusual because, when $R>r$, associations that build up by selection between sex and selected alleles will be weakened. 
+Therefore, mean fitness can decrease, see Figure \ref{fig:Combination_MeanFit}B,D.
 
@@
 Firstly, if the \textbf{A} locus is unlinked to the ancestral sex-determining region ($r=1/2$), a more closely linked neo-W ($R<1/2$) can always invade because $\left( \hat{p}^\male_Y-\hat{p}^\male_X \right)=0$ such that the second term in \eqref{eq:lambda_neoW} disappears and invasion depends on the sign of $(r-R)$.
-Indeed, invasion typically occurs when the neo-W is more closely linked to the selected locus than the ancestral sex-determining region, Figure \ref{fig:Combination_Centimorgans}.
+Indeed, invasion typically occurs when the neo-W is more closely linked to the selected locus than the ancestral sex-determining region (Figure \ref{fig:Combination_Centimorgans}).
 Secondly, we can simplify cases where $R>r$ using the special case where $R=1/2$ and $r<1/2$. 
@@
 Thus, if the zygotic sex ratio is crucial to the evolution of new genetic sex-determining systems, invasion into ZW and XY systems will be distinct. 
-However, we find that invasion by a homogametic neo-sex-determining allele (XY to XY, or ZW to ZW) or by a heterogametic neo-sex-determining allele (XY to ZW or ZY to XY) occur under the same conditions.
-That is, we can show that $\lambda_{Y',XY}=\lambda_{W',ZW}$ and $\lambda_{Y',ZW}=\lambda_{W',XY}$, for a numerical example, compare Figure \ref{fig:Combination_Turnover}A,B to Figure \ref{fig:Combination_Turnover}C,D.
+However, we find that invasion by a homogametic neo-sex-determining allele (XY to XY, or ZW to ZW) or by a heterogametic neo-sex-determining allele (XY to ZW or ZW to XY) occur under the same conditions.
+That is, we can show that $\lambda_{Y',XY}=\lambda_{W',ZW}$ and $\lambda_{Y',ZW}=\lambda_{W',XY}$ (for a numerical example, compare Figure \ref{fig:Combination_Turnover}A,B to Figure \ref{fig:Combination_Turnover}C,D).
 
@@
 
-The growth rate of a rare, dominant offspring-controlled neo-ESD region that produces males or females with equal probability ($k=1/2$) is
+Perhaps sex ratio selection can be invoked only when the invading mutation arises half the time in males and half the time in females, like an autosomal locus.
+If so, then we should see sex ratio influence the invasion of a novel sex-determining region that causes half of its carries to become female and half to become male.
+However, we find that the growth rate of a rare, dominant offspring-controlled neo-ESD region that produces males or females with equal probability ($k=1/2$) is
 \begin{equation}
@@
 \end{equation}
-which is the same for invasion into an ancestrally XY or ZW system.
-Thus with $k=1/2$ the neo-ESD gets half of the advantages of a neo-$W$ and half that of a neo-$Y$, but only has an effect one half of the time (the other half of the time it produces the same sex as the ancestral system would have).
+which is the same for invasion into an ancestrally XY or ZW system (since $\lambda_{Y,XY} = \lambda_{W,ZW}$, $\lambda_{W,XY} = \lambda_{Y,ZW}$).
+Thus by the same argument as above (if drive in males only then sex ratio only biased when ancestrally XY), sex ratio selection does not drive the turnover to a perfect ($k=1/2$), offspring-controlled neo-ESD.
+Also note that with $k=1/2$ the neo-ESD gets half of the advantages of a neo-$W$ and half that of a neo-$Y$, but only has an effect one half of the time (the other half of the time it produces the same sex as the ancestral system would have).
 Recombination between the selected locus and the novel sex-determining locus, $R$, doesn't enter into the $k=1/2$ results because sex is essentially randomized each generation, %as if the novel sex-determiner were on an unlinked site that half the time acts as a neo-$W$ and half the time as a neo-$Y$.
@@
 
-Depends 50\% on its fitness relative to non-mutant males and 50\% on its fitness relative to non-mutant females.
+%Depends 50\% on its fitness relative to non-mutant males and 50\% on its fitness relative to non-mutant females.
 
@@
 
+%I think this should be moved below because we have some 'results' where we don't assume weak selection but we only have the equilibrium calculated analytically for weak selection. 
+\subsection*{Resident equilibrium and stability}
+In the resident population (allele $M$ fixed), we follow the frequency of $A$ in female gametes (eggs) from an XX female, $p^\female_X$, and in X-bearing, $p^\male_X$, and Y-bearing, $p^\male_Y$, male gametes (sperm).
+We also track the total frequency of Y-bearing male gametes, $q$, which may deviate from $1/2$ due to meiotic drive in males.
+
+Various forms of selection can maintain a polymorphism at the \textbf{A} locus, including sexually antagonistic selection, overdominance and conflicts between diploid selection and selection upon haploid genotypes \citep[ploidally antagonistic selection,][]{Immler:2012tl} or a combination of these selective regimes.
+Here, we assume that selection and meiotic drive are weak relative to recombination ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon$). 
+The maintenance of a polymorphism at the \textbf{A} locus then requires that
+
+\begin{equation}
+\begin{split}
+0&<-((1-h^\female)s^\female +(1-h^\male) s^\male + t^\female +t^\male + \alpha_{\Delta}^\female+\alpha_{\Delta}^\male)\\
+%
+0&<(h^\female s^\female +h^\male s^\male + t^\female +t^\male + \alpha_{\Delta}^\female+\alpha_{\Delta}^\male).
+\end{split}
+\end{equation}
+
+\noindent
+which indicates that a polymorphism is maintained under various selective regimes. 
+In particular special cases, e.g., no sex-differences in selection or meiotic drive ($s^\male=s^\female$, $h^\male=h^\female$, and $\alpha^\male=\alpha^\female=1/2$), the equilibrium allele frequency and stability can be calculated analytically without assuming weak selection.
+However, here, we focus on weak selection in order to make fewer assumptions about fitnesses.
+
+Given that a polymorphism is maintained at the \textbf{A} locus by selection, with weak selection and drive, to leading order, the frequencies of $A$ in each type of gamete are the same ($\hat{p}^\female_X=\hat{p}^\male_X=\hat{p}^\male_Y=\bar{p}$) and given by
+
+\begin{equation}
+\bar{p}=\frac{h^\female s^\female + h^\male s^\male +t^\female+t^\male+\alpha_{\Delta}^\female+\alpha_{\Delta}^\male}
+{(2h^\female-1)s^\female+(2h^\male-1)s^\male}
++O(\epsilon)
+.
+\label{eq:pAve}
+\end{equation}
+
+\noindent
+Differences in frequency between gamete types are of order $\epsilon$ to leading order and given by
+
+\begin{equation}
+\begin{split}
+\hat{p}^\male_X-\hat{p}^\female_X&=V_{A}\big{(}D^\male - D^\female +\alpha_{\Delta}^\male-\alpha_{\Delta}^\female \big{)}
++O(\epsilon^2)\\
+%
+\hat{p}^\male_Y-\hat{p}^\female_X&=V_{A}\big{(}D^\male - D^\female+\alpha_{\Delta}^\male-\alpha_{\Delta}^\female+(1-2r)(t^\male-t^\female)\big{)}/2r
++O(\epsilon^2)\\
+%
+\hat{p}^\male_Y-\hat{p}^\male_X&=V_{A}\big{(}D^\male - D^\female+\alpha_{\Delta}^\male-\alpha_{\Delta}^\female+t^\male-t^\female\big{)}(1-2r)/2r
++O(\epsilon^2)
+\end{split}
+\label{eq:freq_diffs}
+\end{equation}
+
+\noindent
+where $V_{A}=\bar{p}(1-\bar{p})$ is the variance in the frequency of $A$ and $D^\Hermaphrodite=\big{(} \bar{p}s^\Hermaphrodite+(1-\bar{p})h^\Hermaphrodite s^\Hermaphrodite\big{)} -\big{(} \bar{p}h^\Hermaphrodite s^\Hermaphrodite+(1-\bar{p}) \big{)}$ corresponds to the difference in fitness between $A$ and $a$ alleles in diploids of sex $\Hermaphrodite \in \{\female,\male\}$ ($\bar{p}$ is the leading-order probability of mating with an $A$-bearing gamete from the opposite sex).
+The frequency of Y among male gametes depends upon the difference in $A$ allele frequency on X- and Y-bearing male gametes and the strength of meiotic drive in favour of the $A$ allele in males, $q=1/2+\alpha_{\Delta}^\male(\hat{p}^\male_Y-\hat{p}^\male_X)/2+O(\epsilon^3)$.
+Without gametic competition or drive ($\alpha_{\Delta}^\Hermaphrodite=t^\Hermaphrodite=0$), these results reduce to those of \citet{vanDoorn:2007eu}.
+
+% the differences in the frequencies of $A$ in each type of gamete are small, as is the bias in the sex-determining factor from the heterogametic sex, and we can solve for the mean frequency of $A$ across all types ($p_A$), the difference in the frequencies of $A$ between two of the three types, and the bias in the frequency of the sex-determining factor, to first order in selection.
+%Linear stability analysis can then be used to determine the stability of this equilibrium.
+%Without haploid selection or meiotic drive our results reduce to those of \cite{vanDoorn:2007eu}.
+%when $k=0$ (neo-$Y$ invading a $ZW$ system) or when $k=1$ (neo-$W$ invading an $XY$ system) (\textcolor{red}{CHECK}).
+%However, with haploid selection or meiotic drive a stable polymorphism at locus \textbf{A} no longer requires sexually antagonistic selection.
+%, as it can also be achieved by ploidally-antagonistic selection.
+
 \newpage
+
+\section*{Supplementary Figures}
 

### 2017-02-03 LaTeX/Turnover.tex
matt version updated to match text, but still only one order of loci

@@
 Furthermore, if the $m$ allele is fully dominant over the ancestral sex-determining system, phenotypes are not affected by the genotype at the ancestral sex-determining region (\textbf{X} locus). 
-Therefore, the invasion of rare mutant neo-Y or neo-W alleles can be simplified and given by the largest eigenvalue that solves the quadratic characteristic polynomial
-$\lambda^2+ b \lambda + c =0$,
+Therefore, the invasion of rare dominant neo-Y or neo-W alleles depends on only two equations and is therefore determined by the largest eigenvalue that solves the quadratic characteristic polynomial
+$\lambda^2+ b \lambda + c =0$.
 %\begin{equation}
@@
 %\noindent
-where $b$ is the average of the growth rates of the two haplotypes that carry the $m$ allele ($mA$ and $ma$), $b=(\lambda_{mA}+\lambda_{ma})/2$, and $c$ also involves the fitness of $m$ alleles when they recombine onto the other \textbf{A} background in a heterozygote, $c=\lambda_{mA}\lambda_{ma}+\rho_{mA}\rho_{ma}$ (see table \ref{tab:haplotype_growth}).
+%where $b$ is the average of the growth rates of the two haplotypes that carry the $m$ allele ($mA$ and $ma$), $b=(\lambda_{mA}+\lambda_{ma})/2$, and $c$ also involves the fitness of $m$ alleles when they recombine onto the other \textbf{A} background in a heterozygote, $c=\lambda_{mA}\lambda_{ma}+\rho_{mA}\rho_{ma}$ (see table \ref{tab:haplotype_growth}).
+In this case $b= - (\lambda_{mA} + \lambda_{ma})$ and $c = \lambda_{mA} \lambda_{ma} -\rho_{mA} \rho_{ma}$, where $2\lambda_{mi}-1$ is the growth rate of mutant haplotypes on background $i\in\{A,a\}$, accounting for loss due to recombination in heterozygotes, and $\rho_{mi}-1$ is the rate of addition of mutant haplotypes onto background $i\in\{A,a\}$ due to recombination in heterozygotes (see table \ref{tab:haplotype_growth}).
+\textcolor{red}{check these interpretations as there are weird 2s in table 2}
 
@@
 %\caption{Parameters determining invasion (equation \ref{eq:charpoly_neoY}) for neo-Y or neo-W alleles}
-\caption{Parameters determining invasion for neo-Y or neo-W alleles}
+\caption{Parameters determining invasion of neo-Y or neo-W alleles into ancestral XY system}
 \begin{tabular}{l}
@@
    neo-Y ($k=0$) \\ [0.5ex] \hline \noalign{\vskip 1ex}
-  $\lambda_{mA}=\{p_{X}^{\female} w_{A}^{\female} w_{A}^{\male} w_{AA}^{\male}+(1-p_{X}^{\female}) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male}\alpha^\male(1-R)\}/ \{ \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\male\} $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\lambda_{ma}=\{(1-p_{X}^{\female}) w_{a}^{\female} w_{a}^{\male} w_{aa}^{\male}+p_{X}^{\female} w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male}(1-\alpha^\male)(1-R)\}/ \{ \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\male \}$ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\rho_{mA}=R (1-p_{X}^{\female}) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} (1-\alpha^{\male})/ \{ \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\male \} $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\rho_{ma}=R p_{X}^{\female} w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male} \alpha^{\male}/ \{ \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\male \}$\\ [1ex] \hline 
+  $\lambda_{mA}=\{p_{X}^{\female} w_{A}^{\female} w_{A}^{\male} w_{AA}^{\male}+2(1-p_{X}^{\female}) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male}\alpha^\male(1-R)\}/ \{ 2 \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\male\} $\\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\lambda_{ma}=\{(1-p_{X}^{\female}) w_{a}^{\female} w_{a}^{\male} w_{aa}^{\male}+2p_{X}^{\female} w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male}(1-\alpha^\male)(1-R)\}/ \{ 2 \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\male \}$ \\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\rho_{mA}=R (1-p_{X}^{\female}) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} \alpha^{\male}/ \{ \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\male \} $\\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\rho_{ma}=R p_{X}^{\female} w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male} (1 - \alpha^{\male})/ \{ \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\male \}$\\ [1ex] \hline 
   \noalign{\vskip 0.5ex}
   neo-W ($k=1$) \\ [0.5ex] \hline \noalign{\vskip 1ex}
-  $\lambda_{mA}=\{\bar{p}^{\male} w_{A}^{\male} w_{A}^{\female} w_{AA}^{\female}+(1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female}\alpha^\female(1-R)\}/ \{ \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\female \}$ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\lambda_{ma}=\{(1-\bar{p}^{\male}) w_{a}^{\male} w_{a}^{\female} w_{aa}^{\female}+\bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female}(1-\alpha^\female)(1-R)\}/ \{\bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\female \}$ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\rho_{mA}=R (1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female} (1-\alpha^{\female})/ \{\bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\female \} $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\rho_{ma}=R\bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female} \alpha^{\female}/ \{\bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\female \}$\\ [1ex] 
+  $\lambda_{mA}=\{\bar{p}^{\male} w_{A}^{\male} w_{A}^{\female} w_{AA}^{\female}+2(1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female}\alpha^\female(1-R)\}/ \{ 2 \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\female \}$ \\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\lambda_{ma}=\{(1-\bar{p}^{\male}) w_{a}^{\male} w_{a}^{\female} w_{aa}^{\female}+2\bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female}(1-\alpha^\female)(1-R)\}/ \{2 \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\female \}$ \\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\rho_{mA}=R (1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female} \alpha^{\female}/ \{\bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\female \} $\\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\rho_{ma}=R\bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female} (1-\alpha^{\female})/ \{\bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\female \}$\\ [1ex] 
   \hline \hline 
@@
       \scriptsize
-      \item $\bar{p}^{\male}=p_{Y}^{\male}q+p_{X}^{\male}(1-q)$ is the average frequency of the $A$ allele among X- and Y-bearing male gametes 
-      \item see Table \ref{tab:meanfitnesses} for mean fitnesses.
+      \item $\bar{p}^{\male}=p_{Y}^{\male}q+p_{X}^{\male}(1-q)$ is the average frequency of the $A$ allele among X- and Y-bearing male gametes.
+      \item See Table \ref{tab:meanfitnesses} for expressions of mean fitnesses.
 %      \item $\bar{w}_H^\female = p_X^\female w_A^\female + (1-p_X^\female) w_a^\female$ is the mean fitness of female gametes during gametic competition
@@
 \begin{equation}
-\lambda_{Y',XY} =1+ \frac{V_{A} \left( r-R \right)(S_{A})^2 }{r R}+O\left(\epsilon^3 \right) 
+\lambda_{Y',XY} =1+ V_{A}S_{A}^2\frac{ \left( r-R \right) }{r R}+O\left(\epsilon^3 \right) 
 \label{eq:lambda_neoY}
@@
 \begin{equation}
-\lambda_{W',XY} =\lambda_{Y',XY}+\left(2\alpha_{\Delta}^\male-2\alpha_{\Delta}^\female+t^\male-t^\female \right) \left( \hat{p}^\male_Y-\hat{p}^\male_X \right)
+\lambda_{W',XY} =\lambda_{Y',XY}+\left(2\alpha_{\Delta}^\male-2\alpha_{\Delta}^\female+t^\male-t^\female \right) \left( \hat{p}^\male_Y-\hat{p}^\male_X \right)/2
 +O\left(\epsilon^3 \right) \\
@@
 The neo-sex-determining allele $m$ will spread if $\lambda_{m,XY}>1$. 
-Equation \eqref{eq:lambda_neoY} demonstrates that a neo-Y will invade if and only if it is more closely linked to the selected locus than the ancestral sex-determining region (i.e., if $R<r$, note that $V_{A}$ and $(S_{A})^2$ are strictly positive).
+Equation \eqref{eq:lambda_neoY} demonstrates that a neo-Y will invade if and only if it is more closely linked to the selected locus than the ancestral sex-determining region (i.e., if $R<r$, note that $V_{A}$ and $S_{A}^2$ are strictly positive).
 This result echoes that of \citet{vanDoorn:2007eu}, who considered diploid selection only and also found that homogametic transitions (XY to XY or ZW to ZW) can occur when the neo-sex-determining locus is more closely linked to a locus under sexually-antagonistic selection.
@@
 
-If there is no selection upon haploid genotypes ($t^\Hermaphrodite=\alpha^\Hermaphrodite_{\Delta}=0$), as considered by \citet{vanDoorn:2010hu}, the spread of a neo-W is equivalent to the spread of a neo-Y ($\lambda_{W',XY}=\lambda_{Y',XY}$) such that heterogametic transitions (XY to ZW or ZW to XY) can also occur only if the neo-sex-determining region is more closely linked to a locus under selection ($R<r$).
-However, if there is any haploid selection, the additional term in equation \eqref{eq:lambda_neoW} can be positive, which can allow invasion ($\lambda_{W',XY}>1$) even when the neo-sex-determining region is less closely linked to the selected locus ($R>r$).
+Equation \eqref{eq:lambda_neoW} shows that if there is no selection upon haploid genotypes ($t^\Hermaphrodite=\alpha^\Hermaphrodite_{\Delta}=0$), as considered by \citet{vanDoorn:2010hu}, the spread of a neo-W is equivalent to the spread of a neo-Y ($\lambda_{W',XY}=\lambda_{Y',XY}$) such that heterogametic transitions (XY to ZW or ZW to XY) can also occur only if the neo-sex-determining region is more closely linked to a locus under selection ($R<r$).
+However, if there is any haploid selection, the additional term in equation \eqref{eq:lambda_neoW} can be positive, which can allow neo-W invasion ($\lambda_{W',XY}>1$) even when the neo-sex-determining region is less closely linked to the selected locus ($R>r$).
 These transitions are unusual because, when $R>r$, associations that build up by selection between sex and selected alleles will be weakened. 
@@
 To clarify the parameter space under which $\lambda_{W',XY}>1$, we consider several special cases. 
-Firstly, if the \textbf{A} locus is unlinked to the ancestral sex-determining region ($r=1/2$), a more closely linked neo-W ($R<1/2$) can always invade because $\left( \hat{p}^\male_Y-\hat{p}^\male_X \right)=0$ such that the second term in \eqref{eq:lambda_neoW} disappears and invasion depends on the sign of $(r-R)$.
+Firstly, if the \textbf{A} locus is unlinked to the ancestral sex-determining region ($r=1/2$), a more closely linked neo-W ($R<1/2$) can always invade because $\left( \hat{p}^\male_Y-\hat{p}^\male_X \right)=0$ such that the second term in equation \eqref{eq:lambda_neoW} disappears and invasion depends only on the sign of $(r-R)$.
 Indeed, invasion typically occurs when the neo-W is more closely linked to the selected locus than the ancestral sex-determining region (Figure \ref{fig:Combination_Centimorgans}).
-Secondly, we can simplify cases where $R>r$ using the special case where $R=1/2$ and $r<1/2$. 
-In table \ref{tab:specialcases} we give the conditions where invasion occurs where we further assume that haploid selection only occurs during one phase in one sex (e.g., during male meiosis only) and equal dominance, $h^\female=h^\male$.
+Secondly, we can simplify cases where invasion occurs despite $R>r$ using the special case where $R=1/2$ and $r<1/2$. 
+In table \ref{tab:specialcases} we give the conditions where invasion occurs where we further assume that haploid selection only occurs during one phase in one sex (e.g., during male meiosis only) and dominance coefficients are equal in the two sexes, $h^\female=h^\male$.
 Where there is no gametic competition and meiotic drive in one sex only, an unlinked neo-W can invade as long as the same allele is favoured in male and female diploid selection ($s^\female s^\male>0$, see Figure \ref{fig:Combination_Centimorgans}B), which is 50\% of the parameter space.
 Where there is no meiotic drive and gametic competition occurs in one sex only, an unlinked neo-W can invade as long as the same allele is favoured in male and female diploid selection and there are sex differences in selection of one type ($s^\female(s^\male-s^\female)>0$, see Figure \ref{fig:Combination_Centimorgans}C,D), which is 25\% of the parameter space.
-These special cases indicate that neo-W invasion can occur for a relatively large fraction of parameter space, even if $R>r$.
+These special cases indicate that neo-W invasion can occur for a relatively large fraction of parameter space, even if the neo-W is less tightly linked to the selected locus, $R>r$.
 
@@
 \smallskip
-\caption{Invasion conditions for unlinked neo-W ($R=1/2$, $r<1/2$) with one form of haploid selection only}
-\begin{tabular}{l c }
+\caption{Invasion conditions for unlinked neo-W ($R=1/2$, $r<1/2$) into ancestral XY with one form of haploid selection}
+\begin{tabular}{l l c }
 \hline\hline
-  Assumptions & neo-W spreads ($\lambda_{W',XY}>1$) if \\ [0.5ex] \hline
+Scenario &  Assumptions & neo-W spreads ($\lambda_{W',XY}>1$) if \\ [0.5ex] \hline
 %  $r=1/2$, $R<1/2$ & Always \\ [0.5ex] \hline
 %  $r<1/2$, $R=1/2$ &  \\ [0.5ex] \hline
-  $h^\male=h^\female$, $t^\female=t^\male=\alpha^\female_{\Delta}=0$ & $s^\female s^\male>0$ \\
-  $h^\male=h^\female$, $t^\female=t^\male=\alpha^\male_{\Delta}=0$ & $s^\female s^\male>0$ \\
-  $h^\male=h^\female$, $t^\female=\alpha^\female_{\Delta}=\alpha^\male_{\Delta}=0$ & $s^\female(s^\male-s^\female)>0$ \\
-  $h^\male=h^\female$, $t^\male=\alpha^\female_{\Delta}=\alpha^\male_{\Delta}=0$ & $s^\male(s^\female-s^\male)>0$ \\
+  male drive only & $h^\male=h^\female$, $t^\female=t^\male=\alpha^\female_{\Delta}=0$ & $s^\female s^\male>0$ \\
+ female drive only & $h^\male=h^\female$, $t^\female=t^\male=\alpha^\male_{\Delta}=0$ & $s^\female s^\male>0$ \\
+ sperm competition only &  $h^\male=h^\female$, $t^\female=\alpha^\female_{\Delta}=\alpha^\male_{\Delta}=0$ & $s^\female(s^\male-s^\female)>0$ \\
+  egg competition only & $h^\male=h^\female$, $t^\male=\alpha^\female_{\Delta}=\alpha^\male_{\Delta}=0$ & $s^\male(s^\female-s^\male)>0$ \\
   \hline \hline
@@
 However, we find that invasion by a homogametic neo-sex-determining allele (XY to XY, or ZW to ZW) or by a heterogametic neo-sex-determining allele (XY to ZW or ZW to XY) occur under the same conditions.
-That is, we can show that $\lambda_{Y',XY}=\lambda_{W',ZW}$ and $\lambda_{Y',ZW}=\lambda_{W',XY}$ (for a numerical example, compare Figure \ref{fig:Combination_Turnover}A,B to Figure \ref{fig:Combination_Turnover}C,D).
+That is, we can show that $\lambda_{Y',XY}=\lambda_{W',ZW}$ and $\lambda_{Y',ZW}=\lambda_{W',XY}$ (at least up to order $\epsilon^3$; for a numerical example, compare Figure \ref{fig:Combination_Turnover}A,B to Figure \ref{fig:Combination_Turnover}C,D).
 
@@
 Perhaps sex ratio selection can be invoked only when the invading mutation arises half the time in males and half the time in females, like an autosomal locus.
-If so, then we should see sex ratio influence the invasion of a novel sex-determining region that causes half of its carries to become female and half to become male.
-However, we find that the growth rate of a rare, dominant offspring-controlled neo-ESD region that produces males or females with equal probability ($k=1/2$) is
-\begin{equation}
-\lambda_{ESD} \approx 1 + \frac{1}{2}\frac{(\lambda_{Y,XY} - 1) + (\lambda_{W,XY} -1)}{2} \Big|_{R=1/2},
+If so, then we should see sex ratio influence the invasion of a novel sex-determining region that causes half of its carries to become female and half to become male (i.e., a perfect environmental sex determiner, ESD).
+However, we find that under weak selection the growth rate of a rare, dominant offspring-controlled neo-ESD allele that produces males or females with equal probability ($k=1/2$) is
+\begin{equation}
+\lambda_{ESD'} = 1 + \frac{1}{2}\frac{(\lambda_{Y',XY} - 1) + (\lambda_{W',XY} -1)}{2} \Big|_{R=1/2} + O\left(\epsilon^3\right),
 %V_A \frac{r}{1-2r}  \frac{s_{f} \left( s^\male - 3 s^\female\right) }{8 \left( s_{f} + s_{m} \right)^2} t_{m}^2.
@@
 \end{equation}
-which is the same for invasion into an ancestrally XY or ZW system (since $\lambda_{Y,XY} = \lambda_{W,ZW}$, $\lambda_{W,XY} = \lambda_{Y,ZW}$).
-Thus by the same argument as above (if drive in males only then sex ratio only biased when ancestrally XY), sex ratio selection does not drive the turnover to a perfect ($k=1/2$), offspring-controlled neo-ESD.
+which is the same for invasion into an ancestrally XY or ZW system (since $\lambda_{Y',XY} = \lambda_{W',ZW}$, $\lambda_{W',XY} = \lambda_{Y',ZW}$).
+Thus by the same argument as above (if drive occurs in males only then the sex ratio is only biased when the ancestral sex-determination system is XY), sex ratio selection does not drive the turnover from genetic sex determination to offspring-controlled neo-ESD.
+
 Also note that with $k=1/2$ the neo-ESD gets half of the advantages of a neo-$W$ and half that of a neo-$Y$, but only has an effect one half of the time (the other half of the time it produces the same sex as the ancestral system would have).
@@
 One might think that when the sex of zygotes is under the control of mothers, there would be strong selection to balance the sex ratio among zygotes. 
-However, we find that, as with offspring control, under weak selection the invasion fitness of a sex-determiner that is maternally controlled can be written
-\begin{equation}
-\lambda_{k,XY} \approx 1 + V_A S_A C_k,
+However, we find that, with no meiotic drive and weak selection, the invasion fitness of a dominant, maternally controlled sex-determiner that produces proportion $k$ daughters can be written
+\begin{equation}
+\lambda_{k} = 1 + V_A S_A C_k + O\left(\epsilon^3\right),
 \end{equation}
@@
 %However, with $k\neq1$ the results with maternal control differ from those with offspring control.
-Of particular interest is $k=1/2$ (i.e., when the mother perfectly balances the sex ratio of her offspring).
-When both recombination rates are small we have $C_{1/2} \approx R(s^\male - s^\female)/8 = \lim_{r \rightarrow 0} C_1/4$.
-This implies that, at least under tight linkage, the invasion of maternally-controlled ESD is independent of $R$ (because $S_A\propto R^{-1}$) and can invade whenever a neo-$W$ can (which can invade even when it biases the sex ratio further; Figures \ref{fig:WinvasionLowR} -- \ref{fig:WinvasionHighR}).
+Interestingly, for all $k\in\{0,1/2,1\}$, we find that invasion into an ancestrally XY system is the same as invasion into an ancestrally ZW system (at least up to order $\epsilon^3$), implying that sex ratio selection does not drive transitions between genetic sex determination and maternally controlled environmental sex determination.
+%Of particular interest is $k=1/2$ (i.e., when the mother perfectly balances the sex ratio of her offspring).
+%When both recombination rates are small we have $C_{1/2} \approx R(s^\male - s^\female)/8 = \lim_{r \rightarrow 0} C_1/4$.
+%This implies that, at least under tight linkage, the invasion of maternally-controlled ESD is independent of $R$ (because $S_A\propto R^{-1}$) and can invade whenever a neo-$W$ can (which can invade even when it biases the sex ratio further; Figures \ref{fig:WinvasionLowR} -- \ref{fig:WinvasionHighR}).
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
+\begin{figure}[!h]
 \centering

### 2017-02-04 LaTeX/Turnover.tex
generic loci order in Matt version analysis

@@
 %where $b$ is the average of the growth rates of the two haplotypes that carry the $m$ allele ($mA$ and $ma$), $b=(\lambda_{mA}+\lambda_{ma})/2$, and $c$ also involves the fitness of $m$ alleles when they recombine onto the other \textbf{A} background in a heterozygote, $c=\lambda_{mA}\lambda_{ma}+\rho_{mA}\rho_{ma}$ (see table \ref{tab:haplotype_growth}).
-In this case $b= - (\lambda_{mA} + \lambda_{ma})$ and $c = \lambda_{mA} \lambda_{ma} -\rho_{mA} \rho_{ma}$, where $2\lambda_{mi}-1$ is the growth rate of mutant haplotypes on background $i\in\{A,a\}$, accounting for loss due to recombination in heterozygotes, and $\rho_{mi}-1$ is the rate of addition of mutant haplotypes onto background $i\in\{A,a\}$ due to recombination in heterozygotes (see table \ref{tab:haplotype_growth}).
-\textcolor{red}{check these interpretations as there are weird 2s in table 2}
+In this case $b= - (\lambda_{mA} + \lambda_{ma})$ and $c = \lambda_{mA} \lambda_{ma} -\rho_{mA} \rho_{ma}$, where $2\lambda_{mi}-1$ is the growth rate of mutant haplotypes on background $i\in\{A,a\}$, accounting for loss due to recombination, and $\rho_{mi}-1$ is the rate of addition of mutant haplotypes onto background $i\in\{A,a\}$ due to recombination (see table \ref{tab:haplotype_growth}).
+\textcolor{red}{check these interpretations as there are now two 2s in the lambdas of table 2.
+perhaps the 2 in the denominator is needed because the frequency of males sums to one as does the frequency of females?
+the two in the numerator is from heterozygotes (like Hardy-Weinberg)?}
 
@@
 %\caption{Parameters determining invasion (equation \ref{eq:charpoly_neoY}) for neo-Y or neo-W alleles}
-\caption{Parameters determining invasion of neo-Y or neo-W alleles into ancestral XY system}
+\caption{Parameters determining invasion of mutant neo-Y and neo-W alleles into an ancestrally XY system}
 \begin{tabular}{l}
@@
    neo-Y ($k=0$) \\ [0.5ex] \hline \noalign{\vskip 1ex}
-  $\lambda_{mA}=\{p_{X}^{\female} w_{A}^{\female} w_{A}^{\male} w_{AA}^{\male}+2(1-p_{X}^{\female}) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male}\alpha^\male(1-R)\}/ \{ 2 \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\male\} $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\lambda_{ma}=\{(1-p_{X}^{\female}) w_{a}^{\female} w_{a}^{\male} w_{aa}^{\male}+2p_{X}^{\female} w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male}(1-\alpha^\male)(1-R)\}/ \{ 2 \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\male \}$ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\rho_{mA}=R (1-p_{X}^{\female}) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} \alpha^{\male}/ \{ \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\male \} $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\rho_{ma}=R p_{X}^{\female} w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male} (1 - \alpha^{\male})/ \{ \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\male \}$\\ [1ex] \hline 
+  $\lambda_{mA}=\{p_{X}^{\female} w_{A}^{\female} w_{A}^{\male} w_{AA}^{\male} + 2(1-p_{X}^{\female}) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} \alpha^\male (1 - r_{AM})\}/ \{ 2 \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\male\} $\\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\lambda_{ma}=\{(1-p_{X}^{\female}) w_{a}^{\female} w_{a}^{\male} w_{aa}^{\male} + 2p_{X}^{\female} w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male}(1 - \alpha^\male) (1 - r_{AM})\}/ \{ 2 \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\male \}$ \\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\rho_{mA}=r_{AM} (1-p_{X}^{\female}) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} \alpha^{\male}/ \{ \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\male \} $\\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\rho_{ma}=r_{AM} p_{X}^{\female} w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male} (1 - \alpha^{\male})/ \{ \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\male \}$\\ [1ex] \hline 
   \noalign{\vskip 0.5ex}
@@
       \item $\bar{p}^{\male}=p_{Y}^{\male}q+p_{X}^{\male}(1-q)$ is the average frequency of the $A$ allele among X- and Y-bearing male gametes.
+      \item $r_{AM}$ is the probability of recombination between loci \textbf{A} and \textbf{M}.
       \item See Table \ref{tab:meanfitnesses} for expressions of mean fitnesses.
@@
 \begin{equation}\label{eq:neoYR}
-R \left[ 
+r_{AM} \left[ 
 \frac{p^\female_X w^\female_A w^\male_a (1-\alpha^\male)}{ \bar{w}^\female_H \bar{w}^\male_H (\lambda_{mA}-1)} + 
@@
 for the neo-$W$.
-Equations \eqref{eq:neoYR} and \eqref{eq:neoWR} show that the new sex-determining allele, $m$, is expected to invade for any recombination rate, $R$, when the net flow of recombinants is from the less fit (smaller $\lambda_{mi}$) to the more fit \textbf{A} background (making the terms inside the square brackets in Equations \ref{eq:neoYR} and \ref{eq:neoWR} negative).
+Equations \eqref{eq:neoYR} and \eqref{eq:neoWR} show that the new sex-determining allele, $m$, is expected to invade for any probability of recombination between loci \textbf{A} and \textbf{M}, $r_{AM}$, when the net flow of recombinants is from the less fit (smaller $\lambda_{mi}$) to the more fit \textbf{A} background (making the terms inside the square brackets in Equations \ref{eq:neoYR} and \ref{eq:neoWR} negative).
 \textcolor{red}{Q: is it definitely possible to have negative square brackets for a equilibria maintained by selection?}
 %Assuming $g_A^* > 0$ and $g_a^* < 0$ without loss of generality, this is $-(1 - p^\female_X) w_{m,A} g_a^* < p^\female_X w_{m,a} g_A^*$.
-When the net flow of recombinants is from the more fit to the less fit haplotype, the new sex-determining allele can still invade when the rate of recombination between it and the selected locus, $R$, is small enough.
-\textcolor{red}{Q:Is it the case that sometimes the square brackets are positive and invasion occurs for $R=1/2$?
+When the net flow of recombinants is from the more fit to the less fit haplotype, the new sex-determining allele can still invade when the rate of recombination between it and the selected locus is small enough.
+\textcolor{red}{Q:Is it the case that sometimes the square brackets are positive and invasion occurs for $r_{AM}=1/2$?
 In which case it might be better to have slightly different phrasing here.}

### 2017-02-06 LaTeX/Turnover.tex
sunday work on general order for matt version

@@
 %where $b$ is the average of the growth rates of the two haplotypes that carry the $m$ allele ($mA$ and $ma$), $b=(\lambda_{mA}+\lambda_{ma})/2$, and $c$ also involves the fitness of $m$ alleles when they recombine onto the other \textbf{A} background in a heterozygote, $c=\lambda_{mA}\lambda_{ma}+\rho_{mA}\rho_{ma}$ (see table \ref{tab:haplotype_growth}).
-In this case $b= - (\lambda_{mA} + \lambda_{ma})$ and $c = \lambda_{mA} \lambda_{ma} -\rho_{mA} \rho_{ma}$, where $2\lambda_{mi}-1$ is the growth rate of mutant haplotypes on background $i\in\{A,a\}$, accounting for loss due to recombination, and $\rho_{mi}-1$ is the rate of addition of mutant haplotypes onto background $i\in\{A,a\}$ due to recombination (see table \ref{tab:haplotype_growth}).
+In this case $b= - (\lambda_{mA} + \lambda_{ma})$ and $c = \lambda_{mA} \lambda_{ma} -\rho_{mA} \rho_{ma}$, where $\lambda_{mi}-1$ is the growth rate of mutant haplotypes on background $i\in\{A,a\}$, accounting for loss due to recombination, and $\rho_{mi}-1$ is the rate of addition of mutant haplotypes onto background $i\in\{A,a\}$ due to recombination (see table \ref{tab:haplotype_growth}).
 \textcolor{red}{check these interpretations as there are now two 2s in the lambdas of table 2.
 perhaps the 2 in the denominator is needed because the frequency of males sums to one as does the frequency of females?
-the two in the numerator is from heterozygotes (like Hardy-Weinberg)?}
+the two in the numerator is from heterozygotes (like Hardy-Weinberg)?
+should we absorb it into the drive or recombination term?}
 
@@
 By contrast, females that do not carry the neo-W only result from matings with X-bearing sperm (e.g., matings with $A$-bearing sperm occur with probability $\bar{p}_{X}^{\male} w_{A}^{\male}/\bar{w}_{H}^{\male}$).
-If the \textbf{A} locus is initially linked to the ancestral sex-determining locus, \textbf{X}, (i.e., $r<1/2$) the frequency of the $A$ allele among X- and Y-bearing sperm can differ (equation \ref{eq:freq_diffs}).
+If the \textbf{A} locus is initially linked to the ancestral sex-determining locus, \textbf{X}, the frequency of the $A$ allele among X- and Y-bearing sperm can differ (equation \ref{eq:freq_diffs}). 
 Thus, eggs with and without a neo-W differ in the frequency of $A$ alleles they obtain from mating with male gametes.

### 2017-02-06 LaTeX/Turnover.tex
Matt analysis of offspring control with general loci order done

@@
    neo-Y ($k=0$) \\ [0.5ex] \hline \noalign{\vskip 1ex}
-  $\lambda_{mA}=\{p_{X}^{\female} w_{A}^{\female} w_{A}^{\male} w_{AA}^{\male} + 2(1-p_{X}^{\female}) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} \alpha^\male (1 - r_{AM})\}/ \{ 2 \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\male\} $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\lambda_{ma}=\{(1-p_{X}^{\female}) w_{a}^{\female} w_{a}^{\male} w_{aa}^{\male} + 2p_{X}^{\female} w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male}(1 - \alpha^\male) (1 - r_{AM})\}/ \{ 2 \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\male \}$ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\rho_{mA}=r_{AM} (1-p_{X}^{\female}) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} \alpha^{\male}/ \{ \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\male \} $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\rho_{ma}=r_{AM} p_{X}^{\female} w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male} (1 - \alpha^{\male})/ \{ \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\male \}$\\ [1ex] \hline 
+  $\lambda_{mA}=\{p_{X}^{\female} w_{A}^{\female} w_{A}^{\male} w_{AA}^{\male} + 2(1-p_{X}^{\female}) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} \alpha^\male (1 - R)\}/ \{ 2 \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\male\} $\\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\lambda_{ma}=\{(1-p_{X}^{\female}) w_{a}^{\female} w_{a}^{\male} w_{aa}^{\male} + 2p_{X}^{\female} w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male}(1 - \alpha^\male) (1 - R)\}/ \{ 2 \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\male \}$ \\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\rho_{mA}=R (1-p_{X}^{\female}) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} \alpha^{\male}/ \{ \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\male \} $\\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\rho_{ma}=R p_{X}^{\female} w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male} (1 - \alpha^{\male})/ \{ \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\male \}$\\ [1ex] \hline 
   \noalign{\vskip 0.5ex}
@@
       \item $\bar{p}^{\male}=p_{Y}^{\male}q+p_{X}^{\male}(1-q)$ is the average frequency of the $A$ allele among X- and Y-bearing male gametes.
-      \item $r_{AM}$ is the probability of recombination between loci \textbf{A} and \textbf{M}.
+      \item $R$ is the probability of recombination between loci \textbf{A} and \textbf{M}.
       \item See Table \ref{tab:meanfitnesses} for expressions of mean fitnesses.
@@
 \begin{equation}\label{eq:neoYR}
-r_{AM} \left[ 
+R \left[ 
 \frac{p^\female_X w^\female_A w^\male_a (1-\alpha^\male)}{ \bar{w}^\female_H \bar{w}^\male_H (\lambda_{mA}-1)} + 
@@
 for the neo-$W$.
-Equations \eqref{eq:neoYR} and \eqref{eq:neoWR} show that the new sex-determining allele, $m$, is expected to invade for any probability of recombination between loci \textbf{A} and \textbf{M}, $r_{AM}$, when the net flow of recombinants is from the less fit (smaller $\lambda_{mi}$) to the more fit \textbf{A} background (making the terms inside the square brackets in Equations \ref{eq:neoYR} and \ref{eq:neoWR} negative).
+Equations \eqref{eq:neoYR} and \eqref{eq:neoWR} show that the new sex-determining allele, $m$, is expected to invade for any probability of recombination between loci \textbf{A} and \textbf{M}, $R$, when the net flow of recombinants is from the less fit (smaller $\lambda_{mi}$) to the more fit \textbf{A} background (making the terms inside the square brackets in Equations \ref{eq:neoYR} and \ref{eq:neoWR} negative).
 \textcolor{red}{Q: is it definitely possible to have negative square brackets for a equilibria maintained by selection?}
@@
 When the net flow of recombinants is from the more fit to the less fit haplotype, the new sex-determining allele can still invade when the rate of recombination between it and the selected locus is small enough.
-\textcolor{red}{Q:Is it the case that sometimes the square brackets are positive and invasion occurs for $r_{AM}=1/2$?
+\textcolor{red}{Q:Is it the case that sometimes the square brackets are positive and invasion occurs for $R=1/2$?
 In which case it might be better to have slightly different phrasing here.}

### 2017-02-10 LaTeX/Turnover.tex
Added some discussion/introduction, especially about sex ratios. Empirical predictions could still use expanding...

--- 2017-02-06 LaTeX/Turnover.tex
@@
 It has been suggested that sex ratio selection could be a particularly important force driving transitions between sex-determining systems \citep[Chapter 7]{Beukeboom:2014vb}. 
-For example, flexible sex determination systems may be favoured in order to exploit local environmental conditions that are optimal for males or females, which creates locally biased sex ratios \citep{Charnov:1977tx,Werren:1984tl,Pen:2010kk}.
-In addition, feminizing mutations may invade when female biased sex ratios are favoured due to selection among demes \citep{Wilson:1981vm,Vuillleumier:2007bh}. 
-In other situations, sex ratio selection may favour transitions in order to restore equal sex ratios. 
+The default mode of sex ratio selection is `Fisherian' sex ratio selection, which favours equal investment in male and female offspring (i.e., a 1:1 zygotic sex ratio when assuming that males and females are equally costly to produce)  \textcolor{red}{(Fisher)}.
+Given that the sex determination system can directly affect the sex ratio, we might expect Fisherian sex ratio selection to influence the spread of new sex determination systems. 
 For example, \citet{Kozielska:2010vm} consider systems in which the ancestral sex chromosomes experience meiotic drive (e.g., where driving X or Y chromosomes are inherited disproportionately often), which causes sex ratios to become biased \citep{Hamilton:1967ts}.
-They find that new, unlinked sex-determining loci (masculinizing or feminizing mutations, i.e., neo-Y or neo-W loci) can then spread, restoring an even sex ratio.
+They find that new, unlinked sex-determining loci (masculinizing or feminizing mutations, i.e., neo-Y or neo-W loci) can then spread, which restoring an even sex ratio.
+
+We note that non-Fisherian (`extraordinary') sex ratios can be favoured in some situations. 
+For example, with local mate competition, where brothers compete for mates, a female biased sex ratio is favoured \citep{Hamilton:1967ts}. 
+Thus, local mate competition could favour new sex determination systems because feminizing mutations bias the sex ratio towards females \citep{Wilson:1981vm,Vuillleumier:2007bh}. 
+Another consideration is that environmental conditions (e.g., maternal condition, mate quality, age, or host size) can differentially affect the fitness of males versus females such that the optimal allocation to males/females depends on the environment (Trivers and Willard, 1973) \citep{Charnov:1977tx} (Charnov, 1982, West 2009, Chapters 6 and 7).
+In such cases, flexible sex determination systems may evolve in order to allow the primary sex ratio to be determined in a way that depends on the environment \citep{Charnov:1977tx,Werren:1984tl,Pen:2010kk}.
+In this study, we do not consider environmental condition dependence or local mate competition (reviewed in Charnov, 1982 and West 2009).
 
@@
 Firstly, if we assume that haploid selection at any particular locus predominantly occurs in one sex (e.g., meiotic drive during spermatogenesis), then such loci experience a form of sex-specific selection.
-In this respect, we might expect that haploid selection might affect transitions between sex determination systems in a similar manner to sex-specific diploid selection \citep[as explored by][]{vanDoorn:2007eu,vanDoorn:2010hu}.
+In this respect, we might expect that haploid selection would affect transitions between sex determination systems in a similar manner to sex-specific diploid selection \citep[as explored by][]{vanDoorn:2007eu,vanDoorn:2010hu}.
 That is, new masculizing mutations (neo-Y chromosomes) could be favoured via associations with alleles that are beneficial in the male haploid stage. 
@@
 
-Surprisingly, our models show that haploid selection influences the evolution of new sex determination systems in a way that is distinct from both diploid sex-specific selection and sex ratio selection.
-We find that new genetic sex determination systems are not affected by any sex ratio biases caused by associations between sex-determining regions and haploid selected loci. 
+Surprisingly, our models show that haploid selection influences the evolution of new sex determination systems in a way that is distinct from both diploid sex-specific selection and Fisherian sex ratio selection.
+We find that the spread of new sex determination systems are independent of there being a zygotic sex ratio bias caused by associations between sex-determining regions and haploid selected loci. 
 In addition, we find that associations that build up between an ancestral sex-determining locus and a haploid-selected locus can favour transitions between male and female heterogamety (e.g., a neo-W allele arising at a previously autosomal locus spreads in an ancestrally XY system), despite the fact that these ancestral associations were built up by selection.
@@
 Locus \textbf{A} is a locus under selection, with alleles $A$ and $a$.
-Locus \textbf{M} is a novel sex-determining region, at which the null allele ($M$) is initially fixed in the population such that sex of zygotes is determined by the genotype at the ancestral sex-determining region, \textbf{X} ($XX$ become females and $XY$ become males, or $ZW$ become females and $ZZ$ become males).
+Locus \textbf{M} is a novel sex-determining region, at which the null allele ($M$) is initially fixed in the population such that sex of zygotes is determined by the genotype at the ancestral sex-determining region, \textbf{X}; $XX$ genotypes become females and $XY$ become males (or $ZW$ become females and $ZZ$ become males).
 To evaluate the evolution of new sex-determination systems, we consider the invasion, fixation, maintenance, and/or loss of novel sex-determining alleles ($m$) at the \textbf{M} locus. 
@@
 With $k=0$, the $m$ allele is a masculinizer (i.e., a neo-Y) and with $k=1$ the $m$ allele is a feminizer (i.e., a neo-W).
-With intermediate $k$, the $m$ allele confers environmental sex determination such that zygotes develop as females in a proportion ($k$) of the environments they experience. 
-Finally, we also analyze a model of maternally-controlled environmental sex-determination (ESD), where mothers with at least one $m$ allele produce daughters with probability $k$.
+With intermediate $k$, the $m$ allele confers environmental sex determination (ESD) such that zygotes develop as females in a proportion ($k$) of the environments they experience. 
+Finally, we also analyze a model of maternally-controlled environmental sex-determination, where mothers with at least one $m$ allele produce daughters with probability $k$.
 
 %life-cycle
-In each generation, we census the genotype frequencies in male and female gametes/gametophytes (hereafter gametes) before gametic competition (see Sup.\ Mat. for recursion equations). 
+In each generation, we census the genotype frequencies in male and female gametes/gametophytes (hereafter gametes) before gametic competition. 
+A full description of our model, including recursion equations, is given in the Appendix. 
 First, competition occurs among male gametes (sperm/pollen competition) and among female gametes (egg/ovule competition) separately. 
@@
 Furthermore, if the $m$ allele is fully dominant over the ancestral sex-determining system, phenotypes are not affected by the genotype at the ancestral sex-determining region (\textbf{X} locus). 
-Therefore, the invasion of rare dominant neo-Y or neo-W alleles depends on only two equations and is therefore determined by the largest eigenvalue that solves the quadratic characteristic polynomial
+Thus, the invasion of rare dominant neo-Y or neo-W alleles is determined by the largest eigenvalue that solves the quadratic characteristic polynomial
 $\lambda^2+ b \lambda + c =0$.
@@
 %where $b$ is the average of the growth rates of the two haplotypes that carry the $m$ allele ($mA$ and $ma$), $b=(\lambda_{mA}+\lambda_{ma})/2$, and $c$ also involves the fitness of $m$ alleles when they recombine onto the other \textbf{A} background in a heterozygote, $c=\lambda_{mA}\lambda_{ma}+\rho_{mA}\rho_{ma}$ (see table \ref{tab:haplotype_growth}).
-In this case $b= - (\lambda_{mA} + \lambda_{ma})$ and $c = \lambda_{mA} \lambda_{ma} -\rho_{mA} \rho_{ma}$, where $\lambda_{mi}-1$ is the growth rate of mutant haplotypes on background $i\in\{A,a\}$, accounting for loss due to recombination, and $\rho_{mi}-1$ is the rate of addition of mutant haplotypes onto background $i\in\{A,a\}$ due to recombination (see table \ref{tab:haplotype_growth}).
-\textcolor{red}{check these interpretations as there are now two 2s in the lambdas of table 2.
-perhaps the 2 in the denominator is needed because the frequency of males sums to one as does the frequency of females?
-the two in the numerator is from heterozygotes (like Hardy-Weinberg)?
-should we absorb it into the drive or recombination term?}
+In this case $b= - (\lambda_{mA} + \lambda_{ma})$ and $c = \lambda_{mA} \lambda_{ma} -\rho_{mA} \rho_{ma}$, where $\lambda_{mi}$ \textcolor{red}{I think we can call this growth rate, rather than reserving "growth rate" for $\lambda-1$.
+e.g., in ecological models, can't we call both R (in discrete time) and r (in continuous time) "growth rates"?} is the growth rate of mutant haplotypes on background $i\in\{A,a\}$, accounting for loss due to recombination, and $\rho_{mi}$ is the rate of addition of mutant haplotypes onto background $i\in\{A,a\}$ due to recombination (see table \ref{tab:haplotype_growth}).
+\textcolor{red}{check these interpretations.
+the $\lambda$s are certainly related to true growth rates because we get them by looking at the case where $R=0$ so that you only have the haplotypes growing/declining.
+}
+% as there are now two 2s in the lambdas of table 2. perhaps the 2 in the denominator is needed because the frequency of males sums to one as does the frequency of females?}
 
@@
 Similarly, invasion of a neo-W depends on the relative lifetime fitness of $A$-bearing and $a$-bearing female gametes (i.e., eggs only). 
-However, in the case of a neo-W, the allele carried by the male gamete that they mate with can come from either an X-bearing or a Y-bearing sperm (e.g., $A$ with probability $\bar{p}^{\male} w_{A}^{\male}/\bar{w}_{H}^{\male}$).
+However, in the case of a neo-W, the allele carried by the male gamete that they mate with can come from either an X-bearing or a Y-bearing sperm (e.g., $A$ with probability $\bar{p}^{\male} w_{A}^{\male}/\bar{w}_{H}^{\male}$, where $\bar{p}^{\male}=p_{Y}^{\male}q+p_{X}^{\male}(1-q)$).
 In either case, the zygote will then develop as a female due to the presence of a neo-W. 
-By contrast, females that do not carry the neo-W only result from matings with X-bearing sperm (e.g., matings with $A$-bearing sperm occur with probability $\bar{p}_{X}^{\male} w_{A}^{\male}/\bar{w}_{H}^{\male}$).
+By contrast, females that do not carry the neo-W only result from matings with X-bearing sperm (e.g., matings with $A$-bearing sperm that result in females occur with probability $(1-q)\bar{p}_{X}^{\male} w_{A}^{\male}/\bar{w}_{H}^{\male}$).
 If the \textbf{A} locus is initially linked to the ancestral sex-determining locus, \textbf{X}, the frequency of the $A$ allele among X- and Y-bearing sperm can differ (equation \ref{eq:freq_diffs}). 
@@
 
+%weak selection
 We are particularly concerned with whether or not a rare neo-sex-determining allele increases in frequency, which occurs when the largest eigenvalue, $\lambda$, is greater than one. 
-If the average change in frequency of the two haplotypes that carry the $m$ allele ($Am$ and $am$) is positive, invasion will always occur (i.e., if $\left\{(\lambda_{mA}-1)+ (\lambda_{ma}-1) \right\}/2 > 0$ then $\lambda > 1$).
-If neither haplotype increases in frequency ($\lambda_{mA}, \lambda_{ma} < 1$), the $m$ allele will not invade. 
-Otherwise, the new sex-determining allele increases in frequency on one \textbf{A} background and declines on the other, and invasion requires
-\begin{equation}\label{eq:neoYR}
-r_{AM} \left[ 
-\frac{p^\female_X w^\female_A w^\male_a (1-\alpha^\male)}{ \bar{w}^\female_H \bar{w}^\male_H (\lambda_{mA}-1)} + 
-%p^\female_X \frac{w^\female_A}{\bar{w}^\female_H} \frac{w^\male_a(1-\alpha^\male)}{\bar{w}^\male_H} \frac{1}{\lambda_{mA}-1} + 
-\frac{(1 - p^\female_X) w^\female_a w^\male_A \alpha^\male}{ \bar{w}^\female_H \bar{w}^\male_H (\lambda_{ma}-1)} 
-\right] 
-\frac{w^\male_{Aa}}{\bar{w}^\male} < 1,
-\end{equation}
-
-\noindent
-for the neo-$Y$, and
-
-\noindent
-\begin{equation}\label{eq:neoWR}
-R \left[ 
-\frac{\bar{p}^\male w^\male_A w^\female_a (1-\alpha^\female)}{ \bar{w}^\male_H \bar{w}^\female_H (\lambda_{mA}-1)} + 
-\frac{(1 - \bar{p}^\male) w^\male_a w^\female_A \alpha^\female}{ \bar{w}^\male_H \bar{w}^\female_H (\lambda_{ma}-1)} 
-\right] 
-\frac{w^\male_{Aa}}{\bar{w}^\male} < 1,
-\end{equation}
-
-\noindent
-for the neo-$W$.
-Equations \eqref{eq:neoYR} and \eqref{eq:neoWR} show that the new sex-determining allele, $m$, is expected to invade for any probability of recombination between loci \textbf{A} and \textbf{M}, $r_{AM}$, when the net flow of recombinants is from the less fit (smaller $\lambda_{mi}$) to the more fit \textbf{A} background (making the terms inside the square brackets in Equations \ref{eq:neoYR} and \ref{eq:neoWR} negative).
-\textcolor{red}{Q: is it definitely possible to have negative square brackets for a equilibria maintained by selection?}
-%Assuming $g_A^* > 0$ and $g_a^* < 0$ without loss of generality, this is $-(1 - p^\female_X) w_{m,A} g_a^* < p^\female_X w_{m,a} g_A^*$.
-When the net flow of recombinants is from the more fit to the less fit haplotype, the new sex-determining allele can still invade when the rate of recombination between it and the selected locus is small enough.
-\textcolor{red}{Q:Is it the case that sometimes the square brackets are positive and invasion occurs for $r_{AM}=1/2$?
-In which case it might be better to have slightly different phrasing here.}
-
-%weak selection
-We can explicitly determine the conditions under which invasion occurs if we assume that the $A$ allele reaches an equilibrium frequency under the ancestral sex-determination system before the neo-sex-determination system ($m$) arises.
+In the Appendix, we derive these conditions without assuming that selection is weak relative to recombination. 
+Here, we explicitly determine the conditions under which invasion occurs by assuming that the $A$ allele reaches an equilibrium frequency under the ancestral sex-determination system before the neo-sex-determination system ($m$) arises.
 The equilibrium  frequency of $A$ on different ancestral backgrounds ($\hat{p}^\male_Y$, $\hat{p}^\male_X$, and $\hat{p}^\female_X$) is given by equations \eqref{eq:pAve} and \eqref{eq:freq_diffs} where we assume selection and meiotic drive are weak relative to recombination ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon$).
-Under weak selection, we denote the leading eigenvalue describing the invasion of a neo-Y ($k=0$) and a neo-W ($k=0$) into an ancestrally XY system by $\lambda_{Y',XY}$ and $\lambda_{W',XY}$, respectively, which are given by
+Under weak selection, we denote the leading eigenvalue describing the invasion of a neo-Y ($k=0$) and a neo-W ($k=1$) into an ancestrally XY system by $\lambda_{Y',XY}$ and $\lambda_{W',XY}$, respectively, which are given by
 
@@
 Where there is no gametic competition and meiotic drive in one sex only, an unlinked neo-W can invade as long as the same allele is favoured in male and female diploid selection ($s^\female s^\male>0$, see Figure \ref{fig:Combination_Centimorgans}B), which is 50\% of the parameter space.
-Where there is no meiotic drive and gametic competition occurs in one sex only, an unlinked neo-W can invade as long as the same allele is favoured in male and female diploid selection and there are sex differences in selection of one type ($s^\female(s^\male-s^\female)>0$, see Figure \ref{fig:Combination_Centimorgans}C,D), which is 25\% of the parameter space.
+Where there is no meiotic drive and gametic competition occurs in one sex only, an unlinked neo-W can invade as long as the same allele is favoured in male and female diploid selection and there are sex differences in selection of one type (e.g., $s^\female(s^\male-s^\female)>0$, see Figure \ref{fig:Combination_Centimorgans}C,D), which is 25\% of the parameter space.
 These special cases indicate that neo-W invasion can occur for a relatively large fraction of parameter space, even if the neo-W is less tightly linked to the selected locus, $R>r$.
@@
 
-%
-%%write in general form without weak selection
-%A rare, dominant neo-$Y$ ($k=0$) is always expected to invade the ancestral $XY$ system when the average growth rate of mutant haplotypes ($Am$ and $am$) is positive, $(g_A + g_a)/2 > 0$.
-%($g_i = where $\lambda_i$ are the two eigenvalues when $R=r=0$; the \textbf{X} locus does not affect the dynamics).
-%When the growth rates of the mutant haplotypes without recombination ($R=0$) are negative, $g_i^* < 0 \; \forall \; i \in \{A,a\}$, where $g_i < g_i^*$, the neo-$Y$ does not invade.
-%Otherwise, the mutant allele increases in frequency on one \textbf{A} background and declines on the other and neo-$Y$ invasion requires
-%\begin{equation}
-%R \left[ \frac{p^\female_X w_{m,a}}{g_A^*} + \frac{(1 - p^\female_X) w_{m,A}}{g_a^*} \right] w_{m,Aa} < \nu_m,
-%\end{equation}
-%where $w_{m,i}$ is the relative viability fitness of males depending on their haploid or diploid genotype at the \textbf{A} locus (with $i\in\{A,a,AA,Aa,aa\}$) and
-%$\nu_m = 
-%  p^\female_X p_{Ym} w^\male_{a} w^\male_{AA} +
-%  p^\female_X (1-p_{Ym}) w^\male_{a} w^\male_{AA} +
-%  (1-p^\female_X) p_{Ym} w^\male_{a} w^\male_{AA} +
-%  (1-p^\female_X) (1-p_{Ym}) w^\male_a w^\male_{AA}$
-%is the mean relative fitness of resident males.
-%%and $g_j^*$ is the growth rate of $X^\male$ and $Ym$ haplotypes when on an $A$ ($j=A$)  or $a$ background ($j=a$).
-%Neo-$Y$ invasion therefore occurs for any recombination rate, $R$, when the net flow of double recombinants is from the less fit to the more fit \textbf{A} background (making the term inside the square brackets negative).
-%%Assuming $g_A^* > 0$ and $g_a^* < 0$ without loss of generality, this is $-(1 - p^\female_X) w_{m,A} g_a^* < p^\female_X w_{m,a} g_A^*$.
-%When the net flow of double recombinants is from the more fit to the less fit haplotype, neo-$Y$ invasion can still occur when the rate of recombination is small enough.
-%
-%%weak selection
-%Assuming weak selection, we can solve for the invasion fitness of the neo-$Y$ explicitly, giving
-%\begin{equation}
-%\lambda_{Y,XY} \approx 1 + V_A S_A (r - R)s^\female,
-%\end{equation}
-%where $V_A = p_A(1-p_A)$ is the variance at the \textbf{A} locus, $S_A = s^\female/ \left[ r R \left( s^\female + s^\male \right)^2 t_m^2 \right]$ (INTERPRETATION), $s^\female$ and $s^\male$ are the respective selection coefficients for $A$ in diploid females and males, $t_m$ is the selection coefficient for $A$ in gametes/gametophytes from males, and we've assumed equal dominance coefficients in the two sexes.
-%The neo-$Y$ can therefore invade whenever it is in tighter linkage with the selected locus than the ancestral sex-determining locus, $r>R$, provided locus \textbf{A} is polymorphic ($V_A>0$) and there is selection among both females ($s^\female\neq0$) and gametes/gametophytes from males ($t_m\neq0$).
-%
-%\subsubsection*{Neo-$W$}
-%
-%%write in general form without weak selection
-%Similarly, a rare, dominant neo-$W$ ($k=1$) will invade the ancestral $XY$ system whenever the average growth rate of $XAm$ and $Xam$ haplotypes is positive, $(g_A + g_a) / 2 > 1$. 
-%When the growth rates of the mutant haplotypes without recombination ($R=0$) are negative, $g_i^* < 0 \; \forall \; i \in \{A,a\}$, where $g_i < g_i^*$, the neo-$W$ does not invade.
-%Otherwise neo-$W$ invasion requires
-%\begin{equation}
-%R \left[ \frac{\bar{p}_m w_{m,A}}{g_a^*} + \frac{(1 - \bar{p}_m) w_{m,a}}{g_A^*} \right] w_{f,Aa} < \nu_f
-%\end{equation}
-%where $\bar{p}_m = (p_{Ym}+p^\male_X) / 2$ is the mean frequency of $A$ in gametes/gametophytes from males, $w_{f,i}$ is the relative viability fitness of females depending on their diploid genotype at the \textbf{A} locus (with $i\in\{AA,Aa,aa\}$), and
-%$\nu_f = 
-%  p^\female_X p^\male_X w^\male_{a} w_{AA,f} +
-%  p^\female_X (1-p^\male_X) w^\male_{a} w_{Aa,f} +
-%  (1-p^\female_X) p^\male_X w^\male_{a} w_{Aa,f} +
-%  (1-p^\female_X) (1-p^\male_X) w^\male_a w_{aa,f}$
-%is the mean relative fitness of resident females. 
-%%The rate of recombination between the \textbf{X} and \textbf{A} loci, $r$, does not explicitly appear because females are homozygous at the \textbf{X} locus with an ancestral $XY$ system.
-%As in the case of the neo-$Y$, neo-$W$ invasion therefore occurs with any recombination rate, $R$, when the net flow of recombinants is from the less fit to the more fit haplotype.
-%%Assuming $g_A^*>0$ and $g_a^*<0$ without loss of generality, this is $(1 - \bar{p}_m) w_{m,a} g_a^*< \bar{p}_m w_{m,A} g_A^*$.
-%And when the net flow of recombinants is from the more fit to the less fit  haplotype, neo-$W$ invasion can still occur when the rate of recombination is small enough.
-%
-%%weak selection
-%Assuming weak selection, we can solve for the invasion fitness of the neo-$W$ explicitly, giving
-%\begin{equation}
-%\lambda_{W,XY} \approx 1 + V_A S_A \frac{(2r(1-R)-R) s^\female + (1-2r)R s^\male }{2},
-%\end{equation}
-%where we've once again assumed equal dominance coefficients in the two sexes.
-%In this case, even when the novel sex-determining locus is in looser linkage with the selected locus than is the ancestral sex-determining locus, $r<R$, a novel sex-determiner can invade.
-%For example, with $R=1/2$ the neo-$W$ invades if there is any linkage between the ancestral sex-determining and selected loci ($r<1/2$), there is selection among gametes/gametophytes in males ($t_m\neq0$), and there is selection for or against $A$ in both males and females ($s^\male s^\female >0$) that is stronger in females than in males ($|s^\female| > |s^\male|$).
-
-%\subsubsection*{Neo-$Y$ and neo-$W$}
-
-%<<<<<<< HEAD
-%\subsubsection*{Neo-$Y$}
-%
-%The growth rate of a rare, dominant neo-$Y$ region ($k=0$) is
-%\begin{equation}
-%\lambda_{Y,XY} = 1 + V_A \frac{(r - R)}{r R} \frac{s_f^2}{\left( s_f + s_m \right)^2} t_m^2,
-%\end{equation}
-%where $V_A = p_A(1-p_A)$ is the variance at the \textbf{A} locus, $s_f$ and $s_m$ are the respective selection coefficients for $A$ in diploid females and males, and $t_m$ is the selection coefficient for $A$ in gametes/gametophytes from males.
-%The neo-Y can therefore invade whenever it is in tighter linkage with the selected locus than is the ancestral sex-determining locus, $r>R$, provided locus \textbf{A} is polymorphic ($V_A>0$) and there is selection among both females ($s_f\neq0$) and gametes/gametophytes from males ($t_m\neq0$).
-%=======
-%>>>>>>> c89cd9e1d25a76e5bffdd1ee7574884f24c08070
-%write in general form without weak selection
-%A rare, dominant neo-$Y$ ($k=0$) or neo-$W$ ($k=1$) is always expected to invade an ancestral $XY$ system when the average growth rate of the mutant haplotypes ($Am$ and $am$) is positive, $(g_A + g_a)/2 > 0$.
-%($g_i = where $\lambda_i$ are the two eigenvalues when $R=r=0$; the \textbf{X} locus does not affect the dynamics).
-%When the growth rates of the mutant haplotypes without recombination ($R=0$) are negative, $g_i^* < 0 \; \forall \; i \in \{A,a\}$, where $g_i < g_i^*$, the new sex-determining allele does not invade.
-
-%Otherwise, the new sex-determining allele increases in frequency on one \textbf{A} background and declines on the other, and invasion requires
-%\begin{equation}\label{eq:neoYR}
-%R \left[ \frac{p^\female_X w^\male_a (1-\alpha^\male)}{g_A^*} + \frac{(1 - p^\female_X) w^\male_A \alpha^\male}{g_a^*} \right] w^\male_{Aa} < \nu^\male,
-%\end{equation}
-%for the neo-$Y$, and 
-%\begin{equation}\label{eq:neoWR}
-%R \left[  \frac{(1 - \bar{p}^\male) w^\male_{a}}{g_A^*} + \frac{\bar{p}^\male w^\male_{A}}{g_a^*} \right] w^\female_{Aa} < \nu^\female
-%\end{equation}
-%for the neo-$W$.
-%Here $\bar{p}^\male = (1-q) p^\male_X+ q p^\male_Y$ is the average frequency of $A$ in gametes produced by males, $w^i_{j}$ is the relative viability fitness of sex $i\in\{m,f\}$ depending on their haploid or diploid genotype at the \textbf{A} locus (with $j\in\{A,a,AA,Aa,aa\}$) and
-%$\nu^i = 
-%  p^\female_X p^\male_{\textbf{X}^i} w^\male_{a} w^i_{AA} +
-%  p^\female_X (1-p^\male_{\textbf{X}^i}) w^\male_{a} w^i_{Aa} +
-%  (1-p^\female_X) p^\male_{\textbf{X}^i} w^\male_{a} w^i_{Aa} +
-%  (1-p^\female_X) (1-p^\male_{\textbf{X}^i}) w^\male_a w^i_{aa}$,
-%with $\textbf{X}^\male = Y$ and $\textbf{X}^\female = X$, is the mean relative fitness of resident individuals of sex $i$.
-%and $g_j^*$ is the growth rate of $X^\male$ and $Ym$ haplotypes when on an $A$ ($j=A$)  or $a$ background ($j=a$).
-%Although male meiotic drive does not explicitly appear in Equation \ref{eq:neoWR}, it does affect the average frequency of $A$ in gametes from males, $\bar{p}^\male$, and thus can play a role in neo-W invasion.
-
-%Equations \eqref{eq:neoYR} and \eqref{eq:neoWR} show that the new sex-determining allele is expected to invade for any recombination rate, $R$, when the net flow of double recombinants is from the less fit to the more fit \textbf{A} background (making the terms inside the square brackets in Equations \ref{eq:neoYR} and \ref{eq:neoWR} negative).
-%Assuming $g_A^* > 0$ and $g_a^* < 0$ without loss of generality, this is $-(1 - p^\female_X) w_{m,A} g_a^* < p^\female_X w_{m,a} g_A^*$.
-%When the net flow of double recombinants is from the more fit to the less fit haplotype, the new sex-determining allele can still invade when the rate of recombination between it and the selected locus, $R$, is small enough.
-
-%weak selection
-%Assuming weak selection and meiotic drive, we can explicitly solve for the invasion fitness of the new sex-determining allele, $m$, into the ancestral $XY$ system, giving
-%\begin{equation}
-%\lambda_{m,XY} \approx 1 + V_A S_A C_m,
-%\end{equation}
-%where $V_A = p_A(1-p_A)$ is the variance at the \textbf{A} locus.
-%We will consider haploid selection and meiotic drive separately.
-%With haploid selection and no drive we have $S_A = s^\female (t^\male)^2 / \left[ r R \left( s^\female + s^\male \right)^2 \right]$, where $s^\female$ and $s^\male$ are the respective selection coefficients for $A$ in diploid females and males, $t^\male$ is the selection coefficient for $A$ in gametes from males, and we've assumed equal dominance coefficients in the two sexes ($h^\female = h^\male$).
-%With drive and no haploid selection one replaces $t^\male$ with $\alpha^\male-1/2$.
-
-%For the neo-$Y$ we have $C_Y = (r - R)s^\female $ with haploid selection and $C_Y = 4(r - R)s^\female $ with drive.
-%The neo-$Y$ can therefore invade whenever it is in tighter linkage with the selected locus than the ancestral sex-determining locus, $r>R$, provided locus \textbf{A} is polymorphic ($V_A>0$), there is diploid selection in females ($s^\female\neq0$), and there is either haploid selection between gametes from males ($t^\male\neq0$) or meiotic drive in males ($\alpha^\male\neq1/2$).
-%This is similar to the conclusion reached concerning sexual-antagonistic selection in \cite{vanDoorn:2007eu} and reduces to their weak-linkage results exactly when we do not assume equal dominance coefficients in the two sexes, there is no haploid selection or meiotic drive, and there is free recombination between locus \textbf{A} and one of the sex-determining regions.
-
-%For the neo-$W$ we have $C_W = [(2r(1-R)-R) s^\female + (1-2r)R s^\male]/2$ with haploid selection and $C_W = 4[r(1-2R) s^\female + (1-2r)R s^\male]/2$ with drive.
-%In this case, even when the novel sex-determining locus is in looser linkage with the selected locus than the ancestral sex-determining locus is, $r<R$, a neo-$W$ can invade (Figures \ref{fig:WinvasionLowR} -- \ref{fig:InvasionVsCentiMorgans}).
-%This does not occur in models with only sexually-antagonistic selection \citep{vanDoorn:2010hu}.
-%For example, with $R=1/2$ the neo-$W$ invades if there is any linkage between the ancestral sex-determining and selected loci ($r<1/2$), there is selection among gametes in males ($t^\male\neq0$), and there is selection for or against $A$ in both males and females ($s^\male s^\female >0$) that is stronger in males than in females ($|s^\male| > |s^\female|$).
-%With meiotic drive and $R=1/2$, all that is required for neo-W invasion is $r<1/2$ and $s^\male s^\female >0$.
-%Our results reduce to the weak-linkage results of \cite[][Equation 3]{vanDoorn:2010hu} when we do not assume equal dominance coefficients in the two sexes and there is no haploid selection or meiotic drive.
-
-%\subsubsection*{Neo-$W$}
-%
-%%write in general form without weak selection
-%Similarly, a rare, dominant neo-$W$ ($k=1$) will invade the ancestral $XY$ system whenever the average growth rate of $XAm$ and $Xam$ haplotypes is positive, $(g_A + g_a) / 2 > 1$. 
-%When the growth rates of the mutant haplotypes without recombination ($R=0$) are negative, $g_i^* < 0 \; \forall \; i \in \{A,a\}$, where $g_i < g_i^*$, the neo-$W$ does not invade.
-%Otherwise neo-$W$ invasion requires
-%\begin{equation}
-%R \left[ \frac{\bar{p}_m w_{m,A}}{g_a^*} + \frac{(1 - \bar{p}_m) w_{m,a}}{g_A^*} \right] w_{f,Aa} < \nu_f
-%\end{equation}
-%where $\bar{p}_m = (p_{Ym}+p^\male_X) / 2$ is the mean frequency of $A$ in gametes/gametophytes from males, $w_{f,i}$ is the relative viability fitness of females depending on their diploid genotype at the \textbf{A} locus (with $i\in\{AA,Aa,aa\}$), and
-%$\nu_f = 
-%  p^\female_X p^\male_X w^\male_{a} w_{AA,f} +
-%  p^\female_X (1-p^\male_X) w^\male_{a} w_{Aa,f} +
-%  (1-p^\female_X) p^\male_X w^\male_{a} w_{Aa,f} +
-%  (1-p^\female_X) (1-p^\male_X) w^\male_a w_{aa,f}$
-%is the mean relative fitness of resident females. 
-%%The rate of recombination between the \textbf{X} and \textbf{A} loci, $r$, does not explicitly appear because females are homozygous at the \textbf{X} locus with an ancestral $XY$ system.
-%As in the case of the neo-$Y$, neo-$W$ invasion therefore occurs with any recombination rate, $R$, when the net flow of recombinants is from the less fit to the more fit haplotype.
-%%Assuming $g_A^*>0$ and $g_a^*<0$ without loss of generality, this is $(1 - \bar{p}_m) w_{m,a} g_a^*< \bar{p}_m w_{m,A} g_A^*$.
-%And when the net flow of recombinants is from the more fit to the less fit  haplotype, neo-$W$ invasion can still occur when the rate of recombination is small enough.
-%
-%%weak selection
-%Assuming weak selection, we can solve for the invasion fitness of the neo-$W$ explicitly, giving
-%\begin{equation}
-%\lambda_{W,XY} \approx 1 + V_A S_A \frac{(2r(1-R)-R) s^\female + (1-2r)R s^\male }{2},
-%\end{equation}
-%where we've once again assumed equal dominance coefficients in the two sexes.
-%In this case, even when the novel sex-determining locus is in looser linkage with the selected locus than is the ancestral sex-determining locus, $r<R$, a novel sex-determiner can invade.
-%For example, with $R=1/2$ the neo-$W$ invades if there is any linkage between the ancestral sex-determining and selected loci ($r<1/2$), there is selection among gametes/gametophytes in males ($t_m\neq0$), and there is selection for or against $A$ in both males and females ($s^\male s^\female >0$) that is stronger in females than in males ($|s^\female| > |s^\male|$).
-
-\subsubsection*{Offspring-controlled neo-ESD}
-
-Perhaps sex ratio selection can be invoked only when the invading mutation arises half the time in males and half the time in females, like an autosomal locus.
-If so, then we should see sex ratio influence the invasion of a novel sex-determining region that causes half of its carries to become female and half to become male (i.e., a perfect environmental sex determiner, ESD).
-However, we find that under weak selection the growth rate of a rare, dominant offspring-controlled neo-ESD allele that produces males or females with equal probability ($k=1/2$) is
-\begin{equation}
-\lambda_{ESD'} = 1 + \frac{1}{2}\frac{(\lambda_{Y',XY} - 1) + (\lambda_{W',XY} -1)}{2} \Big|_{R=1/2} + O\left(\epsilon^3\right),
+We next consider the case where the new sex-determining mutation, $m$, causes sex to be determined by environmental conditions (environmental sex determiner, ESD). 
+We assume that individuals carrying the $m$ allele develop as females in a fraction, $k$, of the environments they experience. 
+The spread of these mutations is given by
+
+\begin{equation}
+\begin{split}
+\lambda_{ESD',XY} =& 1 + (1-2k)^2V_{A}{S_{A}}^2\frac{r-R}{r R} \\
+&+\frac{k(\hat{p}^\male_Y-\hat{p}^\male_X)}{2}\left(k\left(2\alpha_{\Delta}^\male-2\alpha_{\Delta}^\female+t^\male-t^\female \right) -4(1-k)S_{A}\right)+O\left(\epsilon^3\right),
+\end{split}
+\label{eq:lambda_ESD_k}
+\end{equation}
+
+\noindent
+which reduces to $\lambda_{Y',XY}$ when $k=0$ and $\lambda_{W',XY}$ when $k=1$.
+
+Under Fisherian sex ratio selection, autosomal modifiers favour equal investment in male and female offspring, i.e., a 1:1 sex ratio \textcolor{red}{(Fisher... others)}. 
+Therefore, we are particularly interested in the case where the novel environmental sex-determiner causes half of its carriers to become female and half to become male ($k=1/2$). 
+As with an autosomal locus, these sex-determiners will be found in males half of the time and in females half of the time.
+However, we find that the growth rate of a rare, dominant offspring-controlled neo-ESD allele that produces males or females with equal probability ($k=1/2$) is
+\begin{equation}
+\lambda_{ESD',XY} =1+ \frac{1}{2}\frac{(\lambda_{Y',XY}-1) + (\lambda_{W',XY}-1)}{2} \Big|_{R=1/2} + O\left(\epsilon^3\right),
 %V_A \frac{r}{1-2r}  \frac{s_{f} \left( s^\male - 3 s^\female\right) }{8 \left( s_{f} + s_{m} \right)^2} t_{m}^2.
@@
 \end{equation}
-which is the same for invasion into an ancestrally XY or ZW system (since $\lambda_{Y',XY} = \lambda_{W',ZW}$, $\lambda_{W',XY} = \lambda_{Y',ZW}$).
-Thus by the same argument as above (if drive occurs in males only then the sex ratio is only biased when the ancestral sex-determination system is XY), sex ratio selection does not drive the turnover from genetic sex determination to offspring-controlled neo-ESD.
-
-Also note that with $k=1/2$ the neo-ESD gets half of the advantages of a neo-$W$ and half that of a neo-$Y$, but only has an effect one half of the time (the other half of the time it produces the same sex as the ancestral system would have).
-Recombination between the selected locus and the novel sex-determining locus, $R$, doesn't enter into the $k=1/2$ results because sex is essentially randomized each generation, %as if the novel sex-determiner were on an unlinked site that half the time acts as a neo-$W$ and half the time as a neo-$Y$.
+\noindent
+We note that recombination between the selected locus and the novel sex-determining locus, $R$, doesn't enter into the $k=1/2$ results because sex is essentially randomized each generation, %as if the novel sex-determiner were on an unlinked site that half the time acts as a neo-$W$ and half the time as a neo-$Y$.
 preventing associations from building up between allele $A$ and sex.  
+Equation \eqref{eq:lambda_ESD} shows that invasion by a novel `perfect' ESD (equal sex ratio, $k=1/2$) mutation is the same for an ancestrally XY or ZW system (since $\lambda_{Y',XY} = \lambda_{W',ZW}$, $\lambda_{W',XY} = \lambda_{Y',ZW}$).
+Thus, by the same argument as above (if drive occurs in males only then the sex ratio is only biased when the ancestral sex-determination system is XY), Fisherian sex ratio selection does not explain invasion by an offspring-controlled neo-ESD locus.
+Rather, the neo-ESD gets half of the fitness of a feminizing mutation (neo-$W$) and half of the fitness of a masculizing mutation (neo-$Y$), but only has an effect one half of the time (the other half of the time it produces the same sex as the ancestral system would have, to leading order).
+The net result can be that perfect ESD will not invade, even if sex ratios are biased. 
+For example, if there is haploid selection in males (either drive or pollen/sperm competition) but the conditions in table \ref{tab:specialcases} are not met, perfect ESD will not invade, even though it would equalize the zygotic sex ratio from an initially biased case (assuming $r<1/2$).
 
@@
 
-\subsubsection*{Maternally-controlled neo-ESD}
-
-One might think that when the sex of zygotes is under the control of mothers, there would be strong selection to balance the sex ratio among zygotes. 
-However, we find that, with no meiotic drive and weak selection, the invasion fitness of a dominant, maternally controlled sex-determiner that produces proportion $k$ daughters can be written
-\begin{equation}
-\lambda_{k} = 1 + V_A S_A C_k + O\left(\epsilon^3\right),
-\end{equation}
-where
+%\subsubsection*{Maternally-controlled neo-ESD}
+
+Fisherian sex ratio selection is sometimes considered in terms of balancing parental investment in male versus female offspring \textcolor{red}{(citation)}. 
+In addition, under environmental sex-determination, the proportion of males/females is sometimes controlled by the mother, e.g., the proportion of eggs laid in warm versus cold environments could determine the sex ratio of offspring.
+We therefore also considered the invasion of a neo-sex-determining allele ($m$) in a model in which mothers that have at least one $m$ allele produce $k$ daughters and $(1-k)$ males. 
+As with offspring-controlled ESD, for all $k\in\{0,1/2,1\}$, we find that invasion into an ancestrally XY system is the same as invasion into an ancestrally ZW system (at least up to order $\epsilon^3$), implying transitions between genetic sex determination and maternally controlled environmental sex determination are not driven by Fisherian sex ratio selection caused to biased zygotic sex ratios.
+
+%One might think that when the sex of zygotes is under the control of mothers, there would be strong selection to balance the sex ratio among zygotes. 
+%However, we find that, with no meiotic drive and weak selection, the invasion fitness of a dominant, maternally controlled sex-determiner that produces proportion $k$ daughters can be written
+%\begin{equation}
+%\lambda_{k} = 1 + V_A S_A C_k + O\left(\epsilon^3\right),
+%\end{equation}
+%where
 %\begin{equation}
@@
 %with $h$ the dominance coefficient (equal in both sexes), 
-$C_k$ is a term that depends on $k$.
+%$C_k$ is a term that depends on $k$.
 %
@@
 %However, with $k\neq1$ the results with maternal control differ from those with offspring control.
-Interestingly, for all $k\in\{0,1/2,1\}$, we find that invasion into an ancestrally XY system is the same as invasion into an ancestrally ZW system (at least up to order $\epsilon^3$), implying that sex ratio selection does not drive transitions between genetic sex determination and maternally controlled environmental sex determination.
+%Interestingly, for all $k\in\{0,1/2,1\}$, we find that invasion into an ancestrally XY system is the same as invasion into an ancestrally ZW system (at least up to order $\epsilon^3$), implying that sex ratio selection does not drive transitions between genetic sex determination and maternally controlled environmental sex determination.
 %Of particular interest is $k=1/2$ (i.e., when the mother perfectly balances the sex ratio of her offspring).
@@
 
-One might expect Fisherian sex ratio selection to influence the spread of new sex-determining systems because linkage between haploid selected loci and sex-determining regions cause biased zygotic sex ratios \citep{Hamilton:1967ts,Burt:2006,Field:2012fd,Field:2013cc}.
+One might expect Fisherian sex ratio selection to influence the spread of new sex-determining systems in our models because linkage between haploid selected loci and sex-determining regions causes biased zygotic sex ratios \citep{Hamilton:1967ts,Burt:2006,Field:2012fd,Field:2013cc}.
 Fisherian sex ratio selection follows from the fact that, for an autosomal locus, half of the genetic material is inherited from a male, and half from a female. 
@@
 Therefore, a mutant that increases investment in males will spread via the higher per-individual contributions made by males. 
-That is, under Fisherian sex ratio selection, the success of a mutant relative to the non-mutant depends, in equal parts, on the contributions made by males and females to the next generation. 
+%That is, under Fisherian sex ratio selection, the success of a mutant relative to the non-mutant depends, in equal parts, on the contributions made by males and females to the next generation. 
 An implicit assumption of Fisherian sex ratio selection is that the mutant allele is autosomal and has the same inheritance pattern as the non-mutant allele. 
 The mutations we consider here, neo-sex-determining alleles, break this assumption. 
-For example, the success of neo-Y mutations depends only on the number of alleles contributed by males (equation \ref{eq:charpoly_neoY} and Table \ref{tab:haplotype_growth}). 
+For example, the success of neo-Y/neo-W mutations depends only on the number of alleles contributed by males/females (Table \ref{tab:haplotype_growth}). 
+In this respect, a neo-W is similar to a cytoplasmic element, which also do not experience selection to balance sex ratios \textcolor{red}{citations}.
 Even mutants that are equally likely to be found in males or females, such as an environmental sex determination mutation (equation \ref{eq:lambda_ESD}), are not strictly autosomal if they determine sex.
-Thus, despite the fact that sex ratio biases caused by gametic competition or meiotic drive have been shown to exert selection on various autosomal modifiers \citep{Stalker:1961th,Smith:1975ft,Frank:1989vl,Hough:2013uo,Ubeda:2015fx, Otto:2015va}, we do not find evidence of Fisherian sex ratio selection acting upon neo-sex-determination systems (e.g., see Figure \ref{fig:Combination_Turnover} and \citealt{Ubeda:2015fx}, in which a neo-Y invades despite biasing sex ratios).
+Thus, despite the fact that sex ratio biases caused by gametic competition or meiotic drive have been shown to exert Fisherian sex ratio selection on various autosomal modifiers \citep{Stalker:1961th,Smith:1975ft,Frank:1989vl,Hough:2013uo,Ubeda:2015fx, Otto:2015va}, we do not find evidence of Fisherian sex ratio selection acting during invasion by neo-sex-determination systems (e.g., see Figure \ref{fig:Combination_Turnover} and \citealt{Ubeda:2015fx}, in which a neo-Y invades despite biasing sex ratios).
 
@@
 Our results show that genetic variation at loci that experience haploid selection can also generate selection in favour of new sex-determining systems. 
-New sex-determining allleles are again favoured if they are more closely linked with a locus under haploid selection.
+New sex-determining alleles are again favoured if they are more closely linked with a locus under haploid selection.
 However, with haploid selection, heterogametic transitions (XY to ZW or ZW to XY) can also occur when the new sex-determining region is less closely linked to the locus under selection.
@@
 Therefore, new sex-determining alleles only invade if they are more closely linked than the ancestral sex-determining region. 
-However, if there is haploid selection on loci linked to an XY (ZW) sex-determining region, polymorphisms can be maintained at which the mean fitness of females (males) or males is lower than it would be without sex-linkage, allowing unlinked neo-W (neo-Y) alleles to invade, see figure \ref{fig:Combination_MeanFit}.
+However, if there is haploid selection on loci linked to an XY (ZW) sex-determining region, selection can maintain polymorphisms at which the mean fitness of females (males) or males is lower than it would be without sex-linkage.
+In these cases, unlinked neo-W (neo-Y) alleles can invade, see figure \ref{fig:Combination_MeanFit}.
 
@@
 We assume that sex-determining alleles do not experience direct selection except via their associations with sex and alleles at a selected locus. 
-However, in some cases, there may be significant degeneration around the sex-limited allele (Y or W) in the ancestral sex determining region because recessive deleterious mutations and/or deletions may fix around the Y or W allele \citealt{Rice:1996ke,Charlesworth:2000cc,Bachtrog:2006ed,Marais:2008hm}).
+However, in some cases, there may be significant degeneration around the sex-limited allele (Y or W) in the ancestral sex determining region because recessive deleterious mutations and/or deletions may fix around the Y or W allele \citep{Rice:1996ke,Charlesworth:2000cc,Bachtrog:2006ed,Marais:2008hm}.
 During heterogametic transitions (XY to ZW or ZW to XY), the formally sex-limited allele fixes such that all individuals have YY or WW genotypes (Figure \ref{fig:Combination_Turnover}). 
@@
 
-Our model of meiotic drive is very simple, involving a single locus with two alleles. 
+In addition, our model of meiotic drive is simple, involving a single locus with two alleles. 
 However, many meiotic drive systems involve an interaction with another locus at which alleles may `suppress' the action of meiotic drive \citep{Burt:2006} \textcolor{red}{(Lindholm et al. 2016)}. 
 Thus, the dynamics of meiotic drive alleles can be heavily dependent on the interaction between two loci and the recombination rate between them, which in turn can be affected by sex-linkage if there is reduced recombination between sex chromosomes \textcolor{red}{(Hurst and Pomiankowski, 1991)}.
-Furthermore, in some cases, a driving allele may act by killing any gametes that carry a `target' allele at another locus, in which case there is a two-locus drive system and the total number of gametes produced can be reduced by meiotic drive (here, we assume that the total gamete number is not affected by drive).
-Thus, the number of mates competing for fertilization (mating system) can further affect the frequency of a meiotic drive allele \textcolor{red}{Holman et al., 2015)}. 
-Finally, the intensity of pollen/sperm competition under a particular mating system can depend on the density of males available to donate pollen/sperm, which can depend on the sex ratio and population size \textcolor{red}{(Taylor and Jaenike, 2002)}.
-Here, we do not consider feedbacks between sex ratios and the intensity of haploid selection. 
-It remains to be investigated how the evolution of new sex-determining mechanisms could be influenced by ecological feedbacks under different mating systems and by two-locus meiotic drive.
+Furthermore, in some cases, a driving allele may act by killing any gametes that carry a `target' allele at another locus, in which case there is a two-locus drive system and the total number of gametes produced can be reduced by meiotic drive.
+Where gamete number is reduced by meiotic drive, the number of mates competing for fertilization (mating system) can affect the equilibrium frequency of a meiotic drive allele \textcolor{red}{Holman et al., 2015)}.
+In polygamous mating systems, the intensity of pollen/sperm competition can depend on the density of males available to donate pollen/sperm, which can itself depend on the sex ratio \textcolor{red}{(Taylor and Jaenike, 2002)}.
+Since the sex ratio is partly determined by the sex determination system, the evolution of new sex determination system could by influenced by these dynamics. 
+It remains to be investigated how the evolution of new sex-determining mechanisms could be influenced by two-locus meiotic drive and by ecological feedbacks under different mating systems.
 
@@
 2003; Fernandez and Morris 2008; Kitano et al.
-2009; Roberts et al.
-2009)}.
-However, it is possible that sexually antagonistic variation accumulated after sex chromosome transitions because linkage with the sex-determining regions allows sexually antagonistic selection to maintain polymorphisms under a larger parameter space \textcolor{red}{(Rice, 1987, Jordan and Charlesworth, 2010-ish)}.
+2009)} \textcolor{red}{(Roberts et al.
+2009; Ser et al., 2010; Kitano,2012)}.
+However, it is possible that sexually antagonistic variation accumulated after sex chromosome transitions \textcolor{red}{(CHECK: Ser et al., 2010)} because linkage with the sex-determining regions allows sexually antagonistic selection to maintain polymorphisms under a larger parameter space \textcolor{red}{(Rice, 1987, Jordan and Charlesworth, 2010-ish)}.
 We note that linkage with sex chromosomes is not, a priori, more permissive to the maintainence of ploidally antagonistic variation \citep{Immler:2012tl}.
-Secondly, we note that new sex-determination systems can be favoured if either the ancestral sex-determining region or the new sex-determining region are linked to loci under haploid selection. 
+Secondly, we have shown that new sex-determination systems can be favoured if either the ancestral sex-determining region or the new sex-determining region are linked to loci under haploid selection. 
 Therefore, the presence of haploid selected loci around ancestral- or new- sex-determining regions could support their role in sex chromosome turnover. 
+As with sexually-antagonistic variation, a comparison between closely related clades could indicate whether a polymorphism pre-dates a transition in sex-determination or arose afterwards. 
 %It would be particularly informative if selection were evaluated in closely related clades
 
-\textcolor{red}{\noindent Do we have any cool examples?
-Meiotic drive alleles certainly more common on the sex chromosomes - although there are other explanations: (1) Divergence between X and Y provides a ready supply of target alleles for meiotic drive.
-(2) sex-linked meiotic drive has a more obvious phenotype to detect, sex ratio bias.}
-
 Taken at face value, our results indicate that transitions in heterogametey (XY to ZW or vice versa) are more likely to be favoured by selection if there is selection upon both haploid and diploid genotypes rather than diploid selection alone.
-Thus,
-
-In broadcast spawning animal species (e.g., corals, many fish) and species where sperm typically requires greater longevity, haploid selection may be stronger because transcripts shared during spermatogenesis may become depleted \citep{Immler:2014im}.
-\textcolor{red}{also, mating systems (e.g., fewer alleles are available during gametic competition in monogamous species), selfing rates, and estimates of pollen limitation could be used as indicators of the intensity of haploid selection}
-
-\noindent
-We have results where polygenic sex determination is sometimes stable, may be worth mentioning:
-
-``Polygenic sex determination has been reported in many plants (e.g.
+This prediction could be examined using a suitable proxy for haploid selection, for example, \textcolor{red}{Lenormand and Dutheil (2005)} use the outcrossing rate as a proxy for the strength of pollen competition.
+In animals, one might expect gametic competition to be stronger in species where sperm is required to live for a long time after spermatogenesis because transcripts shared during spermatogenesis may become depleted, revealing the haploid phenotype of the sperm \citep{Immler:2014im}.
+Given the caveats mentioned above about the form of meiotic drive modelled, we would also expect that heterogametic transitions in sex determination would be more common in clades where there is meiotic drive.
+
+We have shown that haploid selection can drive transitions between sex determination systems, such that haploid selection is incorporated in the factors influencing the evolution of sex determination.
+However, the particular way in which transitions are affected by haploid selection is not intuitively obvious. 
+Firstly, sex-specific haploid selection affects turnovers between sex determination systems in a manner that is qualitatively different from diploid sex-specific selection. 
+In particular, closer linkage between a sex-determining locus and a selected locus is not always favoured during heterogametic transitions when there is haploid selection. 
+Secondly, even though haploid selection is a source of zygotic sex ratio biases, Fisherian sex ratio selection does not have good explanatory power in our models in determining whether various sex-determination systems evolve; this result is surprising given that sex ratios are ultimately determined via the sex-determination system.
+
+\textcolor{red}{Numerical results suggest that polygenic sex determination can be stable with gametic competition.
+i.e., feminizers/masculinizers sometimes invade but don't fix.
+We have not discussed this.
+Might be interesting because it appears that polygenic sex determination exists (possibly stably, rather than transitionally) but previous models don't show any advantage to polygenic sex determination.
+There are two other ways that polygenic sex determination could be observed.
+(1) Direct selection against WW or YY genotypes during heterogametic transitions, mentioned above.
+(2) Loss of variation at the selected locus: The conditions under which polymorphism is maintained can depend on linkage to the SDR, and when a neo-SDR evolves you can move into a region where $A$ or $a$ fixes, at which point there is no longer any selection.}
+
+%``Polygenic sex determination has been reported in many plants (e.g.
 Shannon \& Holsinger 2007), fishes (Vandeputte et al.
@@
 Battaglia 1958; Battaglia \& Malesani 1959; Voordouw
-\& Anholt 2002), bivalves (Haley 1977; Saavedra et al. 1997), gastropods (Yusa 2007a,b), and polychaetes (Bacci 1965, 1978; Premoli et al. 1996).''
-From Vuilleumier et al. 2007:
-``Polymorphism for sex-determining genes within or among populations has been reported in many species including houseflies, midges, woodlice, platyfish, cichlid fish, and frogs (Gordon, 1944; Kallman, 1970; Thomp-son, 1971; Macdonald, 1978; Bull, 1983; Rigaud et al., 1997; Caubet et al., 2000; Lande et al., 2001; Ogataet al., 2003; Lee et al., 2004; Mank et al., 2006).''
-Also check Kallman (1984) -from vD\&K, 2010.
-
-vD\&K also suggest that this build up of sex-antagonistic polymorphisms may help to stabilize the ancestral sex-determining system, which would not be the case with haploid selection.
+%\& Anholt 2002), bivalves (Haley 1977; Saavedra et al. 1997), gastropods (Yusa 2007a,b), and polychaetes (Bacci 1965, 1978; Premoli et al. 1996).''
+%From Vuilleumier et al. 2007:
+%``Polymorphism for sex-determining genes within or among populations has been reported in many species including houseflies, midges, woodlice, platyfish, cichlid fish, and frogs (Gordon, 1944; Kallman, 1970; Thomp-son, 1971; Macdonald, 1978; Bull, 1983; Rigaud et al., 1997; Caubet et al., 2000; Lande et al., 2001; Ogataet al., 2003; Lee et al., 2004; Mank et al., 2006).''
+%Also check Kallman (1984) -from vD\&K, 2010.
 
@@
 \caption{
+The invasion fitness of a neo-sex-determining locus with various 
 \textcolor{red}{A sexual antagonism (no haploid selection), B drive (no gametic competition), equal selection in sexes ($s^\female=s^\male$), C \& D Pollen/Sperm competition only (no drive).
@@
 
+\subsection*{Invasion without assuming weak selection}
+
+Here, we determine whether a rare neo-Y or neo-W allele spreads when rare, which occurs when $\lambda > 1$. 
+If the average change in frequency of the two haplotypes that carry the $m$ allele ($Am$ and $am$) is positive, invasion will always occur (i.e., if $\left\{(\lambda_{mA}-1)+ (\lambda_{ma}-1) \right\}/2 > 0$ then $\lambda > 1$, see table \ref{tab:haplotype_growth} for $\lambda_{mi}$).
+If neither haplotype increases in frequency ($\lambda_{mA}, \lambda_{ma} < 1$), the $m$ allele will not invade. 
+Otherwise, the new sex-determining allele increases in frequency on one \textbf{A} background and declines on the other, and invasion requires
+\begin{equation}\label{eq:neoYR}
+r_{AM} \left[ 
+\frac{p^\female_X w^\female_A w^\male_a (1-\alpha^\male)}{ \bar{w}^\female_H \bar{w}^\male_H (\lambda_{mA}-1)} + 
+%p^\female_X \frac{w^\female_A}{\bar{w}^\female_H} \frac{w^\male_a(1-\alpha^\male)}{\bar{w}^\male_H} \frac{1}{\lambda_{mA}-1} + 
+\frac{(1 - p^\female_X) w^\female_a w^\male_A \alpha^\male}{ \bar{w}^\female_H \bar{w}^\male_H (\lambda_{ma}-1)} 
+\right] 
+\frac{w^\male_{Aa}}{\bar{w}^\male} < 1,
+\end{equation}
+
+\noindent
+for the neo-$Y$, and
+
+\noindent
+\begin{equation}\label{eq:neoWR}
+R \left[ 
+\frac{\bar{p}^\male w^\male_A w^\female_a (1-\alpha^\female)}{ \bar{w}^\male_H \bar{w}^\female_H (\lambda_{mA}-1)} + 
+\frac{(1 - \bar{p}^\male) w^\male_a w^\female_A \alpha^\female}{ \bar{w}^\male_H \bar{w}^\female_H (\lambda_{ma}-1)} 
+\right] 
+\frac{w^\male_{Aa}}{\bar{w}^\male} < 1,
+\end{equation}
+
+\noindent
+for the neo-$W$.
+Equations \eqref{eq:neoYR} and \eqref{eq:neoWR} show that the new sex-determining allele, $m$, is expected to invade for any probability of recombination between loci \textbf{A} and \textbf{M}, $r_{AM}$, when the net flow of recombinants is from the less fit (smaller $\lambda_{mi}$) to the more fit \textbf{A} background (making the terms inside the square brackets in Equations \ref{eq:neoYR} and \ref{eq:neoWR} negative).
+%\textcolor{red}{Q: is it definitely possible to have negative square brackets for a equilibria maintained by selection?}
+%Assuming $g_A^* > 0$ and $g_a^* < 0$ without loss of generality, this is $-(1 - p^\female_X) w_{m,A} g_a^* < p^\female_X w_{m,a} g_A^*$.
+When the net flow of recombinants is from the more fit to the less fit haplotype, the new sex-determining allele can still invade when the rate of recombination between it and the selected locus is small enough.
+%\textcolor{red}{Q:Is it the case that sometimes the square brackets are positive and invasion occurs for $r_{AM}=1/2$?
+In which case it might be better to have slightly different phrasing here.}
+
 \newpage

### 2017-02-10 LaTeX/Turnover.tex
added some references

--- 2017-02-10 LaTeX/Turnover.tex
@@
 
-It has been suggested that sex ratio selection could be a particularly important force driving transitions between sex-determining systems \citep[Chapter 7]{Beukeboom:2014vb}. 
-The default mode of sex ratio selection is `Fisherian' sex ratio selection, which favours equal investment in male and female offspring (i.e., a 1:1 zygotic sex ratio when assuming that males and females are equally costly to produce)  \textcolor{red}{(Fisher)}.
-Given that the sex determination system can directly affect the sex ratio, we might expect Fisherian sex ratio selection to influence the spread of new sex determination systems. 
+It has been suggested that sex ratio selection could be a particularly important force driving transitions between sex-determining systems (\citealt{Werren:1998co}; \citealt{Beukeboom:2014vb}, Chapter 7).
+For example, flexible sex determination systems may be favoured in order to exploit local environmental conditions that are optimal for males or females, which creates locally biased sex ratios \citep{Charnov:1977tx,Werren:1984tl,Pen:2010kk}.
+In addition, feminizing mutations may invade when female biased sex ratios are favoured due to selection among demes \citep{Wilson:1981vm,Vuillleumier:2007bh}. 
+In other situations, sex ratio selection may favour transitions in order to restore equal sex ratios. 
 For example, \citet{Kozielska:2010vm} consider systems in which the ancestral sex chromosomes experience meiotic drive (e.g., where driving X or Y chromosomes are inherited disproportionately often), which causes sex ratios to become biased \citep{Hamilton:1967ts}.
-They find that new, unlinked sex-determining loci (masculinizing or feminizing mutations, i.e., neo-Y or neo-W loci) can then spread, which restoring an even sex ratio.
-
-We note that non-Fisherian (`extraordinary') sex ratios can be favoured in some situations. 
-For example, with local mate competition, where brothers compete for mates, a female biased sex ratio is favoured \citep{Hamilton:1967ts}. 
-Thus, local mate competition could favour new sex determination systems because feminizing mutations bias the sex ratio towards females \citep{Wilson:1981vm,Vuillleumier:2007bh}. 
-Another consideration is that environmental conditions (e.g., maternal condition, mate quality, age, or host size) can differentially affect the fitness of males versus females such that the optimal allocation to males/females depends on the environment (Trivers and Willard, 1973) \citep{Charnov:1977tx} (Charnov, 1982, West 2009, Chapters 6 and 7).
-In such cases, flexible sex determination systems may evolve in order to allow the primary sex ratio to be determined in a way that depends on the environment \citep{Charnov:1977tx,Werren:1984tl,Pen:2010kk}.
-In this study, we do not consider environmental condition dependence or local mate competition (reviewed in Charnov, 1982 and West 2009).
+They find that new, unlinked sex-determining loci (masculinizing or feminizing mutations, i.e., neo-Y or neo-W loci) can then spread, restoring an even sex ratio.
 
@@
 We use the term `meiotic drive' to refer to the biased (non-medelian) segregation of genotypes during gamete production and the term `gametic competition' to refer to selection upon haploid genotypes within a gamete/gametophyte pool; the term `haploid selection' encompasses both processes.
-Meiotic drive generally occurs either during the production of male or female gametes only \textcolor{red}{(Ubeda and Haig, 2005; Lindholm et al. 2016)}. 
+Meiotic drive generally occurs either during the production of male or female gametes only \citep{Ubeda:2005gw,Lindholm:2016cw}.
 Because there are typically more pollen/sperm than required for fertilization, gametic competition is also typically sex specific, occurring primarily among male gametes.
@@
 Firstly, if we assume that haploid selection at any particular locus predominantly occurs in one sex (e.g., meiotic drive during spermatogenesis), then such loci experience a form of sex-specific selection.
-In this respect, we might expect that haploid selection would affect transitions between sex determination systems in a similar manner to sex-specific diploid selection \citep[as explored by][]{vanDoorn:2007eu,vanDoorn:2010hu}.
+In this respect, we might expect that haploid selection might affect transitions between sex determination systems in a similar manner to sex-specific diploid selection \citep[as explored by][]{vanDoorn:2007eu,vanDoorn:2010hu}.
 That is, new masculizing mutations (neo-Y chromosomes) could be favoured via associations with alleles that are beneficial in the male haploid stage. 
@@
 Surprisingly, our models show that haploid selection influences the evolution of new sex determination systems in a way that is distinct from both diploid sex-specific selection and Fisherian sex ratio selection.
-We find that the spread of new sex determination systems are independent of there being a zygotic sex ratio bias caused by associations between sex-determining regions and haploid selected loci. 
+We find that new genetic sex determination systems are not affected by any sex ratio biases caused by associations between sex-determining regions and haploid selected loci. 
 In addition, we find that associations that build up between an ancestral sex-determining locus and a haploid-selected locus can favour transitions between male and female heterogamety (e.g., a neo-W allele arising at a previously autosomal locus spreads in an ancestrally XY system), despite the fact that these ancestral associations were built up by selection.
@@
 
-Under Fisherian sex ratio selection, autosomal modifiers favour equal investment in male and female offspring, i.e., a 1:1 sex ratio \textcolor{red}{(Fisher... others)}. 
+Under Fisherian sex ratio selection, autosomal modifiers favour equal investment in male and female offspring, i.e., a 1:1 sex ratio \citep{Fisher:1930wy,Charnov:1982wg,West:2009we}. 
 Therefore, we are particularly interested in the case where the novel environmental sex-determiner causes half of its carriers to become female and half to become male ($k=1/2$). 
@@
 \end{equation}
-\noindent
-We note that recombination between the selected locus and the novel sex-determining locus, $R$, doesn't enter into the $k=1/2$ results because sex is essentially randomized each generation, %as if the novel sex-determiner were on an unlinked site that half the time acts as a neo-$W$ and half the time as a neo-$Y$.
+which is the same for invasion into an ancestrally XY or ZW system (since $\lambda_{Y',XY} = \lambda_{W',ZW}$, $\lambda_{W',XY} = \lambda_{Y',ZW}$).
+Thus, by the same argument as above (if drive occurs in males only then the sex ratio is only biased when the ancestral sex-determination system is XY), sex ratio selection does not explain invasion by an offspring-controlled neo-ESD locus.
+Rather, the neo-ESD gets half of the fitness of a feminizing mutation (neo-$W$) and half of the fitness of a masculizing mutation (neo-$Y$), but only has an effect one half of the time (the other half of the time it produces the same sex as the ancestral system would have, to leading order).
+Also note that recombination between the selected locus and the novel sex-determining locus, $R$, doesn't enter into the $k=1/2$ results because sex is essentially randomized each generation, %as if the novel sex-determiner were on an unlinked site that half the time acts as a neo-$W$ and half the time as a neo-$Y$.
 preventing associations from building up between allele $A$ and sex.
-Equation \eqref{eq:lambda_ESD} shows that invasion by a novel `perfect' ESD (equal sex ratio, $k=1/2$) mutation is the same for an ancestrally XY or ZW system (since $\lambda_{Y',XY} = \lambda_{W',ZW}$, $\lambda_{W',XY} = \lambda_{Y',ZW}$).
-Thus, by the same argument as above (if drive occurs in males only then the sex ratio is only biased when the ancestral sex-determination system is XY), Fisherian sex ratio selection does not explain invasion by an offspring-controlled neo-ESD locus.
-Rather, the neo-ESD gets half of the fitness of a feminizing mutation (neo-$W$) and half of the fitness of a masculizing mutation (neo-$Y$), but only has an effect one half of the time (the other half of the time it produces the same sex as the ancestral system would have, to leading order).
-The net result can be that perfect ESD will not invade, even if sex ratios are biased. 
-For example, if there is haploid selection in males (either drive or pollen/sperm competition) but the conditions in table \ref{tab:specialcases} are not met, perfect ESD will not invade, even though it would equalize the zygotic sex ratio from an initially biased case (assuming $r<1/2$).
 
@@
 
-Fisherian sex ratio selection is sometimes considered in terms of balancing parental investment in male versus female offspring \textcolor{red}{(citation)}. 
+Fisherian sex ratio selection is commonly considered in terms of balancing parental investment in male versus female offspring \citep{Fisher:1930wy,Charnov:1982wg,West:2009we}.
 In addition, under environmental sex-determination, the proportion of males/females is sometimes controlled by the mother, e.g., the proportion of eggs laid in warm versus cold environments could determine the sex ratio of offspring.
 We therefore also considered the invasion of a neo-sex-determining allele ($m$) in a model in which mothers that have at least one $m$ allele produce $k$ daughters and $(1-k)$ males. 
-As with offspring-controlled ESD, for all $k\in\{0,1/2,1\}$, we find that invasion into an ancestrally XY system is the same as invasion into an ancestrally ZW system (at least up to order $\epsilon^3$), implying transitions between genetic sex determination and maternally controlled environmental sex determination are not driven by Fisherian sex ratio selection caused to biased zygotic sex ratios.
+As with offspring-controlled ESD, for all $k\in\{0,1/2,1\}$, we find that invasion into an ancestrally XY system is the same as invasion into an ancestrally ZW system (at least up to order $\epsilon^3$), implying that sex ratio selection does not drive transitions between genetic sex determination and maternally controlled environmental sex determination.
 
@@
 One might expect Fisherian sex ratio selection to influence the spread of new sex-determining systems in our models because linkage between haploid selected loci and sex-determining regions causes biased zygotic sex ratios \citep{Hamilton:1967ts,Burt:2006,Field:2012fd,Field:2013cc}.
-Fisherian sex ratio selection follows from the fact that, for an autosomal locus, half of the genetic material is inherited from a male, and half from a female. 
+Fisherian sex ratio selection follows from the fact that, for an autosomal locus, half of the genetic material is inherited from a male, and half from a female \citep{Fisher:1930wy,West:2009we}. 
 Thus, if the population sex ratio is biased towards females, the average per-individual contribution of genetic material to the next generation from males is greater than the contribution from females (and vice versa for male-biased sex ratios).
@@
 For example, the success of neo-Y/neo-W mutations depends only on the number of alleles contributed by males/females (Table \ref{tab:haplotype_growth}). 
-In this respect, a neo-W is similar to a cytoplasmic element, which also do not experience selection to balance sex ratios \textcolor{red}{citations}.
+In this respect, a neo-W is similar to a cytoplasmic element, which also do not experience selection to balance sex ratios \citep{Frank:1989vl,Werren:1998co,Chase:2007bf}.
 Even mutants that are equally likely to be found in males or females, such as an environmental sex determination mutation (equation \ref{eq:lambda_ESD}), are not strictly autosomal if they determine sex.
-Thus, despite the fact that sex ratio biases caused by gametic competition or meiotic drive have been shown to exert Fisherian sex ratio selection on various autosomal modifiers \citep{Stalker:1961th,Smith:1975ft,Frank:1989vl,Hough:2013uo,Ubeda:2015fx, Otto:2015va}, we do not find evidence of Fisherian sex ratio selection acting during invasion by neo-sex-determination systems (e.g., see Figure \ref{fig:Combination_Turnover} and \citealt{Ubeda:2015fx}, in which a neo-Y invades despite biasing sex ratios).
+Thus, despite the fact that sex ratio biases caused by gametic competition or meiotic drive have been shown to exert selection on various autosomal modifiers \citep{Stalker:1961th,Smith:1975ft,Frank:1989vl,Hough:2013uo,Ubeda:2015fx, Otto:2015va}, we do not find evidence of Fisherian sex ratio selection acting upon neo-sex-determination systems (e.g., see Figure \ref{fig:Combination_Turnover} and \citealt{Ubeda:2015fx}, in which a neo-Y invades despite biasing sex ratios).
 
@@
 We assume that sex-determining alleles do not experience direct selection except via their associations with sex and alleles at a selected locus. 
-However, in some cases, there may be significant degeneration around the sex-limited allele (Y or W) in the ancestral sex determining region because recessive deleterious mutations and/or deletions may fix around the Y or W allele \citep{Rice:1996ke,Charlesworth:2000cc,Bachtrog:2006ed,Marais:2008hm}.
+However, in some cases, there may be significant degeneration around the sex-limited allele (Y or W) in the ancestral sex determining region because recessive deleterious mutations and/or deletions may fix around the Y or W allele \citealt{Rice:1996ke,Charlesworth:2000cc,Bachtrog:2006ed,Marais:2008hm}).
 During heterogametic transitions (XY to ZW or ZW to XY), the formally sex-limited allele fixes such that all individuals have YY or WW genotypes (Figure \ref{fig:Combination_Turnover}). 
@@
 In addition, our model of meiotic drive is simple, involving a single locus with two alleles. 
-However, many meiotic drive systems involve an interaction with another locus at which alleles may `suppress' the action of meiotic drive \citep{Burt:2006} \textcolor{red}{(Lindholm et al. 2016)}. 
-Thus, the dynamics of meiotic drive alleles can be heavily dependent on the interaction between two loci and the recombination rate between them, which in turn can be affected by sex-linkage if there is reduced recombination between sex chromosomes \textcolor{red}{(Hurst and Pomiankowski, 1991)}.
+However, many meiotic drive systems involve an interaction with another locus at which alleles may `suppress' the action of meiotic drive \citep{Burt:2006,Lindholm:2016cw}.
+Thus, the dynamics of meiotic drive alleles can be heavily dependent on the interaction between two loci and the recombination rate between them, which in turn can be affected by sex-linkage if there is reduced recombination between sex chromosomes \citep{Hurst:1991uh}.
 Furthermore, in some cases, a driving allele may act by killing any gametes that carry a `target' allele at another locus, in which case there is a two-locus drive system and the total number of gametes produced can be reduced by meiotic drive.
-Where gamete number is reduced by meiotic drive, the number of mates competing for fertilization (mating system) can affect the equilibrium frequency of a meiotic drive allele \textcolor{red}{Holman et al., 2015)}.
-In polygamous mating systems, the intensity of pollen/sperm competition can depend on the density of males available to donate pollen/sperm, which can itself depend on the sex ratio \textcolor{red}{(Taylor and Jaenike, 2002)}.
+Where gamete number is reduced by meiotic drive, the number of mates competing for fertilization (mating system) can affect the equilibrium frequency of a meiotic drive allele \citep{Holman:2015en}. 
+In polygamous mating systems, the intensity of pollen/sperm competition can depend on the density of males available to donate pollen/sperm, which can itself depend on the sex ratio \citep{Taylor:2002wu}.
 Since the sex ratio is partly determined by the sex determination system, the evolution of new sex determination system could by influenced by these dynamics. 
@@
 
-We have shown that haploid selection can drive transitions between sex determination systems, such that haploid selection is incorporated in the factors influencing the evolution of sex determination.
-However, the particular way in which transitions are affected by haploid selection is not intuitively obvious. 
+We have shown that haploid selection can drive transitions between sex determination systems but the particular way in which transitions are affected by haploid selection is not intuitively obvious. 
 Firstly, sex-specific haploid selection affects turnovers between sex determination systems in a manner that is qualitatively different from diploid sex-specific selection. 
 In particular, closer linkage between a sex-determining locus and a selected locus is not always favoured during heterogametic transitions when there is haploid selection. 
-Secondly, even though haploid selection is a source of zygotic sex ratio biases, Fisherian sex ratio selection does not have good explanatory power in our models in determining whether various sex-determination systems evolve; this result is surprising given that sex ratios are ultimately determined via the sex-determination system.
+Secondly, even though haploid selection is a source of zygotic sex ratio biases, Fisherian sex ratio selection does not have good explanatory power in determining whether various sex-determination systems evolve; this result is surprising given that sex ratios are ultimately determined via the sex-determination system.
 

### 2017-02-10 LaTeX/Turnover.tex
references

--- 2017-02-10 LaTeX/Turnover.tex
@@
 %CHECK THROUGHOUT: use of sex-determination SYSTEMS versus MECHANISMS. 
+%CHECK THROUGHOUT: use of haploid selection, gametic selection, and meiotic drive.
 
@@
 It has been suggested that sex ratio selection could be a particularly important force driving transitions between sex-determining systems \citep[Chapter 7]{Beukeboom:2014vb}. 
-The default mode of sex ratio selection is `Fisherian' sex ratio selection, which favours equal investment in male and female offspring (i.e., a 1:1 zygotic sex ratio when assuming that males and females are equally costly to produce)  \textcolor{red}{(Fisher)}.
+The default mode of sex ratio selection is `Fisherian' sex ratio selection, which favours equal investment in male and female offspring \citep[i.e., a 1:1 zygotic sex ratio when assuming that males and females are equally costly to produce,][]{Fisher:1930wy,Charnov:1982wg}.
 Given that the sex determination system can directly affect the sex ratio, we might expect Fisherian sex ratio selection to influence the spread of new sex determination systems. 
@@
 
-We note that non-Fisherian (`extraordinary') sex ratios can be favoured in some situations. 
-For example, with local mate competition, where brothers compete for mates, a female biased sex ratio is favoured \citep{Hamilton:1967ts}. 
-Thus, local mate competition could favour new sex determination systems because feminizing mutations bias the sex ratio towards females \citep{Wilson:1981vm,Vuillleumier:2007bh}. 
-Another consideration is that environmental conditions (e.g., maternal condition, mate quality, age, or host size) can differentially affect the fitness of males versus females such that the optimal allocation to males/females depends on the environment (Trivers and Willard, 1973) \citep{Charnov:1977tx} (Charnov, 1982, West 2009, Chapters 6 and 7).
-In such cases, flexible sex determination systems may evolve in order to allow the primary sex ratio to be determined in a way that depends on the environment \citep{Charnov:1977tx,Werren:1984tl,Pen:2010kk}.
-In this study, we do not consider environmental condition dependence or local mate competition (reviewed in Charnov, 1982 and West 2009).
+We note two other ways in which sex determination has been shown to relate to zygotic sex ratios.
+Firstly, non-Fisherian female-biased sex ratios can be favoured when there is local mate competition, in which brothers compete for mates \citep{Hamilton:1967ts}. 
+Therefore, with local mate competition, feminizing mutations can spread because they bias the sex ratio towards females \citep{Wilson:1981vm,Vuillleumier:2007bh}. 
+Secondly, environmental conditions (e.g., maternal condition, mate quality, age, or host size) can differentially affect the fitness of males versus females such that the optimal allocation to males/females depends on the environment \citep{Trivers:1973wb,Charnov:1977tx,Charnov:1982wg}.
+In such cases, flexible sex determination systems may evolve in order to allow the zygotic sex ratio to be determined in a way that depends on the environment \citep{Charnov:1977tx,Werren:1984tl,Pen:2010kk}.
+In this study, we do not consider environmental condition dependence or local mate competition \citep[reviewed in][]{Charnov:1982wg,West:2009we}.
 
@@
 For example, the success of neo-Y/neo-W mutations depends only on the number of alleles contributed by males/females (Table \ref{tab:haplotype_growth}). 
-In this respect, a neo-W is similar to a cytoplasmic element, which also do not experience selection to balance sex ratios \textcolor{red}{citations}.
+In this respect, a neo-W is similar to a cytoplasmic element, which also do not experience selection to balance sex ratios \citep{Frank:1989vl,Werren:1998co,Chase:2007bf}.
 Even mutants that are equally likely to be found in males or females, such as an environmental sex determination mutation (equation \ref{eq:lambda_ESD}), are not strictly autosomal if they determine sex.
@@
 In addition, our model of meiotic drive is simple, involving a single locus with two alleles. 
-However, many meiotic drive systems involve an interaction with another locus at which alleles may `suppress' the action of meiotic drive \citep{Burt:2006} \textcolor{red}{(Lindholm et al. 2016)}. 
-Thus, the dynamics of meiotic drive alleles can be heavily dependent on the interaction between two loci and the recombination rate between them, which in turn can be affected by sex-linkage if there is reduced recombination between sex chromosomes \textcolor{red}{(Hurst and Pomiankowski, 1991)}.
+However, many meiotic drive systems involve an interaction with another locus at which alleles may `suppress' the action of meiotic drive \citep{Burt:2006,Lindholm:2016cw}.
+Thus, the dynamics of meiotic drive alleles can be heavily dependent on the interaction between two loci and the recombination rate between them, which in turn can be affected by sex-linkage if there is reduced recombination between sex chromosomes \citep{Hurst:1991uh}.
 Furthermore, in some cases, a driving allele may act by killing any gametes that carry a `target' allele at another locus, in which case there is a two-locus drive system and the total number of gametes produced can be reduced by meiotic drive.
-Where gamete number is reduced by meiotic drive, the number of mates competing for fertilization (mating system) can affect the equilibrium frequency of a meiotic drive allele \textcolor{red}{Holman et al., 2015)}.
-In polygamous mating systems, the intensity of pollen/sperm competition can depend on the density of males available to donate pollen/sperm, which can itself depend on the sex ratio \textcolor{red}{(Taylor and Jaenike, 2002)}.
+Where gamete number is reduced by meiotic drive, the number of mates competing for fertilization (mating system) can affect the equilibrium frequency of a meiotic drive allele \citep{Holman:2015en}. 
+In polygamous mating systems, the intensity of pollen/sperm competition can depend on the density of males available to donate pollen/sperm, which can itself depend on the sex ratio \citep{Taylor:2002wu}.
 Since the sex ratio is partly determined by the sex determination system, the evolution of new sex determination system could by influenced by these dynamics. 
-It remains to be investigated how the evolution of new sex-determining mechanisms could be influenced by two-locus meiotic drive and by ecological feedbacks under different mating systems.
+How the evolution of new sex-determining mechanisms could be influenced by two-locus meiotic drive and/or by ecological feedbacks under different mating systems remains to be studied.
 
 The hypotheses presented here can be investigated in a similar manner to the idea that transitions between sex-determining systems are favoured by linkage to sexually antagonistic variation. 
-In the case of sexually antagonistic variation, one supporting observation is that genes that appear to experience sexually-antagonistic selection have been found on recently derived sex chromosomes \textcolor{red}{CHECK (Kallman 1973; Wada et al.
-1998; Lande et al.
-2001; Lindholm and Breden 2002; Streelman et al.
-2003; Fernandez and Morris 2008; Kitano et al.
-2009)} \textcolor{red}{(Roberts et al.
-2009; Ser et al., 2010; Kitano,2012)}.
-However, it is possible that sexually antagonistic variation accumulated after sex chromosome transitions \textcolor{red}{(CHECK: Ser et al., 2010)} because linkage with the sex-determining regions allows sexually antagonistic selection to maintain polymorphisms under a larger parameter space \textcolor{red}{(Rice, 1987, Jordan and Charlesworth, 2010-ish)}.
+In the case of sexually antagonistic variation, one supporting observation is that genes that appear to experience sexually-antagonistic selection have been found on recently derived sex chromosomes \citep{Lindholm:2002dw,Tripathi:2009cw,Ser:2010iq}.
+However, it is possible that sexually antagonistic variation accumulated after sex chromosome transitions because linkage with the sex-determining regions allows sexually antagonistic selection to maintain polymorphisms under a larger parameter space \citep{Rice:1987hs,Jordan:2011fj}.
 We note that linkage with sex chromosomes is not, a priori, more permissive to the maintainence of ploidally antagonistic variation \citep{Immler:2012tl}.
+However, as with sexually-antagonistic variation, a comparison between closely related clades could indicate whether a polymorphism pre-dates a transition in sex-determination or arose afterwards. 
 Secondly, we have shown that new sex-determination systems can be favoured if either the ancestral sex-determining region or the new sex-determining region are linked to loci under haploid selection. 
 Therefore, the presence of haploid selected loci around ancestral- or new- sex-determining regions could support their role in sex chromosome turnover. 
-As with sexually-antagonistic variation, a comparison between closely related clades could indicate whether a polymorphism pre-dates a transition in sex-determination or arose afterwards. 
 %It would be particularly informative if selection were evaluated in closely related clades
@@
 Taken at face value, our results indicate that transitions in heterogametey (XY to ZW or vice versa) are more likely to be favoured by selection if there is selection upon both haploid and diploid genotypes rather than diploid selection alone.
-This prediction could be examined using a suitable proxy for haploid selection, for example, \textcolor{red}{Lenormand and Dutheil (2005)} use the outcrossing rate as a proxy for the strength of pollen competition.
+This prediction could be examined using a suitable proxy for haploid selection, for example, \citep{Lenormand:2005vb} use the outcrossing rate as a proxy for the strength of pollen competition. 
 In animals, one might expect gametic competition to be stronger in species where sperm is required to live for a long time after spermatogenesis because transcripts shared during spermatogenesis may become depleted, revealing the haploid phenotype of the sperm \citep{Immler:2014im}.
@@
 
-We have shown that haploid selection can drive transitions between sex determination systems, such that haploid selection is incorporated in the factors influencing the evolution of sex determination.
+We have shown that haploid selection can drive transitions between sex determination systems, such that haploid selection is should be incorporated into the factors that influence the evolution of sex determination.
 However, the particular way in which transitions are affected by haploid selection is not intuitively obvious. 

### 2017-02-10 LaTeX/Turnover.tex
figure legends and other changes

@@
 We note two other ways in which sex determination has been shown to relate to zygotic sex ratios.
-Firstly, non-Fisherian female-biased sex ratios can be favoured when there is local mate competition, in which brothers compete for mates \citep{Hamilton:1967ts}. 
+Firstly, female-biased sex ratios can be favoured when there is local mate competition, in which brothers compete for mates \citep{Hamilton:1967ts}. 
 Therefore, with local mate competition, feminizing mutations can spread because they bias the sex ratio towards females \citep{Wilson:1981vm,Vuillleumier:2007bh}. 
@@
 In such cases, flexible sex determination systems may evolve in order to allow the zygotic sex ratio to be determined in a way that depends on the environment \citep{Charnov:1977tx,Werren:1984tl,Pen:2010kk}.
-In this study, we do not consider environmental condition dependence or local mate competition \citep[reviewed in][]{Charnov:1982wg,West:2009we}.
+In this study, we do not consider environmental condition dependence or local mate competition \citep[reviewed in][]{Charnov:1982wg,Bull:1983vi,West:2009we}.
 
@@
 In addition, artificial selection pressures applied to male gametophytes cause the frequency of resistant alleles to increase \citep[e.g.,][]{Hormaza:1996cv,Ravikumar:2003uo,Hedhly:2004iv,Clarke:2004ir}.
-A smaller (but non-negligible) proportion of genes are thought to be expressed and selected during competition in animal sperm, although precise estimates are uncertain \citep{Zheng:2001fi,JOSEPH:2004haa,Vibranovski:2010et}.
+A much smaller proportion of genes are thought to be expressed and selected during competition in animal sperm, although precise estimates are uncertain \citep{Zheng:2001fi,JOSEPH:2004haa,Vibranovski:2010et}.
 
@@
 
-Fisherian sex ratio selection is sometimes considered in terms of balancing parental investment in male versus female offspring \textcolor{red}{(citation)}. 
+Fisherian sex ratio selection is sometimes considered in terms of balancing parental investment in male versus female offspring \citep{Charnov:1982wg}.
 In addition, under environmental sex-determination, the proportion of males/females is sometimes controlled by the mother, e.g., the proportion of eggs laid in warm versus cold environments could determine the sex ratio of offspring.
 We therefore also considered the invasion of a neo-sex-determining allele ($m$) in a model in which mothers that have at least one $m$ allele produce $k$ daughters and $(1-k)$ males. 
-As with offspring-controlled ESD, for all $k\in\{0,1/2,1\}$, we find that invasion into an ancestrally XY system is the same as invasion into an ancestrally ZW system (at least up to order $\epsilon^3$), implying transitions between genetic sex determination and maternally controlled environmental sex determination are not driven by Fisherian sex ratio selection caused to biased zygotic sex ratios.
+As with offspring-controlled ESD, for all $k\in\{0,1/2,1\}$, we find that invasion into an ancestrally XY system is the same as invasion into an ancestrally ZW system (at least up to order $\epsilon^3$), implying transitions between genetic sex determination and maternally controlled environmental sex determination are not driven by Fisherian sex ratio selection on biased zygotic sex ratios.
 
@@
 \caption{
-Heterogametic transitions from XY to ZW sex determination (neo-W frequency shown by black lines, panels A and B) or from ZW to XY (neo-Y frequency shown by black lines, panels C and D) occurs similarly regardless of sex ratio biases present before (B versus D) or after (C versus A, dashed lines show male frequency).
-During the invasion of a neo-ZW sex determination system (A and B), the ancestral Y fixes in both males and females (blue and red lines). 
+Heterogametic transitions from XY to ZW sex determination (neo-W frequency shown by black lines, panels A and B) or from ZW to XY (neo-Y frequency shown by black lines, panels C and D) occur similarly regardless of sex ratio biases present before (B versus D) or after (C versus A, dashed lines show male frequency).
+During invasion by a neo-ZW sex determination system (A and B), the ancestral Y fixes in both males and females (blue and red lines). 
 Similarly, the ancestral W allele fixes in males and females (blue and red lines) during a ZW to XY transition. 
@@
 In panels A and C, the neo-sex-determining locus is more closely linked to the \textbf{A} locus than the ancestral sex-detemining region ($r=1/2$, $R=1/20$) such that a neo-Y can caused biased sex ratios (panel C).
-Unlike with diploid selection alone, when there is haploid selection (in this case meiotic drive), neo-sex-determining loci that are less closely linked to the \textbf{A} locus can also spread (panels B and D, $r=1/20$, $R=1/2$), see equation \eqref{eq:lambda_neoW} and Figure \ref{fig:Combination_Centimorgans}B.
-These transitions are unusual because linkage generally allows favourable associations to arise via selection and the new sex determination systems in B and D have looser linkage. 
-Thus, diploid mean fitness decreases over the course of the transitions in B and D, see Figure \ref{fig:Combination_MeanFit}.
-However, the mean fitness of females increases during the spread of dominant neo-W alleles and the mean fitness of males increases during the spread of dominant neo-Y alleles, Figure \ref{fig:Combination_MeanFit}.
-In this plot there are no sex differences in selection and an equilirbium is maintained because selection in diploids opposes meiotic drive, $s^\female =s^\male = 1/5$, $h^\female = h^\male = 7/10$.
+In panels B and D, the ancestral sex-determining locus is more closely linked to the \textbf{A} locus than the neo-sex-detemining locus ($r=1/20$, $R=1/2$). 
+Therefore, an ancestral XY sex determination can have a biased zygotic sex ratio that becomes unbiased after an unlinked neo-W invades (B). 
+However, in panel D, a unlinked neo-Y invades an ancestral ZW sex determination system in a similar manner but no biases to the zygotic sex ratio occur. 
+With diploid selection alone, neo-sex-determining loci do not spread if they are less closely linked to the \textbf{A} locus than the ancestral sex-determining locus (see equation \eqref{eq:lambda_neoW} and Figure \ref{fig:Combination_Centimorgans}A).
+In this plot there are no sex differences in selection and an equilibrium is maintained because selection in diploids opposes meiotic drive, $s^\female =s^\male = 1/5$, $h^\female = h^\male = 7/10$.
 \textcolor{red}{Aethetic adjustments: Could add titles to the columns/rows: neo-W for row 1, neo-Y for row 3, $r=0.5$, $R=0.05$ for column 1 and $r=0.05$, $R=0.5$ for column 2.
@@
 It also seems could increase ratio of font size relative to plot size to make figure more compact.
-Could make sex ratio biases more extreme by reducing the $r$ in A and C and reducing $R$ in B and D.
 Matt - could you uncomment the line legends in the Mathematica file (function not included in my Mathematica version).}
@@
 \label{fig:Combination_Turnover}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Changes in mean fitness
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[!h]
+\centering
+\includegraphics[width=\linewidth]{Combination_MeanFit}\\
+\caption{
+Here, we plot how male mean fitness (blue lines), female mean fitness (red lines), and population mean fitness (male mean fitness plus female mean fitness, black lines) changes during the transitions between sex-determination systems shown in Figure \ref{fig:Combination_Turnover}.
+Here we multiply male mean fitness and female mean fitness by two so that we can show it on the same scale as population mean fitness. 
+The mean fitness of females increases during the spread of neo-W alleles (A and B) and the mean fitness of males increases during the spread of neo-Y alleles (C and D). 
+However, when a neo-sex determining system evolves that is less closely linked to a locus under selection (B and D), population mean fitness decreases. 
+\textcolor{red}{
+Could add titles to the columns/rows: neo-W for row 1, neo-Y for row 3, $r=0.5$, $R=0.05$ for column 1 and $r=0.05$, $R=0.5$ for column 2.
+\& possibly adjust padding (too much whitespace?).
+Matt - could you uncomment the line legends in the Mathematica file (function not included in my Mathematica version).}
+}
+\label{fig:Combination_MeanFit}
 \end{figure}
@@
 \caption{
-The invasion fitness of a neo-sex-determining locus with various 
-\textcolor{red}{A sexual antagonism (no haploid selection), B drive (no gametic competition), equal selection in sexes ($s^\female=s^\male$), C \& D Pollen/Sperm competition only (no drive).
-C allele favoured in pollen/sperm competition selected against less in males ($t<0$, $s^\female, s^\male >0$, $s^\female<s^\female$).
-D allele favoured in pollen/sperm competition selected against more in males than females ($t<0$, $s^\female, s^\male >0$, $s^\female>s^\female$).
-I suspect that panel C has a region where no equilibrium is maintained (CHECK!
-Maybe include different parameters here).
-Currently use different parameters for B than using in figure \ref{fig:Combination_Turnover} (selection/drive twice as strong in turnover figure)}
+The invasion fitness of a neo-W allele plotted against the relative location of a locus under direct selection, \textbf{A}, for various selective regimes. 
+We assume that the ancestral sex-determining locus is located at -0.25, the novel sex-determining locus is located at 0.25 and that there is a polymorphism at the \textbf{A} locus maintained by selection.
+We used Haldane's map function \citep[Equation 3 in ][]{Haldane1919} to convert from map distance (centiMorgans) to the probability of a cross-over event. 
+In A, there is no haploid selection ($t^\Hermaphrodite=\alpha^\Hermaphrodite_{\Delta}=0$) and selection in diploids is sexually antagonistic \citep[following][]{vanDoorn:2010hu}, in which case a neo-W can only invade if it is more closely linked to the selected locus ($s^\female=1/10$, $h^\female=7/10$ $s^\male=-1/10$, $h^\male=3/10$).
+In B-D we include haploid selection and assume that selection in diploids is not sexually-antagonistic ($s^\female s^\male>0$). 
+A polymorphism can then be maintained by opposing selection between the haploid and diploid phases. 
+In B, there is drive in favour of the $a$ allele in males ($\alpha^\male_{\Delta}=-1/10$), no female meiotic drive or gametic competition, $t^\Hermaphrodite=\alpha^\female_{\Delta}=0$), and equal selection in diploid sexes ($s^\female=s^\male=1/10$, $h^\female=h^\male=7/10$).
+In this case, a neo-W can invade even when the selected locus is more closely linked to the ancestral sex determining locus (see Table \ref{tab:specialcases} and Figure \ref{fig:Combination_Turnover}).
+In C and D, there is gametic competition among male gametes only (favouring $a$, $t^\male=-1/10$) and no meiotic drive or gametic competition in females ($t^\female=\alpha^\Hermaphrodite_{\Delta}=0$).
+In this case, if the selected locus is closely linked to the ancestral sex-determining locus, the neo-W only invades when the allele favoured in pollen/sperm competition selected against more in males than females (D versus C, see Table \ref{tab:specialcases}).
+In C, $s^\female=3/20$, and $s^\male=1/20$, whereas in D, $s^\female=1/20$, and $s^\male=3/20$.
+In both C and D, $h^\female=h^\male=7/10$.
+\textcolor{red}{I suspect that panel C has a region where no equilibrium is maintained (CHECK!
+Maybe include different parameters here or remove the part when no equilibrium).
+Currently use different parameters for B than using in figure \ref{fig:Combination_Turnover} (selection/drive twice as strong in turnover figure).
+This plot would also benefit from titles giving, e.g., ``sexually-antagonistic selection, $s^\female s^\male<0$'' for A, ``male meiotic drive, $s^\female s^\male>0$'' for B}
 }
@@
 
-\section*{Supplementary Figures}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Changes in mean fitness
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-\includegraphics[width=\linewidth]{Combination_MeanFit}\\
-\caption{
-\textcolor{red}{Could add titles to the columns/rows: neo-W for row 1, neo-Y for row 3, $r=0.5$, $R=0.05$ for column 1 and $r=0.05$, $R=0.5$ for column 2.
-\& possibly adjust padding (too much whitespace?).
-Matt - could you uncomment the line legends in the Mathematica file (function not included in my Mathematica version).}
-}
-\label{fig:Combination_MeanFit}
-\end{figure}
+%\section*{Supplementary Figures}
 

### 2017-02-10 LaTeX/Turnover.tex
fine editing mikes final version to send to sally

@@
 For example, \citet{Kozielska:2010vm} consider systems in which the ancestral sex chromosomes experience meiotic drive (e.g., where driving X or Y chromosomes are inherited disproportionately often), which causes sex ratios to become biased \citep{Hamilton:1967ts}.
-They find that new, unlinked sex-determining loci (masculinizing or feminizing mutations, i.e., neo-Y or neo-W loci) can then spread, which restoring an even sex ratio.
+They find that new, unlinked sex-determining loci (masculinizing or feminizing mutations, i.e., neo-Y or neo-W loci) can then spread, which restore an even sex ratio.
 
 We note two other ways in which sex determination has been shown to relate to zygotic sex ratios.
-Firstly, female-biased sex ratios can be favoured when there is local mate competition, in which brothers compete for mates \citep{Hamilton:1967ts}. 
+Firstly, female-biased sex ratios can be favoured when there is local mate competition, where all matings are between siblings and assuming one male can inseminate many females \citep{Hamilton:1967ts}.
 Therefore, with local mate competition, feminizing mutations can spread because they bias the sex ratio towards females \citep{Wilson:1981vm,Vuillleumier:2007bh}. 
@@
 Haploid genotypes at many loci experience selection during gamete competition and/or meiotic drive \citep{Mulcahy:1996ha,JOSEPH:2004haa}.
-We use the term `meiotic drive' to refer to the biased (non-medelian) segregation of genotypes during gamete production and the term `gametic competition' to refer to selection upon haploid genotypes within a gamete/gametophyte pool; the term `haploid selection' encompasses both processes.
+We use the term `meiotic drive' to refer to the biased (non-Mendelian) segregation of genotypes during gamete production and the term `gametic competition' to refer to selection upon haploid genotypes within a gamete/gametophyte pool; the term `haploid selection' encompasses both processes.
 Meiotic drive generally occurs either during the production of male or female gametes only \citep{Ubeda:2005gw,Lindholm:2016cw}.
-Because there are typically more pollen/sperm than required for fertilization, gametic competition is also typically sex specific, occurring primarily among male gametes.
+Because there are typically many more pollen/sperm than required for fertilization, gametic competition is also typically sex specific, occurring primarily among male gametes.
 Gametic competition may be particularly common in plants, in which 60-70\% of all genes are expressed in the male gametophyte and these genes exhibit stronger signatures of selection than random genes \citep{Borg:2009jpa,Arunkumar:2013iq,Gossmann:2014dua}.
@@
 We find that the spread of new sex determination systems are independent of there being a zygotic sex ratio bias caused by associations between sex-determining regions and haploid selected loci. 
-In addition, we find that associations that build up between an ancestral sex-determining locus and a haploid-selected locus can favour transitions between male and female heterogamety (e.g., a neo-W allele arising at a previously autosomal locus spreads in an ancestrally XY system), despite the fact that these ancestral associations were built up by selection.
+In addition, we find that associations that build up between an ancestral sex-determining locus and a haploid-selected locus can favour sex chromosome transitions between male and female heterogamety (e.g., a neo-W allele arising at a previously autosomal locus spreads in an ancestrally XY system), despite the fact that these ancestral associations were built up by selection.
 This does not occur in models that do not include haploid selection.
@@
 The next generation of gametes are then produced by meiosis, during which recombination and sex-specific meiotic drive can occur. 
-Recombination occurs between loci \textbf{X} and \textbf{A} with probability $r$, between loci \textbf{A} and \textbf{M} with probability $R$, and between loci \textbf{X} and \textbf{M} with probability $\chi$.
+Recombination (i.e., an odd number of cross-overs) occurs between loci \textbf{X} and \textbf{A} with probability $r$, between loci \textbf{A} and \textbf{M} with probability $R$, and between loci \textbf{X} and \textbf{M} with probability $\chi$.
 Therefore, any order of the loci can be modelled with appropriate choices of $r$, $R$, and $\chi$ (see Table \ref{tab:chisubstitutions}). 
@@
 %where $b$ is the average of the growth rates of the two haplotypes that carry the $m$ allele ($mA$ and $ma$), $b=(\lambda_{mA}+\lambda_{ma})/2$, and $c$ also involves the fitness of $m$ alleles when they recombine onto the other \textbf{A} background in a heterozygote, $c=\lambda_{mA}\lambda_{ma}+\rho_{mA}\rho_{ma}$ (see table \ref{tab:haplotype_growth}).
-In this case $b= - (\lambda_{mA} + \lambda_{ma})$ and $c = \lambda_{mA} \lambda_{ma} -\rho_{mA} \rho_{ma}$, where $\lambda_{mi}$ \textcolor{red}{I think we can call this growth rate, rather than reserving "growth rate" for $\lambda-1$.
-e.g., in ecological models, can't we call both R (in discrete time) and r (in continuous time) "growth rates"?} is the growth rate of mutant haplotypes on background $i\in\{A,a\}$, accounting for loss due to recombination, and $\rho_{mi}$ is the rate of addition of mutant haplotypes onto background $i\in\{A,a\}$ due to recombination (see table \ref{tab:haplotype_growth}).
-\textcolor{red}{check these interpretations.
+In this case $b= - (\lambda_{mA} + \lambda_{ma})$ and $c = \lambda_{mA} \lambda_{ma} -\rho_{mA} \rho_{ma}$, where $\lambda_{mi}$ is the (discrete time) growth rate of mutant haplotypes on background $i\in\{A,a\}$, accounting for loss due to recombination, and $\rho_{mi}$ is the rate of addition of mutant haplotypes onto background $i\in\{A,a\}$ due to recombination (see table \ref{tab:haplotype_growth}).
+\textcolor{red}{check these interpretations (note the 2s in the lambdas of table 2).
 the $\lambda$s are certainly related to true growth rates because we get them by looking at the case where $R=0$ so that you only have the haplotypes growing/declining.
@@
 Equation \eqref{eq:lambda_neoW} shows that if there is no selection upon haploid genotypes ($t^\Hermaphrodite=\alpha^\Hermaphrodite_{\Delta}=0$), as considered by \citet{vanDoorn:2010hu}, the spread of a neo-W is equivalent to the spread of a neo-Y ($\lambda_{W',XY}=\lambda_{Y',XY}$) such that heterogametic transitions (XY to ZW or ZW to XY) can also occur only if the neo-sex-determining region is more closely linked to a locus under selection ($R<r$).
-However, if there is any haploid selection, the additional term in equation \eqref{eq:lambda_neoW} can be positive, which can allow neo-W invasion ($\lambda_{W',XY}>1$) even when the neo-sex-determining region is less closely linked to the selected locus ($R>r$).
+However, if there is any haploid selection, the additional term in equation \eqref{eq:lambda_neoW} can be positive, which can allow, for example, neo-W invasion ($\lambda_{W',XY}>1$) even when the neo-sex-determining region is less closely linked to the selected locus ($R>r$).
 These transitions are unusual because, when $R>r$, associations that build up by selection between sex and selected alleles will be weakened. 
@@
 
-We find that neo-W alleles can invade for a large number of selective regimes. 
+We find that neo-W alleles can invade an XY system for a large number of selective regimes. 
 To clarify the parameter space under which $\lambda_{W',XY}>1$, we consider several special cases. 
@@
 Under Fisherian sex ratio selection, autosomal modifiers favour equal investment in male and female offspring, i.e., a 1:1 sex ratio \citep{Fisher:1930wy,Charnov:1982wg,West:2009we}. 
-Therefore, we are particularly interested in the case where the novel environmental sex-determiner causes half of its carriers to become female and half to become male ($k=1/2$). 
-As with an autosomal locus, these sex-determiners will be found in males half of the time and in females half of the time.
+Therefore, a novel environmental sex-determiner that causes half of its carriers to become female and half to become male ($k=1/2$) will be in males half of the time and in females half of the time (like an autosome), and so should be favoured by sex ratio selection.
+%As with an autosomal locus, these sex-determiners will be found in males half of the time and in females half of the time.
 However, we find that the growth rate of a rare, dominant offspring-controlled neo-ESD allele that produces males or females with equal probability ($k=1/2$) is
@@
 preventing associations from building up between allele $A$ and sex.
+
 Equation \eqref{eq:lambda_ESD} shows that invasion by a novel `perfect' ESD (equal sex ratio, $k=1/2$) mutation is the same for an ancestrally XY or ZW system (since $\lambda_{Y',XY} = \lambda_{W',ZW}$, $\lambda_{W',XY} = \lambda_{Y',ZW}$).
@@
 In addition, under environmental sex-determination, the proportion of males/females is sometimes controlled by the mother, e.g., the proportion of eggs laid in warm versus cold environments could determine the sex ratio of offspring.
-We therefore also considered the invasion of a neo-sex-determining allele ($m$) in a model in which mothers that have at least one $m$ allele produce $k$ daughters and $(1-k)$ males. 
+We therefore also considered the invasion of a neo-sex-determining allele ($m$) in a model in which mothers that have at least one $m$ allele produce daughters with probability $k$. 
 As with offspring-controlled ESD, for all $k\in\{0,1/2,1\}$, we find that invasion into an ancestrally XY system is the same as invasion into an ancestrally ZW system (at least up to order $\epsilon^3$), implying transitions between genetic sex determination and maternally controlled environmental sex determination are not driven by Fisherian sex ratio selection on biased zygotic sex ratios.
@@
 Taken at face value, our results indicate that transitions in heterogametey (XY to ZW or vice versa) are more likely to be favoured by selection if there is selection upon both haploid and diploid genotypes rather than diploid selection alone.
-This prediction could be examined using a suitable proxy for haploid selection, for example, \citep{Lenormand:2005vb} use the outcrossing rate as a proxy for the strength of pollen competition. 
+This prediction could be examined using a suitable proxy for haploid selection, for example, \cite{Lenormand:2005vb} use the outcrossing rate as a proxy for the strength of pollen competition. 
 In animals, one might expect gametic competition to be stronger in species where sperm is required to live for a long time after spermatogenesis because transcripts shared during spermatogenesis may become depleted, revealing the haploid phenotype of the sperm \citep{Immler:2014im}.
@@
 Selection among diploids then occurs according to the diploid genotype at the \textbf{A} locus, $h$, for an individual of type $ij$ ($h \in AA$, $Aa$, $aa$, see Table \ref{tab:fitnesstable}). 
-The diploid frequencies after selection in sex $d$ are given by $xx_{ij}^{\Hermaphrodite,s}=w_{h}^{\Hermaphrodite} xx_{ij}/\bar{w}^{\Hermaphrodite}$, $xy_{ij}^{\Hermaphrodite,s}=w_{h}^{\Hermaphrodite} xy_{ij}/\bar{w}^{\Hermaphrodite}$, and $yy_{ij}^{\Hermaphrodite,s}=w_{h}^{\Hermaphrodite} yy_{ij}/\bar{w}^{\Hermaphrodite}$, where $\bar{w}^{\Hermaphrodite}= \sum_{i=1}^{4}\sum_{j=1}^{4}w_{h}^{\Hermaphrodite}xx_{ij}+w_{h}^{\Hermaphrodite}xy_{ij}+w_{h}^{\Hermaphrodite}yy_{ij}$ is the mean fitness of individuals of sex $d$.
+The diploid frequencies after selection in sex $d$ are given by $xx_{ij}^{\Hermaphrodite,s}=w_{h}^{\Hermaphrodite} xx_{ij}/\bar{w}^{\Hermaphrodite}$, $xy_{ij}^{\Hermaphrodite,s}=w_{h}^{\Hermaphrodite} xy_{ij}/\bar{w}^{\Hermaphrodite}$, and $yy_{ij}^{\Hermaphrodite,s}=w_{h}^{\Hermaphrodite} yy_{ij}/\bar{w}^{\Hermaphrodite}$, where $\bar{w}^{\Hermaphrodite}= \sum_{i=1}^{4}\sum_{j=1}^{4}w_{h}^{\Hermaphrodite}xx_{ij}+w_{h}^{\Hermaphrodite}xy_{ij}+w_{h}^{\Hermaphrodite}yy_{ij}$ is the mean fitness of individuals of sex $\Hermaphrodite$.
 

### 2017-02-23 LaTeX/Turnover.tex
not sure what changes there are
incorporated Sally minor changes, except figures and strong selection Appendix section unchanged

@@
 Here, we utilize population genetic models to study the spread of novel sex-determiners when there is a period of sex-specific haploid selection. 
-Many loci experience sex-specific selection on their haploid genotypes during gametic competition (e.g., pollen/sperm competition) or meiosis (i.e., meiotic drive); selective processes that typically occur in one sex or the other.
+Many loci experience sex-specific selection on their haploid genotypes during gametic competition (e.g., pollen/sperm competition) or meiosis (i.e., non-Mendelian segregation); selective processes that typically occur in one sex or the other.
 %Haploid selected loci typically experience a form of sex-specific selection because meiotic drive and/or gametic competition occurs predominantly in one sex or the other. 
@@
 Notably, we find that the spread of new genetic sex determination systems is not affected by sex ratio biases that are caused by haploid selection. 
-In addition, we find that, with haploid selection, transitions between male and female heterogamety (XY to ZW or ZW to XY) can occur despite breaking up favourable associations the between ancestral sex-determining locus and selected loci.
+A surprising result given that other determinants of sex allocation typically experience strong Fisherian sex ratio selection to equalize sex ratios. 
+In addition, we find that, with haploid selection, transitions between male and female heterogamety (XY to ZW or ZW to XY) can occur despite breaking up favourable associations that build up between the ancestral sex-determining locus and selected loci.
 These transitions occur because an unlinked neo-Y (neo-W) can have higher fitness in males (females), even if the population mean fitness is reduced. 
 Such transitions are not possible with diploid selection alone, in which case tighter linkage increases the fitness of both males and females. 
-Furthermore, a period of selection among haploids can favour the stable maintenance of polymorphic sex determination systems. 
 Thus, our models offer several new insights to be explored as information about sex determination in non-model taxa accumulates.
@@
 I wonder if this is actually a fusion event though?
-In addition, many gonochoric/dioecious clades with genetic sex determination exhibit transitions between male (XY) and female (ZW) heterogamety, including lizards \citep{Ezaz:2009tk}, eight of 26 teleost fish families \citep{Mank:2006bt}, true fruit flies \citep[Tephritids,][]{Vicoso:2015hf}, amphibians \citep{Hillis:1990gu}, the angiosperm genus \textit{Silene} \citep{Slancarova:2013dq}, Coleoptera and Hemiptera \citep[][plate 2]{Beukeboom:2014vb}.
+In addition, many gonochoric clades with genetic sex determination exhibit transitions between male (XY) and female (ZW) heterogamety, including lizards \citep{Ezaz:2009tk}, eight of 26 teleost fish families \citep{Mank:2006bt}, true fruit flies \citep[Tephritids,][]{Vicoso:2015hf}, amphibians \citep{Hillis:1990gu}, the angiosperm genus \textit{Silene} \citep{Slancarova:2013dq}, Coleoptera and Hemiptera \citep[][plate 2]{Beukeboom:2014vb}.
 Indeed, in some cases, both male and female heterogametic sex determination systems can be found in the same species, as exhibited by some cichlid species \citep{Ser:2010iq} and \textit{Rana rugosa} \citep{Ogata:2007jm}.
@@
 
-Predominant theories in which new sex determination systems are favoured by selection involve fitness differences between sexes (e.g., sexually antagonistic selection) or sex ratio selection.
+Predominant theories in accounting for the spread of new sex determination systems by selection involve fitness differences between sexes (e.g., sexually antagonistic selection) or sex ratio selection.
 %\citet{Bull:1977wt} shows that direct selection on new sex determination loci can allow them to spread and switch between male and female heterogamety. 
@@
 
-It has been suggested that sex ratio selection could be a particularly important force driving transitions between sex-determining systems \citep[Chapter 7]{Beukeboom:2014vb}. 
+It has been suggested that sex ratio selection is a dominant force in the evolution of sex determination (e.g., \citealt{Bull:1983vi}, p66-67; \citealt{Beukeboom:2014vb}, Chapter 7). 
 The default mode of sex ratio selection is `Fisherian' sex ratio selection, which favours equal investment in male and female offspring \citep[i.e., a 1:1 zygotic sex ratio when assuming that males and females are equally costly to produce,][]{Fisher:1930wy,Charnov:1982wg}.
@@
 
-We note two other ways in which sex determination has been shown to relate to zygotic sex ratios.
-Firstly, female-biased sex ratios can be favoured when there is local mate competition, where all matings are between siblings and assuming one male can inseminate many females \citep{Hamilton:1967ts}.
-Therefore, with local mate competition, feminizing mutations can spread because they bias the sex ratio towards females \citep{Wilson:1981vm,Vuillleumier:2007bh}. 
-Secondly, environmental conditions (e.g., maternal condition, mate quality, age, or host size) can differentially affect the fitness of males versus females such that the optimal allocation to males/females depends on the environment \citep{Trivers:1973wb,Charnov:1977tx,Charnov:1982wg}.
-In such cases, flexible sex determination systems may evolve in order to allow the zygotic sex ratio to be determined in a way that depends on the environment \citep{Charnov:1977tx,Werren:1984tl,Pen:2010kk}.
-In this study, we do not consider environmental condition dependence or local mate competition \citep[reviewed in][]{Charnov:1982wg,Bull:1983vi,West:2009we}.
-
 %\textcolor{red}{We add haploid selection:}
@@
 Haploid genotypes at many loci experience selection during gamete competition and/or meiotic drive \citep{Mulcahy:1996ha,JOSEPH:2004haa}.
-We use the term `meiotic drive' to refer to the biased (non-Mendelian) segregation of genotypes during gamete production and the term `gametic competition' to refer to selection upon haploid genotypes within a gamete/gametophyte pool; the term `haploid selection' encompasses both processes.
+We use the term `meiotic drive' to refer to the biased (non-Mendelian) segregation of genotypes during gamete production (from one parent) and the term `gametic competition' to refer to selection upon haploid genotypes within a gamete/gametophyte pool (potentially from by multiple parents); the term `haploid selection' encompasses both processes.
 Meiotic drive generally occurs either during the production of male or female gametes only \citep{Ubeda:2005gw,Lindholm:2016cw}.
@@
 Gametic competition may be particularly common in plants, in which 60-70\% of all genes are expressed in the male gametophyte and these genes exhibit stronger signatures of selection than random genes \citep{Borg:2009jpa,Arunkumar:2013iq,Gossmann:2014dua}.
-In addition, artificial selection pressures applied to male gametophytes cause the frequency of resistant alleles to increase \citep[e.g.,][]{Hormaza:1996cv,Ravikumar:2003uo,Hedhly:2004iv,Clarke:2004ir}.
-A much smaller proportion of genes are thought to be expressed and selected during competition in animal sperm, although precise estimates are uncertain \citep{Zheng:2001fi,JOSEPH:2004haa,Vibranovski:2010et}.
+In addition, artificial selection pressures applied to male gametophytes are known to cause a response to selection \citep[e.g.,][]{Hormaza:1996cv,Ravikumar:2003uo,Hedhly:2004iv,Clarke:2004ir}. 
+A much smaller proportion of genes are thought to be expressed and selected during competition in animal sperm, although precise estimates are uncertain \citep{Zheng:2001fi,JOSEPH:2004haa,Vibranovski:2010et,Immler:2014im}.
 
@@
 In addition, we find that associations that build up between an ancestral sex-determining locus and a haploid-selected locus can favour sex chromosome transitions between male and female heterogamety (e.g., a neo-W allele arising at a previously autosomal locus spreads in an ancestrally XY system), despite the fact that these ancestral associations were built up by selection.
-This does not occur in models that do not include haploid selection.
+Such transitions are not favoured in models lacking haploid selection.
 
@@
 %Diploids compete with others of the same sex, where selection depends on the sex of the individual and its genotype at the \textbf{A} locus.
-The next generation of gametes are then produced by meiosis, during which recombination and sex-specific meiotic drive can occur. 
+The next generation of gametes is then produced by meiosis, during which recombination and sex-specific meiotic drive can occur. 
 Recombination (i.e., an odd number of cross-overs) occurs between loci \textbf{X} and \textbf{A} with probability $r$, between loci \textbf{A} and \textbf{M} with probability $R$, and between loci \textbf{X} and \textbf{M} with probability $\chi$.
 Therefore, any order of the loci can be modelled with appropriate choices of $r$, $R$, and $\chi$ (see Table \ref{tab:chisubstitutions}). 
-Males/females that are heterozygous at the \textbf{A} locus experience meiotic drive; $Aa$ heterozgotes of sex $\Hermaphrodite$ produce gametes bearing allele $A$ with probability $\alpha^\Hermaphrodite$.
+Males/females that are heterozygous at the \textbf{A} locus may experience meiotic drive; $Aa$ heterozgotes of sex $\Hermaphrodite$ produce gametes bearing allele $A$ with probability $\alpha^\Hermaphrodite$.
 Thus, the \textbf{A} locus can experience sex-specific gametic competition, diploid selection and/or meiotic drive.
@@
 The only asymmetry between males and females in our model is that, under the ancestral sex determination system, males develop with genotype $XY$ (or $ZZ$) and females with genotype $XX$ (or $ZW$). 
-Therefore, without loss of generality, we primarily present results for ancestral $XY$ sex determination. 
+Therefore, without loss of generality, we primarily present results for an ancestral $XY$ sex determination system. 
 Ancestral $ZW$ sex determination can be considered by changing the notation such that $X$ becomes $Z$, $Y$ becomes $W$ and the labelling of male and female selection terms are reversed.
@@
 The evolution of a new sex determination system requires that a rare mutant allele, $m$, at the novel sex-determining locus  increases in frequency when rare. 
-The spread of a rare mutant $m$ at the \textbf{M} locus is determined by the leading eigenvalue, $\lambda$, of the system described by the next generation frequency of eggs and sperm carrying the mutation, (\ref{eq:recursions}c), (\ref{eq:recursions}d), (\ref{eq:recursions}g), (\ref{eq:recursions}h), which is an eight equation system.
+The spread of a rare mutant $m$ at the \textbf{M} locus is determined by the leading eigenvalue, $\lambda$, of the system of eight equations describing the next generation frequency of eggs and sperm carrying the mutation, (\ref{eq:recursions}c), (\ref{eq:recursions}d), (\ref{eq:recursions}g), (\ref{eq:recursions}h).
 %, evaluated at the above equilibrium.
 %Thus, the system describing the change in frequency of the $m$ allele consists of eight recursion equations. 
+This system simplifies substantially in a number of cases of interest. 
 Dominant neo-Y (when $k=0$) or neo-W alleles (when $k=1$) are only found in male diploids (neo-Y) or female diploids (neo-W) such that their growth rate ultimately depends only on the change in frequency of $m$-bearing gametes produced by males (for a neo-Y) or by females (for a neo-W).
@@
 %where $b$ is the average of the growth rates of the two haplotypes that carry the $m$ allele ($mA$ and $ma$), $b=(\lambda_{mA}+\lambda_{ma})/2$, and $c$ also involves the fitness of $m$ alleles when they recombine onto the other \textbf{A} background in a heterozygote, $c=\lambda_{mA}\lambda_{ma}+\rho_{mA}\rho_{ma}$ (see table \ref{tab:haplotype_growth}).
-In this case $b= - (\lambda_{mA} + \lambda_{ma})$ and $c = \lambda_{mA} \lambda_{ma} -\rho_{mA} \rho_{ma}$, where $\lambda_{mi}$ is the (discrete time) growth rate of mutant haplotypes on background $i\in\{A,a\}$, accounting for loss due to recombination, and $\rho_{mi}$ is the rate of addition of mutant haplotypes onto background $i\in\{A,a\}$ due to recombination (see table \ref{tab:haplotype_growth}).
-\textcolor{red}{check these interpretations (note the 2s in the lambdas of table 2).
-the $\lambda$s are certainly related to true growth rates because we get them by looking at the case where $R=0$ so that you only have the haplotypes growing/declining.
+In this case $b= - (\lambda_{mA} + \lambda_{ma})$ and $c = \lambda_{mA} \lambda_{ma} -\rho_{mA} \rho_{ma}$, where $\lambda_{mi}$ is the (discrete time) growth rate of mutant haplotypes on background $i\in\{A,a\}$, accounting for loss due to recombination, and $\rho_{mi}$ is the rate of addition of mutant haplotypes onto background $i\in\{A,a\}$ due to recombination, see table \ref{tab:haplotype_growth}.
+The spread of the mutant $m$ allele depends on the frequency of alleles at the other loci in the ancestral population. 
+In the ancestral population, it is convenient to follow the frequency of the $A$ allele in female gametes (eggs) from an XX female, $p^\female_X$, and in X-bearing, $p^\male_X$, and Y-bearing, $p^\male_Y$, male gametes (sperm).
+We also track the fraction of male gametes that are Y-bearing, $q$, which may deviate from $1/2$ due to meiotic drive in males.
+
+\textcolor{red}{I have now put the q's in the lamdbas (i.e., removed them from $\bar{w}^{\male}$ and $\bar{w}^{\female}$).
+Let's wait until we have more results before deciding on a consistent system for $\bar{w}$.
 }
@@
    neo-Y ($k=0$) \\ [0.5ex] \hline \noalign{\vskip 1ex}
-  $\lambda_{mA}=\{p_{X}^{\female} w_{A}^{\female} w_{A}^{\male} w_{AA}^{\male} + 2(1-p_{X}^{\female}) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} \alpha^\male (1 - R)\}/ \{ 2 \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\male\} $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\lambda_{ma}=\{(1-p_{X}^{\female}) w_{a}^{\female} w_{a}^{\male} w_{aa}^{\male} + 2p_{X}^{\female} w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male}(1 - \alpha^\male) (1 - R)\}/ \{ 2 \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\male \}$ \\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\lambda_{mA}=\{p_{X}^{\female} w_{A}^{\female} w_{A}^{\male} w_{AA}^{\male} + 2(1-p_{X}^{\female}) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} \alpha^\male (1 - R)\}/ \{2q \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\male\} $\\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\lambda_{ma}=\{(1-p_{X}^{\female}) w_{a}^{\female} w_{a}^{\male} w_{aa}^{\male} + 2p_{X}^{\female} w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male}(1 - \alpha^\male) (1 - R)\}/ \{ 2q \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\male \}$ \\ [0.5ex] \noalign{\vskip 0.5ex}
   $\rho_{mA}=R (1-p_{X}^{\female}) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} \alpha^{\male}/ \{ \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\male \} $\\ [0.5ex] \noalign{\vskip 0.5ex}
@@
   neo-W ($k=1$) \\ [0.5ex] \hline \noalign{\vskip 1ex}
-  $\lambda_{mA}=\{\bar{p}^{\male} w_{A}^{\male} w_{A}^{\female} w_{AA}^{\female}+2(1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female}\alpha^\female(1-R)\}/ \{ 2 \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\female \}$ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\lambda_{ma}=\{(1-\bar{p}^{\male}) w_{a}^{\male} w_{a}^{\female} w_{aa}^{\female}+2\bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female}(1-\alpha^\female)(1-R)\}/ \{2 \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\female \}$ \\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\lambda_{mA}=\{\bar{p}^{\male} w_{A}^{\male} w_{A}^{\female} w_{AA}^{\female}+2(1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female}\alpha^\female(1-R)\}/ \{ 2(1-q) \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\female \}$ \\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\lambda_{ma}=\{(1-\bar{p}^{\male}) w_{a}^{\male} w_{a}^{\female} w_{aa}^{\female}+2\bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female}(1-\alpha^\female)(1-R)\}/ \{2(1-q) \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\female \}$ \\ [0.5ex] \noalign{\vskip 0.5ex}
   $\rho_{mA}=R (1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female} \alpha^{\female}/ \{\bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\female \} $\\ [0.5ex] \noalign{\vskip 0.5ex}
@@
 Table \ref{tab:haplotype_growth} illustrates a number of key points about the invasion of neo-Y and neo-W mutations. 
-For a neo-Y, invasion depends on the relative lifetime fitness of $A$-bearing and $a$-bearing male gametes (i.e., sperm only).
-The lifetime fitness of male gametes partly depends on the allele carried by the female gamete that they mate with (e.g., $A$ with probability $p_{X}^{\female} w_{A}^{\female}/\bar{w}_{H}^{\female}$).
-Similarly, invasion of a neo-W depends on the relative lifetime fitness of $A$-bearing and $a$-bearing female gametes (i.e., eggs only). 
-However, in the case of a neo-W, the allele carried by the male gamete that they mate with can come from either an X-bearing or a Y-bearing sperm (e.g., $A$ with probability $\bar{p}^{\male} w_{A}^{\male}/\bar{w}_{H}^{\male}$, where $\bar{p}^{\male}=p_{Y}^{\male}q+p_{X}^{\male}(1-q)$).
-In either case, the zygote will then develop as a female due to the presence of a neo-W. 
-By contrast, females that do not carry the neo-W only result from matings with X-bearing sperm (e.g., matings with $A$-bearing sperm that result in females occur with probability $(1-q)\bar{p}_{X}^{\male} w_{A}^{\male}/\bar{w}_{H}^{\male}$).
+For a neo-Y, invasion is driven by the fitness of male gametes and diploids, where the latter is weighted by the chance that a female egg will give rise to that diploid. 
+For example, matings with $A$-bearing female gametes occur with probability $p_{X}^{\female} w_{A}^{\female}/\bar{w}_{H}^{\female}$. 
+Since a neo-Y is always found in males, the allele frequencies at the neo-Y (\textbf{M}) locus only change in males. 
+Therefore, invasion by a neo-Y allele does not involve any female diploid selection terms ($w_{g}^{\female}$). 
+Similarly, invasion by a neo-W is driven by the fitness of female gametes and diploids and does not involve any direct selection in male diploids.
+However, in the case of a neo-W, female diploids can result from matings with either an X-bearing or a Y-bearing sperm. 
+In either case, the zygote will develop as a female due to the presence of a neo-W. 
+For example, neo-W females will therefore inherit an $A$ from a male gamete with probability $\bar{p}^{\male} w_{A}^{\male}/\bar{w}_{H}^{\male}$, where $\bar{p}^{\male}=p_{Y}^{\male}q+p_{X}^{\male}(1-q)$.
+By contrast, females that do not carry the neo-W only result from matings with X-bearing sperm. 
+They will therefore inherit an $A$ from a male gamete with probability probability $(1-q)\bar{p}_{X}^{\male} w_{A}^{\male}/\bar{w}_{H}^{\male}$. 
 If the \textbf{A} locus is initially linked to the ancestral sex-determining locus, \textbf{X}, the frequency of the $A$ allele among X- and Y-bearing sperm can differ (equation \ref{eq:freq_diffs}). 
@@
 The equilibrium  frequency of $A$ on different ancestral backgrounds ($\hat{p}^\male_Y$, $\hat{p}^\male_X$, and $\hat{p}^\female_X$) is given by equations \eqref{eq:pAve} and \eqref{eq:freq_diffs} where we assume selection and meiotic drive are weak relative to recombination ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon$).
-Under weak selection, we denote the leading eigenvalue describing the invasion of a neo-Y ($k=0$) and a neo-W ($k=1$) into an ancestrally XY system by $\lambda_{Y',XY}$ and $\lambda_{W',XY}$, respectively, which are given by
+Under weak selection, we denote the leading eigenvalues describing the invasion of a neo-Y ($k=0$) and a neo-W ($k=1$) into an ancestrally XY system by $\lambda_{Y',XY}$ and $\lambda_{W',XY}$, respectively, which are given by
 
@@
 where $V_{A}=\bar{p}(1-\bar{p})$ is the variance in the frequency of $A$ and $S_{A}=(D^\male +\alpha_{\Delta}^\male+t^\male) - (D^\female+\alpha_{\Delta}^\female+t^\female)$ is the difference in fitness in males versus females for the $A$ allele against the $a$ allele across diploid selection, gametic competition, and meiosis.
+$D^\Hermaphrodite=\big{(} \bar{p}s^\Hermaphrodite+(1-\bar{p})h^\Hermaphrodite s^\Hermaphrodite\big{)} -\big{(} \bar{p}h^\Hermaphrodite s^\Hermaphrodite+(1-\bar{p}) \big{)}$ is the difference in fitness between $A$ and $a$ alleles in diploids of sex $\Hermaphrodite \in \{\female,\male\}$; $\bar{p}$ is the leading-order probability of mating with an $A$-bearing gamete from the opposite sex, see appendix.
 
 The neo-sex-determining allele $m$ will spread if $\lambda_{m,XY}>1$. 
-Equation \eqref{eq:lambda_neoY} demonstrates that a neo-Y will invade if and only if it is more closely linked to the selected locus than the ancestral sex-determining region (i.e., if $R<r$, note that $V_{A}$ and $S_{A}^2$ are strictly positive).
+Equation \eqref{eq:lambda_neoY} demonstrates that a neo-Y will invade if and only if it is more closely linked to the selected locus than the ancestral sex-determining region (i.e., if $R<r$, note that $V_{A}$ and $S_{A}^2$ are strictly positive as long as \textbf{A} is polymorphic).
 This result echoes that of \citet{vanDoorn:2007eu}, who considered diploid selection only and also found that homogametic transitions (XY to XY or ZW to ZW) can occur when the neo-sex-determining locus is more closely linked to a locus under sexually-antagonistic selection.
@@
 However, if there is any haploid selection, the additional term in equation \eqref{eq:lambda_neoW} can be positive, which can allow, for example, neo-W invasion ($\lambda_{W',XY}>1$) even when the neo-sex-determining region is less closely linked to the selected locus ($R>r$).
-These transitions are unusual because, when $R>r$, associations that build up by selection between sex and selected alleles will be weakened. 
-Therefore, mean fitness can decrease, see Figure \ref{fig:Combination_MeanFit}B,D.
+These transitions are unusual because, when $R>r$, associations that have built up between alleles more favourable in one sex and that sex will be weakened. 
+Therefore, mean fitness can decrease (Figure \ref{fig:Combination_MeanFit}B,D).
 
@@
 Secondly, we can simplify cases where invasion occurs despite $R>r$ using the special case where $R=1/2$ and $r<1/2$. 
-In table \ref{tab:specialcases} we give the conditions where invasion occurs where we further assume that haploid selection only occurs during one phase in one sex (e.g., during male meiosis only) and dominance coefficients are equal in the two sexes, $h^\female=h^\male$.
-Where there is no gametic competition and meiotic drive in one sex only, an unlinked neo-W can invade as long as the same allele is favoured in male and female diploid selection ($s^\female s^\male>0$, see Figure \ref{fig:Combination_Centimorgans}B), which is 50\% of the parameter space.
-Where there is no meiotic drive and gametic competition occurs in one sex only, an unlinked neo-W can invade as long as the same allele is favoured in male and female diploid selection and there are sex differences in selection of one type (e.g., $s^\female(s^\male-s^\female)>0$, see Figure \ref{fig:Combination_Centimorgans}C,D), which is 25\% of the parameter space.
-These special cases indicate that neo-W invasion can occur for a relatively large fraction of parameter space, even if the neo-W is less tightly linked to the selected locus, $R>r$.
+In table \ref{tab:specialcases} we give the conditions where invasion occurs where we further assume that haploid selection only occurs in one sex (e.g., during male meiosis only) and dominance coefficients are equal in the two sexes, $h^\female=h^\male$.
+Where there is no gametic competition and meiotic drive in one sex only, an unlinked neo-W can invade as long as the same allele is favoured during diploid selection in males and females ($s^\female s^\male>0$, see Figure \ref{fig:Combination_Centimorgans}B).%, which is 50\% of the parameter space.
+Where there is no meiotic drive and gametic competition occurs in one sex only, an unlinked neo-W can invade as long as the same allele is favoured in male and female diploid selection and there are sex differences in selection of one type (e.g., $s^\female(s^\male-s^\female)>0$, see Figure \ref{fig:Combination_Centimorgans}C,D).
+%, which is 25\% of the parameter space.
+These special cases indicate that neo-W invasion can occur for a relatively large fraction of parameter space, even if the neo-W uncouples the sex-determining locus from a locus under selection.
 
@@
 Consider, for example, the case where the \textbf{A} locus is linked to the ancestral-SDR ($r<1/2$) and experiences meiotic drive in males only (e.g., during spermatogenesis but not during oogenesis, $\alpha^\male \neq 1/2$, $\alpha^\female=1/2$).
-We will also disregard gametic competition ($t^\female=t^\male=0$) such that zygotic sex ratios can only be biased by meiotic drive in males. 
+We will also disregard gametic competition ($t^\female=t^\male=0$) such that zygotic sex ratios are only biased by meiotic drive in males. 
 In this case, the zygotic sex ratio can be initially biased only if the ancestral sex-determining system is XY (Figure \ref{fig:Combination_Turnover}B). 
@@
 
-We next consider the case where the new sex-determining mutation, $m$, causes sex to be determined by environmental conditions (environmental sex determiner, ESD). 
+We next consider the case where the new sex-determining mutation, $m$, causes sex to be determined stochastically or by environmental conditions (environmental sex determiner, ESD). 
 We assume that individuals carrying the $m$ allele develop as females in a fraction, $k$, of the environments they experience. 
@@
 Under Fisherian sex ratio selection, autosomal modifiers favour equal investment in male and female offspring, i.e., a 1:1 sex ratio \citep{Fisher:1930wy,Charnov:1982wg,West:2009we}. 
-Therefore, a novel environmental sex-determiner that causes half of its carriers to become female and half to become male ($k=1/2$) will be in males half of the time and in females half of the time (like an autosome), and so should be favoured by sex ratio selection.
-%As with an autosomal locus, these sex-determiners will be found in males half of the time and in females half of the time.
+Therefore, a novel environmental sex-determiner that causes half of its carriers to become female and half to become male ($k=1/2$) will be in males half of the time and in females half of the time (like an autosome).
+In addition, these novel sex-determination alleles equalize the sex ratio and so one might expect them to be favoured by Fisherian sex ratio selection when the resident sex ratio is biased.
 However, we find that the growth rate of a rare, dominant offspring-controlled neo-ESD allele that produces males or females with equal probability ($k=1/2$) is
@@
 \noindent
-We note that recombination between the selected locus and the novel sex-determining locus, $R$, doesn't enter into the $k=1/2$ results because sex is essentially randomized each generation, %as if the novel sex-determiner were on an unlinked site that half the time acts as a neo-$W$ and half the time as a neo-$Y$.
+where we have indicated that $\lambda_{Y',XY}$ and $\lambda_{W',XY}$ are evaluated at $R=1/2$.
+Recombination between the selected locus and the novel sex-determining locus, $R$, doesn't enter into the $k=1/2$ results because sex is essentially randomized each generation, %as if the novel sex-determiner were on an unlinked site that half the time acts as a neo-$W$ and half the time as a neo-$Y$.
 preventing associations from building up between allele $A$ and sex.
@@
 Rather, the neo-ESD gets half of the fitness of a feminizing mutation (neo-$W$) and half of the fitness of a masculizing mutation (neo-$Y$), but only has an effect one half of the time (the other half of the time it produces the same sex as the ancestral system would have, to leading order).
-The net result can be that perfect ESD will not invade, even if sex ratios are biased. 
+The net result can be that perfect ESD will not invade, even if current sex ratios are biased. 
 For example, if there is haploid selection in males (either drive or pollen/sperm competition) but the conditions in table \ref{tab:specialcases} are not met, perfect ESD will not invade, even though it would equalize the zygotic sex ratio from an initially biased case (assuming $r<1/2$).
@@
 
-One might expect Fisherian sex ratio selection to influence the spread of new sex-determining systems in our models because linkage between haploid selected loci and sex-determining regions causes biased zygotic sex ratios \citep{Hamilton:1967ts,Burt:2006,Field:2012fd,Field:2013cc}.
+Because linkage between haploid selected loci and sex-determining regions cases biased zygotic sex ratios \citep{Hamilton:1967ts,Burt:2006,Field:2012fd,Field:2013cc}, one might expect Fisherian sex ratio selection to drive the spread of new sex-determining systems that bring the sex ratio closer to 50:50.
 Fisherian sex ratio selection follows from the fact that, for an autosomal locus, half of the genetic material is inherited from a male, and half from a female \citep{Fisher:1930wy,West:2009we}. 
@@
 For example, the success of neo-Y/neo-W mutations depends only on the number of alleles contributed by males/females (Table \ref{tab:haplotype_growth}). 
-In this respect, a neo-W is similar to a cytoplasmic element, which also do not experience selection to balance sex ratios \citep{Frank:1989vl,Werren:1998co,Chase:2007bf}.
+In this respect, a neo-W is similar to a cytoplasmic element, which also does not experience selection to balance sex ratios \citep{Frank:1989vl,Werren:1998co,Chase:2007bf}.
 Even mutants that are equally likely to be found in males or females, such as an environmental sex determination mutation (equation \ref{eq:lambda_ESD}), are not strictly autosomal if they determine sex.
 Thus, despite the fact that sex ratio biases caused by gametic competition or meiotic drive have been shown to exert Fisherian sex ratio selection on various autosomal modifiers \citep{Stalker:1961th,Smith:1975ft,Frank:1989vl,Hough:2013uo,Ubeda:2015fx, Otto:2015va}, we do not find evidence of Fisherian sex ratio selection acting during invasion by neo-sex-determination systems (e.g., see Figure \ref{fig:Combination_Turnover} and \citealt{Ubeda:2015fx}, in which a neo-Y invades despite biasing sex ratios).
+
+We note two other ways in which sex determination has been shown to relate to zygotic sex ratios.
+Firstly, female-biased sex ratios can be favoured when there is local mate competition, where all matings are between siblings and assuming one male can inseminate many females \citep{Hamilton:1967ts}.
+Therefore, with local mate competition, feminizing mutations can spread because they bias the sex ratio towards females \citep{Wilson:1981vm,Vuillleumier:2007bh}. 
+Secondly, environmental conditions (e.g., maternal condition, mate quality, age, or host size) can differentially affect the fitness of males versus females such that the optimal allocation to males/females depends on the environment \citep{Trivers:1973wb,Charnov:1977tx,Charnov:1982wg}.
+In such cases, flexible sex determination systems may evolve in order to allow the zygotic sex ratio to be determined in a way that depends on the environment \citep{Charnov:1977tx,Werren:1984tl,Pen:2010kk}.
+In this study, we do not consider environmental condition dependence or local mate competition \citep[reviewed in][]{Charnov:1982wg,Bull:1983vi,West:2009we}.
 
@@
 Our results show that genetic variation at loci that experience haploid selection can also generate selection in favour of new sex-determining systems. 
-New sex-determining alleles are again favoured if they are more closely linked with a locus under haploid selection.
+New sex-determining alleles are again favoured if they are linked with a locus under haploid selection and the ancestral sex-determination locus is not.
 However, with haploid selection, heterogametic transitions (XY to ZW or ZW to XY) can also occur when the new sex-determining region is less closely linked to the locus under selection.
@@
 However, they noted that very rare recombination events around the ancestral sex-determining region can allow these heterogametic transitions to complete.  
+While not explicitly studied, we also predict that Y or W degeneration would prevent fixation of the new sex-determiners considered here.
 
@@
 
-The hypotheses presented here can be investigated in a similar manner to the idea that transitions between sex-determining systems are favoured by linkage to sexually antagonistic variation. 
+The hypotheses presented here can be empirically investigated in a similar manner to the idea that transitions between sex-determining systems are favoured by linkage to sexually antagonistic variation.
 In the case of sexually antagonistic variation, one supporting observation is that genes that appear to experience sexually-antagonistic selection have been found on recently derived sex chromosomes \citep{Lindholm:2002dw,Tripathi:2009cw,Ser:2010iq}.
@@
 Taken at face value, our results indicate that transitions in heterogametey (XY to ZW or vice versa) are more likely to be favoured by selection if there is selection upon both haploid and diploid genotypes rather than diploid selection alone.
-This prediction could be examined using a suitable proxy for haploid selection, for example, \cite{Lenormand:2005vb} use the outcrossing rate as a proxy for the strength of pollen competition. 
+This prediction could be examined using a suitable proxy for haploid selection, for example, \cite{Lenormand:2005vb} use the outcrossing rate in plants as a proxy for the strength of pollen competition.
 In animals, one might expect gametic competition to be stronger in species where sperm is required to live for a long time after spermatogenesis because transcripts shared during spermatogenesis may become depleted, revealing the haploid phenotype of the sperm \citep{Immler:2014im}.
@@
 
-We have shown that haploid selection can drive transitions between sex determination systems, such that haploid selection is should be incorporated into the factors that influence the evolution of sex determination.
+We have shown that haploid selection can drive transitions between sex determination systems, such that haploid selection should be incorporated into the factors that influence the evolution of sex determination.
 However, the particular way in which transitions are affected by haploid selection is not intuitively obvious. 
@@
 
-\textcolor{red}{Numerical results suggest that polygenic sex determination can be stable with gametic competition.
+%\textcolor{red}{Numerical results suggest that polygenic sex determination can be stable with gametic competition.
 i.e., feminizers/masculinizers sometimes invade but don't fix.
@@
 In C and D, there is gametic competition among male gametes only (favouring $a$, $t^\male=-1/10$) and no meiotic drive or gametic competition in females ($t^\female=\alpha^\Hermaphrodite_{\Delta}=0$).
-In this case, if the selected locus is closely linked to the ancestral sex-determining locus, the neo-W only invades when the allele favoured in pollen/sperm competition selected against more in males than females (D versus C, see Table \ref{tab:specialcases}).
-In C, $s^\female=3/20$, and $s^\male=1/20$, whereas in D, $s^\female=1/20$, and $s^\male=3/20$.
-In both C and D, $h^\female=h^\male=7/10$.
+In this case, the neo-W does not invade if $s^\female>s^\male$ (panel C: $s^\female=3/20$, $s^\male=1/20$) but does if $s^\female<s^\male$ (panel D: $s^\female=1/20$, $s^\male=3/20$), see Table \ref{tab:specialcases}.
 \textcolor{red}{I suspect that panel C has a region where no equilibrium is maintained (CHECK!
@@
 
-In each generation we census the genotype frequencies in male and female gametes/gametophytes (hereafter, gametes) before gametic competition. 
-Before gametic competition, the frequencies of X-bearing male and female gametes are given by $X_{i}^{\male}$ and $X_{i}^{\female}$ and the frequencies of Y-bearing gametes are given by $Y_{i}^{\male}$ and $Y_{i}^{\female}$ where the index $i$ specifies genotypes $MA=1$, $Ma=2$, $mA=3$, and $ma=4$.
+In each generation we census the genotype frequencies in male and female gametes/gametophytes (hereafter, gametes) after meiosis (and any meiotic drive) and immediately before gametic competition. 
+At this stage, the frequencies of X-bearing male and female gametes are given by $X_{i}^{\male}$ and $X_{i}^{\female}$ and the frequencies of Y-bearing gametes are given by $Y_{i}^{\male}$ and $Y_{i}^{\female}$ where the index $i$ specifies genotypes $MA=1$, $Ma=2$, $mA=3$, and $ma=4$ ($\sum_{i=1}^{4}Y_{i}^{\male}+X_{i}^{\male}=1$ and $\sum_{i=1}^{4}Y_{i}^{\female}+X_{i}^{\female}=1$).
 Competition then occurs among gametes of the same sex (e.g., among eggs and among sperm separately) according to the \textbf{A} locus allele, $g$ ($g\in A$, $a$, see Table \ref{tab:fitnesstable}), carried by individuals with genotype $i$.
@@
 Random mating then occurs between gametes to produce diploid zygotes with genotype $ij$ at the \textbf{A} and \textbf{M} loci, such that $XX$ zygotes are denoted $xx_{ij}$, $XY$ zygotes are $xy_{ij}$, and $YY$ zygotes are $yy_{ij}$.
-In $XX$ and $YY$ zygotes, individuals with genotype $ij$ are equivalent to those with genotype $ji$. 
-For simplicity, we denote the frequency of genotype $ij$ in $XX$ and $YY$ zygotes to the average of these frequencies, $xx_{ij}=(X_{i}^{\female,s}X_{j}^{\male,s}+X_{j}^{\female,s}X_{i}^{\male,s})/2$ and $yy_{ij}=(Y_{i}^{\female,s}Y_{j}^{\male,s}+Y_{j}^{\female,s}Y_{i}^{\male,s})/2$.
+In $XX$ and $YY$ zygotes, individuals with genotype $ij$ are equivalent to those with genotype $ji$; for simplicity, we denote the frequency of genotype $ij$ to the average of these frequencies, $xx_{ij}=(X_{i}^{\female,s}X_{j}^{\male,s}+X_{j}^{\female,s}X_{i}^{\male,s})/2$ and $yy_{ij}=(Y_{i}^{\female,s}Y_{j}^{\male,s}+Y_{j}^{\female,s}Y_{i}^{\male,s})/2$.
 
@@
 Selection among diploids then occurs according to the diploid genotype at the \textbf{A} locus, $h$, for an individual of type $ij$ ($h \in AA$, $Aa$, $aa$, see Table \ref{tab:fitnesstable}). 
-The diploid frequencies after selection in sex $d$ are given by $xx_{ij}^{\Hermaphrodite,s}=w_{h}^{\Hermaphrodite} xx_{ij}/\bar{w}^{\Hermaphrodite}$, $xy_{ij}^{\Hermaphrodite,s}=w_{h}^{\Hermaphrodite} xy_{ij}/\bar{w}^{\Hermaphrodite}$, and $yy_{ij}^{\Hermaphrodite,s}=w_{h}^{\Hermaphrodite} yy_{ij}/\bar{w}^{\Hermaphrodite}$, where $\bar{w}^{\Hermaphrodite}= \sum_{i=1}^{4}\sum_{j=1}^{4}w_{h}^{\Hermaphrodite}xx_{ij}+w_{h}^{\Hermaphrodite}xy_{ij}+w_{h}^{\Hermaphrodite}yy_{ij}$ is the mean fitness of individuals of sex $\Hermaphrodite$.
+The diploid frequencies after selection in sex $\Hermaphrodite$ are given by $xx_{ij}^{\Hermaphrodite,s}=w_{h}^{\Hermaphrodite} xx_{ij}/\bar{w}^{\Hermaphrodite}$, $xy_{ij}^{\Hermaphrodite,s}=w_{h}^{\Hermaphrodite} xy_{ij}/\bar{w}^{\Hermaphrodite}$, and $yy_{ij}^{\Hermaphrodite,s}=w_{h}^{\Hermaphrodite} yy_{ij}/\bar{w}^{\Hermaphrodite}$, where $\bar{w}^{\Hermaphrodite}= \sum_{i=1}^{4}\sum_{j=1}^{4}w_{h}^{\Hermaphrodite}xx_{ij}+w_{h}^{\Hermaphrodite}xy_{ij}+w_{h}^{\Hermaphrodite}yy_{ij}$ is the mean fitness of individuals of sex $\Hermaphrodite$.
 
@@
 Table \ref{tab:chisubstitutions} gives substitutions for $\chi$ for defined relative locations of these loci.
-During meiosis in sex $d$, meiotic drive occurs such that, in $Aa$ heterozygotes, a fraction $\alpha_{d}$ of gametes produced carry the $A$ allele and $(1-\alpha^\Hermaphrodite)$ carry the $a$ allele.
+During meiosis in sex $\Hermaphrodite$, meiotic drive occurs such that, in $Aa$ heterozygotes, a fraction $\alpha^{\Hermaphrodite}$ of gametes produced carry the $A$ allele and $(1-\alpha^\Hermaphrodite)$ carry the $a$ allele.
 
@@
 
-Among gametes from sex $\Hermaphrodite$ (sperm/pollen when $\Hermaphrodite=\male$, eggs/ovules when $\Hermaphrodite=\female$), the frequency of haplotypes (before gametic competition) in the next generation are given by
+Among gametes from sex $\Hermaphrodite$ (sperm/pollen when $\Hermaphrodite=\male$, eggs/ovules when $\Hermaphrodite=\female$), the frequencies of haplotypes (before gametic competition) in the next generation are given by
 
+\begingroup
+\allowdisplaybreaks
 \begin{subequations}
-\begin{equation}
+\begin{align}
+%
 \begin{split}
@@
 \end{split}
-\end{equation}
+\\
 %
-\begin{equation}
 \begin{split}
@@
 \end{split}
-\end{equation}
-%%%%%%%%%%%%%%%%%%%
-%
-\begin{equation}
+\\
 \begin{split}
@@
 \end{split}
-\end{equation}
+\\
 \label{eq:recursions}
+\end{align}
 \end{subequations}
+
+\endgroup
 
@@
 This six-equation system yields equilibrium \eqref{eq:pAve}.
-Within this resident population (when $m$ is absent) we describe frequencies among different gamete types, which are given by $X_{MA}^{\female}=p_{Xf}$, $X_{Ma}^{\female}=(1-p_{Xf})$, $X_{MA}^{\male}=(1-q)p_{Xm}$, $X_{Ma}^{\male}=(1-q)(1-p_{Xm})$, $Y_{MA}^{\male}=q p_{Ym}$, and $Y_{Ma}^{\male}=q(1-p_{Ym})$.
-In this resident population, the mean fitnesses are given in table \ref{tab:meanfitnesses}.
+
+%I think this should be moved below because we have some 'results' where we don't assume weak selection but we only have the equilibrium calculated analytically for weak selection. 
+\subsection*{Resident equilibrium and stability}
+In the resident population (allele $M$ fixed), we follow the frequency of $A$ in female gametes (eggs) from an XX female, $p^\female_X$, and in X-bearing, $p^\male_X$, and Y-bearing, $p^\male_Y$, male gametes (sperm).
+We also track the total frequency of Y among male gametes, $q$, which may deviate from $1/2$ due to meiotic drive in males. 
+Within this resident population (when $m$ is absent) we can then describe frequencies among different gamete types, which are given by $X_{MA}^{\female}=p_{Xf}$, $X_{Ma}^{\female}=(1-p_{Xf})$, $X_{MA}^{\male}=(1-q)p_{Xm}$, $X_{Ma}^{\male}=(1-q)(1-p_{Xm})$, $Y_{MA}^{\male}=q p_{Ym}$, and $Y_{Ma}^{\male}=q(1-p_{Ym})$.
+Mean fitnesses in this resident population are given in table \ref{tab:meanfitnesses}.
 
@@
 
-%I think this should be moved below because we have some 'results' where we don't assume weak selection but we only have the equilibrium calculated analytically for weak selection. 
-\subsection*{Resident equilibrium and stability}
-In the resident population (allele $M$ fixed), we follow the frequency of $A$ in female gametes (eggs) from an XX female, $p^\female_X$, and in X-bearing, $p^\male_X$, and Y-bearing, $p^\male_Y$, male gametes (sperm).
-We also track the total frequency of Y-bearing male gametes, $q$, which may deviate from $1/2$ due to meiotic drive in males.
-
 Various forms of selection can maintain a polymorphism at the \textbf{A} locus, including sexually antagonistic selection, overdominance and conflicts between diploid selection and selection upon haploid genotypes \citep[ploidally antagonistic selection,][]{Immler:2012tl} or a combination of these selective regimes.
@@
 %
-0&<(h^\female s^\female +h^\male s^\male + t^\female +t^\male + \alpha_{\Delta}^\female+\alpha_{\Delta}^\male).
+\text{and }\quad 0&<(h^\female s^\female +h^\male s^\male + t^\female +t^\male + \alpha_{\Delta}^\female+\alpha_{\Delta}^\male).
 \end{split}
@@
 where $V_{A}=\bar{p}(1-\bar{p})$ is the variance in the frequency of $A$ and $D^\Hermaphrodite=\big{(} \bar{p}s^\Hermaphrodite+(1-\bar{p})h^\Hermaphrodite s^\Hermaphrodite\big{)} -\big{(} \bar{p}h^\Hermaphrodite s^\Hermaphrodite+(1-\bar{p}) \big{)}$ corresponds to the difference in fitness between $A$ and $a$ alleles in diploids of sex $\Hermaphrodite \in \{\female,\male\}$ ($\bar{p}$ is the leading-order probability of mating with an $A$-bearing gamete from the opposite sex).
-The frequency of Y among male gametes depends upon the difference in $A$ allele frequency on X- and Y-bearing male gametes and the strength of meiotic drive in favour of the $A$ allele in males, $q=1/2+\alpha_{\Delta}^\male(\hat{p}^\male_Y-\hat{p}^\male_X)/2+O(\epsilon^3)$.
+The frequency of Y among male gametes depends upon the difference in the frequency of the $A$ allele between X- and Y-bearing male gametes and the strength of meiotic drive in favour of the $A$ allele in males, $q=1/2+\alpha_{\Delta}^\male(\hat{p}^\male_Y-\hat{p}^\male_X)/2+O(\epsilon^3)$.
 Without gametic competition or drive ($\alpha_{\Delta}^\Hermaphrodite=t^\Hermaphrodite=0$), these results reduce to those of \citet{vanDoorn:2007eu}.
@@
 \right] 
-\frac{w^\male_{Aa}}{\bar{w}^\male} < 1,
+\frac{w^\female_{Aa}}{\bar{w}^\female} < 1,
 \end{equation}
@@
 for the neo-$W$.
-Equations \eqref{eq:neoYR} and \eqref{eq:neoWR} show that the new sex-determining allele, $m$, is expected to invade for any probability of recombination between loci \textbf{A} and \textbf{M}, $r_{AM}$, when the net flow of recombinants is from the less fit (smaller $\lambda_{mi}$) to the more fit \textbf{A} background (making the terms inside the square brackets in Equations \ref{eq:neoYR} and \ref{eq:neoWR} negative).
+Equations \eqref{eq:neoYR} and \eqref{eq:neoWR} show that the new sex-determining allele, $m$, is expected to invade for any probability of recombination between loci \textbf{A} and \textbf{M}, $R$, when the net flow of recombinants is from the less fit (smaller $\lambda_{mi}$) to the more fit \textbf{A} background (making the terms inside the square brackets in Equations \ref{eq:neoYR} and \ref{eq:neoWR} negative).
 %\textcolor{red}{Q: is it definitely possible to have negative square brackets for a equilibria maintained by selection?}

### 2017-02-27 LaTeX/Turnover.tex
started looking at weak recombination but need sleep

@@
   $\lambda_{ma}=\{(1-p_{X}^{\female}) w_{a}^{\female} w_{a}^{\male} w_{aa}^{\male} + 2p_{X}^{\female} w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male}(1 - \alpha^\male) (1 - R)\}/ \{ 2q \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\male \}$ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\rho_{mA}=R (1-p_{X}^{\female}) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} \alpha^{\male}/ \{ \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\male \} $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\rho_{ma}=R p_{X}^{\female} w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male} (1 - \alpha^{\male})/ \{ \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\male \}$\\ [1ex] \hline 
+  $\rho_{mA}=R (1-p_{X}^{\female}) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} \alpha^{\male}/ \{ q \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\male \} $\\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\rho_{ma}=R p_{X}^{\female} w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male} (1 - \alpha^{\male})/ \{ q \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\male \}$\\ [1ex] \hline 
   \noalign{\vskip 0.5ex}
@@
   $\lambda_{ma}=\{(1-\bar{p}^{\male}) w_{a}^{\male} w_{a}^{\female} w_{aa}^{\female}+2\bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female}(1-\alpha^\female)(1-R)\}/ \{2(1-q) \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\female \}$ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\rho_{mA}=R (1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female} \alpha^{\female}/ \{\bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\female \} $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\rho_{ma}=R\bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female} (1-\alpha^{\female})/ \{\bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\female \}$\\ [1ex] 
+  $\rho_{mA}=R (1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female} \alpha^{\female}/ \{(1-q)\bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\female \} $\\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\rho_{ma}=R\bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female} (1-\alpha^{\female})/ \{(1-q)\bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\female \}$\\ [1ex] 
   \hline \hline 
@@
   females ($\bar{w}^\female$) & 
-  $\begin{array}{l}  \{ p_X^\female w_A^\female (1-q) p_X^\male w_A^\male w_{AA}^\female + \\
-  (1 - p_X^\female) w_a^\female (1-q) p_X^\male w_A^\male w_{Aa}^\female + \\
-  p_X^\female w_A^\female (1-q) (1 - p_X^\male) w_a^\male w_{Aa}^\female + \\
-  (1-p_X^\female) w_a^\female (1-q) (1 - p_X^\male) w_a^\male w_{aa}^\female \} / \{ \bar{w}_H^\female \bar{w}_H^\male\}
+  $\begin{array}{l}  \{ p_X^\female w_A^\female p_X^\male w_A^\male w_{AA}^\female + \\
+  (1 - p_X^\female) w_a^\female p_X^\male w_A^\male w_{Aa}^\female + \\
+  p_X^\female w_A^\female (1 - p_X^\male) w_a^\male w_{Aa}^\female + \\
+  (1-p_X^\female) w_a^\female (1 - p_X^\male) w_a^\male w_{aa}^\female \} / \{ \bar{w}_H^\female \bar{w}_H^\male\}
   \end{array} 
@@
   males ($\bar{w}^\male$) & 
-  $\begin{array}{l} \{ p_X^\female w_A^\female q p_Y^\male w_A^\male w_{AA}^\male + \\
-  (1 - p_X^\female) w_a^\female q p_Y^\male w_A^\male w_{Aa}^\male + \\
-  p_X^\female w_A^\female q (1 - p_Y^\male) w_a^\male w_{Aa}^\male + \\
-  (1-p_X^\female) w_a^\female q (1 - p_Y^\male) w_a^\male w_{aa}^\male \} / \{ \bar{w}_H^\male \bar{w}_H^\male\} 
+  $\begin{array}{l} \{ p_X^\female w_A^\female  p_Y^\male w_A^\male w_{AA}^\male + \\
+  (1 - p_X^\female) w_a^\female  p_Y^\male w_A^\male w_{Aa}^\male + \\
+  p_X^\female w_A^\female  (1 - p_Y^\male) w_a^\male w_{Aa}^\male + \\
+  (1-p_X^\female) w_a^\female  (1 - p_Y^\male) w_a^\male w_{aa}^\male \} / \{ \bar{w}_H^\male \bar{w}_H^\male\} 
   \end{array}
@@
 \right] 
-\frac{w^\male_{Aa}}{\bar{w}^\male} < 1,
+\frac{w^\male_{Aa}}{q\bar{w}^\male} < 1,
 \end{equation}
@@
 \right] 
-\frac{w^\female_{Aa}}{\bar{w}^\female} < 1,
+\frac{w^\female_{Aa}}{(1-q)\bar{w}^\female} < 1,
 \end{equation}

### 2017-03-02 LaTeX/Turnover.tex
position plots for w and y made
merging edits made from Sally's comments and new fig 3

--- 2017-02-23 LaTeX/Turnover.tex
@@
 In either case, the zygote will develop as a female due to the presence of a neo-W. 
-For example, neo-W females will therefore inherit an $A$ from a male gamete with probability $\bar{p}^{\male} w_{A}^{\male}/\bar{w}_{H}^{\male}$, where $\bar{p}^{\male}=p_{Y}^{\male}q+p_{X}^{\male}(1-q)$.
+For example, neo-W females will inherit an $A$ allele from a male gamete with probability $\bar{p}^{\male} w_{A}^{\male}/\bar{w}_{H}^{\male}$, where $\bar{p}^{\male}=p_{Y}^{\male}q+p_{X}^{\male}(1-q)$ is the frequency of the A allele among both X- and Y-bearing male gametes.
 By contrast, females that do not carry the neo-W only result from matings with X-bearing sperm. 
-They will therefore inherit an $A$ from a male gamete with probability probability $(1-q)\bar{p}_{X}^{\male} w_{A}^{\male}/\bar{w}_{H}^{\male}$. 
+They will therefore inherit an $A$ from a male gamete with probability $(1-q)\bar{p}_{X}^{\male} w_{A}^{\male}/\bar{w}_{H}^{\male}$. 
 If the \textbf{A} locus is initially linked to the ancestral sex-determining locus, \textbf{X}, the frequency of the $A$ allele among X- and Y-bearing sperm can differ (equation \ref{eq:freq_diffs}). 
@@
 In this plot there are no sex differences in selection and an equilibrium is maintained because selection in diploids opposes meiotic drive, $s^\female =s^\male = 1/5$, $h^\female = h^\male = 7/10$.
-\textcolor{red}{Aethetic adjustments: Could add titles to the columns/rows: neo-W for row 1, neo-Y for row 3, $r=0.5$, $R=0.05$ for column 1 and $r=0.05$, $R=0.5$ for column 2.
+\textcolor{red}{Aesthetic adjustments: Could add titles to the columns/rows: neo-W for row 1, neo-Y for row 3, $r=0.5$, $R=0.05$ for column 1 and $r=0.05$, $R=0.5$ for column 2.
 Could adjust padding (too much whitespace where there is no axis label).

### 2017-03-02 LaTeX/Turnover.tex

--- 2017-02-27 LaTeX/Turnover.tex
@@
 \centering
-\includegraphics[width=\linewidth]{Combination_Centimorgan}\\
+%\includegraphics[width=\linewidth]{Combination_Centimorgan}\\
+\includegraphics[width=\linewidth]{PositionPlot}\\
 \caption{

### 2017-03-02 LaTeX/Turnover.tex
abstract updated to include tight linkage results

@@
 Predominant theories in which new sex-determining systems are favoured by selection involve sex ratio selection or sex-specific selection (e.g., sexually antagonistic selection).
-Here, we utilize population genetic models to study the spread of novel sex-determiners when there is a period of sex-specific haploid selection. 
-Many loci experience sex-specific selection on their haploid genotypes during gametic competition (e.g., pollen/sperm competition) or meiosis (i.e., non-Mendelian segregation); selective processes that typically occur in one sex or the other.
-%Haploid selected loci typically experience a form of sex-specific selection because meiotic drive and/or gametic competition occurs predominantly in one sex or the other. 
-In addition, haploid selection can cause the zygotic sex ratio to become biased because sex ratios are determined by the production and fertilization success of X- versus Y-bearing pollen/sperm. 
-Notably, we find that the spread of new genetic sex determination systems is not affected by sex ratio biases that are caused by haploid selection. 
-A surprising result given that other determinants of sex allocation typically experience strong Fisherian sex ratio selection to equalize sex ratios. 
-In addition, we find that, with haploid selection, transitions between male and female heterogamety (XY to ZW or ZW to XY) can occur despite breaking up favourable associations that build up between the ancestral sex-determining locus and selected loci.
-These transitions occur because an unlinked neo-Y (neo-W) can have higher fitness in males (females), even if the population mean fitness is reduced. 
-Such transitions are not possible with diploid selection alone, in which case tighter linkage increases the fitness of both males and females. 
-Thus, our models offer several new insights to be explored as information about sex determination in non-model taxa accumulates.
+These studies generally conclude that that novel sex determination systems are favoured if they equalise the sex ratio or increase linkage between the sex-determining region and a sexually-antagonistic locus.
+We use population genetic models to extend these theories in two ways: 
+(1) We explicitly consider how selection on very tightly sex-linked loci influences the spread of novel sex-determiners. 
+We find that tightly sex-linked genetic variation can favour the spread of new sex-determination systems in which the heterogametic sex changes (XY to ZW or ZW to XY) and the new sex-determining region is less closely linked (or unlinked) to the sex linked locus under selection; a result that is not found with loose sex-linkage.
+%With tight linkage, selection can maintain equilibria at which the allele fixed on the sex-limited chromosome (Y or W) is simultaneously favoured in the homogametic sex (XX females or ZZ males) such that heterogametic transitions (XY to ZW or ZW to XY) are favoured by selection.
+%Alternatively, a neo-W (neo-Y) locus can invade when it allows greater specialism on alleles beneficial in females (male) compared to an ancestral XX female (ZZ male), 
+(2) We also consider selection upon haploid genotypes either during gametic competition (e.g., pollen/sperm competition) or meiosis (i.e., non-Mendelian segregation); selective processes that typically occur in one sex or the other.
+As well as having sex-specific fitness consequences, haploid selection can cause the zygotic sex ratio to become biased because sex ratios are determined by the production and fertilization success of X- versus Y-bearing pollen/sperm (or Z- versus W-bearing ovules/eggs).
+With relatively weak linkage, we find that transitions between male and female heterogamety (XY to ZW or ZW to XY) can again occur despite breaking up favourable associations that build up between the ancestral sex-determining locus and selected loci, which does not occur with diploid selection alone.
+In addition, when linkage between the ancestral sex-determining locus and a locus under haploid selection is tight, sex ratio biases can be strong such that there is an asymmetry between invasion of ancestrally XY and ancestrally ZW systems because, e.g., haploid selection in males only causes biased zygotic sex ratios in an ancestrally XY system.
+%Such transitions are not possible with diploid selection alone, in which case tighter linkage increases the fitness of both males and females. 
+%Notably, we find that the spread of new genetic sex determination systems is not affected by sex ratio biases that are caused by haploid selection. 
+%A surprising result given that other determinants of sex allocation typically experience strong Fisherian sex ratio selection to equalize sex ratios. 
+Overall, our models suggest the selective benefits of novel sex-determining systems may have been underestimated, especially when the heterogametic sex changes, and offer several new insights to be explored as information about sex determination in non-model taxa accumulates.
 \end{abstract}
@@
 %\citet{Bull:1977wt} shows that direct selection on new sex determination loci can allow them to spread and switch between male and female heterogamety. 
-\citet{vanDoorn:2007eu,vanDoorn:2010hu} show that new sex determination loci can be favoured if they arise in close linkage with a locus that experiences sexual antagonism. 
+\citet{vanDoorn:2007eu,vanDoorn:2010hu} show that new sex-determining loci can be favoured if they arise in closer linkage with a locus that experiences sexual antagonism. 
 For example, linkage allows favourable associations to build up between a male-beneficial allele and a neo-Y chromosome. 
 Such associations can favour a new master sex-determining gene on a new chromosome \citep{vanDoorn:2007eu} and can also favour a transition between male and female heterogamety \citep[e.g., a ZW to XY transition,][]{vanDoorn:2010hu}.
-However, any sexually-antagonistic loci that are linked to the ancestral sex-determination locus will develop similar, favourable associations and select against the spread of a new sex-determination system.
+However, any sexually-antagonistic loci that are more closely linked to the ancestral sex-determination locus will develop similar, favourable associations and select against the spread of a new sex-determination system.
+Here, we extend these studies by explictly calculating the the equilibrium allele frequencies of loci that are very tightly linked to the ancestral sex-determining region.
 
@@
 Gametic competition may be particularly common in plants, in which 60-70\% of all genes are expressed in the male gametophyte and these genes exhibit stronger signatures of selection than random genes \citep{Borg:2009jpa,Arunkumar:2013iq,Gossmann:2014dua}.
-In addition, artificial selection pressures applied to male gametophytes are known to cause a response to selection \citep[e.g.,][]{Hormaza:1996cv,Ravikumar:2003uo,Hedhly:2004iv,Clarke:2004ir}. 
+In addition, artificial selection pressures applied to male gametophytes are known to cause a response to selection \citep[e.g.,][]{Hormaza:1996cv,Ravikumar:2003uo,Hedhly:2004iv,Clarke:2004ir} and gametic selection appears to occur during the creation of F2 crosses \textcolor{red}{(Kumar, 2007)}.
 A much smaller proportion of genes are thought to be expressed and selected during competition in animal sperm, although precise estimates are uncertain \citep{Zheng:2001fi,JOSEPH:2004haa,Vibranovski:2010et,Immler:2014im}.

### 2017-03-03 LaTeX/Turnover.tex
added r=0 equilibria and stability conditions

@@
 %A surprising result given that other determinants of sex allocation typically experience strong Fisherian sex ratio selection to equalize sex ratios. 
-Overall, our models suggest the selective benefits of novel sex-determining systems may have been underestimated, especially when the heterogametic sex changes, and offer several new insights to be explored as information about sex determination in non-model taxa accumulates.
+Overall, our models add to the view that sex-determination is dynamic by indicating that various selective benefits of novel sex-determining systems may have been underestimated, especially when the heterogametic sex changes, and offer several new insights to be explored as information about sex determination in non-model taxa accumulates.
 \end{abstract}
@@
 \subsection*{Turnover between sex-determination systems}
+
 The evolution of a new sex determination system requires that a rare mutant allele, $m$, at the novel sex-determining locus  increases in frequency when rare. 
@@
 Similarly, the ancestral W allele fixes in males and females (blue and red lines) during a ZW to XY transition. 
-In this plot, there is no gametic competition ($t^\female=t^\male=0$) and meiotic drive occurs during male meiosis only ($\alpha^\female_{\Delta}=0$, $\alpha^\Hermaphrodite_{\Delta}=-1/5$).
+In this plot, there is no gametic competition ($t^\female=t^\male=0$) and meiotic drive occurs during male meiosis only ($\alpha^\female_{\Delta}=0$, $\alpha^\male_{\Delta}=-1/5$).
 Therefore, sex ratio biases can only arise when the \textbf{A} locus is linked to an XY sex-determining locus.
@@
 \end{split}
-\\
+\end{align}
 \label{eq:recursions}
-\end{align}
 \end{subequations}
@@
 \subsection*{Resident equilibrium and stability}
+
 In the resident population (allele $M$ fixed), we follow the frequency of $A$ in female gametes (eggs) from an XX female, $p^\female_X$, and in X-bearing, $p^\male_X$, and Y-bearing, $p^\male_Y$, male gametes (sperm).
 We also track the total frequency of Y among male gametes, $q$, which may deviate from $1/2$ due to meiotic drive in males. 
-Within this resident population (when $m$ is absent) we can then describe frequencies among different gamete types, which are given by $X_{MA}^{\female}=p_{Xf}$, $X_{Ma}^{\female}=(1-p_{Xf})$, $X_{MA}^{\male}=(1-q)p_{Xm}$, $X_{Ma}^{\male}=(1-q)(1-p_{Xm})$, $Y_{MA}^{\male}=q p_{Ym}$, and $Y_{Ma}^{\male}=q(1-p_{Ym})$.
+Within this resident population (when $m$ is absent) we can then describe frequencies among different gamete types, which are given by $X_{MA}^{\female}=p_{X}^{\female}$, $X_{Ma}^{\female}=(1-p_{X}^{\female})$, $X_{MA}^{\male}=(1-q)p_{X}^{\male}$, $X_{Ma}^{\male}=(1-q)(1-p_{X}^{\male})$, $Y_{MA}^{\male}=q p_{Y}^{\male}$, and $Y_{Ma}^{\male}=q(1-p_{Y}^{\male})$.
 Mean fitnesses in this resident population are given in table \ref{tab:meanfitnesses}.
+
+Various forms of selection can maintain a polymorphism at the \textbf{A} locus, including sexually antagonistic selection, overdominance and conflicts between diploid selection and selection upon haploid genotypes \citep[ploidally antagonistic selection,][]{Immler:2012tl} or a combination of these selective regimes.
 
@@
 
-Various forms of selection can maintain a polymorphism at the \textbf{A} locus, including sexually antagonistic selection, overdominance and conflicts between diploid selection and selection upon haploid genotypes \citep[ploidally antagonistic selection,][]{Immler:2012tl} or a combination of these selective regimes.
+\subsubsection*{Recombination weak relative to selection}
+
+We first calculate the equilibrium frequency of the Y and $A$ alleles in the ancestral population when the recombination rate between the \textbf{X} and \textbf{A} loci is small ($r$ of order $\epsilon$).
+The \textbf{A} locus will not affect evolution of novel sex-determination systems (\textbf{M} locus) if one \textbf{A} locus allele is fixed on all backgrounds.
+We therefore focus on the five equilibria that maintain both $A$ and $a$ alleles, of which four are given to leading order by:
+
+\begin{equation*}
+\begin{split}
+(A)\ \ \ &\hat{p}_{Y}^{\male}=0,
+\ \hat{q}=\frac{1}{2}-\frac{(\alpha^{\male}-1/2)w_{Aa}^{\male} \Phi}{w_{Aa}^{\male} \Phi+ w_{aa}^{\male} \Psi},\\
+&\hat{p}_{X}^{\female}=\frac{w_{a}^{\female} \Phi}{w_{a}^{\female} \Phi+ w_{A}^{\female} \Psi},
+\ \hat{p}_{X}^{\male}=\frac{2 \alpha^{\male}w_{Aa}^{\male} \Phi}{2\alpha^{\male}w_{Aa}^{\male} \Phi +w_{AA}^{\male} \Psi}\\
+(A')\ \ \ &\hat{p}_{Y}^{\male}=0,
+\ \hat{q}=\frac{1}{2}+\frac{(\alpha^{\male}-1/2)w_{Aa}^{\male} \Phi'}{w_{Aa}^{\male} \Phi' + w_{AA}^{\male} \Psi'},\\
+&\hat{p}_{X}^{\female}=1-\frac{w_{A}^{\female} \Phi'}{w_{A}^{\female} \Phi'+ w_{a}^{\female} \Psi'},
+\ \hat{p}_{X}^{\male}=1-\frac{2(1-\alpha^{\male})w_{Aa}^{\male} \Phi'}{2(1-\alpha^{\male})w_{Aa}^{\male} \Phi'+w_{aa}^{\male} \Psi'}\\
+(B)\ \ \ &\hat{p}_{Y}^{\male}=0,\ \hat{p}_{X}^{\female}=1,\ \hat{p}_{X}^{\male}=1, \ \hat{q}=(1-\alpha^{\male})\\
+(B')\ \ \ &\hat{p}_{Y}^{\male}=1,\ \hat{p}_{X}^{\female}=0,\ \hat{p}_{X}^{\male}=0, \ \hat{q}=\alpha^{\male}\\
+\end{split}
+\end{equation*}
+\begin{equation*}
+\begin{split}
+\Phi=&\alpha^{\female} w_{A}^{\female} w_{Aa}^{\female}(w_{a}^{\male} w_{aa}^{\male} + 2 \alpha^{\male} w_{A}^{\male} w_{Aa}^{\male}) - w_{a}^{\male} w_{a}^{\female} w_{aa}^{\male} w_{aa}^{\female} \\
+\Psi=&(1-\alpha^{\female}) w_{a}^{\female} w_{Aa}^{\female}(w_{a}^{\male} w_{aa}^{\male} + 2 \alpha^{\male} w_{A}^{\male} w_{Aa}^{\male}) - 2\alpha^{\male} w_{A}^{\male} w_{A}^{\female} w_{Aa}^{\male} w_{AA}^{\female}\\
+\Phi'=&(1-\alpha^{\female}) w_{a}^{\female} w_{Aa}^{\female}(w_{A}^{\male} w_{AA}^{\male} + 2 (1-\alpha^{\male}) w_{a}^{\male} w_{Aa}^{\male}) - w_{A}^{\male} w_{A}^{\female} w_{AA}^{\male} w_{AA}^{\female}\\
+\Psi'=&\alpha^{\female} w_{A}^{\female} w_{Aa}^{\female}(w_{A}^{\male} w_{AA}^{\male} + 2 (1-\alpha^{\male}) w_{a}^{\male} w_{Aa}^{\male}) - 2(1-\alpha^{\male}) w_{a}^{\male} w_{a}^{\female} w_{Aa}^{\male} w_{aa}^{\female}\\
+\end{split}
+\end{equation*}
+
+\noindent
+A fifth equilibrium $(C)$ also exists where $A$ is present at an intermediate frequency on the Y chromosome ($0<\hat{p}_{Y}^{\male}<1$).
+However, equilibrium $(C)$ is never locally stable when $r \approx 0$ and is therefore not considered further.
+Thus, the Y can either be fixed for the $a$ allele (equilibria $A$ and $B$) or the $A$ allele (equilibria $A'$ and $B'$).
+The X chromosome can then either be polymorphic (equilibria $A$ and $A'$) or fixed for the alternative allele (equilibria $B$ and $B'$).
+Since equilibria $(A)$ and $(B)$ are equivalent to equilibria $(A')$ and $(B')$ with the labelling of $A$ and $a$ alleles interchanged, we discuss only equilibria $(A)$ and $(B)$, in which the Y is fixed for the $a$ allele.
+If there is no haploid selection ($\alpha^{\Hermaphrodite}=1/2$, $w_{g}^{\Hermaphrodite}=1$), these equilibria are equivalent to those found by \textcolor{red}{Otto (2014) and Lloyd (197?, see Otto for reference)}.
+
+We next calculate when $(A)$ and $(B)$ are locally stable for $r=0$.
+According to the `small parameter theory' \citep{Karlin:1972ab,Karlin:1972dq}, these stability properties are unaffected by small amounts of recombination between the SDR and \textbf{A} locus, although equilibrium frequencies may be slightly altered.
+For the $a$ allele to be stably fixed on the Y requires that $\bar{w}_{Ya}^{\male}>\bar{w}_{YA}^{\male}$ where $\bar{w}_{Ya}^{\male}=w_{a}^{\male}(2 p_{X}^{\female}(1-\alpha^{\male}) w_{A}^{\female} w_{Aa}^{\male}+ (1-p_{X}^{\female})w_{a}^{\female} w_{aa}^{\male} )$ and $\bar{w}_{YA}^{\male}=w_{A}^{\male}(p_{X}^{\female} w_{A}^{\female} w_{AA}^{\male}+ 2 (1-p_{X}^{\female})\alpha^{\male}w_{a}^{\female} w_{aa}^{\male} )$.
+That is, $Ya$ haplotypes must have higher fitness than $YA$ haplotypes.
+Substituting $\hat{p}_{Xf}$ from above, fixation of the $A$ allele on the Y requires that $\gamma_{i}>0$ where $\gamma_{(A)}=w_{a}^{\male}(2(1-\alpha^{\male})w_{Aa}^{\male} \Phi + w_{aa}^{\male} \Psi)-w_{A}^{\male}(2\alpha^{\male}w_{Aa}^{\male} \Phi + w_{aa}^{\male} \Psi)$ for equilibrium $(A)$ and $\gamma_{(B)}=2(1-\alpha^{\male})w_{a}^{\male}w_{Aa}^{\male}-w_{A}^{\male}w_{AA}^{\male}$ for equilibrium $(B)$.
+Stability of a polymorphism on the X chromosome (equilibrium $A'$) further requires that $\Phi >0$ and $\Psi >0$. 
+Fixation of the $a$ allele on the X (equilibrium $B$) is mutually exclusive with $(A)$ and requires that $\Psi<0$ and $w_{A}^{\female}w_{AA}^{\female}>(1-\alpha^{\female})w_{a}^{\female}w_{Aa}^{\female}$.
+
+\subsubsection*{Selection weak relative to recombination}
+
 Here, we assume that selection and meiotic drive are weak relative to recombination ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon$). 
@@
 
-\subsection*{Invasion without assuming weak selection}
+\subsection*{Invasion conditions}
 
@@
 for the neo-$W$. 
-Equations \eqref{eq:neoYR} and \eqref{eq:neoWR} show that the new sex-determining allele, $m$, is expected to invade for any probability of recombination between loci \textbf{A} and \textbf{M}, $R$, when the net flow of recombinants is from the less fit (smaller $\lambda_{mi}$) to the more fit \textbf{A} background (making the terms inside the square brackets in Equations \ref{eq:neoYR} and \ref{eq:neoWR} negative).
+%Equations \eqref{eq:neoYR} and \eqref{eq:neoWR} show that the new sex-determining allele, $m$, is expected to invade for any probability of recombination between loci \textbf{A} and \textbf{M}, $R$, when the net flow of recombinants is from the less fit (smaller $\lambda_{mi}$) to the more fit \textbf{A} background (making the terms inside the square brackets in Equations \ref{eq:neoYR} and \ref{eq:neoWR} negative).
 %\textcolor{red}{Q: is it definitely possible to have negative square brackets for a equilibria maintained by selection?}
 %Assuming $g_A^* > 0$ and $g_a^* < 0$ without loss of generality, this is $-(1 - p^\female_X) w_{m,A} g_a^* < p^\female_X w_{m,a} g_A^*$.
-When the net flow of recombinants is from the more fit to the less fit haplotype, the new sex-determining allele can still invade when the rate of recombination between it and the selected locus is small enough.
+%When the net flow of recombinants is from the more fit to the less fit haplotype, the new sex-determining allele can still invade when the rate of recombination between it and the selected locus is small enough.
 %\textcolor{red}{Q:Is it the case that sometimes the square brackets are positive and invasion occurs for $r_{AM}=1/2$?

### 2017-05-18 LaTeX/Turnover.tex
initial modifications to abstract and intro to include r=0 results

@@
 Sex determination systems are remarkably dynamic; many studied taxa display transitions of sex-determining genes between chromosomes or the evolution of entirely new sex-determining systems. 
-Predominant theories in which new sex-determining systems are favoured by selection involve sex ratio selection or sex-specific selection (e.g., sexually antagonistic selection).
-These studies generally conclude that that novel sex determination systems are favoured if they equalise the sex ratio or increase linkage between the sex-determining region and a sexually-antagonistic locus.
+Predominant theories in which new sex-determining systems are favoured by selection 
+%involve sex ratio selection or sex-specific selection (e.g., sexually antagonistic selection).
+%These studies 
+generally conclude that that novel sex determination systems are favoured if they equalise the sex ratio or increase linkage between the sex-determining region and a sexually-antagonistic locus. 
 We use population genetic models to extend these theories in two ways: 
@@
 As well as having sex-specific fitness consequences, haploid selection can cause the zygotic sex ratio to become biased because sex ratios are determined by the production and fertilization success of X- versus Y-bearing pollen/sperm (or Z- versus W-bearing ovules/eggs).
-With relatively weak linkage, we find that transitions between male and female heterogamety (XY to ZW or ZW to XY) can again occur despite breaking up favourable associations that build up between the ancestral sex-determining locus and selected loci, which does not occur with diploid selection alone.
-In addition, when linkage between the ancestral sex-determining locus and a locus under haploid selection is tight, sex ratio biases can be strong such that there is an asymmetry between invasion of ancestrally XY and ancestrally ZW systems because, e.g., haploid selection in males only causes biased zygotic sex ratios in an ancestrally XY system.
+Consequently, selection for XY to ZW transitions and ZW to XY transitions can be assymetrical when linkage between the ancestral sex-determining locus and a locus under haploid selection is tight, in which case ancestral sex ratio biases can be strong.
+%In addition, when linkage between the ancestral sex-determining locus and a locus under haploid selection is tight, sex ratio biases can be strong such that there is an asymmetry between invasion of ancestrally XY and ancestrally ZW systems because, e.g., haploid selection in males only causes biased zygotic sex ratios in an ancestrally XY system.
+With looser linkage and haploid selection, we again find
+%In addition, when there is haploid selection, we find 
+that transitions between male and female heterogamety (XY to ZW or ZW to XY) can occur even if the new sex-determining region is less closely linked to the locus under selection. 
+That is, favourable associations that develop between the ancestral sex-determining locus and selected loci can be broken during the spread of a new sex-determining region. 
 %Such transitions are not possible with diploid selection alone, in which case tighter linkage increases the fitness of both males and females. 
@@
 %A surprising result given that other determinants of sex allocation typically experience strong Fisherian sex ratio selection to equalize sex ratios. 
-Overall, our models add to the view that sex-determination is dynamic by indicating that various selective benefits of novel sex-determining systems may have been underestimated, especially when the heterogametic sex changes, and offer several new insights to be explored as information about sex determination in non-model taxa accumulates.
+%Overall, we demonstrate when and how the evolution of sex determining systems is impacted by sex ratio biases resulting from haploid selection and we show that new sex-determining regions can be favoured even if they are not closely linked with a locus under selection.
+Overall, our models provide new predictions for the types of selection and the genomic location of loci that can drive transitions between sex-determination systems.
+%and for the factors determining the phylogenetic pattern of sex-determination systems.
 \end{abstract}
+
+abstract word count: $\approx$ 350
 
@@
 
-It has been suggested that sex ratio selection is a dominant force in the evolution of sex determination (e.g., \citealt{Bull:1983vi}, p66-67; \citealt{Beukeboom:2014vb}, Chapter 7). 
-The default mode of sex ratio selection is `Fisherian' sex ratio selection, which favours equal investment in male and female offspring \citep[i.e., a 1:1 zygotic sex ratio when assuming that males and females are equally costly to produce,][]{Fisher:1930wy,Charnov:1982wg}.
-Given that the sex determination system can directly affect the sex ratio, we might expect Fisherian sex ratio selection to influence the spread of new sex determination systems. 
-For example, \citet{Kozielska:2010vm} consider systems in which the ancestral sex chromosomes experience meiotic drive (e.g., where driving X or Y chromosomes are inherited disproportionately often), which causes sex ratios to become biased \citep{Hamilton:1967ts}.
+The sex ratio is directly affected by the sex determination system, it has therefore been suggested that sex ratio selection is a dominant force in the evolution of sex determination (e.g., \citealt{Bull:1983vi}, p66-67; \citealt{Beukeboom:2014vb}, Chapter 7).
+`Fisherian' sex ratio selection favours a 1:1 zygotic sex ratio when assuming that males and females are equally costly to produce \citep{Fisher:1930wy,Charnov:1982wg}.
+This follows from the fact that, for an autosomal locus, half of the genetic material is inherited from a male, and half from a female \citep{West:2009we}. 
+Thus, if the population sex ratio is biased towards females, the average per-individual contribution of genetic material to the next generation from males is greater than the contribution from females (and vice versa for male-biased sex ratios).
+Therefore, a mutant that increases investment in males (e.g., increases the proportion of males produced) will spread via the higher per-individual contributions made by males. 
+%The default mode of sex ratio selection is `Fisherian' sex ratio selection, which favours equal investment in male and female offspring \citep[i.e., a 1:1 zygotic sex ratio when assuming that males and females are equally costly to produce,][]{Fisher:1930wy,Charnov:1982wg}.
+%Given that the sex determination system can directly affect the sex ratio, we might expect Fisherian sex ratio selection to influence the spread of new sex determination systems. 
+In the case of sex-chromosome evolution, \citet{Kozielska:2010vm} consider systems in which the ancestral sex chromosomes experience meiotic drive (e.g., where driving X or Y chromosomes are inherited disproportionately often), which causes sex ratios to become biased \citep{Hamilton:1967ts}.
 They find that new, unlinked sex-determining loci (masculinizing or feminizing mutations, i.e., neo-Y or neo-W loci) can then spread, which restore an even sex ratio.
@@
 
-Surprisingly, our models show that haploid selection influences the evolution of new sex determination systems in a way that is distinct from both diploid sex-specific selection and Fisherian sex ratio selection.
-We find that the spread of new sex determination systems are independent of there being a zygotic sex ratio bias caused by associations between sex-determining regions and haploid selected loci. 
-In addition, we find that associations that build up between an ancestral sex-determining locus and a haploid-selected locus can favour sex chromosome transitions between male and female heterogamety (e.g., a neo-W allele arising at a previously autosomal locus spreads in an ancestrally XY system), despite the fact that these ancestral associations were built up by selection.
-Such transitions are not favoured in models lacking haploid selection.
+Our models tracking the spread of new sex determination systems therefore have two important new features. 
+Firstly, we consider loci that are under selection and also in very tight linkage with the ancestral sex-determining region. 
+Secondly, we allow sex-specific haploid selection to occur on a locus in tight or loose linkage with the ancestral sex-determining region. 
+We find that sex ratio biases caused by haploid selection can exert Fisherian sex ratio selection upon novel sex-determiners but that their spread is also determined by the fitness of the alleles that are associated with them.
+Indeed, it is only when haploid selected loci are tightly linked to the ancestral sex-determining region (and so sex ratio biases are initially large) that we see an asymmetry between selection for XY to ZW transitions and ZW to XY transitions, e.g., because haploid selection in males only causes biased zygotic sex ratios in an ancestrally XY system.
+%In addition, when linkage between the ancestral sex-determining locus and a locus under haploid selection is tight, sex ratio biases can be strong such that there is an asymmetry between invasion of ancestrally XY and ancestrally ZW systems because, e.g., haploid selection in males only causes biased zygotic sex ratios in an ancestrally XY system.
+In addition, we show that transitions between male and female heterogamety can evolve even when the neo-sex-determining locus is less closely linked to a locus under selection and therefore disrupts favourable ancestral associations between sex and the alleles selected in that sex.
+Such transitions are not favoured in models lacking tight linkage and/or haploid selection.
 
@@
 The only asymmetry between males and females in our model is that, under the ancestral sex determination system, males develop with genotype $XY$ (or $ZZ$) and females with genotype $XX$ (or $ZW$). 
-Therefore, without loss of generality, we primarily present results for an ancestral $XY$ sex determination system. 
-Ancestral $ZW$ sex determination can be considered by changing the notation such that $X$ becomes $Z$, $Y$ becomes $W$ and the labelling of male and female selection terms are reversed.
+Therefore, the model outlined above describes both ancestrally-$XY$ and ancestrally-$ZW$ sex determination systems if we relabel the two sexes as being ancestrally `heterogametic' or ancestrally `homogametic'.
+Without loss of generality, we primarily refer to the ancestrally heterogametic sex as male and the ancestrally homogametic sex as female.
+That is, we describe an ancestral XY sex determination system but our model can easily be applied to an ancestral ZW sex determination system.
 
@@
 
-\textcolor{red}{I have now put the q's in the lamdbas (i.e., removed them from $\bar{w}^{\male}$ and $\bar{w}^{\female}$).
-Let's wait until we have more results before deciding on a consistent system for $\bar{w}$.
-}
+\textcolor{red}{I now remove the zygotic sex ratio $\zeta$ from the mean fitnesses. The mean fitnesses will have to be adjusted in a corresponding way.}
+
+\textcolor{red}{CHECK: DO THE HAPLOID MEAN FITNESSES HAVE TO BE IN THE DENOMINATOR?}
 % as there are now two 2s in the lambdas of table 2. perhaps the 2 in the denominator is needed because the frequency of males sums to one as does the frequency of females?}
@@
    neo-Y ($k=0$) \\ [0.5ex] \hline \noalign{\vskip 1ex}
-  $\lambda_{mA}=\{p_{X}^{\female} w_{A}^{\female} w_{A}^{\male} w_{AA}^{\male} + 2(1-p_{X}^{\female}) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} \alpha^\male (1 - R)\}/ \{2q \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\male\} $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\lambda_{ma}=\{(1-p_{X}^{\female}) w_{a}^{\female} w_{a}^{\male} w_{aa}^{\male} + 2p_{X}^{\female} w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male}(1 - \alpha^\male) (1 - R)\}/ \{ 2q \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\male \}$ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\rho_{mA}=R (1-p_{X}^{\female}) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} \alpha^{\male}/ \{ q \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\male \} $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\rho_{ma}=R p_{X}^{\female} w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male} (1 - \alpha^{\male})/ \{ q \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\male \}$\\ [1ex] \hline 
+  $\lambda_{mA}=[1/(2(1- \zeta))]\{p_{X}^{\female} w_{A}^{\female} w_{A}^{\male} w_{AA}^{\male} + 2(1-p_{X}^{\female}) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} \alpha^\male (1 - R)\}/ \bar{w}^\male $\\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\lambda_{ma}=[1/(2(1- \zeta))]\{(1-p_{X}^{\female}) w_{a}^{\female} w_{a}^{\male} w_{aa}^{\male} + 2p_{X}^{\female} w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male}(1 - \alpha^\male) (1 - R)\}/ \bar{w}^\male $ \\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\rho_{mA}=R (1-p_{X}^{\female}) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} \alpha^{\male}/  (1-\zeta) \bar{w}^\male  $\\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\rho_{ma}=R p_{X}^{\female} w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male} (1 - \alpha^{\male})/ (1-\zeta) \bar{w}^\male $\\ [1ex] \hline 
   \noalign{\vskip 0.5ex}
   neo-W ($k=1$) \\ [0.5ex] \hline \noalign{\vskip 1ex}
-  $\lambda_{mA}=\{\bar{p}^{\male} w_{A}^{\male} w_{A}^{\female} w_{AA}^{\female}+2(1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female}\alpha^\female(1-R)\}/ \{ 2(1-q) \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\female \}$ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\lambda_{ma}=\{(1-\bar{p}^{\male}) w_{a}^{\male} w_{a}^{\female} w_{aa}^{\female}+2\bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female}(1-\alpha^\female)(1-R)\}/ \{2(1-q) \bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\female \}$ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\rho_{mA}=R (1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female} \alpha^{\female}/ \{(1-q)\bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\female \} $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\rho_{ma}=R\bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female} (1-\alpha^{\female})/ \{(1-q)\bar{w}_{H}^{\female} \bar{w}_{H}^{\male} \bar{w}^\female \}$\\ [1ex] 
+  $\lambda_{mA}=[1/(2 \zeta)]\{\bar{p}^{\male} w_{A}^{\male} w_{A}^{\female} w_{AA}^{\female}+2(1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female}\alpha^\female(1-R)\}/ \bar{w}^\female $ \\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\lambda_{ma}=[1/(2 \zeta)]\{(1-\bar{p}^{\male}) w_{a}^{\male} w_{a}^{\female} w_{aa}^{\female}+2\bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female}(1-\alpha^\female)(1-R)\}/ \bar{w}^\female $ \\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\rho_{mA}=R (1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female} \alpha^{\female}/ \zeta \bar{w}^\female  $\\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\rho_{ma}=R\bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female} (1-\alpha^{\female})/ \zeta \bar{w}^\female $\\ [1ex] 
   \hline \hline 
@@
       \item $R$ is the probability of recombination between loci \textbf{A} and \textbf{M}.
-      \item See Table \ref{tab:meanfitnesses} for expressions of mean fitnesses.
+      \item $\zeta$ is the zygotic sex ratio and $\bar{w}^\Hermaphrodite$ is the mean fitness of sex $\Hermaphrodite$, see Table \ref{tab:meanfitnesses}.
 %      \item $\bar{w}_H^\female = p_X^\female w_A^\female + (1-p_X^\female) w_a^\female$ is the mean fitness of female gametes during gametic competition
@@
 
+%%% ADD ZYGOTIC SEX RATIO HERE
+
+We are particularly concerned with the conditions under which a rare neo-sex-determining allele increases in frequency, which occurs when the largest eigenvalue, $\lambda$, is greater than one. 
+If the average change in frequency of the two haplotypes that carry the $m$ allele ($Am$ and $am$) is positive, invasion will always occur (i.e., if $\left\{(\lambda_{mA}-1)+ (\lambda_{ma}-1) \right\}/2 > 0$ then $\lambda > 1$).
+If neither haplotype increases in frequency ($\lambda_{mA}, \lambda_{ma} < 1$), the $m$ allele will not invade. 
+Otherwise, the new sex-determining allele increases in frequency on one \textbf{A} background and declines on the other and invasion depends on the recombination rate between the \textbf{M} and \textbf{A} loci ($R$) see equations \eqref{eq:neoYR} and \eqref{eq:neoWR}.
+
 Table \ref{tab:haplotype_growth} illustrates a number of key points about the invasion of neo-Y and neo-W mutations. 
-For a neo-Y, invasion is driven by the fitness of male gametes and diploids, where the latter is weighted by the chance that a female egg will give rise to that diploid. 
-For example, matings with $A$-bearing female gametes occur with probability $p_{X}^{\female} w_{A}^{\female}/\bar{w}_{H}^{\female}$. 
-Since a neo-Y is always found in males, the allele frequencies at the neo-Y (\textbf{M}) locus only change in males. 
+Firstly, Fisherian sex ratio selection will favour the spread of a neo-Y if the ancestral zygotic sex ratio is biased towards males, $\zeta>1/2$, and vice versa for a neo-W, see terms in square brackets.
+However, the spread of a neo-Y (neo-W) also depends on the male (female) fitness of alleles that they are associated with, see terms in curly brackets. 
+Secondly, since a dominant neo-Y is always found in males, the allele frequencies at the neo-Y (\textbf{M}) locus only change in males. 
 Therefore, invasion by a neo-Y allele does not involve any female diploid selection terms ($w_{g}^{\female}$). 
 Similarly, invasion by a neo-W is driven by the fitness of female gametes and diploids and does not involve any direct selection in male diploids.
-However, in the case of a neo-W, female diploids can result from matings with either an X-bearing or a Y-bearing sperm. 
-In either case, the zygote will develop as a female due to the presence of a neo-W. 
-For example, neo-W females will inherit an $A$ allele from a male gamete with probability $\bar{p}^{\male} w_{A}^{\male}/\bar{w}_{H}^{\male}$, where $\bar{p}^{\male}=p_{Y}^{\male}q+p_{X}^{\male}(1-q)$ is the frequency of the A allele among both X- and Y-bearing male gametes.
-By contrast, females that do not carry the neo-W only result from matings with X-bearing sperm. 
-They will therefore inherit an $A$ from a male gamete with probability $(1-q)\bar{p}_{X}^{\male} w_{A}^{\male}/\bar{w}_{H}^{\male}$. 
-If the \textbf{A} locus is initially linked to the ancestral sex-determining locus, \textbf{X}, the frequency of the $A$ allele among X- and Y-bearing sperm can differ (equation \ref{eq:freq_diffs}). 
-Thus, eggs with and without a neo-W differ in the frequency of $A$ alleles they obtain from mating with male gametes.
+
+Finally, the diploid fitness terms in Table \ref{tab:haplotype_growth} are weighted by the probability of producing those genotypes through matings with gametes of the opposite sex. 
+For example, matings between a neo-Y-bearing male gamete and an $A$-bearing female gamete occur with probability $p_{X}^{\female} w_{A}^{\female}/\bar{w}_{H}^{\female}$. 
+%This is the same probability that an ancestral-Y-bearing male gamete will inherit an $A$ allele via mating with a female gamete. 
+%On the other hand, 
+The probability that a neo-W bearing female gamete mates with an $A$-bearing male gamete is $\bar{p}^{\male} w_{A}^{\male}/\bar{w}_{H}^{\male}$, where $\bar{p}^{\male}=p_{Y}^{\male}q+p_{X}^{\male}(1-q)$ is the frequency of the A allele among both X- and Y-bearing male gametes.
+That is, in the case of a neo-W, female diploids can result from matings with either an X-bearing or a Y-bearing sperm, resulting in zygotes that will develop as females. 
+However, females that do not carry the neo-W only result from matings with X-bearing sperm. 
+Therefore, eggs with and without a neo-W can differ in the frequency of $A$ alleles they obtain from matings with male gametes. 
+Invasions by a neo-Y and a neo-W differ in this respect because sperm with or without a neo-Y allele both mate with X-bearing female gametes only.
+
+% invasion is driven by the fitness of male gametes and diploids, where the latter is weighted by the chance that a female egg will give rise to that diploid. 
+%For example, matings with $A$-bearing female gametes occur with probability $p_{X}^{\female} w_{A}^{\female}/\bar{w}_{H}^{\female}$. 
+%Since a neo-Y is always found in males, the allele frequencies at the neo-Y (\textbf{M}) locus only change in males. 
+%Therefore, invasion by a neo-Y allele does not involve any female diploid selection terms ($w_{g}^{\female}$). 
+%Similarly, invasion by a neo-W is driven by the fitness of female gametes and diploids and does not involve any direct selection in male diploids.
+%However, in the case of a neo-W, female diploids can result from matings with either an X-bearing or a Y-bearing sperm. 
+%In either case, the zygote will develop as a female due to the presence of a neo-W. 
+%For example, neo-W females will inherit an $A$ allele from a male gamete with probability $\bar{p}^{\male} w_{A}^{\male}/\bar{w}_{H}^{\male}$, where $\bar{p}^{\male}=p_{Y}^{\male}q+p_{X}^{\male}(1-q)$ is the frequency of the A allele among both X- and Y-bearing male gametes.
+%By contrast, females that do not carry the neo-W only result from matings with X-bearing sperm. 
+%They will therefore inherit an $A$ from a male gamete with probability $(1-q)\bar{p}_{X}^{\male} w_{A}^{\male}/\bar{w}_{H}^{\male}$. 
+%If the \textbf{A} locus is initially linked to the ancestral sex-determining locus, \textbf{X}, the frequency of the $A$ allele among X- and Y-bearing sperm can differ (equation \ref{eq:freq_diffs}).
+%Thus, eggs with and without a neo-W differ in the frequency of $A$ alleles they obtain from mating with male gametes.
+
+%%% ADD r=0 HERE
+
+In order to explicitly determine the conditions under which a rare neo-sex-determining allele spreads, we must calculate the frequency of the $A$ allele in the ancestral population (i.e., $p^\female_X$, $p^\male_X$, and $p^\male_Y$).
+We assume that the $A$ allele reaches a stable equilibrium frequency under the ancestral sex-determination system before the neo-sex-determining allele ($m$) arises. 
+We can analytically calculate the allele frequency of the $A$ allele using two alternative simplifying assumptions: 
+(1) assuming that the \textbf{A} locus is within the non-recombining region around the ancestral SDR (or within tight linkage, $r \approx 0$) or (2) assuming that selection is weak relative to recombination ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon$).
+%These equilibrium allele frequencies and their stability conditions are given in the appendix. 
+%Considering diploid selection only, \citet{vanDoorn:2007eu,vanDoorn:2010hu} analytically calculated these allele frequencies assuming weak selection and relatively loose linkage (assumption 2 above).
+%We first consider the spread of neo-sex determining loci when the ancestral sex-determining locus is tightly linked to the selected \textbf{A} locus (assumption 1) with or without haploid selection. 
+%We then use the weak selection approximation that was also used in \citet{vanDoorn:2007eu,vanDoorn:2010hu} except that we allow haploid selection on the \textbf{A} locus.
+
+When there is tight linkage between the ancestral sex-determining region and the \textbf{A} locus ($r=0$), either the $A$ allele or the $a$ allele must be fixed on the Y. 
+% because selection on the Y is effectively haploid an incapably of maintaining a polymorphism in the absence of frequency dependent selection. 
+Because the labelling of alleles is arbitrary, we will assume that the $a$ locus is fixed on the Y without loss of generality ($p^\male_Y=0$). 
+If there are two alleles maintained at the \textbf{A} locus, the X can either be fixed for the $A$ allele ($p^\female_X=p^\male_X=1$) or polymorphic (0<$p^\female_X, p^\male_X$<1).
+These equilibrium allele frequencies and their stability conditions are given in the appendix.
+%However, because the X is present in both males and females, there are distinct selection pressures on X's in females and X's in males, which will always be paired with an $A$ allele from the Y.
+
+A neo-Y will never invade an ancestral XY system that already has tight linkage with the locus under selection ($r=0$). 
+When then neo-Y is also tightly linked ($R=0$) a neo-Y will either remain linked to the $A$ allele or to the $a$ allele and so invasion is given directly by the larger of $\lambda_{mA}$ or $\lambda_{ma}$ (evaluated with $R=0$).
+A neo-Y can either be linked to the same allele as the ancestral Y, in which case it is a neutral mutation with no effect ($\lambda_{ma}=1$), or be linked to the alternative \textbf{A} allele, in which case it will not spread given that the initial equilibrium is stable ($\lambda_{mA}<1$).
+Given that $\lambda_{mA}$ and $\lambda_{ma}$ both decrease with increasing $R$, more loosely linked neo-Y alleles also do not spread ($\lambda <1$ when $R>0$).
+
+However, under some conditions, a neo-W can invade an ancestral XY system. 
+When the neo-W is also tightly linked ($R=0$), it can spread in linkage with either the allele that is fixed on the Y or the allele that is more common on the X, i.e., under some conditions $\lambda_{ma}>1$ and/or $\lambda_{mA}>1$.
+These conditions are given in more detail in the appendix.
 
 %weak selection
-We are particularly concerned with whether or not a rare neo-sex-determining allele increases in frequency, which occurs when the largest eigenvalue, $\lambda$, is greater than one. 
-In the Appendix, we derive these conditions without assuming that selection is weak relative to recombination. 
-Here, we explicitly determine the conditions under which invasion occurs by assuming that the $A$ allele reaches an equilibrium frequency under the ancestral sex-determination system before the neo-sex-determination system ($m$) arises.
-The equilibrium  frequency of $A$ on different ancestral backgrounds ($\hat{p}^\male_Y$, $\hat{p}^\male_X$, and $\hat{p}^\female_X$) is given by equations \eqref{eq:pAve} and \eqref{eq:freq_diffs} where we assume selection and meiotic drive are weak relative to recombination ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon$).
+%We are particularly concerned with whether or not a rare neo-sex-determining allele increases in frequency, which occurs when the largest eigenvalue, $\lambda$, is greater than one. 
+%Here, we explicitly determine the conditions under which invasion occurs by assuming that the $A$ allele reaches an equilibrium frequency under the ancestral sex-determination system before the neo-sex-determination system ($m$) arises.
+%The equilibrium frequency of $A$ on different ancestral backgrounds ($\hat{p}^\male_Y$, $\hat{p}^\male_X$, and $\hat{p}^\female_X$) is given by equations \eqref{eq:pAve} and \eqref{eq:freq_diffs} where we assume selection and meiotic drive are weak relative to recombination ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon$).
 Under weak selection, we denote the leading eigenvalues describing the invasion of a neo-Y ($k=0$) and a neo-W ($k=1$) into an ancestrally XY system by $\lambda_{Y',XY}$ and $\lambda_{W',XY}$, respectively, which are given by
@@
 Substituting $\hat{p}_{Xf}$ from above, fixation of the $A$ allele on the Y requires that $\gamma_{i}>0$ where $\gamma_{(A)}=w_{a}^{\male}(2(1-\alpha^{\male})w_{Aa}^{\male} \Phi + w_{aa}^{\male} \Psi)-w_{A}^{\male}(2\alpha^{\male}w_{Aa}^{\male} \Phi + w_{aa}^{\male} \Psi)$ for equilibrium $(A)$ and $\gamma_{(B)}=2(1-\alpha^{\male})w_{a}^{\male}w_{Aa}^{\male}-w_{A}^{\male}w_{AA}^{\male}$ for equilibrium $(B)$.
-Stability of a polymorphism on the X chromosome (equilibrium $A'$) further requires that $\Phi >0$ and $\Psi >0$. 
+Stability of a polymorphism on the X chromosome (equilibrium $A$) further requires that $\Phi >0$ and $\Psi >0$. 
 Fixation of the $a$ allele on the X (equilibrium $B$) is mutually exclusive with $(A)$ and requires that $\Psi<0$ and $w_{A}^{\female}w_{AA}^{\female}>(1-\alpha^{\female})w_{a}^{\female}w_{Aa}^{\female}$.

### 2017-05-18 LaTeX/Turnover.tex
update
small edits to text while reading

--- 2017-03-03 LaTeX/Turnover.tex
@@
 \title{Gametic Selection, Meiotic Drive, Sex Ratio Bias, and Transitions Between Sex Determination Systems}
-\author{Michael F Scott$*^1$ and Matthew M Osmond$*^2$, and Sarah P Otto$^2$}
+\author{Michael F Scott$*^1$, Matthew M Osmond$*^2$, and Sarah P Otto$^2$}
 \date{}
@@
 Predominant theories in which new sex-determining systems are favoured by selection involve sex ratio selection or sex-specific selection (e.g., sexually antagonistic selection).
-These studies generally conclude that that novel sex determination systems are favoured if they equalise the sex ratio or increase linkage between the sex-determining region and a sexually-antagonistic locus.
+These studies generally conclude that novel sex determination systems are favoured if they equalise the sex ratio or increase linkage between the sex-determining region and a sexually-antagonistic locus.
 We use population genetic models to extend these theories in two ways: 
@@
 I wonder if this is actually a fusion event though?
-In addition, many gonochoric clades with genetic sex determination exhibit transitions between male (XY) and female (ZW) heterogamety, including lizards \citep{Ezaz:2009tk}, eight of 26 teleost fish families \citep{Mank:2006bt}, true fruit flies \citep[Tephritids,][]{Vicoso:2015hf}, amphibians \citep{Hillis:1990gu}, the angiosperm genus \textit{Silene} \citep{Slancarova:2013dq}, Coleoptera and Hemiptera \citep[][plate 2]{Beukeboom:2014vb}.
+In addition, many gonochoric clades with genetic sex determination exhibit transitions between male (XY) and female (ZW) heterogamety, including lizards \citep{Ezaz:2009tk}, eight of 26 teleost fish families \citep{Mank:2006bt}, true fruit flies \citep[Tephritids,][]{Vicoso:2015hf}, amphibians \citep{Hillis:1990gu}, the angiosperm genus \textit{Silene} \citep{Slancarova:2013dq}, and Coleoptera and Hemiptera \citep[][plate 2]{Beukeboom:2014vb}.
 Indeed, in some cases, both male and female heterogametic sex determination systems can be found in the same species, as exhibited by some cichlid species \citep{Ser:2010iq} and \textit{Rana rugosa} \citep{Ogata:2007jm}.
@@
 However, any sexually-antagonistic loci that are more closely linked to the ancestral sex-determination locus will develop similar, favourable associations and select against the spread of a new sex-determination system.
-Here, we extend these studies by explictly calculating the the equilibrium allele frequencies of loci that are very tightly linked to the ancestral sex-determining region.
+Here we extend these studies by explictly calculating the the equilibrium allele frequencies of loci that are very tightly linked to the ancestral sex-determining region.
 
@@
 There are various ways in which a period of haploid selection could influence transitions between sex determination systems. 
-Firstly, if we assume that haploid selection at any particular locus predominantly occurs in one sex (e.g., meiotic drive during spermatogenesis), then such loci experience a form of sex-specific selection.
+If we assume that haploid selection at any particular locus predominantly occurs in one sex (e.g., meiotic drive during spermatogenesis), then such loci experience a form of sex-specific selection. 
 In this respect, we might expect that haploid selection would affect transitions between sex determination systems in a similar manner to sex-specific diploid selection \citep[as explored by][]{vanDoorn:2007eu,vanDoorn:2010hu}.
@@
 However, sex ratios can also become biased by linkage between the sex-determining region and a locus that harbours genetic variation in haploid fitness. 
-For example, there are several known cases of sex ratio bias caused by sex-linked meiotic drive alleles \citep[][, Chapter 3]{Burt:2006} or selection among X- and Y-bearing pollen \citep{Lloyd:1974tz,Conn:1981uw,Stehlik:2005ul,Stehlik:2006to,Field:2012fd,Field:2013cc}.
+For example, there are several known cases of sex ratio bias caused by sex-linked meiotic drive alleles \citep[][Chapter 3]{Burt:2006} or selection among X- and Y-bearing pollen \citep{Lloyd:1974tz,Conn:1981uw,Stehlik:2005ul,Stehlik:2006to,Field:2012fd,Field:2013cc}.
 It is not immediately clear how the spread of new sex determination systems would be influenced by the combination of sex ratio biases and associations between haploid selected loci and sex-determining regions.
@@
 %genetic system
-We consider the transition between an ancestral and novel sex determination systems using a three locus model. 
+We consider the transition between ancestral and novel sex determination systems using a three locus model. 
 Locus \textbf{X} is the ancestral sex-determining region, with alleles $X$ and $Y$ (or $Z$ and $W$).
@@
 With $k=0$, the $m$ allele is a masculinizer (i.e., a neo-Y) and with $k=1$ the $m$ allele is a feminizer (i.e., a neo-W).
-With intermediate $k$, the $m$ allele confers environmental sex determination (ESD) such that zygotes develop as females in a proportion ($k$) of the environments they experience. 
+With intermediate $k$, the $m$ allele confers environmental sex determination (ESD) such that zygotes develop as females in a proportion ($k$) of the environments they (randomly) experience. 
 Finally, we also analyze a model of maternally-controlled environmental sex-determination, where mothers with at least one $m$ allele produce daughters with probability $k$.
@@
 The resulting zygotes develop as males or females, depending on their genotypes at the \textbf{X} and \textbf{M} loci (and the \textbf{M} genotype of their mother in the case of maternal control) as described above.
-Diploid males and females then experience selection, relative fitnesses are given by $w_{g}^{\male}$ in males and $w_{g}^{\female}$ in females, where $g$ is the diploid genotype at the \textbf{A} locus ($g \in \{AA, Aa, aa\}$).
+Diploid males and females then experience selection, relative fitnesses are given by $w_{g}^{\Hermaphrodite}$, where $g$ is the diploid genotype at the \textbf{A} locus ($g \in \{AA, Aa, aa\}$).  
 %Diploids compete with others of the same sex, where selection depends on the sex of the individual and its genotype at the \textbf{A} locus.
@@
 Recombination (i.e., an odd number of cross-overs) occurs between loci \textbf{X} and \textbf{A} with probability $r$, between loci \textbf{A} and \textbf{M} with probability $R$, and between loci \textbf{X} and \textbf{M} with probability $\chi$.
-Therefore, any order of the loci can be modelled with appropriate choices of $r$, $R$, and $\chi$ (see Table \ref{tab:chisubstitutions}). 
-Males/females that are heterozygous at the \textbf{A} locus may experience meiotic drive; $Aa$ heterozgotes of sex $\Hermaphrodite$ produce gametes bearing allele $A$ with probability $\alpha^\Hermaphrodite$.
-Thus, the \textbf{A} locus can experience sex-specific gametic competition, diploid selection and/or meiotic drive.
+Any linear order of the loci can be modelled with appropriate choices of $r$, $R$, and $\chi$ (see Table \ref{tab:chisubstitutions}). 
+Individuals that are heterozygous at the \textbf{A} locus may experience meiotic drive; $Aa$ heterozgotes of sex $\Hermaphrodite$ produce gametes bearing allele $A$ with probability $\alpha^\Hermaphrodite$.
+Thus, the \textbf{A} locus can experience sex-specific gametic competition, diploid selection, and/or meiotic drive.
 
@@
   A & $\alpha^\Hermaphrodite=1/2+\alpha_{\Delta}^{\Hermaphrodite}/2$ \\
-  a & $(1-\alpha^\Hermaphrodite)=1/2-\alpha_{\Delta}^{\Hermaphrodite}/2$ \\
+  a & $1-\alpha^\Hermaphrodite=1/2-\alpha_{\Delta}^{\Hermaphrodite}/2$ \\
   \hline \hline
@@
 Therefore, without loss of generality, we primarily present results for an ancestral $XY$ sex determination system. 
-Ancestral $ZW$ sex determination can be considered by changing the notation such that $X$ becomes $Z$, $Y$ becomes $W$ and the labelling of male and female selection terms are reversed.
+Ancestral $ZW$ sex determination can be considered by changing the notation such that $X$ becomes $Z$, $Y$ becomes $W$, and the labelling of male and female selection terms are reversed.
 
@@
 The evolution of a new sex determination system requires that a rare mutant allele, $m$, at the novel sex-determining locus  increases in frequency when rare. 
-The spread of a rare mutant $m$ at the \textbf{M} locus is determined by the leading eigenvalue, $\lambda$, of the system of eight equations describing the next generation frequency of eggs and sperm carrying the mutation, (\ref{eq:recursions}c), (\ref{eq:recursions}d), (\ref{eq:recursions}g), (\ref{eq:recursions}h).
+The spread of a rare mutant $m$ at the \textbf{M} locus is determined by the leading eigenvalue, $\lambda$, of the system of eight equations describing the next generation frequency of eggs and sperm carrying the mutation, (\ref{eq:recursions}c, \ref{eq:recursions}d, \ref{eq:recursions}g, \ref{eq:recursions}h).
 %, evaluated at the above equilibrium.
@@
 Dominant neo-Y (when $k=0$) or neo-W alleles (when $k=1$) are only found in male diploids (neo-Y) or female diploids (neo-W) such that their growth rate ultimately depends only on the change in frequency of $m$-bearing gametes produced by males (for a neo-Y) or by females (for a neo-W).
-Furthermore, if the $m$ allele is fully dominant over the ancestral sex-determining system, phenotypes are not affected by the genotype at the ancestral sex-determining region (\textbf{X} locus). 
+Furthermore, if the $m$ allele is fully epistatically dominant over the ancestral sex-determining system, phenotypes are not affected by the genotype at the ancestral sex-determining region (\textbf{X} locus).
 Thus, the invasion of rare dominant neo-Y or neo-W alleles is determined by the largest eigenvalue that solves the quadratic characteristic polynomial
@@
 %where $b$ is the average of the growth rates of the two haplotypes that carry the $m$ allele ($mA$ and $ma$), $b=(\lambda_{mA}+\lambda_{ma})/2$, and $c$ also involves the fitness of $m$ alleles when they recombine onto the other \textbf{A} background in a heterozygote, $c=\lambda_{mA}\lambda_{ma}+\rho_{mA}\rho_{ma}$ (see table \ref{tab:haplotype_growth}).
-In this case $b= - (\lambda_{mA} + \lambda_{ma})$ and $c = \lambda_{mA} \lambda_{ma} -\rho_{mA} \rho_{ma}$, where $\lambda_{mi}$ is the (discrete time) growth rate of mutant haplotypes on background $i\in\{A,a\}$, accounting for loss due to recombination, and $\rho_{mi}$ is the rate of addition of mutant haplotypes onto background $i\in\{A,a\}$ due to recombination, see table \ref{tab:haplotype_growth}.
-The spread of the mutant $m$ allele depends on the frequency of alleles at the other loci in the ancestral population. 
+In this case $b= - (\lambda_{mA} + \lambda_{ma})$ and $c = \lambda_{mA} \lambda_{ma} -\rho_{mA} \rho_{ma}$, where $\lambda_{mi}$ is the (multiplicative) growth rate of mutant haplotypes on background $i\in\{A,a\}$, accounting for loss due to recombination, and $\rho_{mi}$ is the rate of addition of mutant haplotypes onto background $i\in\{A,a\}$ due to recombination (see table \ref{tab:haplotype_growth}).
+The spread of the mutant $m$ allele depends on the frequency of alleles at the other two loci in the ancestral population. 
 In the ancestral population, it is convenient to follow the frequency of the $A$ allele in female gametes (eggs) from an XX female, $p^\female_X$, and in X-bearing, $p^\male_X$, and Y-bearing, $p^\male_Y$, male gametes (sperm).
@@
 
-\textcolor{red}{I have now put the q's in the lamdbas (i.e., removed them from $\bar{w}^{\male}$ and $\bar{w}^{\female}$).
+%\textcolor{red}{I have now put the q's in the lamdbas (i.e., removed them from $\bar{w}^{\male}$ and $\bar{w}^{\female}$).
 Let's wait until we have more results before deciding on a consistent system for $\bar{w}$.
@@
       \item $R$ is the probability of recombination between loci \textbf{A} and \textbf{M}.
-      \item See Table \ref{tab:meanfitnesses} for expressions of mean fitnesses.
+      \item See Table \ref{tab:meanfitnesses} for expressions of mean haploid, $\bar{w}_{H}^{\Hermaphrodite}$, and diploid, $\bar{w}^\Hermaphrodite$, fitnesses.
 %      \item $\bar{w}_H^\female = p_X^\female w_A^\female + (1-p_X^\female) w_a^\female$ is the mean fitness of female gametes during gametic competition
@@
 Table \ref{tab:haplotype_growth} illustrates a number of key points about the invasion of neo-Y and neo-W mutations. 
-For a neo-Y, invasion is driven by the fitness of male gametes and diploids, where the latter is weighted by the chance that a female egg will give rise to that diploid. 
+For a neo-Y, invasion is driven by the fitness of male gametes and diploids, where the latter is weighted by the chance that diploid arises, which depends on the frequency of $A$ in eggs. 
 For example, matings with $A$-bearing female gametes occur with probability $p_{X}^{\female} w_{A}^{\female}/\bar{w}_{H}^{\female}$. 
@@
 Here, we explicitly determine the conditions under which invasion occurs by assuming that the $A$ allele reaches an equilibrium frequency under the ancestral sex-determination system before the neo-sex-determination system ($m$) arises.
-The equilibrium  frequency of $A$ on different ancestral backgrounds ($\hat{p}^\male_Y$, $\hat{p}^\male_X$, and $\hat{p}^\female_X$) is given by equations \eqref{eq:pAve} and \eqref{eq:freq_diffs} where we assume selection and meiotic drive are weak relative to recombination ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon$).
+The equilibrium  frequency of $A$ on different ancestral backgrounds ($\hat{p}^\male_Y$, $\hat{p}^\male_X$, and $\hat{p}^\female_X$) is given by equations \eqref{eq:pAve} and \eqref{eq:freq_diffs} where we assume selection and meiotic drive are weak relative to recombination ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon$; table \ref{tab:fitnesstable}).
 Under weak selection, we denote the leading eigenvalues describing the invasion of a neo-Y ($k=0$) and a neo-W ($k=1$) into an ancestrally XY system by $\lambda_{Y',XY}$ and $\lambda_{W',XY}$, respectively, which are given by
@@
 where $V_{A}=\bar{p}(1-\bar{p})$ is the variance in the frequency of $A$ and $S_{A}=(D^\male +\alpha_{\Delta}^\male+t^\male) - (D^\female+\alpha_{\Delta}^\female+t^\female)$ is the difference in fitness in males versus females for the $A$ allele against the $a$ allele across diploid selection, gametic competition, and meiosis.
-$D^\Hermaphrodite=\big{(} \bar{p}s^\Hermaphrodite+(1-\bar{p})h^\Hermaphrodite s^\Hermaphrodite\big{)} -\big{(} \bar{p}h^\Hermaphrodite s^\Hermaphrodite+(1-\bar{p}) \big{)}$ is the difference in fitness between $A$ and $a$ alleles in diploids of sex $\Hermaphrodite \in \{\female,\male\}$; $\bar{p}$ is the leading-order probability of mating with an $A$-bearing gamete from the opposite sex, see appendix.
+$D^\Hermaphrodite=\big{(} \bar{p}s^\Hermaphrodite+(1-\bar{p})h^\Hermaphrodite s^\Hermaphrodite\big{)} -\big{(} \bar{p}h^\Hermaphrodite s^\Hermaphrodite+(1-\bar{p}) \big{)}$ is the difference in fitness between $A$ and $a$ alleles in diploids of sex $\Hermaphrodite \in \{\female,\male\}$; $\bar{p}$ is the leading-order probability of mating with an $A$-bearing gamete from the opposite sex (see Appendix).
 
@@
 
-Equation \eqref{eq:lambda_neoW} shows that if there is no selection upon haploid genotypes ($t^\Hermaphrodite=\alpha^\Hermaphrodite_{\Delta}=0$), as considered by \citet{vanDoorn:2010hu}, the spread of a neo-W is equivalent to the spread of a neo-Y ($\lambda_{W',XY}=\lambda_{Y',XY}$) such that heterogametic transitions (XY to ZW or ZW to XY) can also occur only if the neo-sex-determining region is more closely linked to a locus under selection ($R<r$).
+Equation \eqref{eq:lambda_neoW} shows that if there is no haploid selection ($t^\Hermaphrodite=\alpha^\Hermaphrodite_{\Delta}=0$), as considered by \citet{vanDoorn:2010hu}, the spread of a neo-W is equivalent to the spread of a neo-Y ($\lambda_{W',XY}=\lambda_{Y',XY}$) such that heterogametic transitions (XY to ZW or ZW to XY) can also occur only if the neo-sex-determining region is more closely linked to a locus under selection ($R<r$).
 However, if there is any haploid selection, the additional term in equation \eqref{eq:lambda_neoW} can be positive, which can allow, for example, neo-W invasion ($\lambda_{W',XY}>1$) even when the neo-sex-determining region is less closely linked to the selected locus ($R>r$).
@@
 Indeed, invasion typically occurs when the neo-W is more closely linked to the selected locus than the ancestral sex-determining region (Figure \ref{fig:Combination_Centimorgans}).
-Secondly, we can simplify cases where invasion occurs despite $R>r$ using the special case where $R=1/2$ and $r<1/2$. 
-In table \ref{tab:specialcases} we give the conditions where invasion occurs where we further assume that haploid selection only occurs in one sex (e.g., during male meiosis only) and dominance coefficients are equal in the two sexes, $h^\female=h^\male$.
-Where there is no gametic competition and meiotic drive in one sex only, an unlinked neo-W can invade as long as the same allele is favoured during diploid selection in males and females ($s^\female s^\male>0$, see Figure \ref{fig:Combination_Centimorgans}B).%, which is 50\% of the parameter space.
-Where there is no meiotic drive and gametic competition occurs in one sex only, an unlinked neo-W can invade as long as the same allele is favoured in male and female diploid selection and there are sex differences in selection of one type (e.g., $s^\female(s^\male-s^\female)>0$, see Figure \ref{fig:Combination_Centimorgans}C,D).
+Secondly, we can simplify cases where invasion occurs despite $R>r$ using the special case where $R=1/2$ and $r<1/2$ (e.g., in the ancestor the selected locus is on an autosome and the novel sex-determining allele arises on it).
+In table \ref{tab:specialcases} we give the conditions where invasion occurs when we further assume that haploid selection only occurs in one sex (e.g., during male meiosis only) and dominance coefficients are equal in the two sexes, $h^\female=h^\male$.
+Where there is no gametic competition and meiotic drive in one sex only, an unlinked neo-W can invade as long as the same allele is favoured during diploid selection in males and females ($s^\female s^\male>0$, see Figure \ref{fig:Combination_Centimorgans}B).
+%, which is 50\% of the parameter space.
+When there is no meiotic drive and gametic competition occurs in one sex only, an unlinked neo-W can invade as long as the same allele is favoured in male and female diploid selection and there are sex differences in selection of one type (e.g., $s^\female(s^\male-s^\female)>0$, see Figure \ref{fig:Combination_Centimorgans}C,D).
 %, which is 25\% of the parameter space.
@@
 %Sex ratios
-Previous research suggests, when the ancestral sex-determining locus is linked to a locus that experiences haploid selection (e.g., meiotic drive), a new, unlinked sex-determining locus invades in order to restore equal sex ratios \citep{Kozielska:2010vm}.
+Previous research suggests that when the ancestral sex-determining locus is linked to a locus that experiences haploid selection (e.g., meiotic drive), a new, unlinked sex-determining locus invades in order to restore equal sex ratios \citep{Kozielska:2010vm}.
 Our model provides a good opportunity to determine whether Fisherian sex ratio selection provides a useful explanation for the evolution of new sex-determining loci in other contexts. 
@@
 We next consider the case where the new sex-determining mutation, $m$, causes sex to be determined stochastically or by environmental conditions (environmental sex determiner, ESD). 
-We assume that individuals carrying the $m$ allele develop as females in a fraction, $k$, of the environments they experience. 
+We assume that individuals carrying the $m$ allele develop as females in a fraction, $k$, of the environments they (randomly) experience. 
 The spread of these mutations is given by
@@
 Under Fisherian sex ratio selection, autosomal modifiers favour equal investment in male and female offspring, i.e., a 1:1 sex ratio \citep{Fisher:1930wy,Charnov:1982wg,West:2009we}. 
-Therefore, a novel environmental sex-determiner that causes half of its carriers to become female and half to become male ($k=1/2$) will be in males half of the time and in females half of the time (like an autosome).
+A novel environmental sex-determiner that causes half of its carriers to become female and half to become male ($k=1/2$) will be in males half of the time and in females half of the time (like an autosome).
 In addition, these novel sex-determination alleles equalize the sex ratio and so one might expect them to be favoured by Fisherian sex ratio selection when the resident sex ratio is biased.

### 2017-05-18 LaTeX/Turnover.tex

--- 2017-05-18 LaTeX/Turnover.tex
@@
 \textcolor{red}{CHECK: DO THE HAPLOID MEAN FITNESSES HAVE TO BE IN THE DENOMINATOR?}
+
 % as there are now two 2s in the lambdas of table 2. perhaps the 2 in the denominator is needed because the frequency of males sums to one as does the frequency of females?}
@@
 
-%%% ADD ZYGOTIC SEX RATIO HERE
-
+% SOME OF THIS IS REPEATED IN THE APPENDIX CURRENLTY
 We are particularly concerned with the conditions under which a rare neo-sex-determining allele increases in frequency, which occurs when the largest eigenvalue, $\lambda$, is greater than one. 

### 2017-05-19 LaTeX/Turnover.tex
read and edited appendix, didnt quite make it to adding anything about invasion

@@
 The resulting zygotes develop as males or females, depending on their genotypes at the \textbf{X} and \textbf{M} loci (and the \textbf{M} genotype of their mother in the case of maternal control) as described above.
-Diploid males and females then experience selection, relative fitnesses are given by $w_{g}^{\Hermaphrodite}$, where $g$ is the diploid genotype at the \textbf{A} locus ($g \in \{AA, Aa, aa\}$).  
+Diploid males and females then experience selection, with relative fitnesses $w_{AA}^{\Hermaphrodite}$, $w_{Aa}^{\Hermaphrodite}$, and $w_{aa}^{\Hermaphrodite}$.
+%where $g$ is the diploid genotype at the \textbf{A} locus ($g \in \{AA, Aa, aa\}$).
 %Diploids compete with others of the same sex, where selection depends on the sex of the individual and its genotype at the \textbf{A} locus.
@@
 
-\textcolor{red}{CHECK: DO THE HAPLOID MEAN FITNESSES HAVE TO BE IN THE DENOMINATOR?}
+\textcolor{red}{CHECK: DO THE HAPLOID MEAN FITNESSES HAVE TO BE IN THE DENOMINATOR? i think so, based on definitions in table S.2 (mmo)}
 
@@
 
-In each generation we census the genotype frequencies in male and female gametes/gametophytes (hereafter, gametes) after meiosis (and any meiotic drive) and immediately before gametic competition. 
-At this stage, the frequencies of X-bearing male and female gametes are given by $X_{i}^{\male}$ and $X_{i}^{\female}$ and the frequencies of Y-bearing gametes are given by $Y_{i}^{\male}$ and $Y_{i}^{\female}$ where the index $i$ specifies genotypes $MA=1$, $Ma=2$, $mA=3$, and $ma=4$ ($\sum_{i=1}^{4}Y_{i}^{\male}+X_{i}^{\male}=1$ and $\sum_{i=1}^{4}Y_{i}^{\female}+X_{i}^{\female}=1$).
-Competition then occurs among gametes of the same sex (e.g., among eggs and among sperm separately) according to the \textbf{A} locus allele, $g$ ($g\in A$, $a$, see Table \ref{tab:fitnesstable}), carried by individuals with genotype $i$.
-The genotype frequencies after gametic competition are $X_{i}^{\Hermaphrodite,s}= w_{g}X_{i}^{\Hermaphrodite}/\bar{w}_{H}^{\Hermaphrodite}$ and $Y_{i}^{\Hermaphrodite,s}= w_{g}Y_{i}^{\Hermaphrodite}/\bar{w}_{H}^{\Hermaphrodite}$, where $\bar{w}_{H}^{\Hermaphrodite}=\sum_{i=1}^{4} w_{g}X_{i}^{\Hermaphrodite}+w_{g}Y_{i}^{\Hermaphrodite}$ is the mean fitness of male ($\Hermaphrodite=\male$) or female ($\Hermaphrodite=\female$) gametes.
-Random mating then occurs between gametes to produce diploid zygotes with genotype $ij$ at the \textbf{A} and \textbf{M} loci, such that $XX$ zygotes are denoted $xx_{ij}$, $XY$ zygotes are $xy_{ij}$, and $YY$ zygotes are $yy_{ij}$.
-In $XX$ and $YY$ zygotes, individuals with genotype $ij$ are equivalent to those with genotype $ji$; for simplicity, we denote the frequency of genotype $ij$ to the average of these frequencies, $xx_{ij}=(X_{i}^{\female,s}X_{j}^{\male,s}+X_{j}^{\female,s}X_{i}^{\male,s})/2$ and $yy_{ij}=(Y_{i}^{\female,s}Y_{j}^{\male,s}+Y_{j}^{\female,s}Y_{i}^{\male,s})/2$.
-
-Denoting the \textbf{M} locus genotype by $b$ ($b\in MM$, $Mm$, $mm$) and the \textbf{X} locus genotype by $c$ ($c\in XX$, $XY$, $YY$), zygotes develop as females with probability $k_{bc}$. 
-Therefore, the frequencies of $XX$ females are given by $xx_{ij}^{\female}=k_{bc}xx_{ij}$, $XY$ females are given by $xy_{ij}^{\female}=k_{bc}xy_{ij}$, and $YY$ females are given by $yy_{ij}^{\female}=k_{bc}xy_{ij}$.
-Similarly, $XX$ male frequencies are $xx_{ij}^{\male}=(1-k_{bc})xx_{ij}$, $XY$ male frequencies are $xy_{ij}^{\male}=(1-k_{bc})xy_{ij}$, and $YY$ males frequencies are $yy_{ij}^{\male}=(1-k_{bc})xy_{ij}$.
+In each generation we census the genotype frequencies in male and female gametes/gametophytes (hereafter, gametes) between meiosis (and any meiotic drive) and gametic competition. 
+At this stage we denote the frequencies of X- and Y-bearing gametes from males and females $X_{ij}^{\Hermaphrodite}$ and $Y_{ij}^{\Hermaphrodite}$, where $\Hermaphrodite \in \{\male,\female\}$ specifies the sex of the diploid that the gamete came from, $i\in\{A,a\}$ specifies the allele at the selected locus $\mathbf{A}$, and $j\in\{M,m\}$ specifies the allele at the novel sex-determining locus $\mathbf{M}$.
+The gamete frequencies from each sex sum to one, $\sum_{i,j}x_{ij}^{\Hermaphrodite}+y_{ij}^{\Hermaphrodite}=1$.
+
+Competition then occurs among gametes of the same sex (e.g., among eggs and among sperm separately) according to the \textbf{A} locus allele, $i$ (see Table \ref{tab:fitnesstable}).
+The genotype frequencies after gametic competition are $x_{ij}^{\Hermaphrodite,s}= w_{i}x_{ij}^{\Hermaphrodite}/\bar{w}_{H}^{\Hermaphrodite}$ and $y_{ij}^{\Hermaphrodite,s}= w_{i}y_{ij}^{\Hermaphrodite}/\bar{w}_{H}^{\Hermaphrodite}$, where $\bar{w}_{H}^{\Hermaphrodite}=\sum_{i,j} w_{i}x_{ij}^{\Hermaphrodite}+w_{i}y_{ij}^{\Hermaphrodite}$ is the mean fitness of male ($\Hermaphrodite=\male$) or female ($\Hermaphrodite=\female$) gametes.
+
+Random mating then occurs between gametes to produce diploid zygotes.
+To shorten notation we now use index $i$ (and $j$) to denote the alleles at both the $\mathbf{A}$ and $\mathbf{M}$ loci and label $MA=1$, $Ma=2$, $mA=3$, and $ma=4$, such that $i,j\in\{1,2,3,4\}$.
+The frequencies of $XX$ zygotes are then denoted as $xx_{ij}$, $XY$ zygotes as $xy_{ij}$, and $YY$ zygotes as $yy_{ij}$. 
+In $XX$ and $YY$ zygotes, individuals with diploid genotype $ij$ are equivalent to those with diploid genotype $ji$; for simplicity, we use $xx_{ij}$ and $yy_{ij}$ to denote the average of these frequencies, $xx_{ij}=(X_{i}^{\female,s}X_{j}^{\male,s}+X_{j}^{\female,s}X_{i}^{\male,s})/2$ and $yy_{ij}=(Y_{i}^{\female,s}Y_{j}^{\male,s}+Y_{j}^{\female,s}Y_{i}^{\male,s})/2$.
+
+Denoting the \textbf{M} locus genotype by $b$ ($b\in \{MM$, $Mm$, $mm$\}) and the \textbf{X} locus genotype by $c$ ($c\in \{XX$, $XY$, $YY$\}), zygotes develop as females with probability $k_{bc}$. 
+Therefore, the frequencies of $XX$ females are given by $xx_{ij}^{\female}=k_{bc}xx_{ij}$, $XY$ females are given by $xy_{ij}^{\female}=k_{bc}xy_{ij}$, and $YY$ females are given by $yy_{ij}^{\female}=k_{bc}yy_{ij}$.
+Similarly, $XX$ male frequencies are $xx_{ij}^{\male}=(1-k_{bc})xx_{ij}$, $XY$ male frequencies are $xy_{ij}^{\male}=(1-k_{bc})xy_{ij}$, and $YY$ males frequencies are $yy_{ij}^{\male}=(1-k_{bc})yy_{ij}$.
 This notation allows both the ancestral and novel sex-determining regions to determine zygotic sex according to an $XY$ system, a $ZW$ system, or an environmental sex-determining system. 
@@
 
-Selection among diploids then occurs according to the diploid genotype at the \textbf{A} locus, $h$, for an individual of type $ij$ ($h \in AA$, $Aa$, $aa$, see Table \ref{tab:fitnesstable}). 
-The diploid frequencies after selection in sex $\Hermaphrodite$ are given by $xx_{ij}^{\Hermaphrodite,s}=w_{h}^{\Hermaphrodite} xx_{ij}/\bar{w}^{\Hermaphrodite}$, $xy_{ij}^{\Hermaphrodite,s}=w_{h}^{\Hermaphrodite} xy_{ij}/\bar{w}^{\Hermaphrodite}$, and $yy_{ij}^{\Hermaphrodite,s}=w_{h}^{\Hermaphrodite} yy_{ij}/\bar{w}^{\Hermaphrodite}$, where $\bar{w}^{\Hermaphrodite}= \sum_{i=1}^{4}\sum_{j=1}^{4}w_{h}^{\Hermaphrodite}xx_{ij}+w_{h}^{\Hermaphrodite}xy_{ij}+w_{h}^{\Hermaphrodite}yy_{ij}$ is the mean fitness of individuals of sex $\Hermaphrodite$.
+Selection among diploids then occurs according to the diploid genotype at the \textbf{A} locus, $l$, for an individual of type $ij$ ($l \in \{AA$, $Aa$, $aa$\}, see Table \ref{tab:fitnesstable}). 
+The diploid frequencies after selection in sex $\Hermaphrodite$ are given by $xx_{ij}^{\Hermaphrodite,s}=w_{l}^{\Hermaphrodite} xx_{ij}/\bar{w}^{\Hermaphrodite}$, $xy_{ij}^{\Hermaphrodite,s}=w_{l}^{\Hermaphrodite} xy_{ij}/\bar{w}^{\Hermaphrodite}$, and $yy_{ij}^{\Hermaphrodite,s}=w_{l}^{\Hermaphrodite} yy_{ij}/\bar{w}^{\Hermaphrodite}$, where $\bar{w}^{\Hermaphrodite}= \sum_{i=1}^{4}\sum_{j=1}^{4}w_{l}^{\Hermaphrodite}xx_{ij}+w_{l}^{\Hermaphrodite}xy_{ij}+w_{l}^{\Hermaphrodite}yy_{ij}$ is the mean fitness of individuals of sex $\Hermaphrodite$.
 
@@
 $R$ is the recombination rate between the \textbf{A} locus and the \textbf{M} locus, $\chi$ is the recombination rate between the \textbf{M} locus and the \textbf{X} locus, and $r$ is the recombination rate between the \textbf{A} locus and the \textbf{X} locus.
-Table \ref{tab:chisubstitutions} gives substitutions for $\chi$ for defined relative locations of these loci.
+Table \ref{tab:chisubstitutions} shows how $\chi$ can be substituted to give any linear order of loci.
 During meiosis in sex $\Hermaphrodite$, meiotic drive occurs such that, in $Aa$ heterozygotes, a fraction $\alpha^{\Hermaphrodite}$ of gametes produced carry the $A$ allele and $(1-\alpha^\Hermaphrodite)$ carry the $a$ allele.
@@
 \noindent
-The full system is therefore described by 16 recurrence equations (three loci, each with two alleles, and two gamete sexes yields 16 combinations). 
+The full system is therefore described by 16 recurrence equations (three diallelic loci in two sexes, $2^3 \times 2 = 16$). 
 However, some diploid types are not produced under a given sex determination system. 
-For example, with the $M$ allele fixed and ancestral $XY$ sex determination, there are no $XX$ males, $XY$ females, or $YY$ females ($xx_{11}^{\male}$, $xx_{12}^{\male}$, $xx_{22}^\male$, $xy_{11}^{\female}$, $xy_{12}^{\female}$, $xy_{22}^\female$, $yy_{11}^{\female}$, $yy_{12}^{\female}$, and $yy_{22}^\female$ are all 0).
-In this case, the system only involves six recursion equations because there is only one \textbf{M} locus allele and no Y-bearing female gametes. 
-This six-equation system yields equilibrium \eqref{eq:pAve}.
+For example, with the $M$ allele fixed and ancestral $XY$ sex determination, there are no $m$ alleles, $XX$ males, $XY$ females, or $YY$ females ($xx_{11}^{\male}=xx_{12}^{\male}=xx_{22}^\male=xy_{11}^{\female}=xy_{12}^{\female}=xy_{21}^{\female}=xy_{22}^\female=yy_{11}^{\female}=yy_{12}^{\female}=yy_{22}^\female=0$).
+In this case, the system only involves six recursion equations, %because there is only one \textbf{M} locus allele and no Y-bearing female gametes. 
+which yields equilibrium \eqref{eq:pAve}.
 
 %I think this should be moved below because we have some 'results' where we don't assume weak selection but we only have the equilibrium calculated analytically for weak selection.
+
 \subsection*{Resident equilibrium and stability}
 
-In the resident population (allele $M$ fixed), we follow the frequency of $A$ in female gametes (eggs) from an XX female, $p^\female_X$, and in X-bearing, $p^\male_X$, and Y-bearing, $p^\male_Y$, male gametes (sperm).
+In the resident population (allele $M$ fixed), we choose to follow the frequency of $A$ in female gametes (eggs) from an XX female, $p^\female_X$, and in X-bearing, $p^\male_X$, and Y-bearing, $p^\male_Y$, male gametes (sperm).
 We also track the total frequency of Y among male gametes, $q$, which may deviate from $1/2$ due to meiotic drive in males. 
-Within this resident population (when $m$ is absent) we can then describe frequencies among different gamete types, which are given by $X_{MA}^{\female}=p_{X}^{\female}$, $X_{Ma}^{\female}=(1-p_{X}^{\female})$, $X_{MA}^{\male}=(1-q)p_{X}^{\male}$, $X_{Ma}^{\male}=(1-q)(1-p_{X}^{\male})$, $Y_{MA}^{\male}=q p_{Y}^{\male}$, and $Y_{Ma}^{\male}=q(1-p_{Y}^{\male})$.
-Mean fitnesses in this resident population are given in table \ref{tab:meanfitnesses}.
-
-Various forms of selection can maintain a polymorphism at the \textbf{A} locus, including sexually antagonistic selection, overdominance and conflicts between diploid selection and selection upon haploid genotypes \citep[ploidally antagonistic selection,][]{Immler:2012tl} or a combination of these selective regimes.
+These four variables determine the frequencies of the six resident gamete types: $X_{MA}^{\female}=p_{X}^{\female}$, $X_{Ma}^{\female}=1-p_{X}^{\female}$, $X_{MA}^{\male}=(1-q)p_{X}^{\male}$, $X_{Ma}^{\male}=(1-q)(1-p_{X}^{\male})$, $Y_{MA}^{\male}=q p_{Y}^{\male}$, and $Y_{Ma}^{\male}=q(1-p_{Y}^{\male})$.
+Mean fitnesses in the resident population are given in table \ref{tab:meanfitnesses}.
+
+Various forms of selection can maintain a polymorphism at the \textbf{A} locus, including sexually antagonistic selection, overdominance, conflicts between diploid selection and selection upon haploid genotypes \citep[ploidally antagonistic selection,][]{Immler:2012tl}, and a combination of these selective regimes.
 
@@
 
-\subsubsection*{Recombination weak relative to selection}
+In particular special cases, e.g., no sex-differences in selection or meiotic drive ($s^\male=s^\female$, $h^\male=h^\female$, and $\alpha^\male=\alpha^\female=1/2$), the equilibrium allele frequency and stability can be calculated analytically without assuming anything about the relative strengths of selection and recombination.
+However, here, we focus on two regimes (tight linkage and weak selection) in order to make fewer assumptions about fitnesses.
+
+\subsubsection*{Recombination weak relative to selection (tight linkage)}
 
 We first calculate the equilibrium frequency of the Y and $A$ alleles in the ancestral population when the recombination rate between the \textbf{X} and \textbf{A} loci is small ($r$ of order $\epsilon$).
-The \textbf{A} locus will not affect evolution of novel sex-determination systems (\textbf{M} locus) if one \textbf{A} locus allele is fixed on all backgrounds.
+The \textbf{A} locus will not affect evolution at the novel sex-determining locus, \textbf{M}, if one \textbf{A} allele is fixed on all backgrounds. 
 We therefore focus on the five equilibria that maintain both $A$ and $a$ alleles, of which four are given to leading order by:
@@
 \ \hat{p}_{X}^{\male}=\frac{2 \alpha^{\male}w_{Aa}^{\male} \Phi}{2\alpha^{\male}w_{Aa}^{\male} \Phi +w_{AA}^{\male} \Psi}\\
-(A')\ \ \ &\hat{p}_{Y}^{\male}=0,
+(A')\ \ \ &\hat{p}_{Y}^{\male}=1,
 \ \hat{q}=\frac{1}{2}+\frac{(\alpha^{\male}-1/2)w_{Aa}^{\male} \Phi'}{w_{Aa}^{\male} \Phi' + w_{AA}^{\male} \Psi'},\\
@@
 \ \hat{p}_{X}^{\male}=1-\frac{2(1-\alpha^{\male})w_{Aa}^{\male} \Phi'}{2(1-\alpha^{\male})w_{Aa}^{\male} \Phi'+w_{aa}^{\male} \Psi'}\\
-(B)\ \ \ &\hat{p}_{Y}^{\male}=0,\ \hat{p}_{X}^{\female}=1,\ \hat{p}_{X}^{\male}=1, \ \hat{q}=(1-\alpha^{\male})\\
+(B)\ \ \ &\hat{p}_{Y}^{\male}=0,\ \hat{p}_{X}^{\female}=1,\ \hat{p}_{X}^{\male}=1, \ \hat{q}=1-\alpha^{\male}\\
 (B')\ \ \ &\hat{p}_{Y}^{\male}=1,\ \hat{p}_{X}^{\female}=0,\ \hat{p}_{X}^{\male}=0, \ \hat{q}=\alpha^{\male}\\
@@
 Since equilibria $(A)$ and $(B)$ are equivalent to equilibria $(A')$ and $(B')$ with the labelling of $A$ and $a$ alleles interchanged, we discuss only equilibria $(A)$ and $(B)$, in which the Y is fixed for the $a$ allele.
-If there is no haploid selection ($\alpha^{\Hermaphrodite}=1/2$, $w_{g}^{\Hermaphrodite}=1$), these equilibria are equivalent to those found by \textcolor{red}{Otto (2014) and Lloyd (197?, see Otto for reference)}.
+If there is no haploid selection ($\alpha^{\Hermaphrodite}=1/2$, $w_{A}^{\Hermaphrodite}=w_{a}^{\Hermaphrodite}$), these equilibria are equivalent to those found by \cite{Lloyd1977} and \cite{Otto2014}.
 
@@
 That is, $Ya$ haplotypes must have higher fitness than $YA$ haplotypes.
-Substituting $\hat{p}_{Xf}$ from above, fixation of the $A$ allele on the Y requires that $\gamma_{i}>0$ where $\gamma_{(A)}=w_{a}^{\male}(2(1-\alpha^{\male})w_{Aa}^{\male} \Phi + w_{aa}^{\male} \Psi)-w_{A}^{\male}(2\alpha^{\male}w_{Aa}^{\male} \Phi + w_{aa}^{\male} \Psi)$ for equilibrium $(A)$ and $\gamma_{(B)}=2(1-\alpha^{\male})w_{a}^{\male}w_{Aa}^{\male}-w_{A}^{\male}w_{AA}^{\male}$ for equilibrium $(B)$.
+Substituting in $p_{X}^{\female} = \hat{p}_{X}^{\female}$ from above, fixation of the $A$ allele on the Y requires that $\gamma_{i}>0$ where $\gamma_{(A)}=w_{a}^{\male}(2(1-\alpha^{\male})w_{Aa}^{\male} \Phi + w_{aa}^{\male} \Psi)-w_{A}^{\male}(2\alpha^{\male}w_{Aa}^{\male} \Phi + w_{aa}^{\male} \Psi)$ for equilibrium $(A)$ and $\gamma_{(B)}=2(1-\alpha^{\male})w_{a}^{\male}w_{Aa}^{\male}-w_{A}^{\male}w_{AA}^{\male}$ for equilibrium $(B)$.
 Stability of a polymorphism on the X chromosome (equilibrium $A$) further requires that $\Phi >0$ and $\Psi >0$. 
-Fixation of the $a$ allele on the X (equilibrium $B$) is mutually exclusive with $(A)$ and requires that $\Psi<0$ and $w_{A}^{\female}w_{AA}^{\female}>(1-\alpha^{\female})w_{a}^{\female}w_{Aa}^{\female}$.
-
-\subsubsection*{Selection weak relative to recombination}
+Fixation of the $a$ allele on the X (equilibrium ($B$)) is mutually exclusive with equilibrium $(A)$ and requires $\Psi<0$ and $w_{A}^{\female}w_{AA}^{\female}>(1-\alpha^{\female})w_{a}^{\female}w_{Aa}^{\female}$.
+
+\subsubsection*{Selection weak relative to recombination (weak selection)}
 
@@
 \noindent
-which indicates that a polymorphism is maintained under various selective regimes. 
-In particular special cases, e.g., no sex-differences in selection or meiotic drive ($s^\male=s^\female$, $h^\male=h^\female$, and $\alpha^\male=\alpha^\female=1/2$), the equilibrium allele frequency and stability can be calculated analytically without assuming weak selection.
-However, here, we focus on weak selection in order to make fewer assumptions about fitnesses.
-
-Given that a polymorphism is maintained at the \textbf{A} locus by selection, with weak selection and drive, to leading order, the frequencies of $A$ in each type of gamete are the same ($\hat{p}^\female_X=\hat{p}^\male_X=\hat{p}^\male_Y=\bar{p}$) and given by
+which indicates that a polymorphism can be maintained by various selective regimes.
+
+Given that a polymorphism is maintained at the \textbf{A} locus by selection, with weak selection and drive the frequencies of $A$ in each type of gamete are the same ($\hat{p}^\female_X=\hat{p}^\male_X=\hat{p}^\male_Y=\bar{p}$) and given, to leading order, by
 
@@
 \noindent
-Differences in frequency between gamete types are of order $\epsilon$ to leading order and given by
+Differences in frequency between gamete types are of order $\epsilon$ and given, to leading order, by
 
@@
 The frequency of Y among male gametes depends upon the difference in the frequency of the $A$ allele between X- and Y-bearing male gametes and the strength of meiotic drive in favour of the $A$ allele in males, $q=1/2+\alpha_{\Delta}^\male(\hat{p}^\male_Y-\hat{p}^\male_X)/2+O(\epsilon^3)$.
-Without gametic competition or drive ($\alpha_{\Delta}^\Hermaphrodite=t^\Hermaphrodite=0$), these results reduce to those of \citet{vanDoorn:2007eu}.
+Without gametic competition or drive ($\alpha_{\Delta}^\Hermaphrodite=t^\Hermaphrodite=0$) our results reduce to those of \citet{vanDoorn:2007eu}.
 
@@
 Here, we determine whether a rare neo-Y or neo-W allele spreads when rare, which occurs when $\lambda > 1$.
+We begin with the general result and then give explicit solutions under tight linkage and weak selection.
+
 If the average change in frequency of the two haplotypes that carry the $m$ allele ($Am$ and $am$) is positive, invasion will always occur (i.e., if $\left\{(\lambda_{mA}-1)+ (\lambda_{ma}-1) \right\}/2 > 0$ then $\lambda > 1$, see table \ref{tab:haplotype_growth} for $\lambda_{mi}$).
@@
 for the neo-$W$.
+
 %Equations \eqref{eq:neoYR} and \eqref{eq:neoWR} show that the new sex-determining allele, $m$, is expected to invade for any probability of recombination between loci \textbf{A} and \textbf{M}, $R$, when the net flow of recombinants is from the less fit (smaller $\lambda_{mi}$) to the more fit \textbf{A} background (making the terms inside the square brackets in Equations \ref{eq:neoYR} and \ref{eq:neoWR} negative).
@@
 In which case it might be better to have slightly different phrasing here.}
+Equations \eqref{eq:neoYR} and \eqref{eq:neoWR} show that the new sex-determining allele, $m$, is expected to invade for any probability of recombination between loci \textbf{A} and \textbf{M}, $R$, when the net flow of recombinants is from the less fit (smaller $\lambda_{mi}$) to the more fit \textbf{A} background (making the terms inside the square brackets in Equations \ref{eq:neoYR} and \ref{eq:neoWR} negative).
+When the net flow of recombinants is from the more fit to the less fit haplotype, the new sex-determining allele can still invade when the rate of recombination between it and the selected locus is small enough.
+To better understand when these scenarios are possible we next use knowledge of the equilibria and their stability under tight linkage and weak selection.
+
+\subsubsection*{Recombination weak relative to selection (tight linkage)}
+
+At equilibrium ($A$) we have
+
+\subsubsection*{Selection weak relative to recombination (weak selection)}
 

### 2017-05-19 LaTeX/Turnover.tex
table 2 updated and appenidx reworded

@@
 
-\textcolor{red}{I now remove the zygotic sex ratio $\zeta$ from the mean fitnesses. The mean fitnesses will have to be adjusted in a corresponding way.}
-
-\textcolor{red}{CHECK: DO THE HAPLOID MEAN FITNESSES HAVE TO BE IN THE DENOMINATOR? i think so, based on definitions in table S.2 (mmo)}
+%\textcolor{red}{I now remove the zygotic sex ratio $\zeta$ from the mean fitnesses. The mean fitnesses will have to be adjusted in a corresponding way.}
+%
+%\textcolor{red}{CHECK: DO THE HAPLOID MEAN FITNESSES HAVE TO BE IN THE DENOMINATOR? i think so, based on definitions in table S.2 (mmo)}
 
@@
    neo-Y ($k=0$) \\ [0.5ex] \hline \noalign{\vskip 1ex}
-  $\lambda_{mA}=[1/(2(1- \zeta))]\{p_{X}^{\female} w_{A}^{\female} w_{A}^{\male} w_{AA}^{\male} + 2(1-p_{X}^{\female}) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} \alpha^\male (1 - R)\}/ \bar{w}^\male $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\lambda_{ma}=[1/(2(1- \zeta))]\{(1-p_{X}^{\female}) w_{a}^{\female} w_{a}^{\male} w_{aa}^{\male} + 2p_{X}^{\female} w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male}(1 - \alpha^\male) (1 - R)\}/ \bar{w}^\male $ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\rho_{mA}=R (1-p_{X}^{\female}) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} \alpha^{\male}/  (1-\zeta) \bar{w}^\male  $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\rho_{ma}=R p_{X}^{\female} w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male} (1 - \alpha^{\male})/ (1-\zeta) \bar{w}^\male $\\ [1ex] \hline 
+  $\lambda_{mA}=[1/(2 (1- \zeta))]\{p_{X}^{\female} w_{A}^{\female} w_{A}^{\male} w_{AA}^{\male} + 2(1-p_{X}^{\female}) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} \alpha^\male (1 - R)\}/ \{\bar{w}^\male \bar{w}_H^\female \bar{w}_H^\male \}  $\\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\lambda_{ma}=[1/(2(1-\zeta))]\{(1-p_{X}^{\female}) w_{a}^{\female} w_{a}^{\male} w_{aa}^{\male} + 2p_{X}^{\female} w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male}(1 - \alpha^\male) (1 - R)\}/ \{\bar{w}^\male \bar{w}_H^\female \bar{w}_H^\male \}  $ \\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\rho_{mA}=R (1-p_{X}^{\female}) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} \alpha^{\male}/  \{(1-\zeta) \bar{w}^\male \bar{w}_H^\female \bar{w}_H^\male \}   $\\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\rho_{ma}=R p_{X}^{\female} w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male} (1 - \alpha^{\male})/ \{(1-\zeta) \bar{w}^\male \bar{w}_H^\female \bar{w}_H^\male \}  $\\ [1ex] \hline 
   \noalign{\vskip 0.5ex}
   neo-W ($k=1$) \\ [0.5ex] \hline \noalign{\vskip 1ex}
-  $\lambda_{mA}=[1/(2 \zeta)]\{\bar{p}^{\male} w_{A}^{\male} w_{A}^{\female} w_{AA}^{\female}+2(1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female}\alpha^\female(1-R)\}/ \bar{w}^\female $ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\lambda_{ma}=[1/(2 \zeta)]\{(1-\bar{p}^{\male}) w_{a}^{\male} w_{a}^{\female} w_{aa}^{\female}+2\bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female}(1-\alpha^\female)(1-R)\}/ \bar{w}^\female $ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\rho_{mA}=R (1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female} \alpha^{\female}/ \zeta \bar{w}^\female  $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\rho_{ma}=R\bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female} (1-\alpha^{\female})/ \zeta \bar{w}^\female $\\ [1ex] 
+  $\lambda_{mA}=[1/(2 \zeta)]\{\bar{p}^{\male} w_{A}^{\male} w_{A}^{\female} w_{AA}^{\female}+2(1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female}\alpha^\female(1-R)\}/ \{\bar{w}^\female \bar{w}_H^\female \bar{w}_H^\male \} $ \\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\lambda_{ma}=[1/(2 \zeta)]\{(1-\bar{p}^{\male}) w_{a}^{\male} w_{a}^{\female} w_{aa}^{\female}+2\bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female}(1-\alpha^\female)(1-R)\}/ \{\bar{w}^\female \bar{w}_H^\female \bar{w}\} $ \\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\rho_{mA}=R (1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female} \alpha^{\female}/ \{ \zeta \bar{w}^\female \bar{w}_H^\female \bar{w}_H^\male \}  $\\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\rho_{ma}=R\bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female} (1-\alpha^{\female})/ \{ \zeta \bar{w}^\female \bar{w}_H^\female \bar{w}_H^\male \} $\\ [1ex] 
   \hline \hline 
@@
       \item $R$ is the probability of recombination between loci \textbf{A} and \textbf{M}.
-      \item $\zeta$ is the zygotic sex ratio and $\bar{w}^\Hermaphrodite$ is the mean fitness of sex $\Hermaphrodite$, see Table \ref{tab:meanfitnesses}.
+      \item $\zeta$ is the zygotic sex ratio (fraction female)
+      \item $\bar{w}^\Hermaphrodite$ is the mean fitness of diploids of sex $\Hermaphrodite$, see Table \ref{tab:meanfitnesses}
+      \item $\bar{w}_H^\Hermaphrodite$ is the mean fitness of haploids from sex $\Hermaphrodite$, see Table \ref{tab:meanfitnesses}
 %      \item $\bar{w}_H^\female = p_X^\female w_A^\female + (1-p_X^\female) w_a^\female$ is the mean fitness of female gametes during gametic competition
@@
 Table \ref{tab:haplotype_growth} illustrates a number of key points about the invasion of neo-Y and neo-W mutations. 
-Firstly, Fisherian sex ratio selection will favour the spread of a neo-Y if the ancestral zygotic sex ratio is biased towards males, $\zeta>1/2$, and vice versa for a neo-W, see terms in square brackets.
+Firstly, Fisherian sex ratio selection will favour the spread of a neo-Y if the ancestral zygotic sex ratio is biased towards females, $\zeta>1/2$, and vice versa for a neo-W, see terms in square brackets.
 However, the spread of a neo-Y (neo-W) also depends on the male (female) fitness of alleles that they are associated with, see terms in curly brackets. 

### 2017-05-19 LaTeX/Turnover.tex
one sentence

--- 2017-05-18 LaTeX/Turnover.tex
@@
 \title{Gametic Selection, Meiotic Drive, Sex Ratio Bias, and Transitions Between Sex Determination Systems}
-\author{Michael F Scott$*^1$, Matthew M Osmond$*^2$, and Sarah P Otto$^2$}
+\author{Michael F Scott$*^1$ and Matthew M Osmond$*^2$, and Sarah P Otto$^2$}
 \date{}
@@
 I wonder if this is actually a fusion event though?
-In addition, many gonochoric clades with genetic sex determination exhibit transitions between male (XY) and female (ZW) heterogamety, including lizards \citep{Ezaz:2009tk}, eight of 26 teleost fish families \citep{Mank:2006bt}, true fruit flies \citep[Tephritids,][]{Vicoso:2015hf}, amphibians \citep{Hillis:1990gu}, the angiosperm genus \textit{Silene} \citep{Slancarova:2013dq}, and Coleoptera and Hemiptera \citep[][plate 2]{Beukeboom:2014vb}.
+In addition, many gonochoric clades with genetic sex determination exhibit transitions between male (XY) and female (ZW) heterogamety, including lizards \citep{Ezaz:2009tk}, eight of 26 teleost fish families \citep{Mank:2006bt}, true fruit flies \citep[Tephritids,][]{Vicoso:2015hf}, amphibians \citep{Hillis:1990gu}, the angiosperm genus \textit{Silene} \citep{Slancarova:2013dq}, Coleoptera and Hemiptera \citep[][plate 2]{Beukeboom:2014vb}.
 Indeed, in some cases, both male and female heterogametic sex determination systems can be found in the same species, as exhibited by some cichlid species \citep{Ser:2010iq} and \textit{Rana rugosa} \citep{Ogata:2007jm}.
@@
 However, any sexually-antagonistic loci that are more closely linked to the ancestral sex-determination locus will develop similar, favourable associations and select against the spread of a new sex-determination system.
-Here we extend these studies by explictly calculating the the equilibrium allele frequencies of loci that are very tightly linked to the ancestral sex-determining region.
+Here, we extend these studies by explictly calculating the the equilibrium allele frequencies of loci that are very tightly linked to the ancestral sex-determining region.
 
@@
 There are various ways in which a period of haploid selection could influence transitions between sex determination systems. 
-If we assume that haploid selection at any particular locus predominantly occurs in one sex (e.g., meiotic drive during spermatogenesis), then such loci experience a form of sex-specific selection. 
+Firstly, if we assume that haploid selection at any particular locus predominantly occurs in one sex (e.g., meiotic drive during spermatogenesis), then such loci experience a form of sex-specific selection.
 In this respect, we might expect that haploid selection would affect transitions between sex determination systems in a similar manner to sex-specific diploid selection \citep[as explored by][]{vanDoorn:2007eu,vanDoorn:2010hu}.
@@
 However, sex ratios can also become biased by linkage between the sex-determining region and a locus that harbours genetic variation in haploid fitness. 
-For example, there are several known cases of sex ratio bias caused by sex-linked meiotic drive alleles \citep[][Chapter 3]{Burt:2006} or selection among X- and Y-bearing pollen \citep{Lloyd:1974tz,Conn:1981uw,Stehlik:2005ul,Stehlik:2006to,Field:2012fd,Field:2013cc}.
+For example, there are several known cases of sex ratio bias caused by sex-linked meiotic drive alleles \citep[][, Chapter 3]{Burt:2006} or selection among X- and Y-bearing pollen \citep{Lloyd:1974tz,Conn:1981uw,Stehlik:2005ul,Stehlik:2006to,Field:2012fd,Field:2013cc}.
 It is not immediately clear how the spread of new sex determination systems would be influenced by the combination of sex ratio biases and associations between haploid selected loci and sex-determining regions.
@@
 %genetic system
-We consider the transition between ancestral and novel sex determination systems using a three locus model. 
+We consider the transition between an ancestral and novel sex determination systems using a three locus model. 
 Locus \textbf{X} is the ancestral sex-determining region, with alleles $X$ and $Y$ (or $Z$ and $W$).
@@
 With $k=0$, the $m$ allele is a masculinizer (i.e., a neo-Y) and with $k=1$ the $m$ allele is a feminizer (i.e., a neo-W).
-With intermediate $k$, the $m$ allele confers environmental sex determination (ESD) such that zygotes develop as females in a proportion ($k$) of the environments they (randomly) experience. 
+With intermediate $k$, the $m$ allele confers environmental sex determination (ESD) such that zygotes develop as females in a proportion ($k$) of the environments they experience. 
 Finally, we also analyze a model of maternally-controlled environmental sex-determination, where mothers with at least one $m$ allele produce daughters with probability $k$.
@@
 The resulting zygotes develop as males or females, depending on their genotypes at the \textbf{X} and \textbf{M} loci (and the \textbf{M} genotype of their mother in the case of maternal control) as described above.
-Diploid males and females then experience selection, relative fitnesses are given by $w_{g}^{\Hermaphrodite}$, where $g$ is the diploid genotype at the \textbf{A} locus ($g \in \{AA, Aa, aa\}$).  
+Diploid males and females then experience selection, relative fitnesses are given by $w_{g}^{\male}$ in males and $w_{g}^{\female}$ in females, where $g$ is the diploid genotype at the \textbf{A} locus ($g \in \{AA, Aa, aa\}$).
 %Diploids compete with others of the same sex, where selection depends on the sex of the individual and its genotype at the \textbf{A} locus.
@@
 Recombination (i.e., an odd number of cross-overs) occurs between loci \textbf{X} and \textbf{A} with probability $r$, between loci \textbf{A} and \textbf{M} with probability $R$, and between loci \textbf{X} and \textbf{M} with probability $\chi$.
-Any linear order of the loci can be modelled with appropriate choices of $r$, $R$, and $\chi$ (see Table \ref{tab:chisubstitutions}). 
-Individuals that are heterozygous at the \textbf{A} locus may experience meiotic drive; $Aa$ heterozgotes of sex $\Hermaphrodite$ produce gametes bearing allele $A$ with probability $\alpha^\Hermaphrodite$.
-Thus, the \textbf{A} locus can experience sex-specific gametic competition, diploid selection, and/or meiotic drive.
+Therefore, any order of the loci can be modelled with appropriate choices of $r$, $R$, and $\chi$ (see Table \ref{tab:chisubstitutions}). 
+Males/females that are heterozygous at the \textbf{A} locus may experience meiotic drive; $Aa$ heterozgotes of sex $\Hermaphrodite$ produce gametes bearing allele $A$ with probability $\alpha^\Hermaphrodite$.
+Thus, the \textbf{A} locus can experience sex-specific gametic competition, diploid selection and/or meiotic drive.
 
@@
   A & $\alpha^\Hermaphrodite=1/2+\alpha_{\Delta}^{\Hermaphrodite}/2$ \\
-  a & $1-\alpha^\Hermaphrodite=1/2-\alpha_{\Delta}^{\Hermaphrodite}/2$ \\
+  a & $(1-\alpha^\Hermaphrodite)=1/2-\alpha_{\Delta}^{\Hermaphrodite}/2$ \\
   \hline \hline
@@
 The evolution of a new sex determination system requires that a rare mutant allele, $m$, at the novel sex-determining locus  increases in frequency when rare. 
-The spread of a rare mutant $m$ at the \textbf{M} locus is determined by the leading eigenvalue, $\lambda$, of the system of eight equations describing the next generation frequency of eggs and sperm carrying the mutation, (\ref{eq:recursions}c, \ref{eq:recursions}d, \ref{eq:recursions}g, \ref{eq:recursions}h).
+The spread of a rare mutant $m$ at the \textbf{M} locus is determined by the leading eigenvalue, $\lambda$, of the system of eight equations describing the next generation frequency of eggs and sperm carrying the mutation, (\ref{eq:recursions}c), (\ref{eq:recursions}d), (\ref{eq:recursions}g), (\ref{eq:recursions}h).
 %, evaluated at the above equilibrium.
@@
 Dominant neo-Y (when $k=0$) or neo-W alleles (when $k=1$) are only found in male diploids (neo-Y) or female diploids (neo-W) such that their growth rate ultimately depends only on the change in frequency of $m$-bearing gametes produced by males (for a neo-Y) or by females (for a neo-W).
-Furthermore, if the $m$ allele is fully epistatically dominant over the ancestral sex-determining system, phenotypes are not affected by the genotype at the ancestral sex-determining region (\textbf{X} locus).
+Furthermore, if the $m$ allele is fully dominant over the ancestral sex-determining system, phenotypes are not affected by the genotype at the ancestral sex-determining region (\textbf{X} locus). 
 Thus, the invasion of rare dominant neo-Y or neo-W alleles is determined by the largest eigenvalue that solves the quadratic characteristic polynomial
@@
 %where $b$ is the average of the growth rates of the two haplotypes that carry the $m$ allele ($mA$ and $ma$), $b=(\lambda_{mA}+\lambda_{ma})/2$, and $c$ also involves the fitness of $m$ alleles when they recombine onto the other \textbf{A} background in a heterozygote, $c=\lambda_{mA}\lambda_{ma}+\rho_{mA}\rho_{ma}$ (see table \ref{tab:haplotype_growth}).
-In this case $b= - (\lambda_{mA} + \lambda_{ma})$ and $c = \lambda_{mA} \lambda_{ma} -\rho_{mA} \rho_{ma}$, where $\lambda_{mi}$ is the (multiplicative) growth rate of mutant haplotypes on background $i\in\{A,a\}$, accounting for loss due to recombination, and $\rho_{mi}$ is the rate of addition of mutant haplotypes onto background $i\in\{A,a\}$ due to recombination (see table \ref{tab:haplotype_growth}).
-The spread of the mutant $m$ allele depends on the frequency of alleles at the other two loci in the ancestral population. 
+In this case $b= - (\lambda_{mA} + \lambda_{ma})$ and $c = \lambda_{mA} \lambda_{ma} -\rho_{mA} \rho_{ma}$, where $\lambda_{mi}$ is the (discrete time) growth rate of mutant haplotypes on background $i\in\{A,a\}$, accounting for loss due to recombination, and $\rho_{mi}$ is the rate of addition of mutant haplotypes onto background $i\in\{A,a\}$ due to recombination, see table \ref{tab:haplotype_growth}.
+The spread of the mutant $m$ allele depends on the frequency of alleles at the other loci in the ancestral population. 
 In the ancestral population, it is convenient to follow the frequency of the $A$ allele in female gametes (eggs) from an XX female, $p^\female_X$, and in X-bearing, $p^\male_X$, and Y-bearing, $p^\male_Y$, male gametes (sperm).
@@
 \textcolor{red}{CHECK: DO THE HAPLOID MEAN FITNESSES HAVE TO BE IN THE DENOMINATOR?}
-
 % as there are now two 2s in the lambdas of table 2. perhaps the 2 in the denominator is needed because the frequency of males sums to one as does the frequency of females?}
@@
 
-% SOME OF THIS IS REPEATED IN THE APPENDIX CURRENLTY
+%%% ADD ZYGOTIC SEX RATIO HERE
+
 We are particularly concerned with the conditions under which a rare neo-sex-determining allele increases in frequency, which occurs when the largest eigenvalue, $\lambda$, is greater than one. 
@@
 If neither haplotype increases in frequency ($\lambda_{mA}, \lambda_{ma} < 1$), the $m$ allele will not invade. 
-Otherwise, the new sex-determining allele increases in frequency on one \textbf{A} background and declines on the other and invasion depends on the recombination rate between the \textbf{M} and \textbf{A} loci ($R$) see equations \eqref{eq:neoYR} and \eqref{eq:neoWR}.
+Otherwise, the new sex-determining allele increases in frequency on one \textbf{A} background and declines on the other and invasion will occur when the recombination rate between the \textbf{M} and \textbf{A} loci ($R$) is below a critical value (this critical value can be greater than $1/2$ such that unlinked $m$ alleles invade), see equations \eqref{eq:neoYR} and \eqref{eq:neoWR}.
 
@@
 
+When $\lambda_{ma}>1$, a neo-W linked to the $a$ allele spreads because it is favoured by selection in females despite the fact that the $a$ allele was stably fixed on the Y, which we might commonly assume to harbour male beneficial alleles.
+This situation can occur when there is a male-biased zygotic sex ratio and/or when the $a$ allele has higher fitness in females (given the
+
+Explain $ma$ and $mA$ hypotheses.
+
+We can also simplify cases where $R>0$ by assuming that selection and drive are weak ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon$), which implicitly assumes that $R$ is relatively large.
+
 %weak selection
@@
 where $V_{A}=\bar{p}(1-\bar{p})$ is the variance in the frequency of $A$ and $S_{A}=(D^\male +\alpha_{\Delta}^\male+t^\male) - (D^\female+\alpha_{\Delta}^\female+t^\female)$ is the difference in fitness in males versus females for the $A$ allele against the $a$ allele across diploid selection, gametic competition, and meiosis.
-$D^\Hermaphrodite=\big{(} \bar{p}s^\Hermaphrodite+(1-\bar{p})h^\Hermaphrodite s^\Hermaphrodite\big{)} -\big{(} \bar{p}h^\Hermaphrodite s^\Hermaphrodite+(1-\bar{p}) \big{)}$ is the difference in fitness between $A$ and $a$ alleles in diploids of sex $\Hermaphrodite \in \{\female,\male\}$; $\bar{p}$ is the leading-order probability of mating with an $A$-bearing gamete from the opposite sex (see Appendix).
+$D^\Hermaphrodite=\big{(} \bar{p}s^\Hermaphrodite+(1-\bar{p})h^\Hermaphrodite s^\Hermaphrodite\big{)} -\big{(} \bar{p}h^\Hermaphrodite s^\Hermaphrodite+(1-\bar{p}) \big{)}$ is the difference in fitness between $A$ and $a$ alleles in diploids of sex $\Hermaphrodite \in \{\female,\male\}$; $\bar{p}$ is the leading-order probability of mating with an $A$-bearing gamete from the opposite sex, see appendix.
 
@@
 
-Equation \eqref{eq:lambda_neoW} shows that if there is no haploid selection ($t^\Hermaphrodite=\alpha^\Hermaphrodite_{\Delta}=0$), as considered by \citet{vanDoorn:2010hu}, the spread of a neo-W is equivalent to the spread of a neo-Y ($\lambda_{W',XY}=\lambda_{Y',XY}$) such that heterogametic transitions (XY to ZW or ZW to XY) can also occur only if the neo-sex-determining region is more closely linked to a locus under selection ($R<r$).
+Equation \eqref{eq:lambda_neoW} shows that if there is no selection upon haploid genotypes ($t^\Hermaphrodite=\alpha^\Hermaphrodite_{\Delta}=0$), as considered by \citet{vanDoorn:2010hu}, the spread of a neo-W is equivalent to the spread of a neo-Y ($\lambda_{W',XY}=\lambda_{Y',XY}$) such that heterogametic transitions (XY to ZW or ZW to XY) can also occur only if the neo-sex-determining region is more closely linked to a locus under selection ($R<r$).
 However, if there is any haploid selection, the additional term in equation \eqref{eq:lambda_neoW} can be positive, which can allow, for example, neo-W invasion ($\lambda_{W',XY}>1$) even when the neo-sex-determining region is less closely linked to the selected locus ($R>r$).
@@
 Indeed, invasion typically occurs when the neo-W is more closely linked to the selected locus than the ancestral sex-determining region (Figure \ref{fig:Combination_Centimorgans}).
-Secondly, we can simplify cases where invasion occurs despite $R>r$ using the special case where $R=1/2$ and $r<1/2$ (e.g., in the ancestor the selected locus is on an autosome and the novel sex-determining allele arises on it).
-In table \ref{tab:specialcases} we give the conditions where invasion occurs when we further assume that haploid selection only occurs in one sex (e.g., during male meiosis only) and dominance coefficients are equal in the two sexes, $h^\female=h^\male$.
-Where there is no gametic competition and meiotic drive in one sex only, an unlinked neo-W can invade as long as the same allele is favoured during diploid selection in males and females ($s^\female s^\male>0$, see Figure \ref{fig:Combination_Centimorgans}B).
-%, which is 50\% of the parameter space.
-When there is no meiotic drive and gametic competition occurs in one sex only, an unlinked neo-W can invade as long as the same allele is favoured in male and female diploid selection and there are sex differences in selection of one type (e.g., $s^\female(s^\male-s^\female)>0$, see Figure \ref{fig:Combination_Centimorgans}C,D).
+Secondly, we can simplify cases where invasion occurs despite $R>r$ using the special case where $R=1/2$ and $r<1/2$. 
+In table \ref{tab:specialcases} we give the conditions where invasion occurs where we further assume that haploid selection only occurs in one sex (e.g., during male meiosis only) and dominance coefficients are equal in the two sexes, $h^\female=h^\male$.
+Where there is no gametic competition and meiotic drive in one sex only, an unlinked neo-W can invade as long as the same allele is favoured during diploid selection in males and females ($s^\female s^\male>0$, see Figure \ref{fig:Combination_Centimorgans}B).%, which is 50\% of the parameter space.
+Where there is no meiotic drive and gametic competition occurs in one sex only, an unlinked neo-W can invade as long as the same allele is favoured in male and female diploid selection and there are sex differences in selection of one type (e.g., $s^\female(s^\male-s^\female)>0$, see Figure \ref{fig:Combination_Centimorgans}C,D).
 %, which is 25\% of the parameter space.
@@
 %Sex ratios
-Previous research suggests that when the ancestral sex-determining locus is linked to a locus that experiences haploid selection (e.g., meiotic drive), a new, unlinked sex-determining locus invades in order to restore equal sex ratios \citep{Kozielska:2010vm}.
+Previous research suggests, when the ancestral sex-determining locus is linked to a locus that experiences haploid selection (e.g., meiotic drive), a new, unlinked sex-determining locus invades in order to restore equal sex ratios \citep{Kozielska:2010vm}.
 Our model provides a good opportunity to determine whether Fisherian sex ratio selection provides a useful explanation for the evolution of new sex-determining loci in other contexts. 
@@
 We next consider the case where the new sex-determining mutation, $m$, causes sex to be determined stochastically or by environmental conditions (environmental sex determiner, ESD). 
-We assume that individuals carrying the $m$ allele develop as females in a fraction, $k$, of the environments they (randomly) experience. 
+We assume that individuals carrying the $m$ allele develop as females in a fraction, $k$, of the environments they experience. 
 The spread of these mutations is given by
@@
 Under Fisherian sex ratio selection, autosomal modifiers favour equal investment in male and female offspring, i.e., a 1:1 sex ratio \citep{Fisher:1930wy,Charnov:1982wg,West:2009we}. 
-A novel environmental sex-determiner that causes half of its carriers to become female and half to become male ($k=1/2$) will be in males half of the time and in females half of the time (like an autosome).
+Therefore, a novel environmental sex-determiner that causes half of its carriers to become female and half to become male ($k=1/2$) will be in males half of the time and in females half of the time (like an autosome).
 In addition, these novel sex-determination alleles equalize the sex ratio and so one might expect them to be favoured by Fisherian sex ratio selection when the resident sex ratio is biased.

### 2017-05-19 LaTeX/Turnover.tex

--- 2017-05-19 LaTeX/Turnover.tex
@@
 These conditions are given in more detail in the appendix.
+
+When $\lambda_{ma}>1$, a neo-W linked to the $a$ allele spreads because it is favoured by selection in females despite the fact that the $a$ allele was stably fixed on the Y, which we might commonly assume to harbour male beneficial alleles.
+This situation can occur when there is a male-biased zygotic sex ratio and/or when the $a$ allele has higher fitness in females (given the
+
+Explain $ma$ and $mA$ hypotheses.
+
+We can also simplify cases where $R>0$ by assuming that selection and drive are weak ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon$), which implicitly assumes that $R$ is relatively large.
 

### 2017-05-19 LaTeX/Turnover.tex
changed lambda definitions to be for R=0

--- 2017-05-19 LaTeX/Turnover.tex
@@
 
-\subsection*{Turnover between sex-determination systems}
+%\subsection*{Turnover between sex-determination systems}
+
+\subsubsection*{Generic invasion by a neo-Y or neo-W}
 
@@
 %where $b$ is the average of the growth rates of the two haplotypes that carry the $m$ allele ($mA$ and $ma$), $b=(\lambda_{mA}+\lambda_{ma})/2$, and $c$ also involves the fitness of $m$ alleles when they recombine onto the other \textbf{A} background in a heterozygote, $c=\lambda_{mA}\lambda_{ma}+\rho_{mA}\rho_{ma}$ (see table \ref{tab:haplotype_growth}).
-In this case $b= - (\lambda_{mA} + \lambda_{ma})$ and $c = \lambda_{mA} \lambda_{ma} -\rho_{mA} \rho_{ma}$, where $\lambda_{mi}$ is the (multiplicative) growth rate of mutant haplotypes on background $i\in\{A,a\}$, accounting for loss due to recombination, and $\rho_{mi}$ is the rate of addition of mutant haplotypes onto background $i\in\{A,a\}$ due to recombination (see table \ref{tab:haplotype_growth}).
+%Here, $b= - (\lambda_{mA} + \lambda_{ma})$ and $c = \lambda_{mA} \lambda_{ma} -\rho_{mA} \rho_{ma}$, where $\lambda_{mi}$ is the (multiplicative) growth rate of mutant haplotypes on background $i\in\{A,a\}$, accounting for loss due to recombination, and $\rho_{mi}$ is the rate of addition of mutant haplotypes onto background $i\in\{A,a\}$ due to recombination (see table \ref{tab:haplotype_growth}).
+Here, $b= - (\lambda_{mA} + \lambda_{ma})+(\rho_{mA} + \rho_{ma})$ and $c = (\lambda_{mA}-\rho_{mA}) (\lambda_{ma}-\rho_{ma}) -\rho_{mA} \rho_{ma}$, where $\lambda_{mi}$ is the (multiplicative) growth rate of mutant haplotypes on background $i\in\{A,a\}$, without accounting for loss due to recombination, and $\rho_{mi}$ is the rate at which mutant haplotypes on background $i\in\{A,a\}$ recombine onto the other \textbf{A} locus background in heterozygotes (see table \ref{tab:haplotype_growth}).
 The spread of the mutant $m$ allele depends on the frequency of alleles at the other two loci in the ancestral population. 
@@
    neo-Y ($k=0$) \\ [0.5ex] \hline \noalign{\vskip 1ex}
-  $\lambda_{mA}=[1/(2 (1- \zeta))]\{p_{X}^{\female} w_{A}^{\female} w_{A}^{\male} w_{AA}^{\male} + 2(1-p_{X}^{\female}) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} \alpha^\male (1 - R)\}/ \{\bar{w}^\male \bar{w}_H^\female \bar{w}_H^\male \}  $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\lambda_{ma}=[1/(2(1-\zeta))]\{(1-p_{X}^{\female}) w_{a}^{\female} w_{a}^{\male} w_{aa}^{\male} + 2p_{X}^{\female} w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male}(1 - \alpha^\male) (1 - R)\}/ \{\bar{w}^\male \bar{w}_H^\female \bar{w}_H^\male \}  $ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\rho_{mA}=R (1-p_{X}^{\female}) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} \alpha^{\male}/  \{(1-\zeta) \bar{w}^\male \bar{w}_H^\female \bar{w}_H^\male \}   $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\rho_{ma}=R p_{X}^{\female} w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male} (1 - \alpha^{\male})/ \{(1-\zeta) \bar{w}^\male \bar{w}_H^\female \bar{w}_H^\male \}  $\\ [1ex] \hline 
+  $\lambda_{mA}=[1/(2 (1- \zeta))]\{p_{X}^{\female} w_{A}^{\female} w_{A}^{\male} w_{AA}^{\male} + 2(1-p_{X}^{\female}) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} \alpha^\male \}/ \{ \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \} $\\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\lambda_{ma}=[1/(2(1-\zeta))]\{(1-p_{X}^{\female}) w_{a}^{\female} w_{a}^{\male} w_{aa}^{\male} + 2p_{X}^{\female} w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male}(1 - \alpha^\male) \}/ \{\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \} $ \\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\rho_{mA}=R[1/(2(1-\zeta))] \{ 2(1-p_{X}^{\female}) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} \alpha^{\male} \}/  \{ \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \}   $\\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\rho_{ma}= R [1/(2(1-\zeta))] \{  2 p_{X}^{\female} w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male} (1 - \alpha^{\male}) \}/ \{ \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \}  $\\ [1ex] \hline 
   \noalign{\vskip 0.5ex}
   neo-W ($k=1$) \\ [0.5ex] \hline \noalign{\vskip 1ex}
-  $\lambda_{mA}=[1/(2 \zeta)]\{\bar{p}^{\male} w_{A}^{\male} w_{A}^{\female} w_{AA}^{\female}+2(1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female}\alpha^\female(1-R)\}/ \{\bar{w}^\female \bar{w}_H^\female \bar{w}_H^\male \} $ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\lambda_{ma}=[1/(2 \zeta)]\{(1-\bar{p}^{\male}) w_{a}^{\male} w_{a}^{\female} w_{aa}^{\female}+2\bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female}(1-\alpha^\female)(1-R)\}/ \{\bar{w}^\female \bar{w}_H^\female \bar{w}\} $ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\rho_{mA}=R (1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female} \alpha^{\female}/ \{ \zeta \bar{w}^\female \bar{w}_H^\female \bar{w}_H^\male \}  $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\rho_{ma}=R\bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female} (1-\alpha^{\female})/ \{ \zeta \bar{w}^\female \bar{w}_H^\female \bar{w}_H^\male \} $\\ [1ex] 
+  $\lambda_{mA}=[1/(2 \zeta)]\{\bar{p}^{\male} w_{A}^{\male} w_{A}^{\female} w_{AA}^{\female}+2(1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female}\alpha^\female\}/ \{\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \} $ \\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\lambda_{ma}=[1/(2 \zeta)]\{(1-\bar{p}^{\male}) w_{a}^{\male} w_{a}^{\female} w_{aa}^{\female}+2\bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female}(1-\alpha^\female)\}/ \{\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \} $ \\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\rho_{mA}=R [1/(2 \zeta)] \{2(1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female} \alpha^{\female} \}/ \{ \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \}  $\\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\rho_{ma}=R [1/(2 \zeta)] \{ 2\bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female} (1-\alpha^{\female}) \}/ \{ \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \} $\\ [1ex] 
   \hline \hline 
@@
 
-% SOME OF THIS IS REPEATED IN THE APPENDIX CURRENLTY
+%We are particularly concerned with the conditions under which a rare neo-sex-determining allele increases in frequency, which occurs when the largest eigenvalue, $\lambda$, is greater than one. 
+%If one or both of $\lambda_{mA}$ and $\lambda_{ma}$ are greater than one, indicating that at least one haplotype increases in frequency faster than recombination breaks it apart, invasion will always occur ($\lambda>1$).
+%Otherwise, invasion requires
+%\begin{equation}
+%(\lambda_{mA}-1)(\lambda_{ma}-1) - \rho_{mA} \rho_{ma}<0.
+%\end{equation}
+
 We are particularly concerned with the conditions under which a rare neo-sex-determining allele increases in frequency, which occurs when the largest eigenvalue, $\lambda$, is greater than one. 
-If the average change in frequency of the two haplotypes that carry the $m$ allele ($Am$ and $am$) is positive, invasion will always occur (i.e., if $\left\{(\lambda_{mA}-1)+ (\lambda_{ma}-1) \right\}/2 > 0$ then $\lambda > 1$).
+If the average change in frequency of the two haplotypes that carry the $m$ allele ($Am$ and $am$) is positive, invasion will always occur (i.e., if $\left\{(\lambda_{mA}-1)+ (\lambda_{ma}-1) \right\}/2 > 0$ then $\lambda > 1$.
 If neither haplotype increases in frequency ($\lambda_{mA}, \lambda_{ma} < 1$), the $m$ allele will not invade. 
-Otherwise, the new sex-determining allele increases in frequency on one \textbf{A} background and declines on the other and invasion depends on the recombination rate between the \textbf{M} and \textbf{A} loci ($R$) see equations \eqref{eq:neoYR} and \eqref{eq:neoWR}.
+Otherwise, the new sex-determining allele increases in frequency on one \textbf{A} background and declines on the other, and invasion requires
+\begin{equation}\label{eq:lambdasGen}
+\frac{\rho_{mA}}{(\lambda_{mA}-1)}+\frac{\rho_{ma}}{(\lambda_{ma}-1)}>0.
+\end{equation}
+\noindent For example, if we assume that only the $mA$ haplotype has a positive growth rate ($\lambda_{mA}>1$ and $\lambda_{ma}<1$), the second term in \eqref{eq:lambdasGen} is negative and invasion requires that the ratio of recombinants to growth rate from the fitter $mA$ haplotypes is larger than that of the less fit $ma$ haplotypes.
 
 Table \ref{tab:haplotype_growth} illustrates a number of key points about the invasion of neo-Y and neo-W mutations. 
-Firstly, Fisherian sex ratio selection will favour the spread of a neo-Y if the ancestral zygotic sex ratio is biased towards females, $\zeta>1/2$, and vice versa for a neo-W, see terms in square brackets.
+Firstly, Fisherian sex ratio selection will favour the spread of a neo-Y if the ancestral zygotic sex ratio is biased towards females, $\zeta>1/2$, and vice versa for a neo-W (terms in square brackets increase $\lambda_{mi}$).
 However, the spread of a neo-Y (neo-W) also depends on the male (female) fitness of alleles that they are associated with, see terms in curly brackets. 
@@
 
-%%% ADD r=0 HERE
-
 In order to explicitly determine the conditions under which a rare neo-sex-determining allele spreads, we must calculate the frequency of the $A$ allele in the ancestral population (i.e., $p^\female_X$, $p^\male_X$, and $p^\male_Y$).
@@
 
+\subsubsection*{Tight linkage with the ancestral sex-determining region}
+
 When there is tight linkage between the ancestral sex-determining region and the \textbf{A} locus ($r=0$), either the $A$ allele or the $a$ allele must be fixed on the Y. 
@@
 A neo-Y will never invade an ancestral XY system that already has tight linkage with the locus under selection ($r=0$). 
-When then neo-Y is also tightly linked ($R=0$) a neo-Y will either remain linked to the $A$ allele or to the $a$ allele and so invasion is given directly by the larger of $\lambda_{mA}$ or $\lambda_{ma}$ (evaluated with $R=0$).
-A neo-Y can either be linked to the same allele as the ancestral Y, in which case it is a neutral mutation with no effect ($\lambda_{ma}=1$), or be linked to the alternative \textbf{A} allele, in which case it will not spread given that the initial equilibrium is stable ($\lambda_{mA}<1$).
-Given that $\lambda_{mA}$ and $\lambda_{ma}$ both decrease with increasing $R$, more loosely linked neo-Y alleles also do not spread ($\lambda <1$ when $R>0$).
-
-However, under some conditions, a neo-W can invade an ancestral XY system. 
-When the neo-W is also tightly linked ($R=0$), it can spread in linkage with either the allele that is fixed on the Y or the allele that is more common on the X, i.e., under some conditions $\lambda_{ma}>1$ and/or $\lambda_{mA}>1$.
-These conditions are given in more detail in the appendix.
+%When then neo-Y is also tightly linked ($R=0$) a neo-Y will either remain linked to the $A$ allele or to the $a$ allele and so invasion is given directly by the larger of $\lambda_{mA}$ or $\lambda_{ma}$.
+A neo-Y haplotype with the same allele as the ancestral Y is neutral and does not change in frequency ($\lambda_{ma}=1$).
+The other neo-Y haplotype will not spread given that the initial equilibrium is stable ($\lambda_{mA}<1$). 
+Therefore, a neo-Y mutation cannot spread ($\lambda \leq 1$).
+
+Neo-W alleles, on the other hand, can invade an ancestral XY system under some conditions (given in detail in the appendix). 
+Given the ancestral allele frequencies in the population, neo-W-$A$ and/or neo-W-$a$ haplotypes can increase in frequency ($\lambda_{ma}>1$ and/or $\lambda_{mA}>1$). 
+Firstly, haploid selection causes the zygotic sex ratio to be male biased ($\zeta<1/2$) when the $a$ allele (which is fixed on the Y) is favoured during haploid competition or by meiotic drive. 
+This facilitates the spread of a neo-W because neo-W alleles cause zygotes to develop as the rarer female sex. 
+However, neo-W alleles can also be favoured via their associations with \textbf{A} locus alleles that confer a fitness advantage in females.
+We will first explore these situations by assuming that there is no haploid selection, which means that there are no zygotic sex ratio biases.
+
+\subsubsection*{Loose linkage with the ancestral sex-determining region}
 
@@
 %The equilibrium frequency of $A$ on different ancestral backgrounds ($\hat{p}^\male_Y$, $\hat{p}^\male_X$, and $\hat{p}^\female_X$) is given by equations \eqref{eq:pAve} and \eqref{eq:freq_diffs} where we assume selection and meiotic drive are weak relative to recombination ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon$).
-Under weak selection, we denote the leading eigenvalues describing the invasion of a neo-Y ($k=0$) and a neo-W ($k=1$) into an ancestrally XY system by $\lambda_{Y',XY}$ and $\lambda_{W',XY}$, respectively, which are given by
+Assuming that selection is weak relative to all recombination rates ($r$, $R$ and $\chi$), we denote the leading eigenvalues describing the invasion of a neo-Y ($k=0$) and a neo-W ($k=1$) into an ancestrally XY system by $\lambda_{Y',XY}$ and $\lambda_{W',XY}$, respectively, which are given by
 
@@
 That is, we can show that $\lambda_{Y',XY}=\lambda_{W',ZW}$ and $\lambda_{Y',ZW}=\lambda_{W',XY}$ (at least up to order $\epsilon^3$; for a numerical example, compare Figure \ref{fig:Combination_Turnover}A,B to Figure \ref{fig:Combination_Turnover}C,D).
+
+\subsubsection*{Environmental sex determination}
 
@@
 \smallskip
-\caption{mean fitnesses in resident ($M$ fixed, XY sex determination) }
+\caption{mean fitnesses in resident population ($M$ fixed, XY sex determination) }
 \begin{tabular}{l l }
@@
   p_X^\female w_A^\female (1 - p_X^\male) w_a^\male w_{Aa}^\female + \\
-  (1-p_X^\female) w_a^\female (1 - p_X^\male) w_a^\male w_{aa}^\female \} / \{ \bar{w}_H^\female \bar{w}_H^\male\}
+  (1-p_X^\female) w_a^\female (1 - p_X^\male) w_a^\male w_{aa}^\female \} / \{ \bar{w}_H^\female \bar{w}_H^\male \zeta \}
   \end{array} 
@@
   p_X^\female w_A^\female  (1 - p_Y^\male) w_a^\male w_{Aa}^\male + \\
-  (1-p_X^\female) w_a^\female  (1 - p_Y^\male) w_a^\male w_{aa}^\male \} / \{ \bar{w}_H^\male \bar{w}_H^\male\} 
+  (1-p_X^\female) w_a^\female  (1 - p_Y^\male) w_a^\male w_{aa}^\male \} / \{ \bar{w}_H^\female \bar{w}_H^\male (1-\zeta)\} 
   \end{array}
-  $ \\ [0.5ex]  \noalign{\vskip 0.5ex}
+  $ \\ [0.5ex] \hline  \noalign{\vskip 0.5ex}
+  zygotic sex ratio $\zeta$ & $\{ (1-q)(p_X^\male w_A^\male+(1-p_X^\male)w_a^\male)\} / \bar{w}_H^\male $
+   \\ [0.5ex]  \noalign{\vskip 0.5ex}
   \hline \hline
@@
 
-Here, we determine whether a rare neo-Y or neo-W allele spreads when rare, which occurs when $\lambda > 1$.
-We begin with the general result and then give explicit solutions under tight linkage and weak selection.
-
-If the average change in frequency of the two haplotypes that carry the $m$ allele ($Am$ and $am$) is positive, invasion will always occur (i.e., if $\left\{(\lambda_{mA}-1)+ (\lambda_{ma}-1) \right\}/2 > 0$ then $\lambda > 1$, see table \ref{tab:haplotype_growth} for $\lambda_{mi}$).
-If neither haplotype increases in frequency ($\lambda_{mA}, \lambda_{ma} < 1$), the $m$ allele will not invade. 
-Otherwise, the new sex-determining allele increases in frequency on one \textbf{A} background and declines on the other, and invasion requires
-\begin{equation}\label{eq:neoYR}
-R \left[ 
-\frac{p^\female_X w^\female_A w^\male_a (1-\alpha^\male)}{ \bar{w}^\female_H \bar{w}^\male_H (\lambda_{mA}-1)} + 
+%Here, we determine whether a rare neo-Y or neo-W allele spreads when rare, which occurs when $\lambda > 1$.
+%We begin with the general result and then give explicit solutions under tight linkage and weak selection.
+
+%If the average change in frequency of the two haplotypes that carry the $m$ allele ($Am$ and $am$) is positive, invasion will always occur (i.e., if $\left\{(\lambda_{mA}-1)+ (\lambda_{ma}-1) \right\}/2 > 0$ then $\lambda > 1$, see table \ref{tab:haplotype_growth} for $\lambda_{mi}$).
+%If neither haplotype increases in frequency ($\lambda_{mA}, \lambda_{ma} < 1$), the $m$ allele will not invade. 
+%Otherwise, the new sex-determining allele increases in frequency on one \textbf{A} background and declines on the other, and invasion requires
+%\begin{equation}\label{eq:neoYR}
+%R \left[ 
+%\frac{p^\female_X w^\female_A w^\male_a (1-\alpha^\male)}{ \bar{w}^\female_H \bar{w}^\male_H (\lambda_{mA}-1)} + 
 %p^\female_X \frac{w^\female_A}{\bar{w}^\female_H} \frac{w^\male_a(1-\alpha^\male)}{\bar{w}^\male_H} \frac{1}{\lambda_{mA}-1} + 
-\frac{(1 - p^\female_X) w^\female_a w^\male_A \alpha^\male}{ \bar{w}^\female_H \bar{w}^\male_H (\lambda_{ma}-1)} 
-\right] 
-\frac{w^\male_{Aa}}{q\bar{w}^\male} < 1,
-\end{equation}
-
-\noindent
-for the neo-$Y$, and
-
-\noindent
-\begin{equation}\label{eq:neoWR}
-R \left[ 
-\frac{\bar{p}^\male w^\male_A w^\female_a (1-\alpha^\female)}{ \bar{w}^\male_H \bar{w}^\female_H (\lambda_{mA}-1)} + 
-\frac{(1 - \bar{p}^\male) w^\male_a w^\female_A \alpha^\female}{ \bar{w}^\male_H \bar{w}^\female_H (\lambda_{ma}-1)} 
-\right] 
-\frac{w^\female_{Aa}}{(1-q)\bar{w}^\female} < 1,
-\end{equation}
-
-\noindent
-for the neo-$W$.
+%\frac{(1 - p^\female_X) w^\female_a w^\male_A \alpha^\male}{ \bar{w}^\female_H \bar{w}^\male_H (\lambda_{ma}-1)} 
+%\right] 
+%\frac{w^\male_{Aa}}{q\bar{w}^\male} < 1,
+%\end{equation}
+
+%\noindent
+%for the neo-$Y$, and
+
+%\noindent
+%\begin{equation}\label{eq:neoWR}
+%R \left[ 
+%\frac{\bar{p}^\male w^\male_A w^\female_a (1-\alpha^\female)}{ \bar{w}^\male_H \bar{w}^\female_H (\lambda_{mA}-1)} + 
+%\frac{(1 - \bar{p}^\male) w^\male_a w^\female_A \alpha^\female}{ \bar{w}^\male_H \bar{w}^\female_H (\lambda_{ma}-1)} 
+%\right] 
+%\frac{w^\female_{Aa}}{(1-q)\bar{w}^\female} < 1,
+%\end{equation}
+
+%\noindent
+%for the neo-$W$.
 
@@
 In which case it might be better to have slightly different phrasing here.}
-Equations \eqref{eq:neoYR} and \eqref{eq:neoWR} show that the new sex-determining allele, $m$, is expected to invade for any probability of recombination between loci \textbf{A} and \textbf{M}, $R$, when the net flow of recombinants is from the less fit (smaller $\lambda_{mi}$) to the more fit \textbf{A} background (making the terms inside the square brackets in Equations \ref{eq:neoYR} and \ref{eq:neoWR} negative).
-When the net flow of recombinants is from the more fit to the less fit haplotype, the new sex-determining allele can still invade when the rate of recombination between it and the selected locus is small enough.
-To better understand when these scenarios are possible we next use knowledge of the equilibria and their stability under tight linkage and weak selection.
+%Equations \eqref{eq:neoYR} and \eqref{eq:neoWR} show that the new sex-determining allele, $m$, is expected to invade for any probability of recombination between loci \textbf{A} and \textbf{M}, $R$, when the net flow of recombinants is from the less fit (smaller $\lambda_{mi}$) to the more fit \textbf{A} background (making the terms inside the square brackets in Equations \ref{eq:neoYR} and \ref{eq:neoWR} negative).
+%When the net flow of recombinants is from the more fit to the less fit haplotype, the new sex-determining allele can still invade when the rate of recombination between it and the selected locus is small enough.
+%To better understand when these scenarios are possible we next use knowledge of the equilibria and their stability under tight linkage and weak selection.
 
@@
 
-At equilibrium ($A$) we have
+Here, we give the conditions under which a neo-W invades assuming that the \textbf{A} locus is initially in close linkage with the ancestral sex-determining region ($r \approx 0$). 
+We disregard neo-Y mutations, which never spread given that the ancestral population is at a stable equilibrium. 
+At equilibrium $(B)$ we have
+
+\begin{subequations}
+\begin{align}
+\lambda_{mA}&=\frac{w_{A}^\male w_{AA}^\female \alpha^\male + 2 w_{a}^\male w_{Aa}^\female \alpha^\female(1-\alpha^\male)}{2w_{A}^\male  w_{AA}^\female \alpha^\male} \\
+\lambda_{ma}&=\frac{w_{a}^\female(w_{a}^\male w_{aa}^\female (1-\alpha^\male) + 2 w_{A}^\male w_{Aa}^\female(1-\alpha^\female)\alpha^\male)}{2w_{A}^\male w_{A}^\female w_{AA}^\female \alpha^\male} \\
+\rho_{mA}&= \frac{R w_{a}^\male w_{Aa}^\female \alpha^\female(1-\alpha^\male)}{w_{A}^\male w_{AA}^
+\female \alpha^\male} \\
+\rho_{ma}&= \frac{R w_{a}^\female w_{Aa}^\female (1-\alpha^\female)}{w_{A}^\female w_{AA}^
+\female} 
+\end{align}
+\end{subequations}
+
+\textcolor{red}{the versions for equil $(A)$ are not terrible but could be improved by cleverly re-writing with the $\phi$ and $\psi$ terms from above, I think...}
 

### 2017-05-19 LaTeX/Turnover.tex
invasion

@@
 \begin{equation}\label{eq:lambdasGen}
-\frac{\rho_{mA}}{(\lambda_{mA}-1)}+\frac{\rho_{ma}}{(\lambda_{ma}-1)}>0.
+\frac{\rho_{mA}}{\lambda_{mA}-1}+\frac{\rho_{ma}}{\lambda_{ma}-1}>0.
 \end{equation}
@@
 We assume that individuals carrying the $m$ allele develop as females in a fraction, $k$, of the environments they (randomly) experience. 
-The spread of these mutations is given by
+Assuming weak selection, the spread of these mutations is given by
 
@@
 In addition, these novel sex-determination alleles equalize the sex ratio and so one might expect them to be favoured by Fisherian sex ratio selection when the resident sex ratio is biased.
-However, we find that the growth rate of a rare, dominant offspring-controlled neo-ESD allele that produces males or females with equal probability ($k=1/2$) is
+However, assuming weak selection, we find that the growth rate of a rare, dominant offspring-controlled neo-ESD allele that produces males or females with equal probability ($k=1/2$) is
 \begin{equation}
@@
 We therefore also considered the invasion of a neo-sex-determining allele ($m$) in a model in which mothers that have at least one $m$ allele produce daughters with probability $k$. 
-As with offspring-controlled ESD, for all $k\in\{0,1/2,1\}$, we find that invasion into an ancestrally XY system is the same as invasion into an ancestrally ZW system (at least up to order $\epsilon^3$), implying transitions between genetic sex determination and maternally controlled environmental sex determination are not driven by Fisherian sex ratio selection on biased zygotic sex ratios.
+As with offspring-controlled ESD, for all $k\in\{0,1/2,1\}$, we find that invasion into an ancestrally XY system is the same as invasion into an ancestrally ZW system (at least up to order $\epsilon^3$, assuming weak selection), implying transitions between genetic sex determination and maternally controlled environmental sex determination are not driven by Fisherian sex ratio selection on biased zygotic sex ratios.
 
@@
 Since equilibria $(A)$ and $(B)$ are equivalent to equilibria $(A')$ and $(B')$ with the labelling of $A$ and $a$ alleles interchanged, we discuss only equilibria $(A)$ and $(B)$, in which the Y is fixed for the $a$ allele.
-If there is no haploid selection ($\alpha^{\Hermaphrodite}=1/2$, $w_{A}^{\Hermaphrodite}=w_{a}^{\Hermaphrodite}$), these equilibria are equivalent to those found by \cite{Lloyd1977} and \cite{Otto2014}.
+If there is no haploid selection ($\alpha^{\Hermaphrodite}=1/2$, $w_{A}^{\Hermaphrodite}=w_{a}^{\Hermaphrodite}=1$), these equilibria are equivalent to those found by \cite{Lloyd1977} and \cite{Otto2014}.
 
@@
 
-Here, we give the conditions under which a neo-W invades assuming that the \textbf{A} locus is initially in close linkage with the ancestral sex-determining region ($r \approx 0$). 
+Here, we give the conditions under which a neo-W invades an XY system assuming that the \textbf{A} locus is initially in close linkage with the ancestral sex-determining region ($r \approx 0$). 
 We disregard neo-Y mutations, which never spread given that the ancestral population is at a stable equilibrium. 
@@
 
-\begin{subequations}
+\begin{subequations}\label{Binvasion}
 \begin{align}
@@
 
-\textcolor{red}{the versions for equil $(A)$ are not terrible but could be improved by cleverly re-writing with the $\phi$ and $\psi$ terms from above, I think...}
+%\textcolor{red}{the versions for equil $(A)$ are not terrible but could be improved by cleverly re-writing with the $\phi$ and $\psi$ terms from above, I think...}
+
+Similar equations can be derived for equilibrium (A) by subbing the equilibrium allele frequencies into Table \ref{tab:haplotype_growth}.
+This gives
+%These simplify considerably when there is no haploid selection:
+%
+%%\begin{subequations}
+%%\begin{align}
+%%\lambda_{mA}&= \frac{(\phi + \psi)[(w_{AA}^\female + w_{Aa}^\female ) w_{Aa}^\male \phi + 2 w_{Aa}^\female w_{AA}^\male \psi ]}{2 (w_{AA}^\female w_{Aa}^\male \phi^2 + \psi(w_{Aa}^\female(w_{AA}^\male + w_{Aa}^\male)\phi + w_{aa}^\female w_{AA}^\male \psi)}\\
+%%\lambda_{ma}&=  \frac{(\phi + \psi)[(w_{aa}^\female + w_{Aa}^\female ) w_{Aa}^\male \phi + 2 w_{aa}^\female w_{AA}^\male \psi ]}{2 (w_{AA}^\female w_{Aa}^\male \phi^2 + \psi(w_{Aa}^\female(w_{AA}^\male + w_{Aa}^\male)\phi + w_{aa}^\female w_{AA}^\male \psi)}\\
+%%\rho_{mA}&= R \frac{(\phi + \psi) w_{Aa}^\female w_{AA}^\male}{2 (w_{AA}^\female w_{Aa}^\male \phi^2 + \psi(w_{Aa}^\female(w_{AA}^\male + w_{Aa}^\male)\phi + w_{aa}^\female w_{AA}^\male \psi)} \\ 
+%%\rho_{ma}&= R \frac{(\phi + \psi) w_{Aa}^\female w_{Aa}^\male}{2 (w_{AA}^\female w_{Aa}^\male \phi^2 + \psi(w_{Aa}^\female(w_{AA}^\male + w_{Aa}^\male)\phi + w_{aa}^\female w_{AA}^\male \psi)}\\
+%%\end{align}
+%%\end{subequations}
+%
+%\begin{subequations}
+%\begin{align}
+%\lambda_{mA}&= [( w_{AA}^\female + w_{Aa}^\female ) w_{Aa}^\male \phi + 2 w_{Aa}^\female w_{AA}^\male \psi] a \\
+%\lambda_{ma}&=  [(w_{aa}^\female + w_{Aa}^\female ) w_{Aa}^\male \phi + 2 w_{aa}^\female w_{AA}^\male \psi ] a\\
+%\rho_{mA}&= R w_{Aa}^\female (w_{Aa}^\male \phi + 2 w_{AA}^\male \psi) c \\ 
+%\rho_{ma}&= R w_{Aa}^\female w_{Aa}^\male \phi c \\
+%\end{align}
+%\end{subequations}
+%
+%\noindent
+%where 
+%$c = \frac{\phi + \psi}{2 [w_{AA}^\female w_{Aa}^\male \phi^2 + \psi(w_{Aa}^\female(w_{AA}^\male + w_{Aa}^\male)\phi + w_{aa}^\female w_{AA}^\male \psi]}$ and $\phi$ and $\psi$ are evaluated with $\alpha^{\Hermaphrodite}=1/2$ and $w_a^\Hermaphrodite=w_A^\Hermaphrodite=1$.
+%
+%With haploid selection we have
+
+\begin{subequations}\label{Ainvasion}
+\begin{align}
+\lambda_{mA}&= \frac{a}{b} \left[w_{AA}^\female w_{Aa}^\male w_A^\male \alpha^\male \phi + 2 w_{Aa}^\female \alpha^\female w_a^\male \frac{c}{d}\right] / w_a^\female \\
+\lambda_{ma}&= \frac{a}{b} \left[2 w_{Aa}^\female (1-\alpha^\female) w_{Aa}^\male w_A^\male \alpha^\male \phi+  w_{aa}^\female w_a^\male \frac{c}{d}\right] / w_A^\female \\
+\rho_{mA}&= \frac{a}{b} R \left[ 2 w_{Aa}^\female \alpha^\female w_a^\male \frac{c}{d} \right] / w_a^\female\\ 
+\rho_{ma}&= \frac{a}{b} R \left[ 2 w_{Aa}^\female (1-\alpha^\female) w_{Aa}^\male w_A^\male \alpha^\male \phi \right] / w_A^\female
+\end{align}
+\end{subequations}
+
+\noindent
+where
+
+\begin{subequations}
+\begin{align}
+a &= w_a^\female \phi + w_A^\female \psi \\
+b &= w_{AA}^\female \phi (2 w_{Aa}^\male w_A^\male \alpha_\male \phi) + w_{Aa}^\female \psi (2 w_{Aa}^\male w_A^\male \alpha_\male \phi + w_{AA}^\male w_a^\male \psi) + w_{aa}^\female \psi(w_{AA}^\male w_a^\male \psi) \\
+c &= 2(w_{Aa}^\male\phi)^2(1-\alpha^\male)\alpha_\male + w_{Aa}^\male\phi(w_{AA}^\male \psi + w_{aa}^\male \psi \alpha^\male) + w_{aa}^\male \psi w_{AA}^\male \psi \\
+d &= 2 w_{Aa}^\male \alpha^\male \phi + w_{aa}^\male \psi
+\end{align}
+\end{subequations}
+
+%Without haploid selection this reduces to
+%
+%\begin{subequations}
+%\begin{align}
+%\lambda_{mA}&= \frac{a}{b} \left[w_{AA}^\female w_{Aa}^\male \phi / 2 + w_{Aa}^\female \frac{c}{d}\right]  \\
+%\lambda_{ma}&= \frac{a}{b} \left[w_{Aa}^\female w_{Aa}^\male \phi / 2 +  w_{aa}^\female \frac{c}{d}\right] \\
+%\rho_{mA}&= \frac{a}{b} R \left[ w_{Aa}^\female \frac{c}{d} \right] \\ 
+%\rho_{ma}&= \frac{a}{b} R \left[ w_{Aa}^\female w_{Aa}^\male \phi / 2 \right] 
+%\end{align}
+%\end{subequations}
+
+With $R=0$ the two eigenvalues are $\lambda_{mA}$ and $\lambda_{ma}$.
+The neo-W can then invade on the $A$ background when $\lambda_{mA}>1$ and the neo-W can invade on the $a$ background when $\lambda_{ma}>1$.
+Even in this case it is difficult to see from equation \ref{Ainvasion} when the neo-W will invade.
+Below we discuss why $\lambda_{mA}$ and $\lambda_{ma}$ might be larger than one and confirm the logic numerically.
+
+For simplicity, consider the case of no haploid selection.
+A polymorphism at the $\mathbf{A}$ locus then requires sexually-antagonistic selection \citep{vanDoorn:2007eu}.
+Given that $a$ is fixed on the Y, one can consider the $a$ allele `male beneficial' and the $A$ allele to be `female beneficial'. 
+Because X chromosomes spend some time in males the frequency of $A$ on the X can reach an intermediate equilibrium (equilibrium A).
+
+We can therefore reason that when a neo-W invades equilibrium (A), it is likely to spread on the $A$ background as W chromosomes are always in females.
+The neo-W can outcompete the ancestral, `comprimising' X because it can specialize on females by fixing the `female beneficial' allele.  
+We call this the `sex-specialist hypothesis'.
+This hypothesis should only work when the benefit of specializing outweighs the cost of bringing Y chromosomes into females (the neo-W is epistatically dominant over the X/Y locus).
+
+One could also reason that, when the neo-W spreads, it does so precisely because it brings Y chromosomes, and their associated alleles, into females, something the X cannot do.
+However, this requires a somewhat particular (perhaps `perverse') equilibrium, where XX females do worse than XY females despite associations on the X and Y being built up by selection.
+One example of such a perverse equilibrium is produced by overdominance in both sexes.
+Overdominance in females selects for an allele frequency of 0.5 on the X ($A$ and $a$ equally frequent, maximizing the number of heterozygotes). 
+However, given that $a$ is fixed on the Y, overdominance in males selects for the X to become more associated with the $A$. 
+Thus, a compromising equilibrium is reached on the X chromosome and females fitness suffers due to the overproduction of $AA$ homozygotes.
+This sets up a scenario in which a neo-W can invade on the $a$ background, despite the fact that $a$ is fixed on the Y and in that sense `male beneficial'.
+We call this the `perverse hypothesis'.
+
+Figure \ref{fig:Region_Plot_2a} shows that both the sex-specialist and perverse hypotheses are valid.
+In fact, both can be simultaneously valid, which is generally where there is selection for increased recombination between the sex chromosomes \citep[][figure 2a]{Otto2014}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Sex-specialist vs perverse hypotheses
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[!h]
+\centering
+\includegraphics[width=0.5\linewidth]{regionplot_2a}\\
+\caption{
+Colours indicate where sex-specialist (red) and perverse (blue) hypotheses are valid, i.e., where a stable resident equilibrium is invaded by a neo-W that is perfectly linked with the allele not fixed on the Y (red) or the allele that is fixed on the Y (blue).
+Note that the perverse equilibrium is only valid with overdominance and that both are simultaneously valid over much of the parameter space where increased recombination between the sex chromosomes is selected \citep[][figure 2a]{Otto2014}.
+\textcolor{red}{can't make sex symbols in mathematica!}
+}
+\label{fig:Region_Plot_2a}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+With weak selection the leading eigenvalue for any $k$ is given, up to order $\epsilon^2$, by equation \ref{eq:lambda_ESD_k}.
+
 \newpage

### 2017-05-22 LaTeX/Turnover.tex
B conditions discussion appendix, some A equil conditions

@@
 \end{equation}
-\noindent For example, if we assume that only the $mA$ haplotype has a positive growth rate ($\lambda_{mA}>1$ and $\lambda_{ma}<1$), the second term in \eqref{eq:lambdasGen} is negative and invasion requires that the ratio of recombinants to growth rate from the fitter $mA$ haplotypes is larger than that of the less fit $ma$ haplotypes.
+\noindent For example, if we assume that only the $mA$ haplotype has a positive growth rate ($\lambda_{mA}>1$ and $\lambda_{ma}<1$), the second term in \eqref{eq:lambdasGen} is negative and invasion requires that number of recombinants from the fitter $mA$ haplotypes is larger than that of the less fit $ma$ haplotypes, relative to their growth rates.
 
@@
 (A)\ \ \ &\hat{p}_{Y}^{\male}=0,
-\ \hat{q}=\frac{1}{2}-\frac{(\alpha^{\male}-1/2)w_{Aa}^{\male} \Phi}{w_{Aa}^{\male} \Phi+ w_{aa}^{\male} \Psi},\\
-&\hat{p}_{X}^{\female}=\frac{w_{a}^{\female} \Phi}{w_{a}^{\female} \Phi+ w_{A}^{\female} \Psi},
-\ \hat{p}_{X}^{\male}=\frac{2 \alpha^{\male}w_{Aa}^{\male} \Phi}{2\alpha^{\male}w_{Aa}^{\male} \Phi +w_{AA}^{\male} \Psi}\\
+\ \hat{q}=\frac{1}{2}-\frac{(\alpha^{\male}-1/2)w_{Aa}^{\male} \phi}{w_{Aa}^{\male} \phi+ w_{aa}^{\male} \psi},\\
+&\hat{p}_{X}^{\female}=\frac{w_{a}^{\female} \phi}{w_{a}^{\female} \phi+ w_{A}^{\female} \psi},
+\ \hat{p}_{X}^{\male}=\frac{2 \alpha^{\male}w_{Aa}^{\male} \phi}{2\alpha^{\male}w_{Aa}^{\male} \phi +w_{AA}^{\male} \psi}\\
 (A')\ \ \ &\hat{p}_{Y}^{\male}=1,
-\ \hat{q}=\frac{1}{2}+\frac{(\alpha^{\male}-1/2)w_{Aa}^{\male} \Phi'}{w_{Aa}^{\male} \Phi' + w_{AA}^{\male} \Psi'},\\
-&\hat{p}_{X}^{\female}=1-\frac{w_{A}^{\female} \Phi'}{w_{A}^{\female} \Phi'+ w_{a}^{\female} \Psi'},
-\ \hat{p}_{X}^{\male}=1-\frac{2(1-\alpha^{\male})w_{Aa}^{\male} \Phi'}{2(1-\alpha^{\male})w_{Aa}^{\male} \Phi'+w_{aa}^{\male} \Psi'}\\
+\ \hat{q}=\frac{1}{2}+\frac{(\alpha^{\male}-1/2)w_{Aa}^{\male} \phi'}{w_{Aa}^{\male} \phi' + w_{AA}^{\male} \psi'},\\
+&\hat{p}_{X}^{\female}=1-\frac{w_{A}^{\female} \phi'}{w_{A}^{\female} \phi'+ w_{a}^{\female} \psi'},
+\ \hat{p}_{X}^{\male}=1-\frac{2(1-\alpha^{\male})w_{Aa}^{\male} \phi'}{2(1-\alpha^{\male})w_{Aa}^{\male} \phi'+w_{aa}^{\male} \psi'}\\
 (B)\ \ \ &\hat{p}_{Y}^{\male}=0,\ \hat{p}_{X}^{\female}=1,\ \hat{p}_{X}^{\male}=1, \ \hat{q}=1-\alpha^{\male}\\
@@
 \begin{split}
-\Phi=&\alpha^{\female} w_{A}^{\female} w_{Aa}^{\female}(w_{a}^{\male} w_{aa}^{\male} + 2 \alpha^{\male} w_{A}^{\male} w_{Aa}^{\male}) - w_{a}^{\male} w_{a}^{\female} w_{aa}^{\male} w_{aa}^{\female} \\
-\Psi=&(1-\alpha^{\female}) w_{a}^{\female} w_{Aa}^{\female}(w_{a}^{\male} w_{aa}^{\male} + 2 \alpha^{\male} w_{A}^{\male} w_{Aa}^{\male}) - 2\alpha^{\male} w_{A}^{\male} w_{A}^{\female} w_{Aa}^{\male} w_{AA}^{\female}\\
-\Phi'=&(1-\alpha^{\female}) w_{a}^{\female} w_{Aa}^{\female}(w_{A}^{\male} w_{AA}^{\male} + 2 (1-\alpha^{\male}) w_{a}^{\male} w_{Aa}^{\male}) - w_{A}^{\male} w_{A}^{\female} w_{AA}^{\male} w_{AA}^{\female}\\
-\Psi'=&\alpha^{\female} w_{A}^{\female} w_{Aa}^{\female}(w_{A}^{\male} w_{AA}^{\male} + 2 (1-\alpha^{\male}) w_{a}^{\male} w_{Aa}^{\male}) - 2(1-\alpha^{\male}) w_{a}^{\male} w_{a}^{\female} w_{Aa}^{\male} w_{aa}^{\female}\\
+\phi=&\alpha^{\female} w_{A}^{\female} w_{Aa}^{\female}(w_{a}^{\male} w_{aa}^{\male} + 2 \alpha^{\male} w_{A}^{\male} w_{Aa}^{\male}) - w_{a}^{\male} w_{a}^{\female} w_{aa}^{\male} w_{aa}^{\female} \\
+\psi=&(1-\alpha^{\female}) w_{a}^{\female} w_{Aa}^{\female}(w_{a}^{\male} w_{aa}^{\male} + 2 \alpha^{\male} w_{A}^{\male} w_{Aa}^{\male}) - 2\alpha^{\male} w_{A}^{\male} w_{A}^{\female} w_{Aa}^{\male} w_{AA}^{\female}\\
+\phi'=&(1-\alpha^{\female}) w_{a}^{\female} w_{Aa}^{\female}(w_{A}^{\male} w_{AA}^{\male} + 2 (1-\alpha^{\male}) w_{a}^{\male} w_{Aa}^{\male}) - w_{A}^{\male} w_{A}^{\female} w_{AA}^{\male} w_{AA}^{\female}\\
+\psi'=&\alpha^{\female} w_{A}^{\female} w_{Aa}^{\female}(w_{A}^{\male} w_{AA}^{\male} + 2 (1-\alpha^{\male}) w_{a}^{\male} w_{Aa}^{\male}) - 2(1-\alpha^{\male}) w_{a}^{\male} w_{a}^{\female} w_{Aa}^{\male} w_{aa}^{\female}\\
 \end{split}
@@
 That is, $Ya$ haplotypes must have higher fitness than $YA$ haplotypes.
-Substituting in $p_{X}^{\female} = \hat{p}_{X}^{\female}$ from above, fixation of the $A$ allele on the Y requires that $\gamma_{i}>0$ where $\gamma_{(A)}=w_{a}^{\male}(2(1-\alpha^{\male})w_{Aa}^{\male} \Phi + w_{aa}^{\male} \Psi)-w_{A}^{\male}(2\alpha^{\male}w_{Aa}^{\male} \Phi + w_{aa}^{\male} \Psi)$ for equilibrium $(A)$ and $\gamma_{(B)}=2(1-\alpha^{\male})w_{a}^{\male}w_{Aa}^{\male}-w_{A}^{\male}w_{AA}^{\male}$ for equilibrium $(B)$.
-Stability of a polymorphism on the X chromosome (equilibrium $A$) further requires that $\Phi >0$ and $\Psi >0$. 
-Fixation of the $a$ allele on the X (equilibrium ($B$)) is mutually exclusive with equilibrium $(A)$ and requires $\Psi<0$ and $w_{A}^{\female}w_{AA}^{\female}>(1-\alpha^{\female})w_{a}^{\female}w_{Aa}^{\female}$.
+Substituting in $p_{X}^{\female} = \hat{p}_{X}^{\female}$ from above, fixation of the $A$ allele on the Y requires that $\gamma_{i}>0$ where $\gamma_{(A)}=w_{a}^{\male}(2(1-\alpha^{\male})w_{Aa}^{\male} \phi + w_{aa}^{\male} \psi)-w_{A}^{\male}(2\alpha^{\male}w_{Aa}^{\male} \phi + w_{aa}^{\male} \psi)$ for equilibrium $(A)$ and $\gamma_{(B)}=2(1-\alpha^{\male})w_{a}^{\male}w_{Aa}^{\male}-w_{A}^{\male}w_{AA}^{\male}$ for equilibrium $(B)$.
+Stability of a polymorphism on the X chromosome (equilibrium $A$) further requires that $\phi >0$ and $\psi >0$. 
+Fixation of the $a$ allele on the X (equilibrium ($B$)) is mutually exclusive with equilibrium $(A)$ and requires $\psi<0$ and $w_{A}^{\female}w_{AA}^{\female}>(1-\alpha^{\female})w_{a}^{\female}w_{Aa}^{\female}$.
 
@@
 
-\subsubsection*{Recombination weak relative to selection (tight linkage)}
-
-Here, we give the conditions under which a neo-W invades an XY system assuming that the \textbf{A} locus is initially in close linkage with the ancestral sex-determining region ($r \approx 0$). 
+\subsubsection*{Recombination weak relative to selection (tight linkage between \textbf{A} and \textbf{X})}
+
+Here, we explore the conditions under which a neo-W invades an XY system assuming that the \textbf{A} locus is initially in close linkage with the ancestral sex-determining region ($r \approx 0$). 
 We disregard neo-Y mutations, which never spread given that the ancestral population is at a stable equilibrium. 
@@
 
+\noindent
+In this case, the zygotic sex ratio ($\zeta$) is given by the difference in haploid selection in males on $a$ (fixed on the Y) and $A$ (fixed on the X) alleles, i.e., there are more males than females ($\zeta<1/2$) if $\alpha^\male<1/2$ and/or $w_{a}^\male>w_{A}^\male$.
+Populations with a male biased zygotic sex ratio are more permissive to invasion by a neo-W ($\lambda_{mA}$ and $\lambda_{ma}$ larger).
+%In addition, the spread of neo-W alleles depends on the fitness of female diploids after mating with an X-$A$ or Y-$a$ male gamete, relative to the fitness of females in the population (all have genotype $AA$ and fitness $w_{AA}^\female$ at this equilibrium).
+In addition, the spread rate of neo-W haplotypes is determined by their fitness in females. 
+Zygotes carrying dominant neo-W alleles will develop as females regardless of their genotype at the XY locus. Therefore, females result from matings with either X-$A$ or Y-$a$ male gametes. 
+The relative proportion of these male gametes is also determined by haploid selection in males; mating with a Y-$a$ male gamete is more likely if the $a$ allele is favoured during male gamete production or competition ($\alpha^\male<1/2$ and/or $w_{a}^\male>w_{A}^\male$).
+
+Furthermore, haploid selection in females can directly select upon neo-W-$A$ or neo-W-$a$ haplotypes. 
+An $A$-bearing female gamete has the same fitness during haploid competition as the resident $A$-bearing female gametes. 
+On the other hand, $a$-bearing female gametes can be favoured or disfavoured during female haploid competition (favoured if $w_{a}^\female>w_{A}^\female$). 
+Meiotic drive in females ($\alpha^\female$) similarly affects the fitness of these haplotypes, except that meiotic drive only occurs in heterozygotes.
+
+The other terms in equations \eqref{Binvasion} are more easily interpreted if we assume that there is no haploid selection in either sex, in which case $\lambda_{mA}>1$ when $w_{Aa}^\female>w_{AA}^\female$ and $\lambda_{ma}>1$ when $(w_{Aa}^\female+w_{aa}^\female)/2>w_{AA}^\female$.
+These conditions cannot be met under purely sexually antagonistic selection, where $a$ is directionally favoured in males ($w_{AA}^\male>w_{Aa}^\male>w_{aa}^\male$) and $A$ is directionally favoured in females ($w_{AA}^\female>w_{Aa}^\female>w_{aa}^\female$).
+Essentially, the X is already as specialized as possible for the female beneficial allele (X-A is fixed), and the neo-W often makes daughters with the Y-a haplotype, increasing the flow of $a$ alleles into females, which reduces the fitness of those females.
+
+If selection doesn't uniformly favour $A$ in females, however, neo-W-$A$ haplotypes and/or neo-W-$a$ haplotypes can spread at this equilibium.
+If $\lambda_{mA}>1$ (requiring $w_{Aa}^\female>w_{AA}^\female$), the implication is that $a$ is favoured by selection in females despite $A$ being fixed on the X, which must require that X-$A$ is sufficiently favoured in males to drive the frequency of X-$A$ to one (specifically, from the stability conditions, we must have $w_{Aa}^\male/((w_{aa}^\male+w_{Aa}^\male)/2)>w_{Aa}^\female/w_{AA}^\female$).
+
+Even if $w_{Aa}^\female>w_{AA}^\female$, the neo-W can spread alongside the $a$ allele ($\lambda_{ma}>1$) if there is sufficiently strong underdominance in females ($w_{aa}^\female>w_{Aa}^\female$), such that $(w_{Aa}^\female+w_{aa}^\female)/2>w_{AA}^\female$.
+In this case, $a$ is not favored in females near the equilibrium where females are $AA$ (comparing $Aa$ to $AA$ genotypes) and yet the neo-W with $a$ can spread because it produces female $aa$ individuals by capturing Y-$a$ haplotypes.
+
 %\textcolor{red}{the versions for equil $(A)$ are not terrible but could be improved by cleverly re-writing with the $\phi$ and $\psi$ terms from above, I think...}
@@
 This gives
+
+\begin{subequations}\label{Ainvasion}
+\begin{align}
+\lambda_{mA}&= \frac{a}{b} \left[w_{AA}^\female w_{Aa}^\male w_A^\male \alpha^\male \phi + 2 w_{Aa}^\female \alpha^\female w_a^\male \frac{c}{d}\right] / w_a^\female \\
+\lambda_{ma}&= \frac{a}{b} \left[2 w_{Aa}^\female (1-\alpha^\female) w_{Aa}^\male w_A^\male \alpha^\male \phi+  w_{aa}^\female w_a^\male \frac{c}{d}\right] / w_A^\female \\
+\rho_{mA}&= \frac{a}{b} R \left[ 2 w_{Aa}^\female \alpha^\female w_a^\male \frac{c}{d} \right] / w_a^\female\\ 
+\rho_{ma}&= \frac{a}{b} R \left[ 2 w_{Aa}^\female (1-\alpha^\female) w_{Aa}^\male w_A^\male \alpha^\male \phi \right] / w_A^\female
+\end{align}
+\end{subequations}
+
+\noindent
+where
+
+\begin{subequations}
+\begin{align}
+a &= w_a^\female \phi + w_A^\female \psi \\
+b &= w_{AA}^\female \phi (2 w_{Aa}^\male w_A^\male \alpha_\male \phi) + w_{Aa}^\female \psi (2 w_{Aa}^\male w_A^\male \alpha_\male \phi + w_{AA}^\male w_a^\male \psi) + w_{aa}^\female \psi(w_{AA}^\male w_a^\male \psi) \\
+c &= 2(w_{Aa}^\male\phi)^2(1-\alpha^\male)\alpha_\male + w_{Aa}^\male\phi(w_{AA}^\male \psi + w_{aa}^\male \psi \alpha^\male) + w_{aa}^\male \psi w_{AA}^\male \psi \\
+d &= 2 w_{Aa}^\male \alpha^\male \phi + w_{aa}^\male \psi
+\end{align}
+\end{subequations}
+
+\noindent
+Without haploid selection $\lambda_{mA}>1$ if and only if
+
+\begin{equation}
+2(w_{Aa}^\female-w_{aa}^\female)w_{AA}^\male \psi^2 > (w_{AA}^\female-w_{Aa}^\female)w_{Aa}^\male \phi (\phi-\psi)
+\end{equation}
+
+\noindent
+NOTES:  
+$\phi-\psi=w_{AA}^\female w_{Aa}^\male-w_{aa}^\female w_{aa}^\male$ and both $\phi$ and $\psi$ are positive by the equilibrium conditions. 
+Most important advance on the descriptions given for the (B) equilibrium is that this can be met with `purely' sexually antagonistic selection (directional but opposite in both sexes). 
+Basically, because W-A haplotypes never produce $aa$ females, that can be an advantage, even though they also produce a lot of $Aa$ females through obtaining the $a$ from Y-gametes. 
+Can be seen from the fact that the condition will be more easily met if there is a large benefit from never producing $aa$ females (LHS larger, although note that $w_{Aa}^\female$ and $w_{aa}^\female$ enter into $\phi$ and $\psi$ terms too).
+Even if $R\neq 0$, there can be invasion with purely sexually antagonistic selection.
+
+Without haploid selection $\lambda_{ma}>1$ if and only if
+
+\begin{equation}
+w_{Aa}^\male \phi^2(w_{aa}^\female + w_{Aa}^\female-2w_{AA}^\female) + (w_{aa}^\female-w_{Aa}^\female)(w_{Aa}^\male+2w_{AA}^\male) \phi \psi >0
+\end{equation}
+
+\noindent
+NOTES: Not met with purely sexually antagonistic selection but met in some other circumstances.
+
+%Without haploid selection this reduces to
+%\begin{subequations}
+%\begin{align}
+%\lambda_{mA}&= \frac{a}{b} \left[w_{AA}^\female w_{Aa}^\male \phi / 2 + w_{Aa}^\female \frac{c}{d}\right]  \\
+%\lambda_{ma}&= \frac{a}{b} \left[w_{Aa}^\female w_{Aa}^\male \phi / 2 +  w_{aa}^\female \frac{c}{d}\right] \\
+%\rho_{mA}&= \frac{a}{b} R \left[ w_{Aa}^\female \frac{c}{d} \right] \\ 
+%\rho_{ma}&= \frac{a}{b} R \left[ w_{Aa}^\female w_{Aa}^\male \phi / 2 \right] 
+%\end{align}
+%\end{subequations}
+
 %These simplify considerably when there is no haploid selection:
 %
-%%\begin{subequations}
-%%\begin{align}
-%%\lambda_{mA}&= \frac{(\phi + \psi)[(w_{AA}^\female + w_{Aa}^\female ) w_{Aa}^\male \phi + 2 w_{Aa}^\female w_{AA}^\male \psi ]}{2 (w_{AA}^\female w_{Aa}^\male \phi^2 + \psi(w_{Aa}^\female(w_{AA}^\male + w_{Aa}^\male)\phi + w_{aa}^\female w_{AA}^\male \psi)}\\
-%%\lambda_{ma}&=  \frac{(\phi + \psi)[(w_{aa}^\female + w_{Aa}^\female ) w_{Aa}^\male \phi + 2 w_{aa}^\female w_{AA}^\male \psi ]}{2 (w_{AA}^\female w_{Aa}^\male \phi^2 + \psi(w_{Aa}^\female(w_{AA}^\male + w_{Aa}^\male)\phi + w_{aa}^\female w_{AA}^\male \psi)}\\
-%%\rho_{mA}&= R \frac{(\phi + \psi) w_{Aa}^\female w_{AA}^\male}{2 (w_{AA}^\female w_{Aa}^\male \phi^2 + \psi(w_{Aa}^\female(w_{AA}^\male + w_{Aa}^\male)\phi + w_{aa}^\female w_{AA}^\male \psi)} \\ 
-%%\rho_{ma}&= R \frac{(\phi + \psi) w_{Aa}^\female w_{Aa}^\male}{2 (w_{AA}^\female w_{Aa}^\male \phi^2 + \psi(w_{Aa}^\female(w_{AA}^\male + w_{Aa}^\male)\phi + w_{aa}^\female w_{AA}^\male \psi)}\\
-%%\end{align}
-%%\end{subequations}
+%\begin{subequations}
+%\begin{align}
+%\lambda_{mA}&= \frac{(\phi + \psi)[(w_{AA}^\female + w_{Aa}^\female ) w_{Aa}^\male \phi + 2 w_{Aa}^\female w_{AA}^\male \psi ]}{2 (w_{AA}^\female w_{Aa}^\male \phi^2 + \psi(w_{Aa}^\female(w_{AA}^\male + w_{Aa}^\male)\phi + w_{aa}^\female w_{AA}^\male \psi)}\\
+%\lambda_{ma}&=  \frac{(\phi + \psi)[(w_{aa}^\female + w_{Aa}^\female ) w_{Aa}^\male \phi + 2 w_{aa}^\female w_{AA}^\male \psi ]}{2 (w_{AA}^\female w_{Aa}^\male \phi^2 + \psi(w_{Aa}^\female(w_{AA}^\male + w_{Aa}^\male)\phi + w_{aa}^\female w_{AA}^\male \psi)}\\
+%\rho_{mA}&= R \frac{(\phi + \psi) w_{Aa}^\female w_{AA}^\male}{2 (w_{AA}^\female w_{Aa}^\male \phi^2 + \psi(w_{Aa}^\female(w_{AA}^\male + w_{Aa}^\male)\phi + w_{aa}^\female w_{AA}^\male \psi)} \\ 
+%\rho_{ma}&= R \frac{(\phi + \psi) w_{Aa}^\female w_{Aa}^\male}{2 (w_{AA}^\female w_{Aa}^\male \phi^2 + \psi(w_{Aa}^\female(w_{AA}^\male + w_{Aa}^\male)\phi + w_{aa}^\female w_{AA}^\male \psi)}\\
+%\end{align}
+%\end{subequations}
 %
@@
 %\end{subequations}
-%
 %\noindent
@@
 %$c = \frac{\phi + \psi}{2 [w_{AA}^\female w_{Aa}^\male \phi^2 + \psi(w_{Aa}^\female(w_{AA}^\male + w_{Aa}^\male)\phi + w_{aa}^\female w_{AA}^\male \psi]}$ and $\phi$ and $\psi$ are evaluated with $\alpha^{\Hermaphrodite}=1/2$ and $w_a^\Hermaphrodite=w_A^\Hermaphrodite=1$.
-%
-%With haploid selection we have
-
-\begin{subequations}\label{Ainvasion}
-\begin{align}
-\lambda_{mA}&= \frac{a}{b} \left[w_{AA}^\female w_{Aa}^\male w_A^\male \alpha^\male \phi + 2 w_{Aa}^\female \alpha^\female w_a^\male \frac{c}{d}\right] / w_a^\female \\
-\lambda_{ma}&= \frac{a}{b} \left[2 w_{Aa}^\female (1-\alpha^\female) w_{Aa}^\male w_A^\male \alpha^\male \phi+  w_{aa}^\female w_a^\male \frac{c}{d}\right] / w_A^\female \\
-\rho_{mA}&= \frac{a}{b} R \left[ 2 w_{Aa}^\female \alpha^\female w_a^\male \frac{c}{d} \right] / w_a^\female\\ 
-\rho_{ma}&= \frac{a}{b} R \left[ 2 w_{Aa}^\female (1-\alpha^\female) w_{Aa}^\male w_A^\male \alpha^\male \phi \right] / w_A^\female
-\end{align}
-\end{subequations}
-
-\noindent
-where
-
-\begin{subequations}
-\begin{align}
-a &= w_a^\female \phi + w_A^\female \psi \\
-b &= w_{AA}^\female \phi (2 w_{Aa}^\male w_A^\male \alpha_\male \phi) + w_{Aa}^\female \psi (2 w_{Aa}^\male w_A^\male \alpha_\male \phi + w_{AA}^\male w_a^\male \psi) + w_{aa}^\female \psi(w_{AA}^\male w_a^\male \psi) \\
-c &= 2(w_{Aa}^\male\phi)^2(1-\alpha^\male)\alpha_\male + w_{Aa}^\male\phi(w_{AA}^\male \psi + w_{aa}^\male \psi \alpha^\male) + w_{aa}^\male \psi w_{AA}^\male \psi \\
-d &= 2 w_{Aa}^\male \alpha^\male \phi + w_{aa}^\male \psi
-\end{align}
-\end{subequations}
-
-%Without haploid selection this reduces to
-%
-%\begin{subequations}
-%\begin{align}
-%\lambda_{mA}&= \frac{a}{b} \left[w_{AA}^\female w_{Aa}^\male \phi / 2 + w_{Aa}^\female \frac{c}{d}\right]  \\
-%\lambda_{ma}&= \frac{a}{b} \left[w_{Aa}^\female w_{Aa}^\male \phi / 2 +  w_{aa}^\female \frac{c}{d}\right] \\
-%\rho_{mA}&= \frac{a}{b} R \left[ w_{Aa}^\female \frac{c}{d} \right] \\ 
-%\rho_{ma}&= \frac{a}{b} R \left[ w_{Aa}^\female w_{Aa}^\male \phi / 2 \right] 
-%\end{align}
-%\end{subequations}
 

### 2017-05-23 LaTeX/Turnover.tex
added otto 2014 fig 3 panel to fig s.1" git commit -m "added otto 2014 fig 3 panel to fig s.1"

@@
 
+...
+this holds for moderate amounts of recombination between the neo-W and the selected locus, $0<R<<1$, indicating that, contrary to the conclusions of \cite{vanDoorn:2010hu}, neo sex chromosomes that reduce linkage with selected loci can invade.
+
 \subsubsection*{Loose linkage with the ancestral sex-determining region}
@@
 As with offspring-controlled ESD, for all $k\in\{0,1/2,1\}$, we find that invasion into an ancestrally XY system is the same as invasion into an ancestrally ZW system (at least up to order $\epsilon^3$, assuming weak selection), implying transitions between genetic sex determination and maternally controlled environmental sex determination are not driven by Fisherian sex ratio selection on biased zygotic sex ratios.
+\textcolor{red}{(maternal analysis still lacks meiotic drive)}
 
@@
 
-Figure \ref{fig:Region_Plot_2a} shows that both the sex-specialist and perverse hypotheses are valid.
-In fact, both can be simultaneously valid, which is generally where there is selection for increased recombination between the sex chromosomes \citep[][figure 2a]{Otto2014}.
+Figure \ref{fig:Region_Plots} shows where the sex-specialist (red) and perverse (blue) hypotheses are valid.
+The left panel demonstrates that both hypotheses can be simultaneously valid with overdominance in both sexes and sex differences in selection, which is also where there is selection for increased recombination between the sex chromosomes \citep[compare with figure 2(a) in][]{Otto2014}.
+The right panel shows that the perverse hypothesis is no longer valid when selection is exactly the same in both sexes, despite the fact that there is selection for increased recombination between the sex chromosomes with sufficiently strong overdominance \citep[compare with figure 3 in][]{Otto2014}.
 
@@
 \centering
-\includegraphics[width=0.5\linewidth]{regionplot_2a}\\
+\includegraphics[width=0.45\linewidth]{regionplot_2a}
+\includegraphics[width=0.45\linewidth]{regionplot_3}\\
 \caption{
-Colours indicate where sex-specialist (red) and perverse (blue) hypotheses are valid, i.e., where a stable resident equilibrium is invaded by a neo-W that is perfectly linked with the allele not fixed on the Y (red) or the allele that is fixed on the Y (blue).
-Note that the perverse equilibrium is only valid with overdominance and that both are simultaneously valid over much of the parameter space where increased recombination between the sex chromosomes is selected \citep[][figure 2a]{Otto2014}.
-\textcolor{red}{can't make sex symbols in mathematica!}
+Numerical exploration of where sex-specialist (red) and perverse (blue) hypotheses are valid, i.e., where an internally stable resident equilibrium can be invaded by a neo-W that is perfectly linked with the allele not fixed on the Y (red) or the allele that is fixed on the Y (blue).
+\textbf{(Left)}
+The perverse equilibrium is only valid with overdominance while the sex-specialist hypothesis is valid over the entire range shown.
+Both hypotheses are simultaneously valid over much of the parameter space where increased recombination between the sex chromosomes is selected \citep[][figure 2a]{Otto2014}.
+\textbf{(Right)}
+Only the sex-specialist hypothesis is valid with no sex-differences in selection, despite selection for increased recombination between the sex-chromosomes with strong overdominance \citep[][figure 3]{Otto2014}.
+Parameters: $w_{Aa}^\Hermaphrodite = 1$, $w_a^\Hermaphrodite = w_A^\Hermaphrodite = 1$, $\alpha^\Hermaphrodite = 1/2$, $r=R=0$, and in left panel $w_{aa}^\female = w_{AA}^\female = 0.6$.
 }
-\label{fig:Region_Plot_2a}
+\label{fig:Region_Plots}
 \end{figure}

### 2017-05-24 LaTeX/Turnover.tex
small chagnes to s.1 text

@@
 Figure \ref{fig:Region_Plots} shows where the sex-specialist (red) and perverse (blue) hypotheses are valid.
-The left panel demonstrates that both hypotheses can be simultaneously valid with overdominance in both sexes and sex differences in selection, which is also where there is selection for increased recombination between the sex chromosomes \citep[compare with figure 2(a) in][]{Otto2014}.
+The left panel demonstrates that both hypotheses can be simultaneously valid with overdominance in both sexes and sex differences in selection, which overlaps the parameter region where there is selection for increased recombination between the sex chromosomes \citep[compare with figure 2a in][]{Otto2014}.
 The right panel shows that the perverse hypothesis is no longer valid when selection is exactly the same in both sexes, despite the fact that there is selection for increased recombination between the sex chromosomes with sufficiently strong overdominance \citep[compare with figure 3 in][]{Otto2014}.

### 2017-06-21 LaTeX/Turnover.tex
first draft of evol talk done

@@
 In this plot there are no sex differences in selection and an equilibrium is maintained because selection in diploids opposes meiotic drive, $s^\female =s^\male = 1/5$, $h^\female = h^\male = 7/10$.
-\textcolor{red}{Aesthetic adjustments: Could add titles to the columns/rows: neo-W for row 1, neo-Y for row 3, $r=0.5$, $R=0.05$ for column 1 and $r=0.05$, $R=0.5$ for column 2.
-Could adjust padding (too much whitespace where there is no axis label).
-It also seems could increase ratio of font size relative to plot size to make figure more compact.
-Matt - could you uncomment the line legends in the Mathematica file (function not included in my Mathematica version).}
+\textcolor{red}{Aesthetic adjustments: 
+Could add titles to the columns/rows: neo-W for row 1, neo-Y for row 3, $r=0.5$, $R=0.05$ for column 1 and $r=0.05$, $R=0.5$ for column 2. 
+%Could adjust padding (too much whitespace where there is no axis label). 
+%It also seems could increase ratio of font size relative to plot size to make figure more compact. 
+%Matt - could you uncomment the line legends in the Mathematica file (function not included in my Mathematica version).
+}
 }
@@
 Could add titles to the columns/rows: neo-W for row 1, neo-Y for row 3, $r=0.5$, $R=0.05$ for column 1 and $r=0.05$, $R=0.5$ for column 2. 
-\& possibly adjust padding (too much whitespace?).
-Matt - could you uncomment the line legends in the Mathematica file (function not included in my Mathematica version).}
+%\& possibly adjust padding (too much whitespace?). 
+%Matt - could you uncomment the line legends in the Mathematica file (function not included in my Mathematica version).
+}
 }
@@
 A polymorphism can then be maintained by opposing selection between the haploid and diploid phases. 
-In B, there is drive in favour of the $a$ allele in males ($\alpha^\male_{\Delta}=-1/10$), no female meiotic drive or gametic competition, $t^\Hermaphrodite=\alpha^\female_{\Delta}=0$), and equal selection in diploid sexes ($s^\female=s^\male=1/10$, $h^\female=h^\male=7/10$).
+In B, there is drive in favour of the $a$ allele in males ($\alpha^\male_{\Delta}=-1/5$), no female meiotic drive or gametic competition, $t^\Hermaphrodite=\alpha^\female_{\Delta}=0$), and equal selection in diploid sexes ($s^\female=s^\male=1/5$, $h^\female=h^\male=7/10$).
 In this case, a neo-W can invade even when the selected locus is more closely linked to the ancestral sex determining locus (see Table \ref{tab:specialcases} and Figure \ref{fig:Combination_Turnover}).
@@
 In this case, the neo-W does not invade if $s^\female>s^\male$ (panel C: $s^\female=3/20$, $s^\male=1/20$) but does if $s^\female<s^\male$ (panel D: $s^\female=1/20$, $s^\male=3/20$), see Table \ref{tab:specialcases}.
-\textcolor{red}{I suspect that panel C has a region where no equilibrium is maintained (CHECK!
-Maybe include different parameters here or remove the part when no equilibrium).
-Currently use different parameters for B than using in figure \ref{fig:Combination_Turnover} (selection/drive twice as strong in turnover figure).
+\textcolor{red}{
+I suspect that panel C has a region where no equilibrium is maintained (CHECK! Maybe include different parameters here or remove the part when no equilibrium). 
+%Currently use different parameters for B than using in figure \ref{fig:Combination_Turnover} (selection/drive twice as strong in turnover figure). 
 This plot would also benefit from titles giving, e.g., ``sexually-antagonistic selection, $s^\female s^\male<0$'' for A, ``male meiotic drive, $s^\female s^\male>0$'' for B}

### 2017-07-04 LaTeX/Turnover.tex
tight linkage in appendix and main text, figure 1 updated to sal's liking, sex ratio selection discussion softened

@@
 
+\usepackage{tikz}%for putting words on figures
+\usetikzlibrary{positioning}%for relative positioning
+
 \begin{document}
 
-\title{Gametic Selection, Meiotic Drive, Sex Ratio Bias, and Transitions Between Sex Determination Systems}
+\title{Gametic Selection, Meiotic Drive, Sex Ratio Bias, and Transitions Between sex-determination systems}
 \author{Michael F Scott$*^1$, Matthew M Osmond$*^2$, and Sarah P Otto$^2$}
@@
 \begin{abstract}
-Sex determination systems are remarkably dynamic; many studied taxa display transitions of sex-determining genes between chromosomes or the evolution of entirely new sex-determining systems. 
-Predominant theories in which new sex-determining systems are favoured by selection 
-%involve sex ratio selection or sex-specific selection (e.g., sexually antagonistic selection).
+Sex-determination systems are remarkably dynamic; many taxa display shifts in the location of sex-determining loci or the evolution of entirely new sex-determining systems. 
+Predominant theories for why we observe such transitions %in which new sex-determining systems spread by selection 
+%involve sex-ratio selection or sex-specific selection (e.g., sexually antagonistic selection).
 %These studies 
-generally conclude that that novel sex determination systems are favoured if they equalise the sex ratio or increase linkage between the sex-determining region and a sexually-antagonistic locus. 
+generally conclude that novel sex-determining systems are favoured by selection if they equalise the sex ratio or increase linkage with a sexually-antagonistic locus. 
 We use population genetic models to extend these theories in two ways: 
 (1) We explicitly consider how selection on very tightly sex-linked loci influences the spread of novel sex-determiners. 
-We find that tightly sex-linked genetic variation can favour the spread of new sex-determination systems in which the heterogametic sex changes (XY to ZW or ZW to XY) and the new sex-determining region is less closely linked (or unlinked) to the sex linked locus under selection; a result that is not found with loose sex-linkage.
+We find that tightly sex-linked genetic variation can favour the spread of new sex-determination systems in which the heterogametic sex changes (XY to ZW or ZW to XY) and the new sex-determining region is less closely linked (or unlinked) to the sex-linked locus under selection; a result that is not found with loose sex-linkage.
 %With tight linkage, selection can maintain equilibria at which the allele fixed on the sex-limited chromosome (Y or W) is simultaneously favoured in the homogametic sex (XX females or ZZ males) such that heterogametic transitions (XY to ZW or ZW to XY) are favoured by selection.
@@
 %In addition, when there is haploid selection, we find 
-that transitions between male and female heterogamety (XY to ZW or ZW to XY) can occur even if the new sex-determining region is less closely linked to the locus under selection. 
+that transitions between male and female heterogamety can occur even if the new sex-determining region is less closely linked to the locus under selection. 
 That is, favourable associations that develop between the ancestral sex-determining locus and selected loci can be broken during the spread of a new sex-determining region. 
 %Such transitions are not possible with diploid selection alone, in which case tighter linkage increases the fitness of both males and females. 
-%Notably, we find that the spread of new genetic sex determination systems is not affected by sex ratio biases that are caused by haploid selection. 
-%A surprising result given that other determinants of sex allocation typically experience strong Fisherian sex ratio selection to equalize sex ratios. 
+%Notably, we find that the spread of new genetic sex-determination systems is not affected by sex ratio biases that are caused by haploid selection. 
+%A surprising result given that other determinants of sex allocation typically experience strong Fisherian sex-ratio selection to equalize sex ratios. 
 %Overall, we demonstrate when and how the evolution of sex determining systems is impacted by sex ratio biases resulting from haploid selection and we show that new sex-determining regions can be favoured even if they are not closely linked with a locus under selection.
@@
 
-abstract word count: $\approx$ 350
+%abstract word count: $\approx$ 350
 
@@
 
-Animals and angiosperms exhibit extremely diverse sex determination systems \citep[reviewed in][]{Bull:1983vi,Charlesworth:2010it,Beukeboom:2014vb,Bachtrog:2014bx}. 
+Animals and angiosperms exhibit extremely diverse sex-determination systems \citep[reviewed in][]{Bull:1983vi,Charlesworth:2010it,Beukeboom:2014vb,Bachtrog:2014bx}. 
 Among species with genetic sex determination of diploid sexes, some taxa have heterogametic males (XY) and homogametic females (XX), including %non-monotreme? 
@@
 In addition, many gonochoric clades with genetic sex determination exhibit transitions between male (XY) and female (ZW) heterogamety, including lizards \citep{Ezaz:2009tk}, eight of 26 teleost fish families \citep{Mank:2006bt}, true fruit flies \citep[Tephritids,][]{Vicoso:2015hf}, amphibians \citep{Hillis:1990gu}, the angiosperm genus \textit{Silene} \citep{Slancarova:2013dq}, and Coleoptera and Hemiptera \citep[][plate 2]{Beukeboom:2014vb}.
-Indeed, in some cases, both male and female heterogametic sex determination systems can be found in the same species, as exhibited by some cichlid species \citep{Ser:2010iq} and \textit{Rana rugosa} \citep{Ogata:2007jm}.
-In addition, multiple transitions have occurred between genetic and environmental sex determination systems, e.g., in reptiles and fishes \citep{Conover:1987in,Mank:2006bt,Pokorna:2009ui,Ezaz:2009tk,Pen:2010kk,Holleley:2015hc}.
+Indeed, in some cases, both male and female heterogametic sex-determination systems can be found in the same species, as exhibited by some cichlid species \citep{Ser:2010iq} and \textit{Rana rugosa} \citep{Ogata:2007jm}.
+In addition, multiple transitions have occurred between genetic and environmental sex-determination systems, e.g., in reptiles and fishes \citep{Conover:1987in,Mank:2006bt,Pokorna:2009ui,Ezaz:2009tk,Pen:2010kk,Holleley:2015hc}.
 
@@
 
-Predominant theories in accounting for the spread of new sex determination systems by selection involve fitness differences between sexes (e.g., sexually antagonistic selection) or sex ratio selection.
+Predominant theories accounting for the spread of new sex-determination systems by selection involve fitness differences between sexes (e.g., sexually antagonistic selection) or sex-ratio selection. 
 %\citet{Bull:1977wt} shows that direct selection on new sex determination loci can allow them to spread and switch between male and female heterogamety. 
 \citet{vanDoorn:2007eu,vanDoorn:2010hu} show that new sex-determining loci can be favoured if they arise in closer linkage with a locus that experiences sexual antagonism. 
-For example, linkage allows favourable associations to build up between a male-beneficial allele and a neo-Y chromosome. 
+For example, tighter linkage allows a stronger favourable association to build up between a male-beneficial allele and a neo-Y chromosome. 
 Such associations can favour a new master sex-determining gene on a new chromosome \citep{vanDoorn:2007eu} and can also favour a transition between male and female heterogamety \citep[e.g., a ZW to XY transition,][]{vanDoorn:2010hu}.
 However, any sexually-antagonistic loci that are more closely linked to the ancestral sex-determination locus will develop similar, favourable associations and select against the spread of a new sex-determination system.
-Here we extend these studies by explictly calculating the the equilibrium allele frequencies of loci that are very tightly linked to the ancestral sex-determining region.
-
-The sex ratio is directly affected by the sex determination system, it has therefore been suggested that sex ratio selection is a dominant force in the evolution of sex determination (e.g., \citealt{Bull:1983vi}, p66-67; \citealt{Beukeboom:2014vb}, Chapter 7).
-`Fisherian' sex ratio selection favours a 1:1 zygotic sex ratio when assuming that males and females are equally costly to produce \citep{Fisher:1930wy,Charnov:1982wg}.
+%Here we extend these studies by explicitly calculating the the equilibrium allele frequencies of loci that are very tightly linked to the ancestral sex-determining region.
+
+The sex ratio is directly affected by the sex-determination system, and it has therefore been suggested that sex-ratio selection is a dominant force in the evolution of sex determination (e.g., \citealt{Bull:1983vi}, p66-67; \citealt{Beukeboom:2014vb}, Chapter 7).
+`Fisherian' sex-ratio selection favours a 1:1 zygotic sex ratio when assuming that males and females are equally costly to produce \citep{Fisher:1930wy,Charnov:1982wg}.
 This follows from the fact that, for an autosomal locus, half of the genetic material is inherited from a male, and half from a female \citep{West:2009we}. 
@@
 Therefore, a mutant that increases investment in males (e.g., increases the proportion of males produced) will spread via the higher per-individual contributions made by males. 
-%The default mode of sex ratio selection is `Fisherian' sex ratio selection, which favours equal investment in male and female offspring \citep[i.e., a 1:1 zygotic sex ratio when assuming that males and females are equally costly to produce,][]{Fisher:1930wy,Charnov:1982wg}.
-%Given that the sex determination system can directly affect the sex ratio, we might expect Fisherian sex ratio selection to influence the spread of new sex determination systems. 
+%The default mode of sex-ratio selection is `Fisherian' sex-ratio selection, which favours equal investment in male and female offspring \citep[i.e., a 1:1 zygotic sex ratio when assuming that males and females are equally costly to produce,][]{Fisher:1930wy,Charnov:1982wg}.
+%Given that the sex-determination system can directly affect the sex ratio, we might expect Fisherian sex-ratio selection to influence the spread of new sex-determination systems. 
 In the case of sex-chromosome evolution, \citet{Kozielska:2010vm} consider systems in which the ancestral sex chromosomes experience meiotic drive (e.g., where driving X or Y chromosomes are inherited disproportionately often), which causes sex ratios to become biased \citep{Hamilton:1967ts}.
@@
 %\textcolor{red}{We add haploid selection:}
-Here, we use mathematical models to find the conditions under which new sex determination systems are favoured when loci experience haploid selection. 
+Here we extend current theory %on turnover between sex-determining systems 
+by using mathematical models to find the conditions under which new sex-determination systems spread when individuals experience selection at both diploid and haploid stages. 
 Haploid genotypes at many loci experience selection during gamete competition and/or meiotic drive \citep{Mulcahy:1996ha,JOSEPH:2004haa}.
@@
 
-There are various ways in which a period of haploid selection could influence transitions between sex determination systems. 
+There are various ways in which a period of haploid selection could influence transitions between sex-determination systems. 
 If we assume that haploid selection at any particular locus predominantly occurs in one sex (e.g., meiotic drive during spermatogenesis), then such loci experience a form of sex-specific selection. 
-In this respect, we might expect that haploid selection would affect transitions between sex determination systems in a similar manner to sex-specific diploid selection \citep[as explored by][]{vanDoorn:2007eu,vanDoorn:2010hu}.
-That is, new masculizing mutations (neo-Y chromosomes) could be favoured via associations with alleles that are beneficial in the male haploid stage. 
+In this respect, we might expect that haploid selection to affect transitions between sex-determination systems in a similar manner to sex-specific diploid selection \citep[as explored by][]{vanDoorn:2007eu,vanDoorn:2010hu}.
+That is, new masculinizing mutations (neo-Y chromosomes) could be favoured via associations with alleles that are beneficial in the male haploid stage. 
 However, sex ratios can also become biased by linkage between the sex-determining region and a locus that harbours genetic variation in haploid fitness. 
-For example, there are several known cases of sex ratio bias caused by sex-linked meiotic drive alleles \citep[][Chapter 3]{Burt:2006} or selection among X- and Y-bearing pollen \citep{Lloyd:1974tz,Conn:1981uw,Stehlik:2005ul,Stehlik:2006to,Field:2012fd,Field:2013cc}.
-It is not immediately clear how the spread of new sex determination systems would be influenced by the combination of sex ratio biases and associations between haploid selected loci and sex-determining regions.
-
-Our models tracking the spread of new sex determination systems therefore have two important new features. 
-Firstly, we consider loci that are under selection and also in very tight linkage with the ancestral sex-determining region. 
+For example, there are several known cases of sex-ratio bias caused by sex-linked meiotic drive alleles \citep[][Chapter 3]{Burt:2006} or selection among X- and Y-bearing pollen \citep{Lloyd:1974tz,Conn:1981uw,Stehlik:2005ul,Stehlik:2006to,Field:2012fd,Field:2013cc}.
+It is not immediately clear how the spread of new sex-determination systems would be influenced by the combination of sex-ratio biases and associations between haploid selected loci and sex-determining regions.
+
+Our models have two important new features. 
+Firstly, when considering loci that are under selection and also in very tight linkage with the ancestral sex-determining region we explicitly calculate equilibrium allele frequencies.
+This allows us to show that transitions between male and female heterogamety can evolve even when the neo-sex-determining locus is less closely linked to a locus under selection and therefore disrupts favourable ancestral associations between sex and the alleles selected in that sex.
+%Such transitions are not favoured in models lacking tight linkage and/or haploid selection. 
 Secondly, we allow sex-specific haploid selection to occur on a locus in tight or loose linkage with the ancestral sex-determining region. 
-We find that sex ratio biases caused by haploid selection can exert Fisherian sex ratio selection upon novel sex-determiners but that their spread is also determined by the fitness of the alleles that are associated with them.
-Indeed, it is only when haploid selected loci are tightly linked to the ancestral sex-determining region (and so sex ratio biases are initially large) that we see an asymmetry between selection for XY to ZW transitions and ZW to XY transitions, e.g., because haploid selection in males only causes biased zygotic sex ratios in an ancestrally XY system.
+We find that sex-ratio biases caused by haploid selection can exert Fisherian sex-ratio selection upon novel sex-determiners but that their spread is also determined by the fitness of the alleles that are associated with them.
+Indeed, it is only when haploid-selected loci are tightly linked to the ancestral sex-determining region (and so sex-ratio biases are initially large) that we see an asymmetry between selection for XY to ZW transitions and ZW to XY transitions (e.g., because haploid selection in males only causes biased zygotic sex ratios in an ancestrally XY system).
+It is also possible for selection on linked alleles to drive turnover between sex-determining systems despite causing transitory or even permanent increases in sex-ratio bias. 
 %In addition, when linkage between the ancestral sex-determining locus and a locus under haploid selection is tight, sex ratio biases can be strong such that there is an asymmetry between invasion of ancestrally XY and ancestrally ZW systems because, e.g., haploid selection in males only causes biased zygotic sex ratios in an ancestrally XY system.
-In addition, we show that transitions between male and female heterogamety can evolve even when the neo-sex-determining locus is less closely linked to a locus under selection and therefore disrupts favourable ancestral associations between sex and the alleles selected in that sex.
-Such transitions are not favoured in models lacking tight linkage and/or haploid selection.
 
@@
 %genetic system
-We consider the transition between ancestral and novel sex determination systems using a three locus model. 
+We consider transitions between ancestral and novel sex-determining systems using a three locus model, each locus having two alleles. 
 Locus \textbf{X} is the ancestral sex-determining region, with alleles $X$ and $Y$ (or $Z$ and $W$).
@@
 With $k=0$, the $m$ allele is a masculinizer (i.e., a neo-Y) and with $k=1$ the $m$ allele is a feminizer (i.e., a neo-W).
-With intermediate $k$, the $m$ allele confers environmental sex determination (ESD) such that zygotes develop as females in a proportion ($k$) of the environments they (randomly) experience. 
-Finally, we also analyze a model of maternally-controlled environmental sex-determination, where mothers with at least one $m$ allele produce daughters with probability $k$.
+With intermediate $k$, we can interpret $m$ as an environmental sex determination (ESD) allele, such that zygotes develop as females in a proportion ($k$) of the environments they (randomly) experience.
+We also analyze a model of maternally-controlled environmental sex-determination, where mothers with at least one $m$ allele produce daughters with probability $k$.
 
@@
 We assume that all gametes compete for fertilization during gametic competition, which is not the case for monogamous mating systems where gametes from only one mating partner are present. 
-Gametic competition in monogamous mating systems is equivalent to meiotic drive in our model, which only alters the frequency of gametes produced by heterozygotes. 
+Gametic competition in monogamous mating systems is equivalent to meiotic drive in our model (described below), which only alters the frequency of gametes produced by heterozygotes. 
 After gametic competition, random mating occurs between male and female gametes.
@@
 %Diploids compete with others of the same sex, where selection depends on the sex of the individual and its genotype at the \textbf{A} locus.
-The next generation of gametes is then produced by meiosis, during which recombination and sex-specific meiotic drive can occur. 
+The next generation of gametes is produced by meiosis, during which recombination and sex-specific meiotic drive can occur. 
 Recombination (i.e., an odd number of cross-overs) occurs between loci \textbf{X} and \textbf{A} with probability $r$, between loci \textbf{A} and \textbf{M} with probability $R$, and between loci \textbf{X} and \textbf{M} with probability $\chi$.
 Any linear order of the loci can be modelled with appropriate choices of $r$, $R$, and $\chi$ (see Table \ref{tab:chisubstitutions}). 
-Individuals that are heterozygous at the \textbf{A} locus may experience meiotic drive; $Aa$ heterozgotes of sex $\Hermaphrodite$ produce gametes bearing allele $A$ with probability $\alpha^\Hermaphrodite$.
+Individuals that are heterozygous at the \textbf{A} locus may experience meiotic drive; a gamete produced by $Aa$ heterozgotes of sex $\Hermaphrodite$ bear allele $A$ with probability $\alpha^\Hermaphrodite$.
 Thus, the \textbf{A} locus can experience sex-specific gametic competition, diploid selection, and/or meiotic drive.
@@
 
-The only asymmetry between males and females in our model is that, under the ancestral sex determination system, males develop with genotype $XY$ (or $ZZ$) and females with genotype $XX$ (or $ZW$). 
-Therefore, the model outlined above describes both ancestrally-$XY$ and ancestrally-$ZW$ sex determination systems if we relabel the two sexes as being ancestrally `heterogametic' or ancestrally `homogametic'.
+The only asymmetry between males and females in our model is that, under the ancestral sex-determination system, males develop with genotype $XY$ (or $ZZ$) and females with genotype $XX$ (or $ZW$). 
+Therefore, the model outlined above describes both ancestrally-$XY$ and ancestrally-$ZW$ sex-determination systems if we relabel the two sexes as being ancestrally `heterogametic' or ancestrally `homogametic'.
 Without loss of generality, we primarily refer to the ancestrally heterogametic sex as male and the ancestrally homogametic sex as female.
-That is, we describe an ancestral XY sex determination system but our model can easily be applied to an ancestral ZW sex determination system.
+That is, we describe an ancestral XY sex-determination system but our model is just as easily applied to an ancestral ZW sex-determination system.
 
@@
 
-The evolution of a new sex determination system requires that a rare mutant allele, $m$, at the novel sex-determining locus  increases in frequency when rare. 
+The evolution of a new sex-determination system requires that a rare mutant allele at the novel sex-determining locus, $m$, increases in frequency when rare. 
 The spread of a rare mutant $m$ at the \textbf{M} locus is determined by the leading eigenvalue, $\lambda$, of the system of eight equations describing the next generation frequency of eggs and sperm carrying the mutation, (\ref{eq:recursions}c, \ref{eq:recursions}d, \ref{eq:recursions}g, \ref{eq:recursions}h).
@@
 Furthermore, if the $m$ allele is fully epistatically dominant over the ancestral sex-determining system, phenotypes are not affected by the genotype at the ancestral sex-determining region (\textbf{X} locus).
-Thus, the invasion of rare dominant neo-Y or neo-W alleles is determined by the largest eigenvalue that solves the quadratic characteristic polynomial
+Thus, the invasion of rare dominant neo-Y or neo-W alleles is determined by the largest eigenvalue that solves a quadratic characteristic polynomial,
 $\lambda^2+ b \lambda + c =0$.
@@
 %Here, $b= - (\lambda_{mA} + \lambda_{ma})$ and $c = \lambda_{mA} \lambda_{ma} -\rho_{mA} \rho_{ma}$, where $\lambda_{mi}$ is the (multiplicative) growth rate of mutant haplotypes on background $i\in\{A,a\}$, accounting for loss due to recombination, and $\rho_{mi}$ is the rate of addition of mutant haplotypes onto background $i\in\{A,a\}$ due to recombination (see table \ref{tab:haplotype_growth}).
-Here, $b= - (\lambda_{mA} + \lambda_{ma})+(\rho_{mA} + \rho_{ma})$ and $c = (\lambda_{mA}-\rho_{mA}) (\lambda_{ma}-\rho_{ma}) -\rho_{mA} \rho_{ma}$, where $\lambda_{mi}$ is the (multiplicative) growth rate of mutant haplotypes on background $i\in\{A,a\}$, without accounting for loss due to recombination, and $\rho_{mi}$ is the rate at which mutant haplotypes on background $i\in\{A,a\}$ recombine onto the other \textbf{A} locus background in heterozygotes (see table \ref{tab:haplotype_growth}).
-The spread of the mutant $m$ allele depends on the frequency of alleles at the other two loci in the ancestral population. 
-In the ancestral population, it is convenient to follow the frequency of the $A$ allele in female gametes (eggs) from an XX female, $p^\female_X$, and in X-bearing, $p^\male_X$, and Y-bearing, $p^\male_Y$, male gametes (sperm).
+Here, $b= - (\lambda_{mA} + \lambda_{ma})+(\rho_{mA} + \rho_{ma})$ and $c = (\lambda_{mA}-\rho_{mA}) (\lambda_{ma}-\rho_{ma}) -\rho_{mA} \rho_{ma}$, where $\lambda_{mi}$ is the multiplicative growth rate of mutant haplotypes on background $i\in\{A,a\}$, without accounting for loss due to recombination, and $\rho_{mi}$ is the rate at which mutant haplotypes on background $i\in\{A,a\}$ recombine onto the other \textbf{A} locus background in heterozygotes (see table \ref{tab:haplotype_growth}).
+The $\lambda_{mi}$ and $\rho_{mi}$, and thus the spread of the mutant $m$ allele, depend on the frequency of alleles at the other two loci in the ancestral population. 
+In the ancestral population, it is convenient to follow the frequency of the $A$ allele in female gametes (eggs) from an XX female, $p^\female_X$, and in X-bearing, $p^\male_X$, and Y-bearing, $p^\male_Y$, male gametes (sperm/pollem).
 We also track the fraction of male gametes that are Y-bearing, $q$, which may deviate from $1/2$ due to meiotic drive in males.
@@
    neo-Y ($k=0$) \\ [0.5ex] \hline \noalign{\vskip 1ex}
-  $\lambda_{mA}=[1/(2 (1- \zeta))]\{p_{X}^{\female} w_{A}^{\female} w_{A}^{\male} w_{AA}^{\male} + 2(1-p_{X}^{\female}) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} \alpha^\male \}/ \{ \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \} $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\lambda_{ma}=[1/(2(1-\zeta))]\{(1-p_{X}^{\female}) w_{a}^{\female} w_{a}^{\male} w_{aa}^{\male} + 2p_{X}^{\female} w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male}(1 - \alpha^\male) \}/ \{\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \} $ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\rho_{mA}=R[1/(2(1-\zeta))] \{ 2(1-p_{X}^{\female}) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} \alpha^{\male} \}/  \{ \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \}   $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\rho_{ma}= R [1/(2(1-\zeta))] \{  2 p_{X}^{\female} w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male} (1 - \alpha^{\male}) \}/ \{ \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \}  $\\ [1ex] \hline 
+  $\lambda_{mA} = \left[ 2 (1- \zeta) \right]^{-1} \left[p_{X}^{\female} w_{A}^{\female} w_{A}^{\male} w_{AA}^{\male} + 2(1-p_{X}^{\female}) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} \alpha^\male \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right) $\\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\lambda_{ma} = \left[ 2 (1- \zeta) \right]^{-1} \left[(1-p_{X}^{\female}) w_{a}^{\female} w_{a}^{\male} w_{aa}^{\male} + 2p_{X}^{\female} w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male}(1 - \alpha^\male) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\rho_{mA} = R \left[ 2 (1- \zeta) \right]^{-1} \left[ 2(1-p_{X}^{\female}) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} \alpha^{\male} \right]/  \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right)   $\\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\rho_{ma} = R \left[ 2 (1- \zeta) \right]^{-1} \left[  2 p_{X}^{\female} w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male} (1 - \alpha^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right)  $\\ [1ex] \hline
   \noalign{\vskip 0.5ex}
   neo-W ($k=1$) \\ [0.5ex] \hline \noalign{\vskip 1ex}
-  $\lambda_{mA}=[1/(2 \zeta)]\{\bar{p}^{\male} w_{A}^{\male} w_{A}^{\female} w_{AA}^{\female}+2(1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female}\alpha^\female\}/ \{\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \} $ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\lambda_{ma}=[1/(2 \zeta)]\{(1-\bar{p}^{\male}) w_{a}^{\male} w_{a}^{\female} w_{aa}^{\female}+2\bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female}(1-\alpha^\female)\}/ \{\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \} $ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\rho_{mA}=R [1/(2 \zeta)] \{2(1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female} \alpha^{\female} \}/ \{ \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \}  $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\rho_{ma}=R [1/(2 \zeta)] \{ 2\bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female} (1-\alpha^{\female}) \}/ \{ \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \} $\\ [1ex] 
+  $\lambda_{mA} = \left( 2 \zeta \right)^{-1} \left[ \bar{p}^{\male} w_{A}^{\male} w_{A}^{\female} w_{AA}^{\female}+2(1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female}\alpha^\female\right]/ \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\lambda_{ma} = \left( 2 \zeta \right)^{-1} \left[ (1-\bar{p}^{\male}) w_{a}^{\male} w_{a}^{\female} w_{aa}^{\female}+2\bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female}(1-\alpha^\female)\right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\rho_{mA} = R \left( 2 \zeta \right)^{-1} \left[ 2(1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female} \alpha^{\female} \right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \right)  $\\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\rho_{ma} = R \left( 2 \zeta \right)^{-1} \left[ 2\bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female} (1-\alpha^{\female}) \right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \right) $\\ [1ex]
   \hline \hline 
@@
 We are particularly concerned with the conditions under which a rare neo-sex-determining allele increases in frequency, which occurs when the largest eigenvalue, $\lambda$, is greater than one. 
-If the average change in frequency of the two haplotypes that carry the $m$ allele ($Am$ and $am$) is positive, invasion will always occur (i.e., if $\left\{(\lambda_{mA}-1)+ (\lambda_{ma}-1) \right\}/2 > 0$ then $\lambda > 1$.
+If the average change in frequency of the two haplotypes that carry the $m$ allele ($Am$ and $am$) is positive, invasion will always occur, i.e., if $(\lambda_{mA} + \lambda_{ma})/2 > 1$ then $\lambda > 1$.
 If neither haplotype increases in frequency ($\lambda_{mA}, \lambda_{ma} < 1$), the $m$ allele will not invade. 
@@
 \begin{equation}\label{eq:lambdasGen}
-\frac{\rho_{mA}}{\lambda_{mA}-1}+\frac{\rho_{ma}}{\lambda_{ma}-1}>0.
+%\frac{\rho_{mA}}{\lambda_{mA}-1}+\frac{\rho_{ma}}{\lambda_{ma}-1}>0.
+\rho_{ma}\left(\lambda_{mA}-1\right)+\rho_{mA}\left(\lambda_{ma}-1\right)>0.
 \end{equation}
-\noindent For example, if we assume that only the $mA$ haplotype has a positive growth rate ($\lambda_{mA}>1$ and $\lambda_{ma}<1$), the second term in \eqref{eq:lambdasGen} is negative and invasion requires that number of recombinants from the fitter $mA$ haplotypes is larger than that of the less fit $ma$ haplotypes, relative to their growth rates.
+\noindent For example, if we assume that only the $mA$ haplotype has a positive growth rate ($\lambda_{ma}<1<\lambda_{mA}$), the second term on the left-hand side of \eqref{eq:lambdasGen} is negative and invasion requires that the rate at which $mA$ haplotypes are produced by recombination, $\rho_{ma}$, is sufficiently greater than the rate at which $ma$ haplotypes are, $\rho_{mA}$.
+In other words, invasion requires that the average growth rate of recombinants, weighted by the rates they are created, is positive.
+%the number of recombinants from the fitter $mA$ haplotypes is larger than that of the less fit $ma$ haplotypes, relative to their growth rates.
 
 Table \ref{tab:haplotype_growth} illustrates a number of key points about the invasion of neo-Y and neo-W mutations. 
-Firstly, Fisherian sex ratio selection will favour the spread of a neo-Y if the ancestral zygotic sex ratio is biased towards females, $\zeta>1/2$, and vice versa for a neo-W (terms in square brackets increase $\lambda_{mi}$).
-However, the spread of a neo-Y (neo-W) also depends on the male (female) fitness of alleles that they are associated with, see terms in curly brackets. 
-Secondly, since a dominant neo-Y is always found in males, the allele frequencies at the neo-Y (\textbf{M}) locus only change in males. 
-Therefore, invasion by a neo-Y allele does not involve any female diploid selection terms ($w_{g}^{\female}$). 
-Similarly, invasion by a neo-W is driven by the fitness of female gametes and diploids and does not involve any direct selection in male diploids.
-
-Finally, the diploid fitness terms in Table \ref{tab:haplotype_growth} are weighted by the probability of producing those genotypes through matings with gametes of the opposite sex. 
-For example, matings between a neo-Y-bearing male gamete and an $A$-bearing female gamete occur with probability $p_{X}^{\female} w_{A}^{\female}/\bar{w}_{H}^{\female}$. 
+First, Fisherian sex-ratio selection will favour the spread of a neo-Y if the ancestral zygotic sex ratio is biased towards females, $\zeta>1/2$, and vice versa for a neo-W (i.e., $\zeta>1/2$ causes the first factor of the $\lambda_{mi}$ to be greater than one for a neo-Y).
+However, the spread of a neo-Y (neo-W) also depends on the male (female) fitness of alleles that they are associated with. %, see terms in curly brackets. 
+Second, invasion by a neo-Y (neo-W) allele does not directly depend on the fitness of female (male) diploids (although they indirectly affect invasion by determining the allele frequencies $p^\female_X$ and $\hat{p}^\male$).
+%involve any female (male) diploid selection terms ($w_{g}^{\female}$)
+This is because a dominant neo-Y (neo-W) is always found in males (females), and therefore the frequency of the neo-Y (neo-W) allele ($m$) only changes in males (females). 
+%Therefore, invasion by a neo-Y allele does not involve any female diploid selection terms ($w_{g}^{\female}$). 
+%Similarly, invasion by a neo-W is driven by the fitness of female gametes and diploids and does not involve any direct selection in male diploids. 
+Finally, invasions by a neo-Y and a neo-W are qualitatively different.
+This is because a gamete containing a neo-Y always pairs with the same gamete type as a male gamete without the neo-Y does (both pair with a female gamete containing an X), and both develop into males.
+Meanwhile a gamete with a neo-W can pair with an X or Y male gamete, and develop into a female, while female gametes without the neo-W must pair with a male gamete containing an X to remain female.
+This is consequential because it means that females with and without a neo-W differ in the frequency of $A$ alleles they obtain from mating.
+%the diploid fitness terms in Table \ref{tab:haplotype_growth} are weighted by the probability of producing those genotypes through matings with gametes of the opposite sex. 
+%For example, matings between a neo-Y-bearing male gamete and an $A$-bearing female gamete occur with probability $p_{X}^{\female} w_{A}^{\female}/\bar{w}_{H}^{\female}$. 
 %This is the same probability that an ancestral-Y-bearing male gamete will inherit an $A$ allele via mating with a female gamete. 
 %On the other hand, 
-The probability that a neo-W bearing female gamete mates with an $A$-bearing male gamete is $\bar{p}^{\male} w_{A}^{\male}/\bar{w}_{H}^{\male}$, where $\bar{p}^{\male}=p_{Y}^{\male}q+p_{X}^{\male}(1-q)$ is the frequency of the A allele among both X- and Y-bearing male gametes.
-That is, in the case of a neo-W, female diploids can result from matings with either an X-bearing or a Y-bearing sperm, resulting in zygotes that will develop as females. 
-However, females that do not carry the neo-W only result from matings with X-bearing sperm. 
-Therefore, eggs with and without a neo-W can differ in the frequency of $A$ alleles they obtain from matings with male gametes. 
-Invasions by a neo-Y and a neo-W differ in this respect because sperm with or without a neo-Y allele both mate with X-bearing female gametes only.
+%The probability that a neo-W bearing female gamete mates with an $A$-bearing male gamete is $\bar{p}^{\male} w_{A}^{\male}/\bar{w}_{H}^{\male}$, where $\bar{p}^{\male}=p_{Y}^{\male}q+p_{X}^{\male}(1-q)$ is the frequency of the A allele among both X- and Y-bearing male gametes.
+%That is, in the case of a neo-W, female diploids can result from matings with either an X-bearing or a Y-bearing sperm, resulting in zygotes that will develop as females. 
+%However, females that do not carry the neo-W only result from matings with X-bearing sperm. 
+%Therefore, eggs with and without a neo-W can differ in the frequency of $A$ alleles they obtain from matings with male gametes. 
+%Invasions by a neo-Y and a neo-W differ in this respect because sperm with or without a neo-Y allele both mate with X-bearing female gametes only.
 
@@
 In order to explicitly determine the conditions under which a rare neo-sex-determining allele spreads, we must calculate the frequency of the $A$ allele in the ancestral population (i.e., $p^\female_X$, $p^\male_X$, and $p^\male_Y$).
-We assume that the $A$ allele reaches a stable equilibrium frequency under the ancestral sex-determination system before the neo-sex-determining allele ($m$) arises. 
-We can analytically calculate the allele frequency of the $A$ allele using two alternative simplifying assumptions: 
-(1) assuming that the \textbf{A} locus is within the non-recombining region around the ancestral SDR (or within tight linkage, $r \approx 0$) or (2) assuming that selection is weak relative to recombination ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon$).
+To do so we assume that the $A$ allele reaches a stable equilibrium frequency under the ancestral sex-determination system before the neo-sex-determining allele ($m$) arises. 
+We can then analytically calculate the allele frequency of the $A$ allele using two alternative simplifying assumptions: 
+(1) the \textbf{A} locus is within (or tightly linked to) the non-recombining region around the ancestral SDR ($r \approx 0$) or (2) selection is weak relative to recombination ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon<<1$).
 %These equilibrium allele frequencies and their stability conditions are given in the appendix. 
@@
 
-When there is tight linkage between the ancestral sex-determining region and the \textbf{A} locus ($r=0$), either the $A$ allele or the $a$ allele must be fixed on the Y. 
+When there is perfect linkage between the ancestral sex-determining region and the \textbf{A} locus ($r=0$), either the $A$ allele or the $a$ allele must be fixed on the Y. 
 % because selection on the Y is effectively haploid an incapably of maintaining a polymorphism in the absence of frequency dependent selection. 
-Because the labelling of alleles is arbitrary, we will assume that the $a$ locus is fixed on the Y without loss of generality ($p^\male_Y=0$). 
+Because the labelling of alleles is arbitrary, we will assume that the $a$ locus is fixed on the Y ($p^\male_Y=0$), without loss of generality . 
 If there are two alleles maintained at the \textbf{A} locus, the X can either be fixed for the $A$ allele ($p^\female_X=p^\male_X=1$) or polymorphic (0<$p^\female_X, p^\male_X$<1). 
@@
 %When then neo-Y is also tightly linked ($R=0$) a neo-Y will either remain linked to the $A$ allele or to the $a$ allele and so invasion is given directly by the larger of $\lambda_{mA}$ or $\lambda_{ma}$.
-A neo-Y haplotype with the same allele as the ancestral Y is neutral and does not change in frequency ($\lambda_{ma}=1$).
-The other neo-Y haplotype will not spread given that the initial equilibrium is stable ($\lambda_{mA}<1$). 
-Therefore, a neo-Y mutation cannot spread ($\lambda \leq 1$).
+A neo-Y haplotype with the same allele as the ancestral Y is neutral ($\lambda_{ma}=1$) and does not change in frequency.
+The other neo-Y haplotype will not spread ($\lambda_{mA}<1$) given that the initial equilibrium is stable. 
+Therefore, a neo-Y mutation cannot spread ($\lambda \leq 1$) in an ancestral XY system that is at equilibrium with all selected loci within the non-recombining region around the SDR.
 
 Neo-W alleles, on the other hand, can invade an ancestral XY system under some conditions (given in detail in the appendix). 
-Given the ancestral allele frequencies in the population, neo-W-$A$ and/or neo-W-$a$ haplotypes can increase in frequency ($\lambda_{ma}>1$ and/or $\lambda_{mA}>1$). 
-Firstly, haploid selection causes the zygotic sex ratio to be male biased ($\zeta<1/2$) when the $a$ allele (which is fixed on the Y) is favoured during haploid competition or by meiotic drive. 
-This facilitates the spread of a neo-W because neo-W alleles cause zygotes to develop as the rarer female sex. 
-However, neo-W alleles can also be favoured via their associations with \textbf{A} locus alleles that confer a fitness advantage in females.
-We will first explore these situations by assuming that there is no haploid selection, which means that there are no zygotic sex ratio biases.
-
-...
-this holds for moderate amounts of recombination between the neo-W and the selected locus, $0<R<<1$, indicating that, contrary to the conclusions of \cite{vanDoorn:2010hu}, neo sex chromosomes that reduce linkage with selected loci can invade.
+Briefly, neo-W-$A$ and/or neo-W-$a$ haplotypes can spread when rare in the absence of recombination ($\lambda_{ma}>1$ and/or $\lambda_{mA}>1$), depending on the ancestral sex-ratio and allele frequencies.
+Firstly, haploid selection causes the zygotic sex ratio to be male biased ($\zeta<1/2$) when the $a$ allele (which is fixed on the Y) is favoured during haploid competition among male gametes or by meiotic drive in males.
+This facilitates the spread of a neo-W because neo-W alleles cause the zygotes that carry them to develop as the rarer, female, sex. 
+Secondly, neo-W alleles can also be favoured via their associations with \textbf{A} locus alleles that confer a fitness advantage in females.
+\textcolor{red}{In the main text we explore the effect of these associations under the simplifying assumption of no haploid selection, which means that there are no zygotic sex ratio biases.}
+Haploid selection modifies invasion by exerting direct selection on neo-W haplotypes (i.e., competition among eggs favours one neo-W haplotype at the expense of the other while female meiotic drive will affect the spread of neo-W haplotypes only when they arise in $Aa$ heterozygotes).
+The full characteristic polynomials, including the effect of haploid selection, are given in the appendix (equations \ref{Binvasion} and \ref{Ainvasion}).
+
+%\textcolor{red}{SUMMARIZE DETAILS OF APPENDIX HERE}
+In the absence of haploid selection and with the $A$ allele is fixed on the X, it is possible for both neo-W haplotypes can spread, and thus neo-W invasion can occur regardless of its linkage to the selected locus.
+Invasion does not occur with purely sexually-antagonistic selection (i.e., $a$ directionally favoured in males and $A$ directionally favoured in females) because the X is then already as specialized as possible on the female sex.
+However, if, for example, $AA$ individuals suffer a fitness cost in females, yet $A$ is fixed on the X due to strong overdominance in males, both neo-W-$A$ and neo-W-$a$ haplotypes spread because they produce fewer unfit $AA$ females and never experience counterselection in males.
+This is true even for the neo-W-$A$ haplotype because it can pair with a $Y-a$ haplotype and still be female. 
+Because both haplotypes can spread alone, the rate of recombination between the neo-W and the selected locus, $R$, does not prevent invasion, and the system can thus evolve looser sex-linkage (e.g., the neo-W could arise on an autosome, $R=1/2$).
+Even when only one haplotype can spread, invasion can still occur up to some positive rate of recombination, $R>0$ (as long as equation \ref{eq:lambdasGen} is satisfied). 
+That looser sex-linkage can evolve is contrary to the conclusions of \cite{vanDoorn:2010hu}, who did not explicitly calculate invasion fitness under ancestrally tight sex-linkage.
+Similar scenarios have been shown to select for a modifier that increases recombination between the sexes \citep[green regions of Figure 2 in][]{Otto2014}.
+
+It is also possible, in the absence of haploid selection, for a neo-W to invade when there is a stable polymorphism at the $\mathbf{A}$ locus on X chromosomes.
+For example, overdominance in males and strong directional selection for $a$ in females creates a scenario that favours the spread of both neo-W haplotypes at equilibrium, as both bring more $a$ alleles into females and never experience counterselection in males.
+Thus, as in the case of the $A$ being fixed on the X, looser sex-linkage can evolve with a polymorphic X and this is expected under the same scenarios that select for a modifier that increases recombination between the sex chromosomes \citep[blue regions of Figure 2 in][]{Otto2014}.
+
+%\textcolor{red}{With haploid selection the situation becomes more complex, but we can }
 
@@
 %The equilibrium frequency of $A$ on different ancestral backgrounds ($\hat{p}^\male_Y$, $\hat{p}^\male_X$, and $\hat{p}^\female_X$) is given by equations \eqref{eq:pAve} and \eqref{eq:freq_diffs} where we assume selection and meiotic drive are weak relative to recombination ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon$).
-Assuming that selection is weak relative to all recombination rates ($r$, $R$ and $\chi$), we denote the leading eigenvalues describing the invasion of a neo-Y ($k=0$) and a neo-W ($k=1$) into an ancestrally XY system by $\lambda_{Y',XY}$ and $\lambda_{W',XY}$, respectively, which are given by
+Assuming that selection is weak relative to all recombination rates ($r$, $R$ and $\chi$), we denote the leading eigenvalues describing the invasion of a neo-Y ($k=0$) and a neo-W ($k=1$) into an ancestrally XY system by $\lambda_{Y',XY}$ and $\lambda_{W',XY}$, respectively, which are
 
@@
 \noindent
-where $V_{A}=\bar{p}(1-\bar{p})$ is the variance in the frequency of $A$ and $S_{A}=(D^\male +\alpha_{\Delta}^\male+t^\male) - (D^\female+\alpha_{\Delta}^\female+t^\female)$ is the difference in fitness in males versus females for the $A$ allele against the $a$ allele across diploid selection, gametic competition, and meiosis.
-$D^\Hermaphrodite=\big{(} \bar{p}s^\Hermaphrodite+(1-\bar{p})h^\Hermaphrodite s^\Hermaphrodite\big{)} -\big{(} \bar{p}h^\Hermaphrodite s^\Hermaphrodite+(1-\bar{p}) \big{)}$ is the difference in fitness between $A$ and $a$ alleles in diploids of sex $\Hermaphrodite \in \{\female,\male\}$; $\bar{p}$ is the leading-order probability of mating with an $A$-bearing gamete from the opposite sex (see Appendix).
-
-The neo-sex-determining allele $m$ will spread if $\lambda_{m,XY}>1$. 
-Equation \eqref{eq:lambda_neoY} demonstrates that a neo-Y will invade if and only if it is more closely linked to the selected locus than the ancestral sex-determining region (i.e., if $R<r$, note that $V_{A}$ and $S_{A}^2$ are strictly positive as long as \textbf{A} is polymorphic).
+where $V_{A}=\bar{p}(1-\bar{p})$ is the variance in the frequency of $A$ and $S_{A}=(D^\male +\alpha_{\Delta}^\male+t^\male) - (D^\female+\alpha_{\Delta}^\female+t^\female)$ describes sex differences in selection for the $A$ versus $a$ across diploid selection, meiosis, and gametic competition.
+The diploid selection term, $D^\Hermaphrodite=\big{(} \bar{p}s^\Hermaphrodite+(1-\bar{p})h^\Hermaphrodite s^\Hermaphrodite\big{)} -\big{(} \bar{p}h^\Hermaphrodite s^\Hermaphrodite+(1-\bar{p}) \big{)}$, is the difference in fitness between $A$ and $a$ alleles in diploids of sex $\Hermaphrodite \in \{\female,\male\}$, where $\bar{p}$ is the leading-order probability of mating with an $A$-bearing gamete from the opposite sex (see Appendix).
+
+The neo-sex-determining allele, $m$, will spread if $\lambda_{m,XY}>1$. 
+Equation \eqref{eq:lambda_neoY} demonstrates that under weak selection a neo-Y will invade if and only if it is more closely linked to the selected locus than the ancestral sex-determining region (i.e., if $R<r$, note that $V_{A}$ and $S_{A}^2$ are strictly positive as long as \textbf{A} is polymorphic).
 This result echoes that of \citet{vanDoorn:2007eu}, who considered diploid selection only and also found that homogametic transitions (XY to XY or ZW to ZW) can occur when the neo-sex-determining locus is more closely linked to a locus under sexually-antagonistic selection.
@@
 
-Equation \eqref{eq:lambda_neoW} shows that if there is no haploid selection ($t^\Hermaphrodite=\alpha^\Hermaphrodite_{\Delta}=0$), as considered by \citet{vanDoorn:2010hu}, the spread of a neo-W is equivalent to the spread of a neo-Y ($\lambda_{W',XY}=\lambda_{Y',XY}$) such that heterogametic transitions (XY to ZW or ZW to XY) can also occur only if the neo-sex-determining region is more closely linked to a locus under selection ($R<r$).
+Equation \eqref{eq:lambda_neoW} shows that if there is no haploid selection ($t^\Hermaphrodite=\alpha^\Hermaphrodite_{\Delta}=0$), as considered by \citet{vanDoorn:2010hu}, with weak selection the spread of a neo-W is equivalent to the spread of a neo-Y ($\lambda_{W',XY}=\lambda_{Y',XY}$), such that heterogametic transitions (XY to ZW or ZW to XY) can also occur only if the neo-sex-determining region is more closely linked to a locus under selection ($R<r$).
 However, if there is any haploid selection, the additional term in equation \eqref{eq:lambda_neoW} can be positive, which can allow, for example, neo-W invasion ($\lambda_{W',XY}>1$) even when the neo-sex-determining region is less closely linked to the selected locus ($R>r$).
-These transitions are unusual because, when $R>r$, associations that have built up between alleles more favourable in one sex and that sex will be weakened. 
-Therefore, mean fitness can decrease (Figure \ref{fig:Combination_MeanFit}B,D).
-
-We find that neo-W alleles can invade an XY system for a large number of selective regimes. 
+These transitions are unusual because, when $R>r$, associations that selection has built up between alleles more favourable in one sex and alleles that determine sex will be weakened. 
+Mean fitness can therefore decrease with a heterogametic transition (Figure \ref{fig:Combination_MeanFit}B,D).
+
+Equation \eqref{eq:lambda_neoW} shows that neo-W alleles can invade an XY system for a large number of selective regimes. 
 To clarify the parameter space under which $\lambda_{W',XY}>1$, we consider several special cases. 
-Firstly, if the \textbf{A} locus is unlinked to the ancestral sex-determining region ($r=1/2$), a more closely linked neo-W ($R<1/2$) can always invade because $\left( \hat{p}^\male_Y-\hat{p}^\male_X \right)=0$ such that the second term in equation \eqref{eq:lambda_neoW} disappears and invasion depends only on the sign of $(r-R)$.
-Indeed, invasion typically occurs when the neo-W is more closely linked to the selected locus than the ancestral sex-determining region (Figure \ref{fig:Combination_Centimorgans}).
-Secondly, we can simplify cases where invasion occurs despite $R>r$ using the special case where $R=1/2$ and $r<1/2$ (e.g., in the ancestor the selected locus is on an autosome and the novel sex-determining allele arises on it).
+Firstly, if the \textbf{A} locus is unlinked to the ancestral sex-determining region ($r=1/2$), a more closely linked neo-W ($R<1/2$) can always invade because there is then no association between $A$ alleles and sex chromosomes, $\left( \hat{p}^\male_Y-\hat{p}^\male_X \right)=0$.
+The second term in equation \eqref{eq:lambda_neoW} then disappears and invasion depends only on the sign of $(r-R)$. 
+Indeed, invasion typically occurs when the neo-W is more closely linked to the selected locus than the ancestral sex-determining region, under a variety of selective regimes (Figure \ref{fig:Combination_Centimorgans}).
+Secondly, we can simplify cases where invasion occurs despite looser sex-linkage, $R>r$, using the special case where $R=1/2$ and $r<1/2$ (e.g., the selected locus is on the ancestral sex chromosome and the novel sex-determining locus arises on an autosome).
 In table \ref{tab:specialcases} we give the conditions where invasion occurs when we further assume that haploid selection only occurs in one sex (e.g., during male meiosis only) and dominance coefficients are equal in the two sexes, $h^\female=h^\male$.
-Where there is no gametic competition and meiotic drive in one sex only, an unlinked neo-W can invade as long as the same allele is favoured during diploid selection in males and females ($s^\female s^\male>0$, see Figure \ref{fig:Combination_Centimorgans}B).
+When there is no gametic competition and meiotic drive is in one sex only, an unlinked neo-W can invade as long as the same allele is favoured during diploid selection in males and females ($s^\female s^\male>0$, see Figure \ref{fig:Combination_Centimorgans}B).
 %, which is 50\% of the parameter space.
@@
 Previous research suggests that when the ancestral sex-determining locus is linked to a locus that experiences haploid selection (e.g., meiotic drive), a new, unlinked sex-determining locus invades in order to restore equal sex ratios \citep{Kozielska:2010vm}.
-Our model provides a good opportunity to determine whether Fisherian sex ratio selection provides a useful explanation for the evolution of new sex-determining loci in other contexts. 
+Our model provides a good opportunity to determine whether Fisherian sex-ratio selection provides a useful explanation for the evolution of new sex-determining loci in other contexts. 
 Consider, for example, the case where the \textbf{A} locus is linked to the ancestral-SDR ($r<1/2$) and experiences meiotic drive in males only (e.g., during spermatogenesis but not during oogenesis, $\alpha^\male \neq 1/2$, $\alpha^\female=1/2$).
@@
 In this case, the zygotic sex ratio can be initially biased only if the ancestral sex-determining system is XY (Figure \ref{fig:Combination_Turnover}B). 
-If the ancestral sex-determining system is ZW, the zygotic sex ratio will be 1:1 because diploid sex is determined by the proportion of Z-bearing versus W-bearing eggs (and meiosis in females is fair, Figure \ref{fig:Combination_Turnover}D).
+If the ancestral sex-determining system is ZW, the zygotic sex ratio will be 1:1 because diploid sex is determined by the proportion of Z-bearing versus W-bearing eggs and meiosis in females is fair (Figure \ref{fig:Combination_Turnover}D).
 Thus, if the zygotic sex ratio is crucial to the evolution of new genetic sex-determining systems, invasion into ZW and XY systems will be distinct. 
-However, we find that invasion by a homogametic neo-sex-determining allele (XY to XY, or ZW to ZW) or by a heterogametic neo-sex-determining allele (XY to ZW or ZW to XY) occur under the same conditions.
+However, under weak selection we find that invasion by a homogametic neo-sex-determining allele (XY to XY or ZW to ZW) or by a heterogametic neo-sex-determining allele (XY to ZW or ZW to XY) occur under the same conditions.
 That is, we can show that $\lambda_{Y',XY}=\lambda_{W',ZW}$ and $\lambda_{Y',ZW}=\lambda_{W',XY}$ (at least up to order $\epsilon^3$; for a numerical example, compare Figure \ref{fig:Combination_Turnover}A,B to Figure \ref{fig:Combination_Turnover}C,D).
+As it turns out, under weak selection the strength of sex-ratio selection favouring, say, the invasion of a neo-W in an XY system is the same as the strength of meiotic drive favouring the invasion of a neo-Y in a ZW system.
+Even when these forces are not exactly the same (e.g., under tight sex-linkage; compare black and red curves near -25 and 25cM in Figure \ref{fig:Combination_Centimorgans}), it is important to remember that sex-ratio selection is only one of many potential selective forces acting to determine transitions between sex-determining systems.
+It is even possible for the other selective forces to overwhelm sex-ratio selection and favour sex-determination transitions that create sex-ratio biases (Figure \ref{fig:Combination_Turnover}A,C).
 
@@
 
-We next consider the case where the new sex-determining mutation, $m$, causes sex to be determined stochastically or by environmental conditions (environmental sex determiner, ESD). 
-We assume that individuals carrying the $m$ allele develop as females in a fraction, $k$, of the environments they (randomly) experience. 
+We next consider the case where the new sex-determining mutation, $m$, causes sex to be determined probabilistically or by heterogeneous environmental conditions (environmental sex determiner, ESD). 
+We assume that individuals carrying the $m$ allele develop as females with probability $k$ (e.g., in a fraction $k$ of the environments they randomly experience). 
 Assuming weak selection, the spread of these mutations is given by
@@
 
-Under Fisherian sex ratio selection, autosomal modifiers favour equal investment in male and female offspring, i.e., a 1:1 sex ratio \citep{Fisher:1930wy,Charnov:1982wg,West:2009we}. 
+Under Fisherian sex-ratio selection, autosomal modifiers favour equal investment in male and female offspring, i.e., a 1:1 sex ratio \citep{Fisher:1930wy,Charnov:1982wg,West:2009we}. 
 A novel environmental sex-determiner that causes half of its carriers to become female and half to become male ($k=1/2$) will be in males half of the time and in females half of the time (like an autosome).
-In addition, these novel sex-determination alleles equalize the sex ratio and so one might expect them to be favoured by Fisherian sex ratio selection when the resident sex ratio is biased.
+In addition, these novel sex-determination alleles equalize the sex ratio and therefore one might expect them to be favoured by Fisherian sex-ratio selection when the resident sex ratio is biased.
 However, assuming weak selection, we find that the growth rate of a rare, dominant offspring-controlled neo-ESD allele that produces males or females with equal probability ($k=1/2$) is
@@
 where we have indicated that $\lambda_{Y',XY}$ and $\lambda_{W',XY}$ are evaluated at $R=1/2$.
-Recombination between the selected locus and the novel sex-determining locus, $R$, doesn't enter into the $k=1/2$ results because sex is essentially randomized each generation, %as if the novel sex-determiner were on an unlinked site that half the time acts as a neo-$W$ and half the time as a neo-$Y$.
+That is, recombination between the selected locus and the novel sex-determining locus, $R$, doesn't enter into the $k=1/2$ results.
+This is because sex is essentially randomized each generation, %as if the novel sex-determiner were on an unlinked site that half the time acts as a neo-$W$ and half the time as a neo-$Y$.
 preventing associations from building up between allele $A$ and sex.
@@
 Equation \eqref{eq:lambda_ESD} shows that invasion by a novel `perfect' ESD (equal sex ratio, $k=1/2$) mutation is the same for an ancestrally XY or ZW system (since $\lambda_{Y',XY} = \lambda_{W',ZW}$, $\lambda_{W',XY} = \lambda_{Y',ZW}$).
-Thus, by the same argument as above (if drive occurs in males only then the sex ratio is only biased when the ancestral sex-determination system is XY), Fisherian sex ratio selection does not explain invasion by an offspring-controlled neo-ESD locus.
-Rather, the neo-ESD gets half of the fitness of a feminizing mutation (neo-$W$) and half of the fitness of a masculizing mutation (neo-$Y$), but only has an effect one half of the time (the other half of the time it produces the same sex as the ancestral system would have, to leading order).
+Thus, by the same argument as above (if drive only occurs in males then the sex ratio is only biased when the ancestral sex-determination system is XY), Fisherian sex-ratio selection alone does not explain the invasion of an offspring-controlled neo-ESD allele under weak selection.
+Rather, the neo-ESD gets half of the fitness of a feminizing mutation (neo-$W$) and half of the fitness of a masculinizing mutation (neo-$Y$), but only has an effect one half of the time (the other half of the time it produces the same sex as the ancestral system would have, to leading order).
 The net result can be that perfect ESD will not invade, even if current sex ratios are biased. 
@@
 
-Fisherian sex ratio selection is sometimes considered in terms of balancing parental investment in male versus female offspring \citep{Charnov:1982wg}.
-In addition, under environmental sex-determination, the proportion of males/females is sometimes controlled by the mother, e.g., the proportion of eggs laid in warm versus cold environments could determine the sex ratio of offspring.
+Fisherian sex-ratio selection is sometimes considered in terms of balancing parental investment in male versus female offspring \citep{Charnov:1982wg}.
+In addition, under environmental sex-determination, the proportion of males/females is sometimes controlled by the mother (e.g., the proportion of eggs laid in warm versus cold environments). 
 We therefore also considered the invasion of a neo-sex-determining allele ($m$) in a model in which mothers that have at least one $m$ allele produce daughters with probability $k$. 
-As with offspring-controlled ESD, for all $k\in\{0,1/2,1\}$, we find that invasion into an ancestrally XY system is the same as invasion into an ancestrally ZW system (at least up to order $\epsilon^3$, assuming weak selection), implying transitions between genetic sex determination and maternally controlled environmental sex determination are not driven by Fisherian sex ratio selection on biased zygotic sex ratios.
-\textcolor{red}{(maternal analysis still lacks meiotic drive)}
+As with offspring-controlled ESD, for all $k\in\{0,1/2,1\}$, we find that invasion into an ancestral XY system is the same as invasion into an ancestrally ZW system (at least up to order $\epsilon^3$, assuming weak selection), implying that transitions between genetic sex-determination and maternally controlled environmental sex-determination are not driven by Fisherian sex-ratio selection alone.
+\textcolor{red}{(Maternal ESD analysis still lacks meiotic drive -- Mathematica can't seem to deal with the added complexity.)}
 
@@
 %However, with $k\neq1$ the results with maternal control differ from those with offspring control.
-%Interestingly, for all $k\in\{0,1/2,1\}$, we find that invasion into an ancestrally XY system is the same as invasion into an ancestrally ZW system (at least up to order $\epsilon^3$), implying that sex ratio selection does not drive transitions between genetic sex determination and maternally controlled environmental sex determination.
+%Interestingly, for all $k\in\{0,1/2,1\}$, we find that invasion into an ancestrally XY system is the same as invasion into an ancestrally ZW system (at least up to order $\epsilon^3$), implying that sex-ratio selection does not drive transitions between genetic sex determination and maternally controlled environmental sex determination.
 %Of particular interest is $k=1/2$ (i.e., when the mother perfectly balances the sex ratio of her offspring).
@@
 
-Because linkage between haploid selected loci and sex-determining regions cases biased zygotic sex ratios \citep{Hamilton:1967ts,Burt:2006,Field:2012fd,Field:2013cc}, one might expect Fisherian sex ratio selection to drive the spread of new sex-determining systems that bring the sex ratio closer to 50:50.
-Fisherian sex ratio selection follows from the fact that, for an autosomal locus, half of the genetic material is inherited from a male, and half from a female \citep{Fisher:1930wy,West:2009we}. 
+\textcolor{red}{I messed with the sex-ratio selection paragraphs to tone down our "it doesn't matter" speech from before.}
+%SEX-RATIO SELECTION
+Linkage between haploid selected loci and sex-determining regions cases biased zygotic sex ratios \citep{Hamilton:1967ts,Burt:2006,Field:2012fd,Field:2013cc}.
+One might then expect Fisherian sex-ratio selection to drive the spread of new sex-determining systems that bring the sex ratio closer to 50:50. 
+Fisherian sex-ratio selection follows from the fact that, for an autosomal locus, half of the genetic material is inherited from a male, and half from a female \citep{Fisher:1930wy,West:2009we}. 
 Thus, if the population sex ratio is biased towards females, the average per-individual contribution of genetic material to the next generation from males is greater than the contribution from females (and vice versa for male-biased sex ratios).
 Therefore, a mutant that increases investment in males will spread via the higher per-individual contributions made by males. 
-%That is, under Fisherian sex ratio selection, the success of a mutant relative to the non-mutant depends, in equal parts, on the contributions made by males and females to the next generation. 
-An implicit assumption of Fisherian sex ratio selection is that the mutant allele is autosomal and has the same inheritance pattern as the non-mutant allele. 
-The mutations we consider here, neo-sex-determining alleles, break this assumption. 
-For example, the success of neo-Y/neo-W mutations depends only on the number of alleles contributed by males/females (Table \ref{tab:haplotype_growth}). 
-In this respect, a neo-W is similar to a cytoplasmic element, which also does not experience selection to balance sex ratios \citep{Frank:1989vl,Werren:1998co,Chase:2007bf}.
-Even mutants that are equally likely to be found in males or females, such as an environmental sex determination mutation (equation \ref{eq:lambda_ESD}), are not strictly autosomal if they determine sex.
-Thus, despite the fact that sex ratio biases caused by gametic competition or meiotic drive have been shown to exert Fisherian sex ratio selection on various autosomal modifiers \citep{Stalker:1961th,Smith:1975ft,Frank:1989vl,Hough:2013uo,Ubeda:2015fx, Otto:2015va}, we do not find evidence of Fisherian sex ratio selection acting during invasion by neo-sex-determination systems (e.g., see Figure \ref{fig:Combination_Turnover} and \citealt{Ubeda:2015fx}, in which a neo-Y invades despite biasing sex ratios).
-
-We note two other ways in which sex determination has been shown to relate to zygotic sex ratios.
-Firstly, female-biased sex ratios can be favoured when there is local mate competition, where all matings are between siblings and assuming one male can inseminate many females \citep{Hamilton:1967ts}.
-Therefore, with local mate competition, feminizing mutations can spread because they bias the sex ratio towards females \citep{Wilson:1981vm,Vuillleumier:2007bh}. 
-Secondly, environmental conditions (e.g., maternal condition, mate quality, age, or host size) can differentially affect the fitness of males versus females such that the optimal allocation to males/females depends on the environment \citep{Trivers:1973wb,Charnov:1977tx,Charnov:1982wg}.
-In such cases, flexible sex determination systems may evolve in order to allow the zygotic sex ratio to be determined in a way that depends on the environment \citep{Charnov:1977tx,Werren:1984tl,Pen:2010kk}.
-In this study, we do not consider environmental condition dependence or local mate competition \citep[reviewed in][]{Charnov:1982wg,Bull:1983vi,West:2009we}.
-
-It has previously been demonstrated that new sex-determining systems can evolve if there is genetic variation maintained by sexually-antagonistic selection \citep{vanDoorn:2007eu,vanDoorn:2010hu}. 
-In particular, transitions to new sex-determining systems can occur when new sex-determining regions are more closely linked to a sexually-antagonistic locus.
-Our results show that genetic variation at loci that experience haploid selection can also generate selection in favour of new sex-determining systems. 
-New sex-determining alleles are again favoured if they are linked with a locus under haploid selection and the ancestral sex-determination locus is not.
-However, with haploid selection, heterogametic transitions (XY to ZW or ZW to XY) can also occur when the new sex-determining region is less closely linked to the locus under selection.
-
-Neo-W (neo-Y) alleles invade when their fitness in females (males) is greater than the mean fitness of females (males) under the ancestral sex determination system.
-With sexually antagonistic selection (between diploid sexes) only, linkage between a selected locus and the sex-determining region strengthens associations between male beneficial alleles and the male-determining allele (Y or Z) and between female beneficial alleles and the female-determining allele (X or W).
-Thus, the mean fitness of both males and females increases with closer linkage to the sex-determining region. 
-Therefore, new sex-determining alleles only invade if they are more closely linked than the ancestral sex-determining region. 
-However, if there is haploid selection on loci linked to an XY (ZW) sex-determining region, selection can maintain polymorphisms at which the mean fitness of females (males) or males is lower than it would be without sex-linkage.
-In these cases, unlinked neo-W (neo-Y) alleles can invade, see figure \ref{fig:Combination_MeanFit}.
-
+%%%That is, under Fisherian sex-ratio selection, the success of a mutant relative to the non-mutant depends, in equal parts, on the contributions made by males and females to the next generation. 
+%An implicit assumption of Fisherian sex-ratio selection is that the mutant allele is autosomal and has the same inheritance pattern as the non-mutant allele. 
+%The mutations we consider here, neo-sex-determining alleles, break this assumption. 
+%For example, the success of neo-Y/neo-W mutations depends only on the number of alleles contributed by males/females (Table \ref{tab:haplotype_growth}). 
+%In this respect, a neo-W is similar to a cytoplasmic element, which also does not experience selection to balance sex ratios \citep{Frank:1989vl,Werren:1998co,Chase:2007bf}.
+%Even mutants that are equally likely to be found in males or females, such as an environmental sex determination mutation (equation \ref{eq:lambda_ESD}), are not strictly autosomal if they determine sex.
+%Thus, despite the fact that sex ratio biases caused by gametic competition or meiotic drive have been shown to exert Fisherian sex-ratio selection on various autosomal modifiers \citep{Stalker:1961th,Smith:1975ft,Frank:1989vl,Hough:2013uo,Ubeda:2015fx, Otto:2015va}, we do not find evidence of Fisherian sex-ratio selection acting during invasion by neo-sex-determination systems (e.g., see Figure \ref{fig:Combination_Turnover} and \citealt{Ubeda:2015fx}, in which a neo-Y invades despite biasing sex ratios).
+
+Sex ratio biases caused by gametic competition or meiotic drive have been shown to exert Fisherian sex-ratio selection on various autosomal \citep{Stalker:1961th,Smith:1975ft,Frank:1989vl,Hough:2013uo,Ubeda:2015fx, Otto:2015va} and sex-linked \citep{Ubeda:2015fx} modifiers.
+We find that sex-ratio biases caused by haploid selection can also affect transitions between sex-determining systems (e.g., see $\zeta$ terms in Table \ref{tab:haplotype_growth}). 
+For instance, when an allele that drives in males is linked to an XY locus it will often become associated with the Y and therefore produce a male bias ($\zeta<1/2$).
+This male bias increases the potential for a neo-W to invade (as we then have $(2\zeta)^{-1}>1$, Table \ref{tab:haplotype_growth}), which can equalize the sex-ratio \citep[for a related example see][]{Ubeda:2015fx}.
+%However, the neo-W may not equalize the sex-ratio (e.g., if the driving allele also drives in females or affects competition among eggs)
+However, this sex-ratio selection can be overwhelmed when the driving allele has additional selective effects (e.g., when it is detrimental to male diploids but beneficial for female diploids; Table \ref{tab:specialcases}), preventing the neo-W from invading.
+%and equalizing the sex ratio.
+Conversely, these additional selective effects can even favour transitions between sex-determining systems that create new sex-ratio biases.
+For example, in an ancestral ZW system, an allele that drives only in males can allow a linked neo-Y to invade, despite the fact it creates a male bias.
+This of course generates new sex-ratio selection that may drive further turnover \citep{Ubeda:2015fx}.
+What we would like to stress is that sex-ratio selection alone cannot predict when new sex-determining systems can evolve.
+
+%SEX-RATIO BIAS IN UBEDA ET AL
 %DRAFT (improve): In \citet{Ubeda:2015fx}, the new sex determining locus spreads because it arises in linkage with a locus that experiences drive.
@@
 
+%WHY SEX-RATIO BIASES CAN BE FAVOURED
+%We note two other ways in which sex determination has been shown to relate to zygotic sex ratios.
+%Firstly, female-biased sex ratios can be favoured when there is local mate competition, where all matings are between siblings and assuming one male can inseminate many females \citep{Hamilton:1967ts}.
+%Therefore, with local mate competition, feminizing mutations can spread because they bias the sex ratio towards females \citep{Wilson:1981vm,Vuillleumier:2007bh}. 
+%Secondly, environmental conditions (e.g., maternal condition, mate quality, age, or host size) can differentially affect the fitness of males versus females such that the optimal allocation to males/females depends on the environment \citep{Trivers:1973wb,Charnov:1977tx,Charnov:1982wg}.
+%In such cases, flexible sex-determination systems may evolve in order to allow the zygotic sex ratio to be determined in a way that depends on the environment \citep{Charnov:1977tx,Werren:1984tl,Pen:2010kk}.
+%In this study, we do not consider environmental condition dependence or local mate competition \citep[reviewed in][]{Charnov:1982wg,Bull:1983vi,West:2009we}.
+
+%HAPLOID SELECTION CAN ACT LIKE SEXUALLY-ANTAGONISTIC SELECTION
+It has previously been demonstrated that new sex-determining systems can evolve if there is genetic variation maintained by sexually-antagonistic selection \citep{vanDoorn:2007eu,vanDoorn:2010hu}. 
+In particular, transitions to new sex-determining systems can occur when new sex-determining regions are more closely linked to a sexually-antagonistic locus.
+Our results show that genetic variation at loci that experience haploid selection can also generate selection in favour of new sex-determining systems. 
+New sex-determining alleles are again favoured if they are linked with a locus under haploid selection and the ancestral sex-determination locus is not.
+However, with haploid selection, heterogametic transitions (XY to ZW or ZW to XY) can also occur when the new sex-determining region is less closely linked to the locus under selection.
+
+%HAPLOID SELECTION ALSO ALLOWS LOOSER LINKAGE TO EVOLVE
+Neo-W (neo-Y) alleles invade when their fitness in females (males) is greater than the mean fitness of females (males) under the ancestral sex-determination system.
+With sexually-antagonistic selection (between diploid sexes) only, linkage between a selected locus and the sex-determining region strengthens associations between male beneficial alleles and the male-determining allele (Y or Z) and between female beneficial alleles and the female-determining allele (X or W).
+Thus, the mean fitness of both males and females increases with closer linkage to the sex-determining region. 
+Therefore, new sex-determining alleles only invade if they are more closely linked than the ancestral sex-determining region. 
+However, if there is haploid selection on loci linked to an XY (ZW) sex-determining region, selection can maintain polymorphisms at which the mean fitness of females (males) is lower than it would be without sex-linkage.
+In these cases, unlinked neo-W (neo-Y) alleles can increase female (male) fitness, at a cost to the other sex, and invade despite lowering mean fitness (Figure \ref{fig:Combination_MeanFit}).
+
+%Limitation 1: DEGENERATE Y
 We assume that sex-determining alleles do not experience direct selection except via their associations with sex and alleles at a selected locus. 
-However, in some cases, there may be significant degeneration around the sex-limited allele (Y or W) in the ancestral sex determining region because recessive deleterious mutations and/or deletions may fix around the Y or W allele \citep{Rice:1996ke,Charlesworth:2000cc,Bachtrog:2006ed,Marais:2008hm}.
+However, in some cases, there may be significant degeneration around the sex-limited allele (Y or W) in the ancestral sex-determining region because recessive deleterious mutations and/or deletions may fix around the Y or W allele \citep{Rice:1996ke,Charlesworth:2000cc,Bachtrog:2006ed,Marais:2008hm}.
 During heterogametic transitions (XY to ZW or ZW to XY), the formally sex-limited allele fixes such that all individuals have YY or WW genotypes (Figure \ref{fig:Combination_Turnover}). 
 Any recessive deleterious alleles linked to the Y or W will therefore be revealed to selection during a heterogametic transition. 
-This phenomenon was studied by \citet{vanDoorn:2010hu}, who found that degeneration can prevent fixation of a neo-W or a neo-Y allele, leading to a mixed sex determination system where the ancestral- and neo- sex-determining loci are both polymorphic.
+This phenomenon was studied by \citet{vanDoorn:2010hu}, who found that degeneration can prevent fixation of a neo-W or a neo-Y allele, leading to a mixed sex-determination system where the ancestral- and neo- sex-determining loci are both polymorphic.
 However, they noted that very rare recombination events around the ancestral sex-determining region can allow these heterogametic transitions to complete.  
@@
 
+%Limitation 2: TWO ALLELE DRIVE
 In addition, our model of meiotic drive is simple, involving a single locus with two alleles. 
-However, many meiotic drive systems involve an interaction with another locus at which alleles may `suppress' the action of meiotic drive \citep{Burt:2006,Lindholm:2016cw}.
+However, many meiotic drive systems involve an interaction with another locus at which alleles may `suppress' the action of meiotic drive \citep[][]{Burt:2006,Lindholm:2016cw}.
 Thus, the dynamics of meiotic drive alleles can be heavily dependent on the interaction between two loci and the recombination rate between them, which in turn can be affected by sex-linkage if there is reduced recombination between sex chromosomes \citep{Hurst:1991uh}.
@@
 In polygamous mating systems, the intensity of pollen/sperm competition can depend on the density of males available to donate pollen/sperm, which can itself depend on the sex ratio \citep{Taylor:2002wu}.
-Since the sex ratio is partly determined by the sex determination system, the evolution of new sex determination system could by influenced by these dynamics. 
+Since the sex ratio is partly determined by the sex-determination system, the evolution of new sex-determination system could by influenced by these dynamics. 
 How the evolution of new sex-determining mechanisms could be influenced by two-locus meiotic drive and/or by ecological feedbacks under different mating systems remains to be studied.
 
-The hypotheses presented here can be empirically investigated in a similar manner to the idea that transitions between sex-determining systems are favoured by linkage to sexually antagonistic variation.
-In the case of sexually antagonistic variation, one supporting observation is that genes that appear to experience sexually-antagonistic selection have been found on recently derived sex chromosomes \citep{Lindholm:2002dw,Tripathi:2009cw,Ser:2010iq}.
-However, it is possible that sexually antagonistic variation accumulated after sex chromosome transitions because linkage with the sex-determining regions allows sexually antagonistic selection to maintain polymorphisms under a larger parameter space \citep{Rice:1987hs,Jordan:2011fj}.
+%PREDICTIONS TO TEST
+The hypotheses presented here can be empirically investigated in a similar manner to the idea that transitions between sex-determining systems are favoured by linkage to sexually-antagonistic variation.
+In the case of sexually-antagonistic variation, one supporting observation is that genes expected to be under sexually-antagonistic selection (e.g., those causing bright male colouration) have been found on recently derived sex chromosomes \citep{Lindholm:2002dw,Tripathi:2009cw,Ser:2010iq}.
+However, it is possible that sexually-antagonistic variation accumulated after sex chromosome transitions because linkage with the sex-determining regions allows sexually-antagonistic selection to maintain polymorphisms under a larger parameter space \citep{Rice:1987hs,Jordan:2011fj}.
 We note that linkage with sex chromosomes is not, a priori, more permissive to the maintainence of ploidally antagonistic variation \citep{Immler:2012tl}.
-However, as with sexually-antagonistic variation, a comparison between closely related clades could indicate whether a polymorphism pre-dates a transition in sex-determination or arose afterwards. 
+However, as with sexually-antagonistic variation, a comparison between closely related clades could indicate whether a polymorphism pre-dates a transition in sex-determination or arose afterwards (\textcolor{red}{George Sandler, an undergrad in the Wright and Barrett labs, has done some yet-to-be-published work on Rumex that we should cite here.
+We can send him this draft and get his permission to cite him as personal communication or something.
+I think he has basically found that genes retained on the Y are overexpressed in pollen but not in male diploids, suggesting they are being maintained by haploid selection, not sexual antagonism.
+I guess this is a follow up to Crowson et al 2017 Mol Biol Evol 34:1140, which we could potentially cite as well.}).
 Secondly, we have shown that new sex-determination systems can be favoured if either the ancestral sex-determining region or the new sex-determining region are linked to loci under haploid selection. 
-Therefore, the presence of haploid selected loci around ancestral- or new- sex-determining regions could support their role in sex chromosome turnover. 
+Therefore, the presence of haploid selected loci around ancestral- or novel-sex-determining regions could support their role in sex chromosome turnover. 
 %It would be particularly informative if selection were evaluated in closely related clades
 
+%HOW TO TEST EMPIRICALLY
 Taken at face value, our results indicate that transitions in heterogametey (XY to ZW or vice versa) are more likely to be favoured by selection if there is selection upon both haploid and diploid genotypes rather than diploid selection alone.
@@
 
-We have shown that haploid selection can drive transitions between sex determination systems, such that haploid selection should be incorporated into the factors that influence the evolution of sex determination.
-However, the particular way in which transitions are affected by haploid selection is not intuitively obvious. 
-Firstly, sex-specific haploid selection affects turnovers between sex determination systems in a manner that is qualitatively different from diploid sex-specific selection. 
+%CONCLUSION
+We have shown that haploid selection can drive transitions between sex-determination systems.
+We therefore argue that haploid selection should be considered, alongside sex-ratio selection and sexually-antagonistic selection, as an important factor influencing the evolution of sex determination.
+Further, we have shown the way in which transitions are affected by haploid selection is not intuitively obvious. 
+Firstly, sex-specific haploid selection affects turnovers between sex-determination systems in a manner that is qualitatively different from diploid sex-specific selection. 
 In particular, closer linkage between a sex-determining locus and a selected locus is not always favoured during heterogametic transitions when there is haploid selection. 
-Secondly, even though haploid selection is a source of zygotic sex ratio biases, Fisherian sex ratio selection does not have good explanatory power in our models in determining whether various sex-determination systems evolve; this result is surprising given that sex ratios are ultimately determined via the sex-determination system.
-
+Secondly, even though haploid selection is a source of zygotic sex-ratio biases, in our models Fisherian sex-ratio selection does not have good explanatory power in determining whether various sex-determination systems evolve.
+This result is surprising given that sex ratios are ultimately determined via the sex-determination system, and leads us to the conclusion that three selective forces -- haploid, diploid, and sex-ratio selection -- should all be considered when exploring transitions between sex-determination systems.
+
+%POLYGENIC SEX DETERMINATION
 %\textcolor{red}{Numerical results suggest that polygenic sex determination can be stable with gametic competition.
@@
 \centering
-\includegraphics[width=\linewidth]{Combination_Turnover}\\
+\begin{tikzpicture}[remember picture]
+	\node[] (plot) {\includegraphics[width=\linewidth]{Combination_Turnover}};
+	\node[above = 0cm of plot, xshift = -70] () {$r=0.5$, $R=0.05$};
+	\node[above = 0cm of plot, xshift = 120] () {$r=0.05$, $R=0.5$};
+	\node[left = 0cm of plot, yshift = 105, rotate = 90] () {XY $\rightarrow$ ZW};
+	\node[left = 0cm of plot, yshift = -20, rotate = 90] () {ZW $\rightarrow$ XY};
+\end{tikzpicture}
 \caption{
 Heterogametic transitions from XY to ZW sex determination (neo-W frequency shown by black lines, panels A and B) or from ZW to XY (neo-Y frequency shown by black lines, panels C and D) occur similarly regardless of sex ratio biases present before (B versus D) or after (C versus A, dashed lines show male frequency).
-During invasion by a neo-ZW sex determination system (A and B), the ancestral Y fixes in both males and females (blue and red lines). 
+During invasion by a neo-ZW sex-determination system (A and B), the ancestral Y fixes in both males and females (blue and red lines). 
 Similarly, the ancestral W allele fixes in males and females (blue and red lines) during a ZW to XY transition. 
@@
 Therefore, an ancestral XY sex determination can have a biased zygotic sex ratio that becomes unbiased after an unlinked neo-W invades (B). 
-However, in panel D, a unlinked neo-Y invades an ancestral ZW sex determination system in a similar manner but no biases to the zygotic sex ratio occur. 
+However, in panel D, a unlinked neo-Y invades an ancestral ZW sex-determination system in a similar manner but no biases to the zygotic sex ratio occur. 
 With diploid selection alone, neo-sex-determining loci do not spread if they are less closely linked to the \textbf{A} locus than the ancestral sex-determining locus (see equation \eqref{eq:lambda_neoW} and Figure \ref{fig:Combination_Centimorgans}A).
@@
 \textcolor{red}{Aesthetic adjustments: 
-Could add titles to the columns/rows: neo-W for row 1, neo-Y for row 3, $r=0.5$, $R=0.05$ for column 1 and $r=0.05$, $R=0.5$ for column 2. 
+%Could add titles to the columns/rows: neo-W for row 1, neo-Y for row 3, $r=0.5$, $R=0.05$ for column 1 and $r=0.05$, $R=0.5$ for column 2. 
 %Could adjust padding (too much whitespace where there is no axis label). 
@@
 %Matt - could you uncomment the line legends in the Mathematica file (function not included in my Mathematica version).
+Add chromosome cartoons to depict recombination rates?
 }
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Changes in mean fitness
+%Heterogametic transitions with/without sex ratio change
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \centering
-\includegraphics[width=\linewidth]{Combination_MeanFit}\\
+\begin{tikzpicture}[remember picture]
+	\node[] (plot) {\includegraphics[width=\linewidth]{Combination_Turnover_Ratio}};
+	\node[above = 0cm of plot, xshift = -80] () {XY $\rightarrow$ ZW};
+	\node[above = 0cm of plot, xshift = 120] () {ZW $\rightarrow$ XY};
+\end{tikzpicture}
 \caption{
-Here, we plot how male mean fitness (blue lines), female mean fitness (red lines), and population mean fitness (male mean fitness plus female mean fitness, black lines) changes during the transitions between sex-determination systems shown in Figure \ref{fig:Combination_Turnover}.
-Here we multiply male mean fitness and female mean fitness by two so that we can show it on the same scale as population mean fitness. 
+Is this what Sally was thinking?
+}
+\label{fig:Combination_Turnover_Ratio}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Changes in mean fitness
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[!h]
+\centering
+\begin{tikzpicture}[remember picture]
+	\node[] (plot) {\includegraphics[width=\linewidth]{Combination_MeanFit}};
+	\node[above = 0cm of plot, xshift = -70] () {$r=0.5$, $R=0.05$};
+	\node[above = 0cm of plot, xshift = 120] () {$r=0.05$, $R=0.5$};
+	\node[left = 0cm of plot, yshift = 105, rotate = 90] () {XY $\rightarrow$ ZW};
+	\node[left = 0cm of plot, yshift = -20, rotate = 90] () {ZW $\rightarrow$ XY};
+\end{tikzpicture}
+\caption{
+Changes in mean diploid fitness of males (blue lines), females (red lines), and the entire population (male mean fitness plus female mean fitness, black lines) during the transitions between sex-determination systems shown in Figure \ref{fig:Combination_Turnover}.
+Here we multiply male and female mean fitnesses by two so that we can show them on the same scale as population mean fitness. 
 The mean fitness of females increases during the spread of neo-W alleles (A and B) and the mean fitness of males increases during the spread of neo-Y alleles (C and D). 
 However, when a neo-sex determining system evolves that is less closely linked to a locus under selection (B and D), population mean fitness decreases. 
-\textcolor{red}{
-Could add titles to the columns/rows: neo-W for row 1, neo-Y for row 3, $r=0.5$, $R=0.05$ for column 1 and $r=0.05$, $R=0.5$ for column 2. 
-%\& possibly adjust padding (too much whitespace?). 
-%Matt - could you uncomment the line legends in the Mathematica file (function not included in my Mathematica version).
-}
+%\textcolor{red}{
+%Could add titles to the columns/rows: neo-W for row 1, neo-Y for row 3, $r=0.5$, $R=0.05$ for column 1 and $r=0.05$, $R=0.5$ for column 2. 
+%%\& possibly adjust padding (too much whitespace?). 
+%%Matt - could you uncomment the line legends in the Mathematica file (function not included in my Mathematica version).
+%}
+\textcolor{red}{I'm still confused why male and female mean fitnesses aren't normalized by their frequency. I'm not sure we should be calling them means without this normalization step.}
 }
@@
 %\includegraphics[width=\linewidth]{Combination_Centimorgan}\\
-\includegraphics[width=\linewidth]{PositionPlot}\\
+%\includegraphics[width=\linewidth]{PositionPlot}\\
+\begin{tikzpicture}[remember picture]
+	\node[] () {\includegraphics[width=\linewidth]{PositionPlot}};
+	\node[anchor=east] at (0.5, 1.5) {\footnotesize sexual-antagonism, $s^\male s^\female < 0$};
+	\node[anchor=east] at (6.5, 1.5) {\footnotesize male drive, $s^\male s^\female > 0$};
+	\node[anchor=east] at (0.5, -3) {\footnotesize pollen competition, $s^\male < s^\female$};
+	\node[anchor=east] at (6.5, -3) {\footnotesize pollen comptition, $s^\female < s^\female$};
+\end{tikzpicture}
 \caption{
-The invasion fitness of a neo-W allele plotted against the relative location of a locus under direct selection, \textbf{A}, for various selective regimes. 
-We assume that the ancestral sex-determining locus is located at -0.25, the novel sex-determining locus is located at 0.25 and that there is a polymorphism at the \textbf{A} locus maintained by selection.
-We used Haldane's map function \citep[Equation 3 in ][]{Haldane1919} to convert from map distance (centiMorgans) to the probability of a cross-over event. 
+Invasion fitness of a neo-W allele plotted against the relative genomic location of a locus under direct selection, \textbf{A}, for various selective regimes. 
+The ancestral sex-determining locus is located at -25 and the novel sex-determining locus is located at 25. %and that there is a polymorphism at the \textbf{A} locus maintained by selection.
+We use Haldane's map function \citep[Equation 3 in ][]{Haldane1919} to convert from map distance (centiMorgans) to the probability of a cross-over event. 
 In A, there is no haploid selection ($t^\Hermaphrodite=\alpha^\Hermaphrodite_{\Delta}=0$) and selection in diploids is sexually antagonistic \citep[following][]{vanDoorn:2010hu}, in which case a neo-W can only invade if it is more closely linked to the selected locus ($s^\female=1/10$, $h^\female=7/10$ $s^\male=-1/10$, $h^\male=3/10$).
@@
 A polymorphism can then be maintained by opposing selection between the haploid and diploid phases. 
-In B, there is drive in favour of the $a$ allele in males ($\alpha^\male_{\Delta}=-1/5$), no female meiotic drive or gametic competition, $t^\Hermaphrodite=\alpha^\female_{\Delta}=0$), and equal selection in diploid sexes ($s^\female=s^\male=1/5$, $h^\female=h^\male=7/10$).
+In B, there is drive in favour of the $a$ allele in males ($\alpha^\male_{\Delta}=-1/20$), no female meiotic drive or gametic competition, $t^\Hermaphrodite=\alpha^\female_{\Delta}=0$), and equal selection in diploid sexes ($s^\female=s^\male=1/10$, $h^\female=h^\male=7/10$).
 In this case, a neo-W can invade even when the selected locus is more closely linked to the ancestral sex determining locus (see Table \ref{tab:specialcases} and Figure \ref{fig:Combination_Turnover}).
 In C and D, there is gametic competition among male gametes only (favouring $a$, $t^\male=-1/10$) and no meiotic drive or gametic competition in females ($t^\female=\alpha^\Hermaphrodite_{\Delta}=0$).
-In this case, the neo-W does not invade if $s^\female>s^\male$ (panel C: $s^\female=3/20$, $s^\male=1/20$) but does if $s^\female<s^\male$ (panel D: $s^\female=1/20$, $s^\male=3/20$), see Table \ref{tab:specialcases}.
+In this case, the neo-W does not invade if $s^\female>s^\male$ (panel C: $s^\female=3/20$, $s^\male=1/20$) but does if $s^\female<s^\male$ (panel D: $s^\female=1/20$, $s^\male=3/20$), see Table \ref{tab:specialcases}.\\
 \textcolor{red}{
-I suspect that panel C has a region where no equilibrium is maintained (CHECK! Maybe include different parameters here or remove the part when no equilibrium). 
-%Currently use different parameters for B than using in figure \ref{fig:Combination_Turnover} (selection/drive twice as strong in turnover figure). 
-This plot would also benefit from titles giving, e.g., ``sexually-antagonistic selection, $s^\female s^\male<0$'' for A, ``male meiotic drive, $s^\female s^\male>0$'' for B}
+1.
+I suspect that panel C has a region where no equilibrium is maintained (CHECK!
+Maybe include different parameters here or remove the part when no equilibrium).
+MMO: If you trust the sieve function there are stable equilibria across the entire range, although this differ greatly between XY and ZW systems near -25cM.
+\\
+2.
+Currently use different parameters for B than using in figure \ref{fig:Combination_Turnover} (selection/drive twice as strong in turnover figure).
+MMO: this is to keep it within the bounds of the plot -- using the same parameters makes the peak at -25 reach roughly 0.1, and then it is difficult to see the details of A,C, and D.
+%This plot would also benefit from titles giving, e.g., ``sexually-antagonistic selection, $s^\female s^\male<0$'' for A, ``male meiotic drive, $s^\female s^\male>0$'' for B
+}
 }
@@
 
+\textcolor{red}{Should we adjust the subscripts throughout this subsection?
+Right now we end up re-defining $i$ and $j$ (when switching from haploid to diploid) and then introduce three new subscripts $b$, $c$, and $l$, all of which can be derived from $i$ and $j$.
+Might be more straightforward to just use $p^\Hermaphrodite_{x_1,x_2,a_1,a_2,m_1,m_2}$ where 1 is maternal and 2 is paternal?
+We then no longer have to switch indices from haploid to diploid and $b=m_1m_2$, $c=x_1x_2$, and $l=a_1a_2$.
+I guess the downside will be writing the recursion equations...}
+
 In each generation we census the genotype frequencies in male and female gametes/gametophytes (hereafter, gametes) between meiosis (and any meiotic drive) and gametic competition. 
-At this stage we denote the frequencies of X- and Y-bearing gametes from males and females $X_{ij}^{\Hermaphrodite}$ and $Y_{ij}^{\Hermaphrodite}$, where $\Hermaphrodite \in \{\male,\female\}$ specifies the sex of the diploid that the gamete came from, $i\in\{A,a\}$ specifies the allele at the selected locus $\mathbf{A}$, and $j\in\{M,m\}$ specifies the allele at the novel sex-determining locus $\mathbf{M}$.
+At this stage we denote the frequencies of X- and Y-bearing gametes from males and females $x_{ij}^{\Hermaphrodite}$ and $y_{ij}^{\Hermaphrodite}$, where $\Hermaphrodite \in \{\male,\female\}$ specifies the sex of the diploid that the gamete came from, $i\in\{A,a\}$ specifies the allele at the selected locus $\mathbf{A}$, and $j\in\{M,m\}$ specifies the allele at the novel sex-determining locus $\mathbf{M}$.
 The gamete frequencies from each sex sum to one, $\sum_{i,j}x_{ij}^{\Hermaphrodite}+y_{ij}^{\Hermaphrodite}=1$.
@@
 The frequencies of $XX$ zygotes are then denoted as $xx_{ij}$, $XY$ zygotes as $xy_{ij}$, and $YY$ zygotes as $yy_{ij}$. 
-In $XX$ and $YY$ zygotes, individuals with diploid genotype $ij$ are equivalent to those with diploid genotype $ji$; for simplicity, we use $xx_{ij}$ and $yy_{ij}$ to denote the average of these frequencies, $xx_{ij}=(X_{i}^{\female,s}X_{j}^{\male,s}+X_{j}^{\female,s}X_{i}^{\male,s})/2$ and $yy_{ij}=(Y_{i}^{\female,s}Y_{j}^{\male,s}+Y_{j}^{\female,s}Y_{i}^{\male,s})/2$.
-
-Denoting the \textbf{M} locus genotype by $b$ ($b\in \{MM$, $Mm$, $mm$\}) and the \textbf{X} locus genotype by $c$ ($c\in \{XX$, $XY$, $YY$\}), zygotes develop as females with probability $k_{bc}$. 
+In $XX$ and $YY$ zygotes, individuals with diploid genotype $ij$ are equivalent to those with diploid genotype $ji$; for simplicity, we use $xx_{ij}$ and $yy_{ij}$ with $i\neq j$ to denote the average of these frequencies, $xx_{ij}=(x_{i}^{\female,s}x_{j}^{\male,s}+x_{j}^{\female,s}x_{i}^{\male,s})/2$ and $yy_{ij}=(y_{i}^{\female,s}y_{j}^{\male,s}+y_{j}^{\female,s}y_{i}^{\male,s})/2$.
+
+Denoting the \textbf{M} locus genotype by $b \in \{MM, Mm, mm\}$ and the \textbf{X} locus genotype by $c \in \{XX, XY, YY\}$, zygotes develop as females with probability $k_{bc}$. 
 Therefore, the frequencies of $XX$ females are given by $xx_{ij}^{\female}=k_{bc}xx_{ij}$, $XY$ females are given by $xy_{ij}^{\female}=k_{bc}xy_{ij}$, and $YY$ females are given by $yy_{ij}^{\female}=k_{bc}yy_{ij}$.
@@
 In addition, we can consider any epistatic dominance relationship between the two sex-determining loci. 
-Typically, we assume that the ancestral sex-determining system (\textbf{X} locus) is $XY$ ($k_{MMXX}=1$ and $k_{MMXY}=k_{MMYY}=0$) and epistatically recessive to a dominant novel sex-determining locus, \textbf{M} ($k_{Mmc}=k_{mmc}=k$).
-
-Selection among diploids then occurs according to the diploid genotype at the \textbf{A} locus, $l$, for an individual of type $ij$ ($l \in \{AA$, $Aa$, $aa$\}, see Table \ref{tab:fitnesstable}). 
+For example, here we assume that the ancestral sex-determining system (\textbf{X} locus) is $XY$ ($k_{MMXX}=1$ and $k_{MMXY}=k_{MMYY}=0$) or $ZW$ ($k_{MMZZ}=0$ and $k_{MMZW}=k_{MMWW}=1$) and epistatically recessive to a dominant novel sex-determining locus, \textbf{M} ($k_{Mmc}=k_{mmc}=k$).
+
+Selection among diploids then occurs according to the diploid genotype at the \textbf{A} locus, $l \in \{AA, Aa, aa\}$, for an individual of type $ij$ (see Table \ref{tab:fitnesstable}). 
 The diploid frequencies after selection in sex $\Hermaphrodite$ are given by $xx_{ij}^{\Hermaphrodite,s}=w_{l}^{\Hermaphrodite} xx_{ij}/\bar{w}^{\Hermaphrodite}$, $xy_{ij}^{\Hermaphrodite,s}=w_{l}^{\Hermaphrodite} xy_{ij}/\bar{w}^{\Hermaphrodite}$, and $yy_{ij}^{\Hermaphrodite,s}=w_{l}^{\Hermaphrodite} yy_{ij}/\bar{w}^{\Hermaphrodite}$, where $\bar{w}^{\Hermaphrodite}= \sum_{i=1}^{4}\sum_{j=1}^{4}w_{l}^{\Hermaphrodite}xx_{ij}+w_{l}^{\Hermaphrodite}xy_{ij}+w_{l}^{\Hermaphrodite}yy_{ij}$ is the mean fitness of individuals of sex $\Hermaphrodite$.
@@
 %We can also assume that recombination is sex specific and/or affected by the M locus - but generally we don't so I just describe $R=R_{f}=R, r_{MM,d}=r_{Mm,d}=r_{mm,d}=r, \chi_{m}=\chi_{f}=\chi$.
-Here, we allow the relative locations of the SDR, \textbf{A}, and \textbf{M} loci to be generic by using three parameters to describe the recombination rates between them.
+Here, we allow any relative locations for the SDR, \textbf{A}, and \textbf{M} loci by using three parameters to describe the recombination rates between them. 
 $R$ is the recombination rate between the \textbf{A} locus and the \textbf{M} locus, $\chi$ is the recombination rate between the \textbf{M} locus and the \textbf{X} locus, and $r$ is the recombination rate between the \textbf{A} locus and the \textbf{X} locus.
@@
 \begin{split}
-X_{MA}^{{\Hermaphrodite}'}=&xx_{11}^{\Hermaphrodite,s}+xx_{13}^{\Hermaphrodite,s}/2+(xx_{12}^{\Hermaphrodite,s}+xx_{14}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
+x_{MA}^{{\Hermaphrodite}'}=&xx_{11}^{\Hermaphrodite,s}+xx_{13}^{\Hermaphrodite,s}/2+(xx_{12}^{\Hermaphrodite,s}+xx_{14}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
 &-R(xx_{14}^{\Hermaphrodite,s}-xx_{23}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
@@
 \begin{split}
-X_{Ma}^{{\Hermaphrodite}'}=&xx_{22}^{\Hermaphrodite,s}+xx_{24}^{\Hermaphrodite,s}/2+(xx_{12}^{\Hermaphrodite,s}+xx_{23}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
+x_{Ma}^{{\Hermaphrodite}'}=&xx_{22}^{\Hermaphrodite,s}+xx_{24}^{\Hermaphrodite,s}/2+(xx_{12}^{\Hermaphrodite,s}+xx_{23}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
 &-R(xx_{23}^{\Hermaphrodite,s}-xx_{14}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
@@
 \begin{split}
-X_{mA}^{{\Hermaphrodite}'}=&xx_{33}^{\Hermaphrodite,s}+xx_{13}^{\Hermaphrodite,s}/2+(xx_{23}^{\Hermaphrodite,s}+xx_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
+x_{mA}^{{\Hermaphrodite}'}=&xx_{33}^{\Hermaphrodite,s}+xx_{13}^{\Hermaphrodite,s}/2+(xx_{23}^{\Hermaphrodite,s}+xx_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
 &-R(xx_{23}^{\Hermaphrodite,s}-xx_{14}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
@@
 \begin{split}
-X_{ma}^{{\Hermaphrodite}'}=&xx_{44}^{\Hermaphrodite,s}+xx_{34}^{\Hermaphrodite,s}/2+(xx_{14}^{\Hermaphrodite,s}+xx_{24}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
+x_{ma}^{{\Hermaphrodite}'}=&xx_{44}^{\Hermaphrodite,s}+xx_{34}^{\Hermaphrodite,s}/2+(xx_{14}^{\Hermaphrodite,s}+xx_{24}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
 &-R(xx_{14}^{\Hermaphrodite,s}-xx_{23}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
@@
 \begin{split}
-Y_{MA}^{{\Hermaphrodite}'}=&yy_{11}^{\Hermaphrodite,s}+yy_{13}^{\Hermaphrodite,s}/2+(yy_{12}^{\Hermaphrodite,s}+yy_{14}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
+y_{MA}^{{\Hermaphrodite}'}=&yy_{11}^{\Hermaphrodite,s}+yy_{13}^{\Hermaphrodite,s}/2+(yy_{12}^{\Hermaphrodite,s}+yy_{14}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
 &-R(yy_{14}^{\Hermaphrodite,s}-yy_{23}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
@@
 \begin{split}
-Y_{Ma}^{{\Hermaphrodite}'}=&yy_{22}^{\Hermaphrodite,s}+yy_{24}^{\Hermaphrodite,s}/2+(yy_{12}^{\Hermaphrodite,s}+yy_{23}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
+y_{Ma}^{{\Hermaphrodite}'}=&yy_{22}^{\Hermaphrodite,s}+yy_{24}^{\Hermaphrodite,s}/2+(yy_{12}^{\Hermaphrodite,s}+yy_{23}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
 &-R(yy_{23}^{\Hermaphrodite,s}-yy_{14}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
@@
 \begin{split}
-Y_{mA}^{{\Hermaphrodite}'}=&yy_{33}^{\Hermaphrodite,s}+yy_{13}^{\Hermaphrodite,s}/2+(yy_{23}^{\Hermaphrodite,s}+yy_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
+y_{mA}^{{\Hermaphrodite}'}=&yy_{33}^{\Hermaphrodite,s}+yy_{13}^{\Hermaphrodite,s}/2+(yy_{23}^{\Hermaphrodite,s}+yy_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
 &-R(yy_{23}^{\Hermaphrodite,s}-yy_{14}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
@@
 \begin{split}
-Y_{ma}^{{\Hermaphrodite}'}=&yy_{44}^{\Hermaphrodite,s}+yy_{34}^{\Hermaphrodite,s}/2+(yy_{14}^{\Hermaphrodite,s}+yy_{24}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
+y_{ma}^{{\Hermaphrodite}'}=&yy_{44}^{\Hermaphrodite,s}+yy_{34}^{\Hermaphrodite,s}/2+(yy_{14}^{\Hermaphrodite,s}+yy_{24}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
 &-R(yy_{14}^{\Hermaphrodite,s}-yy_{23}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
@@
 The full system is therefore described by 16 recurrence equations (three diallelic loci in two sexes, $2^3 \times 2 = 16$). 
-However, some diploid types are not produced under a given sex determination system. 
+However, some diploid types are not produced under a given sex-determination system. 
 For example, with the $M$ allele fixed and ancestral $XY$ sex determination, there are no $m$ alleles, $XX$ males, $XY$ females, or $YY$ females ($xx_{11}^{\male}=xx_{12}^{\male}=xx_{22}^\male=xy_{11}^{\female}=xy_{12}^{\female}=xy_{21}^{\female}=xy_{22}^\female=yy_{11}^{\female}=yy_{12}^{\female}=yy_{22}^\female=0$).
@@
 We also track the total frequency of Y among male gametes, $q$, which may deviate from $1/2$ due to meiotic drive in males. 
-These four variables determine the frequencies of the six resident gamete types: $X_{MA}^{\female}=p_{X}^{\female}$, $X_{Ma}^{\female}=1-p_{X}^{\female}$, $X_{MA}^{\male}=(1-q)p_{X}^{\male}$, $X_{Ma}^{\male}=(1-q)(1-p_{X}^{\male})$, $Y_{MA}^{\male}=q p_{Y}^{\male}$, and $Y_{Ma}^{\male}=q(1-p_{Y}^{\male})$.
+These four variables determine the frequencies of the six resident gamete types: $x_{MA}^{\female}=p_{X}^{\female}$, $x_{Ma}^{\female}=1-p_{X}^{\female}$, $x_{MA}^{\male}=(1-q)p_{X}^{\male}$, $x_{Ma}^{\male}=(1-q)(1-p_{X}^{\male})$, $y_{MA}^{\male}=q p_{Y}^{\male}$, and $y_{Ma}^{\male}=q(1-p_{Y}^{\male})$.
 Mean fitnesses in the resident population are given in table \ref{tab:meanfitnesses}.
@@
 
-\subsubsection*{Recombination weak relative to selection (tight linkage)}
+\subsubsection*{Recombination weak relative to selection (tight linkage between \textbf{A} and \textbf{X})}
 
@@
 The \textbf{A} locus will not affect evolution at the novel sex-determining locus, \textbf{M}, if one \textbf{A} allele is fixed on all backgrounds. 
-We therefore focus on the five equilibria that maintain both $A$ and $a$ alleles, of which four are given to leading order by:
+We therefore focus on the five equilibria that maintain both $A$ and $a$ alleles, four of which are given to leading order by:
 
@@
 According to the `small parameter theory' \citep{Karlin:1972ab,Karlin:1972dq}, these stability properties are unaffected by small amounts of recombination between the SDR and \textbf{A} locus, although equilibrium frequencies may be slightly altered.
-For the $a$ allele to be stably fixed on the Y requires that $\bar{w}_{Ya}^{\male}>\bar{w}_{YA}^{\male}$ where $\bar{w}_{Ya}^{\male}=w_{a}^{\male}(2 p_{X}^{\female}(1-\alpha^{\male}) w_{A}^{\female} w_{Aa}^{\male}+ (1-p_{X}^{\female})w_{a}^{\female} w_{aa}^{\male} )$ and $\bar{w}_{YA}^{\male}=w_{A}^{\male}(p_{X}^{\female} w_{A}^{\female} w_{AA}^{\male}+ 2 (1-p_{X}^{\female})\alpha^{\male}w_{a}^{\female} w_{aa}^{\male} )$.
+For the $a$ allele to be stably fixed on the Y requires that $\bar{w}_{Ya}^{\male}>\bar{w}_{YA}^{\male}$ where $\bar{w}_{Ya}^{\male}=w_{a}^{\male}(2 p_{X}^{\female}(1-\alpha^{\male}) w_{A}^{\female} w_{Aa}^{\male}+ (1-p_{X}^{\female})w_{a}^{\female} w_{aa}^{\male} )$ and $\bar{w}_{YA}^{\male}=w_{A}^{\male}(p_{X}^{\female} w_{A}^{\female} w_{AA}^{\male}+ 2 (1-p_{X}^{\female})\alpha^{\male}w_{a}^{\female} w_{Aa}^{\male} )$.
 That is, $Ya$ haplotypes must have higher fitness than $YA$ haplotypes.
-Substituting in $p_{X}^{\female} = \hat{p}_{X}^{\female}$ from above, fixation of the $A$ allele on the Y requires that $\gamma_{i}>0$ where $\gamma_{(A)}=w_{a}^{\male}(2(1-\alpha^{\male})w_{Aa}^{\male} \phi + w_{aa}^{\male} \psi)-w_{A}^{\male}(2\alpha^{\male}w_{Aa}^{\male} \phi + w_{aa}^{\male} \psi)$ for equilibrium $(A)$ and $\gamma_{(B)}=2(1-\alpha^{\male})w_{a}^{\male}w_{Aa}^{\male}-w_{A}^{\male}w_{AA}^{\male}$ for equilibrium $(B)$.
+Substituting in $p_{X}^{\female} = \hat{p}_{X}^{\female}$ from above, fixation of the $a$ allele on the Y requires that $\gamma_{i}>0$ where $\gamma_{(A)}=w_{a}^{\male}(2(1-\alpha^{\male})w_{Aa}^{\male} \phi + w_{aa}^{\male} \psi)-w_{A}^{\male}( w_{AA}^{\male} \phi + 2\alpha^{\male}w_{Aa}^{\male} \psi)$ for equilibrium $(A)$ and $\gamma_{(B)}=2(1-\alpha^{\male})w_{a}^{\male}w_{Aa}^{\male}-w_{A}^{\male}w_{AA}^{\male}$ for equilibrium $(B)$.
 Stability of a polymorphism on the X chromosome (equilibrium $A$) further requires that $\phi >0$ and $\psi >0$. 
-Fixation of the $a$ allele on the X (equilibrium ($B$)) is mutually exclusive with equilibrium $(A)$ and requires $\psi<0$ and $w_{A}^{\female}w_{AA}^{\female}>(1-\alpha^{\female})w_{a}^{\female}w_{Aa}^{\female}$.
+Fixation of the $a$ allele on the X (equilibrium $B$) is mutually exclusive with equilibrium $(A)$ and requires $\psi<0$ and $w_{A}^{\female}w_{AA}^{\female}>(1-\alpha^{\female})w_{a}^{\female}w_{Aa}^{\female}$.
 
@@
 
+A rare neo-Y or neo-W will spread from a given ancestral equilibrium when the leading eigenvalue, $\lambda$, of the Jacobian matrix derived from the eight mutant recursion equations (given by \ref{eq:recursions}c,d,g,h), evaluated at the ancestral equilibrium, is greater than one.
+However, because a neo-Y (neo-W) is always in males (females) and is epistatically dominant to the ancestral sex-determining locus, we need only two recursion equations (e.g., tracking the change in the frequency of neo-Y-$A$ and neo-Y-$a$ gametes from males) and thus the leading eigenvalue is the largest solution to a quadratic characteristic polynomial $\lambda^2 + b\lambda + c = 0$.
+It can be shown (see supplementary Mathematica file) that the coefficients are $b= - (\lambda_{mA} + \lambda_{ma})+(\rho_{mA} + \rho_{ma})$ and $c = (\lambda_{mA}-\rho_{mA}) (\lambda_{ma}-\rho_{ma}) -\rho_{mA} \rho_{ma}$, where $\lambda_{mi}$ is the multiplicative growth rate of the frequency of mutants on background $i\in\{A,a\}$, without accounting for loss due to recombination, and $\rho_{mi}$ is the rate at which mutants on background $i\in\{A,a\}$ recombine onto the other \textbf{A} locus background in heterozygotes.
+The leading eigenvalue is then greater than one whenever $\lambda_{mA}>1$ and $\lambda_{ma}>1$, less than one whenever $\lambda_{mA}<1$ and $\lambda_{ma}<1$, and greater than one whenever  $\lambda_{mA}>1$ or $\lambda_{ma}>1$ and $\rho_{ma} (\lambda_{mA}-1) + \rho_{mA} (\lambda_{ma}-1) > 0$.
+
+For tight linkage between the ancestral sex-determining locus and the selected locus we can calculate each of these terms exactly, while for weak selection we take a Taylor series of the leading eigenvalue.
+
 \subsubsection*{Recombination weak relative to selection (tight linkage between \textbf{A} and \textbf{X})}
@@
 We disregard neo-Y mutations, which never spread given that the ancestral population is at a stable equilibrium.
-At equilibrium $(B)$ we have
+
+Starting with the simpler equilibrium $(B)$, the terms of the characteristic polynomial are
 
@@
 \begin{align}
-\lambda_{mA}&=\frac{w_{A}^\male w_{AA}^\female \alpha^\male + 2 w_{a}^\male w_{Aa}^\female \alpha^\female(1-\alpha^\male)}{2w_{A}^\male  w_{AA}^\female \alpha^\male} \\
-\lambda_{ma}&=\frac{w_{a}^\female(w_{a}^\male w_{aa}^\female (1-\alpha^\male) + 2 w_{A}^\male w_{Aa}^\female(1-\alpha^\female)\alpha^\male)}{2w_{A}^\male w_{A}^\female w_{AA}^\female \alpha^\male} \\
-\rho_{mA}&= \frac{R w_{a}^\male w_{Aa}^\female \alpha^\female(1-\alpha^\male)}{w_{A}^\male w_{AA}^
-\female \alpha^\male} \\
-\rho_{ma}&= \frac{R w_{a}^\female w_{Aa}^\female (1-\alpha^\female)}{w_{A}^\female w_{AA}^
-\female} 
+\lambda_{mA}&= (2 \alpha^\male)^{-1}\frac{w_{A}^\female \left[w_{A}^\male w_{AA}^\female \alpha^\male + 2 w_{a}^\male w_{Aa}^\female \alpha^\female(1-\alpha^\male)\right]}{ w_{A}^\male w_{A}^\female w_{AA}^\female } \\
+\lambda_{ma}&= (2 \alpha^\male)^{-1} \frac{w_{a}^\female \left[ w_{a}^\male w_{aa}^\female (1-\alpha^\male) + 2 w_{A}^\male w_{Aa}^\female(1-\alpha^\female)\alpha^\male\right]}{w_{A}^\male w_{A}^\female w_{AA}^\female } \\
+\rho_{mA}&= (2 \alpha^\male)^{-1}\frac{R w_{a}^\male w_{A}^\female w_{Aa}^\female \alpha^\female(1-\alpha^\male)}{w_{A}^\male w_{A}^\female w_{AA}^\female } \\
+\rho_{ma}&= (2 \alpha^\male)^{-1}\frac{R w_{A}^\male w_{a}^\female w_{Aa}^\female (1-\alpha^\female)\alpha^\male}{w_{A}^\male w_{A}^\female w_{AA}^\female} 
 \end{align}
@@
 \noindent
-In this case, the zygotic sex ratio ($\zeta$) is given by the difference in haploid selection in males on $a$ (fixed on the Y) and $A$ (fixed on the X) alleles, i.e., there are more males than females ($\zeta<1/2$) if $\alpha^\male<1/2$ and/or $w_{a}^\male>w_{A}^\male$.
+In this case, the zygotic sex ratio ($\zeta$) is given by the difference in haploid selection in males on $a$ (fixed on the Y) and $A$ (fixed on the X) alleles, i.e., there are more males than females if $\zeta = 2\alpha^\male w_A^\male / (w_a^\male + w_A^\male)<1/2$.
+%$\alpha^\male<1/2$ and/or $w_{a}^\male>w_{A}^\male$.
 Populations with a male biased zygotic sex ratio are more permissive to invasion by a neo-W ($\lambda_{mA}$ and $\lambda_{ma}$ larger).
@@
 Zygotes carrying dominant neo-W alleles will develop as females regardless of their genotype at the XY locus. Therefore, females result from matings with either X-$A$ or Y-$a$ male gametes. 
-The relative proportion of these male gametes is also determined by haploid selection in males; mating with a Y-$a$ male gamete is more likely if the $a$ allele is favoured during male gamete production or competition ($\alpha^\male<1/2$ and/or $w_{a}^\male>w_{A}^\male$).
+The relative proportion of these male gametes is also determined by haploid selection in males; mating with a Y-$a$ male gamete is more likely if the $a$ allele is favoured during male gamete production or competition ($\zeta<1/2$).
 
 Furthermore, haploid selection in females can directly select upon neo-W-$A$ or neo-W-$a$ haplotypes. 
-An $A$-bearing female gamete has the same fitness during haploid competition as the resident $A$-bearing female gametes. 
-On the other hand, $a$-bearing female gametes can be favoured or disfavoured during female haploid competition (favoured if $w_{a}^\female>w_{A}^\female$). 
+A neo-W-$A$ female gamete has the same fitness during haploid competition as resident $A$-bearing female gametes. 
+On the other hand, neo-W-$a$ female gametes can be favoured or disfavoured during female haploid competition (favoured if $w_{a}^\female>w_{A}^\female$). 
 Meiotic drive in females ($\alpha^\female$) similarly affects the fitness of these haplotypes, except that meiotic drive only occurs in heterozygotes.
@@
 The other terms in equations \eqref{Binvasion} are more easily interpreted if we assume that there is no haploid selection in either sex, in which case $\lambda_{mA}>1$ when $w_{Aa}^\female>w_{AA}^\female$ and $\lambda_{ma}>1$ when $(w_{Aa}^\female+w_{aa}^\female)/2>w_{AA}^\female$.
-These conditions cannot be met under purely sexually antagonistic selection, where $a$ is directionally favoured in males ($w_{AA}^\male>w_{Aa}^\male>w_{aa}^\male$) and $A$ is directionally favoured in females ($w_{AA}^\female>w_{Aa}^\female>w_{aa}^\female$).
+These conditions cannot be met under purely sexually-antagonistic selection, where $a$ is directionally favoured in males ($w_{AA}^\male>w_{Aa}^\male>w_{aa}^\male$) and $A$ is directionally favoured in females ($w_{AA}^\female>w_{Aa}^\female>w_{aa}^\female$).
 Essentially, the X is already as specialized as possible for the female beneficial allele (X-A is fixed), and the neo-W often makes daughters with the Y-a haplotype, increasing the flow of $a$ alleles into females, which reduces the fitness of those females.
 
-If selection doesn't uniformly favour $A$ in females, however, neo-W-$A$ haplotypes and/or neo-W-$a$ haplotypes can spread at this equilibium.
-If $\lambda_{mA}>1$ (requiring $w_{Aa}^\female>w_{AA}^\female$), the implication is that $a$ is favoured by selection in females despite $A$ being fixed on the X, which must require that X-$A$ is sufficiently favoured in males to drive the frequency of X-$A$ to one (specifically, from the stability conditions, we must have $w_{Aa}^\male/((w_{aa}^\male+w_{Aa}^\male)/2)>w_{Aa}^\female/w_{AA}^\female$).
-
-Even if $w_{Aa}^\female>w_{AA}^\female$, the neo-W can spread alongside the $a$ allele ($\lambda_{ma}>1$) if there is sufficiently strong underdominance in females ($w_{aa}^\female>w_{Aa}^\female$), such that $(w_{Aa}^\female+w_{aa}^\female)/2>w_{AA}^\female$.
-In this case, $a$ is not favored in females near the equilibrium where females are $AA$ (comparing $Aa$ to $AA$ genotypes) and yet the neo-W with $a$ can spread because it produces female $aa$ individuals by capturing Y-$a$ haplotypes.
+If selection doesn't uniformly favour $A$ in females, however, neo-W-$A$ haplotypes and/or neo-W-$a$ haplotypes can spread ($\lambda_{mA}>1$ and/or $\lambda_{ma}>1$) at this equilibrium.
+%If $\lambda_{mA}>1$ (requiring $w_{Aa}^\female>w_{AA}^\female$), the implication is that the neo-W can spread alongside the $A$ allele, despite the fact that the neo-W sometimes brings $Y-a$ haplotypes into females, because $a$ is favoured by selection in females despite $A$ being fixed on the X.
+A neo-W can spread alongside the $A$ allele ($\lambda_{mA}>1$), despite the fact that a neo-W brings $Y-a$ haplotypes into females, when $w_{Aa}^\female>w_{AA}^\female$.
+In this case the $a$ allele is favoured by selection in females despite $A$ being fixed on the X.
+For this equilibrium to be stable, X-$A$ must be sufficiently favoured in males to keep the frequency of X-$A$ at one (specifically, from the stability conditions, we must have $w_{Aa}^\male/((w_{aa}^\male+w_{Aa}^\male)/2)>w_{Aa}^\female/w_{AA}^\female$).
+
+Under this same condition, $w_{Aa}^\female>w_{AA}^\female$, the neo-W can also spread alongside the $a$ allele ($\lambda_{ma}>1$) if there is sufficiently strong underdominance in females ($w_{aa}^\female>w_{Aa}^\female$), such that $(w_{Aa}^\female+w_{aa}^\female)/2>w_{AA}^\female$.
+In this case, $a$ is not favored in females near the equilibrium where females are $AA$ (comparing $Aa$ to $AA$ genotypes) and yet the neo-W can spread with $a$ because it produces female $aa$ individuals by capturing Y-$a$ haplotypes.
+
+When both haplotypes can spread on their own ($\lambda_{mA}>1$ and $\lambda_{ma}>1$), the neo-W invades regardless the recombination rate between it and the selected locus, $R$.
+When neither haplotype can spread ($\lambda_{mA}<1$ and $\lambda_{ma}<1$) the neo-W can never invade.
+And when only one haplotype can spread on its own the neo-W invades only when the rate of recombination onto the favourable background is sufficiently larger than the rate of recombination off this background (i.e., equation\ref{eq:lambdasGen} is satisfied).
 
@@
 \noindent
-Without haploid selection $\lambda_{mA}>1$ if and only if
-
-\begin{equation}
+As with equilibrium (B), the conditions for invasion are easier to interpret in the absence of haploid selection, which again modifies invasion fitnesses by directly selecting upon neo-W haplotypes.
+For instance, without haploid selection, the neo-W-$A$ haplotype spreads ($\lambda_{mA}>1$) if and only if
+
+\begin{equation}\label{eq:BeqWAspread}
 2(w_{Aa}^\female-w_{aa}^\female)w_{AA}^\male \psi^2 > (w_{AA}^\female-w_{Aa}^\female)w_{Aa}^\male \phi (\phi-\psi)
@@
 \noindent  
-NOTES:  
-$\phi-\psi=w_{AA}^\female w_{Aa}^\male-w_{aa}^\female w_{aa}^\male$ and both $\phi$ and $\psi$ are positive by the equilibrium conditions. 
-Most important advance on the descriptions given for the (B) equilibrium is that this can be met with `purely' sexually antagonistic selection (directional but opposite in both sexes). 
-Basically, because W-A haplotypes never produce $aa$ females, that can be an advantage, even though they also produce a lot of $Aa$ females through obtaining the $a$ from Y-gametes. 
-Can be seen from the fact that the condition will be more easily met if there is a large benefit from never producing $aa$ females (LHS larger, although note that $w_{Aa}^\female$ and $w_{aa}^\female$ enter into $\phi$ and $\psi$ terms too).
-Even if $R\neq 0$, there can be invasion with purely sexually antagonistic selection.
-
-Without haploid selection $\lambda_{ma}>1$ if and only if
-
-\begin{equation}
-w_{Aa}^\male \phi^2(w_{aa}^\female + w_{Aa}^\female-2w_{AA}^\female) + (w_{aa}^\female-w_{Aa}^\female)(w_{Aa}^\male+2w_{AA}^\male) \phi \psi >0
+where $\phi-\psi=w_{AA}^\female w_{Aa}^\male-w_{aa}^\female w_{aa}^\male$ and both $\phi$ and $\psi$ are positive when equilibrium (A) is stable. 
+In contrast to equilibrium (B), a neo-W haplotype can spread under purely sexually-antagonistic selection  ($w_{AA}^\male>w_{Aa}^\male>w_{aa}^\male$ and $w_{AA}^\female>w_{Aa}^\female>w_{aa}^\female$).
+In this case, the neo-W-$A$ haplotype can spread, despite producing a lot of $Aa$ daughters by obtaining the $a$ from Y-gametes, when $aa$ females, which the neo-W-$A$ never makes, are strongly selected against.
+This can be intuited from the fact that \eqref{eq:BeqWAspread} will be more easily met when $w_{Aa}^\female-w_{aa}^\female\approx w_{Aa}^\female$ and $w_{AA}^\female-w_{Aa}^\female\approx 0$, implying $w_{aa}^\female \approx 0$ and $w_{Aa}^\female\approx w_{AA}^\female$ (although this is complicated by the fact that $w_{aa}^\female$ and $w_{Aa}^\female$ affect $\phi$ and $\psi$ too, the intuition holds).
+
+Without haploid selection, the neo-W-$a$ haplotype spreads ($\lambda_{ma}>1$) if and only if
+
+\begin{equation}\label{eq:BeqWaspread}
+(w_{aa}^\female + w_{Aa}^\female-2w_{AA}^\female)w_{Aa}^\male \phi^2 + (w_{aa}^\female-w_{Aa}^\female)(w_{Aa}^\male+2w_{AA}^\male) \phi \psi >0
 \end{equation}
@@
 \noindent
-NOTES: Not met with purely sexually antagonistic selection but met in some other circumstances.
+This condition cannot be met with purely sexually antagonistic selection (as both terms on the left-hand side would then be negative), but it can be met under other circumstances. 
+For example, with overdominance in males there is selection for increased $A$ frequencies on X chromosomes in males, which are always paired with Y-$a$ haplotypes.
+Then, directional selection for $a$ in females maintains a polymorphism at the $\textbf{A}$ locus on the X and by creating selection for decreased $A$ frequencies on X chromosomes in females.
+This scenario selects for a modifier that increases recombination between the sex chromosomes \citep[e.g., blue region of Figure 2d in][]{Otto2014} and facilitates the spread of neo-W-$a$ haplotypes, which create more heterozygote and $aa$ females than ancestral X chromosomes do.
+
+As with equilibrium (B), if both haplotypes can spread ($\lambda_{mA}>1$ and $\lambda_{ma}>1$) then the neo-W invades under any rate of recombination with the selected locus, $R\geq0$. 
+In addition, even when only one haplotype can spread (e.g., under purely sexually-antagonistic selection $\lambda_{mA}>1$ and $\lambda_{ma}<1$), neo-W invasion can still occur under modest rates of recombination between the novel sex-determining and selected loci.
 
@@
 
-With $R=0$ the two eigenvalues are $\lambda_{mA}$ and $\lambda_{ma}$.
-The neo-W can then invade on the $A$ background when $\lambda_{mA}>1$ and the neo-W can invade on the $a$ background when $\lambda_{ma}>1$.
-Even in this case it is difficult to see from equation \ref{Ainvasion} when the neo-W will invade.
-Below we discuss why $\lambda_{mA}$ and $\lambda_{ma}$ might be larger than one and confirm the logic numerically.
-
-For simplicity, consider the case of no haploid selection.
-A polymorphism at the $\mathbf{A}$ locus then requires sexually-antagonistic selection \citep{vanDoorn:2007eu}.
-Given that $a$ is fixed on the Y, one can consider the $a$ allele `male beneficial' and the $A$ allele to be `female beneficial'. 
-Because X chromosomes spend some time in males the frequency of $A$ on the X can reach an intermediate equilibrium (equilibrium A).
-
-We can therefore reason that when a neo-W invades equilibrium (A), it is likely to spread on the $A$ background as W chromosomes are always in females.
-The neo-W can outcompete the ancestral, `comprimising' X because it can specialize on females by fixing the `female beneficial' allele.  
-We call this the `sex-specialist hypothesis'.
-This hypothesis should only work when the benefit of specializing outweighs the cost of bringing Y chromosomes into females (the neo-W is epistatically dominant over the X/Y locus).
-
-One could also reason that, when the neo-W spreads, it does so precisely because it brings Y chromosomes, and their associated alleles, into females, something the X cannot do.
-However, this requires a somewhat particular (perhaps `perverse') equilibrium, where XX females do worse than XY females despite associations on the X and Y being built up by selection.
-One example of such a perverse equilibrium is produced by overdominance in both sexes.
-Overdominance in females selects for an allele frequency of 0.5 on the X ($A$ and $a$ equally frequent, maximizing the number of heterozygotes). 
-However, given that $a$ is fixed on the Y, overdominance in males selects for the X to become more associated with the $A$. 
-Thus, a compromising equilibrium is reached on the X chromosome and females fitness suffers due to the overproduction of $AA$ homozygotes.
-This sets up a scenario in which a neo-W can invade on the $a$ background, despite the fact that $a$ is fixed on the Y and in that sense `male beneficial'.
-We call this the `perverse hypothesis'.
-
-Figure \ref{fig:Region_Plots} shows where the sex-specialist (red) and perverse (blue) hypotheses are valid.
-The left panel demonstrates that both hypotheses can be simultaneously valid with overdominance in both sexes and sex differences in selection, which overlaps the parameter region where there is selection for increased recombination between the sex chromosomes \citep[compare with figure 2a in][]{Otto2014}.
-The right panel shows that the perverse hypothesis is no longer valid when selection is exactly the same in both sexes, despite the fact that there is selection for increased recombination between the sex chromosomes with sufficiently strong overdominance \citep[compare with figure 3 in][]{Otto2014}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Sex-specialist vs perverse hypotheses
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-\includegraphics[width=0.45\linewidth]{regionplot_2a}
-\includegraphics[width=0.45\linewidth]{regionplot_3}\\
-\caption{
-Numerical exploration of where sex-specialist (red) and perverse (blue) hypotheses are valid, i.e., where an internally stable resident equilibrium can be invaded by a neo-W that is perfectly linked with the allele not fixed on the Y (red) or the allele that is fixed on the Y (blue).
-\textbf{(Left)}
-The perverse equilibrium is only valid with overdominance while the sex-specialist hypothesis is valid over the entire range shown.
-Both hypotheses are simultaneously valid over much of the parameter space where increased recombination between the sex chromosomes is selected \citep[][figure 2a]{Otto2014}.
-\textbf{(Right)}
-Only the sex-specialist hypothesis is valid with no sex-differences in selection, despite selection for increased recombination between the sex-chromosomes with strong overdominance \citep[][figure 3]{Otto2014}.
-Parameters: $w_{Aa}^\Hermaphrodite = 1$, $w_a^\Hermaphrodite = w_A^\Hermaphrodite = 1$, $\alpha^\Hermaphrodite = 1/2$, $r=R=0$, and in left panel $w_{aa}^\female = w_{AA}^\female = 0.6$.
-}
-\label{fig:Region_Plots}
-\end{figure}
+%With $R=0$ the two eigenvalues are $\lambda_{mA}$ and $\lambda_{ma}$.
+%The neo-W can then invade on the $A$ background when $\lambda_{mA}>1$ and the neo-W can invade on the $a$ background when $\lambda_{ma}>1$.
+%Even in this case it is difficult to see from equation \ref{Ainvasion} when the neo-W will invade.
+%Below we discuss why $\lambda_{mA}$ and $\lambda_{ma}$ might be larger than one and confirm the logic numerically.
+%
+%
+%For simplicity, consider the case of no haploid selection.
+%A polymorphism at the $\mathbf{A}$ locus then requires sexually-antagonistic selection \citep{vanDoorn:2007eu}.
+%Given that $a$ is fixed on the Y, one can consider the $a$ allele `male beneficial' and the $A$ allele to be `female beneficial'. 
+%Because X chromosomes spend some time in males the frequency of $A$ on the X can reach an intermediate equilibrium (equilibrium A).
+%
+%We can therefore reason that when a neo-W invades equilibrium (A), it is likely to spread on the $A$ background as W chromosomes are always in females.
+%The neo-W can outcompete the ancestral, `comprimising' X because it can specialize on females by fixing the `female beneficial' allele.  
+%We call this the `sex-specialist hypothesis'.
+%This hypothesis should only work when the benefit of specializing outweighs the cost of bringing Y chromosomes into females (the neo-W is epistatically dominant over the X/Y locus).
+%
+%One could also reason that, when the neo-W spreads, it does so precisely because it brings Y chromosomes, and their associated alleles, into females, something the X cannot do.
+%However, this requires a somewhat particular (perhaps `perverse') equilibrium, where XX females do worse than XY females despite associations on the X and Y being built up by selection.
+%One example of such a perverse equilibrium is produced by overdominance in both sexes.
+%Overdominance in females selects for an allele frequency of 0.5 on the X ($A$ and $a$ equally frequent, maximizing the number of heterozygotes). 
+%However, given that $a$ is fixed on the Y, overdominance in males selects for the X to become more associated with the $A$. 
+%Thus, a compromising equilibrium is reached on the X chromosome and females fitness suffers due to the overproduction of $AA$ homozygotes.
+%This sets up a scenario in which a neo-W can invade on the $a$ background, despite the fact that $a$ is fixed on the Y and in that sense `male beneficial'.
+%We call this the `perverse hypothesis'.
+%
+%Figure \ref{fig:Region_Plots} shows where the sex-specialist (red) and perverse (blue) hypotheses are valid.
+%The left panel demonstrates that both hypotheses can be simultaneously valid with overdominance in both sexes and sex differences in selection, which overlaps the parameter region where there is selection for increased recombination between the sex chromosomes \citep[compare with figure 2a in][]{Otto2014}.
+%The right panel shows that the perverse hypothesis is no longer valid when selection is exactly the same in both sexes, despite the fact that there is selection for increased recombination between the sex chromosomes with sufficiently strong overdominance \citep[compare with figure 3 in][]{Otto2014}.
+%
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%Sex-specialist vs perverse hypotheses
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\begin{figure}[!h]
+%\centering
+%\includegraphics[width=0.45\linewidth]{regionplot_2a}
+%\includegraphics[width=0.45\linewidth]{regionplot_3}\\
+%\caption{
+%Numerical exploration of where sex-specialist (red) and perverse (blue) hypotheses are valid, i.e., where an internally stable resident equilibrium can be invaded by a neo-W that is perfectly linked with the allele not fixed on the Y (red) or the allele that is fixed on the Y (blue).
+%\textbf{(Left)}
+%The perverse equilibrium is only valid with overdominance while the sex-specialist hypothesis is valid over the entire range shown.
+%Both hypotheses are simultaneously valid over much of the parameter space where increased recombination between the sex chromosomes is selected \citep[][figure 2a]{Otto2014}.
+%\textbf{(Right)}
+%Only the sex-specialist hypothesis is valid with no sex-differences in selection, despite selection for increased recombination between the sex-chromosomes with strong overdominance \citep[][figure 3]{Otto2014}.
+%Parameters: $w_{Aa}^\Hermaphrodite = 1$, $w_a^\Hermaphrodite = w_A^\Hermaphrodite = 1$, $\alpha^\Hermaphrodite = 1/2$, $r=R=0$, and in left panel $w_{aa}^\female = w_{AA}^\female = 0.6$.
+%}
+%\label{fig:Region_Plots}
+%\end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-With weak selection the leading eigenvalue for any $k$ is given, up to order $\epsilon^2$, by equation \ref{eq:lambda_ESD_k}.
+With weak selection the leading eigenvalue, $\lambda$, for any $k$, is given up to order $\epsilon^2$ by equation \ref{eq:lambda_ESD_k}.
+Scenarios leading to $\lambda>1$ are discussed in the main text.
 

### 2017-07-04 LaTeX/Turnover.tex
sending draft to MScott; new figures to sallys liking and wrote about haploid selection in tight linkage results

@@
 Neo-W alleles, on the other hand, can invade an ancestral XY system under some conditions (given in detail in the appendix). 
+The full characteristic polynomials are given in the appendix (equations \ref{Binvasion} and \ref{Ainvasion}).
 Briefly, neo-W-$A$ and/or neo-W-$a$ haplotypes can spread when rare in the absence of recombination ($\lambda_{ma}>1$ and/or $\lambda_{mA}>1$), depending on the ancestral sex-ratio and allele frequencies.
-Firstly, haploid selection causes the zygotic sex ratio to be male biased ($\zeta<1/2$) when the $a$ allele (which is fixed on the Y) is favoured during haploid competition among male gametes or by meiotic drive in males.
+Below we discuss the main forces determining the spread of these neo-W haplotypes and the impact of recombination for the overall success of the neo-W.
+To simplify our discussion we first outline the potential effects of haploid selection and then consider diploid selection in its absence.
+
+Haploid selection impacts the spread of neo-W haplotypes in three ways.
+Firstly, the zygotic sex ratio becomes male biased ($\zeta<1/2$) when the $a$ allele (which is fixed on the Y) is favoured during competition among male gametes or by meiotic drive in males. 
 This facilitates the spread of a neo-W because neo-W alleles cause the zygotes that carry them to develop as the rarer, female, sex. 
-Secondly, neo-W alleles can also be favoured via their associations with \textbf{A} locus alleles that confer a fitness advantage in females.
-\textcolor{red}{In the main text we explore the effect of these associations under the simplifying assumption of no haploid selection, which means that there are no zygotic sex ratio biases.}
-Haploid selection modifies invasion by exerting direct selection on neo-W haplotypes (i.e., competition among eggs favours one neo-W haplotype at the expense of the other while female meiotic drive will affect the spread of neo-W haplotypes only when they arise in $Aa$ heterozygotes).
-The full characteristic polynomials, including the effect of haploid selection, are given in the appendix (equations \ref{Binvasion} and \ref{Ainvasion}).
-
-%\textcolor{red}{SUMMARIZE DETAILS OF APPENDIX HERE}
-In the absence of haploid selection and with the $A$ allele is fixed on the X, it is possible for both neo-W haplotypes can spread, and thus neo-W invasion can occur regardless of its linkage to the selected locus.
+Secondly, haploid selection in males affects the diploid genotypes of females by altering the allele frequencies in the male gametes that female gametes pair with.
+For instance, because an epistatically dominant neo-W always causes its carrier to become female, it creates females who carry either $Y-a$ or $X$ genotypes from their father.
+Thus, because when there is a polymorphism the $X$ carries some non-zero frequency of $A$, haploid selection in males impacts the diploid genotypes of females (e.g., creating more $Aa$ females when drive in males favours $Y-a$).
+How this affects the spread of the neo-W then depends on diploid and haploid selection in females.
+Thirdly, female drive and gamete competition directly select on neo-W haplotypes.
+Drive for $A$ in females favours neo-W-$A$ haplotypes, at a cost to neo-W-$a$ haplotypes, and vice-versa when there is drive for $a$.
+The impact of this drive depends on how often XX and neo-W females are heterozygous.
+Competition among female gametes acts similarly, and depends on the frequency of $A$ on resident X chromosomes (e.g., competition among eggs has no affect on the initial spread of the neo-W-$A$ haplotype when $A$ is fixed on the X).
+Because haploid selection in females favours one neo-W haplotype at the expense of the other, recombination off the favoured background becomes more detrimental as it becomes more favoured.
+Thus higher rates of recombination between the neo-W and the selected locus, $R$, can lead to smaller leading eigenvalues when there is haploid selection in females.
+
+In the absence of haploid selection and with the $A$ allele is fixed on the X, it is possible for both neo-W haplotypes can spread ($\lambda_{mA}>1$ and $\lambda_{ma}>1$ in \ref{Binvasion}), and thus neo-W invasion can occur regardless of its linkage to the selected locus.
 Invasion does not occur with purely sexually-antagonistic selection (i.e., $a$ directionally favoured in males and $A$ directionally favoured in females) because the X is then already as specialized as possible on the female sex.
-However, if, for example, $AA$ individuals suffer a fitness cost in females, yet $A$ is fixed on the X due to strong overdominance in males, both neo-W-$A$ and neo-W-$a$ haplotypes spread because they produce fewer unfit $AA$ females and never experience counterselection in males.
+However, if, for example, $AA$ individuals suffer a fitness cost in females, yet $A$ is fixed on the X due to strong overdominance in males, both neo-W-$A$ and neo-W-$a$ haplotypes spread because they produce fewer unfit $AA$ females and never experience counter-selection in males.
 This is true even for the neo-W-$A$ haplotype because it can pair with a $Y-a$ haplotype and still be female. 
-Because both haplotypes can spread alone, the rate of recombination between the neo-W and the selected locus, $R$, does not prevent invasion, and the system can thus evolve looser sex-linkage (e.g., the neo-W could arise on an autosome, $R=1/2$).
+When both haplotypes can spread alone the rate of recombination between the neo-W and the selected locus, $R$, does cannot prevent invasion, and thus the system can evolve looser sex-linkage (e.g., the neo-W could arise on an autosome, $R=1/2$).
 Even when only one haplotype can spread, invasion can still occur up to some positive rate of recombination, $R>0$ (as long as equation \ref{eq:lambdasGen} is satisfied). 
@@
 
-It is also possible, in the absence of haploid selection, for a neo-W to invade when there is a stable polymorphism at the $\mathbf{A}$ locus on X chromosomes.
-For example, overdominance in males and strong directional selection for $a$ in females creates a scenario that favours the spread of both neo-W haplotypes at equilibrium, as both bring more $a$ alleles into females and never experience counterselection in males.
-Thus, as in the case of the $A$ being fixed on the X, looser sex-linkage can evolve with a polymorphic X and this is expected under the same scenarios that select for a modifier that increases recombination between the sex chromosomes \citep[blue regions of Figure 2 in][]{Otto2014}.
+In the absence of haploid selection it is also possible for a neo-W to invade when there is a stable polymorphism at the $\mathbf{A}$ locus on X chromosomes.
+For example, overdominance in males and strong directional selection for $a$ in females creates a scenario that favours the spread of both neo-W haplotypes at equilibrium ($\lambda_{mA}>1$ and $\lambda_{ma}>1$ in \ref{Ainvasion}), as both haplotypes bring more $a$ alleles into females and never experience counter-selection in males.
+Thus, as in the case of the $A$ being fixed on the X, looser sex-linkage can evolve with a polymorphic X (i.e., $\lambda>1$ with $R>0$) and this is expected under the same scenarios that select for a modifier that increases recombination between the sex chromosomes \citep[blue regions of Figure 2 in][]{Otto2014}.
 
@@
 
-\textcolor{red}{I messed with the sex-ratio selection paragraphs to tone down our "it doesn't matter" speech from before.}
+\textcolor{red}{I messed with the sex-ratio selection paragraphs to tone down our "it doesn't matter" speech from before. Have at any amendments you'd like to make.}
 %SEX-RATIO SELECTION
@@
 \section*{Figures}
-\newpage
+%\newpage
 
@@
 	\node[] (plot) {\includegraphics[width=\linewidth]{Combination_Turnover_Ratio}};
-	\node[above = 0cm of plot, xshift = -80] () {XY $\rightarrow$ ZW};
-	\node[above = 0cm of plot, xshift = 120] () {ZW $\rightarrow$ XY};
+	\node[above = -1cm of plot, xshift = -100] () {XY $\rightarrow$ ZW};
+	\node[above = -1cm of plot, xshift = 90] () {ZW $\rightarrow$ XY};
 \end{tikzpicture}
 \caption{
-Is this what Sally was thinking?
+\textcolor{red}{Is this what Sally was thinking? I guess the right panel is pretty boring}
 }
 \label{fig:Combination_Turnover_Ratio}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Changes in mean fitness
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[!h]
+\centering
+\begin{tikzpicture}[remember picture]
+	\node[] (plot) {\includegraphics[width=\linewidth]{Combination_Fitness_Rec}};
+	\node[above = -1cm of plot, xshift = -100] () {XY $\rightarrow$ ZW};
+	\node[above = -1cm of plot, xshift = 90] () {ZW $\rightarrow$ XY};
+\end{tikzpicture}
+\caption{
+\textcolor{red}{This complicated thing matches the plot above. We could combine this with that to make a 6 panel-er?}
+}
+\label{fig:Combination_Fitness_Rec}
 \end{figure}
@@
 %}
-\textcolor{red}{I'm still confused why male and female mean fitnesses aren't normalized by their frequency. I'm not sure we should be calling them means without this normalization step.}
+\textcolor{red}{I'm still confused why male and female mean fitnesses aren't normalized by their frequency.
+I'm not sure we should be calling them means without this normalization step.
+Or we should justify this by saying that mean fitness also has something to do with the number of a sex, i.e., multiply *real* mean fitness in females by freqfemale/(1/2)?
+See the next figure for what happens when we do normalize.}
 }
 \label{fig:Combination_MeanFit}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Changes in mean fitness corrected for sex ratio
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[!h]
+\centering
+\begin{tikzpicture}[remember picture]
+	\node[] (plot) {\includegraphics[width=\linewidth]{Combination_MeanFit_Corrected}};
+\end{tikzpicture}
+\caption{
+\textcolor{red}{Last plot with mean fitness of sexes corrected for sex ratio.}
+}
+\label{fig:Combination_MeanFit_Corrected}
 \end{figure}
@@
 Maybe include different parameters here or remove the part when no equilibrium).
-MMO: If you trust the sieve function there are stable equilibria across the entire range, although this differ greatly between XY and ZW systems near -25cM.
+MMO: If you trust the sieve function there are stable equilibria across the entire range, although they differ greatly between XY and ZW systems near -25cM.
 \\
@@
 Currently use different parameters for B than using in figure \ref{fig:Combination_Turnover} (selection/drive twice as strong in turnover figure).
-MMO: this is to keep it within the bounds of the plot -- using the same parameters makes the peak at -25 reach roughly 0.1, and then it is difficult to see the details of A,C, and D.
+MMO: this is to keep it within the bounds of the plot -- using the same parameters as figure 1 makes the peak at -25 reach roughly 0.1, and then it is difficult to see the details of A,C, and D.
 %This plot would also benefit from titles giving, e.g., ``sexually-antagonistic selection, $s^\female s^\male<0$'' for A, ``male meiotic drive, $s^\female s^\male>0$'' for B
@@
 \textcolor{red}{Should we adjust the subscripts throughout this subsection?
-Right now we end up re-defining $i$ and $j$ (when switching from haploid to diploid) and then introduce three new subscripts $b$, $c$, and $l$, all of which can be derived from $i$ and $j$.
+Right now we end up re-defining $i$ and $j$ (when switching from haploid to diploid; this might have been my doing!) and then introduce three new subscripts $b$, $c$, and $l$, all of which can be derived from $i$ and $j$.
 Might be more straightforward to just use $p^\Hermaphrodite_{x_1,x_2,a_1,a_2,m_1,m_2}$ where 1 is maternal and 2 is paternal?
-We then no longer have to switch indices from haploid to diploid and $b=m_1m_2$, $c=x_1x_2$, and $l=a_1a_2$.
-I guess the downside will be writing the recursion equations...}
+We then no longer have to switch indices from haploid to diploid and the connection to other variables is clear: $b=m_1m_2$, $c=x_1x_2$, and $l=a_1a_2$.
+I guess the downside will be re-writing the recursion equations...
+which is why I haven't gone ahead and tried this.}
 
@@
 \noindent
-In this case, the zygotic sex ratio ($\zeta$) is given by the difference in haploid selection in males on $a$ (fixed on the Y) and $A$ (fixed on the X) alleles, i.e., there are more males than females if $\zeta = 2\alpha^\male w_A^\male / (w_a^\male + w_A^\male)<1/2$.
+In this case, the zygotic sex ratio ($\zeta$) is given by the difference in haploid selection in males on $a$ (fixed on the Y) and $A$ (fixed on the X) alleles, i.e., there are more males than females if $\zeta = \alpha^\male w_A^\male / [(1-\alpha^\male)w_a^\male + \alpha^\male w_A^\male]<1/2$.
 %$\alpha^\male<1/2$ and/or $w_{a}^\male>w_{A}^\male$.
-Populations with a male biased zygotic sex ratio are more permissive to invasion by a neo-W ($\lambda_{mA}$ and $\lambda_{ma}$ larger).
+Populations with haploid selection for $a$ in males have a male biased zygotic sex ratio are thus more permissive to invasion by a neo-W ($\lambda_{mA}$ and $\lambda_{ma}$ larger).
 %In addition, the spread of neo-W alleles depends on the fitness of female diploids after mating with an X-$A$ or Y-$a$ male gamete, relative to the fitness of females in the population (all have genotype $AA$ and fitness $w_{AA}^\female$ at this equilibrium).
-In addition, the spread rate of neo-W haplotypes is determined by their fitness in females. 
-Zygotes carrying dominant neo-W alleles will develop as females regardless of their genotype at the XY locus. Therefore, females result from matings with either X-$A$ or Y-$a$ male gametes. 
-The relative proportion of these male gametes is also determined by haploid selection in males; mating with a Y-$a$ male gamete is more likely if the $a$ allele is favoured during male gamete production or competition ($\zeta<1/2$).
-
+Haploid selection in males has a second effect; the spread rate of neo-W haplotypes is determined by their fitness in diploid females, which depends on their diploid genotype and thus on the male gamete they pair with.
+Zygotes carrying dominant neo-W alleles will develop as females regardless of their genotype at the XY locus. 
+Therefore, neo-W females result from matings with either X-$A$ or Y-$a$ male gametes. 
+The relative proportion of these male gametes is determined by haploid selection in males; mating with a Y-$a$ male gamete is more likely if the $a$ allele is favoured during male gamete production or competition ($\zeta<1/2$).
+Thus, neo-W females experience different diploid selection than XX females, and the extent of this difference depends on haploid selection in males.
 Furthermore, haploid selection in females can directly select upon neo-W-$A$ or neo-W-$a$ haplotypes. 
@@
 On the other hand, neo-W-$a$ female gametes can be favoured or disfavoured during female haploid competition (favoured if $w_{a}^\female>w_{A}^\female$). 
-Meiotic drive in females ($\alpha^\female$) similarly affects the fitness of these haplotypes, except that meiotic drive only occurs in heterozygotes.
+Meiotic drive in females ($\alpha^\female$) similarly affects the fitness of these neo-W haplotypes, except that it impacts both haplotypes as meiotic drive only occurs in heterozygotes and therefore does not occur in resident XX females (who are always homozygote $AA$).
 
@@
 
+%Haploid selection affects the conclusions outlined above by altering the zygotic sex ratio and exerting direct selection on neo-W haplotypes.
+%The effect of sex-ratio selection is straightforward and can be seen in equation \eqref{Binvasion}, where male drive and gamete competition for $a$ (which is fixed on the Y and therefore causes a male bias) increases all four terms.
+%Direct selection on neo-W haplotypes can also be seen in equation \eqref{Binvasion} by noticing that increasing female drive in favour of $A$ increases the neo-W-$A$ haplotype growth rate ($\lambda_{mA}$) while female drive and gamete competition in favour of $a$ increases the neo-W-$a$ haplotype growth rate ($\lambda_{ma}$).
+%Gamete competition in females does not impact the spread of neo-W-$A$ haplotypes because they are on the same background as the resident X.
+%Recombination between the selected locus and the neo-W complicates things slightly, as selective advantages for one neo-W haplotype during the haploid stage in females comes at a cost to the other, and thus recombination off the favoured background becomes more detrimental.
+
 %\textcolor{red}{the versions for equil $(A)$ are not terrible but could be improved by cleverly re-writing with the $\phi$ and $\psi$ terms from above, I think...}
@@
 Similar equations can be derived for equilibrium (A) by subbing the equilibrium allele frequencies into Table \ref{tab:haplotype_growth}.
-This gives
 
@@
 
-\noindent
-As with equilibrium (B), the conditions for invasion are easier to interpret in the absence of haploid selection, which again modifies invasion fitnesses by directly selecting upon neo-W haplotypes.
+As with equilibrium (B), haploid selection again modifies invasion fitnesses by altering the sex-ratio and the diploid genotypes of females and directly selecting upon female gametes.
+The only difference is that resident XX females are no longer always homozygote $AA$ and males are no longer always heterozygote $Aa$.
+Thus the effect of haploid selection in males is reduced, as is the difference in fitness between neo-W haplotypes and resident X haplotypes, as both can be on any diploid or haploid background.
+
+The other terms are easier to interpret in the absence of haploid selection.
 For instance, without haploid selection, the neo-W-$A$ haplotype spreads ($\lambda_{mA}>1$) if and only if

### 2017-07-05 LaTeX/Turnover.tex
unknown changes, perhaps trying to resolve matt's new comments
attempt at new main text tight linkage results, some comments to tighten up consistency between old and new results

@@
 That is, new masculinizing mutations (neo-Y chromosomes) could be favoured via associations with alleles that are beneficial in the male haploid stage. 
-However, sex ratios can also become biased by linkage between the sex-determining region and a locus that harbours genetic variation in haploid fitness. 
+On the other hand, sex ratios can also become biased by linkage between the sex-determining region and a locus that harbours genetic variation in haploid fitness. 
 For example, there are several known cases of sex-ratio bias caused by sex-linked meiotic drive alleles \citep[][Chapter 3]{Burt:2006} or selection among X- and Y-bearing pollen \citep{Lloyd:1974tz,Conn:1981uw,Stehlik:2005ul,Stehlik:2006to,Field:2012fd,Field:2013cc}.
@@
 \end{equation}
-\noindent For example, if we assume that only the $mA$ haplotype has a positive growth rate ($\lambda_{ma}<1<\lambda_{mA}$), the second term on the left-hand side of \eqref{eq:lambdasGen} is negative and invasion requires that the rate at which $mA$ haplotypes are produced by recombination, $\rho_{ma}$, is sufficiently greater than the rate at which $ma$ haplotypes are, $\rho_{mA}$.
+\noindent For example, if we assume that only the $mA$ haplotype has a positive growth rate ($\lambda_{ma}<1<\lambda_{mA}$), the second term on the left-hand side of \eqref{eq:lambdasGen} is negative and invasion requires that the growth rate of $mA$ haplotypes and the rate at which they are produced by recombination is sufficiently large relative to that of $ma$ haplotypes.
 In other words, invasion requires that the average growth rate of recombinants, weighted by the rates they are created, is positive.
@@
 %involve any female (male) diploid selection terms ($w_{g}^{\female}$)
-This is because a dominant neo-Y (neo-W) is always found in males (females), and therefore the frequency of the neo-Y (neo-W) allele ($m$) only changes in males (females). 
+This is because a dominant neo-Y (neo-W) is always found in males (females), and therefore the frequency of the neo-Y (neo-W) allele, $m$, only changes in males (females). 
 %Therefore, invasion by a neo-Y allele does not involve any female diploid selection terms ($w_{g}^{\female}$). 
@@
 This is consequential because it means that females with and without a neo-W differ in the frequency of $A$ alleles they obtain from mating.
+\textcolor{blue}{nice}
 %the diploid fitness terms in Table \ref{tab:haplotype_growth} are weighted by the probability of producing those genotypes through matings with gametes of the opposite sex. 
@@
 In order to explicitly determine the conditions under which a rare neo-sex-determining allele spreads, we must calculate the frequency of the $A$ allele in the ancestral population (i.e., $p^\female_X$, $p^\male_X$, and $p^\male_Y$).
-To do so we assume that the $A$ allele reaches a stable equilibrium frequency under the ancestral sex-determination system before the neo-sex-determining allele ($m$) arises. 
-We can then analytically calculate the allele frequency of the $A$ allele using two alternative simplifying assumptions: 
+Since only the \textbf{A} locus experiences selection directly, any deterministic evolution requires that there is a polymorphism at the \textbf{A} locus. 
+Polymorphisms can be transiently present during the spread of uniformly beneficial alleles but polymorphisms maintained by selection can maintain alleles at higher allele frequencies for longer periods, during which time new sex-determining alleles can arise.
+Therefore, we will assume that the $A$ allele reaches a stable intermediate equilibrium frequency under the ancestral sex-determination system before the neo-sex-determining allele ($m$) arises. 
+We can analytically calculate the allele frequency of the $A$ allele using two alternative simplifying assumptions: 
 (1) the \textbf{A} locus is within (or tightly linked to) the non-recombining region around the ancestral SDR ($r \approx 0$) or (2) selection is weak relative to recombination ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon<<1$).
@@
 Therefore, a neo-Y mutation cannot spread ($\lambda \leq 1$) in an ancestral XY system that is at equilibrium with all selected loci within the non-recombining region around the SDR.
+\textcolor{blue}{
+In essence, through tight linkage with the \textbf{A} locus, the ancestral Y becomes strongly specialized on the allele that has the highest fitness across male haploid and diploid phases. 
+Given that the ancestral Y is at this equilibrium, it is not possible for a neo-Y to create males that have higher fitness than the ancestral Y. 
+}
+
+\textcolor{blue}{I might be tempted to focus on the diploid selection only case here because this is a new/surprising result and we have less cool stuff to say about haploid selection beyond describing it affecting stuff (right?).
+I then might also leave the complication of whether there is a polymorphism on the X or not to the appendix???
+Attempt 1:}
+
+\textcolor{blue}{
+%Briefly, the neo-W invades under the ancestral XY sex-determining system, the X chromosome may not be able to as specialised on a female-beneficial allele
+%The full characteristic polynomials are given in the appendix (equations \ref{Binvasion} and \ref{Ainvasion}).
+Neo-W alleles, on the other hand, can invade an ancestral XY system under some conditions (the full invasion conditions are given in the appendix). 
+Significantly, we note that it is possible for both neo-W haplotypes to spread ($\lambda_{mA}>1$ and $\lambda_{ma}>1$ in \ref{Binvasion} and \ref{Ainvasion}), in which case neo-W invasion can occur regardless of linkage to the selected locus.
+That is, selection on loci within the non-recombining region of the SDR can favour an unlinked neo-W. 
+Although haploid selection can favour neo-W alleles because the ancestral sex ratio becomes male biased, this is not the only circumstance in which less tightly linked neo-W alleles invade. 
+For example, unlinked neo-W alleles can invade in the absence of any haploid selection. 
+This result is unexpected given the results of \cite{vanDoorn:2010hu}, who did not explicitly calculate equilibrium allele frequencies under tight linkage and generally concluded that heterogametic transitions occur when neo-sex-determining alleles are in tighter linkage with loci under sex-specific diploid selection.
+Therefore, we focus on cases where there is no haploid selection and discuss the effects of haploid selection in the appendix. 
+}
+
+\textcolor{blue}{
+If we categorise the $a$ allele as being ancestrally `male-beneficial' via the fact that it is fixed on the Y, then $\lambda_{mA}>1$ indicates that the neo-W spreads when found with the ancestrally `female-beneficial' allele.
+Intuitively, this is possible because the ancestral X chromosome is not able to specialise on the `female-beneficial' allele due to the fact that X's are sometimes found in males. 
+For example, a polymorphism of $A$ and $a$ alleles can be maintained on the X despite directional selection in favour of the $A$ allele in females ($s^\female>0$, $0<h^\female<1$) because the $a$ allele is favoured in males.
+W$A$ haplotypes will only create females with high fitness $AA$ or $Aa$ genotypes and can therefore have higher fitness than ancestral females, which sometimes also produce $aa$ females. 
+Thus, the neo-W can spread by allowing increased specialization on female beneficial alleles.
+%As another example, $AA$ individuals can have low fitness in females and yet the $A$ can be fixed on the X due to strong overdominance in males favouring X$A$Y$a$ males. 
+%In this case, W$A$ haplotypes produce fewer unfit $AA$ females because they produce some females through matings with Y$a$-bearing sperm. 
+}
+
+\textcolor{blue}{
+Given that the $a$ allele can be considered ancestrally `male-beneficial' because it is fixed on the Y, it might be surprising that neo-W$a$ haplotypes can be favoured by selection in females, i.e., $\lambda_{ma}>1$.
+Again, this occurs because ancestral X's sometimes experience selection in males, in which they will always be paired with a Y$a$. 
+Hence, if there is overdominance in males, X$A$Y$a$ males have high fitness and the $A$ allele is favoured by selection on the X in males. 
+Therefore, the X can be polymorphic or fixed for the $A$ allele despite favouring the $a$ allele during selection in females \textcolor{red}{(see also Lloyd 197?, Otto 2014)}. 
+In such cases, neo-W$a$ haplotypes can spread. 
+Indeed, it is possible for both W$A$ and W$a$ haplotypes to spread, as is the case when $AA$ individuals have low fitness in females yet the $A$ is fixed on the X due to strong overdominance in males.
+Both neo-W$A$ and neo-W$a$ haplotypes then produce fewer unfit $AA$ females.
+This is true for the neo-W-$A$ haplotype because it can pair with a $Y-a$ haplotype and still be female. 
+}
+
+\textcolor{blue}{
+We plot parameters under which $\lambda_{mA}>1$ and $\lambda_{ma}>1$ in figure XXX with diploid selection only. 
+Wherever both haplotypes have positive growth rates, invasion by a neo-W is expected regardless of its linkage with the selected locus (i.e., even unlinked neo-W alleles can invade). 
+In regions where at least one of these haplotypic growth rates is positive, a new neo-W feminizing mutation as long as \eqref{eq:lambdasGen} is satisfied, which can require that the recombination rate, $R$, is low enough and yet still indicates that more loosely linked sex-determining regions can spread.
+}
 
 Neo-W alleles, on the other hand, can invade an ancestral XY system under some conditions (given in detail in the appendix). 
-The full characteristic polynomials are given in the appendix (equations \ref{Binvasion} and \ref{Ainvasion}).
+%The full characteristic polynomials are given in the appendix (equations \ref{Binvasion} and \ref{Ainvasion}).
 Briefly, neo-W-$A$ and/or neo-W-$a$ haplotypes can spread when rare in the absence of recombination ($\lambda_{ma}>1$ and/or $\lambda_{mA}>1$), depending on the ancestral sex-ratio and allele frequencies.
@@
 
+\textcolor{blue}{This explanation is clearer than the one I put in the appendix, if we drop it here, maybe we should try and re-word the corresponding part of the appendix using this paragraph}
 Haploid selection impacts the spread of neo-W haplotypes in three ways.
@@
 That looser sex-linkage can evolve is contrary to the conclusions of \cite{vanDoorn:2010hu}, who did not explicitly calculate invasion fitness under ancestrally tight sex-linkage.
+\textcolor{blue}{or, just didn't calculate the equilibria (A) an (B).}
 Similar scenarios have been shown to select for a modifier that increases recombination between the sexes \citep[green regions of Figure 2 in][]{Otto2014}.
+\textcolor{blue}{n.b., the recombination regions are only subsets mostly because you also generate a really unfit Y haplotype through recombination. Probably not worth mentioning.}
 
@@
 
-%\textcolor{red}{With haploid selection the situation becomes more complex, but we can }
-
 \subsubsection*{Loose linkage with the ancestral sex-determining region}
+
+\textcolor{blue}{As with the discussion, this section might need some editing for (1) unclearly describing looser linkage never evolving without haploid selection, which we now show is possible above and (2) going on about sex ratio selection too much - this should be changed to something along the lines of  ``male biased zygotic sex ratios ($\zeta-1/2$) are of the order of $\epsilon^2$.
+Therefore Fisherian sex ratio selection directly favours neo-Ws by a similar magnitude.
+Perhaps surprisingly, neo-Ws can be favoured to the same degree by haploid selection in females when female haploid selection favours the alleles that tend to be carried by the neo-W.
+Thus XY to ZW is the same as ZW to XY even though sex ratio biases only exist in one case, given the assumptions made in this section.
+''
+}
 
@@
 Equation \eqref{eq:lambda_neoY} demonstrates that under weak selection a neo-Y will invade if and only if it is more closely linked to the selected locus than the ancestral sex-determining region (i.e., if $R<r$, note that $V_{A}$ and $S_{A}^2$ are strictly positive as long as \textbf{A} is polymorphic).
-This result echoes that of \citet{vanDoorn:2007eu}, who considered diploid selection only and also found that homogametic transitions (XY to XY or ZW to ZW) can occur when the neo-sex-determining locus is more closely linked to a locus under sexually-antagonistic selection.
+This echoes our tight linkage results above and the results of \citet{vanDoorn:2007eu}, who considered diploid selection only and also found that homogametic transitions (XY to XY or ZW to ZW) can occur when the neo-sex-determining locus is more closely linked to a locus under sexually-antagonistic selection.
 %Because tighter linkage between the sex-determining region and a selected locus evolves during these transitions, stronger associations between selected alleles and diploid sexes can build up by selection (e.g., between male-beneficial alleles and the male-determining allele, Y).%, increasing diploid mean fitness (Figure \ref{fig:Combination_MeanFit}).
@@
 
+\textcolor{blue}{maybe re-order to put the results up front and focus on sex ratio less.
+Somewhere around these first two paragraphs we should include our tight linkage results.
+At the moment it doesn't make total sense because it assumes that tighter linkage is always favoured unless there is haploid selection.}
+
+%HAPLOID SELECTION CAN ACT LIKE SEXUALLY-ANTAGONISTIC SELECTION
+It has previously been demonstrated that new sex-determining systems can evolve if there is genetic variation maintained by sexually-antagonistic selection \citep{vanDoorn:2007eu,vanDoorn:2010hu}. 
+In particular, transitions to new sex-determining systems can occur when new sex-determining regions are more closely linked to a sexually-antagonistic locus.
+Our results show that genetic variation at loci that experience haploid selection can also generate selection in favour of new sex-determining systems. 
+New sex-determining alleles are again favoured if they are linked with a locus under haploid selection and the ancestral sex-determination locus is not.
+However, with haploid selection, heterogametic transitions (XY to ZW or ZW to XY) can also occur when the new sex-determining region is less closely linked to the locus under selection.
+
+%HAPLOID SELECTION ALSO ALLOWS LOOSER LINKAGE TO EVOLVE
+Neo-W (neo-Y) alleles invade when their fitness in females (males) is greater than the mean fitness of females (males) under the ancestral sex-determination system.
+With sexually-antagonistic selection (between diploid sexes) only, linkage between a selected locus and the sex-determining region strengthens associations between male beneficial alleles and the male-determining allele (Y or Z) and between female beneficial alleles and the female-determining allele (X or W).
+Thus, the mean fitness of both males and females increases with closer linkage to the sex-determining region. 
+Therefore, new sex-determining alleles only invade if they are more closely linked than the ancestral sex-determining region. 
+However, if there is haploid selection on loci linked to an XY (ZW) sex-determining region, selection can maintain polymorphisms at which the mean fitness of females (males) is lower than it would be without sex-linkage.
+In these cases, unlinked neo-W (neo-Y) alleles can increase female (male) fitness, at a cost to the other sex, and invade despite lowering mean fitness (Figure \ref{fig:Combination_MeanFit}).
+
+%TIGHT LINKAGE RESULTS
+
+\textcolor{blue}{maybe drop paragraph?}
 \textcolor{red}{I messed with the sex-ratio selection paragraphs to tone down our "it doesn't matter" speech from before. Have at any amendments you'd like to make.}
@@
 
+\textcolor{blue}{Maybe we could go along the angle of ``under the weak recombination assumptions, there is no asymmetry between XY to ZW and ZW to XY, indicating that sex ratio selection does not dominate.
+Asymmetry can be larger when linkage is tight (e.g., Fig 2C) but under most circumstances we do not predict asymmetry between XY to ZW and ZW to XY transitions despite the presence/absence of sex ratio selection.
+Thus, haploid selection can favour heterogametic transitions both via sex ratio selection and via the fitness of alleles that are associated with the neo-sex-determining allele; these selection pressures are often of equal magnitude.''}
+
 Sex ratio biases caused by gametic competition or meiotic drive have been shown to exert Fisherian sex-ratio selection on various autosomal \citep{Stalker:1961th,Smith:1975ft,Frank:1989vl,Hough:2013uo,Ubeda:2015fx, Otto:2015va} and sex-linked \citep{Ubeda:2015fx} modifiers.
@@
 %In this study, we do not consider environmental condition dependence or local mate competition \citep[reviewed in][]{Charnov:1982wg,Bull:1983vi,West:2009we}.
-
-%HAPLOID SELECTION CAN ACT LIKE SEXUALLY-ANTAGONISTIC SELECTION
-It has previously been demonstrated that new sex-determining systems can evolve if there is genetic variation maintained by sexually-antagonistic selection \citep{vanDoorn:2007eu,vanDoorn:2010hu}. 
-In particular, transitions to new sex-determining systems can occur when new sex-determining regions are more closely linked to a sexually-antagonistic locus.
-Our results show that genetic variation at loci that experience haploid selection can also generate selection in favour of new sex-determining systems. 
-New sex-determining alleles are again favoured if they are linked with a locus under haploid selection and the ancestral sex-determination locus is not.
-However, with haploid selection, heterogametic transitions (XY to ZW or ZW to XY) can also occur when the new sex-determining region is less closely linked to the locus under selection.
-
-%HAPLOID SELECTION ALSO ALLOWS LOOSER LINKAGE TO EVOLVE
-Neo-W (neo-Y) alleles invade when their fitness in females (males) is greater than the mean fitness of females (males) under the ancestral sex-determination system.
-With sexually-antagonistic selection (between diploid sexes) only, linkage between a selected locus and the sex-determining region strengthens associations between male beneficial alleles and the male-determining allele (Y or Z) and between female beneficial alleles and the female-determining allele (X or W).
-Thus, the mean fitness of both males and females increases with closer linkage to the sex-determining region. 
-Therefore, new sex-determining alleles only invade if they are more closely linked than the ancestral sex-determining region. 
-However, if there is haploid selection on loci linked to an XY (ZW) sex-determining region, selection can maintain polymorphisms at which the mean fitness of females (males) is lower than it would be without sex-linkage.
-In these cases, unlinked neo-W (neo-Y) alleles can increase female (male) fitness, at a cost to the other sex, and invade despite lowering mean fitness (Figure \ref{fig:Combination_MeanFit}).
 
@@
 %HOW TO TEST EMPIRICALLY
+\textcolor{blue}{I think Sally was sceptical of this idea. i.e., if the second term in \ref{eq:lambda_neoW} is negative, then get less transitions with haploid selection included, right? }
 Taken at face value, our results indicate that transitions in heterogametey (XY to ZW or vice versa) are more likely to be favoured by selection if there is selection upon both haploid and diploid genotypes rather than diploid selection alone.
@@
 
+\textcolor{blue}{similarly, this part doesn't discuss our new tight linkage results or our new perspective on sex ratios.}
 %CONCLUSION
@@
 \smallskip
-\caption{mean fitnesses in resident population ($M$ fixed, XY sex determination) }
+\caption{mean fitnesses in the resident population ($M$ fixed, XY sex determination) }
 \begin{tabular}{l l }
@@
 These conditions cannot be met under purely sexually-antagonistic selection, where $a$ is directionally favoured in males ($w_{AA}^\male>w_{Aa}^\male>w_{aa}^\male$) and $A$ is directionally favoured in females ($w_{AA}^\female>w_{Aa}^\female>w_{aa}^\female$).
-Essentially, the X is already as specialized as possible for the female beneficial allele (X-A is fixed), and the neo-W often makes daughters with the Y-a haplotype, increasing the flow of $a$ alleles into females, which reduces the fitness of those females.
+Essentially, the X is already as specialized as possible for the female beneficial allele (X$A$ is fixed), and the neo-W often makes daughters with the Y-a haplotype, increasing the flow of $a$ alleles into females, which reduces the fitness of those females.
 
@@
 %If $\lambda_{mA}>1$ (requiring $w_{Aa}^\female>w_{AA}^\female$), the implication is that the neo-W can spread alongside the $A$ allele, despite the fact that the neo-W sometimes brings $Y-a$ haplotypes into females, because $a$ is favoured by selection in females despite $A$ being fixed on the X.
-A neo-W can spread alongside the $A$ allele ($\lambda_{mA}>1$), despite the fact that a neo-W brings $Y-a$ haplotypes into females, when $w_{Aa}^\female>w_{AA}^\female$.
+A neo-W can spread alongside the $A$ allele ($\lambda_{mA}>1$), despite the fact that a neo-W brings Y$a$ haplotypes into females, when $w_{Aa}^\female>w_{AA}^\female$.
 In this case the $a$ allele is favoured by selection in females despite $A$ being fixed on the X.
-For this equilibrium to be stable, X-$A$ must be sufficiently favoured in males to keep the frequency of X-$A$ at one (specifically, from the stability conditions, we must have $w_{Aa}^\male/((w_{aa}^\male+w_{Aa}^\male)/2)>w_{Aa}^\female/w_{AA}^\female$).
+For this equilibrium to be stable, X-$A$ must be sufficiently favoured in males to keep the frequency of X$A$ at one (specifically, from the stability conditions, we must have $w_{Aa}^\male/((w_{aa}^\male+w_{Aa}^\male)/2)>w_{Aa}^\female/w_{AA}^\female$).
 

### 2017-07-06 LaTeX/Turnover.tex
incorporating mscotts comments

@@
 This is consequential because it means that females with and without a neo-W differ in the frequency of $A$ alleles they obtain from mating.
-\textcolor{blue}{nice}
+%\textcolor{blue}{nice}
 %the diploid fitness terms in Table \ref{tab:haplotype_growth} are weighted by the probability of producing those genotypes through matings with gametes of the opposite sex. 
@@
 Therefore, a neo-Y mutation cannot spread ($\lambda \leq 1$) in an ancestral XY system that is at equilibrium with all selected loci within the non-recombining region around the SDR.
-\textcolor{blue}{
 In essence, through tight linkage with the \textbf{A} locus, the ancestral Y becomes strongly specialized on the allele that has the highest fitness across male haploid and diploid phases. 
 Given that the ancestral Y is at this equilibrium, it is not possible for a neo-Y to create males that have higher fitness than the ancestral Y.
-}
-
-\textcolor{blue}{I might be tempted to focus on the diploid selection only case here because this is a new/surprising result and we have less cool stuff to say about haploid selection beyond describing it affecting stuff (right?).
+
+%\textcolor{blue}{I might be tempted to focus on the diploid selection only case here because this is a new/surprising result and we have less cool stuff to say about haploid selection beyond describing it affecting stuff (right?).
 I then might also leave the complication of whether there is a polymorphism on the X or not to the appendix???
@@
 
-\textcolor{blue}{
+%\textcolor{blue}{
 %Briefly, the neo-W invades under the ancestral XY sex-determining system, the X chromosome may not be able to as specialised on a female-beneficial allele
 %The full characteristic polynomials are given in the appendix (equations \ref{Binvasion} and \ref{Ainvasion}).
-Neo-W alleles, on the other hand, can invade an ancestral XY system under some conditions (the full invasion conditions are given in the appendix). 
-Significantly, we note that it is possible for both neo-W haplotypes to spread ($\lambda_{mA}>1$ and $\lambda_{ma}>1$ in \ref{Binvasion} and \ref{Ainvasion}), in which case neo-W invasion can occur regardless of linkage to the selected locus.
-That is, selection on loci within the non-recombining region of the SDR can favour an unlinked neo-W. 
+Neo-W alleles, on the other hand, can invade an ancestral XY system under some conditions (the full invasion conditions are given in the appendix; equations \ref{Binvasion} and \ref{Ainvasion}). 
+Significantly, we note that it is possible for both neo-W haplotypes to spread ($\lambda_{mA}>1$ and $\lambda_{ma}>1$), in which case neo-W invasion can occur regardless of linkage to the selected locus.
+That is, selection on loci within the non-recombining region of the SDR can favour the invasion of a less closely linked neo-W (e.g., on an autosome). 
 Although haploid selection can favour neo-W alleles because the ancestral sex ratio becomes male biased, this is not the only circumstance in which less tightly linked neo-W alleles invade. 
@@
 Therefore, we focus on cases where there is no haploid selection and discuss the effects of haploid selection in the appendix. 
-}
-
-\textcolor{blue}{
+%}
+
+%\textcolor{blue}{
 If we categorise the $a$ allele as being ancestrally `male-beneficial' via the fact that it is fixed on the Y, then $\lambda_{mA}>1$ indicates that the neo-W spreads when found with the ancestrally `female-beneficial' allele.
@@
 For example, a polymorphism of $A$ and $a$ alleles can be maintained on the X despite directional selection in favour of the $A$ allele in females ($s^\female>0$, $0<h^\female<1$) because the $a$ allele is favoured in males.
-W$A$ haplotypes will only create females with high fitness $AA$ or $Aa$ genotypes and can therefore have higher fitness than ancestral females, which sometimes also produce $aa$ females. 
+W-$A$ haplotypes will only create females with high fitness $AA$ or $Aa$ genotypes and can therefore have higher fitness than ancestral females, which sometimes also produce $aa$ females. 
 Thus, the neo-W can spread by allowing increased specialization on female beneficial alleles.
@@
 %In this case, W$A$ haplotypes produce fewer unfit $AA$ females because they produce some females through matings with Y$a$-bearing sperm. 
-}
-
-\textcolor{blue}{
-Given that the $a$ allele can be considered ancestrally `male-beneficial' because it is fixed on the Y, it might be surprising that neo-W$a$ haplotypes can be favoured by selection in females, i.e., $\lambda_{ma}>1$.
-Again, this occurs because ancestral X's sometimes experience selection in males, in which they will always be paired with a Y$a$. 
-Hence, if there is overdominance in males, X$A$Y$a$ males have high fitness and the $A$ allele is favoured by selection on the X in males. 
-Therefore, the X can be polymorphic or fixed for the $A$ allele despite favouring the $a$ allele during selection in females \textcolor{red}{(see also Lloyd 197?, Otto 2014)}. 
-In such cases, neo-W$a$ haplotypes can spread. 
-Indeed, it is possible for both W$A$ and W$a$ haplotypes to spread, as is the case when $AA$ individuals have low fitness in females yet the $A$ is fixed on the X due to strong overdominance in males.
-Both neo-W$A$ and neo-W$a$ haplotypes then produce fewer unfit $AA$ females.
+%}
+
+%\textcolor{blue}{
+Given that the $a$ allele can be considered ancestrally `male-beneficial' because it is fixed on the Y, it might be surprising that neo-W-$a$ haplotypes can be favoured by selection in females ($\lambda_{ma}>1$).
+Again, this occurs because ancestral X's also experience selection in males, in which they will always be paired with a Y-$a$. 
+Hence, if there is overdominance in males, X-$A$ Y-$a$ males have high fitness and the $A$ allele is favoured by selection on the X in males. 
+Therefore, the X can be polymorphic or even fixed for the $A$ allele despite favouring the $a$ allele during selection in females \citep{Lloyd1977,Otto2014}. 
+In such cases, neo-W-$a$ haplotypes, which are never found in males, can spread because they both create more $Aa$ and $aa$ females when pairing with an X from males and they bring Y-$a$ haplotypes into females, in which case females are always $aa$.
+Indeed, it is possible for both W-$A$ and W-$a$ haplotypes to spread, as is the case when $AA$ individuals have low fitness in females yet the $A$ is fixed on the X due to strong overdominance in males.
+Both neo-W-$A$ and neo-W-$a$ haplotypes then produce fewer unfit $AA$ females.
 This is true for the neo-W-$A$ haplotype because it can pair with a $Y-a$ haplotype and still be female. 
-}
-
-\textcolor{blue}{
-We plot parameters under which $\lambda_{mA}>1$ and $\lambda_{ma}>1$ in figure XXX with diploid selection only. 
-Wherever both haplotypes have positive growth rates, invasion by a neo-W is expected regardless of its linkage with the selected locus (i.e., even unlinked neo-W alleles can invade). 
-In regions where at least one of these haplotypic growth rates is positive, a new neo-W feminizing mutation as long as \eqref{eq:lambdasGen} is satisfied, which can require that the recombination rate, $R$, is low enough and yet still indicates that more loosely linked sex-determining regions can spread.
-}
-
-Neo-W alleles, on the other hand, can invade an ancestral XY system under some conditions (given in detail in the appendix). 
-%The full characteristic polynomials are given in the appendix (equations \ref{Binvasion} and \ref{Ainvasion}).
-Briefly, neo-W-$A$ and/or neo-W-$a$ haplotypes can spread when rare in the absence of recombination ($\lambda_{ma}>1$ and/or $\lambda_{mA}>1$), depending on the ancestral sex-ratio and allele frequencies.
-Below we discuss the main forces determining the spread of these neo-W haplotypes and the impact of recombination for the overall success of the neo-W.
-To simplify our discussion we first outline the potential effects of haploid selection and then consider diploid selection in its absence.
-
-\textcolor{blue}{This explanation is clearer than the one I put in the appendix, if we drop it here, maybe we should try and re-word the corresponding part of the appendix using this paragraph}
-Haploid selection impacts the spread of neo-W haplotypes in three ways.
-Firstly, the zygotic sex ratio becomes male biased ($\zeta<1/2$) when the $a$ allele (which is fixed on the Y) is favoured during competition among male gametes or by meiotic drive in males. 
-This facilitates the spread of a neo-W because neo-W alleles cause the zygotes that carry them to develop as the rarer, female, sex. 
-Secondly, haploid selection in males affects the diploid genotypes of females by altering the allele frequencies in the male gametes that female gametes pair with.
-For instance, because an epistatically dominant neo-W always causes its carrier to become female, it creates females who carry either $Y-a$ or $X$ genotypes from their father.
-Thus, because when there is a polymorphism the $X$ carries some non-zero frequency of $A$, haploid selection in males impacts the diploid genotypes of females (e.g., creating more $Aa$ females when drive in males favours $Y-a$).
-How this affects the spread of the neo-W then depends on diploid and haploid selection in females.
-Thirdly, female drive and gamete competition directly select on neo-W haplotypes.
-Drive for $A$ in females favours neo-W-$A$ haplotypes, at a cost to neo-W-$a$ haplotypes, and vice-versa when there is drive for $a$.
-The impact of this drive depends on how often XX and neo-W females are heterozygous.
-Competition among female gametes acts similarly, and depends on the frequency of $A$ on resident X chromosomes (e.g., competition among eggs has no affect on the initial spread of the neo-W-$A$ haplotype when $A$ is fixed on the X).
-Because haploid selection in females favours one neo-W haplotype at the expense of the other, recombination off the favoured background becomes more detrimental as it becomes more favoured.
+%}
+
+%\textcolor{blue}{
+In Figure \ref{fig:regionplot_ 2a} we show a region of parameter space under which both neo-W haplotypes invade ($\lambda_{mA}>1$ and $\lambda_{ma}>1$) when there is overdominance in females and no haploid selection \citep[corresponding to Figure 2a in][]{Otto2014}.
+Wherever both haplotypes have positive growth rates (gray region of Figure \ref{fig:regionplot_ 2a}), invasion by a neo-W is expected regardless of its linkage with the selected locus (i.e., even unlinked neo-W alleles can invade).
+In regions where only one haplotype can spread (white region of Figure \ref{fig:regionplot_ 2a}), a neo-W can invade as long as equation \eqref{eq:lambdasGen} is satisfied, which can require that the recombination rate, $R$, is small enough and yet still indicates that more loosely linked sex-determining regions can spread.
+%}
+
+%Neo-W alleles, on the other hand, can invade an ancestral XY system under some conditions (given in detail in the appendix). 
+%%The full characteristic polynomials are given in the appendix (equations \ref{Binvasion} and \ref{Ainvasion}).
+%Briefly, neo-W-$A$ and/or neo-W-$a$ haplotypes can spread when rare in the absence of recombination ($\lambda_{ma}>1$ and/or $\lambda_{mA}>1$), depending on the ancestral sex-ratio and allele frequencies.
+%Below we discuss the main forces determining the spread of these neo-W haplotypes and the impact of recombination for the overall success of the neo-W.
+%To simplify our discussion we first outline the potential effects of haploid selection and then consider diploid selection in its absence.
+
+%\textcolor{blue}{This explanation is clearer than the one I put in the appendix, if we drop it here, maybe we should try and re-word the corresponding part of the appendix using this paragraph}
+%Haploid selection impacts the spread of neo-W haplotypes in three ways.
+%Firstly, the zygotic sex ratio becomes male biased ($\zeta<1/2$) when the $a$ allele (which is fixed on the Y) is favoured during competition among male gametes or by meiotic drive in males. 
+%This facilitates the spread of a neo-W because neo-W alleles cause the zygotes that carry them to develop as the rarer, female, sex. 
+%Secondly, haploid selection in males affects the diploid genotypes of females by altering the allele frequencies in the male gametes that female gametes pair with.
+%For instance, because an epistatically dominant neo-W always causes its carrier to become female, it creates females who carry either $Y-a$ or $X$ genotypes from their father.
+%Thus, because when there is a polymorphism the $X$ carries some non-zero frequency of $A$, haploid selection in males impacts the diploid genotypes of females (e.g., creating more $Aa$ females when drive in males favours $Y-a$).
+%How this affects the spread of the neo-W then depends on diploid and haploid selection in females.
+%Thirdly, female drive and gamete competition directly select on neo-W haplotypes.
+%Drive for $A$ in females favours neo-W-$A$ haplotypes, at a cost to neo-W-$a$ haplotypes, and vice-versa when there is drive for $a$.
+%The impact of this drive depends on how often XX and neo-W females are heterozygous.
+%Competition among female gametes acts similarly, and depends on the frequency of $A$ on resident X chromosomes (e.g., competition among eggs has no affect on the initial spread of the neo-W-$A$ haplotype when $A$ is fixed on the X).
+%Because haploid selection in females favours one neo-W haplotype at the expense of the other, recombination off the favoured background becomes more detrimental as it becomes more favoured.
 Thus higher rates of recombination between the neo-W and the selected locus, $R$, can lead to smaller leading eigenvalues when there is haploid selection in females.
 
-In the absence of haploid selection and with the $A$ allele is fixed on the X, it is possible for both neo-W haplotypes can spread ($\lambda_{mA}>1$ and $\lambda_{ma}>1$ in \ref{Binvasion}), and thus neo-W invasion can occur regardless of its linkage to the selected locus.
-Invasion does not occur with purely sexually-antagonistic selection (i.e., $a$ directionally favoured in males and $A$ directionally favoured in females) because the X is then already as specialized as possible on the female sex.
-However, if, for example, $AA$ individuals suffer a fitness cost in females, yet $A$ is fixed on the X due to strong overdominance in males, both neo-W-$A$ and neo-W-$a$ haplotypes spread because they produce fewer unfit $AA$ females and never experience counter-selection in males.
-This is true even for the neo-W-$A$ haplotype because it can pair with a $Y-a$ haplotype and still be female. 
-When both haplotypes can spread alone the rate of recombination between the neo-W and the selected locus, $R$, does cannot prevent invasion, and thus the system can evolve looser sex-linkage (e.g., the neo-W could arise on an autosome, $R=1/2$).
-Even when only one haplotype can spread, invasion can still occur up to some positive rate of recombination, $R>0$ (as long as equation \ref{eq:lambdasGen} is satisfied). 
-That looser sex-linkage can evolve is contrary to the conclusions of \cite{vanDoorn:2010hu}, who did not explicitly calculate invasion fitness under ancestrally tight sex-linkage.
+%In the absence of haploid selection and with the $A$ allele is fixed on the X, it is possible for both neo-W haplotypes can spread ($\lambda_{mA}>1$ and $\lambda_{ma}>1$ in \ref{Binvasion}), and thus neo-W invasion can occur regardless of its linkage to the selected locus.
+%Invasion does not occur with purely sexually-antagonistic selection (i.e., $a$ directionally favoured in males and $A$ directionally favoured in females) because the X is then already as specialized as possible on the female sex.
+%However, if, for example, $AA$ individuals suffer a fitness cost in females, yet $A$ is fixed on the X due to strong overdominance in males, both neo-W-$A$ and neo-W-$a$ haplotypes spread because they produce fewer unfit $AA$ females and never experience counter-selection in males.
+%This is true even for the neo-W-$A$ haplotype because it can pair with a $Y-a$ haplotype and still be female. 
+%When both haplotypes can spread alone the rate of recombination between the neo-W and the selected locus, $R$, does cannot prevent invasion, and thus the system can evolve looser sex-linkage (e.g., the neo-W could arise on an autosome, $R=1/2$).
+%Even when only one haplotype can spread, invasion can still occur up to some positive rate of recombination, $R>0$ (as long as equation \ref{eq:lambdasGen} is satisfied). 
+%That looser sex-linkage can evolve is contrary to the conclusions of \cite{vanDoorn:2010hu}, who did not explicitly calculate invasion fitness under ancestrally tight sex-linkage.
 \textcolor{blue}{or, just didn't calculate the equilibria (A) an (B).}
-Similar scenarios have been shown to select for a modifier that increases recombination between the sexes \citep[green regions of Figure 2 in][]{Otto2014}.
-\textcolor{blue}{n.b., the recombination regions are only subsets mostly because you also generate a really unfit Y haplotype through recombination. Probably not worth mentioning.}
-
-In the absence of haploid selection it is also possible for a neo-W to invade when there is a stable polymorphism at the $\mathbf{A}$ locus on X chromosomes.
-For example, overdominance in males and strong directional selection for $a$ in females creates a scenario that favours the spread of both neo-W haplotypes at equilibrium ($\lambda_{mA}>1$ and $\lambda_{ma}>1$ in \ref{Ainvasion}), as both haplotypes bring more $a$ alleles into females and never experience counter-selection in males.
-Thus, as in the case of the $A$ being fixed on the X, looser sex-linkage can evolve with a polymorphic X (i.e., $\lambda>1$ with $R>0$) and this is expected under the same scenarios that select for a modifier that increases recombination between the sex chromosomes \citep[blue regions of Figure 2 in][]{Otto2014}.
+%Similar scenarios have been shown to select for a modifier that increases recombination between the sexes \citep[green regions of Figure 2 in][]{Otto2014}.
+%\textcolor{blue}{n.b., the recombination regions are only subsets mostly because you also generate a really unfit Y haplotype through recombination. Probably not worth mentioning.}
+%
+%In the absence of haploid selection it is also possible for a neo-W to invade when there is a stable polymorphism at the $\mathbf{A}$ locus on X chromosomes.
+%For example, overdominance in males and strong directional selection for $a$ in females creates a scenario that favours the spread of both neo-W haplotypes at equilibrium ($\lambda_{mA}>1$ and $\lambda_{ma}>1$ in \ref{Ainvasion}), as both haplotypes bring more $a$ alleles into females and never experience counter-selection in males.
+%Thus, as in the case of the $A$ being fixed on the X, looser sex-linkage can evolve with a polymorphic X (i.e., $\lambda>1$ with $R>0$) and this is expected under the same scenarios that select for a modifier that increases recombination between the sex chromosomes \citep[blue regions of Figure 2 in][]{Otto2014}.
 
@@
 The neo-sex-determining allele, $m$, will spread if $\lambda_{m,XY}>1$. 
-Equation \eqref{eq:lambda_neoY} demonstrates that under weak selection a neo-Y will invade if and only if it is more closely linked to the selected locus than the ancestral sex-determining region (i.e., if $R<r$, note that $V_{A}$ and $S_{A}^2$ are strictly positive as long as \textbf{A} is polymorphic).
+Equation \eqref{eq:lambda_neoY} demonstrates that under weak selection a neo-Y will invade if and only if it is more closely linked to the selected locus than the ancestral sex-determining region (i.e., if $R<r$; note that $V_{A}$ and $S_{A}^2$ are strictly positive as long as \textbf{A} is polymorphic).
 This echoes our tight linkage results above and the results of \citet{vanDoorn:2007eu}, who considered diploid selection only and also found that homogametic transitions (XY to XY or ZW to ZW) can occur when the neo-sex-determining locus is more closely linked to a locus under sexually-antagonistic selection.
@@
 
-Equation \eqref{eq:lambda_neoW} shows that if there is no haploid selection ($t^\Hermaphrodite=\alpha^\Hermaphrodite_{\Delta}=0$), as considered by \citet{vanDoorn:2010hu}, with weak selection the spread of a neo-W is equivalent to the spread of a neo-Y ($\lambda_{W',XY}=\lambda_{Y',XY}$), such that heterogametic transitions (XY to ZW or ZW to XY) can also occur only if the neo-sex-determining region is more closely linked to a locus under selection ($R<r$).
+Equation \eqref{eq:lambda_neoW} shows that, in contrast to the tight linkage results of the previous section, if there is no haploid selection ($t^\Hermaphrodite=\alpha^\Hermaphrodite_{\Delta}=0$), as considered by \citet{vanDoorn:2010hu} and weak selection, the spread of a neo-W is equivalent to the spread of a neo-Y ($\lambda_{W',XY}=\lambda_{Y',XY}$), such that heterogametic transitions (XY to ZW or ZW to XY) can also occur only if the neo-sex-determining region is more closely linked to a locus under selection ($R<r$).
 However, if there is any haploid selection, the additional term in equation \eqref{eq:lambda_neoW} can be positive, which can allow, for example, neo-W invasion ($\lambda_{W',XY}>1$) even when the neo-sex-determining region is less closely linked to the selected locus ($R>r$).
 These transitions are unusual because, when $R>r$, associations that selection has built up between alleles more favourable in one sex and alleles that determine sex will be weakened. 
-Mean fitness can therefore decrease with a heterogametic transition (Figure \ref{fig:Combination_MeanFit}B,D).
+Mean diploid fitness therefore decreases during heterogametic transitions that create looser sex-linkage (Figure \ref{fig:Combination_MeanFit}B,D).
 
@@
 It is even possible for the other selective forces to overwhelm sex-ratio selection and favour sex-determination transitions that create sex-ratio biases (Figure \ref{fig:Combination_Turnover}A,C).
+
+Previous research suggests that when the ancestral sex-determining locus is linked to a locus that experiences haploid selection (e.g., meiotic drive), a new, unlinked sex-determining locus invades in order to restore equal sex ratios \citep{Kozielska:2010vm}.
+Consider, for example, the case where the \textbf{A} locus is linked to the ancestral-SDR ($r<1/2$) and experiences meiotic drive in males only (e.g., during spermatogenesis but not during oogenesis, $\alpha^\male \neq 1/2$, $\alpha^\female=1/2$).
+We will also disregard gametic competition ($t^\female=t^\male=0$) such that zygotic sex ratios are only biased by meiotic drive in males. 
+In this case, the zygotic sex ratio can be initially biased only if the ancestral sex-determining system is XY (Figure \ref{fig:Combination_Turnover}B). 
+%If the ancxestral sex-determining system is ZW, the zygotic sex ratio will be 1:1 because diploid sex is determined by the proportion of Z-bearing versus W-bearing eggs and meiosis in females is fair (Figure \ref{fig:Combination_Turnover}D).
+We might therefore predict a difference when we  XY to ZW transitions 
+However, under weak selection we find that invasion by a homogametic neo-sex-determining allele (XY to XY or ZW to ZW) or by a heterogametic neo-sex-determining allele (XY to ZW or ZW to XY) occur under the same conditions.
+This is because, with weak selection, male biased zygotic sex ratios ($\zeta-1/2$) favouring the invasion of a neo-W are of the same order as meiotic drive favouring the invasion of a driving ne $\epsilon^2$.
+
+Therefore Fisherian sex ratio selection directly favours neo-Ws by a similar magnitude. 
+Perhaps surprisingly, neo-Ws can be favoured to the same degree by haploid selection in females when female haploid selection favours the alleles that tend to be carried by the neo-W.
+Thus XY to ZW is the same as ZW to XY even though sex ratio biases only exist in one case, given the assumptions made in this section
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Haplotype invasion region plot
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[!h]
+\centering
+\begin{tikzpicture}[remember picture]
+	\node[] () {
+	\includegraphics[width=0.5\linewidth]{regionplot_2a}
+	\includegraphics[width=0.5\linewidth]{regionplot_hap}
+	};
+\end{tikzpicture}
+\caption{
+Gray region depicts the relative fitnesses of male homozygotes, $w_AA^\male$ and $w_aa^\male$, that allow both neo-W haplotypes to invade, from any stable resident equilibria (equations \ref{eq:tightequil}).
+In the white region neo-W haplotypes paired with the allele fixed on the Y cannot invade.
+Parameters as in \cite{Otto2014} Figure 2a: $w_A^\female=w_a^\female=w_A^\male=w_a^\male=1$, $\alpha^\female=\alpha^\male=1/2$, $w_Aa^\female=w_Aa^\male=1$, and $w_AA^\female=w_aa^\female=0.75$, with $r=0$.
+}
+\label{fig:regionplot_ 2a}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %W invades XY and fixes
@@
 
-\begin{equation*}
-\begin{split}
+\begin{subequations}\label{eq:tightequil}
+\begin{align}
 (A)\ \ \ &\hat{p}_{Y}^{\male}=0,
@@
 &\hat{p}_{X}^{\female}=\frac{w_{a}^{\female} \phi}{w_{a}^{\female} \phi+ w_{A}^{\female} \psi},
-\ \hat{p}_{X}^{\male}=\frac{2 \alpha^{\male}w_{Aa}^{\male} \phi}{2\alpha^{\male}w_{Aa}^{\male} \phi +w_{AA}^{\male} \psi}\\
+\ \hat{p}_{X}^{\male}=\frac{2 \alpha^{\male}w_{Aa}^{\male} \phi}{2\alpha^{\male}w_{Aa}^{\male} \phi +w_{AA}^{\male} \psi} \nonumber \\
 (A')\ \ \ &\hat{p}_{Y}^{\male}=1,
@@
 &\hat{p}_{X}^{\female}=1-\frac{w_{A}^{\female} \phi'}{w_{A}^{\female} \phi'+ w_{a}^{\female} \psi'},
-\ \hat{p}_{X}^{\male}=1-\frac{2(1-\alpha^{\male})w_{Aa}^{\male} \phi'}{2(1-\alpha^{\male})w_{Aa}^{\male} \phi'+w_{aa}^{\male} \psi'}\\
+\ \hat{p}_{X}^{\male}=1-\frac{2(1-\alpha^{\male})w_{Aa}^{\male} \phi'}{2(1-\alpha^{\male})w_{Aa}^{\male} \phi'+w_{aa}^{\male} \psi'} \nonumber \\
 (B)\ \ \ &\hat{p}_{Y}^{\male}=0,\ \hat{p}_{X}^{\female}=1,\ \hat{p}_{X}^{\male}=1, \ \hat{q}=1-\alpha^{\male}\\
-(B')\ \ \ &\hat{p}_{Y}^{\male}=1,\ \hat{p}_{X}^{\female}=0,\ \hat{p}_{X}^{\male}=0, \ \hat{q}=\alpha^{\male}\\
-\end{split}
-\end{equation*}
+(B')\ \ \ &\hat{p}_{Y}^{\male}=1,\ \hat{p}_{X}^{\female}=0,\ \hat{p}_{X}^{\male}=0, \ \hat{q}=\alpha^{\male}
+\end{align}
+\end{subequations}
 \begin{equation*}
@@
 \phi'=&(1-\alpha^{\female}) w_{a}^{\female} w_{Aa}^{\female}(w_{A}^{\male} w_{AA}^{\male} + 2 (1-\alpha^{\male}) w_{a}^{\male} w_{Aa}^{\male}) - w_{A}^{\male} w_{A}^{\female} w_{AA}^{\male} w_{AA}^{\female}\\
-\psi'=&\alpha^{\female} w_{A}^{\female} w_{Aa}^{\female}(w_{A}^{\male} w_{AA}^{\male} + 2 (1-\alpha^{\male}) w_{a}^{\male} w_{Aa}^{\male}) - 2(1-\alpha^{\male}) w_{a}^{\male} w_{a}^{\female} w_{Aa}^{\male} w_{aa}^{\female}\\
+\psi'=&\alpha^{\female} w_{A}^{\female} w_{Aa}^{\female}(w_{A}^{\male} w_{AA}^{\male} + 2 (1-\alpha^{\male}) w_{a}^{\male} w_{Aa}^{\male}) - 2(1-\alpha^{\male}) w_{a}^{\male} w_{a}^{\female} w_{Aa}^{\male} w_{aa}^{\female}
 \end{split}
@@
 
-\noindent
-In this case, the zygotic sex ratio ($\zeta$) is given by the difference in haploid selection in males on $a$ (fixed on the Y) and $A$ (fixed on the X) alleles, i.e., there are more males than females if $\zeta = \alpha^\male w_A^\male / [(1-\alpha^\male)w_a^\male + \alpha^\male w_A^\male]<1/2$.
+%\noindent
+%In this case, the zygotic sex ratio ($\zeta$) is given by the difference in haploid selection in males on $a$ (fixed on the Y) and $A$ (fixed on the X) alleles, i.e., there are more males than females if $\zeta = \alpha^\male w_A^\male / [(1-\alpha^\male)w_a^\male + \alpha^\male w_A^\male]<1/2$.
 %$\alpha^\male<1/2$ and/or $w_{a}^\male>w_{A}^\male$.
-Populations with haploid selection for $a$ in males have a male biased zygotic sex ratio are thus more permissive to invasion by a neo-W ($\lambda_{mA}$ and $\lambda_{ma}$ larger).
-%In addition, the spread of neo-W alleles depends on the fitness of female diploids after mating with an X-$A$ or Y-$a$ male gamete, relative to the fitness of females in the population (all have genotype $AA$ and fitness $w_{AA}^\female$ at this equilibrium).
-Haploid selection in males has a second effect; the spread rate of neo-W haplotypes is determined by their fitness in diploid females, which depends on their diploid genotype and thus on the male gamete they pair with.
-Zygotes carrying dominant neo-W alleles will develop as females regardless of their genotype at the XY locus. 
-Therefore, neo-W females result from matings with either X-$A$ or Y-$a$ male gametes. 
-The relative proportion of these male gametes is determined by haploid selection in males; mating with a Y-$a$ male gamete is more likely if the $a$ allele is favoured during male gamete production or competition ($\zeta<1/2$).
-Thus, neo-W females experience different diploid selection than XX females, and the extent of this difference depends on haploid selection in males.
-Furthermore, haploid selection in females can directly select upon neo-W-$A$ or neo-W-$a$ haplotypes. 
-A neo-W-$A$ female gamete has the same fitness during haploid competition as resident $A$-bearing female gametes. 
-On the other hand, neo-W-$a$ female gametes can be favoured or disfavoured during female haploid competition (favoured if $w_{a}^\female>w_{A}^\female$). 
-Meiotic drive in females ($\alpha^\female$) similarly affects the fitness of these neo-W haplotypes, except that it impacts both haplotypes as meiotic drive only occurs in heterozygotes and therefore does not occur in resident XX females (who are always homozygote $AA$).
+%Populations with haploid selection for $a$ in males have a male biased zygotic sex ratio are thus more permissive to invasion by a neo-W ($\lambda_{mA}$ and $\lambda_{ma}$ larger).
+%%In addition, the spread of neo-W alleles depends on the fitness of female diploids after mating with an X-$A$ or Y-$a$ male gamete, relative to the fitness of females in the population (all have genotype $AA$ and fitness $w_{AA}^\female$ at this equilibrium).
+%Haploid selection in males has a second effect; the spread rate of neo-W haplotypes is determined by their fitness in diploid females, which depends on their diploid genotype and thus on the male gamete they pair with.
+%Zygotes carrying dominant neo-W alleles will develop as females regardless of their genotype at the XY locus. 
+%Therefore, neo-W females result from matings with either X-$A$ or Y-$a$ male gametes. 
+%The relative proportion of these male gametes is determined by haploid selection in males; mating with a Y-$a$ male gamete is more likely if the $a$ allele is favoured during male gamete production or competition ($\zeta<1/2$).
+%Thus, neo-W females experience different diploid selection than XX females, and the extent of this difference depends on haploid selection in males.
+%Furthermore, haploid selection in females can directly select upon neo-W-$A$ or neo-W-$a$ haplotypes. 
+%A neo-W-$A$ female gamete has the same fitness during haploid competition as resident $A$-bearing female gametes. 
+%On the other hand, neo-W-$a$ female gametes can be favoured or disfavoured during female haploid competition (favoured if $w_{a}^\female>w_{A}^\female$). 
+%Meiotic drive in females ($\alpha^\female$) similarly affects the fitness of these neo-W haplotypes, except that it impacts both haplotypes as meiotic drive only occurs in heterozygotes and therefore does not occur in resident XX females (who are always homozygote $AA$).
+
+Haploid selection impacts the spread of neo-W haplotypes in three ways.
+Firstly, the zygotic sex ratio becomes male biased ($\zeta<1/2$; at equilibrium (B) the sex ratio is $\zeta = \alpha^\male w_A^\male / [(1-\alpha^\male)w_a^\male + \alpha^\male w_A^\male]$) when the $a$ allele (which is fixed on the Y) is favoured during competition among male gametes or by meiotic drive in males.
+This facilitates the spread of a neo-W because neo-W alleles cause the zygotes that carry them to develop as the rarer, female, sex. 
+Secondly, haploid selection in males affects the diploid genotypes of females by altering the allele frequencies in the male gametes that female gametes pair with.
+For instance, because an epistatically dominant neo-W always causes its carrier to become female, it creates females who carry either Y-$a$ or X genotypes from their father.
+Thus, because when there is a polymorphism the X carries some non-zero frequency of $A$, haploid selection in males impacts the diploid genotypes of females (e.g., creating more $Aa$ females when drive in males favours Y-$a$).
+How this affects the spread of the neo-W then depends on diploid and haploid selection in females.
+Thirdly, female drive and gamete competition directly select on neo-W haplotypes.
+Drive for $A$ in females favours neo-W-$A$ haplotypes, at a cost to neo-W-$a$ haplotypes, and vice-versa when there is drive for $a$.
+The impact of this drive depends on how often XX and neo-W females are heterozygous.
+Competition among female gametes acts similarly, and depends on the frequency of $A$ on resident X chromosomes (e.g., competition among eggs has no affect on the initial spread of the neo-W-$A$ haplotype when $A$ is fixed on the X).
+Because haploid selection in females favours one neo-W haplotype at the expense of the other, recombination off the favoured background becomes more detrimental as it becomes more favoured.
+Thus higher rates of recombination between the neo-W and the selected locus, $R$, can lead to smaller leading eigenvalues when there is haploid selection in females.
 

### 2017-07-06 LaTeX/Turnover.tex
comment that we can only do ESD for weak sel

@@
 
+\textcolor{blue}{The characteristic polynomial describing eigenvalues of the 8 equation system (describing growth rate on XA, Xa, YA, Ya backgrounds in males and females) does not reduce for ESD mutants as it does for $k=0$ or $k=1$.
+Therefore we focus on weak selection here.}
 We next consider the case where the new sex-determining mutation, $m$, causes sex to be determined probabilistically or by heterogeneous environmental conditions (environmental sex determiner, ESD). 

### 2017-07-06 LaTeX/Turnover.tex
region plot figure added, working through mscott comments on discussion

--- 2017-07-06 LaTeX/Turnover.tex
@@
 %\textcolor{blue}{
-In Figure \ref{fig:regionplot_ 2a} we show a region of parameter space under which both neo-W haplotypes invade ($\lambda_{mA}>1$ and $\lambda_{ma}>1$) when there is overdominance in females and no haploid selection \citep[corresponding to Figure 2a in][]{Otto2014}.
+In Figure \ref{fig:regionplot_ 2a}A we show the region of parameter space within which both neo-W haplotypes invade ($\lambda_{mA}>1$ and $\lambda_{ma}>1$) when there is overdominance in females and no haploid selection \citep[corresponding to Figure 2a in][]{Otto2014}.
 Wherever both haplotypes have positive growth rates (gray region of Figure \ref{fig:regionplot_ 2a}), invasion by a neo-W is expected regardless of its linkage with the selected locus (i.e., even unlinked neo-W alleles can invade).
 In regions where only one haplotype can spread (white region of Figure \ref{fig:regionplot_ 2a}), a neo-W can invade as long as equation \eqref{eq:lambdasGen} is satisfied, which can require that the recombination rate, $R$, is small enough and yet still indicates that more loosely linked sex-determining regions can spread.
+It is also possible for haploid selection to drive the invasion of a loosely linked neo-W. 
+Take for instance selection directionally favouring $A$ in both diploid sexes and meiotic drive in males.
+Figure \ref{fig:regionplot_ 2a}B then shows that ploidally-antagonisitic selection can allow both neo-W haplotypes to invade. 
 %}
@@
 
-\textcolor{blue}{As with the discussion, this section might need some editing for (1) unclearly describing looser linkage never evolving without haploid selection, which we now show is possible above and (2) going on about sex ratio selection too much - this should be changed to something along the lines of  ``male biased zygotic sex ratios ($\zeta-1/2$) are of the order of $\epsilon^2$.
+%\textcolor{blue}{As with the discussion, this section might need some editing for (1) unclearly describing looser linkage never evolving without haploid selection, which we now show is possible above and (2) going on about sex ratio selection too much - this should be changed to something along the lines of  ``male biased zygotic sex ratios ($\zeta-1/2$) are of the order of $\epsilon^2$.
 Therefore Fisherian sex ratio selection directly favours neo-Ws by a similar magnitude.
-Perhaps surprisingly, neo-Ws can be favoured to the same degree by haploid selection in females when female haploid selection favours the alleles that tend to be carried by the neo-W.
-Thus XY to ZW is the same as ZW to XY even though sex ratio biases only exist in one case, given the assumptions made in this section.
-''
-}
+%Perhaps surprisingly, neo-Ws can be favoured to the same degree by haploid selection in females when female haploid selection favours the alleles that tend to be carried by the neo-W.
+%Thus XY to ZW is the same as ZW to XY even though sex ratio biases only exist in one case, given the assumptions made in this section.
+%''
+%}
 
@@
 %Sex ratios
-Previous research suggests that when the ancestral sex-determining locus is linked to a locus that experiences haploid selection (e.g., meiotic drive), a new, unlinked sex-determining locus invades in order to restore equal sex ratios \citep{Kozielska:2010vm}.
-Our model provides a good opportunity to determine whether Fisherian sex-ratio selection provides a useful explanation for the evolution of new sex-determining loci in other contexts. 
-Consider, for example, the case where the \textbf{A} locus is linked to the ancestral-SDR ($r<1/2$) and experiences meiotic drive in males only (e.g., during spermatogenesis but not during oogenesis, $\alpha^\male \neq 1/2$, $\alpha^\female=1/2$).
-We will also disregard gametic competition ($t^\female=t^\male=0$) such that zygotic sex ratios are only biased by meiotic drive in males. 
-In this case, the zygotic sex ratio can be initially biased only if the ancestral sex-determining system is XY (Figure \ref{fig:Combination_Turnover}B). 
-If the ancestral sex-determining system is ZW, the zygotic sex ratio will be 1:1 because diploid sex is determined by the proportion of Z-bearing versus W-bearing eggs and meiosis in females is fair (Figure \ref{fig:Combination_Turnover}D).
-Thus, if the zygotic sex ratio is crucial to the evolution of new genetic sex-determining systems, invasion into ZW and XY systems will be distinct. 
-However, under weak selection we find that invasion by a homogametic neo-sex-determining allele (XY to XY or ZW to ZW) or by a heterogametic neo-sex-determining allele (XY to ZW or ZW to XY) occur under the same conditions.
-That is, we can show that $\lambda_{Y',XY}=\lambda_{W',ZW}$ and $\lambda_{Y',ZW}=\lambda_{W',XY}$ (at least up to order $\epsilon^3$; for a numerical example, compare Figure \ref{fig:Combination_Turnover}A,B to Figure \ref{fig:Combination_Turnover}C,D).
-As it turns out, under weak selection the strength of sex-ratio selection favouring, say, the invasion of a neo-W in an XY system is the same as the strength of meiotic drive favouring the invasion of a neo-Y in a ZW system.
-Even when these forces are not exactly the same (e.g., under tight sex-linkage; compare black and red curves near -25 and 25cM in Figure \ref{fig:Combination_Centimorgans}), it is important to remember that sex-ratio selection is only one of many potential selective forces acting to determine transitions between sex-determining systems.
-It is even possible for the other selective forces to overwhelm sex-ratio selection and favour sex-determination transitions that create sex-ratio biases (Figure \ref{fig:Combination_Turnover}A,C).
+%Previous research suggests that when the ancestral sex-determining locus is linked to a locus that experiences haploid selection (e.g., meiotic drive), a new, unlinked sex-determining locus invades in order to restore equal sex ratios \citep{Kozielska:2010vm}.
+%Our model provides a good opportunity to determine whether Fisherian sex-ratio selection provides a useful explanation for the evolution of new sex-determining loci in other contexts. 
+%Consider, for example, the case where the \textbf{A} locus is linked to the ancestral-SDR ($r<1/2$) and experiences meiotic drive in males only (e.g., during spermatogenesis but not during oogenesis, $\alpha^\male \neq 1/2$, $\alpha^\female=1/2$).
+%We will also disregard gametic competition ($t^\female=t^\male=0$) such that zygotic sex ratios are only biased by meiotic drive in males. 
+%In this case, the zygotic sex ratio can be initially biased only if the ancestral sex-determining system is XY (Figure \ref{fig:Combination_Turnover}B). 
+%If the ancestral sex-determining system is ZW, the zygotic sex ratio will be 1:1 because diploid sex is determined by the proportion of Z-bearing versus W-bearing eggs and meiosis in females is fair (Figure \ref{fig:Combination_Turnover}D).
+%Thus, if the zygotic sex ratio is crucial to the evolution of new genetic sex-determining systems, invasion into ZW and XY systems will be distinct. 
+%However, under weak selection we find that invasion by a homogametic neo-sex-determining allele (XY to XY or ZW to ZW) or by a heterogametic neo-sex-determining allele (XY to ZW or ZW to XY) occur under the same conditions.
+%That is, we can show that $\lambda_{Y',XY}=\lambda_{W',ZW}$ and $\lambda_{Y',ZW}=\lambda_{W',XY}$ (at least up to order $\epsilon^3$; for a numerical example, compare Figure \ref{fig:Combination_Turnover}A,B to Figure \ref{fig:Combination_Turnover}C,D).
+%As it turns out, under weak selection the strength of sex-ratio selection favouring, say, the invasion of a neo-W in an XY system is the same as the strength of meiotic drive favouring the invasion of a neo-Y in a ZW system.
+%Even when these forces are not exactly the same (e.g., under tight sex-linkage; compare black and red curves near -25 and 25cM in Figure \ref{fig:Combination_Centimorgans}), it is important to remember that sex-ratio selection is only one of many potential selective forces acting to determine transitions between sex-determining systems.
+%It is even possible for the other selective forces to overwhelm sex-ratio selection and favour sex-determination transitions that create sex-ratio biases (Figure \ref{fig:Combination_Turnover}A,C).
 
@@
 Consider, for example, the case where the \textbf{A} locus is linked to the ancestral-SDR ($r<1/2$) and experiences meiotic drive in males only (e.g., during spermatogenesis but not during oogenesis, $\alpha^\male \neq 1/2$, $\alpha^\female=1/2$).
-We will also disregard gametic competition ($t^\female=t^\male=0$) such that zygotic sex ratios are only biased by meiotic drive in males. 
+Disregard gametic competition ($t^\female=t^\male=0$) such that zygotic sex ratios are only biased by meiotic drive in males. 
 In this case, the zygotic sex ratio can be initially biased only if the ancestral sex-determining system is XY (Figure \ref{fig:Combination_Turnover}B). 
 %If the ancxestral sex-determining system is ZW, the zygotic sex ratio will be 1:1 because diploid sex is determined by the proportion of Z-bearing versus W-bearing eggs and meiosis in females is fair (Figure \ref{fig:Combination_Turnover}D).
-We might therefore predict a difference when we  XY to ZW transitions 
-However, under weak selection we find that invasion by a homogametic neo-sex-determining allele (XY to XY or ZW to ZW) or by a heterogametic neo-sex-determining allele (XY to ZW or ZW to XY) occur under the same conditions.
-This is because, with weak selection, male biased zygotic sex ratios ($\zeta-1/2$) favouring the invasion of a neo-W are of the same order as meiotic drive favouring the invasion of a driving ne $\epsilon^2$.
-
-Therefore Fisherian sex ratio selection directly favours neo-Ws by a similar magnitude. 
-Perhaps surprisingly, neo-Ws can be favoured to the same degree by haploid selection in females when female haploid selection favours the alleles that tend to be carried by the neo-W.
-Thus XY to ZW is the same as ZW to XY even though sex ratio biases only exist in one case, given the assumptions made in this section
+We might therefore expect a difference in the potential for XY to ZW and ZW to XY transitions. 
+However, with weak selection we find that invasion by a neo-W into an XY system and invasion by a neo-Y into a ZW system occur under the same conditions. 
+As it turns out, with weak selection, the strength of a male biased zygotic sex ratio favouring the invasion of a neo-W is equal to the strength of meiotic drive favouring the invasion of a driving neo-Y are equal (at least up to order $\epsilon^2$).
+As selection becomes stronger (or linkage becomes tighter), this symmetry between sex-ratio selection and drive is lost, causing differences in the strength of selection favouring the two heterogametic transitions (compare red to black near -25cM and 25 cM in Figure \ref{fig:Combination_Centimorgans}).
+
+%Therefore Fisherian sex ratio selection directly favours neo-Ws by a similar magnitude. 
+%Perhaps surprisingly, neo-Ws can be favoured to the same degree by haploid selection in females when female haploid selection favours the alleles that tend to be carried by the neo-W.
+%Thus XY to ZW is the same as ZW to XY even though sex ratio biases only exist in one case, given the assumptions made in this section
 
@@
 We assume that individuals carrying the $m$ allele develop as females with probability $k$ (e.g., in a fraction $k$ of the environments they randomly experience).
+The characteristic polynomial determining the eigenvalues of the 8 equation system (equations \ref{eq:recursions}) does not reduce for ESD mutants as it does for $k=0$ or $k=1$. 
+We therefore focus on weak selection here. 
 Assuming weak selection, the spread of these mutations is given by
@@
 
-\textcolor{blue}{maybe re-order to put the results up front and focus on sex ratio less.
+%\textcolor{blue}{maybe re-order to put the results up front and focus on sex ratio less.
 Somewhere around these first two paragraphs we should include our tight linkage results.
@@
 
+%OPENING
+Two predominant theories explaining the remarkably high frequency of transitions between sex-determination systems are sexually-antagonistic selection and sex-ratio selection \citep[reviewed in][]{Blaser2012}.
+The former predicts that neo-sex-determining alleles can invade when they arise in closer linkage with a sexually-antagonistic locus \citep{vanDoorn:2007eu,vanDoorn:2010hu}.
+The latter predicts that neo-W alleles will invade an XY system when there is a male bias caused by haploid selection in males, and vice-versa, a neo-Y will invade a ZW system when there is a female bias caused by haploid selection in females \citep{Kozielska:2010vm,Ubeda:2015fx}.
+Here we have shown that both predictions must be amended when recombination is weak relative to selection or selection happens in both diploid and haploid phases.
+
+%TIGHT LINKAGE RESULTS
+When the rate of recombination between the ancestral sex-determining locus and a locus under selection is small relative to the strength of selection (i.e., sex-linkage is tight), heterogametic transitions (XY to ZW or ZW to XY) that reduce sex-linkage are possible, with or without haploid selection (Figure \ref{fig:regionplot_2a}A) or sexually-antagonistic selection (Figure \ref{fig:regionplot_2a}B).
+The likelihood of these transitions are driven by sex-ratio selection, direct selection on alleles linked to the neo-sex-determining allele, the ability of the neo-sex-determining allele to avoid selection in one sex, and the ability of the neo-sex-determining allele to bring alleles on the sex-specific chromosome in the ancestor into the other sex (given that the neo-sex determining allele is epistatically dominant to its predecessor).
+This possibility was overlooked in \cite{vanDoorn:2010hu}, possibly because they did not explicitly calculate the resident equilibria \citep[equation \ref{eq:tightequil};][]{Lloyd1977,Otto2014}.
+Interestingly, there is substantial overlap between the parameter space that allows both neo-W-$A$ and neo-W-$a$ haplotypes to spread in an XY system and that which selects for increased recombination between X and Y chromosomes \citep[e.g., compare gray region in Figure \ref{fig:regionplot_2a}A with coloured regions of Figure 2(a) in][]{Otto2014}.
+This makes sense as when both neo-W haplotypes can spread the neo-W can invade despite reducing sex-linkage, i.e., the rate of recombination between the sex-determining allele and the selected locus increases.
+\textcolor{red}{explain difference too? also explain why a neo-Y doesn't invade to reduce linkage despite selection for more recombination? mention something about haploid selection (Fig7B)?}
+
 %HAPLOID SELECTION CAN ACT LIKE SEXUALLY-ANTAGONISTIC SELECTION
-It has previously been demonstrated that new sex-determining systems can evolve if there is genetic variation maintained by sexually-antagonistic selection \citep{vanDoorn:2007eu,vanDoorn:2010hu}. 
-In particular, transitions to new sex-determining systems can occur when new sex-determining regions are more closely linked to a sexually-antagonistic locus.
+%It has previously been demonstrated that new sex-determining systems can evolve if there is genetic variation maintained by sexually-antagonistic selection \citep{vanDoorn:2007eu,vanDoorn:2010hu}. 
+%In particular, 
+Under weak selection (i.e., loose sex-linkage), transitions to new sex-determining systems can occur when new sex-determining regions are more closely linked to a sexually-antagonistic locus \citep{vanDoorn:2007eu,vanDoorn:2010hu}.
 Our results show that genetic variation at loci that experience haploid selection can also generate selection in favour of new sex-determining systems. 
-New sex-determining alleles are again favoured if they are linked with a locus under haploid selection and the ancestral sex-determination locus is not.
+New sex-determining alleles are again favoured if they are more closely linked to a locus under haploid selection.
+%HAPLOID SELECTION ALSO ALLOWS LOOSER LINKAGE TO EVOLVE
 However, with haploid selection, heterogametic transitions (XY to ZW or ZW to XY) can also occur when the new sex-determining region is less closely linked to the locus under selection. 
-
-%HAPLOID SELECTION ALSO ALLOWS LOOSER LINKAGE TO EVOLVE
 Neo-W (neo-Y) alleles invade when their fitness in females (males) is greater than the mean fitness of females (males) under the ancestral sex-determination system.
@@
 
-%TIGHT LINKAGE RESULTS
-
-\textcolor{blue}{maybe drop paragraph?}
-\textcolor{red}{I messed with the sex-ratio selection paragraphs to tone down our "it doesn't matter" speech from before. Have at any amendments you'd like to make.}
-%SEX-RATIO SELECTION
-Linkage between haploid selected loci and sex-determining regions cases biased zygotic sex ratios \citep{Hamilton:1967ts,Burt:2006,Field:2012fd,Field:2013cc}.
-One might then expect Fisherian sex-ratio selection to drive the spread of new sex-determining systems that bring the sex ratio closer to 50:50. 
-Fisherian sex-ratio selection follows from the fact that, for an autosomal locus, half of the genetic material is inherited from a male, and half from a female \citep{Fisher:1930wy,West:2009we}. 
-Thus, if the population sex ratio is biased towards females, the average per-individual contribution of genetic material to the next generation from males is greater than the contribution from females (and vice versa for male-biased sex ratios).
-Therefore, a mutant that increases investment in males will spread via the higher per-individual contributions made by males. 
+%%SEX-RATIO SELECTION
+%\textcolor{blue}{maybe drop paragraph?}
+%\textcolor{red}{I messed with the sex-ratio selection paragraphs to tone down our "it doesn't matter" speech from before. Have at any amendments you'd like to make.}
+%Linkage between haploid selected loci and sex-determining regions cases biased zygotic sex ratios \citep{Hamilton:1967ts,Burt:2006,Field:2012fd,Field:2013cc}.
+%One might then expect Fisherian sex-ratio selection to drive the spread of new sex-determining systems that bring the sex ratio closer to 50:50. 
+%Fisherian sex-ratio selection follows from the fact that, for an autosomal locus, half of the genetic material is inherited from a male, and half from a female \citep{Fisher:1930wy,West:2009we}. 
+%Thus, if the population sex ratio is biased towards females, the average per-individual contribution of genetic material to the next generation from males is greater than the contribution from females (and vice versa for male-biased sex ratios).
+%Therefore, a mutant that increases investment in males will spread via the higher per-individual contributions made by males. 
 %%%That is, under Fisherian sex-ratio selection, the success of a mutant relative to the non-mutant depends, in equal parts, on the contributions made by males and females to the next generation. 
@@
 
-\textcolor{blue}{Maybe we could go along the angle of ``under the weak recombination assumptions, there is no asymmetry between XY to ZW and ZW to XY, indicating that sex ratio selection does not dominate.
+%\textcolor{blue}{Maybe we could go along the angle of ``under the weak recombination assumptions, there is no asymmetry between XY to ZW and ZW to XY, indicating that sex ratio selection does not dominate.
 Asymmetry can be larger when linkage is tight (e.g., Fig 2C) but under most circumstances we do not predict asymmetry between XY to ZW and ZW to XY transitions despite the presence/absence of sex ratio selection.
-Thus, haploid selection can favour heterogametic transitions both via sex ratio selection and via the fitness of alleles that are associated with the neo-sex-determining allele; these selection pressures are often of equal magnitude.''}
+%Thus, haploid selection can favour heterogametic transitions both via sex ratio selection and via the fitness of alleles that are associated with the neo-sex-determining allele; these selection pressures are often of equal magnitude.''}
 
@@
 This of course generates new sex-ratio selection that may drive further turnover \citep{Ubeda:2015fx}.
-What we would like to stress is that sex-ratio selection alone cannot predict when new sex-determining systems can evolve.
+%What we would like to stress is that sex-ratio selection alone cannot predict when new sex-determining systems can evolve.
+Furthermore, with weak selection/loose sex-linkage, there is no asymmetry between XY to ZW and ZW to XY transitions, indicating that sex-ratio selection does not dominate (i.e., the sex-ratio bias created by haploid selection impacts the spread of a neo-W into an XY system the same way it impacts the spread of a neo-Y into an unbiased ZW system).
+An asymmetry can develop when sex-linkage is tight (e.g., Figure \ref{fig:Combination_Centimorgans} near -25cM and 25cM) but under most circumstances we do not predict asymmetry between XY to ZW and ZW to XY transitions despite the presence/absence of sex ratio selection.
+Thus, haploid selection can favour heterogametic transitions both via sex-ratio selection and via the fitness of alleles that are associated with the neo-sex-determining allele; and these selection pressures are often of equal magnitude.
 
@@
 \textcolor{blue}{I think Sally was sceptical of this idea. i.e., if the second term in \ref{eq:lambda_neoW} is negative, then get less transitions with haploid selection included, right? }
+\textcolor{red}{Yeah, and given that only 1/2 the discovered plant sex chromosomes are hetermorphic and there are so few plant sex chromosomes to begin with (Charlesworth 2016 Annual Review Plant Biology), might it be the case that haploid selection is constraining things?
+perhaps we could think of some particular forms of haploid selection that might be common and give their predicted effects, or just say some things that are possible with haploid selection that are not without it -- if there are any.
+just looking at eq 3 though, its gonna be hard to get a low freq of A on the Y if haploid selection in males favours A, i.e., it should often be positive when there is no female haploid selection, right?}
 Taken at face value, our results indicate that transitions in heterogametey (XY to ZW or vice versa) are more likely to be favoured by selection if there is selection upon both haploid and diploid genotypes rather than diploid selection alone.
@@
 \caption{
-Gray region depicts the relative fitnesses of male homozygotes, $w_AA^\male$ and $w_aa^\male$, that allow both neo-W haplotypes to invade, from any stable resident equilibria (equations \ref{eq:tightequil}).
+Parameter space (gray) where both neo-W haplotypes can invade from the same stable resident $r=0$ equilibria (equations \ref{eq:tightequil}), and therefore where an unlinked neo-W can invade an XY system with perfect sex-linkage.
+\textbf{A}, In the absence of haploid selection, both neo-W haplotypes can invade for much of the parameter space where the relative fitnesses of male homozygotes, $w_{AA}^\male$ and $w_{aa}^\male$, are both less than that of the heterozygote, $w_{Aa}^\male = 1$.
 In the white region neo-W haplotypes paired with the allele fixed on the Y cannot invade.
-Parameters as in \cite{Otto2014} Figure 2a: $w_A^\female=w_a^\female=w_A^\male=w_a^\male=1$, $\alpha^\female=\alpha^\male=1/2$, $w_Aa^\female=w_Aa^\male=1$, and $w_AA^\female=w_aa^\female=0.75$, with $r=0$.
+Parameters as in \cite{Otto2014} Figure 2a: $w_A^\Hermaphrodite=w_a^\Hermaphrodite$, $\alpha^\Hermaphrodite=1/2$, $w_Aa^\Hermaphrodite=1$, and $w_AA^\female=w_aa^\female=0.75$.
+\textbf{B}, When selection is the same in both diploid sexes ($w_{aa}^\Hermaphrodite = 1$, $w_{Aa}^\Hermaphrodite = 1 + h s$, $w_{AA}^\Hermaphrodite = 1+s$), both neo-W haplotypes can invade over a portion of the parameter space where selection in diploids ($s$) opposes the force of drive during meiosis in males ($\alpha_{\Delta}^\male$).
+Parameters: $w_A^\Hermaphrodite=w_a^\Hermaphrodite$, $\alpha^\female=1/2$, $h=1/2$.
 }
-\label{fig:regionplot_ 2a}
+\label{fig:regionplot_2a}
 \end{figure}

### 2017-07-07 LaTeX/Turnover.tex
minor thought about conclusions

@@
 This makes sense as when both neo-W haplotypes can spread the neo-W can invade despite reducing sex-linkage, i.e., the rate of recombination between the sex-determining allele and the selected locus increases.
-\textcolor{red}{explain difference too? also explain why a neo-Y doesn't invade to reduce linkage despite selection for more recombination? mention something about haploid selection (Fig7B)?}
+\textcolor{red}{explain difference too?
+also explain why a neo-Y doesn't invade to reduce linkage despite selection for more recombination?
+mention something about haploid selection (Fig7B)?} \textcolor{blue}{maybe leave for now}
 
@@
 In these cases, unlinked neo-W (neo-Y) alleles can increase female (male) fitness, at a cost to the other sex, and invade despite lowering mean fitness (Figure \ref{fig:Combination_MeanFit}).
+
+\textcolor{blue}{thought: maybe we could say somewhere that our results suggest more instability in sex-determination system than previously thought.
+Particularly, we show that variation around the ancestral sex-determining locus could favour new sex-determination systems under both haploid and diploid sex-specific selection, in contrast to previous results that rely on new sex-determining alleles arising in linkage with loci under sex-specific selection.
+This makes potential for cycling (which you mention in the next paragraph wrt sex ratio bias.
+Could be suitable here or in the conclusion?}
 
@@
 %and equalizing the sex ratio.
-Conversely, these additional selective effects can even favour transitions between sex-determining systems that create new sex-ratio biases.
+Indeed, these additional selective effects can even favour transitions between sex-determining systems that create new sex-ratio biases.
 For example, in an ancestral ZW system, an allele that drives only in males can allow a linked neo-Y to invade, despite the fact it creates a male bias.
-This of course generates new sex-ratio selection that may drive further turnover \citep{Ubeda:2015fx}.
+This of course generates new sex-ratio selection that may drive further turnover \citep{Ubeda:2015fx} \textcolor{blue}{and figure 1, where the end of one panel is the same as the beginning of another, however, this figure may change).}
 %What we would like to stress is that sex-ratio selection alone cannot predict when new sex-determining systems can evolve.
@@
 Thus, haploid selection can favour heterogametic transitions both via sex-ratio selection and via the fitness of alleles that are associated with the neo-sex-determining allele; and these selection pressures are often of equal magnitude.
+\textcolor{blue}{nice, pretty subtle argument but I think that's a good job.}
 
@@
 just looking at eq 3 though, its gonna be hard to get a low freq of A on the Y if haploid selection in males favours A, i.e., it should often be positive when there is no female haploid selection, right?}
+\textcolor{blue}{That sounds right to me and is backed up by equation \eqref{eq:freq_diffs}.
+It may be technically possible for that term to be negative though.
+Re: hetermorphism, I see that as a slightly different issue.
+It's thought that haploid selection may prevent deletions from becoming fixed on the Y, like in the Crowson (2017) paper.
+I think the issue of `why so few plant sex chromosomes' is partly an issue of detection and also `why so much hermaphroditism'.
+Is it possible that the ESD results could show selective forces that also favour transitions from dioecy to hermaphroditism?
+I think so.
+Our ESD mutant produces 1/2 females and 1/2 males whereas a hermaphrodite invests roughly equally in each type of gamete produced.
+We don't consider the forces that are usually thought to be involved in these transitions though (inbreeding depression, reproductive assurance and possibly others?).
+}
 Taken at face value, our results indicate that transitions in heterogametey (XY to ZW or vice versa) are more likely to be favoured by selection if there is selection upon both haploid and diploid genotypes rather than diploid selection alone.

### 2017-07-08 LaTeX/Turnover.tex
rewriting the discussion and fixed new zw to xy plots

--- 2017-07-06 LaTeX/Turnover.tex
@@
 
-%OPENING
+%MAIN RESULT
 Two predominant theories explaining the remarkably high frequency of transitions between sex-determination systems are sexually-antagonistic selection and sex-ratio selection \citep[reviewed in][]{Blaser2012}.
@@
 %TIGHT LINKAGE RESULTS
-When the rate of recombination between the ancestral sex-determining locus and a locus under selection is small relative to the strength of selection (i.e., sex-linkage is tight), heterogametic transitions (XY to ZW or ZW to XY) that reduce sex-linkage are possible, with or without haploid selection (Figure \ref{fig:regionplot_2a}A) or sexually-antagonistic selection (Figure \ref{fig:regionplot_2a}B).
-The likelihood of these transitions are driven by sex-ratio selection, direct selection on alleles linked to the neo-sex-determining allele, the ability of the neo-sex-determining allele to avoid selection in one sex, and the ability of the neo-sex-determining allele to bring alleles on the sex-specific chromosome in the ancestor into the other sex (given that the neo-sex determining allele is epistatically dominant to its predecessor).
-This possibility was overlooked in \cite{vanDoorn:2010hu}, possibly because they did not explicitly calculate the resident equilibria \citep[equation \ref{eq:tightequil};][]{Lloyd1977,Otto2014}.
-Interestingly, there is substantial overlap between the parameter space that allows both neo-W-$A$ and neo-W-$a$ haplotypes to spread in an XY system and that which selects for increased recombination between X and Y chromosomes \citep[e.g., compare gray region in Figure \ref{fig:regionplot_2a}A with coloured regions of Figure 2(a) in][]{Otto2014}.
-This makes sense as when both neo-W haplotypes can spread the neo-W can invade despite reducing sex-linkage, i.e., the rate of recombination between the sex-determining allele and the selected locus increases.
-\textcolor{red}{explain difference too? also explain why a neo-Y doesn't invade to reduce linkage despite selection for more recombination? mention something about haploid selection (Fig7B)?}
+When the rate of recombination between the ancestral sex-determining locus and a locus under selection is small relative to the strength of selection (i.e., sex-linkage is tight, or selection is strong), heterogametic transitions (XY to ZW or ZW to XY) that reduce sex-linkage are possible, with or without haploid selection or sexually-antagonistic selection (Figure \ref{fig:regionplot_2a}).
+The likelihoods of these transitions are driven by sex-ratio selection, direct selection on alleles linked to the neo-sex-determining allele, the ability of the neo-sex-determining allele to avoid selection in one sex, and the ability of the neo-sex-determining allele to bring alleles on the sex-specific chromosome in the ancestor into the other sex (given that the neo-sex determining allele is epistatically dominant to its predecessor).
+This possibility that looser sex-linkage could evolve, even in the absence of haploid selection (Figure \ref{fig:regionplot_2a}A), was overlooked in \cite{vanDoorn:2010hu}, likely because they did not explicitly calculate the resident equilibria \citep[equation \ref{eq:tightequil};][]{Lloyd1977,Otto2014}.
+Interestingly, there is substantial overlap between the parameter space that allows both neo-W-$A$ and neo-W-$a$ haplotypes to spread in an XY system and that which selects for increased recombination between X and Y chromosomes \citep[e.g., compare gray region of Figure \ref{fig:regionplot_2a}A with coloured regions of Figure 2(a) in][]{Otto2014}.
+This makes sense, as when both neo-W haplotypes can spread the neo-W can invade despite reducing sex-linkage, i.e., the rate of recombination between the sex-determining allele and the selected locus increases.
+\textcolor{red}{explain difference too?
+also explain why a neo-Y doesn't invade to reduce linkage despite selection for more recombination?
+mention something about haploid selection (Fig7B)?} \textcolor{blue}{maybe leave for now}
 
@@
 %In particular, 
-Under weak selection (i.e., loose sex-linkage), transitions to new sex-determining systems can occur when new sex-determining regions are more closely linked to a sexually-antagonistic locus \citep{vanDoorn:2007eu,vanDoorn:2010hu}.
-Our results show that genetic variation at loci that experience haploid selection can also generate selection in favour of new sex-determining systems. 
+Under weak selection (or loose sex-linkage), transitions to new sex-determining systems can occur when they arise more closely linked to a sexually-antagonistic locus \citep{vanDoorn:2007eu,vanDoorn:2010hu}.
+Our results show that genetic variation at loci that experience haploid selection can generate selection in favour of new sex-determining systems in a similar way. 
 New sex-determining alleles are again favoured if they are more closely linked to a locus under haploid selection.
@@
 However, if there is haploid selection on loci linked to an XY (ZW) sex-determining region, selection can maintain polymorphisms at which the mean fitness of females (males) is lower than it would be without sex-linkage.
-In these cases, unlinked neo-W (neo-Y) alleles can increase female (male) fitness, at a cost to the other sex, and invade despite lowering mean fitness (Figure \ref{fig:Combination_MeanFit}).
+In these cases, unlinked neo-W (neo-Y) alleles can increase the fitness of the only sex they are found in, at a cost to the other sex, and invade despite lowering mean fitness (Figure \ref{fig:Combination_MeanFit}).
+\textcolor{red}{This is similar to mitochondria and male disease ...?}
+
+%\textcolor{blue}{thought: maybe we could say somewhere that our results suggest more instability in sex-determination system than previously thought.
+Particularly, we show that variation around the ancestral sex-determining locus could favour new sex-determination systems under both haploid and diploid sex-specific selection, in contrast to previous results that rely on new sex-determining alleles arising in linkage with loci under sex-specific selection.
+This makes potential for cycling (which you mention in the next paragraph wrt sex ratio bias.
+Could be suitable here or in the conclusion?}
 
@@
 For instance, when an allele that drives in males is linked to an XY locus it will often become associated with the Y and therefore produce a male bias ($\zeta<1/2$).
-This male bias increases the potential for a neo-W to invade (as we then have $(2\zeta)^{-1}>1$, Table \ref{tab:haplotype_growth}), which can equalize the sex-ratio \citep[for a related example see][]{Ubeda:2015fx}.
+This male bias increases the potential for a neo-W to invade (as we then have $(2\zeta)^{-1}>1$ in Table \ref{tab:haplotype_growth}), which can equalize the sex-ratio \citep[for a related example see][]{Ubeda:2015fx}.
 %However, the neo-W may not equalize the sex-ratio (e.g., if the driving allele also drives in females or affects competition among eggs)
-However, this sex-ratio selection can be overwhelmed when the driving allele has additional selective effects (e.g., when it is detrimental to male diploids but beneficial for female diploids; Table \ref{tab:specialcases}), preventing the neo-W from invading.
+However, this sex-ratio selection can be overwhelmed when the driving allele has additional selective effects (e.g., when it is detrimental for male diploids but beneficial for female diploids; Table \ref{tab:specialcases}), preventing the neo-W from invading.
 %and equalizing the sex ratio.
-Conversely, these additional selective effects can even favour transitions between sex-determining systems that create new sex-ratio biases.
-For example, in an ancestral ZW system, an allele that drives only in males can allow a linked neo-Y to invade, despite the fact it creates a male bias.
-This of course generates new sex-ratio selection that may drive further turnover \citep{Ubeda:2015fx}.
+Indeed, these additional selective effects can even favour transitions between sex-determining systems that create new sex-ratio biases.
+For example, in an ancestral ZW system, an allele that drives only in males can allow a linked neo-Y to invade, despite the fact it creates a male bias (Figure \ref{fig:Combination_Turnover}C).
+%\textcolor{blue}{and figure 1, where the end of one panel is the same as the beginning of another, however, this figure may change).}
 %What we would like to stress is that sex-ratio selection alone cannot predict when new sex-determining systems can evolve.
-Furthermore, with weak selection/loose sex-linkage, there is no asymmetry between XY to ZW and ZW to XY transitions, indicating that sex-ratio selection does not dominate (i.e., the sex-ratio bias created by haploid selection impacts the spread of a neo-W into an XY system the same way it impacts the spread of a neo-Y into an unbiased ZW system).
+Furthermore, with weak selection, there is no asymmetry between XY to ZW and ZW to XY transitions, indicating that sex-ratio selection does not dominate (i.e., the sex-ratio bias created by haploid selection impacts the spread of a neo-W into an XY system the same way it impacts the spread of a neo-Y into a ZW system with a 1:1 sex ratio).
 An asymmetry can develop when sex-linkage is tight (e.g., Figure \ref{fig:Combination_Centimorgans} near -25cM and 25cM) but under most circumstances we do not predict asymmetry between XY to ZW and ZW to XY transitions despite the presence/absence of sex ratio selection.
-Thus, haploid selection can favour heterogametic transitions both via sex-ratio selection and via the fitness of alleles that are associated with the neo-sex-determining allele; and these selection pressures are often of equal magnitude.
+Thus, haploid selection can favour heterogametic transitions both via sex-ratio selection and via the fitness of alleles that are associated with the neo-sex-determining allele, and these selection pressures are often of equal magnitude.
+%\textcolor{blue}{nice, pretty subtle argument but I think that's a good job.}
 
@@
 We note that linkage with sex chromosomes is not, a priori, more permissive to the maintainence of ploidally antagonistic variation \citep{Immler:2012tl}.
-However, as with sexually-antagonistic variation, a comparison between closely related clades could indicate whether a polymorphism pre-dates a transition in sex-determination or arose afterwards (\textcolor{red}{George Sandler, an undergrad in the Wright and Barrett labs, has done some yet-to-be-published work on Rumex that we should cite here.
-We can send him this draft and get his permission to cite him as personal communication or something.
+However, as with sexually-antagonistic variation, a comparison between closely related clades could indicate whether a polymorphism pre-dates a transition in sex-determination or arose afterwards (\textcolor{red}{George Sandler, a student in the Wright and Barrett labs, has done some yet-to-be-published work on Rumex that we should cite here.
+We can send him this draft and get his permission to cite him as personal communication or unpublished results.
 I think he has basically found that genes retained on the Y are overexpressed in pollen but not in male diploids, suggesting they are being maintained by haploid selection, not sexual antagonism.
+And I think they know that the sex chromosomes are recently derived, and that in closely related species the autosome matching up with the newly derived sex chromosome also has genes that are over expressed in pollen.
 I guess this is a follow up to Crowson et al 2017 Mol Biol Evol 34:1140, which we could potentially cite as well.}).
-Secondly, we have shown that new sex-determination systems can be favoured if either the ancestral sex-determining region or the new sex-determining region are linked to loci under haploid selection. 
+Secondly, we have shown that new sex-determination systems can be favoured if either the ancestral sex-determining region or the new sex-determining region are linked to loci under haploid selection (\textcolor{red}{George Sandler again here}).
 Therefore, the presence of haploid selected loci around ancestral- or novel-sex-determining regions could support their role in sex chromosome turnover. 
+(\textcolor{red}{Or elaborate on George's work at length here instead of slipping in above}).
 %It would be particularly informative if selection were evaluated in closely related clades
@@
 %HOW TO TEST EMPIRICALLY
-\textcolor{blue}{I think Sally was sceptical of this idea. i.e., if the second term in \ref{eq:lambda_neoW} is negative, then get less transitions with haploid selection included, right? }
-\textcolor{red}{Yeah, and given that only 1/2 the discovered plant sex chromosomes are hetermorphic and there are so few plant sex chromosomes to begin with (Charlesworth 2016 Annual Review Plant Biology), might it be the case that haploid selection is constraining things?
+%\textcolor{blue}{I think Sally was sceptical of this idea. i.e., if the second term in \ref{eq:lambda_neoW} is negative, then get less transitions with haploid selection included, right? }
+%\textcolor{red}{Yeah, and given that only 1/2 the discovered plant sex chromosomes are hetermorphic and there are so few plant sex chromosomes to begin with (Charlesworth 2016 Annual Review Plant Biology), might it be the case that haploid selection is constraining things?
 perhaps we could think of some particular forms of haploid selection that might be common and give their predicted effects, or just say some things that are possible with haploid selection that are not without it -- if there are any.
 just looking at eq 3 though, its gonna be hard to get a low freq of A on the Y if haploid selection in males favours A, i.e., it should often be positive when there is no female haploid selection, right?}
-Taken at face value, our results indicate that transitions in heterogametey (XY to ZW or vice versa) are more likely to be favoured by selection if there is selection upon both haploid and diploid genotypes rather than diploid selection alone.
-This prediction could be examined using a suitable proxy for haploid selection, for example, \cite{Lenormand:2005vb} use the outcrossing rate in plants as a proxy for the strength of pollen competition.
+%\textcolor{blue}{That sounds right to me and is backed up by equation \eqref{eq:freq_diffs}.
+It may be technically possible for that term to be negative though.
+Re: hetermorphism, I see that as a slightly different issue.
+It's thought that haploid selection may prevent deletions from becoming fixed on the Y, like in the Crowson (2017) paper.
+%I think the issue of `why so few plant sex chromosomes' is partly an issue of detection and also `why so much hermaphroditism'.
+Is it possible that the ESD results could show selective forces that also favour transitions from dioecy to hermaphroditism?
+I think so.
+Our ESD mutant produces 1/2 females and 1/2 males whereas a hermaphrodite invests roughly equally in each type of gamete produced.
+We don't consider the forces that are usually thought to be involved in these transitions though (inbreeding depression, reproductive assurance and possibly others?).
+}
+%Taken at face value, our results indicate that transitions in heterogametey (XY to ZW or vice versa) are more likely to be favoured by selection if there is selection upon both haploid and diploid genotypes rather than diploid selection alone ().
+%This prediction could be examined using a suitable proxy for haploid selection, for example, \cite{Lenormand:2005vb} use the outcrossing rate in plants as a proxy for the strength of pollen competition.
+%In animals, one might expect gametic competition to be stronger in species where sperm is required to live for a long time after spermatogenesis because transcripts shared during spermatogenesis may become depleted, revealing the haploid phenotype of the sperm \citep{Immler:2014im}.
+%Given the caveats mentioned above about the form of meiotic drive modelled, we would also expect that heterogametic transitions in sex determination would be more common in clades where there is meiotic drive.
+Taken at face value, our results indicate that transitions in heterogametey (XY to ZW or vice versa) are more likely than transitions in homogamety when genetic conflict is predominately between the haploids of each sex (e.g., with $|D^\male - D^\female| << |\alpha_\Delta^\male - \alpha_\Delta^\female + t^\male - t^\female|$ we have $\lambda_{W',XY} > \lambda_{Y',XY}$; equations \ref{eq:lambda_neoW} and \ref{eq:freq_diffs}).
+In addition, because haploid selection can cause transitions that increase sex-ratio biases (Figure \ref{fig:Combination_Turnover}C), which may drive future transitions \citep[e.g., the male biased sex-ratio at end of Figure \ref{fig:Combination_Turnover}C is the same as the sex ratio at the beginning of  Figure \ref{fig:Combination_Turnover}B, which helps the neo-W invade; see also][]{Ubeda:2015fx}.
+This suggests that haploid selection may lead to less stability, and greater potential for cycling, in sex-determination systems. 
+These predictions could be examined using a suitable proxy for haploid selection, for example, \cite{Lenormand:2005vb} use the outcrossing rate in plants as a proxy for the strength of pollen competition.
 In animals, one might expect gametic competition to be stronger in species where sperm is required to live for a long time after spermatogenesis because transcripts shared during spermatogenesis may become depleted, revealing the haploid phenotype of the sperm \citep{Immler:2014im}.
@@
 
-\textcolor{blue}{similarly, this part doesn't discuss our new tight linkage results or our new perspective on sex ratios.}
+%\textcolor{blue}{similarly, this part doesn't discuss our new tight linkage results or our new perspective on sex ratios.}
 %CONCLUSION
-We have shown that haploid selection can drive transitions between sex-determination systems.
-We therefore argue that haploid selection should be considered, alongside sex-ratio selection and sexually-antagonistic selection, as an important factor influencing the evolution of sex determination.
-Further, we have shown the way in which transitions are affected by haploid selection is not intuitively obvious. 
-Firstly, sex-specific haploid selection affects turnovers between sex-determination systems in a manner that is qualitatively different from diploid sex-specific selection. 
-In particular, closer linkage between a sex-determining locus and a selected locus is not always favoured during heterogametic transitions when there is haploid selection. 
-Secondly, even though haploid selection is a source of zygotic sex-ratio biases, in our models Fisherian sex-ratio selection does not have good explanatory power in determining whether various sex-determination systems evolve.
-This result is surprising given that sex ratios are ultimately determined via the sex-determination system, and leads us to the conclusion that three selective forces -- haploid, diploid, and sex-ratio selection -- should all be considered when exploring transitions between sex-determination systems.
+We have shown that tight sex-linkage and haploid selection can drive previously unexpected transitions between sex-determination systems.
+In particular, both can select for looser sex-linkage and haploid selection alone can cause transitions analogous to those caused by purely sexually-antagonistic selection, eliminating the need for selection at the diploid level.
+Perhaps counterintuitively, haploid selection can also cause transitions driven by sex-ratio selection, or cause transitions that increase sex-ratio bias. 
+We therefore argue that haploid selection should be considered, alongside sexually-antagonistic and sex-ratio selection, as a potentially pivotal factor in the evolution of many sex-determination systems.
+%Further, we have shown the way in which transitions are affected by haploid selection is not intuitively obvious. 
+%Firstly, sex-specific haploid selection affects turnovers between sex-determination systems in a manner that is qualitatively different from diploid sex-specific selection. 
+%In particular, closer linkage between a sex-determining locus and a selected locus is not always favoured during heterogametic transitions when there is haploid selection. 
+%Secondly, even though haploid selection is a source of zygotic sex-ratio biases, in our models Fisherian sex-ratio selection does not have good explanatory power in determining whether various sex-determination systems evolve.
+%This result is surprising given that sex ratios are ultimately determined via the sex-determination system, and leads us to the conclusion that three selective forces -- haploid, diploid, and sex-ratio selection -- should all be considered when exploring transitions between sex-determination systems.
 
@@
 \caption{
-\textcolor{red}{Is this what Sally was thinking? I guess the right panel is pretty boring}
+\textcolor{red}{Is this what Sally was thinking?}
 }
@@
 \caption{
-\textcolor{red}{This complicated thing matches the plot above. We could combine this with that to make a 6 panel-er?}
+\textcolor{red}{This complicated thing matches the plot above. I don't think we want to include it...?}
 }
@@
 \caption{
-Changes in mean diploid fitness of males (blue lines), females (red lines), and the entire population (male mean fitness plus female mean fitness, black lines) during the transitions between sex-determination systems shown in Figure \ref{fig:Combination_Turnover}.
-Here we multiply male and female mean fitnesses by two so that we can show them on the same scale as population mean fitness. 
+Changes in mean diploid fitness of males (blue lines), females (red lines), and the entire population (black lines) during the transitions between sex-determination systems shown in Figure \ref{fig:Combination_Turnover}.
+Here mean diploid fitness of a sex is its mean diploid viability fitness times twice its frequency in the population, to capture the fact that epistatically dominant sex-determining alleles can also invade because they selfishly make more of the sex they are in.
 The mean fitness of females increases during the spread of neo-W alleles (A and B) and the mean fitness of males increases during the spread of neo-Y alleles (C and D). 

### 2017-07-08 LaTeX/Turnover.tex
mean fitness of sex splot caption cleared up

@@
 Changes in mean diploid fitness of males (blue lines), females (red lines), and the entire population (black lines) during the transitions between sex-determination systems shown in Figure \ref{fig:Combination_Turnover}.
-Here mean diploid fitness of a sex is its mean diploid viability fitness times twice its frequency in the population, to capture the fact that epistatically dominant sex-determining alleles can also invade because they selfishly make more of the sex they are in.
+Here mean diploid fitness of a particular sex is its mean diploid viability fitness times twice its frequency in the population, to capture the fact that epistatically dominant sex-determining alleles can also invade because they selfishly make more of the sex they are in.
 The mean fitness of females increases during the spread of neo-W alleles (A and B) and the mean fitness of males increases during the spread of neo-Y alleles (C and D). 
@@
 %}
-\textcolor{red}{I'm still confused why male and female mean fitnesses aren't normalized by their frequency.
+%\textcolor{red}{I'm still confused why male and female mean fitnesses aren't normalized by their frequency.
 I'm not sure we should be calling them means without this normalization step.
@@
 \caption{
-\textcolor{red}{Last plot with mean fitness of sexes corrected for sex ratio.}
+\textcolor{red}{Last plot with mean fitness of sexes corrected for sex ratio. Could add to previous plot with dashed lines?}
 }
@@
 In this case, the neo-W does not invade if $s^\female>s^\male$ (panel C: $s^\female=3/20$, $s^\male=1/20$) but does if $s^\female<s^\male$ (panel D: $s^\female=1/20$, $s^\male=3/20$), see Table \ref{tab:specialcases}.\\
-\textcolor{red}{
-1.
+%\textcolor{red}{
+%1.
 I suspect that panel C has a region where no equilibrium is maintained (CHECK!
@@
 MMO: If you trust the sieve function there are stable equilibria across the entire range, although they differ greatly between XY and ZW systems near -25cM.
-\\
-2.
+%\\
+%2.
 Currently use different parameters for B than using in figure \ref{fig:Combination_Turnover} (selection/drive twice as strong in turnover figure).
 MMO: this is to keep it within the bounds of the plot -- using the same parameters as figure 1 makes the peak at -25 reach roughly 0.1, and then it is difficult to see the details of A,C, and D.
-%This plot would also benefit from titles giving, e.g., ``sexually-antagonistic selection, $s^\female s^\male<0$'' for A, ``male meiotic drive, $s^\female s^\male>0$'' for B
-}
+%%This plot would also benefit from titles giving, e.g., ``sexually-antagonistic selection, $s^\female s^\male<0$'' for A, ``male meiotic drive, $s^\female s^\male>0$'' for B
+%}
 }

### 2017-07-10 LaTeX/Turnover.tex
discussion and Results finessing

@@
 I wonder if this is actually a fusion event though?
-In addition, many gonochoric clades with genetic sex determination exhibit transitions between male (XY) and female (ZW) heterogamety, including lizards \citep{Ezaz:2009tk}, eight of 26 teleost fish families \citep{Mank:2006bt}, true fruit flies \citep[Tephritids,][]{Vicoso:2015hf}, amphibians \citep{Hillis:1990gu}, the angiosperm genus \textit{Silene} \citep{Slancarova:2013dq}, and Coleoptera and Hemiptera \citep[][plate 2]{Beukeboom:2014vb}.
+In addition, many gonochoric clades with genetic sex determination exhibit transitions between male (XY) and female (ZW) heterogamety, including snakes \textcolor{red}{(Gamble et al.
+2017, Current Biology)}, lizards \citep{Ezaz:2009tk}, eight of 26 teleost fish families \citep{Mank:2006bt}, true fruit flies \citep[Tephritids,][]{Vicoso:2015hf}, amphibians \citep{Hillis:1990gu}, the angiosperm genus \textit{Silene} \citep{Slancarova:2013dq}, and Coleoptera and Hemiptera \citep[][plate 2]{Beukeboom:2014vb}.
 Indeed, in some cases, both male and female heterogametic sex-determination systems can be found in the same species, as exhibited by some cichlid species \citep{Ser:2010iq} and \textit{Rana rugosa} \citep{Ogata:2007jm}.
@@
 It is also possible for haploid selection to drive the invasion of a loosely linked neo-W. 
-Take for instance selection directionally favouring $A$ in both diploid sexes and meiotic drive in males.
+Take, for instance, selection directionally favouring $A$ in both diploid sexes and meiotic drive in males.
 Figure \ref{fig:regionplot_ 2a}B then shows that ploidally-antagonisitic selection can allow both neo-W haplotypes to invade. 
@@
 
-Equation \eqref{eq:lambda_neoW} shows that, in contrast to the tight linkage results of the previous section, if there is no haploid selection ($t^\Hermaphrodite=\alpha^\Hermaphrodite_{\Delta}=0$), as considered by \citet{vanDoorn:2010hu} and weak selection, the spread of a neo-W is equivalent to the spread of a neo-Y ($\lambda_{W',XY}=\lambda_{Y',XY}$), such that heterogametic transitions (XY to ZW or ZW to XY) can also occur only if the neo-sex-determining region is more closely linked to a locus under selection ($R<r$).
+Equation \eqref{eq:lambda_neoW} shows that, in contrast to the tight linkage results of the previous section, with weak selection and no haploid selection ($t^\Hermaphrodite=\alpha^\Hermaphrodite_{\Delta}=0$), as considered by \citet{vanDoorn:2010hu}, the spread of a neo-W is equivalent to the spread of a neo-Y ($\lambda_{W',XY}=\lambda_{Y',XY}$), such that heterogametic transitions (XY to ZW or ZW to XY) can also occur only if the neo-sex-determining region is more closely linked to a locus under selection ($R<r$).
 However, if there is any haploid selection, the additional term in equation \eqref{eq:lambda_neoW} can be positive, which can allow, for example, neo-W invasion ($\lambda_{W',XY}>1$) even when the neo-sex-determining region is less closely linked to the selected locus ($R>r$).
@@
 Consider, for example, the case where the \textbf{A} locus is linked to the ancestral-SDR ($r<1/2$) and experiences meiotic drive in males only (e.g., during spermatogenesis but not during oogenesis, $\alpha^\male \neq 1/2$, $\alpha^\female=1/2$).
-Disregard gametic competition ($t^\female=t^\male=0$) such that zygotic sex ratios are only biased by meiotic drive in males. 
+Disregarding gametic competition ($t^\female=t^\male=0$) such that zygotic sex ratios are only biased by meiotic drive in males. 
 In this case, the zygotic sex ratio can be initially biased only if the ancestral sex-determining system is XY (Figure \ref{fig:Combination_Turnover}B). 
@@
 We might therefore expect a difference in the potential for XY to ZW and ZW to XY transitions. 
-However, with weak selection we find that invasion by a neo-W into an XY system and invasion by a neo-Y into a ZW system occur under the same conditions. 
-As it turns out, with weak selection, the strength of a male biased zygotic sex ratio favouring the invasion of a neo-W is equal to the strength of meiotic drive favouring the invasion of a driving neo-Y are equal (at least up to order $\epsilon^2$).
-As selection becomes stronger (or linkage becomes tighter), this symmetry between sex-ratio selection and drive is lost, causing differences in the strength of selection favouring the two heterogametic transitions (compare red to black near -25cM and 25 cM in Figure \ref{fig:Combination_Centimorgans}).
+However, to leading order with selection weak relative to recombination, we find that sex ratio selection (first terms in table \ref{tab:haplotype_growth}) is equal in magnitude to the fitness effects of alleles associated with new sex-determining alleles (second terms in table \ref{tab:haplotype_growth}).
+Thus, invasion by a neo-W into an XY system and invasion by a neo-Y into a ZW system occur under the same conditions ($\lambda_{Y',XY}=\lambda_{W',ZW}$ and $\lambda_{Y',ZW}=\lambda_{W',XY}$, at least up to order $\epsilon^2$).
+As selection becomes stronger (or linkage becomes tighter), this symmetry between sex-ratio selection and haploid selection is lost, causing differences in the strength of selection favouring the two heterogametic transitions (compare red to black near -25cM and 25 cM in Figure \ref{fig:Combination_Centimorgans}).
 
@@
 
-Under Fisherian sex-ratio selection, autosomal modifiers favour equal investment in male and female offspring, i.e., a 1:1 sex ratio \citep{Fisher:1930wy,Charnov:1982wg,West:2009we}. 
-A novel environmental sex-determiner that causes half of its carriers to become female and half to become male ($k=1/2$) will be in males half of the time and in females half of the time (like an autosome).
-In addition, these novel sex-determination alleles equalize the sex ratio and therefore one might expect them to be favoured by Fisherian sex-ratio selection when the resident sex ratio is biased.
-However, assuming weak selection, we find that the growth rate of a rare, dominant offspring-controlled neo-ESD allele that produces males or females with equal probability ($k=1/2$) is
+%Under Fisherian sex-ratio selection, autosomal modifiers favour equal investment in male and female offspring, i.e., a 1:1 sex ratio \citep{Fisher:1930wy,Charnov:1982wg,West:2009we}. 
+%A novel environmental sex-determiner that causes half of its carriers to become female and half to become male ($k=1/2$) will be in males half of the time and in females half of the time (like an autosome).
+%In addition, these novel sex-determination alleles equalize the sex ratio and therefore one might expect them to be favoured by Fisherian sex-ratio selection when the resident sex ratio is biased.
+%However, assuming weak selection, we find that the growth rate of a rare, dominant offspring-controlled neo-ESD allele that produces males or females with equal probability ($k=1/2$) is
+Of particular interest are ESD mutations that cause half of their carriers to develop as females and half as males ($k=1/2$, creating equal sex ratios), the spread of which is given by
 \begin{equation}
@@
 preventing associations from building up between allele $A$ and sex.  
-
-Equation \eqref{eq:lambda_ESD} shows that invasion by a novel `perfect' ESD (equal sex ratio, $k=1/2$) mutation is the same for an ancestrally XY or ZW system (since $\lambda_{Y',XY} = \lambda_{W',ZW}$, $\lambda_{W',XY} = \lambda_{Y',ZW}$).
+An important result from equation \eqref{eq:lambda_ESD} is that ESD can invade if there is haploid selection. 
+When evaluated at $R=1/2$, $\lambda_{Y',XY} \leq 1$ but $\lambda_{W',XY}$ can be greater than one if there is haploid selection, as discussed above. 
+Previous studies where ESD is favoured have typically assumed that environmental conditions (e.g., maternal condition, mate quality, age, or host size) can differentially affect the fitness of males versus females such that ESD invades because it allows sex determination to depend on the environment \citep[reviewed in][]{Charnov:1982wg,Bull:1983vi,West:2009we}.
+Here, ESD mutations can spread because they generate females that are either rare or have high fitness, in the same manner as a neo-W.
+
+Equation \eqref{eq:lambda_ESD} also shows that invasion by a novel `perfect' ESD (equal sex ratio, $k=1/2$) mutation is the same for an ancestrally XY or ZW system (since $\lambda_{Y',XY} = \lambda_{W',ZW}$, $\lambda_{W',XY} = \lambda_{Y',ZW}$).
 Thus, by the same argument as above (if drive only occurs in males then the sex ratio is only biased when the ancestral sex-determination system is XY), Fisherian sex-ratio selection alone does not explain the invasion of an offspring-controlled neo-ESD allele under weak selection.
@@
 
-Fisherian sex-ratio selection is sometimes considered in terms of balancing parental investment in male versus female offspring \citep{Charnov:1982wg}.
-In addition, under environmental sex-determination, the proportion of males/females is sometimes controlled by the mother (e.g., the proportion of eggs laid in warm versus cold environments). 
-We therefore also considered the invasion of a neo-sex-determining allele ($m$) in a model in which mothers that have at least one $m$ allele produce daughters with probability $k$. 
-As with offspring-controlled ESD, for all $k\in\{0,1/2,1\}$, we find that invasion into an ancestral XY system is the same as invasion into an ancestrally ZW system (at least up to order $\epsilon^3$, assuming weak selection), implying that transitions between genetic sex-determination and maternally controlled environmental sex-determination are not driven by Fisherian sex-ratio selection alone.
-\textcolor{red}{(Maternal ESD analysis still lacks meiotic drive -- Mathematica can't seem to deal with the added complexity.)}
+%Fisherian sex-ratio selection is sometimes considered in terms of balancing parental investment in male versus female offspring \citep{Charnov:1982wg}.
+%In addition, under environmental sex-determination, the proportion of males/females is sometimes controlled by the mother (e.g., the proportion of eggs laid in warm versus cold environments). 
+%We therefore also considered the invasion of a neo-sex-determining allele ($m$) in a model in which mothers that have at least one $m$ allele produce daughters with probability $k$. 
+%As with offspring-controlled ESD, for all $k\in\{0,1/2,1\}$, we find that invasion into an ancestral XY system is the same as invasion into an ancestrally ZW system (at least up to order $\epsilon^3$, assuming weak selection), implying that transitions between genetic sex-determination and maternally controlled environmental sex-determination are not driven by Fisherian sex-ratio selection alone.
+%\textcolor{red}{(Maternal ESD analysis still lacks meiotic drive -- Mathematica can't seem to deal with the added complexity.)}
 
@@
 %MAIN RESULT
-Two predominant theories explaining the remarkably high frequency of transitions between sex-determination systems are sexually-antagonistic selection and sex-ratio selection \citep[reviewed in][]{Blaser2012}.
+Two predominant theories explaining the remarkably high frequency of transitions between sex-determination systems are sexually-antagonistic selection and sex-ratio selection \citep[reviewed in][]{Blaser2012} \textcolor{red}{(van Doorn, 2014, sexual development)}.
 The former predicts that neo-sex-determining alleles can invade when they arise in closer linkage with a sexually-antagonistic locus \citep{vanDoorn:2007eu,vanDoorn:2010hu}.
@@
 This makes sense, as when both neo-W haplotypes can spread the neo-W can invade despite reducing sex-linkage, i.e., the rate of recombination between the sex-determining allele and the selected locus increases.
-\textcolor{red}{explain difference too?
+%\textcolor{red}{explain difference too?
 also explain why a neo-Y doesn't invade to reduce linkage despite selection for more recombination?
@@
 However, with haploid selection, heterogametic transitions (XY to ZW or ZW to XY) can also occur when the new sex-determining region is less closely linked to the locus under selection. 
-Neo-W (neo-Y) alleles invade when their fitness in females (males) is greater than the mean fitness of females (males) under the ancestral sex-determination system.
+Neo-W (neo-Y) alleles invade when their fitness in females (males) is greater than the mean fitness of females (males) under the ancestral sex-determination system and/or females (males) are the rarer sex.
 With sexually-antagonistic selection (between diploid sexes) only, linkage between a selected locus and the sex-determining region strengthens associations between male beneficial alleles and the male-determining allele (Y or Z) and between female beneficial alleles and the female-determining allele (X or W).
@@
 Therefore, new sex-determining alleles only invade if they are more closely linked than the ancestral sex-determining region. 
-However, if there is haploid selection on loci linked to an XY (ZW) sex-determining region, selection can maintain polymorphisms at which the mean fitness of females (males) is lower than it would be without sex-linkage.
-In these cases, unlinked neo-W (neo-Y) alleles can increase the fitness of the only sex they are found in, at a cost to the other sex, and invade despite lowering mean fitness (Figure \ref{fig:Combination_MeanFit}).
-\textcolor{red}{This is similar to mitochondria and male disease ...?}
-
-%\textcolor{blue}{thought: maybe we could say somewhere that our results suggest more instability in sex-determination system than previously thought.
-Particularly, we show that variation around the ancestral sex-determining locus could favour new sex-determination systems under both haploid and diploid sex-specific selection, in contrast to previous results that rely on new sex-determining alleles arising in linkage with loci under sex-specific selection.
-This makes potential for cycling (which you mention in the next paragraph wrt sex ratio bias.
-Could be suitable here or in the conclusion?}
+However, if there is haploid selection on loci linked to an XY (ZW) sex-determining region, selection can maintain polymorphisms at which the product of the frequency of females (males) and the mean fitness of females (males) is lower than it would be without sex-linkage.
+In these cases, unlinked neo-W (neo-Y) alleles can increase the frequency and/or fitness of the only sex they are found in, at a cost to the other sex, and invade despite lowering population mean fitness (Figure \ref{fig:Combination_MeanFit}).
+%\textcolor{red}{This is similar to mitochondria and male disease ...?}
 
@@
 
-%\textcolor{blue}{Maybe we could go along the angle of ``under the weak recombination assumptions, there is no asymmetry between XY to ZW and ZW to XY, indicating that sex ratio selection does not dominate.
-Asymmetry can be larger when linkage is tight (e.g., Fig 2C) but under most circumstances we do not predict asymmetry between XY to ZW and ZW to XY transitions despite the presence/absence of sex ratio selection.
-%Thus, haploid selection can favour heterogametic transitions both via sex ratio selection and via the fitness of alleles that are associated with the neo-sex-determining allele; these selection pressures are often of equal magnitude.''}
-
 Sex ratio biases caused by gametic competition or meiotic drive have been shown to exert Fisherian sex-ratio selection on various autosomal \citep{Stalker:1961th,Smith:1975ft,Frank:1989vl,Hough:2013uo,Ubeda:2015fx, Otto:2015va} and sex-linked \citep{Ubeda:2015fx} modifiers.
@@
 %However, the neo-W may not equalize the sex-ratio (e.g., if the driving allele also drives in females or affects competition among eggs)
-However, this sex-ratio selection can be overwhelmed when the driving allele has additional selective effects (e.g., when it is detrimental for male diploids but beneficial for female diploids; Table \ref{tab:specialcases}), preventing the neo-W from invading.
+However, this sex-ratio selection can be overwhelmed when the driving allele has additional selective effects (e.g., when it is beneficial for male diploids but detrimental for female diploids; Table \ref{tab:specialcases}), preventing the neo-W from invading.
 %and equalizing the sex ratio.
@@
 An asymmetry can develop when sex-linkage is tight (e.g., Figure \ref{fig:Combination_Centimorgans} near -25cM and 25cM) but under most circumstances we do not predict asymmetry between XY to ZW and ZW to XY transitions despite the presence/absence of sex ratio selection.
-Thus, haploid selection can favour heterogametic transitions both via sex-ratio selection and via the fitness of alleles that are associated with the neo-sex-determining allele, and these selection pressures are often of equal magnitude.
+Thus, haploid selection can favour heterogametic transitions both via sex-ratio selection and via fitness effects of alleles that are associated with the neo-sex-determining allele, and these selection pressures are often of equal magnitude.
 %\textcolor{blue}{nice, pretty subtle argument but I think that's a good job.}
@@
 In the case of sexually-antagonistic variation, one supporting observation is that genes expected to be under sexually-antagonistic selection (e.g., those causing bright male colouration) have been found on recently derived sex chromosomes \citep{Lindholm:2002dw,Tripathi:2009cw,Ser:2010iq}.
-However, it is possible that sexually-antagonistic variation accumulated after sex chromosome transitions because linkage with the sex-determining regions allows sexually-antagonistic selection to maintain polymorphisms under a larger parameter space \citep{Rice:1987hs,Jordan:2011fj}.
-We note that linkage with sex chromosomes is not, a priori, more permissive to the maintainence of ploidally antagonistic variation \citep{Immler:2012tl}.
-However, as with sexually-antagonistic variation, a comparison between closely related clades could indicate whether a polymorphism pre-dates a transition in sex-determination or arose afterwards (\textcolor{red}{George Sandler, a student in the Wright and Barrett labs, has done some yet-to-be-published work on Rumex that we should cite here.
+Our results suggest that polymorphic loci that are ancestrally sex-linked and under sex-specific selection could also drive heterogametic transitions between sex-determination systems. 
+As noted by \citet{vanDoorn:2010hu}, it would be prudent to compare closely related clades in order to determine whether observed polymorphisms pre-dates a transition in sex-determination or arose afterwards, particularly because sex-linkage allows sexually-antagonistic selection to maintain polymorphisms under a different and larger parameter space \citep{Rice:1987hs,Jordan:2011fj}.
+As with sexually-antagonistic selection, the presence of haploid selected loci around ancestral- or novel-sex-determining regions could support their role in sex chromosome turnover.
+%We note that linkage with sex chromosomes is not, a priori, more permissive to the maintenance of ploidally antagonistic variation \citep{Immler:2012tl}. 
+A recent transcriptome analysis in \textit{Rumex}, suggests a role for haploid competition in the evolution of sex-determination systems by showing that Y-linked genes are overexpressed in pollen but not in male diploids, indicating variation currently or previously maintained by haploid selection; over-expression also occurs on the autosome that is orthologous to the sex chromosomes in closely related species \textcolor{red}{(Sandler et al., 2017, Personal Communication)}.
+% (\textcolor{red}{George Sandler, a student in the Wright and Barrett labs, has done some yet-to-be-published work on Rumex that we should cite here.
 We can send him this draft and get his permission to cite him as personal communication or unpublished results.
@@
 I guess this is a follow up to Crowson et al 2017 Mol Biol Evol 34:1140, which we could potentially cite as well.}).
-Secondly, we have shown that new sex-determination systems can be favoured if either the ancestral sex-determining region or the new sex-determining region are linked to loci under haploid selection (\textcolor{red}{George Sandler again here}).
-Therefore, the presence of haploid selected loci around ancestral- or novel-sex-determining regions could support their role in sex chromosome turnover. 
-(\textcolor{red}{Or elaborate on George's work at length here instead of slipping in above}).
-%It would be particularly informative if selection were evaluated in closely related clades
 
@@
 Taken at face value, our results indicate that transitions in heterogametey (XY to ZW or vice versa) are more likely than transitions in homogamety when genetic conflict is predominately between the haploids of each sex (e.g., with $|D^\male - D^\female| << |\alpha_\Delta^\male - \alpha_\Delta^\female + t^\male - t^\female|$ we have $\lambda_{W',XY} > \lambda_{Y',XY}$; equations \ref{eq:lambda_neoW} and \ref{eq:freq_diffs}).
-In addition, because haploid selection can cause transitions that increase sex-ratio biases (Figure \ref{fig:Combination_Turnover}C), which may drive future transitions \citep[e.g., the male biased sex-ratio at end of Figure \ref{fig:Combination_Turnover}C is the same as the sex ratio at the beginning of  Figure \ref{fig:Combination_Turnover}B, which helps the neo-W invade; see also][]{Ubeda:2015fx}.
-This suggests that haploid selection may lead to less stability, and greater potential for cycling, in sex-determination systems. 
-These predictions could be examined using a suitable proxy for haploid selection, for example, \cite{Lenormand:2005vb} use the outcrossing rate in plants as a proxy for the strength of pollen competition.
+In addition, because haploid selection can cause transitions that increase or decrease sex-linkage, haploid selection may lead to less stability, and greater potential for cycling, in sex-determination systems (e.g., the final state in Figure \ref{fig:Combination_Turnover}C is the starting state in Figure \ref{fig:Combination_Turnover}B).
+Potentially, successive heterogametic transitions between master regulators of sex-determination could be inferred from careful examination of the molecular pathways by which sex is determined. 
+Our predictions could also be examined using a suitable proxy for haploid selection, for example, \cite{Lenormand:2005vb} use the outcrossing rate in plants as a proxy for the strength of pollen competition.
+Furthermore, assuming that transitions from dioecy to hermaphroditism (equal parental investment in male and female gametes) are favoured in a similar manner to the ESD examined here (equal probability of zygotes developing as males or females), our results suggest that haploid competition during the multicellular haploid stage could drive transitions between dioecy and hermaphroditism in plants \textcolor{red}{(Käfer et al., 2017, Sabath et al., 2017)}.
 In animals, one might expect gametic competition to be stronger in species where sperm is required to live for a long time after spermatogenesis because transcripts shared during spermatogenesis may become depleted, revealing the haploid phenotype of the sperm \citep{Immler:2014im}.
@@
 We have shown that tight sex-linkage and haploid selection can drive previously unexpected transitions between sex-determination systems.
-In particular, both can select for looser sex-linkage and haploid selection alone can cause transitions analogous to those caused by purely sexually-antagonistic selection, eliminating the need for selection at the diploid level.
-Perhaps counterintuitively, haploid selection can also cause transitions driven by sex-ratio selection, or cause transitions that increase sex-ratio bias. 
+In particular, both can select for neo-sex-determining loci that are more loosely linked. 
+In addition, haploid selection alone can cause transitions analogous to those caused by purely sexually-antagonistic selection, eliminating the need for differences in selection between male and female diploids.
+Perhaps counterintuitively, transitions involving haploid selection can be driven by sex-ratio selection, or cause sex-ratio biases to evolve. 
 We therefore argue that haploid selection should be considered, alongside sexually-antagonistic and sex-ratio selection, as a potentially pivotal factor in the evolution of many sex-determination systems.
+Overall, our results suggest several new scenarios under which new sex-determination systems are favoured, including sex-specific selection on ancestrally sex-linked loci, which could help to explain why the evolution of sex-determination systems is so dynamic.
 %Further, we have shown the way in which transitions are affected by haploid selection is not intuitively obvious. 
@@
 \textcolor{red}{Is this what Sally was thinking?}
+\textcolor{blue}{I think this works but I'm confused as to why the speed of spread should be so much different for XY and ZW here.
+Figure \ref{fig:Combination_Turnover} and \ref{fig:Combination_Centimorgans} suggests that there's not much difference between XY->ZW and ZW->XY.
+Maybe we should just stick with the 4 cases in figure \ref{fig:Combination_Turnover}.
+}
 }
@@
 See the next figure for what happens when we do normalize.}
+\textcolor{blue}{I think we should give this plot showing (male mean fitness * freq males) and (female mean fitness * freq females), without multiplying by 2 (leave off black lines, population mean fitness).
+We could also re-plot the sex ratios on this same scale. 
+The plot below, `adjusted for sex ratio', could then go in the appendix. The point is that neo-W (neo-Y) can invade when the frequency of females (males) multiplied by their mean fitness increases.  }
 }

### 2017-07-21 LaTeX/Turnover.tex
changing fig6 to sallys liking

@@
 %\textcolor{blue}{
-In Figure \ref{fig:regionplot_ 2a}A we show the region of parameter space within which both neo-W haplotypes invade ($\lambda_{mA}>1$ and $\lambda_{ma}>1$) when there is overdominance in females and no haploid selection \citep[corresponding to Figure 2a in][]{Otto2014}.
-Wherever both haplotypes have positive growth rates (gray region of Figure \ref{fig:regionplot_ 2a}), invasion by a neo-W is expected regardless of its linkage with the selected locus (i.e., even unlinked neo-W alleles can invade).
-In regions where only one haplotype can spread (white region of Figure \ref{fig:regionplot_ 2a}), a neo-W can invade as long as equation \eqref{eq:lambdasGen} is satisfied, which can require that the recombination rate, $R$, is small enough and yet still indicates that more loosely linked sex-determining regions can spread.
+In Figure \ref{fig:regionplot_2a}A we show the region of parameter space within which both neo-W haplotypes invade ($\lambda_{mA}>1$ and $\lambda_{ma}>1$) when there is overdominance in females and no haploid selection \citep[corresponding to Figure 2a in][]{Otto2014}.
+Wherever both haplotypes have positive growth rates (gray region of Figure \ref{fig:regionplot_2a}), invasion by a neo-W is expected regardless of its linkage with the selected locus (i.e., even unlinked neo-W alleles can invade).
+In regions where only one haplotype can spread (white region of Figure \ref{fig:regionplot_2a}), a neo-W can invade as long as equation \eqref{eq:lambdasGen} is satisfied, which can require that the recombination rate, $R$, is small enough and yet still indicates that more loosely linked sex-determining regions can spread.
 It is also possible for haploid selection to drive the invasion of a loosely linked neo-W. 
 Take, for instance, selection directionally favouring $A$ in both diploid sexes and meiotic drive in males.
-Figure \ref{fig:regionplot_ 2a}B then shows that ploidally-antagonisitic selection can allow both neo-W haplotypes to invade. 
+Figure \ref{fig:regionplot_2a}B then shows that ploidally-antagonisitic selection can allow both neo-W haplotypes to invade. 
 %}
@@
 }
+\textcolor{red}{i messed up and had $r=0.5$ instead of $r=0.05$ for B and D. haven't fixed fitness plot below.}
 }
@@
 \begin{tikzpicture}[remember picture]
-	\node[] () {\includegraphics[width=\linewidth]{PositionPlot}};
-	\node[anchor=east] at (0.5, 1.5) {\footnotesize sexual-antagonism, $s^\male s^\female < 0$};
-	\node[anchor=east] at (6.5, 1.5) {\footnotesize male drive, $s^\male s^\female > 0$};
-	\node[anchor=east] at (0.5, -3) {\footnotesize pollen competition, $s^\male < s^\female$};
-	\node[anchor=east] at (6.5, -3) {\footnotesize pollen comptition, $s^\female < s^\female$};
+%	\node[] () {\includegraphics[width=\linewidth]{PositionPlot}};
+	\node[] () {\includegraphics[width=\linewidth]{PositionPlot_2}};
+	\node[anchor=east] at (0, 1.5) {\footnotesize diploid sex-antagonism}; %, $s^\male s^\female < 0$};
+	\node[anchor=east] at (6.5, 1.5) {\footnotesize haploid sex-antagonism}; %, $s^\male s^\female > 0$};
+	\node[anchor=east] at (0, -3) {\footnotesize male drive (ploidy-antagonism)}; %, $s^\male < s^\female$};
+%	\node[anchor=east] at (6.5, -3) {\footnotesize pollen competition (ploidy-antagonism)};%, $s^\female < s^\female$};
+	\node[anchor=center] at (-1.3, 4.25) {\scriptsize tighter sex-linkage};
+	\node[anchor=center] at (2.45, 3.5) {\scriptsize ancestral SDR};
+	\draw[->,thick] (2.45, 3.25) -- (2.45, 2.5);
+	\node[anchor=center] at (-1.4, -0.25) {\scriptsize novel SDR};
+	\draw[->,thick] (-1.4, -0.5) -- (-1.4, -1);
 \end{tikzpicture}
 \caption{
-Invasion fitness of a neo-W allele plotted against the relative genomic location of a locus under direct selection, \textbf{A}, for various selective regimes. 
+Invasion fitness of a neo-sex-determining allele plotted against the relative genomic location of a locus under direct selection, \textbf{A}, for various selective regimes. 
 The ancestral sex-determining locus is located at -25 and the novel sex-determining locus is located at 25. %and that there is a polymorphism at the \textbf{A} locus maintained by selection.
@@
 In A, there is no haploid selection ($t^\Hermaphrodite=\alpha^\Hermaphrodite_{\Delta}=0$) and selection in diploids is sexually antagonistic \citep[following][]{vanDoorn:2010hu}, in which case a neo-W can only invade if it is more closely linked to the selected locus ($s^\female=1/10$, $h^\female=7/10$ $s^\male=-1/10$, $h^\male=3/10$).
-In B-D we include haploid selection and assume that selection in diploids is not sexually-antagonistic ($s^\female s^\male>0$). 
-A polymorphism can then be maintained by opposing selection between the haploid and diploid phases. 
-In B, there is drive in favour of the $a$ allele in males ($\alpha^\male_{\Delta}=-1/20$), no female meiotic drive or gametic competition, $t^\Hermaphrodite=\alpha^\female_{\Delta}=0$), and equal selection in diploid sexes ($s^\female=s^\male=1/10$, $h^\female=h^\male=7/10$).
-In this case, a neo-W can invade even when the selected locus is more closely linked to the ancestral sex determining locus (see Table \ref{tab:specialcases} and Figure \ref{fig:Combination_Turnover}).
-In C and D, there is gametic competition among male gametes only (favouring $a$, $t^\male=-1/10$) and no meiotic drive or gametic competition in females ($t^\female=\alpha^\Hermaphrodite_{\Delta}=0$).
-In this case, the neo-W does not invade if $s^\female>s^\male$ (panel C: $s^\female=3/20$, $s^\male=1/20$) but does if $s^\female<s^\male$ (panel D: $s^\female=1/20$, $s^\male=3/20$), see Table \ref{tab:specialcases}.\\
+In B-D we include haploid selection. %and assume that selection in diploids is not sexually-antagonistic ($s^\female s^\male>0$). 
+%A polymorphism can then be maintained by opposing selection between the haploid and diploid phases. 
+%In B, there is drive in favour of the $a$ allele in males ($\alpha^\male_{\Delta}=-1/20$), no female meiotic drive or gametic competition, $t^\Hermaphrodite=\alpha^\female_{\Delta}=0$), and equal selection in diploid sexes ($s^\female=s^\male=1/10$, $h^\female=h^\male=7/10$).
+%In this case, a neo-W can invade even when the selected locus is more closely linked to the ancestral sex determining locus (see Table \ref{tab:specialcases} and Figure \ref{fig:Combination_Turnover}).
+%In C and D, there is gametic competition among male gametes only (favouring $a$, $t^\male=-1/10$) and no meiotic drive or gametic competition in females ($t^\female=\alpha^\Hermaphrodite_{\Delta}=0$).
+%In this case, the neo-W does not invade if $s^\female>s^\male$ (panel C: $s^\female=3/20$, $s^\male=1/20$) but does if $s^\female<s^\male$ (panel D: $s^\female=1/20$, $s^\male=3/20$), see Table \ref{tab:specialcases}.\\
+In B
 %\textcolor{red}{
@@
 In the white region neo-W haplotypes paired with the allele fixed on the Y cannot invade.
-Parameters as in \cite{Otto2014} Figure 2a: $w_A^\Hermaphrodite=w_a^\Hermaphrodite$, $\alpha^\Hermaphrodite=1/2$, $w_Aa^\Hermaphrodite=1$, and $w_AA^\female=w_aa^\female=0.75$.
+Parameters as in \cite{Otto2014} Figure 2a: $w_A^\Hermaphrodite=w_a^\Hermaphrodite$, $\alpha^\Hermaphrodite=1/2$, $w_{Aa}^\Hermaphrodite=1$, and $w_{AA}^\female=w_{aa}^\female=0.75$.
 \textbf{B}, When selection is the same in both diploid sexes ($w_{aa}^\Hermaphrodite = 1$, $w_{Aa}^\Hermaphrodite = 1 + h s$, $w_{AA}^\Hermaphrodite = 1+s$), both neo-W haplotypes can invade over a portion of the parameter space where selection in diploids ($s$) opposes the force of drive during meiosis in males ($\alpha_{\Delta}^\male$).

### 2017-07-28 LaTeX/Turnover.tex
Minor Sally edits added up until tight linkage section

@@
 
-\title{Gametic Selection, Meiotic Drive, Sex Ratio Bias, and Transitions Between sex-determination systems}
+\title{Haploid Selection, Sex Ratio Bias, and Transitions Between sex-determination systems}
 \author{Michael F Scott$*^1$, Matthew M Osmond$*^2$, and Sarah P Otto$^2$}
@@
 (2) We also consider selection upon haploid genotypes either during gametic competition (e.g., pollen/sperm competition) or meiosis (i.e., non-Mendelian segregation); selective processes that typically occur in one sex or the other.
-As well as having sex-specific fitness consequences, haploid selection can cause the zygotic sex ratio to become biased because sex ratios are determined by the production and fertilization success of X- versus Y-bearing pollen/sperm (or Z- versus W-bearing ovules/eggs).
-Consequently, selection for XY to ZW transitions and ZW to XY transitions can be assymetrical when linkage between the ancestral sex-determining locus and a locus under haploid selection is tight, in which case ancestral sex ratio biases can be strong.
+%As well as having sex-specific fitness consequences, haploid selection can cause the zygotic sex ratio to become biased because sex ratios are determined by the production and fertilization success of X- versus Y-bearing pollen/sperm (or Z- versus W-bearing ovules/eggs).
+%Consequently, selection for XY to ZW transitions and ZW to XY transitions can be assymetrical when linkage between the ancestral sex-determining locus and a locus under haploid selection is tight, in which case ancestral sex ratio biases can be strong.
 %In addition, when linkage between the ancestral sex-determining locus and a locus under haploid selection is tight, sex ratio biases can be strong such that there is an asymmetry between invasion of ancestrally XY and ancestrally ZW systems because, e.g., haploid selection in males only causes biased zygotic sex ratios in an ancestrally XY system.
-With looser linkage and haploid selection, we again find
-%In addition, when there is haploid selection, we find 
-that transitions between male and female heterogamety can occur even if the new sex-determining region is less closely linked to the locus under selection. 
-That is, favourable associations that develop between the ancestral sex-determining locus and selected loci can be broken during the spread of a new sex-determining region. 
+With haploid selection, we again find that transitions between male and female heterogamety can occur even if the new sex-determining region is less closely linked to the locus under selection, and when linkage is tight haploid selection in the heterogametic sex can cause strong sex ratio bias, which may increase or decrease with the spread of new sex chromsomes.
+These results indicate that favourable associations that develop between the ancestral sex-determining locus and selected loci can be broken during the spread of a new sex-determining region. 
 %Such transitions are not possible with diploid selection alone, in which case tighter linkage increases the fitness of both males and females. 
@@
 \citet{vanDoorn:2007eu,vanDoorn:2010hu} show that new sex-determining loci can be favoured if they arise in closer linkage with a locus that experiences sexual antagonism. 
-For example, tighter linkage allows a stronger favourable association to build up between a male-beneficial allele and a neo-Y chromosome. 
+Tighter linkage allows a stronger favourable association to build up between a male-beneficial allele, and a neo-Y chromosome, for example. 
 Such associations can favour a new master sex-determining gene on a new chromosome \citep{vanDoorn:2007eu} and can also favour a transition between male and female heterogamety \citep[e.g., a ZW to XY transition,][]{vanDoorn:2010hu}.
-However, any sexually-antagonistic loci that are more closely linked to the ancestral sex-determination locus will develop similar, favourable associations and select against the spread of a new sex-determination system.
+However, any sexually-antagonistic loci that are more closely linked to the ancestral sex-determination locus will develop similar, favourable associations and hinder the spread of a new sex-determination system.
 %Here we extend these studies by explicitly calculating the the equilibrium allele frequencies of loci that are very tightly linked to the ancestral sex-determining region.
 
-The sex ratio is directly affected by the sex-determination system, and it has therefore been suggested that sex-ratio selection is a dominant force in the evolution of sex determination (e.g., \citealt{Bull:1983vi}, p66-67; \citealt{Beukeboom:2014vb}, Chapter 7).
+The sex ratio is directly affected by the sex-determination system, and it has therefore been suggested that sex-ratio selection is a dominant force in the evolution of sex determination (e.g., \citealt{Bull:1983vi}, p 66-67; \citealt{Beukeboom:2014vb}, Chapter 7).
 `Fisherian' sex-ratio selection favours a 1:1 zygotic sex ratio when assuming that males and females are equally costly to produce \citep{Fisher:1930wy,Charnov:1982wg}.
-This follows from the fact that, for an autosomal locus, half of the genetic material is inherited from a male, and half from a female \citep{West:2009we}. 
-Thus, if the population sex ratio is biased towards females, the average per-individual contribution of genetic material to the next generation from males is greater than the contribution from females (and vice versa for male-biased sex ratios).
-Therefore, a mutant that increases investment in males (e.g., increases the proportion of males produced) will spread via the higher per-individual contributions made by males. 
+This follows from the fact that, for an autosomal locus, half of the genetic material is inherited from a male and half from a female \citep{West:2009we}. 
+Thus, if the population sex ratio is biased towards one sex, the average per-individual contribution of genetic material to the next generation from the opposite sex is greater. 
+Therefore, a mutant that increases investment in the rarer sex will spread via the higher per-individual contributions made by that sex. 
 %The default mode of sex-ratio selection is `Fisherian' sex-ratio selection, which favours equal investment in male and female offspring \citep[i.e., a 1:1 zygotic sex ratio when assuming that males and females are equally costly to produce,][]{Fisher:1930wy,Charnov:1982wg}.
@@
 by using mathematical models to find the conditions under which new sex-determination systems spread when individuals experience selection at both diploid and haploid stages. 
-Haploid genotypes at many loci experience selection during gamete competition and/or meiotic drive \citep{Mulcahy:1996ha,JOSEPH:2004haa}.
-We use the term `meiotic drive' to refer to the biased (non-Mendelian) segregation of genotypes during gamete production (from one parent) and the term `gametic competition' to refer to selection upon haploid genotypes within a gamete/gametophyte pool (potentially from by multiple parents); the term `haploid selection' encompasses both processes.
+Even in animal and plant species that have much larger and more conspicuous diploid phases than haploid phases, many loci experience significant haploid selection through gamete competition and/or meiotic drive \citep{Mulcahy:1996ha,JOSEPH:2004haa}.
+We use the term `meiotic drive' to refer to the biased (non-Mendelian) segregation of genotypes during gamete production (from one parent) and the term `gametic competition' to refer to selection upon haploid genotypes within a gamete/gametophyte pool (potentially from multiple parents); the term `haploid selection' encompasses both processes.
 Meiotic drive generally occurs either during the production of male or female gametes only \citep{Ubeda:2005gw,Lindholm:2016cw}.
@@
 Gametic competition may be particularly common in plants, in which 60-70\% of all genes are expressed in the male gametophyte and these genes exhibit stronger signatures of selection than random genes \citep{Borg:2009jpa,Arunkumar:2013iq,Gossmann:2014dua}.
-In addition, artificial selection pressures applied to male gametophytes are known to cause a response to selection \citep[e.g.,][]{Hormaza:1996cv,Ravikumar:2003uo,Hedhly:2004iv,Clarke:2004ir} and gametic selection appears to occur during the creation of F2 crosses \textcolor{red}{(Kumar, 2007)}.
-A much smaller proportion of genes are thought to be expressed and selected during competition in animal sperm, although precise estimates are uncertain \citep{Zheng:2001fi,JOSEPH:2004haa,Vibranovski:2010et,Immler:2014im}.
+In addition, artificial selection pressures applied to male gametophytes are known to cause a response to selection \citep[e.g.,][]{Hormaza:1996cv,Ravikumar:2003uo,Hedhly:2004iv,Clarke:2004ir}. 
+A smaller proportion of genes are thought to be expressed and selected during competition in animal sperm, although precise estimates are uncertain \citep{Zheng:2001fi,JOSEPH:2004haa,Vibranovski:2010et}.
+Recent studies have demonstrated that sperm competition can alter haploid allele frequencies and increase offspring fitness \citep{Immler:2014im} \textcolor{red}{(Alavioon et al. 2017). 
+Genetic mapping experiments, which are typically designed to minimize selection in diploids, have revealed segregation distortion in various species, including mice, Drosophila, Rice, Maize, Wheat, Barley, Cotton...
+In some of these cases, biased segregation has been shown to be attributable to meiotic drive and/or gametic selection \textcolor{red}{(Leppala et al.
+2013, Didion et al.
+2015, 2016 Xu et al 2013 (rice), Fishman...)}.
+}
+% from Bai et al.
+(2016) ``[Segregation distortion] phenomenon is commonly detected via genetic mapping and has been documented in various species, including mouse (Eversley et al., 2010; Casellas et al., 2012), Drosophila (Phadnis and Orr, 2009; Larracuente and Presgraves, 2012; McDermott and Noor, 2012), Tigriopus (Pritchard et al., 2011), rice (Koide et al., 2012; Reflinur et al., 2014; Xu et al., 2014), maize (Tang et al., 2013), and cotton (Yu et al., 2011; Hulse-Kemp et al., 2015).'' Also more in that paper that might be useful.
+%Drosophila http://www.biorxiv.org/content/early/2017/02/06/106336
 
@@
 If we assume that haploid selection at any particular locus predominantly occurs in one sex (e.g., meiotic drive during spermatogenesis), then such loci experience a form of sex-specific selection. 
-In this respect, we might expect that haploid selection to affect transitions between sex-determination systems in a similar manner to sex-specific diploid selection \citep[as explored by][]{vanDoorn:2007eu,vanDoorn:2010hu}.
+In this respect, we might expect that haploid selection would affect transitions between sex-determination systems in a similar manner to sex-specific diploid selection \citep[as explored by][]{vanDoorn:2007eu,vanDoorn:2010hu}.
 That is, new masculinizing mutations (neo-Y chromosomes) could be favoured via associations with alleles that are beneficial in the male haploid stage. 
@@
 Secondly, we allow sex-specific haploid selection to occur on a locus in tight or loose linkage with the ancestral sex-determining region. 
-We find that sex-ratio biases caused by haploid selection can exert Fisherian sex-ratio selection upon novel sex-determiners but that their spread is also determined by the fitness of the alleles that are associated with them.
-Indeed, it is only when haploid-selected loci are tightly linked to the ancestral sex-determining region (and so sex-ratio biases are initially large) that we see an asymmetry between selection for XY to ZW transitions and ZW to XY transitions (e.g., because haploid selection in males only causes biased zygotic sex ratios in an ancestrally XY system).
-It is also possible for selection on linked alleles to drive turnover between sex-determining systems despite causing transitory or even permanent increases in sex-ratio bias. 
+We find that sex-ratio biases caused by haploid selection can exert Fisherian sex-ratio selection upon novel sex-determiners but that their spread is also determined by selection on genetically-associated alleles.
+%Indeed, it is only when haploid-selected loci are tightly linked to the ancestral sex-determining region (and so sex-ratio biases are initially large) that we see an asymmetry between selection for XY to ZW transitions and ZW to XY transitions (e.g., because haploid selection in males only causes biased zygotic sex ratios in an ancestrally XY system).
+Consequently, it is possible for selection on linked alleles to drive turnover between sex-determining systems despite causing transitory or even permanent increases in sex-ratio bias. 
 %In addition, when linkage between the ancestral sex-determining locus and a locus under haploid selection is tight, sex ratio biases can be strong such that there is an asymmetry between invasion of ancestrally XY and ancestrally ZW systems because, e.g., haploid selection in males only causes biased zygotic sex ratios in an ancestrally XY system.
@@
 
+\textcolor{red}{Change all  $\alpha^\Hermaphrodite$ to $(1+\alpha_{\Delta}^\Hermaphrodite)$.}
+
 %genetic system
-We consider transitions between ancestral and novel sex-determining systems using a three locus model, each locus having two alleles. 
+We consider transitions between ancestral and novel sex-determining systems using a three-locus model, each locus having two alleles. 
 Locus \textbf{X} is the ancestral sex-determining region, with alleles $X$ and $Y$ (or $Z$ and $W$).
@@
 With $k=0$, the $m$ allele is a masculinizer (i.e., a neo-Y) and with $k=1$ the $m$ allele is a feminizer (i.e., a neo-W).
-With intermediate $k$, we can interpret $m$ as an environmental sex determination (ESD) allele, such that zygotes develop as females in a proportion ($k$) of the environments they (randomly) experience.
+With intermediate $k$, we can interpret $m$ as an environmental sex determination (ESD) allele, such that zygotes develop as females in a proportion ($k$) of the environments they experience. 
 We also analyze a model of maternally-controlled environmental sex-determination, where mothers with at least one $m$ allele produce daughters with probability $k$.
@@
 %$w_{A}^\male$ and $w_{a}^\male$ for male gametes and $w_{A}^\female$ and $w_{a}^\female$ for female gametes, see table \ref{tab:fitnesstable}.
-We assume that all gametes compete for fertilization during gametic competition, which is not the case for monogamous mating systems where gametes from only one mating partner are present. 
-Gametic competition in monogamous mating systems is equivalent to meiotic drive in our model (described below), which only alters the frequency of gametes produced by heterozygotes. 
+We assume that all gametes compete for fertilization during gametic competition, which assumes a polygamous mating system. 
+Gametic competition in monogamous mating systems is, however, equivalent to meiotic drive in our model (described below), as both only alter the frequency of gametes produced by heterozygotes. 
 After gametic competition, random mating occurs between male and female gametes.
-The resulting zygotes develop as males or females, depending on their genotypes at the \textbf{X} and \textbf{M} loci (and the \textbf{M} genotype of their mother in the case of maternal control) as described above.
+The resulting zygotes develop as males or females, depending on their genotypes at the \textbf{X} and \textbf{M} loci. %(and the \textbf{M} genotype of their mother in the case of maternal control).
 Diploid males and females then experience selection, with relative fitnesses $w_{AA}^{\Hermaphrodite}$, $w_{Aa}^{\Hermaphrodite}$, and $w_{aa}^{\Hermaphrodite}$.
@@
   aa & $w_{aa}^\Hermaphrodite = 1$ \\ [0.5ex] \hline
-  Genotype & Tranmission during meiosis in $Aa$ heterozygotes \\ [0.5ex] \hline
+  Genotype & Transmission during meiosis in $Aa$ heterozygotes \\ [0.5ex] \hline
   A & $\alpha^\Hermaphrodite=1/2+\alpha_{\Delta}^{\Hermaphrodite}/2$ \\
@@
 
-The only asymmetry between males and females in our model is that, under the ancestral sex-determination system, males develop with genotype $XY$ (or $ZZ$) and females with genotype $XX$ (or $ZW$). 
-Therefore, the model outlined above describes both ancestrally-$XY$ and ancestrally-$ZW$ sex-determination systems if we relabel the two sexes as being ancestrally `heterogametic' or ancestrally `homogametic'.
+The model outlined above describes both ancestrally-$XY$ and ancestrally-$ZW$ sex-determination systems if we relabel the two sexes as being ancestrally `heterogametic' or ancestrally `homogametic'. 
 Without loss of generality, we primarily refer to the ancestrally heterogametic sex as male and the ancestrally homogametic sex as female.
-That is, we describe an ancestral XY sex-determination system but our model is just as easily applied to an ancestral ZW sex-determination system.
+That is, we describe an ancestral XY sex-determination system but our model is equally applicable to an ancestral ZW sex-determination system (relabelling the ancestrally-heterogametic sex as female and the ancestrally-homogametic sex as male).
 
@@
 The evolution of a new sex-determination system requires that a rare mutant allele at the novel sex-determining locus, $m$, increases in frequency when rare. 
-The spread of a rare mutant $m$ at the \textbf{M} locus is determined by the leading eigenvalue, $\lambda$, of the system of eight equations describing the next generation frequency of eggs and sperm carrying the mutation, (\ref{eq:recursions}c, \ref{eq:recursions}d, \ref{eq:recursions}g, \ref{eq:recursions}h).
+The spread of a rare mutant $m$ at the \textbf{M} locus is determined by the leading eigenvalue, $\lambda$, of the system of eight equations describing the frequency of eggs and sperm carrying the $m$ allele in the next generation (equations \ref{eq:recursions}).
 %, evaluated at the above equilibrium.
@@
 This system simplifies substantially in a number of cases of interest. 
-Dominant neo-Y (when $k=0$) or neo-W alleles (when $k=1$) are only found in male diploids (neo-Y) or female diploids (neo-W) such that their growth rate ultimately depends only on the change in frequency of $m$-bearing gametes produced by males (for a neo-Y) or by females (for a neo-W).
+Dominant neo-Y (when $k=0$) or neo-W alleles (when $k=1$) are only found in male diploids (neo-Y) or female diploids (neo-W) such that their growth rate ultimately depends only on the change in frequency of $m$-bearing gametes produced by males or by females, respectively.
 Furthermore, if the $m$ allele is fully epistatically dominant over the ancestral sex-determining system, phenotypes are not affected by the genotype at the ancestral sex-determining region (\textbf{X} locus).
@@
 %Here, $b= - (\lambda_{mA} + \lambda_{ma})$ and $c = \lambda_{mA} \lambda_{ma} -\rho_{mA} \rho_{ma}$, where $\lambda_{mi}$ is the (multiplicative) growth rate of mutant haplotypes on background $i\in\{A,a\}$, accounting for loss due to recombination, and $\rho_{mi}$ is the rate of addition of mutant haplotypes onto background $i\in\{A,a\}$ due to recombination (see table \ref{tab:haplotype_growth}).
-Here, $b= - (\lambda_{mA} + \lambda_{ma})+(\rho_{mA} + \rho_{ma})$ and $c = (\lambda_{mA}-\rho_{mA}) (\lambda_{ma}-\rho_{ma}) -\rho_{mA} \rho_{ma}$, where $\lambda_{mi}$ is the multiplicative growth rate of mutant haplotypes on background $i\in\{A,a\}$, without accounting for loss due to recombination, and $\rho_{mi}$ is the rate at which mutant haplotypes on background $i\in\{A,a\}$ recombine onto the other \textbf{A} locus background in heterozygotes (see table \ref{tab:haplotype_growth}).
-The $\lambda_{mi}$ and $\rho_{mi}$, and thus the spread of the mutant $m$ allele, depend on the frequency of alleles at the other two loci in the ancestral population. 
-In the ancestral population, it is convenient to follow the frequency of the $A$ allele in female gametes (eggs) from an XX female, $p^\female_X$, and in X-bearing, $p^\male_X$, and Y-bearing, $p^\male_Y$, male gametes (sperm/pollem).
+Here, $b= - (\lambda_{mA} + \lambda_{ma})+(\rho_{mA} + \rho_{ma})$ and $c = (\lambda_{mA}-\rho_{mA}) (\lambda_{ma}-\rho_{ma}) -\rho_{mA} \rho_{ma}$, where $\lambda_{mi}$ is the multiplicative growth rate of mutant haplotypes on background $i\in\{A,a\}$, without accounting for loss due to recombination, and $\rho_{mi}$ is the rate at which mutant haplotypes on background $i\in\{A,a\}$ recombine onto the other \textbf{A} locus background in heterozygotes (see Table \ref{tab:haplotype_growth}).
+The $\lambda_{mi}$ and $\rho_{mi}$, and thus the spread of the mutant $m$ allele, depend on the frequency of alleles at the \textbf{A} and \textbf{X} loci in the ancestral population. 
+In the ancestral population, it is convenient to follow the frequency of the $A$ allele among female gametes (eggs), $p^\female_X$, and among X-bearing, $p^\male_X$, and among Y-bearing, $p^\male_Y$, male gametes (sperm/pollen).
 We also track the fraction of male gametes that are Y-bearing, $q$, which may deviate from $1/2$ due to meiotic drive in males.
@@
    neo-Y ($k=0$) \\ [0.5ex] \hline \noalign{\vskip 1ex}
-  $\lambda_{mA} = \left[ 2 (1- \zeta) \right]^{-1} \left[p_{X}^{\female} w_{A}^{\female} w_{A}^{\male} w_{AA}^{\male} + 2(1-p_{X}^{\female}) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} \alpha^\male \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right) $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\lambda_{ma} = \left[ 2 (1- \zeta) \right]^{-1} \left[(1-p_{X}^{\female}) w_{a}^{\female} w_{a}^{\male} w_{aa}^{\male} + 2p_{X}^{\female} w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male}(1 - \alpha^\male) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\rho_{mA} = R \left[ 2 (1- \zeta) \right]^{-1} \left[ 2(1-p_{X}^{\female}) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} \alpha^{\male} \right]/  \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right)   $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\rho_{ma} = R \left[ 2 (1- \zeta) \right]^{-1} \left[  2 p_{X}^{\female} w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male} (1 - \alpha^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right)  $\\ [1ex] \hline
+  $\lambda_{mA} = \left\{ 2 (1- \zeta) \right\}^{-1} \left[p_{X}^{\female} w_{A}^{\female} w_{A}^{\male} w_{AA}^{\male} + 2(1-p_{X}^{\female}) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} \alpha^\male \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right) $\\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\lambda_{ma} = \left\{ 2 (1- \zeta) \right\}^{-1} \left[(1-p_{X}^{\female}) w_{a}^{\female} w_{a}^{\male} w_{aa}^{\male} + 2p_{X}^{\female} w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male}(1 - \alpha^\male) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\rho_{mA} = R \left\{ 2 (1- \zeta) \right\}^{-1} \left[ 2(1-p_{X}^{\female}) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} \alpha^{\male} \right]/  \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right)   $\\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\rho_{ma} = R \left\{ 2 (1- \zeta) \right\}^{-1} \left[  2 p_{X}^{\female} w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male} (1 - \alpha^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right)  $\\ [1ex] \hline
   \noalign{\vskip 0.5ex}
@@
       \scriptsize
-      \item $\bar{p}^{\male}=p_{Y}^{\male}q+p_{X}^{\male}(1-q)$ is the average frequency of the $A$ allele among X- and Y-bearing male gametes.
-      \item $R$ is the probability of recombination between loci \textbf{A} and \textbf{M}.
+      \item $\bar{p}^{\male}=(1-q)p_{X}^{\male} + qp_{Y}^{\male}$ is the average frequency of the $A$ allele among X- and Y-bearing male gametes.
+%      \item $R$ is the probability of recombination between loci \textbf{A} and \textbf{M}.
       \item $\zeta$ is the zygotic sex ratio (fraction female)
@@
 \noindent For example, if we assume that only the $mA$ haplotype has a positive growth rate ($\lambda_{ma}<1<\lambda_{mA}$), the second term on the left-hand side of \eqref{eq:lambdasGen} is negative and invasion requires that the growth rate of $mA$ haplotypes and the rate at which they are produced by recombination is sufficiently large relative to that of $ma$ haplotypes.
-In other words, invasion requires that the average growth rate of recombinants, weighted by the rates they are created, is positive.
+In other words, invasion requires that the average growth rate of the two haplotypes, weighted by the rates they are created by recombination, is positive.
 %the number of recombinants from the fitter $mA$ haplotypes is larger than that of the less fit $ma$ haplotypes, relative to their growth rates.
@@
 Table \ref{tab:haplotype_growth} illustrates a number of key points about the invasion of neo-Y and neo-W mutations. 
-First, Fisherian sex-ratio selection will favour the spread of a neo-Y if the ancestral zygotic sex ratio is biased towards females, $\zeta>1/2$, and vice versa for a neo-W (i.e., $\zeta>1/2$ causes the first factor of the $\lambda_{mi}$ to be greater than one for a neo-Y).
-However, the spread of a neo-Y (neo-W) also depends on the male (female) fitness of alleles that they are associated with. %, see terms in curly brackets. 
-Second, invasion by a neo-Y (neo-W) allele does not directly depend on the fitness of female (male) diploids (although they indirectly affect invasion by determining the allele frequencies $p^\female_X$ and $\hat{p}^\male$).
+First, Fisherian sex-ratio selection will favour the spread of a neo-Y if the ancestral zygotic sex ratio is biased towards females, $\zeta>1/2$ (i.e., $\zeta>1/2$ causes the first factor of the $\lambda_{mi}$ to be greater than one for a neo-Y and vice versa for a neo-W).
+However, the spread of a neo-Y (neo-W) also depends on the male (female) fitness of associated alleles (terms in square brackets). %, see terms in curly brackets. 
+Second, invasion by a neo-Y (neo-W) allele does not directly depend on the fitness of female (male) diploids (for a given set of equilibrium allele frequencies).
 %involve any female (male) diploid selection terms ($w_{g}^{\female}$)
@@
 Finally, invasions by a neo-Y and a neo-W are qualitatively different.
-This is because a gamete containing a neo-Y always pairs with the same gamete type as a male gamete without the neo-Y does (both pair with a female gamete containing an X), and both develop into males.
-Meanwhile a gamete with a neo-W can pair with an X or Y male gamete, and develop into a female, while female gametes without the neo-W must pair with a male gamete containing an X to remain female.
-This is consequential because it means that females with and without a neo-W differ in the frequency of $A$ alleles they obtain from mating.
+This is because a gamete with the ancestral- or neo-Y always pairs with a female gamete containing an X, and both develop into males.
+By contrast, a gamete with a neo-W can pair with an X or Y male gamete, developing into a female, while female gametes without the neo-W can become female (when paired with X) or male (when paired with Y).
+Consequently, the types of females produced differ in the frequency of $A$ alleles they obtain from mating.
 %\textcolor{blue}{nice}
@@
 
-In order to explicitly determine the conditions under which a rare neo-sex-determining allele spreads, we must calculate the frequency of the $A$ allele in the ancestral population (i.e., $p^\female_X$, $p^\male_X$, and $p^\male_Y$).
+In order to explicitly determine the conditions under which a rare neo-sex-determining allele spreads, we must calculate the equilibrium frequency of the $A$ allele in the ancestral population (i.e., $\hat{p}^\female_X$, $\hat{p}^\male_X$, and $\hat{p}^\male_Y$).
 Since only the \textbf{A} locus experiences selection directly, any deterministic evolution requires that there is a polymorphism at the \textbf{A} locus. 
-Polymorphisms can be transiently present during the spread of uniformly beneficial alleles but polymorphisms maintained by selection can maintain alleles at higher allele frequencies for longer periods, during which time new sex-determining alleles can arise.
-Therefore, we will assume that the $A$ allele reaches a stable intermediate equilibrium frequency under the ancestral sex-determination system before the neo-sex-determining allele ($m$) arises. 
+Polymorphisms can be maintained by mutation-selection balance or transiently present during the spread of beneficial alleles.
+However, polymorphisms maintained by selection can maintain alleles at higher allele frequencies for longer periods.
+Here, we focus of polymorphisms maintained by selection, where the $A$ allele reaches a stable intermediate equilibrium frequency under the ancestral sex-determination system before the neo-sex-determining allele ($m$) arises.
 We can analytically calculate the allele frequency of the $A$ allele using two alternative simplifying assumptions: 
@@
 
+\textcolor{red}{Change to $\hat{p}$ throughout as we assume that allele frequencies change slowly such that lambda is unaffected}
+
 \subsubsection*{Tight linkage with the ancestral sex-determining region}
 
-When there is perfect linkage between the ancestral sex-determining region and the \textbf{A} locus ($r=0$), either the $A$ allele or the $a$ allele must be fixed on the Y. 
+The equilibrium allele frequencies and their stability conditions are given in the appendix, when there is complete linkage between the ancestral sex-determining region and the \textbf{A} locus ($r=0$).
+Here, either the $A$ allele or the $a$ allele must be fixed on the Y.
 % because selection on the Y is effectively haploid an incapably of maintaining a polymorphism in the absence of frequency dependent selection. 
@@
 If there are two alleles maintained at the \textbf{A} locus, the X can either be fixed for the $A$ allele ($p^\female_X=p^\male_X=1$) or polymorphic (0<$p^\female_X, p^\male_X$<1). 
-These equilibrium allele frequencies and their stability conditions are given in the appendix.
 %However, because the X is present in both males and females, there are distinct selection pressures on X's in females and X's in males, which will always be paired with an $A$ allele from the Y.
 
-A neo-Y will never invade an ancestral XY system that already has tight linkage with the locus under selection ($r=0$). 
+A neo-Y will never invade an ancestral XY system that already has tight linkage with the locus under selection ($r=0$, for details see supplementary \textit{Mathematica} file). 
 %When then neo-Y is also tightly linked ($R=0$) a neo-Y will either remain linked to the $A$ allele or to the $a$ allele and so invasion is given directly by the larger of $\lambda_{mA}$ or $\lambda_{ma}$.
@@
 Attempt 1:}
+
+\textcolor{red}{Sally edits only looked at up to this point. Next task: figures to match with this tight linkage section.}
 

### 2017-08-02 LaTeX/Turnover.tex
position figure updated

@@
 %	\node[] () {\includegraphics[width=\linewidth]{PositionPlot}};
-	\node[] () {\includegraphics[width=\linewidth]{PositionPlot_2}};
-	\node[anchor=east] at (0, 1.5) {\footnotesize diploid sex-antagonism}; %, $s^\male s^\female < 0$};
-	\node[anchor=east] at (6.5, 1.5) {\footnotesize haploid sex-antagonism}; %, $s^\male s^\female > 0$};
-	\node[anchor=east] at (0, -3) {\footnotesize male drive (ploidy-antagonism)}; %, $s^\male < s^\female$};
-%	\node[anchor=east] at (6.5, -3) {\footnotesize pollen competition (ploidy-antagonism)};%, $s^\female < s^\female$};
-	\node[anchor=center] at (-1.3, 4.25) {\scriptsize tighter sex-linkage};
-	\node[anchor=center] at (2.45, 3.5) {\scriptsize ancestral SDR};
-	\draw[->,thick] (2.45, 3.25) -- (2.45, 2.5);
-	\node[anchor=center] at (-1.4, -0.25) {\scriptsize novel SDR};
-	\draw[->,thick] (-1.4, -0.5) -- (-1.4, -1);
+	\node[] () {\includegraphics[width=0.5\linewidth]{PositionPlot_2}};
+%	\node[anchor=east] at (0, 1.5) {\footnotesize diploid sex-antagonism}; %, $s^\male s^\female < 0$};
+%	\node[anchor=east] at (6.5, 1.5) {\footnotesize haploid sex-antagonism}; %, $s^\male s^\female > 0$};
+%	\node[anchor=east] at (0, -3) {\footnotesize male drive (ploidy-antagonism)}; %, $s^\male < s^\female$};
+%	\node[anchor=east] at (6.5, -3) {\footnotesize find something interesting to plot};%, $s^\female < s^\female$};
+%	\node[anchor=center] at (-1.3, 4.25) {\scriptsize tighter sex-linkage};
+%	\node[anchor=center] at (2.45, 3.5) {\scriptsize ancestral SDR};
+%	\draw[->,thick] (2.45, 3.25) -- (2.45, 2.5);
+%	\node[anchor=center] at (-1.4, -0.25) {\scriptsize novel SDR};
+%	\draw[->,thick] (-1.4, -0.5) -- (-1.4, -1);
 \end{tikzpicture}
 \caption{
-Invasion fitness of a neo-sex-determining allele plotted against the relative genomic location of a locus under direct selection, \textbf{A}, for various selective regimes. 
-The ancestral sex-determining locus is located at -25 and the novel sex-determining locus is located at 25. %and that there is a polymorphism at the \textbf{A} locus maintained by selection.
-We use Haldane's map function \citep[Equation 3 in ][]{Haldane1919} to convert from map distance (centiMorgans) to the probability of a cross-over event. 
-In A, there is no haploid selection ($t^\Hermaphrodite=\alpha^\Hermaphrodite_{\Delta}=0$) and selection in diploids is sexually antagonistic \citep[following][]{vanDoorn:2010hu}, in which case a neo-W can only invade if it is more closely linked to the selected locus ($s^\female=1/10$, $h^\female=7/10$ $s^\male=-1/10$, $h^\male=3/10$).
-In B-D we include haploid selection. %and assume that selection in diploids is not sexually-antagonistic ($s^\female s^\male>0$). 
+Invasion fitness of a neo-sex-determining allele plotted against the relative genomic location of a locus under direct selection for various selective regimes. 
+% (neo-Y invading ZW in black, neo-W invading XY in red)
+%The ancestral sex-determining locus is located at -25 and the novel sex-determining locus is located at 25. %and that there is a polymorphism at the \textbf{A} locus maintained by selection.
+%Thus, if the neo-sex-determining allele invades in the gray region the system evolves tighter sex-linkage.  
+We use Haldane's map function \citep[Equation 3 in ][]{Haldane1919} to convert from map distance (centiMorgans, cM) to the probability of a cross-over event. 
+In panel A, there is no haploid selection ($t^\Hermaphrodite=\alpha^\Hermaphrodite_{\Delta}=0$) and selection in diploids is sexually antagonistic ($s^\male=-s^\female=1/10$, $h^\male=1-h^\female=3/10$), in which case the neo-sex-determining allele can only invade if it is more closely linked to the selected locus ($R<r$; gray region).
+In panel B, there is no diploid selection ($s^\Hermaphrodite=0$) and selection in haploids is sexually antagonistic ($t^\male=-t^\female=0.08$, $\alpha^\Hermaphrodite_{\Delta}=0$), in which case the neo-sex-determining allele can invade regardless of linkage.
+In panel C, selection in diploids ($s^\male=s^\female=1/10$, $h^\male=h^\female=7/10$) opposes drive in males ($\alpha^\male_{\Delta}=-0.05$, $t^\Hermaphrodite=\alpha^\female_{\Delta}=0$), in which case the neo-sex-determining allele can once again invade regardless of linkage.
+%we include haploid selection. %and assume that selection in diploids is not sexually-antagonistic ($s^\female s^\male>0$). 
 %A polymorphism can then be maintained by opposing selection between the haploid and diploid phases. 
@@
 %In this case, the neo-W does not invade if $s^\female>s^\male$ (panel C: $s^\female=3/20$, $s^\male=1/20$) but does if $s^\female<s^\male$ (panel D: $s^\female=1/20$, $s^\male=3/20$), see Table \ref{tab:specialcases}.\\
-In B
 %\textcolor{red}{

### 2017-08-03 LaTeX/Turnover.tex
plotting

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
+%\begin{figure}[!h]
+%\centering
 \begin{tikzpicture}[remember picture]
@@
 \end{tikzpicture}
-\caption{
-Heterogametic transitions from XY to ZW sex determination (neo-W frequency shown by black lines, panels A and B) or from ZW to XY (neo-Y frequency shown by black lines, panels C and D) occur similarly regardless of sex ratio biases present before (B versus D) or after (C versus A, dashed lines show male frequency).
-During invasion by a neo-ZW sex-determination system (A and B), the ancestral Y fixes in both males and females (blue and red lines). 
-Similarly, the ancestral W allele fixes in males and females (blue and red lines) during a ZW to XY transition. 
-In this plot, there is no gametic competition ($t^\female=t^\male=0$) and meiotic drive occurs during male meiosis only ($\alpha^\female_{\Delta}=0$, $\alpha^\male_{\Delta}=-1/5$).
+%\caption{
+%Heterogametic transitions from XY to ZW sex determination (neo-W frequency shown by black lines, panels A and B) or from ZW to XY (neo-Y frequency shown by black lines, panels C and D) occur similarly regardless of sex ratio biases present before (B versus D) or after (C versus A, dashed lines show male frequency).
+%During invasion by a neo-ZW sex-determination system (A and B), the ancestral Y fixes in both males and females (blue and red lines). 
+%Similarly, the ancestral W allele fixes in males and females (blue and red lines) during a ZW to XY transition. 
+%In this plot, there is no gametic competition ($t^\female=t^\male=0$) and meiotic drive occurs during male meiosis only ($\alpha^\female_{\Delta}=0$, $\alpha^\male_{\Delta}=-1/5$).
 Therefore, sex ratio biases can only arise when the \textbf{A} locus is linked to an XY sex-determining locus.
-In panels A and C, the neo-sex-determining locus is more closely linked to the \textbf{A} locus than the ancestral sex-detemining region ($r=1/2$, $R=1/20$) such that a neo-Y can caused biased sex ratios (panel C).
-In panels B and D, the ancestral sex-determining locus is more closely linked to the \textbf{A} locus than the neo-sex-detemining locus ($r=1/20$, $R=1/2$). 
-Therefore, an ancestral XY sex determination can have a biased zygotic sex ratio that becomes unbiased after an unlinked neo-W invades (B). 
-However, in panel D, a unlinked neo-Y invades an ancestral ZW sex-determination system in a similar manner but no biases to the zygotic sex ratio occur. 
-With diploid selection alone, neo-sex-determining loci do not spread if they are less closely linked to the \textbf{A} locus than the ancestral sex-determining locus (see equation \eqref{eq:lambda_neoW} and Figure \ref{fig:Combination_Centimorgans}A).
-In this plot there are no sex differences in selection and an equilibrium is maintained because selection in diploids opposes meiotic drive, $s^\female =s^\male = 1/5$, $h^\female = h^\male = 7/10$.
-\textcolor{red}{Aesthetic adjustments: 
-%Could add titles to the columns/rows: neo-W for row 1, neo-Y for row 3, $r=0.5$, $R=0.05$ for column 1 and $r=0.05$, $R=0.5$ for column 2. 
-%Could adjust padding (too much whitespace where there is no axis label). 
-%It also seems could increase ratio of font size relative to plot size to make figure more compact. 
-%Matt - could you uncomment the line legends in the Mathematica file (function not included in my Mathematica version).
-Add chromosome cartoons to depict recombination rates?
-}
-}
-\label{fig:Combination_Turnover}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
+%In panels A and C, the neo-sex-determining locus is more closely linked to the \textbf{A} locus than the ancestral sex-detemining region ($r=1/2$, $R=1/20$) such that a neo-Y can caused biased sex ratios (panel C).
+%In panels B and D, the ancestral sex-determining locus is more closely linked to the \textbf{A} locus than the neo-sex-detemining locus ($r=1/20$, $R=1/2$). 
+%Therefore, an ancestral XY sex determination can have a biased zygotic sex ratio that becomes unbiased after an unlinked neo-W invades (B). 
+%However, in panel D, a unlinked neo-Y invades an ancestral ZW sex-determination system in a similar manner but no biases to the zygotic sex ratio occur. 
+%With diploid selection alone, neo-sex-determining loci do not spread if they are less closely linked to the \textbf{A} locus than the ancestral sex-determining locus (see equation \eqref{eq:lambda_neoW} and Figure \ref{fig:Combination_Centimorgans}A).
+%In this plot there are no sex differences in selection and an equilibrium is maintained because selection in diploids opposes meiotic drive, $s^\female =s^\male = 1/5$, $h^\female = h^\male = 7/10$.
+%\textcolor{red}{Aesthetic adjustments: 
+%%Could add titles to the columns/rows: neo-W for row 1, neo-Y for row 3, $r=0.5$, $R=0.05$ for column 1 and $r=0.05$, $R=0.5$ for column 2. 
+%%Could adjust padding (too much whitespace where there is no axis label). 
+%%It also seems could increase ratio of font size relative to plot size to make figure more compact. 
+%%Matt - could you uncomment the line legends in the Mathematica file (function not included in my Mathematica version).
+%Add chromosome cartoons to depict recombination rates?
+%}
+%}
+%\label{fig:Combination_Turnover}
+%\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\newpage
 
@@
 \caption{
-\textcolor{red}{Is this what Sally was thinking?}
-\textcolor{blue}{I think this works but I'm confused as to why the speed of spread should be so much different for XY and ZW here.
+%\textcolor{red}{Is this what Sally was thinking?}
+%\textcolor{blue}{I think this works but I'm confused as to why the speed of spread should be so much different for XY and ZW here.
 Figure \ref{fig:Combination_Turnover} and \ref{fig:Combination_Centimorgans} suggests that there's not much difference between XY->ZW and ZW->XY.
@@
 }
-\textcolor{red}{i messed up and had $r=0.5$ instead of $r=0.05$ for B and D. haven't fixed fitness plot below.}
+%\textcolor{red}{i messed up and had $r=0.5$ instead of $r=0.05$ for B and D. haven't fixed fitness plot below.}
+Heterogametic transitions occur (panels A and B) regardless of sex ratio biases (panels C and D).
+A neo-W invades (panel A) and equalizes the male-biased sex ratio (panel C) that was caused by meiotic drive in males.
+A neo-Y invades (panel B) a population with an equal sex ratio. 
+With any amount of linkage ($R<1/2$), the neo-Y becomes associated with the driving allele in males, and in the end causes a male bias.
+Parameters: $s^\female = s^\male = 1/5$, $h^\female = h^\male = 7/10$, $t^\female = t^\male=0$, $\alpha^\female_\Delta = 0$, $\alpha^\male_\Delta = -1/5$, $r = 1/20$.
 }
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%Changes in mean fitness
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\begin{figure}[!h]
+%\centering
+%\begin{tikzpicture}[remember picture]
+%	\node[] (plot) {\includegraphics[width=\linewidth]{Combination_Fitness_Rec}};
+%	\node[above = -1cm of plot, xshift = -100] () {XY $\rightarrow$ ZW};
+%	\node[above = -1cm of plot, xshift = 90] () {ZW $\rightarrow$ XY};
+%\end{tikzpicture}
+%\caption{
+%\textcolor{red}{This complicated thing matches the plot above. I don't think we want to include it...?}
+%}
+%\label{fig:Combination_Fitness_Rec}
+%\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\newpage
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-\begin{tikzpicture}[remember picture]
-	\node[] (plot) {\includegraphics[width=\linewidth]{Combination_Fitness_Rec}};
-	\node[above = -1cm of plot, xshift = -100] () {XY $\rightarrow$ ZW};
-	\node[above = -1cm of plot, xshift = 90] () {ZW $\rightarrow$ XY};
-\end{tikzpicture}
-\caption{
-\textcolor{red}{This complicated thing matches the plot above. I don't think we want to include it...?}
-}
-\label{fig:Combination_Fitness_Rec}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Changes in mean fitness
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-\begin{tikzpicture}[remember picture]
-	\node[] (plot) {\includegraphics[width=\linewidth]{Combination_MeanFit}};
-	\node[above = 0cm of plot, xshift = -70] () {$r=0.5$, $R=0.05$};
-	\node[above = 0cm of plot, xshift = 120] () {$r=0.05$, $R=0.5$};
-	\node[left = 0cm of plot, yshift = 105, rotate = 90] () {XY $\rightarrow$ ZW};
-	\node[left = 0cm of plot, yshift = -20, rotate = 90] () {ZW $\rightarrow$ XY};
-\end{tikzpicture}
-\caption{
-Changes in mean diploid fitness of males (blue lines), females (red lines), and the entire population (black lines) during the transitions between sex-determination systems shown in Figure \ref{fig:Combination_Turnover}.
-Here mean diploid fitness of a particular sex is its mean diploid viability fitness times twice its frequency in the population, to capture the fact that epistatically dominant sex-determining alleles can also invade because they selfishly make more of the sex they are in.
-The mean fitness of females increases during the spread of neo-W alleles (A and B) and the mean fitness of males increases during the spread of neo-Y alleles (C and D). 
-However, when a neo-sex determining system evolves that is less closely linked to a locus under selection (B and D), population mean fitness decreases. 
-%\textcolor{red}{
-%Could add titles to the columns/rows: neo-W for row 1, neo-Y for row 3, $r=0.5$, $R=0.05$ for column 1 and $r=0.05$, $R=0.5$ for column 2. 
-%%\& possibly adjust padding (too much whitespace?). 
-%%Matt - could you uncomment the line legends in the Mathematica file (function not included in my Mathematica version).
-%}
-%\textcolor{red}{I'm still confused why male and female mean fitnesses aren't normalized by their frequency.
+%\begin{figure}[!h]
+%\centering
+%\begin{tikzpicture}[remember picture]
+%	\node[] (plot) {\includegraphics[width=\linewidth]{Combination_MeanFit}};
+%	\node[above = 0cm of plot, xshift = -70] () {$r=0.5$, $R=0.05$};
+%	\node[above = 0cm of plot, xshift = 120] () {$r=0.05$, $R=0.5$};
+%	\node[left = 0cm of plot, yshift = 105, rotate = 90] () {XY $\rightarrow$ ZW};
+%	\node[left = 0cm of plot, yshift = -20, rotate = 90] () {ZW $\rightarrow$ XY};
+%\end{tikzpicture}
+%\caption{
+%Changes in mean diploid fitness of males (blue lines), females (red lines), and the entire population (black lines) during the transitions between sex-determination systems shown in Figure \ref{fig:Combination_Turnover}.
+%Here mean diploid fitness of a particular sex is its mean diploid viability fitness times twice its frequency in the population, to capture the fact that epistatically dominant sex-determining alleles can also invade because they selfishly make more of the sex they are in.
+%The mean fitness of females increases during the spread of neo-W alleles (A and B) and the mean fitness of males increases during the spread of neo-Y alleles (C and D). 
+%However, when a neo-sex determining system evolves that is less closely linked to a locus under selection (B and D), population mean fitness decreases. 
+%%\textcolor{red}{
+%%Could add titles to the columns/rows: neo-W for row 1, neo-Y for row 3, $r=0.5$, $R=0.05$ for column 1 and $r=0.05$, $R=0.5$ for column 2. 
+%%%\& possibly adjust padding (too much whitespace?). 
+%%%Matt - could you uncomment the line legends in the Mathematica file (function not included in my Mathematica version).
+%%}
+%%\textcolor{red}{I'm still confused why male and female mean fitnesses aren't normalized by their frequency.
 I'm not sure we should be calling them means without this normalization step.
@@
 See the next figure for what happens when we do normalize.}
-\textcolor{blue}{I think we should give this plot showing (male mean fitness * freq males) and (female mean fitness * freq females), without multiplying by 2 (leave off black lines, population mean fitness).
-We could also re-plot the sex ratios on this same scale. 
-The plot below, `adjusted for sex ratio', could then go in the appendix. The point is that neo-W (neo-Y) can invade when the frequency of females (males) multiplied by their mean fitness increases.  }
+%\textcolor{blue}{I think we should give this plot showing (male mean fitness * freq males) and (female mean fitness * freq females), without multiplying by 2 (leave off black lines, population mean fitness).
+%We could also re-plot the sex ratios on this same scale. 
+%The plot below, `adjusted for sex ratio', could then go in the appendix.
+The point is that neo-W (neo-Y) can invade when the frequency of females (males) multiplied by their mean fitness increases.
 }
-\label{fig:Combination_MeanFit}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
+%}
+%\label{fig:Combination_MeanFit}
+%\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\newpage
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-\begin{tikzpicture}[remember picture]
-	\node[] (plot) {\includegraphics[width=\linewidth]{Combination_MeanFit_Corrected}};
-\end{tikzpicture}
-\caption{
-\textcolor{red}{Last plot with mean fitness of sexes corrected for sex ratio. Could add to previous plot with dashed lines?}
-}
-\label{fig:Combination_MeanFit_Corrected}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
+%\begin{figure}[!h]
+%\centering
+%\begin{tikzpicture}[remember picture]
+%	\node[] (plot) {\includegraphics[width=\linewidth]{Combination_MeanFit_Corrected}};
+%\end{tikzpicture}
+%\caption{
+%\textcolor{red}{Last plot with mean fitness of sexes corrected for sex ratio. Could add to previous plot with dashed lines?}
+%}
+%\label{fig:Combination_MeanFit_Corrected}
+%\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\newpage
 
@@
 \caption{
-Invasion fitness of a neo-sex-determining allele plotted against the relative genomic location of a locus under direct selection for various selective regimes. 
+Invasion fitness of a neo-sex-determining allele against the relative genomic location of a locus under direct selection. 
 % (neo-Y invading ZW in black, neo-W invading XY in red)
@@
 %Thus, if the neo-sex-determining allele invades in the gray region the system evolves tighter sex-linkage.  
-We use Haldane's map function \citep[Equation 3 in ][]{Haldane1919} to convert from map distance (centiMorgans, cM) to the probability of a cross-over event. 
 In panel A, there is no haploid selection ($t^\Hermaphrodite=\alpha^\Hermaphrodite_{\Delta}=0$) and selection in diploids is sexually antagonistic ($s^\male=-s^\female=1/10$, $h^\male=1-h^\female=3/10$), in which case the neo-sex-determining allele can only invade if it is more closely linked to the selected locus ($R<r$; gray region).
@@
 In panel C, selection in diploids ($s^\male=s^\female=1/10$, $h^\male=h^\female=7/10$) opposes drive in males ($\alpha^\male_{\Delta}=-0.05$, $t^\Hermaphrodite=\alpha^\female_{\Delta}=0$), in which case the neo-sex-determining allele can once again invade regardless of linkage.
+We use Haldane's map function \citep[Equation 3 in ][]{Haldane1919} to convert from map distance (centiMorgans, cM) to the probability of a cross-over event.    
 %we include haploid selection. %and assume that selection in diploids is not sexually-antagonistic ($s^\female s^\male>0$). 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
 

### 2017-08-04 LaTeX/Turnover.tex
ffiguring out what figures should go in main text

@@
 Take, for instance, selection directionally favouring $A$ in both diploid sexes and meiotic drive in males.
-Figure \ref{fig:regionplot_2a}B then shows that ploidally-antagonisitic selection can allow both neo-W haplotypes to invade. 
+Figure \ref{fig:regionplot_2a}B then shows that ploidally-antagonistic selection can allow both neo-W haplotypes to invade. 
 %}
@@
 The neo-sex-determining allele, $m$, will spread if $\lambda_{m,XY}>1$. 
-Equation \eqref{eq:lambda_neoY} demonstrates that under weak selection a neo-Y will invade if and only if it is more closely linked to the selected locus than the ancestral sex-determining region (i.e., if $R<r$; note that $V_{A}$ and $S_{A}^2$ are strictly positive as long as \textbf{A} is polymorphic).
-This echoes our tight linkage results above and the results of \citet{vanDoorn:2007eu}, who considered diploid selection only and also found that homogametic transitions (XY to XY or ZW to ZW) can occur when the neo-sex-determining locus is more closely linked to a locus under sexually-antagonistic selection.
+Equation \eqref{eq:lambda_neoY} demonstrates that under weak selection a neo-Y will invade an XY system if and only if it is more closely linked to the selected locus than the ancestral sex-determining region (i.e., if $R<r$; note that $V_{A}$ and $S_{A}^2$ are strictly positive as long as \textbf{A} is polymorphic).
+This echoes our tight linkage results above and the results of \citet{vanDoorn:2007eu}, who considered diploid selection only and also found that homogametic transitions (XY to XY or ZW to ZW) can only occur when the neo-sex-determining locus is more closely linked to a locus under sexually-antagonistic selection.
 %Because tighter linkage between the sex-determining region and a selected locus evolves during these transitions, stronger associations between selected alleles and diploid sexes can build up by selection (e.g., between male-beneficial alleles and the male-determining allele, Y).%, increasing diploid mean fitness (Figure \ref{fig:Combination_MeanFit}).
@@
 
-Equation \eqref{eq:lambda_neoW} shows that neo-W alleles can invade an XY system for a large number of selective regimes. 
+Equation \eqref{eq:lambda_neoW} shows that, with weak selection, neo-W alleles can invade an XY system for a large number of selective regimes. 
 To clarify the parameter space under which $\lambda_{W',XY}>1$, we consider several special cases. 
@@
 %\centering
-\begin{tikzpicture}[remember picture]
-	\node[] (plot) {\includegraphics[width=\linewidth]{Combination_Turnover}};
-	\node[above = 0cm of plot, xshift = -70] () {$r=0.5$, $R=0.05$};
-	\node[above = 0cm of plot, xshift = 120] () {$r=0.05$, $R=0.5$};
-	\node[left = 0cm of plot, yshift = 105, rotate = 90] () {XY $\rightarrow$ ZW};
-	\node[left = 0cm of plot, yshift = -20, rotate = 90] () {ZW $\rightarrow$ XY};
-\end{tikzpicture}
+%\begin{tikzpicture}[remember picture]
+%	\node[] (plot) {\includegraphics[width=\linewidth]{Combination_Turnover}};
+%	\node[above = 0cm of plot, xshift = -70] () {$r=0.5$, $R=0.05$};
+%	\node[above = 0cm of plot, xshift = 120] () {$r=0.05$, $R=0.5$};
+%	\node[left = 0cm of plot, yshift = 105, rotate = 90] () {XY $\rightarrow$ ZW};
+%	\node[left = 0cm of plot, yshift = -20, rotate = 90] () {ZW $\rightarrow$ XY};
+%\end{tikzpicture}
 %\caption{

### 2017-08-04 LaTeX/Turnover.tex
first draft of new figures done (without sally's type)

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Tighter linkage allows looser sex-linkage to evolve, even in absence of haploid selection
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[!h]
+\centering
+\includegraphics[width=\linewidth]{PositionPlot_SexAntagTighter}
+\caption{
+In the absence of haploid selection, tight linkage allows looser sex-linkage to evolve in transitions between XY and ZW systems.
+In panel A, linkage is loose enough relative to selection that the weak selection analytical results hold, and a neo-W can only invade when it is more tightly linked with the selected locus ($R<r$; shaded region).
+In panel B, linkage is tight enough relative to selection that the weak selection analytical results do no hold, and a neo-W can only invade even when it is less tightly linked with the selected locus ($r<R$; unshaded region).
+Parameters: $w_{AA}^\female = w_{aa}^\male = 1.05$, $w_{aa}^\female = w_{AA}^\male = 0.85$, $w_{Aa}^\female = 1$, $w_{Aa}^\male = 0.925$, $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
+}
+\label{fig:SexAntagTighter}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Both neo-W haplotypes can spread, in the absence of haploid selection, when there is overdominance
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[!h]
+\centering
+\includegraphics[width=0.45\linewidth]{regionplot_2a}
+\includegraphics[width=0.45\linewidth]{BothWsInvade_Overdominance}
+\caption{
+In the absence of haploid selection, both neo-W haplotypes can spread in an XY system when there is overdominance.
+Panel A shows the range of male homozygote fitnesses that allow both neo-W haplotypes to invade.
+Panel B shows the temporal dynamics of the invading neo-W haplotypes; in this case the neo-W does not fix, leading to a polymorphic sex-determining system.
+Asterisk in panel A marks parameter values ($w_{aa}^\male=0.15$, $w_{AA}^\male=0.1$) used in panel B.
+Parameters: $w_{AA}^\female = w_{aa}^\female = 0.6$, $w_{Aa}^\Hermaphrodite = 1$, $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$, $r=R=0$.
+}
+\label{fig:BothOverdominance}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%With weak selection, a less tightly linked neo-W can invade an XY system when there is some haploid selection, and this invasion decreases mean diploid fitness
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[!h]
+\centering
+\includegraphics[width=0.5\linewidth]{Loose_Fitness_Decline}
+\caption{
+With weak selection, a less tightly linked neo-W can invade (and fix in) an XY system (causing the Y to fix in females) when there is some haploid selection (blue and green curves in panel A), and this invasion decreases mean diploid fitness (green and blue curves in panel B).
+Parameters: $s^\Hermaphrodite = 0.2$, $h^\Hermaphrodite = 0.7$, $t^\Hermaphrodite = \alpha^\male_\Delta = 0$, $\alpha^\female_\Delta = -0.1$, $r=1/10$.
+}
+\label{fig:LooseDecline}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%A neo-W can invade an XY system under a large number of selective regimes
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[!h]
+\centering
+\includegraphics[width=0.5\linewidth]{PositionPlot_4}
+\caption{
+ A neo-W can invade an XY system under a large number of selective regimes.
+In panel A, there is no haploid selection ($t^\Hermaphrodite = \alpha^\Hermaphrodite_{\Delta} = 0$) and selection in diploids is sexually antagonistic ($s^\male = -s^\female = 1/10$, $h^\male = 1-h^\female = 3/10$), in which case the neo-sex-determining allele can only invade if it is more closely linked to the selected locus ($R<r$, gray region; but see Figure \ref{fig:SexAntagTighter}B for the case of very tight linkage).
+In panel B, male drive ($\alpha^\male_{\Delta} = -1/20$, $t^\Hermaphrodite = \alpha^\female_{\Delta} = 0$) opposes selection in diploids (no sex-differences: $s^\Hermaphrodite = 1/10$, $h^\Hermaphrodite = 7/10$), in which case the neo-sex-determining allele can invade regardless of linkage.
+In panel C, haploid competition in males ($t^\male = -1/10$, $t^\female = \alpha^\Hermaphrodite_{\Delta} = 0$) opposes selection in diploids (sex-differences: $s^\male = 3 s^\female = 3/20$, $h^\Hermaphrodite = 7/10$), in which case the neo-sex-determining allele can once again invade regardless of linkage.
+We use Haldane's map function \citep[Equation 3 in ][]{Haldane1919} to convert from map distance (centiMorgans, cM) to the probability of recombination (an odd number of cross-over events).   
+}
+\label{fig:Combination_Centimorgans}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Sex-ratio selection is not a good predictor of neo-W invasion into an XY system
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[!h]
+\centering
+\includegraphics[width=\linewidth]{Combination_Turnover_Ratio}
+\caption{
+Sex-ratio selection alone is not a good predictor of turnover between sex-determining systems.
+In panels A and C, male drive in an ancestral XY system causes a male bias, allowing a neo-W to invade and fix (causing the Y to fix in females), which balances the sex ratio (it also avoids selection in males, and thus makes better females in this case of sex-specific ploidally-antagonistic selection).
+In panels B and D, male drive in an ancestral ZW system has no affect on the sex ratio, yet a neo-Y can invade and fix (causing the W to fix in males) because it becomes linked with the driving allele, and this imparts a sex ratio bias.
+Parameters:  $s^\female =s^\male = 0.2$, $h^\female = h^\male = 0.7$, $t^\female = t^\male = \alpha^\male_\Delta = 0$, $\alpha^\female_\Delta = -1/10$, $r=1/20$.
+}
+\label{fig:SexRatioBad}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Haploid selection can lead to polymorphic SD systems 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[!h]
+\centering
+\includegraphics[width=\linewidth]{Polymorphic}
+\caption{
+Tight linkage (relative to selection) and/or haploid selection can cause stable polymorphic sex-determining systems.
+In panel A, there is strong overdominance in both sexes and no haploid selection  (parameters as in Figure \ref{fig:BothOverdominance}B with $r = 1/10$), in which case a neo-W can invade regardless of sex-linkage, but cannot not fix (i.e., the Y does not fix in females, and X, Y, W, and Z all segregate at equilibrium).
+In panel B, there is sex-antagonistic selection at the diploid stage and drive in females (parameters as in Figure \ref{fig:SexAntagTighter} with $\alpha^\female_\Delta = -1/20$ and $r = 1/10$), in which case a sufficiently tightly linked neo-W can invade ($R<\sim r$), but only fixes if $R=0$.
+}
+\label{fig:Polymorphism}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%CYCLES!
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[!h]
+\centering
+\includegraphics[width=0.5\linewidth]{BothWsInvade_Overdominance_Cycles}
+\caption{
+Thought I'd show this just for fun (not for publication).
+}
+\label{fig:Cycles}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %Heterogametic transitions with/without sex ratio change
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-\begin{tikzpicture}[remember picture]
-	\node[] (plot) {\includegraphics[width=\linewidth]{Combination_Turnover_Ratio}};
-	\node[above = -1cm of plot, xshift = -100] () {XY $\rightarrow$ ZW};
-	\node[above = -1cm of plot, xshift = 90] () {ZW $\rightarrow$ XY};
-\end{tikzpicture}
-\caption{
-%\textcolor{red}{Is this what Sally was thinking?}
-%\textcolor{blue}{I think this works but I'm confused as to why the speed of spread should be so much different for XY and ZW here.
+%\begin{figure}[!h]
+%\centering
+%\begin{tikzpicture}[remember picture]
+%	\node[] (plot) {\includegraphics[width=\linewidth]{Combination_Turnover_Ratio}};
+%	\node[above = -1cm of plot, xshift = -100] () {XY $\rightarrow$ ZW};
+%	\node[above = -1cm of plot, xshift = 90] () {ZW $\rightarrow$ XY};
+%\end{tikzpicture}
+%\caption{
+%%\textcolor{red}{Is this what Sally was thinking?}
+%%\textcolor{blue}{I think this works but I'm confused as to why the speed of spread should be so much different for XY and ZW here.
 Figure \ref{fig:Combination_Turnover} and \ref{fig:Combination_Centimorgans} suggests that there's not much difference between XY->ZW and ZW->XY.
@@
 }
-%\textcolor{red}{i messed up and had $r=0.5$ instead of $r=0.05$ for B and D. haven't fixed fitness plot below.}
-Heterogametic transitions occur (panels A and B) regardless of sex ratio biases (panels C and D).
-A neo-W invades (panel A) and equalizes the male-biased sex ratio (panel C) that was caused by meiotic drive in males.
-A neo-Y invades (panel B) a population with an equal sex ratio. 
-With any amount of linkage ($R<1/2$), the neo-Y becomes associated with the driving allele in males, and in the end causes a male bias.
-Parameters: $s^\female = s^\male = 1/5$, $h^\female = h^\male = 7/10$, $t^\female = t^\male=0$, $\alpha^\female_\Delta = 0$, $\alpha^\male_\Delta = -1/5$, $r = 1/20$.
-}
-\label{fig:Combination_Turnover_Ratio}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
+%%\textcolor{red}{i messed up and had $r=0.5$ instead of $r=0.05$ for B and D. haven't fixed fitness plot below.}
+%Heterogametic transitions occur (panels A and B) regardless of sex ratio biases (panels C and D).
+%A neo-W invades (panel A) and equalizes the male-biased sex ratio (panel C) that was caused by meiotic drive in males.
+%A neo-Y invades (panel B) a population with an equal sex ratio. 
+%With any amount of linkage ($R<1/2$), the neo-Y becomes associated with the driving allele in males, and in the end causes a male bias.
+%Parameters: $s^\female = s^\male = 1/5$, $h^\female = h^\male = 7/10$, $t^\female = t^\male=0$, $\alpha^\female_\Delta = 0$, $\alpha^\male_\Delta = -1/5$, $r = 1/20$.
+%}
+%\label{fig:Combination_Turnover_Ratio}
+%\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\newpage
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Chromosomal Positions
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-%\includegraphics[width=\linewidth]{Combination_Centimorgan}\\
-%\includegraphics[width=\linewidth]{PositionPlot}\\
-\begin{tikzpicture}[remember picture]
-%	\node[] () {\includegraphics[width=\linewidth]{PositionPlot}};
-	\node[] () {\includegraphics[width=0.5\linewidth]{PositionPlot_2}};
-%	\node[anchor=east] at (0, 1.5) {\footnotesize diploid sex-antagonism}; %, $s^\male s^\female < 0$};
-%	\node[anchor=east] at (6.5, 1.5) {\footnotesize haploid sex-antagonism}; %, $s^\male s^\female > 0$};
-%	\node[anchor=east] at (0, -3) {\footnotesize male drive (ploidy-antagonism)}; %, $s^\male < s^\female$};
-%	\node[anchor=east] at (6.5, -3) {\footnotesize find something interesting to plot};%, $s^\female < s^\female$};
-%	\node[anchor=center] at (-1.3, 4.25) {\scriptsize tighter sex-linkage};
-%	\node[anchor=center] at (2.45, 3.5) {\scriptsize ancestral SDR};
-%	\draw[->,thick] (2.45, 3.25) -- (2.45, 2.5);
-%	\node[anchor=center] at (-1.4, -0.25) {\scriptsize novel SDR};
-%	\draw[->,thick] (-1.4, -0.5) -- (-1.4, -1);
-\end{tikzpicture}
-\caption{
-Invasion fitness of a neo-sex-determining allele against the relative genomic location of a locus under direct selection. 
-% (neo-Y invading ZW in black, neo-W invading XY in red)
-%The ancestral sex-determining locus is located at -25 and the novel sex-determining locus is located at 25. %and that there is a polymorphism at the \textbf{A} locus maintained by selection.
-%Thus, if the neo-sex-determining allele invades in the gray region the system evolves tighter sex-linkage.  
-In panel A, there is no haploid selection ($t^\Hermaphrodite=\alpha^\Hermaphrodite_{\Delta}=0$) and selection in diploids is sexually antagonistic ($s^\male=-s^\female=1/10$, $h^\male=1-h^\female=3/10$), in which case the neo-sex-determining allele can only invade if it is more closely linked to the selected locus ($R<r$; gray region).
-In panel B, there is no diploid selection ($s^\Hermaphrodite=0$) and selection in haploids is sexually antagonistic ($t^\male=-t^\female=0.08$, $\alpha^\Hermaphrodite_{\Delta}=0$), in which case the neo-sex-determining allele can invade regardless of linkage.
-In panel C, selection in diploids ($s^\male=s^\female=1/10$, $h^\male=h^\female=7/10$) opposes drive in males ($\alpha^\male_{\Delta}=-0.05$, $t^\Hermaphrodite=\alpha^\female_{\Delta}=0$), in which case the neo-sex-determining allele can once again invade regardless of linkage.
-We use Haldane's map function \citep[Equation 3 in ][]{Haldane1919} to convert from map distance (centiMorgans, cM) to the probability of a cross-over event.    
-%we include haploid selection. %and assume that selection in diploids is not sexually-antagonistic ($s^\female s^\male>0$). 
-%A polymorphism can then be maintained by opposing selection between the haploid and diploid phases. 
-%In B, there is drive in favour of the $a$ allele in males ($\alpha^\male_{\Delta}=-1/20$), no female meiotic drive or gametic competition, $t^\Hermaphrodite=\alpha^\female_{\Delta}=0$), and equal selection in diploid sexes ($s^\female=s^\male=1/10$, $h^\female=h^\male=7/10$).
-%In this case, a neo-W can invade even when the selected locus is more closely linked to the ancestral sex determining locus (see Table \ref{tab:specialcases} and Figure \ref{fig:Combination_Turnover}).
-%In C and D, there is gametic competition among male gametes only (favouring $a$, $t^\male=-1/10$) and no meiotic drive or gametic competition in females ($t^\female=\alpha^\Hermaphrodite_{\Delta}=0$).
-%In this case, the neo-W does not invade if $s^\female>s^\male$ (panel C: $s^\female=3/20$, $s^\male=1/20$) but does if $s^\female<s^\male$ (panel D: $s^\female=1/20$, $s^\male=3/20$), see Table \ref{tab:specialcases}.\\
-%\textcolor{red}{
-%1.
+%%Chromosomal Positions
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\begin{figure}[!h]
+%\centering
+%%\includegraphics[width=\linewidth]{Combination_Centimorgan}\\
+%%\includegraphics[width=\linewidth]{PositionPlot}\\
+%\begin{tikzpicture}[remember picture]
+%%	\node[] () {\includegraphics[width=\linewidth]{PositionPlot}};
+%	\node[] () {\includegraphics[width=0.5\linewidth]{PositionPlot_2}};
+%%	\node[anchor=east] at (0, 1.5) {\footnotesize diploid sex-antagonism}; %, $s^\male s^\female < 0$};
+%%	\node[anchor=east] at (6.5, 1.5) {\footnotesize haploid sex-antagonism}; %, $s^\male s^\female > 0$};
+%%	\node[anchor=east] at (0, -3) {\footnotesize male drive (ploidy-antagonism)}; %, $s^\male < s^\female$};
+%%	\node[anchor=east] at (6.5, -3) {\footnotesize find something interesting to plot};%, $s^\female < s^\female$};
+%%	\node[anchor=center] at (-1.3, 4.25) {\scriptsize tighter sex-linkage};
+%%	\node[anchor=center] at (2.45, 3.5) {\scriptsize ancestral SDR};
+%%	\draw[->,thick] (2.45, 3.25) -- (2.45, 2.5);
+%%	\node[anchor=center] at (-1.4, -0.25) {\scriptsize novel SDR};
+%%	\draw[->,thick] (-1.4, -0.5) -- (-1.4, -1);
+%\end{tikzpicture}
+%\caption{
+% A neo-W can invade an XY system under a large number of selective regimes.
+%%Invasion fitness of a neo-sex-determining allele against the relative genomic location of a locus under direct selection. 
+%% (neo-Y invading ZW in black, neo-W invading XY in red)
+%%The ancestral sex-determining locus is located at -25 and the novel sex-determining locus is located at 25. %and that there is a polymorphism at the \textbf{A} locus maintained by selection.
+%%Thus, if the neo-sex-determining allele invades in the gray region the system evolves tighter sex-linkage.  
+%In panel A, there is no haploid selection ($t^\Hermaphrodite=\alpha^\Hermaphrodite_{\Delta}=0$) and selection in diploids is sexually antagonistic ($s^\male=-s^\female=1/10$, $h^\male=1-h^\female=3/10$), in which case the neo-sex-determining allele can only invade if it is more closely linked to the selected locus ($R<r$, gray region; but see Figure \ref{fig:SexAntagTighter}B).
+%In panel B, there is no diploid selection ($s^\Hermaphrodite=0$) and selection in haploids is sexually antagonistic ($t^\male=-t^\female=0.08$, $\alpha^\Hermaphrodite_{\Delta}=0$), in which case the neo-sex-determining allele can invade regardless of linkage.
+%In panel C, selection in diploids ($s^\male=s^\female=1/10$, $h^\male=h^\female=7/10$) opposes drive in males ($\alpha^\male_{\Delta}=-0.05$, $t^\Hermaphrodite=\alpha^\female_{\Delta}=0$), in which case the neo-sex-determining allele can once again invade regardless of linkage.
+%We use Haldane's map function \citep[Equation 3 in ][]{Haldane1919} to convert from map distance (centiMorgans, cM) to the probability of a cross-over event.    
+%%we include haploid selection. %and assume that selection in diploids is not sexually-antagonistic ($s^\female s^\male>0$). 
+%%A polymorphism can then be maintained by opposing selection between the haploid and diploid phases. 
+%%In B, there is drive in favour of the $a$ allele in males ($\alpha^\male_{\Delta}=-1/20$), no female meiotic drive or gametic competition, $t^\Hermaphrodite=\alpha^\female_{\Delta}=0$), and equal selection in diploid sexes ($s^\female=s^\male=1/10$, $h^\female=h^\male=7/10$).
+%%In this case, a neo-W can invade even when the selected locus is more closely linked to the ancestral sex determining locus (see Table \ref{tab:specialcases} and Figure \ref{fig:Combination_Turnover}).
+%%In C and D, there is gametic competition among male gametes only (favouring $a$, $t^\male=-1/10$) and no meiotic drive or gametic competition in females ($t^\female=\alpha^\Hermaphrodite_{\Delta}=0$).
+%%In this case, the neo-W does not invade if $s^\female>s^\male$ (panel C: $s^\female=3/20$, $s^\male=1/20$) but does if $s^\female<s^\male$ (panel D: $s^\female=1/20$, $s^\male=3/20$), see Table \ref{tab:specialcases}.\\
+%%\textcolor{red}{
+%%1.
 I suspect that panel C has a region where no equilibrium is maintained (CHECK!
@@
 MMO: If you trust the sieve function there are stable equilibria across the entire range, although they differ greatly between XY and ZW systems near -25cM.
-%\\
-%2.
+%%\\
+%%2.
 Currently use different parameters for B than using in figure \ref{fig:Combination_Turnover} (selection/drive twice as strong in turnover figure).
 MMO: this is to keep it within the bounds of the plot -- using the same parameters as figure 1 makes the peak at -25 reach roughly 0.1, and then it is difficult to see the details of A,C, and D.
-%%This plot would also benefit from titles giving, e.g., ``sexually-antagonistic selection, $s^\female s^\male<0$'' for A, ``male meiotic drive, $s^\female s^\male>0$'' for B
+%%%This plot would also benefit from titles giving, e.g., ``sexually-antagonistic selection, $s^\female s^\male<0$'' for A, ``male meiotic drive, $s^\female s^\male>0$'' for B
+%%}
 %}
-}
-\label{fig:Combination_Centimorgans}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Haplotype invasion region plot
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-\begin{tikzpicture}[remember picture]
-	\node[] () {
-	\includegraphics[width=0.5\linewidth]{regionplot_2a}
-	\includegraphics[width=0.5\linewidth]{regionplot_hap}
-	};
-\end{tikzpicture}
-\caption{
-Parameter space (gray) where both neo-W haplotypes can invade from the same stable resident $r=0$ equilibria (equations \ref{eq:tightequil}), and therefore where an unlinked neo-W can invade an XY system with perfect sex-linkage.
-\textbf{A}, In the absence of haploid selection, both neo-W haplotypes can invade for much of the parameter space where the relative fitnesses of male homozygotes, $w_{AA}^\male$ and $w_{aa}^\male$, are both less than that of the heterozygote, $w_{Aa}^\male = 1$.
-In the white region neo-W haplotypes paired with the allele fixed on the Y cannot invade.
-Parameters as in \cite{Otto2014} Figure 2a: $w_A^\Hermaphrodite=w_a^\Hermaphrodite$, $\alpha^\Hermaphrodite=1/2$, $w_{Aa}^\Hermaphrodite=1$, and $w_{AA}^\female=w_{aa}^\female=0.75$.
-\textbf{B}, When selection is the same in both diploid sexes ($w_{aa}^\Hermaphrodite = 1$, $w_{Aa}^\Hermaphrodite = 1 + h s$, $w_{AA}^\Hermaphrodite = 1+s$), both neo-W haplotypes can invade over a portion of the parameter space where selection in diploids ($s$) opposes the force of drive during meiosis in males ($\alpha_{\Delta}^\male$).
-Parameters: $w_A^\Hermaphrodite=w_a^\Hermaphrodite$, $\alpha^\female=1/2$, $h=1/2$.
-}
-\label{fig:regionplot_2a}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
+%\label{fig:Combination_Centimorgans}
+%\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\newpage
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%Haplotype invasion region plot
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\begin{figure}[!h]
+%\centering
+%\begin{tikzpicture}[remember picture]
+%	\node[] () {
+%	\includegraphics[width=0.5\linewidth]{regionplot_2a}
+%	\includegraphics[width=0.5\linewidth]{regionplot_hap}
+%	};
+%\end{tikzpicture}
+%\caption{
+%Parameter space (gray) where both neo-W haplotypes can invade from the same stable resident $r=0$ equilibria (equations \ref{eq:tightequil}), and therefore where an unlinked neo-W can invade an XY system with perfect sex-linkage.
+%\textbf{A}, In the absence of haploid selection, both neo-W haplotypes can invade for much of the parameter space where the relative fitnesses of male homozygotes, $w_{AA}^\male$ and $w_{aa}^\male$, are both less than that of the heterozygote, $w_{Aa}^\male = 1$.
+%In the white region neo-W haplotypes paired with the allele fixed on the Y cannot invade.
+%Parameters as in \cite{Otto2014} Figure 2a: $w_A^\Hermaphrodite=w_a^\Hermaphrodite$, $\alpha^\Hermaphrodite=1/2$, $w_{Aa}^\Hermaphrodite=1$, and $w_{AA}^\female=w_{aa}^\female=0.75$.
+%\textbf{B}, When selection is the same in both diploid sexes ($w_{aa}^\Hermaphrodite = 1$, $w_{Aa}^\Hermaphrodite = 1 + h s$, $w_{AA}^\Hermaphrodite = 1+s$), both neo-W haplotypes can invade over a portion of the parameter space where selection in diploids ($s$) opposes the force of drive during meiosis in males ($\alpha_{\Delta}^\male$).
+%Parameters: $w_A^\Hermaphrodite=w_a^\Hermaphrodite$, $\alpha^\female=1/2$, $h=1/2$.
+%}
+%\label{fig:regionplot_2a}
+%\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\newpage
 

### 2017-08-10 LaTeX/Turnover.tex
fixed caption error in fig 6, cited kozi in sex ratio discussion paragraph

@@
 
-Sex ratio biases caused by gametic competition or meiotic drive have been shown to exert Fisherian sex-ratio selection on various autosomal \citep{Stalker:1961th,Smith:1975ft,Frank:1989vl,Hough:2013uo,Ubeda:2015fx, Otto:2015va} and sex-linked \citep{Ubeda:2015fx} modifiers.
+Sex ratio biases caused by gametic competition or meiotic drive have been shown to exert Fisherian sex-ratio selection on various autosomal \citep{Stalker:1961th,Smith:1975ft,Frank:1989vl,Hough:2013uo,Ubeda:2015fx, Otto:2015va} and sex-linked \citep{Kozielska:2010vm} modifiers.
 We find that sex-ratio biases caused by haploid selection can also affect transitions between sex-determining systems (e.g., see $\zeta$ terms in Table \ref{tab:haplotype_growth}). 
 For instance, when an allele that drives in males is linked to an XY locus it will often become associated with the Y and therefore produce a male bias ($\zeta<1/2$).
-This male bias increases the potential for a neo-W to invade (as we then have $(2\zeta)^{-1}>1$ in Table \ref{tab:haplotype_growth}), which can equalize the sex-ratio \citep[for a related example see][]{Ubeda:2015fx}.
+This male bias increases the potential for a neo-W to invade (as we then have $(2\zeta)^{-1}>1$ in Table \ref{tab:haplotype_growth}), which can equalize the sex-ratio \citep[for related examples see][]{Kozielska:2010vm,Ubeda:2015fx}.
 %However, the neo-W may not equalize the sex-ratio (e.g., if the driving allele also drives in females or affects competition among eggs)
-However, this sex-ratio selection can be overwhelmed when the driving allele has additional selective effects (e.g., when it is beneficial for male diploids but detrimental for female diploids; Table \ref{tab:specialcases}), preventing the neo-W from invading.
+However, this sex-ratio selection can be overwhelmed by drive itself or additional selective effects (e.g., when a linked allele is beneficial for male diploids but detrimental for female diploids; Table \ref{tab:specialcases}), preventing the neo-W from invading.
 %and equalizing the sex ratio.
-Indeed, these additional selective effects can even favour transitions between sex-determining systems that create new sex-ratio biases.
+Indeed, these additional selective effects can even favour transitions between sex-determining systems that create new sex-ratio biases \citep{Ubeda:2015fx}.
 For example, in an ancestral ZW system, an allele that drives only in males can allow a linked neo-Y to invade, despite the fact it creates a male bias (Figure \ref{fig:Combination_Turnover}C).
@@
 An asymmetry can develop when sex-linkage is tight (e.g., Figure \ref{fig:Combination_Centimorgans} near -25cM and 25cM) but under most circumstances we do not predict asymmetry between XY to ZW and ZW to XY transitions despite the presence/absence of sex ratio selection.
-Thus, haploid selection can favour heterogametic transitions both via sex-ratio selection and via fitness effects of alleles that are associated with the neo-sex-determining allele, and these selection pressures are often of equal magnitude.
+Thus, haploid selection can favour heterogametic transitions both via sex-ratio selection \citep[as predicted by][]{Kozielska:2010vm} and via fitness effects of alleles that are associated with the neo-sex-determining allele \citep[as predicted in step 1 by][]{Ubeda:2015fx}, and these selection pressures are predicted to often be of roughly equal magnitude.
 %\textcolor{blue}{nice, pretty subtle argument but I think that's a good job.}
@@
 In panel A, there is strong overdominance in both sexes and no haploid selection  (parameters as in Figure \ref{fig:BothOverdominance}B with $r = 1/10$), in which case a neo-W can invade regardless of sex-linkage, but cannot not fix (i.e., the Y does not fix in females, and X, Y, W, and Z all segregate at equilibrium).
-In panel B, there is sex-antagonistic selection at the diploid stage and drive in females (parameters as in Figure \ref{fig:SexAntagTighter} with $\alpha^\female_\Delta = -1/20$ and $r = 1/10$), in which case a sufficiently tightly linked neo-W can invade ($R<\sim r$), but only fixes if $R=0$.
+In panel B, there is sex-antagonistic selection at the diploid stage and drive in females (parameters as in Figure \ref{fig:SexAntagTighter} with $\alpha^\female_\Delta = 1/20$ and $r = 1/10$), in which case a sufficiently tightly linked neo-W can invade ($R<\sim r$), but only fixes if $R=0$.
 }

### 2017-08-10 LaTeX/Turnover.tex
new figure 2

@@
 \centering
-\includegraphics[width=0.45\linewidth]{regionplot_2a}
+%\includegraphics[width=0.45\linewidth]{regionplot_2a}
+\includegraphics[width=0.45\linewidth]{regionplot_2a_Color_Ya_Either}
 \includegraphics[width=0.45\linewidth]{BothWsInvade_Overdominance}
@@
 In the absence of haploid selection, both neo-W haplotypes can spread in an XY system when there is overdominance.
-Panel A shows the range of male homozygote fitnesses that allow both neo-W haplotypes to invade.
+Panel A shows the range of male homozygote fitnesses that allow either neo-W haplotypes to invade.
+The blue region overlaps with a red region, where both neo-W haplotypes can invade a population with $A$ fixed on the X and $a$ fixed on the Y.
+The green region (overlapped by the orange region) is where both neo-W haplotypes can invade a population with $a$ fixed on the Y and a polymorphic X.
+The orange region (outside the green region) is where only the neo-W-$A$ haplotype can invade
 Panel B shows the temporal dynamics of the invading neo-W haplotypes; in this case the neo-W does not fix, leading to a polymorphic sex-determining system.
@@
 Parameters: $w_{AA}^\female = w_{aa}^\female = 0.6$, $w_{Aa}^\Hermaphrodite = 1$, $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$, $r=R=0$.
+\textcolor{red}{make two more temporal plots with visible asterisks in green and orange regions; figure out better colours to show possibilities}
 }

### 2017-08-16 LaTeX/Turnover.tex
new figures attempt

--- 2017-08-10 LaTeX/Turnover.tex
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Tighter linkage allows looser sex-linkage to evolve, even in absence of haploid selection
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[!h]
+\centering
+\centerline{\includegraphics[width=1.5\linewidth]{PositionPlot_SexAntagTighter_Mike}}
+\caption{
+Transitions between XY and ZW systems can occur even when the neo-SDR is more loosely linked to a locus under sexually-antagonistic selection (here, without haploid selection $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$).
+In panel A, linkage is loose enough relative to selection that the weak selection analytical results hold, and a neo-W can only invade when it is more tightly linked with the selected locus ($R<r$; shaded region).
+In panel B, linkage is tight enough relative to selection that the weak selection analytical results do no hold, and a neo-W can only invade even when it is less tightly linked with the selected locus ($r<R$; unshaded region).
+In panel C we vary the recombination rate between the neo-W and the selected locus ($R$) for a fixed recombination rate between the ancestral-SDR and the selected locus ($r=0.005$). 
+Coloured markers show recombination rates for which the temporal dynamics of invasion are plotted in the inset, demonstrating that neo-W alleles can fix (reach frequency $0.5$ among female gametes) if they are more (black) or less (red) closely linked to a locus experiencing sexually-antagonistic selection.
+A very loosely linked neo-W does not spread in this case (blue and green lines overlap and go to 0). 
+Fitness parameters are shown by an asterisk in Figure \ref{fig:regionplots}: $w_{AA}^\female = 1.05$, $w_{aa}^\male = 1.2$, $w_{aa}^\female = w_{AA}^\male = 0.85$, $w_{Aa}^\Hermaphrodite = 1$.
+}
+\label{fig:SexAntagTighter}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 %\textcolor{blue}{
@@
 %}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Both neo-W haplotypes can spread, in the absence of haploid selection, when there is overdominance
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[!h]
+\centering
+\centerline{\includegraphics[width=1.25\linewidth]{Region_plot_combined_Mike}}
+\caption{
+When the ancestral-XY locus is tightly linked to a locus under selection ($r=0$), one or both neo-W haplotypes can spread. 
+We vary the fitness of male homozygotes relative to heterozygotes ($w_{Aa}^\Hermaphrodite=1$) and only consider stable equilibria at which the $a$ allele is initially fixed on the Y, as indicated. 
+Here, selection in females can favour the $A$ allele (panel A, $w_{aa}^\female=0.85$, $w_{AA}^\female=1.05$), favour the $a$ allele (panel B, $w_{aa}^\female=1.05$, $w_{AA}^\female=0.85$), or be overdominant (panel C, $w_{aa}^\female=w_{AA}^\female=0.6$).
+If $\lambda_{wA}$ or $\lambda_{wa}$ is greater than one, then a rare neo-W can spread for, at least, some values of $R>r$. 
+For the parameter values marked with an asterisk, example invasion dynamics are shown in Figure \ref{fig:SexAntagTighter}C. 
+Where both $\lambda_{wA}$ and $\lambda_{wa}$ are greater than one, a neo-W will spread when rare, regardless of linkage with the selected locus (for any $R$). 
+Figure \ref{fig:positionOverdominance} shows two examples using the parameters marked with a dagger. 
+Here, there is no haploid selection $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
+}
+\label{fig:regionplots}
+\end{figure}
 
@@
 Mean diploid fitness therefore decreases during heterogametic transitions that create looser sex-linkage (Figure \ref{fig:Combination_MeanFit}B,D).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%A neo-W can invade an XY system under a large number of selective regimes
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[!h]
+\centering
+\includegraphics[width=0.5\linewidth]{PositionPlot_4}
+\caption{
+ A neo-W can invade an XY system under a large number of selective regimes.
+In panel A, there is no haploid selection ($t^\Hermaphrodite = \alpha^\Hermaphrodite_{\Delta} = 0$) and selection in diploids is sexually antagonistic ($s^\male = -s^\female = 1/10$, $h^\male = 1-h^\female = 3/10$), in which case the neo-sex-determining allele can only invade if it is more closely linked to the selected locus ($R<r$, gray region; but see Figure \ref{fig:SexAntagTighter}B for the case of very tight linkage).
+In panel B, male drive ($\alpha^\male_{\Delta} = -1/20$, $t^\Hermaphrodite = \alpha^\female_{\Delta} = 0$) opposes selection in diploids (no sex-differences: $s^\Hermaphrodite = 1/10$, $h^\Hermaphrodite = 7/10$), in which case the neo-sex-determining allele can invade regardless of linkage.
+In panel C, haploid competition in males ($t^\male = -1/10$, $t^\female = \alpha^\Hermaphrodite_{\Delta} = 0$) opposes selection in diploids (sex-differences: $s^\male = 3 s^\female = 3/20$, $h^\Hermaphrodite = 7/10$), in which case the neo-sex-determining allele can once again invade regardless of linkage.
+We use Haldane's map function \citep[Equation 3 in ][]{Haldane1919} to convert from map distance (centiMorgans, cM) to the probability of recombination (an odd number of cross-over events).   
+}
+\label{fig:Combination_Centimorgans}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 As selection becomes stronger (or linkage becomes tighter), this symmetry between sex-ratio selection and haploid selection is lost, causing differences in the strength of selection favouring the two heterogametic transitions (compare red to black near -25cM and 25 cM in Figure \ref{fig:Combination_Centimorgans}).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Sex-ratio selection is not a good predictor of neo-W invasion into an XY system
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[!h]
+\centering
+\includegraphics[width=\linewidth]{Temporal_SR_Mike}
+\caption{
+Fisherian sex-ratio selection alone is not a good predictor of turnover between sex-determining systems.
+In this figure, selection is ploidally antagonistic with haploid selection favouring the $a$ allele during male meiosis ($s^\female =s^\male = 0.2$, $h^\female = h^\male = 0.7$, $t^\female = t^\male = \alpha^\male_\Delta = 0$).
+In panel A, male drive in an ancestral ZW system has no affect on the sex ratio, yet a neo-Y can invade and replace the ancestral sex-determination system (see inset, the ancestral W also fixes). 
+In this case, the neo-Y becomes associated with the allele favoured by drive, causing the zygotic sex ratio to become biased, hence the frequency of neo-Y among male gametes can be higher than $0.5$ (inset).
+In panel B, male drive in an ancestral XY system causes a male bias, allowing a neo-W to invade and replace the ancestral sex-determination system (see inset, the ancestral Y also fixes), which balances the sex ratio.
+Parameters:  $s^\female =s^\male = 0.2$, $h^\female = h^\male = 0.7$, $t^\female = t^\male = \alpha^\male_\Delta = 0$, $\alpha^\male_\Delta = -0.2$, $r=0.02$.
+}
+\label{fig:SexRatioBad}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \newpage
-\section*{Figures}
+%\section*{Figures}
 %\newpage
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-\includegraphics[width=\linewidth]{PositionPlot_SexAntagTighter}
-\caption{
-In the absence of haploid selection, tight linkage allows looser sex-linkage to evolve in transitions between XY and ZW systems.
-In panel A, linkage is loose enough relative to selection that the weak selection analytical results hold, and a neo-W can only invade when it is more tightly linked with the selected locus ($R<r$; shaded region).
-In panel B, linkage is tight enough relative to selection that the weak selection analytical results do no hold, and a neo-W can only invade even when it is less tightly linked with the selected locus ($r<R$; unshaded region).
-Parameters: $w_{AA}^\female = w_{aa}^\male = 1.05$, $w_{aa}^\female = w_{AA}^\male = 0.85$, $w_{Aa}^\female = 1$, $w_{Aa}^\male = 0.925$, $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
-}
-\label{fig:SexAntagTighter}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
+%\begin{figure}[!h]
+%\centering
+%\includegraphics[width=\linewidth]{PositionPlot_SexAntagTighter}
+%\caption{
+%In the absence of haploid selection, tight linkage allows looser sex-linkage to evolve in transitions between XY and ZW systems.
+%In panel A, linkage is loose enough relative to selection that the weak selection analytical results hold, and a neo-W can only invade when it is more tightly linked with the selected locus ($R<r$; shaded region).
+%In panel B, linkage is tight enough relative to selection that the weak selection analytical results do no hold, and a neo-W can only invade even when it is less tightly linked with the selected locus ($r<R$; unshaded region).
+%Parameters: $w_{AA}^\female = w_{aa}^\male = 1.05$, $w_{aa}^\female = w_{AA}^\male = 0.85$, $w_{Aa}^\female = 1$, $w_{Aa}^\male = 0.925$, $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
+%}
+%\label{fig:SexAntagTighter}
+%\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\newpage
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-\includegraphics[width=0.45\linewidth]{regionplot_2a}
-\includegraphics[width=0.45\linewidth]{BothWsInvade_Overdominance}
-\caption{
-In the absence of haploid selection, both neo-W haplotypes can spread in an XY system when there is overdominance.
-Panel A shows the range of male homozygote fitnesses that allow both neo-W haplotypes to invade.
-Panel B shows the temporal dynamics of the invading neo-W haplotypes; in this case the neo-W does not fix, leading to a polymorphic sex-determining system.
-Asterisk in panel A marks parameter values ($w_{aa}^\male=0.15$, $w_{AA}^\male=0.1$) used in panel B.
-Parameters: $w_{AA}^\female = w_{aa}^\female = 0.6$, $w_{Aa}^\Hermaphrodite = 1$, $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$, $r=R=0$.
-}
-\label{fig:BothOverdominance}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
+%\begin{figure}[!h]
+%\centering
+%\includegraphics[width=0.45\linewidth]{regionplot_2a}
+%\includegraphics[width=0.45\linewidth]{regionplot_2a_Color_Ya_Either}
+%\includegraphics[width=0.45\linewidth]{BothWsInvade_Overdominance}
+%\caption{
+%In the absence of haploid selection, both neo-W haplotypes can spread in an XY system when there is overdominance.
+%Panel A shows the range of male homozygote fitnesses that allow either neo-W haplotypes to invade.
+%The blue region overlaps with a red region, where both neo-W haplotypes can invade a population with $A$ fixed on the X and $a$ fixed on the Y.
+%The green region (overlapped by the orange region) is where both neo-W haplotypes can invade a population with $a$ fixed on the Y and a polymorphic X.
+%The orange region (outside the green region) is where only the neo-W-$A$ haplotype can invade
+%Panel B shows the temporal dynamics of the invading neo-W haplotypes; in this case the neo-W does not fix, leading to a polymorphic sex-determining system.
+%Asterisk in panel A marks parameter values ($w_{aa}^\male=0.15$, $w_{AA}^\male=0.1$) used in panel B.
+%Parameters: $w_{AA}^\female = w_{aa}^\female = 0.6$, $w_{Aa}^\Hermaphrodite = 1$, $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$, $r=R=0$.
+%\textcolor{red}{make two more temporal plots with visible asterisks in green and orange regions; figure out better colours to show possibilities}
+%}
+%\label{fig:BothOverdominance}
+%\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\newpage
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-\includegraphics[width=0.5\linewidth]{Loose_Fitness_Decline}
-\caption{
-With weak selection, a less tightly linked neo-W can invade (and fix in) an XY system (causing the Y to fix in females) when there is some haploid selection (blue and green curves in panel A), and this invasion decreases mean diploid fitness (green and blue curves in panel B).
-Parameters: $s^\Hermaphrodite = 0.2$, $h^\Hermaphrodite = 0.7$, $t^\Hermaphrodite = \alpha^\male_\Delta = 0$, $\alpha^\female_\Delta = -0.1$, $r=1/10$.
-}
-\label{fig:LooseDecline}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
+%\begin{figure}[!h]
+%\centering
+%\includegraphics[width=0.5\linewidth]{Loose_Fitness_Decline}
+%\caption{
+%With weak selection, a less tightly linked neo-W can invade (and fix in) an XY system (causing the Y to fix in females) when there is some haploid selection (blue and green curves in panel A), and this invasion decreases mean diploid fitness (green and blue curves in panel B).
+%Parameters: $s^\Hermaphrodite = 0.2$, $h^\Hermaphrodite = 0.7$, $t^\Hermaphrodite = \alpha^\male_\Delta = 0$, $\alpha^\female_\Delta = -0.1$, $r=1/10$.
+%}
+%\label{fig:LooseDecline}
+%\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\newpage
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-\includegraphics[width=0.5\linewidth]{PositionPlot_4}
-\caption{
- A neo-W can invade an XY system under a large number of selective regimes.
-In panel A, there is no haploid selection ($t^\Hermaphrodite = \alpha^\Hermaphrodite_{\Delta} = 0$) and selection in diploids is sexually antagonistic ($s^\male = -s^\female = 1/10$, $h^\male = 1-h^\female = 3/10$), in which case the neo-sex-determining allele can only invade if it is more closely linked to the selected locus ($R<r$, gray region; but see Figure \ref{fig:SexAntagTighter}B for the case of very tight linkage).
-In panel B, male drive ($\alpha^\male_{\Delta} = -1/20$, $t^\Hermaphrodite = \alpha^\female_{\Delta} = 0$) opposes selection in diploids (no sex-differences: $s^\Hermaphrodite = 1/10$, $h^\Hermaphrodite = 7/10$), in which case the neo-sex-determining allele can invade regardless of linkage.
-In panel C, haploid competition in males ($t^\male = -1/10$, $t^\female = \alpha^\Hermaphrodite_{\Delta} = 0$) opposes selection in diploids (sex-differences: $s^\male = 3 s^\female = 3/20$, $h^\Hermaphrodite = 7/10$), in which case the neo-sex-determining allele can once again invade regardless of linkage.
-We use Haldane's map function \citep[Equation 3 in ][]{Haldane1919} to convert from map distance (centiMorgans, cM) to the probability of recombination (an odd number of cross-over events).   
-}
-\label{fig:Combination_Centimorgans}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
+%\begin{figure}[!h]
+%\centering
+%\includegraphics[width=0.5\linewidth]{PositionPlot_4}
+%\caption{
+% A neo-W can invade an XY system under a large number of selective regimes.
+%In panel A, there is no haploid selection ($t^\Hermaphrodite = \alpha^\Hermaphrodite_{\Delta} = 0$) and selection in diploids is sexually antagonistic ($s^\male = -s^\female = 1/10$, $h^\male = 1-h^\female = 3/10$), in which case the neo-sex-determining allele can only invade if it is more closely linked to the selected locus ($R<r$, gray region; but see Figure \ref{fig:SexAntagTighter}B for the case of very tight linkage).
+%In panel B, male drive ($\alpha^\male_{\Delta} = -1/20$, $t^\Hermaphrodite = \alpha^\female_{\Delta} = 0$) opposes selection in diploids (no sex-differences: $s^\Hermaphrodite = 1/10$, $h^\Hermaphrodite = 7/10$), in which case the neo-sex-determining allele can invade regardless of linkage.
+%In panel C, haploid competition in males ($t^\male = -1/10$, $t^\female = \alpha^\Hermaphrodite_{\Delta} = 0$) opposes selection in diploids (sex-differences: $s^\male = 3 s^\female = 3/20$, $h^\Hermaphrodite = 7/10$), in which case the neo-sex-determining allele can once again invade regardless of linkage.
+%We use Haldane's map function \citep[Equation 3 in ][]{Haldane1919} to convert from map distance (centiMorgans, cM) to the probability of recombination (an odd number of cross-over events).   
+%}
+%\label{fig:Combination_Centimorgans}
+%\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\newpage
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-\includegraphics[width=\linewidth]{Combination_Turnover_Ratio}
-\caption{
-Sex-ratio selection alone is not a good predictor of turnover between sex-determining systems.
-In panels A and C, male drive in an ancestral XY system causes a male bias, allowing a neo-W to invade and fix (causing the Y to fix in females), which balances the sex ratio (it also avoids selection in males, and thus makes better females in this case of sex-specific ploidally-antagonistic selection).
-In panels B and D, male drive in an ancestral ZW system has no affect on the sex ratio, yet a neo-Y can invade and fix (causing the W to fix in males) because it becomes linked with the driving allele, and this imparts a sex ratio bias.
-Parameters:  $s^\female =s^\male = 0.2$, $h^\female = h^\male = 0.7$, $t^\female = t^\male = \alpha^\male_\Delta = 0$, $\alpha^\female_\Delta = -1/10$, $r=1/20$.
-}
-\label{fig:SexRatioBad}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
+%\begin{figure}[!h]
+%\centering
+%\includegraphics[width=\linewidth]{Combination_Turnover_Ratio}
+%\caption{
+%Sex-ratio selection alone is not a good predictor of turnover between sex-determining systems.
+%In panels A and C, male drive in an ancestral XY system causes a male bias, allowing a neo-W to invade and fix (causing the Y to fix in females), which balances the sex ratio (it also avoids selection in males, and thus makes better females in this case of sex-specific ploidally-antagonistic selection).
+%In panels B and D, male drive in an ancestral ZW system has no affect on the sex ratio, yet a neo-Y can invade and fix (causing the W to fix in males) because it becomes linked with the driving allele, and this imparts a sex ratio bias.
+%Parameters:  $s^\female =s^\male = 0.2$, $h^\female = h^\male = 0.7$, $t^\female = t^\male = \alpha^\male_\Delta = 0$, $\alpha^\female_\Delta = -1/10$, $r=1/20$.
+%}
+%\label{fig:SexRatioBad}
+%\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\newpage
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-\includegraphics[width=\linewidth]{Polymorphic}
-\caption{
-Tight linkage (relative to selection) and/or haploid selection can cause stable polymorphic sex-determining systems.
-In panel A, there is strong overdominance in both sexes and no haploid selection  (parameters as in Figure \ref{fig:BothOverdominance}B with $r = 1/10$), in which case a neo-W can invade regardless of sex-linkage, but cannot not fix (i.e., the Y does not fix in females, and X, Y, W, and Z all segregate at equilibrium).
-In panel B, there is sex-antagonistic selection at the diploid stage and drive in females (parameters as in Figure \ref{fig:SexAntagTighter} with $\alpha^\female_\Delta = 1/20$ and $r = 1/10$), in which case a sufficiently tightly linked neo-W can invade ($R<\sim r$), but only fixes if $R=0$.
-}
-\label{fig:Polymorphism}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
+%\begin{figure}[!h]
+%\centering
+%\includegraphics[width=\linewidth]{Polymorphic}
+%\caption{
+%Tight linkage (relative to selection) and/or haploid selection can cause stable polymorphic sex-determining systems.
+%In panel A, there is strong overdominance in both sexes and no haploid selection  (parameters as in Figure \ref{fig:BothOverdominance}B with $r = 1/10$), in which case a neo-W can invade regardless of sex-linkage, but cannot not fix (i.e., the Y does not fix in females, and X, Y, W, and Z all segregate at equilibrium).
+%In panel B, there is sex-antagonistic selection at the diploid stage and drive in females (parameters as in Figure \ref{fig:SexAntagTighter} with $\alpha^\female_\Delta = 1/20$ and $r = 1/10$), in which case a sufficiently tightly linked neo-W can invade ($R<\sim r$), but only fixes if $R=0$.
+%}
+%\label{fig:Polymorphism}
+%\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\newpage
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-\includegraphics[width=0.5\linewidth]{BothWsInvade_Overdominance_Cycles}
-\caption{
-Thought I'd show this just for fun (not for publication).
-}
-\label{fig:Cycles}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
+%\begin{figure}[!h]
+%\centering
+%\includegraphics[width=0.5\linewidth]{BothWsInvade_Overdominance_Cycles}
+%\caption{
+%Thought I'd show this just for fun (not for publication).
+%}
+%\label{fig:Cycles}
+%\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\newpage
 
@@
 
-\subsubsection*{Selection weak relative to recombination (weak selection)}
-
-With weak selection the leading eigenvalue, $\lambda$, for any $k$, is given up to order $\epsilon^2$ by equation \ref{eq:lambda_ESD_k}.
-Scenarios leading to $\lambda>1$ are discussed in the main text.
+\section*{Supplementary Figures}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Both neo-W haplotypes can spread, in the absence of haploid selection, when there is overdominance
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[!h]
+\centering
+\centerline{\includegraphics[width=\linewidth]{PositionPlot_Overdominance_Mike}}
+\caption{
+Neo-W alleles can spread when loci under diploid selection are tightly linked to the ancestral sex determining locus ($r\approx0$). 
+In panels A and B, the $a$ allele is favoured in females ($w_{aa}^\female=1.05$, $w_{Aa}^\Hermaphrodite=1$, $w_{AA}^\female=0.85$) and selection in males is overdominant ($w_{aa}^\male=w_{AA}^\male=0.75$).
+In panels C and D, selection in males and females is overdominant ($w_{aa}^\female=w_{AA}^\female=0.6$, $w_{aa}^\male=0.5$, $w_{AA}^\male=0.7$, $w_{Aa}^\Hermaphrodite=1$). 
+These parameters are marked by a dagger in Figure \ref{fig:regionplots}, which shows that neo-W invasion is expected for any $R$ when the $a$ allele is nearly fixed on the Y (black lines). 
+Equilibria where the $A$ allele is more common among Y-bearing male gametes can also be stable for these parameters (blue lines). 
+The weak selection approximation only holds when all recombination rates are large relative to selection (around 0 in panels A and C), in which case neo-W alleles should spread if they are more tightly linked to the selected locus (positive invasion fitness in the grey region).
+Here, there is no haploid selection $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
+}
+\label{fig:positionOverdominance}
+\end{figure}
 
@@
 
-%\section*{Supplementary Figures}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Both neo-W haplotypes can spread, in the absence of haploid selection, when there is overdominance
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[!h]
+\centering
+\centerline{\includegraphics[width=\linewidth]{Temporal_Overdominance_Mike}}
+\caption{
+Following invasion by a neo-W allele, there can be a complete transition to a new sex-determination system, maintenance of polymorphism at both ancestral-XY and neo-ZW sex determining regions, or loss of the new sex-determining allele.
+Here we plot the frequency of the neo-W allele among female gametes; as the neo-W reaches frequency $0.5$, polymorphism at the ancestral XY locus is lost with Y becoming fixed such that sex is determined only be the ZW allele carried by a female gamete.
+Panels A, C and D show cases where a steady state is reached with the neo-W at a frequency below $0.5$, in which case ancestral-X and Y alleles also both segregate. 
+In all cases, we assume that the $a$ allele is initially more common that the $A$ allele on the Y (Y$a$ is fixed when $r=0$). 
+When $r>0$ (panels B and D), Y$A$ haplotypes created by recombination can become more common than Y$a$ haplotypes as the neo-W spreads.
+In B, this leads to loss of the neo-W and the system goes to an equilibrium with X$a$ and Y$A$ haplotypes fixed (A'), such that all females have the high fitness genotype $aa$ and all males $Aa$. 
+For the parameters in B, neo-W invasion fitness when the Y$A$ haplotype is ancestrally more common than Y$a$ (see blue line in Figure \ref{fig:temporalOverdominance}B). 
+In contrast, the neo-W is not lost in panel D. 
+Fitness parameters are the same as in Figure \ref{fig:temporalOverdominance}, the $a$ allele is favoured in females ($w_{aa}^\female=1.05$, $w_{Aa}^\Hermaphrodite=1$, $w_{AA}^\female=0.85$) and there is overdominant selection in males ($w_{aa}^\male=w_{AA}^\male=0.75$) in panels A and B.
+In panels C and D, selection in males and females is overdominant ($w_{aa}^\female=w_{AA}^\female=0.6$, $w_{aa}^\male=0.5$, $w_{AA}^\male=0.7$, $w_{Aa}^\Hermaphrodite=1$). 
+These parameters are marked by a dagger in Figure \ref{fig:regionplots}. 
+Here, there is no haploid selection $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
+}
+\label{fig:temporalOverdominance}
+\end{figure}
 

### 2017-08-23 LaTeX/Turnover.tex
updated text with new figures

@@
 %In addition, when linkage between the ancestral sex-determining locus and a locus under haploid selection is tight, sex ratio biases can be strong such that there is an asymmetry between invasion of ancestrally XY and ancestrally ZW systems because, e.g., haploid selection in males only causes biased zygotic sex ratios in an ancestrally XY system.
-With haploid selection, we again find that transitions between male and female heterogamety can occur even if the new sex-determining region is less closely linked to the locus under selection, and when linkage is tight haploid selection in the heterogametic sex can cause strong sex ratio bias, which may increase or decrease with the spread of new sex chromsomes.
-These results indicate that favourable associations that develop between the ancestral sex-determining locus and selected loci can be broken during the spread of a new sex-determining region. 
+With haploid selection, we again find that transitions between male and female heterogamety can occur even if the new sex-determining region is less closely linked to the locus under selection. 
+Haploid selection in the heterogametic sex can also cause sex ratio biases, which may increase or decrease with the spread of new sex chromosomes. 
+Thus, transitions between sex-determination systems cannot be simply predicted by selection to equalise the sex-ratio. 
+%These results indicate that loci experiencing haploid selection can favour the evolution of new sex-determination systems. 
+%These results indicate that favourable associations that develop between the ancestral sex-determining locus and selected loci can be broken during the spread of a new sex-determining region. 
 %Such transitions are not possible with diploid selection alone, in which case tighter linkage increases the fitness of both males and females. 
@@
 %Overall, we demonstrate when and how the evolution of sex determining systems is impacted by sex ratio biases resulting from haploid selection and we show that new sex-determining regions can be favoured even if they are not closely linked with a locus under selection.
-Overall, our models provide new predictions for the types of selection and the genomic location of loci that can drive transitions between sex-determination systems.
+Overall, our models reveal that transitions between sex-determination systems, particularly transitions where the heterogametic sex changes, can be driven by loci in unexpected genomic locations that experience selection during diploid and/or haploid phases, which might be reflected by the lability with which sex-determination systems evolve.
 %and for the factors determining the phylogenetic pattern of sex-determination systems.
@@
 In addition, many gonochoric clades with genetic sex determination exhibit transitions between male (XY) and female (ZW) heterogamety, including snakes \textcolor{red}{(Gamble et al.
-2017, Current Biology)}, lizards \citep{Ezaz:2009tk}, eight of 26 teleost fish families \citep{Mank:2006bt}, true fruit flies \citep[Tephritids,][]{Vicoso:2015hf}, amphibians \citep{Hillis:1990gu}, the angiosperm genus \textit{Silene} \citep{Slancarova:2013dq}, and Coleoptera and Hemiptera \citep[][plate 2]{Beukeboom:2014vb}.
-Indeed, in some cases, both male and female heterogametic sex-determination systems can be found in the same species, as exhibited by some cichlid species \citep{Ser:2010iq} and \textit{Rana rugosa} \citep{Ogata:2007jm}.
+2017, Current Biology)}, lizards \citep{Ezaz:2009tk}, eight of 26 teleost fish families \citep{Mank:2006bt}, true fruit flies \citep[Tephritids,][]{Vicoso:2015hf}, amphibians \citep{Hillis:1990gu}, the angiosperm genus \textit{Silene} \citep{Slancarova:2013dq}, \textcolor{red}{the angiosperm family \textit{Salicaceae} (Pucholt et al.
+2015, 2017),} and Coleoptera and Hemiptera \citep[][plate 2]{Beukeboom:2014vb}.
+Indeed, in some cases, both male and female heterogametic sex-determination systems can be found in the same species, as exhibited by some cichlid species \citep{Ser:2010iq} and \textit{Rana rugosa} \citep{Ogata:2007jm} \textcolor{red}{(Miura 2007)}.
 In addition, multiple transitions have occurred between genetic and environmental sex-determination systems, e.g., in reptiles and fishes \citep{Conover:1987in,Mank:2006bt,Pokorna:2009ui,Ezaz:2009tk,Pen:2010kk,Holleley:2015hc}.
@@
 %\textcolor{red}{We add haploid selection:}
-Here we extend current theory %on turnover between sex-determining systems 
-by using mathematical models to find the conditions under which new sex-determination systems spread when individuals experience selection at both diploid and haploid stages. 
+Here we use mathematical models to find the conditions under which new sex-determination systems spread when individuals experience selection at both diploid and haploid stages. 
 Even in animal and plant species that have much larger and more conspicuous diploid phases than haploid phases, many loci experience significant haploid selection through gamete competition and/or meiotic drive \citep{Mulcahy:1996ha,JOSEPH:2004haa}.
 We use the term `meiotic drive' to refer to the biased (non-Mendelian) segregation of genotypes during gamete production (from one parent) and the term `gametic competition' to refer to selection upon haploid genotypes within a gamete/gametophyte pool (potentially from multiple parents); the term `haploid selection' encompasses both processes.
-Meiotic drive generally occurs either during the production of male or female gametes only \citep{Ubeda:2005gw,Lindholm:2016cw}.
-Because there are typically many more pollen/sperm than required for fertilization, gametic competition is also typically sex specific, occurring primarily among male gametes.
-Gametic competition may be particularly common in plants, in which 60-70\% of all genes are expressed in the male gametophyte and these genes exhibit stronger signatures of selection than random genes \citep{Borg:2009jpa,Arunkumar:2013iq,Gossmann:2014dua}.
-In addition, artificial selection pressures applied to male gametophytes are known to cause a response to selection \citep[e.g.,][]{Hormaza:1996cv,Ravikumar:2003uo,Hedhly:2004iv,Clarke:2004ir}. 
-A smaller proportion of genes are thought to be expressed and selected during competition in animal sperm, although precise estimates are uncertain \citep{Zheng:2001fi,JOSEPH:2004haa,Vibranovski:2010et}.
-Recent studies have demonstrated that sperm competition can alter haploid allele frequencies and increase offspring fitness \citep{Immler:2014im} \textcolor{red}{(Alavioon et al. 2017). 
+\textcolor{red}{
 Genetic mapping experiments, which are typically designed to minimize selection in diploids, have revealed segregation distortion in various species, including mice, Drosophila, Rice, Maize, Wheat, Barley, Cotton...
-In some of these cases, biased segregation has been shown to be attributable to meiotic drive and/or gametic selection \textcolor{red}{(Leppala et al.
+In some of these cases, biased segregation has been attributed to meiotic drive and/or gametic selection \textcolor{red}{(Leppala et al.
 2013, Didion et al.
@@
 %Drosophila http://www.biorxiv.org/content/early/2017/02/06/106336
+Meiotic drive generally occurs either during the production of male or female gametes only \citep{Ubeda:2005gw,Lindholm:2016cw}.
+Because there are typically many more pollen/sperm than required for fertilization, gametic competition is also typically sex specific, occurring primarily among male gametes.
+Gametic competition may be particularly common in plants, in which 60-70\% of all genes are expressed in the male gametophyte and these genes exhibit stronger signatures of selection than random genes \citep{Borg:2009jpa,Arunkumar:2013iq,Gossmann:2014dua}.
+In addition, artificial selection pressures applied to male gametophytes are known to cause a response to selection \citep[e.g.,][]{Hormaza:1996cv,Ravikumar:2003uo,Hedhly:2004iv,Clarke:2004ir}. 
+A smaller proportion of genes are thought to be expressed and selected during competition in animal sperm, although precise estimates are uncertain \citep{Zheng:2001fi,JOSEPH:2004haa,Vibranovski:2010et}.
+Recent studies have demonstrated that sperm competition can alter haploid allele frequencies and increase offspring fitness \citep{Immler:2014im} \textcolor{red}{(Alavioon et al. 2017)}.
 
@@
 
-Our models have two important new features. 
-Firstly, when considering loci that are under selection and also in very tight linkage with the ancestral sex-determining region we explicitly calculate equilibrium allele frequencies.
-This allows us to show that transitions between male and female heterogamety can evolve even when the neo-sex-determining locus is less closely linked to a locus under selection and therefore disrupts favourable ancestral associations between sex and the alleles selected in that sex.
-%Such transitions are not favoured in models lacking tight linkage and/or haploid selection. 
-Secondly, we allow sex-specific haploid selection to occur on a locus in tight or loose linkage with the ancestral sex-determining region. 
+%Perhaps longer discussion of tight sex-linkage here? e.g., mention that r=0 is a particularly significant case for sex chromosomes.
+
 We find that sex-ratio biases caused by haploid selection can exert Fisherian sex-ratio selection upon novel sex-determiners but that their spread is also determined by selection on genetically-associated alleles.
@@
 Consequently, it is possible for selection on linked alleles to drive turnover between sex-determining systems despite causing transitory or even permanent increases in sex-ratio bias. 
+Another significant feature of our model is that we consider selection loci that are under selection and also in very tight linkage with the ancestral sex-determining region.
+Even in the absence of haploid selection, we show that transitions between male and female heterogamety can then evolve despite the fact that the neo-sex-determining locus is less closely linked to a locus under selection and therefore disrupts favourable ancestral associations between sex and the alleles selected in that sex.
+%Such transitions are not favoured in models lacking tight linkage and/or haploid selection. 
+%Secondly, we allow sex-specific haploid selection to occur on a locus in tight or loose linkage with the ancestral sex-determining region. 
 %In addition, when linkage between the ancestral sex-determining locus and a locus under haploid selection is tight, sex ratio biases can be strong such that there is an asymmetry between invasion of ancestrally XY and ancestrally ZW systems because, e.g., haploid selection in males only causes biased zygotic sex ratios in an ancestrally XY system.
@@
 \textcolor{red}{Change all  $\alpha^\Hermaphrodite$ to $(1+\alpha_{\Delta}^\Hermaphrodite)$.}
+
+\textcolor{red}{switch between $\chi$ and $\rho$ in all places because $\chi$ is used for double recombination events.}
+
+\textcolor{red}{Change $\zeta$ to represent zygotic sex ratio of males, consistent with $q$ and figures.}
 
@@
 With intermediate $k$, we can interpret $m$ as an environmental sex determination (ESD) allele, such that zygotes develop as females in a proportion ($k$) of the environments they experience. 
-We also analyze a model of maternally-controlled environmental sex-determination, where mothers with at least one $m$ allele produce daughters with probability $k$.
+%We also analyze a model of maternally-controlled environmental sex-determination, where mothers with at least one $m$ allele produce daughters with probability $k$.
 
@@
 Thus, the invasion of rare dominant neo-Y or neo-W alleles is determined by the largest eigenvalue that solves a quadratic characteristic polynomial,
+\textcolor{red}{Mention the possibility that the other roots yield the leading eigenvalue somewhere.}
 $\lambda^2+ b \lambda + c =0$.
@@
 
-The equilibrium allele frequencies and their stability conditions are given in the appendix, when there is complete linkage between the ancestral sex-determining region and the \textbf{A} locus ($r=0$).
-Here, either the $A$ allele or the $a$ allele must be fixed on the Y.
+The ancestral equilibrium allele frequencies and their stability conditions are given in the appendix.
+When there is complete linkage between the ancestral sex-determining region and the \textbf{A} locus ($r=0$), either the $A$ allele or the $a$ allele must be fixed on the Y. 
 % because selection on the Y is effectively haploid an incapably of maintaining a polymorphism in the absence of frequency dependent selection. 
-Because the labelling of alleles is arbitrary, we will assume that the $a$ locus is fixed on the Y ($p^\male_Y=0$), without loss of generality . 
-If there are two alleles maintained at the \textbf{A} locus, the X can either be fixed for the $A$ allele ($p^\female_X=p^\male_X=1$) or polymorphic (0<$p^\female_X, p^\male_X$<1). 
+Because the labelling of alleles is arbitrary, we will assume that the $a$ locus is fixed on the Y ($p^\male_Y=0$), without loss of generality. 
+If there are two alleles maintained at the \textbf{A} locus, the X can either be fixed for the $A$ allele ($\hat{p}^\female_X=\hat{p}^\male_X=1$) or polymorphic (0<$\hat{p}^\female_X, \hat{p}^\male_X$<1).
 %However, because the X is present in both males and females, there are distinct selection pressures on X's in females and X's in males, which will always be paired with an $A$ allele from the Y.
@@
 
-\textcolor{red}{Sally edits only looked at up to this point. Next task: figures to match with this tight linkage section.}
-
 %\textcolor{blue}{
-%Briefly, the neo-W invades under the ancestral XY sex-determining system, the X chromosome may not be able to as specialised on a female-beneficial allele
-%The full characteristic polynomials are given in the appendix (equations \ref{Binvasion} and \ref{Ainvasion}).
 Neo-W alleles, on the other hand, can invade an ancestral XY system under some conditions (the full invasion conditions are given in the appendix; equations \ref{Binvasion} and \ref{Ainvasion}). 
-Significantly, we note that it is possible for both neo-W haplotypes to spread ($\lambda_{mA}>1$ and $\lambda_{ma}>1$), in which case neo-W invasion can occur regardless of linkage to the selected locus.
-That is, selection on loci within the non-recombining region of the SDR can favour the invasion of a less closely linked neo-W (e.g., on an autosome). 
-Although haploid selection can favour neo-W alleles because the ancestral sex ratio becomes male biased, this is not the only circumstance in which less tightly linked neo-W alleles invade. 
-For example, unlinked neo-W alleles can invade in the absence of any haploid selection. 
+That is, selection on loci within the non-recombining region of the SDR can favour the invasion of a less closely linked neo-W, see Figure \ref{fig:SexAntagTighter}. 
+%Although haploid selection can favour neo-W alleles because the ancestral sex ratio becomes male biased, this is not the only circumstance in which less tightly linked neo-W alleles invade. 
+%\textcolor{red}{Sally: unpack, give one condition and relate to figures}
+%For example, we note that it is possible for both neo-W haplotypes to spread ($\lambda_{mA}>1$ and $\lambda_{ma}>1$), in which case neo-W invasion can occur regardless of linkage to the selected locus.
+%For example, unlinked neo-W alleles can invade in the absence of any haploid selection. 
 This result is unexpected given the results of \cite{vanDoorn:2010hu}, who did not explicitly calculate equilibrium allele frequencies under tight linkage and generally concluded that heterogametic transitions occur when neo-sex-determining alleles are in tighter linkage with loci under sex-specific diploid selection.
-Therefore, we focus on cases where there is no haploid selection and discuss the effects of haploid selection in the appendix. 
-%}
+To develop an understanding (intuition) for how this happens, we focus on cases where there is no haploid selection and discuss the effects of haploid selection in the appendix. 
+%}
+%Briefly, a neo-W can spread when the females it produces have higher fitness than the females produced under the ancestral SDR, which all have genotype XX.
+X chromosomes are sometimes found in males and therefore allele frequencies on the X can be suboptimal for females.
+In addition, the neo-W produces females from matings with Y-bearing male gametes.
+The allele associated with the Y can also be beneficial in females.
+%the neo-W invades under the ancestral XY sex-determining system, the X chromosome may not be able to as specialised on a female-beneficial allele
 
@@
 In panel A, linkage is loose enough relative to selection that the weak selection analytical results hold, and a neo-W can only invade when it is more tightly linked with the selected locus ($R<r$; shaded region).
-In panel B, linkage is tight enough relative to selection that the weak selection analytical results do no hold, and a neo-W can only invade even when it is less tightly linked with the selected locus ($r<R$; unshaded region).
+In panel B, linkage is tight enough relative to selection that the weak selection analytical results do not hold, and a neo-W can only invade even when it is less tightly linked with the selected locus ($r<R$; unshaded region).
 In panel C we vary the recombination rate between the neo-W and the selected locus ($R$) for a fixed recombination rate between the ancestral-SDR and the selected locus ($r=0.005$). 
@@
 A very loosely linked neo-W does not spread in this case (blue and green lines overlap and go to 0).
+Indeed, we show that neo-W invasion fitness is negative when $R=1/2$ and $s^\female s^\male<0$, $0<h^\Hermaphrodite<1$) in the supplementary \textit{Mathematica} file.
 Fitness parameters are shown by an asterisk in Figure \ref{fig:regionplots}: $w_{AA}^\female = 1.05$, $w_{aa}^\male = 1.2$, $w_{aa}^\female = w_{AA}^\male = 0.85$, $w_{Aa}^\Hermaphrodite = 1$.
+\textcolor{red}{consider removing panel A, which is repeated in Figure 3.}
 }
@@
 
-%\textcolor{blue}{
 If we categorise the $a$ allele as being ancestrally `male-beneficial' via the fact that it is fixed on the Y, then $\lambda_{mA}>1$ indicates that the neo-W spreads when found with the ancestrally `female-beneficial' allele.
-Intuitively, this is possible because the ancestral X chromosome is not able to specialise on the `female-beneficial' allele due to the fact that X's are sometimes found in males. 
-For example, a polymorphism of $A$ and $a$ alleles can be maintained on the X despite directional selection in favour of the $A$ allele in females ($s^\female>0$, $0<h^\female<1$) because the $a$ allele is favoured in males.
-W-$A$ haplotypes will only create females with high fitness $AA$ or $Aa$ genotypes and can therefore have higher fitness than ancestral females, which sometimes also produce $aa$ females. 
-Thus, the neo-W can spread by allowing increased specialization on female beneficial alleles.
-%As another example, $AA$ individuals can have low fitness in females and yet the $A$ can be fixed on the X due to strong overdominance in males favouring X$A$Y$a$ males. 
-%In this case, W$A$ haplotypes produce fewer unfit $AA$ females because they produce some females through matings with Y$a$-bearing sperm. 
-%}
-
-%\textcolor{blue}{
-Given that the $a$ allele can be considered ancestrally `male-beneficial' because it is fixed on the Y, it might be surprising that neo-W-$a$ haplotypes can be favoured by selection in females ($\lambda_{ma}>1$).
+Broadly, this is possible because the ancestral X chromosome is not able to perfectly specialise on the `female-beneficial' allele due to the fact that X's are sometimes found in males. 
+For example, when the $a$ allele is favoured in males, a polymorphism of $A$ and $a$ alleles can be maintained on the X despite directional selection in favour of the $A$ allele in females ($s^\female>0$, $0<h^\female<1$).
+Indeed, Figure \ref{fig:regionplots}A indicates that $\lambda_{mA}$ tends to be larger than one with sexually-antagonistic selection where the $a$ allele is strongly favoured in males ($w_{aa}$ much larger than $w_{Aa}$).
+In this case, W-$A$ haplotypes will only create females with high fitness ($AA$ or $Aa$ genotypes) and therefore have higher fitness than ancestral females, which sometimes also produce $aa$ females. 
+When only one neo-W haplotype can has a positive growth rate (see Figure \ref{fig:regionplots}), a neo-W can invade as long as equation \eqref{eq:lambdasGen} is satisfied, which may require that the recombination rate, $R$, is small enough.
+Nevertheless, because we assume here that $r$ is small, these results indicate that a more loosely linked sex-determining region can spread.
+Therefore, tightly sex-linked loci that experience sexually-antagonistic selection can drive heterogametic transitions in which the neo-SDR is less closely linked to the locus under selection (Figure \ref{fig:SexAntagTighter}).
+%Prediction (just an idea), considering sexually antagonistic selection alone, we should observe an excess of transitions between XY and ZW systems on the same chromosome because the tight linkage results indicate that there can be selection for heterogametic transitions but only when the neo-SDR is relatively closely linked (but not necessarily more closely linked).
+
+Given that the $a$ allele can be considered ancestrally `male-beneficial' because it is fixed on the Y, it is surprising that neo-W-$a$ haplotypes can sometimes be favoured by selection in females ($\lambda_{ma}>1$).
 Again, this occurs because ancestral X's also experience selection in males, in which they will always be paired with a Y-$a$. 
 Hence, if there is overdominance in males, X-$A$ Y-$a$ males have high fitness and the $A$ allele is favoured by selection on the X in males. 
-Therefore, the X can be polymorphic or even fixed for the $A$ allele despite favouring the $a$ allele during selection in females \citep{Lloyd1977,Otto2014}. 
-In such cases, neo-W-$a$ haplotypes, which are never found in males, can spread because they both create more $Aa$ and $aa$ females when pairing with an X from males and they bring Y-$a$ haplotypes into females, in which case females are always $aa$.
-Indeed, it is possible for both W-$A$ and W-$a$ haplotypes to spread, as is the case when $AA$ individuals have low fitness in females yet the $A$ is fixed on the X due to strong overdominance in males.
+Therefore, the X can be polymorphic or even fixed for the $A$ allele despite favouring the $a$ allele during selection in females \citep[e.g., see outlined region in Figure \ref{fig:regionplots}B and][]{Lloyd1977,Otto2014}.
+In such cases, neo-W-$a$ haplotypes can spread because they create more $Aa$ and $aa$ females when pairing with an X from males and because they bring Y-$a$ haplotypes into females, in which case females are always $aa$.
+As discussed in the appendix, this scenario where neo-W's associated with $a$ are favoured can also occur with haploid selection, even without overdominance (e.g., when $a$ is female-beneficial and favoured by haploid selection in male gametes).
+
+Both W-$A$ and W-$a$ haplotypes can spread, as is the case when $AA$ individuals have low fitness in females yet the $A$ is polymorphic or fixed on the X due to overdominance in males (Figure \ref{fig:regionplots}B and \ref{fig:regionplots}C).
 Both neo-W-$A$ and neo-W-$a$ haplotypes then produce fewer unfit $AA$ females.
 This is true for the neo-W-$A$ haplotype because it can pair with a $Y-a$ haplotype and still be female. 
-%}
-
-%\textcolor{blue}{
-In Figure \ref{fig:regionplot_2a}A we show the region of parameter space within which both neo-W haplotypes invade ($\lambda_{mA}>1$ and $\lambda_{ma}>1$) when there is overdominance in females and no haploid selection \citep[corresponding to Figure 2a in][]{Otto2014}.
-Wherever both haplotypes have positive growth rates (gray region of Figure \ref{fig:regionplot_2a}), invasion by a neo-W is expected regardless of its linkage with the selected locus (i.e., even unlinked neo-W alleles can invade).
-In regions where only one haplotype can spread (white region of Figure \ref{fig:regionplot_2a}), a neo-W can invade as long as equation \eqref{eq:lambdasGen} is satisfied, which can require that the recombination rate, $R$, is small enough and yet still indicates that more loosely linked sex-determining regions can spread.
-It is also possible for haploid selection to drive the invasion of a loosely linked neo-W. 
-Take, for instance, selection directionally favouring $A$ in both diploid sexes and meiotic drive in males.
-Figure \ref{fig:regionplot_2a}B then shows that ploidally-antagonistic selection can allow both neo-W haplotypes to invade. 
-%}
+Wherever both haplotypes have positive growth rates, invasion by a neo-W is expected regardless of its linkage with the selected locus (i.e., even unlinked neo-W alleles can invade, see Figures \ref{fig:positionOverdominance} and \ref{fig:temporalOverdominance} for examples).
+
+\textcolor{red}{
+What can we discuss about haploid selection here. Perhaps the fact that overdominance is not required for $\lambda_{Ma}>1$ when there is haploid selection?
+We also don't yet discuss the fact that polymorphic equilibria (mixed systems) can be stable. 
+}
 
@@
 When the ancestral-XY locus is tightly linked to a locus under selection ($r=0$), one or both neo-W haplotypes can spread. 
-We vary the fitness of male homozygotes relative to heterozygotes ($w_{Aa}^\Hermaphrodite=1$) and only consider stable equilibria at which the $a$ allele is initially fixed on the Y, as indicated. 
+We vary the fitness of male homozygotes relative to heterozygotes ($w_{Aa}^\Hermaphrodite=1$) and only consider stable equilibria at which both \textbf{A} locus alleles are maintained and the $a$ allele is initially fixed on the Y, region outlined.
 Here, selection in females can favour the $A$ allele (panel A, $w_{aa}^\female=0.85$, $w_{AA}^\female=1.05$), favour the $a$ allele (panel B, $w_{aa}^\female=1.05$, $w_{AA}^\female=0.85$), or be overdominant (panel C, $w_{aa}^\female=w_{AA}^\female=0.6$).
@@
 %The equilibrium frequency of $A$ on different ancestral backgrounds ($\hat{p}^\male_Y$, $\hat{p}^\male_X$, and $\hat{p}^\female_X$) is given by equations \eqref{eq:pAve} and \eqref{eq:freq_diffs} where we assume selection and meiotic drive are weak relative to recombination ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon$).
-Assuming that selection is weak relative to all recombination rates ($r$, $R$ and $\chi$), we denote the leading eigenvalues describing the invasion of a neo-Y ($k=0$) and a neo-W ($k=1$) into an ancestrally XY system by $\lambda_{Y',XY}$ and $\lambda_{W',XY}$, respectively, which are
+Assuming that selection is weak relative to all recombination rates ($r$, $R$ and $\chi$), we denote the leading eigenvalues describing the invasion of a neo-Y ($k=0$) and a neo-W ($k=1$) into an ancestrally XY system by $\lambda_{Y',XY}$ and $\lambda_{W',XY}$, respectively.
+To leading order in selection, these are:
 
@@
 The neo-sex-determining allele, $m$, will spread if $\lambda_{m,XY}>1$. 
-Equation \eqref{eq:lambda_neoY} demonstrates that under weak selection a neo-Y will invade an XY system if and only if it is more closely linked to the selected locus than the ancestral sex-determining region (i.e., if $R<r$; note that $V_{A}$ and $S_{A}^2$ are strictly positive as long as \textbf{A} is polymorphic).
-This echoes our tight linkage results above and the results of \citet{vanDoorn:2007eu}, who considered diploid selection only and also found that homogametic transitions (XY to XY or ZW to ZW) can only occur when the neo-sex-determining locus is more closely linked to a locus under sexually-antagonistic selection.
+Equation \eqref{eq:lambda_neoY} demonstrates that under weak selection a neo-Y will invade an XY system if and only if it is more closely linked to the selected locus than the ancestral sex-determining region (i.e., if $R<r$; note that $V_{A}S_{A}^2$ is strictly positive as long as \textbf{A} is polymorphic).
+This echoes our tight linkage results above where a neo-Y could never invade if $r\approx0$ and is consistent with the results of \citet{vanDoorn:2007eu}, who considered diploid selection only and also found that homogametic transitions (XY to XY or ZW to ZW) can only occur when the neo-sex-determining locus is more closely linked to a locus under sexually-antagonistic selection.
 %Because tighter linkage between the sex-determining region and a selected locus evolves during these transitions, stronger associations between selected alleles and diploid sexes can build up by selection (e.g., between male-beneficial alleles and the male-determining allele, Y).%, increasing diploid mean fitness (Figure \ref{fig:Combination_MeanFit}).
 
-Equation \eqref{eq:lambda_neoW} shows that, in contrast to the tight linkage results of the previous section, with weak selection and no haploid selection ($t^\Hermaphrodite=\alpha^\Hermaphrodite_{\Delta}=0$), as considered by \citet{vanDoorn:2010hu}, the spread of a neo-W is equivalent to the spread of a neo-Y ($\lambda_{W',XY}=\lambda_{Y',XY}$), such that heterogametic transitions (XY to ZW or ZW to XY) can also occur only if the neo-sex-determining region is more closely linked to a locus under selection ($R<r$).
-However, if there is any haploid selection, the additional term in equation \eqref{eq:lambda_neoW} can be positive, which can allow, for example, neo-W invasion ($\lambda_{W',XY}>1$) even when the neo-sex-determining region is less closely linked to the selected locus ($R>r$).
-These transitions are unusual because, when $R>r$, associations that selection has built up between alleles more favourable in one sex and alleles that determine sex will be weakened. 
-Mean diploid fitness therefore decreases during heterogametic transitions that create looser sex-linkage (Figure \ref{fig:Combination_MeanFit}B,D).
+With weak selection and no haploid selection ($t^\Hermaphrodite=\alpha^\Hermaphrodite_{\Delta}=0$), the spread of a neo-W is equivalent to the spread of a neo-Y ($\lambda_{W',XY}=\lambda_{Y',XY}$), such that heterogametic transitions (XY to ZW or ZW to XY) can also occur only if the neo-sex-determining region is more closely linked to a locus under selection ($R<r$), as found by \citet{vanDoorn:2010hu}.
+With haploid selection, however, the additional term in equation \eqref{eq:lambda_neoW} can be positive, which can allow, for example, neo-W invasion ($\lambda_{W',XY}>1$) even when the neo-sex-determining region is less closely linked to the selected locus ($R>r$).
+%These transitions are unusual because, when $R>r$, associations that selection has built up between alleles more favourable in one sex and alleles that determine sex will be weakened. 
+%Mean diploid fitness therefore decreases during heterogametic transitions that create looser sex-linkage (Figure \ref{fig:Combination_MeanFit}B,D).
 
@@
 In panel B, male drive ($\alpha^\male_{\Delta} = -1/20$, $t^\Hermaphrodite = \alpha^\female_{\Delta} = 0$) opposes selection in diploids (no sex-differences: $s^\Hermaphrodite = 1/10$, $h^\Hermaphrodite = 7/10$), in which case the neo-sex-determining allele can invade regardless of linkage.
-In panel C, haploid competition in males ($t^\male = -1/10$, $t^\female = \alpha^\Hermaphrodite_{\Delta} = 0$) opposes selection in diploids (sex-differences: $s^\male = 3 s^\female = 3/20$, $h^\Hermaphrodite = 7/10$), in which case the neo-sex-determining allele can once again invade regardless of linkage.
+In panel C, gametic competition in males ($t^\male = -1/10$, $t^\female = \alpha^\Hermaphrodite_{\Delta} = 0$) opposes selection in diploids (sex-differences: $s^\male = 1/20$, $s^\female = 3/20$, $h^\Hermaphrodite = 7/10$), in which case the neo-sex-determining allele can once again invade regardless of linkage.
 We use Haldane's map function \citep[Equation 3 in ][]{Haldane1919} to convert from map distance (centiMorgans, cM) to the probability of recombination (an odd number of cross-over events).   
+\textcolor{red}{Check the mismatch between red and black lines here: probably because of adding or subtracting from 1. }
 }
@@
 To clarify the parameter space under which $\lambda_{W',XY}>1$, we consider several special cases. 
-Firstly, if the \textbf{A} locus is unlinked to the ancestral sex-determining region ($r=1/2$), a more closely linked neo-W ($R<1/2$) can always invade because there is then no association between $A$ alleles and sex chromosomes, $\left( \hat{p}^\male_Y-\hat{p}^\male_X \right)=0$.
+Firstly, if the \textbf{A} locus is unlinked to the ancestral sex-determining region ($r=1/2$), a more closely linked neo-W ($R<1/2$) can always invade because there is then no association between $A$ alleles and sex chromosomes in males, $\left( \hat{p}^\male_Y-\hat{p}^\male_X \right)=0$, see equation \eqref{eq:freq_diffs}.
 The second term in equation \eqref{eq:lambda_neoW} then disappears and invasion depends only on the sign of $(r-R)$. 
 Indeed, invasion typically occurs when the neo-W is more closely linked to the selected locus than the ancestral sex-determining region, under a variety of selective regimes (Figure \ref{fig:Combination_Centimorgans}).
-Secondly, we can simplify cases where invasion occurs despite looser sex-linkage, $R>r$, using the special case where $R=1/2$ and $r<1/2$ (e.g., the selected locus is on the ancestral sex chromosome and the novel sex-determining locus arises on an autosome).
+Secondly, we can simplify the discussion of cases where invasion occurs despite looser sex-linkage, $R>r$, by focussing on the special case where $R=1/2$ and $r<1/2$ (e.g., the selected locus is on the ancestral sex chromosome and the novel sex-determining locus arises on an autosome).
 In table \ref{tab:specialcases} we give the conditions where invasion occurs when we further assume that haploid selection only occurs in one sex (e.g., during male meiosis only) and dominance coefficients are equal in the two sexes, $h^\female=h^\male$.
-When there is no gametic competition and meiotic drive is in one sex only, an unlinked neo-W can invade as long as the same allele is favoured during diploid selection in males and females ($s^\female s^\male>0$, see Figure \ref{fig:Combination_Centimorgans}B).
+When there is no gametic competition and meiotic drive is in one sex only, an unlinked neo-W can invade as long as the same allele is favoured during diploid selection in males and females ($s^\female s^\male>0$, see Figure \ref{fig:Combination_Centimorgans}B and Figure \ref{fig:SexRatioBad}B).
 %, which is 50\% of the parameter space.
-When there is no meiotic drive and gametic competition occurs in one sex only, an unlinked neo-W can invade as long as the same allele is favoured in male and female diploid selection and there are sex differences in selection of one type (e.g., $s^\female(s^\male-s^\female)>0$, see Figure \ref{fig:Combination_Centimorgans}C,D).
+When there is no meiotic drive and gametic competition occurs in one sex only, an unlinked neo-W can invade as long as the same allele is favoured in male and female diploid selection and there are sex differences in selection of one type (e.g., $s^\female(s^\male-s^\female)>0$, see Figure \ref{fig:Combination_Centimorgans}C).
 %, which is 25\% of the parameter space.
-These special cases indicate that neo-W invasion can occur for a relatively large fraction of parameter space, even if the neo-W uncouples the sex-determining locus from a locus under selection.
+These special cases indicate that neo-W invasion can occur for a relatively large fraction of the parameter space, even if the neo-W uncouples the sex-determining locus from a locus under selection.
 
@@
 Previous research suggests that when the ancestral sex-determining locus is linked to a locus that experiences haploid selection (e.g., meiotic drive), a new, unlinked sex-determining locus invades in order to restore equal sex ratios \citep{Kozielska:2010vm}.
-Consider, for example, the case where the \textbf{A} locus is linked to the ancestral-SDR ($r<1/2$) and experiences meiotic drive in males only (e.g., during spermatogenesis but not during oogenesis, $\alpha^\male \neq 1/2$, $\alpha^\female=1/2$).
-Disregarding gametic competition ($t^\female=t^\male=0$) such that zygotic sex ratios are only biased by meiotic drive in males. 
-In this case, the zygotic sex ratio can be initially biased only if the ancestral sex-determining system is XY (Figure \ref{fig:Combination_Turnover}B). 
+Consider, for example, the case where the \textbf{A} locus is linked to the ancestral-SDR ($r<1/2$) and experiences meiotic drive in males only (e.g., during spermatogenesis but not during oogenesis, $\alpha^\male_\Delta \neq 0$, $\alpha^\female_\Delta=0$), without gametic competition ($t^\female=t^\male=0$).
+In this case, the zygotic sex ratio can be initially biased only if the ancestral sex-determining system is XY (Figure \ref{fig:SexRatioBad}B). 
 %If the ancxestral sex-determining system is ZW, the zygotic sex ratio will be 1:1 because diploid sex is determined by the proportion of Z-bearing versus W-bearing eggs and meiosis in females is fair (Figure \ref{fig:Combination_Turnover}D).
 We might therefore expect a difference in the potential for XY to ZW and ZW to XY transitions. 
-However, to leading order with selection weak relative to recombination, we find that sex ratio selection (first terms in table \ref{tab:haplotype_growth}) is equal in magnitude to the fitness effects of alleles associated with new sex-determining alleles (second terms in table \ref{tab:haplotype_growth}).
-Thus, invasion by a neo-W into an XY system and invasion by a neo-Y into a ZW system occur under the same conditions ($\lambda_{Y',XY}=\lambda_{W',ZW}$ and $\lambda_{Y',ZW}=\lambda_{W',XY}$, at least up to order $\epsilon^2$).
-As selection becomes stronger (or linkage becomes tighter), this symmetry between sex-ratio selection and haploid selection is lost, causing differences in the strength of selection favouring the two heterogametic transitions (compare red to black near -25cM and 25 cM in Figure \ref{fig:Combination_Centimorgans}).
+However, to leading order with selection weak relative to recombination, we find that sex ratio selection favours the spread of a neo-W (through the first terms in table \ref{tab:haplotype_growth}) by an amount that is equal in magnitude to the fitness effects of alleles associated with new sex-determining alleles (second terms in table \ref{tab:haplotype_growth}).
+Thus, invasion by a neo-W into an XY system and invasion by a neo-Y into a ZW system occur under the same conditions ($\lambda_{Y',XY}=\lambda_{W',ZW}$ and $\lambda_{Y',ZW}=\lambda_{W',XY}$, at least to order $\epsilon^2$).
+For example, in Figure \ref{fig:SexRatioBad}B neo-W alleles invade an ancestrally XY system where females are initially rare because the ancestral-Y is associated with a male meiotic drive allele.
+However, Figure \ref{fig:SexRatioBad}A shows that a neo-Y can invade an ancestrally ZW system under the same conditions. 
+In fact, where $R<1/2$ the neo-Y becomes associated with the male meiotic drive allele such that the zygotic sex ratio evolves to become biased towards males.
+
+%As selection becomes stronger (or linkage becomes tighter), this symmetry between sex-ratio selection and haploid selection is lost, causing differences in the strength of selection favouring the two heterogametic transitions (compare red to black near -25cM and 25 cM in Figure \ref{fig:Combination_Centimorgans}).
+\textcolor{red}{normalise fitness in sexually antagonistic case}
 
@@
 In this figure, selection is ploidally antagonistic with haploid selection favouring the $a$ allele during male meiosis ($s^\female =s^\male = 0.2$, $h^\female = h^\male = 0.7$, $t^\female = t^\male = \alpha^\male_\Delta = 0$).
-In panel A, male drive in an ancestral ZW system has no affect on the sex ratio, yet a neo-Y can invade and replace the ancestral sex-determination system (see inset, the ancestral W also fixes). 
-In this case, the neo-Y becomes associated with the allele favoured by drive, causing the zygotic sex ratio to become biased, hence the frequency of neo-Y among male gametes can be higher than $0.5$ (inset).
-In panel B, male drive in an ancestral XY system causes a male bias, allowing a neo-W to invade and replace the ancestral sex-determination system (see inset, the ancestral Y also fixes), which balances the sex ratio.
+In panel A, male drive in an ancestral ZW system has no affect on the zygotic sex ratio, yet a neo-Y can invade and replace the ancestral sex-determination system (inset shows neo-Y frequency among male gametes, the ancestral W also goes to fixation during this transition).
+When $R<1/2$, the neo-Y becomes associated with the allele favoured by drive, causing the zygotic sex ratio to become biased, hence the frequency of neo-Y among male gametes can be higher than $0.5$ (inset).
+In panel B, male drive in an ancestral XY system causes a male bias, allowing a neo-W to invade and replace the ancestral sex-determination system (inset shows neo-W frequency among female gametes, the ancestral Y also goes to fixation), which balances the zygotic sex ratio.
 Parameters:  $s^\female =s^\male = 0.2$, $h^\female = h^\male = 0.7$, $t^\female = t^\male = \alpha^\male_\Delta = 0$, $\alpha^\male_\Delta = -0.2$, $r=0.02$.
@@
 
+The green curves in Figure \ref{fig:SexRatioBad} demonstrate a case where transitions between male and female heterogametey occur even though the new sex-determining region is unlinked to a locus that experiences haploid and diploid selection.
+We use this example to discuss why heterogametic transitions can occur when $R=1/2$ and $r<1/2$, as in Table \ref{tab:specialcases}.
+In Figure \ref{fig:SexRatioBad}B, an unlinked neo-W can spread because the zygotic sex ratio is ancestrally male biased. 
+However, in Figure \ref{fig:SexRatioBad}A, an unlinked neo-Y spreads despite the fact that the ancestral zygotic sex ratio is even. 
+In this case, the the male meiotic drive allele, $a$, is initially more common among ancestral-Z-bearing eggs than ancestral-W-bearing eggs because the Z is found in males more often than the W and $r<1/2$ (equation \ref{eq:freq_diffs}).
+%In this case, the ancestral male determining allele, Z, is initially associated with the male meiotic drive allele, $a$, because the Z is found in males more often than the W and $r<1/2$. 
+Polymorphism at the \textbf{A} locus is maintained by counter-selection against the $a$ allele in diploids and therefore ancestral-ZZ males have generally low diploid fitness. 
+A freely recombining neo-Y ($R=1/2$) is not directly favoured or dis-favoured by male meiotic drive because it is equally likely to be segregate with the $A$ or $a$ allele when found in a heterozygote.
+The neo-Y spreads because it produces males with high diploid fitness through matings with ancestral-W-bearing female gametes, which are more likely to carry the $A$ allele. 
+Thus, a key factor in explaining why heterogametic transitions can occur when $R>r$ is that that the neo-SDR determines sex in the diploid phase but then recombination occurs before any subsequent haploid selection.
+
 %Therefore Fisherian sex ratio selection directly favours neo-Ws by a similar magnitude. 
@@
 
-We next consider the case where the new sex-determining mutation, $m$, causes sex to be determined probabilistically or by heterogeneous environmental conditions (environmental sex determiner, ESD). 
-We assume that individuals carrying the $m$ allele develop as females with probability $k$ (e.g., in a fraction $k$ of the environments they randomly experience).
-The characteristic polynomial determining the eigenvalues of the 8 equation system (equations \ref{eq:recursions}) does not reduce for ESD mutants as it does for $k=0$ or $k=1$. 
+We next consider the case where the new sex-determining mutation, $m$, causes sex to be determined probabilistically or by heterogeneous environmental conditions (environmental sex determination, ESD), with individuals carrying allele $m$ developing as females with probability $k$.
+Here, we do not assume that the environmental conditions that determine sex also differentially affect the fitness of males versus females. 
+Such correlations can favour environmental sex-determination systems that allow each sex to be produced in the environment in which it has highest fitness; in the absence of these correlations, previous theory would predict that ESD is favoured when it produces more equal sex ratios than the ancestral system \citep[see reviews by][]{Charnov:1982wg,Bull:1983vi,West:2009we}.
+%(e.g., maternal condition, mate quality, age, or host size)
+
+The characteristic polynomial determining the eigenvalues (equations \ref{eq:recursions}) does not factor for ESD mutants as it does for $k=0$ or $k=1$. 
 We therefore focus on weak selection here. 
-Assuming weak selection, the spread of these mutations is given by
+Assuming weak selection, the spread of the new sex-determining region is given by
 
@@
 \begin{equation}
-\lambda_{ESD',XY} =1+ \frac{1}{2}\frac{(\lambda_{Y',XY}-1) + (\lambda_{W',XY}-1)}{2} \Big|_{R=1/2} + O\left(\epsilon^3\right),
+\lambda_{ESD',XY} =1+ \frac{1}{2}\frac{(\lambda_{Y',XY\rvert R=1/2}-1) + (\lambda_{W',XY\rvert R=1/2}-1)}{2} + O\left(\epsilon^3\right),
 %V_A \frac{r}{1-2r}  \frac{s_{f} \left( s^\male - 3 s^\female\right) }{8 \left( s_{f} + s_{m} \right)^2} t_{m}^2.
@@
 \noindent
-where we have indicated that $\lambda_{Y',XY}$ and $\lambda_{W',XY}$ are evaluated at $R=1/2$.
+where $\lambda_{Y',XY\rvert R=1/2}$ and $\lambda_{W',XY\rvert R=1/2}$ represent $\lambda_{Y',XY}$ and $\lambda_{W',XY}$ when evaluated at $R=1/2$ (equations \ref{eq:lambda_neoY} and \ref{eq:lambda_neoW}).
 That is, recombination between the selected locus and the novel sex-determining locus, $R$, doesn't enter into the $k=1/2$ results.
@@
 preventing associations from building up between allele $A$ and sex. 
-An important result from equation \eqref{eq:lambda_ESD} is that ESD can invade if there is haploid selection. 
-When evaluated at $R=1/2$, $\lambda_{Y',XY} \leq 1$ but $\lambda_{W',XY}$ can be greater than one if there is haploid selection, as discussed above. 
-Previous studies where ESD is favoured have typically assumed that environmental conditions (e.g., maternal condition, mate quality, age, or host size) can differentially affect the fitness of males versus females such that ESD invades because it allows sex determination to depend on the environment \citep[reviewed in][]{Charnov:1982wg,Bull:1983vi,West:2009we}.
-Here, ESD mutations can spread because they generate females that are either rare or have high fitness, in the same manner as a neo-W.
-
-Equation \eqref{eq:lambda_ESD} also shows that invasion by a novel `perfect' ESD (equal sex ratio, $k=1/2$) mutation is the same for an ancestrally XY or ZW system (since $\lambda_{Y',XY} = \lambda_{W',ZW}$, $\lambda_{W',XY} = \lambda_{Y',ZW}$).
-Thus, by the same argument as above (if drive only occurs in males then the sex ratio is only biased when the ancestral sex-determination system is XY), Fisherian sex-ratio selection alone does not explain the invasion of an offspring-controlled neo-ESD allele under weak selection.
-Rather, the neo-ESD gets half of the fitness of a feminizing mutation (neo-$W$) and half of the fitness of a masculinizing mutation (neo-$Y$), but only has an effect one half of the time (the other half of the time it produces the same sex as the ancestral system would have, to leading order).
-The net result can be that perfect ESD will not invade, even if current sex ratios are biased. 
-For example, if there is haploid selection in males (either drive or pollen/sperm competition) but the conditions in table \ref{tab:specialcases} are not met, perfect ESD will not invade, even though it would equalize the zygotic sex ratio from an initially biased case (assuming $r<1/2$).
+Equation \eqref{eq:lambda_ESD} shows that the neo-ESD gets half of the fitness of a feminizing mutation (neo-$W$) and half of the fitness of a masculinizing mutation (neo-$Y$), but only has an effect one half of the time (the other half of the time it produces the same sex as the ancestral system would have, to leading order).
+As discussed above, $\lambda_{Y',XY\rvert R=1/2}$ is necessarily less than one, but $\lambda_{W',XY\rvert R=1/2}$ can be greater than one if there is haploid selection.
+That is, when there is haploid selection, ESD mutations can invade an ancestrally-XY system because they generate females that are either rare or have high fitness, in the same manner as a neo-W.
+
+%An important result from equation \eqref{eq:lambda_ESD} is that ESD can invade if there is haploid selection. 
+%When evaluated at $R=1/2$, $\lambda_{Y',XY}$ is necessarily less than one, but $\lambda_{W',XY}$ can be greater than one if there is haploid selection, as discussed above. 
+%Previous studies where ESD is favoured have typically assumed that environmental conditions (e.g., maternal condition, mate quality, age, or host size) can differentially affect the fitness of males versus females such that ESD invades because it allows sex determination to depend on the environment \citep[reviewed in][]{Charnov:1982wg,Bull:1983vi,West:2009we}.
+%Here, ESD mutations can spread because they generate females that are either rare or have high fitness, in the same manner as a neo-W.
+
+Significantly, equation \eqref{eq:lambda_ESD} is the same whether ESD is invading an ancestrally XY or ZW system (because $\lambda_{Y',XY} = \lambda_{W',ZW}$ and $\lambda_{W',XY} = \lambda_{Y',ZW}$).
+Thus, because the sex ratio is only biased by male haploid selection when the ancestral sex-determination system is XY, Fisherian sex-ratio selection alone does not explain the invasion of ESD under weak selection.
+Specifically, with male haploid selection, the neo-ESD is equally likely to invade when it equalizes the zygotic sex ratio (through $\lambda_{W',XY}$) and when it doesn't (through $\lambda_{Y',ZW}$). 
+%This is again because haploid selection can facilitate the turnover of sex chromosomes either through sex ratio biases or through associations between the new sex determining region with selected alleles.
+%With weak selection, these two forces are nearly equal in strength. 
+In addition, we note that ESD may not invade, even if the sex ratio is initially biased (e.g., with drive in males only, $r<1/2$, $h^\female=h^\male$, and $s^\female s^\male<0$, such that $\lambda_{W',XY}<1$, see Table \ref{tab:specialcases}).
 
@@
 The former predicts that neo-sex-determining alleles can invade when they arise in closer linkage with a sexually-antagonistic locus \citep{vanDoorn:2007eu,vanDoorn:2010hu}.
-The latter predicts that neo-W alleles will invade an XY system when there is a male bias caused by haploid selection in males, and vice-versa, a neo-Y will invade a ZW system when there is a female bias caused by haploid selection in females \citep{Kozielska:2010vm,Ubeda:2015fx}.
-Here we have shown that both predictions must be amended when recombination is weak relative to selection or selection happens in both diploid and haploid phases.
+The latter predicts that new sex-determining systems are generally favoured if they result in more equal sex-ratios than the ancestral system. 
+%The latter predicts that neo-W alleles will invade an XY system when there is a male bias caused by haploid selection in males, and vice-versa, a neo-Y will invade a ZW system when there is a female bias caused by haploid selection in females \citep{Kozielska:2010vm,Ubeda:2015fx}.
+Firstly, we show that selection (including sexually-antagonistic selection) on loci within or near the non-recombining region of the ancestral sex-determining region can favour heterogametic transitions (XY to ZW or ZW to XY) to new sex-determining systems that have looser linkage (e.g., see Figure \ref{fig:SexAntagTighter}).
+Secondly, assuming that selection is weak relative to recombination, we show that new sex-determining alleles are typically favoured if they are more closely linked to a locus under haploid selection, which is the only condition favouring homogametic transitions (XY to XY or ZW to ZW).
+In addition, with haploid selection and weak selection, heterogametic transitions (XY to ZW or ZW to XY) can occur even when the new sex-determining region is less closely linked to the locus under selection (e.g., see Figure \ref{fig:SexRatioBad}).
+%Neo-W (neo-Y) alleles invade when their fitness in females (males) is greater than the mean fitness of females (males) under the ancestral sex-determination system and/or females (males) are the rarer sex.
 
 %TIGHT LINKAGE RESULTS
-When the rate of recombination between the ancestral sex-determining locus and a locus under selection is small relative to the strength of selection (i.e., sex-linkage is tight, or selection is strong), heterogametic transitions (XY to ZW or ZW to XY) that reduce sex-linkage are possible, with or without haploid selection or sexually-antagonistic selection (Figure \ref{fig:regionplot_2a}).
-The likelihoods of these transitions are driven by sex-ratio selection, direct selection on alleles linked to the neo-sex-determining allele, the ability of the neo-sex-determining allele to avoid selection in one sex, and the ability of the neo-sex-determining allele to bring alleles on the sex-specific chromosome in the ancestor into the other sex (given that the neo-sex determining allele is epistatically dominant to its predecessor).
-This possibility that looser sex-linkage could evolve, even in the absence of haploid selection (Figure \ref{fig:regionplot_2a}A), was overlooked in \cite{vanDoorn:2010hu}, likely because they did not explicitly calculate the resident equilibria \citep[equation \ref{eq:tightequil};][]{Lloyd1977,Otto2014}.
-Interestingly, there is substantial overlap between the parameter space that allows both neo-W-$A$ and neo-W-$a$ haplotypes to spread in an XY system and that which selects for increased recombination between X and Y chromosomes \citep[e.g., compare gray region of Figure \ref{fig:regionplot_2a}A with coloured regions of Figure 2(a) in][]{Otto2014}.
-This makes sense, as when both neo-W haplotypes can spread the neo-W can invade despite reducing sex-linkage, i.e., the rate of recombination between the sex-determining allele and the selected locus increases.
+%When the rate of recombination between the ancestral sex-determining locus and a locus under selection is small relative to the strength of selection (i.e., sex-linkage is tight, or selection is strong), heterogametic transitions (XY to ZW or ZW to XY) that reduce sex-linkage are possible, with or without haploid selection (Figures \ref{fig:SexAntagTighter} and \ref{fig:regionplots}).
+
+%The likelihoods of these transitions are driven by sex-ratio selection, direct selection on alleles linked to the neo-sex-determining allele, the ability of the neo-sex-determining allele to avoid selection in one sex, and the ability of the neo-sex-determining allele to bring alleles on the sex-specific chromosome in the ancestor into the other sex (given that the neo-sex determining allele is epistatically dominant to its predecessor).
+
+%This possibility that looser sex-linkage could evolve, even in the absence of haploid selection (Figure \ref{fig:regionplot_2a}A), was overlooked in \cite{vanDoorn:2010hu}, likely because they did not explicitly consider the case of initially tight linkage between the \textbf{A} locus and the ancestral-SDR, which allows substantial differences in allele frequencies to build up \citep[$\hat{p}^\Hermaphrodite_{X} \neq \hat{p}_{Y}^\male$, equation \ref{eq:tightequil};][]{Lloyd1977,Otto2014}.
+%Interestingly, there is substantial overlap between the parameter space that allows both neo-W-$A$ and neo-W-$a$ haplotypes to spread in an XY system and that which selects for increased recombination between X and Y chromosomes \citep[e.g., compare gray region of Figure \ref{fig:regionplot_2a}A with coloured regions of Figure 2(a) in][]{Otto2014}.
+%This makes sense, as when both neo-W haplotypes can spread the neo-W can invade despite reducing sex-linkage, i.e., the rate of recombination between the sex-determining allele and the selected locus increases.
+%We further find that it is easier for a neo-W to invade 
 %\textcolor{red}{explain difference too?
@@
 %In particular, 
-Under weak selection (or loose sex-linkage), transitions to new sex-determining systems can occur when they arise more closely linked to a sexually-antagonistic locus \citep{vanDoorn:2007eu,vanDoorn:2010hu}.
-Our results show that genetic variation at loci that experience haploid selection can generate selection in favour of new sex-determining systems in a similar way. 
-New sex-determining alleles are again favoured if they are more closely linked to a locus under haploid selection.
+%Under weak selection (or loose sex-linkage), transitions to new sex-determining systems can occur when they arise more closely linked to a sexually-antagonistic locus \citep{vanDoorn:2007eu,vanDoorn:2010hu}.
+%New sex-determining alleles are again favoured if they are more closely linked to a locus under haploid selection, which is the only condition favouring homogametic transitions (XY to XY or ZW to ZW).
 %HAPLOID SELECTION ALSO ALLOWS LOOSER LINKAGE TO EVOLVE
-However, with haploid selection, heterogametic transitions (XY to ZW or ZW to XY) can also occur when the new sex-determining region is less closely linked to the locus under selection. 
-Neo-W (neo-Y) alleles invade when their fitness in females (males) is greater than the mean fitness of females (males) under the ancestral sex-determination system and/or females (males) are the rarer sex.
-With sexually-antagonistic selection (between diploid sexes) only, linkage between a selected locus and the sex-determining region strengthens associations between male beneficial alleles and the male-determining allele (Y or Z) and between female beneficial alleles and the female-determining allele (X or W).
-Thus, the mean fitness of both males and females increases with closer linkage to the sex-determining region. 
-Therefore, new sex-determining alleles only invade if they are more closely linked than the ancestral sex-determining region. 
-However, if there is haploid selection on loci linked to an XY (ZW) sex-determining region, selection can maintain polymorphisms at which the product of the frequency of females (males) and the mean fitness of females (males) is lower than it would be without sex-linkage.
-In these cases, unlinked neo-W (neo-Y) alleles can increase the frequency and/or fitness of the only sex they are found in, at a cost to the other sex, and invade despite lowering population mean fitness (Figure \ref{fig:Combination_MeanFit}).
+%However, with haploid selection, heterogametic transitions (XY to ZW or ZW to XY) can occur even when the new sex-determining region is less closely linked to the locus under selection. 
+%Neo-W (neo-Y) alleles invade when their fitness in females (males) is greater than the mean fitness of females (males) under the ancestral sex-determination system and/or females (males) are the rarer sex.
+
+%With sexually-antagonistic selection (between diploid sexes) only, linkage between a selected locus and the sex-determining region strengthens associations between male beneficial alleles and the male-determining allele (Y or Z) and between female beneficial alleles and the female-determining allele (X or W).
+%Thus, the mean fitness of both males and females increases with closer linkage to the sex-determining region. 
+%Therefore, new sex-determining alleles only invade if they are more closely linked than the ancestral sex-determining region. 
+%However, if there is haploid selection on loci linked to an XY (ZW) sex-determining region, selection can maintain polymorphisms at which the product of the frequency of females (males) and the mean fitness of females (males) is lower than it would be without sex-linkage.
+%In these cases, unlinked neo-W (neo-Y) alleles can increase the frequency and/or fitness of the only sex they are found in, at a cost to the other sex, and invade despite lowering population mean fitness (Figure \ref{fig:Combination_MeanFit}).
 %\textcolor{red}{This is similar to mitochondria and male disease ...?}
@@
 
-Sex ratio biases caused by gametic competition or meiotic drive have been shown to exert Fisherian sex-ratio selection on various autosomal \citep{Stalker:1961th,Smith:1975ft,Frank:1989vl,Hough:2013uo,Ubeda:2015fx, Otto:2015va} and sex-linked \citep{Kozielska:2010vm} modifiers.
-We find that sex-ratio biases caused by haploid selection can also affect transitions between sex-determining systems (e.g., see $\zeta$ terms in Table \ref{tab:haplotype_growth}). 
-For instance, when an allele that drives in males is linked to an XY locus it will often become associated with the Y and therefore produce a male bias ($\zeta<1/2$).
-This male bias increases the potential for a neo-W to invade (as we then have $(2\zeta)^{-1}>1$ in Table \ref{tab:haplotype_growth}), which can equalize the sex-ratio \citep[for related examples see][]{Kozielska:2010vm,Ubeda:2015fx}.
+%Sex ratio biases caused by gametic competition or meiotic drive have been shown to exert Fisherian sex-ratio selection on various autosomal \citep{Stalker:1961th,Smith:1975ft,Frank:1989vl,Hough:2013uo,Ubeda:2015fx, Otto:2015va} and sex-linked \citep{Kozielska:2010vm} modifiers.
+Sex-ratio biases caused by haploid selection can facilitate heterogametic transitions between sex-determining systems. 
+For instance, alleles favoured by haploid selection in males often become associated with the Y, which leads to a male sex-ratio bias.
+This male bias increases the potential for a neo-W to invade (Table \ref{tab:haplotype_growth}), which can equalize the sex-ratio \citep[e.g., see Figure \ref{fig:SexRatioBad}B, for related examples see][]{Kozielska:2010vm,Ubeda:2015fx}.
+%We find that sex-ratio biases caused by haploid selection can also affect transitions between sex-determining systems (e.g., see $\zeta$ terms in Table \ref{tab:haplotype_growth}). 
 %However, the neo-W may not equalize the sex-ratio (e.g., if the driving allele also drives in females or affects competition among eggs)
-However, this sex-ratio selection can be overwhelmed by drive itself or additional selective effects (e.g., when a linked allele is beneficial for male diploids but detrimental for female diploids; Table \ref{tab:specialcases}), preventing the neo-W from invading.
+However, sex-ratio selection can be overwhelmed by additional selective effects (e.g., when a linked allele is beneficial for male diploids but detrimental for female diploids; Table \ref{tab:specialcases}), preventing the neo-W from invading.
 %and equalizing the sex ratio.
-Indeed, these additional selective effects can even favour transitions between sex-determining systems that create new sex-ratio biases \citep{Ubeda:2015fx}.
-For example, in an ancestral ZW system, an allele that drives only in males can allow a linked neo-Y to invade, despite the fact it creates a male bias (Figure \ref{fig:Combination_Turnover}C).
+Indeed, transitions between sex-determining systems can even lead to stronger sex-ratio biases.
+For example, where a neo-Y invades and is linked with a locus that experiences haploid selection in male gametes, the sex ratio evolves to become biased \citep[e.g., see Figure \ref{fig:SexRatioBad}A and step 1 in][]{Ubeda:2015fx}.
+%For example, in an ancestral ZW system, haploid selection in males can allow a linked neo-Y to invade, despite the fact that it creates a male-biased sex ratio because the neo-Y becomes associated with the driven allele (Figure \ref{fig:SexRatioBad}A).
 %\textcolor{blue}{and figure 1, where the end of one panel is the same as the beginning of another, however, this figure may change).}
 %What we would like to stress is that sex-ratio selection alone cannot predict when new sex-determining systems can evolve.
-Furthermore, with weak selection, there is no asymmetry between XY to ZW and ZW to XY transitions, indicating that sex-ratio selection does not dominate (i.e., the sex-ratio bias created by haploid selection impacts the spread of a neo-W into an XY system the same way it impacts the spread of a neo-Y into a ZW system with a 1:1 sex ratio).
-An asymmetry can develop when sex-linkage is tight (e.g., Figure \ref{fig:Combination_Centimorgans} near -25cM and 25cM) but under most circumstances we do not predict asymmetry between XY to ZW and ZW to XY transitions despite the presence/absence of sex ratio selection.
-Thus, haploid selection can favour heterogametic transitions both via sex-ratio selection \citep[as predicted by][]{Kozielska:2010vm} and via fitness effects of alleles that are associated with the neo-sex-determining allele \citep[as predicted in step 1 by][]{Ubeda:2015fx}, and these selection pressures are predicted to often be of roughly equal magnitude.
+Furthermore, with weak selection, we find that there is no difference in conditions allowing XY to ZW and ZW to XY transitions, indicating that sex chromosome transitions are not predominantly predicted by their effect on the sex-ratio (i.e., the sex-ratio bias created by male haploid selection facilitates the spread of a neo-W into an XY system the same way that male haploid selection drives the spread of a neo-Y into a ZW system with a 1:1 sex ratio).
+%An asymmetry can develop when sex-linkage is tight (e.g., Figure \ref{fig:Combination_Centimorgans} near -25cM and 25cM) but under most circumstances we do not predict asymmetry between XY to ZW and ZW to XY transitions despite the presence/absence of sex ratio selection.
+Thus, haploid selection can favour heterogametic transitions both via sex-ratio selection %\citep[as predicted by][]{Kozielska:2010vm} 
+and via fitness effects of alleles that are associated with the neo-sex-determining allele, and these selection pressures are predicted to often be of roughly equal magnitude (unless linkage is tight).
+%\textcolor{red}{Maybe try to emphasise surprisingness in the paragraph more? e.g., how wrong you'd be if you assumed selection to equalise sex ratios, or it this implied?}
 %\textcolor{blue}{nice, pretty subtle argument but I think that's a good job.}
+
+%Previous studies where ESD is favoured have typically assumed that environmental conditions (e.g., maternal condition, mate quality, age, or host size) can differentially affect the fitness of males versus females such that ESD invades because it allows sex determination to depend on the environment \citep[reviewed in][]{Charnov:1982wg,Bull:1983vi,West:2009we}.
 
@@
 %In this study, we do not consider environmental condition dependence or local mate competition \citep[reviewed in][]{Charnov:1982wg,Bull:1983vi,West:2009we}.
-
-%Limitation 1: DEGENERATE Y
-We assume that sex-determining alleles do not experience direct selection except via their associations with sex and alleles at a selected locus. 
-However, in some cases, there may be significant degeneration around the sex-limited allele (Y or W) in the ancestral sex-determining region because recessive deleterious mutations and/or deletions may fix around the Y or W allele \citep{Rice:1996ke,Charlesworth:2000cc,Bachtrog:2006ed,Marais:2008hm}.
-During heterogametic transitions (XY to ZW or ZW to XY), the formally sex-limited allele fixes such that all individuals have YY or WW genotypes (Figure \ref{fig:Combination_Turnover}). 
-Any recessive deleterious alleles linked to the Y or W will therefore be revealed to selection during a heterogametic transition. 
-This phenomenon was studied by \citet{vanDoorn:2010hu}, who found that degeneration can prevent fixation of a neo-W or a neo-Y allele, leading to a mixed sex-determination system where the ancestral- and neo- sex-determining loci are both polymorphic.
-However, they noted that very rare recombination events around the ancestral sex-determining region can allow these heterogametic transitions to complete.  
-While not explicitly studied, we also predict that Y or W degeneration would prevent fixation of the new sex-determiners considered here.
-
-%Limitation 2: TWO ALLELE DRIVE
-In addition, our model of meiotic drive is simple, involving a single locus with two alleles. 
-However, many meiotic drive systems involve an interaction with another locus at which alleles may `suppress' the action of meiotic drive \citep[][]{Burt:2006,Lindholm:2016cw}.
-Thus, the dynamics of meiotic drive alleles can be heavily dependent on the interaction between two loci and the recombination rate between them, which in turn can be affected by sex-linkage if there is reduced recombination between sex chromosomes \citep{Hurst:1991uh}.
-Furthermore, in some cases, a driving allele may act by killing any gametes that carry a `target' allele at another locus, in which case there is a two-locus drive system and the total number of gametes produced can be reduced by meiotic drive.
-Where gamete number is reduced by meiotic drive, the number of mates competing for fertilization (mating system) can affect the equilibrium frequency of a meiotic drive allele \citep{Holman:2015en}. 
-In polygamous mating systems, the intensity of pollen/sperm competition can depend on the density of males available to donate pollen/sperm, which can itself depend on the sex ratio \citep{Taylor:2002wu}.
-Since the sex ratio is partly determined by the sex-determination system, the evolution of new sex-determination system could by influenced by these dynamics. 
-How the evolution of new sex-determining mechanisms could be influenced by two-locus meiotic drive and/or by ecological feedbacks under different mating systems remains to be studied.
-
-%PREDICTIONS TO TEST
-The hypotheses presented here can be empirically investigated in a similar manner to the idea that transitions between sex-determining systems are favoured by linkage to sexually-antagonistic variation.
-In the case of sexually-antagonistic variation, one supporting observation is that genes expected to be under sexually-antagonistic selection (e.g., those causing bright male colouration) have been found on recently derived sex chromosomes \citep{Lindholm:2002dw,Tripathi:2009cw,Ser:2010iq}.
-Our results suggest that polymorphic loci that are ancestrally sex-linked and under sex-specific selection could also drive heterogametic transitions between sex-determination systems. 
-As noted by \citet{vanDoorn:2010hu}, it would be prudent to compare closely related clades in order to determine whether observed polymorphisms pre-dates a transition in sex-determination or arose afterwards, particularly because sex-linkage allows sexually-antagonistic selection to maintain polymorphisms under a different and larger parameter space \citep{Rice:1987hs,Jordan:2011fj}.
-As with sexually-antagonistic selection, the presence of haploid selected loci around ancestral- or novel-sex-determining regions could support their role in sex chromosome turnover.
-%We note that linkage with sex chromosomes is not, a priori, more permissive to the maintenance of ploidally antagonistic variation \citep{Immler:2012tl}. 
-A recent transcriptome analysis in \textit{Rumex}, suggests a role for haploid competition in the evolution of sex-determination systems by showing that Y-linked genes are overexpressed in pollen but not in male diploids, indicating variation currently or previously maintained by haploid selection; over-expression also occurs on the autosome that is orthologous to the sex chromosomes in closely related species \textcolor{red}{(Sandler et al., 2017, Personal Communication)}.
-% (\textcolor{red}{George Sandler, a student in the Wright and Barrett labs, has done some yet-to-be-published work on Rumex that we should cite here.
-We can send him this draft and get his permission to cite him as personal communication or unpublished results.
-I think he has basically found that genes retained on the Y are overexpressed in pollen but not in male diploids, suggesting they are being maintained by haploid selection, not sexual antagonism.
-And I think they know that the sex chromosomes are recently derived, and that in closely related species the autosome matching up with the newly derived sex chromosome also has genes that are over expressed in pollen.
-I guess this is a follow up to Crowson et al 2017 Mol Biol Evol 34:1140, which we could potentially cite as well.}).
 
@@
 %Given the caveats mentioned above about the form of meiotic drive modelled, we would also expect that heterogametic transitions in sex determination would be more common in clades where there is meiotic drive.
-Taken at face value, our results indicate that transitions in heterogametey (XY to ZW or vice versa) are more likely than transitions in homogamety when genetic conflict is predominately between the haploids of each sex (e.g., with $|D^\male - D^\female| << |\alpha_\Delta^\male - \alpha_\Delta^\female + t^\male - t^\female|$ we have $\lambda_{W',XY} > \lambda_{Y',XY}$; equations \ref{eq:lambda_neoW} and \ref{eq:freq_diffs}).
-In addition, because haploid selection can cause transitions that increase or decrease sex-linkage, haploid selection may lead to less stability, and greater potential for cycling, in sex-determination systems (e.g., the final state in Figure \ref{fig:Combination_Turnover}C is the starting state in Figure \ref{fig:Combination_Turnover}B).
-Potentially, successive heterogametic transitions between master regulators of sex-determination could be inferred from careful examination of the molecular pathways by which sex is determined. 
-Our predictions could also be examined using a suitable proxy for haploid selection, for example, \cite{Lenormand:2005vb} use the outcrossing rate in plants as a proxy for the strength of pollen competition.
-Furthermore, assuming that transitions from dioecy to hermaphroditism (equal parental investment in male and female gametes) are favoured in a similar manner to the ESD examined here (equal probability of zygotes developing as males or females), our results suggest that haploid competition during the multicellular haploid stage could drive transitions between dioecy and hermaphroditism in plants \textcolor{red}{(Käfer et al., 2017, Sabath et al., 2017)}.
-In animals, one might expect gametic competition to be stronger in species where sperm is required to live for a long time after spermatogenesis because transcripts shared during spermatogenesis may become depleted, revealing the haploid phenotype of the sperm \citep{Immler:2014im}.
-Given the caveats mentioned above about the form of meiotic drive modelled, we would also expect that heterogametic transitions in sex determination would be more common in clades where there is meiotic drive.
+
+%Together, our models demonstrate novel selective forces that favour heterogametic transitions (XY to ZW or ZW to XY). 
+%One common prediction is therefore that heterogametic transitions are favoured under a wider range of conditions than homogametic transitions. 
+%However, heterogametic transitions are not clearly in excess.
+For example, \citet{Vicoso:2015hf} found a dozen sex chromosome configurations among Dipteran species but only one transition between male and female heterogametey.
+%While our models examine the selective forces that favour the spread of new sex-determining regions, observed transitions could also reflect the mutation rate for neo-Y versus neo-W alleles (e.g., duplications of the ancestral sex determining region could be particularly likely).
+%In addition, heterogametic transitions could be limited due to the production of YY males or WW females (see below). 
+%Alternatively, it might be useful to compare clades that are expected to differ in the strength of haploid selection (e.g., plants are thought to experience more selection during their multicellular haploid stage
+
+%COMPARATIVE PATTERNS 
+We show that the spread of new sex determination systems can be driven by loci experiencing haploid selection. 
+Because haploid selection can cause transitions that increase or decrease sex-linkage, haploid selection may lead to less stability, and greater potential for cycling, in sex-determination systems (e.g., the final state of the red line in Figure \ref{fig:SexRatioBad}A is the starting state in Figure \ref{fig:SexRatioBad}B).
+In particular, if haploid selection is strong but selective differences between male and female diploids are weak, we find that heterogametic transitions (XY to ZW or vice versa) are favoured more strongly than homogametic transitions (e.g., with $|D^\male - D^\female| << |\alpha_\Delta^\male - \alpha_\Delta^\female + t^\male - t^\female|$ we have $\lambda_{W',XY} > \lambda_{Y',XY}$; equations \ref{eq:lambda_neoW} and \ref{eq:freq_diffs}).
+Turnovers driven by haploid selection may help to explain the relative rarity of heteromorphic sex chromosomes in plants, which are thought to experience more selection during their multicellular haploid stage.
+For example, among relatively few dioecious clades in which multiple species have well characterized sex chromosomes \citep{Ming:2011iy}, heterogametic transitions have been inferred in \textit{Silene} subsection \textit{Otites} \citep{Slancarova:2013dq} and in \textit{Salicaceae} \textcolor{red}{(Pucholt et al.
+2015, 2017)}.
+%Potentially, successive heterogametic transitions between master regulators of sex-determination could be inferred from careful examination of the molecular pathways by which sex is determined. 
+%Our predictions could also be examined using a suitable proxy for haploid selection, for example, \cite{Lenormand:2005vb} use the outcrossing rate in plants as a proxy for the strength of pollen competition.
+Furthermore, assuming that transitions from dioecy to hermaphroditism (equal parental investment in male and female gametes) are favoured in a similar manner to the ESD examined here (equal probability of zygotes developing as males or females), our results suggest that competition during the haploid stage could drive transitions between dioecy and hermaphroditism, which are frequent in plants \textcolor{red}{(Käfer et al., 2017, Sabath et al., 2017)}.
+%In animals, one might expect gametic competition to be stronger in species where sperm is required to live for a long time after spermatogenesis because transcripts shared during spermatogenesis may become depleted, revealing the haploid phenotype of the sperm \citep{Immler:2014im}.
+%We would also expect that heterogametic transitions in sex determination would be more common in clades where there is meiotic drive.
+
+%IDENTIFICATION OF LOCI IN GENOMIC LOCATIONS THAT IMPLICATE THEM IN SEX-CHROMOSOME TURNOVER
+%The hypotheses presented here can be empirically investigated in a similar manner to the idea that transitions between sex-determining systems are favoured by linkage to sexually-antagonistic variation.
+%In the case of sexually-antagonistic variation, one supporting observation is that genes expected to be under sexually-antagonistic selection (e.g., those causing bright male colouration) have been found on recently derived sex chromosomes \citep{Lindholm:2002dw,Tripathi:2009cw,Ser:2010iq}.
+In support of their role in sex chromosome turnover, genes expected to be under sexually-antagonistic selection (e.g., those causing bright male colouration) have been found on recently derived sex chromosomes \citep{Lindholm:2002dw,Tripathi:2009cw,Ser:2010iq}.
+Our results show that, if loci experiencing overdominance and/or sexually-antagonistic selection can be identified in close linkage with the ancestral sex-determining locus (rather than only the novel sex-determining locus), then they could also be implicated in driving heterogametic transitions between sex-determination systems.
+As noted by \citet{vanDoorn:2010hu}, it would be prudent to compare closely related clades in order to determine whether observed polymorphisms predate a transition in sex-determination or arose afterwards.
+%, particularly because sex-linkage allows sexually-antagonistic selection to maintain polymorphisms under a different and larger parameter space \citep{Rice:1987hs,Jordan:2011fj}.
+ In addition, we show haploid selection on loci around either the ancestral- or the novel-sex-determining regions could have had a role in driving sex chromosome turnover. 
+%Our results suggest that polymorphic loci that are ancestrally sex-linked and under sex-specific selection could also drive heterogametic transitions between sex-determination systems. 
+%As with sexually-antagonistic selection, the presence of haploid selected loci around ancestral- or novel-sex-determining regions could support their role in sex chromosome turnover.
+%We note that linkage with sex chromosomes is not, a priori, more permissive to the maintenance of ploidally antagonistic variation \citep{Immler:2012tl}. 
+A recent transcriptome analysis in \textit{Rumex}, suggests a role for gametic competition in the evolution of sex-determination systems, showing that Y-linked genes are have higher expression in haploid pollen than autosomal genes \textcolor{red}{(check this is accurate)}.
+Interestingly, haploid-expression is also more common on the autosome that is orthologous to the sex chromosomes in closely related species suggesting that new sex chromosomes may have been favoured through their association with haploid selected alleles on these chromosomes \textcolor{red}{(Sandler et al., 2017, Personal Communication)}.
+
+%Limitation 1: DEGENERATE Y
+We assume that sex-determining alleles do not experience direct selection except via their associations with sex and selected alleles.
+However, in some cases, there may be significant degeneration around the sex-limited allele (Y or W) in the ancestral sex-determining region because recessive deleterious mutations and/or deletions accumulate around the Y or W sex-determining regions \citep{Rice:1996ke,Charlesworth:2000cc,Bachtrog:2006ed,Marais:2008hm}.
+During heterogametic transitions (XY to ZW or ZW to XY), but not homogametic transitions (XY to XY or ZW to ZW), any recessive deleterious alleles linked to the Y or W are revealed to selection in YY or WW individuals \citep{Bachtrog:2014bx}.
+This phenomenon was studied by \citet{vanDoorn:2010hu}, who found that degeneration can prevent fixation of a neo-W or a neo-Y allele, leading to a mixed sex-determination system where the ancestral and new sex-determining loci are both segregating.
+However, they noted that very rare recombination events around the ancestral sex-determining region can allow these heterogametic transitions to complete.  
+%While not explicitly studied, we also predict that Y or W degeneration would prevent fixation of the new sex-determining genes considered here.
+Degeneration around the Y or W could explain why heterogametic transitions are not observed to be much more common than homogametic transitions despite the fact that our models demonstrate that they are favoured under a wider range of conditions.
+For example, \citet{Vicoso:2015hf} found a dozen sex chromosome configurations among Dipteran species but only one transition between male and female heterogametey.
+
+%Limitation 2: TWO ALLELE DRIVE
+Another simplification that we made is that meiotic drive involves only a single locus with two alleles. 
+However, many meiotic drive systems involve an interaction with another locus at which alleles may `suppress' the action of meiotic drive \citep[][]{Burt:2006,Lindholm:2016cw} \textcolor{red}{Taylor,1999}.
+Thus, the dynamics of meiotic drive alleles can be heavily dependent on the interaction between two loci and the recombination rate between them, which in turn can be affected by sex-linkage if there is reduced recombination between sex chromosomes \citep{Hurst:1991uh}.
+Furthermore, in some cases, a driving allele may act by killing any gametes that carry a `target' allele at another locus, in which case there can be fertility effects which can affect the equilibrium frequency of a meiotic drive allele \citep{Holman:2015en}.
+In polygamous mating systems, the intensity of pollen/sperm competition can depend on the density of males available to donate pollen/sperm, which can itself depend on the sex ratio \citep{Taylor:2002wu}.
+In terms of our model, this implies that the strength of gametic competition ($t^\male$) may both determine and be determined by the sex ratio. 
+How the evolution of new sex-determining mechanisms could be influenced by two-locus meiotic drive and/or by ecological feedbacks under different mating systems remains to be studied.
 
@@
 In addition, haploid selection alone can cause transitions analogous to those caused by purely sexually-antagonistic selection, eliminating the need for differences in selection between male and female diploids.
-Perhaps counterintuitively, transitions involving haploid selection can be driven by sex-ratio selection, or cause sex-ratio biases to evolve. 
-We therefore argue that haploid selection should be considered, alongside sexually-antagonistic and sex-ratio selection, as a potentially pivotal factor in the evolution of many sex-determination systems.
-Overall, our results suggest several new scenarios under which new sex-determination systems are favoured, including sex-specific selection on ancestrally sex-linked loci, which could help to explain why the evolution of sex-determination systems is so dynamic.
+Perhaps counterintuitively, transitions involving haploid selection can be driven by sex-ratio selection or cause sex-ratio biases to evolve. 
+We therefore argue that haploid selection should be considered as a pivotal factor in the evolution of sex-determination systems. 
+Overall, our results suggest several new scenarios under which new sex-determination systems are favoured, which could help to explain why the evolution of sex-determination systems is so dynamic. 
 %Further, we have shown the way in which transitions are affected by haploid selection is not intuitively obvious. 
@@
 %POLYGENIC SEX DETERMINATION
-%\textcolor{red}{Numerical results suggest that polygenic sex determination can be stable with gametic competition.
-i.e., feminizers/masculinizers sometimes invade but don't fix.
-We have not discussed this.
-Might be interesting because it appears that polygenic sex determination exists (possibly stably, rather than transitionally) but previous models don't show any advantage to polygenic sex determination.
-There are two other ways that polygenic sex determination could be observed.
-(1) Direct selection against WW or YY genotypes during heterogametic transitions, mentioned above.
-(2) Loss of variation at the selected locus: The conditions under which polymorphism is maintained can depend on linkage to the SDR, and when a neo-SDR evolves you can move into a region where $A$ or $a$ fixes, at which point there is no longer any selection.}
-
-%``Polygenic sex determination has been reported in many plants (e.g.
+
+\textcolor{red}{Discuss polymorphic mating systems somewhere?
+Say that haploid selection makes this particularly likely (I think there are examples with gametic competition and weak selection, whereas the vD\&K, 2010 results suggest that it's not possible with weak selection and diploid selection alone)?
+This might be best as a section added to the appendix.
+When giving an example of polymorphic, make sure it's not just that variation was lost at the \textbf{A} locus.
+The following examples copied and pasted from  from Vuilleumier et al.
+2007 and vD\&K, 2010, might be added to this section.}
+
+\textcolor{red}{``Polygenic sex determination has been reported in many plants (e.g.
 Shannon \& Holsinger 2007), fishes (Vandeputte et al.
@@
 Battaglia 1958; Battaglia \& Malesani 1959; Voordouw
-%\& Anholt 2002), bivalves (Haley 1977; Saavedra et al. 1997), gastropods (Yusa 2007a,b), and polychaetes (Bacci 1965, 1978; Premoli et al. 1996).''
-%From Vuilleumier et al. 2007:
-%``Polymorphism for sex-determining genes within or among populations has been reported in many species including houseflies, midges, woodlice, platyfish, cichlid fish, and frogs (Gordon, 1944; Kallman, 1970; Thomp-son, 1971; Macdonald, 1978; Bull, 1983; Rigaud et al., 1997; Caubet et al., 2000; Lande et al., 2001; Ogataet al., 2003; Lee et al., 2004; Mank et al., 2006).''
-%Also check Kallman (1984) -from vD\&K, 2010.
+\& Anholt 2002), bivalves (Haley 1977; Saavedra et al. 1997), gastropods (Yusa 2007a,b), and polychaetes (Bacci 1965, 1978; Premoli et al. 1996).''
+From Vuilleumier et al. 2007:
+``Polymorphism for sex-determining genes within or among populations has been reported in many species including houseflies, midges, woodlice, platyfish, cichlid fish, and frogs (Gordon, 1944; Kallman, 1970; Thompson, 1971; Macdonald, 1978; Bull, 1983; Rigaud et al., 1997; Caubet et al., 2000; Lande et al., 2001; Ogataet al., 2003; Lee et al., 2004; Mank et al., 2006).''
+Also check Kallman (1984) -from vD\&K, 2010. 
+}
 
@@
 
-\textcolor{red}{Should we adjust the subscripts throughout this subsection?
+%\textcolor{red}{Should we adjust the subscripts throughout this subsection?
 Right now we end up re-defining $i$ and $j$ (when switching from haploid to diploid; this might have been my doing!) and then introduce three new subscripts $b$, $c$, and $l$, all of which can be derived from $i$ and $j$.
@@
 In each generation we census the genotype frequencies in male and female gametes/gametophytes (hereafter, gametes) between meiosis (and any meiotic drive) and gametic competition. 
-At this stage we denote the frequencies of X- and Y-bearing gametes from males and females $x_{ij}^{\Hermaphrodite}$ and $y_{ij}^{\Hermaphrodite}$, where $\Hermaphrodite \in \{\male,\female\}$ specifies the sex of the diploid that the gamete came from, $i\in\{A,a\}$ specifies the allele at the selected locus $\mathbf{A}$, and $j\in\{M,m\}$ specifies the allele at the novel sex-determining locus $\mathbf{M}$.
-The gamete frequencies from each sex sum to one, $\sum_{i,j}x_{ij}^{\Hermaphrodite}+y_{ij}^{\Hermaphrodite}=1$.
-
-Competition then occurs among gametes of the same sex (e.g., among eggs and among sperm separately) according to the \textbf{A} locus allele, $i$ (see Table \ref{tab:fitnesstable}).
-The genotype frequencies after gametic competition are $x_{ij}^{\Hermaphrodite,s}= w_{i}x_{ij}^{\Hermaphrodite}/\bar{w}_{H}^{\Hermaphrodite}$ and $y_{ij}^{\Hermaphrodite,s}= w_{i}y_{ij}^{\Hermaphrodite}/\bar{w}_{H}^{\Hermaphrodite}$, where $\bar{w}_{H}^{\Hermaphrodite}=\sum_{i,j} w_{i}x_{ij}^{\Hermaphrodite}+w_{i}y_{ij}^{\Hermaphrodite}$ is the mean fitness of male ($\Hermaphrodite=\male$) or female ($\Hermaphrodite=\female$) gametes.
+At this stage we denote the frequencies of X- and Y-bearing gametes from males and females $x_{i}^{\Hermaphrodite}$ and $y_{i}^{\Hermaphrodite}$, where $\Hermaphrodite \in \{\male,\female\}$ specifies the sex of the diploid that the gamete came from.
+$i\in\{1,2,3,4\}$ specifies the genotype at the selected locus $\mathbf{A}$ and at the novel sex-determining locus $\mathbf{M}$ where $1=MA$, $2=Ma$, $3=mA$, and $4=ma$. 
+The gamete frequencies from each sex sum to one, $\sum_{i}x_{i}^{\Hermaphrodite}+y_{i}^{\Hermaphrodite}=1$.
+
+Competition then occurs among gametes of the same sex (e.g., among eggs and among sperm separately) according to the genotype at the \textbf{A} locus ($w_{1}^\Hermaphrodite=w_{3}^\Hermaphrodite=w_{A}^\Hermaphrodite$, $w_{2}^\Hermaphrodite=w_{4}^\Hermaphrodite=w_{a}^\Hermaphrodite$, see Table \ref{tab:fitnesstable}).
+The genotype frequencies after gametic competition are $x_{i}^{\Hermaphrodite,s}= w_{i}x_{i}^{\Hermaphrodite}/\bar{w}_{H}^{\Hermaphrodite}$ and $y_{i}^{\Hermaphrodite,s}= w_{i}y_{i}^{\Hermaphrodite}/\bar{w}_{H}^{\Hermaphrodite}$, where $\bar{w}_{H}^{\Hermaphrodite}=\sum_{i} w_{i}x_{i}^{\Hermaphrodite}+w_{i}y_{i}^{\Hermaphrodite}$ is the mean fitness of male ($\Hermaphrodite=\male$) or female ($\Hermaphrodite=\female$) gametes.
 
 Random mating then occurs between gametes to produce diploid zygotes.
-To shorten notation we now use index $i$ (and $j$) to denote the alleles at both the $\mathbf{A}$ and $\mathbf{M}$ loci and label $MA=1$, $Ma=2$, $mA=3$, and $ma=4$, such that $i,j\in\{1,2,3,4\}$.
-The frequencies of $XX$ zygotes are then denoted as $xx_{ij}$, $XY$ zygotes as $xy_{ij}$, and $YY$ zygotes as $yy_{ij}$. 
+%To shorten notation we now use index $i$ (and $j$) to denote the alleles at both the $\mathbf{A}$ and $\mathbf{M}$ loci and label $MA=1$, $Ma=2$, $mA=3$, and $ma=4$, such that $i,j\in\{1,2,3,4\}$.
+The frequencies of $XX$ zygotes are then denoted as $xx_{ij}$, $XY$ zygotes as $xy_{ij}$, and $YY$ zygotes as $yy_{ij}$, where \textbf{A} and \textbf{M} locus genotypes are given by $i,j\in\{1,2,3,4\}$, as above.
+In $XY$ zygotes, the haplotype inherited from an X-bearing gamete is given by $i$ and the haplotype from a Y-bearing gamete is given by $j$. 
 In $XX$ and $YY$ zygotes, individuals with diploid genotype $ij$ are equivalent to those with diploid genotype $ji$; for simplicity, we use $xx_{ij}$ and $yy_{ij}$ with $i\neq j$ to denote the average of these frequencies, $xx_{ij}=(x_{i}^{\female,s}x_{j}^{\male,s}+x_{j}^{\female,s}x_{i}^{\male,s})/2$ and $yy_{ij}=(y_{i}^{\female,s}y_{j}^{\male,s}+y_{j}^{\female,s}y_{i}^{\male,s})/2$.
@@
 In addition, we can consider any epistatic dominance relationship between the two sex-determining loci. 
-For example, here we assume that the ancestral sex-determining system (\textbf{X} locus) is $XY$ ($k_{MMXX}=1$ and $k_{MMXY}=k_{MMYY}=0$) or $ZW$ ($k_{MMZZ}=0$ and $k_{MMZW}=k_{MMWW}=1$) and epistatically recessive to a dominant novel sex-determining locus, \textbf{M} ($k_{Mmc}=k_{mmc}=k$).
+Here, we assume that the ancestral sex-determining system (\textbf{X} locus) is $XY$ ($k_{MMXX}=1$ and $k_{MMXY}=k_{MMYY}=0$) or $ZW$ ($k_{MMZZ}=0$ and $k_{MMZW}=k_{MMWW}=1$) and epistatically recessive to a dominant novel sex-determining locus, \textbf{M} ($k_{Mmc}=k_{mmc}=k$).
 
@@
 $R$ is the recombination rate between the \textbf{A} locus and the \textbf{M} locus, $\chi$ is the recombination rate between the \textbf{M} locus and the \textbf{X} locus, and $r$ is the recombination rate between the \textbf{A} locus and the \textbf{X} locus.
-Table \ref{tab:chisubstitutions} shows how $\chi$ can be substituted to give any linear order of loci.
+Table \ref{tab:chisubstitutions} shows the value of $\chi$ in the absence of cross-over interference for each possible ordering of the loci.
 During meiosis in sex $\Hermaphrodite$, meiotic drive occurs such that, in $Aa$ heterozygotes, a fraction $\alpha^{\Hermaphrodite}$ of gametes produced carry the $A$ allele and $(1-\alpha^\Hermaphrodite)$ carry the $a$ allele.
@@
 
-Among gametes from sex $\Hermaphrodite$ (sperm/pollen when $\Hermaphrodite=\male$, eggs/ovules when $\Hermaphrodite=\female$), the frequencies of haplotypes (before gametic competition) in the next generation are given by
+Among gametes from sex $\Hermaphrodite$, the frequencies of haplotypes (before gametic competition) in the next generation are given by
 
@@
 \begin{split}
-x_{MA}^{{\Hermaphrodite}'}=&xx_{11}^{\Hermaphrodite,s}+xx_{13}^{\Hermaphrodite,s}/2+(xx_{12}^{\Hermaphrodite,s}+xx_{14}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
+x_{1}^{{\Hermaphrodite}'}=&xx_{11}^{\Hermaphrodite,s}+xx_{13}^{\Hermaphrodite,s}/2+(xx_{12}^{\Hermaphrodite,s}+xx_{14}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
 &-R(xx_{14}^{\Hermaphrodite,s}-xx_{23}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
@@
 \begin{split}
-x_{Ma}^{{\Hermaphrodite}'}=&xx_{22}^{\Hermaphrodite,s}+xx_{24}^{\Hermaphrodite,s}/2+(xx_{12}^{\Hermaphrodite,s}+xx_{23}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
+x_{2}^{{\Hermaphrodite}'}=&xx_{22}^{\Hermaphrodite,s}+xx_{24}^{\Hermaphrodite,s}/2+(xx_{12}^{\Hermaphrodite,s}+xx_{23}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
 &-R(xx_{23}^{\Hermaphrodite,s}-xx_{14}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
@@
 \begin{split}
-x_{mA}^{{\Hermaphrodite}'}=&xx_{33}^{\Hermaphrodite,s}+xx_{13}^{\Hermaphrodite,s}/2+(xx_{23}^{\Hermaphrodite,s}+xx_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
+x_{3}^{{\Hermaphrodite}'}=&xx_{33}^{\Hermaphrodite,s}+xx_{13}^{\Hermaphrodite,s}/2+(xx_{23}^{\Hermaphrodite,s}+xx_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
 &-R(xx_{23}^{\Hermaphrodite,s}-xx_{14}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
@@
 \begin{split}
-x_{ma}^{{\Hermaphrodite}'}=&xx_{44}^{\Hermaphrodite,s}+xx_{34}^{\Hermaphrodite,s}/2+(xx_{14}^{\Hermaphrodite,s}+xx_{24}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
+x_{4}^{{\Hermaphrodite}'}=&xx_{44}^{\Hermaphrodite,s}+xx_{34}^{\Hermaphrodite,s}/2+(xx_{14}^{\Hermaphrodite,s}+xx_{24}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
 &-R(xx_{14}^{\Hermaphrodite,s}-xx_{23}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
@@
 \begin{split}
-y_{MA}^{{\Hermaphrodite}'}=&yy_{11}^{\Hermaphrodite,s}+yy_{13}^{\Hermaphrodite,s}/2+(yy_{12}^{\Hermaphrodite,s}+yy_{14}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
+y_{1}^{{\Hermaphrodite}'}=&yy_{11}^{\Hermaphrodite,s}+yy_{13}^{\Hermaphrodite,s}/2+(yy_{12}^{\Hermaphrodite,s}+yy_{14}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
 &-R(yy_{14}^{\Hermaphrodite,s}-yy_{23}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
@@
 \begin{split}
-y_{Ma}^{{\Hermaphrodite}'}=&yy_{22}^{\Hermaphrodite,s}+yy_{24}^{\Hermaphrodite,s}/2+(yy_{12}^{\Hermaphrodite,s}+yy_{23}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
+y_{2}^{{\Hermaphrodite}'}=&yy_{22}^{\Hermaphrodite,s}+yy_{24}^{\Hermaphrodite,s}/2+(yy_{12}^{\Hermaphrodite,s}+yy_{23}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
 &-R(yy_{23}^{\Hermaphrodite,s}-yy_{14}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
@@
 \begin{split}
-y_{mA}^{{\Hermaphrodite}'}=&yy_{33}^{\Hermaphrodite,s}+yy_{13}^{\Hermaphrodite,s}/2+(yy_{23}^{\Hermaphrodite,s}+yy_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
+y_{3}^{{\Hermaphrodite}'}=&yy_{33}^{\Hermaphrodite,s}+yy_{13}^{\Hermaphrodite,s}/2+(yy_{23}^{\Hermaphrodite,s}+yy_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
 &-R(yy_{23}^{\Hermaphrodite,s}-yy_{14}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
@@
 \begin{split}
-y_{ma}^{{\Hermaphrodite}'}=&yy_{44}^{\Hermaphrodite,s}+yy_{34}^{\Hermaphrodite,s}/2+(yy_{14}^{\Hermaphrodite,s}+yy_{24}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
+y_{4}^{{\Hermaphrodite}'}=&yy_{44}^{\Hermaphrodite,s}+yy_{34}^{\Hermaphrodite,s}/2+(yy_{14}^{\Hermaphrodite,s}+yy_{24}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
 &-R(yy_{14}^{\Hermaphrodite,s}-yy_{23}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
@@
 The full system is therefore described by 16 recurrence equations (three diallelic loci in two sexes, $2^3 \times 2 = 16$). 
-However, some diploid types are not produced under a given sex-determination system. 
-For example, with the $M$ allele fixed and ancestral $XY$ sex determination, there are no $m$ alleles, $XX$ males, $XY$ females, or $YY$ females ($xx_{11}^{\male}=xx_{12}^{\male}=xx_{22}^\male=xy_{11}^{\female}=xy_{12}^{\female}=xy_{21}^{\female}=xy_{22}^\female=yy_{11}^{\female}=yy_{12}^{\female}=yy_{22}^\female=0$).
+However, not all diploid types are produced under certain sex-determination systems. 
+For example, with the $M$ allele fixed and an ancestral $XY$ sex determination, there are $XX$ males, $XY$ females, or $YY$ females ($x_{3}^\Hermaphrodite=x_{4}^\Hermaphrodite=y_{4}^\Hermaphrodite=y_{3}^\Hermaphrodite=y_{i}^\female=0$).
+%($xx_{11}^{\male}=xx_{12}^{\male}=xx_{22}^\male=xy_{11}^{\female}=xy_{12}^{\female}=xy_{21}^{\female}=xy_{22}^\female=yy_{11}^{\female}=yy_{12}^{\female}=yy_{22}^\female=0$). 
 In this case, the system only involves six recursion equations, %because there is only one \textbf{M} locus allele and no Y-bearing female gametes. 
-which yields equilibrium \eqref{eq:pAve}.
+which we assume below to calculate the equilibria.
 
@@
 
-In the resident population (allele $M$ fixed), we choose to follow the frequency of $A$ in female gametes (eggs) from an XX female, $p^\female_X$, and in X-bearing, $p^\male_X$, and Y-bearing, $p^\male_Y$, male gametes (sperm).
+In the resident population (allele $M$ fixed), we follow the frequency of $A$ in X-bearing female gametes, $p^\female_X$, and X-bearing male gametes, $p^\male_X$, and Y-bearing male gametes, $p^\male_Y$.
 We also track the total frequency of Y among male gametes, $q$, which may deviate from $1/2$ due to meiotic drive in males. 
-These four variables determine the frequencies of the six resident gamete types: $x_{MA}^{\female}=p_{X}^{\female}$, $x_{Ma}^{\female}=1-p_{X}^{\female}$, $x_{MA}^{\male}=(1-q)p_{X}^{\male}$, $x_{Ma}^{\male}=(1-q)(1-p_{X}^{\male})$, $y_{MA}^{\male}=q p_{Y}^{\male}$, and $y_{Ma}^{\male}=q(1-p_{Y}^{\male})$.
+These four variables determine the frequencies of the six resident gamete types: $x_{1}^{\female}=p_{X}^{\female}$, $x_{2}^{\female}=1-p_{X}^{\female}$, $x_{1}^{\male}=(1-q)p_{X}^{\male}$, $x_{2}^{\male}=(1-q)(1-p_{X}^{\male})$, $y_{1}^{\male}=q p_{Y}^{\male}$, and $y_{2}^{\male}=q(1-p_{Y}^{\male})$.
 Mean fitnesses in the resident population are given in table \ref{tab:meanfitnesses}.
 
-Various forms of selection can maintain a polymorphism at the \textbf{A} locus, including sexually antagonistic selection, overdominance, conflicts between diploid selection and selection upon haploid genotypes \citep[ploidally antagonistic selection,][]{Immler:2012tl}, and a combination of these selective regimes.
+Various forms of selection can maintain a polymorphism at the \textbf{A} locus, including sexually antagonistic selection, overdominance, conflicts between diploid selection and selection upon haploid genotypes \citep[ploidally antagonistic selection,][]{Immler:2012tl}, or a combination of these selective regimes.
 
@@
 We first calculate the equilibrium frequency of the Y and $A$ alleles in the ancestral population when the recombination rate between the \textbf{X} and \textbf{A} loci is small ($r$ of order $\epsilon$).
-The \textbf{A} locus will not affect evolution at the novel sex-determining locus, \textbf{M}, if one \textbf{A} allele is fixed on all backgrounds. 
+Selection at the \textbf{A} locus will not affect evolution at the novel sex-determining locus, \textbf{M}, if one allele is fixed on all backgrounds. 
 We therefore focus on the five equilibria that maintain both $A$ and $a$ alleles, four of which are given to leading order by:
@@
 According to the `small parameter theory' \citep{Karlin:1972ab,Karlin:1972dq}, these stability properties are unaffected by small amounts of recombination between the SDR and \textbf{A} locus, although equilibrium frequencies may be slightly altered.
-For the $a$ allele to be stably fixed on the Y requires that $\bar{w}_{Ya}^{\male}>\bar{w}_{YA}^{\male}$ where $\bar{w}_{Ya}^{\male}=w_{a}^{\male}(2 p_{X}^{\female}(1-\alpha^{\male}) w_{A}^{\female} w_{Aa}^{\male}+ (1-p_{X}^{\female})w_{a}^{\female} w_{aa}^{\male} )$ and $\bar{w}_{YA}^{\male}=w_{A}^{\male}(p_{X}^{\female} w_{A}^{\female} w_{AA}^{\male}+ 2 (1-p_{X}^{\female})\alpha^{\male}w_{a}^{\female} w_{Aa}^{\male} )$.
+For the $a$ allele to be stably fixed on the Y is stable if $\bar{w}_{Ya}^{\male}>\bar{w}_{YA}^{\male}$ where $\bar{w}_{Ya}^{\male}=w_{a}^{\male}(2 p_{X}^{\female}(1-\alpha^{\male}) w_{A}^{\female} w_{Aa}^{\male}+ (1-p_{X}^{\female})w_{a}^{\female} w_{aa}^{\male} )$ and $\bar{w}_{YA}^{\male}=w_{A}^{\male}(p_{X}^{\female} w_{A}^{\female} w_{AA}^{\male}+ 2 (1-p_{X}^{\female})\alpha^{\male}w_{a}^{\female} w_{Aa}^{\male} )$.
 That is, $Ya$ haplotypes must have higher fitness than $YA$ haplotypes.
@@
 Stability of a polymorphism on the X chromosome (equilibrium $A$) further requires that $\phi >0$ and $\psi >0$. 
-Fixation of the $a$ allele on the X (equilibrium $B$) is mutually exclusive with equilibrium $(A)$ and requires $\psi<0$ and $w_{A}^{\female}w_{AA}^{\female}>(1-\alpha^{\female})w_{a}^{\female}w_{Aa}^{\female}$.
+Fixation of the $a$ allele on the X (equilibrium $B$) can be stable only if equilibrium $(A)$ is not and requires $\psi<0$ and $w_{A}^{\female}w_{AA}^{\female}>(1-\alpha^{\female})w_{a}^{\female}w_{Aa}^{\female}$.
+
+\textcolor{red}{check last condition and the stability condition below are correct}
 
@@
 
-Given that a polymorphism is maintained at the \textbf{A} locus by selection, with weak selection and drive the frequencies of $A$ in each type of gamete are the same ($\hat{p}^\female_X=\hat{p}^\male_X=\hat{p}^\male_Y=\bar{p}$) and given, to leading order, by
+Given that a polymorphism is maintained at the \textbf{A} locus by weak selection, the frequencies of $A$ in each type of gamete are the same ($\hat{p}^\female_X=\hat{p}^\male_X=\hat{p}^\male_Y=\bar{p}$) and given, to leading order, by
 
@@
 \noindent
-Differences in frequency between gamete types are of order $\epsilon$ and given, to leading order, by
+Differences in frequency between gamete types are of $O(\epsilon)$:
 
@@
 
+\textcolor{red}{Cover the other parts of the characteristic polynomial here.}
+
 A rare neo-Y or neo-W will spread from a given ancestral equilibrium when the leading eigenvalue, $\lambda$, of the Jacobian matrix derived from the eight mutant recursion equations (given by \ref{eq:recursions}c,d,g,h), evaluated at the ancestral equilibrium, is greater than one.
-However, because a neo-Y (neo-W) is always in males (females) and is epistatically dominant to the ancestral sex-determining locus, we need only two recursion equations (e.g., tracking the change in the frequency of neo-Y-$A$ and neo-Y-$a$ gametes from males) and thus the leading eigenvalue is the largest solution to a quadratic characteristic polynomial $\lambda^2 + b\lambda + c = 0$.
-It can be shown (see supplementary Mathematica file) that the coefficients are $b= - (\lambda_{mA} + \lambda_{ma})+(\rho_{mA} + \rho_{ma})$ and $c = (\lambda_{mA}-\rho_{mA}) (\lambda_{ma}-\rho_{ma}) -\rho_{mA} \rho_{ma}$, where $\lambda_{mi}$ is the multiplicative growth rate of the frequency of mutants on background $i\in\{A,a\}$, without accounting for loss due to recombination, and $\rho_{mi}$ is the rate at which mutants on background $i\in\{A,a\}$ recombine onto the other \textbf{A} locus background in heterozygotes.
-The leading eigenvalue is then greater than one whenever $\lambda_{mA}>1$ and $\lambda_{ma}>1$, less than one whenever $\lambda_{mA}<1$ and $\lambda_{ma}<1$, and greater than one whenever  $\lambda_{mA}>1$ or $\lambda_{ma}>1$ and $\rho_{ma} (\lambda_{mA}-1) + \rho_{mA} (\lambda_{ma}-1) > 0$.
+However, because a neo-Y (neo-W) is always in males (females) and is epistatically dominant to the ancestral sex-determining locus, we need only two recursion equations (e.g., tracking the change in the frequency of neo-Y-$A$ and neo-Y-$a$ gametes from males) and thus the leading eigenvalue is the largest solution to a quadratic characteristic polynomial $\lambda^2 + b\lambda + c = 0$ as described in the text (Table \ref{tab:haplotype_growth}).
+%It can be shown (see supplementary Mathematica file) that the coefficients are $b= - (\lambda_{mA} + \lambda_{ma})+(\rho_{mA} + \rho_{ma})$ and $c = (\lambda_{mA}-\rho_{mA}) (\lambda_{ma}-\rho_{ma}) -\rho_{mA} \rho_{ma}$, where $\lambda_{mi}$ is the multiplicative growth rate of the frequency of mutants on background $i\in\{A,a\}$, without accounting for loss due to recombination, and $\rho_{mi}$ is the rate at which mutants on background $i\in\{A,a\}$ recombine onto the other \textbf{A} locus background in heterozygotes.
+%The leading eigenvalue is then greater than one whenever $\lambda_{mA}>1$ and $\lambda_{ma}>1$, less than one whenever $\lambda_{mA}<1$ and $\lambda_{ma}<1$, and greater than one whenever  $\lambda_{mA}>1$ or $\lambda_{ma}>1$ and $\rho_{ma} (\lambda_{mA}-1) + \rho_{mA} (\lambda_{ma}-1) > 0$.
 
 For tight linkage between the ancestral sex-determining locus and the selected locus we can calculate each of these terms exactly, while for weak selection we take a Taylor series of the leading eigenvalue.
-
-\subsubsection*{Recombination weak relative to selection (tight linkage between \textbf{A} and \textbf{X})}
-
-Here, we explore the conditions under which a neo-W invades an XY system assuming that the \textbf{A} locus is initially in close linkage with the ancestral sex-determining region ($r \approx 0$). 
-We disregard neo-Y mutations, which never spread given that the ancestral population is at a stable equilibrium.
+With weak selection, the leading eigenvalue, $\lambda$, for any $k$, is given up to order $\epsilon^2$ by equation \eqref{eq:lambda_ESD_k}.
+
+\subsubsection*{Tight linkage between \textbf{A} and \textbf{X} (recombination weak relative to selection)}
+
+Here, we explore the conditions under which a neo-W invades an XY system assuming that the \textbf{A} locus is initially in tight linkage with the ancestral sex-determining region ($r \approx 0$). 
+We disregard neo-Y mutations, which never spread given that the ancestral population is at a stable equilibrium (see supplementary \textit{Mathematica} notebook for proof).
 
@@
 \begin{align}
-\lambda_{mA}&= (2 \alpha^\male)^{-1}\frac{w_{A}^\female \left[w_{A}^\male w_{AA}^\female \alpha^\male + 2 w_{a}^\male w_{Aa}^\female \alpha^\female(1-\alpha^\male)\right]}{ w_{A}^\male w_{A}^\female w_{AA}^\female } \\
-\lambda_{ma}&= (2 \alpha^\male)^{-1} \frac{w_{a}^\female \left[ w_{a}^\male w_{aa}^\female (1-\alpha^\male) + 2 w_{A}^\male w_{Aa}^\female(1-\alpha^\female)\alpha^\male\right]}{w_{A}^\male w_{A}^\female w_{AA}^\female } \\
-\rho_{mA}&= (2 \alpha^\male)^{-1}\frac{R w_{a}^\male w_{A}^\female w_{Aa}^\female \alpha^\female(1-\alpha^\male)}{w_{A}^\male w_{A}^\female w_{AA}^\female } \\
-\rho_{ma}&= (2 \alpha^\male)^{-1}\frac{R w_{A}^\male w_{a}^\female w_{Aa}^\female (1-\alpha^\female)\alpha^\male}{w_{A}^\male w_{A}^\female w_{AA}^\female} 
+\lambda_{mA}&= (2 \alpha^\male w_{A}^\male)^{-1}
+\frac{w_{A}^\female }{w_{A}^\female}
+\frac{\left[w_{A}^\male \alpha^\male w_{AA}^\female + 
+w_{a}^\male (1-\alpha^\male) w_{Aa}^\female 2\alpha^\female\right]}
+{ w_{A}^\female w_{AA}^\female } \\
+\lambda_{ma}&= (2 \alpha^\male w_{A}^\male)^{-1} 
+\frac{w_{a}^\female}{w_{A}^\female}
+\frac{\left[ w_{A}^\male \alpha^\male w_{Aa}^\female2(1-\alpha^\female)+
+w_{a}^\male (1-\alpha^\male) w_{aa}^\female \right]}
+{ w_{A}^\female w_{AA}^\female } \\
+\rho_{mA}&= (2 \alpha^\male w_{A}^\male)^{-1}
+\frac{w_{A}^\female }{w_{A}^\female}
+\frac{R w_{a}^\male (1-\alpha^\male) w_{Aa}^\female  \alpha^\female}
+{ w_{AA}^\female } \\
+\rho_{ma}&= (2 \alpha^\male w_{A}^\male)^{-1}
+\frac{w_{a}^\female}{w_{A}^\female}
+\frac{R w_{A}^\male \alpha^\male w_{Aa}^\female (1-\alpha^\female)}
+{  w_{AA}^\female} 
 \end{align}
@@
 Haploid selection impacts the spread of neo-W haplotypes in three ways.
-Firstly, the zygotic sex ratio becomes male biased ($\zeta<1/2$; at equilibrium (B) the sex ratio is $\zeta = \alpha^\male w_A^\male / [(1-\alpha^\male)w_a^\male + \alpha^\male w_A^\male]$) when the $a$ allele (which is fixed on the Y) is favoured during competition among male gametes or by meiotic drive in males.
-This facilitates the spread of a neo-W because neo-W alleles cause the zygotes that carry them to develop as the rarer, female, sex. 
-Secondly, haploid selection in males affects the diploid genotypes of females by altering the allele frequencies in the male gametes that female gametes pair with.
-For instance, because an epistatically dominant neo-W always causes its carrier to become female, it creates females who carry either Y-$a$ or X genotypes from their father.
-Thus, because when there is a polymorphism the X carries some non-zero frequency of $A$, haploid selection in males impacts the diploid genotypes of females (e.g., creating more $Aa$ females when drive in males favours Y-$a$).
-How this affects the spread of the neo-W then depends on diploid and haploid selection in females.
-Thirdly, female drive and gamete competition directly select on neo-W haplotypes.
-Drive for $A$ in females favours neo-W-$A$ haplotypes, at a cost to neo-W-$a$ haplotypes, and vice-versa when there is drive for $a$.
-The impact of this drive depends on how often XX and neo-W females are heterozygous.
-Competition among female gametes acts similarly, and depends on the frequency of $A$ on resident X chromosomes (e.g., competition among eggs has no affect on the initial spread of the neo-W-$A$ haplotype when $A$ is fixed on the X).
-Because haploid selection in females favours one neo-W haplotype at the expense of the other, recombination off the favoured background becomes more detrimental as it becomes more favoured.
-Thus higher rates of recombination between the neo-W and the selected locus, $R$, can lead to smaller leading eigenvalues when there is haploid selection in females.
+Firstly, the zygotic sex ratio becomes male biased, $\zeta<1/2$, when the $a$ allele (which is fixed on the Y) is favoured during competition among male gametes or by meiotic drive in males.
+Specifically, at equilibrium $(B)$, the sex ratio is $\zeta = \alpha^\male w_A^\male / \bar{w}_{H}^\male$ where $\bar{w}_{H}^\male=[(1-\alpha^\male)w_a^\male + \alpha^\male w_A^\male]$ has been canceled in equations \eqref{Binvasion} to leave the term $(2 \alpha^\male w_{A}^\male)^{-1}$.
+Male biased sex ratios facilitate the spread of a neo-W because neo-W alleles cause the zygotes that carry them to develop as the rarer, female, sex.
+
+Secondly, haploid selection in females selects on neo-W haplotypes directly.
+At equilibrium $(B)$, the fitness of female gametes under the ancestral sex-determining system is $w_{A}^\female$ such that the relative fitnesses of neo-W-$A$ and neo-W-$a$ haplotypes during female gametic competition are $w_{A}^\female/w_{A}^\female$ and $w_{a}^\female/w_{A}^\female$, see terms in equation \eqref{Binvasion}.
+Meiotic drive in females will also change the proportion of gametes that carry the $A$ versus $a$ alleles, which will be produced by heterozygous females in proportions $(1+\alpha_{\Delta}^\female)$ and $(1-\alpha_{\Delta}^\female)$, respectively.
+These terms are only associated with heterozygous females, i.e., they are found alongside $w_{Aa}^\female$.
+
+Thirdly, haploid selection in males affects the diploid genotypes of females by altering the allele frequencies in the male gametes that female gametes pair with.
+At equlibrium $(B)$, neo-W female gametes will mate with X-$A$ male gametes with probability $\alpha^\male w_A^\male / \bar{w}_{H}^\male$ and Y-$a$ male gametes with probability $(1-\alpha^\male) w_a^\male / \bar{w}_{H}^\male$, where the $\bar{w}_{H}^\male$ terms have been canceled in \eqref{Binvasion}.
+Thus, for example, neo-W-$A$ haplotypes are found in $AA$ female diploids with probability $\alpha^\male w_A^\male / \bar{w}_{H}^\male$ (first term in square brackets in equation \ref{Binvasion}a) and in $Aa$ female diploids with probability $(1-\alpha^\male) w_a^\male / \bar{w}_{H}^\male$ (see equation \ref{Binvasion}c and second term in square brackets in equation \ref{Binvasion}a).
+
+%For instance, because an epistatically dominant neo-W always causes its carrier to become female, it creates females who carry either Y-$a$ or X-$A$ genotypes from their father.
+%Thus, because when there is a polymorphism the X carries some non-zero frequency of $A$, haploid selection in males impacts the diploid genotypes of females (e.g., creating more $Aa$ females when drive in males favours Y-$a$).
+%How this affects the spread of the neo-W then depends on diploid and haploid selection in females.
 
@@
 
-When both haplotypes can spread on their own ($\lambda_{mA}>1$ and $\lambda_{ma}>1$), the neo-W invades regardless the recombination rate between it and the selected locus, $R$.
-When neither haplotype can spread ($\lambda_{mA}<1$ and $\lambda_{ma}<1$) the neo-W can never invade.
-And when only one haplotype can spread on its own the neo-W invades only when the rate of recombination onto the favourable background is sufficiently larger than the rate of recombination off this background (i.e., equation\ref{eq:lambdasGen} is satisfied).
+%When both haplotypes can spread on their own ($\lambda_{mA}>1$ and $\lambda_{ma}>1$), the neo-W invades regardless the recombination rate between it and the selected locus, $R$.
+%When neither haplotype can spread ($\lambda_{mA}<1$ and $\lambda_{ma}<1$) the neo-W can never invade.
+%And when only one haplotype can spread on its own the neo-W invades only when the rate of recombination onto the favourable background is sufficiently larger than the rate of recombination off this background (i.e., equation\ref{eq:lambdasGen} is satisfied).
 
@@
 In contrast to equilibrium (B), a neo-W haplotype can spread under purely sexually-antagonistic selection  ($w_{AA}^\male>w_{Aa}^\male>w_{aa}^\male$ and $w_{AA}^\female>w_{Aa}^\female>w_{aa}^\female$).
-In this case, the neo-W-$A$ haplotype can spread, despite producing a lot of $Aa$ daughters by obtaining the $a$ from Y-gametes, when $aa$ females, which the neo-W-$A$ never makes, are strongly selected against.
-This can be intuited from the fact that \eqref{eq:BeqWAspread} will be more easily met when $w_{Aa}^\female-w_{aa}^\female\approx w_{Aa}^\female$ and $w_{AA}^\female-w_{Aa}^\female\approx 0$, implying $w_{aa}^\female \approx 0$ and $w_{Aa}^\female\approx w_{AA}^\female$ (although this is complicated by the fact that $w_{aa}^\female$ and $w_{Aa}^\female$ affect $\phi$ and $\psi$ too, the intuition holds).
+The neo-W-$A$ can spread as long as it becomes associated with females that bear more $A$ alleles than observed at equilibrium (A). 
+%In this case, the neo-W-$A$ haplotype can spread, despite producing a lot of $Aa$ daughters by obtaining the $a$ from Y-gametes, when $aa$ females, which the neo-W-$A$ never makes, are strongly selected against.
+%This can be intuited from the fact that \eqref{eq:BeqWAspread} will be more easily met when $w_{Aa}^\female-w_{aa}^\female\approx w_{Aa}^\female$ and $w_{AA}^\female-w_{Aa}^\female\approx 0$, implying $w_{aa}^\female \approx 0$ and $w_{Aa}^\female\approx w_{AA}^\female$ (although this is complicated by the fact that $w_{aa}^\female$ and $w_{Aa}^\female$ affect $\phi$ and $\psi$ too, the intuition holds).
 
@@
 For example, with overdominance in males there is selection for increased $A$ frequencies on X chromosomes in males, which are always paired with Y-$a$ haplotypes.
-Then, directional selection for $a$ in females maintains a polymorphism at the $\textbf{A}$ locus on the X and by creating selection for decreased $A$ frequencies on X chromosomes in females.
-This scenario selects for a modifier that increases recombination between the sex chromosomes \citep[e.g., blue region of Figure 2d in][]{Otto2014} and facilitates the spread of neo-W-$a$ haplotypes, which create more heterozygote and $aa$ females than ancestral X chromosomes do.
-
-As with equilibrium (B), if both haplotypes can spread ($\lambda_{mA}>1$ and $\lambda_{ma}>1$) then the neo-W invades under any rate of recombination with the selected locus, $R\geq0$. 
-In addition, even when only one haplotype can spread (e.g., under purely sexually-antagonistic selection $\lambda_{mA}>1$ and $\lambda_{ma}<1$), neo-W invasion can still occur under modest rates of recombination between the novel sex-determining and selected loci.
+Directional selection for $a$ in females can then maintain a polymorphism at the $\textbf{A}$ locus on the X.
+This scenario selects for a modifier that increases recombination between the sex chromosomes \citep[e.g., blue region of Figure 2d in][]{Otto2014} and facilitates the spread of neo-W-$a$ haplotypes, which create more females bearing more $a$ alleles than the ancestral X chromosome does.
+
+%As with equilibrium (B), if both haplotypes can spread ($\lambda_{mA}>1$ and $\lambda_{ma}>1$) then the neo-W invades under any rate of recombination with the selected locus, $R\geq0$. 
+%In addition, even when only one haplotype can spread (e.g., under purely sexually-antagonistic selection $\lambda_{mA}>1$ and $\lambda_{ma}<1$), neo-W invasion can still occur under modest rates of recombination between the novel sex-determining and selected loci.
 
@@
 Equilibria where the $A$ allele is more common among Y-bearing male gametes can also be stable for these parameters (blue lines). 
-The weak selection approximation only holds when all recombination rates are large relative to selection (around 0 in panels A and C), in which case neo-W alleles should spread if they are more tightly linked to the selected locus (positive invasion fitness in the grey region).
+The weak selection approximation holds when all recombination rates are large relative to selection (around 0 in panels A and C), in which case neo-W alleles should spread if they are more tightly linked to the selected locus (positive invasion fitness in the grey region).
+However, when linkage is tight (panels C and D and when the selected locus is near the SDR), this prediction breaks down. 
 Here, there is no haploid selection $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
@@
 In B, this leads to loss of the neo-W and the system goes to an equilibrium with X$a$ and Y$A$ haplotypes fixed (A'), such that all females have the high fitness genotype $aa$ and all males $Aa$. 
-For the parameters in B, neo-W invasion fitness when the Y$A$ haplotype is ancestrally more common than Y$a$ (see blue line in Figure \ref{fig:temporalOverdominance}B). 
-In contrast, the neo-W is not lost in panel D. 
+For the parameters in B, neo-W alleles have negative invasion fitness when the Y$A$ haplotype is ancestrally more common than Y$a$ (see blue line in Figure \ref{fig:temporalOverdominance}A and  \ref{fig:temporalOverdominance}B).
+In contrast, the neo-W is not lost in panel D (see blue line in Figure \ref{fig:temporalOverdominance}C and  \ref{fig:temporalOverdominance}D). 
 Fitness parameters are the same as in Figure \ref{fig:temporalOverdominance}, the $a$ allele is favoured in females ($w_{aa}^\female=1.05$, $w_{Aa}^\Hermaphrodite=1$, $w_{AA}^\female=0.85$) and there is overdominant selection in males ($w_{aa}^\male=w_{AA}^\male=0.75$) in panels A and B.
@@
 
+\newpage
+\textcolor{red}{
+Add Sally's figure showing lambda for small r near equil A versus near equil B.
+Add references to this figure to appendix where we discuss whether lambdas can be greater than 1 with sexually antagonistic selection.}
+
+\textcolor{red}{
+Check that we mention Sally's result that invasion cannot occur with sexually-antagonistic selection and $R=1/2$
+}
+
+\textcolor{red}{
+We could also give versions of Figure \ref{fig:regionplots} where there is also haploid selection of various types. I suggest using $\alpha_{\Delta}^\Hermaphrodite=1/20$ and $t^\Hermaphrodite=1/10$. 
+Haploid selection can favour $A$ or $a$, so this would involve 4x 6-panel figures. Started looking at this in RegionPlots.nb but haven't added gametic competition or labels for $\lambda$s. 
+Try to integrate into the discussion of haploid selection?}
+
+\textcolor{red}{
+Perhaps it would also be useful to add an 8 panel figure that features ploidally antagonistic selection.
+For each type of haploid selection (gametic competition/ meiotic drive in males/females), give a regionplot where $h^\male=h^\female$, e.g., $h^\male=h^\female=0.75$ (or perhaps the value of $h$ we use in the regionplots we have, in which $w_{aa}=0.85$, $w_{Aa}=1$, $w_{AA}=1.05$).
+Matt made a figure like this before but both Y$a$ and Y$A$ equilibria were plotted and there was no outline showing where the Y$a$ equilibrium is stable (as in Figure \ref{fig:regionplots}).
+In Matts plot the axes were $s^\Hermaphrodite$ and $\alpha_{\Delta}^\Hermaphrodite$.
+Add an asterisk to each region plot and show invasion in another panel, using those parameters and various $R$ (e.g., in the stye of \ref{fig:temporalOverdominance}). 
+In an email, Sally has an example of ploidally-antagonistic selection where the neo-W fixes and $R=1/2$. This would cover that case and more. }
+
+\textcolor{red}{
+Perhaps, for one set of parameters, we should plot the dynamics of all the different alleles.
+E.g., we could use the same parameters used in \ref{fig:SexRatioBad}.
+The main purpose would be to show what happens to the ancestral SDR during turnover.
+We could also show an example where XY and ZW sex determining systems are both polymorphic and stable.  
+}
+
 \end{document}

### 2017-08-25 LaTeX/Turnover.tex
new supp figures

@@
 %Overall, we demonstrate when and how the evolution of sex determining systems is impacted by sex ratio biases resulting from haploid selection and we show that new sex-determining regions can be favoured even if they are not closely linked with a locus under selection.
-Overall, our models reveal that transitions between sex-determination systems, particularly transitions where the heterogametic sex changes, can be driven by loci in unexpected genomic locations that experience selection during diploid and/or haploid phases, which might be reflected by the lability with which sex-determination systems evolve.
-%and for the factors determining the phylogenetic pattern of sex-determination systems.
+Overall, our models reveal that transitions between sex-determination systems, particularly transitions where the heterogametic sex changes, can be driven by loci in previously unexpected genomic locations that experience selection during diploid and/or haploid phases.
+These results might be reflected in the lability with which sex-determination systems evolve. %and for the factors determining the phylogenetic pattern of sex-determination systems. 
 \end{abstract}
@@
 Consequently, it is possible for selection on linked alleles to drive turnover between sex-determining systems despite causing transitory or even permanent increases in sex-ratio bias. 
-Another significant feature of our model is that we consider selection loci that are under selection and also in very tight linkage with the ancestral sex-determining region.
+In addition to considering haploid selection, another novel development in our model is that we consider loci that are under diploid and/or haploid selection and also in very tight linkage with the ancestral sex-determining region.
 Even in the absence of haploid selection, we show that transitions between male and female heterogamety can then evolve despite the fact that the neo-sex-determining locus is less closely linked to a locus under selection and therefore disrupts favourable ancestral associations between sex and the alleles selected in that sex.
@@
 For example, when the $a$ allele is favoured in males, a polymorphism of $A$ and $a$ alleles can be maintained on the X despite directional selection in favour of the $A$ allele in females ($s^\female>0$, $0<h^\female<1$).
-Indeed, Figure \ref{fig:regionplots}A indicates that $\lambda_{mA}$ tends to be larger than one with sexually-antagonistic selection where the $a$ allele is strongly favoured in males ($w_{aa}$ much larger than $w_{Aa}$).
-In this case, W-$A$ haplotypes will only create females with high fitness ($AA$ or $Aa$ genotypes) and therefore have higher fitness than ancestral females, which sometimes also produce $aa$ females. 
+Figure \ref{fig:regionplots}A indicates that $\lambda_{mA}$ tends to be larger than one with sexually-antagonistic selection where the $a$ allele is strongly favoured in males ($w_{aa}$ much larger than $w_{Aa}$).
+In this case the $a$ allele is at high frequency among XX females is high due to selection upon the X in males. 
+By contrast, W-$A$ haplotypes will only create females with high fitness ($AA$ or $Aa$ genotypes) and can therefore have higher fitness than ancestral females. 
 When only one neo-W haplotype can has a positive growth rate (see Figure \ref{fig:regionplots}), a neo-W can invade as long as equation \eqref{eq:lambdasGen} is satisfied, which may require that the recombination rate, $R$, is small enough.
@@
 
-Both W-$A$ and W-$a$ haplotypes can spread, as is the case when $AA$ individuals have low fitness in females yet the $A$ is polymorphic or fixed on the X due to overdominance in males (Figure \ref{fig:regionplots}B and \ref{fig:regionplots}C).
+In some cases, both W-$A$ and W-$a$ haplotypes can spread, e.g., when $AA$ individuals have low fitness in females yet the $A$ is polymorphic or fixed on the X due to overdominance in males (Figure \ref{fig:regionplots}B and \ref{fig:regionplots}C).
 Both neo-W-$A$ and neo-W-$a$ haplotypes then produce fewer unfit $AA$ females.
@@
 The green curves in Figure \ref{fig:SexRatioBad} demonstrate a case where transitions between male and female heterogametey occur even though the new sex-determining region is unlinked to a locus that experiences haploid and diploid selection.
-We use this example to discuss why heterogametic transitions can occur when $R=1/2$ and $r<1/2$, as in Table \ref{tab:specialcases}.
+We use these green curves to discuss why heterogametic transitions can occur when $R=1/2$ and $r<1/2$, as in Table \ref{tab:specialcases}.
 In Figure \ref{fig:SexRatioBad}B, an unlinked neo-W can spread because the zygotic sex ratio is ancestrally male biased. 
@@
 The neo-Y spreads because it produces males with high diploid fitness through matings with ancestral-W-bearing female gametes, which are more likely to carry the $A$ allele. 
-Thus, a key factor in explaining why heterogametic transitions can occur when $R>r$ is that that the neo-SDR determines sex in the diploid phase but then recombination occurs before any subsequent haploid selection.
+Thus, a key factor in explaining why heterogametic transitions can occur when $R>r$ is that that the neo-SDR determines sex in the diploid phase but recombination occurs before any subsequent haploid selection.
 
@@
 Sex-ratio biases caused by haploid selection can facilitate heterogametic transitions between sex-determining systems. 
-For instance, alleles favoured by haploid selection in males often become associated with the Y, which leads to a male sex-ratio bias.
+For instance, alleles favoured by haploid selection in males often become associated with the Y, which leads to a male-biased zygotic sex-ratio.
 This male bias increases the potential for a neo-W to invade (Table \ref{tab:haplotype_growth}), which can equalize the sex-ratio \citep[e.g., see Figure \ref{fig:SexRatioBad}B, for related examples see][]{Kozielska:2010vm,Ubeda:2015fx}.
@@
 %COMPARATIVE PATTERNS 
-We show that the spread of new sex determination systems can be driven by loci experiencing haploid selection. 
+We have shown that the spread of new sex determination systems can be driven by loci experiencing haploid selection. 
 Because haploid selection can cause transitions that increase or decrease sex-linkage, haploid selection may lead to less stability, and greater potential for cycling, in sex-determination systems (e.g., the final state of the red line in Figure \ref{fig:SexRatioBad}A is the starting state in Figure \ref{fig:SexRatioBad}B).
@@
 w_{a}^\male (1-\alpha^\male) w_{Aa}^\female 2\alpha^\female\right]}
-{ w_{A}^\female w_{AA}^\female } \\
+{ w_{AA}^\female } \\
 \lambda_{ma}&= (2 \alpha^\male w_{A}^\male)^{-1} 
@@
 w_{a}^\male (1-\alpha^\male) w_{aa}^\female \right]}
-{ w_{A}^\female w_{AA}^\female } \\
+{ w_{AA}^\female } \\
 \rho_{mA}&= (2 \alpha^\male w_{A}^\male)^{-1}
@@
 
-Similar equations can be derived for equilibrium (A) by subbing the equilibrium allele frequencies into Table \ref{tab:haplotype_growth}.
+Similar equations can be derived for equilibrium (A) by substituting the equilibrium allele frequencies into Table \ref{tab:haplotype_growth}.
 
@@
 where $\phi-\psi=w_{AA}^\female w_{Aa}^\male-w_{aa}^\female w_{aa}^\male$ and both $\phi$ and $\psi$ are positive when equilibrium (A) is stable. 
-In contrast to equilibrium (B), a neo-W haplotype can spread under purely sexually-antagonistic selection  ($w_{AA}^\male>w_{Aa}^\male>w_{aa}^\male$ and $w_{AA}^\female>w_{Aa}^\female>w_{aa}^\female$).
+In contrast to equilibrium (B), a neo-W haplotype can spread under purely sexually-antagonistic selection  ($w_{AA}^\male<w_{Aa}^\male<w_{aa}^\male$ and $w_{AA}^\female>w_{Aa}^\female>w_{aa}^\female$).
 The neo-W-$A$ can spread as long as it becomes associated with females that bear more $A$ alleles than observed at equilibrium (A). 
@@
 
+\begin{figure}[!h]
+\centering
+\centerline{\includegraphics[width=1.5\linewidth]{PositionPlot_SexAntagTighter_MaleDrive_Mike}}
+\caption{
+When there is haploid selection and sexually-antagonistic selection, a neo-W may invade for any $R$.
+\textcolor{red}{
+Check that we mention Sally's result that invasion cannot occur with sexually-antagonistic selection and $R=1/2$ (currently only in legend for figure \ref{fig:SexAntagTighter}) 
+Add asterisk to Figure \ref{fig:regionMaleDrive}B to show parameters used in this plot. 
+}
+$w_{aa}^\female=1.05$, $w_{Aa}^\Hermaphrodite=1$, $w_{AA}^\female=0.85$, $w_{aa}^\male=0.85$, $w_{AA}^\female=1.05$, $\alpha_{\Delta}^\male=-0.08$.
+}
+\label{fig:SexAntagTighterMaleDrive}
+\end{figure}
+
+\newpage
+\begin{figure}[!h]
+\centering
+\centerline{\includegraphics[width=\linewidth]{Region_Plot_combined_MaleGS_Mike}}
+\caption{
+ABC, $w_{a}^\male=1.16$, $w_{A}^\male=1$.
+DEF, $w_{a}^\male=1$, $w_{A}^\male=1.16$. 
+\textcolor{red}{I thought that re-running this with $w_{a}^\male=1.16$, $w_{A}^\male=0.84$ and $w_{a}^\male=0.84$, $w_{A}^\male=1.16$ will mean that it matches exactly with the meiotic drive example.
+Checking for panel A, the result was qualitatively similar (e.g., region where both $\lambda$'s are greater than one in panel A, as you might expect from equation \eqref{Binvasion}, however the region where a polymorphism is stable is also altered so they don't exactly match.
+}
+}
+\label{fig:regionMaleGS}
+\end{figure}
+
+\begin{figure}[!h]
+\centering
+\centerline{\includegraphics[width=\linewidth]{Region_Plot_combined_MaleDrive_Mike}}
+\caption{
+ABC, $\alpha_{\Delta}^\male=-0.08$
+DEF, $\alpha_{\Delta}^\male=0.08$. \textcolor{red}{Panel F mislabelled, should have $\lambda_{Wa}>1$ \& $\lambda_{WA}<1$ as the upper label that has the line.}
+}
+\label{fig:regionMaleDrive}
+\end{figure}
+
+\begin{figure}[!h]
+\centering
+\centerline{\includegraphics[width=\linewidth]{Region_Plot_combined_FemaleDrive_Mike}}
+\caption{
+ABC, $\alpha_{\Delta}^\female=-0.08$
+DEF, $\alpha_{\Delta}^\female=0.08$. $\lambda$s are increased for the haplotype that is favoured by female haploid selection, the stability conditions are also affected. 
+}
+\label{fig:regionFemaleDrive}
+\end{figure}
+
 \newpage
@@
 Add references to this figure to appendix where we discuss whether lambdas can be greater than 1 with sexually antagonistic selection.}
-
-\textcolor{red}{
-Check that we mention Sally's result that invasion cannot occur with sexually-antagonistic selection and $R=1/2$
-}
-
-\textcolor{red}{
-We could also give versions of Figure \ref{fig:regionplots} where there is also haploid selection of various types. I suggest using $\alpha_{\Delta}^\Hermaphrodite=1/20$ and $t^\Hermaphrodite=1/10$. 
-Haploid selection can favour $A$ or $a$, so this would involve 4x 6-panel figures. Started looking at this in RegionPlots.nb but haven't added gametic competition or labels for $\lambda$s. 
-Try to integrate into the discussion of haploid selection?}
 
@@
 \textcolor{red}{
+We could also give versions of Figure \ref{fig:regionplots} where there is also haploid selection of various types.
+Haploid selection can favour $A$ or $a$, so this would involve 4x 6-panel figures.
+Started looking at this in Figure \ref{fig:regionMaleGS} and Figure \ref{fig:regionMaleDrive}, add female haploid selection.
+Try to integrate into the discussion of haploid selection? e.g., male haploid selection ones generally show effect of sex ratio, increasing both lambdas when female biased (top rows).}
+
+\textcolor{red}{
 Perhaps, for one set of parameters, we should plot the dynamics of all the different alleles.
@@
 The main purpose would be to show what happens to the ancestral SDR during turnover.
-We could also show an example where XY and ZW sex determining systems are both polymorphic and stable.  
+We could also show an example where XY and ZW sex determining systems are both polymorphic and stable (e.g., using one of the curves in Figure \ref{fig:temporalOverdominance} and the green curve in Figure \ref{fig:SexAntagTighterMaleDrive}).
+I think there are also examples with looser sex linkage and pollen competition that lead to a mixed sex-determination system. We should probably have a short section in the appendix discussing this. 
 }

### 2017-09-13 LaTeX/Turnover.tex
replaced alpha with alpha triangle

@@
    neo-Y ($k=0$) \\ [0.5ex] \hline \noalign{\vskip 1ex}
-  $\lambda_{mA} = \left\{ 2 (1- \zeta) \right\}^{-1} \left[p_{X}^{\female} w_{A}^{\female} w_{A}^{\male} w_{AA}^{\male} + 2(1-p_{X}^{\female}) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} \alpha^\male \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right) $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\lambda_{ma} = \left\{ 2 (1- \zeta) \right\}^{-1} \left[(1-p_{X}^{\female}) w_{a}^{\female} w_{a}^{\male} w_{aa}^{\male} + 2p_{X}^{\female} w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male}(1 - \alpha^\male) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\rho_{mA} = R \left\{ 2 (1- \zeta) \right\}^{-1} \left[ 2(1-p_{X}^{\female}) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} \alpha^{\male} \right]/  \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right)   $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\rho_{ma} = R \left\{ 2 (1- \zeta) \right\}^{-1} \left[  2 p_{X}^{\female} w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male} (1 - \alpha^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right)  $\\ [1ex] \hline
+  $\lambda_{mA} = \left\{ 2 (1- \zeta) \right\}^{-1} \left[p_{X}^{\female} w_{A}^{\female} w_{A}^{\male} w_{AA}^{\male} + (1-p_{X}^{\female}) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} (1+\alpha_{\Delta}^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right) $\\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\lambda_{ma} = \left\{ 2 (1- \zeta) \right\}^{-1} \left[(1-p_{X}^{\female}) w_{a}^{\female} w_{a}^{\male} w_{aa}^{\male} + p_{X}^{\female} w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male}(1 - \alpha_{\Delta}^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\rho_{mA} = R \left\{ 2 (1- \zeta) \right\}^{-1} \left[ (1-p_{X}^{\female}) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} (1+\alpha_{\Delta}^{\male}) \right]/  \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right)   $\\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\rho_{ma} = R \left\{ 2 (1- \zeta) \right\}^{-1} \left[   p_{X}^{\female} w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male} (1 - \alpha_\Delta^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right)  $\\ [1ex] \hline
   \noalign{\vskip 0.5ex}
   neo-W ($k=1$) \\ [0.5ex] \hline \noalign{\vskip 1ex}
-  $\lambda_{mA} = \left( 2 \zeta \right)^{-1} \left[ \bar{p}^{\male} w_{A}^{\male} w_{A}^{\female} w_{AA}^{\female}+2(1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female}\alpha^\female\right]/ \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\lambda_{ma} = \left( 2 \zeta \right)^{-1} \left[ (1-\bar{p}^{\male}) w_{a}^{\male} w_{a}^{\female} w_{aa}^{\female}+2\bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female}(1-\alpha^\female)\right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\rho_{mA} = R \left( 2 \zeta \right)^{-1} \left[ 2(1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female} \alpha^{\female} \right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \right)  $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\rho_{ma} = R \left( 2 \zeta \right)^{-1} \left[ 2\bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female} (1-\alpha^{\female}) \right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \right) $\\ [1ex]
+  $\lambda_{mA} = \left( 2 \zeta \right)^{-1} \left[ \bar{p}^{\male} w_{A}^{\male} w_{A}^{\female} w_{AA}^{\female}+(1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female}(1+\alpha_{\Delta}^{\female})\right]/ \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\lambda_{ma} = \left( 2 \zeta \right)^{-1} \left[ (1-\bar{p}^{\male}) w_{a}^{\male} w_{a}^{\female} w_{aa}^{\female}+\bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female}(1-\alpha_{\Delta}^{\female})\right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\rho_{mA} = R \left( 2 \zeta \right)^{-1} \left[ (1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female} (1+\alpha_{\Delta}^{\female}) \right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \right)  $\\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\rho_{ma} = R \left( 2 \zeta \right)^{-1} \left[ \bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female} (1-\alpha_{\Delta}^{\female}) \right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \right) $\\ [1ex]
   \hline \hline 
@@
 %  $r<1/2$, $R=1/2$ &  \\ [0.5ex] \hline
-  male drive only & $h^\male=h^\female$, $t^\female=t^\male=\alpha^\female_{\Delta}=0$ & $s^\female s^\male>0$ \\
- female drive only & $h^\male=h^\female$, $t^\female=t^\male=\alpha^\male_{\Delta}=0$ & $s^\female s^\male>0$ \\
- sperm competition only &  $h^\male=h^\female$, $t^\female=\alpha^\female_{\Delta}=\alpha^\male_{\Delta}=0$ & $s^\female(s^\male-s^\female)>0$ \\
-  egg competition only & $h^\male=h^\female$, $t^\male=\alpha^\female_{\Delta}=\alpha^\male_{\Delta}=0$ & $s^\male(s^\female-s^\male)>0$ \\
+\noalign{\vskip 1mm}
+  male drive only & $h^\male=h^\female$, $t^\female=t^\male=\alpha^\female_{\Delta}=0$ & $s^\female s^\male>0$ \\ [0.5ex]
+ female drive only & $h^\male=h^\female$, $t^\female=t^\male=\alpha^\male_{\Delta}=0$ & $s^\female s^\male>0$ \\ [0.5ex]
+ sperm competition only &  $h^\male=h^\female$, $t^\female=\alpha^\female_{\Delta}=\alpha^\male_{\Delta}=0$ & $s^\female(s^\male-s^\female)>0$ \\ [0.5ex]
+  egg competition only & $h^\male=h^\female$, $t^\male=\alpha^\female_{\Delta}=\alpha^\male_{\Delta}=0$ & $s^\male(s^\female-s^\male)>0$ \\ [0.5ex]
   \hline \hline

### 2017-09-14 LaTeX/Turnover.tex
alpha and zeta issues being cleared up

@@
 \textcolor{red}{Change all  $\alpha^\Hermaphrodite$ to $(1+\alpha_{\Delta}^\Hermaphrodite)$.}
-
-\textcolor{red}{switch between $\chi$ and $\rho$ in all places because $\chi$ is used for double recombination events.}
-
-\textcolor{red}{Change $\zeta$ to represent zygotic sex ratio of males, consistent with $q$ and figures.}
+\textcolor{blue}{I've attempted this everywhere except in the recursions (S.1), which seem more natural with $\alpha$'s.
+I've run into trouble in equation S.8c,d -- I think we should check the Mathematica results to be sure we haven't made a typo.
+This also introduced an extra 1/2 in S.6c,d that might need to be explained.}
+
+\textcolor{red}{Switch between $\chi$ and $\rho$ in all places because $\chi$ is used for double recombination events.}
+\textcolor{blue}{I think we need a different variable given the $\rho$ terms in the characteristic polynomial.
+Also, where is $\chi$ used for double recombination?
+In other papers?
+Here $\chi$ is the probability of an odd number of cross-overs between the SDR and M loci.}
+
+%\textcolor{red}{Change $\zeta$ to represent zygotic sex ratio of males, consistent with $q$ and figures.}
 
@@
 
-The model outlined above describes both ancestrally-$XY$ and ancestrally-$ZW$ sex-determination systems if we relabel the two sexes as being ancestrally `heterogametic' or ancestrally `homogametic'. 
+The model outlined above describes both ancestrally-XY and ancestrally-ZW sex-determination systems if we relabel the two sexes as being ancestrally `heterogametic' or ancestrally `homogametic'. 
 Without loss of generality, we primarily refer to the ancestrally heterogametic sex as male and the ancestrally homogametic sex as female.
@@
    neo-Y ($k=0$) \\ [0.5ex] \hline \noalign{\vskip 1ex}
-  $\lambda_{mA} = \left\{ 2 (1- \zeta) \right\}^{-1} \left[p_{X}^{\female} w_{A}^{\female} w_{A}^{\male} w_{AA}^{\male} + (1-p_{X}^{\female}) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} (1+\alpha_{\Delta}^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right) $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\lambda_{ma} = \left\{ 2 (1- \zeta) \right\}^{-1} \left[(1-p_{X}^{\female}) w_{a}^{\female} w_{a}^{\male} w_{aa}^{\male} + p_{X}^{\female} w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male}(1 - \alpha_{\Delta}^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\rho_{mA} = R \left\{ 2 (1- \zeta) \right\}^{-1} \left[ (1-p_{X}^{\female}) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} (1+\alpha_{\Delta}^{\male}) \right]/  \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right)   $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\rho_{ma} = R \left\{ 2 (1- \zeta) \right\}^{-1} \left[   p_{X}^{\female} w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male} (1 - \alpha_\Delta^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right)  $\\ [1ex] \hline
+  $\lambda_{mA} = \left( 2 \zeta \right)^{-1} \left[p_{X}^{\female} w_{A}^{\female} w_{A}^{\male} w_{AA}^{\male} + (1-p_{X}^{\female}) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} (1+\alpha_{\Delta}^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right) $\\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\lambda_{ma} = \left( 2 \zeta \right)^{-1} \left[(1-p_{X}^{\female}) w_{a}^{\female} w_{a}^{\male} w_{aa}^{\male} + p_{X}^{\female} w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male}(1 - \alpha_{\Delta}^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\rho_{mA} = R \left( 2 \zeta \right)^{-1} \left[ (1-p_{X}^{\female}) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} (1+\alpha_{\Delta}^{\male}) \right]/  \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right)   $\\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\rho_{ma} = R \left( 2 \zeta \right)^{-1} \left[   p_{X}^{\female} w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male} (1 - \alpha_\Delta^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right)  $\\ [1ex] \hline
   \noalign{\vskip 0.5ex}
   neo-W ($k=1$) \\ [0.5ex] \hline \noalign{\vskip 1ex}
-  $\lambda_{mA} = \left( 2 \zeta \right)^{-1} \left[ \bar{p}^{\male} w_{A}^{\male} w_{A}^{\female} w_{AA}^{\female}+(1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female}(1+\alpha_{\Delta}^{\female})\right]/ \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\lambda_{ma} = \left( 2 \zeta \right)^{-1} \left[ (1-\bar{p}^{\male}) w_{a}^{\male} w_{a}^{\female} w_{aa}^{\female}+\bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female}(1-\alpha_{\Delta}^{\female})\right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\rho_{mA} = R \left( 2 \zeta \right)^{-1} \left[ (1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female} (1+\alpha_{\Delta}^{\female}) \right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \right)  $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\rho_{ma} = R \left( 2 \zeta \right)^{-1} \left[ \bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female} (1-\alpha_{\Delta}^{\female}) \right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \right) $\\ [1ex]
+  $\lambda_{mA} = \left[ 2 (1 - \zeta) \right]^{-1} \left[ \bar{p}^{\male} w_{A}^{\male} w_{A}^{\female} w_{AA}^{\female}+(1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female}(1+\alpha_{\Delta}^{\female})\right]/ \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\lambda_{ma} = \left[ 2 (1 - \zeta) \right]^{-1} \left[ (1-\bar{p}^{\male}) w_{a}^{\male} w_{a}^{\female} w_{aa}^{\female}+\bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female}(1-\alpha_{\Delta}^{\female})\right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\rho_{mA} = R \left[ 2 (1 - \zeta) \right]^{-1} \left[ (1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female} (1+\alpha_{\Delta}^{\female}) \right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \right)  $\\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\rho_{ma} = R \left[ 2 (1 - \zeta) \right]^{-1} \left[ \bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female} (1-\alpha_{\Delta}^{\female}) \right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \right) $\\ [1ex]
   \hline \hline 
@@
 %      \item $R$ is the probability of recombination between loci \textbf{A} and \textbf{M}.
-      \item $\zeta$ is the zygotic sex ratio (fraction female)
+      \item $\zeta$ is the zygotic sex ratio (fraction male)
       \item $\bar{w}^\Hermaphrodite$ is the mean fitness of diploids of sex $\Hermaphrodite$, see Table \ref{tab:meanfitnesses}
@@
 Table \ref{tab:haplotype_growth} illustrates a number of key points about the invasion of neo-Y and neo-W mutations. 
-First, Fisherian sex-ratio selection will favour the spread of a neo-Y if the ancestral zygotic sex ratio is biased towards females, $\zeta>1/2$ (i.e., $\zeta>1/2$ causes the first factor of the $\lambda_{mi}$ to be greater than one for a neo-Y and vice versa for a neo-W).
-However, the spread of a neo-Y (neo-W) also depends on the male (female) fitness of associated alleles (terms in square brackets). %, see terms in curly brackets. 
+First, Fisherian sex-ratio selection will favour the spread of a neo-Y if the ancestral zygotic sex ratio is biased towards females, $\zeta<1/2$ (i.e., the first factor of the $\lambda_{mi}$ is greater than one for a neo-Y and less than one for a neo-W).
+However, the spread of a neo-Y (neo-W) also depends on the male (female) fitness of associated alleles (terms involving equilibrium allele frequencies, $p$'s). %, see terms in curly brackets. 
 Second, invasion by a neo-Y (neo-W) allele does not directly depend on the fitness of female (male) diploids (for a given set of equilibrium allele frequencies).
@@
 \textcolor{red}{Change to $\hat{p}$ throughout as we assume that allele frequencies change slowly such that lambda is unaffected}
+\textcolor{how will we differentiate between equilibrium $p$ and non-equilibrium $p$? or is the point that we can only say anything when at equilibrium?}
 
@@
 Thus, invasion by a neo-W into an XY system and invasion by a neo-Y into a ZW system occur under the same conditions ($\lambda_{Y',XY}=\lambda_{W',ZW}$ and $\lambda_{Y',ZW}=\lambda_{W',XY}$, at least to order $\epsilon^2$).
-For example, in Figure \ref{fig:SexRatioBad}B neo-W alleles invade an ancestrally XY system where females are initially rare because the ancestral-Y is associated with a male meiotic drive allele.
-However, Figure \ref{fig:SexRatioBad}A shows that a neo-Y can invade an ancestrally ZW system under the same conditions. 
+For example, in Figure \ref{fig:SexRatioBad}B neo-W alleles invade an ancestrally-XY system where females are initially rare because the ancestral-Y is associated with a male meiotic drive allele.
+However, Figure \ref{fig:SexRatioBad}A shows that a neo-Y can invade an ancestrally-ZW system under the same conditions. 
 In fact, where $R<1/2$ the neo-Y becomes associated with the male meiotic drive allele such that the zygotic sex ratio evolves to become biased towards males.
@@
 %To shorten notation we now use index $i$ (and $j$) to denote the alleles at both the $\mathbf{A}$ and $\mathbf{M}$ loci and label $MA=1$, $Ma=2$, $mA=3$, and $ma=4$, such that $i,j\in\{1,2,3,4\}$.
-The frequencies of $XX$ zygotes are then denoted as $xx_{ij}$, $XY$ zygotes as $xy_{ij}$, and $YY$ zygotes as $yy_{ij}$, where \textbf{A} and \textbf{M} locus genotypes are given by $i,j\in\{1,2,3,4\}$, as above.
+The frequencies of XX zygotes are then denoted as $xx_{ij}$, XY zygotes as $xy_{ij}$, and YY zygotes as $yy_{ij}$, where \textbf{A} and \textbf{M} locus genotypes are given by $i,j\in\{1,2,3,4\}$, as above.
 In $XY$ zygotes, the haplotype inherited from an X-bearing gamete is given by $i$ and the haplotype from a Y-bearing gamete is given by $j$. 
-In $XX$ and $YY$ zygotes, individuals with diploid genotype $ij$ are equivalent to those with diploid genotype $ji$; for simplicity, we use $xx_{ij}$ and $yy_{ij}$ with $i\neq j$ to denote the average of these frequencies, $xx_{ij}=(x_{i}^{\female,s}x_{j}^{\male,s}+x_{j}^{\female,s}x_{i}^{\male,s})/2$ and $yy_{ij}=(y_{i}^{\female,s}y_{j}^{\male,s}+y_{j}^{\female,s}y_{i}^{\male,s})/2$.
+In XX and YY zygotes, individuals with diploid genotype $ij$ are equivalent to those with diploid genotype $ji$; for simplicity, we use $xx_{ij}$ and $yy_{ij}$ with $i\neq j$ to denote the average of these frequencies, $xx_{ij}=(x_{i}^{\female,s}x_{j}^{\male,s}+x_{j}^{\female,s}x_{i}^{\male,s})/2$ and $yy_{ij}=(y_{i}^{\female,s}y_{j}^{\male,s}+y_{j}^{\female,s}y_{i}^{\male,s})/2$.
 
 Denoting the \textbf{M} locus genotype by $b \in \{MM, Mm, mm\}$ and the \textbf{X} locus genotype by $c \in \{XX, XY, YY\}$, zygotes develop as females with probability $k_{bc}$. 
-Therefore, the frequencies of $XX$ females are given by $xx_{ij}^{\female}=k_{bc}xx_{ij}$, $XY$ females are given by $xy_{ij}^{\female}=k_{bc}xy_{ij}$, and $YY$ females are given by $yy_{ij}^{\female}=k_{bc}yy_{ij}$.
-Similarly, $XX$ male frequencies are $xx_{ij}^{\male}=(1-k_{bc})xx_{ij}$, $XY$ male frequencies are $xy_{ij}^{\male}=(1-k_{bc})xy_{ij}$, and $YY$ males frequencies are $yy_{ij}^{\male}=(1-k_{bc})yy_{ij}$.
-This notation allows both the ancestral and novel sex-determining regions to determine zygotic sex according to an $XY$ system, a $ZW$ system, or an environmental sex-determining system. 
+Therefore, the frequencies of XX females are given by $xx_{ij}^{\female}=k_{bc}xx_{ij}$, XY females are given by $xy_{ij}^{\female}=k_{bc}xy_{ij}$, and YY females are given by $yy_{ij}^{\female}=k_{bc}yy_{ij}$.
+Similarly, XX male frequencies are $xx_{ij}^{\male}=(1-k_{bc})xx_{ij}$, XY male frequencies are $xy_{ij}^{\male}=(1-k_{bc})xy_{ij}$, and YY males frequencies are $yy_{ij}^{\male}=(1-k_{bc})yy_{ij}$.
+This notation allows both the ancestral and novel sex-determining regions to determine zygotic sex according to an XY system, a ZW system, or an environmental sex-determining system. 
 In addition, we can consider any epistatic dominance relationship between the two sex-determining loci. 
-Here, we assume that the ancestral sex-determining system (\textbf{X} locus) is $XY$ ($k_{MMXX}=1$ and $k_{MMXY}=k_{MMYY}=0$) or $ZW$ ($k_{MMZZ}=0$ and $k_{MMZW}=k_{MMWW}=1$) and epistatically recessive to a dominant novel sex-determining locus, \textbf{M} ($k_{Mmc}=k_{mmc}=k$).
+Here, we assume that the ancestral sex-determining system (\textbf{X} locus) is XY ($k_{MMXX}=1$ and $k_{MMXY}=k_{MMYY}=0$) or ZW ($k_{MMZZ}=0$ and $k_{MMZW}=k_{MMWW}=1$) and epistatically recessive to a dominant novel sex-determining locus, \textbf{M} ($k_{Mmc}=k_{mmc}=k$).
 
@@
 \smallskip
-\caption{mean fitnesses in the resident population ($M$ fixed, XY sex determination) }
+\caption{Mean fitnesses and zygotic sex ratio in the resident population ($M$ fixed, XY sex determination). }
 \begin{tabular}{l l }
@@
   females ($\bar{w}^\female$) & 
-  $\begin{array}{l}  \{ p_X^\female w_A^\female p_X^\male w_A^\male w_{AA}^\female + \\
+  $\begin{array}{l}  (1-\zeta)^{-1} \big[ p_X^\female w_A^\female p_X^\male w_A^\male w_{AA}^\female + \\
   (1 - p_X^\female) w_a^\female p_X^\male w_A^\male w_{Aa}^\female + \\
   p_X^\female w_A^\female (1 - p_X^\male) w_a^\male w_{Aa}^\female + \\
-  (1-p_X^\female) w_a^\female (1 - p_X^\male) w_a^\male w_{aa}^\female \} / \{ \bar{w}_H^\female \bar{w}_H^\male \zeta \}
+  (1-p_X^\female) w_a^\female (1 - p_X^\male) w_a^\male w_{aa}^\female \big] / \left( \bar{w}_H^\female \bar{w}_H^\male \right)
   \end{array} 
-  $ \\ [0.5ex] \hline  \noalign{\vskip 0.5ex}
+  $ \\ [0.5ex] \noalign{\vskip 0.5ex} \hline  \noalign{\vskip 0.5ex}
   males ($\bar{w}^\male$) & 
-  $\begin{array}{l} \{ p_X^\female w_A^\female  p_Y^\male w_A^\male w_{AA}^\male + \\
+  $\begin{array}{l} \zeta^{-1} \big[ p_X^\female w_A^\female  p_Y^\male w_A^\male w_{AA}^\male + \\
   (1 - p_X^\female) w_a^\female  p_Y^\male w_A^\male w_{Aa}^\male + \\
   p_X^\female w_A^\female  (1 - p_Y^\male) w_a^\male w_{Aa}^\male + \\
-  (1-p_X^\female) w_a^\female  (1 - p_Y^\male) w_a^\male w_{aa}^\male \} / \{ \bar{w}_H^\female \bar{w}_H^\male (1-\zeta)\} 
+  (1-p_X^\female) w_a^\female  (1 - p_Y^\male) w_a^\male w_{aa}^\male \big] / \left( \bar{w}_H^\female \bar{w}_H^\male \right) 
   \end{array}
-  $ \\ [0.5ex] \hline  \noalign{\vskip 0.5ex}
-  zygotic sex ratio $\zeta$ & $\{ (1-q)(p_X^\male w_A^\male+(1-p_X^\male)w_a^\male)\} / \bar{w}_H^\male $
+  $ \\ [0.5ex] \noalign{\vskip 0.5ex} \hline  \noalign{\vskip 0.5ex}
+  fraction zygotes male ($\zeta$) & $q \left[ p_Y^\male w_A^\male+(1-p_Y^\male)w_a^\male\right] / \bar{w}_H^\male $
    \\ [0.5ex]  \noalign{\vskip 0.5ex}
@@
 (A)\ \ \ &\hat{p}_{Y}^{\male}=0,
-\ \hat{q}=\frac{1}{2}-\frac{(\alpha^{\male}-1/2)w_{Aa}^{\male} \phi}{w_{Aa}^{\male} \phi+ w_{aa}^{\male} \psi},\\
+\ \hat{q}=\frac{1}{2} - \alpha_\Delta^\male \frac{ w_{Aa}^{\male} \phi}{w_{Aa}^{\male} \phi+ w_{aa}^{\male} \psi},\\
 &\hat{p}_{X}^{\female}=\frac{w_{a}^{\female} \phi}{w_{a}^{\female} \phi+ w_{A}^{\female} \psi},
-\ \hat{p}_{X}^{\male}=\frac{2 \alpha^{\male}w_{Aa}^{\male} \phi}{2\alpha^{\male}w_{Aa}^{\male} \phi +w_{AA}^{\male} \psi} \nonumber \\
+\ \hat{p}_{X}^{\male}=\frac{(1+\alpha_\Delta^\male)w_{Aa}^{\male} \phi}{(1+\alpha_\Delta^\male)w_{Aa}^{\male} \phi +w_{AA}^{\male} \psi} \nonumber \\
 (A')\ \ \ &\hat{p}_{Y}^{\male}=1,
-\ \hat{q}=\frac{1}{2}+\frac{(\alpha^{\male}-1/2)w_{Aa}^{\male} \phi'}{w_{Aa}^{\male} \phi' + w_{AA}^{\male} \psi'},\\
+\ \hat{q}=\frac{1}{2} + \alpha_\Delta^\male \frac{w_{Aa}^{\male} \phi'}{w_{Aa}^{\male} \phi' + w_{AA}^{\male} \psi'},\\
 &\hat{p}_{X}^{\female}=1-\frac{w_{A}^{\female} \phi'}{w_{A}^{\female} \phi'+ w_{a}^{\female} \psi'},
-\ \hat{p}_{X}^{\male}=1-\frac{2(1-\alpha^{\male})w_{Aa}^{\male} \phi'}{2(1-\alpha^{\male})w_{Aa}^{\male} \phi'+w_{aa}^{\male} \psi'} \nonumber \\
-(B)\ \ \ &\hat{p}_{Y}^{\male}=0,\ \hat{p}_{X}^{\female}=1,\ \hat{p}_{X}^{\male}=1, \ \hat{q}=1-\alpha^{\male}\\
-(B')\ \ \ &\hat{p}_{Y}^{\male}=1,\ \hat{p}_{X}^{\female}=0,\ \hat{p}_{X}^{\male}=0, \ \hat{q}=\alpha^{\male}
+\ \hat{p}_{X}^{\male}=1-\frac{(1-\alpha_\Delta^\male)w_{Aa}^{\male} \phi'}{(1-\alpha_\Delta^\male)w_{Aa}^{\male} \phi'+w_{aa}^{\male} \psi'} \nonumber \\
+(B)\ \ \ &\hat{p}_{Y}^{\male}=0,\ \hat{p}_{X}^{\female}=1,\ \hat{p}_{X}^{\male}=1, \ \hat{q}=(1 -\alpha^\male_\Delta)/2\\
+(B')\ \ \ &\hat{p}_{Y}^{\male}=1,\ \hat{p}_{X}^{\female}=0,\ \hat{p}_{X}^{\male}=0, \ \hat{q}=(1+\alpha^\male_\Delta)/2
 \end{align}
@@
 \begin{split}
-\phi=&\alpha^{\female} w_{A}^{\female} w_{Aa}^{\female}(w_{a}^{\male} w_{aa}^{\male} + 2 \alpha^{\male} w_{A}^{\male} w_{Aa}^{\male}) - w_{a}^{\male} w_{a}^{\female} w_{aa}^{\male} w_{aa}^{\female} \\
-\psi=&(1-\alpha^{\female}) w_{a}^{\female} w_{Aa}^{\female}(w_{a}^{\male} w_{aa}^{\male} + 2 \alpha^{\male} w_{A}^{\male} w_{Aa}^{\male}) - 2\alpha^{\male} w_{A}^{\male} w_{A}^{\female} w_{Aa}^{\male} w_{AA}^{\female}\\
-\phi'=&(1-\alpha^{\female}) w_{a}^{\female} w_{Aa}^{\female}(w_{A}^{\male} w_{AA}^{\male} + 2 (1-\alpha^{\male}) w_{a}^{\male} w_{Aa}^{\male}) - w_{A}^{\male} w_{A}^{\female} w_{AA}^{\male} w_{AA}^{\female}\\
-\psi'=&\alpha^{\female} w_{A}^{\female} w_{Aa}^{\female}(w_{A}^{\male} w_{AA}^{\male} + 2 (1-\alpha^{\male}) w_{a}^{\male} w_{Aa}^{\male}) - 2(1-\alpha^{\male}) w_{a}^{\male} w_{a}^{\female} w_{Aa}^{\male} w_{aa}^{\female}
+\phi=&(1+\alpha^\female_\Delta) w_{A}^{\female} w_{Aa}^{\female} \left[ w_{a}^{\male} w_{aa}^{\male} + (1+\alpha_\Delta^\male) w_{A}^{\male} w_{Aa}^{\male} \right]/2 - w_{a}^{\male} w_{a}^{\female} w_{aa}^{\male} w_{aa}^{\female} \\
+\psi=&(1-\alpha^\female_\Delta) w_{a}^{\female} w_{Aa}^{\female} \left[ w_{a}^{\male} w_{aa}^{\male} + (1+\alpha_\Delta^\male) w_{A}^{\male} w_{Aa}^{\male}\right]/2 - (1+\alpha_\Delta^\male) w_{A}^{\male} w_{A}^{\female} w_{Aa}^{\male} w_{AA}^{\female}\\
+\phi'=&(1-\alpha^\female_\Delta) w_{a}^{\female} w_{Aa}^{\female} \left[ w_{A}^{\male} w_{AA}^{\male} + (1-\alpha_\Delta^\male) w_{a}^{\male} w_{Aa}^{\male} \right]/2 - w_{A}^{\male} w_{A}^{\female} w_{AA}^{\male} w_{AA}^{\female}\\
+\psi'=&(1+\alpha^\female_\Delta) w_{A}^{\female} w_{Aa}^{\female} \left[ w_{A}^{\male} w_{AA}^{\male} + (1-\alpha_\Delta^\male) w_{a}^{\male} w_{Aa}^{\male} \right]/2 - (1-\alpha_\Delta^\male) w_{a}^{\male} w_{a}^{\female} w_{Aa}^{\male} w_{aa}^{\female}
 \end{split}
@@
 Since equilibria $(A)$ and $(B)$ are equivalent to equilibria $(A')$ and $(B')$ with the labelling of $A$ and $a$ alleles interchanged, we discuss only equilibria $(A)$ and $(B)$, in which the Y is fixed for the $a$ allele.
-If there is no haploid selection ($\alpha^{\Hermaphrodite}=1/2$, $w_{A}^{\Hermaphrodite}=w_{a}^{\Hermaphrodite}=1$), these equilibria are equivalent to those found by \cite{Lloyd1977} and \cite{Otto2014}.
+If there is no haploid selection ($\alpha^{\Hermaphrodite}_\Delta=0$, $w_{A}^{\Hermaphrodite}=w_{a}^{\Hermaphrodite}=1$), these equilibria are equivalent to those found by \cite{Lloyd1977} and \cite{Otto2014}.
 
@@
 According to the `small parameter theory' \citep{Karlin:1972ab,Karlin:1972dq}, these stability properties are unaffected by small amounts of recombination between the SDR and \textbf{A} locus, although equilibrium frequencies may be slightly altered.
-For the $a$ allele to be stably fixed on the Y is stable if $\bar{w}_{Ya}^{\male}>\bar{w}_{YA}^{\male}$ where $\bar{w}_{Ya}^{\male}=w_{a}^{\male}(2 p_{X}^{\female}(1-\alpha^{\male}) w_{A}^{\female} w_{Aa}^{\male}+ (1-p_{X}^{\female})w_{a}^{\female} w_{aa}^{\male} )$ and $\bar{w}_{YA}^{\male}=w_{A}^{\male}(p_{X}^{\female} w_{A}^{\female} w_{AA}^{\male}+ 2 (1-p_{X}^{\female})\alpha^{\male}w_{a}^{\female} w_{Aa}^{\male} )$.
-That is, $Ya$ haplotypes must have higher fitness than $YA$ haplotypes.
-Substituting in $p_{X}^{\female} = \hat{p}_{X}^{\female}$ from above, fixation of the $a$ allele on the Y requires that $\gamma_{i}>0$ where $\gamma_{(A)}=w_{a}^{\male}(2(1-\alpha^{\male})w_{Aa}^{\male} \phi + w_{aa}^{\male} \psi)-w_{A}^{\male}( w_{AA}^{\male} \phi + 2\alpha^{\male}w_{Aa}^{\male} \psi)$ for equilibrium $(A)$ and $\gamma_{(B)}=2(1-\alpha^{\male})w_{a}^{\male}w_{Aa}^{\male}-w_{A}^{\male}w_{AA}^{\male}$ for equilibrium $(B)$.
+For the $a$ allele to be stably fixed on the Y we need $\bar{w}_{Ya}^{\male} > \bar{w}_{YA}^{\male}$ where $\bar{w}_{Ya}^{\male} = w_{a}^{\male} \big[p_{X}^{\female}(1-\alpha^\male_\Delta) w_{A}^{\female} w_{Aa}^{\male} + (1-p_{X}^{\female})w_{a}^{\female} w_{aa}^{\male} \big]$ and $\bar{w}_{YA}^{\male} = w_{A}^{\male} \big[ p_{X}^{\female} w_{A}^{\female} w_{AA}^{\male} + (1-p_{X}^{\female})(1+\alpha^\male_\Delta) w_{a}^{\female} w_{Aa}^{\male} \big]$.
+That is, Y-$a$ haplotypes must have higher fitness than Y-$A$ haplotypes.  
+Substituting in $p_{X}^{\female} = \hat{p}_{X}^{\female}$ from above, fixation of the $a$ allele on the Y requires that $\gamma_{i}>0$ where $\gamma_{(A)}=w_{a}^{\male} \big[ (1-\alpha^\male_\Delta) w_{Aa}^{\male} \phi + w_{aa}^{\male} \psi \big]-w_{A}^{\male} \big[ w_{AA}^{\male} \phi + (1 + \alpha^{\male}_\Delta)w_{Aa}^{\male} \psi \big]$ for equilibrium $(A)$ and $\gamma_{(B)}=(1-\alpha^{\male}_\Delta)w_{a}^{\male}w_{Aa}^{\male}-w_{A}^{\male}w_{AA}^{\male}$ for equilibrium $(B)$.
 Stability of a polymorphism on the X chromosome (equilibrium $A$) further requires that $\phi >0$ and $\psi >0$. 
@@
 \begin{split}
-0&<-((1-h^\female)s^\female +(1-h^\male) s^\male + t^\female +t^\male + \alpha_{\Delta}^\female+\alpha_{\Delta}^\male)\\
-%
-\text{and }\quad 0&<(h^\female s^\female +h^\male s^\male + t^\female +t^\male + \alpha_{\Delta}^\female+\alpha_{\Delta}^\male).
+0&< - \left[(1-h^\female)s^\female +(1-h^\male) s^\male + t^\female +t^\male + \alpha_{\Delta}^\female+\alpha_{\Delta}^\male\right]\\
+%
+\text{and }\quad 0&<h^\female s^\female +h^\male s^\male + t^\female +t^\male + \alpha_{\Delta}^\female+\alpha_{\Delta}^\male.
 \end{split}
@@
 %
-\hat{p}^\male_Y-\hat{p}^\female_X&=V_{A}\big{(}D^\male - D^\female+\alpha_{\Delta}^\male-\alpha_{\Delta}^\female+(1-2r)(t^\male-t^\female)\big{)}/2r
+\hat{p}^\male_Y-\hat{p}^\female_X&=V_{A}\left[D^\male - D^\female+\alpha_{\Delta}^\male-\alpha_{\Delta}^\female+(1-2r)(t^\male-t^\female)\right]/2r
 +O(\epsilon^2)\\
 %
-\hat{p}^\male_Y-\hat{p}^\male_X&=V_{A}\big{(}D^\male - D^\female+\alpha_{\Delta}^\male-\alpha_{\Delta}^\female+t^\male-t^\female\big{)}(1-2r)/2r
+\hat{p}^\male_Y-\hat{p}^\male_X&=V_{A}\left(D^\male - D^\female+\alpha_{\Delta}^\male-\alpha_{\Delta}^\female+t^\male-t^\female\right)(1-2r)/2r
 +O(\epsilon^2)
@@
 \noindent
-where $V_{A}=\bar{p}(1-\bar{p})$ is the variance in the frequency of $A$ and $D^\Hermaphrodite=\big{(} \bar{p}s^\Hermaphrodite+(1-\bar{p})h^\Hermaphrodite s^\Hermaphrodite\big{)} -\big{(} \bar{p}h^\Hermaphrodite s^\Hermaphrodite+(1-\bar{p}) \big{)}$ corresponds to the difference in fitness between $A$ and $a$ alleles in diploids of sex $\Hermaphrodite \in \{\female,\male\}$ ($\bar{p}$ is the leading-order probability of mating with an $A$-bearing gamete from the opposite sex).
+where $V_{A}=\bar{p}(1-\bar{p})$ is the variance in the frequency of $A$ and $D^\Hermaphrodite=\big{[} \bar{p}s^\Hermaphrodite+(1-\bar{p})h^\Hermaphrodite s^\Hermaphrodite\big{]} -\big{[} \bar{p}h^\Hermaphrodite s^\Hermaphrodite+(1-\bar{p}) \big{]}$ corresponds to the difference in fitness between $A$ and $a$ alleles in diploids of sex $\Hermaphrodite \in \{\female,\male\}$ ($\bar{p}$ is the leading-order probability of mating with an $A$-bearing gamete from the opposite sex).
 The frequency of Y among male gametes depends upon the difference in the frequency of the $A$ allele between X- and Y-bearing male gametes and the strength of meiotic drive in favour of the $A$ allele in males, $q=1/2+\alpha_{\Delta}^\male(\hat{p}^\male_Y-\hat{p}^\male_X)/2+O(\epsilon^3)$.
@@
 \begin{align}
-\lambda_{mA}&= (2 \alpha^\male w_{A}^\male)^{-1}
+\lambda_{mA}&= \left[w_{a}^\male (1-\alpha^\male_\Delta) \right]^{-1}
 \frac{w_{A}^\female }{w_{A}^\female}
-\frac{\left[w_{A}^\male \alpha^\male w_{AA}^\female + 
-w_{a}^\male (1-\alpha^\male) w_{Aa}^\female 2\alpha^\female\right]}
-{ w_{AA}^\female } \\
-\lambda_{ma}&= (2 \alpha^\male w_{A}^\male)^{-1} 
+\frac{\left[ w_{A}^\male (1+\alpha^\male_\Delta) w_{AA}^\female + 
+w_{a}^\male (1-\alpha^\male_\Delta) w_{Aa}^\female (1+\alpha^\female_\Delta) \right]}
+{ 2w_{AA}^\female } \\
+\lambda_{ma}&= \left[w_{a}^\male (1-\alpha^\male_\Delta) \right]^{-1}
 \frac{w_{a}^\female}{w_{A}^\female}
-\frac{\left[ w_{A}^\male \alpha^\male w_{Aa}^\female2(1-\alpha^\female)+
-w_{a}^\male (1-\alpha^\male) w_{aa}^\female \right]}
-{ w_{AA}^\female } \\
-\rho_{mA}&= (2 \alpha^\male w_{A}^\male)^{-1}
+\frac{\left[  w_{A}^\male (1+\alpha^\male_\Delta) w_{Aa}^\female (1-\alpha^\female_\Delta)+
+w_{a}^\male (1-\alpha^\male_\Delta) w_{aa}^\female \right]}
+{ 2w_{AA}^\female } \\
+\rho_{mA}&= \frac{1}{2} \left[w_{a}^\male (1-\alpha^\male_\Delta) \right]^{-1}
 \frac{w_{A}^\female }{w_{A}^\female}
-\frac{R w_{a}^\male (1-\alpha^\male) w_{Aa}^\female  \alpha^\female}
-{ w_{AA}^\female } \\
-\rho_{ma}&= (2 \alpha^\male w_{A}^\male)^{-1}
+ \frac{\left[  w_{a}^\male (1-\alpha^\male_\Delta) w_{Aa}^\female (1 + \alpha^\female_\Delta) \right]}
+{ w_{AA}^\female } \frac{R}{2}\\
+\rho_{ma}&= \frac{1}{2} \left[w_{a}^\male (1-\alpha^\male_\Delta) \right]^{-1}
 \frac{w_{a}^\female}{w_{A}^\female}
-\frac{R w_{A}^\male \alpha^\male w_{Aa}^\female (1-\alpha^\female)}
-{  w_{AA}^\female} 
+ \frac{\left[  w_{A}^\male (1+\alpha^\male_\Delta) w_{Aa}^\female (1-\alpha^\female_\Delta) \right]}
+{  w_{AA}^\female} \frac{R}{2}
 \end{align}
@@
 Haploid selection impacts the spread of neo-W haplotypes in three ways.
-Firstly, the zygotic sex ratio becomes male biased, $\zeta<1/2$, when the $a$ allele (which is fixed on the Y) is favoured during competition among male gametes or by meiotic drive in males.
-Specifically, at equilibrium $(B)$, the sex ratio is $\zeta = \alpha^\male w_A^\male / \bar{w}_{H}^\male$ where $\bar{w}_{H}^\male=[(1-\alpha^\male)w_a^\male + \alpha^\male w_A^\male]$ has been canceled in equations \eqref{Binvasion} to leave the term $(2 \alpha^\male w_{A}^\male)^{-1}$.
+Firstly, the zygotic sex ratio becomes male biased, $\zeta>1/2$, when the $a$ allele (which is fixed on the Y) is favoured during competition among male gametes or by meiotic drive in males.
+Specifically, at equilibrium $(B)$, the sex ratio is $\zeta = w_a^\male (1-\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$ where $2\bar{w}_{H}^\male= \big[w_a^\male (1-\alpha^\male_\Delta) +  w_A^\male (1+\alpha^\male_\Delta) \big]$ has been canceled out in equations \eqref{Binvasion} to leave the term $\left[w_{a}^\male (1-\alpha^\male_\Delta) \right]^{-1}$.
 Male biased sex ratios facilitate the spread of a neo-W because neo-W alleles cause the zygotes that carry them to develop as the rarer, female, sex.
@@
 Secondly, haploid selection in females selects on neo-W haplotypes directly.
-At equilibrium $(B)$, the fitness of female gametes under the ancestral sex-determining system is $w_{A}^\female$ such that the relative fitnesses of neo-W-$A$ and neo-W-$a$ haplotypes during female gametic competition are $w_{A}^\female/w_{A}^\female$ and $w_{a}^\female/w_{A}^\female$, see terms in equation \eqref{Binvasion}.
+At equilibrium $(B)$, the fitness of female gametes under the ancestral sex-determining system is $w_{A}^\female$ such that the relative fitnesses of neo-W-$A$ and neo-W-$a$ haplotypes during female gametic competition are $w_{A}^\female/w_{A}^\female$ and $w_{a}^\female/w_{A}^\female$ (see terms in equation \ref{Binvasion}).
 Meiotic drive in females will also change the proportion of gametes that carry the $A$ versus $a$ alleles, which will be produced by heterozygous females in proportions $(1+\alpha_{\Delta}^\female)$ and $(1-\alpha_{\Delta}^\female)$, respectively.
@@
 Thirdly, haploid selection in males affects the diploid genotypes of females by altering the allele frequencies in the male gametes that female gametes pair with.
-At equlibrium $(B)$, neo-W female gametes will mate with X-$A$ male gametes with probability $\alpha^\male w_A^\male / \bar{w}_{H}^\male$ and Y-$a$ male gametes with probability $(1-\alpha^\male) w_a^\male / \bar{w}_{H}^\male$, where the $\bar{w}_{H}^\male$ terms have been canceled in \eqref{Binvasion}.
-Thus, for example, neo-W-$A$ haplotypes are found in $AA$ female diploids with probability $\alpha^\male w_A^\male / \bar{w}_{H}^\male$ (first term in square brackets in equation \ref{Binvasion}a) and in $Aa$ female diploids with probability $(1-\alpha^\male) w_a^\male / \bar{w}_{H}^\male$ (see equation \ref{Binvasion}c and second term in square brackets in equation \ref{Binvasion}a).
+At equlibrium $(B)$, neo-W female gametes will mate with X-$A$ male gametes with probability $ w_A^\male (1+\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$ and Y-$a$ male gametes with probability $w_a^\male (1-\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$, where the $2\bar{w}_{H}^\male$ terms have been canceled in equation \eqref{Binvasion} (as mentioned above).
+Thus, for example, neo-W-$A$ haplotypes are found in $AA$ female diploids with probability $ w_A^\male (1+\alpha^\male_\Delta)/ (2\bar{w}_{H}^\male)$ (first term in square brackets in the numerate of equation \ref{Binvasion}a) and in $Aa$ female diploids with probability $w_a^\male (1-\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$ (see equation \ref{Binvasion}c and second term in square brackets in the numerator of equation \ref{Binvasion}a).
 
@@
 The other terms in equations \eqref{Binvasion} are more easily interpreted if we assume that there is no haploid selection in either sex, in which case $\lambda_{mA}>1$ when $w_{Aa}^\female>w_{AA}^\female$ and $\lambda_{ma}>1$ when $(w_{Aa}^\female+w_{aa}^\female)/2>w_{AA}^\female$.
-These conditions cannot be met under purely sexually-antagonistic selection, where $a$ is directionally favoured in males ($w_{AA}^\male>w_{Aa}^\male>w_{aa}^\male$) and $A$ is directionally favoured in females ($w_{AA}^\female>w_{Aa}^\female>w_{aa}^\female$).
-Essentially, the X is already as specialized as possible for the female beneficial allele (X$A$ is fixed), and the neo-W often makes daughters with the Y-a haplotype, increasing the flow of $a$ alleles into females, which reduces the fitness of those females.
+These conditions cannot be met under purely sexually-antagonistic selection, where $A$ is directionally favoured in females ($w_{AA}^\female>w_{Aa}^\female>w_{aa}^\female$) and $a$ is directionally favoured in males ($w_{AA}^\male>w_{Aa}^\male>w_{aa}^\male$).
+Essentially, the X is then already as specialized as possible for the female beneficial allele ($A$ is fixed on the X), and the neo-W often makes daughters with the Y-$a$ haplotype, increasing the flow of $a$ alleles into females, which reduces the fitness of those females.
 
@@
 %If $\lambda_{mA}>1$ (requiring $w_{Aa}^\female>w_{AA}^\female$), the implication is that the neo-W can spread alongside the $A$ allele, despite the fact that the neo-W sometimes brings $Y-a$ haplotypes into females, because $a$ is favoured by selection in females despite $A$ being fixed on the X.
-A neo-W can spread alongside the $A$ allele ($\lambda_{mA}>1$), despite the fact that a neo-W brings Y$a$ haplotypes into females, when $w_{Aa}^\female>w_{AA}^\female$.
+A neo-W can spread alongside the $A$ allele ($\lambda_{mA}>1$), despite the fact that a neo-W brings Y-$a$ haplotypes into females, when $w_{Aa}^\female>w_{AA}^\female$.
 In this case the $a$ allele is favoured by selection in females despite $A$ being fixed on the X.
-For this equilibrium to be stable, X-$A$ must be sufficiently favoured in males to keep the frequency of X$A$ at one (specifically, from the stability conditions, we must have $w_{Aa}^\male/((w_{aa}^\male+w_{Aa}^\male)/2)>w_{Aa}^\female/w_{AA}^\female$).
-
-Under this same condition, $w_{Aa}^\female>w_{AA}^\female$, the neo-W can also spread alongside the $a$ allele ($\lambda_{ma}>1$) if there is sufficiently strong underdominance in females ($w_{aa}^\female>w_{Aa}^\female$), such that $(w_{Aa}^\female+w_{aa}^\female)/2>w_{AA}^\female$.
+For this equilibrium to be stable, X-$A$ must be sufficiently favoured in males (for example, by overdominance in males, remembering that $a$ is fixed on the Y) to keep $A$ fixed on the X. 
+Specifically, from the stability conditions for equilibrium (B), we must have $w_{Aa}^\male/\big[(w_{aa}^\male+w_{Aa}^\male)/2\big]>w_{Aa}^\female/w_{AA}^\female$.
+
+Still considering $w_{Aa}^\female>w_{AA}^\female$, the neo-W can also spread alongside the $a$ allele ($\lambda_{ma}>1$) if there is sufficiently strong underdominance in females ($w_{aa}^\female>w_{Aa}^\female$) \textcolor{red}{[this is describing directional selection, not overdominance - check the conditions for the case we want to talk about]}, such that $(w_{Aa}^\female+w_{aa}^\female)/2>w_{AA}^\female$.
 In this case, $a$ is not favored in females near the equilibrium where females are $AA$ (comparing $Aa$ to $AA$ genotypes) and yet the neo-W can spread with $a$ because it produces female $aa$ individuals by capturing Y-$a$ haplotypes.
@@
 
-Similar equations can be derived for equilibrium (A) by substituting the equilibrium allele frequencies into Table \ref{tab:haplotype_growth}.
+Similar equations can be derived for equilibrium (A) by substituting the equilibrium allele frequencies into Table \ref{tab:haplotype_growth}
 
@@
 \begin{align}
-\lambda_{mA}&= \frac{a}{b} \left[w_{AA}^\female w_{Aa}^\male w_A^\male \alpha^\male \phi + 2 w_{Aa}^\female \alpha^\female w_a^\male \frac{c}{d}\right] / w_a^\female \\
-\lambda_{ma}&= \frac{a}{b} \left[2 w_{Aa}^\female (1-\alpha^\female) w_{Aa}^\male w_A^\male \alpha^\male \phi+  w_{aa}^\female w_a^\male \frac{c}{d}\right] / w_A^\female \\
-\rho_{mA}&= \frac{a}{b} R \left[ 2 w_{Aa}^\female \alpha^\female w_a^\male \frac{c}{d} \right] / w_a^\female\\ 
-\rho_{ma}&= \frac{a}{b} R \left[ 2 w_{Aa}^\female (1-\alpha^\female) w_{Aa}^\male w_A^\male \alpha^\male \phi \right] / w_A^\female
+\lambda_{mA}&= \frac{a}{b} \left[w_{AA}^\female w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi +  w_{Aa}^\female (1+\alpha^\female_\Delta) w_a^\male \frac{c}{d}\right] / (2 w_a^\female) \\
+\lambda_{ma}&= \frac{a}{b} \left[ w_{Aa}^\female (1-\alpha^\female_\Delta) w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi +  w_{aa}^\female w_a^\male \frac{c}{d}\right] / (2 w_A^\female) \\
+\rho_{mA}&= \frac{a}{b} \frac{R}{2} \left[   w_{Aa}^\female (1+\alpha^\female_\Delta) w_a^\male \frac{c}{d} \right] / w_a^\female\\ 
+\rho_{ma}&= \frac{a}{b} \frac{R}{2} \left[ w_{Aa}^\female (1-\alpha^\female_\Delta) w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi \right] / w_A^\female
 \end{align}
@@
 a &= w_a^\female \phi + w_A^\female \psi \\
-b &= w_{AA}^\female \phi (2 w_{Aa}^\male w_A^\male \alpha_\male \phi) + w_{Aa}^\female \psi (2 w_{Aa}^\male w_A^\male \alpha_\male \phi + w_{AA}^\male w_a^\male \psi) + w_{aa}^\female \psi(w_{AA}^\male w_a^\male \psi) \\
-c &= 2(w_{Aa}^\male\phi)^2(1-\alpha^\male)\alpha_\male + w_{Aa}^\male\phi(w_{AA}^\male \psi + w_{aa}^\male \psi \alpha^\male) + w_{aa}^\male \psi w_{AA}^\male \psi \\
-d &= 2 w_{Aa}^\male \alpha^\male \phi + w_{aa}^\male \psi
+b &= w_{AA}^\female \phi \left[ w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi \right]+ w_{Aa}^\female \psi \left[ w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi + w_{AA}^\male w_a^\male \psi \right] + w_{aa}^\female \psi \left( w_{AA}^\male w_a^\male \psi \right)\\
+c &= w_{Aa}^\male (1-\alpha^\male_\Delta) \phi \left[ w_{Aa}^\male (1+\alpha^\male_\Delta) \phi \right] + 2w_{Aa}^\male\phi(w_{AA}^\male \psi + w_{aa}^\male \alpha^\male \psi ) + 2w_{aa}^\male \psi w_{AA}^\male \psi \\
+d &= w_{Aa}^\male (1+\alpha^\male) \phi + w_{aa}^\male \psi
 \end{align}
@@
 where $\phi-\psi=w_{AA}^\female w_{Aa}^\male-w_{aa}^\female w_{aa}^\male$ and both $\phi$ and $\psi$ are positive when equilibrium (A) is stable. 
-In contrast to equilibrium (B), a neo-W haplotype can spread under purely sexually-antagonistic selection  ($w_{AA}^\male<w_{Aa}^\male<w_{aa}^\male$ and $w_{AA}^\female>w_{Aa}^\female>w_{aa}^\female$).
+In contrast to equilibrium (B), a neo-W haplotype can spread under purely sexually-antagonistic selection  ($w_{aa}^\female<w_{Aa}^\female<w_{AA}^\female$ and $w_{AA}^\male<w_{Aa}^\male<w_{aa}^\male$).
 The neo-W-$A$ can spread as long as it becomes associated with females that bear more $A$ alleles than observed at equilibrium (A). 

### 2017-09-14 LaTeX/Turnover.tex
resolving conflict

--- 2017-08-25 LaTeX/Turnover.tex
@@
 (1) We explicitly consider how selection on very tightly sex-linked loci influences the spread of novel sex-determiners. 
-We find that tightly sex-linked genetic variation can favour the spread of new sex-determination systems in which the heterogametic sex changes (XY to ZW or ZW to XY) and the new sex-determining region is less closely linked (or unlinked) to the sex-linked locus under selection; a result that is not found with loose sex-linkage.
+We find that tightly sex-linked genetic variation can favour the spread of new sex-determination systems in which the heterogametic sex changes (XY to ZW or ZW to XY) and the new sex-determining region is less closely linked (or unlinked) to the sex-linked locus under selection, which would not be predicted by previous theory.
 %With tight linkage, selection can maintain equilibria at which the allele fixed on the sex-limited chromosome (Y or W) is simultaneously favoured in the homogametic sex (XX females or ZZ males) such that heterogametic transitions (XY to ZW or ZW to XY) are favoured by selection.
@@
 The diploid selection term, $D^\Hermaphrodite=\big{(} \bar{p}s^\Hermaphrodite+(1-\bar{p})h^\Hermaphrodite s^\Hermaphrodite\big{)} -\big{(} \bar{p}h^\Hermaphrodite s^\Hermaphrodite+(1-\bar{p}) \big{)}$, is the difference in fitness between $A$ and $a$ alleles in diploids of sex $\Hermaphrodite \in \{\female,\male\}$, where $\bar{p}$ is the leading-order probability of mating with an $A$-bearing gamete from the opposite sex (see Appendix).
+The difference in $A$-allele-frequency among Y-bearing sperm versus X-bearing sperm is given by $\hat{p}^\male_Y-\hat{p}^\male_X=V_{A}\big{(}D^\male - D^\female+\alpha_{\Delta}^\male-\alpha_{\Delta}^\female+t^\male-t^\female\big{)}(1-2r)/2r$.
 

### 2017-09-14 LaTeX/Turnover.tex
some quick comments

@@
 This also introduced an extra 1/2 in S.6c,d that might need to be explained.}
+\textcolor{red}{hmm, not sure.
+This was an idea from Sally, I think in response to terms like $2 \alpha^\Hermaphrodite$ and $2(1-\alpha^\Hermaphrodite)$.
+It's possible that it makes other equations less easy to understand.
+My previous (not explained) logic was to use $w$ and $\alpha$ for strong selection and $s$, $t$, and $\alpha_\Delta$ for weak selection.
+Just to check, I should have written $\alpha^\Hermaphrodite=(1+\alpha_{\Delta}^\Hermaphrodite)/2$, maybe that's where the factors of $1/2$ come from?}
 
@@
 Here $\chi$ is the probability of an odd number of cross-overs between the SDR and M loci.}
+\textcolor{red}{Good point, not sure what's best for \textbf{the-term-formerly-known-as-$\rho$}.
+Yeah, Sally's written comment was something like ``$\chi$ is semi-standard notation for double recombination so it's use as a recombination rate might be confusing''.}
 
@@
 \textcolor{red}{Change to $\hat{p}$ throughout as we assume that allele frequencies change slowly such that lambda is unaffected}
-\textcolor{how will we differentiate between equilibrium $p$ and non-equilibrium $p$? or is the point that we can only say anything when at equilibrium?}
+\textcolor{blue}{how will we differentiate between equilibrium $p$ and non-equilibrium $p$? or is the point that we can only say anything when at equilibrium?}
+\textcolor{red}{I think Sally's point is that the eigenvalue analysis only makes sense if the $p$'s are changing slowly relative to the frequency of the modifier.
+Therefore, even when we don't substitute in any equilibrium frequencies, it might be safest to think of them as equilibrium allele frequencies.
+}
 
@@
 Thus, haploid selection can favour heterogametic transitions both via sex-ratio selection %\citep[as predicted by][]{Kozielska:2010vm} 
-and via fitness effects of alleles that are associated with the neo-sex-determining allele, and these selection pressures are predicted to often be of roughly equal magnitude (unless linkage is tight).
+and via fitness effects of alleles that are associated with the neo-sex-determining allele, and these selection pressures are predicted to often be of equal magnitude when selection is weak. 
 %\textcolor{red}{Maybe try to emphasise surprisingness in the paragraph more? e.g., how wrong you'd be if you assumed selection to equalise sex ratios, or it this implied?}
@@
 Perhaps counterintuitively, transitions involving haploid selection can be driven by sex-ratio selection or cause sex-ratio biases to evolve. 
-We therefore argue that haploid selection should be considered as a pivotal factor in the evolution of sex-determination systems. 
+We conclude that haploid selection should be considered as a pivotal factor driving transitions between sex-determination systems. 
 Overall, our results suggest several new scenarios under which new sex-determination systems are favoured, which could help to explain why the evolution of sex-determination systems is so dynamic. 
@@
 At equilibrium $(B)$, the fitness of female gametes under the ancestral sex-determining system is $w_{A}^\female$ such that the relative fitnesses of neo-W-$A$ and neo-W-$a$ haplotypes during female gametic competition are $w_{A}^\female/w_{A}^\female$ and $w_{a}^\female/w_{A}^\female$ (see terms in equation \ref{Binvasion}).
-Meiotic drive in females will also change the proportion of gametes that carry the $A$ versus $a$ alleles, which will be produced by heterozygous females in proportions $(1+\alpha_{\Delta}^\female)$ and $(1-\alpha_{\Delta}^\female)$, respectively.
+Meiotic drive in females will also change the proportion of gametes that carry the $A$ versus $a$ alleles, which will be produced by heterozygous females in proportions $(1+\alpha_{\Delta}^\female)/2$ and $(1-\alpha_{\Delta}^\female)/2$, respectively.
 These terms are only associated with heterozygous females, i.e., they are found alongside $w_{Aa}^\female$.
@@
 At equlibrium $(B)$, neo-W female gametes will mate with X-$A$ male gametes with probability $ w_A^\male (1+\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$ and Y-$a$ male gametes with probability $w_a^\male (1-\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$, where the $2\bar{w}_{H}^\male$ terms have been canceled in equation \eqref{Binvasion} (as mentioned above).
-Thus, for example, neo-W-$A$ haplotypes are found in $AA$ female diploids with probability $ w_A^\male (1+\alpha^\male_\Delta)/ (2\bar{w}_{H}^\male)$ (first term in square brackets in the numerate of equation \ref{Binvasion}a) and in $Aa$ female diploids with probability $w_a^\male (1-\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$ (see equation \ref{Binvasion}c and second term in square brackets in the numerator of equation \ref{Binvasion}a).
+Thus, for example, neo-W-$A$ haplotypes are found in $AA$ female diploids with probability $ w_A^\male (1+\alpha^\male_\Delta)/ (2\bar{w}_{H}^\male)$ (first term in square brackets in the numerator of equation \ref{Binvasion}a) and in $Aa$ female diploids with probability $w_a^\male (1-\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$ (see equation \ref{Binvasion}c and second term in square brackets in the numerator of equation \ref{Binvasion}a).
 

### 2017-09-15 LaTeX/Turnover.tex
rho and hat p change made, still need to check for alpha eerrors

@@
 
-\title{Haploid Selection, Sex Ratio Bias, and Transitions Between sex-determination systems}
+\title{Haploid Selection, Sex Ratio Bias, and Transitions Between Sex-Determination Systems}
 \author{Michael F Scott$*^1$, Matthew M Osmond$*^2$, and Sarah P Otto$^2$}
@@
 Just to check, I should have written $\alpha^\Hermaphrodite=(1+\alpha_{\Delta}^\Hermaphrodite)/2$, maybe that's where the factors of $1/2$ come from?}
-
-\textcolor{red}{Switch between $\chi$ and $\rho$ in all places because $\chi$ is used for double recombination events.}
-\textcolor{blue}{I think we need a different variable given the $\rho$ terms in the characteristic polynomial.
-Also, where is $\chi$ used for double recombination?
+\textcolor{blue}{shoot, i may have changed too much (i.e. strong selection too), but i did use the correct transformation. still, the form of S.8c,d seems wrong. I'll double check it.}
+
+%\textcolor{red}{Switch between $\rho$ and $\rho$ in all places because $\rho$ is used for double recombination events.}
+%\textcolor{blue}{I think we need a different variable given the $\rho$ terms in the characteristic polynomial.
+Also, where is $\rho$ used for double recombination?
 In other papers?
-Here $\chi$ is the probability of an odd number of cross-overs between the SDR and M loci.}
-\textcolor{red}{Good point, not sure what's best for \textbf{the-term-formerly-known-as-$\rho$}.
-Yeah, Sally's written comment was something like ``$\chi$ is semi-standard notation for double recombination so it's use as a recombination rate might be confusing''.}
+Here $\rho$ is the probability of an odd number of cross-overs between the SDR and M loci.}
+%\textcolor{red}{Good point, not sure what's best for \textbf{the-term-formerly-known-as-$\rho$}.
+Yeah, Sally's written comment was something like ``$\rho$ is semi-standard notation for double recombination so it's use as a recombination rate might be confusing''.}
 
@@
 The next generation of gametes is produced by meiosis, during which recombination and sex-specific meiotic drive can occur. 
-Recombination (i.e., an odd number of cross-overs) occurs between loci \textbf{X} and \textbf{A} with probability $r$, between loci \textbf{A} and \textbf{M} with probability $R$, and between loci \textbf{X} and \textbf{M} with probability $\chi$.
-Any linear order of the loci can be modelled with appropriate choices of $r$, $R$, and $\chi$ (see Table \ref{tab:chisubstitutions}). 
+Recombination (i.e., an odd number of cross-overs) occurs between loci \textbf{X} and \textbf{A} with probability $r$, between loci \textbf{A} and \textbf{M} with probability $R$, and between loci \textbf{X} and \textbf{M} with probability $\rho$.
+Any linear order of the loci can be modelled with appropriate choices of $r$, $R$, and $\rho$ (see Table \ref{tab:chisubstitutions}). 
 Individuals that are heterozygous at the \textbf{A} locus may experience meiotic drive; a gamete produced by $Aa$ heterozgotes of sex $\Hermaphrodite$ bear allele $A$ with probability $\alpha^\Hermaphrodite$.
@@
 %\noindent
-%where $b$ is the average of the growth rates of the two haplotypes that carry the $m$ allele ($mA$ and $ma$), $b=(\lambda_{mA}+\lambda_{ma})/2$, and $c$ also involves the fitness of $m$ alleles when they recombine onto the other \textbf{A} background in a heterozygote, $c=\lambda_{mA}\lambda_{ma}+\rho_{mA}\rho_{ma}$ (see table \ref{tab:haplotype_growth}).
-%Here, $b= - (\lambda_{mA} + \lambda_{ma})$ and $c = \lambda_{mA} \lambda_{ma} -\rho_{mA} \rho_{ma}$, where $\lambda_{mi}$ is the (multiplicative) growth rate of mutant haplotypes on background $i\in\{A,a\}$, accounting for loss due to recombination, and $\rho_{mi}$ is the rate of addition of mutant haplotypes onto background $i\in\{A,a\}$ due to recombination (see table \ref{tab:haplotype_growth}).
-Here, $b= - (\lambda_{mA} + \lambda_{ma})+(\rho_{mA} + \rho_{ma})$ and $c = (\lambda_{mA}-\rho_{mA}) (\lambda_{ma}-\rho_{ma}) -\rho_{mA} \rho_{ma}$, where $\lambda_{mi}$ is the multiplicative growth rate of mutant haplotypes on background $i\in\{A,a\}$, without accounting for loss due to recombination, and $\rho_{mi}$ is the rate at which mutant haplotypes on background $i\in\{A,a\}$ recombine onto the other \textbf{A} locus background in heterozygotes (see Table \ref{tab:haplotype_growth}).
-The $\lambda_{mi}$ and $\rho_{mi}$, and thus the spread of the mutant $m$ allele, depend on the frequency of alleles at the \textbf{A} and \textbf{X} loci in the ancestral population. 
+%where $b$ is the average of the growth rates of the two haplotypes that carry the $m$ allele ($mA$ and $ma$), $b=(\lambda_{mA}+\lambda_{ma})/2$, and $c$ also involves the fitness of $m$ alleles when they recombine onto the other \textbf{A} background in a heterozygote, $c=\lambda_{mA}\lambda_{ma}+\chi_{mA}\chi_{ma}$ (see table \ref{tab:haplotype_growth}).
+%Here, $b= - (\lambda_{mA} + \lambda_{ma})$ and $c = \lambda_{mA} \lambda_{ma} -\chi_{mA} \chi_{ma}$, where $\lambda_{mi}$ is the (multiplicative) growth rate of mutant haplotypes on background $i\in\{A,a\}$, accounting for loss due to recombination, and $\chi_{mi}$ is the rate of addition of mutant haplotypes onto background $i\in\{A,a\}$ due to recombination (see table \ref{tab:haplotype_growth}).
+Here, $b= - (\lambda_{mA} + \lambda_{ma})+(\chi_{mA} + \chi_{ma})$ and $c = (\lambda_{mA}-\chi_{mA}) (\lambda_{ma}-\chi_{ma}) -\chi_{mA} \chi_{ma}$, where $\lambda_{mi}$ is the multiplicative growth rate of mutant haplotypes on background $i\in\{A,a\}$, without accounting for loss due to recombination, and $\chi_{mi}$ is the rate at which mutant haplotypes on background $i\in\{A,a\}$ recombine onto the other \textbf{A} locus background in heterozygotes (see Table \ref{tab:haplotype_growth}).
+The $\lambda_{mi}$ and $\chi_{mi}$, and thus the spread of the mutant $m$ allele, depend on the frequency of alleles at the \textbf{A} and \textbf{X} loci in the ancestral population. 
 In the ancestral population, it is convenient to follow the frequency of the $A$ allele among female gametes (eggs), $p^\female_X$, and among X-bearing, $p^\male_X$, and among Y-bearing, $p^\male_Y$, male gametes (sperm/pollen).
 We also track the fraction of male gametes that are Y-bearing, $q$, which may deviate from $1/2$ due to meiotic drive in males. 
+We will consider only equilibrium frequencies of alleles, $\hat{p}^\Hermaphrodite_i$, and Y-bearing male gametes, $\hat{q}$, to ensure the eigenvalues of the invasion analysis are valid.
 
@@
    neo-Y ($k=0$) \\ [0.5ex] \hline \noalign{\vskip 1ex}
-  $\lambda_{mA} = \left( 2 \zeta \right)^{-1} \left[p_{X}^{\female} w_{A}^{\female} w_{A}^{\male} w_{AA}^{\male} + (1-p_{X}^{\female}) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} (1+\alpha_{\Delta}^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right) $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\lambda_{ma} = \left( 2 \zeta \right)^{-1} \left[(1-p_{X}^{\female}) w_{a}^{\female} w_{a}^{\male} w_{aa}^{\male} + p_{X}^{\female} w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male}(1 - \alpha_{\Delta}^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\rho_{mA} = R \left( 2 \zeta \right)^{-1} \left[ (1-p_{X}^{\female}) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} (1+\alpha_{\Delta}^{\male}) \right]/  \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right)   $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\rho_{ma} = R \left( 2 \zeta \right)^{-1} \left[   p_{X}^{\female} w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male} (1 - \alpha_\Delta^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right)  $\\ [1ex] \hline
+  $\lambda_{mA} = \left( 2 \zeta \right)^{-1} \left[\hat{p}_X^\female w_{A}^{\female} w_{A}^{\male} w_{AA}^{\male} + (1-\hat{p}_X^\female) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} (1+\alpha_{\Delta}^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right) $\\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\lambda_{ma} = \left( 2 \zeta \right)^{-1} \left[(1-\hat{p}_X^\female) w_{a}^{\female} w_{a}^{\male} w_{aa}^{\male} + \hat{p}_X^\female w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male}(1 - \alpha_{\Delta}^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\chi_{mA} = R \left( 2 \zeta \right)^{-1} \left[ (1-\hat{p}_X^\female) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} (1+\alpha_{\Delta}^{\male}) \right]/  \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right)   $\\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\chi_{ma} = R \left( 2 \zeta \right)^{-1} \left[   \hat{p}_X^\female w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male} (1 - \alpha_\Delta^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right)  $\\ [1ex] \hline
   \noalign{\vskip 0.5ex}
@@
   $\lambda_{ma} = \left[ 2 (1 - \zeta) \right]^{-1} \left[ (1-\bar{p}^{\male}) w_{a}^{\male} w_{a}^{\female} w_{aa}^{\female}+\bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female}(1-\alpha_{\Delta}^{\female})\right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\rho_{mA} = R \left[ 2 (1 - \zeta) \right]^{-1} \left[ (1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female} (1+\alpha_{\Delta}^{\female}) \right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \right)  $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\rho_{ma} = R \left[ 2 (1 - \zeta) \right]^{-1} \left[ \bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female} (1-\alpha_{\Delta}^{\female}) \right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \right) $\\ [1ex]
+  $\chi_{mA} = R \left[ 2 (1 - \zeta) \right]^{-1} \left[ (1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female} (1+\alpha_{\Delta}^{\female}) \right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \right)  $\\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\chi_{ma} = R \left[ 2 (1 - \zeta) \right]^{-1} \left[ \bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female} (1-\alpha_{\Delta}^{\female}) \right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \right) $\\ [1ex]
   \hline \hline 
@@
       \scriptsize
-      \item $\bar{p}^{\male}=(1-q)p_{X}^{\male} + qp_{Y}^{\male}$ is the average frequency of the $A$ allele among X- and Y-bearing male gametes.
+      \item $\bar{p}^{\male}=(1-\hat{q})\hat{p}_X^\male + q\hat{p}_Y^\male$ is the average frequency of the $A$ allele among X- and Y-bearing male gametes.
 %      \item $R$ is the probability of recombination between loci \textbf{A} and \textbf{M}.
@@
 %\begin{equation}
-%(\lambda_{mA}-1)(\lambda_{ma}-1) - \rho_{mA} \rho_{ma}<0.
+%(\lambda_{mA}-1)(\lambda_{ma}-1) - \chi_{mA} \chi_{ma}<0.
 %\end{equation}
@@
 \begin{equation}\label{eq:lambdasGen}
-%\frac{\rho_{mA}}{\lambda_{mA}-1}+\frac{\rho_{ma}}{\lambda_{ma}-1}>0.
-\rho_{ma}\left(\lambda_{mA}-1\right)+\rho_{mA}\left(\lambda_{ma}-1\right)>0.
+%\frac{\chi_{mA}}{\lambda_{mA}-1}+\frac{\chi_{ma}}{\lambda_{ma}-1}>0.
+\chi_{ma}\left(\lambda_{mA}-1\right)+\chi_{mA}\left(\lambda_{ma}-1\right)>0.
 \end{equation}
@@
 %the diploid fitness terms in Table \ref{tab:haplotype_growth} are weighted by the probability of producing those genotypes through matings with gametes of the opposite sex. 
-%For example, matings between a neo-Y-bearing male gamete and an $A$-bearing female gamete occur with probability $p_{X}^{\female} w_{A}^{\female}/\bar{w}_{H}^{\female}$. 
+%For example, matings between a neo-Y-bearing male gamete and an $A$-bearing female gamete occur with probability $\hat{p}_X^\female w_{A}^{\female}/\bar{w}_{H}^{\female}$. 
 %This is the same probability that an ancestral-Y-bearing male gamete will inherit an $A$ allele via mating with a female gamete. 
 %On the other hand, 
-%The probability that a neo-W bearing female gamete mates with an $A$-bearing male gamete is $\bar{p}^{\male} w_{A}^{\male}/\bar{w}_{H}^{\male}$, where $\bar{p}^{\male}=p_{Y}^{\male}q+p_{X}^{\male}(1-q)$ is the frequency of the A allele among both X- and Y-bearing male gametes.
+%The probability that a neo-W bearing female gamete mates with an $A$-bearing male gamete is $\bar{p}^{\male} w_{A}^{\male}/\bar{w}_{H}^{\male}$, where $\bar{p}^{\male}=\hat{p}_Y^\maleq+\hat{p}_X^\male(1-q)$ is the frequency of the A allele among both X- and Y-bearing male gametes.
 %That is, in the case of a neo-W, female diploids can result from matings with either an X-bearing or a Y-bearing sperm, resulting in zygotes that will develop as females. 
@@
 % invasion is driven by the fitness of male gametes and diploids, where the latter is weighted by the chance that a female egg will give rise to that diploid. 
-%For example, matings with $A$-bearing female gametes occur with probability $p_{X}^{\female} w_{A}^{\female}/\bar{w}_{H}^{\female}$. 
+%For example, matings with $A$-bearing female gametes occur with probability $\hat{p}_X^\female w_{A}^{\female}/\bar{w}_{H}^{\female}$. 
 %Since a neo-Y is always found in males, the allele frequencies at the neo-Y (\textbf{M}) locus only change in males. 
@@
 %In either case, the zygote will develop as a female due to the presence of a neo-W. 
-%For example, neo-W females will inherit an $A$ allele from a male gamete with probability $\bar{p}^{\male} w_{A}^{\male}/\bar{w}_{H}^{\male}$, where $\bar{p}^{\male}=p_{Y}^{\male}q+p_{X}^{\male}(1-q)$ is the frequency of the A allele among both X- and Y-bearing male gametes.
+%For example, neo-W females will inherit an $A$ allele from a male gamete with probability $\bar{p}^{\male} w_{A}^{\male}/\bar{w}_{H}^{\male}$, where $\bar{p}^{\male}=\hat{p}_Y^\maleq+\hat{p}_X^\male(1-q)$ is the frequency of the A allele among both X- and Y-bearing male gametes.
 %By contrast, females that do not carry the neo-W only result from matings with X-bearing sperm. 
@@
 
-In order to explicitly determine the conditions under which a rare neo-sex-determining allele spreads, we must calculate the equilibrium frequency of the $A$ allele in the ancestral population (i.e., $\hat{p}^\female_X$, $\hat{p}^\male_X$, and $\hat{p}^\male_Y$).
+In order to explicitly determine the conditions under which a rare neo-sex-determining allele spreads, we must calculate the equilibrium frequency of the $A$ allele (i.e., $\hat{p}^\female_X$, $\hat{p}^\male_X$, and $\hat{p}^\male_Y$) and Y-bearing male gametes ($\hat{q}$) in the ancestral population .
 Since only the \textbf{A} locus experiences selection directly, any deterministic evolution requires that there is a polymorphism at the \textbf{A} locus. 
@@
 
-\textcolor{red}{Change to $\hat{p}$ throughout as we assume that allele frequencies change slowly such that lambda is unaffected}
-\textcolor{blue}{how will we differentiate between equilibrium $p$ and non-equilibrium $p$? or is the point that we can only say anything when at equilibrium?}
-\textcolor{red}{I think Sally's point is that the eigenvalue analysis only makes sense if the $p$'s are changing slowly relative to the frequency of the modifier.
+%\textcolor{red}{Change to $\hat{p}$ throughout as we assume that allele frequencies change slowly such that lambda is unaffected}
+%\textcolor{blue}{how will we differentiate between equilibrium $p$ and non-equilibrium $p$? or is the point that we can only say anything when at equilibrium?}
+%\textcolor{red}{I think Sally's point is that the eigenvalue analysis only makes sense if the $p$'s are changing slowly relative to the frequency of the modifier.
 Therefore, even when we don't substitute in any equilibrium frequencies, it might be safest to think of them as equilibrium allele frequencies.
@@
 Both neo-W-$A$ and neo-W-$a$ haplotypes then produce fewer unfit $AA$ females.
-This is true for the neo-W-$A$ haplotype because it can pair with a $Y-a$ haplotype and still be female. 
+This is true for the neo-W-$A$ haplotype because it can pair with a Y-$a$ haplotype and still be female. 
 Wherever both haplotypes have positive growth rates, invasion by a neo-W is expected regardless of its linkage with the selected locus (i.e., even unlinked neo-W alleles can invade, see Figures \ref{fig:positionOverdominance} and \ref{fig:temporalOverdominance} for examples).
@@
 %The equilibrium frequency of $A$ on different ancestral backgrounds ($\hat{p}^\male_Y$, $\hat{p}^\male_X$, and $\hat{p}^\female_X$) is given by equations \eqref{eq:pAve} and \eqref{eq:freq_diffs} where we assume selection and meiotic drive are weak relative to recombination ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon$).
-Assuming that selection is weak relative to all recombination rates ($r$, $R$ and $\chi$), we denote the leading eigenvalues describing the invasion of a neo-Y ($k=0$) and a neo-W ($k=1$) into an ancestrally XY system by $\lambda_{Y',XY}$ and $\lambda_{W',XY}$, respectively.
+Assuming that selection is weak relative to all recombination rates ($r$, $R$ and $\rho$), we denote the leading eigenvalues describing the invasion of a neo-Y ($k=0$) and a neo-W ($k=1$) into an ancestrally XY system by $\lambda_{Y',XY}$ and $\lambda_{W',XY}$, respectively.
 To leading order in selection, these are:
@@
 \noindent
-where $V_{A}=\bar{p}(1-\bar{p})$ is the variance in the frequency of $A$ and $S_{A}=(D^\male +\alpha_{\Delta}^\male+t^\male) - (D^\female+\alpha_{\Delta}^\female+t^\female)$ describes sex differences in selection for the $A$ versus $a$ across diploid selection, meiosis, and gametic competition.
-The diploid selection term, $D^\Hermaphrodite=\big{(} \bar{p}s^\Hermaphrodite+(1-\bar{p})h^\Hermaphrodite s^\Hermaphrodite\big{)} -\big{(} \bar{p}h^\Hermaphrodite s^\Hermaphrodite+(1-\bar{p}) \big{)}$, is the difference in fitness between $A$ and $a$ alleles in diploids of sex $\Hermaphrodite \in \{\female,\male\}$, where $\bar{p}$ is the leading-order probability of mating with an $A$-bearing gamete from the opposite sex (see Appendix).
+where $V_{A}=\bar{p}(1-\bar{p})$ is the variance in the equilibrium frequency of $A$ and $S_{A}=(D^\male +\alpha_{\Delta}^\male+t^\male) - (D^\female+\alpha_{\Delta}^\female+t^\female)$ describes sex differences in selection for the $A$ versus $a$ across diploid selection, meiosis, and gametic competition.
+The diploid selection term, $D^\Hermaphrodite=\big{[} \bar{p}s^\Hermaphrodite+(1-\bar{p})h^\Hermaphrodite s^\Hermaphrodite\big{]} -\big{[} \bar{p}h^\Hermaphrodite s^\Hermaphrodite+(1-\bar{p}) \big{]}$, is the difference in fitness between $A$ and $a$ alleles in diploids of sex $\Hermaphrodite \in \{\female,\male\}$, where $\bar{p}$ is the leading-order probability of mating with an $A$-bearing gamete from the opposite sex (see Appendix).
 The difference in $A$-allele-frequency among Y-bearing sperm versus X-bearing sperm is given by $\hat{p}^\male_Y-\hat{p}^\male_X=V_{A}\big{(}D^\male - D^\female+\alpha_{\Delta}^\male-\alpha_{\Delta}^\female+t^\male-t^\female\big{)}(1-2r)/2r$.
@@
 \lambda_{ESD',XY} =& 1 + (1-2k)^2V_{A}{S_{A}}^2\frac{r-R}{r R} \\
-&+\frac{k(\hat{p}^\male_Y-\hat{p}^\male_X)}{2}\left(k\left(2\alpha_{\Delta}^\male-2\alpha_{\Delta}^\female+t^\male-t^\female \right) -4(1-k)S_{A}\right)+O\left(\epsilon^3\right),
+&+\frac{k(\hat{p}^\male_Y-\hat{p}^\male_X)}{2}\left[ k \left(2\alpha_{\Delta}^\male-2\alpha_{\Delta}^\female+t^\male-t^\female \right) -4(1-k)S_{A}\right]+O\left(\epsilon^3\right),
 \end{split}
@@
 Here, we allow any relative locations for the SDR, \textbf{A}, and \textbf{M} loci by using three parameters to describe the recombination rates between them. 
-$R$ is the recombination rate between the \textbf{A} locus and the \textbf{M} locus, $\chi$ is the recombination rate between the \textbf{M} locus and the \textbf{X} locus, and $r$ is the recombination rate between the \textbf{A} locus and the \textbf{X} locus.
-Table \ref{tab:chisubstitutions} shows the value of $\chi$ in the absence of cross-over interference for each possible ordering of the loci.
+$R$ is the recombination rate between the \textbf{A} locus and the \textbf{M} locus, $\rho$ is the recombination rate between the \textbf{M} locus and the \textbf{X} locus, and $r$ is the recombination rate between the \textbf{A} locus and the \textbf{X} locus.
+Table \ref{tab:chisubstitutions} shows the value of $\rho$ in the absence of cross-over interference for each possible ordering of the loci.
 During meiosis in sex $\Hermaphrodite$, meiotic drive occurs such that, in $Aa$ heterozygotes, a fraction $\alpha^{\Hermaphrodite}$ of gametes produced carry the $A$ allele and $(1-\alpha^\Hermaphrodite)$ carry the $a$ allele.
@@
 \smallskip
-\caption{$\chi$ substitutions for different loci orders (assuming no interference)}
+\caption{$\rho$ substitutions for different loci orders (assuming no interference)}
 \begin{tabular}{l l}
@@
   Order of loci &   \\ [0.5ex] \hline
-  SDR-A-M & $\chi=R(1-r)+r(1-R)$  \\
-  SDR-M-A & $\chi=(r-R)/(1-2R)$ \\
-  A-SDR-M & $\chi=(R-r)/(1-2r)$ \\
+  SDR-A-M & $\rho=R(1-r)+r(1-R)$  \\
+  SDR-M-A & $\rho=(r-R)/(1-2R)$ \\
+  A-SDR-M & $\rho=(R-r)/(1-2r)$ \\
   \hline \hline
@@
 &+(xy_{11}^{\Hermaphrodite,s}+xy_{13}^{\Hermaphrodite,s})/2+(xy_{12}^{\Hermaphrodite,s}+xy_{14}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&- r(xy_{12}^{\Hermaphrodite,s}-xy_{21}^{\Hermaphrodite,s})\alpha^\Hermaphrodite - \chi(xy_{13}^{\Hermaphrodite,s}-xy_{31}^{\Hermaphrodite,s})/2\\
-&+\big{\{}-(R+r+\chi)xy_{14}^{\Hermaphrodite,s} +(r+\chi-R)xy_{41}^{\Hermaphrodite,s}\\
-&+(R+r-\chi) xy_{23}^{\Hermaphrodite,s}+(R+\chi-r)xy_{32}^{\Hermaphrodite,s}\big{\}}\alpha^\Hermaphrodite/2
+&- r(xy_{12}^{\Hermaphrodite,s}-xy_{21}^{\Hermaphrodite,s})\alpha^\Hermaphrodite - \rho(xy_{13}^{\Hermaphrodite,s}-xy_{31}^{\Hermaphrodite,s})/2\\
+&+\big{[}-(R+r+\rho)xy_{14}^{\Hermaphrodite,s} +(R+\rho-r)xy_{41}^{\Hermaphrodite,s}\\
+&+(R+r-\rho) xy_{23}^{\Hermaphrodite,s}+(R+\rho-r)xy_{32}^{\Hermaphrodite,s}\big{]}\alpha^\Hermaphrodite/2
 \end{split}
@@
 &(xy_{22}^{\Hermaphrodite,s}+xy_{24}^{\Hermaphrodite,s})/2+(xy_{21}^{\Hermaphrodite,s}+xy_{23}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite)\\
-&- r(xy_{21}^{\Hermaphrodite,s}-xy_{12}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite) - \chi(xy_{24}^{\Hermaphrodite,s}-xy_{42}^{\Hermaphrodite,s})/2\\
-&+\big{\{}-(R+r+\chi)xy_{23}^{\Hermaphrodite,s}+(r+\chi-R)xy_{32}^{\Hermaphrodite,s}\\
-&+(R+r-\chi) xy_{14}^{\Hermaphrodite,s}+(R+\chi-r)xy_{41}^{\Hermaphrodite,s}\big{\}}(1-\alpha^\Hermaphrodite)/2
+&- r(xy_{21}^{\Hermaphrodite,s}-xy_{12}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite) - \rho(xy_{24}^{\Hermaphrodite,s}-xy_{42}^{\Hermaphrodite,s})/2\\
+&+\big{[}-(R+r+\rho)xy_{23}^{\Hermaphrodite,s}+(R+\rho-r)xy_{32}^{\Hermaphrodite,s}\\
+&+(R+r-\rho) xy_{14}^{\Hermaphrodite,s}+(R+\rho-r)xy_{41}^{\Hermaphrodite,s}\big{]}(1-\alpha^\Hermaphrodite)/2
 \end{split}
@@
 &(xy_{33}^{\Hermaphrodite,s}+xy_{31}^{\Hermaphrodite,s})/2+(xy_{32}^{\Hermaphrodite,s}+xy_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&- r(xy_{34}^{\Hermaphrodite,s}-xy_{43}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite - \chi(xy_{31}^{\Hermaphrodite,s}-xy_{13}^{\Hermaphrodite,s})/2\\
-&+\big{\{}-(R+r+\chi)xy_{32}^{\Hermaphrodite,s} +(r+\chi-R)xy_{23}^{\Hermaphrodite,s}\\
-&+(R+r-\chi) xy_{41}^{\Hermaphrodite,s}+(R+\chi-r)xy_{14}^{\Hermaphrodite,s}\big{\}} \alpha^\Hermaphrodite/2
+&- r(xy_{34}^{\Hermaphrodite,s}-xy_{43}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite - \rho(xy_{31}^{\Hermaphrodite,s}-xy_{13}^{\Hermaphrodite,s})/2\\
+&+\big{[}-(R+r+\rho)xy_{32}^{\Hermaphrodite,s} +(R+\rho-r)xy_{23}^{\Hermaphrodite,s}\\
+&+(R+r-\rho) xy_{41}^{\Hermaphrodite,s}+(R+\rho-r)xy_{14}^{\Hermaphrodite,s}\big{]} \alpha^\Hermaphrodite/2
 \end{split}
@@
 &(xy_{44}^{\Hermaphrodite,s}+xy_{42}^{\Hermaphrodite,s})/2+(xy_{41}^{\Hermaphrodite,s}+xy_{43}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite)\\
-&- r(xy_{43}^{\Hermaphrodite,s}-xy_{34}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite) - \chi(xy_{42}^{\Hermaphrodite,s}-xy_{24}^{\Hermaphrodite,s})/2\\
-&+\big{\{}-(R+r+\chi)xy_{41}^{\Hermaphrodite,s}+(r+\chi-R)xy_{14}^{\Hermaphrodite,s}\\
-&+(R+r-\chi) xy_{32}^{\Hermaphrodite,s}+(R+\chi-r)xy_{23}^{\Hermaphrodite,s}\big{\}}(1-\alpha^\Hermaphrodite)/2
+&- r(xy_{43}^{\Hermaphrodite,s}-xy_{34}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite) - \rho(xy_{42}^{\Hermaphrodite,s}-xy_{24}^{\Hermaphrodite,s})/2\\
+&+\big{[}-(R+r+\rho)xy_{41}^{\Hermaphrodite,s}+(R+\rho-r)xy_{14}^{\Hermaphrodite,s}\\
+&+(R+r-\rho) xy_{32}^{\Hermaphrodite,s}+(R+\rho-r)xy_{23}^{\Hermaphrodite,s}\big{]}(1-\alpha^\Hermaphrodite)/2
 \end{split}
@@
 &(xy_{11}^{\Hermaphrodite,s}+xy_{31}^{\Hermaphrodite,s})/2+(xy_{21}^{\Hermaphrodite,s}+xy_{41}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&- r(xy_{21}^{\Hermaphrodite,s}-xy_{12}^{\Hermaphrodite,s})\alpha^\Hermaphrodite - \chi(xy_{31}^{\Hermaphrodite,s}-xy_{13}^{\Hermaphrodite,s})/2\\
-&+\big{\{} - (R+r+\chi)xy_{41}^{\Hermaphrodite,s} + (r+\chi-R)xy_{14}^{\Hermaphrodite,s}\\
-& + (R+r-\chi)xy_{32}^{\Hermaphrodite,s} + (R+\chi-r) xy_{23}^{\Hermaphrodite,s}\big{\}}\alpha^\Hermaphrodite/2
+&- r(xy_{21}^{\Hermaphrodite,s}-xy_{12}^{\Hermaphrodite,s})\alpha^\Hermaphrodite - \rho(xy_{31}^{\Hermaphrodite,s}-xy_{13}^{\Hermaphrodite,s})/2\\
+&+\big{[} - (R+r+\rho)xy_{41}^{\Hermaphrodite,s} + (R+\rho-r)xy_{14}^{\Hermaphrodite,s}\\
+& + (R+r-\rho)xy_{32}^{\Hermaphrodite,s} + (R+\rho-r) xy_{23}^{\Hermaphrodite,s}\big{]}\alpha^\Hermaphrodite/2
 \end{split}
@@
 &(xy_{22}^{\Hermaphrodite,s}+xy_{42}^{\Hermaphrodite,s})/2+(xy_{12}^{\Hermaphrodite,s}+xy_{32}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite)\\
-&- r(xy_{12}^{\Hermaphrodite,s}-xy_{21}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite) - \chi(xy_{42}^{\Hermaphrodite,s}-xy_{24}^{\Hermaphrodite,s})/2\\
-&+\big{\{}-(R+r+\chi)xy_{32}^{\Hermaphrodite,s} +(r+\chi-R) xy_{23}^{\Hermaphrodite,s}\\
-&+(R+r-\chi)xy_{41}^{\Hermaphrodite,s}+(R+\chi-r)xy_{14}^{\Hermaphrodite,s}\big{\}}(1-\alpha^\Hermaphrodite)/2
+&- r(xy_{12}^{\Hermaphrodite,s}-xy_{21}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite) - \rho(xy_{42}^{\Hermaphrodite,s}-xy_{24}^{\Hermaphrodite,s})/2\\
+&+\big{[}-(R+r+\rho)xy_{32}^{\Hermaphrodite,s} +(R+\rho-r) xy_{23}^{\Hermaphrodite,s}\\
+&+(R+r-\rho)xy_{41}^{\Hermaphrodite,s}+(R+\rho-r)xy_{14}^{\Hermaphrodite,s}\big{]}(1-\alpha^\Hermaphrodite)/2
 \end{split}
@@
 &(xy_{33}^{\Hermaphrodite,s}+xy_{13}^{\Hermaphrodite,s})/2+(xy_{23}^{\Hermaphrodite,s}+xy_{43}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&- r(xy_{43}^{\Hermaphrodite,s}-xy_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite - \chi(xy_{13}^{\Hermaphrodite,s}-xy_{31}^{\Hermaphrodite,s})/2\\
-&+\big{\{}-(R+r+\chi)xy_{23}^{\Hermaphrodite,s} +(r+\chi-R)xy_{32}^{\Hermaphrodite,s}\\
-&+(R+r-\chi) xy_{14}^{\Hermaphrodite,s} + (R+\chi-r) xy_{41}^{\Hermaphrodite,s}\big{\}}\alpha^\Hermaphrodite/2
+&- r(xy_{43}^{\Hermaphrodite,s}-xy_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite - \rho(xy_{13}^{\Hermaphrodite,s}-xy_{31}^{\Hermaphrodite,s})/2\\
+&+\big{[}-(R+r+\rho)xy_{23}^{\Hermaphrodite,s} +(R+\rho-r)xy_{32}^{\Hermaphrodite,s}\\
+&+(R+r-\rho) xy_{14}^{\Hermaphrodite,s} + (R+\rho-r) xy_{41}^{\Hermaphrodite,s}\big{]}\alpha^\Hermaphrodite/2
 \end{split}
@@
 &(xy_{44}^{\Hermaphrodite,s}+xy_{24}^{\Hermaphrodite,s})/2+(xy_{14}^{\Hermaphrodite,s}+xy_{34}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite)\\
-&- r(xy_{34}^{\Hermaphrodite,s}-xy_{43}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite) - \chi(xy_{24}^{\Hermaphrodite,s}-xy_{42}^{\Hermaphrodite,s})/2\\
-&+\big{\{}-(R+r+\chi) xy_{14}^{\Hermaphrodite,s} + (r+\chi-R)xy_{41}^{\Hermaphrodite,s}\\
-&+(R+r-\chi) xy_{23}^{\Hermaphrodite,s} + (R+\chi-r) xy_{32}^{\Hermaphrodite,s}\big{\}}(1-\alpha^\Hermaphrodite)/2
+&- r(xy_{34}^{\Hermaphrodite,s}-xy_{43}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite) - \rho(xy_{24}^{\Hermaphrodite,s}-xy_{42}^{\Hermaphrodite,s})/2\\
+&+\big{[}-(R+r+\rho) xy_{14}^{\Hermaphrodite,s} + (R+\rho-r)xy_{41}^{\Hermaphrodite,s}\\
+&+(R+r-\rho) xy_{23}^{\Hermaphrodite,s} + (R+\rho-r) xy_{32}^{\Hermaphrodite,s}\big{]}(1-\alpha^\Hermaphrodite)/2
 \end{split}
@@
 We also track the total frequency of Y among male gametes, $q$, which may deviate from $1/2$ due to meiotic drive in males. 
-These four variables determine the frequencies of the six resident gamete types: $x_{1}^{\female}=p_{X}^{\female}$, $x_{2}^{\female}=1-p_{X}^{\female}$, $x_{1}^{\male}=(1-q)p_{X}^{\male}$, $x_{2}^{\male}=(1-q)(1-p_{X}^{\male})$, $y_{1}^{\male}=q p_{Y}^{\male}$, and $y_{2}^{\male}=q(1-p_{Y}^{\male})$.
+These four variables determine the frequencies of the six resident gamete types: $x_{1}^{\female}=\hat{p}_X^\female$, $x_{2}^{\female}=1-\hat{p}_X^\female$, $x_{1}^{\male}=(1-q)\hat{p}_X^\male$, $x_{2}^{\male}=(1-q)(1-\hat{p}_X^\male)$, $y_{1}^{\male}=q \hat{p}_Y^\male$, and $y_{2}^{\male}=q(1-\hat{p}_Y^\male)$.
 Mean fitnesses in the resident population are given in table \ref{tab:meanfitnesses}.
@@
 According to the `small parameter theory' \citep{Karlin:1972ab,Karlin:1972dq}, these stability properties are unaffected by small amounts of recombination between the SDR and \textbf{A} locus, although equilibrium frequencies may be slightly altered.
-For the $a$ allele to be stably fixed on the Y we need $\bar{w}_{Ya}^{\male} > \bar{w}_{YA}^{\male}$ where $\bar{w}_{Ya}^{\male} = w_{a}^{\male} \big[p_{X}^{\female}(1-\alpha^\male_\Delta) w_{A}^{\female} w_{Aa}^{\male} + (1-p_{X}^{\female})w_{a}^{\female} w_{aa}^{\male} \big]$ and $\bar{w}_{YA}^{\male} = w_{A}^{\male} \big[ p_{X}^{\female} w_{A}^{\female} w_{AA}^{\male} + (1-p_{X}^{\female})(1+\alpha^\male_\Delta) w_{a}^{\female} w_{Aa}^{\male} \big]$.
+For the $a$ allele to be stably fixed on the Y we need $\bar{w}_{Ya}^{\male} > \bar{w}_{YA}^{\male}$ where $\bar{w}_{Ya}^{\male} = w_{a}^{\male} \big[\hat{p}_X^\female(1-\alpha^\male_\Delta) w_{A}^{\female} w_{Aa}^{\male} + (1-\hat{p}_X^\female)w_{a}^{\female} w_{aa}^{\male} \big]$ and $\bar{w}_{YA}^{\male} = w_{A}^{\male} \big[ \hat{p}_X^\female w_{A}^{\female} w_{AA}^{\male} + (1-\hat{p}_X^\female)(1+\alpha^\male_\Delta) w_{a}^{\female} w_{Aa}^{\male} \big]$.
 That is, Y-$a$ haplotypes must have higher fitness than Y-$A$ haplotypes.  
-Substituting in $p_{X}^{\female} = \hat{p}_{X}^{\female}$ from above, fixation of the $a$ allele on the Y requires that $\gamma_{i}>0$ where $\gamma_{(A)}=w_{a}^{\male} \big[ (1-\alpha^\male_\Delta) w_{Aa}^{\male} \phi + w_{aa}^{\male} \psi \big]-w_{A}^{\male} \big[ w_{AA}^{\male} \phi + (1 + \alpha^{\male}_\Delta)w_{Aa}^{\male} \psi \big]$ for equilibrium $(A)$ and $\gamma_{(B)}=(1-\alpha^{\male}_\Delta)w_{a}^{\male}w_{Aa}^{\male}-w_{A}^{\male}w_{AA}^{\male}$ for equilibrium $(B)$.
+Substituting in $\hat{p}_X^\female = \hat{p}_{X}^{\female}$ from above, fixation of the $a$ allele on the Y requires that $\gamma_{i}>0$ where $\gamma_{(A)}=w_{a}^{\male} \big[ (1-\alpha^\male_\Delta) w_{Aa}^{\male} \phi + w_{aa}^{\male} \psi \big]-w_{A}^{\male} \big[ w_{AA}^{\male} \phi + (1 + \alpha^{\male}_\Delta)w_{Aa}^{\male} \psi \big]$ for equilibrium $(A)$ and $\gamma_{(B)}=(1-\alpha^{\male}_\Delta)w_{a}^{\male}w_{Aa}^{\male}-w_{A}^{\male}w_{AA}^{\male}$ for equilibrium $(B)$.
 Stability of a polymorphism on the X chromosome (equilibrium $A$) further requires that $\phi >0$ and $\psi >0$. 
@@
 However, because a neo-Y (neo-W) is always in males (females) and is epistatically dominant to the ancestral sex-determining locus, we need only two recursion equations (e.g., tracking the change in the frequency of neo-Y-$A$ and neo-Y-$a$ gametes from males) and thus the leading eigenvalue is the largest solution to a quadratic characteristic polynomial $\lambda^2 + b\lambda + c = 0$ as described in the text (Table \ref{tab:haplotype_growth}).
-%It can be shown (see supplementary Mathematica file) that the coefficients are $b= - (\lambda_{mA} + \lambda_{ma})+(\rho_{mA} + \rho_{ma})$ and $c = (\lambda_{mA}-\rho_{mA}) (\lambda_{ma}-\rho_{ma}) -\rho_{mA} \rho_{ma}$, where $\lambda_{mi}$ is the multiplicative growth rate of the frequency of mutants on background $i\in\{A,a\}$, without accounting for loss due to recombination, and $\rho_{mi}$ is the rate at which mutants on background $i\in\{A,a\}$ recombine onto the other \textbf{A} locus background in heterozygotes.
-%The leading eigenvalue is then greater than one whenever $\lambda_{mA}>1$ and $\lambda_{ma}>1$, less than one whenever $\lambda_{mA}<1$ and $\lambda_{ma}<1$, and greater than one whenever  $\lambda_{mA}>1$ or $\lambda_{ma}>1$ and $\rho_{ma} (\lambda_{mA}-1) + \rho_{mA} (\lambda_{ma}-1) > 0$.
+%It can be shown (see supplementary Mathematica file) that the coefficients are $b= - (\lambda_{mA} + \lambda_{ma})+(\chi_{mA} + \chi_{ma})$ and $c = (\lambda_{mA}-\chi_{mA}) (\lambda_{ma}-\chi_{ma}) -\chi_{mA} \chi_{ma}$, where $\lambda_{mi}$ is the multiplicative growth rate of the frequency of mutants on background $i\in\{A,a\}$, without accounting for loss due to recombination, and $\chi_{mi}$ is the rate at which mutants on background $i\in\{A,a\}$ recombine onto the other \textbf{A} locus background in heterozygotes.
+%The leading eigenvalue is then greater than one whenever $\lambda_{mA}>1$ and $\lambda_{ma}>1$, less than one whenever $\lambda_{mA}<1$ and $\lambda_{ma}<1$, and greater than one whenever  $\lambda_{mA}>1$ or $\lambda_{ma}>1$ and $\chi_{ma} (\lambda_{mA}-1) + \chi_{mA} (\lambda_{ma}-1) > 0$.
 
@@
 { 2w_{AA}^\female } \\
-\rho_{mA}&= \frac{1}{2} \left[w_{a}^\male (1-\alpha^\male_\Delta) \right]^{-1}
+\chi_{mA}&= \frac{1}{2} \left[w_{a}^\male (1-\alpha^\male_\Delta) \right]^{-1}
 \frac{w_{A}^\female }{w_{A}^\female}
@@
 { w_{AA}^\female } \frac{R}{2}\\
-\rho_{ma}&= \frac{1}{2} \left[w_{a}^\male (1-\alpha^\male_\Delta) \right]^{-1}
+\chi_{ma}&= \frac{1}{2} \left[w_{a}^\male (1-\alpha^\male_\Delta) \right]^{-1}
 \frac{w_{a}^\female}{w_{A}^\female}
@@
 \lambda_{ma}&= \frac{a}{b} \left[ w_{Aa}^\female (1-\alpha^\female_\Delta) w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi +  w_{aa}^\female w_a^\male \frac{c}{d}\right] / (2 w_A^\female) \\
-\rho_{mA}&= \frac{a}{b} \frac{R}{2} \left[   w_{Aa}^\female (1+\alpha^\female_\Delta) w_a^\male \frac{c}{d} \right] / w_a^\female\\ 
-\rho_{ma}&= \frac{a}{b} \frac{R}{2} \left[ w_{Aa}^\female (1-\alpha^\female_\Delta) w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi \right] / w_A^\female
+\chi_{mA}&= \frac{a}{b} \frac{R}{2} \left[   w_{Aa}^\female (1+\alpha^\female_\Delta) w_a^\male \frac{c}{d} \right] / w_a^\female\\ 
+\chi_{ma}&= \frac{a}{b} \frac{R}{2} \left[ w_{Aa}^\female (1-\alpha^\female_\Delta) w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi \right] / w_A^\female
 \end{align}
@@
 %\lambda_{ma}&= \frac{a}{b} \left[w_{Aa}^\female w_{Aa}^\male \phi / 2 +  w_{aa}^\female \frac{c}{d}\right] \\
-%\rho_{mA}&= \frac{a}{b} R \left[ w_{Aa}^\female \frac{c}{d} \right] \\ 
-%\rho_{ma}&= \frac{a}{b} R \left[ w_{Aa}^\female w_{Aa}^\male \phi / 2 \right] 
+%\chi_{mA}&= \frac{a}{b} R \left[ w_{Aa}^\female \frac{c}{d} \right] \\ 
+%\chi_{ma}&= \frac{a}{b} R \left[ w_{Aa}^\female w_{Aa}^\male \phi / 2 \right] 
 %\end{align}
@@
 %\lambda_{ma}&=  \frac{(\phi + \psi)[(w_{aa}^\female + w_{Aa}^\female ) w_{Aa}^\male \phi + 2 w_{aa}^\female w_{AA}^\male \psi ]}{2 (w_{AA}^\female w_{Aa}^\male \phi^2 + \psi(w_{Aa}^\female(w_{AA}^\male + w_{Aa}^\male)\phi + w_{aa}^\female w_{AA}^\male \psi)}\\
-%\rho_{mA}&= R \frac{(\phi + \psi) w_{Aa}^\female w_{AA}^\male}{2 (w_{AA}^\female w_{Aa}^\male \phi^2 + \psi(w_{Aa}^\female(w_{AA}^\male + w_{Aa}^\male)\phi + w_{aa}^\female w_{AA}^\male \psi)} \\ 
-%\rho_{ma}&= R \frac{(\phi + \psi) w_{Aa}^\female w_{Aa}^\male}{2 (w_{AA}^\female w_{Aa}^\male \phi^2 + \psi(w_{Aa}^\female(w_{AA}^\male + w_{Aa}^\male)\phi + w_{aa}^\female w_{AA}^\male \psi)}\\
+%\chi_{mA}&= R \frac{(\phi + \psi) w_{Aa}^\female w_{AA}^\male}{2 (w_{AA}^\female w_{Aa}^\male \phi^2 + \psi(w_{Aa}^\female(w_{AA}^\male + w_{Aa}^\male)\phi + w_{aa}^\female w_{AA}^\male \psi)} \\ 
+%\chi_{ma}&= R \frac{(\phi + \psi) w_{Aa}^\female w_{Aa}^\male}{2 (w_{AA}^\female w_{Aa}^\male \phi^2 + \psi(w_{Aa}^\female(w_{AA}^\male + w_{Aa}^\male)\phi + w_{aa}^\female w_{AA}^\male \psi)}\\
 %\end{align}
@@
 %\lambda_{ma}&=  [(w_{aa}^\female + w_{Aa}^\female ) w_{Aa}^\male \phi + 2 w_{aa}^\female w_{AA}^\male \psi ] a\\
-%\rho_{mA}&= R w_{Aa}^\female (w_{Aa}^\male \phi + 2 w_{AA}^\male \psi) c \\ 
-%\rho_{ma}&= R w_{Aa}^\female w_{Aa}^\male \phi c \\
+%\chi_{mA}&= R w_{Aa}^\female (w_{Aa}^\male \phi + 2 w_{AA}^\male \psi) c \\ 
+%\chi_{ma}&= R w_{Aa}^\female w_{Aa}^\male \phi c \\
 %\end{align}
@@
 Panels A, C and D show cases where a steady state is reached with the neo-W at a frequency below $0.5$, in which case ancestral-X and Y alleles also both segregate. 
-In all cases, we assume that the $a$ allele is initially more common that the $A$ allele on the Y (Y$a$ is fixed when $r=0$). 
-When $r>0$ (panels B and D), Y$A$ haplotypes created by recombination can become more common than Y$a$ haplotypes as the neo-W spreads.
-In B, this leads to loss of the neo-W and the system goes to an equilibrium with X$a$ and Y$A$ haplotypes fixed (A'), such that all females have the high fitness genotype $aa$ and all males $Aa$. 
-For the parameters in B, neo-W alleles have negative invasion fitness when the Y$A$ haplotype is ancestrally more common than Y$a$ (see blue line in Figure \ref{fig:temporalOverdominance}A and  \ref{fig:temporalOverdominance}B).
+In all cases, we assume that the $a$ allele is initially more common that the $A$ allele on the Y (Y-$a$ is fixed when $r=0$). 
+When $r>0$ (panels B and D), Y-$A$ haplotypes created by recombination can become more common than Y-$a$ haplotypes as the neo-W spreads.
+In B, this leads to loss of the neo-W and the system goes to an equilibrium with X-$a$ and Y-$A$ haplotypes fixed (A'), such that all females have the high fitness genotype $aa$ and all males $Aa$. 
+For the parameters in B, neo-W alleles have negative invasion fitness when the Y-$A$ haplotype is ancestrally more common than Y-$a$ (see blue line in Figure \ref{fig:temporalOverdominance}A and  \ref{fig:temporalOverdominance}B).
 In contrast, the neo-W is not lost in panel D (see blue line in Figure \ref{fig:temporalOverdominance}C and  \ref{fig:temporalOverdominance}D). 

### 2017-09-21 LaTeX/Turnover.tex

@@
 Just to check, I should have written $\alpha^\Hermaphrodite=(1+\alpha_{\Delta}^\Hermaphrodite)/2$, maybe that's where the factors of $1/2$ come from?}
-\textcolor{blue}{shoot, i may have changed too much (i.e. strong selection too), but i did use the correct transformation. still, the form of S.8c,d seems wrong. I'll double check it.}
+\textcolor{blue}{shoot, i may have changed too much (i.e.
+strong selection too), but i did use the correct transformation.
+still, the form of S.8c,d seems wrong.
+I'll double check it.
+CANT FIND ANY ERRORS YET STILL HAVE A "2" IN S.8c.
+These 2s reappear in S.9 and S.10, always with $W_{AA}$.}
 
@@
 \textcolor{red}{Mention the possibility that the other roots yield the leading eigenvalue somewhere.}
+\textcolor{blue}{following the logic above, it seems like we say we go from 8 eqns to 4 eqns by considering only one sex, and then from 4 eqns to 2 eqns by ignoring the ancestral SD allele.
+why then do we have the two quadratic problem?}
 $\lambda^2+ b \lambda + c =0$.
@@
 %The latter predicts that neo-W alleles will invade an XY system when there is a male bias caused by haploid selection in males, and vice-versa, a neo-Y will invade a ZW system when there is a female bias caused by haploid selection in females \citep{Kozielska:2010vm,Ubeda:2015fx}.
-Firstly, we show that selection (including sexually-antagonistic selection) on loci within or near the non-recombining region of the ancestral sex-determining region can favour heterogametic transitions (XY to ZW or ZW to XY) to new sex-determining systems that have looser linkage (e.g., see Figure \ref{fig:SexAntagTighter}).
-Secondly, assuming that selection is weak relative to recombination, we show that new sex-determining alleles are typically favoured if they are more closely linked to a locus under haploid selection, which is the only condition favouring homogametic transitions (XY to XY or ZW to ZW).
+Firstly, we show that selection (including sexually-antagonistic selection) on loci within or near the non-recombining region of the ancestral sex-determining region can favour heterogametic transitions (XY to ZW or ZW to XY) to new sex-determining systems that are less closely linked to the selected loci (e.g., see Figure \ref{fig:SexAntagTighter}).
+Secondly, assuming that selection is weak relative to recombination (`weak selection'), we show that new sex-determining alleles are typically favoured if they are more closely linked to a locus under haploid selection, which is the only condition favouring homogametic transitions (XY to XY or ZW to ZW).
 In addition, with haploid selection and weak selection, heterogametic transitions (XY to ZW or ZW to XY) can occur even when the new sex-determining region is less closely linked to the locus under selection (e.g., see Figure \ref{fig:SexRatioBad}).
+\textcolor{red}{need to mention sex ratio here}
 %Neo-W (neo-Y) alleles invade when their fitness in females (males) is greater than the mean fitness of females (males) under the ancestral sex-determination system and/or females (males) are the rarer sex.
@@
 \smallskip
-\caption{$\rho$ substitutions for different loci orders (assuming no interference)}
+\caption{Values of $\rho$ for different loci orders assuming no interference and $r,R\in(0,1/2)$.}
 \begin{tabular}{l l}
@@
 b &= w_{AA}^\female \phi \left[ w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi \right]+ w_{Aa}^\female \psi \left[ w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi + w_{AA}^\male w_a^\male \psi \right] + w_{aa}^\female \psi \left( w_{AA}^\male w_a^\male \psi \right)\\
-c &= w_{Aa}^\male (1-\alpha^\male_\Delta) \phi \left[ w_{Aa}^\male (1+\alpha^\male_\Delta) \phi \right] + 2w_{Aa}^\male\phi(w_{AA}^\male \psi + w_{aa}^\male \alpha^\male \psi ) + 2w_{aa}^\male \psi w_{AA}^\male \psi \\
-d &= w_{Aa}^\male (1+\alpha^\male) \phi + w_{aa}^\male \psi
+%c &= w_{Aa}^\male (1-\alpha^\male_\Delta) \phi \left[ w_{Aa}^\male (1+\alpha^\male_\Delta) \phi \right] + w_{Aa}^\male\phi \left[ 2w_{AA}^\male + w_{aa}^\male (1+\alpha^\male_\Delta) \right] \psi + w_{aa}^\male \psi \left(2w_{AA}^\male \psi \right) \\
+c &= 
+w_{Aa}^\male (1+\alpha^\male_\Delta) \phi \left[ w_{Aa}^\male (1-\alpha^\male_\Delta) \phi + w_{aa}^\male \psi \right] +
+2 w_{AA}^\male\psi \left[ w_{Aa}^\male \phi + w_{aa}^\male \psi \right]
+ \\
+d &= w_{Aa}^\male (1+\alpha^\male_\Delta) \phi + w_{aa}^\male \psi
 \end{align}

### 2017-09-22 LaTeX/Turnover.tex
lining up red and black in fig 3

@@
 \textcolor{red}{Check the mismatch between red and black lines here: probably because of adding or subtracting from 1. }
+\textcolor{blue}{Can remove the mismatch by flipping the fitnesses between males and females (again).
+That is, if $M_{AA}$ is the fitness of $AA$ male diploids in an ancestral XY system, then $M_{AA}$ is the fitness of $AA$ female diploids in an ancestral ZW system.
+I think this makes sense in A, where we don't really want a difference between the red and black curves, but this makes less sense in B and C where we want to restrict haploid selection to males regardless of the ancestral system.
+We could just not flip the haploid fitnesses, but then does it make sense to flip the diploid fitnesses?}
 }

### 2017-09-22 LaTeX/Turnover.tex
checked stability of tight B condition and W invasion into tight B

@@
 
-\textcolor{red}{Change all  $\alpha^\Hermaphrodite$ to $(1+\alpha_{\Delta}^\Hermaphrodite)$.}
-\textcolor{blue}{I've attempted this everywhere except in the recursions (S.1), which seem more natural with $\alpha$'s.
+%\textcolor{red}{Change all  $\alpha^\Hermaphrodite$ to $(1+\alpha_{\Delta}^\Hermaphrodite)$.}
+%\textcolor{blue}{I've attempted this everywhere except in the recursions (S.1), which seem more natural with $\alpha$'s.
 I've run into trouble in equation S.8c,d -- I think we should check the Mathematica results to be sure we haven't made a typo.
 This also introduced an extra 1/2 in S.6c,d that might need to be explained.}
-\textcolor{red}{hmm, not sure.
+%\textcolor{red}{hmm, not sure.
 This was an idea from Sally, I think in response to terms like $2 \alpha^\Hermaphrodite$ and $2(1-\alpha^\Hermaphrodite)$.
@@
 Just to check, I should have written $\alpha^\Hermaphrodite=(1+\alpha_{\Delta}^\Hermaphrodite)/2$, maybe that's where the factors of $1/2$ come from?}
-\textcolor{blue}{shoot, i may have changed too much (i.e.
+%\textcolor{blue}{shoot, i may have changed too much (i.e.
 strong selection too), but i did use the correct transformation.
@@
 \textcolor{blue}{following the logic above, it seems like we say we go from 8 eqns to 4 eqns by considering only one sex, and then from 4 eqns to 2 eqns by ignoring the ancestral SD allele.
-why then do we have the two quadratic problem?}
+why then do we have the two quadratic problem?
+(b/c the $m$ alleles can arise in either sex?)}
 $\lambda^2+ b \lambda + c =0$.
@@
 Stability of a polymorphism on the X chromosome (equilibrium $A$) further requires that $\phi >0$ and $\psi >0$. 
-Fixation of the $a$ allele on the X (equilibrium $B$) can be stable only if equilibrium $(A)$ is not and requires $\psi<0$ and $w_{A}^{\female}w_{AA}^{\female}>(1-\alpha^{\female})w_{a}^{\female}w_{Aa}^{\female}$.
+Fixation of the $a$ allele on the X (equilibrium $B$) can be stable only if equilibrium $(A)$ is not, as it requires $\psi<0$ and $2w_{A}^{\female}w_{AA}^{\female}>(1-\alpha_\Delta^{\female})w_{a}^{\female}w_{Aa}^{\female}$ or just $4w_{A}^{\female}w_{AA}^{\female}<(1-\alpha_\Delta^{\female})w_{a}^{\female}w_{Aa}^{\female}$ (which prevents $\psi>0$).
 
 \textcolor{red}{check last condition and the stability condition below are correct}
+\textcolor{blue}{The last condition looks good to me, although in your Turnover-norec-MFS.nb you look at YA fixed, so you have to flip everything (so I made Turnover-norec-MFS-MMO.nb to do this).
+The one issue I can find here is that you can also prevent $\lambda>1$ when the slope and intercept of the quadratic, $f(\lambda)$, at $\lambda=1$ are negative (you only looked at both being positive).
+In this case we need $4w_{A}^{\female}w_{AA}^{\female}<(1-\alpha_\Delta^{\female})w_{a}^{\female}w_{Aa}^{\female}$, which also prevents $\psi>0$.
+I've added this in.
+It could also be the case that the slope and intercept are the same sign but the roots are imaginary - but this is never the case here.
+Stability condition below looks good to me (from matt version of turnoverSOM-MIKE.nb).}
 
@@
 At equlibrium $(B)$, neo-W female gametes will mate with X-$A$ male gametes with probability $ w_A^\male (1+\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$ and Y-$a$ male gametes with probability $w_a^\male (1-\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$, where the $2\bar{w}_{H}^\male$ terms have been canceled in equation \eqref{Binvasion} (as mentioned above).
-Thus, for example, neo-W-$A$ haplotypes are found in $AA$ female diploids with probability $ w_A^\male (1+\alpha^\male_\Delta)/ (2\bar{w}_{H}^\male)$ (first term in square brackets in the numerator of equation \ref{Binvasion}a) and in $Aa$ female diploids with probability $w_a^\male (1-\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$ (see equation \ref{Binvasion}c and second term in square brackets in the numerator of equation \ref{Binvasion}a).
+Thus, for example, neo-W-$A$ haplotypes are found in $AA$ female diploids with probability $ w_A^\male (1+\alpha^\male_\Delta)/ (2\bar{w}_{H}^\male)$ (first term in square brackets in the numerator of equation \ref{Binvasion}a) and in $Aa$ female diploids with probability $w_a^\male (1-\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$ (see equation \ref{Binvasion}c and the second term in square brackets in the numerator of equation \ref{Binvasion}a).
 
@@
 %If $\lambda_{mA}>1$ (requiring $w_{Aa}^\female>w_{AA}^\female$), the implication is that the neo-W can spread alongside the $A$ allele, despite the fact that the neo-W sometimes brings $Y-a$ haplotypes into females, because $a$ is favoured by selection in females despite $A$ being fixed on the X.
-A neo-W can spread alongside the $A$ allele ($\lambda_{mA}>1$), despite the fact that a neo-W brings Y-$a$ haplotypes into females, when $w_{Aa}^\female>w_{AA}^\female$.
+A neo-W can spread alongside the $A$ allele ($\lambda_{mA}>1$), despite the fact that a neo-W brings Y-$a$ haplotypes into females, when $w_{Aa}^\female>w_{AA}^\female$, as stated above.
 In this case the $a$ allele is favoured by selection in females despite $A$ being fixed on the X.
-For this equilibrium to be stable, X-$A$ must be sufficiently favoured in males (for example, by overdominance in males, remembering that $a$ is fixed on the Y) to keep $A$ fixed on the X. 
-Specifically, from the stability conditions for equilibrium (B), we must have $w_{Aa}^\male/\big[(w_{aa}^\male+w_{Aa}^\male)/2\big]>w_{Aa}^\female/w_{AA}^\female$.
-
-Still considering $w_{Aa}^\female>w_{AA}^\female$, the neo-W can also spread alongside the $a$ allele ($\lambda_{ma}>1$) if there is sufficiently strong underdominance in females ($w_{aa}^\female>w_{Aa}^\female$) \textcolor{red}{[this is describing directional selection, not overdominance - check the conditions for the case we want to talk about]}, such that $(w_{Aa}^\female+w_{aa}^\female)/2>w_{AA}^\female$.
-In this case, $a$ is not favored in females near the equilibrium where females are $AA$ (comparing $Aa$ to $AA$ genotypes) and yet the neo-W can spread with $a$ because it produces female $aa$ individuals by capturing Y-$a$ haplotypes.
+For this equilibrium to be stable (i.e.,  to keep $A$ fixed on the X), X-$a$ cannot be overly favoured in females and X-$A$ must be sufficiently favoured in males (for example, by overdominance in males, remembering that $a$ is fixed on the Y).
+Specifically, from the stability conditions for equilibrium (B), we must have $w_{Aa}^\female < 2 w_{AA}^\female$ and $w_{Aa}^\male/\big[(w_{aa}^\male+w_{Aa}^\male)/2\big]>w_{Aa}^\female/w_{AA}^\female$.
+
+Still considering $w_{Aa}^\female>w_{AA}^\female$, the neo-W can also spread alongside the $a$ allele ($\lambda_{ma}>1$) if $w_{aa}^\female$ is large enough such that $(w_{Aa}^\female+w_{aa}^\female)/2>w_{AA}^\female$.
+%there is sufficiently strong underdominance in females ($w_{aa}^\female>w_{Aa}^\female$) \textcolor{blue}{[this is describing directional selection, not overdominance - check the conditions for the case we want to talk about]}, such that $(w_{Aa}^\female+w_{aa}^\female)/2>w_{AA}^\female$.
+This can occur with overdominance or directional selection for $a$ in females (Figure \ref{fig:regionplots}B,C).
+\textcolor{blue}{mike, you might want to check these last two statements, and the following.}
+In this case, $a$ is not favoured enough in females near the equilibrium (comparing $Aa$ to $AA$ genotypes) to prevent $A$ from stably fixing on the X, and yet the neo-W can spread with $a$ because it produces female $aa$ individuals by capturing Y-$a$ haplotypes.
 

### 2017-09-25 LaTeX/Turnover.tex
female gam sel plot

@@
 \textcolor{blue}{The last condition looks good to me, although in your Turnover-norec-MFS.nb you look at YA fixed, so you have to flip everything (so I made Turnover-norec-MFS-MMO.nb to do this).
-The one issue I can find here is that you can also prevent $\lambda>1$ when the slope and intercept of the quadratic, $f(\lambda)$, at $\lambda=1$ are negative (you only looked at both being positive).
+The one issue I can find here is that you can also prevent $\lambda>1$ when the slope and intercept of the quadratic at $\lambda=1$ are negative (you only looked at both being positive).
 In this case we need $4w_{A}^{\female}w_{AA}^{\female}<(1-\alpha_\Delta^{\female})w_{a}^{\female}w_{Aa}^{\female}$, which also prevents $\psi>0$.
@@
 This can occur with overdominance or directional selection for $a$ in females (Figure \ref{fig:regionplots}B,C).
-\textcolor{blue}{mike, you might want to check these last two statements, and the following.}
+\textcolor{blue}{mike, you might want to check these last two statements i've edited, and the following.}
 In this case, $a$ is not favoured enough in females near the equilibrium (comparing $Aa$ to $AA$ genotypes) to prevent $A$ from stably fixing on the X, and yet the neo-W can spread with $a$ because it produces female $aa$ individuals by capturing Y-$a$ haplotypes.
@@
 
+\begin{figure}[!h]
+\centering
+\centerline{\includegraphics[width=\linewidth]{Region_Plot_combined_FemaleDrive_Mike}}
+\caption{
+ABC, $\alpha_{\Delta}^\female=-0.08$
+DEF, $\alpha_{\Delta}^\female=0.08$. \textcolor{red}{Panel F mislabelled, should have $\lambda_{Wa}>1$ \& $\lambda_{WA}<1$ as the upper label that has the line.}
+}
+\label{fig:regionFemaleDrive}
+\end{figure}
+
 \newpage

### 2017-09-27 LaTeX/Turnover.tex
labels added to female gam comp region plot

@@
 Thus, the invasion of rare dominant neo-Y or neo-W alleles is determined by the largest eigenvalue that solves a quadratic characteristic polynomial,
-\textcolor{red}{Mention the possibility that the other roots yield the leading eigenvalue somewhere.}
-\textcolor{blue}{following the logic above, it seems like we say we go from 8 eqns to 4 eqns by considering only one sex, and then from 4 eqns to 2 eqns by ignoring the ancestral SD allele.
+%\textcolor{red}{Mention the possibility that the other roots yield the leading eigenvalue somewhere.}
+%\textcolor{blue}{following the logic above, it seems like we say we go from 8 eqns to 4 eqns by considering only one sex, and then from 4 eqns to 2 eqns by ignoring the ancestral SD allele.
 why then do we have the two quadratic problem?
 (b/c the $m$ alleles can arise in either sex?)}
-$\lambda^2+ b \lambda + c =0$.
+$\lambda^2+ b \lambda + c =0$ (see Appendix for a discussion of other roots).
 %\begin{equation}
@@
 }
+\textcolor{blue}{trouble is selection only in heterozygotes with drive?}
 }
@@
 ABC, $\alpha_{\Delta}^\male=-0.08$
-DEF, $\alpha_{\Delta}^\male=0.08$. \textcolor{red}{Panel F mislabelled, should have $\lambda_{Wa}>1$ \& $\lambda_{WA}<1$ as the upper label that has the line.}
+DEF, $\alpha_{\Delta}^\male=0.08$. 
+%\textcolor{red}{Panel F mislabelled, should have $\lambda_{Wa}>1$ \& $\lambda_{WA}<1$ as the upper label that has the line.}
 }
 \label{fig:regionMaleDrive}
+\end{figure}
+
+\begin{figure}[!h]
+\centering
+\centerline{\includegraphics[width=\linewidth]{Region_Plot_combined_FemaleGS_Mike}}
+\caption{
+ABC, $w_{a}^\female=1.16$, $w_{A}^\female=1$.
+DEF, $w_{a}^\female=1$, $w_{A}^\female=1.16$. 
+%\textcolor{red}{Panel F mislabelled, should have $\lambda_{Wa}>1$ \& $\lambda_{WA}<1$ as the upper label that has the line.}
+}
+\label{fig:regionFemaleGS}
 \end{figure}
@@
 
-\begin{figure}[!h]
-\centering
-\centerline{\includegraphics[width=\linewidth]{Region_Plot_combined_FemaleDrive_Mike}}
-\caption{
-ABC, $\alpha_{\Delta}^\female=-0.08$
-DEF, $\alpha_{\Delta}^\female=0.08$. \textcolor{red}{Panel F mislabelled, should have $\lambda_{Wa}>1$ \& $\lambda_{WA}<1$ as the upper label that has the line.}
-}
-\label{fig:regionFemaleDrive}
-\end{figure}
-
 \newpage

### 2017-09-28 LaTeX/Turnover.tex
ploidally antag region plots added

@@
 
+\begin{figure}[!h]
+\centering
+\centerline{\includegraphics[width=0.35\linewidth]{Region_plot_combined_PloidAntag_Matt}}
+\caption{
+$h=0.75$
+}
+\label{fig:regionPloidAntag}
+\end{figure}
+
 \newpage
@@
 In an email, Sally has an example of ploidally-antagonistic selection where the neo-W fixes and $R=1/2$. This would cover that case and more. }
+\textcolor{blue}{
+did the region plots (Figure \ref{fig:regionPloidAntag}), yet to add the temporal dynamics
+}
 
@@
 Try to integrate into the discussion of haploid selection? e.g., male haploid selection ones generally show effect of sex ratio, increasing both lambdas when female biased (top rows).}
+\textcolor{blue}{
+these figures are now done (ensuring frequencies between 0 and 1), but yet to discuss in text.}
 

### 2017-09-28 LaTeX/Turnover.tex
added big sup ploid antag plot

--- 2017-09-27 LaTeX/Turnover.tex
@@
 \usetikzlibrary{positioning}%for relative positioning
+
+%to rotate figures
+\usepackage{rotating}
+\usepackage{pdflscape}
 
@@
 
+\begin{figure}[!h]
+\centering
+\centerline{\includegraphics[width=\linewidth]{Region_Plot_combined_MaleDrive_Mike}}
+\caption{
+ABC, $\alpha_{\Delta}^\male=-0.08$
+DEF, $\alpha_{\Delta}^\male=0.08$. 
+%\textcolor{red}{Panel F mislabelled, should have $\lambda_{Wa}>1$ \& $\lambda_{WA}<1$ as the upper label that has the line.}
+}
+\label{fig:regionMaleDrive}
+\end{figure}
+
 \newpage
@@
 \centering
-\centerline{\includegraphics[width=\linewidth]{Region_Plot_combined_MaleDrive_Mike}}
+\centerline{\includegraphics[width=\linewidth]{Region_Plot_combined_FemaleDrive_Mike}}
 \caption{
-ABC, $\alpha_{\Delta}^\male=-0.08$
-DEF, $\alpha_{\Delta}^\male=0.08$. 
-%\textcolor{red}{Panel F mislabelled, should have $\lambda_{Wa}>1$ \& $\lambda_{WA}<1$ as the upper label that has the line.}
-}
-\label{fig:regionMaleDrive}
+ABC, $\alpha_{\Delta}^\female=-0.08$
+DEF, $\alpha_{\Delta}^\female=0.08$. $\lambda$s are increased for the haplotype that is favoured by female haploid selection, the stability conditions are also affected. 
+}
+\label{fig:regionFemaleDrive}
 \end{figure}
@@
 
+\begin{landscape}
 \begin{figure}[!h]
 \centering
-\centerline{\includegraphics[width=\linewidth]{Region_Plot_combined_FemaleDrive_Mike}}
+\centerline{
+\includegraphics[width=\linewidth]{All_plot_combined_PloidAntag_Matt}
+}
 \caption{
-ABC, $\alpha_{\Delta}^\female=-0.08$
-DEF, $\alpha_{\Delta}^\female=0.08$. $\lambda$s are increased for the haplotype that is favoured by female haploid selection, the stability conditions are also affected. 
-}
-\label{fig:regionFemaleDrive}
+A-D show when each of the neo-W haplotypes invade an internally stable equilibrium with $a$ fixed on the Y (found by setting $r=0$).
+The y-axis shows directional selection in diploids of both sexes, $s^\female=s^\male$, and the x-axes show sex-specific drive, $\alpha_\Delta^\Hermaphrodite$, or haploid competition, $t^\Hermaphrodite$.
+The top left and bottom right quadrants therefore imply ploidally-antagonistic selection (and these are the only places where.
+Dominance is equal in both sexes, $h^\female=s^\male=3/4$. 
+E-F show the temporal dynamics of neo-W frequency with parameters given by the asterisks in the corresponding A-D plot, with $r=1/200$, for four different $R$.
+Black $R=1/1000$, Red $R=2/100$, Blue $R=1/10$, Green $R=1/2$.  
+Dashed line in E-H gives ``fixation" of neo-W.
+\textcolor{blue}{here and elsewhere, we may want to switch to plotting freq of neo-W in females, so that we can see if the difference from 0.5 is due to biased sex ratios or polymorphic SD}
+}
+\label{fig:regionPloidAntag}
 \end{figure}
+\end{landscape}
 
@@
 In an email, Sally has an example of ploidally-antagonistic selection where the neo-W fixes and $R=1/2$. This would cover that case and more. }
+\textcolor{blue}{
+made an attempt (Figure \ref{fig:regionPloidAntag})
+}
 
@@
 Try to integrate into the discussion of haploid selection? e.g., male haploid selection ones generally show effect of sex ratio, increasing both lambdas when female biased (top rows).}
+\textcolor{blue}{
+these figures are now done (\ref{fig:regionMaleDrive}-\ref{fig:regionFemaleGS}) (ensuring frequencies between 0 and 1), but yet to discuss in text.}
 

### 2017-09-29 LaTeX/Turnover.tex
added temporal dynamics plot showing polymorphic SD

@@
 Fisherian sex-ratio selection alone is not a good predictor of turnover between sex-determining systems.
-In this figure, selection is ploidally antagonistic with haploid selection favouring the $a$ allele during male meiosis ($s^\female =s^\male = 0.2$, $h^\female = h^\male = 0.7$, $t^\female = t^\male = \alpha^\male_\Delta = 0$).
+In this figure, selection is ploidally antagonistic with haploid selection favouring the $a$ allele during male meiosis.
 In panel A, male drive in an ancestral ZW system has no affect on the zygotic sex ratio, yet a neo-Y can invade and replace the ancestral sex-determination system (inset shows neo-Y frequency among male gametes, the ancestral W also goes to fixation during this transition).
@@
 In panel B, male drive in an ancestral XY system causes a male bias, allowing a neo-W to invade and replace the ancestral sex-determination system (inset shows neo-W frequency among female gametes, the ancestral Y also goes to fixation), which balances the zygotic sex ratio.
-Parameters:  $s^\female =s^\male = 0.2$, $h^\female = h^\male = 0.7$, $t^\female = t^\male = \alpha^\male_\Delta = 0$, $\alpha^\male_\Delta = -0.2$, $r=0.02$.
+Parameters:  $s^\female =s^\male = 0.2$, $h^\female = h^\male = 0.7$, $t^\female = t^\male = \alpha^\female_\Delta = 0$, $\alpha^\male_\Delta = -0.1$, $r=0.02$.
 }
@@
 \smallskip
-\caption{Values of $\rho$ for different loci orders assuming no interference and $r,R\in(0,1/2)$.}
+\caption{Values of $\rho$ for different loci orders assuming no interference and $r,R\in(0,1/2)$.\textcolor{blue}{write all in form of first line?
+so that 1/2 cases are okay (can't determine chi if R is 1/2 in second line, or if r is 1/2 in third line}}
 \begin{tabular}{l l}
@@
 Check that we mention Sally's result that invasion cannot occur with sexually-antagonistic selection and $R=1/2$ (currently only in legend for figure \ref{fig:SexAntagTighter}) 
-Add asterisk to Figure \ref{fig:regionMaleDrive}B to show parameters used in this plot. 
-}
-$w_{aa}^\female=1.05$, $w_{Aa}^\Hermaphrodite=1$, $w_{AA}^\female=0.85$, $w_{aa}^\male=0.85$, $w_{AA}^\female=1.05$, $\alpha_{\Delta}^\male=-0.08$.
+Add asterisk to Figure \ref{fig:regionMaleDrive}A to show parameters used in this plot. 
+}
+$w_{AA}^\female=1.05$, $w_{Aa}^\Hermaphrodite=1$, $w_{aa}^\female=0.85$, $w_{AA}^\male=0.85$, $w_{aa}^\male=1.05$, $\alpha_{\Delta}^\male=-0.08$.
 }
@@
 The top left and bottom right quadrants therefore imply ploidally-antagonistic selection (and these are the only places where.
-Dominance is equal in both sexes, $h^\female=s^\male=3/4$. 
-E-F show the temporal dynamics of neo-W frequency with parameters given by the asterisks in the corresponding A-D plot, with $r=1/200$, for four different $R$.
+Dominance is equal in both sexes, $h^\female=h^\male=3/4$. 
+E-F show the temporal dynamics of neo-W frequency in females with parameters given by the asterisks in the corresponding A-D plot, with $r=1/200$, for four different $R$.
 Black $R=1/1000$, Red $R=2/100$, Blue $R=1/10$, Green $R=1/2$.  
-Dashed line in E-H gives ``fixation" of neo-W.
-\textcolor{blue}{here and elsewhere, we may want to switch to plotting freq of neo-W in females, so that we can see if the difference from 0.5 is due to biased sex ratios or polymorphic SD}
+Dashed line in E-H gives ``fixation" of neo-W (all females heterozygous ZW).
 }
@@
 \end{landscape}
+
+\begin{landscape}
+\begin{figure}[!h]
+\centering
+\centerline{
+\includegraphics[width=\linewidth]{Freq_plot_combined_PloidAntag_Matt}
+}
+\caption{
+Dynamics of all sex-determining alleles in each sex (males dashed).
+Red is neo-W, Blue is Y, Black is $A$.
+Panel A has the same parameters as the green curve in Figure \ref{fig:SexRatioBad}B (ploidy-antagonism with male drive).
+Panel B has the same parameters as the green curve in Figure \ref{fig:temporalOverdominance}C (overdominance in both sexes).
+Panel C has the same parameters as the green curve in Figure \ref{fig:regionMaleDrive}C (sexual-antagonism with male drive).
+Panel D has the same parameters as the red curve in Figure \ref{fig:regionPloidAntag}F, except $r=0$ (ploidy-antagonism with pollen competition)
+Panel A shows complete sex-determination turnover (XY $\rightarrow$ ZW) whereas panels B-D show the evolution of polymorphic sex-determining systems (X and Y still segregating and the neo-W has a frequency in females that is less than 1/2).
+All begin from equilibrium that would have $a$ fixed on the Y if $r=0$.
+All maintain a polymorphism at $\mathbf{A}$ locus.
+}
+\label{fig:freqAll}
+\end{figure}
+\end{landscape}
+
+\begin{figure}[!h]
+\centering
+\centerline{
+\includegraphics[width=\linewidth]{Sallys_R_plot.pdf}
+}
+\caption{
+\textcolor{blue}{is this the one?}
+}
+\label{fig:lambda_R}
+\end{figure}
 
@@
 Add references to this figure to appendix where we discuss whether lambdas can be greater than 1 with sexually antagonistic selection.}
+\textcolor{blue}{not sure which one you are talking about, but see Figure \ref{fig:lambda_R} }
 
@@
 }
+\textcolor{blue}{made an attempt with Figure \ref{fig:freqAll}, but yet to discuss in text}
 

### 2017-09-30 LaTeX/Turnover.tex
working out general invasion criteria

@@
 We are particularly concerned with the conditions under which a rare neo-sex-determining allele increases in frequency, which occurs when the largest eigenvalue, $\lambda$, is greater than one. 
-If the average change in frequency of the two haplotypes that carry the $m$ allele ($Am$ and $am$) is positive, invasion will always occur, i.e., if $(\lambda_{mA} + \lambda_{ma})/2 > 1$ then $\lambda > 1$.
-If neither haplotype increases in frequency ($\lambda_{mA}, \lambda_{ma} < 1$), the $m$ allele will not invade. 
+%If the average change in frequency of the two haplotypes that carry the $m$ allele ($Am$ and $am$) is positive, invasion will always occur, i.e., if $(\lambda_{mA} + \lambda_{ma})/2 > 1$ then $\lambda > 1$.
+Given the characteristic polynomial and the Perron-Forbenius theorem, at least one $\lambda$ is greater than one when $b<2$ (see supplementary material for details), or  $(\lambda_{mA} - \chi_{mA})/2 + (\lambda_{ma} -  \chi_{ma})/2 > 1$.
+In words, the neo-sex-determining allele will certainly spread when the average change in its frequency, considering that recombination breaks up mutant haplotypes but ignoring the fact that recombination also creates mutant haplotypes, is positive.
+We are also guaranteed to have at least one $\lambda$ greater than one when 1 + b + c < 0.
+This is never true if $\lambda_{mA} < 1$ and $\lambda_{ma} < 1$, i.e., if neither haplotype increases in frequency the neo-sex-determining allele will not invade. 
 Otherwise, the new sex-determining allele increases in frequency on one \textbf{A} background and declines on the other, and invasion requires 

### 2017-09-30 LaTeX/Turnover.tex
still wprking out general invaiosn conditions

--- 2017-09-29 LaTeX/Turnover.tex
@@
 We are particularly concerned with the conditions under which a rare neo-sex-determining allele increases in frequency, which occurs when the largest eigenvalue, $\lambda$, is greater than one. 
-If the average change in frequency of the two haplotypes that carry the $m$ allele ($Am$ and $am$) is positive, invasion will always occur, i.e., if $(\lambda_{mA} + \lambda_{ma})/2 > 1$ then $\lambda > 1$.
-If neither haplotype increases in frequency ($\lambda_{mA}, \lambda_{ma} < 1$), the $m$ allele will not invade. 
-Otherwise, the new sex-determining allele increases in frequency on one \textbf{A} background and declines on the other, and invasion requires 
+%If the average change in frequency of the two haplotypes that carry the $m$ allele ($Am$ and $am$) is positive, invasion will always occur, i.e., if $(\lambda_{mA} + \lambda_{ma})/2 > 1$ then $\lambda > 1$.
+Given the characteristic polynomial and the Perron-Forbenius theorem (see supplementary material for details), at least one $\lambda$ is greater than one when $2 + b < 0$, or  $(\lambda_{mA} - \chi_{mA}) + (\lambda_{ma} -  \chi_{ma}) > 2$.
+In words, the neo-sex-determining allele will certainly spread when the average change in its frequency, taking into account that recombination breaks up mutant $mi$ haplotypes (at rate $\chi_{mi}$) but ignoring the fact that recombination also creates mutant haplotypes, is positive.
+We are also guaranteed to have at least one $\lambda$ greater than one when 1 + b + c < 0.
+This is never true if neither haplotype can spread ($\lambda_{mA}, \lambda_{ma} < 1$). 
+%If both haplotypes can spread ($\lambda_{mA}, \lambda_{ma} > 1$), this condition becomes $\chi_{mA}/(\lambda_{mA} - 1) + \chi_{ma}/(\lambda_{ma} -  1) > 1$.
+If only one haplotype can spread then the new sex-determining allele increases in frequency on one \textbf{A} background and declines on the other, and invasion requires 
 \begin{equation}\label{eq:lambdasGen}
 %\frac{\chi_{mA}}{\lambda_{mA}-1}+\frac{\chi_{ma}}{\lambda_{ma}-1}>0.
-\chi_{ma}\left(\lambda_{mA}-1\right)+\chi_{mA}\left(\lambda_{ma}-1\right)>0.
+\chi_{ma}/\left(\lambda_{ma}-1\right)+\chi_{mA}/\left(\lambda_{mA}-1\right)<1.
 \end{equation}
-\noindent For example, if we assume that only the $mA$ haplotype has a positive growth rate ($\lambda_{ma}<1<\lambda_{mA}$), the second term on the left-hand side of \eqref{eq:lambdasGen} is negative and invasion requires that the growth rate of $mA$ haplotypes and the rate at which they are produced by recombination is sufficiently large relative to that of $ma$ haplotypes.
-In other words, invasion requires that the average growth rate of the two haplotypes, weighted by the rates they are created by recombination, is positive.
+\noindent For example, if we assume that only the $mA$ haplotype has a positive growth rate ($\lambda_{ma}<1<\lambda_{mA}$), the first term on the left-hand side of \eqref{eq:lambdasGen} is negative and invasion requires that the growth rate of $mA$ haplotypes ($\lambda_{mA}-1$) and the rate at which they are produced by recombination in $ma$ haplotypes ($\chi_{ma}$) are sufficiently large relative to the growth rate and recombination gain of $ma$ haplotypes.
+\textcolor{blue}{i've updated this section with the correct $\lambda$ and $\chi$ terms.
+still a bit funny that not guaranteed invasion when both lambdas greater than one, and when both are greater than one then the condition above, (1), has the inequality flipped, which makes no sense (no invasion if no recombination despite both haplotypes growing).
+perhaps i made a mistake somewhere?
+see turnoverhomhet.nb}
+%In other words, invasion requires that the average growth rate of the two haplotypes, weighted by the rates they are created by recombination, is positive.
 %the number of recombinants from the fitter $mA$ haplotypes is larger than that of the less fit $ma$ haplotypes, relative to their growth rates.

### 2017-10-02 LaTeX/Turnover.tex
putting mscotts general condition in the text

@@
 %If the average change in frequency of the two haplotypes that carry the $m$ allele ($Am$ and $am$) is positive, invasion will always occur, i.e., if $(\lambda_{mA} + \lambda_{ma})/2 > 1$ then $\lambda > 1$.
-Given the characteristic polynomial and the Perron-Forbenius theorem (see supplementary material for details), at least one $\lambda$ is greater than one when $2 + b < 0$, or  $(\lambda_{mA} - \chi_{mA}) + (\lambda_{ma} -  \chi_{ma}) > 2$.
-In words, the neo-sex-determining allele will certainly spread when the average change in its frequency, taking into account that recombination breaks up mutant $mi$ haplotypes (at rate $\chi_{mi}$) but ignoring the fact that recombination also creates mutant haplotypes, is positive.
-We are also guaranteed to have at least one $\lambda$ greater than one when 1 + b + c < 0.
-This is never true if neither haplotype can spread ($\lambda_{mA}, \lambda_{ma} < 1$). 
+Given the characteristic polynomial and the Perron-Forbenius theorem (see supplementary material for details), at least one $\lambda$ is greater than one when $2 + b < 0$ or $1 + b + c < 0$.
+% $(\lambda_{mA} - \chi_{mA}) + (\lambda_{ma} -  \chi_{ma}) > 2$.
+%In words, the neo-sex-determining allele will certainly spread when the average change in its frequency, taking into account that recombination breaks up mutant $mi$ haplotypes (at rate $\chi_{mi}$) but ignoring the fact that recombination also creates mutant haplotypes, is positive.
+%When this does not hold ($2+b>0$), we can still have one $\lambda$ greater than one when 1 + b + c < 0.
+At least one of these conditions is true if both haplotypes can spread ($\lambda_{mA}, \lambda_{ma} > 1$) and neither can be true if neither haplotype can spread ($\lambda_{mA}, \lambda_{ma} < 1$). 
 %If both haplotypes can spread ($\lambda_{mA}, \lambda_{ma} > 1$), this condition becomes $\chi_{mA}/(\lambda_{mA} - 1) + \chi_{ma}/(\lambda_{ma} -  1) > 1$.
@@
 %\frac{\chi_{mA}}{\lambda_{mA}-1}+\frac{\chi_{ma}}{\lambda_{ma}-1}>0.
-\chi_{ma}/\left(\lambda_{ma}-1\right)+\chi_{mA}/\left(\lambda_{mA}-1\right)<1.
+\chi_{ma}/\left(\lambda_{ma}-1\right) + \chi_{mA}/\left(\lambda_{mA}-1\right) < 1.
 \end{equation}
 \noindent For example, if we assume that only the $mA$ haplotype has a positive growth rate ($\lambda_{ma}<1<\lambda_{mA}$), the first term on the left-hand side of \eqref{eq:lambdasGen} is negative and invasion requires that the growth rate of $mA$ haplotypes ($\lambda_{mA}-1$) and the rate at which they are produced by recombination in $ma$ haplotypes ($\chi_{ma}$) are sufficiently large relative to the growth rate and recombination gain of $ma$ haplotypes.
-\textcolor{blue}{i've updated this section with the correct $\lambda$ and $\chi$ terms.
+%\textcolor{blue}{i've updated this section with the correct $\lambda$ and $\chi$ terms.
 still a bit funny that not guaranteed invasion when both lambdas greater than one, and when both are greater than one then the condition above, (1), has the inequality flipped, which makes no sense (no invasion if no recombination despite both haplotypes growing).

### 2017-10-02 LaTeX/Turnover.tex
clarified general invasion conditions based on sallys email

@@
 %When this does not hold ($2+b>0$), we can still have one $\lambda$ greater than one when 1 + b + c < 0.
-At least one of these conditions is true if both haplotypes can spread ($\lambda_{mA}, \lambda_{ma} > 1$) and neither can be true if neither haplotype can spread ($\lambda_{mA}, \lambda_{ma} < 1$). 
+Regardless the rate of recombination, at least one of these conditions is true if both haplotypes can spread ($\lambda_{mA}, \lambda_{ma} > 1$) and neither can be true if neither haplotype can spread ($\lambda_{mA}, \lambda_{ma} < 1$).
 %If both haplotypes can spread ($\lambda_{mA}, \lambda_{ma} > 1$), this condition becomes $\chi_{mA}/(\lambda_{mA} - 1) + \chi_{ma}/(\lambda_{ma} -  1) > 1$.
-If only one haplotype can spread then the new sex-determining allele increases in frequency on one \textbf{A} background and declines on the other, and invasion requires 
+If only one haplotype can spread then the new sex-determining allele increases in frequency on one \textbf{A} background and declines on the other.
+Invasion then requires that the average growth rate of the haplotypes is positive when considering loss of haplotypes due to recombination, $(\lambda_{mA}-\chi_{mA}) + (\lambda_{ma}+\chi_{ma}) > 2$, or, if this condition is not held, that
 \begin{equation}\label{eq:lambdasGen}

### 2017-10-02 LaTeX/Turnover.tex
fixed clarification due to slack convo with mike
added sallys alternative polynomial to text to give intuitive argument for general invasion conditoin

@@
 %If the average change in frequency of the two haplotypes that carry the $m$ allele ($Am$ and $am$) is positive, invasion will always occur, i.e., if $(\lambda_{mA} + \lambda_{ma})/2 > 1$ then $\lambda > 1$.
-Given the characteristic polynomial and the Perron-Forbenius theorem (see supplementary material for details), at least one $\lambda$ is greater than one when $2 + b < 0$ or $1 + b + c < 0$.
+Given the characteristic polynomial $f(\lambda)=\lambda^2+b\lambda+c$ and the Perron-Forbenius theorem (guaranteeing that the leading eigenvalue is positive, unique, and real), at least one solution to $f(\lambda)=0$ is greater than one when the polynomial has a negative slope or negative value at $\lambda=1$ ($f'(1) = 2 + b < 0$ or $f(1) = 1 + b + c < 0$).
 % $(\lambda_{mA} - \chi_{mA}) + (\lambda_{ma} -  \chi_{ma}) > 2$.
@@
 If only one haplotype can spread then the new sex-determining allele increases in frequency on one \textbf{A} background and declines on the other.
-Invasion then requires that the average growth rate of the haplotypes is positive when considering loss of haplotypes due to recombination, $(\lambda_{mA}-\chi_{mA}) + (\lambda_{ma}+\chi_{ma}) > 2$, or, if this condition is not held, that
+Considering an alternative polynomial $g(\lambda)=\lambda^2+b\lambda+C$, with $C=(\lambda_{mA}-\chi_{mA})(\lambda_{ma}-\chi_{ma})$, we have $g(\lambda)=(\lambda_{mA} - \chi_{mA} - \lambda)(\lambda_{ma} - \chi_{ma} - \lambda)$ and, since $\chi_{mi}\leq0$, we also have $f(\lambda)<g(\lambda)$.
+Thus if $f'(1)=2+b<0$ and only one $\lambda_{mi}$ is greater than one we are guaranteed that $f(1)<g(1)<0$.
+Therefore, if only one haplotype can spread, invasion is completely determined by $f(1)<0$, which in this case can be rewritten
 \begin{equation}\label{eq:lambdasGen}
@@
 \end{equation}
-\noindent For example, if we assume that only the $mA$ haplotype has a positive growth rate ($\lambda_{ma}<1<\lambda_{mA}$), the first term on the left-hand side of \eqref{eq:lambdasGen} is negative and invasion requires that the growth rate of $mA$ haplotypes ($\lambda_{mA}-1$) and the rate at which they are produced by recombination in $ma$ haplotypes ($\chi_{ma}$) are sufficiently large relative to the growth rate and recombination gain of $ma$ haplotypes.
+\noindent For example, if we assume that only the $mA$ haplotype has a positive growth rate ($\lambda_{ma}<1<\lambda_{mA}$), the first term on the left-hand side of \eqref{eq:lambdasGen} is negative and invasion requires that the growth rate of $mA$ haplotypes ($\lambda_{mA}-1$) and the rate at which they are produced by recombination in $ma$ haplotypes ($\chi_{ma}$) are sufficiently large relative to the rate of decline of $ma$ haplotypes ($1-\lambda_{ma}$) and the rate of loss of $mA$ haplotypes due to recombination ($\chi_{mA}$).
 %\textcolor{blue}{i've updated this section with the correct $\lambda$ and $\chi$ terms.

### 2017-10-05 LaTeX/Turnover.tex
discussing effect of haploid selection on tight linkage results, and some minor figure adjustments

@@
 (b/c the $m$ alleles can arise in either sex?)}
-$\lambda^2+ b \lambda + c =0$ (see Appendix for a discussion of other roots).
+$\lambda^2+ b \lambda + c =0$ \textcolor{blue}{(see Appendix for a discussion of other roots)}.
 %\begin{equation}
@@
 Neo-W alleles, on the other hand, can invade an ancestral XY system under some conditions (the full invasion conditions are given in the appendix; equations \ref{Binvasion} and \ref{Ainvasion}). 
-That is, selection on loci within the non-recombining region of the SDR can favour the invasion of a less closely linked neo-W, see Figure \ref{fig:SexAntagTighter}. 
+That is, selection on loci within the non-recombining region of the SDR can favour the invasion of a less closely linked neo-W, even in the absence of haploid selection (Figure \ref{fig:SexAntagTighter}).
 %Although haploid selection can favour neo-W alleles because the ancestral sex ratio becomes male biased, this is not the only circumstance in which less tightly linked neo-W alleles invade. 
@@
 %For example, unlinked neo-W alleles can invade in the absence of any haploid selection. 
-This result is unexpected given the results of \cite{vanDoorn:2010hu}, who did not explicitly calculate equilibrium allele frequencies under tight linkage and generally concluded that heterogametic transitions occur when neo-sex-determining alleles are in tighter linkage with loci under sex-specific diploid selection.
-To develop an understanding (intuition) for how this happens, we focus on cases where there is no haploid selection and discuss the effects of haploid selection in the appendix. 
+%This result is unexpected given the results of \cite{vanDoorn:2010hu}, who did not explicitly calculate equilibrium allele frequencies under tight linkage and generally concluded that heterogametic transitions can only occur when neo-sex-determining alleles are in tighter linkage with loci under sex-specific diploid selection.
+This is not possible with purely sexually-antagonistic selection \citep[][and supplementary material]{vanDoorn:2010hu}, but is possible with overdominance in at least one sex \textcolor{blue}{(check)}.
+In fact, with tight linkage between the ancestral SDR and the selected locus, haploid selection and/or overdominance can favour completely unlinked neo-W alleles ($R=1/2$), allowing autosomes to become new sex chromosomes.
+To develop an intuition for how less closely linked neo-W alleles invade, we first focus on cases where there is no haploid selection and then discuss the additional effect of haploid selection (more details in the appendix).
 %}
@@
 \caption{
-Transitions between XY and ZW systems can occur even when the neo-SDR is more loosely linked to a locus under sexually-antagonistic selection (here, without haploid selection $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$).
-In panel A, linkage is loose enough relative to selection that the weak selection analytical results hold, and a neo-W can only invade when it is more tightly linked with the selected locus ($R<r$; shaded region).
-In panel B, linkage is tight enough relative to selection that the weak selection analytical results do not hold, and a neo-W can only invade even when it is less tightly linked with the selected locus ($r<R$; unshaded region).
+Transitions between XY and ZW systems can occur even when the neo-SDR is less tightly linked to a locus under sexually-antagonistic selection (here, without haploid selection).
+In panel A, linkage is loose enough relative to selection that the analytical results assuming weak selection hold, and a neo-W can only invade when it is more tightly linked with the selected locus ($R<r$; shaded region).
+In panel B, linkage is tight enough relative to selection that the analytical results assuming weak selection do not hold, and a neo-W can invade even when it is less tightly linked with the selected locus ($r<R$; unshaded region).
 In panel C we vary the recombination rate between the neo-W and the selected locus ($R$) for a fixed recombination rate between the ancestral-SDR and the selected locus ($r=0.005$). 
@@
 A very loosely linked neo-W does not spread in this case (blue and green lines overlap and go to 0). 
-Indeed, we show that neo-W invasion fitness is negative when $R=1/2$ and $s^\female s^\male<0$, $0<h^\Hermaphrodite<1$) in the supplementary \textit{Mathematica} file.
-Fitness parameters are shown by an asterisk in Figure \ref{fig:regionplots}: $w_{AA}^\female = 1.05$, $w_{aa}^\male = 1.2$, $w_{aa}^\female = w_{AA}^\male = 0.85$, $w_{Aa}^\Hermaphrodite = 1$.
-\textcolor{red}{consider removing panel A, which is repeated in Figure 3.}
+Indeed, we can show that neo-W invasion fitness is always negative when $R=1/2$ and there is sex-antagonism but no haploid selection (see supplementary \textit{Mathematica} file). 
+Fitness parameters are shown by an asterisk in Figure \ref{fig:regionplots}A: $w_{AA}^\female = 1.05$, $w_{aa}^\male = 1.2$, $w_{aa}^\female = w_{AA}^\male = 0.85$, $w_{Aa}^\Hermaphrodite = 1$,  $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
+%\textcolor{red}{consider removing panel A, which is repeated in Figure 3.}
+%\textcolor{blue}{probably better to remove from panel 3, eh?}
 }
@@
 When only one neo-W haplotype can has a positive growth rate (see Figure \ref{fig:regionplots}), a neo-W can invade as long as equation \eqref{eq:lambdasGen} is satisfied, which may require that the recombination rate, $R$, is small enough.
-Nevertheless, because we assume here that $r$ is small, these results indicate that a more loosely linked sex-determining region can spread.
+Nevertheless, because we assume here that $r$ is small, these results indicate that a more loosely linked sex-determining region ($r<R$) can spread.
 Therefore, tightly sex-linked loci that experience sexually-antagonistic selection can drive heterogametic transitions in which the neo-SDR is less closely linked to the locus under selection (Figure \ref{fig:SexAntagTighter}).
@@
 In such cases, neo-W-$a$ haplotypes can spread because they create more $Aa$ and $aa$ females when pairing with an X from males and because they bring Y-$a$ haplotypes into females, in which case females are always $aa$.
-As discussed in the appendix, this scenario where neo-W's associated with $a$ are favoured can also occur with haploid selection, even without overdominance (e.g., when $a$ is female-beneficial and favoured by haploid selection in male gametes).
 
@@
 
-\textcolor{red}{
-What can we discuss about haploid selection here. Perhaps the fact that overdominance is not required for $\lambda_{Ma}>1$ when there is haploid selection?
-We also don't yet discuss the fact that polymorphic equilibria (mixed systems) can be stable. 
-}
+%\textcolor{red}{
+%What can we discuss about haploid selection here. Perhaps the fact that overdominance is not required for $\lambda_{Ma}>1$ when there is haploid selection?
+%We also don't yet discuss the fact that polymorphic equilibria (mixed systems) can be stable. 
+%}
+
+Haploid selection impacts the spread of neo-W haplotypes through its direct selective effect on females and their gametes, its indirect effect on the marginal fitness of alleles in females resulting from haploid selection in male gametes, and its effect on the sex ratio.
+These impacts expand the scenarios under which neo-W haplotypes can spread.
+For instance, overdominance is no longer required for neo-W-$a$ haplotypes to spread when there is haploid selection (e.g., when $a$ is female-beneficial, $A$ is male-beneficial, and meiotic drive in males favours $a$, Figure \ref{fig:regionMaleDrive}B).
+
+Haploid selection also makes polymorphic sex-determining systems more likely.
+In fact, our explicit calculation of the invasion criteria for a neo-W entering a system with tight linkage between the ancestral SDR and the selected locus shows that protected polymorphisms, where the neo-W invades but has a frequency of less than 1/2 in females and the ancestral X and Y both segregate, are possible even in the absence of haploid selection (e.g., overdominance in males, Figure \ref{fig:temporalOverdominance}).
+Protected polymorphisms are not possible with sexually-antagonistic selection alone \citep{vanDoorn:2010hu}.
+Adding haploid selection to sexually-antagonistic selection changes this conclusion (Figure \ref{fig:SexAntagTighterMaleDrive}), as does ploidally-antagonistic selection (Figure \ref{fig:regionPloidAntag}).
 
@@
 \centering
-\includegraphics[width=0.5\linewidth]{PositionPlot_4}
+\includegraphics[width=\linewidth]{PositionPlot_8}
 \caption{
- A neo-W can invade an XY system under a large number of selective regimes.
-In panel A, there is no haploid selection ($t^\Hermaphrodite = \alpha^\Hermaphrodite_{\Delta} = 0$) and selection in diploids is sexually antagonistic ($s^\male = -s^\female = 1/10$, $h^\male = 1-h^\female = 3/10$), in which case the neo-sex-determining allele can only invade if it is more closely linked to the selected locus ($R<r$, gray region; but see Figure \ref{fig:SexAntagTighter}B for the case of very tight linkage).
-In panel B, male drive ($\alpha^\male_{\Delta} = -1/20$, $t^\Hermaphrodite = \alpha^\female_{\Delta} = 0$) opposes selection in diploids (no sex-differences: $s^\Hermaphrodite = 1/10$, $h^\Hermaphrodite = 7/10$), in which case the neo-sex-determining allele can invade regardless of linkage.
-In panel C, gametic competition in males ($t^\male = -1/10$, $t^\female = \alpha^\Hermaphrodite_{\Delta} = 0$) opposes selection in diploids (sex-differences: $s^\male = 1/20$, $s^\female = 3/20$, $h^\Hermaphrodite = 7/10$), in which case the neo-sex-determining allele can once again invade regardless of linkage.
+% A neo-W can invade an XY system under a large number of selective regimes.
+%In panel A, there is no haploid selection ($t^\Hermaphrodite = \alpha^\Hermaphrodite_{\Delta} = 0$) and selection in diploids is sexually antagonistic ($s^\male = -s^\female = 1/10$, $h^\male = 1-h^\female = 3/10$), in which case the neo-sex-determining allele can only invade if it is more closely linked to the selected locus ($R<r$, gray region; but see Figure \ref{fig:SexAntagTighter}B for the case of very tight linkage).
+Ploidally-antagonistic selection allows a less tightly linked neo-W to invade.
+In panel A, male drive ($\alpha^\male_{\Delta} = -1/20$, $t^\Hermaphrodite = \alpha^\female_{\Delta} = 0$) opposes selection in diploids (no sex-differences: $s^\Hermaphrodite = 1/10$, $h^\Hermaphrodite = 7/10$), in which case the neo-sex-determining allele can invade regardless of linkage.
+In panel B, gametic competition in males ($t^\male = -1/10$, $t^\female = \alpha^\Hermaphrodite_{\Delta} = 0$) opposes selection in diploids (sex-differences: $s^\male = 1/20$, $s^\female = 3/20$, $h^\Hermaphrodite = 7/10$), in which case the neo-sex-determining allele can once again invade regardless of linkage.
 We use Haldane's map function \citep[Equation 3 in ][]{Haldane1919} to convert from map distance (centiMorgans, cM) to the probability of recombination (an odd number of cross-over events).   
-\textcolor{red}{Check the mismatch between red and black lines here: probably because of adding or subtracting from 1. }
-\textcolor{blue}{Can remove the mismatch by flipping the fitnesses between males and females (again).
+%\textcolor{red}{Check the mismatch between red and black lines here: probably because of adding or subtracting from 1. }
+%\textcolor{blue}{Can remove the mismatch by flipping the fitnesses between males and females (again).
 That is, if $M_{AA}$ is the fitness of $AA$ male diploids in an ancestral XY system, then $M_{AA}$ is the fitness of $AA$ female diploids in an ancestral ZW system.
@@
 2007 and vD\&K, 2010, might be added to this section.}
+\textcolor{blue}{I've added a bit to the end of the tight linkage section in the main text.}
 
@@
 \smallskip
-\caption{Values of $\rho$ for different loci orders assuming no interference and $r,R\in(0,1/2)$.\textcolor{blue}{write all in form of first line?
-so that 1/2 cases are okay (can't determine chi if R is 1/2 in second line, or if r is 1/2 in third line}}
+\caption{
+Substitutions for different loci orders assuming no interference.
+%and $r,R\in(0,1/2)$.\textcolor{blue}{write all in form of first line?
+so that 1/2 cases are okay (can't determine chi if R is 1/2 in second line, or if r is 1/2 in third line}
+}
 \begin{tabular}{l l}
@@
   Order of loci &   \\ [0.5ex] \hline
-  SDR-A-M & $\rho=R(1-r)+r(1-R)$  \\
-  SDR-M-A & $\rho=(r-R)/(1-2R)$ \\
-  A-SDR-M & $\rho=(R-r)/(1-2r)$ \\
+  SDR-A-M & $\rho=r(1-R)+R(1-r)$  \\
+  SDR-M-A & $r=\rho(1-R)+R(1-\rho)$ \\ %$\rho=(r-R)/(1-2R)$ \\
+  A-SDR-M & $R=r(1-\rho)+\rho(1-r)$ \\ %$\rho=(R-r)/(1-2r)$ \\
   \hline \hline
@@
 Stability of a polymorphism on the X chromosome (equilibrium $A$) further requires that $\phi >0$ and $\psi >0$. 
-Fixation of the $a$ allele on the X (equilibrium $B$) can be stable only if equilibrium $(A)$ is not, as it requires $\psi<0$ and $2w_{A}^{\female}w_{AA}^{\female}>(1-\alpha_\Delta^{\female})w_{a}^{\female}w_{Aa}^{\female}$ or just $4w_{A}^{\female}w_{AA}^{\female}<(1-\alpha_\Delta^{\female})w_{a}^{\female}w_{Aa}^{\female}$ (which prevents $\psi>0$).
+Fixation of the $a$ allele on the X (equilibrium $B$) can be stable only if equilibrium $(A)$ is not, as it requires $\psi<0$ and $2w_{A}^{\female}w_{AA}^{\female}>(1-\alpha_\Delta^{\female})w_{a}^{\female}w_{Aa}^{\female}$ or just $4w_{A}^{\female}w_{AA}^{\female}<(1-\alpha_\Delta^{\female})w_{a}^{\female}w_{Aa}^{\female}$ (which also prevents $\psi>0$).
 
@@
 \textcolor{red}{Cover the other parts of the characteristic polynomial here.}
+\textcolor{blue}{Waiting for Sally's proof!}
 
@@
 This can occur with overdominance or directional selection for $a$ in females (Figure \ref{fig:regionplots}B,C).
-\textcolor{blue}{mike, you might want to check these last two statements i've edited, and the following.}
 In this case, $a$ is not favoured enough in females near the equilibrium (comparing $Aa$ to $AA$ genotypes) to prevent $A$ from stably fixing on the X, and yet the neo-W can spread with $a$ because it produces female $aa$ individuals by capturing Y-$a$ haplotypes.
+\textcolor{blue}{mike, could you check this paragraph? i fixed an old problem, and want to make sure i haven't introduced any new errors}
 
@@
 \caption{
-When there is haploid selection and sexually-antagonistic selection, a neo-W may invade for any $R$.
+When there is sexually-antagonistic selection and haploid selection, a neo-W may invade for any $R$.
 \textcolor{red}{
-Check that we mention Sally's result that invasion cannot occur with sexually-antagonistic selection and $R=1/2$ (currently only in legend for figure \ref{fig:SexAntagTighter}) 
-Add asterisk to Figure \ref{fig:regionMaleDrive}A to show parameters used in this plot. 
-}
-$w_{AA}^\female=1.05$, $w_{Aa}^\Hermaphrodite=1$, $w_{aa}^\female=0.85$, $w_{AA}^\male=0.85$, $w_{aa}^\male=1.05$, $\alpha_{\Delta}^\male=-0.08$.
+Check that we mention Sally's result that invasion cannot occur with sexually-antagonistic selection and $R=1/2$ (currently only in legend for figure \ref{fig:SexAntagTighter}). 
+%Add asterisk to Figure \ref{fig:regionMaleDrive}A to show parameters used in this plot. 
+}
+\textcolor{blue}{This is now discussed in a round-about way at the beginning of the tight linkage invasion section in the main text. }
+Parameters given by asterisk in Figure \ref{fig:regionMaleDrive}: $w_{AA}^\female=1.05$, $w_{Aa}^\Hermaphrodite=1$, $w_{aa}^\female=0.85$, $w_{AA}^\male=0.85$, $w_{aa}^\male=1.05$, $\alpha_{\Delta}^\male=-0.08$.
 }
@@
 The y-axis shows directional selection in diploids of both sexes, $s^\female=s^\male$, and the x-axes show sex-specific drive, $\alpha_\Delta^\Hermaphrodite$, or haploid competition, $t^\Hermaphrodite$.
-The top left and bottom right quadrants therefore imply ploidally-antagonistic selection (and these are the only places where.
+The top left and bottom right quadrants therefore imply ploidally-antagonistic selection (and these are the only places where neo-W haplotypes can invade).
 Dominance is equal in both sexes, $h^\female=h^\male=3/4$. 
@@
 Panel C has the same parameters as the green curve in Figure \ref{fig:regionMaleDrive}C (sexual-antagonism with male drive).
-Panel D has the same parameters as the red curve in Figure \ref{fig:regionPloidAntag}F, except $r=0$ (ploidy-antagonism with pollen competition)
+Panel D has the same parameters as the red curve in Figure \ref{fig:regionPloidAntag}F, except $r=0$ (ploidy-antagonism with pollen competition).
 Panel A shows complete sex-determination turnover (XY $\rightarrow$ ZW) whereas panels B-D show the evolution of polymorphic sex-determining systems (X and Y still segregating and the neo-W has a frequency in females that is less than 1/2).

### 2017-10-23 LaTeX/Turnover.tex
polygenic added and references

@@
 I wonder if this is actually a fusion event though?
-In addition, many gonochoric clades with genetic sex determination exhibit transitions between male (XY) and female (ZW) heterogamety, including snakes \textcolor{red}{(Gamble et al.
-2017, Current Biology)}, lizards \citep{Ezaz:2009tk}, eight of 26 teleost fish families \citep{Mank:2006bt}, true fruit flies \citep[Tephritids,][]{Vicoso:2015hf}, amphibians \citep{Hillis:1990gu}, the angiosperm genus \textit{Silene} \citep{Slancarova:2013dq}, \textcolor{red}{the angiosperm family \textit{Salicaceae} (Pucholt et al.
-2015, 2017),} and Coleoptera and Hemiptera \citep[][plate 2]{Beukeboom:2014vb}.
-Indeed, in some cases, both male and female heterogametic sex-determination systems can be found in the same species, as exhibited by some cichlid species \citep{Ser:2010iq} and \textit{Rana rugosa} \citep{Ogata:2007jm} \textcolor{red}{(Miura 2007)}.
+In addition, many gonochoric clades with genetic sex determination exhibit transitions between male (XY) and female (ZW) heterogamety, including snakes \citep{Gamble2017}, lizards \citep{Ezaz:2009tk}, eight of 26 teleost fish families \citep{Mank:2006bt}, true fruit flies \citep[Tephritids,][]{Vicoso:2015hf}, amphibians \citep{Hillis:1990gu}, the angiosperm genus \textit{Silene} \citep{Slancarova:2013dq}, the angiosperm family \textit{Salicaceae} \citep{Pucholt2015,Pucholt2017} and Coleoptera and Hemiptera \citep[][plate 2]{Beukeboom:2014vb}.
+Indeed, in some cases, both male and female heterogametic sex-determination systems can be found in the same species, as exhibited by some cichlid species \citep{Ser:2010iq} and \textit{Rana rugosa} \citep{Ogata:2007jm, Miura2007}.
 In addition, multiple transitions have occurred between genetic and environmental sex-determination systems, e.g., in reptiles and fishes \citep{Conover:1987in,Mank:2006bt,Pokorna:2009ui,Ezaz:2009tk,Pen:2010kk,Holleley:2015hc}.
@@
 
-The sex ratio is directly affected by the sex-determination system, and it has therefore been suggested that sex-ratio selection is a dominant force in the evolution of sex determination (e.g., \citealt{Bull:1983vi}, p 66-67; \citealt{Beukeboom:2014vb}, Chapter 7).
+The sex ratio is directly determined by the sex-determination system, and it has therefore been suggested that sex-ratio selection is a dominant force in the evolution of sex determination (e.g., \citealt{Bull:1983vi}, p 66-67; \citealt{Beukeboom:2014vb}, Chapter 7).
 `Fisherian' sex-ratio selection favours a 1:1 zygotic sex ratio when assuming that males and females are equally costly to produce \citep{Fisher:1930wy,Charnov:1982wg}.
@@
 We use the term `meiotic drive' to refer to the biased (non-Mendelian) segregation of genotypes during gamete production (from one parent) and the term `gametic competition' to refer to selection upon haploid genotypes within a gamete/gametophyte pool (potentially from multiple parents); the term `haploid selection' encompasses both processes.
-\textcolor{red}{
-Genetic mapping experiments, which are typically designed to minimize selection in diploids, have revealed segregation distortion in various species, including mice, Drosophila, Rice, Maize, Wheat, Barley, Cotton...
+
+% from Bai et al.
+(2016) ``[Segregation distortion] phenomenon is commonly detected via genetic mapping and has been documented in various species, including mouse (Eversley et al., 2010; Casellas et al., 2012), Drosophila (Phadnis and Orr, 2009; Larracuente and Presgraves, 2012; McDermott and Noor, 2012), Tigriopus (Pritchard et al., 2011), rice (Koide et al., 2012; Reflinur et al., 2014; Xu et al., 2014), maize (Tang et al., 2013), and cotton (Yu et al., 2011; Hulse-Kemp et al., 2015).'' Also more in that paper that might be useful.
+%Drosophila http://www.biorxiv.org/content/early/2017/02/06/106336
+\textcolor{red}{Genetic mapping experiments, which are typically designed to minimize selection in diploids, have revealed segregation distortion in various species, including mice, Drosophila, Rice, Maize, Wheat, Barley, Cotton...
 In some of these cases, biased segregation has been attributed to meiotic drive and/or gametic selection \textcolor{red}{(Leppala et al.
@@
 }
-% from Bai et al.
-(2016) ``[Segregation distortion] phenomenon is commonly detected via genetic mapping and has been documented in various species, including mouse (Eversley et al., 2010; Casellas et al., 2012), Drosophila (Phadnis and Orr, 2009; Larracuente and Presgraves, 2012; McDermott and Noor, 2012), Tigriopus (Pritchard et al., 2011), rice (Koide et al., 2012; Reflinur et al., 2014; Xu et al., 2014), maize (Tang et al., 2013), and cotton (Yu et al., 2011; Hulse-Kemp et al., 2015).'' Also more in that paper that might be useful.
-%Drosophila http://www.biorxiv.org/content/early/2017/02/06/106336
 Meiotic drive generally occurs either during the production of male or female gametes only \citep{Ubeda:2005gw,Lindholm:2016cw}.
-Because there are typically many more pollen/sperm than required for fertilization, gametic competition is also typically sex specific, occurring primarily among male gametes.
+Gametic competition is also typically sex specific, occurring primarily among male gametes, because there are typically many more pollen/sperm than required for fertilization.
 Gametic competition may be particularly common in plants, in which 60-70\% of all genes are expressed in the male gametophyte and these genes exhibit stronger signatures of selection than random genes \citep{Borg:2009jpa,Arunkumar:2013iq,Gossmann:2014dua}.
@@
 A smaller proportion of genes are thought to be expressed and selected during competition in animal sperm, although precise estimates are uncertain \citep{Zheng:2001fi,JOSEPH:2004haa,Vibranovski:2010et}.
-Recent studies have demonstrated that sperm competition can alter haploid allele frequencies and increase offspring fitness \citep{Immler:2014im} \textcolor{red}{(Alavioon et al. 2017)}.
+Recent studies have demonstrated that sperm competition in animals can alter haploid allele frequencies and increase offspring fitness \citep{Immler:2014im,Alavioon2017}.
 
@@
 %Indeed, it is only when haploid-selected loci are tightly linked to the ancestral sex-determining region (and so sex-ratio biases are initially large) that we see an asymmetry between selection for XY to ZW transitions and ZW to XY transitions (e.g., because haploid selection in males only causes biased zygotic sex ratios in an ancestrally XY system).
-Consequently, it is possible for selection on linked alleles to drive turnover between sex-determining systems despite causing transitory or even permanent increases in sex-ratio bias. 
-In addition to considering haploid selection, another novel development in our model is that we consider loci that are under diploid and/or haploid selection and also in very tight linkage with the ancestral sex-determining region.
-Even in the absence of haploid selection, we show that transitions between male and female heterogamety can then evolve despite the fact that the neo-sex-determining locus is less closely linked to a locus under selection and therefore disrupts favourable ancestral associations between sex and the alleles selected in that sex.
+Consequently, Fisherian sex ratio selection does not dominate and it is possible for selection on linked alleles to drive turnover between sex-determining systems despite causing increases in sex-ratio bias.
+In addition to considering haploid selection, another novel development in our model is that we consider loci that are in very tight linkage with the ancestral sex-determining region.
+We show that transitions between male and female heterogamety can then evolve despite the fact that the neo-sex-determining locus is less closely linked to a locus under selection and therefore disrupts favourable ancestral associations between sex and the alleles selected in that sex.
 %Such transitions are not favoured in models lacking tight linkage and/or haploid selection. 
@@
       \scriptsize
-      \item $\bar{p}^{\male}=(1-\hat{q})\hat{p}_X^\male + q\hat{p}_Y^\male$ is the average frequency of the $A$ allele among X- and Y-bearing male gametes.
+      \item $\bar{p}^{\male}=(1-\hat{q})\hat{p}_X^\male + \hat{q}\hat{p}_Y^\male$ is the average frequency of the $A$ allele among X- and Y-bearing male gametes.
 %      \item $R$ is the probability of recombination between loci \textbf{A} and \textbf{M}.
@@
 If only one haplotype can spread then the new sex-determining allele increases in frequency on one \textbf{A} background and declines on the other.
-Considering an alternative polynomial $g(\lambda)=\lambda^2+b\lambda+C$, with $C=(\lambda_{mA}-\chi_{mA})(\lambda_{ma}-\chi_{ma})$, we have $g(\lambda)=(\lambda_{mA} - \chi_{mA} - \lambda)(\lambda_{ma} - \chi_{ma} - \lambda)$ and, since $\chi_{mi}\leq0$, we also have $f(\lambda)<g(\lambda)$.
-Thus if $f'(1)=2+b<0$ and only one $\lambda_{mi}$ is greater than one we are guaranteed that $f(1)<g(1)<0$.
-Therefore, if only one haplotype can spread, invasion is completely determined by $f(1)<0$, which in this case can be rewritten
+%Considering an alternative polynomial $g(\lambda)=\lambda^2+b\lambda+C$, with $C=(\lambda_{mA}-\chi_{mA})(\lambda_{ma}-\chi_{ma})$, we have $g(\lambda)=(\lambda_{mA} - \chi_{mA} - \lambda)(\lambda_{ma} - \chi_{ma} - \lambda)$ and, since $\chi_{mi}\leq0$, we also have $f(\lambda)<g(\lambda)$.
+%Thus if $f'(1)=2+b<0$ and only one $\lambda_{mi}$ is greater than one we are guaranteed that $f(1)<g(1)<0$.
+%Therefore, if only one haplotype can spread, invasion is completely determined by $f(1)<0$, which in this case can be rewritten
+Invasion then occurs if
 \begin{equation}\label{eq:lambdasGen}
@@
 First, Fisherian sex-ratio selection will favour the spread of a neo-Y if the ancestral zygotic sex ratio is biased towards females, $\zeta<1/2$ (i.e., the first factor of the $\lambda_{mi}$ is greater than one for a neo-Y and less than one for a neo-W).
-However, the spread of a neo-Y (neo-W) also depends on the male (female) fitness of associated alleles (terms involving equilibrium allele frequencies, $p$'s). %, see terms in curly brackets. 
+However, the spread of a neo-Y (neo-W) also depends on the male (female) fitness of associated alleles (terms involving equilibrium allele frequencies, $\hat{p}$'s). %, see terms in curly brackets. 
 Second, invasion by a neo-Y (neo-W) allele does not directly depend on the fitness of female (male) diploids (for a given set of equilibrium allele frequencies).
@@
 
-In order to explicitly determine the conditions under which a rare neo-sex-determining allele spreads, we must calculate the equilibrium frequency of the $A$ allele (i.e., $\hat{p}^\female_X$, $\hat{p}^\male_X$, and $\hat{p}^\male_Y$) and Y-bearing male gametes ($\hat{q}$) in the ancestral population .
+In order to explicitly determine the conditions under which a rare neo-sex-determining allele spreads, we must calculate the equilibrium frequency of the $A$ allele (i.e., $\hat{p}^\female_X$, $\hat{p}^\male_X$, and $\hat{p}^\male_Y$) and Y-bearing male gametes ($\hat{q}$) in the ancestral population.
 Since only the \textbf{A} locus experiences selection directly, any deterministic evolution requires that there is a polymorphism at the \textbf{A} locus. 
@@
 Neo-W alleles, on the other hand, can invade an ancestral XY system under some conditions (the full invasion conditions are given in the appendix; equations \ref{Binvasion} and \ref{Ainvasion}). 
-That is, selection on loci within the non-recombining region of the SDR can favour the invasion of a less closely linked neo-W, even in the absence of haploid selection (Figure \ref{fig:SexAntagTighter}).
+That is, selection on loci within the non-recombining region of the SDR can favour the invasion of a less closely linked neo-W (Figure \ref{fig:SexAntagTighter}). 
 %Although haploid selection can favour neo-W alleles because the ancestral sex ratio becomes male biased, this is not the only circumstance in which less tightly linked neo-W alleles invade. 
@@
 %This result is unexpected given the results of \cite{vanDoorn:2010hu}, who did not explicitly calculate equilibrium allele frequencies under tight linkage and generally concluded that heterogametic transitions can only occur when neo-sex-determining alleles are in tighter linkage with loci under sex-specific diploid selection.
-This is not possible with purely sexually-antagonistic selection \citep[][and supplementary material]{vanDoorn:2010hu}, but is possible with overdominance in at least one sex \textcolor{blue}{(check)}.
 In fact, with tight linkage between the ancestral SDR and the selected locus, haploid selection and/or overdominance can favour completely unlinked neo-W alleles ($R=1/2$), allowing autosomes to become new sex chromosomes.
@@
 If we categorise the $a$ allele as being ancestrally `male-beneficial' via the fact that it is fixed on the Y, then $\lambda_{mA}>1$ indicates that the neo-W spreads when found with the ancestrally `female-beneficial' allele.
-Broadly, this is possible because the ancestral X chromosome is not able to perfectly specialise on the `female-beneficial' allele due to the fact that X's are sometimes found in males. 
+Broadly, this is possible because the ancestral X chromosome is sometimes found in males and is therefore unable to perfectly specialise on the `female-beneficial' allele. 
 For example, when the $a$ allele is favoured in males, a polymorphism of $A$ and $a$ alleles can be maintained on the X despite directional selection in favour of the $A$ allele in females ($s^\female>0$, $0<h^\female<1$).
-Figure \ref{fig:regionplots}A indicates that $\lambda_{mA}$ tends to be larger than one with sexually-antagonistic selection where the $a$ allele is strongly favoured in males ($w_{aa}$ much larger than $w_{Aa}$).
-In this case the $a$ allele is at high frequency among XX females is high due to selection upon the X in males. 
-By contrast, W-$A$ haplotypes will only create females with high fitness ($AA$ or $Aa$ genotypes) and can therefore have higher fitness than ancestral females. 
-When only one neo-W haplotype can has a positive growth rate (see Figure \ref{fig:regionplots}), a neo-W can invade as long as equation \eqref{eq:lambdasGen} is satisfied, which may require that the recombination rate, $R$, is small enough.
+When the $a$ allele is strongly favoured on X chromosomes in males ($w_{aa}$ sufficiently large relative to $w_{Aa}$), neo-W-$A$ haplotypes can spread ($\lambda_{mA}>1$), see Figure \ref{fig:regionplots}A.
+In this case the $a$ allele is at high frequency among ancestral XX females due to selection upon the X in males. 
+By contrast, W-$A$ haplotypes will only create females with high fitness ($AA$ or $Aa$ genotypes) and can therefore spread.
+
+When only one neo-W haplotype has a positive growth rate (see Figure \ref{fig:regionplots}), a neo-W can invade as long as equation \eqref{eq:lambdasGen} is satisfied, which may require that the recombination rate, $R$, is small enough.
 Nevertheless, because we assume here that $r$ is small, these results indicate that a more loosely linked sex-determining region ($r<R$) can spread.
@@
 Therefore, the X can be polymorphic or even fixed for the $A$ allele despite favouring the $a$ allele during selection in females \citep[e.g., see outlined region in Figure \ref{fig:regionplots}B and][]{Lloyd1977,Otto2014}.
-In such cases, neo-W-$a$ haplotypes can spread because they create more $Aa$ and $aa$ females when pairing with an X from males and because they bring Y-$a$ haplotypes into females, in which case females are always $aa$.
+In such cases, neo-W-$a$ haplotypes can spread because they create more $Aa$ and $aa$ females when pairing with an X from males and because they bring Y-$a$ haplotypes into females.
 
@@
 
-%\textcolor{red}{
-%What can we discuss about haploid selection here. Perhaps the fact that overdominance is not required for $\lambda_{Ma}>1$ when there is haploid selection?
-%We also don't yet discuss the fact that polymorphic equilibria (mixed systems) can be stable. 
-%}
-
-Haploid selection impacts the spread of neo-W haplotypes through its direct selective effect on females and their gametes, its indirect effect on the marginal fitness of alleles in females resulting from haploid selection in male gametes, and its effect on the sex ratio.
-These impacts expand the scenarios under which neo-W haplotypes can spread.
-For instance, overdominance is no longer required for neo-W-$a$ haplotypes to spread when there is haploid selection (e.g., when $a$ is female-beneficial, $A$ is male-beneficial, and meiotic drive in males favours $a$, Figure \ref{fig:regionMaleDrive}B).
-
-Haploid selection also makes polymorphic sex-determining systems more likely.
-In fact, our explicit calculation of the invasion criteria for a neo-W entering a system with tight linkage between the ancestral SDR and the selected locus shows that protected polymorphisms, where the neo-W invades but has a frequency of less than 1/2 in females and the ancestral X and Y both segregate, are possible even in the absence of haploid selection (e.g., overdominance in males, Figure \ref{fig:temporalOverdominance}).
-Protected polymorphisms are not possible with sexually-antagonistic selection alone \citep{vanDoorn:2010hu}.
-Adding haploid selection to sexually-antagonistic selection changes this conclusion (Figure \ref{fig:SexAntagTighterMaleDrive}), as does ploidally-antagonistic selection (Figure \ref{fig:regionPloidAntag}).
+Assuming that linkage is not tight, \citet{vanDoorn:2010hu} showed that invasion by a neo-W occurs under the same conditions as `fixation' (where fixation indicates that the neo-W reaches its maximum frequency among eggs, which is 1/2).
+An equivalent analysis is not possible where we assume that linkage is tight. 
+However, numerical simulations with tight linkage demonstrate that the neo-SDR does not necessarily fix, leading to the stable maintenance of a mixed sex-determining system, in which X,Y,Z, and W alleles all segregate, e.g., Figure \ref{fig:freqAll}B-D.
+Within a species, both feminizing and masculinizing alleles have been reported in houseflies \citep{Macdonald1978}, midges \citep{Thompson1971}, frogs \citep{Ogata:2007jm}, cichlid fish \citep{Ser:2010iq}, tilapia \citep{Lee2004}, sea bass \citep{Vandeputte2007}, and lab-strains of Zebrafish \citep{Liew2012,Wilson2014}.
+For example, in the platyfish (\textit{Xiphophorus maculatus}), X,Y, and W alleles segregate at one locus (or two closely-linked loci) near to potentially sexually-antagonistic genes for pigmentation and sexual maturity \citep{Kallman1965,Kallman1968, Volff2001, Schultheis2006}.
+Our results suggest that several forms of selection on nearby loci ($r$ and $R$ small) could maintain multiple sex determination alleles.
+
+%Haploid selection impacts the spread of neo-W haplotypes through its direct selective effect on females and their gametes, its indirect effect on the marginal fitness of alleles in females resulting from haploid selection in male gametes, and its effect on the sex ratio.
+%These impacts expand the scenarios under which neo-W haplotypes can spread.
+%For instance, overdominance is no longer required for neo-W-$a$ haplotypes to spread when there is haploid selection (e.g., when $a$ is female-beneficial, $A$ is male-beneficial, and meiotic drive in males favours $a$, Figure \ref{fig:regionMaleDrive}B).
 
@@
 where $V_{A}=\bar{p}(1-\bar{p})$ is the variance in the equilibrium frequency of $A$ and $S_{A}=(D^\male +\alpha_{\Delta}^\male+t^\male) - (D^\female+\alpha_{\Delta}^\female+t^\female)$ describes sex differences in selection for the $A$ versus $a$ across diploid selection, meiosis, and gametic competition.
-The diploid selection term, $D^\Hermaphrodite=\big{[} \bar{p}s^\Hermaphrodite+(1-\bar{p})h^\Hermaphrodite s^\Hermaphrodite\big{]} -\big{[} \bar{p}h^\Hermaphrodite s^\Hermaphrodite+(1-\bar{p}) \big{]}$, is the difference in fitness between $A$ and $a$ alleles in diploids of sex $\Hermaphrodite \in \{\female,\male\}$, where $\bar{p}$ is the leading-order probability of mating with an $A$-bearing gamete from the opposite sex (see Appendix).
+The diploid selection term, $D^\Hermaphrodite=\big{[} \bar{p}s^\Hermaphrodite+(1-\bar{p})h^\Hermaphrodite s^\Hermaphrodite\big{]} -\big{[} \bar{p}h^\Hermaphrodite s^\Hermaphrodite+(1-\bar{p}) \big{]}$, is the difference in fitness between $A$ and $a$ alleles in diploids of sex $\Hermaphrodite \in \{\female,\male\}$, where $\bar{p}$ is the leading-order probability of mating with an $A$-bearing gamete from the opposite sex (equation \ref{eq:pAve}).
 The difference in $A$-allele-frequency among Y-bearing sperm versus X-bearing sperm is given by $\hat{p}^\male_Y-\hat{p}^\male_X=V_{A}\big{(}D^\male - D^\female+\alpha_{\Delta}^\male-\alpha_{\Delta}^\female+t^\male-t^\female\big{)}(1-2r)/2r$.
@@
 The neo-sex-determining allele, $m$, will spread if $\lambda_{m,XY}>1$. 
-Equation \eqref{eq:lambda_neoY} demonstrates that under weak selection a neo-Y will invade an XY system if and only if it is more closely linked to the selected locus than the ancestral sex-determining region (i.e., if $R<r$; note that $V_{A}S_{A}^2$ is strictly positive as long as \textbf{A} is polymorphic).
-This echoes our tight linkage results above where a neo-Y could never invade if $r\approx0$ and is consistent with the results of \citet{vanDoorn:2007eu}, who considered diploid selection only and also found that homogametic transitions (XY to XY or ZW to ZW) can only occur when the neo-sex-determining locus is more closely linked to a locus under sexually-antagonistic selection.
+Equation \eqref{eq:lambda_neoY} demonstrates that, under weak selection, a neo-Y will invade an XY system if and only if it is more closely linked to the selected locus than the ancestral sex-determining region (i.e., if $R<r$; note that $V_{A}S_{A}^2$ is strictly positive as long as \textbf{A} is polymorphic).
+This echoes our tight linkage results above where a neo-Y could never invade if $r\approx0$.
+It is also consistent with the results of \citet{vanDoorn:2007eu}, who considered diploid selection only and also found that homogametic transitions (XY to XY or ZW to ZW) can only occur when the neo-sex-determining locus is more closely linked to a locus under sexually-antagonistic selection.
 %Because tighter linkage between the sex-determining region and a selected locus evolves during these transitions, stronger associations between selected alleles and diploid sexes can build up by selection (e.g., between male-beneficial alleles and the male-determining allele, Y).%, increasing diploid mean fitness (Figure \ref{fig:Combination_MeanFit}).
@@
 To clarify the parameter space under which $\lambda_{W',XY}>1$, we consider several special cases. 
-Firstly, if the \textbf{A} locus is unlinked to the ancestral sex-determining region ($r=1/2$), a more closely linked neo-W ($R<1/2$) can always invade because there is then no association between $A$ alleles and sex chromosomes in males, $\left( \hat{p}^\male_Y-\hat{p}^\male_X \right)=0$, see equation \eqref{eq:freq_diffs}.
-The second term in equation \eqref{eq:lambda_neoW} then disappears and invasion depends only on the sign of $(r-R)$. 
-Indeed, invasion typically occurs when the neo-W is more closely linked to the selected locus than the ancestral sex-determining region, under a variety of selective regimes (Figure \ref{fig:Combination_Centimorgans}).
+Firstly, if the \textbf{A} locus is unlinked to the ancestral sex-determining region ($r=1/2$), a more closely linked neo-W ($R<1/2$) can always invade because there is no ancestral association between $A$ alleles and sex chromosomes in males, $\left( \hat{p}^\male_Y-\hat{p}^\male_X \right)=0$, see equation \eqref{eq:freq_diffs}.
+The second term in equation \eqref{eq:lambda_neoW} therefore disappears and invasion depends only on the sign of $(r-R)$. 
+Indeed, invasion typically occurs when the neo-W is more closely linked to the selected locus than the ancestral sex-determining region (Figure \ref{fig:Combination_Centimorgans}).
+
 Secondly, we can simplify the discussion of cases where invasion occurs despite looser sex-linkage, $R>r$, by focussing on the special case where $R=1/2$ and $r<1/2$ (e.g., the selected locus is on the ancestral sex chromosome and the novel sex-determining locus arises on an autosome).
 In table \ref{tab:specialcases} we give the conditions where invasion occurs when we further assume that haploid selection only occurs in one sex (e.g., during male meiosis only) and dominance coefficients are equal in the two sexes, $h^\female=h^\male$.
-When there is no gametic competition and meiotic drive is in one sex only, an unlinked neo-W can invade as long as the same allele is favoured during diploid selection in males and females ($s^\female s^\male>0$, see Figure \ref{fig:Combination_Centimorgans}B and Figure \ref{fig:SexRatioBad}B).
+When there is no gametic competition and meiotic drive is in one sex only, an unlinked neo-W can invade as long as the same allele is favoured during diploid selection in males and females ($s^\female s^\male>0$, see Figure \ref{fig:Combination_Centimorgans}A and Figure \ref{fig:SexRatioBad}B).
 %, which is 50\% of the parameter space.
-When there is no meiotic drive and gametic competition occurs in one sex only, an unlinked neo-W can invade as long as the same allele is favoured in male and female diploid selection and there are sex differences in selection of one type (e.g., $s^\female(s^\male-s^\female)>0$, see Figure \ref{fig:Combination_Centimorgans}C).
+When there is no meiotic drive and gametic competition occurs in one sex only, an unlinked neo-W can invade as long as the same allele is favoured in male and female diploid selection and there are sex differences in selection of one type (e.g., $s^\female(s^\male-s^\female)>0$, see Figure \ref{fig:Combination_Centimorgans}B).
 %, which is 25\% of the parameter space.
-These special cases indicate that neo-W invasion can occur for a relatively large fraction of the parameter space, even if the neo-W uncouples the sex-determining locus from a locus under selection.
+These special cases indicate that neo-W invasion occurs for a relatively large fraction of the parameter space, even if the neo-W uncouples the sex-determining locus from a locus under selection.
 
@@
 
-The green curves in Figure \ref{fig:SexRatioBad} demonstrate a case where transitions between male and female heterogametey occur even though the new sex-determining region is unlinked to a locus that experiences haploid and diploid selection.
+The green curves in Figure \ref{fig:SexRatioBad} shows transitions between male and female heterogametey even though the new sex-determining region is unlinked to a locus that experiences haploid and diploid selection.
 We use these green curves to discuss why heterogametic transitions can occur when $R=1/2$ and $r<1/2$, as in Table \ref{tab:specialcases}.
 In Figure \ref{fig:SexRatioBad}B, an unlinked neo-W can spread because the zygotic sex ratio is ancestrally male biased. 
-However, in Figure \ref{fig:SexRatioBad}A, an unlinked neo-Y spreads despite the fact that the ancestral zygotic sex ratio is even. 
-In this case, the the male meiotic drive allele, $a$, is initially more common among ancestral-Z-bearing eggs than ancestral-W-bearing eggs because the Z is found in males more often than the W and $r<1/2$ (equation \ref{eq:freq_diffs}).
+In Figure \ref{fig:SexRatioBad}A, an unlinked neo-Y spreads despite the fact that the ancestral zygotic sex ratio is even. 
+In this case, the the male meiotic drive allele, $a$, is initially more common among ancestral-Z-bearing eggs than ancestral-W-bearing eggs because the Z is found in males more often than the W ($\hat{p}_{W}^\female-\hat{p}_{Z}^\female>0$, equation \ref{eq:freq_diffs}).
 %In this case, the ancestral male determining allele, Z, is initially associated with the male meiotic drive allele, $a$, because the Z is found in males more often than the W and $r<1/2$. 
 Polymorphism at the \textbf{A} locus is maintained by counter-selection against the $a$ allele in diploids and therefore ancestral-ZZ males have generally low diploid fitness. 
-A freely recombining neo-Y ($R=1/2$) is not directly favoured or dis-favoured by male meiotic drive because it is equally likely to be segregate with the $A$ or $a$ allele when found in a heterozygote.
 The neo-Y spreads because it produces males with high diploid fitness through matings with ancestral-W-bearing female gametes, which are more likely to carry the $A$ allele. 
+A freely recombining neo-Y ($R=1/2$) is equally likely to be segregate with the $A$ or $a$ allele and is therefore unaffected by male meiotic drive.
 Thus, a key factor in explaining why heterogametic transitions can occur when $R>r$ is that that the neo-SDR determines sex in the diploid phase but recombination occurs before any subsequent haploid selection.
@@
 %MAIN RESULT
-Two predominant theories explaining the remarkably high frequency of transitions between sex-determination systems are sexually-antagonistic selection and sex-ratio selection \citep[reviewed in][]{Blaser2012} \textcolor{red}{(van Doorn, 2014, sexual development)}.
+Two predominant theories explaining the remarkably high frequency of transitions between sex-determination systems are sexually-antagonistic selection and sex-ratio selection \citep[reviewed in][]{Blaser2012, vanDoorn2014re}.
 The former predicts that neo-sex-determining alleles can invade when they arise in closer linkage with a sexually-antagonistic locus \citep{vanDoorn:2007eu,vanDoorn:2010hu}.
@@
 In addition, with haploid selection and weak selection, heterogametic transitions (XY to ZW or ZW to XY) can occur even when the new sex-determining region is less closely linked to the locus under selection (e.g., see Figure \ref{fig:SexRatioBad}).
-\textcolor{red}{need to mention sex ratio here}
+%\textcolor{red}{need to mention sex ratio here}
 %Neo-W (neo-Y) alleles invade when their fitness in females (males) is greater than the mean fitness of females (males) under the ancestral sex-determination system and/or females (males) are the rarer sex.
@@
 Turnovers driven by haploid selection may help to explain the relative rarity of heteromorphic sex chromosomes in plants, which are thought to experience more selection during their multicellular haploid stage.
-For example, among relatively few dioecious clades in which multiple species have well characterized sex chromosomes \citep{Ming:2011iy}, heterogametic transitions have been inferred in \textit{Silene} subsection \textit{Otites} \citep{Slancarova:2013dq} and in \textit{Salicaceae} \textcolor{red}{(Pucholt et al.
-2015, 2017)}.
+For example, among relatively few dioecious clades in which multiple species have well characterized sex chromosomes \citep{Ming:2011iy}, heterogametic transitions have been inferred in \textit{Silene} subsection \textit{Otites} \citep{Slancarova:2013dq} and in \textit{Salicaceae} \citep{Pucholt2015,Pucholt2017}.
 %Potentially, successive heterogametic transitions between master regulators of sex-determination could be inferred from careful examination of the molecular pathways by which sex is determined. 
 %Our predictions could also be examined using a suitable proxy for haploid selection, for example, \cite{Lenormand:2005vb} use the outcrossing rate in plants as a proxy for the strength of pollen competition.
-Furthermore, assuming that transitions from dioecy to hermaphroditism (equal parental investment in male and female gametes) are favoured in a similar manner to the ESD examined here (equal probability of zygotes developing as males or females), our results suggest that competition during the haploid stage could drive transitions between dioecy and hermaphroditism, which are frequent in plants \textcolor{red}{(Käfer et al., 2017, Sabath et al., 2017)}.
+Furthermore, assuming that transitions from dioecy to hermaphroditism (equal parental investment in male and female gametes) are favoured in a similar manner to the ESD examined here (equal probability of zygotes developing as males or females), our results suggest that competition during the haploid stage could drive transitions between dioecy and hermaphroditism, which are frequent in plants \citep{Kafer2017, Goldberg2017}.
 %In animals, one might expect gametic competition to be stronger in species where sperm is required to live for a long time after spermatogenesis because transcripts shared during spermatogenesis may become depleted, revealing the haploid phenotype of the sperm \citep{Immler:2014im}.
@@
 Our results show that, if loci experiencing overdominance and/or sexually-antagonistic selection can be identified in close linkage with the ancestral sex-determining locus (rather than only the novel sex-determining locus), then they could also be implicated in driving heterogametic transitions between sex-determination systems.
-As noted by \citet{vanDoorn:2010hu}, it would be prudent to compare closely related clades in order to determine whether observed polymorphisms predate a transition in sex-determination or arose afterwards.
+%As noted by \citet{vanDoorn:2010hu}, it would be prudent to compare closely related clades in order to determine whether observed polymorphisms predate a transition in sex-determination or arose afterwards.
 %, particularly because sex-linkage allows sexually-antagonistic selection to maintain polymorphisms under a different and larger parameter space \citep{Rice:1987hs,Jordan:2011fj}.
@@
 Another simplification that we made is that meiotic drive involves only a single locus with two alleles. 
-However, many meiotic drive systems involve an interaction with another locus at which alleles may `suppress' the action of meiotic drive \citep[][]{Burt:2006,Lindholm:2016cw} \textcolor{red}{Taylor,1999}.
+However, many meiotic drive systems involve an interaction with another locus at which alleles may `suppress' the action of meiotic drive \citep[][]{Burt:2006,Lindholm:2016cw}.
 Thus, the dynamics of meiotic drive alleles can be heavily dependent on the interaction between two loci and the recombination rate between them, which in turn can be affected by sex-linkage if there is reduced recombination between sex chromosomes \citep{Hurst:1991uh}.
@@
 %This result is surprising given that sex ratios are ultimately determined via the sex-determination system, and leads us to the conclusion that three selective forces -- haploid, diploid, and sex-ratio selection -- should all be considered when exploring transitions between sex-determination systems.
-
-%POLYGENIC SEX DETERMINATION
-
-\textcolor{red}{Discuss polymorphic mating systems somewhere?
-Say that haploid selection makes this particularly likely (I think there are examples with gametic competition and weak selection, whereas the vD\&K, 2010 results suggest that it's not possible with weak selection and diploid selection alone)?
-This might be best as a section added to the appendix.
-When giving an example of polymorphic, make sure it's not just that variation was lost at the \textbf{A} locus.
-The following examples copied and pasted from  from Vuilleumier et al.
-2007 and vD\&K, 2010, might be added to this section.}
-\textcolor{blue}{I've added a bit to the end of the tight linkage section in the main text.}
-
-\textcolor{red}{``Polygenic sex determination has been reported in many plants (e.g.
-Shannon \& Holsinger 2007), fishes (Vandeputte et al.
-2007; Ser et al.
-2010; Liew et al.
-2012), crustaceans (e.g.
-Battaglia 1958; Battaglia \& Malesani 1959; Voordouw
-\& Anholt 2002), bivalves (Haley 1977; Saavedra et al. 1997), gastropods (Yusa 2007a,b), and polychaetes (Bacci 1965, 1978; Premoli et al. 1996).''
-From Vuilleumier et al. 2007:
-``Polymorphism for sex-determining genes within or among populations has been reported in many species including houseflies, midges, woodlice, platyfish, cichlid fish, and frogs (Gordon, 1944; Kallman, 1970; Thompson, 1971; Macdonald, 1978; Bull, 1983; Rigaud et al., 1997; Caubet et al., 2000; Lande et al., 2001; Ogataet al., 2003; Lee et al., 2004; Mank et al., 2006).''
-Also check Kallman (1984) -from vD\&K, 2010. 
-}
 
@@
 $R$ is the recombination rate between the \textbf{A} locus and the \textbf{M} locus, $\rho$ is the recombination rate between the \textbf{M} locus and the \textbf{X} locus, and $r$ is the recombination rate between the \textbf{A} locus and the \textbf{X} locus.
-Table \ref{tab:chisubstitutions} shows the value of $\rho$ in the absence of cross-over interference for each possible ordering of the loci.
+Table \ref{tab:chisubstitutions} shows replacements that can be made for each possible ordering of the loci assuming that there is no cross-over interference.
 During meiosis in sex $\Hermaphrodite$, meiotic drive occurs such that, in $Aa$ heterozygotes, a fraction $\alpha^{\Hermaphrodite}$ of gametes produced carry the $A$ allele and $(1-\alpha^\Hermaphrodite)$ carry the $a$ allele.

### 2017-10-25 LaTeX/Turnover.tex
minor changes, just reading

@@
 (1) We explicitly consider how selection on very tightly sex-linked loci influences the spread of novel sex-determiners. 
-We find that tightly sex-linked genetic variation can favour the spread of new sex-determination systems in which the heterogametic sex changes (XY to ZW or ZW to XY) and the new sex-determining region is less closely linked (or unlinked) to the sex-linked locus under selection, which would not be predicted by previous theory.
+We find that tightly sex-linked genetic variation can favour the spread of new sex-determination systems in which the heterogametic sex changes (XY to ZW or ZW to XY) and the new sex-determining region is less closely linked (or unlinked) to the sex-linked locus under selection, which is not predicted by previous theory.
 %With tight linkage, selection can maintain equilibria at which the allele fixed on the sex-limited chromosome (Y or W) is simultaneously favoured in the homogametic sex (XX females or ZZ males) such that heterogametic transitions (XY to ZW or ZW to XY) are favoured by selection.
@@
 (b/c the $m$ alleles can arise in either sex?)}
-$\lambda^2+ b \lambda + c =0$ \textcolor{blue}{(see Appendix for a discussion of other roots)}.
+$\lambda^2+ b \lambda + c =0$ \textcolor{blue}{(see Appendix for a discussion of other roots - or Sally's proof!)}.
 %\begin{equation}
@@
 An equivalent analysis is not possible where we assume that linkage is tight. 
-However, numerical simulations with tight linkage demonstrate that the neo-SDR does not necessarily fix, leading to the stable maintenance of a mixed sex-determining system, in which X,Y,Z, and W alleles all segregate, e.g., Figure \ref{fig:freqAll}B-D.
+However, numerical simulations with tight linkage demonstrate that the neo-SDR does not necessarily fix, leading to the stable maintenance of a mixed sex-determining system, in which X, Y, Z, and W alleles all segregate (e.g., Figure \ref{fig:freqAll}B-D).
 Within a species, both feminizing and masculinizing alleles have been reported in houseflies \citep{Macdonald1978}, midges \citep{Thompson1971}, frogs \citep{Ogata:2007jm}, cichlid fish \citep{Ser:2010iq}, tilapia \citep{Lee2004}, sea bass \citep{Vandeputte2007}, and lab-strains of Zebrafish \citep{Liew2012,Wilson2014}.
 For example, in the platyfish (\textit{Xiphophorus maculatus}), X,Y, and W alleles segregate at one locus (or two closely-linked loci) near to potentially sexually-antagonistic genes for pigmentation and sexual maturity \citep{Kallman1965,Kallman1968, Volff2001, Schultheis2006}.
-Our results suggest that several forms of selection on nearby loci ($r$ and $R$ small) could maintain multiple sex determination alleles.
+Our results suggest that several forms of selection on nearby loci (i.e., $r$ and $R$ small) could maintain multiple sex-determining alleles.
 
@@
 %For instance, overdominance is no longer required for neo-W-$a$ haplotypes to spread when there is haploid selection (e.g., when $a$ is female-beneficial, $A$ is male-beneficial, and meiotic drive in males favours $a$, Figure \ref{fig:regionMaleDrive}B).
+\textcolor{blue}{haploid selection?}
 
@@
 
-Secondly, we can simplify the discussion of cases where invasion occurs despite looser sex-linkage, $R>r$, by focussing on the special case where $R=1/2$ and $r<1/2$ (e.g., the selected locus is on the ancestral sex chromosome and the novel sex-determining locus arises on an autosome).
-In table \ref{tab:specialcases} we give the conditions where invasion occurs when we further assume that haploid selection only occurs in one sex (e.g., during male meiosis only) and dominance coefficients are equal in the two sexes, $h^\female=h^\male$.
+Secondly, we can simplify the discussion of cases where invasion occurs despite looser sex-linkage, $R>r$, by focusing on the special case where $R=1/2$ and $r<1/2$ (e.g., the selected locus is on the ancestral sex chromosome and the novel sex-determining locus arises on an autosome).
+In Table \ref{tab:specialcases} we give the conditions where invasion occurs when we further assume that haploid selection only occurs in one sex (e.g., during male meiosis only) and dominance coefficients are equal in the two sexes, $h^\female=h^\male$.
 When there is no gametic competition and meiotic drive is in one sex only, an unlinked neo-W can invade as long as the same allele is favoured during diploid selection in males and females ($s^\female s^\male>0$, see Figure \ref{fig:Combination_Centimorgans}A and Figure \ref{fig:SexRatioBad}B).
@@
 \noindent
-where $\lambda_{Y',XY\rvert R=1/2}$ and $\lambda_{W',XY\rvert R=1/2}$ represent $\lambda_{Y',XY}$ and $\lambda_{W',XY}$ when evaluated at $R=1/2$ (equations \ref{eq:lambda_neoY} and \ref{eq:lambda_neoW}).
+where $\lambda_{Y',XY\rvert R=1/2}$ and $\lambda_{W',XY\rvert R=1/2}$ represent $\lambda_{Y',XY}$ and $\lambda_{W',XY}$ when evaluated at $R=1/2$ (Equations \ref{eq:lambda_neoY} and \ref{eq:lambda_neoW}).
 That is, recombination between the selected locus and the novel sex-determining locus, $R$, doesn't enter into the $k=1/2$ results.
@@
 Because haploid selection can cause transitions that increase or decrease sex-linkage, haploid selection may lead to less stability, and greater potential for cycling, in sex-determination systems (e.g., the final state of the red line in Figure \ref{fig:SexRatioBad}A is the starting state in Figure \ref{fig:SexRatioBad}B).
-In particular, if haploid selection is strong but selective differences between male and female diploids are weak, we find that heterogametic transitions (XY to ZW or vice versa) are favoured more strongly than homogametic transitions (e.g., with $|D^\male - D^\female| << |\alpha_\Delta^\male - \alpha_\Delta^\female + t^\male - t^\female|$ we have $\lambda_{W',XY} > \lambda_{Y',XY}$; equations \ref{eq:lambda_neoW} and \ref{eq:freq_diffs}).
+In particular, if haploid selection is strong but selective differences between male and female diploids are weak, we find that heterogametic transitions (XY to ZW or vice versa) are favoured more strongly than homogametic transitions (e.g., with $|D^\male - D^\female| << |\alpha_\Delta^\male - \alpha_\Delta^\female + t^\male - t^\female|$ we have $\lambda_{W',XY} > \lambda_{Y',XY}$; Equations \ref{eq:lambda_neoW} and \ref{eq:freq_diffs}).
 Turnovers driven by haploid selection may help to explain the relative rarity of heteromorphic sex chromosomes in plants, which are thought to experience more selection during their multicellular haploid stage.
@@
 In panels C and D, selection in males and females is overdominant ($w_{aa}^\female=w_{AA}^\female=0.6$, $w_{aa}^\male=0.5$, $w_{AA}^\male=0.7$, $w_{Aa}^\Hermaphrodite=1$).
-These parameters are marked by a dagger in Figure \ref{fig:regionplots}, which shows that neo-W invasion is expected for any $R$ when the $a$ allele is nearly fixed on the Y (black lines). 
-Equilibria where the $A$ allele is more common among Y-bearing male gametes can also be stable for these parameters (blue lines). 
-The weak selection approximation holds when all recombination rates are large relative to selection (around 0 in panels A and C), in which case neo-W alleles should spread if they are more tightly linked to the selected locus (positive invasion fitness in the grey region).
-However, when linkage is tight (panels C and D and when the selected locus is near the SDR), this prediction breaks down. 
-Here, there is no haploid selection $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
+There is no haploid selection $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
+These parameters are marked by daggers in Figure \ref{fig:regionplots}B and C, which show that neo-W invasion is expected for any $R$ ($\lambda_{WA},\lambda_{Wa}>1$) when the $a$ allele is nearly fixed on the Y (black lines in this figure).
+Equilibria where the $A$ allele is more common among Y-bearing male gametes can also be stable and allow neo-W invasion for these parameters (blue lines). 
+The weak selection approximation holds when all recombination rates are large relative to selection (around 0 in panels A and C), in which case, in the absence of haploid selection, neo-W alleles should spread only if they are more tightly linked to the selected locus (positive invasion fitness if and only if the selected locus is in the grey region).
+However, when linkage is tight (panels C and D and when the selected locus is near the SDR in all panels), this prediction breaks down. 
 }
@@
 \textcolor{blue}{This is now discussed in a round-about way at the beginning of the tight linkage invasion section in the main text. }
-Parameters given by asterisk in Figure \ref{fig:regionMaleDrive}: $w_{AA}^\female=1.05$, $w_{Aa}^\Hermaphrodite=1$, $w_{aa}^\female=0.85$, $w_{AA}^\male=0.85$, $w_{aa}^\male=1.05$, $\alpha_{\Delta}^\male=-0.08$.
+Parameters given by asterisk in Figure \ref{fig:regionMaleDrive}A: $w_{AA}^\female=1.05$, $w_{Aa}^\Hermaphrodite=1$, $w_{aa}^\female=0.85$, $w_{AA}^\male=0.85$, $w_{aa}^\male=1.05$, $\alpha_{\Delta}^\male=-0.08$.
 }

### 2017-10-25 LaTeX/Turnover.tex
haploid tight linkage appendix section

--- 2017-10-23 LaTeX/Turnover.tex
@@
 That is, Y-$a$ haplotypes must have higher fitness than Y-$A$ haplotypes.  
-Substituting in $\hat{p}_X^\female = \hat{p}_{X}^{\female}$ from above, fixation of the $a$ allele on the Y requires that $\gamma_{i}>0$ where $\gamma_{(A)}=w_{a}^{\male} \big[ (1-\alpha^\male_\Delta) w_{Aa}^{\male} \phi + w_{aa}^{\male} \psi \big]-w_{A}^{\male} \big[ w_{AA}^{\male} \phi + (1 + \alpha^{\male}_\Delta)w_{Aa}^{\male} \psi \big]$ for equilibrium $(A)$ and $\gamma_{(B)}=(1-\alpha^{\male}_\Delta)w_{a}^{\male}w_{Aa}^{\male}-w_{A}^{\male}w_{AA}^{\male}$ for equilibrium $(B)$.
+Substituting in $\hat{p}_X^\female$ from equation \eqref{eq:tightequil}, fixation of the $a$ allele on the Y requires that $\gamma_{i}>0$ where $\gamma_{(A)}=w_{a}^{\male} \big[ (1-\alpha^\male_\Delta) w_{Aa}^{\male} \phi + w_{aa}^{\male} \psi \big]-w_{A}^{\male} \big[ w_{AA}^{\male} \phi + (1 + \alpha^{\male}_\Delta)w_{Aa}^{\male} \psi \big]$ for equilibrium $(A)$ and $\gamma_{(B)}=(1-\alpha^{\male}_\Delta)w_{a}^{\male}w_{Aa}^{\male}-w_{A}^{\male}w_{AA}^{\male}$ for equilibrium $(B)$.
 Stability of a polymorphism on the X chromosome (equilibrium $A$) further requires that $\phi >0$ and $\psi >0$. 
@@
 
-%As with equilibrium (B), if both haplotypes can spread ($\lambda_{mA}>1$ and $\lambda_{ma}>1$) then the neo-W invades under any rate of recombination with the selected locus, $R\geq0$. 
-%In addition, even when only one haplotype can spread (e.g., under purely sexually-antagonistic selection $\lambda_{mA}>1$ and $\lambda_{ma}<1$), neo-W invasion can still occur under modest rates of recombination between the novel sex-determining and selected loci.
+\subsubsection*{Tight Linkage and Haploid Selection}
+
+Generally, haploid selection expands the scenarios under which neo-W alleles can spread. 
+For example, when selection is sexually-antagonistic in diploids ($s^\female s^\male <0$ and $0<h^\Hermaphrodite<1$) an unlinked neo-W ($R=1/2$) cannot invade unless there is also haploid selection, c.f., Figure \ref{fig:SexAntagTighter} and Figure \ref{fig:SexAntagTighterMaleDrive}.
+Secondly, with haploid selection, overdominance ($w_{aa}^\Hermaphrodite<w_{Aa}^\Hermaphrodite$ \& $w_{AA}^\Hermaphrodite<w_{Aa}^\Hermaphrodite$) is not required for neo-W-$a$ haplotypes to spread ($\lambda_{ma}>1$), Figures \ref{fig:regionMaleDrive}-\ref{fig:regionFemaleGS}.
+Finally, haploid selection can maintain a polymorphism in the face of directional selection in male and female diploids (ploidally-antagonistic selection). 
+When selection is ploidally-antagonistic, neo-W alleles often spread, for at least some values of $R$, Figure \ref{fig:regionPloidAntag}.
+
+As discussed above, male haploid selection alters the sex ratio and the alleles carried by male gametes that female gametes pair with. 
+Male haploid selection in favour of the $a$ allele ($\alpha_{\Delta}^\male<0$, $w_{A}^\male<w_{a}^\male$) generates male-biased sex ratios at equilibria (A) and (B), where Y-$a$ is fixed ($\hat{p}_{Y}^\male=0$).
+Male-biased sex-ratios facilitate the spread of neo-W-$A$ and neo-W-$a$ haplotypes (increasing $\lambda_{WA}$ and $\lambda_{Wa}$). 
+Panels A-C in Figures \ref{fig:regionMaleDrive} and \ref{fig:regionMaleGS} show that neo-W haplotypes tend to spread for a wider range of parameters when sex ratios are male biased, compared to Figure \ref{fig:regionplots} without haploid selection.
+By contrast, male haploid selection in favour of the $A$ allele generates female-biased sex ratios and reduces $\lambda_{WA}$ and $\lambda_{Wa}$, as demonstrated by panels D-F in Figures \ref{fig:regionMaleDrive} and \ref{fig:regionMaleGS}.
+
+Female haploid selection generates direct selection on the neo-W-$A$ and neo-W-$a$ haplotypes as they spread in females. 
+Thus, female haploid selection in favour of the $a$ allele tends to increase $\lambda_{Wa}$ and decrease $\lambda_{WA}$, as shown by panels A-C in Figures \ref{fig:regionFemaleDrive} and \ref{fig:regionFemaleGS}.
+Conversely, female haploid selection in favour of the $A$ allele increases $\lambda_{WA}$ and decreases $\lambda_{Wa}$, see panels D-F in Figures \ref{fig:regionFemaleDrive} and \ref{fig:regionFemaleGS}.
 
@@
 \caption{
-ABC, $\alpha_{\Delta}^\female=-0.08$
-DEF, $\alpha_{\Delta}^\female=0.08$. $\lambda$s are increased for the haplotype that is favoured by female haploid selection, the stability conditions are also affected. 
+ABC, $\alpha_{\Delta}^\female=-0.16$
+DEF, $\alpha_{\Delta}^\female=0.16$. $\lambda$s are increased for the haplotype that is favoured by female haploid selection, the stability conditions are also affected. 
 }

### 2017-10-26 LaTeX/Turnover.tex

@@
 %Drosophila http://www.biorxiv.org/content/early/2017/02/06/106336
-\textcolor{red}{Genetic mapping experiments, which are typically designed to minimize selection in diploids, have revealed segregation distortion in various species, including mice, Drosophila, Rice, Maize, Wheat, Barley, Cotton...
-In some of these cases, biased segregation has been attributed to meiotic drive and/or gametic selection \textcolor{red}{(Leppala et al.
-2013, Didion et al.
-2015, 2016 Xu et al 2013 (rice), Fishman...)}.
-}
-Meiotic drive generally occurs either during the production of male or female gametes only \citep{Ubeda:2005gw,Lindholm:2016cw}.
+Segregation distortion provides putative evidence of haploid selection and can sometimes be attributed to meiotic drive and/or gametic competition \citep{Lalanne2004,Fishman2005,Leppala2008,Leppala2013,Didion2015,Didion2016}.
+Where it has been characterized, meiotic drive generally occurs either during the production of male or female gametes only \citep{Ubeda:2005gw,Lindholm:2016cw}.
 Gametic competition is also typically sex specific, occurring primarily among male gametes, because there are typically many more pollen/sperm than required for fertilization.
@@
 
-There are various ways in which a period of haploid selection could influence transitions between sex-determination systems. 
+There are various ways by which genes experiencing haploid selection could influence transitions between sex-determination systems. 
 If we assume that haploid selection at any particular locus predominantly occurs in one sex (e.g., meiotic drive during spermatogenesis), then such loci experience a form of sex-specific selection. 
@@
 In addition to considering haploid selection, another novel development in our model is that we consider loci that are in very tight linkage with the ancestral sex-determining region.
-We show that transitions between male and female heterogamety can then evolve despite the fact that the neo-sex-determining locus is less closely linked to a locus under selection and therefore disrupts favourable ancestral associations between sex and the alleles selected in that sex.
+We show that transitions between male and female heterogamety can then evolve despite the fact that the neo-sex-determining locus is less closely linked to a locus under selection and therefore disrupts favourable ancestral associations between sex and the alleles favoured in that sex.
 %Such transitions are not favoured in models lacking tight linkage and/or haploid selection. 
@@
 In fact, with tight linkage between the ancestral SDR and the selected locus, haploid selection and/or overdominance can favour completely unlinked neo-W alleles ($R=1/2$), allowing autosomes to become new sex chromosomes.
-To develop an intuition for how less closely linked neo-W alleles invade, we first focus on cases where there is no haploid selection and then discuss the additional effect of haploid selection (more details in the appendix).
+To develop an intuition for how less closely linked neo-W alleles invade, we first focus on cases where there is no haploid selection and discuss the additional effect of haploid selection in the appendix.
 %}
@@
 %For instance, overdominance is no longer required for neo-W-$a$ haplotypes to spread when there is haploid selection (e.g., when $a$ is female-beneficial, $A$ is male-beneficial, and meiotic drive in males favours $a$, Figure \ref{fig:regionMaleDrive}B).
-\textcolor{blue}{haploid selection?}
 
@@
 Significantly, equation \eqref{eq:lambda_ESD} is the same whether ESD is invading an ancestrally XY or ZW system (because $\lambda_{Y',XY} = \lambda_{W',ZW}$ and $\lambda_{W',XY} = \lambda_{Y',ZW}$).
-Thus, because the sex ratio is only biased by male haploid selection when the ancestral sex-determination system is XY, Fisherian sex-ratio selection alone does not explain the invasion of ESD under weak selection.
+Thus, Fisherian sex-ratio selection alone does not explain the invasion of ESD under weak selection because the sex ratio is only biased by male haploid selection when the ancestral sex-determination system is XY.
 Specifically, with male haploid selection, the neo-ESD is equally likely to invade when it equalizes the zygotic sex ratio (through $\lambda_{W',XY}$) and when it doesn't (through $\lambda_{Y',ZW}$). 
@@
 
-\textcolor{red}{check last condition and the stability condition below are correct}
-\textcolor{blue}{The last condition looks good to me, although in your Turnover-norec-MFS.nb you look at YA fixed, so you have to flip everything (so I made Turnover-norec-MFS-MMO.nb to do this).
-The one issue I can find here is that you can also prevent $\lambda>1$ when the slope and intercept of the quadratic at $\lambda=1$ are negative (you only looked at both being positive).
+%\textcolor{red}{check last condition and the stability condition below are correct}
+%\textcolor{blue}{The last condition looks good to me, although in your Turnover-norec-MFS.nb you look at YA fixed, so you have to flip everything (so I made Turnover-norec-MFS-MMO.nb to do this).
+%The one issue I can find here is that you can also prevent $\lambda>1$ when the slope and intercept of the quadratic at $\lambda=1$ are negative (you only looked at both being positive).
 In this case we need $4w_{A}^{\female}w_{AA}^{\female}<(1-\alpha_\Delta^{\female})w_{a}^{\female}w_{Aa}^{\female}$, which also prevents $\psi>0$.
-I've added this in.
-It could also be the case that the slope and intercept are the same sign but the roots are imaginary - but this is never the case here.
-Stability condition below looks good to me (from matt version of turnoverSOM-MIKE.nb).}
+%I've added this in.
+%It could also be the case that the slope and intercept are the same sign but the roots are imaginary - but this is never the case here.
+%Stability condition below looks good to me (from matt version of turnoverSOM-MIKE.nb).}
 
@@
 This can occur with overdominance or directional selection for $a$ in females (Figure \ref{fig:regionplots}B,C).
-In this case, $a$ is not favoured enough in females near the equilibrium (comparing $Aa$ to $AA$ genotypes) to prevent $A$ from stably fixing on the X, and yet the neo-W can spread with $a$ because it produces female $aa$ individuals by capturing Y-$a$ haplotypes.
-\textcolor{blue}{mike, could you check this paragraph? i fixed an old problem, and want to make sure i haven't introduced any new errors}
+In this case, $a$ is favoured in females (comparing $Aa$ to $AA$ genotypes in females) but $A$ is fixed on the X due to selection in males. 
+The neo-W-$a$ haplotype can spread because it produces females with higher fitness $Aa$ and $aa$ genotypes.
 
@@
 When there is sexually-antagonistic selection and haploid selection, a neo-W may invade for any $R$.
-\textcolor{red}{
-Check that we mention Sally's result that invasion cannot occur with sexually-antagonistic selection and $R=1/2$ (currently only in legend for figure \ref{fig:SexAntagTighter}). 
-%Add asterisk to Figure \ref{fig:regionMaleDrive}A to show parameters used in this plot. 
-}
-\textcolor{blue}{This is now discussed in a round-about way at the beginning of the tight linkage invasion section in the main text. }
-Parameters given by asterisk in Figure \ref{fig:regionMaleDrive}A: $w_{AA}^\female=1.05$, $w_{Aa}^\Hermaphrodite=1$, $w_{aa}^\female=0.85$, $w_{AA}^\male=0.85$, $w_{aa}^\male=1.05$, $\alpha_{\Delta}^\male=-0.08$.
+Panel A shows that the invasion fitness of a neo-W is positive where linkage is tight, even when $r<R$ (unshaded region). \textcolor{red}{(remove A?)}
+In panel B, we vary the recombination rate between the neo-W and the selected locus ($R$) for a fixed recombination rate between the ancestral-SDR and the selected locus ($r=0.005$).
+Coloured markers show recombination rates for which the temporal dynamics of neo-W invasion are plotted in panel C (black $R=0.001$, red $R=0.02$, blue $R=0.1$, green $R=0.5$). 
+The diploid selection parameters used in this plot are the same as in Figure \ref{fig:SexAntagTighter}, marked by an asterisk in Figure \ref{fig:regionMaleDrive}A: $w_{AA}^\female=1.05$, $w_{Aa}^\Hermaphrodite=1$, $w_{aa}^\female=0.85$, $w_{AA}^\male=0.85$, $w_{aa}^\male=1.05$, $\alpha_{\Delta}^\male=-0.08$, except that there is also male meiotic drive in favour of the $a$ allele, $\alpha_{\Delta}^\male=-0.08$.
+When $R=0.5$ (green curve), the neo-W does not reach fixation and X,Y,Z, and W alleles are all maintained in the population, see Figure \ref{fig:freqAll}C.
 }
@@
 \caption{
-ABC, $\alpha_{\Delta}^\male=-0.08$
-DEF, $\alpha_{\Delta}^\male=0.08$. 
+Meiotic drive in males affects whether neo-W-$A$ and neo-W-$a$ haplotypes spread when the ancestral-XY locus is tightly linked to a locus under selection ($r=0$). 
+We vary the fitness of male homozygotes relative to heterozygotes ($w_{Aa}^\Hermaphrodite=1$) and only consider stable equilibria at which both \textbf{A} locus allele are maintained and the $a$ allele is initially fixed on the Y, region outlined.
+In panels A-C, meiotic drive in males favours the $a$ allele ($\alpha_{\Delta}^\male=-0.16$), creating male-biased sex ratios and generally increasing $\lambda_{WA}$ and $\lambda_{Wa}$. 
+By contrast, $\lambda_{WA}$ and $\lambda_{Wa}$ tend to be reduced when meiotic drive in males favours the $A$ allele ($\alpha_{\Delta}^\male=0.16$), panels D-F. 
+We consider three forms of selection in females: directional selection in favour of the $A$ allele (panels A and D, $w_{aa}^\female=0.85$, $w_{AA}^\female=1.05$), direction selection in favour of the $a$ allele (panels B and E, $w_{aa}^\female=1.05$, $w_{AA}^\female=0.85$), and overdominance (panels C and F, $w_{aa}^\female=0.6$, $w_{AA}^\female=0.6$).
 %\textcolor{red}{Panel F mislabelled, should have $\lambda_{Wa}>1$ \& $\lambda_{WA}<1$ as the upper label that has the line.}
@@
 \caption{
-ABC, $w_{a}^\male=1.16$, $w_{A}^\male=1$.
-DEF, $w_{a}^\male=1$, $w_{A}^\male=1.16$. 
-\textcolor{red}{I thought that re-running this with $w_{a}^\male=1.16$, $w_{A}^\male=0.84$ and $w_{a}^\male=0.84$, $w_{A}^\male=1.16$ will mean that it matches exactly with the meiotic drive example.
-Checking for panel A, the result was qualitatively similar (e.g., region where both $\lambda$'s are greater than one in panel A, as you might expect from equation \eqref{Binvasion}, however the region where a polymorphism is stable is also altered so they don't exactly match.
-}
-\textcolor{blue}{trouble is selection only in heterozygotes with drive?}
+Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is male gametic competition at a locus that is tightly linked to the ancestral-XY locus.
+Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in Figure \ref{fig:regionMaleDrive}. 
+The $a$ allele is favoured during male gametic competition in Panels A-C ($w_{a}^\male=1.16$, $w_{A}^\male=1$), which creates male biased sex-ratios and increases $\lambda_{WA}$ and $\lambda_{Wa}$. 
+On the other hand, the $A$ allele is favoured during male gametic competition in Panels D-F ($w_{a}^\male=1$, $w_{A}^\male=1.16$) and $\lambda_{WA}$ and $\lambda_{Wa}$ tend to be reduced. 
+Compared to the meiotic drive parameters in Figure \ref{fig:regionMaleDrive}, the effect of these male gametic competition parameters on the sex ratio is smaller. 
+For example, in Figure \ref{fig:regionMaleDrive}A-C, the ancestral sex ratio is $\alpha^\male=0.58$ at equilibrium (B) and in panels A-C of this plot, the ancestral sex ratio is $w_{a}^\male/(w_{A}^\male+w_{a}^\male)=0.537$ at equilibrium (B).
 }
@@
 \caption{
-ABC, $\alpha_{\Delta}^\female=-0.16$
-DEF, $\alpha_{\Delta}^\female=0.16$. $\lambda$s are increased for the haplotype that is favoured by female haploid selection, the stability conditions are also affected. 
+Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is female meiotic drive at a locus that is tightly linked to the ancestral-XY locus.
+Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in Figure \ref{fig:regionMaleDrive} and \ref{fig:regionMaleGS}. 
+The $a$ allele is favoured by meiotic drive in females in Panels A-C ($\alpha_{\Delta}^\female=-0.16$), which increases $\lambda_{Wa}$ and decreases $\lambda_{WA}$. 
+Female meiotic drive in favour of the $A$ allele (panels D-F, $\alpha_{\Delta}^\female=-0.16$) has the opposite effect. 
 }
@@
 \caption{
-ABC, $w_{a}^\female=1.16$, $w_{A}^\female=1$.
-DEF, $w_{a}^\female=1$, $w_{A}^\female=1.16$. 
-%\textcolor{red}{Panel F mislabelled, should have $\lambda_{Wa}>1$ \& $\lambda_{WA}<1$ as the upper label that has the line.}
+Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is female meiotic drive at a locus that is tightly linked to the ancestral-XY locus.
+Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in Figure \ref{fig:regionMaleDrive}, \ref{fig:regionMaleGS}, and \ref{fig:regionFemaleDrive}. 
+The $a$ allele is favoured during female gametic competition in females in Panels A-C ($\alpha_{\Delta}^\female=-0.16$), which increases $\lambda_{Wa}$ and decreases $\lambda_{WA}$. 
+The $A$ allele is favoured during gametic competition in panels D-F ($\alpha_{\Delta}^\female=-0.16$), giving the opposite effect on $\lambda_{Wa}$ and $\lambda_{WA}$. 
 }
@@
 \caption{
-Dynamics of all sex-determining alleles in each sex (males dashed).
-Red is neo-W, Blue is Y, Black is $A$.
-Panel A has the same parameters as the green curve in Figure \ref{fig:SexRatioBad}B (ploidy-antagonism with male drive).
-Panel B has the same parameters as the green curve in Figure \ref{fig:temporalOverdominance}C (overdominance in both sexes).
-Panel C has the same parameters as the green curve in Figure \ref{fig:regionMaleDrive}C (sexual-antagonism with male drive).
+Dynamics of sex-determining alleles during invasion by a neo-W allele. 
+The curves show the frequencies of the neo-W (red), ancestral-Y (Blue), and $A$ allele among female gametes (solid curves) and among male gametes (dashed curves). 
+In panel A, there is a complete transition from XY sex determination (XX-ZZ females and XY-ZZ males) to ZW sex determination (YY-ZW females and YY-ZZ males).  
+In panels B-D polymorphism is maintained at both the ancestral XY locus and the neo-ZW locus, such that there are males with genotypes XY-ZZ or YY-ZZ and females with genotypes XX-ZZ, XX-ZW, XY-ZW, or YY-ZW.
+In panel A, selection is ploidally antagonistic with drive in males (parameters as in the green curve in Figure \ref{fig:SexRatioBad}B).
+In panel B, there is overdominance in both sexes (parameters as the green curve in Figure \ref{fig:temporalOverdominance}C).
+In panel C, there is male meiotic drive and sexually-antagonistic selection in diploids (parameters as the green curve in Figure \ref{fig:regionMaleDrive}C).
+\textcolor{red}{(remove D?)}
 Panel D has the same parameters as the red curve in Figure \ref{fig:regionPloidAntag}F, except $r=0$ (ploidy-antagonism with pollen competition).
-Panel A shows complete sex-determination turnover (XY $\rightarrow$ ZW) whereas panels B-D show the evolution of polymorphic sex-determining systems (X and Y still segregating and the neo-W has a frequency in females that is less than 1/2).
-All begin from equilibrium that would have $a$ fixed on the Y if $r=0$.
-All maintain a polymorphism at $\mathbf{A}$ locus.
+In all cases, the initial equilibrium frequency has $a$ near fixed on the Y.
 }
@@
 
-\begin{figure}[!h]
-\centering
-\centerline{
-\includegraphics[width=\linewidth]{Sallys_R_plot.pdf}
-}
-\caption{
-\textcolor{blue}{is this the one?}
-}
-\label{fig:lambda_R}
-\end{figure}
-
-\newpage
-\textcolor{red}{
-Add Sally's figure showing lambda for small r near equil A versus near equil B.
+%\begin{figure}[!h]
+%\centering
+%\centerline{
+%\includegraphics[width=\linewidth]{Sallys_R_plot.pdf}
+%}
+%\caption{
+%\textcolor{blue}{is this the one?}
+%}
+%\label{fig:lambda_R}
+%\end{figure}
+
+%\newpage
+%\textcolor{red}{
+%Add Sally's figure showing lambda for small r near equil A versus near equil B.
 Add references to this figure to appendix where we discuss whether lambdas can be greater than 1 with sexually antagonistic selection.}
-\textcolor{blue}{not sure which one you are talking about, but see Figure \ref{fig:lambda_R} }
-
-\textcolor{red}{
-Perhaps it would also be useful to add an 8 panel figure that features ploidally antagonistic selection.
+%\textcolor{blue}{not sure which one you are talking about, but see Figure \ref{fig:lambda_R} }
+%\textcolor{red}{Let's remove this for now.}
+
+%\textcolor{red}{
+%Perhaps it would also be useful to add an 8 panel figure that features ploidally antagonistic selection.
 For each type of haploid selection (gametic competition/ meiotic drive in males/females), give a regionplot where $h^\male=h^\female$, e.g., $h^\male=h^\female=0.75$ (or perhaps the value of $h$ we use in the regionplots we have, in which $w_{aa}=0.85$, $w_{Aa}=1$, $w_{AA}=1.05$).
-Matt made a figure like this before but both Y$a$ and Y$A$ equilibria were plotted and there was no outline showing where the Y$a$ equilibrium is stable (as in Figure \ref{fig:regionplots}).
+%Matt made a figure like this before but both Y$a$ and Y$A$ equilibria were plotted and there was no outline showing where the Y$a$ equilibrium is stable (as in Figure \ref{fig:regionplots}).
 In Matts plot the axes were $s^\Hermaphrodite$ and $\alpha_{\Delta}^\Hermaphrodite$.
-Add an asterisk to each region plot and show invasion in another panel, using those parameters and various $R$ (e.g., in the stye of \ref{fig:temporalOverdominance}). 
-In an email, Sally has an example of ploidally-antagonistic selection where the neo-W fixes and $R=1/2$. This would cover that case and more. }
-\textcolor{blue}{
-made an attempt (Figure \ref{fig:regionPloidAntag})
-}
-
-\textcolor{red}{
-We could also give versions of Figure \ref{fig:regionplots} where there is also haploid selection of various types.
-Haploid selection can favour $A$ or $a$, so this would involve 4x 6-panel figures.
+%Add an asterisk to each region plot and show invasion in another panel, using those parameters and various $R$ (e.g., in the stye of \ref{fig:temporalOverdominance}). 
+%In an email, Sally has an example of ploidally-antagonistic selection where the neo-W fixes and $R=1/2$. This would cover that case and more. }
+%\textcolor{blue}{made an attempt (Figure \ref{fig:regionPloidAntag})}
+
+%\textcolor{red}{
+%We could also give versions of Figure \ref{fig:regionplots} where there is also haploid selection of various types.
+%Haploid selection can favour $A$ or $a$, so this would involve 4x 6-panel figures.
 Started looking at this in Figure \ref{fig:regionMaleGS} and Figure \ref{fig:regionMaleDrive}, add female haploid selection.
-Try to integrate into the discussion of haploid selection? e.g., male haploid selection ones generally show effect of sex ratio, increasing both lambdas when female biased (top rows).}
-\textcolor{blue}{
-these figures are now done (\ref{fig:regionMaleDrive}-\ref{fig:regionFemaleGS}) (ensuring frequencies between 0 and 1), but yet to discuss in text.}
-
-\textcolor{red}{
-Perhaps, for one set of parameters, we should plot the dynamics of all the different alleles.
+%Try to integrate into the discussion of haploid selection? e.g., male haploid selection ones generally show effect of sex ratio, increasing both lambdas when female biased (top rows).}
+%\textcolor{blue}{
+%these figures are now done (\ref{fig:regionMaleDrive}-\ref{fig:regionFemaleGS}) (ensuring frequencies between 0 and 1), but yet to discuss in text.}
+
+%\textcolor{red}{
+%Perhaps, for one set of parameters, we should plot the dynamics of all the different alleles.
 E.g., we could use the same parameters used in \ref{fig:SexRatioBad}.
 The main purpose would be to show what happens to the ancestral SDR during turnover.
-We could also show an example where XY and ZW sex determining systems are both polymorphic and stable (e.g., using one of the curves in Figure \ref{fig:temporalOverdominance} and the green curve in Figure \ref{fig:SexAntagTighterMaleDrive}).
-I think there are also examples with looser sex linkage and pollen competition that lead to a mixed sex-determination system. We should probably have a short section in the appendix discussing this. 
+%We could also show an example where XY and ZW sex determining systems are both polymorphic and stable (e.g., using one of the curves in Figure \ref{fig:temporalOverdominance} and the green curve in Figure \ref{fig:SexAntagTighterMaleDrive}).
+%I think there are also examples with looser sex linkage and pollen competition that lead to a mixed sex-determination system.
+We should probably have a short section in the appendix discussing this.
 }
-\textcolor{blue}{made an attempt with Figure \ref{fig:freqAll}, but yet to discuss in text}
+%\textcolor{blue}{made an attempt with Figure \ref{fig:freqAll}, but yet to discuss in text}
 

### 2017-10-27 LaTeX/Turnover.tex
starting to compile mathematica file

@@
 
-\subsection*{Recursion Equations}
+\subsection*{Recursion equations}
 \label{app:recurs}
@@
 In each generation we census the genotype frequencies in male and female gametes/gametophytes (hereafter, gametes) between meiosis (and any meiotic drive) and gametic competition. 
-At this stage we denote the frequencies of X- and Y-bearing gametes from males and females $x_{i}^{\Hermaphrodite}$ and $y_{i}^{\Hermaphrodite}$, where $\Hermaphrodite \in \{\male,\female\}$ specifies the sex of the diploid that the gamete came from.
-$i\in\{1,2,3,4\}$ specifies the genotype at the selected locus $\mathbf{A}$ and at the novel sex-determining locus $\mathbf{M}$ where $1=MA$, $2=Ma$, $3=mA$, and $4=ma$. 
+At this stage we denote the frequencies of X- and Y-bearing gametes from males and females $x_{i}^{\Hermaphrodite}$ and $y_{i}^{\Hermaphrodite}$.
+The superscript $\Hermaphrodite \in \{\male,\female\}$ specifies the sex of the diploid that the gamete came from. 
+The subscript $i\in\{1,2,3,4\}$ specifies the genotype at the selected locus $\mathbf{A}$ and at the novel sex-determining locus $\mathbf{M}$, where $1=AM$, $2=aM$, $3=Am$, and $4=am$. 
 The gamete frequencies from each sex sum to one, $\sum_{i}x_{i}^{\Hermaphrodite}+y_{i}^{\Hermaphrodite}=1$.
@@
 However, not all diploid types are produced under certain sex-determination systems. 
-For example, with the $M$ allele fixed and an ancestral $XY$ sex determination, there are $XX$ males, $XY$ females, or $YY$ females ($x_{3}^\Hermaphrodite=x_{4}^\Hermaphrodite=y_{4}^\Hermaphrodite=y_{3}^\Hermaphrodite=y_{i}^\female=0$).
+For example, with the $M$ allele fixed and an ancestral $XY$ sex-determining system, there are $XX$ males, $XY$ females, or $YY$ females ($x_{3}^\Hermaphrodite=x_{4}^\Hermaphrodite=y_{4}^\Hermaphrodite=y_{3}^\Hermaphrodite=y_{i}^\female=0$).
 %($xx_{11}^{\male}=xx_{12}^{\male}=xx_{22}^\male=xy_{11}^{\female}=xy_{12}^{\female}=xy_{21}^{\female}=xy_{22}^\female=yy_{11}^{\female}=yy_{12}^{\female}=yy_{22}^\female=0$). 
@@
 
-\subsection*{Resident equilibrium and stability}
+\subsection*{Resident equilibria and stability}
 

### 2017-11-07 LaTeX/Turnover.tex
tight linkage eq and stab compiled

@@
 Various forms of selection can maintain a polymorphism at the \textbf{A} locus, including sexually antagonistic selection, overdominance, conflicts between diploid selection and selection upon haploid genotypes \citep[ploidally antagonistic selection,][]{Immler:2012tl}, or a combination of these selective regimes.
+\textcolor{blue}{add reference or say "see below"}
 
@@
 (A)\ \ \ &\hat{p}_{Y}^{\male}=0,
-\ \hat{q}=\frac{1}{2} - \alpha_\Delta^\male \frac{ w_{Aa}^{\male} \phi}{w_{Aa}^{\male} \phi+ w_{aa}^{\male} \psi},\\
+\ \hat{q}=\frac{1}{2}\left(1 - \alpha_\Delta^\male \frac{ w_{Aa}^{\male} \phi}{w_{Aa}^{\male} \phi+ w_{aa}^{\male} \psi}\right),\\
 &\hat{p}_{X}^{\female}=\frac{w_{a}^{\female} \phi}{w_{a}^{\female} \phi+ w_{A}^{\female} \psi},
-\ \hat{p}_{X}^{\male}=\frac{(1+\alpha_\Delta^\male)w_{Aa}^{\male} \phi}{(1+\alpha_\Delta^\male)w_{Aa}^{\male} \phi +w_{AA}^{\male} \psi} \nonumber \\
+\ \hat{p}_{X}^{\male}=\frac{(1+\alpha_\Delta^\male)w_{Aa}^{\male} \phi}{(1+\alpha_\Delta^\male)w_{Aa}^{\male} \phi +w_{aa}^{\male} \psi} \nonumber \\
 (A')\ \ \ &\hat{p}_{Y}^{\male}=1,
-\ \hat{q}=\frac{1}{2} + \alpha_\Delta^\male \frac{w_{Aa}^{\male} \phi'}{w_{Aa}^{\male} \phi' + w_{AA}^{\male} \psi'},\\
+\ \hat{q}=\frac{1}{2}\left(1 + \alpha_\Delta^\male \frac{w_{Aa}^{\male} \phi'}{w_{Aa}^{\male} \phi' + w_{AA}^{\male} \psi'}\right),\\
 &\hat{p}_{X}^{\female}=1-\frac{w_{A}^{\female} \phi'}{w_{A}^{\female} \phi'+ w_{a}^{\female} \psi'},
-\ \hat{p}_{X}^{\male}=1-\frac{(1-\alpha_\Delta^\male)w_{Aa}^{\male} \phi'}{(1-\alpha_\Delta^\male)w_{Aa}^{\male} \phi'+w_{aa}^{\male} \psi'} \nonumber \\
+\ \hat{p}_{X}^{\male}=1-\frac{(1-\alpha_\Delta^\male)w_{Aa}^{\male} \phi'}{(1-\alpha_\Delta^\male)w_{Aa}^{\male} \phi'+w_{AA}^{\male} \psi'} \nonumber \\
 (B)\ \ \ &\hat{p}_{Y}^{\male}=0,\ \hat{p}_{X}^{\female}=1,\ \hat{p}_{X}^{\male}=1, \ \hat{q}=(1 -\alpha^\male_\Delta)/2\\
@@
 Stability of a polymorphism on the X chromosome (equilibrium $A$) further requires that $\phi >0$ and $\psi >0$. 
-Fixation of the $a$ allele on the X (equilibrium $B$) can be stable only if equilibrium $(A)$ is not, as it requires $\psi<0$ and $2w_{A}^{\female}w_{AA}^{\female}>(1-\alpha_\Delta^{\female})w_{a}^{\female}w_{Aa}^{\female}$ or just $4w_{A}^{\female}w_{AA}^{\female}<(1-\alpha_\Delta^{\female})w_{a}^{\female}w_{Aa}^{\female}$ (which also prevents $\psi>0$).
+Fixation of the $a$ allele on the X (equilibrium $B$) can be stable only if equilibrium $(A)$ is not, as it requires $\psi<0$.
+%and $2w_{A}^{\female}w_{AA}^{\female}>(1-\alpha_\Delta^{\female})w_{a}^{\female}w_{Aa}^{\female}$ or just $4w_{A}^{\female}w_{AA}^{\female}<(1-\alpha_\Delta^{\female})w_{a}^{\female}w_{Aa}^{\female}$ (which also prevents $\psi>0$).
 

### 2017-11-09 LaTeX/Turnover.tex
working out neo W invasion from equilA

@@
 
-For tight linkage between the ancestral sex-determining locus and the selected locus we can calculate each of these terms exactly, while for weak selection we take a Taylor series of the leading eigenvalue.
-With weak selection, the leading eigenvalue, $\lambda$, for any $k$, is given up to order $\epsilon^2$ by equation \eqref{eq:lambda_ESD_k}.
+The general conditions for the invasion of a neo-sex-determining allele are given in the main text, in terms of the growth rates of the mutant haplotypes in the absence of recombination ($\lambda_{mi}$) and the rate that recombination destroys them ($\chi_{mi}$).
+For tight linkage between the ancestral sex-determining locus and the selected locus we can calculate these terms explicitly (see below).
+For weak selection we can take a Taylor series of the leading eigenvalue. 
+The leading eigenvalue, $\lambda$, for any $k$, is given up to order $\epsilon^2$ by equation \eqref{eq:lambda_ESD_k}.
 
@@
 \begin{align}
-\lambda_{mA}&= \left[w_{a}^\male (1-\alpha^\male_\Delta) \right]^{-1}
+\lambda_{mA}&= \left[w_{A}^\male (1+\alpha^\male_\Delta) \right]^{-1}
 \frac{w_{A}^\female }{w_{A}^\female}
@@
 { 2w_{AA}^\female } \\
-\lambda_{ma}&= \left[w_{a}^\male (1-\alpha^\male_\Delta) \right]^{-1}
+\lambda_{ma}&= \left[w_{A}^\male (1+\alpha^\male_\Delta) \right]^{-1}
 \frac{w_{a}^\female}{w_{A}^\female}
@@
 { 2w_{AA}^\female } \\
-\chi_{mA}&= \frac{1}{2} \left[w_{a}^\male (1-\alpha^\male_\Delta) \right]^{-1}
+\chi_{mA}&= \frac{1}{2} \left[w_{A}^\male (1+\alpha^\male_\Delta) \right]^{-1}
 \frac{w_{A}^\female }{w_{A}^\female}
@@
 { w_{AA}^\female } \frac{R}{2}\\
-\chi_{ma}&= \frac{1}{2} \left[w_{a}^\male (1-\alpha^\male_\Delta) \right]^{-1}
+\chi_{ma}&= \frac{1}{2} \left[w_{A}^\male (1+\alpha^\male_\Delta) \right]^{-1}
 \frac{w_{a}^\female}{w_{A}^\female}
@@
 Firstly, the zygotic sex ratio becomes male biased, $\zeta>1/2$, when the $a$ allele (which is fixed on the Y) is favoured during competition among male gametes or by meiotic drive in males.
-Specifically, at equilibrium $(B)$, the sex ratio is $\zeta = w_a^\male (1-\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$ where $2\bar{w}_{H}^\male= \big[w_a^\male (1-\alpha^\male_\Delta) +  w_A^\male (1+\alpha^\male_\Delta) \big]$ has been canceled out in equations \eqref{Binvasion} to leave the term $\left[w_{a}^\male (1-\alpha^\male_\Delta) \right]^{-1}$.
+Specifically, at equilibrium $(B)$, the fraction female is $1 - \zeta = w_A^\male (1+\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$ where $2\bar{w}_{H}^\male= \big[w_a^\male (1-\alpha^\male_\Delta) +  w_A^\male (1+\alpha^\male_\Delta) \big]$ has been canceled out in equations \eqref{Binvasion} to leave the term $\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]^{-1}$.
 Male biased sex ratios facilitate the spread of a neo-W because neo-W alleles cause the zygotes that carry them to develop as the rarer, female, sex.
@@
 \begin{align}
-\lambda_{mA}&= \frac{a}{b} \left[w_{AA}^\female w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi +  w_{Aa}^\female (1+\alpha^\female_\Delta) w_a^\male \frac{c}{d}\right] / (2 w_a^\female) \\
-\lambda_{ma}&= \frac{a}{b} \left[ w_{Aa}^\female (1-\alpha^\female_\Delta) w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi +  w_{aa}^\female w_a^\male \frac{c}{d}\right] / (2 w_A^\female) \\
-\chi_{mA}&= \frac{a}{b} \frac{R}{2} \left[   w_{Aa}^\female (1+\alpha^\female_\Delta) w_a^\male \frac{c}{d} \right] / w_a^\female\\ 
+\lambda_{mA}&= \frac{a}{b} \left[w_{AA}^\female w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi +  w_{Aa}^\female (1+\alpha^\female_\Delta) w_a^\male c \right] / (2 w_a^\female) \\
+\lambda_{ma}&= \frac{a}{b} \left[ w_{Aa}^\female (1-\alpha^\female_\Delta) w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi +  w_{aa}^\female w_a^\male c \right] / (2 w_A^\female) \\
+\chi_{mA}&= \frac{a}{b} \frac{R}{2} \left[   w_{Aa}^\female (1+\alpha^\female_\Delta) w_a^\male c \right] / w_a^\female\\ 
 \chi_{ma}&= \frac{a}{b} \frac{R}{2} \left[ w_{Aa}^\female (1-\alpha^\female_\Delta) w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi \right] / w_A^\female
@@
 a &= w_a^\female \phi + w_A^\female \psi \\
-b &= w_{AA}^\female \phi \left[ w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi \right]+ w_{Aa}^\female \psi \left[ w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi + w_{AA}^\male w_a^\male \psi \right] + w_{aa}^\female \psi \left( w_{AA}^\male w_a^\male \psi \right)\\
+b &= w_{AA}^\female \phi \left[ w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi \right] + w_{Aa}^\female \psi \left[ w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) + w_{aa}^\male w_a^\male \right] \phi + w_{aa}^\female \psi \left( w_{aa}^\male w_a^\male \psi \right)\\
 %c &= w_{Aa}^\male (1-\alpha^\male_\Delta) \phi \left[ w_{Aa}^\male (1+\alpha^\male_\Delta) \phi \right] + w_{Aa}^\male\phi \left[ 2w_{AA}^\male + w_{aa}^\male (1+\alpha^\male_\Delta) \right] \psi + w_{aa}^\male \psi \left(2w_{AA}^\male \psi \right) \\
-c &= 
-w_{Aa}^\male (1+\alpha^\male_\Delta) \phi \left[ w_{Aa}^\male (1-\alpha^\male_\Delta) \phi + w_{aa}^\male \psi \right] +
-2 w_{AA}^\male\psi \left[ w_{Aa}^\male \phi + w_{aa}^\male \psi \right]
- \\
-d &= w_{Aa}^\male (1+\alpha^\male_\Delta) \phi + w_{aa}^\male \psi
+c &= w_{Aa}^\male (1-\alpha^\male_\Delta) \phi + 2w_{aa}^\male \psi
 \end{align}

### 2017-11-10 LaTeX/Turnover.tex
weak selection invasion almost compilied

@@
 a &= w_a^\female \phi + w_A^\female \psi \\
-b &= w_{AA}^\female \phi \left[ w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi \right] + w_{Aa}^\female \psi \left[ w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) + w_{aa}^\male w_a^\male \right] \phi + w_{aa}^\female \psi \left( w_{aa}^\male w_a^\male \psi \right)\\
+b &= w_{AA}^\female \left[ w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \right] \phi^2 + w_{Aa}^\female \left[ w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) + w_{aa}^\male w_a^\male \right] \psi \phi + w_{aa}^\female \left( w_{aa}^\male w_a^\male \right) \psi^2\\
 %c &= w_{Aa}^\male (1-\alpha^\male_\Delta) \phi \left[ w_{Aa}^\male (1+\alpha^\male_\Delta) \phi \right] + w_{Aa}^\male\phi \left[ 2w_{AA}^\male + w_{aa}^\male (1+\alpha^\male_\Delta) \right] \psi + w_{aa}^\male \psi \left(2w_{AA}^\male \psi \right) \\
@@
 \begin{equation}\label{eq:BeqWAspread}
-2(w_{Aa}^\female-w_{aa}^\female)w_{AA}^\male \psi^2 > (w_{AA}^\female-w_{Aa}^\female)w_{Aa}^\male \phi (\phi-\psi)
+2(w_{Aa}^\female-w_{aa}^\female)w_{aa}^\male \psi^2 > (w_{AA}^\female-w_{Aa}^\female)w_{Aa}^\male \phi (\phi-\psi)
 \end{equation}
@@
 \begin{equation}\label{eq:BeqWaspread}
-(w_{aa}^\female + w_{Aa}^\female-2w_{AA}^\female)w_{Aa}^\male \phi^2 + (w_{aa}^\female-w_{Aa}^\female)(w_{Aa}^\male+2w_{AA}^\male) \phi \psi >0
+(w_{aa}^\female + w_{Aa}^\female-2w_{AA}^\female)w_{Aa}^\male \phi^2 + (w_{aa}^\female-w_{Aa}^\female)(w_{Aa}^\male+2w_{aa}^\male) \phi \psi >0
 \end{equation}
@@
 
+\textcolor{blue}{is this specific in any way to tight linkage, $r\approx0$?}
+
 Generally, haploid selection expands the scenarios under which neo-W alleles can spread. 
-For example, when selection is sexually-antagonistic in diploids ($s^\female s^\male <0$ and $0<h^\Hermaphrodite<1$) an unlinked neo-W ($R=1/2$) cannot invade unless there is also haploid selection, c.f., Figure \ref{fig:SexAntagTighter} and Figure \ref{fig:SexAntagTighterMaleDrive}.
-Secondly, with haploid selection, overdominance ($w_{aa}^\Hermaphrodite<w_{Aa}^\Hermaphrodite$ \& $w_{AA}^\Hermaphrodite<w_{Aa}^\Hermaphrodite$) is not required for neo-W-$a$ haplotypes to spread ($\lambda_{ma}>1$), Figures \ref{fig:regionMaleDrive}-\ref{fig:regionFemaleGS}.
+For example, when selection is sexually-antagonistic in diploids ($s^\female s^\male <0$ and $0<h^\Hermaphrodite<1$) an unlinked neo-W ($R=1/2$) cannot invade unless there is also haploid selection (Figures \ref{fig:SexAntagTighter} and \ref{fig:SexAntagTighterMaleDrive}).
+Secondly, with haploid selection, overdominance ($w_{aa}^\Hermaphrodite<w_{Aa}^\Hermaphrodite$ \& $w_{AA}^\Hermaphrodite<w_{Aa}^\Hermaphrodite$) is not required for neo-W-$a$ haplotypes to spread ($\lambda_{ma}>1$) (Figures \ref{fig:regionMaleDrive}-\ref{fig:regionFemaleGS}).
 Finally, haploid selection can maintain a polymorphism in the face of directional selection in male and female diploids (ploidally-antagonistic selection). 
-When selection is ploidally-antagonistic, neo-W alleles often spread, for at least some values of $R$, Figure \ref{fig:regionPloidAntag}.
+When selection is ploidally-antagonistic, neo-W alleles often spread, for at least some values of $R$ (Figure \ref{fig:regionPloidAntag}).
 

### 2017-11-11 LaTeX/Turnover.tex
working out special cases for weak selection

@@
 \begin{equation}
-\lambda_{Y',XY} =1+ V_{A}S_{A}^2\frac{ \left( r-R \right) }{r R}+O\left(\epsilon^3 \right) 
+\lambda_{Y',XY} =1+ \frac{1}{4}V_{A}S_{A}^2\frac{ \left( r-R \right) }{r R}+O\left(\epsilon^3 \right) 
 \label{eq:lambda_neoY}
@@
 The diploid selection term, $D^\Hermaphrodite=\big{[} \bar{p}s^\Hermaphrodite+(1-\bar{p})h^\Hermaphrodite s^\Hermaphrodite\big{]} -\big{[} \bar{p}h^\Hermaphrodite s^\Hermaphrodite+(1-\bar{p}) \big{]}$, is the difference in fitness between $A$ and $a$ alleles in diploids of sex $\Hermaphrodite \in \{\female,\male\}$, where $\bar{p}$ is the leading-order probability of mating with an $A$-bearing gamete from the opposite sex (equation \ref{eq:pAve}).
-The difference in $A$-allele-frequency among Y-bearing sperm versus X-bearing sperm is given by $\hat{p}^\male_Y-\hat{p}^\male_X=V_{A}\big{(}D^\male - D^\female+\alpha_{\Delta}^\male-\alpha_{\Delta}^\female+t^\male-t^\female\big{)}(1-2r)/2r$.
+The difference in $A$-allele-frequency among Y-bearing sperm versus X-bearing sperm is given by $\hat{p}^\male_Y-\hat{p}^\male_X=V_{A}\big{(}D^\male - D^\female+\alpha_{\Delta}^\male-\alpha_{\Delta}^\female+t^\male-t^\female\big{)}(1-2r)/(2r)$.
 
@@
 Firstly, if the \textbf{A} locus is unlinked to the ancestral sex-determining region ($r=1/2$), a more closely linked neo-W ($R<1/2$) can always invade because there is no ancestral association between $A$ alleles and sex chromosomes in males, $\left( \hat{p}^\male_Y-\hat{p}^\male_X \right)=0$, see equation \eqref{eq:freq_diffs}.
-The second term in equation \eqref{eq:lambda_neoW} therefore disappears and invasion depends only on the sign of $(r-R)$. 
+The second term in equation \eqref{eq:lambda_neoW} therefore disappears and invasion depends only on the sign of $(r-R)$, as in the case of the neo-Y. 
 Indeed, invasion typically occurs when the neo-W is more closely linked to the selected locus than the ancestral sex-determining region (Figure \ref{fig:Combination_Centimorgans}).
@@
 \begin{split}
-\lambda_{ESD',XY} =& 1 + (1-2k)^2V_{A}{S_{A}}^2\frac{r-R}{r R} \\
-&+\frac{k(\hat{p}^\male_Y-\hat{p}^\male_X)}{2}\left[ k \left(2\alpha_{\Delta}^\male-2\alpha_{\Delta}^\female+t^\male-t^\female \right) -4(1-k)S_{A}\right]+O\left(\epsilon^3\right),
+\lambda_{ESD',XY} =& 1 + \frac{(1-2k)^2}{4}V_{A}{S_{A}}^2\frac{r-R}{r R} \\
+&+\frac{k(\hat{p}^\male_Y-\hat{p}^\male_X)}{2}\left[ k \left(2\alpha_{\Delta}^\male-2\alpha_{\Delta}^\female+t^\male-t^\female \right) -2(1-k)S_{A}\right]+O\left(\epsilon^3\right),
 \end{split}

### 2017-11-12 LaTeX/Turnover.tex
all text results compiled except discussion and figures

@@
 
-The green curves in Figure \ref{fig:SexRatioBad} shows transitions between male and female heterogametey even though the new sex-determining region is unlinked to a locus that experiences haploid and diploid selection.
+The green curves in Figure \ref{fig:SexRatioBad} show transitions between male and female heterogametey even though the new sex-determining region is unlinked to a locus that experiences haploid and diploid selection.
 We use these green curves to discuss why heterogametic transitions can occur when $R=1/2$ and $r<1/2$, as in Table \ref{tab:specialcases}.
@@
 In Figure \ref{fig:SexRatioBad}A, an unlinked neo-Y spreads despite the fact that the ancestral zygotic sex ratio is even. 
-In this case, the the male meiotic drive allele, $a$, is initially more common among ancestral-Z-bearing eggs than ancestral-W-bearing eggs because the Z is found in males more often than the W ($\hat{p}_{W}^\female-\hat{p}_{Z}^\female>0$, equation \ref{eq:freq_diffs}).
+In this case, the male meiotic drive allele, $a$, is initially more common among ancestral-Z-bearing eggs than ancestral-W-bearing eggs because the Z is found in males more often than the W ($\hat{p}_{W}^\female-\hat{p}_{Z}^\female>0$, equation \ref{eq:freq_diffs}).
 %In this case, the ancestral male determining allele, Z, is initially associated with the male meiotic drive allele, $a$, because the Z is found in males more often than the W and $r<1/2$. 
@@
 A freely recombining neo-Y ($R=1/2$) is equally likely to be segregate with the $A$ or $a$ allele and is therefore unaffected by male meiotic drive.
-Thus, a key factor in explaining why heterogametic transitions can occur when $R>r$ is that that the neo-SDR determines sex in the diploid phase but recombination occurs before any subsequent haploid selection.
+Thus, a key factor in explaining why heterogametic transitions can occur when $R>r$ is that the neo-SDR determines sex in the diploid phase but recombination occurs before any subsequent haploid selection.
 

### 2017-11-16 LaTeX/Turnover.tex
fig 2 and 3 done

@@
 \centering
-\centerline{\includegraphics[width=1.25\linewidth]{Region_plot_combined_Mike}}
+%\centerline{\includegraphics[width=1.25\linewidth]{Region_plot_combined_Mike}}
+\centerline{\includegraphics[width=1.25\linewidth]{Region_plot_combined}}
 \caption{
@@
 \centering
-\includegraphics[width=\linewidth]{PositionPlot_8}
+\includegraphics[width=\linewidth]{PositionPlot}
 \caption{
@@
 In panel A, male drive ($\alpha^\male_{\Delta} = -1/20$, $t^\Hermaphrodite = \alpha^\female_{\Delta} = 0$) opposes selection in diploids (no sex-differences: $s^\Hermaphrodite = 1/10$, $h^\Hermaphrodite = 7/10$), in which case the neo-sex-determining allele can invade regardless of linkage.
-In panel B, gametic competition in males ($t^\male = -1/10$, $t^\female = \alpha^\Hermaphrodite_{\Delta} = 0$) opposes selection in diploids (sex-differences: $s^\male = 1/20$, $s^\female = 3/20$, $h^\Hermaphrodite = 7/10$), in which case the neo-sex-determining allele can once again invade regardless of linkage.
+In panel B, gametic competition in males ($t^\male = -1/10$, $t^\female = \alpha^\Hermaphrodite_{\Delta} = 0$) opposes selection in diploids (sex-differences: $s^\male = 3/20$, $s^\female = 1/20$, $h^\Hermaphrodite = 7/10$), in which case the neo-sex-determining allele can once again invade regardless of linkage.
 We use Haldane's map function \citep[Equation 3 in ][]{Haldane1919} to convert from map distance (centiMorgans, cM) to the probability of recombination (an odd number of cross-over events).   

### 2017-11-18 LaTeX/Turnover.tex
fig 1-3 done-ish
compiled up to fig s3

@@
 \centering
-\centerline{\includegraphics[width=1.5\linewidth]{PositionPlot_SexAntagTighter_Mike}}
+\centerline{\includegraphics[width=1.5\linewidth]{PositionPlot_SexAntagTighter}}
 \caption{
@@
 \centering
-\includegraphics[width=\linewidth]{Temporal_SR_Mike}
+\includegraphics[width=\linewidth]{Temporal_SR}
 \caption{
@@
 \centering
-\centerline{\includegraphics[width=\linewidth]{PositionPlot_Overdominance_Mike}}
+\centerline{\includegraphics[width=\linewidth]{PositionPlot_Overdominance}}
 \caption{
@@
 There is no haploid selection $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
-These parameters are marked by daggers in Figure \ref{fig:regionplots}B and C, which show that neo-W invasion is expected for any $R$ ($\lambda_{WA},\lambda_{Wa}>1$) when the $a$ allele is nearly fixed on the Y (black lines in this figure).
+These parameters are marked by daggers in Figure \ref{fig:regionplots}B and C, which show that neo-W invasion is expected for any $R$ ($\lambda_{WA},\lambda_{Wa}>1$) when the $a$ allele is nearly fixed on the Y (black lines in this figure; not stable for $r>>0$).
 Equilibria where the $A$ allele is more common among Y-bearing male gametes can also be stable and allow neo-W invasion for these parameters (blue lines). 
-The weak selection approximation holds when all recombination rates are large relative to selection (around 0 in panels A and C), in which case, in the absence of haploid selection, neo-W alleles should spread only if they are more tightly linked to the selected locus (positive invasion fitness if and only if the selected locus is in the grey region).
-However, when linkage is tight (panels C and D and when the selected locus is near the SDR in all panels), this prediction breaks down. 
+The weak selection approximation holds when all recombination rates are large relative to selection (around 0 in panels A and C), in which case, in the absence of haploid selection, neo-W alleles should spread if and only if they are more tightly linked to the selected locus (positive invasion fitness if and only if the selected locus is in the grey region).
+However, when linkage is tight (panels B and D and when the selected locus is near the SDRs in all panels), this weak selection prediction can break down. 
 }
@@
 \centering
-\centerline{\includegraphics[width=\linewidth]{Temporal_Overdominance_Mike}}
+\centerline{\includegraphics[width=\linewidth]{Temporal_Overdominance}}
 \caption{
@@
 Panels A, C and D show cases where a steady state is reached with the neo-W at a frequency below $0.5$, in which case ancestral-X and Y alleles also both segregate. 
-In all cases, we assume that the $a$ allele is initially more common that the $A$ allele on the Y (Y-$a$ is fixed when $r=0$). 
+In all cases, we assume that the $a$ allele is initially more common than the $A$ allele on the Y (Y-$a$ is fixed when $r=0$). 
 When $r>0$ (panels B and D), Y-$A$ haplotypes created by recombination can become more common than Y-$a$ haplotypes as the neo-W spreads.
-In B, this leads to loss of the neo-W and the system goes to an equilibrium with X-$a$ and Y-$A$ haplotypes fixed (A'), such that all females have the high fitness genotype $aa$ and all males $Aa$. 
-For the parameters in B, neo-W alleles have negative invasion fitness when the Y-$A$ haplotype is ancestrally more common than Y-$a$ (see blue line in Figure \ref{fig:temporalOverdominance}A and  \ref{fig:temporalOverdominance}B).
-In contrast, the neo-W is not lost in panel D (see blue line in Figure \ref{fig:temporalOverdominance}C and  \ref{fig:temporalOverdominance}D). 
-Fitness parameters are the same as in Figure \ref{fig:temporalOverdominance}, the $a$ allele is favoured in females ($w_{aa}^\female=1.05$, $w_{Aa}^\Hermaphrodite=1$, $w_{AA}^\female=0.85$) and there is overdominant selection in males ($w_{aa}^\male=w_{AA}^\male=0.75$) in panels A and B.
-In panels C and D, selection in males and females is overdominant ($w_{aa}^\female=w_{AA}^\female=0.6$, $w_{aa}^\male=0.5$, $w_{AA}^\male=0.7$, $w_{Aa}^\Hermaphrodite=1$). 
+In B, this leads to loss of the neo-W and the system goes to an equilibrium with X-$a$ and Y-$A$ haplotypes fixed (equilibrium $A'$), such that all females have the high fitness genotype $aa$ and all males are $Aa$.
+For the parameters in B, neo-W alleles have negative invasion fitness when the Y-$A$ haplotype is ancestrally more common than Y-$a$ (see blue lines in Figure \ref{fig:positionOverdominance}A and  \ref{fig:positionOverdominance}B near the ancestral SDR).
+In contrast, the neo-W is not lost in panel D as it is favoured near $r\approx0$ (see blue lines in Figure \ref{fig:positionOverdominance}C and  \ref{fig:positionOverdominance}D near the ancestral SDR).
+Fitness parameters are the same as in Figure \ref{fig:positionOverdominance}; in panels A and B the $a$ allele is favoured in females ($w_{aa}^\female=1.05$, $w_{Aa}^\Hermaphrodite=1$, $w_{AA}^\female=0.85$) while there is overdominance in males ($w_{aa}^\male=w_{AA}^\male=0.75$) and in panels C and D, there is overdominance in both sexes ($w_{aa}^\female=w_{AA}^\female=0.6$, $w_{aa}^\male=0.5$, $w_{AA}^\male=0.7$, $w_{Aa}^\Hermaphrodite=1$).
 These parameters are marked by a dagger in Figure \ref{fig:regionplots}. 
@@
 \centering
-\centerline{\includegraphics[width=1.5\linewidth]{PositionPlot_SexAntagTighter_MaleDrive_Mike}}
+\centerline{\includegraphics[width=1.5\linewidth]{PositionPlot_SexAntagTighter_MaleDrive}}
 \caption{

### 2017-11-21 LaTeX/Turnover.tex
need to check invasion regions are real with invasionplotXY

@@
 \centering
-\centerline{\includegraphics[width=\linewidth]{Region_Plot_combined_MaleDrive_Mike}}
+\centerline{\includegraphics[width=\linewidth]{Region_Plot_combined_MaleDrive}}
 \caption{
@@
 By contrast, $\lambda_{WA}$ and $\lambda_{Wa}$ tend to be reduced when meiotic drive in males favours the $A$ allele ($\alpha_{\Delta}^\male=0.16$), panels D-F. 
-We consider three forms of selection in females: directional selection in favour of the $A$ allele (panels A and D, $w_{aa}^\female=0.85$, $w_{AA}^\female=1.05$), direction selection in favour of the $a$ allele (panels B and E, $w_{aa}^\female=1.05$, $w_{AA}^\female=0.85$), and overdominance (panels C and F, $w_{aa}^\female=0.6$, $w_{AA}^\female=0.6$).
+We consider three forms of selection in females: directional selection in favour of the $A$ allele (panels A and D, $w_{aa}^\female=0.85$, $w_{AA}^\female=1.05$), direction selection in favour of the $a$ allele (panels B and E, $w_{aa}^\female=1.05$, $w_{AA}^\female=0.85$), and overdominance (panels C and F, $w_{aa}^\female=w_{AA}^\female=0.6$).
 %\textcolor{red}{Panel F mislabelled, should have $\lambda_{Wa}>1$ \& $\lambda_{WA}<1$ as the upper label that has the line.}
@@
 \centering
-\centerline{\includegraphics[width=\linewidth]{Region_Plot_combined_MaleGS_Mike}}
+\centerline{\includegraphics[width=\linewidth]{Region_Plot_combined_MaleGS}}
 \caption{
@@
 \centering
-\centerline{\includegraphics[width=\linewidth]{Region_Plot_combined_FemaleDrive_Mike}}
+\centerline{\includegraphics[width=\linewidth]{Region_Plot_combined_FemaleDrive}}
 \caption{
@@
 \centering
-\centerline{\includegraphics[width=\linewidth]{Region_Plot_combined_FemaleGS_Mike}}
+\centerline{\includegraphics[width=\linewidth]{Region_Plot_combined_FemaleGS}}
 \caption{
-Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is female meiotic drive at a locus that is tightly linked to the ancestral-XY locus.
+Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is female gametic competition at a locus that is tightly linked to the ancestral-XY locus.
 Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in Figure \ref{fig:regionMaleDrive}, \ref{fig:regionMaleGS}, and \ref{fig:regionFemaleDrive}. 
-The $a$ allele is favoured during female gametic competition in females in Panels A-C ($\alpha_{\Delta}^\female=-0.16$), which increases $\lambda_{Wa}$ and decreases $\lambda_{WA}$. 
-The $A$ allele is favoured during gametic competition in panels D-F ($\alpha_{\Delta}^\female=-0.16$), giving the opposite effect on $\lambda_{Wa}$ and $\lambda_{WA}$. 
+The $a$ allele is favoured during female gametic competition in females in Panels A-C ($w_{a}^\female=1.16$, $w_{A}^\female=1$), which increases $\lambda_{Wa}$ and decreases $\lambda_{WA}$. 
+The $A$ allele is favoured during gametic competition in panels D-F ($w_{a}^\female=1$, $w_{A}^\female=1.16$), giving the opposite effect on $\lambda_{Wa}$ and $\lambda_{WA}$. 
 }

### 2017-11-22 LaTeX/Turnover.tex
dealing with param order mistake in sims, fig 1-4 good

@@
 In panel A, male drive ($\alpha^\male_{\Delta} = -1/20$, $t^\Hermaphrodite = \alpha^\female_{\Delta} = 0$) opposes selection in diploids (no sex-differences: $s^\Hermaphrodite = 1/10$, $h^\Hermaphrodite = 7/10$), in which case the neo-sex-determining allele can invade regardless of linkage.
-In panel B, gametic competition in males ($t^\male = -1/10$, $t^\female = \alpha^\Hermaphrodite_{\Delta} = 0$) opposes selection in diploids (sex-differences: $s^\male = 3/20$, $s^\female = 1/20$, $h^\Hermaphrodite = 7/10$), in which case the neo-sex-determining allele can once again invade regardless of linkage.
+In panel B, gametic competition in males ($t^\male = -1/10$, $t^\female = \alpha^\Hermaphrodite_{\Delta} = 0$) opposes selection in diploids (sex-differences: $s^\male = 3/20$, $s^\female = 7/50$, $h^\Hermaphrodite = 7/10$), in which case the neo-sex-determining allele can once again invade regardless of linkage.
 We use Haldane's map function \citep[Equation 3 in ][]{Haldane1919} to convert from map distance (centiMorgans, cM) to the probability of recombination (an odd number of cross-over events).   

### 2017-11-23 LaTeX/Turnover.tex
plots good up to and incl s.8

--- 2017-11-21 LaTeX/Turnover.tex
@@
 When there is sexually-antagonistic selection and haploid selection, a neo-W may invade for any $R$.
-Panel A shows that the invasion fitness of a neo-W is positive where linkage is tight, even when $r<R$ (unshaded region). \textcolor{red}{(remove A?)}
+Panel A shows that the invasion fitness of a neo-W is positive where linkage is tight, even when $r<R$ (unshaded region).
 In panel B, we vary the recombination rate between the neo-W and the selected locus ($R$) for a fixed recombination rate between the ancestral-SDR and the selected locus ($r=0.005$).
 Coloured markers show recombination rates for which the temporal dynamics of neo-W invasion are plotted in panel C (black $R=0.001$, red $R=0.02$, blue $R=0.1$, green $R=0.5$). 
-The diploid selection parameters used in this plot are the same as in Figure \ref{fig:SexAntagTighter}, marked by an asterisk in Figure \ref{fig:regionMaleDrive}A: $w_{AA}^\female=1.05$, $w_{Aa}^\Hermaphrodite=1$, $w_{aa}^\female=0.85$, $w_{AA}^\male=0.85$, $w_{aa}^\male=1.05$, $\alpha_{\Delta}^\male=-0.08$, except that there is also male meiotic drive in favour of the $a$ allele, $\alpha_{\Delta}^\male=-0.08$.
+The diploid selection parameters used in this plot are the same as in Figure \ref{fig:SexAntagTighter}. 
+There is also meiotic drive in males favouring $a$ ($\alpha_{\Delta}^\male=-0.08$), this full set of parameters is marked by an asterisk in Figure \ref{fig:regionMaleDrive}A.
 When $R=0.5$ (green curve), the neo-W does not reach fixation and X,Y,Z, and W alleles are all maintained in the population, see Figure \ref{fig:freqAll}C.
@@
 \centerline{
-\includegraphics[width=\linewidth]{All_plot_combined_PloidAntag_Matt}
+\includegraphics[width=\linewidth]{All_plot_combined_PloidAntag}
 }

### 2017-11-24 LaTeX/Turnover.tex
plots correct, now streamlining styles

@@
 
-\textcolor{blue}{is this specific in any way to tight linkage, $r\approx0$?}
+\textcolor{blue}{is this specific in any way to tight linkage, $r\approx0$? i see most of the plots referred to are tight linkage plots...}
 
@@
 Secondly, with haploid selection, overdominance ($w_{aa}^\Hermaphrodite<w_{Aa}^\Hermaphrodite$ \& $w_{AA}^\Hermaphrodite<w_{Aa}^\Hermaphrodite$) is not required for neo-W-$a$ haplotypes to spread ($\lambda_{ma}>1$) (Figures \ref{fig:regionMaleDrive}-\ref{fig:regionFemaleGS}).
+Haploid selection and overdominance allow unlinked neo-W alleles to invade even when there is tight linkage between the ancestral SDR and the selected locus (Figure \ref{fig:loose_invades_tight}).
 Finally, haploid selection can maintain a polymorphism in the face of directional selection in male and female diploids (ploidally-antagonistic selection). 
@@
 
-\begin{landscape}
+%\begin{landscape}
 \begin{figure}[!h]
@@
 \centerline{
-\includegraphics[width=\linewidth]{Freq_plot_combined_PloidAntag_Matt}
+\includegraphics[width=\linewidth]{Freq_plot_combined_PloidAntag}
 }
@@
 In panel A, there is a complete transition from XY sex determination (XX-ZZ females and XY-ZZ males) to ZW sex determination (YY-ZW females and YY-ZZ males).  
-In panels B-D polymorphism is maintained at both the ancestral XY locus and the neo-ZW locus, such that there are males with genotypes XY-ZZ or YY-ZZ and females with genotypes XX-ZZ, XX-ZW, XY-ZW, or YY-ZW.
+In panels B and C a polymorphism is maintained at both the ancestral XY locus and the neo-ZW locus, such that there are males with genotypes XY-ZZ or YY-ZZ and females with genotypes XX-ZZ, XX-ZW, XY-ZW, or YY-ZW.
 In panel A, selection is ploidally antagonistic with drive in males (parameters as in the green curve in Figure \ref{fig:SexRatioBad}B).
-In panel B, there is overdominance in both sexes (parameters as the green curve in Figure \ref{fig:temporalOverdominance}C).
-In panel C, there is male meiotic drive and sexually-antagonistic selection in diploids (parameters as the green curve in Figure \ref{fig:regionMaleDrive}C).
-\textcolor{red}{(remove D?)}
-Panel D has the same parameters as the red curve in Figure \ref{fig:regionPloidAntag}F, except $r=0$ (ploidy-antagonism with pollen competition).
-In all cases, the initial equilibrium frequency has $a$ near fixed on the Y.
+In panel B, there is overdominance in both sexes and no haploid selection (parameters as in the green curve in Figure \ref{fig:temporalOverdominance}C).
+In panel C, there is sexually-antagonistic selection in diploids with drive in males (parameters as in the green curve in Figure \ref{fig:regionMaleDrive}C).
+%In Panel D there is ploidally-antagonistic selection with haploid competition in males (parameters as in the green curve of Figure \ref{fig:regionPloidAntag}F).
+In all cases, the initial equilibrium frequency has $a$ near fixation on the Y.
 }
@@
 \end{figure}
-\end{landscape}
+%\end{landscape}
+
+\begin{figure}[!h]
+\centering
+\centerline{
+\includegraphics[width=\linewidth]{neoW_invades_tight_loose}
+}
+\caption{
+An unlinked neo-W can invade a perfectly linked system with overdominance or haploid selection.
+Here overdominance leads to a polymorphic sex-determining system.
+Before invasion the population is at equilibrium B.
+Parameters:
+}
+\label{fig:loose_invades_tight}
+\end{figure}
 

### 2017-11-24 LaTeX/Turnover.tex
some text adjustments

@@
 %In addition, when linkage between the ancestral sex-determining locus and a locus under haploid selection is tight, sex ratio biases can be strong such that there is an asymmetry between invasion of ancestrally XY and ancestrally ZW systems because, e.g., haploid selection in males only causes biased zygotic sex ratios in an ancestrally XY system.
-With haploid selection, we again find that transitions between male and female heterogamety can occur even if the new sex-determining region is less closely linked to the locus under selection. 
-Haploid selection in the heterogametic sex can also cause sex ratio biases, which may increase or decrease with the spread of new sex chromosomes. 
+We find that associations with haploid selected loci can drive transitions between sex determination systems, as has been shown for sexually-antagonistic loci. 
+In addition, with haploid selection, transitions between male and female heterogamety can also evolve when linkage with the sex-determining locus is weakened. 
+Haploid selection in the heterogametic sex can cause sex ratio biases, which may increase or decrease with the spread of new sex chromosomes. 
 Thus, transitions between sex-determination systems cannot be simply predicted by selection to equalise the sex-ratio. 
@@
 
-Predominant theories accounting for the spread of new sex-determination systems by selection involve fitness differences between sexes (e.g., sexually antagonistic selection) or sex-ratio selection. 
+Predominant theories accounting for the spread of new sex-determination systems by selection involve fitness differences between sexes (e.g., sexually antagonistic selection) or sex-ratio selection \citep{Blaser2012, Beukeboom:2014vb,vanDoorn2014re}.
 %\citet{Bull:1977wt} shows that direct selection on new sex determination loci can allow them to spread and switch between male and female heterogamety. 
@@
 A smaller proportion of genes are thought to be expressed and selected during competition in animal sperm, although precise estimates are uncertain \citep{Zheng:2001fi,JOSEPH:2004haa,Vibranovski:2010et}.
-Recent studies have demonstrated that sperm competition in animals can alter haploid allele frequencies and increase offspring fitness \citep{Immler:2014im,Alavioon2017}.
+However, recent studies have demonstrated that sperm competition in animals can alter haploid allele frequencies and increase offspring fitness \citep{Immler:2014im,Alavioon2017}.
 
@@
 
-We find that sex-ratio biases caused by haploid selection can exert Fisherian sex-ratio selection upon novel sex-determiners but that their spread is also determined by selection on genetically-associated alleles.
+We find that the spread of novel sex-determiners is influenced by both Fisherian sex-ratio selection and by selection on genetically-associated alleles. 
+%We find that sex-ratio biases caused by haploid selection can exert Fisherian sex-ratio selection upon novel sex-determiners but that their spread is also determined by selection on genetically-associated alleles.
 %Indeed, it is only when haploid-selected loci are tightly linked to the ancestral sex-determining region (and so sex-ratio biases are initially large) that we see an asymmetry between selection for XY to ZW transitions and ZW to XY transitions (e.g., because haploid selection in males only causes biased zygotic sex ratios in an ancestrally XY system).
-Consequently, Fisherian sex ratio selection does not dominate and it is possible for selection on linked alleles to drive turnover between sex-determining systems despite causing increases in sex-ratio bias.
+Surprisingly, Fisherian sex ratio selection does not dominate; it is possible for selection on linked alleles to drive turnover between sex-determining systems despite causing increases in sex-ratio bias.
 In addition to considering haploid selection, another novel development in our model is that we consider loci that are in very tight linkage with the ancestral sex-determining region. 
-We show that transitions between male and female heterogamety can then evolve despite the fact that the neo-sex-determining locus is less closely linked to a locus under selection and therefore disrupts favourable ancestral associations between sex and the alleles favoured in that sex.
+Because sex-determining loci are often found within a region of suppressed recombination, there can be a significant number of tightly linked loci. 
+We find that loci linked with the ancestral sex-determining region can drive transitions in which the heterogametic sex changes, even when the neo-sex-determining locus is less closely linked to loci under selection (either including haploid selection or not).
 %Such transitions are not favoured in models lacking tight linkage and/or haploid selection. 
@@
 First, Fisherian sex-ratio selection will favour the spread of a neo-Y if the ancestral zygotic sex ratio is biased towards females, $\zeta<1/2$ (i.e., the first factor of the $\lambda_{mi}$ is greater than one for a neo-Y and less than one for a neo-W).
-However, the spread of a neo-Y (neo-W) also depends on the male (female) fitness of associated alleles (terms involving equilibrium allele frequencies, $\hat{p}$'s). %, see terms in curly brackets. 
-Second, invasion by a neo-Y (neo-W) allele does not directly depend on the fitness of female (male) diploids (for a given set of equilibrium allele frequencies).
+However, the spread of a neo-Y (neo-W) also depends on the male (female) fitness of associated alleles, see terms involving equilibrium allele frequencies, $\hat{p}$'s.
+%, see terms in curly brackets.
+Second, invasion by a neo-Y (neo-W) allele does not directly depend on the fitness of female (male) diploids. %(for a given set of equilibrium allele frequencies).
 %involve any female (male) diploid selection terms ($w_{g}^{\female}$)
@@
 By contrast, a gamete with a neo-W can pair with an X or Y male gamete, developing into a female, while female gametes without the neo-W can become female (when paired with X) or male (when paired with Y).
-Consequently, the types of females produced differ in the frequency of $A$ alleles they obtain from mating.
+Consequently, the types of females produced differ in the frequency of $A$ alleles they obtain from mating when $\hat{p}_X^\male \neq \hat{p}_Y^\male$.
 %\textcolor{blue}{nice}
@@
 The other neo-Y haplotype will not spread ($\lambda_{mA}<1$) given that the initial equilibrium is stable. 
-Therefore, a neo-Y mutation cannot spread ($\lambda \leq 1$) in an ancestral XY system that is at equilibrium with all selected loci within the non-recombining region around the SDR.
+Therefore, a neo-Y mutation cannot spread ($\lambda \leq 1$) in an ancestral XY system where selected loci are within the non-recombining region around the SDR.
 In essence, through tight linkage with the \textbf{A} locus, the ancestral Y becomes strongly specialized on the allele that has the highest fitness across male haploid and diploid phases. 
@@
 Broadly, this is possible because the ancestral X chromosome is sometimes found in males and is therefore unable to perfectly specialise on the `female-beneficial' allele. 
-For example, when the $a$ allele is favoured in males, a polymorphism of $A$ and $a$ alleles can be maintained on the X despite directional selection in favour of the $A$ allele in females ($s^\female>0$, $0<h^\female<1$).
-When the $a$ allele is strongly favoured on X chromosomes in males ($w_{aa}$ sufficiently large relative to $w_{Aa}$), neo-W-$A$ haplotypes can spread ($\lambda_{mA}>1$), see Figure \ref{fig:regionplots}A.
+For example, when the $a$ allele is favoured in males, a polymorphism of $A$ and $a$ alleles can be maintained on the X despite directional selection in favour of the $A$ allele in females ($s^\female>0$, $0<h^\female<1$), see outlined region in Figure \ref{fig:regionplots}A.
+When the $a$ allele is strongly favoured on X chromosomes in males ($w_{aa}$ sufficiently large relative to $w_{Aa}$), neo-W-$A$ haplotypes can spread ($\lambda_{mA}>1$), see grey region in Figure \ref{fig:regionplots}A.
 In this case the $a$ allele is at high frequency among ancestral XX females due to selection upon the X in males. 
@@
 However, numerical simulations with tight linkage demonstrate that the neo-SDR does not necessarily fix, leading to the stable maintenance of a mixed sex-determining system, in which X, Y, Z, and W alleles all segregate (e.g., Figure \ref{fig:freqAll}B-D).
-Within a species, both feminizing and masculinizing alleles have been reported in houseflies \citep{Macdonald1978}, midges \citep{Thompson1971}, frogs \citep{Ogata:2007jm}, cichlid fish \citep{Ser:2010iq}, tilapia \citep{Lee2004}, sea bass \citep{Vandeputte2007}, and lab-strains of Zebrafish \citep{Liew2012,Wilson2014}.
-For example, in the platyfish (\textit{Xiphophorus maculatus}), X,Y, and W alleles segregate at one locus (or two closely-linked loci) near to potentially sexually-antagonistic genes for pigmentation and sexual maturity \citep{Kallman1965,Kallman1968, Volff2001, Schultheis2006}.
-Our results suggest that several forms of selection on nearby loci (i.e., $r$ and $R$ small) could maintain multiple sex-determining alleles.
 
@@
 Previous research suggests that when the ancestral sex-determining locus is linked to a locus that experiences haploid selection (e.g., meiotic drive), a new, unlinked sex-determining locus invades in order to restore equal sex ratios \citep{Kozielska:2010vm}.
-Consider, for example, the case where the \textbf{A} locus is linked to the ancestral-SDR ($r<1/2$) and experiences meiotic drive in males only (e.g., during spermatogenesis but not during oogenesis, $\alpha^\male_\Delta \neq 0$, $\alpha^\female_\Delta=0$), without gametic competition ($t^\female=t^\male=0$).
+Consider, for example, the case where the \textbf{A} locus is linked to the ancestral-SDR ($r<1/2$) and experiences meiotic drive in males only ($\alpha^\male_\Delta \neq 0$, $\alpha^\female_\Delta=0$), without gametic competition ($t^\female=t^\male=0$).
 In this case, the zygotic sex ratio can be initially biased only if the ancestral sex-determining system is XY (Figure \ref{fig:SexRatioBad}B). 
 %If the ancxestral sex-determining system is ZW, the zygotic sex ratio will be 1:1 because diploid sex is determined by the proportion of Z-bearing versus W-bearing eggs and meiosis in females is fair (Figure \ref{fig:Combination_Turnover}D).
-We might therefore expect a difference in the potential for XY to ZW and ZW to XY transitions. 
+If Fisherian sex ratio selection were dominant, we would expect a difference in the potential for XY to ZW and ZW to XY transitions. 
 However, to leading order with selection weak relative to recombination, we find that sex ratio selection favours the spread of a neo-W (through the first terms in table \ref{tab:haplotype_growth}) by an amount that is equal in magnitude to the fitness effects of alleles associated with new sex-determining alleles (second terms in table \ref{tab:haplotype_growth}).
 Thus, invasion by a neo-W into an XY system and invasion by a neo-Y into a ZW system occur under the same conditions ($\lambda_{Y',XY}=\lambda_{W',ZW}$ and $\lambda_{Y',ZW}=\lambda_{W',XY}$, at least to order $\epsilon^2$).
-For example, in Figure \ref{fig:SexRatioBad}B neo-W alleles invade an ancestrally-XY system where females are initially rare because the ancestral-Y is associated with a male meiotic drive allele.
-However, Figure \ref{fig:SexRatioBad}A shows that a neo-Y can invade an ancestrally-ZW system under the same conditions. 
+For example, in Figure \ref{fig:SexRatioBad}B neo-W alleles invade an ancestral-XY system where females are initially rare.
+However, Figure \ref{fig:SexRatioBad}A shows that a neo-Y can invade an ancestral-ZW system under the same conditions. 
 In fact, where $R<1/2$ the neo-Y becomes associated with the male meiotic drive allele such that the zygotic sex ratio evolves to become biased towards males.
@@
 Polymorphism at the \textbf{A} locus is maintained by counter-selection against the $a$ allele in diploids and therefore ancestral-ZZ males have generally low diploid fitness. 
-The neo-Y spreads because it produces males with high diploid fitness through matings with ancestral-W-bearing female gametes, which are more likely to carry the $A$ allele. 
-A freely recombining neo-Y ($R=1/2$) is equally likely to be segregate with the $A$ or $a$ allele and is therefore unaffected by male meiotic drive.
+The neo-Y spreads because it produces males with high diploid fitness through matings with ancestral-W-bearing female gametes, which are more likely to carry the $A$ allele ($\hat{p}_{W}^\female-\hat{p}_{Z}^\female>0$).
+A freely recombining neo-Y ($R=1/2$) is equally likely to be segregate with the $A$ or $a$ allele.
+Therefore, the neo-Y is unaffected by male meiotic drive against the $A$ alleles that it introduces into males. 
 Thus, a key factor in explaining why heterogametic transitions can occur when $R>r$ is that the neo-SDR determines sex in the diploid phase but recombination occurs before any subsequent haploid selection.
@@
 In addition, we note that ESD may not invade, even if the sex ratio is initially biased (e.g., with drive in males only, $r<1/2$, $h^\female=h^\male$, and $s^\female s^\male<0$, such that $\lambda_{W',XY}<1$, see Table \ref{tab:specialcases}).
+We conclude that, as with neo-W and neo-Y loci, associations with selection loci mean that the evolution of neo-ESD systems is not straightforwardly predicted by selection to balance the zygotic sex ratio.
 
@@
 
+Our results suggest that haploid selected loci that have been involved in driving turnovers between sex-determination systems could occur around the ancestral- or novel-sex-determining regions. 
+%Our results suggest that polymorphic loci that are ancestrally sex-linked and under sex-specific selection could also drive heterogametic transitions between sex-determination systems. 
+%As with sexually-antagonistic selection, the presence of haploid selected loci around ancestral- or novel-sex-determining regions could support their role in sex chromosome turnover.
+In agreement with this hypothesis, a recent transcriptome analysis in \textit{Rumex} shows that Y-linked genes have higher expression in haploid pollen than autosomal genes \textcolor{red}{(check this is accurate)}.
+Interestingly, haploid-expression is also more common on the autosome that is orthologous to the sex chromosomes in closely related species suggesting that new sex chromosomes may have been favoured through their association with haploid selected alleles on these chromosomes \textcolor{red}{(Sandler et al., 2017, Personal Communication)}.
+
 %IDENTIFICATION OF LOCI IN GENOMIC LOCATIONS THAT IMPLICATE THEM IN SEX-CHROMOSOME TURNOVER
@@
 %, particularly because sex-linkage allows sexually-antagonistic selection to maintain polymorphisms under a different and larger parameter space \citep{Rice:1987hs,Jordan:2011fj}.
- In addition, we show haploid selection on loci around either the ancestral- or the novel-sex-determining regions could have had a role in driving sex chromosome turnover. 
-%Our results suggest that polymorphic loci that are ancestrally sex-linked and under sex-specific selection could also drive heterogametic transitions between sex-determination systems. 
-%As with sexually-antagonistic selection, the presence of haploid selected loci around ancestral- or novel-sex-determining regions could support their role in sex chromosome turnover.
-%We note that linkage with sex chromosomes is not, a priori, more permissive to the maintenance of ploidally antagonistic variation \citep{Immler:2012tl}. 
-A recent transcriptome analysis in \textit{Rumex}, suggests a role for gametic competition in the evolution of sex-determination systems, showing that Y-linked genes are have higher expression in haploid pollen than autosomal genes \textcolor{red}{(check this is accurate)}.
-Interestingly, haploid-expression is also more common on the autosome that is orthologous to the sex chromosomes in closely related species suggesting that new sex chromosomes may have been favoured through their association with haploid selected alleles on these chromosomes \textcolor{red}{(Sandler et al., 2017, Personal Communication)}.
+In addition, we find that overdominance and/or sexually-antagonistic selection on sex-linked loci can maintain multiple sex-determining alleles (e.g.
+Figures \ref{fig:freqAll}B and \ref{fig:freqAll}C).
+Within a species, both feminizing and masculinizing alleles have been reported in houseflies \citep{Macdonald1978}, midges \citep{Thompson1971}, frogs \citep{Ogata:2007jm}, cichlid fish \citep{Ser:2010iq}, tilapia \citep{Lee2004}, sea bass \citep{Vandeputte2007}, and lab-strains of Zebrafish \citep{Liew2012,Wilson2014}.
+For example, our results suggest a potential mechanism maintaining multiple sex determining alleles in the platyfish (\textit{Xiphophorus maculatus}), in which X,Y, and W alleles segregate at one locus (or two closely-linked loci) near to potentially sexually-antagonistic genes for pigmentation and sexual maturity \citep{Kallman1965,Kallman1968, Volff2001, Schultheis2006}.
 
 %Limitation 1: DEGENERATE Y
-We assume that sex-determining alleles do not experience direct selection except via their associations with sex and selected alleles.
+We note that we assume that sex-determining alleles do not experience direct selection except via their associations with sex and selected alleles.
 However, in some cases, there may be significant degeneration around the sex-limited allele (Y or W) in the ancestral sex-determining region because recessive deleterious mutations and/or deletions accumulate around the Y or W sex-determining regions \citep{Rice:1996ke,Charlesworth:2000cc,Bachtrog:2006ed,Marais:2008hm}.
@@
 Thus, the dynamics of meiotic drive alleles can be heavily dependent on the interaction between two loci and the recombination rate between them, which in turn can be affected by sex-linkage if there is reduced recombination between sex chromosomes \citep{Hurst:1991uh}.
-Furthermore, in some cases, a driving allele may act by killing any gametes that carry a `target' allele at another locus, in which case there can be fertility effects which can affect the equilibrium frequency of a meiotic drive allele \citep{Holman:2015en}.
+Furthermore, in some cases, a driving allele may act by killing any gametes that carry a `target' allele at another locus, in which case there can be fertility effects that alter the equilibrium frequency of a meiotic drive allele \citep{Holman:2015en}.
 In polygamous mating systems, the intensity of pollen/sperm competition can depend on the density of males available to donate pollen/sperm, which can itself depend on the sex ratio \citep{Taylor:2002wu}.
@@
 In particular, both can select for neo-sex-determining loci that are more loosely linked. 
-In addition, haploid selection alone can cause transitions analogous to those caused by purely sexually-antagonistic selection, eliminating the need for differences in selection between male and female diploids.
+In addition, haploid selection can cause transitions analogous to those caused by purely sexually-antagonistic selection, eliminating the need for differences in selection between male and female diploids.
 Perhaps counterintuitively, transitions involving haploid selection can be driven by sex-ratio selection or cause sex-ratio biases to evolve. 
-We conclude that haploid selection should be considered as a pivotal factor driving transitions between sex-determination systems. 
+We conclude that haploid selection should be considered as a potentially pivotal factor driving transitions between sex-determination systems. 
 Overall, our results suggest several new scenarios under which new sex-determination systems are favoured, which could help to explain why the evolution of sex-determination systems is so dynamic. 
@@
 
-Various forms of selection can maintain a polymorphism at the \textbf{A} locus, including sexually antagonistic selection, overdominance, conflicts between diploid selection and selection upon haploid genotypes \citep[ploidally antagonistic selection,][]{Immler:2012tl}, or a combination of these selective regimes.
-\textcolor{blue}{add reference or say "see below"}
+Various forms of selection can maintain a polymorphism at the \textbf{A} locus, including sexually antagonistic selection, overdominance, conflicts between diploid selection and selection upon haploid genotypes \citep[ploidally antagonistic selection,][]{Immler:2012tl}, or a combination of these selective regimes (see below).
 
@@
 Firstly, the zygotic sex ratio becomes male biased, $\zeta>1/2$, when the $a$ allele (which is fixed on the Y) is favoured during competition among male gametes or by meiotic drive in males.
-Specifically, at equilibrium $(B)$, the fraction female is $1 - \zeta = w_A^\male (1+\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$ where $2\bar{w}_{H}^\male= \big[w_a^\male (1-\alpha^\male_\Delta) +  w_A^\male (1+\alpha^\male_\Delta) \big]$ has been canceled out in equations \eqref{Binvasion} to leave the term $\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]^{-1}$.
+Specifically, at equilibrium $(B)$, female zygote frequency is $1 - \zeta = w_A^\male (1+\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$ where $2\bar{w}_{H}^\male= \big[w_a^\male (1-\alpha^\male_\Delta) +  w_A^\male (1+\alpha^\male_\Delta) \big]$ has been canceled out in equations \eqref{Binvasion} to leave the term $\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]^{-1}$.
 Male biased sex ratios facilitate the spread of a neo-W because neo-W alleles cause the zygotes that carry them to develop as the rarer, female, sex.
@@
 
-The other terms in equations \eqref{Binvasion} are more easily interpreted if we assume that there is no haploid selection in either sex, in which case $\lambda_{mA}>1$ when $w_{Aa}^\female>w_{AA}^\female$ and $\lambda_{ma}>1$ when $(w_{Aa}^\female+w_{aa}^\female)/2>w_{AA}^\female$.
-These conditions cannot be met under purely sexually-antagonistic selection, where $A$ is directionally favoured in females ($w_{AA}^\female>w_{Aa}^\female>w_{aa}^\female$) and $a$ is directionally favoured in males ($w_{AA}^\male>w_{Aa}^\male>w_{aa}^\male$).
+The other terms in equations \eqref{Binvasion} are more easily interpreted if we assume that there is no haploid selection in either sex, in which case $\lambda_{mA}=(w_{AA}^\female+w_{Aa}^\female)/2 w_{AA}^\female$ and $\lambda_{ma}=(w_{aa}^\female+w_{Aa}^\female)/ 2 w_{AA}^\female$.
+Neither haplotype can spread under purely sexually-antagonistic selection, where $A$ is directionally favoured in females ($w_{AA}^\female>w_{Aa}^\female>w_{aa}^\female$) and $a$ is directionally favoured in males ($w_{AA}^\male>w_{Aa}^\male>w_{aa}^\male$).
 Essentially, the X is then already as specialized as possible for the female beneficial allele ($A$ is fixed on the X), and the neo-W often makes daughters with the Y-$a$ haplotype, increasing the flow of $a$ alleles into females, which reduces the fitness of those females.
 
-If selection doesn't uniformly favour $A$ in females, however, neo-W-$A$ haplotypes and/or neo-W-$a$ haplotypes can spread ($\lambda_{mA}>1$ and/or $\lambda_{ma}>1$) at this equilibrium.
+If selection doesn't uniformly favour $A$ in females, however, neo-W-$A$ haplotypes and/or neo-W-$a$ haplotypes can spread ($\lambda_{mA}>1$ and/or $\lambda_{ma}>1$).
 %If $\lambda_{mA}>1$ (requiring $w_{Aa}^\female>w_{AA}^\female$), the implication is that the neo-W can spread alongside the $A$ allele, despite the fact that the neo-W sometimes brings $Y-a$ haplotypes into females, because $a$ is favoured by selection in females despite $A$ being fixed on the X.
-A neo-W can spread alongside the $A$ allele ($\lambda_{mA}>1$), despite the fact that a neo-W brings Y-$a$ haplotypes into females, when $w_{Aa}^\female>w_{AA}^\female$, as stated above.
+A neo-W-$A$ haplotype can spread ($\lambda_{mA}>1$) when $w_{Aa}^\female>w_{AA}^\female$, despite the fact that a neo-W brings Y-$a$ haplotypes into females.
 In this case the $a$ allele is favoured by selection in females despite $A$ being fixed on the X.
-For this equilibrium to be stable (i.e.,  to keep $A$ fixed on the X), X-$a$ cannot be overly favoured in females and X-$A$ must be sufficiently favoured in males (for example, by overdominance in males, remembering that $a$ is fixed on the Y).
+For this equilibrium to be stable (i.e.,  to keep $A$ fixed on the X), X-$a$ cannot be overly favoured in females and X-$A$ must be sufficiently favoured in males (for example, by overdominance in males).
 Specifically, from the stability conditions for equilibrium (B), we must have $w_{Aa}^\female < 2 w_{AA}^\female$ and $w_{Aa}^\male/\big[(w_{aa}^\male+w_{Aa}^\male)/2\big]>w_{Aa}^\female/w_{AA}^\female$.

### 2017-11-24 LaTeX/Turnover.tex
minor change

@@
 
-\textcolor{blue}{is this specific in any way to tight linkage, $r\approx0$? i see most of the plots referred to are tight linkage plots...}
-
-Generally, haploid selection expands the scenarios under which neo-W alleles can spread. 
+With tight linkage, haploid selection generally expands the conditions under which neo-W alleles can spread. 
 For example, when selection is sexually-antagonistic in diploids ($s^\female s^\male <0$ and $0<h^\Hermaphrodite<1$) an unlinked neo-W ($R=1/2$) cannot invade unless there is also haploid selection (Figures \ref{fig:SexAntagTighter} and \ref{fig:SexAntagTighterMaleDrive}).

### 2017-11-29 LaTeX/Turnover.tex
added model outline figure caption and some references to it

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Model Outline
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[!h]
+\centering
+\centerline{\includegraphics[width=\linewidth]{Sex_determination_outline.pdf}}
+\caption{
+Outline of model features. 
+Panel A: Recombination rate parameters between the ancestral-sex-determining locus (here, assumed to have X or Y alleles), a locus under selection (\textbf{A}, with alleles $A$ and $a$), and a neo-sex-determining locus (\textbf{M}, with alleles $M$ and $m$).
+If $r<1/2$, then associations between ancestral-sex-determining alleles (X and Y) and \textbf{A} locus alleles can be maintained past recombination in males.
+Panel B: Haploid selection is often sex-specific, occurring during haploid production or competition in either males or females. 
+For example, haploid selection in males only is represented by the dashed circle.  
+If X or Y alleles are associated with alleles that experience haploid selection in males ($r<1/2$), then zygotic sex ratios can become biased because either X or Y male gametes/gametophytes will be abundant after haploid selection.
+However, the zygotic sex ratio is not biased by male haploid selection in ZW sex-determination systems. 
+Similarly, zygotic sex ratio biases can occur if haploid selected alleles are associated with neo-sex-determining alleles ($M$ and $m$, i.e., if $R<1/2$). 
+Panel C: During homogametic transitions, a neo-Y allele spreads to pseudo-fixation (its maximum frequency among male gametes) and the the ancestral-Y allele is lost. 
+Panel D: During heterogametic transitions, a neo-W allele spreads to pseudo-fixation (its maximum frequency among female gametes) and the ancestral-X allele is lost.
+Neo-W mutations allow Y-associated alleles into females, which may impede or aid their spread.
+}
+\label{fig:model_outline}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 %\textcolor{red}{Change all  $\alpha^\Hermaphrodite$ to $(1+\alpha_{\Delta}^\Hermaphrodite)$.}
@@
 Recombination (i.e., an odd number of cross-overs) occurs between loci \textbf{X} and \textbf{A} with probability $r$, between loci \textbf{A} and \textbf{M} with probability $R$, and between loci \textbf{X} and \textbf{M} with probability $\rho$.
-Any linear order of the loci can be modelled with appropriate choices of $r$, $R$, and $\rho$ (see Table \ref{tab:chisubstitutions}). 
+Any linear order of the loci can be modelled with appropriate choices of $r$, $R$, and $\rho$ (see Figure \ref{fig:model_outline}A and Table \ref{tab:chisubstitutions}). 
 Individuals that are heterozygous at the \textbf{A} locus may experience meiotic drive; a gamete produced by $Aa$ heterozgotes of sex $\Hermaphrodite$ bear allele $A$ with probability $\alpha^\Hermaphrodite$.
@@
 %involve any female (male) diploid selection terms ($w_{g}^{\female}$)
-This is because a dominant neo-Y (neo-W) is always found in males (females), and therefore the frequency of the neo-Y (neo-W) allele, $m$, only changes in males (females). 
+This is because a dominant neo-Y (neo-W) is always found in males (females), and therefore the frequency of the neo-Y (neo-W) allele, $m$, only changes in males (females), Figure \ref{model_outline}C,D.
 %Therefore, invasion by a neo-Y allele does not involve any female diploid selection terms ($w_{g}^{\female}$). 
@@
 Finally, invasions by a neo-Y and a neo-W are qualitatively different.
-This is because a gamete with the ancestral- or neo-Y always pairs with a female gamete containing an X, and both develop into males.
-By contrast, a gamete with a neo-W can pair with an X or Y male gamete, developing into a female, while female gametes without the neo-W can become female (when paired with X) or male (when paired with Y).
+This is because a gamete with the ancestral- or neo-Y always pairs with a female gamete containing an X, and both develop into males, Figure \ref{model_outline}C.
+By contrast, a gamete with a neo-W can pair with an X or Y male gamete, developing into a female, while female gametes without the neo-W can become female (when paired with X) or male (when paired with Y), Figure \ref{fig:model_outline}D.
 Consequently, the types of females produced differ in the frequency of $A$ alleles they obtain from mating when $\hat{p}_X^\male \neq \hat{p}_Y^\male$.
@@
 Again, this occurs because ancestral X's also experience selection in males, in which they will always be paired with a Y-$a$. 
-Hence, if there is overdominance in males, X-$A$ Y-$a$ males have high fitness and the $A$ allele is favoured by selection on the X in males. 
+If there is overdominance in males, X-$A$ Y-$a$ males have high fitness and the $A$ allele is favoured by selection on the X in males. 
 Therefore, the X can be polymorphic or even fixed for the $A$ allele despite favouring the $a$ allele during selection in females \citep[e.g., see outlined region in Figure \ref{fig:regionplots}B and][]{Lloyd1977,Otto2014}.
-In such cases, neo-W-$a$ haplotypes can spread because they create more $Aa$ and $aa$ females when pairing with an X from males and because they bring Y-$a$ haplotypes into females.
+In such cases, neo-W-$a$ haplotypes can spread because they create more $Aa$ and $aa$ females when pairing with an X from males and because they bring Y-$a$ haplotypes into females (Figure \ref{fig:model_outline}D).
 
@@
 An equivalent analysis is not possible where we assume that linkage is tight. 
-However, numerical simulations with tight linkage demonstrate that the neo-SDR does not necessarily fix, leading to the stable maintenance of a mixed sex-determining system, in which X, Y, Z, and W alleles all segregate (e.g., Figure \ref{fig:freqAll}B-D).
+However, numerical simulations with tight linkage demonstrate that the neo-SDR does not necessarily fix, leading to the stable maintenance of a mixed sex-determining system, in which X, Y, Z, and W alleles all segregate (e.g., Figure \ref{fig:freqAll}B,C).
 
@@
 Consider, for example, the case where the \textbf{A} locus is linked to the ancestral-SDR ($r<1/2$) and experiences meiotic drive in males only ($\alpha^\male_\Delta \neq 0$, $\alpha^\female_\Delta=0$), without gametic competition ($t^\female=t^\male=0$).
-In this case, the zygotic sex ratio can be initially biased only if the ancestral sex-determining system is XY (Figure \ref{fig:SexRatioBad}B). 
+In this case, the zygotic sex ratio can be initially biased only if the ancestral sex-determining system is XY (Figure \ref{fig:model_outline}B and Figure \ref{fig:SexRatioBad}B). 
 %If the ancxestral sex-determining system is ZW, the zygotic sex ratio will be 1:1 because diploid sex is determined by the proportion of Z-bearing versus W-bearing eggs and meiosis in females is fair (Figure \ref{fig:Combination_Turnover}D).
@@
 In this figure, selection is ploidally antagonistic with haploid selection favouring the $a$ allele during male meiosis.
-In panel A, male drive in an ancestral ZW system has no affect on the zygotic sex ratio, yet a neo-Y can invade and replace the ancestral sex-determination system (inset shows neo-Y frequency among male gametes, the ancestral W also goes to fixation during this transition).
+In panel A, male drive in an ancestral ZW system has no affect on the zygotic sex ratio (see Figure \ref{fig:model_outline}B) yet a neo-Y can invade and replace the ancestral sex-determination system (inset shows neo-Y frequency among male gametes, the ancestral W also goes to fixation during this transition).
 When $R<1/2$, the neo-Y becomes associated with the allele favoured by drive, causing the zygotic sex ratio to become biased, hence the frequency of neo-Y among male gametes can be higher than $0.5$ (inset).
@@
 In addition, haploid selection can cause transitions analogous to those caused by purely sexually-antagonistic selection, eliminating the need for differences in selection between male and female diploids.
+We conclude that haploid selection should be considered as a pivotal factor driving transitions between sex-determination systems. 
 Perhaps counterintuitively, transitions involving haploid selection can be driven by sex-ratio selection or cause sex-ratio biases to evolve. 
-We conclude that haploid selection should be considered as a potentially pivotal factor driving transitions between sex-determination systems. 
 Overall, our results suggest several new scenarios under which new sex-determination systems are favoured, which could help to explain why the evolution of sex-determination systems is so dynamic. 

### 2017-12-21 LaTeX/Turnover.tex
added information about mixed sex-determination systems in rodents. It seems like the Y causes sex reversed females to have increased fitness

@@
 In addition, many gonochoric clades with genetic sex determination exhibit transitions between male (XY) and female (ZW) heterogamety, including snakes \citep{Gamble2017}, lizards \citep{Ezaz:2009tk}, eight of 26 teleost fish families \citep{Mank:2006bt}, true fruit flies \citep[Tephritids,][]{Vicoso:2015hf}, amphibians \citep{Hillis:1990gu}, the angiosperm genus \textit{Silene} \citep{Slancarova:2013dq}, the angiosperm family \textit{Salicaceae} \citep{Pucholt2015,Pucholt2017} and Coleoptera and Hemiptera \citep[][plate 2]{Beukeboom:2014vb}.
-Indeed, in some cases, both male and female heterogametic sex-determination systems can be found in the same species, as exhibited by some cichlid species \citep{Ser:2010iq} and \textit{Rana rugosa} \citep{Ogata:2007jm, Miura2007}.
+Indeed, in some cases, both male and female heterogametic sex-determination systems can be found in the same species, as reported in houseflies \citep{Macdonald1978}, midges \citep{Thompson1971}, frogs \citep{Ogata:2007jm}, cichlid fish \citep{Ser:2010iq}, tilapia \citep{Lee2004}, sea bass \citep{Vandeputte2007}, and lab-strains of Zebrafish \citep{Liew2012,Wilson2014}.
 In addition, multiple transitions have occurred between genetic and environmental sex-determination systems, e.g., in reptiles and fishes \citep{Conover:1987in,Mank:2006bt,Pokorna:2009ui,Ezaz:2009tk,Pen:2010kk,Holleley:2015hc}.
@@
 In support of their role in sex chromosome turnover, genes expected to be under sexually-antagonistic selection (e.g., those causing bright male colouration) have been found on recently derived sex chromosomes \citep{Lindholm:2002dw,Tripathi:2009cw,Ser:2010iq}.
-Our results show that, if loci experiencing overdominance and/or sexually-antagonistic selection can be identified in close linkage with the ancestral sex-determining locus (rather than only the novel sex-determining locus), then they could also be implicated in driving heterogametic transitions between sex-determination systems.
+Our results show that, if loci experiencing sexually-antagonistic selection and/or overdominance can be identified in close linkage with the ancestral sex-determining locus (rather than only the novel sex-determining locus), then they could also be implicated in driving heterogametic transitions between sex-determination systems and/or maintaining multiple sex-determining alleles.
 %As noted by \citet{vanDoorn:2010hu}, it would be prudent to compare closely related clades in order to determine whether observed polymorphisms predate a transition in sex-determination or arose afterwards.
 %, particularly because sex-linkage allows sexually-antagonistic selection to maintain polymorphisms under a different and larger parameter space \citep{Rice:1987hs,Jordan:2011fj}.
-In addition, we find that overdominance and/or sexually-antagonistic selection on sex-linked loci can maintain multiple sex-determining alleles (e.g.
-Figures \ref{fig:freqAll}B and \ref{fig:freqAll}C).
-Within a species, both feminizing and masculinizing alleles have been reported in houseflies \citep{Macdonald1978}, midges \citep{Thompson1971}, frogs \citep{Ogata:2007jm}, cichlid fish \citep{Ser:2010iq}, tilapia \citep{Lee2004}, sea bass \citep{Vandeputte2007}, and lab-strains of Zebrafish \citep{Liew2012,Wilson2014}.
+%Within a species, both feminizing and masculinizing alleles have been reported in houseflies \citep{Macdonald1978}, midges \citep{Thompson1971}, frogs \citep{Ogata:2007jm}, cichlid fish \citep{Ser:2010iq}, tilapia \citep{Lee2004}, sea bass \citep{Vandeputte2007}, and lab-strains of Zebrafish \citep{Liew2012,Wilson2014}.
 For example, our results suggest a potential mechanism maintaining multiple sex determining alleles in the platyfish (\textit{Xiphophorus maculatus}), in which X,Y, and W alleles segregate at one locus (or two closely-linked loci) near to potentially sexually-antagonistic genes for pigmentation and sexual maturity \citep{Kallman1965,Kallman1968, Volff2001, Schultheis2006}.
+Several rodent species also maintain feminizing alleles along with the ancestral X and Y sex-determination alleles \citep[reviewed in][]{Fredga1994}. 
+For example, in nine \textit{Akadon} species, it appears that \textit{sry} expression is suppressed by an autosomal feminizing allele, creating XY females \citep{Bianchi2002,Sanchez2010}, which have increased fitness relative to XX females \citep{Hoekstra2001}.
+In \textit{Mus microtoides}, females can have XX, XX$^\ast$ or X$^\ast$Y genotypes \citep{Veyrunes2010}. 
+Previous theory would predict that the X$^\ast$ chromosome (or the autosome it is fused to) harbours female beneficial alleles, driving its spread. 
+However, XX and XX$^\ast$ females have similar fitness, whereas X$^\ast$Y female fitness is enhanced \citep{Saunders2014}.
+Although Y-linkage of female-beneficial alleles is counterintuitive, our tight linkage model suggests that it can be stably maintained and then favour new feminizing mutations, which is a parsimonious explanation for the spread of feminizing alleles in these rodent species.
 

### 2017-12-22 LaTeX/Turnover.tex
added information about mixed sex-determination systems in rodents. It seems like the Y causes sex reversed females to have increased fitness
changed to cis-GSD and trans-GSD

@@
 Animals and angiosperms exhibit extremely diverse sex-determination systems \citep[reviewed in][]{Bull:1983vi,Charlesworth:2010it,Beukeboom:2014vb,Bachtrog:2014bx}. 
-Among species with genetic sex determination of diploid sexes, some taxa have heterogametic males (XY) and homogametic females (XX), including %non-monotreme? 
+Among species with genetic sex determination of diploid sexes (GSD), some taxa have heterogametic males (XY) and homogametic females (XX), including %non-monotreme?
+I think monotremes have XY but tonnes of translocations, giving: X1,X2...X6 Y1
 mammals and most dioecious plants \citep{Ming:2011iy}; whereas other taxa have homogametic males (ZZ) and heterogametic females (ZW), including Lepidoptera and birds. 
@@
 I wonder if this is actually a fusion event though?
-In addition, many gonochoric clades with genetic sex determination exhibit transitions between male (XY) and female (ZW) heterogamety, including snakes \citep{Gamble2017}, lizards \citep{Ezaz:2009tk}, eight of 26 teleost fish families \citep{Mank:2006bt}, true fruit flies \citep[Tephritids,][]{Vicoso:2015hf}, amphibians \citep{Hillis:1990gu}, the angiosperm genus \textit{Silene} \citep{Slancarova:2013dq}, the angiosperm family \textit{Salicaceae} \citep{Pucholt2015,Pucholt2017} and Coleoptera and Hemiptera \citep[][plate 2]{Beukeboom:2014vb}.
+In addition, many clades exhibit transitions between male (XY) and female (ZW) heterogamety, including snakes \citep{Gamble2017}, lizards \citep{Ezaz:2009tk}, eight of 26 teleost fish families \citep{Mank:2006bt}, true fruit flies \citep[Tephritids,][]{Vicoso:2015hf}, amphibians \citep{Hillis:1990gu}, the angiosperm genus \textit{Silene} \citep{Slancarova:2013dq}, the angiosperm family \textit{Salicaceae} \citep{Pucholt2015,Pucholt2017} and Coleoptera and Hemiptera \citep[][plate 2]{Beukeboom:2014vb}.
 Indeed, in some cases, both male and female heterogametic sex-determination systems can be found in the same species, as reported in houseflies \citep{Macdonald1978}, midges \citep{Thompson1971}, frogs \citep{Ogata:2007jm}, cichlid fish \citep{Ser:2010iq}, tilapia \citep{Lee2004}, sea bass \citep{Vandeputte2007}, and lab-strains of Zebrafish \citep{Liew2012,Wilson2014}.
-In addition, multiple transitions have occurred between genetic and environmental sex-determination systems, e.g., in reptiles and fishes \citep{Conover:1987in,Mank:2006bt,Pokorna:2009ui,Ezaz:2009tk,Pen:2010kk,Holleley:2015hc}.
+In addition, multiple transitions have occurred between genetic (GSD) and environmental sex-determination (ESD) systems, e.g., in reptiles and fishes \citep{Conover:1987in,Mank:2006bt,Pokorna:2009ui,Ezaz:2009tk,Pen:2010kk,Holleley:2015hc}.
 
@@
 A smaller proportion of genes are thought to be expressed and selected during competition in animal sperm, although precise estimates are uncertain \citep{Zheng:2001fi,JOSEPH:2004haa,Vibranovski:2010et}.
-However, recent studies have demonstrated that sperm competition in animals can alter haploid allele frequencies and increase offspring fitness \citep{Immler:2014im,Alavioon2017}.
+Nevertheless, recent studies have demonstrated that sperm competition in animals can alter haploid allele frequencies and increase offspring fitness \citep{Immler:2014im,Alavioon2017}.
 
@@
 Similarly, zygotic sex ratio biases can occur if haploid selected alleles are associated with neo-sex-determining alleles ($M$ and $m$, i.e., if $R<1/2$). 
-Panel C: During homogametic transitions, a neo-Y allele spreads to pseudo-fixation (its maximum frequency among male gametes) and the the ancestral-Y allele is lost. 
-Panel D: During heterogametic transitions, a neo-W allele spreads to pseudo-fixation (its maximum frequency among female gametes) and the ancestral-X allele is lost.
+Panel C: During cis-GSD transitions (XY to XY or ZW to ZW, without loss of generality we assume ancestral XY sex determination here), a neo-Y allele spreads to pseudo-fixation (its maximum frequency among male gametes) and the the ancestral-Y allele is lost.
+Panel D: During trans-GSD transitions (XY to ZW or ZW to XY), a neo-W allele spreads to pseudo-fixation (its maximum frequency among female gametes) and the ancestral-X allele is lost.
 Neo-W mutations allow Y-associated alleles into females, which may impede or aid their spread.
@@
 %involve any female (male) diploid selection terms ($w_{g}^{\female}$)
-This is because a dominant neo-Y (neo-W) is always found in males (females), and therefore the frequency of the neo-Y (neo-W) allele, $m$, only changes in males (females), Figure \ref{model_outline}C,D.
+This is because a dominant neo-Y (neo-W) is always found in males (females), and therefore the frequency of the neo-Y (neo-W) allele, $m$, only changes in males (females), Figure \ref{fig:model_outline}C,D.
 %Therefore, invasion by a neo-Y allele does not involve any female diploid selection terms ($w_{g}^{\female}$). 
@@
 Finally, invasions by a neo-Y and a neo-W are qualitatively different.
-This is because a gamete with the ancestral- or neo-Y always pairs with a female gamete containing an X, and both develop into males, Figure \ref{model_outline}C.
+This is because a gamete with the ancestral- or neo-Y always pairs with a female gamete containing an X, and both develop into males, Figure \ref{fig:model_outline}C.
 By contrast, a gamete with a neo-W can pair with an X or Y male gamete, developing into a female, while female gametes without the neo-W can become female (when paired with X) or male (when paired with Y), Figure \ref{fig:model_outline}D.
@@
 Nevertheless, because we assume here that $r$ is small, these results indicate that a more loosely linked sex-determining region ($r<R$) can spread.
-Therefore, tightly sex-linked loci that experience sexually-antagonistic selection can drive heterogametic transitions in which the neo-SDR is less closely linked to the locus under selection (Figure \ref{fig:SexAntagTighter}).
+Therefore, tightly sex-linked loci that experience sexually-antagonistic selection can drive trans-GSD transitions in which the neo-SDR is less closely linked to the locus under selection (Figure \ref{fig:SexAntagTighter}).
 %Prediction (just an idea), considering sexually antagonistic selection alone, we should observe an excess of transitions between XY and ZW systems on the same chromosome because the tight linkage results indicate that there can be selection for heterogametic transitions but only when the neo-SDR is relatively closely linked (but not necessarily more closely linked).
@@
 This echoes our tight linkage results above where a neo-Y could never invade if $r\approx0$.
-It is also consistent with the results of \citet{vanDoorn:2007eu}, who considered diploid selection only and also found that homogametic transitions (XY to XY or ZW to ZW) can only occur when the neo-sex-determining locus is more closely linked to a locus under sexually-antagonistic selection.
+It is also consistent with the results of \citet{vanDoorn:2007eu}, who considered diploid selection only and also found that cis-GSD transitions (XY to XY or ZW to ZW) can only occur when the neo-sex-determining locus is more closely linked to a locus under sexually-antagonistic selection.
 %Because tighter linkage between the sex-determining region and a selected locus evolves during these transitions, stronger associations between selected alleles and diploid sexes can build up by selection (e.g., between male-beneficial alleles and the male-determining allele, Y).%, increasing diploid mean fitness (Figure \ref{fig:Combination_MeanFit}).
 
-With weak selection and no haploid selection ($t^\Hermaphrodite=\alpha^\Hermaphrodite_{\Delta}=0$), the spread of a neo-W is equivalent to the spread of a neo-Y ($\lambda_{W',XY}=\lambda_{Y',XY}$), such that heterogametic transitions (XY to ZW or ZW to XY) can also occur only if the neo-sex-determining region is more closely linked to a locus under selection ($R<r$), as found by \citet{vanDoorn:2010hu}.
+With weak selection and no haploid selection ($t^\Hermaphrodite=\alpha^\Hermaphrodite_{\Delta}=0$), the spread of a neo-W is equivalent to the spread of a neo-Y ($\lambda_{W',XY}=\lambda_{Y',XY}$), such that trans-GSD transitions (XY to ZW or ZW to XY) can also occur only if the neo-sex-determining region is more closely linked to a locus under selection ($R<r$), as found by \citet{vanDoorn:2010hu}.
 With haploid selection, however, the additional term in equation \eqref{eq:lambda_neoW} can be positive, which can allow, for example, neo-W invasion ($\lambda_{W',XY}>1$) even when the neo-sex-determining region is less closely linked to the selected locus ($R>r$).
@@
 The green curves in Figure \ref{fig:SexRatioBad} show transitions between male and female heterogametey even though the new sex-determining region is unlinked to a locus that experiences haploid and diploid selection.
-We use these green curves to discuss why heterogametic transitions can occur when $R=1/2$ and $r<1/2$, as in Table \ref{tab:specialcases}.
+We use these green curves to discuss why trans-GSD transitions can occur when $R=1/2$ and $r<1/2$, as in Table \ref{tab:specialcases}.
 In Figure \ref{fig:SexRatioBad}B, an unlinked neo-W can spread because the zygotic sex ratio is ancestrally male biased. 
@@
 Therefore, the neo-Y is unaffected by male meiotic drive against the $A$ alleles that it introduces into males. 
-Thus, a key factor in explaining why heterogametic transitions can occur when $R>r$ is that the neo-SDR determines sex in the diploid phase but recombination occurs before any subsequent haploid selection.
+Thus, a key factor in explaining why trans-GSD transitions can occur when $R>r$ is that the neo-SDR determines sex in the diploid phase but recombination occurs before any subsequent haploid selection.
 
@@
 %The latter predicts that neo-W alleles will invade an XY system when there is a male bias caused by haploid selection in males, and vice-versa, a neo-Y will invade a ZW system when there is a female bias caused by haploid selection in females \citep{Kozielska:2010vm,Ubeda:2015fx}.
-Firstly, we show that selection (including sexually-antagonistic selection) on loci within or near the non-recombining region of the ancestral sex-determining region can favour heterogametic transitions (XY to ZW or ZW to XY) to new sex-determining systems that are less closely linked to the selected loci (e.g., see Figure \ref{fig:SexAntagTighter}).
-Secondly, assuming that selection is weak relative to recombination (`weak selection'), we show that new sex-determining alleles are typically favoured if they are more closely linked to a locus under haploid selection, which is the only condition favouring homogametic transitions (XY to XY or ZW to ZW).
-In addition, with haploid selection and weak selection, heterogametic transitions (XY to ZW or ZW to XY) can occur even when the new sex-determining region is less closely linked to the locus under selection (e.g., see Figure \ref{fig:SexRatioBad}).
+Firstly, we show that selection (including sexually-antagonistic selection) on loci within or near the non-recombining region of the ancestral sex-determining region can favour trans-GSD transitions (XY to ZW or ZW to XY) to new sex-determining systems that are less closely linked to the selected loci (e.g., see Figure \ref{fig:SexAntagTighter}).
+Secondly, assuming that selection is weak relative to recombination (`weak selection'), we show that new sex-determining alleles are typically favoured if they are more closely linked to a locus under haploid selection (even in the absence of diploid sex differences), which is the only condition favouring cis-GSD transitions (XY to XY or ZW to ZW).
+In addition, with haploid selection and weak selection, trans-GSD transitions (XY to ZW or ZW to XY) can occur even when the new sex-determining region is less closely linked to the locus under selection (e.g., see Figure \ref{fig:SexRatioBad}).
 %\textcolor{red}{need to mention sex ratio here}
@@
 %Sex ratio biases caused by gametic competition or meiotic drive have been shown to exert Fisherian sex-ratio selection on various autosomal \citep{Stalker:1961th,Smith:1975ft,Frank:1989vl,Hough:2013uo,Ubeda:2015fx, Otto:2015va} and sex-linked \citep{Kozielska:2010vm} modifiers.
-Sex-ratio biases caused by haploid selection can facilitate heterogametic transitions between sex-determining systems. 
+Sex-ratio biases caused by haploid selection can facilitate trans-GSD transitions between sex-determining systems. 
 For instance, alleles favoured by haploid selection in males often become associated with the Y, which leads to a male-biased zygotic sex-ratio.
@@
 %An asymmetry can develop when sex-linkage is tight (e.g., Figure \ref{fig:Combination_Centimorgans} near -25cM and 25cM) but under most circumstances we do not predict asymmetry between XY to ZW and ZW to XY transitions despite the presence/absence of sex ratio selection.
-Thus, haploid selection can favour heterogametic transitions both via sex-ratio selection %\citep[as predicted by][]{Kozielska:2010vm} 
+Thus, haploid selection can favour trans-GSD transitions both via sex-ratio selection %\citep[as predicted by][]{Kozielska:2010vm} 
 and via fitness effects of alleles that are associated with the neo-sex-determining allele, and these selection pressures are predicted to often be of equal magnitude when selection is weak. 
@@
 Because haploid selection can cause transitions that increase or decrease sex-linkage, haploid selection may lead to less stability, and greater potential for cycling, in sex-determination systems (e.g., the final state of the red line in Figure \ref{fig:SexRatioBad}A is the starting state in Figure \ref{fig:SexRatioBad}B).
-In particular, if haploid selection is strong but selective differences between male and female diploids are weak, we find that heterogametic transitions (XY to ZW or vice versa) are favoured more strongly than homogametic transitions (e.g., with $|D^\male - D^\female| << |\alpha_\Delta^\male - \alpha_\Delta^\female + t^\male - t^\female|$ we have $\lambda_{W',XY} > \lambda_{Y',XY}$; Equations \ref{eq:lambda_neoW} and \ref{eq:freq_diffs}).
+In particular, if haploid selection is strong but selective differences between male and female diploids are weak, we find that trans-GSD transitions (XY to ZW or ZW to XY) are favoured more strongly than cis-GSD transitions (e.g., with $|D^\male - D^\female| << |\alpha_\Delta^\male - \alpha_\Delta^\female + t^\male - t^\female|$ we have $\lambda_{W',XY} > \lambda_{Y',XY}$; Equations \ref{eq:lambda_neoW} and \ref{eq:freq_diffs}).
 Turnovers driven by haploid selection may help to explain the relative rarity of heteromorphic sex chromosomes in plants, which are thought to experience more selection during their multicellular haploid stage.
-For example, among relatively few dioecious clades in which multiple species have well characterized sex chromosomes \citep{Ming:2011iy}, heterogametic transitions have been inferred in \textit{Silene} subsection \textit{Otites} \citep{Slancarova:2013dq} and in \textit{Salicaceae} \citep{Pucholt2015,Pucholt2017}.
+For example, among relatively few dioecious clades in which multiple species have well characterized sex chromosomes \citep{Ming:2011iy}, trans-GSD transitions have been inferred in \textit{Silene} subsection \textit{Otites} \citep{Slancarova:2013dq} and in \textit{Salicaceae} \citep{Pucholt2015,Pucholt2017}.
 %Potentially, successive heterogametic transitions between master regulators of sex-determination could be inferred from careful examination of the molecular pathways by which sex is determined. 
@@
 Several rodent species also maintain feminizing alleles along with the ancestral X and Y sex-determination alleles \citep[reviewed in][]{Fredga1994}. 
-For example, in nine \textit{Akadon} species, it appears that \textit{sry} expression is suppressed by an autosomal feminizing allele, creating XY females \citep{Bianchi2002,Sanchez2010}, which have increased fitness relative to XX females \citep{Hoekstra2001}.
+For example, in nine \textit{Akadon} species, it appears that male-determining-\textit{sry} expression is suppressed by an autosomal feminizing allele, creating XY females \citep{Bianchi2002,Sanchez2010}, which have increased fitness relative to XX females \citep{Hoekstra2001}.
 In \textit{Mus microtoides}, females can have XX, XX$^\ast$ or X$^\ast$Y genotypes \citep{Veyrunes2010}. 
 Previous theory would predict that the X$^\ast$ chromosome (or the autosome it is fused to) harbours female beneficial alleles, driving its spread. 
-However, XX and XX$^\ast$ females have similar fitness, whereas X$^\ast$Y female fitness is enhanced \citep{Saunders2014}.
+However, XX and XX$^\ast$ females have similar fitness, whereas X$^\ast$Y female fitness is enhanced \citep{Saunders2014, Veyrunes2017}.
 Although Y-linkage of female-beneficial alleles is counterintuitive, our tight linkage model suggests that it can be stably maintained and then favour new feminizing mutations, which is a parsimonious explanation for the spread of feminizing alleles in these rodent species.
@@
 However, in some cases, there may be significant degeneration around the sex-limited allele (Y or W) in the ancestral sex-determining region because recessive deleterious mutations and/or deletions accumulate around the Y or W sex-determining regions \citep{Rice:1996ke,Charlesworth:2000cc,Bachtrog:2006ed,Marais:2008hm}.
-During heterogametic transitions (XY to ZW or ZW to XY), but not homogametic transitions (XY to XY or ZW to ZW), any recessive deleterious alleles linked to the Y or W are revealed to selection in YY or WW individuals \citep{Bachtrog:2014bx}.
+During trans-GSD transitions (XY to ZW or ZW to XY), but not cis-GSD transitions (XY to XY or ZW to ZW), any recessive deleterious alleles linked to the Y or W are revealed to selection in YY or WW individuals \citep{Bachtrog:2014bx}.
 This phenomenon was studied by \citet{vanDoorn:2010hu}, who found that degeneration can prevent fixation of a neo-W or a neo-Y allele, leading to a mixed sex-determination system where the ancestral and new sex-determining loci are both segregating.
-However, they noted that very rare recombination events around the ancestral sex-determining region can allow these heterogametic transitions to complete.  
+However, they noted that very rare recombination events around the ancestral sex-determining region can allow these trans-GSD transitions to complete.  
 %While not explicitly studied, we also predict that Y or W degeneration would prevent fixation of the new sex-determining genes considered here.
-Degeneration around the Y or W could explain why heterogametic transitions are not observed to be much more common than homogametic transitions despite the fact that our models demonstrate that they are favoured under a wider range of conditions.
+Degeneration around the Y or W could explain why trans-GSD transitions are not observed to be much more common than cis-GSD transitions despite the fact that our models demonstrate that they are favoured under a wider range of conditions.
 For example, \citet{Vicoso:2015hf} found a dozen sex chromosome configurations among Dipteran species but only one transition between male and female heterogametey.

### 2018-01-16 LaTeX/Turnover.tex
changed to cis-GSD and trans-GSD
Sally edits to intro and discussion. I also removed the discussion of two-locus drive and added something about ESD to GSD transitions (which we don't cover) and incomplete masculinizers/feminizers

@@
 Predominant theories for why we observe such transitions %in which new sex-determining systems spread by selection 
-%involve sex-ratio selection or sex-specific selection (e.g., sexually antagonistic selection).
+%involve sex ratio selection or sex-specific selection (e.g., sexually antagonistic selection).
 %These studies 
@@
 We use population genetic models to extend these theories in two ways: 
-(1) We explicitly consider how selection on very tightly sex-linked loci influences the spread of novel sex-determiners. 
-We find that tightly sex-linked genetic variation can favour the spread of new sex-determination systems in which the heterogametic sex changes (XY to ZW or ZW to XY) and the new sex-determining region is less closely linked (or unlinked) to the sex-linked locus under selection, which is not predicted by previous theory.
+(1) We explicitly consider selection on loci very tightly linked to the ancestral sex-determining loci, e.g., within the non-recombining region of the ancestral sex chromosomes. 
+%(1) We explicitly consider how selection on very tightly sex-linked loci influences the spread of novel sex-determiners. 
+Variation at such loci can favour the spread of new sex-determination systems in which the heterogametic sex changes (XY to ZW or ZW to XY) and the new sex-determining region is less closely linked (or unlinked) to the locus under selection, which is not predicted by previous theory.
 %With tight linkage, selection can maintain equilibria at which the allele fixed on the sex-limited chromosome (Y or W) is simultaneously favoured in the homogametic sex (XX females or ZZ males) such that heterogametic transitions (XY to ZW or ZW to XY) are favoured by selection.
@@
 %In addition, when linkage between the ancestral sex-determining locus and a locus under haploid selection is tight, sex ratio biases can be strong such that there is an asymmetry between invasion of ancestrally XY and ancestrally ZW systems because, e.g., haploid selection in males only causes biased zygotic sex ratios in an ancestrally XY system.
-We find that associations with haploid selected loci can drive transitions between sex determination systems, as has been shown for sexually-antagonistic loci. 
-In addition, with haploid selection, transitions between male and female heterogamety can also evolve when linkage with the sex-determining locus is weakened. 
-Haploid selection in the heterogametic sex can cause sex ratio biases, which may increase or decrease with the spread of new sex chromosomes. 
-Thus, transitions between sex-determination systems cannot be simply predicted by selection to equalise the sex-ratio. 
+We find that associations with haploid selected loci can drive transitions between sex determination systems, without requiring sexually-antagonistic selection in diploids. 
+Unexpectedly, with haploid selection, transitions between male and female heterogamety can also evolve where linkage with the sex-determining locus is weakened. 
+Furthermore, haploid selection in the heterogametic sex can cause sex ratio biases, which may increase or decrease with the spread of new sex chromosomes. 
+Thus, we find that transitions between sex-determination systems cannot be simply predicted by selection to equalise the sex ratio. 
 %These results indicate that loci experiencing haploid selection can favour the evolution of new sex-determination systems. 
@@
 %Notably, we find that the spread of new genetic sex-determination systems is not affected by sex ratio biases that are caused by haploid selection. 
-%A surprising result given that other determinants of sex allocation typically experience strong Fisherian sex-ratio selection to equalize sex ratios. 
+%A surprising result given that other determinants of sex allocation typically experience strong Fisherian sex ratio selection to equalize sex ratios. 
 %Overall, we demonstrate when and how the evolution of sex determining systems is impacted by sex ratio biases resulting from haploid selection and we show that new sex-determining regions can be favoured even if they are not closely linked with a locus under selection.
-Overall, our models reveal that transitions between sex-determination systems, particularly transitions where the heterogametic sex changes, can be driven by loci in previously unexpected genomic locations that experience selection during diploid and/or haploid phases.
-These results might be reflected in the lability with which sex-determination systems evolve. %and for the factors determining the phylogenetic pattern of sex-determination systems. 
+Overall, our models reveal that transitions between sex-determination systems, particularly transitions where the heterogametic sex changes, can be driven by loci in previously unpredicted genomic locations that experience selection during diploid and/or haploid phases.
+These results predict conditions under which sex-determination systems are likely to be labile and draw novel connections with sex ratio evolution
+%These results might be reflected in the lability with which sex-determination systems evolve. %and for the factors determining the phylogenetic pattern of sex-determination systems. 
 \end{abstract}
@@
 
-Predominant theories accounting for the spread of new sex-determination systems by selection involve fitness differences between sexes (e.g., sexually antagonistic selection) or sex-ratio selection \citep{Blaser2012, Beukeboom:2014vb,vanDoorn2014re}.
+Predominant theories accounting for the spread of new sex-determination systems by selection involve fitness differences between sexes (e.g., sexually antagonistic selection) or sex ratio selection \citep{Blaser2012, Beukeboom:2014vb,vanDoorn2014re}.
 %\citet{Bull:1977wt} shows that direct selection on new sex determination loci can allow them to spread and switch between male and female heterogamety. 
-\citet{vanDoorn:2007eu,vanDoorn:2010hu} show that new sex-determining loci can be favoured if they arise in closer linkage with a locus that experiences sexual antagonism. 
+\citet{vanDoorn:2007eu,vanDoorn:2010hu} and \citet{Muralidhar2018} have shown that new sex-determining loci can be favoured if they arise in close linkage with a locus that experiences sexual antagonism.
 Tighter linkage allows a stronger favourable association to build up between a male-beneficial allele, and a neo-Y chromosome, for example. 
-Such associations can favour a new master sex-determining gene on a new chromosome \citep{vanDoorn:2007eu} and can also favour a transition between male and female heterogamety \citep[e.g., a ZW to XY transition,][]{vanDoorn:2010hu}.
-However, any sexually-antagonistic loci that are more closely linked to the ancestral sex-determination locus will develop similar, favourable associations and hinder the spread of a new sex-determination system.
+Such associations can favour a new partially-masculinizing or partially-feminizing allele \citep{Muralidhar2018}, a new master sex-determining gene \citep{vanDoorn:2007eu}, and transitions between male and female heterogamety \citep[trans-GSD transitions, ZW to XY or XY to ZW,][]{vanDoorn:2010hu}.
+However, any sexually-antagonistic loci that are more closely linked to the ancestral sex-determination locus will develop similar, favourable associations and are expected to hinder the spread of a new sex-determination system.
 %Here we extend these studies by explicitly calculating the the equilibrium allele frequencies of loci that are very tightly linked to the ancestral sex-determining region.
 
-The sex ratio is directly determined by the sex-determination system, and it has therefore been suggested that sex-ratio selection is a dominant force in the evolution of sex determination (e.g., \citealt{Bull:1983vi}, p 66-67; \citealt{Beukeboom:2014vb}, Chapter 7).
-`Fisherian' sex-ratio selection favours a 1:1 zygotic sex ratio when assuming that males and females are equally costly to produce \citep{Fisher:1930wy,Charnov:1982wg}.
+The sex ratio is directly determined by the sex-determination system, and it has therefore been suggested that sex ratio selection is a dominant force in the evolution of sex determination (e.g., \citealt{Bull:1983vi}, p 66-67; \citealt{Beukeboom:2014vb}, Chapter 7).
+`Fisherian' sex ratio selection favours a 1:1 zygotic sex ratio when assuming that males and females are equally costly to produce \citep{Fisher:1930wy,Charnov:1982wg}.
 This follows from the fact that, for an autosomal locus, half of the genetic material is inherited from a male and half from a female \citep{West:2009we}. 
@@
 Therefore, a mutant that increases investment in the rarer sex will spread via the higher per-individual contributions made by that sex. 
-%The default mode of sex-ratio selection is `Fisherian' sex-ratio selection, which favours equal investment in male and female offspring \citep[i.e., a 1:1 zygotic sex ratio when assuming that males and females are equally costly to produce,][]{Fisher:1930wy,Charnov:1982wg}.
-%Given that the sex-determination system can directly affect the sex ratio, we might expect Fisherian sex-ratio selection to influence the spread of new sex-determination systems. 
+%The default mode of sex ratio selection is `Fisherian' sex ratio selection, which favours equal investment in male and female offspring \citep[i.e., a 1:1 zygotic sex ratio when assuming that males and females are equally costly to produce,][]{Fisher:1930wy,Charnov:1982wg}.
+%Given that the sex-determination system can directly affect the sex ratio, we might expect Fisherian sex ratio selection to influence the spread of new sex-determination systems. 
 In the case of sex-chromosome evolution, \citet{Kozielska:2010vm} consider systems in which the ancestral sex chromosomes experience meiotic drive (e.g., where driving X or Y chromosomes are inherited disproportionately often), which causes sex ratios to become biased \citep{Hamilton:1967ts}.
@@
 Gametic competition is also typically sex specific, occurring primarily among male gametes, because there are typically many more pollen/sperm than required for fertilization.
-Gametic competition may be particularly common in plants, in which 60-70\% of all genes are expressed in the male gametophyte and these genes exhibit stronger signatures of selection than random genes \citep{Borg:2009jpa,Arunkumar:2013iq,Gossmann:2014dua}.
+Gametic competition may be particularly common in plants, in which 60-70\% of all genes are expressed in the male gametophyte, and these genes exhibit stronger signatures of selection than random genes \citep{Borg:2009jpa,Arunkumar:2013iq,Gossmann:2014dua}.
 In addition, artificial selection pressures applied to male gametophytes are known to cause a response to selection \citep[e.g.,][]{Hormaza:1996cv,Ravikumar:2003uo,Hedhly:2004iv,Clarke:2004ir}. 
@@
 On the other hand, sex ratios can also become biased by linkage between the sex-determining region and a locus that harbours genetic variation in haploid fitness. 
-For example, there are several known cases of sex-ratio bias caused by sex-linked meiotic drive alleles \citep[][Chapter 3]{Burt:2006} or selection among X- and Y-bearing pollen \citep{Lloyd:1974tz,Conn:1981uw,Stehlik:2005ul,Stehlik:2006to,Field:2012fd,Field:2013cc}.
-It is not immediately clear how the spread of new sex-determination systems would be influenced by the combination of sex-ratio biases and associations between haploid selected loci and sex-determining regions.
+For example, there are several known cases of sex ratio bias caused by sex-linked meiotic drive alleles \citep[][Chapter 3]{Burt:2006} or selection among X- and Y-bearing pollen \citep{Lloyd:1974tz,Conn:1981uw,Stehlik:2005ul,Stehlik:2006to,Field:2012fd,Field:2013cc}.
+It is not immediately clear how the spread of new sex-determination systems would be influenced by the combination of sex ratio biases and associations between haploid selected loci and sex-determining regions.
 
@@
 
-We find that the spread of novel sex-determiners is influenced by both Fisherian sex-ratio selection and by selection on genetically-associated alleles. 
-%We find that sex-ratio biases caused by haploid selection can exert Fisherian sex-ratio selection upon novel sex-determiners but that their spread is also determined by selection on genetically-associated alleles.
-%Indeed, it is only when haploid-selected loci are tightly linked to the ancestral sex-determining region (and so sex-ratio biases are initially large) that we see an asymmetry between selection for XY to ZW transitions and ZW to XY transitions (e.g., because haploid selection in males only causes biased zygotic sex ratios in an ancestrally XY system).
-Surprisingly, Fisherian sex ratio selection does not dominate; it is possible for selection on linked alleles to drive turnover between sex-determining systems despite causing increases in sex-ratio bias.
+We find that the spread of novel sex-determiners is influenced by both Fisherian sex ratio selection and by selection on genetically-associated alleles. 
+%We find that sex ratio biases caused by haploid selection can exert Fisherian sex ratio selection upon novel sex-determiners but that their spread is also determined by selection on genetically-associated alleles.
+%Indeed, it is only when haploid-selected loci are tightly linked to the ancestral sex-determining region (and so sex ratio biases are initially large) that we see an asymmetry between selection for XY to ZW transitions and ZW to XY transitions (e.g., because haploid selection in males only causes biased zygotic sex ratios in an ancestrally XY system).
+Surprisingly, Fisherian sex ratio selection does not dominate; it is possible for selection on linked alleles to drive turnover between sex-determining systems despite causing increasingly biased sex ratios.
 In addition to considering haploid selection, another novel development in our model is that we consider loci that are in very tight linkage with the ancestral sex-determining region. 
@@
 We assume that all gametes compete for fertilization during gametic competition, which assumes a polygamous mating system. 
-Gametic competition in monogamous mating systems is, however, equivalent to meiotic drive in our model (described below), as both only alter the frequency of gametes produced by heterozygotes. 
+Gametic competition in monogamous mating systems is, however, equivalent to meiotic drive in our model (described below), as either only alters the frequency of gametes produced by heterozygotes. 
 After gametic competition, random mating occurs between male and female gametes.
@@
 Any linear order of the loci can be modelled with appropriate choices of $r$, $R$, and $\rho$ (see Figure \ref{fig:model_outline}A and Table \ref{tab:chisubstitutions}). 
-Individuals that are heterozygous at the \textbf{A} locus may experience meiotic drive; a gamete produced by $Aa$ heterozgotes of sex $\Hermaphrodite$ bear allele $A$ with probability $\alpha^\Hermaphrodite$.
+Individuals that are heterozygous at the \textbf{A} locus may experience meiotic drive; a gamete produced by $Aa$ heterozgotes of sex $\Hermaphrodite$ bears allele $A$ with probability $\alpha^\Hermaphrodite$.
 Thus, the \textbf{A} locus can experience sex-specific gametic competition, diploid selection, and/or meiotic drive.
@@
 Without loss of generality, we primarily refer to the ancestrally heterogametic sex as male and the ancestrally homogametic sex as female.
-That is, we describe an ancestral XY sex-determination system but our model is equally applicable to an ancestral ZW sex-determination system (relabelling the ancestrally-heterogametic sex as female and the ancestrally-homogametic sex as male).
+That is, we describe an ancestral XY sex-determination system but our model is equally applicable to an ancestral ZW sex-determination system (relabelling the ancestrally-heterogametic sex as female and the ancestrally-homogametic sex as male and switching the labels of males and females throughout).
 
@@
 We also track the fraction of male gametes that are Y-bearing, $q$, which may deviate from $1/2$ due to meiotic drive in males. 
-We will consider only equilibrium frequencies of alleles, $\hat{p}^\Hermaphrodite_i$, and Y-bearing male gametes, $\hat{q}$, to ensure the eigenvalues of the invasion analysis are valid.
+We will consider only equilibrium frequencies of alleles, $\hat{p}^\Hermaphrodite_i$, and Y-bearing male gametes, $\hat{q}$, when calculating the eigenvalues.
 
@@
 \end{equation}
-\noindent For example, if we assume that only the $mA$ haplotype has a positive growth rate ($\lambda_{ma}<1<\lambda_{mA}$), the first term on the left-hand side of \eqref{eq:lambdasGen} is negative and invasion requires that the growth rate of $mA$ haplotypes ($\lambda_{mA}-1$) and the rate at which they are produced by recombination in $ma$ haplotypes ($\chi_{ma}$) are sufficiently large relative to the rate of decline of $ma$ haplotypes ($1-\lambda_{ma}$) and the rate of loss of $mA$ haplotypes due to recombination ($\chi_{mA}$).
+\noindent For example, if we assume that only the $mA$ haplotype has a positive growth rate whe $R=0$ ($\lambda_{ma}<1<\lambda_{mA}$), the first term on the left-hand side of \eqref{eq:lambdasGen} is negative and invasion requires that the growth rate of $mA$ haplotypes ($\lambda_{mA}-1$) and the rate at which they are produced by recombination in $ma$ haplotypes ($\chi_{ma}$) are sufficiently large relative to the rate of decline of $ma$ haplotypes ($1-\lambda_{ma}$) and the rate of loss of $mA$ haplotypes due to recombination ($\chi_{mA}$).
 %\textcolor{blue}{i've updated this section with the correct $\lambda$ and $\chi$ terms.
@@
 
-Table \ref{tab:haplotype_growth} illustrates a number of key points about the invasion of neo-Y and neo-W mutations. 
-First, Fisherian sex-ratio selection will favour the spread of a neo-Y if the ancestral zygotic sex ratio is biased towards females, $\zeta<1/2$ (i.e., the first factor of the $\lambda_{mi}$ is greater than one for a neo-Y and less than one for a neo-W).
-However, the spread of a neo-Y (neo-W) also depends on the male (female) fitness of associated alleles, see terms involving equilibrium allele frequencies, $\hat{p}$'s.
+We can draw a number of key points about the invasion of neo-Y and neo-W mutations from Table \ref{tab:haplotype_growth}. 
+First, Fisherian sex ratio selection will favour the spread of a neo-Y if the ancestral zygotic sex ratio is biased towards females, $\zeta<1/2$ (i.e., the first factor of the $\lambda_{mi}$ is greater than one for a neo-Y and less than one for a neo-W).
+However, the spread of a neo-Y (neo-W) also depends on the male (female) fitness of associated alleles (see terms involving equilibrium allele frequencies, $\hat{p}$'s).
 %, see terms in curly brackets.
@@
 Finally, invasions by a neo-Y and a neo-W are qualitatively different.
-This is because a gamete with the ancestral- or neo-Y always pairs with a female gamete containing an X, and both develop into males, Figure \ref{fig:model_outline}C.
-By contrast, a gamete with a neo-W can pair with an X or Y male gamete, developing into a female, while female gametes without the neo-W can become female (when paired with X) or male (when paired with Y), Figure \ref{fig:model_outline}D.
-Consequently, the types of females produced differ in the frequency of $A$ alleles they obtain from mating when $\hat{p}_X^\male \neq \hat{p}_Y^\male$.
+This is because a gamete with the neo-Y always pairs with a female gamete containing an X, and develop into males, Figure \ref{fig:model_outline}C.
+By contrast, a gamete with a neo-W can pair with an X or Y male gamete, developing into a female, Figure \ref{fig:model_outline}D.
+Consequently, neo-W bearing females obtain a differerent frequency of $A$ alleles from mating (when $\hat{p}_X^\male \neq \hat{p}_Y^\male$) compared to ancestral ($MM$) females.
 %\textcolor{blue}{nice}
@@
 Polymorphisms can be maintained by mutation-selection balance or transiently present during the spread of beneficial alleles.
-However, polymorphisms maintained by selection can maintain alleles at higher allele frequencies for longer periods.
-Here, we focus of polymorphisms maintained by selection, where the $A$ allele reaches a stable intermediate equilibrium frequency under the ancestral sex-determination system before the neo-sex-determining allele ($m$) arises.
+However, polymorphisms maintained by selection can maintain alleles at intermediate allele frequencies for longer periods.
+Here, we focus on polymorphisms maintained by selection, where the $A$ allele reaches a stable intermediate equilibrium frequency under the ancestral sex-determination system before the neo-sex-determining allele ($m$) arises.
+Such polymorphisms can be maintained by heterozygote advantage, sexually-antagonistic selection, ploidally-antagonistic selection, or a combination \citep{Immler:2012tl}.
 We can analytically calculate the allele frequency of the $A$ allele using two alternative simplifying assumptions: 
@@
 
-A neo-Y will never invade an ancestral XY system that already has tight linkage with the locus under selection ($r=0$, for details see supplementary \textit{Mathematica} file). 
+We find that a neo-Y can never invade an ancestral XY system that already has tight linkage with the locus under selection ($r=0$, for details see supplementary \textit{Mathematica} file). 
 %When then neo-Y is also tightly linked ($R=0$) a neo-Y will either remain linked to the $A$ allele or to the $a$ allele and so invasion is given directly by the larger of $\lambda_{mA}$ or $\lambda_{ma}$.
-A neo-Y haplotype with the same allele as the ancestral Y is neutral ($\lambda_{ma}=1$) and does not change in frequency.
+When $R=0$, a neo-Y haplotype with the same allele as the ancestral Y is neutral ($\lambda_{ma}=1$) and does not change in frequency.
 The other neo-Y haplotype will not spread ($\lambda_{mA}<1$) given that the initial equilibrium is stable. 
-Therefore, a neo-Y mutation cannot spread ($\lambda \leq 1$) in an ancestral XY system where selected loci are within the non-recombining region around the SDR.
+Therefore, a neo-Y mutation cannot spread ($\lambda \leq 1$,  regardless of $R$) in an ancestral XY system where selected loci are within or very near the non-recombining region around the SDR.
 In essence, through tight linkage with the \textbf{A} locus, the ancestral Y becomes strongly specialized on the allele that has the highest fitness across male haploid and diploid phases. 
@@
 Neo-W alleles, on the other hand, can invade an ancestral XY system under some conditions (the full invasion conditions are given in the appendix; equations \ref{Binvasion} and \ref{Ainvasion}). 
-That is, selection on loci within the non-recombining region of the SDR can favour the invasion of a less closely linked neo-W (Figure \ref{fig:SexAntagTighter}). 
+Counterintuitively, selection on loci within the non-recombining region of the SDR can favour the invasion of a less closely linked neo-W, whether selection involves only sexual antagonism, or overdominance, or haploid selection is also present (e.g., Figures \ref{fig:SexAntagTighter}, \ref{fig:temporalOverdominance}, and \ref{fig:SexAntagTighterMaleDrive}).
 %Although haploid selection can favour neo-W alleles because the ancestral sex ratio becomes male biased, this is not the only circumstance in which less tightly linked neo-W alleles invade. 
@@
 %%The full characteristic polynomials are given in the appendix (equations \ref{Binvasion} and \ref{Ainvasion}).
-%Briefly, neo-W-$A$ and/or neo-W-$a$ haplotypes can spread when rare in the absence of recombination ($\lambda_{ma}>1$ and/or $\lambda_{mA}>1$), depending on the ancestral sex-ratio and allele frequencies.
+%Briefly, neo-W-$A$ and/or neo-W-$a$ haplotypes can spread when rare in the absence of recombination ($\lambda_{ma}>1$ and/or $\lambda_{mA}>1$), depending on the ancestral sex ratio and allele frequencies.
 %Below we discuss the main forces determining the spread of these neo-W haplotypes and the impact of recombination for the overall success of the neo-W.
@@
 %Previous research suggests that when the ancestral sex-determining locus is linked to a locus that experiences haploid selection (e.g., meiotic drive), a new, unlinked sex-determining locus invades in order to restore equal sex ratios \citep{Kozielska:2010vm}.
-%Our model provides a good opportunity to determine whether Fisherian sex-ratio selection provides a useful explanation for the evolution of new sex-determining loci in other contexts. 
+%Our model provides a good opportunity to determine whether Fisherian sex ratio selection provides a useful explanation for the evolution of new sex-determining loci in other contexts. 
 %Consider, for example, the case where the \textbf{A} locus is linked to the ancestral-SDR ($r<1/2$) and experiences meiotic drive in males only (e.g., during spermatogenesis but not during oogenesis, $\alpha^\male \neq 1/2$, $\alpha^\female=1/2$).
@@
 %That is, we can show that $\lambda_{Y',XY}=\lambda_{W',ZW}$ and $\lambda_{Y',ZW}=\lambda_{W',XY}$ (at least up to order $\epsilon^3$; for a numerical example, compare Figure \ref{fig:Combination_Turnover}A,B to Figure \ref{fig:Combination_Turnover}C,D).
-%As it turns out, under weak selection the strength of sex-ratio selection favouring, say, the invasion of a neo-W in an XY system is the same as the strength of meiotic drive favouring the invasion of a neo-Y in a ZW system.
-%Even when these forces are not exactly the same (e.g., under tight sex-linkage; compare black and red curves near -25 and 25cM in Figure \ref{fig:Combination_Centimorgans}), it is important to remember that sex-ratio selection is only one of many potential selective forces acting to determine transitions between sex-determining systems.
-%It is even possible for the other selective forces to overwhelm sex-ratio selection and favour sex-determination transitions that create sex-ratio biases (Figure \ref{fig:Combination_Turnover}A,C).
+%As it turns out, under weak selection the strength of sex ratio selection favouring, say, the invasion of a neo-W in an XY system is the same as the strength of meiotic drive favouring the invasion of a neo-Y in a ZW system.
+%Even when these forces are not exactly the same (e.g., under tight sex-linkage; compare black and red curves near -25 and 25cM in Figure \ref{fig:Combination_Centimorgans}), it is important to remember that sex ratio selection is only one of many potential selective forces acting to determine transitions between sex-determining systems.
+%It is even possible for the other selective forces to overwhelm sex ratio selection and favour sex-determination transitions that create sex ratio biases (Figure \ref{fig:Combination_Turnover}A,C).
 
@@
 
-%As selection becomes stronger (or linkage becomes tighter), this symmetry between sex-ratio selection and haploid selection is lost, causing differences in the strength of selection favouring the two heterogametic transitions (compare red to black near -25cM and 25 cM in Figure \ref{fig:Combination_Centimorgans}).
+%As selection becomes stronger (or linkage becomes tighter), this symmetry between sex ratio selection and haploid selection is lost, causing differences in the strength of selection favouring the two heterogametic transitions (compare red to black near -25cM and 25 cM in Figure \ref{fig:Combination_Centimorgans}).
 \textcolor{red}{normalise fitness in sexually antagonistic case}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Sex-ratio selection is not a good predictor of neo-W invasion into an XY system
+%Sex ratio selection is not a good predictor of neo-W invasion into an XY system
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \caption{
-Fisherian sex-ratio selection alone is not a good predictor of turnover between sex-determining systems.
+Fisherian sex ratio selection alone is not a good predictor of turnover between sex-determining systems.
 In this figure, selection is ploidally antagonistic with haploid selection favouring the $a$ allele during male meiosis.
@@
 
-%Under Fisherian sex-ratio selection, autosomal modifiers favour equal investment in male and female offspring, i.e., a 1:1 sex ratio \citep{Fisher:1930wy,Charnov:1982wg,West:2009we}. 
+%Under Fisherian sex ratio selection, autosomal modifiers favour equal investment in male and female offspring, i.e., a 1:1 sex ratio \citep{Fisher:1930wy,Charnov:1982wg,West:2009we}. 
 %A novel environmental sex-determiner that causes half of its carriers to become female and half to become male ($k=1/2$) will be in males half of the time and in females half of the time (like an autosome).
-%In addition, these novel sex-determination alleles equalize the sex ratio and therefore one might expect them to be favoured by Fisherian sex-ratio selection when the resident sex ratio is biased.
+%In addition, these novel sex-determination alleles equalize the sex ratio and therefore one might expect them to be favoured by Fisherian sex ratio selection when the resident sex ratio is biased.
 %However, assuming weak selection, we find that the growth rate of a rare, dominant offspring-controlled neo-ESD allele that produces males or females with equal probability ($k=1/2$) is
@@
 Significantly, equation \eqref{eq:lambda_ESD} is the same whether ESD is invading an ancestrally XY or ZW system (because $\lambda_{Y',XY} = \lambda_{W',ZW}$ and $\lambda_{W',XY} = \lambda_{Y',ZW}$).
-Thus, Fisherian sex-ratio selection alone does not explain the invasion of ESD under weak selection because the sex ratio is only biased by male haploid selection when the ancestral sex-determination system is XY.
+Thus, Fisherian sex ratio selection alone does not explain the invasion of ESD under weak selection because the sex ratio is only biased by male haploid selection when the ancestral sex-determination system is XY.
 Specifically, with male haploid selection, the neo-ESD is equally likely to invade when it equalizes the zygotic sex ratio (through $\lambda_{W',XY}$) and when it doesn't (through $\lambda_{Y',ZW}$). 
@@
 
-%Fisherian sex-ratio selection is sometimes considered in terms of balancing parental investment in male versus female offspring \citep{Charnov:1982wg}.
+%Fisherian sex ratio selection is sometimes considered in terms of balancing parental investment in male versus female offspring \citep{Charnov:1982wg}.
 %In addition, under environmental sex-determination, the proportion of males/females is sometimes controlled by the mother (e.g., the proportion of eggs laid in warm versus cold environments). 
 %We therefore also considered the invasion of a neo-sex-determining allele ($m$) in a model in which mothers that have at least one $m$ allele produce daughters with probability $k$. 
-%As with offspring-controlled ESD, for all $k\in\{0,1/2,1\}$, we find that invasion into an ancestral XY system is the same as invasion into an ancestrally ZW system (at least up to order $\epsilon^3$, assuming weak selection), implying that transitions between genetic sex-determination and maternally controlled environmental sex-determination are not driven by Fisherian sex-ratio selection alone.
+%As with offspring-controlled ESD, for all $k\in\{0,1/2,1\}$, we find that invasion into an ancestral XY system is the same as invasion into an ancestrally ZW system (at least up to order $\epsilon^3$, assuming weak selection), implying that transitions between genetic sex-determination and maternally controlled environmental sex-determination are not driven by Fisherian sex ratio selection alone.
 %\textcolor{red}{(Maternal ESD analysis still lacks meiotic drive -- Mathematica can't seem to deal with the added complexity.)}
@@
 %However, with $k\neq1$ the results with maternal control differ from those with offspring control.
-%Interestingly, for all $k\in\{0,1/2,1\}$, we find that invasion into an ancestrally XY system is the same as invasion into an ancestrally ZW system (at least up to order $\epsilon^3$), implying that sex-ratio selection does not drive transitions between genetic sex determination and maternally controlled environmental sex determination.
+%Interestingly, for all $k\in\{0,1/2,1\}$, we find that invasion into an ancestrally XY system is the same as invasion into an ancestrally ZW system (at least up to order $\epsilon^3$), implying that sex ratio selection does not drive transitions between genetic sex determination and maternally controlled environmental sex determination.
 %Of particular interest is $k=1/2$ (i.e., when the mother perfectly balances the sex ratio of her offspring).
@@
 %MAIN RESULT
-Two predominant theories explaining the remarkably high frequency of transitions between sex-determination systems are sexually-antagonistic selection and sex-ratio selection \citep[reviewed in][]{Blaser2012, vanDoorn2014re}.
-The former predicts that neo-sex-determining alleles can invade when they arise in closer linkage with a sexually-antagonistic locus \citep{vanDoorn:2007eu,vanDoorn:2010hu}.
-The latter predicts that new sex-determining systems are generally favoured if they result in more equal sex-ratios than the ancestral system. 
+Two predominant theories explaining the remarkably high frequency of transitions between sex-determination systems are sexually-antagonistic selection and sex ratio selection \citep[reviewed in][]{Blaser2012, vanDoorn2014re}.
+The former predicts that neo-sex-determining alleles can invade when they arise in closer linkage with a sexually-antagonistic locus \citep{vanDoorn:2007eu,vanDoorn:2010hu, Muralidhar2018}.
+The latter predicts that new sex-determining systems are generally favoured if they result in more equal sex ratios than the ancestral system. 
 %The latter predicts that neo-W alleles will invade an XY system when there is a male bias caused by haploid selection in males, and vice-versa, a neo-Y will invade a ZW system when there is a female bias caused by haploid selection in females \citep{Kozielska:2010vm,Ubeda:2015fx}.
-Firstly, we show that selection (including sexually-antagonistic selection) on loci within or near the non-recombining region of the ancestral sex-determining region can favour trans-GSD transitions (XY to ZW or ZW to XY) to new sex-determining systems that are less closely linked to the selected loci (e.g., see Figure \ref{fig:SexAntagTighter}).
-Secondly, assuming that selection is weak relative to recombination (`weak selection'), we show that new sex-determining alleles are typically favoured if they are more closely linked to a locus under haploid selection (even in the absence of diploid sex differences), which is the only condition favouring cis-GSD transitions (XY to XY or ZW to ZW).
-In addition, with haploid selection and weak selection, trans-GSD transitions (XY to ZW or ZW to XY) can occur even when the new sex-determining region is less closely linked to the locus under selection (e.g., see Figure \ref{fig:SexRatioBad}).
+In contrast to these prevailing views, we show that selection (including sexually-antagonistic selection, overdominance, and/or ploidally-antagonistic selection) on loci tightly linked to the ancestral sex-determining region can favour trans-GSD transitions (XY to ZW or ZW to XY) to new sex-determining systems that are less closely linked to the selected loci (e.g., see Figure \ref{fig:SexAntagTighter}).
+Similarly, even when linkage is weak relative to selection, we show that %new sex-determining alleles are typically favoured if they are more closely linked to a locus under haploid selection (even in the absence of diploid sex differences), which is the only condition favouring cis-GSD transitions (XY to XY or ZW to ZW).
+%In addition, with haploid selection and weak selection, 
+trans-GSD transitions (XY to ZW or ZW to XY) can occur where the new sex-determining region is less closely linked to the locus under selection if there is haploid selection (e.g., Figures \ref{fig:Combination_Centimorgans} and \ref{fig:SexRatioBad}).
 %\textcolor{red}{need to mention sex ratio here}
@@
 
-%The likelihoods of these transitions are driven by sex-ratio selection, direct selection on alleles linked to the neo-sex-determining allele, the ability of the neo-sex-determining allele to avoid selection in one sex, and the ability of the neo-sex-determining allele to bring alleles on the sex-specific chromosome in the ancestor into the other sex (given that the neo-sex determining allele is epistatically dominant to its predecessor).
+%The likelihoods of these transitions are driven by sex ratio selection, direct selection on alleles linked to the neo-sex-determining allele, the ability of the neo-sex-determining allele to avoid selection in one sex, and the ability of the neo-sex-determining allele to bring alleles on the sex-specific chromosome in the ancestor into the other sex (given that the neo-sex determining allele is epistatically dominant to its predecessor).
 
@@
 %\textcolor{blue}{maybe drop paragraph?}
-%\textcolor{red}{I messed with the sex-ratio selection paragraphs to tone down our "it doesn't matter" speech from before. Have at any amendments you'd like to make.}
+%\textcolor{red}{I messed with the sex ratio selection paragraphs to tone down our "it doesn't matter" speech from before. Have at any amendments you'd like to make.}
 %Linkage between haploid selected loci and sex-determining regions cases biased zygotic sex ratios \citep{Hamilton:1967ts,Burt:2006,Field:2012fd,Field:2013cc}.
-%One might then expect Fisherian sex-ratio selection to drive the spread of new sex-determining systems that bring the sex ratio closer to 50:50. 
-%Fisherian sex-ratio selection follows from the fact that, for an autosomal locus, half of the genetic material is inherited from a male, and half from a female \citep{Fisher:1930wy,West:2009we}. 
+%One might then expect Fisherian sex ratio selection to drive the spread of new sex-determining systems that bring the sex ratio closer to 50:50. 
+%Fisherian sex ratio selection follows from the fact that, for an autosomal locus, half of the genetic material is inherited from a male, and half from a female \citep{Fisher:1930wy,West:2009we}. 
 %Thus, if the population sex ratio is biased towards females, the average per-individual contribution of genetic material to the next generation from males is greater than the contribution from females (and vice versa for male-biased sex ratios).
 %Therefore, a mutant that increases investment in males will spread via the higher per-individual contributions made by males. 
-%%%That is, under Fisherian sex-ratio selection, the success of a mutant relative to the non-mutant depends, in equal parts, on the contributions made by males and females to the next generation. 
-%An implicit assumption of Fisherian sex-ratio selection is that the mutant allele is autosomal and has the same inheritance pattern as the non-mutant allele. 
+%%%That is, under Fisherian sex ratio selection, the success of a mutant relative to the non-mutant depends, in equal parts, on the contributions made by males and females to the next generation. 
+%An implicit assumption of Fisherian sex ratio selection is that the mutant allele is autosomal and has the same inheritance pattern as the non-mutant allele. 
 %The mutations we consider here, neo-sex-determining alleles, break this assumption. 
@@
 %Even mutants that are equally likely to be found in males or females, such as an environmental sex determination mutation (equation \ref{eq:lambda_ESD}), are not strictly autosomal if they determine sex.
-%Thus, despite the fact that sex ratio biases caused by gametic competition or meiotic drive have been shown to exert Fisherian sex-ratio selection on various autosomal modifiers \citep{Stalker:1961th,Smith:1975ft,Frank:1989vl,Hough:2013uo,Ubeda:2015fx, Otto:2015va}, we do not find evidence of Fisherian sex-ratio selection acting during invasion by neo-sex-determination systems (e.g., see Figure \ref{fig:Combination_Turnover} and \citealt{Ubeda:2015fx}, in which a neo-Y invades despite biasing sex ratios).
-
-%Sex ratio biases caused by gametic competition or meiotic drive have been shown to exert Fisherian sex-ratio selection on various autosomal \citep{Stalker:1961th,Smith:1975ft,Frank:1989vl,Hough:2013uo,Ubeda:2015fx, Otto:2015va} and sex-linked \citep{Kozielska:2010vm} modifiers.
-Sex-ratio biases caused by haploid selection can facilitate trans-GSD transitions between sex-determining systems. 
-For instance, alleles favoured by haploid selection in males often become associated with the Y, which leads to a male-biased zygotic sex-ratio.
-This male bias increases the potential for a neo-W to invade (Table \ref{tab:haplotype_growth}), which can equalize the sex-ratio \citep[e.g., see Figure \ref{fig:SexRatioBad}B, for related examples see][]{Kozielska:2010vm,Ubeda:2015fx}.
-%We find that sex-ratio biases caused by haploid selection can also affect transitions between sex-determining systems (e.g., see $\zeta$ terms in Table \ref{tab:haplotype_growth}). 
-%However, the neo-W may not equalize the sex-ratio (e.g., if the driving allele also drives in females or affects competition among eggs)
-However, sex-ratio selection can be overwhelmed by additional selective effects (e.g., when a linked allele is beneficial for male diploids but detrimental for female diploids; Table \ref{tab:specialcases}), preventing the neo-W from invading.
+%Thus, despite the fact that sex ratio biases caused by gametic competition or meiotic drive have been shown to exert Fisherian sex ratio selection on various autosomal modifiers \citep{Stalker:1961th,Smith:1975ft,Frank:1989vl,Hough:2013uo,Ubeda:2015fx, Otto:2015va}, we do not find evidence of Fisherian sex ratio selection acting during invasion by neo-sex-determination systems (e.g., see Figure \ref{fig:Combination_Turnover} and \citealt{Ubeda:2015fx}, in which a neo-Y invades despite biasing sex ratios).
+
+%Sex ratio biases caused by gametic competition or meiotic drive have been shown to exert Fisherian sex ratio selection on various autosomal \citep{Stalker:1961th,Smith:1975ft,Frank:1989vl,Hough:2013uo,Ubeda:2015fx, Otto:2015va} and sex-linked \citep{Kozielska:2010vm} modifiers.
+We find that the spread of neo-sex-determining systems cannot be simply predicted from their effect on the sex ratio. 
+On one hand, sex ratio biases caused by haploid selection can facilitate trans-GSD transitions between sex-determining systems, in agreement with Fisherian sex ratio selection. 
+For instance, alleles favoured by haploid selection in males often become associated with the Y, which leads to a male-biased zygotic sex ratio.
+This male bias increases the potential for a neo-W to invade (Table \ref{tab:haplotype_growth}), which can equalize the sex ratio \citep[e.g., see Figure \ref{fig:SexRatioBad}B, for related examples see][]{Kozielska:2010vm}.
+%We find that sex ratio biases caused by haploid selection can also affect transitions between sex-determining systems (e.g., see $\zeta$ terms in Table \ref{tab:haplotype_growth}). 
+%However, the neo-W may not equalize the sex ratio (e.g., if the driving allele also drives in females or affects competition among eggs)
+On the other hand, sex ratio selection can be overwhelmed by additional selective effects, preventing the neo-W from invading, even if it would balance the sex ratio (e.g., when selection acts in opposite directions in male and female diploids, Table \ref{tab:specialcases}).
 %and equalizing the sex ratio.
-Indeed, transitions between sex-determining systems can even lead to stronger sex-ratio biases.
-For example, where a neo-Y invades and is linked with a locus that experiences haploid selection in male gametes, the sex ratio evolves to become biased \citep[e.g., see Figure \ref{fig:SexRatioBad}A and step 1 in][]{Ubeda:2015fx}.
+Indeed, transitions between sex-determining systems can generate stronger sex ratio biases \citep[e.g., Figure \ref{fig:SexRatioBad}A and step 1 in][]{Ubeda:2015fx}.
+%For example, where a neo-Y invades and is linked with a locus that experiences haploid selection in male gametes, the sex ratio evolves to become biased \citep[e.g., see Figure \ref{fig:SexRatioBad}A and step 1 in][]{Ubeda:2015fx}.
 %For example, in an ancestral ZW system, haploid selection in males can allow a linked neo-Y to invade, despite the fact that it creates a male-biased sex ratio because the neo-Y becomes associated with the driven allele (Figure \ref{fig:SexRatioBad}A).
 %\textcolor{blue}{and figure 1, where the end of one panel is the same as the beginning of another, however, this figure may change).}
-%What we would like to stress is that sex-ratio selection alone cannot predict when new sex-determining systems can evolve.
-Furthermore, with weak selection, we find that there is no difference in conditions allowing XY to ZW and ZW to XY transitions, indicating that sex chromosome transitions are not predominantly predicted by their effect on the sex-ratio (i.e., the sex-ratio bias created by male haploid selection facilitates the spread of a neo-W into an XY system the same way that male haploid selection drives the spread of a neo-Y into a ZW system with a 1:1 sex ratio).
+%What we would like to stress is that sex ratio selection alone cannot predict when new sex-determining systems can evolve.
+Significantly, with weak selection, we find that there is no difference in conditions allowing XY to ZW and ZW to XY transitions, indicating that sex chromosome transitions are not predominantly predicted by their effect on the sex ratio (i.e., the sex ratio bias created by male haploid selection facilitates the spread of a neo-W into an XY system to the same degree that male haploid selection drives the spread of a neo-Y into a ZW system with a 1:1 sex ratio).
 %An asymmetry can develop when sex-linkage is tight (e.g., Figure \ref{fig:Combination_Centimorgans} near -25cM and 25cM) but under most circumstances we do not predict asymmetry between XY to ZW and ZW to XY transitions despite the presence/absence of sex ratio selection.
-Thus, haploid selection can favour trans-GSD transitions both via sex-ratio selection %\citep[as predicted by][]{Kozielska:2010vm} 
-and via fitness effects of alleles that are associated with the neo-sex-determining allele, and these selection pressures are predicted to often be of equal magnitude when selection is weak. 
+Thus, haploid selection can favour trans-GSD transitions both via sex ratio selection and via selection on alleles associated with the neo-sex-determining allele, and these selective pressures are often predicted to be of equal magnitude.
 %\textcolor{red}{Maybe try to emphasise surprisingness in the paragraph more? e.g., how wrong you'd be if you assumed selection to equalise sex ratios, or it this implied?}
@@
 %Previous studies where ESD is favoured have typically assumed that environmental conditions (e.g., maternal condition, mate quality, age, or host size) can differentially affect the fitness of males versus females such that ESD invades because it allows sex determination to depend on the environment \citep[reviewed in][]{Charnov:1982wg,Bull:1983vi,West:2009we}.
-
-%SEX-RATIO BIAS IN UBEDA ET AL
-%DRAFT (improve): In \citet{Ubeda:2015fx}, the new sex determining locus spreads because it arises in linkage with a locus that experiences drive.
-They assume that drive occurs predominantly in one sex, e.g., during spermatogenesis or a 'killer' sperm.
-A driving allele is maintained at an intermediate frequency by selection, e.g., because it causes male sterility when homozygous (because all male sperm are killed).
-Y chromosomes that arise in linkage with the driving allele spread because they allow drive to occur more often, thus genetic sex determination with a sex ratio bias evolves.
-%Thus \citet{Ubeda:2015fx} also find that genetic sex determiners can invade, despite causing sex ratios to become biased. 
-%Finally, they show that autosomal 'restorers' that negate the effects of meiotic drive can invade and restore an equal sex ratio.
 
@@
 
-%COMPARATIVE PATTERNS 
+%HAPLOID SELECTION (genomic location of haploid selected loci and comparative patterns) 
 We have shown that the spread of new sex determination systems can be driven by loci experiencing haploid selection. 
-Because haploid selection can cause transitions that increase or decrease sex-linkage, haploid selection may lead to less stability, and greater potential for cycling, in sex-determination systems (e.g., the final state of the red line in Figure \ref{fig:SexRatioBad}A is the starting state in Figure \ref{fig:SexRatioBad}B).
-In particular, if haploid selection is strong but selective differences between male and female diploids are weak, we find that trans-GSD transitions (XY to ZW or ZW to XY) are favoured more strongly than cis-GSD transitions (e.g., with $|D^\male - D^\female| << |\alpha_\Delta^\male - \alpha_\Delta^\female + t^\male - t^\female|$ we have $\lambda_{W',XY} > \lambda_{Y',XY}$; Equations \ref{eq:lambda_neoW} and \ref{eq:freq_diffs}).
-Turnovers driven by haploid selection may help to explain the relative rarity of heteromorphic sex chromosomes in plants, which are thought to experience more selection during their multicellular haploid stage.
-For example, among relatively few dioecious clades in which multiple species have well characterized sex chromosomes \citep{Ming:2011iy}, trans-GSD transitions have been inferred in \textit{Silene} subsection \textit{Otites} \citep{Slancarova:2013dq} and in \textit{Salicaceae} \citep{Pucholt2015,Pucholt2017}.
-%Potentially, successive heterogametic transitions between master regulators of sex-determination could be inferred from careful examination of the molecular pathways by which sex is determined. 
-%Our predictions could also be examined using a suitable proxy for haploid selection, for example, \cite{Lenormand:2005vb} use the outcrossing rate in plants as a proxy for the strength of pollen competition.
-Furthermore, assuming that transitions from dioecy to hermaphroditism (equal parental investment in male and female gametes) are favoured in a similar manner to the ESD examined here (equal probability of zygotes developing as males or females), our results suggest that competition during the haploid stage could drive transitions between dioecy and hermaphroditism, which are frequent in plants \citep{Kafer2017, Goldberg2017}.
-%In animals, one might expect gametic competition to be stronger in species where sperm is required to live for a long time after spermatogenesis because transcripts shared during spermatogenesis may become depleted, revealing the haploid phenotype of the sperm \citep{Immler:2014im}.
-%We would also expect that heterogametic transitions in sex determination would be more common in clades where there is meiotic drive.
-
-Our results suggest that haploid selected loci that have been involved in driving turnovers between sex-determination systems could occur around the ancestral- or novel-sex-determining regions. 
+%Our results suggest that haploid selected loci that have been involved in driving turnovers between sex-determination systems could occur around the ancestral- or novel-sex-determining regions. 
 %Our results suggest that polymorphic loci that are ancestrally sex-linked and under sex-specific selection could also drive heterogametic transitions between sex-determination systems. 
@@
 In agreement with this hypothesis, a recent transcriptome analysis in \textit{Rumex} shows that Y-linked genes have higher expression in haploid pollen than autosomal genes \textcolor{red}{(check this is accurate)}.
-Interestingly, haploid-expression is also more common on the autosome that is orthologous to the sex chromosomes in closely related species suggesting that new sex chromosomes may have been favoured through their association with haploid selected alleles on these chromosomes \textcolor{red}{(Sandler et al., 2017, Personal Communication)}.
+Interestingly, haploid-expression is also more common on the autosome that is orthologous to the sex chromosomes in closely related species suggesting that new sex chromosomes may have been favoured through their association with haploid selected alleles on these chromosomes \textcolor{red}{(Sandler et al., 2018, Personal Communication)}.
+Because haploid selection can cause transitions that increase or decrease sex-linkage, we predict that haploid selection increases lability of sex-determination systems (e.g., the final state of the red line in Figure \ref{fig:SexRatioBad}B is the starting state in Figure \ref{fig:SexRatioBad}A).
+In particular, if haploid selection is strong but selective differences between male and female diploids are weak, we find that trans-GSD transitions (XY to ZW or ZW to XY) are favoured more strongly than cis-GSD transitions, with transitions to ESD intermediate (e.g., with $|D^\male - D^\female| << |\alpha_\Delta^\male - \alpha_\Delta^\female + t^\male - t^\female|$ we have $\lambda_{W',XY} > \lambda_{Y',XY}$; Equations \ref{eq:lambda_neoW} and \ref{eq:freq_diffs}).
+Turnovers driven by haploid selection may help to explain the relative rarity of heteromorphic sex chromosomes in plants, which are thought to experience more selection during their multicellular haploid stage.
+Furthermore, among the relatively few dioecious clades in which multiple species have well characterized sex chromosomes \citep{Ming:2011iy}, trans-GSD transitions have been inferred in \textit{Silene} subsection \textit{Otites} \citep{Slancarova:2013dq} and in \textit{Salicaceae} \citep{Pucholt2015,Pucholt2017}.
+%Potentially, successive heterogametic transitions between master regulators of sex-determination could be inferred from careful examination of the molecular pathways by which sex is determined. 
+%Our predictions could also be examined using a suitable proxy for haploid selection, for example, \cite{Lenormand:2005vb} use the outcrossing rate in plants as a proxy for the strength of pollen competition.
+Assuming that transitions from dioecy to hermaphroditism (equal parental investment in male and female gametes) are favoured in a similar manner to the ESD examined here (equal probability of zygotes developing as males or females), our results suggest that competition during the haploid stage could also drive transitions between dioecy and hermaphroditism, which are frequent in plants \citep{Kafer2017, Goldberg2017}.
+%In animals, one might expect gametic competition to be stronger in species where sperm is required to live for a long time after spermatogenesis because transcripts shared during spermatogenesis may become depleted, revealing the haploid phenotype of the sperm \citep{Immler:2014im}.
+%We would also expect that heterogametic transitions in sex determination would be more common in clades where there is meiotic drive.
 
@@
 In support of their role in sex chromosome turnover, genes expected to be under sexually-antagonistic selection (e.g., those causing bright male colouration) have been found on recently derived sex chromosomes \citep{Lindholm:2002dw,Tripathi:2009cw,Ser:2010iq}.
-Our results show that, if loci experiencing sexually-antagonistic selection and/or overdominance can be identified in close linkage with the ancestral sex-determining locus (rather than only the novel sex-determining locus), then they could also be implicated in driving heterogametic transitions between sex-determination systems and/or maintaining multiple sex-determining alleles.
+Our results show, however, that tight ancestral-linkage of polymorphic loci can also drive trans-GSD transitions. 
+In addition, we find that polymorphic sex determining systems (X, Y, W, and Z alleles present) can be maintained when a polymorphic selected locus is tightly linked to the ancestral sex-determining system (e.g., Figures \ref{fig:freqAll}B and \ref{fig:freqAll}C), which is not possible with loose linkage \citep{vanDoorn:2010hu}.
 %As noted by \citet{vanDoorn:2010hu}, it would be prudent to compare closely related clades in order to determine whether observed polymorphisms predate a transition in sex-determination or arose afterwards.
 %, particularly because sex-linkage allows sexually-antagonistic selection to maintain polymorphisms under a different and larger parameter space \citep{Rice:1987hs,Jordan:2011fj}.
-%Within a species, both feminizing and masculinizing alleles have been reported in houseflies \citep{Macdonald1978}, midges \citep{Thompson1971}, frogs \citep{Ogata:2007jm}, cichlid fish \citep{Ser:2010iq}, tilapia \citep{Lee2004}, sea bass \citep{Vandeputte2007}, and lab-strains of Zebrafish \citep{Liew2012,Wilson2014}.
 For example, our results suggest a potential mechanism maintaining multiple sex determining alleles in the platyfish (\textit{Xiphophorus maculatus}), in which X,Y, and W alleles segregate at one locus (or two closely-linked loci) near to potentially sexually-antagonistic genes for pigmentation and sexual maturity \citep{Kallman1965,Kallman1968, Volff2001, Schultheis2006}.
@@
 Previous theory would predict that the X$^\ast$ chromosome (or the autosome it is fused to) harbours female beneficial alleles, driving its spread. 
-However, XX and XX$^\ast$ females have similar fitness, whereas X$^\ast$Y female fitness is enhanced \citep{Saunders2014, Veyrunes2017}.
+However, XX and XX$^\ast$ females have similar fitness, whereas X$^\ast$Y female fitness is enhanced \citep{Saunders2014,Saunders2016, Veyrunes2017}.
 Although Y-linkage of female-beneficial alleles is counterintuitive, our tight linkage model suggests that it can be stably maintained and then favour new feminizing mutations, which is a parsimonious explanation for the spread of feminizing alleles in these rodent species.
@@
 %While not explicitly studied, we also predict that Y or W degeneration would prevent fixation of the new sex-determining genes considered here.
-Degeneration around the Y or W could explain why trans-GSD transitions are not observed to be much more common than cis-GSD transitions despite the fact that our models demonstrate that they are favoured under a wider range of conditions.
-For example, \citet{Vicoso:2015hf} found a dozen sex chromosome configurations among Dipteran species but only one transition between male and female heterogametey.
+Degeneration around the Y or W could explain why trans-GSD transitions are not observed to be much more common than cis-GSD transitions despite the fact that our models demonstrate that they are favoured under a wider range of conditions, especially with haploid selection.
+For example, \citet{Vicoso:2015hf} found a dozen sex chromosome configurations among Dipteran species but only one transition between male and female heterogamety.
+
+%Limitation 3: don't consider m alleles with similar k to ancester, no ancestral ESD considered
+In this study, we have only considered neo-sex-determining alleles of large effect. 
+However, we expect similar selective forces to act on masculinizing/feminizing alleles of weaker effect. 
+For example, \citet{Muralidhar2018} consider small effect masculinizing/feminizing alleles within a threshold model of sex determination, finding that they can be favoured when linked to loci that experience sexually-antagonistic selection.
+These results echo those for large-effect neo-Y/neo-W alleles \citep{vanDoorn:2007eu,vanDoorn:2010hu}.
+Finally, while we have considered cis-GSD, trans-GSD, and GSD to ESD transitions, we have not explicitly considered ESD to GSD transitions. 
+Recent models of ESD to GSD transitions \citep{Ubeda:2015fx,Muralidhar2018} show that that neo-Y/neo-W alleles can be favoured when they arise near to haploid and/or diploid selected loci, which also occurs in our model.
 
 %Limitation 2: TWO ALLELE DRIVE
-Another simplification that we made is that meiotic drive involves only a single locus with two alleles. 
-However, many meiotic drive systems involve an interaction with another locus at which alleles may `suppress' the action of meiotic drive \citep[][]{Burt:2006,Lindholm:2016cw}.
-Thus, the dynamics of meiotic drive alleles can be heavily dependent on the interaction between two loci and the recombination rate between them, which in turn can be affected by sex-linkage if there is reduced recombination between sex chromosomes \citep{Hurst:1991uh}.
-Furthermore, in some cases, a driving allele may act by killing any gametes that carry a `target' allele at another locus, in which case there can be fertility effects that alter the equilibrium frequency of a meiotic drive allele \citep{Holman:2015en}.
-In polygamous mating systems, the intensity of pollen/sperm competition can depend on the density of males available to donate pollen/sperm, which can itself depend on the sex ratio \citep{Taylor:2002wu}.
-In terms of our model, this implies that the strength of gametic competition ($t^\male$) may both determine and be determined by the sex ratio. 
-How the evolution of new sex-determining mechanisms could be influenced by two-locus meiotic drive and/or by ecological feedbacks under different mating systems remains to be studied.
+%Another simplification that we made is that meiotic drive involves only a single locus with two alleles. 
+%However, many meiotic drive systems involve an interaction with another locus at which alleles may `suppress' the action of meiotic drive \citep[][]{Burt:2006,Lindholm:2016cw}.
+%Thus, the dynamics of meiotic drive alleles can be heavily dependent on the interaction between two loci and the recombination rate between them, which in turn can be affected by sex-linkage if there is reduced recombination between sex chromosomes \citep{Hurst:1991uh}.
+%Furthermore, in some cases, a driving allele may act by killing any gametes that carry a `target' allele at another locus, in which case there can be fertility effects that alter the equilibrium frequency of a meiotic drive allele \citep{Holman:2015en}.
+%In polygamous mating systems, the intensity of pollen/sperm competition can depend on the density of males available to donate pollen/sperm, which can itself depend on the sex ratio \citep{Taylor:2002wu}.
+%In terms of our model, this implies that the strength of gametic competition ($t^\male$) may both determine and be determined by the sex ratio. 
+%How the evolution of new sex-determining mechanisms could be influenced by two-locus meiotic drive and/or by ecological feedbacks under different mating systems remains to be studied.
 
@@
 We conclude that haploid selection should be considered as a pivotal factor driving transitions between sex-determination systems. 
-Perhaps counterintuitively, transitions involving haploid selection can be driven by sex-ratio selection or cause sex-ratio biases to evolve. 
+Perhaps counterintuitively, transitions involving haploid selection can be driven by sex ratio selection or cause sex ratio biases to evolve. 
 Overall, our results suggest several new scenarios under which new sex-determination systems are favoured, which could help to explain why the evolution of sex-determination systems is so dynamic. 
@@
 %In particular, closer linkage between a sex-determining locus and a selected locus is not always favoured during heterogametic transitions when there is haploid selection. 
-%Secondly, even though haploid selection is a source of zygotic sex-ratio biases, in our models Fisherian sex-ratio selection does not have good explanatory power in determining whether various sex-determination systems evolve.
-%This result is surprising given that sex ratios are ultimately determined via the sex-determination system, and leads us to the conclusion that three selective forces -- haploid, diploid, and sex-ratio selection -- should all be considered when exploring transitions between sex-determination systems.
+%Secondly, even though haploid selection is a source of zygotic sex ratio biases, in our models Fisherian sex ratio selection does not have good explanatory power in determining whether various sex-determination systems evolve.
+%This result is surprising given that sex ratios are ultimately determined via the sex-determination system, and leads us to the conclusion that three selective forces -- haploid, diploid, and sex ratio selection -- should all be considered when exploring transitions between sex-determination systems.
 
@@
 %\caption{
-%Sex-ratio selection alone is not a good predictor of turnover between sex-determining systems.
+%Sex ratio selection alone is not a good predictor of turnover between sex-determining systems.
 %In panels A and C, male drive in an ancestral XY system causes a male bias, allowing a neo-W to invade and fix (causing the Y to fix in females), which balances the sex ratio (it also avoids selection in males, and thus makes better females in this case of sex-specific ploidally-antagonistic selection).
@@
 %Haploid selection affects the conclusions outlined above by altering the zygotic sex ratio and exerting direct selection on neo-W haplotypes.
-%The effect of sex-ratio selection is straightforward and can be seen in equation \eqref{Binvasion}, where male drive and gamete competition for $a$ (which is fixed on the Y and therefore causes a male bias) increases all four terms.
+%The effect of sex ratio selection is straightforward and can be seen in equation \eqref{Binvasion}, where male drive and gamete competition for $a$ (which is fixed on the Y and therefore causes a male bias) increases all four terms.
 %Direct selection on neo-W haplotypes can also be seen in equation \eqref{Binvasion} by noticing that increasing female drive in favour of $A$ increases the neo-W-$A$ haplotype growth rate ($\lambda_{mA}$) while female drive and gamete competition in favour of $a$ increases the neo-W-$a$ haplotype growth rate ($\lambda_{ma}$).
@@
 
-As with equilibrium (B), haploid selection again modifies invasion fitnesses by altering the sex-ratio and the diploid genotypes of females and directly selecting upon female gametes.
+As with equilibrium (B), haploid selection again modifies invasion fitnesses by altering the sex ratio and the diploid genotypes of females and directly selecting upon female gametes.
 The only difference is that resident XX females are no longer always homozygote $AA$ and males are no longer always heterozygote $Aa$.
@@
 Male haploid selection in favour of the $a$ allele ($\alpha_{\Delta}^\male<0$, $w_{A}^\male<w_{a}^\male$) generates male-biased sex ratios at equilibria (A) and (B), where Y-$a$ is fixed ($\hat{p}_{Y}^\male=0$).
-Male-biased sex-ratios facilitate the spread of neo-W-$A$ and neo-W-$a$ haplotypes (increasing $\lambda_{WA}$ and $\lambda_{Wa}$). 
+Male-biased sex ratios facilitate the spread of neo-W-$A$ and neo-W-$a$ haplotypes (increasing $\lambda_{WA}$ and $\lambda_{Wa}$). 
 Panels A-C in Figures \ref{fig:regionMaleDrive} and \ref{fig:regionMaleGS} show that neo-W haplotypes tend to spread for a wider range of parameters when sex ratios are male biased, compared to Figure \ref{fig:regionplots} without haploid selection.
@@
 Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in Figure \ref{fig:regionMaleDrive}. 
-The $a$ allele is favoured during male gametic competition in Panels A-C ($w_{a}^\male=1.16$, $w_{A}^\male=1$), which creates male biased sex-ratios and increases $\lambda_{WA}$ and $\lambda_{Wa}$. 
+The $a$ allele is favoured during male gametic competition in Panels A-C ($w_{a}^\male=1.16$, $w_{A}^\male=1$), which creates male biased sex ratios and increases $\lambda_{WA}$ and $\lambda_{Wa}$. 
 On the other hand, the $A$ allele is favoured during male gametic competition in Panels D-F ($w_{a}^\male=1$, $w_{A}^\male=1.16$) and $\lambda_{WA}$ and $\lambda_{Wa}$ tend to be reduced. 
@@
 Black $R=1/1000$, Red $R=2/100$, Blue $R=1/10$, Green $R=1/2$.  
-Dashed line in E-H gives ``fixation" of neo-W (all females heterozygous ZW).
+%Dashed line in E-H gives ``fixation" of neo-W (all females heterozygous ZW).
 }
@@
 \caption{
-Dynamics of sex-determining alleles during invasion by a neo-W allele. 
-The curves show the frequencies of the neo-W (red), ancestral-Y (Blue), and $A$ allele among female gametes (solid curves) and among male gametes (dashed curves). 
+Fixation of neo-W or maintenance of multiple sex-determining systems. 
+The curves show the frequencies of the neo-W (red), ancestral-Y (blue), and $A$ allele (black) among female gametes (solid curves) and among male gametes (dashed curves). 
 In panel A, there is a complete transition from XY sex determination (XX-ZZ females and XY-ZZ males) to ZW sex determination (YY-ZW females and YY-ZZ males).  

### 2018-01-17 LaTeX/Turnover.tex
added most Sally edits for main text Model and Results

@@
 For example, haploid selection in males only is represented by the dashed circle.  
-If X or Y alleles are associated with alleles that experience haploid selection in males ($r<1/2$), then zygotic sex ratios can become biased because either X or Y male gametes/gametophytes will be abundant after haploid selection.
+If X or Y alleles remain associated with alleles that experience haploid selection in males ($r<1/2$), then zygotic sex ratios can become biased because either X or Y male gametes/gametophytes will be abundant after haploid selection.
 However, the zygotic sex ratio is not biased by male haploid selection in ZW sex-determination systems. 
@@
 Furthermore, if the $m$ allele is fully epistatically dominant over the ancestral sex-determining system, phenotypes are not affected by the genotype at the ancestral sex-determining region (\textbf{X} locus).
-Thus, the invasion of rare dominant neo-Y or neo-W alleles is determined by the largest eigenvalue that solves a quadratic characteristic polynomial,
-%\textcolor{red}{Mention the possibility that the other roots yield the leading eigenvalue somewhere.}
-%\textcolor{blue}{following the logic above, it seems like we say we go from 8 eqns to 4 eqns by considering only one sex, and then from 4 eqns to 2 eqns by ignoring the ancestral SD allele.
-why then do we have the two quadratic problem?
-(b/c the $m$ alleles can arise in either sex?)}
-$\lambda^2+ b \lambda + c =0$ \textcolor{blue}{(see Appendix for a discussion of other roots - or Sally's proof!)}.
-%\begin{equation}
-%\lambda^2+ b \lambda + c =0
-%\label{eq:charpoly_neoY}
-%\end{equation}
-%
-%\noindent
-%where $b$ is the average of the growth rates of the two haplotypes that carry the $m$ allele ($mA$ and $ma$), $b=(\lambda_{mA}+\lambda_{ma})/2$, and $c$ also involves the fitness of $m$ alleles when they recombine onto the other \textbf{A} background in a heterozygote, $c=\lambda_{mA}\lambda_{ma}+\chi_{mA}\chi_{ma}$ (see table \ref{tab:haplotype_growth}).
-%Here, $b= - (\lambda_{mA} + \lambda_{ma})$ and $c = \lambda_{mA} \lambda_{ma} -\chi_{mA} \chi_{ma}$, where $\lambda_{mi}$ is the (multiplicative) growth rate of mutant haplotypes on background $i\in\{A,a\}$, accounting for loss due to recombination, and $\chi_{mi}$ is the rate of addition of mutant haplotypes onto background $i\in\{A,a\}$ due to recombination (see table \ref{tab:haplotype_growth}).
-Here, $b= - (\lambda_{mA} + \lambda_{ma})+(\chi_{mA} + \chi_{ma})$ and $c = (\lambda_{mA}-\chi_{mA}) (\lambda_{ma}-\chi_{ma}) -\chi_{mA} \chi_{ma}$, where $\lambda_{mi}$ is the multiplicative growth rate of mutant haplotypes on background $i\in\{A,a\}$, without accounting for loss due to recombination, and $\chi_{mi}$ is the rate at which mutant haplotypes on background $i\in\{A,a\}$ recombine onto the other \textbf{A} locus background in heterozygotes (see Table \ref{tab:haplotype_growth}).
+Thus, the invasion of rare dominant neo-Y or neo-W alleles is determined by the largest eigenvalue that solves the quadratic, $\lambda^2+ b \lambda + c =0$ \textcolor{blue}{(see Appendix for a discussion of other roots - or Sally's proof!)}.
+Here, $b= - (\lambda_{mA} + \lambda_{ma})+(\chi_{mA} + \chi_{ma})$ and $c = (\lambda_{mA}-\chi_{mA}) (\lambda_{ma}-\chi_{ma}) -\chi_{mA} \chi_{ma}$, where $\lambda_{mi}$ is the multiplicative growth rate (which we will call the ``haplotypic growth rate'') of the neo-sex determination allele $m$ on background $i$ without accounting for loss due to recombination, and $\chi_{mi}$ is the rate at which mutant haplotypes on background $i\in\{A,a\}$ recombine onto the other \textbf{A} locus background in heterozygotes (see Table \ref{tab:haplotype_growth}).
 The $\lambda_{mi}$ and $\chi_{mi}$, and thus the spread of the mutant $m$ allele, depend on the frequency of alleles at the \textbf{A} and \textbf{X} loci in the ancestral population. 
@@
    \noalign{\vskip 0.5ex}
-   neo-Y ($k=0$) \\ [0.5ex] \hline \noalign{\vskip 1ex}
-  $\lambda_{mA} = \left( 2 \zeta \right)^{-1} \left[\hat{p}_X^\female w_{A}^{\female} w_{A}^{\male} w_{AA}^{\male} + (1-\hat{p}_X^\female) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} (1+\alpha_{\Delta}^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right) $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\lambda_{ma} = \left( 2 \zeta \right)^{-1} \left[(1-\hat{p}_X^\female) w_{a}^{\female} w_{a}^{\male} w_{aa}^{\male} + \hat{p}_X^\female w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male}(1 - \alpha_{\Delta}^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\chi_{mA} = R \left( 2 \zeta \right)^{-1} \left[ (1-\hat{p}_X^\female) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} (1+\alpha_{\Delta}^{\male}) \right]/  \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right)   $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\chi_{ma} = R \left( 2 \zeta \right)^{-1} \left[   \hat{p}_X^\female w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male} (1 - \alpha_\Delta^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right)  $\\ [1ex] \hline
+   $m$ is a neo-Y ($k=0$) \\ [0.5ex] \hline \noalign{\vskip 1ex}
+  $\lambda_{YA} = \left( 2 \zeta \right)^{-1} \left[\hat{p}_X^\female w_{A}^{\female} w_{A}^{\male} w_{AA}^{\male} + (1-\hat{p}_X^\female) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} (1+\alpha_{\Delta}^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right) $\\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\lambda_{Ya} = \left( 2 \zeta \right)^{-1} \left[(1-\hat{p}_X^\female) w_{a}^{\female} w_{a}^{\male} w_{aa}^{\male} + \hat{p}_X^\female w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male}(1 - \alpha_{\Delta}^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\chi_{YA} = R \left( 2 \zeta \right)^{-1} \left[ (1-\hat{p}_X^\female) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} (1+\alpha_{\Delta}^{\male}) \right]/  \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right)   $\\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\chi_{Ya} = R \left( 2 \zeta \right)^{-1} \left[   \hat{p}_X^\female w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male} (1 - \alpha_\Delta^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right)  $\\ [1ex] \hline
   \noalign{\vskip 0.5ex}
-  neo-W ($k=1$) \\ [0.5ex] \hline \noalign{\vskip 1ex}
-  $\lambda_{mA} = \left[ 2 (1 - \zeta) \right]^{-1} \left[ \bar{p}^{\male} w_{A}^{\male} w_{A}^{\female} w_{AA}^{\female}+(1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female}(1+\alpha_{\Delta}^{\female})\right]/ \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\lambda_{ma} = \left[ 2 (1 - \zeta) \right]^{-1} \left[ (1-\bar{p}^{\male}) w_{a}^{\male} w_{a}^{\female} w_{aa}^{\female}+\bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female}(1-\alpha_{\Delta}^{\female})\right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\chi_{mA} = R \left[ 2 (1 - \zeta) \right]^{-1} \left[ (1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female} (1+\alpha_{\Delta}^{\female}) \right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \right)  $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\chi_{ma} = R \left[ 2 (1 - \zeta) \right]^{-1} \left[ \bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female} (1-\alpha_{\Delta}^{\female}) \right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \right) $\\ [1ex]
+  $m$ is a neo-W ($k=1$) \\ [0.5ex] \hline \noalign{\vskip 1ex}
+  $\lambda_{WA} = \left[ 2 (1 - \zeta) \right]^{-1} \left[ \bar{p}^{\male} w_{A}^{\male} w_{A}^{\female} w_{AA}^{\female}+(1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female}(1+\alpha_{\Delta}^{\female})\right]/ \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\lambda_{Wa} = \left[ 2 (1 - \zeta) \right]^{-1} \left[ (1-\bar{p}^{\male}) w_{a}^{\male} w_{a}^{\female} w_{aa}^{\female}+\bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female}(1-\alpha_{\Delta}^{\female})\right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\chi_{WA} = R \left[ 2 (1 - \zeta) \right]^{-1} \left[ (1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female} (1+\alpha_{\Delta}^{\female}) \right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \right)  $\\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\chi_{Wa} = R \left[ 2 (1 - \zeta) \right]^{-1} \left[ \bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female} (1-\alpha_{\Delta}^{\female}) \right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \right) $\\ [1ex]
   \hline \hline 
@@
 %If the average change in frequency of the two haplotypes that carry the $m$ allele ($Am$ and $am$) is positive, invasion will always occur, i.e., if $(\lambda_{mA} + \lambda_{ma})/2 > 1$ then $\lambda > 1$.
-Given the characteristic polynomial $f(\lambda)=\lambda^2+b\lambda+c$ and the Perron-Forbenius theorem (guaranteeing that the leading eigenvalue is positive, unique, and real), at least one solution to $f(\lambda)=0$ is greater than one when the polynomial has a negative slope or negative value at $\lambda=1$ ($f'(1) = 2 + b < 0$ or $f(1) = 1 + b + c < 0$).
-% $(\lambda_{mA} - \chi_{mA}) + (\lambda_{ma} -  \chi_{ma}) > 2$.
-%In words, the neo-sex-determining allele will certainly spread when the average change in its frequency, taking into account that recombination breaks up mutant $mi$ haplotypes (at rate $\chi_{mi}$) but ignoring the fact that recombination also creates mutant haplotypes, is positive.
-%When this does not hold ($2+b>0$), we can still have one $\lambda$ greater than one when 1 + b + c < 0.
-Regardless the rate of recombination, at least one of these conditions is true if both haplotypes can spread ($\lambda_{mA}, \lambda_{ma} > 1$) and neither can be true if neither haplotype can spread ($\lambda_{mA}, \lambda_{ma} < 1$).
-%If both haplotypes can spread ($\lambda_{mA}, \lambda_{ma} > 1$), this condition becomes $\chi_{mA}/(\lambda_{mA} - 1) + \chi_{ma}/(\lambda_{ma} -  1) > 1$.
-If only one haplotype can spread then the new sex-determining allele increases in frequency on one \textbf{A} background and declines on the other.
-%Considering an alternative polynomial $g(\lambda)=\lambda^2+b\lambda+C$, with $C=(\lambda_{mA}-\chi_{mA})(\lambda_{ma}-\chi_{ma})$, we have $g(\lambda)=(\lambda_{mA} - \chi_{mA} - \lambda)(\lambda_{ma} - \chi_{ma} - \lambda)$ and, since $\chi_{mi}\leq0$, we also have $f(\lambda)<g(\lambda)$.
-%Thus if $f'(1)=2+b<0$ and only one $\lambda_{mi}$ is greater than one we are guaranteed that $f(1)<g(1)<0$.
-%Therefore, if only one haplotype can spread, invasion is completely determined by $f(1)<0$, which in this case can be rewritten
-Invasion then occurs if
+The leading eigenvalue solves $f(\lambda)=\lambda^2+b\lambda+c=0$ and the Perron-Frobenius theorem guarantees that the leading eigenvalue is positive, unique, and real.  
+Since $f(\lambda_{mA})$ and $f(\lambda_{ma})$ are of opposite signs, the leading eigenvalue must fall between these two quantities and is the larger of them when $R = 0$.  
+Consequently, if both $\lambda_{mA}$ and $\lambda_{ma}$ are greater than one, then the leading eigenvalue will always be greater than one, regardless of the linkage between the neo-sex determination factor and the selected locus ($R$).
+In particular, having $\lambda_{mA} >1$ and $\lambda_{ma}>1$ thus guarantees that an unlinked sex determining factor can invade ($R=1/2$).  
+Conversely, if both $\lambda_{mA}$ and $\lambda_{ma}$ are smaller than one, then invasion can never occur.  
+Finally, if only one of  $\lambda_{mA}$ and $\lambda_{ma}$ is greater than one, the new sex determining factor can always invade when tightly linked to the selected locus ($R$ near 0).  
+Furthermore, it can be shown that the leading eigenvalue declines with $R$, and invasion requires that $R$ is sufficiently small that the following condition holds: 
 \begin{equation}\label{eq:lambdasGen}
@@
 \end{equation}
-\noindent For example, if we assume that only the $mA$ haplotype has a positive growth rate whe $R=0$ ($\lambda_{ma}<1<\lambda_{mA}$), the first term on the left-hand side of \eqref{eq:lambdasGen} is negative and invasion requires that the growth rate of $mA$ haplotypes ($\lambda_{mA}-1$) and the rate at which they are produced by recombination in $ma$ haplotypes ($\chi_{ma}$) are sufficiently large relative to the rate of decline of $ma$ haplotypes ($1-\lambda_{ma}$) and the rate of loss of $mA$ haplotypes due to recombination ($\chi_{mA}$).
-%\textcolor{blue}{i've updated this section with the correct $\lambda$ and $\chi$ terms.
-still a bit funny that not guaranteed invasion when both lambdas greater than one, and when both are greater than one then the condition above, (1), has the inequality flipped, which makes no sense (no invasion if no recombination despite both haplotypes growing).
-perhaps i made a mistake somewhere?
-see turnoverhomhet.nb}
+\noindent 
+This condition may or may not be satisfied for the full range of locations of the new sex determining factor, including $R=1/2$, depending on the nature of selection.  
+Interpreting this condition, if we assume that only the $mA$ haplotype has a positive growth rate when $R=0$, $\lambda_{ma}<1<\lambda_{mA}$, the first term on the left-hand side of \eqref{eq:lambdasGen} is negative and invasion requires that the $mA$ haplotype growth rate ($\lambda_{mA}-1$) and the rate at which they are produced by recombination in $ma$ haplotypes ($\chi_{ma}$) are sufficiently large relative to the $ma$ haplotype rate of decline ($1-\lambda_{ma}$) and the rate of loss of $mA$ haplotypes due to recombination ($\chi_{mA}$).
 %In other words, invasion requires that the average growth rate of the two haplotypes, weighted by the rates they are created by recombination, is positive.
@@
 However, the spread of a neo-Y (neo-W) also depends on the male (female) fitness of associated alleles (see terms involving equilibrium allele frequencies, $\hat{p}$'s).
-%, see terms in curly brackets.
 Second, invasion by a neo-Y (neo-W) allele does not directly depend on the fitness of female (male) diploids. %(for a given set of equilibrium allele frequencies).
-%involve any female (male) diploid selection terms ($w_{g}^{\female}$)
 This is because a dominant neo-Y (neo-W) is always found in males (females), and therefore the frequency of the neo-Y (neo-W) allele, $m$, only changes in males (females), Figure \ref{fig:model_outline}C,D.
-%Therefore, invasion by a neo-Y allele does not involve any female diploid selection terms ($w_{g}^{\female}$). 
-%Similarly, invasion by a neo-W is driven by the fitness of female gametes and diploids and does not involve any direct selection in male diploids. 
 Finally, invasions by a neo-Y and a neo-W are qualitatively different.
@@
 Consequently, neo-W bearing females obtain a differerent frequency of $A$ alleles from mating (when $\hat{p}_X^\male \neq \hat{p}_Y^\male$) compared to ancestral ($MM$) females.
-%\textcolor{blue}{nice}
-%the diploid fitness terms in Table \ref{tab:haplotype_growth} are weighted by the probability of producing those genotypes through matings with gametes of the opposite sex. 
-%For example, matings between a neo-Y-bearing male gamete and an $A$-bearing female gamete occur with probability $\hat{p}_X^\female w_{A}^{\female}/\bar{w}_{H}^{\female}$. 
-%This is the same probability that an ancestral-Y-bearing male gamete will inherit an $A$ allele via mating with a female gamete. 
-%On the other hand, 
-%The probability that a neo-W bearing female gamete mates with an $A$-bearing male gamete is $\bar{p}^{\male} w_{A}^{\male}/\bar{w}_{H}^{\male}$, where $\bar{p}^{\male}=\hat{p}_Y^\maleq+\hat{p}_X^\male(1-q)$ is the frequency of the A allele among both X- and Y-bearing male gametes.
-%That is, in the case of a neo-W, female diploids can result from matings with either an X-bearing or a Y-bearing sperm, resulting in zygotes that will develop as females. 
-%However, females that do not carry the neo-W only result from matings with X-bearing sperm. 
-%Therefore, eggs with and without a neo-W can differ in the frequency of $A$ alleles they obtain from matings with male gametes. 
-%Invasions by a neo-Y and a neo-W differ in this respect because sperm with or without a neo-Y allele both mate with X-bearing female gametes only.
-
-% invasion is driven by the fitness of male gametes and diploids, where the latter is weighted by the chance that a female egg will give rise to that diploid. 
-%For example, matings with $A$-bearing female gametes occur with probability $\hat{p}_X^\female w_{A}^{\female}/\bar{w}_{H}^{\female}$. 
-%Since a neo-Y is always found in males, the allele frequencies at the neo-Y (\textbf{M}) locus only change in males. 
-%Therefore, invasion by a neo-Y allele does not involve any female diploid selection terms ($w_{g}^{\female}$). 
-%Similarly, invasion by a neo-W is driven by the fitness of female gametes and diploids and does not involve any direct selection in male diploids.
-%However, in the case of a neo-W, female diploids can result from matings with either an X-bearing or a Y-bearing sperm. 
-%In either case, the zygote will develop as a female due to the presence of a neo-W. 
-%For example, neo-W females will inherit an $A$ allele from a male gamete with probability $\bar{p}^{\male} w_{A}^{\male}/\bar{w}_{H}^{\male}$, where $\bar{p}^{\male}=\hat{p}_Y^\maleq+\hat{p}_X^\male(1-q)$ is the frequency of the A allele among both X- and Y-bearing male gametes.
-%By contrast, females that do not carry the neo-W only result from matings with X-bearing sperm. 
-%They will therefore inherit an $A$ from a male gamete with probability $(1-q)\bar{p}_{X}^{\male} w_{A}^{\male}/\bar{w}_{H}^{\male}$. 
-%If the \textbf{A} locus is initially linked to the ancestral sex-determining locus, \textbf{X}, the frequency of the $A$ allele among X- and Y-bearing sperm can differ (equation \ref{eq:freq_diffs}).
-%Thus, eggs with and without a neo-W differ in the frequency of $A$ alleles they obtain from mating with male gametes.
 
@@
 (1) the \textbf{A} locus is within (or tightly linked to) the non-recombining region around the ancestral SDR ($r \approx 0$) or (2) selection is weak relative to recombination ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon<<1$).
-%These equilibrium allele frequencies and their stability conditions are given in the appendix. 
-%Considering diploid selection only, \citet{vanDoorn:2007eu,vanDoorn:2010hu} analytically calculated these allele frequencies assuming weak selection and relatively loose linkage (assumption 2 above).
-%We first consider the spread of neo-sex determining loci when the ancestral sex-determining locus is tightly linked to the selected \textbf{A} locus (assumption 1) with or without haploid selection. 
-%We then use the weak selection approximation that was also used in \citet{vanDoorn:2007eu,vanDoorn:2010hu} except that we allow haploid selection on the \textbf{A} locus.
-
-%\textcolor{red}{Change to $\hat{p}$ throughout as we assume that allele frequencies change slowly such that lambda is unaffected}
-%\textcolor{blue}{how will we differentiate between equilibrium $p$ and non-equilibrium $p$? or is the point that we can only say anything when at equilibrium?}
-%\textcolor{red}{I think Sally's point is that the eigenvalue analysis only makes sense if the $p$'s are changing slowly relative to the frequency of the modifier.
-Therefore, even when we don't substitute in any equilibrium frequencies, it might be safest to think of them as equilibrium allele frequencies.
-}
-
-\subsubsection*{Tight linkage with the ancestral sex-determining region}
+
+\subsubsection*{Tight linkage with the ancestral sex-determining region ($r \approx 0$)}
 
@@
 We find that a neo-Y can never invade an ancestral XY system that already has tight linkage with the locus under selection ($r=0$, for details see supplementary \textit{Mathematica} file). 
-%When then neo-Y is also tightly linked ($R=0$) a neo-Y will either remain linked to the $A$ allele or to the $a$ allele and so invasion is given directly by the larger of $\lambda_{mA}$ or $\lambda_{ma}$.
-When $R=0$, a neo-Y haplotype with the same allele as the ancestral Y is neutral ($\lambda_{ma}=1$) and does not change in frequency.
-The other neo-Y haplotype will not spread ($\lambda_{mA}<1$) given that the initial equilibrium is stable. 
+When $R=0$, a neo-Y haplotype with the same allele as the ancestral Y is neutral ($\lambda_{Ya}=1$) and does not change in frequency.
+The other neo-Y haplotype will not spread ($\lambda_{YA}<1$) given that the initial equilibrium is stable. 
 Therefore, a neo-Y mutation cannot spread ($\lambda \leq 1$, regardless of $R$) in an ancestral XY system where selected loci are within or very near the non-recombining region around the SDR.
@@
 
-%\textcolor{blue}{I might be tempted to focus on the diploid selection only case here because this is a new/surprising result and we have less cool stuff to say about haploid selection beyond describing it affecting stuff (right?).
-I then might also leave the complication of whether there is a polymorphism on the X or not to the appendix???
-Attempt 1:}
-
-%\textcolor{blue}{
 Neo-W alleles, on the other hand, can invade an ancestral XY system under some conditions (the full invasion conditions are given in the appendix; equations \ref{Binvasion} and \ref{Ainvasion}). 
-Counterintuitively, selection on loci within the non-recombining region of the SDR can favour the invasion of a less closely linked neo-W, whether selection involves only sexual antagonism, or overdominance, or haploid selection is also present (e.g., Figures \ref{fig:SexAntagTighter}, \ref{fig:temporalOverdominance}, and \ref{fig:SexAntagTighterMaleDrive}).
-%Although haploid selection can favour neo-W alleles because the ancestral sex ratio becomes male biased, this is not the only circumstance in which less tightly linked neo-W alleles invade. 
-%\textcolor{red}{Sally: unpack, give one condition and relate to figures}
-%For example, we note that it is possible for both neo-W haplotypes to spread ($\lambda_{mA}>1$ and $\lambda_{ma}>1$), in which case neo-W invasion can occur regardless of linkage to the selected locus.
-%For example, unlinked neo-W alleles can invade in the absence of any haploid selection. 
-%This result is unexpected given the results of \cite{vanDoorn:2010hu}, who did not explicitly calculate equilibrium allele frequencies under tight linkage and generally concluded that heterogametic transitions can only occur when neo-sex-determining alleles are in tighter linkage with loci under sex-specific diploid selection.
-In fact, with tight linkage between the ancestral SDR and the selected locus, haploid selection and/or overdominance can favour completely unlinked neo-W alleles ($R=1/2$), allowing autosomes to become new sex chromosomes.
-To develop an intuition for how less closely linked neo-W alleles invade, we first focus on cases where there is no haploid selection and discuss the additional effect of haploid selection in the appendix.
-%}
-%Briefly, a neo-W can spread when the females it produces have higher fitness than the females produced under the ancestral SDR, which all have genotype XX.
-X chromosomes are sometimes found in males and therefore allele frequencies on the X can be suboptimal for females.
-In addition, the neo-W produces females from matings with Y-bearing male gametes.
-The allele associated with the Y can also be beneficial in females.
-%the neo-W invades under the ancestral XY sex-determining system, the X chromosome may not be able to as specialised on a female-beneficial allele
+Counterintuitively, selection on loci within the non-recombining region of the SDR can favour the invasion of a less closely linked neo-W, whatever the form of selection maintaining a polymorphism (sexually-antagonistic selection, overdominance, ploidally-antagonistic selection, or some combination, Figures \ref{fig:SexAntagTighter}, \ref{fig:temporalOverdominance}, \ref{fig:regionPloidAntag}, and \ref{fig:SexAntagTighterMaleDrive}).
+The conditions become more restrictive, however, with increasing recombination ($R$) between the new sex determining region and the selected locus.  
+The invasion of completely unlinked neo-W alleles ($R = 1/2$) can occur with overdominance in males or with haploid selection but is not possible with only sexually-antagonistic selection if selection is directional in each diploid sex (see Supplementary \textit{Mathematica} file).
+To develop an intuition for how less closely linked neo-W alleles invade ($R>r$), we first focus on cases where there is no haploid selection and discuss the additional effect of haploid selection in the appendix.
 
@@
 A very loosely linked neo-W does not spread in this case (blue and green lines overlap and go to 0). 
-Indeed, we can show that neo-W invasion fitness is always negative when $R=1/2$ and there is sex-antagonism but no haploid selection (see supplementary \textit{Mathematica} file). 
-Fitness parameters are shown by an asterisk in Figure \ref{fig:regionplots}A: $w_{AA}^\female = 1.05$, $w_{aa}^\male = 1.2$, $w_{aa}^\female = w_{AA}^\male = 0.85$, $w_{Aa}^\Hermaphrodite = 1$,  $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
+Fitness parameters are: $w_{AA}^\female = 1.05$, $w_{aa}^\male = 1.2$, $w_{aa}^\female = w_{AA}^\male = 0.85$, $w_{Aa}^\Hermaphrodite = 1$,  $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
 %\textcolor{red}{consider removing panel A, which is repeated in Figure 3.}
@@
 
-If we categorise the $a$ allele as being ancestrally `male-beneficial' via the fact that it is fixed on the Y, then $\lambda_{mA}>1$ indicates that the neo-W spreads when found with the ancestrally `female-beneficial' allele.
+If we categorise the $a$ allele as being ancestrally `male-beneficial' via the fact that it is fixed on the Y, then $\lambda_{WA}>1$ indicates that the neo-W spreads when found with the ancestrally `female-beneficial' allele.
 Broadly, this is possible because the ancestral X chromosome is sometimes found in males and is therefore unable to perfectly specialise on the `female-beneficial' allele. 
-For example, when the $a$ allele is favoured in males, a polymorphism of $A$ and $a$ alleles can be maintained on the X despite directional selection in favour of the $A$ allele in females ($s^\female>0$, $0<h^\female<1$), see outlined region in Figure \ref{fig:regionplots}A.
-When the $a$ allele is strongly favoured on X chromosomes in males ($w_{aa}$ sufficiently large relative to $w_{Aa}$), neo-W-$A$ haplotypes can spread ($\lambda_{mA}>1$), see grey region in Figure \ref{fig:regionplots}A.
-In this case the $a$ allele is at high frequency among ancestral XX females due to selection upon the X in males. 
-By contrast, W-$A$ haplotypes will only create females with high fitness ($AA$ or $Aa$ genotypes) and can therefore spread.
+For example, when the $a$ allele is favoured on the ancestral X in males, a polymorphism of $A$ and $a$ alleles can be maintained on the X despite directional selection in favour of the $A$ allele in females ($s^\female>0$, $0<h^\female<1$), see outlined region in Figure \ref{fig:regionplots}A.
+When the $a$ allele is strongly favoured on X chromosomes in males ($w_{aa}^\male$ sufficiently large relative to $w_{Aa}^\male$), neo-W-$A$ haplotypes can spread ($\lambda_{WA}>1$, see grey region in Figure \ref{fig:regionplots}A) because they produce hgher fitness females ($AA$ or $Aa$ genotypes) and are unleashed from counterselection in males.
 
@@
 Therefore, tightly sex-linked loci that experience sexually-antagonistic selection can drive trans-GSD transitions in which the neo-SDR is less closely linked to the locus under selection (Figure \ref{fig:SexAntagTighter}).
-%Prediction (just an idea), considering sexually antagonistic selection alone, we should observe an excess of transitions between XY and ZW systems on the same chromosome because the tight linkage results indicate that there can be selection for heterogametic transitions but only when the neo-SDR is relatively closely linked (but not necessarily more closely linked).
-
-Given that the $a$ allele can be considered ancestrally `male-beneficial' because it is fixed on the Y, it is surprising that neo-W-$a$ haplotypes can sometimes be favoured by selection in females ($\lambda_{ma}>1$).
+
+Given that the $a$ allele can be considered ancestrally `male-beneficial' because it is fixed on the Y, it is surprising that neo-W-$a$ haplotypes can sometimes be favoured by selection in females ($\lambda_{Wa}>1$).
 Again, this occurs because ancestral X's also experience selection in males, in which they will always be paired with a Y-$a$. 
@@
 Therefore, the X can be polymorphic or even fixed for the $A$ allele despite favouring the $a$ allele during selection in females \citep[e.g., see outlined region in Figure \ref{fig:regionplots}B and][]{Lloyd1977,Otto2014}.
-In such cases, neo-W-$a$ haplotypes can spread because they create more $Aa$ and $aa$ females when pairing with an X from males and because they bring Y-$a$ haplotypes into females (Figure \ref{fig:model_outline}D).
+In such cases, neo-W-$a$ haplotypes can spread because they create more $Aa$ and $aa$ females when pairing with an X from males and because they bring Y-$a$ haplotypes into females, where it has higher fitness (Figure \ref{fig:model_outline}D).
 
@@
 
-Assuming that linkage is not tight, \citet{vanDoorn:2010hu} showed that invasion by a neo-W occurs under the same conditions as `fixation' (where fixation indicates that the neo-W reaches its maximum frequency among eggs, which is 1/2).
+Assuming that linkage is not tight, \citet{vanDoorn:2010hu} showed that invasion by a neo-W occurs under the same conditions as `pseudo-fixation' (at pseudo-fixation the neo-W reaches its maximum frequency among eggs, which is 1/2).
 An equivalent analysis is not possible where we assume that linkage is tight. 
-However, numerical simulations with tight linkage demonstrate that the neo-SDR does not necessarily fix, leading to the stable maintenance of a mixed sex-determining system, in which X, Y, Z, and W alleles all segregate (e.g., Figure \ref{fig:freqAll}B,C).
+However, numerical simulations with tight linkage demonstrate that the neo-SDR does not necessarily reach pseudo-fixation, leading to the stable maintenance of a mixed sex-determining system, in which X, Y, Z, and W alleles all segregate (e.g., Figure \ref{fig:freqAll}B,C).
 
@@
 If $\lambda_{wA}$ or $\lambda_{wa}$ is greater than one, then a rare neo-W can spread for, at least, some values of $R>r$. 
-For the parameter values marked with an asterisk, example invasion dynamics are shown in Figure \ref{fig:SexAntagTighter}C. 
+The parameter values marked with an asterisk correspond to the fitnesses used in Figure \ref{fig:SexAntagTighter}C. 
 Where both $\lambda_{wA}$ and $\lambda_{wa}$ are greater than one, a neo-W will spread when rare, regardless of linkage with the selected locus (for any $R$). 
-Figure \ref{fig:positionOverdominance} shows two examples using the parameters marked with a dagger. 
+Figure \ref{fig:positionOverdominance} shows the dynamics using the parameters marked with a dagger. 
 Here, there is no haploid selection $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
@@
 %The equilibrium frequency of $A$ on different ancestral backgrounds ($\hat{p}^\male_Y$, $\hat{p}^\male_X$, and $\hat{p}^\female_X$) is given by equations \eqref{eq:pAve} and \eqref{eq:freq_diffs} where we assume selection and meiotic drive are weak relative to recombination ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon$).
-Assuming that selection is weak relative to all recombination rates ($r$, $R$ and $\rho$), we denote the leading eigenvalues describing the invasion of a neo-Y ($k=0$) and a neo-W ($k=1$) into an ancestrally XY system by $\lambda_{Y',XY}$ and $\lambda_{W',XY}$, respectively.
+Assuming that selection is weak ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon<<1$) and thus implicitly assuming that all recombination rates ($r$, $R$ and $\rho$) are large relative to selection, we denote the leading eigenvalues describing the invasion of a neo-Y ($k=0$) and a neo-W ($k=1$) into an ancestrally XY system by $\lambda_{Y',XY}$ and $\lambda_{W',XY}$, respectively.
 To leading order in selection, these are:
@@
 \noindent
-where $V_{A}=\bar{p}(1-\bar{p})$ is the variance in the equilibrium frequency of $A$ and $S_{A}=(D^\male +\alpha_{\Delta}^\male+t^\male) - (D^\female+\alpha_{\Delta}^\female+t^\female)$ describes sex differences in selection for the $A$ versus $a$ across diploid selection, meiosis, and gametic competition.
+where $V_{A}=\bar{p}(1-\bar{p})$ is the variance in the equilibrium frequency of $A$ and $S_{A}=(D^\male +\alpha_{\Delta}^\male+t^\male) - (D^\female+\alpha_{\Delta}^\female+t^\female)$ describes sex differences in selection for the $A$ versus $a$ allele across diploid selection, meiosis, and gametic competition.
 The diploid selection term, $D^\Hermaphrodite=\big{[} \bar{p}s^\Hermaphrodite+(1-\bar{p})h^\Hermaphrodite s^\Hermaphrodite\big{]} -\big{[} \bar{p}h^\Hermaphrodite s^\Hermaphrodite+(1-\bar{p}) \big{]}$, is the difference in fitness between $A$ and $a$ alleles in diploids of sex $\Hermaphrodite \in \{\female,\male\}$, where $\bar{p}$ is the leading-order probability of mating with an $A$-bearing gamete from the opposite sex (equation \ref{eq:pAve}).
@@
 If Fisherian sex ratio selection were dominant, we would expect a difference in the potential for XY to ZW and ZW to XY transitions. 
-However, to leading order with selection weak relative to recombination, we find that sex ratio selection favours the spread of a neo-W (through the first terms in table \ref{tab:haplotype_growth}) by an amount that is equal in magnitude to the fitness effects of alleles associated with new sex-determining alleles (second terms in table \ref{tab:haplotype_growth}).
-Thus, invasion by a neo-W into an XY system and invasion by a neo-Y into a ZW system occur under the same conditions ($\lambda_{Y',XY}=\lambda_{W',ZW}$ and $\lambda_{Y',ZW}=\lambda_{W',XY}$, at least to order $\epsilon^2$).
-For example, in Figure \ref{fig:SexRatioBad}B neo-W alleles invade an ancestral-XY system where females are initially rare.
-However, Figure \ref{fig:SexRatioBad}A shows that a neo-Y can invade an ancestral-ZW system under the same conditions. 
-In fact, where $R<1/2$ the neo-Y becomes associated with the male meiotic drive allele such that the zygotic sex ratio evolves to become biased towards males.
+%However, to leading order with selection weak relative to recombination, we find that sex ratio selection favours the spread of a neo-W by an amount equl to the spread of a neo-Y into a ZW system (relabeling XY as the heterogametic sex and reversing the labels of males and females in Table \ref{tab:specialcases})
+%However, to leading order with selection weak relative to recombination, we find that sex ratio selection favours the spread of a neo-W (through the first terms in table \ref{tab:haplotype_growth}) by an amount that is equal in magnitude to the fitness effects of alleles associated with new sex-determining alleles (second terms in table \ref{tab:haplotype_growth}).
+However, invasion by a neo-W into an XY system and invasion by a neo-Y into a ZW system occur under the same conditions ($\lambda_{Y',XY}=\lambda_{W',ZW}$ and $\lambda_{Y',ZW}=\lambda_{W',XY}$, at least to order $\epsilon^2$).
+For example, in Figure \ref{fig:SexRatioBad}A neo-W alleles invade an ancestral-XY system where females are initially rare.
+However, Figure \ref{fig:SexRatioBad}B shows that a neo-Y can invade an ancestral-ZW system under the same conditions. 
+As a consequence, whenever $R<1/2$, the neo-Y becomes associated with the male meiotic drive allele such that the zygotic sex ratio actually evolves to become biased towards males.
 
@@
 
-The green curves in Figure \ref{fig:SexRatioBad} show transitions between male and female heterogametey even though the new sex-determining region is unlinked to a locus that experiences haploid and diploid selection.
-We use these green curves to discuss why trans-GSD transitions can occur when $R=1/2$ and $r<1/2$, as in Table \ref{tab:specialcases}.
-In Figure \ref{fig:SexRatioBad}B, an unlinked neo-W can spread because the zygotic sex ratio is ancestrally male biased. 
-In Figure \ref{fig:SexRatioBad}A, an unlinked neo-Y spreads despite the fact that the ancestral zygotic sex ratio is even. 
-In this case, the male meiotic drive allele, $a$, is initially more common among ancestral-Z-bearing eggs than ancestral-W-bearing eggs because the Z is found in males more often than the W ($\hat{p}_{W}^\female-\hat{p}_{Z}^\female>0$, equation \ref{eq:freq_diffs}).
-%In this case, the ancestral male determining allele, Z, is initially associated with the male meiotic drive allele, $a$, because the Z is found in males more often than the W and $r<1/2$. 
-Polymorphism at the \textbf{A} locus is maintained by counter-selection against the $a$ allele in diploids and therefore ancestral-ZZ males have generally low diploid fitness. 
-The neo-Y spreads because it produces males with high diploid fitness through matings with ancestral-W-bearing female gametes, which are more likely to carry the $A$ allele ($\hat{p}_{W}^\female-\hat{p}_{Z}^\female>0$).
-A freely recombining neo-Y ($R=1/2$) is equally likely to be segregate with the $A$ or $a$ allele.
-Therefore, the neo-Y is unaffected by male meiotic drive against the $A$ alleles that it introduces into males. 
-Thus, a key factor in explaining why trans-GSD transitions can occur when $R>r$ is that the neo-SDR determines sex in the diploid phase but recombination occurs before any subsequent haploid selection.
-
-%Therefore Fisherian sex ratio selection directly favours neo-Ws by a similar magnitude. 
-%Perhaps surprisingly, neo-Ws can be favoured to the same degree by haploid selection in females when female haploid selection favours the alleles that tend to be carried by the neo-W.
-%Thus XY to ZW is the same as ZW to XY even though sex ratio biases only exist in one case, given the assumptions made in this section
+Why can new sex-determining regions invade when more loosely linked to selected loci ($R>r$)?  
+Consider first the case where both loci are linked to the selected locus ($r<R<1/2$). 
+In an XY system, haploid selection in males can facilitate the spread of a neo-W because the zygotic sex ratio is ancestrally biased and the W helps to equalize the sex ratio (Figure \ref{fig:SexRatioBad}A).
+A new sex determining region can also, however, benefit from becoming more associated with drive.  
+For example in a ZW system with the same selection regime (haploid selection in males), a neo-Y can spread despite the fact that the zygotic sex is initially even; in this case, the neo-Y spreads because it is often found in males and can, if it carries the driven allele $a$, benefit from haploid selection (Figure \ref{fig:SexRatioBad}B).
+While equalizing the sex ratio and benefiting from drive are two primary reasons why haploid selection spurs sex chromosome transitions, more complex situations also arise.  
+For example with $R=1/2$ in Figure \ref{fig:SexRatioBad}B (green curve), the neo-Y spreads despite the fact that it cannot benefit from drive because free recombination moves it randomly between driven and non-driven backgrounds.
+Nevertheless, the unlinked neo-Y can spread because diploids bearing it more often carry the non-driven allele $A$ found at high frequency on the W background, which has higher average diploid fitness to balance the haploid advantage of the $a$ allele at equilibrium.
+
+%The green curves in Figure \ref{fig:SexRatioBad} show transitions between male and female heterogametey even though the new sex-determining region is unlinked to a locus that experiences haploid and diploid selection.
+%We use these green curves to discuss why trans-GSD transitions can occur when $R=1/2$ and $r<1/2$, as in Table \ref{tab:specialcases}.
+%In Figure \ref{fig:SexRatioBad}B, an unlinked neo-W can spread because the zygotic sex ratio is ancestrally male biased. 
+%In Figure \ref{fig:SexRatioBad}A, an unlinked neo-Y spreads despite the fact that the ancestral zygotic sex ratio is even. 
+%In this case, the male meiotic drive allele, $a$, is initially more common among ancestral-Z-bearing eggs than ancestral-W-bearing eggs because the Z is found in males more often than the W ($\hat{p}_{W}^\female-\hat{p}_{Z}^\female>0$, equation \ref{eq:freq_diffs}).
+%Polymorphism at the \textbf{A} locus is maintained by counter-selection against the $a$ allele in diploids and therefore ancestral-ZZ males have generally low diploid fitness. 
+%The neo-Y spreads because it produces males with high diploid fitness through matings with ancestral-W-bearing female gametes, which are more likely to carry the $A$ allele ($\hat{p}_{W}^\female-\hat{p}_{Z}^\female>0$).
+%A freely recombining neo-Y ($R=1/2$) is equally likely to be segregate with the $A$ or $a$ allele.
+%Therefore, the neo-Y is unaffected by male meiotic drive against the $A$ alleles that it introduces into males. 
+%Thus, a key factor in explaining why trans-GSD transitions can occur when $R>r$ is that the neo-SDR determines sex in the diploid phase but recombination occurs before any subsequent haploid selection.
 
@@
 preventing associations from building up between allele $A$ and sex. 
-Equation \eqref{eq:lambda_ESD} shows that the neo-ESD gets half of the fitness of a feminizing mutation (neo-$W$) and half of the fitness of a masculinizing mutation (neo-$Y$), but only has an effect one half of the time (the other half of the time it produces the same sex as the ancestral system would have, to leading order).
+Equation \eqref{eq:lambda_ESD} shows that the neo-ESD gets half of the fitness of a feminizing mutation (neo-$W$) and half of the fitness of a masculinizing mutation (neo-$Y$), but only has an effect one half of the time (the other half of the time it produces the same sex as the ancestral system would have).
 As discussed above, $\lambda_{Y',XY\rvert R=1/2}$ is necessarily less than one, but $\lambda_{W',XY\rvert R=1/2}$ can be greater than one if there is haploid selection.
@@
 %With weak selection, these two forces are nearly equal in strength. 
-In addition, we note that ESD may not invade, even if the sex ratio is initially biased (e.g., with drive in males only, $r<1/2$, $h^\female=h^\male$, and $s^\female s^\male<0$, such that $\lambda_{W',XY}<1$, see Table \ref{tab:specialcases}).
-We conclude that, as with neo-W and neo-Y loci, associations with selection loci mean that the evolution of neo-ESD systems is not straightforwardly predicted by selection to balance the zygotic sex ratio.
+In addition, we note that ESD may not invade, even if the sex ratio is initially biased (e.g., with drive in males only, $r<1/2$, $h^\female=h^\male$, and $s^\female s^\male<0$, then $\lambda_{W',XY}<1$, see Table \ref{tab:specialcases}).
+We conclude that, as with neo-W and neo-Y loci, associations with selected loci mean that the evolution of neo-ESD systems is not straightforwardly predicted by selection to balance the zygotic sex ratio when haploid selection is present.
 
@@
 We find that the spread of neo-sex-determining systems cannot be simply predicted from their effect on the sex ratio. 
-On one hand, sex ratio biases caused by haploid selection can facilitate trans-GSD transitions between sex-determining systems, in agreement with Fisherian sex ratio selection. 
+On one hand, sex ratio biases caused by haploid selection can facilitate trans-GSD transitions or GSD-ESD transitions between sex-determining systems. 
 For instance, alleles favoured by haploid selection in males often become associated with the Y, which leads to a male-biased zygotic sex ratio.
@@
 %However, the neo-W may not equalize the sex ratio (e.g., if the driving allele also drives in females or affects competition among eggs)
-On the other hand, sex ratio selection can be overwhelmed by additional selective effects, preventing the neo-W from invading, even if it would balance the sex ratio (e.g., when selection acts in opposite directions in male and female diploids, Table \ref{tab:specialcases}).
+On the other hand, sex ratio selection can be overwhelmed by additional selective effects, preventing a neo-W or ESD allele from invading, even if it would balance the sex ratio (e.g., when selection acts in opposite directions in male and female diploids, Table \ref{tab:specialcases}).
 %and equalizing the sex ratio.
@@
 Interestingly, haploid-expression is also more common on the autosome that is orthologous to the sex chromosomes in closely related species suggesting that new sex chromosomes may have been favoured through their association with haploid selected alleles on these chromosomes \textcolor{red}{(Sandler et al., 2018, Personal Communication)}.
-Because haploid selection can cause transitions that increase or decrease sex-linkage, we predict that haploid selection increases lability of sex-determination systems (e.g., the final state of the red line in Figure \ref{fig:SexRatioBad}B is the starting state in Figure \ref{fig:SexRatioBad}A).
-In particular, if haploid selection is strong but selective differences between male and female diploids are weak, we find that trans-GSD transitions (XY to ZW or ZW to XY) are favoured more strongly than cis-GSD transitions, with transitions to ESD intermediate (e.g., with $|D^\male - D^\female| << |\alpha_\Delta^\male - \alpha_\Delta^\female + t^\male - t^\female|$ we have $\lambda_{W',XY} > \lambda_{Y',XY}$; Equations \ref{eq:lambda_neoW} and \ref{eq:freq_diffs}).
+%maybe add a flag here for switching to clade-level expectations:
+In general, we predict that haploid selection increases lability of sex-determination systems, particularly because haploid selection can cause transitions that increase or decrease sex-linkage (e.g., the final state of the red line in Figure \ref{fig:SexRatioBad}B is the starting state in Figure \ref{fig:SexRatioBad}A).
 Turnovers driven by haploid selection may help to explain the relative rarity of heteromorphic sex chromosomes in plants, which are thought to experience more selection during their multicellular haploid stage.
-Furthermore, among the relatively few dioecious clades in which multiple species have well characterized sex chromosomes \citep{Ming:2011iy}, trans-GSD transitions have been inferred in \textit{Silene} subsection \textit{Otites} \citep{Slancarova:2013dq} and in \textit{Salicaceae} \citep{Pucholt2015,Pucholt2017}.
+If haploid selection is strong but selective differences between male and female diploids are weak, we find that trans-GSD transitions (XY to ZW or ZW to XY) are favoured more strongly than cis-GSD transitions, with transitions to ESD intermediate (e.g., with $|D^\male - D^\female| << |\alpha_\Delta^\male - \alpha_\Delta^\female + t^\male - t^\female|$ we have $\lambda_{W',XY} > \lambda_{Y',XY}$; Equations \ref{eq:lambda_neoW} and \ref{eq:freq_diffs}).
+Among the relatively few dioecious clades in which multiple species have well characterized sex chromosomes \citep{Ming:2011iy}, trans-GSD transitions have been inferred in \textit{Silene} subsection \textit{Otites} \citep{Slancarova:2013dq} and in \textit{Salicaceae} \citep{Pucholt2015,Pucholt2017}.
 %Potentially, successive heterogametic transitions between master regulators of sex-determination could be inferred from careful examination of the molecular pathways by which sex is determined. 
@@
 Our results show, however, that tight ancestral-linkage of polymorphic loci can also drive trans-GSD transitions. 
-In addition, we find that polymorphic sex determining systems (X, Y, W, and Z alleles present) can be maintained when a polymorphic selected locus is tightly linked to the ancestral sex-determining system (e.g., Figures \ref{fig:freqAll}B and \ref{fig:freqAll}C), which is not possible with loose linkage \citep{vanDoorn:2010hu}.
+In addition, we find that polymorphic sex determining systems (X, Y, W, and Z alleles all present) can be maintained when a selected locus is tightly linked to the ancestral sex-determining system (e.g., Figures \ref{fig:freqAll}B and \ref{fig:freqAll}C), which is not possible with loose linkage \citep{vanDoorn:2010hu}.
 %As noted by \citet{vanDoorn:2010hu}, it would be prudent to compare closely related clades in order to determine whether observed polymorphisms predate a transition in sex-determination or arose afterwards.
@@
 We conclude that haploid selection should be considered as a pivotal factor driving transitions between sex-determination systems. 
-Perhaps counterintuitively, transitions involving haploid selection can be driven by sex ratio selection or cause sex ratio biases to evolve. 
+Perhaps counterintuitively, transitions involving haploid selection can be driven by sex ratio selection or cause sex ratio biases to evolve and Fisherian sex ratio selection is not an overwhelming force.
 Overall, our results suggest several new scenarios under which new sex-determination systems are favoured, which could help to explain why the evolution of sex-determination systems is so dynamic. 
@@
 A rare neo-Y or neo-W will spread from a given ancestral equilibrium when the leading eigenvalue, $\lambda$, of the Jacobian matrix derived from the eight mutant recursion equations (given by \ref{eq:recursions}c,d,g,h), evaluated at the ancestral equilibrium, is greater than one.
-However, because a neo-Y (neo-W) is always in males (females) and is epistatically dominant to the ancestral sex-determining locus, we need only two recursion equations (e.g., tracking the change in the frequency of neo-Y-$A$ and neo-Y-$a$ gametes from males) and thus the leading eigenvalue is the largest solution to a quadratic characteristic polynomial $\lambda^2 + b\lambda + c = 0$ as described in the text (Table \ref{tab:haplotype_growth}).
+However, because a neo-Y (neo-W) is always in males (females) and is epistatically dominant to the ancestral sex-determining locus, we need only two recursion equations (e.g., tracking the change in the frequency of neo-Y-$A$ and neo-Y-$a$ gametes from males) and thus the leading eigenvalue is the largest solution the polynomial $\lambda^2 + b\lambda + c = 0$ as described in the text (Table \ref{tab:haplotype_growth}).
 %It can be shown (see supplementary Mathematica file) that the coefficients are $b= - (\lambda_{mA} + \lambda_{ma})+(\chi_{mA} + \chi_{ma})$ and $c = (\lambda_{mA}-\chi_{mA}) (\lambda_{ma}-\chi_{ma}) -\chi_{mA} \chi_{ma}$, where $\lambda_{mi}$ is the multiplicative growth rate of the frequency of mutants on background $i\in\{A,a\}$, without accounting for loss due to recombination, and $\chi_{mi}$ is the rate at which mutants on background $i\in\{A,a\}$ recombine onto the other \textbf{A} locus background in heterozygotes.
@@
 
-Starting with the simpler equilibrium $(B)$, the terms of the characteristic polynomial are
+Starting with the simpler equilibrium $(B)$, the terms of that determine the leading eigenvalue are
 
@@
 
-\subsubsection*{Tight Linkage and Haploid Selection}
-
-With tight linkage, haploid selection generally expands the conditions under which neo-W alleles can spread. 
-For example, when selection is sexually-antagonistic in diploids ($s^\female s^\male <0$ and $0<h^\Hermaphrodite<1$) an unlinked neo-W ($R=1/2$) cannot invade unless there is also haploid selection (Figures \ref{fig:SexAntagTighter} and \ref{fig:SexAntagTighterMaleDrive}).
-Secondly, with haploid selection, overdominance ($w_{aa}^\Hermaphrodite<w_{Aa}^\Hermaphrodite$ \& $w_{AA}^\Hermaphrodite<w_{Aa}^\Hermaphrodite$) is not required for neo-W-$a$ haplotypes to spread ($\lambda_{ma}>1$) (Figures \ref{fig:regionMaleDrive}-\ref{fig:regionFemaleGS}).
-Haploid selection and overdominance allow unlinked neo-W alleles to invade even when there is tight linkage between the ancestral SDR and the selected locus (Figure \ref{fig:loose_invades_tight}).
-Finally, haploid selection can maintain a polymorphism in the face of directional selection in male and female diploids (ploidally-antagonistic selection). 
-When selection is ploidally-antagonistic, neo-W alleles often spread, for at least some values of $R$ (Figure \ref{fig:regionPloidAntag}).
-
-As discussed above, male haploid selection alters the sex ratio and the alleles carried by male gametes that female gametes pair with. 
+\subsubsection*{Role of Haploid Selection with Tight Linkage}
+
+Haploid selection generally expands the conditions under which neo-W alleles can spread within ancestral systems that have evolved tight linkage between the sex-determining locus and a selected locus ($r \approx 0$).
+First, haploid selection can allow a polymorphism to be maintained when it would not under diploid selection alone (e.g., with directional selection in diploids). 
+In cases of ploidally-antagonistic selection, where there is a balance between alleles favored in the haploid stage and the diploid stage, neo-W alleles - even unlinked alleles - can spread (Figure \ref{fig:regionPloidAntag}).
+Second, even when diploid selection could itself maintain a polymorphism, haploid selection can increase the conditions under which transitions among sex chromosomes are possible.
+Of particularly importance, when selection is sexually-antagonistic in diploids ($s^\female s^\male <0$ and $0<h^\Hermaphrodite<1$), an unlinked neo-W ($R=1/2$) cannot invade unless there is also haploid selection (see proof in supplementary \textit{Mathematica} file; Figures \ref{fig:SexAntagTighter} and \ref{fig:SexAntagTighterMaleDrive}).
+More generally, haploid selection alters the conditions under which neo-W chromosomes can spread (compare Figures \ref{fig:regionMaleDrive}-\ref{fig:regionFemaleGS} to Figure \ref{fig:regionplots}).
+
+%[SALLY:  I think that is enough, but we could add somewhere??: "Without haploid selection, unlinked neo-W alleles ($R=1/2$) can invade only under certain conditions, requiring either overdominance in males or underdominance in females (see proof in supplementary \textit{Mathematica} file).?
+Note that underdominance in females with directional selection in males can lead to the spread of unlinked neo-W?s, but only from equilB (only $\lambda_{ma}$ is greater than one in this case).]
+
 Male haploid selection in favour of the $a$ allele ($\alpha_{\Delta}^\male<0$, $w_{A}^\male<w_{a}^\male$) generates male-biased sex ratios at equilibria (A) and (B), where Y-$a$ is fixed ($\hat{p}_{Y}^\male=0$).
-Male-biased sex ratios facilitate the spread of neo-W-$A$ and neo-W-$a$ haplotypes (increasing $\lambda_{WA}$ and $\lambda_{Wa}$). 
+Male-biased sex-ratios facilitate the spread of neo-W-$A$ and neo-W-$a$ haplotypes (increasing $\lambda_{mA}$ and $\lambda_{ma}$). 
 Panels A-C in Figures \ref{fig:regionMaleDrive} and \ref{fig:regionMaleGS} show that neo-W haplotypes tend to spread for a wider range of parameters when sex ratios are male biased, compared to Figure \ref{fig:regionplots} without haploid selection.
-By contrast, male haploid selection in favour of the $A$ allele generates female-biased sex ratios and reduces $\lambda_{WA}$ and $\lambda_{Wa}$, as demonstrated by panels D-F in Figures \ref{fig:regionMaleDrive} and \ref{fig:regionMaleGS}.
+By contrast, male haploid selection in favour of the $A$ allele generates female-biased sex ratios and reduces $\lambda_{mA}$ and $\lambda_{ma}$, as demonstrated by panels D-F in Figures \ref{fig:regionMaleDrive} and \ref{fig:regionMaleGS}.
 
 Female haploid selection generates direct selection on the neo-W-$A$ and neo-W-$a$ haplotypes as they spread in females. 
-Thus, female haploid selection in favour of the $a$ allele tends to increase $\lambda_{Wa}$ and decrease $\lambda_{WA}$, as shown by panels A-C in Figures \ref{fig:regionFemaleDrive} and \ref{fig:regionFemaleGS}.
-Conversely, female haploid selection in favour of the $A$ allele increases $\lambda_{WA}$ and decreases $\lambda_{Wa}$, see panels D-F in Figures \ref{fig:regionFemaleDrive} and \ref{fig:regionFemaleGS}.
+Thus, female haploid selection in favour of the $a$ allele tends to increase $\lambda_{ma}$ and decrease $\lambda_{mA}$, as shown by panels A-C in Figures \ref{fig:regionFemaleDrive} and \ref{fig:regionFemaleGS}.
+Conversely, female haploid selection in favour of the $A$ allele increases $\lambda_{mA}$ and decreases $\lambda_{ma}$, see panels D-F in Figures \ref{fig:regionFemaleDrive} and \ref{fig:regionFemaleGS}.
+
+Thus, the impact of haploid selection on sex chromosome transitions must be considered as two sides of a coin: it can generate sex ratio biases that drive sex chromosome transitions to equalize the sex ratio, but it can also drive in new sex chromosomes and thereby cause sex ratios to become biased.
+
+%\subsubsection*{Tight Linkage and Haploid Selection}
+
+%With tight linkage, haploid selection generally expands the conditions under which neo-W alleles can spread. 
+%For example, when selection is sexually-antagonistic in diploids ($s^\female s^\male <0$ and $0<h^\Hermaphrodite<1$) an unlinked neo-W ($R=1/2$) cannot invade unless there is also haploid selection (Figures \ref{fig:SexAntagTighter} and \ref{fig:SexAntagTighterMaleDrive}).
+%Secondly, with haploid selection, overdominance ($w_{aa}^\Hermaphrodite<w_{Aa}^\Hermaphrodite$ \& $w_{AA}^\Hermaphrodite<w_{Aa}^\Hermaphrodite$) is not required for neo-W-$a$ haplotypes to spread ($\lambda_{ma}>1$) (Figures \ref{fig:regionMaleDrive}-\ref{fig:regionFemaleGS}).
+%Haploid selection and overdominance allow unlinked neo-W alleles to invade even when there is tight linkage between the ancestral SDR and the selected locus (Figure \ref{fig:loose_invades_tight}).
+%Finally, haploid selection can maintain a polymorphism in the face of directional selection in male and female diploids (ploidally-antagonistic selection). 
+%When selection is ploidally-antagonistic, neo-W alleles often spread, for at least some values of $R$ (Figure \ref{fig:regionPloidAntag}).
+
+%As discussed above, male haploid selection alters the sex ratio and the alleles carried by male gametes that female gametes pair with. 
+%Male haploid selection in favour of the $a$ allele ($\alpha_{\Delta}^\male<0$, $w_{A}^\male<w_{a}^\male$) generates male-biased sex ratios at equilibria (A) and (B), where Y-$a$ is fixed ($\hat{p}_{Y}^\male=0$).
+%Male-biased sex ratios facilitate the spread of neo-W-$A$ and neo-W-$a$ haplotypes (increasing $\lambda_{WA}$ and $\lambda_{Wa}$). 
+%Panels A-C in Figures \ref{fig:regionMaleDrive} and \ref{fig:regionMaleGS} show that neo-W haplotypes tend to spread for a wider range of parameters when sex ratios are male biased, compared to Figure \ref{fig:regionplots} without haploid selection.
+%By contrast, male haploid selection in favour of the $A$ allele generates female-biased sex ratios and reduces $\lambda_{WA}$ and $\lambda_{Wa}$, as demonstrated by panels D-F in Figures \ref{fig:regionMaleDrive} and \ref{fig:regionMaleGS}.
+
+%Female haploid selection generates direct selection on the neo-W-$A$ and neo-W-$a$ haplotypes as they spread in females. 
+%Thus, female haploid selection in favour of the $a$ allele tends to increase $\lambda_{Wa}$ and decrease $\lambda_{WA}$, as shown by panels A-C in Figures \ref{fig:regionFemaleDrive} and \ref{fig:regionFemaleGS}.
+%Conversely, female haploid selection in favour of the $A$ allele increases $\lambda_{WA}$ and decreases $\lambda_{Wa}$, see panels D-F in Figures \ref{fig:regionFemaleDrive} and \ref{fig:regionFemaleGS}.
 

### 2018-01-18 LaTeX/Turnover.tex
added sals comment about mathematica proof

@@
 The leading eigenvalue solves $f(\lambda)=\lambda^2+b\lambda+c=0$ and the Perron-Frobenius theorem guarantees that the leading eigenvalue is positive, unique, and real.  
-Since $f(\lambda_{mA})$ and $f(\lambda_{ma})$ are of opposite signs, the leading eigenvalue must fall between these two quantities and is the larger of them when $R = 0$.  
+Since $f(\lambda_{mA})$ and $f(\lambda_{ma})$ are of opposite signs, the leading eigenvalue must fall between these two quantities and is the larger of them when $R = 0$ (see supplementary Mathematica file).
 Consequently, if both $\lambda_{mA}$ and $\lambda_{ma}$ are greater than one, then the leading eigenvalue will always be greater than one, regardless of the linkage between the neo-sex determination factor and the selected locus ($R$).

### 2018-01-18 LaTeX/S1_Appendix.tex
moved to plos template, appendices have references that are still messed up

--- 2018-01-17 LaTeX/Turnover.tex
@@
 
-\title{Haploid Selection, Sex Ratio Bias, and Transitions Between Sex-Determination Systems}
-\author{Michael F Scott$*^1$, Matthew M Osmond$*^2$, and Sarah P Otto$^2$}
-\date{}
-\maketitle
-\noindent
-$*$ These authors contributed equally to this work
+\setcounter{equation}{0}
+\renewcommand{\theequation}{S1.\arabic{equation}}
 
-\noindent
-$^1$ Department of Botany, University of British Columbia, \#3529 - 6270 University Boulevard, Vancouver, BC, Canada V6T 1Z4
-
-\noindent
-$^2$ Department of Zoology, University of British Columbia, \#4200 - 6270 University Boulevard, Vancouver, BC, Canada V6T 1Z4
-
-\noindent
-email: mfscott@biodiversity.ubc.ca, mmosmond@zoology.ubc.ca
-
-\noindent
-Contributions:
-
-\newpage
-\linenumbers
-\modulolinenumbers[2]
-
-\begin{abstract}
-Sex-determination systems are remarkably dynamic; many taxa display shifts in the location of sex-determining loci or the evolution of entirely new sex-determining systems. 
-Predominant theories for why we observe such transitions %in which new sex-determining systems spread by selection 
-%involve sex ratio selection or sex-specific selection (e.g., sexually antagonistic selection).
-%These studies 
-generally conclude that novel sex-determining systems are favoured by selection if they equalise the sex ratio or increase linkage with a sexually-antagonistic locus. 
-We use population genetic models to extend these theories in two ways: 
-(1) We explicitly consider selection on loci very tightly linked to the ancestral sex-determining loci, e.g., within the non-recombining region of the ancestral sex chromosomes. 
-%(1) We explicitly consider how selection on very tightly sex-linked loci influences the spread of novel sex-determiners. 
-Variation at such loci can favour the spread of new sex-determination systems in which the heterogametic sex changes (XY to ZW or ZW to XY) and the new sex-determining region is less closely linked (or unlinked) to the locus under selection, which is not predicted by previous theory.
-%With tight linkage, selection can maintain equilibria at which the allele fixed on the sex-limited chromosome (Y or W) is simultaneously favoured in the homogametic sex (XX females or ZZ males) such that heterogametic transitions (XY to ZW or ZW to XY) are favoured by selection.
-%Alternatively, a neo-W (neo-Y) locus can invade when it allows greater specialism on alleles beneficial in females (male) compared to an ancestral XX female (ZZ male), 
-(2) We also consider selection upon haploid genotypes either during gametic competition (e.g., pollen/sperm competition) or meiosis (i.e., non-Mendelian segregation); selective processes that typically occur in one sex or the other.
-%As well as having sex-specific fitness consequences, haploid selection can cause the zygotic sex ratio to become biased because sex ratios are determined by the production and fertilization success of X- versus Y-bearing pollen/sperm (or Z- versus W-bearing ovules/eggs).
-%Consequently, selection for XY to ZW transitions and ZW to XY transitions can be assymetrical when linkage between the ancestral sex-determining locus and a locus under haploid selection is tight, in which case ancestral sex ratio biases can be strong.
-%In addition, when linkage between the ancestral sex-determining locus and a locus under haploid selection is tight, sex ratio biases can be strong such that there is an asymmetry between invasion of ancestrally XY and ancestrally ZW systems because, e.g., haploid selection in males only causes biased zygotic sex ratios in an ancestrally XY system.
-We find that associations with haploid selected loci can drive transitions between sex determination systems, without requiring sexually-antagonistic selection in diploids. 
-Unexpectedly, with haploid selection, transitions between male and female heterogamety can also evolve where linkage with the sex-determining locus is weakened. 
-Furthermore, haploid selection in the heterogametic sex can cause sex ratio biases, which may increase or decrease with the spread of new sex chromosomes. 
-Thus, we find that transitions between sex-determination systems cannot be simply predicted by selection to equalise the sex ratio. 
-%These results indicate that loci experiencing haploid selection can favour the evolution of new sex-determination systems. 
-%These results indicate that favourable associations that develop between the ancestral sex-determining locus and selected loci can be broken during the spread of a new sex-determining region. 
-%Such transitions are not possible with diploid selection alone, in which case tighter linkage increases the fitness of both males and females. 
-%Notably, we find that the spread of new genetic sex-determination systems is not affected by sex ratio biases that are caused by haploid selection. 
-%A surprising result given that other determinants of sex allocation typically experience strong Fisherian sex ratio selection to equalize sex ratios. 
-%Overall, we demonstrate when and how the evolution of sex determining systems is impacted by sex ratio biases resulting from haploid selection and we show that new sex-determining regions can be favoured even if they are not closely linked with a locus under selection.
-Overall, our models reveal that transitions between sex-determination systems, particularly transitions where the heterogametic sex changes, can be driven by loci in previously unpredicted genomic locations that experience selection during diploid and/or haploid phases.
-These results predict conditions under which sex-determination systems are likely to be labile and draw novel connections with sex ratio evolution
-%These results might be reflected in the lability with which sex-determination systems evolve. %and for the factors determining the phylogenetic pattern of sex-determination systems. 
-\end{abstract}
-
-%abstract word count: $\approx$ 350
-
-\newpage
-
-\section*{Introduction}
-
-%CHECK THROUGHOUT: use of sex-determination SYSTEMS versus MECHANISMS. 
-%CHECK THROUGHOUT: use of haploid selection, gametic selection, and meiotic drive.
-
-Animals and angiosperms exhibit extremely diverse sex-determination systems \citep[reviewed in][]{Bull:1983vi,Charlesworth:2010it,Beukeboom:2014vb,Bachtrog:2014bx}. 
-Among species with genetic sex determination of diploid sexes (GSD), some taxa have heterogametic males (XY) and homogametic females (XX), including %non-monotreme?
-I think monotremes have XY but tonnes of translocations, giving: X1,X2...X6 Y1
-mammals and most dioecious plants \citep{Ming:2011iy}; whereas other taxa have homogametic males (ZZ) and heterogametic females (ZW), including Lepidoptera and birds. 
-Within several taxa, the chromosome that harbours the master sex-determining region changes. 
-For example, transitions of the master sex-determining gene between chromosomes or the evolution of new master sex-determining genes have occurred in Salmonids \citep{Li:2011fm,Yano:2012di}, Diptera \citep{Vicoso:2015hf}, and \textit{Oryzias} \citep{Myosho:2012fv}.
-%Presentation at evolution found neo sex chromosome in birds, doesn't seem to be published or bioRxiv yet (consider pers com.), title: A previously unknown neo-sex chromosome mediates plumage divergence and speciation in hybridizing birds Jason Sardell; Elizabeth Cooper; J.
-Albert C.
-Uy.
-I wonder if this is actually a fusion event though?
-In addition, many clades exhibit transitions between male (XY) and female (ZW) heterogamety, including snakes \citep{Gamble2017}, lizards \citep{Ezaz:2009tk}, eight of 26 teleost fish families \citep{Mank:2006bt}, true fruit flies \citep[Tephritids,][]{Vicoso:2015hf}, amphibians \citep{Hillis:1990gu}, the angiosperm genus \textit{Silene} \citep{Slancarova:2013dq}, the angiosperm family \textit{Salicaceae} \citep{Pucholt2015,Pucholt2017} and Coleoptera and Hemiptera \citep[][plate 2]{Beukeboom:2014vb}.
-Indeed, in some cases, both male and female heterogametic sex-determination systems can be found in the same species, as reported in houseflies \citep{Macdonald1978}, midges \citep{Thompson1971}, frogs \citep{Ogata:2007jm}, cichlid fish \citep{Ser:2010iq}, tilapia \citep{Lee2004}, sea bass \citep{Vandeputte2007}, and lab-strains of Zebrafish \citep{Liew2012,Wilson2014}.
-In addition, multiple transitions have occurred between genetic (GSD) and environmental sex-determination (ESD) systems, e.g., in reptiles and fishes \citep{Conover:1987in,Mank:2006bt,Pokorna:2009ui,Ezaz:2009tk,Pen:2010kk,Holleley:2015hc}.
-
-%NOTE: ``Bull & Charnov (1977) hypothesized that a new sex-determining gene can rapidly increase and become fixedin a population if it is linked to a gene with high adaptivevalue, and finally cause a change of the heterogametic sex.'' The Bull and Charnov paper is also the one in which the set of neutral equilibria between XY and ZW are identified (where sex ratios are equal)
-%NOTE: Vuilleumier et al. 2007 also find polymorphic sex determination can be stable.
-
-%For example, closely related species in the Medaka lineage (cite Takenhana et al. 2008) and Tilapiinae (cite Lee et al 2004, Cnaani et al 2008), citations in Beukeboom.
-
-%\textcolor{red}{Brief description of sex ratio adjustment and sexual antagonism theories:}
-
-Predominant theories accounting for the spread of new sex-determination systems by selection involve fitness differences between sexes (e.g., sexually antagonistic selection) or sex ratio selection \citep{Blaser2012, Beukeboom:2014vb,vanDoorn2014re}.
-%\citet{Bull:1977wt} shows that direct selection on new sex determination loci can allow them to spread and switch between male and female heterogamety. 
-\citet{vanDoorn:2007eu,vanDoorn:2010hu} and \citet{Muralidhar2018} have shown that new sex-determining loci can be favoured if they arise in close linkage with a locus that experiences sexual antagonism.
-Tighter linkage allows a stronger favourable association to build up between a male-beneficial allele, and a neo-Y chromosome, for example. 
-Such associations can favour a new partially-masculinizing or partially-feminizing allele \citep{Muralidhar2018}, a new master sex-determining gene \citep{vanDoorn:2007eu}, and transitions between male and female heterogamety \citep[trans-GSD transitions, ZW to XY or XY to ZW,][]{vanDoorn:2010hu}.
-However, any sexually-antagonistic loci that are more closely linked to the ancestral sex-determination locus will develop similar, favourable associations and are expected to hinder the spread of a new sex-determination system.
-%Here we extend these studies by explicitly calculating the the equilibrium allele frequencies of loci that are very tightly linked to the ancestral sex-determining region.
-
-The sex ratio is directly determined by the sex-determination system, and it has therefore been suggested that sex ratio selection is a dominant force in the evolution of sex determination (e.g., \citealt{Bull:1983vi}, p 66-67; \citealt{Beukeboom:2014vb}, Chapter 7).
-`Fisherian' sex ratio selection favours a 1:1 zygotic sex ratio when assuming that males and females are equally costly to produce \citep{Fisher:1930wy,Charnov:1982wg}.
-This follows from the fact that, for an autosomal locus, half of the genetic material is inherited from a male and half from a female \citep{West:2009we}. 
-Thus, if the population sex ratio is biased towards one sex, the average per-individual contribution of genetic material to the next generation from the opposite sex is greater. 
-Therefore, a mutant that increases investment in the rarer sex will spread via the higher per-individual contributions made by that sex. 
-%The default mode of sex ratio selection is `Fisherian' sex ratio selection, which favours equal investment in male and female offspring \citep[i.e., a 1:1 zygotic sex ratio when assuming that males and females are equally costly to produce,][]{Fisher:1930wy,Charnov:1982wg}.
-%Given that the sex-determination system can directly affect the sex ratio, we might expect Fisherian sex ratio selection to influence the spread of new sex-determination systems. 
-In the case of sex-chromosome evolution, \citet{Kozielska:2010vm} consider systems in which the ancestral sex chromosomes experience meiotic drive (e.g., where driving X or Y chromosomes are inherited disproportionately often), which causes sex ratios to become biased \citep{Hamilton:1967ts}.
-They find that new, unlinked sex-determining loci (masculinizing or feminizing mutations, i.e., neo-Y or neo-W loci) can then spread, which restore an even sex ratio.
-
-%\textcolor{red}{We add haploid selection:}
-Here we use mathematical models to find the conditions under which new sex-determination systems spread when individuals experience selection at both diploid and haploid stages. 
-Even in animal and plant species that have much larger and more conspicuous diploid phases than haploid phases, many loci experience significant haploid selection through gamete competition and/or meiotic drive \citep{Mulcahy:1996ha,JOSEPH:2004haa}.
-We use the term `meiotic drive' to refer to the biased (non-Mendelian) segregation of genotypes during gamete production (from one parent) and the term `gametic competition' to refer to selection upon haploid genotypes within a gamete/gametophyte pool (potentially from multiple parents); the term `haploid selection' encompasses both processes.
-
-% from Bai et al.
-(2016) ``[Segregation distortion] phenomenon is commonly detected via genetic mapping and has been documented in various species, including mouse (Eversley et al., 2010; Casellas et al., 2012), Drosophila (Phadnis and Orr, 2009; Larracuente and Presgraves, 2012; McDermott and Noor, 2012), Tigriopus (Pritchard et al., 2011), rice (Koide et al., 2012; Reflinur et al., 2014; Xu et al., 2014), maize (Tang et al., 2013), and cotton (Yu et al., 2011; Hulse-Kemp et al., 2015).'' Also more in that paper that might be useful.
-%Drosophila http://www.biorxiv.org/content/early/2017/02/06/106336
-Segregation distortion provides putative evidence of haploid selection and can sometimes be attributed to meiotic drive and/or gametic competition \citep{Lalanne2004,Fishman2005,Leppala2008,Leppala2013,Didion2015,Didion2016}.
-Where it has been characterized, meiotic drive generally occurs either during the production of male or female gametes only \citep{Ubeda:2005gw,Lindholm:2016cw}.
-Gametic competition is also typically sex specific, occurring primarily among male gametes, because there are typically many more pollen/sperm than required for fertilization.
-Gametic competition may be particularly common in plants, in which 60-70\% of all genes are expressed in the male gametophyte, and these genes exhibit stronger signatures of selection than random genes \citep{Borg:2009jpa,Arunkumar:2013iq,Gossmann:2014dua}.
-In addition, artificial selection pressures applied to male gametophytes are known to cause a response to selection \citep[e.g.,][]{Hormaza:1996cv,Ravikumar:2003uo,Hedhly:2004iv,Clarke:2004ir}. 
-A smaller proportion of genes are thought to be expressed and selected during competition in animal sperm, although precise estimates are uncertain \citep{Zheng:2001fi,JOSEPH:2004haa,Vibranovski:2010et}.
-Nevertheless, recent studies have demonstrated that sperm competition in animals can alter haploid allele frequencies and increase offspring fitness \citep{Immler:2014im,Alavioon2017}.
-
-There are various ways by which genes experiencing haploid selection could influence transitions between sex-determination systems. 
-If we assume that haploid selection at any particular locus predominantly occurs in one sex (e.g., meiotic drive during spermatogenesis), then such loci experience a form of sex-specific selection. 
-In this respect, we might expect that haploid selection would affect transitions between sex-determination systems in a similar manner to sex-specific diploid selection \citep[as explored by][]{vanDoorn:2007eu,vanDoorn:2010hu}.
-That is, new masculinizing mutations (neo-Y chromosomes) could be favoured via associations with alleles that are beneficial in the male haploid stage. 
-On the other hand, sex ratios can also become biased by linkage between the sex-determining region and a locus that harbours genetic variation in haploid fitness. 
-For example, there are several known cases of sex ratio bias caused by sex-linked meiotic drive alleles \citep[][Chapter 3]{Burt:2006} or selection among X- and Y-bearing pollen \citep{Lloyd:1974tz,Conn:1981uw,Stehlik:2005ul,Stehlik:2006to,Field:2012fd,Field:2013cc}.
-It is not immediately clear how the spread of new sex-determination systems would be influenced by the combination of sex ratio biases and associations between haploid selected loci and sex-determining regions.
-
-%Perhaps longer discussion of tight sex-linkage here? e.g., mention that r=0 is a particularly significant case for sex chromosomes.
-
-We find that the spread of novel sex-determiners is influenced by both Fisherian sex ratio selection and by selection on genetically-associated alleles. 
-%We find that sex ratio biases caused by haploid selection can exert Fisherian sex ratio selection upon novel sex-determiners but that their spread is also determined by selection on genetically-associated alleles.
-%Indeed, it is only when haploid-selected loci are tightly linked to the ancestral sex-determining region (and so sex ratio biases are initially large) that we see an asymmetry between selection for XY to ZW transitions and ZW to XY transitions (e.g., because haploid selection in males only causes biased zygotic sex ratios in an ancestrally XY system).
-Surprisingly, Fisherian sex ratio selection does not dominate; it is possible for selection on linked alleles to drive turnover between sex-determining systems despite causing increasingly biased sex ratios.
-In addition to considering haploid selection, another novel development in our model is that we consider loci that are in very tight linkage with the ancestral sex-determining region. 
-Because sex-determining loci are often found within a region of suppressed recombination, there can be a significant number of tightly linked loci. 
-We find that loci linked with the ancestral sex-determining region can drive transitions in which the heterogametic sex changes, even when the neo-sex-determining locus is less closely linked to loci under selection (either including haploid selection or not).
-%Such transitions are not favoured in models lacking tight linkage and/or haploid selection. 
-%Secondly, we allow sex-specific haploid selection to occur on a locus in tight or loose linkage with the ancestral sex-determining region. 
-%In addition, when linkage between the ancestral sex-determining locus and a locus under haploid selection is tight, sex ratio biases can be strong such that there is an asymmetry between invasion of ancestrally XY and ancestrally ZW systems because, e.g., haploid selection in males only causes biased zygotic sex ratios in an ancestrally XY system.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Model}
-%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Model Outline
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-\centerline{\includegraphics[width=\linewidth]{Sex_determination_outline.pdf}}
-\caption{
-Outline of model features. 
-Panel A: Recombination rate parameters between the ancestral-sex-determining locus (here, assumed to have X or Y alleles), a locus under selection (\textbf{A}, with alleles $A$ and $a$), and a neo-sex-determining locus (\textbf{M}, with alleles $M$ and $m$).
-If $r<1/2$, then associations between ancestral-sex-determining alleles (X and Y) and \textbf{A} locus alleles can be maintained past recombination in males.
-Panel B: Haploid selection is often sex-specific, occurring during haploid production or competition in either males or females. 
-For example, haploid selection in males only is represented by the dashed circle.  
-If X or Y alleles remain associated with alleles that experience haploid selection in males ($r<1/2$), then zygotic sex ratios can become biased because either X or Y male gametes/gametophytes will be abundant after haploid selection.
-However, the zygotic sex ratio is not biased by male haploid selection in ZW sex-determination systems. 
-Similarly, zygotic sex ratio biases can occur if haploid selected alleles are associated with neo-sex-determining alleles ($M$ and $m$, i.e., if $R<1/2$). 
-Panel C: During cis-GSD transitions (XY to XY or ZW to ZW, without loss of generality we assume ancestral XY sex determination here), a neo-Y allele spreads to pseudo-fixation (its maximum frequency among male gametes) and the the ancestral-Y allele is lost.
-Panel D: During trans-GSD transitions (XY to ZW or ZW to XY), a neo-W allele spreads to pseudo-fixation (its maximum frequency among female gametes) and the ancestral-X allele is lost.
-Neo-W mutations allow Y-associated alleles into females, which may impede or aid their spread.
-}
-\label{fig:model_outline}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\textcolor{red}{Change all  $\alpha^\Hermaphrodite$ to $(1+\alpha_{\Delta}^\Hermaphrodite)$.}
-%\textcolor{blue}{I've attempted this everywhere except in the recursions (S.1), which seem more natural with $\alpha$'s.
-I've run into trouble in equation S.8c,d -- I think we should check the Mathematica results to be sure we haven't made a typo.
-This also introduced an extra 1/2 in S.6c,d that might need to be explained.}
-%\textcolor{red}{hmm, not sure.
-This was an idea from Sally, I think in response to terms like $2 \alpha^\Hermaphrodite$ and $2(1-\alpha^\Hermaphrodite)$.
-It's possible that it makes other equations less easy to understand.
-My previous (not explained) logic was to use $w$ and $\alpha$ for strong selection and $s$, $t$, and $\alpha_\Delta$ for weak selection.
-Just to check, I should have written $\alpha^\Hermaphrodite=(1+\alpha_{\Delta}^\Hermaphrodite)/2$, maybe that's where the factors of $1/2$ come from?}
-%\textcolor{blue}{shoot, i may have changed too much (i.e.
-strong selection too), but i did use the correct transformation.
-still, the form of S.8c,d seems wrong.
-I'll double check it.
-CANT FIND ANY ERRORS YET STILL HAVE A "2" IN S.8c.
-These 2s reappear in S.9 and S.10, always with $W_{AA}$.}
-
-%\textcolor{red}{Switch between $\rho$ and $\rho$ in all places because $\rho$ is used for double recombination events.}
-%\textcolor{blue}{I think we need a different variable given the $\rho$ terms in the characteristic polynomial.
-Also, where is $\rho$ used for double recombination?
-In other papers?
-Here $\rho$ is the probability of an odd number of cross-overs between the SDR and M loci.}
-%\textcolor{red}{Good point, not sure what's best for \textbf{the-term-formerly-known-as-$\rho$}.
-Yeah, Sally's written comment was something like ``$\rho$ is semi-standard notation for double recombination so it's use as a recombination rate might be confusing''.}
-
-%\textcolor{red}{Change $\zeta$ to represent zygotic sex ratio of males, consistent with $q$ and figures.}
-
-%genetic system
-We consider transitions between ancestral and novel sex-determining systems using a three-locus model, each locus having two alleles. 
-Locus \textbf{X} is the ancestral sex-determining region, with alleles $X$ and $Y$ (or $Z$ and $W$).
-Locus \textbf{A} is a locus under selection, with alleles $A$ and $a$.
-Locus \textbf{M} is a novel sex-determining region, at which the null allele ($M$) is initially fixed in the population such that sex of zygotes is determined by the genotype at the ancestral sex-determining region, \textbf{X}; $XX$ genotypes become females and $XY$ become males (or $ZW$ become females and $ZZ$ become males).
-To evaluate the evolution of new sex-determination systems, we consider the invasion, fixation, maintenance, and/or loss of novel sex-determining alleles ($m$) at the \textbf{M} locus. 
-%We only do invasion analytically though (is this sentence still ok?)
-We assume that the \textbf{M} locus is epistatically dominant over the \textbf{X} locus such that zygotes with at least one $m$ allele develop as females with probability $k$ and as males with probability $1-k$, regardless of the \textbf{X} locus genotype.
-With $k=0$, the $m$ allele is a masculinizer (i.e., a neo-Y) and with $k=1$ the $m$ allele is a feminizer (i.e., a neo-W).
-With intermediate $k$, we can interpret $m$ as an environmental sex determination (ESD) allele, such that zygotes develop as females in a proportion ($k$) of the environments they experience. 
-%We also analyze a model of maternally-controlled environmental sex-determination, where mothers with at least one $m$ allele produce daughters with probability $k$.
-
-%life-cycle
-In each generation, we census the genotype frequencies in male and female gametes/gametophytes (hereafter gametes) before gametic competition. 
-A full description of our model, including recursion equations, is given in the Appendix. 
-First, competition occurs among male gametes (sperm/pollen competition) and among female gametes (egg/ovule competition) separately. 
-Selection during gametic competition depends on the \textbf{A} locus genotype, relative fitnesses are given by $w_A^\Hermaphrodite$ and $w_a^\Hermaphrodite$ ($\Hermaphrodite \in \{\female,\male\}$; see table \ref{tab:fitnesstable}).
-%$w_{A}^\male$ and $w_{a}^\male$ for male gametes and $w_{A}^\female$ and $w_{a}^\female$ for female gametes, see table \ref{tab:fitnesstable}.
-We assume that all gametes compete for fertilization during gametic competition, which assumes a polygamous mating system. 
-Gametic competition in monogamous mating systems is, however, equivalent to meiotic drive in our model (described below), as either only alters the frequency of gametes produced by heterozygotes. 
-After gametic competition, random mating occurs between male and female gametes.
-The resulting zygotes develop as males or females, depending on their genotypes at the \textbf{X} and \textbf{M} loci. %(and the \textbf{M} genotype of their mother in the case of maternal control).
-Diploid males and females then experience selection, with relative fitnesses $w_{AA}^{\Hermaphrodite}$, $w_{Aa}^{\Hermaphrodite}$, and $w_{aa}^{\Hermaphrodite}$.
-%where $g$ is the diploid genotype at the \textbf{A} locus ($g \in \{AA, Aa, aa\}$).
-%Diploids compete with others of the same sex, where selection depends on the sex of the individual and its genotype at the \textbf{A} locus.
-The next generation of gametes is produced by meiosis, during which recombination and sex-specific meiotic drive can occur. 
-Recombination (i.e., an odd number of cross-overs) occurs between loci \textbf{X} and \textbf{A} with probability $r$, between loci \textbf{A} and \textbf{M} with probability $R$, and between loci \textbf{X} and \textbf{M} with probability $\rho$.
-Any linear order of the loci can be modelled with appropriate choices of $r$, $R$, and $\rho$ (see Figure \ref{fig:model_outline}A and Table \ref{tab:chisubstitutions}). 
-Individuals that are heterozygous at the \textbf{A} locus may experience meiotic drive; a gamete produced by $Aa$ heterozgotes of sex $\Hermaphrodite$ bears allele $A$ with probability $\alpha^\Hermaphrodite$.
-Thus, the \textbf{A} locus can experience sex-specific gametic competition, diploid selection, and/or meiotic drive.
-
-\begin{table}[ht]
-\centering
-\smallskip
-\caption{Relative fitness of different genotypes in sex $\Hermaphrodite \in \{\female,\male\}$}
-\begin{tabular}{l c }
-\hline\hline
-  Genotype & Relative fitness during gametic competition \\ [0.5ex] \hline
-  A & $w_{A}^\Hermaphrodite = 1+t^\Hermaphrodite$ \\
-  a & $w_{a}^\Hermaphrodite = 1$ \\ [0.5ex] \hline
-  Genotype & Relative fitness during diploid selection \\ [0.5ex] \hline
-  AA & $w_{AA}^\Hermaphrodite = 1+ s^\Hermaphrodite$ \\
-  Aa & $w_{Aa}^\Hermaphrodite = 1+h^\Hermaphrodite s^\Hermaphrodite$ \\
-  aa & $w_{aa}^\Hermaphrodite = 1$ \\ [0.5ex] \hline
-  Genotype & Transmission during meiosis in $Aa$ heterozygotes \\ [0.5ex] \hline
-  A & $\alpha^\Hermaphrodite=1/2+\alpha_{\Delta}^{\Hermaphrodite}/2$ \\
-  a & $1-\alpha^\Hermaphrodite=1/2-\alpha_{\Delta}^{\Hermaphrodite}/2$ \\
-  \hline \hline
-  \label{tab:fitnesstable}
- \end{tabular}
-\end{table}
-
-%Info moved above
-%what were going to do, briefly
-%With allele $M$ fixed at the \textbf{M} locus, sex is determined by locus \textbf{X} and an equilibrium is reached at locus \textbf{A}.
-%where, importantly, locus \textbf{A} can be stably polymorphic.
-%the dynamics can be described by the frequency of $A$ in gametes/gametophytes from the homogametic sex and the frequencies of $A$ in the two types of gametes/gametophytes from the heterogametic sex.
-%We then examine the ability of a rare, novel sex-determiner, $m$, to increase in frequency from this equilibrium.
-%Numerical simulations are used to examine when an invading mutation goes to fixation.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Results}
-%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The model outlined above describes both ancestrally-XY and ancestrally-ZW sex-determination systems if we relabel the two sexes as being ancestrally `heterogametic' or ancestrally `homogametic'. 
-Without loss of generality, we primarily refer to the ancestrally heterogametic sex as male and the ancestrally homogametic sex as female.
-That is, we describe an ancestral XY sex-determination system but our model is equally applicable to an ancestral ZW sex-determination system (relabelling the ancestrally-heterogametic sex as female and the ancestrally-homogametic sex as male and switching the labels of males and females throughout).
-
-%\subsection*{Turnover between sex-determination systems}
-
-\subsubsection*{Generic invasion by a neo-Y or neo-W}
-
-The evolution of a new sex-determination system requires that a rare mutant allele at the novel sex-determining locus, $m$, increases in frequency when rare. 
-The spread of a rare mutant $m$ at the \textbf{M} locus is determined by the leading eigenvalue, $\lambda$, of the system of eight equations describing the frequency of eggs and sperm carrying the $m$ allele in the next generation (equations \ref{eq:recursions}).
-%, evaluated at the above equilibrium.
-%Thus, the system describing the change in frequency of the $m$ allele consists of eight recursion equations. 
-This system simplifies substantially in a number of cases of interest. 
-Dominant neo-Y (when $k=0$) or neo-W alleles (when $k=1$) are only found in male diploids (neo-Y) or female diploids (neo-W) such that their growth rate ultimately depends only on the change in frequency of $m$-bearing gametes produced by males or by females, respectively.
-Furthermore, if the $m$ allele is fully epistatically dominant over the ancestral sex-determining system, phenotypes are not affected by the genotype at the ancestral sex-determining region (\textbf{X} locus).
-Thus, the invasion of rare dominant neo-Y or neo-W alleles is determined by the largest eigenvalue that solves the quadratic, $\lambda^2+ b \lambda + c =0$ \textcolor{blue}{(see Appendix for a discussion of other roots - or Sally's proof!)}.
-Here, $b= - (\lambda_{mA} + \lambda_{ma})+(\chi_{mA} + \chi_{ma})$ and $c = (\lambda_{mA}-\chi_{mA}) (\lambda_{ma}-\chi_{ma}) -\chi_{mA} \chi_{ma}$, where $\lambda_{mi}$ is the multiplicative growth rate (which we will call the ``haplotypic growth rate'') of the neo-sex determination allele $m$ on background $i$ without accounting for loss due to recombination, and $\chi_{mi}$ is the rate at which mutant haplotypes on background $i\in\{A,a\}$ recombine onto the other \textbf{A} locus background in heterozygotes (see Table \ref{tab:haplotype_growth}).
-The $\lambda_{mi}$ and $\chi_{mi}$, and thus the spread of the mutant $m$ allele, depend on the frequency of alleles at the \textbf{A} and \textbf{X} loci in the ancestral population. 
-In the ancestral population, it is convenient to follow the frequency of the $A$ allele among female gametes (eggs), $p^\female_X$, and among X-bearing, $p^\male_X$, and among Y-bearing, $p^\male_Y$, male gametes (sperm/pollen).
-We also track the fraction of male gametes that are Y-bearing, $q$, which may deviate from $1/2$ due to meiotic drive in males. 
-We will consider only equilibrium frequencies of alleles, $\hat{p}^\Hermaphrodite_i$, and Y-bearing male gametes, $\hat{q}$, when calculating the eigenvalues.
-
-%\textcolor{red}{I now remove the zygotic sex ratio $\zeta$ from the mean fitnesses. The mean fitnesses will have to be adjusted in a corresponding way.}
-%
-%\textcolor{red}{CHECK: DO THE HAPLOID MEAN FITNESSES HAVE TO BE IN THE DENOMINATOR? i think so, based on definitions in table S.2 (mmo)}
-
-% as there are now two 2s in the lambdas of table 2. perhaps the 2 in the denominator is needed because the frequency of males sums to one as does the frequency of females?}
-
-\begin{threeparttable}[ht]
-\centering
-\smallskip
-%\caption{Parameters determining invasion (equation \ref{eq:charpoly_neoY}) for neo-Y or neo-W alleles}
-\caption{Parameters determining invasion of mutant neo-Y and neo-W alleles into an ancestrally XY system}
-\begin{tabular}{l}
-\hline\hline
-   \noalign{\vskip 0.5ex}
-   $m$ is a neo-Y ($k=0$) \\ [0.5ex] \hline \noalign{\vskip 1ex}
-  $\lambda_{YA} = \left( 2 \zeta \right)^{-1} \left[\hat{p}_X^\female w_{A}^{\female} w_{A}^{\male} w_{AA}^{\male} + (1-\hat{p}_X^\female) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} (1+\alpha_{\Delta}^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right) $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\lambda_{Ya} = \left( 2 \zeta \right)^{-1} \left[(1-\hat{p}_X^\female) w_{a}^{\female} w_{a}^{\male} w_{aa}^{\male} + \hat{p}_X^\female w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male}(1 - \alpha_{\Delta}^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\chi_{YA} = R \left( 2 \zeta \right)^{-1} \left[ (1-\hat{p}_X^\female) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} (1+\alpha_{\Delta}^{\male}) \right]/  \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right)   $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\chi_{Ya} = R \left( 2 \zeta \right)^{-1} \left[   \hat{p}_X^\female w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male} (1 - \alpha_\Delta^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right)  $\\ [1ex] \hline
-  \noalign{\vskip 0.5ex}
-  $m$ is a neo-W ($k=1$) \\ [0.5ex] \hline \noalign{\vskip 1ex}
-  $\lambda_{WA} = \left[ 2 (1 - \zeta) \right]^{-1} \left[ \bar{p}^{\male} w_{A}^{\male} w_{A}^{\female} w_{AA}^{\female}+(1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female}(1+\alpha_{\Delta}^{\female})\right]/ \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\lambda_{Wa} = \left[ 2 (1 - \zeta) \right]^{-1} \left[ (1-\bar{p}^{\male}) w_{a}^{\male} w_{a}^{\female} w_{aa}^{\female}+\bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female}(1-\alpha_{\Delta}^{\female})\right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\chi_{WA} = R \left[ 2 (1 - \zeta) \right]^{-1} \left[ (1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female} (1+\alpha_{\Delta}^{\female}) \right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \right)  $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\chi_{Wa} = R \left[ 2 (1 - \zeta) \right]^{-1} \left[ \bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female} (1-\alpha_{\Delta}^{\female}) \right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \right) $\\ [1ex]
-  \hline \hline 
-   \end{tabular}
-      \begin{tablenotes}
-      \scriptsize
-      \item $\bar{p}^{\male}=(1-\hat{q})\hat{p}_X^\male + \hat{q}\hat{p}_Y^\male$ is the average frequency of the $A$ allele among X- and Y-bearing male gametes.
-%      \item $R$ is the probability of recombination between loci \textbf{A} and \textbf{M}.
-      \item $\zeta$ is the zygotic sex ratio (fraction male)
-      \item $\bar{w}^\Hermaphrodite$ is the mean fitness of diploids of sex $\Hermaphrodite$, see Table \ref{tab:meanfitnesses}
-      \item $\bar{w}_H^\Hermaphrodite$ is the mean fitness of haploids from sex $\Hermaphrodite$, see Table \ref{tab:meanfitnesses}
-%      \item $\bar{w}_H^\female = p_X^\female w_A^\female + (1-p_X^\female) w_a^\female$ is the mean fitness of female gametes during gametic competition
-%      \item $\bar{w}_H^\male = \bar{p}^{\male} w_A^\male + (1-\bar{p}^{\male}) w_a^\male$ is the mean fitness of male gametes during gametic competition
-%       \item $\bar{w}^\female = \{ p_X^\female w_A^\female (1-q) p_X^\male w_A^\male w_{AA}^\female + (1 - p_X^\female) w_a^\female (1-q) p_X^\male w_A^\male w_{Aa}^\female + p_X^\female w_A^\female (1-q) (1 - p_X^\male) w_a^\male w_{Aa}^\female + (1-p_X^\female) w_a^\female (1-q) (1 - p_X^\male) w_a^\male w_{aa}^\female \} / \{ \bar{w}_H^\female \bar{w}_H^\male\}$ is the mean fitness of females during diploid competition
-%       \item $\bar{w}^\male = \{ p_X^\female w_A^\female q p_Y^\male w_A^\male w_{AA}^\male + (1 - p_X^\female) w_a^\female q p_Y^\male w_A^\male w_{Aa}^\male + p_X^\female w_A^\female q (1 - p_Y^\male) w_a^\male w_{Aa}^\male + (1-p_X^\female) w_a^\female q (1 - p_Y^\male) w_a^\male w_{aa}^\male \} / \{ \bar{w}_H^\male \bar{w}_H^\male\}$ is the mean fitness of males during diploid competition
-    \end{tablenotes}
-  \label{tab:haplotype_growth}
-\end{threeparttable}
-\\
-
-%We are particularly concerned with the conditions under which a rare neo-sex-determining allele increases in frequency, which occurs when the largest eigenvalue, $\lambda$, is greater than one. 
-%If one or both of $\lambda_{mA}$ and $\lambda_{ma}$ are greater than one, indicating that at least one haplotype increases in frequency faster than recombination breaks it apart, invasion will always occur ($\lambda>1$).
-%Otherwise, invasion requires
-%\begin{equation}
-%(\lambda_{mA}-1)(\lambda_{ma}-1) - \chi_{mA} \chi_{ma}<0.
-%\end{equation}
-
-We are particularly concerned with the conditions under which a rare neo-sex-determining allele increases in frequency, which occurs when the largest eigenvalue, $\lambda$, is greater than one. 
-%If the average change in frequency of the two haplotypes that carry the $m$ allele ($Am$ and $am$) is positive, invasion will always occur, i.e., if $(\lambda_{mA} + \lambda_{ma})/2 > 1$ then $\lambda > 1$.
-The leading eigenvalue solves $f(\lambda)=\lambda^2+b\lambda+c=0$ and the Perron-Frobenius theorem guarantees that the leading eigenvalue is positive, unique, and real.  
-Since $f(\lambda_{mA})$ and $f(\lambda_{ma})$ are of opposite signs, the leading eigenvalue must fall between these two quantities and is the larger of them when $R = 0$.  
-Consequently, if both $\lambda_{mA}$ and $\lambda_{ma}$ are greater than one, then the leading eigenvalue will always be greater than one, regardless of the linkage between the neo-sex determination factor and the selected locus ($R$).
-In particular, having $\lambda_{mA} >1$ and $\lambda_{ma}>1$ thus guarantees that an unlinked sex determining factor can invade ($R=1/2$).  
-Conversely, if both $\lambda_{mA}$ and $\lambda_{ma}$ are smaller than one, then invasion can never occur.  
-Finally, if only one of  $\lambda_{mA}$ and $\lambda_{ma}$ is greater than one, the new sex determining factor can always invade when tightly linked to the selected locus ($R$ near 0).  
-Furthermore, it can be shown that the leading eigenvalue declines with $R$, and invasion requires that $R$ is sufficiently small that the following condition holds: 
-\begin{equation}\label{eq:lambdasGen}
-%\frac{\chi_{mA}}{\lambda_{mA}-1}+\frac{\chi_{ma}}{\lambda_{ma}-1}>0.
-\chi_{ma}/\left(\lambda_{ma}-1\right) + \chi_{mA}/\left(\lambda_{mA}-1\right) < 1.
-\end{equation}
-\noindent 
-This condition may or may not be satisfied for the full range of locations of the new sex determining factor, including $R=1/2$, depending on the nature of selection.  
-Interpreting this condition, if we assume that only the $mA$ haplotype has a positive growth rate when $R=0$, $\lambda_{ma}<1<\lambda_{mA}$, the first term on the left-hand side of \eqref{eq:lambdasGen} is negative and invasion requires that the $mA$ haplotype growth rate ($\lambda_{mA}-1$) and the rate at which they are produced by recombination in $ma$ haplotypes ($\chi_{ma}$) are sufficiently large relative to the $ma$ haplotype rate of decline ($1-\lambda_{ma}$) and the rate of loss of $mA$ haplotypes due to recombination ($\chi_{mA}$).
-%In other words, invasion requires that the average growth rate of the two haplotypes, weighted by the rates they are created by recombination, is positive.
-%the number of recombinants from the fitter $mA$ haplotypes is larger than that of the less fit $ma$ haplotypes, relative to their growth rates.
-
-We can draw a number of key points about the invasion of neo-Y and neo-W mutations from Table \ref{tab:haplotype_growth}. 
-First, Fisherian sex ratio selection will favour the spread of a neo-Y if the ancestral zygotic sex ratio is biased towards females, $\zeta<1/2$ (i.e., the first factor of the $\lambda_{mi}$ is greater than one for a neo-Y and less than one for a neo-W).
-However, the spread of a neo-Y (neo-W) also depends on the male (female) fitness of associated alleles (see terms involving equilibrium allele frequencies, $\hat{p}$'s).
-Second, invasion by a neo-Y (neo-W) allele does not directly depend on the fitness of female (male) diploids. %(for a given set of equilibrium allele frequencies).
-This is because a dominant neo-Y (neo-W) is always found in males (females), and therefore the frequency of the neo-Y (neo-W) allele, $m$, only changes in males (females), Figure \ref{fig:model_outline}C,D.
-Finally, invasions by a neo-Y and a neo-W are qualitatively different.
-This is because a gamete with the neo-Y always pairs with a female gamete containing an X, and develop into males, Figure \ref{fig:model_outline}C.
-By contrast, a gamete with a neo-W can pair with an X or Y male gamete, developing into a female, Figure \ref{fig:model_outline}D.
-Consequently, neo-W bearing females obtain a differerent frequency of $A$ alleles from mating (when $\hat{p}_X^\male \neq \hat{p}_Y^\male$) compared to ancestral ($MM$) females.
-
-In order to explicitly determine the conditions under which a rare neo-sex-determining allele spreads, we must calculate the equilibrium frequency of the $A$ allele (i.e., $\hat{p}^\female_X$, $\hat{p}^\male_X$, and $\hat{p}^\male_Y$) and Y-bearing male gametes ($\hat{q}$) in the ancestral population.
-Since only the \textbf{A} locus experiences selection directly, any deterministic evolution requires that there is a polymorphism at the \textbf{A} locus. 
-Polymorphisms can be maintained by mutation-selection balance or transiently present during the spread of beneficial alleles.
-However, polymorphisms maintained by selection can maintain alleles at intermediate allele frequencies for longer periods.
-Here, we focus on polymorphisms maintained by selection, where the $A$ allele reaches a stable intermediate equilibrium frequency under the ancestral sex-determination system before the neo-sex-determining allele ($m$) arises.
-Such polymorphisms can be maintained by heterozygote advantage, sexually-antagonistic selection, ploidally-antagonistic selection, or a combination \citep{Immler:2012tl}.
-We can analytically calculate the allele frequency of the $A$ allele using two alternative simplifying assumptions: 
-(1) the \textbf{A} locus is within (or tightly linked to) the non-recombining region around the ancestral SDR ($r \approx 0$) or (2) selection is weak relative to recombination ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon<<1$).
-
-\subsubsection*{Tight linkage with the ancestral sex-determining region ($r \approx 0$)}
-
-The ancestral equilibrium allele frequencies and their stability conditions are given in the appendix.
-When there is complete linkage between the ancestral sex-determining region and the \textbf{A} locus ($r=0$), either the $A$ allele or the $a$ allele must be fixed on the Y. 
-% because selection on the Y is effectively haploid an incapably of maintaining a polymorphism in the absence of frequency dependent selection. 
-Because the labelling of alleles is arbitrary, we will assume that the $a$ locus is fixed on the Y ($p^\male_Y=0$), without loss of generality. 
-If there are two alleles maintained at the \textbf{A} locus, the X can either be fixed for the $A$ allele ($\hat{p}^\female_X=\hat{p}^\male_X=1$) or polymorphic (0<$\hat{p}^\female_X, \hat{p}^\male_X$<1).
-%However, because the X is present in both males and females, there are distinct selection pressures on X's in females and X's in males, which will always be paired with an $A$ allele from the Y.
-
-We find that a neo-Y can never invade an ancestral XY system that already has tight linkage with the locus under selection ($r=0$, for details see supplementary \textit{Mathematica} file). 
-When $R=0$, a neo-Y haplotype with the same allele as the ancestral Y is neutral ($\lambda_{Ya}=1$) and does not change in frequency.
-The other neo-Y haplotype will not spread ($\lambda_{YA}<1$) given that the initial equilibrium is stable. 
-Therefore, a neo-Y mutation cannot spread ($\lambda \leq 1$, regardless of $R$) in an ancestral XY system where selected loci are within or very near the non-recombining region around the SDR.
-In essence, through tight linkage with the \textbf{A} locus, the ancestral Y becomes strongly specialized on the allele that has the highest fitness across male haploid and diploid phases. 
-Given that the ancestral Y is at this equilibrium, it is not possible for a neo-Y to create males that have higher fitness than the ancestral Y.
-
-Neo-W alleles, on the other hand, can invade an ancestral XY system under some conditions (the full invasion conditions are given in the appendix; equations \ref{Binvasion} and \ref{Ainvasion}). 
-Counterintuitively, selection on loci within the non-recombining region of the SDR can favour the invasion of a less closely linked neo-W, whatever the form of selection maintaining a polymorphism (sexually-antagonistic selection, overdominance, ploidally-antagonistic selection, or some combination, Figures \ref{fig:SexAntagTighter}, \ref{fig:temporalOverdominance}, \ref{fig:regionPloidAntag}, and \ref{fig:SexAntagTighterMaleDrive}).
-The conditions become more restrictive, however, with increasing recombination ($R$) between the new sex determining region and the selected locus.  
-The invasion of completely unlinked neo-W alleles ($R = 1/2$) can occur with overdominance in males or with haploid selection but is not possible with only sexually-antagonistic selection if selection is directional in each diploid sex (see Supplementary \textit{Mathematica} file).
-To develop an intuition for how less closely linked neo-W alleles invade ($R>r$), we first focus on cases where there is no haploid selection and discuss the additional effect of haploid selection in the appendix.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Tighter linkage allows looser sex-linkage to evolve, even in absence of haploid selection
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-\centerline{\includegraphics[width=1.5\linewidth]{PositionPlot_SexAntagTighter}}
-\caption{
-Transitions between XY and ZW systems can occur even when the neo-SDR is less tightly linked to a locus under sexually-antagonistic selection (here, without haploid selection).
-In panel A, linkage is loose enough relative to selection that the analytical results assuming weak selection hold, and a neo-W can only invade when it is more tightly linked with the selected locus ($R<r$; shaded region).
-In panel B, linkage is tight enough relative to selection that the analytical results assuming weak selection do not hold, and a neo-W can invade even when it is less tightly linked with the selected locus ($r<R$; unshaded region).
-In panel C we vary the recombination rate between the neo-W and the selected locus ($R$) for a fixed recombination rate between the ancestral-SDR and the selected locus ($r=0.005$). 
-Coloured markers show recombination rates for which the temporal dynamics of invasion are plotted in the inset, demonstrating that neo-W alleles can fix (reach frequency $0.5$ among female gametes) if they are more (black) or less (red) closely linked to a locus experiencing sexually-antagonistic selection.
-A very loosely linked neo-W does not spread in this case (blue and green lines overlap and go to 0). 
-Fitness parameters are: $w_{AA}^\female = 1.05$, $w_{aa}^\male = 1.2$, $w_{aa}^\female = w_{AA}^\male = 0.85$, $w_{Aa}^\Hermaphrodite = 1$,  $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
-%\textcolor{red}{consider removing panel A, which is repeated in Figure 3.}
-%\textcolor{blue}{probably better to remove from panel 3, eh?}
-}
-\label{fig:SexAntagTighter}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-If we categorise the $a$ allele as being ancestrally `male-beneficial' via the fact that it is fixed on the Y, then $\lambda_{WA}>1$ indicates that the neo-W spreads when found with the ancestrally `female-beneficial' allele.
-Broadly, this is possible because the ancestral X chromosome is sometimes found in males and is therefore unable to perfectly specialise on the `female-beneficial' allele. 
-For example, when the $a$ allele is favoured on the ancestral X in males, a polymorphism of $A$ and $a$ alleles can be maintained on the X despite directional selection in favour of the $A$ allele in females ($s^\female>0$, $0<h^\female<1$), see outlined region in Figure \ref{fig:regionplots}A.
-When the $a$ allele is strongly favoured on X chromosomes in males ($w_{aa}^\male$ sufficiently large relative to $w_{Aa}^\male$), neo-W-$A$ haplotypes can spread ($\lambda_{WA}>1$, see grey region in Figure \ref{fig:regionplots}A) because they produce hgher fitness females ($AA$ or $Aa$ genotypes) and are unleashed from counterselection in males.
-
-When only one neo-W haplotype has a positive growth rate (see Figure \ref{fig:regionplots}), a neo-W can invade as long as equation \eqref{eq:lambdasGen} is satisfied, which may require that the recombination rate, $R$, is small enough.
-Nevertheless, because we assume here that $r$ is small, these results indicate that a more loosely linked sex-determining region ($r<R$) can spread.
-Therefore, tightly sex-linked loci that experience sexually-antagonistic selection can drive trans-GSD transitions in which the neo-SDR is less closely linked to the locus under selection (Figure \ref{fig:SexAntagTighter}).
-
-Given that the $a$ allele can be considered ancestrally `male-beneficial' because it is fixed on the Y, it is surprising that neo-W-$a$ haplotypes can sometimes be favoured by selection in females ($\lambda_{Wa}>1$).
-Again, this occurs because ancestral X's also experience selection in males, in which they will always be paired with a Y-$a$. 
-If there is overdominance in males, X-$A$ Y-$a$ males have high fitness and the $A$ allele is favoured by selection on the X in males. 
-Therefore, the X can be polymorphic or even fixed for the $A$ allele despite favouring the $a$ allele during selection in females \citep[e.g., see outlined region in Figure \ref{fig:regionplots}B and][]{Lloyd1977,Otto2014}.
-In such cases, neo-W-$a$ haplotypes can spread because they create more $Aa$ and $aa$ females when pairing with an X from males and because they bring Y-$a$ haplotypes into females, where it has higher fitness (Figure \ref{fig:model_outline}D).
-
-In some cases, both W-$A$ and W-$a$ haplotypes can spread, e.g., when $AA$ individuals have low fitness in females yet the $A$ is polymorphic or fixed on the X due to overdominance in males (Figure \ref{fig:regionplots}B and \ref{fig:regionplots}C).
-Both neo-W-$A$ and neo-W-$a$ haplotypes then produce fewer unfit $AA$ females.
-This is true for the neo-W-$A$ haplotype because it can pair with a Y-$a$ haplotype and still be female. 
-Wherever both haplotypes have positive growth rates, invasion by a neo-W is expected regardless of its linkage with the selected locus (i.e., even unlinked neo-W alleles can invade, see Figures \ref{fig:positionOverdominance} and \ref{fig:temporalOverdominance} for examples).
-
-Assuming that linkage is not tight, \citet{vanDoorn:2010hu} showed that invasion by a neo-W occurs under the same conditions as `pseudo-fixation' (at pseudo-fixation the neo-W reaches its maximum frequency among eggs, which is 1/2).
-An equivalent analysis is not possible where we assume that linkage is tight. 
-However, numerical simulations with tight linkage demonstrate that the neo-SDR does not necessarily reach pseudo-fixation, leading to the stable maintenance of a mixed sex-determining system, in which X, Y, Z, and W alleles all segregate (e.g., Figure \ref{fig:freqAll}B,C).
-
-%Haploid selection impacts the spread of neo-W haplotypes through its direct selective effect on females and their gametes, its indirect effect on the marginal fitness of alleles in females resulting from haploid selection in male gametes, and its effect on the sex ratio.
-%These impacts expand the scenarios under which neo-W haplotypes can spread.
-%For instance, overdominance is no longer required for neo-W-$a$ haplotypes to spread when there is haploid selection (e.g., when $a$ is female-beneficial, $A$ is male-beneficial, and meiotic drive in males favours $a$, Figure \ref{fig:regionMaleDrive}B).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Both neo-W haplotypes can spread, in the absence of haploid selection, when there is overdominance
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-%\centerline{\includegraphics[width=1.25\linewidth]{Region_plot_combined_Mike}}
-\centerline{\includegraphics[width=1.25\linewidth]{Region_plot_combined}}
-\caption{
-When the ancestral-XY locus is tightly linked to a locus under selection ($r=0$), one or both neo-W haplotypes can spread. 
-We vary the fitness of male homozygotes relative to heterozygotes ($w_{Aa}^\Hermaphrodite=1$) and only consider stable equilibria at which both \textbf{A} locus alleles are maintained and the $a$ allele is initially fixed on the Y, region outlined.
-Here, selection in females can favour the $A$ allele (panel A, $w_{aa}^\female=0.85$, $w_{AA}^\female=1.05$), favour the $a$ allele (panel B, $w_{aa}^\female=1.05$, $w_{AA}^\female=0.85$), or be overdominant (panel C, $w_{aa}^\female=w_{AA}^\female=0.6$).
-If $\lambda_{wA}$ or $\lambda_{wa}$ is greater than one, then a rare neo-W can spread for, at least, some values of $R>r$. 
-The parameter values marked with an asterisk correspond to the fitnesses used in Figure \ref{fig:SexAntagTighter}C. 
-Where both $\lambda_{wA}$ and $\lambda_{wa}$ are greater than one, a neo-W will spread when rare, regardless of linkage with the selected locus (for any $R$). 
-Figure \ref{fig:positionOverdominance} shows the dynamics using the parameters marked with a dagger. 
-Here, there is no haploid selection $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
-}
-\label{fig:regionplots}
-\end{figure}
-
-%Neo-W alleles, on the other hand, can invade an ancestral XY system under some conditions (given in detail in the appendix). 
-%%The full characteristic polynomials are given in the appendix (equations \ref{Binvasion} and \ref{Ainvasion}).
-%Briefly, neo-W-$A$ and/or neo-W-$a$ haplotypes can spread when rare in the absence of recombination ($\lambda_{ma}>1$ and/or $\lambda_{mA}>1$), depending on the ancestral sex ratio and allele frequencies.
-%Below we discuss the main forces determining the spread of these neo-W haplotypes and the impact of recombination for the overall success of the neo-W.
-%To simplify our discussion we first outline the potential effects of haploid selection and then consider diploid selection in its absence.
-
-%\textcolor{blue}{This explanation is clearer than the one I put in the appendix, if we drop it here, maybe we should try and re-word the corresponding part of the appendix using this paragraph}
-%Haploid selection impacts the spread of neo-W haplotypes in three ways.
-%Firstly, the zygotic sex ratio becomes male biased ($\zeta<1/2$) when the $a$ allele (which is fixed on the Y) is favoured during competition among male gametes or by meiotic drive in males. 
-%This facilitates the spread of a neo-W because neo-W alleles cause the zygotes that carry them to develop as the rarer, female, sex. 
-%Secondly, haploid selection in males affects the diploid genotypes of females by altering the allele frequencies in the male gametes that female gametes pair with.
-%For instance, because an epistatically dominant neo-W always causes its carrier to become female, it creates females who carry either $Y-a$ or $X$ genotypes from their father.
-%Thus, because when there is a polymorphism the $X$ carries some non-zero frequency of $A$, haploid selection in males impacts the diploid genotypes of females (e.g., creating more $Aa$ females when drive in males favours $Y-a$).
-%How this affects the spread of the neo-W then depends on diploid and haploid selection in females.
-%Thirdly, female drive and gamete competition directly select on neo-W haplotypes.
-%Drive for $A$ in females favours neo-W-$A$ haplotypes, at a cost to neo-W-$a$ haplotypes, and vice-versa when there is drive for $a$.
-%The impact of this drive depends on how often XX and neo-W females are heterozygous.
-%Competition among female gametes acts similarly, and depends on the frequency of $A$ on resident X chromosomes (e.g., competition among eggs has no affect on the initial spread of the neo-W-$A$ haplotype when $A$ is fixed on the X).
-%Because haploid selection in females favours one neo-W haplotype at the expense of the other, recombination off the favoured background becomes more detrimental as it becomes more favoured.
-Thus higher rates of recombination between the neo-W and the selected locus, $R$, can lead to smaller leading eigenvalues when there is haploid selection in females.
-
-%In the absence of haploid selection and with the $A$ allele is fixed on the X, it is possible for both neo-W haplotypes can spread ($\lambda_{mA}>1$ and $\lambda_{ma}>1$ in \ref{Binvasion}), and thus neo-W invasion can occur regardless of its linkage to the selected locus.
-%Invasion does not occur with purely sexually-antagonistic selection (i.e., $a$ directionally favoured in males and $A$ directionally favoured in females) because the X is then already as specialized as possible on the female sex.
-%However, if, for example, $AA$ individuals suffer a fitness cost in females, yet $A$ is fixed on the X due to strong overdominance in males, both neo-W-$A$ and neo-W-$a$ haplotypes spread because they produce fewer unfit $AA$ females and never experience counter-selection in males.
-%This is true even for the neo-W-$A$ haplotype because it can pair with a $Y-a$ haplotype and still be female. 
-%When both haplotypes can spread alone the rate of recombination between the neo-W and the selected locus, $R$, does cannot prevent invasion, and thus the system can evolve looser sex-linkage (e.g., the neo-W could arise on an autosome, $R=1/2$).
-%Even when only one haplotype can spread, invasion can still occur up to some positive rate of recombination, $R>0$ (as long as equation \ref{eq:lambdasGen} is satisfied). 
-%That looser sex-linkage can evolve is contrary to the conclusions of \cite{vanDoorn:2010hu}, who did not explicitly calculate invasion fitness under ancestrally tight sex-linkage.
-\textcolor{blue}{or, just didn't calculate the equilibria (A) an (B).}
-%Similar scenarios have been shown to select for a modifier that increases recombination between the sexes \citep[green regions of Figure 2 in][]{Otto2014}.
-%\textcolor{blue}{n.b., the recombination regions are only subsets mostly because you also generate a really unfit Y haplotype through recombination. Probably not worth mentioning.}
-%
-%In the absence of haploid selection it is also possible for a neo-W to invade when there is a stable polymorphism at the $\mathbf{A}$ locus on X chromosomes.
-%For example, overdominance in males and strong directional selection for $a$ in females creates a scenario that favours the spread of both neo-W haplotypes at equilibrium ($\lambda_{mA}>1$ and $\lambda_{ma}>1$ in \ref{Ainvasion}), as both haplotypes bring more $a$ alleles into females and never experience counter-selection in males.
-%Thus, as in the case of the $A$ being fixed on the X, looser sex-linkage can evolve with a polymorphic X (i.e., $\lambda>1$ with $R>0$) and this is expected under the same scenarios that select for a modifier that increases recombination between the sex chromosomes \citep[blue regions of Figure 2 in][]{Otto2014}.
-
-\subsubsection*{Loose linkage with the ancestral sex-determining region}
-
-%\textcolor{blue}{As with the discussion, this section might need some editing for (1) unclearly describing looser linkage never evolving without haploid selection, which we now show is possible above and (2) going on about sex ratio selection too much - this should be changed to something along the lines of  ``male biased zygotic sex ratios ($\zeta-1/2$) are of the order of $\epsilon^2$.
-Therefore Fisherian sex ratio selection directly favours neo-Ws by a similar magnitude.
-%Perhaps surprisingly, neo-Ws can be favoured to the same degree by haploid selection in females when female haploid selection favours the alleles that tend to be carried by the neo-W.
-%Thus XY to ZW is the same as ZW to XY even though sex ratio biases only exist in one case, given the assumptions made in this section.
-%''
-%}
-
-%weak selection
-%We are particularly concerned with whether or not a rare neo-sex-determining allele increases in frequency, which occurs when the largest eigenvalue, $\lambda$, is greater than one. 
-%Here, we explicitly determine the conditions under which invasion occurs by assuming that the $A$ allele reaches an equilibrium frequency under the ancestral sex-determination system before the neo-sex-determination system ($m$) arises.
-%The equilibrium frequency of $A$ on different ancestral backgrounds ($\hat{p}^\male_Y$, $\hat{p}^\male_X$, and $\hat{p}^\female_X$) is given by equations \eqref{eq:pAve} and \eqref{eq:freq_diffs} where we assume selection and meiotic drive are weak relative to recombination ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon$).
-Assuming that selection is weak ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon<<1$) and thus implicitly assuming that all recombination rates ($r$, $R$ and $\rho$) are large relative to selection, we denote the leading eigenvalues describing the invasion of a neo-Y ($k=0$) and a neo-W ($k=1$) into an ancestrally XY system by $\lambda_{Y',XY}$ and $\lambda_{W',XY}$, respectively.
-To leading order in selection, these are:
-
-\begin{equation}
-\lambda_{Y',XY} =1+ \frac{1}{4}V_{A}S_{A}^2\frac{ \left( r-R \right) }{r R}+O\left(\epsilon^3 \right) 
-\label{eq:lambda_neoY}
-\end{equation}
-
-\noindent 
-and
-
-\begin{equation}
-\lambda_{W',XY} =\lambda_{Y',XY}+\left(2\alpha_{\Delta}^\male-2\alpha_{\Delta}^\female+t^\male-t^\female \right) \left( \hat{p}^\male_Y-\hat{p}^\male_X \right)/2
-+O\left(\epsilon^3 \right) \\
-\label{eq:lambda_neoW}
-\end{equation}
-
-\noindent
-where $V_{A}=\bar{p}(1-\bar{p})$ is the variance in the equilibrium frequency of $A$ and $S_{A}=(D^\male +\alpha_{\Delta}^\male+t^\male) - (D^\female+\alpha_{\Delta}^\female+t^\female)$ describes sex differences in selection for the $A$ versus $a$ allele across diploid selection, meiosis, and gametic competition.
-The diploid selection term, $D^\Hermaphrodite=\big{[} \bar{p}s^\Hermaphrodite+(1-\bar{p})h^\Hermaphrodite s^\Hermaphrodite\big{]} -\big{[} \bar{p}h^\Hermaphrodite s^\Hermaphrodite+(1-\bar{p}) \big{]}$, is the difference in fitness between $A$ and $a$ alleles in diploids of sex $\Hermaphrodite \in \{\female,\male\}$, where $\bar{p}$ is the leading-order probability of mating with an $A$-bearing gamete from the opposite sex (equation \ref{eq:pAve}).
-The difference in $A$-allele-frequency among Y-bearing sperm versus X-bearing sperm is given by $\hat{p}^\male_Y-\hat{p}^\male_X=V_{A}\big{(}D^\male - D^\female+\alpha_{\Delta}^\male-\alpha_{\Delta}^\female+t^\male-t^\female\big{)}(1-2r)/(2r)$.
-
-The neo-sex-determining allele, $m$, will spread if $\lambda_{m,XY}>1$. 
-Equation \eqref{eq:lambda_neoY} demonstrates that, under weak selection, a neo-Y will invade an XY system if and only if it is more closely linked to the selected locus than the ancestral sex-determining region (i.e., if $R<r$; note that $V_{A}S_{A}^2$ is strictly positive as long as \textbf{A} is polymorphic).
-This echoes our tight linkage results above where a neo-Y could never invade if $r\approx0$.
-It is also consistent with the results of \citet{vanDoorn:2007eu}, who considered diploid selection only and also found that cis-GSD transitions (XY to XY or ZW to ZW) can only occur when the neo-sex-determining locus is more closely linked to a locus under sexually-antagonistic selection.
-%Because tighter linkage between the sex-determining region and a selected locus evolves during these transitions, stronger associations between selected alleles and diploid sexes can build up by selection (e.g., between male-beneficial alleles and the male-determining allele, Y).%, increasing diploid mean fitness (Figure \ref{fig:Combination_MeanFit}).
-
-With weak selection and no haploid selection ($t^\Hermaphrodite=\alpha^\Hermaphrodite_{\Delta}=0$), the spread of a neo-W is equivalent to the spread of a neo-Y ($\lambda_{W',XY}=\lambda_{Y',XY}$), such that trans-GSD transitions (XY to ZW or ZW to XY) can also occur only if the neo-sex-determining region is more closely linked to a locus under selection ($R<r$), as found by \citet{vanDoorn:2010hu}.
-With haploid selection, however, the additional term in equation \eqref{eq:lambda_neoW} can be positive, which can allow, for example, neo-W invasion ($\lambda_{W',XY}>1$) even when the neo-sex-determining region is less closely linked to the selected locus ($R>r$).
-%These transitions are unusual because, when $R>r$, associations that selection has built up between alleles more favourable in one sex and alleles that determine sex will be weakened. 
-%Mean diploid fitness therefore decreases during heterogametic transitions that create looser sex-linkage (Figure \ref{fig:Combination_MeanFit}B,D).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%A neo-W can invade an XY system under a large number of selective regimes
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-\includegraphics[width=\linewidth]{PositionPlot}
-\caption{
-% A neo-W can invade an XY system under a large number of selective regimes.
-%In panel A, there is no haploid selection ($t^\Hermaphrodite = \alpha^\Hermaphrodite_{\Delta} = 0$) and selection in diploids is sexually antagonistic ($s^\male = -s^\female = 1/10$, $h^\male = 1-h^\female = 3/10$), in which case the neo-sex-determining allele can only invade if it is more closely linked to the selected locus ($R<r$, gray region; but see Figure \ref{fig:SexAntagTighter}B for the case of very tight linkage).
-Ploidally-antagonistic selection allows a less tightly linked neo-W to invade.
-In panel A, male drive ($\alpha^\male_{\Delta} = -1/20$, $t^\Hermaphrodite = \alpha^\female_{\Delta} = 0$) opposes selection in diploids (no sex-differences: $s^\Hermaphrodite = 1/10$, $h^\Hermaphrodite = 7/10$), in which case the neo-sex-determining allele can invade regardless of linkage.
-In panel B, gametic competition in males ($t^\male = -1/10$, $t^\female = \alpha^\Hermaphrodite_{\Delta} = 0$) opposes selection in diploids (sex-differences: $s^\male = 3/20$, $s^\female = 1/20$, $h^\Hermaphrodite = 7/10$), in which case the neo-sex-determining allele can once again invade regardless of linkage.
-We use Haldane's map function \citep[Equation 3 in ][]{Haldane1919} to convert from map distance (centiMorgans, cM) to the probability of recombination (an odd number of cross-over events).   
-%\textcolor{red}{Check the mismatch between red and black lines here: probably because of adding or subtracting from 1. }
-%\textcolor{blue}{Can remove the mismatch by flipping the fitnesses between males and females (again).
-That is, if $M_{AA}$ is the fitness of $AA$ male diploids in an ancestral XY system, then $M_{AA}$ is the fitness of $AA$ female diploids in an ancestral ZW system.
-I think this makes sense in A, where we don't really want a difference between the red and black curves, but this makes less sense in B and C where we want to restrict haploid selection to males regardless of the ancestral system.
-We could just not flip the haploid fitnesses, but then does it make sense to flip the diploid fitnesses?}
-}
-\label{fig:Combination_Centimorgans}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Equation \eqref{eq:lambda_neoW} shows that, with weak selection, neo-W alleles can invade an XY system for a large number of selective regimes. 
-To clarify the parameter space under which $\lambda_{W',XY}>1$, we consider several special cases. 
-Firstly, if the \textbf{A} locus is unlinked to the ancestral sex-determining region ($r=1/2$), a more closely linked neo-W ($R<1/2$) can always invade because there is no ancestral association between $A$ alleles and sex chromosomes in males, $\left( \hat{p}^\male_Y-\hat{p}^\male_X \right)=0$, see equation \eqref{eq:freq_diffs}.
-The second term in equation \eqref{eq:lambda_neoW} therefore disappears and invasion depends only on the sign of $(r-R)$, as in the case of the neo-Y. 
-Indeed, invasion typically occurs when the neo-W is more closely linked to the selected locus than the ancestral sex-determining region (Figure \ref{fig:Combination_Centimorgans}).
-
-Secondly, we can simplify the discussion of cases where invasion occurs despite looser sex-linkage, $R>r$, by focusing on the special case where $R=1/2$ and $r<1/2$ (e.g., the selected locus is on the ancestral sex chromosome and the novel sex-determining locus arises on an autosome).
-In Table \ref{tab:specialcases} we give the conditions where invasion occurs when we further assume that haploid selection only occurs in one sex (e.g., during male meiosis only) and dominance coefficients are equal in the two sexes, $h^\female=h^\male$.
-When there is no gametic competition and meiotic drive is in one sex only, an unlinked neo-W can invade as long as the same allele is favoured during diploid selection in males and females ($s^\female s^\male>0$, see Figure \ref{fig:Combination_Centimorgans}A and Figure \ref{fig:SexRatioBad}B).
-%, which is 50\% of the parameter space.
-When there is no meiotic drive and gametic competition occurs in one sex only, an unlinked neo-W can invade as long as the same allele is favoured in male and female diploid selection and there are sex differences in selection of one type (e.g., $s^\female(s^\male-s^\female)>0$, see Figure \ref{fig:Combination_Centimorgans}B).
-%, which is 25\% of the parameter space.
-These special cases indicate that neo-W invasion occurs for a relatively large fraction of the parameter space, even if the neo-W uncouples the sex-determining locus from a locus under selection.
-
-\begin{table}[ht]
-\centering
-\smallskip
-\caption{Invasion conditions for unlinked neo-W ($R=1/2$, $r<1/2$) into ancestral XY with one form of haploid selection}
-\begin{tabular}{l l c }
-\hline\hline
-Scenario &  Assumptions & neo-W spreads ($\lambda_{W',XY}>1$) if \\ [0.5ex] \hline
-%  $r=1/2$, $R<1/2$ & Always \\ [0.5ex] \hline
-%  $r<1/2$, $R=1/2$ &  \\ [0.5ex] \hline
-\noalign{\vskip 1mm}
-  male drive only & $h^\male=h^\female$, $t^\female=t^\male=\alpha^\female_{\Delta}=0$ & $s^\female s^\male>0$ \\ [0.5ex]
- female drive only & $h^\male=h^\female$, $t^\female=t^\male=\alpha^\male_{\Delta}=0$ & $s^\female s^\male>0$ \\ [0.5ex]
- sperm competition only &  $h^\male=h^\female$, $t^\female=\alpha^\female_{\Delta}=\alpha^\male_{\Delta}=0$ & $s^\female(s^\male-s^\female)>0$ \\ [0.5ex]
-  egg competition only & $h^\male=h^\female$, $t^\male=\alpha^\female_{\Delta}=\alpha^\male_{\Delta}=0$ & $s^\male(s^\female-s^\male)>0$ \\ [0.5ex]
-  \hline \hline
-  \label{tab:specialcases}
- \end{tabular}
-\end{table}
-
-%If we further assume equal dominance ($h^\female=h^\male$) and that haploid selection only occurs during male meiosis ($t^\female=t^\male=\alpha^\female_{\Delta}=0$), or female meiosis ($t^\female=t^\male=\alpha^\male_{\Delta}=0$), neo-W invasion occurs when $s^\female s^\male>0$, Figure \ref{fig:Combination_Centimorgans}B.
-%That is, when the same allele is favoured by selection in both males and females (it may remain polymorphic via counter selection during meiotic drive).
-
-%\textcolor{red}{It may seem counterintuitive that, if the $A$ allele is more common on the ancestral-Y than the ancestral-X, and only favoured during haploid selection in males}
-
-%\textcolor{red}{although our predictions also perform well when recombination is small, see figure \ref{fig:WinvasionLowR}.
-We would have to add a line showing what invasion fitness the weak selection approximation would give and add dots to this figure (dots that are currently connected by a line), as in (vD\&K, 2010) }
-
-%Sex ratios
-%Previous research suggests that when the ancestral sex-determining locus is linked to a locus that experiences haploid selection (e.g., meiotic drive), a new, unlinked sex-determining locus invades in order to restore equal sex ratios \citep{Kozielska:2010vm}.
-%Our model provides a good opportunity to determine whether Fisherian sex ratio selection provides a useful explanation for the evolution of new sex-determining loci in other contexts. 
-%Consider, for example, the case where the \textbf{A} locus is linked to the ancestral-SDR ($r<1/2$) and experiences meiotic drive in males only (e.g., during spermatogenesis but not during oogenesis, $\alpha^\male \neq 1/2$, $\alpha^\female=1/2$).
-%We will also disregard gametic competition ($t^\female=t^\male=0$) such that zygotic sex ratios are only biased by meiotic drive in males. 
-%In this case, the zygotic sex ratio can be initially biased only if the ancestral sex-determining system is XY (Figure \ref{fig:Combination_Turnover}B). 
-%If the ancestral sex-determining system is ZW, the zygotic sex ratio will be 1:1 because diploid sex is determined by the proportion of Z-bearing versus W-bearing eggs and meiosis in females is fair (Figure \ref{fig:Combination_Turnover}D).
-%Thus, if the zygotic sex ratio is crucial to the evolution of new genetic sex-determining systems, invasion into ZW and XY systems will be distinct. 
-%However, under weak selection we find that invasion by a homogametic neo-sex-determining allele (XY to XY or ZW to ZW) or by a heterogametic neo-sex-determining allele (XY to ZW or ZW to XY) occur under the same conditions.
-%That is, we can show that $\lambda_{Y',XY}=\lambda_{W',ZW}$ and $\lambda_{Y',ZW}=\lambda_{W',XY}$ (at least up to order $\epsilon^3$; for a numerical example, compare Figure \ref{fig:Combination_Turnover}A,B to Figure \ref{fig:Combination_Turnover}C,D).
-%As it turns out, under weak selection the strength of sex ratio selection favouring, say, the invasion of a neo-W in an XY system is the same as the strength of meiotic drive favouring the invasion of a neo-Y in a ZW system.
-%Even when these forces are not exactly the same (e.g., under tight sex-linkage; compare black and red curves near -25 and 25cM in Figure \ref{fig:Combination_Centimorgans}), it is important to remember that sex ratio selection is only one of many potential selective forces acting to determine transitions between sex-determining systems.
-%It is even possible for the other selective forces to overwhelm sex ratio selection and favour sex-determination transitions that create sex ratio biases (Figure \ref{fig:Combination_Turnover}A,C).
-
-Previous research suggests that when the ancestral sex-determining locus is linked to a locus that experiences haploid selection (e.g., meiotic drive), a new, unlinked sex-determining locus invades in order to restore equal sex ratios \citep{Kozielska:2010vm}.
-Consider, for example, the case where the \textbf{A} locus is linked to the ancestral-SDR ($r<1/2$) and experiences meiotic drive in males only ($\alpha^\male_\Delta \neq 0$, $\alpha^\female_\Delta=0$), without gametic competition ($t^\female=t^\male=0$).
-In this case, the zygotic sex ratio can be initially biased only if the ancestral sex-determining system is XY (Figure \ref{fig:model_outline}B and Figure \ref{fig:SexRatioBad}B). 
-%If the ancxestral sex-determining system is ZW, the zygotic sex ratio will be 1:1 because diploid sex is determined by the proportion of Z-bearing versus W-bearing eggs and meiosis in females is fair (Figure \ref{fig:Combination_Turnover}D).
-If Fisherian sex ratio selection were dominant, we would expect a difference in the potential for XY to ZW and ZW to XY transitions. 
-%However, to leading order with selection weak relative to recombination, we find that sex ratio selection favours the spread of a neo-W by an amount equl to the spread of a neo-Y into a ZW system (relabeling XY as the heterogametic sex and reversing the labels of males and females in Table \ref{tab:specialcases})
-%However, to leading order with selection weak relative to recombination, we find that sex ratio selection favours the spread of a neo-W (through the first terms in table \ref{tab:haplotype_growth}) by an amount that is equal in magnitude to the fitness effects of alleles associated with new sex-determining alleles (second terms in table \ref{tab:haplotype_growth}).
-However, invasion by a neo-W into an XY system and invasion by a neo-Y into a ZW system occur under the same conditions ($\lambda_{Y',XY}=\lambda_{W',ZW}$ and $\lambda_{Y',ZW}=\lambda_{W',XY}$, at least to order $\epsilon^2$).
-For example, in Figure \ref{fig:SexRatioBad}A neo-W alleles invade an ancestral-XY system where females are initially rare.
-However, Figure \ref{fig:SexRatioBad}B shows that a neo-Y can invade an ancestral-ZW system under the same conditions. 
-As a consequence, whenever $R<1/2$, the neo-Y becomes associated with the male meiotic drive allele such that the zygotic sex ratio actually evolves to become biased towards males.
-
-%As selection becomes stronger (or linkage becomes tighter), this symmetry between sex ratio selection and haploid selection is lost, causing differences in the strength of selection favouring the two heterogametic transitions (compare red to black near -25cM and 25 cM in Figure \ref{fig:Combination_Centimorgans}).
-\textcolor{red}{normalise fitness in sexually antagonistic case}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Sex ratio selection is not a good predictor of neo-W invasion into an XY system
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-\includegraphics[width=\linewidth]{Temporal_SR}
-\caption{
-Fisherian sex ratio selection alone is not a good predictor of turnover between sex-determining systems.
-In this figure, selection is ploidally antagonistic with haploid selection favouring the $a$ allele during male meiosis.
-In panel A, male drive in an ancestral ZW system has no affect on the zygotic sex ratio (see Figure \ref{fig:model_outline}B) yet a neo-Y can invade and replace the ancestral sex-determination system (inset shows neo-Y frequency among male gametes, the ancestral W also goes to fixation during this transition).
-When $R<1/2$, the neo-Y becomes associated with the allele favoured by drive, causing the zygotic sex ratio to become biased, hence the frequency of neo-Y among male gametes can be higher than $0.5$ (inset).
-In panel B, male drive in an ancestral XY system causes a male bias, allowing a neo-W to invade and replace the ancestral sex-determination system (inset shows neo-W frequency among female gametes, the ancestral Y also goes to fixation), which balances the zygotic sex ratio.
-Parameters:  $s^\female =s^\male = 0.2$, $h^\female = h^\male = 0.7$, $t^\female = t^\male = \alpha^\female_\Delta = 0$, $\alpha^\male_\Delta = -0.1$, $r=0.02$.
-}
-\label{fig:SexRatioBad}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Why can new sex-determining regions invade when more loosely linked to selected loci ($R>r$)?  
-Consider first the case where both loci are linked to the selected locus ($r<R<1/2$). 
-In an XY system, haploid selection in males can facilitate the spread of a neo-W because the zygotic sex ratio is ancestrally biased and the W helps to equalize the sex ratio (Figure \ref{fig:SexRatioBad}A).
-A new sex determining region can also, however, benefit from becoming more associated with drive.  
-For example in a ZW system with the same selection regime (haploid selection in males), a neo-Y can spread despite the fact that the zygotic sex is initially even; in this case, the neo-Y spreads because it is often found in males and can, if it carries the driven allele $a$, benefit from haploid selection (Figure \ref{fig:SexRatioBad}B).
-While equalizing the sex ratio and benefiting from drive are two primary reasons why haploid selection spurs sex chromosome transitions, more complex situations also arise.  
-For example with $R=1/2$ in Figure \ref{fig:SexRatioBad}B (green curve), the neo-Y spreads despite the fact that it cannot benefit from drive because free recombination moves it randomly between driven and non-driven backgrounds.
-Nevertheless, the unlinked neo-Y can spread because diploids bearing it more often carry the non-driven allele $A$ found at high frequency on the W background, which has higher average diploid fitness to balance the haploid advantage of the $a$ allele at equilibrium.
-
-%The green curves in Figure \ref{fig:SexRatioBad} show transitions between male and female heterogametey even though the new sex-determining region is unlinked to a locus that experiences haploid and diploid selection.
-%We use these green curves to discuss why trans-GSD transitions can occur when $R=1/2$ and $r<1/2$, as in Table \ref{tab:specialcases}.
-%In Figure \ref{fig:SexRatioBad}B, an unlinked neo-W can spread because the zygotic sex ratio is ancestrally male biased. 
-%In Figure \ref{fig:SexRatioBad}A, an unlinked neo-Y spreads despite the fact that the ancestral zygotic sex ratio is even. 
-%In this case, the male meiotic drive allele, $a$, is initially more common among ancestral-Z-bearing eggs than ancestral-W-bearing eggs because the Z is found in males more often than the W ($\hat{p}_{W}^\female-\hat{p}_{Z}^\female>0$, equation \ref{eq:freq_diffs}).
-%Polymorphism at the \textbf{A} locus is maintained by counter-selection against the $a$ allele in diploids and therefore ancestral-ZZ males have generally low diploid fitness. 
-%The neo-Y spreads because it produces males with high diploid fitness through matings with ancestral-W-bearing female gametes, which are more likely to carry the $A$ allele ($\hat{p}_{W}^\female-\hat{p}_{Z}^\female>0$).
-%A freely recombining neo-Y ($R=1/2$) is equally likely to be segregate with the $A$ or $a$ allele.
-%Therefore, the neo-Y is unaffected by male meiotic drive against the $A$ alleles that it introduces into males. 
-%Thus, a key factor in explaining why trans-GSD transitions can occur when $R>r$ is that the neo-SDR determines sex in the diploid phase but recombination occurs before any subsequent haploid selection.
-
-\subsubsection*{Environmental sex determination}
-
-We next consider the case where the new sex-determining mutation, $m$, causes sex to be determined probabilistically or by heterogeneous environmental conditions (environmental sex determination, ESD), with individuals carrying allele $m$ developing as females with probability $k$.
-Here, we do not assume that the environmental conditions that determine sex also differentially affect the fitness of males versus females. 
-Such correlations can favour environmental sex-determination systems that allow each sex to be produced in the environment in which it has highest fitness; in the absence of these correlations, previous theory would predict that ESD is favoured when it produces more equal sex ratios than the ancestral system \citep[see reviews by][]{Charnov:1982wg,Bull:1983vi,West:2009we}.
-%(e.g., maternal condition, mate quality, age, or host size)
-
-The characteristic polynomial determining the eigenvalues (equations \ref{eq:recursions}) does not factor for ESD mutants as it does for $k=0$ or $k=1$. 
-We therefore focus on weak selection here. 
-Assuming weak selection, the spread of the new sex-determining region is given by
-
-\begin{equation}
-\begin{split}
-\lambda_{ESD',XY} =& 1 + \frac{(1-2k)^2}{4}V_{A}{S_{A}}^2\frac{r-R}{r R} \\
-&+\frac{k(\hat{p}^\male_Y-\hat{p}^\male_X)}{2}\left[ k \left(2\alpha_{\Delta}^\male-2\alpha_{\Delta}^\female+t^\male-t^\female \right) -2(1-k)S_{A}\right]+O\left(\epsilon^3\right),
-\end{split}
-\label{eq:lambda_ESD_k}
-\end{equation}
-
-\noindent
-which reduces to $\lambda_{Y',XY}$ when $k=0$ and $\lambda_{W',XY}$ when $k=1$.
-
-%Under Fisherian sex ratio selection, autosomal modifiers favour equal investment in male and female offspring, i.e., a 1:1 sex ratio \citep{Fisher:1930wy,Charnov:1982wg,West:2009we}. 
-%A novel environmental sex-determiner that causes half of its carriers to become female and half to become male ($k=1/2$) will be in males half of the time and in females half of the time (like an autosome).
-%In addition, these novel sex-determination alleles equalize the sex ratio and therefore one might expect them to be favoured by Fisherian sex ratio selection when the resident sex ratio is biased.
-%However, assuming weak selection, we find that the growth rate of a rare, dominant offspring-controlled neo-ESD allele that produces males or females with equal probability ($k=1/2$) is
-Of particular interest are ESD mutations that cause half of their carriers to develop as females and half as males ($k=1/2$, creating equal sex ratios), the spread of which is given by
-\begin{equation}
-\lambda_{ESD',XY} =1+ \frac{1}{2}\frac{(\lambda_{Y',XY\rvert R=1/2}-1) + (\lambda_{W',XY\rvert R=1/2}-1)}{2} + O\left(\epsilon^3\right),
-%V_A \frac{r}{1-2r}  \frac{s_{f} \left( s^\male - 3 s^\female\right) }{8 \left( s_{f} + s_{m} \right)^2} t_{m}^2.
-\label{eq:lambda_ESD}
-\end{equation}
-\noindent
-where $\lambda_{Y',XY\rvert R=1/2}$ and $\lambda_{W',XY\rvert R=1/2}$ represent $\lambda_{Y',XY}$ and $\lambda_{W',XY}$ when evaluated at $R=1/2$ (Equations \ref{eq:lambda_neoY} and \ref{eq:lambda_neoW}).
-That is, recombination between the selected locus and the novel sex-determining locus, $R$, doesn't enter into the $k=1/2$ results.
-This is because sex is essentially randomized each generation, %as if the novel sex-determiner were on an unlinked site that half the time acts as a neo-$W$ and half the time as a neo-$Y$.
-preventing associations from building up between allele $A$ and sex. 
-Equation \eqref{eq:lambda_ESD} shows that the neo-ESD gets half of the fitness of a feminizing mutation (neo-$W$) and half of the fitness of a masculinizing mutation (neo-$Y$), but only has an effect one half of the time (the other half of the time it produces the same sex as the ancestral system would have).
-As discussed above, $\lambda_{Y',XY\rvert R=1/2}$ is necessarily less than one, but $\lambda_{W',XY\rvert R=1/2}$ can be greater than one if there is haploid selection.
-That is, when there is haploid selection, ESD mutations can invade an ancestrally-XY system because they generate females that are either rare or have high fitness, in the same manner as a neo-W.
-
-%An important result from equation \eqref{eq:lambda_ESD} is that ESD can invade if there is haploid selection. 
-%When evaluated at $R=1/2$, $\lambda_{Y',XY}$ is necessarily less than one, but $\lambda_{W',XY}$ can be greater than one if there is haploid selection, as discussed above. 
-%Previous studies where ESD is favoured have typically assumed that environmental conditions (e.g., maternal condition, mate quality, age, or host size) can differentially affect the fitness of males versus females such that ESD invades because it allows sex determination to depend on the environment \citep[reviewed in][]{Charnov:1982wg,Bull:1983vi,West:2009we}.
-%Here, ESD mutations can spread because they generate females that are either rare or have high fitness, in the same manner as a neo-W.
-
-Significantly, equation \eqref{eq:lambda_ESD} is the same whether ESD is invading an ancestrally XY or ZW system (because $\lambda_{Y',XY} = \lambda_{W',ZW}$ and $\lambda_{W',XY} = \lambda_{Y',ZW}$).
-Thus, Fisherian sex ratio selection alone does not explain the invasion of ESD under weak selection because the sex ratio is only biased by male haploid selection when the ancestral sex-determination system is XY.
-Specifically, with male haploid selection, the neo-ESD is equally likely to invade when it equalizes the zygotic sex ratio (through $\lambda_{W',XY}$) and when it doesn't (through $\lambda_{Y',ZW}$). 
-%This is again because haploid selection can facilitate the turnover of sex chromosomes either through sex ratio biases or through associations between the new sex determining region with selected alleles.
-%With weak selection, these two forces are nearly equal in strength. 
-In addition, we note that ESD may not invade, even if the sex ratio is initially biased (e.g., with drive in males only, $r<1/2$, $h^\female=h^\male$, and $s^\female s^\male<0$, then $\lambda_{W',XY}<1$, see Table \ref{tab:specialcases}).
-We conclude that, as with neo-W and neo-Y loci, associations with selected loci mean that the evolution of neo-ESD systems is not straightforwardly predicted by selection to balance the zygotic sex ratio when haploid selection is present.
-
-%Depends 50\% on its fitness relative to non-mutant males and 50\% on its fitness relative to non-mutant females.
-
-%\subsubsection*{Maternally-controlled neo-ESD}
-
-%Fisherian sex ratio selection is sometimes considered in terms of balancing parental investment in male versus female offspring \citep{Charnov:1982wg}.
-%In addition, under environmental sex-determination, the proportion of males/females is sometimes controlled by the mother (e.g., the proportion of eggs laid in warm versus cold environments). 
-%We therefore also considered the invasion of a neo-sex-determining allele ($m$) in a model in which mothers that have at least one $m$ allele produce daughters with probability $k$. 
-%As with offspring-controlled ESD, for all $k\in\{0,1/2,1\}$, we find that invasion into an ancestral XY system is the same as invasion into an ancestrally ZW system (at least up to order $\epsilon^3$, assuming weak selection), implying that transitions between genetic sex-determination and maternally controlled environmental sex-determination are not driven by Fisherian sex ratio selection alone.
-%\textcolor{red}{(Maternal ESD analysis still lacks meiotic drive -- Mathematica can't seem to deal with the added complexity.)}
-
-%One might think that when the sex of zygotes is under the control of mothers, there would be strong selection to balance the sex ratio among zygotes. 
-%However, we find that, with no meiotic drive and weak selection, the invasion fitness of a dominant, maternally controlled sex-determiner that produces proportion $k$ daughters can be written
-%\begin{equation}
-%\lambda_{k} = 1 + V_A S_A C_k + O\left(\epsilon^3\right),
-%\end{equation}
-%where
-%\begin{equation}
-%V_A = \frac{- \left[ t_m + h (s_{f}+s_{m}) \right] \left[ t_m + (1-h) (s_{f}+s_{m}) \right]}{(1-2h)^2(s_{f}+s_{m})^2}
-%\end{equation}
-%is the variance in $A$ ($V_A>0$ when the polymorphic resident equilibrium is stable), 
-%with $h$ the dominance coefficient (equal in both sexes), 
-%$C_k$ is a term that depends on $k$.
-%
-%%k=0
-%\begin{equation}
-%C_0 = big \; ugly \; term
-%\end{equation}
-%
-%%k=1
-%\begin{equation}
-%C_1 = \frac{\left[ (2r(1-R)-R) s^\female + (1-2r)R s^\male \right]}{2}
-%\end{equation}
-%
-%%k=1/2
-%\begin{equation}
-%C_{1/2} = even \; bigger, \; uglier \; term
-%\end{equation}
-%
-%When $k=1$ the maternal- and offspring-controlled results are the same, $C_1 = C_W$, since the mutation remains in females (and hence mutant daughters always have mutant mothers).
-%However, with $k\neq1$ the results with maternal control differ from those with offspring control.
-%Interestingly, for all $k\in\{0,1/2,1\}$, we find that invasion into an ancestrally XY system is the same as invasion into an ancestrally ZW system (at least up to order $\epsilon^3$), implying that sex ratio selection does not drive transitions between genetic sex determination and maternally controlled environmental sex determination.
-%Of particular interest is $k=1/2$ (i.e., when the mother perfectly balances the sex ratio of her offspring).
-%When both recombination rates are small we have $C_{1/2} \approx R(s^\male - s^\female)/8 = \lim_{r \rightarrow 0} C_1/4$.
-%This implies that, at least under tight linkage, the invasion of maternally-controlled ESD is independent of $R$ (because $S_A\propto R^{-1}$) and can invade whenever a neo-$W$ can (which can invade even when it biases the sex ratio further; Figures \ref{fig:WinvasionLowR} -- \ref{fig:WinvasionHighR}).
-
-\section*{Discussion}
-
-%\textcolor{blue}{maybe re-order to put the results up front and focus on sex ratio less.
-Somewhere around these first two paragraphs we should include our tight linkage results.
-At the moment it doesn't make total sense because it assumes that tighter linkage is always favoured unless there is haploid selection.}
-
-%MAIN RESULT
-Two predominant theories explaining the remarkably high frequency of transitions between sex-determination systems are sexually-antagonistic selection and sex ratio selection \citep[reviewed in][]{Blaser2012, vanDoorn2014re}.
-The former predicts that neo-sex-determining alleles can invade when they arise in closer linkage with a sexually-antagonistic locus \citep{vanDoorn:2007eu,vanDoorn:2010hu, Muralidhar2018}.
-The latter predicts that new sex-determining systems are generally favoured if they result in more equal sex ratios than the ancestral system. 
-%The latter predicts that neo-W alleles will invade an XY system when there is a male bias caused by haploid selection in males, and vice-versa, a neo-Y will invade a ZW system when there is a female bias caused by haploid selection in females \citep{Kozielska:2010vm,Ubeda:2015fx}.
-In contrast to these prevailing views, we show that selection (including sexually-antagonistic selection, overdominance, and/or ploidally-antagonistic selection) on loci tightly linked to the ancestral sex-determining region can favour trans-GSD transitions (XY to ZW or ZW to XY) to new sex-determining systems that are less closely linked to the selected loci (e.g., see Figure \ref{fig:SexAntagTighter}).
-Similarly, even when linkage is weak relative to selection, we show that %new sex-determining alleles are typically favoured if they are more closely linked to a locus under haploid selection (even in the absence of diploid sex differences), which is the only condition favouring cis-GSD transitions (XY to XY or ZW to ZW).
-%In addition, with haploid selection and weak selection, 
-trans-GSD transitions (XY to ZW or ZW to XY) can occur where the new sex-determining region is less closely linked to the locus under selection if there is haploid selection (e.g., Figures \ref{fig:Combination_Centimorgans} and \ref{fig:SexRatioBad}).
-%\textcolor{red}{need to mention sex ratio here}
-%Neo-W (neo-Y) alleles invade when their fitness in females (males) is greater than the mean fitness of females (males) under the ancestral sex-determination system and/or females (males) are the rarer sex.
-
-%TIGHT LINKAGE RESULTS
-%When the rate of recombination between the ancestral sex-determining locus and a locus under selection is small relative to the strength of selection (i.e., sex-linkage is tight, or selection is strong), heterogametic transitions (XY to ZW or ZW to XY) that reduce sex-linkage are possible, with or without haploid selection (Figures \ref{fig:SexAntagTighter} and \ref{fig:regionplots}).
-
-%The likelihoods of these transitions are driven by sex ratio selection, direct selection on alleles linked to the neo-sex-determining allele, the ability of the neo-sex-determining allele to avoid selection in one sex, and the ability of the neo-sex-determining allele to bring alleles on the sex-specific chromosome in the ancestor into the other sex (given that the neo-sex determining allele is epistatically dominant to its predecessor).
-
-%This possibility that looser sex-linkage could evolve, even in the absence of haploid selection (Figure \ref{fig:regionplot_2a}A), was overlooked in \cite{vanDoorn:2010hu}, likely because they did not explicitly consider the case of initially tight linkage between the \textbf{A} locus and the ancestral-SDR, which allows substantial differences in allele frequencies to build up \citep[$\hat{p}^\Hermaphrodite_{X} \neq \hat{p}_{Y}^\male$, equation \ref{eq:tightequil};][]{Lloyd1977,Otto2014}.
-%Interestingly, there is substantial overlap between the parameter space that allows both neo-W-$A$ and neo-W-$a$ haplotypes to spread in an XY system and that which selects for increased recombination between X and Y chromosomes \citep[e.g., compare gray region of Figure \ref{fig:regionplot_2a}A with coloured regions of Figure 2(a) in][]{Otto2014}.
-%This makes sense, as when both neo-W haplotypes can spread the neo-W can invade despite reducing sex-linkage, i.e., the rate of recombination between the sex-determining allele and the selected locus increases.
-%We further find that it is easier for a neo-W to invade 
-%\textcolor{red}{explain difference too?
-also explain why a neo-Y doesn't invade to reduce linkage despite selection for more recombination?
-mention something about haploid selection (Fig7B)?} \textcolor{blue}{maybe leave for now}
-
-%HAPLOID SELECTION CAN ACT LIKE SEXUALLY-ANTAGONISTIC SELECTION
-%It has previously been demonstrated that new sex-determining systems can evolve if there is genetic variation maintained by sexually-antagonistic selection \citep{vanDoorn:2007eu,vanDoorn:2010hu}. 
-%In particular, 
-%Under weak selection (or loose sex-linkage), transitions to new sex-determining systems can occur when they arise more closely linked to a sexually-antagonistic locus \citep{vanDoorn:2007eu,vanDoorn:2010hu}.
-%New sex-determining alleles are again favoured if they are more closely linked to a locus under haploid selection, which is the only condition favouring homogametic transitions (XY to XY or ZW to ZW).
-%HAPLOID SELECTION ALSO ALLOWS LOOSER LINKAGE TO EVOLVE
-%However, with haploid selection, heterogametic transitions (XY to ZW or ZW to XY) can occur even when the new sex-determining region is less closely linked to the locus under selection. 
-%Neo-W (neo-Y) alleles invade when their fitness in females (males) is greater than the mean fitness of females (males) under the ancestral sex-determination system and/or females (males) are the rarer sex.
-
-%With sexually-antagonistic selection (between diploid sexes) only, linkage between a selected locus and the sex-determining region strengthens associations between male beneficial alleles and the male-determining allele (Y or Z) and between female beneficial alleles and the female-determining allele (X or W).
-%Thus, the mean fitness of both males and females increases with closer linkage to the sex-determining region. 
-%Therefore, new sex-determining alleles only invade if they are more closely linked than the ancestral sex-determining region. 
-%However, if there is haploid selection on loci linked to an XY (ZW) sex-determining region, selection can maintain polymorphisms at which the product of the frequency of females (males) and the mean fitness of females (males) is lower than it would be without sex-linkage.
-%In these cases, unlinked neo-W (neo-Y) alleles can increase the frequency and/or fitness of the only sex they are found in, at a cost to the other sex, and invade despite lowering population mean fitness (Figure \ref{fig:Combination_MeanFit}).
-%\textcolor{red}{This is similar to mitochondria and male disease ...?}
-
-%%SEX-RATIO SELECTION
-%\textcolor{blue}{maybe drop paragraph?}
-%\textcolor{red}{I messed with the sex ratio selection paragraphs to tone down our "it doesn't matter" speech from before. Have at any amendments you'd like to make.}
-%Linkage between haploid selected loci and sex-determining regions cases biased zygotic sex ratios \citep{Hamilton:1967ts,Burt:2006,Field:2012fd,Field:2013cc}.
-%One might then expect Fisherian sex ratio selection to drive the spread of new sex-determining systems that bring the sex ratio closer to 50:50. 
-%Fisherian sex ratio selection follows from the fact that, for an autosomal locus, half of the genetic material is inherited from a male, and half from a female \citep{Fisher:1930wy,West:2009we}. 
-%Thus, if the population sex ratio is biased towards females, the average per-individual contribution of genetic material to the next generation from males is greater than the contribution from females (and vice versa for male-biased sex ratios).
-%Therefore, a mutant that increases investment in males will spread via the higher per-individual contributions made by males. 
-%%%That is, under Fisherian sex ratio selection, the success of a mutant relative to the non-mutant depends, in equal parts, on the contributions made by males and females to the next generation. 
-%An implicit assumption of Fisherian sex ratio selection is that the mutant allele is autosomal and has the same inheritance pattern as the non-mutant allele. 
-%The mutations we consider here, neo-sex-determining alleles, break this assumption. 
-%For example, the success of neo-Y/neo-W mutations depends only on the number of alleles contributed by males/females (Table \ref{tab:haplotype_growth}). 
-%In this respect, a neo-W is similar to a cytoplasmic element, which also does not experience selection to balance sex ratios \citep{Frank:1989vl,Werren:1998co,Chase:2007bf}.
-%Even mutants that are equally likely to be found in males or females, such as an environmental sex determination mutation (equation \ref{eq:lambda_ESD}), are not strictly autosomal if they determine sex.
-%Thus, despite the fact that sex ratio biases caused by gametic competition or meiotic drive have been shown to exert Fisherian sex ratio selection on various autosomal modifiers \citep{Stalker:1961th,Smith:1975ft,Frank:1989vl,Hough:2013uo,Ubeda:2015fx, Otto:2015va}, we do not find evidence of Fisherian sex ratio selection acting during invasion by neo-sex-determination systems (e.g., see Figure \ref{fig:Combination_Turnover} and \citealt{Ubeda:2015fx}, in which a neo-Y invades despite biasing sex ratios).
-
-%Sex ratio biases caused by gametic competition or meiotic drive have been shown to exert Fisherian sex ratio selection on various autosomal \citep{Stalker:1961th,Smith:1975ft,Frank:1989vl,Hough:2013uo,Ubeda:2015fx, Otto:2015va} and sex-linked \citep{Kozielska:2010vm} modifiers.
-We find that the spread of neo-sex-determining systems cannot be simply predicted from their effect on the sex ratio. 
-On one hand, sex ratio biases caused by haploid selection can facilitate trans-GSD transitions or GSD-ESD transitions between sex-determining systems. 
-For instance, alleles favoured by haploid selection in males often become associated with the Y, which leads to a male-biased zygotic sex ratio.
-This male bias increases the potential for a neo-W to invade (Table \ref{tab:haplotype_growth}), which can equalize the sex ratio \citep[e.g., see Figure \ref{fig:SexRatioBad}B, for related examples see][]{Kozielska:2010vm}.
-%We find that sex ratio biases caused by haploid selection can also affect transitions between sex-determining systems (e.g., see $\zeta$ terms in Table \ref{tab:haplotype_growth}). 
-%However, the neo-W may not equalize the sex ratio (e.g., if the driving allele also drives in females or affects competition among eggs)
-On the other hand, sex ratio selection can be overwhelmed by additional selective effects, preventing a neo-W or ESD allele from invading, even if it would balance the sex ratio (e.g., when selection acts in opposite directions in male and female diploids, Table \ref{tab:specialcases}).
-%and equalizing the sex ratio.
-Indeed, transitions between sex-determining systems can generate stronger sex ratio biases \citep[e.g., Figure \ref{fig:SexRatioBad}A and step 1 in][]{Ubeda:2015fx}.
-%For example, where a neo-Y invades and is linked with a locus that experiences haploid selection in male gametes, the sex ratio evolves to become biased \citep[e.g., see Figure \ref{fig:SexRatioBad}A and step 1 in][]{Ubeda:2015fx}.
-%For example, in an ancestral ZW system, haploid selection in males can allow a linked neo-Y to invade, despite the fact that it creates a male-biased sex ratio because the neo-Y becomes associated with the driven allele (Figure \ref{fig:SexRatioBad}A).
-%\textcolor{blue}{and figure 1, where the end of one panel is the same as the beginning of another, however, this figure may change).}
-%What we would like to stress is that sex ratio selection alone cannot predict when new sex-determining systems can evolve.
-Significantly, with weak selection, we find that there is no difference in conditions allowing XY to ZW and ZW to XY transitions, indicating that sex chromosome transitions are not predominantly predicted by their effect on the sex ratio (i.e., the sex ratio bias created by male haploid selection facilitates the spread of a neo-W into an XY system to the same degree that male haploid selection drives the spread of a neo-Y into a ZW system with a 1:1 sex ratio).
-%An asymmetry can develop when sex-linkage is tight (e.g., Figure \ref{fig:Combination_Centimorgans} near -25cM and 25cM) but under most circumstances we do not predict asymmetry between XY to ZW and ZW to XY transitions despite the presence/absence of sex ratio selection.
-Thus, haploid selection can favour trans-GSD transitions both via sex ratio selection and via selection on alleles associated with the neo-sex-determining allele, and these selective pressures are often predicted to be of equal magnitude.
-%\textcolor{red}{Maybe try to emphasise surprisingness in the paragraph more? e.g., how wrong you'd be if you assumed selection to equalise sex ratios, or it this implied?}
-%\textcolor{blue}{nice, pretty subtle argument but I think that's a good job.}
-
-%Previous studies where ESD is favoured have typically assumed that environmental conditions (e.g., maternal condition, mate quality, age, or host size) can differentially affect the fitness of males versus females such that ESD invades because it allows sex determination to depend on the environment \citep[reviewed in][]{Charnov:1982wg,Bull:1983vi,West:2009we}.
-
-%WHY SEX-RATIO BIASES CAN BE FAVOURED
-%We note two other ways in which sex determination has been shown to relate to zygotic sex ratios.
-%Firstly, female-biased sex ratios can be favoured when there is local mate competition, where all matings are between siblings and assuming one male can inseminate many females \citep{Hamilton:1967ts}.
-%Therefore, with local mate competition, feminizing mutations can spread because they bias the sex ratio towards females \citep{Wilson:1981vm,Vuillleumier:2007bh}. 
-%Secondly, environmental conditions (e.g., maternal condition, mate quality, age, or host size) can differentially affect the fitness of males versus females such that the optimal allocation to males/females depends on the environment \citep{Trivers:1973wb,Charnov:1977tx,Charnov:1982wg}.
-%In such cases, flexible sex-determination systems may evolve in order to allow the zygotic sex ratio to be determined in a way that depends on the environment \citep{Charnov:1977tx,Werren:1984tl,Pen:2010kk}.
-%In this study, we do not consider environmental condition dependence or local mate competition \citep[reviewed in][]{Charnov:1982wg,Bull:1983vi,West:2009we}.
-
-%HOW TO TEST EMPIRICALLY
-%\textcolor{blue}{I think Sally was sceptical of this idea. i.e., if the second term in \ref{eq:lambda_neoW} is negative, then get less transitions with haploid selection included, right? }
-%\textcolor{red}{Yeah, and given that only 1/2 the discovered plant sex chromosomes are hetermorphic and there are so few plant sex chromosomes to begin with (Charlesworth 2016 Annual Review Plant Biology), might it be the case that haploid selection is constraining things?
-perhaps we could think of some particular forms of haploid selection that might be common and give their predicted effects, or just say some things that are possible with haploid selection that are not without it -- if there are any.
-just looking at eq 3 though, its gonna be hard to get a low freq of A on the Y if haploid selection in males favours A, i.e., it should often be positive when there is no female haploid selection, right?}
-%\textcolor{blue}{That sounds right to me and is backed up by equation \eqref{eq:freq_diffs}.
-It may be technically possible for that term to be negative though.
-Re: hetermorphism, I see that as a slightly different issue.
-It's thought that haploid selection may prevent deletions from becoming fixed on the Y, like in the Crowson (2017) paper.
-%I think the issue of `why so few plant sex chromosomes' is partly an issue of detection and also `why so much hermaphroditism'.
-Is it possible that the ESD results could show selective forces that also favour transitions from dioecy to hermaphroditism?
-I think so.
-Our ESD mutant produces 1/2 females and 1/2 males whereas a hermaphrodite invests roughly equally in each type of gamete produced.
-We don't consider the forces that are usually thought to be involved in these transitions though (inbreeding depression, reproductive assurance and possibly others?).
-}
-%Taken at face value, our results indicate that transitions in heterogametey (XY to ZW or vice versa) are more likely to be favoured by selection if there is selection upon both haploid and diploid genotypes rather than diploid selection alone ().
-%This prediction could be examined using a suitable proxy for haploid selection, for example, \cite{Lenormand:2005vb} use the outcrossing rate in plants as a proxy for the strength of pollen competition.
-%In animals, one might expect gametic competition to be stronger in species where sperm is required to live for a long time after spermatogenesis because transcripts shared during spermatogenesis may become depleted, revealing the haploid phenotype of the sperm \citep{Immler:2014im}.
-%Given the caveats mentioned above about the form of meiotic drive modelled, we would also expect that heterogametic transitions in sex determination would be more common in clades where there is meiotic drive.
-
-%Together, our models demonstrate novel selective forces that favour heterogametic transitions (XY to ZW or ZW to XY). 
-%One common prediction is therefore that heterogametic transitions are favoured under a wider range of conditions than homogametic transitions. 
-%However, heterogametic transitions are not clearly in excess.
-For example, \citet{Vicoso:2015hf} found a dozen sex chromosome configurations among Dipteran species but only one transition between male and female heterogametey.
-%While our models examine the selective forces that favour the spread of new sex-determining regions, observed transitions could also reflect the mutation rate for neo-Y versus neo-W alleles (e.g., duplications of the ancestral sex determining region could be particularly likely).
-%In addition, heterogametic transitions could be limited due to the production of YY males or WW females (see below). 
-%Alternatively, it might be useful to compare clades that are expected to differ in the strength of haploid selection (e.g., plants are thought to experience more selection during their multicellular haploid stage
-
-%HAPLOID SELECTION (genomic location of haploid selected loci and comparative patterns) 
-We have shown that the spread of new sex determination systems can be driven by loci experiencing haploid selection. 
-%Our results suggest that haploid selected loci that have been involved in driving turnovers between sex-determination systems could occur around the ancestral- or novel-sex-determining regions. 
-%Our results suggest that polymorphic loci that are ancestrally sex-linked and under sex-specific selection could also drive heterogametic transitions between sex-determination systems. 
-%As with sexually-antagonistic selection, the presence of haploid selected loci around ancestral- or novel-sex-determining regions could support their role in sex chromosome turnover.
-In agreement with this hypothesis, a recent transcriptome analysis in \textit{Rumex} shows that Y-linked genes have higher expression in haploid pollen than autosomal genes \textcolor{red}{(check this is accurate)}.
-Interestingly, haploid-expression is also more common on the autosome that is orthologous to the sex chromosomes in closely related species suggesting that new sex chromosomes may have been favoured through their association with haploid selected alleles on these chromosomes \textcolor{red}{(Sandler et al., 2018, Personal Communication)}.
-%maybe add a flag here for switching to clade-level expectations:
-In general, we predict that haploid selection increases lability of sex-determination systems, particularly because haploid selection can cause transitions that increase or decrease sex-linkage (e.g., the final state of the red line in Figure \ref{fig:SexRatioBad}B is the starting state in Figure \ref{fig:SexRatioBad}A).
-Turnovers driven by haploid selection may help to explain the relative rarity of heteromorphic sex chromosomes in plants, which are thought to experience more selection during their multicellular haploid stage.
-If haploid selection is strong but selective differences between male and female diploids are weak, we find that trans-GSD transitions (XY to ZW or ZW to XY) are favoured more strongly than cis-GSD transitions, with transitions to ESD intermediate (e.g., with $|D^\male - D^\female| << |\alpha_\Delta^\male - \alpha_\Delta^\female + t^\male - t^\female|$ we have $\lambda_{W',XY} > \lambda_{Y',XY}$; Equations \ref{eq:lambda_neoW} and \ref{eq:freq_diffs}).
-Among the relatively few dioecious clades in which multiple species have well characterized sex chromosomes \citep{Ming:2011iy}, trans-GSD transitions have been inferred in \textit{Silene} subsection \textit{Otites} \citep{Slancarova:2013dq} and in \textit{Salicaceae} \citep{Pucholt2015,Pucholt2017}.
-%Potentially, successive heterogametic transitions between master regulators of sex-determination could be inferred from careful examination of the molecular pathways by which sex is determined. 
-%Our predictions could also be examined using a suitable proxy for haploid selection, for example, \cite{Lenormand:2005vb} use the outcrossing rate in plants as a proxy for the strength of pollen competition.
-Assuming that transitions from dioecy to hermaphroditism (equal parental investment in male and female gametes) are favoured in a similar manner to the ESD examined here (equal probability of zygotes developing as males or females), our results suggest that competition during the haploid stage could also drive transitions between dioecy and hermaphroditism, which are frequent in plants \citep{Kafer2017, Goldberg2017}.
-%In animals, one might expect gametic competition to be stronger in species where sperm is required to live for a long time after spermatogenesis because transcripts shared during spermatogenesis may become depleted, revealing the haploid phenotype of the sperm \citep{Immler:2014im}.
-%We would also expect that heterogametic transitions in sex determination would be more common in clades where there is meiotic drive.
-
-%IDENTIFICATION OF LOCI IN GENOMIC LOCATIONS THAT IMPLICATE THEM IN SEX-CHROMOSOME TURNOVER
-%The hypotheses presented here can be empirically investigated in a similar manner to the idea that transitions between sex-determining systems are favoured by linkage to sexually-antagonistic variation.
-%In the case of sexually-antagonistic variation, one supporting observation is that genes expected to be under sexually-antagonistic selection (e.g., those causing bright male colouration) have been found on recently derived sex chromosomes \citep{Lindholm:2002dw,Tripathi:2009cw,Ser:2010iq}.
-In support of their role in sex chromosome turnover, genes expected to be under sexually-antagonistic selection (e.g., those causing bright male colouration) have been found on recently derived sex chromosomes \citep{Lindholm:2002dw,Tripathi:2009cw,Ser:2010iq}.
-Our results show, however, that tight ancestral-linkage of polymorphic loci can also drive trans-GSD transitions. 
-In addition, we find that polymorphic sex determining systems (X, Y, W, and Z alleles all present) can be maintained when a selected locus is tightly linked to the ancestral sex-determining system (e.g., Figures \ref{fig:freqAll}B and \ref{fig:freqAll}C), which is not possible with loose linkage \citep{vanDoorn:2010hu}.
-%As noted by \citet{vanDoorn:2010hu}, it would be prudent to compare closely related clades in order to determine whether observed polymorphisms predate a transition in sex-determination or arose afterwards.
-%, particularly because sex-linkage allows sexually-antagonistic selection to maintain polymorphisms under a different and larger parameter space \citep{Rice:1987hs,Jordan:2011fj}.
-For example, our results suggest a potential mechanism maintaining multiple sex determining alleles in the platyfish (\textit{Xiphophorus maculatus}), in which X,Y, and W alleles segregate at one locus (or two closely-linked loci) near to potentially sexually-antagonistic genes for pigmentation and sexual maturity \citep{Kallman1965,Kallman1968, Volff2001, Schultheis2006}.
-Several rodent species also maintain feminizing alleles along with the ancestral X and Y sex-determination alleles \citep[reviewed in][]{Fredga1994}. 
-For example, in nine \textit{Akadon} species, it appears that male-determining-\textit{sry} expression is suppressed by an autosomal feminizing allele, creating XY females \citep{Bianchi2002,Sanchez2010}, which have increased fitness relative to XX females \citep{Hoekstra2001}.
-In \textit{Mus microtoides}, females can have XX, XX$^\ast$ or X$^\ast$Y genotypes \citep{Veyrunes2010}. 
-Previous theory would predict that the X$^\ast$ chromosome (or the autosome it is fused to) harbours female beneficial alleles, driving its spread. 
-However, XX and XX$^\ast$ females have similar fitness, whereas X$^\ast$Y female fitness is enhanced \citep{Saunders2014,Saunders2016, Veyrunes2017}.
-Although Y-linkage of female-beneficial alleles is counterintuitive, our tight linkage model suggests that it can be stably maintained and then favour new feminizing mutations, which is a parsimonious explanation for the spread of feminizing alleles in these rodent species.
-
-%Limitation 1: DEGENERATE Y
-We note that we assume that sex-determining alleles do not experience direct selection except via their associations with sex and selected alleles.
-However, in some cases, there may be significant degeneration around the sex-limited allele (Y or W) in the ancestral sex-determining region because recessive deleterious mutations and/or deletions accumulate around the Y or W sex-determining regions \citep{Rice:1996ke,Charlesworth:2000cc,Bachtrog:2006ed,Marais:2008hm}.
-During trans-GSD transitions (XY to ZW or ZW to XY), but not cis-GSD transitions (XY to XY or ZW to ZW), any recessive deleterious alleles linked to the Y or W are revealed to selection in YY or WW individuals \citep{Bachtrog:2014bx}.
-This phenomenon was studied by \citet{vanDoorn:2010hu}, who found that degeneration can prevent fixation of a neo-W or a neo-Y allele, leading to a mixed sex-determination system where the ancestral and new sex-determining loci are both segregating.
-However, they noted that very rare recombination events around the ancestral sex-determining region can allow these trans-GSD transitions to complete.  
-%While not explicitly studied, we also predict that Y or W degeneration would prevent fixation of the new sex-determining genes considered here.
-Degeneration around the Y or W could explain why trans-GSD transitions are not observed to be much more common than cis-GSD transitions despite the fact that our models demonstrate that they are favoured under a wider range of conditions, especially with haploid selection.
-For example, \citet{Vicoso:2015hf} found a dozen sex chromosome configurations among Dipteran species but only one transition between male and female heterogamety.
-
-%Limitation 3: don't consider m alleles with similar k to ancester, no ancestral ESD considered
-In this study, we have only considered neo-sex-determining alleles of large effect. 
-However, we expect similar selective forces to act on masculinizing/feminizing alleles of weaker effect. 
-For example, \citet{Muralidhar2018} consider small effect masculinizing/feminizing alleles within a threshold model of sex determination, finding that they can be favoured when linked to loci that experience sexually-antagonistic selection.
-These results echo those for large-effect neo-Y/neo-W alleles \citep{vanDoorn:2007eu,vanDoorn:2010hu}.
-Finally, while we have considered cis-GSD, trans-GSD, and GSD to ESD transitions, we have not explicitly considered ESD to GSD transitions. 
-Recent models of ESD to GSD transitions \citep{Ubeda:2015fx,Muralidhar2018} show that that neo-Y/neo-W alleles can be favoured when they arise near to haploid and/or diploid selected loci, which also occurs in our model.
-
-%Limitation 2: TWO ALLELE DRIVE
-%Another simplification that we made is that meiotic drive involves only a single locus with two alleles. 
-%However, many meiotic drive systems involve an interaction with another locus at which alleles may `suppress' the action of meiotic drive \citep[][]{Burt:2006,Lindholm:2016cw}.
-%Thus, the dynamics of meiotic drive alleles can be heavily dependent on the interaction between two loci and the recombination rate between them, which in turn can be affected by sex-linkage if there is reduced recombination between sex chromosomes \citep{Hurst:1991uh}.
-%Furthermore, in some cases, a driving allele may act by killing any gametes that carry a `target' allele at another locus, in which case there can be fertility effects that alter the equilibrium frequency of a meiotic drive allele \citep{Holman:2015en}.
-%In polygamous mating systems, the intensity of pollen/sperm competition can depend on the density of males available to donate pollen/sperm, which can itself depend on the sex ratio \citep{Taylor:2002wu}.
-%In terms of our model, this implies that the strength of gametic competition ($t^\male$) may both determine and be determined by the sex ratio. 
-%How the evolution of new sex-determining mechanisms could be influenced by two-locus meiotic drive and/or by ecological feedbacks under different mating systems remains to be studied.
-
-%\textcolor{blue}{similarly, this part doesn't discuss our new tight linkage results or our new perspective on sex ratios.}
-%CONCLUSION
-We have shown that tight sex-linkage and haploid selection can drive previously unexpected transitions between sex-determination systems.
-In particular, both can select for neo-sex-determining loci that are more loosely linked. 
-In addition, haploid selection can cause transitions analogous to those caused by purely sexually-antagonistic selection, eliminating the need for differences in selection between male and female diploids.
-We conclude that haploid selection should be considered as a pivotal factor driving transitions between sex-determination systems. 
-Perhaps counterintuitively, transitions involving haploid selection can be driven by sex ratio selection or cause sex ratio biases to evolve and Fisherian sex ratio selection is not an overwhelming force.
-Overall, our results suggest several new scenarios under which new sex-determination systems are favoured, which could help to explain why the evolution of sex-determination systems is so dynamic. 
-%Further, we have shown the way in which transitions are affected by haploid selection is not intuitively obvious. 
-%Firstly, sex-specific haploid selection affects turnovers between sex-determination systems in a manner that is qualitatively different from diploid sex-specific selection. 
-%In particular, closer linkage between a sex-determining locus and a selected locus is not always favoured during heterogametic transitions when there is haploid selection. 
-%Secondly, even though haploid selection is a source of zygotic sex ratio biases, in our models Fisherian sex ratio selection does not have good explanatory power in determining whether various sex-determination systems evolve.
-%This result is surprising given that sex ratios are ultimately determined via the sex-determination system, and leads us to the conclusion that three selective forces -- haploid, diploid, and sex ratio selection -- should all be considered when exploring transitions between sex-determination systems.
-
-\bibliographystyle{amnatnat.bst}
-\bibliography{sex_chromosomes.bib}
-
-\newpage
-%\section*{Figures}
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Tighter linkage allows looser sex-linkage to evolve, even in absence of haploid selection
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\includegraphics[width=\linewidth]{PositionPlot_SexAntagTighter}
-%\caption{
-%In the absence of haploid selection, tight linkage allows looser sex-linkage to evolve in transitions between XY and ZW systems.
-%In panel A, linkage is loose enough relative to selection that the weak selection analytical results hold, and a neo-W can only invade when it is more tightly linked with the selected locus ($R<r$; shaded region).
-%In panel B, linkage is tight enough relative to selection that the weak selection analytical results do no hold, and a neo-W can only invade even when it is less tightly linked with the selected locus ($r<R$; unshaded region).
-%Parameters: $w_{AA}^\female = w_{aa}^\male = 1.05$, $w_{aa}^\female = w_{AA}^\male = 0.85$, $w_{Aa}^\female = 1$, $w_{Aa}^\male = 0.925$, $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
-%}
-%\label{fig:SexAntagTighter}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Both neo-W haplotypes can spread, in the absence of haploid selection, when there is overdominance
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\includegraphics[width=0.45\linewidth]{regionplot_2a}
-%\includegraphics[width=0.45\linewidth]{regionplot_2a_Color_Ya_Either}
-%\includegraphics[width=0.45\linewidth]{BothWsInvade_Overdominance}
-%\caption{
-%In the absence of haploid selection, both neo-W haplotypes can spread in an XY system when there is overdominance.
-%Panel A shows the range of male homozygote fitnesses that allow either neo-W haplotypes to invade.
-%The blue region overlaps with a red region, where both neo-W haplotypes can invade a population with $A$ fixed on the X and $a$ fixed on the Y.
-%The green region (overlapped by the orange region) is where both neo-W haplotypes can invade a population with $a$ fixed on the Y and a polymorphic X.
-%The orange region (outside the green region) is where only the neo-W-$A$ haplotype can invade
-%Panel B shows the temporal dynamics of the invading neo-W haplotypes; in this case the neo-W does not fix, leading to a polymorphic sex-determining system.
-%Asterisk in panel A marks parameter values ($w_{aa}^\male=0.15$, $w_{AA}^\male=0.1$) used in panel B.
-%Parameters: $w_{AA}^\female = w_{aa}^\female = 0.6$, $w_{Aa}^\Hermaphrodite = 1$, $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$, $r=R=0$.
-%\textcolor{red}{make two more temporal plots with visible asterisks in green and orange regions; figure out better colours to show possibilities}
-%}
-%\label{fig:BothOverdominance}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%With weak selection, a less tightly linked neo-W can invade an XY system when there is some haploid selection, and this invasion decreases mean diploid fitness
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\includegraphics[width=0.5\linewidth]{Loose_Fitness_Decline}
-%\caption{
-%With weak selection, a less tightly linked neo-W can invade (and fix in) an XY system (causing the Y to fix in females) when there is some haploid selection (blue and green curves in panel A), and this invasion decreases mean diploid fitness (green and blue curves in panel B).
-%Parameters: $s^\Hermaphrodite = 0.2$, $h^\Hermaphrodite = 0.7$, $t^\Hermaphrodite = \alpha^\male_\Delta = 0$, $\alpha^\female_\Delta = -0.1$, $r=1/10$.
-%}
-%\label{fig:LooseDecline}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%A neo-W can invade an XY system under a large number of selective regimes
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\includegraphics[width=0.5\linewidth]{PositionPlot_4}
-%\caption{
-% A neo-W can invade an XY system under a large number of selective regimes.
-%In panel A, there is no haploid selection ($t^\Hermaphrodite = \alpha^\Hermaphrodite_{\Delta} = 0$) and selection in diploids is sexually antagonistic ($s^\male = -s^\female = 1/10$, $h^\male = 1-h^\female = 3/10$), in which case the neo-sex-determining allele can only invade if it is more closely linked to the selected locus ($R<r$, gray region; but see Figure \ref{fig:SexAntagTighter}B for the case of very tight linkage).
-%In panel B, male drive ($\alpha^\male_{\Delta} = -1/20$, $t^\Hermaphrodite = \alpha^\female_{\Delta} = 0$) opposes selection in diploids (no sex-differences: $s^\Hermaphrodite = 1/10$, $h^\Hermaphrodite = 7/10$), in which case the neo-sex-determining allele can invade regardless of linkage.
-%In panel C, haploid competition in males ($t^\male = -1/10$, $t^\female = \alpha^\Hermaphrodite_{\Delta} = 0$) opposes selection in diploids (sex-differences: $s^\male = 3 s^\female = 3/20$, $h^\Hermaphrodite = 7/10$), in which case the neo-sex-determining allele can once again invade regardless of linkage.
-%We use Haldane's map function \citep[Equation 3 in ][]{Haldane1919} to convert from map distance (centiMorgans, cM) to the probability of recombination (an odd number of cross-over events).   
-%}
-%\label{fig:Combination_Centimorgans}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Sex ratio selection is not a good predictor of neo-W invasion into an XY system
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\includegraphics[width=\linewidth]{Combination_Turnover_Ratio}
-%\caption{
-%Sex ratio selection alone is not a good predictor of turnover between sex-determining systems.
-%In panels A and C, male drive in an ancestral XY system causes a male bias, allowing a neo-W to invade and fix (causing the Y to fix in females), which balances the sex ratio (it also avoids selection in males, and thus makes better females in this case of sex-specific ploidally-antagonistic selection).
-%In panels B and D, male drive in an ancestral ZW system has no affect on the sex ratio, yet a neo-Y can invade and fix (causing the W to fix in males) because it becomes linked with the driving allele, and this imparts a sex ratio bias.
-%Parameters:  $s^\female =s^\male = 0.2$, $h^\female = h^\male = 0.7$, $t^\female = t^\male = \alpha^\male_\Delta = 0$, $\alpha^\female_\Delta = -1/10$, $r=1/20$.
-%}
-%\label{fig:SexRatioBad}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Haploid selection can lead to polymorphic SD systems 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\includegraphics[width=\linewidth]{Polymorphic}
-%\caption{
-%Tight linkage (relative to selection) and/or haploid selection can cause stable polymorphic sex-determining systems.
-%In panel A, there is strong overdominance in both sexes and no haploid selection  (parameters as in Figure \ref{fig:BothOverdominance}B with $r = 1/10$), in which case a neo-W can invade regardless of sex-linkage, but cannot not fix (i.e., the Y does not fix in females, and X, Y, W, and Z all segregate at equilibrium).
-%In panel B, there is sex-antagonistic selection at the diploid stage and drive in females (parameters as in Figure \ref{fig:SexAntagTighter} with $\alpha^\female_\Delta = 1/20$ and $r = 1/10$), in which case a sufficiently tightly linked neo-W can invade ($R<\sim r$), but only fixes if $R=0$.
-%}
-%\label{fig:Polymorphism}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%CYCLES!
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\includegraphics[width=0.5\linewidth]{BothWsInvade_Overdominance_Cycles}
-%\caption{
-%Thought I'd show this just for fun (not for publication).
-%}
-%\label{fig:Cycles}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Heterogametic transitions with/without sex ratio change
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\begin{tikzpicture}[remember picture]
-%	\node[] (plot) {\includegraphics[width=\linewidth]{Combination_Turnover}};
-%	\node[above = 0cm of plot, xshift = -70] () {$r=0.5$, $R=0.05$};
-%	\node[above = 0cm of plot, xshift = 120] () {$r=0.05$, $R=0.5$};
-%	\node[left = 0cm of plot, yshift = 105, rotate = 90] () {XY $\rightarrow$ ZW};
-%	\node[left = 0cm of plot, yshift = -20, rotate = 90] () {ZW $\rightarrow$ XY};
-%\end{tikzpicture}
-%\caption{
-%Heterogametic transitions from XY to ZW sex determination (neo-W frequency shown by black lines, panels A and B) or from ZW to XY (neo-Y frequency shown by black lines, panels C and D) occur similarly regardless of sex ratio biases present before (B versus D) or after (C versus A, dashed lines show male frequency).
-%During invasion by a neo-ZW sex-determination system (A and B), the ancestral Y fixes in both males and females (blue and red lines). 
-%Similarly, the ancestral W allele fixes in males and females (blue and red lines) during a ZW to XY transition. 
-%In this plot, there is no gametic competition ($t^\female=t^\male=0$) and meiotic drive occurs during male meiosis only ($\alpha^\female_{\Delta}=0$, $\alpha^\male_{\Delta}=-1/5$).
-Therefore, sex ratio biases can only arise when the \textbf{A} locus is linked to an XY sex-determining locus.
-%In panels A and C, the neo-sex-determining locus is more closely linked to the \textbf{A} locus than the ancestral sex-detemining region ($r=1/2$, $R=1/20$) such that a neo-Y can caused biased sex ratios (panel C).
-%In panels B and D, the ancestral sex-determining locus is more closely linked to the \textbf{A} locus than the neo-sex-detemining locus ($r=1/20$, $R=1/2$). 
-%Therefore, an ancestral XY sex determination can have a biased zygotic sex ratio that becomes unbiased after an unlinked neo-W invades (B). 
-%However, in panel D, a unlinked neo-Y invades an ancestral ZW sex-determination system in a similar manner but no biases to the zygotic sex ratio occur. 
-%With diploid selection alone, neo-sex-determining loci do not spread if they are less closely linked to the \textbf{A} locus than the ancestral sex-determining locus (see equation \eqref{eq:lambda_neoW} and Figure \ref{fig:Combination_Centimorgans}A).
-%In this plot there are no sex differences in selection and an equilibrium is maintained because selection in diploids opposes meiotic drive, $s^\female =s^\male = 1/5$, $h^\female = h^\male = 7/10$.
-%\textcolor{red}{Aesthetic adjustments: 
-%%Could add titles to the columns/rows: neo-W for row 1, neo-Y for row 3, $r=0.5$, $R=0.05$ for column 1 and $r=0.05$, $R=0.5$ for column 2. 
-%%Could adjust padding (too much whitespace where there is no axis label). 
-%%It also seems could increase ratio of font size relative to plot size to make figure more compact. 
-%%Matt - could you uncomment the line legends in the Mathematica file (function not included in my Mathematica version).
-%Add chromosome cartoons to depict recombination rates?
-%}
-%}
-%\label{fig:Combination_Turnover}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Heterogametic transitions with/without sex ratio change
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\begin{tikzpicture}[remember picture]
-%	\node[] (plot) {\includegraphics[width=\linewidth]{Combination_Turnover_Ratio}};
-%	\node[above = -1cm of plot, xshift = -100] () {XY $\rightarrow$ ZW};
-%	\node[above = -1cm of plot, xshift = 90] () {ZW $\rightarrow$ XY};
-%\end{tikzpicture}
-%\caption{
-%%\textcolor{red}{Is this what Sally was thinking?}
-%%\textcolor{blue}{I think this works but I'm confused as to why the speed of spread should be so much different for XY and ZW here.
-Figure \ref{fig:Combination_Turnover} and \ref{fig:Combination_Centimorgans} suggests that there's not much difference between XY->ZW and ZW->XY.
-Maybe we should just stick with the 4 cases in figure \ref{fig:Combination_Turnover}.
-}
-%%\textcolor{red}{i messed up and had $r=0.5$ instead of $r=0.05$ for B and D. haven't fixed fitness plot below.}
-%Heterogametic transitions occur (panels A and B) regardless of sex ratio biases (panels C and D).
-%A neo-W invades (panel A) and equalizes the male-biased sex ratio (panel C) that was caused by meiotic drive in males.
-%A neo-Y invades (panel B) a population with an equal sex ratio. 
-%With any amount of linkage ($R<1/2$), the neo-Y becomes associated with the driving allele in males, and in the end causes a male bias.
-%Parameters: $s^\female = s^\male = 1/5$, $h^\female = h^\male = 7/10$, $t^\female = t^\male=0$, $\alpha^\female_\Delta = 0$, $\alpha^\male_\Delta = -1/5$, $r = 1/20$.
-%}
-%\label{fig:Combination_Turnover_Ratio}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%Changes in mean fitness
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\begin{tikzpicture}[remember picture]
-%	\node[] (plot) {\includegraphics[width=\linewidth]{Combination_Fitness_Rec}};
-%	\node[above = -1cm of plot, xshift = -100] () {XY $\rightarrow$ ZW};
-%	\node[above = -1cm of plot, xshift = 90] () {ZW $\rightarrow$ XY};
-%\end{tikzpicture}
-%\caption{
-%\textcolor{red}{This complicated thing matches the plot above. I don't think we want to include it...?}
-%}
-%\label{fig:Combination_Fitness_Rec}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Changes in mean fitness
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\begin{tikzpicture}[remember picture]
-%	\node[] (plot) {\includegraphics[width=\linewidth]{Combination_MeanFit}};
-%	\node[above = 0cm of plot, xshift = -70] () {$r=0.5$, $R=0.05$};
-%	\node[above = 0cm of plot, xshift = 120] () {$r=0.05$, $R=0.5$};
-%	\node[left = 0cm of plot, yshift = 105, rotate = 90] () {XY $\rightarrow$ ZW};
-%	\node[left = 0cm of plot, yshift = -20, rotate = 90] () {ZW $\rightarrow$ XY};
-%\end{tikzpicture}
-%\caption{
-%Changes in mean diploid fitness of males (blue lines), females (red lines), and the entire population (black lines) during the transitions between sex-determination systems shown in Figure \ref{fig:Combination_Turnover}.
-%Here mean diploid fitness of a particular sex is its mean diploid viability fitness times twice its frequency in the population, to capture the fact that epistatically dominant sex-determining alleles can also invade because they selfishly make more of the sex they are in.
-%The mean fitness of females increases during the spread of neo-W alleles (A and B) and the mean fitness of males increases during the spread of neo-Y alleles (C and D). 
-%However, when a neo-sex determining system evolves that is less closely linked to a locus under selection (B and D), population mean fitness decreases. 
-%%\textcolor{red}{
-%%Could add titles to the columns/rows: neo-W for row 1, neo-Y for row 3, $r=0.5$, $R=0.05$ for column 1 and $r=0.05$, $R=0.5$ for column 2. 
-%%%\& possibly adjust padding (too much whitespace?). 
-%%%Matt - could you uncomment the line legends in the Mathematica file (function not included in my Mathematica version).
-%%}
-%%\textcolor{red}{I'm still confused why male and female mean fitnesses aren't normalized by their frequency.
-I'm not sure we should be calling them means without this normalization step.
-Or we should justify this by saying that mean fitness also has something to do with the number of a sex, i.e., multiply *real* mean fitness in females by freqfemale/(1/2)?
-See the next figure for what happens when we do normalize.}
-%\textcolor{blue}{I think we should give this plot showing (male mean fitness * freq males) and (female mean fitness * freq females), without multiplying by 2 (leave off black lines, population mean fitness).
-%We could also re-plot the sex ratios on this same scale. 
-%The plot below, `adjusted for sex ratio', could then go in the appendix.
-The point is that neo-W (neo-Y) can invade when the frequency of females (males) multiplied by their mean fitness increases.
-}
-%}
-%\label{fig:Combination_MeanFit}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Changes in mean fitness corrected for sex ratio
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\begin{tikzpicture}[remember picture]
-%	\node[] (plot) {\includegraphics[width=\linewidth]{Combination_MeanFit_Corrected}};
-%\end{tikzpicture}
-%\caption{
-%\textcolor{red}{Last plot with mean fitness of sexes corrected for sex ratio. Could add to previous plot with dashed lines?}
-%}
-%\label{fig:Combination_MeanFit_Corrected}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%Chromosomal Positions
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%%\includegraphics[width=\linewidth]{Combination_Centimorgan}\\
-%%\includegraphics[width=\linewidth]{PositionPlot}\\
-%\begin{tikzpicture}[remember picture]
-%%	\node[] () {\includegraphics[width=\linewidth]{PositionPlot}};
-%	\node[] () {\includegraphics[width=0.5\linewidth]{PositionPlot_2}};
-%%	\node[anchor=east] at (0, 1.5) {\footnotesize diploid sex-antagonism}; %, $s^\male s^\female < 0$};
-%%	\node[anchor=east] at (6.5, 1.5) {\footnotesize haploid sex-antagonism}; %, $s^\male s^\female > 0$};
-%%	\node[anchor=east] at (0, -3) {\footnotesize male drive (ploidy-antagonism)}; %, $s^\male < s^\female$};
-%%	\node[anchor=east] at (6.5, -3) {\footnotesize find something interesting to plot};%, $s^\female < s^\female$};
-%%	\node[anchor=center] at (-1.3, 4.25) {\scriptsize tighter sex-linkage};
-%%	\node[anchor=center] at (2.45, 3.5) {\scriptsize ancestral SDR};
-%%	\draw[->,thick] (2.45, 3.25) -- (2.45, 2.5);
-%%	\node[anchor=center] at (-1.4, -0.25) {\scriptsize novel SDR};
-%%	\draw[->,thick] (-1.4, -0.5) -- (-1.4, -1);
-%\end{tikzpicture}
-%\caption{
-% A neo-W can invade an XY system under a large number of selective regimes.
-%%Invasion fitness of a neo-sex-determining allele against the relative genomic location of a locus under direct selection. 
-%% (neo-Y invading ZW in black, neo-W invading XY in red)
-%%The ancestral sex-determining locus is located at -25 and the novel sex-determining locus is located at 25. %and that there is a polymorphism at the \textbf{A} locus maintained by selection.
-%%Thus, if the neo-sex-determining allele invades in the gray region the system evolves tighter sex-linkage.  
-%In panel A, there is no haploid selection ($t^\Hermaphrodite=\alpha^\Hermaphrodite_{\Delta}=0$) and selection in diploids is sexually antagonistic ($s^\male=-s^\female=1/10$, $h^\male=1-h^\female=3/10$), in which case the neo-sex-determining allele can only invade if it is more closely linked to the selected locus ($R<r$, gray region; but see Figure \ref{fig:SexAntagTighter}B).
-%In panel B, there is no diploid selection ($s^\Hermaphrodite=0$) and selection in haploids is sexually antagonistic ($t^\male=-t^\female=0.08$, $\alpha^\Hermaphrodite_{\Delta}=0$), in which case the neo-sex-determining allele can invade regardless of linkage.
-%In panel C, selection in diploids ($s^\male=s^\female=1/10$, $h^\male=h^\female=7/10$) opposes drive in males ($\alpha^\male_{\Delta}=-0.05$, $t^\Hermaphrodite=\alpha^\female_{\Delta}=0$), in which case the neo-sex-determining allele can once again invade regardless of linkage.
-%We use Haldane's map function \citep[Equation 3 in ][]{Haldane1919} to convert from map distance (centiMorgans, cM) to the probability of a cross-over event.    
-%%we include haploid selection. %and assume that selection in diploids is not sexually-antagonistic ($s^\female s^\male>0$). 
-%%A polymorphism can then be maintained by opposing selection between the haploid and diploid phases. 
-%%In B, there is drive in favour of the $a$ allele in males ($\alpha^\male_{\Delta}=-1/20$), no female meiotic drive or gametic competition, $t^\Hermaphrodite=\alpha^\female_{\Delta}=0$), and equal selection in diploid sexes ($s^\female=s^\male=1/10$, $h^\female=h^\male=7/10$).
-%%In this case, a neo-W can invade even when the selected locus is more closely linked to the ancestral sex determining locus (see Table \ref{tab:specialcases} and Figure \ref{fig:Combination_Turnover}).
-%%In C and D, there is gametic competition among male gametes only (favouring $a$, $t^\male=-1/10$) and no meiotic drive or gametic competition in females ($t^\female=\alpha^\Hermaphrodite_{\Delta}=0$).
-%%In this case, the neo-W does not invade if $s^\female>s^\male$ (panel C: $s^\female=3/20$, $s^\male=1/20$) but does if $s^\female<s^\male$ (panel D: $s^\female=1/20$, $s^\male=3/20$), see Table \ref{tab:specialcases}.\\
-%%\textcolor{red}{
-%%1.
-I suspect that panel C has a region where no equilibrium is maintained (CHECK!
-Maybe include different parameters here or remove the part when no equilibrium).
-MMO: If you trust the sieve function there are stable equilibria across the entire range, although they differ greatly between XY and ZW systems near -25cM.
-%%\\
-%%2.
-Currently use different parameters for B than using in figure \ref{fig:Combination_Turnover} (selection/drive twice as strong in turnover figure).
-MMO: this is to keep it within the bounds of the plot -- using the same parameters as figure 1 makes the peak at -25 reach roughly 0.1, and then it is difficult to see the details of A,C, and D.
-%%%This plot would also benefit from titles giving, e.g., ``sexually-antagonistic selection, $s^\female s^\male<0$'' for A, ``male meiotic drive, $s^\female s^\male>0$'' for B
-%%}
-%}
-%\label{fig:Combination_Centimorgans}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%Haplotype invasion region plot
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\begin{tikzpicture}[remember picture]
-%	\node[] () {
-%	\includegraphics[width=0.5\linewidth]{regionplot_2a}
-%	\includegraphics[width=0.5\linewidth]{regionplot_hap}
-%	};
-%\end{tikzpicture}
-%\caption{
-%Parameter space (gray) where both neo-W haplotypes can invade from the same stable resident $r=0$ equilibria (equations \ref{eq:tightequil}), and therefore where an unlinked neo-W can invade an XY system with perfect sex-linkage.
-%\textbf{A}, In the absence of haploid selection, both neo-W haplotypes can invade for much of the parameter space where the relative fitnesses of male homozygotes, $w_{AA}^\male$ and $w_{aa}^\male$, are both less than that of the heterozygote, $w_{Aa}^\male = 1$.
-%In the white region neo-W haplotypes paired with the allele fixed on the Y cannot invade.
-%Parameters as in \cite{Otto2014} Figure 2a: $w_A^\Hermaphrodite=w_a^\Hermaphrodite$, $\alpha^\Hermaphrodite=1/2$, $w_{Aa}^\Hermaphrodite=1$, and $w_{AA}^\female=w_{aa}^\female=0.75$.
-%\textbf{B}, When selection is the same in both diploid sexes ($w_{aa}^\Hermaphrodite = 1$, $w_{Aa}^\Hermaphrodite = 1 + h s$, $w_{AA}^\Hermaphrodite = 1+s$), both neo-W haplotypes can invade over a portion of the parameter space where selection in diploids ($s$) opposes the force of drive during meiosis in males ($\alpha_{\Delta}^\male$).
-%Parameters: $w_A^\Hermaphrodite=w_a^\Hermaphrodite$, $\alpha^\female=1/2$, $h=1/2$.
-%}
-%\label{fig:regionplot_2a}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%W invades XY and fixes
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}
-%\centering
-%\includegraphics[width=0.5\linewidth]{FreqWLowR}\\
-%\includegraphics[width=0.5\linewidth]{SexRatioLowR}\\
-%\includegraphics[width=0.5\linewidth]{MeanDipFitLowR}
-%\caption{
-%Haploid selection allows a neo-$W$ to invade an ancestral $XY$ system and fix (\textbf{A}) despite temporarily biasing the sex ratio further (\textbf{B}) and decreasing mean diploid viability fitness (\textbf{C}).
-%Complete turnover between genetic sex-determination systems occurs despite the neo-$W$ being less tightly linked to the selected locus than the ancestral sex-determining locus is, $R>r$.
-%Parameters: $k=1$, $s^\female = 0.05$, $s^\male = 0.15$, $h^\female = h^\male = 0.7$, $t^\female = 0$, $t^\male = -0.1$, $\alpha^\male = \alpha^\female = 1/2$, $r=0.01$, $R=0.05$.
-%}
-%\label{fig:WinvasionLowR}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%W invades XY but does not fix
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}
-%\centering
-%\includegraphics[width=0.5\linewidth]{FreqWHighR}\\
-%\includegraphics[width=0.5\linewidth]{SexRatioHighR}\\
-%\includegraphics[width=0.5\linewidth]{MeanDipFitHighR}
-%\caption{
-%Haploid selection allows a completely unlinked neo-$W$ to invade an ancestral $XY$ system (\textbf{A}) despite further biasing the sex ratio (\textbf{B}) and decreasing mean diploid viability fitness (\textbf{C}).
-%The neo-$W$ does not fix (although variation at the \textbf{A} locus is maintained, $V_A>0$), resulting in a polymorphic sex-determination system.
-%Parameters as in Figure \ref{fig:WinvasionLowR} but with $R=0.5$.
-%}
-%\label{fig:WinvasionHighR}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%W invades for all rates of recombination with selected locus
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}
-%\centering
-%\includegraphics[width=0.5\linewidth]{InvasionVsRecombination}
-%\caption{
-%A neo-$W$ invades an ancestral $XY$ system with haploid selection regardless of how tightly it is linked to the selected locus. 
-%Parameters as in Figure \ref{fig:WinvasionLowR}.
-%}
-%\label{fig:InvasionVsRecombination}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%W invasion versus position of selected locus
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}
-%\centering
-%\includegraphics[width=0.5\linewidth]{InvasionVsCentiMorgans}
-%\includegraphics[width=0.5\linewidth]{InvasionVsCentiMorgansAllOrders}
-%\caption{
-%Haploid selection allows a neo-$W$ to invade an ancestral $XY$ system regardless of how tightly it and the ancestral sex-determining locus are linked to the selected locus. 
-%The ancestral sex-determining locus is located at -0.05 and the novel sex-determining locus is located at 0.05 (corresponding to the peaks of invasion fitness), such that the probability of a cross-over between them is $\approx0.1$.
-%The x-axis gives the position of the locus under haploid selection.
-%We used Haldane's map function \citep[Equation 3 in ][]{Haldane1919} to convert from map distance (centiMorgans) to the probability of a cross-over event. 
-%Parameters as in Figure \ref{fig:WinvasionLowR}.
-%}
-%\label{fig:InvasionVsCentiMorgans}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Y invades ZW and fixes (counter example to Kozi explanation)
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}
-%\centering
-%\includegraphics[width=0.5\linewidth]{FreqWCounterKozi}\\
-%\includegraphics[width=0.5\linewidth]{SexRatioCounterKozi}\\
-%\includegraphics[width=0.5\linewidth]{MeanDipFitCounterKozi}
-%\caption{
-%Meiotic drive allows a neo-$Y$ to invade an ancestral $ZW$ system and fix (\textbf{A}) despite temporarily biasing the sex ratio (\textbf{B}).
-%and decreasing mean diploid viability fitness (\textbf{C}).
-%Parameters: $k=0$, $s^\female = s^\male = t^\female = t^\male = 0$, $\alpha^\male = 0.4$, $\alpha^\female = 1/2$, $r=0$, $R=0$.
-%}
-%\label{fig:CounterKozi}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\setcounter{equation}{0}
-\renewcommand{\theequation}{S.\arabic{equation}}
-\setcounter{figure}{0}
-\renewcommand{\thefigure}{S.\arabic{figure}}
-\setcounter{table}{0}
-\renewcommand{\thetable}{S.\arabic{table}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-
-\section*{Appendix}
+\section*{S1 Appendix}
 
@@
 $R$ is the recombination rate between the \textbf{A} locus and the \textbf{M} locus, $\rho$ is the recombination rate between the \textbf{M} locus and the \textbf{X} locus, and $r$ is the recombination rate between the \textbf{A} locus and the \textbf{X} locus.
-Table \ref{tab:chisubstitutions} shows replacements that can be made for each possible ordering of the loci assuming that there is no cross-over interference.
+Table \nameref{tab:chisubstitutions} shows replacements that can be made for each possible ordering of the loci assuming that there is no cross-over interference.
 During meiosis in sex $\Hermaphrodite$, meiotic drive occurs such that, in $Aa$ heterozygotes, a fraction $\alpha^{\Hermaphrodite}$ of gametes produced carry the $A$ allele and $(1-\alpha^\Hermaphrodite)$ carry the $a$ allele.
-
-\begin{table}[ht]
-\centering
-\smallskip
-\caption{
-Substitutions for different loci orders assuming no interference.
-%and $r,R\in(0,1/2)$.\textcolor{blue}{write all in form of first line?
-so that 1/2 cases are okay (can't determine chi if R is 1/2 in second line, or if r is 1/2 in third line}
-}
-\begin{tabular}{l l}
-\hline\hline
-  Order of loci &   \\ [0.5ex] \hline
-  SDR-A-M & $\rho=r(1-R)+R(1-r)$  \\
-  SDR-M-A & $r=\rho(1-R)+R(1-\rho)$ \\ %$\rho=(r-R)/(1-2R)$ \\
-  A-SDR-M & $R=r(1-\rho)+\rho(1-r)$ \\ %$\rho=(R-r)/(1-2r)$ \\
-  \hline \hline
-  \label{tab:chisubstitutions}
- \end{tabular}
-\end{table}
 
@@
 
-\subsection*{Resident equilibria and stability}
-
-In the resident population (allele $M$ fixed), we follow the frequency of $A$ in X-bearing female gametes, $p^\female_X$, and X-bearing male gametes, $p^\male_X$, and Y-bearing male gametes, $p^\male_Y$.
-We also track the total frequency of Y among male gametes, $q$, which may deviate from $1/2$ due to meiotic drive in males. 
-These four variables determine the frequencies of the six resident gamete types: $x_{1}^{\female}=\hat{p}_X^\female$, $x_{2}^{\female}=1-\hat{p}_X^\female$, $x_{1}^{\male}=(1-q)\hat{p}_X^\male$, $x_{2}^{\male}=(1-q)(1-\hat{p}_X^\male)$, $y_{1}^{\male}=q \hat{p}_Y^\male$, and $y_{2}^{\male}=q(1-\hat{p}_Y^\male)$.
-Mean fitnesses in the resident population are given in table \ref{tab:meanfitnesses}.
-
-Various forms of selection can maintain a polymorphism at the \textbf{A} locus, including sexually antagonistic selection, overdominance, conflicts between diploid selection and selection upon haploid genotypes \citep[ploidally antagonistic selection,][]{Immler:2012tl}, or a combination of these selective regimes (see below).
-
-\begin{table}[ht]
-\centering
-\smallskip
-\caption{Mean fitnesses and zygotic sex ratio in the resident population ($M$ fixed, XY sex determination). }
-\begin{tabular}{l l }
-\hline\hline
-  Sex \& Life Cycle Stage & Mean Fitness \\ [0.5ex] \hline  \noalign{\vskip 0.5ex}
-  female gametes ($\bar{w}_H^\female$) & 
-  $p_X^\female w_A^\female + (1-p_X^\female) w_a^\female$ \\ [0.5ex] \hline  \noalign{\vskip 0.5ex}
-  male gametes ($\bar{w}_H^\male$) & 
-  $\bar{p}^{\male} w_A^\male + (1-\bar{p}^{\male}) w_a^\male$ \\ [0.5ex] \hline  \noalign{\vskip 0.5ex}
-  females ($\bar{w}^\female$) & 
-  $\begin{array}{l}  (1-\zeta)^{-1} \big[ p_X^\female w_A^\female p_X^\male w_A^\male w_{AA}^\female + \\
-  (1 - p_X^\female) w_a^\female p_X^\male w_A^\male w_{Aa}^\female + \\
-  p_X^\female w_A^\female (1 - p_X^\male) w_a^\male w_{Aa}^\female + \\
-  (1-p_X^\female) w_a^\female (1 - p_X^\male) w_a^\male w_{aa}^\female \big] / \left( \bar{w}_H^\female \bar{w}_H^\male \right)
-  \end{array} 
-  $ \\ [0.5ex] \noalign{\vskip 0.5ex} \hline  \noalign{\vskip 0.5ex}
-  males ($\bar{w}^\male$) & 
-  $\begin{array}{l} \zeta^{-1} \big[ p_X^\female w_A^\female  p_Y^\male w_A^\male w_{AA}^\male + \\
-  (1 - p_X^\female) w_a^\female  p_Y^\male w_A^\male w_{Aa}^\male + \\
-  p_X^\female w_A^\female  (1 - p_Y^\male) w_a^\male w_{Aa}^\male + \\
-  (1-p_X^\female) w_a^\female  (1 - p_Y^\male) w_a^\male w_{aa}^\male \big] / \left( \bar{w}_H^\female \bar{w}_H^\male \right) 
-  \end{array}
-  $ \\ [0.5ex] \noalign{\vskip 0.5ex} \hline  \noalign{\vskip 0.5ex}
-  fraction zygotes male ($\zeta$) & $q \left[ p_Y^\male w_A^\male+(1-p_Y^\male)w_a^\male\right] / \bar{w}_H^\male $
-   \\ [0.5ex]  \noalign{\vskip 0.5ex}
-  \hline \hline
-  \label{tab:meanfitnesses}
- \end{tabular}
-\end{table}
-
-In particular special cases, e.g., no sex-differences in selection or meiotic drive ($s^\male=s^\female$, $h^\male=h^\female$, and $\alpha^\male=\alpha^\female=1/2$), the equilibrium allele frequency and stability can be calculated analytically without assuming anything about the relative strengths of selection and recombination.
-However, here, we focus on two regimes (tight linkage and weak selection) in order to make fewer assumptions about fitnesses.
-
-\subsubsection*{Recombination weak relative to selection (tight linkage between \textbf{A} and \textbf{X})}
-
-We first calculate the equilibrium frequency of the Y and $A$ alleles in the ancestral population when the recombination rate between the \textbf{X} and \textbf{A} loci is small ($r$ of order $\epsilon$).
-Selection at the \textbf{A} locus will not affect evolution at the novel sex-determining locus, \textbf{M}, if one allele is fixed on all backgrounds. 
-We therefore focus on the five equilibria that maintain both $A$ and $a$ alleles, four of which are given to leading order by:
-
-\begin{subequations}\label{eq:tightequil}
-\begin{align}
-(A)\ \ \ &\hat{p}_{Y}^{\male}=0,
-\ \hat{q}=\frac{1}{2}\left(1 - \alpha_\Delta^\male \frac{ w_{Aa}^{\male} \phi}{w_{Aa}^{\male} \phi+ w_{aa}^{\male} \psi}\right),\\
-&\hat{p}_{X}^{\female}=\frac{w_{a}^{\female} \phi}{w_{a}^{\female} \phi+ w_{A}^{\female} \psi},
-\ \hat{p}_{X}^{\male}=\frac{(1+\alpha_\Delta^\male)w_{Aa}^{\male} \phi}{(1+\alpha_\Delta^\male)w_{Aa}^{\male} \phi +w_{aa}^{\male} \psi} \nonumber \\
-(A')\ \ \ &\hat{p}_{Y}^{\male}=1,
-\ \hat{q}=\frac{1}{2}\left(1 + \alpha_\Delta^\male \frac{w_{Aa}^{\male} \phi'}{w_{Aa}^{\male} \phi' + w_{AA}^{\male} \psi'}\right),\\
-&\hat{p}_{X}^{\female}=1-\frac{w_{A}^{\female} \phi'}{w_{A}^{\female} \phi'+ w_{a}^{\female} \psi'},
-\ \hat{p}_{X}^{\male}=1-\frac{(1-\alpha_\Delta^\male)w_{Aa}^{\male} \phi'}{(1-\alpha_\Delta^\male)w_{Aa}^{\male} \phi'+w_{AA}^{\male} \psi'} \nonumber \\
-(B)\ \ \ &\hat{p}_{Y}^{\male}=0,\ \hat{p}_{X}^{\female}=1,\ \hat{p}_{X}^{\male}=1, \ \hat{q}=(1 -\alpha^\male_\Delta)/2\\
-(B')\ \ \ &\hat{p}_{Y}^{\male}=1,\ \hat{p}_{X}^{\female}=0,\ \hat{p}_{X}^{\male}=0, \ \hat{q}=(1+\alpha^\male_\Delta)/2
-\end{align}
-\end{subequations}
-\begin{equation*}
-\begin{split}
-\phi=&(1+\alpha^\female_\Delta) w_{A}^{\female} w_{Aa}^{\female} \left[ w_{a}^{\male} w_{aa}^{\male} + (1+\alpha_\Delta^\male) w_{A}^{\male} w_{Aa}^{\male} \right]/2 - w_{a}^{\male} w_{a}^{\female} w_{aa}^{\male} w_{aa}^{\female} \\
-\psi=&(1-\alpha^\female_\Delta) w_{a}^{\female} w_{Aa}^{\female} \left[ w_{a}^{\male} w_{aa}^{\male} + (1+\alpha_\Delta^\male) w_{A}^{\male} w_{Aa}^{\male}\right]/2 - (1+\alpha_\Delta^\male) w_{A}^{\male} w_{A}^{\female} w_{Aa}^{\male} w_{AA}^{\female}\\
-\phi'=&(1-\alpha^\female_\Delta) w_{a}^{\female} w_{Aa}^{\female} \left[ w_{A}^{\male} w_{AA}^{\male} + (1-\alpha_\Delta^\male) w_{a}^{\male} w_{Aa}^{\male} \right]/2 - w_{A}^{\male} w_{A}^{\female} w_{AA}^{\male} w_{AA}^{\female}\\
-\psi'=&(1+\alpha^\female_\Delta) w_{A}^{\female} w_{Aa}^{\female} \left[ w_{A}^{\male} w_{AA}^{\male} + (1-\alpha_\Delta^\male) w_{a}^{\male} w_{Aa}^{\male} \right]/2 - (1-\alpha_\Delta^\male) w_{a}^{\male} w_{a}^{\female} w_{Aa}^{\male} w_{aa}^{\female}
-\end{split}
-\end{equation*}
-
-\noindent
-A fifth equilibrium $(C)$ also exists where $A$ is present at an intermediate frequency on the Y chromosome ($0<\hat{p}_{Y}^{\male}<1$). 
-However, equilibrium $(C)$ is never locally stable when $r \approx 0$ and is therefore not considered further.
-Thus, the Y can either be fixed for the $a$ allele (equilibria $A$ and $B$) or the $A$ allele (equilibria $A'$ and $B'$).
-The X chromosome can then either be polymorphic (equilibria $A$ and $A'$) or fixed for the alternative allele (equilibria $B$ and $B'$).
-Since equilibria $(A)$ and $(B)$ are equivalent to equilibria $(A')$ and $(B')$ with the labelling of $A$ and $a$ alleles interchanged, we discuss only equilibria $(A)$ and $(B)$, in which the Y is fixed for the $a$ allele.
-If there is no haploid selection ($\alpha^{\Hermaphrodite}_\Delta=0$, $w_{A}^{\Hermaphrodite}=w_{a}^{\Hermaphrodite}=1$), these equilibria are equivalent to those found by \cite{Lloyd1977} and \cite{Otto2014}.
-
-We next calculate when $(A)$ and $(B)$ are locally stable for $r=0$. 
-According to the `small parameter theory' \citep{Karlin:1972ab,Karlin:1972dq}, these stability properties are unaffected by small amounts of recombination between the SDR and \textbf{A} locus, although equilibrium frequencies may be slightly altered.
-For the $a$ allele to be stably fixed on the Y we need $\bar{w}_{Ya}^{\male} > \bar{w}_{YA}^{\male}$ where $\bar{w}_{Ya}^{\male} = w_{a}^{\male} \big[\hat{p}_X^\female(1-\alpha^\male_\Delta) w_{A}^{\female} w_{Aa}^{\male} + (1-\hat{p}_X^\female)w_{a}^{\female} w_{aa}^{\male} \big]$ and $\bar{w}_{YA}^{\male} = w_{A}^{\male} \big[ \hat{p}_X^\female w_{A}^{\female} w_{AA}^{\male} + (1-\hat{p}_X^\female)(1+\alpha^\male_\Delta) w_{a}^{\female} w_{Aa}^{\male} \big]$.
-That is, Y-$a$ haplotypes must have higher fitness than Y-$A$ haplotypes.  
-Substituting in $\hat{p}_X^\female$ from equation \eqref{eq:tightequil}, fixation of the $a$ allele on the Y requires that $\gamma_{i}>0$ where $\gamma_{(A)}=w_{a}^{\male} \big[ (1-\alpha^\male_\Delta) w_{Aa}^{\male} \phi + w_{aa}^{\male} \psi \big]-w_{A}^{\male} \big[ w_{AA}^{\male} \phi + (1 + \alpha^{\male}_\Delta)w_{Aa}^{\male} \psi \big]$ for equilibrium $(A)$ and $\gamma_{(B)}=(1-\alpha^{\male}_\Delta)w_{a}^{\male}w_{Aa}^{\male}-w_{A}^{\male}w_{AA}^{\male}$ for equilibrium $(B)$.
-Stability of a polymorphism on the X chromosome (equilibrium $A$) further requires that $\phi >0$ and $\psi >0$. 
-Fixation of the $a$ allele on the X (equilibrium $B$) can be stable only if equilibrium $(A)$ is not, as it requires $\psi<0$.
-%and $2w_{A}^{\female}w_{AA}^{\female}>(1-\alpha_\Delta^{\female})w_{a}^{\female}w_{Aa}^{\female}$ or just $4w_{A}^{\female}w_{AA}^{\female}<(1-\alpha_\Delta^{\female})w_{a}^{\female}w_{Aa}^{\female}$ (which also prevents $\psi>0$).
-
-%\textcolor{red}{check last condition and the stability condition below are correct}
-%\textcolor{blue}{The last condition looks good to me, although in your Turnover-norec-MFS.nb you look at YA fixed, so you have to flip everything (so I made Turnover-norec-MFS-MMO.nb to do this).
-%The one issue I can find here is that you can also prevent $\lambda>1$ when the slope and intercept of the quadratic at $\lambda=1$ are negative (you only looked at both being positive).
-In this case we need $4w_{A}^{\female}w_{AA}^{\female}<(1-\alpha_\Delta^{\female})w_{a}^{\female}w_{Aa}^{\female}$, which also prevents $\psi>0$.
-%I've added this in.
-%It could also be the case that the slope and intercept are the same sign but the roots are imaginary - but this is never the case here.
-%Stability condition below looks good to me (from matt version of turnoverSOM-MIKE.nb).}
-
-\subsubsection*{Selection weak relative to recombination (weak selection)}
-
-Here, we assume that selection and meiotic drive are weak relative to recombination ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon$). 
-The maintenance of a polymorphism at the \textbf{A} locus then requires that
-
-\begin{equation}
-\begin{split}
-0&< - \left[(1-h^\female)s^\female +(1-h^\male) s^\male + t^\female +t^\male + \alpha_{\Delta}^\female+\alpha_{\Delta}^\male\right]\\
-%
-\text{and }\quad 0&<h^\female s^\female +h^\male s^\male + t^\female +t^\male + \alpha_{\Delta}^\female+\alpha_{\Delta}^\male.
-\end{split}
-\end{equation}
-
-\noindent
-which indicates that a polymorphism can be maintained by various selective regimes.
-
-Given that a polymorphism is maintained at the \textbf{A} locus by weak selection, the frequencies of $A$ in each type of gamete are the same ($\hat{p}^\female_X=\hat{p}^\male_X=\hat{p}^\male_Y=\bar{p}$) and given, to leading order, by
-
-\begin{equation}
-\bar{p}=\frac{h^\female s^\female + h^\male s^\male +t^\female+t^\male+\alpha_{\Delta}^\female+\alpha_{\Delta}^\male}
-{(2h^\female-1)s^\female+(2h^\male-1)s^\male}
-+O(\epsilon)
-.
-\label{eq:pAve}
-\end{equation}
-
-\noindent
-Differences in frequency between gamete types are of $O(\epsilon)$:
-
-\begin{equation}
-\begin{split}
-\hat{p}^\male_X-\hat{p}^\female_X&=V_{A}\big{(}D^\male - D^\female +\alpha_{\Delta}^\male-\alpha_{\Delta}^\female \big{)}
-+O(\epsilon^2)\\
-%
-\hat{p}^\male_Y-\hat{p}^\female_X&=V_{A}\left[D^\male - D^\female+\alpha_{\Delta}^\male-\alpha_{\Delta}^\female+(1-2r)(t^\male-t^\female)\right]/2r
-+O(\epsilon^2)\\
-%
-\hat{p}^\male_Y-\hat{p}^\male_X&=V_{A}\left(D^\male - D^\female+\alpha_{\Delta}^\male-\alpha_{\Delta}^\female+t^\male-t^\female\right)(1-2r)/2r
-+O(\epsilon^2)
-\end{split}
-\label{eq:freq_diffs}
-\end{equation}
-
-\noindent
-where $V_{A}=\bar{p}(1-\bar{p})$ is the variance in the frequency of $A$ and $D^\Hermaphrodite=\big{[} \bar{p}s^\Hermaphrodite+(1-\bar{p})h^\Hermaphrodite s^\Hermaphrodite\big{]} -\big{[} \bar{p}h^\Hermaphrodite s^\Hermaphrodite+(1-\bar{p}) \big{]}$ corresponds to the difference in fitness between $A$ and $a$ alleles in diploids of sex $\Hermaphrodite \in \{\female,\male\}$ ($\bar{p}$ is the leading-order probability of mating with an $A$-bearing gamete from the opposite sex).
-The frequency of Y among male gametes depends upon the difference in the frequency of the $A$ allele between X- and Y-bearing male gametes and the strength of meiotic drive in favour of the $A$ allele in males, $q=1/2+\alpha_{\Delta}^\male(\hat{p}^\male_Y-\hat{p}^\male_X)/2+O(\epsilon^3)$.
-Without gametic competition or drive ($\alpha_{\Delta}^\Hermaphrodite=t^\Hermaphrodite=0$) our results reduce to those of \citet{vanDoorn:2007eu}.
-
 % the differences in the frequencies of $A$ in each type of gamete are small, as is the bias in the sex-determining factor from the heterogametic sex, and we can solve for the mean frequency of $A$ across all types ($p_A$), the difference in the frequencies of $A$ between two of the three types, and the bias in the frequency of the sex-determining factor, to first order in selection.
@@
 
-\subsection*{Invasion conditions}
-
-%Here, we determine whether a rare neo-Y or neo-W allele spreads when rare, which occurs when $\lambda > 1$.
-%We begin with the general result and then give explicit solutions under tight linkage and weak selection.
-
-%If the average change in frequency of the two haplotypes that carry the $m$ allele ($Am$ and $am$) is positive, invasion will always occur (i.e., if $\left\{(\lambda_{mA}-1)+ (\lambda_{ma}-1) \right\}/2 > 0$ then $\lambda > 1$, see table \ref{tab:haplotype_growth} for $\lambda_{mi}$).
-%If neither haplotype increases in frequency ($\lambda_{mA}, \lambda_{ma} < 1$), the $m$ allele will not invade. 
-%Otherwise, the new sex-determining allele increases in frequency on one \textbf{A} background and declines on the other, and invasion requires
-%\begin{equation}\label{eq:neoYR}
-%R \left[ 
-%\frac{p^\female_X w^\female_A w^\male_a (1-\alpha^\male)}{ \bar{w}^\female_H \bar{w}^\male_H (\lambda_{mA}-1)} + 
-%p^\female_X \frac{w^\female_A}{\bar{w}^\female_H} \frac{w^\male_a(1-\alpha^\male)}{\bar{w}^\male_H} \frac{1}{\lambda_{mA}-1} + 
-%\frac{(1 - p^\female_X) w^\female_a w^\male_A \alpha^\male}{ \bar{w}^\female_H \bar{w}^\male_H (\lambda_{ma}-1)} 
-%\right] 
-%\frac{w^\male_{Aa}}{q\bar{w}^\male} < 1,
-%\end{equation}
-
-%\noindent
-%for the neo-$Y$, and
-
-%\noindent
-%\begin{equation}\label{eq:neoWR}
-%R \left[ 
-%\frac{\bar{p}^\male w^\male_A w^\female_a (1-\alpha^\female)}{ \bar{w}^\male_H \bar{w}^\female_H (\lambda_{mA}-1)} + 
-%\frac{(1 - \bar{p}^\male) w^\male_a w^\female_A \alpha^\female}{ \bar{w}^\male_H \bar{w}^\female_H (\lambda_{ma}-1)} 
-%\right] 
-%\frac{w^\female_{Aa}}{(1-q)\bar{w}^\female} < 1,
-%\end{equation}
-
-%\noindent
-%for the neo-$W$.
-
-%Equations \eqref{eq:neoYR} and \eqref{eq:neoWR} show that the new sex-determining allele, $m$, is expected to invade for any probability of recombination between loci \textbf{A} and \textbf{M}, $R$, when the net flow of recombinants is from the less fit (smaller $\lambda_{mi}$) to the more fit \textbf{A} background (making the terms inside the square brackets in Equations \ref{eq:neoYR} and \ref{eq:neoWR} negative).
-%\textcolor{red}{Q: is it definitely possible to have negative square brackets for a equilibria maintained by selection?}
-%Assuming $g_A^* > 0$ and $g_a^* < 0$ without loss of generality, this is $-(1 - p^\female_X) w_{m,A} g_a^* < p^\female_X w_{m,a} g_A^*$.
-%When the net flow of recombinants is from the more fit to the less fit haplotype, the new sex-determining allele can still invade when the rate of recombination between it and the selected locus is small enough.
-%\textcolor{red}{Q:Is it the case that sometimes the square brackets are positive and invasion occurs for $r_{AM}=1/2$?
-In which case it might be better to have slightly different phrasing here.}
-%Equations \eqref{eq:neoYR} and \eqref{eq:neoWR} show that the new sex-determining allele, $m$, is expected to invade for any probability of recombination between loci \textbf{A} and \textbf{M}, $R$, when the net flow of recombinants is from the less fit (smaller $\lambda_{mi}$) to the more fit \textbf{A} background (making the terms inside the square brackets in Equations \ref{eq:neoYR} and \ref{eq:neoWR} negative).
-%When the net flow of recombinants is from the more fit to the less fit haplotype, the new sex-determining allele can still invade when the rate of recombination between it and the selected locus is small enough.
-%To better understand when these scenarios are possible we next use knowledge of the equilibria and their stability under tight linkage and weak selection.
-
-\textcolor{red}{Cover the other parts of the characteristic polynomial here.}
-\textcolor{blue}{Waiting for Sally's proof!}
-
-A rare neo-Y or neo-W will spread from a given ancestral equilibrium when the leading eigenvalue, $\lambda$, of the Jacobian matrix derived from the eight mutant recursion equations (given by \ref{eq:recursions}c,d,g,h), evaluated at the ancestral equilibrium, is greater than one.
-However, because a neo-Y (neo-W) is always in males (females) and is epistatically dominant to the ancestral sex-determining locus, we need only two recursion equations (e.g., tracking the change in the frequency of neo-Y-$A$ and neo-Y-$a$ gametes from males) and thus the leading eigenvalue is the largest solution the polynomial $\lambda^2 + b\lambda + c = 0$ as described in the text (Table \ref{tab:haplotype_growth}).
-%It can be shown (see supplementary Mathematica file) that the coefficients are $b= - (\lambda_{mA} + \lambda_{ma})+(\chi_{mA} + \chi_{ma})$ and $c = (\lambda_{mA}-\chi_{mA}) (\lambda_{ma}-\chi_{ma}) -\chi_{mA} \chi_{ma}$, where $\lambda_{mi}$ is the multiplicative growth rate of the frequency of mutants on background $i\in\{A,a\}$, without accounting for loss due to recombination, and $\chi_{mi}$ is the rate at which mutants on background $i\in\{A,a\}$ recombine onto the other \textbf{A} locus background in heterozygotes.
-%The leading eigenvalue is then greater than one whenever $\lambda_{mA}>1$ and $\lambda_{ma}>1$, less than one whenever $\lambda_{mA}<1$ and $\lambda_{ma}<1$, and greater than one whenever  $\lambda_{mA}>1$ or $\lambda_{ma}>1$ and $\chi_{ma} (\lambda_{mA}-1) + \chi_{mA} (\lambda_{ma}-1) > 0$.
-
-The general conditions for the invasion of a neo-sex-determining allele are given in the main text, in terms of the growth rates of the mutant haplotypes in the absence of recombination ($\lambda_{mi}$) and the rate that recombination destroys them ($\chi_{mi}$).
-For tight linkage between the ancestral sex-determining locus and the selected locus we can calculate these terms explicitly (see below).
-For weak selection we can take a Taylor series of the leading eigenvalue. 
-The leading eigenvalue, $\lambda$, for any $k$, is given up to order $\epsilon^2$ by equation \eqref{eq:lambda_ESD_k}.
-
-\subsubsection*{Tight linkage between \textbf{A} and \textbf{X} (recombination weak relative to selection)}
-
-Here, we explore the conditions under which a neo-W invades an XY system assuming that the \textbf{A} locus is initially in tight linkage with the ancestral sex-determining region ($r \approx 0$). 
-We disregard neo-Y mutations, which never spread given that the ancestral population is at a stable equilibrium (see supplementary \textit{Mathematica} notebook for proof).
-
-Starting with the simpler equilibrium $(B)$, the terms of that determine the leading eigenvalue are
-
-\begin{subequations}\label{Binvasion}
-\begin{align}
-\lambda_{mA}&= \left[w_{A}^\male (1+\alpha^\male_\Delta) \right]^{-1}
-\frac{w_{A}^\female }{w_{A}^\female}
-\frac{\left[ w_{A}^\male (1+\alpha^\male_\Delta) w_{AA}^\female + 
-w_{a}^\male (1-\alpha^\male_\Delta) w_{Aa}^\female (1+\alpha^\female_\Delta) \right]}
-{ 2w_{AA}^\female } \\
-\lambda_{ma}&= \left[w_{A}^\male (1+\alpha^\male_\Delta) \right]^{-1}
-\frac{w_{a}^\female}{w_{A}^\female}
-\frac{\left[  w_{A}^\male (1+\alpha^\male_\Delta) w_{Aa}^\female (1-\alpha^\female_\Delta)+
-w_{a}^\male (1-\alpha^\male_\Delta) w_{aa}^\female \right]}
-{ 2w_{AA}^\female } \\
-\chi_{mA}&= \frac{1}{2} \left[w_{A}^\male (1+\alpha^\male_\Delta) \right]^{-1}
-\frac{w_{A}^\female }{w_{A}^\female}
- \frac{\left[  w_{a}^\male (1-\alpha^\male_\Delta) w_{Aa}^\female (1 + \alpha^\female_\Delta) \right]}
-{ w_{AA}^\female } \frac{R}{2}\\
-\chi_{ma}&= \frac{1}{2} \left[w_{A}^\male (1+\alpha^\male_\Delta) \right]^{-1}
-\frac{w_{a}^\female}{w_{A}^\female}
- \frac{\left[  w_{A}^\male (1+\alpha^\male_\Delta) w_{Aa}^\female (1-\alpha^\female_\Delta) \right]}
-{  w_{AA}^\female} \frac{R}{2}
-\end{align}
-\end{subequations}
-
-%\noindent
-%In this case, the zygotic sex ratio ($\zeta$) is given by the difference in haploid selection in males on $a$ (fixed on the Y) and $A$ (fixed on the X) alleles, i.e., there are more males than females if $\zeta = \alpha^\male w_A^\male / [(1-\alpha^\male)w_a^\male + \alpha^\male w_A^\male]<1/2$.
-%$\alpha^\male<1/2$ and/or $w_{a}^\male>w_{A}^\male$.
-%Populations with haploid selection for $a$ in males have a male biased zygotic sex ratio are thus more permissive to invasion by a neo-W ($\lambda_{mA}$ and $\lambda_{ma}$ larger).
-%%In addition, the spread of neo-W alleles depends on the fitness of female diploids after mating with an X-$A$ or Y-$a$ male gamete, relative to the fitness of females in the population (all have genotype $AA$ and fitness $w_{AA}^\female$ at this equilibrium).
-%Haploid selection in males has a second effect; the spread rate of neo-W haplotypes is determined by their fitness in diploid females, which depends on their diploid genotype and thus on the male gamete they pair with.
-%Zygotes carrying dominant neo-W alleles will develop as females regardless of their genotype at the XY locus. 
-%Therefore, neo-W females result from matings with either X-$A$ or Y-$a$ male gametes. 
-%The relative proportion of these male gametes is determined by haploid selection in males; mating with a Y-$a$ male gamete is more likely if the $a$ allele is favoured during male gamete production or competition ($\zeta<1/2$).
-%Thus, neo-W females experience different diploid selection than XX females, and the extent of this difference depends on haploid selection in males.
-%Furthermore, haploid selection in females can directly select upon neo-W-$A$ or neo-W-$a$ haplotypes. 
-%A neo-W-$A$ female gamete has the same fitness during haploid competition as resident $A$-bearing female gametes. 
-%On the other hand, neo-W-$a$ female gametes can be favoured or disfavoured during female haploid competition (favoured if $w_{a}^\female>w_{A}^\female$). 
-%Meiotic drive in females ($\alpha^\female$) similarly affects the fitness of these neo-W haplotypes, except that it impacts both haplotypes as meiotic drive only occurs in heterozygotes and therefore does not occur in resident XX females (who are always homozygote $AA$).
-
-Haploid selection impacts the spread of neo-W haplotypes in three ways.
-Firstly, the zygotic sex ratio becomes male biased, $\zeta>1/2$, when the $a$ allele (which is fixed on the Y) is favoured during competition among male gametes or by meiotic drive in males.
-Specifically, at equilibrium $(B)$, female zygote frequency is $1 - \zeta = w_A^\male (1+\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$ where $2\bar{w}_{H}^\male= \big[w_a^\male (1-\alpha^\male_\Delta) +  w_A^\male (1+\alpha^\male_\Delta) \big]$ has been canceled out in equations \eqref{Binvasion} to leave the term $\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]^{-1}$.
-Male biased sex ratios facilitate the spread of a neo-W because neo-W alleles cause the zygotes that carry them to develop as the rarer, female, sex.
-
-Secondly, haploid selection in females selects on neo-W haplotypes directly.
-At equilibrium $(B)$, the fitness of female gametes under the ancestral sex-determining system is $w_{A}^\female$ such that the relative fitnesses of neo-W-$A$ and neo-W-$a$ haplotypes during female gametic competition are $w_{A}^\female/w_{A}^\female$ and $w_{a}^\female/w_{A}^\female$ (see terms in equation \ref{Binvasion}).
-Meiotic drive in females will also change the proportion of gametes that carry the $A$ versus $a$ alleles, which will be produced by heterozygous females in proportions $(1+\alpha_{\Delta}^\female)/2$ and $(1-\alpha_{\Delta}^\female)/2$, respectively.
-These terms are only associated with heterozygous females, i.e., they are found alongside $w_{Aa}^\female$.
-
-Thirdly, haploid selection in males affects the diploid genotypes of females by altering the allele frequencies in the male gametes that female gametes pair with.
-At equlibrium $(B)$, neo-W female gametes will mate with X-$A$ male gametes with probability $ w_A^\male (1+\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$ and Y-$a$ male gametes with probability $w_a^\male (1-\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$, where the $2\bar{w}_{H}^\male$ terms have been canceled in equation \eqref{Binvasion} (as mentioned above).
-Thus, for example, neo-W-$A$ haplotypes are found in $AA$ female diploids with probability $ w_A^\male (1+\alpha^\male_\Delta)/ (2\bar{w}_{H}^\male)$ (first term in square brackets in the numerator of equation \ref{Binvasion}a) and in $Aa$ female diploids with probability $w_a^\male (1-\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$ (see equation \ref{Binvasion}c and the second term in square brackets in the numerator of equation \ref{Binvasion}a).
-
-%For instance, because an epistatically dominant neo-W always causes its carrier to become female, it creates females who carry either Y-$a$ or X-$A$ genotypes from their father.
-%Thus, because when there is a polymorphism the X carries some non-zero frequency of $A$, haploid selection in males impacts the diploid genotypes of females (e.g., creating more $Aa$ females when drive in males favours Y-$a$).
-%How this affects the spread of the neo-W then depends on diploid and haploid selection in females.
-
-The other terms in equations \eqref{Binvasion} are more easily interpreted if we assume that there is no haploid selection in either sex, in which case $\lambda_{mA}=(w_{AA}^\female+w_{Aa}^\female)/2 w_{AA}^\female$ and $\lambda_{ma}=(w_{aa}^\female+w_{Aa}^\female)/ 2 w_{AA}^\female$.
-Neither haplotype can spread under purely sexually-antagonistic selection, where $A$ is directionally favoured in females ($w_{AA}^\female>w_{Aa}^\female>w_{aa}^\female$) and $a$ is directionally favoured in males ($w_{AA}^\male>w_{Aa}^\male>w_{aa}^\male$).
-Essentially, the X is then already as specialized as possible for the female beneficial allele ($A$ is fixed on the X), and the neo-W often makes daughters with the Y-$a$ haplotype, increasing the flow of $a$ alleles into females, which reduces the fitness of those females.
-
-If selection doesn't uniformly favour $A$ in females, however, neo-W-$A$ haplotypes and/or neo-W-$a$ haplotypes can spread ($\lambda_{mA}>1$ and/or $\lambda_{ma}>1$).
-%If $\lambda_{mA}>1$ (requiring $w_{Aa}^\female>w_{AA}^\female$), the implication is that the neo-W can spread alongside the $A$ allele, despite the fact that the neo-W sometimes brings $Y-a$ haplotypes into females, because $a$ is favoured by selection in females despite $A$ being fixed on the X.
-A neo-W-$A$ haplotype can spread ($\lambda_{mA}>1$) when $w_{Aa}^\female>w_{AA}^\female$, despite the fact that a neo-W brings Y-$a$ haplotypes into females.
-In this case the $a$ allele is favoured by selection in females despite $A$ being fixed on the X.
-For this equilibrium to be stable (i.e.,  to keep $A$ fixed on the X), X-$a$ cannot be overly favoured in females and X-$A$ must be sufficiently favoured in males (for example, by overdominance in males).
-Specifically, from the stability conditions for equilibrium (B), we must have $w_{Aa}^\female < 2 w_{AA}^\female$ and $w_{Aa}^\male/\big[(w_{aa}^\male+w_{Aa}^\male)/2\big]>w_{Aa}^\female/w_{AA}^\female$.
-
-Still considering $w_{Aa}^\female>w_{AA}^\female$, the neo-W can also spread alongside the $a$ allele ($\lambda_{ma}>1$) if $w_{aa}^\female$ is large enough such that $(w_{Aa}^\female+w_{aa}^\female)/2>w_{AA}^\female$.
-%there is sufficiently strong underdominance in females ($w_{aa}^\female>w_{Aa}^\female$) \textcolor{blue}{[this is describing directional selection, not overdominance - check the conditions for the case we want to talk about]}, such that $(w_{Aa}^\female+w_{aa}^\female)/2>w_{AA}^\female$.
-This can occur with overdominance or directional selection for $a$ in females (Figure \ref{fig:regionplots}B,C).
-In this case, $a$ is favoured in females (comparing $Aa$ to $AA$ genotypes in females) but $A$ is fixed on the X due to selection in males. 
-The neo-W-$a$ haplotype can spread because it produces females with higher fitness $Aa$ and $aa$ genotypes.
-
-%When both haplotypes can spread on their own ($\lambda_{mA}>1$ and $\lambda_{ma}>1$), the neo-W invades regardless the recombination rate between it and the selected locus, $R$.
-%When neither haplotype can spread ($\lambda_{mA}<1$ and $\lambda_{ma}<1$) the neo-W can never invade.
-%And when only one haplotype can spread on its own the neo-W invades only when the rate of recombination onto the favourable background is sufficiently larger than the rate of recombination off this background (i.e., equation\ref{eq:lambdasGen} is satisfied).
-
-%Haploid selection affects the conclusions outlined above by altering the zygotic sex ratio and exerting direct selection on neo-W haplotypes.
-%The effect of sex ratio selection is straightforward and can be seen in equation \eqref{Binvasion}, where male drive and gamete competition for $a$ (which is fixed on the Y and therefore causes a male bias) increases all four terms.
-%Direct selection on neo-W haplotypes can also be seen in equation \eqref{Binvasion} by noticing that increasing female drive in favour of $A$ increases the neo-W-$A$ haplotype growth rate ($\lambda_{mA}$) while female drive and gamete competition in favour of $a$ increases the neo-W-$a$ haplotype growth rate ($\lambda_{ma}$).
-%Gamete competition in females does not impact the spread of neo-W-$A$ haplotypes because they are on the same background as the resident X.
-%Recombination between the selected locus and the neo-W complicates things slightly, as selective advantages for one neo-W haplotype during the haploid stage in females comes at a cost to the other, and thus recombination off the favoured background becomes more detrimental.
-
-%\textcolor{red}{the versions for equil $(A)$ are not terrible but could be improved by cleverly re-writing with the $\phi$ and $\psi$ terms from above, I think...}
-
-Similar equations can be derived for equilibrium (A) by substituting the equilibrium allele frequencies into Table \ref{tab:haplotype_growth}
-
-\begin{subequations}\label{Ainvasion}
-\begin{align}
-\lambda_{mA}&= \frac{a}{b} \left[w_{AA}^\female w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi +  w_{Aa}^\female (1+\alpha^\female_\Delta) w_a^\male c \right] / (2 w_a^\female) \\
-\lambda_{ma}&= \frac{a}{b} \left[ w_{Aa}^\female (1-\alpha^\female_\Delta) w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi +  w_{aa}^\female w_a^\male c \right] / (2 w_A^\female) \\
-\chi_{mA}&= \frac{a}{b} \frac{R}{2} \left[   w_{Aa}^\female (1+\alpha^\female_\Delta) w_a^\male c \right] / w_a^\female\\ 
-\chi_{ma}&= \frac{a}{b} \frac{R}{2} \left[ w_{Aa}^\female (1-\alpha^\female_\Delta) w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi \right] / w_A^\female
-\end{align}
-\end{subequations}
-
-\noindent
-where
-
-\begin{subequations}
-\begin{align}
-a &= w_a^\female \phi + w_A^\female \psi \\
-b &= w_{AA}^\female \left[ w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \right] \phi^2 + w_{Aa}^\female \left[ w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) + w_{aa}^\male w_a^\male \right] \psi \phi + w_{aa}^\female \left( w_{aa}^\male w_a^\male \right) \psi^2\\
-%c &= w_{Aa}^\male (1-\alpha^\male_\Delta) \phi \left[ w_{Aa}^\male (1+\alpha^\male_\Delta) \phi \right] + w_{Aa}^\male\phi \left[ 2w_{AA}^\male + w_{aa}^\male (1+\alpha^\male_\Delta) \right] \psi + w_{aa}^\male \psi \left(2w_{AA}^\male \psi \right) \\
-c &= w_{Aa}^\male (1-\alpha^\male_\Delta) \phi + 2w_{aa}^\male \psi
-\end{align}
-\end{subequations}
-
-As with equilibrium (B), haploid selection again modifies invasion fitnesses by altering the sex ratio and the diploid genotypes of females and directly selecting upon female gametes.
-The only difference is that resident XX females are no longer always homozygote $AA$ and males are no longer always heterozygote $Aa$.
-Thus the effect of haploid selection in males is reduced, as is the difference in fitness between neo-W haplotypes and resident X haplotypes, as both can be on any diploid or haploid background.
-
-The other terms are easier to interpret in the absence of haploid selection.
-For instance, without haploid selection, the neo-W-$A$ haplotype spreads ($\lambda_{mA}>1$) if and only if
-
-\begin{equation}\label{eq:BeqWAspread}
-2(w_{Aa}^\female-w_{aa}^\female)w_{aa}^\male \psi^2 > (w_{AA}^\female-w_{Aa}^\female)w_{Aa}^\male \phi (\phi-\psi)
-\end{equation}
-
-\noindent  
-where $\phi-\psi=w_{AA}^\female w_{Aa}^\male-w_{aa}^\female w_{aa}^\male$ and both $\phi$ and $\psi$ are positive when equilibrium (A) is stable. 
-In contrast to equilibrium (B), a neo-W haplotype can spread under purely sexually-antagonistic selection  ($w_{aa}^\female<w_{Aa}^\female<w_{AA}^\female$ and $w_{AA}^\male<w_{Aa}^\male<w_{aa}^\male$).
-The neo-W-$A$ can spread as long as it becomes associated with females that bear more $A$ alleles than observed at equilibrium (A). 
-%In this case, the neo-W-$A$ haplotype can spread, despite producing a lot of $Aa$ daughters by obtaining the $a$ from Y-gametes, when $aa$ females, which the neo-W-$A$ never makes, are strongly selected against.
-%This can be intuited from the fact that \eqref{eq:BeqWAspread} will be more easily met when $w_{Aa}^\female-w_{aa}^\female\approx w_{Aa}^\female$ and $w_{AA}^\female-w_{Aa}^\female\approx 0$, implying $w_{aa}^\female \approx 0$ and $w_{Aa}^\female\approx w_{AA}^\female$ (although this is complicated by the fact that $w_{aa}^\female$ and $w_{Aa}^\female$ affect $\phi$ and $\psi$ too, the intuition holds).
-
-Without haploid selection, the neo-W-$a$ haplotype spreads ($\lambda_{ma}>1$) if and only if
-
-\begin{equation}\label{eq:BeqWaspread}
-(w_{aa}^\female + w_{Aa}^\female-2w_{AA}^\female)w_{Aa}^\male \phi^2 + (w_{aa}^\female-w_{Aa}^\female)(w_{Aa}^\male+2w_{aa}^\male) \phi \psi >0
-\end{equation}
-
-\noindent
-This condition cannot be met with purely sexually antagonistic selection (as both terms on the left-hand side would then be negative), but it can be met under other circumstances. 
-For example, with overdominance in males there is selection for increased $A$ frequencies on X chromosomes in males, which are always paired with Y-$a$ haplotypes.
-Directional selection for $a$ in females can then maintain a polymorphism at the $\textbf{A}$ locus on the X.
-This scenario selects for a modifier that increases recombination between the sex chromosomes \citep[e.g., blue region of Figure 2d in][]{Otto2014} and facilitates the spread of neo-W-$a$ haplotypes, which create more females bearing more $a$ alleles than the ancestral X chromosome does.
-
-\subsubsection*{Role of Haploid Selection with Tight Linkage}
-
-Haploid selection generally expands the conditions under which neo-W alleles can spread within ancestral systems that have evolved tight linkage between the sex-determining locus and a selected locus ($r \approx 0$).
-First, haploid selection can allow a polymorphism to be maintained when it would not under diploid selection alone (e.g., with directional selection in diploids). 
-In cases of ploidally-antagonistic selection, where there is a balance between alleles favored in the haploid stage and the diploid stage, neo-W alleles - even unlinked alleles - can spread (Figure \ref{fig:regionPloidAntag}).
-Second, even when diploid selection could itself maintain a polymorphism, haploid selection can increase the conditions under which transitions among sex chromosomes are possible.
-Of particularly importance, when selection is sexually-antagonistic in diploids ($s^\female s^\male <0$ and $0<h^\Hermaphrodite<1$), an unlinked neo-W ($R=1/2$) cannot invade unless there is also haploid selection (see proof in supplementary \textit{Mathematica} file; Figures \ref{fig:SexAntagTighter} and \ref{fig:SexAntagTighterMaleDrive}).
-More generally, haploid selection alters the conditions under which neo-W chromosomes can spread (compare Figures \ref{fig:regionMaleDrive}-\ref{fig:regionFemaleGS} to Figure \ref{fig:regionplots}).
-
-%[SALLY:  I think that is enough, but we could add somewhere??: "Without haploid selection, unlinked neo-W alleles ($R=1/2$) can invade only under certain conditions, requiring either overdominance in males or underdominance in females (see proof in supplementary \textit{Mathematica} file).?
-Note that underdominance in females with directional selection in males can lead to the spread of unlinked neo-W?s, but only from equilB (only $\lambda_{ma}$ is greater than one in this case).]
-
-Male haploid selection in favour of the $a$ allele ($\alpha_{\Delta}^\male<0$, $w_{A}^\male<w_{a}^\male$) generates male-biased sex ratios at equilibria (A) and (B), where Y-$a$ is fixed ($\hat{p}_{Y}^\male=0$).
-Male-biased sex-ratios facilitate the spread of neo-W-$A$ and neo-W-$a$ haplotypes (increasing $\lambda_{mA}$ and $\lambda_{ma}$). 
-Panels A-C in Figures \ref{fig:regionMaleDrive} and \ref{fig:regionMaleGS} show that neo-W haplotypes tend to spread for a wider range of parameters when sex ratios are male biased, compared to Figure \ref{fig:regionplots} without haploid selection.
-By contrast, male haploid selection in favour of the $A$ allele generates female-biased sex ratios and reduces $\lambda_{mA}$ and $\lambda_{ma}$, as demonstrated by panels D-F in Figures \ref{fig:regionMaleDrive} and \ref{fig:regionMaleGS}.
-
-Female haploid selection generates direct selection on the neo-W-$A$ and neo-W-$a$ haplotypes as they spread in females. 
-Thus, female haploid selection in favour of the $a$ allele tends to increase $\lambda_{ma}$ and decrease $\lambda_{mA}$, as shown by panels A-C in Figures \ref{fig:regionFemaleDrive} and \ref{fig:regionFemaleGS}.
-Conversely, female haploid selection in favour of the $A$ allele increases $\lambda_{mA}$ and decreases $\lambda_{ma}$, see panels D-F in Figures \ref{fig:regionFemaleDrive} and \ref{fig:regionFemaleGS}.
-
-Thus, the impact of haploid selection on sex chromosome transitions must be considered as two sides of a coin: it can generate sex ratio biases that drive sex chromosome transitions to equalize the sex ratio, but it can also drive in new sex chromosomes and thereby cause sex ratios to become biased.
-
-%\subsubsection*{Tight Linkage and Haploid Selection}
-
-%With tight linkage, haploid selection generally expands the conditions under which neo-W alleles can spread. 
-%For example, when selection is sexually-antagonistic in diploids ($s^\female s^\male <0$ and $0<h^\Hermaphrodite<1$) an unlinked neo-W ($R=1/2$) cannot invade unless there is also haploid selection (Figures \ref{fig:SexAntagTighter} and \ref{fig:SexAntagTighterMaleDrive}).
-%Secondly, with haploid selection, overdominance ($w_{aa}^\Hermaphrodite<w_{Aa}^\Hermaphrodite$ \& $w_{AA}^\Hermaphrodite<w_{Aa}^\Hermaphrodite$) is not required for neo-W-$a$ haplotypes to spread ($\lambda_{ma}>1$) (Figures \ref{fig:regionMaleDrive}-\ref{fig:regionFemaleGS}).
-%Haploid selection and overdominance allow unlinked neo-W alleles to invade even when there is tight linkage between the ancestral SDR and the selected locus (Figure \ref{fig:loose_invades_tight}).
-%Finally, haploid selection can maintain a polymorphism in the face of directional selection in male and female diploids (ploidally-antagonistic selection). 
-%When selection is ploidally-antagonistic, neo-W alleles often spread, for at least some values of $R$ (Figure \ref{fig:regionPloidAntag}).
-
-%As discussed above, male haploid selection alters the sex ratio and the alleles carried by male gametes that female gametes pair with. 
-%Male haploid selection in favour of the $a$ allele ($\alpha_{\Delta}^\male<0$, $w_{A}^\male<w_{a}^\male$) generates male-biased sex ratios at equilibria (A) and (B), where Y-$a$ is fixed ($\hat{p}_{Y}^\male=0$).
-%Male-biased sex ratios facilitate the spread of neo-W-$A$ and neo-W-$a$ haplotypes (increasing $\lambda_{WA}$ and $\lambda_{Wa}$). 
-%Panels A-C in Figures \ref{fig:regionMaleDrive} and \ref{fig:regionMaleGS} show that neo-W haplotypes tend to spread for a wider range of parameters when sex ratios are male biased, compared to Figure \ref{fig:regionplots} without haploid selection.
-%By contrast, male haploid selection in favour of the $A$ allele generates female-biased sex ratios and reduces $\lambda_{WA}$ and $\lambda_{Wa}$, as demonstrated by panels D-F in Figures \ref{fig:regionMaleDrive} and \ref{fig:regionMaleGS}.
-
-%Female haploid selection generates direct selection on the neo-W-$A$ and neo-W-$a$ haplotypes as they spread in females. 
-%Thus, female haploid selection in favour of the $a$ allele tends to increase $\lambda_{Wa}$ and decrease $\lambda_{WA}$, as shown by panels A-C in Figures \ref{fig:regionFemaleDrive} and \ref{fig:regionFemaleGS}.
-%Conversely, female haploid selection in favour of the $A$ allele increases $\lambda_{WA}$ and decreases $\lambda_{Wa}$, see panels D-F in Figures \ref{fig:regionFemaleDrive} and \ref{fig:regionFemaleGS}.
-
-%Without haploid selection this reduces to
-%\begin{subequations}
-%\begin{align}
-%\lambda_{mA}&= \frac{a}{b} \left[w_{AA}^\female w_{Aa}^\male \phi / 2 + w_{Aa}^\female \frac{c}{d}\right]  \\
-%\lambda_{ma}&= \frac{a}{b} \left[w_{Aa}^\female w_{Aa}^\male \phi / 2 +  w_{aa}^\female \frac{c}{d}\right] \\
-%\chi_{mA}&= \frac{a}{b} R \left[ w_{Aa}^\female \frac{c}{d} \right] \\ 
-%\chi_{ma}&= \frac{a}{b} R \left[ w_{Aa}^\female w_{Aa}^\male \phi / 2 \right] 
-%\end{align}
-%\end{subequations}
-
-%These simplify considerably when there is no haploid selection:
-%
-%\begin{subequations}
-%\begin{align}
-%\lambda_{mA}&= \frac{(\phi + \psi)[(w_{AA}^\female + w_{Aa}^\female ) w_{Aa}^\male \phi + 2 w_{Aa}^\female w_{AA}^\male \psi ]}{2 (w_{AA}^\female w_{Aa}^\male \phi^2 + \psi(w_{Aa}^\female(w_{AA}^\male + w_{Aa}^\male)\phi + w_{aa}^\female w_{AA}^\male \psi)}\\
-%\lambda_{ma}&=  \frac{(\phi + \psi)[(w_{aa}^\female + w_{Aa}^\female ) w_{Aa}^\male \phi + 2 w_{aa}^\female w_{AA}^\male \psi ]}{2 (w_{AA}^\female w_{Aa}^\male \phi^2 + \psi(w_{Aa}^\female(w_{AA}^\male + w_{Aa}^\male)\phi + w_{aa}^\female w_{AA}^\male \psi)}\\
-%\chi_{mA}&= R \frac{(\phi + \psi) w_{Aa}^\female w_{AA}^\male}{2 (w_{AA}^\female w_{Aa}^\male \phi^2 + \psi(w_{Aa}^\female(w_{AA}^\male + w_{Aa}^\male)\phi + w_{aa}^\female w_{AA}^\male \psi)} \\ 
-%\chi_{ma}&= R \frac{(\phi + \psi) w_{Aa}^\female w_{Aa}^\male}{2 (w_{AA}^\female w_{Aa}^\male \phi^2 + \psi(w_{Aa}^\female(w_{AA}^\male + w_{Aa}^\male)\phi + w_{aa}^\female w_{AA}^\male \psi)}\\
-%\end{align}
-%\end{subequations}
-%
-%\begin{subequations}
-%\begin{align}
-%\lambda_{mA}&= [( w_{AA}^\female + w_{Aa}^\female ) w_{Aa}^\male \phi + 2 w_{Aa}^\female w_{AA}^\male \psi] a \\
-%\lambda_{ma}&=  [(w_{aa}^\female + w_{Aa}^\female ) w_{Aa}^\male \phi + 2 w_{aa}^\female w_{AA}^\male \psi ] a\\
-%\chi_{mA}&= R w_{Aa}^\female (w_{Aa}^\male \phi + 2 w_{AA}^\male \psi) c \\ 
-%\chi_{ma}&= R w_{Aa}^\female w_{Aa}^\male \phi c \\
-%\end{align}
-%\end{subequations}
-%\noindent
-%where 
-%$c = \frac{\phi + \psi}{2 [w_{AA}^\female w_{Aa}^\male \phi^2 + \psi(w_{Aa}^\female(w_{AA}^\male + w_{Aa}^\male)\phi + w_{aa}^\female w_{AA}^\male \psi]}$ and $\phi$ and $\psi$ are evaluated with $\alpha^{\Hermaphrodite}=1/2$ and $w_a^\Hermaphrodite=w_A^\Hermaphrodite=1$.
-
-%With $R=0$ the two eigenvalues are $\lambda_{mA}$ and $\lambda_{ma}$.
-%The neo-W can then invade on the $A$ background when $\lambda_{mA}>1$ and the neo-W can invade on the $a$ background when $\lambda_{ma}>1$.
-%Even in this case it is difficult to see from equation \ref{Ainvasion} when the neo-W will invade.
-%Below we discuss why $\lambda_{mA}$ and $\lambda_{ma}$ might be larger than one and confirm the logic numerically.
-%
-%
-%For simplicity, consider the case of no haploid selection.
-%A polymorphism at the $\mathbf{A}$ locus then requires sexually-antagonistic selection \citep{vanDoorn:2007eu}.
-%Given that $a$ is fixed on the Y, one can consider the $a$ allele `male beneficial' and the $A$ allele to be `female beneficial'. 
-%Because X chromosomes spend some time in males the frequency of $A$ on the X can reach an intermediate equilibrium (equilibrium A).
-%
-%We can therefore reason that when a neo-W invades equilibrium (A), it is likely to spread on the $A$ background as W chromosomes are always in females.
-%The neo-W can outcompete the ancestral, `comprimising' X because it can specialize on females by fixing the `female beneficial' allele.  
-%We call this the `sex-specialist hypothesis'.
-%This hypothesis should only work when the benefit of specializing outweighs the cost of bringing Y chromosomes into females (the neo-W is epistatically dominant over the X/Y locus).
-%
-%One could also reason that, when the neo-W spreads, it does so precisely because it brings Y chromosomes, and their associated alleles, into females, something the X cannot do.
-%However, this requires a somewhat particular (perhaps `perverse') equilibrium, where XX females do worse than XY females despite associations on the X and Y being built up by selection.
-%One example of such a perverse equilibrium is produced by overdominance in both sexes.
-%Overdominance in females selects for an allele frequency of 0.5 on the X ($A$ and $a$ equally frequent, maximizing the number of heterozygotes). 
-%However, given that $a$ is fixed on the Y, overdominance in males selects for the X to become more associated with the $A$. 
-%Thus, a compromising equilibrium is reached on the X chromosome and females fitness suffers due to the overproduction of $AA$ homozygotes.
-%This sets up a scenario in which a neo-W can invade on the $a$ background, despite the fact that $a$ is fixed on the Y and in that sense `male beneficial'.
-%We call this the `perverse hypothesis'.
-%
-%Figure \ref{fig:Region_Plots} shows where the sex-specialist (red) and perverse (blue) hypotheses are valid.
-%The left panel demonstrates that both hypotheses can be simultaneously valid with overdominance in both sexes and sex differences in selection, which overlaps the parameter region where there is selection for increased recombination between the sex chromosomes \citep[compare with figure 2a in][]{Otto2014}.
-%The right panel shows that the perverse hypothesis is no longer valid when selection is exactly the same in both sexes, despite the fact that there is selection for increased recombination between the sex chromosomes with sufficiently strong overdominance \citep[compare with figure 3 in][]{Otto2014}.
-%
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%Sex-specialist vs perverse hypotheses
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\includegraphics[width=0.45\linewidth]{regionplot_2a}
-%\includegraphics[width=0.45\linewidth]{regionplot_3}\\
-%\caption{
-%Numerical exploration of where sex-specialist (red) and perverse (blue) hypotheses are valid, i.e., where an internally stable resident equilibrium can be invaded by a neo-W that is perfectly linked with the allele not fixed on the Y (red) or the allele that is fixed on the Y (blue).
-%\textbf{(Left)}
-%The perverse equilibrium is only valid with overdominance while the sex-specialist hypothesis is valid over the entire range shown.
-%Both hypotheses are simultaneously valid over much of the parameter space where increased recombination between the sex chromosomes is selected \citep[][figure 2a]{Otto2014}.
-%\textbf{(Right)}
-%Only the sex-specialist hypothesis is valid with no sex-differences in selection, despite selection for increased recombination between the sex-chromosomes with strong overdominance \citep[][figure 3]{Otto2014}.
-%Parameters: $w_{Aa}^\Hermaphrodite = 1$, $w_a^\Hermaphrodite = w_A^\Hermaphrodite = 1$, $\alpha^\Hermaphrodite = 1/2$, $r=R=0$, and in left panel $w_{aa}^\female = w_{AA}^\female = 0.6$.
-%}
-%\label{fig:Region_Plots}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section*{Supplementary Figures}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Both neo-W haplotypes can spread, in the absence of haploid selection, when there is overdominance
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-\centerline{\includegraphics[width=\linewidth]{PositionPlot_Overdominance}}
-\caption{
-Neo-W alleles can spread when loci under diploid selection are tightly linked to the ancestral sex determining locus ($r\approx0$). 
-In panels A and B, the $a$ allele is favoured in females ($w_{aa}^\female=1.05$, $w_{Aa}^\Hermaphrodite=1$, $w_{AA}^\female=0.85$) and selection in males is overdominant ($w_{aa}^\male=w_{AA}^\male=0.75$).
-In panels C and D, selection in males and females is overdominant ($w_{aa}^\female=w_{AA}^\female=0.6$, $w_{aa}^\male=0.5$, $w_{AA}^\male=0.7$, $w_{Aa}^\Hermaphrodite=1$).
-There is no haploid selection $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
-These parameters are marked by daggers in Figure \ref{fig:regionplots}B and C, which show that neo-W invasion is expected for any $R$ ($\lambda_{WA},\lambda_{Wa}>1$) when the $a$ allele is nearly fixed on the Y (black lines in this figure; not stable for $r>>0$).
-Equilibria where the $A$ allele is more common among Y-bearing male gametes can also be stable and allow neo-W invasion for these parameters (blue lines). 
-The weak selection approximation holds when all recombination rates are large relative to selection (around 0 in panels A and C), in which case, in the absence of haploid selection, neo-W alleles should spread if and only if they are more tightly linked to the selected locus (positive invasion fitness if and only if the selected locus is in the grey region).
-However, when linkage is tight (panels B and D and when the selected locus is near the SDRs in all panels), this weak selection prediction can break down. 
-}
-\label{fig:positionOverdominance}
-\end{figure}
-
-\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Both neo-W haplotypes can spread, in the absence of haploid selection, when there is overdominance
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-\centerline{\includegraphics[width=\linewidth]{Temporal_Overdominance}}
-\caption{
-Following invasion by a neo-W allele, there can be a complete transition to a new sex-determination system, maintenance of polymorphism at both ancestral-XY and neo-ZW sex determining regions, or loss of the new sex-determining allele.
-Here we plot the frequency of the neo-W allele among female gametes; as the neo-W reaches frequency $0.5$, polymorphism at the ancestral XY locus is lost with Y becoming fixed such that sex is determined only be the ZW allele carried by a female gamete.
-Panels A, C and D show cases where a steady state is reached with the neo-W at a frequency below $0.5$, in which case ancestral-X and Y alleles also both segregate. 
-In all cases, we assume that the $a$ allele is initially more common than the $A$ allele on the Y (Y-$a$ is fixed when $r=0$). 
-When $r>0$ (panels B and D), Y-$A$ haplotypes created by recombination can become more common than Y-$a$ haplotypes as the neo-W spreads.
-In B, this leads to loss of the neo-W and the system goes to an equilibrium with X-$a$ and Y-$A$ haplotypes fixed (equilibrium $A'$), such that all females have the high fitness genotype $aa$ and all males are $Aa$.
-For the parameters in B, neo-W alleles have negative invasion fitness when the Y-$A$ haplotype is ancestrally more common than Y-$a$ (see blue lines in Figure \ref{fig:positionOverdominance}A and  \ref{fig:positionOverdominance}B near the ancestral SDR).
-In contrast, the neo-W is not lost in panel D as it is favoured near $r\approx0$ (see blue lines in Figure \ref{fig:positionOverdominance}C and  \ref{fig:positionOverdominance}D near the ancestral SDR).
-Fitness parameters are the same as in Figure \ref{fig:positionOverdominance}; in panels A and B the $a$ allele is favoured in females ($w_{aa}^\female=1.05$, $w_{Aa}^\Hermaphrodite=1$, $w_{AA}^\female=0.85$) while there is overdominance in males ($w_{aa}^\male=w_{AA}^\male=0.75$) and in panels C and D, there is overdominance in both sexes ($w_{aa}^\female=w_{AA}^\female=0.6$, $w_{aa}^\male=0.5$, $w_{AA}^\male=0.7$, $w_{Aa}^\Hermaphrodite=1$).
-These parameters are marked by a dagger in Figure \ref{fig:regionplots}. 
-Here, there is no haploid selection $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
-}
-\label{fig:temporalOverdominance}
-\end{figure}
-
-\begin{figure}[!h]
-\centering
-\centerline{\includegraphics[width=1.5\linewidth]{PositionPlot_SexAntagTighter_MaleDrive}}
-\caption{
-When there is sexually-antagonistic selection and haploid selection, a neo-W may invade for any $R$.
-Panel A shows that the invasion fitness of a neo-W is positive where linkage is tight, even when $r<R$ (unshaded region).
-In panel B, we vary the recombination rate between the neo-W and the selected locus ($R$) for a fixed recombination rate between the ancestral-SDR and the selected locus ($r=0.005$).
-Coloured markers show recombination rates for which the temporal dynamics of neo-W invasion are plotted in panel C (black $R=0.001$, red $R=0.02$, blue $R=0.1$, green $R=0.5$). 
-The diploid selection parameters used in this plot are the same as in Figure \ref{fig:SexAntagTighter}. 
-There is also meiotic drive in males favouring $a$ ($\alpha_{\Delta}^\male=-0.08$), this full set of parameters is marked by an asterisk in Figure \ref{fig:regionMaleDrive}A.
-When $R=0.5$ (green curve), the neo-W does not reach fixation and X,Y,Z, and W alleles are all maintained in the population, see Figure \ref{fig:freqAll}C.
-}
-\label{fig:SexAntagTighterMaleDrive}
-\end{figure}
-
-\begin{figure}[!h]
-\centering
-\centerline{\includegraphics[width=\linewidth]{Region_Plot_combined_MaleDrive}}
-\caption{
-Meiotic drive in males affects whether neo-W-$A$ and neo-W-$a$ haplotypes spread when the ancestral-XY locus is tightly linked to a locus under selection ($r=0$). 
-We vary the fitness of male homozygotes relative to heterozygotes ($w_{Aa}^\Hermaphrodite=1$) and only consider stable equilibria at which both \textbf{A} locus allele are maintained and the $a$ allele is initially fixed on the Y, region outlined.
-In panels A-C, meiotic drive in males favours the $a$ allele ($\alpha_{\Delta}^\male=-0.16$), creating male-biased sex ratios and generally increasing $\lambda_{WA}$ and $\lambda_{Wa}$. 
-By contrast, $\lambda_{WA}$ and $\lambda_{Wa}$ tend to be reduced when meiotic drive in males favours the $A$ allele ($\alpha_{\Delta}^\male=0.16$), panels D-F. 
-We consider three forms of selection in females: directional selection in favour of the $A$ allele (panels A and D, $w_{aa}^\female=0.85$, $w_{AA}^\female=1.05$), direction selection in favour of the $a$ allele (panels B and E, $w_{aa}^\female=1.05$, $w_{AA}^\female=0.85$), and overdominance (panels C and F, $w_{aa}^\female=w_{AA}^\female=0.6$).
-%\textcolor{red}{Panel F mislabelled, should have $\lambda_{Wa}>1$ \& $\lambda_{WA}<1$ as the upper label that has the line.}
-}
-\label{fig:regionMaleDrive}
-\end{figure}
-
-\newpage
-\begin{figure}[!h]
-\centering
-\centerline{\includegraphics[width=\linewidth]{Region_Plot_combined_MaleGS}}
-\caption{
-Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is male gametic competition at a locus that is tightly linked to the ancestral-XY locus.
-Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in Figure \ref{fig:regionMaleDrive}. 
-The $a$ allele is favoured during male gametic competition in Panels A-C ($w_{a}^\male=1.16$, $w_{A}^\male=1$), which creates male biased sex ratios and increases $\lambda_{WA}$ and $\lambda_{Wa}$. 
-On the other hand, the $A$ allele is favoured during male gametic competition in Panels D-F ($w_{a}^\male=1$, $w_{A}^\male=1.16$) and $\lambda_{WA}$ and $\lambda_{Wa}$ tend to be reduced. 
-Compared to the meiotic drive parameters in Figure \ref{fig:regionMaleDrive}, the effect of these male gametic competition parameters on the sex ratio is smaller. 
-For example, in Figure \ref{fig:regionMaleDrive}A-C, the ancestral sex ratio is $\alpha^\male=0.58$ at equilibrium (B) and in panels A-C of this plot, the ancestral sex ratio is $w_{a}^\male/(w_{A}^\male+w_{a}^\male)=0.537$ at equilibrium (B).
-}
-\label{fig:regionMaleGS}
-\end{figure}
-
-\begin{figure}[!h]
-\centering
-\centerline{\includegraphics[width=\linewidth]{Region_Plot_combined_FemaleDrive}}
-\caption{
-Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is female meiotic drive at a locus that is tightly linked to the ancestral-XY locus.
-Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in Figure \ref{fig:regionMaleDrive} and \ref{fig:regionMaleGS}. 
-The $a$ allele is favoured by meiotic drive in females in Panels A-C ($\alpha_{\Delta}^\female=-0.16$), which increases $\lambda_{Wa}$ and decreases $\lambda_{WA}$. 
-Female meiotic drive in favour of the $A$ allele (panels D-F, $\alpha_{\Delta}^\female=-0.16$) has the opposite effect. 
-}
-\label{fig:regionFemaleDrive}
-\end{figure}
-
-\begin{figure}[!h]
-\centering
-\centerline{\includegraphics[width=\linewidth]{Region_Plot_combined_FemaleGS}}
-\caption{
-Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is female gametic competition at a locus that is tightly linked to the ancestral-XY locus.
-Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in Figure \ref{fig:regionMaleDrive}, \ref{fig:regionMaleGS}, and \ref{fig:regionFemaleDrive}. 
-The $a$ allele is favoured during female gametic competition in females in Panels A-C ($w_{a}^\female=1.16$, $w_{A}^\female=1$), which increases $\lambda_{Wa}$ and decreases $\lambda_{WA}$. 
-The $A$ allele is favoured during gametic competition in panels D-F ($w_{a}^\female=1$, $w_{A}^\female=1.16$), giving the opposite effect on $\lambda_{Wa}$ and $\lambda_{WA}$. 
-}
-\label{fig:regionFemaleGS}
-\end{figure}
-
-\begin{landscape}
-\begin{figure}[!h]
-\centering
-\centerline{
-\includegraphics[width=\linewidth]{All_plot_combined_PloidAntag}
-}
-\caption{
-A-D show when each of the neo-W haplotypes invade an internally stable equilibrium with $a$ fixed on the Y (found by setting $r=0$).
-The y-axis shows directional selection in diploids of both sexes, $s^\female=s^\male$, and the x-axes show sex-specific drive, $\alpha_\Delta^\Hermaphrodite$, or haploid competition, $t^\Hermaphrodite$.
-The top left and bottom right quadrants therefore imply ploidally-antagonistic selection (and these are the only places where neo-W haplotypes can invade).
-Dominance is equal in both sexes, $h^\female=h^\male=3/4$. 
-E-F show the temporal dynamics of neo-W frequency in females with parameters given by the asterisks in the corresponding A-D plot, with $r=1/200$, for four different $R$.
-Black $R=1/1000$, Red $R=2/100$, Blue $R=1/10$, Green $R=1/2$.  
-%Dashed line in E-H gives ``fixation" of neo-W (all females heterozygous ZW).
-}
-\label{fig:regionPloidAntag}
-\end{figure}
-\end{landscape}
-
-%\begin{landscape}
-\begin{figure}[!h]
-\centering
-\centerline{
-\includegraphics[width=\linewidth]{Freq_plot_combined_PloidAntag}
-}
-\caption{
-Fixation of neo-W or maintenance of multiple sex-determining systems. 
-The curves show the frequencies of the neo-W (red), ancestral-Y (blue), and $A$ allele (black) among female gametes (solid curves) and among male gametes (dashed curves). 
-In panel A, there is a complete transition from XY sex determination (XX-ZZ females and XY-ZZ males) to ZW sex determination (YY-ZW females and YY-ZZ males).  
-In panels B and C a polymorphism is maintained at both the ancestral XY locus and the neo-ZW locus, such that there are males with genotypes XY-ZZ or YY-ZZ and females with genotypes XX-ZZ, XX-ZW, XY-ZW, or YY-ZW.
-In panel A, selection is ploidally antagonistic with drive in males (parameters as in the green curve in Figure \ref{fig:SexRatioBad}B).
-In panel B, there is overdominance in both sexes and no haploid selection (parameters as in the green curve in Figure \ref{fig:temporalOverdominance}C).
-In panel C, there is sexually-antagonistic selection in diploids with drive in males (parameters as in the green curve in Figure \ref{fig:regionMaleDrive}C).
-%In Panel D there is ploidally-antagonistic selection with haploid competition in males (parameters as in the green curve of Figure \ref{fig:regionPloidAntag}F).
-In all cases, the initial equilibrium frequency has $a$ near fixation on the Y.
-}
-\label{fig:freqAll}
-\end{figure}
-%\end{landscape}
-
-\begin{figure}[!h]
-\centering
-\centerline{
-\includegraphics[width=\linewidth]{neoW_invades_tight_loose}
-}
-\caption{
-An unlinked neo-W can invade a perfectly linked system with overdominance or haploid selection.
-Here overdominance leads to a polymorphic sex-determining system.
-Before invasion the population is at equilibrium B.
-Parameters:
-}
-\label{fig:loose_invades_tight}
-\end{figure}
-
-%\begin{figure}[!h]
-%\centering
-%\centerline{
-%\includegraphics[width=\linewidth]{Sallys_R_plot.pdf}
-%}
-%\caption{
-%\textcolor{blue}{is this the one?}
-%}
-%\label{fig:lambda_R}
-%\end{figure}
-
-%\newpage
-%\textcolor{red}{
-%Add Sally's figure showing lambda for small r near equil A versus near equil B.
-Add references to this figure to appendix where we discuss whether lambdas can be greater than 1 with sexually antagonistic selection.}
-%\textcolor{blue}{not sure which one you are talking about, but see Figure \ref{fig:lambda_R} }
-%\textcolor{red}{Let's remove this for now.}
-
-%\textcolor{red}{
-%Perhaps it would also be useful to add an 8 panel figure that features ploidally antagonistic selection.
-For each type of haploid selection (gametic competition/ meiotic drive in males/females), give a regionplot where $h^\male=h^\female$, e.g., $h^\male=h^\female=0.75$ (or perhaps the value of $h$ we use in the regionplots we have, in which $w_{aa}=0.85$, $w_{Aa}=1$, $w_{AA}=1.05$).
-%Matt made a figure like this before but both Y$a$ and Y$A$ equilibria were plotted and there was no outline showing where the Y$a$ equilibrium is stable (as in Figure \ref{fig:regionplots}).
-In Matts plot the axes were $s^\Hermaphrodite$ and $\alpha_{\Delta}^\Hermaphrodite$.
-%Add an asterisk to each region plot and show invasion in another panel, using those parameters and various $R$ (e.g., in the stye of \ref{fig:temporalOverdominance}). 
-%In an email, Sally has an example of ploidally-antagonistic selection where the neo-W fixes and $R=1/2$. This would cover that case and more. }
-%\textcolor{blue}{made an attempt (Figure \ref{fig:regionPloidAntag})}
-
-%\textcolor{red}{
-%We could also give versions of Figure \ref{fig:regionplots} where there is also haploid selection of various types.
-%Haploid selection can favour $A$ or $a$, so this would involve 4x 6-panel figures.
-Started looking at this in Figure \ref{fig:regionMaleGS} and Figure \ref{fig:regionMaleDrive}, add female haploid selection.
-%Try to integrate into the discussion of haploid selection? e.g., male haploid selection ones generally show effect of sex ratio, increasing both lambdas when female biased (top rows).}
-%\textcolor{blue}{
-%these figures are now done (\ref{fig:regionMaleDrive}-\ref{fig:regionFemaleGS}) (ensuring frequencies between 0 and 1), but yet to discuss in text.}
-
-%\textcolor{red}{
-%Perhaps, for one set of parameters, we should plot the dynamics of all the different alleles.
-E.g., we could use the same parameters used in \ref{fig:SexRatioBad}.
-The main purpose would be to show what happens to the ancestral SDR during turnover.
-%We could also show an example where XY and ZW sex determining systems are both polymorphic and stable (e.g., using one of the curves in Figure \ref{fig:temporalOverdominance} and the green curve in Figure \ref{fig:SexAntagTighterMaleDrive}).
-%I think there are also examples with looser sex linkage and pollen competition that lead to a mixed sex-determination system.
-We should probably have a short section in the appendix discussing this.
-}
-%\textcolor{blue}{made an attempt with Figure \ref{fig:freqAll}, but yet to discuss in text}
-
 \end{document}

### 2018-01-18 LaTeX/S2_Appendix.tex
moved to plos template, appendices have references that are still messed up

--- 2018-01-17 LaTeX/Turnover.tex
@@
 
+\usepackage{hyperref}
+
 \usepackage[flushleft]{threeparttable}
@@
 
+%external document referencing
+\usepackage{xr}
+
 \begin{document}
 
-\title{Haploid Selection, Sex Ratio Bias, and Transitions Between Sex-Determination Systems}
-\author{Michael F Scott$*^1$, Matthew M Osmond$*^2$, and Sarah P Otto$^2$}
-\date{}
-\maketitle
-\noindent
-$*$ These authors contributed equally to this work
-
-\noindent
-$^1$ Department of Botany, University of British Columbia, \#3529 - 6270 University Boulevard, Vancouver, BC, Canada V6T 1Z4
-
-\noindent
-$^2$ Department of Zoology, University of British Columbia, \#4200 - 6270 University Boulevard, Vancouver, BC, Canada V6T 1Z4
-
-\noindent
-email: mfscott@biodiversity.ubc.ca, mmosmond@zoology.ubc.ca
-
-\noindent
-Contributions:
-
-\newpage
-\linenumbers
-\modulolinenumbers[2]
-
-\begin{abstract}
-Sex-determination systems are remarkably dynamic; many taxa display shifts in the location of sex-determining loci or the evolution of entirely new sex-determining systems. 
-Predominant theories for why we observe such transitions %in which new sex-determining systems spread by selection 
-%involve sex ratio selection or sex-specific selection (e.g., sexually antagonistic selection).
-%These studies 
-generally conclude that novel sex-determining systems are favoured by selection if they equalise the sex ratio or increase linkage with a sexually-antagonistic locus. 
-We use population genetic models to extend these theories in two ways: 
-(1) We explicitly consider selection on loci very tightly linked to the ancestral sex-determining loci, e.g., within the non-recombining region of the ancestral sex chromosomes. 
-%(1) We explicitly consider how selection on very tightly sex-linked loci influences the spread of novel sex-determiners. 
-Variation at such loci can favour the spread of new sex-determination systems in which the heterogametic sex changes (XY to ZW or ZW to XY) and the new sex-determining region is less closely linked (or unlinked) to the locus under selection, which is not predicted by previous theory.
-%With tight linkage, selection can maintain equilibria at which the allele fixed on the sex-limited chromosome (Y or W) is simultaneously favoured in the homogametic sex (XX females or ZZ males) such that heterogametic transitions (XY to ZW or ZW to XY) are favoured by selection.
-%Alternatively, a neo-W (neo-Y) locus can invade when it allows greater specialism on alleles beneficial in females (male) compared to an ancestral XX female (ZZ male), 
-(2) We also consider selection upon haploid genotypes either during gametic competition (e.g., pollen/sperm competition) or meiosis (i.e., non-Mendelian segregation); selective processes that typically occur in one sex or the other.
-%As well as having sex-specific fitness consequences, haploid selection can cause the zygotic sex ratio to become biased because sex ratios are determined by the production and fertilization success of X- versus Y-bearing pollen/sperm (or Z- versus W-bearing ovules/eggs).
-%Consequently, selection for XY to ZW transitions and ZW to XY transitions can be assymetrical when linkage between the ancestral sex-determining locus and a locus under haploid selection is tight, in which case ancestral sex ratio biases can be strong.
-%In addition, when linkage between the ancestral sex-determining locus and a locus under haploid selection is tight, sex ratio biases can be strong such that there is an asymmetry between invasion of ancestrally XY and ancestrally ZW systems because, e.g., haploid selection in males only causes biased zygotic sex ratios in an ancestrally XY system.
-We find that associations with haploid selected loci can drive transitions between sex determination systems, without requiring sexually-antagonistic selection in diploids. 
-Unexpectedly, with haploid selection, transitions between male and female heterogamety can also evolve where linkage with the sex-determining locus is weakened. 
-Furthermore, haploid selection in the heterogametic sex can cause sex ratio biases, which may increase or decrease with the spread of new sex chromosomes. 
-Thus, we find that transitions between sex-determination systems cannot be simply predicted by selection to equalise the sex ratio. 
-%These results indicate that loci experiencing haploid selection can favour the evolution of new sex-determination systems. 
-%These results indicate that favourable associations that develop between the ancestral sex-determining locus and selected loci can be broken during the spread of a new sex-determining region. 
-%Such transitions are not possible with diploid selection alone, in which case tighter linkage increases the fitness of both males and females. 
-%Notably, we find that the spread of new genetic sex-determination systems is not affected by sex ratio biases that are caused by haploid selection. 
-%A surprising result given that other determinants of sex allocation typically experience strong Fisherian sex ratio selection to equalize sex ratios. 
-%Overall, we demonstrate when and how the evolution of sex determining systems is impacted by sex ratio biases resulting from haploid selection and we show that new sex-determining regions can be favoured even if they are not closely linked with a locus under selection.
-Overall, our models reveal that transitions between sex-determination systems, particularly transitions where the heterogametic sex changes, can be driven by loci in previously unpredicted genomic locations that experience selection during diploid and/or haploid phases.
-These results predict conditions under which sex-determination systems are likely to be labile and draw novel connections with sex ratio evolution
-%These results might be reflected in the lability with which sex-determination systems evolve. %and for the factors determining the phylogenetic pattern of sex-determination systems. 
-\end{abstract}
-
-%abstract word count: $\approx$ 350
-
-\newpage
-
-\section*{Introduction}
-
-%CHECK THROUGHOUT: use of sex-determination SYSTEMS versus MECHANISMS. 
-%CHECK THROUGHOUT: use of haploid selection, gametic selection, and meiotic drive.
-
-Animals and angiosperms exhibit extremely diverse sex-determination systems \citep[reviewed in][]{Bull:1983vi,Charlesworth:2010it,Beukeboom:2014vb,Bachtrog:2014bx}. 
-Among species with genetic sex determination of diploid sexes (GSD), some taxa have heterogametic males (XY) and homogametic females (XX), including %non-monotreme?
-I think monotremes have XY but tonnes of translocations, giving: X1,X2...X6 Y1
-mammals and most dioecious plants \citep{Ming:2011iy}; whereas other taxa have homogametic males (ZZ) and heterogametic females (ZW), including Lepidoptera and birds. 
-Within several taxa, the chromosome that harbours the master sex-determining region changes. 
-For example, transitions of the master sex-determining gene between chromosomes or the evolution of new master sex-determining genes have occurred in Salmonids \citep{Li:2011fm,Yano:2012di}, Diptera \citep{Vicoso:2015hf}, and \textit{Oryzias} \citep{Myosho:2012fv}.
-%Presentation at evolution found neo sex chromosome in birds, doesn't seem to be published or bioRxiv yet (consider pers com.), title: A previously unknown neo-sex chromosome mediates plumage divergence and speciation in hybridizing birds Jason Sardell; Elizabeth Cooper; J.
-Albert C.
-Uy.
-I wonder if this is actually a fusion event though?
-In addition, many clades exhibit transitions between male (XY) and female (ZW) heterogamety, including snakes \citep{Gamble2017}, lizards \citep{Ezaz:2009tk}, eight of 26 teleost fish families \citep{Mank:2006bt}, true fruit flies \citep[Tephritids,][]{Vicoso:2015hf}, amphibians \citep{Hillis:1990gu}, the angiosperm genus \textit{Silene} \citep{Slancarova:2013dq}, the angiosperm family \textit{Salicaceae} \citep{Pucholt2015,Pucholt2017} and Coleoptera and Hemiptera \citep[][plate 2]{Beukeboom:2014vb}.
-Indeed, in some cases, both male and female heterogametic sex-determination systems can be found in the same species, as reported in houseflies \citep{Macdonald1978}, midges \citep{Thompson1971}, frogs \citep{Ogata:2007jm}, cichlid fish \citep{Ser:2010iq}, tilapia \citep{Lee2004}, sea bass \citep{Vandeputte2007}, and lab-strains of Zebrafish \citep{Liew2012,Wilson2014}.
-In addition, multiple transitions have occurred between genetic (GSD) and environmental sex-determination (ESD) systems, e.g., in reptiles and fishes \citep{Conover:1987in,Mank:2006bt,Pokorna:2009ui,Ezaz:2009tk,Pen:2010kk,Holleley:2015hc}.
-
-%NOTE: ``Bull & Charnov (1977) hypothesized that a new sex-determining gene can rapidly increase and become fixedin a population if it is linked to a gene with high adaptivevalue, and finally cause a change of the heterogametic sex.'' The Bull and Charnov paper is also the one in which the set of neutral equilibria between XY and ZW are identified (where sex ratios are equal)
-%NOTE: Vuilleumier et al. 2007 also find polymorphic sex determination can be stable.
-
-%For example, closely related species in the Medaka lineage (cite Takenhana et al. 2008) and Tilapiinae (cite Lee et al 2004, Cnaani et al 2008), citations in Beukeboom.
-
-%\textcolor{red}{Brief description of sex ratio adjustment and sexual antagonism theories:}
-
-Predominant theories accounting for the spread of new sex-determination systems by selection involve fitness differences between sexes (e.g., sexually antagonistic selection) or sex ratio selection \citep{Blaser2012, Beukeboom:2014vb,vanDoorn2014re}.
-%\citet{Bull:1977wt} shows that direct selection on new sex determination loci can allow them to spread and switch between male and female heterogamety. 
-\citet{vanDoorn:2007eu,vanDoorn:2010hu} and \citet{Muralidhar2018} have shown that new sex-determining loci can be favoured if they arise in close linkage with a locus that experiences sexual antagonism.
-Tighter linkage allows a stronger favourable association to build up between a male-beneficial allele, and a neo-Y chromosome, for example. 
-Such associations can favour a new partially-masculinizing or partially-feminizing allele \citep{Muralidhar2018}, a new master sex-determining gene \citep{vanDoorn:2007eu}, and transitions between male and female heterogamety \citep[trans-GSD transitions, ZW to XY or XY to ZW,][]{vanDoorn:2010hu}.
-However, any sexually-antagonistic loci that are more closely linked to the ancestral sex-determination locus will develop similar, favourable associations and are expected to hinder the spread of a new sex-determination system.
-%Here we extend these studies by explicitly calculating the the equilibrium allele frequencies of loci that are very tightly linked to the ancestral sex-determining region.
-
-The sex ratio is directly determined by the sex-determination system, and it has therefore been suggested that sex ratio selection is a dominant force in the evolution of sex determination (e.g., \citealt{Bull:1983vi}, p 66-67; \citealt{Beukeboom:2014vb}, Chapter 7).
-`Fisherian' sex ratio selection favours a 1:1 zygotic sex ratio when assuming that males and females are equally costly to produce \citep{Fisher:1930wy,Charnov:1982wg}.
-This follows from the fact that, for an autosomal locus, half of the genetic material is inherited from a male and half from a female \citep{West:2009we}. 
-Thus, if the population sex ratio is biased towards one sex, the average per-individual contribution of genetic material to the next generation from the opposite sex is greater. 
-Therefore, a mutant that increases investment in the rarer sex will spread via the higher per-individual contributions made by that sex. 
-%The default mode of sex ratio selection is `Fisherian' sex ratio selection, which favours equal investment in male and female offspring \citep[i.e., a 1:1 zygotic sex ratio when assuming that males and females are equally costly to produce,][]{Fisher:1930wy,Charnov:1982wg}.
-%Given that the sex-determination system can directly affect the sex ratio, we might expect Fisherian sex ratio selection to influence the spread of new sex-determination systems. 
-In the case of sex-chromosome evolution, \citet{Kozielska:2010vm} consider systems in which the ancestral sex chromosomes experience meiotic drive (e.g., where driving X or Y chromosomes are inherited disproportionately often), which causes sex ratios to become biased \citep{Hamilton:1967ts}.
-They find that new, unlinked sex-determining loci (masculinizing or feminizing mutations, i.e., neo-Y or neo-W loci) can then spread, which restore an even sex ratio.
-
-%\textcolor{red}{We add haploid selection:}
-Here we use mathematical models to find the conditions under which new sex-determination systems spread when individuals experience selection at both diploid and haploid stages. 
-Even in animal and plant species that have much larger and more conspicuous diploid phases than haploid phases, many loci experience significant haploid selection through gamete competition and/or meiotic drive \citep{Mulcahy:1996ha,JOSEPH:2004haa}.
-We use the term `meiotic drive' to refer to the biased (non-Mendelian) segregation of genotypes during gamete production (from one parent) and the term `gametic competition' to refer to selection upon haploid genotypes within a gamete/gametophyte pool (potentially from multiple parents); the term `haploid selection' encompasses both processes.
-
-% from Bai et al.
-(2016) ``[Segregation distortion] phenomenon is commonly detected via genetic mapping and has been documented in various species, including mouse (Eversley et al., 2010; Casellas et al., 2012), Drosophila (Phadnis and Orr, 2009; Larracuente and Presgraves, 2012; McDermott and Noor, 2012), Tigriopus (Pritchard et al., 2011), rice (Koide et al., 2012; Reflinur et al., 2014; Xu et al., 2014), maize (Tang et al., 2013), and cotton (Yu et al., 2011; Hulse-Kemp et al., 2015).'' Also more in that paper that might be useful.
-%Drosophila http://www.biorxiv.org/content/early/2017/02/06/106336
-Segregation distortion provides putative evidence of haploid selection and can sometimes be attributed to meiotic drive and/or gametic competition \citep{Lalanne2004,Fishman2005,Leppala2008,Leppala2013,Didion2015,Didion2016}.
-Where it has been characterized, meiotic drive generally occurs either during the production of male or female gametes only \citep{Ubeda:2005gw,Lindholm:2016cw}.
-Gametic competition is also typically sex specific, occurring primarily among male gametes, because there are typically many more pollen/sperm than required for fertilization.
-Gametic competition may be particularly common in plants, in which 60-70\% of all genes are expressed in the male gametophyte, and these genes exhibit stronger signatures of selection than random genes \citep{Borg:2009jpa,Arunkumar:2013iq,Gossmann:2014dua}.
-In addition, artificial selection pressures applied to male gametophytes are known to cause a response to selection \citep[e.g.,][]{Hormaza:1996cv,Ravikumar:2003uo,Hedhly:2004iv,Clarke:2004ir}. 
-A smaller proportion of genes are thought to be expressed and selected during competition in animal sperm, although precise estimates are uncertain \citep{Zheng:2001fi,JOSEPH:2004haa,Vibranovski:2010et}.
-Nevertheless, recent studies have demonstrated that sperm competition in animals can alter haploid allele frequencies and increase offspring fitness \citep{Immler:2014im,Alavioon2017}.
-
-There are various ways by which genes experiencing haploid selection could influence transitions between sex-determination systems. 
-If we assume that haploid selection at any particular locus predominantly occurs in one sex (e.g., meiotic drive during spermatogenesis), then such loci experience a form of sex-specific selection. 
-In this respect, we might expect that haploid selection would affect transitions between sex-determination systems in a similar manner to sex-specific diploid selection \citep[as explored by][]{vanDoorn:2007eu,vanDoorn:2010hu}.
-That is, new masculinizing mutations (neo-Y chromosomes) could be favoured via associations with alleles that are beneficial in the male haploid stage. 
-On the other hand, sex ratios can also become biased by linkage between the sex-determining region and a locus that harbours genetic variation in haploid fitness. 
-For example, there are several known cases of sex ratio bias caused by sex-linked meiotic drive alleles \citep[][Chapter 3]{Burt:2006} or selection among X- and Y-bearing pollen \citep{Lloyd:1974tz,Conn:1981uw,Stehlik:2005ul,Stehlik:2006to,Field:2012fd,Field:2013cc}.
-It is not immediately clear how the spread of new sex-determination systems would be influenced by the combination of sex ratio biases and associations between haploid selected loci and sex-determining regions.
-
-%Perhaps longer discussion of tight sex-linkage here? e.g., mention that r=0 is a particularly significant case for sex chromosomes.
-
-We find that the spread of novel sex-determiners is influenced by both Fisherian sex ratio selection and by selection on genetically-associated alleles. 
-%We find that sex ratio biases caused by haploid selection can exert Fisherian sex ratio selection upon novel sex-determiners but that their spread is also determined by selection on genetically-associated alleles.
-%Indeed, it is only when haploid-selected loci are tightly linked to the ancestral sex-determining region (and so sex ratio biases are initially large) that we see an asymmetry between selection for XY to ZW transitions and ZW to XY transitions (e.g., because haploid selection in males only causes biased zygotic sex ratios in an ancestrally XY system).
-Surprisingly, Fisherian sex ratio selection does not dominate; it is possible for selection on linked alleles to drive turnover between sex-determining systems despite causing increasingly biased sex ratios.
-In addition to considering haploid selection, another novel development in our model is that we consider loci that are in very tight linkage with the ancestral sex-determining region. 
-Because sex-determining loci are often found within a region of suppressed recombination, there can be a significant number of tightly linked loci. 
-We find that loci linked with the ancestral sex-determining region can drive transitions in which the heterogametic sex changes, even when the neo-sex-determining locus is less closely linked to loci under selection (either including haploid selection or not).
-%Such transitions are not favoured in models lacking tight linkage and/or haploid selection. 
-%Secondly, we allow sex-specific haploid selection to occur on a locus in tight or loose linkage with the ancestral sex-determining region. 
-%In addition, when linkage between the ancestral sex-determining locus and a locus under haploid selection is tight, sex ratio biases can be strong such that there is an asymmetry between invasion of ancestrally XY and ancestrally ZW systems because, e.g., haploid selection in males only causes biased zygotic sex ratios in an ancestrally XY system.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Model}
-%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Model Outline
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-\centerline{\includegraphics[width=\linewidth]{Sex_determination_outline.pdf}}
-\caption{
-Outline of model features. 
-Panel A: Recombination rate parameters between the ancestral-sex-determining locus (here, assumed to have X or Y alleles), a locus under selection (\textbf{A}, with alleles $A$ and $a$), and a neo-sex-determining locus (\textbf{M}, with alleles $M$ and $m$).
-If $r<1/2$, then associations between ancestral-sex-determining alleles (X and Y) and \textbf{A} locus alleles can be maintained past recombination in males.
-Panel B: Haploid selection is often sex-specific, occurring during haploid production or competition in either males or females. 
-For example, haploid selection in males only is represented by the dashed circle.  
-If X or Y alleles remain associated with alleles that experience haploid selection in males ($r<1/2$), then zygotic sex ratios can become biased because either X or Y male gametes/gametophytes will be abundant after haploid selection.
-However, the zygotic sex ratio is not biased by male haploid selection in ZW sex-determination systems. 
-Similarly, zygotic sex ratio biases can occur if haploid selected alleles are associated with neo-sex-determining alleles ($M$ and $m$, i.e., if $R<1/2$). 
-Panel C: During cis-GSD transitions (XY to XY or ZW to ZW, without loss of generality we assume ancestral XY sex determination here), a neo-Y allele spreads to pseudo-fixation (its maximum frequency among male gametes) and the the ancestral-Y allele is lost.
-Panel D: During trans-GSD transitions (XY to ZW or ZW to XY), a neo-W allele spreads to pseudo-fixation (its maximum frequency among female gametes) and the ancestral-X allele is lost.
-Neo-W mutations allow Y-associated alleles into females, which may impede or aid their spread.
-}
-\label{fig:model_outline}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\textcolor{red}{Change all  $\alpha^\Hermaphrodite$ to $(1+\alpha_{\Delta}^\Hermaphrodite)$.}
-%\textcolor{blue}{I've attempted this everywhere except in the recursions (S.1), which seem more natural with $\alpha$'s.
-I've run into trouble in equation S.8c,d -- I think we should check the Mathematica results to be sure we haven't made a typo.
-This also introduced an extra 1/2 in S.6c,d that might need to be explained.}
-%\textcolor{red}{hmm, not sure.
-This was an idea from Sally, I think in response to terms like $2 \alpha^\Hermaphrodite$ and $2(1-\alpha^\Hermaphrodite)$.
-It's possible that it makes other equations less easy to understand.
-My previous (not explained) logic was to use $w$ and $\alpha$ for strong selection and $s$, $t$, and $\alpha_\Delta$ for weak selection.
-Just to check, I should have written $\alpha^\Hermaphrodite=(1+\alpha_{\Delta}^\Hermaphrodite)/2$, maybe that's where the factors of $1/2$ come from?}
-%\textcolor{blue}{shoot, i may have changed too much (i.e.
-strong selection too), but i did use the correct transformation.
-still, the form of S.8c,d seems wrong.
-I'll double check it.
-CANT FIND ANY ERRORS YET STILL HAVE A "2" IN S.8c.
-These 2s reappear in S.9 and S.10, always with $W_{AA}$.}
-
-%\textcolor{red}{Switch between $\rho$ and $\rho$ in all places because $\rho$ is used for double recombination events.}
-%\textcolor{blue}{I think we need a different variable given the $\rho$ terms in the characteristic polynomial.
-Also, where is $\rho$ used for double recombination?
-In other papers?
-Here $\rho$ is the probability of an odd number of cross-overs between the SDR and M loci.}
-%\textcolor{red}{Good point, not sure what's best for \textbf{the-term-formerly-known-as-$\rho$}.
-Yeah, Sally's written comment was something like ``$\rho$ is semi-standard notation for double recombination so it's use as a recombination rate might be confusing''.}
-
-%\textcolor{red}{Change $\zeta$ to represent zygotic sex ratio of males, consistent with $q$ and figures.}
-
-%genetic system
-We consider transitions between ancestral and novel sex-determining systems using a three-locus model, each locus having two alleles. 
-Locus \textbf{X} is the ancestral sex-determining region, with alleles $X$ and $Y$ (or $Z$ and $W$).
-Locus \textbf{A} is a locus under selection, with alleles $A$ and $a$.
-Locus \textbf{M} is a novel sex-determining region, at which the null allele ($M$) is initially fixed in the population such that sex of zygotes is determined by the genotype at the ancestral sex-determining region, \textbf{X}; $XX$ genotypes become females and $XY$ become males (or $ZW$ become females and $ZZ$ become males).
-To evaluate the evolution of new sex-determination systems, we consider the invasion, fixation, maintenance, and/or loss of novel sex-determining alleles ($m$) at the \textbf{M} locus. 
-%We only do invasion analytically though (is this sentence still ok?)
-We assume that the \textbf{M} locus is epistatically dominant over the \textbf{X} locus such that zygotes with at least one $m$ allele develop as females with probability $k$ and as males with probability $1-k$, regardless of the \textbf{X} locus genotype.
-With $k=0$, the $m$ allele is a masculinizer (i.e., a neo-Y) and with $k=1$ the $m$ allele is a feminizer (i.e., a neo-W).
-With intermediate $k$, we can interpret $m$ as an environmental sex determination (ESD) allele, such that zygotes develop as females in a proportion ($k$) of the environments they experience. 
-%We also analyze a model of maternally-controlled environmental sex-determination, where mothers with at least one $m$ allele produce daughters with probability $k$.
-
-%life-cycle
-In each generation, we census the genotype frequencies in male and female gametes/gametophytes (hereafter gametes) before gametic competition. 
-A full description of our model, including recursion equations, is given in the Appendix. 
-First, competition occurs among male gametes (sperm/pollen competition) and among female gametes (egg/ovule competition) separately. 
-Selection during gametic competition depends on the \textbf{A} locus genotype, relative fitnesses are given by $w_A^\Hermaphrodite$ and $w_a^\Hermaphrodite$ ($\Hermaphrodite \in \{\female,\male\}$; see table \ref{tab:fitnesstable}).
-%$w_{A}^\male$ and $w_{a}^\male$ for male gametes and $w_{A}^\female$ and $w_{a}^\female$ for female gametes, see table \ref{tab:fitnesstable}.
-We assume that all gametes compete for fertilization during gametic competition, which assumes a polygamous mating system. 
-Gametic competition in monogamous mating systems is, however, equivalent to meiotic drive in our model (described below), as either only alters the frequency of gametes produced by heterozygotes. 
-After gametic competition, random mating occurs between male and female gametes.
-The resulting zygotes develop as males or females, depending on their genotypes at the \textbf{X} and \textbf{M} loci. %(and the \textbf{M} genotype of their mother in the case of maternal control).
-Diploid males and females then experience selection, with relative fitnesses $w_{AA}^{\Hermaphrodite}$, $w_{Aa}^{\Hermaphrodite}$, and $w_{aa}^{\Hermaphrodite}$.
-%where $g$ is the diploid genotype at the \textbf{A} locus ($g \in \{AA, Aa, aa\}$).
-%Diploids compete with others of the same sex, where selection depends on the sex of the individual and its genotype at the \textbf{A} locus.
-The next generation of gametes is produced by meiosis, during which recombination and sex-specific meiotic drive can occur. 
-Recombination (i.e., an odd number of cross-overs) occurs between loci \textbf{X} and \textbf{A} with probability $r$, between loci \textbf{A} and \textbf{M} with probability $R$, and between loci \textbf{X} and \textbf{M} with probability $\rho$.
-Any linear order of the loci can be modelled with appropriate choices of $r$, $R$, and $\rho$ (see Figure \ref{fig:model_outline}A and Table \ref{tab:chisubstitutions}). 
-Individuals that are heterozygous at the \textbf{A} locus may experience meiotic drive; a gamete produced by $Aa$ heterozgotes of sex $\Hermaphrodite$ bears allele $A$ with probability $\alpha^\Hermaphrodite$.
-Thus, the \textbf{A} locus can experience sex-specific gametic competition, diploid selection, and/or meiotic drive.
-
-\begin{table}[ht]
-\centering
-\smallskip
-\caption{Relative fitness of different genotypes in sex $\Hermaphrodite \in \{\female,\male\}$}
-\begin{tabular}{l c }
-\hline\hline
-  Genotype & Relative fitness during gametic competition \\ [0.5ex] \hline
-  A & $w_{A}^\Hermaphrodite = 1+t^\Hermaphrodite$ \\
-  a & $w_{a}^\Hermaphrodite = 1$ \\ [0.5ex] \hline
-  Genotype & Relative fitness during diploid selection \\ [0.5ex] \hline
-  AA & $w_{AA}^\Hermaphrodite = 1+ s^\Hermaphrodite$ \\
-  Aa & $w_{Aa}^\Hermaphrodite = 1+h^\Hermaphrodite s^\Hermaphrodite$ \\
-  aa & $w_{aa}^\Hermaphrodite = 1$ \\ [0.5ex] \hline
-  Genotype & Transmission during meiosis in $Aa$ heterozygotes \\ [0.5ex] \hline
-  A & $\alpha^\Hermaphrodite=1/2+\alpha_{\Delta}^{\Hermaphrodite}/2$ \\
-  a & $1-\alpha^\Hermaphrodite=1/2-\alpha_{\Delta}^{\Hermaphrodite}/2$ \\
-  \hline \hline
-  \label{tab:fitnesstable}
- \end{tabular}
-\end{table}
-
-%Info moved above
-%what were going to do, briefly
-%With allele $M$ fixed at the \textbf{M} locus, sex is determined by locus \textbf{X} and an equilibrium is reached at locus \textbf{A}.
-%where, importantly, locus \textbf{A} can be stably polymorphic.
-%the dynamics can be described by the frequency of $A$ in gametes/gametophytes from the homogametic sex and the frequencies of $A$ in the two types of gametes/gametophytes from the heterogametic sex.
-%We then examine the ability of a rare, novel sex-determiner, $m$, to increase in frequency from this equilibrium.
-%Numerical simulations are used to examine when an invading mutation goes to fixation.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Results}
-%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The model outlined above describes both ancestrally-XY and ancestrally-ZW sex-determination systems if we relabel the two sexes as being ancestrally `heterogametic' or ancestrally `homogametic'. 
-Without loss of generality, we primarily refer to the ancestrally heterogametic sex as male and the ancestrally homogametic sex as female.
-That is, we describe an ancestral XY sex-determination system but our model is equally applicable to an ancestral ZW sex-determination system (relabelling the ancestrally-heterogametic sex as female and the ancestrally-homogametic sex as male and switching the labels of males and females throughout).
-
-%\subsection*{Turnover between sex-determination systems}
-
-\subsubsection*{Generic invasion by a neo-Y or neo-W}
-
-The evolution of a new sex-determination system requires that a rare mutant allele at the novel sex-determining locus, $m$, increases in frequency when rare. 
-The spread of a rare mutant $m$ at the \textbf{M} locus is determined by the leading eigenvalue, $\lambda$, of the system of eight equations describing the frequency of eggs and sperm carrying the $m$ allele in the next generation (equations \ref{eq:recursions}).
-%, evaluated at the above equilibrium.
-%Thus, the system describing the change in frequency of the $m$ allele consists of eight recursion equations. 
-This system simplifies substantially in a number of cases of interest. 
-Dominant neo-Y (when $k=0$) or neo-W alleles (when $k=1$) are only found in male diploids (neo-Y) or female diploids (neo-W) such that their growth rate ultimately depends only on the change in frequency of $m$-bearing gametes produced by males or by females, respectively.
-Furthermore, if the $m$ allele is fully epistatically dominant over the ancestral sex-determining system, phenotypes are not affected by the genotype at the ancestral sex-determining region (\textbf{X} locus).
-Thus, the invasion of rare dominant neo-Y or neo-W alleles is determined by the largest eigenvalue that solves the quadratic, $\lambda^2+ b \lambda + c =0$ \textcolor{blue}{(see Appendix for a discussion of other roots - or Sally's proof!)}.
-Here, $b= - (\lambda_{mA} + \lambda_{ma})+(\chi_{mA} + \chi_{ma})$ and $c = (\lambda_{mA}-\chi_{mA}) (\lambda_{ma}-\chi_{ma}) -\chi_{mA} \chi_{ma}$, where $\lambda_{mi}$ is the multiplicative growth rate (which we will call the ``haplotypic growth rate'') of the neo-sex determination allele $m$ on background $i$ without accounting for loss due to recombination, and $\chi_{mi}$ is the rate at which mutant haplotypes on background $i\in\{A,a\}$ recombine onto the other \textbf{A} locus background in heterozygotes (see Table \ref{tab:haplotype_growth}).
-The $\lambda_{mi}$ and $\chi_{mi}$, and thus the spread of the mutant $m$ allele, depend on the frequency of alleles at the \textbf{A} and \textbf{X} loci in the ancestral population. 
-In the ancestral population, it is convenient to follow the frequency of the $A$ allele among female gametes (eggs), $p^\female_X$, and among X-bearing, $p^\male_X$, and among Y-bearing, $p^\male_Y$, male gametes (sperm/pollen).
-We also track the fraction of male gametes that are Y-bearing, $q$, which may deviate from $1/2$ due to meiotic drive in males. 
-We will consider only equilibrium frequencies of alleles, $\hat{p}^\Hermaphrodite_i$, and Y-bearing male gametes, $\hat{q}$, when calculating the eigenvalues.
-
-%\textcolor{red}{I now remove the zygotic sex ratio $\zeta$ from the mean fitnesses. The mean fitnesses will have to be adjusted in a corresponding way.}
-%
-%\textcolor{red}{CHECK: DO THE HAPLOID MEAN FITNESSES HAVE TO BE IN THE DENOMINATOR? i think so, based on definitions in table S.2 (mmo)}
-
-% as there are now two 2s in the lambdas of table 2. perhaps the 2 in the denominator is needed because the frequency of males sums to one as does the frequency of females?}
-
-\begin{threeparttable}[ht]
-\centering
-\smallskip
-%\caption{Parameters determining invasion (equation \ref{eq:charpoly_neoY}) for neo-Y or neo-W alleles}
-\caption{Parameters determining invasion of mutant neo-Y and neo-W alleles into an ancestrally XY system}
-\begin{tabular}{l}
-\hline\hline
-   \noalign{\vskip 0.5ex}
-   $m$ is a neo-Y ($k=0$) \\ [0.5ex] \hline \noalign{\vskip 1ex}
-  $\lambda_{YA} = \left( 2 \zeta \right)^{-1} \left[\hat{p}_X^\female w_{A}^{\female} w_{A}^{\male} w_{AA}^{\male} + (1-\hat{p}_X^\female) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} (1+\alpha_{\Delta}^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right) $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\lambda_{Ya} = \left( 2 \zeta \right)^{-1} \left[(1-\hat{p}_X^\female) w_{a}^{\female} w_{a}^{\male} w_{aa}^{\male} + \hat{p}_X^\female w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male}(1 - \alpha_{\Delta}^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\chi_{YA} = R \left( 2 \zeta \right)^{-1} \left[ (1-\hat{p}_X^\female) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} (1+\alpha_{\Delta}^{\male}) \right]/  \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right)   $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\chi_{Ya} = R \left( 2 \zeta \right)^{-1} \left[   \hat{p}_X^\female w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male} (1 - \alpha_\Delta^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right)  $\\ [1ex] \hline
-  \noalign{\vskip 0.5ex}
-  $m$ is a neo-W ($k=1$) \\ [0.5ex] \hline \noalign{\vskip 1ex}
-  $\lambda_{WA} = \left[ 2 (1 - \zeta) \right]^{-1} \left[ \bar{p}^{\male} w_{A}^{\male} w_{A}^{\female} w_{AA}^{\female}+(1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female}(1+\alpha_{\Delta}^{\female})\right]/ \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\lambda_{Wa} = \left[ 2 (1 - \zeta) \right]^{-1} \left[ (1-\bar{p}^{\male}) w_{a}^{\male} w_{a}^{\female} w_{aa}^{\female}+\bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female}(1-\alpha_{\Delta}^{\female})\right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\chi_{WA} = R \left[ 2 (1 - \zeta) \right]^{-1} \left[ (1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female} (1+\alpha_{\Delta}^{\female}) \right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \right)  $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\chi_{Wa} = R \left[ 2 (1 - \zeta) \right]^{-1} \left[ \bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female} (1-\alpha_{\Delta}^{\female}) \right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \right) $\\ [1ex]
-  \hline \hline 
-   \end{tabular}
-      \begin{tablenotes}
-      \scriptsize
-      \item $\bar{p}^{\male}=(1-\hat{q})\hat{p}_X^\male + \hat{q}\hat{p}_Y^\male$ is the average frequency of the $A$ allele among X- and Y-bearing male gametes.
-%      \item $R$ is the probability of recombination between loci \textbf{A} and \textbf{M}.
-      \item $\zeta$ is the zygotic sex ratio (fraction male)
-      \item $\bar{w}^\Hermaphrodite$ is the mean fitness of diploids of sex $\Hermaphrodite$, see Table \ref{tab:meanfitnesses}
-      \item $\bar{w}_H^\Hermaphrodite$ is the mean fitness of haploids from sex $\Hermaphrodite$, see Table \ref{tab:meanfitnesses}
-%      \item $\bar{w}_H^\female = p_X^\female w_A^\female + (1-p_X^\female) w_a^\female$ is the mean fitness of female gametes during gametic competition
-%      \item $\bar{w}_H^\male = \bar{p}^{\male} w_A^\male + (1-\bar{p}^{\male}) w_a^\male$ is the mean fitness of male gametes during gametic competition
-%       \item $\bar{w}^\female = \{ p_X^\female w_A^\female (1-q) p_X^\male w_A^\male w_{AA}^\female + (1 - p_X^\female) w_a^\female (1-q) p_X^\male w_A^\male w_{Aa}^\female + p_X^\female w_A^\female (1-q) (1 - p_X^\male) w_a^\male w_{Aa}^\female + (1-p_X^\female) w_a^\female (1-q) (1 - p_X^\male) w_a^\male w_{aa}^\female \} / \{ \bar{w}_H^\female \bar{w}_H^\male\}$ is the mean fitness of females during diploid competition
-%       \item $\bar{w}^\male = \{ p_X^\female w_A^\female q p_Y^\male w_A^\male w_{AA}^\male + (1 - p_X^\female) w_a^\female q p_Y^\male w_A^\male w_{Aa}^\male + p_X^\female w_A^\female q (1 - p_Y^\male) w_a^\male w_{Aa}^\male + (1-p_X^\female) w_a^\female q (1 - p_Y^\male) w_a^\male w_{aa}^\male \} / \{ \bar{w}_H^\male \bar{w}_H^\male\}$ is the mean fitness of males during diploid competition
-    \end{tablenotes}
-  \label{tab:haplotype_growth}
-\end{threeparttable}
-\\
-
-%We are particularly concerned with the conditions under which a rare neo-sex-determining allele increases in frequency, which occurs when the largest eigenvalue, $\lambda$, is greater than one. 
-%If one or both of $\lambda_{mA}$ and $\lambda_{ma}$ are greater than one, indicating that at least one haplotype increases in frequency faster than recombination breaks it apart, invasion will always occur ($\lambda>1$).
-%Otherwise, invasion requires
-%\begin{equation}
-%(\lambda_{mA}-1)(\lambda_{ma}-1) - \chi_{mA} \chi_{ma}<0.
-%\end{equation}
-
-We are particularly concerned with the conditions under which a rare neo-sex-determining allele increases in frequency, which occurs when the largest eigenvalue, $\lambda$, is greater than one. 
-%If the average change in frequency of the two haplotypes that carry the $m$ allele ($Am$ and $am$) is positive, invasion will always occur, i.e., if $(\lambda_{mA} + \lambda_{ma})/2 > 1$ then $\lambda > 1$.
-The leading eigenvalue solves $f(\lambda)=\lambda^2+b\lambda+c=0$ and the Perron-Frobenius theorem guarantees that the leading eigenvalue is positive, unique, and real.  
-Since $f(\lambda_{mA})$ and $f(\lambda_{ma})$ are of opposite signs, the leading eigenvalue must fall between these two quantities and is the larger of them when $R = 0$.  
-Consequently, if both $\lambda_{mA}$ and $\lambda_{ma}$ are greater than one, then the leading eigenvalue will always be greater than one, regardless of the linkage between the neo-sex determination factor and the selected locus ($R$).
-In particular, having $\lambda_{mA} >1$ and $\lambda_{ma}>1$ thus guarantees that an unlinked sex determining factor can invade ($R=1/2$).  
-Conversely, if both $\lambda_{mA}$ and $\lambda_{ma}$ are smaller than one, then invasion can never occur.  
-Finally, if only one of  $\lambda_{mA}$ and $\lambda_{ma}$ is greater than one, the new sex determining factor can always invade when tightly linked to the selected locus ($R$ near 0).  
-Furthermore, it can be shown that the leading eigenvalue declines with $R$, and invasion requires that $R$ is sufficiently small that the following condition holds: 
-\begin{equation}\label{eq:lambdasGen}
-%\frac{\chi_{mA}}{\lambda_{mA}-1}+\frac{\chi_{ma}}{\lambda_{ma}-1}>0.
-\chi_{ma}/\left(\lambda_{ma}-1\right) + \chi_{mA}/\left(\lambda_{mA}-1\right) < 1.
-\end{equation}
-\noindent 
-This condition may or may not be satisfied for the full range of locations of the new sex determining factor, including $R=1/2$, depending on the nature of selection.  
-Interpreting this condition, if we assume that only the $mA$ haplotype has a positive growth rate when $R=0$, $\lambda_{ma}<1<\lambda_{mA}$, the first term on the left-hand side of \eqref{eq:lambdasGen} is negative and invasion requires that the $mA$ haplotype growth rate ($\lambda_{mA}-1$) and the rate at which they are produced by recombination in $ma$ haplotypes ($\chi_{ma}$) are sufficiently large relative to the $ma$ haplotype rate of decline ($1-\lambda_{ma}$) and the rate of loss of $mA$ haplotypes due to recombination ($\chi_{mA}$).
-%In other words, invasion requires that the average growth rate of the two haplotypes, weighted by the rates they are created by recombination, is positive.
-%the number of recombinants from the fitter $mA$ haplotypes is larger than that of the less fit $ma$ haplotypes, relative to their growth rates.
-
-We can draw a number of key points about the invasion of neo-Y and neo-W mutations from Table \ref{tab:haplotype_growth}. 
-First, Fisherian sex ratio selection will favour the spread of a neo-Y if the ancestral zygotic sex ratio is biased towards females, $\zeta<1/2$ (i.e., the first factor of the $\lambda_{mi}$ is greater than one for a neo-Y and less than one for a neo-W).
-However, the spread of a neo-Y (neo-W) also depends on the male (female) fitness of associated alleles (see terms involving equilibrium allele frequencies, $\hat{p}$'s).
-Second, invasion by a neo-Y (neo-W) allele does not directly depend on the fitness of female (male) diploids. %(for a given set of equilibrium allele frequencies).
-This is because a dominant neo-Y (neo-W) is always found in males (females), and therefore the frequency of the neo-Y (neo-W) allele, $m$, only changes in males (females), Figure \ref{fig:model_outline}C,D.
-Finally, invasions by a neo-Y and a neo-W are qualitatively different.
-This is because a gamete with the neo-Y always pairs with a female gamete containing an X, and develop into males, Figure \ref{fig:model_outline}C.
-By contrast, a gamete with a neo-W can pair with an X or Y male gamete, developing into a female, Figure \ref{fig:model_outline}D.
-Consequently, neo-W bearing females obtain a differerent frequency of $A$ alleles from mating (when $\hat{p}_X^\male \neq \hat{p}_Y^\male$) compared to ancestral ($MM$) females.
-
-In order to explicitly determine the conditions under which a rare neo-sex-determining allele spreads, we must calculate the equilibrium frequency of the $A$ allele (i.e., $\hat{p}^\female_X$, $\hat{p}^\male_X$, and $\hat{p}^\male_Y$) and Y-bearing male gametes ($\hat{q}$) in the ancestral population.
-Since only the \textbf{A} locus experiences selection directly, any deterministic evolution requires that there is a polymorphism at the \textbf{A} locus. 
-Polymorphisms can be maintained by mutation-selection balance or transiently present during the spread of beneficial alleles.
-However, polymorphisms maintained by selection can maintain alleles at intermediate allele frequencies for longer periods.
-Here, we focus on polymorphisms maintained by selection, where the $A$ allele reaches a stable intermediate equilibrium frequency under the ancestral sex-determination system before the neo-sex-determining allele ($m$) arises.
-Such polymorphisms can be maintained by heterozygote advantage, sexually-antagonistic selection, ploidally-antagonistic selection, or a combination \citep{Immler:2012tl}.
-We can analytically calculate the allele frequency of the $A$ allele using two alternative simplifying assumptions: 
-(1) the \textbf{A} locus is within (or tightly linked to) the non-recombining region around the ancestral SDR ($r \approx 0$) or (2) selection is weak relative to recombination ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon<<1$).
-
-\subsubsection*{Tight linkage with the ancestral sex-determining region ($r \approx 0$)}
-
-The ancestral equilibrium allele frequencies and their stability conditions are given in the appendix.
-When there is complete linkage between the ancestral sex-determining region and the \textbf{A} locus ($r=0$), either the $A$ allele or the $a$ allele must be fixed on the Y. 
-% because selection on the Y is effectively haploid an incapably of maintaining a polymorphism in the absence of frequency dependent selection. 
-Because the labelling of alleles is arbitrary, we will assume that the $a$ locus is fixed on the Y ($p^\male_Y=0$), without loss of generality. 
-If there are two alleles maintained at the \textbf{A} locus, the X can either be fixed for the $A$ allele ($\hat{p}^\female_X=\hat{p}^\male_X=1$) or polymorphic (0<$\hat{p}^\female_X, \hat{p}^\male_X$<1).
-%However, because the X is present in both males and females, there are distinct selection pressures on X's in females and X's in males, which will always be paired with an $A$ allele from the Y.
-
-We find that a neo-Y can never invade an ancestral XY system that already has tight linkage with the locus under selection ($r=0$, for details see supplementary \textit{Mathematica} file). 
-When $R=0$, a neo-Y haplotype with the same allele as the ancestral Y is neutral ($\lambda_{Ya}=1$) and does not change in frequency.
-The other neo-Y haplotype will not spread ($\lambda_{YA}<1$) given that the initial equilibrium is stable. 
-Therefore, a neo-Y mutation cannot spread ($\lambda \leq 1$, regardless of $R$) in an ancestral XY system where selected loci are within or very near the non-recombining region around the SDR.
-In essence, through tight linkage with the \textbf{A} locus, the ancestral Y becomes strongly specialized on the allele that has the highest fitness across male haploid and diploid phases. 
-Given that the ancestral Y is at this equilibrium, it is not possible for a neo-Y to create males that have higher fitness than the ancestral Y.
-
-Neo-W alleles, on the other hand, can invade an ancestral XY system under some conditions (the full invasion conditions are given in the appendix; equations \ref{Binvasion} and \ref{Ainvasion}). 
-Counterintuitively, selection on loci within the non-recombining region of the SDR can favour the invasion of a less closely linked neo-W, whatever the form of selection maintaining a polymorphism (sexually-antagonistic selection, overdominance, ploidally-antagonistic selection, or some combination, Figures \ref{fig:SexAntagTighter}, \ref{fig:temporalOverdominance}, \ref{fig:regionPloidAntag}, and \ref{fig:SexAntagTighterMaleDrive}).
-The conditions become more restrictive, however, with increasing recombination ($R$) between the new sex determining region and the selected locus.  
-The invasion of completely unlinked neo-W alleles ($R = 1/2$) can occur with overdominance in males or with haploid selection but is not possible with only sexually-antagonistic selection if selection is directional in each diploid sex (see Supplementary \textit{Mathematica} file).
-To develop an intuition for how less closely linked neo-W alleles invade ($R>r$), we first focus on cases where there is no haploid selection and discuss the additional effect of haploid selection in the appendix.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Tighter linkage allows looser sex-linkage to evolve, even in absence of haploid selection
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-\centerline{\includegraphics[width=1.5\linewidth]{PositionPlot_SexAntagTighter}}
-\caption{
-Transitions between XY and ZW systems can occur even when the neo-SDR is less tightly linked to a locus under sexually-antagonistic selection (here, without haploid selection).
-In panel A, linkage is loose enough relative to selection that the analytical results assuming weak selection hold, and a neo-W can only invade when it is more tightly linked with the selected locus ($R<r$; shaded region).
-In panel B, linkage is tight enough relative to selection that the analytical results assuming weak selection do not hold, and a neo-W can invade even when it is less tightly linked with the selected locus ($r<R$; unshaded region).
-In panel C we vary the recombination rate between the neo-W and the selected locus ($R$) for a fixed recombination rate between the ancestral-SDR and the selected locus ($r=0.005$). 
-Coloured markers show recombination rates for which the temporal dynamics of invasion are plotted in the inset, demonstrating that neo-W alleles can fix (reach frequency $0.5$ among female gametes) if they are more (black) or less (red) closely linked to a locus experiencing sexually-antagonistic selection.
-A very loosely linked neo-W does not spread in this case (blue and green lines overlap and go to 0). 
-Fitness parameters are: $w_{AA}^\female = 1.05$, $w_{aa}^\male = 1.2$, $w_{aa}^\female = w_{AA}^\male = 0.85$, $w_{Aa}^\Hermaphrodite = 1$,  $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
-%\textcolor{red}{consider removing panel A, which is repeated in Figure 3.}
-%\textcolor{blue}{probably better to remove from panel 3, eh?}
-}
-\label{fig:SexAntagTighter}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-If we categorise the $a$ allele as being ancestrally `male-beneficial' via the fact that it is fixed on the Y, then $\lambda_{WA}>1$ indicates that the neo-W spreads when found with the ancestrally `female-beneficial' allele.
-Broadly, this is possible because the ancestral X chromosome is sometimes found in males and is therefore unable to perfectly specialise on the `female-beneficial' allele. 
-For example, when the $a$ allele is favoured on the ancestral X in males, a polymorphism of $A$ and $a$ alleles can be maintained on the X despite directional selection in favour of the $A$ allele in females ($s^\female>0$, $0<h^\female<1$), see outlined region in Figure \ref{fig:regionplots}A.
-When the $a$ allele is strongly favoured on X chromosomes in males ($w_{aa}^\male$ sufficiently large relative to $w_{Aa}^\male$), neo-W-$A$ haplotypes can spread ($\lambda_{WA}>1$, see grey region in Figure \ref{fig:regionplots}A) because they produce hgher fitness females ($AA$ or $Aa$ genotypes) and are unleashed from counterselection in males.
-
-When only one neo-W haplotype has a positive growth rate (see Figure \ref{fig:regionplots}), a neo-W can invade as long as equation \eqref{eq:lambdasGen} is satisfied, which may require that the recombination rate, $R$, is small enough.
-Nevertheless, because we assume here that $r$ is small, these results indicate that a more loosely linked sex-determining region ($r<R$) can spread.
-Therefore, tightly sex-linked loci that experience sexually-antagonistic selection can drive trans-GSD transitions in which the neo-SDR is less closely linked to the locus under selection (Figure \ref{fig:SexAntagTighter}).
-
-Given that the $a$ allele can be considered ancestrally `male-beneficial' because it is fixed on the Y, it is surprising that neo-W-$a$ haplotypes can sometimes be favoured by selection in females ($\lambda_{Wa}>1$).
-Again, this occurs because ancestral X's also experience selection in males, in which they will always be paired with a Y-$a$. 
-If there is overdominance in males, X-$A$ Y-$a$ males have high fitness and the $A$ allele is favoured by selection on the X in males. 
-Therefore, the X can be polymorphic or even fixed for the $A$ allele despite favouring the $a$ allele during selection in females \citep[e.g., see outlined region in Figure \ref{fig:regionplots}B and][]{Lloyd1977,Otto2014}.
-In such cases, neo-W-$a$ haplotypes can spread because they create more $Aa$ and $aa$ females when pairing with an X from males and because they bring Y-$a$ haplotypes into females, where it has higher fitness (Figure \ref{fig:model_outline}D).
-
-In some cases, both W-$A$ and W-$a$ haplotypes can spread, e.g., when $AA$ individuals have low fitness in females yet the $A$ is polymorphic or fixed on the X due to overdominance in males (Figure \ref{fig:regionplots}B and \ref{fig:regionplots}C).
-Both neo-W-$A$ and neo-W-$a$ haplotypes then produce fewer unfit $AA$ females.
-This is true for the neo-W-$A$ haplotype because it can pair with a Y-$a$ haplotype and still be female. 
-Wherever both haplotypes have positive growth rates, invasion by a neo-W is expected regardless of its linkage with the selected locus (i.e., even unlinked neo-W alleles can invade, see Figures \ref{fig:positionOverdominance} and \ref{fig:temporalOverdominance} for examples).
-
-Assuming that linkage is not tight, \citet{vanDoorn:2010hu} showed that invasion by a neo-W occurs under the same conditions as `pseudo-fixation' (at pseudo-fixation the neo-W reaches its maximum frequency among eggs, which is 1/2).
-An equivalent analysis is not possible where we assume that linkage is tight. 
-However, numerical simulations with tight linkage demonstrate that the neo-SDR does not necessarily reach pseudo-fixation, leading to the stable maintenance of a mixed sex-determining system, in which X, Y, Z, and W alleles all segregate (e.g., Figure \ref{fig:freqAll}B,C).
-
-%Haploid selection impacts the spread of neo-W haplotypes through its direct selective effect on females and their gametes, its indirect effect on the marginal fitness of alleles in females resulting from haploid selection in male gametes, and its effect on the sex ratio.
-%These impacts expand the scenarios under which neo-W haplotypes can spread.
-%For instance, overdominance is no longer required for neo-W-$a$ haplotypes to spread when there is haploid selection (e.g., when $a$ is female-beneficial, $A$ is male-beneficial, and meiotic drive in males favours $a$, Figure \ref{fig:regionMaleDrive}B).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Both neo-W haplotypes can spread, in the absence of haploid selection, when there is overdominance
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-%\centerline{\includegraphics[width=1.25\linewidth]{Region_plot_combined_Mike}}
-\centerline{\includegraphics[width=1.25\linewidth]{Region_plot_combined}}
-\caption{
-When the ancestral-XY locus is tightly linked to a locus under selection ($r=0$), one or both neo-W haplotypes can spread. 
-We vary the fitness of male homozygotes relative to heterozygotes ($w_{Aa}^\Hermaphrodite=1$) and only consider stable equilibria at which both \textbf{A} locus alleles are maintained and the $a$ allele is initially fixed on the Y, region outlined.
-Here, selection in females can favour the $A$ allele (panel A, $w_{aa}^\female=0.85$, $w_{AA}^\female=1.05$), favour the $a$ allele (panel B, $w_{aa}^\female=1.05$, $w_{AA}^\female=0.85$), or be overdominant (panel C, $w_{aa}^\female=w_{AA}^\female=0.6$).
-If $\lambda_{wA}$ or $\lambda_{wa}$ is greater than one, then a rare neo-W can spread for, at least, some values of $R>r$. 
-The parameter values marked with an asterisk correspond to the fitnesses used in Figure \ref{fig:SexAntagTighter}C. 
-Where both $\lambda_{wA}$ and $\lambda_{wa}$ are greater than one, a neo-W will spread when rare, regardless of linkage with the selected locus (for any $R$). 
-Figure \ref{fig:positionOverdominance} shows the dynamics using the parameters marked with a dagger. 
-Here, there is no haploid selection $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
-}
-\label{fig:regionplots}
-\end{figure}
-
-%Neo-W alleles, on the other hand, can invade an ancestral XY system under some conditions (given in detail in the appendix). 
-%%The full characteristic polynomials are given in the appendix (equations \ref{Binvasion} and \ref{Ainvasion}).
-%Briefly, neo-W-$A$ and/or neo-W-$a$ haplotypes can spread when rare in the absence of recombination ($\lambda_{ma}>1$ and/or $\lambda_{mA}>1$), depending on the ancestral sex ratio and allele frequencies.
-%Below we discuss the main forces determining the spread of these neo-W haplotypes and the impact of recombination for the overall success of the neo-W.
-%To simplify our discussion we first outline the potential effects of haploid selection and then consider diploid selection in its absence.
-
-%\textcolor{blue}{This explanation is clearer than the one I put in the appendix, if we drop it here, maybe we should try and re-word the corresponding part of the appendix using this paragraph}
-%Haploid selection impacts the spread of neo-W haplotypes in three ways.
-%Firstly, the zygotic sex ratio becomes male biased ($\zeta<1/2$) when the $a$ allele (which is fixed on the Y) is favoured during competition among male gametes or by meiotic drive in males. 
-%This facilitates the spread of a neo-W because neo-W alleles cause the zygotes that carry them to develop as the rarer, female, sex. 
-%Secondly, haploid selection in males affects the diploid genotypes of females by altering the allele frequencies in the male gametes that female gametes pair with.
-%For instance, because an epistatically dominant neo-W always causes its carrier to become female, it creates females who carry either $Y-a$ or $X$ genotypes from their father.
-%Thus, because when there is a polymorphism the $X$ carries some non-zero frequency of $A$, haploid selection in males impacts the diploid genotypes of females (e.g., creating more $Aa$ females when drive in males favours $Y-a$).
-%How this affects the spread of the neo-W then depends on diploid and haploid selection in females.
-%Thirdly, female drive and gamete competition directly select on neo-W haplotypes.
-%Drive for $A$ in females favours neo-W-$A$ haplotypes, at a cost to neo-W-$a$ haplotypes, and vice-versa when there is drive for $a$.
-%The impact of this drive depends on how often XX and neo-W females are heterozygous.
-%Competition among female gametes acts similarly, and depends on the frequency of $A$ on resident X chromosomes (e.g., competition among eggs has no affect on the initial spread of the neo-W-$A$ haplotype when $A$ is fixed on the X).
-%Because haploid selection in females favours one neo-W haplotype at the expense of the other, recombination off the favoured background becomes more detrimental as it becomes more favoured.
-Thus higher rates of recombination between the neo-W and the selected locus, $R$, can lead to smaller leading eigenvalues when there is haploid selection in females.
-
-%In the absence of haploid selection and with the $A$ allele is fixed on the X, it is possible for both neo-W haplotypes can spread ($\lambda_{mA}>1$ and $\lambda_{ma}>1$ in \ref{Binvasion}), and thus neo-W invasion can occur regardless of its linkage to the selected locus.
-%Invasion does not occur with purely sexually-antagonistic selection (i.e., $a$ directionally favoured in males and $A$ directionally favoured in females) because the X is then already as specialized as possible on the female sex.
-%However, if, for example, $AA$ individuals suffer a fitness cost in females, yet $A$ is fixed on the X due to strong overdominance in males, both neo-W-$A$ and neo-W-$a$ haplotypes spread because they produce fewer unfit $AA$ females and never experience counter-selection in males.
-%This is true even for the neo-W-$A$ haplotype because it can pair with a $Y-a$ haplotype and still be female. 
-%When both haplotypes can spread alone the rate of recombination between the neo-W and the selected locus, $R$, does cannot prevent invasion, and thus the system can evolve looser sex-linkage (e.g., the neo-W could arise on an autosome, $R=1/2$).
-%Even when only one haplotype can spread, invasion can still occur up to some positive rate of recombination, $R>0$ (as long as equation \ref{eq:lambdasGen} is satisfied). 
-%That looser sex-linkage can evolve is contrary to the conclusions of \cite{vanDoorn:2010hu}, who did not explicitly calculate invasion fitness under ancestrally tight sex-linkage.
-\textcolor{blue}{or, just didn't calculate the equilibria (A) an (B).}
-%Similar scenarios have been shown to select for a modifier that increases recombination between the sexes \citep[green regions of Figure 2 in][]{Otto2014}.
-%\textcolor{blue}{n.b., the recombination regions are only subsets mostly because you also generate a really unfit Y haplotype through recombination. Probably not worth mentioning.}
-%
-%In the absence of haploid selection it is also possible for a neo-W to invade when there is a stable polymorphism at the $\mathbf{A}$ locus on X chromosomes.
-%For example, overdominance in males and strong directional selection for $a$ in females creates a scenario that favours the spread of both neo-W haplotypes at equilibrium ($\lambda_{mA}>1$ and $\lambda_{ma}>1$ in \ref{Ainvasion}), as both haplotypes bring more $a$ alleles into females and never experience counter-selection in males.
-%Thus, as in the case of the $A$ being fixed on the X, looser sex-linkage can evolve with a polymorphic X (i.e., $\lambda>1$ with $R>0$) and this is expected under the same scenarios that select for a modifier that increases recombination between the sex chromosomes \citep[blue regions of Figure 2 in][]{Otto2014}.
-
-\subsubsection*{Loose linkage with the ancestral sex-determining region}
-
-%\textcolor{blue}{As with the discussion, this section might need some editing for (1) unclearly describing looser linkage never evolving without haploid selection, which we now show is possible above and (2) going on about sex ratio selection too much - this should be changed to something along the lines of  ``male biased zygotic sex ratios ($\zeta-1/2$) are of the order of $\epsilon^2$.
-Therefore Fisherian sex ratio selection directly favours neo-Ws by a similar magnitude.
-%Perhaps surprisingly, neo-Ws can be favoured to the same degree by haploid selection in females when female haploid selection favours the alleles that tend to be carried by the neo-W.
-%Thus XY to ZW is the same as ZW to XY even though sex ratio biases only exist in one case, given the assumptions made in this section.
-%''
-%}
-
-%weak selection
-%We are particularly concerned with whether or not a rare neo-sex-determining allele increases in frequency, which occurs when the largest eigenvalue, $\lambda$, is greater than one. 
-%Here, we explicitly determine the conditions under which invasion occurs by assuming that the $A$ allele reaches an equilibrium frequency under the ancestral sex-determination system before the neo-sex-determination system ($m$) arises.
-%The equilibrium frequency of $A$ on different ancestral backgrounds ($\hat{p}^\male_Y$, $\hat{p}^\male_X$, and $\hat{p}^\female_X$) is given by equations \eqref{eq:pAve} and \eqref{eq:freq_diffs} where we assume selection and meiotic drive are weak relative to recombination ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon$).
-Assuming that selection is weak ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon<<1$) and thus implicitly assuming that all recombination rates ($r$, $R$ and $\rho$) are large relative to selection, we denote the leading eigenvalues describing the invasion of a neo-Y ($k=0$) and a neo-W ($k=1$) into an ancestrally XY system by $\lambda_{Y',XY}$ and $\lambda_{W',XY}$, respectively.
-To leading order in selection, these are:
-
-\begin{equation}
-\lambda_{Y',XY} =1+ \frac{1}{4}V_{A}S_{A}^2\frac{ \left( r-R \right) }{r R}+O\left(\epsilon^3 \right) 
-\label{eq:lambda_neoY}
-\end{equation}
-
-\noindent 
-and
-
-\begin{equation}
-\lambda_{W',XY} =\lambda_{Y',XY}+\left(2\alpha_{\Delta}^\male-2\alpha_{\Delta}^\female+t^\male-t^\female \right) \left( \hat{p}^\male_Y-\hat{p}^\male_X \right)/2
-+O\left(\epsilon^3 \right) \\
-\label{eq:lambda_neoW}
-\end{equation}
-
-\noindent
-where $V_{A}=\bar{p}(1-\bar{p})$ is the variance in the equilibrium frequency of $A$ and $S_{A}=(D^\male +\alpha_{\Delta}^\male+t^\male) - (D^\female+\alpha_{\Delta}^\female+t^\female)$ describes sex differences in selection for the $A$ versus $a$ allele across diploid selection, meiosis, and gametic competition.
-The diploid selection term, $D^\Hermaphrodite=\big{[} \bar{p}s^\Hermaphrodite+(1-\bar{p})h^\Hermaphrodite s^\Hermaphrodite\big{]} -\big{[} \bar{p}h^\Hermaphrodite s^\Hermaphrodite+(1-\bar{p}) \big{]}$, is the difference in fitness between $A$ and $a$ alleles in diploids of sex $\Hermaphrodite \in \{\female,\male\}$, where $\bar{p}$ is the leading-order probability of mating with an $A$-bearing gamete from the opposite sex (equation \ref{eq:pAve}).
-The difference in $A$-allele-frequency among Y-bearing sperm versus X-bearing sperm is given by $\hat{p}^\male_Y-\hat{p}^\male_X=V_{A}\big{(}D^\male - D^\female+\alpha_{\Delta}^\male-\alpha_{\Delta}^\female+t^\male-t^\female\big{)}(1-2r)/(2r)$.
-
-The neo-sex-determining allele, $m$, will spread if $\lambda_{m,XY}>1$. 
-Equation \eqref{eq:lambda_neoY} demonstrates that, under weak selection, a neo-Y will invade an XY system if and only if it is more closely linked to the selected locus than the ancestral sex-determining region (i.e., if $R<r$; note that $V_{A}S_{A}^2$ is strictly positive as long as \textbf{A} is polymorphic).
-This echoes our tight linkage results above where a neo-Y could never invade if $r\approx0$.
-It is also consistent with the results of \citet{vanDoorn:2007eu}, who considered diploid selection only and also found that cis-GSD transitions (XY to XY or ZW to ZW) can only occur when the neo-sex-determining locus is more closely linked to a locus under sexually-antagonistic selection.
-%Because tighter linkage between the sex-determining region and a selected locus evolves during these transitions, stronger associations between selected alleles and diploid sexes can build up by selection (e.g., between male-beneficial alleles and the male-determining allele, Y).%, increasing diploid mean fitness (Figure \ref{fig:Combination_MeanFit}).
-
-With weak selection and no haploid selection ($t^\Hermaphrodite=\alpha^\Hermaphrodite_{\Delta}=0$), the spread of a neo-W is equivalent to the spread of a neo-Y ($\lambda_{W',XY}=\lambda_{Y',XY}$), such that trans-GSD transitions (XY to ZW or ZW to XY) can also occur only if the neo-sex-determining region is more closely linked to a locus under selection ($R<r$), as found by \citet{vanDoorn:2010hu}.
-With haploid selection, however, the additional term in equation \eqref{eq:lambda_neoW} can be positive, which can allow, for example, neo-W invasion ($\lambda_{W',XY}>1$) even when the neo-sex-determining region is less closely linked to the selected locus ($R>r$).
-%These transitions are unusual because, when $R>r$, associations that selection has built up between alleles more favourable in one sex and alleles that determine sex will be weakened. 
-%Mean diploid fitness therefore decreases during heterogametic transitions that create looser sex-linkage (Figure \ref{fig:Combination_MeanFit}B,D).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%A neo-W can invade an XY system under a large number of selective regimes
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-\includegraphics[width=\linewidth]{PositionPlot}
-\caption{
-% A neo-W can invade an XY system under a large number of selective regimes.
-%In panel A, there is no haploid selection ($t^\Hermaphrodite = \alpha^\Hermaphrodite_{\Delta} = 0$) and selection in diploids is sexually antagonistic ($s^\male = -s^\female = 1/10$, $h^\male = 1-h^\female = 3/10$), in which case the neo-sex-determining allele can only invade if it is more closely linked to the selected locus ($R<r$, gray region; but see Figure \ref{fig:SexAntagTighter}B for the case of very tight linkage).
-Ploidally-antagonistic selection allows a less tightly linked neo-W to invade.
-In panel A, male drive ($\alpha^\male_{\Delta} = -1/20$, $t^\Hermaphrodite = \alpha^\female_{\Delta} = 0$) opposes selection in diploids (no sex-differences: $s^\Hermaphrodite = 1/10$, $h^\Hermaphrodite = 7/10$), in which case the neo-sex-determining allele can invade regardless of linkage.
-In panel B, gametic competition in males ($t^\male = -1/10$, $t^\female = \alpha^\Hermaphrodite_{\Delta} = 0$) opposes selection in diploids (sex-differences: $s^\male = 3/20$, $s^\female = 1/20$, $h^\Hermaphrodite = 7/10$), in which case the neo-sex-determining allele can once again invade regardless of linkage.
-We use Haldane's map function \citep[Equation 3 in ][]{Haldane1919} to convert from map distance (centiMorgans, cM) to the probability of recombination (an odd number of cross-over events).   
-%\textcolor{red}{Check the mismatch between red and black lines here: probably because of adding or subtracting from 1. }
-%\textcolor{blue}{Can remove the mismatch by flipping the fitnesses between males and females (again).
-That is, if $M_{AA}$ is the fitness of $AA$ male diploids in an ancestral XY system, then $M_{AA}$ is the fitness of $AA$ female diploids in an ancestral ZW system.
-I think this makes sense in A, where we don't really want a difference between the red and black curves, but this makes less sense in B and C where we want to restrict haploid selection to males regardless of the ancestral system.
-We could just not flip the haploid fitnesses, but then does it make sense to flip the diploid fitnesses?}
-}
-\label{fig:Combination_Centimorgans}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Equation \eqref{eq:lambda_neoW} shows that, with weak selection, neo-W alleles can invade an XY system for a large number of selective regimes. 
-To clarify the parameter space under which $\lambda_{W',XY}>1$, we consider several special cases. 
-Firstly, if the \textbf{A} locus is unlinked to the ancestral sex-determining region ($r=1/2$), a more closely linked neo-W ($R<1/2$) can always invade because there is no ancestral association between $A$ alleles and sex chromosomes in males, $\left( \hat{p}^\male_Y-\hat{p}^\male_X \right)=0$, see equation \eqref{eq:freq_diffs}.
-The second term in equation \eqref{eq:lambda_neoW} therefore disappears and invasion depends only on the sign of $(r-R)$, as in the case of the neo-Y. 
-Indeed, invasion typically occurs when the neo-W is more closely linked to the selected locus than the ancestral sex-determining region (Figure \ref{fig:Combination_Centimorgans}).
-
-Secondly, we can simplify the discussion of cases where invasion occurs despite looser sex-linkage, $R>r$, by focusing on the special case where $R=1/2$ and $r<1/2$ (e.g., the selected locus is on the ancestral sex chromosome and the novel sex-determining locus arises on an autosome).
-In Table \ref{tab:specialcases} we give the conditions where invasion occurs when we further assume that haploid selection only occurs in one sex (e.g., during male meiosis only) and dominance coefficients are equal in the two sexes, $h^\female=h^\male$.
-When there is no gametic competition and meiotic drive is in one sex only, an unlinked neo-W can invade as long as the same allele is favoured during diploid selection in males and females ($s^\female s^\male>0$, see Figure \ref{fig:Combination_Centimorgans}A and Figure \ref{fig:SexRatioBad}B).
-%, which is 50\% of the parameter space.
-When there is no meiotic drive and gametic competition occurs in one sex only, an unlinked neo-W can invade as long as the same allele is favoured in male and female diploid selection and there are sex differences in selection of one type (e.g., $s^\female(s^\male-s^\female)>0$, see Figure \ref{fig:Combination_Centimorgans}B).
-%, which is 25\% of the parameter space.
-These special cases indicate that neo-W invasion occurs for a relatively large fraction of the parameter space, even if the neo-W uncouples the sex-determining locus from a locus under selection.
-
-\begin{table}[ht]
-\centering
-\smallskip
-\caption{Invasion conditions for unlinked neo-W ($R=1/2$, $r<1/2$) into ancestral XY with one form of haploid selection}
-\begin{tabular}{l l c }
-\hline\hline
-Scenario &  Assumptions & neo-W spreads ($\lambda_{W',XY}>1$) if \\ [0.5ex] \hline
-%  $r=1/2$, $R<1/2$ & Always \\ [0.5ex] \hline
-%  $r<1/2$, $R=1/2$ &  \\ [0.5ex] \hline
-\noalign{\vskip 1mm}
-  male drive only & $h^\male=h^\female$, $t^\female=t^\male=\alpha^\female_{\Delta}=0$ & $s^\female s^\male>0$ \\ [0.5ex]
- female drive only & $h^\male=h^\female$, $t^\female=t^\male=\alpha^\male_{\Delta}=0$ & $s^\female s^\male>0$ \\ [0.5ex]
- sperm competition only &  $h^\male=h^\female$, $t^\female=\alpha^\female_{\Delta}=\alpha^\male_{\Delta}=0$ & $s^\female(s^\male-s^\female)>0$ \\ [0.5ex]
-  egg competition only & $h^\male=h^\female$, $t^\male=\alpha^\female_{\Delta}=\alpha^\male_{\Delta}=0$ & $s^\male(s^\female-s^\male)>0$ \\ [0.5ex]
-  \hline \hline
-  \label{tab:specialcases}
- \end{tabular}
-\end{table}
-
-%If we further assume equal dominance ($h^\female=h^\male$) and that haploid selection only occurs during male meiosis ($t^\female=t^\male=\alpha^\female_{\Delta}=0$), or female meiosis ($t^\female=t^\male=\alpha^\male_{\Delta}=0$), neo-W invasion occurs when $s^\female s^\male>0$, Figure \ref{fig:Combination_Centimorgans}B.
-%That is, when the same allele is favoured by selection in both males and females (it may remain polymorphic via counter selection during meiotic drive).
-
-%\textcolor{red}{It may seem counterintuitive that, if the $A$ allele is more common on the ancestral-Y than the ancestral-X, and only favoured during haploid selection in males}
-
-%\textcolor{red}{although our predictions also perform well when recombination is small, see figure \ref{fig:WinvasionLowR}.
-We would have to add a line showing what invasion fitness the weak selection approximation would give and add dots to this figure (dots that are currently connected by a line), as in (vD\&K, 2010) }
-
-%Sex ratios
-%Previous research suggests that when the ancestral sex-determining locus is linked to a locus that experiences haploid selection (e.g., meiotic drive), a new, unlinked sex-determining locus invades in order to restore equal sex ratios \citep{Kozielska:2010vm}.
-%Our model provides a good opportunity to determine whether Fisherian sex ratio selection provides a useful explanation for the evolution of new sex-determining loci in other contexts. 
-%Consider, for example, the case where the \textbf{A} locus is linked to the ancestral-SDR ($r<1/2$) and experiences meiotic drive in males only (e.g., during spermatogenesis but not during oogenesis, $\alpha^\male \neq 1/2$, $\alpha^\female=1/2$).
-%We will also disregard gametic competition ($t^\female=t^\male=0$) such that zygotic sex ratios are only biased by meiotic drive in males. 
-%In this case, the zygotic sex ratio can be initially biased only if the ancestral sex-determining system is XY (Figure \ref{fig:Combination_Turnover}B). 
-%If the ancestral sex-determining system is ZW, the zygotic sex ratio will be 1:1 because diploid sex is determined by the proportion of Z-bearing versus W-bearing eggs and meiosis in females is fair (Figure \ref{fig:Combination_Turnover}D).
-%Thus, if the zygotic sex ratio is crucial to the evolution of new genetic sex-determining systems, invasion into ZW and XY systems will be distinct. 
-%However, under weak selection we find that invasion by a homogametic neo-sex-determining allele (XY to XY or ZW to ZW) or by a heterogametic neo-sex-determining allele (XY to ZW or ZW to XY) occur under the same conditions.
-%That is, we can show that $\lambda_{Y',XY}=\lambda_{W',ZW}$ and $\lambda_{Y',ZW}=\lambda_{W',XY}$ (at least up to order $\epsilon^3$; for a numerical example, compare Figure \ref{fig:Combination_Turnover}A,B to Figure \ref{fig:Combination_Turnover}C,D).
-%As it turns out, under weak selection the strength of sex ratio selection favouring, say, the invasion of a neo-W in an XY system is the same as the strength of meiotic drive favouring the invasion of a neo-Y in a ZW system.
-%Even when these forces are not exactly the same (e.g., under tight sex-linkage; compare black and red curves near -25 and 25cM in Figure \ref{fig:Combination_Centimorgans}), it is important to remember that sex ratio selection is only one of many potential selective forces acting to determine transitions between sex-determining systems.
-%It is even possible for the other selective forces to overwhelm sex ratio selection and favour sex-determination transitions that create sex ratio biases (Figure \ref{fig:Combination_Turnover}A,C).
-
-Previous research suggests that when the ancestral sex-determining locus is linked to a locus that experiences haploid selection (e.g., meiotic drive), a new, unlinked sex-determining locus invades in order to restore equal sex ratios \citep{Kozielska:2010vm}.
-Consider, for example, the case where the \textbf{A} locus is linked to the ancestral-SDR ($r<1/2$) and experiences meiotic drive in males only ($\alpha^\male_\Delta \neq 0$, $\alpha^\female_\Delta=0$), without gametic competition ($t^\female=t^\male=0$).
-In this case, the zygotic sex ratio can be initially biased only if the ancestral sex-determining system is XY (Figure \ref{fig:model_outline}B and Figure \ref{fig:SexRatioBad}B). 
-%If the ancxestral sex-determining system is ZW, the zygotic sex ratio will be 1:1 because diploid sex is determined by the proportion of Z-bearing versus W-bearing eggs and meiosis in females is fair (Figure \ref{fig:Combination_Turnover}D).
-If Fisherian sex ratio selection were dominant, we would expect a difference in the potential for XY to ZW and ZW to XY transitions. 
-%However, to leading order with selection weak relative to recombination, we find that sex ratio selection favours the spread of a neo-W by an amount equl to the spread of a neo-Y into a ZW system (relabeling XY as the heterogametic sex and reversing the labels of males and females in Table \ref{tab:specialcases})
-%However, to leading order with selection weak relative to recombination, we find that sex ratio selection favours the spread of a neo-W (through the first terms in table \ref{tab:haplotype_growth}) by an amount that is equal in magnitude to the fitness effects of alleles associated with new sex-determining alleles (second terms in table \ref{tab:haplotype_growth}).
-However, invasion by a neo-W into an XY system and invasion by a neo-Y into a ZW system occur under the same conditions ($\lambda_{Y',XY}=\lambda_{W',ZW}$ and $\lambda_{Y',ZW}=\lambda_{W',XY}$, at least to order $\epsilon^2$).
-For example, in Figure \ref{fig:SexRatioBad}A neo-W alleles invade an ancestral-XY system where females are initially rare.
-However, Figure \ref{fig:SexRatioBad}B shows that a neo-Y can invade an ancestral-ZW system under the same conditions. 
-As a consequence, whenever $R<1/2$, the neo-Y becomes associated with the male meiotic drive allele such that the zygotic sex ratio actually evolves to become biased towards males.
-
-%As selection becomes stronger (or linkage becomes tighter), this symmetry between sex ratio selection and haploid selection is lost, causing differences in the strength of selection favouring the two heterogametic transitions (compare red to black near -25cM and 25 cM in Figure \ref{fig:Combination_Centimorgans}).
-\textcolor{red}{normalise fitness in sexually antagonistic case}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Sex ratio selection is not a good predictor of neo-W invasion into an XY system
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-\includegraphics[width=\linewidth]{Temporal_SR}
-\caption{
-Fisherian sex ratio selection alone is not a good predictor of turnover between sex-determining systems.
-In this figure, selection is ploidally antagonistic with haploid selection favouring the $a$ allele during male meiosis.
-In panel A, male drive in an ancestral ZW system has no affect on the zygotic sex ratio (see Figure \ref{fig:model_outline}B) yet a neo-Y can invade and replace the ancestral sex-determination system (inset shows neo-Y frequency among male gametes, the ancestral W also goes to fixation during this transition).
-When $R<1/2$, the neo-Y becomes associated with the allele favoured by drive, causing the zygotic sex ratio to become biased, hence the frequency of neo-Y among male gametes can be higher than $0.5$ (inset).
-In panel B, male drive in an ancestral XY system causes a male bias, allowing a neo-W to invade and replace the ancestral sex-determination system (inset shows neo-W frequency among female gametes, the ancestral Y also goes to fixation), which balances the zygotic sex ratio.
-Parameters:  $s^\female =s^\male = 0.2$, $h^\female = h^\male = 0.7$, $t^\female = t^\male = \alpha^\female_\Delta = 0$, $\alpha^\male_\Delta = -0.1$, $r=0.02$.
-}
-\label{fig:SexRatioBad}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Why can new sex-determining regions invade when more loosely linked to selected loci ($R>r$)?  
-Consider first the case where both loci are linked to the selected locus ($r<R<1/2$). 
-In an XY system, haploid selection in males can facilitate the spread of a neo-W because the zygotic sex ratio is ancestrally biased and the W helps to equalize the sex ratio (Figure \ref{fig:SexRatioBad}A).
-A new sex determining region can also, however, benefit from becoming more associated with drive.  
-For example in a ZW system with the same selection regime (haploid selection in males), a neo-Y can spread despite the fact that the zygotic sex is initially even; in this case, the neo-Y spreads because it is often found in males and can, if it carries the driven allele $a$, benefit from haploid selection (Figure \ref{fig:SexRatioBad}B).
-While equalizing the sex ratio and benefiting from drive are two primary reasons why haploid selection spurs sex chromosome transitions, more complex situations also arise.  
-For example with $R=1/2$ in Figure \ref{fig:SexRatioBad}B (green curve), the neo-Y spreads despite the fact that it cannot benefit from drive because free recombination moves it randomly between driven and non-driven backgrounds.
-Nevertheless, the unlinked neo-Y can spread because diploids bearing it more often carry the non-driven allele $A$ found at high frequency on the W background, which has higher average diploid fitness to balance the haploid advantage of the $a$ allele at equilibrium.
-
-%The green curves in Figure \ref{fig:SexRatioBad} show transitions between male and female heterogametey even though the new sex-determining region is unlinked to a locus that experiences haploid and diploid selection.
-%We use these green curves to discuss why trans-GSD transitions can occur when $R=1/2$ and $r<1/2$, as in Table \ref{tab:specialcases}.
-%In Figure \ref{fig:SexRatioBad}B, an unlinked neo-W can spread because the zygotic sex ratio is ancestrally male biased. 
-%In Figure \ref{fig:SexRatioBad}A, an unlinked neo-Y spreads despite the fact that the ancestral zygotic sex ratio is even. 
-%In this case, the male meiotic drive allele, $a$, is initially more common among ancestral-Z-bearing eggs than ancestral-W-bearing eggs because the Z is found in males more often than the W ($\hat{p}_{W}^\female-\hat{p}_{Z}^\female>0$, equation \ref{eq:freq_diffs}).
-%Polymorphism at the \textbf{A} locus is maintained by counter-selection against the $a$ allele in diploids and therefore ancestral-ZZ males have generally low diploid fitness. 
-%The neo-Y spreads because it produces males with high diploid fitness through matings with ancestral-W-bearing female gametes, which are more likely to carry the $A$ allele ($\hat{p}_{W}^\female-\hat{p}_{Z}^\female>0$).
-%A freely recombining neo-Y ($R=1/2$) is equally likely to be segregate with the $A$ or $a$ allele.
-%Therefore, the neo-Y is unaffected by male meiotic drive against the $A$ alleles that it introduces into males. 
-%Thus, a key factor in explaining why trans-GSD transitions can occur when $R>r$ is that the neo-SDR determines sex in the diploid phase but recombination occurs before any subsequent haploid selection.
-
-\subsubsection*{Environmental sex determination}
-
-We next consider the case where the new sex-determining mutation, $m$, causes sex to be determined probabilistically or by heterogeneous environmental conditions (environmental sex determination, ESD), with individuals carrying allele $m$ developing as females with probability $k$.
-Here, we do not assume that the environmental conditions that determine sex also differentially affect the fitness of males versus females. 
-Such correlations can favour environmental sex-determination systems that allow each sex to be produced in the environment in which it has highest fitness; in the absence of these correlations, previous theory would predict that ESD is favoured when it produces more equal sex ratios than the ancestral system \citep[see reviews by][]{Charnov:1982wg,Bull:1983vi,West:2009we}.
-%(e.g., maternal condition, mate quality, age, or host size)
-
-The characteristic polynomial determining the eigenvalues (equations \ref{eq:recursions}) does not factor for ESD mutants as it does for $k=0$ or $k=1$. 
-We therefore focus on weak selection here. 
-Assuming weak selection, the spread of the new sex-determining region is given by
-
-\begin{equation}
-\begin{split}
-\lambda_{ESD',XY} =& 1 + \frac{(1-2k)^2}{4}V_{A}{S_{A}}^2\frac{r-R}{r R} \\
-&+\frac{k(\hat{p}^\male_Y-\hat{p}^\male_X)}{2}\left[ k \left(2\alpha_{\Delta}^\male-2\alpha_{\Delta}^\female+t^\male-t^\female \right) -2(1-k)S_{A}\right]+O\left(\epsilon^3\right),
-\end{split}
-\label{eq:lambda_ESD_k}
-\end{equation}
-
-\noindent
-which reduces to $\lambda_{Y',XY}$ when $k=0$ and $\lambda_{W',XY}$ when $k=1$.
-
-%Under Fisherian sex ratio selection, autosomal modifiers favour equal investment in male and female offspring, i.e., a 1:1 sex ratio \citep{Fisher:1930wy,Charnov:1982wg,West:2009we}. 
-%A novel environmental sex-determiner that causes half of its carriers to become female and half to become male ($k=1/2$) will be in males half of the time and in females half of the time (like an autosome).
-%In addition, these novel sex-determination alleles equalize the sex ratio and therefore one might expect them to be favoured by Fisherian sex ratio selection when the resident sex ratio is biased.
-%However, assuming weak selection, we find that the growth rate of a rare, dominant offspring-controlled neo-ESD allele that produces males or females with equal probability ($k=1/2$) is
-Of particular interest are ESD mutations that cause half of their carriers to develop as females and half as males ($k=1/2$, creating equal sex ratios), the spread of which is given by
-\begin{equation}
-\lambda_{ESD',XY} =1+ \frac{1}{2}\frac{(\lambda_{Y',XY\rvert R=1/2}-1) + (\lambda_{W',XY\rvert R=1/2}-1)}{2} + O\left(\epsilon^3\right),
-%V_A \frac{r}{1-2r}  \frac{s_{f} \left( s^\male - 3 s^\female\right) }{8 \left( s_{f} + s_{m} \right)^2} t_{m}^2.
-\label{eq:lambda_ESD}
-\end{equation}
-\noindent
-where $\lambda_{Y',XY\rvert R=1/2}$ and $\lambda_{W',XY\rvert R=1/2}$ represent $\lambda_{Y',XY}$ and $\lambda_{W',XY}$ when evaluated at $R=1/2$ (Equations \ref{eq:lambda_neoY} and \ref{eq:lambda_neoW}).
-That is, recombination between the selected locus and the novel sex-determining locus, $R$, doesn't enter into the $k=1/2$ results.
-This is because sex is essentially randomized each generation, %as if the novel sex-determiner were on an unlinked site that half the time acts as a neo-$W$ and half the time as a neo-$Y$.
-preventing associations from building up between allele $A$ and sex. 
-Equation \eqref{eq:lambda_ESD} shows that the neo-ESD gets half of the fitness of a feminizing mutation (neo-$W$) and half of the fitness of a masculinizing mutation (neo-$Y$), but only has an effect one half of the time (the other half of the time it produces the same sex as the ancestral system would have).
-As discussed above, $\lambda_{Y',XY\rvert R=1/2}$ is necessarily less than one, but $\lambda_{W',XY\rvert R=1/2}$ can be greater than one if there is haploid selection.
-That is, when there is haploid selection, ESD mutations can invade an ancestrally-XY system because they generate females that are either rare or have high fitness, in the same manner as a neo-W.
-
-%An important result from equation \eqref{eq:lambda_ESD} is that ESD can invade if there is haploid selection. 
-%When evaluated at $R=1/2$, $\lambda_{Y',XY}$ is necessarily less than one, but $\lambda_{W',XY}$ can be greater than one if there is haploid selection, as discussed above. 
-%Previous studies where ESD is favoured have typically assumed that environmental conditions (e.g., maternal condition, mate quality, age, or host size) can differentially affect the fitness of males versus females such that ESD invades because it allows sex determination to depend on the environment \citep[reviewed in][]{Charnov:1982wg,Bull:1983vi,West:2009we}.
-%Here, ESD mutations can spread because they generate females that are either rare or have high fitness, in the same manner as a neo-W.
-
-Significantly, equation \eqref{eq:lambda_ESD} is the same whether ESD is invading an ancestrally XY or ZW system (because $\lambda_{Y',XY} = \lambda_{W',ZW}$ and $\lambda_{W',XY} = \lambda_{Y',ZW}$).
-Thus, Fisherian sex ratio selection alone does not explain the invasion of ESD under weak selection because the sex ratio is only biased by male haploid selection when the ancestral sex-determination system is XY.
-Specifically, with male haploid selection, the neo-ESD is equally likely to invade when it equalizes the zygotic sex ratio (through $\lambda_{W',XY}$) and when it doesn't (through $\lambda_{Y',ZW}$). 
-%This is again because haploid selection can facilitate the turnover of sex chromosomes either through sex ratio biases or through associations between the new sex determining region with selected alleles.
-%With weak selection, these two forces are nearly equal in strength. 
-In addition, we note that ESD may not invade, even if the sex ratio is initially biased (e.g., with drive in males only, $r<1/2$, $h^\female=h^\male$, and $s^\female s^\male<0$, then $\lambda_{W',XY}<1$, see Table \ref{tab:specialcases}).
-We conclude that, as with neo-W and neo-Y loci, associations with selected loci mean that the evolution of neo-ESD systems is not straightforwardly predicted by selection to balance the zygotic sex ratio when haploid selection is present.
-
-%Depends 50\% on its fitness relative to non-mutant males and 50\% on its fitness relative to non-mutant females.
-
-%\subsubsection*{Maternally-controlled neo-ESD}
-
-%Fisherian sex ratio selection is sometimes considered in terms of balancing parental investment in male versus female offspring \citep{Charnov:1982wg}.
-%In addition, under environmental sex-determination, the proportion of males/females is sometimes controlled by the mother (e.g., the proportion of eggs laid in warm versus cold environments). 
-%We therefore also considered the invasion of a neo-sex-determining allele ($m$) in a model in which mothers that have at least one $m$ allele produce daughters with probability $k$. 
-%As with offspring-controlled ESD, for all $k\in\{0,1/2,1\}$, we find that invasion into an ancestral XY system is the same as invasion into an ancestrally ZW system (at least up to order $\epsilon^3$, assuming weak selection), implying that transitions between genetic sex-determination and maternally controlled environmental sex-determination are not driven by Fisherian sex ratio selection alone.
-%\textcolor{red}{(Maternal ESD analysis still lacks meiotic drive -- Mathematica can't seem to deal with the added complexity.)}
-
-%One might think that when the sex of zygotes is under the control of mothers, there would be strong selection to balance the sex ratio among zygotes. 
-%However, we find that, with no meiotic drive and weak selection, the invasion fitness of a dominant, maternally controlled sex-determiner that produces proportion $k$ daughters can be written
-%\begin{equation}
-%\lambda_{k} = 1 + V_A S_A C_k + O\left(\epsilon^3\right),
-%\end{equation}
-%where
-%\begin{equation}
-%V_A = \frac{- \left[ t_m + h (s_{f}+s_{m}) \right] \left[ t_m + (1-h) (s_{f}+s_{m}) \right]}{(1-2h)^2(s_{f}+s_{m})^2}
-%\end{equation}
-%is the variance in $A$ ($V_A>0$ when the polymorphic resident equilibrium is stable), 
-%with $h$ the dominance coefficient (equal in both sexes), 
-%$C_k$ is a term that depends on $k$.
-%
-%%k=0
-%\begin{equation}
-%C_0 = big \; ugly \; term
-%\end{equation}
-%
-%%k=1
-%\begin{equation}
-%C_1 = \frac{\left[ (2r(1-R)-R) s^\female + (1-2r)R s^\male \right]}{2}
-%\end{equation}
-%
-%%k=1/2
-%\begin{equation}
-%C_{1/2} = even \; bigger, \; uglier \; term
-%\end{equation}
-%
-%When $k=1$ the maternal- and offspring-controlled results are the same, $C_1 = C_W$, since the mutation remains in females (and hence mutant daughters always have mutant mothers).
-%However, with $k\neq1$ the results with maternal control differ from those with offspring control.
-%Interestingly, for all $k\in\{0,1/2,1\}$, we find that invasion into an ancestrally XY system is the same as invasion into an ancestrally ZW system (at least up to order $\epsilon^3$), implying that sex ratio selection does not drive transitions between genetic sex determination and maternally controlled environmental sex determination.
-%Of particular interest is $k=1/2$ (i.e., when the mother perfectly balances the sex ratio of her offspring).
-%When both recombination rates are small we have $C_{1/2} \approx R(s^\male - s^\female)/8 = \lim_{r \rightarrow 0} C_1/4$.
-%This implies that, at least under tight linkage, the invasion of maternally-controlled ESD is independent of $R$ (because $S_A\propto R^{-1}$) and can invade whenever a neo-$W$ can (which can invade even when it biases the sex ratio further; Figures \ref{fig:WinvasionLowR} -- \ref{fig:WinvasionHighR}).
-
-\section*{Discussion}
-
-%\textcolor{blue}{maybe re-order to put the results up front and focus on sex ratio less.
-Somewhere around these first two paragraphs we should include our tight linkage results.
-At the moment it doesn't make total sense because it assumes that tighter linkage is always favoured unless there is haploid selection.}
-
-%MAIN RESULT
-Two predominant theories explaining the remarkably high frequency of transitions between sex-determination systems are sexually-antagonistic selection and sex ratio selection \citep[reviewed in][]{Blaser2012, vanDoorn2014re}.
-The former predicts that neo-sex-determining alleles can invade when they arise in closer linkage with a sexually-antagonistic locus \citep{vanDoorn:2007eu,vanDoorn:2010hu, Muralidhar2018}.
-The latter predicts that new sex-determining systems are generally favoured if they result in more equal sex ratios than the ancestral system. 
-%The latter predicts that neo-W alleles will invade an XY system when there is a male bias caused by haploid selection in males, and vice-versa, a neo-Y will invade a ZW system when there is a female bias caused by haploid selection in females \citep{Kozielska:2010vm,Ubeda:2015fx}.
-In contrast to these prevailing views, we show that selection (including sexually-antagonistic selection, overdominance, and/or ploidally-antagonistic selection) on loci tightly linked to the ancestral sex-determining region can favour trans-GSD transitions (XY to ZW or ZW to XY) to new sex-determining systems that are less closely linked to the selected loci (e.g., see Figure \ref{fig:SexAntagTighter}).
-Similarly, even when linkage is weak relative to selection, we show that %new sex-determining alleles are typically favoured if they are more closely linked to a locus under haploid selection (even in the absence of diploid sex differences), which is the only condition favouring cis-GSD transitions (XY to XY or ZW to ZW).
-%In addition, with haploid selection and weak selection, 
-trans-GSD transitions (XY to ZW or ZW to XY) can occur where the new sex-determining region is less closely linked to the locus under selection if there is haploid selection (e.g., Figures \ref{fig:Combination_Centimorgans} and \ref{fig:SexRatioBad}).
-%\textcolor{red}{need to mention sex ratio here}
-%Neo-W (neo-Y) alleles invade when their fitness in females (males) is greater than the mean fitness of females (males) under the ancestral sex-determination system and/or females (males) are the rarer sex.
-
-%TIGHT LINKAGE RESULTS
-%When the rate of recombination between the ancestral sex-determining locus and a locus under selection is small relative to the strength of selection (i.e., sex-linkage is tight, or selection is strong), heterogametic transitions (XY to ZW or ZW to XY) that reduce sex-linkage are possible, with or without haploid selection (Figures \ref{fig:SexAntagTighter} and \ref{fig:regionplots}).
-
-%The likelihoods of these transitions are driven by sex ratio selection, direct selection on alleles linked to the neo-sex-determining allele, the ability of the neo-sex-determining allele to avoid selection in one sex, and the ability of the neo-sex-determining allele to bring alleles on the sex-specific chromosome in the ancestor into the other sex (given that the neo-sex determining allele is epistatically dominant to its predecessor).
-
-%This possibility that looser sex-linkage could evolve, even in the absence of haploid selection (Figure \ref{fig:regionplot_2a}A), was overlooked in \cite{vanDoorn:2010hu}, likely because they did not explicitly consider the case of initially tight linkage between the \textbf{A} locus and the ancestral-SDR, which allows substantial differences in allele frequencies to build up \citep[$\hat{p}^\Hermaphrodite_{X} \neq \hat{p}_{Y}^\male$, equation \ref{eq:tightequil};][]{Lloyd1977,Otto2014}.
-%Interestingly, there is substantial overlap between the parameter space that allows both neo-W-$A$ and neo-W-$a$ haplotypes to spread in an XY system and that which selects for increased recombination between X and Y chromosomes \citep[e.g., compare gray region of Figure \ref{fig:regionplot_2a}A with coloured regions of Figure 2(a) in][]{Otto2014}.
-%This makes sense, as when both neo-W haplotypes can spread the neo-W can invade despite reducing sex-linkage, i.e., the rate of recombination between the sex-determining allele and the selected locus increases.
-%We further find that it is easier for a neo-W to invade 
-%\textcolor{red}{explain difference too?
-also explain why a neo-Y doesn't invade to reduce linkage despite selection for more recombination?
-mention something about haploid selection (Fig7B)?} \textcolor{blue}{maybe leave for now}
-
-%HAPLOID SELECTION CAN ACT LIKE SEXUALLY-ANTAGONISTIC SELECTION
-%It has previously been demonstrated that new sex-determining systems can evolve if there is genetic variation maintained by sexually-antagonistic selection \citep{vanDoorn:2007eu,vanDoorn:2010hu}. 
-%In particular, 
-%Under weak selection (or loose sex-linkage), transitions to new sex-determining systems can occur when they arise more closely linked to a sexually-antagonistic locus \citep{vanDoorn:2007eu,vanDoorn:2010hu}.
-%New sex-determining alleles are again favoured if they are more closely linked to a locus under haploid selection, which is the only condition favouring homogametic transitions (XY to XY or ZW to ZW).
-%HAPLOID SELECTION ALSO ALLOWS LOOSER LINKAGE TO EVOLVE
-%However, with haploid selection, heterogametic transitions (XY to ZW or ZW to XY) can occur even when the new sex-determining region is less closely linked to the locus under selection. 
-%Neo-W (neo-Y) alleles invade when their fitness in females (males) is greater than the mean fitness of females (males) under the ancestral sex-determination system and/or females (males) are the rarer sex.
-
-%With sexually-antagonistic selection (between diploid sexes) only, linkage between a selected locus and the sex-determining region strengthens associations between male beneficial alleles and the male-determining allele (Y or Z) and between female beneficial alleles and the female-determining allele (X or W).
-%Thus, the mean fitness of both males and females increases with closer linkage to the sex-determining region. 
-%Therefore, new sex-determining alleles only invade if they are more closely linked than the ancestral sex-determining region. 
-%However, if there is haploid selection on loci linked to an XY (ZW) sex-determining region, selection can maintain polymorphisms at which the product of the frequency of females (males) and the mean fitness of females (males) is lower than it would be without sex-linkage.
-%In these cases, unlinked neo-W (neo-Y) alleles can increase the frequency and/or fitness of the only sex they are found in, at a cost to the other sex, and invade despite lowering population mean fitness (Figure \ref{fig:Combination_MeanFit}).
-%\textcolor{red}{This is similar to mitochondria and male disease ...?}
-
-%%SEX-RATIO SELECTION
-%\textcolor{blue}{maybe drop paragraph?}
-%\textcolor{red}{I messed with the sex ratio selection paragraphs to tone down our "it doesn't matter" speech from before. Have at any amendments you'd like to make.}
-%Linkage between haploid selected loci and sex-determining regions cases biased zygotic sex ratios \citep{Hamilton:1967ts,Burt:2006,Field:2012fd,Field:2013cc}.
-%One might then expect Fisherian sex ratio selection to drive the spread of new sex-determining systems that bring the sex ratio closer to 50:50. 
-%Fisherian sex ratio selection follows from the fact that, for an autosomal locus, half of the genetic material is inherited from a male, and half from a female \citep{Fisher:1930wy,West:2009we}. 
-%Thus, if the population sex ratio is biased towards females, the average per-individual contribution of genetic material to the next generation from males is greater than the contribution from females (and vice versa for male-biased sex ratios).
-%Therefore, a mutant that increases investment in males will spread via the higher per-individual contributions made by males. 
-%%%That is, under Fisherian sex ratio selection, the success of a mutant relative to the non-mutant depends, in equal parts, on the contributions made by males and females to the next generation. 
-%An implicit assumption of Fisherian sex ratio selection is that the mutant allele is autosomal and has the same inheritance pattern as the non-mutant allele. 
-%The mutations we consider here, neo-sex-determining alleles, break this assumption. 
-%For example, the success of neo-Y/neo-W mutations depends only on the number of alleles contributed by males/females (Table \ref{tab:haplotype_growth}). 
-%In this respect, a neo-W is similar to a cytoplasmic element, which also does not experience selection to balance sex ratios \citep{Frank:1989vl,Werren:1998co,Chase:2007bf}.
-%Even mutants that are equally likely to be found in males or females, such as an environmental sex determination mutation (equation \ref{eq:lambda_ESD}), are not strictly autosomal if they determine sex.
-%Thus, despite the fact that sex ratio biases caused by gametic competition or meiotic drive have been shown to exert Fisherian sex ratio selection on various autosomal modifiers \citep{Stalker:1961th,Smith:1975ft,Frank:1989vl,Hough:2013uo,Ubeda:2015fx, Otto:2015va}, we do not find evidence of Fisherian sex ratio selection acting during invasion by neo-sex-determination systems (e.g., see Figure \ref{fig:Combination_Turnover} and \citealt{Ubeda:2015fx}, in which a neo-Y invades despite biasing sex ratios).
-
-%Sex ratio biases caused by gametic competition or meiotic drive have been shown to exert Fisherian sex ratio selection on various autosomal \citep{Stalker:1961th,Smith:1975ft,Frank:1989vl,Hough:2013uo,Ubeda:2015fx, Otto:2015va} and sex-linked \citep{Kozielska:2010vm} modifiers.
-We find that the spread of neo-sex-determining systems cannot be simply predicted from their effect on the sex ratio. 
-On one hand, sex ratio biases caused by haploid selection can facilitate trans-GSD transitions or GSD-ESD transitions between sex-determining systems. 
-For instance, alleles favoured by haploid selection in males often become associated with the Y, which leads to a male-biased zygotic sex ratio.
-This male bias increases the potential for a neo-W to invade (Table \ref{tab:haplotype_growth}), which can equalize the sex ratio \citep[e.g., see Figure \ref{fig:SexRatioBad}B, for related examples see][]{Kozielska:2010vm}.
-%We find that sex ratio biases caused by haploid selection can also affect transitions between sex-determining systems (e.g., see $\zeta$ terms in Table \ref{tab:haplotype_growth}). 
-%However, the neo-W may not equalize the sex ratio (e.g., if the driving allele also drives in females or affects competition among eggs)
-On the other hand, sex ratio selection can be overwhelmed by additional selective effects, preventing a neo-W or ESD allele from invading, even if it would balance the sex ratio (e.g., when selection acts in opposite directions in male and female diploids, Table \ref{tab:specialcases}).
-%and equalizing the sex ratio.
-Indeed, transitions between sex-determining systems can generate stronger sex ratio biases \citep[e.g., Figure \ref{fig:SexRatioBad}A and step 1 in][]{Ubeda:2015fx}.
-%For example, where a neo-Y invades and is linked with a locus that experiences haploid selection in male gametes, the sex ratio evolves to become biased \citep[e.g., see Figure \ref{fig:SexRatioBad}A and step 1 in][]{Ubeda:2015fx}.
-%For example, in an ancestral ZW system, haploid selection in males can allow a linked neo-Y to invade, despite the fact that it creates a male-biased sex ratio because the neo-Y becomes associated with the driven allele (Figure \ref{fig:SexRatioBad}A).
-%\textcolor{blue}{and figure 1, where the end of one panel is the same as the beginning of another, however, this figure may change).}
-%What we would like to stress is that sex ratio selection alone cannot predict when new sex-determining systems can evolve.
-Significantly, with weak selection, we find that there is no difference in conditions allowing XY to ZW and ZW to XY transitions, indicating that sex chromosome transitions are not predominantly predicted by their effect on the sex ratio (i.e., the sex ratio bias created by male haploid selection facilitates the spread of a neo-W into an XY system to the same degree that male haploid selection drives the spread of a neo-Y into a ZW system with a 1:1 sex ratio).
-%An asymmetry can develop when sex-linkage is tight (e.g., Figure \ref{fig:Combination_Centimorgans} near -25cM and 25cM) but under most circumstances we do not predict asymmetry between XY to ZW and ZW to XY transitions despite the presence/absence of sex ratio selection.
-Thus, haploid selection can favour trans-GSD transitions both via sex ratio selection and via selection on alleles associated with the neo-sex-determining allele, and these selective pressures are often predicted to be of equal magnitude.
-%\textcolor{red}{Maybe try to emphasise surprisingness in the paragraph more? e.g., how wrong you'd be if you assumed selection to equalise sex ratios, or it this implied?}
-%\textcolor{blue}{nice, pretty subtle argument but I think that's a good job.}
-
-%Previous studies where ESD is favoured have typically assumed that environmental conditions (e.g., maternal condition, mate quality, age, or host size) can differentially affect the fitness of males versus females such that ESD invades because it allows sex determination to depend on the environment \citep[reviewed in][]{Charnov:1982wg,Bull:1983vi,West:2009we}.
-
-%WHY SEX-RATIO BIASES CAN BE FAVOURED
-%We note two other ways in which sex determination has been shown to relate to zygotic sex ratios.
-%Firstly, female-biased sex ratios can be favoured when there is local mate competition, where all matings are between siblings and assuming one male can inseminate many females \citep{Hamilton:1967ts}.
-%Therefore, with local mate competition, feminizing mutations can spread because they bias the sex ratio towards females \citep{Wilson:1981vm,Vuillleumier:2007bh}. 
-%Secondly, environmental conditions (e.g., maternal condition, mate quality, age, or host size) can differentially affect the fitness of males versus females such that the optimal allocation to males/females depends on the environment \citep{Trivers:1973wb,Charnov:1977tx,Charnov:1982wg}.
-%In such cases, flexible sex-determination systems may evolve in order to allow the zygotic sex ratio to be determined in a way that depends on the environment \citep{Charnov:1977tx,Werren:1984tl,Pen:2010kk}.
-%In this study, we do not consider environmental condition dependence or local mate competition \citep[reviewed in][]{Charnov:1982wg,Bull:1983vi,West:2009we}.
-
-%HOW TO TEST EMPIRICALLY
-%\textcolor{blue}{I think Sally was sceptical of this idea. i.e., if the second term in \ref{eq:lambda_neoW} is negative, then get less transitions with haploid selection included, right? }
-%\textcolor{red}{Yeah, and given that only 1/2 the discovered plant sex chromosomes are hetermorphic and there are so few plant sex chromosomes to begin with (Charlesworth 2016 Annual Review Plant Biology), might it be the case that haploid selection is constraining things?
-perhaps we could think of some particular forms of haploid selection that might be common and give their predicted effects, or just say some things that are possible with haploid selection that are not without it -- if there are any.
-just looking at eq 3 though, its gonna be hard to get a low freq of A on the Y if haploid selection in males favours A, i.e., it should often be positive when there is no female haploid selection, right?}
-%\textcolor{blue}{That sounds right to me and is backed up by equation \eqref{eq:freq_diffs}.
-It may be technically possible for that term to be negative though.
-Re: hetermorphism, I see that as a slightly different issue.
-It's thought that haploid selection may prevent deletions from becoming fixed on the Y, like in the Crowson (2017) paper.
-%I think the issue of `why so few plant sex chromosomes' is partly an issue of detection and also `why so much hermaphroditism'.
-Is it possible that the ESD results could show selective forces that also favour transitions from dioecy to hermaphroditism?
-I think so.
-Our ESD mutant produces 1/2 females and 1/2 males whereas a hermaphrodite invests roughly equally in each type of gamete produced.
-We don't consider the forces that are usually thought to be involved in these transitions though (inbreeding depression, reproductive assurance and possibly others?).
-}
-%Taken at face value, our results indicate that transitions in heterogametey (XY to ZW or vice versa) are more likely to be favoured by selection if there is selection upon both haploid and diploid genotypes rather than diploid selection alone ().
-%This prediction could be examined using a suitable proxy for haploid selection, for example, \cite{Lenormand:2005vb} use the outcrossing rate in plants as a proxy for the strength of pollen competition.
-%In animals, one might expect gametic competition to be stronger in species where sperm is required to live for a long time after spermatogenesis because transcripts shared during spermatogenesis may become depleted, revealing the haploid phenotype of the sperm \citep{Immler:2014im}.
-%Given the caveats mentioned above about the form of meiotic drive modelled, we would also expect that heterogametic transitions in sex determination would be more common in clades where there is meiotic drive.
-
-%Together, our models demonstrate novel selective forces that favour heterogametic transitions (XY to ZW or ZW to XY). 
-%One common prediction is therefore that heterogametic transitions are favoured under a wider range of conditions than homogametic transitions. 
-%However, heterogametic transitions are not clearly in excess.
-For example, \citet{Vicoso:2015hf} found a dozen sex chromosome configurations among Dipteran species but only one transition between male and female heterogametey.
-%While our models examine the selective forces that favour the spread of new sex-determining regions, observed transitions could also reflect the mutation rate for neo-Y versus neo-W alleles (e.g., duplications of the ancestral sex determining region could be particularly likely).
-%In addition, heterogametic transitions could be limited due to the production of YY males or WW females (see below). 
-%Alternatively, it might be useful to compare clades that are expected to differ in the strength of haploid selection (e.g., plants are thought to experience more selection during their multicellular haploid stage
-
-%HAPLOID SELECTION (genomic location of haploid selected loci and comparative patterns) 
-We have shown that the spread of new sex determination systems can be driven by loci experiencing haploid selection. 
-%Our results suggest that haploid selected loci that have been involved in driving turnovers between sex-determination systems could occur around the ancestral- or novel-sex-determining regions. 
-%Our results suggest that polymorphic loci that are ancestrally sex-linked and under sex-specific selection could also drive heterogametic transitions between sex-determination systems. 
-%As with sexually-antagonistic selection, the presence of haploid selected loci around ancestral- or novel-sex-determining regions could support their role in sex chromosome turnover.
-In agreement with this hypothesis, a recent transcriptome analysis in \textit{Rumex} shows that Y-linked genes have higher expression in haploid pollen than autosomal genes \textcolor{red}{(check this is accurate)}.
-Interestingly, haploid-expression is also more common on the autosome that is orthologous to the sex chromosomes in closely related species suggesting that new sex chromosomes may have been favoured through their association with haploid selected alleles on these chromosomes \textcolor{red}{(Sandler et al., 2018, Personal Communication)}.
-%maybe add a flag here for switching to clade-level expectations:
-In general, we predict that haploid selection increases lability of sex-determination systems, particularly because haploid selection can cause transitions that increase or decrease sex-linkage (e.g., the final state of the red line in Figure \ref{fig:SexRatioBad}B is the starting state in Figure \ref{fig:SexRatioBad}A).
-Turnovers driven by haploid selection may help to explain the relative rarity of heteromorphic sex chromosomes in plants, which are thought to experience more selection during their multicellular haploid stage.
-If haploid selection is strong but selective differences between male and female diploids are weak, we find that trans-GSD transitions (XY to ZW or ZW to XY) are favoured more strongly than cis-GSD transitions, with transitions to ESD intermediate (e.g., with $|D^\male - D^\female| << |\alpha_\Delta^\male - \alpha_\Delta^\female + t^\male - t^\female|$ we have $\lambda_{W',XY} > \lambda_{Y',XY}$; Equations \ref{eq:lambda_neoW} and \ref{eq:freq_diffs}).
-Among the relatively few dioecious clades in which multiple species have well characterized sex chromosomes \citep{Ming:2011iy}, trans-GSD transitions have been inferred in \textit{Silene} subsection \textit{Otites} \citep{Slancarova:2013dq} and in \textit{Salicaceae} \citep{Pucholt2015,Pucholt2017}.
-%Potentially, successive heterogametic transitions between master regulators of sex-determination could be inferred from careful examination of the molecular pathways by which sex is determined. 
-%Our predictions could also be examined using a suitable proxy for haploid selection, for example, \cite{Lenormand:2005vb} use the outcrossing rate in plants as a proxy for the strength of pollen competition.
-Assuming that transitions from dioecy to hermaphroditism (equal parental investment in male and female gametes) are favoured in a similar manner to the ESD examined here (equal probability of zygotes developing as males or females), our results suggest that competition during the haploid stage could also drive transitions between dioecy and hermaphroditism, which are frequent in plants \citep{Kafer2017, Goldberg2017}.
-%In animals, one might expect gametic competition to be stronger in species where sperm is required to live for a long time after spermatogenesis because transcripts shared during spermatogenesis may become depleted, revealing the haploid phenotype of the sperm \citep{Immler:2014im}.
-%We would also expect that heterogametic transitions in sex determination would be more common in clades where there is meiotic drive.
-
-%IDENTIFICATION OF LOCI IN GENOMIC LOCATIONS THAT IMPLICATE THEM IN SEX-CHROMOSOME TURNOVER
-%The hypotheses presented here can be empirically investigated in a similar manner to the idea that transitions between sex-determining systems are favoured by linkage to sexually-antagonistic variation.
-%In the case of sexually-antagonistic variation, one supporting observation is that genes expected to be under sexually-antagonistic selection (e.g., those causing bright male colouration) have been found on recently derived sex chromosomes \citep{Lindholm:2002dw,Tripathi:2009cw,Ser:2010iq}.
-In support of their role in sex chromosome turnover, genes expected to be under sexually-antagonistic selection (e.g., those causing bright male colouration) have been found on recently derived sex chromosomes \citep{Lindholm:2002dw,Tripathi:2009cw,Ser:2010iq}.
-Our results show, however, that tight ancestral-linkage of polymorphic loci can also drive trans-GSD transitions. 
-In addition, we find that polymorphic sex determining systems (X, Y, W, and Z alleles all present) can be maintained when a selected locus is tightly linked to the ancestral sex-determining system (e.g., Figures \ref{fig:freqAll}B and \ref{fig:freqAll}C), which is not possible with loose linkage \citep{vanDoorn:2010hu}.
-%As noted by \citet{vanDoorn:2010hu}, it would be prudent to compare closely related clades in order to determine whether observed polymorphisms predate a transition in sex-determination or arose afterwards.
-%, particularly because sex-linkage allows sexually-antagonistic selection to maintain polymorphisms under a different and larger parameter space \citep{Rice:1987hs,Jordan:2011fj}.
-For example, our results suggest a potential mechanism maintaining multiple sex determining alleles in the platyfish (\textit{Xiphophorus maculatus}), in which X,Y, and W alleles segregate at one locus (or two closely-linked loci) near to potentially sexually-antagonistic genes for pigmentation and sexual maturity \citep{Kallman1965,Kallman1968, Volff2001, Schultheis2006}.
-Several rodent species also maintain feminizing alleles along with the ancestral X and Y sex-determination alleles \citep[reviewed in][]{Fredga1994}. 
-For example, in nine \textit{Akadon} species, it appears that male-determining-\textit{sry} expression is suppressed by an autosomal feminizing allele, creating XY females \citep{Bianchi2002,Sanchez2010}, which have increased fitness relative to XX females \citep{Hoekstra2001}.
-In \textit{Mus microtoides}, females can have XX, XX$^\ast$ or X$^\ast$Y genotypes \citep{Veyrunes2010}. 
-Previous theory would predict that the X$^\ast$ chromosome (or the autosome it is fused to) harbours female beneficial alleles, driving its spread. 
-However, XX and XX$^\ast$ females have similar fitness, whereas X$^\ast$Y female fitness is enhanced \citep{Saunders2014,Saunders2016, Veyrunes2017}.
-Although Y-linkage of female-beneficial alleles is counterintuitive, our tight linkage model suggests that it can be stably maintained and then favour new feminizing mutations, which is a parsimonious explanation for the spread of feminizing alleles in these rodent species.
-
-%Limitation 1: DEGENERATE Y
-We note that we assume that sex-determining alleles do not experience direct selection except via their associations with sex and selected alleles.
-However, in some cases, there may be significant degeneration around the sex-limited allele (Y or W) in the ancestral sex-determining region because recessive deleterious mutations and/or deletions accumulate around the Y or W sex-determining regions \citep{Rice:1996ke,Charlesworth:2000cc,Bachtrog:2006ed,Marais:2008hm}.
-During trans-GSD transitions (XY to ZW or ZW to XY), but not cis-GSD transitions (XY to XY or ZW to ZW), any recessive deleterious alleles linked to the Y or W are revealed to selection in YY or WW individuals \citep{Bachtrog:2014bx}.
-This phenomenon was studied by \citet{vanDoorn:2010hu}, who found that degeneration can prevent fixation of a neo-W or a neo-Y allele, leading to a mixed sex-determination system where the ancestral and new sex-determining loci are both segregating.
-However, they noted that very rare recombination events around the ancestral sex-determining region can allow these trans-GSD transitions to complete.  
-%While not explicitly studied, we also predict that Y or W degeneration would prevent fixation of the new sex-determining genes considered here.
-Degeneration around the Y or W could explain why trans-GSD transitions are not observed to be much more common than cis-GSD transitions despite the fact that our models demonstrate that they are favoured under a wider range of conditions, especially with haploid selection.
-For example, \citet{Vicoso:2015hf} found a dozen sex chromosome configurations among Dipteran species but only one transition between male and female heterogamety.
-
-%Limitation 3: don't consider m alleles with similar k to ancester, no ancestral ESD considered
-In this study, we have only considered neo-sex-determining alleles of large effect. 
-However, we expect similar selective forces to act on masculinizing/feminizing alleles of weaker effect. 
-For example, \citet{Muralidhar2018} consider small effect masculinizing/feminizing alleles within a threshold model of sex determination, finding that they can be favoured when linked to loci that experience sexually-antagonistic selection.
-These results echo those for large-effect neo-Y/neo-W alleles \citep{vanDoorn:2007eu,vanDoorn:2010hu}.
-Finally, while we have considered cis-GSD, trans-GSD, and GSD to ESD transitions, we have not explicitly considered ESD to GSD transitions. 
-Recent models of ESD to GSD transitions \citep{Ubeda:2015fx,Muralidhar2018} show that that neo-Y/neo-W alleles can be favoured when they arise near to haploid and/or diploid selected loci, which also occurs in our model.
-
-%Limitation 2: TWO ALLELE DRIVE
-%Another simplification that we made is that meiotic drive involves only a single locus with two alleles. 
-%However, many meiotic drive systems involve an interaction with another locus at which alleles may `suppress' the action of meiotic drive \citep[][]{Burt:2006,Lindholm:2016cw}.
-%Thus, the dynamics of meiotic drive alleles can be heavily dependent on the interaction between two loci and the recombination rate between them, which in turn can be affected by sex-linkage if there is reduced recombination between sex chromosomes \citep{Hurst:1991uh}.
-%Furthermore, in some cases, a driving allele may act by killing any gametes that carry a `target' allele at another locus, in which case there can be fertility effects that alter the equilibrium frequency of a meiotic drive allele \citep{Holman:2015en}.
-%In polygamous mating systems, the intensity of pollen/sperm competition can depend on the density of males available to donate pollen/sperm, which can itself depend on the sex ratio \citep{Taylor:2002wu}.
-%In terms of our model, this implies that the strength of gametic competition ($t^\male$) may both determine and be determined by the sex ratio. 
-%How the evolution of new sex-determining mechanisms could be influenced by two-locus meiotic drive and/or by ecological feedbacks under different mating systems remains to be studied.
-
-%\textcolor{blue}{similarly, this part doesn't discuss our new tight linkage results or our new perspective on sex ratios.}
-%CONCLUSION
-We have shown that tight sex-linkage and haploid selection can drive previously unexpected transitions between sex-determination systems.
-In particular, both can select for neo-sex-determining loci that are more loosely linked. 
-In addition, haploid selection can cause transitions analogous to those caused by purely sexually-antagonistic selection, eliminating the need for differences in selection between male and female diploids.
-We conclude that haploid selection should be considered as a pivotal factor driving transitions between sex-determination systems. 
-Perhaps counterintuitively, transitions involving haploid selection can be driven by sex ratio selection or cause sex ratio biases to evolve and Fisherian sex ratio selection is not an overwhelming force.
-Overall, our results suggest several new scenarios under which new sex-determination systems are favoured, which could help to explain why the evolution of sex-determination systems is so dynamic. 
-%Further, we have shown the way in which transitions are affected by haploid selection is not intuitively obvious. 
-%Firstly, sex-specific haploid selection affects turnovers between sex-determination systems in a manner that is qualitatively different from diploid sex-specific selection. 
-%In particular, closer linkage between a sex-determining locus and a selected locus is not always favoured during heterogametic transitions when there is haploid selection. 
-%Secondly, even though haploid selection is a source of zygotic sex ratio biases, in our models Fisherian sex ratio selection does not have good explanatory power in determining whether various sex-determination systems evolve.
-%This result is surprising given that sex ratios are ultimately determined via the sex-determination system, and leads us to the conclusion that three selective forces -- haploid, diploid, and sex ratio selection -- should all be considered when exploring transitions between sex-determination systems.
-
-\bibliographystyle{amnatnat.bst}
-\bibliography{sex_chromosomes.bib}
-
-\newpage
-%\section*{Figures}
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Tighter linkage allows looser sex-linkage to evolve, even in absence of haploid selection
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\includegraphics[width=\linewidth]{PositionPlot_SexAntagTighter}
-%\caption{
-%In the absence of haploid selection, tight linkage allows looser sex-linkage to evolve in transitions between XY and ZW systems.
-%In panel A, linkage is loose enough relative to selection that the weak selection analytical results hold, and a neo-W can only invade when it is more tightly linked with the selected locus ($R<r$; shaded region).
-%In panel B, linkage is tight enough relative to selection that the weak selection analytical results do no hold, and a neo-W can only invade even when it is less tightly linked with the selected locus ($r<R$; unshaded region).
-%Parameters: $w_{AA}^\female = w_{aa}^\male = 1.05$, $w_{aa}^\female = w_{AA}^\male = 0.85$, $w_{Aa}^\female = 1$, $w_{Aa}^\male = 0.925$, $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
-%}
-%\label{fig:SexAntagTighter}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Both neo-W haplotypes can spread, in the absence of haploid selection, when there is overdominance
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\includegraphics[width=0.45\linewidth]{regionplot_2a}
-%\includegraphics[width=0.45\linewidth]{regionplot_2a_Color_Ya_Either}
-%\includegraphics[width=0.45\linewidth]{BothWsInvade_Overdominance}
-%\caption{
-%In the absence of haploid selection, both neo-W haplotypes can spread in an XY system when there is overdominance.
-%Panel A shows the range of male homozygote fitnesses that allow either neo-W haplotypes to invade.
-%The blue region overlaps with a red region, where both neo-W haplotypes can invade a population with $A$ fixed on the X and $a$ fixed on the Y.
-%The green region (overlapped by the orange region) is where both neo-W haplotypes can invade a population with $a$ fixed on the Y and a polymorphic X.
-%The orange region (outside the green region) is where only the neo-W-$A$ haplotype can invade
-%Panel B shows the temporal dynamics of the invading neo-W haplotypes; in this case the neo-W does not fix, leading to a polymorphic sex-determining system.
-%Asterisk in panel A marks parameter values ($w_{aa}^\male=0.15$, $w_{AA}^\male=0.1$) used in panel B.
-%Parameters: $w_{AA}^\female = w_{aa}^\female = 0.6$, $w_{Aa}^\Hermaphrodite = 1$, $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$, $r=R=0$.
-%\textcolor{red}{make two more temporal plots with visible asterisks in green and orange regions; figure out better colours to show possibilities}
-%}
-%\label{fig:BothOverdominance}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%With weak selection, a less tightly linked neo-W can invade an XY system when there is some haploid selection, and this invasion decreases mean diploid fitness
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\includegraphics[width=0.5\linewidth]{Loose_Fitness_Decline}
-%\caption{
-%With weak selection, a less tightly linked neo-W can invade (and fix in) an XY system (causing the Y to fix in females) when there is some haploid selection (blue and green curves in panel A), and this invasion decreases mean diploid fitness (green and blue curves in panel B).
-%Parameters: $s^\Hermaphrodite = 0.2$, $h^\Hermaphrodite = 0.7$, $t^\Hermaphrodite = \alpha^\male_\Delta = 0$, $\alpha^\female_\Delta = -0.1$, $r=1/10$.
-%}
-%\label{fig:LooseDecline}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%A neo-W can invade an XY system under a large number of selective regimes
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\includegraphics[width=0.5\linewidth]{PositionPlot_4}
-%\caption{
-% A neo-W can invade an XY system under a large number of selective regimes.
-%In panel A, there is no haploid selection ($t^\Hermaphrodite = \alpha^\Hermaphrodite_{\Delta} = 0$) and selection in diploids is sexually antagonistic ($s^\male = -s^\female = 1/10$, $h^\male = 1-h^\female = 3/10$), in which case the neo-sex-determining allele can only invade if it is more closely linked to the selected locus ($R<r$, gray region; but see Figure \ref{fig:SexAntagTighter}B for the case of very tight linkage).
-%In panel B, male drive ($\alpha^\male_{\Delta} = -1/20$, $t^\Hermaphrodite = \alpha^\female_{\Delta} = 0$) opposes selection in diploids (no sex-differences: $s^\Hermaphrodite = 1/10$, $h^\Hermaphrodite = 7/10$), in which case the neo-sex-determining allele can invade regardless of linkage.
-%In panel C, haploid competition in males ($t^\male = -1/10$, $t^\female = \alpha^\Hermaphrodite_{\Delta} = 0$) opposes selection in diploids (sex-differences: $s^\male = 3 s^\female = 3/20$, $h^\Hermaphrodite = 7/10$), in which case the neo-sex-determining allele can once again invade regardless of linkage.
-%We use Haldane's map function \citep[Equation 3 in ][]{Haldane1919} to convert from map distance (centiMorgans, cM) to the probability of recombination (an odd number of cross-over events).   
-%}
-%\label{fig:Combination_Centimorgans}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Sex ratio selection is not a good predictor of neo-W invasion into an XY system
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\includegraphics[width=\linewidth]{Combination_Turnover_Ratio}
-%\caption{
-%Sex ratio selection alone is not a good predictor of turnover between sex-determining systems.
-%In panels A and C, male drive in an ancestral XY system causes a male bias, allowing a neo-W to invade and fix (causing the Y to fix in females), which balances the sex ratio (it also avoids selection in males, and thus makes better females in this case of sex-specific ploidally-antagonistic selection).
-%In panels B and D, male drive in an ancestral ZW system has no affect on the sex ratio, yet a neo-Y can invade and fix (causing the W to fix in males) because it becomes linked with the driving allele, and this imparts a sex ratio bias.
-%Parameters:  $s^\female =s^\male = 0.2$, $h^\female = h^\male = 0.7$, $t^\female = t^\male = \alpha^\male_\Delta = 0$, $\alpha^\female_\Delta = -1/10$, $r=1/20$.
-%}
-%\label{fig:SexRatioBad}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Haploid selection can lead to polymorphic SD systems 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\includegraphics[width=\linewidth]{Polymorphic}
-%\caption{
-%Tight linkage (relative to selection) and/or haploid selection can cause stable polymorphic sex-determining systems.
-%In panel A, there is strong overdominance in both sexes and no haploid selection  (parameters as in Figure \ref{fig:BothOverdominance}B with $r = 1/10$), in which case a neo-W can invade regardless of sex-linkage, but cannot not fix (i.e., the Y does not fix in females, and X, Y, W, and Z all segregate at equilibrium).
-%In panel B, there is sex-antagonistic selection at the diploid stage and drive in females (parameters as in Figure \ref{fig:SexAntagTighter} with $\alpha^\female_\Delta = 1/20$ and $r = 1/10$), in which case a sufficiently tightly linked neo-W can invade ($R<\sim r$), but only fixes if $R=0$.
-%}
-%\label{fig:Polymorphism}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%CYCLES!
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\includegraphics[width=0.5\linewidth]{BothWsInvade_Overdominance_Cycles}
-%\caption{
-%Thought I'd show this just for fun (not for publication).
-%}
-%\label{fig:Cycles}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Heterogametic transitions with/without sex ratio change
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\begin{tikzpicture}[remember picture]
-%	\node[] (plot) {\includegraphics[width=\linewidth]{Combination_Turnover}};
-%	\node[above = 0cm of plot, xshift = -70] () {$r=0.5$, $R=0.05$};
-%	\node[above = 0cm of plot, xshift = 120] () {$r=0.05$, $R=0.5$};
-%	\node[left = 0cm of plot, yshift = 105, rotate = 90] () {XY $\rightarrow$ ZW};
-%	\node[left = 0cm of plot, yshift = -20, rotate = 90] () {ZW $\rightarrow$ XY};
-%\end{tikzpicture}
-%\caption{
-%Heterogametic transitions from XY to ZW sex determination (neo-W frequency shown by black lines, panels A and B) or from ZW to XY (neo-Y frequency shown by black lines, panels C and D) occur similarly regardless of sex ratio biases present before (B versus D) or after (C versus A, dashed lines show male frequency).
-%During invasion by a neo-ZW sex-determination system (A and B), the ancestral Y fixes in both males and females (blue and red lines). 
-%Similarly, the ancestral W allele fixes in males and females (blue and red lines) during a ZW to XY transition. 
-%In this plot, there is no gametic competition ($t^\female=t^\male=0$) and meiotic drive occurs during male meiosis only ($\alpha^\female_{\Delta}=0$, $\alpha^\male_{\Delta}=-1/5$).
-Therefore, sex ratio biases can only arise when the \textbf{A} locus is linked to an XY sex-determining locus.
-%In panels A and C, the neo-sex-determining locus is more closely linked to the \textbf{A} locus than the ancestral sex-detemining region ($r=1/2$, $R=1/20$) such that a neo-Y can caused biased sex ratios (panel C).
-%In panels B and D, the ancestral sex-determining locus is more closely linked to the \textbf{A} locus than the neo-sex-detemining locus ($r=1/20$, $R=1/2$). 
-%Therefore, an ancestral XY sex determination can have a biased zygotic sex ratio that becomes unbiased after an unlinked neo-W invades (B). 
-%However, in panel D, a unlinked neo-Y invades an ancestral ZW sex-determination system in a similar manner but no biases to the zygotic sex ratio occur. 
-%With diploid selection alone, neo-sex-determining loci do not spread if they are less closely linked to the \textbf{A} locus than the ancestral sex-determining locus (see equation \eqref{eq:lambda_neoW} and Figure \ref{fig:Combination_Centimorgans}A).
-%In this plot there are no sex differences in selection and an equilibrium is maintained because selection in diploids opposes meiotic drive, $s^\female =s^\male = 1/5$, $h^\female = h^\male = 7/10$.
-%\textcolor{red}{Aesthetic adjustments: 
-%%Could add titles to the columns/rows: neo-W for row 1, neo-Y for row 3, $r=0.5$, $R=0.05$ for column 1 and $r=0.05$, $R=0.5$ for column 2. 
-%%Could adjust padding (too much whitespace where there is no axis label). 
-%%It also seems could increase ratio of font size relative to plot size to make figure more compact. 
-%%Matt - could you uncomment the line legends in the Mathematica file (function not included in my Mathematica version).
-%Add chromosome cartoons to depict recombination rates?
-%}
-%}
-%\label{fig:Combination_Turnover}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Heterogametic transitions with/without sex ratio change
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\begin{tikzpicture}[remember picture]
-%	\node[] (plot) {\includegraphics[width=\linewidth]{Combination_Turnover_Ratio}};
-%	\node[above = -1cm of plot, xshift = -100] () {XY $\rightarrow$ ZW};
-%	\node[above = -1cm of plot, xshift = 90] () {ZW $\rightarrow$ XY};
-%\end{tikzpicture}
-%\caption{
-%%\textcolor{red}{Is this what Sally was thinking?}
-%%\textcolor{blue}{I think this works but I'm confused as to why the speed of spread should be so much different for XY and ZW here.
-Figure \ref{fig:Combination_Turnover} and \ref{fig:Combination_Centimorgans} suggests that there's not much difference between XY->ZW and ZW->XY.
-Maybe we should just stick with the 4 cases in figure \ref{fig:Combination_Turnover}.
-}
-%%\textcolor{red}{i messed up and had $r=0.5$ instead of $r=0.05$ for B and D. haven't fixed fitness plot below.}
-%Heterogametic transitions occur (panels A and B) regardless of sex ratio biases (panels C and D).
-%A neo-W invades (panel A) and equalizes the male-biased sex ratio (panel C) that was caused by meiotic drive in males.
-%A neo-Y invades (panel B) a population with an equal sex ratio. 
-%With any amount of linkage ($R<1/2$), the neo-Y becomes associated with the driving allele in males, and in the end causes a male bias.
-%Parameters: $s^\female = s^\male = 1/5$, $h^\female = h^\male = 7/10$, $t^\female = t^\male=0$, $\alpha^\female_\Delta = 0$, $\alpha^\male_\Delta = -1/5$, $r = 1/20$.
-%}
-%\label{fig:Combination_Turnover_Ratio}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%Changes in mean fitness
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\begin{tikzpicture}[remember picture]
-%	\node[] (plot) {\includegraphics[width=\linewidth]{Combination_Fitness_Rec}};
-%	\node[above = -1cm of plot, xshift = -100] () {XY $\rightarrow$ ZW};
-%	\node[above = -1cm of plot, xshift = 90] () {ZW $\rightarrow$ XY};
-%\end{tikzpicture}
-%\caption{
-%\textcolor{red}{This complicated thing matches the plot above. I don't think we want to include it...?}
-%}
-%\label{fig:Combination_Fitness_Rec}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Changes in mean fitness
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\begin{tikzpicture}[remember picture]
-%	\node[] (plot) {\includegraphics[width=\linewidth]{Combination_MeanFit}};
-%	\node[above = 0cm of plot, xshift = -70] () {$r=0.5$, $R=0.05$};
-%	\node[above = 0cm of plot, xshift = 120] () {$r=0.05$, $R=0.5$};
-%	\node[left = 0cm of plot, yshift = 105, rotate = 90] () {XY $\rightarrow$ ZW};
-%	\node[left = 0cm of plot, yshift = -20, rotate = 90] () {ZW $\rightarrow$ XY};
-%\end{tikzpicture}
-%\caption{
-%Changes in mean diploid fitness of males (blue lines), females (red lines), and the entire population (black lines) during the transitions between sex-determination systems shown in Figure \ref{fig:Combination_Turnover}.
-%Here mean diploid fitness of a particular sex is its mean diploid viability fitness times twice its frequency in the population, to capture the fact that epistatically dominant sex-determining alleles can also invade because they selfishly make more of the sex they are in.
-%The mean fitness of females increases during the spread of neo-W alleles (A and B) and the mean fitness of males increases during the spread of neo-Y alleles (C and D). 
-%However, when a neo-sex determining system evolves that is less closely linked to a locus under selection (B and D), population mean fitness decreases. 
-%%\textcolor{red}{
-%%Could add titles to the columns/rows: neo-W for row 1, neo-Y for row 3, $r=0.5$, $R=0.05$ for column 1 and $r=0.05$, $R=0.5$ for column 2. 
-%%%\& possibly adjust padding (too much whitespace?). 
-%%%Matt - could you uncomment the line legends in the Mathematica file (function not included in my Mathematica version).
-%%}
-%%\textcolor{red}{I'm still confused why male and female mean fitnesses aren't normalized by their frequency.
-I'm not sure we should be calling them means without this normalization step.
-Or we should justify this by saying that mean fitness also has something to do with the number of a sex, i.e., multiply *real* mean fitness in females by freqfemale/(1/2)?
-See the next figure for what happens when we do normalize.}
-%\textcolor{blue}{I think we should give this plot showing (male mean fitness * freq males) and (female mean fitness * freq females), without multiplying by 2 (leave off black lines, population mean fitness).
-%We could also re-plot the sex ratios on this same scale. 
-%The plot below, `adjusted for sex ratio', could then go in the appendix.
-The point is that neo-W (neo-Y) can invade when the frequency of females (males) multiplied by their mean fitness increases.
-}
-%}
-%\label{fig:Combination_MeanFit}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Changes in mean fitness corrected for sex ratio
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\begin{tikzpicture}[remember picture]
-%	\node[] (plot) {\includegraphics[width=\linewidth]{Combination_MeanFit_Corrected}};
-%\end{tikzpicture}
-%\caption{
-%\textcolor{red}{Last plot with mean fitness of sexes corrected for sex ratio. Could add to previous plot with dashed lines?}
-%}
-%\label{fig:Combination_MeanFit_Corrected}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%Chromosomal Positions
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%%\includegraphics[width=\linewidth]{Combination_Centimorgan}\\
-%%\includegraphics[width=\linewidth]{PositionPlot}\\
-%\begin{tikzpicture}[remember picture]
-%%	\node[] () {\includegraphics[width=\linewidth]{PositionPlot}};
-%	\node[] () {\includegraphics[width=0.5\linewidth]{PositionPlot_2}};
-%%	\node[anchor=east] at (0, 1.5) {\footnotesize diploid sex-antagonism}; %, $s^\male s^\female < 0$};
-%%	\node[anchor=east] at (6.5, 1.5) {\footnotesize haploid sex-antagonism}; %, $s^\male s^\female > 0$};
-%%	\node[anchor=east] at (0, -3) {\footnotesize male drive (ploidy-antagonism)}; %, $s^\male < s^\female$};
-%%	\node[anchor=east] at (6.5, -3) {\footnotesize find something interesting to plot};%, $s^\female < s^\female$};
-%%	\node[anchor=center] at (-1.3, 4.25) {\scriptsize tighter sex-linkage};
-%%	\node[anchor=center] at (2.45, 3.5) {\scriptsize ancestral SDR};
-%%	\draw[->,thick] (2.45, 3.25) -- (2.45, 2.5);
-%%	\node[anchor=center] at (-1.4, -0.25) {\scriptsize novel SDR};
-%%	\draw[->,thick] (-1.4, -0.5) -- (-1.4, -1);
-%\end{tikzpicture}
-%\caption{
-% A neo-W can invade an XY system under a large number of selective regimes.
-%%Invasion fitness of a neo-sex-determining allele against the relative genomic location of a locus under direct selection. 
-%% (neo-Y invading ZW in black, neo-W invading XY in red)
-%%The ancestral sex-determining locus is located at -25 and the novel sex-determining locus is located at 25. %and that there is a polymorphism at the \textbf{A} locus maintained by selection.
-%%Thus, if the neo-sex-determining allele invades in the gray region the system evolves tighter sex-linkage.  
-%In panel A, there is no haploid selection ($t^\Hermaphrodite=\alpha^\Hermaphrodite_{\Delta}=0$) and selection in diploids is sexually antagonistic ($s^\male=-s^\female=1/10$, $h^\male=1-h^\female=3/10$), in which case the neo-sex-determining allele can only invade if it is more closely linked to the selected locus ($R<r$, gray region; but see Figure \ref{fig:SexAntagTighter}B).
-%In panel B, there is no diploid selection ($s^\Hermaphrodite=0$) and selection in haploids is sexually antagonistic ($t^\male=-t^\female=0.08$, $\alpha^\Hermaphrodite_{\Delta}=0$), in which case the neo-sex-determining allele can invade regardless of linkage.
-%In panel C, selection in diploids ($s^\male=s^\female=1/10$, $h^\male=h^\female=7/10$) opposes drive in males ($\alpha^\male_{\Delta}=-0.05$, $t^\Hermaphrodite=\alpha^\female_{\Delta}=0$), in which case the neo-sex-determining allele can once again invade regardless of linkage.
-%We use Haldane's map function \citep[Equation 3 in ][]{Haldane1919} to convert from map distance (centiMorgans, cM) to the probability of a cross-over event.    
-%%we include haploid selection. %and assume that selection in diploids is not sexually-antagonistic ($s^\female s^\male>0$). 
-%%A polymorphism can then be maintained by opposing selection between the haploid and diploid phases. 
-%%In B, there is drive in favour of the $a$ allele in males ($\alpha^\male_{\Delta}=-1/20$), no female meiotic drive or gametic competition, $t^\Hermaphrodite=\alpha^\female_{\Delta}=0$), and equal selection in diploid sexes ($s^\female=s^\male=1/10$, $h^\female=h^\male=7/10$).
-%%In this case, a neo-W can invade even when the selected locus is more closely linked to the ancestral sex determining locus (see Table \ref{tab:specialcases} and Figure \ref{fig:Combination_Turnover}).
-%%In C and D, there is gametic competition among male gametes only (favouring $a$, $t^\male=-1/10$) and no meiotic drive or gametic competition in females ($t^\female=\alpha^\Hermaphrodite_{\Delta}=0$).
-%%In this case, the neo-W does not invade if $s^\female>s^\male$ (panel C: $s^\female=3/20$, $s^\male=1/20$) but does if $s^\female<s^\male$ (panel D: $s^\female=1/20$, $s^\male=3/20$), see Table \ref{tab:specialcases}.\\
-%%\textcolor{red}{
-%%1.
-I suspect that panel C has a region where no equilibrium is maintained (CHECK!
-Maybe include different parameters here or remove the part when no equilibrium).
-MMO: If you trust the sieve function there are stable equilibria across the entire range, although they differ greatly between XY and ZW systems near -25cM.
-%%\\
-%%2.
-Currently use different parameters for B than using in figure \ref{fig:Combination_Turnover} (selection/drive twice as strong in turnover figure).
-MMO: this is to keep it within the bounds of the plot -- using the same parameters as figure 1 makes the peak at -25 reach roughly 0.1, and then it is difficult to see the details of A,C, and D.
-%%%This plot would also benefit from titles giving, e.g., ``sexually-antagonistic selection, $s^\female s^\male<0$'' for A, ``male meiotic drive, $s^\female s^\male>0$'' for B
-%%}
-%}
-%\label{fig:Combination_Centimorgans}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%Haplotype invasion region plot
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\begin{tikzpicture}[remember picture]
-%	\node[] () {
-%	\includegraphics[width=0.5\linewidth]{regionplot_2a}
-%	\includegraphics[width=0.5\linewidth]{regionplot_hap}
-%	};
-%\end{tikzpicture}
-%\caption{
-%Parameter space (gray) where both neo-W haplotypes can invade from the same stable resident $r=0$ equilibria (equations \ref{eq:tightequil}), and therefore where an unlinked neo-W can invade an XY system with perfect sex-linkage.
-%\textbf{A}, In the absence of haploid selection, both neo-W haplotypes can invade for much of the parameter space where the relative fitnesses of male homozygotes, $w_{AA}^\male$ and $w_{aa}^\male$, are both less than that of the heterozygote, $w_{Aa}^\male = 1$.
-%In the white region neo-W haplotypes paired with the allele fixed on the Y cannot invade.
-%Parameters as in \cite{Otto2014} Figure 2a: $w_A^\Hermaphrodite=w_a^\Hermaphrodite$, $\alpha^\Hermaphrodite=1/2$, $w_{Aa}^\Hermaphrodite=1$, and $w_{AA}^\female=w_{aa}^\female=0.75$.
-%\textbf{B}, When selection is the same in both diploid sexes ($w_{aa}^\Hermaphrodite = 1$, $w_{Aa}^\Hermaphrodite = 1 + h s$, $w_{AA}^\Hermaphrodite = 1+s$), both neo-W haplotypes can invade over a portion of the parameter space where selection in diploids ($s$) opposes the force of drive during meiosis in males ($\alpha_{\Delta}^\male$).
-%Parameters: $w_A^\Hermaphrodite=w_a^\Hermaphrodite$, $\alpha^\female=1/2$, $h=1/2$.
-%}
-%\label{fig:regionplot_2a}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%W invades XY and fixes
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}
-%\centering
-%\includegraphics[width=0.5\linewidth]{FreqWLowR}\\
-%\includegraphics[width=0.5\linewidth]{SexRatioLowR}\\
-%\includegraphics[width=0.5\linewidth]{MeanDipFitLowR}
-%\caption{
-%Haploid selection allows a neo-$W$ to invade an ancestral $XY$ system and fix (\textbf{A}) despite temporarily biasing the sex ratio further (\textbf{B}) and decreasing mean diploid viability fitness (\textbf{C}).
-%Complete turnover between genetic sex-determination systems occurs despite the neo-$W$ being less tightly linked to the selected locus than the ancestral sex-determining locus is, $R>r$.
-%Parameters: $k=1$, $s^\female = 0.05$, $s^\male = 0.15$, $h^\female = h^\male = 0.7$, $t^\female = 0$, $t^\male = -0.1$, $\alpha^\male = \alpha^\female = 1/2$, $r=0.01$, $R=0.05$.
-%}
-%\label{fig:WinvasionLowR}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%W invades XY but does not fix
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}
-%\centering
-%\includegraphics[width=0.5\linewidth]{FreqWHighR}\\
-%\includegraphics[width=0.5\linewidth]{SexRatioHighR}\\
-%\includegraphics[width=0.5\linewidth]{MeanDipFitHighR}
-%\caption{
-%Haploid selection allows a completely unlinked neo-$W$ to invade an ancestral $XY$ system (\textbf{A}) despite further biasing the sex ratio (\textbf{B}) and decreasing mean diploid viability fitness (\textbf{C}).
-%The neo-$W$ does not fix (although variation at the \textbf{A} locus is maintained, $V_A>0$), resulting in a polymorphic sex-determination system.
-%Parameters as in Figure \ref{fig:WinvasionLowR} but with $R=0.5$.
-%}
-%\label{fig:WinvasionHighR}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%W invades for all rates of recombination with selected locus
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}
-%\centering
-%\includegraphics[width=0.5\linewidth]{InvasionVsRecombination}
-%\caption{
-%A neo-$W$ invades an ancestral $XY$ system with haploid selection regardless of how tightly it is linked to the selected locus. 
-%Parameters as in Figure \ref{fig:WinvasionLowR}.
-%}
-%\label{fig:InvasionVsRecombination}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%W invasion versus position of selected locus
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}
-%\centering
-%\includegraphics[width=0.5\linewidth]{InvasionVsCentiMorgans}
-%\includegraphics[width=0.5\linewidth]{InvasionVsCentiMorgansAllOrders}
-%\caption{
-%Haploid selection allows a neo-$W$ to invade an ancestral $XY$ system regardless of how tightly it and the ancestral sex-determining locus are linked to the selected locus. 
-%The ancestral sex-determining locus is located at -0.05 and the novel sex-determining locus is located at 0.05 (corresponding to the peaks of invasion fitness), such that the probability of a cross-over between them is $\approx0.1$.
-%The x-axis gives the position of the locus under haploid selection.
-%We used Haldane's map function \citep[Equation 3 in ][]{Haldane1919} to convert from map distance (centiMorgans) to the probability of a cross-over event. 
-%Parameters as in Figure \ref{fig:WinvasionLowR}.
-%}
-%\label{fig:InvasionVsCentiMorgans}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Y invades ZW and fixes (counter example to Kozi explanation)
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}
-%\centering
-%\includegraphics[width=0.5\linewidth]{FreqWCounterKozi}\\
-%\includegraphics[width=0.5\linewidth]{SexRatioCounterKozi}\\
-%\includegraphics[width=0.5\linewidth]{MeanDipFitCounterKozi}
-%\caption{
-%Meiotic drive allows a neo-$Y$ to invade an ancestral $ZW$ system and fix (\textbf{A}) despite temporarily biasing the sex ratio (\textbf{B}).
-%and decreasing mean diploid viability fitness (\textbf{C}).
-%Parameters: $k=0$, $s^\female = s^\male = t^\female = t^\male = 0$, $\alpha^\male = 0.4$, $\alpha^\female = 1/2$, $r=0$, $R=0$.
-%}
-%\label{fig:CounterKozi}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\externaldocument{Turnover_plos.tex}
+\externaldocument{S1_Appendix.tex}
+%\externaldocument{S2_Appendix.tex}
+\externaldocument{S3_Appendix.tex}
 
 \setcounter{equation}{0}
-\renewcommand{\theequation}{S.\arabic{equation}}
-\setcounter{figure}{0}
-\renewcommand{\thefigure}{S.\arabic{figure}}
-\setcounter{table}{0}
-\renewcommand{\thetable}{S.\arabic{table}}
+\renewcommand{\theequation}{S2.\arabic{equation}}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-
-\section*{Appendix}
-
-\subsection*{Recursion equations}
-\label{app:recurs}
-
-%\textcolor{red}{Should we adjust the subscripts throughout this subsection?
-Right now we end up re-defining $i$ and $j$ (when switching from haploid to diploid; this might have been my doing!) and then introduce three new subscripts $b$, $c$, and $l$, all of which can be derived from $i$ and $j$.
-Might be more straightforward to just use $p^\Hermaphrodite_{x_1,x_2,a_1,a_2,m_1,m_2}$ where 1 is maternal and 2 is paternal?
-We then no longer have to switch indices from haploid to diploid and the connection to other variables is clear: $b=m_1m_2$, $c=x_1x_2$, and $l=a_1a_2$.
-I guess the downside will be re-writing the recursion equations...
-which is why I haven't gone ahead and tried this.}
-
-In each generation we census the genotype frequencies in male and female gametes/gametophytes (hereafter, gametes) between meiosis (and any meiotic drive) and gametic competition. 
-At this stage we denote the frequencies of X- and Y-bearing gametes from males and females $x_{i}^{\Hermaphrodite}$ and $y_{i}^{\Hermaphrodite}$.
-The superscript $\Hermaphrodite \in \{\male,\female\}$ specifies the sex of the diploid that the gamete came from. 
-The subscript $i\in\{1,2,3,4\}$ specifies the genotype at the selected locus $\mathbf{A}$ and at the novel sex-determining locus $\mathbf{M}$, where $1=AM$, $2=aM$, $3=Am$, and $4=am$. 
-The gamete frequencies from each sex sum to one, $\sum_{i}x_{i}^{\Hermaphrodite}+y_{i}^{\Hermaphrodite}=1$.
-
-Competition then occurs among gametes of the same sex (e.g., among eggs and among sperm separately) according to the genotype at the \textbf{A} locus ($w_{1}^\Hermaphrodite=w_{3}^\Hermaphrodite=w_{A}^\Hermaphrodite$, $w_{2}^\Hermaphrodite=w_{4}^\Hermaphrodite=w_{a}^\Hermaphrodite$, see Table \ref{tab:fitnesstable}).
-The genotype frequencies after gametic competition are $x_{i}^{\Hermaphrodite,s}= w_{i}x_{i}^{\Hermaphrodite}/\bar{w}_{H}^{\Hermaphrodite}$ and $y_{i}^{\Hermaphrodite,s}= w_{i}y_{i}^{\Hermaphrodite}/\bar{w}_{H}^{\Hermaphrodite}$, where $\bar{w}_{H}^{\Hermaphrodite}=\sum_{i} w_{i}x_{i}^{\Hermaphrodite}+w_{i}y_{i}^{\Hermaphrodite}$ is the mean fitness of male ($\Hermaphrodite=\male$) or female ($\Hermaphrodite=\female$) gametes.
-
-Random mating then occurs between gametes to produce diploid zygotes.
-%To shorten notation we now use index $i$ (and $j$) to denote the alleles at both the $\mathbf{A}$ and $\mathbf{M}$ loci and label $MA=1$, $Ma=2$, $mA=3$, and $ma=4$, such that $i,j\in\{1,2,3,4\}$.
-The frequencies of XX zygotes are then denoted as $xx_{ij}$, XY zygotes as $xy_{ij}$, and YY zygotes as $yy_{ij}$, where \textbf{A} and \textbf{M} locus genotypes are given by $i,j\in\{1,2,3,4\}$, as above.
-In $XY$ zygotes, the haplotype inherited from an X-bearing gamete is given by $i$ and the haplotype from a Y-bearing gamete is given by $j$. 
-In XX and YY zygotes, individuals with diploid genotype $ij$ are equivalent to those with diploid genotype $ji$; for simplicity, we use $xx_{ij}$ and $yy_{ij}$ with $i\neq j$ to denote the average of these frequencies, $xx_{ij}=(x_{i}^{\female,s}x_{j}^{\male,s}+x_{j}^{\female,s}x_{i}^{\male,s})/2$ and $yy_{ij}=(y_{i}^{\female,s}y_{j}^{\male,s}+y_{j}^{\female,s}y_{i}^{\male,s})/2$.
-
-Denoting the \textbf{M} locus genotype by $b \in \{MM, Mm, mm\}$ and the \textbf{X} locus genotype by $c \in \{XX, XY, YY\}$, zygotes develop as females with probability $k_{bc}$. 
-Therefore, the frequencies of XX females are given by $xx_{ij}^{\female}=k_{bc}xx_{ij}$, XY females are given by $xy_{ij}^{\female}=k_{bc}xy_{ij}$, and YY females are given by $yy_{ij}^{\female}=k_{bc}yy_{ij}$.
-Similarly, XX male frequencies are $xx_{ij}^{\male}=(1-k_{bc})xx_{ij}$, XY male frequencies are $xy_{ij}^{\male}=(1-k_{bc})xy_{ij}$, and YY males frequencies are $yy_{ij}^{\male}=(1-k_{bc})yy_{ij}$.
-This notation allows both the ancestral and novel sex-determining regions to determine zygotic sex according to an XY system, a ZW system, or an environmental sex-determining system. 
-In addition, we can consider any epistatic dominance relationship between the two sex-determining loci. 
-Here, we assume that the ancestral sex-determining system (\textbf{X} locus) is XY ($k_{MMXX}=1$ and $k_{MMXY}=k_{MMYY}=0$) or ZW ($k_{MMZZ}=0$ and $k_{MMZW}=k_{MMWW}=1$) and epistatically recessive to a dominant novel sex-determining locus, \textbf{M} ($k_{Mmc}=k_{mmc}=k$).
-
-Selection among diploids then occurs according to the diploid genotype at the \textbf{A} locus, $l \in \{AA, Aa, aa\}$, for an individual of type $ij$ (see Table \ref{tab:fitnesstable}). 
-The diploid frequencies after selection in sex $\Hermaphrodite$ are given by $xx_{ij}^{\Hermaphrodite,s}=w_{l}^{\Hermaphrodite} xx_{ij}/\bar{w}^{\Hermaphrodite}$, $xy_{ij}^{\Hermaphrodite,s}=w_{l}^{\Hermaphrodite} xy_{ij}/\bar{w}^{\Hermaphrodite}$, and $yy_{ij}^{\Hermaphrodite,s}=w_{l}^{\Hermaphrodite} yy_{ij}/\bar{w}^{\Hermaphrodite}$, where $\bar{w}^{\Hermaphrodite}= \sum_{i=1}^{4}\sum_{j=1}^{4}w_{l}^{\Hermaphrodite}xx_{ij}+w_{l}^{\Hermaphrodite}xy_{ij}+w_{l}^{\Hermaphrodite}yy_{ij}$ is the mean fitness of individuals of sex $\Hermaphrodite$.
-
-Finally, these diploids undergo meiosis to produce the next generation of gametes. 
-Recombination and sex-specific meiotic drive occur during meiosis.
-%We can also assume that recombination is sex specific and/or affected by the M locus - but generally we don't so I just describe $R=R_{f}=R, r_{MM,d}=r_{Mm,d}=r_{mm,d}=r, \chi_{m}=\chi_{f}=\chi$.
-Here, we allow any relative locations for the SDR, \textbf{A}, and \textbf{M} loci by using three parameters to describe the recombination rates between them. 
-$R$ is the recombination rate between the \textbf{A} locus and the \textbf{M} locus, $\rho$ is the recombination rate between the \textbf{M} locus and the \textbf{X} locus, and $r$ is the recombination rate between the \textbf{A} locus and the \textbf{X} locus.
-Table \ref{tab:chisubstitutions} shows replacements that can be made for each possible ordering of the loci assuming that there is no cross-over interference.
-During meiosis in sex $\Hermaphrodite$, meiotic drive occurs such that, in $Aa$ heterozygotes, a fraction $\alpha^{\Hermaphrodite}$ of gametes produced carry the $A$ allele and $(1-\alpha^\Hermaphrodite)$ carry the $a$ allele.
-
-\begin{table}[ht]
-\centering
-\smallskip
-\caption{
-Substitutions for different loci orders assuming no interference.
-%and $r,R\in(0,1/2)$.\textcolor{blue}{write all in form of first line?
-so that 1/2 cases are okay (can't determine chi if R is 1/2 in second line, or if r is 1/2 in third line}
-}
-\begin{tabular}{l l}
-\hline\hline
-  Order of loci &   \\ [0.5ex] \hline
-  SDR-A-M & $\rho=r(1-R)+R(1-r)$  \\
-  SDR-M-A & $r=\rho(1-R)+R(1-\rho)$ \\ %$\rho=(r-R)/(1-2R)$ \\
-  A-SDR-M & $R=r(1-\rho)+\rho(1-r)$ \\ %$\rho=(R-r)/(1-2r)$ \\
-  \hline \hline
-  \label{tab:chisubstitutions}
- \end{tabular}
-\end{table}
-
-Among gametes from sex $\Hermaphrodite$, the frequencies of haplotypes (before gametic competition) in the next generation are given by
-
-\begingroup
-\allowdisplaybreaks
-\begin{subequations}
-\begin{align}
-%
-\begin{split}
-x_{1}^{{\Hermaphrodite}'}=&xx_{11}^{\Hermaphrodite,s}+xx_{13}^{\Hermaphrodite,s}/2+(xx_{12}^{\Hermaphrodite,s}+xx_{14}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(xx_{14}^{\Hermaphrodite,s}-xx_{23}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&+(xy_{11}^{\Hermaphrodite,s}+xy_{13}^{\Hermaphrodite,s})/2+(xy_{12}^{\Hermaphrodite,s}+xy_{14}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&- r(xy_{12}^{\Hermaphrodite,s}-xy_{21}^{\Hermaphrodite,s})\alpha^\Hermaphrodite - \rho(xy_{13}^{\Hermaphrodite,s}-xy_{31}^{\Hermaphrodite,s})/2\\
-&+\big{[}-(R+r+\rho)xy_{14}^{\Hermaphrodite,s} +(R+\rho-r)xy_{41}^{\Hermaphrodite,s}\\
-&+(R+r-\rho) xy_{23}^{\Hermaphrodite,s}+(R+\rho-r)xy_{32}^{\Hermaphrodite,s}\big{]}\alpha^\Hermaphrodite/2
-\end{split}
-\\
-%
-\begin{split}
-x_{2}^{{\Hermaphrodite}'}=&xx_{22}^{\Hermaphrodite,s}+xx_{24}^{\Hermaphrodite,s}/2+(xx_{12}^{\Hermaphrodite,s}+xx_{23}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(xx_{23}^{\Hermaphrodite,s}-xx_{14}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&(xy_{22}^{\Hermaphrodite,s}+xy_{24}^{\Hermaphrodite,s})/2+(xy_{21}^{\Hermaphrodite,s}+xy_{23}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite)\\
-&- r(xy_{21}^{\Hermaphrodite,s}-xy_{12}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite) - \rho(xy_{24}^{\Hermaphrodite,s}-xy_{42}^{\Hermaphrodite,s})/2\\
-&+\big{[}-(R+r+\rho)xy_{23}^{\Hermaphrodite,s}+(R+\rho-r)xy_{32}^{\Hermaphrodite,s}\\
-&+(R+r-\rho) xy_{14}^{\Hermaphrodite,s}+(R+\rho-r)xy_{41}^{\Hermaphrodite,s}\big{]}(1-\alpha^\Hermaphrodite)/2
-\end{split}
-\\
-%
-\begin{split}
-x_{3}^{{\Hermaphrodite}'}=&xx_{33}^{\Hermaphrodite,s}+xx_{13}^{\Hermaphrodite,s}/2+(xx_{23}^{\Hermaphrodite,s}+xx_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(xx_{23}^{\Hermaphrodite,s}-xx_{14}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&(xy_{33}^{\Hermaphrodite,s}+xy_{31}^{\Hermaphrodite,s})/2+(xy_{32}^{\Hermaphrodite,s}+xy_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&- r(xy_{34}^{\Hermaphrodite,s}-xy_{43}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite - \rho(xy_{31}^{\Hermaphrodite,s}-xy_{13}^{\Hermaphrodite,s})/2\\
-&+\big{[}-(R+r+\rho)xy_{32}^{\Hermaphrodite,s} +(R+\rho-r)xy_{23}^{\Hermaphrodite,s}\\
-&+(R+r-\rho) xy_{41}^{\Hermaphrodite,s}+(R+\rho-r)xy_{14}^{\Hermaphrodite,s}\big{]} \alpha^\Hermaphrodite/2
-\end{split}
-\\
-%
-\begin{split}
-x_{4}^{{\Hermaphrodite}'}=&xx_{44}^{\Hermaphrodite,s}+xx_{34}^{\Hermaphrodite,s}/2+(xx_{14}^{\Hermaphrodite,s}+xx_{24}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(xx_{14}^{\Hermaphrodite,s}-xx_{23}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&(xy_{44}^{\Hermaphrodite,s}+xy_{42}^{\Hermaphrodite,s})/2+(xy_{41}^{\Hermaphrodite,s}+xy_{43}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite)\\
-&- r(xy_{43}^{\Hermaphrodite,s}-xy_{34}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite) - \rho(xy_{42}^{\Hermaphrodite,s}-xy_{24}^{\Hermaphrodite,s})/2\\
-&+\big{[}-(R+r+\rho)xy_{41}^{\Hermaphrodite,s}+(R+\rho-r)xy_{14}^{\Hermaphrodite,s}\\
-&+(R+r-\rho) xy_{32}^{\Hermaphrodite,s}+(R+\rho-r)xy_{23}^{\Hermaphrodite,s}\big{]}(1-\alpha^\Hermaphrodite)/2
-\end{split}
-\\
-\begin{split}
-y_{1}^{{\Hermaphrodite}'}=&yy_{11}^{\Hermaphrodite,s}+yy_{13}^{\Hermaphrodite,s}/2+(yy_{12}^{\Hermaphrodite,s}+yy_{14}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(yy_{14}^{\Hermaphrodite,s}-yy_{23}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&(xy_{11}^{\Hermaphrodite,s}+xy_{31}^{\Hermaphrodite,s})/2+(xy_{21}^{\Hermaphrodite,s}+xy_{41}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&- r(xy_{21}^{\Hermaphrodite,s}-xy_{12}^{\Hermaphrodite,s})\alpha^\Hermaphrodite - \rho(xy_{31}^{\Hermaphrodite,s}-xy_{13}^{\Hermaphrodite,s})/2\\
-&+\big{[} - (R+r+\rho)xy_{41}^{\Hermaphrodite,s} + (R+\rho-r)xy_{14}^{\Hermaphrodite,s}\\
-& + (R+r-\rho)xy_{32}^{\Hermaphrodite,s} + (R+\rho-r) xy_{23}^{\Hermaphrodite,s}\big{]}\alpha^\Hermaphrodite/2
-\end{split}
-\\
-%
-\begin{split}
-y_{2}^{{\Hermaphrodite}'}=&yy_{22}^{\Hermaphrodite,s}+yy_{24}^{\Hermaphrodite,s}/2+(yy_{12}^{\Hermaphrodite,s}+yy_{23}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(yy_{23}^{\Hermaphrodite,s}-yy_{14}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&(xy_{22}^{\Hermaphrodite,s}+xy_{42}^{\Hermaphrodite,s})/2+(xy_{12}^{\Hermaphrodite,s}+xy_{32}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite)\\
-&- r(xy_{12}^{\Hermaphrodite,s}-xy_{21}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite) - \rho(xy_{42}^{\Hermaphrodite,s}-xy_{24}^{\Hermaphrodite,s})/2\\
-&+\big{[}-(R+r+\rho)xy_{32}^{\Hermaphrodite,s} +(R+\rho-r) xy_{23}^{\Hermaphrodite,s}\\
-&+(R+r-\rho)xy_{41}^{\Hermaphrodite,s}+(R+\rho-r)xy_{14}^{\Hermaphrodite,s}\big{]}(1-\alpha^\Hermaphrodite)/2
-\end{split}
-\\
-%
-\begin{split}
-y_{3}^{{\Hermaphrodite}'}=&yy_{33}^{\Hermaphrodite,s}+yy_{13}^{\Hermaphrodite,s}/2+(yy_{23}^{\Hermaphrodite,s}+yy_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(yy_{23}^{\Hermaphrodite,s}-yy_{14}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&(xy_{33}^{\Hermaphrodite,s}+xy_{13}^{\Hermaphrodite,s})/2+(xy_{23}^{\Hermaphrodite,s}+xy_{43}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&- r(xy_{43}^{\Hermaphrodite,s}-xy_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite - \rho(xy_{13}^{\Hermaphrodite,s}-xy_{31}^{\Hermaphrodite,s})/2\\
-&+\big{[}-(R+r+\rho)xy_{23}^{\Hermaphrodite,s} +(R+\rho-r)xy_{32}^{\Hermaphrodite,s}\\
-&+(R+r-\rho) xy_{14}^{\Hermaphrodite,s} + (R+\rho-r) xy_{41}^{\Hermaphrodite,s}\big{]}\alpha^\Hermaphrodite/2
-\end{split}
-\\
-%
-\begin{split}
-y_{4}^{{\Hermaphrodite}'}=&yy_{44}^{\Hermaphrodite,s}+yy_{34}^{\Hermaphrodite,s}/2+(yy_{14}^{\Hermaphrodite,s}+yy_{24}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(yy_{14}^{\Hermaphrodite,s}-yy_{23}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&(xy_{44}^{\Hermaphrodite,s}+xy_{24}^{\Hermaphrodite,s})/2+(xy_{14}^{\Hermaphrodite,s}+xy_{34}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite)\\
-&- r(xy_{34}^{\Hermaphrodite,s}-xy_{43}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite) - \rho(xy_{24}^{\Hermaphrodite,s}-xy_{42}^{\Hermaphrodite,s})/2\\
-&+\big{[}-(R+r+\rho) xy_{14}^{\Hermaphrodite,s} + (R+\rho-r)xy_{41}^{\Hermaphrodite,s}\\
-&+(R+r-\rho) xy_{23}^{\Hermaphrodite,s} + (R+\rho-r) xy_{32}^{\Hermaphrodite,s}\big{]}(1-\alpha^\Hermaphrodite)/2
-\end{split}
-\end{align}
-\label{eq:recursions}
-\end{subequations}
-
-\endgroup
-
-\noindent
-The full system is therefore described by 16 recurrence equations (three diallelic loci in two sexes, $2^3 \times 2 = 16$). 
-However, not all diploid types are produced under certain sex-determination systems. 
-For example, with the $M$ allele fixed and an ancestral $XY$ sex-determining system, there are $XX$ males, $XY$ females, or $YY$ females ($x_{3}^\Hermaphrodite=x_{4}^\Hermaphrodite=y_{4}^\Hermaphrodite=y_{3}^\Hermaphrodite=y_{i}^\female=0$).
-%($xx_{11}^{\male}=xx_{12}^{\male}=xx_{22}^\male=xy_{11}^{\female}=xy_{12}^{\female}=xy_{21}^{\female}=xy_{22}^\female=yy_{11}^{\female}=yy_{12}^{\female}=yy_{22}^\female=0$). 
-In this case, the system only involves six recursion equations, %because there is only one \textbf{M} locus allele and no Y-bearing female gametes. 
-which we assume below to calculate the equilibria.
-
-%I think this should be moved below because we have some 'results' where we don't assume weak selection but we only have the equilibrium calculated analytically for weak selection.
+\section*{S2 Appendix}
 
@@
 These four variables determine the frequencies of the six resident gamete types: $x_{1}^{\female}=\hat{p}_X^\female$, $x_{2}^{\female}=1-\hat{p}_X^\female$, $x_{1}^{\male}=(1-q)\hat{p}_X^\male$, $x_{2}^{\male}=(1-q)(1-\hat{p}_X^\male)$, $y_{1}^{\male}=q \hat{p}_Y^\male$, and $y_{2}^{\male}=q(1-\hat{p}_Y^\male)$.
-Mean fitnesses in the resident population are given in table \ref{tab:meanfitnesses}.
+Mean fitnesses in the resident population are given in table \nameref{tab:meanfitnesses}.
 
 Various forms of selection can maintain a polymorphism at the \textbf{A} locus, including sexually antagonistic selection, overdominance, conflicts between diploid selection and selection upon haploid genotypes \citep[ploidally antagonistic selection,][]{Immler:2012tl}, or a combination of these selective regimes (see below).
-
-\begin{table}[ht]
-\centering
-\smallskip
-\caption{Mean fitnesses and zygotic sex ratio in the resident population ($M$ fixed, XY sex determination). }
-\begin{tabular}{l l }
-\hline\hline
-  Sex \& Life Cycle Stage & Mean Fitness \\ [0.5ex] \hline  \noalign{\vskip 0.5ex}
-  female gametes ($\bar{w}_H^\female$) & 
-  $p_X^\female w_A^\female + (1-p_X^\female) w_a^\female$ \\ [0.5ex] \hline  \noalign{\vskip 0.5ex}
-  male gametes ($\bar{w}_H^\male$) & 
-  $\bar{p}^{\male} w_A^\male + (1-\bar{p}^{\male}) w_a^\male$ \\ [0.5ex] \hline  \noalign{\vskip 0.5ex}
-  females ($\bar{w}^\female$) & 
-  $\begin{array}{l}  (1-\zeta)^{-1} \big[ p_X^\female w_A^\female p_X^\male w_A^\male w_{AA}^\female + \\
-  (1 - p_X^\female) w_a^\female p_X^\male w_A^\male w_{Aa}^\female + \\
-  p_X^\female w_A^\female (1 - p_X^\male) w_a^\male w_{Aa}^\female + \\
-  (1-p_X^\female) w_a^\female (1 - p_X^\male) w_a^\male w_{aa}^\female \big] / \left( \bar{w}_H^\female \bar{w}_H^\male \right)
-  \end{array} 
-  $ \\ [0.5ex] \noalign{\vskip 0.5ex} \hline  \noalign{\vskip 0.5ex}
-  males ($\bar{w}^\male$) & 
-  $\begin{array}{l} \zeta^{-1} \big[ p_X^\female w_A^\female  p_Y^\male w_A^\male w_{AA}^\male + \\
-  (1 - p_X^\female) w_a^\female  p_Y^\male w_A^\male w_{Aa}^\male + \\
-  p_X^\female w_A^\female  (1 - p_Y^\male) w_a^\male w_{Aa}^\male + \\
-  (1-p_X^\female) w_a^\female  (1 - p_Y^\male) w_a^\male w_{aa}^\male \big] / \left( \bar{w}_H^\female \bar{w}_H^\male \right) 
-  \end{array}
-  $ \\ [0.5ex] \noalign{\vskip 0.5ex} \hline  \noalign{\vskip 0.5ex}
-  fraction zygotes male ($\zeta$) & $q \left[ p_Y^\male w_A^\male+(1-p_Y^\male)w_a^\male\right] / \bar{w}_H^\male $
-   \\ [0.5ex]  \noalign{\vskip 0.5ex}
-  \hline \hline
-  \label{tab:meanfitnesses}
- \end{tabular}
-\end{table}
 
@@
 
-% the differences in the frequencies of $A$ in each type of gamete are small, as is the bias in the sex-determining factor from the heterogametic sex, and we can solve for the mean frequency of $A$ across all types ($p_A$), the difference in the frequencies of $A$ between two of the three types, and the bias in the frequency of the sex-determining factor, to first order in selection.
-%Linear stability analysis can then be used to determine the stability of this equilibrium.
-%Without haploid selection or meiotic drive our results reduce to those of \cite{vanDoorn:2007eu}.
-%when $k=0$ (neo-$Y$ invading a $ZW$ system) or when $k=1$ (neo-$W$ invading an $XY$ system) (\textcolor{red}{CHECK}).
-%However, with haploid selection or meiotic drive a stable polymorphism at locus \textbf{A} no longer requires sexually antagonistic selection.
-%, as it can also be achieved by ploidally-antagonistic selection.
-
-\subsection*{Invasion conditions}
-
-%Here, we determine whether a rare neo-Y or neo-W allele spreads when rare, which occurs when $\lambda > 1$.
-%We begin with the general result and then give explicit solutions under tight linkage and weak selection.
-
-%If the average change in frequency of the two haplotypes that carry the $m$ allele ($Am$ and $am$) is positive, invasion will always occur (i.e., if $\left\{(\lambda_{mA}-1)+ (\lambda_{ma}-1) \right\}/2 > 0$ then $\lambda > 1$, see table \ref{tab:haplotype_growth} for $\lambda_{mi}$).
-%If neither haplotype increases in frequency ($\lambda_{mA}, \lambda_{ma} < 1$), the $m$ allele will not invade. 
-%Otherwise, the new sex-determining allele increases in frequency on one \textbf{A} background and declines on the other, and invasion requires
-%\begin{equation}\label{eq:neoYR}
-%R \left[ 
-%\frac{p^\female_X w^\female_A w^\male_a (1-\alpha^\male)}{ \bar{w}^\female_H \bar{w}^\male_H (\lambda_{mA}-1)} + 
-%p^\female_X \frac{w^\female_A}{\bar{w}^\female_H} \frac{w^\male_a(1-\alpha^\male)}{\bar{w}^\male_H} \frac{1}{\lambda_{mA}-1} + 
-%\frac{(1 - p^\female_X) w^\female_a w^\male_A \alpha^\male}{ \bar{w}^\female_H \bar{w}^\male_H (\lambda_{ma}-1)} 
-%\right] 
-%\frac{w^\male_{Aa}}{q\bar{w}^\male} < 1,
-%\end{equation}
-
-%\noindent
-%for the neo-$Y$, and
-
-%\noindent
-%\begin{equation}\label{eq:neoWR}
-%R \left[ 
-%\frac{\bar{p}^\male w^\male_A w^\female_a (1-\alpha^\female)}{ \bar{w}^\male_H \bar{w}^\female_H (\lambda_{mA}-1)} + 
-%\frac{(1 - \bar{p}^\male) w^\male_a w^\female_A \alpha^\female}{ \bar{w}^\male_H \bar{w}^\female_H (\lambda_{ma}-1)} 
-%\right] 
-%\frac{w^\female_{Aa}}{(1-q)\bar{w}^\female} < 1,
-%\end{equation}
-
-%\noindent
-%for the neo-$W$.
-
-%Equations \eqref{eq:neoYR} and \eqref{eq:neoWR} show that the new sex-determining allele, $m$, is expected to invade for any probability of recombination between loci \textbf{A} and \textbf{M}, $R$, when the net flow of recombinants is from the less fit (smaller $\lambda_{mi}$) to the more fit \textbf{A} background (making the terms inside the square brackets in Equations \ref{eq:neoYR} and \ref{eq:neoWR} negative).
-%\textcolor{red}{Q: is it definitely possible to have negative square brackets for a equilibria maintained by selection?}
-%Assuming $g_A^* > 0$ and $g_a^* < 0$ without loss of generality, this is $-(1 - p^\female_X) w_{m,A} g_a^* < p^\female_X w_{m,a} g_A^*$.
-%When the net flow of recombinants is from the more fit to the less fit haplotype, the new sex-determining allele can still invade when the rate of recombination between it and the selected locus is small enough.
-%\textcolor{red}{Q:Is it the case that sometimes the square brackets are positive and invasion occurs for $r_{AM}=1/2$?
-In which case it might be better to have slightly different phrasing here.}
-%Equations \eqref{eq:neoYR} and \eqref{eq:neoWR} show that the new sex-determining allele, $m$, is expected to invade for any probability of recombination between loci \textbf{A} and \textbf{M}, $R$, when the net flow of recombinants is from the less fit (smaller $\lambda_{mi}$) to the more fit \textbf{A} background (making the terms inside the square brackets in Equations \ref{eq:neoYR} and \ref{eq:neoWR} negative).
-%When the net flow of recombinants is from the more fit to the less fit haplotype, the new sex-determining allele can still invade when the rate of recombination between it and the selected locus is small enough.
-%To better understand when these scenarios are possible we next use knowledge of the equilibria and their stability under tight linkage and weak selection.
-
-\textcolor{red}{Cover the other parts of the characteristic polynomial here.}
-\textcolor{blue}{Waiting for Sally's proof!}
-
-A rare neo-Y or neo-W will spread from a given ancestral equilibrium when the leading eigenvalue, $\lambda$, of the Jacobian matrix derived from the eight mutant recursion equations (given by \ref{eq:recursions}c,d,g,h), evaluated at the ancestral equilibrium, is greater than one.
-However, because a neo-Y (neo-W) is always in males (females) and is epistatically dominant to the ancestral sex-determining locus, we need only two recursion equations (e.g., tracking the change in the frequency of neo-Y-$A$ and neo-Y-$a$ gametes from males) and thus the leading eigenvalue is the largest solution the polynomial $\lambda^2 + b\lambda + c = 0$ as described in the text (Table \ref{tab:haplotype_growth}).
-%It can be shown (see supplementary Mathematica file) that the coefficients are $b= - (\lambda_{mA} + \lambda_{ma})+(\chi_{mA} + \chi_{ma})$ and $c = (\lambda_{mA}-\chi_{mA}) (\lambda_{ma}-\chi_{ma}) -\chi_{mA} \chi_{ma}$, where $\lambda_{mi}$ is the multiplicative growth rate of the frequency of mutants on background $i\in\{A,a\}$, without accounting for loss due to recombination, and $\chi_{mi}$ is the rate at which mutants on background $i\in\{A,a\}$ recombine onto the other \textbf{A} locus background in heterozygotes.
-%The leading eigenvalue is then greater than one whenever $\lambda_{mA}>1$ and $\lambda_{ma}>1$, less than one whenever $\lambda_{mA}<1$ and $\lambda_{ma}<1$, and greater than one whenever  $\lambda_{mA}>1$ or $\lambda_{ma}>1$ and $\chi_{ma} (\lambda_{mA}-1) + \chi_{mA} (\lambda_{ma}-1) > 0$.
-
-The general conditions for the invasion of a neo-sex-determining allele are given in the main text, in terms of the growth rates of the mutant haplotypes in the absence of recombination ($\lambda_{mi}$) and the rate that recombination destroys them ($\chi_{mi}$).
-For tight linkage between the ancestral sex-determining locus and the selected locus we can calculate these terms explicitly (see below).
-For weak selection we can take a Taylor series of the leading eigenvalue. 
-The leading eigenvalue, $\lambda$, for any $k$, is given up to order $\epsilon^2$ by equation \eqref{eq:lambda_ESD_k}.
-
-\subsubsection*{Tight linkage between \textbf{A} and \textbf{X} (recombination weak relative to selection)}
-
-Here, we explore the conditions under which a neo-W invades an XY system assuming that the \textbf{A} locus is initially in tight linkage with the ancestral sex-determining region ($r \approx 0$). 
-We disregard neo-Y mutations, which never spread given that the ancestral population is at a stable equilibrium (see supplementary \textit{Mathematica} notebook for proof).
-
-Starting with the simpler equilibrium $(B)$, the terms of that determine the leading eigenvalue are
-
-\begin{subequations}\label{Binvasion}
-\begin{align}
-\lambda_{mA}&= \left[w_{A}^\male (1+\alpha^\male_\Delta) \right]^{-1}
-\frac{w_{A}^\female }{w_{A}^\female}
-\frac{\left[ w_{A}^\male (1+\alpha^\male_\Delta) w_{AA}^\female + 
-w_{a}^\male (1-\alpha^\male_\Delta) w_{Aa}^\female (1+\alpha^\female_\Delta) \right]}
-{ 2w_{AA}^\female } \\
-\lambda_{ma}&= \left[w_{A}^\male (1+\alpha^\male_\Delta) \right]^{-1}
-\frac{w_{a}^\female}{w_{A}^\female}
-\frac{\left[  w_{A}^\male (1+\alpha^\male_\Delta) w_{Aa}^\female (1-\alpha^\female_\Delta)+
-w_{a}^\male (1-\alpha^\male_\Delta) w_{aa}^\female \right]}
-{ 2w_{AA}^\female } \\
-\chi_{mA}&= \frac{1}{2} \left[w_{A}^\male (1+\alpha^\male_\Delta) \right]^{-1}
-\frac{w_{A}^\female }{w_{A}^\female}
- \frac{\left[  w_{a}^\male (1-\alpha^\male_\Delta) w_{Aa}^\female (1 + \alpha^\female_\Delta) \right]}
-{ w_{AA}^\female } \frac{R}{2}\\
-\chi_{ma}&= \frac{1}{2} \left[w_{A}^\male (1+\alpha^\male_\Delta) \right]^{-1}
-\frac{w_{a}^\female}{w_{A}^\female}
- \frac{\left[  w_{A}^\male (1+\alpha^\male_\Delta) w_{Aa}^\female (1-\alpha^\female_\Delta) \right]}
-{  w_{AA}^\female} \frac{R}{2}
-\end{align}
-\end{subequations}
-
-%\noindent
-%In this case, the zygotic sex ratio ($\zeta$) is given by the difference in haploid selection in males on $a$ (fixed on the Y) and $A$ (fixed on the X) alleles, i.e., there are more males than females if $\zeta = \alpha^\male w_A^\male / [(1-\alpha^\male)w_a^\male + \alpha^\male w_A^\male]<1/2$.
-%$\alpha^\male<1/2$ and/or $w_{a}^\male>w_{A}^\male$.
-%Populations with haploid selection for $a$ in males have a male biased zygotic sex ratio are thus more permissive to invasion by a neo-W ($\lambda_{mA}$ and $\lambda_{ma}$ larger).
-%%In addition, the spread of neo-W alleles depends on the fitness of female diploids after mating with an X-$A$ or Y-$a$ male gamete, relative to the fitness of females in the population (all have genotype $AA$ and fitness $w_{AA}^\female$ at this equilibrium).
-%Haploid selection in males has a second effect; the spread rate of neo-W haplotypes is determined by their fitness in diploid females, which depends on their diploid genotype and thus on the male gamete they pair with.
-%Zygotes carrying dominant neo-W alleles will develop as females regardless of their genotype at the XY locus. 
-%Therefore, neo-W females result from matings with either X-$A$ or Y-$a$ male gametes. 
-%The relative proportion of these male gametes is determined by haploid selection in males; mating with a Y-$a$ male gamete is more likely if the $a$ allele is favoured during male gamete production or competition ($\zeta<1/2$).
-%Thus, neo-W females experience different diploid selection than XX females, and the extent of this difference depends on haploid selection in males.
-%Furthermore, haploid selection in females can directly select upon neo-W-$A$ or neo-W-$a$ haplotypes. 
-%A neo-W-$A$ female gamete has the same fitness during haploid competition as resident $A$-bearing female gametes. 
-%On the other hand, neo-W-$a$ female gametes can be favoured or disfavoured during female haploid competition (favoured if $w_{a}^\female>w_{A}^\female$). 
-%Meiotic drive in females ($\alpha^\female$) similarly affects the fitness of these neo-W haplotypes, except that it impacts both haplotypes as meiotic drive only occurs in heterozygotes and therefore does not occur in resident XX females (who are always homozygote $AA$).
-
-Haploid selection impacts the spread of neo-W haplotypes in three ways.
-Firstly, the zygotic sex ratio becomes male biased, $\zeta>1/2$, when the $a$ allele (which is fixed on the Y) is favoured during competition among male gametes or by meiotic drive in males.
-Specifically, at equilibrium $(B)$, female zygote frequency is $1 - \zeta = w_A^\male (1+\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$ where $2\bar{w}_{H}^\male= \big[w_a^\male (1-\alpha^\male_\Delta) +  w_A^\male (1+\alpha^\male_\Delta) \big]$ has been canceled out in equations \eqref{Binvasion} to leave the term $\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]^{-1}$.
-Male biased sex ratios facilitate the spread of a neo-W because neo-W alleles cause the zygotes that carry them to develop as the rarer, female, sex.
-
-Secondly, haploid selection in females selects on neo-W haplotypes directly.
-At equilibrium $(B)$, the fitness of female gametes under the ancestral sex-determining system is $w_{A}^\female$ such that the relative fitnesses of neo-W-$A$ and neo-W-$a$ haplotypes during female gametic competition are $w_{A}^\female/w_{A}^\female$ and $w_{a}^\female/w_{A}^\female$ (see terms in equation \ref{Binvasion}).
-Meiotic drive in females will also change the proportion of gametes that carry the $A$ versus $a$ alleles, which will be produced by heterozygous females in proportions $(1+\alpha_{\Delta}^\female)/2$ and $(1-\alpha_{\Delta}^\female)/2$, respectively.
-These terms are only associated with heterozygous females, i.e., they are found alongside $w_{Aa}^\female$.
-
-Thirdly, haploid selection in males affects the diploid genotypes of females by altering the allele frequencies in the male gametes that female gametes pair with.
-At equlibrium $(B)$, neo-W female gametes will mate with X-$A$ male gametes with probability $ w_A^\male (1+\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$ and Y-$a$ male gametes with probability $w_a^\male (1-\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$, where the $2\bar{w}_{H}^\male$ terms have been canceled in equation \eqref{Binvasion} (as mentioned above).
-Thus, for example, neo-W-$A$ haplotypes are found in $AA$ female diploids with probability $ w_A^\male (1+\alpha^\male_\Delta)/ (2\bar{w}_{H}^\male)$ (first term in square brackets in the numerator of equation \ref{Binvasion}a) and in $Aa$ female diploids with probability $w_a^\male (1-\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$ (see equation \ref{Binvasion}c and the second term in square brackets in the numerator of equation \ref{Binvasion}a).
-
-%For instance, because an epistatically dominant neo-W always causes its carrier to become female, it creates females who carry either Y-$a$ or X-$A$ genotypes from their father.
-%Thus, because when there is a polymorphism the X carries some non-zero frequency of $A$, haploid selection in males impacts the diploid genotypes of females (e.g., creating more $Aa$ females when drive in males favours Y-$a$).
-%How this affects the spread of the neo-W then depends on diploid and haploid selection in females.
-
-The other terms in equations \eqref{Binvasion} are more easily interpreted if we assume that there is no haploid selection in either sex, in which case $\lambda_{mA}=(w_{AA}^\female+w_{Aa}^\female)/2 w_{AA}^\female$ and $\lambda_{ma}=(w_{aa}^\female+w_{Aa}^\female)/ 2 w_{AA}^\female$.
-Neither haplotype can spread under purely sexually-antagonistic selection, where $A$ is directionally favoured in females ($w_{AA}^\female>w_{Aa}^\female>w_{aa}^\female$) and $a$ is directionally favoured in males ($w_{AA}^\male>w_{Aa}^\male>w_{aa}^\male$).
-Essentially, the X is then already as specialized as possible for the female beneficial allele ($A$ is fixed on the X), and the neo-W often makes daughters with the Y-$a$ haplotype, increasing the flow of $a$ alleles into females, which reduces the fitness of those females.
-
-If selection doesn't uniformly favour $A$ in females, however, neo-W-$A$ haplotypes and/or neo-W-$a$ haplotypes can spread ($\lambda_{mA}>1$ and/or $\lambda_{ma}>1$).
-%If $\lambda_{mA}>1$ (requiring $w_{Aa}^\female>w_{AA}^\female$), the implication is that the neo-W can spread alongside the $A$ allele, despite the fact that the neo-W sometimes brings $Y-a$ haplotypes into females, because $a$ is favoured by selection in females despite $A$ being fixed on the X.
-A neo-W-$A$ haplotype can spread ($\lambda_{mA}>1$) when $w_{Aa}^\female>w_{AA}^\female$, despite the fact that a neo-W brings Y-$a$ haplotypes into females.
-In this case the $a$ allele is favoured by selection in females despite $A$ being fixed on the X.
-For this equilibrium to be stable (i.e.,  to keep $A$ fixed on the X), X-$a$ cannot be overly favoured in females and X-$A$ must be sufficiently favoured in males (for example, by overdominance in males).
-Specifically, from the stability conditions for equilibrium (B), we must have $w_{Aa}^\female < 2 w_{AA}^\female$ and $w_{Aa}^\male/\big[(w_{aa}^\male+w_{Aa}^\male)/2\big]>w_{Aa}^\female/w_{AA}^\female$.
-
-Still considering $w_{Aa}^\female>w_{AA}^\female$, the neo-W can also spread alongside the $a$ allele ($\lambda_{ma}>1$) if $w_{aa}^\female$ is large enough such that $(w_{Aa}^\female+w_{aa}^\female)/2>w_{AA}^\female$.
-%there is sufficiently strong underdominance in females ($w_{aa}^\female>w_{Aa}^\female$) \textcolor{blue}{[this is describing directional selection, not overdominance - check the conditions for the case we want to talk about]}, such that $(w_{Aa}^\female+w_{aa}^\female)/2>w_{AA}^\female$.
-This can occur with overdominance or directional selection for $a$ in females (Figure \ref{fig:regionplots}B,C).
-In this case, $a$ is favoured in females (comparing $Aa$ to $AA$ genotypes in females) but $A$ is fixed on the X due to selection in males. 
-The neo-W-$a$ haplotype can spread because it produces females with higher fitness $Aa$ and $aa$ genotypes.
-
-%When both haplotypes can spread on their own ($\lambda_{mA}>1$ and $\lambda_{ma}>1$), the neo-W invades regardless the recombination rate between it and the selected locus, $R$.
-%When neither haplotype can spread ($\lambda_{mA}<1$ and $\lambda_{ma}<1$) the neo-W can never invade.
-%And when only one haplotype can spread on its own the neo-W invades only when the rate of recombination onto the favourable background is sufficiently larger than the rate of recombination off this background (i.e., equation\ref{eq:lambdasGen} is satisfied).
-
-%Haploid selection affects the conclusions outlined above by altering the zygotic sex ratio and exerting direct selection on neo-W haplotypes.
-%The effect of sex ratio selection is straightforward and can be seen in equation \eqref{Binvasion}, where male drive and gamete competition for $a$ (which is fixed on the Y and therefore causes a male bias) increases all four terms.
-%Direct selection on neo-W haplotypes can also be seen in equation \eqref{Binvasion} by noticing that increasing female drive in favour of $A$ increases the neo-W-$A$ haplotype growth rate ($\lambda_{mA}$) while female drive and gamete competition in favour of $a$ increases the neo-W-$a$ haplotype growth rate ($\lambda_{ma}$).
-%Gamete competition in females does not impact the spread of neo-W-$A$ haplotypes because they are on the same background as the resident X.
-%Recombination between the selected locus and the neo-W complicates things slightly, as selective advantages for one neo-W haplotype during the haploid stage in females comes at a cost to the other, and thus recombination off the favoured background becomes more detrimental.
-
-%\textcolor{red}{the versions for equil $(A)$ are not terrible but could be improved by cleverly re-writing with the $\phi$ and $\psi$ terms from above, I think...}
-
-Similar equations can be derived for equilibrium (A) by substituting the equilibrium allele frequencies into Table \ref{tab:haplotype_growth}
-
-\begin{subequations}\label{Ainvasion}
-\begin{align}
-\lambda_{mA}&= \frac{a}{b} \left[w_{AA}^\female w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi +  w_{Aa}^\female (1+\alpha^\female_\Delta) w_a^\male c \right] / (2 w_a^\female) \\
-\lambda_{ma}&= \frac{a}{b} \left[ w_{Aa}^\female (1-\alpha^\female_\Delta) w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi +  w_{aa}^\female w_a^\male c \right] / (2 w_A^\female) \\
-\chi_{mA}&= \frac{a}{b} \frac{R}{2} \left[   w_{Aa}^\female (1+\alpha^\female_\Delta) w_a^\male c \right] / w_a^\female\\ 
-\chi_{ma}&= \frac{a}{b} \frac{R}{2} \left[ w_{Aa}^\female (1-\alpha^\female_\Delta) w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi \right] / w_A^\female
-\end{align}
-\end{subequations}
-
-\noindent
-where
-
-\begin{subequations}
-\begin{align}
-a &= w_a^\female \phi + w_A^\female \psi \\
-b &= w_{AA}^\female \left[ w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \right] \phi^2 + w_{Aa}^\female \left[ w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) + w_{aa}^\male w_a^\male \right] \psi \phi + w_{aa}^\female \left( w_{aa}^\male w_a^\male \right) \psi^2\\
-%c &= w_{Aa}^\male (1-\alpha^\male_\Delta) \phi \left[ w_{Aa}^\male (1+\alpha^\male_\Delta) \phi \right] + w_{Aa}^\male\phi \left[ 2w_{AA}^\male + w_{aa}^\male (1+\alpha^\male_\Delta) \right] \psi + w_{aa}^\male \psi \left(2w_{AA}^\male \psi \right) \\
-c &= w_{Aa}^\male (1-\alpha^\male_\Delta) \phi + 2w_{aa}^\male \psi
-\end{align}
-\end{subequations}
-
-As with equilibrium (B), haploid selection again modifies invasion fitnesses by altering the sex ratio and the diploid genotypes of females and directly selecting upon female gametes.
-The only difference is that resident XX females are no longer always homozygote $AA$ and males are no longer always heterozygote $Aa$.
-Thus the effect of haploid selection in males is reduced, as is the difference in fitness between neo-W haplotypes and resident X haplotypes, as both can be on any diploid or haploid background.
-
-The other terms are easier to interpret in the absence of haploid selection.
-For instance, without haploid selection, the neo-W-$A$ haplotype spreads ($\lambda_{mA}>1$) if and only if
-
-\begin{equation}\label{eq:BeqWAspread}
-2(w_{Aa}^\female-w_{aa}^\female)w_{aa}^\male \psi^2 > (w_{AA}^\female-w_{Aa}^\female)w_{Aa}^\male \phi (\phi-\psi)
-\end{equation}
-
-\noindent  
-where $\phi-\psi=w_{AA}^\female w_{Aa}^\male-w_{aa}^\female w_{aa}^\male$ and both $\phi$ and $\psi$ are positive when equilibrium (A) is stable. 
-In contrast to equilibrium (B), a neo-W haplotype can spread under purely sexually-antagonistic selection  ($w_{aa}^\female<w_{Aa}^\female<w_{AA}^\female$ and $w_{AA}^\male<w_{Aa}^\male<w_{aa}^\male$).
-The neo-W-$A$ can spread as long as it becomes associated with females that bear more $A$ alleles than observed at equilibrium (A). 
-%In this case, the neo-W-$A$ haplotype can spread, despite producing a lot of $Aa$ daughters by obtaining the $a$ from Y-gametes, when $aa$ females, which the neo-W-$A$ never makes, are strongly selected against.
-%This can be intuited from the fact that \eqref{eq:BeqWAspread} will be more easily met when $w_{Aa}^\female-w_{aa}^\female\approx w_{Aa}^\female$ and $w_{AA}^\female-w_{Aa}^\female\approx 0$, implying $w_{aa}^\female \approx 0$ and $w_{Aa}^\female\approx w_{AA}^\female$ (although this is complicated by the fact that $w_{aa}^\female$ and $w_{Aa}^\female$ affect $\phi$ and $\psi$ too, the intuition holds).
-
-Without haploid selection, the neo-W-$a$ haplotype spreads ($\lambda_{ma}>1$) if and only if
-
-\begin{equation}\label{eq:BeqWaspread}
-(w_{aa}^\female + w_{Aa}^\female-2w_{AA}^\female)w_{Aa}^\male \phi^2 + (w_{aa}^\female-w_{Aa}^\female)(w_{Aa}^\male+2w_{aa}^\male) \phi \psi >0
-\end{equation}
-
-\noindent
-This condition cannot be met with purely sexually antagonistic selection (as both terms on the left-hand side would then be negative), but it can be met under other circumstances. 
-For example, with overdominance in males there is selection for increased $A$ frequencies on X chromosomes in males, which are always paired with Y-$a$ haplotypes.
-Directional selection for $a$ in females can then maintain a polymorphism at the $\textbf{A}$ locus on the X.
-This scenario selects for a modifier that increases recombination between the sex chromosomes \citep[e.g., blue region of Figure 2d in][]{Otto2014} and facilitates the spread of neo-W-$a$ haplotypes, which create more females bearing more $a$ alleles than the ancestral X chromosome does.
-
-\subsubsection*{Role of Haploid Selection with Tight Linkage}
-
-Haploid selection generally expands the conditions under which neo-W alleles can spread within ancestral systems that have evolved tight linkage between the sex-determining locus and a selected locus ($r \approx 0$).
-First, haploid selection can allow a polymorphism to be maintained when it would not under diploid selection alone (e.g., with directional selection in diploids). 
-In cases of ploidally-antagonistic selection, where there is a balance between alleles favored in the haploid stage and the diploid stage, neo-W alleles - even unlinked alleles - can spread (Figure \ref{fig:regionPloidAntag}).
-Second, even when diploid selection could itself maintain a polymorphism, haploid selection can increase the conditions under which transitions among sex chromosomes are possible.
-Of particularly importance, when selection is sexually-antagonistic in diploids ($s^\female s^\male <0$ and $0<h^\Hermaphrodite<1$), an unlinked neo-W ($R=1/2$) cannot invade unless there is also haploid selection (see proof in supplementary \textit{Mathematica} file; Figures \ref{fig:SexAntagTighter} and \ref{fig:SexAntagTighterMaleDrive}).
-More generally, haploid selection alters the conditions under which neo-W chromosomes can spread (compare Figures \ref{fig:regionMaleDrive}-\ref{fig:regionFemaleGS} to Figure \ref{fig:regionplots}).
-
-%[SALLY:  I think that is enough, but we could add somewhere??: "Without haploid selection, unlinked neo-W alleles ($R=1/2$) can invade only under certain conditions, requiring either overdominance in males or underdominance in females (see proof in supplementary \textit{Mathematica} file).?
-Note that underdominance in females with directional selection in males can lead to the spread of unlinked neo-W?s, but only from equilB (only $\lambda_{ma}$ is greater than one in this case).]
-
-Male haploid selection in favour of the $a$ allele ($\alpha_{\Delta}^\male<0$, $w_{A}^\male<w_{a}^\male$) generates male-biased sex ratios at equilibria (A) and (B), where Y-$a$ is fixed ($\hat{p}_{Y}^\male=0$).
-Male-biased sex-ratios facilitate the spread of neo-W-$A$ and neo-W-$a$ haplotypes (increasing $\lambda_{mA}$ and $\lambda_{ma}$). 
-Panels A-C in Figures \ref{fig:regionMaleDrive} and \ref{fig:regionMaleGS} show that neo-W haplotypes tend to spread for a wider range of parameters when sex ratios are male biased, compared to Figure \ref{fig:regionplots} without haploid selection.
-By contrast, male haploid selection in favour of the $A$ allele generates female-biased sex ratios and reduces $\lambda_{mA}$ and $\lambda_{ma}$, as demonstrated by panels D-F in Figures \ref{fig:regionMaleDrive} and \ref{fig:regionMaleGS}.
-
-Female haploid selection generates direct selection on the neo-W-$A$ and neo-W-$a$ haplotypes as they spread in females. 
-Thus, female haploid selection in favour of the $a$ allele tends to increase $\lambda_{ma}$ and decrease $\lambda_{mA}$, as shown by panels A-C in Figures \ref{fig:regionFemaleDrive} and \ref{fig:regionFemaleGS}.
-Conversely, female haploid selection in favour of the $A$ allele increases $\lambda_{mA}$ and decreases $\lambda_{ma}$, see panels D-F in Figures \ref{fig:regionFemaleDrive} and \ref{fig:regionFemaleGS}.
-
-Thus, the impact of haploid selection on sex chromosome transitions must be considered as two sides of a coin: it can generate sex ratio biases that drive sex chromosome transitions to equalize the sex ratio, but it can also drive in new sex chromosomes and thereby cause sex ratios to become biased.
-
-%\subsubsection*{Tight Linkage and Haploid Selection}
-
-%With tight linkage, haploid selection generally expands the conditions under which neo-W alleles can spread. 
-%For example, when selection is sexually-antagonistic in diploids ($s^\female s^\male <0$ and $0<h^\Hermaphrodite<1$) an unlinked neo-W ($R=1/2$) cannot invade unless there is also haploid selection (Figures \ref{fig:SexAntagTighter} and \ref{fig:SexAntagTighterMaleDrive}).
-%Secondly, with haploid selection, overdominance ($w_{aa}^\Hermaphrodite<w_{Aa}^\Hermaphrodite$ \& $w_{AA}^\Hermaphrodite<w_{Aa}^\Hermaphrodite$) is not required for neo-W-$a$ haplotypes to spread ($\lambda_{ma}>1$) (Figures \ref{fig:regionMaleDrive}-\ref{fig:regionFemaleGS}).
-%Haploid selection and overdominance allow unlinked neo-W alleles to invade even when there is tight linkage between the ancestral SDR and the selected locus (Figure \ref{fig:loose_invades_tight}).
-%Finally, haploid selection can maintain a polymorphism in the face of directional selection in male and female diploids (ploidally-antagonistic selection). 
-%When selection is ploidally-antagonistic, neo-W alleles often spread, for at least some values of $R$ (Figure \ref{fig:regionPloidAntag}).
-
-%As discussed above, male haploid selection alters the sex ratio and the alleles carried by male gametes that female gametes pair with. 
-%Male haploid selection in favour of the $a$ allele ($\alpha_{\Delta}^\male<0$, $w_{A}^\male<w_{a}^\male$) generates male-biased sex ratios at equilibria (A) and (B), where Y-$a$ is fixed ($\hat{p}_{Y}^\male=0$).
-%Male-biased sex ratios facilitate the spread of neo-W-$A$ and neo-W-$a$ haplotypes (increasing $\lambda_{WA}$ and $\lambda_{Wa}$). 
-%Panels A-C in Figures \ref{fig:regionMaleDrive} and \ref{fig:regionMaleGS} show that neo-W haplotypes tend to spread for a wider range of parameters when sex ratios are male biased, compared to Figure \ref{fig:regionplots} without haploid selection.
-%By contrast, male haploid selection in favour of the $A$ allele generates female-biased sex ratios and reduces $\lambda_{WA}$ and $\lambda_{Wa}$, as demonstrated by panels D-F in Figures \ref{fig:regionMaleDrive} and \ref{fig:regionMaleGS}.
-
-%Female haploid selection generates direct selection on the neo-W-$A$ and neo-W-$a$ haplotypes as they spread in females. 
-%Thus, female haploid selection in favour of the $a$ allele tends to increase $\lambda_{Wa}$ and decrease $\lambda_{WA}$, as shown by panels A-C in Figures \ref{fig:regionFemaleDrive} and \ref{fig:regionFemaleGS}.
-%Conversely, female haploid selection in favour of the $A$ allele increases $\lambda_{WA}$ and decreases $\lambda_{Wa}$, see panels D-F in Figures \ref{fig:regionFemaleDrive} and \ref{fig:regionFemaleGS}.
-
-%Without haploid selection this reduces to
-%\begin{subequations}
-%\begin{align}
-%\lambda_{mA}&= \frac{a}{b} \left[w_{AA}^\female w_{Aa}^\male \phi / 2 + w_{Aa}^\female \frac{c}{d}\right]  \\
-%\lambda_{ma}&= \frac{a}{b} \left[w_{Aa}^\female w_{Aa}^\male \phi / 2 +  w_{aa}^\female \frac{c}{d}\right] \\
-%\chi_{mA}&= \frac{a}{b} R \left[ w_{Aa}^\female \frac{c}{d} \right] \\ 
-%\chi_{ma}&= \frac{a}{b} R \left[ w_{Aa}^\female w_{Aa}^\male \phi / 2 \right] 
-%\end{align}
-%\end{subequations}
-
-%These simplify considerably when there is no haploid selection:
-%
-%\begin{subequations}
-%\begin{align}
-%\lambda_{mA}&= \frac{(\phi + \psi)[(w_{AA}^\female + w_{Aa}^\female ) w_{Aa}^\male \phi + 2 w_{Aa}^\female w_{AA}^\male \psi ]}{2 (w_{AA}^\female w_{Aa}^\male \phi^2 + \psi(w_{Aa}^\female(w_{AA}^\male + w_{Aa}^\male)\phi + w_{aa}^\female w_{AA}^\male \psi)}\\
-%\lambda_{ma}&=  \frac{(\phi + \psi)[(w_{aa}^\female + w_{Aa}^\female ) w_{Aa}^\male \phi + 2 w_{aa}^\female w_{AA}^\male \psi ]}{2 (w_{AA}^\female w_{Aa}^\male \phi^2 + \psi(w_{Aa}^\female(w_{AA}^\male + w_{Aa}^\male)\phi + w_{aa}^\female w_{AA}^\male \psi)}\\
-%\chi_{mA}&= R \frac{(\phi + \psi) w_{Aa}^\female w_{AA}^\male}{2 (w_{AA}^\female w_{Aa}^\male \phi^2 + \psi(w_{Aa}^\female(w_{AA}^\male + w_{Aa}^\male)\phi + w_{aa}^\female w_{AA}^\male \psi)} \\ 
-%\chi_{ma}&= R \frac{(\phi + \psi) w_{Aa}^\female w_{Aa}^\male}{2 (w_{AA}^\female w_{Aa}^\male \phi^2 + \psi(w_{Aa}^\female(w_{AA}^\male + w_{Aa}^\male)\phi + w_{aa}^\female w_{AA}^\male \psi)}\\
-%\end{align}
-%\end{subequations}
-%
-%\begin{subequations}
-%\begin{align}
-%\lambda_{mA}&= [( w_{AA}^\female + w_{Aa}^\female ) w_{Aa}^\male \phi + 2 w_{Aa}^\female w_{AA}^\male \psi] a \\
-%\lambda_{ma}&=  [(w_{aa}^\female + w_{Aa}^\female ) w_{Aa}^\male \phi + 2 w_{aa}^\female w_{AA}^\male \psi ] a\\
-%\chi_{mA}&= R w_{Aa}^\female (w_{Aa}^\male \phi + 2 w_{AA}^\male \psi) c \\ 
-%\chi_{ma}&= R w_{Aa}^\female w_{Aa}^\male \phi c \\
-%\end{align}
-%\end{subequations}
-%\noindent
-%where 
-%$c = \frac{\phi + \psi}{2 [w_{AA}^\female w_{Aa}^\male \phi^2 + \psi(w_{Aa}^\female(w_{AA}^\male + w_{Aa}^\male)\phi + w_{aa}^\female w_{AA}^\male \psi]}$ and $\phi$ and $\psi$ are evaluated with $\alpha^{\Hermaphrodite}=1/2$ and $w_a^\Hermaphrodite=w_A^\Hermaphrodite=1$.
-
-%With $R=0$ the two eigenvalues are $\lambda_{mA}$ and $\lambda_{ma}$.
-%The neo-W can then invade on the $A$ background when $\lambda_{mA}>1$ and the neo-W can invade on the $a$ background when $\lambda_{ma}>1$.
-%Even in this case it is difficult to see from equation \ref{Ainvasion} when the neo-W will invade.
-%Below we discuss why $\lambda_{mA}$ and $\lambda_{ma}$ might be larger than one and confirm the logic numerically.
-%
-%
-%For simplicity, consider the case of no haploid selection.
-%A polymorphism at the $\mathbf{A}$ locus then requires sexually-antagonistic selection \citep{vanDoorn:2007eu}.
-%Given that $a$ is fixed on the Y, one can consider the $a$ allele `male beneficial' and the $A$ allele to be `female beneficial'. 
-%Because X chromosomes spend some time in males the frequency of $A$ on the X can reach an intermediate equilibrium (equilibrium A).
-%
-%We can therefore reason that when a neo-W invades equilibrium (A), it is likely to spread on the $A$ background as W chromosomes are always in females.
-%The neo-W can outcompete the ancestral, `comprimising' X because it can specialize on females by fixing the `female beneficial' allele.  
-%We call this the `sex-specialist hypothesis'.
-%This hypothesis should only work when the benefit of specializing outweighs the cost of bringing Y chromosomes into females (the neo-W is epistatically dominant over the X/Y locus).
-%
-%One could also reason that, when the neo-W spreads, it does so precisely because it brings Y chromosomes, and their associated alleles, into females, something the X cannot do.
-%However, this requires a somewhat particular (perhaps `perverse') equilibrium, where XX females do worse than XY females despite associations on the X and Y being built up by selection.
-%One example of such a perverse equilibrium is produced by overdominance in both sexes.
-%Overdominance in females selects for an allele frequency of 0.5 on the X ($A$ and $a$ equally frequent, maximizing the number of heterozygotes). 
-%However, given that $a$ is fixed on the Y, overdominance in males selects for the X to become more associated with the $A$. 
-%Thus, a compromising equilibrium is reached on the X chromosome and females fitness suffers due to the overproduction of $AA$ homozygotes.
-%This sets up a scenario in which a neo-W can invade on the $a$ background, despite the fact that $a$ is fixed on the Y and in that sense `male beneficial'.
-%We call this the `perverse hypothesis'.
-%
-%Figure \ref{fig:Region_Plots} shows where the sex-specialist (red) and perverse (blue) hypotheses are valid.
-%The left panel demonstrates that both hypotheses can be simultaneously valid with overdominance in both sexes and sex differences in selection, which overlaps the parameter region where there is selection for increased recombination between the sex chromosomes \citep[compare with figure 2a in][]{Otto2014}.
-%The right panel shows that the perverse hypothesis is no longer valid when selection is exactly the same in both sexes, despite the fact that there is selection for increased recombination between the sex chromosomes with sufficiently strong overdominance \citep[compare with figure 3 in][]{Otto2014}.
-%
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%Sex-specialist vs perverse hypotheses
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\includegraphics[width=0.45\linewidth]{regionplot_2a}
-%\includegraphics[width=0.45\linewidth]{regionplot_3}\\
-%\caption{
-%Numerical exploration of where sex-specialist (red) and perverse (blue) hypotheses are valid, i.e., where an internally stable resident equilibrium can be invaded by a neo-W that is perfectly linked with the allele not fixed on the Y (red) or the allele that is fixed on the Y (blue).
-%\textbf{(Left)}
-%The perverse equilibrium is only valid with overdominance while the sex-specialist hypothesis is valid over the entire range shown.
-%Both hypotheses are simultaneously valid over much of the parameter space where increased recombination between the sex chromosomes is selected \citep[][figure 2a]{Otto2014}.
-%\textbf{(Right)}
-%Only the sex-specialist hypothesis is valid with no sex-differences in selection, despite selection for increased recombination between the sex-chromosomes with strong overdominance \citep[][figure 3]{Otto2014}.
-%Parameters: $w_{Aa}^\Hermaphrodite = 1$, $w_a^\Hermaphrodite = w_A^\Hermaphrodite = 1$, $\alpha^\Hermaphrodite = 1/2$, $r=R=0$, and in left panel $w_{aa}^\female = w_{AA}^\female = 0.6$.
-%}
-%\label{fig:Region_Plots}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section*{Supplementary Figures}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Both neo-W haplotypes can spread, in the absence of haploid selection, when there is overdominance
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-\centerline{\includegraphics[width=\linewidth]{PositionPlot_Overdominance}}
-\caption{
-Neo-W alleles can spread when loci under diploid selection are tightly linked to the ancestral sex determining locus ($r\approx0$). 
-In panels A and B, the $a$ allele is favoured in females ($w_{aa}^\female=1.05$, $w_{Aa}^\Hermaphrodite=1$, $w_{AA}^\female=0.85$) and selection in males is overdominant ($w_{aa}^\male=w_{AA}^\male=0.75$).
-In panels C and D, selection in males and females is overdominant ($w_{aa}^\female=w_{AA}^\female=0.6$, $w_{aa}^\male=0.5$, $w_{AA}^\male=0.7$, $w_{Aa}^\Hermaphrodite=1$).
-There is no haploid selection $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
-These parameters are marked by daggers in Figure \ref{fig:regionplots}B and C, which show that neo-W invasion is expected for any $R$ ($\lambda_{WA},\lambda_{Wa}>1$) when the $a$ allele is nearly fixed on the Y (black lines in this figure; not stable for $r>>0$).
-Equilibria where the $A$ allele is more common among Y-bearing male gametes can also be stable and allow neo-W invasion for these parameters (blue lines). 
-The weak selection approximation holds when all recombination rates are large relative to selection (around 0 in panels A and C), in which case, in the absence of haploid selection, neo-W alleles should spread if and only if they are more tightly linked to the selected locus (positive invasion fitness if and only if the selected locus is in the grey region).
-However, when linkage is tight (panels B and D and when the selected locus is near the SDRs in all panels), this weak selection prediction can break down. 
-}
-\label{fig:positionOverdominance}
-\end{figure}
-
-\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Both neo-W haplotypes can spread, in the absence of haploid selection, when there is overdominance
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-\centerline{\includegraphics[width=\linewidth]{Temporal_Overdominance}}
-\caption{
-Following invasion by a neo-W allele, there can be a complete transition to a new sex-determination system, maintenance of polymorphism at both ancestral-XY and neo-ZW sex determining regions, or loss of the new sex-determining allele.
-Here we plot the frequency of the neo-W allele among female gametes; as the neo-W reaches frequency $0.5$, polymorphism at the ancestral XY locus is lost with Y becoming fixed such that sex is determined only be the ZW allele carried by a female gamete.
-Panels A, C and D show cases where a steady state is reached with the neo-W at a frequency below $0.5$, in which case ancestral-X and Y alleles also both segregate. 
-In all cases, we assume that the $a$ allele is initially more common than the $A$ allele on the Y (Y-$a$ is fixed when $r=0$). 
-When $r>0$ (panels B and D), Y-$A$ haplotypes created by recombination can become more common than Y-$a$ haplotypes as the neo-W spreads.
-In B, this leads to loss of the neo-W and the system goes to an equilibrium with X-$a$ and Y-$A$ haplotypes fixed (equilibrium $A'$), such that all females have the high fitness genotype $aa$ and all males are $Aa$.
-For the parameters in B, neo-W alleles have negative invasion fitness when the Y-$A$ haplotype is ancestrally more common than Y-$a$ (see blue lines in Figure \ref{fig:positionOverdominance}A and  \ref{fig:positionOverdominance}B near the ancestral SDR).
-In contrast, the neo-W is not lost in panel D as it is favoured near $r\approx0$ (see blue lines in Figure \ref{fig:positionOverdominance}C and  \ref{fig:positionOverdominance}D near the ancestral SDR).
-Fitness parameters are the same as in Figure \ref{fig:positionOverdominance}; in panels A and B the $a$ allele is favoured in females ($w_{aa}^\female=1.05$, $w_{Aa}^\Hermaphrodite=1$, $w_{AA}^\female=0.85$) while there is overdominance in males ($w_{aa}^\male=w_{AA}^\male=0.75$) and in panels C and D, there is overdominance in both sexes ($w_{aa}^\female=w_{AA}^\female=0.6$, $w_{aa}^\male=0.5$, $w_{AA}^\male=0.7$, $w_{Aa}^\Hermaphrodite=1$).
-These parameters are marked by a dagger in Figure \ref{fig:regionplots}. 
-Here, there is no haploid selection $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
-}
-\label{fig:temporalOverdominance}
-\end{figure}
-
-\begin{figure}[!h]
-\centering
-\centerline{\includegraphics[width=1.5\linewidth]{PositionPlot_SexAntagTighter_MaleDrive}}
-\caption{
-When there is sexually-antagonistic selection and haploid selection, a neo-W may invade for any $R$.
-Panel A shows that the invasion fitness of a neo-W is positive where linkage is tight, even when $r<R$ (unshaded region).
-In panel B, we vary the recombination rate between the neo-W and the selected locus ($R$) for a fixed recombination rate between the ancestral-SDR and the selected locus ($r=0.005$).
-Coloured markers show recombination rates for which the temporal dynamics of neo-W invasion are plotted in panel C (black $R=0.001$, red $R=0.02$, blue $R=0.1$, green $R=0.5$). 
-The diploid selection parameters used in this plot are the same as in Figure \ref{fig:SexAntagTighter}. 
-There is also meiotic drive in males favouring $a$ ($\alpha_{\Delta}^\male=-0.08$), this full set of parameters is marked by an asterisk in Figure \ref{fig:regionMaleDrive}A.
-When $R=0.5$ (green curve), the neo-W does not reach fixation and X,Y,Z, and W alleles are all maintained in the population, see Figure \ref{fig:freqAll}C.
-}
-\label{fig:SexAntagTighterMaleDrive}
-\end{figure}
-
-\begin{figure}[!h]
-\centering
-\centerline{\includegraphics[width=\linewidth]{Region_Plot_combined_MaleDrive}}
-\caption{
-Meiotic drive in males affects whether neo-W-$A$ and neo-W-$a$ haplotypes spread when the ancestral-XY locus is tightly linked to a locus under selection ($r=0$). 
-We vary the fitness of male homozygotes relative to heterozygotes ($w_{Aa}^\Hermaphrodite=1$) and only consider stable equilibria at which both \textbf{A} locus allele are maintained and the $a$ allele is initially fixed on the Y, region outlined.
-In panels A-C, meiotic drive in males favours the $a$ allele ($\alpha_{\Delta}^\male=-0.16$), creating male-biased sex ratios and generally increasing $\lambda_{WA}$ and $\lambda_{Wa}$. 
-By contrast, $\lambda_{WA}$ and $\lambda_{Wa}$ tend to be reduced when meiotic drive in males favours the $A$ allele ($\alpha_{\Delta}^\male=0.16$), panels D-F. 
-We consider three forms of selection in females: directional selection in favour of the $A$ allele (panels A and D, $w_{aa}^\female=0.85$, $w_{AA}^\female=1.05$), direction selection in favour of the $a$ allele (panels B and E, $w_{aa}^\female=1.05$, $w_{AA}^\female=0.85$), and overdominance (panels C and F, $w_{aa}^\female=w_{AA}^\female=0.6$).
-%\textcolor{red}{Panel F mislabelled, should have $\lambda_{Wa}>1$ \& $\lambda_{WA}<1$ as the upper label that has the line.}
-}
-\label{fig:regionMaleDrive}
-\end{figure}
-
-\newpage
-\begin{figure}[!h]
-\centering
-\centerline{\includegraphics[width=\linewidth]{Region_Plot_combined_MaleGS}}
-\caption{
-Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is male gametic competition at a locus that is tightly linked to the ancestral-XY locus.
-Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in Figure \ref{fig:regionMaleDrive}. 
-The $a$ allele is favoured during male gametic competition in Panels A-C ($w_{a}^\male=1.16$, $w_{A}^\male=1$), which creates male biased sex ratios and increases $\lambda_{WA}$ and $\lambda_{Wa}$. 
-On the other hand, the $A$ allele is favoured during male gametic competition in Panels D-F ($w_{a}^\male=1$, $w_{A}^\male=1.16$) and $\lambda_{WA}$ and $\lambda_{Wa}$ tend to be reduced. 
-Compared to the meiotic drive parameters in Figure \ref{fig:regionMaleDrive}, the effect of these male gametic competition parameters on the sex ratio is smaller. 
-For example, in Figure \ref{fig:regionMaleDrive}A-C, the ancestral sex ratio is $\alpha^\male=0.58$ at equilibrium (B) and in panels A-C of this plot, the ancestral sex ratio is $w_{a}^\male/(w_{A}^\male+w_{a}^\male)=0.537$ at equilibrium (B).
-}
-\label{fig:regionMaleGS}
-\end{figure}
-
-\begin{figure}[!h]
-\centering
-\centerline{\includegraphics[width=\linewidth]{Region_Plot_combined_FemaleDrive}}
-\caption{
-Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is female meiotic drive at a locus that is tightly linked to the ancestral-XY locus.
-Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in Figure \ref{fig:regionMaleDrive} and \ref{fig:regionMaleGS}. 
-The $a$ allele is favoured by meiotic drive in females in Panels A-C ($\alpha_{\Delta}^\female=-0.16$), which increases $\lambda_{Wa}$ and decreases $\lambda_{WA}$. 
-Female meiotic drive in favour of the $A$ allele (panels D-F, $\alpha_{\Delta}^\female=-0.16$) has the opposite effect. 
-}
-\label{fig:regionFemaleDrive}
-\end{figure}
-
-\begin{figure}[!h]
-\centering
-\centerline{\includegraphics[width=\linewidth]{Region_Plot_combined_FemaleGS}}
-\caption{
-Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is female gametic competition at a locus that is tightly linked to the ancestral-XY locus.
-Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in Figure \ref{fig:regionMaleDrive}, \ref{fig:regionMaleGS}, and \ref{fig:regionFemaleDrive}. 
-The $a$ allele is favoured during female gametic competition in females in Panels A-C ($w_{a}^\female=1.16$, $w_{A}^\female=1$), which increases $\lambda_{Wa}$ and decreases $\lambda_{WA}$. 
-The $A$ allele is favoured during gametic competition in panels D-F ($w_{a}^\female=1$, $w_{A}^\female=1.16$), giving the opposite effect on $\lambda_{Wa}$ and $\lambda_{WA}$. 
-}
-\label{fig:regionFemaleGS}
-\end{figure}
-
-\begin{landscape}
-\begin{figure}[!h]
-\centering
-\centerline{
-\includegraphics[width=\linewidth]{All_plot_combined_PloidAntag}
-}
-\caption{
-A-D show when each of the neo-W haplotypes invade an internally stable equilibrium with $a$ fixed on the Y (found by setting $r=0$).
-The y-axis shows directional selection in diploids of both sexes, $s^\female=s^\male$, and the x-axes show sex-specific drive, $\alpha_\Delta^\Hermaphrodite$, or haploid competition, $t^\Hermaphrodite$.
-The top left and bottom right quadrants therefore imply ploidally-antagonistic selection (and these are the only places where neo-W haplotypes can invade).
-Dominance is equal in both sexes, $h^\female=h^\male=3/4$. 
-E-F show the temporal dynamics of neo-W frequency in females with parameters given by the asterisks in the corresponding A-D plot, with $r=1/200$, for four different $R$.
-Black $R=1/1000$, Red $R=2/100$, Blue $R=1/10$, Green $R=1/2$.  
-%Dashed line in E-H gives ``fixation" of neo-W (all females heterozygous ZW).
-}
-\label{fig:regionPloidAntag}
-\end{figure}
-\end{landscape}
-
-%\begin{landscape}
-\begin{figure}[!h]
-\centering
-\centerline{
-\includegraphics[width=\linewidth]{Freq_plot_combined_PloidAntag}
-}
-\caption{
-Fixation of neo-W or maintenance of multiple sex-determining systems. 
-The curves show the frequencies of the neo-W (red), ancestral-Y (blue), and $A$ allele (black) among female gametes (solid curves) and among male gametes (dashed curves). 
-In panel A, there is a complete transition from XY sex determination (XX-ZZ females and XY-ZZ males) to ZW sex determination (YY-ZW females and YY-ZZ males).  
-In panels B and C a polymorphism is maintained at both the ancestral XY locus and the neo-ZW locus, such that there are males with genotypes XY-ZZ or YY-ZZ and females with genotypes XX-ZZ, XX-ZW, XY-ZW, or YY-ZW.
-In panel A, selection is ploidally antagonistic with drive in males (parameters as in the green curve in Figure \ref{fig:SexRatioBad}B).
-In panel B, there is overdominance in both sexes and no haploid selection (parameters as in the green curve in Figure \ref{fig:temporalOverdominance}C).
-In panel C, there is sexually-antagonistic selection in diploids with drive in males (parameters as in the green curve in Figure \ref{fig:regionMaleDrive}C).
-%In Panel D there is ploidally-antagonistic selection with haploid competition in males (parameters as in the green curve of Figure \ref{fig:regionPloidAntag}F).
-In all cases, the initial equilibrium frequency has $a$ near fixation on the Y.
-}
-\label{fig:freqAll}
-\end{figure}
-%\end{landscape}
-
-\begin{figure}[!h]
-\centering
-\centerline{
-\includegraphics[width=\linewidth]{neoW_invades_tight_loose}
-}
-\caption{
-An unlinked neo-W can invade a perfectly linked system with overdominance or haploid selection.
-Here overdominance leads to a polymorphic sex-determining system.
-Before invasion the population is at equilibrium B.
-Parameters:
-}
-\label{fig:loose_invades_tight}
-\end{figure}
-
-%\begin{figure}[!h]
-%\centering
-%\centerline{
-%\includegraphics[width=\linewidth]{Sallys_R_plot.pdf}
-%}
-%\caption{
-%\textcolor{blue}{is this the one?}
-%}
-%\label{fig:lambda_R}
-%\end{figure}
-
-%\newpage
-%\textcolor{red}{
-%Add Sally's figure showing lambda for small r near equil A versus near equil B.
-Add references to this figure to appendix where we discuss whether lambdas can be greater than 1 with sexually antagonistic selection.}
-%\textcolor{blue}{not sure which one you are talking about, but see Figure \ref{fig:lambda_R} }
-%\textcolor{red}{Let's remove this for now.}
-
-%\textcolor{red}{
-%Perhaps it would also be useful to add an 8 panel figure that features ploidally antagonistic selection.
-For each type of haploid selection (gametic competition/ meiotic drive in males/females), give a regionplot where $h^\male=h^\female$, e.g., $h^\male=h^\female=0.75$ (or perhaps the value of $h$ we use in the regionplots we have, in which $w_{aa}=0.85$, $w_{Aa}=1$, $w_{AA}=1.05$).
-%Matt made a figure like this before but both Y$a$ and Y$A$ equilibria were plotted and there was no outline showing where the Y$a$ equilibrium is stable (as in Figure \ref{fig:regionplots}).
-In Matts plot the axes were $s^\Hermaphrodite$ and $\alpha_{\Delta}^\Hermaphrodite$.
-%Add an asterisk to each region plot and show invasion in another panel, using those parameters and various $R$ (e.g., in the stye of \ref{fig:temporalOverdominance}). 
-%In an email, Sally has an example of ploidally-antagonistic selection where the neo-W fixes and $R=1/2$. This would cover that case and more. }
-%\textcolor{blue}{made an attempt (Figure \ref{fig:regionPloidAntag})}
-
-%\textcolor{red}{
-%We could also give versions of Figure \ref{fig:regionplots} where there is also haploid selection of various types.
-%Haploid selection can favour $A$ or $a$, so this would involve 4x 6-panel figures.
-Started looking at this in Figure \ref{fig:regionMaleGS} and Figure \ref{fig:regionMaleDrive}, add female haploid selection.
-%Try to integrate into the discussion of haploid selection? e.g., male haploid selection ones generally show effect of sex ratio, increasing both lambdas when female biased (top rows).}
-%\textcolor{blue}{
-%these figures are now done (\ref{fig:regionMaleDrive}-\ref{fig:regionFemaleGS}) (ensuring frequencies between 0 and 1), but yet to discuss in text.}
-
-%\textcolor{red}{
-%Perhaps, for one set of parameters, we should plot the dynamics of all the different alleles.
-E.g., we could use the same parameters used in \ref{fig:SexRatioBad}.
-The main purpose would be to show what happens to the ancestral SDR during turnover.
-%We could also show an example where XY and ZW sex determining systems are both polymorphic and stable (e.g., using one of the curves in Figure \ref{fig:temporalOverdominance} and the green curve in Figure \ref{fig:SexAntagTighterMaleDrive}).
-%I think there are also examples with looser sex linkage and pollen competition that lead to a mixed sex-determination system.
-We should probably have a short section in the appendix discussing this.
-}
-%\textcolor{blue}{made an attempt with Figure \ref{fig:freqAll}, but yet to discuss in text}
+\bibliographystyle{amnatnat.bst}
+\bibliography{sex_chromosomes.bib}
 

### 2018-01-18 LaTeX/S3_Appendix.tex
moved to plos template, appendices have references that are still messed up

--- 2018-01-17 LaTeX/Turnover.tex
@@
 
+\usepackage{hyperref}
+
 \usepackage[font={scriptsize}]{caption}
@@
 
-\title{Haploid Selection, Sex Ratio Bias, and Transitions Between Sex-Determination Systems}
-\author{Michael F Scott$*^1$, Matthew M Osmond$*^2$, and Sarah P Otto$^2$}
-\date{}
-\maketitle
-\noindent
-$*$ These authors contributed equally to this work
+\setcounter{equation}{0}
+\renewcommand{\theequation}{S1.\arabic{equation}}
 
-\noindent
-$^1$ Department of Botany, University of British Columbia, \#3529 - 6270 University Boulevard, Vancouver, BC, Canada V6T 1Z4
-
-\noindent
-$^2$ Department of Zoology, University of British Columbia, \#4200 - 6270 University Boulevard, Vancouver, BC, Canada V6T 1Z4
-
-\noindent
-email: mfscott@biodiversity.ubc.ca, mmosmond@zoology.ubc.ca
-
-\noindent
-Contributions:
-
-\newpage
-\linenumbers
-\modulolinenumbers[2]
-
-\begin{abstract}
-Sex-determination systems are remarkably dynamic; many taxa display shifts in the location of sex-determining loci or the evolution of entirely new sex-determining systems. 
-Predominant theories for why we observe such transitions %in which new sex-determining systems spread by selection 
-%involve sex ratio selection or sex-specific selection (e.g., sexually antagonistic selection).
-%These studies 
-generally conclude that novel sex-determining systems are favoured by selection if they equalise the sex ratio or increase linkage with a sexually-antagonistic locus. 
-We use population genetic models to extend these theories in two ways: 
-(1) We explicitly consider selection on loci very tightly linked to the ancestral sex-determining loci, e.g., within the non-recombining region of the ancestral sex chromosomes. 
-%(1) We explicitly consider how selection on very tightly sex-linked loci influences the spread of novel sex-determiners. 
-Variation at such loci can favour the spread of new sex-determination systems in which the heterogametic sex changes (XY to ZW or ZW to XY) and the new sex-determining region is less closely linked (or unlinked) to the locus under selection, which is not predicted by previous theory.
-%With tight linkage, selection can maintain equilibria at which the allele fixed on the sex-limited chromosome (Y or W) is simultaneously favoured in the homogametic sex (XX females or ZZ males) such that heterogametic transitions (XY to ZW or ZW to XY) are favoured by selection.
-%Alternatively, a neo-W (neo-Y) locus can invade when it allows greater specialism on alleles beneficial in females (male) compared to an ancestral XX female (ZZ male), 
-(2) We also consider selection upon haploid genotypes either during gametic competition (e.g., pollen/sperm competition) or meiosis (i.e., non-Mendelian segregation); selective processes that typically occur in one sex or the other.
-%As well as having sex-specific fitness consequences, haploid selection can cause the zygotic sex ratio to become biased because sex ratios are determined by the production and fertilization success of X- versus Y-bearing pollen/sperm (or Z- versus W-bearing ovules/eggs).
-%Consequently, selection for XY to ZW transitions and ZW to XY transitions can be assymetrical when linkage between the ancestral sex-determining locus and a locus under haploid selection is tight, in which case ancestral sex ratio biases can be strong.
-%In addition, when linkage between the ancestral sex-determining locus and a locus under haploid selection is tight, sex ratio biases can be strong such that there is an asymmetry between invasion of ancestrally XY and ancestrally ZW systems because, e.g., haploid selection in males only causes biased zygotic sex ratios in an ancestrally XY system.
-We find that associations with haploid selected loci can drive transitions between sex determination systems, without requiring sexually-antagonistic selection in diploids. 
-Unexpectedly, with haploid selection, transitions between male and female heterogamety can also evolve where linkage with the sex-determining locus is weakened. 
-Furthermore, haploid selection in the heterogametic sex can cause sex ratio biases, which may increase or decrease with the spread of new sex chromosomes. 
-Thus, we find that transitions between sex-determination systems cannot be simply predicted by selection to equalise the sex ratio. 
-%These results indicate that loci experiencing haploid selection can favour the evolution of new sex-determination systems. 
-%These results indicate that favourable associations that develop between the ancestral sex-determining locus and selected loci can be broken during the spread of a new sex-determining region. 
-%Such transitions are not possible with diploid selection alone, in which case tighter linkage increases the fitness of both males and females. 
-%Notably, we find that the spread of new genetic sex-determination systems is not affected by sex ratio biases that are caused by haploid selection. 
-%A surprising result given that other determinants of sex allocation typically experience strong Fisherian sex ratio selection to equalize sex ratios. 
-%Overall, we demonstrate when and how the evolution of sex determining systems is impacted by sex ratio biases resulting from haploid selection and we show that new sex-determining regions can be favoured even if they are not closely linked with a locus under selection.
-Overall, our models reveal that transitions between sex-determination systems, particularly transitions where the heterogametic sex changes, can be driven by loci in previously unpredicted genomic locations that experience selection during diploid and/or haploid phases.
-These results predict conditions under which sex-determination systems are likely to be labile and draw novel connections with sex ratio evolution
-%These results might be reflected in the lability with which sex-determination systems evolve. %and for the factors determining the phylogenetic pattern of sex-determination systems. 
-\end{abstract}
-
-%abstract word count: $\approx$ 350
-
-\newpage
-
-\section*{Introduction}
-
-%CHECK THROUGHOUT: use of sex-determination SYSTEMS versus MECHANISMS. 
-%CHECK THROUGHOUT: use of haploid selection, gametic selection, and meiotic drive.
-
-Animals and angiosperms exhibit extremely diverse sex-determination systems \citep[reviewed in][]{Bull:1983vi,Charlesworth:2010it,Beukeboom:2014vb,Bachtrog:2014bx}. 
-Among species with genetic sex determination of diploid sexes (GSD), some taxa have heterogametic males (XY) and homogametic females (XX), including %non-monotreme?
-I think monotremes have XY but tonnes of translocations, giving: X1,X2...X6 Y1
-mammals and most dioecious plants \citep{Ming:2011iy}; whereas other taxa have homogametic males (ZZ) and heterogametic females (ZW), including Lepidoptera and birds. 
-Within several taxa, the chromosome that harbours the master sex-determining region changes. 
-For example, transitions of the master sex-determining gene between chromosomes or the evolution of new master sex-determining genes have occurred in Salmonids \citep{Li:2011fm,Yano:2012di}, Diptera \citep{Vicoso:2015hf}, and \textit{Oryzias} \citep{Myosho:2012fv}.
-%Presentation at evolution found neo sex chromosome in birds, doesn't seem to be published or bioRxiv yet (consider pers com.), title: A previously unknown neo-sex chromosome mediates plumage divergence and speciation in hybridizing birds Jason Sardell; Elizabeth Cooper; J.
-Albert C.
-Uy.
-I wonder if this is actually a fusion event though?
-In addition, many clades exhibit transitions between male (XY) and female (ZW) heterogamety, including snakes \citep{Gamble2017}, lizards \citep{Ezaz:2009tk}, eight of 26 teleost fish families \citep{Mank:2006bt}, true fruit flies \citep[Tephritids,][]{Vicoso:2015hf}, amphibians \citep{Hillis:1990gu}, the angiosperm genus \textit{Silene} \citep{Slancarova:2013dq}, the angiosperm family \textit{Salicaceae} \citep{Pucholt2015,Pucholt2017} and Coleoptera and Hemiptera \citep[][plate 2]{Beukeboom:2014vb}.
-Indeed, in some cases, both male and female heterogametic sex-determination systems can be found in the same species, as reported in houseflies \citep{Macdonald1978}, midges \citep{Thompson1971}, frogs \citep{Ogata:2007jm}, cichlid fish \citep{Ser:2010iq}, tilapia \citep{Lee2004}, sea bass \citep{Vandeputte2007}, and lab-strains of Zebrafish \citep{Liew2012,Wilson2014}.
-In addition, multiple transitions have occurred between genetic (GSD) and environmental sex-determination (ESD) systems, e.g., in reptiles and fishes \citep{Conover:1987in,Mank:2006bt,Pokorna:2009ui,Ezaz:2009tk,Pen:2010kk,Holleley:2015hc}.
-
-%NOTE: ``Bull & Charnov (1977) hypothesized that a new sex-determining gene can rapidly increase and become fixedin a population if it is linked to a gene with high adaptivevalue, and finally cause a change of the heterogametic sex.'' The Bull and Charnov paper is also the one in which the set of neutral equilibria between XY and ZW are identified (where sex ratios are equal)
-%NOTE: Vuilleumier et al. 2007 also find polymorphic sex determination can be stable.
-
-%For example, closely related species in the Medaka lineage (cite Takenhana et al. 2008) and Tilapiinae (cite Lee et al 2004, Cnaani et al 2008), citations in Beukeboom.
-
-%\textcolor{red}{Brief description of sex ratio adjustment and sexual antagonism theories:}
-
-Predominant theories accounting for the spread of new sex-determination systems by selection involve fitness differences between sexes (e.g., sexually antagonistic selection) or sex ratio selection \citep{Blaser2012, Beukeboom:2014vb,vanDoorn2014re}.
-%\citet{Bull:1977wt} shows that direct selection on new sex determination loci can allow them to spread and switch between male and female heterogamety. 
-\citet{vanDoorn:2007eu,vanDoorn:2010hu} and \citet{Muralidhar2018} have shown that new sex-determining loci can be favoured if they arise in close linkage with a locus that experiences sexual antagonism.
-Tighter linkage allows a stronger favourable association to build up between a male-beneficial allele, and a neo-Y chromosome, for example. 
-Such associations can favour a new partially-masculinizing or partially-feminizing allele \citep{Muralidhar2018}, a new master sex-determining gene \citep{vanDoorn:2007eu}, and transitions between male and female heterogamety \citep[trans-GSD transitions, ZW to XY or XY to ZW,][]{vanDoorn:2010hu}.
-However, any sexually-antagonistic loci that are more closely linked to the ancestral sex-determination locus will develop similar, favourable associations and are expected to hinder the spread of a new sex-determination system.
-%Here we extend these studies by explicitly calculating the the equilibrium allele frequencies of loci that are very tightly linked to the ancestral sex-determining region.
-
-The sex ratio is directly determined by the sex-determination system, and it has therefore been suggested that sex ratio selection is a dominant force in the evolution of sex determination (e.g., \citealt{Bull:1983vi}, p 66-67; \citealt{Beukeboom:2014vb}, Chapter 7).
-`Fisherian' sex ratio selection favours a 1:1 zygotic sex ratio when assuming that males and females are equally costly to produce \citep{Fisher:1930wy,Charnov:1982wg}.
-This follows from the fact that, for an autosomal locus, half of the genetic material is inherited from a male and half from a female \citep{West:2009we}. 
-Thus, if the population sex ratio is biased towards one sex, the average per-individual contribution of genetic material to the next generation from the opposite sex is greater. 
-Therefore, a mutant that increases investment in the rarer sex will spread via the higher per-individual contributions made by that sex. 
-%The default mode of sex ratio selection is `Fisherian' sex ratio selection, which favours equal investment in male and female offspring \citep[i.e., a 1:1 zygotic sex ratio when assuming that males and females are equally costly to produce,][]{Fisher:1930wy,Charnov:1982wg}.
-%Given that the sex-determination system can directly affect the sex ratio, we might expect Fisherian sex ratio selection to influence the spread of new sex-determination systems. 
-In the case of sex-chromosome evolution, \citet{Kozielska:2010vm} consider systems in which the ancestral sex chromosomes experience meiotic drive (e.g., where driving X or Y chromosomes are inherited disproportionately often), which causes sex ratios to become biased \citep{Hamilton:1967ts}.
-They find that new, unlinked sex-determining loci (masculinizing or feminizing mutations, i.e., neo-Y or neo-W loci) can then spread, which restore an even sex ratio.
-
-%\textcolor{red}{We add haploid selection:}
-Here we use mathematical models to find the conditions under which new sex-determination systems spread when individuals experience selection at both diploid and haploid stages. 
-Even in animal and plant species that have much larger and more conspicuous diploid phases than haploid phases, many loci experience significant haploid selection through gamete competition and/or meiotic drive \citep{Mulcahy:1996ha,JOSEPH:2004haa}.
-We use the term `meiotic drive' to refer to the biased (non-Mendelian) segregation of genotypes during gamete production (from one parent) and the term `gametic competition' to refer to selection upon haploid genotypes within a gamete/gametophyte pool (potentially from multiple parents); the term `haploid selection' encompasses both processes.
-
-% from Bai et al.
-(2016) ``[Segregation distortion] phenomenon is commonly detected via genetic mapping and has been documented in various species, including mouse (Eversley et al., 2010; Casellas et al., 2012), Drosophila (Phadnis and Orr, 2009; Larracuente and Presgraves, 2012; McDermott and Noor, 2012), Tigriopus (Pritchard et al., 2011), rice (Koide et al., 2012; Reflinur et al., 2014; Xu et al., 2014), maize (Tang et al., 2013), and cotton (Yu et al., 2011; Hulse-Kemp et al., 2015).'' Also more in that paper that might be useful.
-%Drosophila http://www.biorxiv.org/content/early/2017/02/06/106336
-Segregation distortion provides putative evidence of haploid selection and can sometimes be attributed to meiotic drive and/or gametic competition \citep{Lalanne2004,Fishman2005,Leppala2008,Leppala2013,Didion2015,Didion2016}.
-Where it has been characterized, meiotic drive generally occurs either during the production of male or female gametes only \citep{Ubeda:2005gw,Lindholm:2016cw}.
-Gametic competition is also typically sex specific, occurring primarily among male gametes, because there are typically many more pollen/sperm than required for fertilization.
-Gametic competition may be particularly common in plants, in which 60-70\% of all genes are expressed in the male gametophyte, and these genes exhibit stronger signatures of selection than random genes \citep{Borg:2009jpa,Arunkumar:2013iq,Gossmann:2014dua}.
-In addition, artificial selection pressures applied to male gametophytes are known to cause a response to selection \citep[e.g.,][]{Hormaza:1996cv,Ravikumar:2003uo,Hedhly:2004iv,Clarke:2004ir}. 
-A smaller proportion of genes are thought to be expressed and selected during competition in animal sperm, although precise estimates are uncertain \citep{Zheng:2001fi,JOSEPH:2004haa,Vibranovski:2010et}.
-Nevertheless, recent studies have demonstrated that sperm competition in animals can alter haploid allele frequencies and increase offspring fitness \citep{Immler:2014im,Alavioon2017}.
-
-There are various ways by which genes experiencing haploid selection could influence transitions between sex-determination systems. 
-If we assume that haploid selection at any particular locus predominantly occurs in one sex (e.g., meiotic drive during spermatogenesis), then such loci experience a form of sex-specific selection. 
-In this respect, we might expect that haploid selection would affect transitions between sex-determination systems in a similar manner to sex-specific diploid selection \citep[as explored by][]{vanDoorn:2007eu,vanDoorn:2010hu}.
-That is, new masculinizing mutations (neo-Y chromosomes) could be favoured via associations with alleles that are beneficial in the male haploid stage. 
-On the other hand, sex ratios can also become biased by linkage between the sex-determining region and a locus that harbours genetic variation in haploid fitness. 
-For example, there are several known cases of sex ratio bias caused by sex-linked meiotic drive alleles \citep[][Chapter 3]{Burt:2006} or selection among X- and Y-bearing pollen \citep{Lloyd:1974tz,Conn:1981uw,Stehlik:2005ul,Stehlik:2006to,Field:2012fd,Field:2013cc}.
-It is not immediately clear how the spread of new sex-determination systems would be influenced by the combination of sex ratio biases and associations between haploid selected loci and sex-determining regions.
-
-%Perhaps longer discussion of tight sex-linkage here? e.g., mention that r=0 is a particularly significant case for sex chromosomes.
-
-We find that the spread of novel sex-determiners is influenced by both Fisherian sex ratio selection and by selection on genetically-associated alleles. 
-%We find that sex ratio biases caused by haploid selection can exert Fisherian sex ratio selection upon novel sex-determiners but that their spread is also determined by selection on genetically-associated alleles.
-%Indeed, it is only when haploid-selected loci are tightly linked to the ancestral sex-determining region (and so sex ratio biases are initially large) that we see an asymmetry between selection for XY to ZW transitions and ZW to XY transitions (e.g., because haploid selection in males only causes biased zygotic sex ratios in an ancestrally XY system).
-Surprisingly, Fisherian sex ratio selection does not dominate; it is possible for selection on linked alleles to drive turnover between sex-determining systems despite causing increasingly biased sex ratios.
-In addition to considering haploid selection, another novel development in our model is that we consider loci that are in very tight linkage with the ancestral sex-determining region. 
-Because sex-determining loci are often found within a region of suppressed recombination, there can be a significant number of tightly linked loci. 
-We find that loci linked with the ancestral sex-determining region can drive transitions in which the heterogametic sex changes, even when the neo-sex-determining locus is less closely linked to loci under selection (either including haploid selection or not).
-%Such transitions are not favoured in models lacking tight linkage and/or haploid selection. 
-%Secondly, we allow sex-specific haploid selection to occur on a locus in tight or loose linkage with the ancestral sex-determining region. 
-%In addition, when linkage between the ancestral sex-determining locus and a locus under haploid selection is tight, sex ratio biases can be strong such that there is an asymmetry between invasion of ancestrally XY and ancestrally ZW systems because, e.g., haploid selection in males only causes biased zygotic sex ratios in an ancestrally XY system.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Model}
-%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Model Outline
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-\centerline{\includegraphics[width=\linewidth]{Sex_determination_outline.pdf}}
-\caption{
-Outline of model features. 
-Panel A: Recombination rate parameters between the ancestral-sex-determining locus (here, assumed to have X or Y alleles), a locus under selection (\textbf{A}, with alleles $A$ and $a$), and a neo-sex-determining locus (\textbf{M}, with alleles $M$ and $m$).
-If $r<1/2$, then associations between ancestral-sex-determining alleles (X and Y) and \textbf{A} locus alleles can be maintained past recombination in males.
-Panel B: Haploid selection is often sex-specific, occurring during haploid production or competition in either males or females. 
-For example, haploid selection in males only is represented by the dashed circle.  
-If X or Y alleles remain associated with alleles that experience haploid selection in males ($r<1/2$), then zygotic sex ratios can become biased because either X or Y male gametes/gametophytes will be abundant after haploid selection.
-However, the zygotic sex ratio is not biased by male haploid selection in ZW sex-determination systems. 
-Similarly, zygotic sex ratio biases can occur if haploid selected alleles are associated with neo-sex-determining alleles ($M$ and $m$, i.e., if $R<1/2$). 
-Panel C: During cis-GSD transitions (XY to XY or ZW to ZW, without loss of generality we assume ancestral XY sex determination here), a neo-Y allele spreads to pseudo-fixation (its maximum frequency among male gametes) and the the ancestral-Y allele is lost.
-Panel D: During trans-GSD transitions (XY to ZW or ZW to XY), a neo-W allele spreads to pseudo-fixation (its maximum frequency among female gametes) and the ancestral-X allele is lost.
-Neo-W mutations allow Y-associated alleles into females, which may impede or aid their spread.
-}
-\label{fig:model_outline}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\textcolor{red}{Change all  $\alpha^\Hermaphrodite$ to $(1+\alpha_{\Delta}^\Hermaphrodite)$.}
-%\textcolor{blue}{I've attempted this everywhere except in the recursions (S.1), which seem more natural with $\alpha$'s.
-I've run into trouble in equation S.8c,d -- I think we should check the Mathematica results to be sure we haven't made a typo.
-This also introduced an extra 1/2 in S.6c,d that might need to be explained.}
-%\textcolor{red}{hmm, not sure.
-This was an idea from Sally, I think in response to terms like $2 \alpha^\Hermaphrodite$ and $2(1-\alpha^\Hermaphrodite)$.
-It's possible that it makes other equations less easy to understand.
-My previous (not explained) logic was to use $w$ and $\alpha$ for strong selection and $s$, $t$, and $\alpha_\Delta$ for weak selection.
-Just to check, I should have written $\alpha^\Hermaphrodite=(1+\alpha_{\Delta}^\Hermaphrodite)/2$, maybe that's where the factors of $1/2$ come from?}
-%\textcolor{blue}{shoot, i may have changed too much (i.e.
-strong selection too), but i did use the correct transformation.
-still, the form of S.8c,d seems wrong.
-I'll double check it.
-CANT FIND ANY ERRORS YET STILL HAVE A "2" IN S.8c.
-These 2s reappear in S.9 and S.10, always with $W_{AA}$.}
-
-%\textcolor{red}{Switch between $\rho$ and $\rho$ in all places because $\rho$ is used for double recombination events.}
-%\textcolor{blue}{I think we need a different variable given the $\rho$ terms in the characteristic polynomial.
-Also, where is $\rho$ used for double recombination?
-In other papers?
-Here $\rho$ is the probability of an odd number of cross-overs between the SDR and M loci.}
-%\textcolor{red}{Good point, not sure what's best for \textbf{the-term-formerly-known-as-$\rho$}.
-Yeah, Sally's written comment was something like ``$\rho$ is semi-standard notation for double recombination so it's use as a recombination rate might be confusing''.}
-
-%\textcolor{red}{Change $\zeta$ to represent zygotic sex ratio of males, consistent with $q$ and figures.}
-
-%genetic system
-We consider transitions between ancestral and novel sex-determining systems using a three-locus model, each locus having two alleles. 
-Locus \textbf{X} is the ancestral sex-determining region, with alleles $X$ and $Y$ (or $Z$ and $W$).
-Locus \textbf{A} is a locus under selection, with alleles $A$ and $a$.
-Locus \textbf{M} is a novel sex-determining region, at which the null allele ($M$) is initially fixed in the population such that sex of zygotes is determined by the genotype at the ancestral sex-determining region, \textbf{X}; $XX$ genotypes become females and $XY$ become males (or $ZW$ become females and $ZZ$ become males).
-To evaluate the evolution of new sex-determination systems, we consider the invasion, fixation, maintenance, and/or loss of novel sex-determining alleles ($m$) at the \textbf{M} locus. 
-%We only do invasion analytically though (is this sentence still ok?)
-We assume that the \textbf{M} locus is epistatically dominant over the \textbf{X} locus such that zygotes with at least one $m$ allele develop as females with probability $k$ and as males with probability $1-k$, regardless of the \textbf{X} locus genotype.
-With $k=0$, the $m$ allele is a masculinizer (i.e., a neo-Y) and with $k=1$ the $m$ allele is a feminizer (i.e., a neo-W).
-With intermediate $k$, we can interpret $m$ as an environmental sex determination (ESD) allele, such that zygotes develop as females in a proportion ($k$) of the environments they experience. 
-%We also analyze a model of maternally-controlled environmental sex-determination, where mothers with at least one $m$ allele produce daughters with probability $k$.
-
-%life-cycle
-In each generation, we census the genotype frequencies in male and female gametes/gametophytes (hereafter gametes) before gametic competition. 
-A full description of our model, including recursion equations, is given in the Appendix. 
-First, competition occurs among male gametes (sperm/pollen competition) and among female gametes (egg/ovule competition) separately. 
-Selection during gametic competition depends on the \textbf{A} locus genotype, relative fitnesses are given by $w_A^\Hermaphrodite$ and $w_a^\Hermaphrodite$ ($\Hermaphrodite \in \{\female,\male\}$; see table \ref{tab:fitnesstable}).
-%$w_{A}^\male$ and $w_{a}^\male$ for male gametes and $w_{A}^\female$ and $w_{a}^\female$ for female gametes, see table \ref{tab:fitnesstable}.
-We assume that all gametes compete for fertilization during gametic competition, which assumes a polygamous mating system. 
-Gametic competition in monogamous mating systems is, however, equivalent to meiotic drive in our model (described below), as either only alters the frequency of gametes produced by heterozygotes. 
-After gametic competition, random mating occurs between male and female gametes.
-The resulting zygotes develop as males or females, depending on their genotypes at the \textbf{X} and \textbf{M} loci. %(and the \textbf{M} genotype of their mother in the case of maternal control).
-Diploid males and females then experience selection, with relative fitnesses $w_{AA}^{\Hermaphrodite}$, $w_{Aa}^{\Hermaphrodite}$, and $w_{aa}^{\Hermaphrodite}$.
-%where $g$ is the diploid genotype at the \textbf{A} locus ($g \in \{AA, Aa, aa\}$).
-%Diploids compete with others of the same sex, where selection depends on the sex of the individual and its genotype at the \textbf{A} locus.
-The next generation of gametes is produced by meiosis, during which recombination and sex-specific meiotic drive can occur. 
-Recombination (i.e., an odd number of cross-overs) occurs between loci \textbf{X} and \textbf{A} with probability $r$, between loci \textbf{A} and \textbf{M} with probability $R$, and between loci \textbf{X} and \textbf{M} with probability $\rho$.
-Any linear order of the loci can be modelled with appropriate choices of $r$, $R$, and $\rho$ (see Figure \ref{fig:model_outline}A and Table \ref{tab:chisubstitutions}). 
-Individuals that are heterozygous at the \textbf{A} locus may experience meiotic drive; a gamete produced by $Aa$ heterozgotes of sex $\Hermaphrodite$ bears allele $A$ with probability $\alpha^\Hermaphrodite$.
-Thus, the \textbf{A} locus can experience sex-specific gametic competition, diploid selection, and/or meiotic drive.
-
-\begin{table}[ht]
-\centering
-\smallskip
-\caption{Relative fitness of different genotypes in sex $\Hermaphrodite \in \{\female,\male\}$}
-\begin{tabular}{l c }
-\hline\hline
-  Genotype & Relative fitness during gametic competition \\ [0.5ex] \hline
-  A & $w_{A}^\Hermaphrodite = 1+t^\Hermaphrodite$ \\
-  a & $w_{a}^\Hermaphrodite = 1$ \\ [0.5ex] \hline
-  Genotype & Relative fitness during diploid selection \\ [0.5ex] \hline
-  AA & $w_{AA}^\Hermaphrodite = 1+ s^\Hermaphrodite$ \\
-  Aa & $w_{Aa}^\Hermaphrodite = 1+h^\Hermaphrodite s^\Hermaphrodite$ \\
-  aa & $w_{aa}^\Hermaphrodite = 1$ \\ [0.5ex] \hline
-  Genotype & Transmission during meiosis in $Aa$ heterozygotes \\ [0.5ex] \hline
-  A & $\alpha^\Hermaphrodite=1/2+\alpha_{\Delta}^{\Hermaphrodite}/2$ \\
-  a & $1-\alpha^\Hermaphrodite=1/2-\alpha_{\Delta}^{\Hermaphrodite}/2$ \\
-  \hline \hline
-  \label{tab:fitnesstable}
- \end{tabular}
-\end{table}
-
-%Info moved above
-%what were going to do, briefly
-%With allele $M$ fixed at the \textbf{M} locus, sex is determined by locus \textbf{X} and an equilibrium is reached at locus \textbf{A}.
-%where, importantly, locus \textbf{A} can be stably polymorphic.
-%the dynamics can be described by the frequency of $A$ in gametes/gametophytes from the homogametic sex and the frequencies of $A$ in the two types of gametes/gametophytes from the heterogametic sex.
-%We then examine the ability of a rare, novel sex-determiner, $m$, to increase in frequency from this equilibrium.
-%Numerical simulations are used to examine when an invading mutation goes to fixation.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Results}
-%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The model outlined above describes both ancestrally-XY and ancestrally-ZW sex-determination systems if we relabel the two sexes as being ancestrally `heterogametic' or ancestrally `homogametic'. 
-Without loss of generality, we primarily refer to the ancestrally heterogametic sex as male and the ancestrally homogametic sex as female.
-That is, we describe an ancestral XY sex-determination system but our model is equally applicable to an ancestral ZW sex-determination system (relabelling the ancestrally-heterogametic sex as female and the ancestrally-homogametic sex as male and switching the labels of males and females throughout).
-
-%\subsection*{Turnover between sex-determination systems}
-
-\subsubsection*{Generic invasion by a neo-Y or neo-W}
-
-The evolution of a new sex-determination system requires that a rare mutant allele at the novel sex-determining locus, $m$, increases in frequency when rare. 
-The spread of a rare mutant $m$ at the \textbf{M} locus is determined by the leading eigenvalue, $\lambda$, of the system of eight equations describing the frequency of eggs and sperm carrying the $m$ allele in the next generation (equations \ref{eq:recursions}).
-%, evaluated at the above equilibrium.
-%Thus, the system describing the change in frequency of the $m$ allele consists of eight recursion equations. 
-This system simplifies substantially in a number of cases of interest. 
-Dominant neo-Y (when $k=0$) or neo-W alleles (when $k=1$) are only found in male diploids (neo-Y) or female diploids (neo-W) such that their growth rate ultimately depends only on the change in frequency of $m$-bearing gametes produced by males or by females, respectively.
-Furthermore, if the $m$ allele is fully epistatically dominant over the ancestral sex-determining system, phenotypes are not affected by the genotype at the ancestral sex-determining region (\textbf{X} locus).
-Thus, the invasion of rare dominant neo-Y or neo-W alleles is determined by the largest eigenvalue that solves the quadratic, $\lambda^2+ b \lambda + c =0$ \textcolor{blue}{(see Appendix for a discussion of other roots - or Sally's proof!)}.
-Here, $b= - (\lambda_{mA} + \lambda_{ma})+(\chi_{mA} + \chi_{ma})$ and $c = (\lambda_{mA}-\chi_{mA}) (\lambda_{ma}-\chi_{ma}) -\chi_{mA} \chi_{ma}$, where $\lambda_{mi}$ is the multiplicative growth rate (which we will call the ``haplotypic growth rate'') of the neo-sex determination allele $m$ on background $i$ without accounting for loss due to recombination, and $\chi_{mi}$ is the rate at which mutant haplotypes on background $i\in\{A,a\}$ recombine onto the other \textbf{A} locus background in heterozygotes (see Table \ref{tab:haplotype_growth}).
-The $\lambda_{mi}$ and $\chi_{mi}$, and thus the spread of the mutant $m$ allele, depend on the frequency of alleles at the \textbf{A} and \textbf{X} loci in the ancestral population. 
-In the ancestral population, it is convenient to follow the frequency of the $A$ allele among female gametes (eggs), $p^\female_X$, and among X-bearing, $p^\male_X$, and among Y-bearing, $p^\male_Y$, male gametes (sperm/pollen).
-We also track the fraction of male gametes that are Y-bearing, $q$, which may deviate from $1/2$ due to meiotic drive in males. 
-We will consider only equilibrium frequencies of alleles, $\hat{p}^\Hermaphrodite_i$, and Y-bearing male gametes, $\hat{q}$, when calculating the eigenvalues.
-
-%\textcolor{red}{I now remove the zygotic sex ratio $\zeta$ from the mean fitnesses. The mean fitnesses will have to be adjusted in a corresponding way.}
-%
-%\textcolor{red}{CHECK: DO THE HAPLOID MEAN FITNESSES HAVE TO BE IN THE DENOMINATOR? i think so, based on definitions in table S.2 (mmo)}
-
-% as there are now two 2s in the lambdas of table 2. perhaps the 2 in the denominator is needed because the frequency of males sums to one as does the frequency of females?}
-
-\begin{threeparttable}[ht]
-\centering
-\smallskip
-%\caption{Parameters determining invasion (equation \ref{eq:charpoly_neoY}) for neo-Y or neo-W alleles}
-\caption{Parameters determining invasion of mutant neo-Y and neo-W alleles into an ancestrally XY system}
-\begin{tabular}{l}
-\hline\hline
-   \noalign{\vskip 0.5ex}
-   $m$ is a neo-Y ($k=0$) \\ [0.5ex] \hline \noalign{\vskip 1ex}
-  $\lambda_{YA} = \left( 2 \zeta \right)^{-1} \left[\hat{p}_X^\female w_{A}^{\female} w_{A}^{\male} w_{AA}^{\male} + (1-\hat{p}_X^\female) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} (1+\alpha_{\Delta}^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right) $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\lambda_{Ya} = \left( 2 \zeta \right)^{-1} \left[(1-\hat{p}_X^\female) w_{a}^{\female} w_{a}^{\male} w_{aa}^{\male} + \hat{p}_X^\female w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male}(1 - \alpha_{\Delta}^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\chi_{YA} = R \left( 2 \zeta \right)^{-1} \left[ (1-\hat{p}_X^\female) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} (1+\alpha_{\Delta}^{\male}) \right]/  \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right)   $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\chi_{Ya} = R \left( 2 \zeta \right)^{-1} \left[   \hat{p}_X^\female w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male} (1 - \alpha_\Delta^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right)  $\\ [1ex] \hline
-  \noalign{\vskip 0.5ex}
-  $m$ is a neo-W ($k=1$) \\ [0.5ex] \hline \noalign{\vskip 1ex}
-  $\lambda_{WA} = \left[ 2 (1 - \zeta) \right]^{-1} \left[ \bar{p}^{\male} w_{A}^{\male} w_{A}^{\female} w_{AA}^{\female}+(1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female}(1+\alpha_{\Delta}^{\female})\right]/ \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\lambda_{Wa} = \left[ 2 (1 - \zeta) \right]^{-1} \left[ (1-\bar{p}^{\male}) w_{a}^{\male} w_{a}^{\female} w_{aa}^{\female}+\bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female}(1-\alpha_{\Delta}^{\female})\right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\chi_{WA} = R \left[ 2 (1 - \zeta) \right]^{-1} \left[ (1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female} (1+\alpha_{\Delta}^{\female}) \right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \right)  $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\chi_{Wa} = R \left[ 2 (1 - \zeta) \right]^{-1} \left[ \bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female} (1-\alpha_{\Delta}^{\female}) \right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \right) $\\ [1ex]
-  \hline \hline 
-   \end{tabular}
-      \begin{tablenotes}
-      \scriptsize
-      \item $\bar{p}^{\male}=(1-\hat{q})\hat{p}_X^\male + \hat{q}\hat{p}_Y^\male$ is the average frequency of the $A$ allele among X- and Y-bearing male gametes.
-%      \item $R$ is the probability of recombination between loci \textbf{A} and \textbf{M}.
-      \item $\zeta$ is the zygotic sex ratio (fraction male)
-      \item $\bar{w}^\Hermaphrodite$ is the mean fitness of diploids of sex $\Hermaphrodite$, see Table \ref{tab:meanfitnesses}
-      \item $\bar{w}_H^\Hermaphrodite$ is the mean fitness of haploids from sex $\Hermaphrodite$, see Table \ref{tab:meanfitnesses}
-%      \item $\bar{w}_H^\female = p_X^\female w_A^\female + (1-p_X^\female) w_a^\female$ is the mean fitness of female gametes during gametic competition
-%      \item $\bar{w}_H^\male = \bar{p}^{\male} w_A^\male + (1-\bar{p}^{\male}) w_a^\male$ is the mean fitness of male gametes during gametic competition
-%       \item $\bar{w}^\female = \{ p_X^\female w_A^\female (1-q) p_X^\male w_A^\male w_{AA}^\female + (1 - p_X^\female) w_a^\female (1-q) p_X^\male w_A^\male w_{Aa}^\female + p_X^\female w_A^\female (1-q) (1 - p_X^\male) w_a^\male w_{Aa}^\female + (1-p_X^\female) w_a^\female (1-q) (1 - p_X^\male) w_a^\male w_{aa}^\female \} / \{ \bar{w}_H^\female \bar{w}_H^\male\}$ is the mean fitness of females during diploid competition
-%       \item $\bar{w}^\male = \{ p_X^\female w_A^\female q p_Y^\male w_A^\male w_{AA}^\male + (1 - p_X^\female) w_a^\female q p_Y^\male w_A^\male w_{Aa}^\male + p_X^\female w_A^\female q (1 - p_Y^\male) w_a^\male w_{Aa}^\male + (1-p_X^\female) w_a^\female q (1 - p_Y^\male) w_a^\male w_{aa}^\male \} / \{ \bar{w}_H^\male \bar{w}_H^\male\}$ is the mean fitness of males during diploid competition
-    \end{tablenotes}
-  \label{tab:haplotype_growth}
-\end{threeparttable}
-\\
-
-%We are particularly concerned with the conditions under which a rare neo-sex-determining allele increases in frequency, which occurs when the largest eigenvalue, $\lambda$, is greater than one. 
-%If one or both of $\lambda_{mA}$ and $\lambda_{ma}$ are greater than one, indicating that at least one haplotype increases in frequency faster than recombination breaks it apart, invasion will always occur ($\lambda>1$).
-%Otherwise, invasion requires
-%\begin{equation}
-%(\lambda_{mA}-1)(\lambda_{ma}-1) - \chi_{mA} \chi_{ma}<0.
-%\end{equation}
-
-We are particularly concerned with the conditions under which a rare neo-sex-determining allele increases in frequency, which occurs when the largest eigenvalue, $\lambda$, is greater than one. 
-%If the average change in frequency of the two haplotypes that carry the $m$ allele ($Am$ and $am$) is positive, invasion will always occur, i.e., if $(\lambda_{mA} + \lambda_{ma})/2 > 1$ then $\lambda > 1$.
-The leading eigenvalue solves $f(\lambda)=\lambda^2+b\lambda+c=0$ and the Perron-Frobenius theorem guarantees that the leading eigenvalue is positive, unique, and real.  
-Since $f(\lambda_{mA})$ and $f(\lambda_{ma})$ are of opposite signs, the leading eigenvalue must fall between these two quantities and is the larger of them when $R = 0$.  
-Consequently, if both $\lambda_{mA}$ and $\lambda_{ma}$ are greater than one, then the leading eigenvalue will always be greater than one, regardless of the linkage between the neo-sex determination factor and the selected locus ($R$).
-In particular, having $\lambda_{mA} >1$ and $\lambda_{ma}>1$ thus guarantees that an unlinked sex determining factor can invade ($R=1/2$).  
-Conversely, if both $\lambda_{mA}$ and $\lambda_{ma}$ are smaller than one, then invasion can never occur.  
-Finally, if only one of  $\lambda_{mA}$ and $\lambda_{ma}$ is greater than one, the new sex determining factor can always invade when tightly linked to the selected locus ($R$ near 0).  
-Furthermore, it can be shown that the leading eigenvalue declines with $R$, and invasion requires that $R$ is sufficiently small that the following condition holds: 
-\begin{equation}\label{eq:lambdasGen}
-%\frac{\chi_{mA}}{\lambda_{mA}-1}+\frac{\chi_{ma}}{\lambda_{ma}-1}>0.
-\chi_{ma}/\left(\lambda_{ma}-1\right) + \chi_{mA}/\left(\lambda_{mA}-1\right) < 1.
-\end{equation}
-\noindent 
-This condition may or may not be satisfied for the full range of locations of the new sex determining factor, including $R=1/2$, depending on the nature of selection.  
-Interpreting this condition, if we assume that only the $mA$ haplotype has a positive growth rate when $R=0$, $\lambda_{ma}<1<\lambda_{mA}$, the first term on the left-hand side of \eqref{eq:lambdasGen} is negative and invasion requires that the $mA$ haplotype growth rate ($\lambda_{mA}-1$) and the rate at which they are produced by recombination in $ma$ haplotypes ($\chi_{ma}$) are sufficiently large relative to the $ma$ haplotype rate of decline ($1-\lambda_{ma}$) and the rate of loss of $mA$ haplotypes due to recombination ($\chi_{mA}$).
-%In other words, invasion requires that the average growth rate of the two haplotypes, weighted by the rates they are created by recombination, is positive.
-%the number of recombinants from the fitter $mA$ haplotypes is larger than that of the less fit $ma$ haplotypes, relative to their growth rates.
-
-We can draw a number of key points about the invasion of neo-Y and neo-W mutations from Table \ref{tab:haplotype_growth}. 
-First, Fisherian sex ratio selection will favour the spread of a neo-Y if the ancestral zygotic sex ratio is biased towards females, $\zeta<1/2$ (i.e., the first factor of the $\lambda_{mi}$ is greater than one for a neo-Y and less than one for a neo-W).
-However, the spread of a neo-Y (neo-W) also depends on the male (female) fitness of associated alleles (see terms involving equilibrium allele frequencies, $\hat{p}$'s).
-Second, invasion by a neo-Y (neo-W) allele does not directly depend on the fitness of female (male) diploids. %(for a given set of equilibrium allele frequencies).
-This is because a dominant neo-Y (neo-W) is always found in males (females), and therefore the frequency of the neo-Y (neo-W) allele, $m$, only changes in males (females), Figure \ref{fig:model_outline}C,D.
-Finally, invasions by a neo-Y and a neo-W are qualitatively different.
-This is because a gamete with the neo-Y always pairs with a female gamete containing an X, and develop into males, Figure \ref{fig:model_outline}C.
-By contrast, a gamete with a neo-W can pair with an X or Y male gamete, developing into a female, Figure \ref{fig:model_outline}D.
-Consequently, neo-W bearing females obtain a differerent frequency of $A$ alleles from mating (when $\hat{p}_X^\male \neq \hat{p}_Y^\male$) compared to ancestral ($MM$) females.
-
-In order to explicitly determine the conditions under which a rare neo-sex-determining allele spreads, we must calculate the equilibrium frequency of the $A$ allele (i.e., $\hat{p}^\female_X$, $\hat{p}^\male_X$, and $\hat{p}^\male_Y$) and Y-bearing male gametes ($\hat{q}$) in the ancestral population.
-Since only the \textbf{A} locus experiences selection directly, any deterministic evolution requires that there is a polymorphism at the \textbf{A} locus. 
-Polymorphisms can be maintained by mutation-selection balance or transiently present during the spread of beneficial alleles.
-However, polymorphisms maintained by selection can maintain alleles at intermediate allele frequencies for longer periods.
-Here, we focus on polymorphisms maintained by selection, where the $A$ allele reaches a stable intermediate equilibrium frequency under the ancestral sex-determination system before the neo-sex-determining allele ($m$) arises.
-Such polymorphisms can be maintained by heterozygote advantage, sexually-antagonistic selection, ploidally-antagonistic selection, or a combination \citep{Immler:2012tl}.
-We can analytically calculate the allele frequency of the $A$ allele using two alternative simplifying assumptions: 
-(1) the \textbf{A} locus is within (or tightly linked to) the non-recombining region around the ancestral SDR ($r \approx 0$) or (2) selection is weak relative to recombination ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon<<1$).
-
-\subsubsection*{Tight linkage with the ancestral sex-determining region ($r \approx 0$)}
-
-The ancestral equilibrium allele frequencies and their stability conditions are given in the appendix.
-When there is complete linkage between the ancestral sex-determining region and the \textbf{A} locus ($r=0$), either the $A$ allele or the $a$ allele must be fixed on the Y. 
-% because selection on the Y is effectively haploid an incapably of maintaining a polymorphism in the absence of frequency dependent selection. 
-Because the labelling of alleles is arbitrary, we will assume that the $a$ locus is fixed on the Y ($p^\male_Y=0$), without loss of generality. 
-If there are two alleles maintained at the \textbf{A} locus, the X can either be fixed for the $A$ allele ($\hat{p}^\female_X=\hat{p}^\male_X=1$) or polymorphic (0<$\hat{p}^\female_X, \hat{p}^\male_X$<1).
-%However, because the X is present in both males and females, there are distinct selection pressures on X's in females and X's in males, which will always be paired with an $A$ allele from the Y.
-
-We find that a neo-Y can never invade an ancestral XY system that already has tight linkage with the locus under selection ($r=0$, for details see supplementary \textit{Mathematica} file). 
-When $R=0$, a neo-Y haplotype with the same allele as the ancestral Y is neutral ($\lambda_{Ya}=1$) and does not change in frequency.
-The other neo-Y haplotype will not spread ($\lambda_{YA}<1$) given that the initial equilibrium is stable. 
-Therefore, a neo-Y mutation cannot spread ($\lambda \leq 1$, regardless of $R$) in an ancestral XY system where selected loci are within or very near the non-recombining region around the SDR.
-In essence, through tight linkage with the \textbf{A} locus, the ancestral Y becomes strongly specialized on the allele that has the highest fitness across male haploid and diploid phases. 
-Given that the ancestral Y is at this equilibrium, it is not possible for a neo-Y to create males that have higher fitness than the ancestral Y.
-
-Neo-W alleles, on the other hand, can invade an ancestral XY system under some conditions (the full invasion conditions are given in the appendix; equations \ref{Binvasion} and \ref{Ainvasion}). 
-Counterintuitively, selection on loci within the non-recombining region of the SDR can favour the invasion of a less closely linked neo-W, whatever the form of selection maintaining a polymorphism (sexually-antagonistic selection, overdominance, ploidally-antagonistic selection, or some combination, Figures \ref{fig:SexAntagTighter}, \ref{fig:temporalOverdominance}, \ref{fig:regionPloidAntag}, and \ref{fig:SexAntagTighterMaleDrive}).
-The conditions become more restrictive, however, with increasing recombination ($R$) between the new sex determining region and the selected locus.  
-The invasion of completely unlinked neo-W alleles ($R = 1/2$) can occur with overdominance in males or with haploid selection but is not possible with only sexually-antagonistic selection if selection is directional in each diploid sex (see Supplementary \textit{Mathematica} file).
-To develop an intuition for how less closely linked neo-W alleles invade ($R>r$), we first focus on cases where there is no haploid selection and discuss the additional effect of haploid selection in the appendix.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Tighter linkage allows looser sex-linkage to evolve, even in absence of haploid selection
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-\centerline{\includegraphics[width=1.5\linewidth]{PositionPlot_SexAntagTighter}}
-\caption{
-Transitions between XY and ZW systems can occur even when the neo-SDR is less tightly linked to a locus under sexually-antagonistic selection (here, without haploid selection).
-In panel A, linkage is loose enough relative to selection that the analytical results assuming weak selection hold, and a neo-W can only invade when it is more tightly linked with the selected locus ($R<r$; shaded region).
-In panel B, linkage is tight enough relative to selection that the analytical results assuming weak selection do not hold, and a neo-W can invade even when it is less tightly linked with the selected locus ($r<R$; unshaded region).
-In panel C we vary the recombination rate between the neo-W and the selected locus ($R$) for a fixed recombination rate between the ancestral-SDR and the selected locus ($r=0.005$). 
-Coloured markers show recombination rates for which the temporal dynamics of invasion are plotted in the inset, demonstrating that neo-W alleles can fix (reach frequency $0.5$ among female gametes) if they are more (black) or less (red) closely linked to a locus experiencing sexually-antagonistic selection.
-A very loosely linked neo-W does not spread in this case (blue and green lines overlap and go to 0). 
-Fitness parameters are: $w_{AA}^\female = 1.05$, $w_{aa}^\male = 1.2$, $w_{aa}^\female = w_{AA}^\male = 0.85$, $w_{Aa}^\Hermaphrodite = 1$,  $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
-%\textcolor{red}{consider removing panel A, which is repeated in Figure 3.}
-%\textcolor{blue}{probably better to remove from panel 3, eh?}
-}
-\label{fig:SexAntagTighter}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-If we categorise the $a$ allele as being ancestrally `male-beneficial' via the fact that it is fixed on the Y, then $\lambda_{WA}>1$ indicates that the neo-W spreads when found with the ancestrally `female-beneficial' allele.
-Broadly, this is possible because the ancestral X chromosome is sometimes found in males and is therefore unable to perfectly specialise on the `female-beneficial' allele. 
-For example, when the $a$ allele is favoured on the ancestral X in males, a polymorphism of $A$ and $a$ alleles can be maintained on the X despite directional selection in favour of the $A$ allele in females ($s^\female>0$, $0<h^\female<1$), see outlined region in Figure \ref{fig:regionplots}A.
-When the $a$ allele is strongly favoured on X chromosomes in males ($w_{aa}^\male$ sufficiently large relative to $w_{Aa}^\male$), neo-W-$A$ haplotypes can spread ($\lambda_{WA}>1$, see grey region in Figure \ref{fig:regionplots}A) because they produce hgher fitness females ($AA$ or $Aa$ genotypes) and are unleashed from counterselection in males.
-
-When only one neo-W haplotype has a positive growth rate (see Figure \ref{fig:regionplots}), a neo-W can invade as long as equation \eqref{eq:lambdasGen} is satisfied, which may require that the recombination rate, $R$, is small enough.
-Nevertheless, because we assume here that $r$ is small, these results indicate that a more loosely linked sex-determining region ($r<R$) can spread.
-Therefore, tightly sex-linked loci that experience sexually-antagonistic selection can drive trans-GSD transitions in which the neo-SDR is less closely linked to the locus under selection (Figure \ref{fig:SexAntagTighter}).
-
-Given that the $a$ allele can be considered ancestrally `male-beneficial' because it is fixed on the Y, it is surprising that neo-W-$a$ haplotypes can sometimes be favoured by selection in females ($\lambda_{Wa}>1$).
-Again, this occurs because ancestral X's also experience selection in males, in which they will always be paired with a Y-$a$. 
-If there is overdominance in males, X-$A$ Y-$a$ males have high fitness and the $A$ allele is favoured by selection on the X in males. 
-Therefore, the X can be polymorphic or even fixed for the $A$ allele despite favouring the $a$ allele during selection in females \citep[e.g., see outlined region in Figure \ref{fig:regionplots}B and][]{Lloyd1977,Otto2014}.
-In such cases, neo-W-$a$ haplotypes can spread because they create more $Aa$ and $aa$ females when pairing with an X from males and because they bring Y-$a$ haplotypes into females, where it has higher fitness (Figure \ref{fig:model_outline}D).
-
-In some cases, both W-$A$ and W-$a$ haplotypes can spread, e.g., when $AA$ individuals have low fitness in females yet the $A$ is polymorphic or fixed on the X due to overdominance in males (Figure \ref{fig:regionplots}B and \ref{fig:regionplots}C).
-Both neo-W-$A$ and neo-W-$a$ haplotypes then produce fewer unfit $AA$ females.
-This is true for the neo-W-$A$ haplotype because it can pair with a Y-$a$ haplotype and still be female. 
-Wherever both haplotypes have positive growth rates, invasion by a neo-W is expected regardless of its linkage with the selected locus (i.e., even unlinked neo-W alleles can invade, see Figures \ref{fig:positionOverdominance} and \ref{fig:temporalOverdominance} for examples).
-
-Assuming that linkage is not tight, \citet{vanDoorn:2010hu} showed that invasion by a neo-W occurs under the same conditions as `pseudo-fixation' (at pseudo-fixation the neo-W reaches its maximum frequency among eggs, which is 1/2).
-An equivalent analysis is not possible where we assume that linkage is tight. 
-However, numerical simulations with tight linkage demonstrate that the neo-SDR does not necessarily reach pseudo-fixation, leading to the stable maintenance of a mixed sex-determining system, in which X, Y, Z, and W alleles all segregate (e.g., Figure \ref{fig:freqAll}B,C).
-
-%Haploid selection impacts the spread of neo-W haplotypes through its direct selective effect on females and their gametes, its indirect effect on the marginal fitness of alleles in females resulting from haploid selection in male gametes, and its effect on the sex ratio.
-%These impacts expand the scenarios under which neo-W haplotypes can spread.
-%For instance, overdominance is no longer required for neo-W-$a$ haplotypes to spread when there is haploid selection (e.g., when $a$ is female-beneficial, $A$ is male-beneficial, and meiotic drive in males favours $a$, Figure \ref{fig:regionMaleDrive}B).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Both neo-W haplotypes can spread, in the absence of haploid selection, when there is overdominance
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-%\centerline{\includegraphics[width=1.25\linewidth]{Region_plot_combined_Mike}}
-\centerline{\includegraphics[width=1.25\linewidth]{Region_plot_combined}}
-\caption{
-When the ancestral-XY locus is tightly linked to a locus under selection ($r=0$), one or both neo-W haplotypes can spread. 
-We vary the fitness of male homozygotes relative to heterozygotes ($w_{Aa}^\Hermaphrodite=1$) and only consider stable equilibria at which both \textbf{A} locus alleles are maintained and the $a$ allele is initially fixed on the Y, region outlined.
-Here, selection in females can favour the $A$ allele (panel A, $w_{aa}^\female=0.85$, $w_{AA}^\female=1.05$), favour the $a$ allele (panel B, $w_{aa}^\female=1.05$, $w_{AA}^\female=0.85$), or be overdominant (panel C, $w_{aa}^\female=w_{AA}^\female=0.6$).
-If $\lambda_{wA}$ or $\lambda_{wa}$ is greater than one, then a rare neo-W can spread for, at least, some values of $R>r$. 
-The parameter values marked with an asterisk correspond to the fitnesses used in Figure \ref{fig:SexAntagTighter}C. 
-Where both $\lambda_{wA}$ and $\lambda_{wa}$ are greater than one, a neo-W will spread when rare, regardless of linkage with the selected locus (for any $R$). 
-Figure \ref{fig:positionOverdominance} shows the dynamics using the parameters marked with a dagger. 
-Here, there is no haploid selection $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
-}
-\label{fig:regionplots}
-\end{figure}
-
-%Neo-W alleles, on the other hand, can invade an ancestral XY system under some conditions (given in detail in the appendix). 
-%%The full characteristic polynomials are given in the appendix (equations \ref{Binvasion} and \ref{Ainvasion}).
-%Briefly, neo-W-$A$ and/or neo-W-$a$ haplotypes can spread when rare in the absence of recombination ($\lambda_{ma}>1$ and/or $\lambda_{mA}>1$), depending on the ancestral sex ratio and allele frequencies.
-%Below we discuss the main forces determining the spread of these neo-W haplotypes and the impact of recombination for the overall success of the neo-W.
-%To simplify our discussion we first outline the potential effects of haploid selection and then consider diploid selection in its absence.
-
-%\textcolor{blue}{This explanation is clearer than the one I put in the appendix, if we drop it here, maybe we should try and re-word the corresponding part of the appendix using this paragraph}
-%Haploid selection impacts the spread of neo-W haplotypes in three ways.
-%Firstly, the zygotic sex ratio becomes male biased ($\zeta<1/2$) when the $a$ allele (which is fixed on the Y) is favoured during competition among male gametes or by meiotic drive in males. 
-%This facilitates the spread of a neo-W because neo-W alleles cause the zygotes that carry them to develop as the rarer, female, sex. 
-%Secondly, haploid selection in males affects the diploid genotypes of females by altering the allele frequencies in the male gametes that female gametes pair with.
-%For instance, because an epistatically dominant neo-W always causes its carrier to become female, it creates females who carry either $Y-a$ or $X$ genotypes from their father.
-%Thus, because when there is a polymorphism the $X$ carries some non-zero frequency of $A$, haploid selection in males impacts the diploid genotypes of females (e.g., creating more $Aa$ females when drive in males favours $Y-a$).
-%How this affects the spread of the neo-W then depends on diploid and haploid selection in females.
-%Thirdly, female drive and gamete competition directly select on neo-W haplotypes.
-%Drive for $A$ in females favours neo-W-$A$ haplotypes, at a cost to neo-W-$a$ haplotypes, and vice-versa when there is drive for $a$.
-%The impact of this drive depends on how often XX and neo-W females are heterozygous.
-%Competition among female gametes acts similarly, and depends on the frequency of $A$ on resident X chromosomes (e.g., competition among eggs has no affect on the initial spread of the neo-W-$A$ haplotype when $A$ is fixed on the X).
-%Because haploid selection in females favours one neo-W haplotype at the expense of the other, recombination off the favoured background becomes more detrimental as it becomes more favoured.
-Thus higher rates of recombination between the neo-W and the selected locus, $R$, can lead to smaller leading eigenvalues when there is haploid selection in females.
-
-%In the absence of haploid selection and with the $A$ allele is fixed on the X, it is possible for both neo-W haplotypes can spread ($\lambda_{mA}>1$ and $\lambda_{ma}>1$ in \ref{Binvasion}), and thus neo-W invasion can occur regardless of its linkage to the selected locus.
-%Invasion does not occur with purely sexually-antagonistic selection (i.e., $a$ directionally favoured in males and $A$ directionally favoured in females) because the X is then already as specialized as possible on the female sex.
-%However, if, for example, $AA$ individuals suffer a fitness cost in females, yet $A$ is fixed on the X due to strong overdominance in males, both neo-W-$A$ and neo-W-$a$ haplotypes spread because they produce fewer unfit $AA$ females and never experience counter-selection in males.
-%This is true even for the neo-W-$A$ haplotype because it can pair with a $Y-a$ haplotype and still be female. 
-%When both haplotypes can spread alone the rate of recombination between the neo-W and the selected locus, $R$, does cannot prevent invasion, and thus the system can evolve looser sex-linkage (e.g., the neo-W could arise on an autosome, $R=1/2$).
-%Even when only one haplotype can spread, invasion can still occur up to some positive rate of recombination, $R>0$ (as long as equation \ref{eq:lambdasGen} is satisfied). 
-%That looser sex-linkage can evolve is contrary to the conclusions of \cite{vanDoorn:2010hu}, who did not explicitly calculate invasion fitness under ancestrally tight sex-linkage.
-\textcolor{blue}{or, just didn't calculate the equilibria (A) an (B).}
-%Similar scenarios have been shown to select for a modifier that increases recombination between the sexes \citep[green regions of Figure 2 in][]{Otto2014}.
-%\textcolor{blue}{n.b., the recombination regions are only subsets mostly because you also generate a really unfit Y haplotype through recombination. Probably not worth mentioning.}
-%
-%In the absence of haploid selection it is also possible for a neo-W to invade when there is a stable polymorphism at the $\mathbf{A}$ locus on X chromosomes.
-%For example, overdominance in males and strong directional selection for $a$ in females creates a scenario that favours the spread of both neo-W haplotypes at equilibrium ($\lambda_{mA}>1$ and $\lambda_{ma}>1$ in \ref{Ainvasion}), as both haplotypes bring more $a$ alleles into females and never experience counter-selection in males.
-%Thus, as in the case of the $A$ being fixed on the X, looser sex-linkage can evolve with a polymorphic X (i.e., $\lambda>1$ with $R>0$) and this is expected under the same scenarios that select for a modifier that increases recombination between the sex chromosomes \citep[blue regions of Figure 2 in][]{Otto2014}.
-
-\subsubsection*{Loose linkage with the ancestral sex-determining region}
-
-%\textcolor{blue}{As with the discussion, this section might need some editing for (1) unclearly describing looser linkage never evolving without haploid selection, which we now show is possible above and (2) going on about sex ratio selection too much - this should be changed to something along the lines of  ``male biased zygotic sex ratios ($\zeta-1/2$) are of the order of $\epsilon^2$.
-Therefore Fisherian sex ratio selection directly favours neo-Ws by a similar magnitude.
-%Perhaps surprisingly, neo-Ws can be favoured to the same degree by haploid selection in females when female haploid selection favours the alleles that tend to be carried by the neo-W.
-%Thus XY to ZW is the same as ZW to XY even though sex ratio biases only exist in one case, given the assumptions made in this section.
-%''
-%}
-
-%weak selection
-%We are particularly concerned with whether or not a rare neo-sex-determining allele increases in frequency, which occurs when the largest eigenvalue, $\lambda$, is greater than one. 
-%Here, we explicitly determine the conditions under which invasion occurs by assuming that the $A$ allele reaches an equilibrium frequency under the ancestral sex-determination system before the neo-sex-determination system ($m$) arises.
-%The equilibrium frequency of $A$ on different ancestral backgrounds ($\hat{p}^\male_Y$, $\hat{p}^\male_X$, and $\hat{p}^\female_X$) is given by equations \eqref{eq:pAve} and \eqref{eq:freq_diffs} where we assume selection and meiotic drive are weak relative to recombination ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon$).
-Assuming that selection is weak ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon<<1$) and thus implicitly assuming that all recombination rates ($r$, $R$ and $\rho$) are large relative to selection, we denote the leading eigenvalues describing the invasion of a neo-Y ($k=0$) and a neo-W ($k=1$) into an ancestrally XY system by $\lambda_{Y',XY}$ and $\lambda_{W',XY}$, respectively.
-To leading order in selection, these are:
-
-\begin{equation}
-\lambda_{Y',XY} =1+ \frac{1}{4}V_{A}S_{A}^2\frac{ \left( r-R \right) }{r R}+O\left(\epsilon^3 \right) 
-\label{eq:lambda_neoY}
-\end{equation}
-
-\noindent 
-and
-
-\begin{equation}
-\lambda_{W',XY} =\lambda_{Y',XY}+\left(2\alpha_{\Delta}^\male-2\alpha_{\Delta}^\female+t^\male-t^\female \right) \left( \hat{p}^\male_Y-\hat{p}^\male_X \right)/2
-+O\left(\epsilon^3 \right) \\
-\label{eq:lambda_neoW}
-\end{equation}
-
-\noindent
-where $V_{A}=\bar{p}(1-\bar{p})$ is the variance in the equilibrium frequency of $A$ and $S_{A}=(D^\male +\alpha_{\Delta}^\male+t^\male) - (D^\female+\alpha_{\Delta}^\female+t^\female)$ describes sex differences in selection for the $A$ versus $a$ allele across diploid selection, meiosis, and gametic competition.
-The diploid selection term, $D^\Hermaphrodite=\big{[} \bar{p}s^\Hermaphrodite+(1-\bar{p})h^\Hermaphrodite s^\Hermaphrodite\big{]} -\big{[} \bar{p}h^\Hermaphrodite s^\Hermaphrodite+(1-\bar{p}) \big{]}$, is the difference in fitness between $A$ and $a$ alleles in diploids of sex $\Hermaphrodite \in \{\female,\male\}$, where $\bar{p}$ is the leading-order probability of mating with an $A$-bearing gamete from the opposite sex (equation \ref{eq:pAve}).
-The difference in $A$-allele-frequency among Y-bearing sperm versus X-bearing sperm is given by $\hat{p}^\male_Y-\hat{p}^\male_X=V_{A}\big{(}D^\male - D^\female+\alpha_{\Delta}^\male-\alpha_{\Delta}^\female+t^\male-t^\female\big{)}(1-2r)/(2r)$.
-
-The neo-sex-determining allele, $m$, will spread if $\lambda_{m,XY}>1$. 
-Equation \eqref{eq:lambda_neoY} demonstrates that, under weak selection, a neo-Y will invade an XY system if and only if it is more closely linked to the selected locus than the ancestral sex-determining region (i.e., if $R<r$; note that $V_{A}S_{A}^2$ is strictly positive as long as \textbf{A} is polymorphic).
-This echoes our tight linkage results above where a neo-Y could never invade if $r\approx0$.
-It is also consistent with the results of \citet{vanDoorn:2007eu}, who considered diploid selection only and also found that cis-GSD transitions (XY to XY or ZW to ZW) can only occur when the neo-sex-determining locus is more closely linked to a locus under sexually-antagonistic selection.
-%Because tighter linkage between the sex-determining region and a selected locus evolves during these transitions, stronger associations between selected alleles and diploid sexes can build up by selection (e.g., between male-beneficial alleles and the male-determining allele, Y).%, increasing diploid mean fitness (Figure \ref{fig:Combination_MeanFit}).
-
-With weak selection and no haploid selection ($t^\Hermaphrodite=\alpha^\Hermaphrodite_{\Delta}=0$), the spread of a neo-W is equivalent to the spread of a neo-Y ($\lambda_{W',XY}=\lambda_{Y',XY}$), such that trans-GSD transitions (XY to ZW or ZW to XY) can also occur only if the neo-sex-determining region is more closely linked to a locus under selection ($R<r$), as found by \citet{vanDoorn:2010hu}.
-With haploid selection, however, the additional term in equation \eqref{eq:lambda_neoW} can be positive, which can allow, for example, neo-W invasion ($\lambda_{W',XY}>1$) even when the neo-sex-determining region is less closely linked to the selected locus ($R>r$).
-%These transitions are unusual because, when $R>r$, associations that selection has built up between alleles more favourable in one sex and alleles that determine sex will be weakened. 
-%Mean diploid fitness therefore decreases during heterogametic transitions that create looser sex-linkage (Figure \ref{fig:Combination_MeanFit}B,D).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%A neo-W can invade an XY system under a large number of selective regimes
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-\includegraphics[width=\linewidth]{PositionPlot}
-\caption{
-% A neo-W can invade an XY system under a large number of selective regimes.
-%In panel A, there is no haploid selection ($t^\Hermaphrodite = \alpha^\Hermaphrodite_{\Delta} = 0$) and selection in diploids is sexually antagonistic ($s^\male = -s^\female = 1/10$, $h^\male = 1-h^\female = 3/10$), in which case the neo-sex-determining allele can only invade if it is more closely linked to the selected locus ($R<r$, gray region; but see Figure \ref{fig:SexAntagTighter}B for the case of very tight linkage).
-Ploidally-antagonistic selection allows a less tightly linked neo-W to invade.
-In panel A, male drive ($\alpha^\male_{\Delta} = -1/20$, $t^\Hermaphrodite = \alpha^\female_{\Delta} = 0$) opposes selection in diploids (no sex-differences: $s^\Hermaphrodite = 1/10$, $h^\Hermaphrodite = 7/10$), in which case the neo-sex-determining allele can invade regardless of linkage.
-In panel B, gametic competition in males ($t^\male = -1/10$, $t^\female = \alpha^\Hermaphrodite_{\Delta} = 0$) opposes selection in diploids (sex-differences: $s^\male = 3/20$, $s^\female = 1/20$, $h^\Hermaphrodite = 7/10$), in which case the neo-sex-determining allele can once again invade regardless of linkage.
-We use Haldane's map function \citep[Equation 3 in ][]{Haldane1919} to convert from map distance (centiMorgans, cM) to the probability of recombination (an odd number of cross-over events).   
-%\textcolor{red}{Check the mismatch between red and black lines here: probably because of adding or subtracting from 1. }
-%\textcolor{blue}{Can remove the mismatch by flipping the fitnesses between males and females (again).
-That is, if $M_{AA}$ is the fitness of $AA$ male diploids in an ancestral XY system, then $M_{AA}$ is the fitness of $AA$ female diploids in an ancestral ZW system.
-I think this makes sense in A, where we don't really want a difference between the red and black curves, but this makes less sense in B and C where we want to restrict haploid selection to males regardless of the ancestral system.
-We could just not flip the haploid fitnesses, but then does it make sense to flip the diploid fitnesses?}
-}
-\label{fig:Combination_Centimorgans}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Equation \eqref{eq:lambda_neoW} shows that, with weak selection, neo-W alleles can invade an XY system for a large number of selective regimes. 
-To clarify the parameter space under which $\lambda_{W',XY}>1$, we consider several special cases. 
-Firstly, if the \textbf{A} locus is unlinked to the ancestral sex-determining region ($r=1/2$), a more closely linked neo-W ($R<1/2$) can always invade because there is no ancestral association between $A$ alleles and sex chromosomes in males, $\left( \hat{p}^\male_Y-\hat{p}^\male_X \right)=0$, see equation \eqref{eq:freq_diffs}.
-The second term in equation \eqref{eq:lambda_neoW} therefore disappears and invasion depends only on the sign of $(r-R)$, as in the case of the neo-Y. 
-Indeed, invasion typically occurs when the neo-W is more closely linked to the selected locus than the ancestral sex-determining region (Figure \ref{fig:Combination_Centimorgans}).
-
-Secondly, we can simplify the discussion of cases where invasion occurs despite looser sex-linkage, $R>r$, by focusing on the special case where $R=1/2$ and $r<1/2$ (e.g., the selected locus is on the ancestral sex chromosome and the novel sex-determining locus arises on an autosome).
-In Table \ref{tab:specialcases} we give the conditions where invasion occurs when we further assume that haploid selection only occurs in one sex (e.g., during male meiosis only) and dominance coefficients are equal in the two sexes, $h^\female=h^\male$.
-When there is no gametic competition and meiotic drive is in one sex only, an unlinked neo-W can invade as long as the same allele is favoured during diploid selection in males and females ($s^\female s^\male>0$, see Figure \ref{fig:Combination_Centimorgans}A and Figure \ref{fig:SexRatioBad}B).
-%, which is 50\% of the parameter space.
-When there is no meiotic drive and gametic competition occurs in one sex only, an unlinked neo-W can invade as long as the same allele is favoured in male and female diploid selection and there are sex differences in selection of one type (e.g., $s^\female(s^\male-s^\female)>0$, see Figure \ref{fig:Combination_Centimorgans}B).
-%, which is 25\% of the parameter space.
-These special cases indicate that neo-W invasion occurs for a relatively large fraction of the parameter space, even if the neo-W uncouples the sex-determining locus from a locus under selection.
-
-\begin{table}[ht]
-\centering
-\smallskip
-\caption{Invasion conditions for unlinked neo-W ($R=1/2$, $r<1/2$) into ancestral XY with one form of haploid selection}
-\begin{tabular}{l l c }
-\hline\hline
-Scenario &  Assumptions & neo-W spreads ($\lambda_{W',XY}>1$) if \\ [0.5ex] \hline
-%  $r=1/2$, $R<1/2$ & Always \\ [0.5ex] \hline
-%  $r<1/2$, $R=1/2$ &  \\ [0.5ex] \hline
-\noalign{\vskip 1mm}
-  male drive only & $h^\male=h^\female$, $t^\female=t^\male=\alpha^\female_{\Delta}=0$ & $s^\female s^\male>0$ \\ [0.5ex]
- female drive only & $h^\male=h^\female$, $t^\female=t^\male=\alpha^\male_{\Delta}=0$ & $s^\female s^\male>0$ \\ [0.5ex]
- sperm competition only &  $h^\male=h^\female$, $t^\female=\alpha^\female_{\Delta}=\alpha^\male_{\Delta}=0$ & $s^\female(s^\male-s^\female)>0$ \\ [0.5ex]
-  egg competition only & $h^\male=h^\female$, $t^\male=\alpha^\female_{\Delta}=\alpha^\male_{\Delta}=0$ & $s^\male(s^\female-s^\male)>0$ \\ [0.5ex]
-  \hline \hline
-  \label{tab:specialcases}
- \end{tabular}
-\end{table}
-
-%If we further assume equal dominance ($h^\female=h^\male$) and that haploid selection only occurs during male meiosis ($t^\female=t^\male=\alpha^\female_{\Delta}=0$), or female meiosis ($t^\female=t^\male=\alpha^\male_{\Delta}=0$), neo-W invasion occurs when $s^\female s^\male>0$, Figure \ref{fig:Combination_Centimorgans}B.
-%That is, when the same allele is favoured by selection in both males and females (it may remain polymorphic via counter selection during meiotic drive).
-
-%\textcolor{red}{It may seem counterintuitive that, if the $A$ allele is more common on the ancestral-Y than the ancestral-X, and only favoured during haploid selection in males}
-
-%\textcolor{red}{although our predictions also perform well when recombination is small, see figure \ref{fig:WinvasionLowR}.
-We would have to add a line showing what invasion fitness the weak selection approximation would give and add dots to this figure (dots that are currently connected by a line), as in (vD\&K, 2010) }
-
-%Sex ratios
-%Previous research suggests that when the ancestral sex-determining locus is linked to a locus that experiences haploid selection (e.g., meiotic drive), a new, unlinked sex-determining locus invades in order to restore equal sex ratios \citep{Kozielska:2010vm}.
-%Our model provides a good opportunity to determine whether Fisherian sex ratio selection provides a useful explanation for the evolution of new sex-determining loci in other contexts. 
-%Consider, for example, the case where the \textbf{A} locus is linked to the ancestral-SDR ($r<1/2$) and experiences meiotic drive in males only (e.g., during spermatogenesis but not during oogenesis, $\alpha^\male \neq 1/2$, $\alpha^\female=1/2$).
-%We will also disregard gametic competition ($t^\female=t^\male=0$) such that zygotic sex ratios are only biased by meiotic drive in males. 
-%In this case, the zygotic sex ratio can be initially biased only if the ancestral sex-determining system is XY (Figure \ref{fig:Combination_Turnover}B). 
-%If the ancestral sex-determining system is ZW, the zygotic sex ratio will be 1:1 because diploid sex is determined by the proportion of Z-bearing versus W-bearing eggs and meiosis in females is fair (Figure \ref{fig:Combination_Turnover}D).
-%Thus, if the zygotic sex ratio is crucial to the evolution of new genetic sex-determining systems, invasion into ZW and XY systems will be distinct. 
-%However, under weak selection we find that invasion by a homogametic neo-sex-determining allele (XY to XY or ZW to ZW) or by a heterogametic neo-sex-determining allele (XY to ZW or ZW to XY) occur under the same conditions.
-%That is, we can show that $\lambda_{Y',XY}=\lambda_{W',ZW}$ and $\lambda_{Y',ZW}=\lambda_{W',XY}$ (at least up to order $\epsilon^3$; for a numerical example, compare Figure \ref{fig:Combination_Turnover}A,B to Figure \ref{fig:Combination_Turnover}C,D).
-%As it turns out, under weak selection the strength of sex ratio selection favouring, say, the invasion of a neo-W in an XY system is the same as the strength of meiotic drive favouring the invasion of a neo-Y in a ZW system.
-%Even when these forces are not exactly the same (e.g., under tight sex-linkage; compare black and red curves near -25 and 25cM in Figure \ref{fig:Combination_Centimorgans}), it is important to remember that sex ratio selection is only one of many potential selective forces acting to determine transitions between sex-determining systems.
-%It is even possible for the other selective forces to overwhelm sex ratio selection and favour sex-determination transitions that create sex ratio biases (Figure \ref{fig:Combination_Turnover}A,C).
-
-Previous research suggests that when the ancestral sex-determining locus is linked to a locus that experiences haploid selection (e.g., meiotic drive), a new, unlinked sex-determining locus invades in order to restore equal sex ratios \citep{Kozielska:2010vm}.
-Consider, for example, the case where the \textbf{A} locus is linked to the ancestral-SDR ($r<1/2$) and experiences meiotic drive in males only ($\alpha^\male_\Delta \neq 0$, $\alpha^\female_\Delta=0$), without gametic competition ($t^\female=t^\male=0$).
-In this case, the zygotic sex ratio can be initially biased only if the ancestral sex-determining system is XY (Figure \ref{fig:model_outline}B and Figure \ref{fig:SexRatioBad}B). 
-%If the ancxestral sex-determining system is ZW, the zygotic sex ratio will be 1:1 because diploid sex is determined by the proportion of Z-bearing versus W-bearing eggs and meiosis in females is fair (Figure \ref{fig:Combination_Turnover}D).
-If Fisherian sex ratio selection were dominant, we would expect a difference in the potential for XY to ZW and ZW to XY transitions. 
-%However, to leading order with selection weak relative to recombination, we find that sex ratio selection favours the spread of a neo-W by an amount equl to the spread of a neo-Y into a ZW system (relabeling XY as the heterogametic sex and reversing the labels of males and females in Table \ref{tab:specialcases})
-%However, to leading order with selection weak relative to recombination, we find that sex ratio selection favours the spread of a neo-W (through the first terms in table \ref{tab:haplotype_growth}) by an amount that is equal in magnitude to the fitness effects of alleles associated with new sex-determining alleles (second terms in table \ref{tab:haplotype_growth}).
-However, invasion by a neo-W into an XY system and invasion by a neo-Y into a ZW system occur under the same conditions ($\lambda_{Y',XY}=\lambda_{W',ZW}$ and $\lambda_{Y',ZW}=\lambda_{W',XY}$, at least to order $\epsilon^2$).
-For example, in Figure \ref{fig:SexRatioBad}A neo-W alleles invade an ancestral-XY system where females are initially rare.
-However, Figure \ref{fig:SexRatioBad}B shows that a neo-Y can invade an ancestral-ZW system under the same conditions. 
-As a consequence, whenever $R<1/2$, the neo-Y becomes associated with the male meiotic drive allele such that the zygotic sex ratio actually evolves to become biased towards males.
-
-%As selection becomes stronger (or linkage becomes tighter), this symmetry between sex ratio selection and haploid selection is lost, causing differences in the strength of selection favouring the two heterogametic transitions (compare red to black near -25cM and 25 cM in Figure \ref{fig:Combination_Centimorgans}).
-\textcolor{red}{normalise fitness in sexually antagonistic case}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Sex ratio selection is not a good predictor of neo-W invasion into an XY system
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-\includegraphics[width=\linewidth]{Temporal_SR}
-\caption{
-Fisherian sex ratio selection alone is not a good predictor of turnover between sex-determining systems.
-In this figure, selection is ploidally antagonistic with haploid selection favouring the $a$ allele during male meiosis.
-In panel A, male drive in an ancestral ZW system has no affect on the zygotic sex ratio (see Figure \ref{fig:model_outline}B) yet a neo-Y can invade and replace the ancestral sex-determination system (inset shows neo-Y frequency among male gametes, the ancestral W also goes to fixation during this transition).
-When $R<1/2$, the neo-Y becomes associated with the allele favoured by drive, causing the zygotic sex ratio to become biased, hence the frequency of neo-Y among male gametes can be higher than $0.5$ (inset).
-In panel B, male drive in an ancestral XY system causes a male bias, allowing a neo-W to invade and replace the ancestral sex-determination system (inset shows neo-W frequency among female gametes, the ancestral Y also goes to fixation), which balances the zygotic sex ratio.
-Parameters:  $s^\female =s^\male = 0.2$, $h^\female = h^\male = 0.7$, $t^\female = t^\male = \alpha^\female_\Delta = 0$, $\alpha^\male_\Delta = -0.1$, $r=0.02$.
-}
-\label{fig:SexRatioBad}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Why can new sex-determining regions invade when more loosely linked to selected loci ($R>r$)?  
-Consider first the case where both loci are linked to the selected locus ($r<R<1/2$). 
-In an XY system, haploid selection in males can facilitate the spread of a neo-W because the zygotic sex ratio is ancestrally biased and the W helps to equalize the sex ratio (Figure \ref{fig:SexRatioBad}A).
-A new sex determining region can also, however, benefit from becoming more associated with drive.  
-For example in a ZW system with the same selection regime (haploid selection in males), a neo-Y can spread despite the fact that the zygotic sex is initially even; in this case, the neo-Y spreads because it is often found in males and can, if it carries the driven allele $a$, benefit from haploid selection (Figure \ref{fig:SexRatioBad}B).
-While equalizing the sex ratio and benefiting from drive are two primary reasons why haploid selection spurs sex chromosome transitions, more complex situations also arise.  
-For example with $R=1/2$ in Figure \ref{fig:SexRatioBad}B (green curve), the neo-Y spreads despite the fact that it cannot benefit from drive because free recombination moves it randomly between driven and non-driven backgrounds.
-Nevertheless, the unlinked neo-Y can spread because diploids bearing it more often carry the non-driven allele $A$ found at high frequency on the W background, which has higher average diploid fitness to balance the haploid advantage of the $a$ allele at equilibrium.
-
-%The green curves in Figure \ref{fig:SexRatioBad} show transitions between male and female heterogametey even though the new sex-determining region is unlinked to a locus that experiences haploid and diploid selection.
-%We use these green curves to discuss why trans-GSD transitions can occur when $R=1/2$ and $r<1/2$, as in Table \ref{tab:specialcases}.
-%In Figure \ref{fig:SexRatioBad}B, an unlinked neo-W can spread because the zygotic sex ratio is ancestrally male biased. 
-%In Figure \ref{fig:SexRatioBad}A, an unlinked neo-Y spreads despite the fact that the ancestral zygotic sex ratio is even. 
-%In this case, the male meiotic drive allele, $a$, is initially more common among ancestral-Z-bearing eggs than ancestral-W-bearing eggs because the Z is found in males more often than the W ($\hat{p}_{W}^\female-\hat{p}_{Z}^\female>0$, equation \ref{eq:freq_diffs}).
-%Polymorphism at the \textbf{A} locus is maintained by counter-selection against the $a$ allele in diploids and therefore ancestral-ZZ males have generally low diploid fitness. 
-%The neo-Y spreads because it produces males with high diploid fitness through matings with ancestral-W-bearing female gametes, which are more likely to carry the $A$ allele ($\hat{p}_{W}^\female-\hat{p}_{Z}^\female>0$).
-%A freely recombining neo-Y ($R=1/2$) is equally likely to be segregate with the $A$ or $a$ allele.
-%Therefore, the neo-Y is unaffected by male meiotic drive against the $A$ alleles that it introduces into males. 
-%Thus, a key factor in explaining why trans-GSD transitions can occur when $R>r$ is that the neo-SDR determines sex in the diploid phase but recombination occurs before any subsequent haploid selection.
-
-\subsubsection*{Environmental sex determination}
-
-We next consider the case where the new sex-determining mutation, $m$, causes sex to be determined probabilistically or by heterogeneous environmental conditions (environmental sex determination, ESD), with individuals carrying allele $m$ developing as females with probability $k$.
-Here, we do not assume that the environmental conditions that determine sex also differentially affect the fitness of males versus females. 
-Such correlations can favour environmental sex-determination systems that allow each sex to be produced in the environment in which it has highest fitness; in the absence of these correlations, previous theory would predict that ESD is favoured when it produces more equal sex ratios than the ancestral system \citep[see reviews by][]{Charnov:1982wg,Bull:1983vi,West:2009we}.
-%(e.g., maternal condition, mate quality, age, or host size)
-
-The characteristic polynomial determining the eigenvalues (equations \ref{eq:recursions}) does not factor for ESD mutants as it does for $k=0$ or $k=1$. 
-We therefore focus on weak selection here. 
-Assuming weak selection, the spread of the new sex-determining region is given by
-
-\begin{equation}
-\begin{split}
-\lambda_{ESD',XY} =& 1 + \frac{(1-2k)^2}{4}V_{A}{S_{A}}^2\frac{r-R}{r R} \\
-&+\frac{k(\hat{p}^\male_Y-\hat{p}^\male_X)}{2}\left[ k \left(2\alpha_{\Delta}^\male-2\alpha_{\Delta}^\female+t^\male-t^\female \right) -2(1-k)S_{A}\right]+O\left(\epsilon^3\right),
-\end{split}
-\label{eq:lambda_ESD_k}
-\end{equation}
-
-\noindent
-which reduces to $\lambda_{Y',XY}$ when $k=0$ and $\lambda_{W',XY}$ when $k=1$.
-
-%Under Fisherian sex ratio selection, autosomal modifiers favour equal investment in male and female offspring, i.e., a 1:1 sex ratio \citep{Fisher:1930wy,Charnov:1982wg,West:2009we}. 
-%A novel environmental sex-determiner that causes half of its carriers to become female and half to become male ($k=1/2$) will be in males half of the time and in females half of the time (like an autosome).
-%In addition, these novel sex-determination alleles equalize the sex ratio and therefore one might expect them to be favoured by Fisherian sex ratio selection when the resident sex ratio is biased.
-%However, assuming weak selection, we find that the growth rate of a rare, dominant offspring-controlled neo-ESD allele that produces males or females with equal probability ($k=1/2$) is
-Of particular interest are ESD mutations that cause half of their carriers to develop as females and half as males ($k=1/2$, creating equal sex ratios), the spread of which is given by
-\begin{equation}
-\lambda_{ESD',XY} =1+ \frac{1}{2}\frac{(\lambda_{Y',XY\rvert R=1/2}-1) + (\lambda_{W',XY\rvert R=1/2}-1)}{2} + O\left(\epsilon^3\right),
-%V_A \frac{r}{1-2r}  \frac{s_{f} \left( s^\male - 3 s^\female\right) }{8 \left( s_{f} + s_{m} \right)^2} t_{m}^2.
-\label{eq:lambda_ESD}
-\end{equation}
-\noindent
-where $\lambda_{Y',XY\rvert R=1/2}$ and $\lambda_{W',XY\rvert R=1/2}$ represent $\lambda_{Y',XY}$ and $\lambda_{W',XY}$ when evaluated at $R=1/2$ (Equations \ref{eq:lambda_neoY} and \ref{eq:lambda_neoW}).
-That is, recombination between the selected locus and the novel sex-determining locus, $R$, doesn't enter into the $k=1/2$ results.
-This is because sex is essentially randomized each generation, %as if the novel sex-determiner were on an unlinked site that half the time acts as a neo-$W$ and half the time as a neo-$Y$.
-preventing associations from building up between allele $A$ and sex. 
-Equation \eqref{eq:lambda_ESD} shows that the neo-ESD gets half of the fitness of a feminizing mutation (neo-$W$) and half of the fitness of a masculinizing mutation (neo-$Y$), but only has an effect one half of the time (the other half of the time it produces the same sex as the ancestral system would have).
-As discussed above, $\lambda_{Y',XY\rvert R=1/2}$ is necessarily less than one, but $\lambda_{W',XY\rvert R=1/2}$ can be greater than one if there is haploid selection.
-That is, when there is haploid selection, ESD mutations can invade an ancestrally-XY system because they generate females that are either rare or have high fitness, in the same manner as a neo-W.
-
-%An important result from equation \eqref{eq:lambda_ESD} is that ESD can invade if there is haploid selection. 
-%When evaluated at $R=1/2$, $\lambda_{Y',XY}$ is necessarily less than one, but $\lambda_{W',XY}$ can be greater than one if there is haploid selection, as discussed above. 
-%Previous studies where ESD is favoured have typically assumed that environmental conditions (e.g., maternal condition, mate quality, age, or host size) can differentially affect the fitness of males versus females such that ESD invades because it allows sex determination to depend on the environment \citep[reviewed in][]{Charnov:1982wg,Bull:1983vi,West:2009we}.
-%Here, ESD mutations can spread because they generate females that are either rare or have high fitness, in the same manner as a neo-W.
-
-Significantly, equation \eqref{eq:lambda_ESD} is the same whether ESD is invading an ancestrally XY or ZW system (because $\lambda_{Y',XY} = \lambda_{W',ZW}$ and $\lambda_{W',XY} = \lambda_{Y',ZW}$).
-Thus, Fisherian sex ratio selection alone does not explain the invasion of ESD under weak selection because the sex ratio is only biased by male haploid selection when the ancestral sex-determination system is XY.
-Specifically, with male haploid selection, the neo-ESD is equally likely to invade when it equalizes the zygotic sex ratio (through $\lambda_{W',XY}$) and when it doesn't (through $\lambda_{Y',ZW}$). 
-%This is again because haploid selection can facilitate the turnover of sex chromosomes either through sex ratio biases or through associations between the new sex determining region with selected alleles.
-%With weak selection, these two forces are nearly equal in strength. 
-In addition, we note that ESD may not invade, even if the sex ratio is initially biased (e.g., with drive in males only, $r<1/2$, $h^\female=h^\male$, and $s^\female s^\male<0$, then $\lambda_{W',XY}<1$, see Table \ref{tab:specialcases}).
-We conclude that, as with neo-W and neo-Y loci, associations with selected loci mean that the evolution of neo-ESD systems is not straightforwardly predicted by selection to balance the zygotic sex ratio when haploid selection is present.
-
-%Depends 50\% on its fitness relative to non-mutant males and 50\% on its fitness relative to non-mutant females.
-
-%\subsubsection*{Maternally-controlled neo-ESD}
-
-%Fisherian sex ratio selection is sometimes considered in terms of balancing parental investment in male versus female offspring \citep{Charnov:1982wg}.
-%In addition, under environmental sex-determination, the proportion of males/females is sometimes controlled by the mother (e.g., the proportion of eggs laid in warm versus cold environments). 
-%We therefore also considered the invasion of a neo-sex-determining allele ($m$) in a model in which mothers that have at least one $m$ allele produce daughters with probability $k$. 
-%As with offspring-controlled ESD, for all $k\in\{0,1/2,1\}$, we find that invasion into an ancestral XY system is the same as invasion into an ancestrally ZW system (at least up to order $\epsilon^3$, assuming weak selection), implying that transitions between genetic sex-determination and maternally controlled environmental sex-determination are not driven by Fisherian sex ratio selection alone.
-%\textcolor{red}{(Maternal ESD analysis still lacks meiotic drive -- Mathematica can't seem to deal with the added complexity.)}
-
-%One might think that when the sex of zygotes is under the control of mothers, there would be strong selection to balance the sex ratio among zygotes. 
-%However, we find that, with no meiotic drive and weak selection, the invasion fitness of a dominant, maternally controlled sex-determiner that produces proportion $k$ daughters can be written
-%\begin{equation}
-%\lambda_{k} = 1 + V_A S_A C_k + O\left(\epsilon^3\right),
-%\end{equation}
-%where
-%\begin{equation}
-%V_A = \frac{- \left[ t_m + h (s_{f}+s_{m}) \right] \left[ t_m + (1-h) (s_{f}+s_{m}) \right]}{(1-2h)^2(s_{f}+s_{m})^2}
-%\end{equation}
-%is the variance in $A$ ($V_A>0$ when the polymorphic resident equilibrium is stable), 
-%with $h$ the dominance coefficient (equal in both sexes), 
-%$C_k$ is a term that depends on $k$.
-%
-%%k=0
-%\begin{equation}
-%C_0 = big \; ugly \; term
-%\end{equation}
-%
-%%k=1
-%\begin{equation}
-%C_1 = \frac{\left[ (2r(1-R)-R) s^\female + (1-2r)R s^\male \right]}{2}
-%\end{equation}
-%
-%%k=1/2
-%\begin{equation}
-%C_{1/2} = even \; bigger, \; uglier \; term
-%\end{equation}
-%
-%When $k=1$ the maternal- and offspring-controlled results are the same, $C_1 = C_W$, since the mutation remains in females (and hence mutant daughters always have mutant mothers).
-%However, with $k\neq1$ the results with maternal control differ from those with offspring control.
-%Interestingly, for all $k\in\{0,1/2,1\}$, we find that invasion into an ancestrally XY system is the same as invasion into an ancestrally ZW system (at least up to order $\epsilon^3$), implying that sex ratio selection does not drive transitions between genetic sex determination and maternally controlled environmental sex determination.
-%Of particular interest is $k=1/2$ (i.e., when the mother perfectly balances the sex ratio of her offspring).
-%When both recombination rates are small we have $C_{1/2} \approx R(s^\male - s^\female)/8 = \lim_{r \rightarrow 0} C_1/4$.
-%This implies that, at least under tight linkage, the invasion of maternally-controlled ESD is independent of $R$ (because $S_A\propto R^{-1}$) and can invade whenever a neo-$W$ can (which can invade even when it biases the sex ratio further; Figures \ref{fig:WinvasionLowR} -- \ref{fig:WinvasionHighR}).
-
-\section*{Discussion}
-
-%\textcolor{blue}{maybe re-order to put the results up front and focus on sex ratio less.
-Somewhere around these first two paragraphs we should include our tight linkage results.
-At the moment it doesn't make total sense because it assumes that tighter linkage is always favoured unless there is haploid selection.}
-
-%MAIN RESULT
-Two predominant theories explaining the remarkably high frequency of transitions between sex-determination systems are sexually-antagonistic selection and sex ratio selection \citep[reviewed in][]{Blaser2012, vanDoorn2014re}.
-The former predicts that neo-sex-determining alleles can invade when they arise in closer linkage with a sexually-antagonistic locus \citep{vanDoorn:2007eu,vanDoorn:2010hu, Muralidhar2018}.
-The latter predicts that new sex-determining systems are generally favoured if they result in more equal sex ratios than the ancestral system. 
-%The latter predicts that neo-W alleles will invade an XY system when there is a male bias caused by haploid selection in males, and vice-versa, a neo-Y will invade a ZW system when there is a female bias caused by haploid selection in females \citep{Kozielska:2010vm,Ubeda:2015fx}.
-In contrast to these prevailing views, we show that selection (including sexually-antagonistic selection, overdominance, and/or ploidally-antagonistic selection) on loci tightly linked to the ancestral sex-determining region can favour trans-GSD transitions (XY to ZW or ZW to XY) to new sex-determining systems that are less closely linked to the selected loci (e.g., see Figure \ref{fig:SexAntagTighter}).
-Similarly, even when linkage is weak relative to selection, we show that %new sex-determining alleles are typically favoured if they are more closely linked to a locus under haploid selection (even in the absence of diploid sex differences), which is the only condition favouring cis-GSD transitions (XY to XY or ZW to ZW).
-%In addition, with haploid selection and weak selection, 
-trans-GSD transitions (XY to ZW or ZW to XY) can occur where the new sex-determining region is less closely linked to the locus under selection if there is haploid selection (e.g., Figures \ref{fig:Combination_Centimorgans} and \ref{fig:SexRatioBad}).
-%\textcolor{red}{need to mention sex ratio here}
-%Neo-W (neo-Y) alleles invade when their fitness in females (males) is greater than the mean fitness of females (males) under the ancestral sex-determination system and/or females (males) are the rarer sex.
-
-%TIGHT LINKAGE RESULTS
-%When the rate of recombination between the ancestral sex-determining locus and a locus under selection is small relative to the strength of selection (i.e., sex-linkage is tight, or selection is strong), heterogametic transitions (XY to ZW or ZW to XY) that reduce sex-linkage are possible, with or without haploid selection (Figures \ref{fig:SexAntagTighter} and \ref{fig:regionplots}).
-
-%The likelihoods of these transitions are driven by sex ratio selection, direct selection on alleles linked to the neo-sex-determining allele, the ability of the neo-sex-determining allele to avoid selection in one sex, and the ability of the neo-sex-determining allele to bring alleles on the sex-specific chromosome in the ancestor into the other sex (given that the neo-sex determining allele is epistatically dominant to its predecessor).
-
-%This possibility that looser sex-linkage could evolve, even in the absence of haploid selection (Figure \ref{fig:regionplot_2a}A), was overlooked in \cite{vanDoorn:2010hu}, likely because they did not explicitly consider the case of initially tight linkage between the \textbf{A} locus and the ancestral-SDR, which allows substantial differences in allele frequencies to build up \citep[$\hat{p}^\Hermaphrodite_{X} \neq \hat{p}_{Y}^\male$, equation \ref{eq:tightequil};][]{Lloyd1977,Otto2014}.
-%Interestingly, there is substantial overlap between the parameter space that allows both neo-W-$A$ and neo-W-$a$ haplotypes to spread in an XY system and that which selects for increased recombination between X and Y chromosomes \citep[e.g., compare gray region of Figure \ref{fig:regionplot_2a}A with coloured regions of Figure 2(a) in][]{Otto2014}.
-%This makes sense, as when both neo-W haplotypes can spread the neo-W can invade despite reducing sex-linkage, i.e., the rate of recombination between the sex-determining allele and the selected locus increases.
-%We further find that it is easier for a neo-W to invade 
-%\textcolor{red}{explain difference too?
-also explain why a neo-Y doesn't invade to reduce linkage despite selection for more recombination?
-mention something about haploid selection (Fig7B)?} \textcolor{blue}{maybe leave for now}
-
-%HAPLOID SELECTION CAN ACT LIKE SEXUALLY-ANTAGONISTIC SELECTION
-%It has previously been demonstrated that new sex-determining systems can evolve if there is genetic variation maintained by sexually-antagonistic selection \citep{vanDoorn:2007eu,vanDoorn:2010hu}. 
-%In particular, 
-%Under weak selection (or loose sex-linkage), transitions to new sex-determining systems can occur when they arise more closely linked to a sexually-antagonistic locus \citep{vanDoorn:2007eu,vanDoorn:2010hu}.
-%New sex-determining alleles are again favoured if they are more closely linked to a locus under haploid selection, which is the only condition favouring homogametic transitions (XY to XY or ZW to ZW).
-%HAPLOID SELECTION ALSO ALLOWS LOOSER LINKAGE TO EVOLVE
-%However, with haploid selection, heterogametic transitions (XY to ZW or ZW to XY) can occur even when the new sex-determining region is less closely linked to the locus under selection. 
-%Neo-W (neo-Y) alleles invade when their fitness in females (males) is greater than the mean fitness of females (males) under the ancestral sex-determination system and/or females (males) are the rarer sex.
-
-%With sexually-antagonistic selection (between diploid sexes) only, linkage between a selected locus and the sex-determining region strengthens associations between male beneficial alleles and the male-determining allele (Y or Z) and between female beneficial alleles and the female-determining allele (X or W).
-%Thus, the mean fitness of both males and females increases with closer linkage to the sex-determining region. 
-%Therefore, new sex-determining alleles only invade if they are more closely linked than the ancestral sex-determining region. 
-%However, if there is haploid selection on loci linked to an XY (ZW) sex-determining region, selection can maintain polymorphisms at which the product of the frequency of females (males) and the mean fitness of females (males) is lower than it would be without sex-linkage.
-%In these cases, unlinked neo-W (neo-Y) alleles can increase the frequency and/or fitness of the only sex they are found in, at a cost to the other sex, and invade despite lowering population mean fitness (Figure \ref{fig:Combination_MeanFit}).
-%\textcolor{red}{This is similar to mitochondria and male disease ...?}
-
-%%SEX-RATIO SELECTION
-%\textcolor{blue}{maybe drop paragraph?}
-%\textcolor{red}{I messed with the sex ratio selection paragraphs to tone down our "it doesn't matter" speech from before. Have at any amendments you'd like to make.}
-%Linkage between haploid selected loci and sex-determining regions cases biased zygotic sex ratios \citep{Hamilton:1967ts,Burt:2006,Field:2012fd,Field:2013cc}.
-%One might then expect Fisherian sex ratio selection to drive the spread of new sex-determining systems that bring the sex ratio closer to 50:50. 
-%Fisherian sex ratio selection follows from the fact that, for an autosomal locus, half of the genetic material is inherited from a male, and half from a female \citep{Fisher:1930wy,West:2009we}. 
-%Thus, if the population sex ratio is biased towards females, the average per-individual contribution of genetic material to the next generation from males is greater than the contribution from females (and vice versa for male-biased sex ratios).
-%Therefore, a mutant that increases investment in males will spread via the higher per-individual contributions made by males. 
-%%%That is, under Fisherian sex ratio selection, the success of a mutant relative to the non-mutant depends, in equal parts, on the contributions made by males and females to the next generation. 
-%An implicit assumption of Fisherian sex ratio selection is that the mutant allele is autosomal and has the same inheritance pattern as the non-mutant allele. 
-%The mutations we consider here, neo-sex-determining alleles, break this assumption. 
-%For example, the success of neo-Y/neo-W mutations depends only on the number of alleles contributed by males/females (Table \ref{tab:haplotype_growth}). 
-%In this respect, a neo-W is similar to a cytoplasmic element, which also does not experience selection to balance sex ratios \citep{Frank:1989vl,Werren:1998co,Chase:2007bf}.
-%Even mutants that are equally likely to be found in males or females, such as an environmental sex determination mutation (equation \ref{eq:lambda_ESD}), are not strictly autosomal if they determine sex.
-%Thus, despite the fact that sex ratio biases caused by gametic competition or meiotic drive have been shown to exert Fisherian sex ratio selection on various autosomal modifiers \citep{Stalker:1961th,Smith:1975ft,Frank:1989vl,Hough:2013uo,Ubeda:2015fx, Otto:2015va}, we do not find evidence of Fisherian sex ratio selection acting during invasion by neo-sex-determination systems (e.g., see Figure \ref{fig:Combination_Turnover} and \citealt{Ubeda:2015fx}, in which a neo-Y invades despite biasing sex ratios).
-
-%Sex ratio biases caused by gametic competition or meiotic drive have been shown to exert Fisherian sex ratio selection on various autosomal \citep{Stalker:1961th,Smith:1975ft,Frank:1989vl,Hough:2013uo,Ubeda:2015fx, Otto:2015va} and sex-linked \citep{Kozielska:2010vm} modifiers.
-We find that the spread of neo-sex-determining systems cannot be simply predicted from their effect on the sex ratio. 
-On one hand, sex ratio biases caused by haploid selection can facilitate trans-GSD transitions or GSD-ESD transitions between sex-determining systems. 
-For instance, alleles favoured by haploid selection in males often become associated with the Y, which leads to a male-biased zygotic sex ratio.
-This male bias increases the potential for a neo-W to invade (Table \ref{tab:haplotype_growth}), which can equalize the sex ratio \citep[e.g., see Figure \ref{fig:SexRatioBad}B, for related examples see][]{Kozielska:2010vm}.
-%We find that sex ratio biases caused by haploid selection can also affect transitions between sex-determining systems (e.g., see $\zeta$ terms in Table \ref{tab:haplotype_growth}). 
-%However, the neo-W may not equalize the sex ratio (e.g., if the driving allele also drives in females or affects competition among eggs)
-On the other hand, sex ratio selection can be overwhelmed by additional selective effects, preventing a neo-W or ESD allele from invading, even if it would balance the sex ratio (e.g., when selection acts in opposite directions in male and female diploids, Table \ref{tab:specialcases}).
-%and equalizing the sex ratio.
-Indeed, transitions between sex-determining systems can generate stronger sex ratio biases \citep[e.g., Figure \ref{fig:SexRatioBad}A and step 1 in][]{Ubeda:2015fx}.
-%For example, where a neo-Y invades and is linked with a locus that experiences haploid selection in male gametes, the sex ratio evolves to become biased \citep[e.g., see Figure \ref{fig:SexRatioBad}A and step 1 in][]{Ubeda:2015fx}.
-%For example, in an ancestral ZW system, haploid selection in males can allow a linked neo-Y to invade, despite the fact that it creates a male-biased sex ratio because the neo-Y becomes associated with the driven allele (Figure \ref{fig:SexRatioBad}A).
-%\textcolor{blue}{and figure 1, where the end of one panel is the same as the beginning of another, however, this figure may change).}
-%What we would like to stress is that sex ratio selection alone cannot predict when new sex-determining systems can evolve.
-Significantly, with weak selection, we find that there is no difference in conditions allowing XY to ZW and ZW to XY transitions, indicating that sex chromosome transitions are not predominantly predicted by their effect on the sex ratio (i.e., the sex ratio bias created by male haploid selection facilitates the spread of a neo-W into an XY system to the same degree that male haploid selection drives the spread of a neo-Y into a ZW system with a 1:1 sex ratio).
-%An asymmetry can develop when sex-linkage is tight (e.g., Figure \ref{fig:Combination_Centimorgans} near -25cM and 25cM) but under most circumstances we do not predict asymmetry between XY to ZW and ZW to XY transitions despite the presence/absence of sex ratio selection.
-Thus, haploid selection can favour trans-GSD transitions both via sex ratio selection and via selection on alleles associated with the neo-sex-determining allele, and these selective pressures are often predicted to be of equal magnitude.
-%\textcolor{red}{Maybe try to emphasise surprisingness in the paragraph more? e.g., how wrong you'd be if you assumed selection to equalise sex ratios, or it this implied?}
-%\textcolor{blue}{nice, pretty subtle argument but I think that's a good job.}
-
-%Previous studies where ESD is favoured have typically assumed that environmental conditions (e.g., maternal condition, mate quality, age, or host size) can differentially affect the fitness of males versus females such that ESD invades because it allows sex determination to depend on the environment \citep[reviewed in][]{Charnov:1982wg,Bull:1983vi,West:2009we}.
-
-%WHY SEX-RATIO BIASES CAN BE FAVOURED
-%We note two other ways in which sex determination has been shown to relate to zygotic sex ratios.
-%Firstly, female-biased sex ratios can be favoured when there is local mate competition, where all matings are between siblings and assuming one male can inseminate many females \citep{Hamilton:1967ts}.
-%Therefore, with local mate competition, feminizing mutations can spread because they bias the sex ratio towards females \citep{Wilson:1981vm,Vuillleumier:2007bh}. 
-%Secondly, environmental conditions (e.g., maternal condition, mate quality, age, or host size) can differentially affect the fitness of males versus females such that the optimal allocation to males/females depends on the environment \citep{Trivers:1973wb,Charnov:1977tx,Charnov:1982wg}.
-%In such cases, flexible sex-determination systems may evolve in order to allow the zygotic sex ratio to be determined in a way that depends on the environment \citep{Charnov:1977tx,Werren:1984tl,Pen:2010kk}.
-%In this study, we do not consider environmental condition dependence or local mate competition \citep[reviewed in][]{Charnov:1982wg,Bull:1983vi,West:2009we}.
-
-%HOW TO TEST EMPIRICALLY
-%\textcolor{blue}{I think Sally was sceptical of this idea. i.e., if the second term in \ref{eq:lambda_neoW} is negative, then get less transitions with haploid selection included, right? }
-%\textcolor{red}{Yeah, and given that only 1/2 the discovered plant sex chromosomes are hetermorphic and there are so few plant sex chromosomes to begin with (Charlesworth 2016 Annual Review Plant Biology), might it be the case that haploid selection is constraining things?
-perhaps we could think of some particular forms of haploid selection that might be common and give their predicted effects, or just say some things that are possible with haploid selection that are not without it -- if there are any.
-just looking at eq 3 though, its gonna be hard to get a low freq of A on the Y if haploid selection in males favours A, i.e., it should often be positive when there is no female haploid selection, right?}
-%\textcolor{blue}{That sounds right to me and is backed up by equation \eqref{eq:freq_diffs}.
-It may be technically possible for that term to be negative though.
-Re: hetermorphism, I see that as a slightly different issue.
-It's thought that haploid selection may prevent deletions from becoming fixed on the Y, like in the Crowson (2017) paper.
-%I think the issue of `why so few plant sex chromosomes' is partly an issue of detection and also `why so much hermaphroditism'.
-Is it possible that the ESD results could show selective forces that also favour transitions from dioecy to hermaphroditism?
-I think so.
-Our ESD mutant produces 1/2 females and 1/2 males whereas a hermaphrodite invests roughly equally in each type of gamete produced.
-We don't consider the forces that are usually thought to be involved in these transitions though (inbreeding depression, reproductive assurance and possibly others?).
-}
-%Taken at face value, our results indicate that transitions in heterogametey (XY to ZW or vice versa) are more likely to be favoured by selection if there is selection upon both haploid and diploid genotypes rather than diploid selection alone ().
-%This prediction could be examined using a suitable proxy for haploid selection, for example, \cite{Lenormand:2005vb} use the outcrossing rate in plants as a proxy for the strength of pollen competition.
-%In animals, one might expect gametic competition to be stronger in species where sperm is required to live for a long time after spermatogenesis because transcripts shared during spermatogenesis may become depleted, revealing the haploid phenotype of the sperm \citep{Immler:2014im}.
-%Given the caveats mentioned above about the form of meiotic drive modelled, we would also expect that heterogametic transitions in sex determination would be more common in clades where there is meiotic drive.
-
-%Together, our models demonstrate novel selective forces that favour heterogametic transitions (XY to ZW or ZW to XY). 
-%One common prediction is therefore that heterogametic transitions are favoured under a wider range of conditions than homogametic transitions. 
-%However, heterogametic transitions are not clearly in excess.
-For example, \citet{Vicoso:2015hf} found a dozen sex chromosome configurations among Dipteran species but only one transition between male and female heterogametey.
-%While our models examine the selective forces that favour the spread of new sex-determining regions, observed transitions could also reflect the mutation rate for neo-Y versus neo-W alleles (e.g., duplications of the ancestral sex determining region could be particularly likely).
-%In addition, heterogametic transitions could be limited due to the production of YY males or WW females (see below). 
-%Alternatively, it might be useful to compare clades that are expected to differ in the strength of haploid selection (e.g., plants are thought to experience more selection during their multicellular haploid stage
-
-%HAPLOID SELECTION (genomic location of haploid selected loci and comparative patterns) 
-We have shown that the spread of new sex determination systems can be driven by loci experiencing haploid selection. 
-%Our results suggest that haploid selected loci that have been involved in driving turnovers between sex-determination systems could occur around the ancestral- or novel-sex-determining regions. 
-%Our results suggest that polymorphic loci that are ancestrally sex-linked and under sex-specific selection could also drive heterogametic transitions between sex-determination systems. 
-%As with sexually-antagonistic selection, the presence of haploid selected loci around ancestral- or novel-sex-determining regions could support their role in sex chromosome turnover.
-In agreement with this hypothesis, a recent transcriptome analysis in \textit{Rumex} shows that Y-linked genes have higher expression in haploid pollen than autosomal genes \textcolor{red}{(check this is accurate)}.
-Interestingly, haploid-expression is also more common on the autosome that is orthologous to the sex chromosomes in closely related species suggesting that new sex chromosomes may have been favoured through their association with haploid selected alleles on these chromosomes \textcolor{red}{(Sandler et al., 2018, Personal Communication)}.
-%maybe add a flag here for switching to clade-level expectations:
-In general, we predict that haploid selection increases lability of sex-determination systems, particularly because haploid selection can cause transitions that increase or decrease sex-linkage (e.g., the final state of the red line in Figure \ref{fig:SexRatioBad}B is the starting state in Figure \ref{fig:SexRatioBad}A).
-Turnovers driven by haploid selection may help to explain the relative rarity of heteromorphic sex chromosomes in plants, which are thought to experience more selection during their multicellular haploid stage.
-If haploid selection is strong but selective differences between male and female diploids are weak, we find that trans-GSD transitions (XY to ZW or ZW to XY) are favoured more strongly than cis-GSD transitions, with transitions to ESD intermediate (e.g., with $|D^\male - D^\female| << |\alpha_\Delta^\male - \alpha_\Delta^\female + t^\male - t^\female|$ we have $\lambda_{W',XY} > \lambda_{Y',XY}$; Equations \ref{eq:lambda_neoW} and \ref{eq:freq_diffs}).
-Among the relatively few dioecious clades in which multiple species have well characterized sex chromosomes \citep{Ming:2011iy}, trans-GSD transitions have been inferred in \textit{Silene} subsection \textit{Otites} \citep{Slancarova:2013dq} and in \textit{Salicaceae} \citep{Pucholt2015,Pucholt2017}.
-%Potentially, successive heterogametic transitions between master regulators of sex-determination could be inferred from careful examination of the molecular pathways by which sex is determined. 
-%Our predictions could also be examined using a suitable proxy for haploid selection, for example, \cite{Lenormand:2005vb} use the outcrossing rate in plants as a proxy for the strength of pollen competition.
-Assuming that transitions from dioecy to hermaphroditism (equal parental investment in male and female gametes) are favoured in a similar manner to the ESD examined here (equal probability of zygotes developing as males or females), our results suggest that competition during the haploid stage could also drive transitions between dioecy and hermaphroditism, which are frequent in plants \citep{Kafer2017, Goldberg2017}.
-%In animals, one might expect gametic competition to be stronger in species where sperm is required to live for a long time after spermatogenesis because transcripts shared during spermatogenesis may become depleted, revealing the haploid phenotype of the sperm \citep{Immler:2014im}.
-%We would also expect that heterogametic transitions in sex determination would be more common in clades where there is meiotic drive.
-
-%IDENTIFICATION OF LOCI IN GENOMIC LOCATIONS THAT IMPLICATE THEM IN SEX-CHROMOSOME TURNOVER
-%The hypotheses presented here can be empirically investigated in a similar manner to the idea that transitions between sex-determining systems are favoured by linkage to sexually-antagonistic variation.
-%In the case of sexually-antagonistic variation, one supporting observation is that genes expected to be under sexually-antagonistic selection (e.g., those causing bright male colouration) have been found on recently derived sex chromosomes \citep{Lindholm:2002dw,Tripathi:2009cw,Ser:2010iq}.
-In support of their role in sex chromosome turnover, genes expected to be under sexually-antagonistic selection (e.g., those causing bright male colouration) have been found on recently derived sex chromosomes \citep{Lindholm:2002dw,Tripathi:2009cw,Ser:2010iq}.
-Our results show, however, that tight ancestral-linkage of polymorphic loci can also drive trans-GSD transitions. 
-In addition, we find that polymorphic sex determining systems (X, Y, W, and Z alleles all present) can be maintained when a selected locus is tightly linked to the ancestral sex-determining system (e.g., Figures \ref{fig:freqAll}B and \ref{fig:freqAll}C), which is not possible with loose linkage \citep{vanDoorn:2010hu}.
-%As noted by \citet{vanDoorn:2010hu}, it would be prudent to compare closely related clades in order to determine whether observed polymorphisms predate a transition in sex-determination or arose afterwards.
-%, particularly because sex-linkage allows sexually-antagonistic selection to maintain polymorphisms under a different and larger parameter space \citep{Rice:1987hs,Jordan:2011fj}.
-For example, our results suggest a potential mechanism maintaining multiple sex determining alleles in the platyfish (\textit{Xiphophorus maculatus}), in which X,Y, and W alleles segregate at one locus (or two closely-linked loci) near to potentially sexually-antagonistic genes for pigmentation and sexual maturity \citep{Kallman1965,Kallman1968, Volff2001, Schultheis2006}.
-Several rodent species also maintain feminizing alleles along with the ancestral X and Y sex-determination alleles \citep[reviewed in][]{Fredga1994}. 
-For example, in nine \textit{Akadon} species, it appears that male-determining-\textit{sry} expression is suppressed by an autosomal feminizing allele, creating XY females \citep{Bianchi2002,Sanchez2010}, which have increased fitness relative to XX females \citep{Hoekstra2001}.
-In \textit{Mus microtoides}, females can have XX, XX$^\ast$ or X$^\ast$Y genotypes \citep{Veyrunes2010}. 
-Previous theory would predict that the X$^\ast$ chromosome (or the autosome it is fused to) harbours female beneficial alleles, driving its spread. 
-However, XX and XX$^\ast$ females have similar fitness, whereas X$^\ast$Y female fitness is enhanced \citep{Saunders2014,Saunders2016, Veyrunes2017}.
-Although Y-linkage of female-beneficial alleles is counterintuitive, our tight linkage model suggests that it can be stably maintained and then favour new feminizing mutations, which is a parsimonious explanation for the spread of feminizing alleles in these rodent species.
-
-%Limitation 1: DEGENERATE Y
-We note that we assume that sex-determining alleles do not experience direct selection except via their associations with sex and selected alleles.
-However, in some cases, there may be significant degeneration around the sex-limited allele (Y or W) in the ancestral sex-determining region because recessive deleterious mutations and/or deletions accumulate around the Y or W sex-determining regions \citep{Rice:1996ke,Charlesworth:2000cc,Bachtrog:2006ed,Marais:2008hm}.
-During trans-GSD transitions (XY to ZW or ZW to XY), but not cis-GSD transitions (XY to XY or ZW to ZW), any recessive deleterious alleles linked to the Y or W are revealed to selection in YY or WW individuals \citep{Bachtrog:2014bx}.
-This phenomenon was studied by \citet{vanDoorn:2010hu}, who found that degeneration can prevent fixation of a neo-W or a neo-Y allele, leading to a mixed sex-determination system where the ancestral and new sex-determining loci are both segregating.
-However, they noted that very rare recombination events around the ancestral sex-determining region can allow these trans-GSD transitions to complete.  
-%While not explicitly studied, we also predict that Y or W degeneration would prevent fixation of the new sex-determining genes considered here.
-Degeneration around the Y or W could explain why trans-GSD transitions are not observed to be much more common than cis-GSD transitions despite the fact that our models demonstrate that they are favoured under a wider range of conditions, especially with haploid selection.
-For example, \citet{Vicoso:2015hf} found a dozen sex chromosome configurations among Dipteran species but only one transition between male and female heterogamety.
-
-%Limitation 3: don't consider m alleles with similar k to ancester, no ancestral ESD considered
-In this study, we have only considered neo-sex-determining alleles of large effect. 
-However, we expect similar selective forces to act on masculinizing/feminizing alleles of weaker effect. 
-For example, \citet{Muralidhar2018} consider small effect masculinizing/feminizing alleles within a threshold model of sex determination, finding that they can be favoured when linked to loci that experience sexually-antagonistic selection.
-These results echo those for large-effect neo-Y/neo-W alleles \citep{vanDoorn:2007eu,vanDoorn:2010hu}.
-Finally, while we have considered cis-GSD, trans-GSD, and GSD to ESD transitions, we have not explicitly considered ESD to GSD transitions. 
-Recent models of ESD to GSD transitions \citep{Ubeda:2015fx,Muralidhar2018} show that that neo-Y/neo-W alleles can be favoured when they arise near to haploid and/or diploid selected loci, which also occurs in our model.
-
-%Limitation 2: TWO ALLELE DRIVE
-%Another simplification that we made is that meiotic drive involves only a single locus with two alleles. 
-%However, many meiotic drive systems involve an interaction with another locus at which alleles may `suppress' the action of meiotic drive \citep[][]{Burt:2006,Lindholm:2016cw}.
-%Thus, the dynamics of meiotic drive alleles can be heavily dependent on the interaction between two loci and the recombination rate between them, which in turn can be affected by sex-linkage if there is reduced recombination between sex chromosomes \citep{Hurst:1991uh}.
-%Furthermore, in some cases, a driving allele may act by killing any gametes that carry a `target' allele at another locus, in which case there can be fertility effects that alter the equilibrium frequency of a meiotic drive allele \citep{Holman:2015en}.
-%In polygamous mating systems, the intensity of pollen/sperm competition can depend on the density of males available to donate pollen/sperm, which can itself depend on the sex ratio \citep{Taylor:2002wu}.
-%In terms of our model, this implies that the strength of gametic competition ($t^\male$) may both determine and be determined by the sex ratio. 
-%How the evolution of new sex-determining mechanisms could be influenced by two-locus meiotic drive and/or by ecological feedbacks under different mating systems remains to be studied.
-
-%\textcolor{blue}{similarly, this part doesn't discuss our new tight linkage results or our new perspective on sex ratios.}
-%CONCLUSION
-We have shown that tight sex-linkage and haploid selection can drive previously unexpected transitions between sex-determination systems.
-In particular, both can select for neo-sex-determining loci that are more loosely linked. 
-In addition, haploid selection can cause transitions analogous to those caused by purely sexually-antagonistic selection, eliminating the need for differences in selection between male and female diploids.
-We conclude that haploid selection should be considered as a pivotal factor driving transitions between sex-determination systems. 
-Perhaps counterintuitively, transitions involving haploid selection can be driven by sex ratio selection or cause sex ratio biases to evolve and Fisherian sex ratio selection is not an overwhelming force.
-Overall, our results suggest several new scenarios under which new sex-determination systems are favoured, which could help to explain why the evolution of sex-determination systems is so dynamic. 
-%Further, we have shown the way in which transitions are affected by haploid selection is not intuitively obvious. 
-%Firstly, sex-specific haploid selection affects turnovers between sex-determination systems in a manner that is qualitatively different from diploid sex-specific selection. 
-%In particular, closer linkage between a sex-determining locus and a selected locus is not always favoured during heterogametic transitions when there is haploid selection. 
-%Secondly, even though haploid selection is a source of zygotic sex ratio biases, in our models Fisherian sex ratio selection does not have good explanatory power in determining whether various sex-determination systems evolve.
-%This result is surprising given that sex ratios are ultimately determined via the sex-determination system, and leads us to the conclusion that three selective forces -- haploid, diploid, and sex ratio selection -- should all be considered when exploring transitions between sex-determination systems.
-
-\bibliographystyle{amnatnat.bst}
-\bibliography{sex_chromosomes.bib}
-
-\newpage
-%\section*{Figures}
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Tighter linkage allows looser sex-linkage to evolve, even in absence of haploid selection
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\includegraphics[width=\linewidth]{PositionPlot_SexAntagTighter}
-%\caption{
-%In the absence of haploid selection, tight linkage allows looser sex-linkage to evolve in transitions between XY and ZW systems.
-%In panel A, linkage is loose enough relative to selection that the weak selection analytical results hold, and a neo-W can only invade when it is more tightly linked with the selected locus ($R<r$; shaded region).
-%In panel B, linkage is tight enough relative to selection that the weak selection analytical results do no hold, and a neo-W can only invade even when it is less tightly linked with the selected locus ($r<R$; unshaded region).
-%Parameters: $w_{AA}^\female = w_{aa}^\male = 1.05$, $w_{aa}^\female = w_{AA}^\male = 0.85$, $w_{Aa}^\female = 1$, $w_{Aa}^\male = 0.925$, $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
-%}
-%\label{fig:SexAntagTighter}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Both neo-W haplotypes can spread, in the absence of haploid selection, when there is overdominance
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\includegraphics[width=0.45\linewidth]{regionplot_2a}
-%\includegraphics[width=0.45\linewidth]{regionplot_2a_Color_Ya_Either}
-%\includegraphics[width=0.45\linewidth]{BothWsInvade_Overdominance}
-%\caption{
-%In the absence of haploid selection, both neo-W haplotypes can spread in an XY system when there is overdominance.
-%Panel A shows the range of male homozygote fitnesses that allow either neo-W haplotypes to invade.
-%The blue region overlaps with a red region, where both neo-W haplotypes can invade a population with $A$ fixed on the X and $a$ fixed on the Y.
-%The green region (overlapped by the orange region) is where both neo-W haplotypes can invade a population with $a$ fixed on the Y and a polymorphic X.
-%The orange region (outside the green region) is where only the neo-W-$A$ haplotype can invade
-%Panel B shows the temporal dynamics of the invading neo-W haplotypes; in this case the neo-W does not fix, leading to a polymorphic sex-determining system.
-%Asterisk in panel A marks parameter values ($w_{aa}^\male=0.15$, $w_{AA}^\male=0.1$) used in panel B.
-%Parameters: $w_{AA}^\female = w_{aa}^\female = 0.6$, $w_{Aa}^\Hermaphrodite = 1$, $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$, $r=R=0$.
-%\textcolor{red}{make two more temporal plots with visible asterisks in green and orange regions; figure out better colours to show possibilities}
-%}
-%\label{fig:BothOverdominance}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%With weak selection, a less tightly linked neo-W can invade an XY system when there is some haploid selection, and this invasion decreases mean diploid fitness
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\includegraphics[width=0.5\linewidth]{Loose_Fitness_Decline}
-%\caption{
-%With weak selection, a less tightly linked neo-W can invade (and fix in) an XY system (causing the Y to fix in females) when there is some haploid selection (blue and green curves in panel A), and this invasion decreases mean diploid fitness (green and blue curves in panel B).
-%Parameters: $s^\Hermaphrodite = 0.2$, $h^\Hermaphrodite = 0.7$, $t^\Hermaphrodite = \alpha^\male_\Delta = 0$, $\alpha^\female_\Delta = -0.1$, $r=1/10$.
-%}
-%\label{fig:LooseDecline}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%A neo-W can invade an XY system under a large number of selective regimes
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\includegraphics[width=0.5\linewidth]{PositionPlot_4}
-%\caption{
-% A neo-W can invade an XY system under a large number of selective regimes.
-%In panel A, there is no haploid selection ($t^\Hermaphrodite = \alpha^\Hermaphrodite_{\Delta} = 0$) and selection in diploids is sexually antagonistic ($s^\male = -s^\female = 1/10$, $h^\male = 1-h^\female = 3/10$), in which case the neo-sex-determining allele can only invade if it is more closely linked to the selected locus ($R<r$, gray region; but see Figure \ref{fig:SexAntagTighter}B for the case of very tight linkage).
-%In panel B, male drive ($\alpha^\male_{\Delta} = -1/20$, $t^\Hermaphrodite = \alpha^\female_{\Delta} = 0$) opposes selection in diploids (no sex-differences: $s^\Hermaphrodite = 1/10$, $h^\Hermaphrodite = 7/10$), in which case the neo-sex-determining allele can invade regardless of linkage.
-%In panel C, haploid competition in males ($t^\male = -1/10$, $t^\female = \alpha^\Hermaphrodite_{\Delta} = 0$) opposes selection in diploids (sex-differences: $s^\male = 3 s^\female = 3/20$, $h^\Hermaphrodite = 7/10$), in which case the neo-sex-determining allele can once again invade regardless of linkage.
-%We use Haldane's map function \citep[Equation 3 in ][]{Haldane1919} to convert from map distance (centiMorgans, cM) to the probability of recombination (an odd number of cross-over events).   
-%}
-%\label{fig:Combination_Centimorgans}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Sex ratio selection is not a good predictor of neo-W invasion into an XY system
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\includegraphics[width=\linewidth]{Combination_Turnover_Ratio}
-%\caption{
-%Sex ratio selection alone is not a good predictor of turnover between sex-determining systems.
-%In panels A and C, male drive in an ancestral XY system causes a male bias, allowing a neo-W to invade and fix (causing the Y to fix in females), which balances the sex ratio (it also avoids selection in males, and thus makes better females in this case of sex-specific ploidally-antagonistic selection).
-%In panels B and D, male drive in an ancestral ZW system has no affect on the sex ratio, yet a neo-Y can invade and fix (causing the W to fix in males) because it becomes linked with the driving allele, and this imparts a sex ratio bias.
-%Parameters:  $s^\female =s^\male = 0.2$, $h^\female = h^\male = 0.7$, $t^\female = t^\male = \alpha^\male_\Delta = 0$, $\alpha^\female_\Delta = -1/10$, $r=1/20$.
-%}
-%\label{fig:SexRatioBad}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Haploid selection can lead to polymorphic SD systems 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\includegraphics[width=\linewidth]{Polymorphic}
-%\caption{
-%Tight linkage (relative to selection) and/or haploid selection can cause stable polymorphic sex-determining systems.
-%In panel A, there is strong overdominance in both sexes and no haploid selection  (parameters as in Figure \ref{fig:BothOverdominance}B with $r = 1/10$), in which case a neo-W can invade regardless of sex-linkage, but cannot not fix (i.e., the Y does not fix in females, and X, Y, W, and Z all segregate at equilibrium).
-%In panel B, there is sex-antagonistic selection at the diploid stage and drive in females (parameters as in Figure \ref{fig:SexAntagTighter} with $\alpha^\female_\Delta = 1/20$ and $r = 1/10$), in which case a sufficiently tightly linked neo-W can invade ($R<\sim r$), but only fixes if $R=0$.
-%}
-%\label{fig:Polymorphism}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%CYCLES!
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\includegraphics[width=0.5\linewidth]{BothWsInvade_Overdominance_Cycles}
-%\caption{
-%Thought I'd show this just for fun (not for publication).
-%}
-%\label{fig:Cycles}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Heterogametic transitions with/without sex ratio change
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\begin{tikzpicture}[remember picture]
-%	\node[] (plot) {\includegraphics[width=\linewidth]{Combination_Turnover}};
-%	\node[above = 0cm of plot, xshift = -70] () {$r=0.5$, $R=0.05$};
-%	\node[above = 0cm of plot, xshift = 120] () {$r=0.05$, $R=0.5$};
-%	\node[left = 0cm of plot, yshift = 105, rotate = 90] () {XY $\rightarrow$ ZW};
-%	\node[left = 0cm of plot, yshift = -20, rotate = 90] () {ZW $\rightarrow$ XY};
-%\end{tikzpicture}
-%\caption{
-%Heterogametic transitions from XY to ZW sex determination (neo-W frequency shown by black lines, panels A and B) or from ZW to XY (neo-Y frequency shown by black lines, panels C and D) occur similarly regardless of sex ratio biases present before (B versus D) or after (C versus A, dashed lines show male frequency).
-%During invasion by a neo-ZW sex-determination system (A and B), the ancestral Y fixes in both males and females (blue and red lines). 
-%Similarly, the ancestral W allele fixes in males and females (blue and red lines) during a ZW to XY transition. 
-%In this plot, there is no gametic competition ($t^\female=t^\male=0$) and meiotic drive occurs during male meiosis only ($\alpha^\female_{\Delta}=0$, $\alpha^\male_{\Delta}=-1/5$).
-Therefore, sex ratio biases can only arise when the \textbf{A} locus is linked to an XY sex-determining locus.
-%In panels A and C, the neo-sex-determining locus is more closely linked to the \textbf{A} locus than the ancestral sex-detemining region ($r=1/2$, $R=1/20$) such that a neo-Y can caused biased sex ratios (panel C).
-%In panels B and D, the ancestral sex-determining locus is more closely linked to the \textbf{A} locus than the neo-sex-detemining locus ($r=1/20$, $R=1/2$). 
-%Therefore, an ancestral XY sex determination can have a biased zygotic sex ratio that becomes unbiased after an unlinked neo-W invades (B). 
-%However, in panel D, a unlinked neo-Y invades an ancestral ZW sex-determination system in a similar manner but no biases to the zygotic sex ratio occur. 
-%With diploid selection alone, neo-sex-determining loci do not spread if they are less closely linked to the \textbf{A} locus than the ancestral sex-determining locus (see equation \eqref{eq:lambda_neoW} and Figure \ref{fig:Combination_Centimorgans}A).
-%In this plot there are no sex differences in selection and an equilibrium is maintained because selection in diploids opposes meiotic drive, $s^\female =s^\male = 1/5$, $h^\female = h^\male = 7/10$.
-%\textcolor{red}{Aesthetic adjustments: 
-%%Could add titles to the columns/rows: neo-W for row 1, neo-Y for row 3, $r=0.5$, $R=0.05$ for column 1 and $r=0.05$, $R=0.5$ for column 2. 
-%%Could adjust padding (too much whitespace where there is no axis label). 
-%%It also seems could increase ratio of font size relative to plot size to make figure more compact. 
-%%Matt - could you uncomment the line legends in the Mathematica file (function not included in my Mathematica version).
-%Add chromosome cartoons to depict recombination rates?
-%}
-%}
-%\label{fig:Combination_Turnover}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Heterogametic transitions with/without sex ratio change
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\begin{tikzpicture}[remember picture]
-%	\node[] (plot) {\includegraphics[width=\linewidth]{Combination_Turnover_Ratio}};
-%	\node[above = -1cm of plot, xshift = -100] () {XY $\rightarrow$ ZW};
-%	\node[above = -1cm of plot, xshift = 90] () {ZW $\rightarrow$ XY};
-%\end{tikzpicture}
-%\caption{
-%%\textcolor{red}{Is this what Sally was thinking?}
-%%\textcolor{blue}{I think this works but I'm confused as to why the speed of spread should be so much different for XY and ZW here.
-Figure \ref{fig:Combination_Turnover} and \ref{fig:Combination_Centimorgans} suggests that there's not much difference between XY->ZW and ZW->XY.
-Maybe we should just stick with the 4 cases in figure \ref{fig:Combination_Turnover}.
-}
-%%\textcolor{red}{i messed up and had $r=0.5$ instead of $r=0.05$ for B and D. haven't fixed fitness plot below.}
-%Heterogametic transitions occur (panels A and B) regardless of sex ratio biases (panels C and D).
-%A neo-W invades (panel A) and equalizes the male-biased sex ratio (panel C) that was caused by meiotic drive in males.
-%A neo-Y invades (panel B) a population with an equal sex ratio. 
-%With any amount of linkage ($R<1/2$), the neo-Y becomes associated with the driving allele in males, and in the end causes a male bias.
-%Parameters: $s^\female = s^\male = 1/5$, $h^\female = h^\male = 7/10$, $t^\female = t^\male=0$, $\alpha^\female_\Delta = 0$, $\alpha^\male_\Delta = -1/5$, $r = 1/20$.
-%}
-%\label{fig:Combination_Turnover_Ratio}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%Changes in mean fitness
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\begin{tikzpicture}[remember picture]
-%	\node[] (plot) {\includegraphics[width=\linewidth]{Combination_Fitness_Rec}};
-%	\node[above = -1cm of plot, xshift = -100] () {XY $\rightarrow$ ZW};
-%	\node[above = -1cm of plot, xshift = 90] () {ZW $\rightarrow$ XY};
-%\end{tikzpicture}
-%\caption{
-%\textcolor{red}{This complicated thing matches the plot above. I don't think we want to include it...?}
-%}
-%\label{fig:Combination_Fitness_Rec}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Changes in mean fitness
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\begin{tikzpicture}[remember picture]
-%	\node[] (plot) {\includegraphics[width=\linewidth]{Combination_MeanFit}};
-%	\node[above = 0cm of plot, xshift = -70] () {$r=0.5$, $R=0.05$};
-%	\node[above = 0cm of plot, xshift = 120] () {$r=0.05$, $R=0.5$};
-%	\node[left = 0cm of plot, yshift = 105, rotate = 90] () {XY $\rightarrow$ ZW};
-%	\node[left = 0cm of plot, yshift = -20, rotate = 90] () {ZW $\rightarrow$ XY};
-%\end{tikzpicture}
-%\caption{
-%Changes in mean diploid fitness of males (blue lines), females (red lines), and the entire population (black lines) during the transitions between sex-determination systems shown in Figure \ref{fig:Combination_Turnover}.
-%Here mean diploid fitness of a particular sex is its mean diploid viability fitness times twice its frequency in the population, to capture the fact that epistatically dominant sex-determining alleles can also invade because they selfishly make more of the sex they are in.
-%The mean fitness of females increases during the spread of neo-W alleles (A and B) and the mean fitness of males increases during the spread of neo-Y alleles (C and D). 
-%However, when a neo-sex determining system evolves that is less closely linked to a locus under selection (B and D), population mean fitness decreases. 
-%%\textcolor{red}{
-%%Could add titles to the columns/rows: neo-W for row 1, neo-Y for row 3, $r=0.5$, $R=0.05$ for column 1 and $r=0.05$, $R=0.5$ for column 2. 
-%%%\& possibly adjust padding (too much whitespace?). 
-%%%Matt - could you uncomment the line legends in the Mathematica file (function not included in my Mathematica version).
-%%}
-%%\textcolor{red}{I'm still confused why male and female mean fitnesses aren't normalized by their frequency.
-I'm not sure we should be calling them means without this normalization step.
-Or we should justify this by saying that mean fitness also has something to do with the number of a sex, i.e., multiply *real* mean fitness in females by freqfemale/(1/2)?
-See the next figure for what happens when we do normalize.}
-%\textcolor{blue}{I think we should give this plot showing (male mean fitness * freq males) and (female mean fitness * freq females), without multiplying by 2 (leave off black lines, population mean fitness).
-%We could also re-plot the sex ratios on this same scale. 
-%The plot below, `adjusted for sex ratio', could then go in the appendix.
-The point is that neo-W (neo-Y) can invade when the frequency of females (males) multiplied by their mean fitness increases.
-}
-%}
-%\label{fig:Combination_MeanFit}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Changes in mean fitness corrected for sex ratio
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\begin{tikzpicture}[remember picture]
-%	\node[] (plot) {\includegraphics[width=\linewidth]{Combination_MeanFit_Corrected}};
-%\end{tikzpicture}
-%\caption{
-%\textcolor{red}{Last plot with mean fitness of sexes corrected for sex ratio. Could add to previous plot with dashed lines?}
-%}
-%\label{fig:Combination_MeanFit_Corrected}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%Chromosomal Positions
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%%\includegraphics[width=\linewidth]{Combination_Centimorgan}\\
-%%\includegraphics[width=\linewidth]{PositionPlot}\\
-%\begin{tikzpicture}[remember picture]
-%%	\node[] () {\includegraphics[width=\linewidth]{PositionPlot}};
-%	\node[] () {\includegraphics[width=0.5\linewidth]{PositionPlot_2}};
-%%	\node[anchor=east] at (0, 1.5) {\footnotesize diploid sex-antagonism}; %, $s^\male s^\female < 0$};
-%%	\node[anchor=east] at (6.5, 1.5) {\footnotesize haploid sex-antagonism}; %, $s^\male s^\female > 0$};
-%%	\node[anchor=east] at (0, -3) {\footnotesize male drive (ploidy-antagonism)}; %, $s^\male < s^\female$};
-%%	\node[anchor=east] at (6.5, -3) {\footnotesize find something interesting to plot};%, $s^\female < s^\female$};
-%%	\node[anchor=center] at (-1.3, 4.25) {\scriptsize tighter sex-linkage};
-%%	\node[anchor=center] at (2.45, 3.5) {\scriptsize ancestral SDR};
-%%	\draw[->,thick] (2.45, 3.25) -- (2.45, 2.5);
-%%	\node[anchor=center] at (-1.4, -0.25) {\scriptsize novel SDR};
-%%	\draw[->,thick] (-1.4, -0.5) -- (-1.4, -1);
-%\end{tikzpicture}
-%\caption{
-% A neo-W can invade an XY system under a large number of selective regimes.
-%%Invasion fitness of a neo-sex-determining allele against the relative genomic location of a locus under direct selection. 
-%% (neo-Y invading ZW in black, neo-W invading XY in red)
-%%The ancestral sex-determining locus is located at -25 and the novel sex-determining locus is located at 25. %and that there is a polymorphism at the \textbf{A} locus maintained by selection.
-%%Thus, if the neo-sex-determining allele invades in the gray region the system evolves tighter sex-linkage.  
-%In panel A, there is no haploid selection ($t^\Hermaphrodite=\alpha^\Hermaphrodite_{\Delta}=0$) and selection in diploids is sexually antagonistic ($s^\male=-s^\female=1/10$, $h^\male=1-h^\female=3/10$), in which case the neo-sex-determining allele can only invade if it is more closely linked to the selected locus ($R<r$, gray region; but see Figure \ref{fig:SexAntagTighter}B).
-%In panel B, there is no diploid selection ($s^\Hermaphrodite=0$) and selection in haploids is sexually antagonistic ($t^\male=-t^\female=0.08$, $\alpha^\Hermaphrodite_{\Delta}=0$), in which case the neo-sex-determining allele can invade regardless of linkage.
-%In panel C, selection in diploids ($s^\male=s^\female=1/10$, $h^\male=h^\female=7/10$) opposes drive in males ($\alpha^\male_{\Delta}=-0.05$, $t^\Hermaphrodite=\alpha^\female_{\Delta}=0$), in which case the neo-sex-determining allele can once again invade regardless of linkage.
-%We use Haldane's map function \citep[Equation 3 in ][]{Haldane1919} to convert from map distance (centiMorgans, cM) to the probability of a cross-over event.    
-%%we include haploid selection. %and assume that selection in diploids is not sexually-antagonistic ($s^\female s^\male>0$). 
-%%A polymorphism can then be maintained by opposing selection between the haploid and diploid phases. 
-%%In B, there is drive in favour of the $a$ allele in males ($\alpha^\male_{\Delta}=-1/20$), no female meiotic drive or gametic competition, $t^\Hermaphrodite=\alpha^\female_{\Delta}=0$), and equal selection in diploid sexes ($s^\female=s^\male=1/10$, $h^\female=h^\male=7/10$).
-%%In this case, a neo-W can invade even when the selected locus is more closely linked to the ancestral sex determining locus (see Table \ref{tab:specialcases} and Figure \ref{fig:Combination_Turnover}).
-%%In C and D, there is gametic competition among male gametes only (favouring $a$, $t^\male=-1/10$) and no meiotic drive or gametic competition in females ($t^\female=\alpha^\Hermaphrodite_{\Delta}=0$).
-%%In this case, the neo-W does not invade if $s^\female>s^\male$ (panel C: $s^\female=3/20$, $s^\male=1/20$) but does if $s^\female<s^\male$ (panel D: $s^\female=1/20$, $s^\male=3/20$), see Table \ref{tab:specialcases}.\\
-%%\textcolor{red}{
-%%1.
-I suspect that panel C has a region where no equilibrium is maintained (CHECK!
-Maybe include different parameters here or remove the part when no equilibrium).
-MMO: If you trust the sieve function there are stable equilibria across the entire range, although they differ greatly between XY and ZW systems near -25cM.
-%%\\
-%%2.
-Currently use different parameters for B than using in figure \ref{fig:Combination_Turnover} (selection/drive twice as strong in turnover figure).
-MMO: this is to keep it within the bounds of the plot -- using the same parameters as figure 1 makes the peak at -25 reach roughly 0.1, and then it is difficult to see the details of A,C, and D.
-%%%This plot would also benefit from titles giving, e.g., ``sexually-antagonistic selection, $s^\female s^\male<0$'' for A, ``male meiotic drive, $s^\female s^\male>0$'' for B
-%%}
-%}
-%\label{fig:Combination_Centimorgans}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%Haplotype invasion region plot
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\begin{tikzpicture}[remember picture]
-%	\node[] () {
-%	\includegraphics[width=0.5\linewidth]{regionplot_2a}
-%	\includegraphics[width=0.5\linewidth]{regionplot_hap}
-%	};
-%\end{tikzpicture}
-%\caption{
-%Parameter space (gray) where both neo-W haplotypes can invade from the same stable resident $r=0$ equilibria (equations \ref{eq:tightequil}), and therefore where an unlinked neo-W can invade an XY system with perfect sex-linkage.
-%\textbf{A}, In the absence of haploid selection, both neo-W haplotypes can invade for much of the parameter space where the relative fitnesses of male homozygotes, $w_{AA}^\male$ and $w_{aa}^\male$, are both less than that of the heterozygote, $w_{Aa}^\male = 1$.
-%In the white region neo-W haplotypes paired with the allele fixed on the Y cannot invade.
-%Parameters as in \cite{Otto2014} Figure 2a: $w_A^\Hermaphrodite=w_a^\Hermaphrodite$, $\alpha^\Hermaphrodite=1/2$, $w_{Aa}^\Hermaphrodite=1$, and $w_{AA}^\female=w_{aa}^\female=0.75$.
-%\textbf{B}, When selection is the same in both diploid sexes ($w_{aa}^\Hermaphrodite = 1$, $w_{Aa}^\Hermaphrodite = 1 + h s$, $w_{AA}^\Hermaphrodite = 1+s$), both neo-W haplotypes can invade over a portion of the parameter space where selection in diploids ($s$) opposes the force of drive during meiosis in males ($\alpha_{\Delta}^\male$).
-%Parameters: $w_A^\Hermaphrodite=w_a^\Hermaphrodite$, $\alpha^\female=1/2$, $h=1/2$.
-%}
-%\label{fig:regionplot_2a}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%W invades XY and fixes
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}
-%\centering
-%\includegraphics[width=0.5\linewidth]{FreqWLowR}\\
-%\includegraphics[width=0.5\linewidth]{SexRatioLowR}\\
-%\includegraphics[width=0.5\linewidth]{MeanDipFitLowR}
-%\caption{
-%Haploid selection allows a neo-$W$ to invade an ancestral $XY$ system and fix (\textbf{A}) despite temporarily biasing the sex ratio further (\textbf{B}) and decreasing mean diploid viability fitness (\textbf{C}).
-%Complete turnover between genetic sex-determination systems occurs despite the neo-$W$ being less tightly linked to the selected locus than the ancestral sex-determining locus is, $R>r$.
-%Parameters: $k=1$, $s^\female = 0.05$, $s^\male = 0.15$, $h^\female = h^\male = 0.7$, $t^\female = 0$, $t^\male = -0.1$, $\alpha^\male = \alpha^\female = 1/2$, $r=0.01$, $R=0.05$.
-%}
-%\label{fig:WinvasionLowR}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%W invades XY but does not fix
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}
-%\centering
-%\includegraphics[width=0.5\linewidth]{FreqWHighR}\\
-%\includegraphics[width=0.5\linewidth]{SexRatioHighR}\\
-%\includegraphics[width=0.5\linewidth]{MeanDipFitHighR}
-%\caption{
-%Haploid selection allows a completely unlinked neo-$W$ to invade an ancestral $XY$ system (\textbf{A}) despite further biasing the sex ratio (\textbf{B}) and decreasing mean diploid viability fitness (\textbf{C}).
-%The neo-$W$ does not fix (although variation at the \textbf{A} locus is maintained, $V_A>0$), resulting in a polymorphic sex-determination system.
-%Parameters as in Figure \ref{fig:WinvasionLowR} but with $R=0.5$.
-%}
-%\label{fig:WinvasionHighR}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%W invades for all rates of recombination with selected locus
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}
-%\centering
-%\includegraphics[width=0.5\linewidth]{InvasionVsRecombination}
-%\caption{
-%A neo-$W$ invades an ancestral $XY$ system with haploid selection regardless of how tightly it is linked to the selected locus. 
-%Parameters as in Figure \ref{fig:WinvasionLowR}.
-%}
-%\label{fig:InvasionVsRecombination}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%W invasion versus position of selected locus
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}
-%\centering
-%\includegraphics[width=0.5\linewidth]{InvasionVsCentiMorgans}
-%\includegraphics[width=0.5\linewidth]{InvasionVsCentiMorgansAllOrders}
-%\caption{
-%Haploid selection allows a neo-$W$ to invade an ancestral $XY$ system regardless of how tightly it and the ancestral sex-determining locus are linked to the selected locus. 
-%The ancestral sex-determining locus is located at -0.05 and the novel sex-determining locus is located at 0.05 (corresponding to the peaks of invasion fitness), such that the probability of a cross-over between them is $\approx0.1$.
-%The x-axis gives the position of the locus under haploid selection.
-%We used Haldane's map function \citep[Equation 3 in ][]{Haldane1919} to convert from map distance (centiMorgans) to the probability of a cross-over event. 
-%Parameters as in Figure \ref{fig:WinvasionLowR}.
-%}
-%\label{fig:InvasionVsCentiMorgans}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Y invades ZW and fixes (counter example to Kozi explanation)
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}
-%\centering
-%\includegraphics[width=0.5\linewidth]{FreqWCounterKozi}\\
-%\includegraphics[width=0.5\linewidth]{SexRatioCounterKozi}\\
-%\includegraphics[width=0.5\linewidth]{MeanDipFitCounterKozi}
-%\caption{
-%Meiotic drive allows a neo-$Y$ to invade an ancestral $ZW$ system and fix (\textbf{A}) despite temporarily biasing the sex ratio (\textbf{B}).
-%and decreasing mean diploid viability fitness (\textbf{C}).
-%Parameters: $k=0$, $s^\female = s^\male = t^\female = t^\male = 0$, $\alpha^\male = 0.4$, $\alpha^\female = 1/2$, $r=0$, $R=0$.
-%}
-%\label{fig:CounterKozi}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\setcounter{equation}{0}
-\renewcommand{\theequation}{S.\arabic{equation}}
-\setcounter{figure}{0}
-\renewcommand{\thefigure}{S.\arabic{figure}}
-\setcounter{table}{0}
-\renewcommand{\thetable}{S.\arabic{table}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-
-\section*{Appendix}
-
-\subsection*{Recursion equations}
-\label{app:recurs}
-
-%\textcolor{red}{Should we adjust the subscripts throughout this subsection?
-Right now we end up re-defining $i$ and $j$ (when switching from haploid to diploid; this might have been my doing!) and then introduce three new subscripts $b$, $c$, and $l$, all of which can be derived from $i$ and $j$.
-Might be more straightforward to just use $p^\Hermaphrodite_{x_1,x_2,a_1,a_2,m_1,m_2}$ where 1 is maternal and 2 is paternal?
-We then no longer have to switch indices from haploid to diploid and the connection to other variables is clear: $b=m_1m_2$, $c=x_1x_2$, and $l=a_1a_2$.
-I guess the downside will be re-writing the recursion equations...
-which is why I haven't gone ahead and tried this.}
-
-In each generation we census the genotype frequencies in male and female gametes/gametophytes (hereafter, gametes) between meiosis (and any meiotic drive) and gametic competition. 
-At this stage we denote the frequencies of X- and Y-bearing gametes from males and females $x_{i}^{\Hermaphrodite}$ and $y_{i}^{\Hermaphrodite}$.
-The superscript $\Hermaphrodite \in \{\male,\female\}$ specifies the sex of the diploid that the gamete came from. 
-The subscript $i\in\{1,2,3,4\}$ specifies the genotype at the selected locus $\mathbf{A}$ and at the novel sex-determining locus $\mathbf{M}$, where $1=AM$, $2=aM$, $3=Am$, and $4=am$. 
-The gamete frequencies from each sex sum to one, $\sum_{i}x_{i}^{\Hermaphrodite}+y_{i}^{\Hermaphrodite}=1$.
-
-Competition then occurs among gametes of the same sex (e.g., among eggs and among sperm separately) according to the genotype at the \textbf{A} locus ($w_{1}^\Hermaphrodite=w_{3}^\Hermaphrodite=w_{A}^\Hermaphrodite$, $w_{2}^\Hermaphrodite=w_{4}^\Hermaphrodite=w_{a}^\Hermaphrodite$, see Table \ref{tab:fitnesstable}).
-The genotype frequencies after gametic competition are $x_{i}^{\Hermaphrodite,s}= w_{i}x_{i}^{\Hermaphrodite}/\bar{w}_{H}^{\Hermaphrodite}$ and $y_{i}^{\Hermaphrodite,s}= w_{i}y_{i}^{\Hermaphrodite}/\bar{w}_{H}^{\Hermaphrodite}$, where $\bar{w}_{H}^{\Hermaphrodite}=\sum_{i} w_{i}x_{i}^{\Hermaphrodite}+w_{i}y_{i}^{\Hermaphrodite}$ is the mean fitness of male ($\Hermaphrodite=\male$) or female ($\Hermaphrodite=\female$) gametes.
-
-Random mating then occurs between gametes to produce diploid zygotes.
-%To shorten notation we now use index $i$ (and $j$) to denote the alleles at both the $\mathbf{A}$ and $\mathbf{M}$ loci and label $MA=1$, $Ma=2$, $mA=3$, and $ma=4$, such that $i,j\in\{1,2,3,4\}$.
-The frequencies of XX zygotes are then denoted as $xx_{ij}$, XY zygotes as $xy_{ij}$, and YY zygotes as $yy_{ij}$, where \textbf{A} and \textbf{M} locus genotypes are given by $i,j\in\{1,2,3,4\}$, as above.
-In $XY$ zygotes, the haplotype inherited from an X-bearing gamete is given by $i$ and the haplotype from a Y-bearing gamete is given by $j$. 
-In XX and YY zygotes, individuals with diploid genotype $ij$ are equivalent to those with diploid genotype $ji$; for simplicity, we use $xx_{ij}$ and $yy_{ij}$ with $i\neq j$ to denote the average of these frequencies, $xx_{ij}=(x_{i}^{\female,s}x_{j}^{\male,s}+x_{j}^{\female,s}x_{i}^{\male,s})/2$ and $yy_{ij}=(y_{i}^{\female,s}y_{j}^{\male,s}+y_{j}^{\female,s}y_{i}^{\male,s})/2$.
-
-Denoting the \textbf{M} locus genotype by $b \in \{MM, Mm, mm\}$ and the \textbf{X} locus genotype by $c \in \{XX, XY, YY\}$, zygotes develop as females with probability $k_{bc}$. 
-Therefore, the frequencies of XX females are given by $xx_{ij}^{\female}=k_{bc}xx_{ij}$, XY females are given by $xy_{ij}^{\female}=k_{bc}xy_{ij}$, and YY females are given by $yy_{ij}^{\female}=k_{bc}yy_{ij}$.
-Similarly, XX male frequencies are $xx_{ij}^{\male}=(1-k_{bc})xx_{ij}$, XY male frequencies are $xy_{ij}^{\male}=(1-k_{bc})xy_{ij}$, and YY males frequencies are $yy_{ij}^{\male}=(1-k_{bc})yy_{ij}$.
-This notation allows both the ancestral and novel sex-determining regions to determine zygotic sex according to an XY system, a ZW system, or an environmental sex-determining system. 
-In addition, we can consider any epistatic dominance relationship between the two sex-determining loci. 
-Here, we assume that the ancestral sex-determining system (\textbf{X} locus) is XY ($k_{MMXX}=1$ and $k_{MMXY}=k_{MMYY}=0$) or ZW ($k_{MMZZ}=0$ and $k_{MMZW}=k_{MMWW}=1$) and epistatically recessive to a dominant novel sex-determining locus, \textbf{M} ($k_{Mmc}=k_{mmc}=k$).
-
-Selection among diploids then occurs according to the diploid genotype at the \textbf{A} locus, $l \in \{AA, Aa, aa\}$, for an individual of type $ij$ (see Table \ref{tab:fitnesstable}). 
-The diploid frequencies after selection in sex $\Hermaphrodite$ are given by $xx_{ij}^{\Hermaphrodite,s}=w_{l}^{\Hermaphrodite} xx_{ij}/\bar{w}^{\Hermaphrodite}$, $xy_{ij}^{\Hermaphrodite,s}=w_{l}^{\Hermaphrodite} xy_{ij}/\bar{w}^{\Hermaphrodite}$, and $yy_{ij}^{\Hermaphrodite,s}=w_{l}^{\Hermaphrodite} yy_{ij}/\bar{w}^{\Hermaphrodite}$, where $\bar{w}^{\Hermaphrodite}= \sum_{i=1}^{4}\sum_{j=1}^{4}w_{l}^{\Hermaphrodite}xx_{ij}+w_{l}^{\Hermaphrodite}xy_{ij}+w_{l}^{\Hermaphrodite}yy_{ij}$ is the mean fitness of individuals of sex $\Hermaphrodite$.
-
-Finally, these diploids undergo meiosis to produce the next generation of gametes. 
-Recombination and sex-specific meiotic drive occur during meiosis.
-%We can also assume that recombination is sex specific and/or affected by the M locus - but generally we don't so I just describe $R=R_{f}=R, r_{MM,d}=r_{Mm,d}=r_{mm,d}=r, \chi_{m}=\chi_{f}=\chi$.
-Here, we allow any relative locations for the SDR, \textbf{A}, and \textbf{M} loci by using three parameters to describe the recombination rates between them. 
-$R$ is the recombination rate between the \textbf{A} locus and the \textbf{M} locus, $\rho$ is the recombination rate between the \textbf{M} locus and the \textbf{X} locus, and $r$ is the recombination rate between the \textbf{A} locus and the \textbf{X} locus.
-Table \ref{tab:chisubstitutions} shows replacements that can be made for each possible ordering of the loci assuming that there is no cross-over interference.
-During meiosis in sex $\Hermaphrodite$, meiotic drive occurs such that, in $Aa$ heterozygotes, a fraction $\alpha^{\Hermaphrodite}$ of gametes produced carry the $A$ allele and $(1-\alpha^\Hermaphrodite)$ carry the $a$ allele.
-
-\begin{table}[ht]
-\centering
-\smallskip
-\caption{
-Substitutions for different loci orders assuming no interference.
-%and $r,R\in(0,1/2)$.\textcolor{blue}{write all in form of first line?
-so that 1/2 cases are okay (can't determine chi if R is 1/2 in second line, or if r is 1/2 in third line}
-}
-\begin{tabular}{l l}
-\hline\hline
-  Order of loci &   \\ [0.5ex] \hline
-  SDR-A-M & $\rho=r(1-R)+R(1-r)$  \\
-  SDR-M-A & $r=\rho(1-R)+R(1-\rho)$ \\ %$\rho=(r-R)/(1-2R)$ \\
-  A-SDR-M & $R=r(1-\rho)+\rho(1-r)$ \\ %$\rho=(R-r)/(1-2r)$ \\
-  \hline \hline
-  \label{tab:chisubstitutions}
- \end{tabular}
-\end{table}
-
-Among gametes from sex $\Hermaphrodite$, the frequencies of haplotypes (before gametic competition) in the next generation are given by
-
-\begingroup
-\allowdisplaybreaks
-\begin{subequations}
-\begin{align}
-%
-\begin{split}
-x_{1}^{{\Hermaphrodite}'}=&xx_{11}^{\Hermaphrodite,s}+xx_{13}^{\Hermaphrodite,s}/2+(xx_{12}^{\Hermaphrodite,s}+xx_{14}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(xx_{14}^{\Hermaphrodite,s}-xx_{23}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&+(xy_{11}^{\Hermaphrodite,s}+xy_{13}^{\Hermaphrodite,s})/2+(xy_{12}^{\Hermaphrodite,s}+xy_{14}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&- r(xy_{12}^{\Hermaphrodite,s}-xy_{21}^{\Hermaphrodite,s})\alpha^\Hermaphrodite - \rho(xy_{13}^{\Hermaphrodite,s}-xy_{31}^{\Hermaphrodite,s})/2\\
-&+\big{[}-(R+r+\rho)xy_{14}^{\Hermaphrodite,s} +(R+\rho-r)xy_{41}^{\Hermaphrodite,s}\\
-&+(R+r-\rho) xy_{23}^{\Hermaphrodite,s}+(R+\rho-r)xy_{32}^{\Hermaphrodite,s}\big{]}\alpha^\Hermaphrodite/2
-\end{split}
-\\
-%
-\begin{split}
-x_{2}^{{\Hermaphrodite}'}=&xx_{22}^{\Hermaphrodite,s}+xx_{24}^{\Hermaphrodite,s}/2+(xx_{12}^{\Hermaphrodite,s}+xx_{23}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(xx_{23}^{\Hermaphrodite,s}-xx_{14}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&(xy_{22}^{\Hermaphrodite,s}+xy_{24}^{\Hermaphrodite,s})/2+(xy_{21}^{\Hermaphrodite,s}+xy_{23}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite)\\
-&- r(xy_{21}^{\Hermaphrodite,s}-xy_{12}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite) - \rho(xy_{24}^{\Hermaphrodite,s}-xy_{42}^{\Hermaphrodite,s})/2\\
-&+\big{[}-(R+r+\rho)xy_{23}^{\Hermaphrodite,s}+(R+\rho-r)xy_{32}^{\Hermaphrodite,s}\\
-&+(R+r-\rho) xy_{14}^{\Hermaphrodite,s}+(R+\rho-r)xy_{41}^{\Hermaphrodite,s}\big{]}(1-\alpha^\Hermaphrodite)/2
-\end{split}
-\\
-%
-\begin{split}
-x_{3}^{{\Hermaphrodite}'}=&xx_{33}^{\Hermaphrodite,s}+xx_{13}^{\Hermaphrodite,s}/2+(xx_{23}^{\Hermaphrodite,s}+xx_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(xx_{23}^{\Hermaphrodite,s}-xx_{14}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&(xy_{33}^{\Hermaphrodite,s}+xy_{31}^{\Hermaphrodite,s})/2+(xy_{32}^{\Hermaphrodite,s}+xy_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&- r(xy_{34}^{\Hermaphrodite,s}-xy_{43}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite - \rho(xy_{31}^{\Hermaphrodite,s}-xy_{13}^{\Hermaphrodite,s})/2\\
-&+\big{[}-(R+r+\rho)xy_{32}^{\Hermaphrodite,s} +(R+\rho-r)xy_{23}^{\Hermaphrodite,s}\\
-&+(R+r-\rho) xy_{41}^{\Hermaphrodite,s}+(R+\rho-r)xy_{14}^{\Hermaphrodite,s}\big{]} \alpha^\Hermaphrodite/2
-\end{split}
-\\
-%
-\begin{split}
-x_{4}^{{\Hermaphrodite}'}=&xx_{44}^{\Hermaphrodite,s}+xx_{34}^{\Hermaphrodite,s}/2+(xx_{14}^{\Hermaphrodite,s}+xx_{24}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(xx_{14}^{\Hermaphrodite,s}-xx_{23}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&(xy_{44}^{\Hermaphrodite,s}+xy_{42}^{\Hermaphrodite,s})/2+(xy_{41}^{\Hermaphrodite,s}+xy_{43}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite)\\
-&- r(xy_{43}^{\Hermaphrodite,s}-xy_{34}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite) - \rho(xy_{42}^{\Hermaphrodite,s}-xy_{24}^{\Hermaphrodite,s})/2\\
-&+\big{[}-(R+r+\rho)xy_{41}^{\Hermaphrodite,s}+(R+\rho-r)xy_{14}^{\Hermaphrodite,s}\\
-&+(R+r-\rho) xy_{32}^{\Hermaphrodite,s}+(R+\rho-r)xy_{23}^{\Hermaphrodite,s}\big{]}(1-\alpha^\Hermaphrodite)/2
-\end{split}
-\\
-\begin{split}
-y_{1}^{{\Hermaphrodite}'}=&yy_{11}^{\Hermaphrodite,s}+yy_{13}^{\Hermaphrodite,s}/2+(yy_{12}^{\Hermaphrodite,s}+yy_{14}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(yy_{14}^{\Hermaphrodite,s}-yy_{23}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&(xy_{11}^{\Hermaphrodite,s}+xy_{31}^{\Hermaphrodite,s})/2+(xy_{21}^{\Hermaphrodite,s}+xy_{41}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&- r(xy_{21}^{\Hermaphrodite,s}-xy_{12}^{\Hermaphrodite,s})\alpha^\Hermaphrodite - \rho(xy_{31}^{\Hermaphrodite,s}-xy_{13}^{\Hermaphrodite,s})/2\\
-&+\big{[} - (R+r+\rho)xy_{41}^{\Hermaphrodite,s} + (R+\rho-r)xy_{14}^{\Hermaphrodite,s}\\
-& + (R+r-\rho)xy_{32}^{\Hermaphrodite,s} + (R+\rho-r) xy_{23}^{\Hermaphrodite,s}\big{]}\alpha^\Hermaphrodite/2
-\end{split}
-\\
-%
-\begin{split}
-y_{2}^{{\Hermaphrodite}'}=&yy_{22}^{\Hermaphrodite,s}+yy_{24}^{\Hermaphrodite,s}/2+(yy_{12}^{\Hermaphrodite,s}+yy_{23}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(yy_{23}^{\Hermaphrodite,s}-yy_{14}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&(xy_{22}^{\Hermaphrodite,s}+xy_{42}^{\Hermaphrodite,s})/2+(xy_{12}^{\Hermaphrodite,s}+xy_{32}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite)\\
-&- r(xy_{12}^{\Hermaphrodite,s}-xy_{21}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite) - \rho(xy_{42}^{\Hermaphrodite,s}-xy_{24}^{\Hermaphrodite,s})/2\\
-&+\big{[}-(R+r+\rho)xy_{32}^{\Hermaphrodite,s} +(R+\rho-r) xy_{23}^{\Hermaphrodite,s}\\
-&+(R+r-\rho)xy_{41}^{\Hermaphrodite,s}+(R+\rho-r)xy_{14}^{\Hermaphrodite,s}\big{]}(1-\alpha^\Hermaphrodite)/2
-\end{split}
-\\
-%
-\begin{split}
-y_{3}^{{\Hermaphrodite}'}=&yy_{33}^{\Hermaphrodite,s}+yy_{13}^{\Hermaphrodite,s}/2+(yy_{23}^{\Hermaphrodite,s}+yy_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(yy_{23}^{\Hermaphrodite,s}-yy_{14}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&(xy_{33}^{\Hermaphrodite,s}+xy_{13}^{\Hermaphrodite,s})/2+(xy_{23}^{\Hermaphrodite,s}+xy_{43}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&- r(xy_{43}^{\Hermaphrodite,s}-xy_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite - \rho(xy_{13}^{\Hermaphrodite,s}-xy_{31}^{\Hermaphrodite,s})/2\\
-&+\big{[}-(R+r+\rho)xy_{23}^{\Hermaphrodite,s} +(R+\rho-r)xy_{32}^{\Hermaphrodite,s}\\
-&+(R+r-\rho) xy_{14}^{\Hermaphrodite,s} + (R+\rho-r) xy_{41}^{\Hermaphrodite,s}\big{]}\alpha^\Hermaphrodite/2
-\end{split}
-\\
-%
-\begin{split}
-y_{4}^{{\Hermaphrodite}'}=&yy_{44}^{\Hermaphrodite,s}+yy_{34}^{\Hermaphrodite,s}/2+(yy_{14}^{\Hermaphrodite,s}+yy_{24}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(yy_{14}^{\Hermaphrodite,s}-yy_{23}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&(xy_{44}^{\Hermaphrodite,s}+xy_{24}^{\Hermaphrodite,s})/2+(xy_{14}^{\Hermaphrodite,s}+xy_{34}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite)\\
-&- r(xy_{34}^{\Hermaphrodite,s}-xy_{43}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite) - \rho(xy_{24}^{\Hermaphrodite,s}-xy_{42}^{\Hermaphrodite,s})/2\\
-&+\big{[}-(R+r+\rho) xy_{14}^{\Hermaphrodite,s} + (R+\rho-r)xy_{41}^{\Hermaphrodite,s}\\
-&+(R+r-\rho) xy_{23}^{\Hermaphrodite,s} + (R+\rho-r) xy_{32}^{\Hermaphrodite,s}\big{]}(1-\alpha^\Hermaphrodite)/2
-\end{split}
-\end{align}
-\label{eq:recursions}
-\end{subequations}
-
-\endgroup
-
-\noindent
-The full system is therefore described by 16 recurrence equations (three diallelic loci in two sexes, $2^3 \times 2 = 16$). 
-However, not all diploid types are produced under certain sex-determination systems. 
-For example, with the $M$ allele fixed and an ancestral $XY$ sex-determining system, there are $XX$ males, $XY$ females, or $YY$ females ($x_{3}^\Hermaphrodite=x_{4}^\Hermaphrodite=y_{4}^\Hermaphrodite=y_{3}^\Hermaphrodite=y_{i}^\female=0$).
-%($xx_{11}^{\male}=xx_{12}^{\male}=xx_{22}^\male=xy_{11}^{\female}=xy_{12}^{\female}=xy_{21}^{\female}=xy_{22}^\female=yy_{11}^{\female}=yy_{12}^{\female}=yy_{22}^\female=0$). 
-In this case, the system only involves six recursion equations, %because there is only one \textbf{M} locus allele and no Y-bearing female gametes. 
-which we assume below to calculate the equilibria.
-
-%I think this should be moved below because we have some 'results' where we don't assume weak selection but we only have the equilibrium calculated analytically for weak selection.
-
-\subsection*{Resident equilibria and stability}
-
-In the resident population (allele $M$ fixed), we follow the frequency of $A$ in X-bearing female gametes, $p^\female_X$, and X-bearing male gametes, $p^\male_X$, and Y-bearing male gametes, $p^\male_Y$.
-We also track the total frequency of Y among male gametes, $q$, which may deviate from $1/2$ due to meiotic drive in males. 
-These four variables determine the frequencies of the six resident gamete types: $x_{1}^{\female}=\hat{p}_X^\female$, $x_{2}^{\female}=1-\hat{p}_X^\female$, $x_{1}^{\male}=(1-q)\hat{p}_X^\male$, $x_{2}^{\male}=(1-q)(1-\hat{p}_X^\male)$, $y_{1}^{\male}=q \hat{p}_Y^\male$, and $y_{2}^{\male}=q(1-\hat{p}_Y^\male)$.
-Mean fitnesses in the resident population are given in table \ref{tab:meanfitnesses}.
-
-Various forms of selection can maintain a polymorphism at the \textbf{A} locus, including sexually antagonistic selection, overdominance, conflicts between diploid selection and selection upon haploid genotypes \citep[ploidally antagonistic selection,][]{Immler:2012tl}, or a combination of these selective regimes (see below).
-
-\begin{table}[ht]
-\centering
-\smallskip
-\caption{Mean fitnesses and zygotic sex ratio in the resident population ($M$ fixed, XY sex determination). }
-\begin{tabular}{l l }
-\hline\hline
-  Sex \& Life Cycle Stage & Mean Fitness \\ [0.5ex] \hline  \noalign{\vskip 0.5ex}
-  female gametes ($\bar{w}_H^\female$) & 
-  $p_X^\female w_A^\female + (1-p_X^\female) w_a^\female$ \\ [0.5ex] \hline  \noalign{\vskip 0.5ex}
-  male gametes ($\bar{w}_H^\male$) & 
-  $\bar{p}^{\male} w_A^\male + (1-\bar{p}^{\male}) w_a^\male$ \\ [0.5ex] \hline  \noalign{\vskip 0.5ex}
-  females ($\bar{w}^\female$) & 
-  $\begin{array}{l}  (1-\zeta)^{-1} \big[ p_X^\female w_A^\female p_X^\male w_A^\male w_{AA}^\female + \\
-  (1 - p_X^\female) w_a^\female p_X^\male w_A^\male w_{Aa}^\female + \\
-  p_X^\female w_A^\female (1 - p_X^\male) w_a^\male w_{Aa}^\female + \\
-  (1-p_X^\female) w_a^\female (1 - p_X^\male) w_a^\male w_{aa}^\female \big] / \left( \bar{w}_H^\female \bar{w}_H^\male \right)
-  \end{array} 
-  $ \\ [0.5ex] \noalign{\vskip 0.5ex} \hline  \noalign{\vskip 0.5ex}
-  males ($\bar{w}^\male$) & 
-  $\begin{array}{l} \zeta^{-1} \big[ p_X^\female w_A^\female  p_Y^\male w_A^\male w_{AA}^\male + \\
-  (1 - p_X^\female) w_a^\female  p_Y^\male w_A^\male w_{Aa}^\male + \\
-  p_X^\female w_A^\female  (1 - p_Y^\male) w_a^\male w_{Aa}^\male + \\
-  (1-p_X^\female) w_a^\female  (1 - p_Y^\male) w_a^\male w_{aa}^\male \big] / \left( \bar{w}_H^\female \bar{w}_H^\male \right) 
-  \end{array}
-  $ \\ [0.5ex] \noalign{\vskip 0.5ex} \hline  \noalign{\vskip 0.5ex}
-  fraction zygotes male ($\zeta$) & $q \left[ p_Y^\male w_A^\male+(1-p_Y^\male)w_a^\male\right] / \bar{w}_H^\male $
-   \\ [0.5ex]  \noalign{\vskip 0.5ex}
-  \hline \hline
-  \label{tab:meanfitnesses}
- \end{tabular}
-\end{table}
-
-In particular special cases, e.g., no sex-differences in selection or meiotic drive ($s^\male=s^\female$, $h^\male=h^\female$, and $\alpha^\male=\alpha^\female=1/2$), the equilibrium allele frequency and stability can be calculated analytically without assuming anything about the relative strengths of selection and recombination.
-However, here, we focus on two regimes (tight linkage and weak selection) in order to make fewer assumptions about fitnesses.
-
-\subsubsection*{Recombination weak relative to selection (tight linkage between \textbf{A} and \textbf{X})}
-
-We first calculate the equilibrium frequency of the Y and $A$ alleles in the ancestral population when the recombination rate between the \textbf{X} and \textbf{A} loci is small ($r$ of order $\epsilon$).
-Selection at the \textbf{A} locus will not affect evolution at the novel sex-determining locus, \textbf{M}, if one allele is fixed on all backgrounds. 
-We therefore focus on the five equilibria that maintain both $A$ and $a$ alleles, four of which are given to leading order by:
-
-\begin{subequations}\label{eq:tightequil}
-\begin{align}
-(A)\ \ \ &\hat{p}_{Y}^{\male}=0,
-\ \hat{q}=\frac{1}{2}\left(1 - \alpha_\Delta^\male \frac{ w_{Aa}^{\male} \phi}{w_{Aa}^{\male} \phi+ w_{aa}^{\male} \psi}\right),\\
-&\hat{p}_{X}^{\female}=\frac{w_{a}^{\female} \phi}{w_{a}^{\female} \phi+ w_{A}^{\female} \psi},
-\ \hat{p}_{X}^{\male}=\frac{(1+\alpha_\Delta^\male)w_{Aa}^{\male} \phi}{(1+\alpha_\Delta^\male)w_{Aa}^{\male} \phi +w_{aa}^{\male} \psi} \nonumber \\
-(A')\ \ \ &\hat{p}_{Y}^{\male}=1,
-\ \hat{q}=\frac{1}{2}\left(1 + \alpha_\Delta^\male \frac{w_{Aa}^{\male} \phi'}{w_{Aa}^{\male} \phi' + w_{AA}^{\male} \psi'}\right),\\
-&\hat{p}_{X}^{\female}=1-\frac{w_{A}^{\female} \phi'}{w_{A}^{\female} \phi'+ w_{a}^{\female} \psi'},
-\ \hat{p}_{X}^{\male}=1-\frac{(1-\alpha_\Delta^\male)w_{Aa}^{\male} \phi'}{(1-\alpha_\Delta^\male)w_{Aa}^{\male} \phi'+w_{AA}^{\male} \psi'} \nonumber \\
-(B)\ \ \ &\hat{p}_{Y}^{\male}=0,\ \hat{p}_{X}^{\female}=1,\ \hat{p}_{X}^{\male}=1, \ \hat{q}=(1 -\alpha^\male_\Delta)/2\\
-(B')\ \ \ &\hat{p}_{Y}^{\male}=1,\ \hat{p}_{X}^{\female}=0,\ \hat{p}_{X}^{\male}=0, \ \hat{q}=(1+\alpha^\male_\Delta)/2
-\end{align}
-\end{subequations}
-\begin{equation*}
-\begin{split}
-\phi=&(1+\alpha^\female_\Delta) w_{A}^{\female} w_{Aa}^{\female} \left[ w_{a}^{\male} w_{aa}^{\male} + (1+\alpha_\Delta^\male) w_{A}^{\male} w_{Aa}^{\male} \right]/2 - w_{a}^{\male} w_{a}^{\female} w_{aa}^{\male} w_{aa}^{\female} \\
-\psi=&(1-\alpha^\female_\Delta) w_{a}^{\female} w_{Aa}^{\female} \left[ w_{a}^{\male} w_{aa}^{\male} + (1+\alpha_\Delta^\male) w_{A}^{\male} w_{Aa}^{\male}\right]/2 - (1+\alpha_\Delta^\male) w_{A}^{\male} w_{A}^{\female} w_{Aa}^{\male} w_{AA}^{\female}\\
-\phi'=&(1-\alpha^\female_\Delta) w_{a}^{\female} w_{Aa}^{\female} \left[ w_{A}^{\male} w_{AA}^{\male} + (1-\alpha_\Delta^\male) w_{a}^{\male} w_{Aa}^{\male} \right]/2 - w_{A}^{\male} w_{A}^{\female} w_{AA}^{\male} w_{AA}^{\female}\\
-\psi'=&(1+\alpha^\female_\Delta) w_{A}^{\female} w_{Aa}^{\female} \left[ w_{A}^{\male} w_{AA}^{\male} + (1-\alpha_\Delta^\male) w_{a}^{\male} w_{Aa}^{\male} \right]/2 - (1-\alpha_\Delta^\male) w_{a}^{\male} w_{a}^{\female} w_{Aa}^{\male} w_{aa}^{\female}
-\end{split}
-\end{equation*}
-
-\noindent
-A fifth equilibrium $(C)$ also exists where $A$ is present at an intermediate frequency on the Y chromosome ($0<\hat{p}_{Y}^{\male}<1$). 
-However, equilibrium $(C)$ is never locally stable when $r \approx 0$ and is therefore not considered further.
-Thus, the Y can either be fixed for the $a$ allele (equilibria $A$ and $B$) or the $A$ allele (equilibria $A'$ and $B'$).
-The X chromosome can then either be polymorphic (equilibria $A$ and $A'$) or fixed for the alternative allele (equilibria $B$ and $B'$).
-Since equilibria $(A)$ and $(B)$ are equivalent to equilibria $(A')$ and $(B')$ with the labelling of $A$ and $a$ alleles interchanged, we discuss only equilibria $(A)$ and $(B)$, in which the Y is fixed for the $a$ allele.
-If there is no haploid selection ($\alpha^{\Hermaphrodite}_\Delta=0$, $w_{A}^{\Hermaphrodite}=w_{a}^{\Hermaphrodite}=1$), these equilibria are equivalent to those found by \cite{Lloyd1977} and \cite{Otto2014}.
-
-We next calculate when $(A)$ and $(B)$ are locally stable for $r=0$. 
-According to the `small parameter theory' \citep{Karlin:1972ab,Karlin:1972dq}, these stability properties are unaffected by small amounts of recombination between the SDR and \textbf{A} locus, although equilibrium frequencies may be slightly altered.
-For the $a$ allele to be stably fixed on the Y we need $\bar{w}_{Ya}^{\male} > \bar{w}_{YA}^{\male}$ where $\bar{w}_{Ya}^{\male} = w_{a}^{\male} \big[\hat{p}_X^\female(1-\alpha^\male_\Delta) w_{A}^{\female} w_{Aa}^{\male} + (1-\hat{p}_X^\female)w_{a}^{\female} w_{aa}^{\male} \big]$ and $\bar{w}_{YA}^{\male} = w_{A}^{\male} \big[ \hat{p}_X^\female w_{A}^{\female} w_{AA}^{\male} + (1-\hat{p}_X^\female)(1+\alpha^\male_\Delta) w_{a}^{\female} w_{Aa}^{\male} \big]$.
-That is, Y-$a$ haplotypes must have higher fitness than Y-$A$ haplotypes.  
-Substituting in $\hat{p}_X^\female$ from equation \eqref{eq:tightequil}, fixation of the $a$ allele on the Y requires that $\gamma_{i}>0$ where $\gamma_{(A)}=w_{a}^{\male} \big[ (1-\alpha^\male_\Delta) w_{Aa}^{\male} \phi + w_{aa}^{\male} \psi \big]-w_{A}^{\male} \big[ w_{AA}^{\male} \phi + (1 + \alpha^{\male}_\Delta)w_{Aa}^{\male} \psi \big]$ for equilibrium $(A)$ and $\gamma_{(B)}=(1-\alpha^{\male}_\Delta)w_{a}^{\male}w_{Aa}^{\male}-w_{A}^{\male}w_{AA}^{\male}$ for equilibrium $(B)$.
-Stability of a polymorphism on the X chromosome (equilibrium $A$) further requires that $\phi >0$ and $\psi >0$. 
-Fixation of the $a$ allele on the X (equilibrium $B$) can be stable only if equilibrium $(A)$ is not, as it requires $\psi<0$.
-%and $2w_{A}^{\female}w_{AA}^{\female}>(1-\alpha_\Delta^{\female})w_{a}^{\female}w_{Aa}^{\female}$ or just $4w_{A}^{\female}w_{AA}^{\female}<(1-\alpha_\Delta^{\female})w_{a}^{\female}w_{Aa}^{\female}$ (which also prevents $\psi>0$).
-
-%\textcolor{red}{check last condition and the stability condition below are correct}
-%\textcolor{blue}{The last condition looks good to me, although in your Turnover-norec-MFS.nb you look at YA fixed, so you have to flip everything (so I made Turnover-norec-MFS-MMO.nb to do this).
-%The one issue I can find here is that you can also prevent $\lambda>1$ when the slope and intercept of the quadratic at $\lambda=1$ are negative (you only looked at both being positive).
-In this case we need $4w_{A}^{\female}w_{AA}^{\female}<(1-\alpha_\Delta^{\female})w_{a}^{\female}w_{Aa}^{\female}$, which also prevents $\psi>0$.
-%I've added this in.
-%It could also be the case that the slope and intercept are the same sign but the roots are imaginary - but this is never the case here.
-%Stability condition below looks good to me (from matt version of turnoverSOM-MIKE.nb).}
-
-\subsubsection*{Selection weak relative to recombination (weak selection)}
-
-Here, we assume that selection and meiotic drive are weak relative to recombination ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon$). 
-The maintenance of a polymorphism at the \textbf{A} locus then requires that
-
-\begin{equation}
-\begin{split}
-0&< - \left[(1-h^\female)s^\female +(1-h^\male) s^\male + t^\female +t^\male + \alpha_{\Delta}^\female+\alpha_{\Delta}^\male\right]\\
-%
-\text{and }\quad 0&<h^\female s^\female +h^\male s^\male + t^\female +t^\male + \alpha_{\Delta}^\female+\alpha_{\Delta}^\male.
-\end{split}
-\end{equation}
-
-\noindent
-which indicates that a polymorphism can be maintained by various selective regimes.
-
-Given that a polymorphism is maintained at the \textbf{A} locus by weak selection, the frequencies of $A$ in each type of gamete are the same ($\hat{p}^\female_X=\hat{p}^\male_X=\hat{p}^\male_Y=\bar{p}$) and given, to leading order, by
-
-\begin{equation}
-\bar{p}=\frac{h^\female s^\female + h^\male s^\male +t^\female+t^\male+\alpha_{\Delta}^\female+\alpha_{\Delta}^\male}
-{(2h^\female-1)s^\female+(2h^\male-1)s^\male}
-+O(\epsilon)
-.
-\label{eq:pAve}
-\end{equation}
-
-\noindent
-Differences in frequency between gamete types are of $O(\epsilon)$:
-
-\begin{equation}
-\begin{split}
-\hat{p}^\male_X-\hat{p}^\female_X&=V_{A}\big{(}D^\male - D^\female +\alpha_{\Delta}^\male-\alpha_{\Delta}^\female \big{)}
-+O(\epsilon^2)\\
-%
-\hat{p}^\male_Y-\hat{p}^\female_X&=V_{A}\left[D^\male - D^\female+\alpha_{\Delta}^\male-\alpha_{\Delta}^\female+(1-2r)(t^\male-t^\female)\right]/2r
-+O(\epsilon^2)\\
-%
-\hat{p}^\male_Y-\hat{p}^\male_X&=V_{A}\left(D^\male - D^\female+\alpha_{\Delta}^\male-\alpha_{\Delta}^\female+t^\male-t^\female\right)(1-2r)/2r
-+O(\epsilon^2)
-\end{split}
-\label{eq:freq_diffs}
-\end{equation}
-
-\noindent
-where $V_{A}=\bar{p}(1-\bar{p})$ is the variance in the frequency of $A$ and $D^\Hermaphrodite=\big{[} \bar{p}s^\Hermaphrodite+(1-\bar{p})h^\Hermaphrodite s^\Hermaphrodite\big{]} -\big{[} \bar{p}h^\Hermaphrodite s^\Hermaphrodite+(1-\bar{p}) \big{]}$ corresponds to the difference in fitness between $A$ and $a$ alleles in diploids of sex $\Hermaphrodite \in \{\female,\male\}$ ($\bar{p}$ is the leading-order probability of mating with an $A$-bearing gamete from the opposite sex).
-The frequency of Y among male gametes depends upon the difference in the frequency of the $A$ allele between X- and Y-bearing male gametes and the strength of meiotic drive in favour of the $A$ allele in males, $q=1/2+\alpha_{\Delta}^\male(\hat{p}^\male_Y-\hat{p}^\male_X)/2+O(\epsilon^3)$.
-Without gametic competition or drive ($\alpha_{\Delta}^\Hermaphrodite=t^\Hermaphrodite=0$) our results reduce to those of \citet{vanDoorn:2007eu}.
-
-% the differences in the frequencies of $A$ in each type of gamete are small, as is the bias in the sex-determining factor from the heterogametic sex, and we can solve for the mean frequency of $A$ across all types ($p_A$), the difference in the frequencies of $A$ between two of the three types, and the bias in the frequency of the sex-determining factor, to first order in selection.
-%Linear stability analysis can then be used to determine the stability of this equilibrium.
-%Without haploid selection or meiotic drive our results reduce to those of \cite{vanDoorn:2007eu}.
-%when $k=0$ (neo-$Y$ invading a $ZW$ system) or when $k=1$ (neo-$W$ invading an $XY$ system) (\textcolor{red}{CHECK}).
-%However, with haploid selection or meiotic drive a stable polymorphism at locus \textbf{A} no longer requires sexually antagonistic selection.
-%, as it can also be achieved by ploidally-antagonistic selection.
+\section*{S3 Appendix}
 
 \subsection*{Invasion conditions}
-
-%Here, we determine whether a rare neo-Y or neo-W allele spreads when rare, which occurs when $\lambda > 1$.
-%We begin with the general result and then give explicit solutions under tight linkage and weak selection.
-
-%If the average change in frequency of the two haplotypes that carry the $m$ allele ($Am$ and $am$) is positive, invasion will always occur (i.e., if $\left\{(\lambda_{mA}-1)+ (\lambda_{ma}-1) \right\}/2 > 0$ then $\lambda > 1$, see table \ref{tab:haplotype_growth} for $\lambda_{mi}$).
-%If neither haplotype increases in frequency ($\lambda_{mA}, \lambda_{ma} < 1$), the $m$ allele will not invade. 
-%Otherwise, the new sex-determining allele increases in frequency on one \textbf{A} background and declines on the other, and invasion requires
-%\begin{equation}\label{eq:neoYR}
-%R \left[ 
-%\frac{p^\female_X w^\female_A w^\male_a (1-\alpha^\male)}{ \bar{w}^\female_H \bar{w}^\male_H (\lambda_{mA}-1)} + 
-%p^\female_X \frac{w^\female_A}{\bar{w}^\female_H} \frac{w^\male_a(1-\alpha^\male)}{\bar{w}^\male_H} \frac{1}{\lambda_{mA}-1} + 
-%\frac{(1 - p^\female_X) w^\female_a w^\male_A \alpha^\male}{ \bar{w}^\female_H \bar{w}^\male_H (\lambda_{ma}-1)} 
-%\right] 
-%\frac{w^\male_{Aa}}{q\bar{w}^\male} < 1,
-%\end{equation}
-
-%\noindent
-%for the neo-$Y$, and
-
-%\noindent
-%\begin{equation}\label{eq:neoWR}
-%R \left[ 
-%\frac{\bar{p}^\male w^\male_A w^\female_a (1-\alpha^\female)}{ \bar{w}^\male_H \bar{w}^\female_H (\lambda_{mA}-1)} + 
-%\frac{(1 - \bar{p}^\male) w^\male_a w^\female_A \alpha^\female}{ \bar{w}^\male_H \bar{w}^\female_H (\lambda_{ma}-1)} 
-%\right] 
-%\frac{w^\female_{Aa}}{(1-q)\bar{w}^\female} < 1,
-%\end{equation}
-
-%\noindent
-%for the neo-$W$.
-
-%Equations \eqref{eq:neoYR} and \eqref{eq:neoWR} show that the new sex-determining allele, $m$, is expected to invade for any probability of recombination between loci \textbf{A} and \textbf{M}, $R$, when the net flow of recombinants is from the less fit (smaller $\lambda_{mi}$) to the more fit \textbf{A} background (making the terms inside the square brackets in Equations \ref{eq:neoYR} and \ref{eq:neoWR} negative).
-%\textcolor{red}{Q: is it definitely possible to have negative square brackets for a equilibria maintained by selection?}
-%Assuming $g_A^* > 0$ and $g_a^* < 0$ without loss of generality, this is $-(1 - p^\female_X) w_{m,A} g_a^* < p^\female_X w_{m,a} g_A^*$.
-%When the net flow of recombinants is from the more fit to the less fit haplotype, the new sex-determining allele can still invade when the rate of recombination between it and the selected locus is small enough.
-%\textcolor{red}{Q:Is it the case that sometimes the square brackets are positive and invasion occurs for $r_{AM}=1/2$?
-In which case it might be better to have slightly different phrasing here.}
-%Equations \eqref{eq:neoYR} and \eqref{eq:neoWR} show that the new sex-determining allele, $m$, is expected to invade for any probability of recombination between loci \textbf{A} and \textbf{M}, $R$, when the net flow of recombinants is from the less fit (smaller $\lambda_{mi}$) to the more fit \textbf{A} background (making the terms inside the square brackets in Equations \ref{eq:neoYR} and \ref{eq:neoWR} negative).
-%When the net flow of recombinants is from the more fit to the less fit haplotype, the new sex-determining allele can still invade when the rate of recombination between it and the selected locus is small enough.
-%To better understand when these scenarios are possible we next use knowledge of the equilibria and their stability under tight linkage and weak selection.
 
@@
 
-\subsubsection*{Tight linkage between \textbf{A} and \textbf{X} (recombination weak relative to selection)}
+\subsubsection*{Tight linkage between \textbf{A} and \textbf{X} ($r \approx 0$)}
 
@@
 First, haploid selection can allow a polymorphism to be maintained when it would not under diploid selection alone (e.g., with directional selection in diploids). 
-In cases of ploidally-antagonistic selection, where there is a balance between alleles favored in the haploid stage and the diploid stage, neo-W alleles - even unlinked alleles - can spread (Figure \ref{fig:regionPloidAntag}).
+In cases of ploidally-antagonistic selection, where there is a balance between alleles favored in the haploid stage and the diploid stage, neo-W alleles - even unlinked alleles - can spread (Figure \nameref{fig:regionPloidAntag}).
 Second, even when diploid selection could itself maintain a polymorphism, haploid selection can increase the conditions under which transitions among sex chromosomes are possible.
-Of particularly importance, when selection is sexually-antagonistic in diploids ($s^\female s^\male <0$ and $0<h^\Hermaphrodite<1$), an unlinked neo-W ($R=1/2$) cannot invade unless there is also haploid selection (see proof in supplementary \textit{Mathematica} file; Figures \ref{fig:SexAntagTighter} and \ref{fig:SexAntagTighterMaleDrive}).
-More generally, haploid selection alters the conditions under which neo-W chromosomes can spread (compare Figures \ref{fig:regionMaleDrive}-\ref{fig:regionFemaleGS} to Figure \ref{fig:regionplots}).
+Of particularly importance, when selection is sexually-antagonistic in diploids ($s^\female s^\male <0$ and $0<h^\Hermaphrodite<1$), an unlinked neo-W ($R=1/2$) cannot invade unless there is also haploid selection (see proof in supplementary \textit{Mathematica} file; Figures \ref{fig:SexAntagTighter} and \nameref{fig:SexAntagTighterMaleDrive}).
+More generally, haploid selection alters the conditions under which neo-W chromosomes can spread (compare Figures \nameref{fig:regionMaleDrive}-\nameref{fig:regionFemaleGS} to Figure \ref{fig:regionplots}).
 
@@
 Male-biased sex-ratios facilitate the spread of neo-W-$A$ and neo-W-$a$ haplotypes (increasing $\lambda_{mA}$ and $\lambda_{ma}$). 
-Panels A-C in Figures \ref{fig:regionMaleDrive} and \ref{fig:regionMaleGS} show that neo-W haplotypes tend to spread for a wider range of parameters when sex ratios are male biased, compared to Figure \ref{fig:regionplots} without haploid selection.
-By contrast, male haploid selection in favour of the $A$ allele generates female-biased sex ratios and reduces $\lambda_{mA}$ and $\lambda_{ma}$, as demonstrated by panels D-F in Figures \ref{fig:regionMaleDrive} and \ref{fig:regionMaleGS}.
+Panels A-C in Figures \nameref{fig:regionMaleDrive} and \ref{fig:regionMaleGS} show that neo-W haplotypes tend to spread for a wider range of parameters when sex ratios are male biased, compared to Figure \ref{fig:regionplots} without haploid selection.
+By contrast, male haploid selection in favour of the $A$ allele generates female-biased sex ratios and reduces $\lambda_{mA}$ and $\lambda_{ma}$, as demonstrated by panels D-F in Figures \nameref{fig:regionMaleDrive} and \ref{fig:regionMaleGS}.
 
 Female haploid selection generates direct selection on the neo-W-$A$ and neo-W-$a$ haplotypes as they spread in females. 
-Thus, female haploid selection in favour of the $a$ allele tends to increase $\lambda_{ma}$ and decrease $\lambda_{mA}$, as shown by panels A-C in Figures \ref{fig:regionFemaleDrive} and \ref{fig:regionFemaleGS}.
-Conversely, female haploid selection in favour of the $A$ allele increases $\lambda_{mA}$ and decreases $\lambda_{ma}$, see panels D-F in Figures \ref{fig:regionFemaleDrive} and \ref{fig:regionFemaleGS}.
+Thus, female haploid selection in favour of the $a$ allele tends to increase $\lambda_{ma}$ and decrease $\lambda_{mA}$, as shown by panels A-C in Figures \nameref{fig:regionFemaleDrive} and \nameref{fig:regionFemaleGS}.
+Conversely, female haploid selection in favour of the $A$ allele increases $\lambda_{mA}$ and decreases $\lambda_{ma}$, see panels D-F in Figures \nameref{fig:regionFemaleDrive} and \nameref{fig:regionFemaleGS}.
 
@@
 
-%\subsubsection*{Tight Linkage and Haploid Selection}
-
-%With tight linkage, haploid selection generally expands the conditions under which neo-W alleles can spread. 
-%For example, when selection is sexually-antagonistic in diploids ($s^\female s^\male <0$ and $0<h^\Hermaphrodite<1$) an unlinked neo-W ($R=1/2$) cannot invade unless there is also haploid selection (Figures \ref{fig:SexAntagTighter} and \ref{fig:SexAntagTighterMaleDrive}).
-%Secondly, with haploid selection, overdominance ($w_{aa}^\Hermaphrodite<w_{Aa}^\Hermaphrodite$ \& $w_{AA}^\Hermaphrodite<w_{Aa}^\Hermaphrodite$) is not required for neo-W-$a$ haplotypes to spread ($\lambda_{ma}>1$) (Figures \ref{fig:regionMaleDrive}-\ref{fig:regionFemaleGS}).
-%Haploid selection and overdominance allow unlinked neo-W alleles to invade even when there is tight linkage between the ancestral SDR and the selected locus (Figure \ref{fig:loose_invades_tight}).
-%Finally, haploid selection can maintain a polymorphism in the face of directional selection in male and female diploids (ploidally-antagonistic selection). 
-%When selection is ploidally-antagonistic, neo-W alleles often spread, for at least some values of $R$ (Figure \ref{fig:regionPloidAntag}).
-
-%As discussed above, male haploid selection alters the sex ratio and the alleles carried by male gametes that female gametes pair with. 
-%Male haploid selection in favour of the $a$ allele ($\alpha_{\Delta}^\male<0$, $w_{A}^\male<w_{a}^\male$) generates male-biased sex ratios at equilibria (A) and (B), where Y-$a$ is fixed ($\hat{p}_{Y}^\male=0$).
-%Male-biased sex ratios facilitate the spread of neo-W-$A$ and neo-W-$a$ haplotypes (increasing $\lambda_{WA}$ and $\lambda_{Wa}$). 
-%Panels A-C in Figures \ref{fig:regionMaleDrive} and \ref{fig:regionMaleGS} show that neo-W haplotypes tend to spread for a wider range of parameters when sex ratios are male biased, compared to Figure \ref{fig:regionplots} without haploid selection.
-%By contrast, male haploid selection in favour of the $A$ allele generates female-biased sex ratios and reduces $\lambda_{WA}$ and $\lambda_{Wa}$, as demonstrated by panels D-F in Figures \ref{fig:regionMaleDrive} and \ref{fig:regionMaleGS}.
-
-%Female haploid selection generates direct selection on the neo-W-$A$ and neo-W-$a$ haplotypes as they spread in females. 
-%Thus, female haploid selection in favour of the $a$ allele tends to increase $\lambda_{Wa}$ and decrease $\lambda_{WA}$, as shown by panels A-C in Figures \ref{fig:regionFemaleDrive} and \ref{fig:regionFemaleGS}.
-%Conversely, female haploid selection in favour of the $A$ allele increases $\lambda_{WA}$ and decreases $\lambda_{Wa}$, see panels D-F in Figures \ref{fig:regionFemaleDrive} and \ref{fig:regionFemaleGS}.
-
-%Without haploid selection this reduces to
-%\begin{subequations}
-%\begin{align}
-%\lambda_{mA}&= \frac{a}{b} \left[w_{AA}^\female w_{Aa}^\male \phi / 2 + w_{Aa}^\female \frac{c}{d}\right]  \\
-%\lambda_{ma}&= \frac{a}{b} \left[w_{Aa}^\female w_{Aa}^\male \phi / 2 +  w_{aa}^\female \frac{c}{d}\right] \\
-%\chi_{mA}&= \frac{a}{b} R \left[ w_{Aa}^\female \frac{c}{d} \right] \\ 
-%\chi_{ma}&= \frac{a}{b} R \left[ w_{Aa}^\female w_{Aa}^\male \phi / 2 \right] 
-%\end{align}
-%\end{subequations}
-
-%These simplify considerably when there is no haploid selection:
-%
-%\begin{subequations}
-%\begin{align}
-%\lambda_{mA}&= \frac{(\phi + \psi)[(w_{AA}^\female + w_{Aa}^\female ) w_{Aa}^\male \phi + 2 w_{Aa}^\female w_{AA}^\male \psi ]}{2 (w_{AA}^\female w_{Aa}^\male \phi^2 + \psi(w_{Aa}^\female(w_{AA}^\male + w_{Aa}^\male)\phi + w_{aa}^\female w_{AA}^\male \psi)}\\
-%\lambda_{ma}&=  \frac{(\phi + \psi)[(w_{aa}^\female + w_{Aa}^\female ) w_{Aa}^\male \phi + 2 w_{aa}^\female w_{AA}^\male \psi ]}{2 (w_{AA}^\female w_{Aa}^\male \phi^2 + \psi(w_{Aa}^\female(w_{AA}^\male + w_{Aa}^\male)\phi + w_{aa}^\female w_{AA}^\male \psi)}\\
-%\chi_{mA}&= R \frac{(\phi + \psi) w_{Aa}^\female w_{AA}^\male}{2 (w_{AA}^\female w_{Aa}^\male \phi^2 + \psi(w_{Aa}^\female(w_{AA}^\male + w_{Aa}^\male)\phi + w_{aa}^\female w_{AA}^\male \psi)} \\ 
-%\chi_{ma}&= R \frac{(\phi + \psi) w_{Aa}^\female w_{Aa}^\male}{2 (w_{AA}^\female w_{Aa}^\male \phi^2 + \psi(w_{Aa}^\female(w_{AA}^\male + w_{Aa}^\male)\phi + w_{aa}^\female w_{AA}^\male \psi)}\\
-%\end{align}
-%\end{subequations}
-%
-%\begin{subequations}
-%\begin{align}
-%\lambda_{mA}&= [( w_{AA}^\female + w_{Aa}^\female ) w_{Aa}^\male \phi + 2 w_{Aa}^\female w_{AA}^\male \psi] a \\
-%\lambda_{ma}&=  [(w_{aa}^\female + w_{Aa}^\female ) w_{Aa}^\male \phi + 2 w_{aa}^\female w_{AA}^\male \psi ] a\\
-%\chi_{mA}&= R w_{Aa}^\female (w_{Aa}^\male \phi + 2 w_{AA}^\male \psi) c \\ 
-%\chi_{ma}&= R w_{Aa}^\female w_{Aa}^\male \phi c \\
-%\end{align}
-%\end{subequations}
-%\noindent
-%where 
-%$c = \frac{\phi + \psi}{2 [w_{AA}^\female w_{Aa}^\male \phi^2 + \psi(w_{Aa}^\female(w_{AA}^\male + w_{Aa}^\male)\phi + w_{aa}^\female w_{AA}^\male \psi]}$ and $\phi$ and $\psi$ are evaluated with $\alpha^{\Hermaphrodite}=1/2$ and $w_a^\Hermaphrodite=w_A^\Hermaphrodite=1$.
-
-%With $R=0$ the two eigenvalues are $\lambda_{mA}$ and $\lambda_{ma}$.
-%The neo-W can then invade on the $A$ background when $\lambda_{mA}>1$ and the neo-W can invade on the $a$ background when $\lambda_{ma}>1$.
-%Even in this case it is difficult to see from equation \ref{Ainvasion} when the neo-W will invade.
-%Below we discuss why $\lambda_{mA}$ and $\lambda_{ma}$ might be larger than one and confirm the logic numerically.
-%
-%
-%For simplicity, consider the case of no haploid selection.
-%A polymorphism at the $\mathbf{A}$ locus then requires sexually-antagonistic selection \citep{vanDoorn:2007eu}.
-%Given that $a$ is fixed on the Y, one can consider the $a$ allele `male beneficial' and the $A$ allele to be `female beneficial'. 
-%Because X chromosomes spend some time in males the frequency of $A$ on the X can reach an intermediate equilibrium (equilibrium A).
-%
-%We can therefore reason that when a neo-W invades equilibrium (A), it is likely to spread on the $A$ background as W chromosomes are always in females.
-%The neo-W can outcompete the ancestral, `comprimising' X because it can specialize on females by fixing the `female beneficial' allele.  
-%We call this the `sex-specialist hypothesis'.
-%This hypothesis should only work when the benefit of specializing outweighs the cost of bringing Y chromosomes into females (the neo-W is epistatically dominant over the X/Y locus).
-%
-%One could also reason that, when the neo-W spreads, it does so precisely because it brings Y chromosomes, and their associated alleles, into females, something the X cannot do.
-%However, this requires a somewhat particular (perhaps `perverse') equilibrium, where XX females do worse than XY females despite associations on the X and Y being built up by selection.
-%One example of such a perverse equilibrium is produced by overdominance in both sexes.
-%Overdominance in females selects for an allele frequency of 0.5 on the X ($A$ and $a$ equally frequent, maximizing the number of heterozygotes). 
-%However, given that $a$ is fixed on the Y, overdominance in males selects for the X to become more associated with the $A$. 
-%Thus, a compromising equilibrium is reached on the X chromosome and females fitness suffers due to the overproduction of $AA$ homozygotes.
-%This sets up a scenario in which a neo-W can invade on the $a$ background, despite the fact that $a$ is fixed on the Y and in that sense `male beneficial'.
-%We call this the `perverse hypothesis'.
-%
-%Figure \ref{fig:Region_Plots} shows where the sex-specialist (red) and perverse (blue) hypotheses are valid.
-%The left panel demonstrates that both hypotheses can be simultaneously valid with overdominance in both sexes and sex differences in selection, which overlaps the parameter region where there is selection for increased recombination between the sex chromosomes \citep[compare with figure 2a in][]{Otto2014}.
-%The right panel shows that the perverse hypothesis is no longer valid when selection is exactly the same in both sexes, despite the fact that there is selection for increased recombination between the sex chromosomes with sufficiently strong overdominance \citep[compare with figure 3 in][]{Otto2014}.
-%
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%Sex-specialist vs perverse hypotheses
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\includegraphics[width=0.45\linewidth]{regionplot_2a}
-%\includegraphics[width=0.45\linewidth]{regionplot_3}\\
-%\caption{
-%Numerical exploration of where sex-specialist (red) and perverse (blue) hypotheses are valid, i.e., where an internally stable resident equilibrium can be invaded by a neo-W that is perfectly linked with the allele not fixed on the Y (red) or the allele that is fixed on the Y (blue).
-%\textbf{(Left)}
-%The perverse equilibrium is only valid with overdominance while the sex-specialist hypothesis is valid over the entire range shown.
-%Both hypotheses are simultaneously valid over much of the parameter space where increased recombination between the sex chromosomes is selected \citep[][figure 2a]{Otto2014}.
-%\textbf{(Right)}
-%Only the sex-specialist hypothesis is valid with no sex-differences in selection, despite selection for increased recombination between the sex-chromosomes with strong overdominance \citep[][figure 3]{Otto2014}.
-%Parameters: $w_{Aa}^\Hermaphrodite = 1$, $w_a^\Hermaphrodite = w_A^\Hermaphrodite = 1$, $\alpha^\Hermaphrodite = 1/2$, $r=R=0$, and in left panel $w_{aa}^\female = w_{AA}^\female = 0.6$.
-%}
-%\label{fig:Region_Plots}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section*{Supplementary Figures}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Both neo-W haplotypes can spread, in the absence of haploid selection, when there is overdominance
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-\centerline{\includegraphics[width=\linewidth]{PositionPlot_Overdominance}}
-\caption{
-Neo-W alleles can spread when loci under diploid selection are tightly linked to the ancestral sex determining locus ($r\approx0$). 
-In panels A and B, the $a$ allele is favoured in females ($w_{aa}^\female=1.05$, $w_{Aa}^\Hermaphrodite=1$, $w_{AA}^\female=0.85$) and selection in males is overdominant ($w_{aa}^\male=w_{AA}^\male=0.75$).
-In panels C and D, selection in males and females is overdominant ($w_{aa}^\female=w_{AA}^\female=0.6$, $w_{aa}^\male=0.5$, $w_{AA}^\male=0.7$, $w_{Aa}^\Hermaphrodite=1$).
-There is no haploid selection $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
-These parameters are marked by daggers in Figure \ref{fig:regionplots}B and C, which show that neo-W invasion is expected for any $R$ ($\lambda_{WA},\lambda_{Wa}>1$) when the $a$ allele is nearly fixed on the Y (black lines in this figure; not stable for $r>>0$).
-Equilibria where the $A$ allele is more common among Y-bearing male gametes can also be stable and allow neo-W invasion for these parameters (blue lines). 
-The weak selection approximation holds when all recombination rates are large relative to selection (around 0 in panels A and C), in which case, in the absence of haploid selection, neo-W alleles should spread if and only if they are more tightly linked to the selected locus (positive invasion fitness if and only if the selected locus is in the grey region).
-However, when linkage is tight (panels B and D and when the selected locus is near the SDRs in all panels), this weak selection prediction can break down. 
-}
-\label{fig:positionOverdominance}
-\end{figure}
-
-\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Both neo-W haplotypes can spread, in the absence of haploid selection, when there is overdominance
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-\centerline{\includegraphics[width=\linewidth]{Temporal_Overdominance}}
-\caption{
-Following invasion by a neo-W allele, there can be a complete transition to a new sex-determination system, maintenance of polymorphism at both ancestral-XY and neo-ZW sex determining regions, or loss of the new sex-determining allele.
-Here we plot the frequency of the neo-W allele among female gametes; as the neo-W reaches frequency $0.5$, polymorphism at the ancestral XY locus is lost with Y becoming fixed such that sex is determined only be the ZW allele carried by a female gamete.
-Panels A, C and D show cases where a steady state is reached with the neo-W at a frequency below $0.5$, in which case ancestral-X and Y alleles also both segregate. 
-In all cases, we assume that the $a$ allele is initially more common than the $A$ allele on the Y (Y-$a$ is fixed when $r=0$). 
-When $r>0$ (panels B and D), Y-$A$ haplotypes created by recombination can become more common than Y-$a$ haplotypes as the neo-W spreads.
-In B, this leads to loss of the neo-W and the system goes to an equilibrium with X-$a$ and Y-$A$ haplotypes fixed (equilibrium $A'$), such that all females have the high fitness genotype $aa$ and all males are $Aa$.
-For the parameters in B, neo-W alleles have negative invasion fitness when the Y-$A$ haplotype is ancestrally more common than Y-$a$ (see blue lines in Figure \ref{fig:positionOverdominance}A and  \ref{fig:positionOverdominance}B near the ancestral SDR).
-In contrast, the neo-W is not lost in panel D as it is favoured near $r\approx0$ (see blue lines in Figure \ref{fig:positionOverdominance}C and  \ref{fig:positionOverdominance}D near the ancestral SDR).
-Fitness parameters are the same as in Figure \ref{fig:positionOverdominance}; in panels A and B the $a$ allele is favoured in females ($w_{aa}^\female=1.05$, $w_{Aa}^\Hermaphrodite=1$, $w_{AA}^\female=0.85$) while there is overdominance in males ($w_{aa}^\male=w_{AA}^\male=0.75$) and in panels C and D, there is overdominance in both sexes ($w_{aa}^\female=w_{AA}^\female=0.6$, $w_{aa}^\male=0.5$, $w_{AA}^\male=0.7$, $w_{Aa}^\Hermaphrodite=1$).
-These parameters are marked by a dagger in Figure \ref{fig:regionplots}. 
-Here, there is no haploid selection $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
-}
-\label{fig:temporalOverdominance}
-\end{figure}
-
-\begin{figure}[!h]
-\centering
-\centerline{\includegraphics[width=1.5\linewidth]{PositionPlot_SexAntagTighter_MaleDrive}}
-\caption{
-When there is sexually-antagonistic selection and haploid selection, a neo-W may invade for any $R$.
-Panel A shows that the invasion fitness of a neo-W is positive where linkage is tight, even when $r<R$ (unshaded region).
-In panel B, we vary the recombination rate between the neo-W and the selected locus ($R$) for a fixed recombination rate between the ancestral-SDR and the selected locus ($r=0.005$).
-Coloured markers show recombination rates for which the temporal dynamics of neo-W invasion are plotted in panel C (black $R=0.001$, red $R=0.02$, blue $R=0.1$, green $R=0.5$). 
-The diploid selection parameters used in this plot are the same as in Figure \ref{fig:SexAntagTighter}. 
-There is also meiotic drive in males favouring $a$ ($\alpha_{\Delta}^\male=-0.08$), this full set of parameters is marked by an asterisk in Figure \ref{fig:regionMaleDrive}A.
-When $R=0.5$ (green curve), the neo-W does not reach fixation and X,Y,Z, and W alleles are all maintained in the population, see Figure \ref{fig:freqAll}C.
-}
-\label{fig:SexAntagTighterMaleDrive}
-\end{figure}
-
-\begin{figure}[!h]
-\centering
-\centerline{\includegraphics[width=\linewidth]{Region_Plot_combined_MaleDrive}}
-\caption{
-Meiotic drive in males affects whether neo-W-$A$ and neo-W-$a$ haplotypes spread when the ancestral-XY locus is tightly linked to a locus under selection ($r=0$). 
-We vary the fitness of male homozygotes relative to heterozygotes ($w_{Aa}^\Hermaphrodite=1$) and only consider stable equilibria at which both \textbf{A} locus allele are maintained and the $a$ allele is initially fixed on the Y, region outlined.
-In panels A-C, meiotic drive in males favours the $a$ allele ($\alpha_{\Delta}^\male=-0.16$), creating male-biased sex ratios and generally increasing $\lambda_{WA}$ and $\lambda_{Wa}$. 
-By contrast, $\lambda_{WA}$ and $\lambda_{Wa}$ tend to be reduced when meiotic drive in males favours the $A$ allele ($\alpha_{\Delta}^\male=0.16$), panels D-F. 
-We consider three forms of selection in females: directional selection in favour of the $A$ allele (panels A and D, $w_{aa}^\female=0.85$, $w_{AA}^\female=1.05$), direction selection in favour of the $a$ allele (panels B and E, $w_{aa}^\female=1.05$, $w_{AA}^\female=0.85$), and overdominance (panels C and F, $w_{aa}^\female=w_{AA}^\female=0.6$).
-%\textcolor{red}{Panel F mislabelled, should have $\lambda_{Wa}>1$ \& $\lambda_{WA}<1$ as the upper label that has the line.}
-}
-\label{fig:regionMaleDrive}
-\end{figure}
-
-\newpage
-\begin{figure}[!h]
-\centering
-\centerline{\includegraphics[width=\linewidth]{Region_Plot_combined_MaleGS}}
-\caption{
-Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is male gametic competition at a locus that is tightly linked to the ancestral-XY locus.
-Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in Figure \ref{fig:regionMaleDrive}. 
-The $a$ allele is favoured during male gametic competition in Panels A-C ($w_{a}^\male=1.16$, $w_{A}^\male=1$), which creates male biased sex ratios and increases $\lambda_{WA}$ and $\lambda_{Wa}$. 
-On the other hand, the $A$ allele is favoured during male gametic competition in Panels D-F ($w_{a}^\male=1$, $w_{A}^\male=1.16$) and $\lambda_{WA}$ and $\lambda_{Wa}$ tend to be reduced. 
-Compared to the meiotic drive parameters in Figure \ref{fig:regionMaleDrive}, the effect of these male gametic competition parameters on the sex ratio is smaller. 
-For example, in Figure \ref{fig:regionMaleDrive}A-C, the ancestral sex ratio is $\alpha^\male=0.58$ at equilibrium (B) and in panels A-C of this plot, the ancestral sex ratio is $w_{a}^\male/(w_{A}^\male+w_{a}^\male)=0.537$ at equilibrium (B).
-}
-\label{fig:regionMaleGS}
-\end{figure}
-
-\begin{figure}[!h]
-\centering
-\centerline{\includegraphics[width=\linewidth]{Region_Plot_combined_FemaleDrive}}
-\caption{
-Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is female meiotic drive at a locus that is tightly linked to the ancestral-XY locus.
-Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in Figure \ref{fig:regionMaleDrive} and \ref{fig:regionMaleGS}. 
-The $a$ allele is favoured by meiotic drive in females in Panels A-C ($\alpha_{\Delta}^\female=-0.16$), which increases $\lambda_{Wa}$ and decreases $\lambda_{WA}$. 
-Female meiotic drive in favour of the $A$ allele (panels D-F, $\alpha_{\Delta}^\female=-0.16$) has the opposite effect. 
-}
-\label{fig:regionFemaleDrive}
-\end{figure}
-
-\begin{figure}[!h]
-\centering
-\centerline{\includegraphics[width=\linewidth]{Region_Plot_combined_FemaleGS}}
-\caption{
-Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is female gametic competition at a locus that is tightly linked to the ancestral-XY locus.
-Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in Figure \ref{fig:regionMaleDrive}, \ref{fig:regionMaleGS}, and \ref{fig:regionFemaleDrive}. 
-The $a$ allele is favoured during female gametic competition in females in Panels A-C ($w_{a}^\female=1.16$, $w_{A}^\female=1$), which increases $\lambda_{Wa}$ and decreases $\lambda_{WA}$. 
-The $A$ allele is favoured during gametic competition in panels D-F ($w_{a}^\female=1$, $w_{A}^\female=1.16$), giving the opposite effect on $\lambda_{Wa}$ and $\lambda_{WA}$. 
-}
-\label{fig:regionFemaleGS}
-\end{figure}
-
-\begin{landscape}
-\begin{figure}[!h]
-\centering
-\centerline{
-\includegraphics[width=\linewidth]{All_plot_combined_PloidAntag}
-}
-\caption{
-A-D show when each of the neo-W haplotypes invade an internally stable equilibrium with $a$ fixed on the Y (found by setting $r=0$).
-The y-axis shows directional selection in diploids of both sexes, $s^\female=s^\male$, and the x-axes show sex-specific drive, $\alpha_\Delta^\Hermaphrodite$, or haploid competition, $t^\Hermaphrodite$.
-The top left and bottom right quadrants therefore imply ploidally-antagonistic selection (and these are the only places where neo-W haplotypes can invade).
-Dominance is equal in both sexes, $h^\female=h^\male=3/4$. 
-E-F show the temporal dynamics of neo-W frequency in females with parameters given by the asterisks in the corresponding A-D plot, with $r=1/200$, for four different $R$.
-Black $R=1/1000$, Red $R=2/100$, Blue $R=1/10$, Green $R=1/2$.  
-%Dashed line in E-H gives ``fixation" of neo-W (all females heterozygous ZW).
-}
-\label{fig:regionPloidAntag}
-\end{figure}
-\end{landscape}
-
-%\begin{landscape}
-\begin{figure}[!h]
-\centering
-\centerline{
-\includegraphics[width=\linewidth]{Freq_plot_combined_PloidAntag}
-}
-\caption{
-Fixation of neo-W or maintenance of multiple sex-determining systems. 
-The curves show the frequencies of the neo-W (red), ancestral-Y (blue), and $A$ allele (black) among female gametes (solid curves) and among male gametes (dashed curves). 
-In panel A, there is a complete transition from XY sex determination (XX-ZZ females and XY-ZZ males) to ZW sex determination (YY-ZW females and YY-ZZ males).  
-In panels B and C a polymorphism is maintained at both the ancestral XY locus and the neo-ZW locus, such that there are males with genotypes XY-ZZ or YY-ZZ and females with genotypes XX-ZZ, XX-ZW, XY-ZW, or YY-ZW.
-In panel A, selection is ploidally antagonistic with drive in males (parameters as in the green curve in Figure \ref{fig:SexRatioBad}B).
-In panel B, there is overdominance in both sexes and no haploid selection (parameters as in the green curve in Figure \ref{fig:temporalOverdominance}C).
-In panel C, there is sexually-antagonistic selection in diploids with drive in males (parameters as in the green curve in Figure \ref{fig:regionMaleDrive}C).
-%In Panel D there is ploidally-antagonistic selection with haploid competition in males (parameters as in the green curve of Figure \ref{fig:regionPloidAntag}F).
-In all cases, the initial equilibrium frequency has $a$ near fixation on the Y.
-}
-\label{fig:freqAll}
-\end{figure}
-%\end{landscape}
-
-\begin{figure}[!h]
-\centering
-\centerline{
-\includegraphics[width=\linewidth]{neoW_invades_tight_loose}
-}
-\caption{
-An unlinked neo-W can invade a perfectly linked system with overdominance or haploid selection.
-Here overdominance leads to a polymorphic sex-determining system.
-Before invasion the population is at equilibrium B.
-Parameters:
-}
-\label{fig:loose_invades_tight}
-\end{figure}
-
-%\begin{figure}[!h]
-%\centering
-%\centerline{
-%\includegraphics[width=\linewidth]{Sallys_R_plot.pdf}
-%}
-%\caption{
-%\textcolor{blue}{is this the one?}
-%}
-%\label{fig:lambda_R}
-%\end{figure}
-
-%\newpage
-%\textcolor{red}{
-%Add Sally's figure showing lambda for small r near equil A versus near equil B.
-Add references to this figure to appendix where we discuss whether lambdas can be greater than 1 with sexually antagonistic selection.}
-%\textcolor{blue}{not sure which one you are talking about, but see Figure \ref{fig:lambda_R} }
-%\textcolor{red}{Let's remove this for now.}
-
-%\textcolor{red}{
-%Perhaps it would also be useful to add an 8 panel figure that features ploidally antagonistic selection.
-For each type of haploid selection (gametic competition/ meiotic drive in males/females), give a regionplot where $h^\male=h^\female$, e.g., $h^\male=h^\female=0.75$ (or perhaps the value of $h$ we use in the regionplots we have, in which $w_{aa}=0.85$, $w_{Aa}=1$, $w_{AA}=1.05$).
-%Matt made a figure like this before but both Y$a$ and Y$A$ equilibria were plotted and there was no outline showing where the Y$a$ equilibrium is stable (as in Figure \ref{fig:regionplots}).
-In Matts plot the axes were $s^\Hermaphrodite$ and $\alpha_{\Delta}^\Hermaphrodite$.
-%Add an asterisk to each region plot and show invasion in another panel, using those parameters and various $R$ (e.g., in the stye of \ref{fig:temporalOverdominance}). 
-%In an email, Sally has an example of ploidally-antagonistic selection where the neo-W fixes and $R=1/2$. This would cover that case and more. }
-%\textcolor{blue}{made an attempt (Figure \ref{fig:regionPloidAntag})}
-
-%\textcolor{red}{
-%We could also give versions of Figure \ref{fig:regionplots} where there is also haploid selection of various types.
-%Haploid selection can favour $A$ or $a$, so this would involve 4x 6-panel figures.
-Started looking at this in Figure \ref{fig:regionMaleGS} and Figure \ref{fig:regionMaleDrive}, add female haploid selection.
-%Try to integrate into the discussion of haploid selection? e.g., male haploid selection ones generally show effect of sex ratio, increasing both lambdas when female biased (top rows).}
-%\textcolor{blue}{
-%these figures are now done (\ref{fig:regionMaleDrive}-\ref{fig:regionFemaleGS}) (ensuring frequencies between 0 and 1), but yet to discuss in text.}
-
-%\textcolor{red}{
-%Perhaps, for one set of parameters, we should plot the dynamics of all the different alleles.
-E.g., we could use the same parameters used in \ref{fig:SexRatioBad}.
-The main purpose would be to show what happens to the ancestral SDR during turnover.
-%We could also show an example where XY and ZW sex determining systems are both polymorphic and stable (e.g., using one of the curves in Figure \ref{fig:temporalOverdominance} and the green curve in Figure \ref{fig:SexAntagTighterMaleDrive}).
-%I think there are also examples with looser sex linkage and pollen competition that lead to a mixed sex-determination system.
-We should probably have a short section in the appendix discussing this.
-}
-%\textcolor{blue}{made an attempt with Figure \ref{fig:freqAll}, but yet to discuss in text}
-
 \end{document}

### 2018-01-18 LaTeX/Supp_Figures_and_Table.tex
moved to plos template, appendices have references that are still messed up

--- 2018-01-17 LaTeX/Turnover.tex
@@
 
-\title{Haploid Selection, Sex Ratio Bias, and Transitions Between Sex-Determination Systems}
-\author{Michael F Scott$*^1$, Matthew M Osmond$*^2$, and Sarah P Otto$^2$}
-\date{}
-\maketitle
-\noindent
-$*$ These authors contributed equally to this work
-
-\noindent
-$^1$ Department of Botany, University of British Columbia, \#3529 - 6270 University Boulevard, Vancouver, BC, Canada V6T 1Z4
-
-\noindent
-$^2$ Department of Zoology, University of British Columbia, \#4200 - 6270 University Boulevard, Vancouver, BC, Canada V6T 1Z4
-
-\noindent
-email: mfscott@biodiversity.ubc.ca, mmosmond@zoology.ubc.ca
-
-\noindent
-Contributions:
-
-\newpage
-\linenumbers
-\modulolinenumbers[2]
-
-\begin{abstract}
-Sex-determination systems are remarkably dynamic; many taxa display shifts in the location of sex-determining loci or the evolution of entirely new sex-determining systems. 
-Predominant theories for why we observe such transitions %in which new sex-determining systems spread by selection 
-%involve sex ratio selection or sex-specific selection (e.g., sexually antagonistic selection).
-%These studies 
-generally conclude that novel sex-determining systems are favoured by selection if they equalise the sex ratio or increase linkage with a sexually-antagonistic locus. 
-We use population genetic models to extend these theories in two ways: 
-(1) We explicitly consider selection on loci very tightly linked to the ancestral sex-determining loci, e.g., within the non-recombining region of the ancestral sex chromosomes. 
-%(1) We explicitly consider how selection on very tightly sex-linked loci influences the spread of novel sex-determiners. 
-Variation at such loci can favour the spread of new sex-determination systems in which the heterogametic sex changes (XY to ZW or ZW to XY) and the new sex-determining region is less closely linked (or unlinked) to the locus under selection, which is not predicted by previous theory.
-%With tight linkage, selection can maintain equilibria at which the allele fixed on the sex-limited chromosome (Y or W) is simultaneously favoured in the homogametic sex (XX females or ZZ males) such that heterogametic transitions (XY to ZW or ZW to XY) are favoured by selection.
-%Alternatively, a neo-W (neo-Y) locus can invade when it allows greater specialism on alleles beneficial in females (male) compared to an ancestral XX female (ZZ male), 
-(2) We also consider selection upon haploid genotypes either during gametic competition (e.g., pollen/sperm competition) or meiosis (i.e., non-Mendelian segregation); selective processes that typically occur in one sex or the other.
-%As well as having sex-specific fitness consequences, haploid selection can cause the zygotic sex ratio to become biased because sex ratios are determined by the production and fertilization success of X- versus Y-bearing pollen/sperm (or Z- versus W-bearing ovules/eggs).
-%Consequently, selection for XY to ZW transitions and ZW to XY transitions can be assymetrical when linkage between the ancestral sex-determining locus and a locus under haploid selection is tight, in which case ancestral sex ratio biases can be strong.
-%In addition, when linkage between the ancestral sex-determining locus and a locus under haploid selection is tight, sex ratio biases can be strong such that there is an asymmetry between invasion of ancestrally XY and ancestrally ZW systems because, e.g., haploid selection in males only causes biased zygotic sex ratios in an ancestrally XY system.
-We find that associations with haploid selected loci can drive transitions between sex determination systems, without requiring sexually-antagonistic selection in diploids. 
-Unexpectedly, with haploid selection, transitions between male and female heterogamety can also evolve where linkage with the sex-determining locus is weakened. 
-Furthermore, haploid selection in the heterogametic sex can cause sex ratio biases, which may increase or decrease with the spread of new sex chromosomes. 
-Thus, we find that transitions between sex-determination systems cannot be simply predicted by selection to equalise the sex ratio. 
-%These results indicate that loci experiencing haploid selection can favour the evolution of new sex-determination systems. 
-%These results indicate that favourable associations that develop between the ancestral sex-determining locus and selected loci can be broken during the spread of a new sex-determining region. 
-%Such transitions are not possible with diploid selection alone, in which case tighter linkage increases the fitness of both males and females. 
-%Notably, we find that the spread of new genetic sex-determination systems is not affected by sex ratio biases that are caused by haploid selection. 
-%A surprising result given that other determinants of sex allocation typically experience strong Fisherian sex ratio selection to equalize sex ratios. 
-%Overall, we demonstrate when and how the evolution of sex determining systems is impacted by sex ratio biases resulting from haploid selection and we show that new sex-determining regions can be favoured even if they are not closely linked with a locus under selection.
-Overall, our models reveal that transitions between sex-determination systems, particularly transitions where the heterogametic sex changes, can be driven by loci in previously unpredicted genomic locations that experience selection during diploid and/or haploid phases.
-These results predict conditions under which sex-determination systems are likely to be labile and draw novel connections with sex ratio evolution
-%These results might be reflected in the lability with which sex-determination systems evolve. %and for the factors determining the phylogenetic pattern of sex-determination systems. 
-\end{abstract}
-
-%abstract word count: $\approx$ 350
-
-\newpage
-
-\section*{Introduction}
-
-%CHECK THROUGHOUT: use of sex-determination SYSTEMS versus MECHANISMS. 
-%CHECK THROUGHOUT: use of haploid selection, gametic selection, and meiotic drive.
-
-Animals and angiosperms exhibit extremely diverse sex-determination systems \citep[reviewed in][]{Bull:1983vi,Charlesworth:2010it,Beukeboom:2014vb,Bachtrog:2014bx}. 
-Among species with genetic sex determination of diploid sexes (GSD), some taxa have heterogametic males (XY) and homogametic females (XX), including %non-monotreme?
-I think monotremes have XY but tonnes of translocations, giving: X1,X2...X6 Y1
-mammals and most dioecious plants \citep{Ming:2011iy}; whereas other taxa have homogametic males (ZZ) and heterogametic females (ZW), including Lepidoptera and birds. 
-Within several taxa, the chromosome that harbours the master sex-determining region changes. 
-For example, transitions of the master sex-determining gene between chromosomes or the evolution of new master sex-determining genes have occurred in Salmonids \citep{Li:2011fm,Yano:2012di}, Diptera \citep{Vicoso:2015hf}, and \textit{Oryzias} \citep{Myosho:2012fv}.
-%Presentation at evolution found neo sex chromosome in birds, doesn't seem to be published or bioRxiv yet (consider pers com.), title: A previously unknown neo-sex chromosome mediates plumage divergence and speciation in hybridizing birds Jason Sardell; Elizabeth Cooper; J.
-Albert C.
-Uy.
-I wonder if this is actually a fusion event though?
-In addition, many clades exhibit transitions between male (XY) and female (ZW) heterogamety, including snakes \citep{Gamble2017}, lizards \citep{Ezaz:2009tk}, eight of 26 teleost fish families \citep{Mank:2006bt}, true fruit flies \citep[Tephritids,][]{Vicoso:2015hf}, amphibians \citep{Hillis:1990gu}, the angiosperm genus \textit{Silene} \citep{Slancarova:2013dq}, the angiosperm family \textit{Salicaceae} \citep{Pucholt2015,Pucholt2017} and Coleoptera and Hemiptera \citep[][plate 2]{Beukeboom:2014vb}.
-Indeed, in some cases, both male and female heterogametic sex-determination systems can be found in the same species, as reported in houseflies \citep{Macdonald1978}, midges \citep{Thompson1971}, frogs \citep{Ogata:2007jm}, cichlid fish \citep{Ser:2010iq}, tilapia \citep{Lee2004}, sea bass \citep{Vandeputte2007}, and lab-strains of Zebrafish \citep{Liew2012,Wilson2014}.
-In addition, multiple transitions have occurred between genetic (GSD) and environmental sex-determination (ESD) systems, e.g., in reptiles and fishes \citep{Conover:1987in,Mank:2006bt,Pokorna:2009ui,Ezaz:2009tk,Pen:2010kk,Holleley:2015hc}.
-
-%NOTE: ``Bull & Charnov (1977) hypothesized that a new sex-determining gene can rapidly increase and become fixedin a population if it is linked to a gene with high adaptivevalue, and finally cause a change of the heterogametic sex.'' The Bull and Charnov paper is also the one in which the set of neutral equilibria between XY and ZW are identified (where sex ratios are equal)
-%NOTE: Vuilleumier et al. 2007 also find polymorphic sex determination can be stable.
-
-%For example, closely related species in the Medaka lineage (cite Takenhana et al. 2008) and Tilapiinae (cite Lee et al 2004, Cnaani et al 2008), citations in Beukeboom.
-
-%\textcolor{red}{Brief description of sex ratio adjustment and sexual antagonism theories:}
-
-Predominant theories accounting for the spread of new sex-determination systems by selection involve fitness differences between sexes (e.g., sexually antagonistic selection) or sex ratio selection \citep{Blaser2012, Beukeboom:2014vb,vanDoorn2014re}.
-%\citet{Bull:1977wt} shows that direct selection on new sex determination loci can allow them to spread and switch between male and female heterogamety. 
-\citet{vanDoorn:2007eu,vanDoorn:2010hu} and \citet{Muralidhar2018} have shown that new sex-determining loci can be favoured if they arise in close linkage with a locus that experiences sexual antagonism.
-Tighter linkage allows a stronger favourable association to build up between a male-beneficial allele, and a neo-Y chromosome, for example. 
-Such associations can favour a new partially-masculinizing or partially-feminizing allele \citep{Muralidhar2018}, a new master sex-determining gene \citep{vanDoorn:2007eu}, and transitions between male and female heterogamety \citep[trans-GSD transitions, ZW to XY or XY to ZW,][]{vanDoorn:2010hu}.
-However, any sexually-antagonistic loci that are more closely linked to the ancestral sex-determination locus will develop similar, favourable associations and are expected to hinder the spread of a new sex-determination system.
-%Here we extend these studies by explicitly calculating the the equilibrium allele frequencies of loci that are very tightly linked to the ancestral sex-determining region.
-
-The sex ratio is directly determined by the sex-determination system, and it has therefore been suggested that sex ratio selection is a dominant force in the evolution of sex determination (e.g., \citealt{Bull:1983vi}, p 66-67; \citealt{Beukeboom:2014vb}, Chapter 7).
-`Fisherian' sex ratio selection favours a 1:1 zygotic sex ratio when assuming that males and females are equally costly to produce \citep{Fisher:1930wy,Charnov:1982wg}.
-This follows from the fact that, for an autosomal locus, half of the genetic material is inherited from a male and half from a female \citep{West:2009we}. 
-Thus, if the population sex ratio is biased towards one sex, the average per-individual contribution of genetic material to the next generation from the opposite sex is greater. 
-Therefore, a mutant that increases investment in the rarer sex will spread via the higher per-individual contributions made by that sex. 
-%The default mode of sex ratio selection is `Fisherian' sex ratio selection, which favours equal investment in male and female offspring \citep[i.e., a 1:1 zygotic sex ratio when assuming that males and females are equally costly to produce,][]{Fisher:1930wy,Charnov:1982wg}.
-%Given that the sex-determination system can directly affect the sex ratio, we might expect Fisherian sex ratio selection to influence the spread of new sex-determination systems. 
-In the case of sex-chromosome evolution, \citet{Kozielska:2010vm} consider systems in which the ancestral sex chromosomes experience meiotic drive (e.g., where driving X or Y chromosomes are inherited disproportionately often), which causes sex ratios to become biased \citep{Hamilton:1967ts}.
-They find that new, unlinked sex-determining loci (masculinizing or feminizing mutations, i.e., neo-Y or neo-W loci) can then spread, which restore an even sex ratio.
-
-%\textcolor{red}{We add haploid selection:}
-Here we use mathematical models to find the conditions under which new sex-determination systems spread when individuals experience selection at both diploid and haploid stages. 
-Even in animal and plant species that have much larger and more conspicuous diploid phases than haploid phases, many loci experience significant haploid selection through gamete competition and/or meiotic drive \citep{Mulcahy:1996ha,JOSEPH:2004haa}.
-We use the term `meiotic drive' to refer to the biased (non-Mendelian) segregation of genotypes during gamete production (from one parent) and the term `gametic competition' to refer to selection upon haploid genotypes within a gamete/gametophyte pool (potentially from multiple parents); the term `haploid selection' encompasses both processes.
-
-% from Bai et al.
-(2016) ``[Segregation distortion] phenomenon is commonly detected via genetic mapping and has been documented in various species, including mouse (Eversley et al., 2010; Casellas et al., 2012), Drosophila (Phadnis and Orr, 2009; Larracuente and Presgraves, 2012; McDermott and Noor, 2012), Tigriopus (Pritchard et al., 2011), rice (Koide et al., 2012; Reflinur et al., 2014; Xu et al., 2014), maize (Tang et al., 2013), and cotton (Yu et al., 2011; Hulse-Kemp et al., 2015).'' Also more in that paper that might be useful.
-%Drosophila http://www.biorxiv.org/content/early/2017/02/06/106336
-Segregation distortion provides putative evidence of haploid selection and can sometimes be attributed to meiotic drive and/or gametic competition \citep{Lalanne2004,Fishman2005,Leppala2008,Leppala2013,Didion2015,Didion2016}.
-Where it has been characterized, meiotic drive generally occurs either during the production of male or female gametes only \citep{Ubeda:2005gw,Lindholm:2016cw}.
-Gametic competition is also typically sex specific, occurring primarily among male gametes, because there are typically many more pollen/sperm than required for fertilization.
-Gametic competition may be particularly common in plants, in which 60-70\% of all genes are expressed in the male gametophyte, and these genes exhibit stronger signatures of selection than random genes \citep{Borg:2009jpa,Arunkumar:2013iq,Gossmann:2014dua}.
-In addition, artificial selection pressures applied to male gametophytes are known to cause a response to selection \citep[e.g.,][]{Hormaza:1996cv,Ravikumar:2003uo,Hedhly:2004iv,Clarke:2004ir}. 
-A smaller proportion of genes are thought to be expressed and selected during competition in animal sperm, although precise estimates are uncertain \citep{Zheng:2001fi,JOSEPH:2004haa,Vibranovski:2010et}.
-Nevertheless, recent studies have demonstrated that sperm competition in animals can alter haploid allele frequencies and increase offspring fitness \citep{Immler:2014im,Alavioon2017}.
-
-There are various ways by which genes experiencing haploid selection could influence transitions between sex-determination systems. 
-If we assume that haploid selection at any particular locus predominantly occurs in one sex (e.g., meiotic drive during spermatogenesis), then such loci experience a form of sex-specific selection. 
-In this respect, we might expect that haploid selection would affect transitions between sex-determination systems in a similar manner to sex-specific diploid selection \citep[as explored by][]{vanDoorn:2007eu,vanDoorn:2010hu}.
-That is, new masculinizing mutations (neo-Y chromosomes) could be favoured via associations with alleles that are beneficial in the male haploid stage. 
-On the other hand, sex ratios can also become biased by linkage between the sex-determining region and a locus that harbours genetic variation in haploid fitness. 
-For example, there are several known cases of sex ratio bias caused by sex-linked meiotic drive alleles \citep[][Chapter 3]{Burt:2006} or selection among X- and Y-bearing pollen \citep{Lloyd:1974tz,Conn:1981uw,Stehlik:2005ul,Stehlik:2006to,Field:2012fd,Field:2013cc}.
-It is not immediately clear how the spread of new sex-determination systems would be influenced by the combination of sex ratio biases and associations between haploid selected loci and sex-determining regions.
-
-%Perhaps longer discussion of tight sex-linkage here? e.g., mention that r=0 is a particularly significant case for sex chromosomes.
-
-We find that the spread of novel sex-determiners is influenced by both Fisherian sex ratio selection and by selection on genetically-associated alleles. 
-%We find that sex ratio biases caused by haploid selection can exert Fisherian sex ratio selection upon novel sex-determiners but that their spread is also determined by selection on genetically-associated alleles.
-%Indeed, it is only when haploid-selected loci are tightly linked to the ancestral sex-determining region (and so sex ratio biases are initially large) that we see an asymmetry between selection for XY to ZW transitions and ZW to XY transitions (e.g., because haploid selection in males only causes biased zygotic sex ratios in an ancestrally XY system).
-Surprisingly, Fisherian sex ratio selection does not dominate; it is possible for selection on linked alleles to drive turnover between sex-determining systems despite causing increasingly biased sex ratios.
-In addition to considering haploid selection, another novel development in our model is that we consider loci that are in very tight linkage with the ancestral sex-determining region. 
-Because sex-determining loci are often found within a region of suppressed recombination, there can be a significant number of tightly linked loci. 
-We find that loci linked with the ancestral sex-determining region can drive transitions in which the heterogametic sex changes, even when the neo-sex-determining locus is less closely linked to loci under selection (either including haploid selection or not).
-%Such transitions are not favoured in models lacking tight linkage and/or haploid selection. 
-%Secondly, we allow sex-specific haploid selection to occur on a locus in tight or loose linkage with the ancestral sex-determining region. 
-%In addition, when linkage between the ancestral sex-determining locus and a locus under haploid selection is tight, sex ratio biases can be strong such that there is an asymmetry between invasion of ancestrally XY and ancestrally ZW systems because, e.g., haploid selection in males only causes biased zygotic sex ratios in an ancestrally XY system.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Model}
-%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Model Outline
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-\centerline{\includegraphics[width=\linewidth]{Sex_determination_outline.pdf}}
-\caption{
-Outline of model features. 
-Panel A: Recombination rate parameters between the ancestral-sex-determining locus (here, assumed to have X or Y alleles), a locus under selection (\textbf{A}, with alleles $A$ and $a$), and a neo-sex-determining locus (\textbf{M}, with alleles $M$ and $m$).
-If $r<1/2$, then associations between ancestral-sex-determining alleles (X and Y) and \textbf{A} locus alleles can be maintained past recombination in males.
-Panel B: Haploid selection is often sex-specific, occurring during haploid production or competition in either males or females. 
-For example, haploid selection in males only is represented by the dashed circle.  
-If X or Y alleles remain associated with alleles that experience haploid selection in males ($r<1/2$), then zygotic sex ratios can become biased because either X or Y male gametes/gametophytes will be abundant after haploid selection.
-However, the zygotic sex ratio is not biased by male haploid selection in ZW sex-determination systems. 
-Similarly, zygotic sex ratio biases can occur if haploid selected alleles are associated with neo-sex-determining alleles ($M$ and $m$, i.e., if $R<1/2$). 
-Panel C: During cis-GSD transitions (XY to XY or ZW to ZW, without loss of generality we assume ancestral XY sex determination here), a neo-Y allele spreads to pseudo-fixation (its maximum frequency among male gametes) and the the ancestral-Y allele is lost.
-Panel D: During trans-GSD transitions (XY to ZW or ZW to XY), a neo-W allele spreads to pseudo-fixation (its maximum frequency among female gametes) and the ancestral-X allele is lost.
-Neo-W mutations allow Y-associated alleles into females, which may impede or aid their spread.
-}
-\label{fig:model_outline}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\textcolor{red}{Change all  $\alpha^\Hermaphrodite$ to $(1+\alpha_{\Delta}^\Hermaphrodite)$.}
-%\textcolor{blue}{I've attempted this everywhere except in the recursions (S.1), which seem more natural with $\alpha$'s.
-I've run into trouble in equation S.8c,d -- I think we should check the Mathematica results to be sure we haven't made a typo.
-This also introduced an extra 1/2 in S.6c,d that might need to be explained.}
-%\textcolor{red}{hmm, not sure.
-This was an idea from Sally, I think in response to terms like $2 \alpha^\Hermaphrodite$ and $2(1-\alpha^\Hermaphrodite)$.
-It's possible that it makes other equations less easy to understand.
-My previous (not explained) logic was to use $w$ and $\alpha$ for strong selection and $s$, $t$, and $\alpha_\Delta$ for weak selection.
-Just to check, I should have written $\alpha^\Hermaphrodite=(1+\alpha_{\Delta}^\Hermaphrodite)/2$, maybe that's where the factors of $1/2$ come from?}
-%\textcolor{blue}{shoot, i may have changed too much (i.e.
-strong selection too), but i did use the correct transformation.
-still, the form of S.8c,d seems wrong.
-I'll double check it.
-CANT FIND ANY ERRORS YET STILL HAVE A "2" IN S.8c.
-These 2s reappear in S.9 and S.10, always with $W_{AA}$.}
-
-%\textcolor{red}{Switch between $\rho$ and $\rho$ in all places because $\rho$ is used for double recombination events.}
-%\textcolor{blue}{I think we need a different variable given the $\rho$ terms in the characteristic polynomial.
-Also, where is $\rho$ used for double recombination?
-In other papers?
-Here $\rho$ is the probability of an odd number of cross-overs between the SDR and M loci.}
-%\textcolor{red}{Good point, not sure what's best for \textbf{the-term-formerly-known-as-$\rho$}.
-Yeah, Sally's written comment was something like ``$\rho$ is semi-standard notation for double recombination so it's use as a recombination rate might be confusing''.}
-
-%\textcolor{red}{Change $\zeta$ to represent zygotic sex ratio of males, consistent with $q$ and figures.}
-
-%genetic system
-We consider transitions between ancestral and novel sex-determining systems using a three-locus model, each locus having two alleles. 
-Locus \textbf{X} is the ancestral sex-determining region, with alleles $X$ and $Y$ (or $Z$ and $W$).
-Locus \textbf{A} is a locus under selection, with alleles $A$ and $a$.
-Locus \textbf{M} is a novel sex-determining region, at which the null allele ($M$) is initially fixed in the population such that sex of zygotes is determined by the genotype at the ancestral sex-determining region, \textbf{X}; $XX$ genotypes become females and $XY$ become males (or $ZW$ become females and $ZZ$ become males).
-To evaluate the evolution of new sex-determination systems, we consider the invasion, fixation, maintenance, and/or loss of novel sex-determining alleles ($m$) at the \textbf{M} locus. 
-%We only do invasion analytically though (is this sentence still ok?)
-We assume that the \textbf{M} locus is epistatically dominant over the \textbf{X} locus such that zygotes with at least one $m$ allele develop as females with probability $k$ and as males with probability $1-k$, regardless of the \textbf{X} locus genotype.
-With $k=0$, the $m$ allele is a masculinizer (i.e., a neo-Y) and with $k=1$ the $m$ allele is a feminizer (i.e., a neo-W).
-With intermediate $k$, we can interpret $m$ as an environmental sex determination (ESD) allele, such that zygotes develop as females in a proportion ($k$) of the environments they experience. 
-%We also analyze a model of maternally-controlled environmental sex-determination, where mothers with at least one $m$ allele produce daughters with probability $k$.
-
-%life-cycle
-In each generation, we census the genotype frequencies in male and female gametes/gametophytes (hereafter gametes) before gametic competition. 
-A full description of our model, including recursion equations, is given in the Appendix. 
-First, competition occurs among male gametes (sperm/pollen competition) and among female gametes (egg/ovule competition) separately. 
-Selection during gametic competition depends on the \textbf{A} locus genotype, relative fitnesses are given by $w_A^\Hermaphrodite$ and $w_a^\Hermaphrodite$ ($\Hermaphrodite \in \{\female,\male\}$; see table \ref{tab:fitnesstable}).
-%$w_{A}^\male$ and $w_{a}^\male$ for male gametes and $w_{A}^\female$ and $w_{a}^\female$ for female gametes, see table \ref{tab:fitnesstable}.
-We assume that all gametes compete for fertilization during gametic competition, which assumes a polygamous mating system. 
-Gametic competition in monogamous mating systems is, however, equivalent to meiotic drive in our model (described below), as either only alters the frequency of gametes produced by heterozygotes. 
-After gametic competition, random mating occurs between male and female gametes.
-The resulting zygotes develop as males or females, depending on their genotypes at the \textbf{X} and \textbf{M} loci. %(and the \textbf{M} genotype of their mother in the case of maternal control).
-Diploid males and females then experience selection, with relative fitnesses $w_{AA}^{\Hermaphrodite}$, $w_{Aa}^{\Hermaphrodite}$, and $w_{aa}^{\Hermaphrodite}$.
-%where $g$ is the diploid genotype at the \textbf{A} locus ($g \in \{AA, Aa, aa\}$).
-%Diploids compete with others of the same sex, where selection depends on the sex of the individual and its genotype at the \textbf{A} locus.
-The next generation of gametes is produced by meiosis, during which recombination and sex-specific meiotic drive can occur. 
-Recombination (i.e., an odd number of cross-overs) occurs between loci \textbf{X} and \textbf{A} with probability $r$, between loci \textbf{A} and \textbf{M} with probability $R$, and between loci \textbf{X} and \textbf{M} with probability $\rho$.
-Any linear order of the loci can be modelled with appropriate choices of $r$, $R$, and $\rho$ (see Figure \ref{fig:model_outline}A and Table \ref{tab:chisubstitutions}). 
-Individuals that are heterozygous at the \textbf{A} locus may experience meiotic drive; a gamete produced by $Aa$ heterozgotes of sex $\Hermaphrodite$ bears allele $A$ with probability $\alpha^\Hermaphrodite$.
-Thus, the \textbf{A} locus can experience sex-specific gametic competition, diploid selection, and/or meiotic drive.
-
-\begin{table}[ht]
-\centering
-\smallskip
-\caption{Relative fitness of different genotypes in sex $\Hermaphrodite \in \{\female,\male\}$}
-\begin{tabular}{l c }
-\hline\hline
-  Genotype & Relative fitness during gametic competition \\ [0.5ex] \hline
-  A & $w_{A}^\Hermaphrodite = 1+t^\Hermaphrodite$ \\
-  a & $w_{a}^\Hermaphrodite = 1$ \\ [0.5ex] \hline
-  Genotype & Relative fitness during diploid selection \\ [0.5ex] \hline
-  AA & $w_{AA}^\Hermaphrodite = 1+ s^\Hermaphrodite$ \\
-  Aa & $w_{Aa}^\Hermaphrodite = 1+h^\Hermaphrodite s^\Hermaphrodite$ \\
-  aa & $w_{aa}^\Hermaphrodite = 1$ \\ [0.5ex] \hline
-  Genotype & Transmission during meiosis in $Aa$ heterozygotes \\ [0.5ex] \hline
-  A & $\alpha^\Hermaphrodite=1/2+\alpha_{\Delta}^{\Hermaphrodite}/2$ \\
-  a & $1-\alpha^\Hermaphrodite=1/2-\alpha_{\Delta}^{\Hermaphrodite}/2$ \\
-  \hline \hline
-  \label{tab:fitnesstable}
- \end{tabular}
-\end{table}
-
-%Info moved above
-%what were going to do, briefly
-%With allele $M$ fixed at the \textbf{M} locus, sex is determined by locus \textbf{X} and an equilibrium is reached at locus \textbf{A}.
-%where, importantly, locus \textbf{A} can be stably polymorphic.
-%the dynamics can be described by the frequency of $A$ in gametes/gametophytes from the homogametic sex and the frequencies of $A$ in the two types of gametes/gametophytes from the heterogametic sex.
-%We then examine the ability of a rare, novel sex-determiner, $m$, to increase in frequency from this equilibrium.
-%Numerical simulations are used to examine when an invading mutation goes to fixation.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Results}
-%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The model outlined above describes both ancestrally-XY and ancestrally-ZW sex-determination systems if we relabel the two sexes as being ancestrally `heterogametic' or ancestrally `homogametic'. 
-Without loss of generality, we primarily refer to the ancestrally heterogametic sex as male and the ancestrally homogametic sex as female.
-That is, we describe an ancestral XY sex-determination system but our model is equally applicable to an ancestral ZW sex-determination system (relabelling the ancestrally-heterogametic sex as female and the ancestrally-homogametic sex as male and switching the labels of males and females throughout).
-
-%\subsection*{Turnover between sex-determination systems}
-
-\subsubsection*{Generic invasion by a neo-Y or neo-W}
-
-The evolution of a new sex-determination system requires that a rare mutant allele at the novel sex-determining locus, $m$, increases in frequency when rare. 
-The spread of a rare mutant $m$ at the \textbf{M} locus is determined by the leading eigenvalue, $\lambda$, of the system of eight equations describing the frequency of eggs and sperm carrying the $m$ allele in the next generation (equations \ref{eq:recursions}).
-%, evaluated at the above equilibrium.
-%Thus, the system describing the change in frequency of the $m$ allele consists of eight recursion equations. 
-This system simplifies substantially in a number of cases of interest. 
-Dominant neo-Y (when $k=0$) or neo-W alleles (when $k=1$) are only found in male diploids (neo-Y) or female diploids (neo-W) such that their growth rate ultimately depends only on the change in frequency of $m$-bearing gametes produced by males or by females, respectively.
-Furthermore, if the $m$ allele is fully epistatically dominant over the ancestral sex-determining system, phenotypes are not affected by the genotype at the ancestral sex-determining region (\textbf{X} locus).
-Thus, the invasion of rare dominant neo-Y or neo-W alleles is determined by the largest eigenvalue that solves the quadratic, $\lambda^2+ b \lambda + c =0$ \textcolor{blue}{(see Appendix for a discussion of other roots - or Sally's proof!)}.
-Here, $b= - (\lambda_{mA} + \lambda_{ma})+(\chi_{mA} + \chi_{ma})$ and $c = (\lambda_{mA}-\chi_{mA}) (\lambda_{ma}-\chi_{ma}) -\chi_{mA} \chi_{ma}$, where $\lambda_{mi}$ is the multiplicative growth rate (which we will call the ``haplotypic growth rate'') of the neo-sex determination allele $m$ on background $i$ without accounting for loss due to recombination, and $\chi_{mi}$ is the rate at which mutant haplotypes on background $i\in\{A,a\}$ recombine onto the other \textbf{A} locus background in heterozygotes (see Table \ref{tab:haplotype_growth}).
-The $\lambda_{mi}$ and $\chi_{mi}$, and thus the spread of the mutant $m$ allele, depend on the frequency of alleles at the \textbf{A} and \textbf{X} loci in the ancestral population. 
-In the ancestral population, it is convenient to follow the frequency of the $A$ allele among female gametes (eggs), $p^\female_X$, and among X-bearing, $p^\male_X$, and among Y-bearing, $p^\male_Y$, male gametes (sperm/pollen).
-We also track the fraction of male gametes that are Y-bearing, $q$, which may deviate from $1/2$ due to meiotic drive in males. 
-We will consider only equilibrium frequencies of alleles, $\hat{p}^\Hermaphrodite_i$, and Y-bearing male gametes, $\hat{q}$, when calculating the eigenvalues.
-
-%\textcolor{red}{I now remove the zygotic sex ratio $\zeta$ from the mean fitnesses. The mean fitnesses will have to be adjusted in a corresponding way.}
-%
-%\textcolor{red}{CHECK: DO THE HAPLOID MEAN FITNESSES HAVE TO BE IN THE DENOMINATOR? i think so, based on definitions in table S.2 (mmo)}
-
-% as there are now two 2s in the lambdas of table 2. perhaps the 2 in the denominator is needed because the frequency of males sums to one as does the frequency of females?}
-
-\begin{threeparttable}[ht]
-\centering
-\smallskip
-%\caption{Parameters determining invasion (equation \ref{eq:charpoly_neoY}) for neo-Y or neo-W alleles}
-\caption{Parameters determining invasion of mutant neo-Y and neo-W alleles into an ancestrally XY system}
-\begin{tabular}{l}
-\hline\hline
-   \noalign{\vskip 0.5ex}
-   $m$ is a neo-Y ($k=0$) \\ [0.5ex] \hline \noalign{\vskip 1ex}
-  $\lambda_{YA} = \left( 2 \zeta \right)^{-1} \left[\hat{p}_X^\female w_{A}^{\female} w_{A}^{\male} w_{AA}^{\male} + (1-\hat{p}_X^\female) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} (1+\alpha_{\Delta}^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right) $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\lambda_{Ya} = \left( 2 \zeta \right)^{-1} \left[(1-\hat{p}_X^\female) w_{a}^{\female} w_{a}^{\male} w_{aa}^{\male} + \hat{p}_X^\female w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male}(1 - \alpha_{\Delta}^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\chi_{YA} = R \left( 2 \zeta \right)^{-1} \left[ (1-\hat{p}_X^\female) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} (1+\alpha_{\Delta}^{\male}) \right]/  \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right)   $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\chi_{Ya} = R \left( 2 \zeta \right)^{-1} \left[   \hat{p}_X^\female w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male} (1 - \alpha_\Delta^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right)  $\\ [1ex] \hline
-  \noalign{\vskip 0.5ex}
-  $m$ is a neo-W ($k=1$) \\ [0.5ex] \hline \noalign{\vskip 1ex}
-  $\lambda_{WA} = \left[ 2 (1 - \zeta) \right]^{-1} \left[ \bar{p}^{\male} w_{A}^{\male} w_{A}^{\female} w_{AA}^{\female}+(1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female}(1+\alpha_{\Delta}^{\female})\right]/ \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\lambda_{Wa} = \left[ 2 (1 - \zeta) \right]^{-1} \left[ (1-\bar{p}^{\male}) w_{a}^{\male} w_{a}^{\female} w_{aa}^{\female}+\bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female}(1-\alpha_{\Delta}^{\female})\right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\chi_{WA} = R \left[ 2 (1 - \zeta) \right]^{-1} \left[ (1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female} (1+\alpha_{\Delta}^{\female}) \right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \right)  $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\chi_{Wa} = R \left[ 2 (1 - \zeta) \right]^{-1} \left[ \bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female} (1-\alpha_{\Delta}^{\female}) \right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \right) $\\ [1ex]
-  \hline \hline 
-   \end{tabular}
-      \begin{tablenotes}
-      \scriptsize
-      \item $\bar{p}^{\male}=(1-\hat{q})\hat{p}_X^\male + \hat{q}\hat{p}_Y^\male$ is the average frequency of the $A$ allele among X- and Y-bearing male gametes.
-%      \item $R$ is the probability of recombination between loci \textbf{A} and \textbf{M}.
-      \item $\zeta$ is the zygotic sex ratio (fraction male)
-      \item $\bar{w}^\Hermaphrodite$ is the mean fitness of diploids of sex $\Hermaphrodite$, see Table \ref{tab:meanfitnesses}
-      \item $\bar{w}_H^\Hermaphrodite$ is the mean fitness of haploids from sex $\Hermaphrodite$, see Table \ref{tab:meanfitnesses}
-%      \item $\bar{w}_H^\female = p_X^\female w_A^\female + (1-p_X^\female) w_a^\female$ is the mean fitness of female gametes during gametic competition
-%      \item $\bar{w}_H^\male = \bar{p}^{\male} w_A^\male + (1-\bar{p}^{\male}) w_a^\male$ is the mean fitness of male gametes during gametic competition
-%       \item $\bar{w}^\female = \{ p_X^\female w_A^\female (1-q) p_X^\male w_A^\male w_{AA}^\female + (1 - p_X^\female) w_a^\female (1-q) p_X^\male w_A^\male w_{Aa}^\female + p_X^\female w_A^\female (1-q) (1 - p_X^\male) w_a^\male w_{Aa}^\female + (1-p_X^\female) w_a^\female (1-q) (1 - p_X^\male) w_a^\male w_{aa}^\female \} / \{ \bar{w}_H^\female \bar{w}_H^\male\}$ is the mean fitness of females during diploid competition
-%       \item $\bar{w}^\male = \{ p_X^\female w_A^\female q p_Y^\male w_A^\male w_{AA}^\male + (1 - p_X^\female) w_a^\female q p_Y^\male w_A^\male w_{Aa}^\male + p_X^\female w_A^\female q (1 - p_Y^\male) w_a^\male w_{Aa}^\male + (1-p_X^\female) w_a^\female q (1 - p_Y^\male) w_a^\male w_{aa}^\male \} / \{ \bar{w}_H^\male \bar{w}_H^\male\}$ is the mean fitness of males during diploid competition
-    \end{tablenotes}
-  \label{tab:haplotype_growth}
-\end{threeparttable}
-\\
-
-%We are particularly concerned with the conditions under which a rare neo-sex-determining allele increases in frequency, which occurs when the largest eigenvalue, $\lambda$, is greater than one. 
-%If one or both of $\lambda_{mA}$ and $\lambda_{ma}$ are greater than one, indicating that at least one haplotype increases in frequency faster than recombination breaks it apart, invasion will always occur ($\lambda>1$).
-%Otherwise, invasion requires
-%\begin{equation}
-%(\lambda_{mA}-1)(\lambda_{ma}-1) - \chi_{mA} \chi_{ma}<0.
-%\end{equation}
-
-We are particularly concerned with the conditions under which a rare neo-sex-determining allele increases in frequency, which occurs when the largest eigenvalue, $\lambda$, is greater than one. 
-%If the average change in frequency of the two haplotypes that carry the $m$ allele ($Am$ and $am$) is positive, invasion will always occur, i.e., if $(\lambda_{mA} + \lambda_{ma})/2 > 1$ then $\lambda > 1$.
-The leading eigenvalue solves $f(\lambda)=\lambda^2+b\lambda+c=0$ and the Perron-Frobenius theorem guarantees that the leading eigenvalue is positive, unique, and real.  
-Since $f(\lambda_{mA})$ and $f(\lambda_{ma})$ are of opposite signs, the leading eigenvalue must fall between these two quantities and is the larger of them when $R = 0$.  
-Consequently, if both $\lambda_{mA}$ and $\lambda_{ma}$ are greater than one, then the leading eigenvalue will always be greater than one, regardless of the linkage between the neo-sex determination factor and the selected locus ($R$).
-In particular, having $\lambda_{mA} >1$ and $\lambda_{ma}>1$ thus guarantees that an unlinked sex determining factor can invade ($R=1/2$).  
-Conversely, if both $\lambda_{mA}$ and $\lambda_{ma}$ are smaller than one, then invasion can never occur.  
-Finally, if only one of  $\lambda_{mA}$ and $\lambda_{ma}$ is greater than one, the new sex determining factor can always invade when tightly linked to the selected locus ($R$ near 0).  
-Furthermore, it can be shown that the leading eigenvalue declines with $R$, and invasion requires that $R$ is sufficiently small that the following condition holds: 
-\begin{equation}\label{eq:lambdasGen}
-%\frac{\chi_{mA}}{\lambda_{mA}-1}+\frac{\chi_{ma}}{\lambda_{ma}-1}>0.
-\chi_{ma}/\left(\lambda_{ma}-1\right) + \chi_{mA}/\left(\lambda_{mA}-1\right) < 1.
-\end{equation}
-\noindent 
-This condition may or may not be satisfied for the full range of locations of the new sex determining factor, including $R=1/2$, depending on the nature of selection.  
-Interpreting this condition, if we assume that only the $mA$ haplotype has a positive growth rate when $R=0$, $\lambda_{ma}<1<\lambda_{mA}$, the first term on the left-hand side of \eqref{eq:lambdasGen} is negative and invasion requires that the $mA$ haplotype growth rate ($\lambda_{mA}-1$) and the rate at which they are produced by recombination in $ma$ haplotypes ($\chi_{ma}$) are sufficiently large relative to the $ma$ haplotype rate of decline ($1-\lambda_{ma}$) and the rate of loss of $mA$ haplotypes due to recombination ($\chi_{mA}$).
-%In other words, invasion requires that the average growth rate of the two haplotypes, weighted by the rates they are created by recombination, is positive.
-%the number of recombinants from the fitter $mA$ haplotypes is larger than that of the less fit $ma$ haplotypes, relative to their growth rates.
-
-We can draw a number of key points about the invasion of neo-Y and neo-W mutations from Table \ref{tab:haplotype_growth}. 
-First, Fisherian sex ratio selection will favour the spread of a neo-Y if the ancestral zygotic sex ratio is biased towards females, $\zeta<1/2$ (i.e., the first factor of the $\lambda_{mi}$ is greater than one for a neo-Y and less than one for a neo-W).
-However, the spread of a neo-Y (neo-W) also depends on the male (female) fitness of associated alleles (see terms involving equilibrium allele frequencies, $\hat{p}$'s).
-Second, invasion by a neo-Y (neo-W) allele does not directly depend on the fitness of female (male) diploids. %(for a given set of equilibrium allele frequencies).
-This is because a dominant neo-Y (neo-W) is always found in males (females), and therefore the frequency of the neo-Y (neo-W) allele, $m$, only changes in males (females), Figure \ref{fig:model_outline}C,D.
-Finally, invasions by a neo-Y and a neo-W are qualitatively different.
-This is because a gamete with the neo-Y always pairs with a female gamete containing an X, and develop into males, Figure \ref{fig:model_outline}C.
-By contrast, a gamete with a neo-W can pair with an X or Y male gamete, developing into a female, Figure \ref{fig:model_outline}D.
-Consequently, neo-W bearing females obtain a differerent frequency of $A$ alleles from mating (when $\hat{p}_X^\male \neq \hat{p}_Y^\male$) compared to ancestral ($MM$) females.
-
-In order to explicitly determine the conditions under which a rare neo-sex-determining allele spreads, we must calculate the equilibrium frequency of the $A$ allele (i.e., $\hat{p}^\female_X$, $\hat{p}^\male_X$, and $\hat{p}^\male_Y$) and Y-bearing male gametes ($\hat{q}$) in the ancestral population.
-Since only the \textbf{A} locus experiences selection directly, any deterministic evolution requires that there is a polymorphism at the \textbf{A} locus. 
-Polymorphisms can be maintained by mutation-selection balance or transiently present during the spread of beneficial alleles.
-However, polymorphisms maintained by selection can maintain alleles at intermediate allele frequencies for longer periods.
-Here, we focus on polymorphisms maintained by selection, where the $A$ allele reaches a stable intermediate equilibrium frequency under the ancestral sex-determination system before the neo-sex-determining allele ($m$) arises.
-Such polymorphisms can be maintained by heterozygote advantage, sexually-antagonistic selection, ploidally-antagonistic selection, or a combination \citep{Immler:2012tl}.
-We can analytically calculate the allele frequency of the $A$ allele using two alternative simplifying assumptions: 
-(1) the \textbf{A} locus is within (or tightly linked to) the non-recombining region around the ancestral SDR ($r \approx 0$) or (2) selection is weak relative to recombination ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon<<1$).
-
-\subsubsection*{Tight linkage with the ancestral sex-determining region ($r \approx 0$)}
-
-The ancestral equilibrium allele frequencies and their stability conditions are given in the appendix.
-When there is complete linkage between the ancestral sex-determining region and the \textbf{A} locus ($r=0$), either the $A$ allele or the $a$ allele must be fixed on the Y. 
-% because selection on the Y is effectively haploid an incapably of maintaining a polymorphism in the absence of frequency dependent selection. 
-Because the labelling of alleles is arbitrary, we will assume that the $a$ locus is fixed on the Y ($p^\male_Y=0$), without loss of generality. 
-If there are two alleles maintained at the \textbf{A} locus, the X can either be fixed for the $A$ allele ($\hat{p}^\female_X=\hat{p}^\male_X=1$) or polymorphic (0<$\hat{p}^\female_X, \hat{p}^\male_X$<1).
-%However, because the X is present in both males and females, there are distinct selection pressures on X's in females and X's in males, which will always be paired with an $A$ allele from the Y.
-
-We find that a neo-Y can never invade an ancestral XY system that already has tight linkage with the locus under selection ($r=0$, for details see supplementary \textit{Mathematica} file). 
-When $R=0$, a neo-Y haplotype with the same allele as the ancestral Y is neutral ($\lambda_{Ya}=1$) and does not change in frequency.
-The other neo-Y haplotype will not spread ($\lambda_{YA}<1$) given that the initial equilibrium is stable. 
-Therefore, a neo-Y mutation cannot spread ($\lambda \leq 1$, regardless of $R$) in an ancestral XY system where selected loci are within or very near the non-recombining region around the SDR.
-In essence, through tight linkage with the \textbf{A} locus, the ancestral Y becomes strongly specialized on the allele that has the highest fitness across male haploid and diploid phases. 
-Given that the ancestral Y is at this equilibrium, it is not possible for a neo-Y to create males that have higher fitness than the ancestral Y.
-
-Neo-W alleles, on the other hand, can invade an ancestral XY system under some conditions (the full invasion conditions are given in the appendix; equations \ref{Binvasion} and \ref{Ainvasion}). 
-Counterintuitively, selection on loci within the non-recombining region of the SDR can favour the invasion of a less closely linked neo-W, whatever the form of selection maintaining a polymorphism (sexually-antagonistic selection, overdominance, ploidally-antagonistic selection, or some combination, Figures \ref{fig:SexAntagTighter}, \ref{fig:temporalOverdominance}, \ref{fig:regionPloidAntag}, and \ref{fig:SexAntagTighterMaleDrive}).
-The conditions become more restrictive, however, with increasing recombination ($R$) between the new sex determining region and the selected locus.  
-The invasion of completely unlinked neo-W alleles ($R = 1/2$) can occur with overdominance in males or with haploid selection but is not possible with only sexually-antagonistic selection if selection is directional in each diploid sex (see Supplementary \textit{Mathematica} file).
-To develop an intuition for how less closely linked neo-W alleles invade ($R>r$), we first focus on cases where there is no haploid selection and discuss the additional effect of haploid selection in the appendix.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Tighter linkage allows looser sex-linkage to evolve, even in absence of haploid selection
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-\centerline{\includegraphics[width=1.5\linewidth]{PositionPlot_SexAntagTighter}}
-\caption{
-Transitions between XY and ZW systems can occur even when the neo-SDR is less tightly linked to a locus under sexually-antagonistic selection (here, without haploid selection).
-In panel A, linkage is loose enough relative to selection that the analytical results assuming weak selection hold, and a neo-W can only invade when it is more tightly linked with the selected locus ($R<r$; shaded region).
-In panel B, linkage is tight enough relative to selection that the analytical results assuming weak selection do not hold, and a neo-W can invade even when it is less tightly linked with the selected locus ($r<R$; unshaded region).
-In panel C we vary the recombination rate between the neo-W and the selected locus ($R$) for a fixed recombination rate between the ancestral-SDR and the selected locus ($r=0.005$). 
-Coloured markers show recombination rates for which the temporal dynamics of invasion are plotted in the inset, demonstrating that neo-W alleles can fix (reach frequency $0.5$ among female gametes) if they are more (black) or less (red) closely linked to a locus experiencing sexually-antagonistic selection.
-A very loosely linked neo-W does not spread in this case (blue and green lines overlap and go to 0). 
-Fitness parameters are: $w_{AA}^\female = 1.05$, $w_{aa}^\male = 1.2$, $w_{aa}^\female = w_{AA}^\male = 0.85$, $w_{Aa}^\Hermaphrodite = 1$,  $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
-%\textcolor{red}{consider removing panel A, which is repeated in Figure 3.}
-%\textcolor{blue}{probably better to remove from panel 3, eh?}
-}
-\label{fig:SexAntagTighter}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-If we categorise the $a$ allele as being ancestrally `male-beneficial' via the fact that it is fixed on the Y, then $\lambda_{WA}>1$ indicates that the neo-W spreads when found with the ancestrally `female-beneficial' allele.
-Broadly, this is possible because the ancestral X chromosome is sometimes found in males and is therefore unable to perfectly specialise on the `female-beneficial' allele. 
-For example, when the $a$ allele is favoured on the ancestral X in males, a polymorphism of $A$ and $a$ alleles can be maintained on the X despite directional selection in favour of the $A$ allele in females ($s^\female>0$, $0<h^\female<1$), see outlined region in Figure \ref{fig:regionplots}A.
-When the $a$ allele is strongly favoured on X chromosomes in males ($w_{aa}^\male$ sufficiently large relative to $w_{Aa}^\male$), neo-W-$A$ haplotypes can spread ($\lambda_{WA}>1$, see grey region in Figure \ref{fig:regionplots}A) because they produce hgher fitness females ($AA$ or $Aa$ genotypes) and are unleashed from counterselection in males.
-
-When only one neo-W haplotype has a positive growth rate (see Figure \ref{fig:regionplots}), a neo-W can invade as long as equation \eqref{eq:lambdasGen} is satisfied, which may require that the recombination rate, $R$, is small enough.
-Nevertheless, because we assume here that $r$ is small, these results indicate that a more loosely linked sex-determining region ($r<R$) can spread.
-Therefore, tightly sex-linked loci that experience sexually-antagonistic selection can drive trans-GSD transitions in which the neo-SDR is less closely linked to the locus under selection (Figure \ref{fig:SexAntagTighter}).
-
-Given that the $a$ allele can be considered ancestrally `male-beneficial' because it is fixed on the Y, it is surprising that neo-W-$a$ haplotypes can sometimes be favoured by selection in females ($\lambda_{Wa}>1$).
-Again, this occurs because ancestral X's also experience selection in males, in which they will always be paired with a Y-$a$. 
-If there is overdominance in males, X-$A$ Y-$a$ males have high fitness and the $A$ allele is favoured by selection on the X in males. 
-Therefore, the X can be polymorphic or even fixed for the $A$ allele despite favouring the $a$ allele during selection in females \citep[e.g., see outlined region in Figure \ref{fig:regionplots}B and][]{Lloyd1977,Otto2014}.
-In such cases, neo-W-$a$ haplotypes can spread because they create more $Aa$ and $aa$ females when pairing with an X from males and because they bring Y-$a$ haplotypes into females, where it has higher fitness (Figure \ref{fig:model_outline}D).
-
-In some cases, both W-$A$ and W-$a$ haplotypes can spread, e.g., when $AA$ individuals have low fitness in females yet the $A$ is polymorphic or fixed on the X due to overdominance in males (Figure \ref{fig:regionplots}B and \ref{fig:regionplots}C).
-Both neo-W-$A$ and neo-W-$a$ haplotypes then produce fewer unfit $AA$ females.
-This is true for the neo-W-$A$ haplotype because it can pair with a Y-$a$ haplotype and still be female. 
-Wherever both haplotypes have positive growth rates, invasion by a neo-W is expected regardless of its linkage with the selected locus (i.e., even unlinked neo-W alleles can invade, see Figures \ref{fig:positionOverdominance} and \ref{fig:temporalOverdominance} for examples).
-
-Assuming that linkage is not tight, \citet{vanDoorn:2010hu} showed that invasion by a neo-W occurs under the same conditions as `pseudo-fixation' (at pseudo-fixation the neo-W reaches its maximum frequency among eggs, which is 1/2).
-An equivalent analysis is not possible where we assume that linkage is tight. 
-However, numerical simulations with tight linkage demonstrate that the neo-SDR does not necessarily reach pseudo-fixation, leading to the stable maintenance of a mixed sex-determining system, in which X, Y, Z, and W alleles all segregate (e.g., Figure \ref{fig:freqAll}B,C).
-
-%Haploid selection impacts the spread of neo-W haplotypes through its direct selective effect on females and their gametes, its indirect effect on the marginal fitness of alleles in females resulting from haploid selection in male gametes, and its effect on the sex ratio.
-%These impacts expand the scenarios under which neo-W haplotypes can spread.
-%For instance, overdominance is no longer required for neo-W-$a$ haplotypes to spread when there is haploid selection (e.g., when $a$ is female-beneficial, $A$ is male-beneficial, and meiotic drive in males favours $a$, Figure \ref{fig:regionMaleDrive}B).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Both neo-W haplotypes can spread, in the absence of haploid selection, when there is overdominance
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-%\centerline{\includegraphics[width=1.25\linewidth]{Region_plot_combined_Mike}}
-\centerline{\includegraphics[width=1.25\linewidth]{Region_plot_combined}}
-\caption{
-When the ancestral-XY locus is tightly linked to a locus under selection ($r=0$), one or both neo-W haplotypes can spread. 
-We vary the fitness of male homozygotes relative to heterozygotes ($w_{Aa}^\Hermaphrodite=1$) and only consider stable equilibria at which both \textbf{A} locus alleles are maintained and the $a$ allele is initially fixed on the Y, region outlined.
-Here, selection in females can favour the $A$ allele (panel A, $w_{aa}^\female=0.85$, $w_{AA}^\female=1.05$), favour the $a$ allele (panel B, $w_{aa}^\female=1.05$, $w_{AA}^\female=0.85$), or be overdominant (panel C, $w_{aa}^\female=w_{AA}^\female=0.6$).
-If $\lambda_{wA}$ or $\lambda_{wa}$ is greater than one, then a rare neo-W can spread for, at least, some values of $R>r$. 
-The parameter values marked with an asterisk correspond to the fitnesses used in Figure \ref{fig:SexAntagTighter}C. 
-Where both $\lambda_{wA}$ and $\lambda_{wa}$ are greater than one, a neo-W will spread when rare, regardless of linkage with the selected locus (for any $R$). 
-Figure \ref{fig:positionOverdominance} shows the dynamics using the parameters marked with a dagger. 
-Here, there is no haploid selection $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
-}
-\label{fig:regionplots}
-\end{figure}
-
-%Neo-W alleles, on the other hand, can invade an ancestral XY system under some conditions (given in detail in the appendix). 
-%%The full characteristic polynomials are given in the appendix (equations \ref{Binvasion} and \ref{Ainvasion}).
-%Briefly, neo-W-$A$ and/or neo-W-$a$ haplotypes can spread when rare in the absence of recombination ($\lambda_{ma}>1$ and/or $\lambda_{mA}>1$), depending on the ancestral sex ratio and allele frequencies.
-%Below we discuss the main forces determining the spread of these neo-W haplotypes and the impact of recombination for the overall success of the neo-W.
-%To simplify our discussion we first outline the potential effects of haploid selection and then consider diploid selection in its absence.
-
-%\textcolor{blue}{This explanation is clearer than the one I put in the appendix, if we drop it here, maybe we should try and re-word the corresponding part of the appendix using this paragraph}
-%Haploid selection impacts the spread of neo-W haplotypes in three ways.
-%Firstly, the zygotic sex ratio becomes male biased ($\zeta<1/2$) when the $a$ allele (which is fixed on the Y) is favoured during competition among male gametes or by meiotic drive in males. 
-%This facilitates the spread of a neo-W because neo-W alleles cause the zygotes that carry them to develop as the rarer, female, sex. 
-%Secondly, haploid selection in males affects the diploid genotypes of females by altering the allele frequencies in the male gametes that female gametes pair with.
-%For instance, because an epistatically dominant neo-W always causes its carrier to become female, it creates females who carry either $Y-a$ or $X$ genotypes from their father.
-%Thus, because when there is a polymorphism the $X$ carries some non-zero frequency of $A$, haploid selection in males impacts the diploid genotypes of females (e.g., creating more $Aa$ females when drive in males favours $Y-a$).
-%How this affects the spread of the neo-W then depends on diploid and haploid selection in females.
-%Thirdly, female drive and gamete competition directly select on neo-W haplotypes.
-%Drive for $A$ in females favours neo-W-$A$ haplotypes, at a cost to neo-W-$a$ haplotypes, and vice-versa when there is drive for $a$.
-%The impact of this drive depends on how often XX and neo-W females are heterozygous.
-%Competition among female gametes acts similarly, and depends on the frequency of $A$ on resident X chromosomes (e.g., competition among eggs has no affect on the initial spread of the neo-W-$A$ haplotype when $A$ is fixed on the X).
-%Because haploid selection in females favours one neo-W haplotype at the expense of the other, recombination off the favoured background becomes more detrimental as it becomes more favoured.
-Thus higher rates of recombination between the neo-W and the selected locus, $R$, can lead to smaller leading eigenvalues when there is haploid selection in females.
-
-%In the absence of haploid selection and with the $A$ allele is fixed on the X, it is possible for both neo-W haplotypes can spread ($\lambda_{mA}>1$ and $\lambda_{ma}>1$ in \ref{Binvasion}), and thus neo-W invasion can occur regardless of its linkage to the selected locus.
-%Invasion does not occur with purely sexually-antagonistic selection (i.e., $a$ directionally favoured in males and $A$ directionally favoured in females) because the X is then already as specialized as possible on the female sex.
-%However, if, for example, $AA$ individuals suffer a fitness cost in females, yet $A$ is fixed on the X due to strong overdominance in males, both neo-W-$A$ and neo-W-$a$ haplotypes spread because they produce fewer unfit $AA$ females and never experience counter-selection in males.
-%This is true even for the neo-W-$A$ haplotype because it can pair with a $Y-a$ haplotype and still be female. 
-%When both haplotypes can spread alone the rate of recombination between the neo-W and the selected locus, $R$, does cannot prevent invasion, and thus the system can evolve looser sex-linkage (e.g., the neo-W could arise on an autosome, $R=1/2$).
-%Even when only one haplotype can spread, invasion can still occur up to some positive rate of recombination, $R>0$ (as long as equation \ref{eq:lambdasGen} is satisfied). 
-%That looser sex-linkage can evolve is contrary to the conclusions of \cite{vanDoorn:2010hu}, who did not explicitly calculate invasion fitness under ancestrally tight sex-linkage.
-\textcolor{blue}{or, just didn't calculate the equilibria (A) an (B).}
-%Similar scenarios have been shown to select for a modifier that increases recombination between the sexes \citep[green regions of Figure 2 in][]{Otto2014}.
-%\textcolor{blue}{n.b., the recombination regions are only subsets mostly because you also generate a really unfit Y haplotype through recombination. Probably not worth mentioning.}
-%
-%In the absence of haploid selection it is also possible for a neo-W to invade when there is a stable polymorphism at the $\mathbf{A}$ locus on X chromosomes.
-%For example, overdominance in males and strong directional selection for $a$ in females creates a scenario that favours the spread of both neo-W haplotypes at equilibrium ($\lambda_{mA}>1$ and $\lambda_{ma}>1$ in \ref{Ainvasion}), as both haplotypes bring more $a$ alleles into females and never experience counter-selection in males.
-%Thus, as in the case of the $A$ being fixed on the X, looser sex-linkage can evolve with a polymorphic X (i.e., $\lambda>1$ with $R>0$) and this is expected under the same scenarios that select for a modifier that increases recombination between the sex chromosomes \citep[blue regions of Figure 2 in][]{Otto2014}.
-
-\subsubsection*{Loose linkage with the ancestral sex-determining region}
-
-%\textcolor{blue}{As with the discussion, this section might need some editing for (1) unclearly describing looser linkage never evolving without haploid selection, which we now show is possible above and (2) going on about sex ratio selection too much - this should be changed to something along the lines of  ``male biased zygotic sex ratios ($\zeta-1/2$) are of the order of $\epsilon^2$.
-Therefore Fisherian sex ratio selection directly favours neo-Ws by a similar magnitude.
-%Perhaps surprisingly, neo-Ws can be favoured to the same degree by haploid selection in females when female haploid selection favours the alleles that tend to be carried by the neo-W.
-%Thus XY to ZW is the same as ZW to XY even though sex ratio biases only exist in one case, given the assumptions made in this section.
-%''
-%}
-
-%weak selection
-%We are particularly concerned with whether or not a rare neo-sex-determining allele increases in frequency, which occurs when the largest eigenvalue, $\lambda$, is greater than one. 
-%Here, we explicitly determine the conditions under which invasion occurs by assuming that the $A$ allele reaches an equilibrium frequency under the ancestral sex-determination system before the neo-sex-determination system ($m$) arises.
-%The equilibrium frequency of $A$ on different ancestral backgrounds ($\hat{p}^\male_Y$, $\hat{p}^\male_X$, and $\hat{p}^\female_X$) is given by equations \eqref{eq:pAve} and \eqref{eq:freq_diffs} where we assume selection and meiotic drive are weak relative to recombination ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon$).
-Assuming that selection is weak ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon<<1$) and thus implicitly assuming that all recombination rates ($r$, $R$ and $\rho$) are large relative to selection, we denote the leading eigenvalues describing the invasion of a neo-Y ($k=0$) and a neo-W ($k=1$) into an ancestrally XY system by $\lambda_{Y',XY}$ and $\lambda_{W',XY}$, respectively.
-To leading order in selection, these are:
-
-\begin{equation}
-\lambda_{Y',XY} =1+ \frac{1}{4}V_{A}S_{A}^2\frac{ \left( r-R \right) }{r R}+O\left(\epsilon^3 \right) 
-\label{eq:lambda_neoY}
-\end{equation}
-
-\noindent 
-and
-
-\begin{equation}
-\lambda_{W',XY} =\lambda_{Y',XY}+\left(2\alpha_{\Delta}^\male-2\alpha_{\Delta}^\female+t^\male-t^\female \right) \left( \hat{p}^\male_Y-\hat{p}^\male_X \right)/2
-+O\left(\epsilon^3 \right) \\
-\label{eq:lambda_neoW}
-\end{equation}
-
-\noindent
-where $V_{A}=\bar{p}(1-\bar{p})$ is the variance in the equilibrium frequency of $A$ and $S_{A}=(D^\male +\alpha_{\Delta}^\male+t^\male) - (D^\female+\alpha_{\Delta}^\female+t^\female)$ describes sex differences in selection for the $A$ versus $a$ allele across diploid selection, meiosis, and gametic competition.
-The diploid selection term, $D^\Hermaphrodite=\big{[} \bar{p}s^\Hermaphrodite+(1-\bar{p})h^\Hermaphrodite s^\Hermaphrodite\big{]} -\big{[} \bar{p}h^\Hermaphrodite s^\Hermaphrodite+(1-\bar{p}) \big{]}$, is the difference in fitness between $A$ and $a$ alleles in diploids of sex $\Hermaphrodite \in \{\female,\male\}$, where $\bar{p}$ is the leading-order probability of mating with an $A$-bearing gamete from the opposite sex (equation \ref{eq:pAve}).
-The difference in $A$-allele-frequency among Y-bearing sperm versus X-bearing sperm is given by $\hat{p}^\male_Y-\hat{p}^\male_X=V_{A}\big{(}D^\male - D^\female+\alpha_{\Delta}^\male-\alpha_{\Delta}^\female+t^\male-t^\female\big{)}(1-2r)/(2r)$.
-
-The neo-sex-determining allele, $m$, will spread if $\lambda_{m,XY}>1$. 
-Equation \eqref{eq:lambda_neoY} demonstrates that, under weak selection, a neo-Y will invade an XY system if and only if it is more closely linked to the selected locus than the ancestral sex-determining region (i.e., if $R<r$; note that $V_{A}S_{A}^2$ is strictly positive as long as \textbf{A} is polymorphic).
-This echoes our tight linkage results above where a neo-Y could never invade if $r\approx0$.
-It is also consistent with the results of \citet{vanDoorn:2007eu}, who considered diploid selection only and also found that cis-GSD transitions (XY to XY or ZW to ZW) can only occur when the neo-sex-determining locus is more closely linked to a locus under sexually-antagonistic selection.
-%Because tighter linkage between the sex-determining region and a selected locus evolves during these transitions, stronger associations between selected alleles and diploid sexes can build up by selection (e.g., between male-beneficial alleles and the male-determining allele, Y).%, increasing diploid mean fitness (Figure \ref{fig:Combination_MeanFit}).
-
-With weak selection and no haploid selection ($t^\Hermaphrodite=\alpha^\Hermaphrodite_{\Delta}=0$), the spread of a neo-W is equivalent to the spread of a neo-Y ($\lambda_{W',XY}=\lambda_{Y',XY}$), such that trans-GSD transitions (XY to ZW or ZW to XY) can also occur only if the neo-sex-determining region is more closely linked to a locus under selection ($R<r$), as found by \citet{vanDoorn:2010hu}.
-With haploid selection, however, the additional term in equation \eqref{eq:lambda_neoW} can be positive, which can allow, for example, neo-W invasion ($\lambda_{W',XY}>1$) even when the neo-sex-determining region is less closely linked to the selected locus ($R>r$).
-%These transitions are unusual because, when $R>r$, associations that selection has built up between alleles more favourable in one sex and alleles that determine sex will be weakened. 
-%Mean diploid fitness therefore decreases during heterogametic transitions that create looser sex-linkage (Figure \ref{fig:Combination_MeanFit}B,D).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%A neo-W can invade an XY system under a large number of selective regimes
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-\includegraphics[width=\linewidth]{PositionPlot}
-\caption{
-% A neo-W can invade an XY system under a large number of selective regimes.
-%In panel A, there is no haploid selection ($t^\Hermaphrodite = \alpha^\Hermaphrodite_{\Delta} = 0$) and selection in diploids is sexually antagonistic ($s^\male = -s^\female = 1/10$, $h^\male = 1-h^\female = 3/10$), in which case the neo-sex-determining allele can only invade if it is more closely linked to the selected locus ($R<r$, gray region; but see Figure \ref{fig:SexAntagTighter}B for the case of very tight linkage).
-Ploidally-antagonistic selection allows a less tightly linked neo-W to invade.
-In panel A, male drive ($\alpha^\male_{\Delta} = -1/20$, $t^\Hermaphrodite = \alpha^\female_{\Delta} = 0$) opposes selection in diploids (no sex-differences: $s^\Hermaphrodite = 1/10$, $h^\Hermaphrodite = 7/10$), in which case the neo-sex-determining allele can invade regardless of linkage.
-In panel B, gametic competition in males ($t^\male = -1/10$, $t^\female = \alpha^\Hermaphrodite_{\Delta} = 0$) opposes selection in diploids (sex-differences: $s^\male = 3/20$, $s^\female = 1/20$, $h^\Hermaphrodite = 7/10$), in which case the neo-sex-determining allele can once again invade regardless of linkage.
-We use Haldane's map function \citep[Equation 3 in ][]{Haldane1919} to convert from map distance (centiMorgans, cM) to the probability of recombination (an odd number of cross-over events).   
-%\textcolor{red}{Check the mismatch between red and black lines here: probably because of adding or subtracting from 1. }
-%\textcolor{blue}{Can remove the mismatch by flipping the fitnesses between males and females (again).
-That is, if $M_{AA}$ is the fitness of $AA$ male diploids in an ancestral XY system, then $M_{AA}$ is the fitness of $AA$ female diploids in an ancestral ZW system.
-I think this makes sense in A, where we don't really want a difference between the red and black curves, but this makes less sense in B and C where we want to restrict haploid selection to males regardless of the ancestral system.
-We could just not flip the haploid fitnesses, but then does it make sense to flip the diploid fitnesses?}
-}
-\label{fig:Combination_Centimorgans}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Equation \eqref{eq:lambda_neoW} shows that, with weak selection, neo-W alleles can invade an XY system for a large number of selective regimes. 
-To clarify the parameter space under which $\lambda_{W',XY}>1$, we consider several special cases. 
-Firstly, if the \textbf{A} locus is unlinked to the ancestral sex-determining region ($r=1/2$), a more closely linked neo-W ($R<1/2$) can always invade because there is no ancestral association between $A$ alleles and sex chromosomes in males, $\left( \hat{p}^\male_Y-\hat{p}^\male_X \right)=0$, see equation \eqref{eq:freq_diffs}.
-The second term in equation \eqref{eq:lambda_neoW} therefore disappears and invasion depends only on the sign of $(r-R)$, as in the case of the neo-Y. 
-Indeed, invasion typically occurs when the neo-W is more closely linked to the selected locus than the ancestral sex-determining region (Figure \ref{fig:Combination_Centimorgans}).
-
-Secondly, we can simplify the discussion of cases where invasion occurs despite looser sex-linkage, $R>r$, by focusing on the special case where $R=1/2$ and $r<1/2$ (e.g., the selected locus is on the ancestral sex chromosome and the novel sex-determining locus arises on an autosome).
-In Table \ref{tab:specialcases} we give the conditions where invasion occurs when we further assume that haploid selection only occurs in one sex (e.g., during male meiosis only) and dominance coefficients are equal in the two sexes, $h^\female=h^\male$.
-When there is no gametic competition and meiotic drive is in one sex only, an unlinked neo-W can invade as long as the same allele is favoured during diploid selection in males and females ($s^\female s^\male>0$, see Figure \ref{fig:Combination_Centimorgans}A and Figure \ref{fig:SexRatioBad}B).
-%, which is 50\% of the parameter space.
-When there is no meiotic drive and gametic competition occurs in one sex only, an unlinked neo-W can invade as long as the same allele is favoured in male and female diploid selection and there are sex differences in selection of one type (e.g., $s^\female(s^\male-s^\female)>0$, see Figure \ref{fig:Combination_Centimorgans}B).
-%, which is 25\% of the parameter space.
-These special cases indicate that neo-W invasion occurs for a relatively large fraction of the parameter space, even if the neo-W uncouples the sex-determining locus from a locus under selection.
-
-\begin{table}[ht]
-\centering
-\smallskip
-\caption{Invasion conditions for unlinked neo-W ($R=1/2$, $r<1/2$) into ancestral XY with one form of haploid selection}
-\begin{tabular}{l l c }
-\hline\hline
-Scenario &  Assumptions & neo-W spreads ($\lambda_{W',XY}>1$) if \\ [0.5ex] \hline
-%  $r=1/2$, $R<1/2$ & Always \\ [0.5ex] \hline
-%  $r<1/2$, $R=1/2$ &  \\ [0.5ex] \hline
-\noalign{\vskip 1mm}
-  male drive only & $h^\male=h^\female$, $t^\female=t^\male=\alpha^\female_{\Delta}=0$ & $s^\female s^\male>0$ \\ [0.5ex]
- female drive only & $h^\male=h^\female$, $t^\female=t^\male=\alpha^\male_{\Delta}=0$ & $s^\female s^\male>0$ \\ [0.5ex]
- sperm competition only &  $h^\male=h^\female$, $t^\female=\alpha^\female_{\Delta}=\alpha^\male_{\Delta}=0$ & $s^\female(s^\male-s^\female)>0$ \\ [0.5ex]
-  egg competition only & $h^\male=h^\female$, $t^\male=\alpha^\female_{\Delta}=\alpha^\male_{\Delta}=0$ & $s^\male(s^\female-s^\male)>0$ \\ [0.5ex]
-  \hline \hline
-  \label{tab:specialcases}
- \end{tabular}
-\end{table}
-
-%If we further assume equal dominance ($h^\female=h^\male$) and that haploid selection only occurs during male meiosis ($t^\female=t^\male=\alpha^\female_{\Delta}=0$), or female meiosis ($t^\female=t^\male=\alpha^\male_{\Delta}=0$), neo-W invasion occurs when $s^\female s^\male>0$, Figure \ref{fig:Combination_Centimorgans}B.
-%That is, when the same allele is favoured by selection in both males and females (it may remain polymorphic via counter selection during meiotic drive).
-
-%\textcolor{red}{It may seem counterintuitive that, if the $A$ allele is more common on the ancestral-Y than the ancestral-X, and only favoured during haploid selection in males}
-
-%\textcolor{red}{although our predictions also perform well when recombination is small, see figure \ref{fig:WinvasionLowR}.
-We would have to add a line showing what invasion fitness the weak selection approximation would give and add dots to this figure (dots that are currently connected by a line), as in (vD\&K, 2010) }
-
-%Sex ratios
-%Previous research suggests that when the ancestral sex-determining locus is linked to a locus that experiences haploid selection (e.g., meiotic drive), a new, unlinked sex-determining locus invades in order to restore equal sex ratios \citep{Kozielska:2010vm}.
-%Our model provides a good opportunity to determine whether Fisherian sex ratio selection provides a useful explanation for the evolution of new sex-determining loci in other contexts. 
-%Consider, for example, the case where the \textbf{A} locus is linked to the ancestral-SDR ($r<1/2$) and experiences meiotic drive in males only (e.g., during spermatogenesis but not during oogenesis, $\alpha^\male \neq 1/2$, $\alpha^\female=1/2$).
-%We will also disregard gametic competition ($t^\female=t^\male=0$) such that zygotic sex ratios are only biased by meiotic drive in males. 
-%In this case, the zygotic sex ratio can be initially biased only if the ancestral sex-determining system is XY (Figure \ref{fig:Combination_Turnover}B). 
-%If the ancestral sex-determining system is ZW, the zygotic sex ratio will be 1:1 because diploid sex is determined by the proportion of Z-bearing versus W-bearing eggs and meiosis in females is fair (Figure \ref{fig:Combination_Turnover}D).
-%Thus, if the zygotic sex ratio is crucial to the evolution of new genetic sex-determining systems, invasion into ZW and XY systems will be distinct. 
-%However, under weak selection we find that invasion by a homogametic neo-sex-determining allele (XY to XY or ZW to ZW) or by a heterogametic neo-sex-determining allele (XY to ZW or ZW to XY) occur under the same conditions.
-%That is, we can show that $\lambda_{Y',XY}=\lambda_{W',ZW}$ and $\lambda_{Y',ZW}=\lambda_{W',XY}$ (at least up to order $\epsilon^3$; for a numerical example, compare Figure \ref{fig:Combination_Turnover}A,B to Figure \ref{fig:Combination_Turnover}C,D).
-%As it turns out, under weak selection the strength of sex ratio selection favouring, say, the invasion of a neo-W in an XY system is the same as the strength of meiotic drive favouring the invasion of a neo-Y in a ZW system.
-%Even when these forces are not exactly the same (e.g., under tight sex-linkage; compare black and red curves near -25 and 25cM in Figure \ref{fig:Combination_Centimorgans}), it is important to remember that sex ratio selection is only one of many potential selective forces acting to determine transitions between sex-determining systems.
-%It is even possible for the other selective forces to overwhelm sex ratio selection and favour sex-determination transitions that create sex ratio biases (Figure \ref{fig:Combination_Turnover}A,C).
-
-Previous research suggests that when the ancestral sex-determining locus is linked to a locus that experiences haploid selection (e.g., meiotic drive), a new, unlinked sex-determining locus invades in order to restore equal sex ratios \citep{Kozielska:2010vm}.
-Consider, for example, the case where the \textbf{A} locus is linked to the ancestral-SDR ($r<1/2$) and experiences meiotic drive in males only ($\alpha^\male_\Delta \neq 0$, $\alpha^\female_\Delta=0$), without gametic competition ($t^\female=t^\male=0$).
-In this case, the zygotic sex ratio can be initially biased only if the ancestral sex-determining system is XY (Figure \ref{fig:model_outline}B and Figure \ref{fig:SexRatioBad}B). 
-%If the ancxestral sex-determining system is ZW, the zygotic sex ratio will be 1:1 because diploid sex is determined by the proportion of Z-bearing versus W-bearing eggs and meiosis in females is fair (Figure \ref{fig:Combination_Turnover}D).
-If Fisherian sex ratio selection were dominant, we would expect a difference in the potential for XY to ZW and ZW to XY transitions. 
-%However, to leading order with selection weak relative to recombination, we find that sex ratio selection favours the spread of a neo-W by an amount equl to the spread of a neo-Y into a ZW system (relabeling XY as the heterogametic sex and reversing the labels of males and females in Table \ref{tab:specialcases})
-%However, to leading order with selection weak relative to recombination, we find that sex ratio selection favours the spread of a neo-W (through the first terms in table \ref{tab:haplotype_growth}) by an amount that is equal in magnitude to the fitness effects of alleles associated with new sex-determining alleles (second terms in table \ref{tab:haplotype_growth}).
-However, invasion by a neo-W into an XY system and invasion by a neo-Y into a ZW system occur under the same conditions ($\lambda_{Y',XY}=\lambda_{W',ZW}$ and $\lambda_{Y',ZW}=\lambda_{W',XY}$, at least to order $\epsilon^2$).
-For example, in Figure \ref{fig:SexRatioBad}A neo-W alleles invade an ancestral-XY system where females are initially rare.
-However, Figure \ref{fig:SexRatioBad}B shows that a neo-Y can invade an ancestral-ZW system under the same conditions. 
-As a consequence, whenever $R<1/2$, the neo-Y becomes associated with the male meiotic drive allele such that the zygotic sex ratio actually evolves to become biased towards males.
-
-%As selection becomes stronger (or linkage becomes tighter), this symmetry between sex ratio selection and haploid selection is lost, causing differences in the strength of selection favouring the two heterogametic transitions (compare red to black near -25cM and 25 cM in Figure \ref{fig:Combination_Centimorgans}).
-\textcolor{red}{normalise fitness in sexually antagonistic case}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Sex ratio selection is not a good predictor of neo-W invasion into an XY system
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-\includegraphics[width=\linewidth]{Temporal_SR}
-\caption{
-Fisherian sex ratio selection alone is not a good predictor of turnover between sex-determining systems.
-In this figure, selection is ploidally antagonistic with haploid selection favouring the $a$ allele during male meiosis.
-In panel A, male drive in an ancestral ZW system has no affect on the zygotic sex ratio (see Figure \ref{fig:model_outline}B) yet a neo-Y can invade and replace the ancestral sex-determination system (inset shows neo-Y frequency among male gametes, the ancestral W also goes to fixation during this transition).
-When $R<1/2$, the neo-Y becomes associated with the allele favoured by drive, causing the zygotic sex ratio to become biased, hence the frequency of neo-Y among male gametes can be higher than $0.5$ (inset).
-In panel B, male drive in an ancestral XY system causes a male bias, allowing a neo-W to invade and replace the ancestral sex-determination system (inset shows neo-W frequency among female gametes, the ancestral Y also goes to fixation), which balances the zygotic sex ratio.
-Parameters:  $s^\female =s^\male = 0.2$, $h^\female = h^\male = 0.7$, $t^\female = t^\male = \alpha^\female_\Delta = 0$, $\alpha^\male_\Delta = -0.1$, $r=0.02$.
-}
-\label{fig:SexRatioBad}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Why can new sex-determining regions invade when more loosely linked to selected loci ($R>r$)?  
-Consider first the case where both loci are linked to the selected locus ($r<R<1/2$). 
-In an XY system, haploid selection in males can facilitate the spread of a neo-W because the zygotic sex ratio is ancestrally biased and the W helps to equalize the sex ratio (Figure \ref{fig:SexRatioBad}A).
-A new sex determining region can also, however, benefit from becoming more associated with drive.  
-For example in a ZW system with the same selection regime (haploid selection in males), a neo-Y can spread despite the fact that the zygotic sex is initially even; in this case, the neo-Y spreads because it is often found in males and can, if it carries the driven allele $a$, benefit from haploid selection (Figure \ref{fig:SexRatioBad}B).
-While equalizing the sex ratio and benefiting from drive are two primary reasons why haploid selection spurs sex chromosome transitions, more complex situations also arise.  
-For example with $R=1/2$ in Figure \ref{fig:SexRatioBad}B (green curve), the neo-Y spreads despite the fact that it cannot benefit from drive because free recombination moves it randomly between driven and non-driven backgrounds.
-Nevertheless, the unlinked neo-Y can spread because diploids bearing it more often carry the non-driven allele $A$ found at high frequency on the W background, which has higher average diploid fitness to balance the haploid advantage of the $a$ allele at equilibrium.
-
-%The green curves in Figure \ref{fig:SexRatioBad} show transitions between male and female heterogametey even though the new sex-determining region is unlinked to a locus that experiences haploid and diploid selection.
-%We use these green curves to discuss why trans-GSD transitions can occur when $R=1/2$ and $r<1/2$, as in Table \ref{tab:specialcases}.
-%In Figure \ref{fig:SexRatioBad}B, an unlinked neo-W can spread because the zygotic sex ratio is ancestrally male biased. 
-%In Figure \ref{fig:SexRatioBad}A, an unlinked neo-Y spreads despite the fact that the ancestral zygotic sex ratio is even. 
-%In this case, the male meiotic drive allele, $a$, is initially more common among ancestral-Z-bearing eggs than ancestral-W-bearing eggs because the Z is found in males more often than the W ($\hat{p}_{W}^\female-\hat{p}_{Z}^\female>0$, equation \ref{eq:freq_diffs}).
-%Polymorphism at the \textbf{A} locus is maintained by counter-selection against the $a$ allele in diploids and therefore ancestral-ZZ males have generally low diploid fitness. 
-%The neo-Y spreads because it produces males with high diploid fitness through matings with ancestral-W-bearing female gametes, which are more likely to carry the $A$ allele ($\hat{p}_{W}^\female-\hat{p}_{Z}^\female>0$).
-%A freely recombining neo-Y ($R=1/2$) is equally likely to be segregate with the $A$ or $a$ allele.
-%Therefore, the neo-Y is unaffected by male meiotic drive against the $A$ alleles that it introduces into males. 
-%Thus, a key factor in explaining why trans-GSD transitions can occur when $R>r$ is that the neo-SDR determines sex in the diploid phase but recombination occurs before any subsequent haploid selection.
-
-\subsubsection*{Environmental sex determination}
-
-We next consider the case where the new sex-determining mutation, $m$, causes sex to be determined probabilistically or by heterogeneous environmental conditions (environmental sex determination, ESD), with individuals carrying allele $m$ developing as females with probability $k$.
-Here, we do not assume that the environmental conditions that determine sex also differentially affect the fitness of males versus females. 
-Such correlations can favour environmental sex-determination systems that allow each sex to be produced in the environment in which it has highest fitness; in the absence of these correlations, previous theory would predict that ESD is favoured when it produces more equal sex ratios than the ancestral system \citep[see reviews by][]{Charnov:1982wg,Bull:1983vi,West:2009we}.
-%(e.g., maternal condition, mate quality, age, or host size)
-
-The characteristic polynomial determining the eigenvalues (equations \ref{eq:recursions}) does not factor for ESD mutants as it does for $k=0$ or $k=1$. 
-We therefore focus on weak selection here. 
-Assuming weak selection, the spread of the new sex-determining region is given by
-
-\begin{equation}
-\begin{split}
-\lambda_{ESD',XY} =& 1 + \frac{(1-2k)^2}{4}V_{A}{S_{A}}^2\frac{r-R}{r R} \\
-&+\frac{k(\hat{p}^\male_Y-\hat{p}^\male_X)}{2}\left[ k \left(2\alpha_{\Delta}^\male-2\alpha_{\Delta}^\female+t^\male-t^\female \right) -2(1-k)S_{A}\right]+O\left(\epsilon^3\right),
-\end{split}
-\label{eq:lambda_ESD_k}
-\end{equation}
-
-\noindent
-which reduces to $\lambda_{Y',XY}$ when $k=0$ and $\lambda_{W',XY}$ when $k=1$.
-
-%Under Fisherian sex ratio selection, autosomal modifiers favour equal investment in male and female offspring, i.e., a 1:1 sex ratio \citep{Fisher:1930wy,Charnov:1982wg,West:2009we}. 
-%A novel environmental sex-determiner that causes half of its carriers to become female and half to become male ($k=1/2$) will be in males half of the time and in females half of the time (like an autosome).
-%In addition, these novel sex-determination alleles equalize the sex ratio and therefore one might expect them to be favoured by Fisherian sex ratio selection when the resident sex ratio is biased.
-%However, assuming weak selection, we find that the growth rate of a rare, dominant offspring-controlled neo-ESD allele that produces males or females with equal probability ($k=1/2$) is
-Of particular interest are ESD mutations that cause half of their carriers to develop as females and half as males ($k=1/2$, creating equal sex ratios), the spread of which is given by
-\begin{equation}
-\lambda_{ESD',XY} =1+ \frac{1}{2}\frac{(\lambda_{Y',XY\rvert R=1/2}-1) + (\lambda_{W',XY\rvert R=1/2}-1)}{2} + O\left(\epsilon^3\right),
-%V_A \frac{r}{1-2r}  \frac{s_{f} \left( s^\male - 3 s^\female\right) }{8 \left( s_{f} + s_{m} \right)^2} t_{m}^2.
-\label{eq:lambda_ESD}
-\end{equation}
-\noindent
-where $\lambda_{Y',XY\rvert R=1/2}$ and $\lambda_{W',XY\rvert R=1/2}$ represent $\lambda_{Y',XY}$ and $\lambda_{W',XY}$ when evaluated at $R=1/2$ (Equations \ref{eq:lambda_neoY} and \ref{eq:lambda_neoW}).
-That is, recombination between the selected locus and the novel sex-determining locus, $R$, doesn't enter into the $k=1/2$ results.
-This is because sex is essentially randomized each generation, %as if the novel sex-determiner were on an unlinked site that half the time acts as a neo-$W$ and half the time as a neo-$Y$.
-preventing associations from building up between allele $A$ and sex. 
-Equation \eqref{eq:lambda_ESD} shows that the neo-ESD gets half of the fitness of a feminizing mutation (neo-$W$) and half of the fitness of a masculinizing mutation (neo-$Y$), but only has an effect one half of the time (the other half of the time it produces the same sex as the ancestral system would have).
-As discussed above, $\lambda_{Y',XY\rvert R=1/2}$ is necessarily less than one, but $\lambda_{W',XY\rvert R=1/2}$ can be greater than one if there is haploid selection.
-That is, when there is haploid selection, ESD mutations can invade an ancestrally-XY system because they generate females that are either rare or have high fitness, in the same manner as a neo-W.
-
-%An important result from equation \eqref{eq:lambda_ESD} is that ESD can invade if there is haploid selection. 
-%When evaluated at $R=1/2$, $\lambda_{Y',XY}$ is necessarily less than one, but $\lambda_{W',XY}$ can be greater than one if there is haploid selection, as discussed above. 
-%Previous studies where ESD is favoured have typically assumed that environmental conditions (e.g., maternal condition, mate quality, age, or host size) can differentially affect the fitness of males versus females such that ESD invades because it allows sex determination to depend on the environment \citep[reviewed in][]{Charnov:1982wg,Bull:1983vi,West:2009we}.
-%Here, ESD mutations can spread because they generate females that are either rare or have high fitness, in the same manner as a neo-W.
-
-Significantly, equation \eqref{eq:lambda_ESD} is the same whether ESD is invading an ancestrally XY or ZW system (because $\lambda_{Y',XY} = \lambda_{W',ZW}$ and $\lambda_{W',XY} = \lambda_{Y',ZW}$).
-Thus, Fisherian sex ratio selection alone does not explain the invasion of ESD under weak selection because the sex ratio is only biased by male haploid selection when the ancestral sex-determination system is XY.
-Specifically, with male haploid selection, the neo-ESD is equally likely to invade when it equalizes the zygotic sex ratio (through $\lambda_{W',XY}$) and when it doesn't (through $\lambda_{Y',ZW}$). 
-%This is again because haploid selection can facilitate the turnover of sex chromosomes either through sex ratio biases or through associations between the new sex determining region with selected alleles.
-%With weak selection, these two forces are nearly equal in strength. 
-In addition, we note that ESD may not invade, even if the sex ratio is initially biased (e.g., with drive in males only, $r<1/2$, $h^\female=h^\male$, and $s^\female s^\male<0$, then $\lambda_{W',XY}<1$, see Table \ref{tab:specialcases}).
-We conclude that, as with neo-W and neo-Y loci, associations with selected loci mean that the evolution of neo-ESD systems is not straightforwardly predicted by selection to balance the zygotic sex ratio when haploid selection is present.
-
-%Depends 50\% on its fitness relative to non-mutant males and 50\% on its fitness relative to non-mutant females.
-
-%\subsubsection*{Maternally-controlled neo-ESD}
-
-%Fisherian sex ratio selection is sometimes considered in terms of balancing parental investment in male versus female offspring \citep{Charnov:1982wg}.
-%In addition, under environmental sex-determination, the proportion of males/females is sometimes controlled by the mother (e.g., the proportion of eggs laid in warm versus cold environments). 
-%We therefore also considered the invasion of a neo-sex-determining allele ($m$) in a model in which mothers that have at least one $m$ allele produce daughters with probability $k$. 
-%As with offspring-controlled ESD, for all $k\in\{0,1/2,1\}$, we find that invasion into an ancestral XY system is the same as invasion into an ancestrally ZW system (at least up to order $\epsilon^3$, assuming weak selection), implying that transitions between genetic sex-determination and maternally controlled environmental sex-determination are not driven by Fisherian sex ratio selection alone.
-%\textcolor{red}{(Maternal ESD analysis still lacks meiotic drive -- Mathematica can't seem to deal with the added complexity.)}
-
-%One might think that when the sex of zygotes is under the control of mothers, there would be strong selection to balance the sex ratio among zygotes. 
-%However, we find that, with no meiotic drive and weak selection, the invasion fitness of a dominant, maternally controlled sex-determiner that produces proportion $k$ daughters can be written
-%\begin{equation}
-%\lambda_{k} = 1 + V_A S_A C_k + O\left(\epsilon^3\right),
-%\end{equation}
-%where
-%\begin{equation}
-%V_A = \frac{- \left[ t_m + h (s_{f}+s_{m}) \right] \left[ t_m + (1-h) (s_{f}+s_{m}) \right]}{(1-2h)^2(s_{f}+s_{m})^2}
-%\end{equation}
-%is the variance in $A$ ($V_A>0$ when the polymorphic resident equilibrium is stable), 
-%with $h$ the dominance coefficient (equal in both sexes), 
-%$C_k$ is a term that depends on $k$.
-%
-%%k=0
-%\begin{equation}
-%C_0 = big \; ugly \; term
-%\end{equation}
-%
-%%k=1
-%\begin{equation}
-%C_1 = \frac{\left[ (2r(1-R)-R) s^\female + (1-2r)R s^\male \right]}{2}
-%\end{equation}
-%
-%%k=1/2
-%\begin{equation}
-%C_{1/2} = even \; bigger, \; uglier \; term
-%\end{equation}
-%
-%When $k=1$ the maternal- and offspring-controlled results are the same, $C_1 = C_W$, since the mutation remains in females (and hence mutant daughters always have mutant mothers).
-%However, with $k\neq1$ the results with maternal control differ from those with offspring control.
-%Interestingly, for all $k\in\{0,1/2,1\}$, we find that invasion into an ancestrally XY system is the same as invasion into an ancestrally ZW system (at least up to order $\epsilon^3$), implying that sex ratio selection does not drive transitions between genetic sex determination and maternally controlled environmental sex determination.
-%Of particular interest is $k=1/2$ (i.e., when the mother perfectly balances the sex ratio of her offspring).
-%When both recombination rates are small we have $C_{1/2} \approx R(s^\male - s^\female)/8 = \lim_{r \rightarrow 0} C_1/4$.
-%This implies that, at least under tight linkage, the invasion of maternally-controlled ESD is independent of $R$ (because $S_A\propto R^{-1}$) and can invade whenever a neo-$W$ can (which can invade even when it biases the sex ratio further; Figures \ref{fig:WinvasionLowR} -- \ref{fig:WinvasionHighR}).
-
-\section*{Discussion}
-
-%\textcolor{blue}{maybe re-order to put the results up front and focus on sex ratio less.
-Somewhere around these first two paragraphs we should include our tight linkage results.
-At the moment it doesn't make total sense because it assumes that tighter linkage is always favoured unless there is haploid selection.}
-
-%MAIN RESULT
-Two predominant theories explaining the remarkably high frequency of transitions between sex-determination systems are sexually-antagonistic selection and sex ratio selection \citep[reviewed in][]{Blaser2012, vanDoorn2014re}.
-The former predicts that neo-sex-determining alleles can invade when they arise in closer linkage with a sexually-antagonistic locus \citep{vanDoorn:2007eu,vanDoorn:2010hu, Muralidhar2018}.
-The latter predicts that new sex-determining systems are generally favoured if they result in more equal sex ratios than the ancestral system. 
-%The latter predicts that neo-W alleles will invade an XY system when there is a male bias caused by haploid selection in males, and vice-versa, a neo-Y will invade a ZW system when there is a female bias caused by haploid selection in females \citep{Kozielska:2010vm,Ubeda:2015fx}.
-In contrast to these prevailing views, we show that selection (including sexually-antagonistic selection, overdominance, and/or ploidally-antagonistic selection) on loci tightly linked to the ancestral sex-determining region can favour trans-GSD transitions (XY to ZW or ZW to XY) to new sex-determining systems that are less closely linked to the selected loci (e.g., see Figure \ref{fig:SexAntagTighter}).
-Similarly, even when linkage is weak relative to selection, we show that %new sex-determining alleles are typically favoured if they are more closely linked to a locus under haploid selection (even in the absence of diploid sex differences), which is the only condition favouring cis-GSD transitions (XY to XY or ZW to ZW).
-%In addition, with haploid selection and weak selection, 
-trans-GSD transitions (XY to ZW or ZW to XY) can occur where the new sex-determining region is less closely linked to the locus under selection if there is haploid selection (e.g., Figures \ref{fig:Combination_Centimorgans} and \ref{fig:SexRatioBad}).
-%\textcolor{red}{need to mention sex ratio here}
-%Neo-W (neo-Y) alleles invade when their fitness in females (males) is greater than the mean fitness of females (males) under the ancestral sex-determination system and/or females (males) are the rarer sex.
-
-%TIGHT LINKAGE RESULTS
-%When the rate of recombination between the ancestral sex-determining locus and a locus under selection is small relative to the strength of selection (i.e., sex-linkage is tight, or selection is strong), heterogametic transitions (XY to ZW or ZW to XY) that reduce sex-linkage are possible, with or without haploid selection (Figures \ref{fig:SexAntagTighter} and \ref{fig:regionplots}).
-
-%The likelihoods of these transitions are driven by sex ratio selection, direct selection on alleles linked to the neo-sex-determining allele, the ability of the neo-sex-determining allele to avoid selection in one sex, and the ability of the neo-sex-determining allele to bring alleles on the sex-specific chromosome in the ancestor into the other sex (given that the neo-sex determining allele is epistatically dominant to its predecessor).
-
-%This possibility that looser sex-linkage could evolve, even in the absence of haploid selection (Figure \ref{fig:regionplot_2a}A), was overlooked in \cite{vanDoorn:2010hu}, likely because they did not explicitly consider the case of initially tight linkage between the \textbf{A} locus and the ancestral-SDR, which allows substantial differences in allele frequencies to build up \citep[$\hat{p}^\Hermaphrodite_{X} \neq \hat{p}_{Y}^\male$, equation \ref{eq:tightequil};][]{Lloyd1977,Otto2014}.
-%Interestingly, there is substantial overlap between the parameter space that allows both neo-W-$A$ and neo-W-$a$ haplotypes to spread in an XY system and that which selects for increased recombination between X and Y chromosomes \citep[e.g., compare gray region of Figure \ref{fig:regionplot_2a}A with coloured regions of Figure 2(a) in][]{Otto2014}.
-%This makes sense, as when both neo-W haplotypes can spread the neo-W can invade despite reducing sex-linkage, i.e., the rate of recombination between the sex-determining allele and the selected locus increases.
-%We further find that it is easier for a neo-W to invade 
-%\textcolor{red}{explain difference too?
-also explain why a neo-Y doesn't invade to reduce linkage despite selection for more recombination?
-mention something about haploid selection (Fig7B)?} \textcolor{blue}{maybe leave for now}
-
-%HAPLOID SELECTION CAN ACT LIKE SEXUALLY-ANTAGONISTIC SELECTION
-%It has previously been demonstrated that new sex-determining systems can evolve if there is genetic variation maintained by sexually-antagonistic selection \citep{vanDoorn:2007eu,vanDoorn:2010hu}. 
-%In particular, 
-%Under weak selection (or loose sex-linkage), transitions to new sex-determining systems can occur when they arise more closely linked to a sexually-antagonistic locus \citep{vanDoorn:2007eu,vanDoorn:2010hu}.
-%New sex-determining alleles are again favoured if they are more closely linked to a locus under haploid selection, which is the only condition favouring homogametic transitions (XY to XY or ZW to ZW).
-%HAPLOID SELECTION ALSO ALLOWS LOOSER LINKAGE TO EVOLVE
-%However, with haploid selection, heterogametic transitions (XY to ZW or ZW to XY) can occur even when the new sex-determining region is less closely linked to the locus under selection. 
-%Neo-W (neo-Y) alleles invade when their fitness in females (males) is greater than the mean fitness of females (males) under the ancestral sex-determination system and/or females (males) are the rarer sex.
-
-%With sexually-antagonistic selection (between diploid sexes) only, linkage between a selected locus and the sex-determining region strengthens associations between male beneficial alleles and the male-determining allele (Y or Z) and between female beneficial alleles and the female-determining allele (X or W).
-%Thus, the mean fitness of both males and females increases with closer linkage to the sex-determining region. 
-%Therefore, new sex-determining alleles only invade if they are more closely linked than the ancestral sex-determining region. 
-%However, if there is haploid selection on loci linked to an XY (ZW) sex-determining region, selection can maintain polymorphisms at which the product of the frequency of females (males) and the mean fitness of females (males) is lower than it would be without sex-linkage.
-%In these cases, unlinked neo-W (neo-Y) alleles can increase the frequency and/or fitness of the only sex they are found in, at a cost to the other sex, and invade despite lowering population mean fitness (Figure \ref{fig:Combination_MeanFit}).
-%\textcolor{red}{This is similar to mitochondria and male disease ...?}
-
-%%SEX-RATIO SELECTION
-%\textcolor{blue}{maybe drop paragraph?}
-%\textcolor{red}{I messed with the sex ratio selection paragraphs to tone down our "it doesn't matter" speech from before. Have at any amendments you'd like to make.}
-%Linkage between haploid selected loci and sex-determining regions cases biased zygotic sex ratios \citep{Hamilton:1967ts,Burt:2006,Field:2012fd,Field:2013cc}.
-%One might then expect Fisherian sex ratio selection to drive the spread of new sex-determining systems that bring the sex ratio closer to 50:50. 
-%Fisherian sex ratio selection follows from the fact that, for an autosomal locus, half of the genetic material is inherited from a male, and half from a female \citep{Fisher:1930wy,West:2009we}. 
-%Thus, if the population sex ratio is biased towards females, the average per-individual contribution of genetic material to the next generation from males is greater than the contribution from females (and vice versa for male-biased sex ratios).
-%Therefore, a mutant that increases investment in males will spread via the higher per-individual contributions made by males. 
-%%%That is, under Fisherian sex ratio selection, the success of a mutant relative to the non-mutant depends, in equal parts, on the contributions made by males and females to the next generation. 
-%An implicit assumption of Fisherian sex ratio selection is that the mutant allele is autosomal and has the same inheritance pattern as the non-mutant allele. 
-%The mutations we consider here, neo-sex-determining alleles, break this assumption. 
-%For example, the success of neo-Y/neo-W mutations depends only on the number of alleles contributed by males/females (Table \ref{tab:haplotype_growth}). 
-%In this respect, a neo-W is similar to a cytoplasmic element, which also does not experience selection to balance sex ratios \citep{Frank:1989vl,Werren:1998co,Chase:2007bf}.
-%Even mutants that are equally likely to be found in males or females, such as an environmental sex determination mutation (equation \ref{eq:lambda_ESD}), are not strictly autosomal if they determine sex.
-%Thus, despite the fact that sex ratio biases caused by gametic competition or meiotic drive have been shown to exert Fisherian sex ratio selection on various autosomal modifiers \citep{Stalker:1961th,Smith:1975ft,Frank:1989vl,Hough:2013uo,Ubeda:2015fx, Otto:2015va}, we do not find evidence of Fisherian sex ratio selection acting during invasion by neo-sex-determination systems (e.g., see Figure \ref{fig:Combination_Turnover} and \citealt{Ubeda:2015fx}, in which a neo-Y invades despite biasing sex ratios).
-
-%Sex ratio biases caused by gametic competition or meiotic drive have been shown to exert Fisherian sex ratio selection on various autosomal \citep{Stalker:1961th,Smith:1975ft,Frank:1989vl,Hough:2013uo,Ubeda:2015fx, Otto:2015va} and sex-linked \citep{Kozielska:2010vm} modifiers.
-We find that the spread of neo-sex-determining systems cannot be simply predicted from their effect on the sex ratio. 
-On one hand, sex ratio biases caused by haploid selection can facilitate trans-GSD transitions or GSD-ESD transitions between sex-determining systems. 
-For instance, alleles favoured by haploid selection in males often become associated with the Y, which leads to a male-biased zygotic sex ratio.
-This male bias increases the potential for a neo-W to invade (Table \ref{tab:haplotype_growth}), which can equalize the sex ratio \citep[e.g., see Figure \ref{fig:SexRatioBad}B, for related examples see][]{Kozielska:2010vm}.
-%We find that sex ratio biases caused by haploid selection can also affect transitions between sex-determining systems (e.g., see $\zeta$ terms in Table \ref{tab:haplotype_growth}). 
-%However, the neo-W may not equalize the sex ratio (e.g., if the driving allele also drives in females or affects competition among eggs)
-On the other hand, sex ratio selection can be overwhelmed by additional selective effects, preventing a neo-W or ESD allele from invading, even if it would balance the sex ratio (e.g., when selection acts in opposite directions in male and female diploids, Table \ref{tab:specialcases}).
-%and equalizing the sex ratio.
-Indeed, transitions between sex-determining systems can generate stronger sex ratio biases \citep[e.g., Figure \ref{fig:SexRatioBad}A and step 1 in][]{Ubeda:2015fx}.
-%For example, where a neo-Y invades and is linked with a locus that experiences haploid selection in male gametes, the sex ratio evolves to become biased \citep[e.g., see Figure \ref{fig:SexRatioBad}A and step 1 in][]{Ubeda:2015fx}.
-%For example, in an ancestral ZW system, haploid selection in males can allow a linked neo-Y to invade, despite the fact that it creates a male-biased sex ratio because the neo-Y becomes associated with the driven allele (Figure \ref{fig:SexRatioBad}A).
-%\textcolor{blue}{and figure 1, where the end of one panel is the same as the beginning of another, however, this figure may change).}
-%What we would like to stress is that sex ratio selection alone cannot predict when new sex-determining systems can evolve.
-Significantly, with weak selection, we find that there is no difference in conditions allowing XY to ZW and ZW to XY transitions, indicating that sex chromosome transitions are not predominantly predicted by their effect on the sex ratio (i.e., the sex ratio bias created by male haploid selection facilitates the spread of a neo-W into an XY system to the same degree that male haploid selection drives the spread of a neo-Y into a ZW system with a 1:1 sex ratio).
-%An asymmetry can develop when sex-linkage is tight (e.g., Figure \ref{fig:Combination_Centimorgans} near -25cM and 25cM) but under most circumstances we do not predict asymmetry between XY to ZW and ZW to XY transitions despite the presence/absence of sex ratio selection.
-Thus, haploid selection can favour trans-GSD transitions both via sex ratio selection and via selection on alleles associated with the neo-sex-determining allele, and these selective pressures are often predicted to be of equal magnitude.
-%\textcolor{red}{Maybe try to emphasise surprisingness in the paragraph more? e.g., how wrong you'd be if you assumed selection to equalise sex ratios, or it this implied?}
-%\textcolor{blue}{nice, pretty subtle argument but I think that's a good job.}
-
-%Previous studies where ESD is favoured have typically assumed that environmental conditions (e.g., maternal condition, mate quality, age, or host size) can differentially affect the fitness of males versus females such that ESD invades because it allows sex determination to depend on the environment \citep[reviewed in][]{Charnov:1982wg,Bull:1983vi,West:2009we}.
-
-%WHY SEX-RATIO BIASES CAN BE FAVOURED
-%We note two other ways in which sex determination has been shown to relate to zygotic sex ratios.
-%Firstly, female-biased sex ratios can be favoured when there is local mate competition, where all matings are between siblings and assuming one male can inseminate many females \citep{Hamilton:1967ts}.
-%Therefore, with local mate competition, feminizing mutations can spread because they bias the sex ratio towards females \citep{Wilson:1981vm,Vuillleumier:2007bh}. 
-%Secondly, environmental conditions (e.g., maternal condition, mate quality, age, or host size) can differentially affect the fitness of males versus females such that the optimal allocation to males/females depends on the environment \citep{Trivers:1973wb,Charnov:1977tx,Charnov:1982wg}.
-%In such cases, flexible sex-determination systems may evolve in order to allow the zygotic sex ratio to be determined in a way that depends on the environment \citep{Charnov:1977tx,Werren:1984tl,Pen:2010kk}.
-%In this study, we do not consider environmental condition dependence or local mate competition \citep[reviewed in][]{Charnov:1982wg,Bull:1983vi,West:2009we}.
-
-%HOW TO TEST EMPIRICALLY
-%\textcolor{blue}{I think Sally was sceptical of this idea. i.e., if the second term in \ref{eq:lambda_neoW} is negative, then get less transitions with haploid selection included, right? }
-%\textcolor{red}{Yeah, and given that only 1/2 the discovered plant sex chromosomes are hetermorphic and there are so few plant sex chromosomes to begin with (Charlesworth 2016 Annual Review Plant Biology), might it be the case that haploid selection is constraining things?
-perhaps we could think of some particular forms of haploid selection that might be common and give their predicted effects, or just say some things that are possible with haploid selection that are not without it -- if there are any.
-just looking at eq 3 though, its gonna be hard to get a low freq of A on the Y if haploid selection in males favours A, i.e., it should often be positive when there is no female haploid selection, right?}
-%\textcolor{blue}{That sounds right to me and is backed up by equation \eqref{eq:freq_diffs}.
-It may be technically possible for that term to be negative though.
-Re: hetermorphism, I see that as a slightly different issue.
-It's thought that haploid selection may prevent deletions from becoming fixed on the Y, like in the Crowson (2017) paper.
-%I think the issue of `why so few plant sex chromosomes' is partly an issue of detection and also `why so much hermaphroditism'.
-Is it possible that the ESD results could show selective forces that also favour transitions from dioecy to hermaphroditism?
-I think so.
-Our ESD mutant produces 1/2 females and 1/2 males whereas a hermaphrodite invests roughly equally in each type of gamete produced.
-We don't consider the forces that are usually thought to be involved in these transitions though (inbreeding depression, reproductive assurance and possibly others?).
-}
-%Taken at face value, our results indicate that transitions in heterogametey (XY to ZW or vice versa) are more likely to be favoured by selection if there is selection upon both haploid and diploid genotypes rather than diploid selection alone ().
-%This prediction could be examined using a suitable proxy for haploid selection, for example, \cite{Lenormand:2005vb} use the outcrossing rate in plants as a proxy for the strength of pollen competition.
-%In animals, one might expect gametic competition to be stronger in species where sperm is required to live for a long time after spermatogenesis because transcripts shared during spermatogenesis may become depleted, revealing the haploid phenotype of the sperm \citep{Immler:2014im}.
-%Given the caveats mentioned above about the form of meiotic drive modelled, we would also expect that heterogametic transitions in sex determination would be more common in clades where there is meiotic drive.
-
-%Together, our models demonstrate novel selective forces that favour heterogametic transitions (XY to ZW or ZW to XY). 
-%One common prediction is therefore that heterogametic transitions are favoured under a wider range of conditions than homogametic transitions. 
-%However, heterogametic transitions are not clearly in excess.
-For example, \citet{Vicoso:2015hf} found a dozen sex chromosome configurations among Dipteran species but only one transition between male and female heterogametey.
-%While our models examine the selective forces that favour the spread of new sex-determining regions, observed transitions could also reflect the mutation rate for neo-Y versus neo-W alleles (e.g., duplications of the ancestral sex determining region could be particularly likely).
-%In addition, heterogametic transitions could be limited due to the production of YY males or WW females (see below). 
-%Alternatively, it might be useful to compare clades that are expected to differ in the strength of haploid selection (e.g., plants are thought to experience more selection during their multicellular haploid stage
-
-%HAPLOID SELECTION (genomic location of haploid selected loci and comparative patterns) 
-We have shown that the spread of new sex determination systems can be driven by loci experiencing haploid selection. 
-%Our results suggest that haploid selected loci that have been involved in driving turnovers between sex-determination systems could occur around the ancestral- or novel-sex-determining regions. 
-%Our results suggest that polymorphic loci that are ancestrally sex-linked and under sex-specific selection could also drive heterogametic transitions between sex-determination systems. 
-%As with sexually-antagonistic selection, the presence of haploid selected loci around ancestral- or novel-sex-determining regions could support their role in sex chromosome turnover.
-In agreement with this hypothesis, a recent transcriptome analysis in \textit{Rumex} shows that Y-linked genes have higher expression in haploid pollen than autosomal genes \textcolor{red}{(check this is accurate)}.
-Interestingly, haploid-expression is also more common on the autosome that is orthologous to the sex chromosomes in closely related species suggesting that new sex chromosomes may have been favoured through their association with haploid selected alleles on these chromosomes \textcolor{red}{(Sandler et al., 2018, Personal Communication)}.
-%maybe add a flag here for switching to clade-level expectations:
-In general, we predict that haploid selection increases lability of sex-determination systems, particularly because haploid selection can cause transitions that increase or decrease sex-linkage (e.g., the final state of the red line in Figure \ref{fig:SexRatioBad}B is the starting state in Figure \ref{fig:SexRatioBad}A).
-Turnovers driven by haploid selection may help to explain the relative rarity of heteromorphic sex chromosomes in plants, which are thought to experience more selection during their multicellular haploid stage.
-If haploid selection is strong but selective differences between male and female diploids are weak, we find that trans-GSD transitions (XY to ZW or ZW to XY) are favoured more strongly than cis-GSD transitions, with transitions to ESD intermediate (e.g., with $|D^\male - D^\female| << |\alpha_\Delta^\male - \alpha_\Delta^\female + t^\male - t^\female|$ we have $\lambda_{W',XY} > \lambda_{Y',XY}$; Equations \ref{eq:lambda_neoW} and \ref{eq:freq_diffs}).
-Among the relatively few dioecious clades in which multiple species have well characterized sex chromosomes \citep{Ming:2011iy}, trans-GSD transitions have been inferred in \textit{Silene} subsection \textit{Otites} \citep{Slancarova:2013dq} and in \textit{Salicaceae} \citep{Pucholt2015,Pucholt2017}.
-%Potentially, successive heterogametic transitions between master regulators of sex-determination could be inferred from careful examination of the molecular pathways by which sex is determined. 
-%Our predictions could also be examined using a suitable proxy for haploid selection, for example, \cite{Lenormand:2005vb} use the outcrossing rate in plants as a proxy for the strength of pollen competition.
-Assuming that transitions from dioecy to hermaphroditism (equal parental investment in male and female gametes) are favoured in a similar manner to the ESD examined here (equal probability of zygotes developing as males or females), our results suggest that competition during the haploid stage could also drive transitions between dioecy and hermaphroditism, which are frequent in plants \citep{Kafer2017, Goldberg2017}.
-%In animals, one might expect gametic competition to be stronger in species where sperm is required to live for a long time after spermatogenesis because transcripts shared during spermatogenesis may become depleted, revealing the haploid phenotype of the sperm \citep{Immler:2014im}.
-%We would also expect that heterogametic transitions in sex determination would be more common in clades where there is meiotic drive.
-
-%IDENTIFICATION OF LOCI IN GENOMIC LOCATIONS THAT IMPLICATE THEM IN SEX-CHROMOSOME TURNOVER
-%The hypotheses presented here can be empirically investigated in a similar manner to the idea that transitions between sex-determining systems are favoured by linkage to sexually-antagonistic variation.
-%In the case of sexually-antagonistic variation, one supporting observation is that genes expected to be under sexually-antagonistic selection (e.g., those causing bright male colouration) have been found on recently derived sex chromosomes \citep{Lindholm:2002dw,Tripathi:2009cw,Ser:2010iq}.
-In support of their role in sex chromosome turnover, genes expected to be under sexually-antagonistic selection (e.g., those causing bright male colouration) have been found on recently derived sex chromosomes \citep{Lindholm:2002dw,Tripathi:2009cw,Ser:2010iq}.
-Our results show, however, that tight ancestral-linkage of polymorphic loci can also drive trans-GSD transitions. 
-In addition, we find that polymorphic sex determining systems (X, Y, W, and Z alleles all present) can be maintained when a selected locus is tightly linked to the ancestral sex-determining system (e.g., Figures \ref{fig:freqAll}B and \ref{fig:freqAll}C), which is not possible with loose linkage \citep{vanDoorn:2010hu}.
-%As noted by \citet{vanDoorn:2010hu}, it would be prudent to compare closely related clades in order to determine whether observed polymorphisms predate a transition in sex-determination or arose afterwards.
-%, particularly because sex-linkage allows sexually-antagonistic selection to maintain polymorphisms under a different and larger parameter space \citep{Rice:1987hs,Jordan:2011fj}.
-For example, our results suggest a potential mechanism maintaining multiple sex determining alleles in the platyfish (\textit{Xiphophorus maculatus}), in which X,Y, and W alleles segregate at one locus (or two closely-linked loci) near to potentially sexually-antagonistic genes for pigmentation and sexual maturity \citep{Kallman1965,Kallman1968, Volff2001, Schultheis2006}.
-Several rodent species also maintain feminizing alleles along with the ancestral X and Y sex-determination alleles \citep[reviewed in][]{Fredga1994}. 
-For example, in nine \textit{Akadon} species, it appears that male-determining-\textit{sry} expression is suppressed by an autosomal feminizing allele, creating XY females \citep{Bianchi2002,Sanchez2010}, which have increased fitness relative to XX females \citep{Hoekstra2001}.
-In \textit{Mus microtoides}, females can have XX, XX$^\ast$ or X$^\ast$Y genotypes \citep{Veyrunes2010}. 
-Previous theory would predict that the X$^\ast$ chromosome (or the autosome it is fused to) harbours female beneficial alleles, driving its spread. 
-However, XX and XX$^\ast$ females have similar fitness, whereas X$^\ast$Y female fitness is enhanced \citep{Saunders2014,Saunders2016, Veyrunes2017}.
-Although Y-linkage of female-beneficial alleles is counterintuitive, our tight linkage model suggests that it can be stably maintained and then favour new feminizing mutations, which is a parsimonious explanation for the spread of feminizing alleles in these rodent species.
-
-%Limitation 1: DEGENERATE Y
-We note that we assume that sex-determining alleles do not experience direct selection except via their associations with sex and selected alleles.
-However, in some cases, there may be significant degeneration around the sex-limited allele (Y or W) in the ancestral sex-determining region because recessive deleterious mutations and/or deletions accumulate around the Y or W sex-determining regions \citep{Rice:1996ke,Charlesworth:2000cc,Bachtrog:2006ed,Marais:2008hm}.
-During trans-GSD transitions (XY to ZW or ZW to XY), but not cis-GSD transitions (XY to XY or ZW to ZW), any recessive deleterious alleles linked to the Y or W are revealed to selection in YY or WW individuals \citep{Bachtrog:2014bx}.
-This phenomenon was studied by \citet{vanDoorn:2010hu}, who found that degeneration can prevent fixation of a neo-W or a neo-Y allele, leading to a mixed sex-determination system where the ancestral and new sex-determining loci are both segregating.
-However, they noted that very rare recombination events around the ancestral sex-determining region can allow these trans-GSD transitions to complete.  
-%While not explicitly studied, we also predict that Y or W degeneration would prevent fixation of the new sex-determining genes considered here.
-Degeneration around the Y or W could explain why trans-GSD transitions are not observed to be much more common than cis-GSD transitions despite the fact that our models demonstrate that they are favoured under a wider range of conditions, especially with haploid selection.
-For example, \citet{Vicoso:2015hf} found a dozen sex chromosome configurations among Dipteran species but only one transition between male and female heterogamety.
-
-%Limitation 3: don't consider m alleles with similar k to ancester, no ancestral ESD considered
-In this study, we have only considered neo-sex-determining alleles of large effect. 
-However, we expect similar selective forces to act on masculinizing/feminizing alleles of weaker effect. 
-For example, \citet{Muralidhar2018} consider small effect masculinizing/feminizing alleles within a threshold model of sex determination, finding that they can be favoured when linked to loci that experience sexually-antagonistic selection.
-These results echo those for large-effect neo-Y/neo-W alleles \citep{vanDoorn:2007eu,vanDoorn:2010hu}.
-Finally, while we have considered cis-GSD, trans-GSD, and GSD to ESD transitions, we have not explicitly considered ESD to GSD transitions. 
-Recent models of ESD to GSD transitions \citep{Ubeda:2015fx,Muralidhar2018} show that that neo-Y/neo-W alleles can be favoured when they arise near to haploid and/or diploid selected loci, which also occurs in our model.
-
-%Limitation 2: TWO ALLELE DRIVE
-%Another simplification that we made is that meiotic drive involves only a single locus with two alleles. 
-%However, many meiotic drive systems involve an interaction with another locus at which alleles may `suppress' the action of meiotic drive \citep[][]{Burt:2006,Lindholm:2016cw}.
-%Thus, the dynamics of meiotic drive alleles can be heavily dependent on the interaction between two loci and the recombination rate between them, which in turn can be affected by sex-linkage if there is reduced recombination between sex chromosomes \citep{Hurst:1991uh}.
-%Furthermore, in some cases, a driving allele may act by killing any gametes that carry a `target' allele at another locus, in which case there can be fertility effects that alter the equilibrium frequency of a meiotic drive allele \citep{Holman:2015en}.
-%In polygamous mating systems, the intensity of pollen/sperm competition can depend on the density of males available to donate pollen/sperm, which can itself depend on the sex ratio \citep{Taylor:2002wu}.
-%In terms of our model, this implies that the strength of gametic competition ($t^\male$) may both determine and be determined by the sex ratio. 
-%How the evolution of new sex-determining mechanisms could be influenced by two-locus meiotic drive and/or by ecological feedbacks under different mating systems remains to be studied.
-
-%\textcolor{blue}{similarly, this part doesn't discuss our new tight linkage results or our new perspective on sex ratios.}
-%CONCLUSION
-We have shown that tight sex-linkage and haploid selection can drive previously unexpected transitions between sex-determination systems.
-In particular, both can select for neo-sex-determining loci that are more loosely linked. 
-In addition, haploid selection can cause transitions analogous to those caused by purely sexually-antagonistic selection, eliminating the need for differences in selection between male and female diploids.
-We conclude that haploid selection should be considered as a pivotal factor driving transitions between sex-determination systems. 
-Perhaps counterintuitively, transitions involving haploid selection can be driven by sex ratio selection or cause sex ratio biases to evolve and Fisherian sex ratio selection is not an overwhelming force.
-Overall, our results suggest several new scenarios under which new sex-determination systems are favoured, which could help to explain why the evolution of sex-determination systems is so dynamic. 
-%Further, we have shown the way in which transitions are affected by haploid selection is not intuitively obvious. 
-%Firstly, sex-specific haploid selection affects turnovers between sex-determination systems in a manner that is qualitatively different from diploid sex-specific selection. 
-%In particular, closer linkage between a sex-determining locus and a selected locus is not always favoured during heterogametic transitions when there is haploid selection. 
-%Secondly, even though haploid selection is a source of zygotic sex ratio biases, in our models Fisherian sex ratio selection does not have good explanatory power in determining whether various sex-determination systems evolve.
-%This result is surprising given that sex ratios are ultimately determined via the sex-determination system, and leads us to the conclusion that three selective forces -- haploid, diploid, and sex ratio selection -- should all be considered when exploring transitions between sex-determination systems.
-
-\bibliographystyle{amnatnat.bst}
-\bibliography{sex_chromosomes.bib}
-
-\newpage
-%\section*{Figures}
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Tighter linkage allows looser sex-linkage to evolve, even in absence of haploid selection
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\includegraphics[width=\linewidth]{PositionPlot_SexAntagTighter}
-%\caption{
-%In the absence of haploid selection, tight linkage allows looser sex-linkage to evolve in transitions between XY and ZW systems.
-%In panel A, linkage is loose enough relative to selection that the weak selection analytical results hold, and a neo-W can only invade when it is more tightly linked with the selected locus ($R<r$; shaded region).
-%In panel B, linkage is tight enough relative to selection that the weak selection analytical results do no hold, and a neo-W can only invade even when it is less tightly linked with the selected locus ($r<R$; unshaded region).
-%Parameters: $w_{AA}^\female = w_{aa}^\male = 1.05$, $w_{aa}^\female = w_{AA}^\male = 0.85$, $w_{Aa}^\female = 1$, $w_{Aa}^\male = 0.925$, $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
-%}
-%\label{fig:SexAntagTighter}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Both neo-W haplotypes can spread, in the absence of haploid selection, when there is overdominance
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\includegraphics[width=0.45\linewidth]{regionplot_2a}
-%\includegraphics[width=0.45\linewidth]{regionplot_2a_Color_Ya_Either}
-%\includegraphics[width=0.45\linewidth]{BothWsInvade_Overdominance}
-%\caption{
-%In the absence of haploid selection, both neo-W haplotypes can spread in an XY system when there is overdominance.
-%Panel A shows the range of male homozygote fitnesses that allow either neo-W haplotypes to invade.
-%The blue region overlaps with a red region, where both neo-W haplotypes can invade a population with $A$ fixed on the X and $a$ fixed on the Y.
-%The green region (overlapped by the orange region) is where both neo-W haplotypes can invade a population with $a$ fixed on the Y and a polymorphic X.
-%The orange region (outside the green region) is where only the neo-W-$A$ haplotype can invade
-%Panel B shows the temporal dynamics of the invading neo-W haplotypes; in this case the neo-W does not fix, leading to a polymorphic sex-determining system.
-%Asterisk in panel A marks parameter values ($w_{aa}^\male=0.15$, $w_{AA}^\male=0.1$) used in panel B.
-%Parameters: $w_{AA}^\female = w_{aa}^\female = 0.6$, $w_{Aa}^\Hermaphrodite = 1$, $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$, $r=R=0$.
-%\textcolor{red}{make two more temporal plots with visible asterisks in green and orange regions; figure out better colours to show possibilities}
-%}
-%\label{fig:BothOverdominance}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%With weak selection, a less tightly linked neo-W can invade an XY system when there is some haploid selection, and this invasion decreases mean diploid fitness
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\includegraphics[width=0.5\linewidth]{Loose_Fitness_Decline}
-%\caption{
-%With weak selection, a less tightly linked neo-W can invade (and fix in) an XY system (causing the Y to fix in females) when there is some haploid selection (blue and green curves in panel A), and this invasion decreases mean diploid fitness (green and blue curves in panel B).
-%Parameters: $s^\Hermaphrodite = 0.2$, $h^\Hermaphrodite = 0.7$, $t^\Hermaphrodite = \alpha^\male_\Delta = 0$, $\alpha^\female_\Delta = -0.1$, $r=1/10$.
-%}
-%\label{fig:LooseDecline}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%A neo-W can invade an XY system under a large number of selective regimes
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\includegraphics[width=0.5\linewidth]{PositionPlot_4}
-%\caption{
-% A neo-W can invade an XY system under a large number of selective regimes.
-%In panel A, there is no haploid selection ($t^\Hermaphrodite = \alpha^\Hermaphrodite_{\Delta} = 0$) and selection in diploids is sexually antagonistic ($s^\male = -s^\female = 1/10$, $h^\male = 1-h^\female = 3/10$), in which case the neo-sex-determining allele can only invade if it is more closely linked to the selected locus ($R<r$, gray region; but see Figure \ref{fig:SexAntagTighter}B for the case of very tight linkage).
-%In panel B, male drive ($\alpha^\male_{\Delta} = -1/20$, $t^\Hermaphrodite = \alpha^\female_{\Delta} = 0$) opposes selection in diploids (no sex-differences: $s^\Hermaphrodite = 1/10$, $h^\Hermaphrodite = 7/10$), in which case the neo-sex-determining allele can invade regardless of linkage.
-%In panel C, haploid competition in males ($t^\male = -1/10$, $t^\female = \alpha^\Hermaphrodite_{\Delta} = 0$) opposes selection in diploids (sex-differences: $s^\male = 3 s^\female = 3/20$, $h^\Hermaphrodite = 7/10$), in which case the neo-sex-determining allele can once again invade regardless of linkage.
-%We use Haldane's map function \citep[Equation 3 in ][]{Haldane1919} to convert from map distance (centiMorgans, cM) to the probability of recombination (an odd number of cross-over events).   
-%}
-%\label{fig:Combination_Centimorgans}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Sex ratio selection is not a good predictor of neo-W invasion into an XY system
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\includegraphics[width=\linewidth]{Combination_Turnover_Ratio}
-%\caption{
-%Sex ratio selection alone is not a good predictor of turnover between sex-determining systems.
-%In panels A and C, male drive in an ancestral XY system causes a male bias, allowing a neo-W to invade and fix (causing the Y to fix in females), which balances the sex ratio (it also avoids selection in males, and thus makes better females in this case of sex-specific ploidally-antagonistic selection).
-%In panels B and D, male drive in an ancestral ZW system has no affect on the sex ratio, yet a neo-Y can invade and fix (causing the W to fix in males) because it becomes linked with the driving allele, and this imparts a sex ratio bias.
-%Parameters:  $s^\female =s^\male = 0.2$, $h^\female = h^\male = 0.7$, $t^\female = t^\male = \alpha^\male_\Delta = 0$, $\alpha^\female_\Delta = -1/10$, $r=1/20$.
-%}
-%\label{fig:SexRatioBad}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Haploid selection can lead to polymorphic SD systems 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\includegraphics[width=\linewidth]{Polymorphic}
-%\caption{
-%Tight linkage (relative to selection) and/or haploid selection can cause stable polymorphic sex-determining systems.
-%In panel A, there is strong overdominance in both sexes and no haploid selection  (parameters as in Figure \ref{fig:BothOverdominance}B with $r = 1/10$), in which case a neo-W can invade regardless of sex-linkage, but cannot not fix (i.e., the Y does not fix in females, and X, Y, W, and Z all segregate at equilibrium).
-%In panel B, there is sex-antagonistic selection at the diploid stage and drive in females (parameters as in Figure \ref{fig:SexAntagTighter} with $\alpha^\female_\Delta = 1/20$ and $r = 1/10$), in which case a sufficiently tightly linked neo-W can invade ($R<\sim r$), but only fixes if $R=0$.
-%}
-%\label{fig:Polymorphism}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%CYCLES!
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\includegraphics[width=0.5\linewidth]{BothWsInvade_Overdominance_Cycles}
-%\caption{
-%Thought I'd show this just for fun (not for publication).
-%}
-%\label{fig:Cycles}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Heterogametic transitions with/without sex ratio change
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\begin{tikzpicture}[remember picture]
-%	\node[] (plot) {\includegraphics[width=\linewidth]{Combination_Turnover}};
-%	\node[above = 0cm of plot, xshift = -70] () {$r=0.5$, $R=0.05$};
-%	\node[above = 0cm of plot, xshift = 120] () {$r=0.05$, $R=0.5$};
-%	\node[left = 0cm of plot, yshift = 105, rotate = 90] () {XY $\rightarrow$ ZW};
-%	\node[left = 0cm of plot, yshift = -20, rotate = 90] () {ZW $\rightarrow$ XY};
-%\end{tikzpicture}
-%\caption{
-%Heterogametic transitions from XY to ZW sex determination (neo-W frequency shown by black lines, panels A and B) or from ZW to XY (neo-Y frequency shown by black lines, panels C and D) occur similarly regardless of sex ratio biases present before (B versus D) or after (C versus A, dashed lines show male frequency).
-%During invasion by a neo-ZW sex-determination system (A and B), the ancestral Y fixes in both males and females (blue and red lines). 
-%Similarly, the ancestral W allele fixes in males and females (blue and red lines) during a ZW to XY transition. 
-%In this plot, there is no gametic competition ($t^\female=t^\male=0$) and meiotic drive occurs during male meiosis only ($\alpha^\female_{\Delta}=0$, $\alpha^\male_{\Delta}=-1/5$).
-Therefore, sex ratio biases can only arise when the \textbf{A} locus is linked to an XY sex-determining locus.
-%In panels A and C, the neo-sex-determining locus is more closely linked to the \textbf{A} locus than the ancestral sex-detemining region ($r=1/2$, $R=1/20$) such that a neo-Y can caused biased sex ratios (panel C).
-%In panels B and D, the ancestral sex-determining locus is more closely linked to the \textbf{A} locus than the neo-sex-detemining locus ($r=1/20$, $R=1/2$). 
-%Therefore, an ancestral XY sex determination can have a biased zygotic sex ratio that becomes unbiased after an unlinked neo-W invades (B). 
-%However, in panel D, a unlinked neo-Y invades an ancestral ZW sex-determination system in a similar manner but no biases to the zygotic sex ratio occur. 
-%With diploid selection alone, neo-sex-determining loci do not spread if they are less closely linked to the \textbf{A} locus than the ancestral sex-determining locus (see equation \eqref{eq:lambda_neoW} and Figure \ref{fig:Combination_Centimorgans}A).
-%In this plot there are no sex differences in selection and an equilibrium is maintained because selection in diploids opposes meiotic drive, $s^\female =s^\male = 1/5$, $h^\female = h^\male = 7/10$.
-%\textcolor{red}{Aesthetic adjustments: 
-%%Could add titles to the columns/rows: neo-W for row 1, neo-Y for row 3, $r=0.5$, $R=0.05$ for column 1 and $r=0.05$, $R=0.5$ for column 2. 
-%%Could adjust padding (too much whitespace where there is no axis label). 
-%%It also seems could increase ratio of font size relative to plot size to make figure more compact. 
-%%Matt - could you uncomment the line legends in the Mathematica file (function not included in my Mathematica version).
-%Add chromosome cartoons to depict recombination rates?
-%}
-%}
-%\label{fig:Combination_Turnover}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Heterogametic transitions with/without sex ratio change
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\begin{tikzpicture}[remember picture]
-%	\node[] (plot) {\includegraphics[width=\linewidth]{Combination_Turnover_Ratio}};
-%	\node[above = -1cm of plot, xshift = -100] () {XY $\rightarrow$ ZW};
-%	\node[above = -1cm of plot, xshift = 90] () {ZW $\rightarrow$ XY};
-%\end{tikzpicture}
-%\caption{
-%%\textcolor{red}{Is this what Sally was thinking?}
-%%\textcolor{blue}{I think this works but I'm confused as to why the speed of spread should be so much different for XY and ZW here.
-Figure \ref{fig:Combination_Turnover} and \ref{fig:Combination_Centimorgans} suggests that there's not much difference between XY->ZW and ZW->XY.
-Maybe we should just stick with the 4 cases in figure \ref{fig:Combination_Turnover}.
-}
-%%\textcolor{red}{i messed up and had $r=0.5$ instead of $r=0.05$ for B and D. haven't fixed fitness plot below.}
-%Heterogametic transitions occur (panels A and B) regardless of sex ratio biases (panels C and D).
-%A neo-W invades (panel A) and equalizes the male-biased sex ratio (panel C) that was caused by meiotic drive in males.
-%A neo-Y invades (panel B) a population with an equal sex ratio. 
-%With any amount of linkage ($R<1/2$), the neo-Y becomes associated with the driving allele in males, and in the end causes a male bias.
-%Parameters: $s^\female = s^\male = 1/5$, $h^\female = h^\male = 7/10$, $t^\female = t^\male=0$, $\alpha^\female_\Delta = 0$, $\alpha^\male_\Delta = -1/5$, $r = 1/20$.
-%}
-%\label{fig:Combination_Turnover_Ratio}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%Changes in mean fitness
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\begin{tikzpicture}[remember picture]
-%	\node[] (plot) {\includegraphics[width=\linewidth]{Combination_Fitness_Rec}};
-%	\node[above = -1cm of plot, xshift = -100] () {XY $\rightarrow$ ZW};
-%	\node[above = -1cm of plot, xshift = 90] () {ZW $\rightarrow$ XY};
-%\end{tikzpicture}
-%\caption{
-%\textcolor{red}{This complicated thing matches the plot above. I don't think we want to include it...?}
-%}
-%\label{fig:Combination_Fitness_Rec}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Changes in mean fitness
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\begin{tikzpicture}[remember picture]
-%	\node[] (plot) {\includegraphics[width=\linewidth]{Combination_MeanFit}};
-%	\node[above = 0cm of plot, xshift = -70] () {$r=0.5$, $R=0.05$};
-%	\node[above = 0cm of plot, xshift = 120] () {$r=0.05$, $R=0.5$};
-%	\node[left = 0cm of plot, yshift = 105, rotate = 90] () {XY $\rightarrow$ ZW};
-%	\node[left = 0cm of plot, yshift = -20, rotate = 90] () {ZW $\rightarrow$ XY};
-%\end{tikzpicture}
-%\caption{
-%Changes in mean diploid fitness of males (blue lines), females (red lines), and the entire population (black lines) during the transitions between sex-determination systems shown in Figure \ref{fig:Combination_Turnover}.
-%Here mean diploid fitness of a particular sex is its mean diploid viability fitness times twice its frequency in the population, to capture the fact that epistatically dominant sex-determining alleles can also invade because they selfishly make more of the sex they are in.
-%The mean fitness of females increases during the spread of neo-W alleles (A and B) and the mean fitness of males increases during the spread of neo-Y alleles (C and D). 
-%However, when a neo-sex determining system evolves that is less closely linked to a locus under selection (B and D), population mean fitness decreases. 
-%%\textcolor{red}{
-%%Could add titles to the columns/rows: neo-W for row 1, neo-Y for row 3, $r=0.5$, $R=0.05$ for column 1 and $r=0.05$, $R=0.5$ for column 2. 
-%%%\& possibly adjust padding (too much whitespace?). 
-%%%Matt - could you uncomment the line legends in the Mathematica file (function not included in my Mathematica version).
-%%}
-%%\textcolor{red}{I'm still confused why male and female mean fitnesses aren't normalized by their frequency.
-I'm not sure we should be calling them means without this normalization step.
-Or we should justify this by saying that mean fitness also has something to do with the number of a sex, i.e., multiply *real* mean fitness in females by freqfemale/(1/2)?
-See the next figure for what happens when we do normalize.}
-%\textcolor{blue}{I think we should give this plot showing (male mean fitness * freq males) and (female mean fitness * freq females), without multiplying by 2 (leave off black lines, population mean fitness).
-%We could also re-plot the sex ratios on this same scale. 
-%The plot below, `adjusted for sex ratio', could then go in the appendix.
-The point is that neo-W (neo-Y) can invade when the frequency of females (males) multiplied by their mean fitness increases.
-}
-%}
-%\label{fig:Combination_MeanFit}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Changes in mean fitness corrected for sex ratio
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\begin{tikzpicture}[remember picture]
-%	\node[] (plot) {\includegraphics[width=\linewidth]{Combination_MeanFit_Corrected}};
-%\end{tikzpicture}
-%\caption{
-%\textcolor{red}{Last plot with mean fitness of sexes corrected for sex ratio. Could add to previous plot with dashed lines?}
-%}
-%\label{fig:Combination_MeanFit_Corrected}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%Chromosomal Positions
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%%\includegraphics[width=\linewidth]{Combination_Centimorgan}\\
-%%\includegraphics[width=\linewidth]{PositionPlot}\\
-%\begin{tikzpicture}[remember picture]
-%%	\node[] () {\includegraphics[width=\linewidth]{PositionPlot}};
-%	\node[] () {\includegraphics[width=0.5\linewidth]{PositionPlot_2}};
-%%	\node[anchor=east] at (0, 1.5) {\footnotesize diploid sex-antagonism}; %, $s^\male s^\female < 0$};
-%%	\node[anchor=east] at (6.5, 1.5) {\footnotesize haploid sex-antagonism}; %, $s^\male s^\female > 0$};
-%%	\node[anchor=east] at (0, -3) {\footnotesize male drive (ploidy-antagonism)}; %, $s^\male < s^\female$};
-%%	\node[anchor=east] at (6.5, -3) {\footnotesize find something interesting to plot};%, $s^\female < s^\female$};
-%%	\node[anchor=center] at (-1.3, 4.25) {\scriptsize tighter sex-linkage};
-%%	\node[anchor=center] at (2.45, 3.5) {\scriptsize ancestral SDR};
-%%	\draw[->,thick] (2.45, 3.25) -- (2.45, 2.5);
-%%	\node[anchor=center] at (-1.4, -0.25) {\scriptsize novel SDR};
-%%	\draw[->,thick] (-1.4, -0.5) -- (-1.4, -1);
-%\end{tikzpicture}
-%\caption{
-% A neo-W can invade an XY system under a large number of selective regimes.
-%%Invasion fitness of a neo-sex-determining allele against the relative genomic location of a locus under direct selection. 
-%% (neo-Y invading ZW in black, neo-W invading XY in red)
-%%The ancestral sex-determining locus is located at -25 and the novel sex-determining locus is located at 25. %and that there is a polymorphism at the \textbf{A} locus maintained by selection.
-%%Thus, if the neo-sex-determining allele invades in the gray region the system evolves tighter sex-linkage.  
-%In panel A, there is no haploid selection ($t^\Hermaphrodite=\alpha^\Hermaphrodite_{\Delta}=0$) and selection in diploids is sexually antagonistic ($s^\male=-s^\female=1/10$, $h^\male=1-h^\female=3/10$), in which case the neo-sex-determining allele can only invade if it is more closely linked to the selected locus ($R<r$, gray region; but see Figure \ref{fig:SexAntagTighter}B).
-%In panel B, there is no diploid selection ($s^\Hermaphrodite=0$) and selection in haploids is sexually antagonistic ($t^\male=-t^\female=0.08$, $\alpha^\Hermaphrodite_{\Delta}=0$), in which case the neo-sex-determining allele can invade regardless of linkage.
-%In panel C, selection in diploids ($s^\male=s^\female=1/10$, $h^\male=h^\female=7/10$) opposes drive in males ($\alpha^\male_{\Delta}=-0.05$, $t^\Hermaphrodite=\alpha^\female_{\Delta}=0$), in which case the neo-sex-determining allele can once again invade regardless of linkage.
-%We use Haldane's map function \citep[Equation 3 in ][]{Haldane1919} to convert from map distance (centiMorgans, cM) to the probability of a cross-over event.    
-%%we include haploid selection. %and assume that selection in diploids is not sexually-antagonistic ($s^\female s^\male>0$). 
-%%A polymorphism can then be maintained by opposing selection between the haploid and diploid phases. 
-%%In B, there is drive in favour of the $a$ allele in males ($\alpha^\male_{\Delta}=-1/20$), no female meiotic drive or gametic competition, $t^\Hermaphrodite=\alpha^\female_{\Delta}=0$), and equal selection in diploid sexes ($s^\female=s^\male=1/10$, $h^\female=h^\male=7/10$).
-%%In this case, a neo-W can invade even when the selected locus is more closely linked to the ancestral sex determining locus (see Table \ref{tab:specialcases} and Figure \ref{fig:Combination_Turnover}).
-%%In C and D, there is gametic competition among male gametes only (favouring $a$, $t^\male=-1/10$) and no meiotic drive or gametic competition in females ($t^\female=\alpha^\Hermaphrodite_{\Delta}=0$).
-%%In this case, the neo-W does not invade if $s^\female>s^\male$ (panel C: $s^\female=3/20$, $s^\male=1/20$) but does if $s^\female<s^\male$ (panel D: $s^\female=1/20$, $s^\male=3/20$), see Table \ref{tab:specialcases}.\\
-%%\textcolor{red}{
-%%1.
-I suspect that panel C has a region where no equilibrium is maintained (CHECK!
-Maybe include different parameters here or remove the part when no equilibrium).
-MMO: If you trust the sieve function there are stable equilibria across the entire range, although they differ greatly between XY and ZW systems near -25cM.
-%%\\
-%%2.
-Currently use different parameters for B than using in figure \ref{fig:Combination_Turnover} (selection/drive twice as strong in turnover figure).
-MMO: this is to keep it within the bounds of the plot -- using the same parameters as figure 1 makes the peak at -25 reach roughly 0.1, and then it is difficult to see the details of A,C, and D.
-%%%This plot would also benefit from titles giving, e.g., ``sexually-antagonistic selection, $s^\female s^\male<0$'' for A, ``male meiotic drive, $s^\female s^\male>0$'' for B
-%%}
-%}
-%\label{fig:Combination_Centimorgans}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%Haplotype invasion region plot
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\begin{tikzpicture}[remember picture]
-%	\node[] () {
-%	\includegraphics[width=0.5\linewidth]{regionplot_2a}
-%	\includegraphics[width=0.5\linewidth]{regionplot_hap}
-%	};
-%\end{tikzpicture}
-%\caption{
-%Parameter space (gray) where both neo-W haplotypes can invade from the same stable resident $r=0$ equilibria (equations \ref{eq:tightequil}), and therefore where an unlinked neo-W can invade an XY system with perfect sex-linkage.
-%\textbf{A}, In the absence of haploid selection, both neo-W haplotypes can invade for much of the parameter space where the relative fitnesses of male homozygotes, $w_{AA}^\male$ and $w_{aa}^\male$, are both less than that of the heterozygote, $w_{Aa}^\male = 1$.
-%In the white region neo-W haplotypes paired with the allele fixed on the Y cannot invade.
-%Parameters as in \cite{Otto2014} Figure 2a: $w_A^\Hermaphrodite=w_a^\Hermaphrodite$, $\alpha^\Hermaphrodite=1/2$, $w_{Aa}^\Hermaphrodite=1$, and $w_{AA}^\female=w_{aa}^\female=0.75$.
-%\textbf{B}, When selection is the same in both diploid sexes ($w_{aa}^\Hermaphrodite = 1$, $w_{Aa}^\Hermaphrodite = 1 + h s$, $w_{AA}^\Hermaphrodite = 1+s$), both neo-W haplotypes can invade over a portion of the parameter space where selection in diploids ($s$) opposes the force of drive during meiosis in males ($\alpha_{\Delta}^\male$).
-%Parameters: $w_A^\Hermaphrodite=w_a^\Hermaphrodite$, $\alpha^\female=1/2$, $h=1/2$.
-%}
-%\label{fig:regionplot_2a}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%W invades XY and fixes
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}
-%\centering
-%\includegraphics[width=0.5\linewidth]{FreqWLowR}\\
-%\includegraphics[width=0.5\linewidth]{SexRatioLowR}\\
-%\includegraphics[width=0.5\linewidth]{MeanDipFitLowR}
-%\caption{
-%Haploid selection allows a neo-$W$ to invade an ancestral $XY$ system and fix (\textbf{A}) despite temporarily biasing the sex ratio further (\textbf{B}) and decreasing mean diploid viability fitness (\textbf{C}).
-%Complete turnover between genetic sex-determination systems occurs despite the neo-$W$ being less tightly linked to the selected locus than the ancestral sex-determining locus is, $R>r$.
-%Parameters: $k=1$, $s^\female = 0.05$, $s^\male = 0.15$, $h^\female = h^\male = 0.7$, $t^\female = 0$, $t^\male = -0.1$, $\alpha^\male = \alpha^\female = 1/2$, $r=0.01$, $R=0.05$.
-%}
-%\label{fig:WinvasionLowR}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%W invades XY but does not fix
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}
-%\centering
-%\includegraphics[width=0.5\linewidth]{FreqWHighR}\\
-%\includegraphics[width=0.5\linewidth]{SexRatioHighR}\\
-%\includegraphics[width=0.5\linewidth]{MeanDipFitHighR}
-%\caption{
-%Haploid selection allows a completely unlinked neo-$W$ to invade an ancestral $XY$ system (\textbf{A}) despite further biasing the sex ratio (\textbf{B}) and decreasing mean diploid viability fitness (\textbf{C}).
-%The neo-$W$ does not fix (although variation at the \textbf{A} locus is maintained, $V_A>0$), resulting in a polymorphic sex-determination system.
-%Parameters as in Figure \ref{fig:WinvasionLowR} but with $R=0.5$.
-%}
-%\label{fig:WinvasionHighR}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%W invades for all rates of recombination with selected locus
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}
-%\centering
-%\includegraphics[width=0.5\linewidth]{InvasionVsRecombination}
-%\caption{
-%A neo-$W$ invades an ancestral $XY$ system with haploid selection regardless of how tightly it is linked to the selected locus. 
-%Parameters as in Figure \ref{fig:WinvasionLowR}.
-%}
-%\label{fig:InvasionVsRecombination}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%W invasion versus position of selected locus
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}
-%\centering
-%\includegraphics[width=0.5\linewidth]{InvasionVsCentiMorgans}
-%\includegraphics[width=0.5\linewidth]{InvasionVsCentiMorgansAllOrders}
-%\caption{
-%Haploid selection allows a neo-$W$ to invade an ancestral $XY$ system regardless of how tightly it and the ancestral sex-determining locus are linked to the selected locus. 
-%The ancestral sex-determining locus is located at -0.05 and the novel sex-determining locus is located at 0.05 (corresponding to the peaks of invasion fitness), such that the probability of a cross-over between them is $\approx0.1$.
-%The x-axis gives the position of the locus under haploid selection.
-%We used Haldane's map function \citep[Equation 3 in ][]{Haldane1919} to convert from map distance (centiMorgans) to the probability of a cross-over event. 
-%Parameters as in Figure \ref{fig:WinvasionLowR}.
-%}
-%\label{fig:InvasionVsCentiMorgans}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Y invades ZW and fixes (counter example to Kozi explanation)
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}
-%\centering
-%\includegraphics[width=0.5\linewidth]{FreqWCounterKozi}\\
-%\includegraphics[width=0.5\linewidth]{SexRatioCounterKozi}\\
-%\includegraphics[width=0.5\linewidth]{MeanDipFitCounterKozi}
-%\caption{
-%Meiotic drive allows a neo-$Y$ to invade an ancestral $ZW$ system and fix (\textbf{A}) despite temporarily biasing the sex ratio (\textbf{B}).
-%and decreasing mean diploid viability fitness (\textbf{C}).
-%Parameters: $k=0$, $s^\female = s^\male = t^\female = t^\male = 0$, $\alpha^\male = 0.4$, $\alpha^\female = 1/2$, $r=0$, $R=0$.
-%}
-%\label{fig:CounterKozi}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\setcounter{equation}{0}
-\renewcommand{\theequation}{S.\arabic{equation}}
-\setcounter{figure}{0}
-\renewcommand{\thefigure}{S.\arabic{figure}}
-\setcounter{table}{0}
-\renewcommand{\thetable}{S.\arabic{table}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-
-\section*{Appendix}
-
-\subsection*{Recursion equations}
-\label{app:recurs}
-
-%\textcolor{red}{Should we adjust the subscripts throughout this subsection?
-Right now we end up re-defining $i$ and $j$ (when switching from haploid to diploid; this might have been my doing!) and then introduce three new subscripts $b$, $c$, and $l$, all of which can be derived from $i$ and $j$.
-Might be more straightforward to just use $p^\Hermaphrodite_{x_1,x_2,a_1,a_2,m_1,m_2}$ where 1 is maternal and 2 is paternal?
-We then no longer have to switch indices from haploid to diploid and the connection to other variables is clear: $b=m_1m_2$, $c=x_1x_2$, and $l=a_1a_2$.
-I guess the downside will be re-writing the recursion equations...
-which is why I haven't gone ahead and tried this.}
-
-In each generation we census the genotype frequencies in male and female gametes/gametophytes (hereafter, gametes) between meiosis (and any meiotic drive) and gametic competition. 
-At this stage we denote the frequencies of X- and Y-bearing gametes from males and females $x_{i}^{\Hermaphrodite}$ and $y_{i}^{\Hermaphrodite}$.
-The superscript $\Hermaphrodite \in \{\male,\female\}$ specifies the sex of the diploid that the gamete came from. 
-The subscript $i\in\{1,2,3,4\}$ specifies the genotype at the selected locus $\mathbf{A}$ and at the novel sex-determining locus $\mathbf{M}$, where $1=AM$, $2=aM$, $3=Am$, and $4=am$. 
-The gamete frequencies from each sex sum to one, $\sum_{i}x_{i}^{\Hermaphrodite}+y_{i}^{\Hermaphrodite}=1$.
-
-Competition then occurs among gametes of the same sex (e.g., among eggs and among sperm separately) according to the genotype at the \textbf{A} locus ($w_{1}^\Hermaphrodite=w_{3}^\Hermaphrodite=w_{A}^\Hermaphrodite$, $w_{2}^\Hermaphrodite=w_{4}^\Hermaphrodite=w_{a}^\Hermaphrodite$, see Table \ref{tab:fitnesstable}).
-The genotype frequencies after gametic competition are $x_{i}^{\Hermaphrodite,s}= w_{i}x_{i}^{\Hermaphrodite}/\bar{w}_{H}^{\Hermaphrodite}$ and $y_{i}^{\Hermaphrodite,s}= w_{i}y_{i}^{\Hermaphrodite}/\bar{w}_{H}^{\Hermaphrodite}$, where $\bar{w}_{H}^{\Hermaphrodite}=\sum_{i} w_{i}x_{i}^{\Hermaphrodite}+w_{i}y_{i}^{\Hermaphrodite}$ is the mean fitness of male ($\Hermaphrodite=\male$) or female ($\Hermaphrodite=\female$) gametes.
-
-Random mating then occurs between gametes to produce diploid zygotes.
-%To shorten notation we now use index $i$ (and $j$) to denote the alleles at both the $\mathbf{A}$ and $\mathbf{M}$ loci and label $MA=1$, $Ma=2$, $mA=3$, and $ma=4$, such that $i,j\in\{1,2,3,4\}$.
-The frequencies of XX zygotes are then denoted as $xx_{ij}$, XY zygotes as $xy_{ij}$, and YY zygotes as $yy_{ij}$, where \textbf{A} and \textbf{M} locus genotypes are given by $i,j\in\{1,2,3,4\}$, as above.
-In $XY$ zygotes, the haplotype inherited from an X-bearing gamete is given by $i$ and the haplotype from a Y-bearing gamete is given by $j$. 
-In XX and YY zygotes, individuals with diploid genotype $ij$ are equivalent to those with diploid genotype $ji$; for simplicity, we use $xx_{ij}$ and $yy_{ij}$ with $i\neq j$ to denote the average of these frequencies, $xx_{ij}=(x_{i}^{\female,s}x_{j}^{\male,s}+x_{j}^{\female,s}x_{i}^{\male,s})/2$ and $yy_{ij}=(y_{i}^{\female,s}y_{j}^{\male,s}+y_{j}^{\female,s}y_{i}^{\male,s})/2$.
-
-Denoting the \textbf{M} locus genotype by $b \in \{MM, Mm, mm\}$ and the \textbf{X} locus genotype by $c \in \{XX, XY, YY\}$, zygotes develop as females with probability $k_{bc}$. 
-Therefore, the frequencies of XX females are given by $xx_{ij}^{\female}=k_{bc}xx_{ij}$, XY females are given by $xy_{ij}^{\female}=k_{bc}xy_{ij}$, and YY females are given by $yy_{ij}^{\female}=k_{bc}yy_{ij}$.
-Similarly, XX male frequencies are $xx_{ij}^{\male}=(1-k_{bc})xx_{ij}$, XY male frequencies are $xy_{ij}^{\male}=(1-k_{bc})xy_{ij}$, and YY males frequencies are $yy_{ij}^{\male}=(1-k_{bc})yy_{ij}$.
-This notation allows both the ancestral and novel sex-determining regions to determine zygotic sex according to an XY system, a ZW system, or an environmental sex-determining system. 
-In addition, we can consider any epistatic dominance relationship between the two sex-determining loci. 
-Here, we assume that the ancestral sex-determining system (\textbf{X} locus) is XY ($k_{MMXX}=1$ and $k_{MMXY}=k_{MMYY}=0$) or ZW ($k_{MMZZ}=0$ and $k_{MMZW}=k_{MMWW}=1$) and epistatically recessive to a dominant novel sex-determining locus, \textbf{M} ($k_{Mmc}=k_{mmc}=k$).
-
-Selection among diploids then occurs according to the diploid genotype at the \textbf{A} locus, $l \in \{AA, Aa, aa\}$, for an individual of type $ij$ (see Table \ref{tab:fitnesstable}). 
-The diploid frequencies after selection in sex $\Hermaphrodite$ are given by $xx_{ij}^{\Hermaphrodite,s}=w_{l}^{\Hermaphrodite} xx_{ij}/\bar{w}^{\Hermaphrodite}$, $xy_{ij}^{\Hermaphrodite,s}=w_{l}^{\Hermaphrodite} xy_{ij}/\bar{w}^{\Hermaphrodite}$, and $yy_{ij}^{\Hermaphrodite,s}=w_{l}^{\Hermaphrodite} yy_{ij}/\bar{w}^{\Hermaphrodite}$, where $\bar{w}^{\Hermaphrodite}= \sum_{i=1}^{4}\sum_{j=1}^{4}w_{l}^{\Hermaphrodite}xx_{ij}+w_{l}^{\Hermaphrodite}xy_{ij}+w_{l}^{\Hermaphrodite}yy_{ij}$ is the mean fitness of individuals of sex $\Hermaphrodite$.
-
-Finally, these diploids undergo meiosis to produce the next generation of gametes. 
-Recombination and sex-specific meiotic drive occur during meiosis.
-%We can also assume that recombination is sex specific and/or affected by the M locus - but generally we don't so I just describe $R=R_{f}=R, r_{MM,d}=r_{Mm,d}=r_{mm,d}=r, \chi_{m}=\chi_{f}=\chi$.
-Here, we allow any relative locations for the SDR, \textbf{A}, and \textbf{M} loci by using three parameters to describe the recombination rates between them. 
-$R$ is the recombination rate between the \textbf{A} locus and the \textbf{M} locus, $\rho$ is the recombination rate between the \textbf{M} locus and the \textbf{X} locus, and $r$ is the recombination rate between the \textbf{A} locus and the \textbf{X} locus.
-Table \ref{tab:chisubstitutions} shows replacements that can be made for each possible ordering of the loci assuming that there is no cross-over interference.
-During meiosis in sex $\Hermaphrodite$, meiotic drive occurs such that, in $Aa$ heterozygotes, a fraction $\alpha^{\Hermaphrodite}$ of gametes produced carry the $A$ allele and $(1-\alpha^\Hermaphrodite)$ carry the $a$ allele.
-
 \begin{table}[ht]
@@
 \end{table}
-
-Among gametes from sex $\Hermaphrodite$, the frequencies of haplotypes (before gametic competition) in the next generation are given by
-
-\begingroup
-\allowdisplaybreaks
-\begin{subequations}
-\begin{align}
-%
-\begin{split}
-x_{1}^{{\Hermaphrodite}'}=&xx_{11}^{\Hermaphrodite,s}+xx_{13}^{\Hermaphrodite,s}/2+(xx_{12}^{\Hermaphrodite,s}+xx_{14}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(xx_{14}^{\Hermaphrodite,s}-xx_{23}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&+(xy_{11}^{\Hermaphrodite,s}+xy_{13}^{\Hermaphrodite,s})/2+(xy_{12}^{\Hermaphrodite,s}+xy_{14}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&- r(xy_{12}^{\Hermaphrodite,s}-xy_{21}^{\Hermaphrodite,s})\alpha^\Hermaphrodite - \rho(xy_{13}^{\Hermaphrodite,s}-xy_{31}^{\Hermaphrodite,s})/2\\
-&+\big{[}-(R+r+\rho)xy_{14}^{\Hermaphrodite,s} +(R+\rho-r)xy_{41}^{\Hermaphrodite,s}\\
-&+(R+r-\rho) xy_{23}^{\Hermaphrodite,s}+(R+\rho-r)xy_{32}^{\Hermaphrodite,s}\big{]}\alpha^\Hermaphrodite/2
-\end{split}
-\\
-%
-\begin{split}
-x_{2}^{{\Hermaphrodite}'}=&xx_{22}^{\Hermaphrodite,s}+xx_{24}^{\Hermaphrodite,s}/2+(xx_{12}^{\Hermaphrodite,s}+xx_{23}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(xx_{23}^{\Hermaphrodite,s}-xx_{14}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&(xy_{22}^{\Hermaphrodite,s}+xy_{24}^{\Hermaphrodite,s})/2+(xy_{21}^{\Hermaphrodite,s}+xy_{23}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite)\\
-&- r(xy_{21}^{\Hermaphrodite,s}-xy_{12}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite) - \rho(xy_{24}^{\Hermaphrodite,s}-xy_{42}^{\Hermaphrodite,s})/2\\
-&+\big{[}-(R+r+\rho)xy_{23}^{\Hermaphrodite,s}+(R+\rho-r)xy_{32}^{\Hermaphrodite,s}\\
-&+(R+r-\rho) xy_{14}^{\Hermaphrodite,s}+(R+\rho-r)xy_{41}^{\Hermaphrodite,s}\big{]}(1-\alpha^\Hermaphrodite)/2
-\end{split}
-\\
-%
-\begin{split}
-x_{3}^{{\Hermaphrodite}'}=&xx_{33}^{\Hermaphrodite,s}+xx_{13}^{\Hermaphrodite,s}/2+(xx_{23}^{\Hermaphrodite,s}+xx_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(xx_{23}^{\Hermaphrodite,s}-xx_{14}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&(xy_{33}^{\Hermaphrodite,s}+xy_{31}^{\Hermaphrodite,s})/2+(xy_{32}^{\Hermaphrodite,s}+xy_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&- r(xy_{34}^{\Hermaphrodite,s}-xy_{43}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite - \rho(xy_{31}^{\Hermaphrodite,s}-xy_{13}^{\Hermaphrodite,s})/2\\
-&+\big{[}-(R+r+\rho)xy_{32}^{\Hermaphrodite,s} +(R+\rho-r)xy_{23}^{\Hermaphrodite,s}\\
-&+(R+r-\rho) xy_{41}^{\Hermaphrodite,s}+(R+\rho-r)xy_{14}^{\Hermaphrodite,s}\big{]} \alpha^\Hermaphrodite/2
-\end{split}
-\\
-%
-\begin{split}
-x_{4}^{{\Hermaphrodite}'}=&xx_{44}^{\Hermaphrodite,s}+xx_{34}^{\Hermaphrodite,s}/2+(xx_{14}^{\Hermaphrodite,s}+xx_{24}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(xx_{14}^{\Hermaphrodite,s}-xx_{23}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&(xy_{44}^{\Hermaphrodite,s}+xy_{42}^{\Hermaphrodite,s})/2+(xy_{41}^{\Hermaphrodite,s}+xy_{43}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite)\\
-&- r(xy_{43}^{\Hermaphrodite,s}-xy_{34}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite) - \rho(xy_{42}^{\Hermaphrodite,s}-xy_{24}^{\Hermaphrodite,s})/2\\
-&+\big{[}-(R+r+\rho)xy_{41}^{\Hermaphrodite,s}+(R+\rho-r)xy_{14}^{\Hermaphrodite,s}\\
-&+(R+r-\rho) xy_{32}^{\Hermaphrodite,s}+(R+\rho-r)xy_{23}^{\Hermaphrodite,s}\big{]}(1-\alpha^\Hermaphrodite)/2
-\end{split}
-\\
-\begin{split}
-y_{1}^{{\Hermaphrodite}'}=&yy_{11}^{\Hermaphrodite,s}+yy_{13}^{\Hermaphrodite,s}/2+(yy_{12}^{\Hermaphrodite,s}+yy_{14}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(yy_{14}^{\Hermaphrodite,s}-yy_{23}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&(xy_{11}^{\Hermaphrodite,s}+xy_{31}^{\Hermaphrodite,s})/2+(xy_{21}^{\Hermaphrodite,s}+xy_{41}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&- r(xy_{21}^{\Hermaphrodite,s}-xy_{12}^{\Hermaphrodite,s})\alpha^\Hermaphrodite - \rho(xy_{31}^{\Hermaphrodite,s}-xy_{13}^{\Hermaphrodite,s})/2\\
-&+\big{[} - (R+r+\rho)xy_{41}^{\Hermaphrodite,s} + (R+\rho-r)xy_{14}^{\Hermaphrodite,s}\\
-& + (R+r-\rho)xy_{32}^{\Hermaphrodite,s} + (R+\rho-r) xy_{23}^{\Hermaphrodite,s}\big{]}\alpha^\Hermaphrodite/2
-\end{split}
-\\
-%
-\begin{split}
-y_{2}^{{\Hermaphrodite}'}=&yy_{22}^{\Hermaphrodite,s}+yy_{24}^{\Hermaphrodite,s}/2+(yy_{12}^{\Hermaphrodite,s}+yy_{23}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(yy_{23}^{\Hermaphrodite,s}-yy_{14}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&(xy_{22}^{\Hermaphrodite,s}+xy_{42}^{\Hermaphrodite,s})/2+(xy_{12}^{\Hermaphrodite,s}+xy_{32}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite)\\
-&- r(xy_{12}^{\Hermaphrodite,s}-xy_{21}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite) - \rho(xy_{42}^{\Hermaphrodite,s}-xy_{24}^{\Hermaphrodite,s})/2\\
-&+\big{[}-(R+r+\rho)xy_{32}^{\Hermaphrodite,s} +(R+\rho-r) xy_{23}^{\Hermaphrodite,s}\\
-&+(R+r-\rho)xy_{41}^{\Hermaphrodite,s}+(R+\rho-r)xy_{14}^{\Hermaphrodite,s}\big{]}(1-\alpha^\Hermaphrodite)/2
-\end{split}
-\\
-%
-\begin{split}
-y_{3}^{{\Hermaphrodite}'}=&yy_{33}^{\Hermaphrodite,s}+yy_{13}^{\Hermaphrodite,s}/2+(yy_{23}^{\Hermaphrodite,s}+yy_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(yy_{23}^{\Hermaphrodite,s}-yy_{14}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&(xy_{33}^{\Hermaphrodite,s}+xy_{13}^{\Hermaphrodite,s})/2+(xy_{23}^{\Hermaphrodite,s}+xy_{43}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&- r(xy_{43}^{\Hermaphrodite,s}-xy_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite - \rho(xy_{13}^{\Hermaphrodite,s}-xy_{31}^{\Hermaphrodite,s})/2\\
-&+\big{[}-(R+r+\rho)xy_{23}^{\Hermaphrodite,s} +(R+\rho-r)xy_{32}^{\Hermaphrodite,s}\\
-&+(R+r-\rho) xy_{14}^{\Hermaphrodite,s} + (R+\rho-r) xy_{41}^{\Hermaphrodite,s}\big{]}\alpha^\Hermaphrodite/2
-\end{split}
-\\
-%
-\begin{split}
-y_{4}^{{\Hermaphrodite}'}=&yy_{44}^{\Hermaphrodite,s}+yy_{34}^{\Hermaphrodite,s}/2+(yy_{14}^{\Hermaphrodite,s}+yy_{24}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(yy_{14}^{\Hermaphrodite,s}-yy_{23}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&(xy_{44}^{\Hermaphrodite,s}+xy_{24}^{\Hermaphrodite,s})/2+(xy_{14}^{\Hermaphrodite,s}+xy_{34}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite)\\
-&- r(xy_{34}^{\Hermaphrodite,s}-xy_{43}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite) - \rho(xy_{24}^{\Hermaphrodite,s}-xy_{42}^{\Hermaphrodite,s})/2\\
-&+\big{[}-(R+r+\rho) xy_{14}^{\Hermaphrodite,s} + (R+\rho-r)xy_{41}^{\Hermaphrodite,s}\\
-&+(R+r-\rho) xy_{23}^{\Hermaphrodite,s} + (R+\rho-r) xy_{32}^{\Hermaphrodite,s}\big{]}(1-\alpha^\Hermaphrodite)/2
-\end{split}
-\end{align}
-\label{eq:recursions}
-\end{subequations}
-
-\endgroup
-
-\noindent
-The full system is therefore described by 16 recurrence equations (three diallelic loci in two sexes, $2^3 \times 2 = 16$). 
-However, not all diploid types are produced under certain sex-determination systems. 
-For example, with the $M$ allele fixed and an ancestral $XY$ sex-determining system, there are $XX$ males, $XY$ females, or $YY$ females ($x_{3}^\Hermaphrodite=x_{4}^\Hermaphrodite=y_{4}^\Hermaphrodite=y_{3}^\Hermaphrodite=y_{i}^\female=0$).
-%($xx_{11}^{\male}=xx_{12}^{\male}=xx_{22}^\male=xy_{11}^{\female}=xy_{12}^{\female}=xy_{21}^{\female}=xy_{22}^\female=yy_{11}^{\female}=yy_{12}^{\female}=yy_{22}^\female=0$). 
-In this case, the system only involves six recursion equations, %because there is only one \textbf{M} locus allele and no Y-bearing female gametes. 
-which we assume below to calculate the equilibria.
-
-%I think this should be moved below because we have some 'results' where we don't assume weak selection but we only have the equilibrium calculated analytically for weak selection.
-
-\subsection*{Resident equilibria and stability}
-
-In the resident population (allele $M$ fixed), we follow the frequency of $A$ in X-bearing female gametes, $p^\female_X$, and X-bearing male gametes, $p^\male_X$, and Y-bearing male gametes, $p^\male_Y$.
-We also track the total frequency of Y among male gametes, $q$, which may deviate from $1/2$ due to meiotic drive in males. 
-These four variables determine the frequencies of the six resident gamete types: $x_{1}^{\female}=\hat{p}_X^\female$, $x_{2}^{\female}=1-\hat{p}_X^\female$, $x_{1}^{\male}=(1-q)\hat{p}_X^\male$, $x_{2}^{\male}=(1-q)(1-\hat{p}_X^\male)$, $y_{1}^{\male}=q \hat{p}_Y^\male$, and $y_{2}^{\male}=q(1-\hat{p}_Y^\male)$.
-Mean fitnesses in the resident population are given in table \ref{tab:meanfitnesses}.
-
-Various forms of selection can maintain a polymorphism at the \textbf{A} locus, including sexually antagonistic selection, overdominance, conflicts between diploid selection and selection upon haploid genotypes \citep[ploidally antagonistic selection,][]{Immler:2012tl}, or a combination of these selective regimes (see below).
 
@@
 \end{table}
-
-In particular special cases, e.g., no sex-differences in selection or meiotic drive ($s^\male=s^\female$, $h^\male=h^\female$, and $\alpha^\male=\alpha^\female=1/2$), the equilibrium allele frequency and stability can be calculated analytically without assuming anything about the relative strengths of selection and recombination.
-However, here, we focus on two regimes (tight linkage and weak selection) in order to make fewer assumptions about fitnesses.
-
-\subsubsection*{Recombination weak relative to selection (tight linkage between \textbf{A} and \textbf{X})}
-
-We first calculate the equilibrium frequency of the Y and $A$ alleles in the ancestral population when the recombination rate between the \textbf{X} and \textbf{A} loci is small ($r$ of order $\epsilon$).
-Selection at the \textbf{A} locus will not affect evolution at the novel sex-determining locus, \textbf{M}, if one allele is fixed on all backgrounds. 
-We therefore focus on the five equilibria that maintain both $A$ and $a$ alleles, four of which are given to leading order by:
-
-\begin{subequations}\label{eq:tightequil}
-\begin{align}
-(A)\ \ \ &\hat{p}_{Y}^{\male}=0,
-\ \hat{q}=\frac{1}{2}\left(1 - \alpha_\Delta^\male \frac{ w_{Aa}^{\male} \phi}{w_{Aa}^{\male} \phi+ w_{aa}^{\male} \psi}\right),\\
-&\hat{p}_{X}^{\female}=\frac{w_{a}^{\female} \phi}{w_{a}^{\female} \phi+ w_{A}^{\female} \psi},
-\ \hat{p}_{X}^{\male}=\frac{(1+\alpha_\Delta^\male)w_{Aa}^{\male} \phi}{(1+\alpha_\Delta^\male)w_{Aa}^{\male} \phi +w_{aa}^{\male} \psi} \nonumber \\
-(A')\ \ \ &\hat{p}_{Y}^{\male}=1,
-\ \hat{q}=\frac{1}{2}\left(1 + \alpha_\Delta^\male \frac{w_{Aa}^{\male} \phi'}{w_{Aa}^{\male} \phi' + w_{AA}^{\male} \psi'}\right),\\
-&\hat{p}_{X}^{\female}=1-\frac{w_{A}^{\female} \phi'}{w_{A}^{\female} \phi'+ w_{a}^{\female} \psi'},
-\ \hat{p}_{X}^{\male}=1-\frac{(1-\alpha_\Delta^\male)w_{Aa}^{\male} \phi'}{(1-\alpha_\Delta^\male)w_{Aa}^{\male} \phi'+w_{AA}^{\male} \psi'} \nonumber \\
-(B)\ \ \ &\hat{p}_{Y}^{\male}=0,\ \hat{p}_{X}^{\female}=1,\ \hat{p}_{X}^{\male}=1, \ \hat{q}=(1 -\alpha^\male_\Delta)/2\\
-(B')\ \ \ &\hat{p}_{Y}^{\male}=1,\ \hat{p}_{X}^{\female}=0,\ \hat{p}_{X}^{\male}=0, \ \hat{q}=(1+\alpha^\male_\Delta)/2
-\end{align}
-\end{subequations}
-\begin{equation*}
-\begin{split}
-\phi=&(1+\alpha^\female_\Delta) w_{A}^{\female} w_{Aa}^{\female} \left[ w_{a}^{\male} w_{aa}^{\male} + (1+\alpha_\Delta^\male) w_{A}^{\male} w_{Aa}^{\male} \right]/2 - w_{a}^{\male} w_{a}^{\female} w_{aa}^{\male} w_{aa}^{\female} \\
-\psi=&(1-\alpha^\female_\Delta) w_{a}^{\female} w_{Aa}^{\female} \left[ w_{a}^{\male} w_{aa}^{\male} + (1+\alpha_\Delta^\male) w_{A}^{\male} w_{Aa}^{\male}\right]/2 - (1+\alpha_\Delta^\male) w_{A}^{\male} w_{A}^{\female} w_{Aa}^{\male} w_{AA}^{\female}\\
-\phi'=&(1-\alpha^\female_\Delta) w_{a}^{\female} w_{Aa}^{\female} \left[ w_{A}^{\male} w_{AA}^{\male} + (1-\alpha_\Delta^\male) w_{a}^{\male} w_{Aa}^{\male} \right]/2 - w_{A}^{\male} w_{A}^{\female} w_{AA}^{\male} w_{AA}^{\female}\\
-\psi'=&(1+\alpha^\female_\Delta) w_{A}^{\female} w_{Aa}^{\female} \left[ w_{A}^{\male} w_{AA}^{\male} + (1-\alpha_\Delta^\male) w_{a}^{\male} w_{Aa}^{\male} \right]/2 - (1-\alpha_\Delta^\male) w_{a}^{\male} w_{a}^{\female} w_{Aa}^{\male} w_{aa}^{\female}
-\end{split}
-\end{equation*}
-
-\noindent
-A fifth equilibrium $(C)$ also exists where $A$ is present at an intermediate frequency on the Y chromosome ($0<\hat{p}_{Y}^{\male}<1$). 
-However, equilibrium $(C)$ is never locally stable when $r \approx 0$ and is therefore not considered further.
-Thus, the Y can either be fixed for the $a$ allele (equilibria $A$ and $B$) or the $A$ allele (equilibria $A'$ and $B'$).
-The X chromosome can then either be polymorphic (equilibria $A$ and $A'$) or fixed for the alternative allele (equilibria $B$ and $B'$).
-Since equilibria $(A)$ and $(B)$ are equivalent to equilibria $(A')$ and $(B')$ with the labelling of $A$ and $a$ alleles interchanged, we discuss only equilibria $(A)$ and $(B)$, in which the Y is fixed for the $a$ allele.
-If there is no haploid selection ($\alpha^{\Hermaphrodite}_\Delta=0$, $w_{A}^{\Hermaphrodite}=w_{a}^{\Hermaphrodite}=1$), these equilibria are equivalent to those found by \cite{Lloyd1977} and \cite{Otto2014}.
-
-We next calculate when $(A)$ and $(B)$ are locally stable for $r=0$. 
-According to the `small parameter theory' \citep{Karlin:1972ab,Karlin:1972dq}, these stability properties are unaffected by small amounts of recombination between the SDR and \textbf{A} locus, although equilibrium frequencies may be slightly altered.
-For the $a$ allele to be stably fixed on the Y we need $\bar{w}_{Ya}^{\male} > \bar{w}_{YA}^{\male}$ where $\bar{w}_{Ya}^{\male} = w_{a}^{\male} \big[\hat{p}_X^\female(1-\alpha^\male_\Delta) w_{A}^{\female} w_{Aa}^{\male} + (1-\hat{p}_X^\female)w_{a}^{\female} w_{aa}^{\male} \big]$ and $\bar{w}_{YA}^{\male} = w_{A}^{\male} \big[ \hat{p}_X^\female w_{A}^{\female} w_{AA}^{\male} + (1-\hat{p}_X^\female)(1+\alpha^\male_\Delta) w_{a}^{\female} w_{Aa}^{\male} \big]$.
-That is, Y-$a$ haplotypes must have higher fitness than Y-$A$ haplotypes.  
-Substituting in $\hat{p}_X^\female$ from equation \eqref{eq:tightequil}, fixation of the $a$ allele on the Y requires that $\gamma_{i}>0$ where $\gamma_{(A)}=w_{a}^{\male} \big[ (1-\alpha^\male_\Delta) w_{Aa}^{\male} \phi + w_{aa}^{\male} \psi \big]-w_{A}^{\male} \big[ w_{AA}^{\male} \phi + (1 + \alpha^{\male}_\Delta)w_{Aa}^{\male} \psi \big]$ for equilibrium $(A)$ and $\gamma_{(B)}=(1-\alpha^{\male}_\Delta)w_{a}^{\male}w_{Aa}^{\male}-w_{A}^{\male}w_{AA}^{\male}$ for equilibrium $(B)$.
-Stability of a polymorphism on the X chromosome (equilibrium $A$) further requires that $\phi >0$ and $\psi >0$. 
-Fixation of the $a$ allele on the X (equilibrium $B$) can be stable only if equilibrium $(A)$ is not, as it requires $\psi<0$.
-%and $2w_{A}^{\female}w_{AA}^{\female}>(1-\alpha_\Delta^{\female})w_{a}^{\female}w_{Aa}^{\female}$ or just $4w_{A}^{\female}w_{AA}^{\female}<(1-\alpha_\Delta^{\female})w_{a}^{\female}w_{Aa}^{\female}$ (which also prevents $\psi>0$).
-
-%\textcolor{red}{check last condition and the stability condition below are correct}
-%\textcolor{blue}{The last condition looks good to me, although in your Turnover-norec-MFS.nb you look at YA fixed, so you have to flip everything (so I made Turnover-norec-MFS-MMO.nb to do this).
-%The one issue I can find here is that you can also prevent $\lambda>1$ when the slope and intercept of the quadratic at $\lambda=1$ are negative (you only looked at both being positive).
-In this case we need $4w_{A}^{\female}w_{AA}^{\female}<(1-\alpha_\Delta^{\female})w_{a}^{\female}w_{Aa}^{\female}$, which also prevents $\psi>0$.
-%I've added this in.
-%It could also be the case that the slope and intercept are the same sign but the roots are imaginary - but this is never the case here.
-%Stability condition below looks good to me (from matt version of turnoverSOM-MIKE.nb).}
-
-\subsubsection*{Selection weak relative to recombination (weak selection)}
-
-Here, we assume that selection and meiotic drive are weak relative to recombination ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon$). 
-The maintenance of a polymorphism at the \textbf{A} locus then requires that
-
-\begin{equation}
-\begin{split}
-0&< - \left[(1-h^\female)s^\female +(1-h^\male) s^\male + t^\female +t^\male + \alpha_{\Delta}^\female+\alpha_{\Delta}^\male\right]\\
-%
-\text{and }\quad 0&<h^\female s^\female +h^\male s^\male + t^\female +t^\male + \alpha_{\Delta}^\female+\alpha_{\Delta}^\male.
-\end{split}
-\end{equation}
-
-\noindent
-which indicates that a polymorphism can be maintained by various selective regimes.
-
-Given that a polymorphism is maintained at the \textbf{A} locus by weak selection, the frequencies of $A$ in each type of gamete are the same ($\hat{p}^\female_X=\hat{p}^\male_X=\hat{p}^\male_Y=\bar{p}$) and given, to leading order, by
-
-\begin{equation}
-\bar{p}=\frac{h^\female s^\female + h^\male s^\male +t^\female+t^\male+\alpha_{\Delta}^\female+\alpha_{\Delta}^\male}
-{(2h^\female-1)s^\female+(2h^\male-1)s^\male}
-+O(\epsilon)
-.
-\label{eq:pAve}
-\end{equation}
-
-\noindent
-Differences in frequency between gamete types are of $O(\epsilon)$:
-
-\begin{equation}
-\begin{split}
-\hat{p}^\male_X-\hat{p}^\female_X&=V_{A}\big{(}D^\male - D^\female +\alpha_{\Delta}^\male-\alpha_{\Delta}^\female \big{)}
-+O(\epsilon^2)\\
-%
-\hat{p}^\male_Y-\hat{p}^\female_X&=V_{A}\left[D^\male - D^\female+\alpha_{\Delta}^\male-\alpha_{\Delta}^\female+(1-2r)(t^\male-t^\female)\right]/2r
-+O(\epsilon^2)\\
-%
-\hat{p}^\male_Y-\hat{p}^\male_X&=V_{A}\left(D^\male - D^\female+\alpha_{\Delta}^\male-\alpha_{\Delta}^\female+t^\male-t^\female\right)(1-2r)/2r
-+O(\epsilon^2)
-\end{split}
-\label{eq:freq_diffs}
-\end{equation}
-
-\noindent
-where $V_{A}=\bar{p}(1-\bar{p})$ is the variance in the frequency of $A$ and $D^\Hermaphrodite=\big{[} \bar{p}s^\Hermaphrodite+(1-\bar{p})h^\Hermaphrodite s^\Hermaphrodite\big{]} -\big{[} \bar{p}h^\Hermaphrodite s^\Hermaphrodite+(1-\bar{p}) \big{]}$ corresponds to the difference in fitness between $A$ and $a$ alleles in diploids of sex $\Hermaphrodite \in \{\female,\male\}$ ($\bar{p}$ is the leading-order probability of mating with an $A$-bearing gamete from the opposite sex).
-The frequency of Y among male gametes depends upon the difference in the frequency of the $A$ allele between X- and Y-bearing male gametes and the strength of meiotic drive in favour of the $A$ allele in males, $q=1/2+\alpha_{\Delta}^\male(\hat{p}^\male_Y-\hat{p}^\male_X)/2+O(\epsilon^3)$.
-Without gametic competition or drive ($\alpha_{\Delta}^\Hermaphrodite=t^\Hermaphrodite=0$) our results reduce to those of \citet{vanDoorn:2007eu}.
-
-% the differences in the frequencies of $A$ in each type of gamete are small, as is the bias in the sex-determining factor from the heterogametic sex, and we can solve for the mean frequency of $A$ across all types ($p_A$), the difference in the frequencies of $A$ between two of the three types, and the bias in the frequency of the sex-determining factor, to first order in selection.
-%Linear stability analysis can then be used to determine the stability of this equilibrium.
-%Without haploid selection or meiotic drive our results reduce to those of \cite{vanDoorn:2007eu}.
-%when $k=0$ (neo-$Y$ invading a $ZW$ system) or when $k=1$ (neo-$W$ invading an $XY$ system) (\textcolor{red}{CHECK}).
-%However, with haploid selection or meiotic drive a stable polymorphism at locus \textbf{A} no longer requires sexually antagonistic selection.
-%, as it can also be achieved by ploidally-antagonistic selection.
-
-\subsection*{Invasion conditions}
-
-%Here, we determine whether a rare neo-Y or neo-W allele spreads when rare, which occurs when $\lambda > 1$.
-%We begin with the general result and then give explicit solutions under tight linkage and weak selection.
-
-%If the average change in frequency of the two haplotypes that carry the $m$ allele ($Am$ and $am$) is positive, invasion will always occur (i.e., if $\left\{(\lambda_{mA}-1)+ (\lambda_{ma}-1) \right\}/2 > 0$ then $\lambda > 1$, see table \ref{tab:haplotype_growth} for $\lambda_{mi}$).
-%If neither haplotype increases in frequency ($\lambda_{mA}, \lambda_{ma} < 1$), the $m$ allele will not invade. 
-%Otherwise, the new sex-determining allele increases in frequency on one \textbf{A} background and declines on the other, and invasion requires
-%\begin{equation}\label{eq:neoYR}
-%R \left[ 
-%\frac{p^\female_X w^\female_A w^\male_a (1-\alpha^\male)}{ \bar{w}^\female_H \bar{w}^\male_H (\lambda_{mA}-1)} + 
-%p^\female_X \frac{w^\female_A}{\bar{w}^\female_H} \frac{w^\male_a(1-\alpha^\male)}{\bar{w}^\male_H} \frac{1}{\lambda_{mA}-1} + 
-%\frac{(1 - p^\female_X) w^\female_a w^\male_A \alpha^\male}{ \bar{w}^\female_H \bar{w}^\male_H (\lambda_{ma}-1)} 
-%\right] 
-%\frac{w^\male_{Aa}}{q\bar{w}^\male} < 1,
-%\end{equation}
-
-%\noindent
-%for the neo-$Y$, and
-
-%\noindent
-%\begin{equation}\label{eq:neoWR}
-%R \left[ 
-%\frac{\bar{p}^\male w^\male_A w^\female_a (1-\alpha^\female)}{ \bar{w}^\male_H \bar{w}^\female_H (\lambda_{mA}-1)} + 
-%\frac{(1 - \bar{p}^\male) w^\male_a w^\female_A \alpha^\female}{ \bar{w}^\male_H \bar{w}^\female_H (\lambda_{ma}-1)} 
-%\right] 
-%\frac{w^\female_{Aa}}{(1-q)\bar{w}^\female} < 1,
-%\end{equation}
-
-%\noindent
-%for the neo-$W$.
-
-%Equations \eqref{eq:neoYR} and \eqref{eq:neoWR} show that the new sex-determining allele, $m$, is expected to invade for any probability of recombination between loci \textbf{A} and \textbf{M}, $R$, when the net flow of recombinants is from the less fit (smaller $\lambda_{mi}$) to the more fit \textbf{A} background (making the terms inside the square brackets in Equations \ref{eq:neoYR} and \ref{eq:neoWR} negative).
-%\textcolor{red}{Q: is it definitely possible to have negative square brackets for a equilibria maintained by selection?}
-%Assuming $g_A^* > 0$ and $g_a^* < 0$ without loss of generality, this is $-(1 - p^\female_X) w_{m,A} g_a^* < p^\female_X w_{m,a} g_A^*$.
-%When the net flow of recombinants is from the more fit to the less fit haplotype, the new sex-determining allele can still invade when the rate of recombination between it and the selected locus is small enough.
-%\textcolor{red}{Q:Is it the case that sometimes the square brackets are positive and invasion occurs for $r_{AM}=1/2$?
-In which case it might be better to have slightly different phrasing here.}
-%Equations \eqref{eq:neoYR} and \eqref{eq:neoWR} show that the new sex-determining allele, $m$, is expected to invade for any probability of recombination between loci \textbf{A} and \textbf{M}, $R$, when the net flow of recombinants is from the less fit (smaller $\lambda_{mi}$) to the more fit \textbf{A} background (making the terms inside the square brackets in Equations \ref{eq:neoYR} and \ref{eq:neoWR} negative).
-%When the net flow of recombinants is from the more fit to the less fit haplotype, the new sex-determining allele can still invade when the rate of recombination between it and the selected locus is small enough.
-%To better understand when these scenarios are possible we next use knowledge of the equilibria and their stability under tight linkage and weak selection.
-
-\textcolor{red}{Cover the other parts of the characteristic polynomial here.}
-\textcolor{blue}{Waiting for Sally's proof!}
-
-A rare neo-Y or neo-W will spread from a given ancestral equilibrium when the leading eigenvalue, $\lambda$, of the Jacobian matrix derived from the eight mutant recursion equations (given by \ref{eq:recursions}c,d,g,h), evaluated at the ancestral equilibrium, is greater than one.
-However, because a neo-Y (neo-W) is always in males (females) and is epistatically dominant to the ancestral sex-determining locus, we need only two recursion equations (e.g., tracking the change in the frequency of neo-Y-$A$ and neo-Y-$a$ gametes from males) and thus the leading eigenvalue is the largest solution the polynomial $\lambda^2 + b\lambda + c = 0$ as described in the text (Table \ref{tab:haplotype_growth}).
-%It can be shown (see supplementary Mathematica file) that the coefficients are $b= - (\lambda_{mA} + \lambda_{ma})+(\chi_{mA} + \chi_{ma})$ and $c = (\lambda_{mA}-\chi_{mA}) (\lambda_{ma}-\chi_{ma}) -\chi_{mA} \chi_{ma}$, where $\lambda_{mi}$ is the multiplicative growth rate of the frequency of mutants on background $i\in\{A,a\}$, without accounting for loss due to recombination, and $\chi_{mi}$ is the rate at which mutants on background $i\in\{A,a\}$ recombine onto the other \textbf{A} locus background in heterozygotes.
-%The leading eigenvalue is then greater than one whenever $\lambda_{mA}>1$ and $\lambda_{ma}>1$, less than one whenever $\lambda_{mA}<1$ and $\lambda_{ma}<1$, and greater than one whenever  $\lambda_{mA}>1$ or $\lambda_{ma}>1$ and $\chi_{ma} (\lambda_{mA}-1) + \chi_{mA} (\lambda_{ma}-1) > 0$.
-
-The general conditions for the invasion of a neo-sex-determining allele are given in the main text, in terms of the growth rates of the mutant haplotypes in the absence of recombination ($\lambda_{mi}$) and the rate that recombination destroys them ($\chi_{mi}$).
-For tight linkage between the ancestral sex-determining locus and the selected locus we can calculate these terms explicitly (see below).
-For weak selection we can take a Taylor series of the leading eigenvalue. 
-The leading eigenvalue, $\lambda$, for any $k$, is given up to order $\epsilon^2$ by equation \eqref{eq:lambda_ESD_k}.
-
-\subsubsection*{Tight linkage between \textbf{A} and \textbf{X} (recombination weak relative to selection)}
-
-Here, we explore the conditions under which a neo-W invades an XY system assuming that the \textbf{A} locus is initially in tight linkage with the ancestral sex-determining region ($r \approx 0$). 
-We disregard neo-Y mutations, which never spread given that the ancestral population is at a stable equilibrium (see supplementary \textit{Mathematica} notebook for proof).
-
-Starting with the simpler equilibrium $(B)$, the terms of that determine the leading eigenvalue are
-
-\begin{subequations}\label{Binvasion}
-\begin{align}
-\lambda_{mA}&= \left[w_{A}^\male (1+\alpha^\male_\Delta) \right]^{-1}
-\frac{w_{A}^\female }{w_{A}^\female}
-\frac{\left[ w_{A}^\male (1+\alpha^\male_\Delta) w_{AA}^\female + 
-w_{a}^\male (1-\alpha^\male_\Delta) w_{Aa}^\female (1+\alpha^\female_\Delta) \right]}
-{ 2w_{AA}^\female } \\
-\lambda_{ma}&= \left[w_{A}^\male (1+\alpha^\male_\Delta) \right]^{-1}
-\frac{w_{a}^\female}{w_{A}^\female}
-\frac{\left[  w_{A}^\male (1+\alpha^\male_\Delta) w_{Aa}^\female (1-\alpha^\female_\Delta)+
-w_{a}^\male (1-\alpha^\male_\Delta) w_{aa}^\female \right]}
-{ 2w_{AA}^\female } \\
-\chi_{mA}&= \frac{1}{2} \left[w_{A}^\male (1+\alpha^\male_\Delta) \right]^{-1}
-\frac{w_{A}^\female }{w_{A}^\female}
- \frac{\left[  w_{a}^\male (1-\alpha^\male_\Delta) w_{Aa}^\female (1 + \alpha^\female_\Delta) \right]}
-{ w_{AA}^\female } \frac{R}{2}\\
-\chi_{ma}&= \frac{1}{2} \left[w_{A}^\male (1+\alpha^\male_\Delta) \right]^{-1}
-\frac{w_{a}^\female}{w_{A}^\female}
- \frac{\left[  w_{A}^\male (1+\alpha^\male_\Delta) w_{Aa}^\female (1-\alpha^\female_\Delta) \right]}
-{  w_{AA}^\female} \frac{R}{2}
-\end{align}
-\end{subequations}
-
-%\noindent
-%In this case, the zygotic sex ratio ($\zeta$) is given by the difference in haploid selection in males on $a$ (fixed on the Y) and $A$ (fixed on the X) alleles, i.e., there are more males than females if $\zeta = \alpha^\male w_A^\male / [(1-\alpha^\male)w_a^\male + \alpha^\male w_A^\male]<1/2$.
-%$\alpha^\male<1/2$ and/or $w_{a}^\male>w_{A}^\male$.
-%Populations with haploid selection for $a$ in males have a male biased zygotic sex ratio are thus more permissive to invasion by a neo-W ($\lambda_{mA}$ and $\lambda_{ma}$ larger).
-%%In addition, the spread of neo-W alleles depends on the fitness of female diploids after mating with an X-$A$ or Y-$a$ male gamete, relative to the fitness of females in the population (all have genotype $AA$ and fitness $w_{AA}^\female$ at this equilibrium).
-%Haploid selection in males has a second effect; the spread rate of neo-W haplotypes is determined by their fitness in diploid females, which depends on their diploid genotype and thus on the male gamete they pair with.
-%Zygotes carrying dominant neo-W alleles will develop as females regardless of their genotype at the XY locus. 
-%Therefore, neo-W females result from matings with either X-$A$ or Y-$a$ male gametes. 
-%The relative proportion of these male gametes is determined by haploid selection in males; mating with a Y-$a$ male gamete is more likely if the $a$ allele is favoured during male gamete production or competition ($\zeta<1/2$).
-%Thus, neo-W females experience different diploid selection than XX females, and the extent of this difference depends on haploid selection in males.
-%Furthermore, haploid selection in females can directly select upon neo-W-$A$ or neo-W-$a$ haplotypes. 
-%A neo-W-$A$ female gamete has the same fitness during haploid competition as resident $A$-bearing female gametes. 
-%On the other hand, neo-W-$a$ female gametes can be favoured or disfavoured during female haploid competition (favoured if $w_{a}^\female>w_{A}^\female$). 
-%Meiotic drive in females ($\alpha^\female$) similarly affects the fitness of these neo-W haplotypes, except that it impacts both haplotypes as meiotic drive only occurs in heterozygotes and therefore does not occur in resident XX females (who are always homozygote $AA$).
-
-Haploid selection impacts the spread of neo-W haplotypes in three ways.
-Firstly, the zygotic sex ratio becomes male biased, $\zeta>1/2$, when the $a$ allele (which is fixed on the Y) is favoured during competition among male gametes or by meiotic drive in males.
-Specifically, at equilibrium $(B)$, female zygote frequency is $1 - \zeta = w_A^\male (1+\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$ where $2\bar{w}_{H}^\male= \big[w_a^\male (1-\alpha^\male_\Delta) +  w_A^\male (1+\alpha^\male_\Delta) \big]$ has been canceled out in equations \eqref{Binvasion} to leave the term $\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]^{-1}$.
-Male biased sex ratios facilitate the spread of a neo-W because neo-W alleles cause the zygotes that carry them to develop as the rarer, female, sex.
-
-Secondly, haploid selection in females selects on neo-W haplotypes directly.
-At equilibrium $(B)$, the fitness of female gametes under the ancestral sex-determining system is $w_{A}^\female$ such that the relative fitnesses of neo-W-$A$ and neo-W-$a$ haplotypes during female gametic competition are $w_{A}^\female/w_{A}^\female$ and $w_{a}^\female/w_{A}^\female$ (see terms in equation \ref{Binvasion}).
-Meiotic drive in females will also change the proportion of gametes that carry the $A$ versus $a$ alleles, which will be produced by heterozygous females in proportions $(1+\alpha_{\Delta}^\female)/2$ and $(1-\alpha_{\Delta}^\female)/2$, respectively.
-These terms are only associated with heterozygous females, i.e., they are found alongside $w_{Aa}^\female$.
-
-Thirdly, haploid selection in males affects the diploid genotypes of females by altering the allele frequencies in the male gametes that female gametes pair with.
-At equlibrium $(B)$, neo-W female gametes will mate with X-$A$ male gametes with probability $ w_A^\male (1+\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$ and Y-$a$ male gametes with probability $w_a^\male (1-\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$, where the $2\bar{w}_{H}^\male$ terms have been canceled in equation \eqref{Binvasion} (as mentioned above).
-Thus, for example, neo-W-$A$ haplotypes are found in $AA$ female diploids with probability $ w_A^\male (1+\alpha^\male_\Delta)/ (2\bar{w}_{H}^\male)$ (first term in square brackets in the numerator of equation \ref{Binvasion}a) and in $Aa$ female diploids with probability $w_a^\male (1-\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$ (see equation \ref{Binvasion}c and the second term in square brackets in the numerator of equation \ref{Binvasion}a).
-
-%For instance, because an epistatically dominant neo-W always causes its carrier to become female, it creates females who carry either Y-$a$ or X-$A$ genotypes from their father.
-%Thus, because when there is a polymorphism the X carries some non-zero frequency of $A$, haploid selection in males impacts the diploid genotypes of females (e.g., creating more $Aa$ females when drive in males favours Y-$a$).
-%How this affects the spread of the neo-W then depends on diploid and haploid selection in females.
-
-The other terms in equations \eqref{Binvasion} are more easily interpreted if we assume that there is no haploid selection in either sex, in which case $\lambda_{mA}=(w_{AA}^\female+w_{Aa}^\female)/2 w_{AA}^\female$ and $\lambda_{ma}=(w_{aa}^\female+w_{Aa}^\female)/ 2 w_{AA}^\female$.
-Neither haplotype can spread under purely sexually-antagonistic selection, where $A$ is directionally favoured in females ($w_{AA}^\female>w_{Aa}^\female>w_{aa}^\female$) and $a$ is directionally favoured in males ($w_{AA}^\male>w_{Aa}^\male>w_{aa}^\male$).
-Essentially, the X is then already as specialized as possible for the female beneficial allele ($A$ is fixed on the X), and the neo-W often makes daughters with the Y-$a$ haplotype, increasing the flow of $a$ alleles into females, which reduces the fitness of those females.
-
-If selection doesn't uniformly favour $A$ in females, however, neo-W-$A$ haplotypes and/or neo-W-$a$ haplotypes can spread ($\lambda_{mA}>1$ and/or $\lambda_{ma}>1$).
-%If $\lambda_{mA}>1$ (requiring $w_{Aa}^\female>w_{AA}^\female$), the implication is that the neo-W can spread alongside the $A$ allele, despite the fact that the neo-W sometimes brings $Y-a$ haplotypes into females, because $a$ is favoured by selection in females despite $A$ being fixed on the X.
-A neo-W-$A$ haplotype can spread ($\lambda_{mA}>1$) when $w_{Aa}^\female>w_{AA}^\female$, despite the fact that a neo-W brings Y-$a$ haplotypes into females.
-In this case the $a$ allele is favoured by selection in females despite $A$ being fixed on the X.
-For this equilibrium to be stable (i.e.,  to keep $A$ fixed on the X), X-$a$ cannot be overly favoured in females and X-$A$ must be sufficiently favoured in males (for example, by overdominance in males).
-Specifically, from the stability conditions for equilibrium (B), we must have $w_{Aa}^\female < 2 w_{AA}^\female$ and $w_{Aa}^\male/\big[(w_{aa}^\male+w_{Aa}^\male)/2\big]>w_{Aa}^\female/w_{AA}^\female$.
-
-Still considering $w_{Aa}^\female>w_{AA}^\female$, the neo-W can also spread alongside the $a$ allele ($\lambda_{ma}>1$) if $w_{aa}^\female$ is large enough such that $(w_{Aa}^\female+w_{aa}^\female)/2>w_{AA}^\female$.
-%there is sufficiently strong underdominance in females ($w_{aa}^\female>w_{Aa}^\female$) \textcolor{blue}{[this is describing directional selection, not overdominance - check the conditions for the case we want to talk about]}, such that $(w_{Aa}^\female+w_{aa}^\female)/2>w_{AA}^\female$.
-This can occur with overdominance or directional selection for $a$ in females (Figure \ref{fig:regionplots}B,C).
-In this case, $a$ is favoured in females (comparing $Aa$ to $AA$ genotypes in females) but $A$ is fixed on the X due to selection in males. 
-The neo-W-$a$ haplotype can spread because it produces females with higher fitness $Aa$ and $aa$ genotypes.
-
-%When both haplotypes can spread on their own ($\lambda_{mA}>1$ and $\lambda_{ma}>1$), the neo-W invades regardless the recombination rate between it and the selected locus, $R$.
-%When neither haplotype can spread ($\lambda_{mA}<1$ and $\lambda_{ma}<1$) the neo-W can never invade.
-%And when only one haplotype can spread on its own the neo-W invades only when the rate of recombination onto the favourable background is sufficiently larger than the rate of recombination off this background (i.e., equation\ref{eq:lambdasGen} is satisfied).
-
-%Haploid selection affects the conclusions outlined above by altering the zygotic sex ratio and exerting direct selection on neo-W haplotypes.
-%The effect of sex ratio selection is straightforward and can be seen in equation \eqref{Binvasion}, where male drive and gamete competition for $a$ (which is fixed on the Y and therefore causes a male bias) increases all four terms.
-%Direct selection on neo-W haplotypes can also be seen in equation \eqref{Binvasion} by noticing that increasing female drive in favour of $A$ increases the neo-W-$A$ haplotype growth rate ($\lambda_{mA}$) while female drive and gamete competition in favour of $a$ increases the neo-W-$a$ haplotype growth rate ($\lambda_{ma}$).
-%Gamete competition in females does not impact the spread of neo-W-$A$ haplotypes because they are on the same background as the resident X.
-%Recombination between the selected locus and the neo-W complicates things slightly, as selective advantages for one neo-W haplotype during the haploid stage in females comes at a cost to the other, and thus recombination off the favoured background becomes more detrimental.
-
-%\textcolor{red}{the versions for equil $(A)$ are not terrible but could be improved by cleverly re-writing with the $\phi$ and $\psi$ terms from above, I think...}
-
-Similar equations can be derived for equilibrium (A) by substituting the equilibrium allele frequencies into Table \ref{tab:haplotype_growth}
-
-\begin{subequations}\label{Ainvasion}
-\begin{align}
-\lambda_{mA}&= \frac{a}{b} \left[w_{AA}^\female w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi +  w_{Aa}^\female (1+\alpha^\female_\Delta) w_a^\male c \right] / (2 w_a^\female) \\
-\lambda_{ma}&= \frac{a}{b} \left[ w_{Aa}^\female (1-\alpha^\female_\Delta) w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi +  w_{aa}^\female w_a^\male c \right] / (2 w_A^\female) \\
-\chi_{mA}&= \frac{a}{b} \frac{R}{2} \left[   w_{Aa}^\female (1+\alpha^\female_\Delta) w_a^\male c \right] / w_a^\female\\ 
-\chi_{ma}&= \frac{a}{b} \frac{R}{2} \left[ w_{Aa}^\female (1-\alpha^\female_\Delta) w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi \right] / w_A^\female
-\end{align}
-\end{subequations}
-
-\noindent
-where
-
-\begin{subequations}
-\begin{align}
-a &= w_a^\female \phi + w_A^\female \psi \\
-b &= w_{AA}^\female \left[ w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \right] \phi^2 + w_{Aa}^\female \left[ w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) + w_{aa}^\male w_a^\male \right] \psi \phi + w_{aa}^\female \left( w_{aa}^\male w_a^\male \right) \psi^2\\
-%c &= w_{Aa}^\male (1-\alpha^\male_\Delta) \phi \left[ w_{Aa}^\male (1+\alpha^\male_\Delta) \phi \right] + w_{Aa}^\male\phi \left[ 2w_{AA}^\male + w_{aa}^\male (1+\alpha^\male_\Delta) \right] \psi + w_{aa}^\male \psi \left(2w_{AA}^\male \psi \right) \\
-c &= w_{Aa}^\male (1-\alpha^\male_\Delta) \phi + 2w_{aa}^\male \psi
-\end{align}
-\end{subequations}
-
-As with equilibrium (B), haploid selection again modifies invasion fitnesses by altering the sex ratio and the diploid genotypes of females and directly selecting upon female gametes.
-The only difference is that resident XX females are no longer always homozygote $AA$ and males are no longer always heterozygote $Aa$.
-Thus the effect of haploid selection in males is reduced, as is the difference in fitness between neo-W haplotypes and resident X haplotypes, as both can be on any diploid or haploid background.
-
-The other terms are easier to interpret in the absence of haploid selection.
-For instance, without haploid selection, the neo-W-$A$ haplotype spreads ($\lambda_{mA}>1$) if and only if
-
-\begin{equation}\label{eq:BeqWAspread}
-2(w_{Aa}^\female-w_{aa}^\female)w_{aa}^\male \psi^2 > (w_{AA}^\female-w_{Aa}^\female)w_{Aa}^\male \phi (\phi-\psi)
-\end{equation}
-
-\noindent  
-where $\phi-\psi=w_{AA}^\female w_{Aa}^\male-w_{aa}^\female w_{aa}^\male$ and both $\phi$ and $\psi$ are positive when equilibrium (A) is stable. 
-In contrast to equilibrium (B), a neo-W haplotype can spread under purely sexually-antagonistic selection  ($w_{aa}^\female<w_{Aa}^\female<w_{AA}^\female$ and $w_{AA}^\male<w_{Aa}^\male<w_{aa}^\male$).
-The neo-W-$A$ can spread as long as it becomes associated with females that bear more $A$ alleles than observed at equilibrium (A). 
-%In this case, the neo-W-$A$ haplotype can spread, despite producing a lot of $Aa$ daughters by obtaining the $a$ from Y-gametes, when $aa$ females, which the neo-W-$A$ never makes, are strongly selected against.
-%This can be intuited from the fact that \eqref{eq:BeqWAspread} will be more easily met when $w_{Aa}^\female-w_{aa}^\female\approx w_{Aa}^\female$ and $w_{AA}^\female-w_{Aa}^\female\approx 0$, implying $w_{aa}^\female \approx 0$ and $w_{Aa}^\female\approx w_{AA}^\female$ (although this is complicated by the fact that $w_{aa}^\female$ and $w_{Aa}^\female$ affect $\phi$ and $\psi$ too, the intuition holds).
-
-Without haploid selection, the neo-W-$a$ haplotype spreads ($\lambda_{ma}>1$) if and only if
-
-\begin{equation}\label{eq:BeqWaspread}
-(w_{aa}^\female + w_{Aa}^\female-2w_{AA}^\female)w_{Aa}^\male \phi^2 + (w_{aa}^\female-w_{Aa}^\female)(w_{Aa}^\male+2w_{aa}^\male) \phi \psi >0
-\end{equation}
-
-\noindent
-This condition cannot be met with purely sexually antagonistic selection (as both terms on the left-hand side would then be negative), but it can be met under other circumstances. 
-For example, with overdominance in males there is selection for increased $A$ frequencies on X chromosomes in males, which are always paired with Y-$a$ haplotypes.
-Directional selection for $a$ in females can then maintain a polymorphism at the $\textbf{A}$ locus on the X.
-This scenario selects for a modifier that increases recombination between the sex chromosomes \citep[e.g., blue region of Figure 2d in][]{Otto2014} and facilitates the spread of neo-W-$a$ haplotypes, which create more females bearing more $a$ alleles than the ancestral X chromosome does.
-
-\subsubsection*{Role of Haploid Selection with Tight Linkage}
-
-Haploid selection generally expands the conditions under which neo-W alleles can spread within ancestral systems that have evolved tight linkage between the sex-determining locus and a selected locus ($r \approx 0$).
-First, haploid selection can allow a polymorphism to be maintained when it would not under diploid selection alone (e.g., with directional selection in diploids). 
-In cases of ploidally-antagonistic selection, where there is a balance between alleles favored in the haploid stage and the diploid stage, neo-W alleles - even unlinked alleles - can spread (Figure \ref{fig:regionPloidAntag}).
-Second, even when diploid selection could itself maintain a polymorphism, haploid selection can increase the conditions under which transitions among sex chromosomes are possible.
-Of particularly importance, when selection is sexually-antagonistic in diploids ($s^\female s^\male <0$ and $0<h^\Hermaphrodite<1$), an unlinked neo-W ($R=1/2$) cannot invade unless there is also haploid selection (see proof in supplementary \textit{Mathematica} file; Figures \ref{fig:SexAntagTighter} and \ref{fig:SexAntagTighterMaleDrive}).
-More generally, haploid selection alters the conditions under which neo-W chromosomes can spread (compare Figures \ref{fig:regionMaleDrive}-\ref{fig:regionFemaleGS} to Figure \ref{fig:regionplots}).
-
-%[SALLY:  I think that is enough, but we could add somewhere??: "Without haploid selection, unlinked neo-W alleles ($R=1/2$) can invade only under certain conditions, requiring either overdominance in males or underdominance in females (see proof in supplementary \textit{Mathematica} file).?
-Note that underdominance in females with directional selection in males can lead to the spread of unlinked neo-W?s, but only from equilB (only $\lambda_{ma}$ is greater than one in this case).]
-
-Male haploid selection in favour of the $a$ allele ($\alpha_{\Delta}^\male<0$, $w_{A}^\male<w_{a}^\male$) generates male-biased sex ratios at equilibria (A) and (B), where Y-$a$ is fixed ($\hat{p}_{Y}^\male=0$).
-Male-biased sex-ratios facilitate the spread of neo-W-$A$ and neo-W-$a$ haplotypes (increasing $\lambda_{mA}$ and $\lambda_{ma}$). 
-Panels A-C in Figures \ref{fig:regionMaleDrive} and \ref{fig:regionMaleGS} show that neo-W haplotypes tend to spread for a wider range of parameters when sex ratios are male biased, compared to Figure \ref{fig:regionplots} without haploid selection.
-By contrast, male haploid selection in favour of the $A$ allele generates female-biased sex ratios and reduces $\lambda_{mA}$ and $\lambda_{ma}$, as demonstrated by panels D-F in Figures \ref{fig:regionMaleDrive} and \ref{fig:regionMaleGS}.
-
-Female haploid selection generates direct selection on the neo-W-$A$ and neo-W-$a$ haplotypes as they spread in females. 
-Thus, female haploid selection in favour of the $a$ allele tends to increase $\lambda_{ma}$ and decrease $\lambda_{mA}$, as shown by panels A-C in Figures \ref{fig:regionFemaleDrive} and \ref{fig:regionFemaleGS}.
-Conversely, female haploid selection in favour of the $A$ allele increases $\lambda_{mA}$ and decreases $\lambda_{ma}$, see panels D-F in Figures \ref{fig:regionFemaleDrive} and \ref{fig:regionFemaleGS}.
-
-Thus, the impact of haploid selection on sex chromosome transitions must be considered as two sides of a coin: it can generate sex ratio biases that drive sex chromosome transitions to equalize the sex ratio, but it can also drive in new sex chromosomes and thereby cause sex ratios to become biased.
-
-%\subsubsection*{Tight Linkage and Haploid Selection}
-
-%With tight linkage, haploid selection generally expands the conditions under which neo-W alleles can spread. 
-%For example, when selection is sexually-antagonistic in diploids ($s^\female s^\male <0$ and $0<h^\Hermaphrodite<1$) an unlinked neo-W ($R=1/2$) cannot invade unless there is also haploid selection (Figures \ref{fig:SexAntagTighter} and \ref{fig:SexAntagTighterMaleDrive}).
-%Secondly, with haploid selection, overdominance ($w_{aa}^\Hermaphrodite<w_{Aa}^\Hermaphrodite$ \& $w_{AA}^\Hermaphrodite<w_{Aa}^\Hermaphrodite$) is not required for neo-W-$a$ haplotypes to spread ($\lambda_{ma}>1$) (Figures \ref{fig:regionMaleDrive}-\ref{fig:regionFemaleGS}).
-%Haploid selection and overdominance allow unlinked neo-W alleles to invade even when there is tight linkage between the ancestral SDR and the selected locus (Figure \ref{fig:loose_invades_tight}).
-%Finally, haploid selection can maintain a polymorphism in the face of directional selection in male and female diploids (ploidally-antagonistic selection). 
-%When selection is ploidally-antagonistic, neo-W alleles often spread, for at least some values of $R$ (Figure \ref{fig:regionPloidAntag}).
-
-%As discussed above, male haploid selection alters the sex ratio and the alleles carried by male gametes that female gametes pair with. 
-%Male haploid selection in favour of the $a$ allele ($\alpha_{\Delta}^\male<0$, $w_{A}^\male<w_{a}^\male$) generates male-biased sex ratios at equilibria (A) and (B), where Y-$a$ is fixed ($\hat{p}_{Y}^\male=0$).
-%Male-biased sex ratios facilitate the spread of neo-W-$A$ and neo-W-$a$ haplotypes (increasing $\lambda_{WA}$ and $\lambda_{Wa}$). 
-%Panels A-C in Figures \ref{fig:regionMaleDrive} and \ref{fig:regionMaleGS} show that neo-W haplotypes tend to spread for a wider range of parameters when sex ratios are male biased, compared to Figure \ref{fig:regionplots} without haploid selection.
-%By contrast, male haploid selection in favour of the $A$ allele generates female-biased sex ratios and reduces $\lambda_{WA}$ and $\lambda_{Wa}$, as demonstrated by panels D-F in Figures \ref{fig:regionMaleDrive} and \ref{fig:regionMaleGS}.
-
-%Female haploid selection generates direct selection on the neo-W-$A$ and neo-W-$a$ haplotypes as they spread in females. 
-%Thus, female haploid selection in favour of the $a$ allele tends to increase $\lambda_{Wa}$ and decrease $\lambda_{WA}$, as shown by panels A-C in Figures \ref{fig:regionFemaleDrive} and \ref{fig:regionFemaleGS}.
-%Conversely, female haploid selection in favour of the $A$ allele increases $\lambda_{WA}$ and decreases $\lambda_{Wa}$, see panels D-F in Figures \ref{fig:regionFemaleDrive} and \ref{fig:regionFemaleGS}.
-
-%Without haploid selection this reduces to
-%\begin{subequations}
-%\begin{align}
-%\lambda_{mA}&= \frac{a}{b} \left[w_{AA}^\female w_{Aa}^\male \phi / 2 + w_{Aa}^\female \frac{c}{d}\right]  \\
-%\lambda_{ma}&= \frac{a}{b} \left[w_{Aa}^\female w_{Aa}^\male \phi / 2 +  w_{aa}^\female \frac{c}{d}\right] \\
-%\chi_{mA}&= \frac{a}{b} R \left[ w_{Aa}^\female \frac{c}{d} \right] \\ 
-%\chi_{ma}&= \frac{a}{b} R \left[ w_{Aa}^\female w_{Aa}^\male \phi / 2 \right] 
-%\end{align}
-%\end{subequations}
-
-%These simplify considerably when there is no haploid selection:
-%
-%\begin{subequations}
-%\begin{align}
-%\lambda_{mA}&= \frac{(\phi + \psi)[(w_{AA}^\female + w_{Aa}^\female ) w_{Aa}^\male \phi + 2 w_{Aa}^\female w_{AA}^\male \psi ]}{2 (w_{AA}^\female w_{Aa}^\male \phi^2 + \psi(w_{Aa}^\female(w_{AA}^\male + w_{Aa}^\male)\phi + w_{aa}^\female w_{AA}^\male \psi)}\\
-%\lambda_{ma}&=  \frac{(\phi + \psi)[(w_{aa}^\female + w_{Aa}^\female ) w_{Aa}^\male \phi + 2 w_{aa}^\female w_{AA}^\male \psi ]}{2 (w_{AA}^\female w_{Aa}^\male \phi^2 + \psi(w_{Aa}^\female(w_{AA}^\male + w_{Aa}^\male)\phi + w_{aa}^\female w_{AA}^\male \psi)}\\
-%\chi_{mA}&= R \frac{(\phi + \psi) w_{Aa}^\female w_{AA}^\male}{2 (w_{AA}^\female w_{Aa}^\male \phi^2 + \psi(w_{Aa}^\female(w_{AA}^\male + w_{Aa}^\male)\phi + w_{aa}^\female w_{AA}^\male \psi)} \\ 
-%\chi_{ma}&= R \frac{(\phi + \psi) w_{Aa}^\female w_{Aa}^\male}{2 (w_{AA}^\female w_{Aa}^\male \phi^2 + \psi(w_{Aa}^\female(w_{AA}^\male + w_{Aa}^\male)\phi + w_{aa}^\female w_{AA}^\male \psi)}\\
-%\end{align}
-%\end{subequations}
-%
-%\begin{subequations}
-%\begin{align}
-%\lambda_{mA}&= [( w_{AA}^\female + w_{Aa}^\female ) w_{Aa}^\male \phi + 2 w_{Aa}^\female w_{AA}^\male \psi] a \\
-%\lambda_{ma}&=  [(w_{aa}^\female + w_{Aa}^\female ) w_{Aa}^\male \phi + 2 w_{aa}^\female w_{AA}^\male \psi ] a\\
-%\chi_{mA}&= R w_{Aa}^\female (w_{Aa}^\male \phi + 2 w_{AA}^\male \psi) c \\ 
-%\chi_{ma}&= R w_{Aa}^\female w_{Aa}^\male \phi c \\
-%\end{align}
-%\end{subequations}
-%\noindent
-%where 
-%$c = \frac{\phi + \psi}{2 [w_{AA}^\female w_{Aa}^\male \phi^2 + \psi(w_{Aa}^\female(w_{AA}^\male + w_{Aa}^\male)\phi + w_{aa}^\female w_{AA}^\male \psi]}$ and $\phi$ and $\psi$ are evaluated with $\alpha^{\Hermaphrodite}=1/2$ and $w_a^\Hermaphrodite=w_A^\Hermaphrodite=1$.
-
-%With $R=0$ the two eigenvalues are $\lambda_{mA}$ and $\lambda_{ma}$.
-%The neo-W can then invade on the $A$ background when $\lambda_{mA}>1$ and the neo-W can invade on the $a$ background when $\lambda_{ma}>1$.
-%Even in this case it is difficult to see from equation \ref{Ainvasion} when the neo-W will invade.
-%Below we discuss why $\lambda_{mA}$ and $\lambda_{ma}$ might be larger than one and confirm the logic numerically.
-%
-%
-%For simplicity, consider the case of no haploid selection.
-%A polymorphism at the $\mathbf{A}$ locus then requires sexually-antagonistic selection \citep{vanDoorn:2007eu}.
-%Given that $a$ is fixed on the Y, one can consider the $a$ allele `male beneficial' and the $A$ allele to be `female beneficial'. 
-%Because X chromosomes spend some time in males the frequency of $A$ on the X can reach an intermediate equilibrium (equilibrium A).
-%
-%We can therefore reason that when a neo-W invades equilibrium (A), it is likely to spread on the $A$ background as W chromosomes are always in females.
-%The neo-W can outcompete the ancestral, `comprimising' X because it can specialize on females by fixing the `female beneficial' allele.  
-%We call this the `sex-specialist hypothesis'.
-%This hypothesis should only work when the benefit of specializing outweighs the cost of bringing Y chromosomes into females (the neo-W is epistatically dominant over the X/Y locus).
-%
-%One could also reason that, when the neo-W spreads, it does so precisely because it brings Y chromosomes, and their associated alleles, into females, something the X cannot do.
-%However, this requires a somewhat particular (perhaps `perverse') equilibrium, where XX females do worse than XY females despite associations on the X and Y being built up by selection.
-%One example of such a perverse equilibrium is produced by overdominance in both sexes.
-%Overdominance in females selects for an allele frequency of 0.5 on the X ($A$ and $a$ equally frequent, maximizing the number of heterozygotes). 
-%However, given that $a$ is fixed on the Y, overdominance in males selects for the X to become more associated with the $A$. 
-%Thus, a compromising equilibrium is reached on the X chromosome and females fitness suffers due to the overproduction of $AA$ homozygotes.
-%This sets up a scenario in which a neo-W can invade on the $a$ background, despite the fact that $a$ is fixed on the Y and in that sense `male beneficial'.
-%We call this the `perverse hypothesis'.
-%
-%Figure \ref{fig:Region_Plots} shows where the sex-specialist (red) and perverse (blue) hypotheses are valid.
-%The left panel demonstrates that both hypotheses can be simultaneously valid with overdominance in both sexes and sex differences in selection, which overlaps the parameter region where there is selection for increased recombination between the sex chromosomes \citep[compare with figure 2a in][]{Otto2014}.
-%The right panel shows that the perverse hypothesis is no longer valid when selection is exactly the same in both sexes, despite the fact that there is selection for increased recombination between the sex chromosomes with sufficiently strong overdominance \citep[compare with figure 3 in][]{Otto2014}.
-%
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%Sex-specialist vs perverse hypotheses
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\includegraphics[width=0.45\linewidth]{regionplot_2a}
-%\includegraphics[width=0.45\linewidth]{regionplot_3}\\
-%\caption{
-%Numerical exploration of where sex-specialist (red) and perverse (blue) hypotheses are valid, i.e., where an internally stable resident equilibrium can be invaded by a neo-W that is perfectly linked with the allele not fixed on the Y (red) or the allele that is fixed on the Y (blue).
-%\textbf{(Left)}
-%The perverse equilibrium is only valid with overdominance while the sex-specialist hypothesis is valid over the entire range shown.
-%Both hypotheses are simultaneously valid over much of the parameter space where increased recombination between the sex chromosomes is selected \citep[][figure 2a]{Otto2014}.
-%\textbf{(Right)}
-%Only the sex-specialist hypothesis is valid with no sex-differences in selection, despite selection for increased recombination between the sex-chromosomes with strong overdominance \citep[][figure 3]{Otto2014}.
-%Parameters: $w_{Aa}^\Hermaphrodite = 1$, $w_a^\Hermaphrodite = w_A^\Hermaphrodite = 1$, $\alpha^\Hermaphrodite = 1/2$, $r=R=0$, and in left panel $w_{aa}^\female = w_{AA}^\female = 0.6$.
-%}
-%\label{fig:Region_Plots}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\begin{figure}[!h]
-\centering
-\centerline{
-\includegraphics[width=\linewidth]{neoW_invades_tight_loose}
-}
-\caption{
-An unlinked neo-W can invade a perfectly linked system with overdominance or haploid selection.
-Here overdominance leads to a polymorphic sex-determining system.
-Before invasion the population is at equilibrium B.
-Parameters:
-}
-\label{fig:loose_invades_tight}
-\end{figure}
-
-%\begin{figure}[!h]
-%\centering
-%\centerline{
-%\includegraphics[width=\linewidth]{Sallys_R_plot.pdf}
-%}
-%\caption{
-%\textcolor{blue}{is this the one?}
-%}
-%\label{fig:lambda_R}
-%\end{figure}
-
-%\newpage
-%\textcolor{red}{
-%Add Sally's figure showing lambda for small r near equil A versus near equil B.
-Add references to this figure to appendix where we discuss whether lambdas can be greater than 1 with sexually antagonistic selection.}
-%\textcolor{blue}{not sure which one you are talking about, but see Figure \ref{fig:lambda_R} }
-%\textcolor{red}{Let's remove this for now.}
-
-%\textcolor{red}{
-%Perhaps it would also be useful to add an 8 panel figure that features ploidally antagonistic selection.
-For each type of haploid selection (gametic competition/ meiotic drive in males/females), give a regionplot where $h^\male=h^\female$, e.g., $h^\male=h^\female=0.75$ (or perhaps the value of $h$ we use in the regionplots we have, in which $w_{aa}=0.85$, $w_{Aa}=1$, $w_{AA}=1.05$).
-%Matt made a figure like this before but both Y$a$ and Y$A$ equilibria were plotted and there was no outline showing where the Y$a$ equilibrium is stable (as in Figure \ref{fig:regionplots}).
-In Matts plot the axes were $s^\Hermaphrodite$ and $\alpha_{\Delta}^\Hermaphrodite$.
-%Add an asterisk to each region plot and show invasion in another panel, using those parameters and various $R$ (e.g., in the stye of \ref{fig:temporalOverdominance}). 
-%In an email, Sally has an example of ploidally-antagonistic selection where the neo-W fixes and $R=1/2$. This would cover that case and more. }
-%\textcolor{blue}{made an attempt (Figure \ref{fig:regionPloidAntag})}
-
-%\textcolor{red}{
-%We could also give versions of Figure \ref{fig:regionplots} where there is also haploid selection of various types.
-%Haploid selection can favour $A$ or $a$, so this would involve 4x 6-panel figures.
-Started looking at this in Figure \ref{fig:regionMaleGS} and Figure \ref{fig:regionMaleDrive}, add female haploid selection.
-%Try to integrate into the discussion of haploid selection? e.g., male haploid selection ones generally show effect of sex ratio, increasing both lambdas when female biased (top rows).}
-%\textcolor{blue}{
-%these figures are now done (\ref{fig:regionMaleDrive}-\ref{fig:regionFemaleGS}) (ensuring frequencies between 0 and 1), but yet to discuss in text.}
-
-%\textcolor{red}{
-%Perhaps, for one set of parameters, we should plot the dynamics of all the different alleles.
-E.g., we could use the same parameters used in \ref{fig:SexRatioBad}.
-The main purpose would be to show what happens to the ancestral SDR during turnover.
-%We could also show an example where XY and ZW sex determining systems are both polymorphic and stable (e.g., using one of the curves in Figure \ref{fig:temporalOverdominance} and the green curve in Figure \ref{fig:SexAntagTighterMaleDrive}).
-%I think there are also examples with looser sex linkage and pollen competition that lead to a mixed sex-determination system.
-We should probably have a short section in the appendix discussing this.
-}
-%\textcolor{blue}{made an attempt with Figure \ref{fig:freqAll}, but yet to discuss in text}
-
 \end{document}

### 2018-01-18 LaTeX/Turnover_plos.tex
moved to plos template, appendices have references that are still messed up

--- 2018-01-18 LaTeX/Turnover.tex
@@
-\documentclass[12pt]{article}
-%\documentclass{nature}
-
-% Including pdf figures
-\usepackage{graphicx}
-\graphicspath{ {../Plots/} }
-\usepackage{pdfpages}
-%really place a figure in a location
-\usepackage{float}
-%Overrun caption
-\usepackage[CaptionAfterwards]{fltpage}
-% Math stuff
-\usepackage{amsmath}
+% Template for PLoS
+% Version 3.4 January 2017
+%
+% % % % % % % % % % % % % % % % % % % % % %
+%
+% -- IMPORTANT NOTE
+%
+% This template contains comments intended 
+% to minimize problems and delays during our production 
+% process. Please follow the template instructions
+% whenever possible.
+%
+% % % % % % % % % % % % % % % % % % % % % % % 
+%
+% Once your paper is accepted for publication, 
+% PLEASE REMOVE ALL TRACKED CHANGES in this file 
+% and leave only the final text of your manuscript. 
+% PLOS recommends the use of latexdiff to track changes during review, as this will help to maintain a clean tex file.
+% Visit https://www.ctan.org/pkg/latexdiff?lang=en for info or contact us at latex@plos.org.
+%
+%
+% There are no restrictions on package use within the LaTeX files except that 
+% no packages listed in the template may be deleted.
+%
+% Please do not include colors or graphics in the text.
+%
+% The manuscript LaTeX source should be contained within a single file (do not use \input, \externaldocument, or similar commands).
+%
+% % % % % % % % % % % % % % % % % % % % % % %
+%
+% -- FIGURES AND TABLES
+%
+% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
+%
+% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
+% - Figures should be uploaded separately from your manuscript file. 
+% - Figures generated using LaTeX should be extracted and removed from the PDF before submission. 
+% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
+% For figure citations, please use "Fig" instead of "Figure".
+% See http://journals.plos.org/plosone/s/figures for PLOS figure guidelines.
+%
+% Tables should be cell-based and may not contain:
+% - spacing/line breaks within cells to alter layout or alignment
+% - do not nest tabular environments (no tabular environments within tabular environments)
+% - no graphics or colored text (cell background color/shading OK)
+% See http://journals.plos.org/plosone/s/tables for table guidelines.
+%
+% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
+%
+% % % % % % % % % % % % % % % % % % % % % % % %
+%
+% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
+%
+% IMPORTANT
+% Below are a few tips to help format your equations and other special characters according to our specifications.
+For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://journals.plos.org/plosone/s/latex
+%
+% For inline equations, please be sure to include all portions of an equation in the math environment.
+For example, x$^2$ is incorrect; this should be formatted as $x^2$ (or $\mathrm{x}^2$ if the romanized font is desired).
+%
+% Do not include text that is not math in the math environment. For example, CO2 should be written as CO\textsubscript{2} instead of CO$_2$.
+%
+% Please add line breaks to long display equations when possible in order to fit size of the column. 
+%
+% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
+%
+% When adding superscript or subscripts outside of brackets/braces, please group using {}.  For example, change "[U(D,E,\gamma)]^2" to "{[U(D,E,\gamma)]}^2". 
+%
+% Do not use \cal for caligraphic font.  Instead, use \mathcal{}
+%
+% % % % % % % % % % % % % % % % % % % % % % % % 
+%
+% Please contact latex@plos.org with any questions.
+%
+% % % % % % % % % % % % % % % % % % % % % % % %
+
+\documentclass[10pt,letterpaper]{article}
+\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}
+
+% % % % % % % % % % % % % % % % % % % % % % % %
+
+% Extra symbols added
 \usepackage{stix}
-% Bibliographies
-\usepackage[numbers]{natbib}
-\bibpunct{(}{)}{,}{a}{}{;}
-
+%Three part table - I think this is allowed
 \usepackage[flushleft]{threeparttable}
-
-\usepackage[font={scriptsize}]{caption}
-
-\usepackage{lineno} %gives line numbers with \lineno command
-
-\usepackage{setspace}
-\onehalfspace
-
-\usepackage{tikz}%for putting words on figures
-\usetikzlibrary{positioning}%for relative positioning
-
-%to rotate figures
-\usepackage{rotating}
-\usepackage{pdflscape}
+%external document referencing - this is not allowed
+\usepackage{xr}
+
+% % % % % % % % % % % % % % % % % % % % % % % %
+
+% amsmath and amssymb packages, useful for mathematical formulas and symbols
+\usepackage{amsmath,amssymb}
+
+% Use adjustwidth environment to exceed column width (see example table in text)
+\usepackage{changepage}
+
+% Use Unicode characters when possible
+\usepackage[utf8x]{inputenc}
+
+% textcomp package and marvosym package for additional characters
+\usepackage{textcomp,marvosym}
+
+% cite package, to clean up citations in the main text. Do not remove.
+\usepackage{cite}
+
+% Use nameref to cite supporting information files (see Supporting Information section for more info)
+\usepackage{nameref,hyperref}
+
+% line numbers
+\usepackage[right]{lineno}
+
+% ligatures disabled
+\usepackage{microtype}
+\DisableLigatures[f]{encoding = *, family = * }
+
+% color can be used to apply background shading to table cells only
+\usepackage[table]{xcolor}
+
+% array package and thick rules for tables
+\usepackage{array}
+
+% create "+" rule type for thick vertical lines
+\newcolumntype{+}{!{\vrule width 2pt}}
+
+% create \thickcline for thick horizontal lines of variable length
+\newlength\savedwidth
+\newcommand\thickcline[1]{%
+  \noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
+  \cline{#1}%
+  \noalign{\vskip\arrayrulewidth}%
+  \noalign{\global\arrayrulewidth\savedwidth}%
+}
+
+% \thickhline command for thick horizontal lines that span the table
+\newcommand\thickhline{\noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
+\hline
+\noalign{\global\arrayrulewidth\savedwidth}}
+
+% Remove comment for double spacing
+%\usepackage{setspace} 
+%\doublespacing
+
+% Text layout
+\raggedright
+\setlength{\parindent}{0.5cm}
+\textwidth 5.25in 
+\textheight 8.75in
+
+% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
+% Captions will be left justified
+\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
+\renewcommand{\figurename}{Fig}
+
+% Use the PLoS provided BiBTeX style
+\bibliographystyle{plos2015}
+
+% Remove brackets from numbering in List of References
+\makeatletter
+\renewcommand{\@biblabel}[1]{\quad#1.}
+\makeatother
+
+% Leave date blank
+\date{}
+
+% Header and Footer with logo
+\usepackage{lastpage,fancyhdr,graphicx}
+\usepackage{epstopdf}
+\pagestyle{myheadings}
+\pagestyle{fancy}
+\fancyhf{}
+\setlength{\headheight}{27.023pt}
+\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
+\rfoot{\thepage/\pageref{LastPage}}
+\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
+\fancyheadoffset[L]{2.25in}
+\fancyfootoffset[L]{2.25in}
+\lfoot{\sf PLOS}
+
+%% Include all macros below
+
+\newcommand{\lorem}{{\bf LOREM}}
+\newcommand{\ipsum}{{\bf IPSUM}}
+
+%% END MACROS SECTION
 
 \begin{document}
-
-\title{Haploid Selection, Sex Ratio Bias, and Transitions Between Sex-Determination Systems}
-\author{Michael F Scott$*^1$, Matthew M Osmond$*^2$, and Sarah P Otto$^2$}
-\date{}
-\maketitle
-\noindent
-$*$ These authors contributed equally to this work
-
-\noindent
-$^1$ Department of Botany, University of British Columbia, \#3529 - 6270 University Boulevard, Vancouver, BC, Canada V6T 1Z4
-
-\noindent
-$^2$ Department of Zoology, University of British Columbia, \#4200 - 6270 University Boulevard, Vancouver, BC, Canada V6T 1Z4
-
-\noindent
-email: mfscott@biodiversity.ubc.ca, mmosmond@zoology.ubc.ca
-
-\noindent
-Contributions:
-
-\newpage
-\linenumbers
-\modulolinenumbers[2]
-
-\begin{abstract}
+\vspace*{0.2in}
+
+% Title must be 250 characters or less.
+\begin{flushleft}
+{\Large
+\textbf\newline{Haploid selection, sex ratio bias, and transitions between sex-determination systems} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
+}
+\newline
+% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
+\\
+Michael Francis Scott\textsuperscript{1\Yinyang*},
+Matthew Miles Osmond\textsuperscript{2\Yinyang},
+Sarah Perin Otto\textsuperscript{2}
+\\
+\bigskip
+\textbf{1} UCL Genetics Institue, Department of Genetics, Evolution and Environment, University Collect London, Gower Street, London WC1E 6BT 
+\\
+\textbf{2} Department of Zoology, University of British Columbia, \#4200 - 6270 University Boulevard, Vancouver, BC, Canada V6T 1Z4
+\\
+\bigskip
+
+% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
+% 
+% Remove or comment out the author notes below if they aren't used.
+%
+% Primary Equal Contribution Note
+\Yinyang These authors contributed equally to this work.
+
+% Additional Equal Contribution Note
+% Also use this double-dagger symbol for special authorship notes, such as senior authorship.
+%\ddag These authors also contributed equally to this work.
+
+% Current address notes
+%\textcurrency Current Address: Dept/Program/Center, Institution Name, City, State, Country % change symbol to "\textcurrency a" if more than one current address note
+% \textcurrency b Insert second current address 
+% \textcurrency c Insert third current address
+
+% Deceased author note
+%\dag Deceased
+
+% Group/Consortium Author Note
+%\textpilcrow Membership list can be found in the Acknowledgments section.
+
+% Use the asterisk to denote corresponding authorship and provide email address in note below.
+* m.f.scott@ucl.ac.uk
+
+\end{flushleft}
+% Please keep the abstract below 300 words
+\section*{Abstract}
 Sex-determination systems are remarkably dynamic; many taxa display shifts in the location of sex-determining loci or the evolution of entirely new sex-determining systems. 
-Predominant theories for why we observe such transitions %in which new sex-determining systems spread by selection 
-%involve sex ratio selection or sex-specific selection (e.g., sexually antagonistic selection).
-%These studies 
-generally conclude that novel sex-determining systems are favoured by selection if they equalise the sex ratio or increase linkage with a sexually-antagonistic locus. 
+Predominant theories for why we observe such transitions generally conclude that novel sex-determining systems are favoured by selection if they equalise the sex ratio or increase linkage with a sexually-antagonistic locus.
 We use population genetic models to extend these theories in two ways: 
 (1) We explicitly consider selection on loci very tightly linked to the ancestral sex-determining loci, e.g., within the non-recombining region of the ancestral sex chromosomes. 
-%(1) We explicitly consider how selection on very tightly sex-linked loci influences the spread of novel sex-determiners. 
 Variation at such loci can favour the spread of new sex-determination systems in which the heterogametic sex changes (XY to ZW or ZW to XY) and the new sex-determining region is less closely linked (or unlinked) to the locus under selection, which is not predicted by previous theory.
-%With tight linkage, selection can maintain equilibria at which the allele fixed on the sex-limited chromosome (Y or W) is simultaneously favoured in the homogametic sex (XX females or ZZ males) such that heterogametic transitions (XY to ZW or ZW to XY) are favoured by selection.
-%Alternatively, a neo-W (neo-Y) locus can invade when it allows greater specialism on alleles beneficial in females (male) compared to an ancestral XX female (ZZ male), 
 (2) We also consider selection upon haploid genotypes either during gametic competition (e.g., pollen/sperm competition) or meiosis (i.e., non-Mendelian segregation); selective processes that typically occur in one sex or the other.
-%As well as having sex-specific fitness consequences, haploid selection can cause the zygotic sex ratio to become biased because sex ratios are determined by the production and fertilization success of X- versus Y-bearing pollen/sperm (or Z- versus W-bearing ovules/eggs).
-%Consequently, selection for XY to ZW transitions and ZW to XY transitions can be assymetrical when linkage between the ancestral sex-determining locus and a locus under haploid selection is tight, in which case ancestral sex ratio biases can be strong.
-%In addition, when linkage between the ancestral sex-determining locus and a locus under haploid selection is tight, sex ratio biases can be strong such that there is an asymmetry between invasion of ancestrally XY and ancestrally ZW systems because, e.g., haploid selection in males only causes biased zygotic sex ratios in an ancestrally XY system.
 We find that associations with haploid selected loci can drive transitions between sex determination systems, without requiring sexually-antagonistic selection in diploids. 
@@
 Thus, we find that transitions between sex-determination systems cannot be simply predicted by selection to equalise the sex ratio. 
-%These results indicate that loci experiencing haploid selection can favour the evolution of new sex-determination systems. 
-%These results indicate that favourable associations that develop between the ancestral sex-determining locus and selected loci can be broken during the spread of a new sex-determining region. 
-%Such transitions are not possible with diploid selection alone, in which case tighter linkage increases the fitness of both males and females. 
-%Notably, we find that the spread of new genetic sex-determination systems is not affected by sex ratio biases that are caused by haploid selection. 
-%A surprising result given that other determinants of sex allocation typically experience strong Fisherian sex ratio selection to equalize sex ratios. 
-%Overall, we demonstrate when and how the evolution of sex determining systems is impacted by sex ratio biases resulting from haploid selection and we show that new sex-determining regions can be favoured even if they are not closely linked with a locus under selection.
 Overall, our models reveal that transitions between sex-determination systems, particularly transitions where the heterogametic sex changes, can be driven by loci in previously unpredicted genomic locations that experience selection during diploid and/or haploid phases.
 These results predict conditions under which sex-determination systems are likely to be labile and draw novel connections with sex ratio evolution
-%These results might be reflected in the lability with which sex-determination systems evolve. %and for the factors determining the phylogenetic pattern of sex-determination systems. 
-\end{abstract}
-
-%abstract word count: $\approx$ 350
-
-\newpage
-
+
+% Please keep the Author Summary between 150 and 200 words
+% Use first person. PLOS ONE authors please skip this step. 
+% Author Summary not valid for PLOS ONE submissions.   
+\section*{Author summary}
+Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Curabitur eget porta erat.
+Morbi consectetur est vel gravida pretium.
+Suspendisse ut dui eu ante cursus gravida non sed sem.
+Nullam sapien tellus, commodo id velit id, eleifend volutpat quam.
+Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus.
+Nunc pellentesque pretium diam, quis maximus dolor faucibus id.
+Nunc convallis sodales ante, ut ullamcorper est egestas vitae.
+Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.
+%Therefore, our models radically alter our understanding of when and why new sex determination system can evolve. 
+%Therefore, our models cause us to update the prevailing understanding about selective forces that can drive transitions between sex determination systems.
+
+\linenumbers
+
+% Use "Eq" instead of "Equation" for equation citations.
 \section*{Introduction}
 
-%CHECK THROUGHOUT: use of sex-determination SYSTEMS versus MECHANISMS. 
-%CHECK THROUGHOUT: use of haploid selection, gametic selection, and meiotic drive.
-
-Animals and angiosperms exhibit extremely diverse sex-determination systems \citep[reviewed in][]{Bull:1983vi,Charlesworth:2010it,Beukeboom:2014vb,Bachtrog:2014bx}. 
+\externaldocument{Turnover_plos.tex}
+\externaldocument{S1_Appendix.tex}
+%\externaldocument{S2_Appendix.tex}
+\externaldocument{S3_Appendix.tex}
+
+Animals and angiosperms exhibit extremely diverse sex-determination systems (reviewed in~\cite{Bull:1983vi,Charlesworth:2010it,Beukeboom:2014vb,Bachtrog:2014bx}). 
 Among species with genetic sex determination of diploid sexes (GSD), some taxa have heterogametic males (XY) and homogametic females (XX), including %non-monotreme?
 I think monotremes have XY but tonnes of translocations, giving: X1,X2...X6 Y1
-mammals and most dioecious plants \citep{Ming:2011iy}; whereas other taxa have homogametic males (ZZ) and heterogametic females (ZW), including Lepidoptera and birds. 
+mammals and most dioecious plants~\cite{Ming:2011iy}; whereas other taxa have homogametic males (ZZ) and heterogametic females (ZW), including Lepidoptera and birds. 
 Within several taxa, the chromosome that harbours the master sex-determining region changes. 
-For example, transitions of the master sex-determining gene between chromosomes or the evolution of new master sex-determining genes have occurred in Salmonids \citep{Li:2011fm,Yano:2012di}, Diptera \citep{Vicoso:2015hf}, and \textit{Oryzias} \citep{Myosho:2012fv}.
+For example, transitions of the master sex-determining gene between chromosomes or the evolution of new master sex-determining genes have occurred in Salmonids~\cite{Li:2011fm,Yano:2012di}, Diptera~\cite{Vicoso:2015hf}, and \textit{Oryzias}~\cite{Myosho:2012fv}.
 %Presentation at evolution found neo sex chromosome in birds, doesn't seem to be published or bioRxiv yet (consider pers com.), title: A previously unknown neo-sex chromosome mediates plumage divergence and speciation in hybridizing birds Jason Sardell; Elizabeth Cooper; J.
@@
 I wonder if this is actually a fusion event though?
-In addition, many clades exhibit transitions between male (XY) and female (ZW) heterogamety, including snakes \citep{Gamble2017}, lizards \citep{Ezaz:2009tk}, eight of 26 teleost fish families \citep{Mank:2006bt}, true fruit flies \citep[Tephritids,][]{Vicoso:2015hf}, amphibians \citep{Hillis:1990gu}, the angiosperm genus \textit{Silene} \citep{Slancarova:2013dq}, the angiosperm family \textit{Salicaceae} \citep{Pucholt2015,Pucholt2017} and Coleoptera and Hemiptera \citep[][plate 2]{Beukeboom:2014vb}.
-Indeed, in some cases, both male and female heterogametic sex-determination systems can be found in the same species, as reported in houseflies \citep{Macdonald1978}, midges \citep{Thompson1971}, frogs \citep{Ogata:2007jm}, cichlid fish \citep{Ser:2010iq}, tilapia \citep{Lee2004}, sea bass \citep{Vandeputte2007}, and lab-strains of Zebrafish \citep{Liew2012,Wilson2014}.
-In addition, multiple transitions have occurred between genetic (GSD) and environmental sex-determination (ESD) systems, e.g., in reptiles and fishes \citep{Conover:1987in,Mank:2006bt,Pokorna:2009ui,Ezaz:2009tk,Pen:2010kk,Holleley:2015hc}.
-
-%NOTE: ``Bull & Charnov (1977) hypothesized that a new sex-determining gene can rapidly increase and become fixedin a population if it is linked to a gene with high adaptivevalue, and finally cause a change of the heterogametic sex.'' The Bull and Charnov paper is also the one in which the set of neutral equilibria between XY and ZW are identified (where sex ratios are equal)
-%NOTE: Vuilleumier et al. 2007 also find polymorphic sex determination can be stable.
-
-%For example, closely related species in the Medaka lineage (cite Takenhana et al. 2008) and Tilapiinae (cite Lee et al 2004, Cnaani et al 2008), citations in Beukeboom.
-
-%\textcolor{red}{Brief description of sex ratio adjustment and sexual antagonism theories:}
-
-Predominant theories accounting for the spread of new sex-determination systems by selection involve fitness differences between sexes (e.g., sexually antagonistic selection) or sex ratio selection \citep{Blaser2012, Beukeboom:2014vb,vanDoorn2014re}.
+In addition, many clades exhibit transitions between male (XY) and female (ZW) heterogamety, including snakes~\cite{Gamble2017}, lizards~\cite{Ezaz:2009tk}, eight of 26 teleost fish families~\cite{Mank:2006bt}, true fruit flies (Tephritids,~\cite{Vicoso:2015hf}, amphibians~\cite{Hillis:1990gu}, the angiosperm genus \textit{Silene}~\cite{Slancarova:2013dq}, the angiosperm family \textit{Salicaceae}~\cite{Pucholt2015,Pucholt2017} and Coleoptera and Hemiptera (plate 2~\cite{Beukeboom:2014vb}).
+Indeed, in some cases, both male and female heterogametic sex-determination systems can be found in the same species, as reported in houseflies~\cite{Macdonald1978}, midges~\cite{Thompson1971}, frogs~\cite{Ogata:2007jm}, cichlid fish~\cite{Ser:2010iq}, tilapia~\cite{Lee2004}, sea bass~\cite{Vandeputte2007}, and lab-strains of Zebrafish~\cite{Liew2012,Wilson2014}.
+In addition, multiple transitions have occurred between genetic (GSD) and environmental sex-determination (ESD) systems, e.g., in reptiles and fishes~\cite{Conover:1987in,Mank:2006bt,Pokorna:2009ui,Ezaz:2009tk,Pen:2010kk,Holleley:2015hc}.
+
+Predominant theories accounting for the spread of new sex-determination systems by selection involve fitness differences between sexes (e.g., sexually antagonistic selection) or sex ratio selection~\cite{Blaser2012, Beukeboom:2014vb,vanDoorn2014re}.
 %\citet{Bull:1977wt} shows that direct selection on new sex determination loci can allow them to spread and switch between male and female heterogamety. 
-\citet{vanDoorn:2007eu,vanDoorn:2010hu} and \citet{Muralidhar2018} have shown that new sex-determining loci can be favoured if they arise in close linkage with a locus that experiences sexual antagonism.
+van Doorn and Kirkpatrick~\cite{vanDoorn:2007eu,vanDoorn:2010hu} and Muralidhar and Veller~\cite{Muralidhar2018} have shown that new sex-determining loci can be favoured if they arise in close linkage with a locus that experiences sexual antagonism.
 Tighter linkage allows a stronger favourable association to build up between a male-beneficial allele, and a neo-Y chromosome, for example. 
-Such associations can favour a new partially-masculinizing or partially-feminizing allele \citep{Muralidhar2018}, a new master sex-determining gene \citep{vanDoorn:2007eu}, and transitions between male and female heterogamety \citep[trans-GSD transitions, ZW to XY or XY to ZW,][]{vanDoorn:2010hu}.
+Such associations can favour a new partially-masculinizing or partially-feminizing allele~\cite{Muralidhar2018}, a new master sex-determining gene~\cite{vanDoorn:2007eu}, and transitions between male and female heterogamety (trans-GSD transitions, ZW to XY or XY to ZW~\cite{vanDoorn:2010hu}).
 However, any sexually-antagonistic loci that are more closely linked to the ancestral sex-determination locus will develop similar, favourable associations and are expected to hinder the spread of a new sex-determination system.
-%Here we extend these studies by explicitly calculating the the equilibrium allele frequencies of loci that are very tightly linked to the ancestral sex-determining region.
-
-The sex ratio is directly determined by the sex-determination system, and it has therefore been suggested that sex ratio selection is a dominant force in the evolution of sex determination (e.g., \citealt{Bull:1983vi}, p 66-67; \citealt{Beukeboom:2014vb}, Chapter 7).
-`Fisherian' sex ratio selection favours a 1:1 zygotic sex ratio when assuming that males and females are equally costly to produce \citep{Fisher:1930wy,Charnov:1982wg}.
-This follows from the fact that, for an autosomal locus, half of the genetic material is inherited from a male and half from a female \citep{West:2009we}. 
+
+The sex ratio is directly determined by the sex-determination system, and it has therefore been suggested that sex ratio selection is a dominant force in the evolution of sex determination (e.g., Bull, 1983, p 66-67 ~\cite{Bull:1983vi}; Buekeboom and Perrin, 2014, Chapter 7~\cite{Beukeboom:2014vb}).
+`Fisherian' sex ratio selection favours a 1:1 zygotic sex ratio when assuming that males and females are equally costly to produce~\cite{Fisher:1930wy,Charnov:1982wg}.
+This follows from the fact that, for an autosomal locus, half of the genetic material is inherited from a male and half from a female~\cite{West:2009we}. 
 Thus, if the population sex ratio is biased towards one sex, the average per-individual contribution of genetic material to the next generation from the opposite sex is greater. 
@@
 %Given that the sex-determination system can directly affect the sex ratio, we might expect Fisherian sex ratio selection to influence the spread of new sex-determination systems. 
-In the case of sex-chromosome evolution, \citet{Kozielska:2010vm} consider systems in which the ancestral sex chromosomes experience meiotic drive (e.g., where driving X or Y chromosomes are inherited disproportionately often), which causes sex ratios to become biased \citep{Hamilton:1967ts}.
+In the case of sex-chromosome evolution, Kozielska et al.
+(2014)~\cite{Kozielska:2010vm} consider systems in which the ancestral sex chromosomes experience meiotic drive (e.g., where driving X or Y chromosomes are inherited disproportionately often), which causes sex ratios to become biased~\cite{Hamilton:1967ts}.
 They find that new, unlinked sex-determining loci (masculinizing or feminizing mutations, i.e., neo-Y or neo-W loci) can then spread, which restore an even sex ratio.
 
-%\textcolor{red}{We add haploid selection:}
 Here we use mathematical models to find the conditions under which new sex-determination systems spread when individuals experience selection at both diploid and haploid stages. 
-Even in animal and plant species that have much larger and more conspicuous diploid phases than haploid phases, many loci experience significant haploid selection through gamete competition and/or meiotic drive \citep{Mulcahy:1996ha,JOSEPH:2004haa}.
+Even in animal and plant species that have much larger and more conspicuous diploid phases than haploid phases, many loci experience significant haploid selection through gamete competition and/or meiotic drive~\cite{Mulcahy:1996ha,JOSEPH:2004haa}.
 We use the term `meiotic drive' to refer to the biased (non-Mendelian) segregation of genotypes during gamete production (from one parent) and the term `gametic competition' to refer to selection upon haploid genotypes within a gamete/gametophyte pool (potentially from multiple parents); the term `haploid selection' encompasses both processes.
 
-% from Bai et al.
-(2016) ``[Segregation distortion] phenomenon is commonly detected via genetic mapping and has been documented in various species, including mouse (Eversley et al., 2010; Casellas et al., 2012), Drosophila (Phadnis and Orr, 2009; Larracuente and Presgraves, 2012; McDermott and Noor, 2012), Tigriopus (Pritchard et al., 2011), rice (Koide et al., 2012; Reflinur et al., 2014; Xu et al., 2014), maize (Tang et al., 2013), and cotton (Yu et al., 2011; Hulse-Kemp et al., 2015).'' Also more in that paper that might be useful.
-%Drosophila http://www.biorxiv.org/content/early/2017/02/06/106336
-Segregation distortion provides putative evidence of haploid selection and can sometimes be attributed to meiotic drive and/or gametic competition \citep{Lalanne2004,Fishman2005,Leppala2008,Leppala2013,Didion2015,Didion2016}.
-Where it has been characterized, meiotic drive generally occurs either during the production of male or female gametes only \citep{Ubeda:2005gw,Lindholm:2016cw}.
+Segregation distortion provides putative evidence of haploid selection and can sometimes be attributed to meiotic drive and/or gametic competition~\cite{Lalanne2004,Fishman2005,Leppala2008,Leppala2013,Didion2015,Didion2016}.
+Where it has been characterized, meiotic drive generally occurs either during the production of male or female gametes only~\cite{Ubeda:2005gw,Lindholm:2016cw}.
 Gametic competition is also typically sex specific, occurring primarily among male gametes, because there are typically many more pollen/sperm than required for fertilization.
-Gametic competition may be particularly common in plants, in which 60-70\% of all genes are expressed in the male gametophyte, and these genes exhibit stronger signatures of selection than random genes \citep{Borg:2009jpa,Arunkumar:2013iq,Gossmann:2014dua}.
-In addition, artificial selection pressures applied to male gametophytes are known to cause a response to selection \citep[e.g.,][]{Hormaza:1996cv,Ravikumar:2003uo,Hedhly:2004iv,Clarke:2004ir}. 
-A smaller proportion of genes are thought to be expressed and selected during competition in animal sperm, although precise estimates are uncertain \citep{Zheng:2001fi,JOSEPH:2004haa,Vibranovski:2010et}.
-Nevertheless, recent studies have demonstrated that sperm competition in animals can alter haploid allele frequencies and increase offspring fitness \citep{Immler:2014im,Alavioon2017}.
+Gametic competition may be particularly common in plants, in which 60-70\% of all genes are expressed in the male gametophyte, and these genes exhibit stronger signatures of selection than random genes~\cite{Borg:2009jpa,Arunkumar:2013iq,Gossmann:2014dua}.
+In addition, artificial selection pressures applied to male gametophytes are known to cause a response to selection (e.g.,~\cite{Hormaza:1996cv,Ravikumar:2003uo,Hedhly:2004iv,Clarke:2004ir}. 
+A smaller proportion of genes are thought to be expressed and selected during competition in animal sperm, although precise estimates are uncertain~\cite{Zheng:2001fi,JOSEPH:2004haa,Vibranovski:2010et}.
+Nevertheless, recent studies have demonstrated that sperm competition in animals can alter haploid allele frequencies and increase offspring fitness~\cite{Immler:2014im,Alavioon2017}.
 
@@
 If we assume that haploid selection at any particular locus predominantly occurs in one sex (e.g., meiotic drive during spermatogenesis), then such loci experience a form of sex-specific selection. 
-In this respect, we might expect that haploid selection would affect transitions between sex-determination systems in a similar manner to sex-specific diploid selection \citep[as explored by][]{vanDoorn:2007eu,vanDoorn:2010hu}.
+In this respect, we might expect that haploid selection would affect transitions between sex-determination systems in a similar manner to sex-specific diploid selection (as explored in~\cite{vanDoorn:2007eu,vanDoorn:2010hu}).
 That is, new masculinizing mutations (neo-Y chromosomes) could be favoured via associations with alleles that are beneficial in the male haploid stage. 
 On the other hand, sex ratios can also become biased by linkage between the sex-determining region and a locus that harbours genetic variation in haploid fitness. 
-For example, there are several known cases of sex ratio bias caused by sex-linked meiotic drive alleles \citep[][Chapter 3]{Burt:2006} or selection among X- and Y-bearing pollen \citep{Lloyd:1974tz,Conn:1981uw,Stehlik:2005ul,Stehlik:2006to,Field:2012fd,Field:2013cc}.
+For example, there are several known cases of sex ratio bias caused by sex-linked meiotic drive alleles (Burt, 2006, Chapter 6~\cite{Burt:2006}) or selection among X- and Y-bearing pollen~\cite{Lloyd:1974tz,Conn:1981uw,Stehlik:2005ul,Stehlik:2006to,Field:2012fd,Field:2013cc}.
 It is not immediately clear how the spread of new sex-determination systems would be influenced by the combination of sex ratio biases and associations between haploid selected loci and sex-determining regions.
-
-%Perhaps longer discussion of tight sex-linkage here? e.g., mention that r=0 is a particularly significant case for sex chromosomes.
 
@@
 We find that loci linked with the ancestral sex-determining region can drive transitions in which the heterogametic sex changes, even when the neo-sex-determining locus is less closely linked to loci under selection (either including haploid selection or not).
-%Such transitions are not favoured in models lacking tight linkage and/or haploid selection. 
-%Secondly, we allow sex-specific haploid selection to occur on a locus in tight or loose linkage with the ancestral sex-determining region. 
-%In addition, when linkage between the ancestral sex-determining locus and a locus under haploid selection is tight, sex ratio biases can be strong such that there is an asymmetry between invasion of ancestrally XY and ancestrally ZW systems because, e.g., haploid selection in males only causes biased zygotic sex ratios in an ancestrally XY system.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%Lorem ipsum dolor sit~\cite{bib1} amet, consectetur adipiscing elit.
+Curabitur eget porta erat.
+Morbi consectetur est vel gravida pretium.
+Suspendisse ut dui eu ante cursus gravida non sed sem.
+Nullam Eq~(\ref{eq:schemeP}) sapien tellus, commodo id velit id, eleifend volutpat quam.
+Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus.
+Nunc pellentesque pretium diam, quis maximus dolor faucibus id.~\cite{bib2} Nunc convallis sodales ante, ut ullamcorper est egestas vitae.
+Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.
+
+%\begin{eqnarray}
+%\label{eq:schemeP}
+%	\mathrm{P_Y} = \underbrace{H(Y_n) - H(Y_n|\mathbf{V}^{Y}_{n})}_{S_Y} + \underbrace{H(Y_n|\mathbf{V}^{Y}_{n})- H(Y_n|\mathbf{V}^{X,Y}_{n})}_{T_{X\rightarrow Y}},
+%\end{eqnarray}
+
 \section*{Model}
-%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%genetic system
+We consider transitions between ancestral and novel sex-determining systems using a three-locus model, each locus having two alleles (Figure \ref{fig:model_outline}). 
+Locus \textbf{X} is the ancestral sex-determining region, with alleles $X$ and $Y$ (or $Z$ and $W$).
+Locus \textbf{A} is a locus under selection, with alleles $A$ and $a$.
+Locus \textbf{M} is a novel sex-determining region, at which the null allele ($M$) is initially fixed in the population such that sex of zygotes is determined by the genotype at the ancestral sex-determining region, \textbf{X}; $XX$ genotypes become females and $XY$ become males (or $ZW$ become females and $ZZ$ become males).
+To evaluate the evolution of new sex-determination systems, we consider the invasion, fixation, maintenance, and/or loss of novel sex-determining alleles ($m$) at the \textbf{M} locus. 
+%We only do invasion analytically though (is this sentence still ok?)
+We assume that the \textbf{M} locus is epistatically dominant over the \textbf{X} locus such that zygotes with at least one $m$ allele develop as females with probability $k$ and as males with probability $1-k$, regardless of the \textbf{X} locus genotype.
+With $k=0$, the $m$ allele is a masculinizer (i.e., a neo-Y) and with $k=1$ the $m$ allele is a feminizer (i.e., a neo-W).
+With intermediate $k$, we can interpret $m$ as an environmental sex determination (ESD) allele, such that zygotes develop as females in a proportion ($k$) of the environments they experience. 
+%We also analyze a model of maternally-controlled environmental sex-determination, where mothers with at least one $m$ allele produce daughters with probability $k$.
 
@@
 \begin{figure}[!h]
-\centering
-\centerline{\includegraphics[width=\linewidth]{Sex_determination_outline.pdf}}
+%\centering
+%\centerline{\includegraphics[width=\linewidth]{Sex_determination_outline.pdf}}
 \caption{
-Outline of model features. 
+{\bf Outline of model features.}
 Panel A: Recombination rate parameters between the ancestral-sex-determining locus (here, assumed to have X or Y alleles), a locus under selection (\textbf{A}, with alleles $A$ and $a$), and a neo-sex-determining locus (\textbf{M}, with alleles $M$ and $m$).
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\textcolor{red}{Change all  $\alpha^\Hermaphrodite$ to $(1+\alpha_{\Delta}^\Hermaphrodite)$.}
-%\textcolor{blue}{I've attempted this everywhere except in the recursions (S.1), which seem more natural with $\alpha$'s.
-I've run into trouble in equation S.8c,d -- I think we should check the Mathematica results to be sure we haven't made a typo.
-This also introduced an extra 1/2 in S.6c,d that might need to be explained.}
-%\textcolor{red}{hmm, not sure.
-This was an idea from Sally, I think in response to terms like $2 \alpha^\Hermaphrodite$ and $2(1-\alpha^\Hermaphrodite)$.
-It's possible that it makes other equations less easy to understand.
-My previous (not explained) logic was to use $w$ and $\alpha$ for strong selection and $s$, $t$, and $\alpha_\Delta$ for weak selection.
-Just to check, I should have written $\alpha^\Hermaphrodite=(1+\alpha_{\Delta}^\Hermaphrodite)/2$, maybe that's where the factors of $1/2$ come from?}
-%\textcolor{blue}{shoot, i may have changed too much (i.e.
-strong selection too), but i did use the correct transformation.
-still, the form of S.8c,d seems wrong.
-I'll double check it.
-CANT FIND ANY ERRORS YET STILL HAVE A "2" IN S.8c.
-These 2s reappear in S.9 and S.10, always with $W_{AA}$.}
-
-%\textcolor{red}{Switch between $\rho$ and $\rho$ in all places because $\rho$ is used for double recombination events.}
-%\textcolor{blue}{I think we need a different variable given the $\rho$ terms in the characteristic polynomial.
-Also, where is $\rho$ used for double recombination?
-In other papers?
-Here $\rho$ is the probability of an odd number of cross-overs between the SDR and M loci.}
-%\textcolor{red}{Good point, not sure what's best for \textbf{the-term-formerly-known-as-$\rho$}.
-Yeah, Sally's written comment was something like ``$\rho$ is semi-standard notation for double recombination so it's use as a recombination rate might be confusing''.}
-
-%\textcolor{red}{Change $\zeta$ to represent zygotic sex ratio of males, consistent with $q$ and figures.}
-
-%genetic system
-We consider transitions between ancestral and novel sex-determining systems using a three-locus model, each locus having two alleles. 
-Locus \textbf{X} is the ancestral sex-determining region, with alleles $X$ and $Y$ (or $Z$ and $W$).
-Locus \textbf{A} is a locus under selection, with alleles $A$ and $a$.
-Locus \textbf{M} is a novel sex-determining region, at which the null allele ($M$) is initially fixed in the population such that sex of zygotes is determined by the genotype at the ancestral sex-determining region, \textbf{X}; $XX$ genotypes become females and $XY$ become males (or $ZW$ become females and $ZZ$ become males).
-To evaluate the evolution of new sex-determination systems, we consider the invasion, fixation, maintenance, and/or loss of novel sex-determining alleles ($m$) at the \textbf{M} locus. 
-%We only do invasion analytically though (is this sentence still ok?)
-We assume that the \textbf{M} locus is epistatically dominant over the \textbf{X} locus such that zygotes with at least one $m$ allele develop as females with probability $k$ and as males with probability $1-k$, regardless of the \textbf{X} locus genotype.
-With $k=0$, the $m$ allele is a masculinizer (i.e., a neo-Y) and with $k=1$ the $m$ allele is a feminizer (i.e., a neo-W).
-With intermediate $k$, we can interpret $m$ as an environmental sex determination (ESD) allele, such that zygotes develop as females in a proportion ($k$) of the environments they experience. 
-%We also analyze a model of maternally-controlled environmental sex-determination, where mothers with at least one $m$ allele produce daughters with probability $k$.
 
@@
 \begin{table}[ht]
-\centering
+%\centering
 \smallskip
-\caption{Relative fitness of different genotypes in sex $\Hermaphrodite \in \{\female,\male\}$}
+\caption{{\bf Relative fitness of different genotypes in sex $\Hermaphrodite \in \{\female,\male\}$ } }
 \begin{tabular}{l c }
@@
 
-%Info moved above
-%what were going to do, briefly
-%With allele $M$ fixed at the \textbf{M} locus, sex is determined by locus \textbf{X} and an equilibrium is reached at locus \textbf{A}.
-%where, importantly, locus \textbf{A} can be stably polymorphic.
-%the dynamics can be described by the frequency of $A$ in gametes/gametophytes from the homogametic sex and the frequencies of $A$ in the two types of gametes/gametophytes from the heterogametic sex.
-%We then examine the ability of a rare, novel sex-determiner, $m$, to increase in frequency from this equilibrium.
-%Numerical simulations are used to examine when an invading mutation goes to fixation.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-%\subsection*{Turnover between sex-determination systems}
-
-\subsubsection*{Generic invasion by a neo-Y or neo-W}
+\subsection*{Generic invasion by a neo-Y or neo-W}
 
@@
 
-%\textcolor{red}{I now remove the zygotic sex ratio $\zeta$ from the mean fitnesses. The mean fitnesses will have to be adjusted in a corresponding way.}
-%
-%\textcolor{red}{CHECK: DO THE HAPLOID MEAN FITNESSES HAVE TO BE IN THE DENOMINATOR? i think so, based on definitions in table S.2 (mmo)}
-
-% as there are now two 2s in the lambdas of table 2. perhaps the 2 in the denominator is needed because the frequency of males sums to one as does the frequency of females?}
-
-\begin{threeparttable}[ht]
+\begin{table}[!ht]
 \centering
@@
 %\caption{Parameters determining invasion (equation \ref{eq:charpoly_neoY}) for neo-Y or neo-W alleles}
-\caption{Parameters determining invasion of mutant neo-Y and neo-W alleles into an ancestrally XY system}
+\caption{ {\bf Parameters determining invasion of mutant neo-Y and neo-W alleles into an ancestrally XY system}}
 \begin{tabular}{l}
@@
   $\chi_{WA} = R \left[ 2 (1 - \zeta) \right]^{-1} \left[ (1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female} (1+\alpha_{\Delta}^{\female}) \right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \right)  $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\chi_{Wa} = R \left[ 2 (1 - \zeta) \right]^{-1} \left[ \bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female} (1-\alpha_{\Delta}^{\female}) \right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \right) $\\ [1ex]
+  $\chi_{Wa} = R \left[ 2 (1 - \zeta) \right]^{-1} \left[ \bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female} (1-\alpha_{\Delta}^{\female}) \right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \right) $ \\ [1ex]
   \hline \hline 
    \end{tabular}
-      \begin{tablenotes}
-      \scriptsize
-      \item $\bar{p}^{\male}=(1-\hat{q})\hat{p}_X^\male + \hat{q}\hat{p}_Y^\male$ is the average frequency of the $A$ allele among X- and Y-bearing male gametes.
+   \begin{flushleft} 
+$\bar{p}^{\male}=(1-\hat{q})\hat{p}_X^\male + \hat{q}\hat{p}_Y^\male$ is the average frequency of the $A$ allele among X- and Y-bearing male gametes.
 %      \item $R$ is the probability of recombination between loci \textbf{A} and \textbf{M}.
-      \item $\zeta$ is the zygotic sex ratio (fraction male)
-      \item $\bar{w}^\Hermaphrodite$ is the mean fitness of diploids of sex $\Hermaphrodite$, see Table \ref{tab:meanfitnesses}
-      \item $\bar{w}_H^\Hermaphrodite$ is the mean fitness of haploids from sex $\Hermaphrodite$, see Table \ref{tab:meanfitnesses}
-%      \item $\bar{w}_H^\female = p_X^\female w_A^\female + (1-p_X^\female) w_a^\female$ is the mean fitness of female gametes during gametic competition
-%      \item $\bar{w}_H^\male = \bar{p}^{\male} w_A^\male + (1-\bar{p}^{\male}) w_a^\male$ is the mean fitness of male gametes during gametic competition
-%       \item $\bar{w}^\female = \{ p_X^\female w_A^\female (1-q) p_X^\male w_A^\male w_{AA}^\female + (1 - p_X^\female) w_a^\female (1-q) p_X^\male w_A^\male w_{Aa}^\female + p_X^\female w_A^\female (1-q) (1 - p_X^\male) w_a^\male w_{Aa}^\female + (1-p_X^\female) w_a^\female (1-q) (1 - p_X^\male) w_a^\male w_{aa}^\female \} / \{ \bar{w}_H^\female \bar{w}_H^\male\}$ is the mean fitness of females during diploid competition
-%       \item $\bar{w}^\male = \{ p_X^\female w_A^\female q p_Y^\male w_A^\male w_{AA}^\male + (1 - p_X^\female) w_a^\female q p_Y^\male w_A^\male w_{Aa}^\male + p_X^\female w_A^\female q (1 - p_Y^\male) w_a^\male w_{Aa}^\male + (1-p_X^\female) w_a^\female q (1 - p_Y^\male) w_a^\male w_{aa}^\male \} / \{ \bar{w}_H^\male \bar{w}_H^\male\}$ is the mean fitness of males during diploid competition
-    \end{tablenotes}
+$\zeta$ is the zygotic sex ratio (fraction male).
+$\bar{w}^\Hermaphrodite$ is the mean fitness of diploids of sex $\Hermaphrodite$, see Table \ref{tab:meanfitnesses}.
+$\bar{w}_H^\Hermaphrodite$ is the mean fitness of haploids from sex $\Hermaphrodite$, see Table \ref{tab:meanfitnesses}.
+\end{flushleft}
   \label{tab:haplotype_growth}
-\end{threeparttable}
-\\
-
-%We are particularly concerned with the conditions under which a rare neo-sex-determining allele increases in frequency, which occurs when the largest eigenvalue, $\lambda$, is greater than one. 
-%If one or both of $\lambda_{mA}$ and $\lambda_{ma}$ are greater than one, indicating that at least one haplotype increases in frequency faster than recombination breaks it apart, invasion will always occur ($\lambda>1$).
-%Otherwise, invasion requires
-%\begin{equation}
-%(\lambda_{mA}-1)(\lambda_{ma}-1) - \chi_{mA} \chi_{ma}<0.
-%\end{equation}
+\end{table}
 
@@
 Interpreting this condition, if we assume that only the $mA$ haplotype has a positive growth rate when $R=0$, $\lambda_{ma}<1<\lambda_{mA}$, the first term on the left-hand side of \eqref{eq:lambdasGen} is negative and invasion requires that the $mA$ haplotype growth rate ($\lambda_{mA}-1$) and the rate at which they are produced by recombination in $ma$ haplotypes ($\chi_{ma}$) are sufficiently large relative to the $ma$ haplotype rate of decline ($1-\lambda_{ma}$) and the rate of loss of $mA$ haplotypes due to recombination ($\chi_{mA}$).
-%In other words, invasion requires that the average growth rate of the two haplotypes, weighted by the rates they are created by recombination, is positive.
-%the number of recombinants from the fitter $mA$ haplotypes is larger than that of the less fit $ma$ haplotypes, relative to their growth rates.
 
@@
 Here, we focus on polymorphisms maintained by selection, where the $A$ allele reaches a stable intermediate equilibrium frequency under the ancestral sex-determination system before the neo-sex-determining allele ($m$) arises.
-Such polymorphisms can be maintained by heterozygote advantage, sexually-antagonistic selection, ploidally-antagonistic selection, or a combination \citep{Immler:2012tl}.
+Such polymorphisms can be maintained by heterozygote advantage, sexually-antagonistic selection, ploidally-antagonistic selection, or a combination~\cite{Immler:2012tl}.
 We can analytically calculate the allele frequency of the $A$ allele using two alternative simplifying assumptions: 
@@
 
-\subsubsection*{Tight linkage with the ancestral sex-determining region ($r \approx 0$)}
+\subsection*{Tight linkage with the ancestral sex-determining region ($r \approx 0$)}
 
@@
 Neo-W alleles, on the other hand, can invade an ancestral XY system under some conditions (the full invasion conditions are given in the appendix; equations \ref{Binvasion} and \ref{Ainvasion}). 
-Counterintuitively, selection on loci within the non-recombining region of the SDR can favour the invasion of a less closely linked neo-W, whatever the form of selection maintaining a polymorphism (sexually-antagonistic selection, overdominance, ploidally-antagonistic selection, or some combination, Figures \ref{fig:SexAntagTighter}, \ref{fig:temporalOverdominance}, \ref{fig:regionPloidAntag}, and \ref{fig:SexAntagTighterMaleDrive}).
+Counterintuitively, selection on loci within the non-recombining region of the SDR can favour the invasion of a less closely linked neo-W, whatever the form of selection maintaining a polymorphism (sexually-antagonistic selection, overdominance, ploidally-antagonistic selection, or some combination, Figures \ref{fig:SexAntagTighter}, \nameref{fig:temporalOverdominance}, \nameref{fig:regionPloidAntag}, and \nameref{fig:SexAntagTighterMaleDrive}).
 The conditions become more restrictive, however, with increasing recombination ($R$) between the new sex determining region and the selected locus.  
@@
 \centering
-\centerline{\includegraphics[width=1.5\linewidth]{PositionPlot_SexAntagTighter}}
+%\centerline{\includegraphics[width=1.5\linewidth]{PositionPlot_SexAntagTighter}}
 \caption{
-Transitions between XY and ZW systems can occur even when the neo-SDR is less tightly linked to a locus under sexually-antagonistic selection (here, without haploid selection).
+{\bf Transitions between XY and ZW systems can occur even when the neo-SDR is less tightly linked to a locus under sexually-antagonistic selection (here, without haploid selection).}
 In panel A, linkage is loose enough relative to selection that the analytical results assuming weak selection hold, and a neo-W can only invade when it is more tightly linked with the selected locus ($R<r$; shaded region).
-In panel B, linkage is tight enough relative to selection that the analytical results assuming weak selection do not hold, and a neo-W can invade even when it is less tightly linked with the selected locus ($r<R$; unshaded region).
+In panel B, linkage is tight enough relative to selection that the analytical results assuming weak selection do not hold, and a neo-W can invade even when it is less tightly linked with the selected locus ($r<R$; unshaded region marked by \text{*}).
 In panel C we vary the recombination rate between the neo-W and the selected locus ($R$) for a fixed recombination rate between the ancestral-SDR and the selected locus ($r=0.005$). 
-Coloured markers show recombination rates for which the temporal dynamics of invasion are plotted in the inset, demonstrating that neo-W alleles can fix (reach frequency $0.5$ among female gametes) if they are more (black) or less (red) closely linked to a locus experiencing sexually-antagonistic selection.
+Coloured markers show recombination rates for which the temporal dynamics of invasion are plotted in the inset, demonstrating that neo-W alleles can reach pseudo-fixation if they are more (black) or less (red) closely linked to a locus experiencing sexually-antagonistic selection.
 A very loosely linked neo-W does not spread in this case (blue and green lines overlap and go to 0). 
@@
 
-When only one neo-W haplotype has a positive growth rate (see Figure \ref{fig:regionplots}), a neo-W can invade as long as equation \eqref{eq:lambdasGen} is satisfied, which may require that the recombination rate, $R$, is small enough.
-Nevertheless, because we assume here that $r$ is small, these results indicate that a more loosely linked sex-determining region ($r<R$) can spread.
-Therefore, tightly sex-linked loci that experience sexually-antagonistic selection can drive trans-GSD transitions in which the neo-SDR is less closely linked to the locus under selection (Figure \ref{fig:SexAntagTighter}).
-
-Given that the $a$ allele can be considered ancestrally `male-beneficial' because it is fixed on the Y, it is surprising that neo-W-$a$ haplotypes can sometimes be favoured by selection in females ($\lambda_{Wa}>1$).
-Again, this occurs because ancestral X's also experience selection in males, in which they will always be paired with a Y-$a$. 
-If there is overdominance in males, X-$A$ Y-$a$ males have high fitness and the $A$ allele is favoured by selection on the X in males. 
-Therefore, the X can be polymorphic or even fixed for the $A$ allele despite favouring the $a$ allele during selection in females \citep[e.g., see outlined region in Figure \ref{fig:regionplots}B and][]{Lloyd1977,Otto2014}.
-In such cases, neo-W-$a$ haplotypes can spread because they create more $Aa$ and $aa$ females when pairing with an X from males and because they bring Y-$a$ haplotypes into females, where it has higher fitness (Figure \ref{fig:model_outline}D).
-
-In some cases, both W-$A$ and W-$a$ haplotypes can spread, e.g., when $AA$ individuals have low fitness in females yet the $A$ is polymorphic or fixed on the X due to overdominance in males (Figure \ref{fig:regionplots}B and \ref{fig:regionplots}C).
-Both neo-W-$A$ and neo-W-$a$ haplotypes then produce fewer unfit $AA$ females.
-This is true for the neo-W-$A$ haplotype because it can pair with a Y-$a$ haplotype and still be female. 
-Wherever both haplotypes have positive growth rates, invasion by a neo-W is expected regardless of its linkage with the selected locus (i.e., even unlinked neo-W alleles can invade, see Figures \ref{fig:positionOverdominance} and \ref{fig:temporalOverdominance} for examples).
-
-Assuming that linkage is not tight, \citet{vanDoorn:2010hu} showed that invasion by a neo-W occurs under the same conditions as `pseudo-fixation' (at pseudo-fixation the neo-W reaches its maximum frequency among eggs, which is 1/2).
-An equivalent analysis is not possible where we assume that linkage is tight. 
-However, numerical simulations with tight linkage demonstrate that the neo-SDR does not necessarily reach pseudo-fixation, leading to the stable maintenance of a mixed sex-determining system, in which X, Y, Z, and W alleles all segregate (e.g., Figure \ref{fig:freqAll}B,C).
-
-%Haploid selection impacts the spread of neo-W haplotypes through its direct selective effect on females and their gametes, its indirect effect on the marginal fitness of alleles in females resulting from haploid selection in male gametes, and its effect on the sex ratio.
-%These impacts expand the scenarios under which neo-W haplotypes can spread.
-%For instance, overdominance is no longer required for neo-W-$a$ haplotypes to spread when there is haploid selection (e.g., when $a$ is female-beneficial, $A$ is male-beneficial, and meiotic drive in males favours $a$, Figure \ref{fig:regionMaleDrive}B).
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %\centerline{\includegraphics[width=1.25\linewidth]{Region_plot_combined_Mike}}
-\centerline{\includegraphics[width=1.25\linewidth]{Region_plot_combined}}
+%\centerline{\includegraphics[width=1.25\linewidth]{Region_plot_combined}}
 \caption{
-When the ancestral-XY locus is tightly linked to a locus under selection ($r=0$), one or both neo-W haplotypes can spread. 
+{\bf When the ancestral-XY locus is tightly linked to a locus under selection ($r=0$), one or both neo-W haplotypes can spread. }
 We vary the fitness of male homozygotes relative to heterozygotes ($w_{Aa}^\Hermaphrodite=1$) and only consider stable equilibria at which both \textbf{A} locus alleles are maintained and the $a$ allele is initially fixed on the Y, region outlined.
@@
 Where both $\lambda_{wA}$ and $\lambda_{wa}$ are greater than one, a neo-W will spread when rare, regardless of linkage with the selected locus (for any $R$). 
-Figure \ref{fig:positionOverdominance} shows the dynamics using the parameters marked with a dagger. 
+Figure \nameref{fig:positionOverdominance} shows the dynamics using the parameters marked with a dagger. 
 Here, there is no haploid selection $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
@@
 
-%Neo-W alleles, on the other hand, can invade an ancestral XY system under some conditions (given in detail in the appendix). 
-%%The full characteristic polynomials are given in the appendix (equations \ref{Binvasion} and \ref{Ainvasion}).
-%Briefly, neo-W-$A$ and/or neo-W-$a$ haplotypes can spread when rare in the absence of recombination ($\lambda_{ma}>1$ and/or $\lambda_{mA}>1$), depending on the ancestral sex ratio and allele frequencies.
-%Below we discuss the main forces determining the spread of these neo-W haplotypes and the impact of recombination for the overall success of the neo-W.
-%To simplify our discussion we first outline the potential effects of haploid selection and then consider diploid selection in its absence.
-
-%\textcolor{blue}{This explanation is clearer than the one I put in the appendix, if we drop it here, maybe we should try and re-word the corresponding part of the appendix using this paragraph}
-%Haploid selection impacts the spread of neo-W haplotypes in three ways.
-%Firstly, the zygotic sex ratio becomes male biased ($\zeta<1/2$) when the $a$ allele (which is fixed on the Y) is favoured during competition among male gametes or by meiotic drive in males. 
-%This facilitates the spread of a neo-W because neo-W alleles cause the zygotes that carry them to develop as the rarer, female, sex. 
-%Secondly, haploid selection in males affects the diploid genotypes of females by altering the allele frequencies in the male gametes that female gametes pair with.
-%For instance, because an epistatically dominant neo-W always causes its carrier to become female, it creates females who carry either $Y-a$ or $X$ genotypes from their father.
-%Thus, because when there is a polymorphism the $X$ carries some non-zero frequency of $A$, haploid selection in males impacts the diploid genotypes of females (e.g., creating more $Aa$ females when drive in males favours $Y-a$).
-%How this affects the spread of the neo-W then depends on diploid and haploid selection in females.
-%Thirdly, female drive and gamete competition directly select on neo-W haplotypes.
-%Drive for $A$ in females favours neo-W-$A$ haplotypes, at a cost to neo-W-$a$ haplotypes, and vice-versa when there is drive for $a$.
-%The impact of this drive depends on how often XX and neo-W females are heterozygous.
-%Competition among female gametes acts similarly, and depends on the frequency of $A$ on resident X chromosomes (e.g., competition among eggs has no affect on the initial spread of the neo-W-$A$ haplotype when $A$ is fixed on the X).
-%Because haploid selection in females favours one neo-W haplotype at the expense of the other, recombination off the favoured background becomes more detrimental as it becomes more favoured.
-Thus higher rates of recombination between the neo-W and the selected locus, $R$, can lead to smaller leading eigenvalues when there is haploid selection in females.
-
-%In the absence of haploid selection and with the $A$ allele is fixed on the X, it is possible for both neo-W haplotypes can spread ($\lambda_{mA}>1$ and $\lambda_{ma}>1$ in \ref{Binvasion}), and thus neo-W invasion can occur regardless of its linkage to the selected locus.
-%Invasion does not occur with purely sexually-antagonistic selection (i.e., $a$ directionally favoured in males and $A$ directionally favoured in females) because the X is then already as specialized as possible on the female sex.
-%However, if, for example, $AA$ individuals suffer a fitness cost in females, yet $A$ is fixed on the X due to strong overdominance in males, both neo-W-$A$ and neo-W-$a$ haplotypes spread because they produce fewer unfit $AA$ females and never experience counter-selection in males.
-%This is true even for the neo-W-$A$ haplotype because it can pair with a $Y-a$ haplotype and still be female. 
-%When both haplotypes can spread alone the rate of recombination between the neo-W and the selected locus, $R$, does cannot prevent invasion, and thus the system can evolve looser sex-linkage (e.g., the neo-W could arise on an autosome, $R=1/2$).
-%Even when only one haplotype can spread, invasion can still occur up to some positive rate of recombination, $R>0$ (as long as equation \ref{eq:lambdasGen} is satisfied). 
-%That looser sex-linkage can evolve is contrary to the conclusions of \cite{vanDoorn:2010hu}, who did not explicitly calculate invasion fitness under ancestrally tight sex-linkage.
-\textcolor{blue}{or, just didn't calculate the equilibria (A) an (B).}
-%Similar scenarios have been shown to select for a modifier that increases recombination between the sexes \citep[green regions of Figure 2 in][]{Otto2014}.
-%\textcolor{blue}{n.b., the recombination regions are only subsets mostly because you also generate a really unfit Y haplotype through recombination. Probably not worth mentioning.}
-%
-%In the absence of haploid selection it is also possible for a neo-W to invade when there is a stable polymorphism at the $\mathbf{A}$ locus on X chromosomes.
-%For example, overdominance in males and strong directional selection for $a$ in females creates a scenario that favours the spread of both neo-W haplotypes at equilibrium ($\lambda_{mA}>1$ and $\lambda_{ma}>1$ in \ref{Ainvasion}), as both haplotypes bring more $a$ alleles into females and never experience counter-selection in males.
-%Thus, as in the case of the $A$ being fixed on the X, looser sex-linkage can evolve with a polymorphic X (i.e., $\lambda>1$ with $R>0$) and this is expected under the same scenarios that select for a modifier that increases recombination between the sex chromosomes \citep[blue regions of Figure 2 in][]{Otto2014}.
-
-\subsubsection*{Loose linkage with the ancestral sex-determining region}
-
-%\textcolor{blue}{As with the discussion, this section might need some editing for (1) unclearly describing looser linkage never evolving without haploid selection, which we now show is possible above and (2) going on about sex ratio selection too much - this should be changed to something along the lines of  ``male biased zygotic sex ratios ($\zeta-1/2$) are of the order of $\epsilon^2$.
-Therefore Fisherian sex ratio selection directly favours neo-Ws by a similar magnitude.
-%Perhaps surprisingly, neo-Ws can be favoured to the same degree by haploid selection in females when female haploid selection favours the alleles that tend to be carried by the neo-W.
-%Thus XY to ZW is the same as ZW to XY even though sex ratio biases only exist in one case, given the assumptions made in this section.
-%''
-%}
-
-%weak selection
-%We are particularly concerned with whether or not a rare neo-sex-determining allele increases in frequency, which occurs when the largest eigenvalue, $\lambda$, is greater than one. 
-%Here, we explicitly determine the conditions under which invasion occurs by assuming that the $A$ allele reaches an equilibrium frequency under the ancestral sex-determination system before the neo-sex-determination system ($m$) arises.
-%The equilibrium frequency of $A$ on different ancestral backgrounds ($\hat{p}^\male_Y$, $\hat{p}^\male_X$, and $\hat{p}^\female_X$) is given by equations \eqref{eq:pAve} and \eqref{eq:freq_diffs} where we assume selection and meiotic drive are weak relative to recombination ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon$).
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+When only one neo-W haplotype has a positive growth rate (see Figure \ref{fig:regionplots}), a neo-W can invade as long as equation \eqref{eq:lambdasGen} is satisfied, which may require that the recombination rate, $R$, is small enough.
+Nevertheless, because we assume here that $r$ is small, these results indicate that a more loosely linked sex-determining region ($r<R$) can spread.
+Therefore, tightly sex-linked loci that experience sexually-antagonistic selection can drive trans-GSD transitions in which the neo-SDR is less closely linked to the locus under selection (Figure \ref{fig:SexAntagTighter}).
+
+Given that the $a$ allele can be considered ancestrally `male-beneficial' because it is fixed on the Y, it is surprising that neo-W-$a$ haplotypes can sometimes be favoured by selection in females ($\lambda_{Wa}>1$).
+Again, this occurs because ancestral X's also experience selection in males, in which they will always be paired with a Y-$a$. 
+If there is overdominance in males, X-$A$ Y-$a$ males have high fitness and the $A$ allele is favoured by selection on the X in males. 
+Therefore, the X can be polymorphic or even fixed for the $A$ allele despite favouring the $a$ allele during selection in females (e.g., see outlined region in Figure \ref{fig:regionplots}B and~\cite{Lloyd1977,Otto2014}).
+In such cases, neo-W-$a$ haplotypes can spread because they create more $Aa$ and $aa$ females when pairing with an X from males and because they bring Y-$a$ haplotypes into females, where it has higher fitness (Figure \ref{fig:model_outline}D).
+
+In some cases, both W-$A$ and W-$a$ haplotypes can spread, e.g., when $AA$ individuals have low fitness in females yet the $A$ is polymorphic or fixed on the X due to overdominance in males (Figure \ref{fig:regionplots}B and \ref{fig:regionplots}C).
+Both neo-W-$A$ and neo-W-$a$ haplotypes then produce fewer unfit $AA$ females.
+This is true for the neo-W-$A$ haplotype because it can pair with a Y-$a$ haplotype and still be female. 
+Wherever both haplotypes have positive growth rates, invasion by a neo-W is expected regardless of its linkage with the selected locus (i.e., even unlinked neo-W alleles can invade, see Figures \nameref{fig:positionOverdominance} and \nameref{fig:temporalOverdominance} for examples).
+
+Assuming that linkage is not tight, van Doorn and Kirkpatrick (2010)~\cite{vanDoorn:2010hu} showed that invasion by a neo-W occurs under the same conditions as `pseudo-fixation' (at pseudo-fixation the neo-W reaches its maximum frequency among eggs, which is 1/2).
+An equivalent analysis is not possible where we assume that linkage is tight. 
+However, numerical simulations with tight linkage demonstrate that the neo-SDR does not necessarily reach pseudo-fixation, leading to the stable maintenance of a mixed sex-determining system, in which X, Y, Z, and W alleles all segregate (e.g., Figure \nameref{fig:freqAll}B,C).
+
+\subsection*{Loose linkage with the ancestral sex-determining region}
+
 Assuming that selection is weak ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon<<1$) and thus implicitly assuming that all recombination rates ($r$, $R$ and $\rho$) are large relative to selection, we denote the leading eigenvalues describing the invasion of a neo-Y ($k=0$) and a neo-W ($k=1$) into an ancestrally XY system by $\lambda_{Y',XY}$ and $\lambda_{W',XY}$, respectively.
@@
 \lambda_{W',XY} =\lambda_{Y',XY}+\left(2\alpha_{\Delta}^\male-2\alpha_{\Delta}^\female+t^\male-t^\female \right) \left( \hat{p}^\male_Y-\hat{p}^\male_X \right)/2
-+O\left(\epsilon^3 \right) \\
++O\left(\epsilon^3 \right)
 \label{eq:lambda_neoW}
@@
 This echoes our tight linkage results above where a neo-Y could never invade if $r\approx0$.
-It is also consistent with the results of \citet{vanDoorn:2007eu}, who considered diploid selection only and also found that cis-GSD transitions (XY to XY or ZW to ZW) can only occur when the neo-sex-determining locus is more closely linked to a locus under sexually-antagonistic selection.
+It is also consistent with the results of \cite{vanDoorn:2007eu}, who considered diploid selection only and also found that cis-GSD transitions (XY to XY or ZW to ZW) can only occur when the neo-sex-determining locus is more closely linked to a locus under sexually-antagonistic selection.
 %Because tighter linkage between the sex-determining region and a selected locus evolves during these transitions, stronger associations between selected alleles and diploid sexes can build up by selection (e.g., between male-beneficial alleles and the male-determining allele, Y).%, increasing diploid mean fitness (Figure \ref{fig:Combination_MeanFit}).
 
-With weak selection and no haploid selection ($t^\Hermaphrodite=\alpha^\Hermaphrodite_{\Delta}=0$), the spread of a neo-W is equivalent to the spread of a neo-Y ($\lambda_{W',XY}=\lambda_{Y',XY}$), such that trans-GSD transitions (XY to ZW or ZW to XY) can also occur only if the neo-sex-determining region is more closely linked to a locus under selection ($R<r$), as found by \citet{vanDoorn:2010hu}.
+With weak selection and no haploid selection ($t^\Hermaphrodite=\alpha^\Hermaphrodite_{\Delta}=0$), the spread of a neo-W is equivalent to the spread of a neo-Y ($\lambda_{W',XY}=\lambda_{Y',XY}$), such that trans-GSD transitions (XY to ZW or ZW to XY) can also occur only if the neo-sex-determining region is more closely linked to a locus under selection ($R<r$), as found by \cite{vanDoorn:2010hu}.
 With haploid selection, however, the additional term in equation \eqref{eq:lambda_neoW} can be positive, which can allow, for example, neo-W invasion ($\lambda_{W',XY}>1$) even when the neo-sex-determining region is less closely linked to the selected locus ($R>r$).
@@
 %Mean diploid fitness therefore decreases during heterogametic transitions that create looser sex-linkage (Figure \ref{fig:Combination_MeanFit}B,D).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%A neo-W can invade an XY system under a large number of selective regimes
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-\includegraphics[width=\linewidth]{PositionPlot}
-\caption{
-% A neo-W can invade an XY system under a large number of selective regimes.
-%In panel A, there is no haploid selection ($t^\Hermaphrodite = \alpha^\Hermaphrodite_{\Delta} = 0$) and selection in diploids is sexually antagonistic ($s^\male = -s^\female = 1/10$, $h^\male = 1-h^\female = 3/10$), in which case the neo-sex-determining allele can only invade if it is more closely linked to the selected locus ($R<r$, gray region; but see Figure \ref{fig:SexAntagTighter}B for the case of very tight linkage).
-Ploidally-antagonistic selection allows a less tightly linked neo-W to invade.
-In panel A, male drive ($\alpha^\male_{\Delta} = -1/20$, $t^\Hermaphrodite = \alpha^\female_{\Delta} = 0$) opposes selection in diploids (no sex-differences: $s^\Hermaphrodite = 1/10$, $h^\Hermaphrodite = 7/10$), in which case the neo-sex-determining allele can invade regardless of linkage.
-In panel B, gametic competition in males ($t^\male = -1/10$, $t^\female = \alpha^\Hermaphrodite_{\Delta} = 0$) opposes selection in diploids (sex-differences: $s^\male = 3/20$, $s^\female = 1/20$, $h^\Hermaphrodite = 7/10$), in which case the neo-sex-determining allele can once again invade regardless of linkage.
-We use Haldane's map function \citep[Equation 3 in ][]{Haldane1919} to convert from map distance (centiMorgans, cM) to the probability of recombination (an odd number of cross-over events).   
-%\textcolor{red}{Check the mismatch between red and black lines here: probably because of adding or subtracting from 1. }
-%\textcolor{blue}{Can remove the mismatch by flipping the fitnesses between males and females (again).
-That is, if $M_{AA}$ is the fitness of $AA$ male diploids in an ancestral XY system, then $M_{AA}$ is the fitness of $AA$ female diploids in an ancestral ZW system.
-I think this makes sense in A, where we don't really want a difference between the red and black curves, but this makes less sense in B and C where we want to restrict haploid selection to males regardless of the ancestral system.
-We could just not flip the haploid fitnesses, but then does it make sense to flip the diploid fitnesses?}
-}
-\label{fig:Combination_Centimorgans}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 Indeed, invasion typically occurs when the neo-W is more closely linked to the selected locus than the ancestral sex-determining region (Figure \ref{fig:Combination_Centimorgans}).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%A neo-W can invade an XY system under a large number of selective regimes
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[!h]
+\centering
+%\includegraphics[width=\linewidth]{PositionPlot}
+\caption{
+{\bf Ploidally-antagonistic selection allows a less tightly linked neo-W to invade.}
+In panel A, male drive ($\alpha^\male_{\Delta} = -1/20$, $t^\Hermaphrodite = \alpha^\female_{\Delta} = 0$) opposes selection in diploids (no sex-differences: $s^\Hermaphrodite = 1/10$, $h^\Hermaphrodite = 7/10$), in which case the neo-sex-determining allele can invade regardless of linkage.
+In panel B, gametic competition in males ($t^\male = -1/10$, $t^\female = \alpha^\Hermaphrodite_{\Delta} = 0$) opposes selection in diploids (sex-differences: $s^\male = 3/20$, $s^\female = 1/20$, $h^\Hermaphrodite = 7/10$), in which case the neo-sex-determining allele can once again invade regardless of linkage.
+We use Haldane's map function (Equation 3 in \cite{Haldane1919}) to convert from map distance (centiMorgans, cM) to the probability of recombination (an odd number of cross-over events).   
+}
+\label{fig:Combination_Centimorgans}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\begin{table}[ht]
+\begin{table}[!ht]
 \centering
@@
 
-%If we further assume equal dominance ($h^\female=h^\male$) and that haploid selection only occurs during male meiosis ($t^\female=t^\male=\alpha^\female_{\Delta}=0$), or female meiosis ($t^\female=t^\male=\alpha^\male_{\Delta}=0$), neo-W invasion occurs when $s^\female s^\male>0$, Figure \ref{fig:Combination_Centimorgans}B.
-%That is, when the same allele is favoured by selection in both males and females (it may remain polymorphic via counter selection during meiotic drive).
-
-%\textcolor{red}{It may seem counterintuitive that, if the $A$ allele is more common on the ancestral-Y than the ancestral-X, and only favoured during haploid selection in males}
-
-%\textcolor{red}{although our predictions also perform well when recombination is small, see figure \ref{fig:WinvasionLowR}.
-We would have to add a line showing what invasion fitness the weak selection approximation would give and add dots to this figure (dots that are currently connected by a line), as in (vD\&K, 2010) }
-
-%Sex ratios
-%Previous research suggests that when the ancestral sex-determining locus is linked to a locus that experiences haploid selection (e.g., meiotic drive), a new, unlinked sex-determining locus invades in order to restore equal sex ratios \citep{Kozielska:2010vm}.
-%Our model provides a good opportunity to determine whether Fisherian sex ratio selection provides a useful explanation for the evolution of new sex-determining loci in other contexts. 
-%Consider, for example, the case where the \textbf{A} locus is linked to the ancestral-SDR ($r<1/2$) and experiences meiotic drive in males only (e.g., during spermatogenesis but not during oogenesis, $\alpha^\male \neq 1/2$, $\alpha^\female=1/2$).
-%We will also disregard gametic competition ($t^\female=t^\male=0$) such that zygotic sex ratios are only biased by meiotic drive in males. 
-%In this case, the zygotic sex ratio can be initially biased only if the ancestral sex-determining system is XY (Figure \ref{fig:Combination_Turnover}B). 
-%If the ancestral sex-determining system is ZW, the zygotic sex ratio will be 1:1 because diploid sex is determined by the proportion of Z-bearing versus W-bearing eggs and meiosis in females is fair (Figure \ref{fig:Combination_Turnover}D).
-%Thus, if the zygotic sex ratio is crucial to the evolution of new genetic sex-determining systems, invasion into ZW and XY systems will be distinct. 
-%However, under weak selection we find that invasion by a homogametic neo-sex-determining allele (XY to XY or ZW to ZW) or by a heterogametic neo-sex-determining allele (XY to ZW or ZW to XY) occur under the same conditions.
-%That is, we can show that $\lambda_{Y',XY}=\lambda_{W',ZW}$ and $\lambda_{Y',ZW}=\lambda_{W',XY}$ (at least up to order $\epsilon^3$; for a numerical example, compare Figure \ref{fig:Combination_Turnover}A,B to Figure \ref{fig:Combination_Turnover}C,D).
-%As it turns out, under weak selection the strength of sex ratio selection favouring, say, the invasion of a neo-W in an XY system is the same as the strength of meiotic drive favouring the invasion of a neo-Y in a ZW system.
-%Even when these forces are not exactly the same (e.g., under tight sex-linkage; compare black and red curves near -25 and 25cM in Figure \ref{fig:Combination_Centimorgans}), it is important to remember that sex ratio selection is only one of many potential selective forces acting to determine transitions between sex-determining systems.
-%It is even possible for the other selective forces to overwhelm sex ratio selection and favour sex-determination transitions that create sex ratio biases (Figure \ref{fig:Combination_Turnover}A,C).
-
-Previous research suggests that when the ancestral sex-determining locus is linked to a locus that experiences haploid selection (e.g., meiotic drive), a new, unlinked sex-determining locus invades in order to restore equal sex ratios \citep{Kozielska:2010vm}.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Sex ratio selection is not a good predictor of neo-W invasion into an XY system
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[!h]
+\centering
+%\includegraphics[width=\linewidth]{Temporal_SR}
+\caption{
+{\bf Fisherian sex ratio selection alone is not a good predictor of turnover between sex-determining systems.}
+In this figure, selection is ploidally antagonistic with haploid selection favouring the $a$ allele during male meiosis.
+In panel A, male drive in an ancestral XY system causes a male bias (see Figure \ref{fig:model_outline}B), allowing a neo-W to invade and replace the ancestral sex-determination system (inset shows neo-W frequency among female gametes), which balances the zygotic sex ratio.
+In panel B, male drive in an ancestral ZW system has no affect on the zygotic sex ratio (see Figure \ref{fig:model_outline}B) yet a neo-Y can invade and replace the ancestral sex-determination system (inset shows neo-Y frequency among male gametes, the ancestral W also goes to fixation during this transition).
+When $R<1/2$, the neo-Y becomes associated with the allele favoured by drive, causing the zygotic sex ratio to become biased, hence the frequency of the neo-Y at pseudo-fixation can be higher than $0.5$ (inset).
+Parameters:  $s^\female =s^\male = 0.2$, $h^\female = h^\male = 0.7$, $t^\female = t^\male = \alpha^\female_\Delta = 0$, $\alpha^\male_\Delta = -0.1$, $r=0.02$.
+}
+\label{fig:SexRatioBad}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Previous research suggests that when the ancestral sex-determining locus is linked to a locus that experiences haploid selection (e.g., meiotic drive), a new, unlinked sex-determining locus invades in order to restore equal sex ratios~\cite{Kozielska:2010vm}.
 Consider, for example, the case where the \textbf{A} locus is linked to the ancestral-SDR ($r<1/2$) and experiences meiotic drive in males only ($\alpha^\male_\Delta \neq 0$, $\alpha^\female_\Delta=0$), without gametic competition ($t^\female=t^\male=0$).
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Sex ratio selection is not a good predictor of neo-W invasion into an XY system
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-\includegraphics[width=\linewidth]{Temporal_SR}
-\caption{
-Fisherian sex ratio selection alone is not a good predictor of turnover between sex-determining systems.
-In this figure, selection is ploidally antagonistic with haploid selection favouring the $a$ allele during male meiosis.
-In panel A, male drive in an ancestral ZW system has no affect on the zygotic sex ratio (see Figure \ref{fig:model_outline}B) yet a neo-Y can invade and replace the ancestral sex-determination system (inset shows neo-Y frequency among male gametes, the ancestral W also goes to fixation during this transition).
-When $R<1/2$, the neo-Y becomes associated with the allele favoured by drive, causing the zygotic sex ratio to become biased, hence the frequency of neo-Y among male gametes can be higher than $0.5$ (inset).
-In panel B, male drive in an ancestral XY system causes a male bias, allowing a neo-W to invade and replace the ancestral sex-determination system (inset shows neo-W frequency among female gametes, the ancestral Y also goes to fixation), which balances the zygotic sex ratio.
-Parameters:  $s^\female =s^\male = 0.2$, $h^\female = h^\male = 0.7$, $t^\female = t^\male = \alpha^\female_\Delta = 0$, $\alpha^\male_\Delta = -0.1$, $r=0.02$.
-}
-\label{fig:SexRatioBad}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 Why can new sex-determining regions invade when more loosely linked to selected loci ($R>r$)?  
@@
 
-%The green curves in Figure \ref{fig:SexRatioBad} show transitions between male and female heterogametey even though the new sex-determining region is unlinked to a locus that experiences haploid and diploid selection.
-%We use these green curves to discuss why trans-GSD transitions can occur when $R=1/2$ and $r<1/2$, as in Table \ref{tab:specialcases}.
-%In Figure \ref{fig:SexRatioBad}B, an unlinked neo-W can spread because the zygotic sex ratio is ancestrally male biased. 
-%In Figure \ref{fig:SexRatioBad}A, an unlinked neo-Y spreads despite the fact that the ancestral zygotic sex ratio is even. 
-%In this case, the male meiotic drive allele, $a$, is initially more common among ancestral-Z-bearing eggs than ancestral-W-bearing eggs because the Z is found in males more often than the W ($\hat{p}_{W}^\female-\hat{p}_{Z}^\female>0$, equation \ref{eq:freq_diffs}).
-%Polymorphism at the \textbf{A} locus is maintained by counter-selection against the $a$ allele in diploids and therefore ancestral-ZZ males have generally low diploid fitness. 
-%The neo-Y spreads because it produces males with high diploid fitness through matings with ancestral-W-bearing female gametes, which are more likely to carry the $A$ allele ($\hat{p}_{W}^\female-\hat{p}_{Z}^\female>0$).
-%A freely recombining neo-Y ($R=1/2$) is equally likely to be segregate with the $A$ or $a$ allele.
-%Therefore, the neo-Y is unaffected by male meiotic drive against the $A$ alleles that it introduces into males. 
-%Thus, a key factor in explaining why trans-GSD transitions can occur when $R>r$ is that the neo-SDR determines sex in the diploid phase but recombination occurs before any subsequent haploid selection.
-
-\subsubsection*{Environmental sex determination}
+\subsection*{Environmental sex determination}
 
@@
 Here, we do not assume that the environmental conditions that determine sex also differentially affect the fitness of males versus females. 
-Such correlations can favour environmental sex-determination systems that allow each sex to be produced in the environment in which it has highest fitness; in the absence of these correlations, previous theory would predict that ESD is favoured when it produces more equal sex ratios than the ancestral system \citep[see reviews by][]{Charnov:1982wg,Bull:1983vi,West:2009we}.
+Such correlations can favour environmental sex-determination systems that allow each sex to be produced in the environment in which it has highest fitness; in the absence of these correlations, previous theory would predict that ESD is favoured when it produces more equal sex ratios than the ancestral system (see reviews by~\cite{Charnov:1982wg,Bull:1983vi,West:2009we}).
 %(e.g., maternal condition, mate quality, age, or host size)
@@
 
-%Under Fisherian sex ratio selection, autosomal modifiers favour equal investment in male and female offspring, i.e., a 1:1 sex ratio \citep{Fisher:1930wy,Charnov:1982wg,West:2009we}. 
+%Under Fisherian sex ratio selection, autosomal modifiers favour equal investment in male and female offspring, i.e., a 1:1 sex ratio~\cite{Fisher:1930wy,Charnov:1982wg,West:2009we}. 
 %A novel environmental sex-determiner that causes half of its carriers to become female and half to become male ($k=1/2$) will be in males half of the time and in females half of the time (like an autosome).
@@
 Significantly, equation \eqref{eq:lambda_ESD} is the same whether ESD is invading an ancestrally XY or ZW system (because $\lambda_{Y',XY} = \lambda_{W',ZW}$ and $\lambda_{W',XY} = \lambda_{Y',ZW}$).
-Thus, Fisherian sex ratio selection alone does not explain the invasion of ESD under weak selection because the sex ratio is only biased by male haploid selection when the ancestral sex-determination system is XY.
-Specifically, with male haploid selection, the neo-ESD is equally likely to invade when it equalizes the zygotic sex ratio (through $\lambda_{W',XY}$) and when it doesn't (through $\lambda_{Y',ZW}$). 
+Thus, Fisherian sex ratio selection alone does not easily explain the invasion of ESD.
+For example, when the ancestral sex-determination system is XY, but not ZW, the sex ratio is biased by male haploid selection.
+Nevertheless, ESD is equally likely to invade when it equalizes the zygotic sex ratio (through $\lambda_{W',XY}$) and when it doesn't (through $\lambda_{Y',ZW}$). 
 %This is again because haploid selection can facilitate the turnover of sex chromosomes either through sex ratio biases or through associations between the new sex determining region with selected alleles.
@@
 
-%Depends 50\% on its fitness relative to non-mutant males and 50\% on its fitness relative to non-mutant females.
-
-%\subsubsection*{Maternally-controlled neo-ESD}
-
-%Fisherian sex ratio selection is sometimes considered in terms of balancing parental investment in male versus female offspring \citep{Charnov:1982wg}.
-%In addition, under environmental sex-determination, the proportion of males/females is sometimes controlled by the mother (e.g., the proportion of eggs laid in warm versus cold environments). 
-%We therefore also considered the invasion of a neo-sex-determining allele ($m$) in a model in which mothers that have at least one $m$ allele produce daughters with probability $k$. 
-%As with offspring-controlled ESD, for all $k\in\{0,1/2,1\}$, we find that invasion into an ancestral XY system is the same as invasion into an ancestrally ZW system (at least up to order $\epsilon^3$, assuming weak selection), implying that transitions between genetic sex-determination and maternally controlled environmental sex-determination are not driven by Fisherian sex ratio selection alone.
-%\textcolor{red}{(Maternal ESD analysis still lacks meiotic drive -- Mathematica can't seem to deal with the added complexity.)}
-
-%One might think that when the sex of zygotes is under the control of mothers, there would be strong selection to balance the sex ratio among zygotes. 
-%However, we find that, with no meiotic drive and weak selection, the invasion fitness of a dominant, maternally controlled sex-determiner that produces proportion $k$ daughters can be written
-%\begin{equation}
-%\lambda_{k} = 1 + V_A S_A C_k + O\left(\epsilon^3\right),
-%\end{equation}
-%where
-%\begin{equation}
-%V_A = \frac{- \left[ t_m + h (s_{f}+s_{m}) \right] \left[ t_m + (1-h) (s_{f}+s_{m}) \right]}{(1-2h)^2(s_{f}+s_{m})^2}
-%\end{equation}
-%is the variance in $A$ ($V_A>0$ when the polymorphic resident equilibrium is stable), 
-%with $h$ the dominance coefficient (equal in both sexes), 
-%$C_k$ is a term that depends on $k$.
-%
-%%k=0
-%\begin{equation}
-%C_0 = big \; ugly \; term
-%\end{equation}
-%
-%%k=1
-%\begin{equation}
-%C_1 = \frac{\left[ (2r(1-R)-R) s^\female + (1-2r)R s^\male \right]}{2}
-%\end{equation}
-%
-%%k=1/2
-%\begin{equation}
-%C_{1/2} = even \; bigger, \; uglier \; term
-%\end{equation}
-%
-%When $k=1$ the maternal- and offspring-controlled results are the same, $C_1 = C_W$, since the mutation remains in females (and hence mutant daughters always have mutant mothers).
-%However, with $k\neq1$ the results with maternal control differ from those with offspring control.
-%Interestingly, for all $k\in\{0,1/2,1\}$, we find that invasion into an ancestrally XY system is the same as invasion into an ancestrally ZW system (at least up to order $\epsilon^3$), implying that sex ratio selection does not drive transitions between genetic sex determination and maternally controlled environmental sex determination.
-%Of particular interest is $k=1/2$ (i.e., when the mother perfectly balances the sex ratio of her offspring).
-%When both recombination rates are small we have $C_{1/2} \approx R(s^\male - s^\female)/8 = \lim_{r \rightarrow 0} C_1/4$.
-%This implies that, at least under tight linkage, the invasion of maternally-controlled ESD is independent of $R$ (because $S_A\propto R^{-1}$) and can invade whenever a neo-$W$ can (which can invade even when it biases the sex ratio further; Figures \ref{fig:WinvasionLowR} -- \ref{fig:WinvasionHighR}).
-
 \section*{Discussion}
@@
 %MAIN RESULT
-Two predominant theories explaining the remarkably high frequency of transitions between sex-determination systems are sexually-antagonistic selection and sex ratio selection \citep[reviewed in][]{Blaser2012, vanDoorn2014re}.
-The former predicts that neo-sex-determining alleles can invade when they arise in closer linkage with a sexually-antagonistic locus \citep{vanDoorn:2007eu,vanDoorn:2010hu, Muralidhar2018}.
+Two predominant theories explaining the remarkably high frequency of transitions between sex-determination systems are sexually-antagonistic selection and sex ratio selection (reviewed in~\cite{Blaser2012, vanDoorn2014re}).
+The former predicts that neo-sex-determining alleles can invade when they arise in closer linkage with a sexually-antagonistic locus~\cite{vanDoorn:2007eu,vanDoorn:2010hu, Muralidhar2018}.
 The latter predicts that new sex-determining systems are generally favoured if they result in more equal sex ratios than the ancestral system. 
-%The latter predicts that neo-W alleles will invade an XY system when there is a male bias caused by haploid selection in males, and vice-versa, a neo-Y will invade a ZW system when there is a female bias caused by haploid selection in females \citep{Kozielska:2010vm,Ubeda:2015fx}.
+%The latter predicts that neo-W alleles will invade an XY system when there is a male bias caused by haploid selection in males, and vice-versa, a neo-Y will invade a ZW system when there is a female bias caused by haploid selection in females~\cite{Kozielska:2010vm,Ubeda:2015fx}.
 In contrast to these prevailing views, we show that selection (including sexually-antagonistic selection, overdominance, and/or ploidally-antagonistic selection) on loci tightly linked to the ancestral sex-determining region can favour trans-GSD transitions (XY to ZW or ZW to XY) to new sex-determining systems that are less closely linked to the selected loci (e.g., see Figure \ref{fig:SexAntagTighter}).
@@
 trans-GSD transitions (XY to ZW or ZW to XY) can occur where the new sex-determining region is less closely linked to the locus under selection if there is haploid selection (e.g., Figures \ref{fig:Combination_Centimorgans} and \ref{fig:SexRatioBad}).
-%\textcolor{red}{need to mention sex ratio here}
-%Neo-W (neo-Y) alleles invade when their fitness in females (males) is greater than the mean fitness of females (males) under the ancestral sex-determination system and/or females (males) are the rarer sex.
-
-%TIGHT LINKAGE RESULTS
-%When the rate of recombination between the ancestral sex-determining locus and a locus under selection is small relative to the strength of selection (i.e., sex-linkage is tight, or selection is strong), heterogametic transitions (XY to ZW or ZW to XY) that reduce sex-linkage are possible, with or without haploid selection (Figures \ref{fig:SexAntagTighter} and \ref{fig:regionplots}).
-
-%The likelihoods of these transitions are driven by sex ratio selection, direct selection on alleles linked to the neo-sex-determining allele, the ability of the neo-sex-determining allele to avoid selection in one sex, and the ability of the neo-sex-determining allele to bring alleles on the sex-specific chromosome in the ancestor into the other sex (given that the neo-sex determining allele is epistatically dominant to its predecessor).
-
-%This possibility that looser sex-linkage could evolve, even in the absence of haploid selection (Figure \ref{fig:regionplot_2a}A), was overlooked in \cite{vanDoorn:2010hu}, likely because they did not explicitly consider the case of initially tight linkage between the \textbf{A} locus and the ancestral-SDR, which allows substantial differences in allele frequencies to build up \citep[$\hat{p}^\Hermaphrodite_{X} \neq \hat{p}_{Y}^\male$, equation \ref{eq:tightequil};][]{Lloyd1977,Otto2014}.
-%Interestingly, there is substantial overlap between the parameter space that allows both neo-W-$A$ and neo-W-$a$ haplotypes to spread in an XY system and that which selects for increased recombination between X and Y chromosomes \citep[e.g., compare gray region of Figure \ref{fig:regionplot_2a}A with coloured regions of Figure 2(a) in][]{Otto2014}.
-%This makes sense, as when both neo-W haplotypes can spread the neo-W can invade despite reducing sex-linkage, i.e., the rate of recombination between the sex-determining allele and the selected locus increases.
-%We further find that it is easier for a neo-W to invade 
-%\textcolor{red}{explain difference too?
-also explain why a neo-Y doesn't invade to reduce linkage despite selection for more recombination?
-mention something about haploid selection (Fig7B)?} \textcolor{blue}{maybe leave for now}
-
-%HAPLOID SELECTION CAN ACT LIKE SEXUALLY-ANTAGONISTIC SELECTION
-%It has previously been demonstrated that new sex-determining systems can evolve if there is genetic variation maintained by sexually-antagonistic selection \citep{vanDoorn:2007eu,vanDoorn:2010hu}. 
-%In particular, 
-%Under weak selection (or loose sex-linkage), transitions to new sex-determining systems can occur when they arise more closely linked to a sexually-antagonistic locus \citep{vanDoorn:2007eu,vanDoorn:2010hu}.
-%New sex-determining alleles are again favoured if they are more closely linked to a locus under haploid selection, which is the only condition favouring homogametic transitions (XY to XY or ZW to ZW).
-%HAPLOID SELECTION ALSO ALLOWS LOOSER LINKAGE TO EVOLVE
-%However, with haploid selection, heterogametic transitions (XY to ZW or ZW to XY) can occur even when the new sex-determining region is less closely linked to the locus under selection. 
-%Neo-W (neo-Y) alleles invade when their fitness in females (males) is greater than the mean fitness of females (males) under the ancestral sex-determination system and/or females (males) are the rarer sex.
-
-%With sexually-antagonistic selection (between diploid sexes) only, linkage between a selected locus and the sex-determining region strengthens associations between male beneficial alleles and the male-determining allele (Y or Z) and between female beneficial alleles and the female-determining allele (X or W).
-%Thus, the mean fitness of both males and females increases with closer linkage to the sex-determining region. 
-%Therefore, new sex-determining alleles only invade if they are more closely linked than the ancestral sex-determining region. 
-%However, if there is haploid selection on loci linked to an XY (ZW) sex-determining region, selection can maintain polymorphisms at which the product of the frequency of females (males) and the mean fitness of females (males) is lower than it would be without sex-linkage.
-%In these cases, unlinked neo-W (neo-Y) alleles can increase the frequency and/or fitness of the only sex they are found in, at a cost to the other sex, and invade despite lowering population mean fitness (Figure \ref{fig:Combination_MeanFit}).
-%\textcolor{red}{This is similar to mitochondria and male disease ...?}
-
-%%SEX-RATIO SELECTION
-%\textcolor{blue}{maybe drop paragraph?}
-%\textcolor{red}{I messed with the sex ratio selection paragraphs to tone down our "it doesn't matter" speech from before. Have at any amendments you'd like to make.}
-%Linkage between haploid selected loci and sex-determining regions cases biased zygotic sex ratios \citep{Hamilton:1967ts,Burt:2006,Field:2012fd,Field:2013cc}.
-%One might then expect Fisherian sex ratio selection to drive the spread of new sex-determining systems that bring the sex ratio closer to 50:50. 
-%Fisherian sex ratio selection follows from the fact that, for an autosomal locus, half of the genetic material is inherited from a male, and half from a female \citep{Fisher:1930wy,West:2009we}. 
-%Thus, if the population sex ratio is biased towards females, the average per-individual contribution of genetic material to the next generation from males is greater than the contribution from females (and vice versa for male-biased sex ratios).
-%Therefore, a mutant that increases investment in males will spread via the higher per-individual contributions made by males. 
-%%%That is, under Fisherian sex ratio selection, the success of a mutant relative to the non-mutant depends, in equal parts, on the contributions made by males and females to the next generation. 
-%An implicit assumption of Fisherian sex ratio selection is that the mutant allele is autosomal and has the same inheritance pattern as the non-mutant allele. 
-%The mutations we consider here, neo-sex-determining alleles, break this assumption. 
-%For example, the success of neo-Y/neo-W mutations depends only on the number of alleles contributed by males/females (Table \ref{tab:haplotype_growth}). 
-%In this respect, a neo-W is similar to a cytoplasmic element, which also does not experience selection to balance sex ratios \citep{Frank:1989vl,Werren:1998co,Chase:2007bf}.
-%Even mutants that are equally likely to be found in males or females, such as an environmental sex determination mutation (equation \ref{eq:lambda_ESD}), are not strictly autosomal if they determine sex.
-%Thus, despite the fact that sex ratio biases caused by gametic competition or meiotic drive have been shown to exert Fisherian sex ratio selection on various autosomal modifiers \citep{Stalker:1961th,Smith:1975ft,Frank:1989vl,Hough:2013uo,Ubeda:2015fx, Otto:2015va}, we do not find evidence of Fisherian sex ratio selection acting during invasion by neo-sex-determination systems (e.g., see Figure \ref{fig:Combination_Turnover} and \citealt{Ubeda:2015fx}, in which a neo-Y invades despite biasing sex ratios).
-
-%Sex ratio biases caused by gametic competition or meiotic drive have been shown to exert Fisherian sex ratio selection on various autosomal \citep{Stalker:1961th,Smith:1975ft,Frank:1989vl,Hough:2013uo,Ubeda:2015fx, Otto:2015va} and sex-linked \citep{Kozielska:2010vm} modifiers.
+
 We find that the spread of neo-sex-determining systems cannot be simply predicted from their effect on the sex ratio. 
@@
 For instance, alleles favoured by haploid selection in males often become associated with the Y, which leads to a male-biased zygotic sex ratio.
-This male bias increases the potential for a neo-W to invade (Table \ref{tab:haplotype_growth}), which can equalize the sex ratio \citep[e.g., see Figure \ref{fig:SexRatioBad}B, for related examples see][]{Kozielska:2010vm}.
+This male bias increases the potential for a neo-W to invade (Table \ref{tab:haplotype_growth}), which can equalize the sex ratio (e.g., see Figure \ref{fig:SexRatioBad}B, for related examples see~\cite{Kozielska:2010vm}).
 %We find that sex ratio biases caused by haploid selection can also affect transitions between sex-determining systems (e.g., see $\zeta$ terms in Table \ref{tab:haplotype_growth}). 
@@
 %and equalizing the sex ratio.
-Indeed, transitions between sex-determining systems can generate stronger sex ratio biases \citep[e.g., Figure \ref{fig:SexRatioBad}A and step 1 in][]{Ubeda:2015fx}.
+Indeed, transitions between sex-determining systems can generate stronger sex ratio biases (e.g., Figure \ref{fig:SexRatioBad}A and step 1 in~\cite{Ubeda:2015fx}).
 %For example, where a neo-Y invades and is linked with a locus that experiences haploid selection in male gametes, the sex ratio evolves to become biased \citep[e.g., see Figure \ref{fig:SexRatioBad}A and step 1 in][]{Ubeda:2015fx}.
@@
 Thus, haploid selection can favour trans-GSD transitions both via sex ratio selection and via selection on alleles associated with the neo-sex-determining allele, and these selective pressures are often predicted to be of equal magnitude.
-%\textcolor{red}{Maybe try to emphasise surprisingness in the paragraph more? e.g., how wrong you'd be if you assumed selection to equalise sex ratios, or it this implied?}
-%\textcolor{blue}{nice, pretty subtle argument but I think that's a good job.}
-
-%Previous studies where ESD is favoured have typically assumed that environmental conditions (e.g., maternal condition, mate quality, age, or host size) can differentially affect the fitness of males versus females such that ESD invades because it allows sex determination to depend on the environment \citep[reviewed in][]{Charnov:1982wg,Bull:1983vi,West:2009we}.
-
-%WHY SEX-RATIO BIASES CAN BE FAVOURED
-%We note two other ways in which sex determination has been shown to relate to zygotic sex ratios.
-%Firstly, female-biased sex ratios can be favoured when there is local mate competition, where all matings are between siblings and assuming one male can inseminate many females \citep{Hamilton:1967ts}.
-%Therefore, with local mate competition, feminizing mutations can spread because they bias the sex ratio towards females \citep{Wilson:1981vm,Vuillleumier:2007bh}. 
-%Secondly, environmental conditions (e.g., maternal condition, mate quality, age, or host size) can differentially affect the fitness of males versus females such that the optimal allocation to males/females depends on the environment \citep{Trivers:1973wb,Charnov:1977tx,Charnov:1982wg}.
-%In such cases, flexible sex-determination systems may evolve in order to allow the zygotic sex ratio to be determined in a way that depends on the environment \citep{Charnov:1977tx,Werren:1984tl,Pen:2010kk}.
-%In this study, we do not consider environmental condition dependence or local mate competition \citep[reviewed in][]{Charnov:1982wg,Bull:1983vi,West:2009we}.
-
-%HOW TO TEST EMPIRICALLY
-%\textcolor{blue}{I think Sally was sceptical of this idea. i.e., if the second term in \ref{eq:lambda_neoW} is negative, then get less transitions with haploid selection included, right? }
-%\textcolor{red}{Yeah, and given that only 1/2 the discovered plant sex chromosomes are hetermorphic and there are so few plant sex chromosomes to begin with (Charlesworth 2016 Annual Review Plant Biology), might it be the case that haploid selection is constraining things?
-perhaps we could think of some particular forms of haploid selection that might be common and give their predicted effects, or just say some things that are possible with haploid selection that are not without it -- if there are any.
-just looking at eq 3 though, its gonna be hard to get a low freq of A on the Y if haploid selection in males favours A, i.e., it should often be positive when there is no female haploid selection, right?}
-%\textcolor{blue}{That sounds right to me and is backed up by equation \eqref{eq:freq_diffs}.
-It may be technically possible for that term to be negative though.
-Re: hetermorphism, I see that as a slightly different issue.
-It's thought that haploid selection may prevent deletions from becoming fixed on the Y, like in the Crowson (2017) paper.
-%I think the issue of `why so few plant sex chromosomes' is partly an issue of detection and also `why so much hermaphroditism'.
-Is it possible that the ESD results could show selective forces that also favour transitions from dioecy to hermaphroditism?
-I think so.
-Our ESD mutant produces 1/2 females and 1/2 males whereas a hermaphrodite invests roughly equally in each type of gamete produced.
-We don't consider the forces that are usually thought to be involved in these transitions though (inbreeding depression, reproductive assurance and possibly others?).
-}
-%Taken at face value, our results indicate that transitions in heterogametey (XY to ZW or vice versa) are more likely to be favoured by selection if there is selection upon both haploid and diploid genotypes rather than diploid selection alone ().
-%This prediction could be examined using a suitable proxy for haploid selection, for example, \cite{Lenormand:2005vb} use the outcrossing rate in plants as a proxy for the strength of pollen competition.
-%In animals, one might expect gametic competition to be stronger in species where sperm is required to live for a long time after spermatogenesis because transcripts shared during spermatogenesis may become depleted, revealing the haploid phenotype of the sperm \citep{Immler:2014im}.
-%Given the caveats mentioned above about the form of meiotic drive modelled, we would also expect that heterogametic transitions in sex determination would be more common in clades where there is meiotic drive.
-
-%Together, our models demonstrate novel selective forces that favour heterogametic transitions (XY to ZW or ZW to XY). 
-%One common prediction is therefore that heterogametic transitions are favoured under a wider range of conditions than homogametic transitions. 
-%However, heterogametic transitions are not clearly in excess.
-For example, \citet{Vicoso:2015hf} found a dozen sex chromosome configurations among Dipteran species but only one transition between male and female heterogametey.
-%While our models examine the selective forces that favour the spread of new sex-determining regions, observed transitions could also reflect the mutation rate for neo-Y versus neo-W alleles (e.g., duplications of the ancestral sex determining region could be particularly likely).
-%In addition, heterogametic transitions could be limited due to the production of YY males or WW females (see below). 
-%Alternatively, it might be useful to compare clades that are expected to differ in the strength of haploid selection (e.g., plants are thought to experience more selection during their multicellular haploid stage
 
@@
 If haploid selection is strong but selective differences between male and female diploids are weak, we find that trans-GSD transitions (XY to ZW or ZW to XY) are favoured more strongly than cis-GSD transitions, with transitions to ESD intermediate (e.g., with $|D^\male - D^\female| << |\alpha_\Delta^\male - \alpha_\Delta^\female + t^\male - t^\female|$ we have $\lambda_{W',XY} > \lambda_{Y',XY}$; Equations \ref{eq:lambda_neoW} and \ref{eq:freq_diffs}).
-Among the relatively few dioecious clades in which multiple species have well characterized sex chromosomes \citep{Ming:2011iy}, trans-GSD transitions have been inferred in \textit{Silene} subsection \textit{Otites} \citep{Slancarova:2013dq} and in \textit{Salicaceae} \citep{Pucholt2015,Pucholt2017}.
+Among the relatively few dioecious clades in which multiple species have well characterized sex chromosomes~\cite{Ming:2011iy}, trans-GSD transitions have been inferred in \textit{Silene} subsection \textit{Otites}~\cite{Slancarova:2013dq} and in \textit{Salicaceae}~\cite{Pucholt2015,Pucholt2017}.
 %Potentially, successive heterogametic transitions between master regulators of sex-determination could be inferred from careful examination of the molecular pathways by which sex is determined. 
 %Our predictions could also be examined using a suitable proxy for haploid selection, for example, \cite{Lenormand:2005vb} use the outcrossing rate in plants as a proxy for the strength of pollen competition.
-Assuming that transitions from dioecy to hermaphroditism (equal parental investment in male and female gametes) are favoured in a similar manner to the ESD examined here (equal probability of zygotes developing as males or females), our results suggest that competition during the haploid stage could also drive transitions between dioecy and hermaphroditism, which are frequent in plants \citep{Kafer2017, Goldberg2017}.
-%In animals, one might expect gametic competition to be stronger in species where sperm is required to live for a long time after spermatogenesis because transcripts shared during spermatogenesis may become depleted, revealing the haploid phenotype of the sperm \citep{Immler:2014im}.
-%We would also expect that heterogametic transitions in sex determination would be more common in clades where there is meiotic drive.
-
-%IDENTIFICATION OF LOCI IN GENOMIC LOCATIONS THAT IMPLICATE THEM IN SEX-CHROMOSOME TURNOVER
-%The hypotheses presented here can be empirically investigated in a similar manner to the idea that transitions between sex-determining systems are favoured by linkage to sexually-antagonistic variation.
-%In the case of sexually-antagonistic variation, one supporting observation is that genes expected to be under sexually-antagonistic selection (e.g., those causing bright male colouration) have been found on recently derived sex chromosomes \citep{Lindholm:2002dw,Tripathi:2009cw,Ser:2010iq}.
-In support of their role in sex chromosome turnover, genes expected to be under sexually-antagonistic selection (e.g., those causing bright male colouration) have been found on recently derived sex chromosomes \citep{Lindholm:2002dw,Tripathi:2009cw,Ser:2010iq}.
+Assuming that transitions from dioecy to hermaphroditism (equal parental investment in male and female gametes) are favoured in a similar manner to the ESD examined here (equal probability of zygotes developing as males or females), our results suggest that competition during the haploid stage could also drive transitions between dioecy and hermaphroditism, which are frequent in plants~\cite{Kafer2017, Goldberg2017}.
+
+In support of their role in sex chromosome turnover, genes expected to be under sexually-antagonistic selection (e.g., those causing bright male colouration) have been found on recently derived sex chromosomes~\cite{Lindholm:2002dw,Tripathi:2009cw,Ser:2010iq}.
 Our results show, however, that tight ancestral-linkage of polymorphic loci can also drive trans-GSD transitions. 
-In addition, we find that polymorphic sex determining systems (X, Y, W, and Z alleles all present) can be maintained when a selected locus is tightly linked to the ancestral sex-determining system (e.g., Figures \ref{fig:freqAll}B and \ref{fig:freqAll}C), which is not possible with loose linkage \citep{vanDoorn:2010hu}.
+In addition, we find that polymorphic sex determining systems (X, Y, W, and Z alleles all present) can be maintained when a selected locus is tightly linked to the ancestral sex-determining system (e.g., Figures \nameref{fig:freqAll}B and \nameref{fig:freqAll}C), which is not possible with loose linkage~\cite{vanDoorn:2010hu}.
 %As noted by \citet{vanDoorn:2010hu}, it would be prudent to compare closely related clades in order to determine whether observed polymorphisms predate a transition in sex-determination or arose afterwards.
-%, particularly because sex-linkage allows sexually-antagonistic selection to maintain polymorphisms under a different and larger parameter space \citep{Rice:1987hs,Jordan:2011fj}.
-For example, our results suggest a potential mechanism maintaining multiple sex determining alleles in the platyfish (\textit{Xiphophorus maculatus}), in which X,Y, and W alleles segregate at one locus (or two closely-linked loci) near to potentially sexually-antagonistic genes for pigmentation and sexual maturity \citep{Kallman1965,Kallman1968, Volff2001, Schultheis2006}.
-Several rodent species also maintain feminizing alleles along with the ancestral X and Y sex-determination alleles \citep[reviewed in][]{Fredga1994}. 
-For example, in nine \textit{Akadon} species, it appears that male-determining-\textit{sry} expression is suppressed by an autosomal feminizing allele, creating XY females \citep{Bianchi2002,Sanchez2010}, which have increased fitness relative to XX females \citep{Hoekstra2001}.
-In \textit{Mus microtoides}, females can have XX, XX$^\ast$ or X$^\ast$Y genotypes \citep{Veyrunes2010}. 
+%, particularly because sex-linkage allows sexually-antagonistic selection to maintain polymorphisms under a different and larger parameter space~\cite{Rice:1987hs,Jordan:2011fj}.
+For example, our results suggest a potential mechanism maintaining multiple sex determining alleles in the platyfish (\textit{Xiphophorus maculatus}), in which X,Y, and W alleles segregate at one locus (or two closely-linked loci) near to potentially sexually-antagonistic genes for pigmentation and sexual maturity~\cite{Kallman1965,Kallman1968, Volff2001, Schultheis2006}.
+Several rodent species also maintain feminizing alleles along with the ancestral X and Y sex-determination alleles (reviewed in~\cite{Fredga1994}). 
+For example, in nine \textit{Akadon} species, it appears that male-determining-\textit{sry} expression is suppressed by an autosomal feminizing allele, creating XY females~\cite{Bianchi2002,Sanchez2010}, which have increased fitness relative to XX females~\cite{Hoekstra2001}.
+In \textit{Mus microtoides}, females can have XX, XX$^\ast$ or X$^\ast$Y genotypes~\cite{Veyrunes2010}. 
 Previous theory would predict that the X$^\ast$ chromosome (or the autosome it is fused to) harbours female beneficial alleles, driving its spread. 
-However, XX and XX$^\ast$ females have similar fitness, whereas X$^\ast$Y female fitness is enhanced \citep{Saunders2014,Saunders2016, Veyrunes2017}.
+However, XX and XX$^\ast$ females have similar fitness, whereas X$^\ast$Y female fitness is enhanced~\cite{Saunders2014,Saunders2016, Veyrunes2017}.
 Although Y-linkage of female-beneficial alleles is counterintuitive, our tight linkage model suggests that it can be stably maintained and then favour new feminizing mutations, which is a parsimonious explanation for the spread of feminizing alleles in these rodent species.
@@
 We note that we assume that sex-determining alleles do not experience direct selection except via their associations with sex and selected alleles.
-However, in some cases, there may be significant degeneration around the sex-limited allele (Y or W) in the ancestral sex-determining region because recessive deleterious mutations and/or deletions accumulate around the Y or W sex-determining regions \citep{Rice:1996ke,Charlesworth:2000cc,Bachtrog:2006ed,Marais:2008hm}.
-During trans-GSD transitions (XY to ZW or ZW to XY), but not cis-GSD transitions (XY to XY or ZW to ZW), any recessive deleterious alleles linked to the Y or W are revealed to selection in YY or WW individuals \citep{Bachtrog:2014bx}.
-This phenomenon was studied by \citet{vanDoorn:2010hu}, who found that degeneration can prevent fixation of a neo-W or a neo-Y allele, leading to a mixed sex-determination system where the ancestral and new sex-determining loci are both segregating.
+However, in some cases, there may be significant degeneration around the sex-limited allele (Y or W) in the ancestral sex-determining region because recessive deleterious mutations and/or deletions accumulate around the Y or W sex-determining regions~\cite{Rice:1996ke,Charlesworth:2000cc,Bachtrog:2006ed,Marais:2008hm}.
+During trans-GSD transitions (XY to ZW or ZW to XY), but not cis-GSD transitions (XY to XY or ZW to ZW), any recessive deleterious alleles linked to the Y or W are revealed to selection in YY or WW individuals~\cite{Bachtrog:2014bx}.
+This phenomenon was studied by van Doorn and Kirkpatrick (2010)~\cite{vanDoorn:2010hu}, who found that degeneration can prevent fixation of a neo-W or a neo-Y allele, leading to a mixed sex-determination system where the ancestral and new sex-determining loci are both segregating.
 However, they noted that very rare recombination events around the ancestral sex-determining region can allow these trans-GSD transitions to complete.  
@@
 Degeneration around the Y or W could explain why trans-GSD transitions are not observed to be much more common than cis-GSD transitions despite the fact that our models demonstrate that they are favoured under a wider range of conditions, especially with haploid selection.
-For example, \citet{Vicoso:2015hf} found a dozen sex chromosome configurations among Dipteran species but only one transition between male and female heterogamety.
+For example,~\cite{Vicoso:2015hf} found a dozen sex chromosome configurations among Dipteran species but only one transition between male and female heterogamety.
 
@@
 However, we expect similar selective forces to act on masculinizing/feminizing alleles of weaker effect. 
-For example, \citet{Muralidhar2018} consider small effect masculinizing/feminizing alleles within a threshold model of sex determination, finding that they can be favoured when linked to loci that experience sexually-antagonistic selection.
-These results echo those for large-effect neo-Y/neo-W alleles \citep{vanDoorn:2007eu,vanDoorn:2010hu}.
+For example,~\cite{Muralidhar2018} consider small effect masculinizing/feminizing alleles within a threshold model of sex determination, finding that they can be favoured when linked to loci that experience sexually-antagonistic selection.
+These results echo those for large-effect neo-Y/neo-W alleles~\cite{vanDoorn:2007eu,vanDoorn:2010hu}.
 Finally, while we have considered cis-GSD, trans-GSD, and GSD to ESD transitions, we have not explicitly considered ESD to GSD transitions. 
-Recent models of ESD to GSD transitions \citep{Ubeda:2015fx,Muralidhar2018} show that that neo-Y/neo-W alleles can be favoured when they arise near to haploid and/or diploid selected loci, which also occurs in our model.
+Recent models of ESD to GSD transitions~\cite{Ubeda:2015fx,Muralidhar2018} show that that neo-Y/neo-W alleles can be favoured when they arise near to haploid and/or diploid selected loci, which also occurs in our model.
 
@@
 %However, many meiotic drive systems involve an interaction with another locus at which alleles may `suppress' the action of meiotic drive \citep[][]{Burt:2006,Lindholm:2016cw}.
-%Thus, the dynamics of meiotic drive alleles can be heavily dependent on the interaction between two loci and the recombination rate between them, which in turn can be affected by sex-linkage if there is reduced recombination between sex chromosomes \citep{Hurst:1991uh}.
-%Furthermore, in some cases, a driving allele may act by killing any gametes that carry a `target' allele at another locus, in which case there can be fertility effects that alter the equilibrium frequency of a meiotic drive allele \citep{Holman:2015en}.
-%In polygamous mating systems, the intensity of pollen/sperm competition can depend on the density of males available to donate pollen/sperm, which can itself depend on the sex ratio \citep{Taylor:2002wu}.
+%Thus, the dynamics of meiotic drive alleles can be heavily dependent on the interaction between two loci and the recombination rate between them, which in turn can be affected by sex-linkage if there is reduced recombination between sex chromosomes~\cite{Hurst:1991uh}.
+%Furthermore, in some cases, a driving allele may act by killing any gametes that carry a `target' allele at another locus, in which case there can be fertility effects that alter the equilibrium frequency of a meiotic drive allele~\cite{Holman:2015en}.
+%In polygamous mating systems, the intensity of pollen/sperm competition can depend on the density of males available to donate pollen/sperm, which can itself depend on the sex ratio~\cite{Taylor:2002wu}.
 %In terms of our model, this implies that the strength of gametic competition ($t^\male$) may both determine and be determined by the sex ratio. 
@@
 
-%\textcolor{blue}{similarly, this part doesn't discuss our new tight linkage results or our new perspective on sex ratios.}
-%CONCLUSION
+\section*{Conclusion}
+
 We have shown that tight sex-linkage and haploid selection can drive previously unexpected transitions between sex-determination systems.
-In particular, both can select for neo-sex-determining loci that are more loosely linked. 
+In particular, both can select for neo-sex-determining loci that are more loosely linked to loci under selection. 
 In addition, haploid selection can cause transitions analogous to those caused by purely sexually-antagonistic selection, eliminating the need for differences in selection between male and female diploids.
 We conclude that haploid selection should be considered as a pivotal factor driving transitions between sex-determination systems. 
-Perhaps counterintuitively, transitions involving haploid selection can be driven by sex ratio selection or cause sex ratio biases to evolve and Fisherian sex ratio selection is not an overwhelming force.
+Perhaps counterintuitively, transitions involving haploid selection can be driven by sex ratio selection or cause sex ratio biases to evolve; we do not find Fisherian sex ratio selection to be an overwhelming force.
 Overall, our results suggest several new scenarios under which new sex-determination systems are favoured, which could help to explain why the evolution of sex-determination systems is so dynamic.
-%Further, we have shown the way in which transitions are affected by haploid selection is not intuitively obvious. 
-%Firstly, sex-specific haploid selection affects turnovers between sex-determination systems in a manner that is qualitatively different from diploid sex-specific selection. 
-%In particular, closer linkage between a sex-determining locus and a selected locus is not always favoured during heterogametic transitions when there is haploid selection. 
-%Secondly, even though haploid selection is a source of zygotic sex ratio biases, in our models Fisherian sex ratio selection does not have good explanatory power in determining whether various sex-determination systems evolve.
-%This result is surprising given that sex ratios are ultimately determined via the sex-determination system, and leads us to the conclusion that three selective forces -- haploid, diploid, and sex ratio selection -- should all be considered when exploring transitions between sex-determination systems.
-
-\bibliographystyle{amnatnat.bst}
-\bibliography{sex_chromosomes.bib}
-
-\newpage
-%\section*{Figures}
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Tighter linkage allows looser sex-linkage to evolve, even in absence of haploid selection
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\includegraphics[width=\linewidth]{PositionPlot_SexAntagTighter}
-%\caption{
-%In the absence of haploid selection, tight linkage allows looser sex-linkage to evolve in transitions between XY and ZW systems.
-%In panel A, linkage is loose enough relative to selection that the weak selection analytical results hold, and a neo-W can only invade when it is more tightly linked with the selected locus ($R<r$; shaded region).
-%In panel B, linkage is tight enough relative to selection that the weak selection analytical results do no hold, and a neo-W can only invade even when it is less tightly linked with the selected locus ($r<R$; unshaded region).
-%Parameters: $w_{AA}^\female = w_{aa}^\male = 1.05$, $w_{aa}^\female = w_{AA}^\male = 0.85$, $w_{Aa}^\female = 1$, $w_{Aa}^\male = 0.925$, $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
-%}
-%\label{fig:SexAntagTighter}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Both neo-W haplotypes can spread, in the absence of haploid selection, when there is overdominance
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\includegraphics[width=0.45\linewidth]{regionplot_2a}
-%\includegraphics[width=0.45\linewidth]{regionplot_2a_Color_Ya_Either}
-%\includegraphics[width=0.45\linewidth]{BothWsInvade_Overdominance}
-%\caption{
-%In the absence of haploid selection, both neo-W haplotypes can spread in an XY system when there is overdominance.
-%Panel A shows the range of male homozygote fitnesses that allow either neo-W haplotypes to invade.
-%The blue region overlaps with a red region, where both neo-W haplotypes can invade a population with $A$ fixed on the X and $a$ fixed on the Y.
-%The green region (overlapped by the orange region) is where both neo-W haplotypes can invade a population with $a$ fixed on the Y and a polymorphic X.
-%The orange region (outside the green region) is where only the neo-W-$A$ haplotype can invade
-%Panel B shows the temporal dynamics of the invading neo-W haplotypes; in this case the neo-W does not fix, leading to a polymorphic sex-determining system.
-%Asterisk in panel A marks parameter values ($w_{aa}^\male=0.15$, $w_{AA}^\male=0.1$) used in panel B.
-%Parameters: $w_{AA}^\female = w_{aa}^\female = 0.6$, $w_{Aa}^\Hermaphrodite = 1$, $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$, $r=R=0$.
-%\textcolor{red}{make two more temporal plots with visible asterisks in green and orange regions; figure out better colours to show possibilities}
-%}
-%\label{fig:BothOverdominance}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%With weak selection, a less tightly linked neo-W can invade an XY system when there is some haploid selection, and this invasion decreases mean diploid fitness
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\includegraphics[width=0.5\linewidth]{Loose_Fitness_Decline}
-%\caption{
-%With weak selection, a less tightly linked neo-W can invade (and fix in) an XY system (causing the Y to fix in females) when there is some haploid selection (blue and green curves in panel A), and this invasion decreases mean diploid fitness (green and blue curves in panel B).
-%Parameters: $s^\Hermaphrodite = 0.2$, $h^\Hermaphrodite = 0.7$, $t^\Hermaphrodite = \alpha^\male_\Delta = 0$, $\alpha^\female_\Delta = -0.1$, $r=1/10$.
-%}
-%\label{fig:LooseDecline}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%A neo-W can invade an XY system under a large number of selective regimes
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\includegraphics[width=0.5\linewidth]{PositionPlot_4}
-%\caption{
-% A neo-W can invade an XY system under a large number of selective regimes.
-%In panel A, there is no haploid selection ($t^\Hermaphrodite = \alpha^\Hermaphrodite_{\Delta} = 0$) and selection in diploids is sexually antagonistic ($s^\male = -s^\female = 1/10$, $h^\male = 1-h^\female = 3/10$), in which case the neo-sex-determining allele can only invade if it is more closely linked to the selected locus ($R<r$, gray region; but see Figure \ref{fig:SexAntagTighter}B for the case of very tight linkage).
-%In panel B, male drive ($\alpha^\male_{\Delta} = -1/20$, $t^\Hermaphrodite = \alpha^\female_{\Delta} = 0$) opposes selection in diploids (no sex-differences: $s^\Hermaphrodite = 1/10$, $h^\Hermaphrodite = 7/10$), in which case the neo-sex-determining allele can invade regardless of linkage.
-%In panel C, haploid competition in males ($t^\male = -1/10$, $t^\female = \alpha^\Hermaphrodite_{\Delta} = 0$) opposes selection in diploids (sex-differences: $s^\male = 3 s^\female = 3/20$, $h^\Hermaphrodite = 7/10$), in which case the neo-sex-determining allele can once again invade regardless of linkage.
-%We use Haldane's map function \citep[Equation 3 in ][]{Haldane1919} to convert from map distance (centiMorgans, cM) to the probability of recombination (an odd number of cross-over events).   
-%}
-%\label{fig:Combination_Centimorgans}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Sex ratio selection is not a good predictor of neo-W invasion into an XY system
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\includegraphics[width=\linewidth]{Combination_Turnover_Ratio}
-%\caption{
-%Sex ratio selection alone is not a good predictor of turnover between sex-determining systems.
-%In panels A and C, male drive in an ancestral XY system causes a male bias, allowing a neo-W to invade and fix (causing the Y to fix in females), which balances the sex ratio (it also avoids selection in males, and thus makes better females in this case of sex-specific ploidally-antagonistic selection).
-%In panels B and D, male drive in an ancestral ZW system has no affect on the sex ratio, yet a neo-Y can invade and fix (causing the W to fix in males) because it becomes linked with the driving allele, and this imparts a sex ratio bias.
-%Parameters:  $s^\female =s^\male = 0.2$, $h^\female = h^\male = 0.7$, $t^\female = t^\male = \alpha^\male_\Delta = 0$, $\alpha^\female_\Delta = -1/10$, $r=1/20$.
-%}
-%\label{fig:SexRatioBad}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Haploid selection can lead to polymorphic SD systems 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\includegraphics[width=\linewidth]{Polymorphic}
-%\caption{
-%Tight linkage (relative to selection) and/or haploid selection can cause stable polymorphic sex-determining systems.
-%In panel A, there is strong overdominance in both sexes and no haploid selection  (parameters as in Figure \ref{fig:BothOverdominance}B with $r = 1/10$), in which case a neo-W can invade regardless of sex-linkage, but cannot not fix (i.e., the Y does not fix in females, and X, Y, W, and Z all segregate at equilibrium).
-%In panel B, there is sex-antagonistic selection at the diploid stage and drive in females (parameters as in Figure \ref{fig:SexAntagTighter} with $\alpha^\female_\Delta = 1/20$ and $r = 1/10$), in which case a sufficiently tightly linked neo-W can invade ($R<\sim r$), but only fixes if $R=0$.
-%}
-%\label{fig:Polymorphism}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%CYCLES!
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\includegraphics[width=0.5\linewidth]{BothWsInvade_Overdominance_Cycles}
-%\caption{
-%Thought I'd show this just for fun (not for publication).
-%}
-%\label{fig:Cycles}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Heterogametic transitions with/without sex ratio change
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\begin{tikzpicture}[remember picture]
-%	\node[] (plot) {\includegraphics[width=\linewidth]{Combination_Turnover}};
-%	\node[above = 0cm of plot, xshift = -70] () {$r=0.5$, $R=0.05$};
-%	\node[above = 0cm of plot, xshift = 120] () {$r=0.05$, $R=0.5$};
-%	\node[left = 0cm of plot, yshift = 105, rotate = 90] () {XY $\rightarrow$ ZW};
-%	\node[left = 0cm of plot, yshift = -20, rotate = 90] () {ZW $\rightarrow$ XY};
-%\end{tikzpicture}
-%\caption{
-%Heterogametic transitions from XY to ZW sex determination (neo-W frequency shown by black lines, panels A and B) or from ZW to XY (neo-Y frequency shown by black lines, panels C and D) occur similarly regardless of sex ratio biases present before (B versus D) or after (C versus A, dashed lines show male frequency).
-%During invasion by a neo-ZW sex-determination system (A and B), the ancestral Y fixes in both males and females (blue and red lines). 
-%Similarly, the ancestral W allele fixes in males and females (blue and red lines) during a ZW to XY transition. 
-%In this plot, there is no gametic competition ($t^\female=t^\male=0$) and meiotic drive occurs during male meiosis only ($\alpha^\female_{\Delta}=0$, $\alpha^\male_{\Delta}=-1/5$).
-Therefore, sex ratio biases can only arise when the \textbf{A} locus is linked to an XY sex-determining locus.
-%In panels A and C, the neo-sex-determining locus is more closely linked to the \textbf{A} locus than the ancestral sex-detemining region ($r=1/2$, $R=1/20$) such that a neo-Y can caused biased sex ratios (panel C).
-%In panels B and D, the ancestral sex-determining locus is more closely linked to the \textbf{A} locus than the neo-sex-detemining locus ($r=1/20$, $R=1/2$). 
-%Therefore, an ancestral XY sex determination can have a biased zygotic sex ratio that becomes unbiased after an unlinked neo-W invades (B). 
-%However, in panel D, a unlinked neo-Y invades an ancestral ZW sex-determination system in a similar manner but no biases to the zygotic sex ratio occur. 
-%With diploid selection alone, neo-sex-determining loci do not spread if they are less closely linked to the \textbf{A} locus than the ancestral sex-determining locus (see equation \eqref{eq:lambda_neoW} and Figure \ref{fig:Combination_Centimorgans}A).
-%In this plot there are no sex differences in selection and an equilibrium is maintained because selection in diploids opposes meiotic drive, $s^\female =s^\male = 1/5$, $h^\female = h^\male = 7/10$.
-%\textcolor{red}{Aesthetic adjustments: 
-%%Could add titles to the columns/rows: neo-W for row 1, neo-Y for row 3, $r=0.5$, $R=0.05$ for column 1 and $r=0.05$, $R=0.5$ for column 2. 
-%%Could adjust padding (too much whitespace where there is no axis label). 
-%%It also seems could increase ratio of font size relative to plot size to make figure more compact. 
-%%Matt - could you uncomment the line legends in the Mathematica file (function not included in my Mathematica version).
-%Add chromosome cartoons to depict recombination rates?
-%}
-%}
-%\label{fig:Combination_Turnover}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Heterogametic transitions with/without sex ratio change
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\begin{tikzpicture}[remember picture]
-%	\node[] (plot) {\includegraphics[width=\linewidth]{Combination_Turnover_Ratio}};
-%	\node[above = -1cm of plot, xshift = -100] () {XY $\rightarrow$ ZW};
-%	\node[above = -1cm of plot, xshift = 90] () {ZW $\rightarrow$ XY};
-%\end{tikzpicture}
-%\caption{
-%%\textcolor{red}{Is this what Sally was thinking?}
-%%\textcolor{blue}{I think this works but I'm confused as to why the speed of spread should be so much different for XY and ZW here.
-Figure \ref{fig:Combination_Turnover} and \ref{fig:Combination_Centimorgans} suggests that there's not much difference between XY->ZW and ZW->XY.
-Maybe we should just stick with the 4 cases in figure \ref{fig:Combination_Turnover}.
-}
-%%\textcolor{red}{i messed up and had $r=0.5$ instead of $r=0.05$ for B and D. haven't fixed fitness plot below.}
-%Heterogametic transitions occur (panels A and B) regardless of sex ratio biases (panels C and D).
-%A neo-W invades (panel A) and equalizes the male-biased sex ratio (panel C) that was caused by meiotic drive in males.
-%A neo-Y invades (panel B) a population with an equal sex ratio. 
-%With any amount of linkage ($R<1/2$), the neo-Y becomes associated with the driving allele in males, and in the end causes a male bias.
-%Parameters: $s^\female = s^\male = 1/5$, $h^\female = h^\male = 7/10$, $t^\female = t^\male=0$, $\alpha^\female_\Delta = 0$, $\alpha^\male_\Delta = -1/5$, $r = 1/20$.
-%}
-%\label{fig:Combination_Turnover_Ratio}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%Changes in mean fitness
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\begin{tikzpicture}[remember picture]
-%	\node[] (plot) {\includegraphics[width=\linewidth]{Combination_Fitness_Rec}};
-%	\node[above = -1cm of plot, xshift = -100] () {XY $\rightarrow$ ZW};
-%	\node[above = -1cm of plot, xshift = 90] () {ZW $\rightarrow$ XY};
-%\end{tikzpicture}
-%\caption{
-%\textcolor{red}{This complicated thing matches the plot above. I don't think we want to include it...?}
-%}
-%\label{fig:Combination_Fitness_Rec}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Changes in mean fitness
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\begin{tikzpicture}[remember picture]
-%	\node[] (plot) {\includegraphics[width=\linewidth]{Combination_MeanFit}};
-%	\node[above = 0cm of plot, xshift = -70] () {$r=0.5$, $R=0.05$};
-%	\node[above = 0cm of plot, xshift = 120] () {$r=0.05$, $R=0.5$};
-%	\node[left = 0cm of plot, yshift = 105, rotate = 90] () {XY $\rightarrow$ ZW};
-%	\node[left = 0cm of plot, yshift = -20, rotate = 90] () {ZW $\rightarrow$ XY};
-%\end{tikzpicture}
-%\caption{
-%Changes in mean diploid fitness of males (blue lines), females (red lines), and the entire population (black lines) during the transitions between sex-determination systems shown in Figure \ref{fig:Combination_Turnover}.
-%Here mean diploid fitness of a particular sex is its mean diploid viability fitness times twice its frequency in the population, to capture the fact that epistatically dominant sex-determining alleles can also invade because they selfishly make more of the sex they are in.
-%The mean fitness of females increases during the spread of neo-W alleles (A and B) and the mean fitness of males increases during the spread of neo-Y alleles (C and D). 
-%However, when a neo-sex determining system evolves that is less closely linked to a locus under selection (B and D), population mean fitness decreases. 
-%%\textcolor{red}{
-%%Could add titles to the columns/rows: neo-W for row 1, neo-Y for row 3, $r=0.5$, $R=0.05$ for column 1 and $r=0.05$, $R=0.5$ for column 2. 
-%%%\& possibly adjust padding (too much whitespace?). 
-%%%Matt - could you uncomment the line legends in the Mathematica file (function not included in my Mathematica version).
-%%}
-%%\textcolor{red}{I'm still confused why male and female mean fitnesses aren't normalized by their frequency.
-I'm not sure we should be calling them means without this normalization step.
-Or we should justify this by saying that mean fitness also has something to do with the number of a sex, i.e., multiply *real* mean fitness in females by freqfemale/(1/2)?
-See the next figure for what happens when we do normalize.}
-%\textcolor{blue}{I think we should give this plot showing (male mean fitness * freq males) and (female mean fitness * freq females), without multiplying by 2 (leave off black lines, population mean fitness).
-%We could also re-plot the sex ratios on this same scale. 
-%The plot below, `adjusted for sex ratio', could then go in the appendix.
-The point is that neo-W (neo-Y) can invade when the frequency of females (males) multiplied by their mean fitness increases.
-}
-%}
-%\label{fig:Combination_MeanFit}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Changes in mean fitness corrected for sex ratio
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\begin{tikzpicture}[remember picture]
-%	\node[] (plot) {\includegraphics[width=\linewidth]{Combination_MeanFit_Corrected}};
-%\end{tikzpicture}
-%\caption{
-%\textcolor{red}{Last plot with mean fitness of sexes corrected for sex ratio. Could add to previous plot with dashed lines?}
-%}
-%\label{fig:Combination_MeanFit_Corrected}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%Chromosomal Positions
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%%\includegraphics[width=\linewidth]{Combination_Centimorgan}\\
-%%\includegraphics[width=\linewidth]{PositionPlot}\\
-%\begin{tikzpicture}[remember picture]
-%%	\node[] () {\includegraphics[width=\linewidth]{PositionPlot}};
-%	\node[] () {\includegraphics[width=0.5\linewidth]{PositionPlot_2}};
-%%	\node[anchor=east] at (0, 1.5) {\footnotesize diploid sex-antagonism}; %, $s^\male s^\female < 0$};
-%%	\node[anchor=east] at (6.5, 1.5) {\footnotesize haploid sex-antagonism}; %, $s^\male s^\female > 0$};
-%%	\node[anchor=east] at (0, -3) {\footnotesize male drive (ploidy-antagonism)}; %, $s^\male < s^\female$};
-%%	\node[anchor=east] at (6.5, -3) {\footnotesize find something interesting to plot};%, $s^\female < s^\female$};
-%%	\node[anchor=center] at (-1.3, 4.25) {\scriptsize tighter sex-linkage};
-%%	\node[anchor=center] at (2.45, 3.5) {\scriptsize ancestral SDR};
-%%	\draw[->,thick] (2.45, 3.25) -- (2.45, 2.5);
-%%	\node[anchor=center] at (-1.4, -0.25) {\scriptsize novel SDR};
-%%	\draw[->,thick] (-1.4, -0.5) -- (-1.4, -1);
-%\end{tikzpicture}
-%\caption{
-% A neo-W can invade an XY system under a large number of selective regimes.
-%%Invasion fitness of a neo-sex-determining allele against the relative genomic location of a locus under direct selection. 
-%% (neo-Y invading ZW in black, neo-W invading XY in red)
-%%The ancestral sex-determining locus is located at -25 and the novel sex-determining locus is located at 25. %and that there is a polymorphism at the \textbf{A} locus maintained by selection.
-%%Thus, if the neo-sex-determining allele invades in the gray region the system evolves tighter sex-linkage.  
-%In panel A, there is no haploid selection ($t^\Hermaphrodite=\alpha^\Hermaphrodite_{\Delta}=0$) and selection in diploids is sexually antagonistic ($s^\male=-s^\female=1/10$, $h^\male=1-h^\female=3/10$), in which case the neo-sex-determining allele can only invade if it is more closely linked to the selected locus ($R<r$, gray region; but see Figure \ref{fig:SexAntagTighter}B).
-%In panel B, there is no diploid selection ($s^\Hermaphrodite=0$) and selection in haploids is sexually antagonistic ($t^\male=-t^\female=0.08$, $\alpha^\Hermaphrodite_{\Delta}=0$), in which case the neo-sex-determining allele can invade regardless of linkage.
-%In panel C, selection in diploids ($s^\male=s^\female=1/10$, $h^\male=h^\female=7/10$) opposes drive in males ($\alpha^\male_{\Delta}=-0.05$, $t^\Hermaphrodite=\alpha^\female_{\Delta}=0$), in which case the neo-sex-determining allele can once again invade regardless of linkage.
-%We use Haldane's map function \citep[Equation 3 in ][]{Haldane1919} to convert from map distance (centiMorgans, cM) to the probability of a cross-over event.    
-%%we include haploid selection. %and assume that selection in diploids is not sexually-antagonistic ($s^\female s^\male>0$). 
-%%A polymorphism can then be maintained by opposing selection between the haploid and diploid phases. 
-%%In B, there is drive in favour of the $a$ allele in males ($\alpha^\male_{\Delta}=-1/20$), no female meiotic drive or gametic competition, $t^\Hermaphrodite=\alpha^\female_{\Delta}=0$), and equal selection in diploid sexes ($s^\female=s^\male=1/10$, $h^\female=h^\male=7/10$).
-%%In this case, a neo-W can invade even when the selected locus is more closely linked to the ancestral sex determining locus (see Table \ref{tab:specialcases} and Figure \ref{fig:Combination_Turnover}).
-%%In C and D, there is gametic competition among male gametes only (favouring $a$, $t^\male=-1/10$) and no meiotic drive or gametic competition in females ($t^\female=\alpha^\Hermaphrodite_{\Delta}=0$).
-%%In this case, the neo-W does not invade if $s^\female>s^\male$ (panel C: $s^\female=3/20$, $s^\male=1/20$) but does if $s^\female<s^\male$ (panel D: $s^\female=1/20$, $s^\male=3/20$), see Table \ref{tab:specialcases}.\\
-%%\textcolor{red}{
-%%1.
-I suspect that panel C has a region where no equilibrium is maintained (CHECK!
-Maybe include different parameters here or remove the part when no equilibrium).
-MMO: If you trust the sieve function there are stable equilibria across the entire range, although they differ greatly between XY and ZW systems near -25cM.
-%%\\
-%%2.
-Currently use different parameters for B than using in figure \ref{fig:Combination_Turnover} (selection/drive twice as strong in turnover figure).
-MMO: this is to keep it within the bounds of the plot -- using the same parameters as figure 1 makes the peak at -25 reach roughly 0.1, and then it is difficult to see the details of A,C, and D.
-%%%This plot would also benefit from titles giving, e.g., ``sexually-antagonistic selection, $s^\female s^\male<0$'' for A, ``male meiotic drive, $s^\female s^\male>0$'' for B
-%%}
-%}
-%\label{fig:Combination_Centimorgans}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%Haplotype invasion region plot
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\begin{tikzpicture}[remember picture]
-%	\node[] () {
-%	\includegraphics[width=0.5\linewidth]{regionplot_2a}
-%	\includegraphics[width=0.5\linewidth]{regionplot_hap}
-%	};
-%\end{tikzpicture}
-%\caption{
-%Parameter space (gray) where both neo-W haplotypes can invade from the same stable resident $r=0$ equilibria (equations \ref{eq:tightequil}), and therefore where an unlinked neo-W can invade an XY system with perfect sex-linkage.
-%\textbf{A}, In the absence of haploid selection, both neo-W haplotypes can invade for much of the parameter space where the relative fitnesses of male homozygotes, $w_{AA}^\male$ and $w_{aa}^\male$, are both less than that of the heterozygote, $w_{Aa}^\male = 1$.
-%In the white region neo-W haplotypes paired with the allele fixed on the Y cannot invade.
-%Parameters as in \cite{Otto2014} Figure 2a: $w_A^\Hermaphrodite=w_a^\Hermaphrodite$, $\alpha^\Hermaphrodite=1/2$, $w_{Aa}^\Hermaphrodite=1$, and $w_{AA}^\female=w_{aa}^\female=0.75$.
-%\textbf{B}, When selection is the same in both diploid sexes ($w_{aa}^\Hermaphrodite = 1$, $w_{Aa}^\Hermaphrodite = 1 + h s$, $w_{AA}^\Hermaphrodite = 1+s$), both neo-W haplotypes can invade over a portion of the parameter space where selection in diploids ($s$) opposes the force of drive during meiosis in males ($\alpha_{\Delta}^\male$).
-%Parameters: $w_A^\Hermaphrodite=w_a^\Hermaphrodite$, $\alpha^\female=1/2$, $h=1/2$.
-%}
-%\label{fig:regionplot_2a}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%W invades XY and fixes
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}
-%\centering
-%\includegraphics[width=0.5\linewidth]{FreqWLowR}\\
-%\includegraphics[width=0.5\linewidth]{SexRatioLowR}\\
-%\includegraphics[width=0.5\linewidth]{MeanDipFitLowR}
-%\caption{
-%Haploid selection allows a neo-$W$ to invade an ancestral $XY$ system and fix (\textbf{A}) despite temporarily biasing the sex ratio further (\textbf{B}) and decreasing mean diploid viability fitness (\textbf{C}).
-%Complete turnover between genetic sex-determination systems occurs despite the neo-$W$ being less tightly linked to the selected locus than the ancestral sex-determining locus is, $R>r$.
-%Parameters: $k=1$, $s^\female = 0.05$, $s^\male = 0.15$, $h^\female = h^\male = 0.7$, $t^\female = 0$, $t^\male = -0.1$, $\alpha^\male = \alpha^\female = 1/2$, $r=0.01$, $R=0.05$.
-%}
-%\label{fig:WinvasionLowR}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%W invades XY but does not fix
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}
-%\centering
-%\includegraphics[width=0.5\linewidth]{FreqWHighR}\\
-%\includegraphics[width=0.5\linewidth]{SexRatioHighR}\\
-%\includegraphics[width=0.5\linewidth]{MeanDipFitHighR}
-%\caption{
-%Haploid selection allows a completely unlinked neo-$W$ to invade an ancestral $XY$ system (\textbf{A}) despite further biasing the sex ratio (\textbf{B}) and decreasing mean diploid viability fitness (\textbf{C}).
-%The neo-$W$ does not fix (although variation at the \textbf{A} locus is maintained, $V_A>0$), resulting in a polymorphic sex-determination system.
-%Parameters as in Figure \ref{fig:WinvasionLowR} but with $R=0.5$.
-%}
-%\label{fig:WinvasionHighR}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%W invades for all rates of recombination with selected locus
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}
-%\centering
-%\includegraphics[width=0.5\linewidth]{InvasionVsRecombination}
-%\caption{
-%A neo-$W$ invades an ancestral $XY$ system with haploid selection regardless of how tightly it is linked to the selected locus. 
-%Parameters as in Figure \ref{fig:WinvasionLowR}.
-%}
-%\label{fig:InvasionVsRecombination}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%W invasion versus position of selected locus
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}
-%\centering
-%\includegraphics[width=0.5\linewidth]{InvasionVsCentiMorgans}
-%\includegraphics[width=0.5\linewidth]{InvasionVsCentiMorgansAllOrders}
-%\caption{
-%Haploid selection allows a neo-$W$ to invade an ancestral $XY$ system regardless of how tightly it and the ancestral sex-determining locus are linked to the selected locus. 
-%The ancestral sex-determining locus is located at -0.05 and the novel sex-determining locus is located at 0.05 (corresponding to the peaks of invasion fitness), such that the probability of a cross-over between them is $\approx0.1$.
-%The x-axis gives the position of the locus under haploid selection.
-%We used Haldane's map function \citep[Equation 3 in ][]{Haldane1919} to convert from map distance (centiMorgans) to the probability of a cross-over event. 
-%Parameters as in Figure \ref{fig:WinvasionLowR}.
-%}
-%\label{fig:InvasionVsCentiMorgans}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Y invades ZW and fixes (counter example to Kozi explanation)
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}
-%\centering
-%\includegraphics[width=0.5\linewidth]{FreqWCounterKozi}\\
-%\includegraphics[width=0.5\linewidth]{SexRatioCounterKozi}\\
-%\includegraphics[width=0.5\linewidth]{MeanDipFitCounterKozi}
-%\caption{
-%Meiotic drive allows a neo-$Y$ to invade an ancestral $ZW$ system and fix (\textbf{A}) despite temporarily biasing the sex ratio (\textbf{B}).
-%and decreasing mean diploid viability fitness (\textbf{C}).
-%Parameters: $k=0$, $s^\female = s^\male = t^\female = t^\male = 0$, $\alpha^\male = 0.4$, $\alpha^\female = 1/2$, $r=0$, $R=0$.
-%}
-%\label{fig:CounterKozi}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\setcounter{equation}{0}
-\renewcommand{\theequation}{S.\arabic{equation}}
-\setcounter{figure}{0}
-\renewcommand{\thefigure}{S.\arabic{figure}}
-\setcounter{table}{0}
-\renewcommand{\thetable}{S.\arabic{table}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-
-\section*{Appendix}
-
-\subsection*{Recursion equations}
+
+% For figure citations, please use "Fig" instead of "Figure".
+
+% Place figure captions after the first paragraph in which they are cited.
+
+% Results and Discussion can be combined.
+
+% Place tables after the first paragraph in which they are cited.
+
+%PLOS does not support heading levels beyond the 3rd (no 4th level headings).
+
+\section*{Supporting information}
+
+\paragraph*{S1 File.}
+\label{file:Mathematica}
+{\bf Supplementary \textit{Mathematica} file.}  This file can be used to re-derive our results and generate figures.
+
+\paragraph*{S1 Table}
+\label{tab:chisubstitutions}
+{\bf Substitutions for different loci orders assuming no interference.}
+
+\paragraph*{S2 Table}
+\label{tab:meanfitnesses}
+{\bf Mean fitnesses and zygotic sex ratio in the resident population ($M$ fixed, XY sex determination). }
+
+\paragraph*{S1 Appendix.}
 \label{app:recurs}
-
-%\textcolor{red}{Should we adjust the subscripts throughout this subsection?
-Right now we end up re-defining $i$ and $j$ (when switching from haploid to diploid; this might have been my doing!) and then introduce three new subscripts $b$, $c$, and $l$, all of which can be derived from $i$ and $j$.
-Might be more straightforward to just use $p^\Hermaphrodite_{x_1,x_2,a_1,a_2,m_1,m_2}$ where 1 is maternal and 2 is paternal?
-We then no longer have to switch indices from haploid to diploid and the connection to other variables is clear: $b=m_1m_2$, $c=x_1x_2$, and $l=a_1a_2$.
-I guess the downside will be re-writing the recursion equations...
-which is why I haven't gone ahead and tried this.}
-
-In each generation we census the genotype frequencies in male and female gametes/gametophytes (hereafter, gametes) between meiosis (and any meiotic drive) and gametic competition. 
-At this stage we denote the frequencies of X- and Y-bearing gametes from males and females $x_{i}^{\Hermaphrodite}$ and $y_{i}^{\Hermaphrodite}$.
-The superscript $\Hermaphrodite \in \{\male,\female\}$ specifies the sex of the diploid that the gamete came from. 
-The subscript $i\in\{1,2,3,4\}$ specifies the genotype at the selected locus $\mathbf{A}$ and at the novel sex-determining locus $\mathbf{M}$, where $1=AM$, $2=aM$, $3=Am$, and $4=am$. 
-The gamete frequencies from each sex sum to one, $\sum_{i}x_{i}^{\Hermaphrodite}+y_{i}^{\Hermaphrodite}=1$.
-
-Competition then occurs among gametes of the same sex (e.g., among eggs and among sperm separately) according to the genotype at the \textbf{A} locus ($w_{1}^\Hermaphrodite=w_{3}^\Hermaphrodite=w_{A}^\Hermaphrodite$, $w_{2}^\Hermaphrodite=w_{4}^\Hermaphrodite=w_{a}^\Hermaphrodite$, see Table \ref{tab:fitnesstable}).
-The genotype frequencies after gametic competition are $x_{i}^{\Hermaphrodite,s}= w_{i}x_{i}^{\Hermaphrodite}/\bar{w}_{H}^{\Hermaphrodite}$ and $y_{i}^{\Hermaphrodite,s}= w_{i}y_{i}^{\Hermaphrodite}/\bar{w}_{H}^{\Hermaphrodite}$, where $\bar{w}_{H}^{\Hermaphrodite}=\sum_{i} w_{i}x_{i}^{\Hermaphrodite}+w_{i}y_{i}^{\Hermaphrodite}$ is the mean fitness of male ($\Hermaphrodite=\male$) or female ($\Hermaphrodite=\female$) gametes.
-
-Random mating then occurs between gametes to produce diploid zygotes.
-%To shorten notation we now use index $i$ (and $j$) to denote the alleles at both the $\mathbf{A}$ and $\mathbf{M}$ loci and label $MA=1$, $Ma=2$, $mA=3$, and $ma=4$, such that $i,j\in\{1,2,3,4\}$.
-The frequencies of XX zygotes are then denoted as $xx_{ij}$, XY zygotes as $xy_{ij}$, and YY zygotes as $yy_{ij}$, where \textbf{A} and \textbf{M} locus genotypes are given by $i,j\in\{1,2,3,4\}$, as above.
-In $XY$ zygotes, the haplotype inherited from an X-bearing gamete is given by $i$ and the haplotype from a Y-bearing gamete is given by $j$. 
-In XX and YY zygotes, individuals with diploid genotype $ij$ are equivalent to those with diploid genotype $ji$; for simplicity, we use $xx_{ij}$ and $yy_{ij}$ with $i\neq j$ to denote the average of these frequencies, $xx_{ij}=(x_{i}^{\female,s}x_{j}^{\male,s}+x_{j}^{\female,s}x_{i}^{\male,s})/2$ and $yy_{ij}=(y_{i}^{\female,s}y_{j}^{\male,s}+y_{j}^{\female,s}y_{i}^{\male,s})/2$.
-
-Denoting the \textbf{M} locus genotype by $b \in \{MM, Mm, mm\}$ and the \textbf{X} locus genotype by $c \in \{XX, XY, YY\}$, zygotes develop as females with probability $k_{bc}$. 
-Therefore, the frequencies of XX females are given by $xx_{ij}^{\female}=k_{bc}xx_{ij}$, XY females are given by $xy_{ij}^{\female}=k_{bc}xy_{ij}$, and YY females are given by $yy_{ij}^{\female}=k_{bc}yy_{ij}$.
-Similarly, XX male frequencies are $xx_{ij}^{\male}=(1-k_{bc})xx_{ij}$, XY male frequencies are $xy_{ij}^{\male}=(1-k_{bc})xy_{ij}$, and YY males frequencies are $yy_{ij}^{\male}=(1-k_{bc})yy_{ij}$.
-This notation allows both the ancestral and novel sex-determining regions to determine zygotic sex according to an XY system, a ZW system, or an environmental sex-determining system. 
-In addition, we can consider any epistatic dominance relationship between the two sex-determining loci. 
-Here, we assume that the ancestral sex-determining system (\textbf{X} locus) is XY ($k_{MMXX}=1$ and $k_{MMXY}=k_{MMYY}=0$) or ZW ($k_{MMZZ}=0$ and $k_{MMZW}=k_{MMWW}=1$) and epistatically recessive to a dominant novel sex-determining locus, \textbf{M} ($k_{Mmc}=k_{mmc}=k$).
-
-Selection among diploids then occurs according to the diploid genotype at the \textbf{A} locus, $l \in \{AA, Aa, aa\}$, for an individual of type $ij$ (see Table \ref{tab:fitnesstable}). 
-The diploid frequencies after selection in sex $\Hermaphrodite$ are given by $xx_{ij}^{\Hermaphrodite,s}=w_{l}^{\Hermaphrodite} xx_{ij}/\bar{w}^{\Hermaphrodite}$, $xy_{ij}^{\Hermaphrodite,s}=w_{l}^{\Hermaphrodite} xy_{ij}/\bar{w}^{\Hermaphrodite}$, and $yy_{ij}^{\Hermaphrodite,s}=w_{l}^{\Hermaphrodite} yy_{ij}/\bar{w}^{\Hermaphrodite}$, where $\bar{w}^{\Hermaphrodite}= \sum_{i=1}^{4}\sum_{j=1}^{4}w_{l}^{\Hermaphrodite}xx_{ij}+w_{l}^{\Hermaphrodite}xy_{ij}+w_{l}^{\Hermaphrodite}yy_{ij}$ is the mean fitness of individuals of sex $\Hermaphrodite$.
-
-Finally, these diploids undergo meiosis to produce the next generation of gametes. 
-Recombination and sex-specific meiotic drive occur during meiosis.
-%We can also assume that recombination is sex specific and/or affected by the M locus - but generally we don't so I just describe $R=R_{f}=R, r_{MM,d}=r_{Mm,d}=r_{mm,d}=r, \chi_{m}=\chi_{f}=\chi$.
-Here, we allow any relative locations for the SDR, \textbf{A}, and \textbf{M} loci by using three parameters to describe the recombination rates between them. 
-$R$ is the recombination rate between the \textbf{A} locus and the \textbf{M} locus, $\rho$ is the recombination rate between the \textbf{M} locus and the \textbf{X} locus, and $r$ is the recombination rate between the \textbf{A} locus and the \textbf{X} locus.
-Table \ref{tab:chisubstitutions} shows replacements that can be made for each possible ordering of the loci assuming that there is no cross-over interference.
-During meiosis in sex $\Hermaphrodite$, meiotic drive occurs such that, in $Aa$ heterozygotes, a fraction $\alpha^{\Hermaphrodite}$ of gametes produced carry the $A$ allele and $(1-\alpha^\Hermaphrodite)$ carry the $a$ allele.
-
-\begin{table}[ht]
-\centering
-\smallskip
-\caption{
-Substitutions for different loci orders assuming no interference.
-%and $r,R\in(0,1/2)$.\textcolor{blue}{write all in form of first line?
-so that 1/2 cases are okay (can't determine chi if R is 1/2 in second line, or if r is 1/2 in third line}
-}
-\begin{tabular}{l l}
-\hline\hline
-  Order of loci &   \\ [0.5ex] \hline
-  SDR-A-M & $\rho=r(1-R)+R(1-r)$  \\
-  SDR-M-A & $r=\rho(1-R)+R(1-\rho)$ \\ %$\rho=(r-R)/(1-2R)$ \\
-  A-SDR-M & $R=r(1-\rho)+\rho(1-r)$ \\ %$\rho=(R-r)/(1-2r)$ \\
-  \hline \hline
-  \label{tab:chisubstitutions}
- \end{tabular}
-\end{table}
-
-Among gametes from sex $\Hermaphrodite$, the frequencies of haplotypes (before gametic competition) in the next generation are given by
-
-\begingroup
-\allowdisplaybreaks
-\begin{subequations}
-\begin{align}
-%
-\begin{split}
-x_{1}^{{\Hermaphrodite}'}=&xx_{11}^{\Hermaphrodite,s}+xx_{13}^{\Hermaphrodite,s}/2+(xx_{12}^{\Hermaphrodite,s}+xx_{14}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(xx_{14}^{\Hermaphrodite,s}-xx_{23}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&+(xy_{11}^{\Hermaphrodite,s}+xy_{13}^{\Hermaphrodite,s})/2+(xy_{12}^{\Hermaphrodite,s}+xy_{14}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&- r(xy_{12}^{\Hermaphrodite,s}-xy_{21}^{\Hermaphrodite,s})\alpha^\Hermaphrodite - \rho(xy_{13}^{\Hermaphrodite,s}-xy_{31}^{\Hermaphrodite,s})/2\\
-&+\big{[}-(R+r+\rho)xy_{14}^{\Hermaphrodite,s} +(R+\rho-r)xy_{41}^{\Hermaphrodite,s}\\
-&+(R+r-\rho) xy_{23}^{\Hermaphrodite,s}+(R+\rho-r)xy_{32}^{\Hermaphrodite,s}\big{]}\alpha^\Hermaphrodite/2
-\end{split}
-\\
-%
-\begin{split}
-x_{2}^{{\Hermaphrodite}'}=&xx_{22}^{\Hermaphrodite,s}+xx_{24}^{\Hermaphrodite,s}/2+(xx_{12}^{\Hermaphrodite,s}+xx_{23}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(xx_{23}^{\Hermaphrodite,s}-xx_{14}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&(xy_{22}^{\Hermaphrodite,s}+xy_{24}^{\Hermaphrodite,s})/2+(xy_{21}^{\Hermaphrodite,s}+xy_{23}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite)\\
-&- r(xy_{21}^{\Hermaphrodite,s}-xy_{12}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite) - \rho(xy_{24}^{\Hermaphrodite,s}-xy_{42}^{\Hermaphrodite,s})/2\\
-&+\big{[}-(R+r+\rho)xy_{23}^{\Hermaphrodite,s}+(R+\rho-r)xy_{32}^{\Hermaphrodite,s}\\
-&+(R+r-\rho) xy_{14}^{\Hermaphrodite,s}+(R+\rho-r)xy_{41}^{\Hermaphrodite,s}\big{]}(1-\alpha^\Hermaphrodite)/2
-\end{split}
-\\
-%
-\begin{split}
-x_{3}^{{\Hermaphrodite}'}=&xx_{33}^{\Hermaphrodite,s}+xx_{13}^{\Hermaphrodite,s}/2+(xx_{23}^{\Hermaphrodite,s}+xx_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(xx_{23}^{\Hermaphrodite,s}-xx_{14}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&(xy_{33}^{\Hermaphrodite,s}+xy_{31}^{\Hermaphrodite,s})/2+(xy_{32}^{\Hermaphrodite,s}+xy_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&- r(xy_{34}^{\Hermaphrodite,s}-xy_{43}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite - \rho(xy_{31}^{\Hermaphrodite,s}-xy_{13}^{\Hermaphrodite,s})/2\\
-&+\big{[}-(R+r+\rho)xy_{32}^{\Hermaphrodite,s} +(R+\rho-r)xy_{23}^{\Hermaphrodite,s}\\
-&+(R+r-\rho) xy_{41}^{\Hermaphrodite,s}+(R+\rho-r)xy_{14}^{\Hermaphrodite,s}\big{]} \alpha^\Hermaphrodite/2
-\end{split}
-\\
-%
-\begin{split}
-x_{4}^{{\Hermaphrodite}'}=&xx_{44}^{\Hermaphrodite,s}+xx_{34}^{\Hermaphrodite,s}/2+(xx_{14}^{\Hermaphrodite,s}+xx_{24}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(xx_{14}^{\Hermaphrodite,s}-xx_{23}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&(xy_{44}^{\Hermaphrodite,s}+xy_{42}^{\Hermaphrodite,s})/2+(xy_{41}^{\Hermaphrodite,s}+xy_{43}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite)\\
-&- r(xy_{43}^{\Hermaphrodite,s}-xy_{34}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite) - \rho(xy_{42}^{\Hermaphrodite,s}-xy_{24}^{\Hermaphrodite,s})/2\\
-&+\big{[}-(R+r+\rho)xy_{41}^{\Hermaphrodite,s}+(R+\rho-r)xy_{14}^{\Hermaphrodite,s}\\
-&+(R+r-\rho) xy_{32}^{\Hermaphrodite,s}+(R+\rho-r)xy_{23}^{\Hermaphrodite,s}\big{]}(1-\alpha^\Hermaphrodite)/2
-\end{split}
-\\
-\begin{split}
-y_{1}^{{\Hermaphrodite}'}=&yy_{11}^{\Hermaphrodite,s}+yy_{13}^{\Hermaphrodite,s}/2+(yy_{12}^{\Hermaphrodite,s}+yy_{14}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(yy_{14}^{\Hermaphrodite,s}-yy_{23}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&(xy_{11}^{\Hermaphrodite,s}+xy_{31}^{\Hermaphrodite,s})/2+(xy_{21}^{\Hermaphrodite,s}+xy_{41}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&- r(xy_{21}^{\Hermaphrodite,s}-xy_{12}^{\Hermaphrodite,s})\alpha^\Hermaphrodite - \rho(xy_{31}^{\Hermaphrodite,s}-xy_{13}^{\Hermaphrodite,s})/2\\
-&+\big{[} - (R+r+\rho)xy_{41}^{\Hermaphrodite,s} + (R+\rho-r)xy_{14}^{\Hermaphrodite,s}\\
-& + (R+r-\rho)xy_{32}^{\Hermaphrodite,s} + (R+\rho-r) xy_{23}^{\Hermaphrodite,s}\big{]}\alpha^\Hermaphrodite/2
-\end{split}
-\\
-%
-\begin{split}
-y_{2}^{{\Hermaphrodite}'}=&yy_{22}^{\Hermaphrodite,s}+yy_{24}^{\Hermaphrodite,s}/2+(yy_{12}^{\Hermaphrodite,s}+yy_{23}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(yy_{23}^{\Hermaphrodite,s}-yy_{14}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&(xy_{22}^{\Hermaphrodite,s}+xy_{42}^{\Hermaphrodite,s})/2+(xy_{12}^{\Hermaphrodite,s}+xy_{32}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite)\\
-&- r(xy_{12}^{\Hermaphrodite,s}-xy_{21}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite) - \rho(xy_{42}^{\Hermaphrodite,s}-xy_{24}^{\Hermaphrodite,s})/2\\
-&+\big{[}-(R+r+\rho)xy_{32}^{\Hermaphrodite,s} +(R+\rho-r) xy_{23}^{\Hermaphrodite,s}\\
-&+(R+r-\rho)xy_{41}^{\Hermaphrodite,s}+(R+\rho-r)xy_{14}^{\Hermaphrodite,s}\big{]}(1-\alpha^\Hermaphrodite)/2
-\end{split}
-\\
-%
-\begin{split}
-y_{3}^{{\Hermaphrodite}'}=&yy_{33}^{\Hermaphrodite,s}+yy_{13}^{\Hermaphrodite,s}/2+(yy_{23}^{\Hermaphrodite,s}+yy_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(yy_{23}^{\Hermaphrodite,s}-yy_{14}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&(xy_{33}^{\Hermaphrodite,s}+xy_{13}^{\Hermaphrodite,s})/2+(xy_{23}^{\Hermaphrodite,s}+xy_{43}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&- r(xy_{43}^{\Hermaphrodite,s}-xy_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite - \rho(xy_{13}^{\Hermaphrodite,s}-xy_{31}^{\Hermaphrodite,s})/2\\
-&+\big{[}-(R+r+\rho)xy_{23}^{\Hermaphrodite,s} +(R+\rho-r)xy_{32}^{\Hermaphrodite,s}\\
-&+(R+r-\rho) xy_{14}^{\Hermaphrodite,s} + (R+\rho-r) xy_{41}^{\Hermaphrodite,s}\big{]}\alpha^\Hermaphrodite/2
-\end{split}
-\\
-%
-\begin{split}
-y_{4}^{{\Hermaphrodite}'}=&yy_{44}^{\Hermaphrodite,s}+yy_{34}^{\Hermaphrodite,s}/2+(yy_{14}^{\Hermaphrodite,s}+yy_{24}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(yy_{14}^{\Hermaphrodite,s}-yy_{23}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&(xy_{44}^{\Hermaphrodite,s}+xy_{24}^{\Hermaphrodite,s})/2+(xy_{14}^{\Hermaphrodite,s}+xy_{34}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite)\\
-&- r(xy_{34}^{\Hermaphrodite,s}-xy_{43}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite) - \rho(xy_{24}^{\Hermaphrodite,s}-xy_{42}^{\Hermaphrodite,s})/2\\
-&+\big{[}-(R+r+\rho) xy_{14}^{\Hermaphrodite,s} + (R+\rho-r)xy_{41}^{\Hermaphrodite,s}\\
-&+(R+r-\rho) xy_{23}^{\Hermaphrodite,s} + (R+\rho-r) xy_{32}^{\Hermaphrodite,s}\big{]}(1-\alpha^\Hermaphrodite)/2
-\end{split}
-\end{align}
-\label{eq:recursions}
-\end{subequations}
-
-\endgroup
-
-\noindent
-The full system is therefore described by 16 recurrence equations (three diallelic loci in two sexes, $2^3 \times 2 = 16$). 
-However, not all diploid types are produced under certain sex-determination systems. 
-For example, with the $M$ allele fixed and an ancestral $XY$ sex-determining system, there are $XX$ males, $XY$ females, or $YY$ females ($x_{3}^\Hermaphrodite=x_{4}^\Hermaphrodite=y_{4}^\Hermaphrodite=y_{3}^\Hermaphrodite=y_{i}^\female=0$).
-%($xx_{11}^{\male}=xx_{12}^{\male}=xx_{22}^\male=xy_{11}^{\female}=xy_{12}^{\female}=xy_{21}^{\female}=xy_{22}^\female=yy_{11}^{\female}=yy_{12}^{\female}=yy_{22}^\female=0$). 
-In this case, the system only involves six recursion equations, %because there is only one \textbf{M} locus allele and no Y-bearing female gametes. 
-which we assume below to calculate the equilibria.
-
-%I think this should be moved below because we have some 'results' where we don't assume weak selection but we only have the equilibrium calculated analytically for weak selection.
-
-\subsection*{Resident equilibria and stability}
-
-In the resident population (allele $M$ fixed), we follow the frequency of $A$ in X-bearing female gametes, $p^\female_X$, and X-bearing male gametes, $p^\male_X$, and Y-bearing male gametes, $p^\male_Y$.
-We also track the total frequency of Y among male gametes, $q$, which may deviate from $1/2$ due to meiotic drive in males. 
-These four variables determine the frequencies of the six resident gamete types: $x_{1}^{\female}=\hat{p}_X^\female$, $x_{2}^{\female}=1-\hat{p}_X^\female$, $x_{1}^{\male}=(1-q)\hat{p}_X^\male$, $x_{2}^{\male}=(1-q)(1-\hat{p}_X^\male)$, $y_{1}^{\male}=q \hat{p}_Y^\male$, and $y_{2}^{\male}=q(1-\hat{p}_Y^\male)$.
-Mean fitnesses in the resident population are given in table \ref{tab:meanfitnesses}.
-
-Various forms of selection can maintain a polymorphism at the \textbf{A} locus, including sexually antagonistic selection, overdominance, conflicts between diploid selection and selection upon haploid genotypes \citep[ploidally antagonistic selection,][]{Immler:2012tl}, or a combination of these selective regimes (see below).
-
-\begin{table}[ht]
-\centering
-\smallskip
-\caption{Mean fitnesses and zygotic sex ratio in the resident population ($M$ fixed, XY sex determination). }
-\begin{tabular}{l l }
-\hline\hline
-  Sex \& Life Cycle Stage & Mean Fitness \\ [0.5ex] \hline  \noalign{\vskip 0.5ex}
-  female gametes ($\bar{w}_H^\female$) & 
-  $p_X^\female w_A^\female + (1-p_X^\female) w_a^\female$ \\ [0.5ex] \hline  \noalign{\vskip 0.5ex}
-  male gametes ($\bar{w}_H^\male$) & 
-  $\bar{p}^{\male} w_A^\male + (1-\bar{p}^{\male}) w_a^\male$ \\ [0.5ex] \hline  \noalign{\vskip 0.5ex}
-  females ($\bar{w}^\female$) & 
-  $\begin{array}{l}  (1-\zeta)^{-1} \big[ p_X^\female w_A^\female p_X^\male w_A^\male w_{AA}^\female + \\
-  (1 - p_X^\female) w_a^\female p_X^\male w_A^\male w_{Aa}^\female + \\
-  p_X^\female w_A^\female (1 - p_X^\male) w_a^\male w_{Aa}^\female + \\
-  (1-p_X^\female) w_a^\female (1 - p_X^\male) w_a^\male w_{aa}^\female \big] / \left( \bar{w}_H^\female \bar{w}_H^\male \right)
-  \end{array} 
-  $ \\ [0.5ex] \noalign{\vskip 0.5ex} \hline  \noalign{\vskip 0.5ex}
-  males ($\bar{w}^\male$) & 
-  $\begin{array}{l} \zeta^{-1} \big[ p_X^\female w_A^\female  p_Y^\male w_A^\male w_{AA}^\male + \\
-  (1 - p_X^\female) w_a^\female  p_Y^\male w_A^\male w_{Aa}^\male + \\
-  p_X^\female w_A^\female  (1 - p_Y^\male) w_a^\male w_{Aa}^\male + \\
-  (1-p_X^\female) w_a^\female  (1 - p_Y^\male) w_a^\male w_{aa}^\male \big] / \left( \bar{w}_H^\female \bar{w}_H^\male \right) 
-  \end{array}
-  $ \\ [0.5ex] \noalign{\vskip 0.5ex} \hline  \noalign{\vskip 0.5ex}
-  fraction zygotes male ($\zeta$) & $q \left[ p_Y^\male w_A^\male+(1-p_Y^\male)w_a^\male\right] / \bar{w}_H^\male $
-   \\ [0.5ex]  \noalign{\vskip 0.5ex}
-  \hline \hline
-  \label{tab:meanfitnesses}
- \end{tabular}
-\end{table}
-
-In particular special cases, e.g., no sex-differences in selection or meiotic drive ($s^\male=s^\female$, $h^\male=h^\female$, and $\alpha^\male=\alpha^\female=1/2$), the equilibrium allele frequency and stability can be calculated analytically without assuming anything about the relative strengths of selection and recombination.
-However, here, we focus on two regimes (tight linkage and weak selection) in order to make fewer assumptions about fitnesses.
-
-\subsubsection*{Recombination weak relative to selection (tight linkage between \textbf{A} and \textbf{X})}
-
-We first calculate the equilibrium frequency of the Y and $A$ alleles in the ancestral population when the recombination rate between the \textbf{X} and \textbf{A} loci is small ($r$ of order $\epsilon$).
-Selection at the \textbf{A} locus will not affect evolution at the novel sex-determining locus, \textbf{M}, if one allele is fixed on all backgrounds. 
-We therefore focus on the five equilibria that maintain both $A$ and $a$ alleles, four of which are given to leading order by:
-
-\begin{subequations}\label{eq:tightequil}
-\begin{align}
-(A)\ \ \ &\hat{p}_{Y}^{\male}=0,
-\ \hat{q}=\frac{1}{2}\left(1 - \alpha_\Delta^\male \frac{ w_{Aa}^{\male} \phi}{w_{Aa}^{\male} \phi+ w_{aa}^{\male} \psi}\right),\\
-&\hat{p}_{X}^{\female}=\frac{w_{a}^{\female} \phi}{w_{a}^{\female} \phi+ w_{A}^{\female} \psi},
-\ \hat{p}_{X}^{\male}=\frac{(1+\alpha_\Delta^\male)w_{Aa}^{\male} \phi}{(1+\alpha_\Delta^\male)w_{Aa}^{\male} \phi +w_{aa}^{\male} \psi} \nonumber \\
-(A')\ \ \ &\hat{p}_{Y}^{\male}=1,
-\ \hat{q}=\frac{1}{2}\left(1 + \alpha_\Delta^\male \frac{w_{Aa}^{\male} \phi'}{w_{Aa}^{\male} \phi' + w_{AA}^{\male} \psi'}\right),\\
-&\hat{p}_{X}^{\female}=1-\frac{w_{A}^{\female} \phi'}{w_{A}^{\female} \phi'+ w_{a}^{\female} \psi'},
-\ \hat{p}_{X}^{\male}=1-\frac{(1-\alpha_\Delta^\male)w_{Aa}^{\male} \phi'}{(1-\alpha_\Delta^\male)w_{Aa}^{\male} \phi'+w_{AA}^{\male} \psi'} \nonumber \\
-(B)\ \ \ &\hat{p}_{Y}^{\male}=0,\ \hat{p}_{X}^{\female}=1,\ \hat{p}_{X}^{\male}=1, \ \hat{q}=(1 -\alpha^\male_\Delta)/2\\
-(B')\ \ \ &\hat{p}_{Y}^{\male}=1,\ \hat{p}_{X}^{\female}=0,\ \hat{p}_{X}^{\male}=0, \ \hat{q}=(1+\alpha^\male_\Delta)/2
-\end{align}
-\end{subequations}
-\begin{equation*}
-\begin{split}
-\phi=&(1+\alpha^\female_\Delta) w_{A}^{\female} w_{Aa}^{\female} \left[ w_{a}^{\male} w_{aa}^{\male} + (1+\alpha_\Delta^\male) w_{A}^{\male} w_{Aa}^{\male} \right]/2 - w_{a}^{\male} w_{a}^{\female} w_{aa}^{\male} w_{aa}^{\female} \\
-\psi=&(1-\alpha^\female_\Delta) w_{a}^{\female} w_{Aa}^{\female} \left[ w_{a}^{\male} w_{aa}^{\male} + (1+\alpha_\Delta^\male) w_{A}^{\male} w_{Aa}^{\male}\right]/2 - (1+\alpha_\Delta^\male) w_{A}^{\male} w_{A}^{\female} w_{Aa}^{\male} w_{AA}^{\female}\\
-\phi'=&(1-\alpha^\female_\Delta) w_{a}^{\female} w_{Aa}^{\female} \left[ w_{A}^{\male} w_{AA}^{\male} + (1-\alpha_\Delta^\male) w_{a}^{\male} w_{Aa}^{\male} \right]/2 - w_{A}^{\male} w_{A}^{\female} w_{AA}^{\male} w_{AA}^{\female}\\
-\psi'=&(1+\alpha^\female_\Delta) w_{A}^{\female} w_{Aa}^{\female} \left[ w_{A}^{\male} w_{AA}^{\male} + (1-\alpha_\Delta^\male) w_{a}^{\male} w_{Aa}^{\male} \right]/2 - (1-\alpha_\Delta^\male) w_{a}^{\male} w_{a}^{\female} w_{Aa}^{\male} w_{aa}^{\female}
-\end{split}
-\end{equation*}
-
-\noindent
-A fifth equilibrium $(C)$ also exists where $A$ is present at an intermediate frequency on the Y chromosome ($0<\hat{p}_{Y}^{\male}<1$). 
-However, equilibrium $(C)$ is never locally stable when $r \approx 0$ and is therefore not considered further.
-Thus, the Y can either be fixed for the $a$ allele (equilibria $A$ and $B$) or the $A$ allele (equilibria $A'$ and $B'$).
-The X chromosome can then either be polymorphic (equilibria $A$ and $A'$) or fixed for the alternative allele (equilibria $B$ and $B'$).
-Since equilibria $(A)$ and $(B)$ are equivalent to equilibria $(A')$ and $(B')$ with the labelling of $A$ and $a$ alleles interchanged, we discuss only equilibria $(A)$ and $(B)$, in which the Y is fixed for the $a$ allele.
-If there is no haploid selection ($\alpha^{\Hermaphrodite}_\Delta=0$, $w_{A}^{\Hermaphrodite}=w_{a}^{\Hermaphrodite}=1$), these equilibria are equivalent to those found by \cite{Lloyd1977} and \cite{Otto2014}.
-
-We next calculate when $(A)$ and $(B)$ are locally stable for $r=0$. 
-According to the `small parameter theory' \citep{Karlin:1972ab,Karlin:1972dq}, these stability properties are unaffected by small amounts of recombination between the SDR and \textbf{A} locus, although equilibrium frequencies may be slightly altered.
-For the $a$ allele to be stably fixed on the Y we need $\bar{w}_{Ya}^{\male} > \bar{w}_{YA}^{\male}$ where $\bar{w}_{Ya}^{\male} = w_{a}^{\male} \big[\hat{p}_X^\female(1-\alpha^\male_\Delta) w_{A}^{\female} w_{Aa}^{\male} + (1-\hat{p}_X^\female)w_{a}^{\female} w_{aa}^{\male} \big]$ and $\bar{w}_{YA}^{\male} = w_{A}^{\male} \big[ \hat{p}_X^\female w_{A}^{\female} w_{AA}^{\male} + (1-\hat{p}_X^\female)(1+\alpha^\male_\Delta) w_{a}^{\female} w_{Aa}^{\male} \big]$.
-That is, Y-$a$ haplotypes must have higher fitness than Y-$A$ haplotypes.  
-Substituting in $\hat{p}_X^\female$ from equation \eqref{eq:tightequil}, fixation of the $a$ allele on the Y requires that $\gamma_{i}>0$ where $\gamma_{(A)}=w_{a}^{\male} \big[ (1-\alpha^\male_\Delta) w_{Aa}^{\male} \phi + w_{aa}^{\male} \psi \big]-w_{A}^{\male} \big[ w_{AA}^{\male} \phi + (1 + \alpha^{\male}_\Delta)w_{Aa}^{\male} \psi \big]$ for equilibrium $(A)$ and $\gamma_{(B)}=(1-\alpha^{\male}_\Delta)w_{a}^{\male}w_{Aa}^{\male}-w_{A}^{\male}w_{AA}^{\male}$ for equilibrium $(B)$.
-Stability of a polymorphism on the X chromosome (equilibrium $A$) further requires that $\phi >0$ and $\psi >0$. 
-Fixation of the $a$ allele on the X (equilibrium $B$) can be stable only if equilibrium $(A)$ is not, as it requires $\psi<0$.
-%and $2w_{A}^{\female}w_{AA}^{\female}>(1-\alpha_\Delta^{\female})w_{a}^{\female}w_{Aa}^{\female}$ or just $4w_{A}^{\female}w_{AA}^{\female}<(1-\alpha_\Delta^{\female})w_{a}^{\female}w_{Aa}^{\female}$ (which also prevents $\psi>0$).
-
-%\textcolor{red}{check last condition and the stability condition below are correct}
-%\textcolor{blue}{The last condition looks good to me, although in your Turnover-norec-MFS.nb you look at YA fixed, so you have to flip everything (so I made Turnover-norec-MFS-MMO.nb to do this).
-%The one issue I can find here is that you can also prevent $\lambda>1$ when the slope and intercept of the quadratic at $\lambda=1$ are negative (you only looked at both being positive).
-In this case we need $4w_{A}^{\female}w_{AA}^{\female}<(1-\alpha_\Delta^{\female})w_{a}^{\female}w_{Aa}^{\female}$, which also prevents $\psi>0$.
-%I've added this in.
-%It could also be the case that the slope and intercept are the same sign but the roots are imaginary - but this is never the case here.
-%Stability condition below looks good to me (from matt version of turnoverSOM-MIKE.nb).}
-
-\subsubsection*{Selection weak relative to recombination (weak selection)}
-
-Here, we assume that selection and meiotic drive are weak relative to recombination ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon$). 
-The maintenance of a polymorphism at the \textbf{A} locus then requires that
-
-\begin{equation}
-\begin{split}
-0&< - \left[(1-h^\female)s^\female +(1-h^\male) s^\male + t^\female +t^\male + \alpha_{\Delta}^\female+\alpha_{\Delta}^\male\right]\\
-%
-\text{and }\quad 0&<h^\female s^\female +h^\male s^\male + t^\female +t^\male + \alpha_{\Delta}^\female+\alpha_{\Delta}^\male.
-\end{split}
-\end{equation}
-
-\noindent
-which indicates that a polymorphism can be maintained by various selective regimes.
-
-Given that a polymorphism is maintained at the \textbf{A} locus by weak selection, the frequencies of $A$ in each type of gamete are the same ($\hat{p}^\female_X=\hat{p}^\male_X=\hat{p}^\male_Y=\bar{p}$) and given, to leading order, by
-
-\begin{equation}
-\bar{p}=\frac{h^\female s^\female + h^\male s^\male +t^\female+t^\male+\alpha_{\Delta}^\female+\alpha_{\Delta}^\male}
-{(2h^\female-1)s^\female+(2h^\male-1)s^\male}
-+O(\epsilon)
-.
-\label{eq:pAve}
-\end{equation}
-
-\noindent
-Differences in frequency between gamete types are of $O(\epsilon)$:
-
-\begin{equation}
-\begin{split}
-\hat{p}^\male_X-\hat{p}^\female_X&=V_{A}\big{(}D^\male - D^\female +\alpha_{\Delta}^\male-\alpha_{\Delta}^\female \big{)}
-+O(\epsilon^2)\\
-%
-\hat{p}^\male_Y-\hat{p}^\female_X&=V_{A}\left[D^\male - D^\female+\alpha_{\Delta}^\male-\alpha_{\Delta}^\female+(1-2r)(t^\male-t^\female)\right]/2r
-+O(\epsilon^2)\\
-%
-\hat{p}^\male_Y-\hat{p}^\male_X&=V_{A}\left(D^\male - D^\female+\alpha_{\Delta}^\male-\alpha_{\Delta}^\female+t^\male-t^\female\right)(1-2r)/2r
-+O(\epsilon^2)
-\end{split}
-\label{eq:freq_diffs}
-\end{equation}
-
-\noindent
-where $V_{A}=\bar{p}(1-\bar{p})$ is the variance in the frequency of $A$ and $D^\Hermaphrodite=\big{[} \bar{p}s^\Hermaphrodite+(1-\bar{p})h^\Hermaphrodite s^\Hermaphrodite\big{]} -\big{[} \bar{p}h^\Hermaphrodite s^\Hermaphrodite+(1-\bar{p}) \big{]}$ corresponds to the difference in fitness between $A$ and $a$ alleles in diploids of sex $\Hermaphrodite \in \{\female,\male\}$ ($\bar{p}$ is the leading-order probability of mating with an $A$-bearing gamete from the opposite sex).
-The frequency of Y among male gametes depends upon the difference in the frequency of the $A$ allele between X- and Y-bearing male gametes and the strength of meiotic drive in favour of the $A$ allele in males, $q=1/2+\alpha_{\Delta}^\male(\hat{p}^\male_Y-\hat{p}^\male_X)/2+O(\epsilon^3)$.
-Without gametic competition or drive ($\alpha_{\Delta}^\Hermaphrodite=t^\Hermaphrodite=0$) our results reduce to those of \citet{vanDoorn:2007eu}.
-
-% the differences in the frequencies of $A$ in each type of gamete are small, as is the bias in the sex-determining factor from the heterogametic sex, and we can solve for the mean frequency of $A$ across all types ($p_A$), the difference in the frequencies of $A$ between two of the three types, and the bias in the frequency of the sex-determining factor, to first order in selection.
-%Linear stability analysis can then be used to determine the stability of this equilibrium.
-%Without haploid selection or meiotic drive our results reduce to those of \cite{vanDoorn:2007eu}.
-%when $k=0$ (neo-$Y$ invading a $ZW$ system) or when $k=1$ (neo-$W$ invading an $XY$ system) (\textcolor{red}{CHECK}).
-%However, with haploid selection or meiotic drive a stable polymorphism at locus \textbf{A} no longer requires sexually antagonistic selection.
-%, as it can also be achieved by ploidally-antagonistic selection.
-
-\subsection*{Invasion conditions}
-
-%Here, we determine whether a rare neo-Y or neo-W allele spreads when rare, which occurs when $\lambda > 1$.
-%We begin with the general result and then give explicit solutions under tight linkage and weak selection.
-
-%If the average change in frequency of the two haplotypes that carry the $m$ allele ($Am$ and $am$) is positive, invasion will always occur (i.e., if $\left\{(\lambda_{mA}-1)+ (\lambda_{ma}-1) \right\}/2 > 0$ then $\lambda > 1$, see table \ref{tab:haplotype_growth} for $\lambda_{mi}$).
-%If neither haplotype increases in frequency ($\lambda_{mA}, \lambda_{ma} < 1$), the $m$ allele will not invade. 
-%Otherwise, the new sex-determining allele increases in frequency on one \textbf{A} background and declines on the other, and invasion requires
-%\begin{equation}\label{eq:neoYR}
-%R \left[ 
-%\frac{p^\female_X w^\female_A w^\male_a (1-\alpha^\male)}{ \bar{w}^\female_H \bar{w}^\male_H (\lambda_{mA}-1)} + 
-%p^\female_X \frac{w^\female_A}{\bar{w}^\female_H} \frac{w^\male_a(1-\alpha^\male)}{\bar{w}^\male_H} \frac{1}{\lambda_{mA}-1} + 
-%\frac{(1 - p^\female_X) w^\female_a w^\male_A \alpha^\male}{ \bar{w}^\female_H \bar{w}^\male_H (\lambda_{ma}-1)} 
-%\right] 
-%\frac{w^\male_{Aa}}{q\bar{w}^\male} < 1,
-%\end{equation}
-
-%\noindent
-%for the neo-$Y$, and
-
-%\noindent
-%\begin{equation}\label{eq:neoWR}
-%R \left[ 
-%\frac{\bar{p}^\male w^\male_A w^\female_a (1-\alpha^\female)}{ \bar{w}^\male_H \bar{w}^\female_H (\lambda_{mA}-1)} + 
-%\frac{(1 - \bar{p}^\male) w^\male_a w^\female_A \alpha^\female}{ \bar{w}^\male_H \bar{w}^\female_H (\lambda_{ma}-1)} 
-%\right] 
-%\frac{w^\female_{Aa}}{(1-q)\bar{w}^\female} < 1,
-%\end{equation}
-
-%\noindent
-%for the neo-$W$.
-
-%Equations \eqref{eq:neoYR} and \eqref{eq:neoWR} show that the new sex-determining allele, $m$, is expected to invade for any probability of recombination between loci \textbf{A} and \textbf{M}, $R$, when the net flow of recombinants is from the less fit (smaller $\lambda_{mi}$) to the more fit \textbf{A} background (making the terms inside the square brackets in Equations \ref{eq:neoYR} and \ref{eq:neoWR} negative).
-%\textcolor{red}{Q: is it definitely possible to have negative square brackets for a equilibria maintained by selection?}
-%Assuming $g_A^* > 0$ and $g_a^* < 0$ without loss of generality, this is $-(1 - p^\female_X) w_{m,A} g_a^* < p^\female_X w_{m,a} g_A^*$.
-%When the net flow of recombinants is from the more fit to the less fit haplotype, the new sex-determining allele can still invade when the rate of recombination between it and the selected locus is small enough.
-%\textcolor{red}{Q:Is it the case that sometimes the square brackets are positive and invasion occurs for $r_{AM}=1/2$?
-In which case it might be better to have slightly different phrasing here.}
-%Equations \eqref{eq:neoYR} and \eqref{eq:neoWR} show that the new sex-determining allele, $m$, is expected to invade for any probability of recombination between loci \textbf{A} and \textbf{M}, $R$, when the net flow of recombinants is from the less fit (smaller $\lambda_{mi}$) to the more fit \textbf{A} background (making the terms inside the square brackets in Equations \ref{eq:neoYR} and \ref{eq:neoWR} negative).
-%When the net flow of recombinants is from the more fit to the less fit haplotype, the new sex-determining allele can still invade when the rate of recombination between it and the selected locus is small enough.
-%To better understand when these scenarios are possible we next use knowledge of the equilibria and their stability under tight linkage and weak selection.
-
-\textcolor{red}{Cover the other parts of the characteristic polynomial here.}
-\textcolor{blue}{Waiting for Sally's proof!}
-
-A rare neo-Y or neo-W will spread from a given ancestral equilibrium when the leading eigenvalue, $\lambda$, of the Jacobian matrix derived from the eight mutant recursion equations (given by \ref{eq:recursions}c,d,g,h), evaluated at the ancestral equilibrium, is greater than one.
-However, because a neo-Y (neo-W) is always in males (females) and is epistatically dominant to the ancestral sex-determining locus, we need only two recursion equations (e.g., tracking the change in the frequency of neo-Y-$A$ and neo-Y-$a$ gametes from males) and thus the leading eigenvalue is the largest solution the polynomial $\lambda^2 + b\lambda + c = 0$ as described in the text (Table \ref{tab:haplotype_growth}).
-%It can be shown (see supplementary Mathematica file) that the coefficients are $b= - (\lambda_{mA} + \lambda_{ma})+(\chi_{mA} + \chi_{ma})$ and $c = (\lambda_{mA}-\chi_{mA}) (\lambda_{ma}-\chi_{ma}) -\chi_{mA} \chi_{ma}$, where $\lambda_{mi}$ is the multiplicative growth rate of the frequency of mutants on background $i\in\{A,a\}$, without accounting for loss due to recombination, and $\chi_{mi}$ is the rate at which mutants on background $i\in\{A,a\}$ recombine onto the other \textbf{A} locus background in heterozygotes.
-%The leading eigenvalue is then greater than one whenever $\lambda_{mA}>1$ and $\lambda_{ma}>1$, less than one whenever $\lambda_{mA}<1$ and $\lambda_{ma}<1$, and greater than one whenever  $\lambda_{mA}>1$ or $\lambda_{ma}>1$ and $\chi_{ma} (\lambda_{mA}-1) + \chi_{mA} (\lambda_{ma}-1) > 0$.
-
-The general conditions for the invasion of a neo-sex-determining allele are given in the main text, in terms of the growth rates of the mutant haplotypes in the absence of recombination ($\lambda_{mi}$) and the rate that recombination destroys them ($\chi_{mi}$).
-For tight linkage between the ancestral sex-determining locus and the selected locus we can calculate these terms explicitly (see below).
-For weak selection we can take a Taylor series of the leading eigenvalue. 
-The leading eigenvalue, $\lambda$, for any $k$, is given up to order $\epsilon^2$ by equation \eqref{eq:lambda_ESD_k}.
-
-\subsubsection*{Tight linkage between \textbf{A} and \textbf{X} (recombination weak relative to selection)}
-
-Here, we explore the conditions under which a neo-W invades an XY system assuming that the \textbf{A} locus is initially in tight linkage with the ancestral sex-determining region ($r \approx 0$). 
-We disregard neo-Y mutations, which never spread given that the ancestral population is at a stable equilibrium (see supplementary \textit{Mathematica} notebook for proof).
-
-Starting with the simpler equilibrium $(B)$, the terms of that determine the leading eigenvalue are
-
-\begin{subequations}\label{Binvasion}
-\begin{align}
-\lambda_{mA}&= \left[w_{A}^\male (1+\alpha^\male_\Delta) \right]^{-1}
-\frac{w_{A}^\female }{w_{A}^\female}
-\frac{\left[ w_{A}^\male (1+\alpha^\male_\Delta) w_{AA}^\female + 
-w_{a}^\male (1-\alpha^\male_\Delta) w_{Aa}^\female (1+\alpha^\female_\Delta) \right]}
-{ 2w_{AA}^\female } \\
-\lambda_{ma}&= \left[w_{A}^\male (1+\alpha^\male_\Delta) \right]^{-1}
-\frac{w_{a}^\female}{w_{A}^\female}
-\frac{\left[  w_{A}^\male (1+\alpha^\male_\Delta) w_{Aa}^\female (1-\alpha^\female_\Delta)+
-w_{a}^\male (1-\alpha^\male_\Delta) w_{aa}^\female \right]}
-{ 2w_{AA}^\female } \\
-\chi_{mA}&= \frac{1}{2} \left[w_{A}^\male (1+\alpha^\male_\Delta) \right]^{-1}
-\frac{w_{A}^\female }{w_{A}^\female}
- \frac{\left[  w_{a}^\male (1-\alpha^\male_\Delta) w_{Aa}^\female (1 + \alpha^\female_\Delta) \right]}
-{ w_{AA}^\female } \frac{R}{2}\\
-\chi_{ma}&= \frac{1}{2} \left[w_{A}^\male (1+\alpha^\male_\Delta) \right]^{-1}
-\frac{w_{a}^\female}{w_{A}^\female}
- \frac{\left[  w_{A}^\male (1+\alpha^\male_\Delta) w_{Aa}^\female (1-\alpha^\female_\Delta) \right]}
-{  w_{AA}^\female} \frac{R}{2}
-\end{align}
-\end{subequations}
-
-%\noindent
-%In this case, the zygotic sex ratio ($\zeta$) is given by the difference in haploid selection in males on $a$ (fixed on the Y) and $A$ (fixed on the X) alleles, i.e., there are more males than females if $\zeta = \alpha^\male w_A^\male / [(1-\alpha^\male)w_a^\male + \alpha^\male w_A^\male]<1/2$.
-%$\alpha^\male<1/2$ and/or $w_{a}^\male>w_{A}^\male$.
-%Populations with haploid selection for $a$ in males have a male biased zygotic sex ratio are thus more permissive to invasion by a neo-W ($\lambda_{mA}$ and $\lambda_{ma}$ larger).
-%%In addition, the spread of neo-W alleles depends on the fitness of female diploids after mating with an X-$A$ or Y-$a$ male gamete, relative to the fitness of females in the population (all have genotype $AA$ and fitness $w_{AA}^\female$ at this equilibrium).
-%Haploid selection in males has a second effect; the spread rate of neo-W haplotypes is determined by their fitness in diploid females, which depends on their diploid genotype and thus on the male gamete they pair with.
-%Zygotes carrying dominant neo-W alleles will develop as females regardless of their genotype at the XY locus. 
-%Therefore, neo-W females result from matings with either X-$A$ or Y-$a$ male gametes. 
-%The relative proportion of these male gametes is determined by haploid selection in males; mating with a Y-$a$ male gamete is more likely if the $a$ allele is favoured during male gamete production or competition ($\zeta<1/2$).
-%Thus, neo-W females experience different diploid selection than XX females, and the extent of this difference depends on haploid selection in males.
-%Furthermore, haploid selection in females can directly select upon neo-W-$A$ or neo-W-$a$ haplotypes. 
-%A neo-W-$A$ female gamete has the same fitness during haploid competition as resident $A$-bearing female gametes. 
-%On the other hand, neo-W-$a$ female gametes can be favoured or disfavoured during female haploid competition (favoured if $w_{a}^\female>w_{A}^\female$). 
-%Meiotic drive in females ($\alpha^\female$) similarly affects the fitness of these neo-W haplotypes, except that it impacts both haplotypes as meiotic drive only occurs in heterozygotes and therefore does not occur in resident XX females (who are always homozygote $AA$).
-
-Haploid selection impacts the spread of neo-W haplotypes in three ways.
-Firstly, the zygotic sex ratio becomes male biased, $\zeta>1/2$, when the $a$ allele (which is fixed on the Y) is favoured during competition among male gametes or by meiotic drive in males.
-Specifically, at equilibrium $(B)$, female zygote frequency is $1 - \zeta = w_A^\male (1+\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$ where $2\bar{w}_{H}^\male= \big[w_a^\male (1-\alpha^\male_\Delta) +  w_A^\male (1+\alpha^\male_\Delta) \big]$ has been canceled out in equations \eqref{Binvasion} to leave the term $\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]^{-1}$.
-Male biased sex ratios facilitate the spread of a neo-W because neo-W alleles cause the zygotes that carry them to develop as the rarer, female, sex.
-
-Secondly, haploid selection in females selects on neo-W haplotypes directly.
-At equilibrium $(B)$, the fitness of female gametes under the ancestral sex-determining system is $w_{A}^\female$ such that the relative fitnesses of neo-W-$A$ and neo-W-$a$ haplotypes during female gametic competition are $w_{A}^\female/w_{A}^\female$ and $w_{a}^\female/w_{A}^\female$ (see terms in equation \ref{Binvasion}).
-Meiotic drive in females will also change the proportion of gametes that carry the $A$ versus $a$ alleles, which will be produced by heterozygous females in proportions $(1+\alpha_{\Delta}^\female)/2$ and $(1-\alpha_{\Delta}^\female)/2$, respectively.
-These terms are only associated with heterozygous females, i.e., they are found alongside $w_{Aa}^\female$.
-
-Thirdly, haploid selection in males affects the diploid genotypes of females by altering the allele frequencies in the male gametes that female gametes pair with.
-At equlibrium $(B)$, neo-W female gametes will mate with X-$A$ male gametes with probability $ w_A^\male (1+\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$ and Y-$a$ male gametes with probability $w_a^\male (1-\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$, where the $2\bar{w}_{H}^\male$ terms have been canceled in equation \eqref{Binvasion} (as mentioned above).
-Thus, for example, neo-W-$A$ haplotypes are found in $AA$ female diploids with probability $ w_A^\male (1+\alpha^\male_\Delta)/ (2\bar{w}_{H}^\male)$ (first term in square brackets in the numerator of equation \ref{Binvasion}a) and in $Aa$ female diploids with probability $w_a^\male (1-\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$ (see equation \ref{Binvasion}c and the second term in square brackets in the numerator of equation \ref{Binvasion}a).
-
-%For instance, because an epistatically dominant neo-W always causes its carrier to become female, it creates females who carry either Y-$a$ or X-$A$ genotypes from their father.
-%Thus, because when there is a polymorphism the X carries some non-zero frequency of $A$, haploid selection in males impacts the diploid genotypes of females (e.g., creating more $Aa$ females when drive in males favours Y-$a$).
-%How this affects the spread of the neo-W then depends on diploid and haploid selection in females.
-
-The other terms in equations \eqref{Binvasion} are more easily interpreted if we assume that there is no haploid selection in either sex, in which case $\lambda_{mA}=(w_{AA}^\female+w_{Aa}^\female)/2 w_{AA}^\female$ and $\lambda_{ma}=(w_{aa}^\female+w_{Aa}^\female)/ 2 w_{AA}^\female$.
-Neither haplotype can spread under purely sexually-antagonistic selection, where $A$ is directionally favoured in females ($w_{AA}^\female>w_{Aa}^\female>w_{aa}^\female$) and $a$ is directionally favoured in males ($w_{AA}^\male>w_{Aa}^\male>w_{aa}^\male$).
-Essentially, the X is then already as specialized as possible for the female beneficial allele ($A$ is fixed on the X), and the neo-W often makes daughters with the Y-$a$ haplotype, increasing the flow of $a$ alleles into females, which reduces the fitness of those females.
-
-If selection doesn't uniformly favour $A$ in females, however, neo-W-$A$ haplotypes and/or neo-W-$a$ haplotypes can spread ($\lambda_{mA}>1$ and/or $\lambda_{ma}>1$).
-%If $\lambda_{mA}>1$ (requiring $w_{Aa}^\female>w_{AA}^\female$), the implication is that the neo-W can spread alongside the $A$ allele, despite the fact that the neo-W sometimes brings $Y-a$ haplotypes into females, because $a$ is favoured by selection in females despite $A$ being fixed on the X.
-A neo-W-$A$ haplotype can spread ($\lambda_{mA}>1$) when $w_{Aa}^\female>w_{AA}^\female$, despite the fact that a neo-W brings Y-$a$ haplotypes into females.
-In this case the $a$ allele is favoured by selection in females despite $A$ being fixed on the X.
-For this equilibrium to be stable (i.e.,  to keep $A$ fixed on the X), X-$a$ cannot be overly favoured in females and X-$A$ must be sufficiently favoured in males (for example, by overdominance in males).
-Specifically, from the stability conditions for equilibrium (B), we must have $w_{Aa}^\female < 2 w_{AA}^\female$ and $w_{Aa}^\male/\big[(w_{aa}^\male+w_{Aa}^\male)/2\big]>w_{Aa}^\female/w_{AA}^\female$.
-
-Still considering $w_{Aa}^\female>w_{AA}^\female$, the neo-W can also spread alongside the $a$ allele ($\lambda_{ma}>1$) if $w_{aa}^\female$ is large enough such that $(w_{Aa}^\female+w_{aa}^\female)/2>w_{AA}^\female$.
-%there is sufficiently strong underdominance in females ($w_{aa}^\female>w_{Aa}^\female$) \textcolor{blue}{[this is describing directional selection, not overdominance - check the conditions for the case we want to talk about]}, such that $(w_{Aa}^\female+w_{aa}^\female)/2>w_{AA}^\female$.
-This can occur with overdominance or directional selection for $a$ in females (Figure \ref{fig:regionplots}B,C).
-In this case, $a$ is favoured in females (comparing $Aa$ to $AA$ genotypes in females) but $A$ is fixed on the X due to selection in males. 
-The neo-W-$a$ haplotype can spread because it produces females with higher fitness $Aa$ and $aa$ genotypes.
-
-%When both haplotypes can spread on their own ($\lambda_{mA}>1$ and $\lambda_{ma}>1$), the neo-W invades regardless the recombination rate between it and the selected locus, $R$.
-%When neither haplotype can spread ($\lambda_{mA}<1$ and $\lambda_{ma}<1$) the neo-W can never invade.
-%And when only one haplotype can spread on its own the neo-W invades only when the rate of recombination onto the favourable background is sufficiently larger than the rate of recombination off this background (i.e., equation\ref{eq:lambdasGen} is satisfied).
-
-%Haploid selection affects the conclusions outlined above by altering the zygotic sex ratio and exerting direct selection on neo-W haplotypes.
-%The effect of sex ratio selection is straightforward and can be seen in equation \eqref{Binvasion}, where male drive and gamete competition for $a$ (which is fixed on the Y and therefore causes a male bias) increases all four terms.
-%Direct selection on neo-W haplotypes can also be seen in equation \eqref{Binvasion} by noticing that increasing female drive in favour of $A$ increases the neo-W-$A$ haplotype growth rate ($\lambda_{mA}$) while female drive and gamete competition in favour of $a$ increases the neo-W-$a$ haplotype growth rate ($\lambda_{ma}$).
-%Gamete competition in females does not impact the spread of neo-W-$A$ haplotypes because they are on the same background as the resident X.
-%Recombination between the selected locus and the neo-W complicates things slightly, as selective advantages for one neo-W haplotype during the haploid stage in females comes at a cost to the other, and thus recombination off the favoured background becomes more detrimental.
-
-%\textcolor{red}{the versions for equil $(A)$ are not terrible but could be improved by cleverly re-writing with the $\phi$ and $\psi$ terms from above, I think...}
-
-Similar equations can be derived for equilibrium (A) by substituting the equilibrium allele frequencies into Table \ref{tab:haplotype_growth}
-
-\begin{subequations}\label{Ainvasion}
-\begin{align}
-\lambda_{mA}&= \frac{a}{b} \left[w_{AA}^\female w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi +  w_{Aa}^\female (1+\alpha^\female_\Delta) w_a^\male c \right] / (2 w_a^\female) \\
-\lambda_{ma}&= \frac{a}{b} \left[ w_{Aa}^\female (1-\alpha^\female_\Delta) w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi +  w_{aa}^\female w_a^\male c \right] / (2 w_A^\female) \\
-\chi_{mA}&= \frac{a}{b} \frac{R}{2} \left[   w_{Aa}^\female (1+\alpha^\female_\Delta) w_a^\male c \right] / w_a^\female\\ 
-\chi_{ma}&= \frac{a}{b} \frac{R}{2} \left[ w_{Aa}^\female (1-\alpha^\female_\Delta) w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi \right] / w_A^\female
-\end{align}
-\end{subequations}
-
-\noindent
-where
-
-\begin{subequations}
-\begin{align}
-a &= w_a^\female \phi + w_A^\female \psi \\
-b &= w_{AA}^\female \left[ w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \right] \phi^2 + w_{Aa}^\female \left[ w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) + w_{aa}^\male w_a^\male \right] \psi \phi + w_{aa}^\female \left( w_{aa}^\male w_a^\male \right) \psi^2\\
-%c &= w_{Aa}^\male (1-\alpha^\male_\Delta) \phi \left[ w_{Aa}^\male (1+\alpha^\male_\Delta) \phi \right] + w_{Aa}^\male\phi \left[ 2w_{AA}^\male + w_{aa}^\male (1+\alpha^\male_\Delta) \right] \psi + w_{aa}^\male \psi \left(2w_{AA}^\male \psi \right) \\
-c &= w_{Aa}^\male (1-\alpha^\male_\Delta) \phi + 2w_{aa}^\male \psi
-\end{align}
-\end{subequations}
-
-As with equilibrium (B), haploid selection again modifies invasion fitnesses by altering the sex ratio and the diploid genotypes of females and directly selecting upon female gametes.
-The only difference is that resident XX females are no longer always homozygote $AA$ and males are no longer always heterozygote $Aa$.
-Thus the effect of haploid selection in males is reduced, as is the difference in fitness between neo-W haplotypes and resident X haplotypes, as both can be on any diploid or haploid background.
-
-The other terms are easier to interpret in the absence of haploid selection.
-For instance, without haploid selection, the neo-W-$A$ haplotype spreads ($\lambda_{mA}>1$) if and only if
-
-\begin{equation}\label{eq:BeqWAspread}
-2(w_{Aa}^\female-w_{aa}^\female)w_{aa}^\male \psi^2 > (w_{AA}^\female-w_{Aa}^\female)w_{Aa}^\male \phi (\phi-\psi)
-\end{equation}
-
-\noindent  
-where $\phi-\psi=w_{AA}^\female w_{Aa}^\male-w_{aa}^\female w_{aa}^\male$ and both $\phi$ and $\psi$ are positive when equilibrium (A) is stable. 
-In contrast to equilibrium (B), a neo-W haplotype can spread under purely sexually-antagonistic selection  ($w_{aa}^\female<w_{Aa}^\female<w_{AA}^\female$ and $w_{AA}^\male<w_{Aa}^\male<w_{aa}^\male$).
-The neo-W-$A$ can spread as long as it becomes associated with females that bear more $A$ alleles than observed at equilibrium (A). 
-%In this case, the neo-W-$A$ haplotype can spread, despite producing a lot of $Aa$ daughters by obtaining the $a$ from Y-gametes, when $aa$ females, which the neo-W-$A$ never makes, are strongly selected against.
-%This can be intuited from the fact that \eqref{eq:BeqWAspread} will be more easily met when $w_{Aa}^\female-w_{aa}^\female\approx w_{Aa}^\female$ and $w_{AA}^\female-w_{Aa}^\female\approx 0$, implying $w_{aa}^\female \approx 0$ and $w_{Aa}^\female\approx w_{AA}^\female$ (although this is complicated by the fact that $w_{aa}^\female$ and $w_{Aa}^\female$ affect $\phi$ and $\psi$ too, the intuition holds).
-
-Without haploid selection, the neo-W-$a$ haplotype spreads ($\lambda_{ma}>1$) if and only if
-
-\begin{equation}\label{eq:BeqWaspread}
-(w_{aa}^\female + w_{Aa}^\female-2w_{AA}^\female)w_{Aa}^\male \phi^2 + (w_{aa}^\female-w_{Aa}^\female)(w_{Aa}^\male+2w_{aa}^\male) \phi \psi >0
-\end{equation}
-
-\noindent
-This condition cannot be met with purely sexually antagonistic selection (as both terms on the left-hand side would then be negative), but it can be met under other circumstances. 
-For example, with overdominance in males there is selection for increased $A$ frequencies on X chromosomes in males, which are always paired with Y-$a$ haplotypes.
-Directional selection for $a$ in females can then maintain a polymorphism at the $\textbf{A}$ locus on the X.
-This scenario selects for a modifier that increases recombination between the sex chromosomes \citep[e.g., blue region of Figure 2d in][]{Otto2014} and facilitates the spread of neo-W-$a$ haplotypes, which create more females bearing more $a$ alleles than the ancestral X chromosome does.
-
-\subsubsection*{Role of Haploid Selection with Tight Linkage}
-
-Haploid selection generally expands the conditions under which neo-W alleles can spread within ancestral systems that have evolved tight linkage between the sex-determining locus and a selected locus ($r \approx 0$).
-First, haploid selection can allow a polymorphism to be maintained when it would not under diploid selection alone (e.g., with directional selection in diploids). 
-In cases of ploidally-antagonistic selection, where there is a balance between alleles favored in the haploid stage and the diploid stage, neo-W alleles - even unlinked alleles - can spread (Figure \ref{fig:regionPloidAntag}).
-Second, even when diploid selection could itself maintain a polymorphism, haploid selection can increase the conditions under which transitions among sex chromosomes are possible.
-Of particularly importance, when selection is sexually-antagonistic in diploids ($s^\female s^\male <0$ and $0<h^\Hermaphrodite<1$), an unlinked neo-W ($R=1/2$) cannot invade unless there is also haploid selection (see proof in supplementary \textit{Mathematica} file; Figures \ref{fig:SexAntagTighter} and \ref{fig:SexAntagTighterMaleDrive}).
-More generally, haploid selection alters the conditions under which neo-W chromosomes can spread (compare Figures \ref{fig:regionMaleDrive}-\ref{fig:regionFemaleGS} to Figure \ref{fig:regionplots}).
-
-%[SALLY:  I think that is enough, but we could add somewhere??: "Without haploid selection, unlinked neo-W alleles ($R=1/2$) can invade only under certain conditions, requiring either overdominance in males or underdominance in females (see proof in supplementary \textit{Mathematica} file).?
-Note that underdominance in females with directional selection in males can lead to the spread of unlinked neo-W?s, but only from equilB (only $\lambda_{ma}$ is greater than one in this case).]
-
-Male haploid selection in favour of the $a$ allele ($\alpha_{\Delta}^\male<0$, $w_{A}^\male<w_{a}^\male$) generates male-biased sex ratios at equilibria (A) and (B), where Y-$a$ is fixed ($\hat{p}_{Y}^\male=0$).
-Male-biased sex-ratios facilitate the spread of neo-W-$A$ and neo-W-$a$ haplotypes (increasing $\lambda_{mA}$ and $\lambda_{ma}$). 
-Panels A-C in Figures \ref{fig:regionMaleDrive} and \ref{fig:regionMaleGS} show that neo-W haplotypes tend to spread for a wider range of parameters when sex ratios are male biased, compared to Figure \ref{fig:regionplots} without haploid selection.
-By contrast, male haploid selection in favour of the $A$ allele generates female-biased sex ratios and reduces $\lambda_{mA}$ and $\lambda_{ma}$, as demonstrated by panels D-F in Figures \ref{fig:regionMaleDrive} and \ref{fig:regionMaleGS}.
-
-Female haploid selection generates direct selection on the neo-W-$A$ and neo-W-$a$ haplotypes as they spread in females. 
-Thus, female haploid selection in favour of the $a$ allele tends to increase $\lambda_{ma}$ and decrease $\lambda_{mA}$, as shown by panels A-C in Figures \ref{fig:regionFemaleDrive} and \ref{fig:regionFemaleGS}.
-Conversely, female haploid selection in favour of the $A$ allele increases $\lambda_{mA}$ and decreases $\lambda_{ma}$, see panels D-F in Figures \ref{fig:regionFemaleDrive} and \ref{fig:regionFemaleGS}.
-
-Thus, the impact of haploid selection on sex chromosome transitions must be considered as two sides of a coin: it can generate sex ratio biases that drive sex chromosome transitions to equalize the sex ratio, but it can also drive in new sex chromosomes and thereby cause sex ratios to become biased.
-
-%\subsubsection*{Tight Linkage and Haploid Selection}
-
-%With tight linkage, haploid selection generally expands the conditions under which neo-W alleles can spread. 
-%For example, when selection is sexually-antagonistic in diploids ($s^\female s^\male <0$ and $0<h^\Hermaphrodite<1$) an unlinked neo-W ($R=1/2$) cannot invade unless there is also haploid selection (Figures \ref{fig:SexAntagTighter} and \ref{fig:SexAntagTighterMaleDrive}).
-%Secondly, with haploid selection, overdominance ($w_{aa}^\Hermaphrodite<w_{Aa}^\Hermaphrodite$ \& $w_{AA}^\Hermaphrodite<w_{Aa}^\Hermaphrodite$) is not required for neo-W-$a$ haplotypes to spread ($\lambda_{ma}>1$) (Figures \ref{fig:regionMaleDrive}-\ref{fig:regionFemaleGS}).
-%Haploid selection and overdominance allow unlinked neo-W alleles to invade even when there is tight linkage between the ancestral SDR and the selected locus (Figure \ref{fig:loose_invades_tight}).
-%Finally, haploid selection can maintain a polymorphism in the face of directional selection in male and female diploids (ploidally-antagonistic selection). 
-%When selection is ploidally-antagonistic, neo-W alleles often spread, for at least some values of $R$ (Figure \ref{fig:regionPloidAntag}).
-
-%As discussed above, male haploid selection alters the sex ratio and the alleles carried by male gametes that female gametes pair with. 
-%Male haploid selection in favour of the $a$ allele ($\alpha_{\Delta}^\male<0$, $w_{A}^\male<w_{a}^\male$) generates male-biased sex ratios at equilibria (A) and (B), where Y-$a$ is fixed ($\hat{p}_{Y}^\male=0$).
-%Male-biased sex ratios facilitate the spread of neo-W-$A$ and neo-W-$a$ haplotypes (increasing $\lambda_{WA}$ and $\lambda_{Wa}$). 
-%Panels A-C in Figures \ref{fig:regionMaleDrive} and \ref{fig:regionMaleGS} show that neo-W haplotypes tend to spread for a wider range of parameters when sex ratios are male biased, compared to Figure \ref{fig:regionplots} without haploid selection.
-%By contrast, male haploid selection in favour of the $A$ allele generates female-biased sex ratios and reduces $\lambda_{WA}$ and $\lambda_{Wa}$, as demonstrated by panels D-F in Figures \ref{fig:regionMaleDrive} and \ref{fig:regionMaleGS}.
-
-%Female haploid selection generates direct selection on the neo-W-$A$ and neo-W-$a$ haplotypes as they spread in females. 
-%Thus, female haploid selection in favour of the $a$ allele tends to increase $\lambda_{Wa}$ and decrease $\lambda_{WA}$, as shown by panels A-C in Figures \ref{fig:regionFemaleDrive} and \ref{fig:regionFemaleGS}.
-%Conversely, female haploid selection in favour of the $A$ allele increases $\lambda_{WA}$ and decreases $\lambda_{Wa}$, see panels D-F in Figures \ref{fig:regionFemaleDrive} and \ref{fig:regionFemaleGS}.
-
-%Without haploid selection this reduces to
-%\begin{subequations}
-%\begin{align}
-%\lambda_{mA}&= \frac{a}{b} \left[w_{AA}^\female w_{Aa}^\male \phi / 2 + w_{Aa}^\female \frac{c}{d}\right]  \\
-%\lambda_{ma}&= \frac{a}{b} \left[w_{Aa}^\female w_{Aa}^\male \phi / 2 +  w_{aa}^\female \frac{c}{d}\right] \\
-%\chi_{mA}&= \frac{a}{b} R \left[ w_{Aa}^\female \frac{c}{d} \right] \\ 
-%\chi_{ma}&= \frac{a}{b} R \left[ w_{Aa}^\female w_{Aa}^\male \phi / 2 \right] 
-%\end{align}
-%\end{subequations}
-
-%These simplify considerably when there is no haploid selection:
-%
-%\begin{subequations}
-%\begin{align}
-%\lambda_{mA}&= \frac{(\phi + \psi)[(w_{AA}^\female + w_{Aa}^\female ) w_{Aa}^\male \phi + 2 w_{Aa}^\female w_{AA}^\male \psi ]}{2 (w_{AA}^\female w_{Aa}^\male \phi^2 + \psi(w_{Aa}^\female(w_{AA}^\male + w_{Aa}^\male)\phi + w_{aa}^\female w_{AA}^\male \psi)}\\
-%\lambda_{ma}&=  \frac{(\phi + \psi)[(w_{aa}^\female + w_{Aa}^\female ) w_{Aa}^\male \phi + 2 w_{aa}^\female w_{AA}^\male \psi ]}{2 (w_{AA}^\female w_{Aa}^\male \phi^2 + \psi(w_{Aa}^\female(w_{AA}^\male + w_{Aa}^\male)\phi + w_{aa}^\female w_{AA}^\male \psi)}\\
-%\chi_{mA}&= R \frac{(\phi + \psi) w_{Aa}^\female w_{AA}^\male}{2 (w_{AA}^\female w_{Aa}^\male \phi^2 + \psi(w_{Aa}^\female(w_{AA}^\male + w_{Aa}^\male)\phi + w_{aa}^\female w_{AA}^\male \psi)} \\ 
-%\chi_{ma}&= R \frac{(\phi + \psi) w_{Aa}^\female w_{Aa}^\male}{2 (w_{AA}^\female w_{Aa}^\male \phi^2 + \psi(w_{Aa}^\female(w_{AA}^\male + w_{Aa}^\male)\phi + w_{aa}^\female w_{AA}^\male \psi)}\\
-%\end{align}
-%\end{subequations}
-%
-%\begin{subequations}
-%\begin{align}
-%\lambda_{mA}&= [( w_{AA}^\female + w_{Aa}^\female ) w_{Aa}^\male \phi + 2 w_{Aa}^\female w_{AA}^\male \psi] a \\
-%\lambda_{ma}&=  [(w_{aa}^\female + w_{Aa}^\female ) w_{Aa}^\male \phi + 2 w_{aa}^\female w_{AA}^\male \psi ] a\\
-%\chi_{mA}&= R w_{Aa}^\female (w_{Aa}^\male \phi + 2 w_{AA}^\male \psi) c \\ 
-%\chi_{ma}&= R w_{Aa}^\female w_{Aa}^\male \phi c \\
-%\end{align}
-%\end{subequations}
-%\noindent
-%where 
-%$c = \frac{\phi + \psi}{2 [w_{AA}^\female w_{Aa}^\male \phi^2 + \psi(w_{Aa}^\female(w_{AA}^\male + w_{Aa}^\male)\phi + w_{aa}^\female w_{AA}^\male \psi]}$ and $\phi$ and $\psi$ are evaluated with $\alpha^{\Hermaphrodite}=1/2$ and $w_a^\Hermaphrodite=w_A^\Hermaphrodite=1$.
-
-%With $R=0$ the two eigenvalues are $\lambda_{mA}$ and $\lambda_{ma}$.
-%The neo-W can then invade on the $A$ background when $\lambda_{mA}>1$ and the neo-W can invade on the $a$ background when $\lambda_{ma}>1$.
-%Even in this case it is difficult to see from equation \ref{Ainvasion} when the neo-W will invade.
-%Below we discuss why $\lambda_{mA}$ and $\lambda_{ma}$ might be larger than one and confirm the logic numerically.
-%
-%
-%For simplicity, consider the case of no haploid selection.
-%A polymorphism at the $\mathbf{A}$ locus then requires sexually-antagonistic selection \citep{vanDoorn:2007eu}.
-%Given that $a$ is fixed on the Y, one can consider the $a$ allele `male beneficial' and the $A$ allele to be `female beneficial'. 
-%Because X chromosomes spend some time in males the frequency of $A$ on the X can reach an intermediate equilibrium (equilibrium A).
-%
-%We can therefore reason that when a neo-W invades equilibrium (A), it is likely to spread on the $A$ background as W chromosomes are always in females.
-%The neo-W can outcompete the ancestral, `comprimising' X because it can specialize on females by fixing the `female beneficial' allele.  
-%We call this the `sex-specialist hypothesis'.
-%This hypothesis should only work when the benefit of specializing outweighs the cost of bringing Y chromosomes into females (the neo-W is epistatically dominant over the X/Y locus).
-%
-%One could also reason that, when the neo-W spreads, it does so precisely because it brings Y chromosomes, and their associated alleles, into females, something the X cannot do.
-%However, this requires a somewhat particular (perhaps `perverse') equilibrium, where XX females do worse than XY females despite associations on the X and Y being built up by selection.
-%One example of such a perverse equilibrium is produced by overdominance in both sexes.
-%Overdominance in females selects for an allele frequency of 0.5 on the X ($A$ and $a$ equally frequent, maximizing the number of heterozygotes). 
-%However, given that $a$ is fixed on the Y, overdominance in males selects for the X to become more associated with the $A$. 
-%Thus, a compromising equilibrium is reached on the X chromosome and females fitness suffers due to the overproduction of $AA$ homozygotes.
-%This sets up a scenario in which a neo-W can invade on the $a$ background, despite the fact that $a$ is fixed on the Y and in that sense `male beneficial'.
-%We call this the `perverse hypothesis'.
-%
-%Figure \ref{fig:Region_Plots} shows where the sex-specialist (red) and perverse (blue) hypotheses are valid.
-%The left panel demonstrates that both hypotheses can be simultaneously valid with overdominance in both sexes and sex differences in selection, which overlaps the parameter region where there is selection for increased recombination between the sex chromosomes \citep[compare with figure 2a in][]{Otto2014}.
-%The right panel shows that the perverse hypothesis is no longer valid when selection is exactly the same in both sexes, despite the fact that there is selection for increased recombination between the sex chromosomes with sufficiently strong overdominance \citep[compare with figure 3 in][]{Otto2014}.
-%
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%Sex-specialist vs perverse hypotheses
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[!h]
-%\centering
-%\includegraphics[width=0.45\linewidth]{regionplot_2a}
-%\includegraphics[width=0.45\linewidth]{regionplot_3}\\
-%\caption{
-%Numerical exploration of where sex-specialist (red) and perverse (blue) hypotheses are valid, i.e., where an internally stable resident equilibrium can be invaded by a neo-W that is perfectly linked with the allele not fixed on the Y (red) or the allele that is fixed on the Y (blue).
-%\textbf{(Left)}
-%The perverse equilibrium is only valid with overdominance while the sex-specialist hypothesis is valid over the entire range shown.
-%Both hypotheses are simultaneously valid over much of the parameter space where increased recombination between the sex chromosomes is selected \citep[][figure 2a]{Otto2014}.
-%\textbf{(Right)}
-%Only the sex-specialist hypothesis is valid with no sex-differences in selection, despite selection for increased recombination between the sex-chromosomes with strong overdominance \citep[][figure 3]{Otto2014}.
-%Parameters: $w_{Aa}^\Hermaphrodite = 1$, $w_a^\Hermaphrodite = w_A^\Hermaphrodite = 1$, $\alpha^\Hermaphrodite = 1/2$, $r=R=0$, and in left panel $w_{aa}^\female = w_{AA}^\female = 0.6$.
-%}
-%\label{fig:Region_Plots}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section*{Supplementary Figures}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Both neo-W haplotypes can spread, in the absence of haploid selection, when there is overdominance
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-\centerline{\includegraphics[width=\linewidth]{PositionPlot_Overdominance}}
-\caption{
-Neo-W alleles can spread when loci under diploid selection are tightly linked to the ancestral sex determining locus ($r\approx0$). 
+{\bf Recursion equations and complete model description.}
+
+\paragraph*{S2 Appendix.}
+\label{app:eq_stab}
+{\bf Equilibria and stability conditions when $M$ allele is fixed. }
+
+\paragraph*{S3 Appendix.}
+\label{app:inv_cond}
+{\bf Invasion conditions for the $m$ allele.}
+
+% Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
+\paragraph*{S1 Fig.}
+\label{fig:positionOverdominance}
+{\bf Neo-W alleles can spread when loci under diploid selection are tightly linked to the ancestral sex determining locus ($r\approx0$). } 
 In panels A and B, the $a$ allele is favoured in females ($w_{aa}^\female=1.05$, $w_{Aa}^\Hermaphrodite=1$, $w_{AA}^\female=0.85$) and selection in males is overdominant ($w_{aa}^\male=w_{AA}^\male=0.75$).
@@
 However, when linkage is tight (panels B and D and when the selected locus is near the SDRs in all panels), this weak selection prediction can break down.
+
+\paragraph*{S2 Fig.}
+\label{fig:temporalOverdominance}
+{\bf Following invasion by a neo-W allele, there can be a complete transition to a new sex-determination system, maintenance of polymorphism at both ancestral-XY and neo-ZW sex determining regions, or loss of the new sex-determining allele.
 }
-\label{fig:positionOverdominance}
-\end{figure}
-
-\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Both neo-W haplotypes can spread, in the absence of haploid selection, when there is overdominance
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-\centerline{\includegraphics[width=\linewidth]{Temporal_Overdominance}}
-\caption{
-Following invasion by a neo-W allele, there can be a complete transition to a new sex-determination system, maintenance of polymorphism at both ancestral-XY and neo-ZW sex determining regions, or loss of the new sex-determining allele.
 Here we plot the frequency of the neo-W allele among female gametes; as the neo-W reaches frequency $0.5$, polymorphism at the ancestral XY locus is lost with Y becoming fixed such that sex is determined only be the ZW allele carried by a female gamete.
@@
 In B, this leads to loss of the neo-W and the system goes to an equilibrium with X-$a$ and Y-$A$ haplotypes fixed (equilibrium $A'$), such that all females have the high fitness genotype $aa$ and all males are $Aa$.
-For the parameters in B, neo-W alleles have negative invasion fitness when the Y-$A$ haplotype is ancestrally more common than Y-$a$ (see blue lines in Figure \ref{fig:positionOverdominance}A and  \ref{fig:positionOverdominance}B near the ancestral SDR).
-In contrast, the neo-W is not lost in panel D as it is favoured near $r\approx0$ (see blue lines in Figure \ref{fig:positionOverdominance}C and  \ref{fig:positionOverdominance}D near the ancestral SDR).
-Fitness parameters are the same as in Figure \ref{fig:positionOverdominance}; in panels A and B the $a$ allele is favoured in females ($w_{aa}^\female=1.05$, $w_{Aa}^\Hermaphrodite=1$, $w_{AA}^\female=0.85$) while there is overdominance in males ($w_{aa}^\male=w_{AA}^\male=0.75$) and in panels C and D, there is overdominance in both sexes ($w_{aa}^\female=w_{AA}^\female=0.6$, $w_{aa}^\male=0.5$, $w_{AA}^\male=0.7$, $w_{Aa}^\Hermaphrodite=1$).
+For the parameters in B, neo-W alleles have negative invasion fitness when the Y-$A$ haplotype is ancestrally more common than Y-$a$ (see blue lines in Figure \nameref{fig:positionOverdominance}A and  \nameref{fig:positionOverdominance}B near the ancestral SDR).
+In contrast, the neo-W is not lost in panel D as it is favoured near $r\approx0$ (see blue lines in Figure \nameref{fig:positionOverdominance}C and  \nameref{fig:positionOverdominance}D near the ancestral SDR).
+Fitness parameters are the same as in Figure \nameref{fig:positionOverdominance}; in panels A and B the $a$ allele is favoured in females ($w_{aa}^\female=1.05$, $w_{Aa}^\Hermaphrodite=1$, $w_{AA}^\female=0.85$) while there is overdominance in males ($w_{aa}^\male=w_{AA}^\male=0.75$) and in panels C and D, there is overdominance in both sexes ($w_{aa}^\female=w_{AA}^\female=0.6$, $w_{aa}^\male=0.5$, $w_{AA}^\male=0.7$, $w_{Aa}^\Hermaphrodite=1$).
 These parameters are marked by a dagger in Figure \ref{fig:regionplots}. 
 Here, there is no haploid selection $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
-}
-\label{fig:temporalOverdominance}
-\end{figure}
-
-\begin{figure}[!h]
-\centering
-\centerline{\includegraphics[width=1.5\linewidth]{PositionPlot_SexAntagTighter_MaleDrive}}
-\caption{
-When there is sexually-antagonistic selection and haploid selection, a neo-W may invade for any $R$.
+
+\paragraph*{S3 Fig.}
+\label{fig:SexAntagTighterMaleDrive}
+{\bf  When there is sexually-antagonistic selection and haploid selection, a neo-W may invade for any $R$.}
 Panel A shows that the invasion fitness of a neo-W is positive where linkage is tight, even when $r<R$ (unshaded region).
@@
 The diploid selection parameters used in this plot are the same as in Figure \ref{fig:SexAntagTighter}. 
-There is also meiotic drive in males favouring $a$ ($\alpha_{\Delta}^\male=-0.08$), this full set of parameters is marked by an asterisk in Figure \ref{fig:regionMaleDrive}A.
-When $R=0.5$ (green curve), the neo-W does not reach fixation and X,Y,Z, and W alleles are all maintained in the population, see Figure \ref{fig:freqAll}C.
-}
-\label{fig:SexAntagTighterMaleDrive}
-\end{figure}
-
-\begin{figure}[!h]
-\centering
-\centerline{\includegraphics[width=\linewidth]{Region_Plot_combined_MaleDrive}}
-\caption{
-Meiotic drive in males affects whether neo-W-$A$ and neo-W-$a$ haplotypes spread when the ancestral-XY locus is tightly linked to a locus under selection ($r=0$). 
+There is also meiotic drive in males favouring $a$ ($\alpha_{\Delta}^\male=-0.08$), this full set of parameters is marked by an asterisk in Figure \nameref{fig:regionMaleDrive}A.
+When $R=0.5$ (green curve), the neo-W does not reach fixation and X,Y,Z, and W alleles are all maintained in the population, see Figure \nameref{fig:freqAll}C.
+
+\paragraph*{S4 Fig.}
+\label{fig:regionMaleDrive}
+{\bf Meiotic drive in males affects whether neo-W-$A$ and neo-W-$a$ haplotypes spread when the ancestral-XY locus is tightly linked to a locus under selection ($r=0$).}
 We vary the fitness of male homozygotes relative to heterozygotes ($w_{Aa}^\Hermaphrodite=1$) and only consider stable equilibria at which both \textbf{A} locus allele are maintained and the $a$ allele is initially fixed on the Y, region outlined.
@@
 We consider three forms of selection in females: directional selection in favour of the $A$ allele (panels A and D, $w_{aa}^\female=0.85$, $w_{AA}^\female=1.05$), direction selection in favour of the $a$ allele (panels B and E, $w_{aa}^\female=1.05$, $w_{AA}^\female=0.85$), and overdominance (panels C and F, $w_{aa}^\female=w_{AA}^\female=0.6$).
-%\textcolor{red}{Panel F mislabelled, should have $\lambda_{Wa}>1$ \& $\lambda_{WA}<1$ as the upper label that has the line.}
-}
-\label{fig:regionMaleDrive}
-\end{figure}
-
-\newpage
-\begin{figure}[!h]
-\centering
-\centerline{\includegraphics[width=\linewidth]{Region_Plot_combined_MaleGS}}
-\caption{
-Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is male gametic competition at a locus that is tightly linked to the ancestral-XY locus.
-Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in Figure \ref{fig:regionMaleDrive}. 
+
+\paragraph*{S5 Fig.}
+\label{fig:regionMaleGS}
+{\bf Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is male gametic competition at a locus that is tightly linked to the ancestral-XY locus.}
+Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in Figure \nameref{fig:regionMaleDrive}. 
 The $a$ allele is favoured during male gametic competition in Panels A-C ($w_{a}^\male=1.16$, $w_{A}^\male=1$), which creates male biased sex ratios and increases $\lambda_{WA}$ and $\lambda_{Wa}$. 
 On the other hand, the $A$ allele is favoured during male gametic competition in Panels D-F ($w_{a}^\male=1$, $w_{A}^\male=1.16$) and $\lambda_{WA}$ and $\lambda_{Wa}$ tend to be reduced. 
-Compared to the meiotic drive parameters in Figure \ref{fig:regionMaleDrive}, the effect of these male gametic competition parameters on the sex ratio is smaller. 
-For example, in Figure \ref{fig:regionMaleDrive}A-C, the ancestral sex ratio is $\alpha^\male=0.58$ at equilibrium (B) and in panels A-C of this plot, the ancestral sex ratio is $w_{a}^\male/(w_{A}^\male+w_{a}^\male)=0.537$ at equilibrium (B).
-}
-\label{fig:regionMaleGS}
-\end{figure}
-
-\begin{figure}[!h]
-\centering
-\centerline{\includegraphics[width=\linewidth]{Region_Plot_combined_FemaleDrive}}
-\caption{
-Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is female meiotic drive at a locus that is tightly linked to the ancestral-XY locus.
-Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in Figure \ref{fig:regionMaleDrive} and \ref{fig:regionMaleGS}. 
+Compared to the meiotic drive parameters in Figure \nameref{fig:regionMaleDrive}, the effect of these male gametic competition parameters on the sex ratio is smaller. 
+For example, in Figure \nameref{fig:regionMaleDrive}A-C, the ancestral sex ratio is $\alpha^\male=0.58$ at equilibrium (B) and in panels A-C of this plot, the ancestral sex ratio is $w_{a}^\male/(w_{A}^\male+w_{a}^\male)=0.537$ at equilibrium (B).
+
+\paragraph*{S6 Fig.}
+\label{fig:regionFemaleDrive}
+{\bf Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is female meiotic drive at a locus that is tightly linked to the ancestral-XY locus.}
+Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in Figure \nameref{fig:regionMaleDrive} and \nameref{fig:regionMaleGS}. 
 The $a$ allele is favoured by meiotic drive in females in Panels A-C ($\alpha_{\Delta}^\female=-0.16$), which increases $\lambda_{Wa}$ and decreases $\lambda_{WA}$. 
 Female meiotic drive in favour of the $A$ allele (panels D-F, $\alpha_{\Delta}^\female=-0.16$) has the opposite effect.
-}
-\label{fig:regionFemaleDrive}
-\end{figure}
-
-\begin{figure}[!h]
-\centering
-\centerline{\includegraphics[width=\linewidth]{Region_Plot_combined_FemaleGS}}
-\caption{
+
+\paragraph*{S7 Fig.}
+\label{fig:regionFemaleGS}
 Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is female gametic competition at a locus that is tightly linked to the ancestral-XY locus.
-Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in Figure \ref{fig:regionMaleDrive}, \ref{fig:regionMaleGS}, and \ref{fig:regionFemaleDrive}. 
+Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in Figure \nameref{fig:regionMaleDrive}, \nameref{fig:regionMaleGS}, and \nameref{fig:regionFemaleDrive}. 
 The $a$ allele is favoured during female gametic competition in females in Panels A-C ($w_{a}^\female=1.16$, $w_{A}^\female=1$), which increases $\lambda_{Wa}$ and decreases $\lambda_{WA}$. 
 The $A$ allele is favoured during gametic competition in panels D-F ($w_{a}^\female=1$, $w_{A}^\female=1.16$), giving the opposite effect on $\lambda_{Wa}$ and $\lambda_{WA}$.
-}
-\label{fig:regionFemaleGS}
-\end{figure}
-
-\begin{landscape}
-\begin{figure}[!h]
-\centering
-\centerline{
-\includegraphics[width=\linewidth]{All_plot_combined_PloidAntag}
-}
-\caption{
-A-D show when each of the neo-W haplotypes invade an internally stable equilibrium with $a$ fixed on the Y (found by setting $r=0$).
+
+\paragraph*{S8 Fig.}
+\label{fig:regionPloidAntag}
+{\bf A-D show when each of the neo-W haplotypes invade an internally stable equilibrium with $a$ fixed on the Y (found by setting $r=0$).}
 The y-axis shows directional selection in diploids of both sexes, $s^\female=s^\male$, and the x-axes show sex-specific drive, $\alpha_\Delta^\Hermaphrodite$, or haploid competition, $t^\Hermaphrodite$.
@@
 Black $R=1/1000$, Red $R=2/100$, Blue $R=1/10$, Green $R=1/2$.
-%Dashed line in E-H gives ``fixation" of neo-W (all females heterozygous ZW).
-}
-\label{fig:regionPloidAntag}
-\end{figure}
-\end{landscape}
-
-%\begin{landscape}
-\begin{figure}[!h]
-\centering
-\centerline{
-\includegraphics[width=\linewidth]{Freq_plot_combined_PloidAntag}
-}
-\caption{
+
+\paragraph*{S9 Fig.}
+\label{fig:freqAll}
 Fixation of neo-W or maintenance of multiple sex-determining systems. 
@@
 In panel A, selection is ploidally antagonistic with drive in males (parameters as in the green curve in Figure \ref{fig:SexRatioBad}B).
-In panel B, there is overdominance in both sexes and no haploid selection (parameters as in the green curve in Figure \ref{fig:temporalOverdominance}C).
-In panel C, there is sexually-antagonistic selection in diploids with drive in males (parameters as in the green curve in Figure \ref{fig:regionMaleDrive}C).
-%In Panel D there is ploidally-antagonistic selection with haploid competition in males (parameters as in the green curve of Figure \ref{fig:regionPloidAntag}F).
+In panel B, there is overdominance in both sexes and no haploid selection (parameters as in the green curve in Figure \nameref{fig:temporalOverdominance}C).
+In panel C, there is sexually-antagonistic selection in diploids with drive in males (parameters as in the green curve in Figure \nameref{fig:regionMaleDrive}C).
 In all cases, the initial equilibrium frequency has $a$ near fixation on the Y.
-}
-\label{fig:freqAll}
-\end{figure}
-%\end{landscape}
-
-\begin{figure}[!h]
-\centering
-\centerline{
-\includegraphics[width=\linewidth]{neoW_invades_tight_loose}
-}
-\caption{
-An unlinked neo-W can invade a perfectly linked system with overdominance or haploid selection.
-Here overdominance leads to a polymorphic sex-determining system.
-Before invasion the population is at equilibrium B.
-Parameters:
-}
-\label{fig:loose_invades_tight}
-\end{figure}
-
-%\begin{figure}[!h]
-%\centering
-%\centerline{
-%\includegraphics[width=\linewidth]{Sallys_R_plot.pdf}
-%}
-%\caption{
-%\textcolor{blue}{is this the one?}
-%}
-%\label{fig:lambda_R}
-%\end{figure}
-
-%\newpage
-%\textcolor{red}{
-%Add Sally's figure showing lambda for small r near equil A versus near equil B.
-Add references to this figure to appendix where we discuss whether lambdas can be greater than 1 with sexually antagonistic selection.}
-%\textcolor{blue}{not sure which one you are talking about, but see Figure \ref{fig:lambda_R} }
-%\textcolor{red}{Let's remove this for now.}
-
-%\textcolor{red}{
-%Perhaps it would also be useful to add an 8 panel figure that features ploidally antagonistic selection.
-For each type of haploid selection (gametic competition/ meiotic drive in males/females), give a regionplot where $h^\male=h^\female$, e.g., $h^\male=h^\female=0.75$ (or perhaps the value of $h$ we use in the regionplots we have, in which $w_{aa}=0.85$, $w_{Aa}=1$, $w_{AA}=1.05$).
-%Matt made a figure like this before but both Y$a$ and Y$A$ equilibria were plotted and there was no outline showing where the Y$a$ equilibrium is stable (as in Figure \ref{fig:regionplots}).
-In Matts plot the axes were $s^\Hermaphrodite$ and $\alpha_{\Delta}^\Hermaphrodite$.
-%Add an asterisk to each region plot and show invasion in another panel, using those parameters and various $R$ (e.g., in the stye of \ref{fig:temporalOverdominance}). 
-%In an email, Sally has an example of ploidally-antagonistic selection where the neo-W fixes and $R=1/2$. This would cover that case and more. }
-%\textcolor{blue}{made an attempt (Figure \ref{fig:regionPloidAntag})}
-
-%\textcolor{red}{
-%We could also give versions of Figure \ref{fig:regionplots} where there is also haploid selection of various types.
-%Haploid selection can favour $A$ or $a$, so this would involve 4x 6-panel figures.
-Started looking at this in Figure \ref{fig:regionMaleGS} and Figure \ref{fig:regionMaleDrive}, add female haploid selection.
-%Try to integrate into the discussion of haploid selection? e.g., male haploid selection ones generally show effect of sex ratio, increasing both lambdas when female biased (top rows).}
-%\textcolor{blue}{
-%these figures are now done (\ref{fig:regionMaleDrive}-\ref{fig:regionFemaleGS}) (ensuring frequencies between 0 and 1), but yet to discuss in text.}
-
-%\textcolor{red}{
-%Perhaps, for one set of parameters, we should plot the dynamics of all the different alleles.
-E.g., we could use the same parameters used in \ref{fig:SexRatioBad}.
-The main purpose would be to show what happens to the ancestral SDR during turnover.
-%We could also show an example where XY and ZW sex determining systems are both polymorphic and stable (e.g., using one of the curves in Figure \ref{fig:temporalOverdominance} and the green curve in Figure \ref{fig:SexAntagTighterMaleDrive}).
-%I think there are also examples with looser sex linkage and pollen competition that lead to a mixed sex-determination system.
-We should probably have a short section in the appendix discussing this.
-}
-%\textcolor{blue}{made an attempt with Figure \ref{fig:freqAll}, but yet to discuss in text}
+
+\section*{Acknowledgments}
+Cras egestas velit mauris, eu mollis turpis pellentesque sit amet.
+Interdum et malesuada fames ac ante ipsum primis in faucibus.
+Nam id pretium nisi.
+Sed ac quam id nisi malesuada congue.
+Sed interdum aliquet augue, at pellentesque quam rhoncus vitae.
+
+\nolinenumbers
+
+% Either type in your references using
+% \begin{thebibliography}{}
+% \bibitem{}
+% Text
+% \end{thebibliography}
+%
+% or
+%
+% Compile your BiBTeX database using our plos2015.bst
+% style file and paste the contents of your .bbl file
+% here. See http://journals.plos.org/plosone/s/latex for 
+% step-by-step instructions.
+% 
+\bibliography{sex_chromosomes.bib}
 

### 2018-01-19 LaTeX/Turnover_plos.tex
PloS style edits complete. Sally edits to Appendix and References

@@
 % DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
-% - Figures should be uploaded separately from your manuscript file. 
-% - Figures generated using LaTeX should be extracted and removed from the PDF before submission. 
-% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
+% - Figs should be uploaded separately from your manuscript file. 
+% - Figs generated using LaTeX should be extracted and removed from the PDF before submission. 
+% - Figs containing multiple panels/subfigures must be combined into one image file before submission.
 % For figure citations, please use "Fig" instead of "Figure".
@@
 
-% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
+% Bold the 'Fig #' in the caption and separate it from the title/caption with a period
 % Captions will be left justified
@@
 \bigskip
-\textbf{1} UCL Genetics Institue, Department of Genetics, Evolution and Environment, University Collect London, Gower Street, London WC1E 6BT 
+\textbf{1} UCL Genetics Institute, Department of Genetics, Evolution and Environment, University College London, Gower Street, London WC1E 6BT 
 \\
@@
 % Please keep the abstract below 300 words
+%currently 312 words
 \section*{Abstract}
@@
 % Author Summary not valid for PLOS ONE submissions.   
+%currently 193 words
 \section*{Author summary}
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Curabitur eget porta erat.
-Morbi consectetur est vel gravida pretium.
-Suspendisse ut dui eu ante cursus gravida non sed sem.
-Nullam sapien tellus, commodo id velit id, eleifend volutpat quam.
-Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus.
-Nunc pellentesque pretium diam, quis maximus dolor faucibus id.
-Nunc convallis sodales ante, ut ullamcorper est egestas vitae.
-Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.
-%Therefore, our models radically alter our understanding of when and why new sex determination system can evolve. 
-%Therefore, our models cause us to update the prevailing understanding about selective forces that can drive transitions between sex determination systems.
+Accumulating evidence indicates that systems of sex determination are strikingly diverse and labile in many clades. 
+This poses the question: what drives transitions between sex determination systems? 
+Here, we use models to derive conditions under which new sex determination systems spread. 
+Prevailing views suggest that new sex determination systems are favoured when they equalize the sex ratio and/or when they are more closely linked to genes that experience differential selection in males and females.
+Our models include selection upon haploid genotypes (meiotic drive or gametic competition), which both causes sex ratio biases and occurs differently in males and females. 
+Surprisingly, we find that neither force (sex ratio selection nor associations with genes that have sex-specific effects) dominates the spread of new sex determination systems alone. 
+Even more unexpectedly, we find that new sex-determining alleles do not necessarily have to arise in closer linkage with genes that are differentially selected in males and females. 
+Therefore, our models predict loci in unexpected genomic locations and/or experiencing various types of selection (including haploid selection) can now be implicated as drivers of transitions between sex determination systems.
 
@@
 \externaldocument{S1_Appendix.tex}
-%\externaldocument{S2_Appendix.tex}
+\externaldocument{S2_Appendix.tex}
 \externaldocument{S3_Appendix.tex}
@@
 %genetic system
-We consider transitions between ancestral and novel sex-determining systems using a three-locus model, each locus having two alleles (Figure \ref{fig:model_outline}). 
+We consider transitions between ancestral and novel sex-determining systems using a three-locus model, each locus having two alleles (Fig \ref{fig:model_outline}). 
 Locus \textbf{X} is the ancestral sex-determining region, with alleles $X$ and $Y$ (or $Z$ and $W$).
@@
 In each generation, we census the genotype frequencies in male and female gametes/gametophytes (hereafter gametes) before gametic competition. 
-A full description of our model, including recursion equations, is given in the Appendix. 
+A full description of our model, including recursion equations, is given in \nameref{app:recurs}. 
 First, competition occurs among male gametes (sperm/pollen competition) and among female gametes (egg/ovule competition) separately. 
@@
 Recombination (i.e., an odd number of cross-overs) occurs between loci \textbf{X} and \textbf{A} with probability $r$, between loci \textbf{A} and \textbf{M} with probability $R$, and between loci \textbf{X} and \textbf{M} with probability $\rho$.
-Any linear order of the loci can be modelled with appropriate choices of $r$, $R$, and $\rho$ (see Figure \ref{fig:model_outline}A and Table \ref{tab:chisubstitutions}). 
+Any linear order of the loci can be modelled with appropriate choices of $r$, $R$, and $\rho$ (see Fig \ref{fig:model_outline}A and Table \ref{tab:chisubstitutions}). 
 Individuals that are heterozygous at the \textbf{A} locus may experience meiotic drive; a gamete produced by $Aa$ heterozgotes of sex $\Hermaphrodite$ bears allele $A$ with probability $\alpha^\Hermaphrodite$.
@@
 Furthermore, if the $m$ allele is fully epistatically dominant over the ancestral sex-determining system, phenotypes are not affected by the genotype at the ancestral sex-determining region (\textbf{X} locus).
-Thus, the invasion of rare dominant neo-Y or neo-W alleles is determined by the largest eigenvalue that solves the quadratic, $\lambda^2+ b \lambda + c =0$ \textcolor{blue}{(see Appendix for a discussion of other roots - or Sally's proof!)}.
+Thus, the invasion of rare dominant neo-Y or neo-W alleles is determined by the largest eigenvalue that solves the quadratic, $\lambda^2+ b \lambda + c =0$ \textcolor{blue}{(see \nameref{app:inv_cond} for a discussion of other roots - or Sally's proof!)}.
 Here, $b= - (\lambda_{mA} + \lambda_{ma})+(\chi_{mA} + \chi_{ma})$ and $c = (\lambda_{mA}-\chi_{mA}) (\lambda_{ma}-\chi_{ma}) -\chi_{mA} \chi_{ma}$, where $\lambda_{mi}$ is the multiplicative growth rate (which we will call the ``haplotypic growth rate'') of the neo-sex determination allele $m$ on background $i$ without accounting for loss due to recombination, and $\chi_{mi}$ is the rate at which mutant haplotypes on background $i\in\{A,a\}$ recombine onto the other \textbf{A} locus background in heterozygotes (see Table \ref{tab:haplotype_growth}).
@@
    $m$ is a neo-Y ($k=0$) \\ [0.5ex] \hline \noalign{\vskip 1ex}
-  $\lambda_{YA} = \left( 2 \zeta \right)^{-1} \left[\hat{p}_X^\female w_{A}^{\female} w_{A}^{\male} w_{AA}^{\male} + (1-\hat{p}_X^\female) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} (1+\alpha_{\Delta}^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right) $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\lambda_{Ya} = \left( 2 \zeta \right)^{-1} \left[(1-\hat{p}_X^\female) w_{a}^{\female} w_{a}^{\male} w_{aa}^{\male} + \hat{p}_X^\female w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male}(1 - \alpha_{\Delta}^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\chi_{YA} = R \left( 2 \zeta \right)^{-1} \left[ (1-\hat{p}_X^\female) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} (1+\alpha_{\Delta}^{\male}) \right]/  \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right)   $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\chi_{Ya} = R \left( 2 \zeta \right)^{-1} \left[   \hat{p}_X^\female w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male} (1 - \alpha_\Delta^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^\male \right)  $\\ [1ex] \hline
+  $\lambda_{YA} = {\left( 2 \zeta \right)}^{-1} \left[\hat{p}_X^\female w_{A}^{\female} w_{A}^{\male} w_{AA}^{\male} + (1-\hat{p}_X^\female) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} (1+\alpha_{\Delta}^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\male}_{D} \right) $\\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\lambda_{Ya} = {\left( 2 \zeta \right)}^{-1} \left[(1-\hat{p}_X^\female) w_{a}^{\female} w_{a}^{\male} w_{aa}^{\male} + \hat{p}_X^\female w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male}(1 - \alpha_{\Delta}^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\male}_{D} \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\chi_{YA} = R {\left( 2 \zeta \right)}^{-1} \left[ (1-\hat{p}_X^\female) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} (1+\alpha_{\Delta}^{\male}) \right]/  \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\male}_{D} \right)   $\\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\chi_{Ya} = R {\left( 2 \zeta \right)}^{-1} \left[   \hat{p}_X^\female w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male} (1 - \alpha_\Delta^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\male}_{D} \right)  $\\ [1ex] \hline
   \noalign{\vskip 0.5ex}
   $m$ is a neo-W ($k=1$) \\ [0.5ex] \hline \noalign{\vskip 1ex}
-  $\lambda_{WA} = \left[ 2 (1 - \zeta) \right]^{-1} \left[ \bar{p}^{\male} w_{A}^{\male} w_{A}^{\female} w_{AA}^{\female}+(1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female}(1+\alpha_{\Delta}^{\female})\right]/ \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\lambda_{Wa} = \left[ 2 (1 - \zeta) \right]^{-1} \left[ (1-\bar{p}^{\male}) w_{a}^{\male} w_{a}^{\female} w_{aa}^{\female}+\bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female}(1-\alpha_{\Delta}^{\female})\right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\chi_{WA} = R \left[ 2 (1 - \zeta) \right]^{-1} \left[ (1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female} (1+\alpha_{\Delta}^{\female}) \right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \right)  $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\chi_{Wa} = R \left[ 2 (1 - \zeta) \right]^{-1} \left[ \bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female} (1-\alpha_{\Delta}^{\female}) \right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^\female \right) $ \\ [1ex]
+  $\lambda_{WA} = {\left[ 2 (1 - \zeta) \right]}^{-1} \left[ \bar{p}^{\male} w_{A}^{\male} w_{A}^{\female} w_{AA}^{\female}+(1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female}(1+\alpha_{\Delta}^{\female})\right]/ \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\female}_{D} \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\lambda_{Wa} = {\left[ 2 (1 - \zeta) \right]}^{-1} \left[ (1-\bar{p}^{\male}) w_{a}^{\male} w_{a}^{\female} w_{aa}^{\female}+\bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female}(1-\alpha_{\Delta}^{\female})\right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\female}_{D} \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\chi_{WA} = R {\left[ 2 (1 - \zeta) \right]}^{-1} \left[ (1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female} (1+\alpha_{\Delta}^{\female}) \right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\female}_{D} \right)  $\\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\chi_{Wa} = R {\left[ 2 (1 - \zeta) \right]}^{-1} \left[ \bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female} (1-\alpha_{\Delta}^{\female}) \right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\female}_{D} \right) $ \\ [1ex]
   \hline \hline 
@@
 $\zeta$ is the zygotic sex ratio (fraction male).
-$\bar{w}^\Hermaphrodite$ is the mean fitness of diploids of sex $\Hermaphrodite$, see Table \ref{tab:meanfitnesses}.
+$\bar{w}^{\Hermaphrodite}_{D}$ is the mean fitness of diploids of sex $\Hermaphrodite$, see Table \ref{tab:meanfitnesses}.
 $\bar{w}_H^\Hermaphrodite$ is the mean fitness of haploids from sex $\Hermaphrodite$, see Table \ref{tab:meanfitnesses}.
@@
 The leading eigenvalue solves $f(\lambda)=\lambda^2+b\lambda+c=0$ and the Perron-Frobenius theorem guarantees that the leading eigenvalue is positive, unique, and real.  
-Since $f(\lambda_{mA})$ and $f(\lambda_{ma})$ are of opposite signs, the leading eigenvalue must fall between these two quantities and is the larger of them when $R = 0$ (see supplementary Mathematica file).
+Since $f(\lambda_{mA})$ and $f(\lambda_{ma})$ are of opposite signs, the leading eigenvalue must fall between these two quantities and is the larger of them when $R = 0$ (see \nameref{file:Mathematica}).
 Consequently, if both $\lambda_{mA}$ and $\lambda_{ma}$ are greater than one, then the leading eigenvalue will always be greater than one, regardless of the linkage between the neo-sex determination factor and the selected locus ($R$).
@@
 Second, invasion by a neo-Y (neo-W) allele does not directly depend on the fitness of female (male) diploids. %(for a given set of equilibrium allele frequencies).
-This is because a dominant neo-Y (neo-W) is always found in males (females), and therefore the frequency of the neo-Y (neo-W) allele, $m$, only changes in males (females), Figure \ref{fig:model_outline}C,D.
+This is because a dominant neo-Y (neo-W) is always found in males (females), and therefore the frequency of the neo-Y (neo-W) allele, $m$, only changes in males (females), Fig \ref{fig:model_outline}C,D.
 Finally, invasions by a neo-Y and a neo-W are qualitatively different.
-This is because a gamete with the neo-Y always pairs with a female gamete containing an X, and develop into males, Figure \ref{fig:model_outline}C.
-By contrast, a gamete with a neo-W can pair with an X or Y male gamete, developing into a female, Figure \ref{fig:model_outline}D.
+This is because a gamete with the neo-Y always pairs with a female gamete containing an X, and develop into males, Fig \ref{fig:model_outline}C.
+By contrast, a gamete with a neo-W can pair with an X or Y male gamete, developing into a female, Fig \ref{fig:model_outline}D.
 Consequently, neo-W bearing females obtain a differerent frequency of $A$ alleles from mating (when $\hat{p}_X^\male \neq \hat{p}_Y^\male$) compared to ancestral ($MM$) females.
@@
 
-The ancestral equilibrium allele frequencies and their stability conditions are given in the appendix.
+The ancestral equilibrium allele frequencies and their stability conditions are given in \nameref{app:eq_stab}. 
 When there is complete linkage between the ancestral sex-determining region and the \textbf{A} locus ($r=0$), either the $A$ allele or the $a$ allele must be fixed on the Y. 
@@
 
-We find that a neo-Y can never invade an ancestral XY system that already has tight linkage with the locus under selection ($r=0$, for details see supplementary \textit{Mathematica} file). 
+We find that a neo-Y can never invade an ancestral XY system that already has tight linkage with the locus under selection ($r=0$, for details see \nameref{file:Mathematica}). 
 When $R=0$, a neo-Y haplotype with the same allele as the ancestral Y is neutral ($\lambda_{Ya}=1$) and does not change in frequency.
@@
 
-Neo-W alleles, on the other hand, can invade an ancestral XY system under some conditions (the full invasion conditions are given in the appendix; equations \ref{Binvasion} and \ref{Ainvasion}). 
-Counterintuitively, selection on loci within the non-recombining region of the SDR can favour the invasion of a less closely linked neo-W, whatever the form of selection maintaining a polymorphism (sexually-antagonistic selection, overdominance, ploidally-antagonistic selection, or some combination, Figures \ref{fig:SexAntagTighter}, \nameref{fig:temporalOverdominance}, \nameref{fig:regionPloidAntag}, and \nameref{fig:SexAntagTighterMaleDrive}).
+Neo-W alleles, on the other hand, can invade an ancestral XY system under some conditions (the full invasion conditions are given in \nameref{app:inv_cond}; equations \ref{Binvasion} and \ref{Ainvasion}).
+Counterintuitively, selection on loci within the non-recombining region of the SDR can favour the invasion of a less closely linked neo-W, whatever the form of selection maintaining a polymorphism (sexually-antagonistic selection, overdominance, ploidally-antagonistic selection, or some combination, Fig \ref{fig:SexAntagTighter}, \nameref{fig:temporalOverdominance}, \nameref{fig:regionPloidAntag}, and \nameref{fig:SexAntagTighterMaleDrive}).
 The conditions become more restrictive, however, with increasing recombination ($R$) between the new sex determining region and the selected locus.  
-The invasion of completely unlinked neo-W alleles ($R = 1/2$) can occur with overdominance in males or with haploid selection but is not possible with only sexually-antagonistic selection if selection is directional in each diploid sex (see Supplementary \textit{Mathematica} file).
-To develop an intuition for how less closely linked neo-W alleles invade ($R>r$), we first focus on cases where there is no haploid selection and discuss the additional effect of haploid selection in the appendix.
+The invasion of completely unlinked neo-W alleles ($R = 1/2$) can occur with overdominance in males or with haploid selection but is not possible with only sexually-antagonistic selection if selection is directional in each diploid sex (see \nameref{file:Mathematica}).
+To develop an intuition for how less closely linked neo-W alleles invade ($R>r$), we first focus on cases where there is no haploid selection and discuss the additional effect of haploid selection in \nameref{app:inv_cond}.
 
@@
 Fitness parameters are: $w_{AA}^\female = 1.05$, $w_{aa}^\male = 1.2$, $w_{aa}^\female = w_{AA}^\male = 0.85$, $w_{Aa}^\Hermaphrodite = 1$,  $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
-%\textcolor{red}{consider removing panel A, which is repeated in Figure 3.}
+%\textcolor{red}{consider removing panel A, which is repeated in Fig 3.}
 %\textcolor{blue}{probably better to remove from panel 3, eh?}
@@
 Broadly, this is possible because the ancestral X chromosome is sometimes found in males and is therefore unable to perfectly specialise on the `female-beneficial' allele. 
-For example, when the $a$ allele is favoured on the ancestral X in males, a polymorphism of $A$ and $a$ alleles can be maintained on the X despite directional selection in favour of the $A$ allele in females ($s^\female>0$, $0<h^\female<1$), see outlined region in Figure \ref{fig:regionplots}A.
-When the $a$ allele is strongly favoured on X chromosomes in males ($w_{aa}^\male$ sufficiently large relative to $w_{Aa}^\male$), neo-W-$A$ haplotypes can spread ($\lambda_{WA}>1$, see grey region in Figure \ref{fig:regionplots}A) because they produce hgher fitness females ($AA$ or $Aa$ genotypes) and are unleashed from counterselection in males.
+For example, when the $a$ allele is favoured on the ancestral X in males, a polymorphism of $A$ and $a$ alleles can be maintained on the X despite directional selection in favour of the $A$ allele in females ($s^\female>0$, $0<h^\female<1$), see outlined region in Fig \ref{fig:regionplots}A.
+When the $a$ allele is strongly favoured on X chromosomes in males ($w_{aa}^\male$ sufficiently large relative to $w_{Aa}^\male$), neo-W-$A$ haplotypes can spread ($\lambda_{WA}>1$, see grey region in Fig \ref{fig:regionplots}A) because they produce hgher fitness females ($AA$ or $Aa$ genotypes) and are unleashed from counterselection in males.
 
@@
 If $\lambda_{wA}$ or $\lambda_{wa}$ is greater than one, then a rare neo-W can spread for, at least, some values of $R>r$. 
-The parameter values marked with an asterisk correspond to the fitnesses used in Figure \ref{fig:SexAntagTighter}C. 
+The parameter values marked with an asterisk correspond to the fitnesses used in Fig \ref{fig:SexAntagTighter}C. 
 Where both $\lambda_{wA}$ and $\lambda_{wa}$ are greater than one, a neo-W will spread when rare, regardless of linkage with the selected locus (for any $R$). 
-Figure \nameref{fig:positionOverdominance} shows the dynamics using the parameters marked with a dagger. 
+\nameref{fig:positionOverdominance} shows the dynamics using the parameters marked with a dagger. 
 Here, there is no haploid selection $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
@@
 
-When only one neo-W haplotype has a positive growth rate (see Figure \ref{fig:regionplots}), a neo-W can invade as long as equation \eqref{eq:lambdasGen} is satisfied, which may require that the recombination rate, $R$, is small enough.
+When only one neo-W haplotype has a positive growth rate (see Fig \ref{fig:regionplots}), a neo-W can invade as long as equation \eqref{eq:lambdasGen} is satisfied, which may require that the recombination rate, $R$, is small enough.
 Nevertheless, because we assume here that $r$ is small, these results indicate that a more loosely linked sex-determining region ($r<R$) can spread.
-Therefore, tightly sex-linked loci that experience sexually-antagonistic selection can drive trans-GSD transitions in which the neo-SDR is less closely linked to the locus under selection (Figure \ref{fig:SexAntagTighter}).
+Therefore, tightly sex-linked loci that experience sexually-antagonistic selection can drive trans-GSD transitions in which the neo-SDR is less closely linked to the locus under selection (Fig \ref{fig:SexAntagTighter}).
 
@@
 If there is overdominance in males, X-$A$ Y-$a$ males have high fitness and the $A$ allele is favoured by selection on the X in males. 
-Therefore, the X can be polymorphic or even fixed for the $A$ allele despite favouring the $a$ allele during selection in females (e.g., see outlined region in Figure \ref{fig:regionplots}B and~\cite{Lloyd1977,Otto2014}).
-In such cases, neo-W-$a$ haplotypes can spread because they create more $Aa$ and $aa$ females when pairing with an X from males and because they bring Y-$a$ haplotypes into females, where it has higher fitness (Figure \ref{fig:model_outline}D).
-
-In some cases, both W-$A$ and W-$a$ haplotypes can spread, e.g., when $AA$ individuals have low fitness in females yet the $A$ is polymorphic or fixed on the X due to overdominance in males (Figure \ref{fig:regionplots}B and \ref{fig:regionplots}C).
+Therefore, the X can be polymorphic or even fixed for the $A$ allele despite favouring the $a$ allele during selection in females (e.g., see outlined region in Fig \ref{fig:regionplots}B and~\cite{Lloyd1977,Otto2014}).
+In such cases, neo-W-$a$ haplotypes can spread because they create more $Aa$ and $aa$ females when pairing with an X from males and because they bring Y-$a$ haplotypes into females, where it has higher fitness (Fig \ref{fig:model_outline}D).
+
+In some cases, both W-$A$ and W-$a$ haplotypes can spread, e.g., when $AA$ individuals have low fitness in females yet the $A$ is polymorphic or fixed on the X due to overdominance in males (Fig \ref{fig:regionplots}B and \ref{fig:regionplots}C).
 Both neo-W-$A$ and neo-W-$a$ haplotypes then produce fewer unfit $AA$ females.
 This is true for the neo-W-$A$ haplotype because it can pair with a Y-$a$ haplotype and still be female. 
-Wherever both haplotypes have positive growth rates, invasion by a neo-W is expected regardless of its linkage with the selected locus (i.e., even unlinked neo-W alleles can invade, see Figures \nameref{fig:positionOverdominance} and \nameref{fig:temporalOverdominance} for examples).
-
-Assuming that linkage is not tight, van Doorn and Kirkpatrick (2010)~\cite{vanDoorn:2010hu} showed that invasion by a neo-W occurs under the same conditions as `pseudo-fixation' (at pseudo-fixation the neo-W reaches its maximum frequency among eggs, which is 1/2).
-An equivalent analysis is not possible where we assume that linkage is tight. 
-However, numerical simulations with tight linkage demonstrate that the neo-SDR does not necessarily reach pseudo-fixation, leading to the stable maintenance of a mixed sex-determining system, in which X, Y, Z, and W alleles all segregate (e.g., Figure \nameref{fig:freqAll}B,C).
+Wherever both haplotypes have positive growth rates, invasion by a neo-W is expected regardless of its linkage with the selected locus (i.e., for any $R$, see \nameref{fig:positionOverdominance} and \nameref{fig:temporalOverdominance} for examples).
+
+Assuming weak selection, van Doorn and Kirkpatrick~\cite{vanDoorn:2010hu} showed that invasion by a neo-W occurs under the same conditions as `pseudo-fixation' (at pseudo-fixation the neo-W reaches its maximum frequency among eggs, which is 1/2).
+An equivalent analysis is not possible where recombination rates are low. 
+However, numerical simulations demonstrate that the neo-SDR does not necessarily reach pseudo-fixation, leading to the stable maintenance of a mixed sex-determining system, in which X, Y, Z, and W alleles all segregate (e.g., \nameref{fig:freqAll}B,C).
 
@@
 Equation \eqref{eq:lambda_neoY} demonstrates that, under weak selection, a neo-Y will invade an XY system if and only if it is more closely linked to the selected locus than the ancestral sex-determining region (i.e., if $R<r$; note that $V_{A}S_{A}^2$ is strictly positive as long as \textbf{A} is polymorphic).
-This echoes our tight linkage results above where a neo-Y could never invade if $r\approx0$.
+This echoes our $R\approx0$ results above where a neo-Y could never invade if $r\approx0$.
 It is also consistent with the results of \cite{vanDoorn:2007eu}, who considered diploid selection only and also found that cis-GSD transitions (XY to XY or ZW to ZW) can only occur when the neo-sex-determining locus is more closely linked to a locus under sexually-antagonistic selection.
-%Because tighter linkage between the sex-determining region and a selected locus evolves during these transitions, stronger associations between selected alleles and diploid sexes can build up by selection (e.g., between male-beneficial alleles and the male-determining allele, Y).%, increasing diploid mean fitness (Figure \ref{fig:Combination_MeanFit}).
+%Because tighter linkage between the sex-determining region and a selected locus evolves during these transitions, stronger associations between selected alleles and diploid sexes can build up by selection (e.g., between male-beneficial alleles and the male-determining allele, Y).%, increasing diploid mean fitness (Fig \ref{fig:Combination_MeanFit}).
 
@@
 %These transitions are unusual because, when $R>r$, associations that selection has built up between alleles more favourable in one sex and alleles that determine sex will be weakened. 
-%Mean diploid fitness therefore decreases during heterogametic transitions that create looser sex-linkage (Figure \ref{fig:Combination_MeanFit}B,D).
+%Mean diploid fitness therefore decreases during heterogametic transitions that create looser sex-linkage (Fig \ref{fig:Combination_MeanFit}B,D).
 
@@
 The second term in equation \eqref{eq:lambda_neoW} therefore disappears and invasion depends only on the sign of $(r-R)$, as in the case of the neo-Y. 
-Indeed, invasion typically occurs when the neo-W is more closely linked to the selected locus than the ancestral sex-determining region (Figure \ref{fig:Combination_Centimorgans}).
+Indeed, invasion typically occurs when the neo-W is more closely linked to the selected locus than the ancestral sex-determining region (Fig \ref{fig:Combination_Centimorgans}).
 
@@
 {\bf Ploidally-antagonistic selection allows a less tightly linked neo-W to invade.}
-In panel A, male drive ($\alpha^\male_{\Delta} = -1/20$, $t^\Hermaphrodite = \alpha^\female_{\Delta} = 0$) opposes selection in diploids (no sex-differences: $s^\Hermaphrodite = 1/10$, $h^\Hermaphrodite = 7/10$), in which case the neo-sex-determining allele can invade regardless of linkage.
-In panel B, gametic competition in males ($t^\male = -1/10$, $t^\female = \alpha^\Hermaphrodite_{\Delta} = 0$) opposes selection in diploids (sex-differences: $s^\male = 3/20$, $s^\female = 1/20$, $h^\Hermaphrodite = 7/10$), in which case the neo-sex-determining allele can once again invade regardless of linkage.
-We use Haldane's map function (Equation 3 in \cite{Haldane1919}) to convert from map distance (centiMorgans, cM) to the probability of recombination (an odd number of cross-over events).   
+In panel A, male drive ($\alpha^\male_{\Delta} = -1/20$, $t^\Hermaphrodite = \alpha^\female_{\Delta} = 0$) opposes selection in diploids (no sex-differences: $s^\Hermaphrodite = 1/10$, $h^\Hermaphrodite = 7/10$), in which case the neo-sex-determining allele can invade regardless of $R$.
+In panel B, gametic competition in males ($t^\male = -1/10$, $t^\female = \alpha^\Hermaphrodite_{\Delta} = 0$) opposes selection in diploids (sex-differences: $s^\male = 3/20$, $s^\female = 1/20$, $h^\Hermaphrodite = 7/10$), in which case the neo-sex-determining allele can once again invade regardless of $R$.
 }
@@
 In Table \ref{tab:specialcases} we give the conditions where invasion occurs when we further assume that haploid selection only occurs in one sex (e.g., during male meiosis only) and dominance coefficients are equal in the two sexes, $h^\female=h^\male$.
-When there is no gametic competition and meiotic drive is in one sex only, an unlinked neo-W can invade as long as the same allele is favoured during diploid selection in males and females ($s^\female s^\male>0$, see Figure \ref{fig:Combination_Centimorgans}A and Figure \ref{fig:SexRatioBad}B).
+When there is no gametic competition and meiotic drive is in one sex only, an unlinked neo-W can invade as long as the same allele is favoured during diploid selection in males and females ($s^\female s^\male>0$, see Fig \ref{fig:Combination_Centimorgans}A and Fig \ref{fig:SexRatioBad}B).
 %, which is 50\% of the parameter space.
-When there is no meiotic drive and gametic competition occurs in one sex only, an unlinked neo-W can invade as long as the same allele is favoured in male and female diploid selection and there are sex differences in selection of one type (e.g., $s^\female(s^\male-s^\female)>0$, see Figure \ref{fig:Combination_Centimorgans}B).
+When there is no meiotic drive and gametic competition occurs in one sex only, an unlinked neo-W can invade as long as the same allele is favoured in male and female diploid selection and there are sex differences in selection of one type (e.g., $s^\female(s^\male-s^\female)>0$, see Fig \ref{fig:Combination_Centimorgans}B).
 %, which is 25\% of the parameter space.
@@
 In this figure, selection is ploidally antagonistic with haploid selection favouring the $a$ allele during male meiosis.
-In panel A, male drive in an ancestral XY system causes a male bias (see Figure \ref{fig:model_outline}B), allowing a neo-W to invade and replace the ancestral sex-determination system (inset shows neo-W frequency among female gametes), which balances the zygotic sex ratio.
-In panel B, male drive in an ancestral ZW system has no affect on the zygotic sex ratio (see Figure \ref{fig:model_outline}B) yet a neo-Y can invade and replace the ancestral sex-determination system (inset shows neo-Y frequency among male gametes, the ancestral W also goes to fixation during this transition).
-When $R<1/2$, the neo-Y becomes associated with the allele favoured by drive, causing the zygotic sex ratio to become biased, hence the frequency of the neo-Y at pseudo-fixation can be higher than $0.5$ (inset).
+In panel A, male meiotic drive in an ancestral XY system causes a male bias (see Fig \ref{fig:model_outline}B), allowing a neo-W to invade and replace the ancestral sex-determination system (inset shows neo-W frequency among female gametes, reaching pseudo-fixation), which balances the zygotic sex ratio.
+In panel B, male drive in an ancestral ZW system has no effect on the zygotic sex ratio yet a neo-Y can invade and replace the ancestral sex-determination system (inset shows neo-Y frequency among male gametes, reaching pseudo-fixation).
+%When $R<1/2$, the neo-Y becomes associated with the allele favoured by drive, causing the zygotic sex ratio to become biased, hence the frequency of the neo-Y at pseudo-fixation can be higher than $0.5$ (inset).
 Parameters:  $s^\female =s^\male = 0.2$, $h^\female = h^\male = 0.7$, $t^\female = t^\male = \alpha^\female_\Delta = 0$, $\alpha^\male_\Delta = -0.1$, $r=0.02$.
@@
 Consider, for example, the case where the \textbf{A} locus is linked to the ancestral-SDR ($r<1/2$) and experiences meiotic drive in males only ($\alpha^\male_\Delta \neq 0$, $\alpha^\female_\Delta=0$), without gametic competition ($t^\female=t^\male=0$).
-In this case, the zygotic sex ratio can be initially biased only if the ancestral sex-determining system is XY (Figure \ref{fig:model_outline}B and Figure \ref{fig:SexRatioBad}B). 
-%If the ancxestral sex-determining system is ZW, the zygotic sex ratio will be 1:1 because diploid sex is determined by the proportion of Z-bearing versus W-bearing eggs and meiosis in females is fair (Figure \ref{fig:Combination_Turnover}D).
+In this case, the zygotic sex ratio can be initially biased only if the ancestral sex-determining system is XY (Fig \ref{fig:model_outline}B and Fig \ref{fig:SexRatioBad}B). 
+%If the ancxestral sex-determining system is ZW, the zygotic sex ratio will be 1:1 because diploid sex is determined by the proportion of Z-bearing versus W-bearing eggs and meiosis in females is fair (Fig \ref{fig:Combination_Turnover}D).
 If Fisherian sex ratio selection were dominant, we would expect a difference in the potential for XY to ZW and ZW to XY transitions. 
@@
 However, invasion by a neo-W into an XY system and invasion by a neo-Y into a ZW system occur under the same conditions ($\lambda_{Y',XY}=\lambda_{W',ZW}$ and $\lambda_{Y',ZW}=\lambda_{W',XY}$, at least to order $\epsilon^2$).
-For example, in Figure \ref{fig:SexRatioBad}A neo-W alleles invade an ancestral-XY system where females are initially rare.
-However, Figure \ref{fig:SexRatioBad}B shows that a neo-Y can invade an ancestral-ZW system under the same conditions. 
+For example, in Fig \ref{fig:SexRatioBad}A neo-W alleles invade an ancestral-XY system where females are initially rare.
+However, Fig \ref{fig:SexRatioBad}B shows that a neo-Y can invade an ancestral-ZW system under the same conditions. 
 As a consequence, whenever $R<1/2$, the neo-Y becomes associated with the male meiotic drive allele such that the zygotic sex ratio actually evolves to become biased towards males.
 
-%As selection becomes stronger (or linkage becomes tighter), this symmetry between sex ratio selection and haploid selection is lost, causing differences in the strength of selection favouring the two heterogametic transitions (compare red to black near -25cM and 25 cM in Figure \ref{fig:Combination_Centimorgans}).
+%As selection becomes stronger (or linkage becomes tighter), this symmetry between sex ratio selection and haploid selection is lost, causing differences in the strength of selection favouring the two heterogametic transitions (compare red to black near -25cM and 25 cM in Fig \ref{fig:Combination_Centimorgans}).
 \textcolor{red}{normalise fitness in sexually antagonistic case}
@@
 Consider first the case where both loci are linked to the selected locus ($r<R<1/2$). 
-In an XY system, haploid selection in males can facilitate the spread of a neo-W because the zygotic sex ratio is ancestrally biased and the W helps to equalize the sex ratio (Figure \ref{fig:SexRatioBad}A).
+In an XY system, haploid selection in males can facilitate the spread of a neo-W because the zygotic sex ratio is ancestrally biased and the W helps to equalize the sex ratio (Fig \ref{fig:SexRatioBad}A).
 A new sex determining region can also, however, benefit from becoming more associated with drive.  
-For example in a ZW system with the same selection regime (haploid selection in males), a neo-Y can spread despite the fact that the zygotic sex is initially even; in this case, the neo-Y spreads because it is often found in males and can, if it carries the driven allele $a$, benefit from haploid selection (Figure \ref{fig:SexRatioBad}B).
+For example in a ZW system with the same selection regime (haploid selection in males), a neo-Y can spread despite the fact that the zygotic sex is initially even; in this case, the neo-Y spreads because it is often found in males and can, if it carries the driven allele $a$, benefit from haploid selection (Fig \ref{fig:SexRatioBad}B).
 While equalizing the sex ratio and benefiting from drive are two primary reasons why haploid selection spurs sex chromosome transitions, more complex situations also arise.  
-For example with $R=1/2$ in Figure \ref{fig:SexRatioBad}B (green curve), the neo-Y spreads despite the fact that it cannot benefit from drive because free recombination moves it randomly between driven and non-driven backgrounds.
+For example with $R=1/2$ in Fig \ref{fig:SexRatioBad}B (green curve), the neo-Y spreads despite the fact that it cannot benefit from drive because free recombination moves it randomly between driven and non-driven backgrounds.
 Nevertheless, the unlinked neo-Y can spread because diploids bearing it more often carry the non-driven allele $A$ found at high frequency on the W background, which has higher average diploid fitness to balance the haploid advantage of the $a$ allele at equilibrium.
@@
 \begin{split}
-\lambda_{ESD',XY} =& 1 + \frac{(1-2k)^2}{4}V_{A}{S_{A}}^2\frac{r-R}{r R} \\
+\lambda_{ESD',XY} =& 1 + \frac{{(1-2k)}^2}{4}V_{A}{S_{A}}^2\frac{r-R}{r R} \\
 &+\frac{k(\hat{p}^\male_Y-\hat{p}^\male_X)}{2}\left[ k \left(2\alpha_{\Delta}^\male-2\alpha_{\Delta}^\female+t^\male-t^\female \right) -2(1-k)S_{A}\right]+O\left(\epsilon^3\right),
@@
 \lambda_{ESD',XY} =1+ \frac{1}{2}\frac{(\lambda_{Y',XY\rvert R=1/2}-1) + (\lambda_{W',XY\rvert R=1/2}-1)}{2} + O\left(\epsilon^3\right),
-%V_A \frac{r}{1-2r}  \frac{s_{f} \left( s^\male - 3 s^\female\right) }{8 \left( s_{f} + s_{m} \right)^2} t_{m}^2.
+%V_A \frac{r}{1-2r}  \frac{s_{f} \left( s^\male - 3 s^\female\right) }{8 {\left( s_{f} + s_{m} \right)}^2} t_{m}^2.
 \label{eq:lambda_ESD}
@@
 Two predominant theories explaining the remarkably high frequency of transitions between sex-determination systems are sexually-antagonistic selection and sex ratio selection (reviewed in~\cite{Blaser2012, vanDoorn2014re}).
-The former predicts that neo-sex-determining alleles can invade when they arise in closer linkage with a sexually-antagonistic locus~\cite{vanDoorn:2007eu,vanDoorn:2010hu, Muralidhar2018}.
+The former predicts that neo-sex-determining alleles can invade when they arise in closer linkage with a sexually-antagonistic locus ($r<R$,~\cite{vanDoorn:2007eu,vanDoorn:2010hu, Muralidhar2018}).
 The latter predicts that new sex-determining systems are generally favoured if they result in more equal sex ratios than the ancestral system. 
 %The latter predicts that neo-W alleles will invade an XY system when there is a male bias caused by haploid selection in males, and vice-versa, a neo-Y will invade a ZW system when there is a female bias caused by haploid selection in females~\cite{Kozielska:2010vm,Ubeda:2015fx}.
-In contrast to these prevailing views, we show that selection (including sexually-antagonistic selection, overdominance, and/or ploidally-antagonistic selection) on loci tightly linked to the ancestral sex-determining region can favour trans-GSD transitions (XY to ZW or ZW to XY) to new sex-determining systems that are less closely linked to the selected loci (e.g., see Figure \ref{fig:SexAntagTighter}).
+In contrast to these prevailing views, we show that selection (including sexually-antagonistic selection, overdominance, and/or ploidally-antagonistic selection) on loci tightly linked to the ancestral sex-determining region can favour trans-GSD transitions (XY to ZW or ZW to XY) to new sex-determining systems that are less closely linked to the selected loci (e.g., see Fig \ref{fig:SexAntagTighter}).
 Similarly, even when linkage is weak relative to selection, we show that %new sex-determining alleles are typically favoured if they are more closely linked to a locus under haploid selection (even in the absence of diploid sex differences), which is the only condition favouring cis-GSD transitions (XY to XY or ZW to ZW).
 %In addition, with haploid selection and weak selection, 
-trans-GSD transitions (XY to ZW or ZW to XY) can occur where the new sex-determining region is less closely linked to the locus under selection if there is haploid selection (e.g., Figures \ref{fig:Combination_Centimorgans} and \ref{fig:SexRatioBad}).
+trans-GSD transitions (XY to ZW or ZW to XY) can occur where the new sex-determining region is less closely linked to the locus under selection if there is haploid selection (e.g., Figs \ref{fig:Combination_Centimorgans} and \ref{fig:SexRatioBad}).
 
@@
 For instance, alleles favoured by haploid selection in males often become associated with the Y, which leads to a male-biased zygotic sex ratio.
-This male bias increases the potential for a neo-W to invade (Table \ref{tab:haplotype_growth}), which can equalize the sex ratio (e.g., see Figure \ref{fig:SexRatioBad}B, for related examples see~\cite{Kozielska:2010vm}).
+This male bias increases the potential for a neo-W to invade (Table \ref{tab:haplotype_growth}), which can equalize the sex ratio (e.g., see Fig \ref{fig:SexRatioBad}B, for related examples see~\cite{Kozielska:2010vm}).
 %We find that sex ratio biases caused by haploid selection can also affect transitions between sex-determining systems (e.g., see $\zeta$ terms in Table \ref{tab:haplotype_growth}). 
@@
 %and equalizing the sex ratio.
-Indeed, transitions between sex-determining systems can generate stronger sex ratio biases (e.g., Figure \ref{fig:SexRatioBad}A and step 1 in~\cite{Ubeda:2015fx}).
-%For example, where a neo-Y invades and is linked with a locus that experiences haploid selection in male gametes, the sex ratio evolves to become biased \citep[e.g., see Figure \ref{fig:SexRatioBad}A and step 1 in][]{Ubeda:2015fx}.
-%For example, in an ancestral ZW system, haploid selection in males can allow a linked neo-Y to invade, despite the fact that it creates a male-biased sex ratio because the neo-Y becomes associated with the driven allele (Figure \ref{fig:SexRatioBad}A).
+Indeed, transitions between sex-determining systems can generate stronger sex ratio biases (e.g., Fig \ref{fig:SexRatioBad}A and step 1 in~\cite{Ubeda:2015fx}).
+%For example, where a neo-Y invades and is linked with a locus that experiences haploid selection in male gametes, the sex ratio evolves to become biased \citep[e.g., see Fig \ref{fig:SexRatioBad}A and step 1 in][]{Ubeda:2015fx}.
+%For example, in an ancestral ZW system, haploid selection in males can allow a linked neo-Y to invade, despite the fact that it creates a male-biased sex ratio because the neo-Y becomes associated with the driven allele (Fig \ref{fig:SexRatioBad}A).
 %\textcolor{blue}{and figure 1, where the end of one panel is the same as the beginning of another, however, this figure may change).}
@@
 Significantly, with weak selection, we find that there is no difference in conditions allowing XY to ZW and ZW to XY transitions, indicating that sex chromosome transitions are not predominantly predicted by their effect on the sex ratio (i.e., the sex ratio bias created by male haploid selection facilitates the spread of a neo-W into an XY system to the same degree that male haploid selection drives the spread of a neo-Y into a ZW system with a 1:1 sex ratio).
-%An asymmetry can develop when sex-linkage is tight (e.g., Figure \ref{fig:Combination_Centimorgans} near -25cM and 25cM) but under most circumstances we do not predict asymmetry between XY to ZW and ZW to XY transitions despite the presence/absence of sex ratio selection.
+%An asymmetry can develop when sex-linkage is tight (e.g., Fig \ref{fig:Combination_Centimorgans} near -25cM and 25cM) but under most circumstances we do not predict asymmetry between XY to ZW and ZW to XY transitions despite the presence/absence of sex ratio selection.
 Thus, haploid selection can favour trans-GSD transitions both via sex ratio selection and via selection on alleles associated with the neo-sex-determining allele, and these selective pressures are often predicted to be of equal magnitude.
@@
 %maybe add a flag here for switching to clade-level expectations:
-In general, we predict that haploid selection increases lability of sex-determination systems, particularly because haploid selection can cause transitions that increase or decrease sex-linkage (e.g., the final state of the red line in Figure \ref{fig:SexRatioBad}B is the starting state in Figure \ref{fig:SexRatioBad}A).
+In general, we predict that haploid selection increases lability of sex-determination systems, particularly because haploid selection can cause transitions that increase or decrease sex-linkage (e.g., the final state of the red line in Fig \ref{fig:SexRatioBad}B is the starting state in Fig \ref{fig:SexRatioBad}A).
 Turnovers driven by haploid selection may help to explain the relative rarity of heteromorphic sex chromosomes in plants, which are thought to experience more selection during their multicellular haploid stage.
@@
 Our results show, however, that tight ancestral-linkage of polymorphic loci can also drive trans-GSD transitions. 
-In addition, we find that polymorphic sex determining systems (X, Y, W, and Z alleles all present) can be maintained when a selected locus is tightly linked to the ancestral sex-determining system (e.g., Figures \nameref{fig:freqAll}B and \nameref{fig:freqAll}C), which is not possible with loose linkage~\cite{vanDoorn:2010hu}.
+In addition, we find that polymorphic sex determining systems (X, Y, W, and Z alleles all present) can be maintained when a selected locus is tightly linked to the ancestral sex-determining system (e.g., \nameref{fig:freqAll}B and \nameref{fig:freqAll}C), which is not possible with loose linkage~\cite{vanDoorn:2010hu}.
 %As noted by \citet{vanDoorn:2010hu}, it would be prudent to compare closely related clades in order to determine whether observed polymorphisms predate a transition in sex-determination or arose afterwards.
@@
 However, XX and XX$^\ast$ females have similar fitness, whereas X$^\ast$Y female fitness is enhanced~\cite{Saunders2014,Saunders2016, Veyrunes2017}.
-Although Y-linkage of female-beneficial alleles is counterintuitive, our tight linkage model suggests that it can be stably maintained and then favour new feminizing mutations, which is a parsimonious explanation for the spread of feminizing alleles in these rodent species.
+Although Y-linkage of female-beneficial alleles is counterintuitive, our model suggests that it can be stably maintained and then favour new feminizing mutations, which is a parsimonious explanation for the spread of feminizing alleles in these rodent species.
 
@@
 There is no haploid selection $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
-These parameters are marked by daggers in Figure \ref{fig:regionplots}B and C, which show that neo-W invasion is expected for any $R$ ($\lambda_{WA},\lambda_{Wa}>1$) when the $a$ allele is nearly fixed on the Y (black lines in this figure; not stable for $r>>0$).
+These parameters are marked by daggers in Fig \ref{fig:regionplots}B and C, which show that neo-W invasion is expected for any $R$ ($\lambda_{WA},\lambda_{Wa}>1$) when the $a$ allele is nearly fixed on the Y (black lines in this figure; not stable for $r>>0$).
 Equilibria where the $A$ allele is more common among Y-bearing male gametes can also be stable and allow neo-W invasion for these parameters (blue lines). 
 The weak selection approximation holds when all recombination rates are large relative to selection (around 0 in panels A and C), in which case, in the absence of haploid selection, neo-W alleles should spread if and only if they are more tightly linked to the selected locus (positive invasion fitness if and only if the selected locus is in the grey region).
-However, when linkage is tight (panels B and D and when the selected locus is near the SDRs in all panels), this weak selection prediction can break down.
+However, when recombination rates are small (panels B and D and when the selected locus is near the SDRs in all panels), this weak selection prediction can break down.
 
@@
 In B, this leads to loss of the neo-W and the system goes to an equilibrium with X-$a$ and Y-$A$ haplotypes fixed (equilibrium $A'$), such that all females have the high fitness genotype $aa$ and all males are $Aa$.
-For the parameters in B, neo-W alleles have negative invasion fitness when the Y-$A$ haplotype is ancestrally more common than Y-$a$ (see blue lines in Figure \nameref{fig:positionOverdominance}A and  \nameref{fig:positionOverdominance}B near the ancestral SDR).
-In contrast, the neo-W is not lost in panel D as it is favoured near $r\approx0$ (see blue lines in Figure \nameref{fig:positionOverdominance}C and  \nameref{fig:positionOverdominance}D near the ancestral SDR).
-Fitness parameters are the same as in Figure \nameref{fig:positionOverdominance}; in panels A and B the $a$ allele is favoured in females ($w_{aa}^\female=1.05$, $w_{Aa}^\Hermaphrodite=1$, $w_{AA}^\female=0.85$) while there is overdominance in males ($w_{aa}^\male=w_{AA}^\male=0.75$) and in panels C and D, there is overdominance in both sexes ($w_{aa}^\female=w_{AA}^\female=0.6$, $w_{aa}^\male=0.5$, $w_{AA}^\male=0.7$, $w_{Aa}^\Hermaphrodite=1$).
-These parameters are marked by a dagger in Figure \ref{fig:regionplots}. 
+For the parameters in B, neo-W alleles have negative invasion fitness when the Y-$A$ haplotype is ancestrally more common than Y-$a$ (see blue lines in \nameref{fig:positionOverdominance}A and  \nameref{fig:positionOverdominance}B near the ancestral SDR).
+In contrast, the neo-W is not lost in panel D as it is favoured near $r\approx0$ (see blue lines in \nameref{fig:positionOverdominance}C and  \nameref{fig:positionOverdominance}D near the ancestral SDR).
+Fitness parameters are the same as in \nameref{fig:positionOverdominance}; in panels A and B the $a$ allele is favoured in females ($w_{aa}^\female=1.05$, $w_{Aa}^\Hermaphrodite=1$, $w_{AA}^\female=0.85$) while there is overdominance in males ($w_{aa}^\male=w_{AA}^\male=0.75$) and in panels C and D, there is overdominance in both sexes ($w_{aa}^\female=w_{AA}^\female=0.6$, $w_{aa}^\male=0.5$, $w_{AA}^\male=0.7$, $w_{Aa}^\Hermaphrodite=1$).
+These parameters are marked by a dagger in Fig \ref{fig:regionplots}. 
 Here, there is no haploid selection $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
@@
 {\bf  When there is sexually-antagonistic selection and haploid selection, a neo-W may invade for any $R$.}
-Panel A shows that the invasion fitness of a neo-W is positive where linkage is tight, even when $r<R$ (unshaded region).
+Panel A shows that the invasion fitness of a neo-W is positive, even when $r<R$ (unshaded region).
 In panel B, we vary the recombination rate between the neo-W and the selected locus ($R$) for a fixed recombination rate between the ancestral-SDR and the selected locus ($r=0.005$).
 Coloured markers show recombination rates for which the temporal dynamics of neo-W invasion are plotted in panel C (black $R=0.001$, red $R=0.02$, blue $R=0.1$, green $R=0.5$). 
-The diploid selection parameters used in this plot are the same as in Figure \ref{fig:SexAntagTighter}. 
-There is also meiotic drive in males favouring $a$ ($\alpha_{\Delta}^\male=-0.08$), this full set of parameters is marked by an asterisk in Figure \nameref{fig:regionMaleDrive}A.
-When $R=0.5$ (green curve), the neo-W does not reach fixation and X,Y,Z, and W alleles are all maintained in the population, see Figure \nameref{fig:freqAll}C.
+The diploid selection parameters used in this plot are the same as in Fig \ref{fig:SexAntagTighter}. 
+There is also meiotic drive in males favouring $a$ ($\alpha_{\Delta}^\male=-0.08$), this full set of parameters is marked by an asterisk in \nameref{fig:regionMaleDrive}A.
+When $R=0.5$ (green curve), the neo-W does not reach fixation and X,Y,Z, and W alleles are all maintained in the population, see \nameref{fig:freqAll}C.
 
@@
 {\bf Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is male gametic competition at a locus that is tightly linked to the ancestral-XY locus.}
-Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in Figure \nameref{fig:regionMaleDrive}. 
+Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in \nameref{fig:regionMaleDrive}. 
 The $a$ allele is favoured during male gametic competition in Panels A-C ($w_{a}^\male=1.16$, $w_{A}^\male=1$), which creates male biased sex ratios and increases $\lambda_{WA}$ and $\lambda_{Wa}$. 
 On the other hand, the $A$ allele is favoured during male gametic competition in Panels D-F ($w_{a}^\male=1$, $w_{A}^\male=1.16$) and $\lambda_{WA}$ and $\lambda_{Wa}$ tend to be reduced. 
-Compared to the meiotic drive parameters in Figure \nameref{fig:regionMaleDrive}, the effect of these male gametic competition parameters on the sex ratio is smaller. 
-For example, in Figure \nameref{fig:regionMaleDrive}A-C, the ancestral sex ratio is $\alpha^\male=0.58$ at equilibrium (B) and in panels A-C of this plot, the ancestral sex ratio is $w_{a}^\male/(w_{A}^\male+w_{a}^\male)=0.537$ at equilibrium (B).
+Compared to the meiotic drive parameters in \nameref{fig:regionMaleDrive}, the effect of these male gametic competition parameters on the sex ratio is smaller. 
+For example, in \nameref{fig:regionMaleDrive}A-C, the ancestral sex ratio is $\alpha^\male=0.58$ at equilibrium (B) and in panels A-C of this plot, the ancestral sex ratio is $w_{a}^\male/(w_{A}^\male+w_{a}^\male)=0.537$ at equilibrium (B).
 
@@
 {\bf Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is female meiotic drive at a locus that is tightly linked to the ancestral-XY locus.}
-Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in Figure \nameref{fig:regionMaleDrive} and \nameref{fig:regionMaleGS}. 
+Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in \nameref{fig:regionMaleDrive} and \nameref{fig:regionMaleGS}. 
 The $a$ allele is favoured by meiotic drive in females in Panels A-C ($\alpha_{\Delta}^\female=-0.16$), which increases $\lambda_{Wa}$ and decreases $\lambda_{WA}$. 
@@
 Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is female gametic competition at a locus that is tightly linked to the ancestral-XY locus.
-Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in Figure \nameref{fig:regionMaleDrive}, \nameref{fig:regionMaleGS}, and \nameref{fig:regionFemaleDrive}. 
+Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in \nameref{fig:regionMaleDrive}, \nameref{fig:regionMaleGS}, and \nameref{fig:regionFemaleDrive}. 
 The $a$ allele is favoured during female gametic competition in females in Panels A-C ($w_{a}^\female=1.16$, $w_{A}^\female=1$), which increases $\lambda_{Wa}$ and decreases $\lambda_{WA}$. 
@@
 In panels B and C a polymorphism is maintained at both the ancestral XY locus and the neo-ZW locus, such that there are males with genotypes XY-ZZ or YY-ZZ and females with genotypes XX-ZZ, XX-ZW, XY-ZW, or YY-ZW.
-In panel A, selection is ploidally antagonistic with drive in males (parameters as in the green curve in Figure \ref{fig:SexRatioBad}B).
-In panel B, there is overdominance in both sexes and no haploid selection (parameters as in the green curve in Figure \nameref{fig:temporalOverdominance}C).
-In panel C, there is sexually-antagonistic selection in diploids with drive in males (parameters as in the green curve in Figure \nameref{fig:regionMaleDrive}C).
+In panel A, selection is ploidally antagonistic with drive in males (parameters as in the green curve in Fig \ref{fig:SexRatioBad}B).
+In panel B, there is overdominance in both sexes and no haploid selection (parameters as in the green curve in \nameref{fig:temporalOverdominance}C).
+In panel C, there is sexually-antagonistic selection in diploids with drive in males (parameters as in the green curve in \nameref{fig:regionMaleDrive}C).
 In all cases, the initial equilibrium frequency has $a$ near fixation on the Y.
@@
 
+\setcounter{equation}{0}
+\renewcommand{\theequation}{S1.\arabic{equation}}
+
+\section*{S1 Appendix}
+
+\subsection*{Recursion equations}
+
+%\textcolor{red}{Should we adjust the subscripts throughout this subsection?
+Right now we end up re-defining $i$ and $j$ (when switching from haploid to diploid; this might have been my doing!) and then introduce three new subscripts $b$, $c$, and $l$, all of which can be derived from $i$ and $j$.
+Might be more straightforward to just use $p^\Hermaphrodite_{x_1,x_2,a_1,a_2,m_1,m_2}$ where 1 is maternal and 2 is paternal?
+We then no longer have to switch indices from haploid to diploid and the connection to other variables is clear: $b=m_1m_2$, $c=x_1x_2$, and $l=a_1a_2$.
+I guess the downside will be re-writing the recursion equations...
+which is why I haven't gone ahead and tried this.}
+
+In each generation we census the genotype frequencies in male and female gametes/gametophytes (hereafter, gametes) between meiosis (and any meiotic drive) and gametic competition. 
+At this stage we denote the frequencies of X- and Y-bearing gametes from males and females $x_{i}^{\Hermaphrodite}$ and $y_{i}^{\Hermaphrodite}$.
+The superscript $\Hermaphrodite \in \{\male,\female\}$ specifies the sex of the diploid that the gamete came from. 
+The subscript $i\in\{1,2,3,4\}$ specifies the genotype at the selected locus $\mathbf{A}$ and at the novel sex-determining locus $\mathbf{M}$, where $1=AM$, $2=aM$, $3=Am$, and $4=am$. 
+The gamete frequencies from each sex sum to one, $\sum_{i}x_{i}^{\Hermaphrodite}+y_{i}^{\Hermaphrodite}=1$.
+
+Competition then occurs among gametes of the same sex (e.g., among eggs and among sperm separately) according to the genotype at the \textbf{A} locus ($w_{1}^\Hermaphrodite=w_{3}^\Hermaphrodite=w_{A}^\Hermaphrodite$, $w_{2}^\Hermaphrodite=w_{4}^\Hermaphrodite=w_{a}^\Hermaphrodite$, see Table \ref{tab:fitnesstable}).
+The genotype frequencies after gametic competition are $x_{i}^{\Hermaphrodite,s}= w_{i}^{\Hermaphrodite}x_{i}^{\Hermaphrodite}/\bar{w}_{H}^{\Hermaphrodite}$ and $y_{i}^{\Hermaphrodite,s}= w_{i}^{\Hermaphrodite}y_{i}^{\Hermaphrodite}/\bar{w}_{H}^{\Hermaphrodite}$, where $\bar{w}_{H}^{\Hermaphrodite}=\sum_{i} w_{i}^{\Hermaphrodite}x_{i}^{\Hermaphrodite}+w_{i}^{\Hermaphrodite}y_{i}^{\Hermaphrodite}$ is the mean fitness of male ($\Hermaphrodite=\male$) or female ($\Hermaphrodite=\female$) gametes.
+
+Random mating then occurs between gametes to produce diploid zygotes.
+%To shorten notation we now use index $i$ (and $j$) to denote the alleles at both the $\mathbf{A}$ and $\mathbf{M}$ loci and label $MA=1$, $Ma=2$, $mA=3$, and $ma=4$, such that $i,j\in\{1,2,3,4\}$.
+The frequencies of XX zygotes are then denoted as $xx_{ij}$, XY zygotes as $xy_{ij}$, and YY zygotes as $yy_{ij}$, where \textbf{A} and \textbf{M} locus genotypes are given by $i,j\in\{1,2,3,4\}$, as above.
+In $XY$ zygotes, the haplotype inherited from an X-bearing gamete is given by $i$ and the haplotype from a Y-bearing gamete is given by $j$. 
+In XX and YY zygotes, individuals with diploid genotype $ij$ are equivalent to those with diploid genotype $ji$; for simplicity, we use $xx_{ij}$ and $yy_{ij}$ with $i\neq j$ to denote the average of these frequencies, $xx_{ij}=(x_{i}^{\female,s}x_{j}^{\male,s}+x_{j}^{\female,s}x_{i}^{\male,s})/2$ and $yy_{ij}=(y_{i}^{\female,s}y_{j}^{\male,s}+y_{j}^{\female,s}y_{i}^{\male,s})/2$.
+
+Denoting the \textbf{M} locus genotype by $b \in \{MM, Mm, mm\}$ and the \textbf{X} locus genotype by $c \in \{XX, XY, YY\}$, zygotes develop as females with probability $k_{bc}$. 
+Therefore, the frequencies of XX females are given by $xx_{ij}^{\female}=k_{bc}xx_{ij}$, XY females are given by $xy_{ij}^{\female}=k_{bc}xy_{ij}$, and YY females are given by $yy_{ij}^{\female}=k_{bc}yy_{ij}$.
+Similarly, XX male frequencies are $xx_{ij}^{\male}=(1-k_{bc})xx_{ij}$, XY male frequencies are $xy_{ij}^{\male}=(1-k_{bc})xy_{ij}$, and YY males frequencies are $yy_{ij}^{\male}=(1-k_{bc})yy_{ij}$.
+This notation allows both the ancestral and novel sex-determining regions to determine zygotic sex according to an XY system, a ZW system, or an environmental sex-determining system. 
+In addition, we can consider any epistatic dominance relationship between the two sex-determining loci. 
+Here, we assume that the ancestral sex-determining system (\textbf{X} locus) is XY ($k_{MMXX}=1$ and $k_{MMXY}=k_{MMYY}=0$) or ZW ($k_{MMZZ}=0$ and $k_{MMZW}=k_{MMWW}=1$) and epistatically recessive to a dominant novel sex-determining locus, \textbf{M} ($k_{Mmc}=k_{mmc}=k$).
+
+Selection among diploids then occurs according to the diploid genotype at the \textbf{A} locus, $l \in \{AA, Aa, aa\}$, for an individual of type $ij$ (see Table \ref{tab:fitnesstable}). 
+The diploid frequencies after selection in sex $\Hermaphrodite$ are given by $xx_{ij}^{\Hermaphrodite,s}=w_{l}^{\Hermaphrodite} xx_{ij}/\bar{w}^{\Hermaphrodite}_{D}$, $xy_{ij}^{\Hermaphrodite,s}=w_{l}^{\Hermaphrodite} xy_{ij}/\bar{w}^{\Hermaphrodite}_{D}$, and $yy_{ij}^{\Hermaphrodite,s}=w_{l}^{\Hermaphrodite} yy_{ij}/\bar{w}^{\Hermaphrodite}_{D}$, where $\bar{w}^{\Hermaphrodite}_{D}= \sum_{i=1}^{4}\sum_{j=1}^{4}w_{l}^{\Hermaphrodite}xx_{ij}+w_{l}^{\Hermaphrodite}xy_{ij}+w_{l}^{\Hermaphrodite}yy_{ij}$ is the mean fitness of diploids of sex $\Hermaphrodite$.
+
+Finally, these diploids undergo meiosis to produce the next generation of gametes. 
+Recombination and sex-specific meiotic drive occur during meiosis.
+%We can also assume that recombination is sex specific and/or affected by the M locus - but generally we don't so I just describe $R=R_{f}=R, r_{MM,d}=r_{Mm,d}=r_{mm,d}=r, \chi_{m}=\chi_{f}=\chi$.
+Here, we allow any relative locations for the SDR, \textbf{A}, and \textbf{M} loci by using three parameters to describe the recombination rates between them. 
+$R$ is the recombination rate between the \textbf{A} locus and the \textbf{M} locus, $\rho$ is the recombination rate between the \textbf{M} locus and the \textbf{X} locus, and $r$ is the recombination rate between the \textbf{A} locus and the \textbf{X} locus (Fig \ref{fig:model_outline}).
+\nameref{tab:chisubstitutions} shows replacements that can be made for each possible ordering of the loci assuming that there is no cross-over interference.
+During meiosis in sex $\Hermaphrodite$, meiotic drive occurs such that, in $Aa$ heterozygotes, a fraction $\alpha^{\Hermaphrodite}$ of gametes produced carry the $A$ allele and $(1-\alpha^\Hermaphrodite)$ carry the $a$ allele.
+
+Among gametes from sex $\Hermaphrodite$, the frequencies of haplotypes (before gametic competition) in the next generation are given by
+
+\begingroup
+\allowdisplaybreaks
+\begin{subequations}
+\begin{align}
+%
+\begin{split}
+x_{1}^{{\Hermaphrodite}'}=&xx_{11}^{\Hermaphrodite,s}+xx_{13}^{\Hermaphrodite,s}/2+(xx_{12}^{\Hermaphrodite,s}+xx_{14}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
+&-R(xx_{14}^{\Hermaphrodite,s}-xx_{23}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
+&+(xy_{11}^{\Hermaphrodite,s}+xy_{13}^{\Hermaphrodite,s})/2+(xy_{12}^{\Hermaphrodite,s}+xy_{14}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
+&- r(xy_{12}^{\Hermaphrodite,s}-xy_{21}^{\Hermaphrodite,s})\alpha^\Hermaphrodite - \rho(xy_{13}^{\Hermaphrodite,s}-xy_{31}^{\Hermaphrodite,s})/2\\
+&+\big{[}-(R+r+\rho)xy_{14}^{\Hermaphrodite,s} +(R+\rho-r)xy_{41}^{\Hermaphrodite,s}\\
+&+(R+r-\rho) xy_{23}^{\Hermaphrodite,s}+(R+\rho-r)xy_{32}^{\Hermaphrodite,s}\big{]}\alpha^\Hermaphrodite/2
+\end{split}
+\\
+%
+\begin{split}
+x_{2}^{{\Hermaphrodite}'}=&xx_{22}^{\Hermaphrodite,s}+xx_{24}^{\Hermaphrodite,s}/2+(xx_{12}^{\Hermaphrodite,s}+xx_{23}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
+&-R(xx_{23}^{\Hermaphrodite,s}-xx_{14}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
+&(xy_{22}^{\Hermaphrodite,s}+xy_{24}^{\Hermaphrodite,s})/2+(xy_{21}^{\Hermaphrodite,s}+xy_{23}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite)\\
+&- r(xy_{21}^{\Hermaphrodite,s}-xy_{12}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite) - \rho(xy_{24}^{\Hermaphrodite,s}-xy_{42}^{\Hermaphrodite,s})/2\\
+&+\big{[}-(R+r+\rho)xy_{23}^{\Hermaphrodite,s}+(R+\rho-r)xy_{32}^{\Hermaphrodite,s}\\
+&+(R+r-\rho) xy_{14}^{\Hermaphrodite,s}+(R+\rho-r)xy_{41}^{\Hermaphrodite,s}\big{]}(1-\alpha^\Hermaphrodite)/2
+\end{split}
+\\
+%
+\begin{split}
+x_{3}^{{\Hermaphrodite}'}=&xx_{33}^{\Hermaphrodite,s}+xx_{13}^{\Hermaphrodite,s}/2+(xx_{23}^{\Hermaphrodite,s}+xx_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
+&-R(xx_{23}^{\Hermaphrodite,s}-xx_{14}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
+&(xy_{33}^{\Hermaphrodite,s}+xy_{31}^{\Hermaphrodite,s})/2+(xy_{32}^{\Hermaphrodite,s}+xy_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
+&- r(xy_{34}^{\Hermaphrodite,s}-xy_{43}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite - \rho(xy_{31}^{\Hermaphrodite,s}-xy_{13}^{\Hermaphrodite,s})/2\\
+&+\big{[}-(R+r+\rho)xy_{32}^{\Hermaphrodite,s} +(R+\rho-r)xy_{23}^{\Hermaphrodite,s}\\
+&+(R+r-\rho) xy_{41}^{\Hermaphrodite,s}+(R+\rho-r)xy_{14}^{\Hermaphrodite,s}\big{]} \alpha^\Hermaphrodite/2
+\end{split}
+\\
+%
+\begin{split}
+x_{4}^{{\Hermaphrodite}'}=&xx_{44}^{\Hermaphrodite,s}+xx_{34}^{\Hermaphrodite,s}/2+(xx_{14}^{\Hermaphrodite,s}+xx_{24}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
+&-R(xx_{14}^{\Hermaphrodite,s}-xx_{23}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
+&(xy_{44}^{\Hermaphrodite,s}+xy_{42}^{\Hermaphrodite,s})/2+(xy_{41}^{\Hermaphrodite,s}+xy_{43}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite)\\
+&- r(xy_{43}^{\Hermaphrodite,s}-xy_{34}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite) - \rho(xy_{42}^{\Hermaphrodite,s}-xy_{24}^{\Hermaphrodite,s})/2\\
+&+\big{[}-(R+r+\rho)xy_{41}^{\Hermaphrodite,s}+(R+\rho-r)xy_{14}^{\Hermaphrodite,s}\\
+&+(R+r-\rho) xy_{32}^{\Hermaphrodite,s}+(R+\rho-r)xy_{23}^{\Hermaphrodite,s}\big{]}(1-\alpha^\Hermaphrodite)/2
+\end{split}
+\\
+\begin{split}
+y_{1}^{{\Hermaphrodite}'}=&yy_{11}^{\Hermaphrodite,s}+yy_{13}^{\Hermaphrodite,s}/2+(yy_{12}^{\Hermaphrodite,s}+yy_{14}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
+&-R(yy_{14}^{\Hermaphrodite,s}-yy_{23}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
+&(xy_{11}^{\Hermaphrodite,s}+xy_{31}^{\Hermaphrodite,s})/2+(xy_{21}^{\Hermaphrodite,s}+xy_{41}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
+&- r(xy_{21}^{\Hermaphrodite,s}-xy_{12}^{\Hermaphrodite,s})\alpha^\Hermaphrodite - \rho(xy_{31}^{\Hermaphrodite,s}-xy_{13}^{\Hermaphrodite,s})/2\\
+&+\big{[} - (R+r+\rho)xy_{41}^{\Hermaphrodite,s} + (R+\rho-r)xy_{14}^{\Hermaphrodite,s}\\
+& + (R+r-\rho)xy_{32}^{\Hermaphrodite,s} + (R+\rho-r) xy_{23}^{\Hermaphrodite,s}\big{]}\alpha^\Hermaphrodite/2
+\end{split}
+\\
+%
+\begin{split}
+y_{2}^{{\Hermaphrodite}'}=&yy_{22}^{\Hermaphrodite,s}+yy_{24}^{\Hermaphrodite,s}/2+(yy_{12}^{\Hermaphrodite,s}+yy_{23}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
+&-R(yy_{23}^{\Hermaphrodite,s}-yy_{14}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
+&(xy_{22}^{\Hermaphrodite,s}+xy_{42}^{\Hermaphrodite,s})/2+(xy_{12}^{\Hermaphrodite,s}+xy_{32}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite)\\
+&- r(xy_{12}^{\Hermaphrodite,s}-xy_{21}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite) - \rho(xy_{42}^{\Hermaphrodite,s}-xy_{24}^{\Hermaphrodite,s})/2\\
+&+\big{[}-(R+r+\rho)xy_{32}^{\Hermaphrodite,s} +(R+\rho-r) xy_{23}^{\Hermaphrodite,s}\\
+&+(R+r-\rho)xy_{41}^{\Hermaphrodite,s}+(R+\rho-r)xy_{14}^{\Hermaphrodite,s}\big{]}(1-\alpha^\Hermaphrodite)/2
+\end{split}
+\\
+%
+\begin{split}
+y_{3}^{{\Hermaphrodite}'}=&yy_{33}^{\Hermaphrodite,s}+yy_{13}^{\Hermaphrodite,s}/2+(yy_{23}^{\Hermaphrodite,s}+yy_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
+&-R(yy_{23}^{\Hermaphrodite,s}-yy_{14}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
+&(xy_{33}^{\Hermaphrodite,s}+xy_{13}^{\Hermaphrodite,s})/2+(xy_{23}^{\Hermaphrodite,s}+xy_{43}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
+&- r(xy_{43}^{\Hermaphrodite,s}-xy_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite - \rho(xy_{13}^{\Hermaphrodite,s}-xy_{31}^{\Hermaphrodite,s})/2\\
+&+\big{[}-(R+r+\rho)xy_{23}^{\Hermaphrodite,s} +(R+\rho-r)xy_{32}^{\Hermaphrodite,s}\\
+&+(R+r-\rho) xy_{14}^{\Hermaphrodite,s} + (R+\rho-r) xy_{41}^{\Hermaphrodite,s}\big{]}\alpha^\Hermaphrodite/2
+\end{split}
+\\
+%
+\begin{split}
+y_{4}^{{\Hermaphrodite}'}=&yy_{44}^{\Hermaphrodite,s}+yy_{34}^{\Hermaphrodite,s}/2+(yy_{14}^{\Hermaphrodite,s}+yy_{24}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
+&-R(yy_{14}^{\Hermaphrodite,s}-yy_{23}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
+&(xy_{44}^{\Hermaphrodite,s}+xy_{24}^{\Hermaphrodite,s})/2+(xy_{14}^{\Hermaphrodite,s}+xy_{34}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite)\\
+&- r(xy_{34}^{\Hermaphrodite,s}-xy_{43}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite) - \rho(xy_{24}^{\Hermaphrodite,s}-xy_{42}^{\Hermaphrodite,s})/2\\
+&+\big{[}-(R+r+\rho) xy_{14}^{\Hermaphrodite,s} + (R+\rho-r)xy_{41}^{\Hermaphrodite,s}\\
+&+(R+r-\rho) xy_{23}^{\Hermaphrodite,s} + (R+\rho-r) xy_{32}^{\Hermaphrodite,s}\big{]}(1-\alpha^\Hermaphrodite)/2
+\end{split}
+\end{align}
+\label{eq:recursions}
+\end{subequations}
+
+\endgroup
+
+\noindent
+The full system is therefore described by 16 recurrence equations (three diallelic loci in two sexes, $2^3 \times 2 = 16$). 
+However, not all diploid types are produced under certain sex-determination systems. 
+For example, with the $M$ allele fixed and an ancestral $XY$ sex-determining system, there are $XX$ females and $XY$ males ($x_{3}^\Hermaphrodite=x_{4}^\Hermaphrodite=y_{4}^\Hermaphrodite=y_{3}^\Hermaphrodite=y_{i}^\female=0$).
+%($xx_{11}^{\male}=xx_{12}^{\male}=xx_{22}^\male=xy_{11}^{\female}=xy_{12}^{\female}=xy_{21}^{\female}=xy_{22}^\female=yy_{11}^{\female}=yy_{12}^{\female}=yy_{22}^\female=0$). 
+In this case, the system only involves six recursion equations, %because there is only one \textbf{M} locus allele and no Y-bearing female gametes. 
+which we assume below to calculate the equilibria.
+
+\newpage
+
+\section*{S2 Appendix}
+
+\subsection*{Resident equilibria and stability}
+
+In the resident population (allele $M$ fixed), we follow the frequency of $A$ in X-bearing female gametes, $p^\female_X$, and X-bearing male gametes, $p^\male_X$, and Y-bearing male gametes, $p^\male_Y$.
+We also track the total frequency of Y among male gametes, $q$, which may deviate from $1/2$ due to meiotic drive in males. 
+These four variables determine the frequencies of the six resident gamete types, which sum to one in each sex: $x_{1}^{\female}=\hat{p}_X^\female$, $x_{2}^{\female}=1-\hat{p}_X^\female$, $x_{1}^{\male}=(1-q)\hat{p}_X^\male$, $x_{2}^{\male}=(1-q)(1-\hat{p}_X^\male)$, $y_{1}^{\male}=q \hat{p}_Y^\male$, and $y_{2}^{\male}=q(1-\hat{p}_Y^\male)$.
+Mean fitnesses in the resident population are given in \nameref{tab:meanfitnesses}.
+
+Various forms of selection can maintain a polymorphism at the \textbf{A} locus, including sexually antagonistic selection, overdominance, conflicts between diploid selection and selection upon haploid genotypes (ploidally-antagonsitic selection,~\cite{Immler:2012tl}), or a combination of these selective regimes (see below).
+
+In particular special cases, e.g., no sex-differences in selection or meiotic drive ($s^\male=s^\female$, $h^\male=h^\female$, and $\alpha^\male=\alpha^\female=1/2$), the equilibrium allele frequency and stability can be calculated analytically without assuming anything about the relative strengths of selection and recombination.
+However, here, we focus on two regimes (tight linkage between \textbf{A} and \textbf{X} and weak selection) in order to make fewer assumptions about fitnesses.
+
+\subsubsection*{Tight linkage between \textbf{A} and \textbf{X}}
+
+We first calculate the equilibrium frequency of the Y and $A$ alleles in the ancestral population when the recombination rate between the \textbf{X} and \textbf{A} loci is small ($r$ of order $\epsilon$).
+Selection at the \textbf{A} locus will not affect evolution at the novel sex-determining locus, \textbf{M}, if one allele is fixed on all backgrounds. 
+We therefore focus on the five equilibria that maintain both $A$ and $a$ alleles, four of which are given to leading order by:
+
+\begin{subequations}\label{eq:tightequil}
+\begin{align}
+(A)\ \ \ &\hat{p}_{Y}^{\male}=0,
+\ \hat{q}=\frac{1}{2}\left(1 - \alpha_\Delta^\male \frac{ w_{Aa}^{\male} \phi}{w_{Aa}^{\male} \phi+ w_{aa}^{\male} \psi}\right),\\
+&\hat{p}_{X}^{\female}=\frac{w_{a}^{\female} \phi}{w_{a}^{\female} \phi+ w_{A}^{\female} \psi},
+\ \hat{p}_{X}^{\male}=\frac{(1+\alpha_\Delta^\male)w_{Aa}^{\male} \phi}{(1+\alpha_\Delta^\male)w_{Aa}^{\male} \phi +w_{aa}^{\male} \psi} \nonumber \\
+(A')\ \ \ &\hat{p}_{Y}^{\male}=1,
+\ \hat{q}=\frac{1}{2}\left(1 + \alpha_\Delta^\male \frac{w_{Aa}^{\male} \phi'}{w_{Aa}^{\male} \phi' + w_{AA}^{\male} \psi'}\right),\\
+&\hat{p}_{X}^{\female}=1-\frac{w_{A}^{\female} \phi'}{w_{A}^{\female} \phi'+ w_{a}^{\female} \psi'},
+\ \hat{p}_{X}^{\male}=1-\frac{(1-\alpha_\Delta^\male)w_{Aa}^{\male} \phi'}{(1-\alpha_\Delta^\male)w_{Aa}^{\male} \phi'+w_{AA}^{\male} \psi'} \nonumber \\
+(B)\ \ \ &\hat{p}_{Y}^{\male}=0,\ \hat{p}_{X}^{\female}=1,\ \hat{p}_{X}^{\male}=1, \ \hat{q}=(1 -\alpha^\male_\Delta)/2\\
+(B')\ \ \ &\hat{p}_{Y}^{\male}=1,\ \hat{p}_{X}^{\female}=0,\ \hat{p}_{X}^{\male}=0, \ \hat{q}=(1+\alpha^\male_\Delta)/2
+\end{align}
+\end{subequations}
+\begin{equation*}
+\begin{split}
+\phi=&(1+\alpha^\female_\Delta) w_{A}^{\female} w_{Aa}^{\female} \left[ w_{a}^{\male} w_{aa}^{\male} + (1+\alpha_\Delta^\male) w_{A}^{\male} w_{Aa}^{\male} \right]/2 - w_{a}^{\male} w_{a}^{\female} w_{aa}^{\male} w_{aa}^{\female} \\
+\psi=&(1-\alpha^\female_\Delta) w_{a}^{\female} w_{Aa}^{\female} \left[ w_{a}^{\male} w_{aa}^{\male} + (1+\alpha_\Delta^\male) w_{A}^{\male} w_{Aa}^{\male}\right]/2 - (1+\alpha_\Delta^\male) w_{A}^{\male} w_{A}^{\female} w_{Aa}^{\male} w_{AA}^{\female}\\
+\phi'=&(1-\alpha^\female_\Delta) w_{a}^{\female} w_{Aa}^{\female} \left[ w_{A}^{\male} w_{AA}^{\male} + (1-\alpha_\Delta^\male) w_{a}^{\male} w_{Aa}^{\male} \right]/2 - w_{A}^{\male} w_{A}^{\female} w_{AA}^{\male} w_{AA}^{\female}\\
+\psi'=&(1+\alpha^\female_\Delta) w_{A}^{\female} w_{Aa}^{\female} \left[ w_{A}^{\male} w_{AA}^{\male} + (1-\alpha_\Delta^\male) w_{a}^{\male} w_{Aa}^{\male} \right]/2 - (1-\alpha_\Delta^\male) w_{a}^{\male} w_{a}^{\female} w_{Aa}^{\male} w_{aa}^{\female}
+\end{split}
+\end{equation*}
+
+\noindent
+A fifth equilibrium $(C)$ also exists where $A$ is present at an intermediate frequency on the Y chromosome ($0<\hat{p}_{Y}^{\male}<1$). 
+However, equilibrium $(C)$ is never locally stable when $r \approx 0$ and is therefore not considered further.
+Thus, the Y can either be fixed for the $a$ allele (equilibria $A$ and $B$) or the $A$ allele (equilibria $A'$ and $B'$).
+The X chromosome can then either be polymorphic (equilibria $A$ and $A'$) or fixed for the alternative allele (equilibria $B$ and $B'$).
+Since equilibria $(A)$ and $(B)$ are equivalent to equilibria $(A')$ and $(B')$ with the labelling of $A$ and $a$ alleles interchanged, we discuss only equilibria $(A)$ and $(B)$, in which the Y is fixed for the $a$ allele.
+If there is no haploid selection ($\alpha^{\Hermaphrodite}_\Delta=0$, $w_{A}^{\Hermaphrodite}=w_{a}^{\Hermaphrodite}=1$), these equilibria are equivalent to those found by~\cite{Lloyd1977} and~\cite{Otto2014}.
+
+We next calculate when $(A)$ and $(B)$ are locally stable for $r=0$. 
+According to the `small parameter theory'~\cite{Karlin:1972ab,Karlin:1972dq}, these stability properties are unaffected by small amounts of recombination between the SDR and \textbf{A} locus, although equilibrium frequencies may be slightly altered.
+For the $a$ allele to be stably fixed on the Y we need $\bar{w}_{Ya}^{\male} > \bar{w}_{YA}^{\male}$ where $\bar{w}_{Ya}^{\male} = w_{a}^{\male} \big[\hat{p}_X^\female(1-\alpha^\male_\Delta) w_{A}^{\female} w_{Aa}^{\male} + (1-\hat{p}_X^\female)w_{a}^{\female} w_{aa}^{\male} \big]$ and $\bar{w}_{YA}^{\male} = w_{A}^{\male} \big[ \hat{p}_X^\female w_{A}^{\female} w_{AA}^{\male} + (1-\hat{p}_X^\female)(1+\alpha^\male_\Delta) w_{a}^{\female} w_{Aa}^{\male} \big]$.
+That is, Y-$a$ haplotypes must have higher fitness than Y-$A$ haplotypes.  
+Substituting in $\hat{p}_X^\female$ from equation \eqref{eq:tightequil}, fixation of the $a$ allele on the Y requires that $\gamma_{i}>0$ where $\gamma_{(A)}=w_{a}^{\male} \big[ (1-\alpha^\male_\Delta) w_{Aa}^{\male} \phi + w_{aa}^{\male} \psi \big]-w_{A}^{\male} \big[ w_{AA}^{\male} \phi + (1 + \alpha^{\male}_\Delta)w_{Aa}^{\male} \psi \big]$ for equilibrium $(A)$ and $\gamma_{(B)}=(1-\alpha^{\male}_\Delta)w_{a}^{\male}w_{Aa}^{\male}-w_{A}^{\male}w_{AA}^{\male}$ for equilibrium $(B)$.
+Stability of a polymorphism on the X chromosome (equilibrium $A$) further requires that $\phi >0$ and $\psi >0$. 
+Fixation of the $a$ allele on the X (equilibrium $B$) can be stable only if equilibrium $(A)$ is not, as it requires $\psi<0$.
+%and $2w_{A}^{\female}w_{AA}^{\female}>(1-\alpha_\Delta^{\female})w_{a}^{\female}w_{Aa}^{\female}$ or just $4w_{A}^{\female}w_{AA}^{\female}<(1-\alpha_\Delta^{\female})w_{a}^{\female}w_{Aa}^{\female}$ (which also prevents $\psi>0$).
+
+%\textcolor{red}{check last condition and the stability condition below are correct}
+%\textcolor{blue}{The last condition looks good to me, although in your Turnover-norec-MFS.nb you look at YA fixed, so you have to flip everything (so I made Turnover-norec-MFS-MMO.nb to do this).
+%The one issue I can find here is that you can also prevent $\lambda>1$ when the slope and intercept of the quadratic at $\lambda=1$ are negative (you only looked at both being positive).
+In this case we need $4w_{A}^{\female}w_{AA}^{\female}<(1-\alpha_\Delta^{\female})w_{a}^{\female}w_{Aa}^{\female}$, which also prevents $\psi>0$.
+%I've added this in.
+%It could also be the case that the slope and intercept are the same sign but the roots are imaginary - but this is never the case here.
+%Stability condition below looks good to me (from matt version of turnoverSOM-MIKE.nb).}
+
+\subsubsection*{Selection weak relative to recombination}
+
+Here, we assume that selection and meiotic drive are weak relative to recombination ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon$). 
+The maintenance of a polymorphism at the \textbf{A} locus then requires that
+
+\begin{equation}
+\begin{split}
+0&< - \left[(1-h^\female)s^\female +(1-h^\male) s^\male + t^\female +t^\male + \alpha_{\Delta}^\female+\alpha_{\Delta}^\male\right]\\
+%
+\text{and }\quad 0&<h^\female s^\female +h^\male s^\male + t^\female +t^\male + \alpha_{\Delta}^\female+\alpha_{\Delta}^\male.
+\end{split}
+\end{equation}
+
+\noindent
+which indicates that a polymorphism can be maintained by various selective regimes.
+
+Given that a polymorphism is maintained at the \textbf{A} locus by weak selection, the frequencies of $A$ in each type of gamete are the same ($\hat{p}^\female_X=\hat{p}^\male_X=\hat{p}^\male_Y=\bar{p}$) and given, to leading order, by
+
+\begin{equation}
+\bar{p}=\frac{h^\female s^\female + h^\male s^\male +t^\female+t^\male+\alpha_{\Delta}^\female+\alpha_{\Delta}^\male}
+{(2h^\female-1)s^\female+(2h^\male-1)s^\male}
++O(\epsilon)
+.
+\label{eq:pAve}
+\end{equation}
+
+\noindent
+Differences in frequency between gamete types are of $O(\epsilon)$:
+
+\begin{equation}
+\begin{split}
+\hat{p}^\male_X-\hat{p}^\female_X&=V_{A}\big{(}D^\male - D^\female +\alpha_{\Delta}^\male-\alpha_{\Delta}^\female \big{)}
++O(\epsilon^2)\\
+%
+\hat{p}^\male_Y-\hat{p}^\female_X&=V_{A}\left[D^\male - D^\female+\alpha_{\Delta}^\male-\alpha_{\Delta}^\female+(1-2r)(t^\male-t^\female)\right]/2r
++O(\epsilon^2)\\
+%
+\hat{p}^\male_Y-\hat{p}^\male_X&=V_{A}\left(D^\male - D^\female+\alpha_{\Delta}^\male-\alpha_{\Delta}^\female+t^\male-t^\female\right)(1-2r)/2r
++O(\epsilon^2)
+\end{split}
+\label{eq:freq_diffs}
+\end{equation}
+
+\noindent
+where $V_{A}=\bar{p}(1-\bar{p})$ is the variance in the frequency of $A$ and $D^\Hermaphrodite=\big{[} \bar{p}s^\Hermaphrodite+(1-\bar{p})h^\Hermaphrodite s^\Hermaphrodite\big{]} -\big{[} \bar{p}h^\Hermaphrodite s^\Hermaphrodite+(1-\bar{p}) \big{]}$ corresponds to the difference in fitness between $A$ and $a$ alleles in diploids of sex $\Hermaphrodite \in \{\female,\male\}$.
+The frequency of Y among male gametes depends upon the difference in the frequency of the $A$ allele between X- and Y-bearing male gametes and the strength of meiotic drive in favour of the $A$ allele in males, $q=1/2+\alpha_{\Delta}^\male(\hat{p}^\male_Y-\hat{p}^\male_X)/2+O(\epsilon^3)$.
+Without gametic competition or drive ($\alpha_{\Delta}^\Hermaphrodite=t^\Hermaphrodite=0$) our results reduce to those of~\cite{vanDoorn:2007eu}.
+
+\newpage
+
+\setcounter{equation}{0}
+\renewcommand{\theequation}{S3.\arabic{equation}}
+
+\section*{S3 Appendix}
+
+\subsection*{Invasion conditions}
+
+\textcolor{red}{Cover the other parts of the characteristic polynomial here.}
+\textcolor{blue}{Waiting for Sally's proof!}
+
+A rare neo-Y or neo-W will spread from a given ancestral equilibrium when the leading eigenvalue, $\lambda$, of the Jacobian matrix derived from the eight mutant recursion equations (given by \ref{eq:recursions}c,d,g,h), evaluated at the ancestral equilibrium, is greater than one.
+However, because a neo-Y (neo-W) is always in males (females) and is epistatically dominant to the ancestral sex-determining locus, we need only two recursion equations (e.g., tracking the change in the frequency of neo-Y-$A$ and neo-Y-$a$ gametes from males) and thus the leading eigenvalue is the largest solution the polynomial $\lambda^2 + b\lambda + c = 0$ as described in the text (Table \ref{tab:haplotype_growth}).
+%It can be shown (see supplementary Mathematica file) that the coefficients are $b= - (\lambda_{mA} + \lambda_{ma})+(\chi_{mA} + \chi_{ma})$ and $c = (\lambda_{mA}-\chi_{mA}) (\lambda_{ma}-\chi_{ma}) -\chi_{mA} \chi_{ma}$, where $\lambda_{mi}$ is the multiplicative growth rate of the frequency of mutants on background $i\in\{A,a\}$, without accounting for loss due to recombination, and $\chi_{mi}$ is the rate at which mutants on background $i\in\{A,a\}$ recombine onto the other \textbf{A} locus background in heterozygotes.
+%The leading eigenvalue is then greater than one whenever $\lambda_{mA}>1$ and $\lambda_{ma}>1$, less than one whenever $\lambda_{mA}<1$ and $\lambda_{ma}<1$, and greater than one whenever  $\lambda_{mA}>1$ or $\lambda_{ma}>1$ and $\chi_{ma} (\lambda_{mA}-1) + \chi_{mA} (\lambda_{ma}-1) > 0$.
+
+The general conditions for the invasion of a neo-sex-determining allele are given in the main text, in terms of the haplotypic growth rates without accounting for loss due to recombination ($\lambda_{mi}$ terms) and the rates at which recombination between the \textbf{M} and \textbf{A} loci breaks apart these haplotypes ($\chi_{mi}$).
+For tight linkage between the ancestral sex-determining locus (\textbf{X}) and the selected locus (\textbf{A}) we can calculate these terms explicitly (see below).
+For weak selection we can take a Taylor series of the leading eigenvalue. 
+The leading eigenvalue, $\lambda$, for any $k$, is given up to order $\epsilon^2$ by equation \eqref{eq:lambda_ESD_k}.
+
+\subsubsection*{Tight linkage between \textbf{A} and \textbf{X} ($r \approx 0$)}
+
+Here, we explore the conditions under which a neo-W invades an XY system assuming that the \textbf{A} locus is initially in tight linkage with the ancestral sex-determining region ($r \approx 0$). 
+We disregard neo-Y mutations, which never spread given that the ancestral population is at a stable equilibrium (see \nameref{file:Mathematica} for proof).
+
+Starting with the simpler equilibrium $(B)$, the terms of that determine the leading eigenvalue are
+
+\begin{subequations}\label{Binvasion}
+\begin{align}
+\lambda_{mA}&= {\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]}^{-1}
+\frac{w_{A}^\female }{w_{A}^\female}
+\frac{\left[ w_{A}^\male (1+\alpha^\male_\Delta) w_{AA}^\female + 
+w_{a}^\male (1-\alpha^\male_\Delta) w_{Aa}^\female (1+\alpha^\female_\Delta) \right]}
+{ 2w_{AA}^\female } \\
+\lambda_{ma}&= {\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]}^{-1}
+\frac{w_{a}^\female}{w_{A}^\female}
+\frac{\left[  w_{A}^\male (1+\alpha^\male_\Delta) w_{Aa}^\female (1-\alpha^\female_\Delta)+
+w_{a}^\male (1-\alpha^\male_\Delta) w_{aa}^\female \right]}
+{ 2w_{AA}^\female } \\
+\chi_{mA}&= \frac{1}{2} {\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]}^{-1}
+\frac{w_{A}^\female }{w_{A}^\female}
+ \frac{\left[  w_{a}^\male (1-\alpha^\male_\Delta) w_{Aa}^\female (1 + \alpha^\female_\Delta) \right]}
+{ w_{AA}^\female } \frac{R}{2}\\
+\chi_{ma}&= \frac{1}{2} {\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]}^{-1}
+\frac{w_{a}^\female}{w_{A}^\female}
+ \frac{\left[  w_{A}^\male (1+\alpha^\male_\Delta) w_{Aa}^\female (1-\alpha^\female_\Delta) \right]}
+{  w_{AA}^\female} \frac{R}{2}
+\end{align}
+\end{subequations}
+
+%\noindent
+%In this case, the zygotic sex ratio ($\zeta$) is given by the difference in haploid selection in males on $a$ (fixed on the Y) and $A$ (fixed on the X) alleles, i.e., there are more males than females if $\zeta = \alpha^\male w_A^\male / [(1-\alpha^\male)w_a^\male + \alpha^\male w_A^\male]<1/2$.
+%$\alpha^\male<1/2$ and/or $w_{a}^\male>w_{A}^\male$.
+%Populations with haploid selection for $a$ in males have a male biased zygotic sex ratio are thus more permissive to invasion by a neo-W ($\lambda_{mA}$ and $\lambda_{ma}$ larger).
+%%In addition, the spread of neo-W alleles depends on the fitness of female diploids after mating with an X-$A$ or Y-$a$ male gamete, relative to the fitness of females in the population (all have genotype $AA$ and fitness $w_{AA}^\female$ at this equilibrium).
+%Haploid selection in males has a second effect; the spread rate of neo-W haplotypes is determined by their fitness in diploid females, which depends on their diploid genotype and thus on the male gamete they pair with.
+%Zygotes carrying dominant neo-W alleles will develop as females regardless of their genotype at the XY locus. 
+%Therefore, neo-W females result from matings with either X-$A$ or Y-$a$ male gametes. 
+%The relative proportion of these male gametes is determined by haploid selection in males; mating with a Y-$a$ male gamete is more likely if the $a$ allele is favoured during male gamete production or competition ($\zeta<1/2$).
+%Thus, neo-W females experience different diploid selection than XX females, and the extent of this difference depends on haploid selection in males.
+%Furthermore, haploid selection in females can directly select upon neo-W-$A$ or neo-W-$a$ haplotypes. 
+%A neo-W-$A$ female gamete has the same fitness during haploid competition as resident $A$-bearing female gametes. 
+%On the other hand, neo-W-$a$ female gametes can be favoured or disfavoured during female haploid competition (favoured if $w_{a}^\female>w_{A}^\female$). 
+%Meiotic drive in females ($\alpha^\female$) similarly affects the fitness of these neo-W haplotypes, except that it impacts both haplotypes as meiotic drive only occurs in heterozygotes and therefore does not occur in resident XX females (who are always homozygote $AA$).
+
+Haploid selection impacts the spread of neo-W haplotypes in three ways.
+Firstly, the zygotic sex ratio becomes male biased, $\zeta>1/2$, when the $a$ allele (which is fixed on the Y) is favoured during competition among male gametes or by meiotic drive in males.
+Specifically, at equilibrium $(B)$, female zygote frequency is $1 - \zeta = w_A^\male (1+\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$ where $2\bar{w}_{H}^\male= \big[w_a^\male (1-\alpha^\male_\Delta) +  w_A^\male (1+\alpha^\male_\Delta) \big]$ has been canceled out in equations \eqref{Binvasion} to leave the term ${\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]}^{-1}$.
+Male biased sex ratios facilitate the spread of a neo-W because neo-W alleles cause the zygotes that carry them to develop as the rarer, female, sex.
+
+Secondly, haploid selection in females selects on neo-W haplotypes directly.
+At equilibrium $(B)$, the fitness of female gametes under the ancestral sex-determining system is $w_{A}^\female$ such that the relative fitnesses of neo-W-$A$ and neo-W-$a$ haplotypes during female gametic competition are $w_{A}^\female/w_{A}^\female$ and $w_{a}^\female/w_{A}^\female$ (see terms in equation \ref{Binvasion}).
+Meiotic drive in females will also change the proportion of gametes that carry the $A$ versus $a$ alleles, which will be produced by heterozygous females in proportions $(1+\alpha_{\Delta}^\female)/2$ and $(1-\alpha_{\Delta}^\female)/2$, respectively.
+These terms are only associated with heterozygous females, i.e., they are found alongside $w_{Aa}^\female$.
+
+Thirdly, haploid selection in males affects the diploid genotypes of females by altering the allele frequencies in the male gametes with which female gametes pair.
+At equlibrium $(B)$, neo-W female gametes will mate with X-$A$ male gametes with probability $ w_A^\male (1+\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$ and Y-$a$ male gametes with probability $w_a^\male (1-\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$, where the $2\bar{w}_{H}^\male$ terms have been canceled in equation \eqref{Binvasion} (as mentioned above).
+Thus, neo-W-$A$ haplotypes are found in $AA$ female diploids with probability $ w_A^\male (1+\alpha^\male_\Delta)/ (2\bar{w}_{H}^\male)$ (e.g., first term in square brackets in the numerator of equation \ref{Binvasion}a) and in $Aa$ female diploids with probability $w_a^\male (1-\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$ (e.g., the second term in square brackets in the numerator of equation \ref{Binvasion}a).
+
+%For instance, because an epistatically dominant neo-W always causes its carrier to become female, it creates females who carry either Y-$a$ or X-$A$ genotypes from their father.
+%Thus, because when there is a polymorphism the X carries some non-zero frequency of $A$, haploid selection in males impacts the diploid genotypes of females (e.g., creating more $Aa$ females when drive in males favours Y-$a$).
+%How this affects the spread of the neo-W then depends on diploid and haploid selection in females.
+
+The other terms in equations \eqref{Binvasion} are more easily interpreted if we assume that there is no haploid selection in either sex, in which case $\lambda_{mA}=(w_{AA}^\female+w_{Aa}^\female)/2 w_{AA}^\female$ and $\lambda_{ma}=(w_{aa}^\female+w_{Aa}^\female)/ 2 w_{AA}^\female$.
+Neither haplotype can spread under purely sexually-antagonistic selection at equlibrium $(B)$, with directional selection in each sex.
+Essentially, the X is then already as specialized as possible for the female beneficial allele ($A$ is fixed on the X), and the neo-W often makes daughters with the Y-$a$ haplotype, increasing the flow of $a$ alleles into females, which reduces the fitness of those females.
+
+If selection doesn't uniformly favour $A$ in females, however, neo-W-$A$ haplotypes and/or neo-W-$a$ haplotypes can spread ($\lambda_{mA}>1$ and/or $\lambda_{ma}>1$).
+%If $\lambda_{mA}>1$ (requiring $w_{Aa}^\female>w_{AA}^\female$), the implication is that the neo-W can spread alongside the $A$ allele, despite the fact that the neo-W sometimes brings $Y-a$ haplotypes into females, because $a$ is favoured by selection in females despite $A$ being fixed on the X.
+A neo-W-$A$ haplotype can spread ($\lambda_{mA}>1$) when $w_{Aa}^\female>w_{AA}^\female$, despite the fact that a neo-W brings Y-$a$ haplotypes into females.
+In this case the $a$ allele is favoured by selection in females despite $A$ being fixed on the X.
+For this equilibrium to be stable (i.e.,  to keep $A$ fixed on the X), X-$a$ cannot be overly favoured in females and X-$A$ must be sufficiently favoured in males (for example, by overdominance in males).
+Specifically, from the stability conditions for equilibrium (B), we must have $w_{Aa}^\female < 2 w_{AA}^\female$ and $w_{Aa}^\male/\big[(w_{aa}^\male+w_{Aa}^\male)/2\big]>w_{Aa}^\female/w_{AA}^\female$.
+
+Still considering $w_{Aa}^\female>w_{AA}^\female$, the neo-W can also spread alongside the $a$ allele ($\lambda_{ma}>1$) if $w_{aa}^\female$ is large enough such that $(w_{Aa}^\female+w_{aa}^\female)/2>w_{AA}^\female$.
+%there is sufficiently strong underdominance in females ($w_{aa}^\female>w_{Aa}^\female$) \textcolor{blue}{[this is describing directional selection, not overdominance - check the conditions for the case we want to talk about]}, such that $(w_{Aa}^\female+w_{aa}^\female)/2>w_{AA}^\female$.
+This can occur with overdominance or directional selection for $a$ in females (Fig \ref{fig:regionplots}B,C).
+In this case, $a$ is favoured on the ancestral Y in males and on the ancestral X in females (comparing $Aa$ to $AA$ genotypes in females) but $A$ is fixed on the X due to selection in males. 
+The neo-W-$a$ haplotype can spread because it produces females with higher fitness $Aa$ and $aa$ genotypes.
+
+%When both haplotypes can spread on their own ($\lambda_{mA}>1$ and $\lambda_{ma}>1$), the neo-W invades regardless the recombination rate between it and the selected locus, $R$.
+%When neither haplotype can spread ($\lambda_{mA}<1$ and $\lambda_{ma}<1$) the neo-W can never invade.
+%And when only one haplotype can spread on its own the neo-W invades only when the rate of recombination onto the favourable background is sufficiently larger than the rate of recombination off this background (i.e., equation\ref{eq:lambdasGen} is satisfied).
+
+%Haploid selection affects the conclusions outlined above by altering the zygotic sex ratio and exerting direct selection on neo-W haplotypes.
+%The effect of sex ratio selection is straightforward and can be seen in equation \eqref{Binvasion}, where male drive and gamete competition for $a$ (which is fixed on the Y and therefore causes a male bias) increases all four terms.
+%Direct selection on neo-W haplotypes can also be seen in equation \eqref{Binvasion} by noticing that increasing female drive in favour of $A$ increases the neo-W-$A$ haplotype growth rate ($\lambda_{mA}$) while female drive and gamete competition in favour of $a$ increases the neo-W-$a$ haplotype growth rate ($\lambda_{ma}$).
+%Gamete competition in females does not impact the spread of neo-W-$A$ haplotypes because they are on the same background as the resident X.
+%Recombination between the selected locus and the neo-W complicates things slightly, as selective advantages for one neo-W haplotype during the haploid stage in females comes at a cost to the other, and thus recombination off the favoured background becomes more detrimental.
+
+%\textcolor{red}{the versions for equil $(A)$ are not terrible but could be improved by cleverly re-writing with the $\phi$ and $\psi$ terms from above, I think...}
+
+Similar equations can be derived for equilibrium (A) by substituting the equilibrium allele frequencies into Table \ref{tab:haplotype_growth}
+
+\begin{subequations}\label{Ainvasion}
+\begin{align}
+\lambda_{mA}&= \frac{a}{b} \left[w_{AA}^\female w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi +  w_{Aa}^\female (1+\alpha^\female_\Delta) w_a^\male c \right] / (2 w_a^\female) \\
+\lambda_{ma}&= \frac{a}{b} \left[ w_{Aa}^\female (1-\alpha^\female_\Delta) w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi +  w_{aa}^\female w_a^\male c \right] / (2 w_A^\female) \\
+\chi_{mA}&= \frac{a}{b} \frac{R}{2} \left[   w_{Aa}^\female (1+\alpha^\female_\Delta) w_a^\male c \right] / w_a^\female\\ 
+\chi_{ma}&= \frac{a}{b} \frac{R}{2} \left[ w_{Aa}^\female (1-\alpha^\female_\Delta) w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi \right] / w_A^\female
+\end{align}
+\end{subequations}
+
+\noindent
+where
+
+\begin{subequations}
+\begin{align}
+a &= w_a^\female \phi + w_A^\female \psi \\
+b &= w_{AA}^\female \left[ w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \right] \phi^2 + w_{Aa}^\female \left[ w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) + w_{aa}^\male w_a^\male \right] \psi \phi + w_{aa}^\female \left( w_{aa}^\male w_a^\male \right) \psi^2\\
+%c &= w_{Aa}^\male (1-\alpha^\male_\Delta) \phi \left[ w_{Aa}^\male (1+\alpha^\male_\Delta) \phi \right] + w_{Aa}^\male\phi \left[ 2w_{AA}^\male + w_{aa}^\male (1+\alpha^\male_\Delta) \right] \psi + w_{aa}^\male \psi \left(2w_{AA}^\male \psi \right) \\
+c &= w_{Aa}^\male (1-\alpha^\male_\Delta) \phi + 2w_{aa}^\male \psi
+\end{align}
+\end{subequations}
+
+\textcolor{red}{Sally suggests using some $\zeta$ term in the above equations}
+
+As with equilibrium (B), haploid selection again modifies invasion fitnesses by altering the ancestral sex ratio \textcolor{red}{(through $\zeta$)} and directly selecting upon female gametes textcolor{red}{(through $w_{i}^\female$)}.
+The only difference is that resident XX females are no longer always homozygote $AA$ and males are no longer always heterozygote $Aa$.
+Thus the effect of haploid selection in males is reduced, as is the difference in fitness between neo-W haplotypes and resident X haplotypes, as both can be on any diploid or haploid background.
+
+The other terms are easier to interpret in the absence of haploid selection.
+For instance, without haploid selection, the neo-W-$A$ haplotype spreads ($\lambda_{mA}>1$) if and only if
+
+\begin{equation}\label{eq:BeqWAspread}
+2(w_{Aa}^\female-w_{aa}^\female)w_{aa}^\male \psi^2 > (w_{AA}^\female-w_{Aa}^\female)w_{Aa}^\male \phi (\phi-\psi)
+\end{equation}
+
+\noindent  
+where $\phi-\psi=w_{AA}^\female w_{Aa}^\male-w_{aa}^\female w_{aa}^\male$ and both $\phi$ and $\psi$ are positive when equilibrium (A) is stable. 
+In contrast to equilibrium (B), a neo-W haplotype can spread under purely sexually-antagonistic selection  ($w_{aa}^\female<w_{Aa}^\female<w_{AA}^\female$ and $w_{AA}^\male<w_{Aa}^\male<w_{aa}^\male$).
+The neo-W-$A$ can spread as long as it becomes associated with females that bear more $A$ alleles than observed at equilibrium (A), effectively specializing on female fitness. 
+%In this case, the neo-W-$A$ haplotype can spread, despite producing a lot of $Aa$ daughters by obtaining the $a$ from Y-gametes, when $aa$ females, which the neo-W-$A$ never makes, are strongly selected against.
+%This can be intuited from the fact that \eqref{eq:BeqWAspread} will be more easily met when $w_{Aa}^\female-w_{aa}^\female\approx w_{Aa}^\female$ and $w_{AA}^\female-w_{Aa}^\female\approx 0$, implying $w_{aa}^\female \approx 0$ and $w_{Aa}^\female\approx w_{AA}^\female$ (although this is complicated by the fact that $w_{aa}^\female$ and $w_{Aa}^\female$ affect $\phi$ and $\psi$ too, the intuition holds).
+
+Without haploid selection, the neo-W-$a$ haplotype spreads ($\lambda_{ma}>1$) if and only if
+
+\begin{equation}\label{eq:BeqWaspread}
+(w_{aa}^\female + w_{Aa}^\female-2w_{AA}^\female)w_{Aa}^\male \phi^2 + (w_{aa}^\female-w_{Aa}^\female)(w_{Aa}^\male+2w_{aa}^\male) \phi \psi >0
+\end{equation}
+
+\noindent
+This condition cannot be met with purely sexually antagonistic selection (as both terms on the left-hand side would then be negative), but it can be met under other circumstances. 
+For example, with overdominance in males there is selection for increased $A$ frequencies on X chromosomes in males, which are always paired with Y-$a$ haplotypes.
+Directional selection for $a$ in females can then maintain a polymorphism at the $\textbf{A}$ locus on the X.
+This scenario selects for a modifier that increases recombination between the sex chromosomes (e.g., blue region of Fig 2d in~\cite{Otto2014}) and facilitates the spread of neo-W-$a$ haplotypes, which create females bearing more $a$ alleles than the ancestral X chromosome does.
+
+\subsubsection*{Role of haploid selection with tight linkage between \textbf{X} and \textbf{A}}
+
+Haploid selection generally expands the conditions under which neo-W alleles can spread within ancestral systems that have evolved tight linkage between the sex-determining locus and a selected locus ($r \approx 0$).
+First, haploid selection can allow a polymorphism to be maintained when it would not under diploid selection alone (e.g., with directional selection in diploids). 
+In cases of ploidally-antagonistic selection, where there is a balance between alleles favored in the haploid stage and the diploid stage, neo-W alleles - even unlinked alleles - can spread (\nameref{fig:regionPloidAntag}).
+Second, even when diploid selection could itself maintain a polymorphism, haploid selection can increase the conditions under which transitions among sex chromosomes are possible.
+Of particularly importance, when selection is sexually-antagonistic in diploids ($s^\female s^\male <0$ and $0<h^\Hermaphrodite<1$), an unlinked neo-W ($R=1/2$) cannot invade unless there is also haploid selection (see proof in \nameref{file:Mathematica}; Fig \ref{fig:SexAntagTighter} and \nameref{fig:SexAntagTighterMaleDrive}).
+More generally, haploid selection alters the conditions under which neo-W chromosomes can spread (compare \nameref{fig:regionMaleDrive}-\nameref{fig:regionFemaleGS} to Fig \ref{fig:regionplots}).
+
+%[SALLY:  I think that is enough, but we could add somewhere??: "Without haploid selection, unlinked neo-W alleles ($R=1/2$) can invade only under certain conditions, requiring either overdominance in males or underdominance in females (see proof in supplementary \textit{Mathematica} file).?
+Note that underdominance in females with directional selection in males can lead to the spread of unlinked neo-W?s, but only from equilB (only $\lambda_{ma}$ is greater than one in this case).]
+
+Male haploid selection in favour of the $a$ allele ($\alpha_{\Delta}^\male<0$, $w_{A}^\male<w_{a}^\male$) generates male-biased sex ratios at equilibria (A) and (B), where Y-$a$ is fixed ($\hat{p}_{Y}^\male=0$).
+Male-biased sex-ratios facilitate the spread of neo-W-$A$ and neo-W-$a$ haplotypes (increasing $\lambda_{mA}$ and $\lambda_{ma}$). 
+Panels A-C in \nameref{fig:regionMaleDrive} and \ref{fig:regionMaleGS} show that neo-W haplotypes tend to spread for a wider range of parameters when sex ratios are male biased, compared to Fig \ref{fig:regionplots} without haploid selection.
+By contrast, male haploid selection in favour of the $A$ allele generates female-biased sex ratios and reduces $\lambda_{mA}$ and $\lambda_{ma}$, as demonstrated by panels D-F in \nameref{fig:regionMaleDrive} and \nameref{fig:regionMaleGS}.
+
+Female haploid selection generates direct selection on the neo-W-$A$ and neo-W-$a$ haplotypes as they spread in females. 
+Thus, female haploid selection in favour of the $a$ allele tends to increase $\lambda_{ma}$ and decrease $\lambda_{mA}$, as shown by panels A-C in \nameref{fig:regionFemaleDrive} and \nameref{fig:regionFemaleGS}.
+Conversely, female haploid selection in favour of the $A$ allele increases $\lambda_{mA}$ and decreases $\lambda_{ma}$, see panels D-F in \nameref{fig:regionFemaleDrive} and \nameref{fig:regionFemaleGS}.
+
+Thus, the impact of haploid selection on sex chromosome transitions must be considered as two sides of a coin: it can generate sex ratio biases that drive sex chromosome transitions to equalize the sex ratio, but it can also drive in new sex chromosomes and thereby cause sex ratios to become biased.
+
 \end{document}

### 2018-01-19 LaTeX/Turnover_plos.tex
supp fig legends edited

@@
 \label{fig:positionOverdominance}
-{\bf Neo-W alleles can spread when loci under diploid selection are tightly linked to the ancestral sex determining locus ($r\approx0$). } 
+{\bf With overdominance, loci near to the ancestral sex-determining locus ($r\approx0$) can favour neo-W alleles that are less tightly linked ($R>r$).} 
 In panels A and B, the $a$ allele is favoured in females ($w_{aa}^\female=1.05$, $w_{Aa}^\Hermaphrodite=1$, $w_{AA}^\female=0.85$) and selection in males is overdominant ($w_{aa}^\male=w_{AA}^\male=0.75$).
@@
 There is no haploid selection $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
-These parameters are marked by daggers in Fig \ref{fig:regionplots}B and C, which show that neo-W invasion is expected for any $R$ ($\lambda_{WA},\lambda_{Wa}>1$) when the $a$ allele is nearly fixed on the Y (black lines in this figure; not stable for $r>>0$).
+These parameters are marked by daggers in Fig \ref{fig:regionplots}B and C, which show that neo-W invasion is expected for any $R$ ($\lambda_{WA},\lambda_{Wa}>1$) if the $a$ allele is nearly fixed on the Y (black lines in this figure; not stable for $r>>0$).
 Equilibria where the $A$ allele is more common among Y-bearing male gametes can also be stable and allow neo-W invasion for these parameters (blue lines). 
-The weak selection approximation holds when all recombination rates are large relative to selection (around 0 in panels A and C), in which case, in the absence of haploid selection, neo-W alleles should spread if and only if they are more tightly linked to the selected locus (positive invasion fitness if and only if the selected locus is in the grey region).
-However, when recombination rates are small (panels B and D and when the selected locus is near the SDRs in all panels), this weak selection prediction can break down.
+%The weak selection approximation holds when all recombination rates are large relative to selection (around 0 in panels A and C), in which case, in the absence of haploid selection, neo-W alleles should spread if and only if they are more tightly linked to the selected locus (positive invasion fitness if and only if the selected locus is in the grey region).
+%However, when recombination rates are small (panels B and D and when the selected locus is near the SDRs in all panels), this weak selection prediction can break down.
 
@@
 \label{fig:temporalOverdominance}
-{\bf Following invasion by a neo-W allele, there can be a complete transition to a new sex-determination system, maintenance of polymorphism at both ancestral-XY and neo-ZW sex determining regions, or loss of the new sex-determining allele.
-}
-Here we plot the frequency of the neo-W allele among female gametes; as the neo-W reaches frequency $0.5$, polymorphism at the ancestral XY locus is lost with Y becoming fixed such that sex is determined only be the ZW allele carried by a female gamete.
+{\bf Following invasion by a neo-W allele, there can be a complete transition to a new sex-determination system, maintenance of both ancestral-XY and neo-ZW sex determining regions, or loss of the new sex-determining allele.}
+Here, we plot the frequency of the neo-W allele among female gametes.
+%; as the neo-W reaches frequency $0.5$, polymorphism at the ancestral XY locus is lost with Y becoming fixed such that sex is determined only be the ZW allele carried by a female gamete. 
 Panels A, C and D show cases where a steady state is reached with the neo-W at a frequency below $0.5$, in which case ancestral-X and Y alleles also both segregate. 
@@
 In B, this leads to loss of the neo-W and the system goes to an equilibrium with X-$a$ and Y-$A$ haplotypes fixed (equilibrium $A'$), such that all females have the high fitness genotype $aa$ and all males are $Aa$.
-For the parameters in B, neo-W alleles have negative invasion fitness when the Y-$A$ haplotype is ancestrally more common than Y-$a$ (see blue lines in \nameref{fig:positionOverdominance}A and  \nameref{fig:positionOverdominance}B near the ancestral SDR).
-In contrast, the neo-W is not lost in panel D as it is favoured near $r\approx0$ (see blue lines in \nameref{fig:positionOverdominance}C and  \nameref{fig:positionOverdominance}D near the ancestral SDR).
-Fitness parameters are the same as in \nameref{fig:positionOverdominance}; in panels A and B the $a$ allele is favoured in females ($w_{aa}^\female=1.05$, $w_{Aa}^\Hermaphrodite=1$, $w_{AA}^\female=0.85$) while there is overdominance in males ($w_{aa}^\male=w_{AA}^\male=0.75$) and in panels C and D, there is overdominance in both sexes ($w_{aa}^\female=w_{AA}^\female=0.6$, $w_{aa}^\male=0.5$, $w_{AA}^\male=0.7$, $w_{Aa}^\Hermaphrodite=1$).
-These parameters are marked by a dagger in Fig \ref{fig:regionplots}. 
-Here, there is no haploid selection $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
+For the parameters in B, neo-W alleles have negative invasion fitness when the Y-$A$ haplotype is ancestrally more common than Y-$a$ (compare blue to black curves in \nameref{fig:positionOverdominance}A and  \nameref{fig:positionOverdominance}B near the ancestral SDR).
+In contrast, the neo-W is not lost in panel D as it is favoured regardless of whether Y-$A$ or Y-$a$ predominates (again, compare blue to black curves in \nameref{fig:positionOverdominance}C and  \nameref{fig:positionOverdominance}D).
+%Fitness parameters are the same as in \nameref{fig:positionOverdominance}; in panels A and B the $a$ allele is favoured in females ($w_{aa}^\female=1.05$, $w_{Aa}^\Hermaphrodite=1$, $w_{AA}^\female=0.85$) while there is overdominance in males ($w_{aa}^\male=w_{AA}^\male=0.75$) and in panels C and D, there is overdominance in both sexes ($w_{aa}^\female=w_{AA}^\female=0.6$, $w_{aa}^\male=0.5$, $w_{AA}^\male=0.7$, $w_{Aa}^\Hermaphrodite=1$).
+%These parameters are marked by a dagger in Fig \ref{fig:regionplots}. 
+%Here, there is no haploid selection $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
 
@@
 \label{fig:regionMaleDrive}
-{\bf Meiotic drive in males affects whether neo-W-$A$ and neo-W-$a$ haplotypes spread when the ancestral-XY locus is tightly linked to a locus under selection ($r=0$).}
-We vary the fitness of male homozygotes relative to heterozygotes ($w_{Aa}^\Hermaphrodite=1$) and only consider stable equilibria at which both \textbf{A} locus allele are maintained and the $a$ allele is initially fixed on the Y, region outlined.
+{\bf Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is male meiotic drive at a locus that is tightly linked to the ancestral-XY locus ($r=0$).}
+Figure is equivalent to Fig \ref{fig:regionplots} but with meiotic drive in males.
+%We vary the fitness of male homozygotes relative to heterozygotes ($w_{Aa}^\Hermaphrodite=1$) and only consider stable equilibria at which both \textbf{A} locus allele are maintained and the $a$ allele is initially fixed on the Y, region outlined.
 In panels A-C, meiotic drive in males favours the $a$ allele ($\alpha_{\Delta}^\male=-0.16$), creating male-biased sex ratios and generally increasing $\lambda_{WA}$ and $\lambda_{Wa}$. 
 By contrast, $\lambda_{WA}$ and $\lambda_{Wa}$ tend to be reduced when meiotic drive in males favours the $A$ allele ($\alpha_{\Delta}^\male=0.16$), panels D-F. 
-We consider three forms of selection in females: directional selection in favour of the $A$ allele (panels A and D, $w_{aa}^\female=0.85$, $w_{AA}^\female=1.05$), direction selection in favour of the $a$ allele (panels B and E, $w_{aa}^\female=1.05$, $w_{AA}^\female=0.85$), and overdominance (panels C and F, $w_{aa}^\female=w_{AA}^\female=0.6$).
+%We consider three forms of selection in females: directional selection in favour of the $A$ allele (panels A and D, $w_{aa}^\female=0.85$, $w_{AA}^\female=1.05$), direction selection in favour of the $a$ allele (panels B and E, $w_{aa}^\female=1.05$, $w_{AA}^\female=0.85$), and overdominance (panels C and F, $w_{aa}^\female=w_{AA}^\female=0.6$).
 
@@
 \label{fig:regionMaleGS}
-{\bf Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is male gametic competition at a locus that is tightly linked to the ancestral-XY locus.}
-Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in \nameref{fig:regionMaleDrive}. 
+{\bf Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is male gametic competition at a locus that is tightly linked to the ancestral-XY locus ($r=0$).}
+Figure is equivalent to Fig \ref{fig:regionplots} but with gametic competition in males.
+%Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in \nameref{fig:regionMaleDrive}. 
 The $a$ allele is favoured during male gametic competition in Panels A-C ($w_{a}^\male=1.16$, $w_{A}^\male=1$), which creates male biased sex ratios and increases $\lambda_{WA}$ and $\lambda_{Wa}$. 
-On the other hand, the $A$ allele is favoured during male gametic competition in Panels D-F ($w_{a}^\male=1$, $w_{A}^\male=1.16$) and $\lambda_{WA}$ and $\lambda_{Wa}$ tend to be reduced. 
+By contrast, $\lambda_{WA}$ and $\lambda_{Wa}$ tend to be reduced when the $A$ allele is favoured during male gametic competition, panels D-F.
 Compared to the meiotic drive parameters in \nameref{fig:regionMaleDrive}, the effect of these male gametic competition parameters on the sex ratio is smaller. 
@@
 \label{fig:regionFemaleDrive}
-{\bf Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is female meiotic drive at a locus that is tightly linked to the ancestral-XY locus.}
-Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in \nameref{fig:regionMaleDrive} and \nameref{fig:regionMaleGS}. 
+{\bf Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is female meiotic drive at a locus that is tightly linked to the ancestral-XY locus ($r=0$).}
+Figure is equivalent to Fig \ref{fig:regionplots} but with meiotic drive in females.
+%Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in \nameref{fig:regionMaleDrive} and \nameref{fig:regionMaleGS}. 
 The $a$ allele is favoured by meiotic drive in females in Panels A-C ($\alpha_{\Delta}^\female=-0.16$), which increases $\lambda_{Wa}$ and decreases $\lambda_{WA}$. 
@@
 \label{fig:regionFemaleGS}
-Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is female gametic competition at a locus that is tightly linked to the ancestral-XY locus.
-Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in \nameref{fig:regionMaleDrive}, \nameref{fig:regionMaleGS}, and \nameref{fig:regionFemaleDrive}. 
+{\bf Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is female gametic competition at a locus that is tightly linked to the ancestral-XY locus ($r=0$).}
+Figure is equivalent to Fig \ref{fig:regionplots} but with gametic competition in females.
+%Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in \nameref{fig:regionMaleDrive}, \nameref{fig:regionMaleGS}, and \nameref{fig:regionFemaleDrive}. 
 The $a$ allele is favoured during female gametic competition in females in Panels A-C ($w_{a}^\female=1.16$, $w_{A}^\female=1$), which increases $\lambda_{Wa}$ and decreases $\lambda_{WA}$. 
@@
 \label{fig:regionPloidAntag}
-{\bf A-D show when each of the neo-W haplotypes invade an internally stable equilibrium with $a$ fixed on the Y (found by setting $r=0$).}
+{\bf Ploidally-antagonistic selection can drive the spread of neo-W chromosomes. }
+A-D show when each of the neo-W haplotypes invades an internally stable equilibrium with $a$ fixed on the Y (found by setting $r=0$).
 The y-axis shows directional selection in diploids of both sexes, $s^\female=s^\male$, and the x-axes show sex-specific drive, $\alpha_\Delta^\Hermaphrodite$, or haploid competition, $t^\Hermaphrodite$.
@@
 \label{fig:freqAll}
-Fixation of neo-W or maintenance of multiple sex-determining systems. 
+{\bf Pseudo-fixation of neo-W or maintenance of multiple sex-determining alleles. }
 The curves show the frequencies of the neo-W (red), ancestral-Y (blue), and $A$ allele (black) among female gametes (solid curves) and among male gametes (dashed curves). 

### 2018-01-22 LaTeX/Supp_Figures_and_Table.tex
lambda consistency fixed, haploid mean fitness in table s2 improved, author summary edited

@@
 
+\section*{Supplementary Tables}
+
 \begin{table}[ht]
@@
 
-\begin{table}[ht]
+\begin{table}[!h]
 \centering
@@
   $p_X^\female w_A^\female + (1-p_X^\female) w_a^\female$ \\ [0.5ex] \hline  \noalign{\vskip 0.5ex}
+  X-bearing male gametes ($\bar{w}_{HX}^\male$) & 
+  $p_X^{\male} w_A^\male + (1-p_X^{\male}) w_a^\male$ \\ [0.5ex] \hline  \noalign{\vskip 0.5ex}
+  Y-bearing male gametes ($\bar{w}_{HY}^\male$) & 
+  $p_Y^{\male} w_A^\male + (1-p_Y^{\male}) w_a^\male$ \\ [0.5ex] \hline  \noalign{\vskip 0.5ex}
   male gametes ($\bar{w}_H^\male$) & 
-  $\bar{p}^{\male} w_A^\male + (1-\bar{p}^{\male}) w_a^\male$ \\ [0.5ex] \hline  \noalign{\vskip 0.5ex}
+  $(1-q) \bar{w}_{HX}^\male + q \bar{w}_{HY}^\male$ \\ [0.5ex] \hline  \noalign{\vskip 0.5ex}
   females ($\bar{w}^\female$) & 
-  $\begin{array}{l}  (1-\zeta)^{-1} \big[ p_X^\female w_A^\female p_X^\male w_A^\male w_{AA}^\female + \\
+%  $\begin{array}{l}  (1-\zeta)^{-1} (1-q) \big[ p_X^\female w_A^\female p_X^\male w_A^\male w_{AA}^\female + \\
+%  (1 - p_X^\female) w_a^\female p_X^\male w_A^\male w_{Aa}^\female + \\
+%  p_X^\female w_A^\female (1 - p_X^\male) w_a^\male w_{Aa}^\female + \\
+%  (1-p_X^\female) w_a^\female (1 - p_X^\male) w_a^\male w_{aa}^\female \big] / \left( \bar{w}_H^\female \bar{w}_H^\male \right)
+%  \end{array} 
+ $\begin{array}{l} \big[ p_X^\female w_A^\female p_X^\male w_A^\male w_{AA}^\female + \\
   (1 - p_X^\female) w_a^\female p_X^\male w_A^\male w_{Aa}^\female + \\
   p_X^\female w_A^\female (1 - p_X^\male) w_a^\male w_{Aa}^\female + \\
-  (1-p_X^\female) w_a^\female (1 - p_X^\male) w_a^\male w_{aa}^\female \big] / \left( \bar{w}_H^\female \bar{w}_H^\male \right)
+  (1-p_X^\female) w_a^\female (1 - p_X^\male) w_a^\male w_{aa}^\female \big] / \left( \bar{w}_H^\female \bar{w}_{HX}^\male \right)
   \end{array}
@@
   males ($\bar{w}^\male$) & 
-  $\begin{array}{l} \zeta^{-1} \big[ p_X^\female w_A^\female  p_Y^\male w_A^\male w_{AA}^\male + \\
+%  $\begin{array}{l} \zeta^{-1} q \big[ p_X^\female w_A^\female  p_Y^\male w_A^\male w_{AA}^\male + \\
+%  (1 - p_X^\female) w_a^\female  p_Y^\male w_A^\male w_{Aa}^\male + \\
+%  p_X^\female w_A^\female  (1 - p_Y^\male) w_a^\male w_{Aa}^\male + \\
+%  (1-p_X^\female) w_a^\female  (1 - p_Y^\male) w_a^\male w_{aa}^\male \big] / \left( \bar{w}_H^\female \bar{w}_H^\male \right) 
+%  \end{array}
+ $\begin{array}{l} \big[ p_X^\female w_A^\female  p_Y^\male w_A^\male w_{AA}^\male + \\
   (1 - p_X^\female) w_a^\female  p_Y^\male w_A^\male w_{Aa}^\male + \\
   p_X^\female w_A^\female  (1 - p_Y^\male) w_a^\male w_{Aa}^\male + \\
-  (1-p_X^\female) w_a^\female  (1 - p_Y^\male) w_a^\male w_{aa}^\male \big] / \left( \bar{w}_H^\female \bar{w}_H^\male \right) 
+  (1-p_X^\female) w_a^\female  (1 - p_Y^\male) w_a^\male w_{aa}^\male \big] / \left( \bar{w}_H^\female \bar{w}_{HY}^\male \right) 
   \end{array}
@@
 
+\newpage
 \section*{Supplementary Figures}
@@
 There is no haploid selection $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
-These parameters are marked by daggers in Figure \ref{fig:regionplots}B and C, which show that neo-W invasion is expected for any $R$ ($\lambda_{WA},\lambda_{Wa}>1$) when the $a$ allele is nearly fixed on the Y (black lines in this figure; not stable for $r>>0$).
+These parameters are marked by daggers in Figure \ref{fig:regionplots}B and C, which show that neo-W invasion is expected for any $R$ ($\lambda_{W'A}^{(XY)},\lambda_{W'a}^{(XY)}>1$) when the $a$ allele is nearly fixed on the Y (black lines in this figure; not stable for $r>>0$).
 Equilibria where the $A$ allele is more common among Y-bearing male gametes can also be stable and allow neo-W invasion for these parameters (blue lines). 
@@
 In panels A-C, meiotic drive in males favours the $a$ allele ($\alpha_{\Delta}^\male=-0.16$), creating male-biased sex ratios and generally increasing $\lambda_{WA}$ and $\lambda_{Wa}$. 
-By contrast, $\lambda_{WA}$ and $\lambda_{Wa}$ tend to be reduced when meiotic drive in males favours the $A$ allele ($\alpha_{\Delta}^\male=0.16$), panels D-F. 
+By contrast, $\lambda_{W'A}^{(XY)}$ and $\lambda_{W'a}^{(XY)}$ tend to be reduced when meiotic drive in males favours the $A$ allele ($\alpha_{\Delta}^\male=0.16$), panels D-F. 
 We consider three forms of selection in females: directional selection in favour of the $A$ allele (panels A and D, $w_{aa}^\female=0.85$, $w_{AA}^\female=1.05$), direction selection in favour of the $a$ allele (panels B and E, $w_{aa}^\female=1.05$, $w_{AA}^\female=0.85$), and overdominance (panels C and F, $w_{aa}^\female=w_{AA}^\female=0.6$).
@@
 Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in Figure \ref{fig:regionMaleDrive}. 
-The $a$ allele is favoured during male gametic competition in Panels A-C ($w_{a}^\male=1.16$, $w_{A}^\male=1$), which creates male biased sex ratios and increases $\lambda_{WA}$ and $\lambda_{Wa}$. 
-On the other hand, the $A$ allele is favoured during male gametic competition in Panels D-F ($w_{a}^\male=1$, $w_{A}^\male=1.16$) and $\lambda_{WA}$ and $\lambda_{Wa}$ tend to be reduced. 
+The $a$ allele is favoured during male gametic competition in Panels A-C ($w_{a}^\male=1.16$, $w_{A}^\male=1$), which creates male biased sex ratios and increases $\lambda_{W'A}^{(XY)}$ and $\lambda_{W'a}^{(XY)}$.
+On the other hand, the $A$ allele is favoured during male gametic competition in Panels D-F ($w_{a}^\male=1$, $w_{A}^\male=1.16$) and $\lambda_{W'A}^{(XY)}$ and $\lambda_{W'a}^{(XY)}$ tend to be reduced.
 Compared to the meiotic drive parameters in Figure \ref{fig:regionMaleDrive}, the effect of these male gametic competition parameters on the sex ratio is smaller. 
@@
 Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in Figure \ref{fig:regionMaleDrive} and \ref{fig:regionMaleGS}. 
-The $a$ allele is favoured by meiotic drive in females in Panels A-C ($\alpha_{\Delta}^\female=-0.16$), which increases $\lambda_{Wa}$ and decreases $\lambda_{WA}$. 
+The $a$ allele is favoured by meiotic drive in females in Panels A-C ($\alpha_{\Delta}^\female=-0.16$), which increases $\lambda_{W'a}^{(XY)}$ and decreases $\lambda_{W'A}^{(XY)}$. 
 Female meiotic drive in favour of the $A$ allele (panels D-F, $\alpha_{\Delta}^\female=-0.16$) has the opposite effect. 
@@
 Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in Figure \ref{fig:regionMaleDrive}, \ref{fig:regionMaleGS}, and \ref{fig:regionFemaleDrive}. 
-The $a$ allele is favoured during female gametic competition in females in Panels A-C ($w_{a}^\female=1.16$, $w_{A}^\female=1$), which increases $\lambda_{Wa}$ and decreases $\lambda_{WA}$. 
-The $A$ allele is favoured during gametic competition in panels D-F ($w_{a}^\female=1$, $w_{A}^\female=1.16$), giving the opposite effect on $\lambda_{Wa}$ and $\lambda_{WA}$. 
+The $a$ allele is favoured during female gametic competition in females in Panels A-C ($w_{a}^\female=1.16$, $w_{A}^\female=1$), which increases $\lambda_{W'a}^{(XY)}$ and decreases $\lambda_{W'A}^{(XY)}$.
+The $A$ allele is favoured during gametic competition in panels D-F ($w_{a}^\female=1$, $w_{A}^\female=1.16$), giving the opposite effect on $\lambda_{W'a}^{(XY)}$ and $\lambda_{W'A}^{(XY)}$. 
 }

### 2018-01-22 LaTeX/Turnover_plos.tex
lambda consistency fixed, haploid mean fitness in table s2 improved, author summary edited

@@
 Prevailing views suggest that new sex determination systems are favoured when they equalize the sex ratio and/or when they are more closely linked to genes that experience differential selection in males and females.
-Our models include selection upon haploid genotypes (meiotic drive or gametic competition), which both causes sex ratio biases and occurs differently in males and females. 
+Our models extend theory to include selection upon haploid genotypes (meiotic drive or gametic competition), which both causes sex ratio biases and occurs differently in males and females. 
 Surprisingly, we find that neither force (sex ratio selection nor associations with genes that have sex-specific effects) dominates the spread of new sex determination systems alone. 
-Even more unexpectedly, we find that new sex-determining alleles do not necessarily have to arise in closer linkage with genes that are differentially selected in males and females. 
-Therefore, our models predict loci in unexpected genomic locations and/or experiencing various types of selection (including haploid selection) can now be implicated as drivers of transitions between sex determination systems.
+Even more unexpectedly, we find that new sex-determining alleles do not necessarily have to arise in closer linkage with genes that are differentially selected in males and females to spread. 
+Therefore, our models predict loci in previously unexpected genomic locations and/or experiencing various types of selection (including haploid selection) can now be implicated as drivers of transitions between sex determination systems.
 
@@
 The evolution of a new sex-determination system requires that a rare mutant allele at the novel sex-determining locus, $m$, increases in frequency when rare. 
-The spread of a rare mutant $m$ at the \textbf{M} locus is determined by the leading eigenvalue, $\lambda$, of the system of eight equations describing the frequency of eggs and sperm carrying the $m$ allele in the next generation (equations \ref{eq:recursions}).
+The spread of a rare mutant $m$ at the \textbf{M} locus is determined by the leading eigenvalue of the system of eight equations describing the frequency of eggs and sperm carrying the $m$ allele in the next generation (equations \ref{eq:recursions}).
 %, evaluated at the above equilibrium.
@@
 Furthermore, if the $m$ allele is fully epistatically dominant over the ancestral sex-determining system, phenotypes are not affected by the genotype at the ancestral sex-determining region (\textbf{X} locus).
-Thus, the invasion of rare dominant neo-Y or neo-W alleles is determined by the largest eigenvalue that solves the quadratic, $\lambda^2+ b \lambda + c =0$ \textcolor{blue}{(see \nameref{app:inv_cond} for a discussion of other roots - or Sally's proof!)}.
-Here, $b= - (\lambda_{mA} + \lambda_{ma})+(\chi_{mA} + \chi_{ma})$ and $c = (\lambda_{mA}-\chi_{mA}) (\lambda_{ma}-\chi_{ma}) -\chi_{mA} \chi_{ma}$, where $\lambda_{mi}$ is the multiplicative growth rate (which we will call the ``haplotypic growth rate'') of the neo-sex determination allele $m$ on background $i$ without accounting for loss due to recombination, and $\chi_{mi}$ is the rate at which mutant haplotypes on background $i\in\{A,a\}$ recombine onto the other \textbf{A} locus background in heterozygotes (see Table \ref{tab:haplotype_growth}).
-The $\lambda_{mi}$ and $\chi_{mi}$, and thus the spread of the mutant $m$ allele, depend on the frequency of alleles at the \textbf{A} and \textbf{X} loci in the ancestral population. 
+Thus, the invasion of a rare dominant neo-Y or neo-W allele, $m$, into a system with ancestral sex-determination system $i\in\{XY,ZW\}$ is determined by the largest solution of the quadratic, $(\Lambda_m^{(i)})^2+ b \Lambda_m^{(i)} + c =0$ \textcolor{blue}{(see \nameref{app:inv_cond} for a discussion of other roots - or Sally's proof!)}.
+Here, $b= - (\lambda_{mA}^{(i)} + \lambda_{ma}^{(i)})+(\chi_{mA}^{(i)} + \chi_{ma}^{(i)})$ and $c = (\lambda_{mA}^{(i)} - \chi_{mA}^{(i)}) (\lambda_{ma}^{(i)} - \chi_{ma}^{(i)}) - \chi_{mA}^{(i)} \chi_{ma}^{(i)}$, where $\lambda_{mj}^{(i)}$ is the multiplicative growth rate (which we will call the ``haplotypic growth rate'') of the neo-sex determination allele $m$ on background $j\in\{A,a\}$ without accounting for loss due to recombination ($R=0$), and $\chi_{mj}$ is the rate at which mutant haplotypes on background $j\in\{A,a\}$ recombine onto the other \textbf{A} locus background in heterozygotes (see Table \ref{tab:haplotype_growth}).
+To differentiate between the invasion of neo-Y and neo-W alleles we write $m=Y'$ or $m=W'$, respectively (e.g., $\lambda_{Y'A}$ is the growth rate of neo-Y alleles on the $A$ background when $R=0$).
+The $\lambda_{mj}^{(i)}$ and $\chi_{mj}^{(i)}$, and thus the spread of the mutant $m$ allele, depend on the frequency of alleles at the \textbf{A} and \textbf{X} loci in the ancestral population. 
 In the ancestral population, it is convenient to follow the frequency of the $A$ allele among female gametes (eggs), $p^\female_X$, and among X-bearing, $p^\male_X$, and among Y-bearing, $p^\male_Y$, male gametes (sperm/pollen).
@@
    $m$ is a neo-Y ($k=0$) \\ [0.5ex] \hline \noalign{\vskip 1ex}
-  $\lambda_{YA} = {\left( 2 \zeta \right)}^{-1} \left[\hat{p}_X^\female w_{A}^{\female} w_{A}^{\male} w_{AA}^{\male} + (1-\hat{p}_X^\female) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} (1+\alpha_{\Delta}^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\male}_{D} \right) $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\lambda_{Ya} = {\left( 2 \zeta \right)}^{-1} \left[(1-\hat{p}_X^\female) w_{a}^{\female} w_{a}^{\male} w_{aa}^{\male} + \hat{p}_X^\female w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male}(1 - \alpha_{\Delta}^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\male}_{D} \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\chi_{YA} = R {\left( 2 \zeta \right)}^{-1} \left[ (1-\hat{p}_X^\female) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} (1+\alpha_{\Delta}^{\male}) \right]/  \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\male}_{D} \right)   $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\chi_{Ya} = R {\left( 2 \zeta \right)}^{-1} \left[   \hat{p}_X^\female w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male} (1 - \alpha_\Delta^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\male}_{D} \right)  $\\ [1ex] \hline
+  $\lambda_{Y'A}^{(XY)} = {\left( 2 \zeta \right)}^{-1} \left[\hat{p}_X^\female w_{A}^{\female} w_{A}^{\male} w_{AA}^{\male} + (1-\hat{p}_X^\female) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} (1+\alpha_{\Delta}^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\male}_{D} \right) $\\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\lambda_{Y'a}^{(XY)} = {\left( 2 \zeta \right)}^{-1} \left[(1-\hat{p}_X^\female) w_{a}^{\female} w_{a}^{\male} w_{aa}^{\male} + \hat{p}_X^\female w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male}(1 - \alpha_{\Delta}^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\male}_{D} \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\chi_{Y'A}^{(XY)} = R {\left( 2 \zeta \right)}^{-1} \left[ (1-\hat{p}_X^\female) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} (1+\alpha_{\Delta}^{\male}) \right]/  \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\male}_{D} \right)   $\\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\chi_{Y'a}^{(XY)} = R {\left( 2 \zeta \right)}^{-1} \left[   \hat{p}_X^\female w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male} (1 - \alpha_\Delta^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\male}_{D} \right)  $\\ [1ex] \hline
   \noalign{\vskip 0.5ex}
   $m$ is a neo-W ($k=1$) \\ [0.5ex] \hline \noalign{\vskip 1ex}
-  $\lambda_{WA} = {\left[ 2 (1 - \zeta) \right]}^{-1} \left[ \bar{p}^{\male} w_{A}^{\male} w_{A}^{\female} w_{AA}^{\female}+(1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female}(1+\alpha_{\Delta}^{\female})\right]/ \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\female}_{D} \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\lambda_{Wa} = {\left[ 2 (1 - \zeta) \right]}^{-1} \left[ (1-\bar{p}^{\male}) w_{a}^{\male} w_{a}^{\female} w_{aa}^{\female}+\bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female}(1-\alpha_{\Delta}^{\female})\right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\female}_{D} \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\chi_{WA} = R {\left[ 2 (1 - \zeta) \right]}^{-1} \left[ (1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female} (1+\alpha_{\Delta}^{\female}) \right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\female}_{D} \right)  $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\chi_{Wa} = R {\left[ 2 (1 - \zeta) \right]}^{-1} \left[ \bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female} (1-\alpha_{\Delta}^{\female}) \right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\female}_{D} \right) $ \\ [1ex]
+  $\lambda_{W'A}^{(XY)} = {\left[ 2 (1 - \zeta) \right]}^{-1} \left[ \bar{p}^{\male} w_{A}^{\male} w_{A}^{\female} w_{AA}^{\female}+(1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female}(1+\alpha_{\Delta}^{\female})\right]/ \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\female}_{D} \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\lambda_{W'a}^{(XY)} = {\left[ 2 (1 - \zeta) \right]}^{-1} \left[ (1-\bar{p}^{\male}) w_{a}^{\male} w_{a}^{\female} w_{aa}^{\female}+\bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female}(1-\alpha_{\Delta}^{\female})\right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\female}_{D} \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\chi_{W'A}^{(XY)} = R {\left[ 2 (1 - \zeta) \right]}^{-1} \left[ (1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female} (1+\alpha_{\Delta}^{\female}) \right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\female}_{D} \right)  $\\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\chi_{W'a}^{(XY)} = R {\left[ 2 (1 - \zeta) \right]}^{-1} \left[ \bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female} (1-\alpha_{\Delta}^{\female}) \right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\female}_{D} \right) $ \\ [1ex]
   \hline \hline 
@@
 
-We are particularly concerned with the conditions under which a rare neo-sex-determining allele increases in frequency, which occurs when the largest eigenvalue, $\lambda$, is greater than one. 
+We are particularly concerned with the conditions under which a rare neo-sex-determining allele increases in frequency, which occurs when the largest eigenvalue is greater than one. 
 %If the average change in frequency of the two haplotypes that carry the $m$ allele ($Am$ and $am$) is positive, invasion will always occur, i.e., if $(\lambda_{mA} + \lambda_{ma})/2 > 1$ then $\lambda > 1$.
-The leading eigenvalue solves $f(\lambda)=\lambda^2+b\lambda+c=0$ and the Perron-Frobenius theorem guarantees that the leading eigenvalue is positive, unique, and real.  
-Since $f(\lambda_{mA})$ and $f(\lambda_{ma})$ are of opposite signs, the leading eigenvalue must fall between these two quantities and is the larger of them when $R = 0$ (see \nameref{file:Mathematica}).
-Consequently, if both $\lambda_{mA}$ and $\lambda_{ma}$ are greater than one, then the leading eigenvalue will always be greater than one, regardless of the linkage between the neo-sex determination factor and the selected locus ($R$).
-In particular, having $\lambda_{mA} >1$ and $\lambda_{ma}>1$ thus guarantees that an unlinked sex determining factor can invade ($R=1/2$).  
-Conversely, if both $\lambda_{mA}$ and $\lambda_{ma}$ are smaller than one, then invasion can never occur.  
-Finally, if only one of  $\lambda_{mA}$ and $\lambda_{ma}$ is greater than one, the new sex determining factor can always invade when tightly linked to the selected locus ($R$ near 0).  
+The leading eigenvalue is the largest solution of $f(\Lambda_m^{(i)})=(\Lambda_m^{(i)})^2+b\Lambda_m^{(i)}+c=0$ and the Perron-Frobenius theorem guarantees that it is positive, unique, and real.  
+Since $f(\lambda_{mA}^{(i)})$ and $f(\lambda_{ma}^{(i)})$ are of opposite signs, the leading eigenvalue must fall between these two quantities and is the larger of them when $R = 0$ (see \nameref{file:Mathematica}).
+Consequently, if both $\lambda_{mA}^{(i)}$ and $\lambda_{ma}^{(i)}$ are greater than one, then the leading eigenvalue will always be greater than one, regardless of the linkage between the neo-sex determination factor and the selected locus ($R$).
+In particular, having $\lambda_{mA}^{(i)} >1$ and $\lambda_{ma}^{(i)}>1$ thus guarantees that an unlinked sex determining factor can invade ($R=1/2$).  
+Conversely, if both $\lambda_{mA}^{(i)}$ and $\lambda_{ma}^{(i)}$ are smaller than one, then invasion can never occur.  
+Finally, if only one of  $\lambda_{mA}^{(i)}$ and $\lambda_{ma}^{(i)}$ is greater than one, the new sex determining factor can always invade when tightly linked to the selected locus ($R$ near 0).  
 Furthermore, it can be shown that the leading eigenvalue declines with $R$, and invasion requires that $R$ is sufficiently small that the following condition holds: 
@@
 %\frac{\chi_{mA}}{\lambda_{mA}-1}+\frac{\chi_{ma}}{\lambda_{ma}-1}>0.
-\chi_{ma}/\left(\lambda_{ma}-1\right) + \chi_{mA}/\left(\lambda_{mA}-1\right) < 1.
+\chi_{ma}^{(i)}/\left(\lambda_{ma}^{(i)} - 1\right) + \chi_{mA}^{(i)}/\left(\lambda_{mA}^{(i)} - 1\right) < 1.
 \end{equation}
@@
 This condition may or may not be satisfied for the full range of locations of the new sex determining factor, including $R=1/2$, depending on the nature of selection.  
-Interpreting this condition, if we assume that only the $mA$ haplotype has a positive growth rate when $R=0$, $\lambda_{ma}<1<\lambda_{mA}$, the first term on the left-hand side of \eqref{eq:lambdasGen} is negative and invasion requires that the $mA$ haplotype growth rate ($\lambda_{mA}-1$) and the rate at which they are produced by recombination in $ma$ haplotypes ($\chi_{ma}$) are sufficiently large relative to the $ma$ haplotype rate of decline ($1-\lambda_{ma}$) and the rate of loss of $mA$ haplotypes due to recombination ($\chi_{mA}$).
+Interpreting this condition, if we assume that only the $mA$ haplotype has a positive growth rate when $R=0$, $\lambda_{ma}^{(i)}<1<\lambda_{mA}^{(i)}$, the first term on the left-hand side of \eqref{eq:lambdasGen} is negative and invasion requires that the $mA$ haplotype growth rate ($\lambda_{mA}^{(i)} - 1$) and the rate at which they are produced by recombination in $ma$ haplotypes ($\chi_{ma}^{(i)}$) are sufficiently large relative to the $ma$ haplotype rate of decline ($1-\lambda_{ma}^{(i)}$) and the rate of loss of $mA$ haplotypes due to recombination ($\chi_{mA}^{(i)}$).
 
 We can draw a number of key points about the invasion of neo-Y and neo-W mutations from Table \ref{tab:haplotype_growth}. 
-First, Fisherian sex ratio selection will favour the spread of a neo-Y if the ancestral zygotic sex ratio is biased towards females, $\zeta<1/2$ (i.e., the first factor of the $\lambda_{mi}$ is greater than one for a neo-Y and less than one for a neo-W).
+First, Fisherian sex ratio selection will favour the spread of a neo-Y if the ancestral zygotic sex ratio is biased towards females, $\zeta<1/2$ (i.e., the first factor of the $\lambda_{mi}^{(i)}$ is greater than one for a neo-Y and less than one for a neo-W).
 However, the spread of a neo-Y (neo-W) also depends on the male (female) fitness of associated alleles (see terms involving equilibrium allele frequencies, $\hat{p}$'s).
@@
 We find that a neo-Y can never invade an ancestral XY system that already has tight linkage with the locus under selection ($r=0$, for details see \nameref{file:Mathematica}). 
-When $R=0$, a neo-Y haplotype with the same allele as the ancestral Y is neutral ($\lambda_{Ya}=1$) and does not change in frequency.
-The other neo-Y haplotype will not spread ($\lambda_{YA}<1$) given that the initial equilibrium is stable. 
-Therefore, a neo-Y mutation cannot spread ($\lambda \leq 1$, regardless of $R$) in an ancestral XY system where selected loci are within or very near the non-recombining region around the SDR.
+When $R=0$, a neo-Y haplotype with the same allele as the ancestral Y is neutral ($\lambda_{Y'a}^{(XY)}=1$) and does not change in frequency.
+The other neo-Y haplotype will not spread ($\lambda_{Y'A}^{(XY)}<1$) given that the initial equilibrium is stable. 
+Therefore, a neo-Y mutation cannot spread in an ancestral XY system ($\Lambda_{Y'}^{(XY)} \leq 1$, regardless of $R$) where selected loci are within or very near the non-recombining region around the SDR.
 In essence, through tight linkage with the \textbf{A} locus, the ancestral Y becomes strongly specialized on the allele that has the highest fitness across male haploid and diploid phases. 
@@
 
-If we categorise the $a$ allele as being ancestrally `male-beneficial' via the fact that it is fixed on the Y, then $\lambda_{WA}>1$ indicates that the neo-W spreads when found with the ancestrally `female-beneficial' allele.
+If we categorise the $a$ allele as being ancestrally `male-beneficial' via the fact that it is fixed on the Y, then $\lambda_{W'A}^{(XY)}>1$ indicates that the neo-W spreads when found with the ancestrally `female-beneficial' allele.
 Broadly, this is possible because the ancestral X chromosome is sometimes found in males and is therefore unable to perfectly specialise on the `female-beneficial' allele. 
 For example, when the $a$ allele is favoured on the ancestral X in males, a polymorphism of $A$ and $a$ alleles can be maintained on the X despite directional selection in favour of the $A$ allele in females ($s^\female>0$, $0<h^\female<1$), see outlined region in Fig \ref{fig:regionplots}A.
-When the $a$ allele is strongly favoured on X chromosomes in males ($w_{aa}^\male$ sufficiently large relative to $w_{Aa}^\male$), neo-W-$A$ haplotypes can spread ($\lambda_{WA}>1$, see grey region in Fig \ref{fig:regionplots}A) because they produce hgher fitness females ($AA$ or $Aa$ genotypes) and are unleashed from counterselection in males.
+When the $a$ allele is strongly favoured on X chromosomes in males ($w_{aa}^\male$ sufficiently large relative to $w_{Aa}^\male$), neo-W-$A$ haplotypes can spread ($\lambda_{W'A}^{(XY)}>1$, see grey region in Fig \ref{fig:regionplots}A) because they produce hgher fitness females ($AA$ or $Aa$ genotypes) and are unleashed from counterselection in males.
 
@@
 Here, selection in females can favour the $A$ allele (panel A, $w_{aa}^\female=0.85$, $w_{AA}^\female=1.05$), favour the $a$ allele (panel B, $w_{aa}^\female=1.05$, $w_{AA}^\female=0.85$), or be overdominant (panel C, $w_{aa}^\female=w_{AA}^\female=0.6$).
-If $\lambda_{wA}$ or $\lambda_{wa}$ is greater than one, then a rare neo-W can spread for, at least, some values of $R>r$. 
+If $\lambda_{W'A}^{(XY)}$ or $\lambda_{W'a}^{(XY)}$ is greater than one, then a rare neo-W can spread for, at least, some values of $R>r$. 
 The parameter values marked with an asterisk correspond to the fitnesses used in Fig \ref{fig:SexAntagTighter}C. 
-Where both $\lambda_{wA}$ and $\lambda_{wa}$ are greater than one, a neo-W will spread when rare, regardless of linkage with the selected locus (for any $R$). 
+Where both $\lambda_{W'A}^{(XY)}$ and $\lambda_{W'a}^{(XY)}$ are greater than one, a neo-W will spread when rare, regardless of linkage with the selected locus (for any $R$). 
 \nameref{fig:positionOverdominance} shows the dynamics using the parameters marked with a dagger. 
@@
 
-Given that the $a$ allele can be considered ancestrally `male-beneficial' because it is fixed on the Y, it is surprising that neo-W-$a$ haplotypes can sometimes be favoured by selection in females ($\lambda_{Wa}>1$).
+Given that the $a$ allele can be considered ancestrally `male-beneficial' because it is fixed on the Y, it is surprising that neo-W-$a$ haplotypes can sometimes be favoured by selection in females ($\lambda_{W'a}^{(XY)}>1$).
 Again, this occurs because ancestral X's also experience selection in males, in which they will always be paired with a Y-$a$. 
@@
 
-Assuming that selection is weak ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon<<1$) and thus implicitly assuming that all recombination rates ($r$, $R$ and $\rho$) are large relative to selection, we denote the leading eigenvalues describing the invasion of a neo-Y ($k=0$) and a neo-W ($k=1$) into an ancestrally XY system by $\lambda_{Y',XY}$ and $\lambda_{W',XY}$, respectively.
-To leading order in selection, these are:
+Here we assume that selection is weak ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon<<1$) and thus implicitly assuming that all recombination rates ($r$, $R$ and $\rho$) are large relative to selection.
+%, we denote the leading eigenvalues describing the invasion of a neo-Y ($k=0$) and a neo-W ($k=1$) into an ancestrally XY system by $\Lambda_{Y',XY}$ and $\Lambda_{W',XY}$, respectively. 
+To leading order in selection, the leading eigenvalues are:
 
 \begin{equation}
-\lambda_{Y',XY} =1+ \frac{1}{4}V_{A}S_{A}^2\frac{ \left( r-R \right) }{r R}+O\left(\epsilon^3 \right) 
+\Lambda_{Y'}^{(XY)} =1+ \frac{1}{4}V_{A}S_{A}^2\frac{ \left( r-R \right) }{r R}+O\left(\epsilon^3 \right) 
 \label{eq:lambda_neoY}
@@
 \begin{equation}
-\lambda_{W',XY} =\lambda_{Y',XY}+\left(2\alpha_{\Delta}^\male-2\alpha_{\Delta}^\female+t^\male-t^\female \right) \left( \hat{p}^\male_Y-\hat{p}^\male_X \right)/2
+\Lambda_{W'}^{(XY)} =\Lambda_{Y'}^{(XY)}+\left(2\alpha_{\Delta}^\male-2\alpha_{\Delta}^\female+t^\male-t^\female \right) \left( \hat{p}^\male_Y-\hat{p}^\male_X \right)/2
 +O\left(\epsilon^3 \right)
@@
 
-The neo-sex-determining allele, $m$, will spread if $\lambda_{m,XY}>1$. 
+The neo-sex-determining allele, $m$, will spread in an XY system if $\Lambda_{m}^{(XY)}>1$. 
 Equation \eqref{eq:lambda_neoY} demonstrates that, under weak selection, a neo-Y will invade an XY system if and only if it is more closely linked to the selected locus than the ancestral sex-determining region (i.e., if $R<r$; note that $V_{A}S_{A}^2$ is strictly positive as long as \textbf{A} is polymorphic).
@@
 
-With weak selection and no haploid selection ($t^\Hermaphrodite=\alpha^\Hermaphrodite_{\Delta}=0$), the spread of a neo-W is equivalent to the spread of a neo-Y ($\lambda_{W',XY}=\lambda_{Y',XY}$), such that trans-GSD transitions (XY to ZW or ZW to XY) can also occur only if the neo-sex-determining region is more closely linked to a locus under selection ($R<r$), as found by \cite{vanDoorn:2010hu}.
-With haploid selection, however, the additional term in equation \eqref{eq:lambda_neoW} can be positive, which can allow, for example, neo-W invasion ($\lambda_{W',XY}>1$) even when the neo-sex-determining region is less closely linked to the selected locus ($R>r$).
+With weak selection and no haploid selection ($t^\Hermaphrodite=\alpha^\Hermaphrodite_{\Delta}=0$), the spread of a neo-W is equivalent to the spread of a neo-Y ($\Lambda_{W'}^{(XY)}=\Lambda_{Y'}^{(XY)}$), such that trans-GSD transitions (XY to ZW or ZW to XY) can also occur only if the neo-sex-determining region is more closely linked to a locus under selection ($R<r$), as found by \cite{vanDoorn:2010hu}.
+With haploid selection, however, the additional term in equation \eqref{eq:lambda_neoW} can be positive, which can allow, for example, neo-W invasion ($\Lambda_{W'}^{(XY)}>1$) even when the neo-sex-determining region is less closely linked to the selected locus ($R>r$).
 %These transitions are unusual because, when $R>r$, associations that selection has built up between alleles more favourable in one sex and alleles that determine sex will be weakened. 
@@
 Equation \eqref{eq:lambda_neoW} shows that, with weak selection, neo-W alleles can invade an XY system for a large number of selective regimes. 
-To clarify the parameter space under which $\lambda_{W',XY}>1$, we consider several special cases. 
+To clarify the parameter space under which $\Lambda_{W'}^{(XY)}>1$, we consider several special cases. 
 Firstly, if the \textbf{A} locus is unlinked to the ancestral sex-determining region ($r=1/2$), a more closely linked neo-W ($R<1/2$) can always invade because there is no ancestral association between $A$ alleles and sex chromosomes in males, $\left( \hat{p}^\male_Y-\hat{p}^\male_X \right)=0$, see equation \eqref{eq:freq_diffs}.
@@
 \hline\hline
-Scenario &  Assumptions & neo-W spreads ($\lambda_{W',XY}>1$) if \\ [0.5ex] \hline
+Scenario &  Assumptions & neo-W spreads ($\Lambda_{W'}^{(XY)}>1$) if \\ [0.5ex] \hline
 %  $r=1/2$, $R<1/2$ & Always \\ [0.5ex] \hline
@@
 %However, to leading order with selection weak relative to recombination, we find that sex ratio selection favours the spread of a neo-W (through the first terms in table \ref{tab:haplotype_growth}) by an amount that is equal in magnitude to the fitness effects of alleles associated with new sex-determining alleles (second terms in table \ref{tab:haplotype_growth}).
-However, invasion by a neo-W into an XY system and invasion by a neo-Y into a ZW system occur under the same conditions ($\lambda_{Y',XY}=\lambda_{W',ZW}$ and $\lambda_{Y',ZW}=\lambda_{W',XY}$, at least to order $\epsilon^2$).
+However, invasion by a neo-W into an XY system and invasion by a neo-Y into a ZW system occur under the same conditions ($\Lambda_{Y'}^{(XY)} = \Lambda_{W'}^{(XY)}$ and $\Lambda_{Y'}^{(XY)}=\Lambda_{W'}^{(XY)}$, at least to order $\epsilon^2$).
 For example, in Fig \ref{fig:SexRatioBad}A neo-W alleles invade an ancestral-XY system where females are initially rare.
@@
 \begin{split}
-\lambda_{ESD',XY} =& 1 + \frac{{(1-2k)}^2}{4}V_{A}{S_{A}}^2\frac{r-R}{r R} \\
+\Lambda_{ESD'}^{(XY)} =& 1 + \frac{{(1-2k)}^2}{4}V_{A}{S_{A}}^2\frac{r-R}{r R} \\
 &+\frac{k(\hat{p}^\male_Y-\hat{p}^\male_X)}{2}\left[ k \left(2\alpha_{\Delta}^\male-2\alpha_{\Delta}^\female+t^\male-t^\female \right) -2(1-k)S_{A}\right]+O\left(\epsilon^3\right),
@@
 \noindent
-which reduces to $\lambda_{Y',XY}$ when $k=0$ and $\lambda_{W',XY}$ when $k=1$.
+which reduces to $\Lambda_{Y'}^{(XY)}$ when $k=0$ and $\Lambda_{W'}^{(XY)}$ when $k=1$.
 
@@
 \begin{equation}
-\lambda_{ESD',XY} =1+ \frac{1}{2}\frac{(\lambda_{Y',XY\rvert R=1/2}-1) + (\lambda_{W',XY\rvert R=1/2}-1)}{2} + O\left(\epsilon^3\right),
+\Lambda_{ESD'}^{(XY)} =1+ \frac{1}{2}\frac{(\Lambda_{Y'\rvert R=1/2}^{(XY)}-1) + (\Lambda_{W'\rvert R=1/2}^{(XY)}-1)}{2} + O\left(\epsilon^3\right),
 %V_A \frac{r}{1-2r}  \frac{s_{f} \left( s^\male - 3 s^\female\right) }{8 {\left( s_{f} + s_{m} \right)}^2} t_{m}^2.
@@
 \noindent
-where $\lambda_{Y',XY\rvert R=1/2}$ and $\lambda_{W',XY\rvert R=1/2}$ represent $\lambda_{Y',XY}$ and $\lambda_{W',XY}$ when evaluated at $R=1/2$ (Equations \ref{eq:lambda_neoY} and \ref{eq:lambda_neoW}).
+where $\Lambda_{Y'\rvert R=1/2}^{(XY)}$ and $\Lambda_{W'\rvert R=1/2}^{(XY)}$ represent $\Lambda_{Y'}^{(XY)}$ and $\Lambda_{W'}^{(XY)}$ when evaluated at $R=1/2$ (Equations \ref{eq:lambda_neoY} and \ref{eq:lambda_neoW}).
 That is, recombination between the selected locus and the novel sex-determining locus, $R$, doesn't enter into the $k=1/2$ results.
@@
 Equation \eqref{eq:lambda_ESD} shows that the neo-ESD gets half of the fitness of a feminizing mutation (neo-$W$) and half of the fitness of a masculinizing mutation (neo-$Y$), but only has an effect one half of the time (the other half of the time it produces the same sex as the ancestral system would have).
-As discussed above, $\lambda_{Y',XY\rvert R=1/2}$ is necessarily less than one, but $\lambda_{W',XY\rvert R=1/2}$ can be greater than one if there is haploid selection.
+As discussed above, $\Lambda_{Y'\rvert R=1/2}^{(XY)}$ is necessarily less than one, but $\Lambda_{W'\rvert R=1/2}^{(XY)}$ can be greater than one if there is haploid selection.
 That is, when there is haploid selection, ESD mutations can invade an ancestrally-XY system because they generate females that are either rare or have high fitness, in the same manner as a neo-W.
@@
 
-Significantly, equation \eqref{eq:lambda_ESD} is the same whether ESD is invading an ancestrally XY or ZW system (because $\lambda_{Y',XY} = \lambda_{W',ZW}$ and $\lambda_{W',XY} = \lambda_{Y',ZW}$).
+Significantly, equation \eqref{eq:lambda_ESD} is the same whether ESD is invading an ancestrally XY or ZW system (because $\Lambda_{Y'}^{(XY)} = \Lambda_{W'}^{(ZW)}$ and $\Lambda_{W'}^{(XY)} = \Lambda_{Y'}^{(ZW)}$).
 Thus, Fisherian sex ratio selection alone does not easily explain the invasion of ESD.
 For example, when the ancestral sex-determination system is XY, but not ZW, the sex ratio is biased by male haploid selection.
-Nevertheless, ESD is equally likely to invade when it equalizes the zygotic sex ratio (through $\lambda_{W',XY}$) and when it doesn't (through $\lambda_{Y',ZW}$). 
+Nevertheless, ESD is equally likely to invade when it equalizes the zygotic sex ratio (through $\Lambda_{W'}^{(XY)}$) and when it doesn't (through $\Lambda_{Y'}^{(ZW)}$). 
 %This is again because haploid selection can facilitate the turnover of sex chromosomes either through sex ratio biases or through associations between the new sex determining region with selected alleles.
 %With weak selection, these two forces are nearly equal in strength. 
-In addition, we note that ESD may not invade, even if the sex ratio is initially biased (e.g., with drive in males only, $r<1/2$, $h^\female=h^\male$, and $s^\female s^\male<0$, then $\lambda_{W',XY}<1$, see Table \ref{tab:specialcases}).
+In addition, we note that ESD may not invade, even if the sex ratio is initially biased (e.g., with drive in males only, $r<1/2$, $h^\female=h^\male$, and $s^\female s^\male<0$, then $\Lambda_{W'}^{(XY)}<1$, see Table \ref{tab:specialcases}).
 We conclude that, as with neo-W and neo-Y loci, associations with selected loci mean that the evolution of neo-ESD systems is not straightforwardly predicted by selection to balance the zygotic sex ratio when haploid selection is present.
@@
 Turnovers driven by haploid selection may help to explain the relative rarity of heteromorphic sex chromosomes in plants, which are thought to experience more selection during their multicellular haploid stage.
-If haploid selection is strong but selective differences between male and female diploids are weak, we find that trans-GSD transitions (XY to ZW or ZW to XY) are favoured more strongly than cis-GSD transitions, with transitions to ESD intermediate (e.g., with $|D^\male - D^\female| << |\alpha_\Delta^\male - \alpha_\Delta^\female + t^\male - t^\female|$ we have $\lambda_{W',XY} > \lambda_{Y',XY}$; Equations \ref{eq:lambda_neoW} and \ref{eq:freq_diffs}).
+If haploid selection is strong but selective differences between male and female diploids are weak, we find that trans-GSD transitions (XY to ZW or ZW to XY) are favoured more strongly than cis-GSD transitions, with transitions to ESD intermediate (e.g., with $|D^\male - D^\female| << |\alpha_\Delta^\male - \alpha_\Delta^\female + t^\male - t^\female|$ we have $\Lambda_{W'}^{(XY)} > \Lambda_{Y'}^{(XY)}$; Equations \ref{eq:lambda_neoW} and \ref{eq:freq_diffs}).
 Among the relatively few dioecious clades in which multiple species have well characterized sex chromosomes~\cite{Ming:2011iy}, trans-GSD transitions have been inferred in \textit{Silene} subsection \textit{Otites}~\cite{Slancarova:2013dq} and in \textit{Salicaceae}~\cite{Pucholt2015,Pucholt2017}.
@@
 There is no haploid selection $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
-These parameters are marked by daggers in Fig \ref{fig:regionplots}B and C, which show that neo-W invasion is expected for any $R$ ($\lambda_{WA},\lambda_{Wa}>1$) if the $a$ allele is nearly fixed on the Y (black lines in this figure; not stable for $r>>0$).
+These parameters are marked by daggers in Fig \ref{fig:regionplots}B and C, which show that neo-W invasion is expected for any $R$ ($\lambda_{W'A}^{(XY)},\lambda_{W'a}^{(XY)}>1$) if the $a$ allele is nearly fixed on the Y (black lines in this figure; not stable for $r>>0$).
 Equilibria where the $A$ allele is more common among Y-bearing male gametes can also be stable and allow neo-W invasion for these parameters (blue lines). 
@@
 %We vary the fitness of male homozygotes relative to heterozygotes ($w_{Aa}^\Hermaphrodite=1$) and only consider stable equilibria at which both \textbf{A} locus allele are maintained and the $a$ allele is initially fixed on the Y, region outlined.
-In panels A-C, meiotic drive in males favours the $a$ allele ($\alpha_{\Delta}^\male=-0.16$), creating male-biased sex ratios and generally increasing $\lambda_{WA}$ and $\lambda_{Wa}$. 
-By contrast, $\lambda_{WA}$ and $\lambda_{Wa}$ tend to be reduced when meiotic drive in males favours the $A$ allele ($\alpha_{\Delta}^\male=0.16$), panels D-F. 
+In panels A-C, meiotic drive in males favours the $a$ allele ($\alpha_{\Delta}^\male=-0.16$), creating male-biased sex ratios and generally increasing $\lambda_{W'A}^{(XY)}$ and $\lambda_{W'a}^{(XY)}$.
+By contrast, $\lambda_{W'A}^{(XY)}$ and $\lambda_{W'a}^{(XY)}$ tend to be reduced when meiotic drive in males favours the $A$ allele ($\alpha_{\Delta}^\male=0.16$), panels D-F. 
 %We consider three forms of selection in females: directional selection in favour of the $A$ allele (panels A and D, $w_{aa}^\female=0.85$, $w_{AA}^\female=1.05$), direction selection in favour of the $a$ allele (panels B and E, $w_{aa}^\female=1.05$, $w_{AA}^\female=0.85$), and overdominance (panels C and F, $w_{aa}^\female=w_{AA}^\female=0.6$).
@@
 %Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in \nameref{fig:regionMaleDrive}. 
-The $a$ allele is favoured during male gametic competition in Panels A-C ($w_{a}^\male=1.16$, $w_{A}^\male=1$), which creates male biased sex ratios and increases $\lambda_{WA}$ and $\lambda_{Wa}$. 
-By contrast, $\lambda_{WA}$ and $\lambda_{Wa}$ tend to be reduced when the $A$ allele is favoured during male gametic competition, panels D-F.
+The $a$ allele is favoured during male gametic competition in Panels A-C ($w_{a}^\male=1.16$, $w_{A}^\male=1$), which creates male biased sex ratios and increases $\lambda_{W'A}^{(XY)}$ and $\lambda_{W'a}^{(XY)}$.
+By contrast, $\lambda_{W'A}^{(XY)}$ and $\lambda_{W'a}^{(XY)}$ tend to be reduced when the $A$ allele is favoured during male gametic competition, panels D-F.
 Compared to the meiotic drive parameters in \nameref{fig:regionMaleDrive}, the effect of these male gametic competition parameters on the sex ratio is smaller. 
@@
 %Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in \nameref{fig:regionMaleDrive} and \nameref{fig:regionMaleGS}. 
-The $a$ allele is favoured by meiotic drive in females in Panels A-C ($\alpha_{\Delta}^\female=-0.16$), which increases $\lambda_{Wa}$ and decreases $\lambda_{WA}$. 
+The $a$ allele is favoured by meiotic drive in females in Panels A-C ($\alpha_{\Delta}^\female=-0.16$), which increases $\lambda_{W'a}^{(XY)}$ and decreases $\lambda_{W'A}^{(XY)}$. 
 Female meiotic drive in favour of the $A$ allele (panels D-F, $\alpha_{\Delta}^\female=-0.16$) has the opposite effect.
@@
 %Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in \nameref{fig:regionMaleDrive}, \nameref{fig:regionMaleGS}, and \nameref{fig:regionFemaleDrive}. 
-The $a$ allele is favoured during female gametic competition in females in Panels A-C ($w_{a}^\female=1.16$, $w_{A}^\female=1$), which increases $\lambda_{Wa}$ and decreases $\lambda_{WA}$. 
-The $A$ allele is favoured during gametic competition in panels D-F ($w_{a}^\female=1$, $w_{A}^\female=1.16$), giving the opposite effect on $\lambda_{Wa}$ and $\lambda_{WA}$.
+The $a$ allele is favoured during female gametic competition in females in Panels A-C ($w_{a}^\female=1.16$, $w_{A}^\female=1$), which increases $\lambda_{W'a}^{(XY)}$ and decreases $\lambda_{W'A}^{(XY)}$.
+The $A$ allele is favoured during gametic competition in panels D-F ($w_{a}^\female=1$, $w_{A}^\female=1.16$), giving the opposite effect on $\lambda_{W'a}^{(XY)}$ and $\lambda_{W'A}^{(XY)}$.
 
@@
 
-A rare neo-Y or neo-W will spread from a given ancestral equilibrium when the leading eigenvalue, $\lambda$, of the Jacobian matrix derived from the eight mutant recursion equations (given by \ref{eq:recursions}c,d,g,h), evaluated at the ancestral equilibrium, is greater than one.
-However, because a neo-Y (neo-W) is always in males (females) and is epistatically dominant to the ancestral sex-determining locus, we need only two recursion equations (e.g., tracking the change in the frequency of neo-Y-$A$ and neo-Y-$a$ gametes from males) and thus the leading eigenvalue is the largest solution the polynomial $\lambda^2 + b\lambda + c = 0$ as described in the text (Table \ref{tab:haplotype_growth}).
+A rare neo-Y or neo-W allele, $m$, will spread from a given ancestral equilibrium with sex-determination system $i\in\{XY,ZW\}$ when the leading eigenvalue, $\Lambda_m^{(i)}$, of the Jacobian matrix derived from the eight mutant recursion equations (given by \ref{eq:recursions}c,d,g,h), evaluated at the ancestral equilibrium, is greater than one.
+However, because a neo-Y (neo-W) is always in males (females) and is epistatically dominant to the ancestral sex-determining locus, we need only two recursion equations (e.g., tracking the change in the frequency of neo-Y-$A$ and neo-Y-$a$ gametes from males) and thus the leading eigenvalue is the largest solution the polynomial $(\Lambda_m^{(i)})^2 + b\Lambda_m^{(i)} + c = 0$ as described in the text (Table \ref{tab:haplotype_growth}).
 %It can be shown (see supplementary Mathematica file) that the coefficients are $b= - (\lambda_{mA} + \lambda_{ma})+(\chi_{mA} + \chi_{ma})$ and $c = (\lambda_{mA}-\chi_{mA}) (\lambda_{ma}-\chi_{ma}) -\chi_{mA} \chi_{ma}$, where $\lambda_{mi}$ is the multiplicative growth rate of the frequency of mutants on background $i\in\{A,a\}$, without accounting for loss due to recombination, and $\chi_{mi}$ is the rate at which mutants on background $i\in\{A,a\}$ recombine onto the other \textbf{A} locus background in heterozygotes.
@@
 
-The general conditions for the invasion of a neo-sex-determining allele are given in the main text, in terms of the haplotypic growth rates without accounting for loss due to recombination ($\lambda_{mi}$ terms) and the rates at which recombination between the \textbf{M} and \textbf{A} loci breaks apart these haplotypes ($\chi_{mi}$).
+The general conditions for the invasion of a neo-sex-determining allele are given in the main text, in terms of the haplotypic growth rates without accounting for loss due to recombination ($\lambda_{mj}^{(i)}$ terms) and the rates at which recombination between the \textbf{M} and \textbf{A} loci breaks apart these haplotypes ($\chi_{mj}^{(i)}$).
 For tight linkage between the ancestral sex-determining locus (\textbf{X}) and the selected locus (\textbf{A}) we can calculate these terms explicitly (see below).
 For weak selection we can take a Taylor series of the leading eigenvalue. 
-The leading eigenvalue, $\lambda$, for any $k$, is given up to order $\epsilon^2$ by equation \eqref{eq:lambda_ESD_k}.
+The leading eigenvalue for any $k$ is given up to order $\epsilon^2$ by equation \eqref{eq:lambda_ESD_k}.
 
@@
 \begin{align}
-\lambda_{mA}&= {\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]}^{-1}
+\lambda_{W'A}^{(XY)}&= {\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]}^{-1}
 \frac{w_{A}^\female }{w_{A}^\female}
@@
 { 2w_{AA}^\female } \\
-\lambda_{ma}&= {\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]}^{-1}
+\lambda_{W'a}^{(XY)}&= {\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]}^{-1}
 \frac{w_{a}^\female}{w_{A}^\female}
@@
 { 2w_{AA}^\female } \\
-\chi_{mA}&= \frac{1}{2} {\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]}^{-1}
+\chi_{W'A}^{(XY)}&= \frac{1}{2} {\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]}^{-1}
 \frac{w_{A}^\female }{w_{A}^\female}
@@
 { w_{AA}^\female } \frac{R}{2}\\
-\chi_{ma}&= \frac{1}{2} {\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]}^{-1}
+\chi_{W'a}^{(XY)}&= \frac{1}{2} {\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]}^{-1}
 \frac{w_{a}^\female}{w_{A}^\female}
@@
 
-The other terms in equations \eqref{Binvasion} are more easily interpreted if we assume that there is no haploid selection in either sex, in which case $\lambda_{mA}=(w_{AA}^\female+w_{Aa}^\female)/2 w_{AA}^\female$ and $\lambda_{ma}=(w_{aa}^\female+w_{Aa}^\female)/ 2 w_{AA}^\female$.
-Neither haplotype can spread under purely sexually-antagonistic selection at equlibrium $(B)$, with directional selection in each sex.
+The other terms in equations \eqref{Binvasion} are more easily interpreted if we assume that there is no haploid selection in either sex, in which case $\lambda_{W'A}^{(XY)}=(w_{AA}^\female+w_{Aa}^\female)/2 w_{AA}^\female$ and $\lambda_{W'a}^{(XY)}=(w_{aa}^\female+w_{Aa}^\female)/ 2 w_{AA}^\female$.
+Neither haplotype can spread under purely sexually-antagonistic selection at equilibrium $(B)$, with directional selection in each sex.
 Essentially, the X is then already as specialized as possible for the female beneficial allele ($A$ is fixed on the X), and the neo-W often makes daughters with the Y-$a$ haplotype, increasing the flow of $a$ alleles into females, which reduces the fitness of those females.
 
-If selection doesn't uniformly favour $A$ in females, however, neo-W-$A$ haplotypes and/or neo-W-$a$ haplotypes can spread ($\lambda_{mA}>1$ and/or $\lambda_{ma}>1$).
+If selection doesn't uniformly favour $A$ in females, however, neo-W-$A$ haplotypes and/or neo-W-$a$ haplotypes can spread ($\lambda_{W'A}^{(XY)}>1$ and/or $\lambda_{W'a}^{(XY)}>1$).
 %If $\lambda_{mA}>1$ (requiring $w_{Aa}^\female>w_{AA}^\female$), the implication is that the neo-W can spread alongside the $A$ allele, despite the fact that the neo-W sometimes brings $Y-a$ haplotypes into females, because $a$ is favoured by selection in females despite $A$ being fixed on the X.
-A neo-W-$A$ haplotype can spread ($\lambda_{mA}>1$) when $w_{Aa}^\female>w_{AA}^\female$, despite the fact that a neo-W brings Y-$a$ haplotypes into females.
+A neo-W-$A$ haplotype can spread ($\lambda_{W'A}^{(XY)}>1$) when $w_{Aa}^\female>w_{AA}^\female$, despite the fact that a neo-W brings Y-$a$ haplotypes into females.
 In this case the $a$ allele is favoured by selection in females despite $A$ being fixed on the X.
@@
 
-Still considering $w_{Aa}^\female>w_{AA}^\female$, the neo-W can also spread alongside the $a$ allele ($\lambda_{ma}>1$) if $w_{aa}^\female$ is large enough such that $(w_{Aa}^\female+w_{aa}^\female)/2>w_{AA}^\female$.
+Still considering $w_{Aa}^\female>w_{AA}^\female$, the neo-W can also spread alongside the $a$ allele ($\lambda_{W'a}^{(XY)}>1$) if $w_{aa}^\female$ is large enough such that $(w_{Aa}^\female+w_{aa}^\female)/2>w_{AA}^\female$.
 %there is sufficiently strong underdominance in females ($w_{aa}^\female>w_{Aa}^\female$) \textcolor{blue}{[this is describing directional selection, not overdominance - check the conditions for the case we want to talk about]}, such that $(w_{Aa}^\female+w_{aa}^\female)/2>w_{AA}^\female$.
@@
 \begin{align}
-\lambda_{mA}&= \frac{a}{b} \left[w_{AA}^\female w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi +  w_{Aa}^\female (1+\alpha^\female_\Delta) w_a^\male c \right] / (2 w_a^\female) \\
-\lambda_{ma}&= \frac{a}{b} \left[ w_{Aa}^\female (1-\alpha^\female_\Delta) w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi +  w_{aa}^\female w_a^\male c \right] / (2 w_A^\female) \\
-\chi_{mA}&= \frac{a}{b} \frac{R}{2} \left[   w_{Aa}^\female (1+\alpha^\female_\Delta) w_a^\male c \right] / w_a^\female\\ 
-\chi_{ma}&= \frac{a}{b} \frac{R}{2} \left[ w_{Aa}^\female (1-\alpha^\female_\Delta) w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi \right] / w_A^\female
+\lambda_{W'A}^{(XY)}&= \frac{a}{b} \left[w_{AA}^\female w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi +  w_{Aa}^\female (1+\alpha^\female_\Delta) w_a^\male c \right] / (2 w_a^\female) \\
+\lambda_{W'a}^{(XY)}&= \frac{a}{b} \left[ w_{Aa}^\female (1-\alpha^\female_\Delta) w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi +  w_{aa}^\female w_a^\male c \right] / (2 w_A^\female) \\
+\chi_{W'A}^{(XY)}&= \frac{a}{b} \frac{R}{2} \left[   w_{Aa}^\female (1+\alpha^\female_\Delta) w_a^\male c \right] / w_a^\female\\ 
+\chi_{W'a}^{(XY)}&= \frac{a}{b} \frac{R}{2} \left[ w_{Aa}^\female (1-\alpha^\female_\Delta) w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi \right] / w_A^\female
+%\lambda_{W'A}^{(XY)}&=   {\left[ 2 (1 - \zeta) \right]}^{-1} w_A^{\female} \left[ b w_{AA}^\female + c w_{Aa}^\female \left(1 - \alpha^\female_\Delta \right) \right]/ \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\female}_{D} \right)  \\
+%\lambda_{W'a}^{(XY)}&=  \\
+%\chi_{W'A}^{(XY)}&= \\ 
+%\chi_{W'a}^{(XY)}&=
 \end{align}
@@
 \textcolor{red}{Sally suggests using some $\zeta$ term in the above equations}
-
-As with equilibrium (B), haploid selection again modifies invasion fitnesses by altering the ancestral sex ratio \textcolor{red}{(through $\zeta$)} and directly selecting upon female gametes textcolor{red}{(through $w_{i}^\female$)}.
+\textcolor{blue}{Maybe just reference table 2?}
+
+As with equilibrium (B), haploid selection again modifies invasion fitnesses by altering the ancestral sex ratio \textcolor{red}{(through $\zeta$)} and directly selecting upon female gametes \textcolor{red}{(through $w_{i}^\female$)}.
 The only difference is that resident XX females are no longer always homozygote $AA$ and males are no longer always heterozygote $Aa$.
@@
 The other terms are easier to interpret in the absence of haploid selection.
-For instance, without haploid selection, the neo-W-$A$ haplotype spreads ($\lambda_{mA}>1$) if and only if
+For instance, without haploid selection, the neo-W-$A$ haplotype spreads ($\lambda_{W'A}^{(XY)}>1$) if and only if
 
@@
 
-Without haploid selection, the neo-W-$a$ haplotype spreads ($\lambda_{ma}>1$) if and only if
+Without haploid selection, the neo-W-$a$ haplotype spreads ($\lambda_{W'a}^{(XY)}>1$) if and only if
 
@@
 Male haploid selection in favour of the $a$ allele ($\alpha_{\Delta}^\male<0$, $w_{A}^\male<w_{a}^\male$) generates male-biased sex ratios at equilibria (A) and (B), where Y-$a$ is fixed ($\hat{p}_{Y}^\male=0$).
-Male-biased sex-ratios facilitate the spread of neo-W-$A$ and neo-W-$a$ haplotypes (increasing $\lambda_{mA}$ and $\lambda_{ma}$). 
+Male-biased sex-ratios facilitate the spread of neo-W-$A$ and neo-W-$a$ haplotypes (increasing $\lambda_{W'A}^{(XY)}$ and $\lambda_{W'a}^{(XY)}$). 
 Panels A-C in \nameref{fig:regionMaleDrive} and \ref{fig:regionMaleGS} show that neo-W haplotypes tend to spread for a wider range of parameters when sex ratios are male biased, compared to Fig \ref{fig:regionplots} without haploid selection.
-By contrast, male haploid selection in favour of the $A$ allele generates female-biased sex ratios and reduces $\lambda_{mA}$ and $\lambda_{ma}$, as demonstrated by panels D-F in \nameref{fig:regionMaleDrive} and \nameref{fig:regionMaleGS}.
+By contrast, male haploid selection in favour of the $A$ allele generates female-biased sex ratios and reduces $\lambda_{W'A}^{(XY)}$ and $\lambda_{W'a}^{(XY)}$, as demonstrated by panels D-F in \nameref{fig:regionMaleDrive} and \nameref{fig:regionMaleGS}.
 
 Female haploid selection generates direct selection on the neo-W-$A$ and neo-W-$a$ haplotypes as they spread in females. 
-Thus, female haploid selection in favour of the $a$ allele tends to increase $\lambda_{ma}$ and decrease $\lambda_{mA}$, as shown by panels A-C in \nameref{fig:regionFemaleDrive} and \nameref{fig:regionFemaleGS}.
-Conversely, female haploid selection in favour of the $A$ allele increases $\lambda_{mA}$ and decreases $\lambda_{ma}$, see panels D-F in \nameref{fig:regionFemaleDrive} and \nameref{fig:regionFemaleGS}.
+Thus, female haploid selection in favour of the $a$ allele tends to increase $\lambda_{W'a}^{(XY)}$ and decrease $\lambda_{W'A}^{(XY)}$, as shown by panels A-C in \nameref{fig:regionFemaleDrive} and \nameref{fig:regionFemaleGS}.
+Conversely, female haploid selection in favour of the $A$ allele increases $\lambda_{W'A}^{(XY)}$ and decreases $\lambda_{W'a}^{(XY)}$, see panels D-F in \nameref{fig:regionFemaleDrive} and \nameref{fig:regionFemaleGS}.
 

### 2018-01-23 LaTeX/Turnover_plos.tex
some edits to results

@@
 Prevailing views suggest that new sex determination systems are favoured when they equalize the sex ratio and/or when they are more closely linked to genes that experience differential selection in males and females.
-Our models extend theory to include selection upon haploid genotypes (meiotic drive or gametic competition), which both causes sex ratio biases and occurs differently in males and females. 
+Our models extends these theories to include selection upon haploid genotypes (meiotic drive or gametic competition), which causes sex ratio biases and occurs differently in males and females. 
 Surprisingly, we find that neither force (sex ratio selection nor associations with genes that have sex-specific effects) dominates the spread of new sex determination systems alone. 
@@
 In addition to considering haploid selection, another novel development in our model is that we consider loci that are in very tight linkage with the ancestral sex-determining region. 
-Because sex-determining loci are often found within a region of suppressed recombination, there can be a significant number of tightly linked loci. 
-We find that loci linked with the ancestral sex-determining region can drive transitions in which the heterogametic sex changes, even when the neo-sex-determining locus is less closely linked to loci under selection (either including haploid selection or not).
+%Because sex-determining loci are often found within a region of suppressed recombination, there can be a significant number of tightly linked loci. 
+We find that loci tightly linked with the ancestral sex-determining region can drive transitions in which the heterogametic sex changes, even when the neo-sex-determining locus is less closely linked to loci under selection (either including haploid selection or not).
 
@@
 Recombination (i.e., an odd number of cross-overs) occurs between loci \textbf{X} and \textbf{A} with probability $r$, between loci \textbf{A} and \textbf{M} with probability $R$, and between loci \textbf{X} and \textbf{M} with probability $\rho$.
-Any linear order of the loci can be modelled with appropriate choices of $r$, $R$, and $\rho$ (see Fig \ref{fig:model_outline}A and Table \ref{tab:chisubstitutions}). 
+Any linear order of the loci can be modelled with appropriate choices of $r$, $R$, and $\rho$ (see Fig \ref{fig:model_outline}A and \nameref{tab:chisubstitutions}). 
 Individuals that are heterozygous at the \textbf{A} locus may experience meiotic drive; a gamete produced by $Aa$ heterozgotes of sex $\Hermaphrodite$ bears allele $A$ with probability $\alpha^\Hermaphrodite$.
@@
 $\zeta$ is the zygotic sex ratio (fraction male).
-$\bar{w}^{\Hermaphrodite}_{D}$ is the mean fitness of diploids of sex $\Hermaphrodite$, see Table \ref{tab:meanfitnesses}.
-$\bar{w}_H^\Hermaphrodite$ is the mean fitness of haploids from sex $\Hermaphrodite$, see Table \ref{tab:meanfitnesses}.
+$\bar{w}^{\Hermaphrodite}_{D}$ is the mean fitness of diploids of sex $\Hermaphrodite$.
+$\bar{w}_H^\Hermaphrodite$ is the mean fitness of haploids from sex $\Hermaphrodite$, see \nameref{tab:meanfitnesses}.
 \end{flushleft}
@@
 
-We find that a neo-Y can never invade an ancestral XY system that already has tight linkage with the locus under selection ($r=0$, for details see \nameref{file:Mathematica}). 
+We find that a neo-Y can never invade an ancestral XY system that already has tight linkage with the locus under selection ($\Lambda_{Y'}^{(XY)} \leq 1$ when $r=0$, for details see \nameref{file:Mathematica}).
 When $R=0$, a neo-Y haplotype with the same allele as the ancestral Y is neutral ($\lambda_{Y'a}^{(XY)}=1$) and does not change in frequency.
@@
 Broadly, this is possible because the ancestral X chromosome is sometimes found in males and is therefore unable to perfectly specialise on the `female-beneficial' allele. 
-For example, when the $a$ allele is favoured on the ancestral X in males, a polymorphism of $A$ and $a$ alleles can be maintained on the X despite directional selection in favour of the $A$ allele in females ($s^\female>0$, $0<h^\female<1$), see outlined region in Fig \ref{fig:regionplots}A.
+For example, when the $a$ allele is favoured on the ancestral X in males, a polymorphism of $A$ and $a$ alleles can be maintained on the X despite selection for the $A$ allele in females ($s^\female>0$, $0<h^\female<1$), see outlined region in Fig \ref{fig:regionplots}A.
 When the $a$ allele is strongly favoured on X chromosomes in males ($w_{aa}^\male$ sufficiently large relative to $w_{Aa}^\male$), neo-W-$A$ haplotypes can spread ($\lambda_{W'A}^{(XY)}>1$, see grey region in Fig \ref{fig:regionplots}A) because they produce hgher fitness females ($AA$ or $Aa$ genotypes) and are unleashed from counterselection in males.
@@
 Nevertheless, because we assume here that $r$ is small, these results indicate that a more loosely linked sex-determining region ($r<R$) can spread.
-Therefore, tightly sex-linked loci that experience sexually-antagonistic selection can drive trans-GSD transitions in which the neo-SDR is less closely linked to the locus under selection (Fig \ref{fig:SexAntagTighter}).
+For example, tightly sex-linked loci that experience sexually-antagonistic selection can drive trans-GSD transitions in which the neo-SDR is less closely linked to the locus under selection (Fig \ref{fig:SexAntagTighter}).
 
@@
 
-Here we assume that selection is weak ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon<<1$) and thus implicitly assuming that all recombination rates ($r$, $R$ and $\rho$) are large relative to selection.
+Here we assume that selection is weak ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon<<1$) and thus implicitly assume that all recombination rates ($r$, $R$ and $\rho$) are large relative to selection.
 %, we denote the leading eigenvalues describing the invasion of a neo-Y ($k=0$) and a neo-W ($k=1$) into an ancestrally XY system by $\Lambda_{Y',XY}$ and $\Lambda_{W',XY}$, respectively. 
@@
 Equation \eqref{eq:lambda_neoY} demonstrates that, under weak selection, a neo-Y will invade an XY system if and only if it is more closely linked to the selected locus than the ancestral sex-determining region (i.e., if $R<r$; note that $V_{A}S_{A}^2$ is strictly positive as long as \textbf{A} is polymorphic).
-This echoes our $R\approx0$ results above where a neo-Y could never invade if $r\approx0$.
+This echoes our results above where a neo-Y could never invade if $r\approx0$. 
 It is also consistent with the results of \cite{vanDoorn:2007eu}, who considered diploid selection only and also found that cis-GSD transitions (XY to XY or ZW to ZW) can only occur when the neo-sex-determining locus is more closely linked to a locus under sexually-antagonistic selection.
@@
 With weak selection and no haploid selection ($t^\Hermaphrodite=\alpha^\Hermaphrodite_{\Delta}=0$), the spread of a neo-W is equivalent to the spread of a neo-Y ($\Lambda_{W'}^{(XY)}=\Lambda_{Y'}^{(XY)}$), such that trans-GSD transitions (XY to ZW or ZW to XY) can also occur only if the neo-sex-determining region is more closely linked to a locus under selection ($R<r$), as found by \cite{vanDoorn:2010hu}.
-With haploid selection, however, the additional term in equation \eqref{eq:lambda_neoW} can be positive, which can allow, for example, neo-W invasion ($\Lambda_{W'}^{(XY)}>1$) even when the neo-sex-determining region is less closely linked to the selected locus ($R>r$).
-%These transitions are unusual because, when $R>r$, associations that selection has built up between alleles more favourable in one sex and alleles that determine sex will be weakened. 
-%Mean diploid fitness therefore decreases during heterogametic transitions that create looser sex-linkage (Fig \ref{fig:Combination_MeanFit}B,D).
-
-Equation \eqref{eq:lambda_neoW} shows that, with weak selection, neo-W alleles can invade an XY system for a large number of selective regimes. 
-To clarify the parameter space under which $\Lambda_{W'}^{(XY)}>1$, we consider several special cases. 
-Firstly, if the \textbf{A} locus is unlinked to the ancestral sex-determining region ($r=1/2$), a more closely linked neo-W ($R<1/2$) can always invade because there is no ancestral association between $A$ alleles and sex chromosomes in males, $\left( \hat{p}^\male_Y-\hat{p}^\male_X \right)=0$, see equation \eqref{eq:freq_diffs}.
-The second term in equation \eqref{eq:lambda_neoW} therefore disappears and invasion depends only on the sign of $(r-R)$, as in the case of the neo-Y. 
-Indeed, invasion typically occurs when the neo-W is more closely linked to the selected locus than the ancestral sex-determining region (Fig \ref{fig:Combination_Centimorgans}).
+When there is haploid selection, invasion also typically occurs when the neo-W is more closely linked to the selected locus than the ancestral sex-determining region (Fig \ref{fig:Combination_Centimorgans}).
+For example, if the \textbf{A} locus is unlinked to the ancestral sex-determining region ($r=1/2$), a more closely linked neo-W ($R<1/2$) can always invade.
+In this case, there is no ancestral association between \textbf{A} alleles and sex chromosomes in males, $\left( \hat{p}^\male_Y-\hat{p}^\male_X \right)=0$, see equation \eqref{eq:freq_diffs}. 
+The second term in equation \eqref{eq:lambda_neoW} therefore disappears and invasion depends only on the sign of $(r-R)$.%, as in the case of the neo-Y.
 
@@
 
-Secondly, we can simplify the discussion of cases where invasion occurs despite looser sex-linkage, $R>r$, by focusing on the special case where $R=1/2$ and $r<1/2$ (e.g., the selected locus is on the ancestral sex chromosome and the novel sex-determining locus arises on an autosome).
+However, with haploid selection, the additional term in equation \eqref{eq:lambda_neoW} can be positive, which can allow neo-W invasion ($\Lambda_{W'}^{(XY)}>1$), even when the neo-sex-determining region is less closely linked to the selected locus ($R>r$).
+%These transitions are unusual because, when $R>r$, associations that selection has built up between alleles more favourable in one sex and alleles that determine sex will be weakened. 
+%Mean diploid fitness therefore decreases during heterogametic transitions that create looser sex-linkage (Fig \ref{fig:Combination_MeanFit}B,D). 
+%Equation \eqref{eq:lambda_neoW} shows that, with weak selection, neo-W alleles can invade an XY system for a large number of selective regimes. 
+%To clarify the parameter space under which $\Lambda_{W'}^{(XY)}>1$ , we consider several special cases. 
+%Firstly, if the \textbf{A} locus is unlinked to the ancestral sex-determining region ($r=1/2$), a more closely linked neo-W ($R<1/2$) can always invade because there is no ancestral association between $A$ alleles and sex chromosomes in males, $\left( \hat{p}^\male_Y-\hat{p}^\male_X \right)=0$, see equation \eqref{eq:freq_diffs}.
+%The second term in equation \eqref{eq:lambda_neoW} therefore disappears and invasion depends only on the sign of $(r-R)$, as in the case of the neo-Y. 
+%Indeed, invasion typically occurs when the neo-W is more closely linked to the selected locus than the ancestral sex-determining region (Fig \ref{fig:Combination_Centimorgans}).
+To clarify the parameter space under which invasion occurs despite looser sex-linkage ($\Lambda_{W'}^{(XY)}>1$ despite $R>r$), we focus on the special case where $R=1/2$ and $r<1/2$ (e.g., the selected locus is on the ancestral sex chromosome and the novel sex-determining locus arises on an autosome).
 In Table \ref{tab:specialcases} we give the conditions where invasion occurs when we further assume that haploid selection only occurs in one sex (e.g., during male meiosis only) and dominance coefficients are equal in the two sexes, $h^\female=h^\male$.
@@
 Consider, for example, the case where the \textbf{A} locus is linked to the ancestral-SDR ($r<1/2$) and experiences meiotic drive in males only ($\alpha^\male_\Delta \neq 0$, $\alpha^\female_\Delta=0$), without gametic competition ($t^\female=t^\male=0$).
-In this case, the zygotic sex ratio can be initially biased only if the ancestral sex-determining system is XY (Fig \ref{fig:model_outline}B and Fig \ref{fig:SexRatioBad}B). 
+In this case, the zygotic sex ratio can be initially biased only if the ancestral sex-determining system is XY (Fig \ref{fig:model_outline}B and Fig \ref{fig:SexRatioBad}A). 
 %If the ancxestral sex-determining system is ZW, the zygotic sex ratio will be 1:1 because diploid sex is determined by the proportion of Z-bearing versus W-bearing eggs and meiosis in females is fair (Fig \ref{fig:Combination_Turnover}D).
@@
 
-Why can new sex-determining regions invade when more loosely linked to selected loci ($R>r$)?  
-Consider first the case where both loci are linked to the selected locus ($r<R<1/2$). 
-In an XY system, haploid selection in males can facilitate the spread of a neo-W because the zygotic sex ratio is ancestrally biased and the W helps to equalize the sex ratio (Fig \ref{fig:SexRatioBad}A).
+Why can new sex-determining regions invade when they are more loosely linked to selected loci ($R>r$)?  
+Consider first the case where both sex-determining-loci are linked to the selected locus ($r<R<1/2$). 
+In an XY system, haploid selection in males can facilitate the spread of a neo-W because the zygotic sex ratio is ancestrally male biased and the W produces more of the rarer sex (Fig \ref{fig:SexRatioBad}A).
 A new sex determining region can also, however, benefit from becoming more associated with drive. 
-For example in a ZW system with the same selection regime (haploid selection in males), a neo-Y can spread despite the fact that the zygotic sex is initially even; in this case, the neo-Y spreads because it is often found in males and can, if it carries the driven allele $a$, benefit from haploid selection (Fig \ref{fig:SexRatioBad}B).
+For example in a ZW system with the same selection regime (haploid selection in males), a neo-Y can spread despite the fact that the zygotic sex is initially even; in this case, the neo-Y spreads because it is often found in males and can, if it carries the driven allele $a$, benefit from haploid selection in males (Fig \ref{fig:SexRatioBad}B).
 While equalizing the sex ratio and benefiting from drive are two primary reasons why haploid selection spurs sex chromosome transitions, more complex situations also arise.  
 For example with $R=1/2$ in Fig \ref{fig:SexRatioBad}B (green curve), the neo-Y spreads despite the fact that it cannot benefit from drive because free recombination moves it randomly between driven and non-driven backgrounds.
-Nevertheless, the unlinked neo-Y can spread because diploids bearing it more often carry the non-driven allele $A$ found at high frequency on the W background, which has higher average diploid fitness to balance the haploid advantage of the $a$ allele at equilibrium.
+Nevertheless, the unlinked neo-Y can spread because diploids bearing it more often carry the non-driven allele $A$, which is found at high frequency on the W background and has higher average diploid fitness to balance the haploid advantage of the $a$ allele at equilibrium.
 
@@
 \newpage
+
+\setcounter{equation}{0}
+\renewcommand{\theequation}{S2.\arabic{equation}}
 

### 2018-01-23 LaTeX/Turnover_plos.tex
switched lambdas, figures have ^(XY), and ref table 2 below s3.2

@@
 Variation at such loci can favour the spread of new sex-determination systems in which the heterogametic sex changes (XY to ZW or ZW to XY) and the new sex-determining region is less closely linked (or unlinked) to the locus under selection, which is not predicted by previous theory.
-(2) We also consider selection upon haploid genotypes either during gametic competition (e.g., pollen/sperm competition) or meiosis (i.e., non-Mendelian segregation); selective processes that typically occur in one sex or the other.
+(2) We also consider selection upon haploid genotypes either during gametic competition (e.g., pollen/sperm competition) or meiosis (i.e., non-Mendelian segregation), selective processes that typically occur in one sex or the other.
 We find that associations with haploid selected loci can drive transitions between sex determination systems, without requiring sexually-antagonistic selection in diploids. 
@@
 Overall, our models reveal that transitions between sex-determination systems, particularly transitions where the heterogametic sex changes, can be driven by loci in previously unpredicted genomic locations that experience selection during diploid and/or haploid phases.
-These results predict conditions under which sex-determination systems are likely to be labile and draw novel connections with sex ratio evolution
+These results predict conditions under which sex-determination systems are likely to be labile and draw novel connections with sex ratio evolution.
 
@@
 Furthermore, if the $m$ allele is fully epistatically dominant over the ancestral sex-determining system, phenotypes are not affected by the genotype at the ancestral sex-determining region (\textbf{X} locus).
-Thus, the invasion of a rare dominant neo-Y or neo-W allele, $m$, into a system with ancestral sex-determination system $i\in\{XY,ZW\}$ is determined by the largest solution of the quadratic, $(\Lambda_m^{(i)})^2+ b \Lambda_m^{(i)} + c =0$ \textcolor{blue}{(see \nameref{app:inv_cond} for a discussion of other roots - or Sally's proof!)}.
-Here, $b= - (\lambda_{mA}^{(i)} + \lambda_{ma}^{(i)})+(\chi_{mA}^{(i)} + \chi_{ma}^{(i)})$ and $c = (\lambda_{mA}^{(i)} - \chi_{mA}^{(i)}) (\lambda_{ma}^{(i)} - \chi_{ma}^{(i)}) - \chi_{mA}^{(i)} \chi_{ma}^{(i)}$, where $\lambda_{mj}^{(i)}$ is the multiplicative growth rate (which we will call the ``haplotypic growth rate'') of the neo-sex determination allele $m$ on background $j\in\{A,a\}$ without accounting for loss due to recombination ($R=0$), and $\chi_{mj}$ is the rate at which mutant haplotypes on background $j\in\{A,a\}$ recombine onto the other \textbf{A} locus background in heterozygotes (see Table \ref{tab:haplotype_growth}).
-To differentiate between the invasion of neo-Y and neo-W alleles we write $m=Y'$ or $m=W'$, respectively (e.g., $\lambda_{Y'A}$ is the growth rate of neo-Y alleles on the $A$ background when $R=0$).
-The $\lambda_{mj}^{(i)}$ and $\chi_{mj}^{(i)}$, and thus the spread of the mutant $m$ allele, depend on the frequency of alleles at the \textbf{A} and \textbf{X} loci in the ancestral population. 
+Thus, the invasion of a rare dominant neo-Y or neo-W allele, $m$, into a system with ancestral sex-determination system $i\in\{XY,ZW\}$ is determined by the largest solution of the quadratic, $(\lambda_m^{(i)})^2+ b \lambda_m^{(i)} + c =0$ \textcolor{blue}{(see \nameref{app:inv_cond} for a discussion of other roots - or Sally's proof!)}.
+Here, $b= - (\Lambda_{mA}^{(i)} + \Lambda_{ma}^{(i)})+(\chi_{mA}^{(i)} + \chi_{ma}^{(i)})$ and $c = (\Lambda_{mA}^{(i)} - \chi_{mA}^{(i)}) (\Lambda_{ma}^{(i)} - \chi_{ma}^{(i)}) - \chi_{mA}^{(i)} \chi_{ma}^{(i)}$, where $\Lambda_{mj}^{(i)}$ is the multiplicative growth rate (which we will call the ``haplotypic growth rate'') of the neo-sex determination allele $m$ on background $j\in\{A,a\}$ without accounting for loss due to recombination ($R=0$), and $\chi_{mj}$ is the rate at which mutant haplotypes on background $j\in\{A,a\}$ recombine onto the other \textbf{A} locus background in heterozygotes (see Table \ref{tab:haplotype_growth}).
+To differentiate between the invasion of neo-Y and neo-W alleles we write $m=Y'$ or $m=W'$, respectively (e.g., $\Lambda_{W'A}^{(XY)}$ is the growth rate of neo-W alleles on the $A$ background in an ancestral XY system when $R=0$).
+The $\Lambda_{mj}^{(i)}$ and $\chi_{mj}^{(i)}$, and thus the spread of the mutant $m$ allele, depend on the frequency of alleles at the \textbf{A} and \textbf{X} loci in the ancestral population. 
 In the ancestral population, it is convenient to follow the frequency of the $A$ allele among female gametes (eggs), $p^\female_X$, and among X-bearing, $p^\male_X$, and among Y-bearing, $p^\male_Y$, male gametes (sperm/pollen).
@@
    $m$ is a neo-Y ($k=0$) \\ [0.5ex] \hline \noalign{\vskip 1ex}
-  $\lambda_{Y'A}^{(XY)} = {\left( 2 \zeta \right)}^{-1} \left[\hat{p}_X^\female w_{A}^{\female} w_{A}^{\male} w_{AA}^{\male} + (1-\hat{p}_X^\female) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} (1+\alpha_{\Delta}^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\male}_{D} \right) $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\lambda_{Y'a}^{(XY)} = {\left( 2 \zeta \right)}^{-1} \left[(1-\hat{p}_X^\female) w_{a}^{\female} w_{a}^{\male} w_{aa}^{\male} + \hat{p}_X^\female w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male}(1 - \alpha_{\Delta}^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\male}_{D} \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\Lambda_{Y'A}^{(XY)} = {\left( 2 \zeta \right)}^{-1} \left[\hat{p}_X^\female w_{A}^{\female} w_{A}^{\male} w_{AA}^{\male} + (1-\hat{p}_X^\female) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} (1+\alpha_{\Delta}^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\male}_{D} \right) $\\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\Lambda_{Y'a}^{(XY)} = {\left( 2 \zeta \right)}^{-1} \left[(1-\hat{p}_X^\female) w_{a}^{\female} w_{a}^{\male} w_{aa}^{\male} + \hat{p}_X^\female w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male}(1 - \alpha_{\Delta}^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\male}_{D} \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
   $\chi_{Y'A}^{(XY)} = R {\left( 2 \zeta \right)}^{-1} \left[ (1-\hat{p}_X^\female) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} (1+\alpha_{\Delta}^{\male}) \right]/  \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\male}_{D} \right)   $\\ [0.5ex] \noalign{\vskip 0.5ex}
@@
   $m$ is a neo-W ($k=1$) \\ [0.5ex] \hline \noalign{\vskip 1ex}
-  $\lambda_{W'A}^{(XY)} = {\left[ 2 (1 - \zeta) \right]}^{-1} \left[ \bar{p}^{\male} w_{A}^{\male} w_{A}^{\female} w_{AA}^{\female}+(1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female}(1+\alpha_{\Delta}^{\female})\right]/ \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\female}_{D} \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\lambda_{W'a}^{(XY)} = {\left[ 2 (1 - \zeta) \right]}^{-1} \left[ (1-\bar{p}^{\male}) w_{a}^{\male} w_{a}^{\female} w_{aa}^{\female}+\bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female}(1-\alpha_{\Delta}^{\female})\right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\female}_{D} \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\Lambda_{W'A}^{(XY)} = {\left[ 2 (1 - \zeta) \right]}^{-1} \left[ \bar{p}^{\male} w_{A}^{\male} w_{A}^{\female} w_{AA}^{\female}+(1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female}(1+\alpha_{\Delta}^{\female})\right]/ \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\female}_{D} \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
+  $\Lambda_{W'a}^{(XY)} = {\left[ 2 (1 - \zeta) \right]}^{-1} \left[ (1-\bar{p}^{\male}) w_{a}^{\male} w_{a}^{\female} w_{aa}^{\female}+\bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female}(1-\alpha_{\Delta}^{\female})\right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\female}_{D} \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
   $\chi_{W'A}^{(XY)} = R {\left[ 2 (1 - \zeta) \right]}^{-1} \left[ (1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female} (1+\alpha_{\Delta}^{\female}) \right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\female}_{D} \right)  $\\ [0.5ex] \noalign{\vskip 0.5ex}
@@
 We are particularly concerned with the conditions under which a rare neo-sex-determining allele increases in frequency, which occurs when the largest eigenvalue is greater than one. 
-%If the average change in frequency of the two haplotypes that carry the $m$ allele ($Am$ and $am$) is positive, invasion will always occur, i.e., if $(\lambda_{mA} + \lambda_{ma})/2 > 1$ then $\lambda > 1$.
-The leading eigenvalue is the largest solution of $f(\Lambda_m^{(i)})=(\Lambda_m^{(i)})^2+b\Lambda_m^{(i)}+c=0$ and the Perron-Frobenius theorem guarantees that it is positive, unique, and real.  
-Since $f(\lambda_{mA}^{(i)})$ and $f(\lambda_{ma}^{(i)})$ are of opposite signs, the leading eigenvalue must fall between these two quantities and is the larger of them when $R = 0$ (see \nameref{file:Mathematica}).
-Consequently, if both $\lambda_{mA}^{(i)}$ and $\lambda_{ma}^{(i)}$ are greater than one, then the leading eigenvalue will always be greater than one, regardless of the linkage between the neo-sex determination factor and the selected locus ($R$).
-In particular, having $\lambda_{mA}^{(i)} >1$ and $\lambda_{ma}^{(i)}>1$ thus guarantees that an unlinked sex determining factor can invade ($R=1/2$).  
-Conversely, if both $\lambda_{mA}^{(i)}$ and $\lambda_{ma}^{(i)}$ are smaller than one, then invasion can never occur.  
-Finally, if only one of  $\lambda_{mA}^{(i)}$ and $\lambda_{ma}^{(i)}$ is greater than one, the new sex determining factor can always invade when tightly linked to the selected locus ($R$ near 0).  
+%If the average change in frequency of the two haplotypes that carry the $m$ allele ($Am$ and $am$) is positive, invasion will always occur, i.e., if $(\Lambda_{mA} + \Lambda_{ma})/2 > 1$ then $\Lambda > 1$.
+The leading eigenvalue is the largest solution of $f(\lambda_m^{(i)})=(\lambda_m^{(i)})^2+b\lambda_m^{(i)}+c=0$ and the Perron-Frobenius theorem guarantees that it is positive, unique, and real.  
+Since $f(\Lambda_{mA}^{(i)})$ and $f(\Lambda_{ma}^{(i)})$ are of opposite signs, the leading eigenvalue must fall between these two quantities and is the larger of them when $R = 0$ (see \nameref{file:Mathematica}).
+Consequently, if both $\Lambda_{mA}^{(i)}$ and $\Lambda_{ma}^{(i)}$ are greater than one, then the leading eigenvalue will always be greater than one, regardless of the linkage between the neo-sex determination factor and the selected locus ($R$).
+In particular, having $\Lambda_{mA}^{(i)} >1$ and $\Lambda_{ma}^{(i)}>1$ thus guarantees that an unlinked sex determining factor can invade ($R=1/2$).  
+Conversely, if both $\Lambda_{mA}^{(i)}$ and $\Lambda_{ma}^{(i)}$ are smaller than one, then invasion can never occur.  
+Finally, if only one of  $\Lambda_{mA}^{(i)}$ and $\Lambda_{ma}^{(i)}$ is greater than one, the new sex determining factor can always invade when tightly linked to the selected locus ($R$ near 0).  
 Furthermore, it can be shown that the leading eigenvalue declines with $R$, and invasion requires that $R$ is sufficiently small that the following condition holds: 
 \begin{equation}\label{eq:lambdasGen}
-%\frac{\chi_{mA}}{\lambda_{mA}-1}+\frac{\chi_{ma}}{\lambda_{ma}-1}>0.
-\chi_{ma}^{(i)}/\left(\lambda_{ma}^{(i)} - 1\right) + \chi_{mA}^{(i)}/\left(\lambda_{mA}^{(i)} - 1\right) < 1.
+%\frac{\chi_{mA}}{\Lambda_{mA}-1}+\frac{\chi_{ma}}{\Lambda_{ma}-1}>0.
+\chi_{ma}^{(i)}/\left(\Lambda_{ma}^{(i)} - 1\right) + \chi_{mA}^{(i)}/\left(\Lambda_{mA}^{(i)} - 1\right) < 1.
 \end{equation}
@@
 This condition may or may not be satisfied for the full range of locations of the new sex determining factor, including $R=1/2$, depending on the nature of selection.  
-Interpreting this condition, if we assume that only the $mA$ haplotype has a positive growth rate when $R=0$, $\lambda_{ma}^{(i)}<1<\lambda_{mA}^{(i)}$, the first term on the left-hand side of \eqref{eq:lambdasGen} is negative and invasion requires that the $mA$ haplotype growth rate ($\lambda_{mA}^{(i)} - 1$) and the rate at which they are produced by recombination in $ma$ haplotypes ($\chi_{ma}^{(i)}$) are sufficiently large relative to the $ma$ haplotype rate of decline ($1-\lambda_{ma}^{(i)}$) and the rate of loss of $mA$ haplotypes due to recombination ($\chi_{mA}^{(i)}$).
+Interpreting this condition, if we assume that only the $mA$ haplotype has a positive growth rate when $R=0$, $\Lambda_{ma}^{(i)}<1<\Lambda_{mA}^{(i)}$, the first term on the left-hand side of \eqref{eq:lambdasGen} is negative and invasion requires that the $mA$ haplotype growth rate ($\Lambda_{mA}^{(i)} - 1$) and the rate at which they are produced by recombination in $ma$ haplotypes ($\chi_{ma}^{(i)}$) are sufficiently large relative to the $ma$ haplotype rate of decline ($1-\Lambda_{ma}^{(i)}$) and the rate of loss of $mA$ haplotypes due to recombination ($\chi_{mA}^{(i)}$).
 
 We can draw a number of key points about the invasion of neo-Y and neo-W mutations from Table \ref{tab:haplotype_growth}. 
-First, Fisherian sex ratio selection will favour the spread of a neo-Y if the ancestral zygotic sex ratio is biased towards females, $\zeta<1/2$ (i.e., the first factor of the $\lambda_{mi}^{(i)}$ is greater than one for a neo-Y and less than one for a neo-W).
+First, Fisherian sex ratio selection will favour the spread of a neo-Y if the ancestral zygotic sex ratio is biased towards females, $\zeta<1/2$ (i.e., the first factor of the $\Lambda_{mi}^{(i)}$ is greater than one for a neo-Y and less than one for a neo-W).
 However, the spread of a neo-Y (neo-W) also depends on the male (female) fitness of associated alleles (see terms involving equilibrium allele frequencies, $\hat{p}$'s).
@@
 
-We find that a neo-Y can never invade an ancestral XY system that already has tight linkage with the locus under selection ($\Lambda_{Y'}^{(XY)} \leq 1$ when $r=0$, for details see \nameref{file:Mathematica}).
-When $R=0$, a neo-Y haplotype with the same allele as the ancestral Y is neutral ($\lambda_{Y'a}^{(XY)}=1$) and does not change in frequency.
-The other neo-Y haplotype will not spread ($\lambda_{Y'A}^{(XY)}<1$) given that the initial equilibrium is stable. 
-Therefore, a neo-Y mutation cannot spread in an ancestral XY system ($\Lambda_{Y'}^{(XY)} \leq 1$, regardless of $R$) where selected loci are within or very near the non-recombining region around the SDR.
+We find that a neo-Y can never invade an ancestral XY system that already has tight linkage with the locus under selection ($\lambda_{Y'}^{(XY)} \leq 1$ when $r=0$, for details see \nameref{file:Mathematica}).
+When $R=0$, a neo-Y haplotype with the same allele as the ancestral Y is neutral ($\Lambda_{Y'a}^{(XY)}=1$) and does not change in frequency.
+The other neo-Y haplotype will not spread ($\Lambda_{Y'A}^{(XY)}<1$) given that the initial equilibrium is stable. 
+Therefore, a neo-Y mutation cannot spread in an ancestral XY system ($\lambda_{Y'}^{(XY)} \leq 1$, regardless of $R$) where selected loci are within or very near the non-recombining region around the SDR.
 In essence, through tight linkage with the \textbf{A} locus, the ancestral Y becomes strongly specialized on the allele that has the highest fitness across male haploid and diploid phases. 
@@
 
-If we categorise the $a$ allele as being ancestrally `male-beneficial' via the fact that it is fixed on the Y, then $\lambda_{W'A}^{(XY)}>1$ indicates that the neo-W spreads when found with the ancestrally `female-beneficial' allele.
+If we categorise the $a$ allele as being ancestrally `male-beneficial' via the fact that it is fixed on the Y, then $\Lambda_{W'A}^{(XY)}>1$ indicates that the neo-W spreads when found with the ancestrally `female-beneficial' allele.
 Broadly, this is possible because the ancestral X chromosome is sometimes found in males and is therefore unable to perfectly specialise on the `female-beneficial' allele. 
 For example, when the $a$ allele is favoured on the ancestral X in males, a polymorphism of $A$ and $a$ alleles can be maintained on the X despite selection for the $A$ allele in females ($s^\female>0$, $0<h^\female<1$), see outlined region in Fig \ref{fig:regionplots}A.
-When the $a$ allele is strongly favoured on X chromosomes in males ($w_{aa}^\male$ sufficiently large relative to $w_{Aa}^\male$), neo-W-$A$ haplotypes can spread ($\lambda_{W'A}^{(XY)}>1$, see grey region in Fig \ref{fig:regionplots}A) because they produce hgher fitness females ($AA$ or $Aa$ genotypes) and are unleashed from counterselection in males.
+When the $a$ allele is strongly favoured on X chromosomes in males ($w_{aa}^\male$ sufficiently large relative to $w_{Aa}^\male$), neo-W-$A$ haplotypes can spread ($\Lambda_{W'A}^{(XY)}>1$, see grey region in Fig \ref{fig:regionplots}A) because they produce hgher fitness females ($AA$ or $Aa$ genotypes) and are unleashed from counterselection in males.
 
@@
 Here, selection in females can favour the $A$ allele (panel A, $w_{aa}^\female=0.85$, $w_{AA}^\female=1.05$), favour the $a$ allele (panel B, $w_{aa}^\female=1.05$, $w_{AA}^\female=0.85$), or be overdominant (panel C, $w_{aa}^\female=w_{AA}^\female=0.6$).
-If $\lambda_{W'A}^{(XY)}$ or $\lambda_{W'a}^{(XY)}$ is greater than one, then a rare neo-W can spread for, at least, some values of $R>r$. 
+If $\Lambda_{W'A}^{(XY)}$ or $\Lambda_{W'a}^{(XY)}$ is greater than one, then a rare neo-W can spread for, at least, some values of $R>r$. 
 The parameter values marked with an asterisk correspond to the fitnesses used in Fig \ref{fig:SexAntagTighter}C. 
-Where both $\lambda_{W'A}^{(XY)}$ and $\lambda_{W'a}^{(XY)}$ are greater than one, a neo-W will spread when rare, regardless of linkage with the selected locus (for any $R$). 
+Where both $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$ are greater than one, a neo-W will spread when rare, regardless of linkage with the selected locus (for any $R$). 
 \nameref{fig:positionOverdominance} shows the dynamics using the parameters marked with a dagger. 
@@
 
-Given that the $a$ allele can be considered ancestrally `male-beneficial' because it is fixed on the Y, it is surprising that neo-W-$a$ haplotypes can sometimes be favoured by selection in females ($\lambda_{W'a}^{(XY)}>1$).
+Given that the $a$ allele can be considered ancestrally `male-beneficial' because it is fixed on the Y, it is surprising that neo-W-$a$ haplotypes can sometimes be favoured by selection in females ($\Lambda_{W'a}^{(XY)}>1$).
 Again, this occurs because ancestral X's also experience selection in males, in which they will always be paired with a Y-$a$. 
@@
 Here we assume that selection is weak ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon<<1$) and thus implicitly assume that all recombination rates ($r$, $R$ and $\rho$) are large relative to selection.
-%, we denote the leading eigenvalues describing the invasion of a neo-Y ($k=0$) and a neo-W ($k=1$) into an ancestrally XY system by $\Lambda_{Y',XY}$ and $\Lambda_{W',XY}$, respectively. 
+%, we denote the leading eigenvalues describing the invasion of a neo-Y ($k=0$) and a neo-W ($k=1$) into an ancestrally XY system by $\lambda_{Y',XY}$ and $\lambda_{W',XY}$, respectively. 
 To leading order in selection, the leading eigenvalues are:
@@
 \begin{equation}
-\Lambda_{Y'}^{(XY)} =1+ \frac{1}{4}V_{A}S_{A}^2\frac{ \left( r-R \right) }{r R}+O\left(\epsilon^3 \right) 
+\lambda_{Y'}^{(XY)} =1+ \frac{1}{4}V_{A}S_{A}^2\frac{ \left( r-R \right) }{r R}+O\left(\epsilon^3 \right) 
 \label{eq:lambda_neoY}
@@
 \begin{equation}
-\Lambda_{W'}^{(XY)} =\Lambda_{Y'}^{(XY)}+\left(2\alpha_{\Delta}^\male-2\alpha_{\Delta}^\female+t^\male-t^\female \right) \left( \hat{p}^\male_Y-\hat{p}^\male_X \right)/2
+\lambda_{W'}^{(XY)} =\lambda_{Y'}^{(XY)}+\left(2\alpha_{\Delta}^\male-2\alpha_{\Delta}^\female+t^\male-t^\female \right) \left( \hat{p}^\male_Y-\hat{p}^\male_X \right)/2
 +O\left(\epsilon^3 \right)
@@
 
-The neo-sex-determining allele, $m$, will spread in an XY system if $\Lambda_{m}^{(XY)}>1$. 
+The neo-sex-determining allele, $m$, will spread in an XY system if $\lambda_{m}^{(XY)}>1$. 
 Equation \eqref{eq:lambda_neoY} demonstrates that, under weak selection, a neo-Y will invade an XY system if and only if it is more closely linked to the selected locus than the ancestral sex-determining region (i.e., if $R<r$; note that $V_{A}S_{A}^2$ is strictly positive as long as \textbf{A} is polymorphic).
@@
 
-With weak selection and no haploid selection ($t^\Hermaphrodite=\alpha^\Hermaphrodite_{\Delta}=0$), the spread of a neo-W is equivalent to the spread of a neo-Y ($\Lambda_{W'}^{(XY)}=\Lambda_{Y'}^{(XY)}$), such that trans-GSD transitions (XY to ZW or ZW to XY) can also occur only if the neo-sex-determining region is more closely linked to a locus under selection ($R<r$), as found by \cite{vanDoorn:2010hu}.
+With weak selection and no haploid selection ($t^\Hermaphrodite=\alpha^\Hermaphrodite_{\Delta}=0$), the spread of a neo-W is equivalent to the spread of a neo-Y ($\lambda_{W'}^{(XY)}=\lambda_{Y'}^{(XY)}$), such that trans-GSD transitions (XY to ZW or ZW to XY) can also occur only if the neo-sex-determining region is more closely linked to a locus under selection ($R<r$), as found by \cite{vanDoorn:2010hu}.
 When there is haploid selection, invasion also typically occurs when the neo-W is more closely linked to the selected locus than the ancestral sex-determining region (Fig \ref{fig:Combination_Centimorgans}).
@@
 
-However, with haploid selection, the additional term in equation \eqref{eq:lambda_neoW} can be positive, which can allow neo-W invasion ($\Lambda_{W'}^{(XY)}>1$), even when the neo-sex-determining region is less closely linked to the selected locus ($R>r$).
+However, with haploid selection, the additional term in equation \eqref{eq:lambda_neoW} can be positive, which can allow neo-W invasion ($\lambda_{W'}^{(XY)}>1$), even when the neo-sex-determining region is less closely linked to the selected locus ($R>r$).
 %These transitions are unusual because, when $R>r$, associations that selection has built up between alleles more favourable in one sex and alleles that determine sex will be weakened. 
@@
 %Equation \eqref{eq:lambda_neoW} shows that, with weak selection, neo-W alleles can invade an XY system for a large number of selective regimes. 
-%To clarify the parameter space under which $\Lambda_{W'}^{(XY)}>1$ , we consider several special cases. 
+%To clarify the parameter space under which $\lambda_{W'}^{(XY)}>1$ , we consider several special cases. 
 %Firstly, if the \textbf{A} locus is unlinked to the ancestral sex-determining region ($r=1/2$), a more closely linked neo-W ($R<1/2$) can always invade because there is no ancestral association between $A$ alleles and sex chromosomes in males, $\left( \hat{p}^\male_Y-\hat{p}^\male_X \right)=0$, see equation \eqref{eq:freq_diffs}.
@@
 %Indeed, invasion typically occurs when the neo-W is more closely linked to the selected locus than the ancestral sex-determining region (Fig \ref{fig:Combination_Centimorgans}).
-To clarify the parameter space under which invasion occurs despite looser sex-linkage ($\Lambda_{W'}^{(XY)}>1$ despite $R>r$), we focus on the special case where $R=1/2$ and $r<1/2$ (e.g., the selected locus is on the ancestral sex chromosome and the novel sex-determining locus arises on an autosome).
+To clarify the parameter space under which invasion occurs despite looser sex-linkage ($\lambda_{W'}^{(XY)}>1$ despite $R>r$), we focus on the special case where $R=1/2$ and $r<1/2$ (e.g., the selected locus is on the ancestral sex chromosome and the novel sex-determining locus arises on an autosome).
 In Table \ref{tab:specialcases} we give the conditions where invasion occurs when we further assume that haploid selection only occurs in one sex (e.g., during male meiosis only) and dominance coefficients are equal in the two sexes, $h^\female=h^\male$.
@@
 \hline\hline
-Scenario &  Assumptions & neo-W spreads ($\Lambda_{W'}^{(XY)}>1$) if \\ [0.5ex] \hline
+Scenario &  Assumptions & neo-W spreads ($\lambda_{W'}^{(XY)}>1$) if \\ [0.5ex] \hline
 %  $r=1/2$, $R<1/2$ & Always \\ [0.5ex] \hline
@@
 %However, to leading order with selection weak relative to recombination, we find that sex ratio selection favours the spread of a neo-W (through the first terms in table \ref{tab:haplotype_growth}) by an amount that is equal in magnitude to the fitness effects of alleles associated with new sex-determining alleles (second terms in table \ref{tab:haplotype_growth}).
-However, invasion by a neo-W into an XY system and invasion by a neo-Y into a ZW system occur under the same conditions ($\Lambda_{Y'}^{(XY)} = \Lambda_{W'}^{(XY)}$ and $\Lambda_{Y'}^{(XY)}=\Lambda_{W'}^{(XY)}$, at least to order $\epsilon^2$).
+However, invasion by a neo-W into an XY system and invasion by a neo-Y into a ZW system occur under the same conditions ($\lambda_{Y'}^{(XY)} = \lambda_{W'}^{(XY)}$ and $\lambda_{Y'}^{(XY)}=\lambda_{W'}^{(XY)}$, at least to order $\epsilon^2$).
 For example, in Fig \ref{fig:SexRatioBad}A neo-W alleles invade an ancestral-XY system where females are initially rare.
@@
 \begin{split}
-\Lambda_{ESD'}^{(XY)} =& 1 + \frac{{(1-2k)}^2}{4}V_{A}{S_{A}}^2\frac{r-R}{r R} \\
+\lambda_{ESD'}^{(XY)} =& 1 + \frac{{(1-2k)}^2}{4}V_{A}{S_{A}}^2\frac{r-R}{r R} \\
 &+\frac{k(\hat{p}^\male_Y-\hat{p}^\male_X)}{2}\left[ k \left(2\alpha_{\Delta}^\male-2\alpha_{\Delta}^\female+t^\male-t^\female \right) -2(1-k)S_{A}\right]+O\left(\epsilon^3\right),
@@
 \noindent
-which reduces to $\Lambda_{Y'}^{(XY)}$ when $k=0$ and $\Lambda_{W'}^{(XY)}$ when $k=1$.
+which reduces to $\lambda_{Y'}^{(XY)}$ when $k=0$ and $\lambda_{W'}^{(XY)}$ when $k=1$.
 
@@
 \begin{equation}
-\Lambda_{ESD'}^{(XY)} =1+ \frac{1}{2}\frac{(\Lambda_{Y'\rvert R=1/2}^{(XY)}-1) + (\Lambda_{W'\rvert R=1/2}^{(XY)}-1)}{2} + O\left(\epsilon^3\right),
+\lambda_{ESD'}^{(XY)} =1+ \frac{1}{2}\frac{(\lambda_{Y'\rvert R=1/2}^{(XY)}-1) + (\lambda_{W'\rvert R=1/2}^{(XY)}-1)}{2} + O\left(\epsilon^3\right),
 %V_A \frac{r}{1-2r}  \frac{s_{f} \left( s^\male - 3 s^\female\right) }{8 {\left( s_{f} + s_{m} \right)}^2} t_{m}^2.
@@
 \noindent
-where $\Lambda_{Y'\rvert R=1/2}^{(XY)}$ and $\Lambda_{W'\rvert R=1/2}^{(XY)}$ represent $\Lambda_{Y'}^{(XY)}$ and $\Lambda_{W'}^{(XY)}$ when evaluated at $R=1/2$ (Equations \ref{eq:lambda_neoY} and \ref{eq:lambda_neoW}).
+where $\lambda_{Y'\rvert R=1/2}^{(XY)}$ and $\lambda_{W'\rvert R=1/2}^{(XY)}$ represent $\lambda_{Y'}^{(XY)}$ and $\lambda_{W'}^{(XY)}$ when evaluated at $R=1/2$ (Equations \ref{eq:lambda_neoY} and \ref{eq:lambda_neoW}).
 That is, recombination between the selected locus and the novel sex-determining locus, $R$, doesn't enter into the $k=1/2$ results.
@@
 Equation \eqref{eq:lambda_ESD} shows that the neo-ESD gets half of the fitness of a feminizing mutation (neo-$W$) and half of the fitness of a masculinizing mutation (neo-$Y$), but only has an effect one half of the time (the other half of the time it produces the same sex as the ancestral system would have).
-As discussed above, $\Lambda_{Y'\rvert R=1/2}^{(XY)}$ is necessarily less than one, but $\Lambda_{W'\rvert R=1/2}^{(XY)}$ can be greater than one if there is haploid selection.
+As discussed above, $\lambda_{Y'\rvert R=1/2}^{(XY)}$ is necessarily less than one, but $\lambda_{W'\rvert R=1/2}^{(XY)}$ can be greater than one if there is haploid selection.
 That is, when there is haploid selection, ESD mutations can invade an ancestrally-XY system because they generate females that are either rare or have high fitness, in the same manner as a neo-W.
@@
 %An important result from equation \eqref{eq:lambda_ESD} is that ESD can invade if there is haploid selection. 
-%When evaluated at $R=1/2$, $\lambda_{Y',XY}$ is necessarily less than one, but $\lambda_{W',XY}$ can be greater than one if there is haploid selection, as discussed above. 
+%When evaluated at $R=1/2$, $\Lambda_{Y',XY}$ is necessarily less than one, but $\Lambda_{W',XY}$ can be greater than one if there is haploid selection, as discussed above. 
 %Previous studies where ESD is favoured have typically assumed that environmental conditions (e.g., maternal condition, mate quality, age, or host size) can differentially affect the fitness of males versus females such that ESD invades because it allows sex determination to depend on the environment \citep[reviewed in][]{Charnov:1982wg,Bull:1983vi,West:2009we}.
@@
 
-Significantly, equation \eqref{eq:lambda_ESD} is the same whether ESD is invading an ancestrally XY or ZW system (because $\Lambda_{Y'}^{(XY)} = \Lambda_{W'}^{(ZW)}$ and $\Lambda_{W'}^{(XY)} = \Lambda_{Y'}^{(ZW)}$).
+Significantly, equation \eqref{eq:lambda_ESD} is the same whether ESD is invading an ancestrally XY or ZW system (because $\lambda_{Y'}^{(XY)} = \lambda_{W'}^{(ZW)}$ and $\lambda_{W'}^{(XY)} = \lambda_{Y'}^{(ZW)}$).
 Thus, Fisherian sex ratio selection alone does not easily explain the invasion of ESD.
 For example, when the ancestral sex-determination system is XY, but not ZW, the sex ratio is biased by male haploid selection.
-Nevertheless, ESD is equally likely to invade when it equalizes the zygotic sex ratio (through $\Lambda_{W'}^{(XY)}$) and when it doesn't (through $\Lambda_{Y'}^{(ZW)}$). 
+Nevertheless, ESD is equally likely to invade when it equalizes the zygotic sex ratio (through $\lambda_{W'}^{(XY)}$) and when it doesn't (through $\lambda_{Y'}^{(ZW)}$). 
 %This is again because haploid selection can facilitate the turnover of sex chromosomes either through sex ratio biases or through associations between the new sex determining region with selected alleles.
 %With weak selection, these two forces are nearly equal in strength. 
-In addition, we note that ESD may not invade, even if the sex ratio is initially biased (e.g., with drive in males only, $r<1/2$, $h^\female=h^\male$, and $s^\female s^\male<0$, then $\Lambda_{W'}^{(XY)}<1$, see Table \ref{tab:specialcases}).
+In addition, we note that ESD may not invade, even if the sex ratio is initially biased (e.g., with drive in males only, $r<1/2$, $h^\female=h^\male$, and $s^\female s^\male<0$, then $\lambda_{W'}^{(XY)}<1$, see Table \ref{tab:specialcases}).
 We conclude that, as with neo-W and neo-Y loci, associations with selected loci mean that the evolution of neo-ESD systems is not straightforwardly predicted by selection to balance the zygotic sex ratio when haploid selection is present.
@@
 Turnovers driven by haploid selection may help to explain the relative rarity of heteromorphic sex chromosomes in plants, which are thought to experience more selection during their multicellular haploid stage.
-If haploid selection is strong but selective differences between male and female diploids are weak, we find that trans-GSD transitions (XY to ZW or ZW to XY) are favoured more strongly than cis-GSD transitions, with transitions to ESD intermediate (e.g., with $|D^\male - D^\female| << |\alpha_\Delta^\male - \alpha_\Delta^\female + t^\male - t^\female|$ we have $\Lambda_{W'}^{(XY)} > \Lambda_{Y'}^{(XY)}$; Equations \ref{eq:lambda_neoW} and \ref{eq:freq_diffs}).
+If haploid selection is strong but selective differences between male and female diploids are weak, we find that trans-GSD transitions (XY to ZW or ZW to XY) are favoured more strongly than cis-GSD transitions, with transitions to ESD intermediate (e.g., with $|D^\male - D^\female| << |\alpha_\Delta^\male - \alpha_\Delta^\female + t^\male - t^\female|$ we have $\lambda_{W'}^{(XY)} > \lambda_{Y'}^{(XY)}$; Equations \ref{eq:lambda_neoW} and \ref{eq:freq_diffs}).
 Among the relatively few dioecious clades in which multiple species have well characterized sex chromosomes~\cite{Ming:2011iy}, trans-GSD transitions have been inferred in \textit{Silene} subsection \textit{Otites}~\cite{Slancarova:2013dq} and in \textit{Salicaceae}~\cite{Pucholt2015,Pucholt2017}.
@@
 There is no haploid selection $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
-These parameters are marked by daggers in Fig \ref{fig:regionplots}B and C, which show that neo-W invasion is expected for any $R$ ($\lambda_{W'A}^{(XY)},\lambda_{W'a}^{(XY)}>1$) if the $a$ allele is nearly fixed on the Y (black lines in this figure; not stable for $r>>0$).
+These parameters are marked by daggers in Fig \ref{fig:regionplots}B and C, which show that neo-W invasion is expected for any $R$ ($\Lambda_{W'A}^{(XY)},\Lambda_{W'a}^{(XY)}>1$) if the $a$ allele is nearly fixed on the Y (black lines in this figure; not stable for $r>>0$).
 Equilibria where the $A$ allele is more common among Y-bearing male gametes can also be stable and allow neo-W invasion for these parameters (blue lines). 
@@
 %We vary the fitness of male homozygotes relative to heterozygotes ($w_{Aa}^\Hermaphrodite=1$) and only consider stable equilibria at which both \textbf{A} locus allele are maintained and the $a$ allele is initially fixed on the Y, region outlined.
-In panels A-C, meiotic drive in males favours the $a$ allele ($\alpha_{\Delta}^\male=-0.16$), creating male-biased sex ratios and generally increasing $\lambda_{W'A}^{(XY)}$ and $\lambda_{W'a}^{(XY)}$.
-By contrast, $\lambda_{W'A}^{(XY)}$ and $\lambda_{W'a}^{(XY)}$ tend to be reduced when meiotic drive in males favours the $A$ allele ($\alpha_{\Delta}^\male=0.16$), panels D-F. 
+In panels A-C, meiotic drive in males favours the $a$ allele ($\alpha_{\Delta}^\male=-0.16$), creating male-biased sex ratios and generally increasing $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$.
+By contrast, $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$ tend to be reduced when meiotic drive in males favours the $A$ allele ($\alpha_{\Delta}^\male=0.16$), panels D-F. 
 %We consider three forms of selection in females: directional selection in favour of the $A$ allele (panels A and D, $w_{aa}^\female=0.85$, $w_{AA}^\female=1.05$), direction selection in favour of the $a$ allele (panels B and E, $w_{aa}^\female=1.05$, $w_{AA}^\female=0.85$), and overdominance (panels C and F, $w_{aa}^\female=w_{AA}^\female=0.6$).
@@
 %Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in \nameref{fig:regionMaleDrive}. 
-The $a$ allele is favoured during male gametic competition in Panels A-C ($w_{a}^\male=1.16$, $w_{A}^\male=1$), which creates male biased sex ratios and increases $\lambda_{W'A}^{(XY)}$ and $\lambda_{W'a}^{(XY)}$.
-By contrast, $\lambda_{W'A}^{(XY)}$ and $\lambda_{W'a}^{(XY)}$ tend to be reduced when the $A$ allele is favoured during male gametic competition, panels D-F.
+The $a$ allele is favoured during male gametic competition in Panels A-C ($w_{a}^\male=1.16$, $w_{A}^\male=1$), which creates male biased sex ratios and increases $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$.
+By contrast, $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$ tend to be reduced when the $A$ allele is favoured during male gametic competition, panels D-F.
 Compared to the meiotic drive parameters in \nameref{fig:regionMaleDrive}, the effect of these male gametic competition parameters on the sex ratio is smaller. 
@@
 %Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in \nameref{fig:regionMaleDrive} and \nameref{fig:regionMaleGS}. 
-The $a$ allele is favoured by meiotic drive in females in Panels A-C ($\alpha_{\Delta}^\female=-0.16$), which increases $\lambda_{W'a}^{(XY)}$ and decreases $\lambda_{W'A}^{(XY)}$. 
+The $a$ allele is favoured by meiotic drive in females in Panels A-C ($\alpha_{\Delta}^\female=-0.16$), which increases $\Lambda_{W'a}^{(XY)}$ and decreases $\Lambda_{W'A}^{(XY)}$. 
 Female meiotic drive in favour of the $A$ allele (panels D-F, $\alpha_{\Delta}^\female=-0.16$) has the opposite effect.
@@
 %Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in \nameref{fig:regionMaleDrive}, \nameref{fig:regionMaleGS}, and \nameref{fig:regionFemaleDrive}. 
-The $a$ allele is favoured during female gametic competition in females in Panels A-C ($w_{a}^\female=1.16$, $w_{A}^\female=1$), which increases $\lambda_{W'a}^{(XY)}$ and decreases $\lambda_{W'A}^{(XY)}$.
-The $A$ allele is favoured during gametic competition in panels D-F ($w_{a}^\female=1$, $w_{A}^\female=1.16$), giving the opposite effect on $\lambda_{W'a}^{(XY)}$ and $\lambda_{W'A}^{(XY)}$.
+The $a$ allele is favoured during female gametic competition in females in Panels A-C ($w_{a}^\female=1.16$, $w_{A}^\female=1$), which increases $\Lambda_{W'a}^{(XY)}$ and decreases $\Lambda_{W'A}^{(XY)}$.
+The $A$ allele is favoured during gametic competition in panels D-F ($w_{a}^\female=1$, $w_{A}^\female=1.16$), giving the opposite effect on $\Lambda_{W'a}^{(XY)}$ and $\Lambda_{W'A}^{(XY)}$.
 
@@
 %\textcolor{blue}{The last condition looks good to me, although in your Turnover-norec-MFS.nb you look at YA fixed, so you have to flip everything (so I made Turnover-norec-MFS-MMO.nb to do this).
-%The one issue I can find here is that you can also prevent $\lambda>1$ when the slope and intercept of the quadratic at $\lambda=1$ are negative (you only looked at both being positive).
+%The one issue I can find here is that you can also prevent $\Lambda>1$ when the slope and intercept of the quadratic at $\Lambda=1$ are negative (you only looked at both being positive).
 In this case we need $4w_{A}^{\female}w_{AA}^{\female}<(1-\alpha_\Delta^{\female})w_{a}^{\female}w_{Aa}^{\female}$, which also prevents $\psi>0$.
@@
 
-A rare neo-Y or neo-W allele, $m$, will spread from a given ancestral equilibrium with sex-determination system $i\in\{XY,ZW\}$ when the leading eigenvalue, $\Lambda_m^{(i)}$, of the Jacobian matrix derived from the eight mutant recursion equations (given by \ref{eq:recursions}c,d,g,h), evaluated at the ancestral equilibrium, is greater than one.
-However, because a neo-Y (neo-W) is always in males (females) and is epistatically dominant to the ancestral sex-determining locus, we need only two recursion equations (e.g., tracking the change in the frequency of neo-Y-$A$ and neo-Y-$a$ gametes from males) and thus the leading eigenvalue is the largest solution the polynomial $(\Lambda_m^{(i)})^2 + b\Lambda_m^{(i)} + c = 0$ as described in the text (Table \ref{tab:haplotype_growth}).
-%It can be shown (see supplementary Mathematica file) that the coefficients are $b= - (\lambda_{mA} + \lambda_{ma})+(\chi_{mA} + \chi_{ma})$ and $c = (\lambda_{mA}-\chi_{mA}) (\lambda_{ma}-\chi_{ma}) -\chi_{mA} \chi_{ma}$, where $\lambda_{mi}$ is the multiplicative growth rate of the frequency of mutants on background $i\in\{A,a\}$, without accounting for loss due to recombination, and $\chi_{mi}$ is the rate at which mutants on background $i\in\{A,a\}$ recombine onto the other \textbf{A} locus background in heterozygotes.
-%The leading eigenvalue is then greater than one whenever $\lambda_{mA}>1$ and $\lambda_{ma}>1$, less than one whenever $\lambda_{mA}<1$ and $\lambda_{ma}<1$, and greater than one whenever  $\lambda_{mA}>1$ or $\lambda_{ma}>1$ and $\chi_{ma} (\lambda_{mA}-1) + \chi_{mA} (\lambda_{ma}-1) > 0$.
-
-The general conditions for the invasion of a neo-sex-determining allele are given in the main text, in terms of the haplotypic growth rates without accounting for loss due to recombination ($\lambda_{mj}^{(i)}$ terms) and the rates at which recombination between the \textbf{M} and \textbf{A} loci breaks apart these haplotypes ($\chi_{mj}^{(i)}$).
+A rare neo-Y or neo-W allele, $m$, will spread from a given ancestral equilibrium with sex-determination system $i\in\{XY,ZW\}$ when the leading eigenvalue, $\lambda_m^{(i)}$, of the Jacobian matrix derived from the eight mutant recursion equations (given by \ref{eq:recursions}c,d,g,h), evaluated at the ancestral equilibrium, is greater than one.
+However, because a neo-Y (neo-W) is always in males (females) and is epistatically dominant to the ancestral sex-determining locus, we need only two recursion equations (e.g., tracking the change in the frequency of neo-Y-$A$ and neo-Y-$a$ gametes from males) and thus the leading eigenvalue is the largest solution the polynomial $(\lambda_m^{(i)})^2 + b\lambda_m^{(i)} + c = 0$ as described in the text (Table \ref{tab:haplotype_growth}).
+%It can be shown (see supplementary Mathematica file) that the coefficients are $b= - (\Lambda_{mA} + \Lambda_{ma})+(\chi_{mA} + \chi_{ma})$ and $c = (\Lambda_{mA}-\chi_{mA}) (\Lambda_{ma}-\chi_{ma}) -\chi_{mA} \chi_{ma}$, where $\Lambda_{mi}$ is the multiplicative growth rate of the frequency of mutants on background $i\in\{A,a\}$, without accounting for loss due to recombination, and $\chi_{mi}$ is the rate at which mutants on background $i\in\{A,a\}$ recombine onto the other \textbf{A} locus background in heterozygotes.
+%The leading eigenvalue is then greater than one whenever $\Lambda_{mA}>1$ and $\Lambda_{ma}>1$, less than one whenever $\Lambda_{mA}<1$ and $\Lambda_{ma}<1$, and greater than one whenever  $\Lambda_{mA}>1$ or $\Lambda_{ma}>1$ and $\chi_{ma} (\Lambda_{mA}-1) + \chi_{mA} (\Lambda_{ma}-1) > 0$.
+
+The general conditions for the invasion of a neo-sex-determining allele are given in the main text, in terms of the haplotypic growth rates without accounting for loss due to recombination ($\Lambda_{mj}^{(i)}$ terms) and the rates at which recombination between the \textbf{M} and \textbf{A} loci breaks apart these haplotypes ($\chi_{mj}^{(i)}$).
 For tight linkage between the ancestral sex-determining locus (\textbf{X}) and the selected locus (\textbf{A}) we can calculate these terms explicitly (see below).
@@
 \begin{align}
-\lambda_{W'A}^{(XY)}&= {\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]}^{-1}
+\Lambda_{W'A}^{(XY)}&= {\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]}^{-1}
 \frac{w_{A}^\female }{w_{A}^\female}
@@
 { 2w_{AA}^\female } \\
-\lambda_{W'a}^{(XY)}&= {\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]}^{-1}
+\Lambda_{W'a}^{(XY)}&= {\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]}^{-1}
 \frac{w_{a}^\female}{w_{A}^\female}
@@
 %$\alpha^\male<1/2$ and/or $w_{a}^\male>w_{A}^\male$.
-%Populations with haploid selection for $a$ in males have a male biased zygotic sex ratio are thus more permissive to invasion by a neo-W ($\lambda_{mA}$ and $\lambda_{ma}$ larger).
+%Populations with haploid selection for $a$ in males have a male biased zygotic sex ratio are thus more permissive to invasion by a neo-W ($\Lambda_{mA}$ and $\Lambda_{ma}$ larger).
 %%In addition, the spread of neo-W alleles depends on the fitness of female diploids after mating with an X-$A$ or Y-$a$ male gamete, relative to the fitness of females in the population (all have genotype $AA$ and fitness $w_{AA}^\female$ at this equilibrium).
@@
 
-The other terms in equations \eqref{Binvasion} are more easily interpreted if we assume that there is no haploid selection in either sex, in which case $\lambda_{W'A}^{(XY)}=(w_{AA}^\female+w_{Aa}^\female)/2 w_{AA}^\female$ and $\lambda_{W'a}^{(XY)}=(w_{aa}^\female+w_{Aa}^\female)/ 2 w_{AA}^\female$.
+The other terms in equations \eqref{Binvasion} are more easily interpreted if we assume that there is no haploid selection in either sex, in which case $\Lambda_{W'A}^{(XY)}=(w_{AA}^\female+w_{Aa}^\female)/2 w_{AA}^\female$ and $\Lambda_{W'a}^{(XY)}=(w_{aa}^\female+w_{Aa}^\female)/ 2 w_{AA}^\female$.
 Neither haplotype can spread under purely sexually-antagonistic selection at equilibrium $(B)$, with directional selection in each sex.
@@
 
-If selection doesn't uniformly favour $A$ in females, however, neo-W-$A$ haplotypes and/or neo-W-$a$ haplotypes can spread ($\lambda_{W'A}^{(XY)}>1$ and/or $\lambda_{W'a}^{(XY)}>1$).
-%If $\lambda_{mA}>1$ (requiring $w_{Aa}^\female>w_{AA}^\female$), the implication is that the neo-W can spread alongside the $A$ allele, despite the fact that the neo-W sometimes brings $Y-a$ haplotypes into females, because $a$ is favoured by selection in females despite $A$ being fixed on the X.
-A neo-W-$A$ haplotype can spread ($\lambda_{W'A}^{(XY)}>1$) when $w_{Aa}^\female>w_{AA}^\female$, despite the fact that a neo-W brings Y-$a$ haplotypes into females.
+If selection doesn't uniformly favour $A$ in females, however, neo-W-$A$ haplotypes and/or neo-W-$a$ haplotypes can spread ($\Lambda_{W'A}^{(XY)}>1$ and/or $\Lambda_{W'a}^{(XY)}>1$).
+%If $\Lambda_{mA}>1$ (requiring $w_{Aa}^\female>w_{AA}^\female$), the implication is that the neo-W can spread alongside the $A$ allele, despite the fact that the neo-W sometimes brings $Y-a$ haplotypes into females, because $a$ is favoured by selection in females despite $A$ being fixed on the X.
+A neo-W-$A$ haplotype can spread ($\Lambda_{W'A}^{(XY)}>1$) when $w_{Aa}^\female>w_{AA}^\female$, despite the fact that a neo-W brings Y-$a$ haplotypes into females.
 In this case the $a$ allele is favoured by selection in females despite $A$ being fixed on the X.
@@
 
-Still considering $w_{Aa}^\female>w_{AA}^\female$, the neo-W can also spread alongside the $a$ allele ($\lambda_{W'a}^{(XY)}>1$) if $w_{aa}^\female$ is large enough such that $(w_{Aa}^\female+w_{aa}^\female)/2>w_{AA}^\female$.
+Still considering $w_{Aa}^\female>w_{AA}^\female$, the neo-W can also spread alongside the $a$ allele ($\Lambda_{W'a}^{(XY)}>1$) if $w_{aa}^\female$ is large enough such that $(w_{Aa}^\female+w_{aa}^\female)/2>w_{AA}^\female$.
 %there is sufficiently strong underdominance in females ($w_{aa}^\female>w_{Aa}^\female$) \textcolor{blue}{[this is describing directional selection, not overdominance - check the conditions for the case we want to talk about]}, such that $(w_{Aa}^\female+w_{aa}^\female)/2>w_{AA}^\female$.
@@
 
-%When both haplotypes can spread on their own ($\lambda_{mA}>1$ and $\lambda_{ma}>1$), the neo-W invades regardless the recombination rate between it and the selected locus, $R$.
-%When neither haplotype can spread ($\lambda_{mA}<1$ and $\lambda_{ma}<1$) the neo-W can never invade.
+%When both haplotypes can spread on their own ($\Lambda_{mA}>1$ and $\Lambda_{ma}>1$), the neo-W invades regardless the recombination rate between it and the selected locus, $R$.
+%When neither haplotype can spread ($\Lambda_{mA}<1$ and $\Lambda_{ma}<1$) the neo-W can never invade.
 %And when only one haplotype can spread on its own the neo-W invades only when the rate of recombination onto the favourable background is sufficiently larger than the rate of recombination off this background (i.e., equation\ref{eq:lambdasGen} is satisfied).
@@
 %The effect of sex ratio selection is straightforward and can be seen in equation \eqref{Binvasion}, where male drive and gamete competition for $a$ (which is fixed on the Y and therefore causes a male bias) increases all four terms.
-%Direct selection on neo-W haplotypes can also be seen in equation \eqref{Binvasion} by noticing that increasing female drive in favour of $A$ increases the neo-W-$A$ haplotype growth rate ($\lambda_{mA}$) while female drive and gamete competition in favour of $a$ increases the neo-W-$a$ haplotype growth rate ($\lambda_{ma}$).
+%Direct selection on neo-W haplotypes can also be seen in equation \eqref{Binvasion} by noticing that increasing female drive in favour of $A$ increases the neo-W-$A$ haplotype growth rate ($\Lambda_{mA}$) while female drive and gamete competition in favour of $a$ increases the neo-W-$a$ haplotype growth rate ($\Lambda_{ma}$).
 %Gamete competition in females does not impact the spread of neo-W-$A$ haplotypes because they are on the same background as the resident X.
@@
 \begin{align}
-\lambda_{W'A}^{(XY)}&= \frac{a}{b} \left[w_{AA}^\female w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi +  w_{Aa}^\female (1+\alpha^\female_\Delta) w_a^\male c \right] / (2 w_a^\female) \\
-\lambda_{W'a}^{(XY)}&= \frac{a}{b} \left[ w_{Aa}^\female (1-\alpha^\female_\Delta) w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi +  w_{aa}^\female w_a^\male c \right] / (2 w_A^\female) \\
+\Lambda_{W'A}^{(XY)}&= \frac{a}{b} \left[w_{AA}^\female w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi +  w_{Aa}^\female (1+\alpha^\female_\Delta) w_a^\male c \right] / (2 w_a^\female) \\
+\Lambda_{W'a}^{(XY)}&= \frac{a}{b} \left[ w_{Aa}^\female (1-\alpha^\female_\Delta) w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi +  w_{aa}^\female w_a^\male c \right] / (2 w_A^\female) \\
 \chi_{W'A}^{(XY)}&= \frac{a}{b} \frac{R}{2} \left[   w_{Aa}^\female (1+\alpha^\female_\Delta) w_a^\male c \right] / w_a^\female\\ 
 \chi_{W'a}^{(XY)}&= \frac{a}{b} \frac{R}{2} \left[ w_{Aa}^\female (1-\alpha^\female_\Delta) w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi \right] / w_A^\female
-%\lambda_{W'A}^{(XY)}&=   {\left[ 2 (1 - \zeta) \right]}^{-1} w_A^{\female} \left[ b w_{AA}^\female + c w_{Aa}^\female \left(1 - \alpha^\female_\Delta \right) \right]/ \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\female}_{D} \right)  \\
-%\lambda_{W'a}^{(XY)}&=  \\
+%\Lambda_{W'A}^{(XY)}&=   {\left[ 2 (1 - \zeta) \right]}^{-1} w_A^{\female} \left[ b w_{AA}^\female + c w_{Aa}^\female \left(1 - \alpha^\female_\Delta \right) \right]/ \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\female}_{D} \right)  \\
+%\Lambda_{W'a}^{(XY)}&=  \\
 %\chi_{W'A}^{(XY)}&= \\ 
@@
 
-\textcolor{red}{Sally suggests using some $\zeta$ term in the above equations}
-\textcolor{blue}{Maybe just reference table 2?}
-
-As with equilibrium (B), haploid selection again modifies invasion fitnesses by altering the ancestral sex ratio \textcolor{red}{(through $\zeta$)} and directly selecting upon female gametes \textcolor{red}{(through $w_{i}^\female$)}.
+%\textcolor{red}{Sally suggests using some $\zeta$ term in the above equations}
+%\textcolor{blue}{Maybe just reference table 2?}
+
+As with equilibrium (B), haploid selection again modifies invasion fitnesses by altering the ancestral sex ratio, $\zeta$ (see Table \ref{tab:haplotype_growth}), and directly selecting upon female gametes, through $w_{i}^\female$.
 The only difference is that resident XX females are no longer always homozygote $AA$ and males are no longer always heterozygote $Aa$.
@@
 The other terms are easier to interpret in the absence of haploid selection.
-For instance, without haploid selection, the neo-W-$A$ haplotype spreads ($\lambda_{W'A}^{(XY)}>1$) if and only if
+For instance, without haploid selection, the neo-W-$A$ haplotype spreads ($\Lambda_{W'A}^{(XY)}>1$) if and only if
 
@@
 
-Without haploid selection, the neo-W-$a$ haplotype spreads ($\lambda_{W'a}^{(XY)}>1$) if and only if
+Without haploid selection, the neo-W-$a$ haplotype spreads ($\Lambda_{W'a}^{(XY)}>1$) if and only if
 
@@
 %[SALLY:  I think that is enough, but we could add somewhere??: "Without haploid selection, unlinked neo-W alleles ($R=1/2$) can invade only under certain conditions, requiring either overdominance in males or underdominance in females (see proof in supplementary \textit{Mathematica} file).?
-Note that underdominance in females with directional selection in males can lead to the spread of unlinked neo-W?s, but only from equilB (only $\lambda_{ma}$ is greater than one in this case).]
+Note that underdominance in females with directional selection in males can lead to the spread of unlinked neo-W?s, but only from equilB (only $\Lambda_{ma}$ is greater than one in this case).]
 
 Male haploid selection in favour of the $a$ allele ($\alpha_{\Delta}^\male<0$, $w_{A}^\male<w_{a}^\male$) generates male-biased sex ratios at equilibria (A) and (B), where Y-$a$ is fixed ($\hat{p}_{Y}^\male=0$).
-Male-biased sex-ratios facilitate the spread of neo-W-$A$ and neo-W-$a$ haplotypes (increasing $\lambda_{W'A}^{(XY)}$ and $\lambda_{W'a}^{(XY)}$). 
+Male-biased sex-ratios facilitate the spread of neo-W-$A$ and neo-W-$a$ haplotypes (increasing $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$). 
 Panels A-C in \nameref{fig:regionMaleDrive} and \ref{fig:regionMaleGS} show that neo-W haplotypes tend to spread for a wider range of parameters when sex ratios are male biased, compared to Fig \ref{fig:regionplots} without haploid selection.
-By contrast, male haploid selection in favour of the $A$ allele generates female-biased sex ratios and reduces $\lambda_{W'A}^{(XY)}$ and $\lambda_{W'a}^{(XY)}$, as demonstrated by panels D-F in \nameref{fig:regionMaleDrive} and \nameref{fig:regionMaleGS}.
+By contrast, male haploid selection in favour of the $A$ allele generates female-biased sex ratios and reduces $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$, as demonstrated by panels D-F in \nameref{fig:regionMaleDrive} and \nameref{fig:regionMaleGS}.
 
 Female haploid selection generates direct selection on the neo-W-$A$ and neo-W-$a$ haplotypes as they spread in females. 
-Thus, female haploid selection in favour of the $a$ allele tends to increase $\lambda_{W'a}^{(XY)}$ and decrease $\lambda_{W'A}^{(XY)}$, as shown by panels A-C in \nameref{fig:regionFemaleDrive} and \nameref{fig:regionFemaleGS}.
-Conversely, female haploid selection in favour of the $A$ allele increases $\lambda_{W'A}^{(XY)}$ and decreases $\lambda_{W'a}^{(XY)}$, see panels D-F in \nameref{fig:regionFemaleDrive} and \nameref{fig:regionFemaleGS}.
+Thus, female haploid selection in favour of the $a$ allele tends to increase $\Lambda_{W'a}^{(XY)}$ and decrease $\Lambda_{W'A}^{(XY)}$, as shown by panels A-C in \nameref{fig:regionFemaleDrive} and \nameref{fig:regionFemaleGS}.
+Conversely, female haploid selection in favour of the $A$ allele increases $\Lambda_{W'A}^{(XY)}$ and decreases $\Lambda_{W'a}^{(XY)}$, see panels D-F in \nameref{fig:regionFemaleDrive} and \nameref{fig:regionFemaleGS}.
 

### 2018-01-24 LaTeX/Supp_Figures_and_Table.tex
new figures in supp figs and table, loads eps

@@
 \usepackage{pdfpages}
+\usepackage{epstopdf}
+\epstopdfsetup{outdir=./}
 %really place a figure in a location
@@
 \centering
-\centerline{\includegraphics[width=\linewidth]{PositionPlot_Overdominance}}
+\centerline{\includegraphics[width=\linewidth]{PositionPlot_Overdominance.eps}}
 \caption{
@@
 \centering
-\centerline{\includegraphics[width=\linewidth]{Temporal_Overdominance}}
+\centerline{\includegraphics[width=\linewidth]{Temporal_Overdominance.eps}}
 \caption{
@@
 \centering
-\centerline{\includegraphics[width=1.5\linewidth]{PositionPlot_SexAntagTighter_MaleDrive}}
+\centerline{\includegraphics[width=1.5\linewidth]{PositionPlot_SexAntagTighter_MaleDrive.eps}}
 \caption{
@@
 \centering
-\centerline{\includegraphics[width=\linewidth]{Region_Plot_combined_MaleDrive}}
+\centerline{\includegraphics[width=\linewidth]{Region_Plot_combined_MaleDrive.eps}}
 \caption{
@@
 \centering
-\centerline{\includegraphics[width=\linewidth]{Region_Plot_combined_MaleGS}}
+\centerline{\includegraphics[width=\linewidth]{Region_Plot_combined_MaleGS.eps}}
 \caption{
@@
 \centering
-\centerline{\includegraphics[width=\linewidth]{Region_Plot_combined_FemaleDrive}}
+\centerline{\includegraphics[width=\linewidth]{Region_Plot_combined_FemaleDrive.eps}}
 \caption{
@@
 \centering
-\centerline{\includegraphics[width=\linewidth]{Region_Plot_combined_FemaleGS}}
+\centerline{\includegraphics[width=\linewidth]{Region_Plot_combined_FemaleGS.eps}}
 \caption{
@@
 \centerline{
-\includegraphics[width=\linewidth]{All_plot_combined_PloidAntag}
+\includegraphics[width=\linewidth]{All_plot_combined_PloidAntag.eps}
 }
@@
 \centerline{
-\includegraphics[width=\linewidth]{Freq_plot_combined_PloidAntag}
+\includegraphics[width=\linewidth]{Freq_plot_combined_PloidAntag.eps}
 }

### 2018-01-25 LaTeX/Turnover_plos.tex
minor changes?

@@
 \usepackage[flushleft]{threeparttable}
-%external document referencing - this is not allowed
-\usepackage{xr}
 
@@
 
-\externaldocument{Turnover_plos.tex}
-\externaldocument{S1_Appendix.tex}
-\externaldocument{S2_Appendix.tex}
-\externaldocument{S3_Appendix.tex}
-
 Animals and angiosperms exhibit extremely diverse sex-determination systems (reviewed in~\cite{Bull:1983vi,Charlesworth:2010it,Beukeboom:2014vb,Bachtrog:2014bx}). 
@@
 Gametic competition is also typically sex specific, occurring primarily among male gametes, because there are typically many more pollen/sperm than required for fertilization.
-Gametic competition may be particularly common in plants, in which 60-70\% of all genes are expressed in the male gametophyte, and these genes exhibit stronger signatures of selection than random genes~\cite{Borg:2009jpa,Arunkumar:2013iq,Gossmann:2014dua}.
-In addition, artificial selection pressures applied to male gametophytes are known to cause a response to selection (e.g.,~\cite{Hormaza:1996cv,Ravikumar:2003uo,Hedhly:2004iv,Clarke:2004ir}. 
+Gametic competition may be particularly common in plants, in which 60-70\% of all genes are expressed in the male gametophyte, and these genes exhibit stronger signatures of selection than randomly-chosen genes~\cite{Borg:2009jpa,Arunkumar:2013iq,Gossmann:2014dua}.
+In addition, artificial selection pressures applied to male gametophytes are known to cause a response to selection (e.g.,~\cite{Hormaza:1996cv,Ravikumar:2003uo,Hedhly:2004iv,Clarke:2004ir}). 
 A smaller proportion of genes are thought to be expressed and selected during competition in animal sperm, although precise estimates are uncertain~\cite{Zheng:2001fi,JOSEPH:2004haa,Vibranovski:2010et}.
@@
 Furthermore, if the $m$ allele is fully epistatically dominant over the ancestral sex-determining system, phenotypes are not affected by the genotype at the ancestral sex-determining region (\textbf{X} locus).
-Thus, the invasion of a rare dominant neo-Y or neo-W allele, $m$, into a system with ancestral sex-determination system $i\in\{XY,ZW\}$ is determined by the largest solution of the quadratic, $(\lambda_m^{(i)})^2+ b \lambda_m^{(i)} + c =0$ \textcolor{blue}{(see \nameref{app:inv_cond} for a discussion of other roots - or Sally's proof!)}.
-Here, $b= - (\Lambda_{mA}^{(i)} + \Lambda_{ma}^{(i)})+(\chi_{mA}^{(i)} + \chi_{ma}^{(i)})$ and $c = (\Lambda_{mA}^{(i)} - \chi_{mA}^{(i)}) (\Lambda_{ma}^{(i)} - \chi_{ma}^{(i)}) - \chi_{mA}^{(i)} \chi_{ma}^{(i)}$, where $\Lambda_{mj}^{(i)}$ is the multiplicative growth rate (which we will call the ``haplotypic growth rate'') of the neo-sex determination allele $m$ on background $j\in\{A,a\}$ without accounting for loss due to recombination ($R=0$), and $\chi_{mj}$ is the rate at which mutant haplotypes on background $j\in\{A,a\}$ recombine onto the other \textbf{A} locus background in heterozygotes (see Table \ref{tab:haplotype_growth}).
-To differentiate between the invasion of neo-Y and neo-W alleles we write $m=Y'$ or $m=W'$, respectively (e.g., $\Lambda_{W'A}^{(XY)}$ is the growth rate of neo-W alleles on the $A$ background in an ancestral XY system when $R=0$).
+Thus, the invasion of a rare dominant neo-Y or neo-W allele, $m$, into a system with ancestral sex-determination system $i\in\{XY,ZW\}$ is determined by the largest solution of the quadratic, $(\lambda_m^{(i)})^2+ b \lambda_m^{(i)} + c =0$ (see \nameref{app:inv_cond}).
+Here, $b= - (\Lambda_{mA}^{(i)} + \Lambda_{ma}^{(i)})+(\chi_{mA}^{(i)} + \chi_{ma}^{(i)})$ and $c = (\Lambda_{mA}^{(i)} - \chi_{mA}^{(i)}) (\Lambda_{ma}^{(i)} - \chi_{ma}^{(i)}) - \chi_{mA}^{(i)} \chi_{ma}^{(i)}$, where $\Lambda_{mj}^{(i)}$ is the multiplicative growth rate (which we will call the ``haplotypic growth rate'') of the neo-sex determination allele $m$ on background $j\in\{A,a\}$ without accounting for loss due to recombination ($R=0$), and $\chi_{mj}^{(i)}$ is the rate at which mutant haplotypes on background $j\in\{A,a\}$ recombine onto the other \textbf{A} locus background in heterozygotes (see Table \ref{tab:haplotype_growth}).
+To differentiate between the invasion of neo-Y and neo-W alleles we write $m=Y'$ or $m=W'$, respectively (e.g., $\Lambda_{W'A}^{(XY)}$ is the haplotypic growth rate of neo-W alleles on the $A$ background in an ancestral XY system when $R=0$).
 The $\Lambda_{mj}^{(i)}$ and $\chi_{mj}^{(i)}$, and thus the spread of the mutant $m$ allele, depend on the frequency of alleles at the \textbf{A} and \textbf{X} loci in the ancestral population. 
@@
 An equivalent analysis is not possible where recombination rates are low. 
-However, numerical simulations demonstrate that the neo-SDR does not necessarily reach pseudo-fixation, leading to the stable maintenance of a mixed sex-determining system, in which X, Y, Z, and W alleles all segregate (e.g., \nameref{fig:freqAll}B,C).
+However, numerical simulations demonstrate that the neo-SDR does not necessarily reach pseudo-fixation, which can lead to the stable maintenance of a mixed sex-determining system, in which X, Y, Z, and W alleles all segregate (e.g., \nameref{fig:freqAll}B,C).
 
@@
 
-However, with haploid selection, the additional term in equation \eqref{eq:lambda_neoW} can be positive, which can allow neo-W invasion ($\lambda_{W'}^{(XY)}>1$), even when the neo-sex-determining region is less closely linked to the selected locus ($R>r$).
+However, with haploid selection and $r<1/2$, the additional term in equation \eqref{eq:lambda_neoW} can be positive.
+This can allow neo-W invasion ($\lambda_{W'}^{(XY)}>1$), even when the neo-sex-determining region is less closely linked to the selected locus ($R>r$). 
 %These transitions are unusual because, when $R>r$, associations that selection has built up between alleles more favourable in one sex and alleles that determine sex will be weakened. 
@@
 Consider, for example, the case where the \textbf{A} locus is linked to the ancestral-SDR ($r<1/2$) and experiences meiotic drive in males only ($\alpha^\male_\Delta \neq 0$, $\alpha^\female_\Delta=0$), without gametic competition ($t^\female=t^\male=0$).
-In this case, the zygotic sex ratio can be initially biased only if the ancestral sex-determining system is XY (Fig \ref{fig:model_outline}B and Fig \ref{fig:SexRatioBad}A). 
+In this case, the zygotic sex ratio can be initially biased only if the ancestral sex-determining system is XY (Fig \ref{fig:model_outline}A and Fig \ref{fig:SexRatioBad}B). 
 %If the ancxestral sex-determining system is ZW, the zygotic sex ratio will be 1:1 because diploid sex is determined by the proportion of Z-bearing versus W-bearing eggs and meiosis in females is fair (Fig \ref{fig:Combination_Turnover}D).
@@
 However, Fig \ref{fig:SexRatioBad}B shows that a neo-Y can invade an ancestral-ZW system under the same conditions. 
-As a consequence, whenever $R<1/2$, the neo-Y becomes associated with the male meiotic drive allele such that the zygotic sex ratio actually evolves to become biased towards males.
+Whenever $R<1/2$, the neo-Y becomes associated with the male meiotic drive allele such that the zygotic sex ratio actually evolves to become biased towards males.
 
@@
 Consider first the case where both sex-determining-loci are linked to the selected locus ($r<R<1/2$). 
-In an XY system, haploid selection in males can facilitate the spread of a neo-W because the zygotic sex ratio is ancestrally male biased and the W produces more of the rarer sex (Fig \ref{fig:SexRatioBad}A).
+In an ancestral-XY system, haploid selection in males can facilitate the spread of a neo-W because the zygotic sex ratio is ancestrally male biased and the W produces more of the rarer sex (Fig \ref{fig:SexRatioBad}A).
 A new sex determining region can also, however, benefit from becoming more associated with drive. 
-For example in a ZW system with the same selection regime (haploid selection in males), a neo-Y can spread despite the fact that the zygotic sex is initially even; in this case, the neo-Y spreads because it is often found in males and can, if it carries the driven allele $a$, benefit from haploid selection in males (Fig \ref{fig:SexRatioBad}B).
+For example in anancestral-ZW system with the same selection regime (haploid selection in males), a neo-Y can spread despite the fact that the zygotic sex is initially even; in this case, the neo-Y spreads because it is often found in males and can, if it carries the driven allele $a$, benefit from haploid selection in males (Fig \ref{fig:SexRatioBad}B).
 While equalizing the sex ratio and benefiting from drive are two primary reasons why haploid selection spurs sex chromosome transitions, more complex situations also arise.  
 For example with $R=1/2$ in Fig \ref{fig:SexRatioBad}B (green curve), the neo-Y spreads despite the fact that it cannot benefit from drive because free recombination moves it randomly between driven and non-driven backgrounds.
-Nevertheless, the unlinked neo-Y can spread because diploids bearing it more often carry the non-driven allele $A$, which is found at high frequency on the W background and has higher average diploid fitness to balance the haploid advantage of the $a$ allele at equilibrium.
+Nevertheless, the unlinked neo-Y can spread because diploids bearing it more often carry the non-driven allele $A$, which is found at high frequency on the W background and has higher average diploid fitness.% to balance the haploid advantage of the $a$ allele at equilibrium.
 
@@
 %As with sexually-antagonistic selection, the presence of haploid selected loci around ancestral- or novel-sex-determining regions could support their role in sex chromosome turnover.
-In agreement with this hypothesis, a recent transcriptome analysis in \textit{Rumex} shows that Y-linked genes have higher expression in haploid pollen than autosomal genes \textcolor{red}{(check this is accurate)}.
-Interestingly, haploid-expression is also more common on the autosome that is orthologous to the sex chromosomes in closely related species suggesting that new sex chromosomes may have been favoured through their association with haploid selected alleles on these chromosomes \textcolor{red}{(Sandler et al., 2018, Personal Communication)}.
+\textcolor{red}{In agreement with this hypothesis, a recent transcriptome analysis in \textit{Rumex} shows that Y-linked genes have higher expression in haploid pollen than autosomal genes.
+Interestingly, haploid-expression is also more common on the autosome that is orthologous to the sex chromosomes in closely related species suggesting that new sex chromosomes may have been favoured through their association with haploid selected alleles on these chromosomes (Sandler et al., 2018, Personal Communication)}.
 %maybe add a flag here for switching to clade-level expectations:
@@
 \section*{Acknowledgments}
-Cras egestas velit mauris, eu mollis turpis pellentesque sit amet.
-Interdum et malesuada fames ac ante ipsum primis in faucibus.
-Nam id pretium nisi.
-Sed ac quam id nisi malesuada congue.
-Sed interdum aliquet augue, at pellentesque quam rhoncus vitae.
+This project was supported by the Natural Sciences and Engineering Research Council of Canada (CGS-D 6564 to MMO; RGPIN-2016-03711 to SPO).
 
@@
 
-\textcolor{red}{Cover the other parts of the characteristic polynomial here.}
-\textcolor{blue}{Waiting for Sally's proof!}
-
+%\textcolor{red}{Cover the other parts of the characteristic polynomial here.}
+%\textcolor{blue}{Waiting for Sally's proof!}
 A rare neo-Y or neo-W allele, $m$, will spread from a given ancestral equilibrium with sex-determination system $i\in\{XY,ZW\}$ when the leading eigenvalue, $\lambda_m^{(i)}$, of the Jacobian matrix derived from the eight mutant recursion equations (given by \ref{eq:recursions}c,d,g,h), evaluated at the ancestral equilibrium, is greater than one.

### 2018-02-02 LaTeX/Turnover_plos.tex
Sally's proof to Appendix, more edits

@@
 The evolution of a new sex-determination system requires that a rare mutant allele at the novel sex-determining locus, $m$, increases in frequency when rare. 
-The spread of a rare mutant $m$ at the \textbf{M} locus is determined by the leading eigenvalue of the system of eight equations describing the frequency of eggs and sperm carrying the $m$ allele in the next generation (equations \ref{eq:recursions}).
+The spread of a rare mutant $m$ at the \textbf{M} locus into a system with ancestral sex-determination system $i\in\{XY,ZW\}$ is determined by the leading eigenvalue ($\lambda_m^{(i)}$) of the system of eight equations describing the frequency of eggs and sperm carrying the $m$ allele in the next generation (equations \ref{eq:recursions}).
 %, evaluated at the above equilibrium.
 %Thus, the system describing the change in frequency of the $m$ allele consists of eight recursion equations. 
-This system simplifies substantially in a number of cases of interest. 
-Dominant neo-Y (when $k=0$) or neo-W alleles (when $k=1$) are only found in male diploids (neo-Y) or female diploids (neo-W) such that their growth rate ultimately depends only on the change in frequency of $m$-bearing gametes produced by males or by females, respectively.
-Furthermore, if the $m$ allele is fully epistatically dominant over the ancestral sex-determining system, phenotypes are not affected by the genotype at the ancestral sex-determining region (\textbf{X} locus).
-Thus, the invasion of a rare dominant neo-Y or neo-W allele, $m$, into a system with ancestral sex-determination system $i\in\{XY,ZW\}$ is determined by the largest solution of the quadratic, $(\lambda_m^{(i)})^2+ b \lambda_m^{(i)} + c =0$ (see \nameref{app:inv_cond}).
-Here, $b= - (\Lambda_{mA}^{(i)} + \Lambda_{ma}^{(i)})+(\chi_{mA}^{(i)} + \chi_{ma}^{(i)})$ and $c = (\Lambda_{mA}^{(i)} - \chi_{mA}^{(i)}) (\Lambda_{ma}^{(i)} - \chi_{ma}^{(i)}) - \chi_{mA}^{(i)} \chi_{ma}^{(i)}$, where $\Lambda_{mj}^{(i)}$ is the multiplicative growth rate (which we will call the ``haplotypic growth rate'') of the neo-sex determination allele $m$ on background $j\in\{A,a\}$ without accounting for loss due to recombination ($R=0$), and $\chi_{mj}^{(i)}$ is the rate at which mutant haplotypes on background $j\in\{A,a\}$ recombine onto the other \textbf{A} locus background in heterozygotes (see Table \ref{tab:haplotype_growth}).
-To differentiate between the invasion of neo-Y and neo-W alleles we write $m=Y'$ or $m=W'$, respectively (e.g., $\Lambda_{W'A}^{(XY)}$ is the haplotypic growth rate of neo-W alleles on the $A$ background in an ancestral XY system when $R=0$).
-The $\Lambda_{mj}^{(i)}$ and $\chi_{mj}^{(i)}$, and thus the spread of the mutant $m$ allele, depend on the frequency of alleles at the \textbf{A} and \textbf{X} loci in the ancestral population. 
+This system simplifies substantially for a dominant neo-Y ($k=0$) or neo-W ($k=1$), see \nameref{app:inv_cond}. 
+Invasion of a rare neo-Y or neo-W allele, $m\in\{Y',W'\}$, is given by the largest solution to the quadratic $(\lambda_m^{(i)})^2+ b \lambda_m^{(i)} + c =0$. 
+Here, $b= - (\Lambda_{mA}^{(i)} + \Lambda_{ma}^{(i)})+(\chi_{mA}^{(i)} + \chi_{ma}^{(i)})$ and $c = (\Lambda_{mA}^{(i)} - \chi_{mA}^{(i)}) (\Lambda_{ma}^{(i)} - \chi_{ma}^{(i)}) - \chi_{mA}^{(i)} \chi_{ma}^{(i)}$, where $\Lambda_{mj}^{(i)}$ is the multiplicative growth rate (which we will call the ``haplotypic growth rate'') of the neo-sex determination allele $m$ on background $j\in\{A,a\}$ without accounting for loss due to recombination ($R=0$), and $\chi_{mj}^{(i)}$ is the rate at which mutant haplotypes on background $j\in\{A,a\}$ recombine onto the other \textbf{A} locus background in heterozygotes (proportional to $R$), see Table \ref{tab:haplotype_growth}.
 In the ancestral population, it is convenient to follow the frequency of the $A$ allele among female gametes (eggs), $p^\female_X$, and among X-bearing, $p^\male_X$, and among Y-bearing, $p^\male_Y$, male gametes (sperm/pollen).
@@
 
-We are particularly concerned with the conditions under which a rare neo-sex-determining allele increases in frequency, which occurs when the largest eigenvalue is greater than one. 
+We are particularly concerned with the conditions under which a rare neo-sex-determining allele increases in frequency, which occurs when the largest eigenvalue is greater than one ($\lambda_m^{(i)}>1$).
 %If the average change in frequency of the two haplotypes that carry the $m$ allele ($Am$ and $am$) is positive, invasion will always occur, i.e., if $(\Lambda_{mA} + \Lambda_{ma})/2 > 1$ then $\Lambda > 1$.
-The leading eigenvalue is the largest solution of $f(\lambda_m^{(i)})=(\lambda_m^{(i)})^2+b\lambda_m^{(i)}+c=0$ and the Perron-Frobenius theorem guarantees that it is positive, unique, and real.  
-Since $f(\Lambda_{mA}^{(i)})$ and $f(\Lambda_{ma}^{(i)})$ are of opposite signs, the leading eigenvalue must fall between these two quantities and is the larger of them when $R = 0$ (see \nameref{file:Mathematica}).
-Consequently, if both $\Lambda_{mA}^{(i)}$ and $\Lambda_{ma}^{(i)}$ are greater than one, then the leading eigenvalue will always be greater than one, regardless of the linkage between the neo-sex determination factor and the selected locus ($R$).
-In particular, having $\Lambda_{mA}^{(i)} >1$ and $\Lambda_{ma}^{(i)}>1$ thus guarantees that an unlinked sex determining factor can invade ($R=1/2$).  
+%The leading eigenvalue is the largest solution of $f(\lambda_m^{(i)})=(\lambda_m^{(i)})^2+b\lambda_m^{(i)}+c=0$ and the Perron-Frobenius theorem guarantees that it is positive, unique, and real.  
+%Since $f(\Lambda_{mA}^{(i)})$ and $f(\Lambda_{ma}^{(i)})$ are of opposite signs, the leading eigenvalue must fall between these two quantities and is the larger of them when $R = 0$ (see \nameref{file:Mathematica}).
+If both $\Lambda_{mA}^{(i)}$ and $\Lambda_{ma}^{(i)}$ are greater than one, then the leading eigenvalue will always be greater than one, regardless of the linkage between the neo-sex determination factor and the selected locus ($R$), see \nameref{app:inv_cond} for details.
 Conversely, if both $\Lambda_{mA}^{(i)}$ and $\Lambda_{ma}^{(i)}$ are smaller than one, then invasion can never occur.  
@@
 This condition may or may not be satisfied for the full range of locations of the new sex determining factor, including $R=1/2$, depending on the nature of selection.  
-Interpreting this condition, if we assume that only the $mA$ haplotype has a positive growth rate when $R=0$, $\Lambda_{ma}^{(i)}<1<\Lambda_{mA}^{(i)}$, the first term on the left-hand side of \eqref{eq:lambdasGen} is negative and invasion requires that the $mA$ haplotype growth rate ($\Lambda_{mA}^{(i)} - 1$) and the rate at which they are produced by recombination in $ma$ haplotypes ($\chi_{ma}^{(i)}$) are sufficiently large relative to the $ma$ haplotype rate of decline ($1-\Lambda_{ma}^{(i)}$) and the rate of loss of $mA$ haplotypes due to recombination ($\chi_{mA}^{(i)}$).
+Interpreting this condition, if we assume that only the $mA$ haplotype has a positive growth rate when $R=0$, $\Lambda_{ma}^{(i)}<1<\Lambda_{mA}^{(i)}$, the first term on the left-hand side of \eqref{eq:lambdasGen} is negative and invasion requires that the $mA$ haplotypic growth rate ($\Lambda_{mA}^{(i)} - 1$) and the rate at which $mA$ haplotypes are produced by recombination in $ma$ haplotypes ($\chi_{ma}^{(i)}$) are sufficiently large relative to the $ma$ haplotype rate of decline ($1-\Lambda_{ma}^{(i)}$) and the rate of loss of $mA$ haplotypes due to recombination ($\chi_{mA}^{(i)}$).
 
@@
 
-In some cases, both W-$A$ and W-$a$ haplotypes can spread, e.g., when $AA$ individuals have low fitness in females yet the $A$ is polymorphic or fixed on the X due to overdominance in males (Fig \ref{fig:regionplots}B and \ref{fig:regionplots}C).
-Both neo-W-$A$ and neo-W-$a$ haplotypes then produce fewer unfit $AA$ females.
+In some cases, both W-$A$ and W-$a$ haplotypes can spread.
+For example, when $AA$ individuals have low fitness in females yet the $A$ is polymorphic or fixed on the X due to overdominance in males (Fig \ref{fig:regionplots}B and \ref{fig:regionplots}C), both neo-W-$A$ and neo-W-$a$ haplotypes produce fewer unfit $AA$ females.
 This is true for the neo-W-$A$ haplotype because it can pair with a Y-$a$ haplotype and still be female. 
@@
 
-Assuming weak selection, van Doorn and Kirkpatrick~\cite{vanDoorn:2010hu} showed that invasion by a neo-W occurs under the same conditions as `pseudo-fixation' (at pseudo-fixation the neo-W reaches its maximum frequency among eggs, which is 1/2).
+Assuming selection is weak relative to recombination, van Doorn and Kirkpatrick~\cite{vanDoorn:2010hu} showed that invasion by a neo-W occurs under the same conditions as `pseudo-fixation' (at pseudo-fixation the neo-W reaches its maximum frequency among eggs, which is usually 1/2).
 An equivalent analysis is not possible where recombination rates are low. 
@@
 %As with sexually-antagonistic selection, the presence of haploid selected loci around ancestral- or novel-sex-determining regions could support their role in sex chromosome turnover.
-\textcolor{red}{In agreement with this hypothesis, a recent transcriptome analysis in \textit{Rumex} shows that Y-linked genes have higher expression in haploid pollen than autosomal genes.
-Interestingly, haploid-expression is also more common on the autosome that is orthologous to the sex chromosomes in closely related species suggesting that new sex chromosomes may have been favoured through their association with haploid selected alleles on these chromosomes (Sandler et al., 2018, Personal Communication)}.
+In agreement with this hypothesis, a recent transcriptome analysis in Rumex shows that pollen-biased expression (relative to expression in flower buds or leaves) is enhanced among XY-linked genes compared to autosomal genes or compared to hemizygous genes that are only linked to the X (Sandler et al., 2018, personal communication).
+In addition, Y-linked genes are over-expressed relative to X-linked genes in pollen (but not in flower buds or leaves). 
+This suggests that the spread of neo-Y chromosomes in this clade could have been favoured through linkage with haploid selected genes. 
 %maybe add a flag here for switching to clade-level expectations:
@@
 
+\newpage
+
 \setcounter{equation}{0}
@@
 \subsection*{Recursion equations}
-
-%\textcolor{red}{Should we adjust the subscripts throughout this subsection?
-Right now we end up re-defining $i$ and $j$ (when switching from haploid to diploid; this might have been my doing!) and then introduce three new subscripts $b$, $c$, and $l$, all of which can be derived from $i$ and $j$.
-Might be more straightforward to just use $p^\Hermaphrodite_{x_1,x_2,a_1,a_2,m_1,m_2}$ where 1 is maternal and 2 is paternal?
-We then no longer have to switch indices from haploid to diploid and the connection to other variables is clear: $b=m_1m_2$, $c=x_1x_2$, and $l=a_1a_2$.
-I guess the downside will be re-writing the recursion equations...
-which is why I haven't gone ahead and tried this.}
 
@@
 
-%\textcolor{red}{Cover the other parts of the characteristic polynomial here.}
-%\textcolor{blue}{Waiting for Sally's proof!}
 A rare neo-Y or neo-W allele, $m$, will spread from a given ancestral equilibrium with sex-determination system $i\in\{XY,ZW\}$ when the leading eigenvalue, $\lambda_m^{(i)}$, of the Jacobian matrix derived from the eight mutant recursion equations (given by \ref{eq:recursions}c,d,g,h), evaluated at the ancestral equilibrium, is greater than one.
-However, because a neo-Y (neo-W) is always in males (females) and is epistatically dominant to the ancestral sex-determining locus, we need only two recursion equations (e.g., tracking the change in the frequency of neo-Y-$A$ and neo-Y-$a$ gametes from males) and thus the leading eigenvalue is the largest solution the polynomial $(\lambda_m^{(i)})^2 + b\lambda_m^{(i)} + c = 0$ as described in the text (Table \ref{tab:haplotype_growth}).
-%It can be shown (see supplementary Mathematica file) that the coefficients are $b= - (\Lambda_{mA} + \Lambda_{ma})+(\chi_{mA} + \chi_{ma})$ and $c = (\Lambda_{mA}-\chi_{mA}) (\Lambda_{ma}-\chi_{ma}) -\chi_{mA} \chi_{ma}$, where $\Lambda_{mi}$ is the multiplicative growth rate of the frequency of mutants on background $i\in\{A,a\}$, without accounting for loss due to recombination, and $\chi_{mi}$ is the rate at which mutants on background $i\in\{A,a\}$ recombine onto the other \textbf{A} locus background in heterozygotes.
-%The leading eigenvalue is then greater than one whenever $\Lambda_{mA}>1$ and $\Lambda_{ma}>1$, less than one whenever $\Lambda_{mA}<1$ and $\Lambda_{ma}<1$, and greater than one whenever  $\Lambda_{mA}>1$ or $\Lambda_{ma}>1$ and $\chi_{ma} (\Lambda_{mA}-1) + \chi_{mA} (\Lambda_{ma}-1) > 0$.
-
-The general conditions for the invasion of a neo-sex-determining allele are given in the main text, in terms of the haplotypic growth rates without accounting for loss due to recombination ($\Lambda_{mj}^{(i)}$ terms) and the rates at which recombination between the \textbf{M} and \textbf{A} loci breaks apart these haplotypes ($\chi_{mj}^{(i)}$).
+However, because a neo-Y (neo-W) is always in males (females) and is epistatically dominant to the ancestral sex-determining locus, the characteristic polynomial factors into two quadratics times $(\lambda_m^{(i)})^4$.
+One quadratic governs the change in the frequency of the new sex determination factor associated with the A and a allele frequencies, summing across backgrounds at the old sex determination factor (i.e., summing haplotypes carrying the original X and Y).
+It is the largest root of this quadratic that determines the spread of the new m allele (see details in \nameref{file:Mathematica}).  
+The second quadratic describes the dynamics of the difference in the m-A and m-a haplotypes between X and Y backgrounds.  
+Asymptotically, this difference is constrained to grow at a rate equal to or less than the sum while the m allele is rare, because the frequencies can never become negative. 
+We therefore focus on the leading eigenvalue based on the root to the first quadratic $f(\lambda_m^{(i)})=(\lambda_m^{(i)})^2+ b \lambda_m^{(i)} + c =0$, as described in the text.  
+Since $f(\Lambda_{mA}^{(i)})$ and $f(\Lambda_{ma}^{(i)})$ are of opposite signs, the leading eigenvalue must fall between these two quantities and is the larger of them when $R = 0$ (the Perron-Frobenius theorem guarantees that the largest eigenvalue is positive, unique, and real).
+Thus, $\lambda_m^{(i)}>1$ if both $\Lambda_{mA}^{(i)}>1$ and $\Lambda_{ma}^{(i)}>1$; similarly, $\lambda_m^{(i)}<1$ if both $\Lambda_{mA}^{(i)}<1$ and $\Lambda_{ma}^{(i)}<1$.
+If only one haplotypic growth rate is greater than one ($\Lambda_{ma}^{(i)}<1<\Lambda_{mA}^{(i)}$ or $\Lambda_{mA}^{(i)}<1<\Lambda_{ma}^{(i)}$), then $\lambda_m^{(i)}$ is greater than one when condition \eqref{eq:lambdasGen} is met.
+Thus, the invasion of a neo-sex-determining allele is determined by the haplotypic growth rates without accounting for loss due to recombination ($\Lambda_{mj}^{(i)}$ terms) and the rates at which recombination between the \textbf{M} and \textbf{A} loci breaks apart these haplotypes ($\chi_{mj}^{(i)}$).
 For tight linkage between the ancestral sex-determining locus (\textbf{X}) and the selected locus (\textbf{A}) we can calculate these terms explicitly (see below).

### 2018-02-04 cover.tex
cover and route 1

 \documentclass[12pt,letterpaper]{article}
\usepackage{fontenc}
\usepackage[english]{babel}

\usepackage{fullpage}

\usepackage[pdftex]{graphicx}

\begin{document}

\thispagestyle{empty}

\noindent Michael F.\ Scott\\
Genetics, Evolution \& Environment\\
University College London Genetics Institute\\
2nd Floor, Darwin Bldg., Gower St., London, WC1E 6BT, UK\\
 m.f.scott@ucl.ac.uk\\
\smash{\hspace{12cm}\includegraphics[scale=0.5]{UCL.png}}

%\noindent Matthew M.\ Osmond\\
%Department of Zoology\\
%University of British Columbia\\
%6270 University Blvd. \\
%Vancouver, BC V6T 1Z4, Canada\\
%mmosmond@zoology.ubc.ca\\
%\smash{\hspace{11.5cm}\includegraphics[scale=0.25]{IMAGES/UBC.png}}

\noindent Dear Editor, \hfill \today \\

Please find the attached manuscript, entitled ``Haploid selection, sex ratio bias, and transitions between sex-determination systems'', which we submit to you for consideration for publication in \textit{PLoS Biology}.
\\

%findings;why important
[why this is cool]
\\

%Based upon their expertise in theoretical quantitative genetics in changing environments, we suggest Dr.\ Luis-Miguel Chevin$^1$, Dr.\ Richard Gomulkiewicz$^2$, and Dr.\ Reinhard B\"urger$^3$ as potential reviewers.

%This work is original and is not under consideration for publication elsewhere. 
%This work is original, unpublished and is not under consideration for publication elsewhere. %H
%All authors have agreed to the submission of the paper to \textit{Evolution}. %H

We hope you agree that this work is of broad interest to the readership of \textit{PLoS Biology} and we eagerly anticipate your response.\\

Sincerely,

[signature]\\
%\includegraphics[height=1.5cm]{IMAGES/OsmondSignature.pdf}
\indent Michael Scott, Matthew Osmond, Sarah Otto

%reviewer emails
%\small{$^1$ luis-miguel.chevin@cefe.cnrs.fr;  $^2$ gomulki@wsu.edu; $^3$ reinhard.buerger@univie.ac.at}

\end{document}

### 2018-02-04 LaTeX/Turnover_plos.tex
consistent region/locus, hyphens, allele/loci/chromosome, etc

@@
 \lfoot{\sf PLOS}
-
 %% Include all macros below
@@
 {\Large
-\textbf\newline{Haploid selection, sex ratio bias, and transitions between sex-determination systems} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
+\textbf\newline{Haploid selection, sex ratio bias, and transitions between sex-determining systems} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
 }
@@
 \section*{Abstract}
-Sex-determination systems are remarkably dynamic; many taxa display shifts in the location of sex-determining loci or the evolution of entirely new sex-determining systems. 
+Sex determination is remarkably dynamic; many taxa display shifts in the location of sex-determining loci or the evolution of entirely new sex-determining systems. 
 Predominant theories for why we observe such transitions generally conclude that novel sex-determining systems are favoured by selection if they equalise the sex ratio or increase linkage with a sexually-antagonistic locus.
@@
 (1) We explicitly consider selection on loci very tightly linked to the ancestral sex-determining loci, e.g., within the non-recombining region of the ancestral sex chromosomes. 
-Variation at such loci can favour the spread of new sex-determination systems in which the heterogametic sex changes (XY to ZW or ZW to XY) and the new sex-determining region is less closely linked (or unlinked) to the locus under selection, which is not predicted by previous theory.
+Variation at such loci can favour the spread of new sex-determining systems in which the heterogametic sex changes (XY to ZW or ZW to XY) and the new sex-determining region is less closely linked (or unlinked) to the locus under selection, which is not predicted by previous theory.
 (2) We also consider selection upon haploid genotypes either during gametic competition (e.g., pollen/sperm competition) or meiosis (i.e., non-Mendelian segregation), selective processes that typically occur in one sex or the other.
-We find that associations with haploid selected loci can drive transitions between sex determination systems, without requiring sexually-antagonistic selection in diploids. 
+We find that associations with haploid selected loci can drive transitions between sex-determining systems, without requiring sexually-antagonistic selection in diploids. 
 Unexpectedly, with haploid selection, transitions between male and female heterogamety can also evolve where linkage with the sex-determining locus is weakened. 
 Furthermore, haploid selection in the heterogametic sex can cause sex ratio biases, which may increase or decrease with the spread of new sex chromosomes. 
-Thus, we find that transitions between sex-determination systems cannot be simply predicted by selection to equalise the sex ratio. 
-Overall, our models reveal that transitions between sex-determination systems, particularly transitions where the heterogametic sex changes, can be driven by loci in previously unpredicted genomic locations that experience selection during diploid and/or haploid phases.
-These results predict conditions under which sex-determination systems are likely to be labile and draw novel connections with sex ratio evolution.
+Thus, we find that transitions between sex-determining systems cannot be simply predicted by selection to equalise the sex ratio. 
+Overall, our models reveal that transitions between sex-determining systems, particularly transitions where the heterogametic sex changes, can be driven by loci in previously unpredicted genomic locations that experience selection during diploid and/or haploid phases.
+These results predict conditions under which sex-determining systems are likely to be labile and draw novel connections with sex ratio evolution.
 
@@
 Accumulating evidence indicates that systems of sex determination are strikingly diverse and labile in many clades. 
-This poses the question: what drives transitions between sex determination systems? 
-Here, we use models to derive conditions under which new sex determination systems spread. 
-Prevailing views suggest that new sex determination systems are favoured when they equalize the sex ratio and/or when they are more closely linked to genes that experience differential selection in males and females.
+This poses the question: what drives transitions between sex-determining systems? 
+Here, we use models to derive conditions under which new sex-determining systems spread. 
+Prevailing views suggest that new sex-determining systems are favoured when they equalize the sex ratio and/or when they are more closely linked to genes that experience differential selection in males and females.
 Our models extends these theories to include selection upon haploid genotypes (meiotic drive or gametic competition), which causes sex ratio biases and occurs differently in males and females. 
-Surprisingly, we find that neither force (sex ratio selection nor associations with genes that have sex-specific effects) dominates the spread of new sex determination systems alone. 
+Surprisingly, we find that neither force (sex ratio selection nor associations with genes that have sex-specific effects) dominates the spread of new sex-determining systems alone. 
 Even more unexpectedly, we find that new sex-determining alleles do not necessarily have to arise in closer linkage with genes that are differentially selected in males and females to spread. 
-Therefore, our models predict loci in previously unexpected genomic locations and/or experiencing various types of selection (including haploid selection) can now be implicated as drivers of transitions between sex determination systems.
+Therefore, our models predict loci in previously unexpected genomic locations and/or experiencing various types of selection (including haploid selection) can now be implicated as drivers of transitions between sex-determining systems.
 
@@
 
-Animals and angiosperms exhibit extremely diverse sex-determination systems (reviewed in~\cite{Bull:1983vi,Charlesworth:2010it,Beukeboom:2014vb,Bachtrog:2014bx}). 
-Among species with genetic sex determination of diploid sexes (GSD), some taxa have heterogametic males (XY) and homogametic females (XX), including %non-monotreme?
+Animals and angiosperms exhibit extremely diverse sex-determining systems (reviewed in~\cite{Bull:1983vi,Charlesworth:2010it,Beukeboom:2014vb,Bachtrog:2014bx}). 
+Among species with genetic sex determination (GSD) of diploid sexes, some taxa have heterogametic males (XY) and homogametic females (XX), including %non-monotreme?
 I think monotremes have XY but tonnes of translocations, giving: X1,X2...X6 Y1
 mammals and most dioecious plants~\cite{Ming:2011iy}; whereas other taxa have homogametic males (ZZ) and heterogametic females (ZW), including Lepidoptera and birds. 
-Within several taxa, the chromosome that harbours the master sex-determining region changes. 
-For example, transitions of the master sex-determining gene between chromosomes or the evolution of new master sex-determining genes have occurred in Salmonids~\cite{Li:2011fm,Yano:2012di}, Diptera~\cite{Vicoso:2015hf}, and \textit{Oryzias}~\cite{Myosho:2012fv}.
+Within several taxa, the chromosome that harbours the master sex-determining locus changes. 
+For example, transitions of the master sex-determining locus between chromosomes or the evolution of new master sex-determining loci (where the heterogametic sex does not change, hereafter `cis-GSD transitions') have occurred in Salmonids~\cite{Li:2011fm,Yano:2012di}, Diptera~\cite{Vicoso:2015hf}, and \textit{Oryzias}~\cite{Myosho:2012fv}.
 %Presentation at evolution found neo sex chromosome in birds, doesn't seem to be published or bioRxiv yet (consider pers com.), title: A previously unknown neo-sex chromosome mediates plumage divergence and speciation in hybridizing birds Jason Sardell; Elizabeth Cooper; J.
@@
 I wonder if this is actually a fusion event though?
-In addition, many clades exhibit transitions between male (XY) and female (ZW) heterogamety, including snakes~\cite{Gamble2017}, lizards~\cite{Ezaz:2009tk}, eight of 26 teleost fish families~\cite{Mank:2006bt}, true fruit flies (Tephritids,~\cite{Vicoso:2015hf}, amphibians~\cite{Hillis:1990gu}, the angiosperm genus \textit{Silene}~\cite{Slancarova:2013dq}, the angiosperm family \textit{Salicaceae}~\cite{Pucholt2015,Pucholt2017} and Coleoptera and Hemiptera (plate 2~\cite{Beukeboom:2014vb}).
-Indeed, in some cases, both male and female heterogametic sex-determination systems can be found in the same species, as reported in houseflies~\cite{Macdonald1978}, midges~\cite{Thompson1971}, frogs~\cite{Ogata:2007jm}, cichlid fish~\cite{Ser:2010iq}, tilapia~\cite{Lee2004}, sea bass~\cite{Vandeputte2007}, and lab-strains of Zebrafish~\cite{Liew2012,Wilson2014}.
-In addition, multiple transitions have occurred between genetic (GSD) and environmental sex-determination (ESD) systems, e.g., in reptiles and fishes~\cite{Conover:1987in,Mank:2006bt,Pokorna:2009ui,Ezaz:2009tk,Pen:2010kk,Holleley:2015hc}.
-
-Predominant theories accounting for the spread of new sex-determination systems by selection involve fitness differences between sexes (e.g., sexually antagonistic selection) or sex ratio selection~\cite{Blaser2012, Beukeboom:2014vb,vanDoorn2014re}.
+In addition, many clades exhibit transitions between male and female heterogamety (XY$\leftrightarrow$ZW, hereafter `trans-GSD transitions'), including snakes~\cite{Gamble2017}, lizards~\cite{Ezaz:2009tk}, eight of 26 teleost fish families~\cite{Mank:2006bt}, true fruit flies (Tephritids,~\cite{Vicoso:2015hf}, amphibians~\cite{Hillis:1990gu}, the angiosperm genus \textit{Silene}~\cite{Slancarova:2013dq}, the angiosperm family \textit{Salicaceae}~\cite{Pucholt2015,Pucholt2017} and Coleoptera and Hemiptera (plate 2~\cite{Beukeboom:2014vb}).
+Indeed, in some cases, both male and female heterogametic sex-determining systems can be found in the same species, as reported in houseflies~\cite{Macdonald1978}, midges~\cite{Thompson1971}, frogs~\cite{Ogata:2007jm}, cichlid fish~\cite{Ser:2010iq}, tilapia~\cite{Lee2004}, sea bass~\cite{Vandeputte2007}, and lab-strains of Zebrafish~\cite{Liew2012,Wilson2014}.
+In addition, multiple transitions have occurred between genetic and environmental sex-determining systems (GSD$\leftrightarrow$ESD), e.g., in reptiles and fishes~\cite{Conover:1987in,Mank:2006bt,Pokorna:2009ui,Ezaz:2009tk,Pen:2010kk,Holleley:2015hc}.
+
+Predominant theories accounting for the spread of new sex-determining systems by selection involve fitness differences between sexes (e.g., sexually antagonistic selection) or sex ratio selection~\cite{Blaser2012, Beukeboom:2014vb,vanDoorn2014re}.
 %\citet{Bull:1977wt} shows that direct selection on new sex determination loci can allow them to spread and switch between male and female heterogamety. 
-van Doorn and Kirkpatrick~\cite{vanDoorn:2007eu,vanDoorn:2010hu} and Muralidhar and Veller~\cite{Muralidhar2018} have shown that new sex-determining loci can be favoured if they arise in close linkage with a locus that experiences sexual antagonism.
-Tighter linkage allows a stronger favourable association to build up between a male-beneficial allele, and a neo-Y chromosome, for example. 
-Such associations can favour a new partially-masculinizing or partially-feminizing allele~\cite{Muralidhar2018}, a new master sex-determining gene~\cite{vanDoorn:2007eu}, and transitions between male and female heterogamety (trans-GSD transitions, ZW to XY or XY to ZW~\cite{vanDoorn:2010hu}).
-However, any sexually-antagonistic loci that are more closely linked to the ancestral sex-determination locus will develop similar, favourable associations and are expected to hinder the spread of a new sex-determination system.
-
-The sex ratio is directly determined by the sex-determination system, and it has therefore been suggested that sex ratio selection is a dominant force in the evolution of sex determination (e.g., Bull, 1983, p 66-67 ~\cite{Bull:1983vi}; Buekeboom and Perrin, 2014, Chapter 7~\cite{Beukeboom:2014vb}).
+van Doorn and Kirkpatrick~\cite{vanDoorn:2007eu,vanDoorn:2010hu} and Muralidhar and Veller~\cite{Muralidhar2018} have shown that new sex-determining alleles can be favoured if they arise at loci in close linkage with a locus that experiences sexual antagonism.
+Tighter linkage allows a stronger favourable association to build up between a male-beneficial allele, and a neo-Y allele, for example. 
+Such associations can favour cis-GSD transitions~\cite{vanDoorn:2007eu}, trans-GSD transitions~\cite{vanDoorn:2010hu}, and new partially-masculinizing or partially-feminizing alleles~\cite{Muralidhar2018}.
+However, any sexually-antagonistic loci that are more closely linked to the ancestral sex-determining locus will develop similar, favourable associations and are expected to hinder the spread of a new sex-determining system.
+
+The sex ratio is directly determined by the sex-determining system, and it has therefore been suggested that sex ratio selection is a dominant force in the evolution of sex determination (e.g., Bull, 1983, p 66-67 ~\cite{Bull:1983vi}; Buekeboom and Perrin, 2014, Chapter 7~\cite{Beukeboom:2014vb}).
 `Fisherian' sex ratio selection favours a 1:1 zygotic sex ratio when assuming that males and females are equally costly to produce~\cite{Fisher:1930wy,Charnov:1982wg}.
@@
 %The default mode of sex ratio selection is `Fisherian' sex ratio selection, which favours equal investment in male and female offspring \citep[i.e., a 1:1 zygotic sex ratio when assuming that males and females are equally costly to produce,][]{Fisher:1930wy,Charnov:1982wg}.
-%Given that the sex-determination system can directly affect the sex ratio, we might expect Fisherian sex ratio selection to influence the spread of new sex-determination systems. 
+%Given that the sex-determining system can directly affect the sex ratio, we might expect Fisherian sex ratio selection to influence the spread of new sex-determining systems. 
 In the case of sex-chromosome evolution, Kozielska et al.
 (2014)~\cite{Kozielska:2010vm} consider systems in which the ancestral sex chromosomes experience meiotic drive (e.g., where driving X or Y chromosomes are inherited disproportionately often), which causes sex ratios to become biased~\cite{Hamilton:1967ts}.
-They find that new, unlinked sex-determining loci (masculinizing or feminizing mutations, i.e., neo-Y or neo-W loci) can then spread, which restore an even sex ratio.
-
-Here we use mathematical models to find the conditions under which new sex-determination systems spread when individuals experience selection at both diploid and haploid stages. 
+They find that masculinizing or feminizing mutations that arise at a new, unlinked locus (i.e., neo-Y or neo-W chromosomes) can then spread, which restore an even sex ratio.
+
+Here we use mathematical models to find the conditions under which new sex-determining systems spread when individuals experience selection at both diploid and haploid stages, which allows fitness differences between the sexes and sex ratio biases to occur simultaneously.
 Even in animal and plant species that have much larger and more conspicuous diploid phases than haploid phases, many loci experience significant haploid selection through gamete competition and/or meiotic drive~\cite{Mulcahy:1996ha,JOSEPH:2004haa}.
@@
 
-There are various ways by which genes experiencing haploid selection could influence transitions between sex-determination systems. 
+There are various ways by which genes experiencing haploid selection could influence transitions between sex-determining systems. 
 If we assume that haploid selection at any particular locus predominantly occurs in one sex (e.g., meiotic drive during spermatogenesis), then such loci experience a form of sex-specific selection. 
-In this respect, we might expect that haploid selection would affect transitions between sex-determination systems in a similar manner to sex-specific diploid selection (as explored in~\cite{vanDoorn:2007eu,vanDoorn:2010hu}).
-That is, new masculinizing mutations (neo-Y chromosomes) could be favoured via associations with alleles that are beneficial in the male haploid stage. 
-On the other hand, sex ratios can also become biased by linkage between the sex-determining region and a locus that harbours genetic variation in haploid fitness. 
+In this respect, we might expect that haploid selection would affect transitions between sex-determining systems in a similar manner to sex-specific diploid selection (as explored in~\cite{vanDoorn:2007eu,vanDoorn:2010hu}).
+That is, new masculinizing mutations (neo-Y alleles) could be favoured via associations with alleles that are beneficial in the male haploid stage. 
+On the other hand, sex ratios can also become biased by linkage between the sex-determining locus and a locus that harbours genetic variation in haploid fitness. 
 For example, there are several known cases of sex ratio bias caused by sex-linked meiotic drive alleles (Burt, 2006, Chapter 6~\cite{Burt:2006}) or selection among X- and Y-bearing pollen~\cite{Lloyd:1974tz,Conn:1981uw,Stehlik:2005ul,Stehlik:2006to,Field:2012fd,Field:2013cc}.
-It is not immediately clear how the spread of new sex-determination systems would be influenced by the combination of sex ratio biases and associations between haploid selected loci and sex-determining regions.
-
-We find that the spread of novel sex-determiners is influenced by both Fisherian sex ratio selection and by selection on genetically-associated alleles. 
+It is not immediately clear how the spread of new sex-determining systems would be influenced by the combination of sex ratio biases and associations with haploid selected alleles.
+
+We find that the spread of novel sex-determining systems is influenced by both Fisherian sex ratio selection and by selection on linked alleles. 
 %We find that sex ratio biases caused by haploid selection can exert Fisherian sex ratio selection upon novel sex-determiners but that their spread is also determined by selection on genetically-associated alleles.
@@
 Surprisingly, Fisherian sex ratio selection does not dominate; it is possible for selection on linked alleles to drive turnover between sex-determining systems despite causing increasingly biased sex ratios.
-In addition to considering haploid selection, another novel development in our model is that we consider loci that are in very tight linkage with the ancestral sex-determining region. 
+In addition to considering haploid selection, another novel development in our model is that we consider loci that are in very tight linkage with the ancestral sex-determining locus. 
 %Because sex-determining loci are often found within a region of suppressed recombination, there can be a significant number of tightly linked loci. 
-We find that loci tightly linked with the ancestral sex-determining region can drive transitions in which the heterogametic sex changes, even when the neo-sex-determining locus is less closely linked to loci under selection (either including haploid selection or not).
+We find that loci tightly linked with the sex-determining locus can drive transitions in which the heterogametic sex changes, even when the new sex-determining locus is less closely linked to loci under selection (either including haploid selection or not).
 
@@
 We consider transitions between ancestral and novel sex-determining systems using a three-locus model, each locus having two alleles (Fig \ref{fig:model_outline}). 
-Locus \textbf{X} is the ancestral sex-determining region, with alleles $X$ and $Y$ (or $Z$ and $W$).
-Locus \textbf{A} is a locus under selection, with alleles $A$ and $a$.
-Locus \textbf{M} is a novel sex-determining region, at which the null allele ($M$) is initially fixed in the population such that sex of zygotes is determined by the genotype at the ancestral sex-determining region, \textbf{X}; $XX$ genotypes become females and $XY$ become males (or $ZW$ become females and $ZZ$ become males).
-To evaluate the evolution of new sex-determination systems, we consider the invasion, fixation, maintenance, and/or loss of novel sex-determining alleles ($m$) at the \textbf{M} locus. 
+Locus $\mathbf{X}$ is the ancestral sex-determining region, with alleles X and Y (or Z and W).
+Locus $\mathbf{A}$ is a locus under selection, with alleles $A$ and $a$.
+Locus $\mathbf{M}$ is a novel sex-determining region, at which the null allele ($M$) is initially fixed in the population such that sex of zygotes is determined by the genotype at the ancestral sex-determining region, $\mathbf{X}$; XX genotypes become females and XY become males (or ZW become females and ZZ become males).
+To evaluate the evolution of new sex-determining systems, we consider the invasion, fixation, maintenance, and/or loss of a novel sex-determining allele ($m$) at the $\mathbf{M}$ locus. 
 %We only do invasion analytically though (is this sentence still ok?)
-We assume that the \textbf{M} locus is epistatically dominant over the \textbf{X} locus such that zygotes with at least one $m$ allele develop as females with probability $k$ and as males with probability $1-k$, regardless of the \textbf{X} locus genotype.
-With $k=0$, the $m$ allele is a masculinizer (i.e., a neo-Y) and with $k=1$ the $m$ allele is a feminizer (i.e., a neo-W).
-With intermediate $k$, we can interpret $m$ as an environmental sex determination (ESD) allele, such that zygotes develop as females in a proportion ($k$) of the environments they experience. 
+We assume that the $\mathbf{M}$ locus is epistatically dominant over the $\mathbf{X}$ locus such that zygotes with at least one $m$ allele develop as females with probability $k$ and as males with probability $1-k$, regardless of the $\mathbf{X}$ locus genotype.
+With $k=0$, the $m$ allele is a masculinizer (a neo-Y allele) and with $k=1$ the $m$ allele is a feminizer (a neo-W allele).
+With intermediate $k$, we can interpret $m$ as an environmental sex-determination (ESD) allele, such that zygotes develop as females in a proportion ($k$) of the environments they experience. 
 %We also analyze a model of maternally-controlled environmental sex-determination, where mothers with at least one $m$ allele produce daughters with probability $k$.
@@
 {\bf Outline of model features.}
-Panel A: Recombination rate parameters between the ancestral-sex-determining locus (here, assumed to have X or Y alleles), a locus under selection (\textbf{A}, with alleles $A$ and $a$), and a neo-sex-determining locus (\textbf{M}, with alleles $M$ and $m$).
-If $r<1/2$, then associations between ancestral-sex-determining alleles (X and Y) and \textbf{A} locus alleles can be maintained past recombination in males.
+Panel A: Recombination rate parameters between the ancestral-sex-determining locus ($\mathbf{X}$, here assumed to have alleles X and Y), a locus under selection ($\mathbf{A}$, with alleles $A$ and $a$), and a new sex-determining locus ($\mathbf{M}$, with alleles $M$ and $m$).
+If $r<1/2$, then associations between ancestral sex-determining alleles and selected alleles can be maintained past recombination in males. 
 Panel B: Haploid selection is often sex-specific, occurring during haploid production or competition in either males or females. 
 For example, haploid selection in males only is represented by the dashed circle.  
-If X or Y alleles remain associated with alleles that experience haploid selection in males ($r<1/2$), then zygotic sex ratios can become biased because either X or Y male gametes/gametophytes will be abundant after haploid selection.
-However, the zygotic sex ratio is not biased by male haploid selection in ZW sex-determination systems. 
-Similarly, zygotic sex ratio biases can occur if haploid selected alleles are associated with neo-sex-determining alleles ($M$ and $m$, i.e., if $R<1/2$). 
-Panel C: During cis-GSD transitions (XY to XY or ZW to ZW, without loss of generality we assume ancestral XY sex determination here), a neo-Y allele spreads to pseudo-fixation (its maximum frequency among male gametes) and the the ancestral-Y allele is lost.
-Panel D: During trans-GSD transitions (XY to ZW or ZW to XY), a neo-W allele spreads to pseudo-fixation (its maximum frequency among female gametes) and the ancestral-X allele is lost.
-Neo-W mutations allow Y-associated alleles into females, which may impede or aid their spread.
+If X or Y alleles remain associated with alleles that experience haploid selection in males ($r<1/2$), then zygotic sex ratios can become biased because either X- or Y-bearing male gametes/gametophytes will be more abundant after haploid selection.
+However, the zygotic sex ratio is not biased by male haploid selection in ZW sex-determining systems. 
+Similarly, zygotic sex ratio biases can occur if haploid selected alleles are associated with new sex-determining alleles ($R<1/2$). 
+Panel C: During cis-GSD transitions (XY to XY or ZW to ZW), a neo-Y allele spreads to pseudo-fixation (its maximum frequency among male gametes) and the ancestral Y allele is lost. 
+Panel D: During trans-GSD transitions (XY to ZW or ZW to XY), a neo-W allele spreads to pseudo-fixation (its maximum frequency among female gametes) and the ancestral X allele is lost. 
+Neo-W alleles allow Y-associated alleles into females, which may impede or aid their spread. 
 }
@@
 First, competition occurs among male gametes (sperm/pollen competition) and among female gametes (egg/ovule competition) separately. 
-Selection during gametic competition depends on the \textbf{A} locus genotype, relative fitnesses are given by $w_A^\Hermaphrodite$ and $w_a^\Hermaphrodite$ ($\Hermaphrodite \in \{\female,\male\}$; see table \ref{tab:fitnesstable}).
+Selection during gametic competition depends on the $\mathbf{A}$ locus genotype; relative fitnesses are given by $w_A^\Hermaphrodite$ and $w_a^\Hermaphrodite$ ($\Hermaphrodite \in \{\female,\male\}$; see table \ref{tab:fitnesstable}).
 %$w_{A}^\male$ and $w_{a}^\male$ for male gametes and $w_{A}^\female$ and $w_{a}^\female$ for female gametes, see table \ref{tab:fitnesstable}.
-We assume that all gametes compete for fertilization during gametic competition, which assumes a polygamous mating system. 
+We assume that all gametes compete for fertilization during gametic competition, which implies a polygamous mating system. 
 Gametic competition in monogamous mating systems is, however, equivalent to meiotic drive in our model (described below), as either only alters the frequency of gametes produced by heterozygotes. 
-After gametic competition, random mating occurs between male and female gametes.
-The resulting zygotes develop as males or females, depending on their genotypes at the \textbf{X} and \textbf{M} loci. %(and the \textbf{M} genotype of their mother in the case of maternal control).
+After gametic competition, conjugation between male and female gametes occurs at random.
+The resulting zygotes develop as males or females, depending on their genotypes at the $\mathbf{X}$ and $\mathbf{M}$ loci.
+%(and the $\mathbf{M}$ genotype of their mother in the case of maternal control).
 Diploid males and females then experience selection, with relative fitnesses $w_{AA}^{\Hermaphrodite}$, $w_{Aa}^{\Hermaphrodite}$, and $w_{aa}^{\Hermaphrodite}$.
-%where $g$ is the diploid genotype at the \textbf{A} locus ($g \in \{AA, Aa, aa\}$).
-%Diploids compete with others of the same sex, where selection depends on the sex of the individual and its genotype at the \textbf{A} locus.
+%where $g$ is the diploid genotype at the $\mathbf{A}$ locus ($g \in \{AA, Aa, aa\}$).
+%Diploids compete with others of the same sex, where selection depends on the sex of the individual and its genotype at the $\mathbf{A}$ locus.
 The next generation of gametes is produced by meiosis, during which recombination and sex-specific meiotic drive can occur. 
-Recombination (i.e., an odd number of cross-overs) occurs between loci \textbf{X} and \textbf{A} with probability $r$, between loci \textbf{A} and \textbf{M} with probability $R$, and between loci \textbf{X} and \textbf{M} with probability $\rho$.
+Recombination (i.e., an odd number of cross-overs) occurs between loci $\mathbf{X}$ and $\mathbf{A}$ with probability $r$, between loci $\mathbf{A}$ and $\mathbf{M}$ with probability $R$, and between loci $\mathbf{X}$ and $\mathbf{M}$ with probability $\rho$.
 Any linear order of the loci can be modelled with appropriate choices of $r$, $R$, and $\rho$ (see Fig \ref{fig:model_outline}A and \nameref{tab:chisubstitutions}). 
-Individuals that are heterozygous at the \textbf{A} locus may experience meiotic drive; a gamete produced by $Aa$ heterozgotes of sex $\Hermaphrodite$ bears allele $A$ with probability $\alpha^\Hermaphrodite$.
-Thus, the \textbf{A} locus can experience sex-specific gametic competition, diploid selection, and/or meiotic drive.
+Individuals that are heterozygous at the $\mathbf{A}$ locus may experience meiotic drive; a gamete produced by $Aa$ heterozgotes of sex $\Hermaphrodite$ bears allele $A$ with probability $\alpha^\Hermaphrodite$.
+Thus, the $\mathbf{A}$ locus can experience sex-specific gametic competition, diploid selection, and/or meiotic drive.
 
@@
   Genotype & Relative fitness during gametic competition \\ [0.5ex] \hline
-  A & $w_{A}^\Hermaphrodite = 1+t^\Hermaphrodite$ \\
-  a & $w_{a}^\Hermaphrodite = 1$ \\ [0.5ex] \hline
+  $A$ & $w_{A}^\Hermaphrodite = 1+t^\Hermaphrodite$ \\
+  $a$ & $w_{a}^\Hermaphrodite = 1$ \\ [0.5ex] \hline
   Genotype & Relative fitness during diploid selection \\ [0.5ex] \hline
-  AA & $w_{AA}^\Hermaphrodite = 1+ s^\Hermaphrodite$ \\
-  Aa & $w_{Aa}^\Hermaphrodite = 1+h^\Hermaphrodite s^\Hermaphrodite$ \\
-  aa & $w_{aa}^\Hermaphrodite = 1$ \\ [0.5ex] \hline
+  $AA$ & $w_{AA}^\Hermaphrodite = 1+ s^\Hermaphrodite$ \\
+  $Aa$ & $w_{Aa}^\Hermaphrodite = 1+h^\Hermaphrodite s^\Hermaphrodite$ \\
+  $aa$ & $w_{aa}^\Hermaphrodite = 1$ \\ [0.5ex] \hline
   Genotype & Transmission during meiosis in $Aa$ heterozygotes \\ [0.5ex] \hline
-  A & $\alpha^\Hermaphrodite=1/2+\alpha_{\Delta}^{\Hermaphrodite}/2$ \\
-  a & $1-\alpha^\Hermaphrodite=1/2-\alpha_{\Delta}^{\Hermaphrodite}/2$ \\
+  $A$ & $\alpha^\Hermaphrodite=1/2+\alpha_{\Delta}^{\Hermaphrodite}/2$ \\
+  $a$ & $1-\alpha^\Hermaphrodite=1/2-\alpha_{\Delta}^{\Hermaphrodite}/2$ \\
   \hline \hline
@@
 
-The model outlined above describes both ancestrally-XY and ancestrally-ZW sex-determination systems if we relabel the two sexes as being ancestrally `heterogametic' or ancestrally `homogametic'. 
+The model outlined above describes both ancestral XY and ZW sex-determining systems. %if we relabel the two sexes as being ancestrally `heterogametic' or ancestrally `homogametic'. 
 Without loss of generality, we primarily refer to the ancestrally heterogametic sex as male and the ancestrally homogametic sex as female.
-That is, we describe an ancestral XY sex-determination system but our model is equally applicable to an ancestral ZW sex-determination system (relabelling the ancestrally-heterogametic sex as female and the ancestrally-homogametic sex as male and switching the labels of males and females throughout).
+That is, we describe an ancestral XY sex-determining system but our model is equally applicable to an ancestral ZW sex-determining system (relabelling the ancestrally heterogametic sex as female and the ancestrally homogametic sex as male and switching the labels of males and females throughout).
 
@@
 
-The evolution of a new sex-determination system requires that a rare mutant allele at the novel sex-determining locus, $m$, increases in frequency when rare. 
-The spread of a rare mutant $m$ at the \textbf{M} locus into a system with ancestral sex-determination system $i\in\{XY,ZW\}$ is determined by the leading eigenvalue ($\lambda_m^{(i)}$) of the system of eight equations describing the frequency of eggs and sperm carrying the $m$ allele in the next generation (equations \ref{eq:recursions}).
+The evolution of a new sex-determining system requires that a rare mutant allele, $m$, at the novel sex-determining locus, $\mathbf{M}$, increases in frequency when rare. 
+This is determined by the leading eigenvalue ($\lambda_m^{(XY)}$) of the system of eight equations describing the frequency of eggs and sperm carrying the $m$ allele in the next generation (equations \ref{eq:recursions}).
 %, evaluated at the above equilibrium.
@@
 This system simplifies substantially for a dominant neo-Y ($k=0$) or neo-W ($k=1$), see \nameref{app:inv_cond}. 
-Invasion of a rare neo-Y or neo-W allele, $m\in\{Y',W'\}$, is given by the largest solution to the quadratic $(\lambda_m^{(i)})^2+ b \lambda_m^{(i)} + c =0$. 
-Here, $b= - (\Lambda_{mA}^{(i)} + \Lambda_{ma}^{(i)})+(\chi_{mA}^{(i)} + \chi_{ma}^{(i)})$ and $c = (\Lambda_{mA}^{(i)} - \chi_{mA}^{(i)}) (\Lambda_{ma}^{(i)} - \chi_{ma}^{(i)}) - \chi_{mA}^{(i)} \chi_{ma}^{(i)}$, where $\Lambda_{mj}^{(i)}$ is the multiplicative growth rate (which we will call the ``haplotypic growth rate'') of the neo-sex determination allele $m$ on background $j\in\{A,a\}$ without accounting for loss due to recombination ($R=0$), and $\chi_{mj}^{(i)}$ is the rate at which mutant haplotypes on background $j\in\{A,a\}$ recombine onto the other \textbf{A} locus background in heterozygotes (proportional to $R$), see Table \ref{tab:haplotype_growth}.
+The leading eigenvalue for a rare neo-Y or neo-W allele, $m\in\{Y',W'\}$, is the largest value of X that solves $x^2+ b x + c = 0$.  %$(\lambda_m^{(i)})^2+ b \lambda_m^{(i)} + c =0$. 
+The coefficients are $b= - (\Lambda_{mA}^{(XY)} + \Lambda_{ma}^{(XY)})+(\chi_{mA}^{(XY)} + \chi_{ma}^{(XY)})$ and $c = (\Lambda_{mA}^{(XY)} - \chi_{mA}^{(XY)}) (\Lambda_{ma}^{(XY)} - \chi_{ma}^{(XY)}) - \chi_{mA}^{(XY)} \chi_{ma}^{(XY)}$, where $\Lambda_{mi}^{(XY)}>0$ is the multiplicative growth rate (which we will call the ``haplotypic growth rate'') of the neo-sex determination allele $m$ on background $i\in\{A,a\}$ without accounting for loss due to recombination ($R=0$), and $\chi_{mi}^{(XY)}>0$ is the rate at which mutant haplotypes on background $i\in\{A,a\}$ recombine onto the other $\mathbf{A}$ locus background in heterozygotes (proportional to $R$), see Table \ref{tab:haplotype_growth}.
 In the ancestral population, it is convenient to follow the frequency of the $A$ allele among female gametes (eggs), $p^\female_X$, and among X-bearing, $p^\male_X$, and among Y-bearing, $p^\male_Y$, male gametes (sperm/pollen).
@@
 $\bar{p}^{\male}=(1-\hat{q})\hat{p}_X^\male + \hat{q}\hat{p}_Y^\male$ is the average frequency of the $A$ allele among X- and Y-bearing male gametes.
-%      \item $R$ is the probability of recombination between loci \textbf{A} and \textbf{M}.
+%      \item $R$ is the probability of recombination between loci $\mathbf{A}$ and $\mathbf{M}$.
 $\zeta$ is the zygotic sex ratio (fraction male).
@@
 
-We are particularly concerned with the conditions under which a rare neo-sex-determining allele increases in frequency, which occurs when the largest eigenvalue is greater than one ($\lambda_m^{(i)}>1$).
+The new sex-determining allele increases in frequency when rare when the largest eigenvalue is greater than one ($\lambda_m^{(XY)}>1$). 
 %If the average change in frequency of the two haplotypes that carry the $m$ allele ($Am$ and $am$) is positive, invasion will always occur, i.e., if $(\Lambda_{mA} + \Lambda_{ma})/2 > 1$ then $\Lambda > 1$.
@@
 %Since $f(\Lambda_{mA}^{(i)})$ and $f(\Lambda_{ma}^{(i)})$ are of opposite signs, the leading eigenvalue must fall between these two quantities and is the larger of them when $R = 0$ (see \nameref{file:Mathematica}).
-If both $\Lambda_{mA}^{(i)}$ and $\Lambda_{ma}^{(i)}$ are greater than one, then the leading eigenvalue will always be greater than one, regardless of the linkage between the neo-sex determination factor and the selected locus ($R$), see \nameref{app:inv_cond} for details.
-Conversely, if both $\Lambda_{mA}^{(i)}$ and $\Lambda_{ma}^{(i)}$ are smaller than one, then invasion can never occur.  
-Finally, if only one of  $\Lambda_{mA}^{(i)}$ and $\Lambda_{ma}^{(i)}$ is greater than one, the new sex determining factor can always invade when tightly linked to the selected locus ($R$ near 0).  
-Furthermore, it can be shown that the leading eigenvalue declines with $R$, and invasion requires that $R$ is sufficiently small that the following condition holds: 
+If both haplotypic growth rates are greater than one ($\Lambda_{mA}^{(XY)}, \Lambda_{ma}^{(XY)}>1$), then the new sex-determining allele invades regardless the rate of recombination between the new sex-determining locus and the selected locus ($R$), see \nameref{app:inv_cond} for details.
+Conversely, if both haplotypic growth rates are less than one ($\Lambda_{mA}^{(XY)}, \Lambda_{ma}^{(XY)}<1$), then invasion can never occur.  
+Finally, if only one haplotypic growth rate is greater than one, the new sex-determining allele can always invade when arising at a locus that is tightly linked to the selected locus ($R\approx0$).  
+Furthermore, it can be shown that the leading eigenvalue declines with $R$, and invasion requires that $R$ is sufficiently small such that: 
 \begin{equation}\label{eq:lambdasGen}
 %\frac{\chi_{mA}}{\Lambda_{mA}-1}+\frac{\chi_{ma}}{\Lambda_{ma}-1}>0.
-\chi_{ma}^{(i)}/\left(\Lambda_{ma}^{(i)} - 1\right) + \chi_{mA}^{(i)}/\left(\Lambda_{mA}^{(i)} - 1\right) < 1.
+\chi_{ma}^{(XY)}/\left(\Lambda_{ma}^{(XY)} - 1\right) + \chi_{mA}^{(XY)}/\left(\Lambda_{mA}^{(XY)} - 1\right) < 1.
 \end{equation}
 \noindent 
-This condition may or may not be satisfied for the full range of locations of the new sex determining factor, including $R=1/2$, depending on the nature of selection.  
-Interpreting this condition, if we assume that only the $mA$ haplotype has a positive growth rate when $R=0$, $\Lambda_{ma}^{(i)}<1<\Lambda_{mA}^{(i)}$, the first term on the left-hand side of \eqref{eq:lambdasGen} is negative and invasion requires that the $mA$ haplotypic growth rate ($\Lambda_{mA}^{(i)} - 1$) and the rate at which $mA$ haplotypes are produced by recombination in $ma$ haplotypes ($\chi_{ma}^{(i)}$) are sufficiently large relative to the $ma$ haplotype rate of decline ($1-\Lambda_{ma}^{(i)}$) and the rate of loss of $mA$ haplotypes due to recombination ($\chi_{mA}^{(i)}$).
+This condition may or may not be satisfied for the full range of locations of the new sex-determining locus, including $R=1/2$, depending on the nature of selection.  
+Interpreting this condition, if we assume that only the $mA$ haplotype would increase in frequency when $R=0$ ($\Lambda_{ma}^{(XY)}<1<\Lambda_{mA}^{(XY)}$) the first term on the left-hand side of \eqref{eq:lambdasGen} is negative and invasion requires that rate of growth of $mA$ haplotypes ($\Lambda_{mA}^{(i)}-1>0$) and the rate at which $mA$ haplotypes are produced by recombination in $ma$ haplotypes ($\chi_{ma}^{(i)}$) are sufficiently large relative to the rate of decline of $ma$ haplotypes ($1-\Lambda_{ma}^{(i)}>0$) and the rate of loss of $mA$ haplotypes due to recombination ($\chi_{mA}^{(i)}$).
 
 We can draw a number of key points about the invasion of neo-Y and neo-W mutations from Table \ref{tab:haplotype_growth}. 
-First, Fisherian sex ratio selection will favour the spread of a neo-Y if the ancestral zygotic sex ratio is biased towards females, $\zeta<1/2$ (i.e., the first factor of the $\Lambda_{mi}^{(i)}$ is greater than one for a neo-Y and less than one for a neo-W).
+First, Fisherian sex ratio selection will favour the spread of a neo-Y and inhibit the spread of a neo-W if the ancestral zygotic sex ratio is biased towards females, $\zeta<1/2$ (i.e., the first factor of the $\Lambda_{mi}^{(XY)}$ is greater than one for a neo-Y and less than one for a neo-W).
 However, the spread of a neo-Y (neo-W) also depends on the male (female) fitness of associated alleles (see terms involving equilibrium allele frequencies, $\hat{p}$'s).
-Second, invasion by a neo-Y (neo-W) allele does not directly depend on the fitness of female (male) diploids. %(for a given set of equilibrium allele frequencies).
-This is because a dominant neo-Y (neo-W) is always found in males (females), and therefore the frequency of the neo-Y (neo-W) allele, $m$, only changes in males (females), Fig \ref{fig:model_outline}C,D.
+Second, invasion by a neo-Y (neo-W) does not directly depend on the fitness of female (male) diploids. %(for a given set of equilibrium allele frequencies).
+This is because a dominant neo-Y (neo-W) is always found in males (females), and therefore the frequency of the neo-Y (neo-W), $m$, only changes in males (females), Fig \ref{fig:model_outline}C,D. 
 Finally, invasions by a neo-Y and a neo-W are qualitatively different.
-This is because a gamete with the neo-Y always pairs with a female gamete containing an X, and develop into males, Fig \ref{fig:model_outline}C.
-By contrast, a gamete with a neo-W can pair with an X or Y male gamete, developing into a female, Fig \ref{fig:model_outline}D.
-Consequently, neo-W bearing females obtain a differerent frequency of $A$ alleles from mating (when $\hat{p}_X^\male \neq \hat{p}_Y^\male$) compared to ancestral ($MM$) females.
-
-In order to explicitly determine the conditions under which a rare neo-sex-determining allele spreads, we must calculate the equilibrium frequency of the $A$ allele (i.e., $\hat{p}^\female_X$, $\hat{p}^\male_X$, and $\hat{p}^\male_Y$) and Y-bearing male gametes ($\hat{q}$) in the ancestral population.
-Since only the \textbf{A} locus experiences selection directly, any deterministic evolution requires that there is a polymorphism at the \textbf{A} locus. 
+This is because a gamete with the neo-Y always pairs with a female gamete containing an X, Fig \ref{fig:model_outline}C.
+By contrast, a gamete with a neo-W can pair with an X- or Y-bearing male gamete, Fig \ref{fig:model_outline}D.
+Consequently, neo-W-bearing females obtain a different frequency of $A$ alleles from mating (when $\hat{p}_X^\male \neq \hat{p}_Y^\male$) compared to ancestral ($MM$) females.
+
+In order to explicitly determine the conditions under which a rare new sex-determining allele spreads, we must calculate the equilibrium frequency of the $A$ allele (i.e., $\hat{p}^\female_X$, $\hat{p}^\male_X$, and $\hat{p}^\male_Y$) and Y-bearing male gametes ($\hat{q}$) in the ancestral population.
+Since only the $\mathbf{A}$ locus experiences selection directly, any deterministic evolution requires that there is a polymorphism at the $\mathbf{A}$ locus. 
 Polymorphisms can be maintained by mutation-selection balance or transiently present during the spread of beneficial alleles. 
 However, polymorphisms maintained by selection can maintain alleles at intermediate allele frequencies for longer periods. 
-Here, we focus on polymorphisms maintained by selection, where the $A$ allele reaches a stable intermediate equilibrium frequency under the ancestral sex-determination system before the neo-sex-determining allele ($m$) arises.
+Here, we focus on polymorphisms maintained by selection, where the $A$ allele reaches a stable intermediate equilibrium frequency under the ancestral sex-determining system before the new sex-determining allele ($m$) arises.
 Such polymorphisms can be maintained by heterozygote advantage, sexually-antagonistic selection, ploidally-antagonistic selection, or a combination~\cite{Immler:2012tl}.
 We can analytically calculate the allele frequency of the $A$ allele using two alternative simplifying assumptions: 
-(1) the \textbf{A} locus is within (or tightly linked to) the non-recombining region around the ancestral SDR ($r \approx 0$) or (2) selection is weak relative to recombination ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon<<1$).
-
-\subsection*{Tight linkage with the ancestral sex-determining region ($r \approx 0$)}
+(1) the $\mathbf{A}$ locus is within (or tightly linked to) the non-recombining region around the ancestral sex-determining locus ($r \approx 0$) or (2) selection is weak relative to recombination ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon<<1$).
+
+\subsection*{Tight linkage with the ancestral sex-determining locus ($r \approx 0$)}
 
 The ancestral equilibrium allele frequencies and their stability conditions are given in \nameref{app:eq_stab}. 
-When there is complete linkage between the ancestral sex-determining region and the \textbf{A} locus ($r=0$), either the $A$ allele or the $a$ allele must be fixed on the Y. 
+When there is complete linkage between the ancestral sex-determining locus and the $\mathbf{A}$ locus ($r=0$), either the $A$ allele or the $a$ allele must be fixed in gametes containing a Y allele. 
 % because selection on the Y is effectively haploid an incapably of maintaining a polymorphism in the absence of frequency dependent selection. 
-Because the labelling of alleles is arbitrary, we will assume that the $a$ locus is fixed on the Y ($p^\male_Y=0$), without loss of generality. 
-If there are two alleles maintained at the \textbf{A} locus, the X can either be fixed for the $A$ allele ($\hat{p}^\female_X=\hat{p}^\male_X=1$) or polymorphic (0<$\hat{p}^\female_X, \hat{p}^\male_X$<1).
+Because the labelling of alleles is arbitrary, we will assume that the $a$ locus is fixed in gametes with a Y ($p^\male_Y=0$), without loss of generality. 
+If there are two alleles maintained at the $\mathbf{A}$ locus, the $A$ allele can be fixed ($\hat{p}^\female_X=\hat{p}^\male_X=1$) or segregating at an intermediate frequency (0<$\hat{p}^\female_X, \hat{p}^\male_X$<1) in gametes with an X.
 %However, because the X is present in both males and females, there are distinct selection pressures on X's in females and X's in males, which will always be paired with an $A$ allele from the Y.
 
-We find that a neo-Y can never invade an ancestral XY system that already has tight linkage with the locus under selection ($\lambda_{Y'}^{(XY)} \leq 1$ when $r=0$, for details see \nameref{file:Mathematica}).
+We find that a neo-Y allele can never invade an ancestral XY system that already has tight linkage with the locus under selection ($\lambda_{Y'}^{(XY)} \leq 1$ when $r=0$, for details see \nameref{file:Mathematica}).
 When $R=0$, a neo-Y haplotype with the same allele as the ancestral Y is neutral ($\Lambda_{Y'a}^{(XY)}=1$) and does not change in frequency.
 The other neo-Y haplotype will not spread ($\Lambda_{Y'A}^{(XY)}<1$) given that the initial equilibrium is stable. 
-Therefore, a neo-Y mutation cannot spread in an ancestral XY system ($\lambda_{Y'}^{(XY)} \leq 1$, regardless of $R$) where selected loci are within or very near the non-recombining region around the SDR.
-In essence, through tight linkage with the \textbf{A} locus, the ancestral Y becomes strongly specialized on the allele that has the highest fitness across male haploid and diploid phases. 
+Therefore, a neo-Y mutation cannot spread in an ancestral XY system ($\lambda_{Y'}^{(XY)} \leq 1$, regardless of $R$) where selected loci are within or very near the non-recombining region around the sex-determining locus.
+In essence, through tight linkage with the $\mathbf{A}$ locus, the ancestral Y becomes strongly specialized on the allele that has the highest fitness across male haploid and diploid phases. 
 Given that the ancestral Y is at this equilibrium, it is not possible for a neo-Y to create males that have higher fitness than the ancestral Y.
@@
 Neo-W alleles, on the other hand, can invade an ancestral XY system under some conditions (the full invasion conditions are given in \nameref{app:inv_cond}; equations \ref{Binvasion} and \ref{Ainvasion}).
-Counterintuitively, selection on loci within the non-recombining region of the SDR can favour the invasion of a less closely linked neo-W, whatever the form of selection maintaining a polymorphism (sexually-antagonistic selection, overdominance, ploidally-antagonistic selection, or some combination, Fig \ref{fig:SexAntagTighter}, \nameref{fig:temporalOverdominance}, \nameref{fig:regionPloidAntag}, and \nameref{fig:SexAntagTighterMaleDrive}).
-The conditions become more restrictive, however, with increasing recombination ($R$) between the new sex determining region and the selected locus.  
+Counterintuitively, selection on loci within the non-recombining region around the sex-determining locus can favour the invasion of a less closely linked neo-W, whatever the form of selection maintaining a polymorphism (sexually-antagonistic selection, overdominance, ploidally-antagonistic selection, or some combination, Fig \ref{fig:SexAntagTighter}, \nameref{fig:temporalOverdominance}, \nameref{fig:regionPloidAntag}, and \nameref{fig:SexAntagTighterMaleDrive}).
+The conditions become more restrictive, however, with increasing recombination ($R$) between the new sex-determining locus and the selected locus.  
 The invasion of completely unlinked neo-W alleles ($R = 1/2$) can occur with overdominance in males or with haploid selection but is not possible with only sexually-antagonistic selection if selection is directional in each diploid sex (see \nameref{file:Mathematica}).
-To develop an intuition for how less closely linked neo-W alleles invade ($R>r$), we first focus on cases where there is no haploid selection and discuss the additional effect of haploid selection in \nameref{app:inv_cond}.
+To develop an intuition for how less closely linked neo-W alleles invade ($R>r$), we here focus on cases where there is no haploid selection and discuss the additional effect of haploid selection in \nameref{app:inv_cond}.
 
@@
 \caption{
-{\bf Transitions between XY and ZW systems can occur even when the neo-SDR is less tightly linked to a locus under sexually-antagonistic selection (here, without haploid selection).}
-In panel A, linkage is loose enough relative to selection that the analytical results assuming weak selection hold, and a neo-W can only invade when it is more tightly linked with the selected locus ($R<r$; shaded region).
-In panel B, linkage is tight enough relative to selection that the analytical results assuming weak selection do not hold, and a neo-W can invade even when it is less tightly linked with the selected locus ($r<R$; unshaded region marked by \text{*}).
-In panel C we vary the recombination rate between the neo-W and the selected locus ($R$) for a fixed recombination rate between the ancestral-SDR and the selected locus ($r=0.005$). 
+{\bf Transitions between XY and ZW systems can occur even when the new sex-determining locus is less tightly linked to a locus under sexually-antagonistic selection (even without haploid selection).}
+In panel A, linkage is loose enough relative to selection that the analytical results assuming weak selection hold, and a neo-W allele can only invade when it arises at a locus more tightly linked with the selected locus ($R<r$; shaded region).
+In panel B, linkage is tight enough relative to selection that the analytical results assuming weak selection do not hold, and a neo-W can invade even when it is less tightly linked with the selected locus ($r<R$; unshaded region around \text{*}).
+In panel C we vary the recombination rate between the neo-W and the selected locus ($R$) for a fixed recombination rate between the ancestral sex-determining locus and the selected locus ($r=0.005$). 
 Coloured markers show recombination rates for which the temporal dynamics of invasion are plotted in the inset, demonstrating that neo-W alleles can reach pseudo-fixation if they are more (black) or less (red) closely linked to a locus experiencing sexually-antagonistic selection.
-A very loosely linked neo-W does not spread in this case (blue and green lines overlap and go to 0). 
+A very loosely linked neo-W does not spread in this case (blue and green lines overlap and go to 0 in inset). 
 Fitness parameters are: $w_{AA}^\female = 1.05$, $w_{aa}^\male = 1.2$, $w_{aa}^\female = w_{AA}^\male = 0.85$, $w_{Aa}^\Hermaphrodite = 1$,  $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
@@
 
-If we categorise the $a$ allele as being ancestrally `male-beneficial' via the fact that it is fixed on the Y, then $\Lambda_{W'A}^{(XY)}>1$ indicates that the neo-W spreads when found with the ancestrally `female-beneficial' allele.
-Broadly, this is possible because the ancestral X chromosome is sometimes found in males and is therefore unable to perfectly specialise on the `female-beneficial' allele. 
-For example, when the $a$ allele is favoured on the ancestral X in males, a polymorphism of $A$ and $a$ alleles can be maintained on the X despite selection for the $A$ allele in females ($s^\female>0$, $0<h^\female<1$), see outlined region in Fig \ref{fig:regionplots}A.
-When the $a$ allele is strongly favoured on X chromosomes in males ($w_{aa}^\male$ sufficiently large relative to $w_{Aa}^\male$), neo-W-$A$ haplotypes can spread ($\Lambda_{W'A}^{(XY)}>1$, see grey region in Fig \ref{fig:regionplots}A) because they produce hgher fitness females ($AA$ or $Aa$ genotypes) and are unleashed from counterselection in males.
+If we categorise the $a$ allele as being ancestrally `male-beneficial' via the fact that it is fixed on Y backgrounds, then $\Lambda_{W'A}^{(XY)}>1$ indicates that the neo-W spreads when found with the ancestrally `female-beneficial' allele.
+Broadly, this is possible because ancestral X alleles are sometimes in males and are therefore unable to perfectly specialise on the `female-beneficial' allele. 
+For example, when the $a$ allele is favoured on ancestral X backgrounds in males, a polymorphism of $A$ and $a$ alleles can be maintained on the X background despite selection for the $A$ allele in females ($s^\female>0$, $0<h^\female<1$), see outlined region in Fig \ref{fig:regionplots}A.
+When the $a$ allele is strongly favoured on the X background in males ($w_{aa}^\male$ sufficiently large relative to $w_{Aa}^\male$), neo-W-$A$ haplotypes can spread ($\Lambda_{W'A}^{(XY)}>1$, see grey region in Fig \ref{fig:regionplots}A) because they produce higher fitness females ($AA$ or $Aa$ genotypes) and are unleashed from counterselection in males.
 
@@
 \caption{
-{\bf When the ancestral-XY locus is tightly linked to a locus under selection ($r=0$), one or both neo-W haplotypes can spread. }
-We vary the fitness of male homozygotes relative to heterozygotes ($w_{Aa}^\Hermaphrodite=1$) and only consider stable equilibria at which both \textbf{A} locus alleles are maintained and the $a$ allele is initially fixed on the Y, region outlined.
+{\bf When the ancestral XY locus is tightly linked to a locus under selection ($r=0$), one or both neo-W haplotypes can spread. }
+We vary the fitness of male homozygotes relative to heterozygotes ($w_{Aa}^\Hermaphrodite=1$) and only consider stable equilibria at which both $\mathbf{A}$ locus alleles are maintained and the $a$ allele is initially fixed on Y backgrounds, region outlined.
 Here, selection in females can favour the $A$ allele (panel A, $w_{aa}^\female=0.85$, $w_{AA}^\female=1.05$), favour the $a$ allele (panel B, $w_{aa}^\female=1.05$, $w_{AA}^\female=0.85$), or be overdominant (panel C, $w_{aa}^\female=w_{AA}^\female=0.6$).
-If $\Lambda_{W'A}^{(XY)}$ or $\Lambda_{W'a}^{(XY)}$ is greater than one, then a rare neo-W can spread for, at least, some values of $R>r$. 
+If either haplotypic growth rate ($\Lambda_{W'A}^{(XY)}$ or $\Lambda_{W'a}^{(XY)}$) is greater than one, then a rare neo-W allele can spread for, at least, some values of $R>r$. 
 The parameter values marked with an asterisk correspond to the fitnesses used in Fig \ref{fig:SexAntagTighter}C. 
-Where both $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$ are greater than one, a neo-W will spread when rare, regardless of linkage with the selected locus (for any $R$). 
-\nameref{fig:positionOverdominance} shows the dynamics using the parameters marked with a dagger. 
+Where both haplotypic growth rates are greater than one, a neo-W will spread when rare, regardless of linkage with the selected locus (for any $R$). 
+\nameref{fig:positionOverdominance} shows the dynamics arising with the parameters marked with a dagger. 
 Here, there is no haploid selection $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
@@
 
-When only one neo-W haplotype has a positive growth rate (see Fig \ref{fig:regionplots}), a neo-W can invade as long as equation \eqref{eq:lambdasGen} is satisfied, which may require that the recombination rate, $R$, is small enough.
+When only one neo-W haplotype has growth rate greater than one (see Fig \ref{fig:regionplots}), a neo-W allele can invade as long as equation \eqref{eq:lambdasGen} is satisfied, which may require that the recombination rate, $R$, is small enough.
 Nevertheless, because we assume here that $r$ is small, these results indicate that a more loosely linked sex-determining region ($r<R$) can spread.
-For example, tightly sex-linked loci that experience sexually-antagonistic selection can drive trans-GSD transitions in which the neo-SDR is less closely linked to the locus under selection (Fig \ref{fig:SexAntagTighter}).
-
-Given that the $a$ allele can be considered ancestrally `male-beneficial' because it is fixed on the Y, it is surprising that neo-W-$a$ haplotypes can sometimes be favoured by selection in females ($\Lambda_{W'a}^{(XY)}>1$).
-Again, this occurs because ancestral X's also experience selection in males, in which they will always be paired with a Y-$a$. 
-If there is overdominance in males, X-$A$ Y-$a$ males have high fitness and the $A$ allele is favoured by selection on the X in males. 
-Therefore, the X can be polymorphic or even fixed for the $A$ allele despite favouring the $a$ allele during selection in females (e.g., see outlined region in Fig \ref{fig:regionplots}B and~\cite{Lloyd1977,Otto2014}).
-In such cases, neo-W-$a$ haplotypes can spread because they create more $Aa$ and $aa$ females when pairing with an X from males and because they bring Y-$a$ haplotypes into females, where it has higher fitness (Fig \ref{fig:model_outline}D).
+For example, tightly sex-linked loci that experience sexually-antagonistic selection can drive trans-GSD transitions in which the new sex-determining locus is less closely linked to the locus under selection (Fig \ref{fig:SexAntagTighter}).
+
+Given that the $a$ allele can be considered ancestrally `male-beneficial' because it is fixed on Y backgrounds, it is surprising that neo-W-$a$ haplotypes can sometimes be favoured by selection in females ($\Lambda_{W'a}^{(XY)}>1$).
+Again, this occurs because ancestral X alleles also experience selection in males, where they are ancestrally always paired with a Y-$a$ gamete. 
+If there is overdominance in males, X-$A$ Y-$a$ males have high fitness and the $A$ allele is favoured by selection on the X background in males. 
+Therefore, the $A$ allele can be polymorphic or even fixed on the X background despite selection favouring the $a$ allele in females (e.g., see outlined region in Fig \ref{fig:regionplots}B and~\cite{Lloyd1977,Otto2014}).
+In such cases, neo-W-$a$ haplotypes can spread because they create more $Aa$ and $aa$ females when pairing with an X-bearing gamete from males and because they bring Y-$a$ haplotypes into females, where it has higher fitness (Fig \ref{fig:model_outline}D).
 
 In some cases, both W-$A$ and W-$a$ haplotypes can spread.
-For example, when $AA$ individuals have low fitness in females yet the $A$ is polymorphic or fixed on the X due to overdominance in males (Fig \ref{fig:regionplots}B and \ref{fig:regionplots}C), both neo-W-$A$ and neo-W-$a$ haplotypes produce fewer unfit $AA$ females.
+For example, when $AA$ individuals have low fitness in females yet the $A$ is polymorphic or fixed on the X background due to overdominance in males (Fig \ref{fig:regionplots}B and \ref{fig:regionplots}C), both neo-W-$A$ and neo-W-$a$ haplotypes produce fewer unfit $AA$ females.
 This is true for the neo-W-$A$ haplotype because it can pair with a Y-$a$ haplotype and still be female. 
-Wherever both haplotypes have positive growth rates, invasion by a neo-W is expected regardless of its linkage with the selected locus (i.e., for any $R$, see \nameref{fig:positionOverdominance} and \nameref{fig:temporalOverdominance} for examples).
-
-Assuming selection is weak relative to recombination, van Doorn and Kirkpatrick~\cite{vanDoorn:2010hu} showed that invasion by a neo-W occurs under the same conditions as `pseudo-fixation' (at pseudo-fixation the neo-W reaches its maximum frequency among eggs, which is usually 1/2).
+Wherever both haplotypic growth rates are greater than one, invasion by a neo-W is expected regardless of its linkage with the selected locus (i.e., for any $R$, see \nameref{fig:positionOverdominance} and \nameref{fig:temporalOverdominance} for examples).
+
+Assuming selection is weak relative to recombination, van Doorn and Kirkpatrick~\cite{vanDoorn:2010hu} showed that invasion by a neo-W allele occurs under the same conditions as `pseudo-fixation' (at pseudo-fixation the neo-W reaches its maximum frequency among eggs, which is usually 1/2, but can deviate from 1/2 when there is haploid selection before censusing).
 An equivalent analysis is not possible where recombination rates are low. 
-However, numerical simulations demonstrate that the neo-SDR does not necessarily reach pseudo-fixation, which can lead to the stable maintenance of a mixed sex-determining system, in which X, Y, Z, and W alleles all segregate (e.g., \nameref{fig:freqAll}B,C).
+However, numerical simulations demonstrate that new sex-determining alleles do not necessarily reach pseudo-fixation, which can lead to the stable maintenance of a mixed sex-determining system, in which X, Y, Z, and W alleles all segregate (e.g., \nameref{fig:freqAll}B,C).
 
@@
 
-The neo-sex-determining allele, $m$, will spread in an XY system if $\lambda_{m}^{(XY)}>1$. 
-Equation \eqref{eq:lambda_neoY} demonstrates that, under weak selection, a neo-Y will invade an XY system if and only if it is more closely linked to the selected locus than the ancestral sex-determining region (i.e., if $R<r$; note that $V_{A}S_{A}^2$ is strictly positive as long as \textbf{A} is polymorphic).
+%The new sex-determining allele, $m$, will spread in an XY system if $\lambda_{m}^{(XY)}>1$. 
+Equation \eqref{eq:lambda_neoY} demonstrates that, under weak selection, a neo-Y allele will invade an XY system ($\lambda_{Y'}^{(XY)}>1$) if and only if it is more closely linked to the selected locus than the ancestral sex-determining locus (i.e., if $R<r$; note that $V_{A}S_{A}^2$ is strictly positive as long as $\mathbf{A}$ is polymorphic).
 This echoes our results above where a neo-Y could never invade if $r\approx0$. 
-It is also consistent with the results of \cite{vanDoorn:2007eu}, who considered diploid selection only and also found that cis-GSD transitions (XY to XY or ZW to ZW) can only occur when the neo-sex-determining locus is more closely linked to a locus under sexually-antagonistic selection.
+It is also consistent with the results of \cite{vanDoorn:2007eu}, who considered diploid selection only and also found that cis-GSD transitions can only occur when the new sex-determining locus is more closely linked to a locus under sexually-antagonistic selection.
 %Because tighter linkage between the sex-determining region and a selected locus evolves during these transitions, stronger associations between selected alleles and diploid sexes can build up by selection (e.g., between male-beneficial alleles and the male-determining allele, Y).%, increasing diploid mean fitness (Fig \ref{fig:Combination_MeanFit}).
 
-With weak selection and no haploid selection ($t^\Hermaphrodite=\alpha^\Hermaphrodite_{\Delta}=0$), the spread of a neo-W is equivalent to the spread of a neo-Y ($\lambda_{W'}^{(XY)}=\lambda_{Y'}^{(XY)}$), such that trans-GSD transitions (XY to ZW or ZW to XY) can also occur only if the neo-sex-determining region is more closely linked to a locus under selection ($R<r$), as found by \cite{vanDoorn:2010hu}.
+With weak selection and no haploid selection ($t^\Hermaphrodite=\alpha^\Hermaphrodite_{\Delta}=0$), the spread of a neo-W is equivalent to the spread of a neo-Y ($\lambda_{W'}^{(XY)}=\lambda_{Y'}^{(XY)}$), such that trans-GSD transitions can also occur only if the new sex-determining locus is more closely linked to a locus under selection ($R<r$), as found by \cite{vanDoorn:2010hu}.
 When there is haploid selection, invasion also typically occurs when the neo-W is more closely linked to the selected locus than the ancestral sex-determining region (Fig \ref{fig:Combination_Centimorgans}).
-For example, if the \textbf{A} locus is unlinked to the ancestral sex-determining region ($r=1/2$), a more closely linked neo-W ($R<1/2$) can always invade.
-In this case, there is no ancestral association between \textbf{A} alleles and sex chromosomes in males, $\left( \hat{p}^\male_Y-\hat{p}^\male_X \right)=0$, see equation \eqref{eq:freq_diffs}. 
+For example, if the $\mathbf{A}$ locus is unlinked to the ancestral sex-determining locus ($r=1/2$), a more closely linked neo-W ($R<1/2$) can always invade.
+In this case, there is no ancestral association between $\mathbf{A}$ alleles and sex chromosomes in males, $\left( \hat{p}^\male_Y-\hat{p}^\male_X \right)=0$, see equation \eqref{eq:freq_diffs}. 
 The second term in equation \eqref{eq:lambda_neoW} therefore disappears and invasion depends only on the sign of $(r-R)$.%, as in the case of the neo-Y.
@@
 \caption{
-{\bf Ploidally-antagonistic selection allows a less tightly linked neo-W to invade.}
-In panel A, male drive ($\alpha^\male_{\Delta} = -1/20$, $t^\Hermaphrodite = \alpha^\female_{\Delta} = 0$) opposes selection in diploids (no sex-differences: $s^\Hermaphrodite = 1/10$, $h^\Hermaphrodite = 7/10$), in which case the neo-sex-determining allele can invade regardless of $R$.
-In panel B, gametic competition in males ($t^\male = -1/10$, $t^\female = \alpha^\Hermaphrodite_{\Delta} = 0$) opposes selection in diploids (sex-differences: $s^\male = 3/20$, $s^\female = 1/20$, $h^\Hermaphrodite = 7/10$), in which case the neo-sex-determining allele can once again invade regardless of $R$.
+{\bf Ploidally-antagonistic selection allows a less tightly linked neo-W allele to invade.}
+In panel A, male drive ($\alpha^\male_{\Delta} = -1/20$, $t^\Hermaphrodite = \alpha^\female_{\Delta} = 0$) opposes selection in diploids (no sex-differences: $s^\Hermaphrodite = 1/10$, $h^\Hermaphrodite = 7/10$), in which case the new sex-determining allele can invade regardless of its linkage with the selected locus ($R$).
+In panel B, gametic competition in males ($t^\male = -1/10$, $t^\female = \alpha^\Hermaphrodite_{\Delta} = 0$) opposes selection in diploids (sex-differences: $s^\male = 3/20$, $s^\female = 1/20$, $h^\Hermaphrodite = 7/10$), in which case the new sex-determining allele can once again invade regardless of $R$.
 }
@@
 However, with haploid selection and $r<1/2$, the additional term in equation \eqref{eq:lambda_neoW} can be positive.
-This can allow neo-W invasion ($\lambda_{W'}^{(XY)}>1$), even when the neo-sex-determining region is less closely linked to the selected locus ($R>r$). 
+This can allow neo-W invasion ($\lambda_{W'}^{(XY)}>1$), even when the new sex-determining locus is less closely linked to the selected locus ($R>r$). 
 %These transitions are unusual because, when $R>r$, associations that selection has built up between alleles more favourable in one sex and alleles that determine sex will be weakened. 
@@
 %To clarify the parameter space under which $\lambda_{W'}^{(XY)}>1$ , we consider several special cases. 
-%Firstly, if the \textbf{A} locus is unlinked to the ancestral sex-determining region ($r=1/2$), a more closely linked neo-W ($R<1/2$) can always invade because there is no ancestral association between $A$ alleles and sex chromosomes in males, $\left( \hat{p}^\male_Y-\hat{p}^\male_X \right)=0$, see equation \eqref{eq:freq_diffs}.
+%Firstly, if the $\mathbf{A}$ locus is unlinked to the ancestral sex-determining region ($r=1/2$), a more closely linked neo-W ($R<1/2$) can always invade because there is no ancestral association between $A$ alleles and sex chromosomes in males, $\left( \hat{p}^\male_Y-\hat{p}^\male_X \right)=0$, see equation \eqref{eq:freq_diffs}.
 %The second term in equation \eqref{eq:lambda_neoW} therefore disappears and invasion depends only on the sign of $(r-R)$, as in the case of the neo-Y. 
@@
 \smallskip
-\caption{Invasion conditions for unlinked neo-W ($R=1/2$, $r<1/2$) into ancestral XY with one form of haploid selection}
+\caption{Invasion conditions for a neo-W allele at an unlinked locus ($R=1/2$) into an ancestral XY system with linkage ($r<1/2$) and one form of haploid selection}
 \begin{tabular}{l l c }
@@
 In this figure, selection is ploidally antagonistic with haploid selection favouring the $a$ allele during male meiosis.
-In panel A, male meiotic drive in an ancestral XY system causes a male bias (see Fig \ref{fig:model_outline}B), allowing a neo-W to invade and replace the ancestral sex-determination system (inset shows neo-W frequency among female gametes, reaching pseudo-fixation), which balances the zygotic sex ratio.
-In panel B, male drive in an ancestral ZW system has no effect on the zygotic sex ratio yet a neo-Y can invade and replace the ancestral sex-determination system (inset shows neo-Y frequency among male gametes, reaching pseudo-fixation).
+In panel A, male meiotic drive in an ancestral XY system causes a male bias (see Fig \ref{fig:model_outline}B), allowing a neo-W to invade and replace the ancestral sex-determining system (inset shows neo-W frequency among female gametes, reaching pseudo-fixation), which balances the zygotic sex ratio.
+In panel B, male drive in an ancestral ZW system has no effect on the zygotic sex ratio yet a neo-Y can invade and replace the ancestral sex-determining system (inset shows neo-Y frequency among male gametes, reaching pseudo-fixation).
 %When $R<1/2$, the neo-Y becomes associated with the allele favoured by drive, causing the zygotic sex ratio to become biased, hence the frequency of the neo-Y at pseudo-fixation can be higher than $0.5$ (inset).
@@
 
-Previous research suggests that when the ancestral sex-determining locus is linked to a locus that experiences haploid selection (e.g., meiotic drive), a new, unlinked sex-determining locus invades in order to restore equal sex ratios~\cite{Kozielska:2010vm}.
-Consider, for example, the case where the \textbf{A} locus is linked to the ancestral-SDR ($r<1/2$) and experiences meiotic drive in males only ($\alpha^\male_\Delta \neq 0$, $\alpha^\female_\Delta=0$), without gametic competition ($t^\female=t^\male=0$).
+Previous research suggests that when the ancestral sex-determining locus is linked to a locus that experiences haploid selection (e.g., meiotic drive), alleles at a new, unlinked sex-determining locus invade to restore equal sex ratios~\cite{Kozielska:2010vm}.
+Consider, for example, the case where the $\mathbf{A}$ locus is linked to the ancestral sex-determining locus ($r<1/2$) and experiences meiotic drive in males only ($\alpha^\male_\Delta \neq 0$, $\alpha^\female_\Delta=0$), without gametic competition ($t^\female=t^\male=0$).
 In this case, the zygotic sex ratio can be initially biased only if the ancestral sex-determining system is XY (Fig \ref{fig:model_outline}A and Fig \ref{fig:SexRatioBad}B). 
 %If the ancxestral sex-determining system is ZW, the zygotic sex ratio will be 1:1 because diploid sex is determined by the proportion of Z-bearing versus W-bearing eggs and meiosis in females is fair (Fig \ref{fig:Combination_Turnover}D).
-If Fisherian sex ratio selection were dominant, we would expect a difference in the potential for XY to ZW and ZW to XY transitions. 
+If Fisherian sex ratio selection were dominant, we would thus expect a difference in the potential for XY to ZW and ZW to XY transitions. 
 %However, to leading order with selection weak relative to recombination, we find that sex ratio selection favours the spread of a neo-W by an amount equl to the spread of a neo-Y into a ZW system (relabeling XY as the heterogametic sex and reversing the labels of males and females in Table \ref{tab:specialcases})
 %However, to leading order with selection weak relative to recombination, we find that sex ratio selection favours the spread of a neo-W (through the first terms in table \ref{tab:haplotype_growth}) by an amount that is equal in magnitude to the fitness effects of alleles associated with new sex-determining alleles (second terms in table \ref{tab:haplotype_growth}).
-However, invasion by a neo-W into an XY system and invasion by a neo-Y into a ZW system occur under the same conditions ($\lambda_{Y'}^{(XY)} = \lambda_{W'}^{(XY)}$ and $\lambda_{Y'}^{(XY)}=\lambda_{W'}^{(XY)}$, at least to order $\epsilon^2$).
-For example, in Fig \ref{fig:SexRatioBad}A neo-W alleles invade an ancestral-XY system where females are initially rare.
-However, Fig \ref{fig:SexRatioBad}B shows that a neo-Y can invade an ancestral-ZW system under the same conditions. 
-Whenever $R<1/2$, the neo-Y becomes associated with the male meiotic drive allele such that the zygotic sex ratio actually evolves to become biased towards males.
-
+However, invasion by a neo-W allele into an XY system and invasion by a neo-Y allele into a ZW system occur under the same conditions ($\lambda_{Y'}^{(XY)} = \lambda_{W'}^{(XY)}$ and $\lambda_{Y'}^{(XY)}=\lambda_{W'}^{(XY)}$, at least to order $\epsilon^2$).
+For example, in Fig \ref{fig:SexRatioBad}A neo-W alleles invade an ancestral-XY system where females are initially rare, equalizing the sex ratio.
+However, Fig \ref{fig:SexRatioBad}B shows that a neo-Y can invade the resulting ZW system under the same conditions. 
+When $R<1/2$, the invading neo-Y becomes associated with the male meiotic drive allele and the zygotic sex ratio actually evolves to become male-biased.
+%
 %As selection becomes stronger (or linkage becomes tighter), this symmetry between sex ratio selection and haploid selection is lost, causing differences in the strength of selection favouring the two heterogametic transitions (compare red to black near -25cM and 25 cM in Fig \ref{fig:Combination_Centimorgans}).
 \textcolor{red}{normalise fitness in sexually antagonistic case}
-
-Why can new sex-determining regions invade when they are more loosely linked to selected loci ($R>r$)?  
-Consider first the case where both sex-determining-loci are linked to the selected locus ($r<R<1/2$). 
-In an ancestral-XY system, haploid selection in males can facilitate the spread of a neo-W because the zygotic sex ratio is ancestrally male biased and the W produces more of the rarer sex (Fig \ref{fig:SexRatioBad}A).
-A new sex determining region can also, however, benefit from becoming more associated with drive. 
-For example in anancestral-ZW system with the same selection regime (haploid selection in males), a neo-Y can spread despite the fact that the zygotic sex is initially even; in this case, the neo-Y spreads because it is often found in males and can, if it carries the driven allele $a$, benefit from haploid selection in males (Fig \ref{fig:SexRatioBad}B).
-While equalizing the sex ratio and benefiting from drive are two primary reasons why haploid selection spurs sex chromosome transitions, more complex situations also arise.  
-For example with $R=1/2$ in Fig \ref{fig:SexRatioBad}B (green curve), the neo-Y spreads despite the fact that it cannot benefit from drive because free recombination moves it randomly between driven and non-driven backgrounds.
+%
+%Why can new sex-determining regions invade when they are more loosely linked to selected loci ($R>r$)?  
+%Consider first the case where both sex-determining-loci are linked to the selected locus ($r<R<1/2$). 
+%In an ancestral-XY system, haploid selection in males can facilitate the spread of a neo-W because the zygotic sex ratio is ancestrally male biased and the W produces more of the rarer sex (Fig \ref{fig:SexRatioBad}A).
+%A new sex determining region can also, however, benefit from becoming more associated with drive. 
+%For example in an ancestral-ZW system with the same selection regime (haploid selection in males), a neo-Y can spread despite the fact that the zygotic sex is initially even; in this case, the neo-Y spreads because it is often found in males and can, if it carries the driven allele $a$, benefit from haploid selection in males (Fig \ref{fig:SexRatioBad}B).
+
+While equalizing the sex ratio and benefiting from drive are two primary reasons why haploid selection spurs sex chromosome transitions, even when the new sex-determining allele is less closely linked to the selected locus ($r<R$), more complex situations also arise.
+For example with $R=1/2$ in Fig \ref{fig:SexRatioBad}B (green curve), the neo-Y allele spreads despite the fact that it cannot benefit from drive because free recombination moves it randomly between driven and non-driven backgrounds.
 Nevertheless, the unlinked neo-Y can spread because diploids bearing it more often carry the non-driven allele $A$, which is found at high frequency on the W background and has higher average diploid fitness.% to balance the haploid advantage of the $a$ allele at equilibrium.
@@
 Here, we do not assume that the environmental conditions that determine sex also differentially affect the fitness of males versus females. 
-Such correlations can favour environmental sex-determination systems that allow each sex to be produced in the environment in which it has highest fitness; in the absence of these correlations, previous theory would predict that ESD is favoured when it produces more equal sex ratios than the ancestral system (see reviews by~\cite{Charnov:1982wg,Bull:1983vi,West:2009we}).
+Such correlations can favour environmental sex-determining systems that allow each sex to be produced in the environment in which it has highest fitness; in the absence of these correlations, previous theory would predict that ESD is favoured when it produces more equal sex ratios than the ancestral system (see reviews by~\cite{Charnov:1982wg,Bull:1983vi,West:2009we}).
 %(e.g., maternal condition, mate quality, age, or host size)
 
-The characteristic polynomial determining the eigenvalues (equations \ref{eq:recursions}) does not factor for ESD mutants as it does for $k=0$ or $k=1$. 
-We therefore focus on weak selection here. 
-Assuming weak selection, the spread of the new sex-determining region is given by
+The characteristic polynomial determining the leading eigenvalue (equations \ref{eq:recursions}) does not factor for ESD ($0<k<1$) as it does for a neo-Y ($k=0$) or neo-W ($k=1$) allele. 
+We therefore focus on weak selection here, where the leading eigenvalue is
 
@@
 \lambda_{ESD'}^{(XY)} =& 1 + \frac{{(1-2k)}^2}{4}V_{A}{S_{A}}^2\frac{r-R}{r R} \\
-&+\frac{k(\hat{p}^\male_Y-\hat{p}^\male_X)}{2}\left[ k \left(2\alpha_{\Delta}^\male-2\alpha_{\Delta}^\female+t^\male-t^\female \right) -2(1-k)S_{A}\right]+O\left(\epsilon^3\right),
+&+\frac{k(\hat{p}^\male_Y-\hat{p}^\male_X)}{2}\left[ k \left(2\alpha_{\Delta}^\male-2\alpha_{\Delta}^\female+t^\male-t^\female \right) -2(1-k)S_{A}\right]+O\left(\epsilon^3\right).
 \end{split}
@@
 \noindent
-which reduces to $\lambda_{Y'}^{(XY)}$ when $k=0$ and $\lambda_{W'}^{(XY)}$ when $k=1$.
+This reduces to $\lambda_{Y'}^{(XY)}$ when $k=0$ and $\lambda_{W'}^{(XY)}$ when $k=1$.
 
@@
 %However, assuming weak selection, we find that the growth rate of a rare, dominant offspring-controlled neo-ESD allele that produces males or females with equal probability ($k=1/2$) is
-Of particular interest are ESD mutations that cause half of their carriers to develop as females and half as males ($k=1/2$, creating equal sex ratios), the spread of which is given by
+Of particular interest are ESD mutations that cause half of their carriers to develop as females and half as males ($k=1/2$), creating equal sex ratios.
+The spread of such ESD is determined by
 \begin{equation}
@@
 where $\lambda_{Y'\rvert R=1/2}^{(XY)}$ and $\lambda_{W'\rvert R=1/2}^{(XY)}$ represent $\lambda_{Y'}^{(XY)}$ and $\lambda_{W'}^{(XY)}$ when evaluated at $R=1/2$ (Equations \ref{eq:lambda_neoY} and \ref{eq:lambda_neoW}).
-That is, recombination between the selected locus and the novel sex-determining locus, $R$, doesn't enter into the $k=1/2$ results.
-This is because sex is essentially randomized each generation, %as if the novel sex-determiner were on an unlinked site that half the time acts as a neo-$W$ and half the time as a neo-$Y$.
-preventing associations from building up between allele $A$ and sex. 
-Equation \eqref{eq:lambda_ESD} shows that the neo-ESD gets half of the fitness of a feminizing mutation (neo-$W$) and half of the fitness of a masculinizing mutation (neo-$Y$), but only has an effect one half of the time (the other half of the time it produces the same sex as the ancestral system would have).
+That is, recombination between the selected locus and the novel sex-determining locus, $R$, does not enter into the $k=1/2$ results.
+This is because sex is essentially randomized each generation, %as if the novel sex-determiner were on an unlinked site that half the time acts as a neo-W and half the time as a neo-Y.
+preventing associations from building up between alleles at locus $\mathbf{A}$ and sex. 
+Equation \eqref{eq:lambda_ESD} shows that the ESD mutation gets half of the fitness of a feminizing mutation (neo-W) and half of the fitness of a masculinizing mutation (neo-Y), but only has an effect one half of the time (the other half of the time it produces the same sex as the ancestral system would have).
 As discussed above, $\lambda_{Y'\rvert R=1/2}^{(XY)}$ is necessarily less than one, but $\lambda_{W'\rvert R=1/2}^{(XY)}$ can be greater than one if there is haploid selection.
-That is, when there is haploid selection, ESD mutations can invade an ancestrally-XY system because they generate females that are either rare or have high fitness, in the same manner as a neo-W.
+That is, when there is haploid selection, ESD can invade an ancestrally-XY system because it generates females that are either rare or have high fitness, in the same manner as a neo-W.
 
@@
 Significantly, equation \eqref{eq:lambda_ESD} is the same whether ESD is invading an ancestrally XY or ZW system (because $\lambda_{Y'}^{(XY)} = \lambda_{W'}^{(ZW)}$ and $\lambda_{W'}^{(XY)} = \lambda_{Y'}^{(ZW)}$).
-Thus, Fisherian sex ratio selection alone does not easily explain the invasion of ESD.
-For example, when the ancestral sex-determination system is XY, but not ZW, the sex ratio is biased by male haploid selection.
-Nevertheless, ESD is equally likely to invade when it equalizes the zygotic sex ratio (through $\lambda_{W'}^{(XY)}$) and when it doesn't (through $\lambda_{Y'}^{(ZW)}$). 
+Thus, Fisherian sex ratio selection alone does not easily explain GSD to ESD transitions.
+For example, when the ancestral sex-determining system is XY, but not ZW, the sex ratio is biased by male haploid selection.
+Nevertheless, ESD is equally likely to invade when it equalizes the zygotic sex ratio (through $\lambda_{W'}^{(XY)}$) as when it doesn't (through $\lambda_{Y'}^{(ZW)}$). 
 %This is again because haploid selection can facilitate the turnover of sex chromosomes either through sex ratio biases or through associations between the new sex determining region with selected alleles.
@@
 In addition, we note that ESD may not invade, even if the sex ratio is initially biased (e.g., with drive in males only, $r<1/2$, $h^\female=h^\male$, and $s^\female s^\male<0$, then $\lambda_{W'}^{(XY)}<1$, see Table \ref{tab:specialcases}).
-We conclude that, as with neo-W and neo-Y loci, associations with selected loci mean that the evolution of neo-ESD systems is not straightforwardly predicted by selection to balance the zygotic sex ratio when haploid selection is present.
+We conclude that, as with neo-W and neo-Y loci, associations with selected loci mean that the evolution of ESD is not straightforwardly predicted by selection to balance the zygotic sex ratio when haploid selection is present.
 
@@
 %MAIN RESULT
-Two predominant theories explaining the remarkably high frequency of transitions between sex-determination systems are sexually-antagonistic selection and sex ratio selection (reviewed in~\cite{Blaser2012, vanDoorn2014re}).
-The former predicts that neo-sex-determining alleles can invade when they arise in closer linkage with a sexually-antagonistic locus ($r<R$,~\cite{vanDoorn:2007eu,vanDoorn:2010hu, Muralidhar2018}).
+Two predominant theories explaining the remarkably high frequency of transitions between sex-determining systems are sexually-antagonistic selection and sex ratio selection (reviewed in~\cite{Blaser2012, vanDoorn2014re}).
+The former predicts that new sex-determining alleles can invade when they arise in closer linkage with a sexually-antagonistic locus ($r<R$,~\cite{vanDoorn:2007eu,vanDoorn:2010hu, Muralidhar2018}).
 The latter predicts that new sex-determining systems are generally favoured if they result in more equal sex ratios than the ancestral system. 
 %The latter predicts that neo-W alleles will invade an XY system when there is a male bias caused by haploid selection in males, and vice-versa, a neo-Y will invade a ZW system when there is a female bias caused by haploid selection in females~\cite{Kozielska:2010vm,Ubeda:2015fx}.
-In contrast to these prevailing views, we show that selection (including sexually-antagonistic selection, overdominance, and/or ploidally-antagonistic selection) on loci tightly linked to the ancestral sex-determining region can favour trans-GSD transitions (XY to ZW or ZW to XY) to new sex-determining systems that are less closely linked to the selected loci (e.g., see Fig \ref{fig:SexAntagTighter}).
+In contrast to these prevailing views, we show that selection (including sexually-antagonistic selection, overdominance, and/or ploidally-antagonistic selection) on loci tightly linked to the ancestral sex-determining locus can favour trans-GSD transitions (XY$\leftrightarrow$ ZW) to new sex-determining systems that are less closely linked to the selected loci (e.g., see Fig \ref{fig:SexAntagTighter}).
 Similarly, even when linkage is weak relative to selection, we show that %new sex-determining alleles are typically favoured if they are more closely linked to a locus under haploid selection (even in the absence of diploid sex differences), which is the only condition favouring cis-GSD transitions (XY to XY or ZW to ZW).
 %In addition, with haploid selection and weak selection, 
-trans-GSD transitions (XY to ZW or ZW to XY) can occur where the new sex-determining region is less closely linked to the locus under selection if there is haploid selection (e.g., Figs \ref{fig:Combination_Centimorgans} and \ref{fig:SexRatioBad}).
-
-We find that the spread of neo-sex-determining systems cannot be simply predicted from their effect on the sex ratio. 
-On one hand, sex ratio biases caused by haploid selection can facilitate trans-GSD transitions or GSD-ESD transitions between sex-determining systems. 
-For instance, alleles favoured by haploid selection in males often become associated with the Y, which leads to a male-biased zygotic sex ratio.
-This male bias increases the potential for a neo-W to invade (Table \ref{tab:haplotype_growth}), which can equalize the sex ratio (e.g., see Fig \ref{fig:SexRatioBad}B, for related examples see~\cite{Kozielska:2010vm}).
+trans-GSD transitions can occur where the new sex-determining locus is less closely linked to the locus under selection if there is haploid selection (e.g., Figs \ref{fig:Combination_Centimorgans} and \ref{fig:SexRatioBad}).
+
+We find that the spread of new sex-determining systems cannot be simply predicted from their effect on the sex ratio. 
+On one hand, sex ratio biases caused by haploid selection can facilitate trans-GSD transitions or transitions from genetic to environmental sex determination. 
+For instance, alleles favoured by haploid selection in males often become associated with the Y allele, which leads to a male-biased zygotic sex ratio.
+This male bias increases the potential for a neo-W allele to invade (Table \ref{tab:haplotype_growth}), which can equalize the sex ratio (e.g., see Fig \ref{fig:SexRatioBad}B, for related examples see~\cite{Kozielska:2010vm}).
 %We find that sex ratio biases caused by haploid selection can also affect transitions between sex-determining systems (e.g., see $\zeta$ terms in Table \ref{tab:haplotype_growth}). 
@@
 %What we would like to stress is that sex ratio selection alone cannot predict when new sex-determining systems can evolve.
-Significantly, with weak selection, we find that there is no difference in conditions allowing XY to ZW and ZW to XY transitions, indicating that sex chromosome transitions are not predominantly predicted by their effect on the sex ratio (i.e., the sex ratio bias created by male haploid selection facilitates the spread of a neo-W into an XY system to the same degree that male haploid selection drives the spread of a neo-Y into a ZW system with a 1:1 sex ratio).
+Significantly, with weak selection, we find that there is no difference in conditions allowing XY to ZW and ZW to XY transitions, indicating that sex chromosome transitions are not predominantly predicted by their effect on the sex ratio (i.e., the sex ratio bias created by male haploid selection facilitates the spread of a neo-W allele into an XY system to the same degree that male haploid selection drives the spread of a neo-Y into a ZW system with a 1:1 sex ratio).
 %An asymmetry can develop when sex-linkage is tight (e.g., Fig \ref{fig:Combination_Centimorgans} near -25cM and 25cM) but under most circumstances we do not predict asymmetry between XY to ZW and ZW to XY transitions despite the presence/absence of sex ratio selection.
-Thus, haploid selection can favour trans-GSD transitions both via sex ratio selection and via selection on alleles associated with the neo-sex-determining allele, and these selective pressures are often predicted to be of equal magnitude.
+Thus, haploid selection can favour trans-GSD transitions both via sex ratio selection and via selection on alleles associated with the new sex-determining allele, and these selective pressures are often predicted to be of equal magnitude.
 
 %HAPLOID SELECTION (genomic location of haploid selected loci and comparative patterns) 
-We have shown that the spread of new sex determination systems can be driven by loci experiencing haploid selection. 
-%Our results suggest that haploid selected loci that have been involved in driving turnovers between sex-determination systems could occur around the ancestral- or novel-sex-determining regions. 
-%Our results suggest that polymorphic loci that are ancestrally sex-linked and under sex-specific selection could also drive heterogametic transitions between sex-determination systems. 
+We have shown that the spread of new sex-determining systems can be driven by loci experiencing haploid selection. 
+%Our results suggest that haploid selected loci that have been involved in driving turnovers between sex-determining systems could occur around the ancestral- or novel-sex-determining regions. 
+%Our results suggest that polymorphic loci that are ancestrally sex-linked and under sex-specific selection could also drive heterogametic transitions between sex-determining systems. 
 %As with sexually-antagonistic selection, the presence of haploid selected loci around ancestral- or novel-sex-determining regions could support their role in sex chromosome turnover.
@@
 %maybe add a flag here for switching to clade-level expectations:
-In general, we predict that haploid selection increases lability of sex-determination systems, particularly because haploid selection can cause transitions that increase or decrease sex-linkage (e.g., the final state of the red line in Fig \ref{fig:SexRatioBad}B is the starting state in Fig \ref{fig:SexRatioBad}A).
-Turnovers driven by haploid selection may help to explain the relative rarity of heteromorphic sex chromosomes in plants, which are thought to experience more selection during their multicellular haploid stage.
-If haploid selection is strong but selective differences between male and female diploids are weak, we find that trans-GSD transitions (XY to ZW or ZW to XY) are favoured more strongly than cis-GSD transitions, with transitions to ESD intermediate (e.g., with $|D^\male - D^\female| << |\alpha_\Delta^\male - \alpha_\Delta^\female + t^\male - t^\female|$ we have $\lambda_{W'}^{(XY)} > \lambda_{Y'}^{(XY)}$; Equations \ref{eq:lambda_neoW} and \ref{eq:freq_diffs}).
+In general, we predict that haploid selection increases lability of sex-determining systems, particularly because haploid selection can cause transitions that increase or decrease sex-linkage (e.g., the final state of the red line in Fig \ref{fig:SexRatioBad}B is the starting state in Fig \ref{fig:SexRatioBad}A).
+Frequent turnovers driven by haploid selection may help to explain the relative rarity of heteromorphic sex chromosomes in plants, which are thought to experience more selection during their multicellular haploid stage.
+
+If haploid selection is strong but selective differences between male and female diploids are weak, we find that trans-GSD transitions are favoured more strongly than cis-GSD transitions, with transitions to ESD intermediate (e.g., with $|D^\male - D^\female| << |\alpha_\Delta^\male - \alpha_\Delta^\female + t^\male - t^\female|$ we have $\lambda_{W'}^{(XY)} > \lambda_{Y'}^{(XY)}$; Equations \ref{eq:lambda_neoW} and \ref{eq:freq_diffs}).
 Among the relatively few dioecious clades in which multiple species have well characterized sex chromosomes~\cite{Ming:2011iy}, trans-GSD transitions have been inferred in \textit{Silene} subsection \textit{Otites}~\cite{Slancarova:2013dq} and in \textit{Salicaceae}~\cite{Pucholt2015,Pucholt2017}.
@@
 In support of their role in sex chromosome turnover, genes expected to be under sexually-antagonistic selection (e.g., those causing bright male colouration) have been found on recently derived sex chromosomes~\cite{Lindholm:2002dw,Tripathi:2009cw,Ser:2010iq}.
-Our results show, however, that tight ancestral-linkage of polymorphic loci can also drive trans-GSD transitions. 
+Our results show, however, that tight ancestral-linkage of polymorphic loci, maintained by sexually-antagonistic selection or otherwise, can also drive trans-GSD transitions. 
 In addition, we find that polymorphic sex determining systems (X, Y, W, and Z alleles all present) can be maintained when a selected locus is tightly linked to the ancestral sex-determining system (e.g., \nameref{fig:freqAll}B and \nameref{fig:freqAll}C), which is not possible with loose linkage~\cite{vanDoorn:2010hu}.
@@
 We note that we assume that sex-determining alleles do not experience direct selection except via their associations with sex and selected alleles.
-However, in some cases, there may be significant degeneration around the sex-limited allele (Y or W) in the ancestral sex-determining region because recessive deleterious mutations and/or deletions accumulate around the Y or W sex-determining regions~\cite{Rice:1996ke,Charlesworth:2000cc,Bachtrog:2006ed,Marais:2008hm}.
-During trans-GSD transitions (XY to ZW or ZW to XY), but not cis-GSD transitions (XY to XY or ZW to ZW), any recessive deleterious alleles linked to the Y or W are revealed to selection in YY or WW individuals~\cite{Bachtrog:2014bx}.
-This phenomenon was studied by van Doorn and Kirkpatrick (2010)~\cite{vanDoorn:2010hu}, who found that degeneration can prevent fixation of a neo-W or a neo-Y allele, leading to a mixed sex-determination system where the ancestral and new sex-determining loci are both segregating.
-However, they noted that very rare recombination events around the ancestral sex-determining region can allow these trans-GSD transitions to complete.  
+However, in some cases, there may be significant degeneration around the sex-limited allele (Y or W) in the ancestral sex-determining region because recessive deleterious mutations and/or deletions accumulate in this non-recombining regions~\cite{Rice:1996ke,Charlesworth:2000cc,Bachtrog:2006ed,Marais:2008hm}.
+During trans-GSD transitions, but not cis-GSD transitions, any recessive deleterious alleles linked to the Y or W are revealed to selection in YY or WW individuals~\cite{Bachtrog:2014bx}. 
+This phenomenon was studied by van Doorn and Kirkpatrick (2010)~\cite{vanDoorn:2010hu}, who found that degeneration can prevent fixation of a neo-W or a neo-Y allele, leading to a mixed sex-determining system where the ancestral and new sex-determining loci are both segregating.
+However, they noted that very rare recombination events around the ancestral sex-determining locus can allow these trans-GSD transitions to complete.  
 %While not explicitly studied, we also predict that Y or W degeneration would prevent fixation of the new sex-determining genes considered here.
 Degeneration around the Y or W could explain why trans-GSD transitions are not observed to be much more common than cis-GSD transitions despite the fact that our models demonstrate that they are favoured under a wider range of conditions, especially with haploid selection.
-For example,~\cite{Vicoso:2015hf} found a dozen sex chromosome configurations among Dipteran species but only one transition between male and female heterogamety.
+For example, there are a dozen sex chromosome configurations among Dipteran species but only one transition between male and female heterogamety~\cite{Vicoso:2015hf}.
 
 %Limitation 3: don't consider m alleles with similar k to ancester, no ancestral ESD considered
-In this study, we have only considered neo-sex-determining alleles of large effect. 
+In this study, we have only considered new sex-determining alleles of large effect. 
 However, we expect similar selective forces to act on masculinizing/feminizing alleles of weaker effect. 
-For example,~\cite{Muralidhar2018} consider small effect masculinizing/feminizing alleles within a threshold model of sex determination, finding that they can be favoured when linked to loci that experience sexually-antagonistic selection.
+For example, small effect masculinizing/feminizing alleles within a threshold model of sex determination can be favoured when linked to loci that experience sexually-antagonistic selection~\cite{Muralidhar2018}.
 These results echo those for large-effect neo-Y/neo-W alleles~\cite{vanDoorn:2007eu,vanDoorn:2010hu}.
@@
 
-We have shown that tight sex-linkage and haploid selection can drive previously unexpected transitions between sex-determination systems.
-In particular, both can select for neo-sex-determining loci that are more loosely linked to loci under selection. 
+We have shown that tight sex-linkage and haploid selection can drive previously unexpected transitions between sex-determining systems.
+In particular, both can select for new sex-determining loci that are more loosely linked to loci under selection. 
 In addition, haploid selection can cause transitions analogous to those caused by purely sexually-antagonistic selection, eliminating the need for differences in selection between male and female diploids.
-We conclude that haploid selection should be considered as a pivotal factor driving transitions between sex-determination systems. 
+We conclude that haploid selection should be considered as a pivotal factor driving transitions between sex-determining systems. 
 Perhaps counterintuitively, transitions involving haploid selection can be driven by sex ratio selection or cause sex ratio biases to evolve; we do not find Fisherian sex ratio selection to be an overwhelming force.
-Overall, our results suggest several new scenarios under which new sex-determination systems are favoured, which could help to explain why the evolution of sex-determination systems is so dynamic.
+Overall, our results suggest several new scenarios under which new sex-determining systems are favoured, which could help to explain why the evolution of sex-determining systems is so dynamic.
 
@@
 \label{fig:temporalOverdominance}
-{\bf Following invasion by a neo-W allele, there can be a complete transition to a new sex-determination system, maintenance of both ancestral-XY and neo-ZW sex determining regions, or loss of the new sex-determining allele.}
+{\bf Following invasion by a neo-W allele, there can be a complete transition to a new sex-determining system, maintenance of both ancestral-XY and neo-ZW sex determining regions, or loss of the new sex-determining allele.}
 Here, we plot the frequency of the neo-W allele among female gametes.
@@
 Figure is equivalent to Fig \ref{fig:regionplots} but with meiotic drive in males.
-%We vary the fitness of male homozygotes relative to heterozygotes ($w_{Aa}^\Hermaphrodite=1$) and only consider stable equilibria at which both \textbf{A} locus allele are maintained and the $a$ allele is initially fixed on the Y, region outlined.
+%We vary the fitness of male homozygotes relative to heterozygotes ($w_{Aa}^\Hermaphrodite=1$) and only consider stable equilibria at which both $\mathbf{A}$ locus allele are maintained and the $a$ allele is initially fixed on the Y, region outlined.
 In panels A-C, meiotic drive in males favours the $a$ allele ($\alpha_{\Delta}^\male=-0.16$), creating male-biased sex ratios and generally increasing $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$.
@@
 
-Competition then occurs among gametes of the same sex (e.g., among eggs and among sperm separately) according to the genotype at the \textbf{A} locus ($w_{1}^\Hermaphrodite=w_{3}^\Hermaphrodite=w_{A}^\Hermaphrodite$, $w_{2}^\Hermaphrodite=w_{4}^\Hermaphrodite=w_{a}^\Hermaphrodite$, see Table \ref{tab:fitnesstable}).
+Competition then occurs among gametes of the same sex (e.g., among eggs and among sperm separately) according to the genotype at the $\mathbf{A}$ locus ($w_{1}^\Hermaphrodite=w_{3}^\Hermaphrodite=w_{A}^\Hermaphrodite$, $w_{2}^\Hermaphrodite=w_{4}^\Hermaphrodite=w_{a}^\Hermaphrodite$, see Table \ref{tab:fitnesstable}).
 The genotype frequencies after gametic competition are $x_{i}^{\Hermaphrodite,s}= w_{i}^{\Hermaphrodite}x_{i}^{\Hermaphrodite}/\bar{w}_{H}^{\Hermaphrodite}$ and $y_{i}^{\Hermaphrodite,s}= w_{i}^{\Hermaphrodite}y_{i}^{\Hermaphrodite}/\bar{w}_{H}^{\Hermaphrodite}$, where $\bar{w}_{H}^{\Hermaphrodite}=\sum_{i} w_{i}^{\Hermaphrodite}x_{i}^{\Hermaphrodite}+w_{i}^{\Hermaphrodite}y_{i}^{\Hermaphrodite}$ is the mean fitness of male ($\Hermaphrodite=\male$) or female ($\Hermaphrodite=\female$) gametes.
@@
 %To shorten notation we now use index $i$ (and $j$) to denote the alleles at both the $\mathbf{A}$ and $\mathbf{M}$ loci and label $MA=1$, $Ma=2$, $mA=3$, and $ma=4$, such that $i,j\in\{1,2,3,4\}$.
-The frequencies of XX zygotes are then denoted as $xx_{ij}$, XY zygotes as $xy_{ij}$, and YY zygotes as $yy_{ij}$, where \textbf{A} and \textbf{M} locus genotypes are given by $i,j\in\{1,2,3,4\}$, as above.
-In $XY$ zygotes, the haplotype inherited from an X-bearing gamete is given by $i$ and the haplotype from a Y-bearing gamete is given by $j$. 
+The frequencies of XX zygotes are then denoted as $xx_{ij}$, XY zygotes as $xy_{ij}$, and YY zygotes as $yy_{ij}$, where $\mathbf{A}$ and $\mathbf{M}$ locus genotypes are given by $i,j\in\{1,2,3,4\}$, as above.
+In XY zygotes, the haplotype inherited from an X-bearing gamete is given by $i$ and the haplotype from a Y-bearing gamete is given by $j$. 
 In XX and YY zygotes, individuals with diploid genotype $ij$ are equivalent to those with diploid genotype $ji$; for simplicity, we use $xx_{ij}$ and $yy_{ij}$ with $i\neq j$ to denote the average of these frequencies, $xx_{ij}=(x_{i}^{\female,s}x_{j}^{\male,s}+x_{j}^{\female,s}x_{i}^{\male,s})/2$ and $yy_{ij}=(y_{i}^{\female,s}y_{j}^{\male,s}+y_{j}^{\female,s}y_{i}^{\male,s})/2$.
 
-Denoting the \textbf{M} locus genotype by $b \in \{MM, Mm, mm\}$ and the \textbf{X} locus genotype by $c \in \{XX, XY, YY\}$, zygotes develop as females with probability $k_{bc}$. 
+Denoting the $\mathbf{M}$ locus genotype by $b \in \{MM, Mm, mm\}$ and the $\mathbf{X}$ locus genotype by $c \in \{XX, XY, YY\}$, zygotes develop as females with probability $k_{bc}$. 
 Therefore, the frequencies of XX females are given by $xx_{ij}^{\female}=k_{bc}xx_{ij}$, XY females are given by $xy_{ij}^{\female}=k_{bc}xy_{ij}$, and YY females are given by $yy_{ij}^{\female}=k_{bc}yy_{ij}$.
@@
 In addition, we can consider any epistatic dominance relationship between the two sex-determining loci. 
-Here, we assume that the ancestral sex-determining system (\textbf{X} locus) is XY ($k_{MMXX}=1$ and $k_{MMXY}=k_{MMYY}=0$) or ZW ($k_{MMZZ}=0$ and $k_{MMZW}=k_{MMWW}=1$) and epistatically recessive to a dominant novel sex-determining locus, \textbf{M} ($k_{Mmc}=k_{mmc}=k$).
-
-Selection among diploids then occurs according to the diploid genotype at the \textbf{A} locus, $l \in \{AA, Aa, aa\}$, for an individual of type $ij$ (see Table \ref{tab:fitnesstable}). 
+Here, we assume that the ancestral sex-determining system ($\mathbf{X}$ locus) is XY ($k_{MMXX}=1$ and $k_{MMXY}=k_{MMYY}=0$) or ZW ($k_{MMZZ}=0$ and $k_{MMZW}=k_{MMWW}=1$) and epistatically recessive to a dominant novel sex-determining locus, $\mathbf{M}$ ($k_{Mmc}=k_{mmc}=k$).
+
+Selection among diploids then occurs according to the diploid genotype at the $\mathbf{A}$ locus, $l \in \{AA, Aa, aa\}$, for an individual of type $ij$ (see Table \ref{tab:fitnesstable}). 
 The diploid frequencies after selection in sex $\Hermaphrodite$ are given by $xx_{ij}^{\Hermaphrodite,s}=w_{l}^{\Hermaphrodite} xx_{ij}/\bar{w}^{\Hermaphrodite}_{D}$, $xy_{ij}^{\Hermaphrodite,s}=w_{l}^{\Hermaphrodite} xy_{ij}/\bar{w}^{\Hermaphrodite}_{D}$, and $yy_{ij}^{\Hermaphrodite,s}=w_{l}^{\Hermaphrodite} yy_{ij}/\bar{w}^{\Hermaphrodite}_{D}$, where $\bar{w}^{\Hermaphrodite}_{D}= \sum_{i=1}^{4}\sum_{j=1}^{4}w_{l}^{\Hermaphrodite}xx_{ij}+w_{l}^{\Hermaphrodite}xy_{ij}+w_{l}^{\Hermaphrodite}yy_{ij}$ is the mean fitness of diploids of sex $\Hermaphrodite$.
@@
 %We can also assume that recombination is sex specific and/or affected by the M locus - but generally we don't so I just describe $R=R_{f}=R, r_{MM,d}=r_{Mm,d}=r_{mm,d}=r, \chi_{m}=\chi_{f}=\chi$.
-Here, we allow any relative locations for the SDR, \textbf{A}, and \textbf{M} loci by using three parameters to describe the recombination rates between them. 
-$R$ is the recombination rate between the \textbf{A} locus and the \textbf{M} locus, $\rho$ is the recombination rate between the \textbf{M} locus and the \textbf{X} locus, and $r$ is the recombination rate between the \textbf{A} locus and the \textbf{X} locus (Fig \ref{fig:model_outline}).
+Here, we allow any relative locations for the SDR, $\mathbf{A}$, and $\mathbf{M}$ loci by using three parameters to describe the recombination rates between them. 
+$R$ is the recombination rate between the $\mathbf{A}$ locus and the $\mathbf{M}$ locus, $\rho$ is the recombination rate between the $\mathbf{M}$ locus and the $\mathbf{X}$ locus, and $r$ is the recombination rate between the $\mathbf{A}$ locus and the $\mathbf{X}$ locus (Fig \ref{fig:model_outline}).
 \nameref{tab:chisubstitutions} shows replacements that can be made for each possible ordering of the loci assuming that there is no cross-over interference.
@@
 The full system is therefore described by 16 recurrence equations (three diallelic loci in two sexes, $2^3 \times 2 = 16$). 
-However, not all diploid types are produced under certain sex-determination systems. 
-For example, with the $M$ allele fixed and an ancestral $XY$ sex-determining system, there are $XX$ females and $XY$ males ($x_{3}^\Hermaphrodite=x_{4}^\Hermaphrodite=y_{4}^\Hermaphrodite=y_{3}^\Hermaphrodite=y_{i}^\female=0$).
+However, not all diploid types are produced under certain sex-determining systems. 
+For example, with the $M$ allele fixed and an ancestral XY sex-determining system, there are XX females and XY males ($x_{3}^\Hermaphrodite=x_{4}^\Hermaphrodite=y_{4}^\Hermaphrodite=y_{3}^\Hermaphrodite=y_{i}^\female=0$).
 %($xx_{11}^{\male}=xx_{12}^{\male}=xx_{22}^\male=xy_{11}^{\female}=xy_{12}^{\female}=xy_{21}^{\female}=xy_{22}^\female=yy_{11}^{\female}=yy_{12}^{\female}=yy_{22}^\female=0$). 
-In this case, the system only involves six recursion equations, %because there is only one \textbf{M} locus allele and no Y-bearing female gametes. 
+In this case, the system only involves six recursion equations, %because there is only one $\mathbf{M}$ locus allele and no Y-bearing female gametes. 
 which we assume below to calculate the equilibria.
@@
 
-Various forms of selection can maintain a polymorphism at the \textbf{A} locus, including sexually antagonistic selection, overdominance, conflicts between diploid selection and selection upon haploid genotypes (ploidally-antagonsitic selection,~\cite{Immler:2012tl}), or a combination of these selective regimes (see below).
+Various forms of selection can maintain a polymorphism at the $\mathbf{A}$ locus, including sexually antagonistic selection, overdominance, conflicts between diploid selection and selection upon haploid genotypes (ploidally-antagonsitic selection,~\cite{Immler:2012tl}), or a combination of these selective regimes (see below).
 
 In particular special cases, e.g., no sex-differences in selection or meiotic drive ($s^\male=s^\female$, $h^\male=h^\female$, and $\alpha^\male=\alpha^\female=1/2$), the equilibrium allele frequency and stability can be calculated analytically without assuming anything about the relative strengths of selection and recombination.
-However, here, we focus on two regimes (tight linkage between \textbf{A} and \textbf{X} and weak selection) in order to make fewer assumptions about fitnesses.
-
-\subsubsection*{Tight linkage between \textbf{A} and \textbf{X}}
-
-We first calculate the equilibrium frequency of the Y and $A$ alleles in the ancestral population when the recombination rate between the \textbf{X} and \textbf{A} loci is small ($r$ of order $\epsilon$).
-Selection at the \textbf{A} locus will not affect evolution at the novel sex-determining locus, \textbf{M}, if one allele is fixed on all backgrounds. 
+However, here, we focus on two regimes (tight linkage between $\mathbf{A}$ and $\mathbf{X}$ and weak selection) in order to make fewer assumptions about fitnesses.
+
+\subsubsection*{Tight linkage between $\mathbf{A}$ and $\mathbf{X}$}
+
+We first calculate the equilibrium frequency of the Y and $A$ alleles in the ancestral population when the recombination rate between the $\mathbf{X}$ and $\mathbf{A}$ loci is small ($r$ of order $\epsilon$).
+Selection at the $\mathbf{A}$ locus will not affect evolution at the novel sex-determining locus, $\mathbf{M}$, if one allele is fixed on all backgrounds. 
 We therefore focus on the five equilibria that maintain both $A$ and $a$ alleles, four of which are given to leading order by:
@@
 We next calculate when $(A)$ and $(B)$ are locally stable for $r=0$. 
-According to the `small parameter theory'~\cite{Karlin:1972ab,Karlin:1972dq}, these stability properties are unaffected by small amounts of recombination between the SDR and \textbf{A} locus, although equilibrium frequencies may be slightly altered.
+According to the `small parameter theory'~\cite{Karlin:1972ab,Karlin:1972dq}, these stability properties are unaffected by small amounts of recombination between the SDR and $\mathbf{A}$ locus, although equilibrium frequencies may be slightly altered.
 For the $a$ allele to be stably fixed on the Y we need $\bar{w}_{Ya}^{\male} > \bar{w}_{YA}^{\male}$ where $\bar{w}_{Ya}^{\male} = w_{a}^{\male} \big[\hat{p}_X^\female(1-\alpha^\male_\Delta) w_{A}^{\female} w_{Aa}^{\male} + (1-\hat{p}_X^\female)w_{a}^{\female} w_{aa}^{\male} \big]$ and $\bar{w}_{YA}^{\male} = w_{A}^{\male} \big[ \hat{p}_X^\female w_{A}^{\female} w_{AA}^{\male} + (1-\hat{p}_X^\female)(1+\alpha^\male_\Delta) w_{a}^{\female} w_{Aa}^{\male} \big]$.
@@
 Here, we assume that selection and meiotic drive are weak relative to recombination ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon$). 
-The maintenance of a polymorphism at the \textbf{A} locus then requires that
+The maintenance of a polymorphism at the $\mathbf{A}$ locus then requires that
 
@@
 
-Given that a polymorphism is maintained at the \textbf{A} locus by weak selection, the frequencies of $A$ in each type of gamete are the same ($\hat{p}^\female_X=\hat{p}^\male_X=\hat{p}^\male_Y=\bar{p}$) and given, to leading order, by
+Given that a polymorphism is maintained at the $\mathbf{A}$ locus by weak selection, the frequencies of $A$ in each type of gamete are the same ($\hat{p}^\female_X=\hat{p}^\male_X=\hat{p}^\male_Y=\bar{p}$) and given, to leading order, by
 
@@
 
-A rare neo-Y or neo-W allele, $m$, will spread from a given ancestral equilibrium with sex-determination system $i\in\{XY,ZW\}$ when the leading eigenvalue, $\lambda_m^{(i)}$, of the Jacobian matrix derived from the eight mutant recursion equations (given by \ref{eq:recursions}c,d,g,h), evaluated at the ancestral equilibrium, is greater than one.
+A rare neo-Y or neo-W allele, $m$, will spread from a given ancestral equilibrium with sex-determining system $i\in\{XY,ZW\}$ when the leading eigenvalue, $\lambda_m^{(i)}$, of the Jacobian matrix derived from the eight mutant recursion equations (given by \ref{eq:recursions}c,d,g,h), evaluated at the ancestral equilibrium, is greater than one.
 However, because a neo-Y (neo-W) is always in males (females) and is epistatically dominant to the ancestral sex-determining locus, the characteristic polynomial factors into two quadratics times $(\lambda_m^{(i)})^4$.
@@
 If only one haplotypic growth rate is greater than one ($\Lambda_{ma}^{(i)}<1<\Lambda_{mA}^{(i)}$ or $\Lambda_{mA}^{(i)}<1<\Lambda_{ma}^{(i)}$), then $\lambda_m^{(i)}$ is greater than one when condition \eqref{eq:lambdasGen} is met.
-Thus, the invasion of a neo-sex-determining allele is determined by the haplotypic growth rates without accounting for loss due to recombination ($\Lambda_{mj}^{(i)}$ terms) and the rates at which recombination between the \textbf{M} and \textbf{A} loci breaks apart these haplotypes ($\chi_{mj}^{(i)}$).
-For tight linkage between the ancestral sex-determining locus (\textbf{X}) and the selected locus (\textbf{A}) we can calculate these terms explicitly (see below).
+Thus, the invasion of a new sex-determining allele is determined by the haplotypic growth rates without accounting for loss due to recombination ($\Lambda_{mj}^{(i)}$ terms) and the rates at which recombination between the $\mathbf{M}$ and $\mathbf{A}$ loci breaks apart these haplotypes ($\chi_{mj}^{(i)}$).
+For tight linkage between the ancestral sex-determining locus ($\mathbf{X}$) and the selected locus ($\mathbf{A}$) we can calculate these terms explicitly (see below).
 For weak selection we can take a Taylor series of the leading eigenvalue. 
@@
 
-\subsubsection*{Tight linkage between \textbf{A} and \textbf{X} ($r \approx 0$)}
-
-Here, we explore the conditions under which a neo-W invades an XY system assuming that the \textbf{A} locus is initially in tight linkage with the ancestral sex-determining region ($r \approx 0$). 
+\subsubsection*{Tight linkage between $\mathbf{A}$ and $\mathbf{X}$ ($r \approx 0$)}
+
+Here, we explore the conditions under which a neo-W invades an XY system assuming that the $\mathbf{A}$ locus is initially in tight linkage with the ancestral sex-determining region ($r \approx 0$). 
 We disregard neo-Y mutations, which never spread given that the ancestral population is at a stable equilibrium (see \nameref{file:Mathematica} for proof).
@@
 For example, with overdominance in males there is selection for increased $A$ frequencies on X chromosomes in males, which are always paired with Y-$a$ haplotypes.
-Directional selection for $a$ in females can then maintain a polymorphism at the $\textbf{A}$ locus on the X.
+Directional selection for $a$ in females can then maintain a polymorphism at the $$\mathbf{A}$$ locus on the X.
 This scenario selects for a modifier that increases recombination between the sex chromosomes (e.g., blue region of Fig 2d in~\cite{Otto2014}) and facilitates the spread of neo-W-$a$ haplotypes, which create females bearing more $a$ alleles than the ancestral X chromosome does.
 
-\subsubsection*{Role of haploid selection with tight linkage between \textbf{X} and \textbf{A}}
+\subsubsection*{Role of haploid selection with tight linkage between $\mathbf{X}$ and $\mathbf{A}$}
 
@@
 Male haploid selection in favour of the $a$ allele ($\alpha_{\Delta}^\male<0$, $w_{A}^\male<w_{a}^\male$) generates male-biased sex ratios at equilibria (A) and (B), where Y-$a$ is fixed ($\hat{p}_{Y}^\male=0$).
-Male-biased sex-ratios facilitate the spread of neo-W-$A$ and neo-W-$a$ haplotypes (increasing $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$). 
+Male-biased sex ratios facilitate the spread of neo-W-$A$ and neo-W-$a$ haplotypes (increasing $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$). 
 Panels A-C in \nameref{fig:regionMaleDrive} and \ref{fig:regionMaleGS} show that neo-W haplotypes tend to spread for a wider range of parameters when sex ratios are male biased, compared to Fig \ref{fig:regionplots} without haploid selection.

### 2018-02-05 LaTeX/Turnover_plos.tex
cover letter

@@
 Surprisingly, we find that neither force (sex ratio selection nor associations with genes that have sex-specific effects) dominates the spread of new sex-determining systems alone. 
-Even more unexpectedly, we find that new sex-determining alleles do not necessarily have to arise in closer linkage with genes that are differentially selected in males and females to spread. 
+Even more unexpectedly, we find that, to spread, new sex-determining alleles do not necessarily have to arise in closer linkage with genes that are differentially selected in males and females. 
 Therefore, our models predict loci in previously unexpected genomic locations and/or experiencing various types of selection (including haploid selection) can now be implicated as drivers of transitions between sex-determining systems.
@@
 \label{fig:temporalOverdominance}
-{\bf Following invasion by a neo-W allele, there can be a complete transition to a new sex-determining system, maintenance of both ancestral-XY and neo-ZW sex determining regions, or loss of the new sex-determining allele.}
+{\bf Following invasion by a neo-W allele, there can be a complete transition to a new sex-determining system, maintenance of both ancestral-XY and neo-ZW sex determining systems, or loss of the new sex-determining allele.}
 Here, we plot the frequency of the neo-W allele among female gametes.
@@
 Panels A, C and D show cases where a steady state is reached with the neo-W at a frequency below $0.5$, in which case ancestral-X and Y alleles also both segregate. 
-In all cases, we assume that the $a$ allele is initially more common than the $A$ allele on the Y (Y-$a$ is fixed when $r=0$). 
+In all cases, we assume that the $a$ allele is initially more common than the $A$ allele on the Y background (Y-$a$ is fixed when $r=0$). 
 When $r>0$ (panels B and D), Y-$A$ haplotypes created by recombination can become more common than Y-$a$ haplotypes as the neo-W spreads.
 In B, this leads to loss of the neo-W and the system goes to an equilibrium with X-$a$ and Y-$A$ haplotypes fixed (equilibrium $A'$), such that all females have the high fitness genotype $aa$ and all males are $Aa$.
-For the parameters in B, neo-W alleles have negative invasion fitness when the Y-$A$ haplotype is ancestrally more common than Y-$a$ (compare blue to black curves in \nameref{fig:positionOverdominance}A and  \nameref{fig:positionOverdominance}B near the ancestral SDR).
-In contrast, the neo-W is not lost in panel D as it is favoured regardless of whether Y-$A$ or Y-$a$ predominates (again, compare blue to black curves in \nameref{fig:positionOverdominance}C and  \nameref{fig:positionOverdominance}D).
+For the parameters in B, neo-W alleles have negative invasion fitness when the Y-$A$ haplotype is ancestrally more common than Y-$a$ (compare blue to black curves in \nameref{fig:positionOverdominance}A and  \nameref{fig:positionOverdominance}B near the ancestral sex-determining locus).
+In contrast, the neo-W is not lost in panel D as it is favoured regardless of whether Y-$A$ or Y-$a$ haplotypes predominate (again, compare blue to black curves in \nameref{fig:positionOverdominance}C and  \nameref{fig:positionOverdominance}D).
 %Fitness parameters are the same as in \nameref{fig:positionOverdominance}; in panels A and B the $a$ allele is favoured in females ($w_{aa}^\female=1.05$, $w_{Aa}^\Hermaphrodite=1$, $w_{AA}^\female=0.85$) while there is overdominance in males ($w_{aa}^\male=w_{AA}^\male=0.75$) and in panels C and D, there is overdominance in both sexes ($w_{aa}^\female=w_{AA}^\female=0.6$, $w_{aa}^\male=0.5$, $w_{AA}^\male=0.7$, $w_{Aa}^\Hermaphrodite=1$).
@@
 \label{fig:SexAntagTighterMaleDrive}
-{\bf  When there is sexually-antagonistic selection and haploid selection, a neo-W may invade for any $R$.}
+{\bf  When there is sexually-antagonistic selection and haploid selection, a neo-W allele may invade for any $R$.}
 Panel A shows that the invasion fitness of a neo-W is positive, even when $r<R$ (unshaded region).
-In panel B, we vary the recombination rate between the neo-W and the selected locus ($R$) for a fixed recombination rate between the ancestral-SDR and the selected locus ($r=0.005$).
+In panel B, we vary the recombination rate between the neo-W and the selected locus ($R$) for a fixed recombination rate between the ancestral sex-determining locus and the selected locus ($r=0.005$).
 Coloured markers show recombination rates for which the temporal dynamics of neo-W invasion are plotted in panel C (black $R=0.001$, red $R=0.02$, blue $R=0.1$, green $R=0.5$). 
@@
 There is also meiotic drive in males favouring $a$ ($\alpha_{\Delta}^\male=-0.08$), this full set of parameters is marked by an asterisk in \nameref{fig:regionMaleDrive}A.
-When $R=0.5$ (green curve), the neo-W does not reach fixation and X,Y,Z, and W alleles are all maintained in the population, see \nameref{fig:freqAll}C.
+When $R=0.5$ (green curve), the neo-W does not reach fixation and X, Y, Z, and W alleles are all maintained in the population, see \nameref{fig:freqAll}C.
 
@@
 \label{fig:regionMaleDrive}
-{\bf Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is male meiotic drive at a locus that is tightly linked to the ancestral-XY locus ($r=0$).}
-Figure is equivalent to Fig \ref{fig:regionplots} but with meiotic drive in males.
+{\bf Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is male meiotic drive at a locus that is tightly linked to the ancestral XY locus ($r=0$).}
+This figure is equivalent to Fig \ref{fig:regionplots} but with meiotic drive in males.
 %We vary the fitness of male homozygotes relative to heterozygotes ($w_{Aa}^\Hermaphrodite=1$) and only consider stable equilibria at which both $\mathbf{A}$ locus allele are maintained and the $a$ allele is initially fixed on the Y, region outlined.
@@
 \label{fig:regionMaleGS}
-{\bf Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is male gametic competition at a locus that is tightly linked to the ancestral-XY locus ($r=0$).}
-Figure is equivalent to Fig \ref{fig:regionplots} but with gametic competition in males.
+{\bf Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is male gametic competition at a locus that is tightly linked to the ancestral XY locus ($r=0$).}
+This figure is equivalent to Fig \ref{fig:regionplots} but with gametic competition in males.
 %Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in \nameref{fig:regionMaleDrive}. 
@@
 \label{fig:regionFemaleDrive}
-{\bf Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is female meiotic drive at a locus that is tightly linked to the ancestral-XY locus ($r=0$).}
-Figure is equivalent to Fig \ref{fig:regionplots} but with meiotic drive in females.
+{\bf Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is female meiotic drive at a locus that is tightly linked to the ancestral XY locus ($r=0$).}
+This figure is equivalent to Fig \ref{fig:regionplots} but with meiotic drive in females.
 %Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in \nameref{fig:regionMaleDrive} and \nameref{fig:regionMaleGS}. 
@@
 \label{fig:regionFemaleGS}
-{\bf Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is female gametic competition at a locus that is tightly linked to the ancestral-XY locus ($r=0$).}
-Figure is equivalent to Fig \ref{fig:regionplots} but with gametic competition in females.
+{\bf Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is female gametic competition at a locus that is tightly linked to the ancestral XY locus ($r=0$).}
+This figure is equivalent to Fig \ref{fig:regionplots} but with gametic competition in females.
 %Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in \nameref{fig:regionMaleDrive}, \nameref{fig:regionMaleGS}, and \nameref{fig:regionFemaleDrive}. 
@@
 \label{fig:regionPloidAntag}
-{\bf Ploidally-antagonistic selection can drive the spread of neo-W chromosomes. }
+{\bf Ploidally-antagonistic selection can drive the spread of neo-W alleles. }
 A-D show when each of the neo-W haplotypes invades an internally stable equilibrium with $a$ fixed on the Y (found by setting $r=0$).
@@
 {\bf Pseudo-fixation of neo-W or maintenance of multiple sex-determining alleles. }
-The curves show the frequencies of the neo-W (red), ancestral-Y (blue), and $A$ allele (black) among female gametes (solid curves) and among male gametes (dashed curves). 
+The curves show the frequencies of the neo-W (red), ancestral Y (blue), and $A$ allele (black) among female gametes (solid curves) and among male gametes (dashed curves). 
 In panel A, there is a complete transition from XY sex determination (XX-ZZ females and XY-ZZ males) to ZW sex determination (YY-ZW females and YY-ZZ males).  
-In panels B and C a polymorphism is maintained at both the ancestral XY locus and the neo-ZW locus, such that there are males with genotypes XY-ZZ or YY-ZZ and females with genotypes XX-ZZ, XX-ZW, XY-ZW, or YY-ZW.
-In panel A, selection is ploidally antagonistic with drive in males (parameters as in the green curve in Fig \ref{fig:SexRatioBad}B).
+In panels B and C a polymorphism is maintained at both the ancestral XY locus and the new ZW locus, such that there are males with genotypes XY-ZZ and YY-ZZ and females with genotypes XX-ZZ, XX-ZW, XY-ZW, and YY-ZW.
+In panel A, selection is ploidally-antagonistic with drive in males (parameters as in the green curve in Fig \ref{fig:SexRatioBad}B).
 In panel B, there is overdominance in both sexes and no haploid selection (parameters as in the green curve in \nameref{fig:temporalOverdominance}C).
@@
 %We can also assume that recombination is sex specific and/or affected by the M locus - but generally we don't so I just describe $R=R_{f}=R, r_{MM,d}=r_{Mm,d}=r_{mm,d}=r, \chi_{m}=\chi_{f}=\chi$.
-Here, we allow any relative locations for the SDR, $\mathbf{A}$, and $\mathbf{M}$ loci by using three parameters to describe the recombination rates between them. 
-$R$ is the recombination rate between the $\mathbf{A}$ locus and the $\mathbf{M}$ locus, $\rho$ is the recombination rate between the $\mathbf{M}$ locus and the $\mathbf{X}$ locus, and $r$ is the recombination rate between the $\mathbf{A}$ locus and the $\mathbf{X}$ locus (Fig \ref{fig:model_outline}).
+Here, we allow any relative locations for the $\mathbf{X}$, $\mathbf{A}$, and $\mathbf{M}$ loci by using three parameters to describe the recombination rates between them. 
+$R$ is the recombination rate between the $\mathbf{A}$ and $\mathbf{M}$ loci, $\rho$ is the recombination rate between the $\mathbf{M}$ and $\mathbf{X}$ loci, and $r$ is the recombination rate between the $\mathbf{A}$ and $\mathbf{X}$ loci (Fig \ref{fig:model_outline}).
 \nameref{tab:chisubstitutions} shows replacements that can be made for each possible ordering of the loci assuming that there is no cross-over interference.
@@
 &+\big{[}-(R+r+\rho) xy_{14}^{\Hermaphrodite,s} + (R+\rho-r)xy_{41}^{\Hermaphrodite,s}\\
-&+(R+r-\rho) xy_{23}^{\Hermaphrodite,s} + (R+\rho-r) xy_{32}^{\Hermaphrodite,s}\big{]}(1-\alpha^\Hermaphrodite)/2
+&+(R+r-\rho) xy_{23}^{\Hermaphrodite,s} + (R+\rho-r) xy_{32}^{\Hermaphrodite,s}\big{]}(1-\alpha^\Hermaphrodite)/2.
 \end{split}
@@
 However, not all diploid types are produced under certain sex-determining systems. 
-For example, with the $M$ allele fixed and an ancestral XY sex-determining system, there are XX females and XY males ($x_{3}^\Hermaphrodite=x_{4}^\Hermaphrodite=y_{4}^\Hermaphrodite=y_{3}^\Hermaphrodite=y_{i}^\female=0$).
+For example, with the $M$ allele fixed and an ancestral XY sex-determining system, there are XX females and XY males ($x_{3}^\Hermaphrodite=x_{4}^\Hermaphrodite=y_{3}^\male=y_{4}^\male=y_{i}^\female=0,\;\forall\; i$).
 %($xx_{11}^{\male}=xx_{12}^{\male}=xx_{22}^\male=xy_{11}^{\female}=xy_{12}^{\female}=xy_{21}^{\female}=xy_{22}^\female=yy_{11}^{\female}=yy_{12}^{\female}=yy_{22}^\female=0$). 
@@
 
-\subsubsection*{Tight linkage between $\mathbf{A}$ and $\mathbf{X}$}
-
-We first calculate the equilibrium frequency of the Y and $A$ alleles in the ancestral population when the recombination rate between the $\mathbf{X}$ and $\mathbf{A}$ loci is small ($r$ of order $\epsilon$).
+\subsubsection*{Tight linkage between $\mathbf{X}$ and $\mathbf{A}$ loci}
+
+We first calculate the equilibria in the ancestral population when the recombination rate between the $\mathbf{X}$ and $\mathbf{A}$ loci is small ($r$ of order $\epsilon$). 
 Selection at the $\mathbf{A}$ locus will not affect evolution at the novel sex-determining locus, $\mathbf{M}$, if one allele is fixed on all backgrounds. 
@@
 \phi'=&(1-\alpha^\female_\Delta) w_{a}^{\female} w_{Aa}^{\female} \left[ w_{A}^{\male} w_{AA}^{\male} + (1-\alpha_\Delta^\male) w_{a}^{\male} w_{Aa}^{\male} \right]/2 - w_{A}^{\male} w_{A}^{\female} w_{AA}^{\male} w_{AA}^{\female}\\
-\psi'=&(1+\alpha^\female_\Delta) w_{A}^{\female} w_{Aa}^{\female} \left[ w_{A}^{\male} w_{AA}^{\male} + (1-\alpha_\Delta^\male) w_{a}^{\male} w_{Aa}^{\male} \right]/2 - (1-\alpha_\Delta^\male) w_{a}^{\male} w_{a}^{\female} w_{Aa}^{\male} w_{aa}^{\female}
+\psi'=&(1+\alpha^\female_\Delta) w_{A}^{\female} w_{Aa}^{\female} \left[ w_{A}^{\male} w_{AA}^{\male} + (1-\alpha_\Delta^\male) w_{a}^{\male} w_{Aa}^{\male} \right]/2 - (1-\alpha_\Delta^\male) w_{a}^{\male} w_{a}^{\female} w_{Aa}^{\male} w_{aa}^{\female}.
 \end{split}
@@
 \noindent
-A fifth equilibrium $(C)$ also exists where $A$ is present at an intermediate frequency on the Y chromosome ($0<\hat{p}_{Y}^{\male}<1$). 
+A fifth equilibrium $(C)$ also exists where $A$ is present at an intermediate frequency on the Y background ($0<\hat{p}_{Y}^{\male}<1$). 
 However, equilibrium $(C)$ is never locally stable when $r \approx 0$ and is therefore not considered further.
-Thus, the Y can either be fixed for the $a$ allele (equilibria $A$ and $B$) or the $A$ allele (equilibria $A'$ and $B'$).
-The X chromosome can then either be polymorphic (equilibria $A$ and $A'$) or fixed for the alternative allele (equilibria $B$ and $B'$).
-Since equilibria $(A)$ and $(B)$ are equivalent to equilibria $(A')$ and $(B')$ with the labelling of $A$ and $a$ alleles interchanged, we discuss only equilibria $(A)$ and $(B)$, in which the Y is fixed for the $a$ allele.
+Thus, the Y background can either be fixed for the $a$ allele (equilibria ($A$) and ($B$)) or the $A$ allele (equilibria ($A'$) and ($B'$)).
+The X background can then either be polymorphic (equilibria ($A$) and ($A'$)) or fixed for the alternative allele (equilibria ($B$) and ($B'$)).
+Since equilibria $(A)$ and $(B)$ are equivalent to equilibria $(A')$ and $(B')$ with the labelling of $A$ and $a$ alleles interchanged, we discuss only equilibria $(A)$ and $(B)$, in which the Y background is fixed for the $a$ allele.
 If there is no haploid selection ($\alpha^{\Hermaphrodite}_\Delta=0$, $w_{A}^{\Hermaphrodite}=w_{a}^{\Hermaphrodite}=1$), these equilibria are equivalent to those found by~\cite{Lloyd1977} and~\cite{Otto2014}.
 
-We next calculate when $(A)$ and $(B)$ are locally stable for $r=0$. 
-According to the `small parameter theory'~\cite{Karlin:1972ab,Karlin:1972dq}, these stability properties are unaffected by small amounts of recombination between the SDR and $\mathbf{A}$ locus, although equilibrium frequencies may be slightly altered.
-For the $a$ allele to be stably fixed on the Y we need $\bar{w}_{Ya}^{\male} > \bar{w}_{YA}^{\male}$ where $\bar{w}_{Ya}^{\male} = w_{a}^{\male} \big[\hat{p}_X^\female(1-\alpha^\male_\Delta) w_{A}^{\female} w_{Aa}^{\male} + (1-\hat{p}_X^\female)w_{a}^{\female} w_{aa}^{\male} \big]$ and $\bar{w}_{YA}^{\male} = w_{A}^{\male} \big[ \hat{p}_X^\female w_{A}^{\female} w_{AA}^{\male} + (1-\hat{p}_X^\female)(1+\alpha^\male_\Delta) w_{a}^{\female} w_{Aa}^{\male} \big]$.
+We next calculate when equilibria $(A)$ and $(B)$ are locally stable for $r=0$. 
+According to the `small parameter theory'~\cite{Karlin:1972ab,Karlin:1972dq}, these stability properties are unaffected by small amounts of recombination between the sex-determining locus and the $\mathbf{A}$ locus, although equilibrium frequencies may be slightly altered.
+For the $a$ allele to be stably fixed on the Y background we need $\bar{w}_{Ya}^{\male} > \bar{w}_{YA}^{\male}$ where $\bar{w}_{Ya}^{\male} = w_{a}^{\male} \big[\hat{p}_X^\female(1-\alpha^\male_\Delta) w_{A}^{\female} w_{Aa}^{\male} + (1-\hat{p}_X^\female)w_{a}^{\female} w_{aa}^{\male} \big]$ and $\bar{w}_{YA}^{\male} = w_{A}^{\male} \big[ \hat{p}_X^\female w_{A}^{\female} w_{AA}^{\male} + (1-\hat{p}_X^\female)(1+\alpha^\male_\Delta) w_{a}^{\female} w_{Aa}^{\male} \big]$.
 That is, Y-$a$ haplotypes must have higher fitness than Y-$A$ haplotypes.  
-Substituting in $\hat{p}_X^\female$ from equation \eqref{eq:tightequil}, fixation of the $a$ allele on the Y requires that $\gamma_{i}>0$ where $\gamma_{(A)}=w_{a}^{\male} \big[ (1-\alpha^\male_\Delta) w_{Aa}^{\male} \phi + w_{aa}^{\male} \psi \big]-w_{A}^{\male} \big[ w_{AA}^{\male} \phi + (1 + \alpha^{\male}_\Delta)w_{Aa}^{\male} \psi \big]$ for equilibrium $(A)$ and $\gamma_{(B)}=(1-\alpha^{\male}_\Delta)w_{a}^{\male}w_{Aa}^{\male}-w_{A}^{\male}w_{AA}^{\male}$ for equilibrium $(B)$.
-Stability of a polymorphism on the X chromosome (equilibrium $A$) further requires that $\phi >0$ and $\psi >0$. 
-Fixation of the $a$ allele on the X (equilibrium $B$) can be stable only if equilibrium $(A)$ is not, as it requires $\psi<0$.
+Substituting in $\hat{p}_X^\female$ from equation \eqref{eq:tightequil}, fixation of the $a$ allele on the Y background requires that $\gamma_{i}>0$ where $\gamma_{(A)}=w_{a}^{\male} \big[ (1-\alpha^\male_\Delta) w_{Aa}^{\male} \phi + w_{aa}^{\male} \psi \big]-w_{A}^{\male} \big[ w_{AA}^{\male} \phi + (1 + \alpha^{\male}_\Delta)w_{Aa}^{\male} \psi \big]$ for equilibrium $(A)$ and $\gamma_{(B)}=(1-\alpha^{\male}_\Delta)w_{a}^{\male}w_{Aa}^{\male}-w_{A}^{\male}w_{AA}^{\male}$ for equilibrium $(B)$.
+Stability of a polymorphism on the X background (equilibrium $(A)$) further requires that $\phi >0$ and $\psi >0$. 
+Fixation of the $a$ allele on the X background (equilibrium $(B)$) can be stable only if equilibrium $(A)$ is not, as it requires $\psi<0$.
 %and $2w_{A}^{\female}w_{AA}^{\female}>(1-\alpha_\Delta^{\female})w_{a}^{\female}w_{Aa}^{\female}$ or just $4w_{A}^{\female}w_{AA}^{\female}<(1-\alpha_\Delta^{\female})w_{a}^{\female}w_{Aa}^{\female}$ (which also prevents $\psi>0$).
@@
 
-Here, we assume that selection and meiotic drive are weak relative to recombination ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon$). 
+Here, we assume that selection is weak relative to recombination ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon$). 
 The maintenance of a polymorphism at the $\mathbf{A}$ locus then requires that
@@
 \hat{p}^\male_Y-\hat{p}^\male_X&=V_{A}\left(D^\male - D^\female+\alpha_{\Delta}^\male-\alpha_{\Delta}^\female+t^\male-t^\female\right)(1-2r)/2r
-+O(\epsilon^2)
++O(\epsilon^2),
 \end{split}
@@
 where $V_{A}=\bar{p}(1-\bar{p})$ is the variance in the frequency of $A$ and $D^\Hermaphrodite=\big{[} \bar{p}s^\Hermaphrodite+(1-\bar{p})h^\Hermaphrodite s^\Hermaphrodite\big{]} -\big{[} \bar{p}h^\Hermaphrodite s^\Hermaphrodite+(1-\bar{p}) \big{]}$ corresponds to the difference in fitness between $A$ and $a$ alleles in diploids of sex $\Hermaphrodite \in \{\female,\male\}$.
-The frequency of Y among male gametes depends upon the difference in the frequency of the $A$ allele between X- and Y-bearing male gametes and the strength of meiotic drive in favour of the $A$ allele in males, $q=1/2+\alpha_{\Delta}^\male(\hat{p}^\male_Y-\hat{p}^\male_X)/2+O(\epsilon^3)$.
+The frequency of Y-bearing male gametes depends upon the difference in the frequency of the $A$ allele between X- and Y-bearing male gametes and the strength of meiotic drive in favour of the $A$ allele in males, $q=1/2+\alpha_{\Delta}^\male(\hat{p}^\male_Y-\hat{p}^\male_X)/2+O(\epsilon^3)$.
 Without gametic competition or drive ($\alpha_{\Delta}^\Hermaphrodite=t^\Hermaphrodite=0$) our results reduce to those of~\cite{vanDoorn:2007eu}.
@@
 
-A rare neo-Y or neo-W allele, $m$, will spread from a given ancestral equilibrium with sex-determining system $i\in\{XY,ZW\}$ when the leading eigenvalue, $\lambda_m^{(i)}$, of the Jacobian matrix derived from the eight mutant recursion equations (given by \ref{eq:recursions}c,d,g,h), evaluated at the ancestral equilibrium, is greater than one.
-However, because a neo-Y (neo-W) is always in males (females) and is epistatically dominant to the ancestral sex-determining locus, the characteristic polynomial factors into two quadratics times $(\lambda_m^{(i)})^4$.
-One quadratic governs the change in the frequency of the new sex determination factor associated with the A and a allele frequencies, summing across backgrounds at the old sex determination factor (i.e., summing haplotypes carrying the original X and Y).
-It is the largest root of this quadratic that determines the spread of the new m allele (see details in \nameref{file:Mathematica}).  
-The second quadratic describes the dynamics of the difference in the m-A and m-a haplotypes between X and Y backgrounds.  
-Asymptotically, this difference is constrained to grow at a rate equal to or less than the sum while the m allele is rare, because the frequencies can never become negative. 
-We therefore focus on the leading eigenvalue based on the root to the first quadratic $f(\lambda_m^{(i)})=(\lambda_m^{(i)})^2+ b \lambda_m^{(i)} + c =0$, as described in the text.  
-Since $f(\Lambda_{mA}^{(i)})$ and $f(\Lambda_{ma}^{(i)})$ are of opposite signs, the leading eigenvalue must fall between these two quantities and is the larger of them when $R = 0$ (the Perron-Frobenius theorem guarantees that the largest eigenvalue is positive, unique, and real).
-Thus, $\lambda_m^{(i)}>1$ if both $\Lambda_{mA}^{(i)}>1$ and $\Lambda_{ma}^{(i)}>1$; similarly, $\lambda_m^{(i)}<1$ if both $\Lambda_{mA}^{(i)}<1$ and $\Lambda_{ma}^{(i)}<1$.
-If only one haplotypic growth rate is greater than one ($\Lambda_{ma}^{(i)}<1<\Lambda_{mA}^{(i)}$ or $\Lambda_{mA}^{(i)}<1<\Lambda_{ma}^{(i)}$), then $\lambda_m^{(i)}$ is greater than one when condition \eqref{eq:lambdasGen} is met.
-Thus, the invasion of a new sex-determining allele is determined by the haplotypic growth rates without accounting for loss due to recombination ($\Lambda_{mj}^{(i)}$ terms) and the rates at which recombination between the $\mathbf{M}$ and $\mathbf{A}$ loci breaks apart these haplotypes ($\chi_{mj}^{(i)}$).
+A rare neo-Y or neo-W allele, $m$, will spread in an XY sex-determining system when the leading eigenvalue, $\lambda_m^{(XY)}$, of the Jacobian matrix derived from the eight mutant recursion equations (given by \ref{eq:recursions}c,d,g,h), evaluated at the ancestral equilibrium, is greater than one.
+However, because a neo-Y (neo-W) is always in males (females) and is epistatically dominant to the ancestral sex-determining locus, the characteristic polynomial factors into two quadratics times $(\lambda_m^{(XY)})^4$.
+One quadratic governs the change in the frequency of the new sex determination factor associated with the $A$ and $a$ allele frequencies, summing across backgrounds at the old sex-determining locus (i.e., summing haplotypes bearing the original X and Y alleles).
+%It is the largest root of this quadratic that determines the spread of the new $m$ allele (see details in \nameref{file:Mathematica}).  
+The second quadratic describes the dynamics of the difference in the $m$-$A$ and $m$-$a$ haplotypes between X and Y backgrounds.  
+Asymptotically, this difference is constrained to grow at a rate equal to or less than the sum while the $m$ allele is rare, because the frequencies can never become negative. 
+We therefore focus on the leading eigenvalue, $\lambda_m^{(XY)}$, which is the largest root of the first quadratic $f(x) = x^2+ b x + c = 0$, as described in the text (details in \nameref{file:Mathematica}).
+
+When $R=0$ the two roots are $\Lambda_{mA}^{(XY)}$ and $\Lambda_{ma}^{(XY)}$, and the leading eigenvalue is the larger of the two.
+When $R>0$ then $f(\Lambda_{mA}^{(XY)})$ and $f(\Lambda_{ma}^{(XY)})$ are of opposite signs, and the leading eigenvalue must fall between these two quantities (details in \nameref{file:Mathematica}).
+%(the Perron-Frobenius theorem guarantees that the largest eigenvalue is positive, unique, and real).
+Thus, $\lambda_m^{(XY)}>1$ if both $\Lambda_{mA}^{(XY)}>1$ and $\Lambda_{ma}^{(XY)}>1$; similarly, $\lambda_m^{(XY)}<1$ if both $\Lambda_{mA}^{(XY)}<1$ and $\Lambda_{ma}^{(XY)}<1$.
+If only one haplotypic growth rate is greater than one ($\Lambda_{ma}^{(XY)}<1<\Lambda_{mA}^{(XY)}$ or $\Lambda_{mA}^{(XY)}<1<\Lambda_{ma}^{(XY)}$), then $\lambda_m^{(XY)}$ is greater than one when condition \eqref{eq:lambdasGen} is met.
+Thus, the invasion of a new sex-determining allele is determined by the haplotypic growth rates ($\Lambda_{mj}^{(XY)}$ terms), which do not account for loss due to recombination, and the rates at which recombination between the $\mathbf{M}$ and $\mathbf{A}$ loci breaks apart these haplotypes ($\chi_{mj}^{(XY)}$).
 For tight linkage between the ancestral sex-determining locus ($\mathbf{X}$) and the selected locus ($\mathbf{A}$) we can calculate these terms explicitly (see below).
-For weak selection we can take a Taylor series of the leading eigenvalue. 
+For weak selection we approximate the leading eigenvalue with a Taylor series. 
 The leading eigenvalue for any $k$ is given up to order $\epsilon^2$ by equation \eqref{eq:lambda_ESD_k}.
@@
 
-Here, we explore the conditions under which a neo-W invades an XY system assuming that the $\mathbf{A}$ locus is initially in tight linkage with the ancestral sex-determining region ($r \approx 0$). 
+Here, we explore the conditions under which a neo-W invades an XY system assuming that the $\mathbf{A}$ locus is initially in tight linkage with the ancestral sex-determining locus ($r \approx 0$). 
 We disregard neo-Y mutations, which never spread given that the ancestral population is at a stable equilibrium (see \nameref{file:Mathematica} for proof).
 
-Starting with the simpler equilibrium $(B)$, the terms of that determine the leading eigenvalue are
+Starting with the simpler $(B)$ equilibrium, the terms that determine the leading eigenvalue are
 
@@
  \frac{\left[  w_{A}^\male (1+\alpha^\male_\Delta) w_{Aa}^\female (1-\alpha^\female_\Delta) \right]}
-{  w_{AA}^\female} \frac{R}{2}
+{  w_{AA}^\female} \frac{R}{2}.
 \end{align}
@@
 
-Haploid selection impacts the spread of neo-W haplotypes in three ways.
+Haploid selection impacts the spread of neo-W haplotypes in three ways (also seen in Table \ref{tab:haplotype_growth}).
 Firstly, the zygotic sex ratio becomes male biased, $\zeta>1/2$, when the $a$ allele (which is fixed on the Y) is favoured during competition among male gametes or by meiotic drive in males.
@@
 Neither haplotype can spread under purely sexually-antagonistic selection at equilibrium $(B)$, with directional selection in each sex.
-Essentially, the X is then already as specialized as possible for the female beneficial allele ($A$ is fixed on the X), and the neo-W often makes daughters with the Y-$a$ haplotype, increasing the flow of $a$ alleles into females, which reduces the fitness of those females.
+Essentially, the X is then already as specialized as possible for the female beneficial allele ($A$ is fixed on the X background), and the neo-W often makes daughters with the Y-$a$ haplotype, increasing the flow of $a$ alleles into females, which reduces the fitness of those females.
 
@@
 A neo-W-$A$ haplotype can spread ($\Lambda_{W'A}^{(XY)}>1$) when $w_{Aa}^\female>w_{AA}^\female$, despite the fact that a neo-W brings Y-$a$ haplotypes into females.
-In this case the $a$ allele is favoured by selection in females despite $A$ being fixed on the X.
+In this case the $a$ allele is favoured by selection in females despite $A$ being fixed on the X background.
 For this equilibrium to be stable (i.e.,  to keep $A$ fixed on the X), X-$a$ cannot be overly favoured in females and X-$A$ must be sufficiently favoured in males (for example, by overdominance in males).
@@
 This can occur with overdominance or directional selection for $a$ in females (Fig \ref{fig:regionplots}B,C).
-In this case, $a$ is favoured on the ancestral Y in males and on the ancestral X in females (comparing $Aa$ to $AA$ genotypes in females) but $A$ is fixed on the X due to selection in males. 
+In this case, $a$ is favoured on the ancestral Y background in males and on the ancestral X background in females (comparing $Aa$ to $AA$ genotypes in females) but $A$ is fixed on the X background due to selection in males.
 The neo-W-$a$ haplotype can spread because it produces females with higher fitness $Aa$ and $aa$ genotypes.
@@
 
-Similar equations can be derived for equilibrium (A) by substituting the equilibrium allele frequencies into Table \ref{tab:haplotype_growth}
+Similar equations can be derived for equilibrium (A) by substituting the equilibrium frequencies into Table \ref{tab:haplotype_growth}
 
@@
 \chi_{W'A}^{(XY)}&= \frac{a}{b} \frac{R}{2} \left[   w_{Aa}^\female (1+\alpha^\female_\Delta) w_a^\male c \right] / w_a^\female\\ 
-\chi_{W'a}^{(XY)}&= \frac{a}{b} \frac{R}{2} \left[ w_{Aa}^\female (1-\alpha^\female_\Delta) w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi \right] / w_A^\female
+\chi_{W'a}^{(XY)}&= \frac{a}{b} \frac{R}{2} \left[ w_{Aa}^\female (1-\alpha^\female_\Delta) w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi \right] / w_A^\female,
 %\Lambda_{W'A}^{(XY)}&=   {\left[ 2 (1 - \zeta) \right]}^{-1} w_A^{\female} \left[ b w_{AA}^\female + c w_{Aa}^\female \left(1 - \alpha^\female_\Delta \right) \right]/ \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\female}_{D} \right)  \\
@@
 %c &= w_{Aa}^\male (1-\alpha^\male_\Delta) \phi \left[ w_{Aa}^\male (1+\alpha^\male_\Delta) \phi \right] + w_{Aa}^\male\phi \left[ 2w_{AA}^\male + w_{aa}^\male (1+\alpha^\male_\Delta) \right] \psi + w_{aa}^\male \psi \left(2w_{AA}^\male \psi \right) \\
-c &= w_{Aa}^\male (1-\alpha^\male_\Delta) \phi + 2w_{aa}^\male \psi
+c &= w_{Aa}^\male (1-\alpha^\male_\Delta) \phi + 2w_{aa}^\male \psi.
 \end{align}
@@
 \begin{equation}\label{eq:BeqWAspread}
-2(w_{Aa}^\female-w_{aa}^\female)w_{aa}^\male \psi^2 > (w_{AA}^\female-w_{Aa}^\female)w_{Aa}^\male \phi (\phi-\psi)
+2(w_{Aa}^\female-w_{aa}^\female)w_{aa}^\male \psi^2 > (w_{AA}^\female-w_{Aa}^\female)w_{Aa}^\male \phi (\phi-\psi),
 \end{equation}
@@
 \begin{equation}\label{eq:BeqWaspread}
-(w_{aa}^\female + w_{Aa}^\female-2w_{AA}^\female)w_{Aa}^\male \phi^2 + (w_{aa}^\female-w_{Aa}^\female)(w_{Aa}^\male+2w_{aa}^\male) \phi \psi >0
+(w_{aa}^\female + w_{Aa}^\female-2w_{AA}^\female)w_{Aa}^\male \phi^2 + (w_{aa}^\female-w_{Aa}^\female)(w_{Aa}^\male+2w_{aa}^\male) \phi \psi >0.
 \end{equation}
@@
 This condition cannot be met with purely sexually antagonistic selection (as both terms on the left-hand side would then be negative), but it can be met under other circumstances. 
-For example, with overdominance in males there is selection for increased $A$ frequencies on X chromosomes in males, which are always paired with Y-$a$ haplotypes.
-Directional selection for $a$ in females can then maintain a polymorphism at the $$\mathbf{A}$$ locus on the X.
-This scenario selects for a modifier that increases recombination between the sex chromosomes (e.g., blue region of Fig 2d in~\cite{Otto2014}) and facilitates the spread of neo-W-$a$ haplotypes, which create females bearing more $a$ alleles than the ancestral X chromosome does.
-
-\subsubsection*{Role of haploid selection with tight linkage between $\mathbf{X}$ and $\mathbf{A}$}
+For example, with overdominance in males there is selection for increased $A$ frequencies on the X background in males, which are always paired with Y-$a$ haplotypes.
+Directional selection for $a$ in females can then maintain a polymorphism at the $\mathbf{A}$ locus on the X background.
+This scenario selects for a modifier that increases recombination between the sex chromosomes (e.g., blue region of Fig 2d in~\cite{Otto2014}) and facilitates the spread of neo-W-$a$ haplotypes, which create females bearing more $a$ alleles than the ancestral X haplotype does.
+
+\subsubsection*{Role of haploid selection with tight linkage between $\mathbf{X}$ and $\mathbf{A}$ loci}
 
@@
 First, haploid selection can allow a polymorphism to be maintained when it would not under diploid selection alone (e.g., with directional selection in diploids). 
-In cases of ploidally-antagonistic selection, where there is a balance between alleles favored in the haploid stage and the diploid stage, neo-W alleles - even unlinked alleles - can spread (\nameref{fig:regionPloidAntag}).
-Second, even when diploid selection could itself maintain a polymorphism, haploid selection can increase the conditions under which transitions among sex chromosomes are possible.
+In cases of ploidally-antagonistic selection, where there is a balance between alleles favored in the haploid stage and the diploid stage, neo-W alleles - even if unlinked to the selected locus - can spread (\nameref{fig:regionPloidAntag}).
+Second, even when diploid selection could itself maintain a polymorphism, haploid selection can increase the conditions under which transitions among sex-determining systems are possible.
 Of particularly importance, when selection is sexually-antagonistic in diploids ($s^\female s^\male <0$ and $0<h^\Hermaphrodite<1$), an unlinked neo-W ($R=1/2$) cannot invade unless there is also haploid selection (see proof in \nameref{file:Mathematica}; Fig \ref{fig:SexAntagTighter} and \nameref{fig:SexAntagTighterMaleDrive}).
-More generally, haploid selection alters the conditions under which neo-W chromosomes can spread (compare \nameref{fig:regionMaleDrive}-\nameref{fig:regionFemaleGS} to Fig \ref{fig:regionplots}).
+More generally, haploid selection alters the conditions under which neo-W alleles can spread (compare \nameref{fig:regionMaleDrive}-\nameref{fig:regionFemaleGS} to Fig \ref{fig:regionplots}).
 
@@
 
-Thus, the impact of haploid selection on sex chromosome transitions must be considered as two sides of a coin: it can generate sex ratio biases that drive sex chromosome transitions to equalize the sex ratio, but it can also drive in new sex chromosomes and thereby cause sex ratios to become biased.
+Thus, the impact of haploid selection on transitions between sex-determining systems must be considered as two sides of a coin: it can generate sex ratio biases that promote transitions that equalize the sex ratio, but it can also direct select for transitions that cause sex ratios to become biased.
 

### 2018-02-05 cover.tex
cover letter

@@
 %findings;why important
-[why this is cool]
+Sex determination is remarkably dynamic.
+The two main theories for why we observe transitions are selection to 1) equalise the sex ratio and 2) increase linkage with a sexually-antagonistic locus. 
+Here we combine and extend these theories with population genetic models that include both haploid and diploid selection while simultaneously allowing for tight linkage.
+We show that both haploid selection and tight linkage can drive previously unexpected transitions between sex-determining systems.
+In particular, both can select for new sex-determining loci that are \textit{less closely linked} to loci under selection. 
+In addition, haploid selection can cause transitions analogous to those caused by purely sexually-antagonistic selection, \textit{eliminating the need for differences in selection between male and female diploids}.
+Further, transitions involving haploid selection can be driven by sex ratio selection or \textit{cause sex ratio biases to evolve}. 
+We conclude that haploid selection should be considered as a pivotal factor driving transitions between sex-determining systems. 
+Our results suggest several new scenarios under which new sex-determining systems are favoured, which could help  explain why the evolution of sex-determining systems is so dynamic, and indicate that new sex-determining alleles can arise at previously unexpected genomic locations.
 \\

### 2018-02-05 cover.tex
updated cover letter

--- 2018-02-04 cover.tex
@@
 \noindent Michael F.\ Scott\\
-Genetics, Evolution \& Environment\\
-University College London Genetics Institute\\
+UCL Genetics Institute\\
+Department of Genetics, Evolution \& Environment\\
+University College London \\
 2nd Floor, Darwin Bldg., Gower St., London, WC1E 6BT, UK\\
@@
 
+In this manuscript, we develop and thoroughly analyse models to show what conditions favour the evolution of new sex-determination systems.
+Evolutionary transitions between sex-determination systems are an active research focus due to the surprising diversity and lability of sex determination systems, which is becoming increasingly apparent (Bachtrog et al.
+2014, \textit{PLoS Biology}).
+Transitions in such a fundamental trait of large effect warrant evolutionary explanation; our results suggest several new scenarios under which new sex-determining systems are favoured, which could help to explain why the evolution of sex-determining systems is so dynamic.
+\\
+
+Previous modelling studies include Muralidhar and Veller (2018, \textit{Nature Ecology and Evolution}), and van Doorn and Kirkpatrick (2007, \textit{Nature}; 2010, \textit{Genetics}), which have shown that a new sex determining allele can be favoured if it arises in linkage with sexually-antagonistic loci.
+One novel feature of our models is that we explicitly consider selection on loci that are very tightly linked to the ancestral sex-determining region.
+Surprisingly, under various forms of selection, the unusual inheritance pattern of sex-linked loci can give rise to cases where the ancestral-X carries suboptimal alleles for females and/or the ancestral-Y carries female-beneficial alleles.
+This, in turn, can favour new sex-determining alleles that have weaker linkage with the loci under selection, which has not been predicted by previous theory. \\
+
+It has been suggested that selection to balance the sex ratio is a dominant force driving transitions between sex-determining systems. 
+Our models include haploid selection (meiotic drive or gametic competition), which can cause zygotic-sex ratios to become biased. 
+In addition, haploid selection is usually sex-specific (occurring in either males or females only). 
+Consequently, we find that haploid selection can cause transitions analogous to those caused by sexually-antagonistic selection, eliminating the need for differences in selection between male and female diploids.
+Unexpectedly, we do not find that selection to balance the sex ratio is overwhelming; transitions during which sex ratio biases increase or decrease are equally likely to evolve under a wide range of conditions.
+Furthermore, we find that looser linkage with the sex-determining region more often evolves when there is haploid selection, increasing the potential for lability in sex-determination. 
+We conclude that haploid selection should be considered as a pivotal factor driving transitions between sex-determining systems. \\
+
+Overall, we have developed an extensive set of models that explore the forces driving transitions between sex determination systems, an important aspect of diversity. 
+Of particular interest, we find several results (e.g., looser linkage and sex ratio biases evolving) that are surprising, given previous theory. 
+%Therefore, our models predict loci in previously unexpected genomic locations and/or experiencing various types of selection (including haploid selection) can now be implicated as drivers of transitions between sex-determining systems.
+We hope you agree that this work is of broad interest to the readership of \textit{PLoS Biology} and we eagerly anticipate your response. \\
+
 %findings;why important
-[why this is cool]
-\\
+%Sex determination is remarkably dynamic.
+%The two main theories for why we observe transitions are selection to 1) equalise the sex ratio and 2) increase linkage with a sexually-antagonistic locus. 
+%Here we combine and extend these theories with population genetic models that include both haploid and diploid selection while simultaneously allowing for tight linkage.
+%We show that both haploid selection and tight linkage can drive previously unexpected transitions between sex-determining systems.
+%In particular, both can select for new sex-determining loci that are \textit{less closely linked} to loci under selection. 
+%In addition, haploid selection can cause transitions analogous to those caused by purely sexually-antagonistic selection, \textit{eliminating the need for differences in selection between male and female diploids}.
+%Further, transitions involving haploid selection can be driven by sex ratio selection or \textit{cause sex ratio biases to evolve}. 
+%We conclude that haploid selection should be considered as a pivotal factor driving transitions between sex-determining systems. 
+%Our results suggest several new scenarios under which new sex-determining systems are favoured, which could help  explain why the evolution of sex-determining systems is so dynamic, and indicate that new sex-determining alleles can arise at previously unexpected genomic locations.
+%\\
 
@@
 
-We hope you agree that this work is of broad interest to the readership of \textit{PLoS Biology} and we eagerly anticipate your response.\\
+%We hope you agree that this work is of broad interest to the readership of \textit{PLoS Biology} and we eagerly anticipate your response.\\
 
-Sincerely,
-
-[signature]\\
-%\includegraphics[height=1.5cm]{IMAGES/OsmondSignature.pdf}
+Sincerely, \\
+\newline
+\\
 \indent Michael Scott, Matthew Osmond, Sarah Otto

### 2018-02-05 LaTeX/Turnover_plos.tex
remove funding acknowledgements to match journal style
Charnov-Bull effects

@@
 Here, we do not assume that the environmental conditions that determine sex also differentially affect the fitness of males versus females. 
-Such correlations can favour environmental sex-determining systems that allow each sex to be produced in the environment in which it has highest fitness; in the absence of these correlations, previous theory would predict that ESD is favoured when it produces more equal sex ratios than the ancestral system (see reviews by~\cite{Charnov:1982wg,Bull:1983vi,West:2009we}).
+Such correlations (`Charnov-Bull effects') can favour environmental sex-determining systems by allowing each sex to be produced in the environment in which it has highest fitness; in the absence of these correlations, previous theory would predict that ESD is favoured when it produces more equal sex ratios than the ancestral system (see reviews by~\cite{Charnov:1982wg,Bull:1983vi,West:2009we}).
 %(e.g., maternal condition, mate quality, age, or host size)
@@
 
-\section*{Acknowledgments}
-This project was supported by the Natural Sciences and Engineering Research Council of Canada (CGS-D 6564 to MMO; RGPIN-2016-03711 to SPO).
+%\section*{Acknowledgments}
+%This project was supported by the Natural Sciences and Engineering Research Council of Canada (CGS-D 6564 to MMO; RGPIN-2016-03711 to SPO).
 

### 2018-02-05 LaTeX/Turnover_plos.tex
superscript (XY) description added

@@
 On the other hand, sex ratios can also become biased by linkage between the sex-determining locus and a locus that harbours genetic variation in haploid fitness. 
-For example, there are several known cases of sex ratio bias caused by sex-linked meiotic drive alleles (Burt, 2006, Chapter 6~\cite{Burt:2006}) or selection among X- and Y-bearing pollen~\cite{Lloyd:1974tz,Conn:1981uw,Stehlik:2005ul,Stehlik:2006to,Field:2012fd,Field:2013cc}.
+For example, there are several known cases of sex ratio bias caused by sex-linked meiotic drive alleles (Burt and Trivers, 2006, Chapter 6~\cite{Burt:2006}) or selection among X- and Y-bearing pollen~\cite{Lloyd:1974tz,Conn:1981uw,Stehlik:2005ul,Stehlik:2006to,Field:2012fd,Field:2013cc}.
 It is not immediately clear how the spread of new sex-determining systems would be influenced by the combination of sex ratio biases and associations with haploid selected alleles.
@@
 We find that loci tightly linked with the sex-determining locus can drive transitions in which the heterogametic sex changes, even when the new sex-determining locus is less closely linked to loci under selection (either including haploid selection or not).
-
-%Lorem ipsum dolor sit~\cite{bib1} amet, consectetur adipiscing elit.
-Curabitur eget porta erat.
-Morbi consectetur est vel gravida pretium.
-Suspendisse ut dui eu ante cursus gravida non sed sem.
-Nullam Eq~(\ref{eq:schemeP}) sapien tellus, commodo id velit id, eleifend volutpat quam.
-Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus.
-Nunc pellentesque pretium diam, quis maximus dolor faucibus id.~\cite{bib2} Nunc convallis sodales ante, ut ullamcorper est egestas vitae.
-Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.
-
-%\begin{eqnarray}
-%\label{eq:schemeP}
-%	\mathrm{P_Y} = \underbrace{H(Y_n) - H(Y_n|\mathbf{V}^{Y}_{n})}_{S_Y} + \underbrace{H(Y_n|\mathbf{V}^{Y}_{n})- H(Y_n|\mathbf{V}^{X,Y}_{n})}_{T_{X\rightarrow Y}},
-%\end{eqnarray}
 
@@
 The model outlined above describes both ancestral XY and ZW sex-determining systems. %if we relabel the two sexes as being ancestrally `heterogametic' or ancestrally `homogametic'. 
-Without loss of generality, we primarily refer to the ancestrally heterogametic sex as male and the ancestrally homogametic sex as female.
-That is, we describe an ancestral XY sex-determining system but our model is equally applicable to an ancestral ZW sex-determining system (relabelling the ancestrally heterogametic sex as female and the ancestrally homogametic sex as male and switching the labels of males and females throughout).
+Without loss of generality, we refer to the ancestrally heterogametic sex as male and the ancestrally homogametic sex as female.
+That is, we primarily describe an ancestral XY sex-determining system but our model is equally applicable to an ancestral ZW sex-determining system (relabelling the ancestrally heterogametic sex as female and the ancestrally homogametic sex as male and switching the labels of males and females throughout).
+We use a superscript to specify the ancestral sex-determining system described, e.g., $^{(XY)}$ for ancestral XY sex-determination.
 
@@
 %However, to leading order with selection weak relative to recombination, we find that sex ratio selection favours the spread of a neo-W (through the first terms in table \ref{tab:haplotype_growth}) by an amount that is equal in magnitude to the fitness effects of alleles associated with new sex-determining alleles (second terms in table \ref{tab:haplotype_growth}).
-However, invasion by a neo-W allele into an XY system and invasion by a neo-Y allele into a ZW system occur under the same conditions ($\lambda_{Y'}^{(XY)} = \lambda_{W'}^{(XY)}$ and $\lambda_{Y'}^{(XY)}=\lambda_{W'}^{(XY)}$, at least to order $\epsilon^2$).
+However, invasion by a neo-W allele into an XY system and invasion by a neo-Y allele into a ZW system occur under the same conditions ($\lambda_{Y'}^{(XY)} = \lambda_{W'}^{(ZW)}$ and $\lambda_{W'}^{(XY)}=\lambda_{Y'}^{(ZW)}$, at least to order $\epsilon^2$).
 For example, in Fig \ref{fig:SexRatioBad}A neo-W alleles invade an ancestral-XY system where females are initially rare, equalizing the sex ratio.
@@
 Here, we do not assume that the environmental conditions that determine sex also differentially affect the fitness of males versus females. 
-Such correlations (`Charnov-Bull effects') can favour environmental sex-determining systems by allowing each sex to be produced in the environment in which it has highest fitness; in the absence of these correlations, previous theory would predict that ESD is favoured when it produces more equal sex ratios than the ancestral system (see reviews by~\cite{Charnov:1982wg,Bull:1983vi,West:2009we}).
+Such correlations can favour environmental sex-determining systems by allowing each sex to be produced in the environment in which it has highest fitness; in the absence of these correlations, previous theory would predict that ESD is favoured when it produces more equal sex ratios than the ancestral system (see reviews by~\cite{Charnov:1982wg,Bull:1983vi,West:2009we}).
 %(e.g., maternal condition, mate quality, age, or host size)

### 2018-02-06 LaTeX/Turnover_plos.tex
trying to get figures into online system

@@
 Within several taxa, the chromosome that harbours the master sex-determining locus changes. 
-For example, transitions of the master sex-determining locus between chromosomes or the evolution of new master sex-determining loci (where the heterogametic sex does not change, hereafter `cis-GSD transitions') have occurred in Salmonids~\cite{Li:2011fm,Yano:2012di}, Diptera~\cite{Vicoso:2015hf}, and \textit{Oryzias}~\cite{Myosho:2012fv}.
+For example, transitions of the master sex-determining locus between chromosomes or the evolution of new master sex-determining loci where the heterogametic sex does not change (hereafter `cis-GSD transitions') have occurred in Salmonids~\cite{Li:2011fm,Yano:2012di}, Diptera~\cite{Vicoso:2015hf}, and \textit{Oryzias}~\cite{Myosho:2012fv}.
 %Presentation at evolution found neo sex chromosome in birds, doesn't seem to be published or bioRxiv yet (consider pers com.), title: A previously unknown neo-sex chromosome mediates plumage divergence and speciation in hybridizing birds Jason Sardell; Elizabeth Cooper; J.
@@
 
-When only one neo-W haplotype has growth rate greater than one (see Fig \ref{fig:regionplots}), a neo-W allele can invade as long as equation \eqref{eq:lambdasGen} is satisfied, which may require that the recombination rate, $R$, is small enough.
+When only one neo-W haplotype has growth rate greater than one (see Fig \ref{fig:regionplots}), a neo-W allele can invade as long as Eq \eqref{eq:lambdasGen} is satisfied, which may require that the recombination rate, $R$, is small enough.
 Nevertheless, because we assume here that $r$ is small, these results indicate that a more loosely linked sex-determining region ($r<R$) can spread.
@@
 %The new sex-determining allele, $m$, will spread in an XY system if $\lambda_{m}^{(XY)}>1$. 
-Equation \eqref{eq:lambda_neoY} demonstrates that, under weak selection, a neo-Y allele will invade an XY system ($\lambda_{Y'}^{(XY)}>1$) if and only if it is more closely linked to the selected locus than the ancestral sex-determining locus (i.e., if $R<r$; note that $V_{A}S_{A}^2$ is strictly positive as long as $\mathbf{A}$ is polymorphic).
+Eq \eqref{eq:lambda_neoY} demonstrates that, under weak selection, a neo-Y allele will invade an XY system ($\lambda_{Y'}^{(XY)}>1$) if and only if it is more closely linked to the selected locus than the ancestral sex-determining locus (i.e., if $R<r$; note that $V_{A}S_{A}^2$ is strictly positive as long as $\mathbf{A}$ is polymorphic).
 This echoes our results above where a neo-Y could never invade if $r\approx0$. 
@@
 For example, if the $\mathbf{A}$ locus is unlinked to the ancestral sex-determining locus ($r=1/2$), a more closely linked neo-W ($R<1/2$) can always invade.
-In this case, there is no ancestral association between $\mathbf{A}$ alleles and sex chromosomes in males, $\left( \hat{p}^\male_Y-\hat{p}^\male_X \right)=0$, see equation \eqref{eq:freq_diffs}. 
-The second term in equation \eqref{eq:lambda_neoW} therefore disappears and invasion depends only on the sign of $(r-R)$.%, as in the case of the neo-Y.
+In this case, there is no ancestral association between $\mathbf{A}$ alleles and sex chromosomes in males, $\left( \hat{p}^\male_Y-\hat{p}^\male_X \right)=0$, see Eq \eqref{eq:freq_diffs}. 
+The second term in Eq \eqref{eq:lambda_neoW} therefore disappears and invasion depends only on the sign of $(r-R)$.%, as in the case of the neo-Y.
 
@@
 
-However, with haploid selection and $r<1/2$, the additional term in equation \eqref{eq:lambda_neoW} can be positive.
+However, with haploid selection and $r<1/2$, the additional term in Eq \eqref{eq:lambda_neoW} can be positive.
 This can allow neo-W invasion ($\lambda_{W'}^{(XY)}>1$), even when the new sex-determining locus is less closely linked to the selected locus ($R>r$). 
@@
 %Mean diploid fitness therefore decreases during heterogametic transitions that create looser sex-linkage (Fig \ref{fig:Combination_MeanFit}B,D). 
-%Equation \eqref{eq:lambda_neoW} shows that, with weak selection, neo-W alleles can invade an XY system for a large number of selective regimes. 
+%Eq \eqref{eq:lambda_neoW} shows that, with weak selection, neo-W alleles can invade an XY system for a large number of selective regimes. 
 %To clarify the parameter space under which $\lambda_{W'}^{(XY)}>1$ , we consider several special cases. 
-%Firstly, if the $\mathbf{A}$ locus is unlinked to the ancestral sex-determining region ($r=1/2$), a more closely linked neo-W ($R<1/2$) can always invade because there is no ancestral association between $A$ alleles and sex chromosomes in males, $\left( \hat{p}^\male_Y-\hat{p}^\male_X \right)=0$, see equation \eqref{eq:freq_diffs}.
-%The second term in equation \eqref{eq:lambda_neoW} therefore disappears and invasion depends only on the sign of $(r-R)$, as in the case of the neo-Y. 
+%Firstly, if the $\mathbf{A}$ locus is unlinked to the ancestral sex-determining region ($r=1/2$), a more closely linked neo-W ($R<1/2$) can always invade because there is no ancestral association between $A$ alleles and sex chromosomes in males, $\left( \hat{p}^\male_Y-\hat{p}^\male_X \right)=0$, see Eq \eqref{eq:freq_diffs}.
+%The second term in Eq \eqref{eq:lambda_neoW} therefore disappears and invasion depends only on the sign of $(r-R)$, as in the case of the neo-Y. 
 %Indeed, invasion typically occurs when the neo-W is more closely linked to the selected locus than the ancestral sex-determining region (Fig \ref{fig:Combination_Centimorgans}).
@@
 preventing associations from building up between alleles at locus $\mathbf{A}$ and sex. 
-Equation \eqref{eq:lambda_ESD} shows that the ESD mutation gets half of the fitness of a feminizing mutation (neo-W) and half of the fitness of a masculinizing mutation (neo-Y), but only has an effect one half of the time (the other half of the time it produces the same sex as the ancestral system would have).
+Eq \eqref{eq:lambda_ESD} shows that the ESD mutation gets half of the fitness of a feminizing mutation (neo-W) and half of the fitness of a masculinizing mutation (neo-Y), but only has an effect one half of the time (the other half of the time it produces the same sex as the ancestral system would have).
 As discussed above, $\lambda_{Y'\rvert R=1/2}^{(XY)}$ is necessarily less than one, but $\lambda_{W'\rvert R=1/2}^{(XY)}$ can be greater than one if there is haploid selection.
@@
 
-%An important result from equation \eqref{eq:lambda_ESD} is that ESD can invade if there is haploid selection. 
+%An important result from Eq \eqref{eq:lambda_ESD} is that ESD can invade if there is haploid selection. 
 %When evaluated at $R=1/2$, $\Lambda_{Y',XY}$ is necessarily less than one, but $\Lambda_{W',XY}$ can be greater than one if there is haploid selection, as discussed above. 
@@
 
-Significantly, equation \eqref{eq:lambda_ESD} is the same whether ESD is invading an ancestrally XY or ZW system (because $\lambda_{Y'}^{(XY)} = \lambda_{W'}^{(ZW)}$ and $\lambda_{W'}^{(XY)} = \lambda_{Y'}^{(ZW)}$).
+Significantly, Eq \eqref{eq:lambda_ESD} is the same whether ESD is invading an ancestrally XY or ZW system (because $\lambda_{Y'}^{(XY)} = \lambda_{W'}^{(ZW)}$ and $\lambda_{W'}^{(XY)} = \lambda_{Y'}^{(ZW)}$).
 Thus, Fisherian sex ratio selection alone does not easily explain GSD to ESD transitions.
@@
 That is, Y-$a$ haplotypes must have higher fitness than Y-$A$ haplotypes.  
-Substituting in $\hat{p}_X^\female$ from equation \eqref{eq:tightequil}, fixation of the $a$ allele on the Y background requires that $\gamma_{i}>0$ where $\gamma_{(A)}=w_{a}^{\male} \big[ (1-\alpha^\male_\Delta) w_{Aa}^{\male} \phi + w_{aa}^{\male} \psi \big]-w_{A}^{\male} \big[ w_{AA}^{\male} \phi + (1 + \alpha^{\male}_\Delta)w_{Aa}^{\male} \psi \big]$ for equilibrium $(A)$ and $\gamma_{(B)}=(1-\alpha^{\male}_\Delta)w_{a}^{\male}w_{Aa}^{\male}-w_{A}^{\male}w_{AA}^{\male}$ for equilibrium $(B)$.
+Substituting in $\hat{p}_X^\female$ from Eq \eqref{eq:tightequil}, fixation of the $a$ allele on the Y background requires that $\gamma_{i}>0$ where $\gamma_{(A)}=w_{a}^{\male} \big[ (1-\alpha^\male_\Delta) w_{Aa}^{\male} \phi + w_{aa}^{\male} \psi \big]-w_{A}^{\male} \big[ w_{AA}^{\male} \phi + (1 + \alpha^{\male}_\Delta)w_{Aa}^{\male} \psi \big]$ for equilibrium $(A)$ and $\gamma_{(B)}=(1-\alpha^{\male}_\Delta)w_{a}^{\male}w_{Aa}^{\male}-w_{A}^{\male}w_{AA}^{\male}$ for equilibrium $(B)$.
 Stability of a polymorphism on the X background (equilibrium $(A)$) further requires that $\phi >0$ and $\psi >0$. 
@@
 For weak selection we approximate the leading eigenvalue with a Taylor series. 
-The leading eigenvalue for any $k$ is given up to order $\epsilon^2$ by equation \eqref{eq:lambda_ESD_k}.
+The leading eigenvalue for any $k$ is given up to order $\epsilon^2$ by Eq \eqref{eq:lambda_ESD_k}.
 
@@
 Thirdly, haploid selection in males affects the diploid genotypes of females by altering the allele frequencies in the male gametes with which female gametes pair.
-At equlibrium $(B)$, neo-W female gametes will mate with X-$A$ male gametes with probability $ w_A^\male (1+\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$ and Y-$a$ male gametes with probability $w_a^\male (1-\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$, where the $2\bar{w}_{H}^\male$ terms have been canceled in equation \eqref{Binvasion} (as mentioned above).
+At equlibrium $(B)$, neo-W female gametes will mate with X-$A$ male gametes with probability $ w_A^\male (1+\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$ and Y-$a$ male gametes with probability $w_a^\male (1-\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$, where the $2\bar{w}_{H}^\male$ terms have been canceled in Eq \eqref{Binvasion} (as mentioned above).
 Thus, neo-W-$A$ haplotypes are found in $AA$ female diploids with probability $ w_A^\male (1+\alpha^\male_\Delta)/ (2\bar{w}_{H}^\male)$ (e.g., first term in square brackets in the numerator of equation \ref{Binvasion}a) and in $Aa$ female diploids with probability $w_a^\male (1-\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$ (e.g., the second term in square brackets in the numerator of equation \ref{Binvasion}a).
@@
 %Haploid selection affects the conclusions outlined above by altering the zygotic sex ratio and exerting direct selection on neo-W haplotypes.
-%The effect of sex ratio selection is straightforward and can be seen in equation \eqref{Binvasion}, where male drive and gamete competition for $a$ (which is fixed on the Y and therefore causes a male bias) increases all four terms.
-%Direct selection on neo-W haplotypes can also be seen in equation \eqref{Binvasion} by noticing that increasing female drive in favour of $A$ increases the neo-W-$A$ haplotype growth rate ($\Lambda_{mA}$) while female drive and gamete competition in favour of $a$ increases the neo-W-$a$ haplotype growth rate ($\Lambda_{ma}$).
+%The effect of sex ratio selection is straightforward and can be seen in Eq \eqref{Binvasion}, where male drive and gamete competition for $a$ (which is fixed on the Y and therefore causes a male bias) increases all four terms.
+%Direct selection on neo-W haplotypes can also be seen in Eq \eqref{Binvasion} by noticing that increasing female drive in favour of $A$ increases the neo-W-$A$ haplotype growth rate ($\Lambda_{mA}$) while female drive and gamete competition in favour of $a$ increases the neo-W-$a$ haplotype growth rate ($\Lambda_{ma}$).
 %Gamete competition in females does not impact the spread of neo-W-$A$ haplotypes because they are on the same background as the resident X.

### 2018-02-06 cover.tex
trying to get figures into online system

@@
 Please find the attached manuscript, entitled ``Haploid selection, sex ratio bias, and transitions between sex-determination systems'', which we submit to you for consideration for publication in \textit{PLoS Biology}.
+Laurence Hurst and Nick Barton would be well qualified Academic Editors for this manuscript.
 \\
@@
 
-Previous modelling studies include Muralidhar and Veller (2018, \textit{Nature Ecology and Evolution}), and van Doorn and Kirkpatrick (2007, \textit{Nature}; 2010, \textit{Genetics}), which have shown that a new sex determining allele can be favoured if it arises in linkage with sexually-antagonistic loci.
-One novel feature of our models is that we explicitly consider selection on loci that are very tightly linked to the ancestral sex-determining region.
-Surprisingly, under various forms of selection, the unusual inheritance pattern of sex-linked loci can give rise to cases where the ancestral-X carries suboptimal alleles for females and/or the ancestral-Y carries female-beneficial alleles.
-This, in turn, can favour new sex-determining alleles that have weaker linkage with the loci under selection, which has not been predicted by previous theory. \\
+Previous modelling studies, including Muralidhar and Veller (2018, \textit{Nature Ecology and Evolution}) and van Doorn and Kirkpatrick (2007, Nature; 2010, Genetics), have shown that a new sex determining allele can spread if it is more tightly linked to a sexually-antagonistic locus.
+Our work finds several surprising results in light of previous results.
+First, when the old sex determining allele is already tightly linked to a sexually-antagonistic locus, more loosely linked sex determining factors can invade under some circumstances, offering a new potential explanation for sex chromosome turnover.
+Second, when we include selection in the haploid phase (among gametes or gametophytes, including meiotic drive), entirely new predictions are generated for the spread of new sex determining factors.
+In particular, selective differences between male and female diploids are no longer necessary;  conflicts between haploid and diploid selection can instead drive the invasion of new sex chromosomes.
+Interestingly, new sex chromosomes can spread under conditions where they balance the sex ratio but also under conditions where they lead to more skewed sex ratios.
+Indeed, transitions during which sex ratio biases increase or decrease are equally likely to evolve under a wide range of conditions.
+We conclude that haploid selection should be considered as a pivotal factor driving transitions between sex-determining systems.
+\\
 
-It has been suggested that selection to balance the sex ratio is a dominant force driving transitions between sex-determining systems. 
-Our models include haploid selection (meiotic drive or gametic competition), which can cause zygotic-sex ratios to become biased. 
-In addition, haploid selection is usually sex-specific (occurring in either males or females only). 
-Consequently, we find that haploid selection can cause transitions analogous to those caused by sexually-antagonistic selection, eliminating the need for differences in selection between male and female diploids.
-Unexpectedly, we do not find that selection to balance the sex ratio is overwhelming; transitions during which sex ratio biases increase or decrease are equally likely to evolve under a wide range of conditions.
-Furthermore, we find that looser linkage with the sex-determining region more often evolves when there is haploid selection, increasing the potential for lability in sex-determination. 
-We conclude that haploid selection should be considered as a pivotal factor driving transitions between sex-determining systems. \\
+%Previous modelling studies include Muralidhar and Veller (2018, \textit{Nature Ecology and Evolution}), and van Doorn and Kirkpatrick (2007, \textit{Nature}; 2010, \textit{Genetics}), which have shown that a new sex determining allele can be favoured if it arises in linkage with sexually-antagonistic loci.
+%One novel feature of our models is that we explicitly consider selection on loci that are very tightly linked to the ancestral sex-determining region.
+%Surprisingly, under various forms of selection, the unusual inheritance pattern of sex-linked loci can give rise to cases where the ancestral-X carries suboptimal alleles for females and/or the ancestral-Y carries female-beneficial alleles.
+%This, in turn, can favour new sex-determining alleles that have weaker linkage with the loci under selection, which has not been predicted by previous theory. \\
+
+%It has been suggested that selection to balance the sex ratio is a dominant force driving transitions between sex-determining systems. 
+%Our models include haploid selection (meiotic drive or gametic competition), which can cause zygotic-sex ratios to become biased. 
+%In addition, haploid selection is usually sex-specific (occurring in either males or females only). 
+%Consequently, we find that haploid selection can cause transitions analogous to those caused by sexually-antagonistic selection, eliminating the need for differences in selection between male and female diploids.
+%Unexpectedly, we do not find that selection to balance the sex ratio is overwhelming; transitions during which sex ratio biases increase or decrease are equally likely to evolve under a wide range of conditions.
+%Furthermore, we find that looser linkage with the sex-determining region more often evolves when there is haploid selection, increasing the potential for lability in sex-determination. 
+%We conclude that haploid selection should be considered as a pivotal factor driving transitions between sex-determining systems. \\
 

### 2018-02-07 LaTeX/S1Appendix.tex
moved appendices out of main text but can crossref

--- 2018-02-06 LaTeX/Turnover_plos.tex
@@
-% Template for PLoS
-% Version 3.4 January 2017
-%
-% % % % % % % % % % % % % % % % % % % % % %
-%
-% -- IMPORTANT NOTE
-%
-% This template contains comments intended 
-% to minimize problems and delays during our production 
-% process. Please follow the template instructions
-% whenever possible.
-%
-% % % % % % % % % % % % % % % % % % % % % % % 
-%
-% Once your paper is accepted for publication, 
-% PLEASE REMOVE ALL TRACKED CHANGES in this file 
-% and leave only the final text of your manuscript. 
-% PLOS recommends the use of latexdiff to track changes during review, as this will help to maintain a clean tex file.
-% Visit https://www.ctan.org/pkg/latexdiff?lang=en for info or contact us at latex@plos.org.
-%
-%
-% There are no restrictions on package use within the LaTeX files except that 
-% no packages listed in the template may be deleted.
-%
-% Please do not include colors or graphics in the text.
-%
-% The manuscript LaTeX source should be contained within a single file (do not use \input, \externaldocument, or similar commands).
-%
-% % % % % % % % % % % % % % % % % % % % % % %
-%
-% -- FIGURES AND TABLES
-%
-% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
-%
-% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
-% - Figs should be uploaded separately from your manuscript file. 
-% - Figs generated using LaTeX should be extracted and removed from the PDF before submission. 
-% - Figs containing multiple panels/subfigures must be combined into one image file before submission.
-% For figure citations, please use "Fig" instead of "Figure".
-% See http://journals.plos.org/plosone/s/figures for PLOS figure guidelines.
-%
-% Tables should be cell-based and may not contain:
-% - spacing/line breaks within cells to alter layout or alignment
-% - do not nest tabular environments (no tabular environments within tabular environments)
-% - no graphics or colored text (cell background color/shading OK)
-% See http://journals.plos.org/plosone/s/tables for table guidelines.
-%
-% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
-%
-% % % % % % % % % % % % % % % % % % % % % % % %
-%
-% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
-%
-% IMPORTANT
-% Below are a few tips to help format your equations and other special characters according to our specifications.
-For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://journals.plos.org/plosone/s/latex
-%
-% For inline equations, please be sure to include all portions of an equation in the math environment.
-For example, x$^2$ is incorrect; this should be formatted as $x^2$ (or $\mathrm{x}^2$ if the romanized font is desired).
-%
-% Do not include text that is not math in the math environment. For example, CO2 should be written as CO\textsubscript{2} instead of CO$_2$.
-%
-% Please add line breaks to long display equations when possible in order to fit size of the column. 
-%
-% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
-%
-% When adding superscript or subscripts outside of brackets/braces, please group using {}.  For example, change "[U(D,E,\gamma)]^2" to "{[U(D,E,\gamma)]}^2". 
-%
-% Do not use \cal for caligraphic font.  Instead, use \mathcal{}
-%
-% % % % % % % % % % % % % % % % % % % % % % % % 
-%
-% Please contact latex@plos.org with any questions.
-%
-% % % % % % % % % % % % % % % % % % % % % % % %
-
 \documentclass[10pt,letterpaper]{article}
@@
 
+%reference equations in appendices
+\usepackage{xr}
+\externaldocument{main}
+\externaldocument{S2Appendix}
+\externaldocument{S3Appendix}
+
 %% END MACROS SECTION
@@
 \vspace*{0.2in}
-
-% Title must be 250 characters or less.
-\begin{flushleft}
-{\Large
-\textbf\newline{Haploid selection, sex ratio bias, and transitions between sex-determining systems} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
-}
-\newline
-% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
-\\
-Michael Francis Scott\textsuperscript{1\Yinyang*},
-Matthew Miles Osmond\textsuperscript{2\Yinyang},
-Sarah Perin Otto\textsuperscript{2}
-\\
-\bigskip
-\textbf{1} UCL Genetics Institute, Department of Genetics, Evolution and Environment, University College London, Gower Street, London WC1E 6BT 
-\\
-\textbf{2} Department of Zoology, University of British Columbia, \#4200 - 6270 University Boulevard, Vancouver, BC, Canada V6T 1Z4
-\\
-\bigskip
-
-% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
-% 
-% Remove or comment out the author notes below if they aren't used.
-%
-% Primary Equal Contribution Note
-\Yinyang These authors contributed equally to this work.
-
-% Additional Equal Contribution Note
-% Also use this double-dagger symbol for special authorship notes, such as senior authorship.
-%\ddag These authors also contributed equally to this work.
-
-% Current address notes
-%\textcurrency Current Address: Dept/Program/Center, Institution Name, City, State, Country % change symbol to "\textcurrency a" if more than one current address note
-% \textcurrency b Insert second current address 
-% \textcurrency c Insert third current address
-
-% Deceased author note
-%\dag Deceased
-
-% Group/Consortium Author Note
-%\textpilcrow Membership list can be found in the Acknowledgments section.
-
-% Use the asterisk to denote corresponding authorship and provide email address in note below.
-* m.f.scott@ucl.ac.uk
-
-\end{flushleft}
-% Please keep the abstract below 300 words
-%currently 312 words
-\section*{Abstract}
-Sex determination is remarkably dynamic; many taxa display shifts in the location of sex-determining loci or the evolution of entirely new sex-determining systems. 
-Predominant theories for why we observe such transitions generally conclude that novel sex-determining systems are favoured by selection if they equalise the sex ratio or increase linkage with a sexually-antagonistic locus.
-We use population genetic models to extend these theories in two ways: 
-(1) We explicitly consider selection on loci very tightly linked to the ancestral sex-determining loci, e.g., within the non-recombining region of the ancestral sex chromosomes. 
-Variation at such loci can favour the spread of new sex-determining systems in which the heterogametic sex changes (XY to ZW or ZW to XY) and the new sex-determining region is less closely linked (or unlinked) to the locus under selection, which is not predicted by previous theory.
-(2) We also consider selection upon haploid genotypes either during gametic competition (e.g., pollen/sperm competition) or meiosis (i.e., non-Mendelian segregation), selective processes that typically occur in one sex or the other.
-We find that associations with haploid selected loci can drive transitions between sex-determining systems, without requiring sexually-antagonistic selection in diploids. 
-Unexpectedly, with haploid selection, transitions between male and female heterogamety can also evolve where linkage with the sex-determining locus is weakened. 
-Furthermore, haploid selection in the heterogametic sex can cause sex ratio biases, which may increase or decrease with the spread of new sex chromosomes. 
-Thus, we find that transitions between sex-determining systems cannot be simply predicted by selection to equalise the sex ratio. 
-Overall, our models reveal that transitions between sex-determining systems, particularly transitions where the heterogametic sex changes, can be driven by loci in previously unpredicted genomic locations that experience selection during diploid and/or haploid phases.
-These results predict conditions under which sex-determining systems are likely to be labile and draw novel connections with sex ratio evolution.
-
-% Please keep the Author Summary between 150 and 200 words
-% Use first person. PLOS ONE authors please skip this step. 
-% Author Summary not valid for PLOS ONE submissions.   
-%currently 193 words
-\section*{Author summary}
-Accumulating evidence indicates that systems of sex determination are strikingly diverse and labile in many clades. 
-This poses the question: what drives transitions between sex-determining systems? 
-Here, we use models to derive conditions under which new sex-determining systems spread. 
-Prevailing views suggest that new sex-determining systems are favoured when they equalize the sex ratio and/or when they are more closely linked to genes that experience differential selection in males and females.
-Our models extends these theories to include selection upon haploid genotypes (meiotic drive or gametic competition), which causes sex ratio biases and occurs differently in males and females. 
-Surprisingly, we find that neither force (sex ratio selection nor associations with genes that have sex-specific effects) dominates the spread of new sex-determining systems alone. 
-Even more unexpectedly, we find that, to spread, new sex-determining alleles do not necessarily have to arise in closer linkage with genes that are differentially selected in males and females. 
-Therefore, our models predict loci in previously unexpected genomic locations and/or experiencing various types of selection (including haploid selection) can now be implicated as drivers of transitions between sex-determining systems.
-
-\linenumbers
-
-% Use "Eq" instead of "Equation" for equation citations.
-\section*{Introduction}
-
-Animals and angiosperms exhibit extremely diverse sex-determining systems (reviewed in~\cite{Bull:1983vi,Charlesworth:2010it,Beukeboom:2014vb,Bachtrog:2014bx}). 
-Among species with genetic sex determination (GSD) of diploid sexes, some taxa have heterogametic males (XY) and homogametic females (XX), including %non-monotreme?
-I think monotremes have XY but tonnes of translocations, giving: X1,X2...X6 Y1
-mammals and most dioecious plants~\cite{Ming:2011iy}; whereas other taxa have homogametic males (ZZ) and heterogametic females (ZW), including Lepidoptera and birds. 
-Within several taxa, the chromosome that harbours the master sex-determining locus changes. 
-For example, transitions of the master sex-determining locus between chromosomes or the evolution of new master sex-determining loci where the heterogametic sex does not change (hereafter `cis-GSD transitions') have occurred in Salmonids~\cite{Li:2011fm,Yano:2012di}, Diptera~\cite{Vicoso:2015hf}, and \textit{Oryzias}~\cite{Myosho:2012fv}.
-%Presentation at evolution found neo sex chromosome in birds, doesn't seem to be published or bioRxiv yet (consider pers com.), title: A previously unknown neo-sex chromosome mediates plumage divergence and speciation in hybridizing birds Jason Sardell; Elizabeth Cooper; J.
-Albert C.
-Uy.
-I wonder if this is actually a fusion event though?
-In addition, many clades exhibit transitions between male and female heterogamety (XY$\leftrightarrow$ZW, hereafter `trans-GSD transitions'), including snakes~\cite{Gamble2017}, lizards~\cite{Ezaz:2009tk}, eight of 26 teleost fish families~\cite{Mank:2006bt}, true fruit flies (Tephritids,~\cite{Vicoso:2015hf}, amphibians~\cite{Hillis:1990gu}, the angiosperm genus \textit{Silene}~\cite{Slancarova:2013dq}, the angiosperm family \textit{Salicaceae}~\cite{Pucholt2015,Pucholt2017} and Coleoptera and Hemiptera (plate 2~\cite{Beukeboom:2014vb}).
-Indeed, in some cases, both male and female heterogametic sex-determining systems can be found in the same species, as reported in houseflies~\cite{Macdonald1978}, midges~\cite{Thompson1971}, frogs~\cite{Ogata:2007jm}, cichlid fish~\cite{Ser:2010iq}, tilapia~\cite{Lee2004}, sea bass~\cite{Vandeputte2007}, and lab-strains of Zebrafish~\cite{Liew2012,Wilson2014}.
-In addition, multiple transitions have occurred between genetic and environmental sex-determining systems (GSD$\leftrightarrow$ESD), e.g., in reptiles and fishes~\cite{Conover:1987in,Mank:2006bt,Pokorna:2009ui,Ezaz:2009tk,Pen:2010kk,Holleley:2015hc}.
-
-Predominant theories accounting for the spread of new sex-determining systems by selection involve fitness differences between sexes (e.g., sexually antagonistic selection) or sex ratio selection~\cite{Blaser2012, Beukeboom:2014vb,vanDoorn2014re}.
-%\citet{Bull:1977wt} shows that direct selection on new sex determination loci can allow them to spread and switch between male and female heterogamety. 
-van Doorn and Kirkpatrick~\cite{vanDoorn:2007eu,vanDoorn:2010hu} and Muralidhar and Veller~\cite{Muralidhar2018} have shown that new sex-determining alleles can be favoured if they arise at loci in close linkage with a locus that experiences sexual antagonism.
-Tighter linkage allows a stronger favourable association to build up between a male-beneficial allele, and a neo-Y allele, for example. 
-Such associations can favour cis-GSD transitions~\cite{vanDoorn:2007eu}, trans-GSD transitions~\cite{vanDoorn:2010hu}, and new partially-masculinizing or partially-feminizing alleles~\cite{Muralidhar2018}.
-However, any sexually-antagonistic loci that are more closely linked to the ancestral sex-determining locus will develop similar, favourable associations and are expected to hinder the spread of a new sex-determining system.
-
-The sex ratio is directly determined by the sex-determining system, and it has therefore been suggested that sex ratio selection is a dominant force in the evolution of sex determination (e.g., Bull, 1983, p 66-67 ~\cite{Bull:1983vi}; Buekeboom and Perrin, 2014, Chapter 7~\cite{Beukeboom:2014vb}).
-`Fisherian' sex ratio selection favours a 1:1 zygotic sex ratio when assuming that males and females are equally costly to produce~\cite{Fisher:1930wy,Charnov:1982wg}.
-This follows from the fact that, for an autosomal locus, half of the genetic material is inherited from a male and half from a female~\cite{West:2009we}. 
-Thus, if the population sex ratio is biased towards one sex, the average per-individual contribution of genetic material to the next generation from the opposite sex is greater. 
-Therefore, a mutant that increases investment in the rarer sex will spread via the higher per-individual contributions made by that sex. 
-%The default mode of sex ratio selection is `Fisherian' sex ratio selection, which favours equal investment in male and female offspring \citep[i.e., a 1:1 zygotic sex ratio when assuming that males and females are equally costly to produce,][]{Fisher:1930wy,Charnov:1982wg}.
-%Given that the sex-determining system can directly affect the sex ratio, we might expect Fisherian sex ratio selection to influence the spread of new sex-determining systems. 
-In the case of sex-chromosome evolution, Kozielska et al.
-(2014)~\cite{Kozielska:2010vm} consider systems in which the ancestral sex chromosomes experience meiotic drive (e.g., where driving X or Y chromosomes are inherited disproportionately often), which causes sex ratios to become biased~\cite{Hamilton:1967ts}.
-They find that masculinizing or feminizing mutations that arise at a new, unlinked locus (i.e., neo-Y or neo-W chromosomes) can then spread, which restore an even sex ratio.
-
-Here we use mathematical models to find the conditions under which new sex-determining systems spread when individuals experience selection at both diploid and haploid stages, which allows fitness differences between the sexes and sex ratio biases to occur simultaneously.
-Even in animal and plant species that have much larger and more conspicuous diploid phases than haploid phases, many loci experience significant haploid selection through gamete competition and/or meiotic drive~\cite{Mulcahy:1996ha,JOSEPH:2004haa}.
-We use the term `meiotic drive' to refer to the biased (non-Mendelian) segregation of genotypes during gamete production (from one parent) and the term `gametic competition' to refer to selection upon haploid genotypes within a gamete/gametophyte pool (potentially from multiple parents); the term `haploid selection' encompasses both processes.
-
-Segregation distortion provides putative evidence of haploid selection and can sometimes be attributed to meiotic drive and/or gametic competition~\cite{Lalanne2004,Fishman2005,Leppala2008,Leppala2013,Didion2015,Didion2016}.
-Where it has been characterized, meiotic drive generally occurs either during the production of male or female gametes only~\cite{Ubeda:2005gw,Lindholm:2016cw}.
-Gametic competition is also typically sex specific, occurring primarily among male gametes, because there are typically many more pollen/sperm than required for fertilization.
-Gametic competition may be particularly common in plants, in which 60-70\% of all genes are expressed in the male gametophyte, and these genes exhibit stronger signatures of selection than randomly-chosen genes~\cite{Borg:2009jpa,Arunkumar:2013iq,Gossmann:2014dua}.
-In addition, artificial selection pressures applied to male gametophytes are known to cause a response to selection (e.g.,~\cite{Hormaza:1996cv,Ravikumar:2003uo,Hedhly:2004iv,Clarke:2004ir}). 
-A smaller proportion of genes are thought to be expressed and selected during competition in animal sperm, although precise estimates are uncertain~\cite{Zheng:2001fi,JOSEPH:2004haa,Vibranovski:2010et}.
-Nevertheless, recent studies have demonstrated that sperm competition in animals can alter haploid allele frequencies and increase offspring fitness~\cite{Immler:2014im,Alavioon2017}.
-
-There are various ways by which genes experiencing haploid selection could influence transitions between sex-determining systems. 
-If we assume that haploid selection at any particular locus predominantly occurs in one sex (e.g., meiotic drive during spermatogenesis), then such loci experience a form of sex-specific selection. 
-In this respect, we might expect that haploid selection would affect transitions between sex-determining systems in a similar manner to sex-specific diploid selection (as explored in~\cite{vanDoorn:2007eu,vanDoorn:2010hu}).
-That is, new masculinizing mutations (neo-Y alleles) could be favoured via associations with alleles that are beneficial in the male haploid stage. 
-On the other hand, sex ratios can also become biased by linkage between the sex-determining locus and a locus that harbours genetic variation in haploid fitness. 
-For example, there are several known cases of sex ratio bias caused by sex-linked meiotic drive alleles (Burt and Trivers, 2006, Chapter 6~\cite{Burt:2006}) or selection among X- and Y-bearing pollen~\cite{Lloyd:1974tz,Conn:1981uw,Stehlik:2005ul,Stehlik:2006to,Field:2012fd,Field:2013cc}.
-It is not immediately clear how the spread of new sex-determining systems would be influenced by the combination of sex ratio biases and associations with haploid selected alleles.
-
-We find that the spread of novel sex-determining systems is influenced by both Fisherian sex ratio selection and by selection on linked alleles. 
-%We find that sex ratio biases caused by haploid selection can exert Fisherian sex ratio selection upon novel sex-determiners but that their spread is also determined by selection on genetically-associated alleles.
-%Indeed, it is only when haploid-selected loci are tightly linked to the ancestral sex-determining region (and so sex ratio biases are initially large) that we see an asymmetry between selection for XY to ZW transitions and ZW to XY transitions (e.g., because haploid selection in males only causes biased zygotic sex ratios in an ancestrally XY system).
-Surprisingly, Fisherian sex ratio selection does not dominate; it is possible for selection on linked alleles to drive turnover between sex-determining systems despite causing increasingly biased sex ratios.
-In addition to considering haploid selection, another novel development in our model is that we consider loci that are in very tight linkage with the ancestral sex-determining locus. 
-%Because sex-determining loci are often found within a region of suppressed recombination, there can be a significant number of tightly linked loci. 
-We find that loci tightly linked with the sex-determining locus can drive transitions in which the heterogametic sex changes, even when the new sex-determining locus is less closely linked to loci under selection (either including haploid selection or not).
-
-\section*{Model}
-
-%genetic system
-We consider transitions between ancestral and novel sex-determining systems using a three-locus model, each locus having two alleles (Fig \ref{fig:model_outline}). 
-Locus $\mathbf{X}$ is the ancestral sex-determining region, with alleles X and Y (or Z and W).
-Locus $\mathbf{A}$ is a locus under selection, with alleles $A$ and $a$.
-Locus $\mathbf{M}$ is a novel sex-determining region, at which the null allele ($M$) is initially fixed in the population such that sex of zygotes is determined by the genotype at the ancestral sex-determining region, $\mathbf{X}$; XX genotypes become females and XY become males (or ZW become females and ZZ become males).
-To evaluate the evolution of new sex-determining systems, we consider the invasion, fixation, maintenance, and/or loss of a novel sex-determining allele ($m$) at the $\mathbf{M}$ locus. 
-%We only do invasion analytically though (is this sentence still ok?)
-We assume that the $\mathbf{M}$ locus is epistatically dominant over the $\mathbf{X}$ locus such that zygotes with at least one $m$ allele develop as females with probability $k$ and as males with probability $1-k$, regardless of the $\mathbf{X}$ locus genotype.
-With $k=0$, the $m$ allele is a masculinizer (a neo-Y allele) and with $k=1$ the $m$ allele is a feminizer (a neo-W allele).
-With intermediate $k$, we can interpret $m$ as an environmental sex-determination (ESD) allele, such that zygotes develop as females in a proportion ($k$) of the environments they experience. 
-%We also analyze a model of maternally-controlled environmental sex-determination, where mothers with at least one $m$ allele produce daughters with probability $k$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Model Outline
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-%\centering
-%\centerline{\includegraphics[width=\linewidth]{Sex_determination_outline.pdf}}
-\caption{
-{\bf Outline of model features.}
-Panel A: Recombination rate parameters between the ancestral-sex-determining locus ($\mathbf{X}$, here assumed to have alleles X and Y), a locus under selection ($\mathbf{A}$, with alleles $A$ and $a$), and a new sex-determining locus ($\mathbf{M}$, with alleles $M$ and $m$).
-If $r<1/2$, then associations between ancestral sex-determining alleles and selected alleles can be maintained past recombination in males. 
-Panel B: Haploid selection is often sex-specific, occurring during haploid production or competition in either males or females. 
-For example, haploid selection in males only is represented by the dashed circle.  
-If X or Y alleles remain associated with alleles that experience haploid selection in males ($r<1/2$), then zygotic sex ratios can become biased because either X- or Y-bearing male gametes/gametophytes will be more abundant after haploid selection.
-However, the zygotic sex ratio is not biased by male haploid selection in ZW sex-determining systems. 
-Similarly, zygotic sex ratio biases can occur if haploid selected alleles are associated with new sex-determining alleles ($R<1/2$). 
-Panel C: During cis-GSD transitions (XY to XY or ZW to ZW), a neo-Y allele spreads to pseudo-fixation (its maximum frequency among male gametes) and the ancestral Y allele is lost. 
-Panel D: During trans-GSD transitions (XY to ZW or ZW to XY), a neo-W allele spreads to pseudo-fixation (its maximum frequency among female gametes) and the ancestral X allele is lost. 
-Neo-W alleles allow Y-associated alleles into females, which may impede or aid their spread. 
-}
-\label{fig:model_outline}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%life-cycle
-In each generation, we census the genotype frequencies in male and female gametes/gametophytes (hereafter gametes) before gametic competition. 
-A full description of our model, including recursion equations, is given in \nameref{app:recurs}. 
-First, competition occurs among male gametes (sperm/pollen competition) and among female gametes (egg/ovule competition) separately. 
-Selection during gametic competition depends on the $\mathbf{A}$ locus genotype; relative fitnesses are given by $w_A^\Hermaphrodite$ and $w_a^\Hermaphrodite$ ($\Hermaphrodite \in \{\female,\male\}$; see table \ref{tab:fitnesstable}).
-%$w_{A}^\male$ and $w_{a}^\male$ for male gametes and $w_{A}^\female$ and $w_{a}^\female$ for female gametes, see table \ref{tab:fitnesstable}.
-We assume that all gametes compete for fertilization during gametic competition, which implies a polygamous mating system. 
-Gametic competition in monogamous mating systems is, however, equivalent to meiotic drive in our model (described below), as either only alters the frequency of gametes produced by heterozygotes. 
-After gametic competition, conjugation between male and female gametes occurs at random.
-The resulting zygotes develop as males or females, depending on their genotypes at the $\mathbf{X}$ and $\mathbf{M}$ loci.
-%(and the $\mathbf{M}$ genotype of their mother in the case of maternal control).
-Diploid males and females then experience selection, with relative fitnesses $w_{AA}^{\Hermaphrodite}$, $w_{Aa}^{\Hermaphrodite}$, and $w_{aa}^{\Hermaphrodite}$.
-%where $g$ is the diploid genotype at the $\mathbf{A}$ locus ($g \in \{AA, Aa, aa\}$).
-%Diploids compete with others of the same sex, where selection depends on the sex of the individual and its genotype at the $\mathbf{A}$ locus.
-The next generation of gametes is produced by meiosis, during which recombination and sex-specific meiotic drive can occur. 
-Recombination (i.e., an odd number of cross-overs) occurs between loci $\mathbf{X}$ and $\mathbf{A}$ with probability $r$, between loci $\mathbf{A}$ and $\mathbf{M}$ with probability $R$, and between loci $\mathbf{X}$ and $\mathbf{M}$ with probability $\rho$.
-Any linear order of the loci can be modelled with appropriate choices of $r$, $R$, and $\rho$ (see Fig \ref{fig:model_outline}A and \nameref{tab:chisubstitutions}). 
-Individuals that are heterozygous at the $\mathbf{A}$ locus may experience meiotic drive; a gamete produced by $Aa$ heterozgotes of sex $\Hermaphrodite$ bears allele $A$ with probability $\alpha^\Hermaphrodite$.
-Thus, the $\mathbf{A}$ locus can experience sex-specific gametic competition, diploid selection, and/or meiotic drive.
-
-\begin{table}[ht]
-%\centering
-\smallskip
-\caption{{\bf Relative fitness of different genotypes in sex $\Hermaphrodite \in \{\female,\male\}$ } }
-\begin{tabular}{l c }
-\hline\hline
-  Genotype & Relative fitness during gametic competition \\ [0.5ex] \hline
-  $A$ & $w_{A}^\Hermaphrodite = 1+t^\Hermaphrodite$ \\
-  $a$ & $w_{a}^\Hermaphrodite = 1$ \\ [0.5ex] \hline
-  Genotype & Relative fitness during diploid selection \\ [0.5ex] \hline
-  $AA$ & $w_{AA}^\Hermaphrodite = 1+ s^\Hermaphrodite$ \\
-  $Aa$ & $w_{Aa}^\Hermaphrodite = 1+h^\Hermaphrodite s^\Hermaphrodite$ \\
-  $aa$ & $w_{aa}^\Hermaphrodite = 1$ \\ [0.5ex] \hline
-  Genotype & Transmission during meiosis in $Aa$ heterozygotes \\ [0.5ex] \hline
-  $A$ & $\alpha^\Hermaphrodite=1/2+\alpha_{\Delta}^{\Hermaphrodite}/2$ \\
-  $a$ & $1-\alpha^\Hermaphrodite=1/2-\alpha_{\Delta}^{\Hermaphrodite}/2$ \\
-  \hline \hline
-  \label{tab:fitnesstable}
- \end{tabular}
-\end{table}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Results}
-%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The model outlined above describes both ancestral XY and ZW sex-determining systems. %if we relabel the two sexes as being ancestrally `heterogametic' or ancestrally `homogametic'. 
-Without loss of generality, we refer to the ancestrally heterogametic sex as male and the ancestrally homogametic sex as female.
-That is, we primarily describe an ancestral XY sex-determining system but our model is equally applicable to an ancestral ZW sex-determining system (relabelling the ancestrally heterogametic sex as female and the ancestrally homogametic sex as male and switching the labels of males and females throughout).
-We use a superscript to specify the ancestral sex-determining system described, e.g., $^{(XY)}$ for ancestral XY sex-determination.
-
-\subsection*{Generic invasion by a neo-Y or neo-W}
-
-The evolution of a new sex-determining system requires that a rare mutant allele, $m$, at the novel sex-determining locus, $\mathbf{M}$, increases in frequency when rare. 
-This is determined by the leading eigenvalue ($\lambda_m^{(XY)}$) of the system of eight equations describing the frequency of eggs and sperm carrying the $m$ allele in the next generation (equations \ref{eq:recursions}).
-%, evaluated at the above equilibrium.
-%Thus, the system describing the change in frequency of the $m$ allele consists of eight recursion equations. 
-This system simplifies substantially for a dominant neo-Y ($k=0$) or neo-W ($k=1$), see \nameref{app:inv_cond}. 
-The leading eigenvalue for a rare neo-Y or neo-W allele, $m\in\{Y',W'\}$, is the largest value of X that solves $x^2+ b x + c = 0$.  %$(\lambda_m^{(i)})^2+ b \lambda_m^{(i)} + c =0$. 
-The coefficients are $b= - (\Lambda_{mA}^{(XY)} + \Lambda_{ma}^{(XY)})+(\chi_{mA}^{(XY)} + \chi_{ma}^{(XY)})$ and $c = (\Lambda_{mA}^{(XY)} - \chi_{mA}^{(XY)}) (\Lambda_{ma}^{(XY)} - \chi_{ma}^{(XY)}) - \chi_{mA}^{(XY)} \chi_{ma}^{(XY)}$, where $\Lambda_{mi}^{(XY)}>0$ is the multiplicative growth rate (which we will call the ``haplotypic growth rate'') of the neo-sex determination allele $m$ on background $i\in\{A,a\}$ without accounting for loss due to recombination ($R=0$), and $\chi_{mi}^{(XY)}>0$ is the rate at which mutant haplotypes on background $i\in\{A,a\}$ recombine onto the other $\mathbf{A}$ locus background in heterozygotes (proportional to $R$), see Table \ref{tab:haplotype_growth}.
-In the ancestral population, it is convenient to follow the frequency of the $A$ allele among female gametes (eggs), $p^\female_X$, and among X-bearing, $p^\male_X$, and among Y-bearing, $p^\male_Y$, male gametes (sperm/pollen).
-We also track the fraction of male gametes that are Y-bearing, $q$, which may deviate from $1/2$ due to meiotic drive in males. 
-We will consider only equilibrium frequencies of alleles, $\hat{p}^\Hermaphrodite_i$, and Y-bearing male gametes, $\hat{q}$, when calculating the eigenvalues.
-
-\begin{table}[!ht]
-\centering
-\smallskip
-%\caption{Parameters determining invasion (equation \ref{eq:charpoly_neoY}) for neo-Y or neo-W alleles}
-\caption{ {\bf Parameters determining invasion of mutant neo-Y and neo-W alleles into an ancestrally XY system}}
-\begin{tabular}{l}
-\hline\hline
-   \noalign{\vskip 0.5ex}
-   $m$ is a neo-Y ($k=0$) \\ [0.5ex] \hline \noalign{\vskip 1ex}
-  $\Lambda_{Y'A}^{(XY)} = {\left( 2 \zeta \right)}^{-1} \left[\hat{p}_X^\female w_{A}^{\female} w_{A}^{\male} w_{AA}^{\male} + (1-\hat{p}_X^\female) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} (1+\alpha_{\Delta}^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\male}_{D} \right) $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\Lambda_{Y'a}^{(XY)} = {\left( 2 \zeta \right)}^{-1} \left[(1-\hat{p}_X^\female) w_{a}^{\female} w_{a}^{\male} w_{aa}^{\male} + \hat{p}_X^\female w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male}(1 - \alpha_{\Delta}^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\male}_{D} \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\chi_{Y'A}^{(XY)} = R {\left( 2 \zeta \right)}^{-1} \left[ (1-\hat{p}_X^\female) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} (1+\alpha_{\Delta}^{\male}) \right]/  \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\male}_{D} \right)   $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\chi_{Y'a}^{(XY)} = R {\left( 2 \zeta \right)}^{-1} \left[   \hat{p}_X^\female w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male} (1 - \alpha_\Delta^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\male}_{D} \right)  $\\ [1ex] \hline
-  \noalign{\vskip 0.5ex}
-  $m$ is a neo-W ($k=1$) \\ [0.5ex] \hline \noalign{\vskip 1ex}
-  $\Lambda_{W'A}^{(XY)} = {\left[ 2 (1 - \zeta) \right]}^{-1} \left[ \bar{p}^{\male} w_{A}^{\male} w_{A}^{\female} w_{AA}^{\female}+(1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female}(1+\alpha_{\Delta}^{\female})\right]/ \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\female}_{D} \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\Lambda_{W'a}^{(XY)} = {\left[ 2 (1 - \zeta) \right]}^{-1} \left[ (1-\bar{p}^{\male}) w_{a}^{\male} w_{a}^{\female} w_{aa}^{\female}+\bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female}(1-\alpha_{\Delta}^{\female})\right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\female}_{D} \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\chi_{W'A}^{(XY)} = R {\left[ 2 (1 - \zeta) \right]}^{-1} \left[ (1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female} (1+\alpha_{\Delta}^{\female}) \right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\female}_{D} \right)  $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\chi_{W'a}^{(XY)} = R {\left[ 2 (1 - \zeta) \right]}^{-1} \left[ \bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female} (1-\alpha_{\Delta}^{\female}) \right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\female}_{D} \right) $ \\ [1ex]
-  \hline \hline 
-   \end{tabular}
-   \begin{flushleft} 
-$\bar{p}^{\male}=(1-\hat{q})\hat{p}_X^\male + \hat{q}\hat{p}_Y^\male$ is the average frequency of the $A$ allele among X- and Y-bearing male gametes.
-%      \item $R$ is the probability of recombination between loci $\mathbf{A}$ and $\mathbf{M}$.
-$\zeta$ is the zygotic sex ratio (fraction male).
-$\bar{w}^{\Hermaphrodite}_{D}$ is the mean fitness of diploids of sex $\Hermaphrodite$.
-$\bar{w}_H^\Hermaphrodite$ is the mean fitness of haploids from sex $\Hermaphrodite$, see \nameref{tab:meanfitnesses}.
-\end{flushleft}
-  \label{tab:haplotype_growth}
-\end{table}
-
-The new sex-determining allele increases in frequency when rare when the largest eigenvalue is greater than one ($\lambda_m^{(XY)}>1$). 
-%If the average change in frequency of the two haplotypes that carry the $m$ allele ($Am$ and $am$) is positive, invasion will always occur, i.e., if $(\Lambda_{mA} + \Lambda_{ma})/2 > 1$ then $\Lambda > 1$.
-%The leading eigenvalue is the largest solution of $f(\lambda_m^{(i)})=(\lambda_m^{(i)})^2+b\lambda_m^{(i)}+c=0$ and the Perron-Frobenius theorem guarantees that it is positive, unique, and real.  
-%Since $f(\Lambda_{mA}^{(i)})$ and $f(\Lambda_{ma}^{(i)})$ are of opposite signs, the leading eigenvalue must fall between these two quantities and is the larger of them when $R = 0$ (see \nameref{file:Mathematica}).
-If both haplotypic growth rates are greater than one ($\Lambda_{mA}^{(XY)}, \Lambda_{ma}^{(XY)}>1$), then the new sex-determining allele invades regardless the rate of recombination between the new sex-determining locus and the selected locus ($R$), see \nameref{app:inv_cond} for details.
-Conversely, if both haplotypic growth rates are less than one ($\Lambda_{mA}^{(XY)}, \Lambda_{ma}^{(XY)}<1$), then invasion can never occur.  
-Finally, if only one haplotypic growth rate is greater than one, the new sex-determining allele can always invade when arising at a locus that is tightly linked to the selected locus ($R\approx0$).  
-Furthermore, it can be shown that the leading eigenvalue declines with $R$, and invasion requires that $R$ is sufficiently small such that: 
-\begin{equation}\label{eq:lambdasGen}
-%\frac{\chi_{mA}}{\Lambda_{mA}-1}+\frac{\chi_{ma}}{\Lambda_{ma}-1}>0.
-\chi_{ma}^{(XY)}/\left(\Lambda_{ma}^{(XY)} - 1\right) + \chi_{mA}^{(XY)}/\left(\Lambda_{mA}^{(XY)} - 1\right) < 1.
-\end{equation}
-\noindent 
-This condition may or may not be satisfied for the full range of locations of the new sex-determining locus, including $R=1/2$, depending on the nature of selection.  
-Interpreting this condition, if we assume that only the $mA$ haplotype would increase in frequency when $R=0$ ($\Lambda_{ma}^{(XY)}<1<\Lambda_{mA}^{(XY)}$) the first term on the left-hand side of \eqref{eq:lambdasGen} is negative and invasion requires that rate of growth of $mA$ haplotypes ($\Lambda_{mA}^{(i)}-1>0$) and the rate at which $mA$ haplotypes are produced by recombination in $ma$ haplotypes ($\chi_{ma}^{(i)}$) are sufficiently large relative to the rate of decline of $ma$ haplotypes ($1-\Lambda_{ma}^{(i)}>0$) and the rate of loss of $mA$ haplotypes due to recombination ($\chi_{mA}^{(i)}$).
-
-We can draw a number of key points about the invasion of neo-Y and neo-W mutations from Table \ref{tab:haplotype_growth}. 
-First, Fisherian sex ratio selection will favour the spread of a neo-Y and inhibit the spread of a neo-W if the ancestral zygotic sex ratio is biased towards females, $\zeta<1/2$ (i.e., the first factor of the $\Lambda_{mi}^{(XY)}$ is greater than one for a neo-Y and less than one for a neo-W).
-However, the spread of a neo-Y (neo-W) also depends on the male (female) fitness of associated alleles (see terms involving equilibrium allele frequencies, $\hat{p}$'s).
-Second, invasion by a neo-Y (neo-W) does not directly depend on the fitness of female (male) diploids. %(for a given set of equilibrium allele frequencies).
-This is because a dominant neo-Y (neo-W) is always found in males (females), and therefore the frequency of the neo-Y (neo-W), $m$, only changes in males (females), Fig \ref{fig:model_outline}C,D. 
-Finally, invasions by a neo-Y and a neo-W are qualitatively different.
-This is because a gamete with the neo-Y always pairs with a female gamete containing an X, Fig \ref{fig:model_outline}C.
-By contrast, a gamete with a neo-W can pair with an X- or Y-bearing male gamete, Fig \ref{fig:model_outline}D.
-Consequently, neo-W-bearing females obtain a different frequency of $A$ alleles from mating (when $\hat{p}_X^\male \neq \hat{p}_Y^\male$) compared to ancestral ($MM$) females.
-
-In order to explicitly determine the conditions under which a rare new sex-determining allele spreads, we must calculate the equilibrium frequency of the $A$ allele (i.e., $\hat{p}^\female_X$, $\hat{p}^\male_X$, and $\hat{p}^\male_Y$) and Y-bearing male gametes ($\hat{q}$) in the ancestral population.
-Since only the $\mathbf{A}$ locus experiences selection directly, any deterministic evolution requires that there is a polymorphism at the $\mathbf{A}$ locus. 
-Polymorphisms can be maintained by mutation-selection balance or transiently present during the spread of beneficial alleles. 
-However, polymorphisms maintained by selection can maintain alleles at intermediate allele frequencies for longer periods. 
-Here, we focus on polymorphisms maintained by selection, where the $A$ allele reaches a stable intermediate equilibrium frequency under the ancestral sex-determining system before the new sex-determining allele ($m$) arises.
-Such polymorphisms can be maintained by heterozygote advantage, sexually-antagonistic selection, ploidally-antagonistic selection, or a combination~\cite{Immler:2012tl}.
-We can analytically calculate the allele frequency of the $A$ allele using two alternative simplifying assumptions: 
-(1) the $\mathbf{A}$ locus is within (or tightly linked to) the non-recombining region around the ancestral sex-determining locus ($r \approx 0$) or (2) selection is weak relative to recombination ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon<<1$).
-
-\subsection*{Tight linkage with the ancestral sex-determining locus ($r \approx 0$)}
-
-The ancestral equilibrium allele frequencies and their stability conditions are given in \nameref{app:eq_stab}. 
-When there is complete linkage between the ancestral sex-determining locus and the $\mathbf{A}$ locus ($r=0$), either the $A$ allele or the $a$ allele must be fixed in gametes containing a Y allele. 
-% because selection on the Y is effectively haploid an incapably of maintaining a polymorphism in the absence of frequency dependent selection. 
-Because the labelling of alleles is arbitrary, we will assume that the $a$ locus is fixed in gametes with a Y ($p^\male_Y=0$), without loss of generality. 
-If there are two alleles maintained at the $\mathbf{A}$ locus, the $A$ allele can be fixed ($\hat{p}^\female_X=\hat{p}^\male_X=1$) or segregating at an intermediate frequency (0<$\hat{p}^\female_X, \hat{p}^\male_X$<1) in gametes with an X.
-%However, because the X is present in both males and females, there are distinct selection pressures on X's in females and X's in males, which will always be paired with an $A$ allele from the Y.
-
-We find that a neo-Y allele can never invade an ancestral XY system that already has tight linkage with the locus under selection ($\lambda_{Y'}^{(XY)} \leq 1$ when $r=0$, for details see \nameref{file:Mathematica}).
-When $R=0$, a neo-Y haplotype with the same allele as the ancestral Y is neutral ($\Lambda_{Y'a}^{(XY)}=1$) and does not change in frequency.
-The other neo-Y haplotype will not spread ($\Lambda_{Y'A}^{(XY)}<1$) given that the initial equilibrium is stable. 
-Therefore, a neo-Y mutation cannot spread in an ancestral XY system ($\lambda_{Y'}^{(XY)} \leq 1$, regardless of $R$) where selected loci are within or very near the non-recombining region around the sex-determining locus.
-In essence, through tight linkage with the $\mathbf{A}$ locus, the ancestral Y becomes strongly specialized on the allele that has the highest fitness across male haploid and diploid phases. 
-Given that the ancestral Y is at this equilibrium, it is not possible for a neo-Y to create males that have higher fitness than the ancestral Y.
-
-Neo-W alleles, on the other hand, can invade an ancestral XY system under some conditions (the full invasion conditions are given in \nameref{app:inv_cond}; equations \ref{Binvasion} and \ref{Ainvasion}).
-Counterintuitively, selection on loci within the non-recombining region around the sex-determining locus can favour the invasion of a less closely linked neo-W, whatever the form of selection maintaining a polymorphism (sexually-antagonistic selection, overdominance, ploidally-antagonistic selection, or some combination, Fig \ref{fig:SexAntagTighter}, \nameref{fig:temporalOverdominance}, \nameref{fig:regionPloidAntag}, and \nameref{fig:SexAntagTighterMaleDrive}).
-The conditions become more restrictive, however, with increasing recombination ($R$) between the new sex-determining locus and the selected locus.  
-The invasion of completely unlinked neo-W alleles ($R = 1/2$) can occur with overdominance in males or with haploid selection but is not possible with only sexually-antagonistic selection if selection is directional in each diploid sex (see \nameref{file:Mathematica}).
-To develop an intuition for how less closely linked neo-W alleles invade ($R>r$), we here focus on cases where there is no haploid selection and discuss the additional effect of haploid selection in \nameref{app:inv_cond}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Tighter linkage allows looser sex-linkage to evolve, even in absence of haploid selection
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-%\centerline{\includegraphics[width=1.5\linewidth]{PositionPlot_SexAntagTighter}}
-\caption{
-{\bf Transitions between XY and ZW systems can occur even when the new sex-determining locus is less tightly linked to a locus under sexually-antagonistic selection (even without haploid selection).}
-In panel A, linkage is loose enough relative to selection that the analytical results assuming weak selection hold, and a neo-W allele can only invade when it arises at a locus more tightly linked with the selected locus ($R<r$; shaded region).
-In panel B, linkage is tight enough relative to selection that the analytical results assuming weak selection do not hold, and a neo-W can invade even when it is less tightly linked with the selected locus ($r<R$; unshaded region around \text{*}).
-In panel C we vary the recombination rate between the neo-W and the selected locus ($R$) for a fixed recombination rate between the ancestral sex-determining locus and the selected locus ($r=0.005$). 
-Coloured markers show recombination rates for which the temporal dynamics of invasion are plotted in the inset, demonstrating that neo-W alleles can reach pseudo-fixation if they are more (black) or less (red) closely linked to a locus experiencing sexually-antagonistic selection.
-A very loosely linked neo-W does not spread in this case (blue and green lines overlap and go to 0 in inset). 
-Fitness parameters are: $w_{AA}^\female = 1.05$, $w_{aa}^\male = 1.2$, $w_{aa}^\female = w_{AA}^\male = 0.85$, $w_{Aa}^\Hermaphrodite = 1$,  $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
-%\textcolor{red}{consider removing panel A, which is repeated in Fig 3.}
-%\textcolor{blue}{probably better to remove from panel 3, eh?}
-}
-\label{fig:SexAntagTighter}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-If we categorise the $a$ allele as being ancestrally `male-beneficial' via the fact that it is fixed on Y backgrounds, then $\Lambda_{W'A}^{(XY)}>1$ indicates that the neo-W spreads when found with the ancestrally `female-beneficial' allele.
-Broadly, this is possible because ancestral X alleles are sometimes in males and are therefore unable to perfectly specialise on the `female-beneficial' allele. 
-For example, when the $a$ allele is favoured on ancestral X backgrounds in males, a polymorphism of $A$ and $a$ alleles can be maintained on the X background despite selection for the $A$ allele in females ($s^\female>0$, $0<h^\female<1$), see outlined region in Fig \ref{fig:regionplots}A.
-When the $a$ allele is strongly favoured on the X background in males ($w_{aa}^\male$ sufficiently large relative to $w_{Aa}^\male$), neo-W-$A$ haplotypes can spread ($\Lambda_{W'A}^{(XY)}>1$, see grey region in Fig \ref{fig:regionplots}A) because they produce higher fitness females ($AA$ or $Aa$ genotypes) and are unleashed from counterselection in males.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Both neo-W haplotypes can spread, in the absence of haploid selection, when there is overdominance
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-%\centerline{\includegraphics[width=1.25\linewidth]{Region_plot_combined_Mike}}
-%\centerline{\includegraphics[width=1.25\linewidth]{Region_plot_combined}}
-\caption{
-{\bf When the ancestral XY locus is tightly linked to a locus under selection ($r=0$), one or both neo-W haplotypes can spread. }
-We vary the fitness of male homozygotes relative to heterozygotes ($w_{Aa}^\Hermaphrodite=1$) and only consider stable equilibria at which both $\mathbf{A}$ locus alleles are maintained and the $a$ allele is initially fixed on Y backgrounds, region outlined.
-Here, selection in females can favour the $A$ allele (panel A, $w_{aa}^\female=0.85$, $w_{AA}^\female=1.05$), favour the $a$ allele (panel B, $w_{aa}^\female=1.05$, $w_{AA}^\female=0.85$), or be overdominant (panel C, $w_{aa}^\female=w_{AA}^\female=0.6$).
-If either haplotypic growth rate ($\Lambda_{W'A}^{(XY)}$ or $\Lambda_{W'a}^{(XY)}$) is greater than one, then a rare neo-W allele can spread for, at least, some values of $R>r$. 
-The parameter values marked with an asterisk correspond to the fitnesses used in Fig \ref{fig:SexAntagTighter}C. 
-Where both haplotypic growth rates are greater than one, a neo-W will spread when rare, regardless of linkage with the selected locus (for any $R$). 
-\nameref{fig:positionOverdominance} shows the dynamics arising with the parameters marked with a dagger. 
-Here, there is no haploid selection $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
-}
-\label{fig:regionplots}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-When only one neo-W haplotype has growth rate greater than one (see Fig \ref{fig:regionplots}), a neo-W allele can invade as long as Eq \eqref{eq:lambdasGen} is satisfied, which may require that the recombination rate, $R$, is small enough.
-Nevertheless, because we assume here that $r$ is small, these results indicate that a more loosely linked sex-determining region ($r<R$) can spread.
-For example, tightly sex-linked loci that experience sexually-antagonistic selection can drive trans-GSD transitions in which the new sex-determining locus is less closely linked to the locus under selection (Fig \ref{fig:SexAntagTighter}).
-
-Given that the $a$ allele can be considered ancestrally `male-beneficial' because it is fixed on Y backgrounds, it is surprising that neo-W-$a$ haplotypes can sometimes be favoured by selection in females ($\Lambda_{W'a}^{(XY)}>1$).
-Again, this occurs because ancestral X alleles also experience selection in males, where they are ancestrally always paired with a Y-$a$ gamete. 
-If there is overdominance in males, X-$A$ Y-$a$ males have high fitness and the $A$ allele is favoured by selection on the X background in males. 
-Therefore, the $A$ allele can be polymorphic or even fixed on the X background despite selection favouring the $a$ allele in females (e.g., see outlined region in Fig \ref{fig:regionplots}B and~\cite{Lloyd1977,Otto2014}).
-In such cases, neo-W-$a$ haplotypes can spread because they create more $Aa$ and $aa$ females when pairing with an X-bearing gamete from males and because they bring Y-$a$ haplotypes into females, where it has higher fitness (Fig \ref{fig:model_outline}D).
-
-In some cases, both W-$A$ and W-$a$ haplotypes can spread.
-For example, when $AA$ individuals have low fitness in females yet the $A$ is polymorphic or fixed on the X background due to overdominance in males (Fig \ref{fig:regionplots}B and \ref{fig:regionplots}C), both neo-W-$A$ and neo-W-$a$ haplotypes produce fewer unfit $AA$ females.
-This is true for the neo-W-$A$ haplotype because it can pair with a Y-$a$ haplotype and still be female. 
-Wherever both haplotypic growth rates are greater than one, invasion by a neo-W is expected regardless of its linkage with the selected locus (i.e., for any $R$, see \nameref{fig:positionOverdominance} and \nameref{fig:temporalOverdominance} for examples).
-
-Assuming selection is weak relative to recombination, van Doorn and Kirkpatrick~\cite{vanDoorn:2010hu} showed that invasion by a neo-W allele occurs under the same conditions as `pseudo-fixation' (at pseudo-fixation the neo-W reaches its maximum frequency among eggs, which is usually 1/2, but can deviate from 1/2 when there is haploid selection before censusing).
-An equivalent analysis is not possible where recombination rates are low. 
-However, numerical simulations demonstrate that new sex-determining alleles do not necessarily reach pseudo-fixation, which can lead to the stable maintenance of a mixed sex-determining system, in which X, Y, Z, and W alleles all segregate (e.g., \nameref{fig:freqAll}B,C).
-
-\subsection*{Loose linkage with the ancestral sex-determining region}
-
-Here we assume that selection is weak ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon<<1$) and thus implicitly assume that all recombination rates ($r$, $R$ and $\rho$) are large relative to selection.
-%, we denote the leading eigenvalues describing the invasion of a neo-Y ($k=0$) and a neo-W ($k=1$) into an ancestrally XY system by $\lambda_{Y',XY}$ and $\lambda_{W',XY}$, respectively. 
-To leading order in selection, the leading eigenvalues are:
-
-\begin{equation}
-\lambda_{Y'}^{(XY)} =1+ \frac{1}{4}V_{A}S_{A}^2\frac{ \left( r-R \right) }{r R}+O\left(\epsilon^3 \right) 
-\label{eq:lambda_neoY}
-\end{equation}
-
-\noindent 
-and
-
-\begin{equation}
-\lambda_{W'}^{(XY)} =\lambda_{Y'}^{(XY)}+\left(2\alpha_{\Delta}^\male-2\alpha_{\Delta}^\female+t^\male-t^\female \right) \left( \hat{p}^\male_Y-\hat{p}^\male_X \right)/2
-+O\left(\epsilon^3 \right)
-\label{eq:lambda_neoW}
-\end{equation}
-
-\noindent
-where $V_{A}=\bar{p}(1-\bar{p})$ is the variance in the equilibrium frequency of $A$ and $S_{A}=(D^\male +\alpha_{\Delta}^\male+t^\male) - (D^\female+\alpha_{\Delta}^\female+t^\female)$ describes sex differences in selection for the $A$ versus $a$ allele across diploid selection, meiosis, and gametic competition.
-The diploid selection term, $D^\Hermaphrodite=\big{[} \bar{p}s^\Hermaphrodite+(1-\bar{p})h^\Hermaphrodite s^\Hermaphrodite\big{]} -\big{[} \bar{p}h^\Hermaphrodite s^\Hermaphrodite+(1-\bar{p}) \big{]}$, is the difference in fitness between $A$ and $a$ alleles in diploids of sex $\Hermaphrodite \in \{\female,\male\}$, where $\bar{p}$ is the leading-order probability of mating with an $A$-bearing gamete from the opposite sex (equation \ref{eq:pAve}).
-The difference in $A$-allele-frequency among Y-bearing sperm versus X-bearing sperm is given by $\hat{p}^\male_Y-\hat{p}^\male_X=V_{A}\big{(}D^\male - D^\female+\alpha_{\Delta}^\male-\alpha_{\Delta}^\female+t^\male-t^\female\big{)}(1-2r)/(2r)$.
-
-%The new sex-determining allele, $m$, will spread in an XY system if $\lambda_{m}^{(XY)}>1$. 
-Eq \eqref{eq:lambda_neoY} demonstrates that, under weak selection, a neo-Y allele will invade an XY system ($\lambda_{Y'}^{(XY)}>1$) if and only if it is more closely linked to the selected locus than the ancestral sex-determining locus (i.e., if $R<r$; note that $V_{A}S_{A}^2$ is strictly positive as long as $\mathbf{A}$ is polymorphic).
-This echoes our results above where a neo-Y could never invade if $r\approx0$. 
-It is also consistent with the results of \cite{vanDoorn:2007eu}, who considered diploid selection only and also found that cis-GSD transitions can only occur when the new sex-determining locus is more closely linked to a locus under sexually-antagonistic selection.
-%Because tighter linkage between the sex-determining region and a selected locus evolves during these transitions, stronger associations between selected alleles and diploid sexes can build up by selection (e.g., between male-beneficial alleles and the male-determining allele, Y).%, increasing diploid mean fitness (Fig \ref{fig:Combination_MeanFit}).
-
-With weak selection and no haploid selection ($t^\Hermaphrodite=\alpha^\Hermaphrodite_{\Delta}=0$), the spread of a neo-W is equivalent to the spread of a neo-Y ($\lambda_{W'}^{(XY)}=\lambda_{Y'}^{(XY)}$), such that trans-GSD transitions can also occur only if the new sex-determining locus is more closely linked to a locus under selection ($R<r$), as found by \cite{vanDoorn:2010hu}.
-When there is haploid selection, invasion also typically occurs when the neo-W is more closely linked to the selected locus than the ancestral sex-determining region (Fig \ref{fig:Combination_Centimorgans}).
-For example, if the $\mathbf{A}$ locus is unlinked to the ancestral sex-determining locus ($r=1/2$), a more closely linked neo-W ($R<1/2$) can always invade.
-In this case, there is no ancestral association between $\mathbf{A}$ alleles and sex chromosomes in males, $\left( \hat{p}^\male_Y-\hat{p}^\male_X \right)=0$, see Eq \eqref{eq:freq_diffs}. 
-The second term in Eq \eqref{eq:lambda_neoW} therefore disappears and invasion depends only on the sign of $(r-R)$.%, as in the case of the neo-Y.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%A neo-W can invade an XY system under a large number of selective regimes
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-%\includegraphics[width=\linewidth]{PositionPlot}
-\caption{
-{\bf Ploidally-antagonistic selection allows a less tightly linked neo-W allele to invade.}
-In panel A, male drive ($\alpha^\male_{\Delta} = -1/20$, $t^\Hermaphrodite = \alpha^\female_{\Delta} = 0$) opposes selection in diploids (no sex-differences: $s^\Hermaphrodite = 1/10$, $h^\Hermaphrodite = 7/10$), in which case the new sex-determining allele can invade regardless of its linkage with the selected locus ($R$).
-In panel B, gametic competition in males ($t^\male = -1/10$, $t^\female = \alpha^\Hermaphrodite_{\Delta} = 0$) opposes selection in diploids (sex-differences: $s^\male = 3/20$, $s^\female = 1/20$, $h^\Hermaphrodite = 7/10$), in which case the new sex-determining allele can once again invade regardless of $R$.
-}
-\label{fig:Combination_Centimorgans}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-However, with haploid selection and $r<1/2$, the additional term in Eq \eqref{eq:lambda_neoW} can be positive.
-This can allow neo-W invasion ($\lambda_{W'}^{(XY)}>1$), even when the new sex-determining locus is less closely linked to the selected locus ($R>r$). 
-%These transitions are unusual because, when $R>r$, associations that selection has built up between alleles more favourable in one sex and alleles that determine sex will be weakened. 
-%Mean diploid fitness therefore decreases during heterogametic transitions that create looser sex-linkage (Fig \ref{fig:Combination_MeanFit}B,D). 
-%Eq \eqref{eq:lambda_neoW} shows that, with weak selection, neo-W alleles can invade an XY system for a large number of selective regimes. 
-%To clarify the parameter space under which $\lambda_{W'}^{(XY)}>1$ , we consider several special cases. 
-%Firstly, if the $\mathbf{A}$ locus is unlinked to the ancestral sex-determining region ($r=1/2$), a more closely linked neo-W ($R<1/2$) can always invade because there is no ancestral association between $A$ alleles and sex chromosomes in males, $\left( \hat{p}^\male_Y-\hat{p}^\male_X \right)=0$, see Eq \eqref{eq:freq_diffs}.
-%The second term in Eq \eqref{eq:lambda_neoW} therefore disappears and invasion depends only on the sign of $(r-R)$, as in the case of the neo-Y. 
-%Indeed, invasion typically occurs when the neo-W is more closely linked to the selected locus than the ancestral sex-determining region (Fig \ref{fig:Combination_Centimorgans}).
-To clarify the parameter space under which invasion occurs despite looser sex-linkage ($\lambda_{W'}^{(XY)}>1$ despite $R>r$), we focus on the special case where $R=1/2$ and $r<1/2$ (e.g., the selected locus is on the ancestral sex chromosome and the novel sex-determining locus arises on an autosome).
-In Table \ref{tab:specialcases} we give the conditions where invasion occurs when we further assume that haploid selection only occurs in one sex (e.g., during male meiosis only) and dominance coefficients are equal in the two sexes, $h^\female=h^\male$.
-When there is no gametic competition and meiotic drive is in one sex only, an unlinked neo-W can invade as long as the same allele is favoured during diploid selection in males and females ($s^\female s^\male>0$, see Fig \ref{fig:Combination_Centimorgans}A and Fig \ref{fig:SexRatioBad}B).
-%, which is 50\% of the parameter space.
-When there is no meiotic drive and gametic competition occurs in one sex only, an unlinked neo-W can invade as long as the same allele is favoured in male and female diploid selection and there are sex differences in selection of one type (e.g., $s^\female(s^\male-s^\female)>0$, see Fig \ref{fig:Combination_Centimorgans}B).
-%, which is 25\% of the parameter space.
-These special cases indicate that neo-W invasion occurs for a relatively large fraction of the parameter space, even if the neo-W uncouples the sex-determining locus from a locus under selection.
-
-\begin{table}[!ht]
-\centering
-\smallskip
-\caption{Invasion conditions for a neo-W allele at an unlinked locus ($R=1/2$) into an ancestral XY system with linkage ($r<1/2$) and one form of haploid selection}
-\begin{tabular}{l l c }
-\hline\hline
-Scenario &  Assumptions & neo-W spreads ($\lambda_{W'}^{(XY)}>1$) if \\ [0.5ex] \hline
-%  $r=1/2$, $R<1/2$ & Always \\ [0.5ex] \hline
-%  $r<1/2$, $R=1/2$ &  \\ [0.5ex] \hline
-\noalign{\vskip 1mm}
-  male drive only & $h^\male=h^\female$, $t^\female=t^\male=\alpha^\female_{\Delta}=0$ & $s^\female s^\male>0$ \\ [0.5ex]
- female drive only & $h^\male=h^\female$, $t^\female=t^\male=\alpha^\male_{\Delta}=0$ & $s^\female s^\male>0$ \\ [0.5ex]
- sperm competition only &  $h^\male=h^\female$, $t^\female=\alpha^\female_{\Delta}=\alpha^\male_{\Delta}=0$ & $s^\female(s^\male-s^\female)>0$ \\ [0.5ex]
-  egg competition only & $h^\male=h^\female$, $t^\male=\alpha^\female_{\Delta}=\alpha^\male_{\Delta}=0$ & $s^\male(s^\female-s^\male)>0$ \\ [0.5ex]
-  \hline \hline
-  \label{tab:specialcases}
- \end{tabular}
-\end{table}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Sex ratio selection is not a good predictor of neo-W invasion into an XY system
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-%\includegraphics[width=\linewidth]{Temporal_SR}
-\caption{
-{\bf Fisherian sex ratio selection alone is not a good predictor of turnover between sex-determining systems.}
-In this figure, selection is ploidally antagonistic with haploid selection favouring the $a$ allele during male meiosis.
-In panel A, male meiotic drive in an ancestral XY system causes a male bias (see Fig \ref{fig:model_outline}B), allowing a neo-W to invade and replace the ancestral sex-determining system (inset shows neo-W frequency among female gametes, reaching pseudo-fixation), which balances the zygotic sex ratio.
-In panel B, male drive in an ancestral ZW system has no effect on the zygotic sex ratio yet a neo-Y can invade and replace the ancestral sex-determining system (inset shows neo-Y frequency among male gametes, reaching pseudo-fixation).
-%When $R<1/2$, the neo-Y becomes associated with the allele favoured by drive, causing the zygotic sex ratio to become biased, hence the frequency of the neo-Y at pseudo-fixation can be higher than $0.5$ (inset).
-Parameters:  $s^\female =s^\male = 0.2$, $h^\female = h^\male = 0.7$, $t^\female = t^\male = \alpha^\female_\Delta = 0$, $\alpha^\male_\Delta = -0.1$, $r=0.02$.
-}
-\label{fig:SexRatioBad}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Previous research suggests that when the ancestral sex-determining locus is linked to a locus that experiences haploid selection (e.g., meiotic drive), alleles at a new, unlinked sex-determining locus invade to restore equal sex ratios~\cite{Kozielska:2010vm}.
-Consider, for example, the case where the $\mathbf{A}$ locus is linked to the ancestral sex-determining locus ($r<1/2$) and experiences meiotic drive in males only ($\alpha^\male_\Delta \neq 0$, $\alpha^\female_\Delta=0$), without gametic competition ($t^\female=t^\male=0$).
-In this case, the zygotic sex ratio can be initially biased only if the ancestral sex-determining system is XY (Fig \ref{fig:model_outline}A and Fig \ref{fig:SexRatioBad}B). 
-%If the ancxestral sex-determining system is ZW, the zygotic sex ratio will be 1:1 because diploid sex is determined by the proportion of Z-bearing versus W-bearing eggs and meiosis in females is fair (Fig \ref{fig:Combination_Turnover}D).
-If Fisherian sex ratio selection were dominant, we would thus expect a difference in the potential for XY to ZW and ZW to XY transitions. 
-%However, to leading order with selection weak relative to recombination, we find that sex ratio selection favours the spread of a neo-W by an amount equl to the spread of a neo-Y into a ZW system (relabeling XY as the heterogametic sex and reversing the labels of males and females in Table \ref{tab:specialcases})
-%However, to leading order with selection weak relative to recombination, we find that sex ratio selection favours the spread of a neo-W (through the first terms in table \ref{tab:haplotype_growth}) by an amount that is equal in magnitude to the fitness effects of alleles associated with new sex-determining alleles (second terms in table \ref{tab:haplotype_growth}).
-However, invasion by a neo-W allele into an XY system and invasion by a neo-Y allele into a ZW system occur under the same conditions ($\lambda_{Y'}^{(XY)} = \lambda_{W'}^{(ZW)}$ and $\lambda_{W'}^{(XY)}=\lambda_{Y'}^{(ZW)}$, at least to order $\epsilon^2$).
-For example, in Fig \ref{fig:SexRatioBad}A neo-W alleles invade an ancestral-XY system where females are initially rare, equalizing the sex ratio.
-However, Fig \ref{fig:SexRatioBad}B shows that a neo-Y can invade the resulting ZW system under the same conditions. 
-When $R<1/2$, the invading neo-Y becomes associated with the male meiotic drive allele and the zygotic sex ratio actually evolves to become male-biased.
-%
-%As selection becomes stronger (or linkage becomes tighter), this symmetry between sex ratio selection and haploid selection is lost, causing differences in the strength of selection favouring the two heterogametic transitions (compare red to black near -25cM and 25 cM in Fig \ref{fig:Combination_Centimorgans}).
-\textcolor{red}{normalise fitness in sexually antagonistic case}
-%
-%Why can new sex-determining regions invade when they are more loosely linked to selected loci ($R>r$)?  
-%Consider first the case where both sex-determining-loci are linked to the selected locus ($r<R<1/2$). 
-%In an ancestral-XY system, haploid selection in males can facilitate the spread of a neo-W because the zygotic sex ratio is ancestrally male biased and the W produces more of the rarer sex (Fig \ref{fig:SexRatioBad}A).
-%A new sex determining region can also, however, benefit from becoming more associated with drive. 
-%For example in an ancestral-ZW system with the same selection regime (haploid selection in males), a neo-Y can spread despite the fact that the zygotic sex is initially even; in this case, the neo-Y spreads because it is often found in males and can, if it carries the driven allele $a$, benefit from haploid selection in males (Fig \ref{fig:SexRatioBad}B).
-
-While equalizing the sex ratio and benefiting from drive are two primary reasons why haploid selection spurs sex chromosome transitions, even when the new sex-determining allele is less closely linked to the selected locus ($r<R$), more complex situations also arise.
-For example with $R=1/2$ in Fig \ref{fig:SexRatioBad}B (green curve), the neo-Y allele spreads despite the fact that it cannot benefit from drive because free recombination moves it randomly between driven and non-driven backgrounds.
-Nevertheless, the unlinked neo-Y can spread because diploids bearing it more often carry the non-driven allele $A$, which is found at high frequency on the W background and has higher average diploid fitness.% to balance the haploid advantage of the $a$ allele at equilibrium.
-
-\subsection*{Environmental sex determination}
-
-We next consider the case where the new sex-determining mutation, $m$, causes sex to be determined probabilistically or by heterogeneous environmental conditions (environmental sex determination, ESD), with individuals carrying allele $m$ developing as females with probability $k$.
-Here, we do not assume that the environmental conditions that determine sex also differentially affect the fitness of males versus females. 
-Such correlations can favour environmental sex-determining systems by allowing each sex to be produced in the environment in which it has highest fitness; in the absence of these correlations, previous theory would predict that ESD is favoured when it produces more equal sex ratios than the ancestral system (see reviews by~\cite{Charnov:1982wg,Bull:1983vi,West:2009we}).
-%(e.g., maternal condition, mate quality, age, or host size)
-
-The characteristic polynomial determining the leading eigenvalue (equations \ref{eq:recursions}) does not factor for ESD ($0<k<1$) as it does for a neo-Y ($k=0$) or neo-W ($k=1$) allele. 
-We therefore focus on weak selection here, where the leading eigenvalue is
-
-\begin{equation}
-\begin{split}
-\lambda_{ESD'}^{(XY)} =& 1 + \frac{{(1-2k)}^2}{4}V_{A}{S_{A}}^2\frac{r-R}{r R} \\
-&+\frac{k(\hat{p}^\male_Y-\hat{p}^\male_X)}{2}\left[ k \left(2\alpha_{\Delta}^\male-2\alpha_{\Delta}^\female+t^\male-t^\female \right) -2(1-k)S_{A}\right]+O\left(\epsilon^3\right).
-\end{split}
-\label{eq:lambda_ESD_k}
-\end{equation}
-
-\noindent
-This reduces to $\lambda_{Y'}^{(XY)}$ when $k=0$ and $\lambda_{W'}^{(XY)}$ when $k=1$.
-
-%Under Fisherian sex ratio selection, autosomal modifiers favour equal investment in male and female offspring, i.e., a 1:1 sex ratio~\cite{Fisher:1930wy,Charnov:1982wg,West:2009we}. 
-%A novel environmental sex-determiner that causes half of its carriers to become female and half to become male ($k=1/2$) will be in males half of the time and in females half of the time (like an autosome).
-%In addition, these novel sex-determination alleles equalize the sex ratio and therefore one might expect them to be favoured by Fisherian sex ratio selection when the resident sex ratio is biased.
-%However, assuming weak selection, we find that the growth rate of a rare, dominant offspring-controlled neo-ESD allele that produces males or females with equal probability ($k=1/2$) is
-Of particular interest are ESD mutations that cause half of their carriers to develop as females and half as males ($k=1/2$), creating equal sex ratios.
-The spread of such ESD is determined by
-\begin{equation}
-\lambda_{ESD'}^{(XY)} =1+ \frac{1}{2}\frac{(\lambda_{Y'\rvert R=1/2}^{(XY)}-1) + (\lambda_{W'\rvert R=1/2}^{(XY)}-1)}{2} + O\left(\epsilon^3\right),
-%V_A \frac{r}{1-2r}  \frac{s_{f} \left( s^\male - 3 s^\female\right) }{8 {\left( s_{f} + s_{m} \right)}^2} t_{m}^2.
-\label{eq:lambda_ESD}
-\end{equation}
-\noindent
-where $\lambda_{Y'\rvert R=1/2}^{(XY)}$ and $\lambda_{W'\rvert R=1/2}^{(XY)}$ represent $\lambda_{Y'}^{(XY)}$ and $\lambda_{W'}^{(XY)}$ when evaluated at $R=1/2$ (Equations \ref{eq:lambda_neoY} and \ref{eq:lambda_neoW}).
-That is, recombination between the selected locus and the novel sex-determining locus, $R$, does not enter into the $k=1/2$ results.
-This is because sex is essentially randomized each generation, %as if the novel sex-determiner were on an unlinked site that half the time acts as a neo-W and half the time as a neo-Y.
-preventing associations from building up between alleles at locus $\mathbf{A}$ and sex. 
-Eq \eqref{eq:lambda_ESD} shows that the ESD mutation gets half of the fitness of a feminizing mutation (neo-W) and half of the fitness of a masculinizing mutation (neo-Y), but only has an effect one half of the time (the other half of the time it produces the same sex as the ancestral system would have).
-As discussed above, $\lambda_{Y'\rvert R=1/2}^{(XY)}$ is necessarily less than one, but $\lambda_{W'\rvert R=1/2}^{(XY)}$ can be greater than one if there is haploid selection.
-That is, when there is haploid selection, ESD can invade an ancestrally-XY system because it generates females that are either rare or have high fitness, in the same manner as a neo-W.
-
-%An important result from Eq \eqref{eq:lambda_ESD} is that ESD can invade if there is haploid selection. 
-%When evaluated at $R=1/2$, $\Lambda_{Y',XY}$ is necessarily less than one, but $\Lambda_{W',XY}$ can be greater than one if there is haploid selection, as discussed above. 
-%Previous studies where ESD is favoured have typically assumed that environmental conditions (e.g., maternal condition, mate quality, age, or host size) can differentially affect the fitness of males versus females such that ESD invades because it allows sex determination to depend on the environment \citep[reviewed in][]{Charnov:1982wg,Bull:1983vi,West:2009we}.
-%Here, ESD mutations can spread because they generate females that are either rare or have high fitness, in the same manner as a neo-W.
-
-Significantly, Eq \eqref{eq:lambda_ESD} is the same whether ESD is invading an ancestrally XY or ZW system (because $\lambda_{Y'}^{(XY)} = \lambda_{W'}^{(ZW)}$ and $\lambda_{W'}^{(XY)} = \lambda_{Y'}^{(ZW)}$).
-Thus, Fisherian sex ratio selection alone does not easily explain GSD to ESD transitions.
-For example, when the ancestral sex-determining system is XY, but not ZW, the sex ratio is biased by male haploid selection.
-Nevertheless, ESD is equally likely to invade when it equalizes the zygotic sex ratio (through $\lambda_{W'}^{(XY)}$) as when it doesn't (through $\lambda_{Y'}^{(ZW)}$). 
-%This is again because haploid selection can facilitate the turnover of sex chromosomes either through sex ratio biases or through associations between the new sex determining region with selected alleles.
-%With weak selection, these two forces are nearly equal in strength. 
-In addition, we note that ESD may not invade, even if the sex ratio is initially biased (e.g., with drive in males only, $r<1/2$, $h^\female=h^\male$, and $s^\female s^\male<0$, then $\lambda_{W'}^{(XY)}<1$, see Table \ref{tab:specialcases}).
-We conclude that, as with neo-W and neo-Y loci, associations with selected loci mean that the evolution of ESD is not straightforwardly predicted by selection to balance the zygotic sex ratio when haploid selection is present.
-
-\section*{Discussion}
-
-%\textcolor{blue}{maybe re-order to put the results up front and focus on sex ratio less.
-Somewhere around these first two paragraphs we should include our tight linkage results.
-At the moment it doesn't make total sense because it assumes that tighter linkage is always favoured unless there is haploid selection.}
-
-%MAIN RESULT
-Two predominant theories explaining the remarkably high frequency of transitions between sex-determining systems are sexually-antagonistic selection and sex ratio selection (reviewed in~\cite{Blaser2012, vanDoorn2014re}).
-The former predicts that new sex-determining alleles can invade when they arise in closer linkage with a sexually-antagonistic locus ($r<R$,~\cite{vanDoorn:2007eu,vanDoorn:2010hu, Muralidhar2018}).
-The latter predicts that new sex-determining systems are generally favoured if they result in more equal sex ratios than the ancestral system. 
-%The latter predicts that neo-W alleles will invade an XY system when there is a male bias caused by haploid selection in males, and vice-versa, a neo-Y will invade a ZW system when there is a female bias caused by haploid selection in females~\cite{Kozielska:2010vm,Ubeda:2015fx}.
-In contrast to these prevailing views, we show that selection (including sexually-antagonistic selection, overdominance, and/or ploidally-antagonistic selection) on loci tightly linked to the ancestral sex-determining locus can favour trans-GSD transitions (XY$\leftrightarrow$ ZW) to new sex-determining systems that are less closely linked to the selected loci (e.g., see Fig \ref{fig:SexAntagTighter}).
-Similarly, even when linkage is weak relative to selection, we show that %new sex-determining alleles are typically favoured if they are more closely linked to a locus under haploid selection (even in the absence of diploid sex differences), which is the only condition favouring cis-GSD transitions (XY to XY or ZW to ZW).
-%In addition, with haploid selection and weak selection, 
-trans-GSD transitions can occur where the new sex-determining locus is less closely linked to the locus under selection if there is haploid selection (e.g., Figs \ref{fig:Combination_Centimorgans} and \ref{fig:SexRatioBad}).
-
-We find that the spread of new sex-determining systems cannot be simply predicted from their effect on the sex ratio. 
-On one hand, sex ratio biases caused by haploid selection can facilitate trans-GSD transitions or transitions from genetic to environmental sex determination. 
-For instance, alleles favoured by haploid selection in males often become associated with the Y allele, which leads to a male-biased zygotic sex ratio.
-This male bias increases the potential for a neo-W allele to invade (Table \ref{tab:haplotype_growth}), which can equalize the sex ratio (e.g., see Fig \ref{fig:SexRatioBad}B, for related examples see~\cite{Kozielska:2010vm}).
-%We find that sex ratio biases caused by haploid selection can also affect transitions between sex-determining systems (e.g., see $\zeta$ terms in Table \ref{tab:haplotype_growth}). 
-%However, the neo-W may not equalize the sex ratio (e.g., if the driving allele also drives in females or affects competition among eggs)
-On the other hand, sex ratio selection can be overwhelmed by additional selective effects, preventing a neo-W or ESD allele from invading, even if it would balance the sex ratio (e.g., when selection acts in opposite directions in male and female diploids, Table \ref{tab:specialcases}).
-%and equalizing the sex ratio.
-Indeed, transitions between sex-determining systems can generate stronger sex ratio biases (e.g., Fig \ref{fig:SexRatioBad}A and step 1 in~\cite{Ubeda:2015fx}).
-%For example, where a neo-Y invades and is linked with a locus that experiences haploid selection in male gametes, the sex ratio evolves to become biased \citep[e.g., see Fig \ref{fig:SexRatioBad}A and step 1 in][]{Ubeda:2015fx}.
-%For example, in an ancestral ZW system, haploid selection in males can allow a linked neo-Y to invade, despite the fact that it creates a male-biased sex ratio because the neo-Y becomes associated with the driven allele (Fig \ref{fig:SexRatioBad}A).
-%\textcolor{blue}{and figure 1, where the end of one panel is the same as the beginning of another, however, this figure may change).}
-%What we would like to stress is that sex ratio selection alone cannot predict when new sex-determining systems can evolve.
-Significantly, with weak selection, we find that there is no difference in conditions allowing XY to ZW and ZW to XY transitions, indicating that sex chromosome transitions are not predominantly predicted by their effect on the sex ratio (i.e., the sex ratio bias created by male haploid selection facilitates the spread of a neo-W allele into an XY system to the same degree that male haploid selection drives the spread of a neo-Y into a ZW system with a 1:1 sex ratio).
-%An asymmetry can develop when sex-linkage is tight (e.g., Fig \ref{fig:Combination_Centimorgans} near -25cM and 25cM) but under most circumstances we do not predict asymmetry between XY to ZW and ZW to XY transitions despite the presence/absence of sex ratio selection.
-Thus, haploid selection can favour trans-GSD transitions both via sex ratio selection and via selection on alleles associated with the new sex-determining allele, and these selective pressures are often predicted to be of equal magnitude.
-
-%HAPLOID SELECTION (genomic location of haploid selected loci and comparative patterns) 
-We have shown that the spread of new sex-determining systems can be driven by loci experiencing haploid selection. 
-%Our results suggest that haploid selected loci that have been involved in driving turnovers between sex-determining systems could occur around the ancestral- or novel-sex-determining regions. 
-%Our results suggest that polymorphic loci that are ancestrally sex-linked and under sex-specific selection could also drive heterogametic transitions between sex-determining systems. 
-%As with sexually-antagonistic selection, the presence of haploid selected loci around ancestral- or novel-sex-determining regions could support their role in sex chromosome turnover.
-In agreement with this hypothesis, a recent transcriptome analysis in Rumex shows that pollen-biased expression (relative to expression in flower buds or leaves) is enhanced among XY-linked genes compared to autosomal genes or compared to hemizygous genes that are only linked to the X (Sandler et al., 2018, personal communication).
-In addition, Y-linked genes are over-expressed relative to X-linked genes in pollen (but not in flower buds or leaves). 
-This suggests that the spread of neo-Y chromosomes in this clade could have been favoured through linkage with haploid selected genes. 
-%maybe add a flag here for switching to clade-level expectations:
-In general, we predict that haploid selection increases lability of sex-determining systems, particularly because haploid selection can cause transitions that increase or decrease sex-linkage (e.g., the final state of the red line in Fig \ref{fig:SexRatioBad}B is the starting state in Fig \ref{fig:SexRatioBad}A).
-Frequent turnovers driven by haploid selection may help to explain the relative rarity of heteromorphic sex chromosomes in plants, which are thought to experience more selection during their multicellular haploid stage.
-
-If haploid selection is strong but selective differences between male and female diploids are weak, we find that trans-GSD transitions are favoured more strongly than cis-GSD transitions, with transitions to ESD intermediate (e.g., with $|D^\male - D^\female| << |\alpha_\Delta^\male - \alpha_\Delta^\female + t^\male - t^\female|$ we have $\lambda_{W'}^{(XY)} > \lambda_{Y'}^{(XY)}$; Equations \ref{eq:lambda_neoW} and \ref{eq:freq_diffs}).
-Among the relatively few dioecious clades in which multiple species have well characterized sex chromosomes~\cite{Ming:2011iy}, trans-GSD transitions have been inferred in \textit{Silene} subsection \textit{Otites}~\cite{Slancarova:2013dq} and in \textit{Salicaceae}~\cite{Pucholt2015,Pucholt2017}.
-%Potentially, successive heterogametic transitions between master regulators of sex-determination could be inferred from careful examination of the molecular pathways by which sex is determined. 
-%Our predictions could also be examined using a suitable proxy for haploid selection, for example, \cite{Lenormand:2005vb} use the outcrossing rate in plants as a proxy for the strength of pollen competition.
-Assuming that transitions from dioecy to hermaphroditism (equal parental investment in male and female gametes) are favoured in a similar manner to the ESD examined here (equal probability of zygotes developing as males or females), our results suggest that competition during the haploid stage could also drive transitions between dioecy and hermaphroditism, which are frequent in plants~\cite{Kafer2017, Goldberg2017}.
-
-In support of their role in sex chromosome turnover, genes expected to be under sexually-antagonistic selection (e.g., those causing bright male colouration) have been found on recently derived sex chromosomes~\cite{Lindholm:2002dw,Tripathi:2009cw,Ser:2010iq}.
-Our results show, however, that tight ancestral-linkage of polymorphic loci, maintained by sexually-antagonistic selection or otherwise, can also drive trans-GSD transitions. 
-In addition, we find that polymorphic sex determining systems (X, Y, W, and Z alleles all present) can be maintained when a selected locus is tightly linked to the ancestral sex-determining system (e.g., \nameref{fig:freqAll}B and \nameref{fig:freqAll}C), which is not possible with loose linkage~\cite{vanDoorn:2010hu}.
-%As noted by \citet{vanDoorn:2010hu}, it would be prudent to compare closely related clades in order to determine whether observed polymorphisms predate a transition in sex-determination or arose afterwards.
-%, particularly because sex-linkage allows sexually-antagonistic selection to maintain polymorphisms under a different and larger parameter space~\cite{Rice:1987hs,Jordan:2011fj}.
-For example, our results suggest a potential mechanism maintaining multiple sex determining alleles in the platyfish (\textit{Xiphophorus maculatus}), in which X,Y, and W alleles segregate at one locus (or two closely-linked loci) near to potentially sexually-antagonistic genes for pigmentation and sexual maturity~\cite{Kallman1965,Kallman1968, Volff2001, Schultheis2006}.
-Several rodent species also maintain feminizing alleles along with the ancestral X and Y sex-determination alleles (reviewed in~\cite{Fredga1994}). 
-For example, in nine \textit{Akadon} species, it appears that male-determining-\textit{sry} expression is suppressed by an autosomal feminizing allele, creating XY females~\cite{Bianchi2002,Sanchez2010}, which have increased fitness relative to XX females~\cite{Hoekstra2001}.
-In \textit{Mus microtoides}, females can have XX, XX$^\ast$ or X$^\ast$Y genotypes~\cite{Veyrunes2010}. 
-Previous theory would predict that the X$^\ast$ chromosome (or the autosome it is fused to) harbours female beneficial alleles, driving its spread. 
-However, XX and XX$^\ast$ females have similar fitness, whereas X$^\ast$Y female fitness is enhanced~\cite{Saunders2014,Saunders2016, Veyrunes2017}.
-Although Y-linkage of female-beneficial alleles is counterintuitive, our model suggests that it can be stably maintained and then favour new feminizing mutations, which is a parsimonious explanation for the spread of feminizing alleles in these rodent species.
-
-%Limitation 1: DEGENERATE Y
-We note that we assume that sex-determining alleles do not experience direct selection except via their associations with sex and selected alleles.
-However, in some cases, there may be significant degeneration around the sex-limited allele (Y or W) in the ancestral sex-determining region because recessive deleterious mutations and/or deletions accumulate in this non-recombining regions~\cite{Rice:1996ke,Charlesworth:2000cc,Bachtrog:2006ed,Marais:2008hm}.
-During trans-GSD transitions, but not cis-GSD transitions, any recessive deleterious alleles linked to the Y or W are revealed to selection in YY or WW individuals~\cite{Bachtrog:2014bx}. 
-This phenomenon was studied by van Doorn and Kirkpatrick (2010)~\cite{vanDoorn:2010hu}, who found that degeneration can prevent fixation of a neo-W or a neo-Y allele, leading to a mixed sex-determining system where the ancestral and new sex-determining loci are both segregating.
-However, they noted that very rare recombination events around the ancestral sex-determining locus can allow these trans-GSD transitions to complete.  
-%While not explicitly studied, we also predict that Y or W degeneration would prevent fixation of the new sex-determining genes considered here.
-Degeneration around the Y or W could explain why trans-GSD transitions are not observed to be much more common than cis-GSD transitions despite the fact that our models demonstrate that they are favoured under a wider range of conditions, especially with haploid selection.
-For example, there are a dozen sex chromosome configurations among Dipteran species but only one transition between male and female heterogamety~\cite{Vicoso:2015hf}.
-
-%Limitation 3: don't consider m alleles with similar k to ancester, no ancestral ESD considered
-In this study, we have only considered new sex-determining alleles of large effect. 
-However, we expect similar selective forces to act on masculinizing/feminizing alleles of weaker effect. 
-For example, small effect masculinizing/feminizing alleles within a threshold model of sex determination can be favoured when linked to loci that experience sexually-antagonistic selection~\cite{Muralidhar2018}.
-These results echo those for large-effect neo-Y/neo-W alleles~\cite{vanDoorn:2007eu,vanDoorn:2010hu}.
-Finally, while we have considered cis-GSD, trans-GSD, and GSD to ESD transitions, we have not explicitly considered ESD to GSD transitions. 
-Recent models of ESD to GSD transitions~\cite{Ubeda:2015fx,Muralidhar2018} show that that neo-Y/neo-W alleles can be favoured when they arise near to haploid and/or diploid selected loci, which also occurs in our model.
-
-%Limitation 2: TWO ALLELE DRIVE
-%Another simplification that we made is that meiotic drive involves only a single locus with two alleles. 
-%However, many meiotic drive systems involve an interaction with another locus at which alleles may `suppress' the action of meiotic drive \citep[][]{Burt:2006,Lindholm:2016cw}.
-%Thus, the dynamics of meiotic drive alleles can be heavily dependent on the interaction between two loci and the recombination rate between them, which in turn can be affected by sex-linkage if there is reduced recombination between sex chromosomes~\cite{Hurst:1991uh}.
-%Furthermore, in some cases, a driving allele may act by killing any gametes that carry a `target' allele at another locus, in which case there can be fertility effects that alter the equilibrium frequency of a meiotic drive allele~\cite{Holman:2015en}.
-%In polygamous mating systems, the intensity of pollen/sperm competition can depend on the density of males available to donate pollen/sperm, which can itself depend on the sex ratio~\cite{Taylor:2002wu}.
-%In terms of our model, this implies that the strength of gametic competition ($t^\male$) may both determine and be determined by the sex ratio. 
-%How the evolution of new sex-determining mechanisms could be influenced by two-locus meiotic drive and/or by ecological feedbacks under different mating systems remains to be studied.
-
-\section*{Conclusion}
-
-We have shown that tight sex-linkage and haploid selection can drive previously unexpected transitions between sex-determining systems.
-In particular, both can select for new sex-determining loci that are more loosely linked to loci under selection. 
-In addition, haploid selection can cause transitions analogous to those caused by purely sexually-antagonistic selection, eliminating the need for differences in selection between male and female diploids.
-We conclude that haploid selection should be considered as a pivotal factor driving transitions between sex-determining systems. 
-Perhaps counterintuitively, transitions involving haploid selection can be driven by sex ratio selection or cause sex ratio biases to evolve; we do not find Fisherian sex ratio selection to be an overwhelming force.
-Overall, our results suggest several new scenarios under which new sex-determining systems are favoured, which could help to explain why the evolution of sex-determining systems is so dynamic.
-
-% For figure citations, please use "Fig" instead of "Figure".
-
-% Place figure captions after the first paragraph in which they are cited.
-
-% Results and Discussion can be combined.
-
-% Place tables after the first paragraph in which they are cited.
-
-%PLOS does not support heading levels beyond the 3rd (no 4th level headings).
-
-\section*{Supporting information}
-
-\paragraph*{S1 File.}
-\label{file:Mathematica}
-{\bf Supplementary \textit{Mathematica} file.}  This file can be used to re-derive our results and generate figures.
-
-\paragraph*{S1 Table}
-\label{tab:chisubstitutions}
-{\bf Substitutions for different loci orders assuming no interference.}
-
-\paragraph*{S2 Table}
-\label{tab:meanfitnesses}
-{\bf Mean fitnesses and zygotic sex ratio in the resident population ($M$ fixed, XY sex determination). }
-
-\paragraph*{S1 Appendix.}
-\label{app:recurs}
-{\bf Recursion equations and complete model description.}
-
-\paragraph*{S2 Appendix.}
-\label{app:eq_stab}
-{\bf Equilibria and stability conditions when $M$ allele is fixed. }
-
-\paragraph*{S3 Appendix.}
-\label{app:inv_cond}
-{\bf Invasion conditions for the $m$ allele.}
-
-% Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
-\paragraph*{S1 Fig.}
-\label{fig:positionOverdominance}
-{\bf With overdominance, loci near to the ancestral sex-determining locus ($r\approx0$) can favour neo-W alleles that are less tightly linked ($R>r$).} 
-In panels A and B, the $a$ allele is favoured in females ($w_{aa}^\female=1.05$, $w_{Aa}^\Hermaphrodite=1$, $w_{AA}^\female=0.85$) and selection in males is overdominant ($w_{aa}^\male=w_{AA}^\male=0.75$).
-In panels C and D, selection in males and females is overdominant ($w_{aa}^\female=w_{AA}^\female=0.6$, $w_{aa}^\male=0.5$, $w_{AA}^\male=0.7$, $w_{Aa}^\Hermaphrodite=1$).
-There is no haploid selection $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
-These parameters are marked by daggers in Fig \ref{fig:regionplots}B and C, which show that neo-W invasion is expected for any $R$ ($\Lambda_{W'A}^{(XY)},\Lambda_{W'a}^{(XY)}>1$) if the $a$ allele is nearly fixed on the Y (black lines in this figure; not stable for $r>>0$).
-Equilibria where the $A$ allele is more common among Y-bearing male gametes can also be stable and allow neo-W invasion for these parameters (blue lines). 
-%The weak selection approximation holds when all recombination rates are large relative to selection (around 0 in panels A and C), in which case, in the absence of haploid selection, neo-W alleles should spread if and only if they are more tightly linked to the selected locus (positive invasion fitness if and only if the selected locus is in the grey region).
-%However, when recombination rates are small (panels B and D and when the selected locus is near the SDRs in all panels), this weak selection prediction can break down.
-
-\paragraph*{S2 Fig.}
-\label{fig:temporalOverdominance}
-{\bf Following invasion by a neo-W allele, there can be a complete transition to a new sex-determining system, maintenance of both ancestral-XY and neo-ZW sex determining systems, or loss of the new sex-determining allele.}
-Here, we plot the frequency of the neo-W allele among female gametes.
-%; as the neo-W reaches frequency $0.5$, polymorphism at the ancestral XY locus is lost with Y becoming fixed such that sex is determined only be the ZW allele carried by a female gamete. 
-Panels A, C and D show cases where a steady state is reached with the neo-W at a frequency below $0.5$, in which case ancestral-X and Y alleles also both segregate. 
-In all cases, we assume that the $a$ allele is initially more common than the $A$ allele on the Y background (Y-$a$ is fixed when $r=0$). 
-When $r>0$ (panels B and D), Y-$A$ haplotypes created by recombination can become more common than Y-$a$ haplotypes as the neo-W spreads.
-In B, this leads to loss of the neo-W and the system goes to an equilibrium with X-$a$ and Y-$A$ haplotypes fixed (equilibrium $A'$), such that all females have the high fitness genotype $aa$ and all males are $Aa$.
-For the parameters in B, neo-W alleles have negative invasion fitness when the Y-$A$ haplotype is ancestrally more common than Y-$a$ (compare blue to black curves in \nameref{fig:positionOverdominance}A and  \nameref{fig:positionOverdominance}B near the ancestral sex-determining locus).
-In contrast, the neo-W is not lost in panel D as it is favoured regardless of whether Y-$A$ or Y-$a$ haplotypes predominate (again, compare blue to black curves in \nameref{fig:positionOverdominance}C and  \nameref{fig:positionOverdominance}D).
-%Fitness parameters are the same as in \nameref{fig:positionOverdominance}; in panels A and B the $a$ allele is favoured in females ($w_{aa}^\female=1.05$, $w_{Aa}^\Hermaphrodite=1$, $w_{AA}^\female=0.85$) while there is overdominance in males ($w_{aa}^\male=w_{AA}^\male=0.75$) and in panels C and D, there is overdominance in both sexes ($w_{aa}^\female=w_{AA}^\female=0.6$, $w_{aa}^\male=0.5$, $w_{AA}^\male=0.7$, $w_{Aa}^\Hermaphrodite=1$).
-%These parameters are marked by a dagger in Fig \ref{fig:regionplots}. 
-%Here, there is no haploid selection $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
-
-\paragraph*{S3 Fig.}
-\label{fig:SexAntagTighterMaleDrive}
-{\bf  When there is sexually-antagonistic selection and haploid selection, a neo-W allele may invade for any $R$.}
-Panel A shows that the invasion fitness of a neo-W is positive, even when $r<R$ (unshaded region).
-In panel B, we vary the recombination rate between the neo-W and the selected locus ($R$) for a fixed recombination rate between the ancestral sex-determining locus and the selected locus ($r=0.005$).
-Coloured markers show recombination rates for which the temporal dynamics of neo-W invasion are plotted in panel C (black $R=0.001$, red $R=0.02$, blue $R=0.1$, green $R=0.5$). 
-The diploid selection parameters used in this plot are the same as in Fig \ref{fig:SexAntagTighter}. 
-There is also meiotic drive in males favouring $a$ ($\alpha_{\Delta}^\male=-0.08$), this full set of parameters is marked by an asterisk in \nameref{fig:regionMaleDrive}A.
-When $R=0.5$ (green curve), the neo-W does not reach fixation and X, Y, Z, and W alleles are all maintained in the population, see \nameref{fig:freqAll}C.
-
-\paragraph*{S4 Fig.}
-\label{fig:regionMaleDrive}
-{\bf Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is male meiotic drive at a locus that is tightly linked to the ancestral XY locus ($r=0$).}
-This figure is equivalent to Fig \ref{fig:regionplots} but with meiotic drive in males.
-%We vary the fitness of male homozygotes relative to heterozygotes ($w_{Aa}^\Hermaphrodite=1$) and only consider stable equilibria at which both $\mathbf{A}$ locus allele are maintained and the $a$ allele is initially fixed on the Y, region outlined.
-In panels A-C, meiotic drive in males favours the $a$ allele ($\alpha_{\Delta}^\male=-0.16$), creating male-biased sex ratios and generally increasing $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$.
-By contrast, $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$ tend to be reduced when meiotic drive in males favours the $A$ allele ($\alpha_{\Delta}^\male=0.16$), panels D-F. 
-%We consider three forms of selection in females: directional selection in favour of the $A$ allele (panels A and D, $w_{aa}^\female=0.85$, $w_{AA}^\female=1.05$), direction selection in favour of the $a$ allele (panels B and E, $w_{aa}^\female=1.05$, $w_{AA}^\female=0.85$), and overdominance (panels C and F, $w_{aa}^\female=w_{AA}^\female=0.6$).
-
-\paragraph*{S5 Fig.}
-\label{fig:regionMaleGS}
-{\bf Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is male gametic competition at a locus that is tightly linked to the ancestral XY locus ($r=0$).}
-This figure is equivalent to Fig \ref{fig:regionplots} but with gametic competition in males.
-%Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in \nameref{fig:regionMaleDrive}. 
-The $a$ allele is favoured during male gametic competition in Panels A-C ($w_{a}^\male=1.16$, $w_{A}^\male=1$), which creates male biased sex ratios and increases $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$.
-By contrast, $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$ tend to be reduced when the $A$ allele is favoured during male gametic competition, panels D-F.
-Compared to the meiotic drive parameters in \nameref{fig:regionMaleDrive}, the effect of these male gametic competition parameters on the sex ratio is smaller. 
-For example, in \nameref{fig:regionMaleDrive}A-C, the ancestral sex ratio is $\alpha^\male=0.58$ at equilibrium (B) and in panels A-C of this plot, the ancestral sex ratio is $w_{a}^\male/(w_{A}^\male+w_{a}^\male)=0.537$ at equilibrium (B).
-
-\paragraph*{S6 Fig.}
-\label{fig:regionFemaleDrive}
-{\bf Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is female meiotic drive at a locus that is tightly linked to the ancestral XY locus ($r=0$).}
-This figure is equivalent to Fig \ref{fig:regionplots} but with meiotic drive in females.
-%Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in \nameref{fig:regionMaleDrive} and \nameref{fig:regionMaleGS}. 
-The $a$ allele is favoured by meiotic drive in females in Panels A-C ($\alpha_{\Delta}^\female=-0.16$), which increases $\Lambda_{W'a}^{(XY)}$ and decreases $\Lambda_{W'A}^{(XY)}$. 
-Female meiotic drive in favour of the $A$ allele (panels D-F, $\alpha_{\Delta}^\female=-0.16$) has the opposite effect.
-
-\paragraph*{S7 Fig.}
-\label{fig:regionFemaleGS}
-{\bf Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is female gametic competition at a locus that is tightly linked to the ancestral XY locus ($r=0$).}
-This figure is equivalent to Fig \ref{fig:regionplots} but with gametic competition in females.
-%Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in \nameref{fig:regionMaleDrive}, \nameref{fig:regionMaleGS}, and \nameref{fig:regionFemaleDrive}. 
-The $a$ allele is favoured during female gametic competition in females in Panels A-C ($w_{a}^\female=1.16$, $w_{A}^\female=1$), which increases $\Lambda_{W'a}^{(XY)}$ and decreases $\Lambda_{W'A}^{(XY)}$.
-The $A$ allele is favoured during gametic competition in panels D-F ($w_{a}^\female=1$, $w_{A}^\female=1.16$), giving the opposite effect on $\Lambda_{W'a}^{(XY)}$ and $\Lambda_{W'A}^{(XY)}$.
-
-\paragraph*{S8 Fig.}
-\label{fig:regionPloidAntag}
-{\bf Ploidally-antagonistic selection can drive the spread of neo-W alleles. }
-A-D show when each of the neo-W haplotypes invades an internally stable equilibrium with $a$ fixed on the Y (found by setting $r=0$).
-The y-axis shows directional selection in diploids of both sexes, $s^\female=s^\male$, and the x-axes show sex-specific drive, $\alpha_\Delta^\Hermaphrodite$, or haploid competition, $t^\Hermaphrodite$.
-The top left and bottom right quadrants therefore imply ploidally-antagonistic selection (and these are the only places where neo-W haplotypes can invade).
-Dominance is equal in both sexes, $h^\female=h^\male=3/4$. 
-E-F show the temporal dynamics of neo-W frequency in females with parameters given by the asterisks in the corresponding A-D plot, with $r=1/200$, for four different $R$.
-Black $R=1/1000$, Red $R=2/100$, Blue $R=1/10$, Green $R=1/2$.
-
-\paragraph*{S9 Fig.}
-\label{fig:freqAll}
-{\bf Pseudo-fixation of neo-W or maintenance of multiple sex-determining alleles. }
-The curves show the frequencies of the neo-W (red), ancestral Y (blue), and $A$ allele (black) among female gametes (solid curves) and among male gametes (dashed curves). 
-In panel A, there is a complete transition from XY sex determination (XX-ZZ females and XY-ZZ males) to ZW sex determination (YY-ZW females and YY-ZZ males).  
-In panels B and C a polymorphism is maintained at both the ancestral XY locus and the new ZW locus, such that there are males with genotypes XY-ZZ and YY-ZZ and females with genotypes XX-ZZ, XX-ZW, XY-ZW, and YY-ZW.
-In panel A, selection is ploidally-antagonistic with drive in males (parameters as in the green curve in Fig \ref{fig:SexRatioBad}B).
-In panel B, there is overdominance in both sexes and no haploid selection (parameters as in the green curve in \nameref{fig:temporalOverdominance}C).
-In panel C, there is sexually-antagonistic selection in diploids with drive in males (parameters as in the green curve in \nameref{fig:regionMaleDrive}C).
-In all cases, the initial equilibrium frequency has $a$ near fixation on the Y.
-
-%\section*{Acknowledgments}
-%This project was supported by the Natural Sciences and Engineering Research Council of Canada (CGS-D 6564 to MMO; RGPIN-2016-03711 to SPO).
-
-\nolinenumbers
-
-% Either type in your references using
-% \begin{thebibliography}{}
-% \bibitem{}
-% Text
-% \end{thebibliography}
-%
-% or
-%
-% Compile your BiBTeX database using our plos2015.bst
-% style file and paste the contents of your .bbl file
-% here. See http://journals.plos.org/plosone/s/latex for 
-% step-by-step instructions.
-% 
-\bibliography{sex_chromosomes.bib}
-
-\newpage
 
@@
 
-\newpage
-
-\setcounter{equation}{0}
-\renewcommand{\theequation}{S2.\arabic{equation}}
-
-\section*{S2 Appendix}
-
-\subsection*{Resident equilibria and stability}
-
-In the resident population (allele $M$ fixed), we follow the frequency of $A$ in X-bearing female gametes, $p^\female_X$, and X-bearing male gametes, $p^\male_X$, and Y-bearing male gametes, $p^\male_Y$.
-We also track the total frequency of Y among male gametes, $q$, which may deviate from $1/2$ due to meiotic drive in males. 
-These four variables determine the frequencies of the six resident gamete types, which sum to one in each sex: $x_{1}^{\female}=\hat{p}_X^\female$, $x_{2}^{\female}=1-\hat{p}_X^\female$, $x_{1}^{\male}=(1-q)\hat{p}_X^\male$, $x_{2}^{\male}=(1-q)(1-\hat{p}_X^\male)$, $y_{1}^{\male}=q \hat{p}_Y^\male$, and $y_{2}^{\male}=q(1-\hat{p}_Y^\male)$.
-Mean fitnesses in the resident population are given in \nameref{tab:meanfitnesses}.
-
-Various forms of selection can maintain a polymorphism at the $\mathbf{A}$ locus, including sexually antagonistic selection, overdominance, conflicts between diploid selection and selection upon haploid genotypes (ploidally-antagonsitic selection,~\cite{Immler:2012tl}), or a combination of these selective regimes (see below).
-
-In particular special cases, e.g., no sex-differences in selection or meiotic drive ($s^\male=s^\female$, $h^\male=h^\female$, and $\alpha^\male=\alpha^\female=1/2$), the equilibrium allele frequency and stability can be calculated analytically without assuming anything about the relative strengths of selection and recombination.
-However, here, we focus on two regimes (tight linkage between $\mathbf{A}$ and $\mathbf{X}$ and weak selection) in order to make fewer assumptions about fitnesses.
-
-\subsubsection*{Tight linkage between $\mathbf{X}$ and $\mathbf{A}$ loci}
-
-We first calculate the equilibria in the ancestral population when the recombination rate between the $\mathbf{X}$ and $\mathbf{A}$ loci is small ($r$ of order $\epsilon$). 
-Selection at the $\mathbf{A}$ locus will not affect evolution at the novel sex-determining locus, $\mathbf{M}$, if one allele is fixed on all backgrounds. 
-We therefore focus on the five equilibria that maintain both $A$ and $a$ alleles, four of which are given to leading order by:
-
-\begin{subequations}\label{eq:tightequil}
-\begin{align}
-(A)\ \ \ &\hat{p}_{Y}^{\male}=0,
-\ \hat{q}=\frac{1}{2}\left(1 - \alpha_\Delta^\male \frac{ w_{Aa}^{\male} \phi}{w_{Aa}^{\male} \phi+ w_{aa}^{\male} \psi}\right),\\
-&\hat{p}_{X}^{\female}=\frac{w_{a}^{\female} \phi}{w_{a}^{\female} \phi+ w_{A}^{\female} \psi},
-\ \hat{p}_{X}^{\male}=\frac{(1+\alpha_\Delta^\male)w_{Aa}^{\male} \phi}{(1+\alpha_\Delta^\male)w_{Aa}^{\male} \phi +w_{aa}^{\male} \psi} \nonumber \\
-(A')\ \ \ &\hat{p}_{Y}^{\male}=1,
-\ \hat{q}=\frac{1}{2}\left(1 + \alpha_\Delta^\male \frac{w_{Aa}^{\male} \phi'}{w_{Aa}^{\male} \phi' + w_{AA}^{\male} \psi'}\right),\\
-&\hat{p}_{X}^{\female}=1-\frac{w_{A}^{\female} \phi'}{w_{A}^{\female} \phi'+ w_{a}^{\female} \psi'},
-\ \hat{p}_{X}^{\male}=1-\frac{(1-\alpha_\Delta^\male)w_{Aa}^{\male} \phi'}{(1-\alpha_\Delta^\male)w_{Aa}^{\male} \phi'+w_{AA}^{\male} \psi'} \nonumber \\
-(B)\ \ \ &\hat{p}_{Y}^{\male}=0,\ \hat{p}_{X}^{\female}=1,\ \hat{p}_{X}^{\male}=1, \ \hat{q}=(1 -\alpha^\male_\Delta)/2\\
-(B')\ \ \ &\hat{p}_{Y}^{\male}=1,\ \hat{p}_{X}^{\female}=0,\ \hat{p}_{X}^{\male}=0, \ \hat{q}=(1+\alpha^\male_\Delta)/2
-\end{align}
-\end{subequations}
-\begin{equation*}
-\begin{split}
-\phi=&(1+\alpha^\female_\Delta) w_{A}^{\female} w_{Aa}^{\female} \left[ w_{a}^{\male} w_{aa}^{\male} + (1+\alpha_\Delta^\male) w_{A}^{\male} w_{Aa}^{\male} \right]/2 - w_{a}^{\male} w_{a}^{\female} w_{aa}^{\male} w_{aa}^{\female} \\
-\psi=&(1-\alpha^\female_\Delta) w_{a}^{\female} w_{Aa}^{\female} \left[ w_{a}^{\male} w_{aa}^{\male} + (1+\alpha_\Delta^\male) w_{A}^{\male} w_{Aa}^{\male}\right]/2 - (1+\alpha_\Delta^\male) w_{A}^{\male} w_{A}^{\female} w_{Aa}^{\male} w_{AA}^{\female}\\
-\phi'=&(1-\alpha^\female_\Delta) w_{a}^{\female} w_{Aa}^{\female} \left[ w_{A}^{\male} w_{AA}^{\male} + (1-\alpha_\Delta^\male) w_{a}^{\male} w_{Aa}^{\male} \right]/2 - w_{A}^{\male} w_{A}^{\female} w_{AA}^{\male} w_{AA}^{\female}\\
-\psi'=&(1+\alpha^\female_\Delta) w_{A}^{\female} w_{Aa}^{\female} \left[ w_{A}^{\male} w_{AA}^{\male} + (1-\alpha_\Delta^\male) w_{a}^{\male} w_{Aa}^{\male} \right]/2 - (1-\alpha_\Delta^\male) w_{a}^{\male} w_{a}^{\female} w_{Aa}^{\male} w_{aa}^{\female}.
-\end{split}
-\end{equation*}
-
-\noindent
-A fifth equilibrium $(C)$ also exists where $A$ is present at an intermediate frequency on the Y background ($0<\hat{p}_{Y}^{\male}<1$). 
-However, equilibrium $(C)$ is never locally stable when $r \approx 0$ and is therefore not considered further.
-Thus, the Y background can either be fixed for the $a$ allele (equilibria ($A$) and ($B$)) or the $A$ allele (equilibria ($A'$) and ($B'$)).
-The X background can then either be polymorphic (equilibria ($A$) and ($A'$)) or fixed for the alternative allele (equilibria ($B$) and ($B'$)).
-Since equilibria $(A)$ and $(B)$ are equivalent to equilibria $(A')$ and $(B')$ with the labelling of $A$ and $a$ alleles interchanged, we discuss only equilibria $(A)$ and $(B)$, in which the Y background is fixed for the $a$ allele.
-If there is no haploid selection ($\alpha^{\Hermaphrodite}_\Delta=0$, $w_{A}^{\Hermaphrodite}=w_{a}^{\Hermaphrodite}=1$), these equilibria are equivalent to those found by~\cite{Lloyd1977} and~\cite{Otto2014}.
-
-We next calculate when equilibria $(A)$ and $(B)$ are locally stable for $r=0$. 
-According to the `small parameter theory'~\cite{Karlin:1972ab,Karlin:1972dq}, these stability properties are unaffected by small amounts of recombination between the sex-determining locus and the $\mathbf{A}$ locus, although equilibrium frequencies may be slightly altered.
-For the $a$ allele to be stably fixed on the Y background we need $\bar{w}_{Ya}^{\male} > \bar{w}_{YA}^{\male}$ where $\bar{w}_{Ya}^{\male} = w_{a}^{\male} \big[\hat{p}_X^\female(1-\alpha^\male_\Delta) w_{A}^{\female} w_{Aa}^{\male} + (1-\hat{p}_X^\female)w_{a}^{\female} w_{aa}^{\male} \big]$ and $\bar{w}_{YA}^{\male} = w_{A}^{\male} \big[ \hat{p}_X^\female w_{A}^{\female} w_{AA}^{\male} + (1-\hat{p}_X^\female)(1+\alpha^\male_\Delta) w_{a}^{\female} w_{Aa}^{\male} \big]$.
-That is, Y-$a$ haplotypes must have higher fitness than Y-$A$ haplotypes.  
-Substituting in $\hat{p}_X^\female$ from Eq \eqref{eq:tightequil}, fixation of the $a$ allele on the Y background requires that $\gamma_{i}>0$ where $\gamma_{(A)}=w_{a}^{\male} \big[ (1-\alpha^\male_\Delta) w_{Aa}^{\male} \phi + w_{aa}^{\male} \psi \big]-w_{A}^{\male} \big[ w_{AA}^{\male} \phi + (1 + \alpha^{\male}_\Delta)w_{Aa}^{\male} \psi \big]$ for equilibrium $(A)$ and $\gamma_{(B)}=(1-\alpha^{\male}_\Delta)w_{a}^{\male}w_{Aa}^{\male}-w_{A}^{\male}w_{AA}^{\male}$ for equilibrium $(B)$.
-Stability of a polymorphism on the X background (equilibrium $(A)$) further requires that $\phi >0$ and $\psi >0$. 
-Fixation of the $a$ allele on the X background (equilibrium $(B)$) can be stable only if equilibrium $(A)$ is not, as it requires $\psi<0$.
-%and $2w_{A}^{\female}w_{AA}^{\female}>(1-\alpha_\Delta^{\female})w_{a}^{\female}w_{Aa}^{\female}$ or just $4w_{A}^{\female}w_{AA}^{\female}<(1-\alpha_\Delta^{\female})w_{a}^{\female}w_{Aa}^{\female}$ (which also prevents $\psi>0$).
-
-%\textcolor{red}{check last condition and the stability condition below are correct}
-%\textcolor{blue}{The last condition looks good to me, although in your Turnover-norec-MFS.nb you look at YA fixed, so you have to flip everything (so I made Turnover-norec-MFS-MMO.nb to do this).
-%The one issue I can find here is that you can also prevent $\Lambda>1$ when the slope and intercept of the quadratic at $\Lambda=1$ are negative (you only looked at both being positive).
-In this case we need $4w_{A}^{\female}w_{AA}^{\female}<(1-\alpha_\Delta^{\female})w_{a}^{\female}w_{Aa}^{\female}$, which also prevents $\psi>0$.
-%I've added this in.
-%It could also be the case that the slope and intercept are the same sign but the roots are imaginary - but this is never the case here.
-%Stability condition below looks good to me (from matt version of turnoverSOM-MIKE.nb).}
-
-\subsubsection*{Selection weak relative to recombination}
-
-Here, we assume that selection is weak relative to recombination ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon$). 
-The maintenance of a polymorphism at the $\mathbf{A}$ locus then requires that
-
-\begin{equation}
-\begin{split}
-0&< - \left[(1-h^\female)s^\female +(1-h^\male) s^\male + t^\female +t^\male + \alpha_{\Delta}^\female+\alpha_{\Delta}^\male\right]\\
-%
-\text{and }\quad 0&<h^\female s^\female +h^\male s^\male + t^\female +t^\male + \alpha_{\Delta}^\female+\alpha_{\Delta}^\male.
-\end{split}
-\end{equation}
-
-\noindent
-which indicates that a polymorphism can be maintained by various selective regimes.
-
-Given that a polymorphism is maintained at the $\mathbf{A}$ locus by weak selection, the frequencies of $A$ in each type of gamete are the same ($\hat{p}^\female_X=\hat{p}^\male_X=\hat{p}^\male_Y=\bar{p}$) and given, to leading order, by
-
-\begin{equation}
-\bar{p}=\frac{h^\female s^\female + h^\male s^\male +t^\female+t^\male+\alpha_{\Delta}^\female+\alpha_{\Delta}^\male}
-{(2h^\female-1)s^\female+(2h^\male-1)s^\male}
-+O(\epsilon)
-.
-\label{eq:pAve}
-\end{equation}
-
-\noindent
-Differences in frequency between gamete types are of $O(\epsilon)$:
-
-\begin{equation}
-\begin{split}
-\hat{p}^\male_X-\hat{p}^\female_X&=V_{A}\big{(}D^\male - D^\female +\alpha_{\Delta}^\male-\alpha_{\Delta}^\female \big{)}
-+O(\epsilon^2)\\
-%
-\hat{p}^\male_Y-\hat{p}^\female_X&=V_{A}\left[D^\male - D^\female+\alpha_{\Delta}^\male-\alpha_{\Delta}^\female+(1-2r)(t^\male-t^\female)\right]/2r
-+O(\epsilon^2)\\
-%
-\hat{p}^\male_Y-\hat{p}^\male_X&=V_{A}\left(D^\male - D^\female+\alpha_{\Delta}^\male-\alpha_{\Delta}^\female+t^\male-t^\female\right)(1-2r)/2r
-+O(\epsilon^2),
-\end{split}
-\label{eq:freq_diffs}
-\end{equation}
-
-\noindent
-where $V_{A}=\bar{p}(1-\bar{p})$ is the variance in the frequency of $A$ and $D^\Hermaphrodite=\big{[} \bar{p}s^\Hermaphrodite+(1-\bar{p})h^\Hermaphrodite s^\Hermaphrodite\big{]} -\big{[} \bar{p}h^\Hermaphrodite s^\Hermaphrodite+(1-\bar{p}) \big{]}$ corresponds to the difference in fitness between $A$ and $a$ alleles in diploids of sex $\Hermaphrodite \in \{\female,\male\}$.
-The frequency of Y-bearing male gametes depends upon the difference in the frequency of the $A$ allele between X- and Y-bearing male gametes and the strength of meiotic drive in favour of the $A$ allele in males, $q=1/2+\alpha_{\Delta}^\male(\hat{p}^\male_Y-\hat{p}^\male_X)/2+O(\epsilon^3)$.
-Without gametic competition or drive ($\alpha_{\Delta}^\Hermaphrodite=t^\Hermaphrodite=0$) our results reduce to those of~\cite{vanDoorn:2007eu}.
-
-\newpage
-
-\setcounter{equation}{0}
-\renewcommand{\theequation}{S3.\arabic{equation}}
-
-\section*{S3 Appendix}
-
-\subsection*{Invasion conditions}
-
-A rare neo-Y or neo-W allele, $m$, will spread in an XY sex-determining system when the leading eigenvalue, $\lambda_m^{(XY)}$, of the Jacobian matrix derived from the eight mutant recursion equations (given by \ref{eq:recursions}c,d,g,h), evaluated at the ancestral equilibrium, is greater than one.
-However, because a neo-Y (neo-W) is always in males (females) and is epistatically dominant to the ancestral sex-determining locus, the characteristic polynomial factors into two quadratics times $(\lambda_m^{(XY)})^4$.
-One quadratic governs the change in the frequency of the new sex determination factor associated with the $A$ and $a$ allele frequencies, summing across backgrounds at the old sex-determining locus (i.e., summing haplotypes bearing the original X and Y alleles).
-%It is the largest root of this quadratic that determines the spread of the new $m$ allele (see details in \nameref{file:Mathematica}).  
-The second quadratic describes the dynamics of the difference in the $m$-$A$ and $m$-$a$ haplotypes between X and Y backgrounds.  
-Asymptotically, this difference is constrained to grow at a rate equal to or less than the sum while the $m$ allele is rare, because the frequencies can never become negative. 
-We therefore focus on the leading eigenvalue, $\lambda_m^{(XY)}$, which is the largest root of the first quadratic $f(x) = x^2+ b x + c = 0$, as described in the text (details in \nameref{file:Mathematica}).
-
-When $R=0$ the two roots are $\Lambda_{mA}^{(XY)}$ and $\Lambda_{ma}^{(XY)}$, and the leading eigenvalue is the larger of the two.
-When $R>0$ then $f(\Lambda_{mA}^{(XY)})$ and $f(\Lambda_{ma}^{(XY)})$ are of opposite signs, and the leading eigenvalue must fall between these two quantities (details in \nameref{file:Mathematica}).
-%(the Perron-Frobenius theorem guarantees that the largest eigenvalue is positive, unique, and real).
-Thus, $\lambda_m^{(XY)}>1$ if both $\Lambda_{mA}^{(XY)}>1$ and $\Lambda_{ma}^{(XY)}>1$; similarly, $\lambda_m^{(XY)}<1$ if both $\Lambda_{mA}^{(XY)}<1$ and $\Lambda_{ma}^{(XY)}<1$.
-If only one haplotypic growth rate is greater than one ($\Lambda_{ma}^{(XY)}<1<\Lambda_{mA}^{(XY)}$ or $\Lambda_{mA}^{(XY)}<1<\Lambda_{ma}^{(XY)}$), then $\lambda_m^{(XY)}$ is greater than one when condition \eqref{eq:lambdasGen} is met.
-Thus, the invasion of a new sex-determining allele is determined by the haplotypic growth rates ($\Lambda_{mj}^{(XY)}$ terms), which do not account for loss due to recombination, and the rates at which recombination between the $\mathbf{M}$ and $\mathbf{A}$ loci breaks apart these haplotypes ($\chi_{mj}^{(XY)}$).
-For tight linkage between the ancestral sex-determining locus ($\mathbf{X}$) and the selected locus ($\mathbf{A}$) we can calculate these terms explicitly (see below).
-For weak selection we approximate the leading eigenvalue with a Taylor series. 
-The leading eigenvalue for any $k$ is given up to order $\epsilon^2$ by Eq \eqref{eq:lambda_ESD_k}.
-
-\subsubsection*{Tight linkage between $\mathbf{A}$ and $\mathbf{X}$ ($r \approx 0$)}
-
-Here, we explore the conditions under which a neo-W invades an XY system assuming that the $\mathbf{A}$ locus is initially in tight linkage with the ancestral sex-determining locus ($r \approx 0$). 
-We disregard neo-Y mutations, which never spread given that the ancestral population is at a stable equilibrium (see \nameref{file:Mathematica} for proof).
-
-Starting with the simpler $(B)$ equilibrium, the terms that determine the leading eigenvalue are
-
-\begin{subequations}\label{Binvasion}
-\begin{align}
-\Lambda_{W'A}^{(XY)}&= {\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]}^{-1}
-\frac{w_{A}^\female }{w_{A}^\female}
-\frac{\left[ w_{A}^\male (1+\alpha^\male_\Delta) w_{AA}^\female + 
-w_{a}^\male (1-\alpha^\male_\Delta) w_{Aa}^\female (1+\alpha^\female_\Delta) \right]}
-{ 2w_{AA}^\female } \\
-\Lambda_{W'a}^{(XY)}&= {\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]}^{-1}
-\frac{w_{a}^\female}{w_{A}^\female}
-\frac{\left[  w_{A}^\male (1+\alpha^\male_\Delta) w_{Aa}^\female (1-\alpha^\female_\Delta)+
-w_{a}^\male (1-\alpha^\male_\Delta) w_{aa}^\female \right]}
-{ 2w_{AA}^\female } \\
-\chi_{W'A}^{(XY)}&= \frac{1}{2} {\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]}^{-1}
-\frac{w_{A}^\female }{w_{A}^\female}
- \frac{\left[  w_{a}^\male (1-\alpha^\male_\Delta) w_{Aa}^\female (1 + \alpha^\female_\Delta) \right]}
-{ w_{AA}^\female } \frac{R}{2}\\
-\chi_{W'a}^{(XY)}&= \frac{1}{2} {\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]}^{-1}
-\frac{w_{a}^\female}{w_{A}^\female}
- \frac{\left[  w_{A}^\male (1+\alpha^\male_\Delta) w_{Aa}^\female (1-\alpha^\female_\Delta) \right]}
-{  w_{AA}^\female} \frac{R}{2}.
-\end{align}
-\end{subequations}
-
-%\noindent
-%In this case, the zygotic sex ratio ($\zeta$) is given by the difference in haploid selection in males on $a$ (fixed on the Y) and $A$ (fixed on the X) alleles, i.e., there are more males than females if $\zeta = \alpha^\male w_A^\male / [(1-\alpha^\male)w_a^\male + \alpha^\male w_A^\male]<1/2$.
-%$\alpha^\male<1/2$ and/or $w_{a}^\male>w_{A}^\male$.
-%Populations with haploid selection for $a$ in males have a male biased zygotic sex ratio are thus more permissive to invasion by a neo-W ($\Lambda_{mA}$ and $\Lambda_{ma}$ larger).
-%%In addition, the spread of neo-W alleles depends on the fitness of female diploids after mating with an X-$A$ or Y-$a$ male gamete, relative to the fitness of females in the population (all have genotype $AA$ and fitness $w_{AA}^\female$ at this equilibrium).
-%Haploid selection in males has a second effect; the spread rate of neo-W haplotypes is determined by their fitness in diploid females, which depends on their diploid genotype and thus on the male gamete they pair with.
-%Zygotes carrying dominant neo-W alleles will develop as females regardless of their genotype at the XY locus. 
-%Therefore, neo-W females result from matings with either X-$A$ or Y-$a$ male gametes. 
-%The relative proportion of these male gametes is determined by haploid selection in males; mating with a Y-$a$ male gamete is more likely if the $a$ allele is favoured during male gamete production or competition ($\zeta<1/2$).
-%Thus, neo-W females experience different diploid selection than XX females, and the extent of this difference depends on haploid selection in males.
-%Furthermore, haploid selection in females can directly select upon neo-W-$A$ or neo-W-$a$ haplotypes. 
-%A neo-W-$A$ female gamete has the same fitness during haploid competition as resident $A$-bearing female gametes. 
-%On the other hand, neo-W-$a$ female gametes can be favoured or disfavoured during female haploid competition (favoured if $w_{a}^\female>w_{A}^\female$). 
-%Meiotic drive in females ($\alpha^\female$) similarly affects the fitness of these neo-W haplotypes, except that it impacts both haplotypes as meiotic drive only occurs in heterozygotes and therefore does not occur in resident XX females (who are always homozygote $AA$).
-
-Haploid selection impacts the spread of neo-W haplotypes in three ways (also seen in Table \ref{tab:haplotype_growth}).
-Firstly, the zygotic sex ratio becomes male biased, $\zeta>1/2$, when the $a$ allele (which is fixed on the Y) is favoured during competition among male gametes or by meiotic drive in males.
-Specifically, at equilibrium $(B)$, female zygote frequency is $1 - \zeta = w_A^\male (1+\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$ where $2\bar{w}_{H}^\male= \big[w_a^\male (1-\alpha^\male_\Delta) +  w_A^\male (1+\alpha^\male_\Delta) \big]$ has been canceled out in equations \eqref{Binvasion} to leave the term ${\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]}^{-1}$.
-Male biased sex ratios facilitate the spread of a neo-W because neo-W alleles cause the zygotes that carry them to develop as the rarer, female, sex.
-
-Secondly, haploid selection in females selects on neo-W haplotypes directly.
-At equilibrium $(B)$, the fitness of female gametes under the ancestral sex-determining system is $w_{A}^\female$ such that the relative fitnesses of neo-W-$A$ and neo-W-$a$ haplotypes during female gametic competition are $w_{A}^\female/w_{A}^\female$ and $w_{a}^\female/w_{A}^\female$ (see terms in equation \ref{Binvasion}).
-Meiotic drive in females will also change the proportion of gametes that carry the $A$ versus $a$ alleles, which will be produced by heterozygous females in proportions $(1+\alpha_{\Delta}^\female)/2$ and $(1-\alpha_{\Delta}^\female)/2$, respectively.
-These terms are only associated with heterozygous females, i.e., they are found alongside $w_{Aa}^\female$.
-
-Thirdly, haploid selection in males affects the diploid genotypes of females by altering the allele frequencies in the male gametes with which female gametes pair.
-At equlibrium $(B)$, neo-W female gametes will mate with X-$A$ male gametes with probability $ w_A^\male (1+\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$ and Y-$a$ male gametes with probability $w_a^\male (1-\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$, where the $2\bar{w}_{H}^\male$ terms have been canceled in Eq \eqref{Binvasion} (as mentioned above).
-Thus, neo-W-$A$ haplotypes are found in $AA$ female diploids with probability $ w_A^\male (1+\alpha^\male_\Delta)/ (2\bar{w}_{H}^\male)$ (e.g., first term in square brackets in the numerator of equation \ref{Binvasion}a) and in $Aa$ female diploids with probability $w_a^\male (1-\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$ (e.g., the second term in square brackets in the numerator of equation \ref{Binvasion}a).
-
-%For instance, because an epistatically dominant neo-W always causes its carrier to become female, it creates females who carry either Y-$a$ or X-$A$ genotypes from their father.
-%Thus, because when there is a polymorphism the X carries some non-zero frequency of $A$, haploid selection in males impacts the diploid genotypes of females (e.g., creating more $Aa$ females when drive in males favours Y-$a$).
-%How this affects the spread of the neo-W then depends on diploid and haploid selection in females.
-
-The other terms in equations \eqref{Binvasion} are more easily interpreted if we assume that there is no haploid selection in either sex, in which case $\Lambda_{W'A}^{(XY)}=(w_{AA}^\female+w_{Aa}^\female)/2 w_{AA}^\female$ and $\Lambda_{W'a}^{(XY)}=(w_{aa}^\female+w_{Aa}^\female)/ 2 w_{AA}^\female$.
-Neither haplotype can spread under purely sexually-antagonistic selection at equilibrium $(B)$, with directional selection in each sex.
-Essentially, the X is then already as specialized as possible for the female beneficial allele ($A$ is fixed on the X background), and the neo-W often makes daughters with the Y-$a$ haplotype, increasing the flow of $a$ alleles into females, which reduces the fitness of those females.
-
-If selection doesn't uniformly favour $A$ in females, however, neo-W-$A$ haplotypes and/or neo-W-$a$ haplotypes can spread ($\Lambda_{W'A}^{(XY)}>1$ and/or $\Lambda_{W'a}^{(XY)}>1$).
-%If $\Lambda_{mA}>1$ (requiring $w_{Aa}^\female>w_{AA}^\female$), the implication is that the neo-W can spread alongside the $A$ allele, despite the fact that the neo-W sometimes brings $Y-a$ haplotypes into females, because $a$ is favoured by selection in females despite $A$ being fixed on the X.
-A neo-W-$A$ haplotype can spread ($\Lambda_{W'A}^{(XY)}>1$) when $w_{Aa}^\female>w_{AA}^\female$, despite the fact that a neo-W brings Y-$a$ haplotypes into females.
-In this case the $a$ allele is favoured by selection in females despite $A$ being fixed on the X background.
-For this equilibrium to be stable (i.e.,  to keep $A$ fixed on the X), X-$a$ cannot be overly favoured in females and X-$A$ must be sufficiently favoured in males (for example, by overdominance in males).
-Specifically, from the stability conditions for equilibrium (B), we must have $w_{Aa}^\female < 2 w_{AA}^\female$ and $w_{Aa}^\male/\big[(w_{aa}^\male+w_{Aa}^\male)/2\big]>w_{Aa}^\female/w_{AA}^\female$.
-
-Still considering $w_{Aa}^\female>w_{AA}^\female$, the neo-W can also spread alongside the $a$ allele ($\Lambda_{W'a}^{(XY)}>1$) if $w_{aa}^\female$ is large enough such that $(w_{Aa}^\female+w_{aa}^\female)/2>w_{AA}^\female$.
-%there is sufficiently strong underdominance in females ($w_{aa}^\female>w_{Aa}^\female$) \textcolor{blue}{[this is describing directional selection, not overdominance - check the conditions for the case we want to talk about]}, such that $(w_{Aa}^\female+w_{aa}^\female)/2>w_{AA}^\female$.
-This can occur with overdominance or directional selection for $a$ in females (Fig \ref{fig:regionplots}B,C).
-In this case, $a$ is favoured on the ancestral Y background in males and on the ancestral X background in females (comparing $Aa$ to $AA$ genotypes in females) but $A$ is fixed on the X background due to selection in males.
-The neo-W-$a$ haplotype can spread because it produces females with higher fitness $Aa$ and $aa$ genotypes.
-
-%When both haplotypes can spread on their own ($\Lambda_{mA}>1$ and $\Lambda_{ma}>1$), the neo-W invades regardless the recombination rate between it and the selected locus, $R$.
-%When neither haplotype can spread ($\Lambda_{mA}<1$ and $\Lambda_{ma}<1$) the neo-W can never invade.
-%And when only one haplotype can spread on its own the neo-W invades only when the rate of recombination onto the favourable background is sufficiently larger than the rate of recombination off this background (i.e., equation\ref{eq:lambdasGen} is satisfied).
-
-%Haploid selection affects the conclusions outlined above by altering the zygotic sex ratio and exerting direct selection on neo-W haplotypes.
-%The effect of sex ratio selection is straightforward and can be seen in Eq \eqref{Binvasion}, where male drive and gamete competition for $a$ (which is fixed on the Y and therefore causes a male bias) increases all four terms.
-%Direct selection on neo-W haplotypes can also be seen in Eq \eqref{Binvasion} by noticing that increasing female drive in favour of $A$ increases the neo-W-$A$ haplotype growth rate ($\Lambda_{mA}$) while female drive and gamete competition in favour of $a$ increases the neo-W-$a$ haplotype growth rate ($\Lambda_{ma}$).
-%Gamete competition in females does not impact the spread of neo-W-$A$ haplotypes because they are on the same background as the resident X.
-%Recombination between the selected locus and the neo-W complicates things slightly, as selective advantages for one neo-W haplotype during the haploid stage in females comes at a cost to the other, and thus recombination off the favoured background becomes more detrimental.
-
-%\textcolor{red}{the versions for equil $(A)$ are not terrible but could be improved by cleverly re-writing with the $\phi$ and $\psi$ terms from above, I think...}
-
-Similar equations can be derived for equilibrium (A) by substituting the equilibrium frequencies into Table \ref{tab:haplotype_growth}
-
-\begin{subequations}\label{Ainvasion}
-\begin{align}
-\Lambda_{W'A}^{(XY)}&= \frac{a}{b} \left[w_{AA}^\female w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi +  w_{Aa}^\female (1+\alpha^\female_\Delta) w_a^\male c \right] / (2 w_a^\female) \\
-\Lambda_{W'a}^{(XY)}&= \frac{a}{b} \left[ w_{Aa}^\female (1-\alpha^\female_\Delta) w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi +  w_{aa}^\female w_a^\male c \right] / (2 w_A^\female) \\
-\chi_{W'A}^{(XY)}&= \frac{a}{b} \frac{R}{2} \left[   w_{Aa}^\female (1+\alpha^\female_\Delta) w_a^\male c \right] / w_a^\female\\ 
-\chi_{W'a}^{(XY)}&= \frac{a}{b} \frac{R}{2} \left[ w_{Aa}^\female (1-\alpha^\female_\Delta) w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi \right] / w_A^\female,
-%\Lambda_{W'A}^{(XY)}&=   {\left[ 2 (1 - \zeta) \right]}^{-1} w_A^{\female} \left[ b w_{AA}^\female + c w_{Aa}^\female \left(1 - \alpha^\female_\Delta \right) \right]/ \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\female}_{D} \right)  \\
-%\Lambda_{W'a}^{(XY)}&=  \\
-%\chi_{W'A}^{(XY)}&= \\ 
-%\chi_{W'a}^{(XY)}&=
-\end{align}
-\end{subequations}
-
-\noindent
-where
-
-\begin{subequations}
-\begin{align}
-a &= w_a^\female \phi + w_A^\female \psi \\
-b &= w_{AA}^\female \left[ w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \right] \phi^2 + w_{Aa}^\female \left[ w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) + w_{aa}^\male w_a^\male \right] \psi \phi + w_{aa}^\female \left( w_{aa}^\male w_a^\male \right) \psi^2\\
-%c &= w_{Aa}^\male (1-\alpha^\male_\Delta) \phi \left[ w_{Aa}^\male (1+\alpha^\male_\Delta) \phi \right] + w_{Aa}^\male\phi \left[ 2w_{AA}^\male + w_{aa}^\male (1+\alpha^\male_\Delta) \right] \psi + w_{aa}^\male \psi \left(2w_{AA}^\male \psi \right) \\
-c &= w_{Aa}^\male (1-\alpha^\male_\Delta) \phi + 2w_{aa}^\male \psi.
-\end{align}
-\end{subequations}
-
-%\textcolor{red}{Sally suggests using some $\zeta$ term in the above equations}
-%\textcolor{blue}{Maybe just reference table 2?}
-
-As with equilibrium (B), haploid selection again modifies invasion fitnesses by altering the ancestral sex ratio, $\zeta$ (see Table \ref{tab:haplotype_growth}), and directly selecting upon female gametes, through $w_{i}^\female$.
-The only difference is that resident XX females are no longer always homozygote $AA$ and males are no longer always heterozygote $Aa$.
-Thus the effect of haploid selection in males is reduced, as is the difference in fitness between neo-W haplotypes and resident X haplotypes, as both can be on any diploid or haploid background.
-
-The other terms are easier to interpret in the absence of haploid selection.
-For instance, without haploid selection, the neo-W-$A$ haplotype spreads ($\Lambda_{W'A}^{(XY)}>1$) if and only if
-
-\begin{equation}\label{eq:BeqWAspread}
-2(w_{Aa}^\female-w_{aa}^\female)w_{aa}^\male \psi^2 > (w_{AA}^\female-w_{Aa}^\female)w_{Aa}^\male \phi (\phi-\psi),
-\end{equation}
-
-\noindent  
-where $\phi-\psi=w_{AA}^\female w_{Aa}^\male-w_{aa}^\female w_{aa}^\male$ and both $\phi$ and $\psi$ are positive when equilibrium (A) is stable. 
-In contrast to equilibrium (B), a neo-W haplotype can spread under purely sexually-antagonistic selection  ($w_{aa}^\female<w_{Aa}^\female<w_{AA}^\female$ and $w_{AA}^\male<w_{Aa}^\male<w_{aa}^\male$).
-The neo-W-$A$ can spread as long as it becomes associated with females that bear more $A$ alleles than observed at equilibrium (A), effectively specializing on female fitness. 
-%In this case, the neo-W-$A$ haplotype can spread, despite producing a lot of $Aa$ daughters by obtaining the $a$ from Y-gametes, when $aa$ females, which the neo-W-$A$ never makes, are strongly selected against.
-%This can be intuited from the fact that \eqref{eq:BeqWAspread} will be more easily met when $w_{Aa}^\female-w_{aa}^\female\approx w_{Aa}^\female$ and $w_{AA}^\female-w_{Aa}^\female\approx 0$, implying $w_{aa}^\female \approx 0$ and $w_{Aa}^\female\approx w_{AA}^\female$ (although this is complicated by the fact that $w_{aa}^\female$ and $w_{Aa}^\female$ affect $\phi$ and $\psi$ too, the intuition holds).
-
-Without haploid selection, the neo-W-$a$ haplotype spreads ($\Lambda_{W'a}^{(XY)}>1$) if and only if
-
-\begin{equation}\label{eq:BeqWaspread}
-(w_{aa}^\female + w_{Aa}^\female-2w_{AA}^\female)w_{Aa}^\male \phi^2 + (w_{aa}^\female-w_{Aa}^\female)(w_{Aa}^\male+2w_{aa}^\male) \phi \psi >0.
-\end{equation}
-
-\noindent
-This condition cannot be met with purely sexually antagonistic selection (as both terms on the left-hand side would then be negative), but it can be met under other circumstances. 
-For example, with overdominance in males there is selection for increased $A$ frequencies on the X background in males, which are always paired with Y-$a$ haplotypes.
-Directional selection for $a$ in females can then maintain a polymorphism at the $\mathbf{A}$ locus on the X background.
-This scenario selects for a modifier that increases recombination between the sex chromosomes (e.g., blue region of Fig 2d in~\cite{Otto2014}) and facilitates the spread of neo-W-$a$ haplotypes, which create females bearing more $a$ alleles than the ancestral X haplotype does.
-
-\subsubsection*{Role of haploid selection with tight linkage between $\mathbf{X}$ and $\mathbf{A}$ loci}
-
-Haploid selection generally expands the conditions under which neo-W alleles can spread within ancestral systems that have evolved tight linkage between the sex-determining locus and a selected locus ($r \approx 0$).
-First, haploid selection can allow a polymorphism to be maintained when it would not under diploid selection alone (e.g., with directional selection in diploids). 
-In cases of ploidally-antagonistic selection, where there is a balance between alleles favored in the haploid stage and the diploid stage, neo-W alleles - even if unlinked to the selected locus - can spread (\nameref{fig:regionPloidAntag}).
-Second, even when diploid selection could itself maintain a polymorphism, haploid selection can increase the conditions under which transitions among sex-determining systems are possible.
-Of particularly importance, when selection is sexually-antagonistic in diploids ($s^\female s^\male <0$ and $0<h^\Hermaphrodite<1$), an unlinked neo-W ($R=1/2$) cannot invade unless there is also haploid selection (see proof in \nameref{file:Mathematica}; Fig \ref{fig:SexAntagTighter} and \nameref{fig:SexAntagTighterMaleDrive}).
-More generally, haploid selection alters the conditions under which neo-W alleles can spread (compare \nameref{fig:regionMaleDrive}-\nameref{fig:regionFemaleGS} to Fig \ref{fig:regionplots}).
-
-%[SALLY:  I think that is enough, but we could add somewhere??: "Without haploid selection, unlinked neo-W alleles ($R=1/2$) can invade only under certain conditions, requiring either overdominance in males or underdominance in females (see proof in supplementary \textit{Mathematica} file).?
-Note that underdominance in females with directional selection in males can lead to the spread of unlinked neo-W?s, but only from equilB (only $\Lambda_{ma}$ is greater than one in this case).]
-
-Male haploid selection in favour of the $a$ allele ($\alpha_{\Delta}^\male<0$, $w_{A}^\male<w_{a}^\male$) generates male-biased sex ratios at equilibria (A) and (B), where Y-$a$ is fixed ($\hat{p}_{Y}^\male=0$).
-Male-biased sex ratios facilitate the spread of neo-W-$A$ and neo-W-$a$ haplotypes (increasing $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$). 
-Panels A-C in \nameref{fig:regionMaleDrive} and \ref{fig:regionMaleGS} show that neo-W haplotypes tend to spread for a wider range of parameters when sex ratios are male biased, compared to Fig \ref{fig:regionplots} without haploid selection.
-By contrast, male haploid selection in favour of the $A$ allele generates female-biased sex ratios and reduces $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$, as demonstrated by panels D-F in \nameref{fig:regionMaleDrive} and \nameref{fig:regionMaleGS}.
-
-Female haploid selection generates direct selection on the neo-W-$A$ and neo-W-$a$ haplotypes as they spread in females. 
-Thus, female haploid selection in favour of the $a$ allele tends to increase $\Lambda_{W'a}^{(XY)}$ and decrease $\Lambda_{W'A}^{(XY)}$, as shown by panels A-C in \nameref{fig:regionFemaleDrive} and \nameref{fig:regionFemaleGS}.
-Conversely, female haploid selection in favour of the $A$ allele increases $\Lambda_{W'A}^{(XY)}$ and decreases $\Lambda_{W'a}^{(XY)}$, see panels D-F in \nameref{fig:regionFemaleDrive} and \nameref{fig:regionFemaleGS}.
-
-Thus, the impact of haploid selection on transitions between sex-determining systems must be considered as two sides of a coin: it can generate sex ratio biases that promote transitions that equalize the sex ratio, but it can also direct select for transitions that cause sex ratios to become biased.
-
 \end{document}

### 2018-02-07 LaTeX/S2Appendix.tex
moved appendices out of main text but can crossref

--- 2018-02-06 LaTeX/Turnover_plos.tex
@@
 
+%reference equations in appendices
+\usepackage{xr}
+\externaldocument{S1Appendix}
+\externaldocument{main}
+\externaldocument{S3Appendix}
+
 %% END MACROS SECTION
@@
 \vspace*{0.2in}
-
-% Title must be 250 characters or less.
-\begin{flushleft}
-{\Large
-\textbf\newline{Haploid selection, sex ratio bias, and transitions between sex-determining systems} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
-}
-\newline
-% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
-\\
-Michael Francis Scott\textsuperscript{1\Yinyang*},
-Matthew Miles Osmond\textsuperscript{2\Yinyang},
-Sarah Perin Otto\textsuperscript{2}
-\\
-\bigskip
-\textbf{1} UCL Genetics Institute, Department of Genetics, Evolution and Environment, University College London, Gower Street, London WC1E 6BT 
-\\
-\textbf{2} Department of Zoology, University of British Columbia, \#4200 - 6270 University Boulevard, Vancouver, BC, Canada V6T 1Z4
-\\
-\bigskip
-
-% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
-% 
-% Remove or comment out the author notes below if they aren't used.
-%
-% Primary Equal Contribution Note
-\Yinyang These authors contributed equally to this work.
-
-% Additional Equal Contribution Note
-% Also use this double-dagger symbol for special authorship notes, such as senior authorship.
-%\ddag These authors also contributed equally to this work.
-
-% Current address notes
-%\textcurrency Current Address: Dept/Program/Center, Institution Name, City, State, Country % change symbol to "\textcurrency a" if more than one current address note
-% \textcurrency b Insert second current address 
-% \textcurrency c Insert third current address
-
-% Deceased author note
-%\dag Deceased
-
-% Group/Consortium Author Note
-%\textpilcrow Membership list can be found in the Acknowledgments section.
-
-% Use the asterisk to denote corresponding authorship and provide email address in note below.
-* m.f.scott@ucl.ac.uk
-
-\end{flushleft}
-% Please keep the abstract below 300 words
-%currently 312 words
-\section*{Abstract}
-Sex determination is remarkably dynamic; many taxa display shifts in the location of sex-determining loci or the evolution of entirely new sex-determining systems. 
-Predominant theories for why we observe such transitions generally conclude that novel sex-determining systems are favoured by selection if they equalise the sex ratio or increase linkage with a sexually-antagonistic locus.
-We use population genetic models to extend these theories in two ways: 
-(1) We explicitly consider selection on loci very tightly linked to the ancestral sex-determining loci, e.g., within the non-recombining region of the ancestral sex chromosomes. 
-Variation at such loci can favour the spread of new sex-determining systems in which the heterogametic sex changes (XY to ZW or ZW to XY) and the new sex-determining region is less closely linked (or unlinked) to the locus under selection, which is not predicted by previous theory.
-(2) We also consider selection upon haploid genotypes either during gametic competition (e.g., pollen/sperm competition) or meiosis (i.e., non-Mendelian segregation), selective processes that typically occur in one sex or the other.
-We find that associations with haploid selected loci can drive transitions between sex-determining systems, without requiring sexually-antagonistic selection in diploids. 
-Unexpectedly, with haploid selection, transitions between male and female heterogamety can also evolve where linkage with the sex-determining locus is weakened. 
-Furthermore, haploid selection in the heterogametic sex can cause sex ratio biases, which may increase or decrease with the spread of new sex chromosomes. 
-Thus, we find that transitions between sex-determining systems cannot be simply predicted by selection to equalise the sex ratio. 
-Overall, our models reveal that transitions between sex-determining systems, particularly transitions where the heterogametic sex changes, can be driven by loci in previously unpredicted genomic locations that experience selection during diploid and/or haploid phases.
-These results predict conditions under which sex-determining systems are likely to be labile and draw novel connections with sex ratio evolution.
-
-% Please keep the Author Summary between 150 and 200 words
-% Use first person. PLOS ONE authors please skip this step. 
-% Author Summary not valid for PLOS ONE submissions.   
-%currently 193 words
-\section*{Author summary}
-Accumulating evidence indicates that systems of sex determination are strikingly diverse and labile in many clades. 
-This poses the question: what drives transitions between sex-determining systems? 
-Here, we use models to derive conditions under which new sex-determining systems spread. 
-Prevailing views suggest that new sex-determining systems are favoured when they equalize the sex ratio and/or when they are more closely linked to genes that experience differential selection in males and females.
-Our models extends these theories to include selection upon haploid genotypes (meiotic drive or gametic competition), which causes sex ratio biases and occurs differently in males and females. 
-Surprisingly, we find that neither force (sex ratio selection nor associations with genes that have sex-specific effects) dominates the spread of new sex-determining systems alone. 
-Even more unexpectedly, we find that, to spread, new sex-determining alleles do not necessarily have to arise in closer linkage with genes that are differentially selected in males and females. 
-Therefore, our models predict loci in previously unexpected genomic locations and/or experiencing various types of selection (including haploid selection) can now be implicated as drivers of transitions between sex-determining systems.
-
-\linenumbers
-
-% Use "Eq" instead of "Equation" for equation citations.
-\section*{Introduction}
-
-Animals and angiosperms exhibit extremely diverse sex-determining systems (reviewed in~\cite{Bull:1983vi,Charlesworth:2010it,Beukeboom:2014vb,Bachtrog:2014bx}). 
-Among species with genetic sex determination (GSD) of diploid sexes, some taxa have heterogametic males (XY) and homogametic females (XX), including %non-monotreme?
-I think monotremes have XY but tonnes of translocations, giving: X1,X2...X6 Y1
-mammals and most dioecious plants~\cite{Ming:2011iy}; whereas other taxa have homogametic males (ZZ) and heterogametic females (ZW), including Lepidoptera and birds. 
-Within several taxa, the chromosome that harbours the master sex-determining locus changes. 
-For example, transitions of the master sex-determining locus between chromosomes or the evolution of new master sex-determining loci where the heterogametic sex does not change (hereafter `cis-GSD transitions') have occurred in Salmonids~\cite{Li:2011fm,Yano:2012di}, Diptera~\cite{Vicoso:2015hf}, and \textit{Oryzias}~\cite{Myosho:2012fv}.
-%Presentation at evolution found neo sex chromosome in birds, doesn't seem to be published or bioRxiv yet (consider pers com.), title: A previously unknown neo-sex chromosome mediates plumage divergence and speciation in hybridizing birds Jason Sardell; Elizabeth Cooper; J.
-Albert C.
-Uy.
-I wonder if this is actually a fusion event though?
-In addition, many clades exhibit transitions between male and female heterogamety (XY$\leftrightarrow$ZW, hereafter `trans-GSD transitions'), including snakes~\cite{Gamble2017}, lizards~\cite{Ezaz:2009tk}, eight of 26 teleost fish families~\cite{Mank:2006bt}, true fruit flies (Tephritids,~\cite{Vicoso:2015hf}, amphibians~\cite{Hillis:1990gu}, the angiosperm genus \textit{Silene}~\cite{Slancarova:2013dq}, the angiosperm family \textit{Salicaceae}~\cite{Pucholt2015,Pucholt2017} and Coleoptera and Hemiptera (plate 2~\cite{Beukeboom:2014vb}).
-Indeed, in some cases, both male and female heterogametic sex-determining systems can be found in the same species, as reported in houseflies~\cite{Macdonald1978}, midges~\cite{Thompson1971}, frogs~\cite{Ogata:2007jm}, cichlid fish~\cite{Ser:2010iq}, tilapia~\cite{Lee2004}, sea bass~\cite{Vandeputte2007}, and lab-strains of Zebrafish~\cite{Liew2012,Wilson2014}.
-In addition, multiple transitions have occurred between genetic and environmental sex-determining systems (GSD$\leftrightarrow$ESD), e.g., in reptiles and fishes~\cite{Conover:1987in,Mank:2006bt,Pokorna:2009ui,Ezaz:2009tk,Pen:2010kk,Holleley:2015hc}.
-
-Predominant theories accounting for the spread of new sex-determining systems by selection involve fitness differences between sexes (e.g., sexually antagonistic selection) or sex ratio selection~\cite{Blaser2012, Beukeboom:2014vb,vanDoorn2014re}.
-%\citet{Bull:1977wt} shows that direct selection on new sex determination loci can allow them to spread and switch between male and female heterogamety. 
-van Doorn and Kirkpatrick~\cite{vanDoorn:2007eu,vanDoorn:2010hu} and Muralidhar and Veller~\cite{Muralidhar2018} have shown that new sex-determining alleles can be favoured if they arise at loci in close linkage with a locus that experiences sexual antagonism.
-Tighter linkage allows a stronger favourable association to build up between a male-beneficial allele, and a neo-Y allele, for example. 
-Such associations can favour cis-GSD transitions~\cite{vanDoorn:2007eu}, trans-GSD transitions~\cite{vanDoorn:2010hu}, and new partially-masculinizing or partially-feminizing alleles~\cite{Muralidhar2018}.
-However, any sexually-antagonistic loci that are more closely linked to the ancestral sex-determining locus will develop similar, favourable associations and are expected to hinder the spread of a new sex-determining system.
-
-The sex ratio is directly determined by the sex-determining system, and it has therefore been suggested that sex ratio selection is a dominant force in the evolution of sex determination (e.g., Bull, 1983, p 66-67 ~\cite{Bull:1983vi}; Buekeboom and Perrin, 2014, Chapter 7~\cite{Beukeboom:2014vb}).
-`Fisherian' sex ratio selection favours a 1:1 zygotic sex ratio when assuming that males and females are equally costly to produce~\cite{Fisher:1930wy,Charnov:1982wg}.
-This follows from the fact that, for an autosomal locus, half of the genetic material is inherited from a male and half from a female~\cite{West:2009we}. 
-Thus, if the population sex ratio is biased towards one sex, the average per-individual contribution of genetic material to the next generation from the opposite sex is greater. 
-Therefore, a mutant that increases investment in the rarer sex will spread via the higher per-individual contributions made by that sex. 
-%The default mode of sex ratio selection is `Fisherian' sex ratio selection, which favours equal investment in male and female offspring \citep[i.e., a 1:1 zygotic sex ratio when assuming that males and females are equally costly to produce,][]{Fisher:1930wy,Charnov:1982wg}.
-%Given that the sex-determining system can directly affect the sex ratio, we might expect Fisherian sex ratio selection to influence the spread of new sex-determining systems. 
-In the case of sex-chromosome evolution, Kozielska et al.
-(2014)~\cite{Kozielska:2010vm} consider systems in which the ancestral sex chromosomes experience meiotic drive (e.g., where driving X or Y chromosomes are inherited disproportionately often), which causes sex ratios to become biased~\cite{Hamilton:1967ts}.
-They find that masculinizing or feminizing mutations that arise at a new, unlinked locus (i.e., neo-Y or neo-W chromosomes) can then spread, which restore an even sex ratio.
-
-Here we use mathematical models to find the conditions under which new sex-determining systems spread when individuals experience selection at both diploid and haploid stages, which allows fitness differences between the sexes and sex ratio biases to occur simultaneously.
-Even in animal and plant species that have much larger and more conspicuous diploid phases than haploid phases, many loci experience significant haploid selection through gamete competition and/or meiotic drive~\cite{Mulcahy:1996ha,JOSEPH:2004haa}.
-We use the term `meiotic drive' to refer to the biased (non-Mendelian) segregation of genotypes during gamete production (from one parent) and the term `gametic competition' to refer to selection upon haploid genotypes within a gamete/gametophyte pool (potentially from multiple parents); the term `haploid selection' encompasses both processes.
-
-Segregation distortion provides putative evidence of haploid selection and can sometimes be attributed to meiotic drive and/or gametic competition~\cite{Lalanne2004,Fishman2005,Leppala2008,Leppala2013,Didion2015,Didion2016}.
-Where it has been characterized, meiotic drive generally occurs either during the production of male or female gametes only~\cite{Ubeda:2005gw,Lindholm:2016cw}.
-Gametic competition is also typically sex specific, occurring primarily among male gametes, because there are typically many more pollen/sperm than required for fertilization.
-Gametic competition may be particularly common in plants, in which 60-70\% of all genes are expressed in the male gametophyte, and these genes exhibit stronger signatures of selection than randomly-chosen genes~\cite{Borg:2009jpa,Arunkumar:2013iq,Gossmann:2014dua}.
-In addition, artificial selection pressures applied to male gametophytes are known to cause a response to selection (e.g.,~\cite{Hormaza:1996cv,Ravikumar:2003uo,Hedhly:2004iv,Clarke:2004ir}). 
-A smaller proportion of genes are thought to be expressed and selected during competition in animal sperm, although precise estimates are uncertain~\cite{Zheng:2001fi,JOSEPH:2004haa,Vibranovski:2010et}.
-Nevertheless, recent studies have demonstrated that sperm competition in animals can alter haploid allele frequencies and increase offspring fitness~\cite{Immler:2014im,Alavioon2017}.
-
-There are various ways by which genes experiencing haploid selection could influence transitions between sex-determining systems. 
-If we assume that haploid selection at any particular locus predominantly occurs in one sex (e.g., meiotic drive during spermatogenesis), then such loci experience a form of sex-specific selection. 
-In this respect, we might expect that haploid selection would affect transitions between sex-determining systems in a similar manner to sex-specific diploid selection (as explored in~\cite{vanDoorn:2007eu,vanDoorn:2010hu}).
-That is, new masculinizing mutations (neo-Y alleles) could be favoured via associations with alleles that are beneficial in the male haploid stage. 
-On the other hand, sex ratios can also become biased by linkage between the sex-determining locus and a locus that harbours genetic variation in haploid fitness. 
-For example, there are several known cases of sex ratio bias caused by sex-linked meiotic drive alleles (Burt and Trivers, 2006, Chapter 6~\cite{Burt:2006}) or selection among X- and Y-bearing pollen~\cite{Lloyd:1974tz,Conn:1981uw,Stehlik:2005ul,Stehlik:2006to,Field:2012fd,Field:2013cc}.
-It is not immediately clear how the spread of new sex-determining systems would be influenced by the combination of sex ratio biases and associations with haploid selected alleles.
-
-We find that the spread of novel sex-determining systems is influenced by both Fisherian sex ratio selection and by selection on linked alleles. 
-%We find that sex ratio biases caused by haploid selection can exert Fisherian sex ratio selection upon novel sex-determiners but that their spread is also determined by selection on genetically-associated alleles.
-%Indeed, it is only when haploid-selected loci are tightly linked to the ancestral sex-determining region (and so sex ratio biases are initially large) that we see an asymmetry between selection for XY to ZW transitions and ZW to XY transitions (e.g., because haploid selection in males only causes biased zygotic sex ratios in an ancestrally XY system).
-Surprisingly, Fisherian sex ratio selection does not dominate; it is possible for selection on linked alleles to drive turnover between sex-determining systems despite causing increasingly biased sex ratios.
-In addition to considering haploid selection, another novel development in our model is that we consider loci that are in very tight linkage with the ancestral sex-determining locus. 
-%Because sex-determining loci are often found within a region of suppressed recombination, there can be a significant number of tightly linked loci. 
-We find that loci tightly linked with the sex-determining locus can drive transitions in which the heterogametic sex changes, even when the new sex-determining locus is less closely linked to loci under selection (either including haploid selection or not).
-
-\section*{Model}
-
-%genetic system
-We consider transitions between ancestral and novel sex-determining systems using a three-locus model, each locus having two alleles (Fig \ref{fig:model_outline}). 
-Locus $\mathbf{X}$ is the ancestral sex-determining region, with alleles X and Y (or Z and W).
-Locus $\mathbf{A}$ is a locus under selection, with alleles $A$ and $a$.
-Locus $\mathbf{M}$ is a novel sex-determining region, at which the null allele ($M$) is initially fixed in the population such that sex of zygotes is determined by the genotype at the ancestral sex-determining region, $\mathbf{X}$; XX genotypes become females and XY become males (or ZW become females and ZZ become males).
-To evaluate the evolution of new sex-determining systems, we consider the invasion, fixation, maintenance, and/or loss of a novel sex-determining allele ($m$) at the $\mathbf{M}$ locus. 
-%We only do invasion analytically though (is this sentence still ok?)
-We assume that the $\mathbf{M}$ locus is epistatically dominant over the $\mathbf{X}$ locus such that zygotes with at least one $m$ allele develop as females with probability $k$ and as males with probability $1-k$, regardless of the $\mathbf{X}$ locus genotype.
-With $k=0$, the $m$ allele is a masculinizer (a neo-Y allele) and with $k=1$ the $m$ allele is a feminizer (a neo-W allele).
-With intermediate $k$, we can interpret $m$ as an environmental sex-determination (ESD) allele, such that zygotes develop as females in a proportion ($k$) of the environments they experience. 
-%We also analyze a model of maternally-controlled environmental sex-determination, where mothers with at least one $m$ allele produce daughters with probability $k$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Model Outline
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-%\centering
-%\centerline{\includegraphics[width=\linewidth]{Sex_determination_outline.pdf}}
-\caption{
-{\bf Outline of model features.}
-Panel A: Recombination rate parameters between the ancestral-sex-determining locus ($\mathbf{X}$, here assumed to have alleles X and Y), a locus under selection ($\mathbf{A}$, with alleles $A$ and $a$), and a new sex-determining locus ($\mathbf{M}$, with alleles $M$ and $m$).
-If $r<1/2$, then associations between ancestral sex-determining alleles and selected alleles can be maintained past recombination in males. 
-Panel B: Haploid selection is often sex-specific, occurring during haploid production or competition in either males or females. 
-For example, haploid selection in males only is represented by the dashed circle.  
-If X or Y alleles remain associated with alleles that experience haploid selection in males ($r<1/2$), then zygotic sex ratios can become biased because either X- or Y-bearing male gametes/gametophytes will be more abundant after haploid selection.
-However, the zygotic sex ratio is not biased by male haploid selection in ZW sex-determining systems. 
-Similarly, zygotic sex ratio biases can occur if haploid selected alleles are associated with new sex-determining alleles ($R<1/2$). 
-Panel C: During cis-GSD transitions (XY to XY or ZW to ZW), a neo-Y allele spreads to pseudo-fixation (its maximum frequency among male gametes) and the ancestral Y allele is lost. 
-Panel D: During trans-GSD transitions (XY to ZW or ZW to XY), a neo-W allele spreads to pseudo-fixation (its maximum frequency among female gametes) and the ancestral X allele is lost. 
-Neo-W alleles allow Y-associated alleles into females, which may impede or aid their spread. 
-}
-\label{fig:model_outline}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%life-cycle
-In each generation, we census the genotype frequencies in male and female gametes/gametophytes (hereafter gametes) before gametic competition. 
-A full description of our model, including recursion equations, is given in \nameref{app:recurs}. 
-First, competition occurs among male gametes (sperm/pollen competition) and among female gametes (egg/ovule competition) separately. 
-Selection during gametic competition depends on the $\mathbf{A}$ locus genotype; relative fitnesses are given by $w_A^\Hermaphrodite$ and $w_a^\Hermaphrodite$ ($\Hermaphrodite \in \{\female,\male\}$; see table \ref{tab:fitnesstable}).
-%$w_{A}^\male$ and $w_{a}^\male$ for male gametes and $w_{A}^\female$ and $w_{a}^\female$ for female gametes, see table \ref{tab:fitnesstable}.
-We assume that all gametes compete for fertilization during gametic competition, which implies a polygamous mating system. 
-Gametic competition in monogamous mating systems is, however, equivalent to meiotic drive in our model (described below), as either only alters the frequency of gametes produced by heterozygotes. 
-After gametic competition, conjugation between male and female gametes occurs at random.
-The resulting zygotes develop as males or females, depending on their genotypes at the $\mathbf{X}$ and $\mathbf{M}$ loci.
-%(and the $\mathbf{M}$ genotype of their mother in the case of maternal control).
-Diploid males and females then experience selection, with relative fitnesses $w_{AA}^{\Hermaphrodite}$, $w_{Aa}^{\Hermaphrodite}$, and $w_{aa}^{\Hermaphrodite}$.
-%where $g$ is the diploid genotype at the $\mathbf{A}$ locus ($g \in \{AA, Aa, aa\}$).
-%Diploids compete with others of the same sex, where selection depends on the sex of the individual and its genotype at the $\mathbf{A}$ locus.
-The next generation of gametes is produced by meiosis, during which recombination and sex-specific meiotic drive can occur. 
-Recombination (i.e., an odd number of cross-overs) occurs between loci $\mathbf{X}$ and $\mathbf{A}$ with probability $r$, between loci $\mathbf{A}$ and $\mathbf{M}$ with probability $R$, and between loci $\mathbf{X}$ and $\mathbf{M}$ with probability $\rho$.
-Any linear order of the loci can be modelled with appropriate choices of $r$, $R$, and $\rho$ (see Fig \ref{fig:model_outline}A and \nameref{tab:chisubstitutions}). 
-Individuals that are heterozygous at the $\mathbf{A}$ locus may experience meiotic drive; a gamete produced by $Aa$ heterozgotes of sex $\Hermaphrodite$ bears allele $A$ with probability $\alpha^\Hermaphrodite$.
-Thus, the $\mathbf{A}$ locus can experience sex-specific gametic competition, diploid selection, and/or meiotic drive.
-
-\begin{table}[ht]
-%\centering
-\smallskip
-\caption{{\bf Relative fitness of different genotypes in sex $\Hermaphrodite \in \{\female,\male\}$ } }
-\begin{tabular}{l c }
-\hline\hline
-  Genotype & Relative fitness during gametic competition \\ [0.5ex] \hline
-  $A$ & $w_{A}^\Hermaphrodite = 1+t^\Hermaphrodite$ \\
-  $a$ & $w_{a}^\Hermaphrodite = 1$ \\ [0.5ex] \hline
-  Genotype & Relative fitness during diploid selection \\ [0.5ex] \hline
-  $AA$ & $w_{AA}^\Hermaphrodite = 1+ s^\Hermaphrodite$ \\
-  $Aa$ & $w_{Aa}^\Hermaphrodite = 1+h^\Hermaphrodite s^\Hermaphrodite$ \\
-  $aa$ & $w_{aa}^\Hermaphrodite = 1$ \\ [0.5ex] \hline
-  Genotype & Transmission during meiosis in $Aa$ heterozygotes \\ [0.5ex] \hline
-  $A$ & $\alpha^\Hermaphrodite=1/2+\alpha_{\Delta}^{\Hermaphrodite}/2$ \\
-  $a$ & $1-\alpha^\Hermaphrodite=1/2-\alpha_{\Delta}^{\Hermaphrodite}/2$ \\
-  \hline \hline
-  \label{tab:fitnesstable}
- \end{tabular}
-\end{table}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Results}
-%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The model outlined above describes both ancestral XY and ZW sex-determining systems. %if we relabel the two sexes as being ancestrally `heterogametic' or ancestrally `homogametic'. 
-Without loss of generality, we refer to the ancestrally heterogametic sex as male and the ancestrally homogametic sex as female.
-That is, we primarily describe an ancestral XY sex-determining system but our model is equally applicable to an ancestral ZW sex-determining system (relabelling the ancestrally heterogametic sex as female and the ancestrally homogametic sex as male and switching the labels of males and females throughout).
-We use a superscript to specify the ancestral sex-determining system described, e.g., $^{(XY)}$ for ancestral XY sex-determination.
-
-\subsection*{Generic invasion by a neo-Y or neo-W}
-
-The evolution of a new sex-determining system requires that a rare mutant allele, $m$, at the novel sex-determining locus, $\mathbf{M}$, increases in frequency when rare. 
-This is determined by the leading eigenvalue ($\lambda_m^{(XY)}$) of the system of eight equations describing the frequency of eggs and sperm carrying the $m$ allele in the next generation (equations \ref{eq:recursions}).
-%, evaluated at the above equilibrium.
-%Thus, the system describing the change in frequency of the $m$ allele consists of eight recursion equations. 
-This system simplifies substantially for a dominant neo-Y ($k=0$) or neo-W ($k=1$), see \nameref{app:inv_cond}. 
-The leading eigenvalue for a rare neo-Y or neo-W allele, $m\in\{Y',W'\}$, is the largest value of X that solves $x^2+ b x + c = 0$.  %$(\lambda_m^{(i)})^2+ b \lambda_m^{(i)} + c =0$. 
-The coefficients are $b= - (\Lambda_{mA}^{(XY)} + \Lambda_{ma}^{(XY)})+(\chi_{mA}^{(XY)} + \chi_{ma}^{(XY)})$ and $c = (\Lambda_{mA}^{(XY)} - \chi_{mA}^{(XY)}) (\Lambda_{ma}^{(XY)} - \chi_{ma}^{(XY)}) - \chi_{mA}^{(XY)} \chi_{ma}^{(XY)}$, where $\Lambda_{mi}^{(XY)}>0$ is the multiplicative growth rate (which we will call the ``haplotypic growth rate'') of the neo-sex determination allele $m$ on background $i\in\{A,a\}$ without accounting for loss due to recombination ($R=0$), and $\chi_{mi}^{(XY)}>0$ is the rate at which mutant haplotypes on background $i\in\{A,a\}$ recombine onto the other $\mathbf{A}$ locus background in heterozygotes (proportional to $R$), see Table \ref{tab:haplotype_growth}.
-In the ancestral population, it is convenient to follow the frequency of the $A$ allele among female gametes (eggs), $p^\female_X$, and among X-bearing, $p^\male_X$, and among Y-bearing, $p^\male_Y$, male gametes (sperm/pollen).
-We also track the fraction of male gametes that are Y-bearing, $q$, which may deviate from $1/2$ due to meiotic drive in males. 
-We will consider only equilibrium frequencies of alleles, $\hat{p}^\Hermaphrodite_i$, and Y-bearing male gametes, $\hat{q}$, when calculating the eigenvalues.
-
-\begin{table}[!ht]
-\centering
-\smallskip
-%\caption{Parameters determining invasion (equation \ref{eq:charpoly_neoY}) for neo-Y or neo-W alleles}
-\caption{ {\bf Parameters determining invasion of mutant neo-Y and neo-W alleles into an ancestrally XY system}}
-\begin{tabular}{l}
-\hline\hline
-   \noalign{\vskip 0.5ex}
-   $m$ is a neo-Y ($k=0$) \\ [0.5ex] \hline \noalign{\vskip 1ex}
-  $\Lambda_{Y'A}^{(XY)} = {\left( 2 \zeta \right)}^{-1} \left[\hat{p}_X^\female w_{A}^{\female} w_{A}^{\male} w_{AA}^{\male} + (1-\hat{p}_X^\female) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} (1+\alpha_{\Delta}^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\male}_{D} \right) $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\Lambda_{Y'a}^{(XY)} = {\left( 2 \zeta \right)}^{-1} \left[(1-\hat{p}_X^\female) w_{a}^{\female} w_{a}^{\male} w_{aa}^{\male} + \hat{p}_X^\female w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male}(1 - \alpha_{\Delta}^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\male}_{D} \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\chi_{Y'A}^{(XY)} = R {\left( 2 \zeta \right)}^{-1} \left[ (1-\hat{p}_X^\female) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} (1+\alpha_{\Delta}^{\male}) \right]/  \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\male}_{D} \right)   $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\chi_{Y'a}^{(XY)} = R {\left( 2 \zeta \right)}^{-1} \left[   \hat{p}_X^\female w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male} (1 - \alpha_\Delta^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\male}_{D} \right)  $\\ [1ex] \hline
-  \noalign{\vskip 0.5ex}
-  $m$ is a neo-W ($k=1$) \\ [0.5ex] \hline \noalign{\vskip 1ex}
-  $\Lambda_{W'A}^{(XY)} = {\left[ 2 (1 - \zeta) \right]}^{-1} \left[ \bar{p}^{\male} w_{A}^{\male} w_{A}^{\female} w_{AA}^{\female}+(1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female}(1+\alpha_{\Delta}^{\female})\right]/ \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\female}_{D} \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\Lambda_{W'a}^{(XY)} = {\left[ 2 (1 - \zeta) \right]}^{-1} \left[ (1-\bar{p}^{\male}) w_{a}^{\male} w_{a}^{\female} w_{aa}^{\female}+\bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female}(1-\alpha_{\Delta}^{\female})\right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\female}_{D} \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\chi_{W'A}^{(XY)} = R {\left[ 2 (1 - \zeta) \right]}^{-1} \left[ (1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female} (1+\alpha_{\Delta}^{\female}) \right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\female}_{D} \right)  $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\chi_{W'a}^{(XY)} = R {\left[ 2 (1 - \zeta) \right]}^{-1} \left[ \bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female} (1-\alpha_{\Delta}^{\female}) \right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\female}_{D} \right) $ \\ [1ex]
-  \hline \hline 
-   \end{tabular}
-   \begin{flushleft} 
-$\bar{p}^{\male}=(1-\hat{q})\hat{p}_X^\male + \hat{q}\hat{p}_Y^\male$ is the average frequency of the $A$ allele among X- and Y-bearing male gametes.
-%      \item $R$ is the probability of recombination between loci $\mathbf{A}$ and $\mathbf{M}$.
-$\zeta$ is the zygotic sex ratio (fraction male).
-$\bar{w}^{\Hermaphrodite}_{D}$ is the mean fitness of diploids of sex $\Hermaphrodite$.
-$\bar{w}_H^\Hermaphrodite$ is the mean fitness of haploids from sex $\Hermaphrodite$, see \nameref{tab:meanfitnesses}.
-\end{flushleft}
-  \label{tab:haplotype_growth}
-\end{table}
-
-The new sex-determining allele increases in frequency when rare when the largest eigenvalue is greater than one ($\lambda_m^{(XY)}>1$). 
-%If the average change in frequency of the two haplotypes that carry the $m$ allele ($Am$ and $am$) is positive, invasion will always occur, i.e., if $(\Lambda_{mA} + \Lambda_{ma})/2 > 1$ then $\Lambda > 1$.
-%The leading eigenvalue is the largest solution of $f(\lambda_m^{(i)})=(\lambda_m^{(i)})^2+b\lambda_m^{(i)}+c=0$ and the Perron-Frobenius theorem guarantees that it is positive, unique, and real.  
-%Since $f(\Lambda_{mA}^{(i)})$ and $f(\Lambda_{ma}^{(i)})$ are of opposite signs, the leading eigenvalue must fall between these two quantities and is the larger of them when $R = 0$ (see \nameref{file:Mathematica}).
-If both haplotypic growth rates are greater than one ($\Lambda_{mA}^{(XY)}, \Lambda_{ma}^{(XY)}>1$), then the new sex-determining allele invades regardless the rate of recombination between the new sex-determining locus and the selected locus ($R$), see \nameref{app:inv_cond} for details.
-Conversely, if both haplotypic growth rates are less than one ($\Lambda_{mA}^{(XY)}, \Lambda_{ma}^{(XY)}<1$), then invasion can never occur.  
-Finally, if only one haplotypic growth rate is greater than one, the new sex-determining allele can always invade when arising at a locus that is tightly linked to the selected locus ($R\approx0$).  
-Furthermore, it can be shown that the leading eigenvalue declines with $R$, and invasion requires that $R$ is sufficiently small such that: 
-\begin{equation}\label{eq:lambdasGen}
-%\frac{\chi_{mA}}{\Lambda_{mA}-1}+\frac{\chi_{ma}}{\Lambda_{ma}-1}>0.
-\chi_{ma}^{(XY)}/\left(\Lambda_{ma}^{(XY)} - 1\right) + \chi_{mA}^{(XY)}/\left(\Lambda_{mA}^{(XY)} - 1\right) < 1.
-\end{equation}
-\noindent 
-This condition may or may not be satisfied for the full range of locations of the new sex-determining locus, including $R=1/2$, depending on the nature of selection.  
-Interpreting this condition, if we assume that only the $mA$ haplotype would increase in frequency when $R=0$ ($\Lambda_{ma}^{(XY)}<1<\Lambda_{mA}^{(XY)}$) the first term on the left-hand side of \eqref{eq:lambdasGen} is negative and invasion requires that rate of growth of $mA$ haplotypes ($\Lambda_{mA}^{(i)}-1>0$) and the rate at which $mA$ haplotypes are produced by recombination in $ma$ haplotypes ($\chi_{ma}^{(i)}$) are sufficiently large relative to the rate of decline of $ma$ haplotypes ($1-\Lambda_{ma}^{(i)}>0$) and the rate of loss of $mA$ haplotypes due to recombination ($\chi_{mA}^{(i)}$).
-
-We can draw a number of key points about the invasion of neo-Y and neo-W mutations from Table \ref{tab:haplotype_growth}. 
-First, Fisherian sex ratio selection will favour the spread of a neo-Y and inhibit the spread of a neo-W if the ancestral zygotic sex ratio is biased towards females, $\zeta<1/2$ (i.e., the first factor of the $\Lambda_{mi}^{(XY)}$ is greater than one for a neo-Y and less than one for a neo-W).
-However, the spread of a neo-Y (neo-W) also depends on the male (female) fitness of associated alleles (see terms involving equilibrium allele frequencies, $\hat{p}$'s).
-Second, invasion by a neo-Y (neo-W) does not directly depend on the fitness of female (male) diploids. %(for a given set of equilibrium allele frequencies).
-This is because a dominant neo-Y (neo-W) is always found in males (females), and therefore the frequency of the neo-Y (neo-W), $m$, only changes in males (females), Fig \ref{fig:model_outline}C,D. 
-Finally, invasions by a neo-Y and a neo-W are qualitatively different.
-This is because a gamete with the neo-Y always pairs with a female gamete containing an X, Fig \ref{fig:model_outline}C.
-By contrast, a gamete with a neo-W can pair with an X- or Y-bearing male gamete, Fig \ref{fig:model_outline}D.
-Consequently, neo-W-bearing females obtain a different frequency of $A$ alleles from mating (when $\hat{p}_X^\male \neq \hat{p}_Y^\male$) compared to ancestral ($MM$) females.
-
-In order to explicitly determine the conditions under which a rare new sex-determining allele spreads, we must calculate the equilibrium frequency of the $A$ allele (i.e., $\hat{p}^\female_X$, $\hat{p}^\male_X$, and $\hat{p}^\male_Y$) and Y-bearing male gametes ($\hat{q}$) in the ancestral population.
-Since only the $\mathbf{A}$ locus experiences selection directly, any deterministic evolution requires that there is a polymorphism at the $\mathbf{A}$ locus. 
-Polymorphisms can be maintained by mutation-selection balance or transiently present during the spread of beneficial alleles. 
-However, polymorphisms maintained by selection can maintain alleles at intermediate allele frequencies for longer periods. 
-Here, we focus on polymorphisms maintained by selection, where the $A$ allele reaches a stable intermediate equilibrium frequency under the ancestral sex-determining system before the new sex-determining allele ($m$) arises.
-Such polymorphisms can be maintained by heterozygote advantage, sexually-antagonistic selection, ploidally-antagonistic selection, or a combination~\cite{Immler:2012tl}.
-We can analytically calculate the allele frequency of the $A$ allele using two alternative simplifying assumptions: 
-(1) the $\mathbf{A}$ locus is within (or tightly linked to) the non-recombining region around the ancestral sex-determining locus ($r \approx 0$) or (2) selection is weak relative to recombination ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon<<1$).
-
-\subsection*{Tight linkage with the ancestral sex-determining locus ($r \approx 0$)}
-
-The ancestral equilibrium allele frequencies and their stability conditions are given in \nameref{app:eq_stab}. 
-When there is complete linkage between the ancestral sex-determining locus and the $\mathbf{A}$ locus ($r=0$), either the $A$ allele or the $a$ allele must be fixed in gametes containing a Y allele. 
-% because selection on the Y is effectively haploid an incapably of maintaining a polymorphism in the absence of frequency dependent selection. 
-Because the labelling of alleles is arbitrary, we will assume that the $a$ locus is fixed in gametes with a Y ($p^\male_Y=0$), without loss of generality. 
-If there are two alleles maintained at the $\mathbf{A}$ locus, the $A$ allele can be fixed ($\hat{p}^\female_X=\hat{p}^\male_X=1$) or segregating at an intermediate frequency (0<$\hat{p}^\female_X, \hat{p}^\male_X$<1) in gametes with an X.
-%However, because the X is present in both males and females, there are distinct selection pressures on X's in females and X's in males, which will always be paired with an $A$ allele from the Y.
-
-We find that a neo-Y allele can never invade an ancestral XY system that already has tight linkage with the locus under selection ($\lambda_{Y'}^{(XY)} \leq 1$ when $r=0$, for details see \nameref{file:Mathematica}).
-When $R=0$, a neo-Y haplotype with the same allele as the ancestral Y is neutral ($\Lambda_{Y'a}^{(XY)}=1$) and does not change in frequency.
-The other neo-Y haplotype will not spread ($\Lambda_{Y'A}^{(XY)}<1$) given that the initial equilibrium is stable. 
-Therefore, a neo-Y mutation cannot spread in an ancestral XY system ($\lambda_{Y'}^{(XY)} \leq 1$, regardless of $R$) where selected loci are within or very near the non-recombining region around the sex-determining locus.
-In essence, through tight linkage with the $\mathbf{A}$ locus, the ancestral Y becomes strongly specialized on the allele that has the highest fitness across male haploid and diploid phases. 
-Given that the ancestral Y is at this equilibrium, it is not possible for a neo-Y to create males that have higher fitness than the ancestral Y.
-
-Neo-W alleles, on the other hand, can invade an ancestral XY system under some conditions (the full invasion conditions are given in \nameref{app:inv_cond}; equations \ref{Binvasion} and \ref{Ainvasion}).
-Counterintuitively, selection on loci within the non-recombining region around the sex-determining locus can favour the invasion of a less closely linked neo-W, whatever the form of selection maintaining a polymorphism (sexually-antagonistic selection, overdominance, ploidally-antagonistic selection, or some combination, Fig \ref{fig:SexAntagTighter}, \nameref{fig:temporalOverdominance}, \nameref{fig:regionPloidAntag}, and \nameref{fig:SexAntagTighterMaleDrive}).
-The conditions become more restrictive, however, with increasing recombination ($R$) between the new sex-determining locus and the selected locus.  
-The invasion of completely unlinked neo-W alleles ($R = 1/2$) can occur with overdominance in males or with haploid selection but is not possible with only sexually-antagonistic selection if selection is directional in each diploid sex (see \nameref{file:Mathematica}).
-To develop an intuition for how less closely linked neo-W alleles invade ($R>r$), we here focus on cases where there is no haploid selection and discuss the additional effect of haploid selection in \nameref{app:inv_cond}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Tighter linkage allows looser sex-linkage to evolve, even in absence of haploid selection
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-%\centerline{\includegraphics[width=1.5\linewidth]{PositionPlot_SexAntagTighter}}
-\caption{
-{\bf Transitions between XY and ZW systems can occur even when the new sex-determining locus is less tightly linked to a locus under sexually-antagonistic selection (even without haploid selection).}
-In panel A, linkage is loose enough relative to selection that the analytical results assuming weak selection hold, and a neo-W allele can only invade when it arises at a locus more tightly linked with the selected locus ($R<r$; shaded region).
-In panel B, linkage is tight enough relative to selection that the analytical results assuming weak selection do not hold, and a neo-W can invade even when it is less tightly linked with the selected locus ($r<R$; unshaded region around \text{*}).
-In panel C we vary the recombination rate between the neo-W and the selected locus ($R$) for a fixed recombination rate between the ancestral sex-determining locus and the selected locus ($r=0.005$). 
-Coloured markers show recombination rates for which the temporal dynamics of invasion are plotted in the inset, demonstrating that neo-W alleles can reach pseudo-fixation if they are more (black) or less (red) closely linked to a locus experiencing sexually-antagonistic selection.
-A very loosely linked neo-W does not spread in this case (blue and green lines overlap and go to 0 in inset). 
-Fitness parameters are: $w_{AA}^\female = 1.05$, $w_{aa}^\male = 1.2$, $w_{aa}^\female = w_{AA}^\male = 0.85$, $w_{Aa}^\Hermaphrodite = 1$,  $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
-%\textcolor{red}{consider removing panel A, which is repeated in Fig 3.}
-%\textcolor{blue}{probably better to remove from panel 3, eh?}
-}
-\label{fig:SexAntagTighter}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-If we categorise the $a$ allele as being ancestrally `male-beneficial' via the fact that it is fixed on Y backgrounds, then $\Lambda_{W'A}^{(XY)}>1$ indicates that the neo-W spreads when found with the ancestrally `female-beneficial' allele.
-Broadly, this is possible because ancestral X alleles are sometimes in males and are therefore unable to perfectly specialise on the `female-beneficial' allele. 
-For example, when the $a$ allele is favoured on ancestral X backgrounds in males, a polymorphism of $A$ and $a$ alleles can be maintained on the X background despite selection for the $A$ allele in females ($s^\female>0$, $0<h^\female<1$), see outlined region in Fig \ref{fig:regionplots}A.
-When the $a$ allele is strongly favoured on the X background in males ($w_{aa}^\male$ sufficiently large relative to $w_{Aa}^\male$), neo-W-$A$ haplotypes can spread ($\Lambda_{W'A}^{(XY)}>1$, see grey region in Fig \ref{fig:regionplots}A) because they produce higher fitness females ($AA$ or $Aa$ genotypes) and are unleashed from counterselection in males.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Both neo-W haplotypes can spread, in the absence of haploid selection, when there is overdominance
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-%\centerline{\includegraphics[width=1.25\linewidth]{Region_plot_combined_Mike}}
-%\centerline{\includegraphics[width=1.25\linewidth]{Region_plot_combined}}
-\caption{
-{\bf When the ancestral XY locus is tightly linked to a locus under selection ($r=0$), one or both neo-W haplotypes can spread. }
-We vary the fitness of male homozygotes relative to heterozygotes ($w_{Aa}^\Hermaphrodite=1$) and only consider stable equilibria at which both $\mathbf{A}$ locus alleles are maintained and the $a$ allele is initially fixed on Y backgrounds, region outlined.
-Here, selection in females can favour the $A$ allele (panel A, $w_{aa}^\female=0.85$, $w_{AA}^\female=1.05$), favour the $a$ allele (panel B, $w_{aa}^\female=1.05$, $w_{AA}^\female=0.85$), or be overdominant (panel C, $w_{aa}^\female=w_{AA}^\female=0.6$).
-If either haplotypic growth rate ($\Lambda_{W'A}^{(XY)}$ or $\Lambda_{W'a}^{(XY)}$) is greater than one, then a rare neo-W allele can spread for, at least, some values of $R>r$. 
-The parameter values marked with an asterisk correspond to the fitnesses used in Fig \ref{fig:SexAntagTighter}C. 
-Where both haplotypic growth rates are greater than one, a neo-W will spread when rare, regardless of linkage with the selected locus (for any $R$). 
-\nameref{fig:positionOverdominance} shows the dynamics arising with the parameters marked with a dagger. 
-Here, there is no haploid selection $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
-}
-\label{fig:regionplots}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-When only one neo-W haplotype has growth rate greater than one (see Fig \ref{fig:regionplots}), a neo-W allele can invade as long as Eq \eqref{eq:lambdasGen} is satisfied, which may require that the recombination rate, $R$, is small enough.
-Nevertheless, because we assume here that $r$ is small, these results indicate that a more loosely linked sex-determining region ($r<R$) can spread.
-For example, tightly sex-linked loci that experience sexually-antagonistic selection can drive trans-GSD transitions in which the new sex-determining locus is less closely linked to the locus under selection (Fig \ref{fig:SexAntagTighter}).
-
-Given that the $a$ allele can be considered ancestrally `male-beneficial' because it is fixed on Y backgrounds, it is surprising that neo-W-$a$ haplotypes can sometimes be favoured by selection in females ($\Lambda_{W'a}^{(XY)}>1$).
-Again, this occurs because ancestral X alleles also experience selection in males, where they are ancestrally always paired with a Y-$a$ gamete. 
-If there is overdominance in males, X-$A$ Y-$a$ males have high fitness and the $A$ allele is favoured by selection on the X background in males. 
-Therefore, the $A$ allele can be polymorphic or even fixed on the X background despite selection favouring the $a$ allele in females (e.g., see outlined region in Fig \ref{fig:regionplots}B and~\cite{Lloyd1977,Otto2014}).
-In such cases, neo-W-$a$ haplotypes can spread because they create more $Aa$ and $aa$ females when pairing with an X-bearing gamete from males and because they bring Y-$a$ haplotypes into females, where it has higher fitness (Fig \ref{fig:model_outline}D).
-
-In some cases, both W-$A$ and W-$a$ haplotypes can spread.
-For example, when $AA$ individuals have low fitness in females yet the $A$ is polymorphic or fixed on the X background due to overdominance in males (Fig \ref{fig:regionplots}B and \ref{fig:regionplots}C), both neo-W-$A$ and neo-W-$a$ haplotypes produce fewer unfit $AA$ females.
-This is true for the neo-W-$A$ haplotype because it can pair with a Y-$a$ haplotype and still be female. 
-Wherever both haplotypic growth rates are greater than one, invasion by a neo-W is expected regardless of its linkage with the selected locus (i.e., for any $R$, see \nameref{fig:positionOverdominance} and \nameref{fig:temporalOverdominance} for examples).
-
-Assuming selection is weak relative to recombination, van Doorn and Kirkpatrick~\cite{vanDoorn:2010hu} showed that invasion by a neo-W allele occurs under the same conditions as `pseudo-fixation' (at pseudo-fixation the neo-W reaches its maximum frequency among eggs, which is usually 1/2, but can deviate from 1/2 when there is haploid selection before censusing).
-An equivalent analysis is not possible where recombination rates are low. 
-However, numerical simulations demonstrate that new sex-determining alleles do not necessarily reach pseudo-fixation, which can lead to the stable maintenance of a mixed sex-determining system, in which X, Y, Z, and W alleles all segregate (e.g., \nameref{fig:freqAll}B,C).
-
-\subsection*{Loose linkage with the ancestral sex-determining region}
-
-Here we assume that selection is weak ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon<<1$) and thus implicitly assume that all recombination rates ($r$, $R$ and $\rho$) are large relative to selection.
-%, we denote the leading eigenvalues describing the invasion of a neo-Y ($k=0$) and a neo-W ($k=1$) into an ancestrally XY system by $\lambda_{Y',XY}$ and $\lambda_{W',XY}$, respectively. 
-To leading order in selection, the leading eigenvalues are:
-
-\begin{equation}
-\lambda_{Y'}^{(XY)} =1+ \frac{1}{4}V_{A}S_{A}^2\frac{ \left( r-R \right) }{r R}+O\left(\epsilon^3 \right) 
-\label{eq:lambda_neoY}
-\end{equation}
-
-\noindent 
-and
-
-\begin{equation}
-\lambda_{W'}^{(XY)} =\lambda_{Y'}^{(XY)}+\left(2\alpha_{\Delta}^\male-2\alpha_{\Delta}^\female+t^\male-t^\female \right) \left( \hat{p}^\male_Y-\hat{p}^\male_X \right)/2
-+O\left(\epsilon^3 \right)
-\label{eq:lambda_neoW}
-\end{equation}
-
-\noindent
-where $V_{A}=\bar{p}(1-\bar{p})$ is the variance in the equilibrium frequency of $A$ and $S_{A}=(D^\male +\alpha_{\Delta}^\male+t^\male) - (D^\female+\alpha_{\Delta}^\female+t^\female)$ describes sex differences in selection for the $A$ versus $a$ allele across diploid selection, meiosis, and gametic competition.
-The diploid selection term, $D^\Hermaphrodite=\big{[} \bar{p}s^\Hermaphrodite+(1-\bar{p})h^\Hermaphrodite s^\Hermaphrodite\big{]} -\big{[} \bar{p}h^\Hermaphrodite s^\Hermaphrodite+(1-\bar{p}) \big{]}$, is the difference in fitness between $A$ and $a$ alleles in diploids of sex $\Hermaphrodite \in \{\female,\male\}$, where $\bar{p}$ is the leading-order probability of mating with an $A$-bearing gamete from the opposite sex (equation \ref{eq:pAve}).
-The difference in $A$-allele-frequency among Y-bearing sperm versus X-bearing sperm is given by $\hat{p}^\male_Y-\hat{p}^\male_X=V_{A}\big{(}D^\male - D^\female+\alpha_{\Delta}^\male-\alpha_{\Delta}^\female+t^\male-t^\female\big{)}(1-2r)/(2r)$.
-
-%The new sex-determining allele, $m$, will spread in an XY system if $\lambda_{m}^{(XY)}>1$. 
-Eq \eqref{eq:lambda_neoY} demonstrates that, under weak selection, a neo-Y allele will invade an XY system ($\lambda_{Y'}^{(XY)}>1$) if and only if it is more closely linked to the selected locus than the ancestral sex-determining locus (i.e., if $R<r$; note that $V_{A}S_{A}^2$ is strictly positive as long as $\mathbf{A}$ is polymorphic).
-This echoes our results above where a neo-Y could never invade if $r\approx0$. 
-It is also consistent with the results of \cite{vanDoorn:2007eu}, who considered diploid selection only and also found that cis-GSD transitions can only occur when the new sex-determining locus is more closely linked to a locus under sexually-antagonistic selection.
-%Because tighter linkage between the sex-determining region and a selected locus evolves during these transitions, stronger associations between selected alleles and diploid sexes can build up by selection (e.g., between male-beneficial alleles and the male-determining allele, Y).%, increasing diploid mean fitness (Fig \ref{fig:Combination_MeanFit}).
-
-With weak selection and no haploid selection ($t^\Hermaphrodite=\alpha^\Hermaphrodite_{\Delta}=0$), the spread of a neo-W is equivalent to the spread of a neo-Y ($\lambda_{W'}^{(XY)}=\lambda_{Y'}^{(XY)}$), such that trans-GSD transitions can also occur only if the new sex-determining locus is more closely linked to a locus under selection ($R<r$), as found by \cite{vanDoorn:2010hu}.
-When there is haploid selection, invasion also typically occurs when the neo-W is more closely linked to the selected locus than the ancestral sex-determining region (Fig \ref{fig:Combination_Centimorgans}).
-For example, if the $\mathbf{A}$ locus is unlinked to the ancestral sex-determining locus ($r=1/2$), a more closely linked neo-W ($R<1/2$) can always invade.
-In this case, there is no ancestral association between $\mathbf{A}$ alleles and sex chromosomes in males, $\left( \hat{p}^\male_Y-\hat{p}^\male_X \right)=0$, see Eq \eqref{eq:freq_diffs}. 
-The second term in Eq \eqref{eq:lambda_neoW} therefore disappears and invasion depends only on the sign of $(r-R)$.%, as in the case of the neo-Y.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%A neo-W can invade an XY system under a large number of selective regimes
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-%\includegraphics[width=\linewidth]{PositionPlot}
-\caption{
-{\bf Ploidally-antagonistic selection allows a less tightly linked neo-W allele to invade.}
-In panel A, male drive ($\alpha^\male_{\Delta} = -1/20$, $t^\Hermaphrodite = \alpha^\female_{\Delta} = 0$) opposes selection in diploids (no sex-differences: $s^\Hermaphrodite = 1/10$, $h^\Hermaphrodite = 7/10$), in which case the new sex-determining allele can invade regardless of its linkage with the selected locus ($R$).
-In panel B, gametic competition in males ($t^\male = -1/10$, $t^\female = \alpha^\Hermaphrodite_{\Delta} = 0$) opposes selection in diploids (sex-differences: $s^\male = 3/20$, $s^\female = 1/20$, $h^\Hermaphrodite = 7/10$), in which case the new sex-determining allele can once again invade regardless of $R$.
-}
-\label{fig:Combination_Centimorgans}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-However, with haploid selection and $r<1/2$, the additional term in Eq \eqref{eq:lambda_neoW} can be positive.
-This can allow neo-W invasion ($\lambda_{W'}^{(XY)}>1$), even when the new sex-determining locus is less closely linked to the selected locus ($R>r$). 
-%These transitions are unusual because, when $R>r$, associations that selection has built up between alleles more favourable in one sex and alleles that determine sex will be weakened. 
-%Mean diploid fitness therefore decreases during heterogametic transitions that create looser sex-linkage (Fig \ref{fig:Combination_MeanFit}B,D). 
-%Eq \eqref{eq:lambda_neoW} shows that, with weak selection, neo-W alleles can invade an XY system for a large number of selective regimes. 
-%To clarify the parameter space under which $\lambda_{W'}^{(XY)}>1$ , we consider several special cases. 
-%Firstly, if the $\mathbf{A}$ locus is unlinked to the ancestral sex-determining region ($r=1/2$), a more closely linked neo-W ($R<1/2$) can always invade because there is no ancestral association between $A$ alleles and sex chromosomes in males, $\left( \hat{p}^\male_Y-\hat{p}^\male_X \right)=0$, see Eq \eqref{eq:freq_diffs}.
-%The second term in Eq \eqref{eq:lambda_neoW} therefore disappears and invasion depends only on the sign of $(r-R)$, as in the case of the neo-Y. 
-%Indeed, invasion typically occurs when the neo-W is more closely linked to the selected locus than the ancestral sex-determining region (Fig \ref{fig:Combination_Centimorgans}).
-To clarify the parameter space under which invasion occurs despite looser sex-linkage ($\lambda_{W'}^{(XY)}>1$ despite $R>r$), we focus on the special case where $R=1/2$ and $r<1/2$ (e.g., the selected locus is on the ancestral sex chromosome and the novel sex-determining locus arises on an autosome).
-In Table \ref{tab:specialcases} we give the conditions where invasion occurs when we further assume that haploid selection only occurs in one sex (e.g., during male meiosis only) and dominance coefficients are equal in the two sexes, $h^\female=h^\male$.
-When there is no gametic competition and meiotic drive is in one sex only, an unlinked neo-W can invade as long as the same allele is favoured during diploid selection in males and females ($s^\female s^\male>0$, see Fig \ref{fig:Combination_Centimorgans}A and Fig \ref{fig:SexRatioBad}B).
-%, which is 50\% of the parameter space.
-When there is no meiotic drive and gametic competition occurs in one sex only, an unlinked neo-W can invade as long as the same allele is favoured in male and female diploid selection and there are sex differences in selection of one type (e.g., $s^\female(s^\male-s^\female)>0$, see Fig \ref{fig:Combination_Centimorgans}B).
-%, which is 25\% of the parameter space.
-These special cases indicate that neo-W invasion occurs for a relatively large fraction of the parameter space, even if the neo-W uncouples the sex-determining locus from a locus under selection.
-
-\begin{table}[!ht]
-\centering
-\smallskip
-\caption{Invasion conditions for a neo-W allele at an unlinked locus ($R=1/2$) into an ancestral XY system with linkage ($r<1/2$) and one form of haploid selection}
-\begin{tabular}{l l c }
-\hline\hline
-Scenario &  Assumptions & neo-W spreads ($\lambda_{W'}^{(XY)}>1$) if \\ [0.5ex] \hline
-%  $r=1/2$, $R<1/2$ & Always \\ [0.5ex] \hline
-%  $r<1/2$, $R=1/2$ &  \\ [0.5ex] \hline
-\noalign{\vskip 1mm}
-  male drive only & $h^\male=h^\female$, $t^\female=t^\male=\alpha^\female_{\Delta}=0$ & $s^\female s^\male>0$ \\ [0.5ex]
- female drive only & $h^\male=h^\female$, $t^\female=t^\male=\alpha^\male_{\Delta}=0$ & $s^\female s^\male>0$ \\ [0.5ex]
- sperm competition only &  $h^\male=h^\female$, $t^\female=\alpha^\female_{\Delta}=\alpha^\male_{\Delta}=0$ & $s^\female(s^\male-s^\female)>0$ \\ [0.5ex]
-  egg competition only & $h^\male=h^\female$, $t^\male=\alpha^\female_{\Delta}=\alpha^\male_{\Delta}=0$ & $s^\male(s^\female-s^\male)>0$ \\ [0.5ex]
-  \hline \hline
-  \label{tab:specialcases}
- \end{tabular}
-\end{table}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Sex ratio selection is not a good predictor of neo-W invasion into an XY system
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-%\includegraphics[width=\linewidth]{Temporal_SR}
-\caption{
-{\bf Fisherian sex ratio selection alone is not a good predictor of turnover between sex-determining systems.}
-In this figure, selection is ploidally antagonistic with haploid selection favouring the $a$ allele during male meiosis.
-In panel A, male meiotic drive in an ancestral XY system causes a male bias (see Fig \ref{fig:model_outline}B), allowing a neo-W to invade and replace the ancestral sex-determining system (inset shows neo-W frequency among female gametes, reaching pseudo-fixation), which balances the zygotic sex ratio.
-In panel B, male drive in an ancestral ZW system has no effect on the zygotic sex ratio yet a neo-Y can invade and replace the ancestral sex-determining system (inset shows neo-Y frequency among male gametes, reaching pseudo-fixation).
-%When $R<1/2$, the neo-Y becomes associated with the allele favoured by drive, causing the zygotic sex ratio to become biased, hence the frequency of the neo-Y at pseudo-fixation can be higher than $0.5$ (inset).
-Parameters:  $s^\female =s^\male = 0.2$, $h^\female = h^\male = 0.7$, $t^\female = t^\male = \alpha^\female_\Delta = 0$, $\alpha^\male_\Delta = -0.1$, $r=0.02$.
-}
-\label{fig:SexRatioBad}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Previous research suggests that when the ancestral sex-determining locus is linked to a locus that experiences haploid selection (e.g., meiotic drive), alleles at a new, unlinked sex-determining locus invade to restore equal sex ratios~\cite{Kozielska:2010vm}.
-Consider, for example, the case where the $\mathbf{A}$ locus is linked to the ancestral sex-determining locus ($r<1/2$) and experiences meiotic drive in males only ($\alpha^\male_\Delta \neq 0$, $\alpha^\female_\Delta=0$), without gametic competition ($t^\female=t^\male=0$).
-In this case, the zygotic sex ratio can be initially biased only if the ancestral sex-determining system is XY (Fig \ref{fig:model_outline}A and Fig \ref{fig:SexRatioBad}B). 
-%If the ancxestral sex-determining system is ZW, the zygotic sex ratio will be 1:1 because diploid sex is determined by the proportion of Z-bearing versus W-bearing eggs and meiosis in females is fair (Fig \ref{fig:Combination_Turnover}D).
-If Fisherian sex ratio selection were dominant, we would thus expect a difference in the potential for XY to ZW and ZW to XY transitions. 
-%However, to leading order with selection weak relative to recombination, we find that sex ratio selection favours the spread of a neo-W by an amount equl to the spread of a neo-Y into a ZW system (relabeling XY as the heterogametic sex and reversing the labels of males and females in Table \ref{tab:specialcases})
-%However, to leading order with selection weak relative to recombination, we find that sex ratio selection favours the spread of a neo-W (through the first terms in table \ref{tab:haplotype_growth}) by an amount that is equal in magnitude to the fitness effects of alleles associated with new sex-determining alleles (second terms in table \ref{tab:haplotype_growth}).
-However, invasion by a neo-W allele into an XY system and invasion by a neo-Y allele into a ZW system occur under the same conditions ($\lambda_{Y'}^{(XY)} = \lambda_{W'}^{(ZW)}$ and $\lambda_{W'}^{(XY)}=\lambda_{Y'}^{(ZW)}$, at least to order $\epsilon^2$).
-For example, in Fig \ref{fig:SexRatioBad}A neo-W alleles invade an ancestral-XY system where females are initially rare, equalizing the sex ratio.
-However, Fig \ref{fig:SexRatioBad}B shows that a neo-Y can invade the resulting ZW system under the same conditions. 
-When $R<1/2$, the invading neo-Y becomes associated with the male meiotic drive allele and the zygotic sex ratio actually evolves to become male-biased.
-%
-%As selection becomes stronger (or linkage becomes tighter), this symmetry between sex ratio selection and haploid selection is lost, causing differences in the strength of selection favouring the two heterogametic transitions (compare red to black near -25cM and 25 cM in Fig \ref{fig:Combination_Centimorgans}).
-\textcolor{red}{normalise fitness in sexually antagonistic case}
-%
-%Why can new sex-determining regions invade when they are more loosely linked to selected loci ($R>r$)?  
-%Consider first the case where both sex-determining-loci are linked to the selected locus ($r<R<1/2$). 
-%In an ancestral-XY system, haploid selection in males can facilitate the spread of a neo-W because the zygotic sex ratio is ancestrally male biased and the W produces more of the rarer sex (Fig \ref{fig:SexRatioBad}A).
-%A new sex determining region can also, however, benefit from becoming more associated with drive. 
-%For example in an ancestral-ZW system with the same selection regime (haploid selection in males), a neo-Y can spread despite the fact that the zygotic sex is initially even; in this case, the neo-Y spreads because it is often found in males and can, if it carries the driven allele $a$, benefit from haploid selection in males (Fig \ref{fig:SexRatioBad}B).
-
-While equalizing the sex ratio and benefiting from drive are two primary reasons why haploid selection spurs sex chromosome transitions, even when the new sex-determining allele is less closely linked to the selected locus ($r<R$), more complex situations also arise.
-For example with $R=1/2$ in Fig \ref{fig:SexRatioBad}B (green curve), the neo-Y allele spreads despite the fact that it cannot benefit from drive because free recombination moves it randomly between driven and non-driven backgrounds.
-Nevertheless, the unlinked neo-Y can spread because diploids bearing it more often carry the non-driven allele $A$, which is found at high frequency on the W background and has higher average diploid fitness.% to balance the haploid advantage of the $a$ allele at equilibrium.
-
-\subsection*{Environmental sex determination}
-
-We next consider the case where the new sex-determining mutation, $m$, causes sex to be determined probabilistically or by heterogeneous environmental conditions (environmental sex determination, ESD), with individuals carrying allele $m$ developing as females with probability $k$.
-Here, we do not assume that the environmental conditions that determine sex also differentially affect the fitness of males versus females. 
-Such correlations can favour environmental sex-determining systems by allowing each sex to be produced in the environment in which it has highest fitness; in the absence of these correlations, previous theory would predict that ESD is favoured when it produces more equal sex ratios than the ancestral system (see reviews by~\cite{Charnov:1982wg,Bull:1983vi,West:2009we}).
-%(e.g., maternal condition, mate quality, age, or host size)
-
-The characteristic polynomial determining the leading eigenvalue (equations \ref{eq:recursions}) does not factor for ESD ($0<k<1$) as it does for a neo-Y ($k=0$) or neo-W ($k=1$) allele. 
-We therefore focus on weak selection here, where the leading eigenvalue is
-
-\begin{equation}
-\begin{split}
-\lambda_{ESD'}^{(XY)} =& 1 + \frac{{(1-2k)}^2}{4}V_{A}{S_{A}}^2\frac{r-R}{r R} \\
-&+\frac{k(\hat{p}^\male_Y-\hat{p}^\male_X)}{2}\left[ k \left(2\alpha_{\Delta}^\male-2\alpha_{\Delta}^\female+t^\male-t^\female \right) -2(1-k)S_{A}\right]+O\left(\epsilon^3\right).
-\end{split}
-\label{eq:lambda_ESD_k}
-\end{equation}
-
-\noindent
-This reduces to $\lambda_{Y'}^{(XY)}$ when $k=0$ and $\lambda_{W'}^{(XY)}$ when $k=1$.
-
-%Under Fisherian sex ratio selection, autosomal modifiers favour equal investment in male and female offspring, i.e., a 1:1 sex ratio~\cite{Fisher:1930wy,Charnov:1982wg,West:2009we}. 
-%A novel environmental sex-determiner that causes half of its carriers to become female and half to become male ($k=1/2$) will be in males half of the time and in females half of the time (like an autosome).
-%In addition, these novel sex-determination alleles equalize the sex ratio and therefore one might expect them to be favoured by Fisherian sex ratio selection when the resident sex ratio is biased.
-%However, assuming weak selection, we find that the growth rate of a rare, dominant offspring-controlled neo-ESD allele that produces males or females with equal probability ($k=1/2$) is
-Of particular interest are ESD mutations that cause half of their carriers to develop as females and half as males ($k=1/2$), creating equal sex ratios.
-The spread of such ESD is determined by
-\begin{equation}
-\lambda_{ESD'}^{(XY)} =1+ \frac{1}{2}\frac{(\lambda_{Y'\rvert R=1/2}^{(XY)}-1) + (\lambda_{W'\rvert R=1/2}^{(XY)}-1)}{2} + O\left(\epsilon^3\right),
-%V_A \frac{r}{1-2r}  \frac{s_{f} \left( s^\male - 3 s^\female\right) }{8 {\left( s_{f} + s_{m} \right)}^2} t_{m}^2.
-\label{eq:lambda_ESD}
-\end{equation}
-\noindent
-where $\lambda_{Y'\rvert R=1/2}^{(XY)}$ and $\lambda_{W'\rvert R=1/2}^{(XY)}$ represent $\lambda_{Y'}^{(XY)}$ and $\lambda_{W'}^{(XY)}$ when evaluated at $R=1/2$ (Equations \ref{eq:lambda_neoY} and \ref{eq:lambda_neoW}).
-That is, recombination between the selected locus and the novel sex-determining locus, $R$, does not enter into the $k=1/2$ results.
-This is because sex is essentially randomized each generation, %as if the novel sex-determiner were on an unlinked site that half the time acts as a neo-W and half the time as a neo-Y.
-preventing associations from building up between alleles at locus $\mathbf{A}$ and sex. 
-Eq \eqref{eq:lambda_ESD} shows that the ESD mutation gets half of the fitness of a feminizing mutation (neo-W) and half of the fitness of a masculinizing mutation (neo-Y), but only has an effect one half of the time (the other half of the time it produces the same sex as the ancestral system would have).
-As discussed above, $\lambda_{Y'\rvert R=1/2}^{(XY)}$ is necessarily less than one, but $\lambda_{W'\rvert R=1/2}^{(XY)}$ can be greater than one if there is haploid selection.
-That is, when there is haploid selection, ESD can invade an ancestrally-XY system because it generates females that are either rare or have high fitness, in the same manner as a neo-W.
-
-%An important result from Eq \eqref{eq:lambda_ESD} is that ESD can invade if there is haploid selection. 
-%When evaluated at $R=1/2$, $\Lambda_{Y',XY}$ is necessarily less than one, but $\Lambda_{W',XY}$ can be greater than one if there is haploid selection, as discussed above. 
-%Previous studies where ESD is favoured have typically assumed that environmental conditions (e.g., maternal condition, mate quality, age, or host size) can differentially affect the fitness of males versus females such that ESD invades because it allows sex determination to depend on the environment \citep[reviewed in][]{Charnov:1982wg,Bull:1983vi,West:2009we}.
-%Here, ESD mutations can spread because they generate females that are either rare or have high fitness, in the same manner as a neo-W.
-
-Significantly, Eq \eqref{eq:lambda_ESD} is the same whether ESD is invading an ancestrally XY or ZW system (because $\lambda_{Y'}^{(XY)} = \lambda_{W'}^{(ZW)}$ and $\lambda_{W'}^{(XY)} = \lambda_{Y'}^{(ZW)}$).
-Thus, Fisherian sex ratio selection alone does not easily explain GSD to ESD transitions.
-For example, when the ancestral sex-determining system is XY, but not ZW, the sex ratio is biased by male haploid selection.
-Nevertheless, ESD is equally likely to invade when it equalizes the zygotic sex ratio (through $\lambda_{W'}^{(XY)}$) as when it doesn't (through $\lambda_{Y'}^{(ZW)}$). 
-%This is again because haploid selection can facilitate the turnover of sex chromosomes either through sex ratio biases or through associations between the new sex determining region with selected alleles.
-%With weak selection, these two forces are nearly equal in strength. 
-In addition, we note that ESD may not invade, even if the sex ratio is initially biased (e.g., with drive in males only, $r<1/2$, $h^\female=h^\male$, and $s^\female s^\male<0$, then $\lambda_{W'}^{(XY)}<1$, see Table \ref{tab:specialcases}).
-We conclude that, as with neo-W and neo-Y loci, associations with selected loci mean that the evolution of ESD is not straightforwardly predicted by selection to balance the zygotic sex ratio when haploid selection is present.
-
-\section*{Discussion}
-
-%\textcolor{blue}{maybe re-order to put the results up front and focus on sex ratio less.
-Somewhere around these first two paragraphs we should include our tight linkage results.
-At the moment it doesn't make total sense because it assumes that tighter linkage is always favoured unless there is haploid selection.}
-
-%MAIN RESULT
-Two predominant theories explaining the remarkably high frequency of transitions between sex-determining systems are sexually-antagonistic selection and sex ratio selection (reviewed in~\cite{Blaser2012, vanDoorn2014re}).
-The former predicts that new sex-determining alleles can invade when they arise in closer linkage with a sexually-antagonistic locus ($r<R$,~\cite{vanDoorn:2007eu,vanDoorn:2010hu, Muralidhar2018}).
-The latter predicts that new sex-determining systems are generally favoured if they result in more equal sex ratios than the ancestral system. 
-%The latter predicts that neo-W alleles will invade an XY system when there is a male bias caused by haploid selection in males, and vice-versa, a neo-Y will invade a ZW system when there is a female bias caused by haploid selection in females~\cite{Kozielska:2010vm,Ubeda:2015fx}.
-In contrast to these prevailing views, we show that selection (including sexually-antagonistic selection, overdominance, and/or ploidally-antagonistic selection) on loci tightly linked to the ancestral sex-determining locus can favour trans-GSD transitions (XY$\leftrightarrow$ ZW) to new sex-determining systems that are less closely linked to the selected loci (e.g., see Fig \ref{fig:SexAntagTighter}).
-Similarly, even when linkage is weak relative to selection, we show that %new sex-determining alleles are typically favoured if they are more closely linked to a locus under haploid selection (even in the absence of diploid sex differences), which is the only condition favouring cis-GSD transitions (XY to XY or ZW to ZW).
-%In addition, with haploid selection and weak selection, 
-trans-GSD transitions can occur where the new sex-determining locus is less closely linked to the locus under selection if there is haploid selection (e.g., Figs \ref{fig:Combination_Centimorgans} and \ref{fig:SexRatioBad}).
-
-We find that the spread of new sex-determining systems cannot be simply predicted from their effect on the sex ratio. 
-On one hand, sex ratio biases caused by haploid selection can facilitate trans-GSD transitions or transitions from genetic to environmental sex determination. 
-For instance, alleles favoured by haploid selection in males often become associated with the Y allele, which leads to a male-biased zygotic sex ratio.
-This male bias increases the potential for a neo-W allele to invade (Table \ref{tab:haplotype_growth}), which can equalize the sex ratio (e.g., see Fig \ref{fig:SexRatioBad}B, for related examples see~\cite{Kozielska:2010vm}).
-%We find that sex ratio biases caused by haploid selection can also affect transitions between sex-determining systems (e.g., see $\zeta$ terms in Table \ref{tab:haplotype_growth}). 
-%However, the neo-W may not equalize the sex ratio (e.g., if the driving allele also drives in females or affects competition among eggs)
-On the other hand, sex ratio selection can be overwhelmed by additional selective effects, preventing a neo-W or ESD allele from invading, even if it would balance the sex ratio (e.g., when selection acts in opposite directions in male and female diploids, Table \ref{tab:specialcases}).
-%and equalizing the sex ratio.
-Indeed, transitions between sex-determining systems can generate stronger sex ratio biases (e.g., Fig \ref{fig:SexRatioBad}A and step 1 in~\cite{Ubeda:2015fx}).
-%For example, where a neo-Y invades and is linked with a locus that experiences haploid selection in male gametes, the sex ratio evolves to become biased \citep[e.g., see Fig \ref{fig:SexRatioBad}A and step 1 in][]{Ubeda:2015fx}.
-%For example, in an ancestral ZW system, haploid selection in males can allow a linked neo-Y to invade, despite the fact that it creates a male-biased sex ratio because the neo-Y becomes associated with the driven allele (Fig \ref{fig:SexRatioBad}A).
-%\textcolor{blue}{and figure 1, where the end of one panel is the same as the beginning of another, however, this figure may change).}
-%What we would like to stress is that sex ratio selection alone cannot predict when new sex-determining systems can evolve.
-Significantly, with weak selection, we find that there is no difference in conditions allowing XY to ZW and ZW to XY transitions, indicating that sex chromosome transitions are not predominantly predicted by their effect on the sex ratio (i.e., the sex ratio bias created by male haploid selection facilitates the spread of a neo-W allele into an XY system to the same degree that male haploid selection drives the spread of a neo-Y into a ZW system with a 1:1 sex ratio).
-%An asymmetry can develop when sex-linkage is tight (e.g., Fig \ref{fig:Combination_Centimorgans} near -25cM and 25cM) but under most circumstances we do not predict asymmetry between XY to ZW and ZW to XY transitions despite the presence/absence of sex ratio selection.
-Thus, haploid selection can favour trans-GSD transitions both via sex ratio selection and via selection on alleles associated with the new sex-determining allele, and these selective pressures are often predicted to be of equal magnitude.
-
-%HAPLOID SELECTION (genomic location of haploid selected loci and comparative patterns) 
-We have shown that the spread of new sex-determining systems can be driven by loci experiencing haploid selection. 
-%Our results suggest that haploid selected loci that have been involved in driving turnovers between sex-determining systems could occur around the ancestral- or novel-sex-determining regions. 
-%Our results suggest that polymorphic loci that are ancestrally sex-linked and under sex-specific selection could also drive heterogametic transitions between sex-determining systems. 
-%As with sexually-antagonistic selection, the presence of haploid selected loci around ancestral- or novel-sex-determining regions could support their role in sex chromosome turnover.
-In agreement with this hypothesis, a recent transcriptome analysis in Rumex shows that pollen-biased expression (relative to expression in flower buds or leaves) is enhanced among XY-linked genes compared to autosomal genes or compared to hemizygous genes that are only linked to the X (Sandler et al., 2018, personal communication).
-In addition, Y-linked genes are over-expressed relative to X-linked genes in pollen (but not in flower buds or leaves). 
-This suggests that the spread of neo-Y chromosomes in this clade could have been favoured through linkage with haploid selected genes. 
-%maybe add a flag here for switching to clade-level expectations:
-In general, we predict that haploid selection increases lability of sex-determining systems, particularly because haploid selection can cause transitions that increase or decrease sex-linkage (e.g., the final state of the red line in Fig \ref{fig:SexRatioBad}B is the starting state in Fig \ref{fig:SexRatioBad}A).
-Frequent turnovers driven by haploid selection may help to explain the relative rarity of heteromorphic sex chromosomes in plants, which are thought to experience more selection during their multicellular haploid stage.
-
-If haploid selection is strong but selective differences between male and female diploids are weak, we find that trans-GSD transitions are favoured more strongly than cis-GSD transitions, with transitions to ESD intermediate (e.g., with $|D^\male - D^\female| << |\alpha_\Delta^\male - \alpha_\Delta^\female + t^\male - t^\female|$ we have $\lambda_{W'}^{(XY)} > \lambda_{Y'}^{(XY)}$; Equations \ref{eq:lambda_neoW} and \ref{eq:freq_diffs}).
-Among the relatively few dioecious clades in which multiple species have well characterized sex chromosomes~\cite{Ming:2011iy}, trans-GSD transitions have been inferred in \textit{Silene} subsection \textit{Otites}~\cite{Slancarova:2013dq} and in \textit{Salicaceae}~\cite{Pucholt2015,Pucholt2017}.
-%Potentially, successive heterogametic transitions between master regulators of sex-determination could be inferred from careful examination of the molecular pathways by which sex is determined. 
-%Our predictions could also be examined using a suitable proxy for haploid selection, for example, \cite{Lenormand:2005vb} use the outcrossing rate in plants as a proxy for the strength of pollen competition.
-Assuming that transitions from dioecy to hermaphroditism (equal parental investment in male and female gametes) are favoured in a similar manner to the ESD examined here (equal probability of zygotes developing as males or females), our results suggest that competition during the haploid stage could also drive transitions between dioecy and hermaphroditism, which are frequent in plants~\cite{Kafer2017, Goldberg2017}.
-
-In support of their role in sex chromosome turnover, genes expected to be under sexually-antagonistic selection (e.g., those causing bright male colouration) have been found on recently derived sex chromosomes~\cite{Lindholm:2002dw,Tripathi:2009cw,Ser:2010iq}.
-Our results show, however, that tight ancestral-linkage of polymorphic loci, maintained by sexually-antagonistic selection or otherwise, can also drive trans-GSD transitions. 
-In addition, we find that polymorphic sex determining systems (X, Y, W, and Z alleles all present) can be maintained when a selected locus is tightly linked to the ancestral sex-determining system (e.g., \nameref{fig:freqAll}B and \nameref{fig:freqAll}C), which is not possible with loose linkage~\cite{vanDoorn:2010hu}.
-%As noted by \citet{vanDoorn:2010hu}, it would be prudent to compare closely related clades in order to determine whether observed polymorphisms predate a transition in sex-determination or arose afterwards.
-%, particularly because sex-linkage allows sexually-antagonistic selection to maintain polymorphisms under a different and larger parameter space~\cite{Rice:1987hs,Jordan:2011fj}.
-For example, our results suggest a potential mechanism maintaining multiple sex determining alleles in the platyfish (\textit{Xiphophorus maculatus}), in which X,Y, and W alleles segregate at one locus (or two closely-linked loci) near to potentially sexually-antagonistic genes for pigmentation and sexual maturity~\cite{Kallman1965,Kallman1968, Volff2001, Schultheis2006}.
-Several rodent species also maintain feminizing alleles along with the ancestral X and Y sex-determination alleles (reviewed in~\cite{Fredga1994}). 
-For example, in nine \textit{Akadon} species, it appears that male-determining-\textit{sry} expression is suppressed by an autosomal feminizing allele, creating XY females~\cite{Bianchi2002,Sanchez2010}, which have increased fitness relative to XX females~\cite{Hoekstra2001}.
-In \textit{Mus microtoides}, females can have XX, XX$^\ast$ or X$^\ast$Y genotypes~\cite{Veyrunes2010}. 
-Previous theory would predict that the X$^\ast$ chromosome (or the autosome it is fused to) harbours female beneficial alleles, driving its spread. 
-However, XX and XX$^\ast$ females have similar fitness, whereas X$^\ast$Y female fitness is enhanced~\cite{Saunders2014,Saunders2016, Veyrunes2017}.
-Although Y-linkage of female-beneficial alleles is counterintuitive, our model suggests that it can be stably maintained and then favour new feminizing mutations, which is a parsimonious explanation for the spread of feminizing alleles in these rodent species.
-
-%Limitation 1: DEGENERATE Y
-We note that we assume that sex-determining alleles do not experience direct selection except via their associations with sex and selected alleles.
-However, in some cases, there may be significant degeneration around the sex-limited allele (Y or W) in the ancestral sex-determining region because recessive deleterious mutations and/or deletions accumulate in this non-recombining regions~\cite{Rice:1996ke,Charlesworth:2000cc,Bachtrog:2006ed,Marais:2008hm}.
-During trans-GSD transitions, but not cis-GSD transitions, any recessive deleterious alleles linked to the Y or W are revealed to selection in YY or WW individuals~\cite{Bachtrog:2014bx}. 
-This phenomenon was studied by van Doorn and Kirkpatrick (2010)~\cite{vanDoorn:2010hu}, who found that degeneration can prevent fixation of a neo-W or a neo-Y allele, leading to a mixed sex-determining system where the ancestral and new sex-determining loci are both segregating.
-However, they noted that very rare recombination events around the ancestral sex-determining locus can allow these trans-GSD transitions to complete.  
-%While not explicitly studied, we also predict that Y or W degeneration would prevent fixation of the new sex-determining genes considered here.
-Degeneration around the Y or W could explain why trans-GSD transitions are not observed to be much more common than cis-GSD transitions despite the fact that our models demonstrate that they are favoured under a wider range of conditions, especially with haploid selection.
-For example, there are a dozen sex chromosome configurations among Dipteran species but only one transition between male and female heterogamety~\cite{Vicoso:2015hf}.
-
-%Limitation 3: don't consider m alleles with similar k to ancester, no ancestral ESD considered
-In this study, we have only considered new sex-determining alleles of large effect. 
-However, we expect similar selective forces to act on masculinizing/feminizing alleles of weaker effect. 
-For example, small effect masculinizing/feminizing alleles within a threshold model of sex determination can be favoured when linked to loci that experience sexually-antagonistic selection~\cite{Muralidhar2018}.
-These results echo those for large-effect neo-Y/neo-W alleles~\cite{vanDoorn:2007eu,vanDoorn:2010hu}.
-Finally, while we have considered cis-GSD, trans-GSD, and GSD to ESD transitions, we have not explicitly considered ESD to GSD transitions. 
-Recent models of ESD to GSD transitions~\cite{Ubeda:2015fx,Muralidhar2018} show that that neo-Y/neo-W alleles can be favoured when they arise near to haploid and/or diploid selected loci, which also occurs in our model.
-
-%Limitation 2: TWO ALLELE DRIVE
-%Another simplification that we made is that meiotic drive involves only a single locus with two alleles. 
-%However, many meiotic drive systems involve an interaction with another locus at which alleles may `suppress' the action of meiotic drive \citep[][]{Burt:2006,Lindholm:2016cw}.
-%Thus, the dynamics of meiotic drive alleles can be heavily dependent on the interaction between two loci and the recombination rate between them, which in turn can be affected by sex-linkage if there is reduced recombination between sex chromosomes~\cite{Hurst:1991uh}.
-%Furthermore, in some cases, a driving allele may act by killing any gametes that carry a `target' allele at another locus, in which case there can be fertility effects that alter the equilibrium frequency of a meiotic drive allele~\cite{Holman:2015en}.
-%In polygamous mating systems, the intensity of pollen/sperm competition can depend on the density of males available to donate pollen/sperm, which can itself depend on the sex ratio~\cite{Taylor:2002wu}.
-%In terms of our model, this implies that the strength of gametic competition ($t^\male$) may both determine and be determined by the sex ratio. 
-%How the evolution of new sex-determining mechanisms could be influenced by two-locus meiotic drive and/or by ecological feedbacks under different mating systems remains to be studied.
-
-\section*{Conclusion}
-
-We have shown that tight sex-linkage and haploid selection can drive previously unexpected transitions between sex-determining systems.
-In particular, both can select for new sex-determining loci that are more loosely linked to loci under selection. 
-In addition, haploid selection can cause transitions analogous to those caused by purely sexually-antagonistic selection, eliminating the need for differences in selection between male and female diploids.
-We conclude that haploid selection should be considered as a pivotal factor driving transitions between sex-determining systems. 
-Perhaps counterintuitively, transitions involving haploid selection can be driven by sex ratio selection or cause sex ratio biases to evolve; we do not find Fisherian sex ratio selection to be an overwhelming force.
-Overall, our results suggest several new scenarios under which new sex-determining systems are favoured, which could help to explain why the evolution of sex-determining systems is so dynamic.
-
-% For figure citations, please use "Fig" instead of "Figure".
-
-% Place figure captions after the first paragraph in which they are cited.
-
-% Results and Discussion can be combined.
-
-% Place tables after the first paragraph in which they are cited.
-
-%PLOS does not support heading levels beyond the 3rd (no 4th level headings).
-
-\section*{Supporting information}
-
-\paragraph*{S1 File.}
-\label{file:Mathematica}
-{\bf Supplementary \textit{Mathematica} file.}  This file can be used to re-derive our results and generate figures.
-
-\paragraph*{S1 Table}
-\label{tab:chisubstitutions}
-{\bf Substitutions for different loci orders assuming no interference.}
-
-\paragraph*{S2 Table}
-\label{tab:meanfitnesses}
-{\bf Mean fitnesses and zygotic sex ratio in the resident population ($M$ fixed, XY sex determination). }
-
-\paragraph*{S1 Appendix.}
-\label{app:recurs}
-{\bf Recursion equations and complete model description.}
-
-\paragraph*{S2 Appendix.}
-\label{app:eq_stab}
-{\bf Equilibria and stability conditions when $M$ allele is fixed. }
-
-\paragraph*{S3 Appendix.}
-\label{app:inv_cond}
-{\bf Invasion conditions for the $m$ allele.}
-
-% Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
-\paragraph*{S1 Fig.}
-\label{fig:positionOverdominance}
-{\bf With overdominance, loci near to the ancestral sex-determining locus ($r\approx0$) can favour neo-W alleles that are less tightly linked ($R>r$).} 
-In panels A and B, the $a$ allele is favoured in females ($w_{aa}^\female=1.05$, $w_{Aa}^\Hermaphrodite=1$, $w_{AA}^\female=0.85$) and selection in males is overdominant ($w_{aa}^\male=w_{AA}^\male=0.75$).
-In panels C and D, selection in males and females is overdominant ($w_{aa}^\female=w_{AA}^\female=0.6$, $w_{aa}^\male=0.5$, $w_{AA}^\male=0.7$, $w_{Aa}^\Hermaphrodite=1$).
-There is no haploid selection $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
-These parameters are marked by daggers in Fig \ref{fig:regionplots}B and C, which show that neo-W invasion is expected for any $R$ ($\Lambda_{W'A}^{(XY)},\Lambda_{W'a}^{(XY)}>1$) if the $a$ allele is nearly fixed on the Y (black lines in this figure; not stable for $r>>0$).
-Equilibria where the $A$ allele is more common among Y-bearing male gametes can also be stable and allow neo-W invasion for these parameters (blue lines). 
-%The weak selection approximation holds when all recombination rates are large relative to selection (around 0 in panels A and C), in which case, in the absence of haploid selection, neo-W alleles should spread if and only if they are more tightly linked to the selected locus (positive invasion fitness if and only if the selected locus is in the grey region).
-%However, when recombination rates are small (panels B and D and when the selected locus is near the SDRs in all panels), this weak selection prediction can break down.
-
-\paragraph*{S2 Fig.}
-\label{fig:temporalOverdominance}
-{\bf Following invasion by a neo-W allele, there can be a complete transition to a new sex-determining system, maintenance of both ancestral-XY and neo-ZW sex determining systems, or loss of the new sex-determining allele.}
-Here, we plot the frequency of the neo-W allele among female gametes.
-%; as the neo-W reaches frequency $0.5$, polymorphism at the ancestral XY locus is lost with Y becoming fixed such that sex is determined only be the ZW allele carried by a female gamete. 
-Panels A, C and D show cases where a steady state is reached with the neo-W at a frequency below $0.5$, in which case ancestral-X and Y alleles also both segregate. 
-In all cases, we assume that the $a$ allele is initially more common than the $A$ allele on the Y background (Y-$a$ is fixed when $r=0$). 
-When $r>0$ (panels B and D), Y-$A$ haplotypes created by recombination can become more common than Y-$a$ haplotypes as the neo-W spreads.
-In B, this leads to loss of the neo-W and the system goes to an equilibrium with X-$a$ and Y-$A$ haplotypes fixed (equilibrium $A'$), such that all females have the high fitness genotype $aa$ and all males are $Aa$.
-For the parameters in B, neo-W alleles have negative invasion fitness when the Y-$A$ haplotype is ancestrally more common than Y-$a$ (compare blue to black curves in \nameref{fig:positionOverdominance}A and  \nameref{fig:positionOverdominance}B near the ancestral sex-determining locus).
-In contrast, the neo-W is not lost in panel D as it is favoured regardless of whether Y-$A$ or Y-$a$ haplotypes predominate (again, compare blue to black curves in \nameref{fig:positionOverdominance}C and  \nameref{fig:positionOverdominance}D).
-%Fitness parameters are the same as in \nameref{fig:positionOverdominance}; in panels A and B the $a$ allele is favoured in females ($w_{aa}^\female=1.05$, $w_{Aa}^\Hermaphrodite=1$, $w_{AA}^\female=0.85$) while there is overdominance in males ($w_{aa}^\male=w_{AA}^\male=0.75$) and in panels C and D, there is overdominance in both sexes ($w_{aa}^\female=w_{AA}^\female=0.6$, $w_{aa}^\male=0.5$, $w_{AA}^\male=0.7$, $w_{Aa}^\Hermaphrodite=1$).
-%These parameters are marked by a dagger in Fig \ref{fig:regionplots}. 
-%Here, there is no haploid selection $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
-
-\paragraph*{S3 Fig.}
-\label{fig:SexAntagTighterMaleDrive}
-{\bf  When there is sexually-antagonistic selection and haploid selection, a neo-W allele may invade for any $R$.}
-Panel A shows that the invasion fitness of a neo-W is positive, even when $r<R$ (unshaded region).
-In panel B, we vary the recombination rate between the neo-W and the selected locus ($R$) for a fixed recombination rate between the ancestral sex-determining locus and the selected locus ($r=0.005$).
-Coloured markers show recombination rates for which the temporal dynamics of neo-W invasion are plotted in panel C (black $R=0.001$, red $R=0.02$, blue $R=0.1$, green $R=0.5$). 
-The diploid selection parameters used in this plot are the same as in Fig \ref{fig:SexAntagTighter}. 
-There is also meiotic drive in males favouring $a$ ($\alpha_{\Delta}^\male=-0.08$), this full set of parameters is marked by an asterisk in \nameref{fig:regionMaleDrive}A.
-When $R=0.5$ (green curve), the neo-W does not reach fixation and X, Y, Z, and W alleles are all maintained in the population, see \nameref{fig:freqAll}C.
-
-\paragraph*{S4 Fig.}
-\label{fig:regionMaleDrive}
-{\bf Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is male meiotic drive at a locus that is tightly linked to the ancestral XY locus ($r=0$).}
-This figure is equivalent to Fig \ref{fig:regionplots} but with meiotic drive in males.
-%We vary the fitness of male homozygotes relative to heterozygotes ($w_{Aa}^\Hermaphrodite=1$) and only consider stable equilibria at which both $\mathbf{A}$ locus allele are maintained and the $a$ allele is initially fixed on the Y, region outlined.
-In panels A-C, meiotic drive in males favours the $a$ allele ($\alpha_{\Delta}^\male=-0.16$), creating male-biased sex ratios and generally increasing $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$.
-By contrast, $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$ tend to be reduced when meiotic drive in males favours the $A$ allele ($\alpha_{\Delta}^\male=0.16$), panels D-F. 
-%We consider three forms of selection in females: directional selection in favour of the $A$ allele (panels A and D, $w_{aa}^\female=0.85$, $w_{AA}^\female=1.05$), direction selection in favour of the $a$ allele (panels B and E, $w_{aa}^\female=1.05$, $w_{AA}^\female=0.85$), and overdominance (panels C and F, $w_{aa}^\female=w_{AA}^\female=0.6$).
-
-\paragraph*{S5 Fig.}
-\label{fig:regionMaleGS}
-{\bf Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is male gametic competition at a locus that is tightly linked to the ancestral XY locus ($r=0$).}
-This figure is equivalent to Fig \ref{fig:regionplots} but with gametic competition in males.
-%Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in \nameref{fig:regionMaleDrive}. 
-The $a$ allele is favoured during male gametic competition in Panels A-C ($w_{a}^\male=1.16$, $w_{A}^\male=1$), which creates male biased sex ratios and increases $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$.
-By contrast, $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$ tend to be reduced when the $A$ allele is favoured during male gametic competition, panels D-F.
-Compared to the meiotic drive parameters in \nameref{fig:regionMaleDrive}, the effect of these male gametic competition parameters on the sex ratio is smaller. 
-For example, in \nameref{fig:regionMaleDrive}A-C, the ancestral sex ratio is $\alpha^\male=0.58$ at equilibrium (B) and in panels A-C of this plot, the ancestral sex ratio is $w_{a}^\male/(w_{A}^\male+w_{a}^\male)=0.537$ at equilibrium (B).
-
-\paragraph*{S6 Fig.}
-\label{fig:regionFemaleDrive}
-{\bf Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is female meiotic drive at a locus that is tightly linked to the ancestral XY locus ($r=0$).}
-This figure is equivalent to Fig \ref{fig:regionplots} but with meiotic drive in females.
-%Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in \nameref{fig:regionMaleDrive} and \nameref{fig:regionMaleGS}. 
-The $a$ allele is favoured by meiotic drive in females in Panels A-C ($\alpha_{\Delta}^\female=-0.16$), which increases $\Lambda_{W'a}^{(XY)}$ and decreases $\Lambda_{W'A}^{(XY)}$. 
-Female meiotic drive in favour of the $A$ allele (panels D-F, $\alpha_{\Delta}^\female=-0.16$) has the opposite effect.
-
-\paragraph*{S7 Fig.}
-\label{fig:regionFemaleGS}
-{\bf Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is female gametic competition at a locus that is tightly linked to the ancestral XY locus ($r=0$).}
-This figure is equivalent to Fig \ref{fig:regionplots} but with gametic competition in females.
-%Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in \nameref{fig:regionMaleDrive}, \nameref{fig:regionMaleGS}, and \nameref{fig:regionFemaleDrive}. 
-The $a$ allele is favoured during female gametic competition in females in Panels A-C ($w_{a}^\female=1.16$, $w_{A}^\female=1$), which increases $\Lambda_{W'a}^{(XY)}$ and decreases $\Lambda_{W'A}^{(XY)}$.
-The $A$ allele is favoured during gametic competition in panels D-F ($w_{a}^\female=1$, $w_{A}^\female=1.16$), giving the opposite effect on $\Lambda_{W'a}^{(XY)}$ and $\Lambda_{W'A}^{(XY)}$.
-
-\paragraph*{S8 Fig.}
-\label{fig:regionPloidAntag}
-{\bf Ploidally-antagonistic selection can drive the spread of neo-W alleles. }
-A-D show when each of the neo-W haplotypes invades an internally stable equilibrium with $a$ fixed on the Y (found by setting $r=0$).
-The y-axis shows directional selection in diploids of both sexes, $s^\female=s^\male$, and the x-axes show sex-specific drive, $\alpha_\Delta^\Hermaphrodite$, or haploid competition, $t^\Hermaphrodite$.
-The top left and bottom right quadrants therefore imply ploidally-antagonistic selection (and these are the only places where neo-W haplotypes can invade).
-Dominance is equal in both sexes, $h^\female=h^\male=3/4$. 
-E-F show the temporal dynamics of neo-W frequency in females with parameters given by the asterisks in the corresponding A-D plot, with $r=1/200$, for four different $R$.
-Black $R=1/1000$, Red $R=2/100$, Blue $R=1/10$, Green $R=1/2$.
-
-\paragraph*{S9 Fig.}
-\label{fig:freqAll}
-{\bf Pseudo-fixation of neo-W or maintenance of multiple sex-determining alleles. }
-The curves show the frequencies of the neo-W (red), ancestral Y (blue), and $A$ allele (black) among female gametes (solid curves) and among male gametes (dashed curves). 
-In panel A, there is a complete transition from XY sex determination (XX-ZZ females and XY-ZZ males) to ZW sex determination (YY-ZW females and YY-ZZ males).  
-In panels B and C a polymorphism is maintained at both the ancestral XY locus and the new ZW locus, such that there are males with genotypes XY-ZZ and YY-ZZ and females with genotypes XX-ZZ, XX-ZW, XY-ZW, and YY-ZW.
-In panel A, selection is ploidally-antagonistic with drive in males (parameters as in the green curve in Fig \ref{fig:SexRatioBad}B).
-In panel B, there is overdominance in both sexes and no haploid selection (parameters as in the green curve in \nameref{fig:temporalOverdominance}C).
-In panel C, there is sexually-antagonistic selection in diploids with drive in males (parameters as in the green curve in \nameref{fig:regionMaleDrive}C).
-In all cases, the initial equilibrium frequency has $a$ near fixation on the Y.
-
-%\section*{Acknowledgments}
-%This project was supported by the Natural Sciences and Engineering Research Council of Canada (CGS-D 6564 to MMO; RGPIN-2016-03711 to SPO).
-
-\nolinenumbers
-
-% Either type in your references using
-% \begin{thebibliography}{}
-% \bibitem{}
-% Text
-% \end{thebibliography}
-%
-% or
-%
-% Compile your BiBTeX database using our plos2015.bst
-% style file and paste the contents of your .bbl file
-% here. See http://journals.plos.org/plosone/s/latex for 
-% step-by-step instructions.
-% 
-\bibliography{sex_chromosomes.bib}
-
-\newpage
-
-\setcounter{equation}{0}
-\renewcommand{\theequation}{S1.\arabic{equation}}
-
-\section*{S1 Appendix}
-
-\subsection*{Recursion equations}
-
-In each generation we census the genotype frequencies in male and female gametes/gametophytes (hereafter, gametes) between meiosis (and any meiotic drive) and gametic competition. 
-At this stage we denote the frequencies of X- and Y-bearing gametes from males and females $x_{i}^{\Hermaphrodite}$ and $y_{i}^{\Hermaphrodite}$.
-The superscript $\Hermaphrodite \in \{\male,\female\}$ specifies the sex of the diploid that the gamete came from. 
-The subscript $i\in\{1,2,3,4\}$ specifies the genotype at the selected locus $\mathbf{A}$ and at the novel sex-determining locus $\mathbf{M}$, where $1=AM$, $2=aM$, $3=Am$, and $4=am$. 
-The gamete frequencies from each sex sum to one, $\sum_{i}x_{i}^{\Hermaphrodite}+y_{i}^{\Hermaphrodite}=1$.
-
-Competition then occurs among gametes of the same sex (e.g., among eggs and among sperm separately) according to the genotype at the $\mathbf{A}$ locus ($w_{1}^\Hermaphrodite=w_{3}^\Hermaphrodite=w_{A}^\Hermaphrodite$, $w_{2}^\Hermaphrodite=w_{4}^\Hermaphrodite=w_{a}^\Hermaphrodite$, see Table \ref{tab:fitnesstable}).
-The genotype frequencies after gametic competition are $x_{i}^{\Hermaphrodite,s}= w_{i}^{\Hermaphrodite}x_{i}^{\Hermaphrodite}/\bar{w}_{H}^{\Hermaphrodite}$ and $y_{i}^{\Hermaphrodite,s}= w_{i}^{\Hermaphrodite}y_{i}^{\Hermaphrodite}/\bar{w}_{H}^{\Hermaphrodite}$, where $\bar{w}_{H}^{\Hermaphrodite}=\sum_{i} w_{i}^{\Hermaphrodite}x_{i}^{\Hermaphrodite}+w_{i}^{\Hermaphrodite}y_{i}^{\Hermaphrodite}$ is the mean fitness of male ($\Hermaphrodite=\male$) or female ($\Hermaphrodite=\female$) gametes.
-
-Random mating then occurs between gametes to produce diploid zygotes.
-%To shorten notation we now use index $i$ (and $j$) to denote the alleles at both the $\mathbf{A}$ and $\mathbf{M}$ loci and label $MA=1$, $Ma=2$, $mA=3$, and $ma=4$, such that $i,j\in\{1,2,3,4\}$.
-The frequencies of XX zygotes are then denoted as $xx_{ij}$, XY zygotes as $xy_{ij}$, and YY zygotes as $yy_{ij}$, where $\mathbf{A}$ and $\mathbf{M}$ locus genotypes are given by $i,j\in\{1,2,3,4\}$, as above.
-In XY zygotes, the haplotype inherited from an X-bearing gamete is given by $i$ and the haplotype from a Y-bearing gamete is given by $j$. 
-In XX and YY zygotes, individuals with diploid genotype $ij$ are equivalent to those with diploid genotype $ji$; for simplicity, we use $xx_{ij}$ and $yy_{ij}$ with $i\neq j$ to denote the average of these frequencies, $xx_{ij}=(x_{i}^{\female,s}x_{j}^{\male,s}+x_{j}^{\female,s}x_{i}^{\male,s})/2$ and $yy_{ij}=(y_{i}^{\female,s}y_{j}^{\male,s}+y_{j}^{\female,s}y_{i}^{\male,s})/2$.
-
-Denoting the $\mathbf{M}$ locus genotype by $b \in \{MM, Mm, mm\}$ and the $\mathbf{X}$ locus genotype by $c \in \{XX, XY, YY\}$, zygotes develop as females with probability $k_{bc}$. 
-Therefore, the frequencies of XX females are given by $xx_{ij}^{\female}=k_{bc}xx_{ij}$, XY females are given by $xy_{ij}^{\female}=k_{bc}xy_{ij}$, and YY females are given by $yy_{ij}^{\female}=k_{bc}yy_{ij}$.
-Similarly, XX male frequencies are $xx_{ij}^{\male}=(1-k_{bc})xx_{ij}$, XY male frequencies are $xy_{ij}^{\male}=(1-k_{bc})xy_{ij}$, and YY males frequencies are $yy_{ij}^{\male}=(1-k_{bc})yy_{ij}$.
-This notation allows both the ancestral and novel sex-determining regions to determine zygotic sex according to an XY system, a ZW system, or an environmental sex-determining system. 
-In addition, we can consider any epistatic dominance relationship between the two sex-determining loci. 
-Here, we assume that the ancestral sex-determining system ($\mathbf{X}$ locus) is XY ($k_{MMXX}=1$ and $k_{MMXY}=k_{MMYY}=0$) or ZW ($k_{MMZZ}=0$ and $k_{MMZW}=k_{MMWW}=1$) and epistatically recessive to a dominant novel sex-determining locus, $\mathbf{M}$ ($k_{Mmc}=k_{mmc}=k$).
-
-Selection among diploids then occurs according to the diploid genotype at the $\mathbf{A}$ locus, $l \in \{AA, Aa, aa\}$, for an individual of type $ij$ (see Table \ref{tab:fitnesstable}). 
-The diploid frequencies after selection in sex $\Hermaphrodite$ are given by $xx_{ij}^{\Hermaphrodite,s}=w_{l}^{\Hermaphrodite} xx_{ij}/\bar{w}^{\Hermaphrodite}_{D}$, $xy_{ij}^{\Hermaphrodite,s}=w_{l}^{\Hermaphrodite} xy_{ij}/\bar{w}^{\Hermaphrodite}_{D}$, and $yy_{ij}^{\Hermaphrodite,s}=w_{l}^{\Hermaphrodite} yy_{ij}/\bar{w}^{\Hermaphrodite}_{D}$, where $\bar{w}^{\Hermaphrodite}_{D}= \sum_{i=1}^{4}\sum_{j=1}^{4}w_{l}^{\Hermaphrodite}xx_{ij}+w_{l}^{\Hermaphrodite}xy_{ij}+w_{l}^{\Hermaphrodite}yy_{ij}$ is the mean fitness of diploids of sex $\Hermaphrodite$.
-
-Finally, these diploids undergo meiosis to produce the next generation of gametes. 
-Recombination and sex-specific meiotic drive occur during meiosis.
-%We can also assume that recombination is sex specific and/or affected by the M locus - but generally we don't so I just describe $R=R_{f}=R, r_{MM,d}=r_{Mm,d}=r_{mm,d}=r, \chi_{m}=\chi_{f}=\chi$.
-Here, we allow any relative locations for the $\mathbf{X}$, $\mathbf{A}$, and $\mathbf{M}$ loci by using three parameters to describe the recombination rates between them. 
-$R$ is the recombination rate between the $\mathbf{A}$ and $\mathbf{M}$ loci, $\rho$ is the recombination rate between the $\mathbf{M}$ and $\mathbf{X}$ loci, and $r$ is the recombination rate between the $\mathbf{A}$ and $\mathbf{X}$ loci (Fig \ref{fig:model_outline}).
-\nameref{tab:chisubstitutions} shows replacements that can be made for each possible ordering of the loci assuming that there is no cross-over interference.
-During meiosis in sex $\Hermaphrodite$, meiotic drive occurs such that, in $Aa$ heterozygotes, a fraction $\alpha^{\Hermaphrodite}$ of gametes produced carry the $A$ allele and $(1-\alpha^\Hermaphrodite)$ carry the $a$ allele.
-
-Among gametes from sex $\Hermaphrodite$, the frequencies of haplotypes (before gametic competition) in the next generation are given by
-
-\begingroup
-\allowdisplaybreaks
-\begin{subequations}
-\begin{align}
-%
-\begin{split}
-x_{1}^{{\Hermaphrodite}'}=&xx_{11}^{\Hermaphrodite,s}+xx_{13}^{\Hermaphrodite,s}/2+(xx_{12}^{\Hermaphrodite,s}+xx_{14}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(xx_{14}^{\Hermaphrodite,s}-xx_{23}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&+(xy_{11}^{\Hermaphrodite,s}+xy_{13}^{\Hermaphrodite,s})/2+(xy_{12}^{\Hermaphrodite,s}+xy_{14}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&- r(xy_{12}^{\Hermaphrodite,s}-xy_{21}^{\Hermaphrodite,s})\alpha^\Hermaphrodite - \rho(xy_{13}^{\Hermaphrodite,s}-xy_{31}^{\Hermaphrodite,s})/2\\
-&+\big{[}-(R+r+\rho)xy_{14}^{\Hermaphrodite,s} +(R+\rho-r)xy_{41}^{\Hermaphrodite,s}\\
-&+(R+r-\rho) xy_{23}^{\Hermaphrodite,s}+(R+\rho-r)xy_{32}^{\Hermaphrodite,s}\big{]}\alpha^\Hermaphrodite/2
-\end{split}
-\\
-%
-\begin{split}
-x_{2}^{{\Hermaphrodite}'}=&xx_{22}^{\Hermaphrodite,s}+xx_{24}^{\Hermaphrodite,s}/2+(xx_{12}^{\Hermaphrodite,s}+xx_{23}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(xx_{23}^{\Hermaphrodite,s}-xx_{14}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&(xy_{22}^{\Hermaphrodite,s}+xy_{24}^{\Hermaphrodite,s})/2+(xy_{21}^{\Hermaphrodite,s}+xy_{23}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite)\\
-&- r(xy_{21}^{\Hermaphrodite,s}-xy_{12}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite) - \rho(xy_{24}^{\Hermaphrodite,s}-xy_{42}^{\Hermaphrodite,s})/2\\
-&+\big{[}-(R+r+\rho)xy_{23}^{\Hermaphrodite,s}+(R+\rho-r)xy_{32}^{\Hermaphrodite,s}\\
-&+(R+r-\rho) xy_{14}^{\Hermaphrodite,s}+(R+\rho-r)xy_{41}^{\Hermaphrodite,s}\big{]}(1-\alpha^\Hermaphrodite)/2
-\end{split}
-\\
-%
-\begin{split}
-x_{3}^{{\Hermaphrodite}'}=&xx_{33}^{\Hermaphrodite,s}+xx_{13}^{\Hermaphrodite,s}/2+(xx_{23}^{\Hermaphrodite,s}+xx_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(xx_{23}^{\Hermaphrodite,s}-xx_{14}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&(xy_{33}^{\Hermaphrodite,s}+xy_{31}^{\Hermaphrodite,s})/2+(xy_{32}^{\Hermaphrodite,s}+xy_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&- r(xy_{34}^{\Hermaphrodite,s}-xy_{43}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite - \rho(xy_{31}^{\Hermaphrodite,s}-xy_{13}^{\Hermaphrodite,s})/2\\
-&+\big{[}-(R+r+\rho)xy_{32}^{\Hermaphrodite,s} +(R+\rho-r)xy_{23}^{\Hermaphrodite,s}\\
-&+(R+r-\rho) xy_{41}^{\Hermaphrodite,s}+(R+\rho-r)xy_{14}^{\Hermaphrodite,s}\big{]} \alpha^\Hermaphrodite/2
-\end{split}
-\\
-%
-\begin{split}
-x_{4}^{{\Hermaphrodite}'}=&xx_{44}^{\Hermaphrodite,s}+xx_{34}^{\Hermaphrodite,s}/2+(xx_{14}^{\Hermaphrodite,s}+xx_{24}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(xx_{14}^{\Hermaphrodite,s}-xx_{23}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&(xy_{44}^{\Hermaphrodite,s}+xy_{42}^{\Hermaphrodite,s})/2+(xy_{41}^{\Hermaphrodite,s}+xy_{43}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite)\\
-&- r(xy_{43}^{\Hermaphrodite,s}-xy_{34}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite) - \rho(xy_{42}^{\Hermaphrodite,s}-xy_{24}^{\Hermaphrodite,s})/2\\
-&+\big{[}-(R+r+\rho)xy_{41}^{\Hermaphrodite,s}+(R+\rho-r)xy_{14}^{\Hermaphrodite,s}\\
-&+(R+r-\rho) xy_{32}^{\Hermaphrodite,s}+(R+\rho-r)xy_{23}^{\Hermaphrodite,s}\big{]}(1-\alpha^\Hermaphrodite)/2
-\end{split}
-\\
-\begin{split}
-y_{1}^{{\Hermaphrodite}'}=&yy_{11}^{\Hermaphrodite,s}+yy_{13}^{\Hermaphrodite,s}/2+(yy_{12}^{\Hermaphrodite,s}+yy_{14}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(yy_{14}^{\Hermaphrodite,s}-yy_{23}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&(xy_{11}^{\Hermaphrodite,s}+xy_{31}^{\Hermaphrodite,s})/2+(xy_{21}^{\Hermaphrodite,s}+xy_{41}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&- r(xy_{21}^{\Hermaphrodite,s}-xy_{12}^{\Hermaphrodite,s})\alpha^\Hermaphrodite - \rho(xy_{31}^{\Hermaphrodite,s}-xy_{13}^{\Hermaphrodite,s})/2\\
-&+\big{[} - (R+r+\rho)xy_{41}^{\Hermaphrodite,s} + (R+\rho-r)xy_{14}^{\Hermaphrodite,s}\\
-& + (R+r-\rho)xy_{32}^{\Hermaphrodite,s} + (R+\rho-r) xy_{23}^{\Hermaphrodite,s}\big{]}\alpha^\Hermaphrodite/2
-\end{split}
-\\
-%
-\begin{split}
-y_{2}^{{\Hermaphrodite}'}=&yy_{22}^{\Hermaphrodite,s}+yy_{24}^{\Hermaphrodite,s}/2+(yy_{12}^{\Hermaphrodite,s}+yy_{23}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(yy_{23}^{\Hermaphrodite,s}-yy_{14}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&(xy_{22}^{\Hermaphrodite,s}+xy_{42}^{\Hermaphrodite,s})/2+(xy_{12}^{\Hermaphrodite,s}+xy_{32}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite)\\
-&- r(xy_{12}^{\Hermaphrodite,s}-xy_{21}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite) - \rho(xy_{42}^{\Hermaphrodite,s}-xy_{24}^{\Hermaphrodite,s})/2\\
-&+\big{[}-(R+r+\rho)xy_{32}^{\Hermaphrodite,s} +(R+\rho-r) xy_{23}^{\Hermaphrodite,s}\\
-&+(R+r-\rho)xy_{41}^{\Hermaphrodite,s}+(R+\rho-r)xy_{14}^{\Hermaphrodite,s}\big{]}(1-\alpha^\Hermaphrodite)/2
-\end{split}
-\\
-%
-\begin{split}
-y_{3}^{{\Hermaphrodite}'}=&yy_{33}^{\Hermaphrodite,s}+yy_{13}^{\Hermaphrodite,s}/2+(yy_{23}^{\Hermaphrodite,s}+yy_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(yy_{23}^{\Hermaphrodite,s}-yy_{14}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&(xy_{33}^{\Hermaphrodite,s}+xy_{13}^{\Hermaphrodite,s})/2+(xy_{23}^{\Hermaphrodite,s}+xy_{43}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&- r(xy_{43}^{\Hermaphrodite,s}-xy_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite - \rho(xy_{13}^{\Hermaphrodite,s}-xy_{31}^{\Hermaphrodite,s})/2\\
-&+\big{[}-(R+r+\rho)xy_{23}^{\Hermaphrodite,s} +(R+\rho-r)xy_{32}^{\Hermaphrodite,s}\\
-&+(R+r-\rho) xy_{14}^{\Hermaphrodite,s} + (R+\rho-r) xy_{41}^{\Hermaphrodite,s}\big{]}\alpha^\Hermaphrodite/2
-\end{split}
-\\
-%
-\begin{split}
-y_{4}^{{\Hermaphrodite}'}=&yy_{44}^{\Hermaphrodite,s}+yy_{34}^{\Hermaphrodite,s}/2+(yy_{14}^{\Hermaphrodite,s}+yy_{24}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(yy_{14}^{\Hermaphrodite,s}-yy_{23}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&(xy_{44}^{\Hermaphrodite,s}+xy_{24}^{\Hermaphrodite,s})/2+(xy_{14}^{\Hermaphrodite,s}+xy_{34}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite)\\
-&- r(xy_{34}^{\Hermaphrodite,s}-xy_{43}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite) - \rho(xy_{24}^{\Hermaphrodite,s}-xy_{42}^{\Hermaphrodite,s})/2\\
-&+\big{[}-(R+r+\rho) xy_{14}^{\Hermaphrodite,s} + (R+\rho-r)xy_{41}^{\Hermaphrodite,s}\\
-&+(R+r-\rho) xy_{23}^{\Hermaphrodite,s} + (R+\rho-r) xy_{32}^{\Hermaphrodite,s}\big{]}(1-\alpha^\Hermaphrodite)/2.
-\end{split}
-\end{align}
-\label{eq:recursions}
-\end{subequations}
-
-\endgroup
-
-\noindent
-The full system is therefore described by 16 recurrence equations (three diallelic loci in two sexes, $2^3 \times 2 = 16$). 
-However, not all diploid types are produced under certain sex-determining systems. 
-For example, with the $M$ allele fixed and an ancestral XY sex-determining system, there are XX females and XY males ($x_{3}^\Hermaphrodite=x_{4}^\Hermaphrodite=y_{3}^\male=y_{4}^\male=y_{i}^\female=0,\;\forall\; i$).
-%($xx_{11}^{\male}=xx_{12}^{\male}=xx_{22}^\male=xy_{11}^{\female}=xy_{12}^{\female}=xy_{21}^{\female}=xy_{22}^\female=yy_{11}^{\female}=yy_{12}^{\female}=yy_{22}^\female=0$). 
-In this case, the system only involves six recursion equations, %because there is only one $\mathbf{M}$ locus allele and no Y-bearing female gametes. 
-which we assume below to calculate the equilibria.
-
-\newpage
 
@@
 
-\newpage
-
-\setcounter{equation}{0}
-\renewcommand{\theequation}{S3.\arabic{equation}}
-
-\section*{S3 Appendix}
-
-\subsection*{Invasion conditions}
-
-A rare neo-Y or neo-W allele, $m$, will spread in an XY sex-determining system when the leading eigenvalue, $\lambda_m^{(XY)}$, of the Jacobian matrix derived from the eight mutant recursion equations (given by \ref{eq:recursions}c,d,g,h), evaluated at the ancestral equilibrium, is greater than one.
-However, because a neo-Y (neo-W) is always in males (females) and is epistatically dominant to the ancestral sex-determining locus, the characteristic polynomial factors into two quadratics times $(\lambda_m^{(XY)})^4$.
-One quadratic governs the change in the frequency of the new sex determination factor associated with the $A$ and $a$ allele frequencies, summing across backgrounds at the old sex-determining locus (i.e., summing haplotypes bearing the original X and Y alleles).
-%It is the largest root of this quadratic that determines the spread of the new $m$ allele (see details in \nameref{file:Mathematica}).  
-The second quadratic describes the dynamics of the difference in the $m$-$A$ and $m$-$a$ haplotypes between X and Y backgrounds.  
-Asymptotically, this difference is constrained to grow at a rate equal to or less than the sum while the $m$ allele is rare, because the frequencies can never become negative. 
-We therefore focus on the leading eigenvalue, $\lambda_m^{(XY)}$, which is the largest root of the first quadratic $f(x) = x^2+ b x + c = 0$, as described in the text (details in \nameref{file:Mathematica}).
-
-When $R=0$ the two roots are $\Lambda_{mA}^{(XY)}$ and $\Lambda_{ma}^{(XY)}$, and the leading eigenvalue is the larger of the two.
-When $R>0$ then $f(\Lambda_{mA}^{(XY)})$ and $f(\Lambda_{ma}^{(XY)})$ are of opposite signs, and the leading eigenvalue must fall between these two quantities (details in \nameref{file:Mathematica}).
-%(the Perron-Frobenius theorem guarantees that the largest eigenvalue is positive, unique, and real).
-Thus, $\lambda_m^{(XY)}>1$ if both $\Lambda_{mA}^{(XY)}>1$ and $\Lambda_{ma}^{(XY)}>1$; similarly, $\lambda_m^{(XY)}<1$ if both $\Lambda_{mA}^{(XY)}<1$ and $\Lambda_{ma}^{(XY)}<1$.
-If only one haplotypic growth rate is greater than one ($\Lambda_{ma}^{(XY)}<1<\Lambda_{mA}^{(XY)}$ or $\Lambda_{mA}^{(XY)}<1<\Lambda_{ma}^{(XY)}$), then $\lambda_m^{(XY)}$ is greater than one when condition \eqref{eq:lambdasGen} is met.
-Thus, the invasion of a new sex-determining allele is determined by the haplotypic growth rates ($\Lambda_{mj}^{(XY)}$ terms), which do not account for loss due to recombination, and the rates at which recombination between the $\mathbf{M}$ and $\mathbf{A}$ loci breaks apart these haplotypes ($\chi_{mj}^{(XY)}$).
-For tight linkage between the ancestral sex-determining locus ($\mathbf{X}$) and the selected locus ($\mathbf{A}$) we can calculate these terms explicitly (see below).
-For weak selection we approximate the leading eigenvalue with a Taylor series. 
-The leading eigenvalue for any $k$ is given up to order $\epsilon^2$ by Eq \eqref{eq:lambda_ESD_k}.
-
-\subsubsection*{Tight linkage between $\mathbf{A}$ and $\mathbf{X}$ ($r \approx 0$)}
-
-Here, we explore the conditions under which a neo-W invades an XY system assuming that the $\mathbf{A}$ locus is initially in tight linkage with the ancestral sex-determining locus ($r \approx 0$). 
-We disregard neo-Y mutations, which never spread given that the ancestral population is at a stable equilibrium (see \nameref{file:Mathematica} for proof).
-
-Starting with the simpler $(B)$ equilibrium, the terms that determine the leading eigenvalue are
-
-\begin{subequations}\label{Binvasion}
-\begin{align}
-\Lambda_{W'A}^{(XY)}&= {\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]}^{-1}
-\frac{w_{A}^\female }{w_{A}^\female}
-\frac{\left[ w_{A}^\male (1+\alpha^\male_\Delta) w_{AA}^\female + 
-w_{a}^\male (1-\alpha^\male_\Delta) w_{Aa}^\female (1+\alpha^\female_\Delta) \right]}
-{ 2w_{AA}^\female } \\
-\Lambda_{W'a}^{(XY)}&= {\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]}^{-1}
-\frac{w_{a}^\female}{w_{A}^\female}
-\frac{\left[  w_{A}^\male (1+\alpha^\male_\Delta) w_{Aa}^\female (1-\alpha^\female_\Delta)+
-w_{a}^\male (1-\alpha^\male_\Delta) w_{aa}^\female \right]}
-{ 2w_{AA}^\female } \\
-\chi_{W'A}^{(XY)}&= \frac{1}{2} {\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]}^{-1}
-\frac{w_{A}^\female }{w_{A}^\female}
- \frac{\left[  w_{a}^\male (1-\alpha^\male_\Delta) w_{Aa}^\female (1 + \alpha^\female_\Delta) \right]}
-{ w_{AA}^\female } \frac{R}{2}\\
-\chi_{W'a}^{(XY)}&= \frac{1}{2} {\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]}^{-1}
-\frac{w_{a}^\female}{w_{A}^\female}
- \frac{\left[  w_{A}^\male (1+\alpha^\male_\Delta) w_{Aa}^\female (1-\alpha^\female_\Delta) \right]}
-{  w_{AA}^\female} \frac{R}{2}.
-\end{align}
-\end{subequations}
-
-%\noindent
-%In this case, the zygotic sex ratio ($\zeta$) is given by the difference in haploid selection in males on $a$ (fixed on the Y) and $A$ (fixed on the X) alleles, i.e., there are more males than females if $\zeta = \alpha^\male w_A^\male / [(1-\alpha^\male)w_a^\male + \alpha^\male w_A^\male]<1/2$.
-%$\alpha^\male<1/2$ and/or $w_{a}^\male>w_{A}^\male$.
-%Populations with haploid selection for $a$ in males have a male biased zygotic sex ratio are thus more permissive to invasion by a neo-W ($\Lambda_{mA}$ and $\Lambda_{ma}$ larger).
-%%In addition, the spread of neo-W alleles depends on the fitness of female diploids after mating with an X-$A$ or Y-$a$ male gamete, relative to the fitness of females in the population (all have genotype $AA$ and fitness $w_{AA}^\female$ at this equilibrium).
-%Haploid selection in males has a second effect; the spread rate of neo-W haplotypes is determined by their fitness in diploid females, which depends on their diploid genotype and thus on the male gamete they pair with.
-%Zygotes carrying dominant neo-W alleles will develop as females regardless of their genotype at the XY locus. 
-%Therefore, neo-W females result from matings with either X-$A$ or Y-$a$ male gametes. 
-%The relative proportion of these male gametes is determined by haploid selection in males; mating with a Y-$a$ male gamete is more likely if the $a$ allele is favoured during male gamete production or competition ($\zeta<1/2$).
-%Thus, neo-W females experience different diploid selection than XX females, and the extent of this difference depends on haploid selection in males.
-%Furthermore, haploid selection in females can directly select upon neo-W-$A$ or neo-W-$a$ haplotypes. 
-%A neo-W-$A$ female gamete has the same fitness during haploid competition as resident $A$-bearing female gametes. 
-%On the other hand, neo-W-$a$ female gametes can be favoured or disfavoured during female haploid competition (favoured if $w_{a}^\female>w_{A}^\female$). 
-%Meiotic drive in females ($\alpha^\female$) similarly affects the fitness of these neo-W haplotypes, except that it impacts both haplotypes as meiotic drive only occurs in heterozygotes and therefore does not occur in resident XX females (who are always homozygote $AA$).
-
-Haploid selection impacts the spread of neo-W haplotypes in three ways (also seen in Table \ref{tab:haplotype_growth}).
-Firstly, the zygotic sex ratio becomes male biased, $\zeta>1/2$, when the $a$ allele (which is fixed on the Y) is favoured during competition among male gametes or by meiotic drive in males.
-Specifically, at equilibrium $(B)$, female zygote frequency is $1 - \zeta = w_A^\male (1+\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$ where $2\bar{w}_{H}^\male= \big[w_a^\male (1-\alpha^\male_\Delta) +  w_A^\male (1+\alpha^\male_\Delta) \big]$ has been canceled out in equations \eqref{Binvasion} to leave the term ${\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]}^{-1}$.
-Male biased sex ratios facilitate the spread of a neo-W because neo-W alleles cause the zygotes that carry them to develop as the rarer, female, sex.
-
-Secondly, haploid selection in females selects on neo-W haplotypes directly.
-At equilibrium $(B)$, the fitness of female gametes under the ancestral sex-determining system is $w_{A}^\female$ such that the relative fitnesses of neo-W-$A$ and neo-W-$a$ haplotypes during female gametic competition are $w_{A}^\female/w_{A}^\female$ and $w_{a}^\female/w_{A}^\female$ (see terms in equation \ref{Binvasion}).
-Meiotic drive in females will also change the proportion of gametes that carry the $A$ versus $a$ alleles, which will be produced by heterozygous females in proportions $(1+\alpha_{\Delta}^\female)/2$ and $(1-\alpha_{\Delta}^\female)/2$, respectively.
-These terms are only associated with heterozygous females, i.e., they are found alongside $w_{Aa}^\female$.
-
-Thirdly, haploid selection in males affects the diploid genotypes of females by altering the allele frequencies in the male gametes with which female gametes pair.
-At equlibrium $(B)$, neo-W female gametes will mate with X-$A$ male gametes with probability $ w_A^\male (1+\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$ and Y-$a$ male gametes with probability $w_a^\male (1-\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$, where the $2\bar{w}_{H}^\male$ terms have been canceled in Eq \eqref{Binvasion} (as mentioned above).
-Thus, neo-W-$A$ haplotypes are found in $AA$ female diploids with probability $ w_A^\male (1+\alpha^\male_\Delta)/ (2\bar{w}_{H}^\male)$ (e.g., first term in square brackets in the numerator of equation \ref{Binvasion}a) and in $Aa$ female diploids with probability $w_a^\male (1-\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$ (e.g., the second term in square brackets in the numerator of equation \ref{Binvasion}a).
-
-%For instance, because an epistatically dominant neo-W always causes its carrier to become female, it creates females who carry either Y-$a$ or X-$A$ genotypes from their father.
-%Thus, because when there is a polymorphism the X carries some non-zero frequency of $A$, haploid selection in males impacts the diploid genotypes of females (e.g., creating more $Aa$ females when drive in males favours Y-$a$).
-%How this affects the spread of the neo-W then depends on diploid and haploid selection in females.
-
-The other terms in equations \eqref{Binvasion} are more easily interpreted if we assume that there is no haploid selection in either sex, in which case $\Lambda_{W'A}^{(XY)}=(w_{AA}^\female+w_{Aa}^\female)/2 w_{AA}^\female$ and $\Lambda_{W'a}^{(XY)}=(w_{aa}^\female+w_{Aa}^\female)/ 2 w_{AA}^\female$.
-Neither haplotype can spread under purely sexually-antagonistic selection at equilibrium $(B)$, with directional selection in each sex.
-Essentially, the X is then already as specialized as possible for the female beneficial allele ($A$ is fixed on the X background), and the neo-W often makes daughters with the Y-$a$ haplotype, increasing the flow of $a$ alleles into females, which reduces the fitness of those females.
-
-If selection doesn't uniformly favour $A$ in females, however, neo-W-$A$ haplotypes and/or neo-W-$a$ haplotypes can spread ($\Lambda_{W'A}^{(XY)}>1$ and/or $\Lambda_{W'a}^{(XY)}>1$).
-%If $\Lambda_{mA}>1$ (requiring $w_{Aa}^\female>w_{AA}^\female$), the implication is that the neo-W can spread alongside the $A$ allele, despite the fact that the neo-W sometimes brings $Y-a$ haplotypes into females, because $a$ is favoured by selection in females despite $A$ being fixed on the X.
-A neo-W-$A$ haplotype can spread ($\Lambda_{W'A}^{(XY)}>1$) when $w_{Aa}^\female>w_{AA}^\female$, despite the fact that a neo-W brings Y-$a$ haplotypes into females.
-In this case the $a$ allele is favoured by selection in females despite $A$ being fixed on the X background.
-For this equilibrium to be stable (i.e.,  to keep $A$ fixed on the X), X-$a$ cannot be overly favoured in females and X-$A$ must be sufficiently favoured in males (for example, by overdominance in males).
-Specifically, from the stability conditions for equilibrium (B), we must have $w_{Aa}^\female < 2 w_{AA}^\female$ and $w_{Aa}^\male/\big[(w_{aa}^\male+w_{Aa}^\male)/2\big]>w_{Aa}^\female/w_{AA}^\female$.
-
-Still considering $w_{Aa}^\female>w_{AA}^\female$, the neo-W can also spread alongside the $a$ allele ($\Lambda_{W'a}^{(XY)}>1$) if $w_{aa}^\female$ is large enough such that $(w_{Aa}^\female+w_{aa}^\female)/2>w_{AA}^\female$.
-%there is sufficiently strong underdominance in females ($w_{aa}^\female>w_{Aa}^\female$) \textcolor{blue}{[this is describing directional selection, not overdominance - check the conditions for the case we want to talk about]}, such that $(w_{Aa}^\female+w_{aa}^\female)/2>w_{AA}^\female$.
-This can occur with overdominance or directional selection for $a$ in females (Fig \ref{fig:regionplots}B,C).
-In this case, $a$ is favoured on the ancestral Y background in males and on the ancestral X background in females (comparing $Aa$ to $AA$ genotypes in females) but $A$ is fixed on the X background due to selection in males.
-The neo-W-$a$ haplotype can spread because it produces females with higher fitness $Aa$ and $aa$ genotypes.
-
-%When both haplotypes can spread on their own ($\Lambda_{mA}>1$ and $\Lambda_{ma}>1$), the neo-W invades regardless the recombination rate between it and the selected locus, $R$.
-%When neither haplotype can spread ($\Lambda_{mA}<1$ and $\Lambda_{ma}<1$) the neo-W can never invade.
-%And when only one haplotype can spread on its own the neo-W invades only when the rate of recombination onto the favourable background is sufficiently larger than the rate of recombination off this background (i.e., equation\ref{eq:lambdasGen} is satisfied).
-
-%Haploid selection affects the conclusions outlined above by altering the zygotic sex ratio and exerting direct selection on neo-W haplotypes.
-%The effect of sex ratio selection is straightforward and can be seen in Eq \eqref{Binvasion}, where male drive and gamete competition for $a$ (which is fixed on the Y and therefore causes a male bias) increases all four terms.
-%Direct selection on neo-W haplotypes can also be seen in Eq \eqref{Binvasion} by noticing that increasing female drive in favour of $A$ increases the neo-W-$A$ haplotype growth rate ($\Lambda_{mA}$) while female drive and gamete competition in favour of $a$ increases the neo-W-$a$ haplotype growth rate ($\Lambda_{ma}$).
-%Gamete competition in females does not impact the spread of neo-W-$A$ haplotypes because they are on the same background as the resident X.
-%Recombination between the selected locus and the neo-W complicates things slightly, as selective advantages for one neo-W haplotype during the haploid stage in females comes at a cost to the other, and thus recombination off the favoured background becomes more detrimental.
-
-%\textcolor{red}{the versions for equil $(A)$ are not terrible but could be improved by cleverly re-writing with the $\phi$ and $\psi$ terms from above, I think...}
-
-Similar equations can be derived for equilibrium (A) by substituting the equilibrium frequencies into Table \ref{tab:haplotype_growth}
-
-\begin{subequations}\label{Ainvasion}
-\begin{align}
-\Lambda_{W'A}^{(XY)}&= \frac{a}{b} \left[w_{AA}^\female w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi +  w_{Aa}^\female (1+\alpha^\female_\Delta) w_a^\male c \right] / (2 w_a^\female) \\
-\Lambda_{W'a}^{(XY)}&= \frac{a}{b} \left[ w_{Aa}^\female (1-\alpha^\female_\Delta) w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi +  w_{aa}^\female w_a^\male c \right] / (2 w_A^\female) \\
-\chi_{W'A}^{(XY)}&= \frac{a}{b} \frac{R}{2} \left[   w_{Aa}^\female (1+\alpha^\female_\Delta) w_a^\male c \right] / w_a^\female\\ 
-\chi_{W'a}^{(XY)}&= \frac{a}{b} \frac{R}{2} \left[ w_{Aa}^\female (1-\alpha^\female_\Delta) w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi \right] / w_A^\female,
-%\Lambda_{W'A}^{(XY)}&=   {\left[ 2 (1 - \zeta) \right]}^{-1} w_A^{\female} \left[ b w_{AA}^\female + c w_{Aa}^\female \left(1 - \alpha^\female_\Delta \right) \right]/ \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\female}_{D} \right)  \\
-%\Lambda_{W'a}^{(XY)}&=  \\
-%\chi_{W'A}^{(XY)}&= \\ 
-%\chi_{W'a}^{(XY)}&=
-\end{align}
-\end{subequations}
-
-\noindent
-where
-
-\begin{subequations}
-\begin{align}
-a &= w_a^\female \phi + w_A^\female \psi \\
-b &= w_{AA}^\female \left[ w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \right] \phi^2 + w_{Aa}^\female \left[ w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) + w_{aa}^\male w_a^\male \right] \psi \phi + w_{aa}^\female \left( w_{aa}^\male w_a^\male \right) \psi^2\\
-%c &= w_{Aa}^\male (1-\alpha^\male_\Delta) \phi \left[ w_{Aa}^\male (1+\alpha^\male_\Delta) \phi \right] + w_{Aa}^\male\phi \left[ 2w_{AA}^\male + w_{aa}^\male (1+\alpha^\male_\Delta) \right] \psi + w_{aa}^\male \psi \left(2w_{AA}^\male \psi \right) \\
-c &= w_{Aa}^\male (1-\alpha^\male_\Delta) \phi + 2w_{aa}^\male \psi.
-\end{align}
-\end{subequations}
-
-%\textcolor{red}{Sally suggests using some $\zeta$ term in the above equations}
-%\textcolor{blue}{Maybe just reference table 2?}
-
-As with equilibrium (B), haploid selection again modifies invasion fitnesses by altering the ancestral sex ratio, $\zeta$ (see Table \ref{tab:haplotype_growth}), and directly selecting upon female gametes, through $w_{i}^\female$.
-The only difference is that resident XX females are no longer always homozygote $AA$ and males are no longer always heterozygote $Aa$.
-Thus the effect of haploid selection in males is reduced, as is the difference in fitness between neo-W haplotypes and resident X haplotypes, as both can be on any diploid or haploid background.
-
-The other terms are easier to interpret in the absence of haploid selection.
-For instance, without haploid selection, the neo-W-$A$ haplotype spreads ($\Lambda_{W'A}^{(XY)}>1$) if and only if
-
-\begin{equation}\label{eq:BeqWAspread}
-2(w_{Aa}^\female-w_{aa}^\female)w_{aa}^\male \psi^2 > (w_{AA}^\female-w_{Aa}^\female)w_{Aa}^\male \phi (\phi-\psi),
-\end{equation}
-
-\noindent  
-where $\phi-\psi=w_{AA}^\female w_{Aa}^\male-w_{aa}^\female w_{aa}^\male$ and both $\phi$ and $\psi$ are positive when equilibrium (A) is stable. 
-In contrast to equilibrium (B), a neo-W haplotype can spread under purely sexually-antagonistic selection  ($w_{aa}^\female<w_{Aa}^\female<w_{AA}^\female$ and $w_{AA}^\male<w_{Aa}^\male<w_{aa}^\male$).
-The neo-W-$A$ can spread as long as it becomes associated with females that bear more $A$ alleles than observed at equilibrium (A), effectively specializing on female fitness. 
-%In this case, the neo-W-$A$ haplotype can spread, despite producing a lot of $Aa$ daughters by obtaining the $a$ from Y-gametes, when $aa$ females, which the neo-W-$A$ never makes, are strongly selected against.
-%This can be intuited from the fact that \eqref{eq:BeqWAspread} will be more easily met when $w_{Aa}^\female-w_{aa}^\female\approx w_{Aa}^\female$ and $w_{AA}^\female-w_{Aa}^\female\approx 0$, implying $w_{aa}^\female \approx 0$ and $w_{Aa}^\female\approx w_{AA}^\female$ (although this is complicated by the fact that $w_{aa}^\female$ and $w_{Aa}^\female$ affect $\phi$ and $\psi$ too, the intuition holds).
-
-Without haploid selection, the neo-W-$a$ haplotype spreads ($\Lambda_{W'a}^{(XY)}>1$) if and only if
-
-\begin{equation}\label{eq:BeqWaspread}
-(w_{aa}^\female + w_{Aa}^\female-2w_{AA}^\female)w_{Aa}^\male \phi^2 + (w_{aa}^\female-w_{Aa}^\female)(w_{Aa}^\male+2w_{aa}^\male) \phi \psi >0.
-\end{equation}
-
-\noindent
-This condition cannot be met with purely sexually antagonistic selection (as both terms on the left-hand side would then be negative), but it can be met under other circumstances. 
-For example, with overdominance in males there is selection for increased $A$ frequencies on the X background in males, which are always paired with Y-$a$ haplotypes.
-Directional selection for $a$ in females can then maintain a polymorphism at the $\mathbf{A}$ locus on the X background.
-This scenario selects for a modifier that increases recombination between the sex chromosomes (e.g., blue region of Fig 2d in~\cite{Otto2014}) and facilitates the spread of neo-W-$a$ haplotypes, which create females bearing more $a$ alleles than the ancestral X haplotype does.
-
-\subsubsection*{Role of haploid selection with tight linkage between $\mathbf{X}$ and $\mathbf{A}$ loci}
-
-Haploid selection generally expands the conditions under which neo-W alleles can spread within ancestral systems that have evolved tight linkage between the sex-determining locus and a selected locus ($r \approx 0$).
-First, haploid selection can allow a polymorphism to be maintained when it would not under diploid selection alone (e.g., with directional selection in diploids). 
-In cases of ploidally-antagonistic selection, where there is a balance between alleles favored in the haploid stage and the diploid stage, neo-W alleles - even if unlinked to the selected locus - can spread (\nameref{fig:regionPloidAntag}).
-Second, even when diploid selection could itself maintain a polymorphism, haploid selection can increase the conditions under which transitions among sex-determining systems are possible.
-Of particularly importance, when selection is sexually-antagonistic in diploids ($s^\female s^\male <0$ and $0<h^\Hermaphrodite<1$), an unlinked neo-W ($R=1/2$) cannot invade unless there is also haploid selection (see proof in \nameref{file:Mathematica}; Fig \ref{fig:SexAntagTighter} and \nameref{fig:SexAntagTighterMaleDrive}).
-More generally, haploid selection alters the conditions under which neo-W alleles can spread (compare \nameref{fig:regionMaleDrive}-\nameref{fig:regionFemaleGS} to Fig \ref{fig:regionplots}).
-
-%[SALLY:  I think that is enough, but we could add somewhere??: "Without haploid selection, unlinked neo-W alleles ($R=1/2$) can invade only under certain conditions, requiring either overdominance in males or underdominance in females (see proof in supplementary \textit{Mathematica} file).?
-Note that underdominance in females with directional selection in males can lead to the spread of unlinked neo-W?s, but only from equilB (only $\Lambda_{ma}$ is greater than one in this case).]
-
-Male haploid selection in favour of the $a$ allele ($\alpha_{\Delta}^\male<0$, $w_{A}^\male<w_{a}^\male$) generates male-biased sex ratios at equilibria (A) and (B), where Y-$a$ is fixed ($\hat{p}_{Y}^\male=0$).
-Male-biased sex ratios facilitate the spread of neo-W-$A$ and neo-W-$a$ haplotypes (increasing $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$). 
-Panels A-C in \nameref{fig:regionMaleDrive} and \ref{fig:regionMaleGS} show that neo-W haplotypes tend to spread for a wider range of parameters when sex ratios are male biased, compared to Fig \ref{fig:regionplots} without haploid selection.
-By contrast, male haploid selection in favour of the $A$ allele generates female-biased sex ratios and reduces $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$, as demonstrated by panels D-F in \nameref{fig:regionMaleDrive} and \nameref{fig:regionMaleGS}.
-
-Female haploid selection generates direct selection on the neo-W-$A$ and neo-W-$a$ haplotypes as they spread in females. 
-Thus, female haploid selection in favour of the $a$ allele tends to increase $\Lambda_{W'a}^{(XY)}$ and decrease $\Lambda_{W'A}^{(XY)}$, as shown by panels A-C in \nameref{fig:regionFemaleDrive} and \nameref{fig:regionFemaleGS}.
-Conversely, female haploid selection in favour of the $A$ allele increases $\Lambda_{W'A}^{(XY)}$ and decreases $\Lambda_{W'a}^{(XY)}$, see panels D-F in \nameref{fig:regionFemaleDrive} and \nameref{fig:regionFemaleGS}.
-
-Thus, the impact of haploid selection on transitions between sex-determining systems must be considered as two sides of a coin: it can generate sex ratio biases that promote transitions that equalize the sex ratio, but it can also direct select for transitions that cause sex ratios to become biased.
+\bibliography{sex_chromosomes.bib}
 

### 2018-02-07 LaTeX/S3Appendix.tex
moved appendices out of main text but can crossref

--- 2018-02-06 LaTeX/Turnover_plos.tex
@@
 
+%reference equations in appendices
+\usepackage{xr}
+\externaldocument{S1Appendix}
+\externaldocument{S2Appendix}
+\externaldocument{main}
+
 %% END MACROS SECTION
@@
 \vspace*{0.2in}
-
-% Title must be 250 characters or less.
-\begin{flushleft}
-{\Large
-\textbf\newline{Haploid selection, sex ratio bias, and transitions between sex-determining systems} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
-}
-\newline
-% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
-\\
-Michael Francis Scott\textsuperscript{1\Yinyang*},
-Matthew Miles Osmond\textsuperscript{2\Yinyang},
-Sarah Perin Otto\textsuperscript{2}
-\\
-\bigskip
-\textbf{1} UCL Genetics Institute, Department of Genetics, Evolution and Environment, University College London, Gower Street, London WC1E 6BT 
-\\
-\textbf{2} Department of Zoology, University of British Columbia, \#4200 - 6270 University Boulevard, Vancouver, BC, Canada V6T 1Z4
-\\
-\bigskip
-
-% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
-% 
-% Remove or comment out the author notes below if they aren't used.
-%
-% Primary Equal Contribution Note
-\Yinyang These authors contributed equally to this work.
-
-% Additional Equal Contribution Note
-% Also use this double-dagger symbol for special authorship notes, such as senior authorship.
-%\ddag These authors also contributed equally to this work.
-
-% Current address notes
-%\textcurrency Current Address: Dept/Program/Center, Institution Name, City, State, Country % change symbol to "\textcurrency a" if more than one current address note
-% \textcurrency b Insert second current address 
-% \textcurrency c Insert third current address
-
-% Deceased author note
-%\dag Deceased
-
-% Group/Consortium Author Note
-%\textpilcrow Membership list can be found in the Acknowledgments section.
-
-% Use the asterisk to denote corresponding authorship and provide email address in note below.
-* m.f.scott@ucl.ac.uk
-
-\end{flushleft}
-% Please keep the abstract below 300 words
-%currently 312 words
-\section*{Abstract}
-Sex determination is remarkably dynamic; many taxa display shifts in the location of sex-determining loci or the evolution of entirely new sex-determining systems. 
-Predominant theories for why we observe such transitions generally conclude that novel sex-determining systems are favoured by selection if they equalise the sex ratio or increase linkage with a sexually-antagonistic locus.
-We use population genetic models to extend these theories in two ways: 
-(1) We explicitly consider selection on loci very tightly linked to the ancestral sex-determining loci, e.g., within the non-recombining region of the ancestral sex chromosomes. 
-Variation at such loci can favour the spread of new sex-determining systems in which the heterogametic sex changes (XY to ZW or ZW to XY) and the new sex-determining region is less closely linked (or unlinked) to the locus under selection, which is not predicted by previous theory.
-(2) We also consider selection upon haploid genotypes either during gametic competition (e.g., pollen/sperm competition) or meiosis (i.e., non-Mendelian segregation), selective processes that typically occur in one sex or the other.
-We find that associations with haploid selected loci can drive transitions between sex-determining systems, without requiring sexually-antagonistic selection in diploids. 
-Unexpectedly, with haploid selection, transitions between male and female heterogamety can also evolve where linkage with the sex-determining locus is weakened. 
-Furthermore, haploid selection in the heterogametic sex can cause sex ratio biases, which may increase or decrease with the spread of new sex chromosomes. 
-Thus, we find that transitions between sex-determining systems cannot be simply predicted by selection to equalise the sex ratio. 
-Overall, our models reveal that transitions between sex-determining systems, particularly transitions where the heterogametic sex changes, can be driven by loci in previously unpredicted genomic locations that experience selection during diploid and/or haploid phases.
-These results predict conditions under which sex-determining systems are likely to be labile and draw novel connections with sex ratio evolution.
-
-% Please keep the Author Summary between 150 and 200 words
-% Use first person. PLOS ONE authors please skip this step. 
-% Author Summary not valid for PLOS ONE submissions.   
-%currently 193 words
-\section*{Author summary}
-Accumulating evidence indicates that systems of sex determination are strikingly diverse and labile in many clades. 
-This poses the question: what drives transitions between sex-determining systems? 
-Here, we use models to derive conditions under which new sex-determining systems spread. 
-Prevailing views suggest that new sex-determining systems are favoured when they equalize the sex ratio and/or when they are more closely linked to genes that experience differential selection in males and females.
-Our models extends these theories to include selection upon haploid genotypes (meiotic drive or gametic competition), which causes sex ratio biases and occurs differently in males and females. 
-Surprisingly, we find that neither force (sex ratio selection nor associations with genes that have sex-specific effects) dominates the spread of new sex-determining systems alone. 
-Even more unexpectedly, we find that, to spread, new sex-determining alleles do not necessarily have to arise in closer linkage with genes that are differentially selected in males and females. 
-Therefore, our models predict loci in previously unexpected genomic locations and/or experiencing various types of selection (including haploid selection) can now be implicated as drivers of transitions between sex-determining systems.
-
-\linenumbers
-
-% Use "Eq" instead of "Equation" for equation citations.
-\section*{Introduction}
-
-Animals and angiosperms exhibit extremely diverse sex-determining systems (reviewed in~\cite{Bull:1983vi,Charlesworth:2010it,Beukeboom:2014vb,Bachtrog:2014bx}). 
-Among species with genetic sex determination (GSD) of diploid sexes, some taxa have heterogametic males (XY) and homogametic females (XX), including %non-monotreme?
-I think monotremes have XY but tonnes of translocations, giving: X1,X2...X6 Y1
-mammals and most dioecious plants~\cite{Ming:2011iy}; whereas other taxa have homogametic males (ZZ) and heterogametic females (ZW), including Lepidoptera and birds. 
-Within several taxa, the chromosome that harbours the master sex-determining locus changes. 
-For example, transitions of the master sex-determining locus between chromosomes or the evolution of new master sex-determining loci where the heterogametic sex does not change (hereafter `cis-GSD transitions') have occurred in Salmonids~\cite{Li:2011fm,Yano:2012di}, Diptera~\cite{Vicoso:2015hf}, and \textit{Oryzias}~\cite{Myosho:2012fv}.
-%Presentation at evolution found neo sex chromosome in birds, doesn't seem to be published or bioRxiv yet (consider pers com.), title: A previously unknown neo-sex chromosome mediates plumage divergence and speciation in hybridizing birds Jason Sardell; Elizabeth Cooper; J.
-Albert C.
-Uy.
-I wonder if this is actually a fusion event though?
-In addition, many clades exhibit transitions between male and female heterogamety (XY$\leftrightarrow$ZW, hereafter `trans-GSD transitions'), including snakes~\cite{Gamble2017}, lizards~\cite{Ezaz:2009tk}, eight of 26 teleost fish families~\cite{Mank:2006bt}, true fruit flies (Tephritids,~\cite{Vicoso:2015hf}, amphibians~\cite{Hillis:1990gu}, the angiosperm genus \textit{Silene}~\cite{Slancarova:2013dq}, the angiosperm family \textit{Salicaceae}~\cite{Pucholt2015,Pucholt2017} and Coleoptera and Hemiptera (plate 2~\cite{Beukeboom:2014vb}).
-Indeed, in some cases, both male and female heterogametic sex-determining systems can be found in the same species, as reported in houseflies~\cite{Macdonald1978}, midges~\cite{Thompson1971}, frogs~\cite{Ogata:2007jm}, cichlid fish~\cite{Ser:2010iq}, tilapia~\cite{Lee2004}, sea bass~\cite{Vandeputte2007}, and lab-strains of Zebrafish~\cite{Liew2012,Wilson2014}.
-In addition, multiple transitions have occurred between genetic and environmental sex-determining systems (GSD$\leftrightarrow$ESD), e.g., in reptiles and fishes~\cite{Conover:1987in,Mank:2006bt,Pokorna:2009ui,Ezaz:2009tk,Pen:2010kk,Holleley:2015hc}.
-
-Predominant theories accounting for the spread of new sex-determining systems by selection involve fitness differences between sexes (e.g., sexually antagonistic selection) or sex ratio selection~\cite{Blaser2012, Beukeboom:2014vb,vanDoorn2014re}.
-%\citet{Bull:1977wt} shows that direct selection on new sex determination loci can allow them to spread and switch between male and female heterogamety. 
-van Doorn and Kirkpatrick~\cite{vanDoorn:2007eu,vanDoorn:2010hu} and Muralidhar and Veller~\cite{Muralidhar2018} have shown that new sex-determining alleles can be favoured if they arise at loci in close linkage with a locus that experiences sexual antagonism.
-Tighter linkage allows a stronger favourable association to build up between a male-beneficial allele, and a neo-Y allele, for example. 
-Such associations can favour cis-GSD transitions~\cite{vanDoorn:2007eu}, trans-GSD transitions~\cite{vanDoorn:2010hu}, and new partially-masculinizing or partially-feminizing alleles~\cite{Muralidhar2018}.
-However, any sexually-antagonistic loci that are more closely linked to the ancestral sex-determining locus will develop similar, favourable associations and are expected to hinder the spread of a new sex-determining system.
-
-The sex ratio is directly determined by the sex-determining system, and it has therefore been suggested that sex ratio selection is a dominant force in the evolution of sex determination (e.g., Bull, 1983, p 66-67 ~\cite{Bull:1983vi}; Buekeboom and Perrin, 2014, Chapter 7~\cite{Beukeboom:2014vb}).
-`Fisherian' sex ratio selection favours a 1:1 zygotic sex ratio when assuming that males and females are equally costly to produce~\cite{Fisher:1930wy,Charnov:1982wg}.
-This follows from the fact that, for an autosomal locus, half of the genetic material is inherited from a male and half from a female~\cite{West:2009we}. 
-Thus, if the population sex ratio is biased towards one sex, the average per-individual contribution of genetic material to the next generation from the opposite sex is greater. 
-Therefore, a mutant that increases investment in the rarer sex will spread via the higher per-individual contributions made by that sex. 
-%The default mode of sex ratio selection is `Fisherian' sex ratio selection, which favours equal investment in male and female offspring \citep[i.e., a 1:1 zygotic sex ratio when assuming that males and females are equally costly to produce,][]{Fisher:1930wy,Charnov:1982wg}.
-%Given that the sex-determining system can directly affect the sex ratio, we might expect Fisherian sex ratio selection to influence the spread of new sex-determining systems. 
-In the case of sex-chromosome evolution, Kozielska et al.
-(2014)~\cite{Kozielska:2010vm} consider systems in which the ancestral sex chromosomes experience meiotic drive (e.g., where driving X or Y chromosomes are inherited disproportionately often), which causes sex ratios to become biased~\cite{Hamilton:1967ts}.
-They find that masculinizing or feminizing mutations that arise at a new, unlinked locus (i.e., neo-Y or neo-W chromosomes) can then spread, which restore an even sex ratio.
-
-Here we use mathematical models to find the conditions under which new sex-determining systems spread when individuals experience selection at both diploid and haploid stages, which allows fitness differences between the sexes and sex ratio biases to occur simultaneously.
-Even in animal and plant species that have much larger and more conspicuous diploid phases than haploid phases, many loci experience significant haploid selection through gamete competition and/or meiotic drive~\cite{Mulcahy:1996ha,JOSEPH:2004haa}.
-We use the term `meiotic drive' to refer to the biased (non-Mendelian) segregation of genotypes during gamete production (from one parent) and the term `gametic competition' to refer to selection upon haploid genotypes within a gamete/gametophyte pool (potentially from multiple parents); the term `haploid selection' encompasses both processes.
-
-Segregation distortion provides putative evidence of haploid selection and can sometimes be attributed to meiotic drive and/or gametic competition~\cite{Lalanne2004,Fishman2005,Leppala2008,Leppala2013,Didion2015,Didion2016}.
-Where it has been characterized, meiotic drive generally occurs either during the production of male or female gametes only~\cite{Ubeda:2005gw,Lindholm:2016cw}.
-Gametic competition is also typically sex specific, occurring primarily among male gametes, because there are typically many more pollen/sperm than required for fertilization.
-Gametic competition may be particularly common in plants, in which 60-70\% of all genes are expressed in the male gametophyte, and these genes exhibit stronger signatures of selection than randomly-chosen genes~\cite{Borg:2009jpa,Arunkumar:2013iq,Gossmann:2014dua}.
-In addition, artificial selection pressures applied to male gametophytes are known to cause a response to selection (e.g.,~\cite{Hormaza:1996cv,Ravikumar:2003uo,Hedhly:2004iv,Clarke:2004ir}). 
-A smaller proportion of genes are thought to be expressed and selected during competition in animal sperm, although precise estimates are uncertain~\cite{Zheng:2001fi,JOSEPH:2004haa,Vibranovski:2010et}.
-Nevertheless, recent studies have demonstrated that sperm competition in animals can alter haploid allele frequencies and increase offspring fitness~\cite{Immler:2014im,Alavioon2017}.
-
-There are various ways by which genes experiencing haploid selection could influence transitions between sex-determining systems. 
-If we assume that haploid selection at any particular locus predominantly occurs in one sex (e.g., meiotic drive during spermatogenesis), then such loci experience a form of sex-specific selection. 
-In this respect, we might expect that haploid selection would affect transitions between sex-determining systems in a similar manner to sex-specific diploid selection (as explored in~\cite{vanDoorn:2007eu,vanDoorn:2010hu}).
-That is, new masculinizing mutations (neo-Y alleles) could be favoured via associations with alleles that are beneficial in the male haploid stage. 
-On the other hand, sex ratios can also become biased by linkage between the sex-determining locus and a locus that harbours genetic variation in haploid fitness. 
-For example, there are several known cases of sex ratio bias caused by sex-linked meiotic drive alleles (Burt and Trivers, 2006, Chapter 6~\cite{Burt:2006}) or selection among X- and Y-bearing pollen~\cite{Lloyd:1974tz,Conn:1981uw,Stehlik:2005ul,Stehlik:2006to,Field:2012fd,Field:2013cc}.
-It is not immediately clear how the spread of new sex-determining systems would be influenced by the combination of sex ratio biases and associations with haploid selected alleles.
-
-We find that the spread of novel sex-determining systems is influenced by both Fisherian sex ratio selection and by selection on linked alleles. 
-%We find that sex ratio biases caused by haploid selection can exert Fisherian sex ratio selection upon novel sex-determiners but that their spread is also determined by selection on genetically-associated alleles.
-%Indeed, it is only when haploid-selected loci are tightly linked to the ancestral sex-determining region (and so sex ratio biases are initially large) that we see an asymmetry between selection for XY to ZW transitions and ZW to XY transitions (e.g., because haploid selection in males only causes biased zygotic sex ratios in an ancestrally XY system).
-Surprisingly, Fisherian sex ratio selection does not dominate; it is possible for selection on linked alleles to drive turnover between sex-determining systems despite causing increasingly biased sex ratios.
-In addition to considering haploid selection, another novel development in our model is that we consider loci that are in very tight linkage with the ancestral sex-determining locus. 
-%Because sex-determining loci are often found within a region of suppressed recombination, there can be a significant number of tightly linked loci. 
-We find that loci tightly linked with the sex-determining locus can drive transitions in which the heterogametic sex changes, even when the new sex-determining locus is less closely linked to loci under selection (either including haploid selection or not).
-
-\section*{Model}
-
-%genetic system
-We consider transitions between ancestral and novel sex-determining systems using a three-locus model, each locus having two alleles (Fig \ref{fig:model_outline}). 
-Locus $\mathbf{X}$ is the ancestral sex-determining region, with alleles X and Y (or Z and W).
-Locus $\mathbf{A}$ is a locus under selection, with alleles $A$ and $a$.
-Locus $\mathbf{M}$ is a novel sex-determining region, at which the null allele ($M$) is initially fixed in the population such that sex of zygotes is determined by the genotype at the ancestral sex-determining region, $\mathbf{X}$; XX genotypes become females and XY become males (or ZW become females and ZZ become males).
-To evaluate the evolution of new sex-determining systems, we consider the invasion, fixation, maintenance, and/or loss of a novel sex-determining allele ($m$) at the $\mathbf{M}$ locus. 
-%We only do invasion analytically though (is this sentence still ok?)
-We assume that the $\mathbf{M}$ locus is epistatically dominant over the $\mathbf{X}$ locus such that zygotes with at least one $m$ allele develop as females with probability $k$ and as males with probability $1-k$, regardless of the $\mathbf{X}$ locus genotype.
-With $k=0$, the $m$ allele is a masculinizer (a neo-Y allele) and with $k=1$ the $m$ allele is a feminizer (a neo-W allele).
-With intermediate $k$, we can interpret $m$ as an environmental sex-determination (ESD) allele, such that zygotes develop as females in a proportion ($k$) of the environments they experience. 
-%We also analyze a model of maternally-controlled environmental sex-determination, where mothers with at least one $m$ allele produce daughters with probability $k$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Model Outline
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-%\centering
-%\centerline{\includegraphics[width=\linewidth]{Sex_determination_outline.pdf}}
-\caption{
-{\bf Outline of model features.}
-Panel A: Recombination rate parameters between the ancestral-sex-determining locus ($\mathbf{X}$, here assumed to have alleles X and Y), a locus under selection ($\mathbf{A}$, with alleles $A$ and $a$), and a new sex-determining locus ($\mathbf{M}$, with alleles $M$ and $m$).
-If $r<1/2$, then associations between ancestral sex-determining alleles and selected alleles can be maintained past recombination in males. 
-Panel B: Haploid selection is often sex-specific, occurring during haploid production or competition in either males or females. 
-For example, haploid selection in males only is represented by the dashed circle.  
-If X or Y alleles remain associated with alleles that experience haploid selection in males ($r<1/2$), then zygotic sex ratios can become biased because either X- or Y-bearing male gametes/gametophytes will be more abundant after haploid selection.
-However, the zygotic sex ratio is not biased by male haploid selection in ZW sex-determining systems. 
-Similarly, zygotic sex ratio biases can occur if haploid selected alleles are associated with new sex-determining alleles ($R<1/2$). 
-Panel C: During cis-GSD transitions (XY to XY or ZW to ZW), a neo-Y allele spreads to pseudo-fixation (its maximum frequency among male gametes) and the ancestral Y allele is lost. 
-Panel D: During trans-GSD transitions (XY to ZW or ZW to XY), a neo-W allele spreads to pseudo-fixation (its maximum frequency among female gametes) and the ancestral X allele is lost. 
-Neo-W alleles allow Y-associated alleles into females, which may impede or aid their spread. 
-}
-\label{fig:model_outline}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%life-cycle
-In each generation, we census the genotype frequencies in male and female gametes/gametophytes (hereafter gametes) before gametic competition. 
-A full description of our model, including recursion equations, is given in \nameref{app:recurs}. 
-First, competition occurs among male gametes (sperm/pollen competition) and among female gametes (egg/ovule competition) separately. 
-Selection during gametic competition depends on the $\mathbf{A}$ locus genotype; relative fitnesses are given by $w_A^\Hermaphrodite$ and $w_a^\Hermaphrodite$ ($\Hermaphrodite \in \{\female,\male\}$; see table \ref{tab:fitnesstable}).
-%$w_{A}^\male$ and $w_{a}^\male$ for male gametes and $w_{A}^\female$ and $w_{a}^\female$ for female gametes, see table \ref{tab:fitnesstable}.
-We assume that all gametes compete for fertilization during gametic competition, which implies a polygamous mating system. 
-Gametic competition in monogamous mating systems is, however, equivalent to meiotic drive in our model (described below), as either only alters the frequency of gametes produced by heterozygotes. 
-After gametic competition, conjugation between male and female gametes occurs at random.
-The resulting zygotes develop as males or females, depending on their genotypes at the $\mathbf{X}$ and $\mathbf{M}$ loci.
-%(and the $\mathbf{M}$ genotype of their mother in the case of maternal control).
-Diploid males and females then experience selection, with relative fitnesses $w_{AA}^{\Hermaphrodite}$, $w_{Aa}^{\Hermaphrodite}$, and $w_{aa}^{\Hermaphrodite}$.
-%where $g$ is the diploid genotype at the $\mathbf{A}$ locus ($g \in \{AA, Aa, aa\}$).
-%Diploids compete with others of the same sex, where selection depends on the sex of the individual and its genotype at the $\mathbf{A}$ locus.
-The next generation of gametes is produced by meiosis, during which recombination and sex-specific meiotic drive can occur. 
-Recombination (i.e., an odd number of cross-overs) occurs between loci $\mathbf{X}$ and $\mathbf{A}$ with probability $r$, between loci $\mathbf{A}$ and $\mathbf{M}$ with probability $R$, and between loci $\mathbf{X}$ and $\mathbf{M}$ with probability $\rho$.
-Any linear order of the loci can be modelled with appropriate choices of $r$, $R$, and $\rho$ (see Fig \ref{fig:model_outline}A and \nameref{tab:chisubstitutions}). 
-Individuals that are heterozygous at the $\mathbf{A}$ locus may experience meiotic drive; a gamete produced by $Aa$ heterozgotes of sex $\Hermaphrodite$ bears allele $A$ with probability $\alpha^\Hermaphrodite$.
-Thus, the $\mathbf{A}$ locus can experience sex-specific gametic competition, diploid selection, and/or meiotic drive.
-
-\begin{table}[ht]
-%\centering
-\smallskip
-\caption{{\bf Relative fitness of different genotypes in sex $\Hermaphrodite \in \{\female,\male\}$ } }
-\begin{tabular}{l c }
-\hline\hline
-  Genotype & Relative fitness during gametic competition \\ [0.5ex] \hline
-  $A$ & $w_{A}^\Hermaphrodite = 1+t^\Hermaphrodite$ \\
-  $a$ & $w_{a}^\Hermaphrodite = 1$ \\ [0.5ex] \hline
-  Genotype & Relative fitness during diploid selection \\ [0.5ex] \hline
-  $AA$ & $w_{AA}^\Hermaphrodite = 1+ s^\Hermaphrodite$ \\
-  $Aa$ & $w_{Aa}^\Hermaphrodite = 1+h^\Hermaphrodite s^\Hermaphrodite$ \\
-  $aa$ & $w_{aa}^\Hermaphrodite = 1$ \\ [0.5ex] \hline
-  Genotype & Transmission during meiosis in $Aa$ heterozygotes \\ [0.5ex] \hline
-  $A$ & $\alpha^\Hermaphrodite=1/2+\alpha_{\Delta}^{\Hermaphrodite}/2$ \\
-  $a$ & $1-\alpha^\Hermaphrodite=1/2-\alpha_{\Delta}^{\Hermaphrodite}/2$ \\
-  \hline \hline
-  \label{tab:fitnesstable}
- \end{tabular}
-\end{table}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Results}
-%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The model outlined above describes both ancestral XY and ZW sex-determining systems. %if we relabel the two sexes as being ancestrally `heterogametic' or ancestrally `homogametic'. 
-Without loss of generality, we refer to the ancestrally heterogametic sex as male and the ancestrally homogametic sex as female.
-That is, we primarily describe an ancestral XY sex-determining system but our model is equally applicable to an ancestral ZW sex-determining system (relabelling the ancestrally heterogametic sex as female and the ancestrally homogametic sex as male and switching the labels of males and females throughout).
-We use a superscript to specify the ancestral sex-determining system described, e.g., $^{(XY)}$ for ancestral XY sex-determination.
-
-\subsection*{Generic invasion by a neo-Y or neo-W}
-
-The evolution of a new sex-determining system requires that a rare mutant allele, $m$, at the novel sex-determining locus, $\mathbf{M}$, increases in frequency when rare. 
-This is determined by the leading eigenvalue ($\lambda_m^{(XY)}$) of the system of eight equations describing the frequency of eggs and sperm carrying the $m$ allele in the next generation (equations \ref{eq:recursions}).
-%, evaluated at the above equilibrium.
-%Thus, the system describing the change in frequency of the $m$ allele consists of eight recursion equations. 
-This system simplifies substantially for a dominant neo-Y ($k=0$) or neo-W ($k=1$), see \nameref{app:inv_cond}. 
-The leading eigenvalue for a rare neo-Y or neo-W allele, $m\in\{Y',W'\}$, is the largest value of X that solves $x^2+ b x + c = 0$.  %$(\lambda_m^{(i)})^2+ b \lambda_m^{(i)} + c =0$. 
-The coefficients are $b= - (\Lambda_{mA}^{(XY)} + \Lambda_{ma}^{(XY)})+(\chi_{mA}^{(XY)} + \chi_{ma}^{(XY)})$ and $c = (\Lambda_{mA}^{(XY)} - \chi_{mA}^{(XY)}) (\Lambda_{ma}^{(XY)} - \chi_{ma}^{(XY)}) - \chi_{mA}^{(XY)} \chi_{ma}^{(XY)}$, where $\Lambda_{mi}^{(XY)}>0$ is the multiplicative growth rate (which we will call the ``haplotypic growth rate'') of the neo-sex determination allele $m$ on background $i\in\{A,a\}$ without accounting for loss due to recombination ($R=0$), and $\chi_{mi}^{(XY)}>0$ is the rate at which mutant haplotypes on background $i\in\{A,a\}$ recombine onto the other $\mathbf{A}$ locus background in heterozygotes (proportional to $R$), see Table \ref{tab:haplotype_growth}.
-In the ancestral population, it is convenient to follow the frequency of the $A$ allele among female gametes (eggs), $p^\female_X$, and among X-bearing, $p^\male_X$, and among Y-bearing, $p^\male_Y$, male gametes (sperm/pollen).
-We also track the fraction of male gametes that are Y-bearing, $q$, which may deviate from $1/2$ due to meiotic drive in males. 
-We will consider only equilibrium frequencies of alleles, $\hat{p}^\Hermaphrodite_i$, and Y-bearing male gametes, $\hat{q}$, when calculating the eigenvalues.
-
-\begin{table}[!ht]
-\centering
-\smallskip
-%\caption{Parameters determining invasion (equation \ref{eq:charpoly_neoY}) for neo-Y or neo-W alleles}
-\caption{ {\bf Parameters determining invasion of mutant neo-Y and neo-W alleles into an ancestrally XY system}}
-\begin{tabular}{l}
-\hline\hline
-   \noalign{\vskip 0.5ex}
-   $m$ is a neo-Y ($k=0$) \\ [0.5ex] \hline \noalign{\vskip 1ex}
-  $\Lambda_{Y'A}^{(XY)} = {\left( 2 \zeta \right)}^{-1} \left[\hat{p}_X^\female w_{A}^{\female} w_{A}^{\male} w_{AA}^{\male} + (1-\hat{p}_X^\female) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} (1+\alpha_{\Delta}^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\male}_{D} \right) $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\Lambda_{Y'a}^{(XY)} = {\left( 2 \zeta \right)}^{-1} \left[(1-\hat{p}_X^\female) w_{a}^{\female} w_{a}^{\male} w_{aa}^{\male} + \hat{p}_X^\female w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male}(1 - \alpha_{\Delta}^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\male}_{D} \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\chi_{Y'A}^{(XY)} = R {\left( 2 \zeta \right)}^{-1} \left[ (1-\hat{p}_X^\female) w_{a}^{\female} w_{A}^{\male} w_{Aa}^{\male} (1+\alpha_{\Delta}^{\male}) \right]/  \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\male}_{D} \right)   $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\chi_{Y'a}^{(XY)} = R {\left( 2 \zeta \right)}^{-1} \left[   \hat{p}_X^\female w_{A}^{\female} w_{a}^{\male} w_{Aa}^{\male} (1 - \alpha_\Delta^{\male}) \right]/ \left( \bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\male}_{D} \right)  $\\ [1ex] \hline
-  \noalign{\vskip 0.5ex}
-  $m$ is a neo-W ($k=1$) \\ [0.5ex] \hline \noalign{\vskip 1ex}
-  $\Lambda_{W'A}^{(XY)} = {\left[ 2 (1 - \zeta) \right]}^{-1} \left[ \bar{p}^{\male} w_{A}^{\male} w_{A}^{\female} w_{AA}^{\female}+(1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female}(1+\alpha_{\Delta}^{\female})\right]/ \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\female}_{D} \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\Lambda_{W'a}^{(XY)} = {\left[ 2 (1 - \zeta) \right]}^{-1} \left[ (1-\bar{p}^{\male}) w_{a}^{\male} w_{a}^{\female} w_{aa}^{\female}+\bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female}(1-\alpha_{\Delta}^{\female})\right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\female}_{D} \right) $ \\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\chi_{W'A}^{(XY)} = R {\left[ 2 (1 - \zeta) \right]}^{-1} \left[ (1-\bar{p}^{\male}) w_{a}^{\male} w_{A}^{\female} w_{Aa}^{\female} (1+\alpha_{\Delta}^{\female}) \right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\female}_{D} \right)  $\\ [0.5ex] \noalign{\vskip 0.5ex}
-  $\chi_{W'a}^{(XY)} = R {\left[ 2 (1 - \zeta) \right]}^{-1} \left[ \bar{p}^{\male} w_{A}^{\male} w_{a}^{\female} w_{Aa}^{\female} (1-\alpha_{\Delta}^{\female}) \right] / \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\female}_{D} \right) $ \\ [1ex]
-  \hline \hline 
-   \end{tabular}
-   \begin{flushleft} 
-$\bar{p}^{\male}=(1-\hat{q})\hat{p}_X^\male + \hat{q}\hat{p}_Y^\male$ is the average frequency of the $A$ allele among X- and Y-bearing male gametes.
-%      \item $R$ is the probability of recombination between loci $\mathbf{A}$ and $\mathbf{M}$.
-$\zeta$ is the zygotic sex ratio (fraction male).
-$\bar{w}^{\Hermaphrodite}_{D}$ is the mean fitness of diploids of sex $\Hermaphrodite$.
-$\bar{w}_H^\Hermaphrodite$ is the mean fitness of haploids from sex $\Hermaphrodite$, see \nameref{tab:meanfitnesses}.
-\end{flushleft}
-  \label{tab:haplotype_growth}
-\end{table}
-
-The new sex-determining allele increases in frequency when rare when the largest eigenvalue is greater than one ($\lambda_m^{(XY)}>1$). 
-%If the average change in frequency of the two haplotypes that carry the $m$ allele ($Am$ and $am$) is positive, invasion will always occur, i.e., if $(\Lambda_{mA} + \Lambda_{ma})/2 > 1$ then $\Lambda > 1$.
-%The leading eigenvalue is the largest solution of $f(\lambda_m^{(i)})=(\lambda_m^{(i)})^2+b\lambda_m^{(i)}+c=0$ and the Perron-Frobenius theorem guarantees that it is positive, unique, and real.  
-%Since $f(\Lambda_{mA}^{(i)})$ and $f(\Lambda_{ma}^{(i)})$ are of opposite signs, the leading eigenvalue must fall between these two quantities and is the larger of them when $R = 0$ (see \nameref{file:Mathematica}).
-If both haplotypic growth rates are greater than one ($\Lambda_{mA}^{(XY)}, \Lambda_{ma}^{(XY)}>1$), then the new sex-determining allele invades regardless the rate of recombination between the new sex-determining locus and the selected locus ($R$), see \nameref{app:inv_cond} for details.
-Conversely, if both haplotypic growth rates are less than one ($\Lambda_{mA}^{(XY)}, \Lambda_{ma}^{(XY)}<1$), then invasion can never occur.  
-Finally, if only one haplotypic growth rate is greater than one, the new sex-determining allele can always invade when arising at a locus that is tightly linked to the selected locus ($R\approx0$).  
-Furthermore, it can be shown that the leading eigenvalue declines with $R$, and invasion requires that $R$ is sufficiently small such that: 
-\begin{equation}\label{eq:lambdasGen}
-%\frac{\chi_{mA}}{\Lambda_{mA}-1}+\frac{\chi_{ma}}{\Lambda_{ma}-1}>0.
-\chi_{ma}^{(XY)}/\left(\Lambda_{ma}^{(XY)} - 1\right) + \chi_{mA}^{(XY)}/\left(\Lambda_{mA}^{(XY)} - 1\right) < 1.
-\end{equation}
-\noindent 
-This condition may or may not be satisfied for the full range of locations of the new sex-determining locus, including $R=1/2$, depending on the nature of selection.  
-Interpreting this condition, if we assume that only the $mA$ haplotype would increase in frequency when $R=0$ ($\Lambda_{ma}^{(XY)}<1<\Lambda_{mA}^{(XY)}$) the first term on the left-hand side of \eqref{eq:lambdasGen} is negative and invasion requires that rate of growth of $mA$ haplotypes ($\Lambda_{mA}^{(i)}-1>0$) and the rate at which $mA$ haplotypes are produced by recombination in $ma$ haplotypes ($\chi_{ma}^{(i)}$) are sufficiently large relative to the rate of decline of $ma$ haplotypes ($1-\Lambda_{ma}^{(i)}>0$) and the rate of loss of $mA$ haplotypes due to recombination ($\chi_{mA}^{(i)}$).
-
-We can draw a number of key points about the invasion of neo-Y and neo-W mutations from Table \ref{tab:haplotype_growth}. 
-First, Fisherian sex ratio selection will favour the spread of a neo-Y and inhibit the spread of a neo-W if the ancestral zygotic sex ratio is biased towards females, $\zeta<1/2$ (i.e., the first factor of the $\Lambda_{mi}^{(XY)}$ is greater than one for a neo-Y and less than one for a neo-W).
-However, the spread of a neo-Y (neo-W) also depends on the male (female) fitness of associated alleles (see terms involving equilibrium allele frequencies, $\hat{p}$'s).
-Second, invasion by a neo-Y (neo-W) does not directly depend on the fitness of female (male) diploids. %(for a given set of equilibrium allele frequencies).
-This is because a dominant neo-Y (neo-W) is always found in males (females), and therefore the frequency of the neo-Y (neo-W), $m$, only changes in males (females), Fig \ref{fig:model_outline}C,D. 
-Finally, invasions by a neo-Y and a neo-W are qualitatively different.
-This is because a gamete with the neo-Y always pairs with a female gamete containing an X, Fig \ref{fig:model_outline}C.
-By contrast, a gamete with a neo-W can pair with an X- or Y-bearing male gamete, Fig \ref{fig:model_outline}D.
-Consequently, neo-W-bearing females obtain a different frequency of $A$ alleles from mating (when $\hat{p}_X^\male \neq \hat{p}_Y^\male$) compared to ancestral ($MM$) females.
-
-In order to explicitly determine the conditions under which a rare new sex-determining allele spreads, we must calculate the equilibrium frequency of the $A$ allele (i.e., $\hat{p}^\female_X$, $\hat{p}^\male_X$, and $\hat{p}^\male_Y$) and Y-bearing male gametes ($\hat{q}$) in the ancestral population.
-Since only the $\mathbf{A}$ locus experiences selection directly, any deterministic evolution requires that there is a polymorphism at the $\mathbf{A}$ locus. 
-Polymorphisms can be maintained by mutation-selection balance or transiently present during the spread of beneficial alleles. 
-However, polymorphisms maintained by selection can maintain alleles at intermediate allele frequencies for longer periods. 
-Here, we focus on polymorphisms maintained by selection, where the $A$ allele reaches a stable intermediate equilibrium frequency under the ancestral sex-determining system before the new sex-determining allele ($m$) arises.
-Such polymorphisms can be maintained by heterozygote advantage, sexually-antagonistic selection, ploidally-antagonistic selection, or a combination~\cite{Immler:2012tl}.
-We can analytically calculate the allele frequency of the $A$ allele using two alternative simplifying assumptions: 
-(1) the $\mathbf{A}$ locus is within (or tightly linked to) the non-recombining region around the ancestral sex-determining locus ($r \approx 0$) or (2) selection is weak relative to recombination ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon<<1$).
-
-\subsection*{Tight linkage with the ancestral sex-determining locus ($r \approx 0$)}
-
-The ancestral equilibrium allele frequencies and their stability conditions are given in \nameref{app:eq_stab}. 
-When there is complete linkage between the ancestral sex-determining locus and the $\mathbf{A}$ locus ($r=0$), either the $A$ allele or the $a$ allele must be fixed in gametes containing a Y allele. 
-% because selection on the Y is effectively haploid an incapably of maintaining a polymorphism in the absence of frequency dependent selection. 
-Because the labelling of alleles is arbitrary, we will assume that the $a$ locus is fixed in gametes with a Y ($p^\male_Y=0$), without loss of generality. 
-If there are two alleles maintained at the $\mathbf{A}$ locus, the $A$ allele can be fixed ($\hat{p}^\female_X=\hat{p}^\male_X=1$) or segregating at an intermediate frequency (0<$\hat{p}^\female_X, \hat{p}^\male_X$<1) in gametes with an X.
-%However, because the X is present in both males and females, there are distinct selection pressures on X's in females and X's in males, which will always be paired with an $A$ allele from the Y.
-
-We find that a neo-Y allele can never invade an ancestral XY system that already has tight linkage with the locus under selection ($\lambda_{Y'}^{(XY)} \leq 1$ when $r=0$, for details see \nameref{file:Mathematica}).
-When $R=0$, a neo-Y haplotype with the same allele as the ancestral Y is neutral ($\Lambda_{Y'a}^{(XY)}=1$) and does not change in frequency.
-The other neo-Y haplotype will not spread ($\Lambda_{Y'A}^{(XY)}<1$) given that the initial equilibrium is stable. 
-Therefore, a neo-Y mutation cannot spread in an ancestral XY system ($\lambda_{Y'}^{(XY)} \leq 1$, regardless of $R$) where selected loci are within or very near the non-recombining region around the sex-determining locus.
-In essence, through tight linkage with the $\mathbf{A}$ locus, the ancestral Y becomes strongly specialized on the allele that has the highest fitness across male haploid and diploid phases. 
-Given that the ancestral Y is at this equilibrium, it is not possible for a neo-Y to create males that have higher fitness than the ancestral Y.
-
-Neo-W alleles, on the other hand, can invade an ancestral XY system under some conditions (the full invasion conditions are given in \nameref{app:inv_cond}; equations \ref{Binvasion} and \ref{Ainvasion}).
-Counterintuitively, selection on loci within the non-recombining region around the sex-determining locus can favour the invasion of a less closely linked neo-W, whatever the form of selection maintaining a polymorphism (sexually-antagonistic selection, overdominance, ploidally-antagonistic selection, or some combination, Fig \ref{fig:SexAntagTighter}, \nameref{fig:temporalOverdominance}, \nameref{fig:regionPloidAntag}, and \nameref{fig:SexAntagTighterMaleDrive}).
-The conditions become more restrictive, however, with increasing recombination ($R$) between the new sex-determining locus and the selected locus.  
-The invasion of completely unlinked neo-W alleles ($R = 1/2$) can occur with overdominance in males or with haploid selection but is not possible with only sexually-antagonistic selection if selection is directional in each diploid sex (see \nameref{file:Mathematica}).
-To develop an intuition for how less closely linked neo-W alleles invade ($R>r$), we here focus on cases where there is no haploid selection and discuss the additional effect of haploid selection in \nameref{app:inv_cond}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Tighter linkage allows looser sex-linkage to evolve, even in absence of haploid selection
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-%\centerline{\includegraphics[width=1.5\linewidth]{PositionPlot_SexAntagTighter}}
-\caption{
-{\bf Transitions between XY and ZW systems can occur even when the new sex-determining locus is less tightly linked to a locus under sexually-antagonistic selection (even without haploid selection).}
-In panel A, linkage is loose enough relative to selection that the analytical results assuming weak selection hold, and a neo-W allele can only invade when it arises at a locus more tightly linked with the selected locus ($R<r$; shaded region).
-In panel B, linkage is tight enough relative to selection that the analytical results assuming weak selection do not hold, and a neo-W can invade even when it is less tightly linked with the selected locus ($r<R$; unshaded region around \text{*}).
-In panel C we vary the recombination rate between the neo-W and the selected locus ($R$) for a fixed recombination rate between the ancestral sex-determining locus and the selected locus ($r=0.005$). 
-Coloured markers show recombination rates for which the temporal dynamics of invasion are plotted in the inset, demonstrating that neo-W alleles can reach pseudo-fixation if they are more (black) or less (red) closely linked to a locus experiencing sexually-antagonistic selection.
-A very loosely linked neo-W does not spread in this case (blue and green lines overlap and go to 0 in inset). 
-Fitness parameters are: $w_{AA}^\female = 1.05$, $w_{aa}^\male = 1.2$, $w_{aa}^\female = w_{AA}^\male = 0.85$, $w_{Aa}^\Hermaphrodite = 1$,  $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
-%\textcolor{red}{consider removing panel A, which is repeated in Fig 3.}
-%\textcolor{blue}{probably better to remove from panel 3, eh?}
-}
-\label{fig:SexAntagTighter}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-If we categorise the $a$ allele as being ancestrally `male-beneficial' via the fact that it is fixed on Y backgrounds, then $\Lambda_{W'A}^{(XY)}>1$ indicates that the neo-W spreads when found with the ancestrally `female-beneficial' allele.
-Broadly, this is possible because ancestral X alleles are sometimes in males and are therefore unable to perfectly specialise on the `female-beneficial' allele. 
-For example, when the $a$ allele is favoured on ancestral X backgrounds in males, a polymorphism of $A$ and $a$ alleles can be maintained on the X background despite selection for the $A$ allele in females ($s^\female>0$, $0<h^\female<1$), see outlined region in Fig \ref{fig:regionplots}A.
-When the $a$ allele is strongly favoured on the X background in males ($w_{aa}^\male$ sufficiently large relative to $w_{Aa}^\male$), neo-W-$A$ haplotypes can spread ($\Lambda_{W'A}^{(XY)}>1$, see grey region in Fig \ref{fig:regionplots}A) because they produce higher fitness females ($AA$ or $Aa$ genotypes) and are unleashed from counterselection in males.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Both neo-W haplotypes can spread, in the absence of haploid selection, when there is overdominance
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-%\centerline{\includegraphics[width=1.25\linewidth]{Region_plot_combined_Mike}}
-%\centerline{\includegraphics[width=1.25\linewidth]{Region_plot_combined}}
-\caption{
-{\bf When the ancestral XY locus is tightly linked to a locus under selection ($r=0$), one or both neo-W haplotypes can spread. }
-We vary the fitness of male homozygotes relative to heterozygotes ($w_{Aa}^\Hermaphrodite=1$) and only consider stable equilibria at which both $\mathbf{A}$ locus alleles are maintained and the $a$ allele is initially fixed on Y backgrounds, region outlined.
-Here, selection in females can favour the $A$ allele (panel A, $w_{aa}^\female=0.85$, $w_{AA}^\female=1.05$), favour the $a$ allele (panel B, $w_{aa}^\female=1.05$, $w_{AA}^\female=0.85$), or be overdominant (panel C, $w_{aa}^\female=w_{AA}^\female=0.6$).
-If either haplotypic growth rate ($\Lambda_{W'A}^{(XY)}$ or $\Lambda_{W'a}^{(XY)}$) is greater than one, then a rare neo-W allele can spread for, at least, some values of $R>r$. 
-The parameter values marked with an asterisk correspond to the fitnesses used in Fig \ref{fig:SexAntagTighter}C. 
-Where both haplotypic growth rates are greater than one, a neo-W will spread when rare, regardless of linkage with the selected locus (for any $R$). 
-\nameref{fig:positionOverdominance} shows the dynamics arising with the parameters marked with a dagger. 
-Here, there is no haploid selection $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
-}
-\label{fig:regionplots}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-When only one neo-W haplotype has growth rate greater than one (see Fig \ref{fig:regionplots}), a neo-W allele can invade as long as Eq \eqref{eq:lambdasGen} is satisfied, which may require that the recombination rate, $R$, is small enough.
-Nevertheless, because we assume here that $r$ is small, these results indicate that a more loosely linked sex-determining region ($r<R$) can spread.
-For example, tightly sex-linked loci that experience sexually-antagonistic selection can drive trans-GSD transitions in which the new sex-determining locus is less closely linked to the locus under selection (Fig \ref{fig:SexAntagTighter}).
-
-Given that the $a$ allele can be considered ancestrally `male-beneficial' because it is fixed on Y backgrounds, it is surprising that neo-W-$a$ haplotypes can sometimes be favoured by selection in females ($\Lambda_{W'a}^{(XY)}>1$).
-Again, this occurs because ancestral X alleles also experience selection in males, where they are ancestrally always paired with a Y-$a$ gamete. 
-If there is overdominance in males, X-$A$ Y-$a$ males have high fitness and the $A$ allele is favoured by selection on the X background in males. 
-Therefore, the $A$ allele can be polymorphic or even fixed on the X background despite selection favouring the $a$ allele in females (e.g., see outlined region in Fig \ref{fig:regionplots}B and~\cite{Lloyd1977,Otto2014}).
-In such cases, neo-W-$a$ haplotypes can spread because they create more $Aa$ and $aa$ females when pairing with an X-bearing gamete from males and because they bring Y-$a$ haplotypes into females, where it has higher fitness (Fig \ref{fig:model_outline}D).
-
-In some cases, both W-$A$ and W-$a$ haplotypes can spread.
-For example, when $AA$ individuals have low fitness in females yet the $A$ is polymorphic or fixed on the X background due to overdominance in males (Fig \ref{fig:regionplots}B and \ref{fig:regionplots}C), both neo-W-$A$ and neo-W-$a$ haplotypes produce fewer unfit $AA$ females.
-This is true for the neo-W-$A$ haplotype because it can pair with a Y-$a$ haplotype and still be female. 
-Wherever both haplotypic growth rates are greater than one, invasion by a neo-W is expected regardless of its linkage with the selected locus (i.e., for any $R$, see \nameref{fig:positionOverdominance} and \nameref{fig:temporalOverdominance} for examples).
-
-Assuming selection is weak relative to recombination, van Doorn and Kirkpatrick~\cite{vanDoorn:2010hu} showed that invasion by a neo-W allele occurs under the same conditions as `pseudo-fixation' (at pseudo-fixation the neo-W reaches its maximum frequency among eggs, which is usually 1/2, but can deviate from 1/2 when there is haploid selection before censusing).
-An equivalent analysis is not possible where recombination rates are low. 
-However, numerical simulations demonstrate that new sex-determining alleles do not necessarily reach pseudo-fixation, which can lead to the stable maintenance of a mixed sex-determining system, in which X, Y, Z, and W alleles all segregate (e.g., \nameref{fig:freqAll}B,C).
-
-\subsection*{Loose linkage with the ancestral sex-determining region}
-
-Here we assume that selection is weak ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon<<1$) and thus implicitly assume that all recombination rates ($r$, $R$ and $\rho$) are large relative to selection.
-%, we denote the leading eigenvalues describing the invasion of a neo-Y ($k=0$) and a neo-W ($k=1$) into an ancestrally XY system by $\lambda_{Y',XY}$ and $\lambda_{W',XY}$, respectively. 
-To leading order in selection, the leading eigenvalues are:
-
-\begin{equation}
-\lambda_{Y'}^{(XY)} =1+ \frac{1}{4}V_{A}S_{A}^2\frac{ \left( r-R \right) }{r R}+O\left(\epsilon^3 \right) 
-\label{eq:lambda_neoY}
-\end{equation}
-
-\noindent 
-and
-
-\begin{equation}
-\lambda_{W'}^{(XY)} =\lambda_{Y'}^{(XY)}+\left(2\alpha_{\Delta}^\male-2\alpha_{\Delta}^\female+t^\male-t^\female \right) \left( \hat{p}^\male_Y-\hat{p}^\male_X \right)/2
-+O\left(\epsilon^3 \right)
-\label{eq:lambda_neoW}
-\end{equation}
-
-\noindent
-where $V_{A}=\bar{p}(1-\bar{p})$ is the variance in the equilibrium frequency of $A$ and $S_{A}=(D^\male +\alpha_{\Delta}^\male+t^\male) - (D^\female+\alpha_{\Delta}^\female+t^\female)$ describes sex differences in selection for the $A$ versus $a$ allele across diploid selection, meiosis, and gametic competition.
-The diploid selection term, $D^\Hermaphrodite=\big{[} \bar{p}s^\Hermaphrodite+(1-\bar{p})h^\Hermaphrodite s^\Hermaphrodite\big{]} -\big{[} \bar{p}h^\Hermaphrodite s^\Hermaphrodite+(1-\bar{p}) \big{]}$, is the difference in fitness between $A$ and $a$ alleles in diploids of sex $\Hermaphrodite \in \{\female,\male\}$, where $\bar{p}$ is the leading-order probability of mating with an $A$-bearing gamete from the opposite sex (equation \ref{eq:pAve}).
-The difference in $A$-allele-frequency among Y-bearing sperm versus X-bearing sperm is given by $\hat{p}^\male_Y-\hat{p}^\male_X=V_{A}\big{(}D^\male - D^\female+\alpha_{\Delta}^\male-\alpha_{\Delta}^\female+t^\male-t^\female\big{)}(1-2r)/(2r)$.
-
-%The new sex-determining allele, $m$, will spread in an XY system if $\lambda_{m}^{(XY)}>1$. 
-Eq \eqref{eq:lambda_neoY} demonstrates that, under weak selection, a neo-Y allele will invade an XY system ($\lambda_{Y'}^{(XY)}>1$) if and only if it is more closely linked to the selected locus than the ancestral sex-determining locus (i.e., if $R<r$; note that $V_{A}S_{A}^2$ is strictly positive as long as $\mathbf{A}$ is polymorphic).
-This echoes our results above where a neo-Y could never invade if $r\approx0$. 
-It is also consistent with the results of \cite{vanDoorn:2007eu}, who considered diploid selection only and also found that cis-GSD transitions can only occur when the new sex-determining locus is more closely linked to a locus under sexually-antagonistic selection.
-%Because tighter linkage between the sex-determining region and a selected locus evolves during these transitions, stronger associations between selected alleles and diploid sexes can build up by selection (e.g., between male-beneficial alleles and the male-determining allele, Y).%, increasing diploid mean fitness (Fig \ref{fig:Combination_MeanFit}).
-
-With weak selection and no haploid selection ($t^\Hermaphrodite=\alpha^\Hermaphrodite_{\Delta}=0$), the spread of a neo-W is equivalent to the spread of a neo-Y ($\lambda_{W'}^{(XY)}=\lambda_{Y'}^{(XY)}$), such that trans-GSD transitions can also occur only if the new sex-determining locus is more closely linked to a locus under selection ($R<r$), as found by \cite{vanDoorn:2010hu}.
-When there is haploid selection, invasion also typically occurs when the neo-W is more closely linked to the selected locus than the ancestral sex-determining region (Fig \ref{fig:Combination_Centimorgans}).
-For example, if the $\mathbf{A}$ locus is unlinked to the ancestral sex-determining locus ($r=1/2$), a more closely linked neo-W ($R<1/2$) can always invade.
-In this case, there is no ancestral association between $\mathbf{A}$ alleles and sex chromosomes in males, $\left( \hat{p}^\male_Y-\hat{p}^\male_X \right)=0$, see Eq \eqref{eq:freq_diffs}. 
-The second term in Eq \eqref{eq:lambda_neoW} therefore disappears and invasion depends only on the sign of $(r-R)$.%, as in the case of the neo-Y.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%A neo-W can invade an XY system under a large number of selective regimes
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-%\includegraphics[width=\linewidth]{PositionPlot}
-\caption{
-{\bf Ploidally-antagonistic selection allows a less tightly linked neo-W allele to invade.}
-In panel A, male drive ($\alpha^\male_{\Delta} = -1/20$, $t^\Hermaphrodite = \alpha^\female_{\Delta} = 0$) opposes selection in diploids (no sex-differences: $s^\Hermaphrodite = 1/10$, $h^\Hermaphrodite = 7/10$), in which case the new sex-determining allele can invade regardless of its linkage with the selected locus ($R$).
-In panel B, gametic competition in males ($t^\male = -1/10$, $t^\female = \alpha^\Hermaphrodite_{\Delta} = 0$) opposes selection in diploids (sex-differences: $s^\male = 3/20$, $s^\female = 1/20$, $h^\Hermaphrodite = 7/10$), in which case the new sex-determining allele can once again invade regardless of $R$.
-}
-\label{fig:Combination_Centimorgans}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-However, with haploid selection and $r<1/2$, the additional term in Eq \eqref{eq:lambda_neoW} can be positive.
-This can allow neo-W invasion ($\lambda_{W'}^{(XY)}>1$), even when the new sex-determining locus is less closely linked to the selected locus ($R>r$). 
-%These transitions are unusual because, when $R>r$, associations that selection has built up between alleles more favourable in one sex and alleles that determine sex will be weakened. 
-%Mean diploid fitness therefore decreases during heterogametic transitions that create looser sex-linkage (Fig \ref{fig:Combination_MeanFit}B,D). 
-%Eq \eqref{eq:lambda_neoW} shows that, with weak selection, neo-W alleles can invade an XY system for a large number of selective regimes. 
-%To clarify the parameter space under which $\lambda_{W'}^{(XY)}>1$ , we consider several special cases. 
-%Firstly, if the $\mathbf{A}$ locus is unlinked to the ancestral sex-determining region ($r=1/2$), a more closely linked neo-W ($R<1/2$) can always invade because there is no ancestral association between $A$ alleles and sex chromosomes in males, $\left( \hat{p}^\male_Y-\hat{p}^\male_X \right)=0$, see Eq \eqref{eq:freq_diffs}.
-%The second term in Eq \eqref{eq:lambda_neoW} therefore disappears and invasion depends only on the sign of $(r-R)$, as in the case of the neo-Y. 
-%Indeed, invasion typically occurs when the neo-W is more closely linked to the selected locus than the ancestral sex-determining region (Fig \ref{fig:Combination_Centimorgans}).
-To clarify the parameter space under which invasion occurs despite looser sex-linkage ($\lambda_{W'}^{(XY)}>1$ despite $R>r$), we focus on the special case where $R=1/2$ and $r<1/2$ (e.g., the selected locus is on the ancestral sex chromosome and the novel sex-determining locus arises on an autosome).
-In Table \ref{tab:specialcases} we give the conditions where invasion occurs when we further assume that haploid selection only occurs in one sex (e.g., during male meiosis only) and dominance coefficients are equal in the two sexes, $h^\female=h^\male$.
-When there is no gametic competition and meiotic drive is in one sex only, an unlinked neo-W can invade as long as the same allele is favoured during diploid selection in males and females ($s^\female s^\male>0$, see Fig \ref{fig:Combination_Centimorgans}A and Fig \ref{fig:SexRatioBad}B).
-%, which is 50\% of the parameter space.
-When there is no meiotic drive and gametic competition occurs in one sex only, an unlinked neo-W can invade as long as the same allele is favoured in male and female diploid selection and there are sex differences in selection of one type (e.g., $s^\female(s^\male-s^\female)>0$, see Fig \ref{fig:Combination_Centimorgans}B).
-%, which is 25\% of the parameter space.
-These special cases indicate that neo-W invasion occurs for a relatively large fraction of the parameter space, even if the neo-W uncouples the sex-determining locus from a locus under selection.
-
-\begin{table}[!ht]
-\centering
-\smallskip
-\caption{Invasion conditions for a neo-W allele at an unlinked locus ($R=1/2$) into an ancestral XY system with linkage ($r<1/2$) and one form of haploid selection}
-\begin{tabular}{l l c }
-\hline\hline
-Scenario &  Assumptions & neo-W spreads ($\lambda_{W'}^{(XY)}>1$) if \\ [0.5ex] \hline
-%  $r=1/2$, $R<1/2$ & Always \\ [0.5ex] \hline
-%  $r<1/2$, $R=1/2$ &  \\ [0.5ex] \hline
-\noalign{\vskip 1mm}
-  male drive only & $h^\male=h^\female$, $t^\female=t^\male=\alpha^\female_{\Delta}=0$ & $s^\female s^\male>0$ \\ [0.5ex]
- female drive only & $h^\male=h^\female$, $t^\female=t^\male=\alpha^\male_{\Delta}=0$ & $s^\female s^\male>0$ \\ [0.5ex]
- sperm competition only &  $h^\male=h^\female$, $t^\female=\alpha^\female_{\Delta}=\alpha^\male_{\Delta}=0$ & $s^\female(s^\male-s^\female)>0$ \\ [0.5ex]
-  egg competition only & $h^\male=h^\female$, $t^\male=\alpha^\female_{\Delta}=\alpha^\male_{\Delta}=0$ & $s^\male(s^\female-s^\male)>0$ \\ [0.5ex]
-  \hline \hline
-  \label{tab:specialcases}
- \end{tabular}
-\end{table}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Sex ratio selection is not a good predictor of neo-W invasion into an XY system
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-%\includegraphics[width=\linewidth]{Temporal_SR}
-\caption{
-{\bf Fisherian sex ratio selection alone is not a good predictor of turnover between sex-determining systems.}
-In this figure, selection is ploidally antagonistic with haploid selection favouring the $a$ allele during male meiosis.
-In panel A, male meiotic drive in an ancestral XY system causes a male bias (see Fig \ref{fig:model_outline}B), allowing a neo-W to invade and replace the ancestral sex-determining system (inset shows neo-W frequency among female gametes, reaching pseudo-fixation), which balances the zygotic sex ratio.
-In panel B, male drive in an ancestral ZW system has no effect on the zygotic sex ratio yet a neo-Y can invade and replace the ancestral sex-determining system (inset shows neo-Y frequency among male gametes, reaching pseudo-fixation).
-%When $R<1/2$, the neo-Y becomes associated with the allele favoured by drive, causing the zygotic sex ratio to become biased, hence the frequency of the neo-Y at pseudo-fixation can be higher than $0.5$ (inset).
-Parameters:  $s^\female =s^\male = 0.2$, $h^\female = h^\male = 0.7$, $t^\female = t^\male = \alpha^\female_\Delta = 0$, $\alpha^\male_\Delta = -0.1$, $r=0.02$.
-}
-\label{fig:SexRatioBad}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Previous research suggests that when the ancestral sex-determining locus is linked to a locus that experiences haploid selection (e.g., meiotic drive), alleles at a new, unlinked sex-determining locus invade to restore equal sex ratios~\cite{Kozielska:2010vm}.
-Consider, for example, the case where the $\mathbf{A}$ locus is linked to the ancestral sex-determining locus ($r<1/2$) and experiences meiotic drive in males only ($\alpha^\male_\Delta \neq 0$, $\alpha^\female_\Delta=0$), without gametic competition ($t^\female=t^\male=0$).
-In this case, the zygotic sex ratio can be initially biased only if the ancestral sex-determining system is XY (Fig \ref{fig:model_outline}A and Fig \ref{fig:SexRatioBad}B). 
-%If the ancxestral sex-determining system is ZW, the zygotic sex ratio will be 1:1 because diploid sex is determined by the proportion of Z-bearing versus W-bearing eggs and meiosis in females is fair (Fig \ref{fig:Combination_Turnover}D).
-If Fisherian sex ratio selection were dominant, we would thus expect a difference in the potential for XY to ZW and ZW to XY transitions. 
-%However, to leading order with selection weak relative to recombination, we find that sex ratio selection favours the spread of a neo-W by an amount equl to the spread of a neo-Y into a ZW system (relabeling XY as the heterogametic sex and reversing the labels of males and females in Table \ref{tab:specialcases})
-%However, to leading order with selection weak relative to recombination, we find that sex ratio selection favours the spread of a neo-W (through the first terms in table \ref{tab:haplotype_growth}) by an amount that is equal in magnitude to the fitness effects of alleles associated with new sex-determining alleles (second terms in table \ref{tab:haplotype_growth}).
-However, invasion by a neo-W allele into an XY system and invasion by a neo-Y allele into a ZW system occur under the same conditions ($\lambda_{Y'}^{(XY)} = \lambda_{W'}^{(ZW)}$ and $\lambda_{W'}^{(XY)}=\lambda_{Y'}^{(ZW)}$, at least to order $\epsilon^2$).
-For example, in Fig \ref{fig:SexRatioBad}A neo-W alleles invade an ancestral-XY system where females are initially rare, equalizing the sex ratio.
-However, Fig \ref{fig:SexRatioBad}B shows that a neo-Y can invade the resulting ZW system under the same conditions. 
-When $R<1/2$, the invading neo-Y becomes associated with the male meiotic drive allele and the zygotic sex ratio actually evolves to become male-biased.
-%
-%As selection becomes stronger (or linkage becomes tighter), this symmetry between sex ratio selection and haploid selection is lost, causing differences in the strength of selection favouring the two heterogametic transitions (compare red to black near -25cM and 25 cM in Fig \ref{fig:Combination_Centimorgans}).
-\textcolor{red}{normalise fitness in sexually antagonistic case}
-%
-%Why can new sex-determining regions invade when they are more loosely linked to selected loci ($R>r$)?  
-%Consider first the case where both sex-determining-loci are linked to the selected locus ($r<R<1/2$). 
-%In an ancestral-XY system, haploid selection in males can facilitate the spread of a neo-W because the zygotic sex ratio is ancestrally male biased and the W produces more of the rarer sex (Fig \ref{fig:SexRatioBad}A).
-%A new sex determining region can also, however, benefit from becoming more associated with drive. 
-%For example in an ancestral-ZW system with the same selection regime (haploid selection in males), a neo-Y can spread despite the fact that the zygotic sex is initially even; in this case, the neo-Y spreads because it is often found in males and can, if it carries the driven allele $a$, benefit from haploid selection in males (Fig \ref{fig:SexRatioBad}B).
-
-While equalizing the sex ratio and benefiting from drive are two primary reasons why haploid selection spurs sex chromosome transitions, even when the new sex-determining allele is less closely linked to the selected locus ($r<R$), more complex situations also arise.
-For example with $R=1/2$ in Fig \ref{fig:SexRatioBad}B (green curve), the neo-Y allele spreads despite the fact that it cannot benefit from drive because free recombination moves it randomly between driven and non-driven backgrounds.
-Nevertheless, the unlinked neo-Y can spread because diploids bearing it more often carry the non-driven allele $A$, which is found at high frequency on the W background and has higher average diploid fitness.% to balance the haploid advantage of the $a$ allele at equilibrium.
-
-\subsection*{Environmental sex determination}
-
-We next consider the case where the new sex-determining mutation, $m$, causes sex to be determined probabilistically or by heterogeneous environmental conditions (environmental sex determination, ESD), with individuals carrying allele $m$ developing as females with probability $k$.
-Here, we do not assume that the environmental conditions that determine sex also differentially affect the fitness of males versus females. 
-Such correlations can favour environmental sex-determining systems by allowing each sex to be produced in the environment in which it has highest fitness; in the absence of these correlations, previous theory would predict that ESD is favoured when it produces more equal sex ratios than the ancestral system (see reviews by~\cite{Charnov:1982wg,Bull:1983vi,West:2009we}).
-%(e.g., maternal condition, mate quality, age, or host size)
-
-The characteristic polynomial determining the leading eigenvalue (equations \ref{eq:recursions}) does not factor for ESD ($0<k<1$) as it does for a neo-Y ($k=0$) or neo-W ($k=1$) allele. 
-We therefore focus on weak selection here, where the leading eigenvalue is
-
-\begin{equation}
-\begin{split}
-\lambda_{ESD'}^{(XY)} =& 1 + \frac{{(1-2k)}^2}{4}V_{A}{S_{A}}^2\frac{r-R}{r R} \\
-&+\frac{k(\hat{p}^\male_Y-\hat{p}^\male_X)}{2}\left[ k \left(2\alpha_{\Delta}^\male-2\alpha_{\Delta}^\female+t^\male-t^\female \right) -2(1-k)S_{A}\right]+O\left(\epsilon^3\right).
-\end{split}
-\label{eq:lambda_ESD_k}
-\end{equation}
-
-\noindent
-This reduces to $\lambda_{Y'}^{(XY)}$ when $k=0$ and $\lambda_{W'}^{(XY)}$ when $k=1$.
-
-%Under Fisherian sex ratio selection, autosomal modifiers favour equal investment in male and female offspring, i.e., a 1:1 sex ratio~\cite{Fisher:1930wy,Charnov:1982wg,West:2009we}. 
-%A novel environmental sex-determiner that causes half of its carriers to become female and half to become male ($k=1/2$) will be in males half of the time and in females half of the time (like an autosome).
-%In addition, these novel sex-determination alleles equalize the sex ratio and therefore one might expect them to be favoured by Fisherian sex ratio selection when the resident sex ratio is biased.
-%However, assuming weak selection, we find that the growth rate of a rare, dominant offspring-controlled neo-ESD allele that produces males or females with equal probability ($k=1/2$) is
-Of particular interest are ESD mutations that cause half of their carriers to develop as females and half as males ($k=1/2$), creating equal sex ratios.
-The spread of such ESD is determined by
-\begin{equation}
-\lambda_{ESD'}^{(XY)} =1+ \frac{1}{2}\frac{(\lambda_{Y'\rvert R=1/2}^{(XY)}-1) + (\lambda_{W'\rvert R=1/2}^{(XY)}-1)}{2} + O\left(\epsilon^3\right),
-%V_A \frac{r}{1-2r}  \frac{s_{f} \left( s^\male - 3 s^\female\right) }{8 {\left( s_{f} + s_{m} \right)}^2} t_{m}^2.
-\label{eq:lambda_ESD}
-\end{equation}
-\noindent
-where $\lambda_{Y'\rvert R=1/2}^{(XY)}$ and $\lambda_{W'\rvert R=1/2}^{(XY)}$ represent $\lambda_{Y'}^{(XY)}$ and $\lambda_{W'}^{(XY)}$ when evaluated at $R=1/2$ (Equations \ref{eq:lambda_neoY} and \ref{eq:lambda_neoW}).
-That is, recombination between the selected locus and the novel sex-determining locus, $R$, does not enter into the $k=1/2$ results.
-This is because sex is essentially randomized each generation, %as if the novel sex-determiner were on an unlinked site that half the time acts as a neo-W and half the time as a neo-Y.
-preventing associations from building up between alleles at locus $\mathbf{A}$ and sex. 
-Eq \eqref{eq:lambda_ESD} shows that the ESD mutation gets half of the fitness of a feminizing mutation (neo-W) and half of the fitness of a masculinizing mutation (neo-Y), but only has an effect one half of the time (the other half of the time it produces the same sex as the ancestral system would have).
-As discussed above, $\lambda_{Y'\rvert R=1/2}^{(XY)}$ is necessarily less than one, but $\lambda_{W'\rvert R=1/2}^{(XY)}$ can be greater than one if there is haploid selection.
-That is, when there is haploid selection, ESD can invade an ancestrally-XY system because it generates females that are either rare or have high fitness, in the same manner as a neo-W.
-
-%An important result from Eq \eqref{eq:lambda_ESD} is that ESD can invade if there is haploid selection. 
-%When evaluated at $R=1/2$, $\Lambda_{Y',XY}$ is necessarily less than one, but $\Lambda_{W',XY}$ can be greater than one if there is haploid selection, as discussed above. 
-%Previous studies where ESD is favoured have typically assumed that environmental conditions (e.g., maternal condition, mate quality, age, or host size) can differentially affect the fitness of males versus females such that ESD invades because it allows sex determination to depend on the environment \citep[reviewed in][]{Charnov:1982wg,Bull:1983vi,West:2009we}.
-%Here, ESD mutations can spread because they generate females that are either rare or have high fitness, in the same manner as a neo-W.
-
-Significantly, Eq \eqref{eq:lambda_ESD} is the same whether ESD is invading an ancestrally XY or ZW system (because $\lambda_{Y'}^{(XY)} = \lambda_{W'}^{(ZW)}$ and $\lambda_{W'}^{(XY)} = \lambda_{Y'}^{(ZW)}$).
-Thus, Fisherian sex ratio selection alone does not easily explain GSD to ESD transitions.
-For example, when the ancestral sex-determining system is XY, but not ZW, the sex ratio is biased by male haploid selection.
-Nevertheless, ESD is equally likely to invade when it equalizes the zygotic sex ratio (through $\lambda_{W'}^{(XY)}$) as when it doesn't (through $\lambda_{Y'}^{(ZW)}$). 
-%This is again because haploid selection can facilitate the turnover of sex chromosomes either through sex ratio biases or through associations between the new sex determining region with selected alleles.
-%With weak selection, these two forces are nearly equal in strength. 
-In addition, we note that ESD may not invade, even if the sex ratio is initially biased (e.g., with drive in males only, $r<1/2$, $h^\female=h^\male$, and $s^\female s^\male<0$, then $\lambda_{W'}^{(XY)}<1$, see Table \ref{tab:specialcases}).
-We conclude that, as with neo-W and neo-Y loci, associations with selected loci mean that the evolution of ESD is not straightforwardly predicted by selection to balance the zygotic sex ratio when haploid selection is present.
-
-\section*{Discussion}
-
-%\textcolor{blue}{maybe re-order to put the results up front and focus on sex ratio less.
-Somewhere around these first two paragraphs we should include our tight linkage results.
-At the moment it doesn't make total sense because it assumes that tighter linkage is always favoured unless there is haploid selection.}
-
-%MAIN RESULT
-Two predominant theories explaining the remarkably high frequency of transitions between sex-determining systems are sexually-antagonistic selection and sex ratio selection (reviewed in~\cite{Blaser2012, vanDoorn2014re}).
-The former predicts that new sex-determining alleles can invade when they arise in closer linkage with a sexually-antagonistic locus ($r<R$,~\cite{vanDoorn:2007eu,vanDoorn:2010hu, Muralidhar2018}).
-The latter predicts that new sex-determining systems are generally favoured if they result in more equal sex ratios than the ancestral system. 
-%The latter predicts that neo-W alleles will invade an XY system when there is a male bias caused by haploid selection in males, and vice-versa, a neo-Y will invade a ZW system when there is a female bias caused by haploid selection in females~\cite{Kozielska:2010vm,Ubeda:2015fx}.
-In contrast to these prevailing views, we show that selection (including sexually-antagonistic selection, overdominance, and/or ploidally-antagonistic selection) on loci tightly linked to the ancestral sex-determining locus can favour trans-GSD transitions (XY$\leftrightarrow$ ZW) to new sex-determining systems that are less closely linked to the selected loci (e.g., see Fig \ref{fig:SexAntagTighter}).
-Similarly, even when linkage is weak relative to selection, we show that %new sex-determining alleles are typically favoured if they are more closely linked to a locus under haploid selection (even in the absence of diploid sex differences), which is the only condition favouring cis-GSD transitions (XY to XY or ZW to ZW).
-%In addition, with haploid selection and weak selection, 
-trans-GSD transitions can occur where the new sex-determining locus is less closely linked to the locus under selection if there is haploid selection (e.g., Figs \ref{fig:Combination_Centimorgans} and \ref{fig:SexRatioBad}).
-
-We find that the spread of new sex-determining systems cannot be simply predicted from their effect on the sex ratio. 
-On one hand, sex ratio biases caused by haploid selection can facilitate trans-GSD transitions or transitions from genetic to environmental sex determination. 
-For instance, alleles favoured by haploid selection in males often become associated with the Y allele, which leads to a male-biased zygotic sex ratio.
-This male bias increases the potential for a neo-W allele to invade (Table \ref{tab:haplotype_growth}), which can equalize the sex ratio (e.g., see Fig \ref{fig:SexRatioBad}B, for related examples see~\cite{Kozielska:2010vm}).
-%We find that sex ratio biases caused by haploid selection can also affect transitions between sex-determining systems (e.g., see $\zeta$ terms in Table \ref{tab:haplotype_growth}). 
-%However, the neo-W may not equalize the sex ratio (e.g., if the driving allele also drives in females or affects competition among eggs)
-On the other hand, sex ratio selection can be overwhelmed by additional selective effects, preventing a neo-W or ESD allele from invading, even if it would balance the sex ratio (e.g., when selection acts in opposite directions in male and female diploids, Table \ref{tab:specialcases}).
-%and equalizing the sex ratio.
-Indeed, transitions between sex-determining systems can generate stronger sex ratio biases (e.g., Fig \ref{fig:SexRatioBad}A and step 1 in~\cite{Ubeda:2015fx}).
-%For example, where a neo-Y invades and is linked with a locus that experiences haploid selection in male gametes, the sex ratio evolves to become biased \citep[e.g., see Fig \ref{fig:SexRatioBad}A and step 1 in][]{Ubeda:2015fx}.
-%For example, in an ancestral ZW system, haploid selection in males can allow a linked neo-Y to invade, despite the fact that it creates a male-biased sex ratio because the neo-Y becomes associated with the driven allele (Fig \ref{fig:SexRatioBad}A).
-%\textcolor{blue}{and figure 1, where the end of one panel is the same as the beginning of another, however, this figure may change).}
-%What we would like to stress is that sex ratio selection alone cannot predict when new sex-determining systems can evolve.
-Significantly, with weak selection, we find that there is no difference in conditions allowing XY to ZW and ZW to XY transitions, indicating that sex chromosome transitions are not predominantly predicted by their effect on the sex ratio (i.e., the sex ratio bias created by male haploid selection facilitates the spread of a neo-W allele into an XY system to the same degree that male haploid selection drives the spread of a neo-Y into a ZW system with a 1:1 sex ratio).
-%An asymmetry can develop when sex-linkage is tight (e.g., Fig \ref{fig:Combination_Centimorgans} near -25cM and 25cM) but under most circumstances we do not predict asymmetry between XY to ZW and ZW to XY transitions despite the presence/absence of sex ratio selection.
-Thus, haploid selection can favour trans-GSD transitions both via sex ratio selection and via selection on alleles associated with the new sex-determining allele, and these selective pressures are often predicted to be of equal magnitude.
-
-%HAPLOID SELECTION (genomic location of haploid selected loci and comparative patterns) 
-We have shown that the spread of new sex-determining systems can be driven by loci experiencing haploid selection. 
-%Our results suggest that haploid selected loci that have been involved in driving turnovers between sex-determining systems could occur around the ancestral- or novel-sex-determining regions. 
-%Our results suggest that polymorphic loci that are ancestrally sex-linked and under sex-specific selection could also drive heterogametic transitions between sex-determining systems. 
-%As with sexually-antagonistic selection, the presence of haploid selected loci around ancestral- or novel-sex-determining regions could support their role in sex chromosome turnover.
-In agreement with this hypothesis, a recent transcriptome analysis in Rumex shows that pollen-biased expression (relative to expression in flower buds or leaves) is enhanced among XY-linked genes compared to autosomal genes or compared to hemizygous genes that are only linked to the X (Sandler et al., 2018, personal communication).
-In addition, Y-linked genes are over-expressed relative to X-linked genes in pollen (but not in flower buds or leaves). 
-This suggests that the spread of neo-Y chromosomes in this clade could have been favoured through linkage with haploid selected genes. 
-%maybe add a flag here for switching to clade-level expectations:
-In general, we predict that haploid selection increases lability of sex-determining systems, particularly because haploid selection can cause transitions that increase or decrease sex-linkage (e.g., the final state of the red line in Fig \ref{fig:SexRatioBad}B is the starting state in Fig \ref{fig:SexRatioBad}A).
-Frequent turnovers driven by haploid selection may help to explain the relative rarity of heteromorphic sex chromosomes in plants, which are thought to experience more selection during their multicellular haploid stage.
-
-If haploid selection is strong but selective differences between male and female diploids are weak, we find that trans-GSD transitions are favoured more strongly than cis-GSD transitions, with transitions to ESD intermediate (e.g., with $|D^\male - D^\female| << |\alpha_\Delta^\male - \alpha_\Delta^\female + t^\male - t^\female|$ we have $\lambda_{W'}^{(XY)} > \lambda_{Y'}^{(XY)}$; Equations \ref{eq:lambda_neoW} and \ref{eq:freq_diffs}).
-Among the relatively few dioecious clades in which multiple species have well characterized sex chromosomes~\cite{Ming:2011iy}, trans-GSD transitions have been inferred in \textit{Silene} subsection \textit{Otites}~\cite{Slancarova:2013dq} and in \textit{Salicaceae}~\cite{Pucholt2015,Pucholt2017}.
-%Potentially, successive heterogametic transitions between master regulators of sex-determination could be inferred from careful examination of the molecular pathways by which sex is determined. 
-%Our predictions could also be examined using a suitable proxy for haploid selection, for example, \cite{Lenormand:2005vb} use the outcrossing rate in plants as a proxy for the strength of pollen competition.
-Assuming that transitions from dioecy to hermaphroditism (equal parental investment in male and female gametes) are favoured in a similar manner to the ESD examined here (equal probability of zygotes developing as males or females), our results suggest that competition during the haploid stage could also drive transitions between dioecy and hermaphroditism, which are frequent in plants~\cite{Kafer2017, Goldberg2017}.
-
-In support of their role in sex chromosome turnover, genes expected to be under sexually-antagonistic selection (e.g., those causing bright male colouration) have been found on recently derived sex chromosomes~\cite{Lindholm:2002dw,Tripathi:2009cw,Ser:2010iq}.
-Our results show, however, that tight ancestral-linkage of polymorphic loci, maintained by sexually-antagonistic selection or otherwise, can also drive trans-GSD transitions. 
-In addition, we find that polymorphic sex determining systems (X, Y, W, and Z alleles all present) can be maintained when a selected locus is tightly linked to the ancestral sex-determining system (e.g., \nameref{fig:freqAll}B and \nameref{fig:freqAll}C), which is not possible with loose linkage~\cite{vanDoorn:2010hu}.
-%As noted by \citet{vanDoorn:2010hu}, it would be prudent to compare closely related clades in order to determine whether observed polymorphisms predate a transition in sex-determination or arose afterwards.
-%, particularly because sex-linkage allows sexually-antagonistic selection to maintain polymorphisms under a different and larger parameter space~\cite{Rice:1987hs,Jordan:2011fj}.
-For example, our results suggest a potential mechanism maintaining multiple sex determining alleles in the platyfish (\textit{Xiphophorus maculatus}), in which X,Y, and W alleles segregate at one locus (or two closely-linked loci) near to potentially sexually-antagonistic genes for pigmentation and sexual maturity~\cite{Kallman1965,Kallman1968, Volff2001, Schultheis2006}.
-Several rodent species also maintain feminizing alleles along with the ancestral X and Y sex-determination alleles (reviewed in~\cite{Fredga1994}). 
-For example, in nine \textit{Akadon} species, it appears that male-determining-\textit{sry} expression is suppressed by an autosomal feminizing allele, creating XY females~\cite{Bianchi2002,Sanchez2010}, which have increased fitness relative to XX females~\cite{Hoekstra2001}.
-In \textit{Mus microtoides}, females can have XX, XX$^\ast$ or X$^\ast$Y genotypes~\cite{Veyrunes2010}. 
-Previous theory would predict that the X$^\ast$ chromosome (or the autosome it is fused to) harbours female beneficial alleles, driving its spread. 
-However, XX and XX$^\ast$ females have similar fitness, whereas X$^\ast$Y female fitness is enhanced~\cite{Saunders2014,Saunders2016, Veyrunes2017}.
-Although Y-linkage of female-beneficial alleles is counterintuitive, our model suggests that it can be stably maintained and then favour new feminizing mutations, which is a parsimonious explanation for the spread of feminizing alleles in these rodent species.
-
-%Limitation 1: DEGENERATE Y
-We note that we assume that sex-determining alleles do not experience direct selection except via their associations with sex and selected alleles.
-However, in some cases, there may be significant degeneration around the sex-limited allele (Y or W) in the ancestral sex-determining region because recessive deleterious mutations and/or deletions accumulate in this non-recombining regions~\cite{Rice:1996ke,Charlesworth:2000cc,Bachtrog:2006ed,Marais:2008hm}.
-During trans-GSD transitions, but not cis-GSD transitions, any recessive deleterious alleles linked to the Y or W are revealed to selection in YY or WW individuals~\cite{Bachtrog:2014bx}. 
-This phenomenon was studied by van Doorn and Kirkpatrick (2010)~\cite{vanDoorn:2010hu}, who found that degeneration can prevent fixation of a neo-W or a neo-Y allele, leading to a mixed sex-determining system where the ancestral and new sex-determining loci are both segregating.
-However, they noted that very rare recombination events around the ancestral sex-determining locus can allow these trans-GSD transitions to complete.  
-%While not explicitly studied, we also predict that Y or W degeneration would prevent fixation of the new sex-determining genes considered here.
-Degeneration around the Y or W could explain why trans-GSD transitions are not observed to be much more common than cis-GSD transitions despite the fact that our models demonstrate that they are favoured under a wider range of conditions, especially with haploid selection.
-For example, there are a dozen sex chromosome configurations among Dipteran species but only one transition between male and female heterogamety~\cite{Vicoso:2015hf}.
-
-%Limitation 3: don't consider m alleles with similar k to ancester, no ancestral ESD considered
-In this study, we have only considered new sex-determining alleles of large effect. 
-However, we expect similar selective forces to act on masculinizing/feminizing alleles of weaker effect. 
-For example, small effect masculinizing/feminizing alleles within a threshold model of sex determination can be favoured when linked to loci that experience sexually-antagonistic selection~\cite{Muralidhar2018}.
-These results echo those for large-effect neo-Y/neo-W alleles~\cite{vanDoorn:2007eu,vanDoorn:2010hu}.
-Finally, while we have considered cis-GSD, trans-GSD, and GSD to ESD transitions, we have not explicitly considered ESD to GSD transitions. 
-Recent models of ESD to GSD transitions~\cite{Ubeda:2015fx,Muralidhar2018} show that that neo-Y/neo-W alleles can be favoured when they arise near to haploid and/or diploid selected loci, which also occurs in our model.
-
-%Limitation 2: TWO ALLELE DRIVE
-%Another simplification that we made is that meiotic drive involves only a single locus with two alleles. 
-%However, many meiotic drive systems involve an interaction with another locus at which alleles may `suppress' the action of meiotic drive \citep[][]{Burt:2006,Lindholm:2016cw}.
-%Thus, the dynamics of meiotic drive alleles can be heavily dependent on the interaction between two loci and the recombination rate between them, which in turn can be affected by sex-linkage if there is reduced recombination between sex chromosomes~\cite{Hurst:1991uh}.
-%Furthermore, in some cases, a driving allele may act by killing any gametes that carry a `target' allele at another locus, in which case there can be fertility effects that alter the equilibrium frequency of a meiotic drive allele~\cite{Holman:2015en}.
-%In polygamous mating systems, the intensity of pollen/sperm competition can depend on the density of males available to donate pollen/sperm, which can itself depend on the sex ratio~\cite{Taylor:2002wu}.
-%In terms of our model, this implies that the strength of gametic competition ($t^\male$) may both determine and be determined by the sex ratio. 
-%How the evolution of new sex-determining mechanisms could be influenced by two-locus meiotic drive and/or by ecological feedbacks under different mating systems remains to be studied.
-
-\section*{Conclusion}
-
-We have shown that tight sex-linkage and haploid selection can drive previously unexpected transitions between sex-determining systems.
-In particular, both can select for new sex-determining loci that are more loosely linked to loci under selection. 
-In addition, haploid selection can cause transitions analogous to those caused by purely sexually-antagonistic selection, eliminating the need for differences in selection between male and female diploids.
-We conclude that haploid selection should be considered as a pivotal factor driving transitions between sex-determining systems. 
-Perhaps counterintuitively, transitions involving haploid selection can be driven by sex ratio selection or cause sex ratio biases to evolve; we do not find Fisherian sex ratio selection to be an overwhelming force.
-Overall, our results suggest several new scenarios under which new sex-determining systems are favoured, which could help to explain why the evolution of sex-determining systems is so dynamic.
-
-% For figure citations, please use "Fig" instead of "Figure".
-
-% Place figure captions after the first paragraph in which they are cited.
-
-% Results and Discussion can be combined.
-
-% Place tables after the first paragraph in which they are cited.
-
-%PLOS does not support heading levels beyond the 3rd (no 4th level headings).
-
-\section*{Supporting information}
-
-\paragraph*{S1 File.}
-\label{file:Mathematica}
-{\bf Supplementary \textit{Mathematica} file.}  This file can be used to re-derive our results and generate figures.
-
-\paragraph*{S1 Table}
-\label{tab:chisubstitutions}
-{\bf Substitutions for different loci orders assuming no interference.}
-
-\paragraph*{S2 Table}
-\label{tab:meanfitnesses}
-{\bf Mean fitnesses and zygotic sex ratio in the resident population ($M$ fixed, XY sex determination). }
-
-\paragraph*{S1 Appendix.}
-\label{app:recurs}
-{\bf Recursion equations and complete model description.}
-
-\paragraph*{S2 Appendix.}
-\label{app:eq_stab}
-{\bf Equilibria and stability conditions when $M$ allele is fixed. }
-
-\paragraph*{S3 Appendix.}
-\label{app:inv_cond}
-{\bf Invasion conditions for the $m$ allele.}
-
-% Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
-\paragraph*{S1 Fig.}
-\label{fig:positionOverdominance}
-{\bf With overdominance, loci near to the ancestral sex-determining locus ($r\approx0$) can favour neo-W alleles that are less tightly linked ($R>r$).} 
-In panels A and B, the $a$ allele is favoured in females ($w_{aa}^\female=1.05$, $w_{Aa}^\Hermaphrodite=1$, $w_{AA}^\female=0.85$) and selection in males is overdominant ($w_{aa}^\male=w_{AA}^\male=0.75$).
-In panels C and D, selection in males and females is overdominant ($w_{aa}^\female=w_{AA}^\female=0.6$, $w_{aa}^\male=0.5$, $w_{AA}^\male=0.7$, $w_{Aa}^\Hermaphrodite=1$).
-There is no haploid selection $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
-These parameters are marked by daggers in Fig \ref{fig:regionplots}B and C, which show that neo-W invasion is expected for any $R$ ($\Lambda_{W'A}^{(XY)},\Lambda_{W'a}^{(XY)}>1$) if the $a$ allele is nearly fixed on the Y (black lines in this figure; not stable for $r>>0$).
-Equilibria where the $A$ allele is more common among Y-bearing male gametes can also be stable and allow neo-W invasion for these parameters (blue lines). 
-%The weak selection approximation holds when all recombination rates are large relative to selection (around 0 in panels A and C), in which case, in the absence of haploid selection, neo-W alleles should spread if and only if they are more tightly linked to the selected locus (positive invasion fitness if and only if the selected locus is in the grey region).
-%However, when recombination rates are small (panels B and D and when the selected locus is near the SDRs in all panels), this weak selection prediction can break down.
-
-\paragraph*{S2 Fig.}
-\label{fig:temporalOverdominance}
-{\bf Following invasion by a neo-W allele, there can be a complete transition to a new sex-determining system, maintenance of both ancestral-XY and neo-ZW sex determining systems, or loss of the new sex-determining allele.}
-Here, we plot the frequency of the neo-W allele among female gametes.
-%; as the neo-W reaches frequency $0.5$, polymorphism at the ancestral XY locus is lost with Y becoming fixed such that sex is determined only be the ZW allele carried by a female gamete. 
-Panels A, C and D show cases where a steady state is reached with the neo-W at a frequency below $0.5$, in which case ancestral-X and Y alleles also both segregate. 
-In all cases, we assume that the $a$ allele is initially more common than the $A$ allele on the Y background (Y-$a$ is fixed when $r=0$). 
-When $r>0$ (panels B and D), Y-$A$ haplotypes created by recombination can become more common than Y-$a$ haplotypes as the neo-W spreads.
-In B, this leads to loss of the neo-W and the system goes to an equilibrium with X-$a$ and Y-$A$ haplotypes fixed (equilibrium $A'$), such that all females have the high fitness genotype $aa$ and all males are $Aa$.
-For the parameters in B, neo-W alleles have negative invasion fitness when the Y-$A$ haplotype is ancestrally more common than Y-$a$ (compare blue to black curves in \nameref{fig:positionOverdominance}A and  \nameref{fig:positionOverdominance}B near the ancestral sex-determining locus).
-In contrast, the neo-W is not lost in panel D as it is favoured regardless of whether Y-$A$ or Y-$a$ haplotypes predominate (again, compare blue to black curves in \nameref{fig:positionOverdominance}C and  \nameref{fig:positionOverdominance}D).
-%Fitness parameters are the same as in \nameref{fig:positionOverdominance}; in panels A and B the $a$ allele is favoured in females ($w_{aa}^\female=1.05$, $w_{Aa}^\Hermaphrodite=1$, $w_{AA}^\female=0.85$) while there is overdominance in males ($w_{aa}^\male=w_{AA}^\male=0.75$) and in panels C and D, there is overdominance in both sexes ($w_{aa}^\female=w_{AA}^\female=0.6$, $w_{aa}^\male=0.5$, $w_{AA}^\male=0.7$, $w_{Aa}^\Hermaphrodite=1$).
-%These parameters are marked by a dagger in Fig \ref{fig:regionplots}. 
-%Here, there is no haploid selection $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
-
-\paragraph*{S3 Fig.}
-\label{fig:SexAntagTighterMaleDrive}
-{\bf  When there is sexually-antagonistic selection and haploid selection, a neo-W allele may invade for any $R$.}
-Panel A shows that the invasion fitness of a neo-W is positive, even when $r<R$ (unshaded region).
-In panel B, we vary the recombination rate between the neo-W and the selected locus ($R$) for a fixed recombination rate between the ancestral sex-determining locus and the selected locus ($r=0.005$).
-Coloured markers show recombination rates for which the temporal dynamics of neo-W invasion are plotted in panel C (black $R=0.001$, red $R=0.02$, blue $R=0.1$, green $R=0.5$). 
-The diploid selection parameters used in this plot are the same as in Fig \ref{fig:SexAntagTighter}. 
-There is also meiotic drive in males favouring $a$ ($\alpha_{\Delta}^\male=-0.08$), this full set of parameters is marked by an asterisk in \nameref{fig:regionMaleDrive}A.
-When $R=0.5$ (green curve), the neo-W does not reach fixation and X, Y, Z, and W alleles are all maintained in the population, see \nameref{fig:freqAll}C.
-
-\paragraph*{S4 Fig.}
-\label{fig:regionMaleDrive}
-{\bf Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is male meiotic drive at a locus that is tightly linked to the ancestral XY locus ($r=0$).}
-This figure is equivalent to Fig \ref{fig:regionplots} but with meiotic drive in males.
-%We vary the fitness of male homozygotes relative to heterozygotes ($w_{Aa}^\Hermaphrodite=1$) and only consider stable equilibria at which both $\mathbf{A}$ locus allele are maintained and the $a$ allele is initially fixed on the Y, region outlined.
-In panels A-C, meiotic drive in males favours the $a$ allele ($\alpha_{\Delta}^\male=-0.16$), creating male-biased sex ratios and generally increasing $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$.
-By contrast, $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$ tend to be reduced when meiotic drive in males favours the $A$ allele ($\alpha_{\Delta}^\male=0.16$), panels D-F. 
-%We consider three forms of selection in females: directional selection in favour of the $A$ allele (panels A and D, $w_{aa}^\female=0.85$, $w_{AA}^\female=1.05$), direction selection in favour of the $a$ allele (panels B and E, $w_{aa}^\female=1.05$, $w_{AA}^\female=0.85$), and overdominance (panels C and F, $w_{aa}^\female=w_{AA}^\female=0.6$).
-
-\paragraph*{S5 Fig.}
-\label{fig:regionMaleGS}
-{\bf Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is male gametic competition at a locus that is tightly linked to the ancestral XY locus ($r=0$).}
-This figure is equivalent to Fig \ref{fig:regionplots} but with gametic competition in males.
-%Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in \nameref{fig:regionMaleDrive}. 
-The $a$ allele is favoured during male gametic competition in Panels A-C ($w_{a}^\male=1.16$, $w_{A}^\male=1$), which creates male biased sex ratios and increases $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$.
-By contrast, $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$ tend to be reduced when the $A$ allele is favoured during male gametic competition, panels D-F.
-Compared to the meiotic drive parameters in \nameref{fig:regionMaleDrive}, the effect of these male gametic competition parameters on the sex ratio is smaller. 
-For example, in \nameref{fig:regionMaleDrive}A-C, the ancestral sex ratio is $\alpha^\male=0.58$ at equilibrium (B) and in panels A-C of this plot, the ancestral sex ratio is $w_{a}^\male/(w_{A}^\male+w_{a}^\male)=0.537$ at equilibrium (B).
-
-\paragraph*{S6 Fig.}
-\label{fig:regionFemaleDrive}
-{\bf Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is female meiotic drive at a locus that is tightly linked to the ancestral XY locus ($r=0$).}
-This figure is equivalent to Fig \ref{fig:regionplots} but with meiotic drive in females.
-%Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in \nameref{fig:regionMaleDrive} and \nameref{fig:regionMaleGS}. 
-The $a$ allele is favoured by meiotic drive in females in Panels A-C ($\alpha_{\Delta}^\female=-0.16$), which increases $\Lambda_{W'a}^{(XY)}$ and decreases $\Lambda_{W'A}^{(XY)}$. 
-Female meiotic drive in favour of the $A$ allele (panels D-F, $\alpha_{\Delta}^\female=-0.16$) has the opposite effect.
-
-\paragraph*{S7 Fig.}
-\label{fig:regionFemaleGS}
-{\bf Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is female gametic competition at a locus that is tightly linked to the ancestral XY locus ($r=0$).}
-This figure is equivalent to Fig \ref{fig:regionplots} but with gametic competition in females.
-%Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in \nameref{fig:regionMaleDrive}, \nameref{fig:regionMaleGS}, and \nameref{fig:regionFemaleDrive}. 
-The $a$ allele is favoured during female gametic competition in females in Panels A-C ($w_{a}^\female=1.16$, $w_{A}^\female=1$), which increases $\Lambda_{W'a}^{(XY)}$ and decreases $\Lambda_{W'A}^{(XY)}$.
-The $A$ allele is favoured during gametic competition in panels D-F ($w_{a}^\female=1$, $w_{A}^\female=1.16$), giving the opposite effect on $\Lambda_{W'a}^{(XY)}$ and $\Lambda_{W'A}^{(XY)}$.
-
-\paragraph*{S8 Fig.}
-\label{fig:regionPloidAntag}
-{\bf Ploidally-antagonistic selection can drive the spread of neo-W alleles. }
-A-D show when each of the neo-W haplotypes invades an internally stable equilibrium with $a$ fixed on the Y (found by setting $r=0$).
-The y-axis shows directional selection in diploids of both sexes, $s^\female=s^\male$, and the x-axes show sex-specific drive, $\alpha_\Delta^\Hermaphrodite$, or haploid competition, $t^\Hermaphrodite$.
-The top left and bottom right quadrants therefore imply ploidally-antagonistic selection (and these are the only places where neo-W haplotypes can invade).
-Dominance is equal in both sexes, $h^\female=h^\male=3/4$. 
-E-F show the temporal dynamics of neo-W frequency in females with parameters given by the asterisks in the corresponding A-D plot, with $r=1/200$, for four different $R$.
-Black $R=1/1000$, Red $R=2/100$, Blue $R=1/10$, Green $R=1/2$.
-
-\paragraph*{S9 Fig.}
-\label{fig:freqAll}
-{\bf Pseudo-fixation of neo-W or maintenance of multiple sex-determining alleles. }
-The curves show the frequencies of the neo-W (red), ancestral Y (blue), and $A$ allele (black) among female gametes (solid curves) and among male gametes (dashed curves). 
-In panel A, there is a complete transition from XY sex determination (XX-ZZ females and XY-ZZ males) to ZW sex determination (YY-ZW females and YY-ZZ males).  
-In panels B and C a polymorphism is maintained at both the ancestral XY locus and the new ZW locus, such that there are males with genotypes XY-ZZ and YY-ZZ and females with genotypes XX-ZZ, XX-ZW, XY-ZW, and YY-ZW.
-In panel A, selection is ploidally-antagonistic with drive in males (parameters as in the green curve in Fig \ref{fig:SexRatioBad}B).
-In panel B, there is overdominance in both sexes and no haploid selection (parameters as in the green curve in \nameref{fig:temporalOverdominance}C).
-In panel C, there is sexually-antagonistic selection in diploids with drive in males (parameters as in the green curve in \nameref{fig:regionMaleDrive}C).
-In all cases, the initial equilibrium frequency has $a$ near fixation on the Y.
-
-%\section*{Acknowledgments}
-%This project was supported by the Natural Sciences and Engineering Research Council of Canada (CGS-D 6564 to MMO; RGPIN-2016-03711 to SPO).
-
-\nolinenumbers
-
-% Either type in your references using
-% \begin{thebibliography}{}
-% \bibitem{}
-% Text
-% \end{thebibliography}
-%
-% or
-%
-% Compile your BiBTeX database using our plos2015.bst
-% style file and paste the contents of your .bbl file
-% here. See http://journals.plos.org/plosone/s/latex for 
-% step-by-step instructions.
-% 
-\bibliography{sex_chromosomes.bib}
-
-\newpage
-
-\setcounter{equation}{0}
-\renewcommand{\theequation}{S1.\arabic{equation}}
-
-\section*{S1 Appendix}
-
-\subsection*{Recursion equations}
-
-In each generation we census the genotype frequencies in male and female gametes/gametophytes (hereafter, gametes) between meiosis (and any meiotic drive) and gametic competition. 
-At this stage we denote the frequencies of X- and Y-bearing gametes from males and females $x_{i}^{\Hermaphrodite}$ and $y_{i}^{\Hermaphrodite}$.
-The superscript $\Hermaphrodite \in \{\male,\female\}$ specifies the sex of the diploid that the gamete came from. 
-The subscript $i\in\{1,2,3,4\}$ specifies the genotype at the selected locus $\mathbf{A}$ and at the novel sex-determining locus $\mathbf{M}$, where $1=AM$, $2=aM$, $3=Am$, and $4=am$. 
-The gamete frequencies from each sex sum to one, $\sum_{i}x_{i}^{\Hermaphrodite}+y_{i}^{\Hermaphrodite}=1$.
-
-Competition then occurs among gametes of the same sex (e.g., among eggs and among sperm separately) according to the genotype at the $\mathbf{A}$ locus ($w_{1}^\Hermaphrodite=w_{3}^\Hermaphrodite=w_{A}^\Hermaphrodite$, $w_{2}^\Hermaphrodite=w_{4}^\Hermaphrodite=w_{a}^\Hermaphrodite$, see Table \ref{tab:fitnesstable}).
-The genotype frequencies after gametic competition are $x_{i}^{\Hermaphrodite,s}= w_{i}^{\Hermaphrodite}x_{i}^{\Hermaphrodite}/\bar{w}_{H}^{\Hermaphrodite}$ and $y_{i}^{\Hermaphrodite,s}= w_{i}^{\Hermaphrodite}y_{i}^{\Hermaphrodite}/\bar{w}_{H}^{\Hermaphrodite}$, where $\bar{w}_{H}^{\Hermaphrodite}=\sum_{i} w_{i}^{\Hermaphrodite}x_{i}^{\Hermaphrodite}+w_{i}^{\Hermaphrodite}y_{i}^{\Hermaphrodite}$ is the mean fitness of male ($\Hermaphrodite=\male$) or female ($\Hermaphrodite=\female$) gametes.
-
-Random mating then occurs between gametes to produce diploid zygotes.
-%To shorten notation we now use index $i$ (and $j$) to denote the alleles at both the $\mathbf{A}$ and $\mathbf{M}$ loci and label $MA=1$, $Ma=2$, $mA=3$, and $ma=4$, such that $i,j\in\{1,2,3,4\}$.
-The frequencies of XX zygotes are then denoted as $xx_{ij}$, XY zygotes as $xy_{ij}$, and YY zygotes as $yy_{ij}$, where $\mathbf{A}$ and $\mathbf{M}$ locus genotypes are given by $i,j\in\{1,2,3,4\}$, as above.
-In XY zygotes, the haplotype inherited from an X-bearing gamete is given by $i$ and the haplotype from a Y-bearing gamete is given by $j$. 
-In XX and YY zygotes, individuals with diploid genotype $ij$ are equivalent to those with diploid genotype $ji$; for simplicity, we use $xx_{ij}$ and $yy_{ij}$ with $i\neq j$ to denote the average of these frequencies, $xx_{ij}=(x_{i}^{\female,s}x_{j}^{\male,s}+x_{j}^{\female,s}x_{i}^{\male,s})/2$ and $yy_{ij}=(y_{i}^{\female,s}y_{j}^{\male,s}+y_{j}^{\female,s}y_{i}^{\male,s})/2$.
-
-Denoting the $\mathbf{M}$ locus genotype by $b \in \{MM, Mm, mm\}$ and the $\mathbf{X}$ locus genotype by $c \in \{XX, XY, YY\}$, zygotes develop as females with probability $k_{bc}$. 
-Therefore, the frequencies of XX females are given by $xx_{ij}^{\female}=k_{bc}xx_{ij}$, XY females are given by $xy_{ij}^{\female}=k_{bc}xy_{ij}$, and YY females are given by $yy_{ij}^{\female}=k_{bc}yy_{ij}$.
-Similarly, XX male frequencies are $xx_{ij}^{\male}=(1-k_{bc})xx_{ij}$, XY male frequencies are $xy_{ij}^{\male}=(1-k_{bc})xy_{ij}$, and YY males frequencies are $yy_{ij}^{\male}=(1-k_{bc})yy_{ij}$.
-This notation allows both the ancestral and novel sex-determining regions to determine zygotic sex according to an XY system, a ZW system, or an environmental sex-determining system. 
-In addition, we can consider any epistatic dominance relationship between the two sex-determining loci. 
-Here, we assume that the ancestral sex-determining system ($\mathbf{X}$ locus) is XY ($k_{MMXX}=1$ and $k_{MMXY}=k_{MMYY}=0$) or ZW ($k_{MMZZ}=0$ and $k_{MMZW}=k_{MMWW}=1$) and epistatically recessive to a dominant novel sex-determining locus, $\mathbf{M}$ ($k_{Mmc}=k_{mmc}=k$).
-
-Selection among diploids then occurs according to the diploid genotype at the $\mathbf{A}$ locus, $l \in \{AA, Aa, aa\}$, for an individual of type $ij$ (see Table \ref{tab:fitnesstable}). 
-The diploid frequencies after selection in sex $\Hermaphrodite$ are given by $xx_{ij}^{\Hermaphrodite,s}=w_{l}^{\Hermaphrodite} xx_{ij}/\bar{w}^{\Hermaphrodite}_{D}$, $xy_{ij}^{\Hermaphrodite,s}=w_{l}^{\Hermaphrodite} xy_{ij}/\bar{w}^{\Hermaphrodite}_{D}$, and $yy_{ij}^{\Hermaphrodite,s}=w_{l}^{\Hermaphrodite} yy_{ij}/\bar{w}^{\Hermaphrodite}_{D}$, where $\bar{w}^{\Hermaphrodite}_{D}= \sum_{i=1}^{4}\sum_{j=1}^{4}w_{l}^{\Hermaphrodite}xx_{ij}+w_{l}^{\Hermaphrodite}xy_{ij}+w_{l}^{\Hermaphrodite}yy_{ij}$ is the mean fitness of diploids of sex $\Hermaphrodite$.
-
-Finally, these diploids undergo meiosis to produce the next generation of gametes. 
-Recombination and sex-specific meiotic drive occur during meiosis.
-%We can also assume that recombination is sex specific and/or affected by the M locus - but generally we don't so I just describe $R=R_{f}=R, r_{MM,d}=r_{Mm,d}=r_{mm,d}=r, \chi_{m}=\chi_{f}=\chi$.
-Here, we allow any relative locations for the $\mathbf{X}$, $\mathbf{A}$, and $\mathbf{M}$ loci by using three parameters to describe the recombination rates between them. 
-$R$ is the recombination rate between the $\mathbf{A}$ and $\mathbf{M}$ loci, $\rho$ is the recombination rate between the $\mathbf{M}$ and $\mathbf{X}$ loci, and $r$ is the recombination rate between the $\mathbf{A}$ and $\mathbf{X}$ loci (Fig \ref{fig:model_outline}).
-\nameref{tab:chisubstitutions} shows replacements that can be made for each possible ordering of the loci assuming that there is no cross-over interference.
-During meiosis in sex $\Hermaphrodite$, meiotic drive occurs such that, in $Aa$ heterozygotes, a fraction $\alpha^{\Hermaphrodite}$ of gametes produced carry the $A$ allele and $(1-\alpha^\Hermaphrodite)$ carry the $a$ allele.
-
-Among gametes from sex $\Hermaphrodite$, the frequencies of haplotypes (before gametic competition) in the next generation are given by
-
-\begingroup
-\allowdisplaybreaks
-\begin{subequations}
-\begin{align}
-%
-\begin{split}
-x_{1}^{{\Hermaphrodite}'}=&xx_{11}^{\Hermaphrodite,s}+xx_{13}^{\Hermaphrodite,s}/2+(xx_{12}^{\Hermaphrodite,s}+xx_{14}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(xx_{14}^{\Hermaphrodite,s}-xx_{23}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&+(xy_{11}^{\Hermaphrodite,s}+xy_{13}^{\Hermaphrodite,s})/2+(xy_{12}^{\Hermaphrodite,s}+xy_{14}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&- r(xy_{12}^{\Hermaphrodite,s}-xy_{21}^{\Hermaphrodite,s})\alpha^\Hermaphrodite - \rho(xy_{13}^{\Hermaphrodite,s}-xy_{31}^{\Hermaphrodite,s})/2\\
-&+\big{[}-(R+r+\rho)xy_{14}^{\Hermaphrodite,s} +(R+\rho-r)xy_{41}^{\Hermaphrodite,s}\\
-&+(R+r-\rho) xy_{23}^{\Hermaphrodite,s}+(R+\rho-r)xy_{32}^{\Hermaphrodite,s}\big{]}\alpha^\Hermaphrodite/2
-\end{split}
-\\
-%
-\begin{split}
-x_{2}^{{\Hermaphrodite}'}=&xx_{22}^{\Hermaphrodite,s}+xx_{24}^{\Hermaphrodite,s}/2+(xx_{12}^{\Hermaphrodite,s}+xx_{23}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(xx_{23}^{\Hermaphrodite,s}-xx_{14}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&(xy_{22}^{\Hermaphrodite,s}+xy_{24}^{\Hermaphrodite,s})/2+(xy_{21}^{\Hermaphrodite,s}+xy_{23}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite)\\
-&- r(xy_{21}^{\Hermaphrodite,s}-xy_{12}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite) - \rho(xy_{24}^{\Hermaphrodite,s}-xy_{42}^{\Hermaphrodite,s})/2\\
-&+\big{[}-(R+r+\rho)xy_{23}^{\Hermaphrodite,s}+(R+\rho-r)xy_{32}^{\Hermaphrodite,s}\\
-&+(R+r-\rho) xy_{14}^{\Hermaphrodite,s}+(R+\rho-r)xy_{41}^{\Hermaphrodite,s}\big{]}(1-\alpha^\Hermaphrodite)/2
-\end{split}
-\\
-%
-\begin{split}
-x_{3}^{{\Hermaphrodite}'}=&xx_{33}^{\Hermaphrodite,s}+xx_{13}^{\Hermaphrodite,s}/2+(xx_{23}^{\Hermaphrodite,s}+xx_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(xx_{23}^{\Hermaphrodite,s}-xx_{14}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&(xy_{33}^{\Hermaphrodite,s}+xy_{31}^{\Hermaphrodite,s})/2+(xy_{32}^{\Hermaphrodite,s}+xy_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&- r(xy_{34}^{\Hermaphrodite,s}-xy_{43}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite - \rho(xy_{31}^{\Hermaphrodite,s}-xy_{13}^{\Hermaphrodite,s})/2\\
-&+\big{[}-(R+r+\rho)xy_{32}^{\Hermaphrodite,s} +(R+\rho-r)xy_{23}^{\Hermaphrodite,s}\\
-&+(R+r-\rho) xy_{41}^{\Hermaphrodite,s}+(R+\rho-r)xy_{14}^{\Hermaphrodite,s}\big{]} \alpha^\Hermaphrodite/2
-\end{split}
-\\
-%
-\begin{split}
-x_{4}^{{\Hermaphrodite}'}=&xx_{44}^{\Hermaphrodite,s}+xx_{34}^{\Hermaphrodite,s}/2+(xx_{14}^{\Hermaphrodite,s}+xx_{24}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(xx_{14}^{\Hermaphrodite,s}-xx_{23}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&(xy_{44}^{\Hermaphrodite,s}+xy_{42}^{\Hermaphrodite,s})/2+(xy_{41}^{\Hermaphrodite,s}+xy_{43}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite)\\
-&- r(xy_{43}^{\Hermaphrodite,s}-xy_{34}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite) - \rho(xy_{42}^{\Hermaphrodite,s}-xy_{24}^{\Hermaphrodite,s})/2\\
-&+\big{[}-(R+r+\rho)xy_{41}^{\Hermaphrodite,s}+(R+\rho-r)xy_{14}^{\Hermaphrodite,s}\\
-&+(R+r-\rho) xy_{32}^{\Hermaphrodite,s}+(R+\rho-r)xy_{23}^{\Hermaphrodite,s}\big{]}(1-\alpha^\Hermaphrodite)/2
-\end{split}
-\\
-\begin{split}
-y_{1}^{{\Hermaphrodite}'}=&yy_{11}^{\Hermaphrodite,s}+yy_{13}^{\Hermaphrodite,s}/2+(yy_{12}^{\Hermaphrodite,s}+yy_{14}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(yy_{14}^{\Hermaphrodite,s}-yy_{23}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&(xy_{11}^{\Hermaphrodite,s}+xy_{31}^{\Hermaphrodite,s})/2+(xy_{21}^{\Hermaphrodite,s}+xy_{41}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&- r(xy_{21}^{\Hermaphrodite,s}-xy_{12}^{\Hermaphrodite,s})\alpha^\Hermaphrodite - \rho(xy_{31}^{\Hermaphrodite,s}-xy_{13}^{\Hermaphrodite,s})/2\\
-&+\big{[} - (R+r+\rho)xy_{41}^{\Hermaphrodite,s} + (R+\rho-r)xy_{14}^{\Hermaphrodite,s}\\
-& + (R+r-\rho)xy_{32}^{\Hermaphrodite,s} + (R+\rho-r) xy_{23}^{\Hermaphrodite,s}\big{]}\alpha^\Hermaphrodite/2
-\end{split}
-\\
-%
-\begin{split}
-y_{2}^{{\Hermaphrodite}'}=&yy_{22}^{\Hermaphrodite,s}+yy_{24}^{\Hermaphrodite,s}/2+(yy_{12}^{\Hermaphrodite,s}+yy_{23}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(yy_{23}^{\Hermaphrodite,s}-yy_{14}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&(xy_{22}^{\Hermaphrodite,s}+xy_{42}^{\Hermaphrodite,s})/2+(xy_{12}^{\Hermaphrodite,s}+xy_{32}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite)\\
-&- r(xy_{12}^{\Hermaphrodite,s}-xy_{21}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite) - \rho(xy_{42}^{\Hermaphrodite,s}-xy_{24}^{\Hermaphrodite,s})/2\\
-&+\big{[}-(R+r+\rho)xy_{32}^{\Hermaphrodite,s} +(R+\rho-r) xy_{23}^{\Hermaphrodite,s}\\
-&+(R+r-\rho)xy_{41}^{\Hermaphrodite,s}+(R+\rho-r)xy_{14}^{\Hermaphrodite,s}\big{]}(1-\alpha^\Hermaphrodite)/2
-\end{split}
-\\
-%
-\begin{split}
-y_{3}^{{\Hermaphrodite}'}=&yy_{33}^{\Hermaphrodite,s}+yy_{13}^{\Hermaphrodite,s}/2+(yy_{23}^{\Hermaphrodite,s}+yy_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(yy_{23}^{\Hermaphrodite,s}-yy_{14}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&(xy_{33}^{\Hermaphrodite,s}+xy_{13}^{\Hermaphrodite,s})/2+(xy_{23}^{\Hermaphrodite,s}+xy_{43}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&- r(xy_{43}^{\Hermaphrodite,s}-xy_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite - \rho(xy_{13}^{\Hermaphrodite,s}-xy_{31}^{\Hermaphrodite,s})/2\\
-&+\big{[}-(R+r+\rho)xy_{23}^{\Hermaphrodite,s} +(R+\rho-r)xy_{32}^{\Hermaphrodite,s}\\
-&+(R+r-\rho) xy_{14}^{\Hermaphrodite,s} + (R+\rho-r) xy_{41}^{\Hermaphrodite,s}\big{]}\alpha^\Hermaphrodite/2
-\end{split}
-\\
-%
-\begin{split}
-y_{4}^{{\Hermaphrodite}'}=&yy_{44}^{\Hermaphrodite,s}+yy_{34}^{\Hermaphrodite,s}/2+(yy_{14}^{\Hermaphrodite,s}+yy_{24}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(yy_{14}^{\Hermaphrodite,s}-yy_{23}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&(xy_{44}^{\Hermaphrodite,s}+xy_{24}^{\Hermaphrodite,s})/2+(xy_{14}^{\Hermaphrodite,s}+xy_{34}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite)\\
-&- r(xy_{34}^{\Hermaphrodite,s}-xy_{43}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite) - \rho(xy_{24}^{\Hermaphrodite,s}-xy_{42}^{\Hermaphrodite,s})/2\\
-&+\big{[}-(R+r+\rho) xy_{14}^{\Hermaphrodite,s} + (R+\rho-r)xy_{41}^{\Hermaphrodite,s}\\
-&+(R+r-\rho) xy_{23}^{\Hermaphrodite,s} + (R+\rho-r) xy_{32}^{\Hermaphrodite,s}\big{]}(1-\alpha^\Hermaphrodite)/2.
-\end{split}
-\end{align}
-\label{eq:recursions}
-\end{subequations}
-
-\endgroup
-
-\noindent
-The full system is therefore described by 16 recurrence equations (three diallelic loci in two sexes, $2^3 \times 2 = 16$). 
-However, not all diploid types are produced under certain sex-determining systems. 
-For example, with the $M$ allele fixed and an ancestral XY sex-determining system, there are XX females and XY males ($x_{3}^\Hermaphrodite=x_{4}^\Hermaphrodite=y_{3}^\male=y_{4}^\male=y_{i}^\female=0,\;\forall\; i$).
-%($xx_{11}^{\male}=xx_{12}^{\male}=xx_{22}^\male=xy_{11}^{\female}=xy_{12}^{\female}=xy_{21}^{\female}=xy_{22}^\female=yy_{11}^{\female}=yy_{12}^{\female}=yy_{22}^\female=0$). 
-In this case, the system only involves six recursion equations, %because there is only one $\mathbf{M}$ locus allele and no Y-bearing female gametes. 
-which we assume below to calculate the equilibria.
-
-\newpage
-
-\setcounter{equation}{0}
-\renewcommand{\theequation}{S2.\arabic{equation}}
-
-\section*{S2 Appendix}
-
-\subsection*{Resident equilibria and stability}
-
-In the resident population (allele $M$ fixed), we follow the frequency of $A$ in X-bearing female gametes, $p^\female_X$, and X-bearing male gametes, $p^\male_X$, and Y-bearing male gametes, $p^\male_Y$.
-We also track the total frequency of Y among male gametes, $q$, which may deviate from $1/2$ due to meiotic drive in males. 
-These four variables determine the frequencies of the six resident gamete types, which sum to one in each sex: $x_{1}^{\female}=\hat{p}_X^\female$, $x_{2}^{\female}=1-\hat{p}_X^\female$, $x_{1}^{\male}=(1-q)\hat{p}_X^\male$, $x_{2}^{\male}=(1-q)(1-\hat{p}_X^\male)$, $y_{1}^{\male}=q \hat{p}_Y^\male$, and $y_{2}^{\male}=q(1-\hat{p}_Y^\male)$.
-Mean fitnesses in the resident population are given in \nameref{tab:meanfitnesses}.
-
-Various forms of selection can maintain a polymorphism at the $\mathbf{A}$ locus, including sexually antagonistic selection, overdominance, conflicts between diploid selection and selection upon haploid genotypes (ploidally-antagonsitic selection,~\cite{Immler:2012tl}), or a combination of these selective regimes (see below).
-
-In particular special cases, e.g., no sex-differences in selection or meiotic drive ($s^\male=s^\female$, $h^\male=h^\female$, and $\alpha^\male=\alpha^\female=1/2$), the equilibrium allele frequency and stability can be calculated analytically without assuming anything about the relative strengths of selection and recombination.
-However, here, we focus on two regimes (tight linkage between $\mathbf{A}$ and $\mathbf{X}$ and weak selection) in order to make fewer assumptions about fitnesses.
-
-\subsubsection*{Tight linkage between $\mathbf{X}$ and $\mathbf{A}$ loci}
-
-We first calculate the equilibria in the ancestral population when the recombination rate between the $\mathbf{X}$ and $\mathbf{A}$ loci is small ($r$ of order $\epsilon$). 
-Selection at the $\mathbf{A}$ locus will not affect evolution at the novel sex-determining locus, $\mathbf{M}$, if one allele is fixed on all backgrounds. 
-We therefore focus on the five equilibria that maintain both $A$ and $a$ alleles, four of which are given to leading order by:
-
-\begin{subequations}\label{eq:tightequil}
-\begin{align}
-(A)\ \ \ &\hat{p}_{Y}^{\male}=0,
-\ \hat{q}=\frac{1}{2}\left(1 - \alpha_\Delta^\male \frac{ w_{Aa}^{\male} \phi}{w_{Aa}^{\male} \phi+ w_{aa}^{\male} \psi}\right),\\
-&\hat{p}_{X}^{\female}=\frac{w_{a}^{\female} \phi}{w_{a}^{\female} \phi+ w_{A}^{\female} \psi},
-\ \hat{p}_{X}^{\male}=\frac{(1+\alpha_\Delta^\male)w_{Aa}^{\male} \phi}{(1+\alpha_\Delta^\male)w_{Aa}^{\male} \phi +w_{aa}^{\male} \psi} \nonumber \\
-(A')\ \ \ &\hat{p}_{Y}^{\male}=1,
-\ \hat{q}=\frac{1}{2}\left(1 + \alpha_\Delta^\male \frac{w_{Aa}^{\male} \phi'}{w_{Aa}^{\male} \phi' + w_{AA}^{\male} \psi'}\right),\\
-&\hat{p}_{X}^{\female}=1-\frac{w_{A}^{\female} \phi'}{w_{A}^{\female} \phi'+ w_{a}^{\female} \psi'},
-\ \hat{p}_{X}^{\male}=1-\frac{(1-\alpha_\Delta^\male)w_{Aa}^{\male} \phi'}{(1-\alpha_\Delta^\male)w_{Aa}^{\male} \phi'+w_{AA}^{\male} \psi'} \nonumber \\
-(B)\ \ \ &\hat{p}_{Y}^{\male}=0,\ \hat{p}_{X}^{\female}=1,\ \hat{p}_{X}^{\male}=1, \ \hat{q}=(1 -\alpha^\male_\Delta)/2\\
-(B')\ \ \ &\hat{p}_{Y}^{\male}=1,\ \hat{p}_{X}^{\female}=0,\ \hat{p}_{X}^{\male}=0, \ \hat{q}=(1+\alpha^\male_\Delta)/2
-\end{align}
-\end{subequations}
-\begin{equation*}
-\begin{split}
-\phi=&(1+\alpha^\female_\Delta) w_{A}^{\female} w_{Aa}^{\female} \left[ w_{a}^{\male} w_{aa}^{\male} + (1+\alpha_\Delta^\male) w_{A}^{\male} w_{Aa}^{\male} \right]/2 - w_{a}^{\male} w_{a}^{\female} w_{aa}^{\male} w_{aa}^{\female} \\
-\psi=&(1-\alpha^\female_\Delta) w_{a}^{\female} w_{Aa}^{\female} \left[ w_{a}^{\male} w_{aa}^{\male} + (1+\alpha_\Delta^\male) w_{A}^{\male} w_{Aa}^{\male}\right]/2 - (1+\alpha_\Delta^\male) w_{A}^{\male} w_{A}^{\female} w_{Aa}^{\male} w_{AA}^{\female}\\
-\phi'=&(1-\alpha^\female_\Delta) w_{a}^{\female} w_{Aa}^{\female} \left[ w_{A}^{\male} w_{AA}^{\male} + (1-\alpha_\Delta^\male) w_{a}^{\male} w_{Aa}^{\male} \right]/2 - w_{A}^{\male} w_{A}^{\female} w_{AA}^{\male} w_{AA}^{\female}\\
-\psi'=&(1+\alpha^\female_\Delta) w_{A}^{\female} w_{Aa}^{\female} \left[ w_{A}^{\male} w_{AA}^{\male} + (1-\alpha_\Delta^\male) w_{a}^{\male} w_{Aa}^{\male} \right]/2 - (1-\alpha_\Delta^\male) w_{a}^{\male} w_{a}^{\female} w_{Aa}^{\male} w_{aa}^{\female}.
-\end{split}
-\end{equation*}
-
-\noindent
-A fifth equilibrium $(C)$ also exists where $A$ is present at an intermediate frequency on the Y background ($0<\hat{p}_{Y}^{\male}<1$). 
-However, equilibrium $(C)$ is never locally stable when $r \approx 0$ and is therefore not considered further.
-Thus, the Y background can either be fixed for the $a$ allele (equilibria ($A$) and ($B$)) or the $A$ allele (equilibria ($A'$) and ($B'$)).
-The X background can then either be polymorphic (equilibria ($A$) and ($A'$)) or fixed for the alternative allele (equilibria ($B$) and ($B'$)).
-Since equilibria $(A)$ and $(B)$ are equivalent to equilibria $(A')$ and $(B')$ with the labelling of $A$ and $a$ alleles interchanged, we discuss only equilibria $(A)$ and $(B)$, in which the Y background is fixed for the $a$ allele.
-If there is no haploid selection ($\alpha^{\Hermaphrodite}_\Delta=0$, $w_{A}^{\Hermaphrodite}=w_{a}^{\Hermaphrodite}=1$), these equilibria are equivalent to those found by~\cite{Lloyd1977} and~\cite{Otto2014}.
-
-We next calculate when equilibria $(A)$ and $(B)$ are locally stable for $r=0$. 
-According to the `small parameter theory'~\cite{Karlin:1972ab,Karlin:1972dq}, these stability properties are unaffected by small amounts of recombination between the sex-determining locus and the $\mathbf{A}$ locus, although equilibrium frequencies may be slightly altered.
-For the $a$ allele to be stably fixed on the Y background we need $\bar{w}_{Ya}^{\male} > \bar{w}_{YA}^{\male}$ where $\bar{w}_{Ya}^{\male} = w_{a}^{\male} \big[\hat{p}_X^\female(1-\alpha^\male_\Delta) w_{A}^{\female} w_{Aa}^{\male} + (1-\hat{p}_X^\female)w_{a}^{\female} w_{aa}^{\male} \big]$ and $\bar{w}_{YA}^{\male} = w_{A}^{\male} \big[ \hat{p}_X^\female w_{A}^{\female} w_{AA}^{\male} + (1-\hat{p}_X^\female)(1+\alpha^\male_\Delta) w_{a}^{\female} w_{Aa}^{\male} \big]$.
-That is, Y-$a$ haplotypes must have higher fitness than Y-$A$ haplotypes.  
-Substituting in $\hat{p}_X^\female$ from Eq \eqref{eq:tightequil}, fixation of the $a$ allele on the Y background requires that $\gamma_{i}>0$ where $\gamma_{(A)}=w_{a}^{\male} \big[ (1-\alpha^\male_\Delta) w_{Aa}^{\male} \phi + w_{aa}^{\male} \psi \big]-w_{A}^{\male} \big[ w_{AA}^{\male} \phi + (1 + \alpha^{\male}_\Delta)w_{Aa}^{\male} \psi \big]$ for equilibrium $(A)$ and $\gamma_{(B)}=(1-\alpha^{\male}_\Delta)w_{a}^{\male}w_{Aa}^{\male}-w_{A}^{\male}w_{AA}^{\male}$ for equilibrium $(B)$.
-Stability of a polymorphism on the X background (equilibrium $(A)$) further requires that $\phi >0$ and $\psi >0$. 
-Fixation of the $a$ allele on the X background (equilibrium $(B)$) can be stable only if equilibrium $(A)$ is not, as it requires $\psi<0$.
-%and $2w_{A}^{\female}w_{AA}^{\female}>(1-\alpha_\Delta^{\female})w_{a}^{\female}w_{Aa}^{\female}$ or just $4w_{A}^{\female}w_{AA}^{\female}<(1-\alpha_\Delta^{\female})w_{a}^{\female}w_{Aa}^{\female}$ (which also prevents $\psi>0$).
-
-%\textcolor{red}{check last condition and the stability condition below are correct}
-%\textcolor{blue}{The last condition looks good to me, although in your Turnover-norec-MFS.nb you look at YA fixed, so you have to flip everything (so I made Turnover-norec-MFS-MMO.nb to do this).
-%The one issue I can find here is that you can also prevent $\Lambda>1$ when the slope and intercept of the quadratic at $\Lambda=1$ are negative (you only looked at both being positive).
-In this case we need $4w_{A}^{\female}w_{AA}^{\female}<(1-\alpha_\Delta^{\female})w_{a}^{\female}w_{Aa}^{\female}$, which also prevents $\psi>0$.
-%I've added this in.
-%It could also be the case that the slope and intercept are the same sign but the roots are imaginary - but this is never the case here.
-%Stability condition below looks good to me (from matt version of turnoverSOM-MIKE.nb).}
-
-\subsubsection*{Selection weak relative to recombination}
-
-Here, we assume that selection is weak relative to recombination ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon$). 
-The maintenance of a polymorphism at the $\mathbf{A}$ locus then requires that
-
-\begin{equation}
-\begin{split}
-0&< - \left[(1-h^\female)s^\female +(1-h^\male) s^\male + t^\female +t^\male + \alpha_{\Delta}^\female+\alpha_{\Delta}^\male\right]\\
-%
-\text{and }\quad 0&<h^\female s^\female +h^\male s^\male + t^\female +t^\male + \alpha_{\Delta}^\female+\alpha_{\Delta}^\male.
-\end{split}
-\end{equation}
-
-\noindent
-which indicates that a polymorphism can be maintained by various selective regimes.
-
-Given that a polymorphism is maintained at the $\mathbf{A}$ locus by weak selection, the frequencies of $A$ in each type of gamete are the same ($\hat{p}^\female_X=\hat{p}^\male_X=\hat{p}^\male_Y=\bar{p}$) and given, to leading order, by
-
-\begin{equation}
-\bar{p}=\frac{h^\female s^\female + h^\male s^\male +t^\female+t^\male+\alpha_{\Delta}^\female+\alpha_{\Delta}^\male}
-{(2h^\female-1)s^\female+(2h^\male-1)s^\male}
-+O(\epsilon)
-.
-\label{eq:pAve}
-\end{equation}
-
-\noindent
-Differences in frequency between gamete types are of $O(\epsilon)$:
-
-\begin{equation}
-\begin{split}
-\hat{p}^\male_X-\hat{p}^\female_X&=V_{A}\big{(}D^\male - D^\female +\alpha_{\Delta}^\male-\alpha_{\Delta}^\female \big{)}
-+O(\epsilon^2)\\
-%
-\hat{p}^\male_Y-\hat{p}^\female_X&=V_{A}\left[D^\male - D^\female+\alpha_{\Delta}^\male-\alpha_{\Delta}^\female+(1-2r)(t^\male-t^\female)\right]/2r
-+O(\epsilon^2)\\
-%
-\hat{p}^\male_Y-\hat{p}^\male_X&=V_{A}\left(D^\male - D^\female+\alpha_{\Delta}^\male-\alpha_{\Delta}^\female+t^\male-t^\female\right)(1-2r)/2r
-+O(\epsilon^2),
-\end{split}
-\label{eq:freq_diffs}
-\end{equation}
-
-\noindent
-where $V_{A}=\bar{p}(1-\bar{p})$ is the variance in the frequency of $A$ and $D^\Hermaphrodite=\big{[} \bar{p}s^\Hermaphrodite+(1-\bar{p})h^\Hermaphrodite s^\Hermaphrodite\big{]} -\big{[} \bar{p}h^\Hermaphrodite s^\Hermaphrodite+(1-\bar{p}) \big{]}$ corresponds to the difference in fitness between $A$ and $a$ alleles in diploids of sex $\Hermaphrodite \in \{\female,\male\}$.
-The frequency of Y-bearing male gametes depends upon the difference in the frequency of the $A$ allele between X- and Y-bearing male gametes and the strength of meiotic drive in favour of the $A$ allele in males, $q=1/2+\alpha_{\Delta}^\male(\hat{p}^\male_Y-\hat{p}^\male_X)/2+O(\epsilon^3)$.
-Without gametic competition or drive ($\alpha_{\Delta}^\Hermaphrodite=t^\Hermaphrodite=0$) our results reduce to those of~\cite{vanDoorn:2007eu}.
-
-\newpage
 
@@
 
+\bibliography{sex_chromosomes.bib}
+
 \end{document}

### 2018-02-07 LaTeX/main.tex
moved appendices out of main text but can crossref

--- 2018-02-06 LaTeX/Turnover_plos.tex
@@
 \newcommand{\ipsum}{{\bf IPSUM}}
+
+%reference equations in appendices
+\usepackage{xr}
+\externaldocument{S1Appendix}
+\externaldocument{S2Appendix}
+\externaldocument{S3Appendix}
 
@@
 
-\newpage
-
-\setcounter{equation}{0}
-\renewcommand{\theequation}{S1.\arabic{equation}}
-
-\section*{S1 Appendix}
-
-\subsection*{Recursion equations}
-
-In each generation we census the genotype frequencies in male and female gametes/gametophytes (hereafter, gametes) between meiosis (and any meiotic drive) and gametic competition. 
-At this stage we denote the frequencies of X- and Y-bearing gametes from males and females $x_{i}^{\Hermaphrodite}$ and $y_{i}^{\Hermaphrodite}$.
-The superscript $\Hermaphrodite \in \{\male,\female\}$ specifies the sex of the diploid that the gamete came from. 
-The subscript $i\in\{1,2,3,4\}$ specifies the genotype at the selected locus $\mathbf{A}$ and at the novel sex-determining locus $\mathbf{M}$, where $1=AM$, $2=aM$, $3=Am$, and $4=am$. 
-The gamete frequencies from each sex sum to one, $\sum_{i}x_{i}^{\Hermaphrodite}+y_{i}^{\Hermaphrodite}=1$.
-
-Competition then occurs among gametes of the same sex (e.g., among eggs and among sperm separately) according to the genotype at the $\mathbf{A}$ locus ($w_{1}^\Hermaphrodite=w_{3}^\Hermaphrodite=w_{A}^\Hermaphrodite$, $w_{2}^\Hermaphrodite=w_{4}^\Hermaphrodite=w_{a}^\Hermaphrodite$, see Table \ref{tab:fitnesstable}).
-The genotype frequencies after gametic competition are $x_{i}^{\Hermaphrodite,s}= w_{i}^{\Hermaphrodite}x_{i}^{\Hermaphrodite}/\bar{w}_{H}^{\Hermaphrodite}$ and $y_{i}^{\Hermaphrodite,s}= w_{i}^{\Hermaphrodite}y_{i}^{\Hermaphrodite}/\bar{w}_{H}^{\Hermaphrodite}$, where $\bar{w}_{H}^{\Hermaphrodite}=\sum_{i} w_{i}^{\Hermaphrodite}x_{i}^{\Hermaphrodite}+w_{i}^{\Hermaphrodite}y_{i}^{\Hermaphrodite}$ is the mean fitness of male ($\Hermaphrodite=\male$) or female ($\Hermaphrodite=\female$) gametes.
-
-Random mating then occurs between gametes to produce diploid zygotes.
-%To shorten notation we now use index $i$ (and $j$) to denote the alleles at both the $\mathbf{A}$ and $\mathbf{M}$ loci and label $MA=1$, $Ma=2$, $mA=3$, and $ma=4$, such that $i,j\in\{1,2,3,4\}$.
-The frequencies of XX zygotes are then denoted as $xx_{ij}$, XY zygotes as $xy_{ij}$, and YY zygotes as $yy_{ij}$, where $\mathbf{A}$ and $\mathbf{M}$ locus genotypes are given by $i,j\in\{1,2,3,4\}$, as above.
-In XY zygotes, the haplotype inherited from an X-bearing gamete is given by $i$ and the haplotype from a Y-bearing gamete is given by $j$. 
-In XX and YY zygotes, individuals with diploid genotype $ij$ are equivalent to those with diploid genotype $ji$; for simplicity, we use $xx_{ij}$ and $yy_{ij}$ with $i\neq j$ to denote the average of these frequencies, $xx_{ij}=(x_{i}^{\female,s}x_{j}^{\male,s}+x_{j}^{\female,s}x_{i}^{\male,s})/2$ and $yy_{ij}=(y_{i}^{\female,s}y_{j}^{\male,s}+y_{j}^{\female,s}y_{i}^{\male,s})/2$.
-
-Denoting the $\mathbf{M}$ locus genotype by $b \in \{MM, Mm, mm\}$ and the $\mathbf{X}$ locus genotype by $c \in \{XX, XY, YY\}$, zygotes develop as females with probability $k_{bc}$. 
-Therefore, the frequencies of XX females are given by $xx_{ij}^{\female}=k_{bc}xx_{ij}$, XY females are given by $xy_{ij}^{\female}=k_{bc}xy_{ij}$, and YY females are given by $yy_{ij}^{\female}=k_{bc}yy_{ij}$.
-Similarly, XX male frequencies are $xx_{ij}^{\male}=(1-k_{bc})xx_{ij}$, XY male frequencies are $xy_{ij}^{\male}=(1-k_{bc})xy_{ij}$, and YY males frequencies are $yy_{ij}^{\male}=(1-k_{bc})yy_{ij}$.
-This notation allows both the ancestral and novel sex-determining regions to determine zygotic sex according to an XY system, a ZW system, or an environmental sex-determining system. 
-In addition, we can consider any epistatic dominance relationship between the two sex-determining loci. 
-Here, we assume that the ancestral sex-determining system ($\mathbf{X}$ locus) is XY ($k_{MMXX}=1$ and $k_{MMXY}=k_{MMYY}=0$) or ZW ($k_{MMZZ}=0$ and $k_{MMZW}=k_{MMWW}=1$) and epistatically recessive to a dominant novel sex-determining locus, $\mathbf{M}$ ($k_{Mmc}=k_{mmc}=k$).
-
-Selection among diploids then occurs according to the diploid genotype at the $\mathbf{A}$ locus, $l \in \{AA, Aa, aa\}$, for an individual of type $ij$ (see Table \ref{tab:fitnesstable}). 
-The diploid frequencies after selection in sex $\Hermaphrodite$ are given by $xx_{ij}^{\Hermaphrodite,s}=w_{l}^{\Hermaphrodite} xx_{ij}/\bar{w}^{\Hermaphrodite}_{D}$, $xy_{ij}^{\Hermaphrodite,s}=w_{l}^{\Hermaphrodite} xy_{ij}/\bar{w}^{\Hermaphrodite}_{D}$, and $yy_{ij}^{\Hermaphrodite,s}=w_{l}^{\Hermaphrodite} yy_{ij}/\bar{w}^{\Hermaphrodite}_{D}$, where $\bar{w}^{\Hermaphrodite}_{D}= \sum_{i=1}^{4}\sum_{j=1}^{4}w_{l}^{\Hermaphrodite}xx_{ij}+w_{l}^{\Hermaphrodite}xy_{ij}+w_{l}^{\Hermaphrodite}yy_{ij}$ is the mean fitness of diploids of sex $\Hermaphrodite$.
-
-Finally, these diploids undergo meiosis to produce the next generation of gametes. 
-Recombination and sex-specific meiotic drive occur during meiosis.
-%We can also assume that recombination is sex specific and/or affected by the M locus - but generally we don't so I just describe $R=R_{f}=R, r_{MM,d}=r_{Mm,d}=r_{mm,d}=r, \chi_{m}=\chi_{f}=\chi$.
-Here, we allow any relative locations for the $\mathbf{X}$, $\mathbf{A}$, and $\mathbf{M}$ loci by using three parameters to describe the recombination rates between them. 
-$R$ is the recombination rate between the $\mathbf{A}$ and $\mathbf{M}$ loci, $\rho$ is the recombination rate between the $\mathbf{M}$ and $\mathbf{X}$ loci, and $r$ is the recombination rate between the $\mathbf{A}$ and $\mathbf{X}$ loci (Fig \ref{fig:model_outline}).
-\nameref{tab:chisubstitutions} shows replacements that can be made for each possible ordering of the loci assuming that there is no cross-over interference.
-During meiosis in sex $\Hermaphrodite$, meiotic drive occurs such that, in $Aa$ heterozygotes, a fraction $\alpha^{\Hermaphrodite}$ of gametes produced carry the $A$ allele and $(1-\alpha^\Hermaphrodite)$ carry the $a$ allele.
-
-Among gametes from sex $\Hermaphrodite$, the frequencies of haplotypes (before gametic competition) in the next generation are given by
-
-\begingroup
-\allowdisplaybreaks
-\begin{subequations}
-\begin{align}
-%
-\begin{split}
-x_{1}^{{\Hermaphrodite}'}=&xx_{11}^{\Hermaphrodite,s}+xx_{13}^{\Hermaphrodite,s}/2+(xx_{12}^{\Hermaphrodite,s}+xx_{14}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(xx_{14}^{\Hermaphrodite,s}-xx_{23}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&+(xy_{11}^{\Hermaphrodite,s}+xy_{13}^{\Hermaphrodite,s})/2+(xy_{12}^{\Hermaphrodite,s}+xy_{14}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&- r(xy_{12}^{\Hermaphrodite,s}-xy_{21}^{\Hermaphrodite,s})\alpha^\Hermaphrodite - \rho(xy_{13}^{\Hermaphrodite,s}-xy_{31}^{\Hermaphrodite,s})/2\\
-&+\big{[}-(R+r+\rho)xy_{14}^{\Hermaphrodite,s} +(R+\rho-r)xy_{41}^{\Hermaphrodite,s}\\
-&+(R+r-\rho) xy_{23}^{\Hermaphrodite,s}+(R+\rho-r)xy_{32}^{\Hermaphrodite,s}\big{]}\alpha^\Hermaphrodite/2
-\end{split}
-\\
-%
-\begin{split}
-x_{2}^{{\Hermaphrodite}'}=&xx_{22}^{\Hermaphrodite,s}+xx_{24}^{\Hermaphrodite,s}/2+(xx_{12}^{\Hermaphrodite,s}+xx_{23}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(xx_{23}^{\Hermaphrodite,s}-xx_{14}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&(xy_{22}^{\Hermaphrodite,s}+xy_{24}^{\Hermaphrodite,s})/2+(xy_{21}^{\Hermaphrodite,s}+xy_{23}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite)\\
-&- r(xy_{21}^{\Hermaphrodite,s}-xy_{12}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite) - \rho(xy_{24}^{\Hermaphrodite,s}-xy_{42}^{\Hermaphrodite,s})/2\\
-&+\big{[}-(R+r+\rho)xy_{23}^{\Hermaphrodite,s}+(R+\rho-r)xy_{32}^{\Hermaphrodite,s}\\
-&+(R+r-\rho) xy_{14}^{\Hermaphrodite,s}+(R+\rho-r)xy_{41}^{\Hermaphrodite,s}\big{]}(1-\alpha^\Hermaphrodite)/2
-\end{split}
-\\
-%
-\begin{split}
-x_{3}^{{\Hermaphrodite}'}=&xx_{33}^{\Hermaphrodite,s}+xx_{13}^{\Hermaphrodite,s}/2+(xx_{23}^{\Hermaphrodite,s}+xx_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(xx_{23}^{\Hermaphrodite,s}-xx_{14}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&(xy_{33}^{\Hermaphrodite,s}+xy_{31}^{\Hermaphrodite,s})/2+(xy_{32}^{\Hermaphrodite,s}+xy_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&- r(xy_{34}^{\Hermaphrodite,s}-xy_{43}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite - \rho(xy_{31}^{\Hermaphrodite,s}-xy_{13}^{\Hermaphrodite,s})/2\\
-&+\big{[}-(R+r+\rho)xy_{32}^{\Hermaphrodite,s} +(R+\rho-r)xy_{23}^{\Hermaphrodite,s}\\
-&+(R+r-\rho) xy_{41}^{\Hermaphrodite,s}+(R+\rho-r)xy_{14}^{\Hermaphrodite,s}\big{]} \alpha^\Hermaphrodite/2
-\end{split}
-\\
-%
-\begin{split}
-x_{4}^{{\Hermaphrodite}'}=&xx_{44}^{\Hermaphrodite,s}+xx_{34}^{\Hermaphrodite,s}/2+(xx_{14}^{\Hermaphrodite,s}+xx_{24}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(xx_{14}^{\Hermaphrodite,s}-xx_{23}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&(xy_{44}^{\Hermaphrodite,s}+xy_{42}^{\Hermaphrodite,s})/2+(xy_{41}^{\Hermaphrodite,s}+xy_{43}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite)\\
-&- r(xy_{43}^{\Hermaphrodite,s}-xy_{34}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite) - \rho(xy_{42}^{\Hermaphrodite,s}-xy_{24}^{\Hermaphrodite,s})/2\\
-&+\big{[}-(R+r+\rho)xy_{41}^{\Hermaphrodite,s}+(R+\rho-r)xy_{14}^{\Hermaphrodite,s}\\
-&+(R+r-\rho) xy_{32}^{\Hermaphrodite,s}+(R+\rho-r)xy_{23}^{\Hermaphrodite,s}\big{]}(1-\alpha^\Hermaphrodite)/2
-\end{split}
-\\
-\begin{split}
-y_{1}^{{\Hermaphrodite}'}=&yy_{11}^{\Hermaphrodite,s}+yy_{13}^{\Hermaphrodite,s}/2+(yy_{12}^{\Hermaphrodite,s}+yy_{14}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(yy_{14}^{\Hermaphrodite,s}-yy_{23}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&(xy_{11}^{\Hermaphrodite,s}+xy_{31}^{\Hermaphrodite,s})/2+(xy_{21}^{\Hermaphrodite,s}+xy_{41}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&- r(xy_{21}^{\Hermaphrodite,s}-xy_{12}^{\Hermaphrodite,s})\alpha^\Hermaphrodite - \rho(xy_{31}^{\Hermaphrodite,s}-xy_{13}^{\Hermaphrodite,s})/2\\
-&+\big{[} - (R+r+\rho)xy_{41}^{\Hermaphrodite,s} + (R+\rho-r)xy_{14}^{\Hermaphrodite,s}\\
-& + (R+r-\rho)xy_{32}^{\Hermaphrodite,s} + (R+\rho-r) xy_{23}^{\Hermaphrodite,s}\big{]}\alpha^\Hermaphrodite/2
-\end{split}
-\\
-%
-\begin{split}
-y_{2}^{{\Hermaphrodite}'}=&yy_{22}^{\Hermaphrodite,s}+yy_{24}^{\Hermaphrodite,s}/2+(yy_{12}^{\Hermaphrodite,s}+yy_{23}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(yy_{23}^{\Hermaphrodite,s}-yy_{14}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&(xy_{22}^{\Hermaphrodite,s}+xy_{42}^{\Hermaphrodite,s})/2+(xy_{12}^{\Hermaphrodite,s}+xy_{32}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite)\\
-&- r(xy_{12}^{\Hermaphrodite,s}-xy_{21}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite) - \rho(xy_{42}^{\Hermaphrodite,s}-xy_{24}^{\Hermaphrodite,s})/2\\
-&+\big{[}-(R+r+\rho)xy_{32}^{\Hermaphrodite,s} +(R+\rho-r) xy_{23}^{\Hermaphrodite,s}\\
-&+(R+r-\rho)xy_{41}^{\Hermaphrodite,s}+(R+\rho-r)xy_{14}^{\Hermaphrodite,s}\big{]}(1-\alpha^\Hermaphrodite)/2
-\end{split}
-\\
-%
-\begin{split}
-y_{3}^{{\Hermaphrodite}'}=&yy_{33}^{\Hermaphrodite,s}+yy_{13}^{\Hermaphrodite,s}/2+(yy_{23}^{\Hermaphrodite,s}+yy_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(yy_{23}^{\Hermaphrodite,s}-yy_{14}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&(xy_{33}^{\Hermaphrodite,s}+xy_{13}^{\Hermaphrodite,s})/2+(xy_{23}^{\Hermaphrodite,s}+xy_{43}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&- r(xy_{43}^{\Hermaphrodite,s}-xy_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite - \rho(xy_{13}^{\Hermaphrodite,s}-xy_{31}^{\Hermaphrodite,s})/2\\
-&+\big{[}-(R+r+\rho)xy_{23}^{\Hermaphrodite,s} +(R+\rho-r)xy_{32}^{\Hermaphrodite,s}\\
-&+(R+r-\rho) xy_{14}^{\Hermaphrodite,s} + (R+\rho-r) xy_{41}^{\Hermaphrodite,s}\big{]}\alpha^\Hermaphrodite/2
-\end{split}
-\\
-%
-\begin{split}
-y_{4}^{{\Hermaphrodite}'}=&yy_{44}^{\Hermaphrodite,s}+yy_{34}^{\Hermaphrodite,s}/2+(yy_{14}^{\Hermaphrodite,s}+yy_{24}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(yy_{14}^{\Hermaphrodite,s}-yy_{23}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&(xy_{44}^{\Hermaphrodite,s}+xy_{24}^{\Hermaphrodite,s})/2+(xy_{14}^{\Hermaphrodite,s}+xy_{34}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite)\\
-&- r(xy_{34}^{\Hermaphrodite,s}-xy_{43}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite) - \rho(xy_{24}^{\Hermaphrodite,s}-xy_{42}^{\Hermaphrodite,s})/2\\
-&+\big{[}-(R+r+\rho) xy_{14}^{\Hermaphrodite,s} + (R+\rho-r)xy_{41}^{\Hermaphrodite,s}\\
-&+(R+r-\rho) xy_{23}^{\Hermaphrodite,s} + (R+\rho-r) xy_{32}^{\Hermaphrodite,s}\big{]}(1-\alpha^\Hermaphrodite)/2.
-\end{split}
-\end{align}
-\label{eq:recursions}
-\end{subequations}
-
-\endgroup
-
-\noindent
-The full system is therefore described by 16 recurrence equations (three diallelic loci in two sexes, $2^3 \times 2 = 16$). 
-However, not all diploid types are produced under certain sex-determining systems. 
-For example, with the $M$ allele fixed and an ancestral XY sex-determining system, there are XX females and XY males ($x_{3}^\Hermaphrodite=x_{4}^\Hermaphrodite=y_{3}^\male=y_{4}^\male=y_{i}^\female=0,\;\forall\; i$).
-%($xx_{11}^{\male}=xx_{12}^{\male}=xx_{22}^\male=xy_{11}^{\female}=xy_{12}^{\female}=xy_{21}^{\female}=xy_{22}^\female=yy_{11}^{\female}=yy_{12}^{\female}=yy_{22}^\female=0$). 
-In this case, the system only involves six recursion equations, %because there is only one $\mathbf{M}$ locus allele and no Y-bearing female gametes. 
-which we assume below to calculate the equilibria.
-
-\newpage
-
-\setcounter{equation}{0}
-\renewcommand{\theequation}{S2.\arabic{equation}}
-
-\section*{S2 Appendix}
-
-\subsection*{Resident equilibria and stability}
-
-In the resident population (allele $M$ fixed), we follow the frequency of $A$ in X-bearing female gametes, $p^\female_X$, and X-bearing male gametes, $p^\male_X$, and Y-bearing male gametes, $p^\male_Y$.
-We also track the total frequency of Y among male gametes, $q$, which may deviate from $1/2$ due to meiotic drive in males. 
-These four variables determine the frequencies of the six resident gamete types, which sum to one in each sex: $x_{1}^{\female}=\hat{p}_X^\female$, $x_{2}^{\female}=1-\hat{p}_X^\female$, $x_{1}^{\male}=(1-q)\hat{p}_X^\male$, $x_{2}^{\male}=(1-q)(1-\hat{p}_X^\male)$, $y_{1}^{\male}=q \hat{p}_Y^\male$, and $y_{2}^{\male}=q(1-\hat{p}_Y^\male)$.
-Mean fitnesses in the resident population are given in \nameref{tab:meanfitnesses}.
-
-Various forms of selection can maintain a polymorphism at the $\mathbf{A}$ locus, including sexually antagonistic selection, overdominance, conflicts between diploid selection and selection upon haploid genotypes (ploidally-antagonsitic selection,~\cite{Immler:2012tl}), or a combination of these selective regimes (see below).
-
-In particular special cases, e.g., no sex-differences in selection or meiotic drive ($s^\male=s^\female$, $h^\male=h^\female$, and $\alpha^\male=\alpha^\female=1/2$), the equilibrium allele frequency and stability can be calculated analytically without assuming anything about the relative strengths of selection and recombination.
-However, here, we focus on two regimes (tight linkage between $\mathbf{A}$ and $\mathbf{X}$ and weak selection) in order to make fewer assumptions about fitnesses.
-
-\subsubsection*{Tight linkage between $\mathbf{X}$ and $\mathbf{A}$ loci}
-
-We first calculate the equilibria in the ancestral population when the recombination rate between the $\mathbf{X}$ and $\mathbf{A}$ loci is small ($r$ of order $\epsilon$). 
-Selection at the $\mathbf{A}$ locus will not affect evolution at the novel sex-determining locus, $\mathbf{M}$, if one allele is fixed on all backgrounds. 
-We therefore focus on the five equilibria that maintain both $A$ and $a$ alleles, four of which are given to leading order by:
-
-\begin{subequations}\label{eq:tightequil}
-\begin{align}
-(A)\ \ \ &\hat{p}_{Y}^{\male}=0,
-\ \hat{q}=\frac{1}{2}\left(1 - \alpha_\Delta^\male \frac{ w_{Aa}^{\male} \phi}{w_{Aa}^{\male} \phi+ w_{aa}^{\male} \psi}\right),\\
-&\hat{p}_{X}^{\female}=\frac{w_{a}^{\female} \phi}{w_{a}^{\female} \phi+ w_{A}^{\female} \psi},
-\ \hat{p}_{X}^{\male}=\frac{(1+\alpha_\Delta^\male)w_{Aa}^{\male} \phi}{(1+\alpha_\Delta^\male)w_{Aa}^{\male} \phi +w_{aa}^{\male} \psi} \nonumber \\
-(A')\ \ \ &\hat{p}_{Y}^{\male}=1,
-\ \hat{q}=\frac{1}{2}\left(1 + \alpha_\Delta^\male \frac{w_{Aa}^{\male} \phi'}{w_{Aa}^{\male} \phi' + w_{AA}^{\male} \psi'}\right),\\
-&\hat{p}_{X}^{\female}=1-\frac{w_{A}^{\female} \phi'}{w_{A}^{\female} \phi'+ w_{a}^{\female} \psi'},
-\ \hat{p}_{X}^{\male}=1-\frac{(1-\alpha_\Delta^\male)w_{Aa}^{\male} \phi'}{(1-\alpha_\Delta^\male)w_{Aa}^{\male} \phi'+w_{AA}^{\male} \psi'} \nonumber \\
-(B)\ \ \ &\hat{p}_{Y}^{\male}=0,\ \hat{p}_{X}^{\female}=1,\ \hat{p}_{X}^{\male}=1, \ \hat{q}=(1 -\alpha^\male_\Delta)/2\\
-(B')\ \ \ &\hat{p}_{Y}^{\male}=1,\ \hat{p}_{X}^{\female}=0,\ \hat{p}_{X}^{\male}=0, \ \hat{q}=(1+\alpha^\male_\Delta)/2
-\end{align}
-\end{subequations}
-\begin{equation*}
-\begin{split}
-\phi=&(1+\alpha^\female_\Delta) w_{A}^{\female} w_{Aa}^{\female} \left[ w_{a}^{\male} w_{aa}^{\male} + (1+\alpha_\Delta^\male) w_{A}^{\male} w_{Aa}^{\male} \right]/2 - w_{a}^{\male} w_{a}^{\female} w_{aa}^{\male} w_{aa}^{\female} \\
-\psi=&(1-\alpha^\female_\Delta) w_{a}^{\female} w_{Aa}^{\female} \left[ w_{a}^{\male} w_{aa}^{\male} + (1+\alpha_\Delta^\male) w_{A}^{\male} w_{Aa}^{\male}\right]/2 - (1+\alpha_\Delta^\male) w_{A}^{\male} w_{A}^{\female} w_{Aa}^{\male} w_{AA}^{\female}\\
-\phi'=&(1-\alpha^\female_\Delta) w_{a}^{\female} w_{Aa}^{\female} \left[ w_{A}^{\male} w_{AA}^{\male} + (1-\alpha_\Delta^\male) w_{a}^{\male} w_{Aa}^{\male} \right]/2 - w_{A}^{\male} w_{A}^{\female} w_{AA}^{\male} w_{AA}^{\female}\\
-\psi'=&(1+\alpha^\female_\Delta) w_{A}^{\female} w_{Aa}^{\female} \left[ w_{A}^{\male} w_{AA}^{\male} + (1-\alpha_\Delta^\male) w_{a}^{\male} w_{Aa}^{\male} \right]/2 - (1-\alpha_\Delta^\male) w_{a}^{\male} w_{a}^{\female} w_{Aa}^{\male} w_{aa}^{\female}.
-\end{split}
-\end{equation*}
-
-\noindent
-A fifth equilibrium $(C)$ also exists where $A$ is present at an intermediate frequency on the Y background ($0<\hat{p}_{Y}^{\male}<1$). 
-However, equilibrium $(C)$ is never locally stable when $r \approx 0$ and is therefore not considered further.
-Thus, the Y background can either be fixed for the $a$ allele (equilibria ($A$) and ($B$)) or the $A$ allele (equilibria ($A'$) and ($B'$)).
-The X background can then either be polymorphic (equilibria ($A$) and ($A'$)) or fixed for the alternative allele (equilibria ($B$) and ($B'$)).
-Since equilibria $(A)$ and $(B)$ are equivalent to equilibria $(A')$ and $(B')$ with the labelling of $A$ and $a$ alleles interchanged, we discuss only equilibria $(A)$ and $(B)$, in which the Y background is fixed for the $a$ allele.
-If there is no haploid selection ($\alpha^{\Hermaphrodite}_\Delta=0$, $w_{A}^{\Hermaphrodite}=w_{a}^{\Hermaphrodite}=1$), these equilibria are equivalent to those found by~\cite{Lloyd1977} and~\cite{Otto2014}.
-
-We next calculate when equilibria $(A)$ and $(B)$ are locally stable for $r=0$. 
-According to the `small parameter theory'~\cite{Karlin:1972ab,Karlin:1972dq}, these stability properties are unaffected by small amounts of recombination between the sex-determining locus and the $\mathbf{A}$ locus, although equilibrium frequencies may be slightly altered.
-For the $a$ allele to be stably fixed on the Y background we need $\bar{w}_{Ya}^{\male} > \bar{w}_{YA}^{\male}$ where $\bar{w}_{Ya}^{\male} = w_{a}^{\male} \big[\hat{p}_X^\female(1-\alpha^\male_\Delta) w_{A}^{\female} w_{Aa}^{\male} + (1-\hat{p}_X^\female)w_{a}^{\female} w_{aa}^{\male} \big]$ and $\bar{w}_{YA}^{\male} = w_{A}^{\male} \big[ \hat{p}_X^\female w_{A}^{\female} w_{AA}^{\male} + (1-\hat{p}_X^\female)(1+\alpha^\male_\Delta) w_{a}^{\female} w_{Aa}^{\male} \big]$.
-That is, Y-$a$ haplotypes must have higher fitness than Y-$A$ haplotypes.  
-Substituting in $\hat{p}_X^\female$ from Eq \eqref{eq:tightequil}, fixation of the $a$ allele on the Y background requires that $\gamma_{i}>0$ where $\gamma_{(A)}=w_{a}^{\male} \big[ (1-\alpha^\male_\Delta) w_{Aa}^{\male} \phi + w_{aa}^{\male} \psi \big]-w_{A}^{\male} \big[ w_{AA}^{\male} \phi + (1 + \alpha^{\male}_\Delta)w_{Aa}^{\male} \psi \big]$ for equilibrium $(A)$ and $\gamma_{(B)}=(1-\alpha^{\male}_\Delta)w_{a}^{\male}w_{Aa}^{\male}-w_{A}^{\male}w_{AA}^{\male}$ for equilibrium $(B)$.
-Stability of a polymorphism on the X background (equilibrium $(A)$) further requires that $\phi >0$ and $\psi >0$. 
-Fixation of the $a$ allele on the X background (equilibrium $(B)$) can be stable only if equilibrium $(A)$ is not, as it requires $\psi<0$.
+%\newpage
+%
+%\setcounter{equation}{0}
+%\renewcommand{\theequation}{S1.\arabic{equation}}
+%
+%\section*{S1 Appendix}
+%
+%\subsection*{Recursion equations}
+%
+%
+%In each generation we census the genotype frequencies in male and female gametes/gametophytes (hereafter, gametes) between meiosis (and any meiotic drive) and gametic competition. 
+%At this stage we denote the frequencies of X- and Y-bearing gametes from males and females $x_{i}^{\Hermaphrodite}$ and $y_{i}^{\Hermaphrodite}$.
+%The superscript $\Hermaphrodite \in \{\male,\female\}$ specifies the sex of the diploid that the gamete came from. 
+%The subscript $i\in\{1,2,3,4\}$ specifies the genotype at the selected locus $\mathbf{A}$ and at the novel sex-determining locus $\mathbf{M}$, where $1=AM$, $2=aM$, $3=Am$, and $4=am$. 
+%The gamete frequencies from each sex sum to one, $\sum_{i}x_{i}^{\Hermaphrodite}+y_{i}^{\Hermaphrodite}=1$. 
+%
+%Competition then occurs among gametes of the same sex (e.g., among eggs and among sperm separately) according to the genotype at the $\mathbf{A}$ locus ($w_{1}^\Hermaphrodite=w_{3}^\Hermaphrodite=w_{A}^\Hermaphrodite$, $w_{2}^\Hermaphrodite=w_{4}^\Hermaphrodite=w_{a}^\Hermaphrodite$, see Table \ref{tab:fitnesstable}).
+%The genotype frequencies after gametic competition are $x_{i}^{\Hermaphrodite,s}= w_{i}^{\Hermaphrodite}x_{i}^{\Hermaphrodite}/\bar{w}_{H}^{\Hermaphrodite}$ and $y_{i}^{\Hermaphrodite,s}= w_{i}^{\Hermaphrodite}y_{i}^{\Hermaphrodite}/\bar{w}_{H}^{\Hermaphrodite}$, where $\bar{w}_{H}^{\Hermaphrodite}=\sum_{i} w_{i}^{\Hermaphrodite}x_{i}^{\Hermaphrodite}+w_{i}^{\Hermaphrodite}y_{i}^{\Hermaphrodite}$ is the mean fitness of male ($\Hermaphrodite=\male$) or female ($\Hermaphrodite=\female$) gametes.
+%
+%Random mating then occurs between gametes to produce diploid zygotes.
+%%To shorten notation we now use index $i$ (and $j$) to denote the alleles at both the $\mathbf{A}$ and $\mathbf{M}$ loci and label $MA=1$, $Ma=2$, $mA=3$, and $ma=4$, such that $i,j\in\{1,2,3,4\}$.
+%The frequencies of XX zygotes are then denoted as $xx_{ij}$, XY zygotes as $xy_{ij}$, and YY zygotes as $yy_{ij}$, where $\mathbf{A}$ and $\mathbf{M}$ locus genotypes are given by $i,j\in\{1,2,3,4\}$, as above.
+%In XY zygotes, the haplotype inherited from an X-bearing gamete is given by $i$ and the haplotype from a Y-bearing gamete is given by $j$. 
+%In XX and YY zygotes, individuals with diploid genotype $ij$ are equivalent to those with diploid genotype $ji$; for simplicity, we use $xx_{ij}$ and $yy_{ij}$ with $i\neq j$ to denote the average of these frequencies, $xx_{ij}=(x_{i}^{\female,s}x_{j}^{\male,s}+x_{j}^{\female,s}x_{i}^{\male,s})/2$ and $yy_{ij}=(y_{i}^{\female,s}y_{j}^{\male,s}+y_{j}^{\female,s}y_{i}^{\male,s})/2$.
+%
+%
+%Denoting the $\mathbf{M}$ locus genotype by $b \in \{MM, Mm, mm\}$ and the $\mathbf{X}$ locus genotype by $c \in \{XX, XY, YY\}$, zygotes develop as females with probability $k_{bc}$. 
+%Therefore, the frequencies of XX females are given by $xx_{ij}^{\female}=k_{bc}xx_{ij}$, XY females are given by $xy_{ij}^{\female}=k_{bc}xy_{ij}$, and YY females are given by $yy_{ij}^{\female}=k_{bc}yy_{ij}$.
+%Similarly, XX male frequencies are $xx_{ij}^{\male}=(1-k_{bc})xx_{ij}$, XY male frequencies are $xy_{ij}^{\male}=(1-k_{bc})xy_{ij}$, and YY males frequencies are $yy_{ij}^{\male}=(1-k_{bc})yy_{ij}$.
+%This notation allows both the ancestral and novel sex-determining regions to determine zygotic sex according to an XY system, a ZW system, or an environmental sex-determining system. 
+%In addition, we can consider any epistatic dominance relationship between the two sex-determining loci. 
+%Here, we assume that the ancestral sex-determining system ($\mathbf{X}$ locus) is XY ($k_{MMXX}=1$ and $k_{MMXY}=k_{MMYY}=0$) or ZW ($k_{MMZZ}=0$ and $k_{MMZW}=k_{MMWW}=1$) and epistatically recessive to a dominant novel sex-determining locus, $\mathbf{M}$ ($k_{Mmc}=k_{mmc}=k$).
+%
+%
+%Selection among diploids then occurs according to the diploid genotype at the $\mathbf{A}$ locus, $l \in \{AA, Aa, aa\}$, for an individual of type $ij$ (see Table \ref{tab:fitnesstable}). 
+%The diploid frequencies after selection in sex $\Hermaphrodite$ are given by $xx_{ij}^{\Hermaphrodite,s}=w_{l}^{\Hermaphrodite} xx_{ij}/\bar{w}^{\Hermaphrodite}_{D}$, $xy_{ij}^{\Hermaphrodite,s}=w_{l}^{\Hermaphrodite} xy_{ij}/\bar{w}^{\Hermaphrodite}_{D}$, and $yy_{ij}^{\Hermaphrodite,s}=w_{l}^{\Hermaphrodite} yy_{ij}/\bar{w}^{\Hermaphrodite}_{D}$, where $\bar{w}^{\Hermaphrodite}_{D}= \sum_{i=1}^{4}\sum_{j=1}^{4}w_{l}^{\Hermaphrodite}xx_{ij}+w_{l}^{\Hermaphrodite}xy_{ij}+w_{l}^{\Hermaphrodite}yy_{ij}$ is the mean fitness of diploids of sex $\Hermaphrodite$.
+%
+%Finally, these diploids undergo meiosis to produce the next generation of gametes. 
+%Recombination and sex-specific meiotic drive occur during meiosis.
+%%We can also assume that recombination is sex specific and/or affected by the M locus - but generally we don't so I just describe $R=R_{f}=R, r_{MM,d}=r_{Mm,d}=r_{mm,d}=r, \chi_{m}=\chi_{f}=\chi$.
+%Here, we allow any relative locations for the $\mathbf{X}$, $\mathbf{A}$, and $\mathbf{M}$ loci by using three parameters to describe the recombination rates between them. 
+%$R$ is the recombination rate between the $\mathbf{A}$ and $\mathbf{M}$ loci, $\rho$ is the recombination rate between the $\mathbf{M}$ and $\mathbf{X}$ loci, and $r$ is the recombination rate between the $\mathbf{A}$ and $\mathbf{X}$ loci (Fig \ref{fig:model_outline}).
+%\nameref{tab:chisubstitutions} shows replacements that can be made for each possible ordering of the loci assuming that there is no cross-over interference.
+%During meiosis in sex $\Hermaphrodite$, meiotic drive occurs such that, in $Aa$ heterozygotes, a fraction $\alpha^{\Hermaphrodite}$ of gametes produced carry the $A$ allele and $(1-\alpha^\Hermaphrodite)$ carry the $a$ allele.
+%
+%Among gametes from sex $\Hermaphrodite$, the frequencies of haplotypes (before gametic competition) in the next generation are given by
+%
+%\begingroup
+%\allowdisplaybreaks
+%\begin{subequations}
+%\begin{align}
+%%
+%\begin{split}
+%x_{1}^{{\Hermaphrodite}'}=&xx_{11}^{\Hermaphrodite,s}+xx_{13}^{\Hermaphrodite,s}/2+(xx_{12}^{\Hermaphrodite,s}+xx_{14}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
+%&-R(xx_{14}^{\Hermaphrodite,s}-xx_{23}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
+%&+(xy_{11}^{\Hermaphrodite,s}+xy_{13}^{\Hermaphrodite,s})/2+(xy_{12}^{\Hermaphrodite,s}+xy_{14}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
+%&- r(xy_{12}^{\Hermaphrodite,s}-xy_{21}^{\Hermaphrodite,s})\alpha^\Hermaphrodite - \rho(xy_{13}^{\Hermaphrodite,s}-xy_{31}^{\Hermaphrodite,s})/2\\
+%&+\big{[}-(R+r+\rho)xy_{14}^{\Hermaphrodite,s} +(R+\rho-r)xy_{41}^{\Hermaphrodite,s}\\
+%&+(R+r-\rho) xy_{23}^{\Hermaphrodite,s}+(R+\rho-r)xy_{32}^{\Hermaphrodite,s}\big{]}\alpha^\Hermaphrodite/2
+%\end{split}
+%\\
+%%
+%\begin{split}
+%x_{2}^{{\Hermaphrodite}'}=&xx_{22}^{\Hermaphrodite,s}+xx_{24}^{\Hermaphrodite,s}/2+(xx_{12}^{\Hermaphrodite,s}+xx_{23}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
+%&-R(xx_{23}^{\Hermaphrodite,s}-xx_{14}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
+%&(xy_{22}^{\Hermaphrodite,s}+xy_{24}^{\Hermaphrodite,s})/2+(xy_{21}^{\Hermaphrodite,s}+xy_{23}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite)\\
+%&- r(xy_{21}^{\Hermaphrodite,s}-xy_{12}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite) - \rho(xy_{24}^{\Hermaphrodite,s}-xy_{42}^{\Hermaphrodite,s})/2\\
+%&+\big{[}-(R+r+\rho)xy_{23}^{\Hermaphrodite,s}+(R+\rho-r)xy_{32}^{\Hermaphrodite,s}\\
+%&+(R+r-\rho) xy_{14}^{\Hermaphrodite,s}+(R+\rho-r)xy_{41}^{\Hermaphrodite,s}\big{]}(1-\alpha^\Hermaphrodite)/2
+%\end{split}
+%\\
+%%
+%\begin{split}
+%x_{3}^{{\Hermaphrodite}'}=&xx_{33}^{\Hermaphrodite,s}+xx_{13}^{\Hermaphrodite,s}/2+(xx_{23}^{\Hermaphrodite,s}+xx_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
+%&-R(xx_{23}^{\Hermaphrodite,s}-xx_{14}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
+%&(xy_{33}^{\Hermaphrodite,s}+xy_{31}^{\Hermaphrodite,s})/2+(xy_{32}^{\Hermaphrodite,s}+xy_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
+%&- r(xy_{34}^{\Hermaphrodite,s}-xy_{43}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite - \rho(xy_{31}^{\Hermaphrodite,s}-xy_{13}^{\Hermaphrodite,s})/2\\
+%&+\big{[}-(R+r+\rho)xy_{32}^{\Hermaphrodite,s} +(R+\rho-r)xy_{23}^{\Hermaphrodite,s}\\
+%&+(R+r-\rho) xy_{41}^{\Hermaphrodite,s}+(R+\rho-r)xy_{14}^{\Hermaphrodite,s}\big{]} \alpha^\Hermaphrodite/2
+%\end{split}
+%\\
+%%
+%\begin{split}
+%x_{4}^{{\Hermaphrodite}'}=&xx_{44}^{\Hermaphrodite,s}+xx_{34}^{\Hermaphrodite,s}/2+(xx_{14}^{\Hermaphrodite,s}+xx_{24}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
+%&-R(xx_{14}^{\Hermaphrodite,s}-xx_{23}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
+%&(xy_{44}^{\Hermaphrodite,s}+xy_{42}^{\Hermaphrodite,s})/2+(xy_{41}^{\Hermaphrodite,s}+xy_{43}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite)\\
+%&- r(xy_{43}^{\Hermaphrodite,s}-xy_{34}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite) - \rho(xy_{42}^{\Hermaphrodite,s}-xy_{24}^{\Hermaphrodite,s})/2\\
+%&+\big{[}-(R+r+\rho)xy_{41}^{\Hermaphrodite,s}+(R+\rho-r)xy_{14}^{\Hermaphrodite,s}\\
+%&+(R+r-\rho) xy_{32}^{\Hermaphrodite,s}+(R+\rho-r)xy_{23}^{\Hermaphrodite,s}\big{]}(1-\alpha^\Hermaphrodite)/2
+%\end{split}
+%\\
+%\begin{split}
+%y_{1}^{{\Hermaphrodite}'}=&yy_{11}^{\Hermaphrodite,s}+yy_{13}^{\Hermaphrodite,s}/2+(yy_{12}^{\Hermaphrodite,s}+yy_{14}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
+%&-R(yy_{14}^{\Hermaphrodite,s}-yy_{23}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
+%&(xy_{11}^{\Hermaphrodite,s}+xy_{31}^{\Hermaphrodite,s})/2+(xy_{21}^{\Hermaphrodite,s}+xy_{41}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
+%&- r(xy_{21}^{\Hermaphrodite,s}-xy_{12}^{\Hermaphrodite,s})\alpha^\Hermaphrodite - \rho(xy_{31}^{\Hermaphrodite,s}-xy_{13}^{\Hermaphrodite,s})/2\\
+%&+\big{[} - (R+r+\rho)xy_{41}^{\Hermaphrodite,s} + (R+\rho-r)xy_{14}^{\Hermaphrodite,s}\\
+%& + (R+r-\rho)xy_{32}^{\Hermaphrodite,s} + (R+\rho-r) xy_{23}^{\Hermaphrodite,s}\big{]}\alpha^\Hermaphrodite/2
+%\end{split}
+%\\
+%%
+%\begin{split}
+%y_{2}^{{\Hermaphrodite}'}=&yy_{22}^{\Hermaphrodite,s}+yy_{24}^{\Hermaphrodite,s}/2+(yy_{12}^{\Hermaphrodite,s}+yy_{23}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
+%&-R(yy_{23}^{\Hermaphrodite,s}-yy_{14}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
+%&(xy_{22}^{\Hermaphrodite,s}+xy_{42}^{\Hermaphrodite,s})/2+(xy_{12}^{\Hermaphrodite,s}+xy_{32}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite)\\
+%&- r(xy_{12}^{\Hermaphrodite,s}-xy_{21}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite) - \rho(xy_{42}^{\Hermaphrodite,s}-xy_{24}^{\Hermaphrodite,s})/2\\
+%&+\big{[}-(R+r+\rho)xy_{32}^{\Hermaphrodite,s} +(R+\rho-r) xy_{23}^{\Hermaphrodite,s}\\
+%&+(R+r-\rho)xy_{41}^{\Hermaphrodite,s}+(R+\rho-r)xy_{14}^{\Hermaphrodite,s}\big{]}(1-\alpha^\Hermaphrodite)/2
+%\end{split}
+%\\
+%%
+%\begin{split}
+%y_{3}^{{\Hermaphrodite}'}=&yy_{33}^{\Hermaphrodite,s}+yy_{13}^{\Hermaphrodite,s}/2+(yy_{23}^{\Hermaphrodite,s}+yy_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
+%&-R(yy_{23}^{\Hermaphrodite,s}-yy_{14}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
+%&(xy_{33}^{\Hermaphrodite,s}+xy_{13}^{\Hermaphrodite,s})/2+(xy_{23}^{\Hermaphrodite,s}+xy_{43}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
+%&- r(xy_{43}^{\Hermaphrodite,s}-xy_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite - \rho(xy_{13}^{\Hermaphrodite,s}-xy_{31}^{\Hermaphrodite,s})/2\\
+%&+\big{[}-(R+r+\rho)xy_{23}^{\Hermaphrodite,s} +(R+\rho-r)xy_{32}^{\Hermaphrodite,s}\\
+%&+(R+r-\rho) xy_{14}^{\Hermaphrodite,s} + (R+\rho-r) xy_{41}^{\Hermaphrodite,s}\big{]}\alpha^\Hermaphrodite/2
+%\end{split}
+%\\
+%%
+%\begin{split}
+%y_{4}^{{\Hermaphrodite}'}=&yy_{44}^{\Hermaphrodite,s}+yy_{34}^{\Hermaphrodite,s}/2+(yy_{14}^{\Hermaphrodite,s}+yy_{24}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
+%&-R(yy_{14}^{\Hermaphrodite,s}-yy_{23}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
+%&(xy_{44}^{\Hermaphrodite,s}+xy_{24}^{\Hermaphrodite,s})/2+(xy_{14}^{\Hermaphrodite,s}+xy_{34}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite)\\
+%&- r(xy_{34}^{\Hermaphrodite,s}-xy_{43}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite) - \rho(xy_{24}^{\Hermaphrodite,s}-xy_{42}^{\Hermaphrodite,s})/2\\
+%&+\big{[}-(R+r+\rho) xy_{14}^{\Hermaphrodite,s} + (R+\rho-r)xy_{41}^{\Hermaphrodite,s}\\
+%&+(R+r-\rho) xy_{23}^{\Hermaphrodite,s} + (R+\rho-r) xy_{32}^{\Hermaphrodite,s}\big{]}(1-\alpha^\Hermaphrodite)/2.
+%\end{split}
+%\end{align}
+%\label{eq:recursions}
+%\end{subequations}
+%
+%\endgroup
+%
+%\noindent
+%The full system is therefore described by 16 recurrence equations (three diallelic loci in two sexes, $2^3 \times 2 = 16$). 
+%However, not all diploid types are produced under certain sex-determining systems. 
+%For example, with the $M$ allele fixed and an ancestral XY sex-determining system, there are XX females and XY males ($x_{3}^\Hermaphrodite=x_{4}^\Hermaphrodite=y_{3}^\male=y_{4}^\male=y_{i}^\female=0,\;\forall\; i$).
+%%($xx_{11}^{\male}=xx_{12}^{\male}=xx_{22}^\male=xy_{11}^{\female}=xy_{12}^{\female}=xy_{21}^{\female}=xy_{22}^\female=yy_{11}^{\female}=yy_{12}^{\female}=yy_{22}^\female=0$). 
+%In this case, the system only involves six recursion equations, %because there is only one $\mathbf{M}$ locus allele and no Y-bearing female gametes. 
+%which we assume below to calculate the equilibria.
+
+%\newpage
+
+%\setcounter{equation}{0}
+%\renewcommand{\theequation}{S2.\arabic{equation}}
+%
+%\section*{S2 Appendix}
+%
+%\subsection*{Resident equilibria and stability}
+%
+%In the resident population (allele $M$ fixed), we follow the frequency of $A$ in X-bearing female gametes, $p^\female_X$, and X-bearing male gametes, $p^\male_X$, and Y-bearing male gametes, $p^\male_Y$.
+%We also track the total frequency of Y among male gametes, $q$, which may deviate from $1/2$ due to meiotic drive in males. 
+%These four variables determine the frequencies of the six resident gamete types, which sum to one in each sex: $x_{1}^{\female}=\hat{p}_X^\female$, $x_{2}^{\female}=1-\hat{p}_X^\female$, $x_{1}^{\male}=(1-q)\hat{p}_X^\male$, $x_{2}^{\male}=(1-q)(1-\hat{p}_X^\male)$, $y_{1}^{\male}=q \hat{p}_Y^\male$, and $y_{2}^{\male}=q(1-\hat{p}_Y^\male)$.
+%Mean fitnesses in the resident population are given in \nameref{tab:meanfitnesses}.
+%
+%Various forms of selection can maintain a polymorphism at the $\mathbf{A}$ locus, including sexually antagonistic selection, overdominance, conflicts between diploid selection and selection upon haploid genotypes (ploidally-antagonsitic selection,~\cite{Immler:2012tl}), or a combination of these selective regimes (see below).
+%
+%In particular special cases, e.g., no sex-differences in selection or meiotic drive ($s^\male=s^\female$, $h^\male=h^\female$, and $\alpha^\male=\alpha^\female=1/2$), the equilibrium allele frequency and stability can be calculated analytically without assuming anything about the relative strengths of selection and recombination.
+%However, here, we focus on two regimes (tight linkage between $\mathbf{A}$ and $\mathbf{X}$ and weak selection) in order to make fewer assumptions about fitnesses. 
+%
+%\subsubsection*{Tight linkage between $\mathbf{X}$ and $\mathbf{A}$ loci}
+%
+%We first calculate the equilibria in the ancestral population when the recombination rate between the $\mathbf{X}$ and $\mathbf{A}$ loci is small ($r$ of order $\epsilon$). 
+%Selection at the $\mathbf{A}$ locus will not affect evolution at the novel sex-determining locus, $\mathbf{M}$, if one allele is fixed on all backgrounds. 
+%We therefore focus on the five equilibria that maintain both $A$ and $a$ alleles, four of which are given to leading order by:
+%
+%\begin{subequations}\label{eq:tightequil}
+%\begin{align}
+%(A)\ \ \ &\hat{p}_{Y}^{\male}=0,
+%\ \hat{q}=\frac{1}{2}\left(1 - \alpha_\Delta^\male \frac{ w_{Aa}^{\male} \phi}{w_{Aa}^{\male} \phi+ w_{aa}^{\male} \psi}\right),\\
+%&\hat{p}_{X}^{\female}=\frac{w_{a}^{\female} \phi}{w_{a}^{\female} \phi+ w_{A}^{\female} \psi},
+%\ \hat{p}_{X}^{\male}=\frac{(1+\alpha_\Delta^\male)w_{Aa}^{\male} \phi}{(1+\alpha_\Delta^\male)w_{Aa}^{\male} \phi +w_{aa}^{\male} \psi} \nonumber \\
+%(A')\ \ \ &\hat{p}_{Y}^{\male}=1,
+%\ \hat{q}=\frac{1}{2}\left(1 + \alpha_\Delta^\male \frac{w_{Aa}^{\male} \phi'}{w_{Aa}^{\male} \phi' + w_{AA}^{\male} \psi'}\right),\\
+%&\hat{p}_{X}^{\female}=1-\frac{w_{A}^{\female} \phi'}{w_{A}^{\female} \phi'+ w_{a}^{\female} \psi'},
+%\ \hat{p}_{X}^{\male}=1-\frac{(1-\alpha_\Delta^\male)w_{Aa}^{\male} \phi'}{(1-\alpha_\Delta^\male)w_{Aa}^{\male} \phi'+w_{AA}^{\male} \psi'} \nonumber \\
+%(B)\ \ \ &\hat{p}_{Y}^{\male}=0,\ \hat{p}_{X}^{\female}=1,\ \hat{p}_{X}^{\male}=1, \ \hat{q}=(1 -\alpha^\male_\Delta)/2\\
+%(B')\ \ \ &\hat{p}_{Y}^{\male}=1,\ \hat{p}_{X}^{\female}=0,\ \hat{p}_{X}^{\male}=0, \ \hat{q}=(1+\alpha^\male_\Delta)/2
+%\end{align}
+%\end{subequations}
+%\begin{equation*}
+%\begin{split}
+%\phi=&(1+\alpha^\female_\Delta) w_{A}^{\female} w_{Aa}^{\female} \left[ w_{a}^{\male} w_{aa}^{\male} + (1+\alpha_\Delta^\male) w_{A}^{\male} w_{Aa}^{\male} \right]/2 - w_{a}^{\male} w_{a}^{\female} w_{aa}^{\male} w_{aa}^{\female} \\
+%\psi=&(1-\alpha^\female_\Delta) w_{a}^{\female} w_{Aa}^{\female} \left[ w_{a}^{\male} w_{aa}^{\male} + (1+\alpha_\Delta^\male) w_{A}^{\male} w_{Aa}^{\male}\right]/2 - (1+\alpha_\Delta^\male) w_{A}^{\male} w_{A}^{\female} w_{Aa}^{\male} w_{AA}^{\female}\\
+%\phi'=&(1-\alpha^\female_\Delta) w_{a}^{\female} w_{Aa}^{\female} \left[ w_{A}^{\male} w_{AA}^{\male} + (1-\alpha_\Delta^\male) w_{a}^{\male} w_{Aa}^{\male} \right]/2 - w_{A}^{\male} w_{A}^{\female} w_{AA}^{\male} w_{AA}^{\female}\\
+%\psi'=&(1+\alpha^\female_\Delta) w_{A}^{\female} w_{Aa}^{\female} \left[ w_{A}^{\male} w_{AA}^{\male} + (1-\alpha_\Delta^\male) w_{a}^{\male} w_{Aa}^{\male} \right]/2 - (1-\alpha_\Delta^\male) w_{a}^{\male} w_{a}^{\female} w_{Aa}^{\male} w_{aa}^{\female}.
+%\end{split}
+%\end{equation*}
+%
+%\noindent
+%A fifth equilibrium $(C)$ also exists where $A$ is present at an intermediate frequency on the Y background ($0<\hat{p}_{Y}^{\male}<1$). 
+%However, equilibrium $(C)$ is never locally stable when $r \approx 0$ and is therefore not considered further.
+%Thus, the Y background can either be fixed for the $a$ allele (equilibria ($A$) and ($B$)) or the $A$ allele (equilibria ($A'$) and ($B'$)).
+%The X background can then either be polymorphic (equilibria ($A$) and ($A'$)) or fixed for the alternative allele (equilibria ($B$) and ($B'$)).
+%Since equilibria $(A)$ and $(B)$ are equivalent to equilibria $(A')$ and $(B')$ with the labelling of $A$ and $a$ alleles interchanged, we discuss only equilibria $(A)$ and $(B)$, in which the Y background is fixed for the $a$ allele.
+%If there is no haploid selection ($\alpha^{\Hermaphrodite}_\Delta=0$, $w_{A}^{\Hermaphrodite}=w_{a}^{\Hermaphrodite}=1$), these equilibria are equivalent to those found by~\cite{Lloyd1977} and~\cite{Otto2014}.
+%
+%We next calculate when equilibria $(A)$ and $(B)$ are locally stable for $r=0$. 
+%According to the `small parameter theory'~\cite{Karlin:1972ab,Karlin:1972dq}, these stability properties are unaffected by small amounts of recombination between the sex-determining locus and the $\mathbf{A}$ locus, although equilibrium frequencies may be slightly altered.
+%For the $a$ allele to be stably fixed on the Y background we need $\bar{w}_{Ya}^{\male} > \bar{w}_{YA}^{\male}$ where $\bar{w}_{Ya}^{\male} = w_{a}^{\male} \big[\hat{p}_X^\female(1-\alpha^\male_\Delta) w_{A}^{\female} w_{Aa}^{\male} + (1-\hat{p}_X^\female)w_{a}^{\female} w_{aa}^{\male} \big]$ and $\bar{w}_{YA}^{\male} = w_{A}^{\male} \big[ \hat{p}_X^\female w_{A}^{\female} w_{AA}^{\male} + (1-\hat{p}_X^\female)(1+\alpha^\male_\Delta) w_{a}^{\female} w_{Aa}^{\male} \big]$.
+%That is, Y-$a$ haplotypes must have higher fitness than Y-$A$ haplotypes.  
+%Substituting in $\hat{p}_X^\female$ from Eq \eqref{eq:tightequil}, fixation of the $a$ allele on the Y background requires that $\gamma_{i}>0$ where $\gamma_{(A)}=w_{a}^{\male} \big[ (1-\alpha^\male_\Delta) w_{Aa}^{\male} \phi + w_{aa}^{\male} \psi \big]-w_{A}^{\male} \big[ w_{AA}^{\male} \phi + (1 + \alpha^{\male}_\Delta)w_{Aa}^{\male} \psi \big]$ for equilibrium $(A)$ and $\gamma_{(B)}=(1-\alpha^{\male}_\Delta)w_{a}^{\male}w_{Aa}^{\male}-w_{A}^{\male}w_{AA}^{\male}$ for equilibrium $(B)$.
+%Stability of a polymorphism on the X background (equilibrium $(A)$) further requires that $\phi >0$ and $\psi >0$. 
+%Fixation of the $a$ allele on the X background (equilibrium $(B)$) can be stable only if equilibrium $(A)$ is not, as it requires $\psi<0$.
 %and $2w_{A}^{\female}w_{AA}^{\female}>(1-\alpha_\Delta^{\female})w_{a}^{\female}w_{Aa}^{\female}$ or just $4w_{A}^{\female}w_{AA}^{\female}<(1-\alpha_\Delta^{\female})w_{a}^{\female}w_{Aa}^{\female}$ (which also prevents $\psi>0$).
-
-%\textcolor{red}{check last condition and the stability condition below are correct}
-%\textcolor{blue}{The last condition looks good to me, although in your Turnover-norec-MFS.nb you look at YA fixed, so you have to flip everything (so I made Turnover-norec-MFS-MMO.nb to do this).
-%The one issue I can find here is that you can also prevent $\Lambda>1$ when the slope and intercept of the quadratic at $\Lambda=1$ are negative (you only looked at both being positive).
+%
+%%\textcolor{red}{check last condition and the stability condition below are correct}
+%%\textcolor{blue}{The last condition looks good to me, although in your Turnover-norec-MFS.nb you look at YA fixed, so you have to flip everything (so I made Turnover-norec-MFS-MMO.nb to do this).
+%%The one issue I can find here is that you can also prevent $\Lambda>1$ when the slope and intercept of the quadratic at $\Lambda=1$ are negative (you only looked at both being positive).
 In this case we need $4w_{A}^{\female}w_{AA}^{\female}<(1-\alpha_\Delta^{\female})w_{a}^{\female}w_{Aa}^{\female}$, which also prevents $\psi>0$.
-%I've added this in.
-%It could also be the case that the slope and intercept are the same sign but the roots are imaginary - but this is never the case here.
-%Stability condition below looks good to me (from matt version of turnoverSOM-MIKE.nb).}
-
-\subsubsection*{Selection weak relative to recombination}
-
-Here, we assume that selection is weak relative to recombination ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon$). 
-The maintenance of a polymorphism at the $\mathbf{A}$ locus then requires that
-
-\begin{equation}
-\begin{split}
-0&< - \left[(1-h^\female)s^\female +(1-h^\male) s^\male + t^\female +t^\male + \alpha_{\Delta}^\female+\alpha_{\Delta}^\male\right]\\
-%
-\text{and }\quad 0&<h^\female s^\female +h^\male s^\male + t^\female +t^\male + \alpha_{\Delta}^\female+\alpha_{\Delta}^\male.
-\end{split}
-\end{equation}
-
-\noindent
-which indicates that a polymorphism can be maintained by various selective regimes.
-
-Given that a polymorphism is maintained at the $\mathbf{A}$ locus by weak selection, the frequencies of $A$ in each type of gamete are the same ($\hat{p}^\female_X=\hat{p}^\male_X=\hat{p}^\male_Y=\bar{p}$) and given, to leading order, by
-
-\begin{equation}
-\bar{p}=\frac{h^\female s^\female + h^\male s^\male +t^\female+t^\male+\alpha_{\Delta}^\female+\alpha_{\Delta}^\male}
-{(2h^\female-1)s^\female+(2h^\male-1)s^\male}
-+O(\epsilon)
-.
-\label{eq:pAve}
-\end{equation}
-
-\noindent
-Differences in frequency between gamete types are of $O(\epsilon)$:
-
-\begin{equation}
-\begin{split}
-\hat{p}^\male_X-\hat{p}^\female_X&=V_{A}\big{(}D^\male - D^\female +\alpha_{\Delta}^\male-\alpha_{\Delta}^\female \big{)}
-+O(\epsilon^2)\\
-%
-\hat{p}^\male_Y-\hat{p}^\female_X&=V_{A}\left[D^\male - D^\female+\alpha_{\Delta}^\male-\alpha_{\Delta}^\female+(1-2r)(t^\male-t^\female)\right]/2r
-+O(\epsilon^2)\\
-%
-\hat{p}^\male_Y-\hat{p}^\male_X&=V_{A}\left(D^\male - D^\female+\alpha_{\Delta}^\male-\alpha_{\Delta}^\female+t^\male-t^\female\right)(1-2r)/2r
-+O(\epsilon^2),
-\end{split}
-\label{eq:freq_diffs}
-\end{equation}
-
-\noindent
-where $V_{A}=\bar{p}(1-\bar{p})$ is the variance in the frequency of $A$ and $D^\Hermaphrodite=\big{[} \bar{p}s^\Hermaphrodite+(1-\bar{p})h^\Hermaphrodite s^\Hermaphrodite\big{]} -\big{[} \bar{p}h^\Hermaphrodite s^\Hermaphrodite+(1-\bar{p}) \big{]}$ corresponds to the difference in fitness between $A$ and $a$ alleles in diploids of sex $\Hermaphrodite \in \{\female,\male\}$.
-The frequency of Y-bearing male gametes depends upon the difference in the frequency of the $A$ allele between X- and Y-bearing male gametes and the strength of meiotic drive in favour of the $A$ allele in males, $q=1/2+\alpha_{\Delta}^\male(\hat{p}^\male_Y-\hat{p}^\male_X)/2+O(\epsilon^3)$.
-Without gametic competition or drive ($\alpha_{\Delta}^\Hermaphrodite=t^\Hermaphrodite=0$) our results reduce to those of~\cite{vanDoorn:2007eu}.
-
-\newpage
-
-\setcounter{equation}{0}
-\renewcommand{\theequation}{S3.\arabic{equation}}
-
-\section*{S3 Appendix}
-
-\subsection*{Invasion conditions}
-
-A rare neo-Y or neo-W allele, $m$, will spread in an XY sex-determining system when the leading eigenvalue, $\lambda_m^{(XY)}$, of the Jacobian matrix derived from the eight mutant recursion equations (given by \ref{eq:recursions}c,d,g,h), evaluated at the ancestral equilibrium, is greater than one.
-However, because a neo-Y (neo-W) is always in males (females) and is epistatically dominant to the ancestral sex-determining locus, the characteristic polynomial factors into two quadratics times $(\lambda_m^{(XY)})^4$.
-One quadratic governs the change in the frequency of the new sex determination factor associated with the $A$ and $a$ allele frequencies, summing across backgrounds at the old sex-determining locus (i.e., summing haplotypes bearing the original X and Y alleles).
-%It is the largest root of this quadratic that determines the spread of the new $m$ allele (see details in \nameref{file:Mathematica}).  
-The second quadratic describes the dynamics of the difference in the $m$-$A$ and $m$-$a$ haplotypes between X and Y backgrounds.  
-Asymptotically, this difference is constrained to grow at a rate equal to or less than the sum while the $m$ allele is rare, because the frequencies can never become negative. 
-We therefore focus on the leading eigenvalue, $\lambda_m^{(XY)}$, which is the largest root of the first quadratic $f(x) = x^2+ b x + c = 0$, as described in the text (details in \nameref{file:Mathematica}).
-
-When $R=0$ the two roots are $\Lambda_{mA}^{(XY)}$ and $\Lambda_{ma}^{(XY)}$, and the leading eigenvalue is the larger of the two.
-When $R>0$ then $f(\Lambda_{mA}^{(XY)})$ and $f(\Lambda_{ma}^{(XY)})$ are of opposite signs, and the leading eigenvalue must fall between these two quantities (details in \nameref{file:Mathematica}).
+%%I've added this in.
+%%It could also be the case that the slope and intercept are the same sign but the roots are imaginary - but this is never the case here.
+%%Stability condition below looks good to me (from matt version of turnoverSOM-MIKE.nb).}
+%
+%\subsubsection*{Selection weak relative to recombination}
+%
+%Here, we assume that selection is weak relative to recombination ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon$). 
+%The maintenance of a polymorphism at the $\mathbf{A}$ locus then requires that
+%
+%\begin{equation}
+%\begin{split}
+%0&< - \left[(1-h^\female)s^\female +(1-h^\male) s^\male + t^\female +t^\male + \alpha_{\Delta}^\female+\alpha_{\Delta}^\male\right]\\
+%%
+%\text{and }\quad 0&<h^\female s^\female +h^\male s^\male + t^\female +t^\male + \alpha_{\Delta}^\female+\alpha_{\Delta}^\male.
+%\end{split}
+%\end{equation}
+%
+%\noindent
+%which indicates that a polymorphism can be maintained by various selective regimes. 
+%
+%Given that a polymorphism is maintained at the $\mathbf{A}$ locus by weak selection, the frequencies of $A$ in each type of gamete are the same ($\hat{p}^\female_X=\hat{p}^\male_X=\hat{p}^\male_Y=\bar{p}$) and given, to leading order, by
+%
+%\begin{equation}
+%\bar{p}=\frac{h^\female s^\female + h^\male s^\male +t^\female+t^\male+\alpha_{\Delta}^\female+\alpha_{\Delta}^\male}
+%{(2h^\female-1)s^\female+(2h^\male-1)s^\male}
+%+O(\epsilon)
+%.
+%\label{eq:pAve}
+%\end{equation}
+%
+%\noindent
+%Differences in frequency between gamete types are of $O(\epsilon)$:
+%
+%\begin{equation}
+%\begin{split}
+%\hat{p}^\male_X-\hat{p}^\female_X&=V_{A}\big{(}D^\male - D^\female +\alpha_{\Delta}^\male-\alpha_{\Delta}^\female \big{)}
+%+O(\epsilon^2)\\
+%%
+%\hat{p}^\male_Y-\hat{p}^\female_X&=V_{A}\left[D^\male - D^\female+\alpha_{\Delta}^\male-\alpha_{\Delta}^\female+(1-2r)(t^\male-t^\female)\right]/2r
+%+O(\epsilon^2)\\
+%%
+%\hat{p}^\male_Y-\hat{p}^\male_X&=V_{A}\left(D^\male - D^\female+\alpha_{\Delta}^\male-\alpha_{\Delta}^\female+t^\male-t^\female\right)(1-2r)/2r
+%+O(\epsilon^2),
+%\end{split}
+%\label{eq:freq_diffs}
+%\end{equation}
+%
+%\noindent
+%where $V_{A}=\bar{p}(1-\bar{p})$ is the variance in the frequency of $A$ and $D^\Hermaphrodite=\big{[} \bar{p}s^\Hermaphrodite+(1-\bar{p})h^\Hermaphrodite s^\Hermaphrodite\big{]} -\big{[} \bar{p}h^\Hermaphrodite s^\Hermaphrodite+(1-\bar{p}) \big{]}$ corresponds to the difference in fitness between $A$ and $a$ alleles in diploids of sex $\Hermaphrodite \in \{\female,\male\}$.
+%The frequency of Y-bearing male gametes depends upon the difference in the frequency of the $A$ allele between X- and Y-bearing male gametes and the strength of meiotic drive in favour of the $A$ allele in males, $q=1/2+\alpha_{\Delta}^\male(\hat{p}^\male_Y-\hat{p}^\male_X)/2+O(\epsilon^3)$.
+%Without gametic competition or drive ($\alpha_{\Delta}^\Hermaphrodite=t^\Hermaphrodite=0$) our results reduce to those of~\cite{vanDoorn:2007eu}.
+
+%\newpage
+
+%\setcounter{equation}{0}
+%\renewcommand{\theequation}{S3.\arabic{equation}}
+%
+%\section*{S3 Appendix}
+%
+%\subsection*{Invasion conditions}
+%
+%A rare neo-Y or neo-W allele, $m$, will spread in an XY sex-determining system when the leading eigenvalue, $\lambda_m^{(XY)}$, of the Jacobian matrix derived from the eight mutant recursion equations (given by \ref{eq:recursions}c,d,g,h), evaluated at the ancestral equilibrium, is greater than one.
+%However, because a neo-Y (neo-W) is always in males (females) and is epistatically dominant to the ancestral sex-determining locus, the characteristic polynomial factors into two quadratics times $(\lambda_m^{(XY)})^4$.
+%One quadratic governs the change in the frequency of the new sex determination factor associated with the $A$ and $a$ allele frequencies, summing across backgrounds at the old sex-determining locus (i.e., summing haplotypes bearing the original X and Y alleles).
+%%It is the largest root of this quadratic that determines the spread of the new $m$ allele (see details in \nameref{file:Mathematica}).  
+%The second quadratic describes the dynamics of the difference in the $m$-$A$ and $m$-$a$ haplotypes between X and Y backgrounds.  
+%Asymptotically, this difference is constrained to grow at a rate equal to or less than the sum while the $m$ allele is rare, because the frequencies can never become negative. 
+%We therefore focus on the leading eigenvalue, $\lambda_m^{(XY)}$, which is the largest root of the first quadratic $f(x) = x^2+ b x + c = 0$, as described in the text (details in \nameref{file:Mathematica}).
+%
+%When $R=0$ the two roots are $\Lambda_{mA}^{(XY)}$ and $\Lambda_{ma}^{(XY)}$, and the leading eigenvalue is the larger of the two.
+%When $R>0$ then $f(\Lambda_{mA}^{(XY)})$ and $f(\Lambda_{ma}^{(XY)})$ are of opposite signs, and the leading eigenvalue must fall between these two quantities (details in \nameref{file:Mathematica}).
 %(the Perron-Frobenius theorem guarantees that the largest eigenvalue is positive, unique, and real).
-Thus, $\lambda_m^{(XY)}>1$ if both $\Lambda_{mA}^{(XY)}>1$ and $\Lambda_{ma}^{(XY)}>1$; similarly, $\lambda_m^{(XY)}<1$ if both $\Lambda_{mA}^{(XY)}<1$ and $\Lambda_{ma}^{(XY)}<1$.
-If only one haplotypic growth rate is greater than one ($\Lambda_{ma}^{(XY)}<1<\Lambda_{mA}^{(XY)}$ or $\Lambda_{mA}^{(XY)}<1<\Lambda_{ma}^{(XY)}$), then $\lambda_m^{(XY)}$ is greater than one when condition \eqref{eq:lambdasGen} is met.
-Thus, the invasion of a new sex-determining allele is determined by the haplotypic growth rates ($\Lambda_{mj}^{(XY)}$ terms), which do not account for loss due to recombination, and the rates at which recombination between the $\mathbf{M}$ and $\mathbf{A}$ loci breaks apart these haplotypes ($\chi_{mj}^{(XY)}$).
-For tight linkage between the ancestral sex-determining locus ($\mathbf{X}$) and the selected locus ($\mathbf{A}$) we can calculate these terms explicitly (see below).
-For weak selection we approximate the leading eigenvalue with a Taylor series. 
-The leading eigenvalue for any $k$ is given up to order $\epsilon^2$ by Eq \eqref{eq:lambda_ESD_k}.
-
-\subsubsection*{Tight linkage between $\mathbf{A}$ and $\mathbf{X}$ ($r \approx 0$)}
-
-Here, we explore the conditions under which a neo-W invades an XY system assuming that the $\mathbf{A}$ locus is initially in tight linkage with the ancestral sex-determining locus ($r \approx 0$). 
-We disregard neo-Y mutations, which never spread given that the ancestral population is at a stable equilibrium (see \nameref{file:Mathematica} for proof).
-
-Starting with the simpler $(B)$ equilibrium, the terms that determine the leading eigenvalue are
-
-\begin{subequations}\label{Binvasion}
-\begin{align}
-\Lambda_{W'A}^{(XY)}&= {\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]}^{-1}
-\frac{w_{A}^\female }{w_{A}^\female}
-\frac{\left[ w_{A}^\male (1+\alpha^\male_\Delta) w_{AA}^\female + 
-w_{a}^\male (1-\alpha^\male_\Delta) w_{Aa}^\female (1+\alpha^\female_\Delta) \right]}
-{ 2w_{AA}^\female } \\
-\Lambda_{W'a}^{(XY)}&= {\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]}^{-1}
-\frac{w_{a}^\female}{w_{A}^\female}
-\frac{\left[  w_{A}^\male (1+\alpha^\male_\Delta) w_{Aa}^\female (1-\alpha^\female_\Delta)+
-w_{a}^\male (1-\alpha^\male_\Delta) w_{aa}^\female \right]}
-{ 2w_{AA}^\female } \\
-\chi_{W'A}^{(XY)}&= \frac{1}{2} {\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]}^{-1}
-\frac{w_{A}^\female }{w_{A}^\female}
- \frac{\left[  w_{a}^\male (1-\alpha^\male_\Delta) w_{Aa}^\female (1 + \alpha^\female_\Delta) \right]}
-{ w_{AA}^\female } \frac{R}{2}\\
-\chi_{W'a}^{(XY)}&= \frac{1}{2} {\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]}^{-1}
-\frac{w_{a}^\female}{w_{A}^\female}
- \frac{\left[  w_{A}^\male (1+\alpha^\male_\Delta) w_{Aa}^\female (1-\alpha^\female_\Delta) \right]}
-{  w_{AA}^\female} \frac{R}{2}.
-\end{align}
-\end{subequations}
-
+%Thus, $\lambda_m^{(XY)}>1$ if both $\Lambda_{mA}^{(XY)}>1$ and $\Lambda_{ma}^{(XY)}>1$; similarly, $\lambda_m^{(XY)}<1$ if both $\Lambda_{mA}^{(XY)}<1$ and $\Lambda_{ma}^{(XY)}<1$.
+%If only one haplotypic growth rate is greater than one ($\Lambda_{ma}^{(XY)}<1<\Lambda_{mA}^{(XY)}$ or $\Lambda_{mA}^{(XY)}<1<\Lambda_{ma}^{(XY)}$), then $\lambda_m^{(XY)}$ is greater than one when condition \eqref{eq:lambdasGen} is met.
+%Thus, the invasion of a new sex-determining allele is determined by the haplotypic growth rates ($\Lambda_{mj}^{(XY)}$ terms), which do not account for loss due to recombination, and the rates at which recombination between the $\mathbf{M}$ and $\mathbf{A}$ loci breaks apart these haplotypes ($\chi_{mj}^{(XY)}$).
+%For tight linkage between the ancestral sex-determining locus ($\mathbf{X}$) and the selected locus ($\mathbf{A}$) we can calculate these terms explicitly (see below).
+%For weak selection we approximate the leading eigenvalue with a Taylor series. 
+%The leading eigenvalue for any $k$ is given up to order $\epsilon^2$ by Eq \eqref{eq:lambda_ESD_k}.
+%
+%\subsubsection*{Tight linkage between $\mathbf{A}$ and $\mathbf{X}$ ($r \approx 0$)}
+%
+%Here, we explore the conditions under which a neo-W invades an XY system assuming that the $\mathbf{A}$ locus is initially in tight linkage with the ancestral sex-determining locus ($r \approx 0$). 
+%We disregard neo-Y mutations, which never spread given that the ancestral population is at a stable equilibrium (see \nameref{file:Mathematica} for proof). 
+%
+%Starting with the simpler $(B)$ equilibrium, the terms that determine the leading eigenvalue are
+%
+%\begin{subequations}\label{Binvasion}
+%\begin{align}
+%\Lambda_{W'A}^{(XY)}&= {\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]}^{-1}
+%\frac{w_{A}^\female }{w_{A}^\female}
+%\frac{\left[ w_{A}^\male (1+\alpha^\male_\Delta) w_{AA}^\female + 
+%w_{a}^\male (1-\alpha^\male_\Delta) w_{Aa}^\female (1+\alpha^\female_\Delta) \right]}
+%{ 2w_{AA}^\female } \\
+%\Lambda_{W'a}^{(XY)}&= {\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]}^{-1}
+%\frac{w_{a}^\female}{w_{A}^\female}
+%\frac{\left[  w_{A}^\male (1+\alpha^\male_\Delta) w_{Aa}^\female (1-\alpha^\female_\Delta)+
+%w_{a}^\male (1-\alpha^\male_\Delta) w_{aa}^\female \right]}
+%{ 2w_{AA}^\female } \\
+%\chi_{W'A}^{(XY)}&= \frac{1}{2} {\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]}^{-1}
+%\frac{w_{A}^\female }{w_{A}^\female}
+% \frac{\left[  w_{a}^\male (1-\alpha^\male_\Delta) w_{Aa}^\female (1 + \alpha^\female_\Delta) \right]}
+%{ w_{AA}^\female } \frac{R}{2}\\
+%\chi_{W'a}^{(XY)}&= \frac{1}{2} {\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]}^{-1}
+%\frac{w_{a}^\female}{w_{A}^\female}
+% \frac{\left[  w_{A}^\male (1+\alpha^\male_\Delta) w_{Aa}^\female (1-\alpha^\female_\Delta) \right]}
+%{  w_{AA}^\female} \frac{R}{2}.
+%\end{align}
+%\end{subequations}
+%
+%%\noindent
+%%In this case, the zygotic sex ratio ($\zeta$) is given by the difference in haploid selection in males on $a$ (fixed on the Y) and $A$ (fixed on the X) alleles, i.e., there are more males than females if $\zeta = \alpha^\male w_A^\male / [(1-\alpha^\male)w_a^\male + \alpha^\male w_A^\male]<1/2$.
+%$\alpha^\male<1/2$ and/or $w_{a}^\male>w_{A}^\male$.
+%%Populations with haploid selection for $a$ in males have a male biased zygotic sex ratio are thus more permissive to invasion by a neo-W ($\Lambda_{mA}$ and $\Lambda_{ma}$ larger).
+%%%In addition, the spread of neo-W alleles depends on the fitness of female diploids after mating with an X-$A$ or Y-$a$ male gamete, relative to the fitness of females in the population (all have genotype $AA$ and fitness $w_{AA}^\female$ at this equilibrium).
+%%Haploid selection in males has a second effect; the spread rate of neo-W haplotypes is determined by their fitness in diploid females, which depends on their diploid genotype and thus on the male gamete they pair with.
+%%Zygotes carrying dominant neo-W alleles will develop as females regardless of their genotype at the XY locus. 
+%%Therefore, neo-W females result from matings with either X-$A$ or Y-$a$ male gametes. 
+%%The relative proportion of these male gametes is determined by haploid selection in males; mating with a Y-$a$ male gamete is more likely if the $a$ allele is favoured during male gamete production or competition ($\zeta<1/2$).
+%%Thus, neo-W females experience different diploid selection than XX females, and the extent of this difference depends on haploid selection in males.
+%%Furthermore, haploid selection in females can directly select upon neo-W-$A$ or neo-W-$a$ haplotypes. 
+%%A neo-W-$A$ female gamete has the same fitness during haploid competition as resident $A$-bearing female gametes. 
+%%On the other hand, neo-W-$a$ female gametes can be favoured or disfavoured during female haploid competition (favoured if $w_{a}^\female>w_{A}^\female$). 
+%%Meiotic drive in females ($\alpha^\female$) similarly affects the fitness of these neo-W haplotypes, except that it impacts both haplotypes as meiotic drive only occurs in heterozygotes and therefore does not occur in resident XX females (who are always homozygote $AA$).
+%
+%Haploid selection impacts the spread of neo-W haplotypes in three ways (also seen in Table \ref{tab:haplotype_growth}).
+%Firstly, the zygotic sex ratio becomes male biased, $\zeta>1/2$, when the $a$ allele (which is fixed on the Y) is favoured during competition among male gametes or by meiotic drive in males.
+%Specifically, at equilibrium $(B)$, female zygote frequency is $1 - \zeta = w_A^\male (1+\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$ where $2\bar{w}_{H}^\male= \big[w_a^\male (1-\alpha^\male_\Delta) +  w_A^\male (1+\alpha^\male_\Delta) \big]$ has been canceled out in equations \eqref{Binvasion} to leave the term ${\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]}^{-1}$.
+%Male biased sex ratios facilitate the spread of a neo-W because neo-W alleles cause the zygotes that carry them to develop as the rarer, female, sex. 
+%
+%Secondly, haploid selection in females selects on neo-W haplotypes directly.
+%At equilibrium $(B)$, the fitness of female gametes under the ancestral sex-determining system is $w_{A}^\female$ such that the relative fitnesses of neo-W-$A$ and neo-W-$a$ haplotypes during female gametic competition are $w_{A}^\female/w_{A}^\female$ and $w_{a}^\female/w_{A}^\female$ (see terms in equation \ref{Binvasion}).
+%Meiotic drive in females will also change the proportion of gametes that carry the $A$ versus $a$ alleles, which will be produced by heterozygous females in proportions $(1+\alpha_{\Delta}^\female)/2$ and $(1-\alpha_{\Delta}^\female)/2$, respectively.
+%These terms are only associated with heterozygous females, i.e., they are found alongside $w_{Aa}^\female$.
+%
+%Thirdly, haploid selection in males affects the diploid genotypes of females by altering the allele frequencies in the male gametes with which female gametes pair.
+%At equlibrium $(B)$, neo-W female gametes will mate with X-$A$ male gametes with probability $ w_A^\male (1+\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$ and Y-$a$ male gametes with probability $w_a^\male (1-\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$, where the $2\bar{w}_{H}^\male$ terms have been canceled in Eq \eqref{Binvasion} (as mentioned above).
+%Thus, neo-W-$A$ haplotypes are found in $AA$ female diploids with probability $ w_A^\male (1+\alpha^\male_\Delta)/ (2\bar{w}_{H}^\male)$ (e.g., first term in square brackets in the numerator of equation \ref{Binvasion}a) and in $Aa$ female diploids with probability $w_a^\male (1-\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$ (e.g., the second term in square brackets in the numerator of equation \ref{Binvasion}a).
+%
+%%For instance, because an epistatically dominant neo-W always causes its carrier to become female, it creates females who carry either Y-$a$ or X-$A$ genotypes from their father.
+%%Thus, because when there is a polymorphism the X carries some non-zero frequency of $A$, haploid selection in males impacts the diploid genotypes of females (e.g., creating more $Aa$ females when drive in males favours Y-$a$).
+%%How this affects the spread of the neo-W then depends on diploid and haploid selection in females.
+%
+%The other terms in equations \eqref{Binvasion} are more easily interpreted if we assume that there is no haploid selection in either sex, in which case $\Lambda_{W'A}^{(XY)}=(w_{AA}^\female+w_{Aa}^\female)/2 w_{AA}^\female$ and $\Lambda_{W'a}^{(XY)}=(w_{aa}^\female+w_{Aa}^\female)/ 2 w_{AA}^\female$.
+%Neither haplotype can spread under purely sexually-antagonistic selection at equilibrium $(B)$, with directional selection in each sex.
+%Essentially, the X is then already as specialized as possible for the female beneficial allele ($A$ is fixed on the X background), and the neo-W often makes daughters with the Y-$a$ haplotype, increasing the flow of $a$ alleles into females, which reduces the fitness of those females.
+%
+%If selection doesn't uniformly favour $A$ in females, however, neo-W-$A$ haplotypes and/or neo-W-$a$ haplotypes can spread ($\Lambda_{W'A}^{(XY)}>1$ and/or $\Lambda_{W'a}^{(XY)}>1$).
+%%If $\Lambda_{mA}>1$ (requiring $w_{Aa}^\female>w_{AA}^\female$), the implication is that the neo-W can spread alongside the $A$ allele, despite the fact that the neo-W sometimes brings $Y-a$ haplotypes into females, because $a$ is favoured by selection in females despite $A$ being fixed on the X.
+%A neo-W-$A$ haplotype can spread ($\Lambda_{W'A}^{(XY)}>1$) when $w_{Aa}^\female>w_{AA}^\female$, despite the fact that a neo-W brings Y-$a$ haplotypes into females.
+%In this case the $a$ allele is favoured by selection in females despite $A$ being fixed on the X background.
+%For this equilibrium to be stable (i.e.,  to keep $A$ fixed on the X), X-$a$ cannot be overly favoured in females and X-$A$ must be sufficiently favoured in males (for example, by overdominance in males).
+%Specifically, from the stability conditions for equilibrium (B), we must have $w_{Aa}^\female < 2 w_{AA}^\female$ and $w_{Aa}^\male/\big[(w_{aa}^\male+w_{Aa}^\male)/2\big]>w_{Aa}^\female/w_{AA}^\female$.
+%
+%Still considering $w_{Aa}^\female>w_{AA}^\female$, the neo-W can also spread alongside the $a$ allele ($\Lambda_{W'a}^{(XY)}>1$) if $w_{aa}^\female$ is large enough such that $(w_{Aa}^\female+w_{aa}^\female)/2>w_{AA}^\female$.
+%%there is sufficiently strong underdominance in females ($w_{aa}^\female>w_{Aa}^\female$) \textcolor{blue}{[this is describing directional selection, not overdominance - check the conditions for the case we want to talk about]}, such that $(w_{Aa}^\female+w_{aa}^\female)/2>w_{AA}^\female$.
+%This can occur with overdominance or directional selection for $a$ in females (Fig \ref{fig:regionplots}B,C).
+%In this case, $a$ is favoured on the ancestral Y background in males and on the ancestral X background in females (comparing $Aa$ to $AA$ genotypes in females) but $A$ is fixed on the X background due to selection in males.
+%The neo-W-$a$ haplotype can spread because it produces females with higher fitness $Aa$ and $aa$ genotypes. 
+%
+%%When both haplotypes can spread on their own ($\Lambda_{mA}>1$ and $\Lambda_{ma}>1$), the neo-W invades regardless the recombination rate between it and the selected locus, $R$.
+%%When neither haplotype can spread ($\Lambda_{mA}<1$ and $\Lambda_{ma}<1$) the neo-W can never invade.
+%%And when only one haplotype can spread on its own the neo-W invades only when the rate of recombination onto the favourable background is sufficiently larger than the rate of recombination off this background (i.e., equation\ref{eq:lambdasGen} is satisfied).
+%
+%%Haploid selection affects the conclusions outlined above by altering the zygotic sex ratio and exerting direct selection on neo-W haplotypes.
+%%The effect of sex ratio selection is straightforward and can be seen in Eq \eqref{Binvasion}, where male drive and gamete competition for $a$ (which is fixed on the Y and therefore causes a male bias) increases all four terms.
+%%Direct selection on neo-W haplotypes can also be seen in Eq \eqref{Binvasion} by noticing that increasing female drive in favour of $A$ increases the neo-W-$A$ haplotype growth rate ($\Lambda_{mA}$) while female drive and gamete competition in favour of $a$ increases the neo-W-$a$ haplotype growth rate ($\Lambda_{ma}$).
+%%Gamete competition in females does not impact the spread of neo-W-$A$ haplotypes because they are on the same background as the resident X.
+%%Recombination between the selected locus and the neo-W complicates things slightly, as selective advantages for one neo-W haplotype during the haploid stage in females comes at a cost to the other, and thus recombination off the favoured background becomes more detrimental.
+%
+%%\textcolor{red}{the versions for equil $(A)$ are not terrible but could be improved by cleverly re-writing with the $\phi$ and $\psi$ terms from above, I think...}
+%
+%Similar equations can be derived for equilibrium (A) by substituting the equilibrium frequencies into Table \ref{tab:haplotype_growth}
+%
+%\begin{subequations}\label{Ainvasion}
+%\begin{align}
+%\Lambda_{W'A}^{(XY)}&= \frac{a}{b} \left[w_{AA}^\female w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi +  w_{Aa}^\female (1+\alpha^\female_\Delta) w_a^\male c \right] / (2 w_a^\female) \\
+%\Lambda_{W'a}^{(XY)}&= \frac{a}{b} \left[ w_{Aa}^\female (1-\alpha^\female_\Delta) w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi +  w_{aa}^\female w_a^\male c \right] / (2 w_A^\female) \\
+%\chi_{W'A}^{(XY)}&= \frac{a}{b} \frac{R}{2} \left[   w_{Aa}^\female (1+\alpha^\female_\Delta) w_a^\male c \right] / w_a^\female\\ 
+%\chi_{W'a}^{(XY)}&= \frac{a}{b} \frac{R}{2} \left[ w_{Aa}^\female (1-\alpha^\female_\Delta) w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi \right] / w_A^\female,
+%%\Lambda_{W'A}^{(XY)}&=   {\left[ 2 (1 - \zeta) \right]}^{-1} w_A^{\female} \left[ b w_{AA}^\female + c w_{Aa}^\female \left(1 - \alpha^\female_\Delta \right) \right]/ \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\female}_{D} \right)  \\
+%%\Lambda_{W'a}^{(XY)}&=  \\
+%%\chi_{W'A}^{(XY)}&= \\ 
+%%\chi_{W'a}^{(XY)}&=
+%\end{align}
+%\end{subequations}
+%
 %\noindent
-%In this case, the zygotic sex ratio ($\zeta$) is given by the difference in haploid selection in males on $a$ (fixed on the Y) and $A$ (fixed on the X) alleles, i.e., there are more males than females if $\zeta = \alpha^\male w_A^\male / [(1-\alpha^\male)w_a^\male + \alpha^\male w_A^\male]<1/2$.
-%$\alpha^\male<1/2$ and/or $w_{a}^\male>w_{A}^\male$.
-%Populations with haploid selection for $a$ in males have a male biased zygotic sex ratio are thus more permissive to invasion by a neo-W ($\Lambda_{mA}$ and $\Lambda_{ma}$ larger).
-%%In addition, the spread of neo-W alleles depends on the fitness of female diploids after mating with an X-$A$ or Y-$a$ male gamete, relative to the fitness of females in the population (all have genotype $AA$ and fitness $w_{AA}^\female$ at this equilibrium).
-%Haploid selection in males has a second effect; the spread rate of neo-W haplotypes is determined by their fitness in diploid females, which depends on their diploid genotype and thus on the male gamete they pair with.
-%Zygotes carrying dominant neo-W alleles will develop as females regardless of their genotype at the XY locus. 
-%Therefore, neo-W females result from matings with either X-$A$ or Y-$a$ male gametes. 
-%The relative proportion of these male gametes is determined by haploid selection in males; mating with a Y-$a$ male gamete is more likely if the $a$ allele is favoured during male gamete production or competition ($\zeta<1/2$).
-%Thus, neo-W females experience different diploid selection than XX females, and the extent of this difference depends on haploid selection in males.
-%Furthermore, haploid selection in females can directly select upon neo-W-$A$ or neo-W-$a$ haplotypes. 
-%A neo-W-$A$ female gamete has the same fitness during haploid competition as resident $A$-bearing female gametes. 
-%On the other hand, neo-W-$a$ female gametes can be favoured or disfavoured during female haploid competition (favoured if $w_{a}^\female>w_{A}^\female$). 
-%Meiotic drive in females ($\alpha^\female$) similarly affects the fitness of these neo-W haplotypes, except that it impacts both haplotypes as meiotic drive only occurs in heterozygotes and therefore does not occur in resident XX females (who are always homozygote $AA$).
-
-Haploid selection impacts the spread of neo-W haplotypes in three ways (also seen in Table \ref{tab:haplotype_growth}).
-Firstly, the zygotic sex ratio becomes male biased, $\zeta>1/2$, when the $a$ allele (which is fixed on the Y) is favoured during competition among male gametes or by meiotic drive in males.
-Specifically, at equilibrium $(B)$, female zygote frequency is $1 - \zeta = w_A^\male (1+\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$ where $2\bar{w}_{H}^\male= \big[w_a^\male (1-\alpha^\male_\Delta) +  w_A^\male (1+\alpha^\male_\Delta) \big]$ has been canceled out in equations \eqref{Binvasion} to leave the term ${\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]}^{-1}$.
-Male biased sex ratios facilitate the spread of a neo-W because neo-W alleles cause the zygotes that carry them to develop as the rarer, female, sex.
-
-Secondly, haploid selection in females selects on neo-W haplotypes directly.
-At equilibrium $(B)$, the fitness of female gametes under the ancestral sex-determining system is $w_{A}^\female$ such that the relative fitnesses of neo-W-$A$ and neo-W-$a$ haplotypes during female gametic competition are $w_{A}^\female/w_{A}^\female$ and $w_{a}^\female/w_{A}^\female$ (see terms in equation \ref{Binvasion}).
-Meiotic drive in females will also change the proportion of gametes that carry the $A$ versus $a$ alleles, which will be produced by heterozygous females in proportions $(1+\alpha_{\Delta}^\female)/2$ and $(1-\alpha_{\Delta}^\female)/2$, respectively.
-These terms are only associated with heterozygous females, i.e., they are found alongside $w_{Aa}^\female$.
-
-Thirdly, haploid selection in males affects the diploid genotypes of females by altering the allele frequencies in the male gametes with which female gametes pair.
-At equlibrium $(B)$, neo-W female gametes will mate with X-$A$ male gametes with probability $ w_A^\male (1+\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$ and Y-$a$ male gametes with probability $w_a^\male (1-\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$, where the $2\bar{w}_{H}^\male$ terms have been canceled in Eq \eqref{Binvasion} (as mentioned above).
-Thus, neo-W-$A$ haplotypes are found in $AA$ female diploids with probability $ w_A^\male (1+\alpha^\male_\Delta)/ (2\bar{w}_{H}^\male)$ (e.g., first term in square brackets in the numerator of equation \ref{Binvasion}a) and in $Aa$ female diploids with probability $w_a^\male (1-\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$ (e.g., the second term in square brackets in the numerator of equation \ref{Binvasion}a).
-
-%For instance, because an epistatically dominant neo-W always causes its carrier to become female, it creates females who carry either Y-$a$ or X-$A$ genotypes from their father.
-%Thus, because when there is a polymorphism the X carries some non-zero frequency of $A$, haploid selection in males impacts the diploid genotypes of females (e.g., creating more $Aa$ females when drive in males favours Y-$a$).
-%How this affects the spread of the neo-W then depends on diploid and haploid selection in females.
-
-The other terms in equations \eqref{Binvasion} are more easily interpreted if we assume that there is no haploid selection in either sex, in which case $\Lambda_{W'A}^{(XY)}=(w_{AA}^\female+w_{Aa}^\female)/2 w_{AA}^\female$ and $\Lambda_{W'a}^{(XY)}=(w_{aa}^\female+w_{Aa}^\female)/ 2 w_{AA}^\female$.
-Neither haplotype can spread under purely sexually-antagonistic selection at equilibrium $(B)$, with directional selection in each sex.
-Essentially, the X is then already as specialized as possible for the female beneficial allele ($A$ is fixed on the X background), and the neo-W often makes daughters with the Y-$a$ haplotype, increasing the flow of $a$ alleles into females, which reduces the fitness of those females.
-
-If selection doesn't uniformly favour $A$ in females, however, neo-W-$A$ haplotypes and/or neo-W-$a$ haplotypes can spread ($\Lambda_{W'A}^{(XY)}>1$ and/or $\Lambda_{W'a}^{(XY)}>1$).
-%If $\Lambda_{mA}>1$ (requiring $w_{Aa}^\female>w_{AA}^\female$), the implication is that the neo-W can spread alongside the $A$ allele, despite the fact that the neo-W sometimes brings $Y-a$ haplotypes into females, because $a$ is favoured by selection in females despite $A$ being fixed on the X.
-A neo-W-$A$ haplotype can spread ($\Lambda_{W'A}^{(XY)}>1$) when $w_{Aa}^\female>w_{AA}^\female$, despite the fact that a neo-W brings Y-$a$ haplotypes into females.
-In this case the $a$ allele is favoured by selection in females despite $A$ being fixed on the X background.
-For this equilibrium to be stable (i.e.,  to keep $A$ fixed on the X), X-$a$ cannot be overly favoured in females and X-$A$ must be sufficiently favoured in males (for example, by overdominance in males).
-Specifically, from the stability conditions for equilibrium (B), we must have $w_{Aa}^\female < 2 w_{AA}^\female$ and $w_{Aa}^\male/\big[(w_{aa}^\male+w_{Aa}^\male)/2\big]>w_{Aa}^\female/w_{AA}^\female$.
-
-Still considering $w_{Aa}^\female>w_{AA}^\female$, the neo-W can also spread alongside the $a$ allele ($\Lambda_{W'a}^{(XY)}>1$) if $w_{aa}^\female$ is large enough such that $(w_{Aa}^\female+w_{aa}^\female)/2>w_{AA}^\female$.
-%there is sufficiently strong underdominance in females ($w_{aa}^\female>w_{Aa}^\female$) \textcolor{blue}{[this is describing directional selection, not overdominance - check the conditions for the case we want to talk about]}, such that $(w_{Aa}^\female+w_{aa}^\female)/2>w_{AA}^\female$.
-This can occur with overdominance or directional selection for $a$ in females (Fig \ref{fig:regionplots}B,C).
-In this case, $a$ is favoured on the ancestral Y background in males and on the ancestral X background in females (comparing $Aa$ to $AA$ genotypes in females) but $A$ is fixed on the X background due to selection in males.
-The neo-W-$a$ haplotype can spread because it produces females with higher fitness $Aa$ and $aa$ genotypes.
-
-%When both haplotypes can spread on their own ($\Lambda_{mA}>1$ and $\Lambda_{ma}>1$), the neo-W invades regardless the recombination rate between it and the selected locus, $R$.
-%When neither haplotype can spread ($\Lambda_{mA}<1$ and $\Lambda_{ma}<1$) the neo-W can never invade.
-%And when only one haplotype can spread on its own the neo-W invades only when the rate of recombination onto the favourable background is sufficiently larger than the rate of recombination off this background (i.e., equation\ref{eq:lambdasGen} is satisfied).
-
-%Haploid selection affects the conclusions outlined above by altering the zygotic sex ratio and exerting direct selection on neo-W haplotypes.
-%The effect of sex ratio selection is straightforward and can be seen in Eq \eqref{Binvasion}, where male drive and gamete competition for $a$ (which is fixed on the Y and therefore causes a male bias) increases all four terms.
-%Direct selection on neo-W haplotypes can also be seen in Eq \eqref{Binvasion} by noticing that increasing female drive in favour of $A$ increases the neo-W-$A$ haplotype growth rate ($\Lambda_{mA}$) while female drive and gamete competition in favour of $a$ increases the neo-W-$a$ haplotype growth rate ($\Lambda_{ma}$).
-%Gamete competition in females does not impact the spread of neo-W-$A$ haplotypes because they are on the same background as the resident X.
-%Recombination between the selected locus and the neo-W complicates things slightly, as selective advantages for one neo-W haplotype during the haploid stage in females comes at a cost to the other, and thus recombination off the favoured background becomes more detrimental.
-
-%\textcolor{red}{the versions for equil $(A)$ are not terrible but could be improved by cleverly re-writing with the $\phi$ and $\psi$ terms from above, I think...}
-
-Similar equations can be derived for equilibrium (A) by substituting the equilibrium frequencies into Table \ref{tab:haplotype_growth}
-
-\begin{subequations}\label{Ainvasion}
-\begin{align}
-\Lambda_{W'A}^{(XY)}&= \frac{a}{b} \left[w_{AA}^\female w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi +  w_{Aa}^\female (1+\alpha^\female_\Delta) w_a^\male c \right] / (2 w_a^\female) \\
-\Lambda_{W'a}^{(XY)}&= \frac{a}{b} \left[ w_{Aa}^\female (1-\alpha^\female_\Delta) w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi +  w_{aa}^\female w_a^\male c \right] / (2 w_A^\female) \\
-\chi_{W'A}^{(XY)}&= \frac{a}{b} \frac{R}{2} \left[   w_{Aa}^\female (1+\alpha^\female_\Delta) w_a^\male c \right] / w_a^\female\\ 
-\chi_{W'a}^{(XY)}&= \frac{a}{b} \frac{R}{2} \left[ w_{Aa}^\female (1-\alpha^\female_\Delta) w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi \right] / w_A^\female,
-%\Lambda_{W'A}^{(XY)}&=   {\left[ 2 (1 - \zeta) \right]}^{-1} w_A^{\female} \left[ b w_{AA}^\female + c w_{Aa}^\female \left(1 - \alpha^\female_\Delta \right) \right]/ \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\female}_{D} \right)  \\
-%\Lambda_{W'a}^{(XY)}&=  \\
-%\chi_{W'A}^{(XY)}&= \\ 
-%\chi_{W'a}^{(XY)}&=
-\end{align}
-\end{subequations}
-
-\noindent
-where
-
-\begin{subequations}
-\begin{align}
-a &= w_a^\female \phi + w_A^\female \psi \\
-b &= w_{AA}^\female \left[ w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \right] \phi^2 + w_{Aa}^\female \left[ w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) + w_{aa}^\male w_a^\male \right] \psi \phi + w_{aa}^\female \left( w_{aa}^\male w_a^\male \right) \psi^2\\
-%c &= w_{Aa}^\male (1-\alpha^\male_\Delta) \phi \left[ w_{Aa}^\male (1+\alpha^\male_\Delta) \phi \right] + w_{Aa}^\male\phi \left[ 2w_{AA}^\male + w_{aa}^\male (1+\alpha^\male_\Delta) \right] \psi + w_{aa}^\male \psi \left(2w_{AA}^\male \psi \right) \\
-c &= w_{Aa}^\male (1-\alpha^\male_\Delta) \phi + 2w_{aa}^\male \psi.
-\end{align}
-\end{subequations}
-
-%\textcolor{red}{Sally suggests using some $\zeta$ term in the above equations}
-%\textcolor{blue}{Maybe just reference table 2?}
-
-As with equilibrium (B), haploid selection again modifies invasion fitnesses by altering the ancestral sex ratio, $\zeta$ (see Table \ref{tab:haplotype_growth}), and directly selecting upon female gametes, through $w_{i}^\female$.
-The only difference is that resident XX females are no longer always homozygote $AA$ and males are no longer always heterozygote $Aa$.
-Thus the effect of haploid selection in males is reduced, as is the difference in fitness between neo-W haplotypes and resident X haplotypes, as both can be on any diploid or haploid background.
-
-The other terms are easier to interpret in the absence of haploid selection.
-For instance, without haploid selection, the neo-W-$A$ haplotype spreads ($\Lambda_{W'A}^{(XY)}>1$) if and only if
-
-\begin{equation}\label{eq:BeqWAspread}
-2(w_{Aa}^\female-w_{aa}^\female)w_{aa}^\male \psi^2 > (w_{AA}^\female-w_{Aa}^\female)w_{Aa}^\male \phi (\phi-\psi),
-\end{equation}
-
-\noindent  
-where $\phi-\psi=w_{AA}^\female w_{Aa}^\male-w_{aa}^\female w_{aa}^\male$ and both $\phi$ and $\psi$ are positive when equilibrium (A) is stable. 
-In contrast to equilibrium (B), a neo-W haplotype can spread under purely sexually-antagonistic selection  ($w_{aa}^\female<w_{Aa}^\female<w_{AA}^\female$ and $w_{AA}^\male<w_{Aa}^\male<w_{aa}^\male$).
-The neo-W-$A$ can spread as long as it becomes associated with females that bear more $A$ alleles than observed at equilibrium (A), effectively specializing on female fitness. 
-%In this case, the neo-W-$A$ haplotype can spread, despite producing a lot of $Aa$ daughters by obtaining the $a$ from Y-gametes, when $aa$ females, which the neo-W-$A$ never makes, are strongly selected against.
-%This can be intuited from the fact that \eqref{eq:BeqWAspread} will be more easily met when $w_{Aa}^\female-w_{aa}^\female\approx w_{Aa}^\female$ and $w_{AA}^\female-w_{Aa}^\female\approx 0$, implying $w_{aa}^\female \approx 0$ and $w_{Aa}^\female\approx w_{AA}^\female$ (although this is complicated by the fact that $w_{aa}^\female$ and $w_{Aa}^\female$ affect $\phi$ and $\psi$ too, the intuition holds).
-
-Without haploid selection, the neo-W-$a$ haplotype spreads ($\Lambda_{W'a}^{(XY)}>1$) if and only if
-
-\begin{equation}\label{eq:BeqWaspread}
-(w_{aa}^\female + w_{Aa}^\female-2w_{AA}^\female)w_{Aa}^\male \phi^2 + (w_{aa}^\female-w_{Aa}^\female)(w_{Aa}^\male+2w_{aa}^\male) \phi \psi >0.
-\end{equation}
-
-\noindent
-This condition cannot be met with purely sexually antagonistic selection (as both terms on the left-hand side would then be negative), but it can be met under other circumstances. 
-For example, with overdominance in males there is selection for increased $A$ frequencies on the X background in males, which are always paired with Y-$a$ haplotypes.
-Directional selection for $a$ in females can then maintain a polymorphism at the $\mathbf{A}$ locus on the X background.
-This scenario selects for a modifier that increases recombination between the sex chromosomes (e.g., blue region of Fig 2d in~\cite{Otto2014}) and facilitates the spread of neo-W-$a$ haplotypes, which create females bearing more $a$ alleles than the ancestral X haplotype does.
-
-\subsubsection*{Role of haploid selection with tight linkage between $\mathbf{X}$ and $\mathbf{A}$ loci}
-
-Haploid selection generally expands the conditions under which neo-W alleles can spread within ancestral systems that have evolved tight linkage between the sex-determining locus and a selected locus ($r \approx 0$).
-First, haploid selection can allow a polymorphism to be maintained when it would not under diploid selection alone (e.g., with directional selection in diploids). 
-In cases of ploidally-antagonistic selection, where there is a balance between alleles favored in the haploid stage and the diploid stage, neo-W alleles - even if unlinked to the selected locus - can spread (\nameref{fig:regionPloidAntag}).
-Second, even when diploid selection could itself maintain a polymorphism, haploid selection can increase the conditions under which transitions among sex-determining systems are possible.
-Of particularly importance, when selection is sexually-antagonistic in diploids ($s^\female s^\male <0$ and $0<h^\Hermaphrodite<1$), an unlinked neo-W ($R=1/2$) cannot invade unless there is also haploid selection (see proof in \nameref{file:Mathematica}; Fig \ref{fig:SexAntagTighter} and \nameref{fig:SexAntagTighterMaleDrive}).
-More generally, haploid selection alters the conditions under which neo-W alleles can spread (compare \nameref{fig:regionMaleDrive}-\nameref{fig:regionFemaleGS} to Fig \ref{fig:regionplots}).
-
-%[SALLY:  I think that is enough, but we could add somewhere??: "Without haploid selection, unlinked neo-W alleles ($R=1/2$) can invade only under certain conditions, requiring either overdominance in males or underdominance in females (see proof in supplementary \textit{Mathematica} file).?
+%where 
+%
+%\begin{subequations}
+%\begin{align}
+%a &= w_a^\female \phi + w_A^\female \psi \\
+%b &= w_{AA}^\female \left[ w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \right] \phi^2 + w_{Aa}^\female \left[ w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) + w_{aa}^\male w_a^\male \right] \psi \phi + w_{aa}^\female \left( w_{aa}^\male w_a^\male \right) \psi^2\\
+%%c &= w_{Aa}^\male (1-\alpha^\male_\Delta) \phi \left[ w_{Aa}^\male (1+\alpha^\male_\Delta) \phi \right] + w_{Aa}^\male\phi \left[ 2w_{AA}^\male + w_{aa}^\male (1+\alpha^\male_\Delta) \right] \psi + w_{aa}^\male \psi \left(2w_{AA}^\male \psi \right) \\
+%c &= w_{Aa}^\male (1-\alpha^\male_\Delta) \phi + 2w_{aa}^\male \psi.
+%\end{align}
+%\end{subequations}
+%
+%%\textcolor{red}{Sally suggests using some $\zeta$ term in the above equations}
+%%\textcolor{blue}{Maybe just reference table 2?}
+%
+%As with equilibrium (B), haploid selection again modifies invasion fitnesses by altering the ancestral sex ratio, $\zeta$ (see Table \ref{tab:haplotype_growth}), and directly selecting upon female gametes, through $w_{i}^\female$.
+%The only difference is that resident XX females are no longer always homozygote $AA$ and males are no longer always heterozygote $Aa$.
+%Thus the effect of haploid selection in males is reduced, as is the difference in fitness between neo-W haplotypes and resident X haplotypes, as both can be on any diploid or haploid background.  
+%
+%The other terms are easier to interpret in the absence of haploid selection.
+%For instance, without haploid selection, the neo-W-$A$ haplotype spreads ($\Lambda_{W'A}^{(XY)}>1$) if and only if
+%
+%\begin{equation}\label{eq:BeqWAspread}
+%2(w_{Aa}^\female-w_{aa}^\female)w_{aa}^\male \psi^2 > (w_{AA}^\female-w_{Aa}^\female)w_{Aa}^\male \phi (\phi-\psi),
+%\end{equation}
+%
+%\noindent  
+%where $\phi-\psi=w_{AA}^\female w_{Aa}^\male-w_{aa}^\female w_{aa}^\male$ and both $\phi$ and $\psi$ are positive when equilibrium (A) is stable. 
+%In contrast to equilibrium (B), a neo-W haplotype can spread under purely sexually-antagonistic selection  ($w_{aa}^\female<w_{Aa}^\female<w_{AA}^\female$ and $w_{AA}^\male<w_{Aa}^\male<w_{aa}^\male$).
+%The neo-W-$A$ can spread as long as it becomes associated with females that bear more $A$ alleles than observed at equilibrium (A), effectively specializing on female fitness. 
+%%In this case, the neo-W-$A$ haplotype can spread, despite producing a lot of $Aa$ daughters by obtaining the $a$ from Y-gametes, when $aa$ females, which the neo-W-$A$ never makes, are strongly selected against.
+%%This can be intuited from the fact that \eqref{eq:BeqWAspread} will be more easily met when $w_{Aa}^\female-w_{aa}^\female\approx w_{Aa}^\female$ and $w_{AA}^\female-w_{Aa}^\female\approx 0$, implying $w_{aa}^\female \approx 0$ and $w_{Aa}^\female\approx w_{AA}^\female$ (although this is complicated by the fact that $w_{aa}^\female$ and $w_{Aa}^\female$ affect $\phi$ and $\psi$ too, the intuition holds).
+%
+%Without haploid selection, the neo-W-$a$ haplotype spreads ($\Lambda_{W'a}^{(XY)}>1$) if and only if
+%
+%\begin{equation}\label{eq:BeqWaspread}
+%(w_{aa}^\female + w_{Aa}^\female-2w_{AA}^\female)w_{Aa}^\male \phi^2 + (w_{aa}^\female-w_{Aa}^\female)(w_{Aa}^\male+2w_{aa}^\male) \phi \psi >0.
+%\end{equation}
+%
+%\noindent
+%This condition cannot be met with purely sexually antagonistic selection (as both terms on the left-hand side would then be negative), but it can be met under other circumstances. 
+%For example, with overdominance in males there is selection for increased $A$ frequencies on the X background in males, which are always paired with Y-$a$ haplotypes.
+%Directional selection for $a$ in females can then maintain a polymorphism at the $\mathbf{A}$ locus on the X background.
+%This scenario selects for a modifier that increases recombination between the sex chromosomes (e.g., blue region of Fig 2d in~\cite{Otto2014}) and facilitates the spread of neo-W-$a$ haplotypes, which create females bearing more $a$ alleles than the ancestral X haplotype does.
+%
+%\subsubsection*{Role of haploid selection with tight linkage between $\mathbf{X}$ and $\mathbf{A}$ loci}
+%
+%Haploid selection generally expands the conditions under which neo-W alleles can spread within ancestral systems that have evolved tight linkage between the sex-determining locus and a selected locus ($r \approx 0$).
+%First, haploid selection can allow a polymorphism to be maintained when it would not under diploid selection alone (e.g., with directional selection in diploids). 
+%In cases of ploidally-antagonistic selection, where there is a balance between alleles favored in the haploid stage and the diploid stage, neo-W alleles - even if unlinked to the selected locus - can spread (\nameref{fig:regionPloidAntag}).
+%Second, even when diploid selection could itself maintain a polymorphism, haploid selection can increase the conditions under which transitions among sex-determining systems are possible.
+%Of particularly importance, when selection is sexually-antagonistic in diploids ($s^\female s^\male <0$ and $0<h^\Hermaphrodite<1$), an unlinked neo-W ($R=1/2$) cannot invade unless there is also haploid selection (see proof in \nameref{file:Mathematica}; Fig \ref{fig:SexAntagTighter} and \nameref{fig:SexAntagTighterMaleDrive}).
+%More generally, haploid selection alters the conditions under which neo-W alleles can spread (compare \nameref{fig:regionMaleDrive}-\nameref{fig:regionFemaleGS} to Fig \ref{fig:regionplots}). 
+%
+%%[SALLY:  I think that is enough, but we could add somewhere??: "Without haploid selection, unlinked neo-W alleles ($R=1/2$) can invade only under certain conditions, requiring either overdominance in males or underdominance in females (see proof in supplementary \textit{Mathematica} file).?
 Note that underdominance in females with directional selection in males can lead to the spread of unlinked neo-W?s, but only from equilB (only $\Lambda_{ma}$ is greater than one in this case).]
-
-Male haploid selection in favour of the $a$ allele ($\alpha_{\Delta}^\male<0$, $w_{A}^\male<w_{a}^\male$) generates male-biased sex ratios at equilibria (A) and (B), where Y-$a$ is fixed ($\hat{p}_{Y}^\male=0$).
-Male-biased sex ratios facilitate the spread of neo-W-$A$ and neo-W-$a$ haplotypes (increasing $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$). 
-Panels A-C in \nameref{fig:regionMaleDrive} and \ref{fig:regionMaleGS} show that neo-W haplotypes tend to spread for a wider range of parameters when sex ratios are male biased, compared to Fig \ref{fig:regionplots} without haploid selection.
-By contrast, male haploid selection in favour of the $A$ allele generates female-biased sex ratios and reduces $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$, as demonstrated by panels D-F in \nameref{fig:regionMaleDrive} and \nameref{fig:regionMaleGS}.
-
-Female haploid selection generates direct selection on the neo-W-$A$ and neo-W-$a$ haplotypes as they spread in females. 
-Thus, female haploid selection in favour of the $a$ allele tends to increase $\Lambda_{W'a}^{(XY)}$ and decrease $\Lambda_{W'A}^{(XY)}$, as shown by panels A-C in \nameref{fig:regionFemaleDrive} and \nameref{fig:regionFemaleGS}.
-Conversely, female haploid selection in favour of the $A$ allele increases $\Lambda_{W'A}^{(XY)}$ and decreases $\Lambda_{W'a}^{(XY)}$, see panels D-F in \nameref{fig:regionFemaleDrive} and \nameref{fig:regionFemaleGS}.
-
-Thus, the impact of haploid selection on transitions between sex-determining systems must be considered as two sides of a coin: it can generate sex ratio biases that promote transitions that equalize the sex ratio, but it can also direct select for transitions that cause sex ratios to become biased.
+%
+%Male haploid selection in favour of the $a$ allele ($\alpha_{\Delta}^\male<0$, $w_{A}^\male<w_{a}^\male$) generates male-biased sex ratios at equilibria (A) and (B), where Y-$a$ is fixed ($\hat{p}_{Y}^\male=0$).
+%Male-biased sex ratios facilitate the spread of neo-W-$A$ and neo-W-$a$ haplotypes (increasing $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$). 
+%Panels A-C in \nameref{fig:regionMaleDrive} and \ref{fig:regionMaleGS} show that neo-W haplotypes tend to spread for a wider range of parameters when sex ratios are male biased, compared to Fig \ref{fig:regionplots} without haploid selection.
+%By contrast, male haploid selection in favour of the $A$ allele generates female-biased sex ratios and reduces $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$, as demonstrated by panels D-F in \nameref{fig:regionMaleDrive} and \nameref{fig:regionMaleGS}.
+%
+%Female haploid selection generates direct selection on the neo-W-$A$ and neo-W-$a$ haplotypes as they spread in females. 
+%Thus, female haploid selection in favour of the $a$ allele tends to increase $\Lambda_{W'a}^{(XY)}$ and decrease $\Lambda_{W'A}^{(XY)}$, as shown by panels A-C in \nameref{fig:regionFemaleDrive} and \nameref{fig:regionFemaleGS}.
+%Conversely, female haploid selection in favour of the $A$ allele increases $\Lambda_{W'A}^{(XY)}$ and decreases $\Lambda_{W'a}^{(XY)}$, see panels D-F in \nameref{fig:regionFemaleDrive} and \nameref{fig:regionFemaleGS}.
+%
+%Thus, the impact of haploid selection on transitions between sex-determining systems must be considered as two sides of a coin: it can generate sex ratio biases that promote transitions that equalize the sex ratio, but it can also direct select for transitions that cause sex ratios to become biased.
 

### 2018-02-07 LaTeX/main.tex
typo in Author Summary

@@
 \section*{Author summary}
-Accumulating evidence indicates that systems of sex determination are strikingly diverse and labile in many clades. 
+Systems of sex determination are strikingly diverse and labile in many clades. 
 This poses the question: what drives transitions between sex-determining systems? 
@@
 Prevailing views suggest that new sex-determining systems are favoured when they equalize the sex ratio and/or when they are more closely linked to genes that experience differential selection in males and females.
-Our models extends these theories to include selection upon haploid genotypes (meiotic drive or gametic competition), which causes sex ratio biases and occurs differently in males and females. 
+Our models extend these theories to include selection upon haploid genotypes (meiotic drive or gametic competition), which causes sex ratio biases and occurs differently in males and females. 
 Surprisingly, we find that neither force (sex ratio selection nor associations with genes that have sex-specific effects) dominates the spread of new sex-determining systems alone. 
@@
 %\section*{Acknowledgments}
+%We thank Georgy Sandler and Stephen Wright for sharing their results with us. 
 %This project was supported by the Natural Sciences and Engineering Research Council of Canada (CGS-D 6564 to MMO; RGPIN-2016-03711 to SPO).

### 2018-02-07 LaTeX/main.tex
striking image added

@@
 
-If haploid selection is strong but selective differences between male and female diploids are weak, we find that trans-GSD transitions are favoured more strongly than cis-GSD transitions, with transitions to ESD intermediate (e.g., with $|D^\male - D^\female| << |\alpha_\Delta^\male - \alpha_\Delta^\female + t^\male - t^\female|$ we have $\lambda_{W'}^{(XY)} > \lambda_{Y'}^{(XY)}$; Equations \ref{eq:lambda_neoW} and \ref{eq:freq_diffs}).
+If haploid selection is strong but selective differences between male and female diploids are weak, we find that trans-GSD transitions are favoured more strongly than cis-GSD transitions, with transitions to ESD intermediate (e.g., with $|D^\male - D^\female| << |\alpha_\Delta^\male - \alpha_\Delta^\female + t^\male - t^\female|$ we have $\lambda_{W'}^{(XY)} > \lambda_{Y'}^{(XY)}$; Eqs \ref{eq:lambda_neoW} and \ref{eq:freq_diffs}).
 Among the relatively few dioecious clades in which multiple species have well characterized sex chromosomes~\cite{Ming:2011iy}, trans-GSD transitions have been inferred in \textit{Silene} subsection \textit{Otites}~\cite{Slancarova:2013dq} and in \textit{Salicaceae}~\cite{Pucholt2015,Pucholt2017}.

### 2018-02-17 LaTeX/main.tex
minor change to text

@@
 Variation at such loci can favour the spread of new sex-determining systems in which the heterogametic sex changes (XY to ZW or ZW to XY) and the new sex-determining region is less closely linked (or unlinked) to the locus under selection, which is not predicted by previous theory.
-(2) We also consider selection upon haploid genotypes either during gametic competition (e.g., pollen/sperm competition) or meiosis (i.e., non-Mendelian segregation), selective processes that typically occur in one sex or the other.
+(2) We also consider selection upon haploid genotypes either during gametic competition (e.g., pollen/sperm competition) or meiosis (i.e., non-Mendelian segregation), which can cause the zygotic sex ratio to become biased.
 We find that associations with haploid selected loci can drive transitions between sex-determining systems, without requiring sexually-antagonistic selection in diploids. 
 Unexpectedly, with haploid selection, transitions between male and female heterogamety can also evolve where linkage with the sex-determining locus is weakened. 
-Furthermore, haploid selection in the heterogametic sex can cause sex ratio biases, which may increase or decrease with the spread of new sex chromosomes. 
+Furthermore, sex ratio biases may increase or decrease with the spread of new sex chromosomes. 
 Thus, we find that transitions between sex-determining systems cannot be simply predicted by selection to equalise the sex ratio. 
@@
 When $R<1/2$, the invading neo-Y becomes associated with the male meiotic drive allele and the zygotic sex ratio actually evolves to become male-biased.
+In this case, the neo-Y spreads because it is often found in males and can, if it carries the driven allele $a$, benefit from haploid selection in males (Fig \ref{fig:SexRatioBad}B).
 %
@@
 
-While equalizing the sex ratio and benefiting from drive are two primary reasons why haploid selection spurs sex chromosome transitions, even when the new sex-determining allele is less closely linked to the selected locus ($r<R$), more complex situations also arise.
+While equalizing the sex ratio and benefiting from drive are two primary reasons why haploid selection spurs sex chromosome transitions, more complex situations also arise.  
 For example with $R=1/2$ in Fig \ref{fig:SexRatioBad}B (green curve), the neo-Y allele spreads despite the fact that it cannot benefit from drive because free recombination moves it randomly between driven and non-driven backgrounds.
@@
 
-%\section*{Acknowledgments}
-%We thank Georgy Sandler and Stephen Wright for sharing their results with us. 
+\section*{Acknowledgments}
+We thank Georgy Sandler and Stephen Wright for sharing their results with us and we thank Bret Payseur for helpful comments on this manuscript. 
 %This project was supported by the Natural Sciences and Engineering Research Council of Canada (CGS-D 6564 to MMO; RGPIN-2016-03711 to SPO).

### 2018-02-21 LaTeX/Turnover_bioRXiv.tex
tex, sup figs pdf, and mathematica pdf for bioRxiv submission

--- 2018-02-06 LaTeX/Turnover_plos.tex
@@
 \documentclass[10pt,letterpaper]{article}
-\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}
+\usepackage[top=0.85in,footskip=0.75in]{geometry}
 
@@
 \setlength{\parindent}{0.5cm}
-\textwidth 5.25in 
+\textwidth 6.25in 
 \textheight 8.75in
@@
 \setlength{\headheight}{27.023pt}
-\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
+%\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
 \rfoot{\thepage/\pageref{LastPage}}
 \renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
-\fancyheadoffset[L]{2.25in}
-\fancyfootoffset[L]{2.25in}
-\lfoot{\sf PLOS}
+%\fancyheadoffset[L]{2.25in}
+%\fancyfootoffset[L]{2.25in}
+%\lfoot{\sf PLOS}
 %% Include all macros below
@@
 \begin{figure}[!h]
-%\centering
-%\centerline{\includegraphics[width=\linewidth]{Sex_determination_outline.pdf}}
+\centering
+\centerline{\includegraphics[width=\linewidth]{../Plots/Sex_determination_outline.pdf}}
 \caption{
@@
 \begin{table}[!ht]
-\centering
+%\centering
 \smallskip
@@
 \centering
-%\centerline{\includegraphics[width=1.5\linewidth]{PositionPlot_SexAntagTighter}}
+\centerline{\includegraphics[width=1.25\linewidth]{../Plots/PositionPlot_SexAntagTighter}}
 \caption{
@@
 %\centerline{\includegraphics[width=1.25\linewidth]{Region_plot_combined_Mike}}
-%\centerline{\includegraphics[width=1.25\linewidth]{Region_plot_combined}}
+\centerline{\includegraphics[width=1.25\linewidth]{../Plots/Region_plot_combined}}
 \caption{
@@
 \centering
-%\includegraphics[width=\linewidth]{PositionPlot}
+\includegraphics[width=\linewidth]{../Plots/PositionPlot}
 \caption{
@@
 \centering
-%\includegraphics[width=\linewidth]{Temporal_SR}
+\includegraphics[width=\linewidth]{../Plots/Temporal_SR}
 \caption{
@@
 \label{tab:meanfitnesses}
-{\bf Mean fitnesses and zygotic sex ratio in the resident population ($M$ fixed, XY sex determination). }
+{\bf Mean fitnesses and zygotic sex ratio in the resident population ($M$ fixed, XY sex determination).}
 

### 2018-02-21 LaTeX/Turnover_bioRXiv.tex
moved sup figs and tables into biorxiv file for standalone pdf

@@
 Recombination (i.e., an odd number of cross-overs) occurs between loci $\mathbf{X}$ and $\mathbf{A}$ with probability $r$, between loci $\mathbf{A}$ and $\mathbf{M}$ with probability $R$, and between loci $\mathbf{X}$ and $\mathbf{M}$ with probability $\rho$.
-Any linear order of the loci can be modelled with appropriate choices of $r$, $R$, and $\rho$ (see Fig \ref{fig:model_outline}A and \nameref{tab:chisubstitutions}). 
+Any linear order of the loci can be modelled with appropriate choices of $r$, $R$, and $\rho$ (see Fig \ref{fig:model_outline}A and Table \ref{tab:chisubstitutions}). 
 Individuals that are heterozygous at the $\mathbf{A}$ locus may experience meiotic drive; a gamete produced by $Aa$ heterozgotes of sex $\Hermaphrodite$ bears allele $A$ with probability $\alpha^\Hermaphrodite$.
@@
 $\bar{w}^{\Hermaphrodite}_{D}$ is the mean fitness of diploids of sex $\Hermaphrodite$.
-$\bar{w}_H^\Hermaphrodite$ is the mean fitness of haploids from sex $\Hermaphrodite$, see \nameref{tab:meanfitnesses}.
+$\bar{w}_H^\Hermaphrodite$ is the mean fitness of haploids from sex $\Hermaphrodite$, see Table \ref{tab:meanfitnesses}.
 \end{flushleft}
@@
 Neo-W alleles, on the other hand, can invade an ancestral XY system under some conditions (the full invasion conditions are given in \nameref{app:inv_cond}; equations \ref{Binvasion} and \ref{Ainvasion}).
-Counterintuitively, selection on loci within the non-recombining region around the sex-determining locus can favour the invasion of a less closely linked neo-W, whatever the form of selection maintaining a polymorphism (sexually-antagonistic selection, overdominance, ploidally-antagonistic selection, or some combination, Fig \ref{fig:SexAntagTighter}, \nameref{fig:temporalOverdominance}, \nameref{fig:regionPloidAntag}, and \nameref{fig:SexAntagTighterMaleDrive}).
+Counterintuitively, selection on loci within the non-recombining region around the sex-determining locus can favour the invasion of a less closely linked neo-W, whatever the form of selection maintaining a polymorphism (sexually-antagonistic selection, overdominance, ploidally-antagonistic selection, or some combination, Fig \ref{fig:SexAntagTighter}, Figure \ref{fig:temporalOverdominance}, Figure \ref{fig:regionPloidAntag}, and Figure \ref{fig:SexAntagTighterMaleDrive}).
 The conditions become more restrictive, however, with increasing recombination ($R$) between the new sex-determining locus and the selected locus.  
@@
 Where both haplotypic growth rates are greater than one, a neo-W will spread when rare, regardless of linkage with the selected locus (for any $R$). 
-\nameref{fig:positionOverdominance} shows the dynamics arising with the parameters marked with a dagger. 
+Figure \ref{fig:positionOverdominance} shows the dynamics arising with the parameters marked with a dagger. 
 Here, there is no haploid selection $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
@@
 This is true for the neo-W-$A$ haplotype because it can pair with a Y-$a$ haplotype and still be female. 
-Wherever both haplotypic growth rates are greater than one, invasion by a neo-W is expected regardless of its linkage with the selected locus (i.e., for any $R$, see \nameref{fig:positionOverdominance} and \nameref{fig:temporalOverdominance} for examples).
+Wherever both haplotypic growth rates are greater than one, invasion by a neo-W is expected regardless of its linkage with the selected locus (i.e., for any $R$, see Figure \ref{fig:positionOverdominance} and Figure \ref{fig:temporalOverdominance} for examples).
 
@@
 An equivalent analysis is not possible where recombination rates are low. 
-However, numerical simulations demonstrate that new sex-determining alleles do not necessarily reach pseudo-fixation, which can lead to the stable maintenance of a mixed sex-determining system, in which X, Y, Z, and W alleles all segregate (e.g., \nameref{fig:freqAll}B,C).
+However, numerical simulations demonstrate that new sex-determining alleles do not necessarily reach pseudo-fixation, which can lead to the stable maintenance of a mixed sex-determining system, in which X, Y, Z, and W alleles all segregate (e.g., Figure \ref{fig:freqAll}B,C).
 
@@
 Our results show, however, that tight ancestral-linkage of polymorphic loci, maintained by sexually-antagonistic selection or otherwise, can also drive trans-GSD transitions. 
-In addition, we find that polymorphic sex determining systems (X, Y, W, and Z alleles all present) can be maintained when a selected locus is tightly linked to the ancestral sex-determining system (e.g., \nameref{fig:freqAll}B and \nameref{fig:freqAll}C), which is not possible with loose linkage~\cite{vanDoorn:2010hu}.
+In addition, we find that polymorphic sex determining systems (X, Y, W, and Z alleles all present) can be maintained when a selected locus is tightly linked to the ancestral sex-determining system (e.g., Figure \ref{fig:freqAll}B and Figure \ref{fig:freqAll}C), which is not possible with loose linkage~\cite{vanDoorn:2010hu}.
 %As noted by \citet{vanDoorn:2010hu}, it would be prudent to compare closely related clades in order to determine whether observed polymorphisms predate a transition in sex-determination or arose afterwards.
@@
 
+\section*{Acknowledgments}
+This project was supported by the Natural Sciences and Engineering Research Council of Canada (CGS-D 6564 to MMO; RGPIN-2016-03711 to SPO).
+
 % For figure citations, please use "Fig" instead of "Figure".
@@
 %PLOS does not support heading levels beyond the 3rd (no 4th level headings).
-
-\section*{Supporting information}
-
-\paragraph*{S1 File.}
-\label{file:Mathematica}
-{\bf Supplementary \textit{Mathematica} file.}  This file can be used to re-derive our results and generate figures.
-
-\paragraph*{S1 Table}
-\label{tab:chisubstitutions}
-{\bf Substitutions for different loci orders assuming no interference.}
-
-\paragraph*{S2 Table}
-\label{tab:meanfitnesses}
-{\bf Mean fitnesses and zygotic sex ratio in the resident population ($M$ fixed, XY sex determination).}
-
-\paragraph*{S1 Appendix.}
-\label{app:recurs}
-{\bf Recursion equations and complete model description.}
-
-\paragraph*{S2 Appendix.}
-\label{app:eq_stab}
-{\bf Equilibria and stability conditions when $M$ allele is fixed. }
-
-\paragraph*{S3 Appendix.}
-\label{app:inv_cond}
-{\bf Invasion conditions for the $m$ allele.}
-
-% Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
-\paragraph*{S1 Fig.}
-\label{fig:positionOverdominance}
-{\bf With overdominance, loci near to the ancestral sex-determining locus ($r\approx0$) can favour neo-W alleles that are less tightly linked ($R>r$).} 
-In panels A and B, the $a$ allele is favoured in females ($w_{aa}^\female=1.05$, $w_{Aa}^\Hermaphrodite=1$, $w_{AA}^\female=0.85$) and selection in males is overdominant ($w_{aa}^\male=w_{AA}^\male=0.75$).
-In panels C and D, selection in males and females is overdominant ($w_{aa}^\female=w_{AA}^\female=0.6$, $w_{aa}^\male=0.5$, $w_{AA}^\male=0.7$, $w_{Aa}^\Hermaphrodite=1$).
-There is no haploid selection $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
-These parameters are marked by daggers in Fig \ref{fig:regionplots}B and C, which show that neo-W invasion is expected for any $R$ ($\Lambda_{W'A}^{(XY)},\Lambda_{W'a}^{(XY)}>1$) if the $a$ allele is nearly fixed on the Y (black lines in this figure; not stable for $r>>0$).
-Equilibria where the $A$ allele is more common among Y-bearing male gametes can also be stable and allow neo-W invasion for these parameters (blue lines). 
-%The weak selection approximation holds when all recombination rates are large relative to selection (around 0 in panels A and C), in which case, in the absence of haploid selection, neo-W alleles should spread if and only if they are more tightly linked to the selected locus (positive invasion fitness if and only if the selected locus is in the grey region).
-%However, when recombination rates are small (panels B and D and when the selected locus is near the SDRs in all panels), this weak selection prediction can break down.
-
-\paragraph*{S2 Fig.}
-\label{fig:temporalOverdominance}
-{\bf Following invasion by a neo-W allele, there can be a complete transition to a new sex-determining system, maintenance of both ancestral-XY and neo-ZW sex determining systems, or loss of the new sex-determining allele.}
-Here, we plot the frequency of the neo-W allele among female gametes.
-%; as the neo-W reaches frequency $0.5$, polymorphism at the ancestral XY locus is lost with Y becoming fixed such that sex is determined only be the ZW allele carried by a female gamete. 
-Panels A, C and D show cases where a steady state is reached with the neo-W at a frequency below $0.5$, in which case ancestral-X and Y alleles also both segregate. 
-In all cases, we assume that the $a$ allele is initially more common than the $A$ allele on the Y background (Y-$a$ is fixed when $r=0$). 
-When $r>0$ (panels B and D), Y-$A$ haplotypes created by recombination can become more common than Y-$a$ haplotypes as the neo-W spreads.
-In B, this leads to loss of the neo-W and the system goes to an equilibrium with X-$a$ and Y-$A$ haplotypes fixed (equilibrium $A'$), such that all females have the high fitness genotype $aa$ and all males are $Aa$.
-For the parameters in B, neo-W alleles have negative invasion fitness when the Y-$A$ haplotype is ancestrally more common than Y-$a$ (compare blue to black curves in \nameref{fig:positionOverdominance}A and  \nameref{fig:positionOverdominance}B near the ancestral sex-determining locus).
-In contrast, the neo-W is not lost in panel D as it is favoured regardless of whether Y-$A$ or Y-$a$ haplotypes predominate (again, compare blue to black curves in \nameref{fig:positionOverdominance}C and  \nameref{fig:positionOverdominance}D).
-%Fitness parameters are the same as in \nameref{fig:positionOverdominance}; in panels A and B the $a$ allele is favoured in females ($w_{aa}^\female=1.05$, $w_{Aa}^\Hermaphrodite=1$, $w_{AA}^\female=0.85$) while there is overdominance in males ($w_{aa}^\male=w_{AA}^\male=0.75$) and in panels C and D, there is overdominance in both sexes ($w_{aa}^\female=w_{AA}^\female=0.6$, $w_{aa}^\male=0.5$, $w_{AA}^\male=0.7$, $w_{Aa}^\Hermaphrodite=1$).
-%These parameters are marked by a dagger in Fig \ref{fig:regionplots}. 
-%Here, there is no haploid selection $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
-
-\paragraph*{S3 Fig.}
-\label{fig:SexAntagTighterMaleDrive}
-{\bf  When there is sexually-antagonistic selection and haploid selection, a neo-W allele may invade for any $R$.}
-Panel A shows that the invasion fitness of a neo-W is positive, even when $r<R$ (unshaded region).
-In panel B, we vary the recombination rate between the neo-W and the selected locus ($R$) for a fixed recombination rate between the ancestral sex-determining locus and the selected locus ($r=0.005$).
-Coloured markers show recombination rates for which the temporal dynamics of neo-W invasion are plotted in panel C (black $R=0.001$, red $R=0.02$, blue $R=0.1$, green $R=0.5$). 
-The diploid selection parameters used in this plot are the same as in Fig \ref{fig:SexAntagTighter}. 
-There is also meiotic drive in males favouring $a$ ($\alpha_{\Delta}^\male=-0.08$), this full set of parameters is marked by an asterisk in \nameref{fig:regionMaleDrive}A.
-When $R=0.5$ (green curve), the neo-W does not reach fixation and X, Y, Z, and W alleles are all maintained in the population, see \nameref{fig:freqAll}C.
-
-\paragraph*{S4 Fig.}
-\label{fig:regionMaleDrive}
-{\bf Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is male meiotic drive at a locus that is tightly linked to the ancestral XY locus ($r=0$).}
-This figure is equivalent to Fig \ref{fig:regionplots} but with meiotic drive in males.
-%We vary the fitness of male homozygotes relative to heterozygotes ($w_{Aa}^\Hermaphrodite=1$) and only consider stable equilibria at which both $\mathbf{A}$ locus allele are maintained and the $a$ allele is initially fixed on the Y, region outlined.
-In panels A-C, meiotic drive in males favours the $a$ allele ($\alpha_{\Delta}^\male=-0.16$), creating male-biased sex ratios and generally increasing $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$.
-By contrast, $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$ tend to be reduced when meiotic drive in males favours the $A$ allele ($\alpha_{\Delta}^\male=0.16$), panels D-F. 
-%We consider three forms of selection in females: directional selection in favour of the $A$ allele (panels A and D, $w_{aa}^\female=0.85$, $w_{AA}^\female=1.05$), direction selection in favour of the $a$ allele (panels B and E, $w_{aa}^\female=1.05$, $w_{AA}^\female=0.85$), and overdominance (panels C and F, $w_{aa}^\female=w_{AA}^\female=0.6$).
-
-\paragraph*{S5 Fig.}
-\label{fig:regionMaleGS}
-{\bf Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is male gametic competition at a locus that is tightly linked to the ancestral XY locus ($r=0$).}
-This figure is equivalent to Fig \ref{fig:regionplots} but with gametic competition in males.
-%Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in \nameref{fig:regionMaleDrive}. 
-The $a$ allele is favoured during male gametic competition in Panels A-C ($w_{a}^\male=1.16$, $w_{A}^\male=1$), which creates male biased sex ratios and increases $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$.
-By contrast, $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$ tend to be reduced when the $A$ allele is favoured during male gametic competition, panels D-F.
-Compared to the meiotic drive parameters in \nameref{fig:regionMaleDrive}, the effect of these male gametic competition parameters on the sex ratio is smaller. 
-For example, in \nameref{fig:regionMaleDrive}A-C, the ancestral sex ratio is $\alpha^\male=0.58$ at equilibrium (B) and in panels A-C of this plot, the ancestral sex ratio is $w_{a}^\male/(w_{A}^\male+w_{a}^\male)=0.537$ at equilibrium (B).
-
-\paragraph*{S6 Fig.}
-\label{fig:regionFemaleDrive}
-{\bf Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is female meiotic drive at a locus that is tightly linked to the ancestral XY locus ($r=0$).}
-This figure is equivalent to Fig \ref{fig:regionplots} but with meiotic drive in females.
-%Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in \nameref{fig:regionMaleDrive} and \nameref{fig:regionMaleGS}. 
-The $a$ allele is favoured by meiotic drive in females in Panels A-C ($\alpha_{\Delta}^\female=-0.16$), which increases $\Lambda_{W'a}^{(XY)}$ and decreases $\Lambda_{W'A}^{(XY)}$. 
-Female meiotic drive in favour of the $A$ allele (panels D-F, $\alpha_{\Delta}^\female=-0.16$) has the opposite effect.
-
-\paragraph*{S7 Fig.}
-\label{fig:regionFemaleGS}
-{\bf Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is female gametic competition at a locus that is tightly linked to the ancestral XY locus ($r=0$).}
-This figure is equivalent to Fig \ref{fig:regionplots} but with gametic competition in females.
-%Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in \nameref{fig:regionMaleDrive}, \nameref{fig:regionMaleGS}, and \nameref{fig:regionFemaleDrive}. 
-The $a$ allele is favoured during female gametic competition in females in Panels A-C ($w_{a}^\female=1.16$, $w_{A}^\female=1$), which increases $\Lambda_{W'a}^{(XY)}$ and decreases $\Lambda_{W'A}^{(XY)}$.
-The $A$ allele is favoured during gametic competition in panels D-F ($w_{a}^\female=1$, $w_{A}^\female=1.16$), giving the opposite effect on $\Lambda_{W'a}^{(XY)}$ and $\Lambda_{W'A}^{(XY)}$.
-
-\paragraph*{S8 Fig.}
-\label{fig:regionPloidAntag}
-{\bf Ploidally-antagonistic selection can drive the spread of neo-W alleles. }
-A-D show when each of the neo-W haplotypes invades an internally stable equilibrium with $a$ fixed on the Y (found by setting $r=0$).
-The y-axis shows directional selection in diploids of both sexes, $s^\female=s^\male$, and the x-axes show sex-specific drive, $\alpha_\Delta^\Hermaphrodite$, or haploid competition, $t^\Hermaphrodite$.
-The top left and bottom right quadrants therefore imply ploidally-antagonistic selection (and these are the only places where neo-W haplotypes can invade).
-Dominance is equal in both sexes, $h^\female=h^\male=3/4$. 
-E-F show the temporal dynamics of neo-W frequency in females with parameters given by the asterisks in the corresponding A-D plot, with $r=1/200$, for four different $R$.
-Black $R=1/1000$, Red $R=2/100$, Blue $R=1/10$, Green $R=1/2$.
-
-\paragraph*{S9 Fig.}
-\label{fig:freqAll}
-{\bf Pseudo-fixation of neo-W or maintenance of multiple sex-determining alleles. }
-The curves show the frequencies of the neo-W (red), ancestral Y (blue), and $A$ allele (black) among female gametes (solid curves) and among male gametes (dashed curves). 
-In panel A, there is a complete transition from XY sex determination (XX-ZZ females and XY-ZZ males) to ZW sex determination (YY-ZW females and YY-ZZ males).  
-In panels B and C a polymorphism is maintained at both the ancestral XY locus and the new ZW locus, such that there are males with genotypes XY-ZZ and YY-ZZ and females with genotypes XX-ZZ, XX-ZW, XY-ZW, and YY-ZW.
-In panel A, selection is ploidally-antagonistic with drive in males (parameters as in the green curve in Fig \ref{fig:SexRatioBad}B).
-In panel B, there is overdominance in both sexes and no haploid selection (parameters as in the green curve in \nameref{fig:temporalOverdominance}C).
-In panel C, there is sexually-antagonistic selection in diploids with drive in males (parameters as in the green curve in \nameref{fig:regionMaleDrive}C).
-In all cases, the initial equilibrium frequency has $a$ near fixation on the Y.
-
-%\section*{Acknowledgments}
-%This project was supported by the Natural Sciences and Engineering Research Council of Canada (CGS-D 6564 to MMO; RGPIN-2016-03711 to SPO).
 
@@
 
+\section*{Supporting information}
+
 \setcounter{equation}{0}
@@
 \section*{S1 Appendix}
+\label{app:recurs}
 
@@
 $R$ is the recombination rate between the $\mathbf{A}$ and $\mathbf{M}$ loci, $\rho$ is the recombination rate between the $\mathbf{M}$ and $\mathbf{X}$ loci, and $r$ is the recombination rate between the $\mathbf{A}$ and $\mathbf{X}$ loci (Fig \ref{fig:model_outline}).
-\nameref{tab:chisubstitutions} shows replacements that can be made for each possible ordering of the loci assuming that there is no cross-over interference.
+Table \ref{tab:chisubstitutions} shows replacements that can be made for each possible ordering of the loci assuming that there is no cross-over interference.
 During meiosis in sex $\Hermaphrodite$, meiotic drive occurs such that, in $Aa$ heterozygotes, a fraction $\alpha^{\Hermaphrodite}$ of gametes produced carry the $A$ allele and $(1-\alpha^\Hermaphrodite)$ carry the $a$ allele.
@@
 \section*{S2 Appendix}
+\label{app:eq_stab}
 
@@
 These four variables determine the frequencies of the six resident gamete types, which sum to one in each sex: $x_{1}^{\female}=\hat{p}_X^\female$, $x_{2}^{\female}=1-\hat{p}_X^\female$, $x_{1}^{\male}=(1-q)\hat{p}_X^\male$, $x_{2}^{\male}=(1-q)(1-\hat{p}_X^\male)$, $y_{1}^{\male}=q \hat{p}_Y^\male$, and $y_{2}^{\male}=q(1-\hat{p}_Y^\male)$.
-Mean fitnesses in the resident population are given in \nameref{tab:meanfitnesses}.
+Mean fitnesses in the resident population are given in Table \ref{tab:meanfitnesses}.
 
@@
 \section*{S3 Appendix}
+\label{app:inv_cond}
 
@@
 First, haploid selection can allow a polymorphism to be maintained when it would not under diploid selection alone (e.g., with directional selection in diploids). 
-In cases of ploidally-antagonistic selection, where there is a balance between alleles favored in the haploid stage and the diploid stage, neo-W alleles - even if unlinked to the selected locus - can spread (\nameref{fig:regionPloidAntag}).
+In cases of ploidally-antagonistic selection, where there is a balance between alleles favored in the haploid stage and the diploid stage, neo-W alleles - even if unlinked to the selected locus - can spread (Figure \ref{fig:regionPloidAntag}).
 Second, even when diploid selection could itself maintain a polymorphism, haploid selection can increase the conditions under which transitions among sex-determining systems are possible.
-Of particularly importance, when selection is sexually-antagonistic in diploids ($s^\female s^\male <0$ and $0<h^\Hermaphrodite<1$), an unlinked neo-W ($R=1/2$) cannot invade unless there is also haploid selection (see proof in \nameref{file:Mathematica}; Fig \ref{fig:SexAntagTighter} and \nameref{fig:SexAntagTighterMaleDrive}).
-More generally, haploid selection alters the conditions under which neo-W alleles can spread (compare \nameref{fig:regionMaleDrive}-\nameref{fig:regionFemaleGS} to Fig \ref{fig:regionplots}).
+Of particularly importance, when selection is sexually-antagonistic in diploids ($s^\female s^\male <0$ and $0<h^\Hermaphrodite<1$), an unlinked neo-W ($R=1/2$) cannot invade unless there is also haploid selection (see proof in \nameref{file:Mathematica}; Fig \ref{fig:SexAntagTighter} and Figure \ref{fig:SexAntagTighterMaleDrive}).
+More generally, haploid selection alters the conditions under which neo-W alleles can spread (compare Figure \ref{fig:regionMaleDrive}-Figure \ref{fig:regionFemaleGS} to Fig \ref{fig:regionplots}).
 
@@
 Male-biased sex ratios facilitate the spread of neo-W-$A$ and neo-W-$a$ haplotypes (increasing $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$). 
-Panels A-C in \nameref{fig:regionMaleDrive} and \ref{fig:regionMaleGS} show that neo-W haplotypes tend to spread for a wider range of parameters when sex ratios are male biased, compared to Fig \ref{fig:regionplots} without haploid selection.
-By contrast, male haploid selection in favour of the $A$ allele generates female-biased sex ratios and reduces $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$, as demonstrated by panels D-F in \nameref{fig:regionMaleDrive} and \nameref{fig:regionMaleGS}.
+Panels A-C in Figure \ref{fig:regionMaleDrive} and \ref{fig:regionMaleGS} show that neo-W haplotypes tend to spread for a wider range of parameters when sex ratios are male biased, compared to Fig \ref{fig:regionplots} without haploid selection.
+By contrast, male haploid selection in favour of the $A$ allele generates female-biased sex ratios and reduces $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$, as demonstrated by panels D-F in Figure \ref{fig:regionMaleDrive} and Figure \ref{fig:regionMaleGS}.
 
 Female haploid selection generates direct selection on the neo-W-$A$ and neo-W-$a$ haplotypes as they spread in females. 
-Thus, female haploid selection in favour of the $a$ allele tends to increase $\Lambda_{W'a}^{(XY)}$ and decrease $\Lambda_{W'A}^{(XY)}$, as shown by panels A-C in \nameref{fig:regionFemaleDrive} and \nameref{fig:regionFemaleGS}.
-Conversely, female haploid selection in favour of the $A$ allele increases $\Lambda_{W'A}^{(XY)}$ and decreases $\Lambda_{W'a}^{(XY)}$, see panels D-F in \nameref{fig:regionFemaleDrive} and \nameref{fig:regionFemaleGS}.
+Thus, female haploid selection in favour of the $a$ allele tends to increase $\Lambda_{W'a}^{(XY)}$ and decrease $\Lambda_{W'A}^{(XY)}$, as shown by panels A-C in Figure \ref{fig:regionFemaleDrive} and Figure \ref{fig:regionFemaleGS}.
+Conversely, female haploid selection in favour of the $A$ allele increases $\Lambda_{W'A}^{(XY)}$ and decreases $\Lambda_{W'a}^{(XY)}$, see panels D-F in Figure \ref{fig:regionFemaleDrive} and Figure \ref{fig:regionFemaleGS}.
 
@@
 
+%\paragraph*{S1 File.}
+%\label{file:Mathematica}
+%{\bf Supplementary \textit{Mathematica} file.}  This file can be used to re-derive our results and generate figures. 
+%
+%\paragraph*{S1 Table}
+%\label{tab:chisubstitutions}
+%{\bf Substitutions for different loci orders assuming no interference.}
+%
+%\paragraph*{S2 Table}
+%\label{tab:meanfitnesses}
+%{\bf Mean fitnesses and zygotic sex ratio in the resident population ($M$ fixed, XY sex determination).}
+%
+%\paragraph*{S1 Appendix.}
+%\label{app:recurs}
+%{\bf Recursion equations and complete model description.} 
+%
+%\paragraph*{S2 Appendix.}
+%\label{app:eq_stab}
+%{\bf Equilibria and stability conditions when $M$ allele is fixed. } 
+%
+%\paragraph*{S3 Appendix.}
+%\label{app:inv_cond}
+%{\bf Invasion conditions for the $m$ allele.}
+
+\section*{Supplementary Files}
+\paragraph*{S1 File.}
+\label{file:Mathematica}
+{\bf Supplementary \textit{Mathematica} file.}  This file can be used to re-derive our results and generate figures. Please contact authors for access.
+
+\newpage
+\section*{Supplementary Tables}
+\setcounter{table}{0} 
+\renewcommand{\thetable}{S\arabic{table}}
+
+\begin{table}[ht]
+\centering
+\smallskip
+\caption{
+Substitutions for different loci orders assuming no interference.
+%and $r,R\in(0,1/2)$.\textcolor{blue}{write all in form of first line?
+so that 1/2 cases are okay (can't determine chi if R is 1/2 in second line, or if r is 1/2 in third line}
+}
+\begin{tabular}{l l}
+\hline\hline
+  Order of loci &   \\ [0.5ex] \hline
+  SDR-A-M & $\rho=r(1-R)+R(1-r)$  \\
+  SDR-M-A & $r=\rho(1-R)+R(1-\rho)$ \\ %$\rho=(r-R)/(1-2R)$ \\
+  A-SDR-M & $R=r(1-\rho)+\rho(1-r)$ \\ %$\rho=(R-r)/(1-2r)$ \\
+  \hline \hline
+  \label{tab:chisubstitutions}
+ \end{tabular}
+\end{table}
+
+\begin{table}[!h]
+\centering
+\smallskip
+\caption{Mean fitnesses and zygotic sex ratio in the resident population ($M$ fixed, XY sex determination). }
+\begin{tabular}{l l }
+\hline\hline
+  Sex \& Life Cycle Stage & Mean Fitness \\ [0.5ex] \hline  \noalign{\vskip 0.5ex}
+  female gametes ($\bar{w}_H^\female$) & 
+  $p_X^\female w_A^\female + (1-p_X^\female) w_a^\female$ \\ [0.5ex] \hline  \noalign{\vskip 0.5ex}
+  X-bearing male gametes ($\bar{w}_{HX}^\male$) & 
+  $p_X^{\male} w_A^\male + (1-p_X^{\male}) w_a^\male$ \\ [0.5ex] \hline  \noalign{\vskip 0.5ex}
+  Y-bearing male gametes ($\bar{w}_{HY}^\male$) & 
+  $p_Y^{\male} w_A^\male + (1-p_Y^{\male}) w_a^\male$ \\ [0.5ex] \hline  \noalign{\vskip 0.5ex}
+  male gametes ($\bar{w}_H^\male$) & 
+  $(1-q) \bar{w}_{HX}^\male + q \bar{w}_{HY}^\male$ \\ [0.5ex] \hline  \noalign{\vskip 0.5ex}
+  females ($\bar{w}^\female$) & 
+%  $\begin{array}{l}  (1-\zeta)^{-1} (1-q) \big[ p_X^\female w_A^\female p_X^\male w_A^\male w_{AA}^\female + \\
+%  (1 - p_X^\female) w_a^\female p_X^\male w_A^\male w_{Aa}^\female + \\
+%  p_X^\female w_A^\female (1 - p_X^\male) w_a^\male w_{Aa}^\female + \\
+%  (1-p_X^\female) w_a^\female (1 - p_X^\male) w_a^\male w_{aa}^\female \big] / \left( \bar{w}_H^\female \bar{w}_H^\male \right)
+%  \end{array} 
+ $\begin{array}{l} \big[ p_X^\female w_A^\female p_X^\male w_A^\male w_{AA}^\female + \\
+  (1 - p_X^\female) w_a^\female p_X^\male w_A^\male w_{Aa}^\female + \\
+  p_X^\female w_A^\female (1 - p_X^\male) w_a^\male w_{Aa}^\female + \\
+  (1-p_X^\female) w_a^\female (1 - p_X^\male) w_a^\male w_{aa}^\female \big] / \left( \bar{w}_H^\female \bar{w}_{HX}^\male \right)
+  \end{array}
+  $ \\ [0.5ex] \noalign{\vskip 0.5ex} \hline  \noalign{\vskip 0.5ex}
+  males ($\bar{w}^\male$) & 
+%  $\begin{array}{l} \zeta^{-1} q \big[ p_X^\female w_A^\female  p_Y^\male w_A^\male w_{AA}^\male + \\
+%  (1 - p_X^\female) w_a^\female  p_Y^\male w_A^\male w_{Aa}^\male + \\
+%  p_X^\female w_A^\female  (1 - p_Y^\male) w_a^\male w_{Aa}^\male + \\
+%  (1-p_X^\female) w_a^\female  (1 - p_Y^\male) w_a^\male w_{aa}^\male \big] / \left( \bar{w}_H^\female \bar{w}_H^\male \right) 
+%  \end{array}
+ $\begin{array}{l} \big[ p_X^\female w_A^\female  p_Y^\male w_A^\male w_{AA}^\male + \\
+  (1 - p_X^\female) w_a^\female  p_Y^\male w_A^\male w_{Aa}^\male + \\
+  p_X^\female w_A^\female  (1 - p_Y^\male) w_a^\male w_{Aa}^\male + \\
+  (1-p_X^\female) w_a^\female  (1 - p_Y^\male) w_a^\male w_{aa}^\male \big] / \left( \bar{w}_H^\female \bar{w}_{HY}^\male \right) 
+  \end{array}
+  $ \\ [0.5ex] \noalign{\vskip 0.5ex} \hline  \noalign{\vskip 0.5ex}
+  fraction zygotes male ($\zeta$) & $q \left[ p_Y^\male w_A^\male+(1-p_Y^\male)w_a^\male\right] / \bar{w}_H^\male $
+   \\ [0.5ex]  \noalign{\vskip 0.5ex}
+  \hline \hline
+  \label{tab:meanfitnesses}
+ \end{tabular}
+\end{table}
+
+\newpage
+\section*{Supplementary Figures}
+\setcounter{figure}{0} 
+\renewcommand{\thefigure}{S\arabic{figure}}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Both neo-W haplotypes can spread, in the absence of haploid selection, when there is overdominance
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[!h]
+\centering
+\centerline{\includegraphics[width=\linewidth]{PositionPlot_Overdominance.eps}}
+\caption{
+{\bf With overdominance, loci near to the ancestral sex-determining locus ($r\approx0$) can favour neo-W alleles that are less tightly linked ($R>r$).} 
+In panels A and B, the $a$ allele is favoured in females ($w_{aa}^\female=1.05$, $w_{Aa}^\Hermaphrodite=1$, $w_{AA}^\female=0.85$) and selection in males is overdominant ($w_{aa}^\male=w_{AA}^\male=0.75$).
+In panels C and D, selection in males and females is overdominant ($w_{aa}^\female=w_{AA}^\female=0.6$, $w_{aa}^\male=0.5$, $w_{AA}^\male=0.7$, $w_{Aa}^\Hermaphrodite=1$).
+There is no haploid selection $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
+These parameters are marked by daggers in Fig \ref{fig:regionplots}B and C, which show that neo-W invasion is expected for any $R$ ($\Lambda_{W'A}^{(XY)},\Lambda_{W'a}^{(XY)}>1$) if the $a$ allele is nearly fixed on the Y (black lines in this figure; not stable for $r>>0$).
+Equilibria where the $A$ allele is more common among Y-bearing male gametes can also be stable and allow neo-W invasion for these parameters (blue lines). 
+}
+\label{fig:positionOverdominance}
+\end{figure}
+
+\newpage
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Both neo-W haplotypes can spread, in the absence of haploid selection, when there is overdominance
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[!h]
+\centering
+\centerline{\includegraphics[width=\linewidth]{Temporal_Overdominance.eps}}
+\caption{
+{\bf Following invasion by a neo-W allele, there can be a complete transition to a new sex-determining system, maintenance of both ancestral-XY and neo-ZW sex determining systems, or loss of the new sex-determining allele.}
+Here, we plot the frequency of the neo-W allele among female gametes.
+%; as the neo-W reaches frequency $0.5$, polymorphism at the ancestral XY locus is lost with Y becoming fixed such that sex is determined only be the ZW allele carried by a female gamete. 
+Panels A, C and D show cases where a steady state is reached with the neo-W at a frequency below $0.5$, in which case ancestral-X and Y alleles also both segregate. 
+In all cases, we assume that the $a$ allele is initially more common than the $A$ allele on the Y background (Y-$a$ is fixed when $r=0$). 
+When $r>0$ (panels B and D), Y-$A$ haplotypes created by recombination can become more common than Y-$a$ haplotypes as the neo-W spreads.
+In B, this leads to loss of the neo-W and the system goes to an equilibrium with X-$a$ and Y-$A$ haplotypes fixed (equilibrium $A'$), such that all females have the high fitness genotype $aa$ and all males are $Aa$.
+For the parameters in B, neo-W alleles have negative invasion fitness when the Y-$A$ haplotype is ancestrally more common than Y-$a$ (compare blue to black curves in Figure \ref{fig:positionOverdominance}A and  Figure \ref{fig:positionOverdominance}B near the ancestral sex-determining locus).
+In contrast, the neo-W is not lost in panel D as it is favoured regardless of whether Y-$A$ or Y-$a$ haplotypes predominate (again, compare blue to black curves in Figure \ref{fig:positionOverdominance}C and  Figure \ref{fig:positionOverdominance}D).
+}
+\label{fig:temporalOverdominance}
+\end{figure}
+
+\begin{figure}[!h]
+\centering
+\centerline{\includegraphics[width=1.25\linewidth]{PositionPlot_SexAntagTighter_MaleDrive.eps}}
+\caption{
+{\bf  When there is sexually-antagonistic selection and haploid selection, a neo-W allele may invade for any $R$.}
+Panel A shows that the invasion fitness of a neo-W is positive, even when $r<R$ (unshaded region).
+In panel B, we vary the recombination rate between the neo-W and the selected locus ($R$) for a fixed recombination rate between the ancestral sex-determining locus and the selected locus ($r=0.005$).
+Coloured markers show recombination rates for which the temporal dynamics of neo-W invasion are plotted in panel C (black $R=0.001$, red $R=0.02$, blue $R=0.1$, green $R=0.5$). 
+The diploid selection parameters used in this plot are the same as in Fig \ref{fig:SexAntagTighter}. 
+There is also meiotic drive in males favouring $a$ ($\alpha_{\Delta}^\male=-0.08$), this full set of parameters is marked by an asterisk in Figure \ref{fig:regionMaleDrive}A.
+When $R=0.5$ (green curve), the neo-W does not reach fixation and X, Y, Z, and W alleles are all maintained in the population, see Figure \ref{fig:freqAll}C.
+}
+\label{fig:SexAntagTighterMaleDrive}
+\end{figure}
+
+\begin{figure}[!h]
+\centering
+\centerline{\includegraphics[width=1.25\linewidth]{Region_Plot_combined_MaleDrive.eps}}
+\caption{
+{\bf Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is male meiotic drive at a locus that is tightly linked to the ancestral XY locus ($r=0$).}
+This figure is equivalent to Fig \ref{fig:regionplots} but with meiotic drive in males.
+%We vary the fitness of male homozygotes relative to heterozygotes ($w_{Aa}^\Hermaphrodite=1$) and only consider stable equilibria at which both $\mathbf{A}$ locus allele are maintained and the $a$ allele is initially fixed on the Y, region outlined.
+In panels A-C, meiotic drive in males favours the $a$ allele ($\alpha_{\Delta}^\male=-0.16$), creating male-biased sex ratios and generally increasing $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$.
+By contrast, $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$ tend to be reduced when meiotic drive in males favours the $A$ allele ($\alpha_{\Delta}^\male=0.16$), panels D-F. 
+}
+\label{fig:regionMaleDrive}
+\end{figure}
+
+%\newpage
+\begin{figure}[!h]
+\centering
+\centerline{\includegraphics[width=1.25\linewidth]{Region_Plot_combined_MaleGS.eps}}
+\caption{
+{\bf Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is male gametic competition at a locus that is tightly linked to the ancestral XY locus ($r=0$).}
+This figure is equivalent to Fig \ref{fig:regionplots} but with gametic competition in males.
+%Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in Figure \ref{fig:regionMaleDrive}. 
+The $a$ allele is favoured during male gametic competition in Panels A-C ($w_{a}^\male=1.16$, $w_{A}^\male=1$), which creates male biased sex ratios and increases $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$.
+By contrast, $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$ tend to be reduced when the $A$ allele is favoured during male gametic competition, panels D-F.
+Compared to the meiotic drive parameters in Figure \ref{fig:regionMaleDrive}, the effect of these male gametic competition parameters on the sex ratio is smaller. 
+For example, in Figure \ref{fig:regionMaleDrive}A-C, the ancestral sex ratio is $\alpha^\male=0.58$ at equilibrium (B) and in panels A-C of this plot, the ancestral sex ratio is $w_{a}^\male/(w_{A}^\male+w_{a}^\male)=0.537$ at equilibrium (B).
+}
+\label{fig:regionMaleGS}
+\end{figure}
+
+\begin{figure}[!h]
+\centering
+\centerline{\includegraphics[width=\linewidth]{Region_Plot_combined_FemaleDrive.eps}}
+\caption{
+{\bf Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is female meiotic drive at a locus that is tightly linked to the ancestral XY locus ($r=0$).}
+This figure is equivalent to Fig \ref{fig:regionplots} but with meiotic drive in females.
+%Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in Figure \ref{fig:regionMaleDrive} and Figure \ref{fig:regionMaleGS}. 
+The $a$ allele is favoured by meiotic drive in females in Panels A-C ($\alpha_{\Delta}^\female=-0.16$), which increases $\Lambda_{W'a}^{(XY)}$ and decreases $\Lambda_{W'A}^{(XY)}$. 
+Female meiotic drive in favour of the $A$ allele (panels D-F, $\alpha_{\Delta}^\female=-0.16$) has the opposite effect. 
+}
+\label{fig:regionFemaleDrive}
+\end{figure}
+
+\begin{figure}[!h]
+\centering
+\centerline{\includegraphics[width=1.25\linewidth]{Region_Plot_combined_FemaleGS.eps}}
+\caption{
+{\bf Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is female gametic competition at a locus that is tightly linked to the ancestral XY locus ($r=0$).}
+This figure is equivalent to Fig \ref{fig:regionplots} but with gametic competition in females.
+%Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in Figure \ref{fig:regionMaleDrive}, Figure \ref{fig:regionMaleGS}, and Figure \ref{fig:regionFemaleDrive}. 
+The $a$ allele is favoured during female gametic competition in females in Panels A-C ($w_{a}^\female=1.16$, $w_{A}^\female=1$), which increases $\Lambda_{W'a}^{(XY)}$ and decreases $\Lambda_{W'A}^{(XY)}$.
+The $A$ allele is favoured during gametic competition in panels D-F ($w_{a}^\female=1$, $w_{A}^\female=1.16$), giving the opposite effect on $\Lambda_{W'a}^{(XY)}$ and $\Lambda_{W'A}^{(XY)}$. 
+}
+\label{fig:regionFemaleGS}
+\end{figure}
+
+%\begin{landscape}
+\begin{figure}[!h]
+\centering
+\centerline{
+\includegraphics[width=1.25\linewidth]{All_plot_combined_PloidAntag.eps}
+}
+\caption{
+{\bf Ploidally-antagonistic selection can drive the spread of neo-W alleles. }
+A-D show when each of the neo-W haplotypes invades an internally stable equilibrium with $a$ fixed on the Y (found by setting $r=0$).
+The y-axis shows directional selection in diploids of both sexes, $s^\female=s^\male$, and the x-axes show sex-specific drive, $\alpha_\Delta^\Hermaphrodite$, or haploid competition, $t^\Hermaphrodite$.
+The top left and bottom right quadrants therefore imply ploidally-antagonistic selection (and these are the only places where neo-W haplotypes can invade).
+Dominance is equal in both sexes, $h^\female=h^\male=3/4$. 
+E-F show the temporal dynamics of neo-W frequency in females with parameters given by the asterisks in the corresponding A-D plot, with $r=1/200$, for four different $R$.
+Black $R=1/1000$, Red $R=2/100$, Blue $R=1/10$, Green $R=1/2$.  
+}
+\label{fig:regionPloidAntag}
+\end{figure}
+%\end{landscape}
+
+%\begin{landscape}
+\begin{figure}[!h]
+\centering
+\centerline{
+\includegraphics[width=1.25\linewidth]{Freq_plot_combined_PloidAntag.eps}
+}
+\caption{
+{\bf Pseudo-fixation of neo-W or maintenance of multiple sex-determining alleles. }
+The curves show the frequencies of the neo-W (red), ancestral Y (blue), and $A$ allele (black) among female gametes (solid curves) and among male gametes (dashed curves). 
+In panel A, there is a complete transition from XY sex determination (XX-ZZ females and XY-ZZ males) to ZW sex determination (YY-ZW females and YY-ZZ males).  
+In panels B and C a polymorphism is maintained at both the ancestral XY locus and the new ZW locus, such that there are males with genotypes XY-ZZ and YY-ZZ and females with genotypes XX-ZZ, XX-ZW, XY-ZW, and YY-ZW.
+In panel A, selection is ploidally-antagonistic with drive in males (parameters as in the green curve in Fig \ref{fig:SexRatioBad}B).
+In panel B, there is overdominance in both sexes and no haploid selection (parameters as in the green curve in Figure \ref{fig:temporalOverdominance}C).
+In panel C, there is sexually-antagonistic selection in diploids with drive in males (parameters as in the green curve in Figure \ref{fig:regionMaleDrive}C).
+In all cases, the initial equilibrium frequency has $a$ near fixation on the Y.
+}
+\label{fig:freqAll}
+\end{figure}
+%\end{landscape}
+
 \end{document}

### 2018-03-25 LaTeX/main_revision.tex
revision started, changed hermaphrodite to circle, wrote 6 conclusions, added more ubeda citations, and made diff

--- 2018-02-17 LaTeX/main.tex
@@
 \section*{Abstract}
-Sex determination is remarkably dynamic; many taxa display shifts in the location of sex-determining loci or the evolution of entirely new sex-determining systems. 
+Genetic sex determination is remarkably dynamic; many taxa display shifts in the location of sex-determining loci or the evolution of entirely new sex-determining systems. 
 Predominant theories for why we observe such transitions generally conclude that novel sex-determining systems are favoured by selection if they equalise the sex ratio or increase linkage with a sexually-antagonistic locus.
@@
 
-Predominant theories accounting for the spread of new sex-determining systems by selection involve fitness differences between sexes (e.g., sexually antagonistic selection) or sex ratio selection~\cite{Blaser2012, Beukeboom:2014vb,vanDoorn2014re}.
+Predominant theories accounting for transitions between GSD systems by selection involve fitness differences between sexes (e.g., sexually antagonistic selection) or sex ratio selection~\cite{Blaser2012, Beukeboom:2014vb,vanDoorn2014re}.
 %\citet{Bull:1977wt} shows that direct selection on new sex determination loci can allow them to spread and switch between male and female heterogamety. 
@@
 The sex ratio is directly determined by the sex-determining system, and it has therefore been suggested that sex ratio selection is a dominant force in the evolution of sex determination (e.g., Bull, 1983, p 66-67 ~\cite{Bull:1983vi}; Buekeboom and Perrin, 2014, Chapter 7~\cite{Beukeboom:2014vb}).
-`Fisherian' sex ratio selection favours a 1:1 zygotic sex ratio when assuming that males and females are equally costly to produce~\cite{Fisher:1930wy,Charnov:1982wg}.
+`Fisherian' sex-ratio selection favours a 1:1 zygotic sex ratio when assuming that males and females are equally costly to produce~\cite{Fisher:1930wy,Charnov:1982wg}.
 This follows from the fact that, for an autosomal locus, half of the genetic material is inherited from a male and half from a female~\cite{West:2009we}. 
@@
 In the case of sex-chromosome evolution, Kozielska et al.
-(2014)~\cite{Kozielska:2010vm} consider systems in which the ancestral sex chromosomes experience meiotic drive (e.g., where driving X or Y chromosomes are inherited disproportionately often), which causes sex ratios to become biased~\cite{Hamilton:1967ts}.
+(2010)~\cite{Kozielska:2010vm} consider systems in which the ancestral sex chromosomes experience meiotic drive (e.g., where driving X or Y chromosomes are inherited disproportionately often), which causes sex ratios to become biased~\cite{Hamilton:1967ts}.
 They find that masculinizing or feminizing mutations that arise at a new, unlinked locus (i.e., neo-Y or neo-W chromosomes) can then spread, which restore an even sex ratio. 
-
-Here we use mathematical models to find the conditions under which new sex-determining systems spread when individuals experience selection at both diploid and haploid stages, which allows fitness differences between the sexes and sex ratio biases to occur simultaneously.
+However, starting from ESD, Ubeda et al.
+(2015)~\cite{Ubeda:2015fx} have numerically shown that sex-specific meiotic drive can allow masculinizing and feminizing mutations to spread (i.e., ESD $\rightarrow$ GSD) despite causing a sex-ratio bias.
+
+Here we use mathematical models to clarify the conditions under which new sex-determining systems spread when individuals experience selection at both diploid and haploid stages, which allows fitness differences between the sexes and sex-ratio biases to occur simultaneously.
 Even in animal and plant species that have much larger and more conspicuous diploid phases than haploid phases, many loci experience significant haploid selection through gamete competition and/or meiotic drive~\cite{Mulcahy:1996ha,JOSEPH:2004haa}.
-We use the term `meiotic drive' to refer to the biased (non-Mendelian) segregation of genotypes during gamete production (from one parent) and the term `gametic competition' to refer to selection upon haploid genotypes within a gamete/gametophyte pool (potentially from multiple parents); the term `haploid selection' encompasses both processes.
+We use the term `meiotic drive' to refer to the biased (non-Mendelian) segregation of genotypes during gamete production (from one parent only) and the term `gametic competition' to refer to selection upon haploid genotypes within a gamete/gametophyte pool (from many parents); the term `haploid selection' encompasses both processes.
 
@@
 In this respect, we might expect that haploid selection would affect transitions between sex-determining systems in a similar manner to sex-specific diploid selection (as explored in~\cite{vanDoorn:2007eu,vanDoorn:2010hu}).
-That is, new masculinizing mutations (neo-Y alleles) could be favoured via associations with alleles that are beneficial in the male haploid stage. 
+That is, new masculinizing mutations (neo-Y alleles) could be favoured via associations with alleles that are beneficial in the male haploid stage (e.g., \cite{Ubeda:2015fx}). 
 On the other hand, sex ratios can also become biased by linkage between the sex-determining locus and a locus that harbours genetic variation in haploid fitness.
-For example, there are several known cases of sex ratio bias caused by sex-linked meiotic drive alleles (Burt and Trivers, 2006, Chapter 6~\cite{Burt:2006}) or selection among X- and Y-bearing pollen~\cite{Lloyd:1974tz,Conn:1981uw,Stehlik:2005ul,Stehlik:2006to,Field:2012fd,Field:2013cc}.
-It is not immediately clear how the spread of new sex-determining systems would be influenced by the combination of sex ratio biases and associations with haploid selected alleles.
-
-We find that the spread of novel sex-determining systems is influenced by both Fisherian sex ratio selection and by selection on linked alleles. 
+For example, there are several known cases of sex-ratio bias caused by sex-linked meiotic drive alleles (Burt and Trivers, 2006, Chapter 6~\cite{Burt:2006}) or selection among X- and Y-bearing pollen~\cite{Lloyd:1974tz,Conn:1981uw,Stehlik:2005ul,Stehlik:2006to,Field:2012fd,Field:2013cc}.
+Sex-ratio selection can thus select against the spread of linked sex-determining alleles and favour the invasion of alternative, unlinked sex-determination systems \cite{Kozielska:2010vm}.
+%It is not immediately clear how the spread of new sex-determining systems would be influenced by the combination of sex ratio biases and associations with haploid selected alleles. 
+It is not yet clear when new sex-determining alleles are favoured by associations with haploid selected alleles vs.
+sex-ratio bias, especially under a wide range of possible diploid selection regimes (e.g., sex-antagonism, overdominance).
+
+We find that the spread of novel sex-determining systems is influenced by both Fisherian sex-ratio selection and by selection on linked alleles. 
 %We find that sex ratio biases caused by haploid selection can exert Fisherian sex ratio selection upon novel sex-determiners but that their spread is also determined by selection on genetically-associated alleles.
 %Indeed, it is only when haploid-selected loci are tightly linked to the ancestral sex-determining region (and so sex ratio biases are initially large) that we see an asymmetry between selection for XY to ZW transitions and ZW to XY transitions (e.g., because haploid selection in males only causes biased zygotic sex ratios in an ancestrally XY system).
-Surprisingly, Fisherian sex ratio selection does not dominate; it is possible for selection on linked alleles to drive turnover between sex-determining systems despite causing increasingly biased sex ratios.
+Fisherian sex-ratio selection does not always dominate; it is possible for selection on linked alleles to drive turnover between sex-determining systems despite causing increasingly biased sex ratios, and our analytical results elucidate what is required for this to be so.
 In addition to considering haploid selection, another novel development in our model is that we consider loci that are in very tight linkage with the ancestral sex-determining locus. 
@@
 However, the zygotic sex ratio is not biased by male haploid selection in ZW sex-determining systems. 
-Similarly, zygotic sex ratio biases can occur if haploid selected alleles are associated with new sex-determining alleles ($R<1/2$). 
+Similarly, zygotic sex-ratio biases can occur if haploid selected alleles are associated with new sex-determining alleles ($R<1/2$). 
 Panel C: During cis-GSD transitions (XY to XY or ZW to ZW), a neo-Y allele spreads to pseudo-fixation (its maximum frequency among male gametes) and the ancestral Y allele is lost. 
@@
 First, competition occurs among male gametes (sperm/pollen competition) and among female gametes (egg/ovule competition) separately. 
-Selection during gametic competition depends on the $\mathbf{A}$ locus genotype; relative fitnesses are given by $w_A^\Hermaphrodite$ and $w_a^\Hermaphrodite$ ($\Hermaphrodite \in \{\female,\male\}$; see table \ref{tab:fitnesstable}).
+Selection during gametic competition depends on the $\mathbf{A}$ locus genotype; relative fitnesses are given by $w_A^\circ$ and $w_a^\circ$ ($\circ \in \{\female,\male\}$; see table \ref{tab:fitnesstable}).
 %$w_{A}^\male$ and $w_{a}^\male$ for male gametes and $w_{A}^\female$ and $w_{a}^\female$ for female gametes, see table \ref{tab:fitnesstable}.
@@
 %(and the $\mathbf{M}$ genotype of their mother in the case of maternal control).
-Diploid males and females then experience selection, with relative fitnesses $w_{AA}^{\Hermaphrodite}$, $w_{Aa}^{\Hermaphrodite}$, and $w_{aa}^{\Hermaphrodite}$.
+Diploid males and females then experience selection, with relative fitnesses $w_{AA}^{\circ}$, $w_{Aa}^{\circ}$, and $w_{aa}^{\circ}$.
 %where $g$ is the diploid genotype at the $\mathbf{A}$ locus ($g \in \{AA, Aa, aa\}$).
@@
 Any linear order of the loci can be modelled with appropriate choices of $r$, $R$, and $\rho$ (see Fig \ref{fig:model_outline}A and \nameref{tab:chisubstitutions}). 
-Individuals that are heterozygous at the $\mathbf{A}$ locus may experience meiotic drive; a gamete produced by $Aa$ heterozgotes of sex $\Hermaphrodite$ bears allele $A$ with probability $\alpha^\Hermaphrodite$.
+Individuals that are heterozygous at the $\mathbf{A}$ locus may experience meiotic drive; a gamete produced by $Aa$ heterozgotes of sex $\circ$ bears allele $A$ with probability $\alpha^\circ$. 
 Thus, the $\mathbf{A}$ locus can experience sex-specific gametic competition, diploid selection, and/or meiotic drive.
@@
 \smallskip
-\caption{{\bf Relative fitness of different genotypes in sex $\Hermaphrodite \in \{\female,\male\}$ } }
+\caption{{\bf Relative fitness of different genotypes in sex $\circ \in \{\female,\male\}$ } }
 \begin{tabular}{l c }
@@
   Genotype & Relative fitness during gametic competition \\ [0.5ex] \hline
-  $A$ & $w_{A}^\Hermaphrodite = 1+t^\Hermaphrodite$ \\
-  $a$ & $w_{a}^\Hermaphrodite = 1$ \\ [0.5ex] \hline
+  $A$ & $w_{A}^\circ = 1+t^\circ$ \\
+  $a$ & $w_{a}^\circ = 1$ \\ [0.5ex] \hline
   Genotype & Relative fitness during diploid selection \\ [0.5ex] \hline
-  $AA$ & $w_{AA}^\Hermaphrodite = 1+ s^\Hermaphrodite$ \\
-  $Aa$ & $w_{Aa}^\Hermaphrodite = 1+h^\Hermaphrodite s^\Hermaphrodite$ \\
-  $aa$ & $w_{aa}^\Hermaphrodite = 1$ \\ [0.5ex] \hline
+  $AA$ & $w_{AA}^\circ = 1+ s^\circ$ \\
+  $Aa$ & $w_{Aa}^\circ = 1+h^\circ s^\circ$ \\
+  $aa$ & $w_{aa}^\circ = 1$ \\ [0.5ex] \hline
   Genotype & Transmission during meiosis in $Aa$ heterozygotes \\ [0.5ex] \hline
-  $A$ & $\alpha^\Hermaphrodite=1/2+\alpha_{\Delta}^{\Hermaphrodite}/2$ \\
-  $a$ & $1-\alpha^\Hermaphrodite=1/2-\alpha_{\Delta}^{\Hermaphrodite}/2$ \\
+  $A$ & $\alpha^\circ=1/2+\alpha_{\Delta}^{\circ}/2$ \\
+  $a$ & $1-\alpha^\circ=1/2-\alpha_{\Delta}^{\circ}/2$ \\
   \hline \hline
@@
 We also track the fraction of male gametes that are Y-bearing, $q$, which may deviate from $1/2$ due to meiotic drive in males. 
-We will consider only equilibrium frequencies of alleles, $\hat{p}^\Hermaphrodite_i$, and Y-bearing male gametes, $\hat{q}$, when calculating the eigenvalues.
+We will consider only equilibrium frequencies of alleles, $\hat{p}^\circ_i$, and Y-bearing male gametes, $\hat{q}$, when calculating the eigenvalues.
 
@@
 $\zeta$ is the zygotic sex ratio (fraction male).
-$\bar{w}^{\Hermaphrodite}_{D}$ is the mean fitness of diploids of sex $\Hermaphrodite$.
-$\bar{w}_H^\Hermaphrodite$ is the mean fitness of haploids from sex $\Hermaphrodite$, see \nameref{tab:meanfitnesses}.
+$\bar{w}^{\circ}_{D}$ is the mean fitness of diploids of sex $\circ$ $\in\{\female,\male\}$.
+$\bar{w}_H^\circ$ is the mean fitness of haploids from sex $\circ$, see \nameref{tab:meanfitnesses}.
 \end{flushleft}
@@
 
-We can draw a number of key points about the invasion of neo-Y and neo-W mutations from Table \ref{tab:haplotype_growth}. 
-First, Fisherian sex ratio selection will favour the spread of a neo-Y and inhibit the spread of a neo-W if the ancestral zygotic sex ratio is biased towards females, $\zeta<1/2$ (i.e., the first factor of the $\Lambda_{mi}^{(XY)}$ is greater than one for a neo-Y and less than one for a neo-W).
+We draw three main conclusions about the generic invasion of neo-Y and neo-W mutations from Table \ref{tab:haplotype_growth}:
+\vspace{0.5cm}
+
+\noindent\textit{Conclusion 1: Fisherian sex-ratio selection will favour the spread of a neo-Y and inhibit the spread of a neo-W if the ancestral zygotic sex ratio is biased towards females}, $\zeta<1/2$ (i.e., the first factor of the $\Lambda_{mi}^{(XY)}$ is greater than one for a neo-Y and less than one for a neo-W).
 However, the spread of a neo-Y (neo-W) also depends on the male (female) fitness of associated alleles (see terms involving equilibrium allele frequencies, $\hat{p}$'s).
-Second, invasion by a neo-Y (neo-W) does not directly depend on the fitness of female (male) diploids. %(for a given set of equilibrium allele frequencies).
+\vspace{0.5cm}
+
+\noindent\textit{Conclusion 2: invasion by a neo-Y (neo-W) does not directly depend on the fitness of female (male) diploids}. %(for a given set of equilibrium allele frequencies).
 This is because a dominant neo-Y (neo-W) is always found in males (females), and therefore the frequency of the neo-Y (neo-W), $m$, only changes in males (females), Fig \ref{fig:model_outline}C,D. 
-Finally, invasions by a neo-Y and a neo-W are qualitatively different.
+\vspace{0.5cm}
+
+\noindent\textit{Conclusion 3: invasions by a neo-Y and a neo-W are qualitatively different}.
 This is because a gamete with the neo-Y always pairs with a female gamete containing an X, Fig \ref{fig:model_outline}C.
@@
 Consequently, neo-W-bearing females obtain a different frequency of $A$ alleles from mating (when $\hat{p}_X^\male \neq \hat{p}_Y^\male$) compared to ancestral ($MM$) females.
+\vspace{0.5cm}
 
@@
 We can analytically calculate the allele frequency of the $A$ allele using two alternative simplifying assumptions: 
-(1) the $\mathbf{A}$ locus is within (or tightly linked to) the non-recombining region around the ancestral sex-determining locus ($r \approx 0$) or (2) selection is weak relative to recombination ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon<<1$).
+(1) the $\mathbf{A}$ locus is within (or tightly linked to) the non-recombining region around the ancestral sex-determining locus ($r \approx 0$) or (2) selection is weak relative to recombination ($s^\circ$, $t^\circ$, $\alpha_{\Delta}^\circ$ of order $\epsilon<<1$).
 
@@
 
-Neo-W alleles, on the other hand, can invade an ancestral XY system under some conditions (the full invasion conditions are given in \nameref{app:inv_cond}; equations \ref{Binvasion} and \ref{Ainvasion}).
-Counterintuitively, selection on loci within the non-recombining region around the sex-determining locus can favour the invasion of a less closely linked neo-W, whatever the form of selection maintaining a polymorphism (sexually-antagonistic selection, overdominance, ploidally-antagonistic selection, or some combination, Fig \ref{fig:SexAntagTighter}, \nameref{fig:temporalOverdominance}, \nameref{fig:regionPloidAntag}, and \nameref{fig:SexAntagTighterMaleDrive}).
+Neo-W alleles, on the other hand, can invade an ancestral XY system under some conditions (the full invasion conditions are given in \nameref{app:inv_cond}; equations \ref{Binvasion} and \ref{Ainvasion}):
+\vspace{0.5cm}
+
+\noindent\textit{Conclusion 4: counterintuitively, selection on loci within the non-recombining region around the sex-determining locus ($r\approx0$) can favour the invasion of a less closely linked neo-W ($r<R$)}, whatever the form of selection maintaining a polymorphism (sexually-antagonistic selection, overdominance, ploidally-antagonistic selection, or some combination, Fig \ref{fig:SexAntagTighter}, \nameref{fig:temporalOverdominance}, \nameref{fig:regionPloidAntag}, and \nameref{fig:SexAntagTighterMaleDrive}).
 The conditions become more restrictive, however, with increasing recombination ($R$) between the new sex-determining locus and the selected locus.  
 The invasion of completely unlinked neo-W alleles ($R = 1/2$) can occur with overdominance in males or with haploid selection but is not possible with only sexually-antagonistic selection if selection is directional in each diploid sex (see \nameref{file:Mathematica}).
-To develop an intuition for how less closely linked neo-W alleles invade ($R>r$), we here focus on cases where there is no haploid selection and discuss the additional effect of haploid selection in \nameref{app:inv_cond}.
+\vspace{0.5cm}
 
@@
 A very loosely linked neo-W does not spread in this case (blue and green lines overlap and go to 0 in inset). 
-Fitness parameters are: $w_{AA}^\female = 1.05$, $w_{aa}^\male = 1.2$, $w_{aa}^\female = w_{AA}^\male = 0.85$, $w_{Aa}^\Hermaphrodite = 1$,  $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
+Fitness parameters are: $w_{AA}^\female = 1.05$, $w_{aa}^\male = 1.2$, $w_{aa}^\female = w_{AA}^\male = 0.85$, $w_{Aa}^\circ = 1$,  $t^\circ = \alpha^\circ_\Delta = 0$.
 %\textcolor{red}{consider removing panel A, which is repeated in Fig 3.}
@@
 
+To develop an intuition for how less closely linked neo-W alleles invade ($R>r$), we here focus on cases where there is no haploid selection and discuss the additional effect of haploid selection in \nameref{app:inv_cond}.
 If we categorise the $a$ allele as being ancestrally `male-beneficial' via the fact that it is fixed on Y backgrounds, then $\Lambda_{W'A}^{(XY)}>1$ indicates that the neo-W spreads when found with the ancestrally `female-beneficial' allele.
@@
 {\bf When the ancestral XY locus is tightly linked to a locus under selection ($r=0$), one or both neo-W haplotypes can spread. }
-We vary the fitness of male homozygotes relative to heterozygotes ($w_{Aa}^\Hermaphrodite=1$) and only consider stable equilibria at which both $\mathbf{A}$ locus alleles are maintained and the $a$ allele is initially fixed on Y backgrounds, region outlined.
+We vary the fitness of male homozygotes relative to heterozygotes ($w_{Aa}^\circ=1$) and only consider stable equilibria at which both $\mathbf{A}$ locus alleles are maintained and the $a$ allele is initially fixed on Y backgrounds, region outlined.
 Here, selection in females can favour the $A$ allele (panel A, $w_{aa}^\female=0.85$, $w_{AA}^\female=1.05$), favour the $a$ allele (panel B, $w_{aa}^\female=1.05$, $w_{AA}^\female=0.85$), or be overdominant (panel C, $w_{aa}^\female=w_{AA}^\female=0.6$).
@@
 \nameref{fig:positionOverdominance} shows the dynamics arising with the parameters marked with a dagger. 
-Here, there is no haploid selection $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
+Here, there is no haploid selection $t^\circ = \alpha^\circ_\Delta = 0$.
 }
@@
 
-Here we assume that selection is weak ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon<<1$) and thus implicitly assume that all recombination rates ($r$, $R$ and $\rho$) are large relative to selection.
+Here we assume that selection is weak ($s^\circ$, $t^\circ$, $\alpha_{\Delta}^\circ$ of order $\epsilon<<1$) and thus implicitly assume that all recombination rates ($r$, $R$ and $\rho$) are large relative to selection.
 %, we denote the leading eigenvalues describing the invasion of a neo-Y ($k=0$) and a neo-W ($k=1$) into an ancestrally XY system by $\lambda_{Y',XY}$ and $\lambda_{W',XY}$, respectively. 
@@
 where $V_{A}=\bar{p}(1-\bar{p})$ is the variance in the equilibrium frequency of $A$ and $S_{A}=(D^\male +\alpha_{\Delta}^\male+t^\male) - (D^\female+\alpha_{\Delta}^\female+t^\female)$ describes sex differences in selection for the $A$ versus $a$ allele across diploid selection, meiosis, and gametic competition.
-The diploid selection term, $D^\Hermaphrodite=\big{[} \bar{p}s^\Hermaphrodite+(1-\bar{p})h^\Hermaphrodite s^\Hermaphrodite\big{]} -\big{[} \bar{p}h^\Hermaphrodite s^\Hermaphrodite+(1-\bar{p}) \big{]}$, is the difference in fitness between $A$ and $a$ alleles in diploids of sex $\Hermaphrodite \in \{\female,\male\}$, where $\bar{p}$ is the leading-order probability of mating with an $A$-bearing gamete from the opposite sex (equation \ref{eq:pAve}).
+The diploid selection term, $D^\circ=\big{[} \bar{p}s^\circ+(1-\bar{p})h^\circ s^\circ\big{]} -\big{[} \bar{p}h^\circ s^\circ+(1-\bar{p}) \big{]}$, is the difference in fitness between $A$ and $a$ alleles in diploids of sex $\circ \in \{\female,\male\}$, where $\bar{p}$ is the leading-order probability of mating with an $A$-bearing gamete from the opposite sex (equation \ref{eq:pAve}).
 The difference in $A$-allele-frequency among Y-bearing sperm versus X-bearing sperm is given by $\hat{p}^\male_Y-\hat{p}^\male_X=V_{A}\big{(}D^\male - D^\female+\alpha_{\Delta}^\male-\alpha_{\Delta}^\female+t^\male-t^\female\big{)}(1-2r)/(2r)$.
@@
 
-With weak selection and no haploid selection ($t^\Hermaphrodite=\alpha^\Hermaphrodite_{\Delta}=0$), the spread of a neo-W is equivalent to the spread of a neo-Y ($\lambda_{W'}^{(XY)}=\lambda_{Y'}^{(XY)}$), such that trans-GSD transitions can also occur only if the new sex-determining locus is more closely linked to a locus under selection ($R<r$), as found by \cite{vanDoorn:2010hu}.
+With weak selection and no haploid selection ($t^\circ=\alpha^\circ_{\Delta}=0$), the spread of a neo-W is equivalent to the spread of a neo-Y ($\lambda_{W'}^{(XY)}=\lambda_{Y'}^{(XY)}$), such that trans-GSD transitions can also occur only if the new sex-determining locus is more closely linked to a locus under selection ($R<r$), as found by \cite{vanDoorn:2010hu}.
 When there is haploid selection, invasion also typically occurs when the neo-W is more closely linked to the selected locus than the ancestral sex-determining region (Fig \ref{fig:Combination_Centimorgans}).
@@
 {\bf Ploidally-antagonistic selection allows a less tightly linked neo-W allele to invade.}
-In panel A, male drive ($\alpha^\male_{\Delta} = -1/20$, $t^\Hermaphrodite = \alpha^\female_{\Delta} = 0$) opposes selection in diploids (no sex-differences: $s^\Hermaphrodite = 1/10$, $h^\Hermaphrodite = 7/10$), in which case the new sex-determining allele can invade regardless of its linkage with the selected locus ($R$).
-In panel B, gametic competition in males ($t^\male = -1/10$, $t^\female = \alpha^\Hermaphrodite_{\Delta} = 0$) opposes selection in diploids (sex-differences: $s^\male = 3/20$, $s^\female = 1/20$, $h^\Hermaphrodite = 7/10$), in which case the new sex-determining allele can once again invade regardless of $R$.
+In panel A, male drive ($\alpha^\male_{\Delta} = -1/20$, $t^\circ = \alpha^\female_{\Delta} = 0$) opposes selection in diploids (no sex-differences: $s^\circ = 1/10$, $h^\circ = 7/10$), in which case the new sex-determining allele can invade regardless of its linkage with the selected locus ($R$).
+In panel B, gametic competition in males ($t^\male = -1/10$, $t^\female = \alpha^\circ_{\Delta} = 0$) opposes selection in diploids (sex-differences: $s^\male = 3/20$, $s^\female = 1/20$, $h^\circ = 7/10$), in which case the new sex-determining allele can once again invade regardless of $R$.
 }
@@
 However, with haploid selection and $r<1/2$, the additional term in Eq \eqref{eq:lambda_neoW} can be positive.
-This can allow neo-W invasion ($\lambda_{W'}^{(XY)}>1$), even when the new sex-determining locus is less closely linked to the selected locus ($R>r$). 
+This implies: 
+\vspace{0.5cm}
+
+\noindent\textit{Conclusion 5: with intermediate recombination between the ancestral sex-determining allele and a selected locus, $0<r<1/2$, a less closely linked neo-W ($r<R$) can invade} ($\lambda_{W'}^{(XY)}>1$).
+\vspace{0.5cm}
+
 %These transitions are unusual because, when $R>r$, associations that selection has built up between alleles more favourable in one sex and alleles that determine sex will be weakened. 
@@
 \caption{
-{\bf Fisherian sex ratio selection alone is not a good predictor of turnover between sex-determining systems.}
+{\bf Fisherian sex-ratio selection alone is not a good predictor of turnover between sex-determining systems.}
 In this figure, selection is ploidally antagonistic with haploid selection favouring the $a$ allele during male meiosis.
@@
 %If the ancxestral sex-determining system is ZW, the zygotic sex ratio will be 1:1 because diploid sex is determined by the proportion of Z-bearing versus W-bearing eggs and meiosis in females is fair (Fig \ref{fig:Combination_Turnover}D).
-If Fisherian sex ratio selection were dominant, we would thus expect a difference in the potential for XY to ZW and ZW to XY transitions. 
+If Fisherian sex-ratio selection were dominant, we would thus expect a difference in the potential for XY to ZW and ZW to XY transitions. 
 %However, to leading order with selection weak relative to recombination, we find that sex ratio selection favours the spread of a neo-W by an amount equl to the spread of a neo-Y into a ZW system (relabeling XY as the heterogametic sex and reversing the labels of males and females in Table \ref{tab:specialcases})
@@
 However, Fig \ref{fig:SexRatioBad}B shows that a neo-Y can invade the resulting ZW system under the same conditions. 
-When $R<1/2$, the invading neo-Y becomes associated with the male meiotic drive allele and the zygotic sex ratio actually evolves to become male-biased.
+When $R<1/2$, the invading neo-Y becomes associated with the male meiotic drive allele and the zygotic sex ratio actually evolves to become male-biased (similar to the scenario considered in \cite{Ubeda:2015fx}).
 In this case, the neo-Y spreads because it is often found in males and can, if it carries the driven allele $a$, benefit from haploid selection in males (Fig \ref{fig:SexRatioBad}B).
@@
 As discussed above, $\lambda_{Y'\rvert R=1/2}^{(XY)}$ is necessarily less than one, but $\lambda_{W'\rvert R=1/2}^{(XY)}$ can be greater than one if there is haploid selection.
-That is, when there is haploid selection, ESD can invade an ancestrally-XY system because it generates females that are either rare or have high fitness, in the same manner as a neo-W.
+That is:
+\vspace{0.5cm}
+
+\noindent\textit{Conclusion 6: when there is haploid selection, ESD can invade an ancestrally-XY system because it generates females that are either rare or have high fitness, in the same manner as a neo-W}.
+\vspace{0.5cm}
 
@@
 Significantly, Eq \eqref{eq:lambda_ESD} is the same whether ESD is invading an ancestrally XY or ZW system (because $\lambda_{Y'}^{(XY)} = \lambda_{W'}^{(ZW)}$ and $\lambda_{W'}^{(XY)} = \lambda_{Y'}^{(ZW)}$).
-Thus, Fisherian sex ratio selection alone does not easily explain GSD to ESD transitions.
+Thus, Fisherian sex-ratio selection alone does not easily explain GSD to ESD transitions.
 For example, when the ancestral sex-determining system is XY, but not ZW, the sex ratio is biased by male haploid selection.
@@
 %MAIN RESULT
-Two predominant theories explaining the remarkably high frequency of transitions between sex-determining systems are sexually-antagonistic selection and sex ratio selection (reviewed in~\cite{Blaser2012, vanDoorn2014re}).
+Two predominant theories explaining the remarkably high frequency of transitions between genetic sex-determining systems are sexually-antagonistic selection and sex ratio selection (reviewed in~\cite{Blaser2012, vanDoorn2014re}).
 The former predicts that new sex-determining alleles can invade when they arise in closer linkage with a sexually-antagonistic locus ($r<R$,~\cite{vanDoorn:2007eu,vanDoorn:2010hu, Muralidhar2018}).
@@
 We conclude that haploid selection should be considered as a pivotal factor driving transitions between sex-determining systems. 
-Perhaps counterintuitively, transitions involving haploid selection can be driven by sex ratio selection or cause sex ratio biases to evolve; we do not find Fisherian sex ratio selection to be an overwhelming force.
+Further, transitions involving haploid selection can be driven by sex-ratio selection or cause sex ratio biases to evolve; Fisherian sex-ratio selection is not an overwhelming force. 
 Overall, our results suggest several new scenarios under which new sex-determining systems are favoured, which could help to explain why the evolution of sex-determining systems is so dynamic.
@@
 {\bf With overdominance, loci near to the ancestral sex-determining locus ($r\approx0$) can favour neo-W alleles that are less tightly linked ($R>r$).} 
-In panels A and B, the $a$ allele is favoured in females ($w_{aa}^\female=1.05$, $w_{Aa}^\Hermaphrodite=1$, $w_{AA}^\female=0.85$) and selection in males is overdominant ($w_{aa}^\male=w_{AA}^\male=0.75$).
-In panels C and D, selection in males and females is overdominant ($w_{aa}^\female=w_{AA}^\female=0.6$, $w_{aa}^\male=0.5$, $w_{AA}^\male=0.7$, $w_{Aa}^\Hermaphrodite=1$).
-There is no haploid selection $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
+In panels A and B, the $a$ allele is favoured in females ($w_{aa}^\female=1.05$, $w_{Aa}^\circ=1$, $w_{AA}^\female=0.85$) and selection in males is overdominant ($w_{aa}^\male=w_{AA}^\male=0.75$).
+In panels C and D, selection in males and females is overdominant ($w_{aa}^\female=w_{AA}^\female=0.6$, $w_{aa}^\male=0.5$, $w_{AA}^\male=0.7$, $w_{Aa}^\circ=1$).
+There is no haploid selection $t^\circ = \alpha^\circ_\Delta = 0$.
 These parameters are marked by daggers in Fig \ref{fig:regionplots}B and C, which show that neo-W invasion is expected for any $R$ ($\Lambda_{W'A}^{(XY)},\Lambda_{W'a}^{(XY)}>1$) if the $a$ allele is nearly fixed on the Y (black lines in this figure; not stable for $r>>0$).
@@
 In contrast, the neo-W is not lost in panel D as it is favoured regardless of whether Y-$A$ or Y-$a$ haplotypes predominate (again, compare blue to black curves in \nameref{fig:positionOverdominance}C and  \nameref{fig:positionOverdominance}D).
-%Fitness parameters are the same as in \nameref{fig:positionOverdominance}; in panels A and B the $a$ allele is favoured in females ($w_{aa}^\female=1.05$, $w_{Aa}^\Hermaphrodite=1$, $w_{AA}^\female=0.85$) while there is overdominance in males ($w_{aa}^\male=w_{AA}^\male=0.75$) and in panels C and D, there is overdominance in both sexes ($w_{aa}^\female=w_{AA}^\female=0.6$, $w_{aa}^\male=0.5$, $w_{AA}^\male=0.7$, $w_{Aa}^\Hermaphrodite=1$).
+%Fitness parameters are the same as in \nameref{fig:positionOverdominance}; in panels A and B the $a$ allele is favoured in females ($w_{aa}^\female=1.05$, $w_{Aa}^\circ=1$, $w_{AA}^\female=0.85$) while there is overdominance in males ($w_{aa}^\male=w_{AA}^\male=0.75$) and in panels C and D, there is overdominance in both sexes ($w_{aa}^\female=w_{AA}^\female=0.6$, $w_{aa}^\male=0.5$, $w_{AA}^\male=0.7$, $w_{Aa}^\circ=1$).
 %These parameters are marked by a dagger in Fig \ref{fig:regionplots}. 
-%Here, there is no haploid selection $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
+%Here, there is no haploid selection $t^\circ = \alpha^\circ_\Delta = 0$.
 
@@
 This figure is equivalent to Fig \ref{fig:regionplots} but with meiotic drive in males.
-%We vary the fitness of male homozygotes relative to heterozygotes ($w_{Aa}^\Hermaphrodite=1$) and only consider stable equilibria at which both $\mathbf{A}$ locus allele are maintained and the $a$ allele is initially fixed on the Y, region outlined.
+%We vary the fitness of male homozygotes relative to heterozygotes ($w_{Aa}^\circ=1$) and only consider stable equilibria at which both $\mathbf{A}$ locus allele are maintained and the $a$ allele is initially fixed on the Y, region outlined.
 In panels A-C, meiotic drive in males favours the $a$ allele ($\alpha_{\Delta}^\male=-0.16$), creating male-biased sex ratios and generally increasing $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$.
@@
 This figure is equivalent to Fig \ref{fig:regionplots} but with gametic competition in males.
-%Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in \nameref{fig:regionMaleDrive}. 
+%Diploid selection parameters ($w_{ij}^\circ$) are the same as those in \nameref{fig:regionMaleDrive}. 
 The $a$ allele is favoured during male gametic competition in Panels A-C ($w_{a}^\male=1.16$, $w_{A}^\male=1$), which creates male biased sex ratios and increases $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$.
@@
 This figure is equivalent to Fig \ref{fig:regionplots} but with meiotic drive in females.
-%Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in \nameref{fig:regionMaleDrive} and \nameref{fig:regionMaleGS}. 
+%Diploid selection parameters ($w_{ij}^\circ$) are the same as those in \nameref{fig:regionMaleDrive} and \nameref{fig:regionMaleGS}. 
 The $a$ allele is favoured by meiotic drive in females in Panels A-C ($\alpha_{\Delta}^\female=-0.16$), which increases $\Lambda_{W'a}^{(XY)}$ and decreases $\Lambda_{W'A}^{(XY)}$. 
@@
 This figure is equivalent to Fig \ref{fig:regionplots} but with gametic competition in females.
-%Diploid selection parameters ($w_{ij}^\Hermaphrodite$) are the same as those in \nameref{fig:regionMaleDrive}, \nameref{fig:regionMaleGS}, and \nameref{fig:regionFemaleDrive}. 
+%Diploid selection parameters ($w_{ij}^\circ$) are the same as those in \nameref{fig:regionMaleDrive}, \nameref{fig:regionMaleGS}, and \nameref{fig:regionFemaleDrive}. 
 The $a$ allele is favoured during female gametic competition in females in Panels A-C ($w_{a}^\female=1.16$, $w_{A}^\female=1$), which increases $\Lambda_{W'a}^{(XY)}$ and decreases $\Lambda_{W'A}^{(XY)}$.
@@
 A-D show when each of the neo-W haplotypes invades an internally stable equilibrium with $a$ fixed on the Y (found by setting $r=0$).
-The y-axis shows directional selection in diploids of both sexes, $s^\female=s^\male$, and the x-axes show sex-specific drive, $\alpha_\Delta^\Hermaphrodite$, or haploid competition, $t^\Hermaphrodite$.
+The y-axis shows directional selection in diploids of both sexes, $s^\female=s^\male$, and the x-axes show sex-specific drive, $\alpha_\Delta^\circ$, or haploid competition, $t^\circ$.
 The top left and bottom right quadrants therefore imply ploidally-antagonistic selection (and these are the only places where neo-W haplotypes can invade).
@@
 %In each generation we census the genotype frequencies in male and female gametes/gametophytes (hereafter, gametes) between meiosis (and any meiotic drive) and gametic competition. 
-%At this stage we denote the frequencies of X- and Y-bearing gametes from males and females $x_{i}^{\Hermaphrodite}$ and $y_{i}^{\Hermaphrodite}$.
-%The superscript $\Hermaphrodite \in \{\male,\female\}$ specifies the sex of the diploid that the gamete came from. 
+%At this stage we denote the frequencies of X- and Y-bearing gametes from males and females $x_{i}^{\circ}$ and $y_{i}^{\circ}$.
+%The superscript $\circ \in \{\male,\female\}$ specifies the sex of the diploid that the gamete came from. 
 %The subscript $i\in\{1,2,3,4\}$ specifies the genotype at the selected locus $\mathbf{A}$ and at the novel sex-determining locus $\mathbf{M}$, where $1=AM$, $2=aM$, $3=Am$, and $4=am$. 
-%The gamete frequencies from each sex sum to one, $\sum_{i}x_{i}^{\Hermaphrodite}+y_{i}^{\Hermaphrodite}=1$. 
-%
-%Competition then occurs among gametes of the same sex (e.g., among eggs and among sperm separately) according to the genotype at the $\mathbf{A}$ locus ($w_{1}^\Hermaphrodite=w_{3}^\Hermaphrodite=w_{A}^\Hermaphrodite$, $w_{2}^\Hermaphrodite=w_{4}^\Hermaphrodite=w_{a}^\Hermaphrodite$, see Table \ref{tab:fitnesstable}).
-%The genotype frequencies after gametic competition are $x_{i}^{\Hermaphrodite,s}= w_{i}^{\Hermaphrodite}x_{i}^{\Hermaphrodite}/\bar{w}_{H}^{\Hermaphrodite}$ and $y_{i}^{\Hermaphrodite,s}= w_{i}^{\Hermaphrodite}y_{i}^{\Hermaphrodite}/\bar{w}_{H}^{\Hermaphrodite}$, where $\bar{w}_{H}^{\Hermaphrodite}=\sum_{i} w_{i}^{\Hermaphrodite}x_{i}^{\Hermaphrodite}+w_{i}^{\Hermaphrodite}y_{i}^{\Hermaphrodite}$ is the mean fitness of male ($\Hermaphrodite=\male$) or female ($\Hermaphrodite=\female$) gametes.
+%The gamete frequencies from each sex sum to one, $\sum_{i}x_{i}^{\circ}+y_{i}^{\circ}=1$. 
+%
+%Competition then occurs among gametes of the same sex (e.g., among eggs and among sperm separately) according to the genotype at the $\mathbf{A}$ locus ($w_{1}^\circ=w_{3}^\circ=w_{A}^\circ$, $w_{2}^\circ=w_{4}^\circ=w_{a}^\circ$, see Table \ref{tab:fitnesstable}).
+%The genotype frequencies after gametic competition are $x_{i}^{\circ,s}= w_{i}^{\circ}x_{i}^{\circ}/\bar{w}_{H}^{\circ}$ and $y_{i}^{\circ,s}= w_{i}^{\circ}y_{i}^{\circ}/\bar{w}_{H}^{\circ}$, where $\bar{w}_{H}^{\circ}=\sum_{i} w_{i}^{\circ}x_{i}^{\circ}+w_{i}^{\circ}y_{i}^{\circ}$ is the mean fitness of male ($\circ=\male$) or female ($\circ=\female$) gametes.
 %
@@
 %Selection among diploids then occurs according to the diploid genotype at the $\mathbf{A}$ locus, $l \in \{AA, Aa, aa\}$, for an individual of type $ij$ (see Table \ref{tab:fitnesstable}). 
-%The diploid frequencies after selection in sex $\Hermaphrodite$ are given by $xx_{ij}^{\Hermaphrodite,s}=w_{l}^{\Hermaphrodite} xx_{ij}/\bar{w}^{\Hermaphrodite}_{D}$, $xy_{ij}^{\Hermaphrodite,s}=w_{l}^{\Hermaphrodite} xy_{ij}/\bar{w}^{\Hermaphrodite}_{D}$, and $yy_{ij}^{\Hermaphrodite,s}=w_{l}^{\Hermaphrodite} yy_{ij}/\bar{w}^{\Hermaphrodite}_{D}$, where $\bar{w}^{\Hermaphrodite}_{D}= \sum_{i=1}^{4}\sum_{j=1}^{4}w_{l}^{\Hermaphrodite}xx_{ij}+w_{l}^{\Hermaphrodite}xy_{ij}+w_{l}^{\Hermaphrodite}yy_{ij}$ is the mean fitness of diploids of sex $\Hermaphrodite$.
+%The diploid frequencies after selection in sex $\circ$ are given by $xx_{ij}^{\circ,s}=w_{l}^{\circ} xx_{ij}/\bar{w}^{\circ}_{D}$, $xy_{ij}^{\circ,s}=w_{l}^{\circ} xy_{ij}/\bar{w}^{\circ}_{D}$, and $yy_{ij}^{\circ,s}=w_{l}^{\circ} yy_{ij}/\bar{w}^{\circ}_{D}$, where $\bar{w}^{\circ}_{D}= \sum_{i=1}^{4}\sum_{j=1}^{4}w_{l}^{\circ}xx_{ij}+w_{l}^{\circ}xy_{ij}+w_{l}^{\circ}yy_{ij}$ is the mean fitness of diploids of sex $\circ$.
 %
@@
 %\nameref{tab:chisubstitutions} shows replacements that can be made for each possible ordering of the loci assuming that there is no cross-over interference.
-%During meiosis in sex $\Hermaphrodite$, meiotic drive occurs such that, in $Aa$ heterozygotes, a fraction $\alpha^{\Hermaphrodite}$ of gametes produced carry the $A$ allele and $(1-\alpha^\Hermaphrodite)$ carry the $a$ allele.
-%
-%Among gametes from sex $\Hermaphrodite$, the frequencies of haplotypes (before gametic competition) in the next generation are given by
+%During meiosis in sex $\circ$, meiotic drive occurs such that, in $Aa$ heterozygotes, a fraction $\alpha^{\circ}$ of gametes produced carry the $A$ allele and $(1-\alpha^\circ)$ carry the $a$ allele.
+%
+%Among gametes from sex $\circ$, the frequencies of haplotypes (before gametic competition) in the next generation are given by
 %
@@
 %\begin{split}
-%x_{1}^{{\Hermaphrodite}'}=&xx_{11}^{\Hermaphrodite,s}+xx_{13}^{\Hermaphrodite,s}/2+(xx_{12}^{\Hermaphrodite,s}+xx_{14}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-%&-R(xx_{14}^{\Hermaphrodite,s}-xx_{23}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-%&+(xy_{11}^{\Hermaphrodite,s}+xy_{13}^{\Hermaphrodite,s})/2+(xy_{12}^{\Hermaphrodite,s}+xy_{14}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-%&- r(xy_{12}^{\Hermaphrodite,s}-xy_{21}^{\Hermaphrodite,s})\alpha^\Hermaphrodite - \rho(xy_{13}^{\Hermaphrodite,s}-xy_{31}^{\Hermaphrodite,s})/2\\
-%&+\big{[}-(R+r+\rho)xy_{14}^{\Hermaphrodite,s} +(R+\rho-r)xy_{41}^{\Hermaphrodite,s}\\
-%&+(R+r-\rho) xy_{23}^{\Hermaphrodite,s}+(R+\rho-r)xy_{32}^{\Hermaphrodite,s}\big{]}\alpha^\Hermaphrodite/2
+%x_{1}^{{\circ}'}=&xx_{11}^{\circ,s}+xx_{13}^{\circ,s}/2+(xx_{12}^{\circ,s}+xx_{14}^{\circ,s})\alpha^\circ\\
+%&-R(xx_{14}^{\circ,s}-xx_{23}^{\circ,s}) \alpha^\circ\\
+%&+(xy_{11}^{\circ,s}+xy_{13}^{\circ,s})/2+(xy_{12}^{\circ,s}+xy_{14}^{\circ,s})\alpha^\circ\\
+%&- r(xy_{12}^{\circ,s}-xy_{21}^{\circ,s})\alpha^\circ - \rho(xy_{13}^{\circ,s}-xy_{31}^{\circ,s})/2\\
+%&+\big{[}-(R+r+\rho)xy_{14}^{\circ,s} +(R+\rho-r)xy_{41}^{\circ,s}\\
+%&+(R+r-\rho) xy_{23}^{\circ,s}+(R+\rho-r)xy_{32}^{\circ,s}\big{]}\alpha^\circ/2
 %\end{split}
@@
 %\begin{split}
-%x_{2}^{{\Hermaphrodite}'}=&xx_{22}^{\Hermaphrodite,s}+xx_{24}^{\Hermaphrodite,s}/2+(xx_{12}^{\Hermaphrodite,s}+xx_{23}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-%&-R(xx_{23}^{\Hermaphrodite,s}-xx_{14}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-%&(xy_{22}^{\Hermaphrodite,s}+xy_{24}^{\Hermaphrodite,s})/2+(xy_{21}^{\Hermaphrodite,s}+xy_{23}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite)\\
-%&- r(xy_{21}^{\Hermaphrodite,s}-xy_{12}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite) - \rho(xy_{24}^{\Hermaphrodite,s}-xy_{42}^{\Hermaphrodite,s})/2\\
-%&+\big{[}-(R+r+\rho)xy_{23}^{\Hermaphrodite,s}+(R+\rho-r)xy_{32}^{\Hermaphrodite,s}\\
-%&+(R+r-\rho) xy_{14}^{\Hermaphrodite,s}+(R+\rho-r)xy_{41}^{\Hermaphrodite,s}\big{]}(1-\alpha^\Hermaphrodite)/2
+%x_{2}^{{\circ}'}=&xx_{22}^{\circ,s}+xx_{24}^{\circ,s}/2+(xx_{12}^{\circ,s}+xx_{23}^{\circ,s})\alpha^\circ\\
+%&-R(xx_{23}^{\circ,s}-xx_{14}^{\circ,s}) \alpha^\circ\\
+%&(xy_{22}^{\circ,s}+xy_{24}^{\circ,s})/2+(xy_{21}^{\circ,s}+xy_{23}^{\circ,s})(1-\alpha^\circ)\\
+%&- r(xy_{21}^{\circ,s}-xy_{12}^{\circ,s})(1-\alpha^\circ) - \rho(xy_{24}^{\circ,s}-xy_{42}^{\circ,s})/2\\
+%&+\big{[}-(R+r+\rho)xy_{23}^{\circ,s}+(R+\rho-r)xy_{32}^{\circ,s}\\
+%&+(R+r-\rho) xy_{14}^{\circ,s}+(R+\rho-r)xy_{41}^{\circ,s}\big{]}(1-\alpha^\circ)/2
 %\end{split}
@@
 %\begin{split}
-%x_{3}^{{\Hermaphrodite}'}=&xx_{33}^{\Hermaphrodite,s}+xx_{13}^{\Hermaphrodite,s}/2+(xx_{23}^{\Hermaphrodite,s}+xx_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-%&-R(xx_{23}^{\Hermaphrodite,s}-xx_{14}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-%&(xy_{33}^{\Hermaphrodite,s}+xy_{31}^{\Hermaphrodite,s})/2+(xy_{32}^{\Hermaphrodite,s}+xy_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-%&- r(xy_{34}^{\Hermaphrodite,s}-xy_{43}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite - \rho(xy_{31}^{\Hermaphrodite,s}-xy_{13}^{\Hermaphrodite,s})/2\\
-%&+\big{[}-(R+r+\rho)xy_{32}^{\Hermaphrodite,s} +(R+\rho-r)xy_{23}^{\Hermaphrodite,s}\\
-%&+(R+r-\rho) xy_{41}^{\Hermaphrodite,s}+(R+\rho-r)xy_{14}^{\Hermaphrodite,s}\big{]} \alpha^\Hermaphrodite/2
+%x_{3}^{{\circ}'}=&xx_{33}^{\circ,s}+xx_{13}^{\circ,s}/2+(xx_{23}^{\circ,s}+xx_{34}^{\circ,s})\alpha^\circ\\
+%&-R(xx_{23}^{\circ,s}-xx_{14}^{\circ,s}) \alpha^\circ\\
+%&(xy_{33}^{\circ,s}+xy_{31}^{\circ,s})/2+(xy_{32}^{\circ,s}+xy_{34}^{\circ,s})\alpha^\circ\\
+%&- r(xy_{34}^{\circ,s}-xy_{43}^{\circ,s}) \alpha^\circ - \rho(xy_{31}^{\circ,s}-xy_{13}^{\circ,s})/2\\
+%&+\big{[}-(R+r+\rho)xy_{32}^{\circ,s} +(R+\rho-r)xy_{23}^{\circ,s}\\
+%&+(R+r-\rho) xy_{41}^{\circ,s}+(R+\rho-r)xy_{14}^{\circ,s}\big{]} \alpha^\circ/2
 %\end{split}
@@
 %\begin{split}
-%x_{4}^{{\Hermaphrodite}'}=&xx_{44}^{\Hermaphrodite,s}+xx_{34}^{\Hermaphrodite,s}/2+(xx_{14}^{\Hermaphrodite,s}+xx_{24}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-%&-R(xx_{14}^{\Hermaphrodite,s}-xx_{23}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-%&(xy_{44}^{\Hermaphrodite,s}+xy_{42}^{\Hermaphrodite,s})/2+(xy_{41}^{\Hermaphrodite,s}+xy_{43}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite)\\
-%&- r(xy_{43}^{\Hermaphrodite,s}-xy_{34}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite) - \rho(xy_{42}^{\Hermaphrodite,s}-xy_{24}^{\Hermaphrodite,s})/2\\
-%&+\big{[}-(R+r+\rho)xy_{41}^{\Hermaphrodite,s}+(R+\rho-r)xy_{14}^{\Hermaphrodite,s}\\
-%&+(R+r-\rho) xy_{32}^{\Hermaphrodite,s}+(R+\rho-r)xy_{23}^{\Hermaphrodite,s}\big{]}(1-\alpha^\Hermaphrodite)/2
+%x_{4}^{{\circ}'}=&xx_{44}^{\circ,s}+xx_{34}^{\circ,s}/2+(xx_{14}^{\circ,s}+xx_{24}^{\circ,s})\alpha^\circ\\
+%&-R(xx_{14}^{\circ,s}-xx_{23}^{\circ,s}) \alpha^\circ\\
+%&(xy_{44}^{\circ,s}+xy_{42}^{\circ,s})/2+(xy_{41}^{\circ,s}+xy_{43}^{\circ,s})(1-\alpha^\circ)\\
+%&- r(xy_{43}^{\circ,s}-xy_{34}^{\circ,s})(1-\alpha^\circ) - \rho(xy_{42}^{\circ,s}-xy_{24}^{\circ,s})/2\\
+%&+\big{[}-(R+r+\rho)xy_{41}^{\circ,s}+(R+\rho-r)xy_{14}^{\circ,s}\\
+%&+(R+r-\rho) xy_{32}^{\circ,s}+(R+\rho-r)xy_{23}^{\circ,s}\big{]}(1-\alpha^\circ)/2
 %\end{split}
@@
 %\begin{split}
-%y_{1}^{{\Hermaphrodite}'}=&yy_{11}^{\Hermaphrodite,s}+yy_{13}^{\Hermaphrodite,s}/2+(yy_{12}^{\Hermaphrodite,s}+yy_{14}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-%&-R(yy_{14}^{\Hermaphrodite,s}-yy_{23}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-%&(xy_{11}^{\Hermaphrodite,s}+xy_{31}^{\Hermaphrodite,s})/2+(xy_{21}^{\Hermaphrodite,s}+xy_{41}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-%&- r(xy_{21}^{\Hermaphrodite,s}-xy_{12}^{\Hermaphrodite,s})\alpha^\Hermaphrodite - \rho(xy_{31}^{\Hermaphrodite,s}-xy_{13}^{\Hermaphrodite,s})/2\\
-%&+\big{[} - (R+r+\rho)xy_{41}^{\Hermaphrodite,s} + (R+\rho-r)xy_{14}^{\Hermaphrodite,s}\\
-%& + (R+r-\rho)xy_{32}^{\Hermaphrodite,s} + (R+\rho-r) xy_{23}^{\Hermaphrodite,s}\big{]}\alpha^\Hermaphrodite/2
+%y_{1}^{{\circ}'}=&yy_{11}^{\circ,s}+yy_{13}^{\circ,s}/2+(yy_{12}^{\circ,s}+yy_{14}^{\circ,s})\alpha^\circ\\
+%&-R(yy_{14}^{\circ,s}-yy_{23}^{\circ,s}) \alpha^\circ\\
+%&(xy_{11}^{\circ,s}+xy_{31}^{\circ,s})/2+(xy_{21}^{\circ,s}+xy_{41}^{\circ,s})\alpha^\circ\\
+%&- r(xy_{21}^{\circ,s}-xy_{12}^{\circ,s})\alpha^\circ - \rho(xy_{31}^{\circ,s}-xy_{13}^{\circ,s})/2\\
+%&+\big{[} - (R+r+\rho)xy_{41}^{\circ,s} + (R+\rho-r)xy_{14}^{\circ,s}\\
+%& + (R+r-\rho)xy_{32}^{\circ,s} + (R+\rho-r) xy_{23}^{\circ,s}\big{]}\alpha^\circ/2
 %\end{split}
@@
 %\begin{split}
-%y_{2}^{{\Hermaphrodite}'}=&yy_{22}^{\Hermaphrodite,s}+yy_{24}^{\Hermaphrodite,s}/2+(yy_{12}^{\Hermaphrodite,s}+yy_{23}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-%&-R(yy_{23}^{\Hermaphrodite,s}-yy_{14}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-%&(xy_{22}^{\Hermaphrodite,s}+xy_{42}^{\Hermaphrodite,s})/2+(xy_{12}^{\Hermaphrodite,s}+xy_{32}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite)\\
-%&- r(xy_{12}^{\Hermaphrodite,s}-xy_{21}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite) - \rho(xy_{42}^{\Hermaphrodite,s}-xy_{24}^{\Hermaphrodite,s})/2\\
-%&+\big{[}-(R+r+\rho)xy_{32}^{\Hermaphrodite,s} +(R+\rho-r) xy_{23}^{\Hermaphrodite,s}\\
-%&+(R+r-\rho)xy_{41}^{\Hermaphrodite,s}+(R+\rho-r)xy_{14}^{\Hermaphrodite,s}\big{]}(1-\alpha^\Hermaphrodite)/2
+%y_{2}^{{\circ}'}=&yy_{22}^{\circ,s}+yy_{24}^{\circ,s}/2+(yy_{12}^{\circ,s}+yy_{23}^{\circ,s})\alpha^\circ\\
+%&-R(yy_{23}^{\circ,s}-yy_{14}^{\circ,s}) \alpha^\circ\\
+%&(xy_{22}^{\circ,s}+xy_{42}^{\circ,s})/2+(xy_{12}^{\circ,s}+xy_{32}^{\circ,s})(1-\alpha^\circ)\\
+%&- r(xy_{12}^{\circ,s}-xy_{21}^{\circ,s})(1-\alpha^\circ) - \rho(xy_{42}^{\circ,s}-xy_{24}^{\circ,s})/2\\
+%&+\big{[}-(R+r+\rho)xy_{32}^{\circ,s} +(R+\rho-r) xy_{23}^{\circ,s}\\
+%&+(R+r-\rho)xy_{41}^{\circ,s}+(R+\rho-r)xy_{14}^{\circ,s}\big{]}(1-\alpha^\circ)/2
 %\end{split}
@@
 %\begin{split}
-%y_{3}^{{\Hermaphrodite}'}=&yy_{33}^{\Hermaphrodite,s}+yy_{13}^{\Hermaphrodite,s}/2+(yy_{23}^{\Hermaphrodite,s}+yy_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-%&-R(yy_{23}^{\Hermaphrodite,s}-yy_{14}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-%&(xy_{33}^{\Hermaphrodite,s}+xy_{13}^{\Hermaphrodite,s})/2+(xy_{23}^{\Hermaphrodite,s}+xy_{43}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-%&- r(xy_{43}^{\Hermaphrodite,s}-xy_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite - \rho(xy_{13}^{\Hermaphrodite,s}-xy_{31}^{\Hermaphrodite,s})/2\\
-%&+\big{[}-(R+r+\rho)xy_{23}^{\Hermaphrodite,s} +(R+\rho-r)xy_{32}^{\Hermaphrodite,s}\\
-%&+(R+r-\rho) xy_{14}^{\Hermaphrodite,s} + (R+\rho-r) xy_{41}^{\Hermaphrodite,s}\big{]}\alpha^\Hermaphrodite/2
+%y_{3}^{{\circ}'}=&yy_{33}^{\circ,s}+yy_{13}^{\circ,s}/2+(yy_{23}^{\circ,s}+yy_{34}^{\circ,s})\alpha^\circ\\
+%&-R(yy_{23}^{\circ,s}-yy_{14}^{\circ,s}) \alpha^\circ\\
+%&(xy_{33}^{\circ,s}+xy_{13}^{\circ,s})/2+(xy_{23}^{\circ,s}+xy_{43}^{\circ,s})\alpha^\circ\\
+%&- r(xy_{43}^{\circ,s}-xy_{34}^{\circ,s})\alpha^\circ - \rho(xy_{13}^{\circ,s}-xy_{31}^{\circ,s})/2\\
+%&+\big{[}-(R+r+\rho)xy_{23}^{\circ,s} +(R+\rho-r)xy_{32}^{\circ,s}\\
+%&+(R+r-\rho) xy_{14}^{\circ,s} + (R+\rho-r) xy_{41}^{\circ,s}\big{]}\alpha^\circ/2
 %\end{split}
@@
 %\begin{split}
-%y_{4}^{{\Hermaphrodite}'}=&yy_{44}^{\Hermaphrodite,s}+yy_{34}^{\Hermaphrodite,s}/2+(yy_{14}^{\Hermaphrodite,s}+yy_{24}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-%&-R(yy_{14}^{\Hermaphrodite,s}-yy_{23}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-%&(xy_{44}^{\Hermaphrodite,s}+xy_{24}^{\Hermaphrodite,s})/2+(xy_{14}^{\Hermaphrodite,s}+xy_{34}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite)\\
-%&- r(xy_{34}^{\Hermaphrodite,s}-xy_{43}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite) - \rho(xy_{24}^{\Hermaphrodite,s}-xy_{42}^{\Hermaphrodite,s})/2\\
-%&+\big{[}-(R+r+\rho) xy_{14}^{\Hermaphrodite,s} + (R+\rho-r)xy_{41}^{\Hermaphrodite,s}\\
-%&+(R+r-\rho) xy_{23}^{\Hermaphrodite,s} + (R+\rho-r) xy_{32}^{\Hermaphrodite,s}\big{]}(1-\alpha^\Hermaphrodite)/2.
+%y_{4}^{{\circ}'}=&yy_{44}^{\circ,s}+yy_{34}^{\circ,s}/2+(yy_{14}^{\circ,s}+yy_{24}^{\circ,s})\alpha^\circ\\
+%&-R(yy_{14}^{\circ,s}-yy_{23}^{\circ,s}) \alpha^\circ\\
+%&(xy_{44}^{\circ,s}+xy_{24}^{\circ,s})/2+(xy_{14}^{\circ,s}+xy_{34}^{\circ,s})(1-\alpha^\circ)\\
+%&- r(xy_{34}^{\circ,s}-xy_{43}^{\circ,s})(1-\alpha^\circ) - \rho(xy_{24}^{\circ,s}-xy_{42}^{\circ,s})/2\\
+%&+\big{[}-(R+r+\rho) xy_{14}^{\circ,s} + (R+\rho-r)xy_{41}^{\circ,s}\\
+%&+(R+r-\rho) xy_{23}^{\circ,s} + (R+\rho-r) xy_{32}^{\circ,s}\big{]}(1-\alpha^\circ)/2.
 %\end{split}
@@
 %However, not all diploid types are produced under certain sex-determining systems. 
-%For example, with the $M$ allele fixed and an ancestral XY sex-determining system, there are XX females and XY males ($x_{3}^\Hermaphrodite=x_{4}^\Hermaphrodite=y_{3}^\male=y_{4}^\male=y_{i}^\female=0,\;\forall\; i$).
+%For example, with the $M$ allele fixed and an ancestral XY sex-determining system, there are XX females and XY males ($x_{3}^\circ=x_{4}^\circ=y_{3}^\male=y_{4}^\male=y_{i}^\female=0,\;\forall\; i$).
 %%($xx_{11}^{\male}=xx_{12}^{\male}=xx_{22}^\male=xy_{11}^{\female}=xy_{12}^{\female}=xy_{21}^{\female}=xy_{22}^\female=yy_{11}^{\female}=yy_{12}^{\female}=yy_{22}^\female=0$). 
@@
 %Since equilibria $(A)$ and $(B)$ are equivalent to equilibria $(A')$ and $(B')$ with the labelling of $A$ and $a$ alleles interchanged, we discuss only equilibria $(A)$ and $(B)$, in which the Y background is fixed for the $a$ allele.
-%If there is no haploid selection ($\alpha^{\Hermaphrodite}_\Delta=0$, $w_{A}^{\Hermaphrodite}=w_{a}^{\Hermaphrodite}=1$), these equilibria are equivalent to those found by~\cite{Lloyd1977} and~\cite{Otto2014}.
+%If there is no haploid selection ($\alpha^{\circ}_\Delta=0$, $w_{A}^{\circ}=w_{a}^{\circ}=1$), these equilibria are equivalent to those found by~\cite{Lloyd1977} and~\cite{Otto2014}.
 %
@@
 %
-%Here, we assume that selection is weak relative to recombination ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon$). 
+%Here, we assume that selection is weak relative to recombination ($s^\circ$, $t^\circ$, $\alpha_{\Delta}^\circ$ of order $\epsilon$). 
 %The maintenance of a polymorphism at the $\mathbf{A}$ locus then requires that
@@
 %\noindent
-%where $V_{A}=\bar{p}(1-\bar{p})$ is the variance in the frequency of $A$ and $D^\Hermaphrodite=\big{[} \bar{p}s^\Hermaphrodite+(1-\bar{p})h^\Hermaphrodite s^\Hermaphrodite\big{]} -\big{[} \bar{p}h^\Hermaphrodite s^\Hermaphrodite+(1-\bar{p}) \big{]}$ corresponds to the difference in fitness between $A$ and $a$ alleles in diploids of sex $\Hermaphrodite \in \{\female,\male\}$.
+%where $V_{A}=\bar{p}(1-\bar{p})$ is the variance in the frequency of $A$ and $D^\circ=\big{[} \bar{p}s^\circ+(1-\bar{p})h^\circ s^\circ\big{]} -\big{[} \bar{p}h^\circ s^\circ+(1-\bar{p}) \big{]}$ corresponds to the difference in fitness between $A$ and $a$ alleles in diploids of sex $\circ \in \{\female,\male\}$.
 %The frequency of Y-bearing male gametes depends upon the difference in the frequency of the $A$ allele between X- and Y-bearing male gametes and the strength of meiotic drive in favour of the $A$ allele in males, $q=1/2+\alpha_{\Delta}^\male(\hat{p}^\male_Y-\hat{p}^\male_X)/2+O(\epsilon^3)$.
-%Without gametic competition or drive ($\alpha_{\Delta}^\Hermaphrodite=t^\Hermaphrodite=0$) our results reduce to those of~\cite{vanDoorn:2007eu}.
+%Without gametic competition or drive ($\alpha_{\Delta}^\circ=t^\circ=0$) our results reduce to those of~\cite{vanDoorn:2007eu}.
 
@@
 %Second, even when diploid selection could itself maintain a polymorphism, haploid selection can increase the conditions under which transitions among sex-determining systems are possible.
-%Of particularly importance, when selection is sexually-antagonistic in diploids ($s^\female s^\male <0$ and $0<h^\Hermaphrodite<1$), an unlinked neo-W ($R=1/2$) cannot invade unless there is also haploid selection (see proof in \nameref{file:Mathematica}; Fig \ref{fig:SexAntagTighter} and \nameref{fig:SexAntagTighterMaleDrive}).
+%Of particularly importance, when selection is sexually-antagonistic in diploids ($s^\female s^\male <0$ and $0<h^\circ<1$), an unlinked neo-W ($R=1/2$) cannot invade unless there is also haploid selection (see proof in \nameref{file:Mathematica}; Fig \ref{fig:SexAntagTighter} and \nameref{fig:SexAntagTighterMaleDrive}).
 %More generally, haploid selection alters the conditions under which neo-W alleles can spread (compare \nameref{fig:regionMaleDrive}-\nameref{fig:regionFemaleGS} to Fig \ref{fig:regionplots}). 

### 2018-03-25 LaTeX/response.tex
reviewer 1 comments thought about, going for a walk

\documentclass[10pt,letterpaper]{article}
\usepackage[top=0.85in,left=0.75in,right=0.75in,footskip=0.75in]{geometry}
\usepackage[utf8x]{inputenc}
\usepackage{amsmath,amssymb}
\bibliographystyle{plos2015}
\usepackage{color}

\begin{document}

\noindent\textbf{Color code}:\\
reviewers' words\\
\textcolor{red}{to do/thoughts/questions between coauthors (temporary)}\\
\textcolor{blue}{authors' response}

\section{Reviewer 1}

The turnover within a species from one genetic means of sex determination to another is surprisingly common, and it poses a challenging puzzle for evolutionary geneticists.  Existing theory on the topic suggests that there must be either sexually-antagonistic selection or selection variants that bring the sex ratio closer to 1:1.  This paper builds explicit models of the situation and asks about the role of selection in the haploid stage (i.e. meiotic drive and gametic selection), and finds that such effects can also serve as the primary driver of turnover of sex determining mechanisms.  While this is a rather focused topic, it is a striking evolutionary puzzle, and the paper presents a very satisfying solution that is much more general than we had previously thought.  It also overturns the primacy of Fisherian sex ratio evolution as the driver of the dynamics of genes of this sort.

The authors devise a satisfyingly simple genetic scenario, with one ancestral sex-determining locus, one locus under selection, and a third locus for the nascent sex determining locus.  They manage to collapse some messy algebra into terms like the ``haplotypic growth rate" that allow the reader to intuit many of the results.  I only have a few suggestions:

\noindent\subsection{}
The selected locus allows for three modes of selection: gametic selection (weighting the frequencies of gamete genotypes), the usual diploid viability selection, and meiotic drive (where heterozygotes may produce gametes that deviate from 50:50 proportions).  It should be noted that the model does not accommodate fertility or sexual selection.

\noindent\paragraph{Response}
\textcolor{red}{One could interpret our diploid selection as fertility selection, or does the reviewer mean that we have only one selective event in the diploid phase? Sexual selection does seem like a different model though, with for example, male fitnesses depending on female frequencies. A note such as "We do not consider fertility or sexual selection." in the paragraph beginning near L111.}

\noindent\subsection{}
The ``haplotypic growth rate" plays a really essential role in providing intuition about the results. Similarly the $\chi_{mi}^{(XY)}$ terms also are crucial.  I suggest giving a short name for the chi terms (currently they are the ``rate at which mutant haplotypes on background i recombine onto the other A locus background in heterozygotes"...).   The importance of these becomes clear in Table 2, but I wonder if there is a graphical way to make their meaning even clearer.

\noindent\paragraph{Response}
\textcolor{red}{We could call it the ``haplotypic recombination rate" near L153, but I'm not sure how much we will use this term in the text.}

\noindent\subsection{}
It needs to be stated somewhere that the models are entirely deterministic, implying that the authors assume that the selective forces always exceed the force of random drift. It might be useful to discuss this a bit. Is there evidence that in no case has drift been a key factor in changes of sex determination system?  The discussion mentions alleles of weaker effect, but does not mention that in this scenario, models of weak effects would need to consider drift as well.

\noindent\paragraph{Response}
\textcolor{red}{We could first mention that the model is deterministic, and hence ignores drift, near L131. As for the role of drift in transitions, we could certainly elaborate on the Veller et al 2017 Genetics paper that discusses how ``drift-induced selection" causes trans-GSD transitions. I've put a possible sentence in near L482: ``It should be noted, however, that the dynamics of sex-determining alleles with very weak effect will be influenced by genetic drift, which itself has been shown to cause trans-GSD transitions (Veller et al 2017)."}

\noindent\subsection{}
A glitch appears in the section ``Loose linkage with the ancestral sex-determining region" on line 270, where the text reads, ``To leading order in selection, the leading eigenvalues are..."

\noindent\paragraph{Response}
\textcolor{red}{Perhaps we could just drop the words ``the leading eigenvalues are" (which I have done)?}

\noindent\subsection{}
Gametic selection among sperm is a bit different from sperm competition, since the latter involves pair-wise (or multi-way) bouts, whereas gametic selection assigns constant fitnesses to each haplotype. I would replace occurrences of ``sperm competition" with ``male gametic selection", or maybe ``sperm gametic competition". To be consistent, replace ``egg competition" with ``female/egg gametic competition".

\noindent\paragraph{Response}
\textcolor{blue}{We have made the suggested replacements. There are two exceptions. In the abstract we use sperm competition as an example of gametic competition, but we now state that this would involve multiple males. In the introduction we mention that sperm competition has been shown to alter allele frequencies and fitness, and in this case we now mention this was shown within a single ejaculate (L68).}

\noindent\subsection{}
I am not certain of this, but it seems that a potentially important difference between ESD and GSD has to do with the variance in proportion male? Since ESD (in a constant environment, as is implicitly modeled here) has a binomial sampling of sexes, but GSD might deviate from this.  This might be an issue because Fisherian sex ratio selection acts on the mean and not the variance.

\noindent\paragraph{Response}
\textcolor{red}{I think that, with our deterministic model (where the number of binomial trials is infinite), the variance in the fraction male is 0, and so is the same as GSD. We could briefly mention this at the beginning or end of the ESD section, and say that modeling ESD in a finite population could be interesting?}

\noindent\subsection{}
Full sharing of the Mathematica file is to be commended.

\section{Reviewer 2}

Scott et al. present a 3-locus model for sex-determination (SD) evolution (1 locus has an ancestral SD function; 1 has a derived SD function; 1 locus affects selection in the haploid or diploid phase of the life cycle). Their results converge on previously-identified conditions for the spread of new SD alleles, while also broadening the range of scenarios and conditions that can favour transitions between SD systems.

The paper is interesting and conceptually appropriate for PLoS Biology. The authors have done a great job of analysing a somewhat complicated model and drawing out a relatively complete picture of the conditions favouring the evolution of new sex determination systems, and I expect their expert treatment will go over well with people that are close to the research context of the new theory.

On the other hand, I am much less sure that this paper will reach beyond experts in this subject area, though the authors should seek to broaden the appeal. This is not because the results are narrow -- I think they can have a broad appeal. Rather, the paper is written in a technical manner that is likely to limit the appeal beyond the expert class. I am reasonably comfortable with models like this, but still found the presentation to be very hard going in a variety of places, particularly in the results. I offer some suggestions for presentation that may help improve the presentation and broaden the potential appeal of the paper.

\noindent\subsection{}
I think the introduction could be simplified so that the context of the study is more obvious. The authors essentially need to make three key points, which are there, but could be better drawn out. First, transitions between sex-determining systems are common, and recent empirical work has given us a much greater appreciation for just how common these transitions are. Second, there are two major mechanisms that are thought induce evolution of new sex-determination mechanisms: (1) selection to stabilize the sex ratio, and (2) hitchhiking between (tightly linked) sex-determination and sexually antagonistic alleles. Third, the authors should clearly outline the major limitations of current theory as a means of motivating their mega-model that captures an array of genetic and selection scenarios that may lead to transitions in sex determination. As I mentioned, these elements can all be found in the introduction, but the pitch can be substantially streamlined to allow readers to easily see: (1) what is the context? (2) What do we currently think drives transitions between SD systems? And (3) what are the holes in the theory and how will the authors address them?

\noindent\paragraph{Response}
\textcolor{blue}{We now ...}

\noindent\subsection{}
Likewise, the results yield three major insights:\\
(1) SD transitions can, counterintuitively, potentially INCREASE sex ratio bias\\
(2) Tight linkage and sexual antagonism are not required for transitions to occur\\
(3) Under haploid selection, conditions for the spread of new sex-determining alleles are extremely permissive.\\
Again, all of these points are there, but they could be better drawn out than they currently are. The results, as written, are hard-going, and I expect will be particularly challenging for readers that are not heavily immersed in evolutionary theory.

One potential way to help readers ? particularly those interested in what the paper has to say, but are not mathematically inclined ? is to conspicuously highlight each important result and briefly place it into context of earlier theory. But at the same time, the authors have done a great job of drawing out general mathematical results from a relatively complicated model ? their mathematical insights ARE the results and I am not suggesting that they be minimized or shunted into appendices.

One tactic for including analytical details which specialists will want to see, while allowing less mathematically inclined readers to easily find each main result, is to place short and accessible summaries at the close of each section of the Results. Such a tactic has been put to good use in a hugely influential paper by Allen Orr (1998 Evolution), which I expect the authors will be familiar with. Orr presents the major mathematical results of his analysis alongside prominently labelled punchline paragraphs that summarize each of his main results in a concise and easily understandable manner. If the authors choose to take this approach, please be clear to place the take-home messages in context: clearly state whether the result confirms previous theory, or represents a new result or contradiction of an earlier result.

\noindent\paragraph{Response}
\textcolor{blue}{We now ...}

\subsection{MINOR COMMENTS}

\noindent\subsubsection{}
L3: "of diploid sexes" can be deleted

\noindent\paragraph{Response}
\textcolor{blue}{We now ...}

\noindent\subsubsection{}
L12: missing a ``)"

\noindent\paragraph{Response}
\textcolor{blue}{We now ...}

\noindent\subsubsection{}
L35-37: sentence could use an edit for ease of reading.

\noindent\paragraph{Response}
\textcolor{blue}{We now ...}

\noindent\subsubsection{}
Immediately preceding the paragraph beginning line 44: It would be worth establishing the limitations of previous work. What exactly motivated you to do this mathematical modelling?

\noindent\paragraph{Response}
\textcolor{blue}{We now ...}

\noindent\subsubsection{}
L56-57: Rephrase for clarity "individual cases of meiotic drive are generally sex-limited, and exclusively effect male or female gametes". And on line 57, "sex specific" could be changed to "sex-limited".

\noindent\paragraph{Response}
\textcolor{blue}{We now ...}

\noindent\subsubsection{}
Lines 80-81: This primary finding is completely aligned with the earlier views of theory that are summarized above. Are you sure you want to lead with this as the main emphasis of the study? It understates what is new.

\noindent\paragraph{Response}
\textcolor{blue}{We now ...}

\noindent\subsubsection{}
M locus is dominant to X. How important is this assumption? Is this compatible with any data (e.g., on feminizing or masculinizing factors in Musca domestica)?

\noindent\paragraph{Response}
\textcolor{blue}{We now ...}

\noindent\subsubsection{}
Paragraph beginning L104: the sex symbols are not ideal. The combined male/female symbol has been used In other contexts to refer to "male and female" rather than representing either/or

\noindent\paragraph{Response}
\textcolor{blue}{We now ...}

\noindent\subsubsection{}
Table 2: a footnote to the table would be useful in defining the terms in the equations, some of which are far less obvious than others.

\noindent\paragraph{Response}
\textcolor{blue}{We now ...}

\noindent\subsubsection{}
L169-170. This statement makes sense, but I wonder when such an initial condition would arise, since invasion criteria are evaluated at an equilibrium state? What ancestral conditions lead to the equilibrium sex-ratio bias, upon which the invasion results are based? This is touched on later, but a statement up front will help to not leave the reader hanging.

\noindent\paragraph{Response}
\textcolor{blue}{We now ...}

\noindent\subsubsection{}
L195: define the epsilon character, which has not appeared before, or specify the size of the selection parameters relative to recombination, since this is the key point of contrast (e.g., s $<<$ r).

\noindent\paragraph{Response}
\textcolor{blue}{We now ...}

\noindent\subsubsection{}
Fig. 2, panel C. You might consider using log scale on the y-axis of the inset, since the blue and green curves do not really show.

\noindent\paragraph{Response}
\textcolor{blue}{We now ...}

\noindent\subsubsection{}
Eq. (2): the use of $V_A$ is not really useful here. Much more straightforward to place the p(1 - p) in the main equation.

\noindent\paragraph{Response}
\textcolor{blue}{We now ...}

\section{Reviewer 3}

This work (henceforth [SOO]) explores the role of both diploid and haploid selection on the evolution of new sex-chromosomes and or transitions between sex-determination systems. For that purpose, the authors develop a population genetics model of three loci with two alleles in each locus. The first locus X is the ancestral sex-determining locus, the second locus A is the locus under diploid and haploid selection. The third locus M is the novel sex-determining locus.

\noindent\subsection{}
I find the article is not clearly written and could benefit from improving the presentation of the main results.

\noindent\paragraph{Response}
\textcolor{blue}{We now ...}

\noindent\subsection{}
I also find the article claims that: (a) the modeling work is novel and (b) the findings are unexpected to be only partially justified.

\noindent\paragraph{Response}
\textcolor{blue}{We hope the responses below help...}

\noindent\subsubsection{}
The works of Kozielska 2014 and Ubeda 2015 model the combined effects of both haploid and diploid selection on the evolution of new sex-chromosomes. The work of [SOO] is thus not novel in considering both haploid and diploid selection on the evolution of new sex-chromosomes. It does generalize previous work by considering sex-specific viability selection and get some nice analytical results.

\noindent\paragraph{Response}
\textcolor{blue}{We now ...}

\noindent\subsubsection{}
The findings in [SOO] claimed to be surprising (``Surprisingly, we find that neither force (sex ratio selection nor associations with genes that have sex-specific effects) dominates the spread of new sex-determining systems alone.") and unexpected (``Even more unexpectedly, we find that, to spread, new sex-determining alleles do not necessarily have to arise in closer linkage with genes that are differentially selected in males and females"), are rather similar to those in Ubeda et al 2015. This is a problem that repeats itself over the paper

\noindent\paragraph{Response}
\textcolor{blue}{We now ...}

For example in:

\noindent\subsubsection{}
Page 2. The authors claim that predominant theories of the evolution of sex sex-determining systems are two: sexually-antagonistic selection and sex-ratio selection. They ignore other two: inbreeding (Charlesworth 1978) and sex-different drive (Ubeda et al 2015).

\noindent\paragraph{Response}
\textcolor{blue}{We now ...}

\noindent\subsubsection{}
Page 3 ``Here we use mathematical models to find the conditions under which new sex-determining systems spread when individuals experience selection at both diploid and haploid stages, which allows fitness differences between the sexes and sex ratio biases to occur simultaneously"

This would be the same model as Ubeda et al 2015 adding sex-specific viability.

\noindent\paragraph{Response}
\textcolor{blue}{We now ...}

\noindent\subsubsection{}
Lines 68-69: ``If we assume that haploid selection at any particular locus predominantly occurs in one sex (e.g., meiotic drive during spermatogenesis), then such loci experience a form of sex-specific selection."

This is a stretch and creates confusion. I consider selection acting on individuals with different sex sex-specific selection, now when selection is acting on gametes (which are neither males or females) males or females are just different environments in which selection may take place. Neither the dynamics nor the constraints are the same.

\noindent\paragraph{Response}
\textcolor{blue}{We now ...}

\noindent\subsubsection{}
Lines 70-71: ``In this respect, we might expect that haploid selection would affect transitions between sex-determining systems in a similar manner to sex-specific diploid selection (as explored in [31,32])"

Following up my previous comment Ubeda 2015 explores this and shows that both forms of selection are different. For example sex-antagonistic selection is needed for the invasion of a new sex-determining gene with diploid selection while antagonistic drive in each of the sexes is not needed for the invasion of a new sex-determining gene with haploid selection.

\noindent\paragraph{Response}
\textcolor{blue}{We now ...}

\noindent\subsubsection{}
Lines 77-78: ``It is not immediately clear how the spread of new sex-determining systems would be influenced by the combination of sex ratio biases and associations with haploid selected allele"

This is indeed the focus of Ubeda et al 2015.

\noindent\paragraph{Response}
\textcolor{blue}{We now ...}
\\

I will not provide further examples, but it is surprising thatI the work of Ubeda et al 2015, which is closely related to the one presented here, is cited in page 12 supporting a statement only tangential to the work of Ubeda et al 2015.

\noindent\subsection{}
In terms of modeling the distinction between meiotic drive and gametic competition is unnecessary and only complicates notation. Furthermore, from biological perspective the division seems blurry with molecular biologists considering that meiotic drive only happens in females and never in males and what is often called meiotic drive in males is gamete competition. I would suggest using a single parameter measuring transmission distortion.

\noindent\paragraph{Response}
\textcolor{blue}{We now ...}

\end{document}

### 2018-03-25 LaTeX/main_revision.tex
reviewer 1 comments thought about, going for a walk

@@
 Variation at such loci can favour the spread of new sex-determining systems in which the heterogametic sex changes (XY to ZW or ZW to XY) and the new sex-determining region is less closely linked (or unlinked) to the locus under selection, which is not predicted by previous theory.
-(2) We also consider selection upon haploid genotypes either during gametic competition (e.g., pollen/sperm competition) or meiosis (i.e., non-Mendelian segregation), which can cause the zygotic sex ratio to become biased.
+(2) We also consider selection upon haploid genotypes either during gametic competition (e.g., pollen/sperm competition involving multiple males) or meiosis (i.e., non-Mendelian segregation), which can cause the zygotic sex ratio to become biased.
 We find that associations with haploid selected loci can drive transitions between sex-determining systems, without requiring sexually-antagonistic selection in diploids. 
@@
 A smaller proportion of genes are thought to be expressed and selected during competition in animal sperm, although precise estimates are uncertain~\cite{Zheng:2001fi,JOSEPH:2004haa,Vibranovski:2010et}.
-Nevertheless, recent studies have demonstrated that sperm competition in animals can alter haploid allele frequencies and increase offspring fitness~\cite{Immler:2014im,Alavioon2017}.
+Nevertheless, recent studies have demonstrated that sperm competition in animals, even within a single ejaculate, can alter haploid allele frequencies and increase offspring fitness~\cite{Immler:2014im,Alavioon2017}.
 
@@
 %life-cycle
+A full description of our model, including recursion equations, is given in \nameref{app:recurs}. 
 In each generation, we census the genotype frequencies in male and female gametes/gametophytes (hereafter gametes) before gametic competition. 
-A full description of our model, including recursion equations, is given in \nameref{app:recurs}. 
 First, competition occurs among male gametes (sperm/pollen competition) and among female gametes (egg/ovule competition) separately. 
@@
 %(and the $\mathbf{M}$ genotype of their mother in the case of maternal control).
-Diploid males and females then experience selection, with relative fitnesses $w_{AA}^{\circ}$, $w_{Aa}^{\circ}$, and $w_{aa}^{\circ}$.
+Diploid males and females then experience \textcolor{red}{viability(?)} selection, with relative fitnesses $w_{AA}^{\circ}$, $w_{Aa}^{\circ}$, and $w_{aa}^{\circ}$.
 %where $g$ is the diploid genotype at the $\mathbf{A}$ locus ($g \in \{AA, Aa, aa\}$).
 %Diploids compete with others of the same sex, where selection depends on the sex of the individual and its genotype at the $\mathbf{A}$ locus.
+\textcolor{red}{We do not consider fertility(?) or sexual selection.}
 The next generation of gametes is produced by meiosis, during which recombination and sex-specific meiotic drive can occur. 
@@
 Thus, the $\mathbf{A}$ locus can experience sex-specific gametic competition, diploid selection, and/or meiotic drive. 
-
+`
 \begin{table}[ht]
@@
 The leading eigenvalue for a rare neo-Y or neo-W allele, $m\in\{Y',W'\}$, is the largest value of X that solves $x^2+ b x + c = 0$.  %$(\lambda_m^{(i)})^2+ b \lambda_m^{(i)} + c =0$. 
-The coefficients are $b= - (\Lambda_{mA}^{(XY)} + \Lambda_{ma}^{(XY)})+(\chi_{mA}^{(XY)} + \chi_{ma}^{(XY)})$ and $c = (\Lambda_{mA}^{(XY)} - \chi_{mA}^{(XY)}) (\Lambda_{ma}^{(XY)} - \chi_{ma}^{(XY)}) - \chi_{mA}^{(XY)} \chi_{ma}^{(XY)}$, where $\Lambda_{mi}^{(XY)}>0$ is the multiplicative growth rate (which we will call the ``haplotypic growth rate'') of the neo-sex determination allele $m$ on background $i\in\{A,a\}$ without accounting for loss due to recombination ($R=0$), and $\chi_{mi}^{(XY)}>0$ is the rate at which mutant haplotypes on background $i\in\{A,a\}$ recombine onto the other $\mathbf{A}$ locus background in heterozygotes (proportional to $R$), see Table \ref{tab:haplotype_growth}.
+The coefficients are $b= - (\Lambda_{mA}^{(XY)} + \Lambda_{ma}^{(XY)})+(\chi_{mA}^{(XY)} + \chi_{ma}^{(XY)})$ and $c = (\Lambda_{mA}^{(XY)} - \chi_{mA}^{(XY)}) (\Lambda_{ma}^{(XY)} - \chi_{ma}^{(XY)}) - \chi_{mA}^{(XY)} \chi_{ma}^{(XY)}$, where $\Lambda_{mi}^{(XY)}>0$ is the multiplicative growth rate (which we will call the ``haplotypic growth rate'') of the neo-sex determination allele $m$ on background $i\in\{A,a\}$ without accounting for loss due to recombination ($R=0$), and $\chi_{mi}^{(XY)}>0$ is the rate at which mutant haplotypes on background $i\in\{A,a\}$ recombine onto the other $\mathbf{A}$ locus background in heterozygotes (proportional to $R$; \textcolor{red}{we call this the ``haplotypic recombination rate"(?)}), see Table \ref{tab:haplotype_growth}.
 In the ancestral population, it is convenient to follow the frequency of the $A$ allele among female gametes (eggs), $p^\female_X$, and among X-bearing, $p^\male_X$, and among Y-bearing, $p^\male_Y$, male gametes (sperm/pollen).
@@
 %, we denote the leading eigenvalues describing the invasion of a neo-Y ($k=0$) and a neo-W ($k=1$) into an ancestrally XY system by $\lambda_{Y',XY}$ and $\lambda_{W',XY}$, respectively. 
-To leading order in selection, the leading eigenvalues are:
+To leading order in selection,
 
 \begin{equation}
-\lambda_{Y'}^{(XY)} =1+ \frac{1}{4}V_{A}S_{A}^2\frac{ \left( r-R \right) }{r R}+O\left(\epsilon^3 \right) 
+\lambda_{Y'}^{(XY)} = 1 + \frac{1}{4}V_{A}S_{A}^2\frac{ \left( r-R \right) }{r R}+O\left(\epsilon^3 \right) 
 \label{eq:lambda_neoY}
@@
  female drive only & $h^\male=h^\female$, $t^\female=t^\male=\alpha^\male_{\Delta}=0$ & $s^\female s^\male>0$ \\ [0.5ex]
- sperm competition only &  $h^\male=h^\female$, $t^\female=\alpha^\female_{\Delta}=\alpha^\male_{\Delta}=0$ & $s^\female(s^\male-s^\female)>0$ \\ [0.5ex]
-  egg competition only & $h^\male=h^\female$, $t^\male=\alpha^\female_{\Delta}=\alpha^\male_{\Delta}=0$ & $s^\male(s^\female-s^\male)>0$ \\ [0.5ex]
+ male gametic competition only &  $h^\male=h^\female$, $t^\female=\alpha^\female_{\Delta}=\alpha^\male_{\Delta}=0$ & $s^\female(s^\male-s^\female)>0$ \\ [0.5ex]
+  female gametic competition only & $h^\male=h^\female$, $t^\male=\alpha^\female_{\Delta}=\alpha^\male_{\Delta}=0$ & $s^\male(s^\female-s^\male)>0$ \\ [0.5ex]
   \hline \hline
@@
 These results echo those for large-effect neo-Y/neo-W alleles~\cite{vanDoorn:2007eu,vanDoorn:2010hu}.
+\textcolor{red}{It should be noted, however, that the dynamics of sex-determining alleles with very weak effect will be influenced by genetic drift, which itself has been shown to cause trans-GSD transitions \cite{Veller2017}}.
 Finally, while we have considered cis-GSD, trans-GSD, and GSD to ESD transitions, we have not explicitly considered ESD to GSD transitions. 

### 2018-03-26 LaTeX/response.tex
review 2 major comments thought about, going to a show

@@
 \textcolor{blue}{authors' response}
+\\
+
+\noindent  Line numbers (L\#) in authors' comments refer to those in the revised PDF.
 
@@
 \noindent\paragraph{Response}
-\textcolor{blue}{We now ...}
+\textcolor{blue}{The introduction is now arranged as follows.
+The first paragraph discusses how common transitions are.
+The second and third paragraphs discuss the two major mechanisms currently hypothesized to drive the observed transitions, respectively.
+The fourth paragraph introduces haploid selection and the fifth talks about its potential implications for transitions, motivating our model.
+The final, sixth, paragraph briefly mentions our main findings.}
 
@@
 
-One potential way to help readers ?
-particularly those interested in what the paper has to say, but are not mathematically inclined ?
-is to conspicuously highlight each important result and briefly place it into context of earlier theory.
-But at the same time, the authors have done a great job of drawing out general mathematical results from a relatively complicated model ?
-their mathematical insights ARE the results and I am not suggesting that they be minimized or shunted into appendices.
+One potential way to help readers -- particularly those interested in what the paper has to say, but are not mathematically inclined -- is to conspicuously highlight each important result and briefly place it into context of earlier theory.
+But at the same time, the authors have done a great job of drawing out general mathematical results from a relatively complicated model -- their mathematical insights ARE the results and I am not suggesting that they be minimized or shunted into appendices.
 
@@
 \noindent\paragraph{Response}
-\textcolor{blue}{We now ...}
+\textcolor{red}{We now highlight 5 conclusions in the style of Orr 1998...}
 
@@
 \noindent\paragraph{Response}
-\textcolor{blue}{We now ...}
+\textcolor{blue}{Deleted.}
 
@@
 \noindent\paragraph{Response}
-\textcolor{blue}{We now ...}
+\textcolor{blue}{Fixed.}
 

### 2018-03-26 LaTeX/main_revision.tex
review 2 major comments thought about, going to a show

@@
 
+%TRANSITIONS ARE COMMON
 Animals and angiosperms exhibit extremely diverse sex-determining systems (reviewed in~\cite{Bull:1983vi,Charlesworth:2010it,Beukeboom:2014vb,Bachtrog:2014bx}). 
-Among species with genetic sex determination (GSD) of diploid sexes, some taxa have heterogametic males (XY) and homogametic females (XX), including %non-monotreme?
+Among species with genetic sex determination (GSD), some taxa have heterogametic males (XY) and homogametic females (XX), including %non-monotreme?
 I think monotremes have XY but tonnes of translocations, giving: X1,X2...X6 Y1
@@
 I wonder if this is actually a fusion event though?
-In addition, many clades exhibit transitions between male and female heterogamety (XY$\leftrightarrow$ZW, hereafter `trans-GSD transitions'), including snakes~\cite{Gamble2017}, lizards~\cite{Ezaz:2009tk}, eight of 26 teleost fish families~\cite{Mank:2006bt}, true fruit flies (Tephritids,~\cite{Vicoso:2015hf}, amphibians~\cite{Hillis:1990gu}, the angiosperm genus \textit{Silene}~\cite{Slancarova:2013dq}, the angiosperm family \textit{Salicaceae}~\cite{Pucholt2015,Pucholt2017} and Coleoptera and Hemiptera (plate 2~\cite{Beukeboom:2014vb}).
+In addition, many clades exhibit transitions between male and female heterogamety (XY$\leftrightarrow$ZW, hereafter `trans-GSD transitions'), including snakes~\cite{Gamble2017}, lizards~\cite{Ezaz:2009tk}, eight of 26 teleost fish families~\cite{Mank:2006bt}, true fruit flies (Tephritids,~\cite{Vicoso:2015hf}), amphibians~\cite{Hillis:1990gu}, the angiosperm genus \textit{Silene}~\cite{Slancarova:2013dq}, the angiosperm family \textit{Salicaceae}~\cite{Pucholt2015,Pucholt2017} and Coleoptera and Hemiptera (plate 2~\cite{Beukeboom:2014vb}).
 Indeed, in some cases, both male and female heterogametic sex-determining systems can be found in the same species, as reported in houseflies~\cite{Macdonald1978}, midges~\cite{Thompson1971}, frogs~\cite{Ogata:2007jm}, cichlid fish~\cite{Ser:2010iq}, tilapia~\cite{Lee2004}, sea bass~\cite{Vandeputte2007}, and lab-strains of Zebrafish~\cite{Liew2012,Wilson2014}.
@@
 
+%MAJOR MECHANISMS
+%(1) sex-antagonism
 Predominant theories accounting for transitions between GSD systems by selection involve fitness differences between sexes (e.g., sexually antagonistic selection) or sex ratio selection~\cite{Blaser2012, Beukeboom:2014vb,vanDoorn2014re}.
@@
 
+%MAJOR MECHANISMS
+%(2) sex-ratio selection
 The sex ratio is directly determined by the sex-determining system, and it has therefore been suggested that sex ratio selection is a dominant force in the evolution of sex determination (e.g., Bull, 1983, p 66-67 ~\cite{Bull:1983vi}; Buekeboom and Perrin, 2014, Chapter 7~\cite{Beukeboom:2014vb}).
@@
 %Given that the sex-determining system can directly affect the sex ratio, we might expect Fisherian sex ratio selection to influence the spread of new sex-determining systems. 
-In the case of sex-chromosome evolution, Kozielska et al.
+%In the case of sex-chromosome evolution, Kozielska et al.
 (2010)~\cite{Kozielska:2010vm} consider systems in which the ancestral sex chromosomes experience meiotic drive (e.g., where driving X or Y chromosomes are inherited disproportionately often), which causes sex ratios to become biased~\cite{Hamilton:1967ts}.
-They find that masculinizing or feminizing mutations that arise at a new, unlinked locus (i.e., neo-Y or neo-W chromosomes) can then spread, which restore an even sex ratio. 
-However, starting from ESD, Ubeda et al.
+%They find that masculinizing or feminizing mutations that arise at a new, unlinked locus (i.e., neo-Y or neo-W chromosomes) can then spread, which restore an even sex ratio. 
+%However, starting from ESD, Ubeda et al.
 (2015)~\cite{Ubeda:2015fx} have numerically shown that sex-specific meiotic drive can allow masculinizing and feminizing mutations to spread (i.e., ESD $\rightarrow$ GSD) despite causing a sex-ratio bias.
 
-Here we use mathematical models to clarify the conditions under which new sex-determining systems spread when individuals experience selection at both diploid and haploid stages, which allows fitness differences between the sexes and sex-ratio biases to occur simultaneously.
+%HOLES IN CURRENT THEORY
+%(1) haploid selection; it exists in many spp
+While both opposing selection in the diploid sexes and sex-ratio selection surely influence the evolution of new sex-determining factors, so too might selection in the haploid phase.
 Even in animal and plant species that have much larger and more conspicuous diploid phases than haploid phases, many loci experience significant haploid selection through gamete competition and/or meiotic drive~\cite{Mulcahy:1996ha,JOSEPH:2004haa}.
 We use the term `meiotic drive' to refer to the biased (non-Mendelian) segregation of genotypes during gamete production (from one parent only) and the term `gametic competition' to refer to selection upon haploid genotypes within a gamete/gametophyte pool (from many parents); the term `haploid selection' encompasses both processes.
-
 Segregation distortion provides putative evidence of haploid selection and can sometimes be attributed to meiotic drive and/or gametic competition~\cite{Lalanne2004,Fishman2005,Leppala2008,Leppala2013,Didion2015,Didion2016}.
@@
 
-There are various ways by which genes experiencing haploid selection could influence transitions between sex-determining systems. 
+%HOLES IN CURRENT THEORY
+%(2) haploid selection; it can complicate outcomes for SD transitions
+There are various ways by which haploid selection could influence transitions between sex-determining systems. 
 If we assume that haploid selection at any particular locus predominantly occurs in one sex (e.g., meiotic drive during spermatogenesis), then such loci experience a form of sex-specific selection. 
@@
 That is, new masculinizing mutations (neo-Y alleles) could be favoured via associations with alleles that are beneficial in the male haploid stage (e.g., \cite{Ubeda:2015fx}). 
-On the other hand, sex ratios can also become biased by linkage between the sex-determining locus and a locus that harbours genetic variation in haploid fitness.
-For example, there are several known cases of sex-ratio bias caused by sex-linked meiotic drive alleles (Burt and Trivers, 2006, Chapter 6~\cite{Burt:2006}) or selection among X- and Y-bearing pollen~\cite{Lloyd:1974tz,Conn:1981uw,Stehlik:2005ul,Stehlik:2006to,Field:2012fd,Field:2013cc}.
-Sex-ratio selection can thus select against the spread of linked sex-determining alleles and favour the invasion of alternative, unlinked sex-determination systems \cite{Kozielska:2010vm}.
+Kozielska et al.
+(2010)~\cite{Kozielska:2010vm} have shown this to be theoretically possible for the special case of perfect linkage between the new sex-determining locus and a locus that experiences meiotic drive in one sex, under a limited number of forms of diploid selection.
+Similarly, Ubeda et al.
+(2015)~\cite{Ubeda:2015fx} numerically show that sex-specific meiotic drive can allow masculinizing and feminizing mutations to spread in an ancestrally environmental-sex-determination system, again under a limited number of forms of diploid selection.
+On the other hand, sex ratios can also become biased by linkage between the sex-determining locus and a locus that harbours genetic variation in haploid fitness, as indeed occurs in the two examples above.
+There are also several known empirical cases of sex-ratio bias caused by sex-linked meiotic drive alleles (Burt and Trivers, 2006, Chapter 6~\cite{Burt:2006}) or selection among X- and Y-bearing pollen~\cite{Lloyd:1974tz,Conn:1981uw,Stehlik:2005ul,Stehlik:2006to,Field:2012fd,Field:2013cc}.
+Sex-ratio selection can thus select against the spread of linked sex-determining alleles and favour the invasion of alternative, unlinked sex-determination systems \cite{Kozielska:2010vm,Ubeda:2015fx}.
 %It is not immediately clear how the spread of new sex-determining systems would be influenced by the combination of sex ratio biases and associations with haploid selected alleles. 
@@
 sex-ratio bias, especially under a wide range of possible diploid selection regimes (e.g., sex-antagonism, overdominance).
-
+Here we use mathematical models to clarify the conditions under which new sex-determining systems spread when individuals experience extremely general and potentially sex-specific selection at both diploid and haploid stages, which allows fitness differences between the sexes and sex-ratio biases to occur simultaneously.
+
+%MAIN FINDINGS IN GENERAL TERMS
 We find that the spread of novel sex-determining systems is influenced by both Fisherian sex-ratio selection and by selection on linked alleles. 
@@
 
-We draw three main conclusions about the generic invasion of neo-Y and neo-W mutations from Table \ref{tab:haplotype_growth}:
+We draw three main points about the generic invasion of neo-Y and neo-W mutations from Table \ref{tab:haplotype_growth}.
+First, invasion by a neo-Y (neo-W) does not directly depend on the fitness of female (male) diploids. %(for a given set of equilibrium allele frequencies).
+This is because a dominant neo-Y (neo-W) is always found in males (females), and therefore the frequency of the neo-Y (neo-W), $m$, only changes in males (females), Fig \ref{fig:model_outline}C,D.
+Second, Fisherian sex-ratio selection will favour the spread of a neo-Y and inhibit the spread of a neo-W if the ancestral zygotic sex ratio is biased towards females (i.e., the first factor of the $\Lambda_{mi}^{(XY)}$ is greater than one for a neo-Y and less than one for a neo-W when $\zeta<1/2$).
+However, the spread of a neo-Y (neo-W) also depends on the male (female) fitness of associated alleles (see terms involving equilibrium allele frequencies, $\hat{p}$'s). That is, 
 \vspace{0.5cm}
 
-\noindent\textit{Conclusion 1: Fisherian sex-ratio selection will favour the spread of a neo-Y and inhibit the spread of a neo-W if the ancestral zygotic sex ratio is biased towards females}, $\zeta<1/2$ (i.e., the first factor of the $\Lambda_{mi}^{(XY)}$ is greater than one for a neo-Y and less than one for a neo-W).
-However, the spread of a neo-Y (neo-W) also depends on the male (female) fitness of associated alleles (see terms involving equilibrium allele frequencies, $\hat{p}$'s).
+\noindent\textit{Conclusion 1:} 
+\textit{neither sex-ratio selection or selection on associated alleles dominates the invasion dynamics of a new sex-determining allele, allowing the sex ratio to become more or less biased during a transition.}
+\textcolor{red}{[as suspected from Kozielska and Ubeda special cases]}
 \vspace{0.5cm}
 
-\noindent\textit{Conclusion 2: invasion by a neo-Y (neo-W) does not directly depend on the fitness of female (male) diploids}. %(for a given set of equilibrium allele frequencies).
-This is because a dominant neo-Y (neo-W) is always found in males (females), and therefore the frequency of the neo-Y (neo-W), $m$, only changes in males (females), Fig \ref{fig:model_outline}C,D. 
+\noindent And thirdly, Table \ref{tab:haplotype_growth} also shows that
 \vspace{0.5cm}
 
-\noindent\textit{Conclusion 3: invasions by a neo-Y and a neo-W are qualitatively different}.
-This is because a gamete with the neo-Y always pairs with a female gamete containing an X, Fig \ref{fig:model_outline}C.
+\noindent\textit{Conclusion 2: cis- and trans-GSD transitions are qualitatively different.}
+\textcolor{red}{[already known from van Doorn and Kirkpatrick?]}
+\vspace{0.5cm}
+
+\noindent This is because, in an ancestrally XY system, a gamete with the neo-Y always pairs with a female gamete containing an X, Fig \ref{fig:model_outline}C.
 By contrast, a gamete with a neo-W can pair with an X- or Y-bearing male gamete, Fig \ref{fig:model_outline}D.
-Consequently, neo-W-bearing females obtain a different frequency of $A$ alleles from mating (when $\hat{p}_X^\male \neq \hat{p}_Y^\male$) compared to ancestral ($MM$) females.
-\vspace{0.5cm}
+Consequently, neo-W-bearing females obtain a different frequency of $A$ alleles from mating (when $\hat{p}_X^\male \neq \hat{p}_Y^\male$) compared to ancestral ($MM$) females, which can inhibit or favour its spread.
 
@@
 
-Neo-W alleles, on the other hand, can invade an ancestral XY system under some conditions (the full invasion conditions are given in \nameref{app:inv_cond}; equations \ref{Binvasion} and \ref{Ainvasion}):
+Neo-W alleles, on the other hand, can invade an ancestral XY system under some conditions (the full invasion conditions are given in \nameref{app:inv_cond}; equations \ref{Binvasion} and \ref{Ainvasion}).
+In particular,
 \vspace{0.5cm}
 
-\noindent\textit{Conclusion 4: counterintuitively, selection on loci within the non-recombining region around the sex-determining locus ($r\approx0$) can favour the invasion of a less closely linked neo-W ($r<R$)}, whatever the form of selection maintaining a polymorphism (sexually-antagonistic selection, overdominance, ploidally-antagonistic selection, or some combination, Fig \ref{fig:SexAntagTighter}, \nameref{fig:temporalOverdominance}, \nameref{fig:regionPloidAntag}, and \nameref{fig:SexAntagTighterMaleDrive}).
+\noindent\textit{Conclusion 3: selection on loci within the non-recombining region around the sex-determining locus ($r\approx0$) allows the invasion of less closely linked sex-determining alleles ($r<R\leq1/2$) during a trans-GSD transition}.
+\textcolor{red}{[new result for sex-antagonism and overdominance, but already shown by Kozielska for ploidy-antagonism]}
+\vspace{0.5cm}
+
+\noindent This does not depend on the form of selection maintaining a polymorphism (sexually-antagonistic selection, overdominance, ploidally-antagonistic selection, or some combination, Fig \ref{fig:SexAntagTighter}, \nameref{fig:temporalOverdominance}, \nameref{fig:regionPloidAntag}, and \nameref{fig:SexAntagTighterMaleDrive}).
 The conditions become more restrictive, however, with increasing recombination ($R$) between the new sex-determining locus and the selected locus.  
@@
 An equivalent analysis is not possible where recombination rates are low. 
-However, numerical simulations demonstrate that new sex-determining alleles do not necessarily reach pseudo-fixation, which can lead to the stable maintenance of a mixed sex-determining system, in which X, Y, Z, and W alleles all segregate (e.g., \nameref{fig:freqAll}B,C).
+However, numerical simulations demonstrate that, with tight sex linkage, new sex-determining alleles do not necessarily reach pseudo-fixation, which can lead to the stable maintenance of a mixed sex-determining system, in which X, Y, Z, and W alleles all segregate (e.g., \nameref{fig:freqAll}B,C).
 
@@
 However, with haploid selection and $r<1/2$, the additional term in Eq \eqref{eq:lambda_neoW} can be positive.
-This implies: 
+This implies, 
 \vspace{0.5cm}
 
-\noindent\textit{Conclusion 5: with intermediate recombination between the ancestral sex-determining allele and a selected locus, $0<r<1/2$, a less closely linked neo-W ($r<R$) can invade} ($\lambda_{W'}^{(XY)}>1$).
+\noindent\textit{Conclusion 4: when there is an intermediate rate of recombination between the ancestral sex-determining allele and a selected locus ($0<r<1/2$), haploid selection allows less closely linked sex-determining alleles ($r<R$) to invade during trans-GSD transitions ($\lambda_{W'}^{(XY)}>1$).}
+\textcolor{red}{[new result because Kozielska had tight linkage and Ubeda had ESD]}
 \vspace{0.5cm}
@@
 
-Previous research suggests that when the ancestral sex-determining locus is linked to a locus that experiences haploid selection (e.g., meiotic drive), alleles at a new, unlinked sex-determining locus invade to restore equal sex ratios~\cite{Kozielska:2010vm}.
+Previous research has shown that when the ancestral sex-determining locus is linked to a locus that experiences haploid selection (e.g., meiotic drive), alleles at a new, unlinked sex-determining locus can invade and restore equal sex ratios~\cite{Kozielska:2010vm,Ubeda:2015fx}.
 Consider, for example, the case where the $\mathbf{A}$ locus is linked to the ancestral sex-determining locus ($r<1/2$) and experiences meiotic drive in males only ($\alpha^\male_\Delta \neq 0$, $\alpha^\female_\Delta=0$), without gametic competition ($t^\female=t^\male=0$).
@@
 However, Fig \ref{fig:SexRatioBad}B shows that a neo-Y can invade the resulting ZW system under the same conditions. 
-When $R<1/2$, the invading neo-Y becomes associated with the male meiotic drive allele and the zygotic sex ratio actually evolves to become male-biased (similar to the scenario considered in \cite{Ubeda:2015fx}).
+When $R<1/2$, the invading neo-Y becomes associated with the male meiotic drive allele and the zygotic sex ratio actually evolves to become male-biased (as in the scenarios considered in \cite{Kozielska:2010vm,Ubeda:2015fx}).
 In this case, the neo-Y spreads because it is often found in males and can, if it carries the driven allele $a$, benefit from haploid selection in males (Fig \ref{fig:SexRatioBad}B).
@@
 We next consider the case where the new sex-determining mutation, $m$, causes sex to be determined probabilistically or by heterogeneous environmental conditions (environmental sex determination, ESD), with individuals carrying allele $m$ developing as females with probability $k$.
+\textcolor{red}{In our deterministic model this means the fraction female is exactly $k$, even when $m$ is rare (exploring the effect of the variance induced by ESD would also be interesting).}
 Here, we do not assume that the environmental conditions that determine sex also differentially affect the fitness of males versus females. 
@@
 
-\noindent\textit{Conclusion 6: when there is haploid selection, ESD can invade an ancestrally-XY system because it generates females that are either rare or have high fitness, in the same manner as a neo-W}.
+\noindent\textit{Conclusion 5: with haploid selection, an allele causing environmental-sex-determination can invade an ancestrally-XY system because it generates females that are either rare or have high fitness, in the same manner as a neo-W (likewise, ESD invades a ZW system for the same reasons a neo-Y can)}.
+\textcolor{red}{[I imagine this is a new result as it requires the evolution of effectively looser linkage from a weak recombination ancestor, which requires haploid selection, and neither Kozielska or Ubeda had GSD to ESD.]}
 \vspace{0.5cm}
@@
 We conclude that, as with neo-W and neo-Y loci, associations with selected loci mean that the evolution of ESD is not straightforwardly predicted by selection to balance the zygotic sex ratio when haploid selection is present.
+
+\textcolor{red}{
+Somehow need to add two further conclusions suggested by review 2:
+\vspace{0.5cm}
+\\
+\noindent\textit{Conclusion 6: sex-antagonism and tighter sex linkage not required for transitions.}
+\vspace{0.5cm}
+\\
+\noindent\textit{Conclusion 7: haploid selection makes conditions for transitions permissive.}
+\vspace{0.5cm}
+\\
+\noindent Or are these evident from the first 5 conclusions?
+}
 

### 2018-03-26 LaTeX/response.tex
added some thoughts below rev3 comments

@@
 \noindent\subsubsection{}
-The findings in [SOO] claimed to be surprising (``Surprisingly, we find that neither force (sex ratio selection nor associations with genes that have sex-specific effects) dominates the spread of new sex-determining systems alone.") and unexpected (``Even more unexpectedly, we find that, to spread, new sex-determining alleles do not necessarily have to arise in closer linkage with genes that are differentially selected in males and females"), are rather similar to those in Ubeda et al 2015.
+The findings in [SOO] claimed to be surprising (``Surprisingly, we find that neither force (sex ratio selection nor associations with genes that have sex-specific effects) dominates the spread of new sex-determining systems alone.") ...
+[but this result is rather similar to those in Ubeda et al 2015].
+
+\noindent\paragraph{Response}
+\textcolor{red}{Here, we were referring to the result that $\lambda_{W'}^{XY} = \lambda_{Y'}^{ZW}$ with haploid selection, even when sex ratio biases evolve to become stronger or weaker (e.g., $\lambda_{Y'}^{ZW}$ vs.
+$\lambda_{W'}^{XY}$ with $r<R$ and male meiotic drive) or when sex ratio biases are present or absent (e.g., $\lambda_{W'}^{XY}$ vs.
+$\lambda_{Y'}^{ZW}$ with $r=1/2$ and male meiotic drive).
+The Ubeda et al.
+(2015) step 1 [?] results show that associations with a haploid selected locus can favour a new sex-determining allele despite causing biased sex ratios.
+Nevertheless, it was difficult for us to intuit whether the presence/absence of ancestral sex ratio bias would have a negligible or overwhelming effect on the evolution of new sex-determining alleles.
+For example, the second stage of Ubeda et al.
+(2015) involves the spread of a autosomal meiotic drive suppressor driven by fisherian sex ratio selection [CHECK SEX RATIO SELECTION MENTIONED] and Kozielska et al.
+show that ancestral sex ratio bias can favour new sex determining systems.
+We found our result, that these forces are equal, such that there is no difference between the propensity for XY-ZW or ZW-XY transitions with selection weak relative to recombination, to be surprising.} \textcolor{blue}{To clarify our meaning...
+}
+
+\paragraph{} \noindent 
+\noindent and unexpected (``Even more unexpectedly, we find that, to spread, new sex-determining alleles do not necessarily have to arise in closer linkage with genes that are differentially selected in males and females"), are rather similar to those in Ubeda et al 2015.
 This is a problem that repeats itself over the paper
@@
 \noindent\paragraph{Response}
+\textcolor{red}{The Ubeda et al 2015 results do indeed show that differential selection between male and female diploids is not required for new sex-determining alleles to spread; they show that a new genetic sex-determining allele can spread from ancestral ESD when it is linked to a locus that experiences sex-specific meiotic drive.
+In this sentence, we were referring differential male/female selection in diploids \textit{or} the haploids produced by males/females. 
+That is, we mean to say that our results demonstrate that new sex determining alleles can spread when they are \textit{less closely linked or completely unlinked} to loci under differential male/female haploid and/or diploid selection.
+To our knowledge, this has not been predicted by any verbal or mathematical models and we found this result to be very unexpected. }
 \textcolor{blue}{We now ...}
@@
 \noindent\paragraph{Response}
+\textcolor{red}{In this study, we are referring to organisms, such as animals and angiosperms, in which the type of gamete depends on the sex of the diploid that produced it.
+In this respect, one could consider gametic selection among sperm to be a form of male-specific selection.
+However, as noted here, the dynamics of selection during gametic selection cannot be captured by a diploid selection coefficient, which is why we model selection upon haploid genotypes specifically in two ways.
+[could tie this in with an expanded explanation of the mating system and the way we model haploid selection.]}
 \textcolor{blue}{We now ...}
@@
 \noindent\paragraph{Response}
-\textcolor{blue}{We now ...}
+\textcolor{red}{but \textit{differences} in haploid selection between the sexes are needed (i.e., drive in only one sex, maintained by ploidally-antagonistic selection).
+If $\alpha^{m}=\alpha^{f}$ (and all diploid male/female selection terms equal), then the new sex-determining allele does not invade.
+So I wouldn't use this argument to demonstrate that the two forms of selection are different.
+In this sentence, I was just trying to introduce the 'sex-specific' aspect of haploid selection in precisely the way Ubeda et al (2015) considers it.
+i.e., associations with alleles favoured in one sex (or the gametes produced by that sex) should favour a new sex-determining allele.
+Would have helped if I'd cited though...
+}
 

### 2018-03-26 LaTeX/response.tex
added some thoughts to response

@@
 \noindent\paragraph{Response}
-\textcolor{red}{Here, we were referring to the result that $\lambda_{W'}^{XY} = \lambda_{Y'}^{ZW}$ with haploid selection, even when sex ratio biases evolve to become stronger or weaker (e.g., $\lambda_{Y'}^{ZW}$ vs.
-$\lambda_{W'}^{XY}$ with $r<R$ and male meiotic drive) or when sex ratio biases are present or absent (e.g., $\lambda_{W'}^{XY}$ vs.
-$\lambda_{Y'}^{ZW}$ with $r=1/2$ and male meiotic drive).
+\textcolor{red}{Here, we were referring to the result that $\lambda_{W'}^{XY} = \lambda_{Y'}^{ZW}$ with haploid selection, even when sex ratio biases evolve to become either stronger or weaker (e.g., $\lambda_{Y'}^{ZW}$ vs.
+$\lambda_{W'}^{XY}$ with $R<r$ and male meiotic drive) or when sex ratio biases are either present or absent (e.g., $\lambda_{W'}^{XY}$ vs.
+$\lambda_{Y'}^{ZW}$ with $r<1/2$, $R=1/2$, and male meiotic drive).
 The Ubeda et al.

### 2018-03-26 LaTeX/response.tex
first pass at all revisions done

--- 2018-03-26 LaTeX/response.tex
@@
 Sexual selection does seem like a different model though, with for example, male fitnesses depending on female frequencies.
-A note such as "We do not consider fertility or sexual selection." in the paragraph beginning near L111.}
+A note such as "We do not consider fertility or sexual selection." in the paragraph beginning near L111 might do it?}
 
@@
 \noindent\paragraph{Response}
-\textcolor{red}{Perhaps we could just drop the words ``the leading eigenvalues are" (which I have done)?}
+\textcolor{blue}{We have dropped the words ``the leading eigenvalues are".}
 
@@
 \textcolor{red}{I think that, with our deterministic model (where the number of binomial trials is infinite), the variance in the fraction male is 0, and so is the same as GSD.
-We could briefly mention this at the beginning or end of the ESD section, and say that modeling ESD in a finite population could be interesting?}
+We could briefly mention this at the beginning or end of the ESD section, and say that modeling ESD in a finite population could be interesting?
+I've put in an attempt on L.}
 
@@
 \noindent\paragraph{Response}
-\textcolor{red}{We now highlight 5 conclusions in the style of Orr 1998...}
+\textcolor{blue}{We now give these 3 main conclusions at the end of the introduction. Further, in the results we now also highlight 5 conclusions in the style of Orr 1998.}
 
@@
 \noindent\paragraph{Response}
-\textcolor{blue}{We now ...}
+\textcolor{blue}{We have replaced ``Thus, if the population sex ratio is biased towards one sex, the average per-individual contribution of genetic material to the next generation from the opposite sex is greater" with ``Thus, if the sex ratio is biased, an individual of the rarer sex will, on average, contribute more genetic material to the next generation".}
 
@@
 \noindent\paragraph{Response}
-\textcolor{blue}{We now ...}
+\textcolor{blue}{We have rearranged and rewritten the introduction to better motivate our model (see Response 2.1).
+In particular, paragraph 5 explains how the effect of haploid selection on SD transitions is unclear.}
 
@@
 \noindent\paragraph{Response}
-\textcolor{blue}{We now ...}
+\textcolor{blue}{Rewritten as suggested.}
 
@@
 \noindent\paragraph{Response}
-\textcolor{blue}{We now ...}
+\textcolor{blue}{We have rewritten the main conclusions to be those three suggested in 2.2 (see Response 2.2).}
 
@@
 \noindent\paragraph{Response}
-\textcolor{blue}{We now ...}
+\textcolor{red}{This is obviously very important, and is commonly assumed (Kozielska et al.
+2010, van Doorn and Kirkpatrick 2007, 2010).
+There are a large number of other possibilities (given 9 genotypes that determine 2 sexes, ie $2^9$), and it seems like these alternatives could either increase or decrease selection on the invader.
+van Doorn and Kirkpatrick don't give any motivation (from my quick skim), but Kozielska et al.
+cite the housefly (Musca domestica), where it seems a single W is epistatically dominant over any number of loci with Y alleles.
+Is this ``compatible" with our model?}
 
@@
 \noindent\paragraph{Response}
-\textcolor{blue}{We now ...}
+\textcolor{blue}{We have replaced the male/female symbol with a circle.}
 
@@
 \noindent\paragraph{Response}
-\textcolor{blue}{We now ...}
+\textcolor{blue}{We have extended the footnote to define all terms in Table 2.}
 
@@
 \noindent\paragraph{Response}
-\textcolor{blue}{We now ...}
+\textcolor{blue}{We have flipped the statement to talk about male biased sex-ratios instead, and mention that this is possible at equilibrium under the more familiar scenario of meiotic drive in males.}
 
@@
 \noindent\paragraph{Response}
-\textcolor{blue}{We now ...}
+\textcolor{blue}{We have replaced this instance of $\epsilon$ with the more familiar $s<<r$ style assumption.
+When we introduce $\epsilon$ in the weak selection section we now verbally explain that it is just a number that is much less than one.}
 
@@
 \noindent\paragraph{Response}
-\textcolor{blue}{We now ...}
+\textcolor{blue}{The blue and green curves should not really show as they are not expected to increase from a very small initial frequency.
+We have kept the original scale but now state in the legend that the blue and green loci do not invade.}
 
@@
 \noindent\paragraph{Response}
-\textcolor{blue}{We now ...}
+\textcolor{blue}{We have kept the $V_A$ as we reuse this shorter, strictly positive, term throughout the text. This is also consistent with the well-known van Doorn and Kirkpatrick 2007, 2010 models.}
 
@@
 \noindent\paragraph{Response}
-\textcolor{blue}{We now ...}
+\textcolor{blue}{We hope the improvements discussed above (e.g., Response 2.1 and 2.2) and below have increased the clarity of our writing, especially regarding the main results.}
 
@@
 \noindent\paragraph{Response}
-\textcolor{blue}{We hope the responses below help...}
+\textcolor{blue}{As described at length below, we now give more weight to two previous papers (Kozielska et al 2010 and Ubeda et al 2015) and more precisely indicate which of our results are new and unexpected.}
 
@@
 \noindent\paragraph{Response}
-\textcolor{blue}{We now ...}
+\textcolor{red}{The abstract and summary still seem to be a little over-selling...}
+\textcolor{blue}{}
 
 \noindent\subsubsection{}
-The findings in [SOO] claimed to be surprising (``Surprisingly, we find that neither force (sex ratio selection nor associations with genes that have sex-specific effects) dominates the spread of new sex-determining systems alone.") and unexpected (``Even more unexpectedly, we find that, to spread, new sex-determining alleles do not necessarily have to arise in closer linkage with genes that are differentially selected in males and females"), are rather similar to those in Ubeda et al 2015.
+The findings in [SOO] claimed to be surprising (``Surprisingly, we find that neither force (sex ratio selection nor associations with genes that have sex-specific effects) dominates the spread of new sex-determining systems alone.") ...
+[but this result is rather similar to those in Ubeda et al 2015].
+
+\noindent\paragraph{Response}
+\textcolor{blue}{Here, we were referring to the result that $\lambda_{W'}^{XY} = \lambda_{Y'}^{ZW}$ with haploid selection, even when sex-ratio biases evolve to become either stronger or weaker (e.g., $\lambda_{Y'}^{ZW}$ vs.
+$\lambda_{W'}^{XY}$ with $R<r$ and male meiotic drive) or when sex-ratio biases are either present or absent (e.g., $\lambda_{W'}^{XY}$ vs.
+$\lambda_{Y'}^{ZW}$ with $r<1/2$, $R=1/2$, and male meiotic drive).
+The Ubeda et al.
+(2015) step 2 result shows that associations with a haploid selected locus can favour a new sex-determining allele despite causing biased sex ratios.
+Nevertheless, it was difficult for us to intuit whether the presence/absence of ancestral sex-ratio bias would have a negligible or overwhelming effect on the evolution of new sex-determining alleles.
+For example, step 3 of Ubeda et al.
+(2015) involves the spread of a autosomal meiotic drive suppressor driven by Fisherian sex-ratio selection and Kozielska et al.
+(2010) show that ancestral sex-ratio bias can favour new sex determining systems.
+We found our result, that these forces are equal, such that there is no difference between the propensity for XY-ZW or ZW-XY transitions with selection weak relative to recombination, to be surprising.} \textcolor{blue}{To clarify our meaning we have rephrased as ``Surprisingly, we find the two forces (sex-ratio selection and associations with genes that have sex-specific effects) will often be equally strong, and thus neither dominates the spread of new sex-determining systems alone."}
+
+\noindent\subsubsection{}
+\noindent and unexpected (``Even more unexpectedly, we find that, to spread, new sex-determining alleles do not necessarily have to arise in closer linkage with genes that are differentially selected in males and females"), are rather similar to those in Ubeda et al 2015.
 This is a problem that repeats itself over the paper
@@
 \noindent\paragraph{Response}
-\textcolor{blue}{We now ...}
-
-For example in:
+\textcolor{blue}{The Ubeda et al 2015 results do indeed show that differential selection between male and female diploids is not required for new sex-determining alleles to spread; they show that a new genetic sex-determining allele can spread from ancestral ESD when it is linked to a locus that experiences sex-specific meiotic drive.
+In this sentence, we were attempting to stress that new sex determining alleles can spread when they are \textit{less closely linked or completely unlinked} to loci under differential male/female haploid and/or diploid selection.
+To our knowledge, this has only been shown for the special case of $r=0$ and $R=1/2$ driven by sex-ratio selection (Kozielska et al 2010; Ubeda et al 2015 show that an unlinked modifier of drive can spread, but this is much different from a sex-determining allele).
+We therefore found the large parameter space allowing invasion with $r<R$ very unexpected.}
+\textcolor{blue}{To communicate this we have rephrased: ``Even more unexpectedly, we find that new sex-determining alleles can spread despite being less closely linked to selected loci under a wide range of conditions."}
 
 \noindent\subsubsection{}
-Page 2.
-The authors claim that predominant theories of the evolution of sex sex-determining systems are two: sexually-antagonistic selection and sex-ratio selection.
+For example in: Page 2.
+The authors claim that predominant theories of the evolution of sex-determining systems are two: sexually-antagonistic selection and sex-ratio selection.
 They ignore other two: inbreeding (Charlesworth 1978) and sex-different drive (Ubeda et al 2015).
@@
 \noindent\paragraph{Response}
-\textcolor{blue}{We now ...}
+\textcolor{blue}{
+We are unsure of which paper the reviewer is referring to.
+Charlesworth 1978 PNAS 75:5618 discusses the degradation of the Y by Muller's ratchet and subsequent dosage compensation, which has little relevance here.
+Charlesworth and Charlesworth 1978 Am Nat 112:975-997 discuss the role of inbreeding in transitions from hermaphrodism (ie no sex-determining alleles) to the case of dioecy (with sex-determining alleles).
+Charlesworth and Charlesworth 1978 Heredity 41:137-153 is similar but begins with monoecy.
+Assuming the reviewer meant one of the latter two, both it and Ubeda et al 2015 consider the origin of genetic sex-determination from hermaphrodism/monoecy or environmental sex-determination. 
+Here we are much more concerned with transitions between genetic sex-determination systems.
+Further, we do not state that sex-antagonism is one of the predominant theories explaining SD transitions, it is but one example where fitness differs between the sexes, another example being ``sex-different drive".
+We discuss the fact that sex-specific drive can be thought of as a sex difference in selection in paragraph 5 of the introduction (see Response 3.2.6).
+We have rephrased slightly to restrict ourselves to transitions between GSD: ``Predominant theories accounting for transitions between GSD systems by selection involve fitness differences between sexes (e.g., sexually antagonistic selection) or sex-ratio selection...".}
 
 \noindent\subsubsection{}
-Page 3 ``Here we use mathematical models to find the conditions under which new sex-determining systems spread when individuals experience selection at both diploid and haploid stages, which allows fitness differences between the sexes and sex ratio biases to occur simultaneously"
-
+Page 3 ``Here we use mathematical models to find the conditions under which new sex-determining systems spread when individuals experience selection at both diploid and haploid stages, which allows fitness differences between the sexes and sex ratio biases to occur simultaneously".
 This would be the same model as Ubeda et al 2015 adding sex-specific viability.
@@
 \noindent\paragraph{Response}
-\textcolor{blue}{We now ...}
+\textcolor{blue}{It is true that Ubeda et al 2015 is a special case of our model. 
+However, Ubeda et al 2015 was primarily a numerical investigation, providing a less general treatment of this special case and developing less intuition.
+Further, our model and intuition-giving analytical solutions explore a much wider range of scenarios, allowing, for example, sex-specific selection (e.g., sex-antagonism) and various genomic arrangements (any order/linkage of the three loci).
+Our model is thus much more general and clarifies just when one should expect to see the numerical results of Ubeda et al 2015.
+We have rephrased to make this clear (after discussing Ubeda et al 2015, see Response 2.1): ``Here we use mathematical models to clarify the conditions under which new sex-determining systems spread when individuals experience extremely general and potentially sex-specific selection at both diploid and haploid stages, which allows fitness differences between the sexes and sex-ratio biases to occur simultaneously."
+}
 
@@
 This is a stretch and creates confusion.
-I consider selection acting on individuals with different sex sex-specific selection, now when selection is acting on gametes (which are neither males or females) males or females are just different environments in which selection may take place.
+I consider selection acting on individuals with different sex-specific selection, now when selection is acting on gametes (which are neither males or females) males or females are just different environments in which selection may take place.
 Neither the dynamics nor the constraints are the same.
@@
 \noindent\paragraph{Response}
-\textcolor{blue}{We now ...}
+\textcolor{blue}{In this study, we are referring to organisms, such as animals and angiosperms, in which the type of gamete depends on the sex of the diploid that produced it.
+In this respect, one could consider gametic selection among sperm to be a form of male-specific selection.
+However, as noted here, the dynamics of selection during gametic selection cannot be captured by a diploid selection coefficient, which is why we model selection upon haploid genotypes specifically in two ways.
+}
+\textcolor{red}{
+[could tie this in with an expanded explanation of the mating system and the way we model haploid selection (see Response 3.3).]}
 
@@
 \noindent\paragraph{Response}
-\textcolor{blue}{We now ...}
+\textcolor{blue}{In the absence of sex-differences in selection it is true that antagonistic drive is not needed, but \textit{differences} in haploid selection between the sexes are needed (e.g., drive in only one sex, maintained by ploidally-antagonistic selection).
+If drive was the same in both sexes, $\alpha^{m}=\alpha^{f}$ (and all diploid male/female selection terms equal), then the new sex-determining allele would not invade. 
+In this sense haploid selection is indeed similar o sex-specific diploid selection, and together haploid and diploid selection determine the differences in male vs.
+female fitness, which can drive sex-determination transitions (see Response 3.2.4).
+In this sentence, we are introducing the 'sex-specific' aspect of haploid selection in precisely the way Ubeda et al (2015) considers it; i.e., associations with alleles favoured in one sex (or the gametes produced by that sex) should favour a new sex-determining allele.
+We now follow this sentence up with two sentences that clarify its meaning by comparing with the results of Kozielska et al (2010) and Ubeda et al (2015).}
 
@@
 \noindent\paragraph{Response}
-\textcolor{blue}{We now ...}
-\\
+\textcolor{blue}{While it was the focus of Ubeda et al 2015, the restricted scope of that study prevents us from generalizing beyond its special case (see Response 3.2.5).
+We have rephrased: ``It is not yet clear when new sex-determining alleles are favoured by associations with haploid selected alleles vs.
+sex-ratio bias, especially under a wide range of possible diploid selection regimes (e.g., sex-antagonism, overdominance)."
+}
 
+\noindent\subsubsection{}
 I will not provide further examples, but it is surprising thatI the work of Ubeda et al 2015, which is closely related to the one presented here, is cited in page 12 supporting a statement only tangential to the work of Ubeda et al 2015.
+
+\noindent\paragraph{Response}
+\textcolor{blue}{Ubeda et al 2015 was already cited on line 396 of the original submission, where we mentioned that it showed that sex-ratio biases could become more severe during a transition.
+Nevertheless, we now discuss Ubeda et al 2015 in the introduction, results, and discussion.}
 
@@
 \noindent\paragraph{Response}
-\textcolor{blue}{We now ...}
+\textcolor{blue}{We do not agree. 
+Given our definition of meiotic drive and gametic competition in the introduction, the two processes are different.
+In particular, meiotic drive is assumed to occur during meiosis, and thus is ``gametic competition" amongst the gametes produced by a single individual. 
+As such, meiotic drive can only have an effect in heterozygotes.
+Gametic competition on the other hand, is competition amongst all the gametes produced by one sex (e.g., pollen from many male plants).
+Thus allele frequency changes can occur by gametic competition even if all individuals were homozygous (as long as there is a polymorphism).
+We have rephrased our definitions in the introduction to read: ``We use the term `meiotic drive' to refer to the biased (non-Mendelian) segregation of genotypes during gamete production (from one parent only) and the term `gametic competition' to refer to selection upon haploid genotypes within a gamete/gametophyte pool (from many parents)."
+}
 

### 2018-03-26 LaTeX/main_revision.tex
first pass at all revisions done

@@
 {\Large
-\textbf\newline{Haploid selection, sex ratio bias, and transitions between sex-determining systems} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
+\textbf\newline{Haploid selection, sex-ratio bias, and transitions between sex-determining systems} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
 }
@@
 \section*{Abstract}
-Genetic sex determination is remarkably dynamic; many taxa display shifts in the location of sex-determining loci or the evolution of entirely new sex-determining systems. 
+Sex determination is remarkably dynamic; many taxa display shifts in the location of sex-determining loci or the evolution of entirely new sex-determining systems. 
 Predominant theories for why we observe such transitions generally conclude that novel sex-determining systems are favoured by selection if they equalise the sex ratio or increase linkage with a sexually-antagonistic locus.
@@
 Variation at such loci can favour the spread of new sex-determining systems in which the heterogametic sex changes (XY to ZW or ZW to XY) and the new sex-determining region is less closely linked (or unlinked) to the locus under selection, which is not predicted by previous theory.
-(2) We also consider selection upon haploid genotypes either during gametic competition (e.g., pollen/sperm competition involving multiple males) or meiosis (i.e., non-Mendelian segregation), which can cause the zygotic sex ratio to become biased.
+(2) We consider selection upon haploid genotypes either during gametic competition (e.g., pollen/sperm competition involving multiple males) or meiosis (i.e., non-Mendelian segregation), which can cause the zygotic sex ratio to become biased.
 We find that associations with haploid selected loci can drive transitions between sex-determining systems, without requiring sexually-antagonistic selection in diploids. 
 Unexpectedly, with haploid selection, transitions between male and female heterogamety can also evolve where linkage with the sex-determining locus is weakened. 
-Furthermore, sex ratio biases may increase or decrease with the spread of new sex chromosomes. 
+Furthermore, sex-ratio biases may increase or decrease with the spread of new sex chromosomes. 
 Thus, we find that transitions between sex-determining systems cannot be simply predicted by selection to equalise the sex ratio. 
 Overall, our models reveal that transitions between sex-determining systems, particularly transitions where the heterogametic sex changes, can be driven by loci in previously unpredicted genomic locations that experience selection during diploid and/or haploid phases.
-These results predict conditions under which sex-determining systems are likely to be labile and draw novel connections with sex ratio evolution.
+These results predict conditions under which sex-determining systems are likely to be labile and draw connections with sex-ratio evolution.
 
@@
 Prevailing views suggest that new sex-determining systems are favoured when they equalize the sex ratio and/or when they are more closely linked to genes that experience differential selection in males and females.
-Our models extend these theories to include selection upon haploid genotypes (meiotic drive or gametic competition), which causes sex ratio biases and occurs differently in males and females. 
-Surprisingly, we find that neither force (sex ratio selection nor associations with genes that have sex-specific effects) dominates the spread of new sex-determining systems alone. 
-Even more unexpectedly, we find that, to spread, new sex-determining alleles do not necessarily have to arise in closer linkage with genes that are differentially selected in males and females. 
+Our models extend these theories to include selection upon haploid genotypes (meiotic drive or gametic competition), which causes sex-ratio biases and occurs differently in males and females. 
+Surprisingly, we find the two forces (sex-ratio selection and associations with genes that have sex-specific effects) will often be equally strong, and thus neither dominates the spread of new sex-determining systems alone.
+Even more unexpectedly, we find that new sex-determining alleles can spread despite being less closely linked to selected loci under a wide range of conditions. 
 Therefore, our models predict loci in previously unexpected genomic locations and/or experiencing various types of selection (including haploid selection) can now be implicated as drivers of transitions between sex-determining systems.
@@
 %(1) sex-antagonism
-Predominant theories accounting for transitions between GSD systems by selection involve fitness differences between sexes (e.g., sexually antagonistic selection) or sex ratio selection~\cite{Blaser2012, Beukeboom:2014vb,vanDoorn2014re}.
+Predominant theories accounting for transitions between GSD systems by selection involve fitness differences between sexes (e.g., sexually antagonistic selection) or sex-ratio selection~\cite{Blaser2012, Beukeboom:2014vb,vanDoorn2014re}.
 %\citet{Bull:1977wt} shows that direct selection on new sex determination loci can allow them to spread and switch between male and female heterogamety. 
@@
 %(2) sex-ratio selection
-The sex ratio is directly determined by the sex-determining system, and it has therefore been suggested that sex ratio selection is a dominant force in the evolution of sex determination (e.g., Bull, 1983, p 66-67 ~\cite{Bull:1983vi}; Buekeboom and Perrin, 2014, Chapter 7~\cite{Beukeboom:2014vb}).
+The sex ratio is directly determined by the sex-determining system, and it has therefore been suggested that sex-ratio selection is a dominant force in the evolution of sex determination (e.g., Bull, 1983, p 66-67 ~\cite{Bull:1983vi}; Buekeboom and Perrin, 2014, Chapter 7~\cite{Beukeboom:2014vb}).
 `Fisherian' sex-ratio selection favours a 1:1 zygotic sex ratio when assuming that males and females are equally costly to produce~\cite{Fisher:1930wy,Charnov:1982wg}.
 This follows from the fact that, for an autosomal locus, half of the genetic material is inherited from a male and half from a female~\cite{West:2009we}. 
-Thus, if the population sex ratio is biased towards one sex, the average per-individual contribution of genetic material to the next generation from the opposite sex is greater. 
-Therefore, a mutant that increases investment in the rarer sex will spread via the higher per-individual contributions made by that sex. 
-%The default mode of sex ratio selection is `Fisherian' sex ratio selection, which favours equal investment in male and female offspring \citep[i.e., a 1:1 zygotic sex ratio when assuming that males and females are equally costly to produce,][]{Fisher:1930wy,Charnov:1982wg}.
-%Given that the sex-determining system can directly affect the sex ratio, we might expect Fisherian sex ratio selection to influence the spread of new sex-determining systems. 
+Thus, if the sex ratio is biased, an individual of the rarer sex will, on average, contribute more genetic material to the next generation. 
+Selection therefore favours mutants that increase investment in the rarer sex.
+%The default mode of sex-ratio selection is `Fisherian' sex-ratio selection, which favours equal investment in male and female offspring \citep[i.e., a 1:1 zygotic sex ratio when assuming that males and females are equally costly to produce,][]{Fisher:1930wy,Charnov:1982wg}.
+%Given that the sex-determining system can directly affect the sex ratio, we might expect Fisherian sex-ratio selection to influence the spread of new sex-determining systems. 
 %In the case of sex-chromosome evolution, Kozielska et al.
@@
 Segregation distortion provides putative evidence of haploid selection and can sometimes be attributed to meiotic drive and/or gametic competition~\cite{Lalanne2004,Fishman2005,Leppala2008,Leppala2013,Didion2015,Didion2016}.
-Where it has been characterized, meiotic drive generally occurs either during the production of male or female gametes only~\cite{Ubeda:2005gw,Lindholm:2016cw}.
-Gametic competition is also typically sex specific, occurring primarily among male gametes, because there are typically many more pollen/sperm than required for fertilization.
+Where it has been characterized, individual cases of meiotic drive are generally sex-limited, exclusively affecting male or female gametes~\cite{Ubeda:2005gw,Lindholm:2016cw}.
+Gametic competition is also typically sex-limited, occurring primarily among male gametes, because there are typically many more pollen/sperm than required for fertilization.
 Gametic competition may be particularly common in plants, in which 60-70\% of all genes are expressed in the male gametophyte, and these genes exhibit stronger signatures of selection than randomly-chosen genes~\cite{Borg:2009jpa,Arunkumar:2013iq,Gossmann:2014dua}.
@@
 Sex-ratio selection can thus select against the spread of linked sex-determining alleles and favour the invasion of alternative, unlinked sex-determination systems \cite{Kozielska:2010vm,Ubeda:2015fx}.
-%It is not immediately clear how the spread of new sex-determining systems would be influenced by the combination of sex ratio biases and associations with haploid selected alleles. 
+%It is not immediately clear how the spread of new sex-determining systems would be influenced by the combination of sex-ratio biases and associations with haploid selected alleles. 
 It is not yet clear when new sex-determining alleles are favoured by associations with haploid selected alleles vs.
 sex-ratio bias, especially under a wide range of possible diploid selection regimes (e.g., sex-antagonism, overdominance).
-Here we use mathematical models to clarify the conditions under which new sex-determining systems spread when individuals experience extremely general and potentially sex-specific selection at both diploid and haploid stages, which allows fitness differences between the sexes and sex-ratio biases to occur simultaneously.
-
+
+` 
+We consider both selected loci that are loosely linked to the sex-determining region (e.g., on an autosome) and selected loci that are in very tight linkage with the ancestral sex-determining locus (e.g., within the non-recombining sex-determining region).
+Our main findings are three:
+(1) transitions between sex-determining systems can decrease or increase sex-ratio bias, and with sufficiently loose linkage between the selected locus and the sex-determining locus, the selective force exerted by sex-ratio selection and favourable associations with haploid-selected alleles are exactly equivalent;
+(2) ancestrally-tight sex-linkage and haploid selection allow trans-GSD transitions that weaken sex-linkage; and
+(3) haploid selection removes the need for sex-antagonism, increasing the range of scenarios that select for transitions between sex-determining systems.
 %MAIN FINDINGS IN GENERAL TERMS
-We find that the spread of novel sex-determining systems is influenced by both Fisherian sex-ratio selection and by selection on linked alleles. 
-%We find that sex ratio biases caused by haploid selection can exert Fisherian sex ratio selection upon novel sex-determiners but that their spread is also determined by selection on genetically-associated alleles.
-%Indeed, it is only when haploid-selected loci are tightly linked to the ancestral sex-determining region (and so sex ratio biases are initially large) that we see an asymmetry between selection for XY to ZW transitions and ZW to XY transitions (e.g., because haploid selection in males only causes biased zygotic sex ratios in an ancestrally XY system).
-Fisherian sex-ratio selection does not always dominate; it is possible for selection on linked alleles to drive turnover between sex-determining systems despite causing increasingly biased sex ratios, and our analytical results elucidate what is required for this to be so.
-In addition to considering haploid selection, another novel development in our model is that we consider loci that are in very tight linkage with the ancestral sex-determining locus. 
+%We find that the spread of novel sex-determining systems is influenced by both Fisherian sex-ratio selection and by selection on linked alleles. 
+%We find that sex-ratio biases caused by haploid selection can exert Fisherian sex-ratio selection upon novel sex-determiners but that their spread is also determined by selection on genetically-associated alleles.
+%Indeed, it is only when haploid-selected loci are tightly linked to the ancestral sex-determining region (and so sex-ratio biases are initially large) that we see an asymmetry between selection for XY to ZW transitions and ZW to XY transitions (e.g., because haploid selection in males only causes biased zygotic sex ratios in an ancestrally XY system).
+%Fisherian sex-ratio selection does not always dominate; it is possible for selection on linked alleles to drive turnover between sex-determining systems despite causing increasingly biased sex ratios, and our analytical results elucidate what is required for this to be so.
 %Because sex-determining loci are often found within a region of suppressed recombination, there can be a significant number of tightly linked loci. 
-We find that loci tightly linked with the sex-determining locus can drive transitions in which the heterogametic sex changes, even when the new sex-determining locus is less closely linked to loci under selection (either including haploid selection or not).
+%We find that loci tightly linked with the sex-determining locus can drive transitions in which the heterogametic sex changes, even when the new sex-determining locus is less closely linked to loci under selection (either including haploid selection or not).
 
@@
    \begin{flushleft} 
+$\hat{p}_X^\female$ is the frequency of $A$ among female gametes.
 $\bar{p}^{\male}=(1-\hat{q})\hat{p}_X^\male + \hat{q}\hat{p}_Y^\male$ is the average frequency of the $A$ allele among X- and Y-bearing male gametes.
@@
 $\bar{w}_H^\circ$ is the mean fitness of haploids from sex $\circ$, see \nameref{tab:meanfitnesses}.
+$R$ is the rate of recombination between the neo-sex-determiner and the selected locus.
+Selection terms ($w_i^\circ$, $\alpha_\Delta^\circ$) are described in Table \ref{tab:fitnesstable}. 
 \end{flushleft}
@@
 This is because a dominant neo-Y (neo-W) is always found in males (females), and therefore the frequency of the neo-Y (neo-W), $m$, only changes in males (females), Fig \ref{fig:model_outline}C,D.
-Second, Fisherian sex-ratio selection will favour the spread of a neo-Y and inhibit the spread of a neo-W if the ancestral zygotic sex ratio is biased towards females (i.e., the first factor of the $\Lambda_{mi}^{(XY)}$ is greater than one for a neo-Y and less than one for a neo-W when $\zeta<1/2$).
+Second, Fisherian sex-ratio selection will favour the spread of a neo-W and inhibit the spread of a neo-Y if the ancestral zygotic sex ratio is biased towards males (i.e., the first factor of the $\Lambda_{mi}^{(XY)}$ is greater than one for a neo-W and less than one for a neo-Y when $\zeta>1/2$), as might occur when the ancestral sex-determining locus is linked to a locus experiencing meiotic drive in males, for example.
 However, the spread of a neo-Y (neo-W) also depends on the male (female) fitness of associated alleles (see terms involving equilibrium allele frequencies, $\hat{p}$'s). That is, 
@@
 We can analytically calculate the allele frequency of the $A$ allele using two alternative simplifying assumptions: 
-(1) the $\mathbf{A}$ locus is within (or tightly linked to) the non-recombining region around the ancestral sex-determining locus ($r \approx 0$) or (2) selection is weak relative to recombination ($s^\circ$, $t^\circ$, $\alpha_{\Delta}^\circ$ of order $\epsilon<<1$).
+(1) the $\mathbf{A}$ locus is within (or tightly linked to) the non-recombining region around the ancestral sex-determining locus ($r \approx 0$) or (2) selection is weak relative to recombination ($s^\circ$, $t^\circ$, $\alpha_{\Delta}^\circ$ $<<$ $r$).
 
@@
 In panel C we vary the recombination rate between the neo-W and the selected locus ($R$) for a fixed recombination rate between the ancestral sex-determining locus and the selected locus ($r=0.005$). 
-Coloured markers show recombination rates for which the temporal dynamics of invasion are plotted in the inset, demonstrating that neo-W alleles can reach pseudo-fixation if they are more (black) or less (red) closely linked to a locus experiencing sexually-antagonistic selection.
+Coloured markers show recombination rates for which the temporal dynamics of invasion are plotted in the inset, demonstrating that neo-W alleles can reach pseudo-fixation if they are more (black) or less (red) closely linked to a locus experiencing sexually-antagonistic selection (neo-W which are too loosely linked (blue and green) do not invade).
 A very loosely linked neo-W does not spread in this case (blue and green lines overlap and go to 0 in inset). 
@@
 
-Here we assume that selection is weak ($s^\circ$, $t^\circ$, $\alpha_{\Delta}^\circ$ of order $\epsilon<<1$) and thus implicitly assume that all recombination rates ($r$, $R$ and $\rho$) are large relative to selection.
+Here we assume that selection is weak ($s^\circ$, $t^\circ$, $\alpha_{\Delta}^\circ$ of order $\epsilon$, where $\epsilon$ is some number much less than one) and thus implicitly assume that all recombination rates ($r$, $R$ and $\rho$) are large relative to selection.
 %, we denote the leading eigenvalues describing the invasion of a neo-Y ($k=0$) and a neo-W ($k=1$) into an ancestrally XY system by $\lambda_{Y',XY}$ and $\lambda_{W',XY}$, respectively. 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Sex ratio selection is not a good predictor of neo-W invasion into an XY system
+%sex-ratio selection is not a good predictor of neo-W invasion into an XY system
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 If Fisherian sex-ratio selection were dominant, we would thus expect a difference in the potential for XY to ZW and ZW to XY transitions. 
-%However, to leading order with selection weak relative to recombination, we find that sex ratio selection favours the spread of a neo-W by an amount equl to the spread of a neo-Y into a ZW system (relabeling XY as the heterogametic sex and reversing the labels of males and females in Table \ref{tab:specialcases})
-%However, to leading order with selection weak relative to recombination, we find that sex ratio selection favours the spread of a neo-W (through the first terms in table \ref{tab:haplotype_growth}) by an amount that is equal in magnitude to the fitness effects of alleles associated with new sex-determining alleles (second terms in table \ref{tab:haplotype_growth}).
+%However, to leading order with selection weak relative to recombination, we find that sex-ratio selection favours the spread of a neo-W by an amount equl to the spread of a neo-Y into a ZW system (relabeling XY as the heterogametic sex and reversing the labels of males and females in Table \ref{tab:specialcases})
+%However, to leading order with selection weak relative to recombination, we find that sex-ratio selection favours the spread of a neo-W (through the first terms in table \ref{tab:haplotype_growth}) by an amount that is equal in magnitude to the fitness effects of alleles associated with new sex-determining alleles (second terms in table \ref{tab:haplotype_growth}).
 However, invasion by a neo-W allele into an XY system and invasion by a neo-Y allele into a ZW system occur under the same conditions ($\lambda_{Y'}^{(XY)} = \lambda_{W'}^{(ZW)}$ and $\lambda_{W'}^{(XY)}=\lambda_{Y'}^{(ZW)}$, at least to order $\epsilon^2$).
@@
 %
-%As selection becomes stronger (or linkage becomes tighter), this symmetry between sex ratio selection and haploid selection is lost, causing differences in the strength of selection favouring the two heterogametic transitions (compare red to black near -25cM and 25 cM in Fig \ref{fig:Combination_Centimorgans}).
+%As selection becomes stronger (or linkage becomes tighter), this symmetry between sex-ratio selection and haploid selection is lost, causing differences in the strength of selection favouring the two heterogametic transitions (compare red to black near -25cM and 25 cM in Fig \ref{fig:Combination_Centimorgans}).
 \textcolor{red}{normalise fitness in sexually antagonistic case}
@@
 
-%Under Fisherian sex ratio selection, autosomal modifiers favour equal investment in male and female offspring, i.e., a 1:1 sex ratio~\cite{Fisher:1930wy,Charnov:1982wg,West:2009we}. 
+%Under Fisherian sex-ratio selection, autosomal modifiers favour equal investment in male and female offspring, i.e., a 1:1 sex ratio~\cite{Fisher:1930wy,Charnov:1982wg,West:2009we}. 
 %A novel environmental sex-determiner that causes half of its carriers to become female and half to become male ($k=1/2$) will be in males half of the time and in females half of the time (like an autosome).
-%In addition, these novel sex-determination alleles equalize the sex ratio and therefore one might expect them to be favoured by Fisherian sex ratio selection when the resident sex ratio is biased.
+%In addition, these novel sex-determination alleles equalize the sex ratio and therefore one might expect them to be favoured by Fisherian sex-ratio selection when the resident sex ratio is biased.
 %However, assuming weak selection, we find that the growth rate of a rare, dominant offspring-controlled neo-ESD allele that produces males or females with equal probability ($k=1/2$) is
@@
 Nevertheless, ESD is equally likely to invade when it equalizes the zygotic sex ratio (through $\lambda_{W'}^{(XY)}$) as when it doesn't (through $\lambda_{Y'}^{(ZW)}$). 
-%This is again because haploid selection can facilitate the turnover of sex chromosomes either through sex ratio biases or through associations between the new sex determining region with selected alleles.
+%This is again because haploid selection can facilitate the turnover of sex chromosomes either through sex-ratio biases or through associations between the new sex determining region with selected alleles.
 %With weak selection, these two forces are nearly equal in strength. 
@@
 %MAIN RESULT
-Two predominant theories explaining the remarkably high frequency of transitions between genetic sex-determining systems are sexually-antagonistic selection and sex ratio selection (reviewed in~\cite{Blaser2012, vanDoorn2014re}).
+Two predominant theories explaining the remarkably high frequency of transitions between genetic sex-determining systems are sexually-antagonistic selection and sex-ratio selection (reviewed in~\cite{Blaser2012, vanDoorn2014re}).
 The former predicts that new sex-determining alleles can invade when they arise in closer linkage with a sexually-antagonistic locus ($r<R$,~\cite{vanDoorn:2007eu,vanDoorn:2010hu, Muralidhar2018}).
@@
 We find that the spread of new sex-determining systems cannot be simply predicted from their effect on the sex ratio. 
-On one hand, sex ratio biases caused by haploid selection can facilitate trans-GSD transitions or transitions from genetic to environmental sex determination. 
+On one hand, sex-ratio biases caused by haploid selection can facilitate trans-GSD transitions or transitions from genetic to environmental sex determination. 
 For instance, alleles favoured by haploid selection in males often become associated with the Y allele, which leads to a male-biased zygotic sex ratio.
 This male bias increases the potential for a neo-W allele to invade (Table \ref{tab:haplotype_growth}), which can equalize the sex ratio (e.g., see Fig \ref{fig:SexRatioBad}B, for related examples see~\cite{Kozielska:2010vm}).
-%We find that sex ratio biases caused by haploid selection can also affect transitions between sex-determining systems (e.g., see $\zeta$ terms in Table \ref{tab:haplotype_growth}). 
+%We find that sex-ratio biases caused by haploid selection can also affect transitions between sex-determining systems (e.g., see $\zeta$ terms in Table \ref{tab:haplotype_growth}). 
 %However, the neo-W may not equalize the sex ratio (e.g., if the driving allele also drives in females or affects competition among eggs)
-On the other hand, sex ratio selection can be overwhelmed by additional selective effects, preventing a neo-W or ESD allele from invading, even if it would balance the sex ratio (e.g., when selection acts in opposite directions in male and female diploids, Table \ref{tab:specialcases}).
+On the other hand, sex-ratio selection can be overwhelmed by additional selective effects, preventing a neo-W or ESD allele from invading, even if it would balance the sex ratio (e.g., when selection acts in opposite directions in male and female diploids, Table \ref{tab:specialcases}).
 %and equalizing the sex ratio.
-Indeed, transitions between sex-determining systems can generate stronger sex ratio biases (e.g., Fig \ref{fig:SexRatioBad}A and step 1 in~\cite{Ubeda:2015fx}).
+Indeed, transitions between sex-determining systems can generate stronger sex-ratio biases (e.g., Fig \ref{fig:SexRatioBad}A and step 1 in~\cite{Ubeda:2015fx}).
 %For example, where a neo-Y invades and is linked with a locus that experiences haploid selection in male gametes, the sex ratio evolves to become biased \citep[e.g., see Fig \ref{fig:SexRatioBad}A and step 1 in][]{Ubeda:2015fx}.
@@
 %\textcolor{blue}{and figure 1, where the end of one panel is the same as the beginning of another, however, this figure may change).}
-%What we would like to stress is that sex ratio selection alone cannot predict when new sex-determining systems can evolve.
-Significantly, with weak selection, we find that there is no difference in conditions allowing XY to ZW and ZW to XY transitions, indicating that sex chromosome transitions are not predominantly predicted by their effect on the sex ratio (i.e., the sex ratio bias created by male haploid selection facilitates the spread of a neo-W allele into an XY system to the same degree that male haploid selection drives the spread of a neo-Y into a ZW system with a 1:1 sex ratio).
-%An asymmetry can develop when sex-linkage is tight (e.g., Fig \ref{fig:Combination_Centimorgans} near -25cM and 25cM) but under most circumstances we do not predict asymmetry between XY to ZW and ZW to XY transitions despite the presence/absence of sex ratio selection.
-Thus, haploid selection can favour trans-GSD transitions both via sex ratio selection and via selection on alleles associated with the new sex-determining allele, and these selective pressures are often predicted to be of equal magnitude.
+%What we would like to stress is that sex-ratio selection alone cannot predict when new sex-determining systems can evolve.
+Significantly, with weak selection, we find that there is no difference in conditions allowing XY to ZW and ZW to XY transitions, indicating that sex chromosome transitions are not predominantly predicted by their effect on the sex ratio (i.e., the sex-ratio bias created by male haploid selection facilitates the spread of a neo-W allele into an XY system to the same degree that male haploid selection drives the spread of a neo-Y into a ZW system with a 1:1 sex ratio).
+%An asymmetry can develop when sex-linkage is tight (e.g., Fig \ref{fig:Combination_Centimorgans} near -25cM and 25cM) but under most circumstances we do not predict asymmetry between XY to ZW and ZW to XY transitions despite the presence/absence of sex-ratio selection.
+Thus, haploid selection can favour trans-GSD transitions both via sex-ratio selection and via selection on alleles associated with the new sex-determining allele, and these selective pressures are often predicted to be of equal magnitude.
 
@@
 We conclude that haploid selection should be considered as a pivotal factor driving transitions between sex-determining systems. 
-Further, transitions involving haploid selection can be driven by sex-ratio selection or cause sex ratio biases to evolve; Fisherian sex-ratio selection is not an overwhelming force. 
+Further, transitions involving haploid selection can be driven by sex-ratio selection or cause sex-ratio biases to evolve; Fisherian sex-ratio selection is not an overwhelming force. 
 Overall, our results suggest several new scenarios under which new sex-determining systems are favoured, which could help to explain why the evolution of sex-determining systems is so dynamic.
@@
 %%Haploid selection affects the conclusions outlined above by altering the zygotic sex ratio and exerting direct selection on neo-W haplotypes.
-%%The effect of sex ratio selection is straightforward and can be seen in Eq \eqref{Binvasion}, where male drive and gamete competition for $a$ (which is fixed on the Y and therefore causes a male bias) increases all four terms.
+%%The effect of sex-ratio selection is straightforward and can be seen in Eq \eqref{Binvasion}, where male drive and gamete competition for $a$ (which is fixed on the Y and therefore causes a male bias) increases all four terms.
 %%Direct selection on neo-W haplotypes can also be seen in Eq \eqref{Binvasion} by noticing that increasing female drive in favour of $A$ increases the neo-W-$A$ haplotype growth rate ($\Lambda_{mA}$) while female drive and gamete competition in favour of $a$ increases the neo-W-$a$ haplotype growth rate ($\Lambda_{ma}$).
@@
 %
-%Thus, the impact of haploid selection on transitions between sex-determining systems must be considered as two sides of a coin: it can generate sex ratio biases that promote transitions that equalize the sex ratio, but it can also direct select for transitions that cause sex ratios to become biased.
+%Thus, the impact of haploid selection on transitions between sex-determining systems must be considered as two sides of a coin: it can generate sex-ratio biases that promote transitions that equalize the sex ratio, but it can also direct select for transitions that cause sex ratios to become biased.
 

### 2018-03-27 LaTeX/response.tex
reworking intro again (not completed)

@@
 
+\textcolor{red}{Our analysis shows that the end state of the system depends on the `epistatic dominance' (term removed from our paper?) of the loci.
+Could draw this out more for this response.
+The drift-transitions Genetics paper rests on the difference in dominance, I'm pretty sure they have examples and the majority of new GSD systems are epistatically dominant.
+Also vD\&K 2010.
+}
+
 \noindent\subsubsection{}
@@
 I find the article is not clearly written and could benefit from improving the presentation of the main results. 
-
-\noindent\paragraph{Response}
-\textcolor{blue}{We hope the improvements discussed above (e.g., Response 2.1 and 2.2) and below have increased the clarity of our writing, especially regarding the main results.}
-
-\noindent\subsection{}
+%
+%\noindent\paragraph{Response}
+%\textcolor{blue}{We hope the improvements discussed above (e.g., Response 2.1 and 2.2) and below have increased the clarity of our writing, especially regarding the main results.}
+%
+%\noindent\subsection{}
 I also find the article claims that: (a) the modeling work is novel and (b) the findings are unexpected to be only partially justified.
-
-\noindent\paragraph{Response}
-\textcolor{blue}{As described at length below, we now give more weight to two previous papers (Kozielska et al 2010 and Ubeda et al 2015) and more precisely indicate which of our results are new and unexpected.}
-
-\noindent\subsubsection{}
+%
+%\noindent\paragraph{Response}
+%\textcolor{blue}{As described at length below, we now give more weight to two previous papers (Kozielska et al 2010 and Ubeda et al 2015) and more precisely indicate which of our results are new and unexpected.}
+%
+%\noindent\subsubsection{}
 The works of Kozielska 2014 and Ubeda 2015 model the combined effects of both haploid and diploid selection on the evolution of new sex-chromosomes.
@@
 \textcolor{red}{The abstract and summary still seem to be a little over-selling...}
-\textcolor{blue}{}
+\textcolor{blue}{We have performed an extensive re-arrangement (e.g., Response 2.1 and 2.2 and below) to improve the clarity of our writing, especially regarding the main results. 
+We believe that our new presentation makes the novel and unexpected features of our results much more apparent. }
+\textcolor{red}{In particular, as described at length below, we now give more weight to the two previous papers suggested (Kozielska et al 2010 and Ubeda et al 2015) and more precisely indicate which of our model features and results are new and unexpected.
+To be clear, we do not claim to be the first to include both haploid and diploid selection and the evolution of new sex-chromosomes and we do not consider the addition of sex-specific selection or analytical results for previously numerical models to be our most significant contributions.
+}
 
@@
 In this sentence, we were attempting to stress that new sex determining alleles can spread when they are \textit{less closely linked or completely unlinked} to loci under differential male/female haploid and/or diploid selection.
-To our knowledge, this has only been shown for the special case of $r=0$ and $R=1/2$ driven by sex-ratio selection (Kozielska et al 2010; Ubeda et al 2015 show that an unlinked modifier of drive can spread, but this is much different from a sex-determining allele).
-We therefore found the large parameter space allowing invasion with $r<R$ very unexpected.}
-\textcolor{blue}{To communicate this we have rephrased: ``Even more unexpectedly, we find that new sex-determining alleles can spread despite being less closely linked to selected loci under a wide range of conditions."}
+To our knowledge, this has only been shown for the special case of male meiotic drive in an ancestral XY system with $r=0$ and $R=1/2$ with a neo-W, which is driven by sex-ratio selection (Kozielska et al 2010).
+We therefore found the large parameter space allowing invasion with $r<R$, sometimes in the absence of sex-ratio selection (or even in the absence of haploid selection), to be very unexpected.
+}
+\textcolor{blue}{To communicate this we have rephrased: ``Even more unexpectedly, we find that new sex-determining alleles can spread despite being less closely linked to selected loci under a wide range of conditions."
+We believe that the changes to the presentation of the Introduction and Results should also help to clarify this point further.
+(e.g., paragraph, lines 40-47, and more clearly highlighted conclusions on lines XXX).
+}
+\textcolor{red}{We also discuss the results of Kozielska and Ubeda more thoroughly in the paragraph...}
 
@@
 \textcolor{blue}{
-We are unsure of which paper the reviewer is referring to.
-Charlesworth 1978 PNAS 75:5618 discusses the degradation of the Y by Muller's ratchet and subsequent dosage compensation, which has little relevance here.
-Charlesworth and Charlesworth 1978 Am Nat 112:975-997 discuss the role of inbreeding in transitions from hermaphrodism (ie no sex-determining alleles) to the case of dioecy (with sex-determining alleles).
-Charlesworth and Charlesworth 1978 Heredity 41:137-153 is similar but begins with monoecy.
-Assuming the reviewer meant one of the latter two, both it and Ubeda et al 2015 consider the origin of genetic sex-determination from hermaphrodism/monoecy or environmental sex-determination. 
-Here we are much more concerned with transitions between genetic sex-determination systems.
-Further, we do not state that sex-antagonism is one of the predominant theories explaining SD transitions, it is but one example where fitness differs between the sexes, another example being ``sex-different drive".
-We discuss the fact that sex-specific drive can be thought of as a sex difference in selection in paragraph 5 of the introduction (see Response 3.2.6).
-We have rephrased slightly to restrict ourselves to transitions between GSD: ``Predominant theories accounting for transitions between GSD systems by selection involve fitness differences between sexes (e.g., sexually antagonistic selection) or sex-ratio selection...".}
+Charlesworth and Charlesworth 1978 (Am Nat and Heredity) discuss the role of inbreeding (and particularly inbreeding depression) in transitions from hermaphroditism to dioecy. 
+As noted on lines 468-472 (original submission), we have only considered GSD-GSD transitions and GSD-ESD transitions.
+For clarity, we have moved this description into the introduction (lines XXX). 
+In addition, where we draw a parallel between ESD and hermaphroditism on lines 451-455 XXX (revision), we now bring up the limitation that our model of ESD does not include inbreeding. }
+
+\textcolor{blue}{
+We have rephrased line referred to here as ``Predominant theories accounting for transitions between GSD systems by selection involve selective differences between sexes (e.g., sexually antagonistic selection) or sex-ratio selection.".
+We think this phrasing includes sex-differences in drive (Ubeda et al 2015) under the term 'selective difference between the sexes' (occurring during haploid rather than diploid selection), see also Response 3.2.6.
+}
+\textcolor{red}{Furthermore, we now discuss the Ubeda and Kozielska results, involving meiotic drive, thoroughly in paragraph...
+}
+
+%\textcolor{blue}{
+%We are unsure of which paper the reviewer is referring to.
+%Charlesworth 1978 PNAS 75:5618 discusses the degradation of the Y by Muller's ratchet and subsequent dosage compensation, which has little relevance here.
+%Charlesworth and Charlesworth 1978 Am Nat 112:975-997 discuss the role of inbreeding in transitions from hermaphrodism (ie no sex-determining alleles) to the case of dioecy (with sex-determining alleles).
+%Charlesworth and Charlesworth 1978 Heredity 41:137-153 is similar but begins with monoecy.
+%Assuming the reviewer meant one of the latter two, both it and Ubeda et al 2015 consider the origin of genetic sex-determination from hermaphrodism/monoecy or environmental sex-determination. 
+%Here we are much more concerned with transitions between genetic sex-determination systems.
+%Further, we do not state that sex-antagonism is one of the predominant theories explaining SD transitions, it is but one example where fitness differs between the sexes, another example being ``sex-different drive".
+%We discuss the fact that sex-specific drive can be thought of as a sex difference in selection in paragraph 5 of the introduction (see Response 3.2.6).
+%We have rephrased slightly to restrict ourselves to transitions between GSD: ``Predominant theories accounting for transitions between GSD systems by selection involve fitness differences between sexes (e.g., sexually antagonistic selection) or sex-ratio selection...".}
 
@@
 \noindent\paragraph{Response}
+\textcolor{red}{As we now make clear, we do not look at the same situation as Ubeda et al 2015 and our contribution is not just to add sex specific viability and analytical results. 
+For example, Ubeda starts from ESD. 
+Therefore, associations with an ancestral sex-determining locus cannot build up.
+These lead to some of our most surprising results (e.g., haploid selection favours trans-GSD transitions for a wider variety of genomic locations than diploid selection alone, non-invasion of ESD despite initial sex ratio bias).
+}
 \textcolor{blue}{It is true that Ubeda et al 2015 is a special case of our model. 
@@
 \textcolor{blue}{In the absence of sex-differences in selection it is true that antagonistic drive is not needed, but \textit{differences} in haploid selection between the sexes are needed (e.g., drive in only one sex, maintained by ploidally-antagonistic selection).
-If drive was the same in both sexes, $\alpha^{m}=\alpha^{f}$ (and all diploid male/female selection terms equal), then the new sex-determining allele would not invade. 
-In this sense haploid selection is indeed similar o sex-specific diploid selection, and together haploid and diploid selection determine the differences in male vs.
+If drive was the same in both sexes, $\alpha^{m}=\alpha^{f}$ (and all diploid male/female selection terms equal), we show that the new sex-determining allele would not invade. 
+In this sense haploid selection is similar to sex-specific diploid selection, and together haploid and diploid selection determine the differences in male vs.
 female fitness, which can drive sex-determination transitions (see Response 3.2.4).
-In this sentence, we are introducing the 'sex-specific' aspect of haploid selection in precisely the way Ubeda et al (2015) considers it; i.e., associations with alleles favoured in one sex (or the gametes produced by that sex) should favour a new sex-determining allele.
+In this sentence, we are introducing the 'sex-specific' aspect of haploid selection in the way Ubeda et al (2015) considers it; i.e., associations with alleles favoured in one sex (or the gametes produced by that sex) should favour a new sex-determining allele.
 We now follow this sentence up with two sentences that clarify its meaning by comparing with the results of Kozielska et al (2010) and Ubeda et al (2015).}

### 2018-03-27 LaTeX/main_revision.tex
reworking intro again (not completed)

@@
 In addition, multiple transitions have occurred between genetic and environmental sex-determining systems (GSD$\leftrightarrow$ESD), e.g., in reptiles and fishes~\cite{Conover:1987in,Mank:2006bt,Pokorna:2009ui,Ezaz:2009tk,Pen:2010kk,Holleley:2015hc}.
+In sum, accumulating evidence indicates that transitions between sex-determining systems are common~\cite{Bachtrog:2014bx}.
 
 %MAJOR MECHANISMS
-%(1) sex-antagonism
-Predominant theories accounting for transitions between GSD systems by selection involve fitness differences between sexes (e.g., sexually antagonistic selection) or sex-ratio selection~\cite{Blaser2012, Beukeboom:2014vb,vanDoorn2014re}.
+%(1) sex-ratio selection
+Predominant theories accounting for transitions between GSD systems by selection involve sex-ratio selection or fitness differences between sexes (e.g., sexually antagonistic selection)~\cite{Blaser2012, Beukeboom:2014vb,vanDoorn2014re}.
 %\citet{Bull:1977wt} shows that direct selection on new sex determination loci can allow them to spread and switch between male and female heterogamety. 
-van Doorn and Kirkpatrick~\cite{vanDoorn:2007eu,vanDoorn:2010hu} and Muralidhar and Veller~\cite{Muralidhar2018} have shown that new sex-determining alleles can be favoured if they arise at loci in close linkage with a locus that experiences sexual antagonism.
-Tighter linkage allows a stronger favourable association to build up between a male-beneficial allele, and a neo-Y allele, for example. 
-Such associations can favour cis-GSD transitions~\cite{vanDoorn:2007eu}, trans-GSD transitions~\cite{vanDoorn:2010hu}, and new partially-masculinizing or partially-feminizing alleles~\cite{Muralidhar2018}.
-However, any sexually-antagonistic loci that are more closely linked to the ancestral sex-determining locus will develop similar, favourable associations and are expected to hinder the spread of a new sex-determining system.
-
-%MAJOR MECHANISMS
-%(2) sex-ratio selection
-The sex ratio is directly determined by the sex-determining system, and it has therefore been suggested that sex-ratio selection is a dominant force in the evolution of sex determination (e.g., Bull, 1983, p 66-67 ~\cite{Bull:1983vi}; Buekeboom and Perrin, 2014, Chapter 7~\cite{Beukeboom:2014vb}).
 `Fisherian' sex-ratio selection favours a 1:1 zygotic sex ratio when assuming that males and females are equally costly to produce~\cite{Fisher:1930wy,Charnov:1982wg}.
@@
 Thus, if the sex ratio is biased, an individual of the rarer sex will, on average, contribute more genetic material to the next generation. 
-Selection therefore favours mutants that increase investment in the rarer sex.
+Selection therefore typically favours mutants that increase investment in the rarer sex.
+Because the sex ratio is directly determined by the sex-determining system, it has been suggested that sex-ratio selection is a particularly dominant force in the evolution of sex determination (e.g., Bull, 1983, p 66-67 ~\cite{Bull:1983vi}; Buekeboom and Perrin, 2014, Chapter 7~\cite{Beukeboom:2014vb}).
+
+%MAJOR MECHANISMS
+%(2) sex-antagonism
+New genetic sex-determining alleles have been shown to be favoured in they arise in close linkage with a locus that experiences sexual antagonism ~\cite{vanDoorn:2007eu,vanDoorn:2010hu,Muralidhar2018}.
+%van Doorn and Kirkpatrick~\cite{vanDoorn:2007eu,vanDoorn:2010hu} and Muralidhar and Veller~\cite{Muralidhar2018} have shown that new sex-determining alleles can be favoured if they arise at loci in close linkage with a locus that experiences sexual antagonism.
+Tighter linkage allows a stronger favourable association to build up between a male-beneficial allele, and a neo-Y allele, for example. 
+Such associations can favour cis-GSD transitions~\cite{vanDoorn:2007eu}, trans-GSD transitions~\cite{vanDoorn:2010hu}, and new partially-masculinizing or partially-feminizing alleles~\cite{Muralidhar2018}.
+However, any sexually-antagonistic loci that are more closely linked to the ancestral sex-determining locus will develop similar, favourable associations and are expected to hinder the spread of a new sex-determining system~\cite{vanDoorn:2007eu,vanDoorn:2010hu}.
+
+%Tight linkage Model Feature and Result
+One novel feature of the models developed here is that we explicitly \textcolor{red}{(is this wording fair to vD\&K?)} consider loci in very tight linkage with the ancestral sex-determining locus (e.g., within the non-recombining region of a sex chromosome).
+% in the results section: `Tight linkage with the ancestral sex-determining locus').
+Our analysis shows that, under various forms of selection, the ancestral-X can carry suboptimal alleles for females and/or the ancestral-Y can carry female-beneficial alleles. 
+This, in turn, can favour a new ZW sex-determining locus that has weaker linkage with loci under selection, which has not been predicted by previous theory. 
+That is, very tight linkage with the ancestral GSD locus can favour trans-GSD transitions in which associations with selected loci are actually weakened.
+
+%Haploid selection model feature and discussion of why needed
+Furthermore, we include haploid selection in models describing cis-GSD, trans-GSD, and GSD to ESD transitions. 
+Haploid selection (gametic competition or meiotic drive) is typically sex-specific in that it usually occurs among gametes produced by one sex only~\cite{Mulcahy:1996ha,JOSEPH:2004haa,Ubeda:2005gw,Lindholm:2016cw}.
+Therefore, one might expect new sex-determining systems to benefit from close linkage with haploid selected loci, as found for sex-specific diploid selection~\cite{vanDoorn:2007eu,vanDoorn:2010hu, Muralidhar2018}.
+On the other hand, associations between sex-determining loci and haploid selected loci generate biased zygotic sex ratios. 
+Nevertheless, numerical simulations by Ubeda et al.
+(2015)~\cite{Ubeda:2015fx} suggest that, starting from GSD, new masculinizing mutations (neo-Y alleles) spread via associations with alleles that are beneficial in the male haploid stage (e.g., \cite{Ubeda:2015fx}), leading to male-biased sex ratios.
+
+But Kozielska uses numerical simulations to show that ancestral sex ratio biases caused by haploid selection...
+
+%Here we use mathematical models to find the conditions under which new sex-determining systems spread when individuals experience selection at both diploid and haploid stages, which allows fitness differences between the sexes and sex ratio biases to occur simultaneously
+
+%Haploid selection results
+
+%The sex ratio is directly determined by the sex-determining system, and it has therefore been suggested that sex-ratio selection is a dominant force in the evolution of sex determination (e.g., Bull, 1983, p 66-67 ~\cite{Bull:1983vi}; Buekeboom and Perrin, 2014, Chapter 7~\cite{Beukeboom:2014vb}).
+%`Fisherian' sex-ratio selection favours a 1:1 zygotic sex ratio when assuming that males and females are equally costly to produce~\cite{Fisher:1930wy,Charnov:1982wg}.
+%This follows from the fact that, for an autosomal locus, half of the genetic material is inherited from a male and half from a female~\cite{West:2009we}. 
+%Thus, if the sex ratio is biased, an individual of the rarer sex will, on average, contribute more genetic material to the next generation. 
+%Selection therefore favours mutants that increase investment in the rarer sex.
+
 %The default mode of sex-ratio selection is `Fisherian' sex-ratio selection, which favours equal investment in male and female offspring \citep[i.e., a 1:1 zygotic sex ratio when assuming that males and females are equally costly to produce,][]{Fisher:1930wy,Charnov:1982wg}.
@@
 %(1) haploid selection; it exists in many spp
-While both opposing selection in the diploid sexes and sex-ratio selection surely influence the evolution of new sex-determining factors, so too might selection in the haploid phase.
+%While both opposing selection in the diploid sexes and sex-ratio selection surely influence the evolution of new sex-determining factors, so too might selection in the haploid phase.
+\textcolor{red}{move to discussion somewhere:
 Even in animal and plant species that have much larger and more conspicuous diploid phases than haploid phases, many loci experience significant haploid selection through gamete competition and/or meiotic drive~\cite{Mulcahy:1996ha,JOSEPH:2004haa}.
+}
+
+\textcolor{red}{move to results somewhere:
 We use the term `meiotic drive' to refer to the biased (non-Mendelian) segregation of genotypes during gamete production (from one parent only) and the term `gametic competition' to refer to selection upon haploid genotypes within a gamete/gametophyte pool (from many parents); the term `haploid selection' encompasses both processes.
+}
+
+\textcolor{red}{move to discussion somewhere:
 Segregation distortion provides putative evidence of haploid selection and can sometimes be attributed to meiotic drive and/or gametic competition~\cite{Lalanne2004,Fishman2005,Leppala2008,Leppala2013,Didion2015,Didion2016}.
@@
 Nevertheless, recent studies have demonstrated that sperm competition in animals, even within a single ejaculate, can alter haploid allele frequencies and increase offspring fitness~\cite{Immler:2014im,Alavioon2017}.
+}
 
@@
 
-` 
 We consider both selected loci that are loosely linked to the sex-determining region (e.g., on an autosome) and selected loci that are in very tight linkage with the ancestral sex-determining locus (e.g., within the non-recombining sex-determining region).
@@
 %Our predictions could also be examined using a suitable proxy for haploid selection, for example, \cite{Lenormand:2005vb} use the outcrossing rate in plants as a proxy for the strength of pollen competition.
-Assuming that transitions from dioecy to hermaphroditism (equal parental investment in male and female gametes) are favoured in a similar manner to the ESD examined here (equal probability of zygotes developing as males or females), our results suggest that competition during the haploid stage could also drive transitions between dioecy and hermaphroditism, which are frequent in plants~\cite{Kafer2017, Goldberg2017}.
+Assuming that transitions from dioecy to hermaphroditism (equal parental investment in male and female gametes) are favoured in a similar manner to the ESD examined here (equal probability of zygotes developing as males or females), our results suggest that competition among haploid pollen could drive transitions between dioecy and hermaphroditism, which are frequent in plants~\cite{Kafer2017, Goldberg2017}.
+To further examine this link, future investigations could examine the combined effects of haploid pollen competition, selfing, and inbreeding depression in allowing transitions between dioecy and hermaphroditism.
 

### 2018-03-28 LaTeX/main_revision.tex
finished editing intro, added more complete discussion of Kozielska and Ubeda

@@
 %Haploid selection model feature and discussion of why needed
-Furthermore, we include haploid selection in models describing cis-GSD, trans-GSD, and GSD to ESD transitions. 
-Haploid selection (gametic competition or meiotic drive) is typically sex-specific in that it usually occurs among gametes produced by one sex only~\cite{Mulcahy:1996ha,JOSEPH:2004haa,Ubeda:2005gw,Lindholm:2016cw}.
-Therefore, one might expect new sex-determining systems to benefit from close linkage with haploid selected loci, as found for sex-specific diploid selection~\cite{vanDoorn:2007eu,vanDoorn:2010hu, Muralidhar2018}.
-On the other hand, associations between sex-determining loci and haploid selected loci generate biased zygotic sex ratios. 
-Nevertheless, numerical simulations by Ubeda et al.
-(2015)~\cite{Ubeda:2015fx} suggest that, starting from GSD, new masculinizing mutations (neo-Y alleles) spread via associations with alleles that are beneficial in the male haploid stage (e.g., \cite{Ubeda:2015fx}), leading to male-biased sex ratios.
-
-But Kozielska uses numerical simulations to show that ancestral sex ratio biases caused by haploid selection...
+Most significantly, we include haploid selection (gametic competition or meiotic drive) in models describing cis-GSD, trans-GSD, and GSD to ESD transitions, which poses an apparent evolutionary problem.
+On one hand, haploid selection is typically sex-specific in that it usually occurs among gametes produced by one sex only~\cite{Mulcahy:1996ha,JOSEPH:2004haa,Ubeda:2005gw,Lindholm:2016cw}. 
+Therefore, one might expect new sex-determining systems to benefit from close linkage with haploid selected loci, as found for sex-differences in diploid selection~\cite{vanDoorn:2007eu,vanDoorn:2010hu, Muralidhar2018}.
+On the other hand, associations between sex-determining loci and haploid selected loci generate biased zygotic sex ratios, which should generally hinder the spread of new sex-determining systems.
+
+%Previous models with haploid selection
+Two previous numerical simulation studies have considered the spread of GSD with sex-specific meiotic drive~\cite{Kozielska:2010vm,Ubeda:2015fx} under a small number of possible genetic architectures and diploid selective regimes.
+Ubeda et al. (2015)~\cite{Ubeda:2015fx}, considers ancestral-ESD (with no sex ratio bias) and find that new GSD alleles can spread if they arise in linkage with meiotic drive loci. 
+For example, a masculinizing allele spreads in association with an allele that is favoured during male meiosis, causing sex ratios to become male-biased and thereby suggesting that such beneficial associations overwhelm selection to balance the sex ratio.
+However, Kozielska et al. (2010)~\cite{Kozielska:2010vm} consider meiotic drive on an ancestral GSD sex chromosome (creating a sex ratio bias). 
+They find that new, unlinked, GSD systems can spread if they generate the rarer sex, creating a balanced sex ratio. 
+That is, they conclude that Fisherian sex ratio selection caused by haploid selection favours new GSD systems. 
+Here, we analytically find conditions under which new GSD or ESD systems spread with generic linkage between the loci involved (and generic sex-specific haploid and diploid selection).
+
+%main results
+Strikingly, we reconcile the results of Kozielska et al.
+(2010)~\cite{Kozielska:2010vm} and Ubeda et al.
+(2015)~\cite{Ubeda:2015fx} by showing that new GSD systems commonly spread when they increase \textit{or} decrease linkage with loci that experience haploid selection.
+This result is qualitatively distinct from those for diploid selection alone~\cite{vanDoorn:2007eu,vanDoorn:2010hu} and suggests that haploid selection is more likely to promote transitions between sex-determination systems.
+However, we also show that transitions involving haploid selection cannot be simply explained by invoking sex ratio selection. 
+In particular, under a wide range of conditions, we show that haploid selection drives transitions in sex-determining system \textit{equally strongly} whether sex-ratio biases increase or decrease (and whether sex-ratio biases are present or absent).
+Finally, we show that ESD may not evolve, even if the sex-ratio is initially biased by haploid selection, which would not be predicted by previous theories for transitions to ESD~\cite{Charnov:1982wg,Bull:1983vi,West:2009we}.
 
@@
 %(2) haploid selection; it can complicate outcomes for SD transitions
-There are various ways by which haploid selection could influence transitions between sex-determining systems. 
-If we assume that haploid selection at any particular locus predominantly occurs in one sex (e.g., meiotic drive during spermatogenesis), then such loci experience a form of sex-specific selection. 
-In this respect, we might expect that haploid selection would affect transitions between sex-determining systems in a similar manner to sex-specific diploid selection (as explored in~\cite{vanDoorn:2007eu,vanDoorn:2010hu}).
-That is, new masculinizing mutations (neo-Y alleles) could be favoured via associations with alleles that are beneficial in the male haploid stage (e.g., \cite{Ubeda:2015fx}). 
-Kozielska et al.
+%There are various ways by which haploid selection could influence transitions between sex-determining systems. 
+%If we assume that haploid selection at any particular locus predominantly occurs in one sex (e.g., meiotic drive during spermatogenesis), then such loci experience a form of sex-specific selection. 
+%In this respect, we might expect that haploid selection would affect transitions between sex-determining systems in a similar manner to sex-specific diploid selection (as explored in~\cite{vanDoorn:2007eu,vanDoorn:2010hu}).
+%That is, new masculinizing mutations (neo-Y alleles) could be favoured via associations with alleles that are beneficial in the male haploid stage (e.g., \cite{Ubeda:2015fx}). 
+%Kozielska et al.
 (2010)~\cite{Kozielska:2010vm} have shown this to be theoretically possible for the special case of perfect linkage between the new sex-determining locus and a locus that experiences meiotic drive in one sex, under a limited number of forms of diploid selection.
-Similarly, Ubeda et al.
+%Similarly, Ubeda et al.
 (2015)~\cite{Ubeda:2015fx} numerically show that sex-specific meiotic drive can allow masculinizing and feminizing mutations to spread in an ancestrally environmental-sex-determination system, again under a limited number of forms of diploid selection.
-On the other hand, sex ratios can also become biased by linkage between the sex-determining locus and a locus that harbours genetic variation in haploid fitness, as indeed occurs in the two examples above.
-There are also several known empirical cases of sex-ratio bias caused by sex-linked meiotic drive alleles (Burt and Trivers, 2006, Chapter 6~\cite{Burt:2006}) or selection among X- and Y-bearing pollen~\cite{Lloyd:1974tz,Conn:1981uw,Stehlik:2005ul,Stehlik:2006to,Field:2012fd,Field:2013cc}.
-Sex-ratio selection can thus select against the spread of linked sex-determining alleles and favour the invasion of alternative, unlinked sex-determination systems \cite{Kozielska:2010vm,Ubeda:2015fx}.
-%It is not immediately clear how the spread of new sex-determining systems would be influenced by the combination of sex-ratio biases and associations with haploid selected alleles. 
-It is not yet clear when new sex-determining alleles are favoured by associations with haploid selected alleles vs.
+%On the other hand, sex ratios can also become biased by linkage between the sex-determining locus and a locus that harbours genetic variation in haploid fitness, as indeed occurs in the two examples above.
+%There are also several known empirical cases of sex-ratio bias caused by sex-linked meiotic drive alleles (Burt and Trivers, 2006, Chapter 6~\cite{Burt:2006}) or selection among X- and Y-bearing pollen~\cite{Lloyd:1974tz,Conn:1981uw,Stehlik:2005ul,Stehlik:2006to,Field:2012fd,Field:2013cc}.
+%Sex-ratio selection can thus select against the spread of linked sex-determining alleles and favour the invasion of alternative, unlinked sex-determination systems \cite{Kozielska:2010vm,Ubeda:2015fx}.
+%It is not yet clear when new sex-determining alleles are favoured by associations with haploid selected alleles vs.
 sex-ratio bias, especially under a wide range of possible diploid selection regimes (e.g., sex-antagonism, overdominance).
 
-We consider both selected loci that are loosely linked to the sex-determining region (e.g., on an autosome) and selected loci that are in very tight linkage with the ancestral sex-determining locus (e.g., within the non-recombining sex-determining region).
-Our main findings are three:
-(1) transitions between sex-determining systems can decrease or increase sex-ratio bias, and with sufficiently loose linkage between the selected locus and the sex-determining locus, the selective force exerted by sex-ratio selection and favourable associations with haploid-selected alleles are exactly equivalent;
-(2) ancestrally-tight sex-linkage and haploid selection allow trans-GSD transitions that weaken sex-linkage; and
-(3) haploid selection removes the need for sex-antagonism, increasing the range of scenarios that select for transitions between sex-determining systems.
+%We consider both selected loci that are loosely linked to the sex-determining region (e.g., on an autosome) and selected loci that are in very tight linkage with the ancestral sex-determining locus (e.g., within the non-recombining sex-determining region).
+%Our main findings are three:
+%(1) transitions between sex-determining systems can decrease or increase sex-ratio bias, and with sufficiently loose linkage between the selected locus and the sex-determining locus, the selective force exerted by sex-ratio selection and favourable associations with haploid-selected alleles are exactly equivalent;
+%(2) ancestrally-tight sex-linkage and haploid selection allow trans-GSD transitions that weaken sex-linkage; and
+%(3) haploid selection removes the need for sex-antagonism, increasing the range of scenarios that select for transitions between sex-determining systems.
+
 %MAIN FINDINGS IN GENERAL TERMS
@@
 
+\textcolor{red}{Discussion of `epistatic dominance' assumption to go here somewhere?
+The model in the Mathematica file is actual general to this assumption I think (or at least we wrote one that is), which we could mention in the response.}
+
 The evolution of a new sex-determining system requires that a rare mutant allele, $m$, at the novel sex-determining locus, $\mathbf{M}$, increases in frequency when rare. 
@@
 \textcolor{red}{It should be noted, however, that the dynamics of sex-determining alleles with very weak effect will be influenced by genetic drift, which itself has been shown to cause trans-GSD transitions \cite{Veller2017}}.
-Finally, while we have considered cis-GSD, trans-GSD, and GSD to ESD transitions, we have not explicitly considered ESD to GSD transitions. 
-Recent models of ESD to GSD transitions~\cite{Ubeda:2015fx,Muralidhar2018} show that that neo-Y/neo-W alleles can be favoured when they arise near to haploid and/or diploid selected loci, which also occurs in our model.
 

### 2018-03-28 LaTeX/response.tex
refining conclusions and reviewer 2 responses

@@
 \noindent  Line numbers (L\#) in authors' comments refer to those in the revised PDF.
+\\
+
+\noindent See diff.pdf for highlighted differences between the original submission and the revised version.
 
@@
 \noindent\paragraph{Response}
-\textcolor{red}{We could call it the ``haplotypic recombination rate" near L153, but I'm not sure how much we will use this term in the text.}
+\textcolor{blue}{We now call these terms the ``dissociative force" as they break down linkage disequilibrium (L162).}
 
@@
 \noindent\paragraph{Response}
-\textcolor{red}{We could first mention that the model is deterministic, and hence ignores drift, near L131.
-As for the role of drift in transitions, we could certainly elaborate on the Veller et al 2017 Genetics paper that discusses how ``drift-induced selection" causes trans-GSD transitions.
-I've put a possible sentence in near L482: ``It should be noted, however, that the dynamics of sex-determining alleles with very weak effect will be influenced by genetic drift, which itself has been shown to cause trans-GSD transitions (Veller et al 2017)."}
+\textcolor{blue}{We now mention that the model is deterministic, and hence ignores drift (L136). 
+We later mention that drift can in fact be a key factor in transitions: ``It should be noted, however, that the dynamics of sex-determining alleles with very weak effect will be influenced by genetic drift, which itself has been shown to cause trans-GSD transitions (Veller et al 2017)." (L511)}
 
@@
 \textcolor{blue}{We have made the suggested replacements.
-There are two exceptions.
-In the abstract we use sperm competition as an example of gametic competition, but we now state that this would involve multiple males.
-In the introduction we mention that sperm competition has been shown to alter allele frequencies and fitness, and in this case we now mention this was shown within a single ejaculate (L68).}
+There is one exception.
+In the abstract we use the familiar term ``sperm competition" as an example of gametic competition, but we now explicitly state that we imply sperm from multiple males.
+%n the introduction we mention that sperm competition has been shown to alter allele frequencies and fitness, and in this case we now mention this was shown within a single ejaculate (L68).
+}
 
@@
 \noindent\paragraph{Response}
-\textcolor{blue}{The introduction is now arranged as follows.
-The first paragraph discusses how common transitions are.
-The second and third paragraphs discuss the two major mechanisms currently hypothesized to drive the observed transitions, respectively.
-The fourth paragraph introduces haploid selection and the fifth talks about its potential implications for transitions, motivating our model.
-The final, sixth, paragraph briefly mentions our main findings.}
+\textcolor{blue}{
+The introduction has been simplified to be as follows.
+The first paragraph discusses how common transitions are (context). 
+The second and third paragraphs discuss the two major mechanisms currently hypothesized to drive the observed transitions, respectively (current theory). 
+The fourth paragraph explains how assuming ancestrally-tight sex-linkage produces previously unexpected transitions (one hole in current theory, and how we address it).
+The fifth paragraph discusses the potential complications of haploid selection for transitions (another hole in current theory).
+The sixth paragraph describes previous studies on transitions with haploid selection (attempts to address the second hole). 
+The final, seventh, paragraph states how our approach differs from previous attempts and the major findings we uncover (how we address the second hole).  
+}
 
@@
 \noindent\paragraph{Response}
-\textcolor{blue}{We now give these 3 main conclusions at the end of the introduction. Further, in the results we now also highlight 5 conclusions in the style of Orr 1998.}
+\textcolor{blue}{
+We now give 3 main conclusions at the end of the introduction (L69) which echo those mentioned by the reviewer (looser linkage can evolve, equal selection to increase or decrease the sex ratio, ESD does not always invade biased sex ratio; all of which suggest haploid selection makes conditions for transitions more permissive).
+These are highlighted again in the results, in the style of Orr 1998:\\
+%(1) transitions are determined by both sex-ratio selection and selection on associated alleles,\\
+%(2) cis- and trans-GSD transitions are qualitatively different,\\
+(1A) ancestrally-tight sex-linkage allows looser sex-linkage to evolve in trans-GSD transitions (with or without haploid selection),\\
+(1B) haploid selection allows looser sex-linkage to evolve in trans-GSD transitions,\\
+(2) when selection is weak relative to recombination, sex-ratio selection is exactly equal in magnitude to the selection imposed by associations with selected alleles, and\\
+(3) transitions from genetic to environmental sex-determination are not straightforwardly predicted by selection to balance the zygotic sex ratio when haploid selection is present.
+\vspace{0.25cm}\\
+These are all new results, although (1A) was shown for the special case of $r=0$, $R=1/2$, and ploidally-antagonistic selection in Kozielska et al 2010, which we now mention immediately below (1A). 
+}
 
@@
 \textcolor{blue}{We have rearranged and rewritten the introduction to better motivate our model (see Response 2.1).
-In particular, paragraph 5 explains how the effect of haploid selection on SD transitions is unclear.}
+In particular, paragraphs 6 and 7 explain the previous attempts and our approach, respectively.}
 
@@
 \noindent\paragraph{Response}
-\textcolor{blue}{We have rewritten the main conclusions to be those three suggested in 2.2 (see Response 2.2).}
+\textcolor{blue}{We have rewritten the main conclusions (see Response 2.2).}
 
@@
 The drift-transitions Genetics paper rests on the difference in dominance, I'm pretty sure they have examples and the majority of new GSD systems are epistatically dominant.
-Also vD\&K 2010.
+Also vD\&K 2010 say that there is evidence that epistatic dominance is common, and explain why a completely recessive should not invade.
 }

### 2018-03-28 LaTeX/S1Appendix_revised.tex
refining conclusions and reviewer 2 responses

--- 2018-02-07 LaTeX/S1Appendix.tex
@@
 % amsmath and amssymb packages, useful for mathematical formulas and symbols
-\usepackage{amsmath,amssymb}
+\usepackage{amsmath} %amssymb
 
@@
 \usepackage{xr}
-\externaldocument{main}
-\externaldocument{S2Appendix}
-\externaldocument{S3Appendix}
+\externaldocument{main_revised}
+\externaldocument{S2Appendix_revised}
+\externaldocument{S3Appendix_revised}
 
@@
 In each generation we census the genotype frequencies in male and female gametes/gametophytes (hereafter, gametes) between meiosis (and any meiotic drive) and gametic competition. 
-At this stage we denote the frequencies of X- and Y-bearing gametes from males and females $x_{i}^{\Hermaphrodite}$ and $y_{i}^{\Hermaphrodite}$.
-The superscript $\Hermaphrodite \in \{\male,\female\}$ specifies the sex of the diploid that the gamete came from. 
+At this stage we denote the frequencies of X- and Y-bearing gametes from males and females $x_{i}^{\circ}$ and $y_{i}^{\circ}$.
+The superscript $\circ \in \{\male,\female\}$ specifies the sex of the diploid that the gamete came from. 
 The subscript $i\in\{1,2,3,4\}$ specifies the genotype at the selected locus $\mathbf{A}$ and at the novel sex-determining locus $\mathbf{M}$, where $1=AM$, $2=aM$, $3=Am$, and $4=am$. 
-The gamete frequencies from each sex sum to one, $\sum_{i}x_{i}^{\Hermaphrodite}+y_{i}^{\Hermaphrodite}=1$.
+The gamete frequencies from each sex sum to one, $\sum_{i}x_{i}^{\circ}+y_{i}^{\circ}=1$.
 
-Competition then occurs among gametes of the same sex (e.g., among eggs and among sperm separately) according to the genotype at the $\mathbf{A}$ locus ($w_{1}^\Hermaphrodite=w_{3}^\Hermaphrodite=w_{A}^\Hermaphrodite$, $w_{2}^\Hermaphrodite=w_{4}^\Hermaphrodite=w_{a}^\Hermaphrodite$, see Table \ref{tab:fitnesstable}).
-The genotype frequencies after gametic competition are $x_{i}^{\Hermaphrodite,s}= w_{i}^{\Hermaphrodite}x_{i}^{\Hermaphrodite}/\bar{w}_{H}^{\Hermaphrodite}$ and $y_{i}^{\Hermaphrodite,s}= w_{i}^{\Hermaphrodite}y_{i}^{\Hermaphrodite}/\bar{w}_{H}^{\Hermaphrodite}$, where $\bar{w}_{H}^{\Hermaphrodite}=\sum_{i} w_{i}^{\Hermaphrodite}x_{i}^{\Hermaphrodite}+w_{i}^{\Hermaphrodite}y_{i}^{\Hermaphrodite}$ is the mean fitness of male ($\Hermaphrodite=\male$) or female ($\Hermaphrodite=\female$) gametes.
+Competition then occurs among gametes of the same sex (e.g., among eggs and among sperm separately) according to the genotype at the $\mathbf{A}$ locus ($w_{1}^\circ=w_{3}^\circ=w_{A}^\circ$, $w_{2}^\circ=w_{4}^\circ=w_{a}^\circ$, see Table \ref{tab:fitnesstable}).
+The genotype frequencies after gametic competition are $x_{i}^{\circ,s}= w_{i}^{\circ}x_{i}^{\circ}/\bar{w}_{H}^{\circ}$ and $y_{i}^{\circ,s}= w_{i}^{\circ}y_{i}^{\circ}/\bar{w}_{H}^{\circ}$, where $\bar{w}_{H}^{\circ}=\sum_{i} w_{i}^{\circ}x_{i}^{\circ}+w_{i}^{\circ}y_{i}^{\circ}$ is the mean fitness of male ($\circ=\male$) or female ($\circ=\female$) gametes.
 
@@
 Selection among diploids then occurs according to the diploid genotype at the $\mathbf{A}$ locus, $l \in \{AA, Aa, aa\}$, for an individual of type $ij$ (see Table \ref{tab:fitnesstable}). 
-The diploid frequencies after selection in sex $\Hermaphrodite$ are given by $xx_{ij}^{\Hermaphrodite,s}=w_{l}^{\Hermaphrodite} xx_{ij}/\bar{w}^{\Hermaphrodite}_{D}$, $xy_{ij}^{\Hermaphrodite,s}=w_{l}^{\Hermaphrodite} xy_{ij}/\bar{w}^{\Hermaphrodite}_{D}$, and $yy_{ij}^{\Hermaphrodite,s}=w_{l}^{\Hermaphrodite} yy_{ij}/\bar{w}^{\Hermaphrodite}_{D}$, where $\bar{w}^{\Hermaphrodite}_{D}= \sum_{i=1}^{4}\sum_{j=1}^{4}w_{l}^{\Hermaphrodite}xx_{ij}+w_{l}^{\Hermaphrodite}xy_{ij}+w_{l}^{\Hermaphrodite}yy_{ij}$ is the mean fitness of diploids of sex $\Hermaphrodite$.
+The diploid frequencies after selection in sex $\circ$ are given by $xx_{ij}^{\circ,s}=w_{l}^{\circ} xx_{ij}/\bar{w}^{\circ}_{D}$, $xy_{ij}^{\circ,s}=w_{l}^{\circ} xy_{ij}/\bar{w}^{\circ}_{D}$, and $yy_{ij}^{\circ,s}=w_{l}^{\circ} yy_{ij}/\bar{w}^{\circ}_{D}$, where $\bar{w}^{\circ}_{D}= \sum_{i=1}^{4}\sum_{j=1}^{4}w_{l}^{\circ}xx_{ij}+w_{l}^{\circ}xy_{ij}+w_{l}^{\circ}yy_{ij}$ is the mean fitness of diploids of sex $\circ$.
 
@@
 \nameref{tab:chisubstitutions} shows replacements that can be made for each possible ordering of the loci assuming that there is no cross-over interference.
-During meiosis in sex $\Hermaphrodite$, meiotic drive occurs such that, in $Aa$ heterozygotes, a fraction $\alpha^{\Hermaphrodite}$ of gametes produced carry the $A$ allele and $(1-\alpha^\Hermaphrodite)$ carry the $a$ allele.
+During meiosis in sex $\circ$, meiotic drive occurs such that, in $Aa$ heterozygotes, a fraction $\alpha^{\circ}$ of gametes produced carry the $A$ allele and $(1-\alpha^\circ)$ carry the $a$ allele.
 
-Among gametes from sex $\Hermaphrodite$, the frequencies of haplotypes (before gametic competition) in the next generation are given by
+Among gametes from sex $\circ$, the frequencies of haplotypes (before gametic competition) in the next generation are given by
 
@@
 \begin{split}
-x_{1}^{{\Hermaphrodite}'}=&xx_{11}^{\Hermaphrodite,s}+xx_{13}^{\Hermaphrodite,s}/2+(xx_{12}^{\Hermaphrodite,s}+xx_{14}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(xx_{14}^{\Hermaphrodite,s}-xx_{23}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&+(xy_{11}^{\Hermaphrodite,s}+xy_{13}^{\Hermaphrodite,s})/2+(xy_{12}^{\Hermaphrodite,s}+xy_{14}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&- r(xy_{12}^{\Hermaphrodite,s}-xy_{21}^{\Hermaphrodite,s})\alpha^\Hermaphrodite - \rho(xy_{13}^{\Hermaphrodite,s}-xy_{31}^{\Hermaphrodite,s})/2\\
-&+\big{[}-(R+r+\rho)xy_{14}^{\Hermaphrodite,s} +(R+\rho-r)xy_{41}^{\Hermaphrodite,s}\\
-&+(R+r-\rho) xy_{23}^{\Hermaphrodite,s}+(R+\rho-r)xy_{32}^{\Hermaphrodite,s}\big{]}\alpha^\Hermaphrodite/2
+x_{1}^{{\circ}'}=&xx_{11}^{\circ,s}+xx_{13}^{\circ,s}/2+(xx_{12}^{\circ,s}+xx_{14}^{\circ,s})\alpha^\circ\\
+&-R(xx_{14}^{\circ,s}-xx_{23}^{\circ,s}) \alpha^\circ\\
+&+(xy_{11}^{\circ,s}+xy_{13}^{\circ,s})/2+(xy_{12}^{\circ,s}+xy_{14}^{\circ,s})\alpha^\circ\\
+&- r(xy_{12}^{\circ,s}-xy_{21}^{\circ,s})\alpha^\circ - \rho(xy_{13}^{\circ,s}-xy_{31}^{\circ,s})/2\\
+&+\big{[}-(R+r+\rho)xy_{14}^{\circ,s} +(R+\rho-r)xy_{41}^{\circ,s}\\
+&+(R+r-\rho) xy_{23}^{\circ,s}+(R+\rho-r)xy_{32}^{\circ,s}\big{]}\alpha^\circ/2
 \end{split}
@@
 \begin{split}
-x_{2}^{{\Hermaphrodite}'}=&xx_{22}^{\Hermaphrodite,s}+xx_{24}^{\Hermaphrodite,s}/2+(xx_{12}^{\Hermaphrodite,s}+xx_{23}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(xx_{23}^{\Hermaphrodite,s}-xx_{14}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&(xy_{22}^{\Hermaphrodite,s}+xy_{24}^{\Hermaphrodite,s})/2+(xy_{21}^{\Hermaphrodite,s}+xy_{23}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite)\\
-&- r(xy_{21}^{\Hermaphrodite,s}-xy_{12}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite) - \rho(xy_{24}^{\Hermaphrodite,s}-xy_{42}^{\Hermaphrodite,s})/2\\
-&+\big{[}-(R+r+\rho)xy_{23}^{\Hermaphrodite,s}+(R+\rho-r)xy_{32}^{\Hermaphrodite,s}\\
-&+(R+r-\rho) xy_{14}^{\Hermaphrodite,s}+(R+\rho-r)xy_{41}^{\Hermaphrodite,s}\big{]}(1-\alpha^\Hermaphrodite)/2
+x_{2}^{{\circ}'}=&xx_{22}^{\circ,s}+xx_{24}^{\circ,s}/2+(xx_{12}^{\circ,s}+xx_{23}^{\circ,s})\alpha^\circ\\
+&-R(xx_{23}^{\circ,s}-xx_{14}^{\circ,s}) \alpha^\circ\\
+&(xy_{22}^{\circ,s}+xy_{24}^{\circ,s})/2+(xy_{21}^{\circ,s}+xy_{23}^{\circ,s})(1-\alpha^\circ)\\
+&- r(xy_{21}^{\circ,s}-xy_{12}^{\circ,s})(1-\alpha^\circ) - \rho(xy_{24}^{\circ,s}-xy_{42}^{\circ,s})/2\\
+&+\big{[}-(R+r+\rho)xy_{23}^{\circ,s}+(R+\rho-r)xy_{32}^{\circ,s}\\
+&+(R+r-\rho) xy_{14}^{\circ,s}+(R+\rho-r)xy_{41}^{\circ,s}\big{]}(1-\alpha^\circ)/2
 \end{split}
@@
 \begin{split}
-x_{3}^{{\Hermaphrodite}'}=&xx_{33}^{\Hermaphrodite,s}+xx_{13}^{\Hermaphrodite,s}/2+(xx_{23}^{\Hermaphrodite,s}+xx_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(xx_{23}^{\Hermaphrodite,s}-xx_{14}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&(xy_{33}^{\Hermaphrodite,s}+xy_{31}^{\Hermaphrodite,s})/2+(xy_{32}^{\Hermaphrodite,s}+xy_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&- r(xy_{34}^{\Hermaphrodite,s}-xy_{43}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite - \rho(xy_{31}^{\Hermaphrodite,s}-xy_{13}^{\Hermaphrodite,s})/2\\
-&+\big{[}-(R+r+\rho)xy_{32}^{\Hermaphrodite,s} +(R+\rho-r)xy_{23}^{\Hermaphrodite,s}\\
-&+(R+r-\rho) xy_{41}^{\Hermaphrodite,s}+(R+\rho-r)xy_{14}^{\Hermaphrodite,s}\big{]} \alpha^\Hermaphrodite/2
+x_{3}^{{\circ}'}=&xx_{33}^{\circ,s}+xx_{13}^{\circ,s}/2+(xx_{23}^{\circ,s}+xx_{34}^{\circ,s})\alpha^\circ\\
+&-R(xx_{23}^{\circ,s}-xx_{14}^{\circ,s}) \alpha^\circ\\
+&(xy_{33}^{\circ,s}+xy_{31}^{\circ,s})/2+(xy_{32}^{\circ,s}+xy_{34}^{\circ,s})\alpha^\circ\\
+&- r(xy_{34}^{\circ,s}-xy_{43}^{\circ,s}) \alpha^\circ - \rho(xy_{31}^{\circ,s}-xy_{13}^{\circ,s})/2\\
+&+\big{[}-(R+r+\rho)xy_{32}^{\circ,s} +(R+\rho-r)xy_{23}^{\circ,s}\\
+&+(R+r-\rho) xy_{41}^{\circ,s}+(R+\rho-r)xy_{14}^{\circ,s}\big{]} \alpha^\circ/2
 \end{split}
@@
 \begin{split}
-x_{4}^{{\Hermaphrodite}'}=&xx_{44}^{\Hermaphrodite,s}+xx_{34}^{\Hermaphrodite,s}/2+(xx_{14}^{\Hermaphrodite,s}+xx_{24}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(xx_{14}^{\Hermaphrodite,s}-xx_{23}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&(xy_{44}^{\Hermaphrodite,s}+xy_{42}^{\Hermaphrodite,s})/2+(xy_{41}^{\Hermaphrodite,s}+xy_{43}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite)\\
-&- r(xy_{43}^{\Hermaphrodite,s}-xy_{34}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite) - \rho(xy_{42}^{\Hermaphrodite,s}-xy_{24}^{\Hermaphrodite,s})/2\\
-&+\big{[}-(R+r+\rho)xy_{41}^{\Hermaphrodite,s}+(R+\rho-r)xy_{14}^{\Hermaphrodite,s}\\
-&+(R+r-\rho) xy_{32}^{\Hermaphrodite,s}+(R+\rho-r)xy_{23}^{\Hermaphrodite,s}\big{]}(1-\alpha^\Hermaphrodite)/2
+x_{4}^{{\circ}'}=&xx_{44}^{\circ,s}+xx_{34}^{\circ,s}/2+(xx_{14}^{\circ,s}+xx_{24}^{\circ,s})\alpha^\circ\\
+&-R(xx_{14}^{\circ,s}-xx_{23}^{\circ,s}) \alpha^\circ\\
+&(xy_{44}^{\circ,s}+xy_{42}^{\circ,s})/2+(xy_{41}^{\circ,s}+xy_{43}^{\circ,s})(1-\alpha^\circ)\\
+&- r(xy_{43}^{\circ,s}-xy_{34}^{\circ,s})(1-\alpha^\circ) - \rho(xy_{42}^{\circ,s}-xy_{24}^{\circ,s})/2\\
+&+\big{[}-(R+r+\rho)xy_{41}^{\circ,s}+(R+\rho-r)xy_{14}^{\circ,s}\\
+&+(R+r-\rho) xy_{32}^{\circ,s}+(R+\rho-r)xy_{23}^{\circ,s}\big{]}(1-\alpha^\circ)/2
 \end{split}
@@
 \begin{split}
-y_{1}^{{\Hermaphrodite}'}=&yy_{11}^{\Hermaphrodite,s}+yy_{13}^{\Hermaphrodite,s}/2+(yy_{12}^{\Hermaphrodite,s}+yy_{14}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(yy_{14}^{\Hermaphrodite,s}-yy_{23}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&(xy_{11}^{\Hermaphrodite,s}+xy_{31}^{\Hermaphrodite,s})/2+(xy_{21}^{\Hermaphrodite,s}+xy_{41}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&- r(xy_{21}^{\Hermaphrodite,s}-xy_{12}^{\Hermaphrodite,s})\alpha^\Hermaphrodite - \rho(xy_{31}^{\Hermaphrodite,s}-xy_{13}^{\Hermaphrodite,s})/2\\
-&+\big{[} - (R+r+\rho)xy_{41}^{\Hermaphrodite,s} + (R+\rho-r)xy_{14}^{\Hermaphrodite,s}\\
-& + (R+r-\rho)xy_{32}^{\Hermaphrodite,s} + (R+\rho-r) xy_{23}^{\Hermaphrodite,s}\big{]}\alpha^\Hermaphrodite/2
+y_{1}^{{\circ}'}=&yy_{11}^{\circ,s}+yy_{13}^{\circ,s}/2+(yy_{12}^{\circ,s}+yy_{14}^{\circ,s})\alpha^\circ\\
+&-R(yy_{14}^{\circ,s}-yy_{23}^{\circ,s}) \alpha^\circ\\
+&(xy_{11}^{\circ,s}+xy_{31}^{\circ,s})/2+(xy_{21}^{\circ,s}+xy_{41}^{\circ,s})\alpha^\circ\\
+&- r(xy_{21}^{\circ,s}-xy_{12}^{\circ,s})\alpha^\circ - \rho(xy_{31}^{\circ,s}-xy_{13}^{\circ,s})/2\\
+&+\big{[} - (R+r+\rho)xy_{41}^{\circ,s} + (R+\rho-r)xy_{14}^{\circ,s}\\
+& + (R+r-\rho)xy_{32}^{\circ,s} + (R+\rho-r) xy_{23}^{\circ,s}\big{]}\alpha^\circ/2
 \end{split}
@@
 \begin{split}
-y_{2}^{{\Hermaphrodite}'}=&yy_{22}^{\Hermaphrodite,s}+yy_{24}^{\Hermaphrodite,s}/2+(yy_{12}^{\Hermaphrodite,s}+yy_{23}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(yy_{23}^{\Hermaphrodite,s}-yy_{14}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&(xy_{22}^{\Hermaphrodite,s}+xy_{42}^{\Hermaphrodite,s})/2+(xy_{12}^{\Hermaphrodite,s}+xy_{32}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite)\\
-&- r(xy_{12}^{\Hermaphrodite,s}-xy_{21}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite) - \rho(xy_{42}^{\Hermaphrodite,s}-xy_{24}^{\Hermaphrodite,s})/2\\
-&+\big{[}-(R+r+\rho)xy_{32}^{\Hermaphrodite,s} +(R+\rho-r) xy_{23}^{\Hermaphrodite,s}\\
-&+(R+r-\rho)xy_{41}^{\Hermaphrodite,s}+(R+\rho-r)xy_{14}^{\Hermaphrodite,s}\big{]}(1-\alpha^\Hermaphrodite)/2
+y_{2}^{{\circ}'}=&yy_{22}^{\circ,s}+yy_{24}^{\circ,s}/2+(yy_{12}^{\circ,s}+yy_{23}^{\circ,s})\alpha^\circ\\
+&-R(yy_{23}^{\circ,s}-yy_{14}^{\circ,s}) \alpha^\circ\\
+&(xy_{22}^{\circ,s}+xy_{42}^{\circ,s})/2+(xy_{12}^{\circ,s}+xy_{32}^{\circ,s})(1-\alpha^\circ)\\
+&- r(xy_{12}^{\circ,s}-xy_{21}^{\circ,s})(1-\alpha^\circ) - \rho(xy_{42}^{\circ,s}-xy_{24}^{\circ,s})/2\\
+&+\big{[}-(R+r+\rho)xy_{32}^{\circ,s} +(R+\rho-r) xy_{23}^{\circ,s}\\
+&+(R+r-\rho)xy_{41}^{\circ,s}+(R+\rho-r)xy_{14}^{\circ,s}\big{]}(1-\alpha^\circ)/2
 \end{split}
@@
 \begin{split}
-y_{3}^{{\Hermaphrodite}'}=&yy_{33}^{\Hermaphrodite,s}+yy_{13}^{\Hermaphrodite,s}/2+(yy_{23}^{\Hermaphrodite,s}+yy_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(yy_{23}^{\Hermaphrodite,s}-yy_{14}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&(xy_{33}^{\Hermaphrodite,s}+xy_{13}^{\Hermaphrodite,s})/2+(xy_{23}^{\Hermaphrodite,s}+xy_{43}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&- r(xy_{43}^{\Hermaphrodite,s}-xy_{34}^{\Hermaphrodite,s})\alpha^\Hermaphrodite - \rho(xy_{13}^{\Hermaphrodite,s}-xy_{31}^{\Hermaphrodite,s})/2\\
-&+\big{[}-(R+r+\rho)xy_{23}^{\Hermaphrodite,s} +(R+\rho-r)xy_{32}^{\Hermaphrodite,s}\\
-&+(R+r-\rho) xy_{14}^{\Hermaphrodite,s} + (R+\rho-r) xy_{41}^{\Hermaphrodite,s}\big{]}\alpha^\Hermaphrodite/2
+y_{3}^{{\circ}'}=&yy_{33}^{\circ,s}+yy_{13}^{\circ,s}/2+(yy_{23}^{\circ,s}+yy_{34}^{\circ,s})\alpha^\circ\\
+&-R(yy_{23}^{\circ,s}-yy_{14}^{\circ,s}) \alpha^\circ\\
+&(xy_{33}^{\circ,s}+xy_{13}^{\circ,s})/2+(xy_{23}^{\circ,s}+xy_{43}^{\circ,s})\alpha^\circ\\
+&- r(xy_{43}^{\circ,s}-xy_{34}^{\circ,s})\alpha^\circ - \rho(xy_{13}^{\circ,s}-xy_{31}^{\circ,s})/2\\
+&+\big{[}-(R+r+\rho)xy_{23}^{\circ,s} +(R+\rho-r)xy_{32}^{\circ,s}\\
+&+(R+r-\rho) xy_{14}^{\circ,s} + (R+\rho-r) xy_{41}^{\circ,s}\big{]}\alpha^\circ/2
 \end{split}
@@
 \begin{split}
-y_{4}^{{\Hermaphrodite}'}=&yy_{44}^{\Hermaphrodite,s}+yy_{34}^{\Hermaphrodite,s}/2+(yy_{14}^{\Hermaphrodite,s}+yy_{24}^{\Hermaphrodite,s})\alpha^\Hermaphrodite\\
-&-R(yy_{14}^{\Hermaphrodite,s}-yy_{23}^{\Hermaphrodite,s}) \alpha^\Hermaphrodite\\
-&(xy_{44}^{\Hermaphrodite,s}+xy_{24}^{\Hermaphrodite,s})/2+(xy_{14}^{\Hermaphrodite,s}+xy_{34}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite)\\
-&- r(xy_{34}^{\Hermaphrodite,s}-xy_{43}^{\Hermaphrodite,s})(1-\alpha^\Hermaphrodite) - \rho(xy_{24}^{\Hermaphrodite,s}-xy_{42}^{\Hermaphrodite,s})/2\\
-&+\big{[}-(R+r+\rho) xy_{14}^{\Hermaphrodite,s} + (R+\rho-r)xy_{41}^{\Hermaphrodite,s}\\
-&+(R+r-\rho) xy_{23}^{\Hermaphrodite,s} + (R+\rho-r) xy_{32}^{\Hermaphrodite,s}\big{]}(1-\alpha^\Hermaphrodite)/2.
+y_{4}^{{\circ}'}=&yy_{44}^{\circ,s}+yy_{34}^{\circ,s}/2+(yy_{14}^{\circ,s}+yy_{24}^{\circ,s})\alpha^\circ\\
+&-R(yy_{14}^{\circ,s}-yy_{23}^{\circ,s}) \alpha^\circ\\
+&(xy_{44}^{\circ,s}+xy_{24}^{\circ,s})/2+(xy_{14}^{\circ,s}+xy_{34}^{\circ,s})(1-\alpha^\circ)\\
+&- r(xy_{34}^{\circ,s}-xy_{43}^{\circ,s})(1-\alpha^\circ) - \rho(xy_{24}^{\circ,s}-xy_{42}^{\circ,s})/2\\
+&+\big{[}-(R+r+\rho) xy_{14}^{\circ,s} + (R+\rho-r)xy_{41}^{\circ,s}\\
+&+(R+r-\rho) xy_{23}^{\circ,s} + (R+\rho-r) xy_{32}^{\circ,s}\big{]}(1-\alpha^\circ)/2.
 \end{split}
@@
 However, not all diploid types are produced under certain sex-determining systems. 
-For example, with the $M$ allele fixed and an ancestral XY sex-determining system, there are XX females and XY males ($x_{3}^\Hermaphrodite=x_{4}^\Hermaphrodite=y_{3}^\male=y_{4}^\male=y_{i}^\female=0,\;\forall\; i$).
+For example, with the $M$ allele fixed and an ancestral XY sex-determining system, there are XX females and XY males ($x_{3}^\circ=x_{4}^\circ=y_{3}^\male=y_{4}^\male=y_{i}^\female=0,\;\forall\; i$). 
 %($xx_{11}^{\male}=xx_{12}^{\male}=xx_{22}^\male=xy_{11}^{\female}=xy_{12}^{\female}=xy_{21}^{\female}=xy_{22}^\female=yy_{11}^{\female}=yy_{12}^{\female}=yy_{22}^\female=0$). 

### 2018-03-28 LaTeX/S2Appendix_revised.tex
refining conclusions and reviewer 2 responses

--- 2018-02-07 LaTeX/S2Appendix.tex
@@
 \usepackage{xr}
-\externaldocument{S1Appendix}
-\externaldocument{main}
-\externaldocument{S3Appendix}
+\externaldocument{S1Appendix_revised}
+\externaldocument{main_revised}
+\externaldocument{S3Appendix_revised}
 
@@
 Since equilibria $(A)$ and $(B)$ are equivalent to equilibria $(A')$ and $(B')$ with the labelling of $A$ and $a$ alleles interchanged, we discuss only equilibria $(A)$ and $(B)$, in which the Y background is fixed for the $a$ allele.
-If there is no haploid selection ($\alpha^{\Hermaphrodite}_\Delta=0$, $w_{A}^{\Hermaphrodite}=w_{a}^{\Hermaphrodite}=1$), these equilibria are equivalent to those found by~\cite{Lloyd1977} and~\cite{Otto2014}.
+If there is no haploid selection ($\alpha^{\circ}_\Delta=0$, $w_{A}^{\circ}=w_{a}^{\circ}=1$), these equilibria are equivalent to those found by~\cite{Lloyd1977} and~\cite{Otto2014}.
 
@@
 
-Here, we assume that selection is weak relative to recombination ($s^\Hermaphrodite$, $t^\Hermaphrodite$, $\alpha_{\Delta}^\Hermaphrodite$ of order $\epsilon$). 
+Here, we assume that selection is weak relative to recombination ($s^\circ$, $t^\circ$, $\alpha_{\Delta}^\circ$ of order $\epsilon$). 
 The maintenance of a polymorphism at the $\mathbf{A}$ locus then requires that
@@
 \noindent
-where $V_{A}=\bar{p}(1-\bar{p})$ is the variance in the frequency of $A$ and $D^\Hermaphrodite=\big{[} \bar{p}s^\Hermaphrodite+(1-\bar{p})h^\Hermaphrodite s^\Hermaphrodite\big{]} -\big{[} \bar{p}h^\Hermaphrodite s^\Hermaphrodite+(1-\bar{p}) \big{]}$ corresponds to the difference in fitness between $A$ and $a$ alleles in diploids of sex $\Hermaphrodite \in \{\female,\male\}$.
+where $V_{A}=\bar{p}(1-\bar{p})$ is the variance in the frequency of $A$ and $D^\circ=\big{[} \bar{p}s^\circ+(1-\bar{p})h^\circ s^\circ\big{]} -\big{[} \bar{p}h^\circ s^\circ+(1-\bar{p}) \big{]}$ corresponds to the difference in fitness between $A$ and $a$ alleles in diploids of sex $\circ \in \{\female,\male\}$.
 The frequency of Y-bearing male gametes depends upon the difference in the frequency of the $A$ allele between X- and Y-bearing male gametes and the strength of meiotic drive in favour of the $A$ allele in males, $q=1/2+\alpha_{\Delta}^\male(\hat{p}^\male_Y-\hat{p}^\male_X)/2+O(\epsilon^3)$.
-Without gametic competition or drive ($\alpha_{\Delta}^\Hermaphrodite=t^\Hermaphrodite=0$) our results reduce to those of~\cite{vanDoorn:2007eu}.
+Without gametic competition or drive ($\alpha_{\Delta}^\circ=t^\circ=0$) our results reduce to those of~\cite{vanDoorn:2007eu}.
 

### 2018-03-28 LaTeX/S3Appendix_revised.tex
refining conclusions and reviewer 2 responses

--- 2018-02-07 LaTeX/S3Appendix.tex
@@
 \usepackage{xr}
-\externaldocument{S1Appendix}
-\externaldocument{S2Appendix}
-\externaldocument{main}
+\externaldocument{S1Appendix_revised}
+\externaldocument{S2Appendix_revised}
+\externaldocument{main_revised}
 
@@
 Second, even when diploid selection could itself maintain a polymorphism, haploid selection can increase the conditions under which transitions among sex-determining systems are possible.
-Of particularly importance, when selection is sexually-antagonistic in diploids ($s^\female s^\male <0$ and $0<h^\Hermaphrodite<1$), an unlinked neo-W ($R=1/2$) cannot invade unless there is also haploid selection (see proof in \nameref{file:Mathematica}; Fig \ref{fig:SexAntagTighter} and \nameref{fig:SexAntagTighterMaleDrive}).
+Of particularly importance, when selection is sexually-antagonistic in diploids ($s^\female s^\male <0$ and $0<h^\circ<1$), an unlinked neo-W ($R=1/2$) cannot invade unless there is also haploid selection (see proof in \nameref{file:Mathematica}; Fig \ref{fig:SexAntagTighter} and \nameref{fig:SexAntagTighterMaleDrive}).
 More generally, haploid selection alters the conditions under which neo-W alleles can spread (compare \nameref{fig:regionMaleDrive}-\nameref{fig:regionFemaleGS} to Fig \ref{fig:regionplots}).

### 2018-03-28 LaTeX/main_revised.tex
refining conclusions and reviewer 2 responses

--- 2018-03-28 LaTeX/main_revision.tex
@@
 % amsmath and amssymb packages, useful for mathematical formulas and symbols
-\usepackage{amsmath,amssymb}
+\usepackage{amsmath}%amssymb
 
@@
 \usepackage{xr}
-\externaldocument{S1Appendix}
-\externaldocument{S2Appendix}
-\externaldocument{S3Appendix}
+\externaldocument{S1Appendix_revised}
+\externaldocument{S2Appendix_revised}
+\externaldocument{S3Appendix_revised}
 
@@
 %Previous models with haploid selection
-Two previous numerical simulation studies have considered the spread of GSD with sex-specific meiotic drive~\cite{Kozielska:2010vm,Ubeda:2015fx} under a small number of possible genetic architectures and diploid selective regimes.
-Ubeda et al. (2015)~\cite{Ubeda:2015fx}, considers ancestral-ESD (with no sex ratio bias) and find that new GSD alleles can spread if they arise in linkage with meiotic drive loci. 
+Two previous studies have considered the spread of GSD with sex-specific meiotic drive~\cite{Kozielska:2010vm,Ubeda:2015fx} under a limited number of possible genetic architectures and diploid selective regimes.
+Ubeda et al. (2015)~\cite{Ubeda:2015fx}, considers ancestral-ESD (with no sex-ratio bias) and numerically show that new GSD alleles can spread if they arise in linkage with meiotic drive loci. 
 For example, a masculinizing allele spreads in association with an allele that is favoured during male meiosis, causing sex ratios to become male-biased and thereby suggesting that such beneficial associations overwhelm selection to balance the sex ratio.
 However, Kozielska et al. (2010)~\cite{Kozielska:2010vm} consider meiotic drive on an ancestral GSD sex chromosome (creating a sex ratio bias). 
-They find that new, unlinked, GSD systems can spread if they generate the rarer sex, creating a balanced sex ratio. 
-That is, they conclude that Fisherian sex ratio selection caused by haploid selection favours new GSD systems. 
-Here, we analytically find conditions under which new GSD or ESD systems spread with generic linkage between the loci involved (and generic sex-specific haploid and diploid selection).
+They find that new, completely unlinked, GSD systems can spread if they generate the rarer sex, creating a balanced sex ratio. 
+That is, they conclude that Fisherian sex-ratio selection caused by haploid selection favours new GSD systems.
 
 %main results
+Here, we analytically find the conditions under which new GSD or ESD systems spread with generic linkage between the loci involved (and generic sex-specific haploid and diploid selection). 
 Strikingly, we reconcile the results of Kozielska et al.
@@
 This result is qualitatively distinct from those for diploid selection alone~\cite{vanDoorn:2007eu,vanDoorn:2010hu} and suggests that haploid selection is more likely to promote transitions between sex-determination systems.
-However, we also show that transitions involving haploid selection cannot be simply explained by invoking sex ratio selection. 
+However, we also show that transitions involving haploid selection cannot be simply explained by invoking sex-ratio selection. 
 In particular, under a wide range of conditions, we show that haploid selection drives transitions in sex-determining system \textit{equally strongly} whether sex-ratio biases increase or decrease (and whether sex-ratio biases are present or absent).
-Finally, we show that ESD may not evolve, even if the sex-ratio is initially biased by haploid selection, which would not be predicted by previous theories for transitions to ESD~\cite{Charnov:1982wg,Bull:1983vi,West:2009we}.
+Finally, we show that ESD may not evolve, even if the sex ratio is initially biased by haploid selection, which would not be predicted by previous theories for transitions to ESD~\cite{Charnov:1982wg,Bull:1983vi,West:2009we}.
 
@@
 Thus, the $\mathbf{A}$ locus can experience sex-specific gametic competition, diploid selection, and/or meiotic drive.
-`
+The model is entirely deterministic and hence ignores chance fluctuations in allele frequencies due to genetic drift.
+
 \begin{table}[ht]
@@
 The leading eigenvalue for a rare neo-Y or neo-W allele, $m\in\{Y',W'\}$, is the largest value of X that solves $x^2+ b x + c = 0$.  %$(\lambda_m^{(i)})^2+ b \lambda_m^{(i)} + c =0$. 
-The coefficients are $b= - (\Lambda_{mA}^{(XY)} + \Lambda_{ma}^{(XY)})+(\chi_{mA}^{(XY)} + \chi_{ma}^{(XY)})$ and $c = (\Lambda_{mA}^{(XY)} - \chi_{mA}^{(XY)}) (\Lambda_{ma}^{(XY)} - \chi_{ma}^{(XY)}) - \chi_{mA}^{(XY)} \chi_{ma}^{(XY)}$, where $\Lambda_{mi}^{(XY)}>0$ is the multiplicative growth rate (which we will call the ``haplotypic growth rate'') of the neo-sex determination allele $m$ on background $i\in\{A,a\}$ without accounting for loss due to recombination ($R=0$), and $\chi_{mi}^{(XY)}>0$ is the rate at which mutant haplotypes on background $i\in\{A,a\}$ recombine onto the other $\mathbf{A}$ locus background in heterozygotes (proportional to $R$; \textcolor{red}{we call this the ``haplotypic recombination rate"(?)}), see Table \ref{tab:haplotype_growth}.
+The coefficients are $b= - (\Lambda_{mA}^{(XY)} + \Lambda_{ma}^{(XY)})+(\chi_{mA}^{(XY)} + \chi_{ma}^{(XY)})$ and $c = (\Lambda_{mA}^{(XY)} - \chi_{mA}^{(XY)}) (\Lambda_{ma}^{(XY)} - \chi_{ma}^{(XY)}) - \chi_{mA}^{(XY)} \chi_{ma}^{(XY)}$, where $\Lambda_{mi}^{(XY)}>0$ is the multiplicative growth rate (which we will call the ``haplotypic growth rate'') of the neo-sex determination allele $m$ on background $i\in\{A,a\}$ without accounting for loss due to recombination ($R=0$), and $\chi_{mi}^{(XY)}>0$ is the rate at which mutant haplotypes on background $i\in\{A,a\}$ recombine onto the other $\mathbf{A}$ locus background in heterozygotes (proportional to $R$; we call this the ``dissociative force" as it breaks down linkage disequilibrium), see Table \ref{tab:haplotype_growth}.
 In the ancestral population, it is convenient to follow the frequency of the $A$ allele among female gametes (eggs), $p^\female_X$, and among X-bearing, $p^\male_X$, and among Y-bearing, $p^\male_Y$, male gametes (sperm/pollen).
@@
 This condition may or may not be satisfied for the full range of locations of the new sex-determining locus, including $R=1/2$, depending on the nature of selection.  
-Interpreting this condition, if we assume that only the $mA$ haplotype would increase in frequency when $R=0$ ($\Lambda_{ma}^{(XY)}<1<\Lambda_{mA}^{(XY)}$) the first term on the left-hand side of \eqref{eq:lambdasGen} is negative and invasion requires that rate of growth of $mA$ haplotypes ($\Lambda_{mA}^{(i)}-1>0$) and the rate at which $mA$ haplotypes are produced by recombination in $ma$ haplotypes ($\chi_{ma}^{(i)}$) are sufficiently large relative to the rate of decline of $ma$ haplotypes ($1-\Lambda_{ma}^{(i)}>0$) and the rate of loss of $mA$ haplotypes due to recombination ($\chi_{mA}^{(i)}$).
+Interpreting this condition, if we assume that only the $mA$ haplotype would increase in frequency when $R=0$ ($\Lambda_{ma}^{(XY)}<1<\Lambda_{mA}^{(XY)}$) then the first term on the left-hand side of \eqref{eq:lambdasGen} is negative and invasion requires that growth rate of $mA$ haplotypes ($\Lambda_{mA}^{(i)}-1>0$) and the rate at which they are produced by recombination ($\chi_{ma}^{(i)}$) are sufficiently large relative to the rate of decline of $ma$ haplotypes ($1-\Lambda_{ma}^{(i)}>0$) and the rate at which $m$ and $A$ are dissociated by recombination ($\chi_{mA}^{(i)}$).
 
@@
 Second, Fisherian sex-ratio selection will favour the spread of a neo-W and inhibit the spread of a neo-Y if the ancestral zygotic sex ratio is biased towards males (i.e., the first factor of the $\Lambda_{mi}^{(XY)}$ is greater than one for a neo-W and less than one for a neo-Y when $\zeta>1/2$), as might occur when the ancestral sex-determining locus is linked to a locus experiencing meiotic drive in males, for example.
-However, the spread of a neo-Y (neo-W) also depends on the male (female) fitness of associated alleles (see terms involving equilibrium allele frequencies, $\hat{p}$'s). That is, 
-\vspace{0.5cm}
-
-\noindent\textit{Conclusion 1:} 
-\textit{neither sex-ratio selection or selection on associated alleles dominates the invasion dynamics of a new sex-determining allele, allowing the sex ratio to become more or less biased during a transition.}
-\textcolor{red}{[as suspected from Kozielska and Ubeda special cases]}
-\vspace{0.5cm}
-
-\noindent And thirdly, Table \ref{tab:haplotype_growth} also shows that
-\vspace{0.5cm}
-
-\noindent\textit{Conclusion 2: cis- and trans-GSD transitions are qualitatively different.}
-\textcolor{red}{[already known from van Doorn and Kirkpatrick?]}
-\vspace{0.5cm}
-
-\noindent This is because, in an ancestrally XY system, a gamete with the neo-Y always pairs with a female gamete containing an X, Fig \ref{fig:model_outline}C.
+However, the spread of a neo-Y (neo-W) also depends on the male (female) fitness of associated alleles (see terms involving equilibrium allele frequencies, $\hat{p}$'s).
+This implies that neither sex-ratio selection or selection on associated alleles dominates the invasion dynamics of a new sex-determining allele, allowing the sex ratio to become more or less biased during a transition (as previously shown in two special cases; \cite{Kozielska:2010vm,Ubeda:2015fx}).
+%That is, 
+%\vspace{0.5cm}
+%
+%\noindent\textit{Conclusion 1:} 
+%\textbf{neither sex-ratio selection or selection on associated alleles dominates the invasion dynamics of a new sex-determining allele, allowing the sex ratio to become more or less biased during a transition.}
+%\textcolor{red}{[as suspected from Kozielska and Ubeda special cases]}
+%\vspace{0.5cm}
+%
+And thirdly, Table \ref{tab:haplotype_growth} also shows that
+%\vspace{0.5cm}
+%
+%\noindent\textit{Conclusion 2:}
+%\textbf{cis- and trans-GSD transitions are qualitatively different.}
+%\textcolor{red}{[already known from van Doorn and Kirkpatrick]}
+%\vspace{0.5cm}
+%
+cis- and trans-GSD transitions are qualitatively different.
+This is because, in an ancestrally XY system, a gamete with the neo-Y always pairs with a female gamete containing an X, Fig \ref{fig:model_outline}C.
 By contrast, a gamete with a neo-W can pair with an X- or Y-bearing male gamete, Fig \ref{fig:model_outline}D.
@@
 
-\noindent\textit{Conclusion 3: selection on loci within the non-recombining region around the sex-determining locus ($r\approx0$) allows the invasion of less closely linked sex-determining alleles ($r<R\leq1/2$) during a trans-GSD transition}.
-\textcolor{red}{[new result for sex-antagonism and overdominance, but already shown by Kozielska for ploidy-antagonism]}
+\noindent\textit{Conclusion 1A:}
+\textbf{selection on loci within the non-recombining region around the sex-determining locus ($r\approx0$) allows the invasion of less closely linked sex-determining alleles ($r<R\leq1/2$) during a trans-GSD transition}.
+%\textcolor{red}{[new result for sex-antagonism and overdominance, but already shown by Kozielska for ploidy-antagonism]}
 \vspace{0.5cm}
@@
 The conditions become more restrictive, however, with increasing recombination ($R$) between the new sex-determining locus and the selected locus.  
-The invasion of completely unlinked neo-W alleles ($R = 1/2$) can occur with overdominance in males or with haploid selection but is not possible with only sexually-antagonistic selection if selection is directional in each diploid sex (see \nameref{file:Mathematica}).
-\vspace{0.5cm}
+The invasion of completely unlinked neo-W alleles ($R = 1/2$) can occur with overdominance in males or with haploid selection (as shown for the case of male drive opposed by diploid selection in \cite{Kozielska:2010vm}) but is not possible with only sexually-antagonistic selection if selection is directional in each diploid sex (see \nameref{file:Mathematica}).
+%\vspace{0.5cm}
 
@@
 
-\noindent\textit{Conclusion 4: when there is an intermediate rate of recombination between the ancestral sex-determining allele and a selected locus ($0<r<1/2$), haploid selection allows less closely linked sex-determining alleles ($r<R$) to invade during trans-GSD transitions ($\lambda_{W'}^{(XY)}>1$).}
-\textcolor{red}{[new result because Kozielska had tight linkage and Ubeda had ESD]}
+\noindent\textit{Conclusion 1B:}\
+\textbf{when there is an intermediate rate of recombination between the ancestral sex-determining allele and a selected locus ($0<r<1/2$), haploid selection allows less closely linked sex-determining alleles ($r<R$) to invade during trans-GSD transitions ($\lambda_{W'}^{(XY)}>1$).}
+%\textcolor{red}{[new result because Kozielska had ancestrally-tight sex-linkage and Ubeda had ESD]}
 \vspace{0.5cm}
@@
 
-Previous research has shown that when the ancestral sex-determining locus is linked to a locus that experiences haploid selection (e.g., meiotic drive), alleles at a new, unlinked sex-determining locus can invade and restore equal sex ratios~\cite{Kozielska:2010vm,Ubeda:2015fx}.
+Previous research has shown that when the ancestral sex-determining locus is linked to a locus that experiences haploid selection (e.g., meiotic drive), alleles at a new, unlinked sex-determining locus can invade and restore equal sex ratios~\cite{Kozielska:2010vm}.
 Consider, for example, the case where the $\mathbf{A}$ locus is linked to the ancestral sex-determining locus ($r<1/2$) and experiences meiotic drive in males only ($\alpha^\male_\Delta \neq 0$, $\alpha^\female_\Delta=0$), without gametic competition ($t^\female=t^\male=0$).
@@
 %However, to leading order with selection weak relative to recombination, we find that sex-ratio selection favours the spread of a neo-W by an amount equl to the spread of a neo-Y into a ZW system (relabeling XY as the heterogametic sex and reversing the labels of males and females in Table \ref{tab:specialcases})
-%However, to leading order with selection weak relative to recombination, we find that sex-ratio selection favours the spread of a neo-W (through the first terms in table \ref{tab:haplotype_growth}) by an amount that is equal in magnitude to the fitness effects of alleles associated with new sex-determining alleles (second terms in table \ref{tab:haplotype_growth}).
-However, invasion by a neo-W allele into an XY system and invasion by a neo-Y allele into a ZW system occur under the same conditions ($\lambda_{Y'}^{(XY)} = \lambda_{W'}^{(ZW)}$ and $\lambda_{W'}^{(XY)}=\lambda_{Y'}^{(ZW)}$, at least to order $\epsilon^2$).
-For example, in Fig \ref{fig:SexRatioBad}A neo-W alleles invade an ancestral-XY system where females are initially rare, equalizing the sex ratio.
+However, invasion by a neo-W allele into an XY system and invasion by a neo-Y allele into a ZW system occur under the same conditions ($\lambda_{Y'}^{(XY)} = \lambda_{W'}^{(ZW)}$ and $\lambda_{W'}^{(XY)}=\lambda_{Y'}^{(ZW)}$, at least to order $\epsilon^2$), implying that
+\vspace{0.5cm}
+
+\noindent\textit{Conclusion 2:}
+\textbf{when selection is weak relative to recombination, sex-ratio selection is exactly equal in magnitude to the selection imposed by associations with selected alleles.}
+%\textcolor{red}{[new result]}
+\vspace{0.5cm}
+
+\noindent For example, in Fig \ref{fig:SexRatioBad}A neo-W alleles invade an ancestral-XY system where females are initially rare, equalizing the sex ratio.
 However, Fig \ref{fig:SexRatioBad}B shows that a neo-Y can invade the resulting ZW system under the same conditions. 
@@
 In this case, the neo-Y spreads because it is often found in males and can, if it carries the driven allele $a$, benefit from haploid selection in males (Fig \ref{fig:SexRatioBad}B).
+
 %
@@
 As discussed above, $\lambda_{Y'\rvert R=1/2}^{(XY)}$ is necessarily less than one, but $\lambda_{W'\rvert R=1/2}^{(XY)}$ can be greater than one if there is haploid selection.
-That is:
-\vspace{0.5cm}
-
-\noindent\textit{Conclusion 5: with haploid selection, an allele causing environmental-sex-determination can invade an ancestrally-XY system because it generates females that are either rare or have high fitness, in the same manner as a neo-W (likewise, ESD invades a ZW system for the same reasons a neo-Y can)}.
-\textcolor{red}{[I imagine this is a new result as it requires the evolution of effectively looser linkage from a weak recombination ancestor, which requires haploid selection, and neither Kozielska or Ubeda had GSD to ESD.]}
-\vspace{0.5cm}
-
+That is, with haploid selection, an allele causing environmental-sex-determination can invade an ancestrally-XY system because it generates females that are either rare or have high fitness, in the same manner as a neo-W (likewise, ESD invades a ZW system for the same reasons a neo-Y can).
 %An important result from Eq \eqref{eq:lambda_ESD} is that ESD can invade if there is haploid selection. 
@@
 In addition, we note that ESD may not invade, even if the sex ratio is initially biased (e.g., with drive in males only, $r<1/2$, $h^\female=h^\male$, and $s^\female s^\male<0$, then $\lambda_{W'}^{(XY)}<1$, see Table \ref{tab:specialcases}).
-We conclude that, as with neo-W and neo-Y loci, associations with selected loci mean that the evolution of ESD is not straightforwardly predicted by selection to balance the zygotic sex ratio when haploid selection is present.
-
-\textcolor{red}{
-Somehow need to add two further conclusions suggested by review 2:
+We conclude that, as with neo-W and neo-Y loci, associations with selected loci mean that
 \vspace{0.5cm}
-\\
-\noindent\textit{Conclusion 6: sex-antagonism and tighter sex linkage not required for transitions.}
-\vspace{0.5cm}
-\\
-\noindent\textit{Conclusion 7: haploid selection makes conditions for transitions permissive.}
-\vspace{0.5cm}
-\\
-\noindent Or are these evident from the first 5 conclusions?
+
+\noindent\textit{Conclusion 3:}
+\textbf{
+transitions from genetic to environmental sex-determination are not straightforwardly predicted by selection to balance the zygotic sex ratio when haploid selection is present. 
 }
+%\textcolor{red}{[new result]}
+
+%\textcolor{red}{
+%Somehow need to add two further conclusions suggested by review 2:
+%\vspace{0.5cm}
+%\\
+%\noindent\textit{Conclusion 6: sex-antagonism and tighter sex linkage not required for transitions.}
+%\vspace{0.5cm}
+%\\
+%\noindent\textit{Conclusion 7: haploid selection makes conditions for transitions permissive.}
+%\vspace{0.5cm}
+%\\
+%\noindent Or are these evident from the first 5 conclusions?
+%}
 
@@
 These results echo those for large-effect neo-Y/neo-W alleles~\cite{vanDoorn:2007eu,vanDoorn:2010hu}.
-\textcolor{red}{It should be noted, however, that the dynamics of sex-determining alleles with very weak effect will be influenced by genetic drift, which itself has been shown to cause trans-GSD transitions \cite{Veller2017}}.
+It should be noted, however, that the dynamics of sex-determining alleles with very weak effect will be influenced by genetic drift, which itself has been shown to cause trans-GSD transitions \cite{Veller2017}.
 
@@
 % 
-\bibliography{sex_chromosomes.bib}
+\bibliography{sex_chromosomes}
 

### 2018-03-29 LaTeX/main_revised.tex
half baked thoughts added in red...

@@
 Sex determination is remarkably dynamic; many taxa display shifts in the location of sex-determining loci or the evolution of entirely new sex-determining systems. 
-Predominant theories for why we observe such transitions generally conclude that novel sex-determining systems are favoured by selection if they equalise the sex ratio or increase linkage with a sexually-antagonistic locus.
+Predominant theories for why we observe such transitions generally conclude that novel sex-determining systems are favoured by selection if they equalise the sex ratio or increase linkage with a \textcolor{red}{sexually-antagonistic locus}.
 We use population genetic models to extend these theories in two ways: 
@@
 (2) We consider selection upon haploid genotypes either during gametic competition (e.g., pollen/sperm competition involving multiple males) or meiosis (i.e., non-Mendelian segregation), which can cause the zygotic sex ratio to become biased.
-We find that associations with haploid selected loci can drive transitions between sex-determining systems, without requiring sexually-antagonistic selection in diploids. 
+We find that associations with haploid selected loci can drive transitions between sex-determining systems \textcolor{red}{, without requiring sexually-antagonistic selection in diploids}. 
 Unexpectedly, with haploid selection, transitions between male and female heterogamety can also evolve where linkage with the sex-determining locus is weakened. 
@@
 Prevailing views suggest that new sex-determining systems are favoured when they equalize the sex ratio and/or when they are more closely linked to genes that experience differential selection in males and females.
-Our models extend these theories to include selection upon haploid genotypes (meiotic drive or gametic competition), which causes sex-ratio biases and occurs differently in males and females. 
+Our models extend these theories to include selection upon haploid genotypes (meiotic drive or gametic competition), which causes sex-ratio biases and occurs differently in male and female gametes. 
 Surprisingly, we find the two forces (sex-ratio selection and associations with genes that have sex-specific effects) will often be equally strong, and thus neither dominates the spread of new sex-determining systems alone.
@@
 %(1) sex-ratio selection
-Predominant theories accounting for transitions between GSD systems by selection involve sex-ratio selection or fitness differences between sexes (e.g., sexually antagonistic selection)~\cite{Blaser2012, Beukeboom:2014vb,vanDoorn2014re}.
+Predominant theories accounting for transitions between GSD systems by selection involve sex-ratio selection or selective differences between the sexes (e.g., sexually antagonistic selection)~\cite{Blaser2012, Beukeboom:2014vb,vanDoorn2014re}.
 %\citet{Bull:1977wt} shows that direct selection on new sex determination loci can allow them to spread and switch between male and female heterogamety. 
@@
 %(2) sex-antagonism
-New genetic sex-determining alleles have been shown to be favoured in they arise in close linkage with a locus that experiences sexual antagonism ~\cite{vanDoorn:2007eu,vanDoorn:2010hu,Muralidhar2018}.
+Loci experiencing sexual antagonism have been shown to favour the spread of new genetic sex-determining alleles that are closely linked~\cite{vanDoorn:2007eu,vanDoorn:2010hu,Muralidhar2018}. 
 %van Doorn and Kirkpatrick~\cite{vanDoorn:2007eu,vanDoorn:2010hu} and Muralidhar and Veller~\cite{Muralidhar2018} have shown that new sex-determining alleles can be favoured if they arise at loci in close linkage with a locus that experiences sexual antagonism.
-Tighter linkage allows a stronger favourable association to build up between a male-beneficial allele, and a neo-Y allele, for example. 
-Such associations can favour cis-GSD transitions~\cite{vanDoorn:2007eu}, trans-GSD transitions~\cite{vanDoorn:2010hu}, and new partially-masculinizing or partially-feminizing alleles~\cite{Muralidhar2018}.
+Linkage allows a stronger favourable association to build up between a male-beneficial allele, and a neo-Y allele, for example. 
+Such associations can favour cis-GSD transitions~\cite{vanDoorn:2007eu}, trans-GSD transitions~\cite{vanDoorn:2010hu}, and new partially-masculinizing or partially-feminizing alleles in a population with ESD~\cite{Muralidhar2018}.
 However, any sexually-antagonistic loci that are more closely linked to the ancestral sex-determining locus will develop similar, favourable associations and are expected to hinder the spread of a new sex-determining system~\cite{vanDoorn:2007eu,vanDoorn:2010hu}.
@@
 However, we also show that transitions involving haploid selection cannot be simply explained by invoking sex-ratio selection. 
-In particular, under a wide range of conditions, we show that haploid selection drives transitions in sex-determining system \textit{equally strongly} whether sex-ratio biases increase or decrease (and whether sex-ratio biases are present or absent).
+In particular, under a wide range of conditions, we show that haploid selection drives transitions in sex-determining system \textit{equally strongly} in situations where sex-ratio biases increase or decrease (and in situations where sex-ratio biases are present or absent).
 Finally, we show that ESD may not evolve, even if the sex ratio is initially biased by haploid selection, which would not be predicted by previous theories for transitions to ESD~\cite{Charnov:1982wg,Bull:1983vi,West:2009we}.
+Together, in this context, our results suggest that sex ratio selection is not an overwhelming force driving transitions between sex-determining systems.
 
@@
 Locus $\mathbf{M}$ is a novel sex-determining region, at which the null allele ($M$) is initially fixed in the population such that sex of zygotes is determined by the genotype at the ancestral sex-determining region, $\mathbf{X}$; XX genotypes become females and XY become males (or ZW become females and ZZ become males).
-To evaluate the evolution of new sex-determining systems, we consider the invasion, fixation, maintenance, and/or loss of a novel sex-determining allele ($m$) at the $\mathbf{M}$ locus. 
+To evaluate the evolution of new sex-determining systems, we consider the spread of a novel sex-determining allele ($m$) at the $\mathbf{M}$ locus. 
 %We only do invasion analytically though (is this sentence still ok?)
-We assume that the $\mathbf{M}$ locus is epistatically dominant over the $\mathbf{X}$ locus such that zygotes with at least one $m$ allele develop as females with probability $k$ and as males with probability $1-k$, regardless of the $\mathbf{X}$ locus genotype.
+
+Here, we assume that the $\mathbf{M}$ locus is `epistatically dominant' over the $\mathbf{X}$ locus such that zygotes with at least one $m$ allele develop as females with probability $k$ and as males with probability $1-k$, regardless of the $\mathbf{X}$ locus genotype.
 With $k=0$, the $m$ allele is a masculinizer (a neo-Y allele) and with $k=1$ the $m$ allele is a feminizer (a neo-W allele). 
 With intermediate $k$, we can interpret $m$ as an environmental sex-determination (ESD) allele, such that zygotes develop as females in a proportion ($k$) of the environments they experience. 
+The assumption that derived sex-determining loci are epistatically dominant is motivated by empirical systems in which multiple sex determining alleles segregate (i.e., X, Y, Z, and W alleles present), such as, cichlid fish~\cite{Ser:2010iq}, platyfish (\textit{Xiphophorus maculatus}~\cite{Kallman1968}), houseflies (\textit{Musca domestica} \textcolor{red}{CITATION}), western clawed frogs (\textit{Xenopus tropicalis}~\cite{Roco2015}) and \textit{Rana rugosa}~\cite{Ogata:2007jm}.
+Nevertheless, our supplementary analysis file (\nameref{file:Mathematica}) allows other dominance relationships between loci to be specified. 
 %We also analyze a model of maternally-controlled environmental sex-determination, where mothers with at least one $m$ allele produce daughters with probability $k$.
@@
 
-\textcolor{red}{Discussion of `epistatic dominance' assumption to go here somewhere?
-The model in the Mathematica file is actual general to this assumption I think (or at least we wrote one that is), which we could mention in the response.}
-
+\textcolor{red}{possibly simplify?}
 The evolution of a new sex-determining system requires that a rare mutant allele, $m$, at the novel sex-determining locus, $\mathbf{M}$, increases in frequency when rare. 
@@
 %Thus, the system describing the change in frequency of the $m$ allele consists of eight recursion equations. 
-This system simplifies substantially for a dominant neo-Y ($k=0$) or neo-W ($k=1$), see \nameref{app:inv_cond}. 
+This system simplifies substantially for an epistatically dominant neo-Y ($k=0$) or neo-W ($k=1$), see \nameref{app:inv_cond}. 
 The leading eigenvalue for a rare neo-Y or neo-W allele, $m\in\{Y',W'\}$, is the largest value of X that solves $x^2+ b x + c = 0$.  %$(\lambda_m^{(i)})^2+ b \lambda_m^{(i)} + c =0$. 
@@
 
+\textcolor{red}{note: vD\&K (2010) use a QLE and therefore point out that their results does not require equilibria maintained by sexually antagonistic selection, only differences in fitness between male and females ($s^\male\neq s^\female$).
+e.g., during a sweep of a positive beneficial mutation, a new SDR can spread because it generates a stronger association with the sex that is favoured the most (e.g., putting the selected allele more often in females and  $s^\male< s^\female$).
+This is only transient, and most of the time during sweeps or mutation-selection balance, $V_A$ is small so the importance is probably small.
+}
+
 \subsection*{Tight linkage with the ancestral sex-determining locus ($r \approx 0$)}
@@
 
+\noindent\textcolor{red}{\textit{Conclusion 2A:}\
+\textbf{New sex-determining alleles (causing cis- \textit{or} trans-GSD transitions) can spread if the arise in closer linkage with a locus that experiences haploid selection than the ancestral-sex-determining locus ($R<r$).} (This is different but similar to Ubeda et al (2015), who started from ESD)}
+
+\noindent\textcolor{red}{\textit{Conclusion 2B:}\
+\textbf{New sex-determining alleles (causing trans-GSD transitions) can spread if they arise in looser linkage with a locus that experiences haploid selection than the ancestral-sex-determining locus ($r<R$).
+} }
+
 %These transitions are unusual because, when $R>r$, associations that selection has built up between alleles more favourable in one sex and alleles that determine sex will be weakened. 
@@
 In Table \ref{tab:specialcases} we give the conditions where invasion occurs when we further assume that haploid selection only occurs in one sex (e.g., during male meiosis only) and dominance coefficients are equal in the two sexes, $h^\female=h^\male$.
-When there is no gametic competition and meiotic drive is in one sex only, an unlinked neo-W can invade as long as the same allele is favoured during diploid selection in males and females ($s^\female s^\male>0$, see Fig \ref{fig:Combination_Centimorgans}A and Fig \ref{fig:SexRatioBad}B).
+These special cases indicate that neo-W invasion occurs for a large fraction of the parameter space, even if the neo-W uncouples the sex-determining locus from a locus under selection. 
+We show that neo-W alleles can spread for when they are more closely \textit{or} more loosely linked to a locus that experiences haploid selection in Fig \ref{fig:Combination_Centimorgans} (c.f., Fig \ref{fig:SexAntagTighter}A for diploid sexually-antagonistic selection alone).
+In Fig \ref{fig:SexRatioBad}, we also show that trans-GSD transitions in sex determination occur during which linkage with a haploid selected locus increases \textit{or} decreases.
+
+%When there is no gametic competition and meiotic drive is in one sex only, an unlinked neo-W can invade as long as the same allele is favoured during diploid selection in males and females ($s^\female s^\male>0$, see Fig \ref{fig:Combination_Centimorgans}A and Fig \ref{fig:SexRatioBad}B).
 %, which is 50\% of the parameter space.
-When there is no meiotic drive and gametic competition occurs in one sex only, an unlinked neo-W can invade as long as the same allele is favoured in male and female diploid selection and there are sex differences in selection of one type (e.g., $s^\female(s^\male-s^\female)>0$, see Fig \ref{fig:Combination_Centimorgans}B).
+%When there is no meiotic drive and gametic competition occurs in one sex only, an unlinked neo-W can invade as long as the same allele is favoured in male and female diploid selection and there are sex differences in selection of one type (e.g., $s^\female(s^\male-s^\female)>0$, see Fig \ref{fig:Combination_Centimorgans}B).
 %, which is 25\% of the parameter space.
-These special cases indicate that neo-W invasion occurs for a relatively large fraction of the parameter space, even if the neo-W uncouples the sex-determining locus from a locus under selection.
+%These special cases indicate that neo-W invasion occurs for a relatively large fraction of the parameter space, even if the neo-W uncouples the sex-determining locus from a locus under selection.
 
@@
 
-\noindent\textit{Conclusion 2:}
-\textbf{when selection is weak relative to recombination, sex-ratio selection is exactly equal in magnitude to the selection imposed by associations with selected alleles.}
+\noindent\textit{Conclusion 3:}
+\textbf{when selection is weak relative to recombination, sex-ratio selection is exactly equal in magnitude to the selection imposed by associations with selected alleles. }
+%\textcolor{red}{[new result]}
+\vspace{0.5cm}
+
+\noindent\textcolor{red}{\textit{Conclusion 3:}
+\textbf{when selection is weak relative to recombination, sex-ratio selection is exactly equal in magnitude to the selection imposed by associations with selected alleles. } }
 %\textcolor{red}{[new result]}
@@
 
+\textcolor{red}{Tight ancestral linkage favours looser linked SDRs with diploid selection only:}
+\textcolor{red}{New sex-determining alleles are thought to spread when they arise in linkage with loci that experience sex differences in selection due to beneficial associations between alleles that determine sex and alleles that are favoured in that sex~\cite{vanDoorn:2007eu,vanDoorn:2010hu,Ubeda:2015fx,Muralidhar2018}.
+However, when loci are 
+that tight ancestral-linkage of polymorphic loci, maintained by sexually-antagonistic selection or otherwise, can also drive trans-GSD transitions.
+}
+
+% Evidence
+\textcolor{red}{Evidence: Our results show, however, that tight ancestral-linkage of polymorphic loci, maintained by sexually-antagonistic selection or otherwise, can also drive trans-GSD transitions.
+In addition, we find that polymorphic sex determining systems (X, Y, W, and Z alleles all present) can be maintained when a selected locus is tightly linked to the ancestral sex-determining system (e.g., \nameref{fig:freqAll}B and \nameref{fig:freqAll}C), which is not possible with loose linkage~\cite{vanDoorn:2010hu}.
+For example, our results suggest a potential mechanism maintaining multiple sex determining alleles in the platyfish (\textit{Xiphophorus maculatus}), in which X,Y, and W alleles segregate at one locus (or two closely-linked loci) near to potentially sexually-antagonistic genes for pigmentation and sexual maturity~\cite{Kallman1965,Kallman1968, Volff2001, Schultheis2006}.
+Several rodent species also maintain feminizing alleles along with the ancestral X and Y sex-determination alleles (reviewed in~\cite{Fredga1994}). 
+For example, in nine \textit{Akadon} species, it appears that male-determining-\textit{sry} expression is suppressed by an autosomal feminizing allele, creating XY females~\cite{Bianchi2002,Sanchez2010}, which have increased fitness relative to XX females~\cite{Hoekstra2001}.
+In \textit{Mus microtoides}, females can have XX, XX$^\ast$ or X$^\ast$Y genotypes~\cite{Veyrunes2010}. 
+Previous theory would predict that the X$^\ast$ chromosome (or the autosome it is fused to) harbours female beneficial alleles, driving its spread. 
+However, XX and XX$^\ast$ females have similar fitness, whereas X$^\ast$Y female fitness is enhanced~\cite{Saunders2014,Saunders2016, Veyrunes2017}.
+Although Y-linkage of female-beneficial alleles is counterintuitive, our model suggests that it can be stably maintained and then favour new feminizing mutations, which is a parsimonious explanation for the spread of feminizing alleles in these rodent species.
+}
+
 %MAIN RESULT
@@
 %The latter predicts that neo-W alleles will invade an XY system when there is a male bias caused by haploid selection in males, and vice-versa, a neo-Y will invade a ZW system when there is a female bias caused by haploid selection in females~\cite{Kozielska:2010vm,Ubeda:2015fx}.
-In contrast to these prevailing views, we show that selection (including sexually-antagonistic selection, overdominance, and/or ploidally-antagonistic selection) on loci tightly linked to the ancestral sex-determining locus can favour trans-GSD transitions (XY$\leftrightarrow$ ZW) to new sex-determining systems that are less closely linked to the selected loci (e.g., see Fig \ref{fig:SexAntagTighter}).
+In contrast to these prevailing views, we show that selection (including sexually-antagonistic selection, overdominance, and/or ploidally-antagonistic selection) on loci tightly linked to the ancestral sex-determining locus can favour trans-GSD transitions (XY$\leftrightarrow$ ZW) to new sex-determining systems that are less closely linked to the selected loci ($r>R$, e.g., see Fig \ref{fig:SexAntagTighter}).
 Similarly, even when linkage is weak relative to selection, we show that %new sex-determining alleles are typically favoured if they are more closely linked to a locus under haploid selection (even in the absence of diploid sex differences), which is the only condition favouring cis-GSD transitions (XY to XY or ZW to ZW).

### 2018-04-02 LaTeX/main_revised.tex
refining responses, attempting to pass off to mscott

@@
 % Please keep the abstract below 300 words
-%currently 312 words
+%currently 308 words
 \section*{Abstract}
 Sex determination is remarkably dynamic; many taxa display shifts in the location of sex-determining loci or the evolution of entirely new sex-determining systems. 
-Predominant theories for why we observe such transitions generally conclude that novel sex-determining systems are favoured by selection if they equalise the sex ratio or increase linkage with a \textcolor{red}{sexually-antagonistic locus}.
+Predominant theories for why we observe such transitions generally conclude that novel sex-determining systems are favoured by selection if they equalise the sex ratio or increase linkage with a locus that experiences different selection in males vs.\ females.
 We use population genetic models to extend these theories in two ways: 
 (1) We explicitly consider selection on loci very tightly linked to the ancestral sex-determining loci, e.g., within the non-recombining region of the ancestral sex chromosomes. 
-Variation at such loci can favour the spread of new sex-determining systems in which the heterogametic sex changes (XY to ZW or ZW to XY) and the new sex-determining region is less closely linked (or unlinked) to the locus under selection, which is not predicted by previous theory.
-(2) We consider selection upon haploid genotypes either during gametic competition (e.g., pollen/sperm competition involving multiple males) or meiosis (i.e., non-Mendelian segregation), which can cause the zygotic sex ratio to become biased.
-We find that associations with haploid selected loci can drive transitions between sex-determining systems \textcolor{red}{, without requiring sexually-antagonistic selection in diploids}. 
-Unexpectedly, with haploid selection, transitions between male and female heterogamety can also evolve where linkage with the sex-determining locus is weakened. 
-Furthermore, sex-ratio biases may increase or decrease with the spread of new sex chromosomes. 
-Thus, we find that transitions between sex-determining systems cannot be simply predicted by selection to equalise the sex ratio. 
+Variation at such loci can favour the spread of new sex-determining systems in which the heterogametic sex changes (XY to ZW or ZW to XY) and the new sex-determining region is less closely linked (or even unlinked) to the locus under selection, which is not apparent from previous theory.
+(2) We consider selection upon haploid genotypes either during gametic competition (e.g., pollen competition) or meiosis (i.e., non-Mendelian segregation), which can cause the zygotic sex ratio to become biased.
+We find that associations with haploid selected loci can drive transitions between sex-determining systems, without requiring selection to act differently in diploid males vs.\ females. 
+Further, with haploid selection, transitions between male and female heterogamety can also evolve where linkage with the sex-determining locus is weakened. 
+Unexpectedly, we find that the selective strengths exerted by the sex-ratio and associations with selected alleles are equivalent.
+This allows sex-ratio biases to increase or decrease with the spread of new sex chromosomes, and implies that transitions between sex-determining systems cannot be simply predicted by selection to equalise the sex ratio.
 Overall, our models reveal that transitions between sex-determining systems, particularly transitions where the heterogametic sex changes, can be driven by loci in previously unpredicted genomic locations that experience selection during diploid and/or haploid phases.
-These results predict conditions under which sex-determining systems are likely to be labile and draw connections with sex-ratio evolution.
+%Our results predict conditions under which sex-determining systems are likely to be labile and draw connections with sex-ratio evolution.
 
@@
 %Tight linkage Model Feature and Result
-One novel feature of the models developed here is that we explicitly \textcolor{red}{(is this wording fair to vD\&K?)} consider loci in very tight linkage with the ancestral sex-determining locus (e.g., within the non-recombining region of a sex chromosome).
-% in the results section: `Tight linkage with the ancestral sex-determining locus').
-Our analysis shows that, under various forms of selection, the ancestral-X can carry suboptimal alleles for females and/or the ancestral-Y can carry female-beneficial alleles. 
-This, in turn, can favour a new ZW sex-determining locus that has weaker linkage with loci under selection, which has not been predicted by previous theory. 
+One novel feature of the models developed here is that, when considering loci in very tight linkage with the ancestral sex-determining locus (e.g., within the non-recombining region of a sex chromosome), % in the results section: `Tight linkage with the ancestral sex-determining locus').
+%\textcolor{red}{[vDK2007 does "explicitly" consider this as well (although on pg 15 of their SOM they say they will ignore equilibrium A, as it is stable under a "limited range of biologically relevant parameter combinations"; perhaps haploid selection changes this impression), but only for cis-GSD transitions.
+They find that if equil B is stable the neo-Y never spreads when r=0.
+vDK2010 does not "explicitly" calculate pX and pY, which are required to see if their equation 7 is positive or negative, but nowhere do they seem to say that weaker linkage \textit{can't} evolve given r initially small.]}
+we explicitly calculate ancestral equilibrium allele frequencies.
+This analysis uncovers that, under various forms of selection, the ancestral-X can carry suboptimal alleles for females and/or the ancestral-Y can carry female-beneficial alleles. 
+This, in turn, can favour a new ZW sex-determining locus that has weaker linkage with loci under selection, which has not been apparent in previous theory \cite{vanDoorn:2010hu}. 
 That is, very tight linkage with the ancestral GSD locus can favour trans-GSD transitions in which associations with selected loci are actually weakened.
@@
 With intermediate $k$, we can interpret $m$ as an environmental sex-determination (ESD) allele, such that zygotes develop as females in a proportion ($k$) of the environments they experience. 
-The assumption that derived sex-determining loci are epistatically dominant is motivated by empirical systems in which multiple sex determining alleles segregate (i.e., X, Y, Z, and W alleles present), such as, cichlid fish~\cite{Ser:2010iq}, platyfish (\textit{Xiphophorus maculatus}~\cite{Kallman1968}), houseflies (\textit{Musca domestica} \textcolor{red}{CITATION}), western clawed frogs (\textit{Xenopus tropicalis}~\cite{Roco2015}) and \textit{Rana rugosa}~\cite{Ogata:2007jm}.
+The assumption that derived sex-determining loci are epistatically dominant is motivated by empirical systems in which multiple sex determining alleles segregate (i.e., X, Y, Z, and W alleles present), such as, cichlid fish~\cite{Ser:2010iq}, platyfish (\textit{Xiphophorus maculatus}~\cite{Kallman1968}), houseflies (\textit{Musca domestica}~\cite{Dubendorfer2002}), western clawed frogs (\textit{Xenopus tropicalis}~\cite{Roco2015}) and \textit{Rana rugosa}~\cite{Ogata:2007jm}.
 Nevertheless, our supplementary analysis file (\nameref{file:Mathematica}) allows other dominance relationships between loci to be specified. 
+See also the supplementary material in \cite{vanDoorn:2007eu} for a numerical analysis that relaxes the assumption of epistatic dominance.
 %We also analyze a model of maternally-controlled environmental sex-determination, where mothers with at least one $m$ allele produce daughters with probability $k$.
@@
 \noindent\textit{Conclusion 1A:}
-\textbf{selection on loci within the non-recombining region around the sex-determining locus ($r\approx0$) allows the invasion of less closely linked sex-determining alleles ($r<R\leq1/2$) during a trans-GSD transition}.
-%\textcolor{red}{[new result for sex-antagonism and overdominance, but already shown by Kozielska for ploidy-antagonism]}
+\textbf{selection on loci within the non-recombining region around the sex-determining locus ($r\approx0$) allows the invasion of less closely linked sex-determining alleles ($r<R\leq1/2$) during a trans-GSD transition} (XY $\leftrightarrow$ ZW).
 \vspace{0.5cm}
@@
 The invasion of completely unlinked neo-W alleles ($R = 1/2$) can occur with overdominance in males or with haploid selection (as shown for the case of male drive opposed by diploid selection in \cite{Kozielska:2010vm}) but is not possible with only sexually-antagonistic selection if selection is directional in each diploid sex (see \nameref{file:Mathematica}).
+\textcolor{red}{In absence of haploid selection Conclusion 1A can also be reached from Equation 7 in \cite{vanDoorn:2010hu}; for example, with no polymorphism on the Y ($V_Y=0$) and an allelic substitution favoured in females ($\alpha^f,\alpha_X^f>0$) a loosely linked neo-W can invade given the allelic substitution is sufficiently disfavoured on the X in males ($\alpha_X^m < -2\alpha_X^f$), although it is unclear from their implicit equation if and when such an equilibrium is stable.}
 %\vspace{0.5cm}
@@
 
-However, with haploid selection and $r<1/2$, the additional term in Eq \eqref{eq:lambda_neoW} can be positive.
-This implies, 
+However, with haploid selection and some ancestral sex-linkage ($r<1/2$; allowing allele frequency differences on the X and Y), the additional term in Eq \eqref{eq:lambda_neoW} can be positive.
+This implies the following two conclusions: 
 \vspace{0.5cm}
 
+%\noindent\textit{Conclusion 1B:}\
+%\textbf{when there is an intermediate rate of recombination between the ancestral sex-determining allele and a selected locus ($0<r<1/2$), haploid selection allows less closely linked sex-determining alleles ($r<R$) to invade during trans-GSD transitions ($\lambda_{W'}^{(XY)}>1$).}
+%%\textcolor{red}{[new result because Kozielska had ancestrally-tight sex-linkage and Ubeda had ESD]}
+%\vspace{0.5cm}
+
 \noindent\textit{Conclusion 1B:}\
-\textbf{when there is an intermediate rate of recombination between the ancestral sex-determining allele and a selected locus ($0<r<1/2$), haploid selection allows less closely linked sex-determining alleles ($r<R$) to invade during trans-GSD transitions ($\lambda_{W'}^{(XY)}>1$).}
-%\textcolor{red}{[new result because Kozielska had ancestrally-tight sex-linkage and Ubeda had ESD]}
+%\textbf{new sex-determining alleles (causing trans-GSD transitions) can spread if they arise in looser linkage with a locus that experiences haploid selection ($r<R$). }
+\textbf{haploid selection on loci weakly linked to the sex-determining locus ($0<r<1/2$) allows the invasion of less closely linked sex-determining alleles ($r<R\leq1/2$) during a trans-GSD transition} (XY $\leftrightarrow$ ZW).
 \vspace{0.5cm}
 
-\noindent\textcolor{red}{\textit{Conclusion 2A:}\
-\textbf{New sex-determining alleles (causing cis- \textit{or} trans-GSD transitions) can spread if the arise in closer linkage with a locus that experiences haploid selection than the ancestral-sex-determining locus ($R<r$).} (This is different but similar to Ubeda et al (2015), who started from ESD)}
-
-\noindent\textcolor{red}{\textit{Conclusion 2B:}\
-\textbf{New sex-determining alleles (causing trans-GSD transitions) can spread if they arise in looser linkage with a locus that experiences haploid selection than the ancestral-sex-determining locus ($r<R$).
-} }
+\noindent{\textit{Conclusion 2:}\
+\textbf{new sex-determining alleles (causing cis- \textit{or} trans-GSD transitions) can spread if they arise in closer linkage with a locus that experiences haploid selection ($R<r$). }
+%(This is different but similar to Ubeda et al (2015), who started from ESD)
+\vspace{0.5cm}
+
+\noindent The numerical results of \cite{Ubeda:2015fx} are consistent with Conclusion 1B, but arise from an ESD to GSD transition, where the ancestral equilibrium is considerably simpler.
+Conclusion 2 echoes the diploid-selection-only results of \cite{vanDoorn:2007eu,vanDoorn:2010hu}, but greatly extends the number of selective scenarios favouring transitions.
 
@@
 %Indeed, invasion typically occurs when the neo-W is more closely linked to the selected locus than the ancestral sex-determining region (Fig \ref{fig:Combination_Centimorgans}).
-To clarify the parameter space under which invasion occurs despite looser sex-linkage ($\lambda_{W'}^{(XY)}>1$ despite $R>r$), we focus on the special case where $R=1/2$ and $r<1/2$ (e.g., the selected locus is on the ancestral sex chromosome and the novel sex-determining locus arises on an autosome).
+To clarify the parameter space under which invasion occurs despite looser sex-linkage ($\lambda_{W'}^{(XY)}>1$ despite $R>r$; Conclusion 1B), we focus on the special case where $R=1/2$ and $r<1/2$ (e.g., the selected locus is on the ancestral sex chromosome and the novel sex-determining locus arises on an autosome).
 In Table \ref{tab:specialcases} we give the conditions where invasion occurs when we further assume that haploid selection only occurs in one sex (e.g., during male meiosis only) and dominance coefficients are equal in the two sexes, $h^\female=h^\male$.
@@
 %However, to leading order with selection weak relative to recombination, we find that sex-ratio selection favours the spread of a neo-W by an amount equl to the spread of a neo-Y into a ZW system (relabeling XY as the heterogametic sex and reversing the labels of males and females in Table \ref{tab:specialcases})
-However, invasion by a neo-W allele into an XY system and invasion by a neo-Y allele into a ZW system occur under the same conditions ($\lambda_{Y'}^{(XY)} = \lambda_{W'}^{(ZW)}$ and $\lambda_{W'}^{(XY)}=\lambda_{Y'}^{(ZW)}$, at least to order $\epsilon^2$), implying that
+However, invasion by a neo-W allele into an XY system and invasion by a neo-Y allele into a ZW system occur under the same conditions ($\lambda_{Y'}^{(XY)} = \lambda_{W'}^{(ZW)}$ and $\lambda_{W'}^{(XY)}=\lambda_{Y'}^{(ZW)}$, at least to order $\epsilon^2$), implying that, surprisingly,
 \vspace{0.5cm}
@@
 
-\noindent\textcolor{red}{\textit{Conclusion 3:}
-\textbf{when selection is weak relative to recombination, sex-ratio selection is exactly equal in magnitude to the selection imposed by associations with selected alleles. } }
-%\textcolor{red}{[new result]}
-\vspace{0.5cm}
+%\noindent\textcolor{red}{\textit{Conclusion 3:}
+%\textbf{when selection is weak relative to recombination, sex-ratio selection is exactly equal in magnitude to the selection imposed by associations with selected alleles. } }
+%%\textcolor{red}{[new result]}
+%\vspace{0.5cm}
 
@@
 We next consider the case where the new sex-determining mutation, $m$, causes sex to be determined probabilistically or by heterogeneous environmental conditions (environmental sex determination, ESD), with individuals carrying allele $m$ developing as females with probability $k$.
-\textcolor{red}{In our deterministic model this means the fraction female is exactly $k$, even when $m$ is rare (exploring the effect of the variance induced by ESD would also be interesting).}
+%\textcolor{red}{In our deterministic model this means the fraction female is exactly $k$, even when $m$ is rare (exploring the effect of the variance induced by ESD would also be interesting).}
+In our deterministic model this means the fraction female is exactly $k$, even when $m$ is rare (exploring the effect of the variance induced by ESD would also be interesting).
 Here, we do not assume that the environmental conditions that determine sex also differentially affect the fitness of males versus females. 
@@
 
-\noindent\textit{Conclusion 3:}
+\noindent\textit{Conclusion 4:}
 \textbf{
@@
 %As with sexually-antagonistic selection, the presence of haploid selected loci around ancestral- or novel-sex-determining regions could support their role in sex chromosome turnover.
-In agreement with this hypothesis, a recent transcriptome analysis in Rumex shows that pollen-biased expression (relative to expression in flower buds or leaves) is enhanced among XY-linked genes compared to autosomal genes or compared to hemizygous genes that are only linked to the X (Sandler et al., 2018, personal communication).
+In agreement with this hypothesis, a recent transcriptome analysis in Rumex shows that pollen-biased expression (relative to expression in flower buds or leaves) is enhanced among XY-linked genes compared to autosomal genes or compared to hemizygous genes that are only linked to the X
+\cite{Sandler264382}. 
 In addition, Y-linked genes are over-expressed relative to X-linked genes in pollen (but not in flower buds or leaves). 

### 2018-04-04 LaTeX/main_revised.tex
changes to be merged

--- 2018-03-29 LaTeX/main_revised.tex
@@
 We find that a neo-Y allele can never invade an ancestral XY system that already has tight linkage with the locus under selection ($\lambda_{Y'}^{(XY)} \leq 1$ when $r=0$, for details see \nameref{file:Mathematica}).
-When $R=0$, a neo-Y haplotype with the same allele as the ancestral Y is neutral ($\Lambda_{Y'a}^{(XY)}=1$) and does not change in frequency.
-The other neo-Y haplotype will not spread ($\Lambda_{Y'A}^{(XY)}<1$) given that the initial equilibrium is stable. 
-Therefore, a neo-Y mutation cannot spread in an ancestral XY system ($\lambda_{Y'}^{(XY)} \leq 1$, regardless of $R$) where selected loci are within or very near the non-recombining region around the sex-determining locus.
+%When $R=0$, a neo-Y haplotype with the same allele as the ancestral Y is neutral ($\Lambda_{Y'a}^{(XY)}=1$) and does not change in frequency.
+%The other neo-Y haplotype will not spread ($\Lambda_{Y'A}^{(XY)}<1$) given that the initial equilibrium is stable. 
+%Therefore, a neo-Y mutation cannot spread in an ancestral XY system ($\lambda_{Y'}^{(XY)} \leq 1$, regardless of $R$) where selected loci are within or very near the non-recombining region around the sex-determining locus.
 In essence, through tight linkage with the $\mathbf{A}$ locus, the ancestral Y becomes strongly specialized on the allele that has the highest fitness across male haploid and diploid phases. 
@@
 \noindent\textit{Conclusion 1A:}
-\textbf{selection on loci within the non-recombining region around the sex-determining locus ($r\approx0$) allows the invasion of less closely linked sex-determining alleles ($r<R\leq1/2$) during a trans-GSD transition}.
+\textbf{selection on loci within the non-recombining region around the sex-determining locus ($r\approx0$) drives the invasion of less closely linked sex-determining alleles ($r<R\leq1/2$) during a trans-GSD transition}.
 %\textcolor{red}{[new result for sex-antagonism and overdominance, but already shown by Kozielska for ploidy-antagonism]}
@@
 The conditions become more restrictive, however, with increasing recombination ($R$) between the new sex-determining locus and the selected locus.  
-The invasion of completely unlinked neo-W alleles ($R = 1/2$) can occur with overdominance in males or with haploid selection (as shown for the case of male drive opposed by diploid selection in \cite{Kozielska:2010vm}) but is not possible with only sexually-antagonistic selection if selection is directional in each diploid sex (see \nameref{file:Mathematica}).
+The invasion of completely unlinked neo-W alleles ($R = 1/2$) can occur with overdominance in males or with haploid selection (e.g., a case with male drive opposed by diploid selection in \cite{Kozielska:2010vm}) but is not possible with only sexually-antagonistic selection where selection is directional in each diploid sex (see \nameref{file:Mathematica}).
+Here, we focus on cases where there is no haploid selection and discuss the additional effect of haploid selection in \nameref{app:inv_cond}. 
+Essentially, neo-W alleles are able to invade (even with $R>r$) because the ancestral X experiences selection in males. 
+This can lead to (1) XX females having lower than maximum fitness ($\Lambda_{W'A}^{(XY)}>1$) and/or (2) the Y carrying alleles that are beneficial in females.
+
 %\vspace{0.5cm}
@@
 
-To develop an intuition for how less closely linked neo-W alleles invade ($R>r$), we here focus on cases where there is no haploid selection and discuss the additional effect of haploid selection in \nameref{app:inv_cond}.
+%To develop an intuition for how less closely linked neo-W alleles invade ($R>r$), we here focus on cases where there is no haploid selection and discuss the additional effect of haploid selection in \nameref{app:inv_cond}.
 If we categorise the $a$ allele as being ancestrally `male-beneficial' via the fact that it is fixed on Y backgrounds, then $\Lambda_{W'A}^{(XY)}>1$ indicates that the neo-W spreads when found with the ancestrally `female-beneficial' allele.
@@
 When there is haploid selection, invasion also typically occurs when the neo-W is more closely linked to the selected locus than the ancestral sex-determining region (Fig \ref{fig:Combination_Centimorgans}).
-For example, if the $\mathbf{A}$ locus is unlinked to the ancestral sex-determining locus ($r=1/2$), a more closely linked neo-W ($R<1/2$) can always invade.
-In this case, there is no ancestral association between $\mathbf{A}$ alleles and sex chromosomes in males, $\left( \hat{p}^\male_Y-\hat{p}^\male_X \right)=0$, see Eq \eqref{eq:freq_diffs}. 
-The second term in Eq \eqref{eq:lambda_neoW} therefore disappears and invasion depends only on the sign of $(r-R)$.%, as in the case of the neo-Y.
+For example, if the $\mathbf{A}$ locus is unlinked to the ancestral sex-determining locus ($r=1/2$, which implies that $ \hat{p}^\male_Y-\hat{p}^\male_X =0$), a more closely linked neo-W ($R<1/2$) can always invade.
+Thus,
+%In this case, there is no ancestral association between $\mathbf{A}$ alleles and sex chromosomes in males, $\left( \hat{p}^\male_Y-\hat{p}^\male_X \right)=0$, see Eq \eqref{eq:freq_diffs}. 
+%The second term in Eq \eqref{eq:lambda_neoW} therefore disappears and invasion depends only on the sign of $(r-R)$.%, as in the case of the neo-Y.
 
@@
 
+%However, with haploid selection and $r<1/2$, the additional term in Eq \eqref{eq:lambda_neoW} can be positive.
+%This implies, 
+%\vspace{0.5cm}
+
+%\noindent\textit{Conclusion 1B:}\
+%\textbf{when there is an intermediate rate of recombination between the ancestral sex-determining allele and a selected locus ($0<r<1/2$), haploid selection allows less closely linked sex-determining alleles ($r<R$) to invade during trans-GSD transitions ($\lambda_{W'}^{(XY)}>1$).}
+%\textcolor{red}{[new result because Kozielska had ancestrally-tight sex-linkage and Ubeda had ESD]}
+%\vspace{0.5cm}
+
+\vspace{0.5cm}
+\noindent\textcolor{red}{\textit{Conclusion 2A:}\
+\textbf{new sex-determining alleles (causing cis- \textit{or} trans-GSD transitions) can spread if the arise in closer linkage with a locus that experiences haploid selection than the ancestral-sex-determining locus ($R<r$).} (This is different but similar to Ubeda et al (2015), who started from ESD)}
+\vspace{0.5cm}
+
 However, with haploid selection and $r<1/2$, the additional term in Eq \eqref{eq:lambda_neoW} can be positive.
@@
 
-\noindent\textit{Conclusion 1B:}\
-\textbf{when there is an intermediate rate of recombination between the ancestral sex-determining allele and a selected locus ($0<r<1/2$), haploid selection allows less closely linked sex-determining alleles ($r<R$) to invade during trans-GSD transitions ($\lambda_{W'}^{(XY)}>1$).}
-%\textcolor{red}{[new result because Kozielska had ancestrally-tight sex-linkage and Ubeda had ESD]}
+\noindent\textcolor{red}{\textit{Conclusion 2B:}\
+\textbf{new sex-determining alleles (causing trans-GSD transitions) can spread if they arise in looser linkage with a locus that experiences haploid selection than the ancestral-sex-determining locus ($r<R$).
+} }
 \vspace{0.5cm}
-
-\noindent\textcolor{red}{\textit{Conclusion 2A:}\
-\textbf{New sex-determining alleles (causing cis- \textit{or} trans-GSD transitions) can spread if the arise in closer linkage with a locus that experiences haploid selection than the ancestral-sex-determining locus ($R<r$).} (This is different but similar to Ubeda et al (2015), who started from ESD)}
-
-\noindent\textcolor{red}{\textit{Conclusion 2B:}\
-\textbf{New sex-determining alleles (causing trans-GSD transitions) can spread if they arise in looser linkage with a locus that experiences haploid selection than the ancestral-sex-determining locus ($r<R$).
-} }
 
@@
 In Fig \ref{fig:SexRatioBad}, we also show that trans-GSD transitions in sex determination occur during which linkage with a haploid selected locus increases \textit{or} decreases. 
+\textcolor{red}{When $R>r$, neo-W alleles can benefit from Y-associated alleles that have higher fitness in the female diploid phase but then dissociate from these alleles during meiosis, which occurs before any subsequent haploid selection.
+}
 
@@
 
-Previous research has shown that when the ancestral sex-determining locus is linked to a locus that experiences haploid selection (e.g., meiotic drive), alleles at a new, unlinked sex-determining locus can invade and restore equal sex ratios~\cite{Kozielska:2010vm}.
-Consider, for example, the case where the $\mathbf{A}$ locus is linked to the ancestral sex-determining locus ($r<1/2$) and experiences meiotic drive in males only ($\alpha^\male_\Delta \neq 0$, $\alpha^\female_\Delta=0$), without gametic competition ($t^\female=t^\male=0$).
-In this case, the zygotic sex ratio can be initially biased only if the ancestral sex-determining system is XY (Fig \ref{fig:model_outline}A and Fig \ref{fig:SexRatioBad}B). 
+%Previous research has shown that when the ancestral sex-determining locus is linked to a locus that experiences haploid selection (e.g., meiotic drive), alleles at a new, unlinked sex-determining locus can invade and restore equal sex ratios~\cite{Kozielska:2010vm}.
+Our model allows us to consider GSD-GSD transitions where sex-ratio bias increases, decreases, or remains equal. 
+For example, if there is meiotic drive in males only ($\alpha^\male_\Delta \neq 0$, $\alpha^\female_\Delta=0$), without gametic competition ($t^\female=t^\male=0$) the zygotic sex ratio is initially biased only when the ancestral sex-determining system is XY (Fig \ref{fig:model_outline}A and Fig \ref{fig:SexRatioBad}A) and not ZW (Fig \ref{fig:SexRatioBad}B).
 %If the ancxestral sex-determining system is ZW, the zygotic sex ratio will be 1:1 because diploid sex is determined by the proportion of Z-bearing versus W-bearing eggs and meiosis in females is fair (Fig \ref{fig:Combination_Turnover}D).
@@
 \noindent\textcolor{red}{\textit{Conclusion 3:}
-\textbf{when selection is weak relative to recombination, sex-ratio selection is exactly equal in magnitude to the selection imposed by associations with selected alleles. } }
+\textbf{when selection is weak relative to recombination, the presence or absence of sex-ratio biases do not create an assymetry in the likelihood of GSD-GSD transitions. } }
 %\textcolor{red}{[new result]}
@@
 
-\noindent For example, in Fig \ref{fig:SexRatioBad}A neo-W alleles invade an ancestral-XY system where females are initially rare, equalizing the sex ratio.
+\noindent For example, in Fig \ref{fig:SexRatioBad}A neo-W alleles invade an ancestral-XY system where females are initially rare, equalizing the sex ratio (as occurs in \cite{Kozielska:2010vm}).
 However, Fig \ref{fig:SexRatioBad}B shows that a neo-Y can invade the resulting ZW system under the same conditions. 
-When $R<1/2$, the invading neo-Y becomes associated with the male meiotic drive allele and the zygotic sex ratio actually evolves to become male-biased (as in the scenarios considered in \cite{Kozielska:2010vm,Ubeda:2015fx}).
+When $R<1/2$, the invading neo-Y becomes associated with the male meiotic drive allele and the zygotic sex ratio actually evolves to become male-biased (as occurs in \cite{Ubeda:2015fx}, beginning from ESD).
 In this case, the neo-Y spreads because it is often found in males and can, if it carries the driven allele $a$, benefit from haploid selection in males (Fig \ref{fig:SexRatioBad}B).
@@
 \textcolor{red}{New sex-determining alleles are thought to spread when they arise in linkage with loci that experience sex differences in selection due to beneficial associations between alleles that determine sex and alleles that are favoured in that sex~\cite{vanDoorn:2007eu,vanDoorn:2010hu,Ubeda:2015fx,Muralidhar2018}.
-However, when loci are 
-that tight ancestral-linkage of polymorphic loci, maintained by sexually-antagonistic selection or otherwise, can also drive trans-GSD transitions.
+However, we show that loci tightly linked to the ancestral sex-determining locus can drive trans-GSD transitions that reduce linkage (Conclusion 1). 
+In addition, we find that polymorphic sex determining systems (X, Y, W, and Z alleles all present) can be maintained when a selected locus is tightly linked to the ancestral sex-determining system (e.g., \nameref{fig:freqAll}B and \nameref{fig:freqAll}C), which is not possible with loose linkage~\cite{vanDoorn:2010hu}.
 }
@@
 % Evidence
-\textcolor{red}{Evidence: Our results show, however, that tight ancestral-linkage of polymorphic loci, maintained by sexually-antagonistic selection or otherwise, can also drive trans-GSD transitions.
-In addition, we find that polymorphic sex determining systems (X, Y, W, and Z alleles all present) can be maintained when a selected locus is tightly linked to the ancestral sex-determining system (e.g., \nameref{fig:freqAll}B and \nameref{fig:freqAll}C), which is not possible with loose linkage~\cite{vanDoorn:2010hu}.
-For example, our results suggest a potential mechanism maintaining multiple sex determining alleles in the platyfish (\textit{Xiphophorus maculatus}), in which X,Y, and W alleles segregate at one locus (or two closely-linked loci) near to potentially sexually-antagonistic genes for pigmentation and sexual maturity~\cite{Kallman1965,Kallman1968, Volff2001, Schultheis2006}.
-Several rodent species also maintain feminizing alleles along with the ancestral X and Y sex-determination alleles (reviewed in~\cite{Fredga1994}). 
+\textcolor{red}{These results suggest a potential mechanism maintaining multiple sex determining alleles in species such as platyfish (\textit{Xiphophorus maculatus}), in which X,Y, and W alleles segregate at one locus (or two closely-linked loci) near to potentially sexually-antagonistic genes for pigmentation and sexual maturity~\cite{Kallman1965,Kallman1968, Volff2001, Schultheis2006}.
+Furthermore, several rodent species maintain feminizing alleles along with the ancestral X and Y sex-determination alleles (reviewed in~\cite{Fredga1994}). 
 For example, in nine \textit{Akadon} species, it appears that male-determining-\textit{sry} expression is suppressed by an autosomal feminizing allele, creating XY females~\cite{Bianchi2002,Sanchez2010}, which have increased fitness relative to XX females~\cite{Hoekstra2001}.
@@
 Although Y-linkage of female-beneficial alleles is counterintuitive, our model suggests that it can be stably maintained and then favour new feminizing mutations, which is a parsimonious explanation for the spread of feminizing alleles in these rodent species.
+}
+
+% Sex ratio bit.
+
+\textcolor{red}{move to discussion somewhere:
+Even in animal and plant species that have much larger and more conspicuous diploid phases than haploid phases, many loci have been shown to experience haploid selection through gamete competition and/or meiotic drive~\cite{Mulcahy:1996ha,JOSEPH:2004haa, Lalanne2004,Ubeda:2005gw,Fishman2005,Leppala2008,Leppala2013,Didion2015,Didion2016, Lindholm:2016cw}.
+%Segregation distortion provides putative evidence of haploid selection and can sometimes be attributed to meiotic drive and/or gametic competition~\cite{Lalanne2004,Fishman2005,Leppala2008,Leppala2013,Didion2015,Didion2016}.
+%Where it has been characterized, individual cases of meiotic drive are generally sex-limited, exclusively affecting male or female gametes~\cite{Ubeda:2005gw,Lindholm:2016cw}.
+%Gametic competition is also typically sex-limited, occurring primarily among male gametes, because there are typically many more pollen/sperm than required for fertilization.
+For example, recent studies have demonstrated that sperm competition in animals, even within a single ejaculate, can alter haploid allele frequencies and increase offspring fitness~\cite{Immler:2014im,Alavioon2017}.
+Nevertheless, as a proportion of all genes, a relatively small fraction are thought to be expressed and selected during competition in animal sperm, although precise estimates are uncertain~\cite{Zheng:2001fi,JOSEPH:2004haa,Vibranovski:2010et}.
+On the other hand, gametic competition may be particularly common in plants, which have a multicellular haploid stage.
+Artificial selection pressures applied to male gametophytes are known to cause a response to selection (e.g.,~\cite{Hormaza:1996cv,Ravikumar:2003uo,Hedhly:2004iv,Clarke:2004ir}). 
+60-70\% of all genes are expressed in the male gametophyte, and these genes exhibit stronger signatures of selection than randomly-chosen genes~\cite{Borg:2009jpa,Arunkumar:2013iq,Gossmann:2014dua}.
 }

### 2018-04-05 LaTeX/response.tex

@@
 \noindent\paragraph{Response}
-\textcolor{red}{One could interpret our diploid selection as fertility selection, or does the reviewer mean that we have only one selective event in the diploid phase?
-Sexual selection does seem like a different model though, with for example, male fitnesses depending on female frequencies.
-A note such as "We do not consider fertility or sexual selection." in the paragraph beginning near L111 might do it?}
+\textcolor{red}{One could interpret our diploid selection as fertility selection, or am I missing something?
+Sexual selection does seem like a different model though, with for example, male fitnesses depending on female frequencies; a note such as "We do not consider sexual selection" in the paragraph beginning near L111 might do it?}
 
@@
 \textcolor{blue}{We have made the suggested replacements.
-There is one exception.
-In the abstract we use the familiar term ``sperm competition" as an example of gametic competition, but we now explicitly state that we imply sperm from multiple males.
 %n the introduction we mention that sperm competition has been shown to alter allele frequencies and fitness, and in this case we now mention this was shown within a single ejaculate (L68).
@@
 \noindent\paragraph{Response}
-\textcolor{red}{I think that, with our deterministic model (where the number of binomial trials is infinite), the variance in the fraction male is 0, and so is the same as GSD.
-We could briefly mention this at the beginning or end of the ESD section, and say that modeling ESD in a finite population could be interesting?
-I've put in an attempt on L.}
+\textcolor{blue}{In our deterministic model (where the number of binomial trials is infinite), the variance in the fraction male is 0 with ESD, as it is with GSD. 
+We now mention this on L392: ``In our deterministic model this means the fraction female is exactly $k$, even when $m$ is rare (exploring the effect of the variance induced by ESD would also be interesting)."
+ }
 
@@
 The fourth paragraph explains how assuming ancestrally-tight sex-linkage produces previously unexpected transitions (one hole in current theory, and how we address it).
-The fifth paragraph discusses the potential complications of haploid selection for transitions (another hole in current theory).
+The fifth paragraph discusses the potential complications of haploid selection for transitions (a second hole in current theory).
 The sixth paragraph describes previous studies on transitions with haploid selection (attempts to address the second hole). 
@@
 \textcolor{blue}{
-We now give 3 main conclusions at the end of the introduction (L69) which echo those mentioned by the reviewer (looser linkage can evolve, equal selection to increase or decrease the sex ratio, ESD does not always invade biased sex ratio; all of which suggest haploid selection makes conditions for transitions more permissive).
-These are highlighted again in the results, in the style of Orr 1998:\\
+%We now give 3 main conclusions at the end of the introduction (L69) which echo those mentioned by the reviewer (looser linkage can evolve, equal selection to increase or decrease the sex ratio, ESD does not always invade biased sex ratio; all of which suggest haploid selection makes conditions for transitions more permissive).
+We now give 4 main conclusions in the results, in the style of Orr 1998:\\
 %(1) transitions are determined by both sex-ratio selection and selection on associated alleles,\\
@@
 (1B) haploid selection allows looser sex-linkage to evolve in trans-GSD transitions,\\
-(2) when selection is weak relative to recombination, sex-ratio selection is exactly equal in magnitude to the selection imposed by associations with selected alleles, and\\
-(3) transitions from genetic to environmental sex-determination are not straightforwardly predicted by selection to balance the zygotic sex ratio when haploid selection is present.
+(2) transitions can occur when new sex-determining alleles increase linkage with haploid selected loci,\\
+(3) when selection is weak relative to recombination, sex-ratio selection is exactly equal in magnitude to the selection imposed by associations with selected alleles, and\\
+(4) transitions from genetic to environmental sex-determination are not straightforwardly predicted by selection to balance the zygotic sex ratio when haploid selection is present.
 \vspace{0.25cm}\\
-These are all new results, although (1A) was shown for the special case of $r=0$, $R=1/2$, and ploidally-antagonistic selection in Kozielska et al 2010, which we now mention immediately below (1A). 
+As (1A), (1B), and (2) have some antecedents in the literature, we discuss these immediately below each conclusion. 
+%We also discuss, immediately below each conclusion, its novelty.
+%These are all new results, although (1A) was shown for the special case of $r=0$, $R=1/2$, and ploidally-antagonistic selection in Kozielska et al 2010, which we now mention immediately below (1A). 
 }
@@
 \noindent\paragraph{Response}
-\textcolor{blue}{We have rewritten the main conclusions (see Response 2.2).}
+\textcolor{blue}{We have rewritten the introduction, as well as our main conclusions (see Responses 2.1 and 2.2).}
 
@@
 \noindent\paragraph{Response}
-\textcolor{red}{This is obviously very important, and is commonly assumed (Kozielska et al.
+\textcolor{blue}{
+This is an important assumption.
+As discussed in the supplementary of van Doorn \& Kirkpatrick (2007, Nature), partial dominance and incomplete penetrance (partial epistatic dominance) reduce the range parameter values that favour transitions.
+However, this reduction in parameter space is smooth and does not preclude transitions, meaning the qualitative conclusions are robust.
+Further, there are many systems in which one sex-determining allele is epistatically dominant.
+And finally, our Mathematica file allows for arbitrary epistatic dominance coefficients.
+We now discuss the empirical evidence for epistatic dominance, our general Mathematica file, and the analysis of van Doorn and Kirkpartick when introducing our model (L117).
+}
+%\textcolor{red}{This is obviously very important, and is commonly assumed (Kozielska et al.
 2010, van Doorn and Kirkpatrick 2007, 2010).
@@
 Is this ``compatible" with our model?}
-
-\textcolor{red}{Our analysis shows that the end state of the system depends on the `epistatic dominance' (term removed from our paper?) of the loci.
+%
+%\textcolor{red}{Our analysis shows that the end state of the system depends on the `epistatic dominance' (term removed from our paper?) of the loci.
 Could draw this out more for this response.
@@
 \noindent\paragraph{Response}
-\textcolor{red}{The abstract and summary still seem to be a little over-selling...}
-\textcolor{blue}{We have performed an extensive re-arrangement (e.g., Response 2.1 and 2.2 and below) to improve the clarity of our writing, especially regarding the main results. 
-We believe that our new presentation makes the novel and unexpected features of our results much more apparent. }
-\textcolor{red}{In particular, as described at length below, we now give more weight to the two previous papers suggested (Kozielska et al 2010 and Ubeda et al 2015) and more precisely indicate which of our model features and results are new and unexpected.
-To be clear, we do not claim to be the first to include both haploid and diploid selection and the evolution of new sex-chromosomes and we do not consider the addition of sex-specific selection or analytical results for previously numerical models to be our most significant contributions.
+%\textcolor{red}{The abstract and summary still seem to be a little over-selling...}
+\textcolor{blue}{We have performed an extensive re-arrangement (e.g., Responses 2.1 and 2.2 and below) to improve the clarity of our writing, especially regarding the main results. 
+We believe that our new presentation makes the novel and unexpected features of our results much more apparent. 
+In particular, as described at length below, we now give more weight to the two previous papers suggested (Kozielska et al 2010 and Ubeda et al 2015) and more precisely indicate which of our model features and results are new and unexpected in light of these previous results.
+To be clear, we do not claim to be the first to include both haploid and diploid selection to a model investigating the evolution of new sex-chromosomes and we do not consider the addition of sex-specific selection or analytical results for previously numerical models to be our most significant contributions (again, see Responses 2.1 and 2.2 and below for more detail on what these are).
 }
@@
 For example, step 3 of Ubeda et al.
-(2015) involves the spread of a autosomal meiotic drive suppressor driven by Fisherian sex-ratio selection and Kozielska et al.
-(2010) show that ancestral sex-ratio bias can favour new sex determining systems.
-We found our result, that these forces are equal, such that there is no difference between the propensity for XY-ZW or ZW-XY transitions with selection weak relative to recombination, to be surprising.} \textcolor{blue}{To clarify our meaning we have rephrased as ``Surprisingly, we find the two forces (sex-ratio selection and associations with genes that have sex-specific effects) will often be equally strong, and thus neither dominates the spread of new sex-determining systems alone."}
+(2015) involves the spread of a autosomal meiotic drive suppressor favoured by Fisherian sex-ratio selection and Kozielska et al.
+(2010) show that ancestral sex-ratio bias can favour new sex determining systems that balance the sex ratio (now discussed in the Introduction, lines 56-66).
+We found our result, that these forces are exactly equal (with selection weak relative to recombination), such that there is no difference between the propensity for XY-ZW or ZW-XY transitions, to be surprising.
+To clarify our meaning we have rephrased (in Author summary): ``Surprisingly, we find the two forces (sex-ratio selection and associations with genes that have sex-specific effects) will often be equally strong, and thus neither dominates the spread of new sex-determining systems alone."}
 
@@
 \textcolor{blue}{To communicate this we have rephrased: ``Even more unexpectedly, we find that new sex-determining alleles can spread despite being less closely linked to selected loci under a wide range of conditions."
-We believe that the changes to the presentation of the Introduction and Results should also help to clarify this point further.
-(e.g., paragraph, lines 40-47, and more clearly highlighted conclusions on lines XXX).
+We believe that the changes to the presentation of the Introduction and Results should also help to clarify this point further (e.g., paragraph, lines 40-47, and more clearly highlighted conclusions on lines XXX; see Responses 2.1 and 2.2).
 }
-\textcolor{red}{We also discuss the results of Kozielska and Ubeda more thoroughly in the paragraph...}
+\textcolor{blue}{We discuss the related results of Kozielska and Ubeda on lines 261 and 350.}
 
@@
 \textcolor{blue}{
-We have rephrased line referred to here as ``Predominant theories accounting for transitions between GSD systems by selection involve selective differences between sexes (e.g., sexually antagonistic selection) or sex-ratio selection.".
-We think this phrasing includes sex-differences in drive (Ubeda et al 2015) under the term 'selective difference between the sexes' (occurring during haploid rather than diploid selection), see also Response 3.2.6.
+The line referred to used sexually-antagonistic selection as an example of ``selective differences between the sexes". 
+We believe the phrase 'selective differences between the sexes' includes sex-differences in drive (Ubeda et al 2015), which just occur during haploid rather than diploid selection (see also Response 3.2.6).
 }
-\textcolor{red}{Furthermore, we now discuss the Ubeda and Kozielska results, involving meiotic drive, thoroughly in paragraph...
+
+\textcolor{blue}{
+We have rephrased the line referred to here to clarify our focus on GSD: ``Predominant theories accounting for transitions between GSD systems by selection involve sex-ratio selection or selective differences between the sexes (e.g., sexually antagonistic selection)".
 }
@@
 \noindent\paragraph{Response}
-\textcolor{red}{As we now make clear, we do not look at the same situation as Ubeda et al 2015 and our contribution is not just to add sex specific viability and analytical results. 
-For example, Ubeda starts from ESD. 
+\textcolor{blue}{
+As we now make clear, we do not look at the same situation as Ubeda et al 2015 and our contribution is not just to add sex-specific viability. 
+In particular, Ubeda starts from ESD. 
 Therefore, associations with an ancestral sex-determining locus cannot build up. 
-These lead to some of our most surprising results (e.g., haploid selection favours trans-GSD transitions for a wider variety of genomic locations than diploid selection alone, non-invasion of ESD despite initial sex ratio bias).
+These lead to some of our most surprising results (e.g., haploid selection favours trans-GSD transitions for a wider variety of genomic locations than diploid selection alone; ESD does not invade despite initial sex-ratio bias).
 }
-\textcolor{blue}{It is true that Ubeda et al 2015 is a special case of our model. 
-However, Ubeda et al 2015 was primarily a numerical investigation, providing a less general treatment of this special case and developing less intuition.
-Further, our model and intuition-giving analytical solutions explore a much wider range of scenarios, allowing, for example, sex-specific selection (e.g., sex-antagonism) and various genomic arrangements (any order/linkage of the three loci).
+\textcolor{blue}{
+%It is true that Ubeda et al 2015 is a special case of our model. 
+%However, Ubeda et al 2015 was primarily a numerical investigation, providing a less general treatment of this special case and developing less intuition.
+Further, our model and intuition-giving analytical solutions explore a much wider range of scenarios than the numerical results of Ubeda, allowing, for example, sex-specific selection (e.g., sex-antagonism) and various genomic arrangements (any order/linkage of the three loci).
 Our model is thus much more general and clarifies just when one should expect to see the numerical results of Ubeda et al 2015.
-We have rephrased to make this clear (after discussing Ubeda et al 2015, see Response 2.1): ``Here we use mathematical models to clarify the conditions under which new sex-determining systems spread when individuals experience extremely general and potentially sex-specific selection at both diploid and haploid stages, which allows fitness differences between the sexes and sex-ratio biases to occur simultaneously."
+We have rephrased to make this clear (after discussing Ubeda et al 2015, see Response 2.1): ``Here, we analytically find the conditions under which new GSD or ESD systems spread with generic linkage between the loci involved (and generic sex-specific haploid and diploid selection)." (L67-69).
 }
@@
 \textcolor{blue}{In this study, we are referring to organisms, such as animals and angiosperms, in which the type of gamete depends on the sex of the diploid that produced it.
-In this respect, one could consider gametic selection among sperm to be a form of male-specific selection.
+In this respect, one could consider gametic selection among sperm, for example, to be a form of male-specific selection.
 However, as noted here, the dynamics of selection during gametic selection cannot be captured by a diploid selection coefficient, which is why we model selection upon haploid genotypes specifically in two ways.
 }
-\textcolor{red}{
-[could tie this in with an expanded explanation of the mating system and the way we model haploid selection (see Response 3.3).]}
+\textcolor{blue}{
+We have attempted to clarify by expanding our explanation of the mating system and the way we model haploid selection (see Response 3.2).}
 
@@
 \textcolor{blue}{In the absence of sex-differences in selection it is true that antagonistic drive is not needed, but \textit{differences} in haploid selection between the sexes are needed (e.g., drive in only one sex, maintained by ploidally-antagonistic selection).
-If drive was the same in both sexes, $\alpha^{m}=\alpha^{f}$ (and all diploid male/female selection terms equal), we show that the new sex-determining allele would not invade. 
+If drive was the same in both sexes, $\alpha^{m}=\alpha^{f}$ (and all other male/female selection terms also equal), we show that the new sex-determining allele would not invade (e.g., equation 2 and 3).
 In this sense haploid selection is similar to sex-specific diploid selection, and together haploid and diploid selection determine the differences in male vs.
 female fitness, which can drive sex-determination transitions (see Response 3.2.4).
-In this sentence, we are introducing the 'sex-specific' aspect of haploid selection in the way Ubeda et al (2015) considers it; i.e., associations with alleles favoured in one sex (or the gametes produced by that sex) should favour a new sex-determining allele.
-We now follow this sentence up with two sentences that clarify its meaning by comparing with the results of Kozielska et al (2010) and Ubeda et al (2015).}
+This sentence meant to introduce the 'sex-specific' aspect of haploid selection in the way Ubeda et al (2015) considers it; i.e., associations with alleles favoured in one sex (or the gametes produced by that sex) should favour a new sex-determining allele.
+We have rephrased to make this clear: ``Therefore, one might expect new sex-determining systems to benefit from close linkage with haploid selected loci, as found for sex-differences in diploid selection" (L51-53).
+We now follow this sentence up with a paragraph that clarifies its meaning by comparing with the results of Kozielska et al (2010) and Ubeda et al (2015).}
 
@@
 \noindent\paragraph{Response}
-\textcolor{blue}{While it was the focus of Ubeda et al 2015, the restricted scope of that study prevents us from generalizing beyond its special case (see Response 3.2.5).
-We have rephrased: ``It is not yet clear when new sex-determining alleles are favoured by associations with haploid selected alleles vs.
-sex-ratio bias, especially under a wide range of possible diploid selection regimes (e.g., sex-antagonism, overdominance)."
+\textcolor{blue}{While Ubeda et al 2015 did focus on sex ratio biases and haploid selected alleles, the system started with ESD, where there are no associations (see Response 3.1.4).
+Further, the restricted scope of that numerical study prevents us from generalizing beyond its special case (see Response 3.1.4).
+Lines 48-66 present a refurbished argument for why it is difficult to intuit the implications of haploid selection, while summarizing the results of Ubeda and Kozielska.
 }
@@
 \textcolor{blue}{Ubeda et al 2015 was already cited on line 396 of the original submission, where we mentioned that it showed that sex-ratio biases could become more severe during a transition.
-Nevertheless, we now discuss Ubeda et al 2015 in the introduction, results, and discussion.}
+Nevertheless, we now discuss Ubeda et al 2015 in the introduction, results, and discussion (see Responses above).}
 
@@
 \textcolor{blue}{We do not agree. 
-Given our definition of meiotic drive and gametic competition in the introduction, the two processes are different.
+Given our definition of meiotic drive and gametic competition in the Introduction, the two processes are different.
 In particular, meiotic drive is assumed to occur during meiosis, and thus is ``gametic competition" amongst the gametes produced by a single individual. 
@@
 Thus allele frequency changes can occur by gametic competition even if all individuals were homozygous (as long as there is a polymorphism).
-We have rephrased our definitions in the introduction to read: ``We use the term `meiotic drive' to refer to the biased (non-Mendelian) segregation of genotypes during gamete production (from one parent only) and the term `gametic competition' to refer to selection upon haploid genotypes within a gamete/gametophyte pool (from many parents)."
+We have rephrased our definitions in the Introduction to read: ``We use the term `meiotic drive' to refer to the biased (non-Mendelian) segregation of genotypes during gamete production (from one parent only) and the term `gametic competition' to refer to selection upon haploid genotypes within a gamete/gametophyte pool (from many parents)."
 }

### 2018-04-05 LaTeX/main_revised.tex

--- 2018-04-02 LaTeX/main_revised.tex
@@
 We use population genetic models to extend these theories in two ways: 
-(1) We explicitly consider selection on loci very tightly linked to the ancestral sex-determining loci, e.g., within the non-recombining region of the ancestral sex chromosomes. 
-Variation at such loci can favour the spread of new sex-determining systems in which the heterogametic sex changes (XY to ZW or ZW to XY) and the new sex-determining region is less closely linked (or even unlinked) to the locus under selection, which is not apparent from previous theory.
+(1) We consider the dynamics of loci very tightly linked to the ancestral sex-determining loci, e.g., within the non-recombining region of the ancestral sex chromosomes. 
+Variation at such loci can favour the spread of new sex-determining systems in which the heterogametic sex changes (XY to ZW or ZW to XY) and the new sex-determining region is less closely linked (or even unlinked) to the locus under selection, which is not expected from previous theory.
 (2) We consider selection upon haploid genotypes either during gametic competition (e.g., pollen competition) or meiosis (i.e., non-Mendelian segregation), which can cause the zygotic sex ratio to become biased.
-We find that associations with haploid selected loci can drive transitions between sex-determining systems, without requiring selection to act differently in diploid males vs.\ females. 
-Further, with haploid selection, transitions between male and female heterogamety can also evolve where linkage with the sex-determining locus is weakened. 
-Unexpectedly, we find that the selective strengths exerted by the sex-ratio and associations with selected alleles are equivalent.
+Haploid selection can drive transitions between sex-determining systems without requiring selection to act differently in diploid males vs.\ females. 
+With haploid selection, we find that transitions between male and female heterogamety can evolve where linkage with the sex-determining locus is either strengthened or weakened. 
+Furthermore, we find that the selective strengths exerted by the sex-ratio and associations with selected alleles are often equivalent. 
 This allows sex-ratio biases to increase or decrease with the spread of new sex chromosomes, and implies that transitions between sex-determining systems cannot be simply predicted by selection to equalise the sex ratio.
@@
 Prevailing views suggest that new sex-determining systems are favoured when they equalize the sex ratio and/or when they are more closely linked to genes that experience differential selection in males and females.
-Our models extend these theories to include selection upon haploid genotypes (meiotic drive or gametic competition), which causes sex-ratio biases and occurs differently in male and female gametes. 
+Our models include selection upon haploid genotypes (meiotic drive or gametic competition), which causes sex-ratio biases and occurs differently in male and female gametes. 
 Surprisingly, we find the two forces (sex-ratio selection and associations with genes that have sex-specific effects) will often be equally strong, and thus neither dominates the spread of new sex-determining systems alone.
-Even more unexpectedly, we find that new sex-determining alleles can spread despite being less closely linked to selected loci under a wide range of conditions. 
+Even more unexpectedly, we find that new sex-determining alleles can spread despite being less closely linked to selected loci. 
 Therefore, our models predict loci in previously unexpected genomic locations and/or experiencing various types of selection (including haploid selection) can now be implicated as drivers of transitions between sex-determining systems.
@@
 %(1) sex-ratio selection
-Predominant theories accounting for transitions between GSD systems by selection involve sex-ratio selection or selective differences between the sexes (e.g., sexually antagonistic selection)~\cite{Blaser2012, Beukeboom:2014vb,vanDoorn2014re}.
+%Predominant theories accounting for transitions between GSD systems by selection involve sex-ratio selection or selective differences between the sexes (e.g., sexually antagonistic selection)~\cite{Blaser2012, Beukeboom:2014vb,vanDoorn2014re}.
 %\citet{Bull:1977wt} shows that direct selection on new sex determination loci can allow them to spread and switch between male and female heterogamety. 
-`Fisherian' sex-ratio selection favours a 1:1 zygotic sex ratio when assuming that males and females are equally costly to produce~\cite{Fisher:1930wy,Charnov:1982wg}.
+It has been suggested that sex-ratio selection is a particularly dominant force in the evolution of sex determination because the sex ratio is directly determined by the sex-determining system (e.g., Bull, 1983, p 66-67 ~\cite{Bull:1983vi}; Buekeboom and Perrin, 2014, Chapter 7~\cite{Beukeboom:2014vb}).
+Classic `Fisherian' sex-ratio selection favours a 1:1 zygotic sex ratio when assuming that males and females are equally costly to produce~\cite{Fisher:1930wy,Charnov:1982wg}. 
 This follows from the fact that, for an autosomal locus, half of the genetic material is inherited from a male and half from a female~\cite{West:2009we}. 
@@
 Selection therefore typically favours mutants that increase investment in the rarer sex.
-Because the sex ratio is directly determined by the sex-determining system, it has been suggested that sex-ratio selection is a particularly dominant force in the evolution of sex determination (e.g., Bull, 1983, p 66-67 ~\cite{Bull:1983vi}; Buekeboom and Perrin, 2014, Chapter 7~\cite{Beukeboom:2014vb}).
+%Because the sex ratio is directly determined by the sex-determining system, it has been suggested that sex-ratio selection is a particularly dominant force in the evolution of sex determination (e.g., Bull, 1983, p 66-67 ~\cite{Bull:1983vi}; Buekeboom and Perrin, 2014, Chapter 7~\cite{Beukeboom:2014vb}).
 
@@
 %(2) sex-antagonism
-Loci experiencing sexual antagonism have been shown to favour the spread of new genetic sex-determining alleles that are closely linked~\cite{vanDoorn:2007eu,vanDoorn:2010hu,Muralidhar2018}. 
+The evolution of sex determination is also thought to be strongly influenced by differences in selection between the sexes ~\cite{Blaser2012, Beukeboom:2014vb,vanDoorn2014re}.
+For example, loci experiencing sexual antagonism have been shown to favour the spread of new genetic sex-determining alleles that are closely linked~\cite{vanDoorn:2007eu,vanDoorn:2010hu,Muralidhar2018}.
 %van Doorn and Kirkpatrick~\cite{vanDoorn:2007eu,vanDoorn:2010hu} and Muralidhar and Veller~\cite{Muralidhar2018} have shown that new sex-determining alleles can be favoured if they arise at loci in close linkage with a locus that experiences sexual antagonism.
@@
 Such associations can favour cis-GSD transitions~\cite{vanDoorn:2007eu}, trans-GSD transitions~\cite{vanDoorn:2010hu}, and new partially-masculinizing or partially-feminizing alleles in a population with ESD~\cite{Muralidhar2018}.
-However, any sexually-antagonistic loci that are more closely linked to the ancestral sex-determining locus will develop similar, favourable associations and are expected to hinder the spread of a new sex-determining system~\cite{vanDoorn:2007eu,vanDoorn:2010hu}.
+However, any sexually-antagonistic loci that are more closely linked to the ancestral sex-determining locus should develop similar, favourable associations and are expected to hinder the spread of a new sex-determining system~\cite{vanDoorn:2007eu,vanDoorn:2010hu}.
 
 %Tight linkage Model Feature and Result
-One novel feature of the models developed here is that, when considering loci in very tight linkage with the ancestral sex-determining locus (e.g., within the non-recombining region of a sex chromosome), % in the results section: `Tight linkage with the ancestral sex-determining locus').
+One novel feature of the models developed here is that we explicitly consider the maintenance of genetic variation around the ancestral sex-determining locus (e.g., within the non-recombining region of a sex chromosome).
+%during trans-GSD transitions
+%, when considering loci in very tight linkage with the ancestral sex-determining locus (e.g., within the non-recombining region of a sex chromosome), 
 %\textcolor{red}{[vDK2007 does "explicitly" consider this as well (although on pg 15 of their SOM they say they will ignore equilibrium A, as it is stable under a "limited range of biologically relevant parameter combinations"; perhaps haploid selection changes this impression), but only for cis-GSD transitions.
@@
 vDK2010 does not "explicitly" calculate pX and pY, which are required to see if their equation 7 is positive or negative, but nowhere do they seem to say that weaker linkage \textit{can't} evolve given r initially small.]}
-we explicitly calculate ancestral equilibrium allele frequencies.
-This analysis uncovers that, under various forms of selection, the ancestral-X can carry suboptimal alleles for females and/or the ancestral-Y can carry female-beneficial alleles. 
+%we explicitly calculate ancestral polymorphisms. 
+Our analysis reveals that, under various forms of selection, the ancestral-X can carry suboptimal alleles for females and/or the ancestral-Y can carry female-beneficial alleles. 
 This, in turn, can favour a new ZW sex-determining locus that has weaker linkage with loci under selection, which has not been apparent in previous theory \cite{vanDoorn:2010hu}. 
-That is, very tight linkage with the ancestral GSD locus can favour trans-GSD transitions in which associations with selected loci are actually weakened.
+That is, we show that selected loci in very tight linkage with the ancestral GSD locus can favour trans-GSD transitions in which associations are actually weakened.
 
@@
 However, we also show that transitions involving haploid selection cannot be simply explained by invoking sex-ratio selection. 
-In particular, under a wide range of conditions, we show that haploid selection drives transitions in sex-determining system \textit{equally strongly} in situations where sex-ratio biases increase or decrease (and in situations where sex-ratio biases are present or absent).
+In particular, under a wide range of conditions, we show that transitions in sex-determining system are favoured \textit{equally strongly} in situations where sex-ratio biases increase or decrease (and in situations where sex-ratio biases are present or absent).
 Finally, we show that ESD may not evolve, even if the sex ratio is initially biased by haploid selection, which would not be predicted by previous theories for transitions to ESD~\cite{Charnov:1982wg,Bull:1983vi,West:2009we}.
-Together, in this context, our results suggest that sex ratio selection is not an overwhelming force driving transitions between sex-determining systems.
+Together, our results suggest that sex ratio selection is not an overwhelming force driving transitions between sex-determining systems.
 
@@
 %While both opposing selection in the diploid sexes and sex-ratio selection surely influence the evolution of new sex-determining factors, so too might selection in the haploid phase.
-\textcolor{red}{move to discussion somewhere:
-Even in animal and plant species that have much larger and more conspicuous diploid phases than haploid phases, many loci experience significant haploid selection through gamete competition and/or meiotic drive~\cite{Mulcahy:1996ha,JOSEPH:2004haa}.
-}
-
-\textcolor{red}{move to results somewhere:
-We use the term `meiotic drive' to refer to the biased (non-Mendelian) segregation of genotypes during gamete production (from one parent only) and the term `gametic competition' to refer to selection upon haploid genotypes within a gamete/gametophyte pool (from many parents); the term `haploid selection' encompasses both processes.
-}
-
-\textcolor{red}{move to discussion somewhere:
-Segregation distortion provides putative evidence of haploid selection and can sometimes be attributed to meiotic drive and/or gametic competition~\cite{Lalanne2004,Fishman2005,Leppala2008,Leppala2013,Didion2015,Didion2016}.
-Where it has been characterized, individual cases of meiotic drive are generally sex-limited, exclusively affecting male or female gametes~\cite{Ubeda:2005gw,Lindholm:2016cw}.
-Gametic competition is also typically sex-limited, occurring primarily among male gametes, because there are typically many more pollen/sperm than required for fertilization.
-Gametic competition may be particularly common in plants, in which 60-70\% of all genes are expressed in the male gametophyte, and these genes exhibit stronger signatures of selection than randomly-chosen genes~\cite{Borg:2009jpa,Arunkumar:2013iq,Gossmann:2014dua}.
-In addition, artificial selection pressures applied to male gametophytes are known to cause a response to selection (e.g.,~\cite{Hormaza:1996cv,Ravikumar:2003uo,Hedhly:2004iv,Clarke:2004ir}). 
-A smaller proportion of genes are thought to be expressed and selected during competition in animal sperm, although precise estimates are uncertain~\cite{Zheng:2001fi,JOSEPH:2004haa,Vibranovski:2010et}.
-Nevertheless, recent studies have demonstrated that sperm competition in animals, even within a single ejaculate, can alter haploid allele frequencies and increase offspring fitness~\cite{Immler:2014im,Alavioon2017}.
-}
 
@@
 We consider transitions between ancestral and novel sex-determining systems using a three-locus model, each locus having two alleles (Fig \ref{fig:model_outline}).
+A full description of our model, including recursion equations, is given in \nameref{app:recurs}.
 Locus $\mathbf{X}$ is the ancestral sex-determining region, with alleles X and Y (or Z and W).
@@
 The assumption that derived sex-determining loci are epistatically dominant is motivated by empirical systems in which multiple sex determining alleles segregate (i.e., X, Y, Z, and W alleles present), such as, cichlid fish~\cite{Ser:2010iq}, platyfish (\textit{Xiphophorus maculatus}~\cite{Kallman1968}), houseflies (\textit{Musca domestica}~\cite{Dubendorfer2002}), western clawed frogs (\textit{Xenopus tropicalis}~\cite{Roco2015}) and \textit{Rana rugosa}~\cite{Ogata:2007jm}.
-Nevertheless, our supplementary analysis file (\nameref{file:Mathematica}) allows other dominance relationships between loci to be specified. 
-See also the supplementary material in \cite{vanDoorn:2007eu} for a numerical analysis that relaxes the assumption of epistatic dominance.
+Nevertheless, our supplementary analysis file (\nameref{file:Mathematica}) allows other dominance relationships between loci to be specified (see also \cite{vanDoorn:2007eu} supplementary material for a numerical analysis).
+%See also the supplementary material in \cite{vanDoorn:2007eu} for a numerical analysis that relaxes the assumption of epistatic dominance.
 %We also analyze a model of maternally-controlled environmental sex-determination, where mothers with at least one $m$ allele produce daughters with probability $k$.
@@
 
-%life-cycle
-A full description of our model, including recursion equations, is given in \nameref{app:recurs}. 
-In each generation, we census the genotype frequencies in male and female gametes/gametophytes (hereafter gametes) before gametic competition. 
-First, competition occurs among male gametes (sperm/pollen competition) and among female gametes (egg/ovule competition) separately. 
-Selection during gametic competition depends on the $\mathbf{A}$ locus genotype; relative fitnesses are given by $w_A^\circ$ and $w_a^\circ$ ($\circ \in \{\female,\male\}$; see table \ref{tab:fitnesstable}).
-%$w_{A}^\male$ and $w_{a}^\male$ for male gametes and $w_{A}^\female$ and $w_{a}^\female$ for female gametes, see table \ref{tab:fitnesstable}.
-We assume that all gametes compete for fertilization during gametic competition, which implies a polygamous mating system. 
-Gametic competition in monogamous mating systems is, however, equivalent to meiotic drive in our model (described below), as either only alters the frequency of gametes produced by heterozygotes. 
+We consider two forms of selection upon haploid genotypes, `gametic competition' and `meiotic drive'. 
+During gametic competition, we assume that a representative sample of all gametes/gametophytes (hereafter gametes) compete for fertilization, which implies a polygamous mating system. 
+Relative fitnesses during gametic competition are given by $w_A^\circ$ and $w_a^\circ$ ($\circ \in \{\female,\male\}$; see table \ref{tab:fitnesstable}).
+On the other hand, meiotic drive in our model only affects the segregation of gametes produced by heterozgotes.
+Specifically, gametes produced by $Aa$ heterozgotes of sex $\circ$ bear allele $A$ with probability $\alpha^\circ$. 
+We note that competition between sperm produced by a single male (e.g.
+in a monogamous mating system) would be appropriately modelled as male meiotic drive, as only the frequency of gametes produced by heterozygotes would be affected.
+However, we do not consider scenarios in which there is competition among gametes produced by a small number of males/females (e.g.,~\cite{Holman:2015en}).
+
+In each generation, we census the genotype frequencies in male and female gametes before gametic competition. 
 After gametic competition, conjugation between male and female gametes occurs at random.
@@
 %where $g$ is the diploid genotype at the $\mathbf{A}$ locus ($g \in \{AA, Aa, aa\}$).
-%Diploids compete with others of the same sex, where selection depends on the sex of the individual and its genotype at the $\mathbf{A}$ locus.
 \textcolor{red}{We do not consider fertility(?) or sexual selection.}
@@
 Any linear order of the loci can be modelled with appropriate choices of $r$, $R$, and $\rho$ (see Fig \ref{fig:model_outline}A and \nameref{tab:chisubstitutions}). 
-Individuals that are heterozygous at the $\mathbf{A}$ locus may experience meiotic drive; a gamete produced by $Aa$ heterozgotes of sex $\circ$ bears allele $A$ with probability $\alpha^\circ$. 
-Thus, the $\mathbf{A}$ locus can experience sex-specific gametic competition, diploid selection, and/or meiotic drive.
-The model is entirely deterministic and hence ignores chance fluctuations in allele frequencies due to genetic drift.
+Our model is entirely deterministic and hence ignores chance fluctuations in allele frequencies due to genetic drift.
+%During the , the $\mathbf{A}$ locus can experience sex-specific gametic competition, diploid selection, and/or meiotic drive.
 
@@
 
-\textcolor{red}{possibly simplify?}
 The evolution of a new sex-determining system requires that a rare mutant allele, $m$, at the novel sex-determining locus, $\mathbf{M}$, increases in frequency when rare. 
@@
 This system simplifies substantially for an epistatically dominant neo-Y ($k=0$) or neo-W ($k=1$), see \nameref{app:inv_cond}. 
-The leading eigenvalue for a rare neo-Y or neo-W allele, $m\in\{Y',W'\}$, is the largest value of X that solves $x^2+ b x + c = 0$.  %$(\lambda_m^{(i)})^2+ b \lambda_m^{(i)} + c =0$. 
+The leading eigenvalue for a rare neo-Y or neo-W allele, $m\in\{Y',W'\}$, is the largest value of $x$ that solves $x^2+ b x + c = 0$.  %$(\lambda_m^{(i)})^2+ b \lambda_m^{(i)} + c =0$. 
 The coefficients are $b= - (\Lambda_{mA}^{(XY)} + \Lambda_{ma}^{(XY)})+(\chi_{mA}^{(XY)} + \chi_{ma}^{(XY)})$ and $c = (\Lambda_{mA}^{(XY)} - \chi_{mA}^{(XY)}) (\Lambda_{ma}^{(XY)} - \chi_{ma}^{(XY)}) - \chi_{mA}^{(XY)} \chi_{ma}^{(XY)}$, where $\Lambda_{mi}^{(XY)}>0$ is the multiplicative growth rate (which we will call the ``haplotypic growth rate'') of the neo-sex determination allele $m$ on background $i\in\{A,a\}$ without accounting for loss due to recombination ($R=0$), and $\chi_{mi}^{(XY)}>0$ is the rate at which mutant haplotypes on background $i\in\{A,a\}$ recombine onto the other $\mathbf{A}$ locus background in heterozygotes (proportional to $R$; we call this the ``dissociative force" as it breaks down linkage disequilibrium), see Table \ref{tab:haplotype_growth}.
@@
 
-\textcolor{red}{note: vD\&K (2010) use a QLE and therefore point out that their results does not require equilibria maintained by sexually antagonistic selection, only differences in fitness between male and females ($s^\male\neq s^\female$).
+%\textcolor{red}{note: vD\&K (2010) use a QLE and therefore point out that their results does not require equilibria maintained by sexually antagonistic selection, only differences in fitness between male and females ($s^\male\neq s^\female$).
 e.g., during a sweep of a positive beneficial mutation, a new SDR can spread because it generates a stronger association with the sex that is favoured the most (e.g., putting the selected allele more often in females and  $s^\male< s^\female$).
@@
 Neo-W alleles, on the other hand, can invade an ancestral XY system under some conditions (the full invasion conditions are given in \nameref{app:inv_cond}; equations \ref{Binvasion} and \ref{Ainvasion}).
-In particular,
+Thus,
 \vspace{0.5cm}
 
-\noindent\textit{Conclusion 1A:}
+\noindent\textit{Conclusion 1:}
 \textbf{selection on loci within the non-recombining region around the sex-determining locus ($r\approx0$) allows the invasion of less closely linked sex-determining alleles ($r<R\leq1/2$) during a trans-GSD transition} (XY $\leftrightarrow$ ZW).
@@
 The conditions become more restrictive, however, with increasing recombination ($R$) between the new sex-determining locus and the selected locus.  
-The invasion of completely unlinked neo-W alleles ($R = 1/2$) can occur with overdominance in males or with haploid selection (as shown for the case of male drive opposed by diploid selection in \cite{Kozielska:2010vm}) but is not possible with only sexually-antagonistic selection if selection is directional in each diploid sex (see \nameref{file:Mathematica}).
+The invasion of completely unlinked neo-W alleles ($R = 1/2$) can occur with overdominance in males or with haploid selection (e.g., a case with male drive opposed by diploid selection in \cite{Kozielska:2010vm}) but is not possible with only sexually-antagonistic selection where selection is directional in each diploid sex (see \nameref{file:Mathematica}).
+Here, we focus on cases where there is no haploid selection and discuss the additional effect of haploid selection in \nameref{app:inv_cond}. 
+%Essentially, neo-W alleles are able to invade (even with $R>r$) because the ancestral X experiences selection in males. 
+%This can lead to (1) XX females having lower than maximum fitness ($\Lambda_{W'A}^{(XY)}>1$) and/or (2) the Y carrying alleles that are beneficial in females.
+
+\textcolor{red}{add to Appendix:}
 \textcolor{red}{In absence of haploid selection Conclusion 1A can also be reached from Equation 7 in \cite{vanDoorn:2010hu}; for example, with no polymorphism on the Y ($V_Y=0$) and an allelic substitution favoured in females ($\alpha^f,\alpha_X^f>0$) a loosely linked neo-W can invade given the allelic substitution is sufficiently disfavoured on the X in males ($\alpha_X^m < -2\alpha_X^f$), although it is unclear from their implicit equation if and when such an equilibrium is stable.}
+
 %\vspace{0.5cm}
@@
 When there is haploid selection, invasion also typically occurs when the neo-W is more closely linked to the selected locus than the ancestral sex-determining region (Fig \ref{fig:Combination_Centimorgans}).
-For example, if the $\mathbf{A}$ locus is unlinked to the ancestral sex-determining locus ($r=1/2$), a more closely linked neo-W ($R<1/2$) can always invade.
-In this case, there is no ancestral association between $\mathbf{A}$ alleles and sex chromosomes in males, $\left( \hat{p}^\male_Y-\hat{p}^\male_X \right)=0$, see Eq \eqref{eq:freq_diffs}. 
-The second term in Eq \eqref{eq:lambda_neoW} therefore disappears and invasion depends only on the sign of $(r-R)$.%, as in the case of the neo-Y.
+For example, if the $\mathbf{A}$ locus is unlinked to the ancestral sex-determining locus ($r=1/2$, which implies that $ \hat{p}^\male_Y-\hat{p}^\male_X =0$), a more closely linked neo-W ($R<1/2$) can always invade.
+%In this case, there is no ancestral association between $\mathbf{A}$ alleles and sex chromosomes in males, $\left( \hat{p}^\male_Y-\hat{p}^\male_X \right)=0$, see Eq \eqref{eq:freq_diffs}. 
+%The second term in Eq \eqref{eq:lambda_neoW} therefore disappears and invasion depends only on the sign of $(r-R)$.%, as in the case of the neo-Y. 
+However, with haploid selection and some ancestral sex-linkage ($r<1/2$; allowing allele frequency differences on the X and Y), the additional term in Eq \eqref{eq:lambda_neoW} can be positive.
+This implies the following two conclusions:
+
+\vspace{0.5cm}
+\noindent\textit{Conclusion 2A:}\
+\textbf{new sex-determining alleles (causing cis- \textit{or} trans-GSD transitions) can spread if the arise in closer linkage with a locus that experiences haploid selection than the ancestral-sex-determining locus ($R<r$).}
+\vspace{0.5cm}
+
+%However, with haploid selection and some ancestral sex-linkage ($r<1/2$; allowing allele frequency differences on the X and Y), the additional term in Eq \eqref{eq:lambda_neoW} can be positive.
+%This implies, 
+%\vspace{0.5cm}
+\noindent\textit{Conclusion 2B:}\
+\textbf{new sex-determining alleles (causing trans-GSD transitions) can spread if they arise in looser linkage with a locus that experiences haploid selection than the ancestral-sex-determining locus ($r<R$).
+}
+\vspace{0.5cm}
 
@@
 
-However, with haploid selection and some ancestral sex-linkage ($r<1/2$; allowing allele frequency differences on the X and Y), the additional term in Eq \eqref{eq:lambda_neoW} can be positive.
-This implies the following two conclusions: 
-\vspace{0.5cm}
-
 %\noindent\textit{Conclusion 1B:}\
-%\textbf{when there is an intermediate rate of recombination between the ancestral sex-determining allele and a selected locus ($0<r<1/2$), haploid selection allows less closely linked sex-determining alleles ($r<R$) to invade during trans-GSD transitions ($\lambda_{W'}^{(XY)}>1$).}
-%%\textcolor{red}{[new result because Kozielska had ancestrally-tight sex-linkage and Ubeda had ESD]}
+%\textbf{new sex-determining alleles (causing trans-GSD transitions) can spread if they arise in looser linkage with a locus that experiences haploid selection ($r<R$). }
+%\textbf{haploid selection on loci weakly linked to the sex-determining locus ($0<r<1/2$) allows the invasion of less closely linked sex-determining alleles ($r<R\leq1/2$) during a trans-GSD transition} (XY $\leftrightarrow$ ZW).
 %\vspace{0.5cm}
 
-\noindent\textit{Conclusion 1B:}\
-%\textbf{new sex-determining alleles (causing trans-GSD transitions) can spread if they arise in looser linkage with a locus that experiences haploid selection ($r<R$). }
-\textbf{haploid selection on loci weakly linked to the sex-determining locus ($0<r<1/2$) allows the invasion of less closely linked sex-determining alleles ($r<R\leq1/2$) during a trans-GSD transition} (XY $\leftrightarrow$ ZW).
-\vspace{0.5cm}
-
-\noindent{\textit{Conclusion 2:}\
-\textbf{new sex-determining alleles (causing cis- \textit{or} trans-GSD transitions) can spread if they arise in closer linkage with a locus that experiences haploid selection ($R<r$). }
+%\noindent{\textit{Conclusion 2:}\
+%\textbf{new sex-determining alleles (causing cis- \textit{or} trans-GSD transitions) can spread if they arise in closer linkage with a locus that experiences haploid selection ($R<r$). }
 %(This is different but similar to Ubeda et al (2015), who started from ESD)
-\vspace{0.5cm}
-
-\noindent The numerical results of \cite{Ubeda:2015fx} are consistent with Conclusion 1B, but arise from an ESD to GSD transition, where the ancestral equilibrium is considerably simpler.
-Conclusion 2 echoes the diploid-selection-only results of \cite{vanDoorn:2007eu,vanDoorn:2010hu}, but greatly extends the number of selective scenarios favouring transitions.
+%\vspace{0.5cm}
+
+%\noindent The numerical results of \cite{Ubeda:2015fx} are consistent with Conclusion 2A, but arise from an ESD to GSD transition, where the ancestral equilibrium is considerably simpler.
+%Conclusion 2B echoes the diploid-selection-only results of \cite{vanDoorn:2007eu,vanDoorn:2010hu}, but greatly extends the number of selective scenarios favouring transitions.
 
@@
 We show that neo-W alleles can spread for when they are more closely \textit{or} more loosely linked to a locus that experiences haploid selection in Fig \ref{fig:Combination_Centimorgans} (c.f., Fig \ref{fig:SexAntagTighter}A for diploid sexually-antagonistic selection alone).
-In Fig \ref{fig:SexRatioBad}, we also show that trans-GSD transitions in sex determination occur during which linkage with a haploid selected locus increases \textit{or} decreases.
+In Fig \ref{fig:SexRatioBad}, we also show that trans-GSD transitions in sex determination during which linkage with a haploid selected locus increases \textit{or} decreases. 
+When $R>r$, neo-W alleles can benefit from Y-associated alleles that have higher fitness in the female diploid phase but then dissociate from these alleles through recombination, which occurs before any subsequent haploid selection.
 
@@
 
-Previous research has shown that when the ancestral sex-determining locus is linked to a locus that experiences haploid selection (e.g., meiotic drive), alleles at a new, unlinked sex-determining locus can invade and restore equal sex ratios~\cite{Kozielska:2010vm}.
-Consider, for example, the case where the $\mathbf{A}$ locus is linked to the ancestral sex-determining locus ($r<1/2$) and experiences meiotic drive in males only ($\alpha^\male_\Delta \neq 0$, $\alpha^\female_\Delta=0$), without gametic competition ($t^\female=t^\male=0$).
-In this case, the zygotic sex ratio can be initially biased only if the ancestral sex-determining system is XY (Fig \ref{fig:model_outline}A and Fig \ref{fig:SexRatioBad}B). 
+%Previous research has shown that when the ancestral sex-determining locus is linked to a locus that experiences haploid selection (e.g., meiotic drive), alleles at a new, unlinked sex-determining locus can invade and restore equal sex ratios~\cite{Kozielska:2010vm}.
+Our model allows us to analytically compare GSD-GSD transitions where sex-ratio bias increases, decreases, or remains equal. 
+For example, if there is meiotic drive in males only ($\alpha^\male_\Delta \neq 0$, $\alpha^\female_\Delta=0$), without gametic competition ($t^\female=t^\male=0$) the zygotic sex ratio is initially biased only when the ancestral sex-determining system is XY (Fig \ref{fig:model_outline}A and Fig \ref{fig:SexRatioBad}A) and not ZW (Fig \ref{fig:SexRatioBad}B).
 %If the ancxestral sex-determining system is ZW, the zygotic sex ratio will be 1:1 because diploid sex is determined by the proportion of Z-bearing versus W-bearing eggs and meiosis in females is fair (Fig \ref{fig:Combination_Turnover}D).
@@
 %However, to leading order with selection weak relative to recombination, we find that sex-ratio selection favours the spread of a neo-W by an amount equl to the spread of a neo-Y into a ZW system (relabeling XY as the heterogametic sex and reversing the labels of males and females in Table \ref{tab:specialcases})
-However, invasion by a neo-W allele into an XY system and invasion by a neo-Y allele into a ZW system occur under the same conditions ($\lambda_{Y'}^{(XY)} = \lambda_{W'}^{(ZW)}$ and $\lambda_{W'}^{(XY)}=\lambda_{Y'}^{(ZW)}$, at least to order $\epsilon^2$), implying that, surprisingly,
+However, invasion by a neo-W allele into an XY system and invasion by a neo-Y allele into a ZW system occur under the same conditions ($\lambda_{Y'}^{(XY)} = \lambda_{W'}^{(ZW)}$ and $\lambda_{W'}^{(XY)}=\lambda_{Y'}^{(ZW)}$, at least to order $\epsilon^2$), implying that,% surprisingly,
 \vspace{0.5cm}
@@
 \noindent\textit{Conclusion 3:}
-\textbf{when selection is weak relative to recombination, sex-ratio selection is exactly equal in magnitude to the selection imposed by associations with selected alleles. }
-%\textcolor{red}{[new result]}
+\textbf{when selection is weak relative to recombination, the presence or absence of sex-ratio biases do not create an assymetry in the likelihood of GSD-GSD transitions. } 
 \vspace{0.5cm}
-
 %\noindent\textcolor{red}{\textit{Conclusion 3:}
@@
 
-%\textcolor{blue}{maybe re-order to put the results up front and focus on sex ratio less.
-Somewhere around these first two paragraphs we should include our tight linkage results.
-At the moment it doesn't make total sense because it assumes that tighter linkage is always favoured unless there is haploid selection.}
-
-\textcolor{red}{Tight ancestral linkage favours looser linked SDRs with diploid selection only:}
-\textcolor{red}{New sex-determining alleles are thought to spread when they arise in linkage with loci that experience sex differences in selection due to beneficial associations between alleles that determine sex and alleles that are favoured in that sex~\cite{vanDoorn:2007eu,vanDoorn:2010hu,Ubeda:2015fx,Muralidhar2018}.
-However, when loci are 
-that tight ancestral-linkage of polymorphic loci, maintained by sexually-antagonistic selection or otherwise, can also drive trans-GSD transitions.
-}
-
-% Evidence
-\textcolor{red}{Evidence: Our results show, however, that tight ancestral-linkage of polymorphic loci, maintained by sexually-antagonistic selection or otherwise, can also drive trans-GSD transitions.
-In addition, we find that polymorphic sex determining systems (X, Y, W, and Z alleles all present) can be maintained when a selected locus is tightly linked to the ancestral sex-determining system (e.g., \nameref{fig:freqAll}B and \nameref{fig:freqAll}C), which is not possible with loose linkage~\cite{vanDoorn:2010hu}.
-For example, our results suggest a potential mechanism maintaining multiple sex determining alleles in the platyfish (\textit{Xiphophorus maculatus}), in which X,Y, and W alleles segregate at one locus (or two closely-linked loci) near to potentially sexually-antagonistic genes for pigmentation and sexual maturity~\cite{Kallman1965,Kallman1968, Volff2001, Schultheis2006}.
-Several rodent species also maintain feminizing alleles along with the ancestral X and Y sex-determination alleles (reviewed in~\cite{Fredga1994}). 
-For example, in nine \textit{Akadon} species, it appears that male-determining-\textit{sry} expression is suppressed by an autosomal feminizing allele, creating XY females~\cite{Bianchi2002,Sanchez2010}, which have increased fitness relative to XX females~\cite{Hoekstra2001}.
-In \textit{Mus microtoides}, females can have XX, XX$^\ast$ or X$^\ast$Y genotypes~\cite{Veyrunes2010}. 
-Previous theory would predict that the X$^\ast$ chromosome (or the autosome it is fused to) harbours female beneficial alleles, driving its spread. 
-However, XX and XX$^\ast$ females have similar fitness, whereas X$^\ast$Y female fitness is enhanced~\cite{Saunders2014,Saunders2016, Veyrunes2017}.
-Although Y-linkage of female-beneficial alleles is counterintuitive, our model suggests that it can be stably maintained and then favour new feminizing mutations, which is a parsimonious explanation for the spread of feminizing alleles in these rodent species.
-}
-
-%MAIN RESULT
-Two predominant theories explaining the remarkably high frequency of transitions between genetic sex-determining systems are sexually-antagonistic selection and sex-ratio selection (reviewed in~\cite{Blaser2012, vanDoorn2014re}).
-The former predicts that new sex-determining alleles can invade when they arise in closer linkage with a sexually-antagonistic locus ($r<R$,~\cite{vanDoorn:2007eu,vanDoorn:2010hu, Muralidhar2018}).
-The latter predicts that new sex-determining systems are generally favoured if they result in more equal sex ratios than the ancestral system. 
-%The latter predicts that neo-W alleles will invade an XY system when there is a male bias caused by haploid selection in males, and vice-versa, a neo-Y will invade a ZW system when there is a female bias caused by haploid selection in females~\cite{Kozielska:2010vm,Ubeda:2015fx}.
-In contrast to these prevailing views, we show that selection (including sexually-antagonistic selection, overdominance, and/or ploidally-antagonistic selection) on loci tightly linked to the ancestral sex-determining locus can favour trans-GSD transitions (XY$\leftrightarrow$ ZW) to new sex-determining systems that are less closely linked to the selected loci ($r>R$, e.g., see Fig \ref{fig:SexAntagTighter}).
-Similarly, even when linkage is weak relative to selection, we show that %new sex-determining alleles are typically favoured if they are more closely linked to a locus under haploid selection (even in the absence of diploid sex differences), which is the only condition favouring cis-GSD transitions (XY to XY or ZW to ZW).
-%In addition, with haploid selection and weak selection, 
-trans-GSD transitions can occur where the new sex-determining locus is less closely linked to the locus under selection if there is haploid selection (e.g., Figs \ref{fig:Combination_Centimorgans} and \ref{fig:SexRatioBad}).
-
-We find that the spread of new sex-determining systems cannot be simply predicted from their effect on the sex ratio. 
+New sex determination systems are typically expected to spread when they equalise the sex ratio and/or when they increase linkage with loci that experience sex-differences in selection~\cite{Blaser2012, vanDoorn2014re} (including sex-differences at the haploid stage, Conclusion 2a and~\cite{Ubeda:2015fx}).
+However, we show that the spread of new sex-determination systems is not dominated by selection to balance the sex ratio (Conclusions 3 \& 4, Fig \ref{fig:SexRatioBad}). 
+Furthermore, we find that trans-GSD transitions can be favoured in cases where linkage with the sex-determining locus is actually weakened (Conclusions 1 \& 2b, Fig \ref{fig:SexAntagTighter}), especially when there is haploid selection (Conclusion 2b, Figs \ref{fig:Combination_Centimorgans} \& \ref{fig:SexRatioBad}).
+
+%We find that the spread of new sex-determining systems cannot be simply predicted from their effect on the sex ratio. 
 On one hand, sex-ratio biases caused by haploid selection can facilitate trans-GSD transitions or transitions from genetic to environmental sex determination. 
-For instance, alleles favoured by haploid selection in males often become associated with the Y allele, which leads to a male-biased zygotic sex ratio.
-This male bias increases the potential for a neo-W allele to invade (Table \ref{tab:haplotype_growth}), which can equalize the sex ratio (e.g., see Fig \ref{fig:SexRatioBad}B, for related examples see~\cite{Kozielska:2010vm}).
+For instance, alleles favoured by haploid selection in males often become associated with the Y allele, which leads to an ancestral male-biased zygotic sex ratio.
+This male bias increases the potential for a neo-W or ESD allele to invade (Table \ref{tab:haplotype_growth}), which can equalize the sex ratio (e.g., see Fig \ref{fig:SexRatioBad}B, for related examples see~\cite{Kozielska:2010vm}).
 %We find that sex-ratio biases caused by haploid selection can also affect transitions between sex-determining systems (e.g., see $\zeta$ terms in Table \ref{tab:haplotype_growth}). 
 %However, the neo-W may not equalize the sex ratio (e.g., if the driving allele also drives in females or affects competition among eggs)
-On the other hand, sex-ratio selection can be overwhelmed by additional selective effects, preventing a neo-W or ESD allele from invading, even if it would balance the sex ratio (e.g., when selection acts in opposite directions in male and female diploids, Table \ref{tab:specialcases}).
+On the other hand, sex-ratio selection can be overwhelmed by additional selective effects, preventing a neo-W or ESD allele from invading, even if it would balance the sex ratio (e.g., when selection also acts in opposite directions in male and female diploids, Table \ref{tab:specialcases}).
 %and equalizing the sex ratio.
@@
 %What we would like to stress is that sex-ratio selection alone cannot predict when new sex-determining systems can evolve.
-Significantly, with weak selection, we find that there is no difference in conditions allowing XY to ZW and ZW to XY transitions, indicating that sex chromosome transitions are not predominantly predicted by their effect on the sex ratio (i.e., the sex-ratio bias created by male haploid selection facilitates the spread of a neo-W allele into an XY system to the same degree that male haploid selection drives the spread of a neo-Y into a ZW system with a 1:1 sex ratio).
+Significantly, with weak selection, we find that there is no difference in conditions allowing XY to ZW and ZW to XY transitions (Conclusion 3), indicating that transitions in sex determination are not predominantly predicted by their effect on the sex ratio (i.e., the sex-ratio bias created by male haploid selection facilitates the spread of a neo-W allele into an XY system to the same degree that male haploid selection drives the spread of a neo-Y into a ZW system with a 1:1 sex ratio).
 %An asymmetry can develop when sex-linkage is tight (e.g., Fig \ref{fig:Combination_Centimorgans} near -25cM and 25cM) but under most circumstances we do not predict asymmetry between XY to ZW and ZW to XY transitions despite the presence/absence of sex-ratio selection.
@@
 
+Our results indicate that haploid selection could be an important factor driving the evolution of new sex-determining systems. 
+Even in animal and plant species that have much larger and more conspicuous diploid phases than haploid phases, many loci have been shown to experience haploid selection through gamete competition and/or meiotic drive~\cite{Mulcahy:1996ha,JOSEPH:2004haa, Lalanne2004,Ubeda:2005gw,Fishman2005,Leppala2008,Leppala2013,Didion2015,Didion2016, Lindholm:2016cw}.
+%Segregation distortion provides putative evidence of haploid selection and can sometimes be attributed to meiotic drive and/or gametic competition~\cite{Lalanne2004,Fishman2005,Leppala2008,Leppala2013,Didion2015,Didion2016}.
+%Where it has been characterized, individual cases of meiotic drive are generally sex-limited, exclusively affecting male or female gametes~\cite{Ubeda:2005gw,Lindholm:2016cw}.
+%Gametic competition is also typically sex-limited, occurring primarily among male gametes, because there are typically many more pollen/sperm than required for fertilization.
+For example, recent studies have demonstrated that sperm competition in animals, even within a single ejaculate, can alter haploid allele frequencies and increase offspring fitness~\cite{Immler:2014im,Alavioon2017}.
+Nevertheless, although precise estimates are uncertain, a relatively small proportion of all genes are thought to be expressed and selected during competition in animal sperm~\cite{Zheng:2001fi,JOSEPH:2004haa,Vibranovski:2010et}.
+In plants, however, haploid selection may be particularly important due to the presence of a multicellular haploid stage. 
+For example, 60-70\% of all genes are expressed in the male gametophyte, and these genes exhibit stronger signatures of selection than randomly-chosen genes~\cite{Borg:2009jpa,Arunkumar:2013iq,Gossmann:2014dua}.
+Furthermore, artificial selection pressures applied to male gametophytes are known to cause a response to selection (e.g.,~\cite{Hormaza:1996cv,Ravikumar:2003uo,Hedhly:2004iv,Clarke:2004ir}).
+
 %HAPLOID SELECTION (genomic location of haploid selected loci and comparative patterns) 
-We have shown that the spread of new sex-determining systems can be driven by loci experiencing haploid selection. 
+%We have shown that the spread of new sex-determining systems can be driven by loci experiencing haploid selection. 
 %Our results suggest that haploid selected loci that have been involved in driving turnovers between sex-determining systems could occur around the ancestral- or novel-sex-determining regions. 
@@
 %As with sexually-antagonistic selection, the presence of haploid selected loci around ancestral- or novel-sex-determining regions could support their role in sex chromosome turnover.
-In agreement with this hypothesis, a recent transcriptome analysis in Rumex shows that pollen-biased expression (relative to expression in flower buds or leaves) is enhanced among XY-linked genes compared to autosomal genes or compared to hemizygous genes that are only linked to the X
+Linking haploid expression with the evolution of sex-determination, a recent transcriptome analysis in \textit{Rumex} shows that pollen-biased expression (relative to expression in flower buds or leaves) is enhanced among XY-linked genes compared to autosomal genes or compared to hemizygous genes that are only linked to the X
 \cite{Sandler264382}. 
@@
 %maybe add a flag here for switching to clade-level expectations:
-In general, we predict that haploid selection increases lability of sex-determining systems, particularly because haploid selection can cause transitions that increase or decrease sex-linkage (e.g., the final state of the red line in Fig \ref{fig:SexRatioBad}B is the starting state in Fig \ref{fig:SexRatioBad}A).
-Frequent turnovers driven by haploid selection may help to explain the relative rarity of heteromorphic sex chromosomes in plants, which are thought to experience more selection during their multicellular haploid stage.
-
-If haploid selection is strong but selective differences between male and female diploids are weak, we find that trans-GSD transitions are favoured more strongly than cis-GSD transitions, with transitions to ESD intermediate (e.g., with $|D^\male - D^\female| << |\alpha_\Delta^\male - \alpha_\Delta^\female + t^\male - t^\female|$ we have $\lambda_{W'}^{(XY)} > \lambda_{Y'}^{(XY)}$; Eqs \ref{eq:lambda_neoW} and \ref{eq:freq_diffs}).
+
+In general, we predict that haploid selection increases lability of sex-determining systems, particularly because haploid selection can cause transitions that increase or decrease sex-linkage (Conclusion 2B, e.g., the final state of the red line in Fig \ref{fig:SexRatioBad}B is the starting state in Fig \ref{fig:SexRatioBad}A).
+Frequent turnovers driven by haploid selection may help to explain the relative rarity of heteromorphic sex chromosomes in plants.
+If haploid selection is strong but selective differences between male and female diploids are weak, we specifically predict that trans-GSD transitions are favoured more strongly than cis-GSD transitions, with transitions to ESD intermediate (e.g., with $|D^\male - D^\female| << |\alpha_\Delta^\male - \alpha_\Delta^\female + t^\male - t^\female|$ we have $\lambda_{W'}^{(XY)} > \lambda_{Y'}^{(XY)}$; Eq \ref{eq:lambda_neoW}).
 Among the relatively few dioecious clades in which multiple species have well characterized sex chromosomes~\cite{Ming:2011iy}, trans-GSD transitions have been inferred in \textit{Silene} subsection \textit{Otites}~\cite{Slancarova:2013dq} and in \textit{Salicaceae}~\cite{Pucholt2015,Pucholt2017}.
-%Potentially, successive heterogametic transitions between master regulators of sex-determination could be inferred from careful examination of the molecular pathways by which sex is determined. 
-%Our predictions could also be examined using a suitable proxy for haploid selection, for example, \cite{Lenormand:2005vb} use the outcrossing rate in plants as a proxy for the strength of pollen competition.
 Assuming that transitions from dioecy to hermaphroditism (equal parental investment in male and female gametes) are favoured in a similar manner to the ESD examined here (equal probability of zygotes developing as males or females), our results suggest that competition among haploid pollen could drive transitions between dioecy and hermaphroditism, which are frequent in plants~\cite{Kafer2017, Goldberg2017}.
-To further examine this link, future investigations could examine the combined effects of haploid pollen competition, selfing, and inbreeding depression in allowing transitions between dioecy and hermaphroditism.
-
-In support of their role in sex chromosome turnover, genes expected to be under sexually-antagonistic selection (e.g., those causing bright male colouration) have been found on recently derived sex chromosomes~\cite{Lindholm:2002dw,Tripathi:2009cw,Ser:2010iq}.
-Our results show, however, that tight ancestral-linkage of polymorphic loci, maintained by sexually-antagonistic selection or otherwise, can also drive trans-GSD transitions. 
+To further examine this link, future theoretical investigations could also include selfing and inbreeding depression during transitions between dioecy and hermaphroditism. 
+Future empirical investigations could look for evidence of haploid selection acting on former sex chromosomes in hermaphroditic species (e.g., a study such as \cite{Sandler264382} on ancestral, rather than derived, sex chromosomes).
+
+New sex-determining alleles have previously be shown to spread when they arise in linkage with loci that experience sex differences in selection because beneficial associations build up between alleles that determine sex and alleles that are favoured in that sex~\cite{vanDoorn:2007eu,vanDoorn:2010hu,Ubeda:2015fx,Muralidhar2018}.
+In support of this hypothesis, researchers have identified genes on recently derived sex chromosomes that might be under sexually-antagonistic selection~\cite{Lindholm:2002dw,Tripathi:2009cw,Ser:2010iq}.
+However, we show that, if selected loci are linked to the ancestral sex-determining locus, they can drive trans-GSD transitions during which sex-linkage is reduced (Conclusion 1), thus widening the genomic locations that could be driving trans-GSD transitions.
 In addition, we find that polymorphic sex determining systems (X, Y, W, and Z alleles all present) can be maintained when a selected locus is tightly linked to the ancestral sex-determining system (e.g., \nameref{fig:freqAll}B and \nameref{fig:freqAll}C), which is not possible with loose linkage~\cite{vanDoorn:2010hu}.
-%As noted by \citet{vanDoorn:2010hu}, it would be prudent to compare closely related clades in order to determine whether observed polymorphisms predate a transition in sex-determination or arose afterwards.
-%, particularly because sex-linkage allows sexually-antagonistic selection to maintain polymorphisms under a different and larger parameter space~\cite{Rice:1987hs,Jordan:2011fj}.
-For example, our results suggest a potential mechanism maintaining multiple sex determining alleles in the platyfish (\textit{Xiphophorus maculatus}), in which X,Y, and W alleles segregate at one locus (or two closely-linked loci) near to potentially sexually-antagonistic genes for pigmentation and sexual maturity~\cite{Kallman1965,Kallman1968, Volff2001, Schultheis2006}.
-Several rodent species also maintain feminizing alleles along with the ancestral X and Y sex-determination alleles (reviewed in~\cite{Fredga1994}). 
-For example, in nine \textit{Akadon} species, it appears that male-determining-\textit{sry} expression is suppressed by an autosomal feminizing allele, creating XY females~\cite{Bianchi2002,Sanchez2010}, which have increased fitness relative to XX females~\cite{Hoekstra2001}.
-In \textit{Mus microtoides}, females can have XX, XX$^\ast$ or X$^\ast$Y genotypes~\cite{Veyrunes2010}. 
+These conclusions apply in cases with or without haploid selection.
+
+Our tight linkage results are consistent with empirical data from species in which new feminizing mutations are found alongside ancestral XY loci. 
+For example, in the platyfish (\textit{Xiphophorus maculatus}), X,Y, and W alleles segregate at one locus (or two closely-linked loci) near to potentially sexually-antagonistic genes for pigmentation and sexual maturity~\cite{Kallman1965,Kallman1968, Volff2001, Schultheis2006}.
+Furthermore, several rodent species maintain feminizing alleles along with the ancestral X and Y sex-determination alleles (reviewed in~\cite{Fredga1994}). 
+In nine \textit{Akadon} rodent species, it appears that male-determining-\textit{sry} expression is suppressed by an autosomal feminizing allele, creating XY females~\cite{Bianchi2002,Sanchez2010}. 
+XY females have increased fitness relative to XX females~\cite{Hoekstra2001}. However, it is not yet clear whether loci linked to the feminizing factor or the ancestral Y cause this effect. 
+Most convincingly, in \textit{Mus microtoides}, females can have XX, XX$^\ast$ or X$^\ast$Y genotypes~\cite{Veyrunes2010}. 
 Previous theory would predict that the X$^\ast$ chromosome (or the autosome it is fused to) harbours female beneficial alleles, driving its spread. 
 However, XX and XX$^\ast$ females have similar fitness, whereas X$^\ast$Y female fitness is enhanced~\cite{Saunders2014,Saunders2016, Veyrunes2017}. 
-Although Y-linkage of female-beneficial alleles is counterintuitive, our model suggests that it can be stably maintained and then favour new feminizing mutations, which is a parsimonious explanation for the spread of feminizing alleles in these rodent species.
+Although Y-linkage of female-beneficial alleles is counterintuitive, our model suggests that it can be stably maintained and then favour new feminizing mutations, which would be a parsimonious explanation for the spread of feminizing alleles in this case.
 
@@
 We note that we assume that sex-determining alleles do not experience direct selection except via their associations with sex and selected alleles.
-However, in some cases, there may be significant degeneration around the sex-limited allele (Y or W) in the ancestral sex-determining region because recessive deleterious mutations and/or deletions accumulate in this non-recombining regions~\cite{Rice:1996ke,Charlesworth:2000cc,Bachtrog:2006ed,Marais:2008hm}.
+However, in some cases, there may be significant degeneration around the sex-limited allele (Y or W) in the ancestral sex-determining region because recessive deleterious mutations and/or deletions accumulate in the surrounding non-recombining regions~\cite{Rice:1996ke,Charlesworth:2000cc,Bachtrog:2006ed,Marais:2008hm}.
 During trans-GSD transitions, but not cis-GSD transitions, any recessive deleterious alleles linked to the Y or W are revealed to selection in YY or WW individuals~\cite{Bachtrog:2014bx}. 
@@
 These results echo those for large-effect neo-Y/neo-W alleles~\cite{vanDoorn:2007eu,vanDoorn:2010hu}.
-It should be noted, however, that the dynamics of sex-determining alleles with very weak effect will be influenced by genetic drift, which itself has been shown to cause trans-GSD transitions \cite{Veller2017}.
+It should be noted, however, that the dynamics of sex-determining alleles with very weak effect will be influenced by genetic drift, which itself has been shown to favour trans- over cis-GSD transitions when there is no selection \cite{Veller2017}.
 
@@
 We have shown that tight sex-linkage and haploid selection can drive previously unexpected transitions between sex-determining systems.
-In particular, both can select for new sex-determining loci that are more loosely linked to loci under selection. 
-In addition, haploid selection can cause transitions analogous to those caused by purely sexually-antagonistic selection, eliminating the need for differences in selection between male and female diploids.
+In particular, both can select for new sex-determining loci that are more loosely linked to loci under selection (Conclusions 1 \& 2B). 
+In addition, haploid selection can cause transitions analogous to those caused by purely sexually-antagonistic selection, eliminating the need for differences in selection between male and female diploids (Conclusion 2A).
 We conclude that haploid selection should be considered as a pivotal factor driving transitions between sex-determining systems. 
-Further, transitions involving haploid selection can be driven by sex-ratio selection or cause sex-ratio biases to evolve; Fisherian sex-ratio selection is not an overwhelming force. 
+Further, transitions involving haploid selection can be driven by sex-ratio selection or cause sex-ratio biases to evolve; Fisherian sex-ratio selection is not an overwhelming force (Conclusions 3 \& 4).
 Overall, our results suggest several new scenarios under which new sex-determining systems are favoured, which could help to explain why the evolution of sex-determining systems is so dynamic.

### 2018-04-17 LaTeX/response.tex
minor changes, ready to incorporate Sally comments

@@
 \noindent\paragraph{Response}
-\textcolor{blue}{We now call these terms the ``dissociative force" as they break down linkage disequilibrium (L162).}
+\textcolor{blue}{We now call these terms the ``dissociative force" as they break down linkage disequilibrium (L162).
+We have attempted various graphical schemes for representing the three loci in two sexes and the associations that evolve between them in various scenarios.
+However, apart from Fig 1, we found these too complicated or opaque to be useful.
+}
 
@@
 \textcolor{blue}{We now mention that the model is deterministic, and hence ignores drift (L136). 
-We later mention that drift can in fact be a key factor in transitions: ``It should be noted, however, that the dynamics of sex-determining alleles with very weak effect will be influenced by genetic drift, which itself has been shown to cause trans-GSD transitions (Veller et al 2017)." (L511)}
+When discussing the model limitations, we later mention a study on the effect of drift during trans-GSD transitions, which tend to drift in the direction of epistatically-dominant sex-determining loci: ``It should be noted, however, that the dynamics of sex-determining alleles with very weak effect will be influenced by genetic drift, which itself has been shown to cause trans-GSD transitions (Veller et al 2017)." (L511)}
 
@@
 \textcolor{blue}{
-The introduction has been simplified to be as follows.
-The first paragraph discusses how common transitions are (context). 
-The second and third paragraphs discuss the two major mechanisms currently hypothesized to drive the observed transitions, respectively (current theory). 
-The fourth paragraph explains how assuming ancestrally-tight sex-linkage produces previously unexpected transitions (one hole in current theory, and how we address it).
-The fifth paragraph discusses the potential complications of haploid selection for transitions (a second hole in current theory).
-The sixth paragraph describes previous studies on transitions with haploid selection (attempts to address the second hole). 
-The final, seventh, paragraph states how our approach differs from previous attempts and the major findings we uncover (how we address the second hole).  
+Thank you for these very constructive suggestions. We have simplified the introduction according to the suggested format. 
+\begin{enumerate}
+\item{The first paragraph discusses how common transitions are, and now mentions that recent empirical evidence is making this increasingly apparent (lines XXX)}
+\item{The second and third paragraphs lay out the theories thought to drive transitions in sex-determination, as suggested, (1) selection to stabilize the sex ratio, and (2) linkage associations between alleles favoured in one sex and the alleles that determine that sex.
+}
+\item{Connecting to point (2), we then found it useful to introduce one novel aspect of our model - we consider variation that is very tightly linked to the ancestral sex-determining locus and find the surprising result that transitions in which linkage is reduced can be favoured.}
+\item{Next, we introduce our most significant model feature, haploid selection, which we present as an evolutionary problem (as suggested by reviewer 1) in light of (1) and (2). }
+\item{The sixth paragraph then describes previous studies that have included haploid selection (see also reviewer 3 recommendations).
+These studies suggest that (1) and (2) are both very important with haploid selection}
+\item{Finally, we lay out our main results in this context.
+This makes it clear that our general model is necessary to determine the important forces driving transitions in sex determination.
+We particularly highlight the unexpected conclusions that our model allows us to reach.
+}
+\end{enumerate}
+To accommodate these changes, we have moved any discussion of empirical evidence for haploid selection to the discussion. 
 }
@@
 %\textcolor{red}{The abstract and summary still seem to be a little over-selling...}
-\textcolor{blue}{We have performed an extensive re-arrangement (e.g., Responses 2.1 and 2.2 and below) to improve the clarity of our writing, especially regarding the main results. 
+\textcolor{blue}{We have performed an extensive re-arrangement to improve the clarity of our writing, especially regarding the main results. 
+As described in Response 2.1 and below, we now provide a longer discussion of two papers suggested (Kozielska et al 2010 and Ubeda et al 2015), lines XXXX, and more precisely indicate which of our model features and results are new and unexpected in light of these previous results (e.g., Response 2.2 and lines XXXX).
+While related, these studies considered particular cases that we do not consider at length.
+For example, Ubeda et al 2015 consider ESD-GSD transitions.
+Nevertheless, these transitions involve increased linkage with a haploid selection locus, which is precedent for our conclusion 2A (where we consider GSD-GSD transitions).
+Similarly, Kozielska et al (2010) involves a special case of GSD transitions during which linkage is reduced, which is somewhat similar to conclusion 2B.
+Nevertheless, the permissive parameter space should be considered surprising.
+Especially because their main conclusion involved the strong influence of sex-ratio selection, which is explicitly not a driver during many such transitions.
+In addition, our conclusions 3 and 4 are to show that sex-ratio selection is not an overwhelming force driving transitions in sex determination.
 We believe that our new presentation makes the novel and unexpected features of our results much more apparent. 
-In particular, as described at length below, we now give more weight to the two previous papers suggested (Kozielska et al 2010 and Ubeda et al 2015) and more precisely indicate which of our model features and results are new and unexpected in light of these previous results.
-To be clear, we do not claim to be the first to include both haploid and diploid selection to a model investigating the evolution of new sex-chromosomes and we do not consider the addition of sex-specific selection or analytical results for previously numerical models to be our most significant contributions (again, see Responses 2.1 and 2.2 and below for more detail on what these are).
+%To be clear, we do not claim to be the first to include both haploid and diploid selection to a model investigating the evolution of new sex-chromosomes and we do not consider the addition of sex-specific selection or analytical results for previously numerical models to be our most significant contributions (again, see Responses 2.1 and 2.2 and below for more detail on what these are).
 }
@@
 We found our result, that these forces are exactly equal (with selection weak relative to recombination), such that there is no difference between the propensity for XY-ZW or ZW-XY transitions, to be surprising.
-To clarify our meaning we have rephrased (in Author summary): ``Surprisingly, we find the two forces (sex-ratio selection and associations with genes that have sex-specific effects) will often be equally strong, and thus neither dominates the spread of new sex-determining systems alone."}
+To clarify our meaning we have rephrased (in Author summary): ``Surprisingly, we find the two forces (sex-ratio selection and associations with genes that have sex-specific effects) will often be equally strong, and thus neither dominates the spread of new sex-determining systems alone." We believe that the re-framing of the introduction/discussion and the emphasis given to specific Conclusions 1-4 will also help to clarify this point over the rest of the paper.
+}
 
@@
 \textcolor{blue}{To communicate this we have rephrased: ``Even more unexpectedly, we find that new sex-determining alleles can spread despite being less closely linked to selected loci under a wide range of conditions."
-We believe that the changes to the presentation of the Introduction and Results should also help to clarify this point further (e.g., paragraph, lines 40-47, and more clearly highlighted conclusions on lines XXX; see Responses 2.1 and 2.2).
+The changes to the presentation of the Introduction and Results should also help to clarify this point further (e.g., paragraph, lines 40-47, and more clearly highlighted conclusions on lines XXX; see Responses 2.1 and 2.2).
 }

### 2018-04-17 LaTeX/main_revised.tex
minor changes, ready to incorporate Sally comments

@@
 \section*{Introduction}
-
 %TRANSITIONS ARE COMMON
-Animals and angiosperms exhibit extremely diverse sex-determining systems (reviewed in~\cite{Bull:1983vi,Charlesworth:2010it,Beukeboom:2014vb,Bachtrog:2014bx}). 
+Animals and angiosperms exhibit extremely diverse sex-determining systems (reviewed in~\cite{Bull:1983vi,Charlesworth:2010it,Beukeboom:2014vb,Bachtrog:2014bx, Pennell2018}). 
 Among species with genetic sex determination (GSD), some taxa have heterogametic males (XY) and homogametic females (XX), including %non-monotreme?
@@
 Indeed, in some cases, both male and female heterogametic sex-determining systems can be found in the same species, as reported in houseflies~\cite{Macdonald1978}, midges~\cite{Thompson1971}, frogs~\cite{Ogata:2007jm}, cichlid fish~\cite{Ser:2010iq}, tilapia~\cite{Lee2004}, sea bass~\cite{Vandeputte2007}, and lab-strains of Zebrafish~\cite{Liew2012,Wilson2014}.
-In addition, multiple transitions have occurred between genetic and environmental sex-determining systems (GSD$\leftrightarrow$ESD), e.g., in reptiles and fishes~\cite{Conover:1987in,Mank:2006bt,Pokorna:2009ui,Ezaz:2009tk,Pen:2010kk,Holleley:2015hc}.
+In addition, multiple transitions have occurred between genetic and environmental sex-determining systems (GSD$\leftrightarrow$ESD), e.g., in reptiles and fishes~\cite{Conover:1987in,Mank:2006bt,Pokorna:2009ui,Ezaz:2009tk,Pen:2010kk,Holleley:2015hc, Pennell2018}.
 In sum, accumulating evidence indicates that transitions between sex-determining systems are common~\cite{Bachtrog:2014bx}.
@@
 This, in turn, can favour a new ZW sex-determining locus that has weaker linkage with loci under selection, which has not been apparent in previous theory \cite{vanDoorn:2010hu}. 
-That is, we show that selected loci in very tight linkage with the ancestral GSD locus can favour trans-GSD transitions in which associations are actually weakened.
+That is, we show that selected loci in very tight linkage with the ancestral GSD locus can favour trans-GSD transitions during which linkage associations are actually weakened.
 
@@
 The diploid selection term, $D^\circ=\big{[} \bar{p}s^\circ+(1-\bar{p})h^\circ s^\circ\big{]} -\big{[} \bar{p}h^\circ s^\circ+(1-\bar{p}) \big{]}$, is the difference in fitness between $A$ and $a$ alleles in diploids of sex $\circ \in \{\female,\male\}$, where $\bar{p}$ is the leading-order probability of mating with an $A$-bearing gamete from the opposite sex (equation \ref{eq:pAve}).
-The difference in $A$-allele-frequency among Y-bearing sperm versus X-bearing sperm is given by $\hat{p}^\male_Y-\hat{p}^\male_X=V_{A}\big{(}D^\male - D^\female+\alpha_{\Delta}^\male-\alpha_{\Delta}^\female+t^\male-t^\female\big{)}(1-2r)/(2r)$.
+The difference in $A$-allele-frequency among Y-bearing sperm versus X-bearing sperm is given by $\hat{p}^\male_Y-\hat{p}^\male_X=V_{A}S_{A}(1-2r)/(2r)$.
 
@@
 %Indeed, invasion typically occurs when the neo-W is more closely linked to the selected locus than the ancestral sex-determining region (Fig \ref{fig:Combination_Centimorgans}).
-To clarify the parameter space under which invasion occurs despite looser sex-linkage ($\lambda_{W'}^{(XY)}>1$ despite $R>r$; Conclusion 1B), we focus on the special case where $R=1/2$ and $r<1/2$ (e.g., the selected locus is on the ancestral sex chromosome and the novel sex-determining locus arises on an autosome).
+To clarify the parameter space under which invasion occurs despite looser sex-linkage ($\lambda_{W'}^{(XY)}>1$ despite $R>r$; Conclusion 2B), we focus on the special case where $R=1/2$ and $r<1/2$ (e.g., the selected locus is on the ancestral sex chromosome and the novel sex-determining locus arises on an autosome).
 In Table \ref{tab:specialcases} we give the conditions where invasion occurs when we further assume that haploid selection only occurs in one sex (e.g., during male meiosis only) and dominance coefficients are equal in the two sexes, $h^\female=h^\male$.
@@
 We show that neo-W alleles can spread for when they are more closely \textit{or} more loosely linked to a locus that experiences haploid selection in Fig \ref{fig:Combination_Centimorgans} (c.f., Fig \ref{fig:SexAntagTighter}A for diploid sexually-antagonistic selection alone).
-In Fig \ref{fig:SexRatioBad}, we also show that trans-GSD transitions in sex determination during which linkage with a haploid selected locus increases \textit{or} decreases. 
-When $R>r$, neo-W alleles can benefit from Y-associated alleles that have higher fitness in the female diploid phase but then dissociate from these alleles through recombination, which occurs before any subsequent haploid selection.
+In Fig \ref{fig:SexRatioBad}, we also show examples of trans-GSD transitions in sex determination during which linkage with a haploid selected locus increases \textit{or} decreases. 
+When sex-linkage decreases ($R>r$), neo-W alleles can benefit from Y-associated alleles that have higher fitness in the female diploid phase but then dissociate from these alleles through recombination, which occurs before any subsequent haploid selection.
 
@@
 %\textcolor{red}{In our deterministic model this means the fraction female is exactly $k$, even when $m$ is rare (exploring the effect of the variance induced by ESD would also be interesting).}
-In our deterministic model this means the fraction female is exactly $k$, even when $m$ is rare (exploring the effect of the variance induced by ESD would also be interesting).
+In our deterministic model this means the fraction female is exactly $k$, even when $m$ is rare (i.e., ESD does not introduce any additional variance in sex determination). 
 Here, we do not assume that the environmental conditions that determine sex also differentially affect the fitness of males versus females. 
@@
 
-New sex determination systems are typically expected to spread when they equalise the sex ratio and/or when they increase linkage with loci that experience sex-differences in selection~\cite{Blaser2012, vanDoorn2014re} (including sex-differences at the haploid stage, Conclusion 2a and~\cite{Ubeda:2015fx}).
-However, we show that the spread of new sex-determination systems is not dominated by selection to balance the sex ratio (Conclusions 3 \& 4, Fig \ref{fig:SexRatioBad}). 
-Furthermore, we find that trans-GSD transitions can be favoured in cases where linkage with the sex-determining locus is actually weakened (Conclusions 1 \& 2b, Fig \ref{fig:SexAntagTighter}), especially when there is haploid selection (Conclusion 2b, Figs \ref{fig:Combination_Centimorgans} \& \ref{fig:SexRatioBad}).
+New sex determination systems are typically expected to spread when they equalise the sex ratio and/or when they increase linkage with loci that experience sex-differences in selection~\cite{Blaser2012, vanDoorn2014re} (including sex-differences at the haploid stage, Conclusion 2A and~\cite{Ubeda:2015fx}).
+However, we find that trans-GSD transitions can be favoured in cases where linkage with the sex-determining locus is actually weakened (Conclusions 1 \& 2B, Fig \ref{fig:SexAntagTighter}), especially when there is haploid selection (Conclusion 2B, Figs \ref{fig:Combination_Centimorgans} \& \ref{fig:SexRatioBad}).
+Furthermore, we show that the spread of new sex-determination systems is not dominated by selection to balance the sex ratio (Conclusions 3 \& 4, Fig \ref{fig:SexRatioBad}).
 
 %We find that the spread of new sex-determining systems cannot be simply predicted from their effect on the sex ratio. 
-On one hand, sex-ratio biases caused by haploid selection can facilitate trans-GSD transitions or transitions from genetic to environmental sex determination. 
+On one hand, sex-ratio biases caused by haploid selection can facilitate trans-GSD transitions or transitions from genetic to environmental sex determination~\cite{Kozielska:2010vm}. 
 For instance, alleles favoured by haploid selection in males often become associated with the Y allele, which leads to an ancestral male-biased zygotic sex ratio.
@@
 Even in animal and plant species that have much larger and more conspicuous diploid phases than haploid phases, many loci have been shown to experience haploid selection through gamete competition and/or meiotic drive~\cite{Mulcahy:1996ha,JOSEPH:2004haa, Lalanne2004,Ubeda:2005gw,Fishman2005,Leppala2008,Leppala2013,Didion2015,Didion2016, Lindholm:2016cw}.
+In some cases, meiotic drive (Burt and Trivers, 2006, Chapter 6~\cite{Burt:2006}) or gametic competition~\cite{Lloyd:1974tz,Conn:1981uw,Stehlik:2005ul,Stehlik:2006to,Field:2012fd,Field:2013cc} among X- and Y-bearing gametes is known to cause sex ratio biases.
 %Segregation distortion provides putative evidence of haploid selection and can sometimes be attributed to meiotic drive and/or gametic competition~\cite{Lalanne2004,Fishman2005,Leppala2008,Leppala2013,Didion2015,Didion2016}.
@@
 %Gametic competition is also typically sex-limited, occurring primarily among male gametes, because there are typically many more pollen/sperm than required for fertilization.
-For example, recent studies have demonstrated that sperm competition in animals, even within a single ejaculate, can alter haploid allele frequencies and increase offspring fitness~\cite{Immler:2014im,Alavioon2017}.
+In animals, recent studies have demonstrated that sperm competition, even within a single ejaculate, can alter haploid allele frequencies and increase offspring fitness~\cite{Immler:2014im,Alavioon2017}.
 Nevertheless, although precise estimates are uncertain, a relatively small proportion of all genes are thought to be expressed and selected during competition in animal sperm~\cite{Zheng:2001fi,JOSEPH:2004haa,Vibranovski:2010et}.
@@
 
-In general, we predict that haploid selection increases lability of sex-determining systems, particularly because haploid selection can cause transitions that increase or decrease sex-linkage (Conclusion 2B, e.g., the final state of the red line in Fig \ref{fig:SexRatioBad}B is the starting state in Fig \ref{fig:SexRatioBad}A).
+In general, we predict that haploid selection increases lability of sex-determining systems, particularly because haploid selection can cause transitions that increase or decrease sex-linkage (Conclusion 2A \& 2B, e.g., the final state of the red line in Fig \ref{fig:SexRatioBad}B is the starting state in Fig \ref{fig:SexRatioBad}A).
 Frequent turnovers driven by haploid selection may help to explain the relative rarity of heteromorphic sex chromosomes in plants.
@@
 In support of this hypothesis, researchers have identified genes on recently derived sex chromosomes that might be under sexually-antagonistic selection~\cite{Lindholm:2002dw,Tripathi:2009cw,Ser:2010iq}.
-However, we show that, if selected loci are linked to the ancestral sex-determining locus, they can drive trans-GSD transitions during which sex-linkage is reduced (Conclusion 1), thus widening the genomic locations that could be driving trans-GSD transitions.
+However, we show that, if selected loci are tightly linked to the ancestral sex-determining locus, they can drive trans-GSD transitions during which sex-linkage is reduced (Conclusion 1), thus widening the genomic locations that could be driving trans-GSD transitions.
 In addition, we find that polymorphic sex determining systems (X, Y, W, and Z alleles all present) can be maintained when a selected locus is tightly linked to the ancestral sex-determining system (e.g., \nameref{fig:freqAll}B and \nameref{fig:freqAll}C), which is not possible with loose linkage~\cite{vanDoorn:2010hu}.
@@
 These results echo those for large-effect neo-Y/neo-W alleles~\cite{vanDoorn:2007eu,vanDoorn:2010hu}.
-It should be noted, however, that the dynamics of sex-determining alleles with very weak effect will be influenced by genetic drift, which itself has been shown to favour trans- over cis-GSD transitions when there is no selection \cite{Veller2017}.
+It should be noted, however, that the dynamics of sex-determining alleles with very weak effect will be influenced by genetic drift, which itself has been shown to bias transitions towards epistatically-dominant sex-determining systems when there is no selection \cite{Veller2017}.
 
@@
 In particular, both can select for new sex-determining loci that are more loosely linked to loci under selection (Conclusions 1 \& 2B). 
-In addition, haploid selection can cause transitions analogous to those caused by purely sexually-antagonistic selection, eliminating the need for differences in selection between male and female diploids (Conclusion 2A).
+In addition, haploid selection can cause transitions in GSD analogous to those caused by purely sexually-antagonistic selection, eliminating the need for differences in selection between male and female diploids (Conclusion 2A).
 We conclude that haploid selection should be considered as a pivotal factor driving transitions between sex-determining systems. 

### 2018-04-17 LaTeX/main_revised.tex
almost done sallys comments to weak linkage

@@
 \externaldocument{S3Appendix_revised}
+
+%for figures
+%\usepackage{epstopdf}
 
@@
 With haploid selection, we find that transitions between male and female heterogamety can evolve where linkage with the sex-determining locus is either strengthened or weakened. 
-Furthermore, we find that the selective strengths exerted by the sex-ratio and associations with selected alleles are often equivalent. 
-This allows sex-ratio biases to increase or decrease with the spread of new sex chromosomes, and implies that transitions between sex-determining systems cannot be simply predicted by selection to equalise the sex ratio.
+%Furthermore, we find that the selective strengths exerted by the sex-ratio and associations with selected alleles are often equivalent. 
+Furthermore, we find that the selective forces to equalize the sex ratio are equally important to selective forces that generate skewed sex ratios when accounting for the spread of new sex chromosomes.
+This allows sex-ratio biases to increase or decrease with the spread of new sex chromosomes and implies that transitions between sex-determining systems cannot be simply predicted by selection to equalise the sex ratio.
 Overall, our models reveal that transitions between sex-determining systems, particularly transitions where the heterogametic sex changes, can be driven by loci in previously unpredicted genomic locations that experience selection during diploid and/or haploid phases.
@@
 Our models include selection upon haploid genotypes (meiotic drive or gametic competition), which causes sex-ratio biases and occurs differently in male and female gametes. 
-Surprisingly, we find the two forces (sex-ratio selection and associations with genes that have sex-specific effects) will often be equally strong, and thus neither dominates the spread of new sex-determining systems alone.
+Surprisingly, we find the two forces (selection to equalize the sex ratio and the benefits of hitchhiking with driven alleles that distort the sex ratio) will often be equally strong, and thus neither is sufficient to explain  the spread of new sex-determining systems in every case.
 Even more unexpectedly, we find that new sex-determining alleles can spread despite being less closely linked to selected loci. 
@@
 %van Doorn and Kirkpatrick~\cite{vanDoorn:2007eu,vanDoorn:2010hu} and Muralidhar and Veller~\cite{Muralidhar2018} have shown that new sex-determining alleles can be favoured if they arise at loci in close linkage with a locus that experiences sexual antagonism.
-Linkage allows a stronger favourable association to build up between a male-beneficial allele, and a neo-Y allele, for example. 
+Linkage allows a stronger favourable association to build up between a male-beneficial allele and a neo-Y allele, for example. 
 Such associations can favour cis-GSD transitions~\cite{vanDoorn:2007eu}, trans-GSD transitions~\cite{vanDoorn:2010hu}, and new partially-masculinizing or partially-feminizing alleles in a population with ESD~\cite{Muralidhar2018}.
-However, any sexually-antagonistic loci that are more closely linked to the ancestral sex-determining locus should develop similar, favourable associations and are expected to hinder the spread of a new sex-determining system~\cite{vanDoorn:2007eu,vanDoorn:2010hu}.
+%However, any sexually-antagonistic loci that are more closely linked to the ancestral sex-determining locus should develop similar, favourable associations and are expected to hinder the spread of a new sex-determining system~\cite{vanDoorn:2007eu,vanDoorn:2010hu}.
+By similar logic, however, existing sexually-antagonistic alleles associated with the current sex-determining locus are expected to hinder the spread of a new sex-determining system~\cite{vanDoorn:2007eu,vanDoorn:2010hu}.
 
@@
 %we explicitly calculate ancestral polymorphisms. 
-Our analysis reveals that, under various forms of selection, the ancestral-X can carry suboptimal alleles for females and/or the ancestral-Y can carry female-beneficial alleles. 
-This, in turn, can favour a new ZW sex-determining locus that has weaker linkage with loci under selection, which has not been apparent in previous theory \cite{vanDoorn:2010hu}. 
+%Our analysis reveals that, under various forms of selection, the ancestral-X can carry suboptimal alleles for females and/or the ancestral-Y can carry female-beneficial alleles. 
+Counterintuitively, when linkage is tight between the sex-determining locus and a selected locus, an allele good for females can be at higher frequency on the ancestral-Y than on the ancestral-X under a variety of forms of selection.
+This, in turn, can favour a new ZW sex-determining locus that has weaker linkage with loci under selection (a similar argument applies to ZW$\rightarrow$XY transitions), which was not considered in previous theory \cite{vanDoorn:2010hu}.
 That is, we show that selected loci in very tight linkage with the ancestral GSD locus can favour trans-GSD transitions during which linkage associations are actually weakened.
@@
 Two previous studies have considered the spread of GSD with sex-specific meiotic drive~\cite{Kozielska:2010vm,Ubeda:2015fx} under a limited number of possible genetic architectures and diploid selective regimes.
-Ubeda et al. (2015)~\cite{Ubeda:2015fx}, considers ancestral-ESD (with no sex-ratio bias) and numerically show that new GSD alleles can spread if they arise in linkage with meiotic drive loci. 
+Ubeda et al. (2015)~\cite{Ubeda:2015fx} considers ancestral-ESD (with no sex-ratio bias) and numerically show that new GSD alleles can spread if they arise in linkage with meiotic drive loci. 
 For example, a masculinizing allele spreads in association with an allele that is favoured during male meiosis, causing sex ratios to become male-biased and thereby suggesting that such beneficial associations overwhelm selection to balance the sex ratio.
@@
 (2010)~\cite{Kozielska:2010vm} and Ubeda et al.
-(2015)~\cite{Ubeda:2015fx} by showing that new GSD systems commonly spread when they increase \textit{or} decrease linkage with loci that experience haploid selection.
+(2015)~\cite{Ubeda:2015fx} by showing when new GSD systems that increase \textit{or} decrease linkage with loci spread.
+%that experience haploid selection.
 This result is qualitatively distinct from those for diploid selection alone~\cite{vanDoorn:2007eu,vanDoorn:2010hu} and suggests that haploid selection is more likely to promote transitions between sex-determination systems.
-However, we also show that transitions involving haploid selection cannot be simply explained by invoking sex-ratio selection. 
-In particular, under a wide range of conditions, we show that transitions in sex-determining system are favoured \textit{equally strongly} in situations where sex-ratio biases increase or decrease (and in situations where sex-ratio biases are present or absent).
+We also show that transitions involving haploid selection cannot be simply explained by invoking sex-ratio selection. 
+In particular, under a wide range of conditions, we show that transitions in sex-determining system are favoured \textit{equally strongly} in situations where sex-ratio biases increase or decrease (and in situations where sex-ratio biases are ancestrally present or absent).
 Finally, we show that ESD may not evolve, even if the sex ratio is initially biased by haploid selection, which would not be predicted by previous theories for transitions to ESD~\cite{Charnov:1982wg,Bull:1983vi,West:2009we}.
-Together, our results suggest that sex ratio selection is not an overwhelming force driving transitions between sex-determining systems.
+Together, our results suggest that selection to equalize the sex ratio is not an overwhelming force driving transitions between sex-determining systems.
 
@@
 %\centering
-%\centerline{\includegraphics[width=\linewidth]{Sex_determination_outline.pdf}}
+\centerline{\includegraphics[width=\linewidth]{../Plots/Sex_determination_outline.pdf}}
 \caption{
@@
 Panel A: Recombination rate parameters between the ancestral-sex-determining locus ($\mathbf{X}$, here assumed to have alleles X and Y), a locus under selection ($\mathbf{A}$, with alleles $A$ and $a$), and a new sex-determining locus ($\mathbf{M}$, with alleles $M$ and $m$).
-If $r<1/2$, then associations between ancestral sex-determining alleles and selected alleles can be maintained past recombination in males. 
+If $r<1/2$, then associations between ancestral sex-determining alleles and selected alleles can be maintained in males. 
 Panel B: Haploid selection is often sex-specific, occurring during haploid production or competition in either males or females. 
@@
 However, the zygotic sex ratio is not biased by male haploid selection in ZW sex-determining systems. 
-Similarly, zygotic sex-ratio biases can occur if haploid selected alleles are associated with new sex-determining alleles ($R<1/2$). 
+Similarly, zygotic sex-ratio biases can arise if haploid selected alleles are associated with new sex-determining alleles ($R<1/2$). 
 Panel C: During cis-GSD transitions (XY to XY or ZW to ZW), a neo-Y allele spreads to pseudo-fixation (its maximum frequency among male gametes) and the ancestral Y allele is lost. 
@@
 %(and the $\mathbf{M}$ genotype of their mother in the case of maternal control).
-Diploid males and females then experience \textcolor{red}{viability(?)} selection, with relative fitnesses $w_{AA}^{\circ}$, $w_{Aa}^{\circ}$, and $w_{aa}^{\circ}$.
+Diploid males and females then experience viability and/or individual-based fertility selection, with relative fitnesses $w_{AA}^{\circ}$, $w_{Aa}^{\circ}$, and $w_{aa}^{\circ}$.
 %where $g$ is the diploid genotype at the $\mathbf{A}$ locus ($g \in \{AA, Aa, aa\}$).
-\textcolor{red}{We do not consider fertility(?) or sexual selection.}
+We do not consider fertility selection based on the mating pair or sexual selection.
 The next generation of gametes is produced by meiosis, during which recombination and sex-specific meiotic drive can occur. 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Results}
-%%%%%%%%%%%%%%%%%%%%%%%%%
-
 The model outlined above describes both ancestral XY and ZW sex-determining systems. %if we relabel the two sexes as being ancestrally `heterogametic' or ancestrally `homogametic'. 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Results}
+%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsection*{Generic invasion by a neo-Y or neo-W}
+
+We begin by describing the precise conditions under which new sex determining alleles can spread within a population.  
+These general conditions then allow us to consider several special cases of interest in subsequent sections.
 
@@
 %Since $f(\Lambda_{mA}^{(i)})$ and $f(\Lambda_{ma}^{(i)})$ are of opposite signs, the leading eigenvalue must fall between these two quantities and is the larger of them when $R = 0$ (see \nameref{file:Mathematica}).
-If both haplotypic growth rates are greater than one ($\Lambda_{mA}^{(XY)}, \Lambda_{ma}^{(XY)}>1$), then the new sex-determining allele invades regardless the rate of recombination between the new sex-determining locus and the selected locus ($R$), see \nameref{app:inv_cond} for details.
+If both haplotypic growth rates are greater than one ($\Lambda_{mA}^{(XY)}, \Lambda_{ma}^{(XY)}>1$), then the new sex-determining allele invades regardless of the rate of recombination between the new sex-determining locus and the selected locus ($R$), see \nameref{app:inv_cond} for details.
 Conversely, if both haplotypic growth rates are less than one ($\Lambda_{mA}^{(XY)}, \Lambda_{ma}^{(XY)}<1$), then invasion can never occur.  
@@
 Second, Fisherian sex-ratio selection will favour the spread of a neo-W and inhibit the spread of a neo-Y if the ancestral zygotic sex ratio is biased towards males (i.e., the first factor of the $\Lambda_{mi}^{(XY)}$ is greater than one for a neo-W and less than one for a neo-Y when $\zeta>1/2$), as might occur when the ancestral sex-determining locus is linked to a locus experiencing meiotic drive in males, for example.
-However, the spread of a neo-Y (neo-W) also depends on the male (female) fitness of associated alleles (see terms involving equilibrium allele frequencies, $\hat{p}$'s).
-This implies that neither sex-ratio selection or selection on associated alleles dominates the invasion dynamics of a new sex-determining allele, allowing the sex ratio to become more or less biased during a transition (as previously shown in two special cases; \cite{Kozielska:2010vm,Ubeda:2015fx}).
+However, the spread of a neo-Y (neo-W) also depends on the male (female) fitness of associated alleles (see terms involving equilibrium allele frequencies, $\hat{p}$'s), including haploid selection that additionally biases the sex ratio.
+This implies that both Fisherian selection to equalize the sex-ratio and selection favoring sex-linked drivers that distort the sex ratio play roles in the invasion dynamics of a new sex-determining allele, allowing the sex ratio to become more or less biased during a transition (as previously shown in two special cases; \cite{Kozielska:2010vm,Ubeda:2015fx}).
+%neiher sex-ratio selection nor selection on associated alleles dominates the invasion dynamics of a new sex-determining allele, allowing the sex ratio to become more or less biased during a transition (as previously shown in two special cases; \cite{Kozielska:2010vm,Ubeda:2015fx}).
 %That is, 
@@
 
-In order to explicitly determine the conditions under which a rare new sex-determining allele spreads, we must calculate the equilibrium frequency of the $A$ allele (i.e., $\hat{p}^\female_X$, $\hat{p}^\male_X$, and $\hat{p}^\male_Y$) and Y-bearing male gametes ($\hat{q}$) in the ancestral population.
-Since only the $\mathbf{A}$ locus experiences selection directly, any deterministic evolution requires that there is a polymorphism at the $\mathbf{A}$ locus. 
+In order to explicitly determine the conditions under which a new sex-determining allele spreads, we must calculate the equilibrium frequency of the $A$ allele (i.e., $\hat{p}^\female_X$, $\hat{p}^\male_X$, and $\hat{p}^\male_Y$) and Y-bearing male gametes ($\hat{q}$) in the ancestral population.
+Because only the $\mathbf{A}$ locus experiences selection directly, any deterministic evolution requires that there be a polymorphism at the $\mathbf{A}$ locus. 
 Polymorphisms can be maintained by mutation-selection balance or transiently present during the spread of beneficial alleles. 
-However, polymorphisms maintained by selection can maintain alleles at intermediate allele frequencies for longer periods. 
-Here, we focus on polymorphisms maintained by selection, where the $A$ allele reaches a stable intermediate equilibrium frequency under the ancestral sex-determining system before the new sex-determining allele ($m$) arises.
+%However, polymorphisms maintained by selection can maintain alleles at intermediate allele frequencies for longer periods. 
+Here, however, we focus on polymorphisms maintained by selection, which can maintain alleles at intermediate frequencies for longer periods. 
+%where the $A$ allele reaches a stable intermediate equilibrium frequency under the ancestral sex-determining system before the new sex-determining allele ($m$) arises. 
 Such polymorphisms can be maintained by heterozygote advantage, sexually-antagonistic selection, ploidally-antagonistic selection, or a combination~\cite{Immler:2012tl}.
 We can analytically calculate the allele frequency of the $A$ allele using two alternative simplifying assumptions: 
-(1) the $\mathbf{A}$ locus is within (or tightly linked to) the non-recombining region around the ancestral sex-determining locus ($r \approx 0$) or (2) selection is weak relative to recombination ($s^\circ$, $t^\circ$, $\alpha_{\Delta}^\circ$ $<<$ $r$).
+(1) the $\mathbf{A}$ locus is tightly linked to the non-recombining region around the ancestral sex-determining locus ($r \approx 0$) or (2) selection is weak relative to recombination ($s^\circ$, $t^\circ$, $\alpha_{\Delta}^\circ$ $<<$ $r$).
 
@@
 In essence, through tight linkage with the $\mathbf{A}$ locus, the ancestral Y becomes strongly specialized on the allele that has the highest fitness across male haploid and diploid phases. 
-Given that the ancestral Y is at this equilibrium, it is not possible for a neo-Y to create males that have higher fitness than the ancestral Y.
-
-Neo-W alleles, on the other hand, can invade an ancestral XY system under some conditions (the full invasion conditions are given in \nameref{app:inv_cond}; equations \ref{Binvasion} and \ref{Ainvasion}).
+It is thus not possible for a neo-Y to create males that have higher fitness than the ancestral Y, and cis-GSD transitions are never favoured.
+
+Neo-W alleles, on the other hand, can invade an ancestral XY system because, under some conditions the W can become more strongly specialized for females (the full invasion conditions are given in \nameref{app:inv_cond}; equations \ref{Binvasion} and \ref{Ainvasion}).
 Thus,
@@
 
-\noindent\textit{Conclusion 1:}
-\textbf{selection on loci within the non-recombining region around the sex-determining locus ($r\approx0$) allows the invasion of less closely linked sex-determining alleles ($r<R\leq1/2$) during a trans-GSD transition} (XY $\leftrightarrow$ ZW).
+\noindent\textit{Conclusion 1A:}
+%\textbf{selection on loci within the non-recombining region around the sex-determining locus ($r\approx0$) allows the invasion of less closely linked sex-determining alleles ($r<R\leq1/2$) during a trans-GSD transition} (XY $\leftrightarrow$ ZW).
+\textbf{Selection on loci in or near the non-recombining region around the sex-determining locus ($r\approx0$) prevents cis-GSD transitions (XY $\leftrightarrow$ XY, ZW $\leftrightarrow$ ZW) but can spur trans-GSD transitions (XY $\leftrightarrow$ ZW).}
 \vspace{0.5cm}
 
-\noindent This does not depend on the form of selection maintaining a polymorphism (sexually-antagonistic selection, overdominance, ploidally-antagonistic selection, or some combination, Fig \ref{fig:SexAntagTighter}, \nameref{fig:temporalOverdominance}, \nameref{fig:regionPloidAntag}, and \nameref{fig:SexAntagTighterMaleDrive}).
+Conclusion 1A does not depend on the form of selection maintaining a polymorphism (sexually-antagonistic selection, overdominance, ploidally-antagonistic selection, or some combination, Fig \ref{fig:SexAntagTighter}, \nameref{fig:temporalOverdominance}, \nameref{fig:regionPloidAntag}, and \nameref{fig:SexAntagTighterMaleDrive}).
 The conditions become more restrictive, however, with increasing recombination ($R$) between the new sex-determining locus and the selected locus.  
 The invasion of completely unlinked neo-W alleles ($R = 1/2$) can occur with overdominance in males or with haploid selection (e.g., a case with male drive opposed by diploid selection in \cite{Kozielska:2010vm}) but is not possible with only sexually-antagonistic selection where selection is directional in each diploid sex (see \nameref{file:Mathematica}).
-Here, we focus on cases where there is no haploid selection and discuss the additional effect of haploid selection in \nameref{app:inv_cond}. 
+Here, we focus on cases where there is no haploid selection (Fig \ref{fig:SexAntagTighter}A) and discuss the additional effect of haploid selection in \nameref{app:inv_cond}. 
 %Essentially, neo-W alleles are able to invade (even with $R>r$) because the ancestral X experiences selection in males. 
@@
 \centering
-%\centerline{\includegraphics[width=1.5\linewidth]{PositionPlot_SexAntagTighter}}
+\centerline{\includegraphics[width=\linewidth]{../Plots/PositionPlot_SexAntagTighter}}
 \caption{
-{\bf Transitions between XY and ZW systems can occur even when the new sex-determining locus is less tightly linked to a locus under sexually-antagonistic selection (even without haploid selection).}
-In panel A, linkage is loose enough relative to selection that the analytical results assuming weak selection hold, and a neo-W allele can only invade when it arises at a locus more tightly linked with the selected locus ($R<r$; shaded region).
-In panel B, linkage is tight enough relative to selection that the analytical results assuming weak selection do not hold, and a neo-W can invade even when it is less tightly linked with the selected locus ($r<R$; unshaded region around \text{*}).
+{\bf Transitions between XY and ZW systems can occur even when the new sex-determining locus is less tightly linked to a locus under sexually-antagonistic selection (no haploid selection).}
+In panel A, linkage is initially tight relative to selection and a neo-W can invade even when it is less tightly linked with the selected locus ($r<R$; unshaded region around \textbf{*}).
+In panel B, linkage is loose enough relative to selection that the analytical results assuming weak selection hold, and a neo-W allele can only invade when it arises at a locus more tightly linked with the selected locus ($R<r$; shaded region).
 In panel C we vary the recombination rate between the neo-W and the selected locus ($R$) for a fixed recombination rate between the ancestral sex-determining locus and the selected locus ($r=0.005$). 
-Coloured markers show recombination rates for which the temporal dynamics of invasion are plotted in the inset, demonstrating that neo-W alleles can reach pseudo-fixation if they are more (black) or less (red) closely linked to a locus experiencing sexually-antagonistic selection (neo-W which are too loosely linked (blue and green) do not invade).
+Coloured markers show recombination rates for which the temporal dynamics of invasion are plotted in the inset, demonstrating that neo-W alleles can reach pseudo-fixation if they are more (black) or less (red) closely linked to a locus experiencing sexually-antagonistic selection.
 A very loosely linked neo-W does not spread in this case (blue and green lines overlap and go to 0 in inset). 
-Fitness parameters are: $w_{AA}^\female = 1.05$, $w_{aa}^\male = 1.2$, $w_{aa}^\female = w_{AA}^\male = 0.85$, $w_{Aa}^\circ = 1$,  $t^\circ = \alpha^\circ_\Delta = 0$.
+Fitness parameters are: $w_{AA}^\female = 1.05$, $w_{aa}^\male = 1.2$, $w_{aa}^\female = w_{AA}^\male = 0.85$, $w_{Aa}^\circ = 1$.%,  $t^\circ = \alpha^\circ_\Delta = 0$.
 %\textcolor{red}{consider removing panel A, which is repeated in Fig 3.}
@@
 %To develop an intuition for how less closely linked neo-W alleles invade ($R>r$), we here focus on cases where there is no haploid selection and discuss the additional effect of haploid selection in \nameref{app:inv_cond}.
-If we categorise the $a$ allele as being ancestrally `male-beneficial' via the fact that it is fixed on Y backgrounds, then $\Lambda_{W'A}^{(XY)}>1$ indicates that the neo-W spreads when found with the ancestrally `female-beneficial' allele.
-Broadly, this is possible because ancestral X alleles are sometimes in males and are therefore unable to perfectly specialise on the `female-beneficial' allele. 
-For example, when the $a$ allele is favoured on ancestral X backgrounds in males, a polymorphism of $A$ and $a$ alleles can be maintained on the X background despite selection for the $A$ allele in females ($s^\female>0$, $0<h^\female<1$), see outlined region in Fig \ref{fig:regionplots}A.
-When the $a$ allele is strongly favoured on the X background in males ($w_{aa}^\male$ sufficiently large relative to $w_{Aa}^\male$), neo-W-$A$ haplotypes can spread ($\Lambda_{W'A}^{(XY)}>1$, see grey region in Fig \ref{fig:regionplots}A) because they produce higher fitness females ($AA$ or $Aa$ genotypes) and are unleashed from counterselection in males.
+%If we categorise the $a$ allele as being ancestrally `male-beneficial' via the fact that it is fixed on Y backgrounds, then $\Lambda_{W'A}^{(XY)}>1$ indicates that the neo-W spreads when found with the ancestrally `female-beneficial' allele.
+%Broadly, this is possible because ancestral X alleles are sometimes in males and are therefore unable to perfectly specialise on the `female-beneficial' allele. 
+%For example, when the $a$ allele is favoured on ancestral X backgrounds in males, a polymorphism of $A$ and $a$ alleles can be maintained on the X background despite selection for the $A$ allele in females ($s^\female>0$, $0<h^\female<1$), see outlined region in Fig \ref{fig:regionplots}A.
+%When the $a$ allele is strongly favoured on the X background in males ($w_{aa}^\male$ sufficiently large relative to $w_{Aa}^\male$), neo-W-$A$ haplotypes can spread ($\Lambda_{W'A}^{(XY)}>1$, see grey region in Fig \ref{fig:regionplots}A) because they produce higher fitness females ($AA$ or $Aa$ genotypes) and are unleashed from counterselection in males.
+The reason that neo-W-$A$  haplotypes can spread ($\Lambda_{W'A}^{(XY)}>1$) is because they can sometimes produce higher fitness females that are unleashed from counterselection in males. 
+Broadly, this is possible because ancestral X alleles are found in both males and females and are therefore unable to perfectly specialize on the `female-beneficial' allele. 
+For example, when $A$ is female beneficial and $a$ is male beneficial, a polymorphism can be maintained on the X when the $A$ allele is strongly counterselected in males ($w^\male_{Aa}$  sufficiently small relative to $w^\male_{aa}$).
+Neo-Ws, however, spend no time in males and can build stronger associations with the female-beneficial allele (see gray region in Fig \ref{fig:regionplots}A).
 
@@
 %\centerline{\includegraphics[width=1.25\linewidth]{Region_plot_combined_Mike}}
-%\centerline{\includegraphics[width=1.25\linewidth]{Region_plot_combined}}
+\centerline{\includegraphics[width=1\linewidth]{../Plots/Region_plot_combined}}
 \caption{
-{\bf When the ancestral XY locus is tightly linked to a locus under selection ($r=0$), one or both neo-W haplotypes can spread. }
-We vary the fitness of male homozygotes relative to heterozygotes ($w_{Aa}^\circ=1$) and only consider stable equilibria at which both $\mathbf{A}$ locus alleles are maintained and the $a$ allele is initially fixed on Y backgrounds, region outlined.
+{\bf When the ancestral XY locus is tightly linked to a locus under selection ($r=0$), one or both neo-W haplotypes can spread (no haploid selection).}
+We vary the fitness of male homozygotes relative to heterozygotes ($w_{Aa}^\circ=1$) and only consider stable equilibria at which both $\mathbf{A}$ locus alleles are maintained and the $a$ allele is initially fixed on the Y (region outlined).
 Here, selection in females can favour the $A$ allele (panel A, $w_{aa}^\female=0.85$, $w_{AA}^\female=1.05$), favour the $a$ allele (panel B, $w_{aa}^\female=1.05$, $w_{AA}^\female=0.85$), or be overdominant (panel C, $w_{aa}^\female=w_{AA}^\female=0.6$).
@@
 \nameref{fig:positionOverdominance} shows the dynamics arising with the parameters marked with a dagger. 
-Here, there is no haploid selection $t^\circ = \alpha^\circ_\Delta = 0$.
+%Here, there is no haploid selection $t^\circ = \alpha^\circ_\Delta = 0$.
 }
@@
 
-Given that the $a$ allele can be considered ancestrally `male-beneficial' because it is fixed on Y backgrounds, it is surprising that neo-W-$a$ haplotypes can sometimes be favoured by selection in females ($\Lambda_{W'a}^{(XY)}>1$).
-Again, this occurs because ancestral X alleles also experience selection in males, where they are ancestrally always paired with a Y-$a$ gamete. 
-If there is overdominance in males, X-$A$ Y-$a$ males have high fitness and the $A$ allele is favoured by selection on the X background in males. 
+Given that the $a$ allele is fixed on the Y and can be considered ancestrally `male-beneficial', it is surprising that neo-W-$a$ haplotypes can sometimes be favoured by selection in females ($\Lambda_{W'a}^{(XY)}>1$).
+Again, this occurs because ancestral X alleles experience selection in both males and females, and conditions can arise where increases in the $a$ allele would be favored in females too.
+%, where they are ancestrally always paired with a Y-$a$ gamete.
+For example, if there is overdominance in males, X-$A$ Y-$a$ males have high fitness and the $A$ allele is favoured by selection on the X background in males. 
 Therefore, the $A$ allele can be polymorphic or even fixed on the X background despite selection favouring the $a$ allele in females (e.g., see outlined region in Fig \ref{fig:regionplots}B and~\cite{Lloyd1977,Otto2014}).
@@
 Wherever both haplotypic growth rates are greater than one, invasion by a neo-W is expected regardless of its linkage with the selected locus (i.e., for any $R$, see \nameref{fig:positionOverdominance} and \nameref{fig:temporalOverdominance} for examples).
-
-Assuming selection is weak relative to recombination, van Doorn and Kirkpatrick~\cite{vanDoorn:2010hu} showed that invasion by a neo-W allele occurs under the same conditions as `pseudo-fixation' (at pseudo-fixation the neo-W reaches its maximum frequency among eggs, which is usually 1/2, but can deviate from 1/2 when there is haploid selection before censusing).
+As a consequence, evolution can favor a new sex determination system on a different chromosome, despite the fact that this unlinks the sex determination locus from the selected locus.
+
+Assuming selection is weak relative to recombination, van Doorn and Kirkpatrick~\cite{vanDoorn:2010hu} showed that invasion by a neo-W allele occurs under the same conditions as its fixation in females.
+%`pseudo-fixation' (at pseudo-fixation the neo-W reaches its maximum frequency among eggs, which is usually 1/2, but can deviate from 1/2 when there is haploid selection before censusing). 
 An equivalent analysis is not possible where recombination rates are low. 
-However, numerical simulations demonstrate that, with tight sex linkage, new sex-determining alleles do not necessarily reach pseudo-fixation, which can lead to the stable maintenance of a mixed sex-determining system, in which X, Y, Z, and W alleles all segregate (e.g., \nameref{fig:freqAll}B,C).
+However, numerical simulations demonstrate that, with tight sex linkage, neo-Y or neo-W alleles do not necessarily reach fixation in males or females, respectively, which can lead to the stable maintenance of a mixed sex-determining system, in which X, Y, Z, and W alleles all segregate (e.g., \nameref{fig:freqAll}B,C).
+
+From the arguments above we conclude that
+\vspace{0.5cm}
+
+\noindent\textit{Conclusion 1B:}
+\textbf{With tight linkage between a selected locus and the ancestral sex determination system ($r\approx0$), selection to better specialize on the ancestrally-non-heterogametic sex can drive trans-GSD transitions (XY $\leftrightarrow$ ZW) that weaken sex-linkage ($r<R\leq1/2$; potentially even shifting sex determination to a different chromosome) and/or lead to polymorphic sex-determination systems.}
+\vspace{0.5cm}
+
+Adding haploid selection (\nameref{app:inv_cond}) we also conclude that
+\vspace{0.5cm}
+
+\noindent\textit{Conclusion 1C:}
+\textbf{
+
+}
+\vspace{0.5cm}
 

### 2018-04-18 LaTeX/main_revised.tex
almost done sallys comments to weak linkage

@@
 \textbf{
-
+Haploid selection allows trans-GSD transitions that weaken sex-linkage ($r<R\leq1/2$; potentially even shifting sex determination to a different chromosome) even when selection is sexually-antagonistic with directional selection in each diploid sex.
+With initially tight linkage, these transitions equalize the sex ratio by reducing linkage to alleles under haploid selection.
 }

### 2018-04-18 LaTeX/main_revised.tex
sallys comments added to start of ESD

@@
 \begin{equation}
-\lambda_{W'}^{(XY)} =\lambda_{Y'}^{(XY)}+\left(2\alpha_{\Delta}^\male-2\alpha_{\Delta}^\female+t^\male-t^\female \right) \left( \hat{p}^\male_Y-\hat{p}^\male_X \right)/2
+\lambda_{W'}^{(XY)} =\lambda_{Y'}^{(XY)}+\left[\left(2\alpha_{\Delta}^\male-2\alpha_{\Delta}^\female+t^\male-t^\female \right) \left( \hat{p}^\male_Y-\hat{p}^\male_X \right)/2\right]
 +O\left(\epsilon^3 \right)
@@
 \noindent
-where $V_{A}=\bar{p}(1-\bar{p})$ is the variance in the equilibrium frequency of $A$ and $S_{A}=(D^\male +\alpha_{\Delta}^\male+t^\male) - (D^\female+\alpha_{\Delta}^\female+t^\female)$ describes sex differences in selection for the $A$ versus $a$ allele across diploid selection, meiosis, and gametic competition.
-The diploid selection term, $D^\circ=\big{[} \bar{p}s^\circ+(1-\bar{p})h^\circ s^\circ\big{]} -\big{[} \bar{p}h^\circ s^\circ+(1-\bar{p}) \big{]}$, is the difference in fitness between $A$ and $a$ alleles in diploids of sex $\circ \in \{\female,\male\}$, where $\bar{p}$ is the leading-order probability of mating with an $A$-bearing gamete from the opposite sex (equation \ref{eq:pAve}).
-The difference in $A$-allele-frequency among Y-bearing sperm versus X-bearing sperm is given by $\hat{p}^\male_Y-\hat{p}^\male_X=V_{A}S_{A}(1-2r)/(2r)$.
+where $V_{A}=\bar{p}(1-\bar{p})$ is the variance in the equilibrium frequency of $A$ and $S_{A}=(\bar{s}^\male +\alpha_{\Delta}^\male+t^\male) - (\bar{s}^\female+\alpha_{\Delta}^\female+t^\female)$ describes sex differences in selection for the $A$ versus $a$ allele across diploid selection, meiosis, and gametic competition.
+The diploid selection term, $\bar{s}^\circ=\big{[} \bar{p}s^\circ+(1-\bar{p})h^\circ s^\circ\big{]} -\big{[} \bar{p}h^\circ s^\circ+(1-\bar{p}) \big{]}$, is the difference in fitness between $A$ and $a$ alleles in diploids of sex $\circ \in \{\female,\male\}$, where $\bar{p}$ is the leading-order probability of mating with an A-bearing gamete from the opposite sex (equation \ref{eq:pAve}) and the difference in $A$-allele-frequency among Y-bearing sperm versus X-bearing sperm is, at equilibrium, $\hat{p}^\male_Y-\hat{p}^\male_X=V_{A}S_{A}(1-2r)/(2r)$.
 
@@
 
-With weak selection and no haploid selection ($t^\circ=\alpha^\circ_{\Delta}=0$), the spread of a neo-W is equivalent to the spread of a neo-Y ($\lambda_{W'}^{(XY)}=\lambda_{Y'}^{(XY)}$), such that trans-GSD transitions can also occur only if the new sex-determining locus is more closely linked to a locus under selection ($R<r$), as found by \cite{vanDoorn:2010hu}.
+Without haploid selection ($t^\circ=\alpha^\circ_{\Delta}=0$), the spread of a neo-W is equivalent to the spread of a neo-Y ($\lambda_{W'}^{(XY)}=\lambda_{Y'}^{(XY)}$), when selection is weak relative to recombination, such that trans-GSD transitions can also occur only if the new sex-determining locus is more closely linked to a locus under selection ($R<r$), as found by \cite{vanDoorn:2010hu}.
 When there is haploid selection, invasion also typically occurs when the neo-W is more closely linked to the selected locus than the ancestral sex-determining region (Fig \ref{fig:Combination_Centimorgans}).
@@
 %The second term in Eq \eqref{eq:lambda_neoW} therefore disappears and invasion depends only on the sign of $(r-R)$.%, as in the case of the neo-Y. 
-However, with haploid selection and some ancestral sex-linkage ($r<1/2$; allowing allele frequency differences on the X and Y), the additional term in Eq \eqref{eq:lambda_neoW} can be positive.
+However, with haploid selection and some ancestral sex-linkage ($r<1/2$; allowing allele frequency differences on the X and Y), the term in square brackets in Eq \eqref{eq:lambda_neoW} can be positive.
 This implies the following two conclusions:
@@
 \noindent\textit{Conclusion 2A:}\
-\textbf{new sex-determining alleles (causing cis- \textit{or} trans-GSD transitions) can spread if the arise in closer linkage with a locus that experiences haploid selection than the ancestral-sex-determining locus ($R<r$).}
+\textbf{New sex-determining alleles (causing cis- \textit{or} trans-GSD transitions) can spread if they arise in closer linkage with a locus that experiences selection than the ancestral-sex-determining locus ($R<r$).}
 \vspace{0.5cm}
@@
 \noindent\textit{Conclusion 2B:}\
-\textbf{new sex-determining alleles (causing trans-GSD transitions) can spread if they arise in looser linkage with a locus that experiences haploid selection than the ancestral-sex-determining locus ($r<R$).
-}
+\textbf{New sex-determining alleles (causing trans-GSD transitions) can spread if they arise in looser linkage with a locus that experiences selection than the ancestral-sex-determining locus ($r<R$), requiring haploid selection and some initial sex-linkage ($r<1/2$) as necessary conditions.}
 \vspace{0.5cm}
@@
 \centering
-%\includegraphics[width=\linewidth]{PositionPlot}
+\includegraphics[width=\linewidth]{../Plots/PositionPlot}
 \caption{
 {\bf Ploidally-antagonistic selection allows a less tightly linked neo-W allele to invade.}
-In panel A, male drive ($\alpha^\male_{\Delta} = -1/20$, $t^\circ = \alpha^\female_{\Delta} = 0$) opposes selection in diploids (no sex-differences: $s^\circ = 1/10$, $h^\circ = 7/10$), in which case the new sex-determining allele can invade regardless of its linkage with the selected locus ($R$).
-In panel B, gametic competition in males ($t^\male = -1/10$, $t^\female = \alpha^\circ_{\Delta} = 0$) opposes selection in diploids (sex-differences: $s^\male = 3/20$, $s^\female = 1/20$, $h^\circ = 7/10$), in which case the new sex-determining allele can once again invade regardless of $R$.
+In panel A, male drive ($\alpha^\male_{\Delta} = -1/20$, $t^\circ = \alpha^\female_{\Delta} = 0$) opposes selection in diploids (no sex-differences: $s^\circ = 1/10$, $h^\circ = 7/10$).
+%, in which case the new sex-determining allele can invade regardless of its linkage with the selected locus ($R$).
+In panel B, gametic competition in males ($t^\male = -1/10$, $t^\female = \alpha^\circ_{\Delta} = 0$) opposes selection in diploids (sex-differences: $s^\male = 3/20$, $s^\female = 1/20$, $h^\circ = 7/10$).
+In either case the new sex-determining allele can invade regardless of $R$.
 }
@@
 To clarify the parameter space under which invasion occurs despite looser sex-linkage ($\lambda_{W'}^{(XY)}>1$ despite $R>r$; Conclusion 2B), we focus on the special case where $R=1/2$ and $r<1/2$ (e.g., the selected locus is on the ancestral sex chromosome and the novel sex-determining locus arises on an autosome).
-In Table \ref{tab:specialcases} we give the conditions where invasion occurs when we further assume that haploid selection only occurs in one sex (e.g., during male meiosis only) and dominance coefficients are equal in the two sexes, $h^\female=h^\male$.
+In Table \ref{tab:specialcases} we give the conditions where invasion occurs when we further assume that haploid selection only occurs in one sex \textcolor{red}{(e.g., during male meiosis only)} and dominance coefficients are equal in the two sexes, $h^\female=h^\male$.
 These special cases indicate that neo-W invasion occurs for a large fraction of the parameter space, even if the neo-W uncouples the sex-determining locus from a locus under selection. 
-We show that neo-W alleles can spread for when they are more closely \textit{or} more loosely linked to a locus that experiences haploid selection in Fig \ref{fig:Combination_Centimorgans} (c.f., Fig \ref{fig:SexAntagTighter}A for diploid sexually-antagonistic selection alone).
-In Fig \ref{fig:SexRatioBad}, we also show examples of trans-GSD transitions in sex determination during which linkage with a haploid selected locus increases \textit{or} decreases. 
-When sex-linkage decreases ($R>r$), neo-W alleles can benefit from Y-associated alleles that have higher fitness in the female diploid phase but then dissociate from these alleles through recombination, which occurs before any subsequent haploid selection.
+Surprisingly, neo-W alleles can spread when they are more closely \textit{or} more loosely linked to a locus that experiences haploid selection, as shown in Fig \ref{fig:Combination_Centimorgans} (c.f., Fig \ref{fig:SexAntagTighter}A for diploid sexually-antagonistic selection alone).
+In Fig \ref{fig:SexRatioBad}, we also show examples of trans-GSD transitions in sex determination during which linkage with a haploid selected locus increases \textit{or} decreases, increasing or decreasing sex-ratio bias.
+When sex-linkage decreases ($R>r$), neo-W alleles can benefit from Y-associated alleles that have higher fitness in the female diploid phase but then dissociate from these alleles through recombination before any subsequent haploid selection.
 
@@
 \smallskip
-\caption{Invasion conditions for a neo-W allele at an unlinked locus ($R=1/2$) into an ancestral XY system with linkage ($r<1/2$) and one form of haploid selection}
+\caption{Invasion conditions for a neo-W allele at an unlinked locus ($R=1/2$) into an ancestral XY system with linkage ($r<1/2$) and a single form of haploid selection}
 \begin{tabular}{l l c }
@@
 In this figure, selection is ploidally antagonistic with haploid selection favouring the $a$ allele during male meiosis.
-In panel A, male meiotic drive in an ancestral XY system causes a male bias (see Fig \ref{fig:model_outline}B), allowing a neo-W to invade and replace the ancestral sex-determining system (inset shows neo-W frequency among female gametes, reaching pseudo-fixation), which balances the zygotic sex ratio.
-In panel B, male drive in an ancestral ZW system has no effect on the zygotic sex ratio yet a neo-Y can invade and replace the ancestral sex-determining system (inset shows neo-Y frequency among male gametes, reaching pseudo-fixation).
+In panel A, male meiotic drive in an ancestral XY system causes a male bias (see Fig \ref{fig:model_outline}B), allowing a neo-W to invade and replace the ancestral sex-determining system (inset shows neo-W frequency rising to fixation among female gametes), which balances the zygotic sex ratio.
+In panel B, male drive in an ancestral ZW system has no effect on the zygotic sex ratio yet a neo-Y can invade and replace the ancestral sex-determining system (inset shows neo-Y frequency rising to fixation among male gametes).
 %When $R<1/2$, the neo-Y becomes associated with the allele favoured by drive, causing the zygotic sex ratio to become biased, hence the frequency of the neo-Y at pseudo-fixation can be higher than $0.5$ (inset).
@@
 %Previous research has shown that when the ancestral sex-determining locus is linked to a locus that experiences haploid selection (e.g., meiotic drive), alleles at a new, unlinked sex-determining locus can invade and restore equal sex ratios~\cite{Kozielska:2010vm}.
-Our model allows us to analytically compare GSD-GSD transitions where sex-ratio bias increases, decreases, or remains equal. 
+Our model allows us to analytically compare transitions in genetic sex-determination where sex-ratio bias increases, decreases, or remains equal. 
 For example, if there is meiotic drive in males only ($\alpha^\male_\Delta \neq 0$, $\alpha^\female_\Delta=0$), without gametic competition ($t^\female=t^\male=0$) the zygotic sex ratio is initially biased only when the ancestral sex-determining system is XY (Fig \ref{fig:model_outline}A and Fig \ref{fig:SexRatioBad}A) and not ZW (Fig \ref{fig:SexRatioBad}B).
@@
 \noindent\textit{Conclusion 3:}
-\textbf{when selection is weak relative to recombination, the presence or absence of sex-ratio biases do not create an assymetry in the likelihood of GSD-GSD transitions. } 
+\textbf{When selection is weak relative to recombination, the presence of haploid selection equally favors the spread of a new sex chromosome that reduces sex-ratio bias (benefiting from Fisherian sex ratio selection) as a new sex chromosome that generates a sex-ratio bias (benefiting from drive)" }
 \vspace{0.5cm}
@@
 For example with $R=1/2$ in Fig \ref{fig:SexRatioBad}B (green curve), the neo-Y allele spreads despite the fact that it cannot benefit from drive because free recombination moves it randomly between driven and non-driven backgrounds.
-Nevertheless, the unlinked neo-Y can spread because diploids bearing it more often carry the non-driven allele $A$, which is found at high frequency on the W background and has higher average diploid fitness.% to balance the haploid advantage of the $a$ allele at equilibrium.
+%Nevertheless, the unlinked neo-Y can spread because diploids bearing it more often carry the non-driven allele $A$, which is found at high frequency on the W background and has higher average diploid fitness.% to balance the haploid advantage of the $a$ allele at equilibrium.
+Nevertheless, the unlinked neo-Y can spread because males bearing it more often carry the non-driven allele $A$ and have higher average diploid fitness compared to ZZ males, which bear a high frequency of the driven allele (since $r<R$).
 

### 2018-04-18 LaTeX/main_revised.tex
sallys comments added up to discussion

@@
 %\textcolor{red}{In our deterministic model this means the fraction female is exactly $k$, even when $m$ is rare (exploring the effect of the variance induced by ESD would also be interesting).}
-In our deterministic model this means the fraction female is exactly $k$, even when $m$ is rare (i.e., ESD does not introduce any additional variance in sex determination). 
-Here, we do not assume that the environmental conditions that determine sex also differentially affect the fitness of males versus females. 
+In our deterministic model this means the fraction female in the subpopulation containing $m$ is exactly $k$, even when $m$ is rare (i.e., ESD does not introduce any additional variance in sex determination).
+Here, we assume that the environmental conditions that determine sex does not differentially affect the fitness of males versus females. 
 Such correlations can favour environmental sex-determining systems by allowing each sex to be produced in the environment in which it has highest fitness; in the absence of these correlations, previous theory would predict that ESD is favoured when it produces more equal sex ratios than the ancestral system (see reviews by~\cite{Charnov:1982wg,Bull:1983vi,West:2009we}).
@@
 Of particular interest are ESD mutations that cause half of their carriers to develop as females and half as males ($k=1/2$), creating equal sex ratios.
-The spread of such ESD is determined by
+The spread of such mutations is determined by
 \begin{equation}
@@
 Eq \eqref{eq:lambda_ESD} shows that the ESD mutation gets half of the fitness of a feminizing mutation (neo-W) and half of the fitness of a masculinizing mutation (neo-Y), but only has an effect one half of the time (the other half of the time it produces the same sex as the ancestral system would have).
-As discussed above, $\lambda_{Y'\rvert R=1/2}^{(XY)}$ is necessarily less than one, but $\lambda_{W'\rvert R=1/2}^{(XY)}$ can be greater than one if there is haploid selection.
-That is, with haploid selection, an allele causing environmental-sex-determination can invade an ancestrally-XY system because it generates females that are either rare or have high fitness, in the same manner as a neo-W (likewise, ESD invades a ZW system for the same reasons a neo-Y can).
+As discussed above, $\lambda_{Y'\rvert R=1/2}^{(XY)}$ is necessarily less than one (cis-GSD transition), but $\lambda_{W'\rvert R=1/2}^{(XY)}$ (trans-GSD transition) can be greater than one if there is haploid selection (see Conclusion 2B).
+That is, with haploid selection, an allele causing environmental-sex-determination can invade an ancestrally-XY system because it generates females that are either rare or have high fitness, in the same manner as a neo-W (likewise, ESD invades a ZW system for the same reasons as a neo-Y can).
 %An important result from Eq \eqref{eq:lambda_ESD} is that ESD can invade if there is haploid selection. 
@@
 Significantly, Eq \eqref{eq:lambda_ESD} is the same whether ESD is invading an ancestrally XY or ZW system (because $\lambda_{Y'}^{(XY)} = \lambda_{W'}^{(ZW)}$ and $\lambda_{W'}^{(XY)} = \lambda_{Y'}^{(ZW)}$).
-Thus, Fisherian sex-ratio selection alone does not easily explain GSD to ESD transitions.
-For example, when the ancestral sex-determining system is XY, but not ZW, the sex ratio is biased by male haploid selection.
-Nevertheless, ESD is equally likely to invade when it equalizes the zygotic sex ratio (through $\lambda_{W'}^{(XY)}$) as when it doesn't (through $\lambda_{Y'}^{(ZW)}$). 
+Thus, focusing solely on Fisherian selection to equalize the sex-ratio does not fully explain GSD to ESD transitions.
+For example, when the ancestral sex-determining system is XY the sex ratio is biased by male haploid selection.
+When the ancestral sex-determining system is ZW the sex ratio is not biased.
+Nevertheless, ESD is equally likely to invade both XY and ZW systems, equalizing the zygotic sex ratio in the former case (through $\lambda_{W'}^{(XY)}$) but not in the latter (through $\lambda_{Y'}^{(ZW)}$).
 %This is again because haploid selection can facilitate the turnover of sex chromosomes either through sex-ratio biases or through associations between the new sex determining region with selected alleles.
@@
 In addition, we note that ESD may not invade, even if the sex ratio is initially biased (e.g., with drive in males only, $r<1/2$, $h^\female=h^\male$, and $s^\female s^\male<0$, then $\lambda_{W'}^{(XY)}<1$, see Table \ref{tab:specialcases}).
-We conclude that, as with neo-W and neo-Y loci, associations with selected loci mean that
+We conclude that, as with neo-W and neo-Y loci:
 \vspace{0.5cm}
@@
 \textbf{
-transitions from genetic to environmental sex-determination are not straightforwardly predicted by selection to balance the zygotic sex ratio when haploid selection is present. 
+Transitions from genetic to environmental sex-determination are not straightforwardly predicted by selection to balance the zygotic sex ratio when haploid selection is present. 
 }

### 2018-04-18 LaTeX/main_revised.tex
sallys comments added, still some red text though

@@
 An equivalent analysis is not possible where recombination rates are low. 
-However, numerical simulations demonstrate that, with tight sex linkage, neo-Y or neo-W alleles do not necessarily reach fixation in males or females, respectively, which can lead to the stable maintenance of a mixed sex-determining system, in which X, Y, Z, and W alleles all segregate (e.g., \nameref{fig:freqAll}B,C).
+However, numerical simulations demonstrate that, with tight sex linkage, neo-Y or neo-W alleles do not necessarily reach fixation in males or females, respectively, which can lead to the stable maintenance of a mixed sex-determining system, in which X, Y, and neo-W alleles all segregate (e.g., \nameref{fig:freqAll}B,C).
 
@@
 \noindent\textit{Conclusion 3:}
-\textbf{When selection is weak relative to recombination, the presence of haploid selection equally favors the spread of a new sex chromosome that reduces sex-ratio bias (benefiting from Fisherian sex ratio selection) as a new sex chromosome that generates a sex-ratio bias (benefiting from drive)" }
+\textbf{When selection is weak relative to recombination, the presence of haploid selection equally favors the spread of new sex determination systems that reduce sex-ratio bias (benefiting from Fisherian sex ratio selection) or generate a sex-ratio bias (benefiting from drive)" }
 \vspace{0.5cm}
@@
 %What we would like to stress is that sex-ratio selection alone cannot predict when new sex-determining systems can evolve.
-Significantly, with weak selection, we find that there is no difference in conditions allowing XY to ZW and ZW to XY transitions (Conclusion 3), indicating that transitions in sex determination are not predominantly predicted by their effect on the sex ratio (i.e., the sex-ratio bias created by male haploid selection facilitates the spread of a neo-W allele into an XY system to the same degree that male haploid selection drives the spread of a neo-Y into a ZW system with a 1:1 sex ratio).
+Significantly, with weak selection, we find that there is no difference in conditions allowing XY to ZW and ZW to XY transitions (Conclusion 3)%, indicating that transitions in sex determination are not predominantly predicted by their effect on the sex ratio (i.e., the sex-ratio bias created by male haploid selection facilitates the spread of a neo-W allele into an XY system to the same degree that male haploid selection drives the spread of a neo-Y into a ZW system with a 1:1 sex ratio).
 %An asymmetry can develop when sex-linkage is tight (e.g., Fig \ref{fig:Combination_Centimorgans} near -25cM and 25cM) but under most circumstances we do not predict asymmetry between XY to ZW and ZW to XY transitions despite the presence/absence of sex-ratio selection.
-Thus, haploid selection can favour trans-GSD transitions both via sex-ratio selection and via selection on alleles associated with the new sex-determining allele, and these selective pressures are often predicted to be of equal magnitude.
-
-Our results indicate that haploid selection could be an important factor driving the evolution of new sex-determining systems. 
+even when haploid selection always acts in the same sex (e.g., males).  
+That is, the sex-ratio bias created by male haploid selection facilitates the spread of a neo-W allele into an XY system to the same degree that male haploid selection drives the spread of a neo-Y into a ZW system with a 1:1 sex ratio.
+%Thus, haploid selection can favour trans-GSD transitions both via sex-ratio selection and via selection on alleles associated with the new sex-determining allele, and these selective pressures are often predicted to be of equal magnitude.
+
+%Our results indicate that haploid selection could be an important factor driving the evolution of new sex-determining systems. 
+Because both Fisherian selection to equalize the sex ratio and the benefits of hitchhiking with driven alleles can facilitate transitions among sex chromosome systems, we predict that haploid selection should increase the lability of sex determination systems.
 Even in animal and plant species that have much larger and more conspicuous diploid phases than haploid phases, many loci have been shown to experience haploid selection through gamete competition and/or meiotic drive~\cite{Mulcahy:1996ha,JOSEPH:2004haa, Lalanne2004,Ubeda:2005gw,Fishman2005,Leppala2008,Leppala2013,Didion2015,Didion2016, Lindholm:2016cw}.
@@
 In animals, recent studies have demonstrated that sperm competition, even within a single ejaculate, can alter haploid allele frequencies and increase offspring fitness~\cite{Immler:2014im,Alavioon2017}.
-Nevertheless, although precise estimates are uncertain, a relatively small proportion of all genes are thought to be expressed and selected during competition in animal sperm~\cite{Zheng:2001fi,JOSEPH:2004haa,Vibranovski:2010et}.
-In plants, however, haploid selection may be particularly important due to the presence of a multicellular haploid stage. 
+Nevertheless, although precise estimates are uncertain, a relatively small proportion of all genes are thought to be \textcolor{red}{expressed} and selected during competition in animal sperm~\cite{Zheng:2001fi,JOSEPH:2004haa,Vibranovski:2010et}.
+In plants, however, haploid selection may be particularly important. %due to the presence of a multicellular haploid stage. 
 For example, 60-70\% of all genes are expressed in the male gametophyte, and these genes exhibit stronger signatures of selection than randomly-chosen genes~\cite{Borg:2009jpa,Arunkumar:2013iq,Gossmann:2014dua}.
@@
 
-In general, we predict that haploid selection increases lability of sex-determining systems, particularly because haploid selection can cause transitions that increase or decrease sex-linkage (Conclusion 2A \& 2B, e.g., the final state of the red line in Fig \ref{fig:SexRatioBad}B is the starting state in Fig \ref{fig:SexRatioBad}A).
+%In general, we predict that haploid selection increases lability of sex-determining systems, particularly because haploid selection can cause transitions that increase or decrease sex-linkage (Conclusion 2A \& 2B, e.g., the final state of the red line in Fig \ref{fig:SexRatioBad}B is the starting state in Fig \ref{fig:SexRatioBad}A).
 Frequent turnovers driven by haploid selection may help to explain the relative rarity of heteromorphic sex chromosomes in plants.
-If haploid selection is strong but selective differences between male and female diploids are weak, we specifically predict that trans-GSD transitions are favoured more strongly than cis-GSD transitions, with transitions to ESD intermediate (e.g., with $|D^\male - D^\female| << |\alpha_\Delta^\male - \alpha_\Delta^\female + t^\male - t^\female|$ we have $\lambda_{W'}^{(XY)} > \lambda_{Y'}^{(XY)}$; Eq \ref{eq:lambda_neoW}).
+If haploid selection is strong but selective differences between male and female diploids are weak, we specifically predict that trans-GSD transitions are favoured more strongly than cis-GSD transitions, with transitions to ESD intermediate (e.g., with $|\bar{s}^\male - \bar{s}^\female| << |\alpha_\Delta^\male - \alpha_\Delta^\female + t^\male - t^\female|$ we have $\lambda_{W'}^{(XY)} > \lambda_{Y'}^{(XY)}$; Eq \ref{eq:lambda_neoW}).
 Among the relatively few dioecious clades in which multiple species have well characterized sex chromosomes~\cite{Ming:2011iy}, trans-GSD transitions have been inferred in \textit{Silene} subsection \textit{Otites}~\cite{Slancarova:2013dq} and in \textit{Salicaceae}~\cite{Pucholt2015,Pucholt2017}.
 Assuming that transitions from dioecy to hermaphroditism (equal parental investment in male and female gametes) are favoured in a similar manner to the ESD examined here (equal probability of zygotes developing as males or females), our results suggest that competition among haploid pollen could drive transitions between dioecy and hermaphroditism, which are frequent in plants~\cite{Kafer2017, Goldberg2017}.
-To further examine this link, future theoretical investigations could also include selfing and inbreeding depression during transitions between dioecy and hermaphroditism. 
-Future empirical investigations could look for evidence of haploid selection acting on former sex chromosomes in hermaphroditic species (e.g., a study such as \cite{Sandler264382} on ancestral, rather than derived, sex chromosomes).
-
-New sex-determining alleles have previously be shown to spread when they arise in linkage with loci that experience sex differences in selection because beneficial associations build up between alleles that determine sex and alleles that are favoured in that sex~\cite{vanDoorn:2007eu,vanDoorn:2010hu,Ubeda:2015fx,Muralidhar2018}.
+To further examine this link, future theory could include haploid selection and sex chromosomes when investigating transitions between dioecy and hermaphroditism. 
+Future empirical studies could look for evidence of haploid selection acting on former sex chromosomes in hermaphroditic species (e.g., a study such as \cite{Sandler264382} on ancestral, rather than derived, sex chromosomes).
+
+New sex-determining alleles have previously been shown to spread when they arise in linkage with loci that experience sex differences in selection because beneficial associations build up between alleles that determine sex and alleles that are favoured in that sex~\cite{vanDoorn:2007eu,vanDoorn:2010hu,Ubeda:2015fx,Muralidhar2018}.
 In support of this hypothesis, researchers have identified genes on recently derived sex chromosomes that might be under sexually-antagonistic selection~\cite{Lindholm:2002dw,Tripathi:2009cw,Ser:2010iq}.
 However, we show that, if selected loci are tightly linked to the ancestral sex-determining locus, they can drive trans-GSD transitions during which sex-linkage is reduced (Conclusion 1), thus widening the genomic locations that could be driving trans-GSD transitions.
-In addition, we find that polymorphic sex determining systems (X, Y, W, and Z alleles all present) can be maintained when a selected locus is tightly linked to the ancestral sex-determining system (e.g., \nameref{fig:freqAll}B and \nameref{fig:freqAll}C), which is not possible with loose linkage~\cite{vanDoorn:2010hu}.
+In addition, we find that polymorphic sex determining systems (X, Y, and neo-W alleles all segregating) can be maintained when a selected locus is tightly linked to the ancestral sex-determining system (e.g., \nameref{fig:freqAll}B and \nameref{fig:freqAll}C), which is not possible with loose linkage~\cite{vanDoorn:2010hu}.
 These conclusions apply in cases with or without haploid selection.
@@
 Furthermore, several rodent species maintain feminizing alleles along with the ancestral X and Y sex-determination alleles (reviewed in~\cite{Fredga1994}). 
-In nine \textit{Akadon} rodent species, it appears that male-determining-\textit{sry} expression is suppressed by an autosomal feminizing allele, creating XY females~\cite{Bianchi2002,Sanchez2010}. 
+In nine \textit{Akadon} rodent species, it appears that male-determining-\textit{sry} expression is suppressed by an autosomal feminizing allele (a neo-W allele), creating XY females~\cite{Bianchi2002,Sanchez2010}.
 XY females have increased fitness relative to XX females~\cite{Hoekstra2001}. However, it is not yet clear whether loci linked to the feminizing factor or the ancestral Y cause this effect. 
 Most convincingly, in \textit{Mus microtoides}, females can have XX, XX$^\ast$ or X$^\ast$Y genotypes~\cite{Veyrunes2010}. 
-Previous theory would predict that the X$^\ast$ chromosome (or the autosome it is fused to) harbours female beneficial alleles, driving its spread. 
+Previous theory would predict that the X$^\ast$ chromosome (potentially an autosome that has fused with the sex chromosome) harbours female beneficial alleles, driving its spread. 
 However, XX and XX$^\ast$ females have similar fitness, whereas X$^\ast$Y female fitness is enhanced~\cite{Saunders2014,Saunders2016, Veyrunes2017}. 
-Although Y-linkage of female-beneficial alleles is counterintuitive, our model suggests that it can be stably maintained and then favour new feminizing mutations, which would be a parsimonious explanation for the spread of feminizing alleles in this case.
+Although Y-linkage of female-beneficial alleles is counterintuitive, our model suggests that it can be stably maintained when linkage is initially tight between the sex determining region and the selected locus, subsequently favoring new feminizing mutations, which would be a parsimonious explanation for the spread of feminizing alleles in this case.
 
@@
 This phenomenon was studied by van Doorn and Kirkpatrick (2010)~\cite{vanDoorn:2010hu}, who found that degeneration can prevent fixation of a neo-W or a neo-Y allele, leading to a mixed sex-determining system where the ancestral and new sex-determining loci are both segregating.
-However, they noted that very rare recombination events around the ancestral sex-determining locus can allow these trans-GSD transitions to complete.  
+However, they noted that very rare recombination events around the ancestral sex-determining locus can allow the completion of trans-GSD transitions.  
 %While not explicitly studied, we also predict that Y or W degeneration would prevent fixation of the new sex-determining genes considered here.
 Degeneration around the Y or W could explain why trans-GSD transitions are not observed to be much more common than cis-GSD transitions despite the fact that our models demonstrate that they are favoured under a wider range of conditions, especially with haploid selection.
-For example, there are a dozen sex chromosome configurations among Dipteran species but only one transition between male and female heterogamety~\cite{Vicoso:2015hf}.
+For example, there are a dozen sex chromosome configurations among Dipteran species but only one transition between male and female heterogamety~\cite{Vicoso:2015hf}, but Y degeneration or absence is also very common among \textit{Diptera}.
 
@@
 We conclude that haploid selection should be considered as a pivotal factor driving transitions between sex-determining systems. 
-Further, transitions involving haploid selection can be driven by sex-ratio selection or cause sex-ratio biases to evolve; Fisherian sex-ratio selection is not an overwhelming force (Conclusions 3 \& 4).
+Further, transitions involving haploid selection can be driven by sex-ratio selection or cause sex-ratio biases to evolve; to leading order, selection to balance the sex ratio and hitch-hiking with haploid selected alleles are of equal magnitude (Conclusions 3 \& 4).
 Overall, our results suggest several new scenarios under which new sex-determining systems are favoured, which could help to explain why the evolution of sex-determining systems is so dynamic.
@@
 \section*{Acknowledgments}
-We thank Georgy Sandler and Stephen Wright for sharing their results with us and we thank Bret Payseur for helpful comments on this manuscript. 
+We thank Georgy Sandler and Stephen Wright for sharing their results with us, and we thank Bret Payseur and three anonymous reviewers for helpful comments on this manuscript. 
 %This project was supported by the Natural Sciences and Engineering Research Council of Canada (CGS-D 6564 to MMO; RGPIN-2016-03711 to SPO).

### 2018-04-18 LaTeX/S3Appendix_revised.tex
appendices updated after sally comments addressed

@@
 
+In absence of haploid selection, the fact that a less closely linked neo-W ($R>0$) can invade an XY system with tight sex-linkage can also be reached from Equation 7 in \cite{vanDoorn:2010hu}; for example, with no polymorphism on the Y ($V_Y=0$) and an allelic substitution favoured in females ($\alpha^f,\alpha_X^f>0$) a loosely linked neo-W can invade given the allelic substitution is sufficiently disfavoured on the X in males ($\alpha_X^m < -2\alpha_X^f$), although it is unclear from their implicit equation if and when such an equilibrium is stable.
+
 \subsubsection*{Role of haploid selection with tight linkage between $\mathbf{X}$ and $\mathbf{A}$ loci}

### 2018-04-18 LaTeX/main_revised.tex
appendices updated after sally comments addressed

@@
 
-\textcolor{red}{add to Appendix:}
-\textcolor{red}{In absence of haploid selection Conclusion 1A can also be reached from Equation 7 in \cite{vanDoorn:2010hu}; for example, with no polymorphism on the Y ($V_Y=0$) and an allelic substitution favoured in females ($\alpha^f,\alpha_X^f>0$) a loosely linked neo-W can invade given the allelic substitution is sufficiently disfavoured on the X in males ($\alpha_X^m < -2\alpha_X^f$), although it is unclear from their implicit equation if and when such an equilibrium is stable.}
+%\textcolor{red}{add to Appendix:}
+%\textcolor{red}{In absence of haploid selection Conclusion 1A can also be reached from Equation 7 in \cite{vanDoorn:2010hu}; for example, with no polymorphism on the Y ($V_Y=0$) and an allelic substitution favoured in females ($\alpha^f,\alpha_X^f>0$) a loosely linked neo-W can invade given the allelic substitution is sufficiently disfavoured on the X in males ($\alpha_X^m < -2\alpha_X^f$), although it is unclear from their implicit equation if and when such an equilibrium is stable.}
 
@@
 Degeneration around the Y or W could explain why trans-GSD transitions are not observed to be much more common than cis-GSD transitions despite the fact that our models demonstrate that they are favoured under a wider range of conditions, especially with haploid selection.
-For example, there are a dozen sex chromosome configurations among Dipteran species but only one transition between male and female heterogamety~\cite{Vicoso:2015hf}, but Y degeneration or absence is also very common among \textit{Diptera}.
+For example, there are a dozen sex chromosome configurations among Dipteran species but only one transition between male and female heterogamety~\cite{Vicoso:2015hf}, but Y degeneration or absence is also very common among \textit{Diptera}~\cite{Vicoso:2015hf}.
 

### 2018-05-01 LaTeX/response.tex
matt o went over all revision main text

--- 2018-04-05 LaTeX/response.tex
@@
 reviewers' words\\
-\textcolor{red}{to do/thoughts/questions between coauthors (temporary)}\\
+%\textcolor{red}{to do/thoughts/questions between coauthors (temporary)}\\
 \textcolor{blue}{authors' response}
@@
 \noindent  Line numbers (L\#) in authors' comments refer to those in the revised PDF.
+\textcolor{red}{check line numbers}
 \\
 
-\noindent See diff.pdf for highlighted differences between the original submission and the revised version.
+\noindent See diff.pdf for all differences between the original submission and the revised version.
 
@@
 \noindent\paragraph{Response}
-\textcolor{red}{One could interpret our diploid selection as fertility selection, or am I missing something?
-Sexual selection does seem like a different model though, with for example, male fitnesses depending on female frequencies; a note such as "We do not consider sexual selection" in the paragraph beginning near L111 might do it?}
+\textcolor{blue}{
+One could interpret our diploid selection as a combination of viability and fertility selection, where fertility selection is independent of the mating partner.
+Fertility selection that depends on the mating pair and sexual selection require a different formulation.
+We now note this in the model section (L120-122):
+``Diploid males and females then experience viability and/or individual-based fertility selection, with relative fitnesses $w_{AA}^{\circ}$, $w_{Aa}^{\circ}$, and $w_{aa}^{\circ}$. 
+We do not consider fertility selection based on the mating pair or sexual selection."
+}
 
@@
 \noindent\paragraph{Response}
-\textcolor{blue}{We now call these terms the ``dissociative force" as they break down linkage disequilibrium (L162).}
+\textcolor{blue}{
+We now call these terms the ``dissociative force" as they break down linkage disequilibrium (L161). 
+We have attempted various graphical schemes for representing the three loci in two sexes and the associations that evolve between them in various scenarios. 
+However, apart from Fig 1, we found these too complicated or opaque to be useful. 
+}
 
@@
 \noindent\paragraph{Response}
-\textcolor{blue}{We now mention that the model is deterministic, and hence ignores drift (L136). 
-We later mention that drift can in fact be a key factor in transitions: ``It should be noted, however, that the dynamics of sex-determining alleles with very weak effect will be influenced by genetic drift, which itself has been shown to cause trans-GSD transitions (Veller et al 2017)." (L511)}
+\textcolor{blue}{
+We now mention that the model is deterministic, and hence ignores drift (L127-128). 
+When discussing the model limitations at the end of the Discussion we now mention a study on the effect of drift during trans-GSD transitions, which tend to drift in the direction of epistatically-dominant sex-determining loci (L529-532): ``It should be noted, however, that the dynamics of sex-determining alleles with very weak effect will be influenced by genetic drift, which itself has been shown to cause trans-GSD transitions (Veller et al 2017)."}
 
@@
 \textcolor{blue}{In our deterministic model (where the number of binomial trials is infinite), the variance in the fraction male is 0 with ESD, as it is with GSD. 
-We now mention this on L392: ``In our deterministic model this means the fraction female is exactly $k$, even when $m$ is rare (exploring the effect of the variance induced by ESD would also be interesting)."
+We now mention this (L373-375): ``In our deterministic model this means the fraction female in the subpopulation containing $m$ is exactly $k$, even when $m$ is rare (i.e., ESD does not introduce any additional variance in sex determination)."
  }
@@
 \textcolor{blue}{
-The introduction has been simplified to be as follows.
-The first paragraph discusses how common transitions are (context). 
-The second and third paragraphs discuss the two major mechanisms currently hypothesized to drive the observed transitions, respectively (current theory). 
-The fourth paragraph explains how assuming ancestrally-tight sex-linkage produces previously unexpected transitions (one hole in current theory, and how we address it).
-The fifth paragraph discusses the potential complications of haploid selection for transitions (a second hole in current theory).
-The sixth paragraph describes previous studies on transitions with haploid selection (attempts to address the second hole). 
-The final, seventh, paragraph states how our approach differs from previous attempts and the major findings we uncover (how we address the second hole).  
+Thank you for these very constructive suggestions. We have simplified the introduction according to the suggested format: 
+\begin{enumerate}
+\item[1.]{The first paragraph discusses how common transitions are, and now mentions that recent empirical evidence is making this increasingly apparent. (L2-20)}
+\item[2-3.]{The second and third paragraphs lay out the two major mechanisms thought to drive transitions in sex-determination, (1) selection to stabilize the sex ratio, and (2) linkage associations between alleles favoured in one sex and the alleles that determine that sex.
+(L21-29, L30-38) }
+\item[4.]{Connecting to point (2), we then found it useful to introduce one novel aspect of our model -- we consider a selected locus that is very tightly linked to the ancestral sex-determining locus and find the surprising result that transitions in which linkage is reduced can be favoured.
+(L39-48)}
+\item[5.]{Next, we introduce the most significant model feature, haploid selection, which we present as an evolutionary problem (as suggested by reviewer 1) in light of (1) and (2). (L49-56) }
+\item[6.]{The sixth paragraph then describes previous studies that have included haploid selection (see also reviewer 3 recommendations).
+These studies suggest that (1) and (2) are both very important with haploid selection and point to the major limitations in solving the evolutionary puzzle.
+(L57-69)}
+\item[7.]{Finally, we lay out our main results in this context.
+This makes it clear that our general model is necessary to determine the important forces driving transitions in sex determination.
+We particularly highlight the unexpected conclusions that our model allows us to reach.
+(L70-83)}
+\end{enumerate}
+To accommodate these changes, we have moved the discussion of empirical evidence for haploid selection to the discussion (L441-454). 
 }
@@
 %We now give 3 main conclusions at the end of the introduction (L69) which echo those mentioned by the reviewer (looser linkage can evolve, equal selection to increase or decrease the sex ratio, ESD does not always invade biased sex ratio; all of which suggest haploid selection makes conditions for transitions more permissive).
-We now give 4 main conclusions in the results, in the style of Orr 1998:\\
-%(1) transitions are determined by both sex-ratio selection and selection on associated alleles,\\
-%(2) cis- and trans-GSD transitions are qualitatively different,\\
-(1A) ancestrally-tight sex-linkage allows looser sex-linkage to evolve in trans-GSD transitions (with or without haploid selection),\\
-(1B) haploid selection allows looser sex-linkage to evolve in trans-GSD transitions,\\
-(2) transitions can occur when new sex-determining alleles increase linkage with haploid selected loci,\\
-(3) when selection is weak relative to recombination, sex-ratio selection is exactly equal in magnitude to the selection imposed by associations with selected alleles, and\\
-(4) transitions from genetic to environmental sex-determination are not straightforwardly predicted by selection to balance the zygotic sex ratio when haploid selection is present.
-\vspace{0.25cm}\\
-As (1A), (1B), and (2) have some antecedents in the literature, we discuss these immediately below each conclusion. 
+Following this advice, we now highlight our main conclusions in the results section in the style of Orr 1998:
+\begin{enumerate}
+\item[(1A)] ancestrally-tight sex-linkage allows trans-GSD transitions but not cis-GSD transitions (L228-230)
+\item[(1B)] with ancestrally-tight sex-linkage, trans-GSD transitions (which weaken sex-linkage and can lead to polymorphic sex determination systems) are driven by selection to better specialize on the ancestrally-non-heterogametic sex (L282-286)
+\item[(1C)] with ancestrally-tight sex-linkage, haploid selection can spur trans-GSD transitions (which weaken sex-linkage and equalize the sex-ratio) even when selection is sexually-antagonistic in diploids  (L288-293)
+\item[(2A)] when selection is weak relative to ancestral sex-linkage, cis- or trans-GSD transitions can occur when the new sex-determining allele increases linkage with selected loci (L324-326)
+\item[(2B)] when selection is weak relative to ancestral sex-linkage, haploid selection allows trans-GSD transitions to occur even when the new sex-determining allele decreases linkage with the selected locus (L327-330)
+\item[(3)] when selection is weak relative to ancestral sex-linkage, sex-ratio selection is exactly equal in magnitude to the selection imposed by associations with selected alleles (and thus transitions can increase or decrease the sex-ratio bias) (L350-353)
+\item[(4)] transitions from genetic to environmental sex-determination are not straightforwardly predicted by selection to balance the zygotic sex ratio when haploid selection is present (L411-413)
+%\vspace{0.25cm}\\
+\end{enumerate}
+%As (1A), (1B), and (2) have some antecedents in the literature, we discuss these immediately below each conclusion. 
 %We also discuss, immediately below each conclusion, its novelty.
 %These are all new results, although (1A) was shown for the special case of $r=0$, $R=1/2$, and ploidally-antagonistic selection in Kozielska et al 2010, which we now mention immediately below (1A).
+\textcolor{red}{what is new and what is confirmatory?} 
 }
@@
 \noindent\paragraph{Response}
-\textcolor{blue}{We have replaced ``Thus, if the population sex ratio is biased towards one sex, the average per-individual contribution of genetic material to the next generation from the opposite sex is greater" with ``Thus, if the sex ratio is biased, an individual of the rarer sex will, on average, contribute more genetic material to the next generation".}
+\textcolor{blue}{We have replaced ``Thus, if the population sex ratio is biased towards one sex, the average per-individual contribution of genetic material to the next generation from the opposite sex is greater" with ``Thus, if the sex ratio is biased, an individual of the rarer sex will, on average, contribute more genetic material to the next generation".
+(L26-28)}
 
@@
 \textcolor{blue}{We have rearranged and rewritten the introduction to better motivate our model (see Response 2.1).
-In particular, paragraphs 6 and 7 explain the previous attempts and our approach, respectively.}
+In particular, paragraph 5 presents the role of haploid selection as an evolutionary puzzle and paragraph 6 explains the limitations of previous attempts to solve the puzzle.
+(L49-69)}
 
@@
 \noindent\paragraph{Response}
-\textcolor{blue}{Rewritten as suggested.}
+\textcolor{blue}{This section has been substantially rewritten.
+A roughly corresponding comment now reads: ``...haploid selection is typically sex-specific in that it usually occurs among gametes produced by one sex only." (L51-52)}
 
@@
 \noindent\paragraph{Response}
-\textcolor{blue}{We have rewritten the introduction, as well as our main conclusions (see Responses 2.1 and 2.2).}
+\textcolor{blue}{We have rewritten the Introduction as well as our main conclusions in line with this reviewers major comments (see Responses 2.1 and 2.2).}
 
@@
 And finally, our Mathematica file allows for arbitrary epistatic dominance coefficients.
-We now discuss the empirical evidence for epistatic dominance, our general Mathematica file, and the analysis of van Doorn and Kirkpartick when introducing our model (L117).
+We now discuss the empirical evidence for epistatic dominance, our general Mathematica file, and the analysis of van Doorn and Kirkpartick when introducing our model. (L94-105)
 }
@@
 \noindent\paragraph{Response}
-\textcolor{blue}{We have flipped the statement to talk about male biased sex-ratios instead, and mention that this is possible at equilibrium under the more familiar scenario of meiotic drive in males.}
+\textcolor{blue}{We have flipped the statement to talk about male biased sex-ratios instead, and mention that this is possible at equilibrium in an XY system under the more familiar scenario of meiotic drive in males.
+(L183-187)}
 
@@
 \noindent\paragraph{Response}
-\textcolor{blue}{We have replaced this instance of $\epsilon$ with the more familiar $s<<r$ style assumption.
-When we introduce $\epsilon$ in the weak selection section we now verbally explain that it is just a number that is much less than one.}
+\textcolor{blue}{We have replaced this instance of $\epsilon$ with the more familiar $s<<r$ style assumption (L210).
+When we introduce $\epsilon$ in the weak selection section we now verbally explain that it is just a number that is much less than one (L295-296).}
 
@@
 %\textcolor{red}{The abstract and summary still seem to be a little over-selling...}
-\textcolor{blue}{We have performed an extensive re-arrangement (e.g., Responses 2.1 and 2.2 and below) to improve the clarity of our writing, especially regarding the main results. 
+\textcolor{blue}{
+We have performed an extensive re-arrangement to improve the clarity of our writing, especially regarding the main results. 
+As described in Response 2.1 (point 6) and below, we now provide a prominent and longer discussion of Kozielska et al 2010 and Ubeda et al 2015 (L57-69) and more precisely indicate which of our model features and results are new and unexpected in light of these previous results (see Response 2.2).
+While related, these two studies considered particular cases that we do not consider at length. 
+For example, Ubeda et al consider ESD-GSD transitions. 
+Nevertheless, these transitions involve increased linkage with a haploid selected locus, which is precedent for our Conclusion 2A (which considers only GSD-GSD transitions).
+We now mention this in the Introduction (L59-61) and again in the Discussion (L432).  
+Similarly, Kozielska et al involves a special case of GSD transitions during which sex-linkage goes from perfect to none, which is is an extreme example of our Conclusion 2B.
+This is twice mentioned (L64-67, L237). 
+Despite this precedent, we find the permissive parameter space allowing GSD-GSD transitions surprising. 
+%Especially because their main conclusion involved the strong influence of sex-ratio selection, which is explicitly not a driver during many such transitions. 
+In addition, our Conclusions 3 and 4 reconcile Kozielska et al and Ubeda et al, explaining that sex-ratio selection is not an overwhelming force driving transitions in sex determination. 
 We believe that our new presentation makes the novel and unexpected features of our results much more apparent. 
-In particular, as described at length below, we now give more weight to the two previous papers suggested (Kozielska et al 2010 and Ubeda et al 2015) and more precisely indicate which of our model features and results are new and unexpected in light of these previous results.
-To be clear, we do not claim to be the first to include both haploid and diploid selection to a model investigating the evolution of new sex-chromosomes and we do not consider the addition of sex-specific selection or analytical results for previously numerical models to be our most significant contributions (again, see Responses 2.1 and 2.2 and below for more detail on what these are).
+%To be clear, we do not claim to be the first to include both haploid and diploid selection to a model investigating the evolution of new sex-chromosomes and we do not consider the addition of sex-specific selection or analytical results for previously numerical models to be our most significant contributions (again, see Responses 2.1 and 2.2 and below for more detail on what these are).
 }
@@
 \noindent\paragraph{Response}
-\textcolor{blue}{Here, we were referring to the result that $\lambda_{W'}^{XY} = \lambda_{Y'}^{ZW}$ with haploid selection, even when sex-ratio biases evolve to become either stronger or weaker (e.g., $\lambda_{Y'}^{ZW}$ vs.
+\textcolor{blue}{
+Here we were referring to the result that $\lambda_{W'}^{XY} = \lambda_{Y'}^{ZW}$ with haploid selection, even when sex-ratio biases evolve to become either stronger or weaker (e.g., $\lambda_{Y'}^{ZW}$ vs.
 $\lambda_{W'}^{XY}$ with $R<r$ and male meiotic drive) or when sex-ratio biases are either present or absent (e.g., $\lambda_{W'}^{XY}$ vs.
 $\lambda_{Y'}^{ZW}$ with $r<1/2$, $R=1/2$, and male meiotic drive).
-The Ubeda et al.
-(2015) step 2 result shows that associations with a haploid selected locus can favour a new sex-determining allele despite causing biased sex ratios.
+Step 2 in Ubeda et al 2015 shows that associations with a haploid selected locus can favour a new sex-determining allele despite causing biased sex ratios. 
 Nevertheless, it was difficult for us to intuit whether the presence/absence of ancestral sex-ratio bias would have a negligible or overwhelming effect on the evolution of new sex-determining alleles.
-For example, step 3 of Ubeda et al.
-(2015) involves the spread of a autosomal meiotic drive suppressor favoured by Fisherian sex-ratio selection and Kozielska et al.
-(2010) show that ancestral sex-ratio bias can favour new sex determining systems that balance the sex ratio (now discussed in the Introduction, lines 56-66).
-We found our result, that these forces are exactly equal (with selection weak relative to recombination), such that there is no difference between the propensity for XY-ZW or ZW-XY transitions, to be surprising.
-To clarify our meaning we have rephrased (in Author summary): ``Surprisingly, we find the two forces (sex-ratio selection and associations with genes that have sex-specific effects) will often be equally strong, and thus neither dominates the spread of new sex-determining systems alone."}
+For example, step 3 of Ubeda et al involves the spread of an autosomal meiotic drive suppressor favoured by Fisherian sex-ratio selection and Kozielska et al 2010 show that ancestral sex-ratio bias can favour new sex determining systems that balance the sex ratio.
+These previous results are now discussed in the Introduction (L57-69). 
+We found our result, that these two forces are exactly equal (with selection weak relative to recombination), such that there is no difference between the propensity for XY-ZW or ZW-XY transitions, to be surprising.
+To clarify our meaning we have rephrased (in Author summary): ``Surprisingly, we find the two forces (selection to equalize the sex-ratio and the benefits of hitch-hiking with driven alleles that distort the sex ratio) will often be equally strong, and thus neither is sufficient to explain the spread of new sex-determining systems in every case."
+We believe that the re-framing of the Introduction/Discussion and the emphasis given to specific Conclusions 1-4 will help to clarify this point throughout the paper.
+}
 
@@
 \noindent\paragraph{Response}
-\textcolor{blue}{The Ubeda et al 2015 results do indeed show that differential selection between male and female diploids is not required for new sex-determining alleles to spread; they show that a new genetic sex-determining allele can spread from ancestral ESD when it is linked to a locus that experiences sex-specific meiotic drive.
-In this sentence, we were attempting to stress that new sex determining alleles can spread when they are \textit{less closely linked or completely unlinked} to loci under differential male/female haploid and/or diploid selection.
+\textcolor{blue}{
+The Ubeda et al 2015 results do indeed show that differential selection between male and female diploids is not required for new sex-determining alleles to spread; they show that a new genetic sex-determining allele can spread from ancestral ESD when it is linked to a locus that experiences sex-specific meiotic drive.
+In this sentence, we were attempting to stress that new sex determining alleles can spread when they are \textit{less closely linked or even completely unlinked} to loci under differential male/female haploid and/or diploid selection.
 To our knowledge, this has only been shown for the special case of male meiotic drive in an ancestral XY system with $r=0$ and $R=1/2$ with a neo-W, which is driven by sex-ratio selection (Kozielska et al 2010).
 We therefore found the large parameter space allowing invasion with $r<R$, sometimes in the absence of sex-ratio selection (or even in the absence of haploid selection), to be very unexpected.
+Nevertheless, we have rephrased (in Author Summary): ``We also find that new sex-determining alleles can spread despite being less closely linked to selected loci, driven by initially tight linkage or haploid selection."
+The changes to the presentation of the Introduction and Results should also help to clarify this point further (see Responses 2.1 and 2.2).
+%We discuss the related results of Kozielska and Ubeda on lines 261 and 350.
 }
-\textcolor{blue}{To communicate this we have rephrased: ``Even more unexpectedly, we find that new sex-determining alleles can spread despite being less closely linked to selected loci under a wide range of conditions."
-We believe that the changes to the presentation of the Introduction and Results should also help to clarify this point further (e.g., paragraph, lines 40-47, and more clearly highlighted conclusions on lines XXX; see Responses 2.1 and 2.2).
-}
-\textcolor{blue}{We discuss the related results of Kozielska and Ubeda on lines 261 and 350.}
 
@@
 \textcolor{blue}{
-Charlesworth and Charlesworth 1978 (Am Nat and Heredity) discuss the role of inbreeding (and particularly inbreeding depression) in transitions from hermaphroditism to dioecy. 
-As noted on lines 468-472 (original submission), we have only considered GSD-GSD transitions and GSD-ESD transitions.
-For clarity, we have moved this description into the introduction (lines XXX). 
-In addition, where we draw a parallel between ESD and hermaphroditism on lines 451-455 XXX (revision), we now bring up the limitation that our model of ESD does not include inbreeding. }
-
-\textcolor{blue}{
-The line referred to used sexually-antagonistic selection as an example of ``selective differences between the sexes". 
-We believe the phrase 'selective differences between the sexes' includes sex-differences in drive (Ubeda et al 2015), which just occur during haploid rather than diploid selection (see also Response 3.2.6).
-}
-
-\textcolor{blue}{
-We have rephrased the line referred to here to clarify our focus on GSD: ``Predominant theories accounting for transitions between GSD systems by selection involve sex-ratio selection or selective differences between the sexes (e.g., sexually antagonistic selection)".
+First, we believe sex-differences in selection and sex ratio selection are two ``predominant" theories explaining sex-determination transitions. 
+Second, sexually-antagonistic selection was referred to as an example of ``selective differences between the sexes". 
+We believe the phrase 'selective differences between the sexes' includes sex-differences in drive (Ubeda et al 2015), which just occurs during haploid rather than diploid selection (see also Response 3.2.6).
+Finally, Charlesworth and Charlesworth 1978 (Am Nat and Heredity) discuss the role of inbreeding (and particularly inbreeding depression) in transitions from hermaphroditism to dioecy, without regard for genetic sex-determination.
+As noted on lines 468-472 in the original submission, we have only considered GSD-GSD transitions and GSD-ESD transitions.
+For clarity, we have moved this description into the Introduction (L49-50). 
+In addition, where we draw a parallel between ESD and hermaphroditism (L468-476), we suggest future theory include inbreeding, haploid selection, and sex chromosomes. 
 }
@@
 As we now make clear, we do not look at the same situation as Ubeda et al 2015 and our contribution is not just to add sex-specific viability. 
-In particular, Ubeda starts from ESD. 
+In particular, Ubeda et al start from ESD. 
 Therefore, associations with an ancestral sex-determining locus cannot build up. 
 These lead to some of our most surprising results (e.g., haploid selection favours trans-GSD transitions for a wider variety of genomic locations than diploid selection alone; ESD does not invade despite initial sex-ratio bias).
-}
-\textcolor{blue}{
-%It is true that Ubeda et al 2015 is a special case of our model. 
-%However, Ubeda et al 2015 was primarily a numerical investigation, providing a less general treatment of this special case and developing less intuition.
-Further, our model and intuition-giving analytical solutions explore a much wider range of scenarios than the numerical results of Ubeda, allowing, for example, sex-specific selection (e.g., sex-antagonism) and various genomic arrangements (any order/linkage of the three loci).
-Our model is thus much more general and clarifies just when one should expect to see the numerical results of Ubeda et al 2015.
-We have rephrased to make this clear (after discussing Ubeda et al 2015, see Response 2.1): ``Here, we analytically find the conditions under which new GSD or ESD systems spread with generic linkage between the loci involved (and generic sex-specific haploid and diploid selection)." (L67-69).
+Further, our model and intuition-giving analytical solutions explore a much wider range of scenarios than the numerical results of Ubeda et al, allowing, for example, sex-specific selection (e.g., sex-antagonism) and various genomic arrangements (any order/linkage of the three loci).
+Our model is thus much more general and clarifies just when one should expect to see the numerical results of Ubeda et al.
+We have rephrased to make this clear (after discussing Ubeda et al 2015 in the Introduction, see Response 2.1; L70-74): ``Here, we analytically find the conditions under which new GSD or ESD systems spread in ancestral GSD systems with generic linkage between the loci involved and generic sex-specific haploid and diploid selection.
+Doing so, we reconcile the results of Kozielska et al.\ (2010) and Ubeda et al.\ (2015) by showing when new GSD systems that increase \textit{or} decrease linkage with loci under haploid selection spread."
 }
@@
 \textcolor{blue}{
-We have attempted to clarify by expanding our explanation of the mating system and the way we model haploid selection (see Response 3.2).}
+We have attempted to clarify by expanding our explanation of the mating system and the way we model haploid selection (see Response 3.2 below).}
 
@@
 If drive was the same in both sexes, $\alpha^{m}=\alpha^{f}$ (and all other male/female selection terms also equal), we show that the new sex-determining allele would not invade (e.g., equation 2 and 3).
-In this sense haploid selection is similar to sex-specific diploid selection, and together haploid and diploid selection determine the differences in male vs.
-female fitness, which can drive sex-determination transitions (see Response 3.2.4).
-This sentence meant to introduce the 'sex-specific' aspect of haploid selection in the way Ubeda et al (2015) considers it; i.e., associations with alleles favoured in one sex (or the gametes produced by that sex) should favour a new sex-determining allele.
-We have rephrased to make this clear: ``Therefore, one might expect new sex-determining systems to benefit from close linkage with haploid selected loci, as found for sex-differences in diploid selection" (L51-53).
-We now follow this sentence up with a paragraph that clarifies its meaning by comparing with the results of Kozielska et al (2010) and Ubeda et al (2015).}
+In this sense haploid selection is similar to sex-specific diploid selection, and together haploid and diploid selection determine the differences in male vs.\ female fitness, which can drive sex-determination transitions (see Response 3.2.4).
+This sentence meant to introduce the `sex-specific' aspect of haploid selection in the way Ubeda et al 2015 considers it; associations with alleles favoured in one sex (or the gametes produced by that sex) should favour a new sex-determining allele.
+We have rephrased to make this clear (L52-54): ``Therefore, one might expect new sex-determining systems to benefit from close linkage with haploid selected loci, as found for sex-differences in diploid selection."
+We now follow this sentence up with a paragraph that clarifies its meaning by comparing with the results of Kozielska et al 2010 and Ubeda et al 2015 (see Response 2.1).}
 
@@
 Further, the restricted scope of that numerical study prevents us from generalizing beyond its special case (see Response 3.1.4).
-Lines 48-66 present a refurbished argument for why it is difficult to intuit the implications of haploid selection, while summarizing the results of Ubeda and Kozielska.
+We now present a refurbished argument for why it is difficult to intuit the implications of haploid selection while summarizing the results of Ubeda et al and Kozielska et al 2010 in the Introduction (see Response 2.1).
 }
@@
 \textcolor{blue}{Ubeda et al 2015 was already cited on line 396 of the original submission, where we mentioned that it showed that sex-ratio biases could become more severe during a transition.
-Nevertheless, we now discuss Ubeda et al 2015 in the introduction, results, and discussion (see Responses above).}
+Nevertheless, we now discuss Ubeda et al 2015 in the Introduction, Results, and Discussion (see Responses above).}
 
@@
 \textcolor{blue}{We do not agree. 
-Given our definition of meiotic drive and gametic competition in the Introduction, the two processes are different.
+Given our definition of meiotic drive and gametic competition (L106-116), the two processes are different.
 In particular, meiotic drive is assumed to occur during meiosis, and thus is ``gametic competition" amongst the gametes produced by a single individual. 
@@
 Thus allele frequency changes can occur by gametic competition even if all individuals were homozygous (as long as there is a polymorphism).
-We have rephrased our definitions in the Introduction to read: ``We use the term `meiotic drive' to refer to the biased (non-Mendelian) segregation of genotypes during gamete production (from one parent only) and the term `gametic competition' to refer to selection upon haploid genotypes within a gamete/gametophyte pool (from many parents)."
+We highlight these differences in the model section (L106-116).
 }

### 2018-05-01 LaTeX/main_revised.tex
matt o went over all revision main text

@@
 \usepackage{lastpage,fancyhdr,graphicx}
-\usepackage{epstopdf}
+\usepackage[outdir=./]{epstopdf}
 \pagestyle{myheadings}
@@
 (1) We consider the dynamics of loci very tightly linked to the ancestral sex-determining loci, e.g., within the non-recombining region of the ancestral sex chromosomes. 
-Variation at such loci can favour the spread of new sex-determining systems in which the heterogametic sex changes (XY to ZW or ZW to XY) and the new sex-determining region is less closely linked (or even unlinked) to the locus under selection, which is not expected from previous theory.
+Variation at such loci can favour the spread of new sex-determining systems in which the heterogametic sex changes (XY to ZW or ZW to XY) and the new sex-determining region is less closely linked (or even unlinked) to the locus under selection.
+%, which is \textcolor{red}{not expected from previous theory}.
 (2) We consider selection upon haploid genotypes either during gametic competition (e.g., pollen competition) or meiosis (i.e., non-Mendelian segregation), which can cause the zygotic sex ratio to become biased.
@@
 Prevailing views suggest that new sex-determining systems are favoured when they equalize the sex ratio and/or when they are more closely linked to genes that experience differential selection in males and females.
-Our models include selection upon haploid genotypes (meiotic drive or gametic competition), which causes sex-ratio biases and occurs differently in male and female gametes. 
+Our models include selection upon haploid genotypes (meiotic drive or gametic competition), which biases the sex-ratio and occurs differently in male and female gametes. 
 Surprisingly, we find the two forces (selection to equalize the sex ratio and the benefits of hitchhiking with driven alleles that distort the sex ratio) will often be equally strong, and thus neither is sufficient to explain the spread of new sex-determining systems in every case.
-Even more unexpectedly, we find that new sex-determining alleles can spread despite being less closely linked to selected loci. 
-Therefore, our models predict loci in previously unexpected genomic locations and/or experiencing various types of selection (including haploid selection) can now be implicated as drivers of transitions between sex-determining systems.
+We also find that new sex-determining alleles can spread despite being less closely linked to selected loci, driven by initially tight linkage or haploid selection. 
+Our models therefore predict that loci in previously unexpected genomic locations and/or experiencing various types of selection (including haploid selection) can now be implicated as drivers of transitions between sex-determining systems.
 
@@
 Counterintuitively, when linkage is tight between the sex-determining locus and a selected locus, an allele good for females can be at higher frequency on the ancestral-Y than on the ancestral-X under a variety of forms of selection.
-This, in turn, can favour a new ZW sex-determining locus that has weaker linkage with loci under selection (a similar argument applies to ZW$\rightarrow$XY transitions), which was not considered in previous theory \cite{vanDoorn:2010hu}.
+This, in turn, can favour a new ZW sex-determining locus that has weaker linkage with loci under selection (a similar argument applies to ZW$\rightarrow$XY transitions), which was not \textcolor{red}{apparent/discovered/considered} in previous theory \cite{vanDoorn:2010hu}.
 That is, we show that selected loci in very tight linkage with the ancestral GSD locus can favour trans-GSD transitions during which linkage associations are actually weakened.
@@
 %Haploid selection model feature and discussion of why needed
-Most significantly, we include haploid selection (gametic competition or meiotic drive) in models describing cis-GSD, trans-GSD, and GSD to ESD transitions, which poses an apparent evolutionary problem.
+Most significantly, we include haploid selection (gametic competition or meiotic drive) in models describing cis-GSD, trans-GSD, and GSD to ESD transitions.
+This poses an apparent evolutionary problem. 
 On one hand, haploid selection is typically sex-specific in that it usually occurs among gametes produced by one sex only~\cite{Mulcahy:1996ha,JOSEPH:2004haa,Ubeda:2005gw,Lindholm:2016cw}. 
@@
 Two previous studies have considered the spread of GSD with sex-specific meiotic drive~\cite{Kozielska:2010vm,Ubeda:2015fx} under a limited number of possible genetic architectures and diploid selective regimes.
-Ubeda et al. (2015)~\cite{Ubeda:2015fx} considers ancestral-ESD (with no sex-ratio bias) and numerically show that new GSD alleles can spread if they arise in linkage with meiotic drive loci. 
-For example, a masculinizing allele spreads in association with an allele that is favoured during male meiosis, causing sex ratios to become male-biased and thereby suggesting that such beneficial associations overwhelm selection to balance the sex ratio.
-However, Kozielska et al. (2010)~\cite{Kozielska:2010vm} consider meiotic drive on an ancestral GSD sex chromosome (creating a sex ratio bias). 
-They find that new, completely unlinked, GSD systems can spread if they generate the rarer sex, creating a balanced sex ratio. 
-That is, they conclude that Fisherian sex-ratio selection caused by haploid selection favours new GSD systems.
+Ubeda et al. (2015)~\cite{Ubeda:2015fx} considered ancestral-ESD (with no sex-ratio bias) and numerically showed that new GSD alleles can spread if they arise in linkage with meiotic drive loci. 
+For example, a masculinizing allele spreads in association with an allele that is favoured during male meiosis, causing sex ratios to become male-biased.
+This suggests that the benefits of associating with driving alleles overwhelms selection to balance the sex ratio and that haploid selection should cause increased sex-linkage.
+%, at least when new sex-determining alleles are rare.
+However, Kozielska et al. (2010)~\cite{Kozielska:2010vm} considered an ancestral GSD system that is perfectly linked to a meiotic driver (creating a sex ratio bias). 
+They found that new, completely unlinked, GSD systems can spread if they generate the rarer sex, creating a balanced sex ratio. 
+This suggests that Fisherian sex-ratio selection overwhelms the benefits of being associated with driving alleles and that haploid selection should cause decreased sex-linkage.
 
 %main results
-Here, we analytically find the conditions under which new GSD or ESD systems spread with generic linkage between the loci involved (and generic sex-specific haploid and diploid selection). 
-Strikingly, we reconcile the results of Kozielska et al.
+Here, we analytically find the conditions under which new GSD or ESD systems spread in ancestral GSD systems with generic linkage between the loci involved and generic sex-specific haploid and diploid selection.
+Doing so, we reconcile the results of Kozielska et al.
 (2010)~\cite{Kozielska:2010vm} and Ubeda et al.
-(2015)~\cite{Ubeda:2015fx} by showing when new GSD systems that increase \textit{or} decrease linkage with loci spread.
+(2015)~\cite{Ubeda:2015fx} by showing when new GSD systems that increase \textit{or} decrease linkage with loci under haploid selection spread.
 %that experience haploid selection.
 This result is qualitatively distinct from those for diploid selection alone~\cite{vanDoorn:2007eu,vanDoorn:2010hu} and suggests that haploid selection is more likely to promote transitions between sex-determination systems.
-We also show that transitions involving haploid selection cannot be simply explained by invoking sex-ratio selection. 
-In particular, under a wide range of conditions, we show that transitions in sex-determining system are favoured \textit{equally strongly} in situations where sex-ratio biases increase or decrease (and in situations where sex-ratio biases are ancestrally present or absent).
-Finally, we show that ESD may not evolve, even if the sex ratio is initially biased by haploid selection, which would not be predicted by previous theories for transitions to ESD~\cite{Charnov:1982wg,Bull:1983vi,West:2009we}.
-Together, our results suggest that selection to equalize the sex ratio is not an overwhelming force driving transitions between sex-determining systems.
+This also implies that transitions involving haploid selection cannot be simply explained by invoking sex-ratio selection. 
+In particular, we show that under a wide range of conditions, transitions to sex-determining systems that increase or decrease the sex-ratio bias are favoured \textit{equally strongly}.
+%(and in situations where sex-ratio biases are ancestrally present or absent).
+Finally, we show that ESD may not evolve, even if the sex ratio is initially biased by haploid selection, which is not predicted by previous theories for transitions to ESD~\cite{Charnov:1982wg,Bull:1983vi,West:2009we}.
+%Together, our results suggest that neither selection to equalize the sex ratio nor the benefits of associating with haploid selected alleles is an overwhelming force driving transitions between sex-determining systems.
+Together, our results suggest that both selection to equalize the sex ratio and the benefits of associating with haploid selected alleles can drive transitions between sex-determining systems, leading to tighter or weaker sex-linkage.
 
@@
 We consider two forms of selection upon haploid genotypes, `gametic competition' and `meiotic drive'. 
-During gametic competition, we assume that a representative sample of all gametes/gametophytes (hereafter gametes) compete for fertilization, which implies a polygamous mating system. 
-Relative fitnesses during gametic competition are given by $w_A^\circ$ and $w_a^\circ$ ($\circ \in \{\female,\male\}$; see table \ref{tab:fitnesstable}).
+During gametic competition, we assume that a representative sample of all gametes/gametophytes (hereafter gametes) compete with others of the same sex for fertilization, which implies a polygamous mating system.
+Relative fitnesses in sex $\circ \in \{\female,\male\}$ during gametic competition are given by $w_A^\circ$ and $w_a^\circ$ (see table \ref{tab:fitnesstable}).
 On the other hand, meiotic drive in our model only affects the segregation of gametes produced by heterozgotes.
@@
 
+In the ancestral population, it is convenient to follow the frequency of the $A$ allele among female gametes (eggs), $p^\female_X$, and among X-bearing, $p^\male_X$, and among Y-bearing, $p^\male_Y$, male gametes (sperm/pollen).
+We also track the fraction of male gametes that are Y-bearing, $q$, which may deviate from $1/2$ due to meiotic drive in males. 
+We consider only equilibrium frequencies of alleles, $\hat{p}^\circ_i$, and Y-bearing male gametes, $\hat{q}$, when determining the invasion of new sex-determining factors.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-We begin by describing the precise conditions under which new sex determining alleles can spread within a population.  
-These general conditions then allow us to consider several special cases of interest in subsequent sections.
-
-The evolution of a new sex-determining system requires that a rare mutant allele, $m$, at the novel sex-determining locus, $\mathbf{M}$, increases in frequency when rare. 
-This is determined by the leading eigenvalue ($\lambda_m^{(XY)}$) of the system of eight equations describing the frequency of eggs and sperm carrying the $m$ allele in the next generation (equations \ref{eq:recursions}).
+We begin by describing the conditions under which new sex determining alleles can spread within a population, without explicitly specifying ancestral allele frequencies.
+These general conditions then allow us to consider several special cases of interest in subsequent sections, where equilibrium ancestral allele frequencies are explicitly calculated.
+
+The evolution of a new sex-determining system depends on the growth rate of a rare mutant allele, $m$, at the novel sex-determining locus, $\mathbf{M}$. %, increases in frequency when rare. 
+This growth rate is determined by the leading eigenvalue ($\lambda_m^{(XY)}$) of the system of eight equations describing the frequency of eggs and sperm carrying the $m$ allele in the next generation (equations \ref{eq:recursions}).
 %, evaluated at the above equilibrium.
@@
 This system simplifies substantially for an epistatically dominant neo-Y ($k=0$) or neo-W ($k=1$), see \nameref{app:inv_cond}. 
-The leading eigenvalue for a rare neo-Y or neo-W allele, $m\in\{Y',W'\}$, is the largest value of $x$ that solves $x^2+ b x + c = 0$.  %$(\lambda_m^{(i)})^2+ b \lambda_m^{(i)} + c =0$. 
-The coefficients are $b= - (\Lambda_{mA}^{(XY)} + \Lambda_{ma}^{(XY)})+(\chi_{mA}^{(XY)} + \chi_{ma}^{(XY)})$ and $c = (\Lambda_{mA}^{(XY)} - \chi_{mA}^{(XY)}) (\Lambda_{ma}^{(XY)} - \chi_{ma}^{(XY)}) - \chi_{mA}^{(XY)} \chi_{ma}^{(XY)}$, where $\Lambda_{mi}^{(XY)}>0$ is the multiplicative growth rate (which we will call the ``haplotypic growth rate'') of the neo-sex determination allele $m$ on background $i\in\{A,a\}$ without accounting for loss due to recombination ($R=0$), and $\chi_{mi}^{(XY)}>0$ is the rate at which mutant haplotypes on background $i\in\{A,a\}$ recombine onto the other $\mathbf{A}$ locus background in heterozygotes (proportional to $R$; we call this the ``dissociative force" as it breaks down linkage disequilibrium), see Table \ref{tab:haplotype_growth}.
-In the ancestral population, it is convenient to follow the frequency of the $A$ allele among female gametes (eggs), $p^\female_X$, and among X-bearing, $p^\male_X$, and among Y-bearing, $p^\male_Y$, male gametes (sperm/pollen).
-We also track the fraction of male gametes that are Y-bearing, $q$, which may deviate from $1/2$ due to meiotic drive in males. 
-We will consider only equilibrium frequencies of alleles, $\hat{p}^\circ_i$, and Y-bearing male gametes, $\hat{q}$, when calculating the eigenvalues.
+The leading eigenvalue for a rare neo-Y or neo-W allele, $m\in\{Y',W'\}$, is the largest value of $x$ that solves $x^2+ b x + c = 0$, where $b= - (\Lambda_{mA}^{(XY)} + \Lambda_{ma}^{(XY)})+(\chi_{mA}^{(XY)} + \chi_{ma}^{(XY)})$ and $c = (\Lambda_{mA}^{(XY)} - \chi_{mA}^{(XY)}) (\Lambda_{ma}^{(XY)} - \chi_{ma}^{(XY)}) - \chi_{mA}^{(XY)} \chi_{ma}^{(XY)}$.
+The variable $\Lambda_{mi}^{(XY)}>0$ is the multiplicative growth rate of the neo-sex-determining allele $m$ on background $i\in\{A,a\}$ without accounting for loss due to recombination ($R=0$).
+We will call  $\Lambda_{mi}^{(XY)}$ the ``haplotypic growth rate''.
+The variable $\chi_{mi}^{(XY)}>0$ is the rate at which mutant haplotypes on background $i\in\{A,a\}$ recombine onto the other $\mathbf{A}$ locus background in heterozygotes (proportional to $R$).
+We call $\chi_{mi}^{(XY)}$ the ``dissociative force", as it breaks down linkage disequilibrium.
+Both variables are listed in Table \ref{tab:haplotype_growth} for neo-Y and neo-W mutants.
 
@@
 %Since $f(\Lambda_{mA}^{(i)})$ and $f(\Lambda_{ma}^{(i)})$ are of opposite signs, the leading eigenvalue must fall between these two quantities and is the larger of them when $R = 0$ (see \nameref{file:Mathematica}).
-If both haplotypic growth rates are greater than one ($\Lambda_{mA}^{(XY)}, \Lambda_{ma}^{(XY)}>1$), then the new sex-determining allele invades regardless of the rate of recombination between the new sex-determining locus and the selected locus ($R$), see \nameref{app:inv_cond} for details.
-Conversely, if both haplotypic growth rates are less than one ($\Lambda_{mA}^{(XY)}, \Lambda_{ma}^{(XY)}<1$), then invasion can never occur.  
+If both haplotypic growth rates are greater than one ($\Lambda_{mA}^{(XY)}, \Lambda_{ma}^{(XY)}>1$) then the new sex-determining allele invades regardless of the rate of recombination between the new sex-determining locus and the selected locus ($R$; see \nameref{app:inv_cond} for details).
+Conversely, if both haplotypic growth rates are less than one ($\Lambda_{mA}^{(XY)}, \Lambda_{ma}^{(XY)}<1$) then invasion can never occur.  
 Finally, if only one haplotypic growth rate is greater than one, the new sex-determining allele can always invade when arising at a locus that is tightly linked to the selected locus ($R\approx0$).  
@@
 cis- and trans-GSD transitions are qualitatively different.
-This is because, in an ancestrally XY system, a gamete with the neo-Y always pairs with a female gamete containing an X, Fig \ref{fig:model_outline}C.
-By contrast, a gamete with a neo-W can pair with an X- or Y-bearing male gamete, Fig \ref{fig:model_outline}D.
+This is because, in an ancestrally XY system, a gamete with the neo-Y always pairs with a female gamete containing an X (Fig \ref{fig:model_outline}C).
+By contrast, a gamete with a neo-W can pair with an X- or Y-bearing male gamete (Fig \ref{fig:model_outline}D).
 Consequently, neo-W-bearing females obtain a different frequency of $A$ alleles from mating (when $\hat{p}_X^\male \neq \hat{p}_Y^\male$) compared to ancestral ($MM$) females, which can inhibit or favour its spread.
 
-In order to explicitly determine the conditions under which a new sex-determining allele spreads, we must calculate the equilibrium frequency of the $A$ allele (i.e., $\hat{p}^\female_X$, $\hat{p}^\male_X$, and $\hat{p}^\male_Y$) and Y-bearing male gametes ($\hat{q}$) in the ancestral population.
+In order to explicitly determine the conditions under which a new sex-determining allele spreads, we next calculate the equilibrium frequency of the $A$ allele (i.e., $\hat{p}^\female_X$, $\hat{p}^\male_X$, and $\hat{p}^\male_Y$) and Y-bearing male gametes ($\hat{q}$) in the ancestral population.
 Because only the $\mathbf{A}$ locus experiences selection directly, any deterministic evolution requires that there be a polymorphism at the $\mathbf{A}$ locus. 
@@
 Such polymorphisms can be maintained by heterozygote advantage, sexually-antagonistic selection, ploidally-antagonistic selection, or a combination~\cite{Immler:2012tl}.
-We can analytically calculate the allele frequency of the $A$ allele using two alternative simplifying assumptions: 
+We analytically calculate equilibrium frequencies using two alternative simplifying assumptions: 
 (1) the $\mathbf{A}$ locus is tightly linked to the non-recombining region around the ancestral sex-determining locus ($r \approx 0$) or (2) selection is weak relative to recombination ($s^\circ$, $t^\circ$, $\alpha_{\Delta}^\circ$ $<<$ $r$).
+The ancestral equilibria and their stability conditions are given in \nameref{app:eq_stab}.
 
@@
 
-The ancestral equilibrium allele frequencies and their stability conditions are given in \nameref{app:eq_stab}. 
 When there is complete linkage between the ancestral sex-determining locus and the $\mathbf{A}$ locus ($r=0$), either the $A$ allele or the $a$ allele must be fixed in gametes containing a Y allele. 
@@
 
-We find that a neo-Y allele can never invade an ancestral XY system that already has tight linkage with the locus under selection ($\lambda_{Y'}^{(XY)} \leq 1$ when $r=0$, for details see \nameref{file:Mathematica}).
+We find that a neo-Y allele can never invade an ancestral XY system that already has tight linkage with the locus under selection ($\lambda_{Y'}^{(XY)} \leq 1$ when $r=0$; for details see \nameref{file:Mathematica}).
 %When $R=0$, a neo-Y haplotype with the same allele as the ancestral Y is neutral ($\Lambda_{Y'a}^{(XY)}=1$) and does not change in frequency.
@@
 
-Neo-W alleles, on the other hand, can invade an ancestral XY system because, under some conditions the W can become more strongly specialized for females (the full invasion conditions are given in \nameref{app:inv_cond}; equations \ref{Binvasion} and \ref{Ainvasion}).
+Neo-W alleles, on the other hand, can invade an ancestral XY system because, under some conditions, the neo-W can become more strongly specialized for females (the full invasion conditions are given in \nameref{app:inv_cond}; equations \ref{Binvasion} and \ref{Ainvasion}).
 Thus,
@@
 %\textbf{selection on loci within the non-recombining region around the sex-determining locus ($r\approx0$) allows the invasion of less closely linked sex-determining alleles ($r<R\leq1/2$) during a trans-GSD transition} (XY $\leftrightarrow$ ZW).
-\textbf{Selection on loci in or near the non-recombining region around the sex-determining locus ($r\approx0$) prevents cis-GSD transitions (XY $\leftrightarrow$ XY, ZW $\leftrightarrow$ ZW) but can spur trans-GSD transitions (XY $\leftrightarrow$ ZW).}
+\textbf{Selection on loci in or near the non-recombining region around the sex-determining locus ($r\approx0$) prevents cis-GSD transitions (XY $\leftrightarrow$ XY, ZW $\leftrightarrow$ ZW) but can spur trans-GSD transitions (XY $\leftrightarrow$ ZW), which weaken sex-linkage.}
 \vspace{0.5cm}
@@
 The conditions become more restrictive, however, with increasing recombination ($R$) between the new sex-determining locus and the selected locus.  
-The invasion of completely unlinked neo-W alleles ($R = 1/2$) can occur with overdominance in males or with haploid selection (e.g., a case with male drive opposed by diploid selection in \cite{Kozielska:2010vm}) but is not possible with only sexually-antagonistic selection where selection is directional in each diploid sex (see \nameref{file:Mathematica}).
-Here, we focus on cases where there is no haploid selection (Fig \ref{fig:SexAntagTighter}A) and discuss the additional effect of haploid selection in \nameref{app:inv_cond}. 
+The invasion of completely unlinked neo-W alleles ($R = 1/2$) can occur with overdominance in males or with haploid selection (e.g., when male drive is opposed by diploid selection, as in \cite{Kozielska:2010vm}) but is not possible with only sexually-antagonistic selection where selection is directional in each diploid sex (see \nameref{file:Mathematica}).
+Here, we focus on cases where there is no haploid selection (Fig \ref{fig:SexAntagTighter}A) and discuss the additional effect of haploid selection in \nameref{app:inv_cond} (see also Conclusion 1C). 
 %Essentially, neo-W alleles are able to invade (even with $R>r$) because the ancestral X experiences selection in males. 
@@
 Wherever both haplotypic growth rates are greater than one, invasion by a neo-W is expected regardless of its linkage with the selected locus (i.e., for any $R$, see \nameref{fig:positionOverdominance} and \nameref{fig:temporalOverdominance} for examples).
-As a consequence, evolution can favor a new sex determination system on a different chromosome, despite the fact that this unlinks the sex determination locus from the selected locus.
+As a consequence, evolution can favor a new sex determination system on a different chromosome, despite the fact that this unlinks the sex-determining locus from the selected locus.
 
@@
 \noindent\textit{Conclusion 1B:}
-\textbf{With tight linkage between a selected locus and the ancestral sex determination system ($r\approx0$), selection to better specialize on the ancestrally-non-heterogametic sex can drive trans-GSD transitions (XY $\leftrightarrow$ ZW) that weaken sex-linkage ($r<R\leq1/2$; potentially even shifting sex determination to a different chromosome) and/or lead to polymorphic sex-determination systems.}
+\textbf{With tight linkage between a selected locus and the ancestral sex-determining locus ($r\approx0$), selection to better specialize on the ancestrally-non-heterogametic sex can drive trans-GSD transitions (XY $\leftrightarrow$ ZW) that weaken sex-linkage ($r<R\leq1/2$; potentially even shifting sex determination to a different chromosome) and sometimes lead to polymorphic sex-determination systems.}
 \vspace{0.5cm}
@@
 \textbf{
-Haploid selection allows trans-GSD transitions that weaken sex-linkage ($r<R\leq1/2$; potentially even shifting sex determination to a different chromosome) even when selection is sexually-antagonistic with directional selection in each diploid sex.
-With initially tight linkage, these transitions equalize the sex ratio by reducing linkage to alleles under haploid selection.
+With tight linkage between a selected locus and the ancestral sex-determining locus ($r\approx0$), haploid selection allows trans-GSD transitions (XY $\leftrightarrow$ ZW) that weaken sex-linkage ($r<R\leq1/2$; potentially even shifting sex determination to a different chromosome) even when selection is sexually-antagonistic with directional selection in each diploid sex.
+These trans-GSD transitions equalize the sex ratio.
 }
@@
 
-Without haploid selection ($t^\circ=\alpha^\circ_{\Delta}=0$), the spread of a neo-W is equivalent to the spread of a neo-Y ($\lambda_{W'}^{(XY)}=\lambda_{Y'}^{(XY)}$), when selection is weak relative to recombination, such that trans-GSD transitions can also occur only if the new sex-determining locus is more closely linked to a locus under selection ($R<r$), as found by \cite{vanDoorn:2010hu}.
+When selection is weak relative to recombination, the absence of haploid selection ($t^\circ=\alpha^\circ_{\Delta}=0$), implies that the spread of a neo-W is equivalent to the spread of a neo-Y ($\lambda_{W'}^{(XY)}=\lambda_{Y'}^{(XY)}$), such that trans-GSD transitions can also occur only if the new sex-determining locus is more closely linked to a locus under selection ($R<r$), as found by \cite{vanDoorn:2010hu}.
 When there is haploid selection, invasion also typically occurs when the neo-W is more closely linked to the selected locus than the ancestral sex-determining region (Fig \ref{fig:Combination_Centimorgans}).
@@
 \noindent\textit{Conclusion 2A:}\
-\textbf{New sex-determining alleles (causing cis- \textit{or} trans-GSD transitions) can spread if they arise in closer linkage with a locus that experiences selection than the ancestral-sex-determining locus ($R<r$).}
+\textbf{New sex-determining alleles (causing cis- \textit{or} trans-GSD transitions) can spread if they arise morely closely linked with a locus that experiences selection than the ancestral-sex-determining locus is ($R<r$).}
 \vspace{0.5cm}
@@
 \noindent\textit{Conclusion 2B:}\
-\textbf{New sex-determining alleles (causing trans-GSD transitions) can spread if they arise in looser linkage with a locus that experiences selection than the ancestral-sex-determining locus ($r<R$), requiring haploid selection and some initial sex-linkage ($r<1/2$) as necessary conditions.}
+\textbf{New sex-determining alleles (causing trans-GSD transitions, XY $\leftrightarrow$ ZW) can spread even if they arise less closely linked with a locus that experiences selection than the ancestral-sex-determining locus is ($r<R$), requiring haploid selection and some initial sex-linkage ($r<1/2$) as necessary conditions.}
 \vspace{0.5cm}
@@
 %Indeed, invasion typically occurs when the neo-W is more closely linked to the selected locus than the ancestral sex-determining region (Fig \ref{fig:Combination_Centimorgans}).
-To clarify the parameter space under which invasion occurs despite looser sex-linkage ($\lambda_{W'}^{(XY)}>1$ despite $R>r$; Conclusion 2B), we focus on the special case where $R=1/2$ and $r<1/2$ (e.g., the selected locus is on the ancestral sex chromosome and the novel sex-determining locus arises on an autosome).
-In Table \ref{tab:specialcases} we give the conditions where invasion occurs when we further assume that haploid selection only occurs in one sex \textcolor{red}{(e.g., during male meiosis only)} and dominance coefficients are equal in the two sexes, $h^\female=h^\male$.
-These special cases indicate that neo-W invasion occurs for a large fraction of the parameter space, even if the neo-W uncouples the sex-determining locus from a locus under selection. 
-Surprisingly, neo-W alleles can spread when they are more closely \textit{or} more loosely linked to a locus that experiences haploid selection, as shown in Fig \ref{fig:Combination_Centimorgans} (c.f., Fig \ref{fig:SexAntagTighter}A for diploid sexually-antagonistic selection alone).
-In Fig \ref{fig:SexRatioBad}, we also show examples of trans-GSD transitions in sex determination during which linkage with a haploid selected locus increases \textit{or} decreases, increasing or decreasing sex-ratio bias.
-When sex-linkage decreases ($R>r$), neo-W alleles can benefit from Y-associated alleles that have higher fitness in the female diploid phase but then dissociate from these alleles through recombination before any subsequent haploid selection.
+To clarify the parameter space under which invasion occurs with weak selection ($\lambda_{W'}^{(XY)}>1$), we focus on cases where dominance coefficients are equal in the two sexes, $h^\female=h^\male$, and haploid selection only occurs in one sex (e.g., during male meiosis only).
+Table \ref{tab:specialcases} then gives the conditions required for unlinked ($R=1/2$) neo-W invasion when there is some ancestral sex-linkage ($r<1/2$; e.g., the selected locus is on the ancestral sex chromosome and the novel sex-determining locus arises on an autosome).
+These special cases indicate that neo-W invasion occurs for a large fraction of the parameter space, even though the neo-W uncouples the sex-determining locus from a locus under selection. 
+Fig \ref{fig:Combination_Centimorgans} then demonstrates that under these conditions neo-W alleles can spread when they are more loosely \textit{or} more closely linked to the locus that experiences haploid selection (c.f., Fig \ref{fig:SexAntagTighter}A for diploid sexually-antagonistic selection alone).
+%When the neo-W is more closely linked to the haploid selected locus its invasion increases (or creates anew) sex-ratio bias (Fig \ref{fig:SexRatioBad}A).
+%Under the same selection scenario (drive in males), a neo-Y would invade an ancestrally ZW system
+% shows that when a neo-W invades that increases linkage with a haploid selected locus, it biases the sex-ratio.
+%, while those that decrease sex-linkage equalize the sex-ratio. 
+%When sex-linkage decreases ($R>r$), neo-W alleles can benefit from Y-associated alleles that have higher fitness in the female diploid phase but then dissociate from these alleles through recombination before any subsequent haploid selection.
 
@@
 
+%Previous research has shown that when the ancestral sex-determining locus is linked to a locus that experiences haploid selection (e.g., meiotic drive), alleles at a new, unlinked sex-determining locus can invade and restore equal sex ratios~\cite{Kozielska:2010vm}.
+We can also compare transitions in genetic sex-determination where sex-ratio bias increases, decreases, or remains equal. 
+For example, if there is meiotic drive in males only ($\alpha^\male_\Delta \neq 0$, $\alpha^\female_\Delta=0$), without gametic competition ($t^\female=t^\male=0$) the zygotic sex ratio is initially biased only when the ancestral sex-determining system is XY (Fig \ref{fig:model_outline}A and Fig \ref{fig:SexRatioBad}A) and not ZW (Fig \ref{fig:SexRatioBad}B).
+%If the ancxestral sex-determining system is ZW, the zygotic sex ratio will be 1:1 because diploid sex is determined by the proportion of Z-bearing versus W-bearing eggs and meiosis in females is fair (Fig \ref{fig:Combination_Turnover}D).
+If Fisherian sex-ratio selection were dominant, we would thus expect a difference in the potential for XY to ZW and ZW to XY transitions. 
+%However, to leading order with selection weak relative to recombination, we find that sex-ratio selection favours the spread of a neo-W by an amount equl to the spread of a neo-Y into a ZW system (relabeling XY as the heterogametic sex and reversing the labels of males and females in Table \ref{tab:specialcases})
+However, invasion by a neo-W allele into an XY system and invasion by a neo-Y allele into a ZW system occur under the same conditions ($\lambda_{Y'}^{(XY)} = \lambda_{W'}^{(ZW)}$ and $\lambda_{W'}^{(XY)}=\lambda_{Y'}^{(ZW)}$, at least to order $\epsilon^2$), implying that,% surprisingly,
+\vspace{0.5cm}
+
+\noindent\textit{Conclusion 3:}
+\textbf{When selection is weak relative to recombination, the presence of haploid selection equally favors the spread of new sex determination systems that reduce sex-ratio bias (benefiting from Fisherian sex ratio selection) or generate a sex-ratio bias (benefiting from associations with selected alleles).
+}
+\vspace{0.5cm}
+%\noindent\textcolor{red}{\textit{Conclusion 3:}
+%\textbf{when selection is weak relative to recombination, sex-ratio selection is exactly equal in magnitude to the selection imposed by associations with selected alleles. } }
+%%\textcolor{red}{[new result]}
+%\vspace{0.5cm}
+
+\noindent For example, in Fig \ref{fig:SexRatioBad}A neo-W alleles invade an ancestral-XY system where females are initially rare, equalizing the sex ratio (as occurs in \cite{Kozielska:2010vm}).
+However, Fig \ref{fig:SexRatioBad}B shows that a neo-Y can invade the resulting ZW system under the same conditions. 
+When $R<1/2$, the invading neo-Y becomes associated with the male meiotic drive allele and the zygotic sex ratio actually evolves to become male-biased (as occurs in \cite{Ubeda:2015fx}, beginning from ESD).
+In this case, the neo-Y spreads because it is often found in males and can, if it carries the driven allele $a$, benefit from haploid selection in males (Fig \ref{fig:SexRatioBad}B).
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \centering
-\includegraphics[width=\linewidth]{../Plots/Temporal_SR}
+\includegraphics[width=\linewidth]{../Plots/Temporal_SR.eps}
 \caption{
@@
 
-%Previous research has shown that when the ancestral sex-determining locus is linked to a locus that experiences haploid selection (e.g., meiotic drive), alleles at a new, unlinked sex-determining locus can invade and restore equal sex ratios~\cite{Kozielska:2010vm}.
-Our model allows us to analytically compare transitions in genetic sex-determination where sex-ratio bias increases, decreases, or remains equal. 
-For example, if there is meiotic drive in males only ($\alpha^\male_\Delta \neq 0$, $\alpha^\female_\Delta=0$), without gametic competition ($t^\female=t^\male=0$) the zygotic sex ratio is initially biased only when the ancestral sex-determining system is XY (Fig \ref{fig:model_outline}A and Fig \ref{fig:SexRatioBad}A) and not ZW (Fig \ref{fig:SexRatioBad}B).
-%If the ancxestral sex-determining system is ZW, the zygotic sex ratio will be 1:1 because diploid sex is determined by the proportion of Z-bearing versus W-bearing eggs and meiosis in females is fair (Fig \ref{fig:Combination_Turnover}D).
-If Fisherian sex-ratio selection were dominant, we would thus expect a difference in the potential for XY to ZW and ZW to XY transitions. 
-%However, to leading order with selection weak relative to recombination, we find that sex-ratio selection favours the spread of a neo-W by an amount equl to the spread of a neo-Y into a ZW system (relabeling XY as the heterogametic sex and reversing the labels of males and females in Table \ref{tab:specialcases})
-However, invasion by a neo-W allele into an XY system and invasion by a neo-Y allele into a ZW system occur under the same conditions ($\lambda_{Y'}^{(XY)} = \lambda_{W'}^{(ZW)}$ and $\lambda_{W'}^{(XY)}=\lambda_{Y'}^{(ZW)}$, at least to order $\epsilon^2$), implying that,% surprisingly,
-\vspace{0.5cm}
-
-\noindent\textit{Conclusion 3:}
-\textbf{When selection is weak relative to recombination, the presence of haploid selection equally favors the spread of new sex determination systems that reduce sex-ratio bias (benefiting from Fisherian sex ratio selection) or generate a sex-ratio bias (benefiting from drive)" }
-\vspace{0.5cm}
-%\noindent\textcolor{red}{\textit{Conclusion 3:}
-%\textbf{when selection is weak relative to recombination, sex-ratio selection is exactly equal in magnitude to the selection imposed by associations with selected alleles. } }
-%%\textcolor{red}{[new result]}
-%\vspace{0.5cm}
-
-\noindent For example, in Fig \ref{fig:SexRatioBad}A neo-W alleles invade an ancestral-XY system where females are initially rare, equalizing the sex ratio (as occurs in \cite{Kozielska:2010vm}).
-However, Fig \ref{fig:SexRatioBad}B shows that a neo-Y can invade the resulting ZW system under the same conditions. 
-When $R<1/2$, the invading neo-Y becomes associated with the male meiotic drive allele and the zygotic sex ratio actually evolves to become male-biased (as occurs in \cite{Ubeda:2015fx}, beginning from ESD).
-In this case, the neo-Y spreads because it is often found in males and can, if it carries the driven allele $a$, benefit from haploid selection in males (Fig \ref{fig:SexRatioBad}B).
-
 %
@@
 
-While equalizing the sex ratio and benefiting from drive are two primary reasons why haploid selection spurs sex chromosome transitions, more complex situations also arise.  
+While equalizing the sex ratio and benefiting from associations with selected alleles are two primary reasons why haploid selection spurs sex chromosome transitions, more complex situations also arise.
 For example with $R=1/2$ in Fig \ref{fig:SexRatioBad}B (green curve), the neo-Y allele spreads despite the fact that it cannot benefit from drive because free recombination moves it randomly between driven and non-driven backgrounds.
@@
 
-We next consider the case where the new sex-determining mutation, $m$, causes sex to be determined probabilistically or by heterogeneous environmental conditions (environmental sex determination, ESD), with individuals carrying allele $m$ developing as females with probability $k$.
+We next consider the case where the new sex-determining allele, $m$, causes sex to be determined probabilistically or by heterogeneous environmental conditions (environmental sex determination, ESD).
+In particular, we assume individuals carrying allele $m$ develop as females with probability $k\in(0,1)$.
 %\textcolor{red}{In our deterministic model this means the fraction female is exactly $k$, even when $m$ is rare (exploring the effect of the variance induced by ESD would also be interesting).}
 In our deterministic model this means the fraction female in the subpopulation containing $m$ is exactly $k$, even when $m$ is rare (i.e., ESD does not introduce any additional variance in sex determination).
-Here, we assume that the environmental conditions that determine sex does not differentially affect the fitness of males versus females. 
-Such correlations can favour environmental sex-determining systems by allowing each sex to be produced in the environment in which it has highest fitness; in the absence of these correlations, previous theory would predict that ESD is favoured when it produces more equal sex ratios than the ancestral system (see reviews by~\cite{Charnov:1982wg,Bull:1983vi,West:2009we}).
+We also assume that the environmental conditions that determine sex do not differentially affect the fitness of males versus females. 
+Such correlations can favour environmental sex-determining systems by allowing each sex to be produced in the environment in which it has highest fitness; in the absence of these correlations previous theory would predict that ESD is favoured when it produces more equal sex ratios than the ancestral system (see reviews by~\cite{Charnov:1982wg,Bull:1983vi,West:2009we}).
 %(e.g., maternal condition, mate quality, age, or host size)
@@
 As discussed above, $\lambda_{Y'\rvert R=1/2}^{(XY)}$ is necessarily less than one (cis-GSD transition), but $\lambda_{W'\rvert R=1/2}^{(XY)}$ (trans-GSD transition) can be greater than one if there is haploid selection (see Conclusion 2B).
-That is, with haploid selection, an allele causing environmental-sex-determination can invade an ancestrally-XY system because it generates females that are either rare or have high fitness, in the same manner as a neo-W (likewise, ESD invades a ZW system for the same reasons as a neo-Y can).
+That is, with haploid selection, an allele causing environmental-sex-determination can invade an ancestrally-XY system because it generates females that are either rare or have high fitness, in the same manner as a neo-W (likewise, ESD invades a ZW system for the same reasons a neo-Y can).
 %An important result from Eq \eqref{eq:lambda_ESD} is that ESD can invade if there is haploid selection. 
@@
 When the ancestral sex-determining system is ZW the sex ratio is not biased.
-Nevertheless, ESD is equally likely to invade both XY and ZW systems, equalizing the zygotic sex ratio in the former case (through $\lambda_{W'}^{(XY)}$) but not in the latter (through $\lambda_{Y'}^{(ZW)}$).
+Nevertheless, ESD is equally likely to invade both XY (through $\lambda_{W'}^{(XY)}$) and ZW (through $\lambda_{Y'}^{(ZW)}$) systems, equalizing the zygotic sex ratio in the former case but not in the latter.
 %This is again because haploid selection can facilitate the turnover of sex chromosomes either through sex-ratio biases or through associations between the new sex determining region with selected alleles.
@@
 In addition, we note that ESD may not invade, even if the sex ratio is initially biased (e.g., with drive in males only, $r<1/2$, $h^\female=h^\male$, and $s^\female s^\male<0$, then $\lambda_{W'}^{(XY)}<1$, see Table \ref{tab:specialcases}).
-We conclude that, as with neo-W and neo-Y loci:
+We conclude that, as with neo-W and neo-Y mutations:
 \vspace{0.5cm}
@@
 
-New sex determination systems are typically expected to spread when they equalise the sex ratio and/or when they increase linkage with loci that experience sex-differences in selection~\cite{Blaser2012, vanDoorn2014re} (including sex-differences at the haploid stage, Conclusion 2A and~\cite{Ubeda:2015fx}).
-However, we find that trans-GSD transitions can be favoured in cases where linkage with the sex-determining locus is actually weakened (Conclusions 1 \& 2B, Fig \ref{fig:SexAntagTighter}), especially when there is haploid selection (Conclusion 2B, Figs \ref{fig:Combination_Centimorgans} \& \ref{fig:SexRatioBad}).
+New sex-determination systems are typically expected to spread when they equalise the sex ratio and/or when they increase linkage with loci that experience sex-differences in selection~\cite{Blaser2012, vanDoorn2014re}.
+In accordance with the latter mechanism, we find that sex-differences in selection at the haploid stage can favour trans-GSD transitions that tighten sex-linkage (Conclusion 2A).
+%, as exemplified in~\cite{Ubeda:2015fx} for ESD-GSD transitions.
+However, we also find that trans-GSD transitions can be favoured in cases where linkage with the sex-determining locus is actually weakened (Conclusions 1A-1C \& 2B, Fig \ref{fig:SexAntagTighter} \& \ref{fig:regionplots}), especially when there is haploid selection (Conclusion 2B, Figs \ref{fig:Combination_Centimorgans} \& \ref{fig:SexRatioBad}).
 Furthermore, we show that the spread of new sex-determination systems is not dominated by selection to balance the sex ratio (Conclusions 3 \& 4, Fig \ref{fig:SexRatioBad}).
@@
 %What we would like to stress is that sex-ratio selection alone cannot predict when new sex-determining systems can evolve.
-Significantly, with weak selection, we find that there is no difference in conditions allowing XY to ZW and ZW to XY transitions (Conclusion 3)%, indicating that transitions in sex determination are not predominantly predicted by their effect on the sex ratio (i.e., the sex-ratio bias created by male haploid selection facilitates the spread of a neo-W allele into an XY system to the same degree that male haploid selection drives the spread of a neo-Y into a ZW system with a 1:1 sex ratio).
+Significantly, with weak selection, we find that there is no difference in conditions allowing XY to ZW and ZW to XY transitions (Conclusion 3) %, indicating that transitions in sex determination are not predominantly predicted by their effect on the sex ratio (i.e., the sex-ratio bias created by male haploid selection facilitates the spread of a neo-W allele into an XY system to the same degree that male haploid selection drives the spread of a neo-Y into a ZW system with a 1:1 sex ratio).
 %An asymmetry can develop when sex-linkage is tight (e.g., Fig \ref{fig:Combination_Centimorgans} near -25cM and 25cM) but under most circumstances we do not predict asymmetry between XY to ZW and ZW to XY transitions despite the presence/absence of sex-ratio selection.
@@
 Even in animal and plant species that have much larger and more conspicuous diploid phases than haploid phases, many loci have been shown to experience haploid selection through gamete competition and/or meiotic drive~\cite{Mulcahy:1996ha,JOSEPH:2004haa, Lalanne2004,Ubeda:2005gw,Fishman2005,Leppala2008,Leppala2013,Didion2015,Didion2016, Lindholm:2016cw}.
-In some cases, meiotic drive (Burt and Trivers, 2006, Chapter 6~\cite{Burt:2006}) or gametic competition~\cite{Lloyd:1974tz,Conn:1981uw,Stehlik:2005ul,Stehlik:2006to,Field:2012fd,Field:2013cc} among X- and Y-bearing gametes is known to cause sex ratio biases.
+In some cases, meiotic drive (Burt and Trivers, 2006, Chapter 6~\cite{Burt:2006}) or gametic competition~\cite{Lloyd:1974tz,Conn:1981uw,Stehlik:2005ul,Stehlik:2006to,Field:2012fd,Field:2013cc} among X- and Y-bearing gametes is known to cause sex-ratio biases.
 %Segregation distortion provides putative evidence of haploid selection and can sometimes be attributed to meiotic drive and/or gametic competition~\cite{Lalanne2004,Fishman2005,Leppala2008,Leppala2013,Didion2015,Didion2016}.
@@
 In animals, recent studies have demonstrated that sperm competition, even within a single ejaculate, can alter haploid allele frequencies and increase offspring fitness~\cite{Immler:2014im,Alavioon2017}.
-Nevertheless, although precise estimates are uncertain, a relatively small proportion of all genes are thought to be \textcolor{red}{expressed} and selected during competition in animal sperm~\cite{Zheng:2001fi,JOSEPH:2004haa,Vibranovski:2010et}.
-In plants, however, haploid selection may be particularly important. %due to the presence of a multicellular haploid stage. 
+Although precise estimates are uncertain, a relatively small proportion of all genes are thought to be expressed and selected during competition in animal sperm~\cite{Zheng:2001fi,JOSEPH:2004haa,Vibranovski:2010et}.
+However, expression is not required for haploid selection if the fitness of a gamete depends on its ability to condense DNA~\cite{Immler2018}.   
+In plants haploid selection may be particularly important. %due to the presence of a multicellular haploid stage. 
 For example, 60-70\% of all genes are expressed in the male gametophyte, and these genes exhibit stronger signatures of selection than randomly-chosen genes~\cite{Borg:2009jpa,Arunkumar:2013iq,Gossmann:2014dua}.
@@
 In addition, Y-linked genes are over-expressed relative to X-linked genes in pollen (but not in flower buds or leaves). 
-This suggests that the spread of neo-Y chromosomes in this clade could have been favoured through linkage with haploid selected genes. 
+This suggests that the spread of neo-Y chromosomes in this clade could have been favoured through linkage with haploid selected genes rather than those under sexual antagonism. 
 %maybe add a flag here for switching to clade-level expectations:
@@
 Assuming that transitions from dioecy to hermaphroditism (equal parental investment in male and female gametes) are favoured in a similar manner to the ESD examined here (equal probability of zygotes developing as males or females), our results suggest that competition among haploid pollen could drive transitions between dioecy and hermaphroditism, which are frequent in plants~\cite{Kafer2017, Goldberg2017}.
-To further examine this link, future theory could include haploid selection and sex chromosomes when investigating transitions between dioecy and hermaphroditism. 
+To further examine this link, future theory could simultaneously include inbreeding, haploid selection, and sex chromosomes when investigating transitions between dioecy and hermaphroditism. 
 Future empirical studies could look for evidence of haploid selection acting on former sex chromosomes in hermaphroditic species (e.g., a study such as \cite{Sandler264382} on ancestral, rather than derived, sex chromosomes).
@@
 In support of this hypothesis, researchers have identified genes on recently derived sex chromosomes that might be under sexually-antagonistic selection~\cite{Lindholm:2002dw,Tripathi:2009cw,Ser:2010iq}.
-However, we show that, if selected loci are tightly linked to the ancestral sex-determining locus, they can drive trans-GSD transitions during which sex-linkage is reduced (Conclusion 1), thus widening the genomic locations that could be driving trans-GSD transitions.
+However, we show that, if selected loci are tightly linked to the ancestral sex-determining locus, they can drive trans-GSD transitions which reduce sex-linkage (Conclusions 1A-1C \& 2B), thus widening the range of genomic locations that could be driving observed trans-GSD transitions.
 In addition, we find that polymorphic sex determining systems (X, Y, and neo-W alleles all segregating) can be maintained when a selected locus is tightly linked to the ancestral sex-determining system (e.g., \nameref{fig:freqAll}B and \nameref{fig:freqAll}C), which is not possible with loose linkage~\cite{vanDoorn:2010hu}.
@@
 
-Our tight linkage results are consistent with empirical data from species in which new feminizing mutations are found alongside ancestral XY loci. 
+Our tight linkage result, in particular the prediction that invasion can lead to polymorphic sex determination, is consistent with empirical data from species in which new feminizing mutations are found segregating with ancestral XY loci.
 For example, in the platyfish (\textit{Xiphophorus maculatus}), X,Y, and W alleles segregate at one locus (or two closely-linked loci) near to potentially sexually-antagonistic genes for pigmentation and sexual maturity~\cite{Kallman1965,Kallman1968, Volff2001, Schultheis2006}.
-Furthermore, several rodent species maintain feminizing alleles along with the ancestral X and Y sex-determination alleles (reviewed in~\cite{Fredga1994}). 
+Furthermore, several rodent species maintain \textcolor{red}{dominant?} feminizing alleles along with the ancestral X and Y sex-determination alleles (reviewed in~\cite{Fredga1994}). 
 In nine \textit{Akadon} rodent species, it appears that male-determining-\textit{sry} expression is suppressed by an autosomal feminizing allele (a neo-W allele), creating XY females~\cite{Bianchi2002,Sanchez2010}.
-XY females have increased fitness relative to XX females~\cite{Hoekstra2001}. However, it is not yet clear whether loci linked to the feminizing factor or the ancestral Y cause this effect. 
-Most convincingly, in \textit{Mus microtoides}, females can have XX, XX$^\ast$ or X$^\ast$Y genotypes~\cite{Veyrunes2010}. 
-Previous theory would predict that the X$^\ast$ chromosome (potentially an autosome that has fused with the sex chromosome) harbours female beneficial alleles, driving its spread. 
+XY females have increased fitness relative to XX females~\cite{Hoekstra2001}. 
+However, it is not yet clear whether loci linked to the feminizing factor or the ancestral Y cause this effect. 
+Most convincingly, in \textit{Mus minutoides}, females can have XX, XX$^\ast$ or X$^\ast$Y genotypes~\cite{Veyrunes2010}. 
+Previous theory would predict that the dominant X$^\ast$ chromosome (potentially an autosome that has fused with the sex chromosome) harbours female beneficial alleles, driving its spread. 
 However, XX and XX$^\ast$ females have similar fitness, whereas X$^\ast$Y female fitness is enhanced~\cite{Saunders2014,Saunders2016, Veyrunes2017}. 
@@
 %Limitation 1: DEGENERATE Y
-We note that we assume that sex-determining alleles do not experience direct selection except via their associations with sex and selected alleles.
+Our models assume that sex-determining alleles do not experience direct selection except via their associations with sex and selected alleles.
 However, in some cases, there may be significant degeneration around the sex-limited allele (Y or W) in the ancestral sex-determining region because recessive deleterious mutations and/or deletions accumulate in the surrounding non-recombining regions~\cite{Rice:1996ke,Charlesworth:2000cc,Bachtrog:2006ed,Marais:2008hm}.
@@
 %While not explicitly studied, we also predict that Y or W degeneration would prevent fixation of the new sex-determining genes considered here.
-Degeneration around the Y or W could explain why trans-GSD transitions are not observed to be much more common than cis-GSD transitions despite the fact that our models demonstrate that they are favoured under a wider range of conditions, especially with haploid selection.
+Degeneration around the Y or W could explain why trans-GSD transitions are not observed to be much more common than cis-GSD transitions \textcolor{red}{(citation?)} despite the fact that our models demonstrate that they are favoured under a wider range of conditions, especially with haploid selection.
 For example, there are a dozen sex chromosome configurations among Dipteran species but only one transition between male and female heterogamety~\cite{Vicoso:2015hf}, but Y degeneration or absence is also very common among \textit{Diptera}~\cite{Vicoso:2015hf}.
@@
 We have shown that tight sex-linkage and haploid selection can drive previously unexpected transitions between sex-determining systems.
-In particular, both can select for new sex-determining loci that are more loosely linked to loci under selection (Conclusions 1 \& 2B). 
+In particular, both can select for new sex-determining loci that are more loosely linked to loci under selection (Conclusions 1A-1C \& 2B). 
 In addition, haploid selection can cause transitions in GSD analogous to those caused by purely sexually-antagonistic selection, eliminating the need for differences in selection between male and female diploids (Conclusion 2A).
 We conclude that haploid selection should be considered as a pivotal factor driving transitions between sex-determining systems. 
-Further, transitions involving haploid selection can be driven by sex-ratio selection or cause sex-ratio biases to evolve; to leading order, selection to balance the sex ratio and hitch-hiking with haploid selected alleles are of equal magnitude (Conclusions 3 \& 4).
+Further, transitions involving haploid selection can be driven by sex-ratio selection or cause sex-ratio biases to evolve; to leading order, selection to balance the sex ratio and the benefits of hitch-hiking with haploid selected alleles are of equal magnitude (Conclusions 3 \& 4).
 Overall, our results suggest several new scenarios under which new sex-determining systems are favoured, which could help to explain why the evolution of sex-determining systems is so dynamic.

### 2018-05-01 LaTeX/main_revised.tex
updated conclusions, but havent referenced them proprely

@@
 
-Neo-W alleles, on the other hand, can invade an ancestral XY system because, under some conditions, the neo-W can become more strongly specialized for females (the full invasion conditions are given in \nameref{app:inv_cond}; equations \ref{Binvasion} and \ref{Ainvasion}).
+Neo-W alleles, on the other hand, can invade an ancestral XY system (the full invasion conditions are given in \nameref{app:inv_cond}; equations \ref{Binvasion} and \ref{Ainvasion}).
 Thus,
@@
 
-\noindent\textit{Conclusion 1A:}
+\noindent\textit{Conclusion 1:}
 %\textbf{selection on loci within the non-recombining region around the sex-determining locus ($r\approx0$) allows the invasion of less closely linked sex-determining alleles ($r<R\leq1/2$) during a trans-GSD transition} (XY $\leftrightarrow$ ZW).
-\textbf{Selection on loci in or near the non-recombining region around the sex-determining locus ($r\approx0$) prevents cis-GSD transitions (XY $\leftrightarrow$ XY, ZW $\leftrightarrow$ ZW) but can spur trans-GSD transitions (XY $\leftrightarrow$ ZW), which weaken sex-linkage.}
+\textbf{Selection on loci in or near the non-recombining region around the sex-determining locus ($r\approx0$) prevents cis-GSD transitions (XY $\leftrightarrow$ XY, ZW $\leftrightarrow$ ZW) but can spur trans-GSD transitions (XY $\leftrightarrow$ ZW).}
+\textcolor{red}{[Not clear from van Doorn \& Kirkpatrick 2007, 2010]}
 \vspace{0.5cm}
 
-Conclusion 1A does not depend on the form of selection maintaining a polymorphism (sexually-antagonistic selection, overdominance, ploidally-antagonistic selection, or some combination, Fig \ref{fig:SexAntagTighter}, \nameref{fig:temporalOverdominance}, \nameref{fig:regionPloidAntag}, and \nameref{fig:SexAntagTighterMaleDrive}).
-The conditions become more restrictive, however, with increasing recombination ($R$) between the new sex-determining locus and the selected locus.  
+\noindent Trans-GSD transitions can occur because, under some conditions, the neo-W can become more strongly specialized for females.
+This does not depend on the form of selection maintaining a polymorphism (sexually-antagonistic selection, overdominance, ploidally-antagonistic selection, or some combination, Fig \ref{fig:SexAntagTighter}, \nameref{fig:temporalOverdominance}, \nameref{fig:regionPloidAntag}, and \nameref{fig:SexAntagTighterMaleDrive}).
+
+The conditions allowing trans-GSD transitions become more restrictive with increasing recombination ($R$) between the new sex-determining locus and the selected locus.  
 The invasion of completely unlinked neo-W alleles ($R = 1/2$) can occur with overdominance in males or with haploid selection (e.g., when male drive is opposed by diploid selection, as in \cite{Kozielska:2010vm}) but is not possible with only sexually-antagonistic selection where selection is directional in each diploid sex (see \nameref{file:Mathematica}).
-Here, we focus on cases where there is no haploid selection (Fig \ref{fig:SexAntagTighter}A) and discuss the additional effect of haploid selection in \nameref{app:inv_cond} (see also Conclusion 1C). 
+To clarify the conditions under which trans-GSD transitions occur, we focus here on cases where there is no haploid selection (Fig \ref{fig:SexAntagTighter}A) and discuss the additional effect of haploid selection in \nameref{app:inv_cond} (see also Conclusion 2B).
 %Essentially, neo-W alleles are able to invade (even with $R>r$) because the ancestral X experiences selection in males. 
@@
 
-When only one neo-W haplotype has growth rate greater than one (see Fig \ref{fig:regionplots}), a neo-W allele can invade as long as Eq \eqref{eq:lambdasGen} is satisfied, which may require that the recombination rate, $R$, is small enough.
-Nevertheless, because we assume here that $r$ is small, these results indicate that a more loosely linked sex-determining region ($r<R$) can spread.
-For example, tightly sex-linked loci that experience sexually-antagonistic selection can drive trans-GSD transitions in which the new sex-determining locus is less closely linked to the locus under selection (Fig \ref{fig:SexAntagTighter}).
-
 Given that the $a$ allele is fixed on the Y and can be considered ancestrally `male-beneficial', it is surprising that neo-W-$a$ haplotypes can sometimes be favoured by selection in females ($\Lambda_{W'a}^{(XY)}>1$).
@@
 
+When only one neo-W haplotype has growth rate greater than one (see Fig \ref{fig:regionplots}), a neo-W allele can invade as long as Eq \eqref{eq:lambdasGen} is satisfied, which may require that the recombination rate, $R$, is small enough.
+Nevertheless, because we assume here that $r$ is small, these results indicate that a more loosely linked sex-determining region ($r<R$) can spread.
+For example, tightly sex-linked loci that experience sexually-antagonistic selection can drive trans-GSD transitions in which the new sex-determining locus is less closely linked to the locus under selection (Fig \ref{fig:SexAntagTighter}).
+
 In some cases, both W-$A$ and W-$a$ haplotypes can spread.
@@
 
-\noindent\textit{Conclusion 1B:}
-\textbf{With tight linkage between a selected locus and the ancestral sex-determining locus ($r\approx0$), selection to better specialize on the ancestrally-non-heterogametic sex can drive trans-GSD transitions (XY $\leftrightarrow$ ZW) that weaken sex-linkage ($r<R\leq1/2$; potentially even shifting sex determination to a different chromosome) and sometimes lead to polymorphic sex-determination systems.}
+\noindent\textit{Conclusion 2A:}
+\textbf{
+With tight linkage between a selected locus and the ancestral sex-determining locus ($r\approx0$), trans-GSD transitions (XY $\leftrightarrow$ ZW) can be driven by selection to better specialize on the ancestrally-non-heterogametic sex.
+These transitions weaken sex-linkage ($r<R$), potentially shifting sex determination to a different chromosome ($R=1/2$). 
+Such transitions can lead to polymorphic sex-determination systems.
+}
+\textcolor{red}{[consistent with special case of Kozielska et al 2010]}
 \vspace{0.5cm}
 
-Adding haploid selection (\nameref{app:inv_cond}) we also conclude that
+\nameref{app:inv_cond}) shows that Conclusion 2A holds with or without haploid selection, and further demonstrates that
 \vspace{0.5cm}
 
-\noindent\textit{Conclusion 1C:}
+\noindent\textit{Conclusion 2B:}
 \textbf{
-With tight linkage between a selected locus and the ancestral sex-determining locus ($r\approx0$), haploid selection allows trans-GSD transitions (XY $\leftrightarrow$ ZW) that weaken sex-linkage ($r<R\leq1/2$; potentially even shifting sex determination to a different chromosome) even when selection is sexually-antagonistic with directional selection in each diploid sex.
-These trans-GSD transitions equalize the sex ratio.
-}
-\vspace{0.5cm}
+With tight linkage between a selected locus and the ancestral sex-determining locus ($r\approx0$), haploid selection can drive trans-GSD transitions (XY $\leftrightarrow$ ZW) that weaken sex-linkage ($r<R$), even when selection is sexually-antagonistic with directional selection in each diploid sex.
+These trans-GSD transitions are driven by selection to equalize the sex ratio.
+As in Conclusion 2A, such transitions potentially shift sex determination to a different chromosome ($R=1/2$) and can lead to polymorphic sex-determination systems.}
+\textcolor{red}{[consistent with special case of Kozielska et al 2010]}
 
@@
 \vspace{0.5cm}
-\noindent\textit{Conclusion 2A:}\
-\textbf{New sex-determining alleles (causing cis- \textit{or} trans-GSD transitions) can spread if they arise morely closely linked with a locus that experiences selection than the ancestral-sex-determining locus is ($R<r$).}
+\noindent\textit{Conclusion 3A:}\
+\textbf{New sex-determining alleles (causing cis- \textit{or} trans-GSD transitions) can spread if they arise more closely linked with a locus that experiences selection than the ancestral-sex-determining locus is ($R<r$).}
+\textcolor{red}{[consistent with van Doorn \& Kirkpatrick 2007, 2010]} 
 \vspace{0.5cm}
@@
 %\vspace{0.5cm}
-\noindent\textit{Conclusion 2B:}\
+\noindent\textit{Conclusion 3B:}\
 \textbf{New sex-determining alleles (causing trans-GSD transitions, XY $\leftrightarrow$ ZW) can spread even if they arise less closely linked with a locus that experiences selection than the ancestral-sex-determining locus is ($r<R$), requiring haploid selection and some initial sex-linkage ($r<1/2$) as necessary conditions.}
+\textcolor{red}{[consistent with examples in Ubeda et al 2015]}  
 \vspace{0.5cm}
@@
 
-\noindent\textit{Conclusion 3:}
+\noindent\textit{Conclusion 4A:}
 \textbf{When selection is weak relative to recombination, the presence of haploid selection equally favors the spread of new sex determination systems that reduce sex-ratio bias (benefiting from Fisherian sex ratio selection) or generate a sex-ratio bias (benefiting from associations with selected alleles).
 }
+\textcolor{red}{[new result]}  
 \vspace{0.5cm}
@@
 
-\noindent\textit{Conclusion 4:}
+\noindent\textit{Conclusion 4B:}
 \textbf{
@@
 }
+\textcolor{red}{[new result]}  
 %\textcolor{red}{[new result]}

### 2018-05-01 LaTeX/response.tex
rearranged conclusions once again

@@
 \begin{enumerate}
-\item[(1A)] ancestrally-tight sex-linkage allows trans-GSD transitions but not cis-GSD transitions (L228-230)
-\item[(1B)] with ancestrally-tight sex-linkage, trans-GSD transitions (which weaken sex-linkage and can lead to polymorphic sex determination systems) are driven by selection to better specialize on the ancestrally-non-heterogametic sex (L282-286)
-\item[(1C)] with ancestrally-tight sex-linkage, haploid selection can spur trans-GSD transitions (which weaken sex-linkage and equalize the sex-ratio) even when selection is sexually-antagonistic in diploids  (L288-293)
-\item[(2A)] when selection is weak relative to ancestral sex-linkage, cis- or trans-GSD transitions can occur when the new sex-determining allele increases linkage with selected loci (L324-326)
-\item[(2B)] when selection is weak relative to ancestral sex-linkage, haploid selection allows trans-GSD transitions to occur even when the new sex-determining allele decreases linkage with the selected locus (L327-330)
-\item[(3)] when selection is weak relative to ancestral sex-linkage, sex-ratio selection is exactly equal in magnitude to the selection imposed by associations with selected alleles (and thus transitions can increase or decrease the sex-ratio bias) (L350-353)
-\item[(4)] transitions from genetic to environmental sex-determination are not straightforwardly predicted by selection to balance the zygotic sex ratio when haploid selection is present (L411-413)
+\item[(1)] ancestrally-tight sex-linkage allows trans-GSD transitions but not cis-GSD transitions (L228-230)
+\item[(2A)] with ancestrally-tight sex-linkage, trans-GSD transitions (which weaken sex-linkage and can lead to polymorphic sex determination systems) can be driven by selection to better specialize on the ancestrally-non-heterogametic sex (L282-286)
+\item[(2B)] with ancestrally-tight sex-linkage, haploid selection can spur trans-GSD transitions (which weaken sex-linkage and equalize the sex-ratio) even when selection is sexually-antagonistic in diploids  (L288-293)
+\item[(3A)] when selection is weak relative to ancestral sex-linkage, cis- or trans-GSD transitions can occur when the new sex-determining allele increases linkage with selected loci (L324-326)
+\item[(3B)] when selection is weak relative to ancestral sex-linkage, haploid selection allows trans-GSD transitions to occur even when the new sex-determining allele decreases linkage with the selected locus (L327-330)
+\item[(4A)] when selection is weak relative to ancestral sex-linkage, sex-ratio selection is exactly equal in magnitude to the selection imposed by associations with selected alleles (and thus transitions can increase or decrease the sex-ratio bias) (L350-353)
+\item[(4B)] transitions from genetic to environmental sex-determination are not straightforwardly predicted by selection to balance the zygotic sex ratio when haploid selection is present (L411-413)
 %\vspace{0.25cm}\\
@@
 %These are all new results, although (1A) was shown for the special case of $r=0$, $R=1/2$, and ploidally-antagonistic selection in Kozielska et al 2010, which we now mention immediately below (1A).
-\textcolor{red}{what is new and what is confirmatory?} 
+\textcolor{red}{what is new and what is confirmatory? [see red notes in main text in conclusions]} 
 }
@@
 For example, Ubeda et al consider ESD-GSD transitions. 
-Nevertheless, these transitions involve increased linkage with a haploid selected locus, which is precedent for our Conclusion 2A (which considers only GSD-GSD transitions).
+Nevertheless, these transitions involve increased linkage with a haploid selected locus, which is precedent for our Conclusion 3A (which considers only GSD-GSD transitions).
 We now mention this in the Introduction (L59-61) and again in the Discussion (L432).  
-Similarly, Kozielska et al involves a special case of GSD transitions during which sex-linkage goes from perfect to none, which is is an extreme example of our Conclusion 2B.
+Similarly, Kozielska et al involves a special case of GSD transitions during which sex-linkage goes from perfect to none, which is is an extreme example of our Conclusions 2A \&2B.
 This is twice mentioned (L64-67, L237). 
@@
 %Especially because their main conclusion involved the strong influence of sex-ratio selection, which is explicitly not a driver during many such transitions. 
-In addition, our Conclusions 3 and 4 reconcile Kozielska et al and Ubeda et al, explaining that sex-ratio selection is not an overwhelming force driving transitions in sex determination. 
+In addition, our Conclusions 4A and 4B reconcile Kozielska et al and Ubeda et al, explaining that sex-ratio selection is not an overwhelming force driving transitions in sex determination. 
 We believe that our new presentation makes the novel and unexpected features of our results much more apparent. 
@@
 To clarify our meaning we have rephrased (in Author summary): ``Surprisingly, we find the two forces (selection to equalize the sex-ratio and the benefits of hitch-hiking with driven alleles that distort the sex ratio) will often be equally strong, and thus neither is sufficient to explain the spread of new sex-determining systems in every case."
-We believe that the re-framing of the Introduction/Discussion and the emphasis given to specific Conclusions 1-4 will help to clarify this point throughout the paper.
+We believe that the re-framing of the Introduction/Discussion and the emphasis given to specific Conclusions will help to clarify this point throughout the paper.
 }

### 2018-05-01 LaTeX/main_revised.tex
rearranged conclusions once again

@@
 
-From the arguments above we conclude that
+From the arguments above and in \nameref{app:inv_cond} we conclude that
 \vspace{0.5cm}
@@
 
-\nameref{app:inv_cond}) shows that Conclusion 2A holds with or without haploid selection, and further demonstrates that
+\nameref{app:inv_cond} shows that Conclusion 2A holds with or without haploid selection and further demonstrates that
 \vspace{0.5cm}
@@
 \textbf{
-With tight linkage between a selected locus and the ancestral sex-determining locus ($r\approx0$), haploid selection can drive trans-GSD transitions (XY $\leftrightarrow$ ZW) that weaken sex-linkage ($r<R$), even when selection is sexually-antagonistic with directional selection in each diploid sex.
-These trans-GSD transitions are driven by selection to equalize the sex ratio.
-As in Conclusion 2A, such transitions potentially shift sex determination to a different chromosome ($R=1/2$) and can lead to polymorphic sex-determination systems.}
+With tight linkage between a haploid selected locus and the ancestral sex-determining locus ($r\approx0$), trans-GSD transitions (XY $\leftrightarrow$ ZW) can be driven by selection to better specialize on the ancestrally-non-heterogametic sex and/or sex-ratio selection.
+Such transitions reduce sex ratio bias.
+}
 \textcolor{red}{[consistent with special case of Kozielska et al 2010]}
@@
 \noindent\textit{Conclusion 3B:}\
-\textbf{New sex-determining alleles (causing trans-GSD transitions, XY $\leftrightarrow$ ZW) can spread even if they arise less closely linked with a locus that experiences selection than the ancestral-sex-determining locus is ($r<R$), requiring haploid selection and some initial sex-linkage ($r<1/2$) as necessary conditions.}
+\textbf{New sex-determining alleles (causing trans-GSD transitions, XY $\leftrightarrow$ ZW) can spread even if they arise less closely linked with a locus that experiences selection than the ancestral-sex-determining locus is ($r<R$), requiring haploid selection and some initial sex-linkage ($r<1/2$).}
 \textcolor{red}{[consistent with examples in Ubeda et al 2015]}  
@@
 Eq \eqref{eq:lambda_ESD} shows that the ESD mutation gets half of the fitness of a feminizing mutation (neo-W) and half of the fitness of a masculinizing mutation (neo-Y), but only has an effect one half of the time (the other half of the time it produces the same sex as the ancestral system would have).
-As discussed above, $\lambda_{Y'\rvert R=1/2}^{(XY)}$ is necessarily less than one (cis-GSD transition), but $\lambda_{W'\rvert R=1/2}^{(XY)}$ (trans-GSD transition) can be greater than one if there is haploid selection (see Conclusion 2B).
+As discussed above, $\lambda_{Y'\rvert R=1/2}^{(XY)}$ is necessarily less than one (cis-GSD transition), but $\lambda_{W'\rvert R=1/2}^{(XY)}$ (trans-GSD transition) can be greater than one if there is haploid selection (see Conclusion 3B).
 That is, with haploid selection, an allele causing environmental-sex-determination can invade an ancestrally-XY system because it generates females that are either rare or have high fitness, in the same manner as a neo-W (likewise, ESD invades a ZW system for the same reasons a neo-Y can).
@@
 New sex-determination systems are typically expected to spread when they equalise the sex ratio and/or when they increase linkage with loci that experience sex-differences in selection~\cite{Blaser2012, vanDoorn2014re}.
-In accordance with the latter mechanism, we find that sex-differences in selection at the haploid stage can favour trans-GSD transitions that tighten sex-linkage (Conclusion 2A).
+In accordance with the latter mechanism, we find that sex-differences in selection at the haploid stage can favour trans-GSD transitions that tighten sex-linkage (Conclusion 3A).
 %, as exemplified in~\cite{Ubeda:2015fx} for ESD-GSD transitions.
-However, we also find that trans-GSD transitions can be favoured in cases where linkage with the sex-determining locus is actually weakened (Conclusions 1A-1C \& 2B, Fig \ref{fig:SexAntagTighter} \& \ref{fig:regionplots}), especially when there is haploid selection (Conclusion 2B, Figs \ref{fig:Combination_Centimorgans} \& \ref{fig:SexRatioBad}).
-Furthermore, we show that the spread of new sex-determination systems is not dominated by selection to balance the sex ratio (Conclusions 3 \& 4, Fig \ref{fig:SexRatioBad}).
+However, we also find that trans-GSD transitions can be favoured in cases where linkage with the sex-determining locus is actually weakened (Conclusions 2A, 2B \& 3B, Fig \ref{fig:SexAntagTighter} \& \ref{fig:regionplots}), especially when there is haploid selection (Conclusion 3B, Figs \ref{fig:Combination_Centimorgans} \& \ref{fig:SexRatioBad}).
+Furthermore, we show that the spread of new sex-determination systems is not dominated by selection to balance the sex ratio (Conclusions 4A \& 4B, Fig \ref{fig:SexRatioBad}).
 
@@
 %What we would like to stress is that sex-ratio selection alone cannot predict when new sex-determining systems can evolve.
-Significantly, with weak selection, we find that there is no difference in conditions allowing XY to ZW and ZW to XY transitions (Conclusion 3) %, indicating that transitions in sex determination are not predominantly predicted by their effect on the sex ratio (i.e., the sex-ratio bias created by male haploid selection facilitates the spread of a neo-W allele into an XY system to the same degree that male haploid selection drives the spread of a neo-Y into a ZW system with a 1:1 sex ratio).
+Significantly, with weak selection, we find that there is no difference in conditions allowing XY to ZW and ZW to XY transitions (Conclusion 4A) %, indicating that transitions in sex determination are not predominantly predicted by their effect on the sex ratio (i.e., the sex-ratio bias created by male haploid selection facilitates the spread of a neo-W allele into an XY system to the same degree that male haploid selection drives the spread of a neo-Y into a ZW system with a 1:1 sex ratio).
 %An asymmetry can develop when sex-linkage is tight (e.g., Fig \ref{fig:Combination_Centimorgans} near -25cM and 25cM) but under most circumstances we do not predict asymmetry between XY to ZW and ZW to XY transitions despite the presence/absence of sex-ratio selection.
@@
 In support of this hypothesis, researchers have identified genes on recently derived sex chromosomes that might be under sexually-antagonistic selection~\cite{Lindholm:2002dw,Tripathi:2009cw,Ser:2010iq}.
-However, we show that, if selected loci are tightly linked to the ancestral sex-determining locus, they can drive trans-GSD transitions which reduce sex-linkage (Conclusions 1A-1C \& 2B), thus widening the range of genomic locations that could be driving observed trans-GSD transitions.
+However, we show that, if selected loci are tightly linked to the ancestral sex-determining locus, they can drive trans-GSD transitions which reduce sex-linkage (Conclusions 2A, 2B, \& 3B), thus widening the range of genomic locations that could be driving observed trans-GSD transitions.
 In addition, we find that polymorphic sex determining systems (X, Y, and neo-W alleles all segregating) can be maintained when a selected locus is tightly linked to the ancestral sex-determining system (e.g., \nameref{fig:freqAll}B and \nameref{fig:freqAll}C), which is not possible with loose linkage~\cite{vanDoorn:2010hu}.
@@
 We have shown that tight sex-linkage and haploid selection can drive previously unexpected transitions between sex-determining systems.
-In particular, both can select for new sex-determining loci that are more loosely linked to loci under selection (Conclusions 1A-1C \& 2B). 
-In addition, haploid selection can cause transitions in GSD analogous to those caused by purely sexually-antagonistic selection, eliminating the need for differences in selection between male and female diploids (Conclusion 2A).
+In particular, both can select for new sex-determining loci that are more loosely linked to loci under selection (Conclusions 2A, 2B \& 3B). 
+In addition, haploid selection can cause transitions in GSD analogous to those caused by purely sexually-antagonistic selection, eliminating the need for differences in selection between male and female diploids (Conclusion 2B \& 3B).
 We conclude that haploid selection should be considered as a pivotal factor driving transitions between sex-determining systems. 
-Further, transitions involving haploid selection can be driven by sex-ratio selection or cause sex-ratio biases to evolve; to leading order, selection to balance the sex ratio and the benefits of hitch-hiking with haploid selected alleles are of equal magnitude (Conclusions 3 \& 4).
+Further, transitions involving haploid selection can be driven by sex-ratio selection or cause sex-ratio biases to evolve; to leading order, selection to balance the sex ratio and the benefits of hitch-hiking with haploid selected alleles are of equal magnitude (Conclusions 4A \& 4B).
 Overall, our results suggest several new scenarios under which new sex-determining systems are favoured, which could help to explain why the evolution of sex-determining systems is so dynamic.

### 2018-05-01 LaTeX/main_revised.tex
simplified beginning of results, WARNING: the detail about the charpoly should be added to the appendix

--- 2018-05-01 LaTeX/main_revised.tex
@@
 \usepackage{lastpage,fancyhdr,graphicx}
-\usepackage[outdir=./]{epstopdf}
+\usepackage{epstopdf}
 \pagestyle{myheadings}
@@
 (1) We consider the dynamics of loci very tightly linked to the ancestral sex-determining loci, e.g., within the non-recombining region of the ancestral sex chromosomes. 
-Variation at such loci can favour the spread of new sex-determining systems in which the heterogametic sex changes (XY to ZW or ZW to XY) and the new sex-determining region is less closely linked (or even unlinked) to the locus under selection.
-%, which is \textcolor{red}{not expected from previous theory}.
+Variation at such loci can favour the spread of new sex-determining systems in which the heterogametic sex changes (XY to ZW or ZW to XY) and the new sex-determining region is less closely linked (or even unlinked) to the locus under selection, which is not expected from previous theory.
 (2) We consider selection upon haploid genotypes either during gametic competition (e.g., pollen competition) or meiosis (i.e., non-Mendelian segregation), which can cause the zygotic sex ratio to become biased.
@@
 %Furthermore, we find that the selective strengths exerted by the sex-ratio and associations with selected alleles are often equivalent. 
-Furthermore, we find that the selective forces to equalize the sex ratio are equally important to selective forces that generate skewed sex ratios when accounting for the spread of new sex chromosomes.
-This allows sex-ratio biases to increase or decrease with the spread of new sex chromosomes and implies that transitions between sex-determining systems cannot be simply predicted by selection to equalise the sex ratio.
+Furthermore, we find that sex-ratio biases may increase or decrease with the spread of new sex chromosomes, which implies that transitions between sex-determining systems cannot be simply predicted by selection to equalise the sex ratio.
+In fact, under many conditions, we find that transitions in sex determination are favoured equally strongly in cases where the sex ratio bias increases or decreases.
+%Furthermore, we find that the selective forces to equalize the sex ratio are equally important to selective forces that generate skewed sex ratios when accounting for the spread of new sex chromosomes.
+%This allows sex-ratio biases to increase or decrease with the spread of new sex chromosomes and implies that transitions between sex-determining systems cannot be simply predicted by selection to equalise the sex ratio.
 Overall, our models reveal that transitions between sex-determining systems, particularly transitions where the heterogametic sex changes, can be driven by loci in previously unpredicted genomic locations that experience selection during diploid and/or haploid phases.
@@
 Prevailing views suggest that new sex-determining systems are favoured when they equalize the sex ratio and/or when they are more closely linked to genes that experience differential selection in males and females.
-Our models include selection upon haploid genotypes (meiotic drive or gametic competition), which biases the sex-ratio and occurs differently in male and female gametes. 
+Our models include selection upon haploid genotypes (meiotic drive or gametic competition), which causes sex-ratio biases and occurs differently in male and female gametes. 
 Surprisingly, we find the two forces (selection to equalize the sex ratio and the benefits of hitchhiking with driven alleles that distort the sex ratio) will often be equally strong, and thus neither is sufficient to explain the spread of new sex-determining systems in every case.
-We also find that new sex-determining alleles can spread despite being less closely linked to selected loci, driven by initially tight linkage or haploid selection. 
-Our models therefore predict that loci in previously unexpected genomic locations and/or experiencing various types of selection (including haploid selection) can now be implicated as drivers of transitions between sex-determining systems.
+Even more unexpectedly, we find that new sex-determining alleles can spread despite being less closely linked (or unlinked) to selected loci. 
+Therefore, our models predict loci in previously unexpected genomic locations and/or experiencing various types of selection (including haploid selection) can now be implicated as drivers of transitions between sex-determining systems.
 
@@
 Counterintuitively, when linkage is tight between the sex-determining locus and a selected locus, an allele good for females can be at higher frequency on the ancestral-Y than on the ancestral-X under a variety of forms of selection.
-This, in turn, can favour a new ZW sex-determining locus that has weaker linkage with loci under selection (a similar argument applies to ZW$\rightarrow$XY transitions), which was not \textcolor{red}{apparent/discovered/considered} in previous theory \cite{vanDoorn:2010hu}.
-That is, we show that selected loci in very tight linkage with the ancestral GSD locus can favour trans-GSD transitions during which linkage associations are actually weakened.
+This, in turn, can favour a new ZW sex-determining locus that has weaker linkage with loci under selection, which was not considered in previous theory \cite{vanDoorn:2010hu}.
+A similar argument applies to ZW$\rightarrow$XY transitions.
+Thus, we show that selected loci in very tight linkage with the ancestral GSD locus can favour trans-GSD transitions during which linkage associations are actually weakened.
 
 %Haploid selection model feature and discussion of why needed
-Most significantly, we include haploid selection (gametic competition or meiotic drive) in models describing cis-GSD, trans-GSD, and GSD to ESD transitions.
-This poses an apparent evolutionary problem. 
+Most significantly, we include haploid selection (gametic competition or meiotic drive) in models describing cis-GSD, trans-GSD, and GSD to ESD transitions, which poses an apparent evolutionary problem.
 On one hand, haploid selection is typically sex-specific in that it usually occurs among gametes produced by one sex only~\cite{Mulcahy:1996ha,JOSEPH:2004haa,Ubeda:2005gw,Lindholm:2016cw}. 
@@
 Two previous studies have considered the spread of GSD with sex-specific meiotic drive~\cite{Kozielska:2010vm,Ubeda:2015fx} under a limited number of possible genetic architectures and diploid selective regimes.
-Ubeda et al. (2015)~\cite{Ubeda:2015fx} considered ancestral-ESD (with no sex-ratio bias) and numerically showed that new GSD alleles can spread if they arise in linkage with meiotic drive loci. 
-For example, a masculinizing allele spreads in association with an allele that is favoured during male meiosis, causing sex ratios to become male-biased.
-This suggests that the benefits of associating with driving alleles overwhelms selection to balance the sex ratio and that haploid selection should cause increased sex-linkage.
-%, at least when new sex-determining alleles are rare.
-However, Kozielska et al. (2010)~\cite{Kozielska:2010vm} considered an ancestral GSD system that is perfectly linked to a meiotic driver (creating a sex ratio bias). 
-They found that new, completely unlinked, GSD systems can spread if they generate the rarer sex, creating a balanced sex ratio. 
-This suggests that Fisherian sex-ratio selection overwhelms the benefits of being associated with driving alleles and that haploid selection should cause decreased sex-linkage.
+Ubeda et al. ~\cite{Ubeda:2015fx} consider ancestral-ESD (with no sex-ratio bias) and numerically show that new GSD alleles can spread if they arise in linkage with meiotic drive loci. 
+For example, a masculinizing allele spreads in association with an allele that is favoured during male meiosis, causing sex ratios to become male-biased and thereby suggesting that such beneficial associations overwhelm selection to balance the sex ratio.
+However, Kozielska et al. (2010)~\cite{Kozielska:2010vm} consider meiotic drive on an ancestral GSD sex chromosome (creating a sex ratio bias). 
+They find that new, completely unlinked, GSD systems can spread if they generate the rarer sex, creating a balanced sex ratio. 
+That is, they conclude that Fisherian sex-ratio selection caused by haploid selection favours new GSD systems.
 
 %main results
-Here, we analytically find the conditions under which new GSD or ESD systems spread in ancestral GSD systems with generic linkage between the loci involved and generic sex-specific haploid and diploid selection.
-Doing so, we reconcile the results of Kozielska et al.
-(2010)~\cite{Kozielska:2010vm} and Ubeda et al.
-(2015)~\cite{Ubeda:2015fx} by showing when new GSD systems that increase \textit{or} decrease linkage with loci under haploid selection spread.
+Here, we analytically find the conditions under which new GSD or ESD systems spread with generic linkage between the loci involved (and generic sex-specific haploid and diploid selection). 
+Strikingly, we reconcile the results of Kozielska et al.~\cite{Kozielska:2010vm} and Ubeda et al.~\cite{Ubeda:2015fx} by deriving conditions for the spread of new GSD systems that increase \textit{or} decrease linkage with haploid selected loci.
 %that experience haploid selection.
-This result is qualitatively distinct from those for diploid selection alone~\cite{vanDoorn:2007eu,vanDoorn:2010hu} and suggests that haploid selection is more likely to promote transitions between sex-determination systems.
-This also implies that transitions involving haploid selection cannot be simply explained by invoking sex-ratio selection. 
-In particular, we show that under a wide range of conditions, transitions to sex-determining systems that increase or decrease the sex-ratio bias are favoured \textit{equally strongly}.
-%(and in situations where sex-ratio biases are ancestrally present or absent).
-Finally, we show that ESD may not evolve, even if the sex ratio is initially biased by haploid selection, which is not predicted by previous theories for transitions to ESD~\cite{Charnov:1982wg,Bull:1983vi,West:2009we}.
-%Together, our results suggest that neither selection to equalize the sex ratio nor the benefits of associating with haploid selected alleles is an overwhelming force driving transitions between sex-determining systems.
-Together, our results suggest that both selection to equalize the sex ratio and the benefits of associating with haploid selected alleles can drive transitions between sex-determining systems, leading to tighter or weaker sex-linkage.
+Our result is qualitatively distinct from those for diploid selection alone~\cite{vanDoorn:2007eu,vanDoorn:2010hu} and suggests that haploid selection is more likely to promote transitions between sex-determination systems.
+We also show that transitions involving haploid selection cannot be simply explained by invoking sex-ratio selection. 
+In particular, under a wide range of conditions, we show that transitions in sex-determining system are favoured \textit{equally strongly} in situations where sex-ratio biases increase or decrease (and in situations where sex-ratio biases are ancestrally present or absent).
+Finally, we show that ESD may not evolve, even if the sex ratio is initially biased by haploid selection, which would not be predicted by previous theories for transitions to ESD~\cite{Charnov:1982wg,Bull:1983vi,West:2009we}.
+Together, these results suggest that selection to equalize the sex ratio is not an overwhelming force driving transitions between sex-determining systems.
 
@@
 Panel A: Recombination rate parameters between the ancestral-sex-determining locus ($\mathbf{X}$, here assumed to have alleles X and Y), a locus under selection ($\mathbf{A}$, with alleles $A$ and $a$), and a new sex-determining locus ($\mathbf{M}$, with alleles $M$ and $m$).
-If $r<1/2$, then associations between ancestral sex-determining alleles and selected alleles can be maintained in males. 
+If $r<1/2$, then associations between ancestral sex-determining alleles and selected alleles can be present in new male gametes/gametophytes. 
 Panel B: Haploid selection is often sex-specific, occurring during haploid production or competition in either males or females. 
@@
 We consider two forms of selection upon haploid genotypes, `gametic competition' and `meiotic drive'. 
-During gametic competition, we assume that a representative sample of all gametes/gametophytes (hereafter gametes) compete with others of the same sex for fertilization, which implies a polygamous mating system.
-Relative fitnesses in sex $\circ \in \{\female,\male\}$ during gametic competition are given by $w_A^\circ$ and $w_a^\circ$ (see table \ref{tab:fitnesstable}).
+During gametic competition, we assume that a representative sample of all gametes/gametophytes (hereafter gametes) compete for fertilization, which implies a polygamous mating system. 
+Relative fitnesses during gametic competition are given by $w_A^\circ$ and $w_a^\circ$ ($\circ \in \{\female,\male\}$; see table \ref{tab:fitnesstable}).
 On the other hand, meiotic drive in our model only affects the segregation of gametes produced by heterozgotes.
@@
 In each generation, we census the genotype frequencies in male and female gametes before gametic competition. 
+Below, it is convenient to follow the ancestral equilibrium frequency of the $A$ allele among female gametes (eggs), $\hat{p}^\female_X$, and among X-bearing, $\hat{p}^\male_X$, and among Y-bearing, $\hat{p}^\male_Y$, male gametes (sperm/pollen).
+We also track the ancestral fraction of male gametes that are Y-bearing, $\hat{q}$, which may deviate from $1/2$ due to meiotic drive in males.
+
 After gametic competition, conjugation between male and female gametes occurs at random.
@@
 %where $g$ is the diploid genotype at the $\mathbf{A}$ locus ($g \in \{AA, Aa, aa\}$).
-We do not consider fertility selection based on the mating pair or sexual selection.
+We do not consider fertility selection that depends on the mating partner, e.g., sexual selection with variation in choosiness. 
 The next generation of gametes is produced by meiosis, during which recombination and sex-specific meiotic drive can occur. 
@@
 \smallskip
-\caption{{\bf Relative fitness of different genotypes in sex $\circ \in \{\female,\male\}$ } }
+\caption{{\bf Relative fitness of different genotypes in sex, $\circ \in \{\female,\male\}$ } }
 \begin{tabular}{l c }
@@
 
-In the ancestral population, it is convenient to follow the frequency of the $A$ allele among female gametes (eggs), $p^\female_X$, and among X-bearing, $p^\male_X$, and among Y-bearing, $p^\male_Y$, male gametes (sperm/pollen).
-We also track the fraction of male gametes that are Y-bearing, $q$, which may deviate from $1/2$ due to meiotic drive in males. 
-We consider only equilibrium frequencies of alleles, $\hat{p}^\circ_i$, and Y-bearing male gametes, $\hat{q}$, when determining the invasion of new sex-determining factors.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+We begin by describing the general conditions under which new genetic sex determining alleles can spread within a population.  
+These general conditions then allow us to consider several special cases of interest in subsequent sections. 
+Finally, we consider the spread of alleles that specify environmental sex determination.
+
 \subsection*{Generic invasion by a neo-Y or neo-W}
 
-We begin by describing the conditions under which new sex determining alleles can spread within a population, without explicitly specifying ancestral allele frequencies.
-These general conditions then allow us to consider several special cases of interest in subsequent sections, where equilibrium ancestral allele frequencies are explicitly calculated.
-
-The evolution of a new sex-determining system depends on the growth rate of a rare mutant allele, $m$, at the novel sex-determining locus, $\mathbf{M}$. %, increases in frequency when rare. 
-This growth rate is determined by the leading eigenvalue ($\lambda_m^{(XY)}$) of the system of eight equations describing the frequency of eggs and sperm carrying the $m$ allele in the next generation (equations \ref{eq:recursions}).
-%, evaluated at the above equilibrium.
-%Thus, the system describing the change in frequency of the $m$ allele consists of eight recursion equations. 
+The evolution of a new sex-determining system requires that a rare mutant allele, $m$, at the novel sex-determining locus, $\mathbf{M}$, increases in frequency when rare (i.e., $\lambda_m^{(XY)}>1$, where $\lambda_m^{(XY)}$ is the leading eigenvalue of the system of eight equations describing $m$-bearing gamete frequencies, \ref{eq:recursions}).
+%This is determined by the leading eigenvalue ($\lambda_m^{(XY)}$) of the system of eight equations describing the frequency of eggs and sperm carrying the $m$ allele in the next generation (equations \ref{eq:recursions}).
 This system simplifies substantially for an epistatically dominant neo-Y ($k=0$) or neo-W ($k=1$), see \nameref{app:inv_cond}. 
-The leading eigenvalue for a rare neo-Y or neo-W allele, $m\in\{Y',W'\}$, is the largest value of $x$ that solves $x^2+ b x + c = 0$, where $b= - (\Lambda_{mA}^{(XY)} + \Lambda_{ma}^{(XY)})+(\chi_{mA}^{(XY)} + \chi_{ma}^{(XY)})$ and $c = (\Lambda_{mA}^{(XY)} - \chi_{mA}^{(XY)}) (\Lambda_{ma}^{(XY)} - \chi_{ma}^{(XY)}) - \chi_{mA}^{(XY)} \chi_{ma}^{(XY)}$.
-The variable $\Lambda_{mi}^{(XY)}>0$ is the multiplicative growth rate of the neo-sex-determining allele $m$ on background $i\in\{A,a\}$ without accounting for loss due to recombination ($R=0$).
-We will call  $\Lambda_{mi}^{(XY)}$ the ``haplotypic growth rate''.
-The variable $\chi_{mi}^{(XY)}>0$ is the rate at which mutant haplotypes on background $i\in\{A,a\}$ recombine onto the other $\mathbf{A}$ locus background in heterozygotes (proportional to $R$).
-We call $\chi_{mi}^{(XY)}$ the ``dissociative force", as it breaks down linkage disequilibrium.
-Both variables are listed in Table \ref{tab:haplotype_growth} for neo-Y and neo-W mutants.
+%We will consider only equilibrium frequencies of alleles, $\hat{p}^\circ_i$, and Y-bearing male gametes, $\hat{q}$, when calculating the eigenvalues.
+
+Invasion by a neo-Y or a neo-W primarily depends on the ``haplotypic growth rates'' (denoted by $\Lambda_{mi}^{(XY)}$) of the neo-sex determination allele $m$ on background $i\in\{A,a\}$ without accounting for loss due to recombination ($R=0$), see Table \ref{tab:haplotype_growth}.
+If both haplotypic growth rates are greater than one ($\Lambda_{mA}^{(XY)}, \Lambda_{ma}^{(XY)}>1$), then the new sex-determining allele invades regardless of the rate of recombination between the new sex-determining locus and the selected locus ($R$), see \nameref{app:inv_cond} for details.
+Conversely, if both haplotypic growth rates are less than one ($\Lambda_{mA}^{(XY)}, \Lambda_{ma}^{(XY)}<1$), then invasion can never occur.  
+Finally, if only one haplotypic growth rate is greater than one, the new sex-determining allele can always invade when arising at a locus that is tightly linked to the selected locus ($R\approx0$).  
+Furthermore, it can be shown that the leading eigenvalue declines with $R$, and invasion requires that $R$ is sufficiently small such that: 
+\begin{equation}\label{eq:lambdasGen}
+%\frac{\chi_{mA}}{\Lambda_{mA}-1}+\frac{\chi_{ma}}{\Lambda_{ma}-1}>0.
+\chi_{ma}^{(XY)}/\left(\Lambda_{ma}^{(XY)} - 1\right) + \chi_{mA}^{(XY)}/\left(\Lambda_{mA}^{(XY)} - 1\right) < 1
+\end{equation}
+\noindent 
+where $\chi_{mi}^{(XY)}>0$ is the rate at which mutant haplotypes on background $i\in\{A,a\}$ recombine onto the other $\mathbf{A}$ locus background in heterozygotes (proportional to $R$; we call this the ``dissociative force" as it breaks down linkage disequilibrium), see Table \ref{tab:haplotype_growth}.
+Condition \ref{eq:lambdasGen} may or may not be satisfied for the full range of locations of the new sex-determining locus, including $R=1/2$, depending on the nature of selection.  
+Interpreting this condition, if we assume that only the $mA$ haplotype would increase in frequency when $R=0$ ($\Lambda_{ma}^{(XY)}<1<\Lambda_{mA}^{(XY)}$) then the first term on the left-hand side of \eqref{eq:lambdasGen} is negative and invasion requires that growth rate of $mA$ haplotypes ($\Lambda_{mA}^{(i)}-1>0$) and the rate at which they are produced by recombination ($\chi_{ma}^{(i)}$) are sufficiently large relative to the rate of decline of $ma$ haplotypes ($1-\Lambda_{ma}^{(i)}>0$) and the rate at which $m$ and $A$ are dissociated by recombination ($\chi_{mA}^{(i)}$).
+
+%The leading eigenvalue for a rare neo-Y or neo-W allele, $m\in\{Y',W'\}$, is the largest value of $x$ that solves $x^2+ b x + c = 0$.  %$(\lambda_m^{(i)})^2+ b \lambda_m^{(i)} + c =0$. 
+%The coefficients are $b= - (\Lambda_{mA}^{(XY)} + \Lambda_{ma}^{(XY)})+(\chi_{mA}^{(XY)} + \chi_{ma}^{(XY)})$ and $c = (\Lambda_{mA}^{(XY)} - \chi_{mA}^{(XY)}) (\Lambda_{ma}^{(XY)} - \chi_{ma}^{(XY)}) - \chi_{mA}^{(XY)} \chi_{ma}^{(XY)}$, where $\Lambda_{mi}^{(XY)}>0$ is the multiplicative growth rate (which we will call the ``haplotypic growth rate'') of the neo-sex determination allele $m$ on background $i\in\{A,a\}$ without accounting for loss due to recombination ($R=0$), and $\chi_{mi}^{(XY)}>0$ is the rate at which mutant haplotypes on background $i\in\{A,a\}$ recombine onto the other $\mathbf{A}$ locus background in heterozygotes (proportional to $R$; we call this the ``dissociative force" as it breaks down linkage disequilibrium), see Table \ref{tab:haplotype_growth}.
+%In the ancestral population, it is convenient to follow the frequency of the $A$ allele among female gametes (eggs), $p^\female_X$, and among X-bearing, $p^\male_X$, and among Y-bearing, $p^\male_Y$, male gametes (sperm/pollen).
+%We also track the fraction of male gametes that are Y-bearing, $q$, which may deviate from $1/2$ due to meiotic drive in males. 
+%We will consider only equilibrium frequencies of alleles, $\hat{p}^\circ_i$, and Y-bearing male gametes, $\hat{q}$, when calculating the eigenvalues.
 
@@
 $\bar{p}^{\male}=(1-\hat{q})\hat{p}_X^\male + \hat{q}\hat{p}_Y^\male$ is the average frequency of the $A$ allele among X- and Y-bearing male gametes.
+$\hat{q}$ is the frequency of Y-bearing male gametes. 
 %      \item $R$ is the probability of recombination between loci $\mathbf{A}$ and $\mathbf{M}$.
@@
 
-The new sex-determining allele increases in frequency when rare when the largest eigenvalue is greater than one ($\lambda_m^{(XY)}>1$). 
+%The new sex-determining allele increases in frequency when rare when the largest eigenvalue is greater than one ($\lambda_m^{(XY)}>1$). 
 %If the average change in frequency of the two haplotypes that carry the $m$ allele ($Am$ and $am$) is positive, invasion will always occur, i.e., if $(\Lambda_{mA} + \Lambda_{ma})/2 > 1$ then $\Lambda > 1$.
@@
 %Since $f(\Lambda_{mA}^{(i)})$ and $f(\Lambda_{ma}^{(i)})$ are of opposite signs, the leading eigenvalue must fall between these two quantities and is the larger of them when $R = 0$ (see \nameref{file:Mathematica}).
-If both haplotypic growth rates are greater than one ($\Lambda_{mA}^{(XY)}, \Lambda_{ma}^{(XY)}>1$) then the new sex-determining allele invades regardless of the rate of recombination between the new sex-determining locus and the selected locus ($R$; see \nameref{app:inv_cond} for details).
-Conversely, if both haplotypic growth rates are less than one ($\Lambda_{mA}^{(XY)}, \Lambda_{ma}^{(XY)}<1$) then invasion can never occur.  
-Finally, if only one haplotypic growth rate is greater than one, the new sex-determining allele can always invade when arising at a locus that is tightly linked to the selected locus ($R\approx0$).  
-Furthermore, it can be shown that the leading eigenvalue declines with $R$, and invasion requires that $R$ is sufficiently small such that: 
-\begin{equation}\label{eq:lambdasGen}
+%If both haplotypic growth rates are greater than one ($\Lambda_{mA}^{(XY)}, \Lambda_{ma}^{(XY)}>1$), then the new sex-determining allele invades regardless of the rate of recombination between the new sex-determining locus and the selected locus ($R$), see \nameref{app:inv_cond} for details.
+%Conversely, if both haplotypic growth rates are less than one ($\Lambda_{mA}^{(XY)}, \Lambda_{ma}^{(XY)}<1$), then invasion can never occur.  
+%Finally, if only one haplotypic growth rate is greater than one, the new sex-determining allele can always invade when arising at a locus that is tightly linked to the selected locus ($R\approx0$).  
+%Furthermore, it can be shown that the leading eigenvalue declines with $R$, and invasion requires that $R$ is sufficiently small such that: 
+%\begin{equation}\label{eq:lambdasGen}
 %\frac{\chi_{mA}}{\Lambda_{mA}-1}+\frac{\chi_{ma}}{\Lambda_{ma}-1}>0.
-\chi_{ma}^{(XY)}/\left(\Lambda_{ma}^{(XY)} - 1\right) + \chi_{mA}^{(XY)}/\left(\Lambda_{mA}^{(XY)} - 1\right) < 1.
-\end{equation}
-\noindent 
-This condition may or may not be satisfied for the full range of locations of the new sex-determining locus, including $R=1/2$, depending on the nature of selection.  
-Interpreting this condition, if we assume that only the $mA$ haplotype would increase in frequency when $R=0$ ($\Lambda_{ma}^{(XY)}<1<\Lambda_{mA}^{(XY)}$) then the first term on the left-hand side of \eqref{eq:lambdasGen} is negative and invasion requires that growth rate of $mA$ haplotypes ($\Lambda_{mA}^{(i)}-1>0$) and the rate at which they are produced by recombination ($\chi_{ma}^{(i)}$) are sufficiently large relative to the rate of decline of $ma$ haplotypes ($1-\Lambda_{ma}^{(i)}>0$) and the rate at which $m$ and $A$ are dissociated by recombination ($\chi_{mA}^{(i)}$).
-
-We draw three main points about the generic invasion of neo-Y and neo-W mutations from Table \ref{tab:haplotype_growth}.
-First, invasion by a neo-Y (neo-W) does not directly depend on the fitness of female (male) diploids. %(for a given set of equilibrium allele frequencies).
+%\chi_{ma}^{(XY)}/\left(\Lambda_{ma}^{(XY)} - 1\right) + \chi_{mA}^{(XY)}/\left(\Lambda_{mA}^{(XY)} - 1\right) < 1.
+%\end{equation}
+%\noindent 
+%This condition may or may not be satisfied for the full range of locations of the new sex-determining locus, including $R=1/2$, depending on the nature of selection.  
+%Interpreting this condition, if we assume that only the $mA$ haplotype would increase in frequency when $R=0$ ($\Lambda_{ma}^{(XY)}<1<\Lambda_{mA}^{(XY)}$) then the first term on the left-hand side of \eqref{eq:lambdasGen} is negative and invasion requires that growth rate of $mA$ haplotypes ($\Lambda_{mA}^{(i)}-1>0$) and the rate at which they are produced by recombination ($\chi_{ma}^{(i)}$) are sufficiently large relative to the rate of decline of $ma$ haplotypes ($1-\Lambda_{ma}^{(i)}>0$) and the rate at which $m$ and $A$ are dissociated by recombination ($\chi_{mA}^{(i)}$).
+
+We draw three main points about the generic invasion of neo-Y and neo-W mutations from Table \ref{tab:haplotype_growth}:
+(1) invasion by a neo-Y (neo-W) does not directly depend on the fitness of female (male) diploids. %(for a given set of equilibrium allele frequencies).
 This is because a dominant neo-Y (neo-W) is always found in males (females), and therefore the frequency of the neo-Y (neo-W), $m$, only changes in males (females), Fig \ref{fig:model_outline}C,D.
-Second, Fisherian sex-ratio selection will favour the spread of a neo-W and inhibit the spread of a neo-Y if the ancestral zygotic sex ratio is biased towards males (i.e., the first factor of the $\Lambda_{mi}^{(XY)}$ is greater than one for a neo-W and less than one for a neo-Y when $\zeta>1/2$), as might occur when the ancestral sex-determining locus is linked to a locus experiencing meiotic drive in males, for example.
+(2) Fisherian sex-ratio selection will favour the spread of a neo-W and inhibit the spread of a neo-Y if the ancestral zygotic sex ratio is biased towards males (i.e., the first factor of the $\Lambda_{mi}^{(XY)}$ is greater than one for a neo-W and less than one for a neo-Y when $\zeta>1/2$).
+%, as might occur when the ancestral sex-determining locus is linked to a locus experiencing meiotic drive in males, for example.
 However, the spread of a neo-Y (neo-W) also depends on the male (female) fitness of associated alleles (see terms involving equilibrium allele frequencies, $\hat{p}$'s), including haploid selection that additionally biases the sex ratio.
@@
 %
-And thirdly, Table \ref{tab:haplotype_growth} also shows that
+(3) Table \ref{tab:haplotype_growth} shows that
 %\vspace{0.5cm}
@@
 cis- and trans-GSD transitions are qualitatively different.
-This is because, in an ancestrally XY system, a gamete with the neo-Y always pairs with a female gamete containing an X (Fig \ref{fig:model_outline}C).
-By contrast, a gamete with a neo-W can pair with an X- or Y-bearing male gamete (Fig \ref{fig:model_outline}D).
-Consequently, neo-W-bearing females obtain a different frequency of $A$ alleles from mating (when $\hat{p}_X^\male \neq \hat{p}_Y^\male$) compared to ancestral ($MM$) females, which can inhibit or favour its spread.
-
-In order to explicitly determine the conditions under which a new sex-determining allele spreads, we next calculate the equilibrium frequency of the $A$ allele (i.e., $\hat{p}^\female_X$, $\hat{p}^\male_X$, and $\hat{p}^\male_Y$) and Y-bearing male gametes ($\hat{q}$) in the ancestral population.
+This is because, in an ancestrally XY system, a gamete with the neo-Y always pairs with a female gamete containing an X, Fig \ref{fig:model_outline}C.
+By contrast, a gamete with a neo-W can pair with an X- or Y-bearing male gamete, Fig \ref{fig:model_outline}D.
+Consequently, neo-W-bearing females obtain a different frequency of $A$ alleles from mating (when $\hat{p}_X^\male \neq \hat{p}_Y^\male$) compared to ancestral ($MM$) females. 
+This can inhibit or favour the spread of a neo-W.
+
+In order to explicitly determine the conditions under which a new sex-determining allele spreads, we must calculate the equilibrium frequency of the $A$ allele (i.e., $\hat{p}^\female_X$, $\hat{p}^\male_X$, and $\hat{p}^\male_Y$) and Y-bearing male gametes ($\hat{q}$) in the ancestral population.
 Because only the $\mathbf{A}$ locus experiences selection directly, any deterministic evolution requires that there be a polymorphism at the $\mathbf{A}$ locus. 
@@
 Such polymorphisms can be maintained by heterozygote advantage, sexually-antagonistic selection, ploidally-antagonistic selection, or a combination~\cite{Immler:2012tl}.
-We analytically calculate equilibrium frequencies using two alternative simplifying assumptions: 
-(1) the $\mathbf{A}$ locus is tightly linked to the non-recombining region around the ancestral sex-determining locus ($r \approx 0$) or (2) selection is weak relative to recombination ($s^\circ$, $t^\circ$, $\alpha_{\Delta}^\circ$ $<<$ $r$).
-The ancestral equilibria and their stability conditions are given in \nameref{app:eq_stab}.
+We can analytically calculate the allele frequency of the $A$ allele using two alternative simplifying assumptions: 
+(a) the $\mathbf{A}$ locus is tightly linked to the non-recombining region around the ancestral sex-determining locus ($r \approx 0$) or (b) selection is weak relative to recombination ($s^\circ$, $t^\circ$, $\alpha_{\Delta}^\circ$ $<<$ $r$).
 
@@
 
+The ancestral equilibrium allele frequencies and their stability conditions are given in \nameref{app:eq_stab}. 
 When there is complete linkage between the ancestral sex-determining locus and the $\mathbf{A}$ locus ($r=0$), either the $A$ allele or the $a$ allele must be fixed in gametes containing a Y allele. 
@@
 
-We find that a neo-Y allele can never invade an ancestral XY system that already has tight linkage with the locus under selection ($\lambda_{Y'}^{(XY)} \leq 1$ when $r=0$; for details see \nameref{file:Mathematica}).
+We find that a neo-Y allele can never invade an ancestral XY system that already has tight linkage with the locus under selection ($\lambda_{Y'}^{(XY)} \leq 1$ when $r=0$, for details see \nameref{file:Mathematica}).
 %When $R=0$, a neo-Y haplotype with the same allele as the ancestral Y is neutral ($\Lambda_{Y'a}^{(XY)}=1$) and does not change in frequency.
@@
 
-Neo-W alleles, on the other hand, can invade an ancestral XY system because, under some conditions, the neo-W can become more strongly specialized for females (the full invasion conditions are given in \nameref{app:inv_cond}; equations \ref{Binvasion} and \ref{Ainvasion}).
+Neo-W alleles, on the other hand, can invade an ancestral XY system because, under some conditions the W can become more strongly specialized for females (the full invasion conditions are given in \nameref{app:inv_cond}; equations \ref{Binvasion} and \ref{Ainvasion}).
 Thus,
@@
 %\textbf{selection on loci within the non-recombining region around the sex-determining locus ($r\approx0$) allows the invasion of less closely linked sex-determining alleles ($r<R\leq1/2$) during a trans-GSD transition} (XY $\leftrightarrow$ ZW).
-\textbf{Selection on loci in or near the non-recombining region around the sex-determining locus ($r\approx0$) prevents cis-GSD transitions (XY $\leftrightarrow$ XY, ZW $\leftrightarrow$ ZW) but can spur trans-GSD transitions (XY $\leftrightarrow$ ZW), which weaken sex-linkage.}
+\textbf{Selection on loci in or near the non-recombining region around the sex-determining locus ($r\approx0$) prevents cis-GSD transitions (XY $\leftrightarrow$ XY, ZW $\leftrightarrow$ ZW) but can spur trans-GSD transitions (XY $\leftrightarrow$ ZW).}
 \vspace{0.5cm}
@@
 The conditions become more restrictive, however, with increasing recombination ($R$) between the new sex-determining locus and the selected locus.  
-The invasion of completely unlinked neo-W alleles ($R = 1/2$) can occur with overdominance in males or with haploid selection (e.g., when male drive is opposed by diploid selection, as in \cite{Kozielska:2010vm}) but is not possible with only sexually-antagonistic selection where selection is directional in each diploid sex (see \nameref{file:Mathematica}).
-Here, we focus on cases where there is no haploid selection (Fig \ref{fig:SexAntagTighter}A) and discuss the additional effect of haploid selection in \nameref{app:inv_cond} (see also Conclusion 1C). 
+The invasion of completely unlinked neo-W alleles ($R = 1/2$) can occur with overdominance in males or with haploid selection (e.g., a case with male drive opposed by diploid selection in \cite{Kozielska:2010vm}) but is not possible with only sexually-antagonistic selection where selection is directional in each diploid sex (see \nameref{file:Mathematica}).
+Here, we focus on cases where there is no haploid selection (Fig \ref{fig:SexAntagTighter}A) and discuss the additional effect of haploid selection in \nameref{app:inv_cond}. 
 %Essentially, neo-W alleles are able to invade (even with $R>r$) because the ancestral X experiences selection in males. 
@@
 Wherever both haplotypic growth rates are greater than one, invasion by a neo-W is expected regardless of its linkage with the selected locus (i.e., for any $R$, see \nameref{fig:positionOverdominance} and \nameref{fig:temporalOverdominance} for examples).
-As a consequence, evolution can favor a new sex determination system on a different chromosome, despite the fact that this unlinks the sex-determining locus from the selected locus.
+As a consequence, evolution can favor a new sex determination system on a different chromosome, despite the fact that this unlinks the sex determination locus from the selected locus.
 
@@
 \noindent\textit{Conclusion 1B:}
-\textbf{With tight linkage between a selected locus and the ancestral sex-determining locus ($r\approx0$), selection to better specialize on the ancestrally-non-heterogametic sex can drive trans-GSD transitions (XY $\leftrightarrow$ ZW) that weaken sex-linkage ($r<R\leq1/2$; potentially even shifting sex determination to a different chromosome) and sometimes lead to polymorphic sex-determination systems.}
+\textbf{With tight linkage between a selected locus and the ancestral sex determination system ($r\approx0$), selection to better specialize on the ancestrally-non-heterogametic sex can drive trans-GSD transitions (XY $\leftrightarrow$ ZW) that weaken sex-linkage ($r<R\leq1/2$; potentially even shifting sex determination to a different chromosome) and/or lead to polymorphic sex-determination systems.}
 \vspace{0.5cm}
@@
 \textbf{
-With tight linkage between a selected locus and the ancestral sex-determining locus ($r\approx0$), haploid selection allows trans-GSD transitions (XY $\leftrightarrow$ ZW) that weaken sex-linkage ($r<R\leq1/2$; potentially even shifting sex determination to a different chromosome) even when selection is sexually-antagonistic with directional selection in each diploid sex.
-These trans-GSD transitions equalize the sex ratio.
+Haploid selection allows trans-GSD transitions that weaken sex-linkage ($r<R\leq1/2$; potentially even shifting sex determination to a different chromosome) even when selection is sexually-antagonistic with directional selection in each diploid sex.
+With initially tight linkage, these transitions equalize the sex ratio by reducing linkage to alleles under haploid selection.
 }
@@
 
-When selection is weak relative to recombination, the absence of haploid selection ($t^\circ=\alpha^\circ_{\Delta}=0$), implies that the spread of a neo-W is equivalent to the spread of a neo-Y ($\lambda_{W'}^{(XY)}=\lambda_{Y'}^{(XY)}$), such that trans-GSD transitions can also occur only if the new sex-determining locus is more closely linked to a locus under selection ($R<r$), as found by \cite{vanDoorn:2010hu}.
+Without haploid selection ($t^\circ=\alpha^\circ_{\Delta}=0$), the spread of a neo-W is equivalent to the spread of a neo-Y ($\lambda_{W'}^{(XY)}=\lambda_{Y'}^{(XY)}$), when selection is weak relative to recombination, such that trans-GSD transitions can also occur only if the new sex-determining locus is more closely linked to a locus under selection ($R<r$), as found by \cite{vanDoorn:2010hu}.
 When there is haploid selection, invasion also typically occurs when the neo-W is more closely linked to the selected locus than the ancestral sex-determining region (Fig \ref{fig:Combination_Centimorgans}).
@@
 \noindent\textit{Conclusion 2A:}\
-\textbf{New sex-determining alleles (causing cis- \textit{or} trans-GSD transitions) can spread if they arise morely closely linked with a locus that experiences selection than the ancestral-sex-determining locus is ($R<r$).}
+\textbf{New sex-determining alleles (causing cis- \textit{or} trans-GSD transitions) can spread if they arise in closer linkage with a locus that experiences selection than the ancestral-sex-determining locus ($R<r$).}
 \vspace{0.5cm}
@@
 \noindent\textit{Conclusion 2B:}\
-\textbf{New sex-determining alleles (causing trans-GSD transitions, XY $\leftrightarrow$ ZW) can spread even if they arise less closely linked with a locus that experiences selection than the ancestral-sex-determining locus is ($r<R$), requiring haploid selection and some initial sex-linkage ($r<1/2$) as necessary conditions.}
+\textbf{New sex-determining alleles (causing trans-GSD transitions) can spread if they arise in looser linkage with a locus that experiences selection than the ancestral-sex-determining locus ($r<R$), requiring haploid selection as a necessary conditions.}
 \vspace{0.5cm}
@@
 %Indeed, invasion typically occurs when the neo-W is more closely linked to the selected locus than the ancestral sex-determining region (Fig \ref{fig:Combination_Centimorgans}).
-To clarify the parameter space under which invasion occurs with weak selection ($\lambda_{W'}^{(XY)}>1$), we focus on cases where dominance coefficients are equal in the two sexes, $h^\female=h^\male$, and haploid selection only occurs in one sex (e.g., during male meiosis only).
-Table \ref{tab:specialcases} then gives the conditions required for unlinked ($R=1/2$) neo-W invasion when there is some ancestral sex-linkage ($r<1/2$; e.g., the selected locus is on the ancestral sex chromosome and the novel sex-determining locus arises on an autosome).
-These special cases indicate that neo-W invasion occurs for a large fraction of the parameter space, even though the neo-W uncouples the sex-determining locus from a locus under selection. 
-Fig \ref{fig:Combination_Centimorgans} then demonstrates that under these conditions neo-W alleles can spread when they are more loosely \textit{or} more closely linked to the locus that experiences haploid selection (c.f., Fig \ref{fig:SexAntagTighter}A for diploid sexually-antagonistic selection alone).
-%When the neo-W is more closely linked to the haploid selected locus its invasion increases (or creates anew) sex-ratio bias (Fig \ref{fig:SexRatioBad}A).
-%Under the same selection scenario (drive in males), a neo-Y would invade an ancestrally ZW system
-% shows that when a neo-W invades that increases linkage with a haploid selected locus, it biases the sex-ratio.
-%, while those that decrease sex-linkage equalize the sex-ratio. 
-%When sex-linkage decreases ($R>r$), neo-W alleles can benefit from Y-associated alleles that have higher fitness in the female diploid phase but then dissociate from these alleles through recombination before any subsequent haploid selection.
+To clarify the parameter space under which invasion occurs despite looser sex-linkage ($\lambda_{W'}^{(XY)}>1$ despite $R>r$; Conclusion 2B), we focus on the special case where $R=1/2$ and $r<1/2$ (e.g., the selected locus is on the ancestral sex chromosome and the novel sex-determining locus arises on an autosome).
+In Table \ref{tab:specialcases} we give the conditions where invasion occurs when we further assume that haploid selection only occurs in one sex \textcolor{red}{(e.g., during male meiosis only)} and dominance coefficients are equal in the two sexes, $h^\female=h^\male$.
+These special cases indicate that neo-W invasion occurs for a large fraction of the parameter space, even if the neo-W uncouples the sex-determining locus from a locus under selection. 
+Surprisingly, neo-W alleles can spread when they are more closely \textit{or} more loosely linked to a locus that experiences haploid selection, as shown in Fig \ref{fig:Combination_Centimorgans} (c.f., Fig \ref{fig:SexAntagTighter}A for diploid sexually-antagonistic selection alone).
+In Fig \ref{fig:SexRatioBad}, we also show examples of trans-GSD transitions in sex determination during which linkage with a haploid selected locus increases \textit{or} decreases, increasing or decreasing sex-ratio bias.
+When sex-linkage decreases ($R>r$), neo-W alleles can benefit from Y-associated alleles that have higher fitness in the female diploid phase but then dissociate from these alleles through recombination before any subsequent haploid selection.
 
@@
 
-%Previous research has shown that when the ancestral sex-determining locus is linked to a locus that experiences haploid selection (e.g., meiotic drive), alleles at a new, unlinked sex-determining locus can invade and restore equal sex ratios~\cite{Kozielska:2010vm}.
-We can also compare transitions in genetic sex-determination where sex-ratio bias increases, decreases, or remains equal. 
-For example, if there is meiotic drive in males only ($\alpha^\male_\Delta \neq 0$, $\alpha^\female_\Delta=0$), without gametic competition ($t^\female=t^\male=0$) the zygotic sex ratio is initially biased only when the ancestral sex-determining system is XY (Fig \ref{fig:model_outline}A and Fig \ref{fig:SexRatioBad}A) and not ZW (Fig \ref{fig:SexRatioBad}B).
-%If the ancxestral sex-determining system is ZW, the zygotic sex ratio will be 1:1 because diploid sex is determined by the proportion of Z-bearing versus W-bearing eggs and meiosis in females is fair (Fig \ref{fig:Combination_Turnover}D).
-If Fisherian sex-ratio selection were dominant, we would thus expect a difference in the potential for XY to ZW and ZW to XY transitions. 
-%However, to leading order with selection weak relative to recombination, we find that sex-ratio selection favours the spread of a neo-W by an amount equl to the spread of a neo-Y into a ZW system (relabeling XY as the heterogametic sex and reversing the labels of males and females in Table \ref{tab:specialcases})
-However, invasion by a neo-W allele into an XY system and invasion by a neo-Y allele into a ZW system occur under the same conditions ($\lambda_{Y'}^{(XY)} = \lambda_{W'}^{(ZW)}$ and $\lambda_{W'}^{(XY)}=\lambda_{Y'}^{(ZW)}$, at least to order $\epsilon^2$), implying that,% surprisingly,
-\vspace{0.5cm}
-
-\noindent\textit{Conclusion 3:}
-\textbf{When selection is weak relative to recombination, the presence of haploid selection equally favors the spread of new sex determination systems that reduce sex-ratio bias (benefiting from Fisherian sex ratio selection) or generate a sex-ratio bias (benefiting from associations with selected alleles).
-}
-\vspace{0.5cm}
-%\noindent\textcolor{red}{\textit{Conclusion 3:}
-%\textbf{when selection is weak relative to recombination, sex-ratio selection is exactly equal in magnitude to the selection imposed by associations with selected alleles. } }
-%%\textcolor{red}{[new result]}
-%\vspace{0.5cm}
-
-\noindent For example, in Fig \ref{fig:SexRatioBad}A neo-W alleles invade an ancestral-XY system where females are initially rare, equalizing the sex ratio (as occurs in \cite{Kozielska:2010vm}).
-However, Fig \ref{fig:SexRatioBad}B shows that a neo-Y can invade the resulting ZW system under the same conditions. 
-When $R<1/2$, the invading neo-Y becomes associated with the male meiotic drive allele and the zygotic sex ratio actually evolves to become male-biased (as occurs in \cite{Ubeda:2015fx}, beginning from ESD).
-In this case, the neo-Y spreads because it is often found in males and can, if it carries the driven allele $a$, benefit from haploid selection in males (Fig \ref{fig:SexRatioBad}B).
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \centering
-\includegraphics[width=\linewidth]{../Plots/Temporal_SR.eps}
+\includegraphics[width=\linewidth]{../Plots/Temporal_SR}
 \caption{
@@
 
+%Previous research has shown that when the ancestral sex-determining locus is linked to a locus that experiences haploid selection (e.g., meiotic drive), alleles at a new, unlinked sex-determining locus can invade and restore equal sex ratios~\cite{Kozielska:2010vm}.
+Our model allows us to analytically compare transitions in genetic sex-determination where sex-ratio bias increases, decreases, or remains equal. 
+For example, if there is meiotic drive in males only ($\alpha^\male_\Delta \neq 0$, $\alpha^\female_\Delta=0$), without gametic competition ($t^\female=t^\male=0$) the zygotic sex ratio is initially biased only when the ancestral sex-determining system is XY (Fig \ref{fig:model_outline}A and Fig \ref{fig:SexRatioBad}A) and not ZW (Fig \ref{fig:SexRatioBad}B).
+%If the ancxestral sex-determining system is ZW, the zygotic sex ratio will be 1:1 because diploid sex is determined by the proportion of Z-bearing versus W-bearing eggs and meiosis in females is fair (Fig \ref{fig:Combination_Turnover}D).
+If Fisherian sex-ratio selection were dominant, we would thus expect a difference in the potential for XY to ZW and ZW to XY transitions. 
+%However, to leading order with selection weak relative to recombination, we find that sex-ratio selection favours the spread of a neo-W by an amount equl to the spread of a neo-Y into a ZW system (relabeling XY as the heterogametic sex and reversing the labels of males and females in Table \ref{tab:specialcases})
+However, invasion by a neo-W allele into an XY system and invasion by a neo-Y allele into a ZW system occur under the same conditions ($\lambda_{Y'}^{(XY)} = \lambda_{W'}^{(ZW)}$ and $\lambda_{W'}^{(XY)}=\lambda_{Y'}^{(ZW)}$, at least to order $\epsilon^2$), implying that,% surprisingly,
+\vspace{0.5cm}
+
+\noindent\textit{Conclusion 3:}
+\textbf{When selection is weak relative to recombination, the presence of haploid selection equally favors the spread of new sex determination systems that reduce sex-ratio bias (benefiting from Fisherian sex ratio selection) or generate a sex-ratio bias (benefiting from drive)" }
+\vspace{0.5cm}
+%\noindent\textcolor{red}{\textit{Conclusion 3:}
+%\textbf{when selection is weak relative to recombination, sex-ratio selection is exactly equal in magnitude to the selection imposed by associations with selected alleles. } }
+%%\textcolor{red}{[new result]}
+%\vspace{0.5cm}
+
+\noindent For example, in Fig \ref{fig:SexRatioBad}A neo-W alleles invade an ancestral-XY system where females are initially rare, equalizing the sex ratio (as occurs in \cite{Kozielska:2010vm}).
+However, Fig \ref{fig:SexRatioBad}B shows that a neo-Y can invade the resulting ZW system under the same conditions. 
+When $R<1/2$, the invading neo-Y becomes associated with the male meiotic drive allele and the zygotic sex ratio actually evolves to become male-biased (as occurs in \cite{Ubeda:2015fx}, beginning from ESD).
+In this case, the neo-Y spreads because it is often found in males and can, if it carries the driven allele $a$, benefit from haploid selection in males (Fig \ref{fig:SexRatioBad}B).
+
 %
@@
 
-While equalizing the sex ratio and benefiting from associations with selected alleles are two primary reasons why haploid selection spurs sex chromosome transitions, more complex situations also arise.
+While equalizing the sex ratio and benefiting from drive are two primary reasons why haploid selection spurs sex chromosome transitions, more complex situations also arise.  
 For example with $R=1/2$ in Fig \ref{fig:SexRatioBad}B (green curve), the neo-Y allele spreads despite the fact that it cannot benefit from drive because free recombination moves it randomly between driven and non-driven backgrounds.
@@
 
-We next consider the case where the new sex-determining allele, $m$, causes sex to be determined probabilistically or by heterogeneous environmental conditions (environmental sex determination, ESD).
-In particular, we assume individuals carrying allele $m$ develop as females with probability $k\in(0,1)$.
+We next consider the case where the new sex-determining mutation, $m$, causes sex to be determined probabilistically or by heterogeneous environmental conditions (environmental sex determination, ESD), with individuals carrying allele $m$ developing as females with probability $k$.
 %\textcolor{red}{In our deterministic model this means the fraction female is exactly $k$, even when $m$ is rare (exploring the effect of the variance induced by ESD would also be interesting).}
 In our deterministic model this means the fraction female in the subpopulation containing $m$ is exactly $k$, even when $m$ is rare (i.e., ESD does not introduce any additional variance in sex determination).
-We also assume that the environmental conditions that determine sex do not differentially affect the fitness of males versus females. 
-Such correlations can favour environmental sex-determining systems by allowing each sex to be produced in the environment in which it has highest fitness; in the absence of these correlations previous theory would predict that ESD is favoured when it produces more equal sex ratios than the ancestral system (see reviews by~\cite{Charnov:1982wg,Bull:1983vi,West:2009we}).
+Here, we assume that the environmental conditions that determine sex does not differentially affect the fitness of males versus females. 
+Such correlations can favour environmental sex-determining systems by allowing each sex to be produced in the environment in which it has highest fitness; in the absence of these correlations, previous theory would predict that ESD is favoured when it produces more equal sex ratios than the ancestral system (see reviews by~\cite{Charnov:1982wg,Bull:1983vi,West:2009we}).
 %(e.g., maternal condition, mate quality, age, or host size)
@@
 As discussed above, $\lambda_{Y'\rvert R=1/2}^{(XY)}$ is necessarily less than one (cis-GSD transition), but $\lambda_{W'\rvert R=1/2}^{(XY)}$ (trans-GSD transition) can be greater than one if there is haploid selection (see Conclusion 2B).
-That is, with haploid selection, an allele causing environmental-sex-determination can invade an ancestrally-XY system because it generates females that are either rare or have high fitness, in the same manner as a neo-W (likewise, ESD invades a ZW system for the same reasons a neo-Y can).
+That is, with haploid selection, an allele causing environmental-sex-determination can invade an ancestrally-XY system because it generates females that are either rare or have high fitness, in the same manner as a neo-W (likewise, ESD invades a ZW system for the same reasons as a neo-Y can).
 %An important result from Eq \eqref{eq:lambda_ESD} is that ESD can invade if there is haploid selection. 
@@
 When the ancestral sex-determining system is ZW the sex ratio is not biased.
-Nevertheless, ESD is equally likely to invade both XY (through $\lambda_{W'}^{(XY)}$) and ZW (through $\lambda_{Y'}^{(ZW)}$) systems, equalizing the zygotic sex ratio in the former case but not in the latter.
+Nevertheless, ESD is equally likely to invade both XY and ZW systems, equalizing the zygotic sex ratio in the former case (through $\lambda_{W'}^{(XY)}$) but not in the latter (through $\lambda_{Y'}^{(ZW)}$).
 %This is again because haploid selection can facilitate the turnover of sex chromosomes either through sex-ratio biases or through associations between the new sex determining region with selected alleles.
@@
 In addition, we note that ESD may not invade, even if the sex ratio is initially biased (e.g., with drive in males only, $r<1/2$, $h^\female=h^\male$, and $s^\female s^\male<0$, then $\lambda_{W'}^{(XY)}<1$, see Table \ref{tab:specialcases}).
-We conclude that, as with neo-W and neo-Y mutations:
+We conclude that, as with neo-W and neo-Y loci:
 \vspace{0.5cm}
@@
 
-New sex-determination systems are typically expected to spread when they equalise the sex ratio and/or when they increase linkage with loci that experience sex-differences in selection~\cite{Blaser2012, vanDoorn2014re}.
-In accordance with the latter mechanism, we find that sex-differences in selection at the haploid stage can favour trans-GSD transitions that tighten sex-linkage (Conclusion 2A).
-%, as exemplified in~\cite{Ubeda:2015fx} for ESD-GSD transitions.
-However, we also find that trans-GSD transitions can be favoured in cases where linkage with the sex-determining locus is actually weakened (Conclusions 1A-1C \& 2B, Fig \ref{fig:SexAntagTighter} \& \ref{fig:regionplots}), especially when there is haploid selection (Conclusion 2B, Figs \ref{fig:Combination_Centimorgans} \& \ref{fig:SexRatioBad}).
+New sex determination systems are typically expected to spread when they equalise the sex ratio and/or when they increase linkage with loci that experience sex-differences in selection~\cite{Blaser2012, vanDoorn2014re} (including sex-differences at the haploid stage, Conclusion 2A and~\cite{Ubeda:2015fx}).
+However, we find that trans-GSD transitions can be favoured in cases where linkage with the sex-determining locus is actually weakened (Conclusions 1 \& 2B, Fig \ref{fig:SexAntagTighter}), especially when there is haploid selection (Conclusion 2B, Figs \ref{fig:Combination_Centimorgans} \& \ref{fig:SexRatioBad}).
 Furthermore, we show that the spread of new sex-determination systems is not dominated by selection to balance the sex ratio (Conclusions 3 \& 4, Fig \ref{fig:SexRatioBad}).
@@
 %What we would like to stress is that sex-ratio selection alone cannot predict when new sex-determining systems can evolve.
-Significantly, with weak selection, we find that there is no difference in conditions allowing XY to ZW and ZW to XY transitions (Conclusion 3) %, indicating that transitions in sex determination are not predominantly predicted by their effect on the sex ratio (i.e., the sex-ratio bias created by male haploid selection facilitates the spread of a neo-W allele into an XY system to the same degree that male haploid selection drives the spread of a neo-Y into a ZW system with a 1:1 sex ratio).
+Significantly, with weak selection, we find that there is no difference in conditions allowing XY to ZW and ZW to XY transitions (Conclusion 3)%, indicating that transitions in sex determination are not predominantly predicted by their effect on the sex ratio (i.e., the sex-ratio bias created by male haploid selection facilitates the spread of a neo-W allele into an XY system to the same degree that male haploid selection drives the spread of a neo-Y into a ZW system with a 1:1 sex ratio).
 %An asymmetry can develop when sex-linkage is tight (e.g., Fig \ref{fig:Combination_Centimorgans} near -25cM and 25cM) but under most circumstances we do not predict asymmetry between XY to ZW and ZW to XY transitions despite the presence/absence of sex-ratio selection.
@@
 Even in animal and plant species that have much larger and more conspicuous diploid phases than haploid phases, many loci have been shown to experience haploid selection through gamete competition and/or meiotic drive~\cite{Mulcahy:1996ha,JOSEPH:2004haa, Lalanne2004,Ubeda:2005gw,Fishman2005,Leppala2008,Leppala2013,Didion2015,Didion2016, Lindholm:2016cw}.
-In some cases, meiotic drive (Burt and Trivers, 2006, Chapter 6~\cite{Burt:2006}) or gametic competition~\cite{Lloyd:1974tz,Conn:1981uw,Stehlik:2005ul,Stehlik:2006to,Field:2012fd,Field:2013cc} among X- and Y-bearing gametes is known to cause sex-ratio biases.
+In some cases, meiotic drive (Burt and Trivers, 2006, Chapter 6~\cite{Burt:2006}) or gametic competition~\cite{Lloyd:1974tz,Conn:1981uw,Stehlik:2005ul,Stehlik:2006to,Field:2012fd,Field:2013cc} among X- and Y-bearing gametes is known to cause sex ratio biases.
 %Segregation distortion provides putative evidence of haploid selection and can sometimes be attributed to meiotic drive and/or gametic competition~\cite{Lalanne2004,Fishman2005,Leppala2008,Leppala2013,Didion2015,Didion2016}.
@@
 In animals, recent studies have demonstrated that sperm competition, even within a single ejaculate, can alter haploid allele frequencies and increase offspring fitness~\cite{Immler:2014im,Alavioon2017}.
-Although precise estimates are uncertain, a relatively small proportion of all genes are thought to be expressed and selected during competition in animal sperm~\cite{Zheng:2001fi,JOSEPH:2004haa,Vibranovski:2010et}.
-However, expression is not required for haploid selection if the fitness of a gamete depends on its ability to condense DNA~\cite{Immler2018}.   
-In plants haploid selection may be particularly important. %due to the presence of a multicellular haploid stage. 
+Nevertheless, although precise estimates are uncertain, a relatively small proportion of all genes are thought to be \textcolor{red}{expressed} and selected during competition in animal sperm~\cite{Zheng:2001fi,JOSEPH:2004haa,Vibranovski:2010et}.
+In plants, however, haploid selection may be particularly important. %due to the presence of a multicellular haploid stage. 
 For example, 60-70\% of all genes are expressed in the male gametophyte, and these genes exhibit stronger signatures of selection than randomly-chosen genes~\cite{Borg:2009jpa,Arunkumar:2013iq,Gossmann:2014dua}.
@@
 In addition, Y-linked genes are over-expressed relative to X-linked genes in pollen (but not in flower buds or leaves). 
-This suggests that the spread of neo-Y chromosomes in this clade could have been favoured through linkage with haploid selected genes rather than those under sexual antagonism. 
+This suggests that the spread of neo-Y chromosomes in this clade could have been favoured through linkage with haploid selected genes. 
 %maybe add a flag here for switching to clade-level expectations:
@@
 Assuming that transitions from dioecy to hermaphroditism (equal parental investment in male and female gametes) are favoured in a similar manner to the ESD examined here (equal probability of zygotes developing as males or females), our results suggest that competition among haploid pollen could drive transitions between dioecy and hermaphroditism, which are frequent in plants~\cite{Kafer2017, Goldberg2017}.
-To further examine this link, future theory could simultaneously include inbreeding, haploid selection, and sex chromosomes when investigating transitions between dioecy and hermaphroditism. 
+To further examine this link, future theory could include haploid selection and sex chromosomes when investigating transitions between dioecy and hermaphroditism. 
 Future empirical studies could look for evidence of haploid selection acting on former sex chromosomes in hermaphroditic species (e.g., a study such as \cite{Sandler264382} on ancestral, rather than derived, sex chromosomes).
@@
 In support of this hypothesis, researchers have identified genes on recently derived sex chromosomes that might be under sexually-antagonistic selection~\cite{Lindholm:2002dw,Tripathi:2009cw,Ser:2010iq}.
-However, we show that, if selected loci are tightly linked to the ancestral sex-determining locus, they can drive trans-GSD transitions which reduce sex-linkage (Conclusions 1A-1C \& 2B), thus widening the range of genomic locations that could be driving observed trans-GSD transitions.
+However, we show that, if selected loci are tightly linked to the ancestral sex-determining locus, they can drive trans-GSD transitions during which sex-linkage is reduced (Conclusion 1), thus widening the genomic locations that could be driving trans-GSD transitions.
 In addition, we find that polymorphic sex determining systems (X, Y, and neo-W alleles all segregating) can be maintained when a selected locus is tightly linked to the ancestral sex-determining system (e.g., \nameref{fig:freqAll}B and \nameref{fig:freqAll}C), which is not possible with loose linkage~\cite{vanDoorn:2010hu}.
@@
 
-Our tight linkage result, in particular the prediction that invasion can lead to polymorphic sex determination, is consistent with empirical data from species in which new feminizing mutations are found segregating with ancestral XY loci.
+Our tight linkage results are consistent with empirical data from species in which new feminizing mutations are found alongside ancestral XY loci. 
 For example, in the platyfish (\textit{Xiphophorus maculatus}), X,Y, and W alleles segregate at one locus (or two closely-linked loci) near to potentially sexually-antagonistic genes for pigmentation and sexual maturity~\cite{Kallman1965,Kallman1968, Volff2001, Schultheis2006}.
-Furthermore, several rodent species maintain \textcolor{red}{dominant?} feminizing alleles along with the ancestral X and Y sex-determination alleles (reviewed in~\cite{Fredga1994}). 
+Furthermore, several rodent species maintain feminizing alleles along with the ancestral X and Y sex-determination alleles (reviewed in~\cite{Fredga1994}). 
 In nine \textit{Akadon} rodent species, it appears that male-determining-\textit{sry} expression is suppressed by an autosomal feminizing allele (a neo-W allele), creating XY females~\cite{Bianchi2002,Sanchez2010}.
-XY females have increased fitness relative to XX females~\cite{Hoekstra2001}. 
-However, it is not yet clear whether loci linked to the feminizing factor or the ancestral Y cause this effect. 
-Most convincingly, in \textit{Mus minutoides}, females can have XX, XX$^\ast$ or X$^\ast$Y genotypes~\cite{Veyrunes2010}. 
-Previous theory would predict that the dominant X$^\ast$ chromosome (potentially an autosome that has fused with the sex chromosome) harbours female beneficial alleles, driving its spread. 
+XY females have increased fitness relative to XX females~\cite{Hoekstra2001}. However, it is not yet clear whether loci linked to the feminizing factor or the ancestral Y cause this effect. 
+Most convincingly, in \textit{Mus microtoides}, females can have XX, XX$^\ast$ or X$^\ast$Y genotypes~\cite{Veyrunes2010}. 
+Previous theory would predict that the X$^\ast$ chromosome (potentially an autosome that has fused with the sex chromosome) harbours female beneficial alleles, driving its spread. 
 However, XX and XX$^\ast$ females have similar fitness, whereas X$^\ast$Y female fitness is enhanced~\cite{Saunders2014,Saunders2016, Veyrunes2017}. 
@@
 %Limitation 1: DEGENERATE Y
-Our models assume that sex-determining alleles do not experience direct selection except via their associations with sex and selected alleles.
+We note that we assume that sex-determining alleles do not experience direct selection except via their associations with sex and selected alleles.
 However, in some cases, there may be significant degeneration around the sex-limited allele (Y or W) in the ancestral sex-determining region because recessive deleterious mutations and/or deletions accumulate in the surrounding non-recombining regions~\cite{Rice:1996ke,Charlesworth:2000cc,Bachtrog:2006ed,Marais:2008hm}.
@@
 %While not explicitly studied, we also predict that Y or W degeneration would prevent fixation of the new sex-determining genes considered here.
-Degeneration around the Y or W could explain why trans-GSD transitions are not observed to be much more common than cis-GSD transitions \textcolor{red}{(citation?)} despite the fact that our models demonstrate that they are favoured under a wider range of conditions, especially with haploid selection.
+Degeneration around the Y or W could explain why trans-GSD transitions are not observed to be much more common than cis-GSD transitions despite the fact that our models demonstrate that they are favoured under a wider range of conditions, especially with haploid selection.
 For example, there are a dozen sex chromosome configurations among Dipteran species but only one transition between male and female heterogamety~\cite{Vicoso:2015hf}, but Y degeneration or absence is also very common among \textit{Diptera}~\cite{Vicoso:2015hf}.
@@
 We have shown that tight sex-linkage and haploid selection can drive previously unexpected transitions between sex-determining systems.
-In particular, both can select for new sex-determining loci that are more loosely linked to loci under selection (Conclusions 1A-1C \& 2B). 
+In particular, both can select for new sex-determining loci that are more loosely linked to loci under selection (Conclusions 1 \& 2B). 
 In addition, haploid selection can cause transitions in GSD analogous to those caused by purely sexually-antagonistic selection, eliminating the need for differences in selection between male and female diploids (Conclusion 2A).
 We conclude that haploid selection should be considered as a pivotal factor driving transitions between sex-determining systems. 
-Further, transitions involving haploid selection can be driven by sex-ratio selection or cause sex-ratio biases to evolve; to leading order, selection to balance the sex ratio and the benefits of hitch-hiking with haploid selected alleles are of equal magnitude (Conclusions 3 \& 4).
+Further, transitions involving haploid selection can be driven by sex-ratio selection or cause sex-ratio biases to evolve; to leading order, selection to balance the sex ratio and hitch-hiking with haploid selected alleles are of equal magnitude (Conclusions 3 \& 4).
 Overall, our results suggest several new scenarios under which new sex-determining systems are favoured, which could help to explain why the evolution of sex-determining systems is so dynamic.

### 2018-05-01 LaTeX/main_revised.tex

--- 2018-05-01 LaTeX/main_revised.tex
@@
 Counterintuitively, when linkage is tight between the sex-determining locus and a selected locus, an allele good for females can be at higher frequency on the ancestral-Y than on the ancestral-X under a variety of forms of selection.
-This, in turn, can favour a new ZW sex-determining locus that has weaker linkage with loci under selection (a similar argument applies to ZW$\rightarrow$XY transitions), which was not \textcolor{red}{apparent/discovered/considered} in previous theory \cite{vanDoorn:2010hu}.
-That is, we show that selected loci in very tight linkage with the ancestral GSD locus can favour trans-GSD transitions during which linkage associations are actually weakened.
+This, in turn, can favour a new ZW sex-determining locus that has weaker linkage with loci under selection, which was not \textcolor{red}{apparent/discovered/considered} in previous theory \cite{vanDoorn:2010hu}.
+A similar argument applies to ZW$\rightarrow$XY transitions.
+Thus, we show that selected loci in very tight linkage with the ancestral GSD locus can favour trans-GSD transitions during which linkage associations are actually weakened.
 
@@
 (2010)~\cite{Kozielska:2010vm} and Ubeda et al.
-(2015)~\cite{Ubeda:2015fx} by showing when new GSD systems that increase \textit{or} decrease linkage with loci under haploid selection spread.
+(2015)~\cite{Ubeda:2015fx} by deriving conditions for the spread of new GSD systems that increase \textit{or} decrease linkage with haploid selected loci.
 %that experience haploid selection.
-This result is qualitatively distinct from those for diploid selection alone~\cite{vanDoorn:2007eu,vanDoorn:2010hu} and suggests that haploid selection is more likely to promote transitions between sex-determination systems.
-This also implies that transitions involving haploid selection cannot be simply explained by invoking sex-ratio selection. 
-In particular, we show that under a wide range of conditions, transitions to sex-determining systems that increase or decrease the sex-ratio bias are favoured \textit{equally strongly}.
-%(and in situations where sex-ratio biases are ancestrally present or absent).
+Our result is qualitatively distinct from those for diploid selection alone~\cite{vanDoorn:2007eu,vanDoorn:2010hu} and suggests that haploid selection is more likely to promote transitions between sex-determination systems.
+We also show that transitions involving haploid selection cannot be simply explained by invoking sex-ratio selection. 
+In particular, under a wide range of conditions, we show that transitions in sex-determining system are favoured \textit{equally strongly} in situations where sex-ratio biases increase or decrease (and in situations where sex-ratio biases are ancestrally present or absent).
 Finally, we show that ESD may not evolve, even if the sex ratio is initially biased by haploid selection, which is not predicted by previous theories for transitions to ESD~\cite{Charnov:1982wg,Bull:1983vi,West:2009we}.
@@
 
+We begin by describing the general conditions under which new genetic sex determining alleles can spread within a population, without explicitly specifying ancestral allele frequencies.
+These general conditions then allow us to consider several special cases of interest in subsequent sections, where equilibrium ancestral allele frequencies are explicitly calculated.
+Finally, we consider the spread of alleles that specify environmental sex determination.
+
 \subsection*{Generic invasion by a neo-Y or neo-W}
 
-We begin by describing the conditions under which new sex determining alleles can spread within a population, without explicitly specifying ancestral allele frequencies.
-These general conditions then allow us to consider several special cases of interest in subsequent sections, where equilibrium ancestral allele frequencies are explicitly calculated.
-
-The evolution of a new sex-determining system depends on the growth rate of a rare mutant allele, $m$, at the novel sex-determining locus, $\mathbf{M}$. %, increases in frequency when rare. 
-This growth rate is determined by the leading eigenvalue ($\lambda_m^{(XY)}$) of the system of eight equations describing the frequency of eggs and sperm carrying the $m$ allele in the next generation (equations \ref{eq:recursions}).
+The evolution of a new sex-determining system requires that a rare mutant allele, $m$, at the novel sex-determining locus, $\mathbf{M}$, increases in frequency when rare (i.e., $\lambda_m^{(XY)}>1$, where $\lambda_m^{(XY)}$ is the leading eigenvalue of the system of eight equations describing $m$-bearing gamete frequencies, \ref{eq:recursions}).
+%This is determined by the leading eigenvalue ($\lambda_m^{(XY)}$) of the system of eight equations describing the frequency of eggs and sperm carrying the $m$ allele in the next generation (equations \ref{eq:recursions}).
+This system simplifies substantially for an epistatically dominant neo-Y ($k=0$) or neo-W ($k=1$), see \nameref{app:inv_cond}. 
+%We will consider only equilibrium frequencies of alleles, $\hat{p}^\circ_i$, and Y-bearing male gametes, $\hat{q}$, when calculating the eigenvalues.
+
+Invasion by a neo-Y or a neo-W primarily depends on the ``haplotypic growth rates'' (denoted by $\Lambda_{mi}^{(XY)}$) of the neo-sex determination allele $m$ on background $i\in\{A,a\}$ without accounting for loss due to recombination ($R=0$), see Table \ref{tab:haplotype_growth}.
+If both haplotypic growth rates are greater than one ($\Lambda_{mA}^{(XY)}, \Lambda_{ma}^{(XY)}>1$), then the new sex-determining allele invades regardless of the rate of recombination between the new sex-determining locus and the selected locus ($R$), see \nameref{app:inv_cond} for details.
+Conversely, if both haplotypic growth rates are less than one ($\Lambda_{mA}^{(XY)}, \Lambda_{ma}^{(XY)}<1$), then invasion can never occur.  
+Finally, if only one haplotypic growth rate is greater than one, the new sex-determining allele can always invade when arising at a locus that is tightly linked to the selected locus ($R\approx0$).  
+Furthermore, it can be shown that the leading eigenvalue declines with $R$, and invasion requires that $R$ is sufficiently small such that: 
+\begin{equation}\label{eq:lambdasGen}
+%\frac{\chi_{mA}}{\Lambda_{mA}-1}+\frac{\chi_{ma}}{\Lambda_{ma}-1}>0.
+\chi_{ma}^{(XY)}/\left(\Lambda_{ma}^{(XY)} - 1\right) + \chi_{mA}^{(XY)}/\left(\Lambda_{mA}^{(XY)} - 1\right) < 1
+\end{equation}
+\noindent 
+where $\chi_{mi}^{(XY)}>0$ is the rate at which mutant haplotypes on background $i\in\{A,a\}$ recombine onto the other $\mathbf{A}$ locus background in heterozygotes (proportional to $R$; we call this the ``dissociative force" as it breaks down linkage disequilibrium), see Table \ref{tab:haplotype_growth}.
+Condition \ref{eq:lambdasGen} may or may not be satisfied for the full range of locations of the new sex-determining locus, including $R=1/2$, depending on the nature of selection.  
+Interpreting this condition, if we assume that only the $mA$ haplotype would increase in frequency when $R=0$ ($\Lambda_{ma}^{(XY)}<1<\Lambda_{mA}^{(XY)}$) then the first term on the left-hand side of \eqref{eq:lambdasGen} is negative and invasion requires that growth rate of $mA$ haplotypes ($\Lambda_{mA}^{(i)}-1>0$) and the rate at which they are produced by recombination ($\chi_{ma}^{(i)}$) are sufficiently large relative to the rate of decline of $ma$ haplotypes ($1-\Lambda_{ma}^{(i)}>0$) and the rate at which $m$ and $A$ are dissociated by recombination ($\chi_{mA}^{(i)}$).
+
+%The leading eigenvalue for a rare neo-Y or neo-W allele, $m\in\{Y',W'\}$, is the largest value of $x$ that solves $x^2+ b x + c = 0$.  %$(\lambda_m^{(i)})^2+ b \lambda_m^{(i)} + c =0$. 
+%The coefficients are $b= - (\Lambda_{mA}^{(XY)} + \Lambda_{ma}^{(XY)})+(\chi_{mA}^{(XY)} + \chi_{ma}^{(XY)})$ and $c = (\Lambda_{mA}^{(XY)} - \chi_{mA}^{(XY)}) (\Lambda_{ma}^{(XY)} - \chi_{ma}^{(XY)}) - \chi_{mA}^{(XY)} \chi_{ma}^{(XY)}$, where $\Lambda_{mi}^{(XY)}>0$ is the multiplicative growth rate (which we will call the ``haplotypic growth rate'') of the neo-sex determination allele $m$ on background $i\in\{A,a\}$ without accounting for loss due to recombination ($R=0$), and $\chi_{mi}^{(XY)}>0$ is the rate at which mutant haplotypes on background $i\in\{A,a\}$ recombine onto the other $\mathbf{A}$ locus background in heterozygotes (proportional to $R$; we call this the ``dissociative force" as it breaks down linkage disequilibrium), see Table \ref{tab:haplotype_growth}.
+%In the ancestral population, it is convenient to follow the frequency of the $A$ allele among female gametes (eggs), $p^\female_X$, and among X-bearing, $p^\male_X$, and among Y-bearing, $p^\male_Y$, male gametes (sperm/pollen).
+%We also track the fraction of male gametes that are Y-bearing, $q$, which may deviate from $1/2$ due to meiotic drive in males. 
+%We will consider only equilibrium frequencies of alleles, $\hat{p}^\circ_i$, and Y-bearing male gametes, $\hat{q}$, when calculating the eigenvalues.
+
+%The evolution of a new sex-determining system depends on the growth rate of a rare mutant allele, $m$, at the novel sex-determining locus, $\mathbf{M}$. %, increases in frequency when rare. 
+%This growth rate is determined by the leading eigenvalue ($\lambda_m^{(XY)}$) of the system of eight equations describing the frequency of eggs and sperm carrying the $m$ allele in the next generation (equations \ref{eq:recursions}).
 %, evaluated at the above equilibrium.
 %Thus, the system describing the change in frequency of the $m$ allele consists of eight recursion equations. 
-This system simplifies substantially for an epistatically dominant neo-Y ($k=0$) or neo-W ($k=1$), see \nameref{app:inv_cond}. 
-The leading eigenvalue for a rare neo-Y or neo-W allele, $m\in\{Y',W'\}$, is the largest value of $x$ that solves $x^2+ b x + c = 0$, where $b= - (\Lambda_{mA}^{(XY)} + \Lambda_{ma}^{(XY)})+(\chi_{mA}^{(XY)} + \chi_{ma}^{(XY)})$ and $c = (\Lambda_{mA}^{(XY)} - \chi_{mA}^{(XY)}) (\Lambda_{ma}^{(XY)} - \chi_{ma}^{(XY)}) - \chi_{mA}^{(XY)} \chi_{ma}^{(XY)}$.
-The variable $\Lambda_{mi}^{(XY)}>0$ is the multiplicative growth rate of the neo-sex-determining allele $m$ on background $i\in\{A,a\}$ without accounting for loss due to recombination ($R=0$).
-We will call  $\Lambda_{mi}^{(XY)}$ the ``haplotypic growth rate''.
-The variable $\chi_{mi}^{(XY)}>0$ is the rate at which mutant haplotypes on background $i\in\{A,a\}$ recombine onto the other $\mathbf{A}$ locus background in heterozygotes (proportional to $R$).
-We call $\chi_{mi}^{(XY)}$ the ``dissociative force", as it breaks down linkage disequilibrium.
-Both variables are listed in Table \ref{tab:haplotype_growth} for neo-Y and neo-W mutants.
+%This system simplifies substantially for an epistatically dominant neo-Y ($k=0$) or neo-W ($k=1$), see \nameref{app:inv_cond}. 
+%The leading eigenvalue for a rare neo-Y or neo-W allele, $m\in\{Y',W'\}$, is the largest value of $x$ that solves $x^2+ b x + c = 0$, where $b= - (\Lambda_{mA}^{(XY)} + \Lambda_{ma}^{(XY)})+(\chi_{mA}^{(XY)} + \chi_{ma}^{(XY)})$ and $c = (\Lambda_{mA}^{(XY)} - \chi_{mA}^{(XY)}) (\Lambda_{ma}^{(XY)} - \chi_{ma}^{(XY)}) - \chi_{mA}^{(XY)} \chi_{ma}^{(XY)}$.
+%The variable $\Lambda_{mi}^{(XY)}>0$ is the multiplicative growth rate of the neo-sex-determining allele $m$ on background $i\in\{A,a\}$ without accounting for loss due to recombination ($R=0$).
+%We will call  $\Lambda_{mi}^{(XY)}$ the ``haplotypic growth rate''.
+%The variable $\chi_{mi}^{(XY)}>0$ is the rate at which mutant haplotypes on background $i\in\{A,a\}$ recombine onto the other $\mathbf{A}$ locus background in heterozygotes (proportional to $R$).
+%We call $\chi_{mi}^{(XY)}$ the ``dissociative force", as it breaks down linkage disequilibrium.
+%Both variables are listed in Table \ref{tab:haplotype_growth} for neo-Y and neo-W mutants.
 
@@
 cis- and trans-GSD transitions are qualitatively different.
-This is because, in an ancestrally XY system, a gamete with the neo-Y always pairs with a female gamete containing an X (Fig \ref{fig:model_outline}C).
-By contrast, a gamete with a neo-W can pair with an X- or Y-bearing male gamete (Fig \ref{fig:model_outline}D).
-Consequently, neo-W-bearing females obtain a different frequency of $A$ alleles from mating (when $\hat{p}_X^\male \neq \hat{p}_Y^\male$) compared to ancestral ($MM$) females, which can inhibit or favour its spread.
+This is because, in an ancestrally XY system, a gamete with the neo-Y always pairs with a female gamete containing an X, Fig \ref{fig:model_outline}C.
+By contrast, a gamete with a neo-W can pair with an X- or Y-bearing male gamete, Fig \ref{fig:model_outline}D.
+Consequently, neo-W-bearing females obtain a different frequency of $A$ alleles from mating (when $\hat{p}_X^\male \neq \hat{p}_Y^\male$) compared to ancestral ($MM$) females. 
+This can inhibit or favour the spread of a neo-W.
 

### 2018-05-01 LaTeX/S3Appendix_revised.tex
charpoly detail added to appendix

@@
 
-A rare neo-Y or neo-W allele, $m$, will spread in an XY sex-determining system when the leading eigenvalue, $\lambda_m^{(XY)}$, of the Jacobian matrix derived from the eight mutant recursion equations (given by \ref{eq:recursions}c,d,g,h), evaluated at the ancestral equilibrium, is greater than one.
-However, because a neo-Y (neo-W) is always in males (females) and is epistatically dominant to the ancestral sex-determining locus, the characteristic polynomial factors into two quadratics times $(\lambda_m^{(XY)})^4$.
+A rare sex-determining allele, $m$, will spread in an XY sex-determining system when the leading eigenvalue, $\lambda_m^{(XY)}$, of the Jacobian matrix derived from the eight mutant recursion equations (given by \ref{eq:recursions}c,d,g,h), evaluated at the ancestral equilibrium, is greater than one.
+Because a neo-Y (neo-W) is always in males (females) and is epistatically dominant to the ancestral sex-determining locus, the characteristic polynomial factors into two quadratics times $(\lambda_m^{(XY)})^4$, which greatly simplifies analysis.
 One quadratic governs the change in the frequency of the new sex determination factor associated with the $A$ and $a$ allele frequencies, summing across backgrounds at the old sex-determining locus (i.e., summing haplotypes bearing the original X and Y alleles).
@@
 Asymptotically, this difference is constrained to grow at a rate equal to or less than the sum while the $m$ allele is rare, because the frequencies can never become negative. 
-We therefore focus on the leading eigenvalue, $\lambda_m^{(XY)}$, which is the largest root of the first quadratic $f(x) = x^2+ b x + c = 0$, as described in the text (details in \nameref{file:Mathematica}).
+We therefore focus on the leading eigenvalue, $\lambda_m^{(XY)}$, which is the largest root of the quadratic $f(x) = x^2+ b x + c = 0$,  where $b= - (\Lambda_{mA}^{(XY)} + \Lambda_{ma}^{(XY)})+(\chi_{mA}^{(XY)} + \chi_{ma}^{(XY)})$ and $c = (\Lambda_{mA}^{(XY)} - \chi_{mA}^{(XY)}) (\Lambda_{ma}^{(XY)} - \chi_{ma}^{(XY)}) - \chi_{mA}^{(XY)} \chi_{ma}^{(XY)}$ (details in \nameref{file:Mathematica}), see Table \ref{tab:haplotype_growth}.
 
@@
 If only one haplotypic growth rate is greater than one ($\Lambda_{ma}^{(XY)}<1<\Lambda_{mA}^{(XY)}$ or $\Lambda_{mA}^{(XY)}<1<\Lambda_{ma}^{(XY)}$), then $\lambda_m^{(XY)}$ is greater than one when condition \eqref{eq:lambdasGen} is met.
-Thus, the invasion of a new sex-determining allele is determined by the haplotypic growth rates ($\Lambda_{mj}^{(XY)}$ terms), which do not account for loss due to recombination, and the rates at which recombination between the $\mathbf{M}$ and $\mathbf{A}$ loci breaks apart these haplotypes ($\chi_{mj}^{(XY)}$).
+Thus, the invasion of a new sex-determining allele is determined by the haplotypic growth rates ($\Lambda_{mj}^{(XY)}$ terms), which do not account for loss due to recombination, and the dissociative force that breaks apart these haplotypes by recombination ($\chi_{mj}^{(XY)}$).
 For tight linkage between the ancestral sex-determining locus ($\mathbf{X}$) and the selected locus ($\mathbf{A}$) we can calculate these terms explicitly (see below).
@@
 
-Starting with the simpler $(B)$ equilibrium, the terms that determine the leading eigenvalue are
+Starting with the simpler $(B)$ equilibrium, the haplotypic growth rates ($\Lambda_{mi}^{(XY)}$) and dissociative forces ($\chi_{mi}^{(XY)}$) are
 

### 2018-05-01 LaTeX/main_revised.tex
adjustment to discussion of tight linkage in intro, lack of X-specialisation was missing

@@
 Counterintuitively, when linkage is tight between the sex-determining locus and a selected locus, an allele good for females can be at higher frequency on the ancestral-Y than on the ancestral-X under a variety of forms of selection.
-This, in turn, can favour a new ZW sex-determining locus that has weaker linkage with loci under selection, which was not \textcolor{red}{apparent/discovered/considered} in previous theory \cite{vanDoorn:2010hu}.
+In addition, selection on ancestral-X chromosomes in males can prevent the X from becoming optimally specialised for female-beneficial alleles. 
+These factors, in turn, can favour a new ZW sex-determining locus that has weaker linkage with loci under selection, which was not \textcolor{red}{apparent/discovered/considered} in previous theory \cite{vanDoorn:2010hu}.
 A similar argument applies to ZW$\rightarrow$XY transitions.
@@
 \textbf{Selection on loci in or near the non-recombining region around the sex-determining locus ($r\approx0$) prevents cis-GSD transitions (XY $\leftrightarrow$ XY, ZW $\leftrightarrow$ ZW) but can spur trans-GSD transitions (XY $\leftrightarrow$ ZW).}
-\textcolor{red}{[Not clear from van Doorn \& Kirkpatrick 2007, 2010]}
+%\textcolor{red}{[Not clear from van Doorn \& Kirkpatrick 2007, 2010]}
 \vspace{0.5cm}

### 2018-05-02 LaTeX/main_revised.tex
re-arrangement of tight linkage results section

@@
 %% Include all macros below
+
+%for figure alignment
+\usepackage[export]{adjustbox}
 
@@
 
-The evolution of a new sex-determining system requires that a rare mutant allele, $m$, at the novel sex-determining locus, $\mathbf{M}$, increases in frequency when rare (i.e., $\lambda_m^{(XY)}>1$, where $\lambda_m^{(XY)}$ is the leading eigenvalue of the system of eight equations describing $m$-bearing gamete frequencies, \ref{eq:recursions}).
+The evolution of a new sex-determining system requires that a rare mutant allele, $m$, at the novel sex-determining locus, $\mathbf{M}$, increases in frequency when rare. 
+Specifically, $m$ invades when $\lambda_m^{(XY)}>1$, where $\lambda_m^{(XY)}$ is the leading eigenvalue of the system of eight equations describing $m$-bearing gamete frequencies, \ref{eq:recursions}.
 %This is determined by the leading eigenvalue ($\lambda_m^{(XY)}$) of the system of eight equations describing the frequency of eggs and sperm carrying the $m$ allele in the next generation (equations \ref{eq:recursions}).
-This system simplifies substantially for an epistatically dominant neo-Y ($k=0$) or neo-W ($k=1$), see \nameref{app:inv_cond}. 
+This system simplifies substantially for an epistatically dominant neo-Y ($k=0$) or neo-W ($k=1$), see \nameref{app:inv_cond} for details. 
 %We will consider only equilibrium frequencies of alleles, $\hat{p}^\circ_i$, and Y-bearing male gametes, $\hat{q}$, when calculating the eigenvalues.
@@
 Invasion by a neo-Y or a neo-W primarily depends on the ``haplotypic growth rates'' (denoted by $\Lambda_{mi}^{(XY)}$) of the neo-sex determination allele $m$ on background $i\in\{A,a\}$ without accounting for loss due to recombination ($R=0$), see Table \ref{tab:haplotype_growth}.
-If both haplotypic growth rates are greater than one ($\Lambda_{mA}^{(XY)}, \Lambda_{ma}^{(XY)}>1$), then the new sex-determining allele invades regardless of the rate of recombination between the new sex-determining locus and the selected locus ($R$), see \nameref{app:inv_cond} for details.
+If both haplotypic growth rates are greater than one ($\Lambda_{mA}^{(XY)}, \Lambda_{ma}^{(XY)}>1$), then the new sex-determining allele invades regardless of the rate of recombination between the new sex-determining locus and the selected locus ($R$).
 Conversely, if both haplotypic growth rates are less than one ($\Lambda_{mA}^{(XY)}, \Lambda_{ma}^{(XY)}<1$), then invasion can never occur.  
@@
 Condition \ref{eq:lambdasGen} may or may not be satisfied for the full range of locations of the new sex-determining locus, including $R=1/2$, depending on the nature of selection.  
-Interpreting this condition, if we assume that only the $mA$ haplotype would increase in frequency when $R=0$ ($\Lambda_{ma}^{(XY)}<1<\Lambda_{mA}^{(XY)}$) then the first term on the left-hand side of \eqref{eq:lambdasGen} is negative and invasion requires that growth rate of $mA$ haplotypes ($\Lambda_{mA}^{(i)}-1>0$) and the rate at which they are produced by recombination ($\chi_{ma}^{(i)}$) are sufficiently large relative to the rate of decline of $ma$ haplotypes ($1-\Lambda_{ma}^{(i)}>0$) and the rate at which $m$ and $A$ are dissociated by recombination ($\chi_{mA}^{(i)}$).
+Interpreting this condition, if we assume that only the $mA$ haplotype would increase in frequency when $R=0$ ($\Lambda_{ma}^{(XY)}<1<\Lambda_{mA}^{(XY)}$) then the first term on the left-hand side of \eqref{eq:lambdasGen} is negative and invasion requires that growth rate of $mA$ haplotypes ($\Lambda_{mA}^{(XY)}-1>0$) and the rate at which they are produced by recombination ($\chi_{ma}^{(XY)}$) are sufficiently large relative to the rate of decline of $ma$ haplotypes ($1-\Lambda_{ma}^{(XY)}>0$) and the rate at which $m$ and $A$ are dissociated by recombination ($\chi_{mA}^{(XY)}$).
 
@@
 However, the spread of a neo-Y (neo-W) also depends on the male (female) fitness of associated alleles (see terms involving equilibrium allele frequencies, $\hat{p}$'s), including haploid selection that additionally biases the sex ratio.
-This implies that both Fisherian selection to equalize the sex-ratio and selection favoring sex-linked drivers that distort the sex ratio play roles in the invasion dynamics of a new sex-determining allele, allowing the sex ratio to become more or less biased during a transition (as previously shown in two special cases; \cite{Kozielska:2010vm,Ubeda:2015fx}).
+This implies that both Fisherian selection to equalize the sex-ratio and selection favoring sex-linked drivers that distort the sex ratio play roles in the invasion dynamics of a new sex-determining allele, allowing the sex ratio to become more or less biased during a transition (as previously found in two special cases; \cite{Kozielska:2010vm,Ubeda:2015fx}).
 %neiher sex-ratio selection nor selection on associated alleles dominates the invasion dynamics of a new sex-determining allele, allowing the sex ratio to become more or less biased during a transition (as previously shown in two special cases; \cite{Kozielska:2010vm,Ubeda:2015fx}).
@@
 
-When there is complete linkage between the ancestral sex-determining locus and the $\mathbf{A}$ locus ($r=0$), either the $A$ allele or the $a$ allele must be fixed in gametes containing a Y allele. 
+When there is complete linkage between the ancestral sex-determining locus and the selected locus $\mathbf{A}$ ($r=0$), either the $A$ allele or the $a$ allele must be fixed in gametes containing a Y allele.
 % because selection on the Y is effectively haploid an incapably of maintaining a polymorphism in the absence of frequency dependent selection. 
@@
 Neo-W alleles, on the other hand, can invade an ancestral XY system (the full invasion conditions are given in \nameref{app:inv_cond}; equations \ref{Binvasion} and \ref{Ainvasion}).
+This implies that neo-W females can have higher fitness than the XX females in the ancestral population.
+Neo-W invasion is possible under all forms of selection that can maintain a polymorphism (sexually-antagonistic selection, overdominance, ploidally-antagonistic selection, or some combination, e.g., \nameref{fig:temporalOverdominance}, \nameref{fig:SexAntagTighterMaleDrive}, and \nameref{fig:regionPloidAntag}).
 Thus,
@@
 %\textbf{selection on loci within the non-recombining region around the sex-determining locus ($r\approx0$) allows the invasion of less closely linked sex-determining alleles ($r<R\leq1/2$) during a trans-GSD transition} (XY $\leftrightarrow$ ZW).
-\textbf{Selection on loci in or near the non-recombining region around the sex-determining locus ($r\approx0$) prevents cis-GSD transitions (XY $\leftrightarrow$ XY, ZW $\leftrightarrow$ ZW) but can spur trans-GSD transitions (XY $\leftrightarrow$ ZW).}
+\textbf{Selection on loci in or near the non-recombining region around the ancestral sex-determining locus ($r\approx0$) prevents cis-GSD transitions (XY $\leftrightarrow$ XY, ZW $\leftrightarrow$ ZW) but can spur trans-GSD transitions (XY $\leftrightarrow$ ZW).}
 %\textcolor{red}{[Not clear from van Doorn \& Kirkpatrick 2007, 2010]}
@@
 
-\noindent Trans-GSD transitions can occur because, under some conditions, the neo-W can become more strongly specialized for females.
-This does not depend on the form of selection maintaining a polymorphism (sexually-antagonistic selection, overdominance, ploidally-antagonistic selection, or some combination, Fig \ref{fig:SexAntagTighter}, \nameref{fig:temporalOverdominance}, \nameref{fig:regionPloidAntag}, and \nameref{fig:SexAntagTighterMaleDrive}).
-
-The conditions allowing trans-GSD transitions become more restrictive with increasing recombination ($R$) between the new sex-determining locus and the selected locus.  
-The invasion of completely unlinked neo-W alleles ($R = 1/2$) can occur with overdominance in males or with haploid selection (e.g., when male drive is opposed by diploid selection, as in \cite{Kozielska:2010vm}) but is not possible with only sexually-antagonistic selection where selection is directional in each diploid sex (see \nameref{file:Mathematica}).
-To clarify the conditions under which trans-GSD transitions occur, we focus here on cases where there is no haploid selection (Fig \ref{fig:SexAntagTighter}A) and discuss the additional effect of haploid selection in \nameref{app:inv_cond} (see also Conclusion 2B).
 %Essentially, neo-W alleles are able to invade (even with $R>r$) because the ancestral X experiences selection in males. 
 %This can lead to (1) XX females having lower than maximum fitness ($\Lambda_{W'A}^{(XY)}>1$) and/or (2) the Y carrying alleles that are beneficial in females. 
-
-%\textcolor{red}{add to Appendix:}
-%\textcolor{red}{In absence of haploid selection Conclusion 1A can also be reached from Equation 7 in \cite{vanDoorn:2010hu}; for example, with no polymorphism on the Y ($V_Y=0$) and an allelic substitution favoured in females ($\alpha^f,\alpha_X^f>0$) a loosely linked neo-W can invade given the allelic substitution is sufficiently disfavoured on the X in males ($\alpha_X^m < -2\alpha_X^f$), although it is unclear from their implicit equation if and when such an equilibrium is stable.}
-
-%\vspace{0.5cm}
+\noindent Broadly, it is possible for neo-W females to have higher fitness than the XX females because of the way that the ancestral X experiences selection in both males and females.
+Consequently, (a) the ancestral X may be unable to specialize strongly on an allele favoured in females and (b) an allele can be associated with the Y and yet favoured in females. 
+In turn, a neo-W can spread because (a) it is only found in females and is therefore unleashed from counterselection in males (corresponding to $\Lambda_{W'A}^{(XY)}>1$) and (b) it allows Y-associated alleles into females (corresponding to $\Lambda_{W'a}^{(XY)}>1$).
+
+To clarify the conditions under which trans-GSD transitions occur, we focus here on cases where there is no haploid selection and discuss the additional effect of haploid selection in \nameref{app:inv_cond}.
+Firstly, we discuss an example where neo-W-$A$ haplotypes spread (case (a), where $\Lambda_{W'A}^{(XY)}>1$).
+When $A$ is female beneficial and $a$ is male beneficial, the $A$ allele can be fixed ($\hat{p}^\female_X=\hat{p}^\male_X=1$) or polymorphic (0<$\hat{p}^\female_X, \hat{p}^\male_X$<1) on the X. 
+In this case, polymorphism on the ancestral-X indicates suboptimal specialisation for females fitness, which occurs because the $A$ allele is counterselected in males (requires that $w^\male_{Aa}$  sufficiently small relative to $w^\male_{aa}$).
+Neo-Ws, however, spend no time in males and can build stronger associations with the female-beneficial $A$ allele, allowing them to spread (see gray region in Fig \ref{fig:regionplots}A).
+Secondly, we dicuss an example where neo-W-$a$ haplotypes spread (case (b), where $\Lambda_{W'a}^{(XY)}>1$). 
+When there is overdominance in males, X-$A$ Y-$a$ males have high fitness and the $A$ allele is favoured by selection on the X background in males.
+Therefore, the $A$ allele can be polymorphic or even fixed on the X background despite selection favouring the $a$ allele in females (e.g., see outlined region in Fig \ref{fig:regionplots}B and~\cite{Lloyd1977,Otto2014}).
+In such cases, neo-W-$a$ haplotypes can spread because they create more $Aa$ and $aa$ females when pairing with an X-bearing gamete from males and because they bring Y-$a$ haplotypes into females, where it has higher fitness (Fig \ref{fig:model_outline}D).
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Tighter linkage allows looser sex-linkage to evolve, even in absence of haploid selection
+%Both neo-W haplotypes can spread, in the absence of haploid selection, when there is overdominance
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \centering
-\centerline{\includegraphics[width=\linewidth]{../Plots/PositionPlot_SexAntagTighter}}
+%\centerline{\includegraphics[width=1.25\linewidth]{Region_plot_combined_Mike}}
+\centerline{\includegraphics[width=1.4\linewidth, right]{../Plots/Region_plot_combined}}
+\caption{
+{\bf When the ancestral XY locus is tightly linked to a locus under selection ($r=0$), one or both neo-W haplotypes can spread (no haploid selection).}
+We vary the fitness of male homozygotes relative to heterozygotes ($w_{Aa}^\circ=1$) and only consider stable equilibria at which both $\mathbf{A}$ locus alleles are maintained and the $a$ allele is initially fixed on the Y (region outlined).
+Here, selection in females can favour the $A$ allele (panel A, $w_{aa}^\female=0.85$, $w_{AA}^\female=1.05$), favour the $a$ allele (panel B, $w_{aa}^\female=1.05$, $w_{AA}^\female=0.85$), or be overdominant (panel C, $w_{aa}^\female=w_{AA}^\female=0.6$).
+If either haplotypic growth rate ($\Lambda_{W'A}^{(XY)}$ or $\Lambda_{W'a}^{(XY)}$) is greater than one, then a rare neo-W allele can spread for, at least, some values of $R>r$. 
+The parameter values marked with an asterisk correspond to the fitnesses used in Fig \ref{fig:SexAntagTighter}C. 
+Where both haplotypic growth rates are greater than one, a neo-W will spread when rare, regardless of linkage with the selected locus (for any $R$). 
+\nameref{fig:positionOverdominance} shows the dynamics arising with the parameters marked with a dagger. 
+%Here, there is no haploid selection $t^\circ = \alpha^\circ_\Delta = 0$.
+}
+\label{fig:regionplots}
+\end{figure}
+
+In some cases, both W-$A$ and W-$a$ haplotypes can spread.
+For example, when $AA$ individuals have low fitness in females yet the $A$ is polymorphic or fixed on the X background due to overdominance in males (Fig \ref{fig:regionplots}B and \ref{fig:regionplots}C), both neo-W-$A$ and neo-W-$a$ haplotypes produce fewer unfit $AA$ females.
+This is true for the neo-W-$A$ haplotype because it can pair with a Y-$a$ haplotype and still be female. 
+Wherever both haplotypic growth rates are greater than one, invasion by a neo-W is expected regardless of its linkage with the selected locus (i.e., for any $R$, see \nameref{fig:positionOverdominance} and \nameref{fig:temporalOverdominance} for examples).
+As a consequence, evolution can favor a new sex determination system on a different chromosome ($R = 1/2$), despite the fact that this unlinks the sex-determining locus from the selected locus.
+
+When only one neo-W haplotype has growth rate greater than one (see Fig \ref{fig:regionplots}), a neo-W allele can invade as long as Eq \eqref{eq:lambdasGen} is satisfied, which may require that the recombination rate, $R$, is small enough.
+Nevertheless, because we assume here that $r$ is small, these results indicate that a more loosely linked sex-determining region ($r<R$) can spread.
+For example, tightly sex-linked loci that experience sexually-antagonistic selection can drive trans-GSD transitions in which the new sex-determining locus is less closely linked (but not unlinked, $R<1/2$) to the locus under selection (Fig \ref{fig:SexAntagTighter}).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Tight linkage allows looser sex-linkage to evolve, even in absence of haploid selection
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[!h]
+\centering
+\centerline{\includegraphics[width=1.4\linewidth, right]{../Plots/PositionPlot_SexAntagTighter}}
 \caption{
@@
 
-%To develop an intuition for how less closely linked neo-W alleles invade ($R>r$), we here focus on cases where there is no haploid selection and discuss the additional effect of haploid selection in \nameref{app:inv_cond}.
-%If we categorise the $a$ allele as being ancestrally `male-beneficial' via the fact that it is fixed on Y backgrounds, then $\Lambda_{W'A}^{(XY)}>1$ indicates that the neo-W spreads when found with the ancestrally `female-beneficial' allele.
-%Broadly, this is possible because ancestral X alleles are sometimes in males and are therefore unable to perfectly specialise on the `female-beneficial' allele. 
-%For example, when the $a$ allele is favoured on ancestral X backgrounds in males, a polymorphism of $A$ and $a$ alleles can be maintained on the X background despite selection for the $A$ allele in females ($s^\female>0$, $0<h^\female<1$), see outlined region in Fig \ref{fig:regionplots}A.
-%When the $a$ allele is strongly favoured on the X background in males ($w_{aa}^\male$ sufficiently large relative to $w_{Aa}^\male$), neo-W-$A$ haplotypes can spread ($\Lambda_{W'A}^{(XY)}>1$, see grey region in Fig \ref{fig:regionplots}A) because they produce higher fitness females ($AA$ or $Aa$ genotypes) and are unleashed from counterselection in males.
-The reason that neo-W-$A$  haplotypes can spread ($\Lambda_{W'A}^{(XY)}>1$) is because they can sometimes produce higher fitness females that are unleashed from counterselection in males. 
-Broadly, this is possible because ancestral X alleles are found in both males and females and are therefore unable to perfectly specialize on the `female-beneficial' allele. 
-For example, when $A$ is female beneficial and $a$ is male beneficial, a polymorphism can be maintained on the X when the $A$ allele is strongly counterselected in males ($w^\male_{Aa}$  sufficiently small relative to $w^\male_{aa}$).
-Neo-Ws, however, spend no time in males and can build stronger associations with the female-beneficial allele (see gray region in Fig \ref{fig:regionplots}A).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Both neo-W haplotypes can spread, in the absence of haploid selection, when there is overdominance
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!h]
-\centering
-%\centerline{\includegraphics[width=1.25\linewidth]{Region_plot_combined_Mike}}
-\centerline{\includegraphics[width=1\linewidth]{../Plots/Region_plot_combined}}
-\caption{
-{\bf When the ancestral XY locus is tightly linked to a locus under selection ($r=0$), one or both neo-W haplotypes can spread (no haploid selection).}
-We vary the fitness of male homozygotes relative to heterozygotes ($w_{Aa}^\circ=1$) and only consider stable equilibria at which both $\mathbf{A}$ locus alleles are maintained and the $a$ allele is initially fixed on the Y (region outlined).
-Here, selection in females can favour the $A$ allele (panel A, $w_{aa}^\female=0.85$, $w_{AA}^\female=1.05$), favour the $a$ allele (panel B, $w_{aa}^\female=1.05$, $w_{AA}^\female=0.85$), or be overdominant (panel C, $w_{aa}^\female=w_{AA}^\female=0.6$).
-If either haplotypic growth rate ($\Lambda_{W'A}^{(XY)}$ or $\Lambda_{W'a}^{(XY)}$) is greater than one, then a rare neo-W allele can spread for, at least, some values of $R>r$. 
-The parameter values marked with an asterisk correspond to the fitnesses used in Fig \ref{fig:SexAntagTighter}C. 
-Where both haplotypic growth rates are greater than one, a neo-W will spread when rare, regardless of linkage with the selected locus (for any $R$). 
-\nameref{fig:positionOverdominance} shows the dynamics arising with the parameters marked with a dagger. 
-%Here, there is no haploid selection $t^\circ = \alpha^\circ_\Delta = 0$.
-}
-\label{fig:regionplots}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Given that the $a$ allele is fixed on the Y and can be considered ancestrally `male-beneficial', it is surprising that neo-W-$a$ haplotypes can sometimes be favoured by selection in females ($\Lambda_{W'a}^{(XY)}>1$).
-Again, this occurs because ancestral X alleles experience selection in both males and females, and conditions can arise where increases in the $a$ allele would be favored in females too.
-%, where they are ancestrally always paired with a Y-$a$ gamete.
-For example, if there is overdominance in males, X-$A$ Y-$a$ males have high fitness and the $A$ allele is favoured by selection on the X background in males. 
-Therefore, the $A$ allele can be polymorphic or even fixed on the X background despite selection favouring the $a$ allele in females (e.g., see outlined region in Fig \ref{fig:regionplots}B and~\cite{Lloyd1977,Otto2014}).
-In such cases, neo-W-$a$ haplotypes can spread because they create more $Aa$ and $aa$ females when pairing with an X-bearing gamete from males and because they bring Y-$a$ haplotypes into females, where it has higher fitness (Fig \ref{fig:model_outline}D).
-
-When only one neo-W haplotype has growth rate greater than one (see Fig \ref{fig:regionplots}), a neo-W allele can invade as long as Eq \eqref{eq:lambdasGen} is satisfied, which may require that the recombination rate, $R$, is small enough.
-Nevertheless, because we assume here that $r$ is small, these results indicate that a more loosely linked sex-determining region ($r<R$) can spread.
-For example, tightly sex-linked loci that experience sexually-antagonistic selection can drive trans-GSD transitions in which the new sex-determining locus is less closely linked to the locus under selection (Fig \ref{fig:SexAntagTighter}).
-
-In some cases, both W-$A$ and W-$a$ haplotypes can spread.
-For example, when $AA$ individuals have low fitness in females yet the $A$ is polymorphic or fixed on the X background due to overdominance in males (Fig \ref{fig:regionplots}B and \ref{fig:regionplots}C), both neo-W-$A$ and neo-W-$a$ haplotypes produce fewer unfit $AA$ females.
-This is true for the neo-W-$A$ haplotype because it can pair with a Y-$a$ haplotype and still be female. 
-Wherever both haplotypic growth rates are greater than one, invasion by a neo-W is expected regardless of its linkage with the selected locus (i.e., for any $R$, see \nameref{fig:positionOverdominance} and \nameref{fig:temporalOverdominance} for examples).
-As a consequence, evolution can favor a new sex determination system on a different chromosome, despite the fact that this unlinks the sex-determining locus from the selected locus.
-
 Assuming selection is weak relative to recombination, van Doorn and Kirkpatrick~\cite{vanDoorn:2010hu} showed that invasion by a neo-W allele occurs under the same conditions as its fixation in females.
@@
 
-From the arguments above and in \nameref{app:inv_cond} we conclude that
+From the arguments above we conclude that
 \vspace{0.5cm}
 
-\noindent\textit{Conclusion 2A:}
+\noindent\textit{Conclusion 2:}
 \textbf{
-With tight linkage between a selected locus and the ancestral sex-determining locus ($r\approx0$), trans-GSD transitions (XY $\leftrightarrow$ ZW) can be driven by selection to better specialize on the ancestrally-non-heterogametic sex.
-These transitions weaken sex-linkage ($r<R$), potentially shifting sex determination to a different chromosome ($R=1/2$). 
-Such transitions can lead to polymorphic sex-determination systems.
+With tight linkage between a selected locus and the ancestral sex-determining locus ($r\approx0$), trans-GSD transitions (XY $\leftrightarrow$ ZW) can be favoured by selection \textit{even if they weaken sex-linkage} ($r<R$), potentially shifting sex determination to a different chromosome ($R=1/2$).
+Such transitions can also lead to the maintenance of multifactorial sex-determination systems.
 }
-\textcolor{red}{[consistent with special case of Kozielska et al 2010]}
 \vspace{0.5cm}
 
-\nameref{app:inv_cond} shows that Conclusion 2A holds with or without haploid selection and further demonstrates that
-\vspace{0.5cm}
-
-\noindent\textit{Conclusion 2B:}
-\textbf{
-With tight linkage between a haploid selected locus and the ancestral sex-determining locus ($r\approx0$), trans-GSD transitions (XY $\leftrightarrow$ ZW) can be driven by selection to better specialize on the ancestrally-non-heterogametic sex and/or sex-ratio selection.
-Such transitions reduce sex ratio bias.
-}
-\textcolor{red}{[consistent with special case of Kozielska et al 2010]}
+\noindent
+With haploid selection, Conclusions 1 \& 2 continue to apply (\nameref{app:inv_cond}). 
+The parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread under various forms of haploid selection are plotted in \nameref{fig:regionMaleDrive}, \nameref{fig:regionMaleGS}, \nameref{fig:regionFemaleDrive}, \nameref{fig:regionFemaleGS}
+In particular, we note that adding haploid selection allows shifts in sex determination to a different chromosome ($R=1/2$) even when selection is sexually antagonistic with directional selection in each diploid sex, e.g., \nameref{fig:SexAntagTighterMaleDrive}.
+Furthermore, haploid selection allows variation to be maintained by ploidally-antagonistic selection, under which trans-GSD transitions may also be favoured, \nameref{fig:regionPloidAntag}.
+Some cases of XY $\rightarrow$ ZW transitions where $r=0$, $R=1/2$ and selection is ploidally-antagonistic (meiotic drive in males opposed by diploid selection) were studied by Kozielska et al.
+\cite{Kozielska:2010vm}, who found that sex ratio biases are reduced during these transitions.
+However, such transitions do not necessarily involve a reduction of sex ratio bias. 
+For example, with haploid selection in females and XY sex determination, sex ratios are not ancestrally biased but ZW invasion can occur (\nameref{fig:regionPloidAntag}).
 
@@
 \textbf{New sex-determining alleles (causing cis- \textit{or} trans-GSD transitions) can spread if they arise more closely linked with a locus that experiences selection than the ancestral-sex-determining locus is ($R<r$).}
-\textcolor{red}{[consistent with van Doorn \& Kirkpatrick 2007, 2010]} 
+\textcolor{red}{[consistent with van Doorn \& Kirkpatrick 2007, 2010, except that we add haploid selection, these connections are mentioned above], consistent with Ubeda et al 2015 (assuming ancestral ESD something similar to $r=1/2$, invasion with $R<1/2$.), not yet mentioned  }
 \vspace{0.5cm}
@@
 \textbf{New sex-determining alleles (causing trans-GSD transitions, XY $\leftrightarrow$ ZW) can spread even if they arise less closely linked with a locus that experiences selection than the ancestral-sex-determining locus is ($r<R$), requiring haploid selection and some initial sex-linkage ($r<1/2$).}
-\textcolor{red}{[consistent with examples in Ubeda et al 2015]}  
 \vspace{0.5cm}
@@
 
-\noindent\textit{Conclusion 4A:}
+\noindent\textit{Conclusion 4:}
 \textbf{When selection is weak relative to recombination, the presence of haploid selection equally favors the spread of new sex determination systems that reduce sex-ratio bias (benefiting from Fisherian sex ratio selection) or generate a sex-ratio bias (benefiting from associations with selected alleles).
 }
-\textcolor{red}{[new result]}  
 \vspace{0.5cm}
@@
 
-\noindent\textit{Conclusion 4B:}
+\noindent\textit{Conclusion 5:}
 \textbf{
@@
 }
-\textcolor{red}{[new result]}  
 %\textcolor{red}{[new result]}
@@
 %, as exemplified in~\cite{Ubeda:2015fx} for ESD-GSD transitions.
-However, we also find that trans-GSD transitions can be favoured in cases where linkage with the sex-determining locus is actually weakened (Conclusions 2A, 2B \& 3B, Fig \ref{fig:SexAntagTighter} \& \ref{fig:regionplots}), especially when there is haploid selection (Conclusion 3B, Figs \ref{fig:Combination_Centimorgans} \& \ref{fig:SexRatioBad}).
-Furthermore, we show that the spread of new sex-determination systems is not dominated by selection to balance the sex ratio (Conclusions 4A \& 4B, Fig \ref{fig:SexRatioBad}).
+However, we also find that trans-GSD transitions can be favoured in cases where linkage with the sex-determining locus is actually weakened (Conclusions 2 \& 3B, Fig \ref{fig:SexAntagTighter} \& \ref{fig:regionplots}), especially when there is haploid selection (Conclusion 3B, Figs \ref{fig:Combination_Centimorgans} \& \ref{fig:SexRatioBad}).
+Furthermore, we show that the spread of new sex-determination systems is not dominated by selection to balance the sex ratio (Conclusions 4 \& 5, Fig \ref{fig:SexRatioBad}).
 
@@
 %What we would like to stress is that sex-ratio selection alone cannot predict when new sex-determining systems can evolve.
-Significantly, with weak selection, we find that there is no difference in conditions allowing XY to ZW and ZW to XY transitions (Conclusion 4A) %, indicating that transitions in sex determination are not predominantly predicted by their effect on the sex ratio (i.e., the sex-ratio bias created by male haploid selection facilitates the spread of a neo-W allele into an XY system to the same degree that male haploid selection drives the spread of a neo-Y into a ZW system with a 1:1 sex ratio).
+Significantly, with weak selection, we find that there is no difference in conditions allowing XY to ZW and ZW to XY transitions (Conclusion 4) %, indicating that transitions in sex determination are not predominantly predicted by their effect on the sex ratio (i.e., the sex-ratio bias created by male haploid selection facilitates the spread of a neo-W allele into an XY system to the same degree that male haploid selection drives the spread of a neo-Y into a ZW system with a 1:1 sex ratio).
 %An asymmetry can develop when sex-linkage is tight (e.g., Fig \ref{fig:Combination_Centimorgans} near -25cM and 25cM) but under most circumstances we do not predict asymmetry between XY to ZW and ZW to XY transitions despite the presence/absence of sex-ratio selection.
@@
 New sex-determining alleles have previously been shown to spread when they arise in linkage with loci that experience sex differences in selection because beneficial associations build up between alleles that determine sex and alleles that are favoured in that sex~\cite{vanDoorn:2007eu,vanDoorn:2010hu,Ubeda:2015fx,Muralidhar2018}.
-In support of this hypothesis, researchers have identified genes on recently derived sex chromosomes that might be under sexually-antagonistic selection~\cite{Lindholm:2002dw,Tripathi:2009cw,Ser:2010iq}.
-However, we show that, if selected loci are tightly linked to the ancestral sex-determining locus, they can drive trans-GSD transitions which reduce sex-linkage (Conclusions 2A, 2B, \& 3B), thus widening the range of genomic locations that could be driving observed trans-GSD transitions.
+In support of this hypothesis, researchers have identified genes on recently derived sex chromosomes that might be under sexually-antagonistic selection~\cite{Lindholm:2002dw,Tripathi:2009cw,Roberts2009,Ser:2010iq}.
+However, we show that, if selected loci are tightly linked to the ancestral sex-determining locus, they can drive trans-GSD transitions which reduce sex-linkage (Conclusion 2, \& 3B), thus widening the range of genomic locations that could be driving observed trans-GSD transitions.
 In addition, we find that polymorphic sex determining systems (X, Y, and neo-W alleles all segregating) can be maintained when a selected locus is tightly linked to the ancestral sex-determining system (e.g., \nameref{fig:freqAll}B and \nameref{fig:freqAll}C), which is not possible with loose linkage~\cite{vanDoorn:2010hu}.
@@
 
+%Limitation 3: don't consider m alleles with similar k to ancester, no ancestral ESD considered
+In this study, we have only considered new sex-determining alleles of large effect. 
+However, we expect similar selective forces to act on masculinizing/feminizing alleles of weaker effect.
+For example, small effect masculinizing/feminizing alleles within a threshold model of sex determination can be favoured when linked to loci that experience sexually-antagonistic selection~\cite{Muralidhar2018}.
+These results echo those for large-effect neo-Y/neo-W alleles~\cite{vanDoorn:2007eu,vanDoorn:2010hu}.
+It should be noted, however, that the dynamics of sex-determining alleles with very weak effect will be influenced by genetic drift, which itself has been shown to bias transitions towards epistatically-dominant sex-determining systems when there is no selection \cite{Veller2017}.
+
 %Limitation 1: DEGENERATE Y
@@
 %While not explicitly studied, we also predict that Y or W degeneration would prevent fixation of the new sex-determining genes considered here.
-Degeneration around the Y or W could explain why trans-GSD transitions are not observed to be much more common than cis-GSD transitions \textcolor{red}{(citation?)} despite the fact that our models demonstrate that they are favoured under a wider range of conditions, especially with haploid selection.
+Degeneration around the Y or W could explain why trans-GSD transitions are not observed to be much more common than cis-GSD transitions \textcolor{red}{(citation?
+relevant citation below ok?
+I'm not aware of a study that can give an absolute generalisation for this across all clades.)} despite the fact that our models demonstrate that they are favoured under a wider range of conditions, especially with haploid selection.
 For example, there are a dozen sex chromosome configurations among Dipteran species but only one transition between male and female heterogamety~\cite{Vicoso:2015hf}, but Y degeneration or absence is also very common among \textit{Diptera}~\cite{Vicoso:2015hf}.
-
-%Limitation 3: don't consider m alleles with similar k to ancester, no ancestral ESD considered
-In this study, we have only considered new sex-determining alleles of large effect. 
-However, we expect similar selective forces to act on masculinizing/feminizing alleles of weaker effect.
-For example, small effect masculinizing/feminizing alleles within a threshold model of sex determination can be favoured when linked to loci that experience sexually-antagonistic selection~\cite{Muralidhar2018}.
-These results echo those for large-effect neo-Y/neo-W alleles~\cite{vanDoorn:2007eu,vanDoorn:2010hu}.
-It should be noted, however, that the dynamics of sex-determining alleles with very weak effect will be influenced by genetic drift, which itself has been shown to bias transitions towards epistatically-dominant sex-determining systems when there is no selection \cite{Veller2017}.
 
@@
 We have shown that tight sex-linkage and haploid selection can drive previously unexpected transitions between sex-determining systems.
-In particular, both can select for new sex-determining loci that are more loosely linked to loci under selection (Conclusions 2A, 2B \& 3B). 
-In addition, haploid selection can cause transitions in GSD analogous to those caused by purely sexually-antagonistic selection, eliminating the need for differences in selection between male and female diploids (Conclusion 2B \& 3B).
+In particular, both can select for new sex-determining loci that are more loosely linked to loci under selection (Conclusions 2 \& 3B). 
+In addition, haploid selection can cause transitions in GSD analogous to those caused by purely sexually-antagonistic selection, eliminating the need for differences in selection between male and female diploids (Conclusion 3A \& 3B).
 We conclude that haploid selection should be considered as a pivotal factor driving transitions between sex-determining systems. 
-Further, transitions involving haploid selection can be driven by sex-ratio selection or cause sex-ratio biases to evolve; to leading order, selection to balance the sex ratio and the benefits of hitch-hiking with haploid selected alleles are of equal magnitude (Conclusions 4A \& 4B).
+Further, transitions involving haploid selection can be driven by sex-ratio selection or cause sex-ratio biases to evolve; to leading order, selection to balance the sex ratio and the benefits of hitch-hiking with haploid selected alleles are of equal magnitude (Conclusions 4 \& 5).
 Overall, our results suggest several new scenarios under which new sex-determining systems are favoured, which could help to explain why the evolution of sex-determining systems is so dynamic.

### 2018-05-03 LaTeX/main_revised.tex
streamlining mikes results streamlining

@@
 In each generation, we census the genotype frequencies in male and female gametes before gametic competition. 
-Below, it is convenient to follow the ancestral equilibrium frequency of the $A$ allele among female gametes (eggs), $\hat{p}^\female_X$, and among X-bearing, $\hat{p}^\male_X$, and among Y-bearing, $\hat{p}^\male_Y$, male gametes (sperm/pollen).
-We also track the ancestral fraction of male gametes that are Y-bearing, $\hat{q}$, which may deviate from $1/2$ due to meiotic drive in males.
-
+%Below, it is convenient to follow the ancestral equilibrium frequency of the $A$ allele among female gametes (eggs), $\hat{p}^\female_X$, and among X-bearing, $\hat{p}^\male_X$, and among Y-bearing, $\hat{p}^\male_Y$, male gametes (sperm/pollen).
+%We also track the ancestral fraction of male gametes that are Y-bearing, $\hat{q}$, which may deviate from $1/2$ due to meiotic drive in males. 
+%
 After gametic competition, conjugation between male and female gametes occurs at random.
@@
 Finally, if only one haplotypic growth rate is greater than one, the new sex-determining allele can always invade when arising at a locus that is tightly linked to the selected locus ($R\approx0$).  
-Furthermore, it can be shown that the leading eigenvalue declines with $R$, and invasion requires that $R$ is sufficiently small such that: 
+Furthermore, it can be shown that the leading eigenvalue declines with recombination rate, $R$, and invasion requires that $R$ is sufficiently small such that: 
 \begin{equation}\label{eq:lambdasGen}
 %\frac{\chi_{mA}}{\Lambda_{mA}-1}+\frac{\chi_{ma}}{\Lambda_{ma}-1}>0.
-\chi_{ma}^{(XY)}/\left(\Lambda_{ma}^{(XY)} - 1\right) + \chi_{mA}^{(XY)}/\left(\Lambda_{mA}^{(XY)} - 1\right) < 1
+\chi_{ma}^{(XY)}/\left(\Lambda_{ma}^{(XY)} - 1\right) + \chi_{mA}^{(XY)}/\left(\Lambda_{mA}^{(XY)} - 1\right) < 1.
 \end{equation}
 \noindent 
-where $\chi_{mi}^{(XY)}>0$ is the rate at which mutant haplotypes on background $i\in\{A,a\}$ recombine onto the other $\mathbf{A}$ locus background in heterozygotes (proportional to $R$; we call this the ``dissociative force" as it breaks down linkage disequilibrium), see Table \ref{tab:haplotype_growth}.
-Condition \ref{eq:lambdasGen} may or may not be satisfied for the full range of locations of the new sex-determining locus, including $R=1/2$, depending on the nature of selection.  
-Interpreting this condition, if we assume that only the $mA$ haplotype would increase in frequency when $R=0$ ($\Lambda_{ma}^{(XY)}<1<\Lambda_{mA}^{(XY)}$) then the first term on the left-hand side of \eqref{eq:lambdasGen} is negative and invasion requires that growth rate of $mA$ haplotypes ($\Lambda_{mA}^{(XY)}-1>0$) and the rate at which they are produced by recombination ($\chi_{ma}^{(XY)}$) are sufficiently large relative to the rate of decline of $ma$ haplotypes ($1-\Lambda_{ma}^{(XY)}>0$) and the rate at which $m$ and $A$ are dissociated by recombination ($\chi_{mA}^{(XY)}$).
+Here $\chi_{mi}^{(XY)}>0$ is the rate at which mutant haplotypes on background $i\in\{A,a\}$ recombine onto the other $\mathbf{A}$ locus background in heterozygotes (which is proportional to $R$,  see Table \ref{tab:haplotype_growth}).
+This is a ``dissociative force" that breaks down linkage disequilibrium.
+
+Condition \ref{eq:lambdasGen} may or may not be satisfied for the full range of locations of the new sex-determining locus, including $R=1/2$ (e.g., on an autosome), depending on the nature of selection.
+Interpreting this condition, if we assume that only the $mA$ haplotype would increase in frequency when $R=0$ (i.e., $\Lambda_{ma}^{(XY)}<1<\Lambda_{mA}^{(XY)}$), then the first term on the left-hand side of \eqref{eq:lambdasGen} is negative and invasion requires that growth rate of $mA$ haplotypes ($\Lambda_{mA}^{(XY)}-1>0$) and the rate at which they are produced by recombination ($\chi_{ma}^{(XY)}$) are sufficiently large relative to the rate of decline of $ma$ haplotypes ($1-\Lambda_{ma}^{(XY)}>0$) and the rate at which $m$ and $A$ are dissociated by recombination ($\chi_{mA}^{(XY)}$).
 
@@
 
-We draw three main points about the generic invasion of neo-Y and neo-W mutations from Table \ref{tab:haplotype_growth}:
+The haplotypic growth rates and dissociative forces are listed in Table 2 for a neo-Y and neo-W invading an ancestrally XY system.
+From this table and the arguments above we draw three main points about the generic invasion of neo-Y and neo-W mutations (without specifying the ancestral equilibrium):
 (1) invasion by a neo-Y (neo-W) does not directly depend on the fitness of female (male) diploids. %(for a given set of equilibrium allele frequencies).
@@
 %This can lead to (1) XX females having lower than maximum fitness ($\Lambda_{W'A}^{(XY)}>1$) and/or (2) the Y carrying alleles that are beneficial in females. 
-\noindent Broadly, it is possible for neo-W females to have higher fitness than the XX females because of the way that the ancestral X experiences selection in both males and females.
-Consequently, (a) the ancestral X may be unable to specialize strongly on an allele favoured in females and (b) an allele can be associated with the Y and yet favoured in females. 
-In turn, a neo-W can spread because (a) it is only found in females and is therefore unleashed from counterselection in males (corresponding to $\Lambda_{W'A}^{(XY)}>1$) and (b) it allows Y-associated alleles into females (corresponding to $\Lambda_{W'a}^{(XY)}>1$).
-
-To clarify the conditions under which trans-GSD transitions occur, we focus here on cases where there is no haploid selection and discuss the additional effect of haploid selection in \nameref{app:inv_cond}.
-Firstly, we discuss an example where neo-W-$A$ haplotypes spread (case (a), where $\Lambda_{W'A}^{(XY)}>1$).
+\noindent Broadly, it is possible for neo-W females to have higher fitness than XX females for three reasons.
+Firstly, because the ancestral X experiences selection in both males and females, it may be unable to specialize strongly on an allele favoured in females.
+Secondly, an allele can be associated with the Y and yet favoured in females.
+Thirdly, haploid selection can create a male sex-ratio bias. 
+In turn, a neo-W can spread because (a) it is only found in females and is therefore unleashed from counterselection in males (corresponding to $\Lambda_{W'A}^{(XY)}>1$), (b) it allows Y-associated alleles into females (corresponding to $\Lambda_{W'a}^{(XY)}>1$), and (c) it may produce the rarer sex and thus be favoured by sex-ratio selection (increasing both haplotypic growth rates).
+To clarify conditions under which trans-GSD transitions can occur, we focus here on cases where there is no haploid selection (and hence no sex-ratio bias) and discuss the additional effect of haploid selection in \nameref{app:inv_cond}.
+
+We first give an example where neo-W-$A$ haplotypes can spread because the neo-W is unleashed from counterselection in males (case (a), where $\Lambda_{W'A}^{(XY)}>1$).
 When $A$ is female beneficial and $a$ is male beneficial, the $A$ allele can be fixed ($\hat{p}^\female_X=\hat{p}^\male_X=1$) or polymorphic (0<$\hat{p}^\female_X, \hat{p}^\male_X$<1) on the X. 
@@
 Neo-Ws, however, spend no time in males and can build stronger associations with the female-beneficial $A$ allele, allowing them to spread (see gray region in Fig \ref{fig:regionplots}A).
-Secondly, we dicuss an example where neo-W-$a$ haplotypes spread (case (b), where $\Lambda_{W'a}^{(XY)}>1$). 
+
+We next give an example where neo-W-$a$ haplotypes can spread because they bring in female beneficial alleles associated with the Y (case (b), where $\Lambda_{W'a}^{(XY)}>1$). 
 When there is overdominance in males, X-$A$ Y-$a$ males have high fitness and the $A$ allele is favoured by selection on the X background in males.
 Therefore, the $A$ allele can be polymorphic or even fixed on the X background despite selection favouring the $a$ allele in females (e.g., see outlined region in Fig \ref{fig:regionplots}B and~\cite{Lloyd1977,Otto2014}).
-In such cases, neo-W-$a$ haplotypes can spread because they create more $Aa$ and $aa$ females when pairing with an X-bearing gamete from males and because they bring Y-$a$ haplotypes into females, where it has higher fitness (Fig \ref{fig:model_outline}D).
+In such cases, neo-W-$a$ haplotypes can spread because they create more $Aa$ and $aa$ females when pairing with an X-bearing gamete from males and because they bring more of the Y-$a$ haplotype into females, where it has higher fitness (Fig \ref{fig:model_outline}D).
 
@@
 
-In some cases, both W-$A$ and W-$a$ haplotypes can spread.
+In some cases, both neo-W-$A$ and neo-W-$a$ haplotypes can spread.
 For example, when $AA$ individuals have low fitness in females yet the $A$ is polymorphic or fixed on the X background due to overdominance in males (Fig \ref{fig:regionplots}B and \ref{fig:regionplots}C), both neo-W-$A$ and neo-W-$a$ haplotypes produce fewer unfit $AA$ females.
 This is true for the neo-W-$A$ haplotype because it can pair with a Y-$a$ haplotype and still be female. 
-Wherever both haplotypic growth rates are greater than one, invasion by a neo-W is expected regardless of its linkage with the selected locus (i.e., for any $R$, see \nameref{fig:positionOverdominance} and \nameref{fig:temporalOverdominance} for examples).
+Whenever both haplotypic growth rates are greater than one, invasion by a neo-W is expected regardless of its linkage with the selected locus (i.e., for any $R$, see \nameref{fig:positionOverdominance} and \nameref{fig:temporalOverdominance} for examples).
 As a consequence, evolution can favor a new sex determination system on a different chromosome ($R = 1/2$), despite the fact that this unlinks the sex-determining locus from the selected locus.
@@
 With haploid selection, Conclusions 1 \& 2 continue to apply (\nameref{app:inv_cond}). 
-The parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread under various forms of haploid selection are plotted in \nameref{fig:regionMaleDrive}, \nameref{fig:regionMaleGS}, \nameref{fig:regionFemaleDrive}, \nameref{fig:regionFemaleGS}
+The parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread under various forms of haploid selection are plotted in \nameref{fig:regionMaleDrive}, \nameref{fig:regionMaleGS}, \nameref{fig:regionFemaleDrive}, \nameref{fig:regionFemaleGS}.
 In particular, we note that adding haploid selection allows shifts in sex determination to a different chromosome ($R=1/2$) even when selection is sexually antagonistic with directional selection in each diploid sex, e.g., \nameref{fig:SexAntagTighterMaleDrive}.
 Furthermore, haploid selection allows variation to be maintained by ploidally-antagonistic selection, under which trans-GSD transitions may also be favoured, \nameref{fig:regionPloidAntag}.
-Some cases of XY $\rightarrow$ ZW transitions where $r=0$, $R=1/2$ and selection is ploidally-antagonistic (meiotic drive in males opposed by diploid selection) were studied by Kozielska et al.
-\cite{Kozielska:2010vm}, who found that sex ratio biases are reduced during these transitions.
-However, such transitions do not necessarily involve a reduction of sex ratio bias. 
-For example, with haploid selection in females and XY sex determination, sex ratios are not ancestrally biased but ZW invasion can occur (\nameref{fig:regionPloidAntag}).
+Some cases of XY $\rightarrow$ ZW transitions where $r=0$, $R=1/2$, and selection is ploidally-antagonistic (meiotic drive in males opposed by diploid selection) were studied by Kozielska et al.
+\cite{Kozielska:2010vm}, who found that sex-ratio biases are reduced during these transitions.
+However, such transitions are not always driven by selection to reduce sex-ratio bias. 
+For example, with XY sex determination and haploid selection in females, sex ratios are not ancestrally biased yet a neo-W can invade (\nameref{fig:regionPloidAntag}).
 
@@
 \textbf{New sex-determining alleles (causing cis- \textit{or} trans-GSD transitions) can spread if they arise more closely linked with a locus that experiences selection than the ancestral-sex-determining locus is ($R<r$).}
-\textcolor{red}{[consistent with van Doorn \& Kirkpatrick 2007, 2010, except that we add haploid selection, these connections are mentioned above], consistent with Ubeda et al 2015 (assuming ancestral ESD something similar to $r=1/2$, invasion with $R<1/2$.), not yet mentioned  }
+%\textcolor{red}{[consistent with van Doorn \& Kirkpatrick 2007, 2010, except that we add haploid selection, these connections are mentioned above], consistent with Ubeda et al 2015 (assuming ancestral ESD something similar to $r=1/2$, invasion with $R<1/2$.), not yet mentioned [mentioned below on 370]  }
 \vspace{0.5cm}

### 2018-05-03 LaTeX/response.tex
more minor adjustments to Tight Linkage sections, beginning on response letter detail with new changes

@@
 
+\textcolor{blue}{
+We thank the reviewer for their careful consideration of our manuscript and pithy summary.
+Indeed, we have incorporated the sentiment of ``a striking evolutionary puzzle'' to help frame our study, L51.
+We believe that the modifications outlined below have helped to further improve the communication of our results.
+}
+
 \noindent\subsection{}
@@
 \textcolor{blue}{
-One could interpret our diploid selection as a combination of viability and fertility selection, where fertility selection is independent of the mating partner.
-Fertility selection that depends on the mating pair and sexual selection require a different formulation.
+One could interpret our diploid selection terms as a combination of viability and fertility selection, where fertility selection is independent of the mating partner.
+However, fertility selection that depends on the mating pair would require a different formulation.
 We now note this in the model section (L120-122):
 ``Diploid males and females then experience viability and/or individual-based fertility selection, with relative fitnesses $w_{AA}^{\circ}$, $w_{Aa}^{\circ}$, and $w_{aa}^{\circ}$.
-We do not consider fertility selection based on the mating pair or sexual selection."
+We do not consider fertility selection that depends on the mating partner, e.g., sexual selection with variation in choosiness."
 }
@@
 \textcolor{blue}{
-We now call these terms the ``dissociative force" as they break down linkage disequilibrium (L161). 
+We now refer to the $\chi_{mi}^{(XY)}$ terms as the ``dissociative force" as they break down linkage disequilibrium (L161). 
 We have attempted various graphical schemes for representing the three loci in two sexes and the associations that evolve between them in various scenarios. 
 However, apart from Fig 1, we found these too complicated or opaque to be useful. 
+Instead, we have substantially restructured the results section and reduced the technicality (see responses XXXXXX), which should generally help to make the important messages clearer. 
+Specific to this point, in the paragraph 179-199, we itemize three take-home messages from table 2 about the ``haplotypic growth rates'' and ``dissociative forces''. 
 }
@@
 \textcolor{blue}{
-We now mention that the model is deterministic, and hence ignores drift (L127-128). 
-When discussing the model limitations at the end of the Discussion we now mention a study on the effect of drift during trans-GSD transitions, which tend to drift in the direction of epistatically-dominant sex-determining loci (L529-532): ``It should be noted, however, that the dynamics of sex-determining alleles with very weak effect will be influenced by genetic drift, which itself has been shown to cause trans-GSD transitions (Veller et al 2017)."}
+This is true, we now mention that the model is deterministic, and hence ignores drift (L130-131). 
+As suggested, when discussing the model limitations at the end of the Discussion we now mention a study on the effect of drift during trans-GSD transitions, which tend to drift in the direction of epistatically-dominant sex-determining loci (L538-541): ``It should be noted, however, that the dynamics of sex-determining alleles with very weak effect will be influenced by genetic drift, which itself has been shown to cause trans-GSD transitions (Veller et al 2017)."}
 
@@
 \noindent\paragraph{Response}
-\textcolor{blue}{We have dropped the words ``the leading eigenvalues are".}
+\textcolor{blue}{Thank you. We have dropped the words ``the leading eigenvalues are".}
 
@@
 \textcolor{blue}{We have made the suggested replacements.
+In addition, we have added a more detailed discussion of how gametic competition relates to the number of mating partners involved, L108-118 (see also response XXXXXX).
+Specifically, our model explicitly considers within-ejaculate competition or competition among sperm from many males but not competition among sperm from pairs (or small numbers) of males.
 %n the introduction we mention that sperm competition has been shown to alter allele frequencies and fitness, and in this case we now mention this was shown within a single ejaculate (L68).
@@
 
+\textcolor{blue}{
+We thank the reviewer for their thoughtful, positive, and very constructive comments.
+We have substantially restructured the Introduction, Model, and Results in response to these suggestions (and comments from other reviewers), as outlined below.
+This has significantly improved the accessibility and appeal of our results. 
+}
+
 \noindent\subsection{}
@@
 \textcolor{blue}{
-Thank you for these very constructive suggestions. We have simplified the introduction according to the suggested format: 
+We have simplified the introduction according to the suggested format.
+In addition, when discussing holes in current theory we have expanded our discussion of previous studies that include haploid selection, as suggested by reviewer 3.
+To accommodate these changes, we have moved the discussion of empirical evidence for haploid selection to the discussion (L441-454). The introduction is now structured as follows:
 \begin{enumerate}
@@
 (L39-48)}
-\item[5.]{Next, we introduce the most significant model feature, haploid selection, which we present as an evolutionary problem (as suggested by reviewer 1) in light of (1) and (2). (L49-56) }
+\item[5.]{Next, we introduce the most significant novel model feature, haploid selection, which we present as an evolutionary problem in light of (1) and (2). (L49-56) }
 \item[6.]{The sixth paragraph then describes previous studies that have included haploid selection (see also reviewer 3 recommendations).
@@
 \item[7.]{Finally, we lay out our main results in this context.
-This makes it clear that our general model is necessary to determine the important forces driving transitions in sex determination.
+This makes it clear that our general model is necessary to determine the important forces driving transitions in sex determination (e.g., considering various genomic locations).
 We particularly highlight the unexpected conclusions that our model allows us to reach.
@@
 \end{enumerate}
-To accommodate these changes, we have moved the discussion of empirical evidence for haploid selection to the discussion (L441-454). 
 }
@@
 \textcolor{blue}{
+This is an excellent suggestion and has greatly improved the clarity of presentation in our manuscript.
+In the results, we have specifically highlighted our main conclusions in the style of Orr 1998 (slightly modified from the three conclusions suggested by the reviewer):
 %We now give 3 main conclusions at the end of the introduction (L69) which echo those mentioned by the reviewer (looser linkage can evolve, equal selection to increase or decrease the sex ratio, ESD does not always invade biased sex ratio; all of which suggest haploid selection makes conditions for transitions more permissive).
-Following this advice, we now highlight our main conclusions in the results section in the style of Orr 1998:
 \begin{enumerate}
-\item[(1)] ancestrally-tight sex-linkage allows trans-GSD transitions but not cis-GSD transitions (L228-230)
-\item[(2A)] with ancestrally-tight sex-linkage, trans-GSD transitions (which weaken sex-linkage and can lead to polymorphic sex determination systems) can be driven by selection to better specialize on the ancestrally-non-heterogametic sex (L282-286)
-\item[(2B)] with ancestrally-tight sex-linkage, haploid selection can spur trans-GSD transitions (which weaken sex-linkage and equalize the sex-ratio) even when selection is sexually-antagonistic in diploids  (L288-293)
-\item[(3A)] when selection is weak relative to ancestral sex-linkage, cis- or trans-GSD transitions can occur when the new sex-determining allele increases linkage with selected loci (L324-326)
-\item[(3B)] when selection is weak relative to ancestral sex-linkage, haploid selection allows trans-GSD transitions to occur even when the new sex-determining allele decreases linkage with the selected locus (L327-330)
-\item[(4A)] when selection is weak relative to ancestral sex-linkage, sex-ratio selection is exactly equal in magnitude to the selection imposed by associations with selected alleles (and thus transitions can increase or decrease the sex-ratio bias) (L350-353)
-\item[(4B)] transitions from genetic to environmental sex-determination are not straightforwardly predicted by selection to balance the zygotic sex ratio when haploid selection is present (L411-413)
+\item[(1)] Selection on loci in or near the non-recombining region around the ancestral sex-determining locus ($r\approx0$) prevents cis-GSD transitions (XY $\leftrightarrow$ XY, ZW $\leftrightarrow$ ZW) but can spur trans-GSD transitions (XY $\leftrightarrow$ ZW).
+(L228-230)
+\item[(2)] With tight linkage between a selected locus and the ancestral sex-determining locus ($r\approx0$), trans-GSD transitions (XY $\leftrightarrow$ ZW) can be favoured by selection \textit{even if they weaken sex-linkage} ($r<R$), potentially shifting sex determination to a different chromosome ($R=1/2$).
+Such transitions can also lead to the maintenance of multifactorial sex-determination systems. (L282-286)
+\item[(3A)] New sex-determining alleles (causing cis- \textit{or} trans-GSD transitions) can spread if they arise more closely linked with a locus that experiences selection than the ancestral-sex-determining locus is ($R<r$).
+(L324-326)
+\item[(3B)] New sex-determining alleles (causing trans-GSD transitions, XY $\leftrightarrow$ ZW) can spread even if they arise less closely linked with a locus that experiences selection than the ancestral-sex-determining locus is ($r<R$), requiring haploid selection.
+(L327-330)
+\item[(4)] When selection is weak relative to recombination, the presence of haploid selection equally favors the spread of new sex determination systems that reduce sex-ratio bias (benefiting from Fisherian sex ratio selection) or generate a sex-ratio bias (benefiting from associations with selected alleles).
+(L350-353)
+\item[(5)] Transitions from genetic to environmental sex-determination are not straightforwardly predicted by selection to balance the zygotic sex ratio when haploid selection is present.  (L411-413)
 %\vspace{0.25cm}\\
 \end{enumerate}
+These conclusions are also more clearly laid out in the introduction (L48-49, L74-85) and are referenced directly in summarisations in the discussion (L424-432, L543-554). 
 %As (1A), (1B), and (2) have some antecedents in the literature, we discuss these immediately below each conclusion. 
@@
 \textcolor{red}{what is new and what is confirmatory? [see red notes in main text in conclusions]} 
+}
+
+\textcolor{blue}{
+Furthermore, to reduce the technicality of our presentation, we have restructured the presentation of the results subsections "Generic invasion by a neo-Y or neo-W" and ``Tight linkage with the ancestral sex-determining locus''.
+Some details have been moved to the supplementary material (particularly, proofs regarding the leading eigenvalue, formally LXXX-XXX). 
+In the ``Tight linkage'' section, we now first describe specific cases why neo-W's can have improved female fitness, L235-259, with more focus on non-technical interpretation (e.g., L237-240). 
+Then we discuss the fact that looser sex-linkage can evolve (L260-275, Conclusion 2). 
 }
@@
 \noindent\paragraph{Response}
-\textcolor{blue}{This section has been substantially rewritten.
-A roughly corresponding comment now reads: ``...haploid selection is typically sex-specific in that it usually occurs among gametes produced by one sex only." (L51-52)}
+\textcolor{blue}{
+Thank you for this suggestion, ``sex-limited'' is a more efficient way to communicate that haploid selection often only occurs in gametes produced by one sex. 
+We now use ``sex-limited'' throughout, with two exceptions.
+L72 and L126, where we are referring to the fact that we model haploid selection in either/both sexes (focussing on sex-limited cases in our examples).
+This section was re-written but the section that roughly corresponds to the highlighted sentence now reads: ``...haploid selection is typically sex-limited in that it usually occurs among gametes produced by one sex only." (L51-52)
+}
 
@@
 \noindent\paragraph{Response}
-\textcolor{blue}{We have rewritten the Introduction as well as our main conclusions in line with this reviewers major comments (see Responses 2.1 and 2.2).}
+\textcolor{blue}{
+As suggested above, we have re-written to focus on our most novel findings, which are now laid our more specifically, e.g., L71-85 (see also Responses 2.1 and 2.2). 
+}
 
@@
 \textcolor{blue}{
+
 This is an important assumption.
@@
 However, this reduction in parameter space is smooth and does not preclude transitions, meaning the qualitative conclusions are robust.
+\textcolor{red}{I actually think that parameter space is only reduced because they also have a locus near the ancestral SDR that selects against new sex determining systems.
+In a 3-locus system, like ours, I would expect the $\lambda-1$ to be lower for incomplete penetrance (partial epistatic dominance) but not to change sign.
+}
 Further, there are many systems in which one sex-determining allele is epistatically dominant.

### 2018-05-03 LaTeX/main_revised.tex
more minor adjustments to Tight Linkage sections, beginning on response letter detail with new changes

@@
 This poses an apparent evolutionary problem. 
-On one hand, haploid selection is typically sex-specific in that it usually occurs among gametes produced by one sex only~\cite{Mulcahy:1996ha,JOSEPH:2004haa,Ubeda:2005gw,Lindholm:2016cw}. 
+On one hand, haploid selection is typically sex-limited in that it usually occurs among gametes produced by one sex only~\cite{Mulcahy:1996ha,JOSEPH:2004haa,Ubeda:2005gw,Lindholm:2016cw}. 
 Therefore, one might expect new sex-determining systems to benefit from close linkage with haploid selected loci, as found for sex-differences in diploid selection~\cite{vanDoorn:2007eu,vanDoorn:2010hu, Muralidhar2018}.
@@
 %Previous models with haploid selection
-Two previous studies have considered the spread of GSD with sex-specific meiotic drive~\cite{Kozielska:2010vm,Ubeda:2015fx} under a limited number of possible genetic architectures and diploid selective regimes.
+Two previous studies have considered the spread of GSD with sex-limited meiotic drive~\cite{Kozielska:2010vm,Ubeda:2015fx} under a limited number of possible genetic architectures and diploid selective regimes.
 Ubeda et al. (2015)~\cite{Ubeda:2015fx} considered ancestral-ESD (with no sex-ratio bias) and numerically showed that new GSD alleles can spread if they arise in linkage with meiotic drive loci. 
@@
 If $r<1/2$, then associations between ancestral sex-determining alleles and selected alleles can be present in new male gametes/gametophytes. 
-Panel B: Haploid selection is often sex-specific, occurring during haploid production or competition in either males or females. 
+Panel B: Haploid selection is often sex-limited, occurring during haploid production or competition in either males or females. 
 For example, haploid selection in males only is represented by the dashed circle.  
@@
 %This can lead to (1) XX females having lower than maximum fitness ($\Lambda_{W'A}^{(XY)}>1$) and/or (2) the Y carrying alleles that are beneficial in females. 
-\noindent Broadly, it is possible for neo-W females to have higher fitness than XX females for three reasons.
+\noindent 
+To clarify conditions under which trans-GSD transitions can occur, we focus here on cases where there is no haploid selection (and hence no sex-ratio bias) and discuss the additional effect of haploid selection in \nameref{app:inv_cond}.
+Broadly, it is possible for neo-W females to have higher fitness than XX females for two reasons.
 Firstly, because the ancestral X experiences selection in both males and females, it may be unable to specialize strongly on an allele favoured in females.
 Secondly, an allele can be associated with the Y and yet favoured in females.
-Thirdly, haploid selection can create a male sex-ratio bias. 
-In turn, a neo-W can spread because (a) it is only found in females and is therefore unleashed from counterselection in males (corresponding to $\Lambda_{W'A}^{(XY)}>1$), (b) it allows Y-associated alleles into females (corresponding to $\Lambda_{W'a}^{(XY)}>1$), and (c) it may produce the rarer sex and thus be favoured by sex-ratio selection (increasing both haplotypic growth rates).
-To clarify conditions under which trans-GSD transitions can occur, we focus here on cases where there is no haploid selection (and hence no sex-ratio bias) and discuss the additional effect of haploid selection in \nameref{app:inv_cond}.
+In turn, a neo-W can spread because (a) it is only found in females and is therefore unleashed from counterselection in males (corresponding to $\Lambda_{W'A}^{(XY)}>1$), (b) it allows Y-associated alleles into females (corresponding to $\Lambda_{W'a}^{(XY)}>1$).
 
@@
 This is true for the neo-W-$A$ haplotype because it can pair with a Y-$a$ haplotype and still be female. 
-Whenever both haplotypic growth rates are greater than one, invasion by a neo-W is expected regardless of its linkage with the selected locus (i.e., for any $R$, see \nameref{fig:positionOverdominance} and \nameref{fig:temporalOverdominance} for examples).
+Whenever both haplotypic growth rates are greater than one, invasion by a neo-W is expected regardless of its linkage with the selected locus (i.e., for any $R$), see \nameref{fig:positionOverdominance} and \nameref{fig:temporalOverdominance} for examples.
 As a consequence, evolution can favor a new sex determination system on a different chromosome ($R = 1/2$), despite the fact that this unlinks the sex-determining locus from the selected locus.
@@
 For example, with XY sex determination and haploid selection in females, sex ratios are not ancestrally biased yet a neo-W can invade (\nameref{fig:regionPloidAntag}). 
+We further discuss how the spread of neo-sex-determining alleles is influenced by associations with haploid selected loci in the next section.
 
@@
 For example, if the $\mathbf{A}$ locus is unlinked to the ancestral sex-determining locus ($r=1/2$, which implies that $ \hat{p}^\male_Y-\hat{p}^\male_X =0$), a more closely linked neo-W ($R<1/2$) can always invade.
+Thus,
 %In this case, there is no ancestral association between $\mathbf{A}$ alleles and sex chromosomes in males, $\left( \hat{p}^\male_Y-\hat{p}^\male_X \right)=0$, see Eq \eqref{eq:freq_diffs}. 
 %The second term in Eq \eqref{eq:lambda_neoW} therefore disappears and invasion depends only on the sign of $(r-R)$.%, as in the case of the neo-Y.
-However, with haploid selection and some ancestral sex-linkage ($r<1/2$; allowing allele frequency differences on the X and Y), the term in square brackets in Eq \eqref{eq:lambda_neoW} can be positive.
-This implies the following two conclusions:
 
@@
 
-%However, with haploid selection and some ancestral sex-linkage ($r<1/2$; allowing allele frequency differences on the X and Y), the additional term in Eq \eqref{eq:lambda_neoW} can be positive.
-%This implies, 
-%\vspace{0.5cm}
+\noindent
+However, with haploid selection and some ancestral sex-linkage ($r<1/2$; allowing allele frequency differences on the X and Y), the term in square brackets in Eq \eqref{eq:lambda_neoW} can be positive.
+This implies,
+
+\vspace{0.5cm}
 \noindent\textit{Conclusion 3B:}\
-\textbf{New sex-determining alleles (causing trans-GSD transitions, XY $\leftrightarrow$ ZW) can spread even if they arise less closely linked with a locus that experiences selection than the ancestral-sex-determining locus is ($r<R$), requiring haploid selection and some initial sex-linkage ($r<1/2$).}
+\textbf{New sex-determining alleles (causing trans-GSD transitions, XY $\leftrightarrow$ ZW) can spread even if they arise less closely linked with a locus that experiences selection than the ancestral-sex-determining locus is ($r<R$), requiring haploid selection.}
 \vspace{0.5cm}
@@
 %Indeed, invasion typically occurs when the neo-W is more closely linked to the selected locus than the ancestral sex-determining region (Fig \ref{fig:Combination_Centimorgans}).
-To clarify the parameter space under which invasion occurs with weak selection ($\lambda_{W'}^{(XY)}>1$), we focus on cases where dominance coefficients are equal in the two sexes, $h^\female=h^\male$, and haploid selection only occurs in one sex (e.g., during male meiosis only).
+To clarify the parameter space under which invasion occurs with weak selection ($\lambda_{W'}^{(XY)}>1$) and $R>r$, we focus on cases where dominance coefficients are equal in the two sexes, $h^\female=h^\male$, and haploid selection only occurs in one sex (e.g., during male meiosis only).
 Table \ref{tab:specialcases} then gives the conditions required for unlinked ($R=1/2$) neo-W invasion when there is some ancestral sex-linkage ($r<1/2$; e.g., the selected locus is on the ancestral sex chromosome and the novel sex-determining locus arises on an autosome).
@@
 For example, in the platyfish (\textit{Xiphophorus maculatus}), X,Y, and W alleles segregate at one locus (or two closely-linked loci) near to potentially sexually-antagonistic genes for pigmentation and sexual maturity~\cite{Kallman1965,Kallman1968, Volff2001, Schultheis2006}.
-Furthermore, several rodent species maintain \textcolor{red}{dominant?} feminizing alleles along with the ancestral X and Y sex-determination alleles (reviewed in~\cite{Fredga1994}). 
+Furthermore, several rodent species maintain feminizing alleles along with the ancestral X and Y sex-determination alleles (reviewed in~\cite{Fredga1994}). 
 In nine \textit{Akadon} rodent species, it appears that male-determining-\textit{sry} expression is suppressed by an autosomal feminizing allele (a neo-W allele), creating XY females~\cite{Bianchi2002,Sanchez2010}.
@@
 
-%Limitation 3: don't consider m alleles with similar k to ancester, no ancestral ESD considered
-In this study, we have only considered new sex-determining alleles of large effect. 
-However, we expect similar selective forces to act on masculinizing/feminizing alleles of weaker effect.
-For example, small effect masculinizing/feminizing alleles within a threshold model of sex determination can be favoured when linked to loci that experience sexually-antagonistic selection~\cite{Muralidhar2018}.
-These results echo those for large-effect neo-Y/neo-W alleles~\cite{vanDoorn:2007eu,vanDoorn:2010hu}.
-It should be noted, however, that the dynamics of sex-determining alleles with very weak effect will be influenced by genetic drift, which itself has been shown to bias transitions towards epistatically-dominant sex-determining systems when there is no selection \cite{Veller2017}.
-
 %Limitation 1: DEGENERATE Y
@@
 %While not explicitly studied, we also predict that Y or W degeneration would prevent fixation of the new sex-determining genes considered here.
-Degeneration around the Y or W could explain why trans-GSD transitions are not observed to be much more common than cis-GSD transitions \textcolor{red}{(citation?
-relevant citation below ok?
-I'm not aware of a study that can give an absolute generalisation for this across all clades.)} despite the fact that our models demonstrate that they are favoured under a wider range of conditions, especially with haploid selection.
+Degeneration around the Y or W could explain why trans-GSD transitions are not observed to be much more common than cis-GSD transitions despite the fact that our models demonstrate that they are favoured under a wider range of conditions, especially with haploid selection.
 For example, there are a dozen sex chromosome configurations among Dipteran species but only one transition between male and female heterogamety~\cite{Vicoso:2015hf}, but Y degeneration or absence is also very common among \textit{Diptera}~\cite{Vicoso:2015hf}.
+
+%Limitation 3: don't consider m alleles with similar k to ancester, no ancestral ESD considered
+In this study, we have only considered new sex-determining alleles of large effect. 
+However, we expect similar selective forces to act on masculinizing/feminizing alleles of weaker effect.
+For example, small effect masculinizing/feminizing alleles within a threshold model of sex determination can be favoured when linked to loci that experience sexually-antagonistic selection~\cite{Muralidhar2018}.
+These results echo those for large-effect neo-Y/neo-W alleles~\cite{vanDoorn:2007eu,vanDoorn:2010hu}.
+It should be noted, however, that the dynamics of sex-determining alleles with very weak effect will be influenced by genetic drift, which itself has been shown to bias transitions towards epistatically-dominant sex-determining systems when there is no selection \cite{Veller2017}.
 
@@
 A-D show when each of the neo-W haplotypes invades an internally stable equilibrium with $a$ fixed on the Y (found by setting $r=0$).
-The y-axis shows directional selection in diploids of both sexes, $s^\female=s^\male$, and the x-axes show sex-specific drive, $\alpha_\Delta^\circ$, or haploid competition, $t^\circ$.
+The y-axis shows directional selection in diploids of both sexes, $s^\female=s^\male$, and the x-axes show sex-limited drive, $\alpha_\Delta^\circ$, or haploid competition, $t^\circ$.
 The top left and bottom right quadrants therefore imply ploidally-antagonistic selection (and these are the only places where neo-W haplotypes can invade).

### 2018-05-17 LaTeX/response.tex
Sally's main text edits incorporated, not Figure changes after Figure 1

@@
 We thank the reviewer for their careful consideration of our manuscript and pithy summary.
-Indeed, we have incorporated the sentiment of ``a striking evolutionary puzzle'' to help frame our study, L51.
-We believe that the modifications outlined below have helped to further improve the communication of our results.
+We have incorporated the sentiment of ``a striking evolutionary puzzle'' to help frame our study, L51.
+Below, we itemize further improvements we have made that correspond to more specific reviewer comments.
 }
@@
 In addition, we have added a more detailed discussion of how gametic competition relates to the number of mating partners involved, L108-118 (see also response XXXXXX). 
-Specifically, our model explicitly considers within-ejaculate competition or competition among sperm from many males but not competition among sperm from pairs (or small numbers) of males.
+Specifically, we note that our model explicitly considers within-ejaculate competition or competition among sperm from many males but not competition among sperm from pairs (or small numbers) of males.
 %n the introduction we mention that sperm competition has been shown to alter allele frequencies and fitness, and in this case we now mention this was shown within a single ejaculate (L68).
@@
 
+\noindent\paragraph{Response}
+\textcolor{blue}{
+As discussed further below (response XXXXX), we have highlighted conclusions in the results section as suggested. 
+To further reduce the technicality of our presentation, we have also revised the results section. 
+In particular, we have restructured the presentation of the subsections ``Generic invasion by a neo-Y or neo-W'' and ``Tight linkage with the ancestral sex-determining locus''. 
+In the ``Generic invasion by a neo-Y or neo-W" section, we have moved some details to the supplementary material (particularly, proofs regarding the leading eigenvalue, formally LXXX-XXX). 
+Now, we focus on explaining the intuition behind our technical results.  
+For example, we first discuss the `haplotypic growth rates' and 'dissociative forces' (L158-170 and `interpreting this condition...', L173).
+We then lay out three specific conclusions (L179-199). 
+In the ``Tight linkage'' section, we now first describe specific cases why neo-W's can have improved female fitness, L235-259, with more focus on non-technical interpretation (e.g., L237-240). 
+Then we discuss the fact that looser sex-linkage can evolve (L260-275, Conclusion 2). 
+This re-organisation allows us to break down the logic behind Conclusion 2 more clearly. 
+}
+
+\noindent\subsection{}
 One potential way to help readers -- particularly those interested in what the paper has to say, but are not mathematically inclined -- is to conspicuously highlight each important result and briefly place it into context of earlier theory.
@@
 This is an excellent suggestion and has greatly improved the clarity of presentation in our manuscript.
-In the results, we have specifically highlighted our main conclusions in the style of Orr 1998 (slightly modified from the three conclusions suggested by the reviewer):
+In the results, we have specifically highlighted our main conclusions in the style of Orr 1998.
+We have chosen slightly different conclusions from the three suggested by the reviewer:
 %We now give 3 main conclusions at the end of the introduction (L69) which echo those mentioned by the reviewer (looser linkage can evolve, equal selection to increase or decrease the sex ratio, ESD does not always invade biased sex ratio; all of which suggest haploid selection makes conditions for transitions more permissive).
@@
 These conclusions are also more clearly laid out in the introduction (L48-49, L74-85) and are referenced directly in summarisations in the discussion (L424-432, L543-554). 
+}
+
+\textcolor{blue}{Of these conclusions, (3A) and (3B) have some precendent.
+(3A) is similar to studies by van Doorn and Kirkpatrick (2007,2010) that do not include haploid selection.
+These comparisons are made immediately above the conclusions (L316-330) and mentioned elsewhere (L55, L77, L489).
+Including haploid selection, Ubeda et al. (2015) also involved examples similar to (3A), except that the starting state was ESD. 
+Kozielska et al. (2010) also had numerical examples that involved trans-GSD transitions with ($R>r$), as stated in (3B), but focussed only on sex ratio selection. 
+We discuss how our results compare to these studies in the introduction (L58-75), discussion (L433-447) and results (L193, L363-369).
+Nevertheless, we have kept Conclusions 3A and 3B as highlighted conclusions. 
+This is partly to highlight these conclusions for clarity of communication and partly because our results are more general. 
+That is, as stated by the reviewer, our results ``converge on previously-identified conditions for the spread of new SD alleles, while also broadening the range of scenarios and conditions that can favour transitions between SD systems''}
 %As (1A), (1B), and (2) have some antecedents in the literature, we discuss these immediately below each conclusion. 
@@
 %These are all new results, although (1A) was shown for the special case of $r=0$, $R=1/2$, and ploidally-antagonistic selection in Kozielska et al 2010, which we now mention immediately below (1A).
-\textcolor{red}{what is new and what is confirmatory? [see red notes in main text in conclusions]} 
-}
-
-\textcolor{blue}{
-Furthermore, to reduce the technicality of our presentation, we have restructured the presentation of the results subsections "Generic invasion by a neo-Y or neo-W" and ``Tight linkage with the ancestral sex-determining locus''.
-Some details have been moved to the supplementary material (particularly, proofs regarding the leading eigenvalue, formally LXXX-XXX). 
-In the ``Tight linkage'' section, we now first describe specific cases why neo-W's can have improved female fitness, L235-259, with more focus on non-technical interpretation (e.g., L237-240). 
-Then we discuss the fact that looser sex-linkage can evolve (L260-275, Conclusion 2). 
 }
@@
 \textcolor{blue}{
-
 This is an important assumption.
@@
 \textcolor{blue}{We have kept the $V_A$ as we reuse this shorter, strictly positive, term throughout the text. This is also consistent with the well-known van Doorn and Kirkpatrick 2007, 2010 models.}
+\textcolor{red}{Maybe just change this?}
 
@@
 We now mention this in the Introduction (L59-61) and again in the Discussion (L432).  
-Similarly, Kozielska et al involves a special case of GSD transitions during which sex-linkage goes from perfect to none, which is is an extreme example of our Conclusions 2A \&2B.
+Similarly, Kozielska et al involves a special case of GSD transitions during which sex-linkage goes from perfect to none, which is is an  example of our Conclusion 3B.
 This is twice mentioned (L64-67, L237). 
@@
 %Especially because their main conclusion involved the strong influence of sex-ratio selection, which is explicitly not a driver during many such transitions. 
-In addition, our Conclusions 4A and 4B reconcile Kozielska et al and Ubeda et al, explaining that sex-ratio selection is not an overwhelming force driving transitions in sex determination. 
+In addition, our Conclusions 3A and 3B reconcile Kozielska et al and Ubeda et al, explaining that sex-ratio selection is not an overwhelming force driving transitions in sex determination. 
 We believe that our new presentation makes the novel and unexpected features of our results much more apparent. 
@@
 Thus allele frequency changes can occur by gametic competition even if all individuals were homozygous (as long as there is a polymorphism).
-We highlight these differences in the model section (L106-116).
+We have extended our description of how `gametic competition' and `meiotic drive' are modelled in the model section (L106-116), which helps to clarify why they are different and under what circumstances each applies.
 }

### 2018-05-17 LaTeX/main_revised.tex
Sally's main text edits incorporated, not Figure changes after Figure 1

@@
 %This allows sex-ratio biases to increase or decrease with the spread of new sex chromosomes and implies that transitions between sex-determining systems cannot be simply predicted by selection to equalise the sex ratio.
-Overall, our models reveal that transitions between sex-determining systems, particularly transitions where the heterogametic sex changes, can be driven by loci in previously unpredicted genomic locations that experience selection during diploid and/or haploid phases.
+Overall, our models predict that sex determination systems should be highly dynamic, particularly when haploid selection is present, consistent with the evolutionary lability of this trait in many taxa.
+%Overall, our models reveal that transitions between sex-determining systems, particularly transitions where the heterogametic sex changes, can be driven by loci in previously unpredicted genomic locations that experience selection during diploid and/or haploid phases.
 %Our results predict conditions under which sex-determining systems are likely to be labile and draw connections with sex-ratio evolution.
@@
 Our models include selection upon haploid genotypes (meiotic drive or gametic competition), which biases the sex-ratio and occurs differently in male and female gametes. 
-Surprisingly, we find the two forces (selection to equalize the sex ratio and the benefits of hitchhiking with driven alleles that distort the sex ratio) will often be equally strong, and thus neither is sufficient to explain the spread of new sex-determining systems in every case.
-We also find that new sex-determining alleles can spread despite being less closely linked to selected loci, driven by initially tight linkage or haploid selection. 
+Surprisingly, we find the two forces (selection to equalize the sex ratio and the benefits of hitchhiking alongside driven alleles that distort the sex ratio) will often be equally strong, and thus neither is sufficient to explain the spread of new sex-determining systems in every case.
+We also find that new sex-determining alleles can spread despite being less closely linked to selected loci as long as initial linkage is tight or haploid selection is present.. 
 Our models therefore predict that loci in previously unexpected genomic locations and/or experiencing various types of selection (including haploid selection) can now be implicated as drivers of transitions between sex-determining systems.
@@
 mammals and most dioecious plants~\cite{Ming:2011iy}; whereas other taxa have homogametic males (ZZ) and heterogametic females (ZW), including Lepidoptera and birds. 
-Within several taxa, the chromosome that harbours the master sex-determining locus changes. 
-For example, transitions of the master sex-determining locus between chromosomes or the evolution of new master sex-determining loci where the heterogametic sex does not change (hereafter `cis-GSD transitions') have occurred in Salmonids~\cite{Li:2011fm,Yano:2012di}, Diptera~\cite{Vicoso:2015hf}, and \textit{Oryzias}~\cite{Myosho:2012fv}.
+Within several taxa, the chromosome that harbours the master sex-determining locus changes, due either to translocation of the master sex-determining locus or to the evolution of a new master locus.  
+During these transitions, the heterogametic sex can remain the same (hereafter `cis-GSD transitions') as in Salmonids~\cite{Li:2011fm,Yano:2012di}, Diptera~\cite{Vicoso:2015hf}, and \textit{Oryzias}~\cite{Myosho:2012fv}.
 %Presentation at evolution found neo sex chromosome in birds, doesn't seem to be published or bioRxiv yet (consider pers com.), title: A previously unknown neo-sex chromosome mediates plumage divergence and speciation in hybridizing birds Jason Sardell; Elizabeth Cooper; J.
@@
 I wonder if this is actually a fusion event though?
-In addition, many clades exhibit transitions between male and female heterogamety (XY$\leftrightarrow$ZW, hereafter `trans-GSD transitions'), including snakes~\cite{Gamble2017}, lizards~\cite{Ezaz:2009tk}, eight of 26 teleost fish families~\cite{Mank:2006bt}, true fruit flies (Tephritids,~\cite{Vicoso:2015hf}), amphibians~\cite{Hillis:1990gu}, the angiosperm genus \textit{Silene}~\cite{Slancarova:2013dq}, the angiosperm family \textit{Salicaceae}~\cite{Pucholt2015,Pucholt2017} and Coleoptera and Hemiptera (plate 2~\cite{Beukeboom:2014vb}).
+Alternatively, species can switch between male and female heterogamety (XY$\leftrightarrow$ZW, hereafter `trans-GSD transitions'), as in snakes~\cite{Gamble2017}, lizards~\cite{Ezaz:2009tk}, eight of 26 teleost fish families~\cite{Mank:2006bt}, true fruit flies (Tephritids,~\cite{Vicoso:2015hf}), amphibians~\cite{Hillis:1990gu}, the angiosperm genus \textit{Silene}~\cite{Slancarova:2013dq}, the angiosperm family \textit{Salicaceae}~\cite{Pucholt2015,Pucholt2017} and Coleoptera and Hemiptera (plate 2~\cite{Beukeboom:2014vb}).
 Indeed, in some cases, both male and female heterogametic sex-determining systems can be found in the same species, as reported in houseflies~\cite{Macdonald1978}, midges~\cite{Thompson1971}, frogs~\cite{Ogata:2007jm}, cichlid fish~\cite{Ser:2010iq}, tilapia~\cite{Lee2004}, sea bass~\cite{Vandeputte2007}, and lab-strains of Zebrafish~\cite{Liew2012,Wilson2014}.
@@
 %\citet{Bull:1977wt} shows that direct selection on new sex determination loci can allow them to spread and switch between male and female heterogamety. 
-It has been suggested that sex-ratio selection is a particularly dominant force in the evolution of sex determination because the sex ratio is directly determined by the sex-determining system (e.g., Bull, 1983, p 66-67 ~\cite{Bull:1983vi}; Buekeboom and Perrin, 2014, Chapter 7~\cite{Beukeboom:2014vb}).
+It has been suggested that sex-ratio selection is a particularly dominant force in the evolution of sex determination (e.g., Bull, 1983, p 66-67 ~\cite{Bull:1983vi}; Buekeboom and Perrin, 2014, Chapter 7~\cite{Beukeboom:2014vb}).
 Classic `Fisherian' sex-ratio selection favours a 1:1 zygotic sex ratio when assuming that males and females are equally costly to produce~\cite{Fisher:1930wy,Charnov:1982wg}. 
@@
 Thus, if the sex ratio is biased, an individual of the rarer sex will, on average, contribute more genetic material to the next generation. 
-Selection therefore typically favours mutants that increase investment in the rarer sex.
+Selection therefore typically favours mutants that increase investment in the rarer sex, including new sex determination systems.
 %Because the sex ratio is directly determined by the sex-determining system, it has been suggested that sex-ratio selection is a particularly dominant force in the evolution of sex determination (e.g., Bull, 1983, p 66-67 ~\cite{Bull:1983vi}; Buekeboom and Perrin, 2014, Chapter 7~\cite{Beukeboom:2014vb}).
@@
 In addition, selection on ancestral-X chromosomes in males can prevent the X from becoming optimally specialised for female-beneficial alleles. 
-These factors, in turn, can favour a new ZW sex-determining locus that has weaker linkage with loci under selection, which was not \textcolor{red}{apparent/discovered/considered} in previous theory \cite{vanDoorn:2010hu}.
+These factors, in turn, can favour a new ZW sex-determining locus that has weaker linkage with loci under selection, which was not revealed by previous theory \cite{vanDoorn:2010hu}.
 A similar argument applies to ZW$\rightarrow$XY transitions.
@@
 On one hand, haploid selection is typically sex-limited in that it usually occurs among gametes produced by one sex only~\cite{Mulcahy:1996ha,JOSEPH:2004haa,Ubeda:2005gw,Lindholm:2016cw}. 
-Therefore, one might expect new sex-determining systems to benefit from close linkage with haploid selected loci, as found for sex-differences in diploid selection~\cite{vanDoorn:2007eu,vanDoorn:2010hu, Muralidhar2018}.
+Therefore, one might expect new sex-determining systems to benefit from close linkage with haploid selected loci, as found for loci that experience diploid-sex-differences in selection~\cite{vanDoorn:2007eu,vanDoorn:2010hu, Muralidhar2018}.
 On the other hand, associations between sex-determining loci and haploid selected loci generate biased zygotic sex ratios, which should generally hinder the spread of new sex-determining systems.
@@
 For example, a masculinizing allele spreads in association with an allele that is favoured during male meiosis, causing sex ratios to become male-biased.
-This suggests that the benefits of associating with driving alleles overwhelms selection to balance the sex ratio and that haploid selection should cause increased sex-linkage.
-%, at least when new sex-determining alleles are rare.
-However, Kozielska et al. (2010)~\cite{Kozielska:2010vm} considered an ancestral GSD system that is perfectly linked to a meiotic driver (creating a sex ratio bias). 
-They found that new, completely unlinked, GSD systems can spread if they generate the rarer sex, creating a balanced sex ratio. 
-This suggests that Fisherian sex-ratio selection overwhelms the benefits of being associated with driving alleles and that haploid selection should cause decreased sex-linkage.
+This suggests that the benefits of associating with driving alleles can overwhelm selection to balance the sex ratio. %, at least when new sex-determining alleles are rare. 
+However, Kozielska et al. (2010)~\cite{Kozielska:2010vm} considered an ancestral GSD system that is perfectly linked to a meiotic driver and therefore exhibiting an ancestral sex ratio bias. 
+They found that a new, completely unlinked, GSD system can spread if it generates the rarer sex, creating a balanced sex ratio. 
+This suggests that Fisherian sex-ratio selection can overwhelm the benefits of being associated with driving alleles. 
+It is thus currently unclear when haploid selection favors increased versus decreased linkage between haploid selected loci and a new sex-determining locus. 
+In addition, because the sex ratio is determined by linkage between haploid selected loci and the sex-determining locus, it is also unclear when Fisherian sex-ratio selection is the most important driver of transitions between sex-determining systems.
 
 %main results
-Here, we analytically find the conditions under which new GSD or ESD systems spread in ancestral GSD systems with generic linkage between the loci involved and generic sex-specific haploid and diploid selection.
-Doing so, we reconcile the results of Kozielska et al.
+Here, we analytically find the conditions under which new GSD or ESD systems spread in ancestral GSD systems with any degree of linkage between the loci involved and arbitrary forms of haploid and diploid selection.
+Doing so, we reconcile and generalize the results of Kozielska et al.
 (2010)~\cite{Kozielska:2010vm} and Ubeda et al.
-(2015)~\cite{Ubeda:2015fx} by deriving conditions for the spread of new GSD systems that increase \textit{or} decrease linkage with haploid selected loci.
-%that experience haploid selection.
+(2015)~\cite{Ubeda:2015fx} by deriving conditions for the spread of new GSD systems that alter linkage with haploid selected loci.
 Our result is qualitatively distinct from those for diploid selection alone~\cite{vanDoorn:2007eu,vanDoorn:2010hu} and suggests that haploid selection is more likely to promote transitions between sex-determination systems.
@@
 %Together, our results suggest that neither selection to equalize the sex ratio nor the benefits of associating with haploid selected alleles is an overwhelming force driving transitions between sex-determining systems.
-Together, our results suggest that both selection to equalize the sex ratio and the benefits of associating with haploid selected alleles can drive transitions between sex-determining systems, leading to tighter or weaker sex-linkage.
+Together, our results suggest that both selection to equalize the sex ratio and the benefits of associating with haploid selected alleles can drive transitions between sex-determining systems, leading to stronger or weaker sex-linkage and increased or decreased sex ratio bias.
 
@@
 %\centering
-\centerline{\includegraphics[width=\linewidth]{../Plots/Sex_determination_outline.pdf}}
+\centerline{\includegraphics[width=0.9\linewidth]{../Plots/Sex_determination_outline.pdf}}
 \caption{
@@
 Panel A: Recombination rate parameters between the ancestral-sex-determining locus ($\mathbf{X}$, here assumed to have alleles X and Y), a locus under selection ($\mathbf{A}$, with alleles $A$ and $a$), and a new sex-determining locus ($\mathbf{M}$, with alleles $M$ and $m$).
-If $r<1/2$, then associations between ancestral sex-determining alleles and selected alleles can be present in new male gametes/gametophytes. 
-Panel B: Haploid selection is often sex-limited, occurring during haploid production or competition in either males or females. 
-For example, haploid selection in males only is represented by the dashed circle.  
-If X or Y alleles remain associated with alleles that experience haploid selection in males ($r<1/2$), then zygotic sex ratios can become biased because either X- or Y-bearing male gametes/gametophytes will be more abundant after haploid selection.
+%If $r<1/2$, then associations between ancestral sex-determining alleles and selected alleles can be present in new male gametes/gametophytes. 
+Panel B: Haploid selection is often sex-limited, occurring during haploid production or competition in one sex (shown here in males by dashed circles). 
+If X or Y alleles are linked with alleles that experience haploid selection in males ($r<1/2$), then zygotic sex ratios can become biased because either X- or Y-bearing male gametes/gametophytes will be more abundant after haploid selection.
+Similarly, zygotic sex-ratio biases can arise if haploid selected alleles are linked with new sex-determining alleles ($R<1/2$). 
 However, the zygotic sex ratio is not biased by male haploid selection in ZW sex-determining systems. 
-Similarly, zygotic sex-ratio biases can arise if haploid selected alleles are associated with new sex-determining alleles ($R<1/2$). 
-Panel C: During cis-GSD transitions (XY to XY or ZW to ZW), a neo-Y allele spreads to pseudo-fixation (its maximum frequency among male gametes) and the ancestral Y allele is lost. 
-Panel D: During trans-GSD transitions (XY to ZW or ZW to XY), a neo-W allele spreads to pseudo-fixation (its maximum frequency among female gametes) and the ancestral X allele is lost. 
+Panel C: During cis-GSD transitions (XY to XY or ZW to ZW), a neo-Y allele ($m$) spreads to pseudo-fixation (i.e, all males bear the neo-Y) and the ancestral Y allele is lost. 
+Panel D: During trans-GSD transitions (XY to ZW or ZW to XY), a neo-W allele ($m$) spreads to pseudo-fixation (i.e, all females bear the neo-W) and the ancestral X allele is lost. 
 Neo-W alleles allow Y-associated alleles into females, which may impede or aid their spread. 
@@
 During gametic competition, we assume that a representative sample of all gametes/gametophytes (hereafter gametes) compete with others of the same sex for fertilization, which implies a polygamous mating system.
-Relative fitnesses in sex $\circ \in \{\female,\male\}$ during gametic competition are given by $w_A^\circ$ and $w_a^\circ$ (see table \ref{tab:fitnesstable}).
+Relative fitnesses in sex $\circ \in \{\female,\male\}$ during gametic competition are given by $w_A^\circ$ and $w_a^\circ$ (see Table \ref{tab:fitnesstable}).
 On the other hand, meiotic drive in our model only affects the segregation of gametes produced by heterozgotes.
 Specifically, gametes produced by $Aa$ heterozgotes of sex $\circ$ bear allele $A$ with probability $\alpha^\circ$. 
-We note that competition between sperm produced by a single male (e.g.
-in a monogamous mating system) would be appropriately modelled as male meiotic drive, as only the frequency of gametes produced by heterozygotes would be affected.
+We note that competition between sperm produced by a single male (e.g., in a monogamous mating system) would be appropriately modelled as male meiotic drive, as only the frequency of gametes produced by heterozygotes would be affected.
 However, we do not consider scenarios in which there is competition among gametes produced by a small number of males/females (e.g.,~\cite{Holman:2015en}).
@@
 %Below, it is convenient to follow the ancestral equilibrium frequency of the $A$ allele among female gametes (eggs), $\hat{p}^\female_X$, and among X-bearing, $\hat{p}^\male_X$, and among Y-bearing, $\hat{p}^\male_Y$, male gametes (sperm/pollen).
-%We also track the ancestral fraction of male gametes that are Y-bearing, $\hat{q}$, which may deviate from $1/2$ due to meiotic drive in males. 
+%We also track the ancestral fraction of male gametes that are Y-bearing, $\hat{q}_{Y}$, which may deviate from $1/2$ due to meiotic drive in males. 
 %
@@
 
-In the ancestral population, it is convenient to follow the frequency of the $A$ allele among female gametes (eggs), $p^\female_X$, and among X-bearing, $p^\male_X$, and among Y-bearing, $p^\male_Y$, male gametes (sperm/pollen).
+In the ancestral population, it is convenient to follow the frequency of the $A$ allele among female gametes (eggs), $p^\female_X$, and among X-bearing, $p^\male_X$, or among Y-bearing, $p^\male_Y$, male gametes (sperm/pollen).
 We also track the fraction of male gametes that are Y-bearing, $q$, which may deviate from $1/2$ due to meiotic drive in males. 
-We consider only equilibrium frequencies of alleles, $\hat{p}^\circ_i$, and Y-bearing male gametes, $\hat{q}$, when determining the invasion of new sex-determining factors.
+We consider only equilibrium frequencies of alleles, $\hat{p}^\circ_i$, and Y-bearing male gametes, $\hat{q}_{Y}$, when determining the invasion of new sex-determining factors.
+We use $\zeta$ to measure the sex ratio (fraction male) among zygotes, which is determined by the allele frequencies and haploid selection coefficients (\nameref{tab:meanfitnesses}).
 
@@
 This system simplifies substantially for an epistatically dominant neo-Y ($k=0$) or neo-W ($k=1$), see \nameref{app:inv_cond} for details. 
-%We will consider only equilibrium frequencies of alleles, $\hat{p}^\circ_i$, and Y-bearing male gametes, $\hat{q}$, when calculating the eigenvalues.
+%We will consider only equilibrium frequencies of alleles, $\hat{p}^\circ_i$, and Y-bearing male gametes, $\hat{q}_{Y}$, when calculating the eigenvalues.
 
@@
 %We also track the fraction of male gametes that are Y-bearing, $q$, which may deviate from $1/2$ due to meiotic drive in males. 
-%We will consider only equilibrium frequencies of alleles, $\hat{p}^\circ_i$, and Y-bearing male gametes, $\hat{q}$, when calculating the eigenvalues.
+%We will consider only equilibrium frequencies of alleles, $\hat{p}^\circ_i$, and Y-bearing male gametes, $\hat{q}_{Y}$, when calculating the eigenvalues.
 
@@
    \begin{flushleft} 
-$\hat{p}_X^\female$ is the frequency of $A$ among female gametes.
-$\bar{p}^{\male}=(1-\hat{q})\hat{p}_X^\male + \hat{q}\hat{p}_Y^\male$ is the average frequency of the $A$ allele among X- and Y-bearing male gametes.
-$\hat{q}$ is the frequency of Y-bearing male gametes. 
+$\bar{p}^{\male}=(1-\hat{q}_{Y})\hat{p}_X^\male + \hat{q}_{Y}\hat{p}_Y^\male$ is the average frequency of the $A$ allele among X- and Y-bearing male gametes.
+$\hat{q}_{Y}$ is the frequency of Y-bearing male gametes. 
 %      \item $R$ is the probability of recombination between loci $\mathbf{A}$ and $\mathbf{M}$.
@@
 
-The haplotypic growth rates and dissociative forces are listed in Table 2 for a neo-Y and neo-W invading an ancestrally XY system.
-From this table and the arguments above we draw three main points about the generic invasion of neo-Y and neo-W mutations (without specifying the ancestral equilibrium):
-(1) invasion by a neo-Y (neo-W) does not directly depend on the fitness of female (male) diploids. %(for a given set of equilibrium allele frequencies).
+The haplotypic growth rates and dissociative forces are listed in Table \ref{tab:haplotype_growth} for a neo-Y and neo-W invading an ancestrally XY system.
+From this table and the arguments above we draw four main points about the generic invasion of neo-Y and neo-W mutations (without specifying the ancestral equilibrium):
+(1) Fisherian sex-ratio selection will favour the spread of a neo-W and inhibit the spread of a neo-Y if the ancestral zygotic sex ratio is biased towards males (i.e., the first factor of the $\Lambda_{mi}^{(XY)}$ is greater than one for a neo-W and less than one for a neo-Y when $\zeta>1/2$).
+Thus, neo-sex-determining alleles that specify the rarer sex are favoured by Fisherian sex ratio selection. 
+(2) In addition, the new sex determining allele has associations with alleles favored by either haploid or diploid selection (terms in square brackets).    
+Importantly, invasion by a neo-Y (neo-W) does not directly depend on the fitness of female (male) diploids. 
 This is because a dominant neo-Y (neo-W) is always found in males (females), and therefore the frequency of the neo-Y (neo-W), $m$, only changes in males (females), Fig \ref{fig:model_outline}C,D.
-(2) Fisherian sex-ratio selection will favour the spread of a neo-W and inhibit the spread of a neo-Y if the ancestral zygotic sex ratio is biased towards males (i.e., the first factor of the $\Lambda_{mi}^{(XY)}$ is greater than one for a neo-W and less than one for a neo-Y when $\zeta>1/2$).
-%, as might occur when the ancestral sex-determining locus is linked to a locus experiencing meiotic drive in males, for example.
-However, the spread of a neo-Y (neo-W) also depends on the male (female) fitness of associated alleles (see terms involving equilibrium allele frequencies, $\hat{p}$'s), including haploid selection that additionally biases the sex ratio.
-This implies that both Fisherian selection to equalize the sex-ratio and selection favoring sex-linked drivers that distort the sex ratio play roles in the invasion dynamics of a new sex-determining allele, allowing the sex ratio to become more or less biased during a transition (as previously found in two special cases; \cite{Kozielska:2010vm,Ubeda:2015fx}).
-%neiher sex-ratio selection nor selection on associated alleles dominates the invasion dynamics of a new sex-determining allele, allowing the sex ratio to become more or less biased during a transition (as previously shown in two special cases; \cite{Kozielska:2010vm,Ubeda:2015fx}).
-%That is, 
-%\vspace{0.5cm}
-%
-%\noindent\textit{Conclusion 1:} 
-%\textbf{neither sex-ratio selection or selection on associated alleles dominates the invasion dynamics of a new sex-determining allele, allowing the sex ratio to become more or less biased during a transition.}
-%\textcolor{red}{[as suspected from Kozielska and Ubeda special cases]}
-%\vspace{0.5cm}
-%
-(3) Table \ref{tab:haplotype_growth} shows that
-%\vspace{0.5cm}
-%
-%\noindent\textit{Conclusion 2:}
-%\textbf{cis- and trans-GSD transitions are qualitatively different.}
-%\textcolor{red}{[already known from van Doorn and Kirkpatrick]}
-%\vspace{0.5cm}
-%
-cis- and trans-GSD transitions are qualitatively different.
+%Beyond the direct effects of selection, there are also indirect effects caused by past selection molding the equilibrium allele frequencies ($\hat{p}^\circ_i$ terms), which generally do depend on selection in both sexes.
+(3) Haploid selection thus plays two roles, generating Fisherian selection to equalize the ancestral sex-ratio (through $\zeta$) and generating selection for the neo-Y/neo-W through associations with haploid selected loci, which can distort the sex ratio.
+Each role influences the invasion dynamics of a new sex-determining allele, allowing the sex ratio to become more or less biased during a transition (as previously found in two special cases; \cite{Kozielska:2010vm,Ubeda:2015fx}).
+(4) Finally, Table \ref{tab:haplotype_growth} shows that the genetic contexts that arise during cis- and trans-GSD transitions are qualitatively different.
 This is because, in an ancestrally XY system, a gamete with the neo-Y always pairs with a female gamete containing an X, Fig \ref{fig:model_outline}C.
 By contrast, a gamete with a neo-W can pair with an X- or Y-bearing male gamete, Fig \ref{fig:model_outline}D.
-Consequently, neo-W-bearing females obtain a different frequency of $A$ alleles from mating (when $\hat{p}_X^\male \neq \hat{p}_Y^\male$) compared to ancestral ($MM$) females. 
+Consequently, neo-W-bearing females obtain a different frequency of $A$ alleles from mating compared to ancestral ($MM$) females ($\bar{p}^\male$ versus $\hat{p}_X^\male$, respectively). 
 This can inhibit or favour the spread of a neo-W.
 
-In order to explicitly determine the conditions under which a new sex-determining allele spreads, we next calculate the equilibrium frequency of the $A$ allele (i.e., $\hat{p}^\female_X$, $\hat{p}^\male_X$, and $\hat{p}^\male_Y$) and Y-bearing male gametes ($\hat{q}$) in the ancestral population.
+In order to explicitly determine the conditions under which a new sex-determining allele spreads, we next calculate the equilibrium frequency of the $A$ allele (i.e., $\hat{p}^\female_X$, $\hat{p}^\male_X$, and $\hat{p}^\male_Y$) and Y-bearing male gametes ($\hat{q}_{Y}$) in the ancestral population.
 Because only the $\mathbf{A}$ locus experiences selection directly, any deterministic evolution requires that there be a polymorphism at the $\mathbf{A}$ locus. 
-Polymorphisms can be maintained by mutation-selection balance or transiently present during the spread of beneficial alleles. 
+Polymorphisms can be maintained by mutation-selection balance or occur transiently during the spread of beneficial alleles. 
 %However, polymorphisms maintained by selection can maintain alleles at intermediate allele frequencies for longer periods. 
-Here, however, we focus on polymorphisms maintained by selection, which can maintain alleles at intermediate frequencies for longer periods. 
+Here, however, we focus on polymorphisms maintained by selection for longer periods. 
 %where the $A$ allele reaches a stable intermediate equilibrium frequency under the ancestral sex-determining system before the new sex-determining allele ($m$) arises. 
@@
 
-When there is complete linkage between the ancestral sex-determining locus and the selected locus $\mathbf{A}$ ($r=0$), either the $A$ allele or the $a$ allele must be fixed in gametes containing a Y allele.
+When there is complete linkage between the ancestral sex-determining locus and the selected locus $\mathbf{A}$ ($r=0$), either the $A$ allele or the $a$ allele must be fixed in gametes containing a Y allele (\nameref{app:eq_stab}).
 % because selection on the Y is effectively haploid an incapably of maintaining a polymorphism in the absence of frequency dependent selection. 
@@
 Neo-W alleles, on the other hand, can invade an ancestral XY system (the full invasion conditions are given in \nameref{app:inv_cond}; equations \ref{Binvasion} and \ref{Ainvasion}).
-This implies that neo-W females can have higher fitness than the XX females in the ancestral population.
+Invasion occurs when neo-W females can have higher fitness than the XX females in the ancestral population.
 Neo-W invasion is possible under all forms of selection that can maintain a polymorphism (sexually-antagonistic selection, overdominance, ploidally-antagonistic selection, or some combination, e.g., \nameref{fig:temporalOverdominance}, \nameref{fig:SexAntagTighterMaleDrive}, and \nameref{fig:regionPloidAntag}).
@@
 Broadly, it is possible for neo-W females to have higher fitness than XX females for two reasons.
-Firstly, because the ancestral X experiences selection in both males and females, it may be unable to specialize strongly on an allele favoured in females.
+Firstly, because the ancestral X experiences selection in both males and females, the X may be unable to specialize strongly on an allele favoured in females.
 Secondly, an allele can be associated with the Y and yet favoured in females.
@@
 Here, selection in females can favour the $A$ allele (panel A, $w_{aa}^\female=0.85$, $w_{AA}^\female=1.05$), favour the $a$ allele (panel B, $w_{aa}^\female=1.05$, $w_{AA}^\female=0.85$), or be overdominant (panel C, $w_{aa}^\female=w_{AA}^\female=0.6$).
-If either haplotypic growth rate ($\Lambda_{W'A}^{(XY)}$ or $\Lambda_{W'a}^{(XY)}$) is greater than one, then a rare neo-W allele can spread for, at least, some values of $R>r$. 
+If either haplotypic growth rate ($\Lambda_{W'A}^{(XY)}$ or $\Lambda_{W'a}^{(XY)}$) is greater than one, then a rare neo-W allele can spread for, at least, some values of $R>r$ (grey regions). 
 The parameter values marked with an asterisk correspond to the fitnesses used in Fig \ref{fig:SexAntagTighter}C. 
-Where both haplotypic growth rates are greater than one, a neo-W will spread when rare, regardless of linkage with the selected locus (for any $R$). 
+%Where both haplotypic growth rates are greater than one, a neo-W will spread when rare, regardless of linkage with the selected locus (for any $R$). 
 \nameref{fig:positionOverdominance} shows the dynamics arising with the parameters marked with a dagger. 
@@
 Nevertheless, because we assume here that $r$ is small, these results indicate that a more loosely linked sex-determining region ($r<R$) can spread.
-For example, tightly sex-linked loci that experience sexually-antagonistic selection can drive trans-GSD transitions in which the new sex-determining locus is less closely linked (but not unlinked, $R<1/2$) to the locus under selection (Fig \ref{fig:SexAntagTighter}).
+For example, tightly sex-linked loci that experience sexually-antagonistic selection can drive trans-GSD transitions in which the new sex-determining locus is less closely linked ($R>r$, Fig \ref{fig:SexAntagTighter}), but the analysis in \nameref{file:Mathematica} indicates that a new unlinked sex-determining allele ($R=1/2$) cannot invade when selection is purely sexually-antognistic (directional selection in each sex and no haploid selection).
 
@@
 
-From the arguments above we conclude that
+From the arguments above we reach:
 \vspace{0.5cm}
@@
 \begin{equation}
-\lambda_{Y'}^{(XY)} = 1 + \frac{1}{4}V_{A}S_{A}^2\frac{ \left( r-R \right) }{r R}+O\left(\epsilon^3 \right) 
+\lambda_{Y'}^{(XY)} = 1 + \frac{1}{4}\bar{p}(1-\bar{p})S_{A}^2\frac{ \left( r-R \right) }{r R}+O\left(\epsilon^3 \right) 
 \label{eq:lambda_neoY}
@@
 \noindent
-where $V_{A}=\bar{p}(1-\bar{p})$ is the variance in the equilibrium frequency of $A$ and $S_{A}=(\bar{s}^\male +\alpha_{\Delta}^\male+t^\male) - (\bar{s}^\female+\alpha_{\Delta}^\female+t^\female)$ describes sex differences in selection for the $A$ versus $a$ allele across diploid selection, meiosis, and gametic competition.
-The diploid selection term, $\bar{s}^\circ=\big{[} \bar{p}s^\circ+(1-\bar{p})h^\circ s^\circ\big{]} -\big{[} \bar{p}h^\circ s^\circ+(1-\bar{p}) \big{]}$, is the difference in fitness between $A$ and $a$ alleles in diploids of sex $\circ \in \{\female,\male\}$, where $\bar{p}$ is the leading-order probability of mating with an A-bearing gamete from the opposite sex (equation \ref{eq:pAve}) and the difference in $A$-allele-frequency among Y-bearing sperm versus X-bearing sperm is, at equilibrium, $\hat{p}^\male_Y-\hat{p}^\male_X=V_{A}S_{A}(1-2r)/(2r)$.
+where $\bar{p}$ is the frequency of $A$, to leading-order (Eq \ref{eq:pAve}), and $S_{A}=(\bar{s}^\male +\alpha_{\Delta}^\male+t^\male) - (\bar{s}^\female+\alpha_{\Delta}^\female+t^\female)$ describes sex differences in selection for the $A$ versus $a$ allele across diploid selection, meiosis, and gametic competition.
+The diploid selection term, $\bar{s}^\circ=\big{[} \bar{p}s^\circ+(1-\bar{p})h^\circ s^\circ\big{]} -\big{[} \bar{p}h^\circ s^\circ+(1-\bar{p}) \big{]}$, is the difference in fitness between $A$ and $a$ alleles in diploids of sex $\circ \in \{\female,\male\}$.
+The difference in $A$-allele-frequency among Y-bearing sperm versus X-bearing sperm is, at equilibrium, $\hat{p}^\male_Y-\hat{p}^\male_X=\bar{p}(1-\bar{p})S_{A}(1-2r)/(2r)$.
 
 %The new sex-determining allele, $m$, will spread in an XY system if $\lambda_{m}^{(XY)}>1$. 
-Eq \eqref{eq:lambda_neoY} demonstrates that, under weak selection, a neo-Y allele will invade an XY system ($\lambda_{Y'}^{(XY)}>1$) if and only if it is more closely linked to the selected locus than the ancestral sex-determining locus (i.e., if $R<r$; note that $V_{A}S_{A}^2$ is strictly positive as long as $\mathbf{A}$ is polymorphic).
+Eq \eqref{eq:lambda_neoY} demonstrates that, under weak selection, a neo-Y allele will invade an XY system ($\lambda_{Y'}^{(XY)}>1$) if and only if it is more closely linked to the selected locus than the ancestral sex-determining locus (i.e., if $R<r$; note that $\bar{p}(1-\bar{p})S_{A}^2$ is strictly positive as long as $\mathbf{A}$ is polymorphic).
 This echoes our results above where a neo-Y could never invade if $r\approx0$. 
@@
 
-When selection is weak relative to recombination, the absence of haploid selection ($t^\circ=\alpha^\circ_{\Delta}=0$), implies that the spread of a neo-W is equivalent to the spread of a neo-Y ($\lambda_{W'}^{(XY)}=\lambda_{Y'}^{(XY)}$), such that trans-GSD transitions can also occur only if the new sex-determining locus is more closely linked to a locus under selection ($R<r$), as found by \cite{vanDoorn:2010hu}.
-When there is haploid selection, invasion also typically occurs when the neo-W is more closely linked to the selected locus than the ancestral sex-determining region (Fig \ref{fig:Combination_Centimorgans}).
-For example, if the $\mathbf{A}$ locus is unlinked to the ancestral sex-determining locus ($r=1/2$, which implies that $ \hat{p}^\male_Y-\hat{p}^\male_X =0$), a more closely linked neo-W ($R<1/2$) can always invade.
-Thus,
-%In this case, there is no ancestral association between $\mathbf{A}$ alleles and sex chromosomes in males, $\left( \hat{p}^\male_Y-\hat{p}^\male_X \right)=0$, see Eq \eqref{eq:freq_diffs}. 
-%The second term in Eq \eqref{eq:lambda_neoW} therefore disappears and invasion depends only on the sign of $(r-R)$.%, as in the case of the neo-Y.
-
 \vspace{0.5cm}
 \noindent\textit{Conclusion 3A:}\
-\textbf{New sex-determining alleles (causing cis- \textit{or} trans-GSD transitions) can spread if they arise more closely linked with a locus that experiences selection than the ancestral-sex-determining locus is ($R<r$).}
-%\textcolor{red}{[consistent with van Doorn \& Kirkpatrick 2007, 2010, except that we add haploid selection, these connections are mentioned above], consistent with Ubeda et al 2015 (assuming ancestral ESD something similar to $r=1/2$, invasion with $R<1/2$.), not yet mentioned [mentioned below on 370]  }
+\textbf{New sex-determining alleles (causing cis-GSD transitions, XY $\leftrightarrow$ XY or ZW $\leftrightarrow$ ZW) are favoured if they arise more closely linked with a locus that experiences (haploid and/or diploid) selection than the ancestral-sex-determining locus is ($R<r$).}
 \vspace{0.5cm}
@@
 \noindent
-However, with haploid selection and some ancestral sex-linkage ($r<1/2$; allowing allele frequency differences on the X and Y), the term in square brackets in Eq \eqref{eq:lambda_neoW} can be positive.
-This implies,
+Similarly, a neo-W is typically favoured when it is more closely linked to the selected locus than the ancestral sex-determining region is, ($R<r$, e.g., Figs \ref{fig:SexAntagTighter}B and \ref{fig:Combination_Centimorgans}).
+Specifically, if the selected locus ($\mathbf{A}$) is ancestrally autosomal ($r=1/2$, leading to $ \hat{p}^\male_Y-\hat{p}^\male_X =0$ such that $\lambda_{W'}^{(XY)}=\lambda_{Y'}^{(XY)}$, Eqs \eqref{eq:lambda_neoY} and Eq \eqref{eq:lambda_neoW}), a more closely linked neo-W ($R<1/2$) is favoured.
 
@@
 \noindent\textit{Conclusion 3B:}\
-\textbf{New sex-determining alleles (causing trans-GSD transitions, XY $\leftrightarrow$ ZW) can spread even if they arise less closely linked with a locus that experiences selection than the ancestral-sex-determining locus is ($r<R$), requiring haploid selection.}
+\textbf{New sex-determining alleles (causing trans-GSD transitions, XY $\leftrightarrow$ ZW) are favoured if they are linked with an ancestrally-autosomal locus that experiences (haploid and/or diploid) selection ($R<1/2$, $r=1/2$).}
+\vspace{0.5cm}
+
+\noindent
+In the absence of haploid selection ($t^\circ=\alpha^\circ_{\Delta}=0$), the spread of a neo-W is equivalent to the spread of a neo-Y ($\lambda_{W'}^{(XY)}=\lambda_{Y'}^{(XY)}$), such that trans-GSD transitions can occur if and only if the new sex-determining locus is more closely linked to a locus under selection ($R<r$), as found by \cite{vanDoorn:2010hu}.
+However, with haploid selection and some ancestral sex-linkage ($r<1/2$; allowing allele frequency differences on the X and Y), the term in square brackets in Eq \eqref{eq:lambda_neoW} can be positive.
+Thus,
+
+\vspace{0.5cm}
+\noindent\textit{Conclusion 3C:}\
+\textbf{With haploid selection, new sex-determining alleles (causing trans-GSD transitions, XY $\leftrightarrow$ ZW) can spread even if they arise less closely linked with a locus that experiences selection than the ancestral-sex-determining locus is ($r<R$).}
 \vspace{0.5cm}
@@
 In panel B, gametic competition in males ($t^\male = -1/10$, $t^\female = \alpha^\circ_{\Delta} = 0$) opposes selection in diploids (sex-differences: $s^\male = 3/20$, $s^\female = 1/20$, $h^\circ = 7/10$).
-In either case the new sex-determining allele can invade regardless of $R$.
+In either case the new sex-determining allele can invade regardless of $R$, even when linkage to the selected locus is reduced (white regions).
 }
@@
 
-%\noindent\textit{Conclusion 1B:}\
-%\textbf{new sex-determining alleles (causing trans-GSD transitions) can spread if they arise in looser linkage with a locus that experiences haploid selection ($r<R$). }
-%\textbf{haploid selection on loci weakly linked to the sex-determining locus ($0<r<1/2$) allows the invasion of less closely linked sex-determining alleles ($r<R\leq1/2$) during a trans-GSD transition} (XY $\leftrightarrow$ ZW).
-%\vspace{0.5cm}
-
-%\noindent{\textit{Conclusion 2:}\
-%\textbf{new sex-determining alleles (causing cis- \textit{or} trans-GSD transitions) can spread if they arise in closer linkage with a locus that experiences haploid selection ($R<r$). }
-%(This is different but similar to Ubeda et al (2015), who started from ESD)
-%\vspace{0.5cm}
-
-%\noindent The numerical results of \cite{Ubeda:2015fx} are consistent with Conclusion 2A, but arise from an ESD to GSD transition, where the ancestral equilibrium is considerably simpler.
-%Conclusion 2B echoes the diploid-selection-only results of \cite{vanDoorn:2007eu,vanDoorn:2010hu}, but greatly extends the number of selective scenarios favouring transitions.
-
-%These transitions are unusual because, when $R>r$, associations that selection has built up between alleles more favourable in one sex and alleles that determine sex will be weakened. 
-%Mean diploid fitness therefore decreases during heterogametic transitions that create looser sex-linkage (Fig \ref{fig:Combination_MeanFit}B,D). 
-%Eq \eqref{eq:lambda_neoW} shows that, with weak selection, neo-W alleles can invade an XY system for a large number of selective regimes. 
-%To clarify the parameter space under which $\lambda_{W'}^{(XY)}>1$ , we consider several special cases. 
-%Firstly, if the $\mathbf{A}$ locus is unlinked to the ancestral sex-determining region ($r=1/2$), a more closely linked neo-W ($R<1/2$) can always invade because there is no ancestral association between $A$ alleles and sex chromosomes in males, $\left( \hat{p}^\male_Y-\hat{p}^\male_X \right)=0$, see Eq \eqref{eq:freq_diffs}.
-%The second term in Eq \eqref{eq:lambda_neoW} therefore disappears and invasion depends only on the sign of $(r-R)$, as in the case of the neo-Y. 
-%Indeed, invasion typically occurs when the neo-W is more closely linked to the selected locus than the ancestral sex-determining region (Fig \ref{fig:Combination_Centimorgans}).
 To clarify the parameter space under which invasion occurs with weak selection ($\lambda_{W'}^{(XY)}>1$) and $R>r$, we focus on cases where dominance coefficients are equal in the two sexes, $h^\female=h^\male$, and haploid selection only occurs in one sex (e.g., during male meiosis only).
@@
 These special cases indicate that neo-W invasion occurs for a large fraction of the parameter space, even though the neo-W uncouples the sex-determining locus from a locus under selection. 
-Fig \ref{fig:Combination_Centimorgans} then demonstrates that under these conditions neo-W alleles can spread when they are more loosely \textit{or} more closely linked to the locus that experiences haploid selection (c.f., Fig \ref{fig:SexAntagTighter}A for diploid sexually-antagonistic selection alone).
+Fig \ref{fig:Combination_Centimorgans} then demonstrates that under these conditions neo-W alleles can spread when they are more loosely \textit{or} more closely linked to the locus that experiences haploid selection, i.e., Conclusions 3B and 3C (c.f., Fig \ref{fig:SexAntagTighter}A for diploid sexually-antagonistic selection alone).
 %When the neo-W is more closely linked to the haploid selected locus its invasion increases (or creates anew) sex-ratio bias (Fig \ref{fig:SexRatioBad}A).
@@
 \noindent\textit{Conclusion 4:}
-\textbf{When selection is weak relative to recombination, the presence of haploid selection equally favors the spread of new sex determination systems that reduce sex-ratio bias (benefiting from Fisherian sex ratio selection) or generate a sex-ratio bias (benefiting from associations with selected alleles).
+\textbf{When selection is weak relative to recombination, the presence of haploid selection equally favors the spread of new sex determination systems that reduce sex-ratio bias (benefiting from Fisherian sex ratio selection) or that generate a sex-ratio bias (benefiting from associations with selected alleles).
 }
@@
 However, Fig \ref{fig:SexRatioBad}B shows that a neo-Y can invade the resulting ZW system under the same conditions. 
-When $R<1/2$, the invading neo-Y becomes associated with the male meiotic drive allele and the zygotic sex ratio actually evolves to become male-biased (as occurs in \cite{Ubeda:2015fx}, beginning from ESD).
+When $R<1/2$, the invading neo-Y becomes associated with the male meiotic drive allele and the zygotic sex ratio evolves to become male-biased (as occurs in \cite{Ubeda:2015fx}, beginning from ESD). 
 In this case, the neo-Y spreads because it is often found in males and can, if it carries the driven allele $a$, benefit from haploid selection in males (Fig \ref{fig:SexRatioBad}B).
@@
 In panel A, male meiotic drive in an ancestral XY system causes a male bias (see Fig \ref{fig:model_outline}B), allowing a neo-W to invade and replace the ancestral sex-determining system (inset shows neo-W frequency rising to fixation among female gametes), which balances the zygotic sex ratio.
-In panel B, male drive in an ancestral ZW system has no effect on the zygotic sex ratio yet a neo-Y can invade and replace the ancestral sex-determining system (inset shows neo-Y frequency rising to fixation among male gametes).
+In panel B, male drive in an ancestral ZW system has no effect on the zygotic sex ratio (50:50 at generation 0), yet a neo-Y can invade and replace the ancestral sex-determining system (inset shows neo-Y frequency rising among male gametes, reaching an asymptote where all males bear neo-Y, with meiotic drive sometimes causing more than 50\% of male gametes to bear the neo-Y).
 %When $R<1/2$, the neo-Y becomes associated with the allele favoured by drive, causing the zygotic sex ratio to become biased, hence the frequency of the neo-Y at pseudo-fixation can be higher than $0.5$ (inset).
@@
 For example with $R=1/2$ in Fig \ref{fig:SexRatioBad}B (green curve), the neo-Y allele spreads despite the fact that it cannot benefit from drive because free recombination moves it randomly between driven and non-driven backgrounds.
-%Nevertheless, the unlinked neo-Y can spread because diploids bearing it more often carry the non-driven allele $A$, which is found at high frequency on the W background and has higher average diploid fitness.% to balance the haploid advantage of the $a$ allele at equilibrium.
-Nevertheless, the unlinked neo-Y can spread because males bearing it more often carry the non-driven allele $A$ and have higher average diploid fitness compared to ZZ males, which bear a high frequency of the driven allele (since $r<R$).
+Nevertheless, the unlinked neo-Y can spread because males bearing it more often carry the non-driven allele $A$ and have higher average diploid fitness compared to ZZ males, which bear a high frequency of the driven allele, $a$, from their mothers.
 
@@
 \begin{split}
-\lambda_{ESD'}^{(XY)} =& 1 + \frac{{(1-2k)}^2}{4}V_{A}{S_{A}}^2\frac{r-R}{r R} \\
+\lambda_{ESD'}^{(XY)} =& 1 + \frac{{(1-2k)}^2}{4}\bar{p}(1-\bar{p}){S_{A}}^2\frac{r-R}{r R} \\
 &+\frac{k(\hat{p}^\male_Y-\hat{p}^\male_X)}{2}\left[ k \left(2\alpha_{\Delta}^\male-2\alpha_{\Delta}^\female+t^\male-t^\female \right) -2(1-k)S_{A}\right]+O\left(\epsilon^3\right).
@@
 where $\lambda_{Y'\rvert R=1/2}^{(XY)}$ and $\lambda_{W'\rvert R=1/2}^{(XY)}$ represent $\lambda_{Y'}^{(XY)}$ and $\lambda_{W'}^{(XY)}$ when evaluated at $R=1/2$ (Equations \ref{eq:lambda_neoY} and \ref{eq:lambda_neoW}).
-That is, recombination between the selected locus and the novel sex-determining locus, $R$, does not enter into the $k=1/2$ results.
-This is because sex is essentially randomized each generation, %as if the novel sex-determiner were on an unlinked site that half the time acts as a neo-W and half the time as a neo-Y.
-preventing associations from building up between alleles at locus $\mathbf{A}$ and sex. 
+That is, ESD with $k=1/2$ behaves as if the $\mathbf{M}$ and $\mathbf{A}$ loci were unlinked, regardless of the actual value of $R$.
+This is because sex is randomized each generation in individuals bearing the $m$ allele, preventing associations from building up between it and alleles at locus $\mathbf{A}$. 
 Eq \eqref{eq:lambda_ESD} shows that the ESD mutation gets half of the fitness of a feminizing mutation (neo-W) and half of the fitness of a masculinizing mutation (neo-Y), but only has an effect one half of the time (the other half of the time it produces the same sex as the ancestral system would have).
-As discussed above, $\lambda_{Y'\rvert R=1/2}^{(XY)}$ is necessarily less than one (cis-GSD transition), but $\lambda_{W'\rvert R=1/2}^{(XY)}$ (trans-GSD transition) can be greater than one if there is haploid selection (see Conclusion 3B).
-That is, with haploid selection, an allele causing environmental-sex-determination can invade an ancestrally-XY system because it generates females that are either rare or have high fitness, in the same manner as a neo-W (likewise, ESD invades a ZW system for the same reasons a neo-Y can).
+As discussed above, $\lambda_{Y'\rvert R=1/2}^{(XY)}$ is necessarily less than or equal to one when selection is weak (Conclusion 3A), but $\lambda_{W'\rvert R=1/2}^{(XY)}$ can be greater than one if there is haploid selection (see Conclusion 3C).
+That is, with haploid selection, an allele causing environmental-sex-determination can invade an ancestrally-XY system because it generates females that are either rare or have high fitness, in the same manner as a neo-W (likewise, ESD invades a ZW system for the same reasons that a neo-Y can).
 %An important result from Eq \eqref{eq:lambda_ESD} is that ESD can invade if there is haploid selection. 
@@
 New sex-determination systems are typically expected to spread when they equalise the sex ratio and/or when they increase linkage with loci that experience sex-differences in selection~\cite{Blaser2012, vanDoorn2014re}.
-In accordance with the latter mechanism, we find that sex-differences in selection at the haploid stage can favour trans-GSD transitions that tighten sex-linkage (Conclusion 3A).
+In accordance with the latter mechanism, we find that sex-differences in selection at the haploid stage can favour cis- or trans-GSD transitions that tighten sex-linkage (Conclusion 3A \&3B).
 %, as exemplified in~\cite{Ubeda:2015fx} for ESD-GSD transitions.
-However, we also find that trans-GSD transitions can be favoured in cases where linkage with the sex-determining locus is actually weakened (Conclusions 2 \& 3B, Fig \ref{fig:SexAntagTighter} \& \ref{fig:regionplots}), especially when there is haploid selection (Conclusion 3B, Figs \ref{fig:Combination_Centimorgans} \& \ref{fig:SexRatioBad}).
+Contrary to this expectation, however, we find that trans-GSD transitions can be favoured that loosen linkage with the sex-determining locus, either when linkage is initially tight (Conclusions 1 \& 2, \ref{fig:regionplots} \& Fig \ref{fig:SexAntagTighter}) or when there is haploid selection (Conclusion 3C, Figs \ref{fig:Combination_Centimorgans} \& \ref{fig:SexRatioBad}).
 Furthermore, we show that the spread of new sex-determination systems is not dominated by selection to balance the sex ratio (Conclusions 4 \& 5, Fig \ref{fig:SexRatioBad}).
@@
 %We find that the spread of new sex-determining systems cannot be simply predicted from their effect on the sex ratio. 
-On one hand, sex-ratio biases caused by haploid selection can facilitate trans-GSD transitions or transitions from genetic to environmental sex determination~\cite{Kozielska:2010vm}. 
+On the one hand, sex-ratio biases caused by haploid selection can facilitate trans-GSD transitions or transitions from genetic to environmental sex determination~\cite{Kozielska:2010vm}. 
 For instance, alleles favoured by haploid selection in males often become associated with the Y allele, which leads to an ancestral male-biased zygotic sex ratio.
-This male bias increases the potential for a neo-W or ESD allele to invade (Table \ref{tab:haplotype_growth}), which can equalize the sex ratio (e.g., see Fig \ref{fig:SexRatioBad}B, for related examples see~\cite{Kozielska:2010vm}).
+This male bias increases the potential for a neo-W or ESD allele to invade (Table \ref{tab:haplotype_growth}), equalizing the sex ratio (e.g., see Fig \ref{fig:SexRatioBad}B, for related examples see~\cite{Kozielska:2010vm}).
 %We find that sex-ratio biases caused by haploid selection can also affect transitions between sex-determining systems (e.g., see $\zeta$ terms in Table \ref{tab:haplotype_growth}). 
@@
 Indeed, transitions between sex-determining systems can generate stronger sex-ratio biases (e.g., Fig \ref{fig:SexRatioBad}A and step 1 in~\cite{Ubeda:2015fx}).
-%For example, where a neo-Y invades and is linked with a locus that experiences haploid selection in male gametes, the sex ratio evolves to become biased \citep[e.g., see Fig \ref{fig:SexRatioBad}A and step 1 in][]{Ubeda:2015fx}.
-%For example, in an ancestral ZW system, haploid selection in males can allow a linked neo-Y to invade, despite the fact that it creates a male-biased sex ratio because the neo-Y becomes associated with the driven allele (Fig \ref{fig:SexRatioBad}A).
-%\textcolor{blue}{and figure 1, where the end of one panel is the same as the beginning of another, however, this figure may change).}
-%What we would like to stress is that sex-ratio selection alone cannot predict when new sex-determining systems can evolve.
-Significantly, with weak selection, we find that there is no difference in conditions allowing XY to ZW and ZW to XY transitions (Conclusion 4) %, indicating that transitions in sex determination are not predominantly predicted by their effect on the sex ratio (i.e., the sex-ratio bias created by male haploid selection facilitates the spread of a neo-W allele into an XY system to the same degree that male haploid selection drives the spread of a neo-Y into a ZW system with a 1:1 sex ratio).
-%An asymmetry can develop when sex-linkage is tight (e.g., Fig \ref{fig:Combination_Centimorgans} near -25cM and 25cM) but under most circumstances we do not predict asymmetry between XY to ZW and ZW to XY transitions despite the presence/absence of sex-ratio selection.
+Significantly, with weak selection, we find that there is no difference in conditions allowing XY to ZW and ZW to XY transitions (Conclusion 4) 
 even when haploid selection always acts in the same sex (e.g., males).  
@@
 In addition, Y-linked genes are over-expressed relative to X-linked genes in pollen (but not in flower buds or leaves). 
-This suggests that the spread of neo-Y chromosomes in this clade could have been favoured through linkage with haploid selected genes rather than those under sexual antagonism. 
+This suggests that the spread of neo-Y chromosomes in this clade could have been favoured through linkage with haploid selected genes rather than those under sexually antagonistic selection. 
 %maybe add a flag here for switching to clade-level expectations:
@@
 In support of this hypothesis, researchers have identified genes on recently derived sex chromosomes that might be under sexually-antagonistic selection~\cite{Lindholm:2002dw,Tripathi:2009cw,Roberts2009,Ser:2010iq}.
-However, we show that, if selected loci are tightly linked to the ancestral sex-determining locus, they can drive trans-GSD transitions which reduce sex-linkage (Conclusion 2, \& 3B), thus widening the range of genomic locations that could be driving observed trans-GSD transitions.
+However, we show that, if selected loci are tightly linked to the ancestral sex-determining locus, they can drive trans-GSD transitions that reduce sex-linkage (Conclusion 2, \& 3C), thus widening the range of genomic locations where selection could be driving observed trans-GSD transitions.
 In addition, we find that polymorphic sex determining systems (X, Y, and neo-W alleles all segregating) can be maintained when a selected locus is tightly linked to the ancestral sex-determining system (e.g., \nameref{fig:freqAll}B and \nameref{fig:freqAll}C), which is not possible with loose linkage~\cite{vanDoorn:2010hu}.
-These conclusions apply in cases with or without haploid selection.
+This pair of conclusions apply in cases with or without haploid selection.
 
@@
 We have shown that tight sex-linkage and haploid selection can drive previously unexpected transitions between sex-determining systems.
-In particular, both can select for new sex-determining loci that are more loosely linked to loci under selection (Conclusions 2 \& 3B). 
-In addition, haploid selection can cause transitions in GSD analogous to those caused by purely sexually-antagonistic selection, eliminating the need for differences in selection between male and female diploids (Conclusion 3A \& 3B).
+In particular, both can select for new sex-determining loci that are more loosely linked to loci under selection (Conclusions 2 \& 3C). 
+In addition, haploid selection can cause transitions in GSD analogous to those caused by purely sexually-antagonistic selection, eliminating the need for differences in selection between male and female diploids (Conclusion 3A, 3B \& 3C).
 We conclude that haploid selection should be considered as a pivotal factor driving transitions between sex-determining systems. 
@@
 %(A)\ \ \ &\hat{p}_{Y}^{\male}=0,
-%\ \hat{q}=\frac{1}{2}\left(1 - \alpha_\Delta^\male \frac{ w_{Aa}^{\male} \phi}{w_{Aa}^{\male} \phi+ w_{aa}^{\male} \psi}\right),\\
+%\ \hat{q}_{Y}=\frac{1}{2}\left(1 - \alpha_\Delta^\male \frac{ w_{Aa}^{\male} \phi}{w_{Aa}^{\male} \phi+ w_{aa}^{\male} \psi}\right),\\
 %&\hat{p}_{X}^{\female}=\frac{w_{a}^{\female} \phi}{w_{a}^{\female} \phi+ w_{A}^{\female} \psi},
@@
 %(A')\ \ \ &\hat{p}_{Y}^{\male}=1,
-%\ \hat{q}=\frac{1}{2}\left(1 + \alpha_\Delta^\male \frac{w_{Aa}^{\male} \phi'}{w_{Aa}^{\male} \phi' + w_{AA}^{\male} \psi'}\right),\\
+%\ \hat{q}_{Y}=\frac{1}{2}\left(1 + \alpha_\Delta^\male \frac{w_{Aa}^{\male} \phi'}{w_{Aa}^{\male} \phi' + w_{AA}^{\male} \psi'}\right),\\
 %&\hat{p}_{X}^{\female}=1-\frac{w_{A}^{\female} \phi'}{w_{A}^{\female} \phi'+ w_{a}^{\female} \psi'},
 %\ \hat{p}_{X}^{\male}=1-\frac{(1-\alpha_\Delta^\male)w_{Aa}^{\male} \phi'}{(1-\alpha_\Delta^\male)w_{Aa}^{\male} \phi'+w_{AA}^{\male} \psi'} \nonumber \\
-%(B)\ \ \ &\hat{p}_{Y}^{\male}=0,\ \hat{p}_{X}^{\female}=1,\ \hat{p}_{X}^{\male}=1, \ \hat{q}=(1 -\alpha^\male_\Delta)/2\\
-%(B')\ \ \ &\hat{p}_{Y}^{\male}=1,\ \hat{p}_{X}^{\female}=0,\ \hat{p}_{X}^{\male}=0, \ \hat{q}=(1+\alpha^\male_\Delta)/2
+%(B)\ \ \ &\hat{p}_{Y}^{\male}=0,\ \hat{p}_{X}^{\female}=1,\ \hat{p}_{X}^{\male}=1, \ \hat{q}_{Y}=(1 -\alpha^\male_\Delta)/2\\
+%(B')\ \ \ &\hat{p}_{Y}^{\male}=1,\ \hat{p}_{X}^{\female}=0,\ \hat{p}_{X}^{\male}=0, \ \hat{q}_{Y}=(1+\alpha^\male_\Delta)/2
 %\end{align}
@@
 %\begin{split}
-%\hat{p}^\male_X-\hat{p}^\female_X&=V_{A}\big{(}D^\male - D^\female +\alpha_{\Delta}^\male-\alpha_{\Delta}^\female \big{)}
+%\hat{p}^\male_X-\hat{p}^\female_X&=\bar{p}(1-\bar{p})\big{(}D^\male - D^\female +\alpha_{\Delta}^\male-\alpha_{\Delta}^\female \big{)}
 %+O(\epsilon^2)\\
 %%
-%\hat{p}^\male_Y-\hat{p}^\female_X&=V_{A}\left[D^\male - D^\female+\alpha_{\Delta}^\male-\alpha_{\Delta}^\female+(1-2r)(t^\male-t^\female)\right]/2r
+%\hat{p}^\male_Y-\hat{p}^\female_X&=\bar{p}(1-\bar{p})\left[D^\male - D^\female+\alpha_{\Delta}^\male-\alpha_{\Delta}^\female+(1-2r)(t^\male-t^\female)\right]/2r
 %+O(\epsilon^2)\\
 %%
-%\hat{p}^\male_Y-\hat{p}^\male_X&=V_{A}\left(D^\male - D^\female+\alpha_{\Delta}^\male-\alpha_{\Delta}^\female+t^\male-t^\female\right)(1-2r)/2r
+%\hat{p}^\male_Y-\hat{p}^\male_X&=\bar{p}(1-\bar{p})\left(D^\male - D^\female+\alpha_{\Delta}^\male-\alpha_{\Delta}^\female+t^\male-t^\female\right)(1-2r)/2r
 %+O(\epsilon^2),
@@
 %\noindent
-%where $V_{A}=\bar{p}(1-\bar{p})$ is the variance in the frequency of $A$ and $D^\circ=\big{[} \bar{p}s^\circ+(1-\bar{p})h^\circ s^\circ\big{]} -\big{[} \bar{p}h^\circ s^\circ+(1-\bar{p}) \big{]}$ corresponds to the difference in fitness between $A$ and $a$ alleles in diploids of sex $\circ \in \{\female,\male\}$.
+%where $\bar{p}(1-\bar{p})=\bar{p}(1-\bar{p})$ is the variance in the frequency of $A$ and $D^\circ=\big{[} \bar{p}s^\circ+(1-\bar{p})h^\circ s^\circ\big{]} -\big{[} \bar{p}h^\circ s^\circ+(1-\bar{p}) \big{]}$ corresponds to the difference in fitness between $A$ and $a$ alleles in diploids of sex $\circ \in \{\female,\male\}$.
 %The frequency of Y-bearing male gametes depends upon the difference in the frequency of the $A$ allele between X- and Y-bearing male gametes and the strength of meiotic drive in favour of the $A$ allele in males, $q=1/2+\alpha_{\Delta}^\male(\hat{p}^\male_Y-\hat{p}^\male_X)/2+O(\epsilon^3)$.

### 2018-05-17 LaTeX/main_revised.tex
final Sally changes to main text

@@
 We conclude that haploid selection should be considered as a pivotal factor driving transitions between sex-determining systems. 
-Further, transitions involving haploid selection can be driven by sex-ratio selection or cause sex-ratio biases to evolve; to leading order, selection to balance the sex ratio and the benefits of hitch-hiking with haploid selected alleles are of equal magnitude (Conclusions 4 \& 5).
-Overall, our results suggest several new scenarios under which new sex-determining systems are favoured, which could help to explain why the evolution of sex-determining systems is so dynamic.
+Further, transitions involving haploid selection can eliminate or generate sex-ratio biases; to leading order, selection to balance the sex ratio and the benefits of hitch-hiking with haploid selected alleles, leading to a biased sex ratio, are of equal magnitude (Conclusions 4 \& 5).
+Overall, our results suggest several novel scenarios under which new sex-determining systems are favoured, which could help to explain why the evolution of sex-determining systems is so dynamic.
 

### 2018-05-18 LaTeX/main_revised.tex
figures updated with hatching

--- 2018-05-17 LaTeX/main_revised.tex
@@
 When there is overdominance in males, X-$A$ Y-$a$ males have high fitness and the $A$ allele is favoured by selection on the X background in males.
-Therefore, the $A$ allele can be polymorphic or even fixed on the X background despite selection favouring the $a$ allele in females (e.g., see outlined region in Fig \ref{fig:regionplots}B and~\cite{Lloyd1977,Otto2014}).
+Therefore, the $A$ allele can be polymorphic or even fixed on the X background despite selection favouring the $a$ allele in females (e.g., see non-hatched region in Fig \ref{fig:regionplots}B and~\cite{Lloyd1977,Otto2014}).
 In such cases, neo-W-$a$ haplotypes can spread because they create more $Aa$ and $aa$ females when pairing with an X-bearing gamete from males and because they bring more of the Y-$a$ haplotype into females, where it has higher fitness (Fig \ref{fig:model_outline}D).
@@
 %\centerline{\includegraphics[width=1.25\linewidth]{Region_plot_combined_Mike}}
-\centerline{\includegraphics[width=1.4\linewidth, right]{../Plots/Region_plot_combined}}
+\centerline{\includegraphics[width=1.4\linewidth, right]{../Plots/Region_plot_combined.eps}}
 \caption{
 {\bf When the ancestral XY locus is tightly linked to a locus under selection ($r=0$), one or both neo-W haplotypes can spread (no haploid selection).}
-We vary the fitness of male homozygotes relative to heterozygotes ($w_{Aa}^\circ=1$) and only consider stable equilibria at which both $\mathbf{A}$ locus alleles are maintained and the $a$ allele is initially fixed on the Y (region outlined).
+We vary the fitness of male homozygotes relative to heterozygotes ($w_{Aa}^\circ=1$) and only consider stable equilibria at which both $\mathbf{A}$ locus alleles are maintained and the $a$ allele is initially fixed on the Y (non-hatched region).
 Here, selection in females can favour the $A$ allele (panel A, $w_{aa}^\female=0.85$, $w_{AA}^\female=1.05$), favour the $a$ allele (panel B, $w_{aa}^\female=1.05$, $w_{AA}^\female=0.85$), or be overdominant (panel C, $w_{aa}^\female=w_{AA}^\female=0.6$).
@@
 \centering
-\centerline{\includegraphics[width=1.4\linewidth, right]{../Plots/PositionPlot_SexAntagTighter}}
+\centerline{\includegraphics[width=1.4\linewidth, right]{../Plots/PositionPlot_SexAntagTighter.eps}}
 \caption{
@@
 In panel C we vary the recombination rate between the neo-W and the selected locus ($R$) for a fixed recombination rate between the ancestral sex-determining locus and the selected locus ($r=0.005$). 
-Coloured markers show recombination rates for which the temporal dynamics of invasion are plotted in the inset, demonstrating that neo-W alleles can reach pseudo-fixation if they are more (black) or less (red) closely linked to a locus experiencing sexually-antagonistic selection.
+Coloured markers show recombination rates for which the temporal dynamics of invasion are plotted in the inset, demonstrating that neo-W alleles reach fixation if they are more (black) or less (red) closely linked to a locus experiencing sexually-antagonistic selection.
 A very loosely linked neo-W does not spread in this case (blue and green lines overlap and go to 0 in inset). 
@@
 \centering
-\includegraphics[width=\linewidth]{../Plots/PositionPlot}
+\includegraphics[width=\linewidth]{../Plots/PositionPlot.eps}
 \caption{

### 2018-05-18 LaTeX/main_revised.tex
added some references for meiotic drive to discussion

--- 2018-05-17 LaTeX/main_revised.tex
@@
 %, as exemplified in~\cite{Ubeda:2015fx} for ESD-GSD transitions.
-Contrary to this expectation, however, we find that trans-GSD transitions can be favoured that loosen linkage with the sex-determining locus, either when linkage is initially tight (Conclusions 1 \& 2, \ref{fig:regionplots} \& Fig \ref{fig:SexAntagTighter}) or when there is haploid selection (Conclusion 3C, Figs \ref{fig:Combination_Centimorgans} \& \ref{fig:SexRatioBad}).
+Contrary to this expectation, however, we find that trans-GSD transitions can be favoured that loosen linkage with the sex-determining locus, either when linkage is initially tight (Conclusions 1 \& 2, Figs \ref{fig:regionplots} \& \ref{fig:SexAntagTighter}) or when there is haploid selection (Conclusion 3C, Figs \ref{fig:Combination_Centimorgans} \& \ref{fig:SexRatioBad}).
 Furthermore, we show that the spread of new sex-determination systems is not dominated by selection to balance the sex ratio (Conclusions 4 \& 5, Fig \ref{fig:SexRatioBad}).
@@
 even when haploid selection always acts in the same sex (e.g., males).  
-That is, the sex-ratio bias created by male haploid selection facilitates the spread of a neo-W allele into an XY system to the same degree that male haploid selection drives the spread of a neo-Y into a ZW system with a 1:1 sex ratio.
+That is, the sex-ratio bias created by male haploid selection facilitates the spread of a neo-W allele into an XY system to the same degree that male haploid selection drives the spread of a neo-Y into a ZW system with a 1:1 sex ratio (Fig \ref{fig:SexRatioBad}).
 %Thus, haploid selection can favour trans-GSD transitions both via sex-ratio selection and via selection on alleles associated with the new sex-determining allele, and these selective pressures are often predicted to be of equal magnitude.
@@
 Because both Fisherian selection to equalize the sex ratio and the benefits of hitchhiking with driven alleles can facilitate transitions among sex chromosome systems, we predict that haploid selection should increase the lability of sex determination systems.
-Even in animal and plant species that have much larger and more conspicuous diploid phases than haploid phases, many loci have been shown to experience haploid selection through gamete competition and/or meiotic drive~\cite{Mulcahy:1996ha,JOSEPH:2004haa, Lalanne2004,Ubeda:2005gw,Fishman2005,Leppala2008,Leppala2013,Didion2015,Didion2016, Lindholm:2016cw}.
-In some cases, meiotic drive (Burt and Trivers, 2006, Chapter 6~\cite{Burt:2006}) or gametic competition~\cite{Lloyd:1974tz,Conn:1981uw,Stehlik:2005ul,Stehlik:2006to,Field:2012fd,Field:2013cc} among X- and Y-bearing gametes is known to cause sex-ratio biases.
-%Segregation distortion provides putative evidence of haploid selection and can sometimes be attributed to meiotic drive and/or gametic competition~\cite{Lalanne2004,Fishman2005,Leppala2008,Leppala2013,Didion2015,Didion2016}.
-%Where it has been characterized, individual cases of meiotic drive are generally sex-limited, exclusively affecting male or female gametes~\cite{Ubeda:2005gw,Lindholm:2016cw}.
-%Gametic competition is also typically sex-limited, occurring primarily among male gametes, because there are typically many more pollen/sperm than required for fertilization.
-In animals, recent studies have demonstrated that sperm competition, even within a single ejaculate, can alter haploid allele frequencies and increase offspring fitness~\cite{Immler:2014im,Alavioon2017}.
-Although precise estimates are uncertain, a relatively small proportion of all genes are thought to be expressed and selected during competition in animal sperm~\cite{Zheng:2001fi,JOSEPH:2004haa,Vibranovski:2010et}.
-However, expression is not required for haploid selection if the fitness of a gamete depends on its ability to condense DNA~\cite{Immler2018}.   
-In plants haploid selection may be particularly important. %due to the presence of a multicellular haploid stage. 
-For example, 60-70\% of all genes are expressed in the male gametophyte, and these genes exhibit stronger signatures of selection than randomly-chosen genes~\cite{Borg:2009jpa,Arunkumar:2013iq,Gossmann:2014dua}.
+Even in animal and plant species that have much larger and more conspicuous diploid phases than haploid phases, many loci have been shown to experience haploid selection through gamete competition and/or meiotic drive~\cite{Mulcahy:1996ha,JOSEPH:2004haa, Lalanne2004,Ubeda:2005gw,Fishman2005,Leppala2008,Leppala2013,Didion2015,Didion2016,Lindholm:2016cw}, which can generate biased sex-ratios~\cite{Jaenike:2001vb,Burt:2006,Lloyd:1974tz,Conn:1981uw,Stehlik:2005ul,Stehlik:2006to,Field:2012fd,Field:2013cc}.
+In animals, a relatively small proportion of all genes are thought to be expressed and selected during competition in animal sperm~\cite{Zheng:2001fi,JOSEPH:2004haa,Vibranovski:2010et}.
+Nevertheless, recent studies have demonstrated that sperm competition, even within a single ejaculate, can alter haploid allele frequencies and increase offspring fitness~\cite{Immler:2014im,Alavioon2017}.
+Expression in the gamete is not required for haploid selection if the fitness of a gamete depends on its ability to condense DNA~\cite{Immler2018}. 
+Furthermore, expression during gamete production often underlies systems of meiotic drive~\cite{Tau2007,Cocquet2012,Helleu2016}, which may be a common form of haploid selection in animals~\cite{Bachtrog2018}.
+In plants, competition among gametophytes may be particularly important. 
+It is estimated that 60-70\% of all genes are expressed in the male gametophyte, and these genes exhibit stronger signatures of selection than randomly-chosen genes~\cite{Borg:2009jpa,Arunkumar:2013iq,Gossmann:2014dua}.
 Furthermore, artificial selection pressures applied to male gametophytes are known to cause a response to selection (e.g.,~\cite{Hormaza:1996cv,Ravikumar:2003uo,Hedhly:2004iv,Clarke:2004ir}).
@@
 %HAPLOID SELECTION (genomic location of haploid selected loci and comparative patterns) 
-%We have shown that the spread of new sex-determining systems can be driven by loci experiencing haploid selection. 
-%Our results suggest that haploid selected loci that have been involved in driving turnovers between sex-determining systems could occur around the ancestral- or novel-sex-determining regions. 
-%Our results suggest that polymorphic loci that are ancestrally sex-linked and under sex-specific selection could also drive heterogametic transitions between sex-determining systems. 
-%As with sexually-antagonistic selection, the presence of haploid selected loci around ancestral- or novel-sex-determining regions could support their role in sex chromosome turnover.
 Linking haploid expression with the evolution of sex-determination, a recent transcriptome analysis in \textit{Rumex} shows that pollen-biased expression (relative to expression in flower buds or leaves) is enhanced among XY-linked genes compared to autosomal genes or compared to hemizygous genes that are only linked to the X
@@
 Assuming that transitions from dioecy to hermaphroditism (equal parental investment in male and female gametes) are favoured in a similar manner to the ESD examined here (equal probability of zygotes developing as males or females), our results suggest that competition among haploid pollen could drive transitions between dioecy and hermaphroditism, which are frequent in plants~\cite{Kafer2017, Goldberg2017}.
-To further examine this link, future theory could simultaneously include inbreeding, haploid selection, and sex chromosomes when investigating transitions between dioecy and hermaphroditism. 
+To further examine this link, future theory could also include inbreeding, which is an important consideration during transitions between dioecy and hermaphroditism~\cite{Charlesworth1978}. 
 Future empirical studies could look for evidence of haploid selection acting on former sex chromosomes in hermaphroditic species (e.g., a study such as \cite{Sandler264382} on ancestral, rather than derived, sex chromosomes).
@@
 In support of this hypothesis, researchers have identified genes on recently derived sex chromosomes that might be under sexually-antagonistic selection~\cite{Lindholm:2002dw,Tripathi:2009cw,Roberts2009,Ser:2010iq}.
-However, we show that, if selected loci are tightly linked to the ancestral sex-determining locus, they can drive trans-GSD transitions that reduce sex-linkage (Conclusion 2, \& 3C), thus widening the range of genomic locations where selection could be driving observed trans-GSD transitions.
+However, we show that, if selected loci are tightly linked to the ancestral sex-determining locus, they can drive trans-GSD transitions that reduce sex-linkage (Conclusions 1 \& 2), thus widening the range of genomic locations where selection could be driving observed trans-GSD transitions.
 In addition, we find that polymorphic sex determining systems (X, Y, and neo-W alleles all segregating) can be maintained when a selected locus is tightly linked to the ancestral sex-determining system (e.g., \nameref{fig:freqAll}B and \nameref{fig:freqAll}C), which is not possible with loose linkage~\cite{vanDoorn:2010hu}.

### 2018-05-18 LaTeX/response.tex
improving response letter

@@
 For example, we first discuss the `haplotypic growth rates' and 'dissociative forces' (L158-170 and `interpreting this condition...', L173).
-We then lay out three specific conclusions (L179-199). 
-In the ``Tight linkage'' section, we now first describe specific cases why neo-W's can have improved female fitness, L235-259, with more focus on non-technical interpretation (e.g., L237-240). 
+We then lay out four specific conclusions (L179-199). 
+In the ``Tight linkage'' section, we now first describe specific cases why neo-W's can have improved female fitness, Conclusion 1, L235-259, with more focus on non-technical interpretation (e.g., L237-240).
 Then we discuss the fact that looser sex-linkage can evolve (L260-275, Conclusion 2). 
@@
 \item[(1)] Selection on loci in or near the non-recombining region around the ancestral sex-determining locus ($r\approx0$) prevents cis-GSD transitions (XY $\leftrightarrow$ XY, ZW $\leftrightarrow$ ZW) but can spur trans-GSD transitions (XY $\leftrightarrow$ ZW).
-(L228-230)
+(L236-238)
 \item[(2)] With tight linkage between a selected locus and the ancestral sex-determining locus ($r\approx0$), trans-GSD transitions (XY $\leftrightarrow$ ZW) can be favoured by selection \textit{even if they weaken sex-linkage} ($r<R$), potentially shifting sex determination to a different chromosome ($R=1/2$).
-Such transitions can also lead to the maintenance of multifactorial sex-determination systems. (L282-286)
-\item[(3A)] New sex-determining alleles (causing cis- \textit{or} trans-GSD transitions) can spread if they arise more closely linked with a locus that experiences selection than the ancestral-sex-determining locus is ($R<r$).
-(L324-326)
-\item[(3B)] New sex-determining alleles (causing trans-GSD transitions, XY $\leftrightarrow$ ZW) can spread even if they arise less closely linked with a locus that experiences selection than the ancestral-sex-determining locus is ($r<R$), requiring haploid selection.
-(L327-330)
+Such transitions can also lead to the maintenance of multifactorial sex-determination systems. (L290-294)
+\item[(3A)] New sex-determining alleles (causing cis-GSD transitions, XY $\leftrightarrow$ XY or ZW $\leftrightarrow$ ZW) are favoured if they arise more closely linked with a locus that experiences (haploid and/or diploid) selection than the ancestral-sex-determining locus is ($R<r$).
+(L326-328)
+\item[(3B)] New sex-determining alleles (causing trans-GSD transitions, XY $\leftrightarrow$ ZW) are favoured if they are linked with an ancestrally-autosomal locus that experiences (haploid and/or diploid) selection ($R<1/2$, $r=1/2$).
+(L333-335)
+\item[(3C)] With haploid selection, new sex-determining alleles (causing trans-GSD transitions, XY $\leftrightarrow$ ZW) can spread even if they arise less closely linked with a locus that experiences selection than the ancestral-sex-determining locus is ($r<R$).
+(L341-343)
 \item[(4)] When selection is weak relative to recombination, the presence of haploid selection equally favors the spread of new sex determination systems that reduce sex-ratio bias (benefiting from Fisherian sex ratio selection) or generate a sex-ratio bias (benefiting from associations with selected alleles).
@@
 
-\textcolor{blue}{Of these conclusions, (3A) and (3B) have some precendent.
-(3A) is similar to studies by van Doorn and Kirkpatrick (2007,2010) that do not include haploid selection.
+\textcolor{blue}{Of these conclusions, (3A), (3B), and (3C) have some precendent.
+(3A) and (3B) are similar to studies by van Doorn and Kirkpatrick (2007,2010) that do not include haploid selection.
 These comparisons are made immediately above the conclusions (L316-330) and mentioned elsewhere (L55, L77, L489).
-Including haploid selection, Ubeda et al. (2015) also involved examples similar to (3A), except that the starting state was ESD. 
-Kozielska et al. (2010) also had numerical examples that involved trans-GSD transitions with ($R>r$), as stated in (3B), but focussed only on sex ratio selection. 
+Including haploid selection, Ubeda et al. (2015) also involved examples similar to (3A) and (3B), except that the starting state was ESD. 
+Kozielska et al. (2010) also had numerical examples that involved trans-GSD transitions with ($R>r$), as stated in (3C), but focussed only on sex ratio selection. 
 We discuss how our results compare to these studies in the introduction (L58-75), discussion (L433-447) and results (L193, L363-369).
-Nevertheless, we have kept Conclusions 3A and 3B as highlighted conclusions. 
-This is partly to highlight these conclusions for clarity of communication and partly because our results are more general. 
-That is, as stated by the reviewer, our results ``converge on previously-identified conditions for the spread of new SD alleles, while also broadening the range of scenarios and conditions that can favour transitions between SD systems''}
+Nevertheless, we have highlighted these conclusions, partly for clarity of communication and partly because our results are more general. 
+That is, as stated by the reviewer, these results ``converge on previously-identified conditions for the spread of new SD alleles, while also broadening the range of scenarios and conditions that can favour transitions between SD systems''}
 %As (1A), (1B), and (2) have some antecedents in the literature, we discuss these immediately below each conclusion. 
@@
 \textcolor{blue}{
-This is an important assumption.
-As discussed in the supplementary of van Doorn \& Kirkpatrick (2007, Nature), partial dominance and incomplete penetrance (partial epistatic dominance) reduce the range parameter values that favour transitions.
-However, this reduction in parameter space is smooth and does not preclude transitions, meaning the qualitative conclusions are robust.
-\textcolor{red}{I actually think that parameter space is only reduced because they also have a locus near the ancestral SDR that selects against new sex determining systems.
-In a 3-locus system, like ours, I would expect the $\lambda-1$ to be lower for incomplete penetrance (partial epistatic dominance) but not to change sign.
+The `epistatic-dominance' between loci is important to the evolutionary dynamics.
+For example, Veller et al.
+(2018, Genetics) show that there is a tendency for drift to occur in the direction of the epistatically-dominant sex-determining locus (mentioned on L545-546).
+Our results also show that the outcome can depend on which sex-determining locus has an epistatically-dominant effect.
+For example, the end state of the red line in Fig 5 is the starting condition of the other panel.
+That is, we find that recurrent invasion can occur by a sequence of sex-determining loci that are epistatically-dominant over their predecessors (requiring haploid selection).
  }
-Further, there are many systems in which one sex-determining allele is epistatically dominant.
-And finally, our Mathematica file allows for arbitrary epistatic dominance coefficients.
-We now discuss the empirical evidence for epistatic dominance, our general Mathematica file, and the analysis of van Doorn and Kirkpartick when introducing our model. (L94-105)
-}
-%\textcolor{red}{This is obviously very important, and is commonly assumed (Kozielska et al.
-2010, van Doorn and Kirkpatrick 2007, 2010).
-There are a large number of other possibilities (given 9 genotypes that determine 2 sexes, ie $2^9$), and it seems like these alternatives could either increase or decrease selection on the invader.
-van Doorn and Kirkpatrick don't give any motivation (from my quick skim), but Kozielska et al.
-cite the housefly (Musca domestica), where it seems a single W is epistatically dominant over any number of loci with Y alleles.
-Is this ``compatible" with our model?}
-%
-%\textcolor{red}{Our analysis shows that the end state of the system depends on the `epistatic dominance' (term removed from our paper?) of the loci.
-Could draw this out more for this response.
-The drift-transitions Genetics paper rests on the difference in dominance, I'm pretty sure they have examples and the majority of new GSD systems are epistatically dominant.
-Also vD\&K 2010 say that there is evidence that epistatic dominance is common, and explain why a completely recessive should not invade.
+
+\textcolor{blue}{
+Empirical systems with multi-factoral sex-determination (including \textit{Musca domestica}) do indeed indicate that derived sex-determining systems are often `epistatically-dominant'. 
+We now mention this where we introduce this aspect of the model (L98-109). 
+We also point to the supplementary Mathematica file, which allows arbitrary `epistatic dominance' to be specified. 
+There are some numerical examples with reduced `epistatic dominance' in the supplementary material of van Doorn \& Kirkpatrick (2007, Nature), which we also point to here.
+Their findings suggest that the selective advantage is reduced (the modifier mutation effectively has a smaller effect) but the direction of evolution is expected to be qualitatively unchanged. 
 }
@@
 \noindent\paragraph{Response}
-\textcolor{blue}{We have replaced the male/female symbol with a circle.}
+\textcolor{blue}{This is true, the male/female symbol is commonly used to represent hermaphrodites, we have replaced the male/female symbol with a circle, which is a basis for both the male and female symbols.}
 
@@
 \noindent\paragraph{Response}
-\textcolor{blue}{We have kept the $V_A$ as we reuse this shorter, strictly positive, term throughout the text. This is also consistent with the well-known van Doorn and Kirkpatrick 2007, 2010 models.}
-\textcolor{red}{Maybe just change this?}
+\textcolor{blue}{We have made the suggested change.}
 
@@
 I find the article is not clearly written and could benefit from improving the presentation of the main results. 
-%
-%\noindent\paragraph{Response}
-%\textcolor{blue}{We hope the improvements discussed above (e.g., Response 2.1 and 2.2) and below have increased the clarity of our writing, especially regarding the main results.}
-%
-%\noindent\subsection{}
 I also find the article claims that: (a) the modeling work is novel and (b) the findings are unexpected to be only partially justified.
-%
-%\noindent\paragraph{Response}
-%\textcolor{blue}{As described at length below, we now give more weight to two previous papers (Kozielska et al 2010 and Ubeda et al 2015) and more precisely indicate which of our results are new and unexpected.}
-%
-%\noindent\subsubsection{}
 The works of Kozielska 2014 and Ubeda 2015 model the combined effects of both haploid and diploid selection on the evolution of new sex-chromosomes.
@@
 \textcolor{blue}{
-We have performed an extensive re-arrangement to improve the clarity of our writing, especially regarding the main results. 
-As described in Response 2.1 (point 6) and below, we now provide a prominent and longer discussion of Kozielska et al 2010 and Ubeda et al 2015 (L57-69) and more precisely indicate which of our model features and results are new and unexpected in light of these previous results (see Response 2.2).
+We have performed an extensive re-arrangement to improve the clarity of our writing, especially regarding the main results (see Responses 2.1-2.3). 
+As suggested by the reviewer (here and below), we also now give more prominence to the related results by Kozielska et al 2010 and Ubeda et al 2015 (e.g., L56-71, L198, L367-373, L440-446). 
+In particular, we introduce these studies on Lines 56-71 and more precisely indicate which of our model features and results are new and unexpected in light of these previous results.
+}
+
+\textcolor{blue}{
 While related, these two studies considered particular cases that we do not consider at length. 
-For example, Ubeda et al consider ESD-GSD transitions. 
-Nevertheless, these transitions involve increased linkage with a haploid selected locus, which is precedent for our Conclusion 3A (which considers only GSD-GSD transitions).
-We now mention this in the Introduction (L59-61) and again in the Discussion (L432).  
-Similarly, Kozielska et al involves a special case of GSD transitions during which sex-linkage goes from perfect to none, which is is an  example of our Conclusion 3B.
-This is twice mentioned (L64-67, L237). 
-Despite this precedent, we find the permissive parameter space allowing GSD-GSD transitions surprising. 
-%Especially because their main conclusion involved the strong influence of sex-ratio selection, which is explicitly not a driver during many such transitions. 
-In addition, our Conclusions 3A and 3B reconcile Kozielska et al and Ubeda et al, explaining that sex-ratio selection is not an overwhelming force driving transitions in sex determination. 
+For example, Ubeda et al. (2015) consider ESD-GSD transitions. 
+Nevertheless, the transitions in Ubeda et al.
+(2015) involve increased linkage with a haploid selected locus, which is precedent for our Conclusions 3A and 3B (which are for GSD-GSD transitions in which linkage with a haploid selected locus is increased).
+We now mention this in the Introduction (L59-61), Results (L369-373), and Discussion (L432).  
+Similarly, Kozielska et al.
+(2010) involves a special case of GSD transitions during which sex-linkage goes from perfect to none, which is is an example of our Conclusion 2 (and similar to Conclusion 3C, which are conclusions regarding GSD-GSD transitions in which linkage with a haploid selected locus is decreased).
+This is mentioned on lines (L63-64, L303, and L368). 
 We believe that our new presentation makes the novel and unexpected features of our results much more apparent. 
-%To be clear, we do not claim to be the first to include both haploid and diploid selection to a model investigating the evolution of new sex-chromosomes and we do not consider the addition of sex-specific selection or analytical results for previously numerical models to be our most significant contributions (again, see Responses 2.1 and 2.2 and below for more detail on what these are).
+For example, despite these precedents, we find the combination of Conclusions 3A, 3B, and 3C to be a striking solution that reconciles the results of Kozielska et al. (2010) and Ubeda et al. (2015). 
+We elaborate further on what makes our results novel and surprising in the responses below.
 }
@@
 $\lambda_{Y'}^{ZW}$ with $r<1/2$, $R=1/2$, and male meiotic drive).
-Step 2 in Ubeda et al 2015 shows that associations with a haploid selected locus can favour a new sex-determining allele despite causing biased sex ratios. 
+As mentioned by the reviewer, Step 2 in Ubeda et al 2015 shows that associations with a haploid selected locus can favour a new sex-determining allele despite causing biased sex ratios. 
 Nevertheless, it was difficult for us to intuit whether the presence/absence of ancestral sex-ratio bias would have a negligible or overwhelming effect on the evolution of new sex-determining alleles.
+Because we start from GSD, our model allows ancestral sex-ratio biases to build up due to the presence of haploid selected loci near to the ancestral sex-determining locus. 
+There are reasons to suspect that ancestral-sex-ratio biases would strongly influence the spread of new sex-determining systems.
 For example, step 3 of Ubeda et al involves the spread of an autosomal meiotic drive suppressor favoured by Fisherian sex-ratio selection and Kozielska et al 2010 show that ancestral sex-ratio bias can favour new sex determining systems that balance the sex ratio.
-These previous results are now discussed in the Introduction (L57-69). 
-We found our result, that these two forces are exactly equal (with selection weak relative to recombination), such that there is no difference between the propensity for XY-ZW or ZW-XY transitions, to be surprising.
+We found our result, that these forces are exactly equal (with selection weak relative to recombination), such that there is no difference between the propensity for XY-ZW or ZW-XY transitions, to be surprising.
 To clarify our meaning we have rephrased (in Author summary): ``Surprisingly, we find the two forces (selection to equalize the sex-ratio and the benefits of hitch-hiking with driven alleles that distort the sex ratio) will often be equally strong, and thus neither is sufficient to explain the spread of new sex-determining systems in every case."
@@
 \textcolor{blue}{
-The Ubeda et al 2015 results do indeed show that differential selection between male and female diploids is not required for new sex-determining alleles to spread; they show that a new genetic sex-determining allele can spread from ancestral ESD when it is linked to a locus that experiences sex-specific meiotic drive.
+The Ubeda et al.
+(2015) results do indeed show that differential selection between male and female diploids is not required for new sex-determining alleles to spread; they show that a new genetic sex-determining allele can spread from ancestral ESD when it is linked to a locus that experiences sex-specific meiotic drive.
 In this sentence, we were attempting to stress that new sex determining alleles can spread when they are \textit{less closely linked or even completely unlinked} to loci under differential male/female haploid and/or diploid selection.
@@
 We therefore found the large parameter space allowing invasion with $r<R$, sometimes in the absence of sex-ratio selection (or even in the absence of haploid selection), to be very unexpected.
-Nevertheless, we have rephrased (in Author Summary): ``We also find that new sex-determining alleles can spread despite being less closely linked to selected loci, driven by initially tight linkage or haploid selection."
-The changes to the presentation of the Introduction and Results should also help to clarify this point further (see Responses 2.1 and 2.2).
-%We discuss the related results of Kozielska and Ubeda on lines 261 and 350.
+To improve our communication of this result, we have rephrased (in Author Summary): ``We also find that new sex-determining alleles can spread despite being less closely linked to selected loci, driven by initially tight linkage or haploid selection."
+The changes to the presentation of the Introduction, Results, and Discussion should also help to clarify this point further (see Responses 2.1 and 2.2), this result is now also highlighted as `Conclusion 4'.
 }
@@
 \textcolor{blue}{
-First, we believe sex-differences in selection and sex ratio selection are two ``predominant" theories explaining sex-determination transitions. 
-Second, sexually-antagonistic selection was referred to as an example of ``selective differences between the sexes". 
-We believe the phrase 'selective differences between the sexes' includes sex-differences in drive (Ubeda et al 2015), which just occurs during haploid rather than diploid selection (see also Response 3.2.6).
-Finally, Charlesworth and Charlesworth 1978 (Am Nat and Heredity) discuss the role of inbreeding (and particularly inbreeding depression) in transitions from hermaphroditism to dioecy, without regard for genetic sex-determination.
-As noted on lines 468-472 in the original submission, we have only considered GSD-GSD transitions and GSD-ESD transitions.
+Here, sexually-antagonistic selection was referred to as an example of ``selective differences between the sexes". 
+We believe the phrase 'selective differences between the sexes' includes sex-differences in drive (Ubeda et al 2015), which occurs during haploid rather than diploid selection, as indicated in Fig 1B (see also Response 3.1.6).
+As mentioned elsewhere, the enhanced discussion of Ubeda et al. (2015) should help to clarify this point. 
+Charlesworth and Charlesworth 1978 (Am Nat and Heredity) discuss the role of inbreeding (and particularly inbreeding depression) in transitions from hermaphroditism to dioecy. 
+As described in the model section and lines 468-472 of the original submission, we have only considered GSD-GSD transitions and GSD-ESD transitions.
 For clarity, we have moved this description into the Introduction (L49-50). 
-In addition, where we draw a parallel between ESD and hermaphroditism (L468-476), we suggest future theory include inbreeding, haploid selection, and sex chromosomes. 
+Where we draw a parallel between ESD and hermaphroditism (L468-476), we suggest future theory include inbreeding and cite Charlesworth and Charlesworth (1978). 
 }
-
-%\textcolor{blue}{
-%We are unsure of which paper the reviewer is referring to.
-%Charlesworth 1978 PNAS 75:5618 discusses the degradation of the Y by Muller's ratchet and subsequent dosage compensation, which has little relevance here.
-%Charlesworth and Charlesworth 1978 Am Nat 112:975-997 discuss the role of inbreeding in transitions from hermaphrodism (ie no sex-determining alleles) to the case of dioecy (with sex-determining alleles).
-%Charlesworth and Charlesworth 1978 Heredity 41:137-153 is similar but begins with monoecy.
-%Assuming the reviewer meant one of the latter two, both it and Ubeda et al 2015 consider the origin of genetic sex-determination from hermaphrodism/monoecy or environmental sex-determination. 
-%Here we are much more concerned with transitions between genetic sex-determination systems.
-%Further, we do not state that sex-antagonism is one of the predominant theories explaining SD transitions, it is but one example where fitness differs between the sexes, another example being ``sex-different drive".
-%We discuss the fact that sex-specific drive can be thought of as a sex difference in selection in paragraph 5 of the introduction (see Response 3.2.6).
-%We have rephrased slightly to restrict ourselves to transitions between GSD: ``Predominant theories accounting for transitions between GSD systems by selection involve fitness differences between sexes (e.g., sexually antagonistic selection) or sex-ratio selection...".}
 
@@
 In this respect, one could consider gametic selection among sperm, for example, to be a form of male-specific selection.
-However, as noted here, the dynamics of selection during gametic selection cannot be captured by a diploid selection coefficient, which is why we model selection upon haploid genotypes specifically in two ways.
+However, as noted by the reviewer here, the dynamics of selection during gametic selection cannot be captured by a diploid selection coefficient, which is why we specifically model selection upon haploid genotypes.
+In our new manuscript, a roughly corresponding statement now reads ``On one hand, haploid selection is typically sex-limited in that it usually occurs among gametes produced by one sex only [38-41].''.
+We have also expanded our explanation of the mating system and the way we model haploid selection (see Response 3.2 below).
 }
-\textcolor{blue}{
-We have attempted to clarify by expanding our explanation of the mating system and the way we model haploid selection (see Response 3.2 below).}
 
@@
 \noindent\paragraph{Response}
-\textcolor{blue}{In the absence of sex-differences in selection it is true that antagonistic drive is not needed, but \textit{differences} in haploid selection between the sexes are needed (e.g., drive in only one sex, maintained by ploidally-antagonistic selection).
+\textcolor{blue}{In the absence of sex-differences in selection it is true that antagonistic drive is not needed, but \textit{differences} in haploid selection between the sexes are needed (e.g., drive in only one sex, with variations maintained by ploidally-antagonistic selection).
 If drive was the same in both sexes, $\alpha^{m}=\alpha^{f}$ (and all other male/female selection terms also equal), we show that the new sex-determining allele would not invade (e.g., equation 2 and 3).
@@
 \noindent\paragraph{Response}
-\textcolor{blue}{We do not agree. 
+\textcolor{blue}{
+We have chosen not to adjust our models to include a single parameter that measures transmission distortion. 
 Given our definition of meiotic drive and gametic competition (L106-116), the two processes are different.
-In particular, meiotic drive is assumed to occur during meiosis, and thus is ``gametic competition" amongst the gametes produced by a single individual. 
-As such, meiotic drive can only have an effect in heterozygotes.
-Gametic competition on the other hand, is competition amongst all the gametes produced by one sex (e.g., pollen from many male plants).
-Thus allele frequency changes can occur by gametic competition even if all individuals were homozygous (as long as there is a polymorphism).
-We have extended our description of how `gametic competition' and `meiotic drive' are modelled in the model section (L106-116), which helps to clarify why they are different and under what circumstances each applies.
+In particular, meiotic drive can only have an effect in heterozygotes.
+For example, this means that cases with `sperm killers' and then ``gametic competition" amongst the gametes produced by a single individual are appropriately modelled by our `meiotic drive' parameter.
+For the same reason, ``gametic competition'' of any type in a monogamous mating system corresponds to `meiotic drive' in our model (L116-119). 
+On the other hand, in our model, ``gametic competition'' is competition amongst all the gametes produced by one sex (e.g., pollen from many male plants).
+Thus, for example, allele frequency changes can occur by gametic competition even if all individuals were homozygous (as long as there is a polymorphism).
+We have extended our description of how we use the terms `gametic competition' and `meiotic drive' and how they are modelled in the model section (L106-116), which helps to clarify why they are different and under what circumstances each applies.
+Unfortunately, beyond defining our terms, it was not straightforward to resolve the different usages of the terms by different communities.
 }

### 2018-05-18 LaTeX/main_revised.tex
improving response letter

@@
 In panel C we vary the recombination rate between the neo-W and the selected locus ($R$) for a fixed recombination rate between the ancestral sex-determining locus and the selected locus ($r=0.005$). 
-Coloured markers show recombination rates for which the temporal dynamics of invasion are plotted in the inset, demonstrating that neo-W alleles reach fixation if they are more (black) or less (red) closely linked to a locus experiencing sexually-antagonistic selection.
+Coloured markers show recombination rates for which the temporal dynamics of invasion are plotted in the inset (frequency of females carrying a neo-W), demonstrating that neo-W alleles can reach fixation if they are more (black) or less (red) closely linked to a locus experiencing sexually-antagonistic selection.
 A very loosely linked neo-W does not spread in this case (blue and green lines overlap and go to 0 in inset). 
@@
 \begin{equation}
-\lambda_{Y'}^{(XY)} = 1 + \frac{1}{4}\bar{p}(1-\bar{p})S_{A}^2\frac{ \left( r-R \right) }{r R}+O\left(\epsilon^3 \right) 
+\lambda_{Y'}^{(XY)} = 1 + \frac{1}{4}\bar{p}(1-\bar{p}){S_{A}}^2\frac{ \left( r-R \right) }{r R}+O\left(\epsilon^3 \right) 
 \label{eq:lambda_neoY}
@@
 %The new sex-determining allele, $m$, will spread in an XY system if $\lambda_{m}^{(XY)}>1$. 
-Eq \eqref{eq:lambda_neoY} demonstrates that, under weak selection, a neo-Y allele will invade an XY system ($\lambda_{Y'}^{(XY)}>1$) if and only if it is more closely linked to the selected locus than the ancestral sex-determining locus (i.e., if $R<r$; note that $\bar{p}(1-\bar{p})S_{A}^2$ is strictly positive as long as $\mathbf{A}$ is polymorphic).
+Eq \eqref{eq:lambda_neoY} demonstrates that, under weak selection, a neo-Y allele will invade an XY system ($\lambda_{Y'}^{(XY)}>1$) if and only if it is more closely linked to the selected locus than the ancestral sex-determining locus (i.e., if $R<r$).%; note that $\bar{p}(1-\bar{p})S_{A}^2$ is strictly positive as long as $\mathbf{A}$ is polymorphic).
 This echoes our results above where a neo-Y could never invade if $r\approx0$. 
@@
 Similarly, a neo-W is typically favoured when it is more closely linked to the selected locus than the ancestral sex-determining region is, ($R<r$, e.g., Figs \ref{fig:SexAntagTighter}B and \ref{fig:Combination_Centimorgans}).
-Specifically, if the selected locus ($\mathbf{A}$) is ancestrally autosomal ($r=1/2$, leading to $ \hat{p}^\male_Y-\hat{p}^\male_X =0$ such that $\lambda_{W'}^{(XY)}=\lambda_{Y'}^{(XY)}$, Eqs \eqref{eq:lambda_neoY} and Eq \eqref{eq:lambda_neoW}), a more closely linked neo-W ($R<1/2$) is favoured.
+Specifically, if the selected locus ($\mathbf{A}$) is ancestrally autosomal ($r=1/2$, leading to $ \hat{p}^\male_Y-\hat{p}^\male_X =0$), a neo-W linked to the selected locus ($R<1/2$) will spread ($\lambda_{W'}^{(XY)}>1$).
 
@@
 \noindent
-In the absence of haploid selection ($t^\circ=\alpha^\circ_{\Delta}=0$), the spread of a neo-W is equivalent to the spread of a neo-Y ($\lambda_{W'}^{(XY)}=\lambda_{Y'}^{(XY)}$), such that trans-GSD transitions can occur if and only if the new sex-determining locus is more closely linked to a locus under selection ($R<r$), as found by \cite{vanDoorn:2010hu}.
+In the absence of haploid selection ($t^\circ=\alpha^\circ_{\Delta}=0$), Eq \eqref{eq:lambda_neoW} indicates that trans-GSD transitions can occur if and only if the new sex-determining locus is more closely linked to a locus under selection, $R<r$, as found by \cite{vanDoorn:2010hu}.
 However, with haploid selection and some ancestral sex-linkage ($r<1/2$; allowing allele frequency differences on the X and Y), the term in square brackets in Eq \eqref{eq:lambda_neoW} can be positive.
-Thus,
+This leads to
 
@@
 
-To clarify the parameter space under which invasion occurs with weak selection ($\lambda_{W'}^{(XY)}>1$) and $R>r$, we focus on cases where dominance coefficients are equal in the two sexes, $h^\female=h^\male$, and haploid selection only occurs in one sex (e.g., during male meiosis only).
+To clarify the parameter space under which neo-W alleles spread despite looser linkage with the selected locus ($R>r$), we focus on cases where dominance coefficients are equal in the two sexes, $h^\female=h^\male$, and haploid selection only occurs in one sex (e.g., during male meiosis only).
 Table \ref{tab:specialcases} then gives the conditions required for unlinked ($R=1/2$) neo-W invasion when there is some ancestral sex-linkage ($r<1/2$; e.g., the selected locus is on the ancestral sex chromosome and the novel sex-determining locus arises on an autosome).
@@
 
-%Previous research has shown that when the ancestral sex-determining locus is linked to a locus that experiences haploid selection (e.g., meiotic drive), alleles at a new, unlinked sex-determining locus can invade and restore equal sex ratios~\cite{Kozielska:2010vm}.
 We can also compare transitions in genetic sex-determination where sex-ratio bias increases, decreases, or remains equal. 
-For example, if there is meiotic drive in males only ($\alpha^\male_\Delta \neq 0$, $\alpha^\female_\Delta=0$), without gametic competition ($t^\female=t^\male=0$) the zygotic sex ratio is initially biased only when the ancestral sex-determining system is XY (Fig \ref{fig:model_outline}A and Fig \ref{fig:SexRatioBad}A) and not ZW (Fig \ref{fig:SexRatioBad}B).
+For example, if there is meiotic drive in males only ($\alpha^\male_\Delta \neq 0$, $\alpha^\female_\Delta=0$), without gametic competition ($t^\female=t^\male=0$) the zygotic sex ratio is initially biased only when the ancestral sex-determining system is XY (Figs \ref{fig:model_outline}B and \ref{fig:SexRatioBad}A) and not ZW (Figs \ref{fig:model_outline}B and \ref{fig:SexRatioBad}B).
 %If the ancxestral sex-determining system is ZW, the zygotic sex ratio will be 1:1 because diploid sex is determined by the proportion of Z-bearing versus W-bearing eggs and meiosis in females is fair (Fig \ref{fig:Combination_Turnover}D).
@@
 In this figure, selection is ploidally antagonistic with haploid selection favouring the $a$ allele during male meiosis.
-In panel A, male meiotic drive in an ancestral XY system causes a male bias (see Fig \ref{fig:model_outline}B), allowing a neo-W to invade and replace the ancestral sex-determining system (inset shows neo-W frequency rising to fixation among female gametes), which balances the zygotic sex ratio.
-In panel B, male drive in an ancestral ZW system has no effect on the zygotic sex ratio (50:50 at generation 0), yet a neo-Y can invade and replace the ancestral sex-determining system (inset shows neo-Y frequency rising among male gametes, reaching an asymptote where all males bear neo-Y, with meiotic drive sometimes causing more than 50\% of male gametes to bear the neo-Y).
+In panel A, male meiotic drive in an ancestral XY system causes a male bias (see Fig \ref{fig:model_outline}B), allowing a neo-W to invade and replace the ancestral sex-determining system (inset shows the frequency of females carrying a neo-W), which balances the zygotic sex ratio.
+In panel B, male drive in an ancestral ZW system has no effect on the zygotic sex ratio (50:50 at generation 0), yet a neo-Y can invade and replace the ancestral sex-determining system (inset shows the frequency of males carrying a neo-Y).
 %When $R<1/2$, the neo-Y becomes associated with the allele favoured by drive, causing the zygotic sex ratio to become biased, hence the frequency of the neo-Y at pseudo-fixation can be higher than $0.5$ (inset).

### 2018-05-18 LaTeX/response.tex
response letter minor additions

@@
 For example, Ubeda et al. (2015) consider ESD-GSD transitions. 
-Nevertheless, the transitions in Ubeda et al.
+Nevertheless, some steps in Ubeda et al.
 (2015) involve increased linkage with a haploid selected locus, which is precedent for our Conclusions 3A and 3B (which are for GSD-GSD transitions in which linkage with a haploid selected locus is increased).
@@
 Similarly, Kozielska et al.
-(2010) involves a special case of GSD transitions during which sex-linkage goes from perfect to none, which is is an example of our Conclusion 2 (and similar to Conclusion 3C, which are conclusions regarding GSD-GSD transitions in which linkage with a haploid selected locus is decreased).
+(2010) involves a special case of GSD transitions during which sex-linkage goes from perfect to none, which is is an example of our Conclusion 2 and is similar to Conclusion 3C, which are conclusions regarding GSD-GSD transitions in which linkage with a haploid selected locus is decreased.
 This is mentioned on lines (L63-64, L303, and L368). 
 We believe that our new presentation makes the novel and unexpected features of our results much more apparent. 
-For example, despite these precedents, we find the combination of Conclusions 3A, 3B, and 3C to be a striking solution that reconciles the results of Kozielska et al. (2010) and Ubeda et al. (2015). 
+For example, despite these precedents, we find the combination of Conclusions 3A, 3B, and 3C to be a striking reconciliation of the results of Kozielska et al. (2010) and Ubeda et al. (2015). 
 We elaborate further on what makes our results novel and surprising in the responses below.
@@
 For example, step 3 of Ubeda et al involves the spread of an autosomal meiotic drive suppressor favoured by Fisherian sex-ratio selection and Kozielska et al 2010 show that ancestral sex-ratio bias can favour new sex determining systems that balance the sex ratio.
-We found our result, that these forces are exactly equal (with selection weak relative to recombination), such that there is no difference between the propensity for XY-ZW or ZW-XY transitions, to be surprising.
+Furthermore, reviews mentioned on L20-21 suggest that Fisherian sex-ratio selection is a particularly dominant force driving transitions between sex-determining systems
+We found our result, that beneficial associations and sex ratio selection exert exactly equal forces on the spread of neo-sex-chromosomes (with selection weak relative to recombination), such that there is no difference between the propensity for XY-ZW or ZW-XY transitions, to be surprising.
 To clarify our meaning we have rephrased (in Author summary): ``Surprisingly, we find the two forces (selection to equalize the sex-ratio and the benefits of hitch-hiking with driven alleles that distort the sex ratio) will often be equally strong, and thus neither is sufficient to explain the spread of new sex-determining systems in every case."
 We believe that the re-framing of the Introduction/Discussion and the emphasis given to specific Conclusions will help to clarify this point throughout the paper. 
+In particular, this result is now highlighted as `Conclusion 4'.
 }
@@
 To our knowledge, this has only been shown for the special case of male meiotic drive in an ancestral XY system with $r=0$ and $R=1/2$ with a neo-W, which is driven by sex-ratio selection (Kozielska et al 2010).
-We therefore found the large parameter space allowing invasion with $r<R$, sometimes in the absence of sex-ratio selection (or even in the absence of haploid selection), to be very unexpected.
+We therefore found the large parameter space allowing invasion with $r<R$ (Table 3), sometimes in the absence of sex-ratio selection (or even in the absence of haploid selection), to be very unexpected.
 To improve our communication of this result, we have rephrased (in Author Summary): ``We also find that new sex-determining alleles can spread despite being less closely linked to selected loci, driven by initially tight linkage or haploid selection."
-The changes to the presentation of the Introduction, Results, and Discussion should also help to clarify this point further (see Responses 2.1 and 2.2), this result is now also highlighted as `Conclusion 4'.
+The changes to the presentation of the Introduction, Results, and Discussion should also help to clarify this point further (see Responses 2.1 and 2.2). 
 }
@@
 We believe the phrase 'selective differences between the sexes' includes sex-differences in drive (Ubeda et al 2015), which occurs during haploid rather than diploid selection, as indicated in Fig 1B (see also Response 3.1.6).
-As mentioned elsewhere, the enhanced discussion of Ubeda et al. (2015) should help to clarify this point. 
+The enhanced discussion of Ubeda et al. (2015) below this statement should help to clarify this point. 
 Charlesworth and Charlesworth 1978 (Am Nat and Heredity) discuss the role of inbreeding (and particularly inbreeding depression) in transitions from hermaphroditism to dioecy. 
@@
 For clarity, we have moved this description into the Introduction (L49-50). 
-Where we draw a parallel between ESD and hermaphroditism (L468-476), we suggest future theory include inbreeding and cite Charlesworth and Charlesworth (1978). 
+When we draw a parallel between ESD and hermaphroditism (L468-476), we suggest future theory include inbreeding and cite Charlesworth and Charlesworth (1978). 
 }
@@
 \noindent\paragraph{Response}
+\textcolor{red}{edit}
 \textcolor{blue}{
@@
 \noindent\paragraph{Response}
-\textcolor{blue}{In the absence of sex-differences in selection it is true that antagonistic drive is not needed, but \textit{differences} in haploid selection between the sexes are needed (e.g., drive in only one sex, with variations maintained by ploidally-antagonistic selection).
+\textcolor{red}{edit}
+\textcolor{blue}{In the absence of sexually-antagonistic diploid selection it is true that antagonistic drive is not needed, but \textit{differences} in haploid selection between the sexes are needed (e.g., drive in only one sex, with variations maintained by ploidally-antagonistic selection).
 If drive was the same in both sexes, $\alpha^{m}=\alpha^{f}$ (and all other male/female selection terms also equal), we show that the new sex-determining allele would not invade (e.g., equation 2 and 3).
@@
 \noindent\paragraph{Response}
-\textcolor{blue}{While Ubeda et al 2015 did focus on sex ratio biases and haploid selected alleles, the system started with ESD, where there are no associations (see Response 3.1.4).
+\textcolor{red}{edit}
+\textcolor{blue}{While Ubeda et al (2015) did focus on sex ratio biases and haploid selected alleles, the system started with ESD, where there are no associations (see Response 3.1.4).
 Further, the restricted scope of that numerical study prevents us from generalizing beyond its special case (see Response 3.1.4).
@@
 \noindent\paragraph{Response}
+\textcolor{red}{edit}
 \textcolor{blue}{Ubeda et al 2015 was already cited on line 396 of the original submission, where we mentioned that it showed that sex-ratio biases could become more severe during a transition.

### 2018-05-20 LaTeX/response.tex
response letter correct and diff.pdf made

@@
 \noindent  Line numbers (L\#) in authors' comments refer to those in the revised PDF.
-\textcolor{red}{check line numbers}
+%\textcolor{red}{check line numbers}
 \\
@@
 We thank the reviewer for their careful consideration of our manuscript and pithy summary.
-We have incorporated the sentiment of ``a striking evolutionary puzzle'' to help frame our study, L51.
+We have incorporated the sentiment of ``a striking evolutionary puzzle'' to help frame our study, L49-50.
 Below, we itemize further improvements we have made that correspond to more specific reviewer comments.
@@
 However, fertility selection that depends on the mating pair would require a different formulation.
-We now note this in the model section (L120-122):
+We now note this in the model section (L124-127):
 ``Diploid males and females then experience viability and/or individual-based fertility selection, with relative fitnesses $w_{AA}^{\circ}$, $w_{Aa}^{\circ}$, and $w_{aa}^{\circ}$.
@@
 \textcolor{blue}{
-We now refer to the $\chi_{mi}^{(XY)}$ terms as the ``dissociative force" as they break down linkage disequilibrium (L161). 
+We now refer to the $\chi_{mi}^{(XY)}$ terms as the ``dissociative force" as they break down linkage disequilibrium (L173). 
 We have attempted various graphical schemes for representing the three loci in two sexes and the associations that evolve between them in various scenarios. 
 However, apart from Fig 1, we found these too complicated or opaque to be useful. 
-Instead, we have substantially restructured the results section and reduced the technicality (see responses XXXXXX), which should generally help to make the important messages clearer. 
-Specific to this point, in the paragraph 179-199, we itemize three take-home messages from table 2 about the ``haplotypic growth rates'' and ``dissociative forces''. 
+Instead, we have substantially restructured the results section and reduced the technicality (see responses 2.2 and 2.3), which should generally help to make the important messages clearer. 
+Specific to this point, in the paragraph on L182-204, we itemize three take-home messages from table 2 about the ``haplotypic growth rates'' and ``dissociative forces''. 
 }
@@
 \textcolor{blue}{
-This is true, we now mention that the model is deterministic, and hence ignores drift (L130-131). 
-As suggested, when discussing the model limitations at the end of the Discussion we now mention a study on the effect of drift during trans-GSD transitions, which tend to drift in the direction of epistatically-dominant sex-determining loci (L538-541): ``It should be noted, however, that the dynamics of sex-determining alleles with very weak effect will be influenced by genetic drift, which itself has been shown to cause trans-GSD transitions (Veller et al 2017)."}
+This is true, we now mention that the model is deterministic, and hence ignores drift (L131-133). 
+As suggested, when discussing the model limitations at the end of the Discussion we now mention a study on the effect of drift during trans-GSD transitions, which tend to drift in the direction of epistatically-dominant sex-determining loci (L543-546): ``It should be noted, however, that the dynamics of sex-determining alleles with very weak effect will be influenced by genetic drift, which itself has been shown to bias transitions towards epistatically-dominant sex-determining systems when there is no direct selection (Veller et al 2017)."}
 
@@
 \textcolor{blue}{We have made the suggested replacements.
-In addition, we have added a more detailed discussion of how gametic competition relates to the number of mating partners involved, L108-118 (see also response XXXXXX). 
+In addition, we have added a more detailed discussion of how gametic competition relates to the number of mating partners involved, L110-120 (see also response 3.2). 
 Specifically, we note that our model explicitly considers within-ejaculate competition or competition among sperm from many males but not competition among sperm from pairs (or small numbers) of males.
@@
 \textcolor{blue}{In our deterministic model (where the number of binomial trials is infinite), the variance in the fraction male is 0 with ESD, as it is with GSD. 
-We now mention this (L373-375): ``In our deterministic model this means the fraction female in the subpopulation containing $m$ is exactly $k$, even when $m$ is rare (i.e., ESD does not introduce any additional variance in sex determination)."
+We now mention this (L386-388): ``In our deterministic model this means the fraction female in the subpopulation containing $m$ is exactly $k$, even when $m$ is rare (i.e., ESD does not introduce any additional variance in sex determination)."
  }
@@
 
-Scott et al.
-present a 3-locus model for sex-determination (SD) evolution (1 locus has an ancestral SD function; 1 has a derived SD function; 1 locus affects selection in the haploid or diploid phase of the life cycle).
+Scott et al.\ present a 3-locus model for sex-determination (SD) evolution (1 locus has an ancestral SD function; 1 has a derived SD function; 1 locus affects selection in the haploid or diploid phase of the life cycle).
 Their results converge on previously-identified conditions for the spread of new SD alleles, while also broadening the range of scenarios and conditions that can favour transitions between SD systems.
@@
 We have simplified the introduction according to the suggested format.
-In addition, when discussing holes in current theory we have expanded our discussion of previous studies that include haploid selection, as suggested by reviewer 3.
-To accommodate these changes, we have moved the discussion of empirical evidence for haploid selection to the discussion (L441-454). The introduction is now structured as follows:
+In addition, when discussing holes in current theory we have expanded our discussion of previous studies that include haploid selection, as suggested by reviewer 3 (see response 3.1).
+To accommodate these changes, we have moved the discussion of empirical evidence for haploid selection to the discussion (L454-468). The introduction is now structured as follows:
 \begin{enumerate}
-\item[1.]{The first paragraph discusses how common transitions are, and now mentions that recent empirical evidence is making this increasingly apparent. (L2-20)}
+\item[1.]{The first paragraph discusses how common transitions are, and now mentions that recent empirical evidence is making this increasingly apparent. (L2-19)}
 \item[2-3.]{The second and third paragraphs lay out the two major mechanisms thought to drive transitions in sex-determination, (1) selection to stabilize the sex ratio, and (2) linkage associations between alleles favoured in one sex and the alleles that determine that sex.
-(L21-29, L30-38) }
-\item[4.]{Connecting to point (2), we then found it useful to introduce one novel aspect of our model -- we consider a selected locus that is very tightly linked to the ancestral sex-determining locus and find the surprising result that transitions in which linkage is reduced can be favoured.
-(L39-48)}
-\item[5.]{Next, we introduce the most significant novel model feature, haploid selection, which we present as an evolutionary problem in light of (1) and (2). (L49-56) }
+(L2-27, L28-36) }
+\item[4.]{Connecting to point 2 (hitchhiking), we then found it useful to introduce one novel aspect of our model -- we consider a selected locus that is very tightly linked to the ancestral sex-determining locus -- and find the surprising result that transitions in which linkage is reduced can be favoured.
+(L37-47)}
+\item[5.]{Next, we introduce the most significant novel model feature, haploid selection, which we present as an evolutionary problem in light of points 1 and 2 (sex ratios and hitchhiking).
+(L48-55) }
 \item[6.]{The sixth paragraph then describes previous studies that have included haploid selection (see also reviewer 3 recommendations).
-These studies suggest that (1) and (2) are both very important with haploid selection and point to the major limitations in solving the evolutionary puzzle.
-(L57-69)}
+These studies suggest that points 1 and 2 are both very important with haploid selection and point to the major limitations in solving the evolutionary puzzle.
+(L56-71)}
 \item[7.]{Finally, we lay out our main results in this context.
@@
 We particularly highlight the unexpected conclusions that our model allows us to reach.
-(L70-83)}
+(L72-87)}
 \end{enumerate}
@@
 \textcolor{blue}{
-As discussed further below (response XXXXX), we have highlighted conclusions in the results section as suggested. 
-To further reduce the technicality of our presentation, we have also revised the results section. 
+As discussed further below, we have highlighted conclusions in the results section as suggested (see response 2.3). 
+To further reduce the technicality of our presentation, we have made additional revisions in the results section. 
 In particular, we have restructured the presentation of the subsections ``Generic invasion by a neo-Y or neo-W'' and ``Tight linkage with the ancestral sex-determining locus''. 
-In the ``Generic invasion by a neo-Y or neo-W" section, we have moved some details to the supplementary material (particularly, proofs regarding the leading eigenvalue, formally LXXX-XXX). 
+In the ``Generic invasion by a neo-Y or neo-W" section, we have moved some details to the supplementary material (particularly, proofs regarding the leading eigenvalue, formally L135-145). 
 Now, we focus on explaining the intuition behind our technical results.  
-For example, we first discuss the `haplotypic growth rates' and 'dissociative forces' (L158-170 and `interpreting this condition...', L173).
-We then lay out four specific conclusions (L179-199). 
-In the ``Tight linkage'' section, we now first describe specific cases why neo-W's can have improved female fitness, Conclusion 1, L235-259, with more focus on non-technical interpretation (e.g., L237-240).
-Then we discuss the fact that looser sex-linkage can evolve (L260-275, Conclusion 2). 
+For example, we first discuss the `haplotypic growth rates' and 'dissociative forces' (L161-173) and discuss when they allow invasion (L174-181).
+We then lay out four specific conclusions (L182-204). 
+In the ``Tight linkage'' section, we now first describe specific cases why neo-W's can have improved female fitness, Conclusion 1, L230-281, with more focus on non-technical interpretation (e.g., L241-247).
+This includes the case where looser sex-linkage can evolve (L265-281, Conclusion 2). 
 This re-organisation allows us to break down the logic behind Conclusion 2 more clearly. 
@@
 (L326-328)
-\item[(3B)] New sex-determining alleles (causing trans-GSD transitions, XY $\leftrightarrow$ ZW) are favoured if they are linked with an ancestrally-autosomal locus that experiences (haploid and/or diploid) selection ($R<1/2$, $r=1/2$).
+\item[(3B)] New sex-determining alleles (causing trans-GSD transitions, XY $\leftrightarrow$ ZW) are favoured if they are linked with an ancestrally-autosomal locus ($R<1/2$, $r=1/2$) that experiences (haploid and/or diploid) selection.
 (L333-335)
@@
 \item[(4)] When selection is weak relative to recombination, the presence of haploid selection equally favors the spread of new sex determination systems that reduce sex-ratio bias (benefiting from Fisherian sex ratio selection) or generate a sex-ratio bias (benefiting from associations with selected alleles).
-(L350-353)
-\item[(5)] Transitions from genetic to environmental sex-determination are not straightforwardly predicted by selection to balance the zygotic sex ratio when haploid selection is present.  (L411-413)
+(L363-366)
+\item[(5)] Transitions from genetic to environmental sex-determination are not straightforwardly predicted by selection to balance the zygotic sex ratio when haploid selection is present.  (L424-426)
 %\vspace{0.25cm}\\
 \end{enumerate}
-These conclusions are also more clearly laid out in the introduction (L48-49, L74-85) and are referenced directly in summarisations in the discussion (L424-432, L543-554). 
+These conclusions are also more clearly laid out in the introduction (L45-47, L72-87) and are referenced directly in summarisations in the discussion (L428-436, L548-559). 
 }
 
-\textcolor{blue}{Of these conclusions, (3A), (3B), and (3C) have some precendent.
+\textcolor{blue}{Of these conclusions, (3A), (3B), and (3C) have some precedent. 
 (3A) and (3B) are similar to studies by van Doorn and Kirkpatrick (2007,2010) that do not include haploid selection.
-These comparisons are made immediately above the conclusions (L316-330) and mentioned elsewhere (L55, L77, L489).
-Including haploid selection, Ubeda et al. (2015) also involved examples similar to (3A) and (3B), except that the starting state was ESD. 
-Kozielska et al. (2010) also had numerical examples that involved trans-GSD transitions with ($R>r$), as stated in (3C), but focussed only on sex ratio selection. 
-We discuss how our results compare to these studies in the introduction (L58-75), discussion (L433-447) and results (L193, L363-369).
-Nevertheless, we have highlighted these conclusions, partly for clarity of communication and partly because our results are more general. 
-That is, as stated by the reviewer, these results ``converge on previously-identified conditions for the spread of new SD alleles, while also broadening the range of scenarios and conditions that can favour transitions between SD systems''}
+These comparisons are made immediately above (L322-325) and below (L336-338) the conclusions and are mentioned elsewhere (L53, L77, L494).
+Including haploid selection, Ubeda et al.\ (2015) had numerical examples similar to (3A) and (3B), except that the starting state was ESD. 
+Kozielska et al.\ (2010) had examples that involved trans-GSD transitions with ($R>r$), as stated in (3C), but focussed only on sex ratio selection. 
+We clarify how our results compare to these two studies in the introduction (L56-71), results (L198, L367-343), and discussion (L437-451).
+In particular, while these previous studies provide some precedent for conclusions (3A)-(3C), our results are more general and reconcile their results (see conclusion (4) and L367-373). 
+As stated by the reviewer, our results ``converge on previously-identified conditions for the spread of new SD alleles, while also broadening the range of scenarios and conditions that can favour transitions between SD systems''}
 %As (1A), (1B), and (2) have some antecedents in the literature, we discuss these immediately below each conclusion. 
@@
 %These are all new results, although (1A) was shown for the special case of $r=0$, $R=1/2$, and ploidally-antagonistic selection in Kozielska et al 2010, which we now mention immediately below (1A).
-}
+%}
 
@@
 \textcolor{blue}{We have replaced ``Thus, if the population sex ratio is biased towards one sex, the average per-individual contribution of genetic material to the next generation from the opposite sex is greater" with ``Thus, if the sex ratio is biased, an individual of the rarer sex will, on average, contribute more genetic material to the next generation".
-(L26-28)}
+(L25-26)}
 
@@
 In particular, paragraph 5 presents the role of haploid selection as an evolutionary puzzle and paragraph 6 explains the limitations of previous attempts to solve the puzzle.
-(L49-69)}
+(L48-71)}
 
@@
 Thank you for this suggestion, ``sex-limited'' is a more efficient way to communicate that haploid selection often only occurs in gametes produced by one sex. 
-We now use ``sex-limited'' throughout, with two exceptions.
-L72 and L126, where we are referring to the fact that we model haploid selection in either/both sexes (focussing on sex-limited cases in our examples).
-This section was re-written but the section that roughly corresponds to the highlighted sentence now reads: ``...haploid selection is typically sex-limited in that it usually occurs among gametes produced by one sex only." (L51-52)
+We now use ``sex-limited'' throughout, with one exception: on L126 we use ``sex-specific meiotic drive", where we are referring to the fact that we model haploid selection in either/both sexes (focusing on sex-limited cases in our examples).
+%This section was re-written but the section that roughly corresponds to the highlighted sentence now reads: ``...haploid selection is typically sex-limited in that it usually occurs among gametes produced by one sex only." (L51-52)
 }
@@
 \textcolor{blue}{
-As suggested above, we have re-written to focus on our most novel findings, which are now laid our more specifically, e.g., L71-85 (see also Responses 2.1 and 2.2). 
+As suggested above (see responses 2.1 and 2.2), we have re-written to focus on our most novel findings, which are now laid our more specifically, e.g., L72-87 . 
 }
@@
 \textcolor{blue}{We have flipped the statement to talk about male biased sex-ratios instead, and mention that this is possible at equilibrium in an XY system under the more familiar scenario of meiotic drive in males.
-(L183-187)}
+(L185-189)}
 
@@
 \noindent\paragraph{Response}
-\textcolor{blue}{We have replaced this instance of $\epsilon$ with the more familiar $s<<r$ style assumption (L210).
-When we introduce $\epsilon$ in the weak selection section we now verbally explain that it is just a number that is much less than one (L295-296).}
+\textcolor{blue}{We have replaced this instance of $\epsilon$ with the more familiar $s<<r$ style assumption (L215-216). 
+When we introduce $\epsilon$ in the weak selection section we now verbally explain that it is just a number that is much less than one (L310-312).}
 
@@
 \noindent\paragraph{Response}
-\textcolor{blue}{The blue and green curves should not really show as they are not expected to increase from a very small initial frequency.
+\textcolor{blue}{This is now Figure 3, panel C.
+Here the blue and green curves should not really show as they are not expected to increase from a very small initial frequency.
 We have kept the original scale but now state in the legend that the blue and green loci do not invade.}
@@
 We have performed an extensive re-arrangement to improve the clarity of our writing, especially regarding the main results (see Responses 2.1-2.3). 
-As suggested by the reviewer (here and below), we also now give more prominence to the related results by Kozielska et al 2010 and Ubeda et al 2015 (e.g., L56-71, L198, L367-373, L440-446). 
-In particular, we introduce these studies on Lines 56-71 and more precisely indicate which of our model features and results are new and unexpected in light of these previous results.
+As suggested by the reviewer (here and below), we also now give more prominence to the related results by Kozielska et al.\ 2010 and Ubeda et al.\ 2015 (e.g., L56-71, L198, L367-373, L440-446). 
+In particular, we introduce these studies (L56-71) and more precisely indicate which of our model features and results are new and unexpected in light of these previous results.
 }
@@
 While related, these two studies considered particular cases that we do not consider at length. 
-For example, Ubeda et al. (2015) consider ESD-GSD transitions. 
-Nevertheless, some steps in Ubeda et al.
-(2015) involve increased linkage with a haploid selected locus, which is precedent for our Conclusions 3A and 3B (which are for GSD-GSD transitions in which linkage with a haploid selected locus is increased).
-We now mention this in the Introduction (L59-61), Results (L369-373), and Discussion (L432).  
-Similarly, Kozielska et al.
-(2010) involves a special case of GSD transitions during which sex-linkage goes from perfect to none, which is is an example of our Conclusion 2 and is similar to Conclusion 3C, which are conclusions regarding GSD-GSD transitions in which linkage with a haploid selected locus is decreased.
-This is mentioned on lines (L63-64, L303, and L368). 
+For example, Ubeda et al.\ (2015) consider ESD-GSD transitions. 
+Nevertheless, some steps in Ubeda et al.\ (2015) involve increased linkage with a haploid selected locus, which is precedent for our Conclusions 3A and 3B (which are for GSD-GSD transitions in which linkage with a haploid selected locus is increased).
+We now mention this in the introduction (L58-60) and results (L369-371). %, and Discussion (L432).  
+Similarly, Kozielska et al.\ (2010) involves a special case of GSD transitions during which sex-linkage goes from perfect to none, which is an example of our Conclusion 2 and is similar to Conclusion 3C, which are conclusions regarding GSD-GSD transitions in which linkage with a haploid selected locus is decreased.
+This is mentioned on in numerous places in the text (L62-67, L301-304, and L367-368). 
 We believe that our new presentation makes the novel and unexpected features of our results much more apparent. 
-For example, despite these precedents, we find the combination of Conclusions 3A, 3B, and 3C to be a striking reconciliation of the results of Kozielska et al. (2010) and Ubeda et al. (2015). 
+For example, despite these precedents, we find the combination of Conclusions 3A, 3B, and 3C to be a striking reconciliation of the results of Kozielska et al.\ (2010) and Ubeda et al.\ (2015), see Conclusion 4 as well.
 We elaborate further on what makes our results novel and surprising in the responses below.
@@
 $\lambda_{Y'}^{ZW}$ with $r<1/2$, $R=1/2$, and male meiotic drive).
-As mentioned by the reviewer, Step 2 in Ubeda et al 2015 shows that associations with a haploid selected locus can favour a new sex-determining allele despite causing biased sex ratios. 
+As mentioned by the reviewer, Step 2 in Ubeda et al.\ 2015 shows that associations with a haploid selected locus can favour a new sex-determining allele despite causing biased sex ratios. 
 Nevertheless, it was difficult for us to intuit whether the presence/absence of ancestral sex-ratio bias would have a negligible or overwhelming effect on the evolution of new sex-determining alleles.
@@
 There are reasons to suspect that ancestral-sex-ratio biases would strongly influence the spread of new sex-determining systems.
-For example, step 3 of Ubeda et al involves the spread of an autosomal meiotic drive suppressor favoured by Fisherian sex-ratio selection and Kozielska et al 2010 show that ancestral sex-ratio bias can favour new sex determining systems that balance the sex ratio.
-Furthermore, reviews mentioned on L20-21 suggest that Fisherian sex-ratio selection is a particularly dominant force driving transitions between sex-determining systems
+For example, step 3 of Ubeda et al.\ involves the spread of an autosomal meiotic drive suppressor favoured by Fisherian sex-ratio selection and Kozielska et al.\ 2010 show that ancestral sex-ratio bias can favour new sex determining systems that balance the sex ratio.
+Furthermore, reviews mentioned on L21 suggest that Fisherian sex-ratio selection is a particularly dominant force driving transitions between sex-determining systems.
 We found our result, that beneficial associations and sex ratio selection exert exactly equal forces on the spread of neo-sex-chromosomes (with selection weak relative to recombination), such that there is no difference between the propensity for XY-ZW or ZW-XY transitions, to be surprising.
-To clarify our meaning we have rephrased (in Author summary): ``Surprisingly, we find the two forces (selection to equalize the sex-ratio and the benefits of hitch-hiking with driven alleles that distort the sex ratio) will often be equally strong, and thus neither is sufficient to explain the spread of new sex-determining systems in every case."
-We believe that the re-framing of the Introduction/Discussion and the emphasis given to specific Conclusions will help to clarify this point throughout the paper. 
+To clarify our meaning we have rephrased (in Author summary): ``Surprisingly, we find the two forces (selection to equalize the sex-ratio and the benefits of hitchhiking alongside driven alleles that distort the sex ratio) will often be equally strong, and thus neither is sufficient to explain the spread of new sex-determining systems in every case."
+We believe that the re-framing of the Introduction/Results and the emphasis given to specific Conclusions will help to clarify this point throughout the paper (see Responses 2.1-2.3). 
 In particular, this result is now highlighted as `Conclusion 4'.
@@
 \textcolor{blue}{
-The Ubeda et al.
-(2015) results do indeed show that differential selection between male and female diploids is not required for new sex-determining alleles to spread; they show that a new genetic sex-determining allele can spread from ancestral ESD when it is linked to a locus that experiences sex-specific meiotic drive.
+The Ubeda et al.\ (2015) results do indeed show that differential selection between male and female diploids is not required for new sex-determining alleles to spread; they show that a new genetic sex-determining allele can spread from ancestral ESD when it is linked to a locus that experiences sex-specific meiotic drive.
 In this sentence, we were attempting to stress that new sex determining alleles can spread when they are \textit{less closely linked or even completely unlinked} to loci under differential male/female haploid and/or diploid selection.
-To our knowledge, this has only been shown for the special case of male meiotic drive in an ancestral XY system with $r=0$ and $R=1/2$ with a neo-W, which is driven by sex-ratio selection (Kozielska et al 2010).
+To our knowledge, this has only been shown for the special case of male meiotic drive in an ancestral XY system with $r=0$ and $R=1/2$ with a neo-W, which is driven by sex-ratio selection (Kozielska et al.\ 2010).
 We therefore found the large parameter space allowing invasion with $r<R$ (Table 3), sometimes in the absence of sex-ratio selection (or even in the absence of haploid selection), to be very unexpected.
-To improve our communication of this result, we have rephrased (in Author Summary): ``We also find that new sex-determining alleles can spread despite being less closely linked to selected loci, driven by initially tight linkage or haploid selection."
-The changes to the presentation of the Introduction, Results, and Discussion should also help to clarify this point further (see Responses 2.1 and 2.2). 
+To improve our communication of this result, we have rephrased (in Author Summary): ``We also find that new sex-determining alleles can spread despite being less closely linked to selected loci as long as initial linkage is tight or haploid selection is present."
+The changes to the presentation of the Introduction, Results, and Discussion should also help to clarify this point further (see Responses 2.1-2.3). 
 }
@@
 Here, sexually-antagonistic selection was referred to as an example of ``selective differences between the sexes". 
-We believe the phrase 'selective differences between the sexes' includes sex-differences in drive (Ubeda et al 2015), which occurs during haploid rather than diploid selection, as indicated in Fig 1B (see also Response 3.1.6).
-The enhanced discussion of Ubeda et al. (2015) below this statement should help to clarify this point. 
+We believe the phrase `selective differences between the sexes' includes sex-differences in drive (Ubeda et al 2015), which occurs during haploid rather than diploid selection, as indicated in Fig 1B (see also Response 3.1.6).
+The enhanced discussion of Ubeda et al.\ (2015) immediately below this statement should help to clarify this point (L58-62).
+\\ 
 Charlesworth and Charlesworth 1978 (Am Nat and Heredity) discuss the role of inbreeding (and particularly inbreeding depression) in transitions from hermaphroditism to dioecy. 
 As described in the model section and lines 468-472 of the original submission, we have only considered GSD-GSD transitions and GSD-ESD transitions.
-For clarity, we have moved this description into the Introduction (L49-50). 
-When we draw a parallel between ESD and hermaphroditism (L468-476), we suggest future theory include inbreeding and cite Charlesworth and Charlesworth (1978). 
+For clarity, we have moved this description into the Introduction (L48-49). 
+When we draw a parallel between ESD and hermaphroditism (L483-491), we suggest future theory include inbreeding and cite Charlesworth and Charlesworth (1978). 
 }
@@
 \noindent\paragraph{Response}
-\textcolor{red}{edit}
+%\textcolor{red}{edit}
 \textcolor{blue}{
-As we now make clear, we do not look at the same situation as Ubeda et al 2015 and our contribution is not just to add sex-specific viability. 
+As we now make clear (see response 3.1), we do not look at the same situation as Ubeda et al 2015 and our contribution is not just to add sex-specific viability. 
 In particular, Ubeda et al start from ESD. 
@@
 These lead to some of our most surprising results (e.g., haploid selection favours trans-GSD transitions for a wider variety of genomic locations than diploid selection alone; ESD does not invade despite initial sex-ratio bias).
-Further, our model and intuition-giving analytical solutions explore a much wider range of scenarios than the numerical results of Ubeda et al, allowing, for example, sex-specific selection (e.g., sex-antagonism) and various genomic arrangements (any order/linkage of the three loci).
+Further, our model and intuition-giving analytical solutions explore a much wider range of scenarios than the numerical results of Ubeda et al., allowing, for example, sex-specific selection (e.g., sex-antagonism) and various genomic arrangements (any order/linkage of the three loci).
 Our model is thus much more general and clarifies just when one should expect to see the numerical results of Ubeda et al.
-We have rephrased to make this clear (after discussing Ubeda et al 2015 in the Introduction, see Response 2.1; L70-74): ``Here, we analytically find the conditions under which new GSD or ESD systems spread in ancestral GSD systems with generic linkage between the loci involved and generic sex-specific haploid and diploid selection.
-Doing so, we reconcile the results of Kozielska et al.\ (2010) and Ubeda et al.\ (2015) by showing when new GSD systems that increase \textit{or} decrease linkage with loci under haploid selection spread."
+We have rephrased to make this clear (after discussing Ubeda et al.\ 2015 in the Introduction, see Response 2.1; L72-76): ``Here, we analytically find the conditions under which new GSD or ESD systems spread in ancestral GSD systems with any degree of linkage between the loci involved and arbitrary forms of haploid and diploid selection.
+Doing so, we reconcile and generalize the results of Kozielska et al.\ (2010) and Ubeda et al.\ (2015) by deriving conditions for the spread of new GSD systems that alter linkage with haploid selected loci."
 }
@@
 However, as noted by the reviewer here, the dynamics of selection during gametic selection cannot be captured by a diploid selection coefficient, which is why we specifically model selection upon haploid genotypes.
-In our new manuscript, a roughly corresponding statement now reads ``On one hand, haploid selection is typically sex-limited in that it usually occurs among gametes produced by one sex only [38-41].''.
+In our revision, a roughly corresponding statement now reads (L50-51) ``On one hand, haploid selection is typically sex-limited in that it usually occurs among gametes produced by one sex only [38-41].''.
 We have also expanded our explanation of the mating system and the way we model haploid selection (see Response 3.2 below).
@@
 \noindent\paragraph{Response}
-\textcolor{red}{edit}
+%\textcolor{red}{edit}
 \textcolor{blue}{In the absence of sexually-antagonistic diploid selection it is true that antagonistic drive is not needed, but \textit{differences} in haploid selection between the sexes are needed (e.g., drive in only one sex, with variations maintained by ploidally-antagonistic selection).
 If drive was the same in both sexes, $\alpha^{m}=\alpha^{f}$ (and all other male/female selection terms also equal), we show that the new sex-determining allele would not invade (e.g., equation 2 and 3).
-In this sense haploid selection is similar to sex-specific diploid selection, and together haploid and diploid selection determine the differences in male vs.\ female fitness, which can drive sex-determination transitions (see Response 3.2.4).
-This sentence meant to introduce the `sex-specific' aspect of haploid selection in the way Ubeda et al 2015 considers it; associations with alleles favoured in one sex (or the gametes produced by that sex) should favour a new sex-determining allele.
-We have rephrased to make this clear (L52-54): ``Therefore, one might expect new sex-determining systems to benefit from close linkage with haploid selected loci, as found for sex-differences in diploid selection."
-We now follow this sentence up with a paragraph that clarifies its meaning by comparing with the results of Kozielska et al 2010 and Ubeda et al 2015 (see Response 2.1).}
+In this sense haploid selection is similar to sex-specific diploid selection, and together haploid and diploid selection determine the differences in male vs.\ female fitness, which can drive sex-determination transitions (see Response 3.1.4).\\
+This sentence meant to introduce the `sex-specific' aspect of haploid selection in the way Ubeda et al.\ 2015 considers it; associations with alleles favoured in one sex (or the gametes produced by that sex) should favour a new sex-determining allele.
+We have rephrased to make this clear (L51-53): ``Therefore, one might expect new sex-determining systems to benefit from close linkage with haploid selected loci, as found for loci that experience diploid-sex-differences in selection [35-37]."
+We now follow this sentence up with a paragraph that clarifies its meaning by comparing with the results of Kozielska et al.\ 2010 and Ubeda et al.\ 2015 (L56-71; see also Response 2.1).}
 
@@
 \noindent\paragraph{Response}
-\textcolor{red}{edit}
-\textcolor{blue}{While Ubeda et al (2015) did focus on sex ratio biases and haploid selected alleles, the system started with ESD, where there are no associations (see Response 3.1.4).
+%\textcolor{red}{edit}
+\textcolor{blue}{While Ubeda et al.\ (2015) did focus on sex ratio biases and haploid selected alleles, the system started with ESD, where there are no associations (see Response 3.1.4).
 Further, the restricted scope of that numerical study prevents us from generalizing beyond its special case (see Response 3.1.4).
-We now present a refurbished argument for why it is difficult to intuit the implications of haploid selection while summarizing the results of Ubeda et al and Kozielska et al 2010 in the Introduction (see Response 2.1).
+We now present a refurbished argument for why it is difficult to intuit the implications of haploid selection while summarizing the results of Ubeda et al.\ and Kozielska et al.\ 2010 in the Introduction (see Response 2.1).
 }
@@
 \noindent\subsubsection{}
-I will not provide further examples, but it is surprising thatI the work of Ubeda et al 2015, which is closely related to the one presented here, is cited in page 12 supporting a statement only tangential to the work of Ubeda et al 2015.
+I will not provide further examples, but it is surprising that the work of Ubeda et al 2015, which is closely related to the one presented here, is cited in page 12 supporting a statement only tangential to the work of Ubeda et al 2015.
 
 \noindent\paragraph{Response}
-\textcolor{red}{edit}
-\textcolor{blue}{Ubeda et al 2015 was already cited on line 396 of the original submission, where we mentioned that it showed that sex-ratio biases could become more severe during a transition.
-Nevertheless, we now discuss Ubeda et al 2015 in the Introduction, Results, and Discussion (see Responses above).}
+%\textcolor{red}{edit}
+\textcolor{blue}{
+Ubeda et al 2015 was in fact cited in the main text (line 396) of the original submission, where we mentioned that it showed that sex-ratio biases could become more severe during a transition.
+However, we thank the reviewer for emphasizing the similarities between that study and our own.
+We now discuss Ubeda et al.\ 2015 in the Introduction, Results, and Discussion (see Responses above), which we believe clarifies and strengthens our arguments while giving credit to this earlier work.}
 
@@
 We have chosen not to adjust our models to include a single parameter that measures transmission distortion. 
-Given our definition of meiotic drive and gametic competition (L106-116), the two processes are different.
+Given our definition of meiotic drive and gametic competition (L110-120), the two processes are different.
 In particular, meiotic drive can only have an effect in heterozygotes.
@@
 Thus, for example, allele frequency changes can occur by gametic competition even if all individuals were homozygous (as long as there is a polymorphism).
-We have extended our description of how we use the terms `gametic competition' and `meiotic drive' and how they are modelled in the model section (L106-116), which helps to clarify why they are different and under what circumstances each applies.
+We have extended our description of how we use the terms `gametic competition' and `meiotic drive' and how they are modelled in the model section (L110-120), which helps to clarify why they are different and under what circumstances each applies.
 Unfortunately, beyond defining our terms, it was not straightforward to resolve the different usages of the terms by different communities.

### 2018-05-20 LaTeX/main_revised.tex
response letter correct and diff.pdf made

@@
 Surprisingly, we find the two forces (selection to equalize the sex ratio and the benefits of hitchhiking alongside driven alleles that distort the sex ratio) will often be equally strong, and thus neither is sufficient to explain the spread of new sex-determining systems in every case.
-We also find that new sex-determining alleles can spread despite being less closely linked to selected loci as long as initial linkage is tight or haploid selection is present.. 
+We also find that new sex-determining alleles can spread despite being less closely linked to selected loci as long as initial linkage is tight or haploid selection is present.
 Our models therefore predict that loci in previously unexpected genomic locations and/or experiencing various types of selection (including haploid selection) can now be implicated as drivers of transitions between sex-determining systems.
@@
 %The new sex-determining allele, $m$, will spread in an XY system if $\lambda_{m}^{(XY)}>1$. 
-Eq \eqref{eq:lambda_neoY} demonstrates that, under weak selection, a neo-Y allele will invade an XY system ($\lambda_{Y'}^{(XY)}>1$) if and only if it is more closely linked to the selected locus than the ancestral sex-determining locus (i.e., if $R<r$).%; note that $\bar{p}(1-\bar{p})S_{A}^2$ is strictly positive as long as $\mathbf{A}$ is polymorphic).
+Eq \eqref{eq:lambda_neoY} demonstrates that, under weak selection, a neo-Y allele will invade an XY system ($\lambda_{Y'}^{(XY)}>1$) if and only if it is more closely linked to the selected locus than the ancestral sex-determining locus (i.e., if $R<r$).
+%; note that $\bar{p}(1-\bar{p})S_{A}^2$ is strictly positive as long as $\mathbf{A}$ is polymorphic).
 This echoes our results above where a neo-Y could never invade if $r\approx0$. 
@@
 \noindent\textit{Conclusion 3B:}\
-\textbf{New sex-determining alleles (causing trans-GSD transitions, XY $\leftrightarrow$ ZW) are favoured if they are linked with an ancestrally-autosomal locus that experiences (haploid and/or diploid) selection ($R<1/2$, $r=1/2$).}
+\textbf{New sex-determining alleles (causing trans-GSD transitions, XY $\leftrightarrow$ ZW) are favoured if they are linked with an ancestrally-autosomal locus ($R<1/2$, $r=1/2$) that experiences (haploid and/or diploid) selection.}
 \vspace{0.5cm}
@@
 These results echo those for large-effect neo-Y/neo-W alleles~\cite{vanDoorn:2007eu,vanDoorn:2010hu}.
-It should be noted, however, that the dynamics of sex-determining alleles with very weak effect will be influenced by genetic drift, which itself has been shown to bias transitions towards epistatically-dominant sex-determining systems when there is no selection \cite{Veller2017}.
+It should be noted, however, that the dynamics of sex-determining alleles with very weak effect will be influenced by genetic drift, which itself has been shown to bias transitions towards epistatically-dominant sex-determining systems when there is no direct selection \cite{Veller2017}.
 

### 2018-05-21 LaTeX/response.tex
updated response letter and changed Conclusions 3 again

@@
 \bibliographystyle{plos2015}
-\usepackage{color}
+\usepackage[dvipsnames]{xcolor}
+
+\title{Response to Reviewers}
+\date{}
+
+\date{\vspace{-5ex}}
 
@@
 
-\noindent\textbf{Color code}:\\
-reviewers' words\\
-%\textcolor{red}{to do/thoughts/questions between coauthors (temporary)}\\
-\textcolor{blue}{authors' response}
-\\
+\maketitle
 
-\noindent  Line numbers (L\#) in authors' comments refer to those in the revised PDF.
-%\textcolor{red}{check line numbers}
-\\
+\noindent
+Here, we provide `point-by-point' responses to reviewer suggestions, highlighting changes made to the manuscript.
+Line numbers (L\#) in authors' comments refer to those in the revised PDF unless otherwise specified.
+The reviewer comments have been provided in full (black text) with author responses interspersed (\textcolor{blue}{blue text})
 
-\noindent See diff.pdf for all differences between the original submission and the revised version.
+As recommended, we also provide a file of differences between the original submission and the revised version (diff.pdf), which was generated using LaTeXdiff.
 
 \section{Reviewer 1}
+
+\noindent\subsection{}
 
@@
 
+\noindent\paragraph{Response}
 \textcolor{blue}{
@@
 
-\noindent\subsection{}
+\noindent\subsubsection{}
+
 The selected locus allows for three modes of selection: gametic selection (weighting the frequencies of gamete genotypes), the usual diploid viability selection, and meiotic drive (where heterozygotes may produce gametes that deviate from 50:50 proportions).
@@
 
-\noindent\subsection{}
+\noindent\subsubsection{}
 The ``haplotypic growth rate" plays a really essential role in providing intuition about the results.
@@
 However, apart from Fig 1, we found these too complicated or opaque to be useful. 
-Instead, we have substantially restructured the results section and reduced the technicality (see responses 2.2 and 2.3), which should generally help to make the important messages clearer. 
+Instead, we have substantially restructured the results section and reduced the technicality (see also Responses 2.3 and 2.4), which should generally help to make the important messages clearer. 
 Specific to this point, in the paragraph on L182-204, we itemize three take-home messages from table 2 about the ``haplotypic growth rates'' and ``dissociative forces''. 
@@
 
-\noindent\subsection{}
+\noindent\subsubsection{}
 It needs to be stated somewhere that the models are entirely deterministic, implying that the authors assume that the selective forces always exceed the force of random drift.
@@
 This is true, we now mention that the model is deterministic, and hence ignores drift (L131-133). 
-As suggested, when discussing the model limitations at the end of the Discussion we now mention a study on the effect of drift during trans-GSD transitions, which tend to drift in the direction of epistatically-dominant sex-determining loci (L543-546): ``It should be noted, however, that the dynamics of sex-determining alleles with very weak effect will be influenced by genetic drift, which itself has been shown to bias transitions towards epistatically-dominant sex-determining systems when there is no direct selection (Veller et al 2017)."}
+As suggested, when discussing the model limitations at the end of the Discussion we now mention a study on the effect of drift during trans-GSD transitions, which tend to drift in the direction of epistatically-dominant sex-determining loci (L543-546): ``It should be noted, however, that the dynamics of sex-determining alleles with very weak effect will be influenced by genetic drift, which itself has been shown to bias transitions towards epistatically-dominant sex-determining systems when there is no direct selection (Veller et al.\ (2017)."}
 
-\noindent\subsection{}
+\noindent\subsubsection{}
 A glitch appears in the section ``Loose linkage with the ancestral sex-determining region" on line 270, where the text reads, ``To leading order in selection, the leading eigenvalues are..."
@@
 
-\noindent\subsection{}
+\noindent\subsubsection{}
 Gametic selection among sperm is a bit different from sperm competition, since the latter involves pair-wise (or multi-way) bouts, whereas gametic selection assigns constant fitnesses to each haplotype.
@@
 
-\noindent\subsection{}
+\noindent\subsubsection{}
 I am not certain of this, but it seems that a potentially important difference between ESD and GSD has to do with the variance in proportion male?
@@
 
-\noindent\subsection{}
+\noindent\subsubsection{}
 Full sharing of the Mathematica file is to be commended.
@@
 \section{Reviewer 2}
+
+\noindent\subsection{}
 
@@
 \textcolor{blue}{
-As discussed further below, we have highlighted conclusions in the results section as suggested (see response 2.3). 
+As discussed further below, we have highlighted conclusions in the results section as suggested (see Response 2.4). 
 To further reduce the technicality of our presentation, we have made additional revisions in the results section. 
@@
 
-\textcolor{blue}{Of these conclusions, (3A), (3B), and (3C) have some precedent. 
+\textcolor{blue}{Of these conclusions, (2), (3A), and (3B) have some precedent. 
 (3A) and (3B) are similar to studies by van Doorn and Kirkpatrick (2007,2010) that do not include haploid selection.
@@
 Including haploid selection, Ubeda et al.\ (2015) had numerical examples similar to (3A) and (3B), except that the starting state was ESD. 
-Kozielska et al.\ (2010) had examples that involved trans-GSD transitions with ($R>r$), as stated in (3C), but focussed only on sex ratio selection. 
-We clarify how our results compare to these two studies in the introduction (L56-71), results (L198, L367-343), and discussion (L437-451).
-In particular, while these previous studies provide some precedent for conclusions (3A)-(3C), our results are more general and reconcile their results (see conclusion (4) and L367-373). 
+Kozielska et al.\ (2010) had examples that involved trans-GSD transitions with haploid selection and $r=0$, $R=1/2$, a sub-case of (2) (and somewhat similar to (3C)), but focussed only on sex ratio selection.
+We clarify how our results compare to these two studies in the introduction (L56-71), results (L198, L301-304, L367-343), and discussion (L437-451).
+In particular, while these previous studies provide some precedent for conclusions (2), (3A), and (3B), our results are more general and reconcile their results (see conclusion (4) and L367-373). 
 As stated by the reviewer, our results ``converge on previously-identified conditions for the spread of new SD alleles, while also broadening the range of scenarios and conditions that can favour transitions between SD systems''}
@@
 %We also discuss, immediately below each conclusion, its novelty.
-%These are all new results, although (1A) was shown for the special case of $r=0$, $R=1/2$, and ploidally-antagonistic selection in Kozielska et al 2010, which we now mention immediately below (1A).
+%These are all new results, although (1A) was shown for the special case of $r=0$, $R=1/2$, and ploidally-antagonistic selection in Kozielska et al.\ (2010, which we now mention immediately below (1A).
 %}
 
-\subsection{MINOR COMMENTS}
+\subsection{}
+
+MINOR COMMENTS
 
@@
 \noindent\paragraph{Response}
-\textcolor{blue}{We have rearranged and rewritten the introduction to better motivate our model (see Response 2.1).
+\textcolor{blue}{We have rearranged and rewritten the introduction to better motivate our model (see Response 2.2).
 In particular, paragraph 5 presents the role of haploid selection as an evolutionary puzzle and paragraph 6 explains the limitations of previous attempts to solve the puzzle.
@@
 \textcolor{blue}{
-As suggested above (see responses 2.1 and 2.2), we have re-written to focus on our most novel findings, which are now laid our more specifically, e.g., L72-87 . 
+As suggested above (Responses 2.1-2.4), we have re-written to focus on our most novel findings, which are now laid our more specifically, e.g., L72-87 . 
 }
@@
 The `epistatic-dominance' between loci is important to the evolutionary dynamics.
-For example, Veller et al.
-(2018, Genetics) show that there is a tendency for drift to occur in the direction of the epistatically-dominant sex-determining locus (mentioned on L545-546).
+For example, Veller et al.\ (2018, Genetics) show that there is a tendency for drift to occur in the direction of the epistatically-dominant sex-determining locus (mentioned on L545-546).
 Our results also show that the outcome can depend on which sex-determining locus has an epistatically-dominant effect.
@@
 There are some numerical examples with reduced `epistatic dominance' in the supplementary material of van Doorn \& Kirkpatrick (2007, Nature), which we also point to here.
-Their findings suggest that the selective advantage is reduced (the modifier mutation effectively has a smaller effect) but the direction of evolution is expected to be qualitatively unchanged. 
+Their findings suggest that the selective advantage is reduced (the modifier mutation effectively has a smaller effect) but the direction of evolution is likely to be qualitatively unchanged. 
 }
@@
 \textcolor{blue}{This is now Figure 3, panel C.
-Here the blue and green curves should not really show as they are not expected to increase from a very small initial frequency.
-We have kept the original scale but now state in the legend that the blue and green loci do not invade.}
+Here the blue and green curves are failed invasions, i.e., they start from a low frequency and are expected to further decrease in frequency.
+We have kept the original scale but now state more clearly in the legend that the blue and green loci do not invade and do not show.
+We believe that it is clearer to retain the more familiar curve shape that shows the spread of the successful invasions.
+}
 
@@
 I also find the article claims that: (a) the modeling work is novel and (b) the findings are unexpected to be only partially justified.
-The works of Kozielska 2014 and Ubeda 2015 model the combined effects of both haploid and diploid selection on the evolution of new sex-chromosomes.
+The works of Kozielska 2014 and Ubeda (2015) model the combined effects of both haploid and diploid selection on the evolution of new sex-chromosomes.
 The work of [SOO] is thus not novel in considering both haploid and diploid selection on the evolution of new sex-chromosomes.
@@
 \textcolor{blue}{
-We have performed an extensive re-arrangement to improve the clarity of our writing, especially regarding the main results (see Responses 2.1-2.3). 
-As suggested by the reviewer (here and below), we also now give more prominence to the related results by Kozielska et al.\ 2010 and Ubeda et al.\ 2015 (e.g., L56-71, L198, L367-373, L440-446). 
-In particular, we introduce these studies (L56-71) and more precisely indicate which of our model features and results are new and unexpected in light of these previous results.
-}
-
-\textcolor{blue}{
+We have performed an extensive re-arrangement to improve the clarity of our writing, especially regarding the main results (see Responses 2.2-2.4). 
+As suggested by the reviewer (here and below), we also now give more prominence to the related results by Kozielska et al.\ (2010) and Ubeda et al.\ (2015) (e.g., L56-71, L198, L367-373, L440-446). 
+In particular, we introduce the study by Ubeda et al.\ (2015) earlier (L56-71) and more precisely indicate which of our model features and results are new and unexpected in light of these previous results.
+\\
+\indent
 While related, these two studies considered particular cases that we do not consider at length. 
@@
 Similarly, Kozielska et al.\ (2010) involves a special case of GSD transitions during which sex-linkage goes from perfect to none, which is an example of our Conclusion 2 and is similar to Conclusion 3C, which are conclusions regarding GSD-GSD transitions in which linkage with a haploid selected locus is decreased.
-This is mentioned on in numerous places in the text (L62-67, L301-304, and L367-368). 
+This is now mentioned in more numerous places in the text (L62-67, L301-304, and L367-368). 
+\\
+\indent
 We believe that our new presentation makes the novel and unexpected features of our results much more apparent. 
+For example, we have re-written summaries in the closing paragraph of the introduction (L72-87) and opening paragraph of the discussion (L428-436) and highlighted particular conclusions (see Response 2.4).
 For example, despite these precedents, we find the combination of Conclusions 3A, 3B, and 3C to be a striking reconciliation of the results of Kozielska et al.\ (2010) and Ubeda et al.\ (2015), see Conclusion 4 as well.
+Furthermore, we do not see a clear precedent of any kind for Conclusions 4 and 5, or Conclusions 1 and 2 with diploid selection only. 
 We elaborate further on what makes our results novel and surprising in the responses below.
@@
 The findings in [SOO] claimed to be surprising (``Surprisingly, we find that neither force (sex ratio selection nor associations with genes that have sex-specific effects) dominates the spread of new sex-determining systems alone.") ...
-[but this result is rather similar to those in Ubeda et al 2015].
+[but this result is rather similar to those in Ubeda et al.
+2015].
 
@@
 $\lambda_{Y'}^{ZW}$ with $r<1/2$, $R=1/2$, and male meiotic drive).
-As mentioned by the reviewer, Step 2 in Ubeda et al.\ 2015 shows that associations with a haploid selected locus can favour a new sex-determining allele despite causing biased sex ratios. 
+As mentioned by the reviewer, Step 2 in Ubeda et al.\ (2015) shows that associations with a haploid selected locus can favour a new sex-determining allele despite causing biased sex ratios. 
 Nevertheless, it was difficult for us to intuit whether the presence/absence of ancestral sex-ratio bias would have a negligible or overwhelming effect on the evolution of new sex-determining alleles.
@@
 There are reasons to suspect that ancestral-sex-ratio biases would strongly influence the spread of new sex-determining systems.
-For example, step 3 of Ubeda et al.\ involves the spread of an autosomal meiotic drive suppressor favoured by Fisherian sex-ratio selection and Kozielska et al.\ 2010 show that ancestral sex-ratio bias can favour new sex determining systems that balance the sex ratio.
-Furthermore, reviews mentioned on L21 suggest that Fisherian sex-ratio selection is a particularly dominant force driving transitions between sex-determining systems.
+For example, step 3 of Ubeda et al.\ involves the spread of an autosomal meiotic drive suppressor favoured by Fisherian sex-ratio selection and Kozielska et al.\ (2010) show that ancestral sex-ratio bias can favour new sex determining systems that balance the sex ratio.
+Furthermore, reviews mentioned on L21 and L429 suggest that Fisherian sex-ratio selection is a particularly dominant force driving transitions between sex-determining systems.
 We found our result, that beneficial associations and sex ratio selection exert exactly equal forces on the spread of neo-sex-chromosomes (with selection weak relative to recombination), such that there is no difference between the propensity for XY-ZW or ZW-XY transitions, to be surprising.
+\\
+\indent
 To clarify our meaning we have rephrased (in Author summary): ``Surprisingly, we find the two forces (selection to equalize the sex-ratio and the benefits of hitchhiking alongside driven alleles that distort the sex ratio) will often be equally strong, and thus neither is sufficient to explain the spread of new sex-determining systems in every case."
-We believe that the re-framing of the Introduction/Results and the emphasis given to specific Conclusions will help to clarify this point throughout the paper (see Responses 2.1-2.3). 
-In particular, this result is now highlighted as `Conclusion 4'.
+We believe that the re-framing of the Introduction/Results and the emphasis given to specific Conclusions will help to clarify this point throughout the paper (see Responses 2.2-2.4). 
+In particular, this result is now highlighted as Conclusion 4.
 }
@@
 \noindent\subsubsection{}
-\noindent and unexpected (``Even more unexpectedly, we find that, to spread, new sex-determining alleles do not necessarily have to arise in closer linkage with genes that are differentially selected in males and females"), are rather similar to those in Ubeda et al 2015.
+\noindent and unexpected (``Even more unexpectedly, we find that, to spread, new sex-determining alleles do not necessarily have to arise in closer linkage with genes that are differentially selected in males and females"), are rather similar to those in Ubeda et al.
+2015.
 This is a problem that repeats itself over the paper
@@
 \textcolor{blue}{
-The Ubeda et al.\ (2015) results do indeed show that differential selection between male and female diploids is not required for new sex-determining alleles to spread; they show that a new genetic sex-determining allele can spread from ancestral ESD when it is linked to a locus that experiences sex-specific meiotic drive.
+The Ubeda et al.\ (2015) results do indeed show that differential selection between male and female diploids is not required for new sex-determining alleles to spread; they show that a new genetic sex-determining allele can spread from ancestral ESD when it is linked to a locus that experiences sex-limited meiotic drive.
 In this sentence, we were attempting to stress that new sex determining alleles can spread when they are \textit{less closely linked or even completely unlinked} to loci under differential male/female haploid and/or diploid selection.
 To our knowledge, this has only been shown for the special case of male meiotic drive in an ancestral XY system with $r=0$ and $R=1/2$ with a neo-W, which is driven by sex-ratio selection (Kozielska et al.\ 2010).
-We therefore found the large parameter space allowing invasion with $r<R$ (Table 3), sometimes in the absence of sex-ratio selection (or even in the absence of haploid selection), to be very unexpected.
+We therefore found the large parameter space allowing invasion with $r<R$ (Table 3), sometimes in the absence of sex-ratio selection (or even in the absence of haploid selection, Conclusion 2), to be very unexpected.
+\\
+\indent
 To improve our communication of this result, we have rephrased (in Author Summary): ``We also find that new sex-determining alleles can spread despite being less closely linked to selected loci as long as initial linkage is tight or haploid selection is present."
-The changes to the presentation of the Introduction, Results, and Discussion should also help to clarify this point further (see Responses 2.1-2.3). 
+The changes to the presentation of the Introduction, Results, and Discussion should also help to clarify this point further (see Responses 2.2-2.4). 
+In particular, this result is now highlighted in Conclusions 2 and 3C.
 }
@@
 Here, sexually-antagonistic selection was referred to as an example of ``selective differences between the sexes". 
-We believe the phrase `selective differences between the sexes' includes sex-differences in drive (Ubeda et al 2015), which occurs during haploid rather than diploid selection, as indicated in Fig 1B (see also Response 3.1.6).
+We believe the phrase `selective differences between the sexes' includes sex-differences in drive (as in Ubeda et al.\ (2015)), which occurs during haploid rather than diploid selection, as indicated in Fig 1B, see also Response 3.1.6.
 The enhanced discussion of Ubeda et al.\ (2015) immediately below this statement should help to clarify this point (L58-62).
 \\
+\indent 
 Charlesworth and Charlesworth 1978 (Am Nat and Heredity) discuss the role of inbreeding (and particularly inbreeding depression) in transitions from hermaphroditism to dioecy. 
@@
 For clarity, we have moved this description into the Introduction (L48-49). 
-When we draw a parallel between ESD and hermaphroditism (L483-491), we suggest future theory include inbreeding and cite Charlesworth and Charlesworth (1978). 
+In addition, when we draw a parallel between ESD and hermaphroditism (L483-491), we now suggest future theory include inbreeding and cite Charlesworth and Charlesworth (1978). 
 }
@@
 \textcolor{blue}{
-As we now make clear (see response 3.1), we do not look at the same situation as Ubeda et al 2015 and our contribution is not just to add sex-specific viability. 
-In particular, Ubeda et al start from ESD. 
+We believe that our model explores situations that are significantly different from those in Ubeda et al.\ (2015). 
+For example, Ubeda et al.\ (2015) start from ESD. 
 Therefore, associations with an ancestral sex-determining locus cannot build up. 
 These lead to some of our most surprising results (e.g., haploid selection favours trans-GSD transitions for a wider variety of genomic locations than diploid selection alone; ESD does not invade despite initial sex-ratio bias).
-Further, our model and intuition-giving analytical solutions explore a much wider range of scenarios than the numerical results of Ubeda et al., allowing, for example, sex-specific selection (e.g., sex-antagonism) and various genomic arrangements (any order/linkage of the three loci).
-Our model is thus much more general and clarifies just when one should expect to see the numerical results of Ubeda et al.
-We have rephrased to make this clear (after discussing Ubeda et al.\ 2015 in the Introduction, see Response 2.1; L72-76): ``Here, we analytically find the conditions under which new GSD or ESD systems spread in ancestral GSD systems with any degree of linkage between the loci involved and arbitrary forms of haploid and diploid selection.
+Further, our model and intuition-giving analytical solutions explore a much wider range of scenarios, allowing, for example, sex-specific selection (e.g., sex-antagonism) and various genomic arrangements (any order/linkage of the three relevant loci).
+\\
+\indent
+We have rephrased to make this clear (after discussing Ubeda et al.\ (2015) in the Introduction, see Response 2.2; L72-76): ``Here, we analytically find the conditions under which new GSD or ESD systems spread in ancestral GSD systems with any degree of linkage between the loci involved and arbitrary forms of haploid and diploid selection.
 Doing so, we reconcile and generalize the results of Kozielska et al.\ (2010) and Ubeda et al.\ (2015) by deriving conditions for the spread of new GSD systems that alter linkage with haploid selected loci."
@@
 \textcolor{blue}{In this study, we are referring to organisms, such as animals and angiosperms, in which the type of gamete depends on the sex of the diploid that produced it.
-In this respect, one could consider gametic selection among sperm, for example, to be a form of male-specific selection.
-However, as noted by the reviewer here, the dynamics of selection during gametic selection cannot be captured by a diploid selection coefficient, which is why we specifically model selection upon haploid genotypes.
+In this respect, one could consider gametic competition among sperm, for example, to be a form of male-specific selection.
+However, as noted by the reviewer here, the dynamics of selection during gametic competition cannot be captured by a diploid selection coefficient, which is why we specifically model selection upon haploid genotypes.
+\\
+\indent
 In our revision, a roughly corresponding statement now reads (L50-51) ``On one hand, haploid selection is typically sex-limited in that it usually occurs among gametes produced by one sex only [38-41].''.
@@
 
-Following up my previous comment Ubeda 2015 explores this and shows that both forms of selection are different.
+Following up my previous comment Ubeda (2015) explores this and shows that both forms of selection are different.
 For example sex-antagonistic selection is needed for the invasion of a new sex-determining gene with diploid selection while antagonistic drive in each of the sexes is not needed for the invasion of a new sex-determining gene with haploid selection.
@@
 If drive was the same in both sexes, $\alpha^{m}=\alpha^{f}$ (and all other male/female selection terms also equal), we show that the new sex-determining allele would not invade (e.g., equation 2 and 3).
-In this sense haploid selection is similar to sex-specific diploid selection, and together haploid and diploid selection determine the differences in male vs.\ female fitness, which can drive sex-determination transitions (see Response 3.1.4).\\
-This sentence meant to introduce the `sex-specific' aspect of haploid selection in the way Ubeda et al.\ 2015 considers it; associations with alleles favoured in one sex (or the gametes produced by that sex) should favour a new sex-determining allele.
+In this sense haploid selection is similar to sex-specific diploid selection, and together haploid and diploid selection determine the differences in male vs.\ female fitness, which can drive sex-determination transitions (see also Response 3.1.4).
+\\
+\indent
+This sentence meant to introduce the `sex-specific' aspect of haploid selection in the way Ubeda et al.\ (2015) considers it; associations with alleles favoured in one sex, or the gametes produced by that sex, should favour a new sex-determining allele.
 We have rephrased to make this clear (L51-53): ``Therefore, one might expect new sex-determining systems to benefit from close linkage with haploid selected loci, as found for loci that experience diploid-sex-differences in selection [35-37]."
-We now follow this sentence up with a paragraph that clarifies its meaning by comparing with the results of Kozielska et al.\ 2010 and Ubeda et al.\ 2015 (L56-71; see also Response 2.1).}
+We now follow this sentence up with a paragraph that clarifies its meaning by comparing with the results of Kozielska et al.\ (2010) and Ubeda et al.\ (2015) (L56-71; see also Response 2.2).}
 
@@
 %\textcolor{red}{edit}
-\textcolor{blue}{While Ubeda et al.\ (2015) did focus on sex ratio biases and haploid selected alleles, the system started with ESD, where there are no associations (see Response 3.1.4).
-Further, the restricted scope of that numerical study prevents us from generalizing beyond its special case (see Response 3.1.4).
-We now present a refurbished argument for why it is difficult to intuit the implications of haploid selection while summarizing the results of Ubeda et al.\ and Kozielska et al.\ 2010 in the Introduction (see Response 2.1).
+\textcolor{blue}{
+This sentence was intended to present the `evolutionary puzzle' presented by haploid selection, it has been removed. 
+We now present a refurbished argument for why it is difficult to intuit the full implications of haploid selection, even in the light of previous results, which we present while summarizing the results of Ubeda et al.\ and Kozielska et al.\ (2010) in the Introduction (see Response 2.2).
+We discuss this further in Responses 3.1., 3.1.1., 3.1.2, 3.1.4, and 3.1.8.
 }
@@
 \noindent\subsubsection{}
-I will not provide further examples, but it is surprising that the work of Ubeda et al 2015, which is closely related to the one presented here, is cited in page 12 supporting a statement only tangential to the work of Ubeda et al 2015.
+I will not provide further examples, but it is surprising that the work of Ubeda et al.\ (2015, which is closely related to the one presented here, is cited in page 12 supporting a statement only tangential to the work of Ubeda et al.\ (2015.
 
@@
 \textcolor{blue}{
-Ubeda et al 2015 was in fact cited in the main text (line 396) of the original submission, where we mentioned that it showed that sex-ratio biases could become more severe during a transition.
-However, we thank the reviewer for emphasizing the similarities between that study and our own.
-We now discuss Ubeda et al.\ 2015 in the Introduction, Results, and Discussion (see Responses above), which we believe clarifies and strengthens our arguments while giving credit to this earlier work.}
+We thank the reviewer for emphasizing comparisons between our study and the work by Ubeda et al.\ (2015). 
+While we were very familiar with this work, our original submission only introduced it in the discussion (line 396), where we mentioned that it showed that associations can develop between new sex-determining alleles and haploid selected loci, resulting in the evolution of sex-ratio biases.
+We now discuss Ubeda et al.\ (2015) in the Introduction, Results, and Discussion (see Responses above), which we believe clarifies and strengthens our arguments while giving appropriate credit to this earlier work.
+}
+
+\textcolor{blue}{To conclude, despite the precedent set by result by Ubeda et al.\ (2015), Kozielska et al.\ (2010), van Doorn and Kirkpatrick (2007,2010), and Muralidhar and Veller (2018), we found there to be an intellectual gap for a study that explored GSD-GSD transitions and GSD-ESD transitions with haploid selection and generalized genomic locations for the loci involved.
+For example, this allows us to examine the influence of Fisherian sex ratio selection by comparing cases with and without ancestral sex ratio biases (L355-366). 
+Although we were expecting to find that haploid selection could favour transitions in sex-determination, we found several very unexpected results, which we have tried to emphasize further in our revision (in particular, see Conclusions 2, 3C, 4, and 5 and Responses 3.1.1 and 3.1.2).
+}
 

### 2018-05-21 LaTeX/main_revised.tex
updated response letter and changed Conclusions 3 again

@@
 \noindent\textit{Conclusion 3A:}\
-\textbf{New sex-determining alleles (causing cis-GSD transitions, XY $\leftrightarrow$ XY or ZW $\leftrightarrow$ ZW) are favoured if they arise more closely linked with a locus that experiences (haploid and/or diploid) selection than the ancestral-sex-determining locus is ($R<r$).}
+\textbf{New sex-determining alleles (causing cis-GSD transitions, XY $\leftrightarrow$ XY or ZW $\leftrightarrow$ ZW) are favoured if they arise more closely linked with a locus that experiences (haploid and/or diploid) selection than the ancestral-sex-determining locus ($R<r$).}
 \vspace{0.5cm}
@@
 \noindent
-Similarly, a neo-W is typically favoured when it is more closely linked to the selected locus than the ancestral sex-determining region is, ($R<r$, e.g., Figs \ref{fig:SexAntagTighter}B and \ref{fig:Combination_Centimorgans}).
-Specifically, if the selected locus ($\mathbf{A}$) is ancestrally autosomal ($r=1/2$, leading to $ \hat{p}^\male_Y-\hat{p}^\male_X =0$), a neo-W linked to the selected locus ($R<1/2$) will spread ($\lambda_{W'}^{(XY)}>1$).
+%Similarly, a neo-W is typically favoured when it is more closely linked to the selected locus than the ancestral sex-determining region is, ($R<r$).
+Similarly, in the absence of haploid selection ($t^\circ=\alpha^\circ_{\Delta}=0$), Eq \eqref{eq:lambda_neoW} indicates that trans-GSD transitions can occur if and only if the new sex-determining locus is more closely linked to a locus under selection, $R<r$, as found by \cite{vanDoorn:2010hu}.
+With haploid selection, a neo-W is also usually favoured when it is more closely linked to the selected locus than the ancestral sex-determining region is, ($R<r$, e.g., Figs \ref{fig:SexAntagTighter}B and \ref{fig:Combination_Centimorgans}); this is true unless the last term in Eq \eqref{eq:lambda_neoW} is negative and dominant over the first, which requires relatively restrictive combinations of selection and recombination parameters.
+For example, with haploid selection, a neo-W will always be favoured if it arises in linkage with a selected locus ($R<1/2$) that is ancestrally autosomal ($r=1/2$, leading to $ \hat{p}^\male_Y-\hat{p}^\male_X =0$).
 
@@
 \noindent\textit{Conclusion 3B:}\
-\textbf{New sex-determining alleles (causing trans-GSD transitions, XY $\leftrightarrow$ ZW) are favoured if they are linked with an ancestrally-autosomal locus ($R<1/2$, $r=1/2$) that experiences (haploid and/or diploid) selection.}
+\textbf{New sex-determining alleles (causing trans-GSD transitions, XY $\leftrightarrow$ ZW) are usually favoured if they arise more closely linked with a locus that experiences (haploid and/or diploid) selection than the ancestral-sex-determining locus ($R<r$).
+}
 \vspace{0.5cm}
@@
 \noindent
-In the absence of haploid selection ($t^\circ=\alpha^\circ_{\Delta}=0$), Eq \eqref{eq:lambda_neoW} indicates that trans-GSD transitions can occur if and only if the new sex-determining locus is more closely linked to a locus under selection, $R<r$, as found by \cite{vanDoorn:2010hu}.
 However, with haploid selection and some ancestral sex-linkage ($r<1/2$; allowing allele frequency differences on the X and Y), the term in square brackets in Eq \eqref{eq:lambda_neoW} can be positive.
@@
 \noindent\textit{Conclusion 3C:}\
-\textbf{With haploid selection, new sex-determining alleles (causing trans-GSD transitions, XY $\leftrightarrow$ ZW) can spread even if they arise less closely linked with a locus that experiences selection than the ancestral-sex-determining locus is ($r<R$).}
+\textbf{With haploid selection, new sex-determining alleles (causing trans-GSD transitions, XY $\leftrightarrow$ ZW) can spread even if they arise less closely linked with a locus that experiences selection than the ancestral-sex-determining locus ($r<R$).}
 \vspace{0.5cm}

### 2018-05-21 LaTeX/response.tex
revisions done

@@
 This is true, we now mention that the model is deterministic, and hence ignores drift (L131-133). 
-As suggested, when discussing the model limitations at the end of the Discussion we now mention a study on the effect of drift during trans-GSD transitions, which tend to drift in the direction of epistatically-dominant sex-determining loci (L543-546): ``It should be noted, however, that the dynamics of sex-determining alleles with very weak effect will be influenced by genetic drift, which itself has been shown to bias transitions towards epistatically-dominant sex-determining systems when there is no direct selection (Veller et al.\ (2017)."}
+As suggested, when discussing the model limitations at the end of the Discussion we now mention a study on the effect of drift during trans-GSD transitions, which tend to drift in the direction of epistatically-dominant sex-determining loci (L546-549): ``It should be noted, however, that the dynamics of sex-determining alleles with very weak effect will be influenced by genetic drift, which itself has been shown to bias transitions towards epistatically-dominant sex-determining systems when there is no direct selection (Veller et al.\ (2017)."}
 
@@
 \textcolor{blue}{In our deterministic model (where the number of binomial trials is infinite), the variance in the fraction male is 0 with ESD, as it is with GSD. 
-We now mention this (L386-388): ``In our deterministic model this means the fraction female in the subpopulation containing $m$ is exactly $k$, even when $m$ is rare (i.e., ESD does not introduce any additional variance in sex determination)."
+We now mention this (L389-391): ``In our deterministic model this means the fraction female in the subpopulation containing $m$ is exactly $k$, even when $m$ is rare (i.e., ESD does not introduce any additional variance in sex determination)."
  }
@@
 We then lay out four specific conclusions (L182-204). 
-In the ``Tight linkage'' section, we now first describe specific cases why neo-W's can have improved female fitness, Conclusion 1, L230-281, with more focus on non-technical interpretation (e.g., L241-247).
+In the ``Tight linkage'' section, we now first describe specific cases why neo-W's can have improved female fitness (L230-281, Conclusion 1), with more focus on non-technical interpretation (e.g., L241-247).
 This includes the case where looser sex-linkage can evolve (L265-281, Conclusion 2). 
@@
 \item[(3B)] New sex-determining alleles (causing trans-GSD transitions, XY $\leftrightarrow$ ZW) are favoured if they are linked with an ancestrally-autosomal locus ($R<1/2$, $r=1/2$) that experiences (haploid and/or diploid) selection.
-(L333-335)
+(L338-340)
 \item[(3C)] With haploid selection, new sex-determining alleles (causing trans-GSD transitions, XY $\leftrightarrow$ ZW) can spread even if they arise less closely linked with a locus that experiences selection than the ancestral-sex-determining locus is ($r<R$).
-(L341-343)
+(L344-346)
 \item[(4)] When selection is weak relative to recombination, the presence of haploid selection equally favors the spread of new sex determination systems that reduce sex-ratio bias (benefiting from Fisherian sex ratio selection) or generate a sex-ratio bias (benefiting from associations with selected alleles).
-(L363-366)
-\item[(5)] Transitions from genetic to environmental sex-determination are not straightforwardly predicted by selection to balance the zygotic sex ratio when haploid selection is present.  (L424-426)
+(L366-369)
+\item[(5)] Transitions from genetic to environmental sex-determination are not straightforwardly predicted by selection to balance the zygotic sex ratio when haploid selection is present.  (L427-429)
 %\vspace{0.25cm}\\
 \end{enumerate}
-These conclusions are also more clearly laid out in the introduction (L45-47, L72-87) and are referenced directly in summarisations in the discussion (L428-436, L548-559). 
+These conclusions are also more clearly laid out in the introduction (L45-47, L72-87) and are referenced directly in summarisations in the discussion (L431-439, L551-562). 
 }
@@
 \textcolor{blue}{Of these conclusions, (2), (3A), and (3B) have some precedent. 
-(3A) and (3B) are similar to studies by van Doorn and Kirkpatrick (2007,2010) that do not include haploid selection.
-These comparisons are made immediately above (L322-325) and below (L336-338) the conclusions and are mentioned elsewhere (L53, L77, L494).
+(3A) and (3B) are similar to studies by van Doorn and Kirkpatrick (2007, 2010) that do not include haploid selection.
+These comparisons are made immediately above (L322-325) and below (L329-3331) the conclusions and are mentioned elsewhere (L53, L77, L497).
 Including haploid selection, Ubeda et al.\ (2015) had numerical examples similar to (3A) and (3B), except that the starting state was ESD. 
 Kozielska et al.\ (2010) had examples that involved trans-GSD transitions with haploid selection and $r=0$, $R=1/2$, a sub-case of (2) (and somewhat similar to (3C)), but focussed only on sex ratio selection.
-We clarify how our results compare to these two studies in the introduction (L56-71), results (L198, L301-304, L367-343), and discussion (L437-451).
-In particular, while these previous studies provide some precedent for conclusions (2), (3A), and (3B), our results are more general and reconcile their results (see conclusion (4) and L367-373). 
+We clarify how our results compare to these two studies in the introduction (L56-71), results (L198, L301-304, L370-346), and discussion (L440-454).
+In particular, while these previous studies provide some precedent for conclusions (2), (3A), and (3B), our results are more general and reconcile their results (see Conclusion 4 and L370-376). 
 As stated by the reviewer, our results ``converge on previously-identified conditions for the spread of new SD alleles, while also broadening the range of scenarios and conditions that can favour transitions between SD systems''}
@@
 The `epistatic-dominance' between loci is important to the evolutionary dynamics.
-For example, Veller et al.\ (2018, Genetics) show that there is a tendency for drift to occur in the direction of the epistatically-dominant sex-determining locus (mentioned on L545-546).
+For example, Veller et al.\ (2018, Genetics) show that there is a tendency for drift to occur in the direction of the epistatically-dominant sex-determining locus (mentioned on L548-549).
 Our results also show that the outcome can depend on which sex-determining locus has an epistatically-dominant effect.
@@
 We have performed an extensive re-arrangement to improve the clarity of our writing, especially regarding the main results (see Responses 2.2-2.4). 
-As suggested by the reviewer (here and below), we also now give more prominence to the related results by Kozielska et al.\ (2010) and Ubeda et al.\ (2015) (e.g., L56-71, L198, L367-373, L440-446). 
+As suggested by the reviewer (here and below), we also now give more prominence to the related results by Kozielska et al.\ (2010) and Ubeda et al.\ (2015) (e.g., L56-71, L198, L370-376, L443-449). 
 In particular, we introduce the study by Ubeda et al.\ (2015) earlier (L56-71) and more precisely indicate which of our model features and results are new and unexpected in light of these previous results.
@@
 Nevertheless, some steps in Ubeda et al.\ (2015) involve increased linkage with a haploid selected locus, which is precedent for our Conclusions 3A and 3B (which are for GSD-GSD transitions in which linkage with a haploid selected locus is increased).
-We now mention this in the introduction (L58-60) and results (L369-371). %, and Discussion (L432).  
+We now mention this in the introduction (L58-60) and results (L372-374). %, and Discussion (L432).  
 Similarly, Kozielska et al.\ (2010) involves a special case of GSD transitions during which sex-linkage goes from perfect to none, which is an example of our Conclusion 2 and is similar to Conclusion 3C, which are conclusions regarding GSD-GSD transitions in which linkage with a haploid selected locus is decreased.
-This is now mentioned in more numerous places in the text (L62-67, L301-304, and L367-368). 
+This is now mentioned in more numerous places in the text (L62-67, L301-304, and L370-371). 
 \\
@@
 We believe that our new presentation makes the novel and unexpected features of our results much more apparent. 
-For example, we have re-written summaries in the closing paragraph of the introduction (L72-87) and opening paragraph of the discussion (L428-436) and highlighted particular conclusions (see Response 2.4).
+For example, we have re-written summaries in the closing paragraph of the introduction (L72-87) and opening paragraph of the discussion (L431-439) and highlighted particular conclusions (see Response 2.4).
 For example, despite these precedents, we find the combination of Conclusions 3A, 3B, and 3C to be a striking reconciliation of the results of Kozielska et al.\ (2010) and Ubeda et al.\ (2015), see Conclusion 4 as well.
@@
 For example, step 3 of Ubeda et al.\ involves the spread of an autosomal meiotic drive suppressor favoured by Fisherian sex-ratio selection and Kozielska et al.\ (2010) show that ancestral sex-ratio bias can favour new sex determining systems that balance the sex ratio.
-Furthermore, reviews mentioned on L21 and L429 suggest that Fisherian sex-ratio selection is a particularly dominant force driving transitions between sex-determining systems.
+Furthermore, reviews mentioned on L21 and L432 suggest that Fisherian sex-ratio selection is a particularly dominant force driving transitions between sex-determining systems.
 We found our result, that beneficial associations and sex ratio selection exert exactly equal forces on the spread of neo-sex-chromosomes (with selection weak relative to recombination), such that there is no difference between the propensity for XY-ZW or ZW-XY transitions, to be surprising.
@@
 For clarity, we have moved this description into the Introduction (L48-49). 
-In addition, when we draw a parallel between ESD and hermaphroditism (L483-491), we now suggest future theory include inbreeding and cite Charlesworth and Charlesworth (1978). 
+In addition, when we draw a parallel between ESD and hermaphroditism (L486-494), we now suggest future theory include inbreeding and cite Charlesworth and Charlesworth (1978). 
 }
@@
 We thank the reviewer for emphasizing comparisons between our study and the work by Ubeda et al.\ (2015). 
-While we were very familiar with this work, our original submission only introduced it in the discussion (line 396), where we mentioned that it showed that associations can develop between new sex-determining alleles and haploid selected loci, resulting in the evolution of sex-ratio biases.
+While we were very familiar with this work, our original submission only introduced it in the discussion (line 396 in the original), where we mentioned that it showed that associations can develop between new sex-determining alleles and haploid selected loci, resulting in the evolution of sex-ratio biases.
 We now discuss Ubeda et al.\ (2015) in the Introduction, Results, and Discussion (see Responses above), which we believe clarifies and strengthens our arguments while giving appropriate credit to this earlier work.
@@
 
-\textcolor{blue}{To conclude, despite the precedent set by result by Ubeda et al.\ (2015), Kozielska et al.\ (2010), van Doorn and Kirkpatrick (2007,2010), and Muralidhar and Veller (2018), we found there to be an intellectual gap for a study that explored GSD-GSD transitions and GSD-ESD transitions with haploid selection and generalized genomic locations for the loci involved.
-For example, this allows us to examine the influence of Fisherian sex ratio selection by comparing cases with and without ancestral sex ratio biases (L355-366). 
+\textcolor{blue}{To conclude, despite the precedent set by result by Ubeda et al.\ (2015), Kozielska et al.\ (2010), van Doorn and Kirkpatrick (2007, 2010), and Muralidhar and Veller (2018), we found there to be an intellectual gap for a study that explored GSD-GSD transitions and GSD-ESD transitions with haploid selection and generalized genomic locations for the loci involved.
+For example, this allows us to examine the influence of Fisherian sex ratio selection by comparing cases with and without ancestral sex ratio biases (L358-369). 
 Although we were expecting to find that haploid selection could favour transitions in sex-determination, we found several very unexpected results, which we have tried to emphasize further in our revision (in particular, see Conclusions 2, 3C, 4, and 5 and Responses 3.1.1 and 3.1.2).

### 2018-06-02 LaTeX/S3Appendix_revised.tex
revision 2 complete by matt

@@
 Male-biased sex ratios facilitate the spread of neo-W-$A$ and neo-W-$a$ haplotypes (increasing $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$). 
-Panels A-C in \nameref{fig:regionMaleDrive} and \ref{fig:regionMaleGS} show that neo-W haplotypes tend to spread for a wider range of parameters when sex ratios are male biased, compared to Fig \ref{fig:regionplots} without haploid selection.
+Panels A-C in Figure \ref{fig:regionMaleDrive} and \ref{fig:regionMaleGS} show that neo-W haplotypes tend to spread for a wider range of parameters when sex ratios are male biased, compared to Fig \ref{fig:regionplots} without haploid selection.
 By contrast, male haploid selection in favour of the $A$ allele generates female-biased sex ratios and reduces $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$, as demonstrated by panels D-F in \nameref{fig:regionMaleDrive} and \nameref{fig:regionMaleGS}.

### 2018-06-02 LaTeX/Turnover_bioRXiv_revision.tex
revision 2 complete by matt

--- 2018-05-21 LaTeX/main_revised.tex
@@
 % amsmath and amssymb packages, useful for mathematical formulas and symbols
-\usepackage{amsmath}%amssymb
+\usepackage{amsmath,amssymb}
 
@@
 \setlength{\headheight}{27.023pt}
-\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
+%\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
 \rfoot{\thepage/\pageref{LastPage}}
 \renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
-\fancyheadoffset[L]{2.25in}
-\fancyfootoffset[L]{2.25in}
-\lfoot{\sf PLOS}
+%\fancyheadoffset[L]{2.25in}
+%\fancyfootoffset[L]{2.25in}
+%\lfoot{\sf PLOS}
 %% Include all macros below
-
-%for figure alignment
-\usepackage[export]{adjustbox}
 
@@
 \newcommand{\ipsum}{{\bf IPSUM}}
-
-%reference equations in appendices
-\usepackage{xr}
-\externaldocument{S1Appendix_revised}
-\externaldocument{S2Appendix_revised}
-\externaldocument{S3Appendix_revised}
-
-%for figures
-%\usepackage{epstopdf}
 
@@
 {\Large
-\textbf\newline{Haploid selection, sex-ratio bias, and transitions between sex-determining systems} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
+\textbf\newline{Haploid selection, sex ratio bias, and transitions between sex-determining systems} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
 }
@@
 % Please keep the abstract below 300 words
-%currently 308 words
+%currently 312 words
 \section*{Abstract}
@@
 Recombination (i.e., an odd number of cross-overs) occurs between loci $\mathbf{X}$ and $\mathbf{A}$ with probability $r$, between loci $\mathbf{A}$ and $\mathbf{M}$ with probability $R$, and between loci $\mathbf{X}$ and $\mathbf{M}$ with probability $\rho$.
-Any linear order of the loci can be modelled with appropriate choices of $r$, $R$, and $\rho$ (see Fig \ref{fig:model_outline}A and \nameref{tab:chisubstitutions}). 
+Any linear order of the loci can be modelled with appropriate choices of $r$, $R$, and $\rho$ (see Fig \ref{fig:model_outline}A and Table \ref{tab:chisubstitutions}). 
 Our model is entirely deterministic and hence ignores chance fluctuations in allele frequencies due to genetic drift.
@@
 We consider only equilibrium frequencies of alleles, $\hat{p}^\circ_i$, and Y-bearing male gametes, $\hat{q}_{Y}$, when determining the invasion of new sex-determining factors.
-We use $\zeta$ to measure the sex ratio (fraction male) among zygotes, which is determined by the allele frequencies and haploid selection coefficients (\nameref{tab:meanfitnesses}).
+We use $\zeta$ to measure the sex ratio (fraction male) among zygotes, which is determined by the allele frequencies and haploid selection coefficients (Table \ref{tab:meanfitnesses}).
 
@@
 $\bar{w}^{\circ}_{D}$ is the mean fitness of diploids of sex $\circ$ $\in\{\female,\male\}$.
-$\bar{w}_H^\circ$ is the mean fitness of haploids from sex $\circ$, see \nameref{tab:meanfitnesses}.
+$\bar{w}_H^\circ$ is the mean fitness of haploids from sex $\circ$, see Table \ref{tab:meanfitnesses}.
 $R$ is the rate of recombination between the neo-sex-determiner and the selected locus.
@@
 Invasion occurs when neo-W females can have higher fitness than the XX females in the ancestral population.
-Neo-W invasion is possible under all forms of selection that can maintain a polymorphism (sexually-antagonistic selection, overdominance, ploidally-antagonistic selection, or some combination, e.g., \nameref{fig:temporalOverdominance}, \nameref{fig:SexAntagTighterMaleDrive}, and \nameref{fig:regionPloidAntag}).
+Neo-W invasion is possible under all forms of selection that can maintain a polymorphism (sexually-antagonistic selection, overdominance, ploidally-antagonistic selection, or some combination, e.g., Fig \ref{fig:temporalOverdominance}, Fig \ref{fig:SexAntagTighterMaleDrive}, and Fig \ref{fig:regionPloidAntag}).
 Thus,
@@
 %\centerline{\includegraphics[width=1.25\linewidth]{Region_plot_combined_Mike}}
-\centerline{\includegraphics[width=1.4\linewidth, right]{../Plots/Region_plot_combined.eps}}
+\centerline{\includegraphics[width=1.2\linewidth]{../Plots/Region_plot_combined.eps}}
 \caption{
@@
 %Where both haplotypic growth rates are greater than one, a neo-W will spread when rare, regardless of linkage with the selected locus (for any $R$). 
-\nameref{fig:positionOverdominance} shows the dynamics arising with the parameters marked with a dagger. 
+Fig \ref{fig:positionOverdominance} shows the dynamics arising with the parameters marked with a dagger. 
 %Here, there is no haploid selection $t^\circ = \alpha^\circ_\Delta = 0$.
@@
 This is true for the neo-W-$A$ haplotype because it can pair with a Y-$a$ haplotype and still be female. 
-Whenever both haplotypic growth rates are greater than one, invasion by a neo-W is expected regardless of its linkage with the selected locus (i.e., for any $R$), see \nameref{fig:positionOverdominance} and \nameref{fig:temporalOverdominance} for examples.
+Whenever both haplotypic growth rates are greater than one, invasion by a neo-W is expected regardless of its linkage with the selected locus (i.e., for any $R$), see Fig \ref{fig:positionOverdominance} and Fig \ref{fig:temporalOverdominance} for examples.
 As a consequence, evolution can favor a new sex determination system on a different chromosome ($R = 1/2$), despite the fact that this unlinks the sex-determining locus from the selected locus.
@@
 \centering
-\centerline{\includegraphics[width=1.4\linewidth, right]{../Plots/PositionPlot_SexAntagTighter.eps}}
+\centerline{\includegraphics[width=1.2\linewidth]{../Plots/PositionPlot_SexAntagTighter.eps}}
 \caption{
@@
 An equivalent analysis is not possible where recombination rates are low. 
-However, numerical simulations demonstrate that, with tight sex linkage, neo-Y or neo-W alleles do not necessarily reach fixation in males or females, respectively, which can lead to the stable maintenance of a mixed sex-determining system, in which X, Y, and neo-W alleles all segregate (e.g., \nameref{fig:freqAll}B,C).
+However, numerical simulations demonstrate that, with tight sex linkage, neo-Y or neo-W alleles do not necessarily reach fixation in males or females, respectively, which can lead to the stable maintenance of a mixed sex-determining system, in which X, Y, and neo-W alleles all segregate (e.g., Fig \ref{fig:freqAll}B,C).
 
@@
 With haploid selection, Conclusions 1 \& 2 continue to apply (\nameref{app:inv_cond}). 
-The parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread under various forms of haploid selection are plotted in \nameref{fig:regionMaleDrive}, \nameref{fig:regionMaleGS}, \nameref{fig:regionFemaleDrive}, \nameref{fig:regionFemaleGS}.
-In particular, we note that adding haploid selection allows shifts in sex determination to a different chromosome ($R=1/2$) even when selection is sexually antagonistic with directional selection in each diploid sex, e.g., \nameref{fig:SexAntagTighterMaleDrive}.
-Furthermore, haploid selection allows variation to be maintained by ploidally-antagonistic selection, under which trans-GSD transitions may also be favoured, \nameref{fig:regionPloidAntag}.
+The parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread under various forms of haploid selection are plotted in Fig \ref{fig:regionMaleDrive}, Fig \ref{fig:regionMaleGS}, Fig \ref{fig:regionFemaleDrive}, Fig \ref{fig:regionFemaleGS}.
+In particular, we note that adding haploid selection allows shifts in sex determination to a different chromosome ($R=1/2$) even when selection is sexually antagonistic with directional selection in each diploid sex, e.g., Fig \ref{fig:SexAntagTighterMaleDrive}.
+Furthermore, haploid selection allows variation to be maintained by ploidally-antagonistic selection, under which trans-GSD transitions may also be favoured, Fig \ref{fig:regionPloidAntag}.
 Some cases of XY $\rightarrow$ ZW transitions where $r=0$, $R=1/2$, and selection is ploidally-antagonistic (meiotic drive in males opposed by diploid selection) were studied by Kozielska et al.
@@
 However, such transitions are not always driven by selection to reduce sex-ratio bias. 
-For example, with XY sex determination and haploid selection in females, sex ratios are not ancestrally biased yet a neo-W can invade (\nameref{fig:regionPloidAntag}). 
+For example, with XY sex determination and haploid selection in females, sex ratios are not ancestrally biased yet a neo-W can invade (Fig \ref{fig:regionPloidAntag}). 
 We further discuss how the spread of neo-sex-determining alleles is influenced by associations with haploid selected loci in the next section.
@@
 However, we show that, if selected loci are tightly linked to the ancestral sex-determining locus, they can drive trans-GSD transitions that reduce sex-linkage (Conclusions 1 \& 2), thus widening the range of genomic locations where selection could be driving observed trans-GSD transitions.
-In addition, we find that polymorphic sex determining systems (X, Y, and neo-W alleles all segregating) can be maintained when a selected locus is tightly linked to the ancestral sex-determining system (e.g., \nameref{fig:freqAll}B and \nameref{fig:freqAll}C), which is not possible with loose linkage~\cite{vanDoorn:2010hu}.
+In addition, we find that polymorphic sex determining systems (X, Y, and neo-W alleles all segregating) can be maintained when a selected locus is tightly linked to the ancestral sex-determining system (e.g., Fig \ref{fig:freqAll}B and Fig \ref{fig:freqAll}C), which is not possible with loose linkage~\cite{vanDoorn:2010hu}.
 This pair of conclusions apply in cases with or without haploid selection.
@@
 
+\nolinenumbers
+
+\section*{Acknowledgments}
+We thank Georgy Sandler and Stephen Wright for sharing their results with us, and we thank Bret Payseur and three anonymous reviewers for helpful comments on this manuscript.
+
+% Either type in your references using
+% \begin{thebibliography}{}
+% \bibitem{}
+% Text
+% \end{thebibliography}
+%
+% or
+%
+% Compile your BiBTeX database using our plos2015.bst
+% style file and paste the contents of your .bbl file
+% here. See http://journals.plos.org/plosone/s/latex for 
+% step-by-step instructions.
+% 
+\bibliography{sex_chromosomes.bib}
+
+%\newpage
+
 \section*{Supporting information}
 
+\section*{Supplementary Files}
 \paragraph*{S1 File.}
 \label{file:Mathematica}
-{\bf Supplementary \textit{Mathematica} file.}  This file can be used to re-derive our results and generate figures.
-
-\paragraph*{S1 Table}
+{\bf Supplementary \textit{Mathematica} file.}  This file can be used to re-derive our results and generate figures. Please contact authors for access.
+
+\setcounter{equation}{0}
+\renewcommand{\theequation}{S1.\arabic{equation}}
+
+\section*{S1 Appendix}
+\label{app:recurs}
+
+\subsection*{Recursion equations}
+
+In each generation we census the genotype frequencies in male and female gametes/gametophytes (hereafter, gametes) between meiosis (and any meiotic drive) and gametic competition. 
+At this stage we denote the frequencies of X- and Y-bearing gametes from males and females $x_{i}^{\circ}$ and $y_{i}^{\circ}$.
+The superscript $\circ \in \{\male,\female\}$ specifies the sex of the diploid that the gamete came from. 
+The subscript $i\in\{1,2,3,4\}$ specifies the genotype at the selected locus $\mathbf{A}$ and at the novel sex-determining locus $\mathbf{M}$, where $1=AM$, $2=aM$, $3=Am$, and $4=am$. 
+The gamete frequencies from each sex sum to one, $\sum_{i}x_{i}^{\circ}+y_{i}^{\circ}=1$.
+
+Competition then occurs among gametes of the same sex (e.g., among eggs and among sperm separately) according to the genotype at the $\mathbf{A}$ locus ($w_{1}^\circ=w_{3}^\circ=w_{A}^\circ$, $w_{2}^\circ=w_{4}^\circ=w_{a}^\circ$, see Table \ref{tab:fitnesstable}).
+The genotype frequencies after gametic competition are $x_{i}^{\circ,s}= w_{i}^{\circ}x_{i}^{\circ}/\bar{w}_{H}^{\circ}$ and $y_{i}^{\circ,s}= w_{i}^{\circ}y_{i}^{\circ}/\bar{w}_{H}^{\circ}$, where $\bar{w}_{H}^{\circ}=\sum_{i} w_{i}^{\circ}x_{i}^{\circ}+w_{i}^{\circ}y_{i}^{\circ}$ is the mean fitness of male ($\circ=\male$) or female ($\circ=\female$) gametes.
+
+Random mating then occurs between gametes to produce diploid zygotes.
+%To shorten notation we now use index $i$ (and $j$) to denote the alleles at both the $\mathbf{A}$ and $\mathbf{M}$ loci and label $MA=1$, $Ma=2$, $mA=3$, and $ma=4$, such that $i,j\in\{1,2,3,4\}$.
+The frequencies of XX zygotes are then denoted as $xx_{ij}$, XY zygotes as $xy_{ij}$, and YY zygotes as $yy_{ij}$, where $\mathbf{A}$ and $\mathbf{M}$ locus genotypes are given by $i,j\in\{1,2,3,4\}$, as above.
+In XY zygotes, the haplotype inherited from an X-bearing gamete is given by $i$ and the haplotype from a Y-bearing gamete is given by $j$. 
+In XX and YY zygotes, individuals with diploid genotype $ij$ are equivalent to those with diploid genotype $ji$; for simplicity, we use $xx_{ij}$ and $yy_{ij}$ with $i\neq j$ to denote the average of these frequencies, $xx_{ij}=(x_{i}^{\female,s}x_{j}^{\male,s}+x_{j}^{\female,s}x_{i}^{\male,s})/2$ and $yy_{ij}=(y_{i}^{\female,s}y_{j}^{\male,s}+y_{j}^{\female,s}y_{i}^{\male,s})/2$.
+
+Denoting the $\mathbf{M}$ locus genotype by $b \in \{MM, Mm, mm\}$ and the $\mathbf{X}$ locus genotype by $c \in \{XX, XY, YY\}$, zygotes develop as females with probability $k_{bc}$. 
+Therefore, the frequencies of XX females are given by $xx_{ij}^{\female}=k_{bc}xx_{ij}$, XY females are given by $xy_{ij}^{\female}=k_{bc}xy_{ij}$, and YY females are given by $yy_{ij}^{\female}=k_{bc}yy_{ij}$.
+Similarly, XX male frequencies are $xx_{ij}^{\male}=(1-k_{bc})xx_{ij}$, XY male frequencies are $xy_{ij}^{\male}=(1-k_{bc})xy_{ij}$, and YY males frequencies are $yy_{ij}^{\male}=(1-k_{bc})yy_{ij}$.
+This notation allows both the ancestral and novel sex-determining regions to determine zygotic sex according to an XY system, a ZW system, or an environmental sex-determining system. 
+In addition, we can consider any epistatic dominance relationship between the two sex-determining loci. 
+Here, we assume that the ancestral sex-determining system ($\mathbf{X}$ locus) is XY ($k_{MMXX}=1$ and $k_{MMXY}=k_{MMYY}=0$) or ZW ($k_{MMZZ}=0$ and $k_{MMZW}=k_{MMWW}=1$) and epistatically recessive to a dominant novel sex-determining locus, $\mathbf{M}$ ($k_{Mmc}=k_{mmc}=k$).
+
+Selection among diploids then occurs according to the diploid genotype at the $\mathbf{A}$ locus, $l \in \{AA, Aa, aa\}$, for an individual of type $ij$ (see Table \ref{tab:fitnesstable}). 
+The diploid frequencies after selection in sex $\circ$ are given by $xx_{ij}^{\circ,s}=w_{l}^{\circ} xx_{ij}/\bar{w}^{\circ}_{D}$, $xy_{ij}^{\circ,s}=w_{l}^{\circ} xy_{ij}/\bar{w}^{\circ}_{D}$, and $yy_{ij}^{\circ,s}=w_{l}^{\circ} yy_{ij}/\bar{w}^{\circ}_{D}$, where $\bar{w}^{\circ}_{D}= \sum_{i=1}^{4}\sum_{j=1}^{4}w_{l}^{\circ}xx_{ij}+w_{l}^{\circ}xy_{ij}+w_{l}^{\circ}yy_{ij}$ is the mean fitness of diploids of sex $\circ$.
+
+Finally, these diploids undergo meiosis to produce the next generation of gametes. 
+Recombination and sex-specific meiotic drive occur during meiosis.
+%We can also assume that recombination is sex specific and/or affected by the M locus - but generally we don't so I just describe $R=R_{f}=R, r_{MM,d}=r_{Mm,d}=r_{mm,d}=r, \chi_{m}=\chi_{f}=\chi$.
+Here, we allow any relative locations for the $\mathbf{X}$, $\mathbf{A}$, and $\mathbf{M}$ loci by using three parameters to describe the recombination rates between them. 
+$R$ is the recombination rate between the $\mathbf{A}$ and $\mathbf{M}$ loci, $\rho$ is the recombination rate between the $\mathbf{M}$ and $\mathbf{X}$ loci, and $r$ is the recombination rate between the $\mathbf{A}$ and $\mathbf{X}$ loci (Fig \ref{fig:model_outline}).
+Table \ref{tab:chisubstitutions} shows replacements that can be made for each possible ordering of the loci assuming that there is no cross-over interference.
+During meiosis in sex $\circ$, meiotic drive occurs such that, in $Aa$ heterozygotes, a fraction $\alpha^{\circ}$ of gametes produced carry the $A$ allele and $(1-\alpha^\circ)$ carry the $a$ allele.
+
+Among gametes from sex $\circ$, the frequencies of haplotypes (before gametic competition) in the next generation are given by
+
+\begingroup
+\allowdisplaybreaks
+\begin{subequations}
+\begin{align}
+%
+\begin{split}
+x_{1}^{{\circ}'}=&xx_{11}^{\circ,s}+xx_{13}^{\circ,s}/2+(xx_{12}^{\circ,s}+xx_{14}^{\circ,s})\alpha^\circ\\
+&-R(xx_{14}^{\circ,s}-xx_{23}^{\circ,s}) \alpha^\circ\\
+&+(xy_{11}^{\circ,s}+xy_{13}^{\circ,s})/2+(xy_{12}^{\circ,s}+xy_{14}^{\circ,s})\alpha^\circ\\
+&- r(xy_{12}^{\circ,s}-xy_{21}^{\circ,s})\alpha^\circ - \rho(xy_{13}^{\circ,s}-xy_{31}^{\circ,s})/2\\
+&+\big{[}-(R+r+\rho)xy_{14}^{\circ,s} +(R+\rho-r)xy_{41}^{\circ,s}\\
+&+(R+r-\rho) xy_{23}^{\circ,s}+(R+\rho-r)xy_{32}^{\circ,s}\big{]}\alpha^\circ/2
+\end{split}
+\\
+%
+\begin{split}
+x_{2}^{{\circ}'}=&xx_{22}^{\circ,s}+xx_{24}^{\circ,s}/2+(xx_{12}^{\circ,s}+xx_{23}^{\circ,s})\alpha^\circ\\
+&-R(xx_{23}^{\circ,s}-xx_{14}^{\circ,s}) \alpha^\circ\\
+&(xy_{22}^{\circ,s}+xy_{24}^{\circ,s})/2+(xy_{21}^{\circ,s}+xy_{23}^{\circ,s})(1-\alpha^\circ)\\
+&- r(xy_{21}^{\circ,s}-xy_{12}^{\circ,s})(1-\alpha^\circ) - \rho(xy_{24}^{\circ,s}-xy_{42}^{\circ,s})/2\\
+&+\big{[}-(R+r+\rho)xy_{23}^{\circ,s}+(R+\rho-r)xy_{32}^{\circ,s}\\
+&+(R+r-\rho) xy_{14}^{\circ,s}+(R+\rho-r)xy_{41}^{\circ,s}\big{]}(1-\alpha^\circ)/2
+\end{split}
+\\
+%
+\begin{split}
+x_{3}^{{\circ}'}=&xx_{33}^{\circ,s}+xx_{13}^{\circ,s}/2+(xx_{23}^{\circ,s}+xx_{34}^{\circ,s})\alpha^\circ\\
+&-R(xx_{23}^{\circ,s}-xx_{14}^{\circ,s}) \alpha^\circ\\
+&(xy_{33}^{\circ,s}+xy_{31}^{\circ,s})/2+(xy_{32}^{\circ,s}+xy_{34}^{\circ,s})\alpha^\circ\\
+&- r(xy_{34}^{\circ,s}-xy_{43}^{\circ,s}) \alpha^\circ - \rho(xy_{31}^{\circ,s}-xy_{13}^{\circ,s})/2\\
+&+\big{[}-(R+r+\rho)xy_{32}^{\circ,s} +(R+\rho-r)xy_{23}^{\circ,s}\\
+&+(R+r-\rho) xy_{41}^{\circ,s}+(R+\rho-r)xy_{14}^{\circ,s}\big{]} \alpha^\circ/2
+\end{split}
+\\
+%
+\begin{split}
+x_{4}^{{\circ}'}=&xx_{44}^{\circ,s}+xx_{34}^{\circ,s}/2+(xx_{14}^{\circ,s}+xx_{24}^{\circ,s})\alpha^\circ\\
+&-R(xx_{14}^{\circ,s}-xx_{23}^{\circ,s}) \alpha^\circ\\
+&(xy_{44}^{\circ,s}+xy_{42}^{\circ,s})/2+(xy_{41}^{\circ,s}+xy_{43}^{\circ,s})(1-\alpha^\circ)\\
+&- r(xy_{43}^{\circ,s}-xy_{34}^{\circ,s})(1-\alpha^\circ) - \rho(xy_{42}^{\circ,s}-xy_{24}^{\circ,s})/2\\
+&+\big{[}-(R+r+\rho)xy_{41}^{\circ,s}+(R+\rho-r)xy_{14}^{\circ,s}\\
+&+(R+r-\rho) xy_{32}^{\circ,s}+(R+\rho-r)xy_{23}^{\circ,s}\big{]}(1-\alpha^\circ)/2
+\end{split}
+\\
+\begin{split}
+y_{1}^{{\circ}'}=&yy_{11}^{\circ,s}+yy_{13}^{\circ,s}/2+(yy_{12}^{\circ,s}+yy_{14}^{\circ,s})\alpha^\circ\\
+&-R(yy_{14}^{\circ,s}-yy_{23}^{\circ,s}) \alpha^\circ\\
+&(xy_{11}^{\circ,s}+xy_{31}^{\circ,s})/2+(xy_{21}^{\circ,s}+xy_{41}^{\circ,s})\alpha^\circ\\
+&- r(xy_{21}^{\circ,s}-xy_{12}^{\circ,s})\alpha^\circ - \rho(xy_{31}^{\circ,s}-xy_{13}^{\circ,s})/2\\
+&+\big{[} - (R+r+\rho)xy_{41}^{\circ,s} + (R+\rho-r)xy_{14}^{\circ,s}\\
+& + (R+r-\rho)xy_{32}^{\circ,s} + (R+\rho-r) xy_{23}^{\circ,s}\big{]}\alpha^\circ/2
+\end{split}
+\\
+%
+\begin{split}
+y_{2}^{{\circ}'}=&yy_{22}^{\circ,s}+yy_{24}^{\circ,s}/2+(yy_{12}^{\circ,s}+yy_{23}^{\circ,s})\alpha^\circ\\
+&-R(yy_{23}^{\circ,s}-yy_{14}^{\circ,s}) \alpha^\circ\\
+&(xy_{22}^{\circ,s}+xy_{42}^{\circ,s})/2+(xy_{12}^{\circ,s}+xy_{32}^{\circ,s})(1-\alpha^\circ)\\
+&- r(xy_{12}^{\circ,s}-xy_{21}^{\circ,s})(1-\alpha^\circ) - \rho(xy_{42}^{\circ,s}-xy_{24}^{\circ,s})/2\\
+&+\big{[}-(R+r+\rho)xy_{32}^{\circ,s} +(R+\rho-r) xy_{23}^{\circ,s}\\
+&+(R+r-\rho)xy_{41}^{\circ,s}+(R+\rho-r)xy_{14}^{\circ,s}\big{]}(1-\alpha^\circ)/2
+\end{split}
+\\
+%
+\begin{split}
+y_{3}^{{\circ}'}=&yy_{33}^{\circ,s}+yy_{13}^{\circ,s}/2+(yy_{23}^{\circ,s}+yy_{34}^{\circ,s})\alpha^\circ\\
+&-R(yy_{23}^{\circ,s}-yy_{14}^{\circ,s}) \alpha^\circ\\
+&(xy_{33}^{\circ,s}+xy_{13}^{\circ,s})/2+(xy_{23}^{\circ,s}+xy_{43}^{\circ,s})\alpha^\circ\\
+&- r(xy_{43}^{\circ,s}-xy_{34}^{\circ,s})\alpha^\circ - \rho(xy_{13}^{\circ,s}-xy_{31}^{\circ,s})/2\\
+&+\big{[}-(R+r+\rho)xy_{23}^{\circ,s} +(R+\rho-r)xy_{32}^{\circ,s}\\
+&+(R+r-\rho) xy_{14}^{\circ,s} + (R+\rho-r) xy_{41}^{\circ,s}\big{]}\alpha^\circ/2
+\end{split}
+\\
+%
+\begin{split}
+y_{4}^{{\circ}'}=&yy_{44}^{\circ,s}+yy_{34}^{\circ,s}/2+(yy_{14}^{\circ,s}+yy_{24}^{\circ,s})\alpha^\circ\\
+&-R(yy_{14}^{\circ,s}-yy_{23}^{\circ,s}) \alpha^\circ\\
+&(xy_{44}^{\circ,s}+xy_{24}^{\circ,s})/2+(xy_{14}^{\circ,s}+xy_{34}^{\circ,s})(1-\alpha^\circ)\\
+&- r(xy_{34}^{\circ,s}-xy_{43}^{\circ,s})(1-\alpha^\circ) - \rho(xy_{24}^{\circ,s}-xy_{42}^{\circ,s})/2\\
+&+\big{[}-(R+r+\rho) xy_{14}^{\circ,s} + (R+\rho-r)xy_{41}^{\circ,s}\\
+&+(R+r-\rho) xy_{23}^{\circ,s} + (R+\rho-r) xy_{32}^{\circ,s}\big{]}(1-\alpha^\circ)/2.
+\end{split}
+\end{align}
+\label{eq:recursions}
+\end{subequations}
+
+\endgroup
+
+\noindent
+The full system is therefore described by 16 recurrence equations (three diallelic loci in two sexes, $2^3 \times 2 = 16$). 
+However, not all diploid types are produced under certain sex-determining systems. 
+For example, with the $M$ allele fixed and an ancestral XY sex-determining system, there are XX females and XY males ($x_{3}^\circ=x_{4}^\circ=y_{3}^\male=y_{4}^\male=y_{i}^\female=0,\;\forall\; i$). 
+%($xx_{11}^{\male}=xx_{12}^{\male}=xx_{22}^\male=xy_{11}^{\female}=xy_{12}^{\female}=xy_{21}^{\female}=xy_{22}^\female=yy_{11}^{\female}=yy_{12}^{\female}=yy_{22}^\female=0$). 
+In this case, the system only involves six recursion equations, %because there is only one $\mathbf{M}$ locus allele and no Y-bearing female gametes. 
+which we assume below to calculate the equilibria.
+
+%\newpage
+
+\setcounter{equation}{0}
+\renewcommand{\theequation}{S2.\arabic{equation}}
+
+\section*{S2 Appendix}
+\label{app:eq_stab}
+
+\subsection*{Resident equilibria and stability}
+
+In the resident population (allele $M$ fixed), we follow the frequency of $A$ in X-bearing female gametes, $p^\female_X$, and X-bearing male gametes, $p^\male_X$, and Y-bearing male gametes, $p^\male_Y$.
+We also track the total frequency of Y among male gametes, $q$, which may deviate from $1/2$ due to meiotic drive in males. 
+These four variables determine the frequencies of the six resident gamete types, which sum to one in each sex: $x_{1}^{\female}=\hat{p}_X^\female$, $x_{2}^{\female}=1-\hat{p}_X^\female$, $x_{1}^{\male}=(1-q)\hat{p}_X^\male$, $x_{2}^{\male}=(1-q)(1-\hat{p}_X^\male)$, $y_{1}^{\male}=q \hat{p}_Y^\male$, and $y_{2}^{\male}=q(1-\hat{p}_Y^\male)$.
+Mean fitnesses in the resident population are given in Table \ref{tab:meanfitnesses}.
+
+Various forms of selection can maintain a polymorphism at the $\mathbf{A}$ locus, including sexually antagonistic selection, overdominance, conflicts between diploid selection and selection upon haploid genotypes (ploidally-antagonsitic selection,~\cite{Immler:2012tl}), or a combination of these selective regimes (see below).
+
+In particular special cases, e.g., no sex-differences in selection or meiotic drive ($s^\male=s^\female$, $h^\male=h^\female$, and $\alpha^\male=\alpha^\female=1/2$), the equilibrium allele frequency and stability can be calculated analytically without assuming anything about the relative strengths of selection and recombination.
+However, here, we focus on two regimes (tight linkage between $\mathbf{A}$ and $\mathbf{X}$ and weak selection) in order to make fewer assumptions about fitnesses.
+
+\subsubsection*{Tight linkage between $\mathbf{X}$ and $\mathbf{A}$ loci}
+
+We first calculate the equilibria in the ancestral population when the recombination rate between the $\mathbf{X}$ and $\mathbf{A}$ loci is small ($r$ of order $\epsilon$). 
+Selection at the $\mathbf{A}$ locus will not affect evolution at the novel sex-determining locus, $\mathbf{M}$, if one allele is fixed on all backgrounds. 
+We therefore focus on the five equilibria that maintain both $A$ and $a$ alleles, four of which are given to leading order by:
+
+\begin{subequations}\label{eq:tightequil}
+\begin{align}
+(A)\ \ \ &\hat{p}_{Y}^{\male}=0,
+\ \hat{q}=\frac{1}{2}\left(1 - \alpha_\Delta^\male \frac{ w_{Aa}^{\male} \phi}{w_{Aa}^{\male} \phi+ w_{aa}^{\male} \psi}\right),\\
+&\hat{p}_{X}^{\female}=\frac{w_{a}^{\female} \phi}{w_{a}^{\female} \phi+ w_{A}^{\female} \psi},
+\ \hat{p}_{X}^{\male}=\frac{(1+\alpha_\Delta^\male)w_{Aa}^{\male} \phi}{(1+\alpha_\Delta^\male)w_{Aa}^{\male} \phi +w_{aa}^{\male} \psi} \nonumber \\
+(A')\ \ \ &\hat{p}_{Y}^{\male}=1,
+\ \hat{q}=\frac{1}{2}\left(1 + \alpha_\Delta^\male \frac{w_{Aa}^{\male} \phi'}{w_{Aa}^{\male} \phi' + w_{AA}^{\male} \psi'}\right),\\
+&\hat{p}_{X}^{\female}=1-\frac{w_{A}^{\female} \phi'}{w_{A}^{\female} \phi'+ w_{a}^{\female} \psi'},
+\ \hat{p}_{X}^{\male}=1-\frac{(1-\alpha_\Delta^\male)w_{Aa}^{\male} \phi'}{(1-\alpha_\Delta^\male)w_{Aa}^{\male} \phi'+w_{AA}^{\male} \psi'} \nonumber \\
+(B)\ \ \ &\hat{p}_{Y}^{\male}=0,\ \hat{p}_{X}^{\female}=1,\ \hat{p}_{X}^{\male}=1, \ \hat{q}=(1 -\alpha^\male_\Delta)/2\\
+(B')\ \ \ &\hat{p}_{Y}^{\male}=1,\ \hat{p}_{X}^{\female}=0,\ \hat{p}_{X}^{\male}=0, \ \hat{q}=(1+\alpha^\male_\Delta)/2
+\end{align}
+\end{subequations}
+\begin{equation*}
+\begin{split}
+\phi=&(1+\alpha^\female_\Delta) w_{A}^{\female} w_{Aa}^{\female} \left[ w_{a}^{\male} w_{aa}^{\male} + (1+\alpha_\Delta^\male) w_{A}^{\male} w_{Aa}^{\male} \right]/2 - w_{a}^{\male} w_{a}^{\female} w_{aa}^{\male} w_{aa}^{\female} \\
+\psi=&(1-\alpha^\female_\Delta) w_{a}^{\female} w_{Aa}^{\female} \left[ w_{a}^{\male} w_{aa}^{\male} + (1+\alpha_\Delta^\male) w_{A}^{\male} w_{Aa}^{\male}\right]/2 - (1+\alpha_\Delta^\male) w_{A}^{\male} w_{A}^{\female} w_{Aa}^{\male} w_{AA}^{\female}\\
+\phi'=&(1-\alpha^\female_\Delta) w_{a}^{\female} w_{Aa}^{\female} \left[ w_{A}^{\male} w_{AA}^{\male} + (1-\alpha_\Delta^\male) w_{a}^{\male} w_{Aa}^{\male} \right]/2 - w_{A}^{\male} w_{A}^{\female} w_{AA}^{\male} w_{AA}^{\female}\\
+\psi'=&(1+\alpha^\female_\Delta) w_{A}^{\female} w_{Aa}^{\female} \left[ w_{A}^{\male} w_{AA}^{\male} + (1-\alpha_\Delta^\male) w_{a}^{\male} w_{Aa}^{\male} \right]/2 - (1-\alpha_\Delta^\male) w_{a}^{\male} w_{a}^{\female} w_{Aa}^{\male} w_{aa}^{\female}.
+\end{split}
+\end{equation*}
+
+\noindent
+A fifth equilibrium $(C)$ also exists where $A$ is present at an intermediate frequency on the Y background ($0<\hat{p}_{Y}^{\male}<1$). 
+However, equilibrium $(C)$ is never locally stable when $r \approx 0$ and is therefore not considered further.
+Thus, the Y background can either be fixed for the $a$ allele (equilibria ($A$) and ($B$)) or the $A$ allele (equilibria ($A'$) and ($B'$)).
+The X background can then either be polymorphic (equilibria ($A$) and ($A'$)) or fixed for the alternative allele (equilibria ($B$) and ($B'$)).
+Since equilibria $(A)$ and $(B)$ are equivalent to equilibria $(A')$ and $(B')$ with the labelling of $A$ and $a$ alleles interchanged, we discuss only equilibria $(A)$ and $(B)$, in which the Y background is fixed for the $a$ allele.
+If there is no haploid selection ($\alpha^{\circ}_\Delta=0$, $w_{A}^{\circ}=w_{a}^{\circ}=1$), these equilibria are equivalent to those found by~\cite{Lloyd1977} and~\cite{Otto2014}.
+
+We next calculate when equilibria $(A)$ and $(B)$ are locally stable for $r=0$. 
+According to the `small parameter theory'~\cite{Karlin:1972ab,Karlin:1972dq}, these stability properties are unaffected by small amounts of recombination between the sex-determining locus and the $\mathbf{A}$ locus, although equilibrium frequencies may be slightly altered.
+For the $a$ allele to be stably fixed on the Y background we need $\bar{w}_{Ya}^{\male} > \bar{w}_{YA}^{\male}$ where $\bar{w}_{Ya}^{\male} = w_{a}^{\male} \big[\hat{p}_X^\female(1-\alpha^\male_\Delta) w_{A}^{\female} w_{Aa}^{\male} + (1-\hat{p}_X^\female)w_{a}^{\female} w_{aa}^{\male} \big]$ and $\bar{w}_{YA}^{\male} = w_{A}^{\male} \big[ \hat{p}_X^\female w_{A}^{\female} w_{AA}^{\male} + (1-\hat{p}_X^\female)(1+\alpha^\male_\Delta) w_{a}^{\female} w_{Aa}^{\male} \big]$.
+That is, Y-$a$ haplotypes must have higher fitness than Y-$A$ haplotypes.  
+Substituting in $\hat{p}_X^\female$ from Eq \eqref{eq:tightequil}, fixation of the $a$ allele on the Y background requires that $\gamma_{i}>0$ where $\gamma_{(A)}=w_{a}^{\male} \big[ (1-\alpha^\male_\Delta) w_{Aa}^{\male} \phi + w_{aa}^{\male} \psi \big]-w_{A}^{\male} \big[ w_{AA}^{\male} \phi + (1 + \alpha^{\male}_\Delta)w_{Aa}^{\male} \psi \big]$ for equilibrium $(A)$ and $\gamma_{(B)}=(1-\alpha^{\male}_\Delta)w_{a}^{\male}w_{Aa}^{\male}-w_{A}^{\male}w_{AA}^{\male}$ for equilibrium $(B)$.
+Stability of a polymorphism on the X background (equilibrium $(A)$) further requires that $\phi >0$ and $\psi >0$. 
+Fixation of the $a$ allele on the X background (equilibrium $(B)$) can be stable only if equilibrium $(A)$ is not, as it requires $\psi<0$.
+%and $2w_{A}^{\female}w_{AA}^{\female}>(1-\alpha_\Delta^{\female})w_{a}^{\female}w_{Aa}^{\female}$ or just $4w_{A}^{\female}w_{AA}^{\female}<(1-\alpha_\Delta^{\female})w_{a}^{\female}w_{Aa}^{\female}$ (which also prevents $\psi>0$).
+
+%\textcolor{red}{check last condition and the stability condition below are correct}
+%\textcolor{blue}{The last condition looks good to me, although in your Turnover-norec-MFS.nb you look at YA fixed, so you have to flip everything (so I made Turnover-norec-MFS-MMO.nb to do this).
+%The one issue I can find here is that you can also prevent $\Lambda>1$ when the slope and intercept of the quadratic at $\Lambda=1$ are negative (you only looked at both being positive).
+In this case we need $4w_{A}^{\female}w_{AA}^{\female}<(1-\alpha_\Delta^{\female})w_{a}^{\female}w_{Aa}^{\female}$, which also prevents $\psi>0$.
+%I've added this in.
+%It could also be the case that the slope and intercept are the same sign but the roots are imaginary - but this is never the case here.
+%Stability condition below looks good to me (from matt version of turnoverSOM-MIKE.nb).}
+
+\subsubsection*{Selection weak relative to recombination}
+
+Here, we assume that selection is weak relative to recombination ($s^\circ$, $t^\circ$, $\alpha_{\Delta}^\circ$ of order $\epsilon$). 
+The maintenance of a polymorphism at the $\mathbf{A}$ locus then requires that
+
+\begin{equation}
+\begin{split}
+0&< - \left[(1-h^\female)s^\female +(1-h^\male) s^\male + t^\female +t^\male + \alpha_{\Delta}^\female+\alpha_{\Delta}^\male\right]\\
+%
+\text{and }\quad 0&<h^\female s^\female +h^\male s^\male + t^\female +t^\male + \alpha_{\Delta}^\female+\alpha_{\Delta}^\male.
+\end{split}
+\end{equation}
+
+\noindent
+which indicates that a polymorphism can be maintained by various selective regimes.
+
+Given that a polymorphism is maintained at the $\mathbf{A}$ locus by weak selection, the frequencies of $A$ in each type of gamete are the same ($\hat{p}^\female_X=\hat{p}^\male_X=\hat{p}^\male_Y=\bar{p}$) and given, to leading order, by
+
+\begin{equation}
+\bar{p}=\frac{h^\female s^\female + h^\male s^\male +t^\female+t^\male+\alpha_{\Delta}^\female+\alpha_{\Delta}^\male}
+{(2h^\female-1)s^\female+(2h^\male-1)s^\male}
++O(\epsilon)
+.
+\label{eq:pAve}
+\end{equation}
+
+\noindent
+Differences in frequency between gamete types are of $O(\epsilon)$:
+
+\begin{equation}
+\begin{split}
+\hat{p}^\male_X-\hat{p}^\female_X&=V_{A}\big{(}D^\male - D^\female +\alpha_{\Delta}^\male-\alpha_{\Delta}^\female \big{)}
++O(\epsilon^2)\\
+%
+\hat{p}^\male_Y-\hat{p}^\female_X&=V_{A}\left[D^\male - D^\female+\alpha_{\Delta}^\male-\alpha_{\Delta}^\female+(1-2r)(t^\male-t^\female)\right]/2r
++O(\epsilon^2)\\
+%
+\hat{p}^\male_Y-\hat{p}^\male_X&=V_{A}\left(D^\male - D^\female+\alpha_{\Delta}^\male-\alpha_{\Delta}^\female+t^\male-t^\female\right)(1-2r)/2r
++O(\epsilon^2),
+\end{split}
+\label{eq:freq_diffs}
+\end{equation}
+
+\noindent
+where $V_{A}=\bar{p}(1-\bar{p})$ is the variance in the frequency of $A$ and $D^\circ=\big{[} \bar{p}s^\circ+(1-\bar{p})h^\circ s^\circ\big{]} -\big{[} \bar{p}h^\circ s^\circ+(1-\bar{p}) \big{]}$ corresponds to the difference in fitness between $A$ and $a$ alleles in diploids of sex $\circ \in \{\female,\male\}$.
+The frequency of Y-bearing male gametes depends upon the difference in the frequency of the $A$ allele between X- and Y-bearing male gametes and the strength of meiotic drive in favour of the $A$ allele in males, $q=1/2+\alpha_{\Delta}^\male(\hat{p}^\male_Y-\hat{p}^\male_X)/2+O(\epsilon^3)$.
+Without gametic competition or drive ($\alpha_{\Delta}^\circ=t^\circ=0$) our results reduce to those of~\cite{vanDoorn:2007eu}.
+
+%\newpage
+
+\setcounter{equation}{0}
+\renewcommand{\theequation}{S3.\arabic{equation}}
+
+\section*{S3 Appendix}
+\label{app:inv_cond}
+
+\subsection*{Invasion conditions}
+
+A rare sex-determining allele, $m$, will spread in an XY sex-determining system when the leading eigenvalue, $\lambda_m^{(XY)}$, of the Jacobian matrix derived from the eight mutant recursion equations (given by \ref{eq:recursions}c,d,g,h), evaluated at the ancestral equilibrium, is greater than one.
+Because a neo-Y (neo-W) is always in males (females) and is epistatically dominant to the ancestral sex-determining locus, the characteristic polynomial factors into two quadratics times $(\lambda_m^{(XY)})^4$, which greatly simplifies analysis.
+One quadratic governs the change in the frequency of the new sex determination factor associated with the $A$ and $a$ allele frequencies, summing across backgrounds at the old sex-determining locus (i.e., summing haplotypes bearing the original X and Y alleles).
+%It is the largest root of this quadratic that determines the spread of the new $m$ allele (see details in \nameref{file:Mathematica}).  
+The second quadratic describes the dynamics of the difference in the $m$-$A$ and $m$-$a$ haplotypes between X and Y backgrounds.  
+Asymptotically, this difference is constrained to grow at a rate equal to or less than the sum while the $m$ allele is rare, because the frequencies can never become negative. 
+We therefore focus on the leading eigenvalue, $\lambda_m^{(XY)}$, which is the largest root of the quadratic $f(x) = x^2+ b x + c = 0$,  where $b= - (\Lambda_{mA}^{(XY)} + \Lambda_{ma}^{(XY)})+(\chi_{mA}^{(XY)} + \chi_{ma}^{(XY)})$ and $c = (\Lambda_{mA}^{(XY)} - \chi_{mA}^{(XY)}) (\Lambda_{ma}^{(XY)} - \chi_{ma}^{(XY)}) - \chi_{mA}^{(XY)} \chi_{ma}^{(XY)}$ (details in \nameref{file:Mathematica}), see Table \ref{tab:haplotype_growth}.
+
+When $R=0$ the two roots are $\Lambda_{mA}^{(XY)}$ and $\Lambda_{ma}^{(XY)}$, and the leading eigenvalue is the larger of the two.
+When $R>0$ then $f(\Lambda_{mA}^{(XY)})$ and $f(\Lambda_{ma}^{(XY)})$ are of opposite signs, and the leading eigenvalue must fall between these two quantities (details in \nameref{file:Mathematica}).
+%(the Perron-Frobenius theorem guarantees that the largest eigenvalue is positive, unique, and real).
+Thus, $\lambda_m^{(XY)}>1$ if both $\Lambda_{mA}^{(XY)}>1$ and $\Lambda_{ma}^{(XY)}>1$; similarly, $\lambda_m^{(XY)}<1$ if both $\Lambda_{mA}^{(XY)}<1$ and $\Lambda_{ma}^{(XY)}<1$.
+If only one haplotypic growth rate is greater than one ($\Lambda_{ma}^{(XY)}<1<\Lambda_{mA}^{(XY)}$ or $\Lambda_{mA}^{(XY)}<1<\Lambda_{ma}^{(XY)}$), then $\lambda_m^{(XY)}$ is greater than one when condition \eqref{eq:lambdasGen} is met.
+Thus, the invasion of a new sex-determining allele is determined by the haplotypic growth rates ($\Lambda_{mj}^{(XY)}$ terms), which do not account for loss due to recombination, and the dissociative force that breaks apart these haplotypes by recombination ($\chi_{mj}^{(XY)}$).
+For tight linkage between the ancestral sex-determining locus ($\mathbf{X}$) and the selected locus ($\mathbf{A}$) we can calculate these terms explicitly (see below).
+For weak selection we approximate the leading eigenvalue with a Taylor series. 
+The leading eigenvalue for any $k$ is given up to order $\epsilon^2$ by Eq \eqref{eq:lambda_ESD_k}.
+
+\subsubsection*{Tight linkage between $\mathbf{A}$ and $\mathbf{X}$ ($r \approx 0$)}
+
+Here, we explore the conditions under which a neo-W invades an XY system assuming that the $\mathbf{A}$ locus is initially in tight linkage with the ancestral sex-determining locus ($r \approx 0$). 
+We disregard neo-Y mutations, which never spread given that the ancestral population is at a stable equilibrium (see \nameref{file:Mathematica} for proof).
+
+Starting with the simpler $(B)$ equilibrium, the haplotypic growth rates ($\Lambda_{mi}^{(XY)}$) and dissociative forces ($\chi_{mi}^{(XY)}$) are
+
+\begin{subequations}\label{Binvasion}
+\begin{align}
+\Lambda_{W'A}^{(XY)}&= {\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]}^{-1}
+\frac{w_{A}^\female }{w_{A}^\female}
+\frac{\left[ w_{A}^\male (1+\alpha^\male_\Delta) w_{AA}^\female + 
+w_{a}^\male (1-\alpha^\male_\Delta) w_{Aa}^\female (1+\alpha^\female_\Delta) \right]}
+{ 2w_{AA}^\female } \\
+\Lambda_{W'a}^{(XY)}&= {\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]}^{-1}
+\frac{w_{a}^\female}{w_{A}^\female}
+\frac{\left[  w_{A}^\male (1+\alpha^\male_\Delta) w_{Aa}^\female (1-\alpha^\female_\Delta)+
+w_{a}^\male (1-\alpha^\male_\Delta) w_{aa}^\female \right]}
+{ 2w_{AA}^\female } \\
+\chi_{W'A}^{(XY)}&= \frac{1}{2} {\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]}^{-1}
+\frac{w_{A}^\female }{w_{A}^\female}
+ \frac{\left[  w_{a}^\male (1-\alpha^\male_\Delta) w_{Aa}^\female (1 + \alpha^\female_\Delta) \right]}
+{ w_{AA}^\female } \frac{R}{2}\\
+\chi_{W'a}^{(XY)}&= \frac{1}{2} {\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]}^{-1}
+\frac{w_{a}^\female}{w_{A}^\female}
+ \frac{\left[  w_{A}^\male (1+\alpha^\male_\Delta) w_{Aa}^\female (1-\alpha^\female_\Delta) \right]}
+{  w_{AA}^\female} \frac{R}{2}.
+\end{align}
+\end{subequations}
+
+%\noindent
+%In this case, the zygotic sex ratio ($\zeta$) is given by the difference in haploid selection in males on $a$ (fixed on the Y) and $A$ (fixed on the X) alleles, i.e., there are more males than females if $\zeta = \alpha^\male w_A^\male / [(1-\alpha^\male)w_a^\male + \alpha^\male w_A^\male]<1/2$.
+%$\alpha^\male<1/2$ and/or $w_{a}^\male>w_{A}^\male$.
+%Populations with haploid selection for $a$ in males have a male biased zygotic sex ratio are thus more permissive to invasion by a neo-W ($\Lambda_{mA}$ and $\Lambda_{ma}$ larger).
+%%In addition, the spread of neo-W alleles depends on the fitness of female diploids after mating with an X-$A$ or Y-$a$ male gamete, relative to the fitness of females in the population (all have genotype $AA$ and fitness $w_{AA}^\female$ at this equilibrium).
+%Haploid selection in males has a second effect; the spread rate of neo-W haplotypes is determined by their fitness in diploid females, which depends on their diploid genotype and thus on the male gamete they pair with.
+%Zygotes carrying dominant neo-W alleles will develop as females regardless of their genotype at the XY locus. 
+%Therefore, neo-W females result from matings with either X-$A$ or Y-$a$ male gametes. 
+%The relative proportion of these male gametes is determined by haploid selection in males; mating with a Y-$a$ male gamete is more likely if the $a$ allele is favoured during male gamete production or competition ($\zeta<1/2$).
+%Thus, neo-W females experience different diploid selection than XX females, and the extent of this difference depends on haploid selection in males.
+%Furthermore, haploid selection in females can directly select upon neo-W-$A$ or neo-W-$a$ haplotypes. 
+%A neo-W-$A$ female gamete has the same fitness during haploid competition as resident $A$-bearing female gametes. 
+%On the other hand, neo-W-$a$ female gametes can be favoured or disfavoured during female haploid competition (favoured if $w_{a}^\female>w_{A}^\female$). 
+%Meiotic drive in females ($\alpha^\female$) similarly affects the fitness of these neo-W haplotypes, except that it impacts both haplotypes as meiotic drive only occurs in heterozygotes and therefore does not occur in resident XX females (who are always homozygote $AA$).
+
+Haploid selection impacts the spread of neo-W haplotypes in three ways (also seen in Table \ref{tab:haplotype_growth}).
+Firstly, the zygotic sex ratio becomes male biased, $\zeta>1/2$, when the $a$ allele (which is fixed on the Y) is favoured during competition among male gametes or by meiotic drive in males.
+Specifically, at equilibrium $(B)$, female zygote frequency is $1 - \zeta = w_A^\male (1+\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$ where $2\bar{w}_{H}^\male= \big[w_a^\male (1-\alpha^\male_\Delta) +  w_A^\male (1+\alpha^\male_\Delta) \big]$ has been canceled out in equations \eqref{Binvasion} to leave the term ${\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]}^{-1}$.
+Male biased sex ratios facilitate the spread of a neo-W because neo-W alleles cause the zygotes that carry them to develop as the rarer, female, sex.
+
+Secondly, haploid selection in females selects on neo-W haplotypes directly.
+At equilibrium $(B)$, the fitness of female gametes under the ancestral sex-determining system is $w_{A}^\female$ such that the relative fitnesses of neo-W-$A$ and neo-W-$a$ haplotypes during female gametic competition are $w_{A}^\female/w_{A}^\female$ and $w_{a}^\female/w_{A}^\female$ (see terms in equation \ref{Binvasion}).
+Meiotic drive in females will also change the proportion of gametes that carry the $A$ versus $a$ alleles, which will be produced by heterozygous females in proportions $(1+\alpha_{\Delta}^\female)/2$ and $(1-\alpha_{\Delta}^\female)/2$, respectively.
+These terms are only associated with heterozygous females, i.e., they are found alongside $w_{Aa}^\female$.
+
+Thirdly, haploid selection in males affects the diploid genotypes of females by altering the allele frequencies in the male gametes with which female gametes pair.
+At equlibrium $(B)$, neo-W female gametes will mate with X-$A$ male gametes with probability $ w_A^\male (1+\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$ and Y-$a$ male gametes with probability $w_a^\male (1-\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$, where the $2\bar{w}_{H}^\male$ terms have been canceled in Eq \eqref{Binvasion} (as mentioned above).
+Thus, neo-W-$A$ haplotypes are found in $AA$ female diploids with probability $ w_A^\male (1+\alpha^\male_\Delta)/ (2\bar{w}_{H}^\male)$ (e.g., first term in square brackets in the numerator of equation \ref{Binvasion}a) and in $Aa$ female diploids with probability $w_a^\male (1-\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$ (e.g., the second term in square brackets in the numerator of equation \ref{Binvasion}a).
+
+%For instance, because an epistatically dominant neo-W always causes its carrier to become female, it creates females who carry either Y-$a$ or X-$A$ genotypes from their father.
+%Thus, because when there is a polymorphism the X carries some non-zero frequency of $A$, haploid selection in males impacts the diploid genotypes of females (e.g., creating more $Aa$ females when drive in males favours Y-$a$).
+%How this affects the spread of the neo-W then depends on diploid and haploid selection in females.
+
+The other terms in equations \eqref{Binvasion} are more easily interpreted if we assume that there is no haploid selection in either sex, in which case $\Lambda_{W'A}^{(XY)}=(w_{AA}^\female+w_{Aa}^\female)/2 w_{AA}^\female$ and $\Lambda_{W'a}^{(XY)}=(w_{aa}^\female+w_{Aa}^\female)/ 2 w_{AA}^\female$.
+Neither haplotype can spread under purely sexually-antagonistic selection at equilibrium $(B)$, with directional selection in each sex.
+Essentially, the X is then already as specialized as possible for the female beneficial allele ($A$ is fixed on the X background), and the neo-W often makes daughters with the Y-$a$ haplotype, increasing the flow of $a$ alleles into females, which reduces the fitness of those females.
+
+If selection doesn't uniformly favour $A$ in females, however, neo-W-$A$ haplotypes and/or neo-W-$a$ haplotypes can spread ($\Lambda_{W'A}^{(XY)}>1$ and/or $\Lambda_{W'a}^{(XY)}>1$).
+%If $\Lambda_{mA}>1$ (requiring $w_{Aa}^\female>w_{AA}^\female$), the implication is that the neo-W can spread alongside the $A$ allele, despite the fact that the neo-W sometimes brings $Y-a$ haplotypes into females, because $a$ is favoured by selection in females despite $A$ being fixed on the X.
+A neo-W-$A$ haplotype can spread ($\Lambda_{W'A}^{(XY)}>1$) when $w_{Aa}^\female>w_{AA}^\female$, despite the fact that a neo-W brings Y-$a$ haplotypes into females.
+In this case the $a$ allele is favoured by selection in females despite $A$ being fixed on the X background.
+For this equilibrium to be stable (i.e.,  to keep $A$ fixed on the X), X-$a$ cannot be overly favoured in females and X-$A$ must be sufficiently favoured in males (for example, by overdominance in males).
+Specifically, from the stability conditions for equilibrium (B), we must have $w_{Aa}^\female < 2 w_{AA}^\female$ and $w_{Aa}^\male/\big[(w_{aa}^\male+w_{Aa}^\male)/2\big]>w_{Aa}^\female/w_{AA}^\female$.
+
+Still considering $w_{Aa}^\female>w_{AA}^\female$, the neo-W can also spread alongside the $a$ allele ($\Lambda_{W'a}^{(XY)}>1$) if $w_{aa}^\female$ is large enough such that $(w_{Aa}^\female+w_{aa}^\female)/2>w_{AA}^\female$.
+%there is sufficiently strong underdominance in females ($w_{aa}^\female>w_{Aa}^\female$) \textcolor{blue}{[this is describing directional selection, not overdominance - check the conditions for the case we want to talk about]}, such that $(w_{Aa}^\female+w_{aa}^\female)/2>w_{AA}^\female$.
+This can occur with overdominance or directional selection for $a$ in females (Fig \ref{fig:regionplots}B,C).
+In this case, $a$ is favoured on the ancestral Y background in males and on the ancestral X background in females (comparing $Aa$ to $AA$ genotypes in females) but $A$ is fixed on the X background due to selection in males.
+The neo-W-$a$ haplotype can spread because it produces females with higher fitness $Aa$ and $aa$ genotypes.
+
+%When both haplotypes can spread on their own ($\Lambda_{mA}>1$ and $\Lambda_{ma}>1$), the neo-W invades regardless the recombination rate between it and the selected locus, $R$.
+%When neither haplotype can spread ($\Lambda_{mA}<1$ and $\Lambda_{ma}<1$) the neo-W can never invade.
+%And when only one haplotype can spread on its own the neo-W invades only when the rate of recombination onto the favourable background is sufficiently larger than the rate of recombination off this background (i.e., equation\ref{eq:lambdasGen} is satisfied).
+
+%Haploid selection affects the conclusions outlined above by altering the zygotic sex ratio and exerting direct selection on neo-W haplotypes.
+%The effect of sex ratio selection is straightforward and can be seen in Eq \eqref{Binvasion}, where male drive and gamete competition for $a$ (which is fixed on the Y and therefore causes a male bias) increases all four terms.
+%Direct selection on neo-W haplotypes can also be seen in Eq \eqref{Binvasion} by noticing that increasing female drive in favour of $A$ increases the neo-W-$A$ haplotype growth rate ($\Lambda_{mA}$) while female drive and gamete competition in favour of $a$ increases the neo-W-$a$ haplotype growth rate ($\Lambda_{ma}$).
+%Gamete competition in females does not impact the spread of neo-W-$A$ haplotypes because they are on the same background as the resident X.
+%Recombination between the selected locus and the neo-W complicates things slightly, as selective advantages for one neo-W haplotype during the haploid stage in females comes at a cost to the other, and thus recombination off the favoured background becomes more detrimental.
+
+%\textcolor{red}{the versions for equil $(A)$ are not terrible but could be improved by cleverly re-writing with the $\phi$ and $\psi$ terms from above, I think...}
+
+Similar equations can be derived for equilibrium (A) by substituting the equilibrium frequencies into Table \ref{tab:haplotype_growth}
+
+\begin{subequations}\label{Ainvasion}
+\begin{align}
+\Lambda_{W'A}^{(XY)}&= \frac{a}{b} \left[w_{AA}^\female w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi +  w_{Aa}^\female (1+\alpha^\female_\Delta) w_a^\male c \right] / (2 w_a^\female) \\
+\Lambda_{W'a}^{(XY)}&= \frac{a}{b} \left[ w_{Aa}^\female (1-\alpha^\female_\Delta) w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi +  w_{aa}^\female w_a^\male c \right] / (2 w_A^\female) \\
+\chi_{W'A}^{(XY)}&= \frac{a}{b} \frac{R}{2} \left[   w_{Aa}^\female (1+\alpha^\female_\Delta) w_a^\male c \right] / w_a^\female\\ 
+\chi_{W'a}^{(XY)}&= \frac{a}{b} \frac{R}{2} \left[ w_{Aa}^\female (1-\alpha^\female_\Delta) w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi \right] / w_A^\female,
+%\Lambda_{W'A}^{(XY)}&=   {\left[ 2 (1 - \zeta) \right]}^{-1} w_A^{\female} \left[ b w_{AA}^\female + c w_{Aa}^\female \left(1 - \alpha^\female_\Delta \right) \right]/ \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\female}_{D} \right)  \\
+%\Lambda_{W'a}^{(XY)}&=  \\
+%\chi_{W'A}^{(XY)}&= \\ 
+%\chi_{W'a}^{(XY)}&=
+\end{align}
+\end{subequations}
+
+\noindent
+where
+
+\begin{subequations}
+\begin{align}
+a &= w_a^\female \phi + w_A^\female \psi \\
+b &= w_{AA}^\female \left[ w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \right] \phi^2 + w_{Aa}^\female \left[ w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) + w_{aa}^\male w_a^\male \right] \psi \phi + w_{aa}^\female \left( w_{aa}^\male w_a^\male \right) \psi^2\\
+%c &= w_{Aa}^\male (1-\alpha^\male_\Delta) \phi \left[ w_{Aa}^\male (1+\alpha^\male_\Delta) \phi \right] + w_{Aa}^\male\phi \left[ 2w_{AA}^\male + w_{aa}^\male (1+\alpha^\male_\Delta) \right] \psi + w_{aa}^\male \psi \left(2w_{AA}^\male \psi \right) \\
+c &= w_{Aa}^\male (1-\alpha^\male_\Delta) \phi + 2w_{aa}^\male \psi.
+\end{align}
+\end{subequations}
+
+%\textcolor{red}{Sally suggests using some $\zeta$ term in the above equations}
+%\textcolor{blue}{Maybe just reference table 2?}
+
+As with equilibrium (B), haploid selection again modifies invasion fitnesses by altering the ancestral sex ratio, $\zeta$ (see Table \ref{tab:haplotype_growth}), and directly selecting upon female gametes, through $w_{i}^\female$.
+The only difference is that resident XX females are no longer always homozygote $AA$ and males are no longer always heterozygote $Aa$.
+Thus the effect of haploid selection in males is reduced, as is the difference in fitness between neo-W haplotypes and resident X haplotypes, as both can be on any diploid or haploid background.
+
+The other terms are easier to interpret in the absence of haploid selection.
+For instance, without haploid selection, the neo-W-$A$ haplotype spreads ($\Lambda_{W'A}^{(XY)}>1$) if and only if
+
+\begin{equation}\label{eq:BeqWAspread}
+2(w_{Aa}^\female-w_{aa}^\female)w_{aa}^\male \psi^2 > (w_{AA}^\female-w_{Aa}^\female)w_{Aa}^\male \phi (\phi-\psi),
+\end{equation}
+
+\noindent  
+where $\phi-\psi=w_{AA}^\female w_{Aa}^\male-w_{aa}^\female w_{aa}^\male$ and both $\phi$ and $\psi$ are positive when equilibrium (A) is stable. 
+In contrast to equilibrium (B), a neo-W haplotype can spread under purely sexually-antagonistic selection  ($w_{aa}^\female<w_{Aa}^\female<w_{AA}^\female$ and $w_{AA}^\male<w_{Aa}^\male<w_{aa}^\male$).
+The neo-W-$A$ can spread as long as it becomes associated with females that bear more $A$ alleles than observed at equilibrium (A), effectively specializing on female fitness. 
+%In this case, the neo-W-$A$ haplotype can spread, despite producing a lot of $Aa$ daughters by obtaining the $a$ from Y-gametes, when $aa$ females, which the neo-W-$A$ never makes, are strongly selected against.
+%This can be intuited from the fact that \eqref{eq:BeqWAspread} will be more easily met when $w_{Aa}^\female-w_{aa}^\female\approx w_{Aa}^\female$ and $w_{AA}^\female-w_{Aa}^\female\approx 0$, implying $w_{aa}^\female \approx 0$ and $w_{Aa}^\female\approx w_{AA}^\female$ (although this is complicated by the fact that $w_{aa}^\female$ and $w_{Aa}^\female$ affect $\phi$ and $\psi$ too, the intuition holds).
+
+Without haploid selection, the neo-W-$a$ haplotype spreads ($\Lambda_{W'a}^{(XY)}>1$) if and only if
+
+\begin{equation}\label{eq:BeqWaspread}
+(w_{aa}^\female + w_{Aa}^\female-2w_{AA}^\female)w_{Aa}^\male \phi^2 + (w_{aa}^\female-w_{Aa}^\female)(w_{Aa}^\male+2w_{aa}^\male) \phi \psi >0.
+\end{equation}
+
+\noindent
+This condition cannot be met with purely sexually antagonistic selection (as both terms on the left-hand side would then be negative), but it can be met under other circumstances. 
+For example, with overdominance in males there is selection for increased $A$ frequencies on the X background in males, which are always paired with Y-$a$ haplotypes.
+Directional selection for $a$ in females can then maintain a polymorphism at the $\mathbf{A}$ locus on the X background.
+This scenario selects for a modifier that increases recombination between the sex chromosomes (e.g., blue region of Fig 2d in~\cite{Otto2014}) and facilitates the spread of neo-W-$a$ haplotypes, which create females bearing more $a$ alleles than the ancestral X haplotype does.
+
+In absence of haploid selection, the fact that a less closely linked neo-W ($R>0$) can invade an XY system with tight sex-linkage can also be reached from Equation 7 in \cite{vanDoorn:2010hu}; for example, with no polymorphism on the Y ($V_Y=0$) and an allelic substitution favoured in females ($\alpha^f,\alpha_X^f>0$) a loosely linked neo-W can invade given the allelic substitution is sufficiently disfavoured on the X in males ($\alpha_X^m < -2\alpha_X^f$), although it is unclear from their implicit equation if and when such an equilibrium is stable.
+
+\subsubsection*{Role of haploid selection with tight linkage between $\mathbf{X}$ and $\mathbf{A}$ loci}
+
+Haploid selection generally expands the conditions under which neo-W alleles can spread within ancestral systems that have evolved tight linkage between the sex-determining locus and a selected locus ($r \approx 0$).
+First, haploid selection can allow a polymorphism to be maintained when it would not under diploid selection alone (e.g., with directional selection in diploids). 
+In cases of ploidally-antagonistic selection, where there is a balance between alleles favored in the haploid stage and the diploid stage, neo-W alleles - even if unlinked to the selected locus - can spread (Fig \ref{fig:regionPloidAntag}).
+Second, even when diploid selection could itself maintain a polymorphism, haploid selection can increase the conditions under which transitions among sex-determining systems are possible.
+Of particularly importance, when selection is sexually-antagonistic in diploids ($s^\female s^\male <0$ and $0<h^\circ<1$), an unlinked neo-W ($R=1/2$) cannot invade unless there is also haploid selection (see proof in \nameref{file:Mathematica}; Fig \ref{fig:SexAntagTighter} and Fig \ref{fig:SexAntagTighterMaleDrive}).
+More generally, haploid selection alters the conditions under which neo-W alleles can spread (compare Fig \ref{fig:regionMaleDrive}-Fig \ref{fig:regionFemaleGS} to Fig \ref{fig:regionplots}).
+
+%[SALLY:  I think that is enough, but we could add somewhere??: "Without haploid selection, unlinked neo-W alleles ($R=1/2$) can invade only under certain conditions, requiring either overdominance in males or underdominance in females (see proof in supplementary \textit{Mathematica} file).?
+Note that underdominance in females with directional selection in males can lead to the spread of unlinked neo-W?s, but only from equilB (only $\Lambda_{ma}$ is greater than one in this case).]
+
+Male haploid selection in favour of the $a$ allele ($\alpha_{\Delta}^\male<0$, $w_{A}^\male<w_{a}^\male$) generates male-biased sex ratios at equilibria (A) and (B), where Y-$a$ is fixed ($\hat{p}_{Y}^\male=0$).
+Male-biased sex ratios facilitate the spread of neo-W-$A$ and neo-W-$a$ haplotypes (increasing $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$). 
+Panels A-C in Fig \ref{fig:regionMaleDrive} and \ref{fig:regionMaleGS} show that neo-W haplotypes tend to spread for a wider range of parameters when sex ratios are male biased, compared to Fig \ref{fig:regionplots} without haploid selection.
+By contrast, male haploid selection in favour of the $A$ allele generates female-biased sex ratios and reduces $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$, as demonstrated by panels D-F in Fig \ref{fig:regionMaleDrive} and Fig \ref{fig:regionMaleGS}.
+
+Female haploid selection generates direct selection on the neo-W-$A$ and neo-W-$a$ haplotypes as they spread in females. 
+Thus, female haploid selection in favour of the $a$ allele tends to increase $\Lambda_{W'a}^{(XY)}$ and decrease $\Lambda_{W'A}^{(XY)}$, as shown by panels A-C in Fig \ref{fig:regionFemaleDrive} and Fig \ref{fig:regionFemaleGS}.
+Conversely, female haploid selection in favour of the $A$ allele increases $\Lambda_{W'A}^{(XY)}$ and decreases $\Lambda_{W'a}^{(XY)}$, see panels D-F in Fig \ref{fig:regionFemaleDrive} and Fig \ref{fig:regionFemaleGS}.
+
+Thus, the impact of haploid selection on transitions between sex-determining systems must be considered as two sides of a coin: it can generate sex ratio biases that promote transitions that equalize the sex ratio, but it can also direct select for transitions that cause sex ratios to become biased.
+
+%\paragraph*{S1 File.}
+%\label{file:Mathematica}
+%{\bf Supplementary \textit{Mathematica} file.}  This file can be used to re-derive our results and generate figures. 
+%
+%\paragraph*{S1 Table}
+%\label{tab:chisubstitutions}
+%{\bf Substitutions for different loci orders assuming no interference.}
+%
+%\paragraph*{S2 Table}
+%\label{tab:meanfitnesses}
+%{\bf Mean fitnesses and zygotic sex ratio in the resident population ($M$ fixed, XY sex determination).}
+%
+%\paragraph*{S1 Appendix.}
+%\label{app:recurs}
+%{\bf Recursion equations and complete model description.} 
+%
+%\paragraph*{S2 Appendix.}
+%\label{app:eq_stab}
+%{\bf Equilibria and stability conditions when $M$ allele is fixed. } 
+%
+%\paragraph*{S3 Appendix.}
+%\label{app:inv_cond}
+%{\bf Invasion conditions for the $m$ allele.}
+
+%\newpage
+\section*{Supplementary Tables}
+\setcounter{table}{0} 
+\renewcommand{\thetable}{S\arabic{table}}
+
+\begin{table}[ht]
+%\centering
+\smallskip
+\caption{
+Substitutions for different loci orders assuming no interference.
+%and $r,R\in(0,1/2)$.\textcolor{blue}{write all in form of first line?
+so that 1/2 cases are okay (can't determine chi if R is 1/2 in second line, or if r is 1/2 in third line}
+}
+\begin{tabular}{l l}
+\hline\hline
+  Order of loci &   \\ [0.5ex] \hline
+  SDR-A-M & $\rho=r(1-R)+R(1-r)$  \\
+  SDR-M-A & $r=\rho(1-R)+R(1-\rho)$ \\ %$\rho=(r-R)/(1-2R)$ \\
+  A-SDR-M & $R=r(1-\rho)+\rho(1-r)$ \\ %$\rho=(R-r)/(1-2r)$ \\
+  \hline \hline
   \label{tab:chisubstitutions}
-{\bf Substitutions for different loci orders assuming no interference.}
-
-\paragraph*{S2 Table}
+ \end{tabular}
+\end{table}
+
+\begin{table}[!h]
+%\centering
+\smallskip
+\caption{Mean fitnesses and zygotic sex ratio in the resident population ($M$ fixed, XY sex determination). }
+\begin{tabular}{l l }
+\hline\hline
+  Sex \& Life Cycle Stage & Mean Fitness \\ [0.5ex] \hline  \noalign{\vskip 0.5ex}
+  female gametes ($\bar{w}_H^\female$) & 
+  $p_X^\female w_A^\female + (1-p_X^\female) w_a^\female$ \\ [0.5ex] \hline  \noalign{\vskip 0.5ex}
+  X-bearing male gametes ($\bar{w}_{HX}^\male$) & 
+  $p_X^{\male} w_A^\male + (1-p_X^{\male}) w_a^\male$ \\ [0.5ex] \hline  \noalign{\vskip 0.5ex}
+  Y-bearing male gametes ($\bar{w}_{HY}^\male$) & 
+  $p_Y^{\male} w_A^\male + (1-p_Y^{\male}) w_a^\male$ \\ [0.5ex] \hline  \noalign{\vskip 0.5ex}
+  male gametes ($\bar{w}_H^\male$) & 
+  $(1-q) \bar{w}_{HX}^\male + q \bar{w}_{HY}^\male$ \\ [0.5ex] \hline  \noalign{\vskip 0.5ex}
+  females ($\bar{w}^\female$) & 
+%  $\begin{array}{l}  (1-\zeta)^{-1} (1-q) \big[ p_X^\female w_A^\female p_X^\male w_A^\male w_{AA}^\female + \\
+%  (1 - p_X^\female) w_a^\female p_X^\male w_A^\male w_{Aa}^\female + \\
+%  p_X^\female w_A^\female (1 - p_X^\male) w_a^\male w_{Aa}^\female + \\
+%  (1-p_X^\female) w_a^\female (1 - p_X^\male) w_a^\male w_{aa}^\female \big] / \left( \bar{w}_H^\female \bar{w}_H^\male \right)
+%  \end{array} 
+ $\begin{array}{l} \big[ p_X^\female w_A^\female p_X^\male w_A^\male w_{AA}^\female + \\
+  (1 - p_X^\female) w_a^\female p_X^\male w_A^\male w_{Aa}^\female + \\
+  p_X^\female w_A^\female (1 - p_X^\male) w_a^\male w_{Aa}^\female + \\
+  (1-p_X^\female) w_a^\female (1 - p_X^\male) w_a^\male w_{aa}^\female \big] / \left( \bar{w}_H^\female \bar{w}_{HX}^\male \right)
+  \end{array}
+  $ \\ [0.5ex] \noalign{\vskip 0.5ex} \hline  \noalign{\vskip 0.5ex}
+  males ($\bar{w}^\male$) & 
+%  $\begin{array}{l} \zeta^{-1} q \big[ p_X^\female w_A^\female  p_Y^\male w_A^\male w_{AA}^\male + \\
+%  (1 - p_X^\female) w_a^\female  p_Y^\male w_A^\male w_{Aa}^\male + \\
+%  p_X^\female w_A^\female  (1 - p_Y^\male) w_a^\male w_{Aa}^\male + \\
+%  (1-p_X^\female) w_a^\female  (1 - p_Y^\male) w_a^\male w_{aa}^\male \big] / \left( \bar{w}_H^\female \bar{w}_H^\male \right) 
+%  \end{array}
+ $\begin{array}{l} \big[ p_X^\female w_A^\female  p_Y^\male w_A^\male w_{AA}^\male + \\
+  (1 - p_X^\female) w_a^\female  p_Y^\male w_A^\male w_{Aa}^\male + \\
+  p_X^\female w_A^\female  (1 - p_Y^\male) w_a^\male w_{Aa}^\male + \\
+  (1-p_X^\female) w_a^\female  (1 - p_Y^\male) w_a^\male w_{aa}^\male \big] / \left( \bar{w}_H^\female \bar{w}_{HY}^\male \right) 
+  \end{array}
+  $ \\ [0.5ex] \noalign{\vskip 0.5ex} \hline  \noalign{\vskip 0.5ex}
+  fraction zygotes male ($\zeta$) & $q \left[ p_Y^\male w_A^\male+(1-p_Y^\male)w_a^\male\right] / \bar{w}_H^\male $
+   \\ [0.5ex]  \noalign{\vskip 0.5ex}
+  \hline \hline
   \label{tab:meanfitnesses}
-{\bf Mean fitnesses and zygotic sex ratio in the resident population ($M$ fixed, XY sex determination). }
-
-\paragraph*{S1 Appendix.}
-\label{app:recurs}
-{\bf Recursion equations and complete model description.}
-
-\paragraph*{S2 Appendix.}
-\label{app:eq_stab}
-{\bf Equilibria and stability conditions when $M$ allele is fixed. }
-
-\paragraph*{S3 Appendix.}
-\label{app:inv_cond}
-{\bf Invasion conditions for the $m$ allele.}
-
-% Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
-\paragraph*{S1 Fig.}
-\label{fig:positionOverdominance}
+ \end{tabular}
+\end{table}
+
+\newpage
+\section*{Supplementary Figures}
+\setcounter{figure}{0} 
+\renewcommand{\thefigure}{S\arabic{figure}}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Both neo-W haplotypes can spread, in the absence of haploid selection, when there is overdominance
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[!h]
+\centering
+\centerline{\includegraphics[width=\linewidth]{../Plots/PositionPlot_Overdominance.eps}}
+\caption{
 {\bf With overdominance, loci near to the ancestral sex-determining locus ($r\approx0$) can favour neo-W alleles that are less tightly linked ($R>r$).} 
@@
 Equilibria where the $A$ allele is more common among Y-bearing male gametes can also be stable and allow neo-W invasion for these parameters (blue lines). 
-%The weak selection approximation holds when all recombination rates are large relative to selection (around 0 in panels A and C), in which case, in the absence of haploid selection, neo-W alleles should spread if and only if they are more tightly linked to the selected locus (positive invasion fitness if and only if the selected locus is in the grey region).
-%However, when recombination rates are small (panels B and D and when the selected locus is near the SDRs in all panels), this weak selection prediction can break down.
-
-\paragraph*{S2 Fig.}
-\label{fig:temporalOverdominance}
+}
+\label{fig:positionOverdominance}
+\end{figure}
+
+\newpage
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Both neo-W haplotypes can spread, in the absence of haploid selection, when there is overdominance
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[!h]
+\centering
+\centerline{\includegraphics[width=\linewidth]{../Plots/Temporal_Overdominance.eps}}
+\caption{
 {\bf Following invasion by a neo-W allele, there can be a complete transition to a new sex-determining system, maintenance of both ancestral-XY and neo-ZW sex determining systems, or loss of the new sex-determining allele.}
@@
 In B, this leads to loss of the neo-W and the system goes to an equilibrium with X-$a$ and Y-$A$ haplotypes fixed (equilibrium $A'$), such that all females have the high fitness genotype $aa$ and all males are $Aa$.
-For the parameters in B, neo-W alleles have negative invasion fitness when the Y-$A$ haplotype is ancestrally more common than Y-$a$ (compare blue to black curves in \nameref{fig:positionOverdominance}A and  \nameref{fig:positionOverdominance}B near the ancestral sex-determining locus).
-In contrast, the neo-W is not lost in panel D as it is favoured regardless of whether Y-$A$ or Y-$a$ haplotypes predominate (again, compare blue to black curves in \nameref{fig:positionOverdominance}C and  \nameref{fig:positionOverdominance}D).
-%Fitness parameters are the same as in \nameref{fig:positionOverdominance}; in panels A and B the $a$ allele is favoured in females ($w_{aa}^\female=1.05$, $w_{Aa}^\circ=1$, $w_{AA}^\female=0.85$) while there is overdominance in males ($w_{aa}^\male=w_{AA}^\male=0.75$) and in panels C and D, there is overdominance in both sexes ($w_{aa}^\female=w_{AA}^\female=0.6$, $w_{aa}^\male=0.5$, $w_{AA}^\male=0.7$, $w_{Aa}^\circ=1$).
-%These parameters are marked by a dagger in Fig \ref{fig:regionplots}. 
-%Here, there is no haploid selection $t^\circ = \alpha^\circ_\Delta = 0$.
-
-\paragraph*{S3 Fig.}
-\label{fig:SexAntagTighterMaleDrive}
+For the parameters in B, neo-W alleles have negative invasion fitness when the Y-$A$ haplotype is ancestrally more common than Y-$a$ (compare blue to black curves in Fig \ref{fig:positionOverdominance}A and  Fig \ref{fig:positionOverdominance}B near the ancestral sex-determining locus).
+In contrast, the neo-W is not lost in panel D as it is favoured regardless of whether Y-$A$ or Y-$a$ haplotypes predominate (again, compare blue to black curves in Fig \ref{fig:positionOverdominance}C and  Fig \ref{fig:positionOverdominance}D).
+}
+\label{fig:temporalOverdominance}
+\end{figure}
+
+\begin{figure}[!h]
+\centering
+\centerline{\includegraphics[width=1.25\linewidth]{../Plots/PositionPlot_SexAntagTighter_MaleDrive.eps}}
+\caption{
 {\bf  When there is sexually-antagonistic selection and haploid selection, a neo-W allele may invade for any $R$.}
@@
 The diploid selection parameters used in this plot are the same as in Fig \ref{fig:SexAntagTighter}. 
-There is also meiotic drive in males favouring $a$ ($\alpha_{\Delta}^\male=-0.08$), this full set of parameters is marked by an asterisk in \nameref{fig:regionMaleDrive}A.
-When $R=0.5$ (green curve), the neo-W does not reach fixation and X, Y, Z, and W alleles are all maintained in the population, see \nameref{fig:freqAll}C.
-
-\paragraph*{S4 Fig.}
-\label{fig:regionMaleDrive}
+There is also meiotic drive in males favouring $a$ ($\alpha_{\Delta}^\male=-0.08$), this full set of parameters is marked by an asterisk in Fig \ref{fig:regionMaleDrive}A.
+When $R=0.5$ (green curve), the neo-W does not reach fixation and X, Y, Z, and W alleles are all maintained in the population, see Fig \ref{fig:freqAll}C.
+}
+\label{fig:SexAntagTighterMaleDrive}
+\end{figure}
+
+\begin{figure}[!h]
+\centering
+\centerline{\includegraphics[width=1.25\linewidth]{../Plots/Region_Plot_combined_MaleDrive.eps}}
+\caption{
 {\bf Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is male meiotic drive at a locus that is tightly linked to the ancestral XY locus ($r=0$).}
@@
 By contrast, $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$ tend to be reduced when meiotic drive in males favours the $A$ allele ($\alpha_{\Delta}^\male=0.16$), panels D-F. 
-%We consider three forms of selection in females: directional selection in favour of the $A$ allele (panels A and D, $w_{aa}^\female=0.85$, $w_{AA}^\female=1.05$), direction selection in favour of the $a$ allele (panels B and E, $w_{aa}^\female=1.05$, $w_{AA}^\female=0.85$), and overdominance (panels C and F, $w_{aa}^\female=w_{AA}^\female=0.6$).
-
-\paragraph*{S5 Fig.}
-\label{fig:regionMaleGS}
+}
+\label{fig:regionMaleDrive}
+\end{figure}
+
+%\newpage
+\begin{figure}[!h]
+\centering
+\centerline{\includegraphics[width=1.25\linewidth]{../Plots/Region_Plot_combined_MaleGS.eps}}
+\caption{
 {\bf Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is male gametic competition at a locus that is tightly linked to the ancestral XY locus ($r=0$).}
 This figure is equivalent to Fig \ref{fig:regionplots} but with gametic competition in males.
-%Diploid selection parameters ($w_{ij}^\circ$) are the same as those in \nameref{fig:regionMaleDrive}. 
+%Diploid selection parameters ($w_{ij}^\circ$) are the same as those in Fig \ref{fig:regionMaleDrive}. 
 The $a$ allele is favoured during male gametic competition in Panels A-C ($w_{a}^\male=1.16$, $w_{A}^\male=1$), which creates male biased sex ratios and increases $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$.
 By contrast, $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$ tend to be reduced when the $A$ allele is favoured during male gametic competition, panels D-F.
-Compared to the meiotic drive parameters in \nameref{fig:regionMaleDrive}, the effect of these male gametic competition parameters on the sex ratio is smaller. 
-For example, in \nameref{fig:regionMaleDrive}A-C, the ancestral sex ratio is $\alpha^\male=0.58$ at equilibrium (B) and in panels A-C of this plot, the ancestral sex ratio is $w_{a}^\male/(w_{A}^\male+w_{a}^\male)=0.537$ at equilibrium (B).
-
-\paragraph*{S6 Fig.}
-\label{fig:regionFemaleDrive}
+Compared to the meiotic drive parameters in Fig \ref{fig:regionMaleDrive}, the effect of these male gametic competition parameters on the sex ratio is smaller. 
+For example, in Fig \ref{fig:regionMaleDrive}A-C, the ancestral sex ratio is $\alpha^\male=0.58$ at equilibrium (B) and in panels A-C of this plot, the ancestral sex ratio is $w_{a}^\male/(w_{A}^\male+w_{a}^\male)=0.537$ at equilibrium (B).
+}
+\label{fig:regionMaleGS}
+\end{figure}
+
+\begin{figure}[!h]
+\centering
+\centerline{\includegraphics[width=1.25\linewidth]{../Plots/Region_Plot_combined_FemaleDrive.eps}}
+\caption{
 {\bf Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is female meiotic drive at a locus that is tightly linked to the ancestral XY locus ($r=0$).}
 This figure is equivalent to Fig \ref{fig:regionplots} but with meiotic drive in females.
-%Diploid selection parameters ($w_{ij}^\circ$) are the same as those in \nameref{fig:regionMaleDrive} and \nameref{fig:regionMaleGS}. 
+%Diploid selection parameters ($w_{ij}^\circ$) are the same as those in Fig \ref{fig:regionMaleDrive} and Fig \ref{fig:regionMaleGS}. 
 The $a$ allele is favoured by meiotic drive in females in Panels A-C ($\alpha_{\Delta}^\female=-0.16$), which increases $\Lambda_{W'a}^{(XY)}$ and decreases $\Lambda_{W'A}^{(XY)}$. 
 Female meiotic drive in favour of the $A$ allele (panels D-F, $\alpha_{\Delta}^\female=-0.16$) has the opposite effect. 
-
-\paragraph*{S7 Fig.}
-\label{fig:regionFemaleGS}
+}
+\label{fig:regionFemaleDrive}
+\end{figure}
+
+\begin{figure}[!h]
+\centering
+\centerline{\includegraphics[width=1.25\linewidth]{../Plots/Region_Plot_combined_FemaleGS.eps}}
+\caption{
 {\bf Parameters for which neo-W-$A$ and neo-W-$a$ haplotypes spread when there is female gametic competition at a locus that is tightly linked to the ancestral XY locus ($r=0$).}
 This figure is equivalent to Fig \ref{fig:regionplots} but with gametic competition in females.
-%Diploid selection parameters ($w_{ij}^\circ$) are the same as those in \nameref{fig:regionMaleDrive}, \nameref{fig:regionMaleGS}, and \nameref{fig:regionFemaleDrive}. 
+%Diploid selection parameters ($w_{ij}^\circ$) are the same as those in Fig \ref{fig:regionMaleDrive}, Fig \ref{fig:regionMaleGS}, and Fig \ref{fig:regionFemaleDrive}. 
 The $a$ allele is favoured during female gametic competition in females in Panels A-C ($w_{a}^\female=1.16$, $w_{A}^\female=1$), which increases $\Lambda_{W'a}^{(XY)}$ and decreases $\Lambda_{W'A}^{(XY)}$.
 The $A$ allele is favoured during gametic competition in panels D-F ($w_{a}^\female=1$, $w_{A}^\female=1.16$), giving the opposite effect on $\Lambda_{W'a}^{(XY)}$ and $\Lambda_{W'A}^{(XY)}$. 
-
-\paragraph*{S8 Fig.}
-\label{fig:regionPloidAntag}
+}
+\label{fig:regionFemaleGS}
+\end{figure}
+
+%\begin{landscape}
+\begin{figure}[!h]
+\centering
+\centerline{
+\includegraphics[width=1.25\linewidth]{../Plots/All_plot_combined_PloidAntag.eps}
+}
+\caption{
 {\bf Ploidally-antagonistic selection can drive the spread of neo-W alleles. }
@@
 Black $R=1/1000$, Red $R=2/100$, Blue $R=1/10$, Green $R=1/2$.  
-
-\paragraph*{S9 Fig.}
-\label{fig:freqAll}
+}
+\label{fig:regionPloidAntag}
+\end{figure}
+%\end{landscape}
+
+%\begin{landscape}
+\begin{figure}[!h]
+\centering
+\centerline{
+\includegraphics[width=1.25\linewidth]{../Plots/Freq_plot_combined_PloidAntag.eps}
+}
+\caption{
 {\bf Pseudo-fixation of neo-W or maintenance of multiple sex-determining alleles. }
@@
 In panel A, selection is ploidally-antagonistic with drive in males (parameters as in the green curve in Fig \ref{fig:SexRatioBad}B).
-In panel B, there is overdominance in both sexes and no haploid selection (parameters as in the green curve in \nameref{fig:temporalOverdominance}C).
-In panel C, there is sexually-antagonistic selection in diploids with drive in males (parameters as in the green curve in \nameref{fig:regionMaleDrive}C).
+In panel B, there is overdominance in both sexes and no haploid selection (parameters as in the green curve in Fig \ref{fig:temporalOverdominance}C).
+In panel C, there is sexually-antagonistic selection in diploids with drive in males (parameters as in the green curve in Fig \ref{fig:regionMaleDrive}C).
 In all cases, the initial equilibrium frequency has $a$ near fixation on the Y.
-
-\section*{Acknowledgments}
-We thank Georgy Sandler and Stephen Wright for sharing their results with us, and we thank Bret Payseur and three anonymous reviewers for helpful comments on this manuscript. 
-%This project was supported by the Natural Sciences and Engineering Research Council of Canada (CGS-D 6564 to MMO; RGPIN-2016-03711 to SPO).
-
-\nolinenumbers
-
-% Either type in your references using
-% \begin{thebibliography}{}
-% \bibitem{}
-% Text
-% \end{thebibliography}
-%
-% or
-%
-% Compile your BiBTeX database using our plos2015.bst
-% style file and paste the contents of your .bbl file
-% here. See http://journals.plos.org/plosone/s/latex for 
-% step-by-step instructions.
-% 
-\bibliography{sex_chromosomes}
-
-%\newpage
-%
-%\setcounter{equation}{0}
-%\renewcommand{\theequation}{S1.\arabic{equation}}
-%
-%\section*{S1 Appendix}
-%
-%\subsection*{Recursion equations}
-%
-%
-%In each generation we census the genotype frequencies in male and female gametes/gametophytes (hereafter, gametes) between meiosis (and any meiotic drive) and gametic competition. 
-%At this stage we denote the frequencies of X- and Y-bearing gametes from males and females $x_{i}^{\circ}$ and $y_{i}^{\circ}$.
-%The superscript $\circ \in \{\male,\female\}$ specifies the sex of the diploid that the gamete came from. 
-%The subscript $i\in\{1,2,3,4\}$ specifies the genotype at the selected locus $\mathbf{A}$ and at the novel sex-determining locus $\mathbf{M}$, where $1=AM$, $2=aM$, $3=Am$, and $4=am$. 
-%The gamete frequencies from each sex sum to one, $\sum_{i}x_{i}^{\circ}+y_{i}^{\circ}=1$. 
-%
-%Competition then occurs among gametes of the same sex (e.g., among eggs and among sperm separately) according to the genotype at the $\mathbf{A}$ locus ($w_{1}^\circ=w_{3}^\circ=w_{A}^\circ$, $w_{2}^\circ=w_{4}^\circ=w_{a}^\circ$, see Table \ref{tab:fitnesstable}).
-%The genotype frequencies after gametic competition are $x_{i}^{\circ,s}= w_{i}^{\circ}x_{i}^{\circ}/\bar{w}_{H}^{\circ}$ and $y_{i}^{\circ,s}= w_{i}^{\circ}y_{i}^{\circ}/\bar{w}_{H}^{\circ}$, where $\bar{w}_{H}^{\circ}=\sum_{i} w_{i}^{\circ}x_{i}^{\circ}+w_{i}^{\circ}y_{i}^{\circ}$ is the mean fitness of male ($\circ=\male$) or female ($\circ=\female$) gametes.
-%
-%Random mating then occurs between gametes to produce diploid zygotes.
-%%To shorten notation we now use index $i$ (and $j$) to denote the alleles at both the $\mathbf{A}$ and $\mathbf{M}$ loci and label $MA=1$, $Ma=2$, $mA=3$, and $ma=4$, such that $i,j\in\{1,2,3,4\}$.
-%The frequencies of XX zygotes are then denoted as $xx_{ij}$, XY zygotes as $xy_{ij}$, and YY zygotes as $yy_{ij}$, where $\mathbf{A}$ and $\mathbf{M}$ locus genotypes are given by $i,j\in\{1,2,3,4\}$, as above.
-%In XY zygotes, the haplotype inherited from an X-bearing gamete is given by $i$ and the haplotype from a Y-bearing gamete is given by $j$. 
-%In XX and YY zygotes, individuals with diploid genotype $ij$ are equivalent to those with diploid genotype $ji$; for simplicity, we use $xx_{ij}$ and $yy_{ij}$ with $i\neq j$ to denote the average of these frequencies, $xx_{ij}=(x_{i}^{\female,s}x_{j}^{\male,s}+x_{j}^{\female,s}x_{i}^{\male,s})/2$ and $yy_{ij}=(y_{i}^{\female,s}y_{j}^{\male,s}+y_{j}^{\female,s}y_{i}^{\male,s})/2$.
-%
-%
-%Denoting the $\mathbf{M}$ locus genotype by $b \in \{MM, Mm, mm\}$ and the $\mathbf{X}$ locus genotype by $c \in \{XX, XY, YY\}$, zygotes develop as females with probability $k_{bc}$. 
-%Therefore, the frequencies of XX females are given by $xx_{ij}^{\female}=k_{bc}xx_{ij}$, XY females are given by $xy_{ij}^{\female}=k_{bc}xy_{ij}$, and YY females are given by $yy_{ij}^{\female}=k_{bc}yy_{ij}$.
-%Similarly, XX male frequencies are $xx_{ij}^{\male}=(1-k_{bc})xx_{ij}$, XY male frequencies are $xy_{ij}^{\male}=(1-k_{bc})xy_{ij}$, and YY males frequencies are $yy_{ij}^{\male}=(1-k_{bc})yy_{ij}$.
-%This notation allows both the ancestral and novel sex-determining regions to determine zygotic sex according to an XY system, a ZW system, or an environmental sex-determining system. 
-%In addition, we can consider any epistatic dominance relationship between the two sex-determining loci. 
-%Here, we assume that the ancestral sex-determining system ($\mathbf{X}$ locus) is XY ($k_{MMXX}=1$ and $k_{MMXY}=k_{MMYY}=0$) or ZW ($k_{MMZZ}=0$ and $k_{MMZW}=k_{MMWW}=1$) and epistatically recessive to a dominant novel sex-determining locus, $\mathbf{M}$ ($k_{Mmc}=k_{mmc}=k$).
-%
-%
-%Selection among diploids then occurs according to the diploid genotype at the $\mathbf{A}$ locus, $l \in \{AA, Aa, aa\}$, for an individual of type $ij$ (see Table \ref{tab:fitnesstable}). 
-%The diploid frequencies after selection in sex $\circ$ are given by $xx_{ij}^{\circ,s}=w_{l}^{\circ} xx_{ij}/\bar{w}^{\circ}_{D}$, $xy_{ij}^{\circ,s}=w_{l}^{\circ} xy_{ij}/\bar{w}^{\circ}_{D}$, and $yy_{ij}^{\circ,s}=w_{l}^{\circ} yy_{ij}/\bar{w}^{\circ}_{D}$, where $\bar{w}^{\circ}_{D}= \sum_{i=1}^{4}\sum_{j=1}^{4}w_{l}^{\circ}xx_{ij}+w_{l}^{\circ}xy_{ij}+w_{l}^{\circ}yy_{ij}$ is the mean fitness of diploids of sex $\circ$.
-%
-%Finally, these diploids undergo meiosis to produce the next generation of gametes. 
-%Recombination and sex-specific meiotic drive occur during meiosis.
-%%We can also assume that recombination is sex specific and/or affected by the M locus - but generally we don't so I just describe $R=R_{f}=R, r_{MM,d}=r_{Mm,d}=r_{mm,d}=r, \chi_{m}=\chi_{f}=\chi$.
-%Here, we allow any relative locations for the $\mathbf{X}$, $\mathbf{A}$, and $\mathbf{M}$ loci by using three parameters to describe the recombination rates between them. 
-%$R$ is the recombination rate between the $\mathbf{A}$ and $\mathbf{M}$ loci, $\rho$ is the recombination rate between the $\mathbf{M}$ and $\mathbf{X}$ loci, and $r$ is the recombination rate between the $\mathbf{A}$ and $\mathbf{X}$ loci (Fig \ref{fig:model_outline}).
-%\nameref{tab:chisubstitutions} shows replacements that can be made for each possible ordering of the loci assuming that there is no cross-over interference.
-%During meiosis in sex $\circ$, meiotic drive occurs such that, in $Aa$ heterozygotes, a fraction $\alpha^{\circ}$ of gametes produced carry the $A$ allele and $(1-\alpha^\circ)$ carry the $a$ allele.
-%
-%Among gametes from sex $\circ$, the frequencies of haplotypes (before gametic competition) in the next generation are given by
-%
-%\begingroup
-%\allowdisplaybreaks
-%\begin{subequations}
-%\begin{align}
-%%
-%\begin{split}
-%x_{1}^{{\circ}'}=&xx_{11}^{\circ,s}+xx_{13}^{\circ,s}/2+(xx_{12}^{\circ,s}+xx_{14}^{\circ,s})\alpha^\circ\\
-%&-R(xx_{14}^{\circ,s}-xx_{23}^{\circ,s}) \alpha^\circ\\
-%&+(xy_{11}^{\circ,s}+xy_{13}^{\circ,s})/2+(xy_{12}^{\circ,s}+xy_{14}^{\circ,s})\alpha^\circ\\
-%&- r(xy_{12}^{\circ,s}-xy_{21}^{\circ,s})\alpha^\circ - \rho(xy_{13}^{\circ,s}-xy_{31}^{\circ,s})/2\\
-%&+\big{[}-(R+r+\rho)xy_{14}^{\circ,s} +(R+\rho-r)xy_{41}^{\circ,s}\\
-%&+(R+r-\rho) xy_{23}^{\circ,s}+(R+\rho-r)xy_{32}^{\circ,s}\big{]}\alpha^\circ/2
-%\end{split}
-%\\
-%%
-%\begin{split}
-%x_{2}^{{\circ}'}=&xx_{22}^{\circ,s}+xx_{24}^{\circ,s}/2+(xx_{12}^{\circ,s}+xx_{23}^{\circ,s})\alpha^\circ\\
-%&-R(xx_{23}^{\circ,s}-xx_{14}^{\circ,s}) \alpha^\circ\\
-%&(xy_{22}^{\circ,s}+xy_{24}^{\circ,s})/2+(xy_{21}^{\circ,s}+xy_{23}^{\circ,s})(1-\alpha^\circ)\\
-%&- r(xy_{21}^{\circ,s}-xy_{12}^{\circ,s})(1-\alpha^\circ) - \rho(xy_{24}^{\circ,s}-xy_{42}^{\circ,s})/2\\
-%&+\big{[}-(R+r+\rho)xy_{23}^{\circ,s}+(R+\rho-r)xy_{32}^{\circ,s}\\
-%&+(R+r-\rho) xy_{14}^{\circ,s}+(R+\rho-r)xy_{41}^{\circ,s}\big{]}(1-\alpha^\circ)/2
-%\end{split}
-%\\
-%%
-%\begin{split}
-%x_{3}^{{\circ}'}=&xx_{33}^{\circ,s}+xx_{13}^{\circ,s}/2+(xx_{23}^{\circ,s}+xx_{34}^{\circ,s})\alpha^\circ\\
-%&-R(xx_{23}^{\circ,s}-xx_{14}^{\circ,s}) \alpha^\circ\\
-%&(xy_{33}^{\circ,s}+xy_{31}^{\circ,s})/2+(xy_{32}^{\circ,s}+xy_{34}^{\circ,s})\alpha^\circ\\
-%&- r(xy_{34}^{\circ,s}-xy_{43}^{\circ,s}) \alpha^\circ - \rho(xy_{31}^{\circ,s}-xy_{13}^{\circ,s})/2\\
-%&+\big{[}-(R+r+\rho)xy_{32}^{\circ,s} +(R+\rho-r)xy_{23}^{\circ,s}\\
-%&+(R+r-\rho) xy_{41}^{\circ,s}+(R+\rho-r)xy_{14}^{\circ,s}\big{]} \alpha^\circ/2
-%\end{split}
-%\\
-%%
-%\begin{split}
-%x_{4}^{{\circ}'}=&xx_{44}^{\circ,s}+xx_{34}^{\circ,s}/2+(xx_{14}^{\circ,s}+xx_{24}^{\circ,s})\alpha^\circ\\
-%&-R(xx_{14}^{\circ,s}-xx_{23}^{\circ,s}) \alpha^\circ\\
-%&(xy_{44}^{\circ,s}+xy_{42}^{\circ,s})/2+(xy_{41}^{\circ,s}+xy_{43}^{\circ,s})(1-\alpha^\circ)\\
-%&- r(xy_{43}^{\circ,s}-xy_{34}^{\circ,s})(1-\alpha^\circ) - \rho(xy_{42}^{\circ,s}-xy_{24}^{\circ,s})/2\\
-%&+\big{[}-(R+r+\rho)xy_{41}^{\circ,s}+(R+\rho-r)xy_{14}^{\circ,s}\\
-%&+(R+r-\rho) xy_{32}^{\circ,s}+(R+\rho-r)xy_{23}^{\circ,s}\big{]}(1-\alpha^\circ)/2
-%\end{split}
-%\\
-%\begin{split}
-%y_{1}^{{\circ}'}=&yy_{11}^{\circ,s}+yy_{13}^{\circ,s}/2+(yy_{12}^{\circ,s}+yy_{14}^{\circ,s})\alpha^\circ\\
-%&-R(yy_{14}^{\circ,s}-yy_{23}^{\circ,s}) \alpha^\circ\\
-%&(xy_{11}^{\circ,s}+xy_{31}^{\circ,s})/2+(xy_{21}^{\circ,s}+xy_{41}^{\circ,s})\alpha^\circ\\
-%&- r(xy_{21}^{\circ,s}-xy_{12}^{\circ,s})\alpha^\circ - \rho(xy_{31}^{\circ,s}-xy_{13}^{\circ,s})/2\\
-%&+\big{[} - (R+r+\rho)xy_{41}^{\circ,s} + (R+\rho-r)xy_{14}^{\circ,s}\\
-%& + (R+r-\rho)xy_{32}^{\circ,s} + (R+\rho-r) xy_{23}^{\circ,s}\big{]}\alpha^\circ/2
-%\end{split}
-%\\
-%%
-%\begin{split}
-%y_{2}^{{\circ}'}=&yy_{22}^{\circ,s}+yy_{24}^{\circ,s}/2+(yy_{12}^{\circ,s}+yy_{23}^{\circ,s})\alpha^\circ\\
-%&-R(yy_{23}^{\circ,s}-yy_{14}^{\circ,s}) \alpha^\circ\\
-%&(xy_{22}^{\circ,s}+xy_{42}^{\circ,s})/2+(xy_{12}^{\circ,s}+xy_{32}^{\circ,s})(1-\alpha^\circ)\\
-%&- r(xy_{12}^{\circ,s}-xy_{21}^{\circ,s})(1-\alpha^\circ) - \rho(xy_{42}^{\circ,s}-xy_{24}^{\circ,s})/2\\
-%&+\big{[}-(R+r+\rho)xy_{32}^{\circ,s} +(R+\rho-r) xy_{23}^{\circ,s}\\
-%&+(R+r-\rho)xy_{41}^{\circ,s}+(R+\rho-r)xy_{14}^{\circ,s}\big{]}(1-\alpha^\circ)/2
-%\end{split}
-%\\
-%%
-%\begin{split}
-%y_{3}^{{\circ}'}=&yy_{33}^{\circ,s}+yy_{13}^{\circ,s}/2+(yy_{23}^{\circ,s}+yy_{34}^{\circ,s})\alpha^\circ\\
-%&-R(yy_{23}^{\circ,s}-yy_{14}^{\circ,s}) \alpha^\circ\\
-%&(xy_{33}^{\circ,s}+xy_{13}^{\circ,s})/2+(xy_{23}^{\circ,s}+xy_{43}^{\circ,s})\alpha^\circ\\
-%&- r(xy_{43}^{\circ,s}-xy_{34}^{\circ,s})\alpha^\circ - \rho(xy_{13}^{\circ,s}-xy_{31}^{\circ,s})/2\\
-%&+\big{[}-(R+r+\rho)xy_{23}^{\circ,s} +(R+\rho-r)xy_{32}^{\circ,s}\\
-%&+(R+r-\rho) xy_{14}^{\circ,s} + (R+\rho-r) xy_{41}^{\circ,s}\big{]}\alpha^\circ/2
-%\end{split}
-%\\
-%%
-%\begin{split}
-%y_{4}^{{\circ}'}=&yy_{44}^{\circ,s}+yy_{34}^{\circ,s}/2+(yy_{14}^{\circ,s}+yy_{24}^{\circ,s})\alpha^\circ\\
-%&-R(yy_{14}^{\circ,s}-yy_{23}^{\circ,s}) \alpha^\circ\\
-%&(xy_{44}^{\circ,s}+xy_{24}^{\circ,s})/2+(xy_{14}^{\circ,s}+xy_{34}^{\circ,s})(1-\alpha^\circ)\\
-%&- r(xy_{34}^{\circ,s}-xy_{43}^{\circ,s})(1-\alpha^\circ) - \rho(xy_{24}^{\circ,s}-xy_{42}^{\circ,s})/2\\
-%&+\big{[}-(R+r+\rho) xy_{14}^{\circ,s} + (R+\rho-r)xy_{41}^{\circ,s}\\
-%&+(R+r-\rho) xy_{23}^{\circ,s} + (R+\rho-r) xy_{32}^{\circ,s}\big{]}(1-\alpha^\circ)/2.
-%\end{split}
-%\end{align}
-%\label{eq:recursions}
-%\end{subequations}
-%
-%\endgroup
-%
-%\noindent
-%The full system is therefore described by 16 recurrence equations (three diallelic loci in two sexes, $2^3 \times 2 = 16$). 
-%However, not all diploid types are produced under certain sex-determining systems. 
-%For example, with the $M$ allele fixed and an ancestral XY sex-determining system, there are XX females and XY males ($x_{3}^\circ=x_{4}^\circ=y_{3}^\male=y_{4}^\male=y_{i}^\female=0,\;\forall\; i$).
-%%($xx_{11}^{\male}=xx_{12}^{\male}=xx_{22}^\male=xy_{11}^{\female}=xy_{12}^{\female}=xy_{21}^{\female}=xy_{22}^\female=yy_{11}^{\female}=yy_{12}^{\female}=yy_{22}^\female=0$). 
-%In this case, the system only involves six recursion equations, %because there is only one $\mathbf{M}$ locus allele and no Y-bearing female gametes. 
-%which we assume below to calculate the equilibria.
-
-%\newpage
-
-%\setcounter{equation}{0}
-%\renewcommand{\theequation}{S2.\arabic{equation}}
-%
-%\section*{S2 Appendix}
-%
-%\subsection*{Resident equilibria and stability}
-%
-%In the resident population (allele $M$ fixed), we follow the frequency of $A$ in X-bearing female gametes, $p^\female_X$, and X-bearing male gametes, $p^\male_X$, and Y-bearing male gametes, $p^\male_Y$.
-%We also track the total frequency of Y among male gametes, $q$, which may deviate from $1/2$ due to meiotic drive in males. 
-%These four variables determine the frequencies of the six resident gamete types, which sum to one in each sex: $x_{1}^{\female}=\hat{p}_X^\female$, $x_{2}^{\female}=1-\hat{p}_X^\female$, $x_{1}^{\male}=(1-q)\hat{p}_X^\male$, $x_{2}^{\male}=(1-q)(1-\hat{p}_X^\male)$, $y_{1}^{\male}=q \hat{p}_Y^\male$, and $y_{2}^{\male}=q(1-\hat{p}_Y^\male)$.
-%Mean fitnesses in the resident population are given in \nameref{tab:meanfitnesses}.
-%
-%Various forms of selection can maintain a polymorphism at the $\mathbf{A}$ locus, including sexually antagonistic selection, overdominance, conflicts between diploid selection and selection upon haploid genotypes (ploidally-antagonsitic selection,~\cite{Immler:2012tl}), or a combination of these selective regimes (see below).
-%
-%In particular special cases, e.g., no sex-differences in selection or meiotic drive ($s^\male=s^\female$, $h^\male=h^\female$, and $\alpha^\male=\alpha^\female=1/2$), the equilibrium allele frequency and stability can be calculated analytically without assuming anything about the relative strengths of selection and recombination.
-%However, here, we focus on two regimes (tight linkage between $\mathbf{A}$ and $\mathbf{X}$ and weak selection) in order to make fewer assumptions about fitnesses. 
-%
-%\subsubsection*{Tight linkage between $\mathbf{X}$ and $\mathbf{A}$ loci}
-%
-%We first calculate the equilibria in the ancestral population when the recombination rate between the $\mathbf{X}$ and $\mathbf{A}$ loci is small ($r$ of order $\epsilon$). 
-%Selection at the $\mathbf{A}$ locus will not affect evolution at the novel sex-determining locus, $\mathbf{M}$, if one allele is fixed on all backgrounds. 
-%We therefore focus on the five equilibria that maintain both $A$ and $a$ alleles, four of which are given to leading order by:
-%
-%\begin{subequations}\label{eq:tightequil}
-%\begin{align}
-%(A)\ \ \ &\hat{p}_{Y}^{\male}=0,
-%\ \hat{q}_{Y}=\frac{1}{2}\left(1 - \alpha_\Delta^\male \frac{ w_{Aa}^{\male} \phi}{w_{Aa}^{\male} \phi+ w_{aa}^{\male} \psi}\right),\\
-%&\hat{p}_{X}^{\female}=\frac{w_{a}^{\female} \phi}{w_{a}^{\female} \phi+ w_{A}^{\female} \psi},
-%\ \hat{p}_{X}^{\male}=\frac{(1+\alpha_\Delta^\male)w_{Aa}^{\male} \phi}{(1+\alpha_\Delta^\male)w_{Aa}^{\male} \phi +w_{aa}^{\male} \psi} \nonumber \\
-%(A')\ \ \ &\hat{p}_{Y}^{\male}=1,
-%\ \hat{q}_{Y}=\frac{1}{2}\left(1 + \alpha_\Delta^\male \frac{w_{Aa}^{\male} \phi'}{w_{Aa}^{\male} \phi' + w_{AA}^{\male} \psi'}\right),\\
-%&\hat{p}_{X}^{\female}=1-\frac{w_{A}^{\female} \phi'}{w_{A}^{\female} \phi'+ w_{a}^{\female} \psi'},
-%\ \hat{p}_{X}^{\male}=1-\frac{(1-\alpha_\Delta^\male)w_{Aa}^{\male} \phi'}{(1-\alpha_\Delta^\male)w_{Aa}^{\male} \phi'+w_{AA}^{\male} \psi'} \nonumber \\
-%(B)\ \ \ &\hat{p}_{Y}^{\male}=0,\ \hat{p}_{X}^{\female}=1,\ \hat{p}_{X}^{\male}=1, \ \hat{q}_{Y}=(1 -\alpha^\male_\Delta)/2\\
-%(B')\ \ \ &\hat{p}_{Y}^{\male}=1,\ \hat{p}_{X}^{\female}=0,\ \hat{p}_{X}^{\male}=0, \ \hat{q}_{Y}=(1+\alpha^\male_\Delta)/2
-%\end{align}
-%\end{subequations}
-%\begin{equation*}
-%\begin{split}
-%\phi=&(1+\alpha^\female_\Delta) w_{A}^{\female} w_{Aa}^{\female} \left[ w_{a}^{\male} w_{aa}^{\male} + (1+\alpha_\Delta^\male) w_{A}^{\male} w_{Aa}^{\male} \right]/2 - w_{a}^{\male} w_{a}^{\female} w_{aa}^{\male} w_{aa}^{\female} \\
-%\psi=&(1-\alpha^\female_\Delta) w_{a}^{\female} w_{Aa}^{\female} \left[ w_{a}^{\male} w_{aa}^{\male} + (1+\alpha_\Delta^\male) w_{A}^{\male} w_{Aa}^{\male}\right]/2 - (1+\alpha_\Delta^\male) w_{A}^{\male} w_{A}^{\female} w_{Aa}^{\male} w_{AA}^{\female}\\
-%\phi'=&(1-\alpha^\female_\Delta) w_{a}^{\female} w_{Aa}^{\female} \left[ w_{A}^{\male} w_{AA}^{\male} + (1-\alpha_\Delta^\male) w_{a}^{\male} w_{Aa}^{\male} \right]/2 - w_{A}^{\male} w_{A}^{\female} w_{AA}^{\male} w_{AA}^{\female}\\
-%\psi'=&(1+\alpha^\female_\Delta) w_{A}^{\female} w_{Aa}^{\female} \left[ w_{A}^{\male} w_{AA}^{\male} + (1-\alpha_\Delta^\male) w_{a}^{\male} w_{Aa}^{\male} \right]/2 - (1-\alpha_\Delta^\male) w_{a}^{\male} w_{a}^{\female} w_{Aa}^{\male} w_{aa}^{\female}.
-%\end{split}
-%\end{equation*}
-%
-%\noindent
-%A fifth equilibrium $(C)$ also exists where $A$ is present at an intermediate frequency on the Y background ($0<\hat{p}_{Y}^{\male}<1$). 
-%However, equilibrium $(C)$ is never locally stable when $r \approx 0$ and is therefore not considered further.
-%Thus, the Y background can either be fixed for the $a$ allele (equilibria ($A$) and ($B$)) or the $A$ allele (equilibria ($A'$) and ($B'$)).
-%The X background can then either be polymorphic (equilibria ($A$) and ($A'$)) or fixed for the alternative allele (equilibria ($B$) and ($B'$)).
-%Since equilibria $(A)$ and $(B)$ are equivalent to equilibria $(A')$ and $(B')$ with the labelling of $A$ and $a$ alleles interchanged, we discuss only equilibria $(A)$ and $(B)$, in which the Y background is fixed for the $a$ allele.
-%If there is no haploid selection ($\alpha^{\circ}_\Delta=0$, $w_{A}^{\circ}=w_{a}^{\circ}=1$), these equilibria are equivalent to those found by~\cite{Lloyd1977} and~\cite{Otto2014}.
-%
-%We next calculate when equilibria $(A)$ and $(B)$ are locally stable for $r=0$. 
-%According to the `small parameter theory'~\cite{Karlin:1972ab,Karlin:1972dq}, these stability properties are unaffected by small amounts of recombination between the sex-determining locus and the $\mathbf{A}$ locus, although equilibrium frequencies may be slightly altered.
-%For the $a$ allele to be stably fixed on the Y background we need $\bar{w}_{Ya}^{\male} > \bar{w}_{YA}^{\male}$ where $\bar{w}_{Ya}^{\male} = w_{a}^{\male} \big[\hat{p}_X^\female(1-\alpha^\male_\Delta) w_{A}^{\female} w_{Aa}^{\male} + (1-\hat{p}_X^\female)w_{a}^{\female} w_{aa}^{\male} \big]$ and $\bar{w}_{YA}^{\male} = w_{A}^{\male} \big[ \hat{p}_X^\female w_{A}^{\female} w_{AA}^{\male} + (1-\hat{p}_X^\female)(1+\alpha^\male_\Delta) w_{a}^{\female} w_{Aa}^{\male} \big]$.
-%That is, Y-$a$ haplotypes must have higher fitness than Y-$A$ haplotypes.  
-%Substituting in $\hat{p}_X^\female$ from Eq \eqref{eq:tightequil}, fixation of the $a$ allele on the Y background requires that $\gamma_{i}>0$ where $\gamma_{(A)}=w_{a}^{\male} \big[ (1-\alpha^\male_\Delta) w_{Aa}^{\male} \phi + w_{aa}^{\male} \psi \big]-w_{A}^{\male} \big[ w_{AA}^{\male} \phi + (1 + \alpha^{\male}_\Delta)w_{Aa}^{\male} \psi \big]$ for equilibrium $(A)$ and $\gamma_{(B)}=(1-\alpha^{\male}_\Delta)w_{a}^{\male}w_{Aa}^{\male}-w_{A}^{\male}w_{AA}^{\male}$ for equilibrium $(B)$.
-%Stability of a polymorphism on the X background (equilibrium $(A)$) further requires that $\phi >0$ and $\psi >0$. 
-%Fixation of the $a$ allele on the X background (equilibrium $(B)$) can be stable only if equilibrium $(A)$ is not, as it requires $\psi<0$.
-%and $2w_{A}^{\female}w_{AA}^{\female}>(1-\alpha_\Delta^{\female})w_{a}^{\female}w_{Aa}^{\female}$ or just $4w_{A}^{\female}w_{AA}^{\female}<(1-\alpha_\Delta^{\female})w_{a}^{\female}w_{Aa}^{\female}$ (which also prevents $\psi>0$).
-%
-%%\textcolor{red}{check last condition and the stability condition below are correct}
-%%\textcolor{blue}{The last condition looks good to me, although in your Turnover-norec-MFS.nb you look at YA fixed, so you have to flip everything (so I made Turnover-norec-MFS-MMO.nb to do this).
-%%The one issue I can find here is that you can also prevent $\Lambda>1$ when the slope and intercept of the quadratic at $\Lambda=1$ are negative (you only looked at both being positive).
-In this case we need $4w_{A}^{\female}w_{AA}^{\female}<(1-\alpha_\Delta^{\female})w_{a}^{\female}w_{Aa}^{\female}$, which also prevents $\psi>0$.
-%%I've added this in.
-%%It could also be the case that the slope and intercept are the same sign but the roots are imaginary - but this is never the case here.
-%%Stability condition below looks good to me (from matt version of turnoverSOM-MIKE.nb).}
-%
-%\subsubsection*{Selection weak relative to recombination}
-%
-%Here, we assume that selection is weak relative to recombination ($s^\circ$, $t^\circ$, $\alpha_{\Delta}^\circ$ of order $\epsilon$). 
-%The maintenance of a polymorphism at the $\mathbf{A}$ locus then requires that
-%
-%\begin{equation}
-%\begin{split}
-%0&< - \left[(1-h^\female)s^\female +(1-h^\male) s^\male + t^\female +t^\male + \alpha_{\Delta}^\female+\alpha_{\Delta}^\male\right]\\
-%%
-%\text{and }\quad 0&<h^\female s^\female +h^\male s^\male + t^\female +t^\male + \alpha_{\Delta}^\female+\alpha_{\Delta}^\male.
-%\end{split}
-%\end{equation}
-%
-%\noindent
-%which indicates that a polymorphism can be maintained by various selective regimes. 
-%
-%Given that a polymorphism is maintained at the $\mathbf{A}$ locus by weak selection, the frequencies of $A$ in each type of gamete are the same ($\hat{p}^\female_X=\hat{p}^\male_X=\hat{p}^\male_Y=\bar{p}$) and given, to leading order, by
-%
-%\begin{equation}
-%\bar{p}=\frac{h^\female s^\female + h^\male s^\male +t^\female+t^\male+\alpha_{\Delta}^\female+\alpha_{\Delta}^\male}
-%{(2h^\female-1)s^\female+(2h^\male-1)s^\male}
-%+O(\epsilon)
-%.
-%\label{eq:pAve}
-%\end{equation}
-%
-%\noindent
-%Differences in frequency between gamete types are of $O(\epsilon)$:
-%
-%\begin{equation}
-%\begin{split}
-%\hat{p}^\male_X-\hat{p}^\female_X&=\bar{p}(1-\bar{p})\big{(}D^\male - D^\female +\alpha_{\Delta}^\male-\alpha_{\Delta}^\female \big{)}
-%+O(\epsilon^2)\\
-%%
-%\hat{p}^\male_Y-\hat{p}^\female_X&=\bar{p}(1-\bar{p})\left[D^\male - D^\female+\alpha_{\Delta}^\male-\alpha_{\Delta}^\female+(1-2r)(t^\male-t^\female)\right]/2r
-%+O(\epsilon^2)\\
-%%
-%\hat{p}^\male_Y-\hat{p}^\male_X&=\bar{p}(1-\bar{p})\left(D^\male - D^\female+\alpha_{\Delta}^\male-\alpha_{\Delta}^\female+t^\male-t^\female\right)(1-2r)/2r
-%+O(\epsilon^2),
-%\end{split}
-%\label{eq:freq_diffs}
-%\end{equation}
-%
-%\noindent
-%where $\bar{p}(1-\bar{p})=\bar{p}(1-\bar{p})$ is the variance in the frequency of $A$ and $D^\circ=\big{[} \bar{p}s^\circ+(1-\bar{p})h^\circ s^\circ\big{]} -\big{[} \bar{p}h^\circ s^\circ+(1-\bar{p}) \big{]}$ corresponds to the difference in fitness between $A$ and $a$ alleles in diploids of sex $\circ \in \{\female,\male\}$.
-%The frequency of Y-bearing male gametes depends upon the difference in the frequency of the $A$ allele between X- and Y-bearing male gametes and the strength of meiotic drive in favour of the $A$ allele in males, $q=1/2+\alpha_{\Delta}^\male(\hat{p}^\male_Y-\hat{p}^\male_X)/2+O(\epsilon^3)$.
-%Without gametic competition or drive ($\alpha_{\Delta}^\circ=t^\circ=0$) our results reduce to those of~\cite{vanDoorn:2007eu}.
-
-%\newpage
-
-%\setcounter{equation}{0}
-%\renewcommand{\theequation}{S3.\arabic{equation}}
-%
-%\section*{S3 Appendix}
-%
-%\subsection*{Invasion conditions}
-%
-%A rare neo-Y or neo-W allele, $m$, will spread in an XY sex-determining system when the leading eigenvalue, $\lambda_m^{(XY)}$, of the Jacobian matrix derived from the eight mutant recursion equations (given by \ref{eq:recursions}c,d,g,h), evaluated at the ancestral equilibrium, is greater than one.
-%However, because a neo-Y (neo-W) is always in males (females) and is epistatically dominant to the ancestral sex-determining locus, the characteristic polynomial factors into two quadratics times $(\lambda_m^{(XY)})^4$.
-%One quadratic governs the change in the frequency of the new sex determination factor associated with the $A$ and $a$ allele frequencies, summing across backgrounds at the old sex-determining locus (i.e., summing haplotypes bearing the original X and Y alleles).
-%%It is the largest root of this quadratic that determines the spread of the new $m$ allele (see details in \nameref{file:Mathematica}).  
-%The second quadratic describes the dynamics of the difference in the $m$-$A$ and $m$-$a$ haplotypes between X and Y backgrounds.  
-%Asymptotically, this difference is constrained to grow at a rate equal to or less than the sum while the $m$ allele is rare, because the frequencies can never become negative. 
-%We therefore focus on the leading eigenvalue, $\lambda_m^{(XY)}$, which is the largest root of the first quadratic $f(x) = x^2+ b x + c = 0$, as described in the text (details in \nameref{file:Mathematica}).
-%
-%When $R=0$ the two roots are $\Lambda_{mA}^{(XY)}$ and $\Lambda_{ma}^{(XY)}$, and the leading eigenvalue is the larger of the two.
-%When $R>0$ then $f(\Lambda_{mA}^{(XY)})$ and $f(\Lambda_{ma}^{(XY)})$ are of opposite signs, and the leading eigenvalue must fall between these two quantities (details in \nameref{file:Mathematica}).
-%(the Perron-Frobenius theorem guarantees that the largest eigenvalue is positive, unique, and real).
-%Thus, $\lambda_m^{(XY)}>1$ if both $\Lambda_{mA}^{(XY)}>1$ and $\Lambda_{ma}^{(XY)}>1$; similarly, $\lambda_m^{(XY)}<1$ if both $\Lambda_{mA}^{(XY)}<1$ and $\Lambda_{ma}^{(XY)}<1$.
-%If only one haplotypic growth rate is greater than one ($\Lambda_{ma}^{(XY)}<1<\Lambda_{mA}^{(XY)}$ or $\Lambda_{mA}^{(XY)}<1<\Lambda_{ma}^{(XY)}$), then $\lambda_m^{(XY)}$ is greater than one when condition \eqref{eq:lambdasGen} is met.
-%Thus, the invasion of a new sex-determining allele is determined by the haplotypic growth rates ($\Lambda_{mj}^{(XY)}$ terms), which do not account for loss due to recombination, and the rates at which recombination between the $\mathbf{M}$ and $\mathbf{A}$ loci breaks apart these haplotypes ($\chi_{mj}^{(XY)}$).
-%For tight linkage between the ancestral sex-determining locus ($\mathbf{X}$) and the selected locus ($\mathbf{A}$) we can calculate these terms explicitly (see below).
-%For weak selection we approximate the leading eigenvalue with a Taylor series. 
-%The leading eigenvalue for any $k$ is given up to order $\epsilon^2$ by Eq \eqref{eq:lambda_ESD_k}.
-%
-%\subsubsection*{Tight linkage between $\mathbf{A}$ and $\mathbf{X}$ ($r \approx 0$)}
-%
-%Here, we explore the conditions under which a neo-W invades an XY system assuming that the $\mathbf{A}$ locus is initially in tight linkage with the ancestral sex-determining locus ($r \approx 0$). 
-%We disregard neo-Y mutations, which never spread given that the ancestral population is at a stable equilibrium (see \nameref{file:Mathematica} for proof). 
-%
-%Starting with the simpler $(B)$ equilibrium, the terms that determine the leading eigenvalue are
-%
-%\begin{subequations}\label{Binvasion}
-%\begin{align}
-%\Lambda_{W'A}^{(XY)}&= {\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]}^{-1}
-%\frac{w_{A}^\female }{w_{A}^\female}
-%\frac{\left[ w_{A}^\male (1+\alpha^\male_\Delta) w_{AA}^\female + 
-%w_{a}^\male (1-\alpha^\male_\Delta) w_{Aa}^\female (1+\alpha^\female_\Delta) \right]}
-%{ 2w_{AA}^\female } \\
-%\Lambda_{W'a}^{(XY)}&= {\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]}^{-1}
-%\frac{w_{a}^\female}{w_{A}^\female}
-%\frac{\left[  w_{A}^\male (1+\alpha^\male_\Delta) w_{Aa}^\female (1-\alpha^\female_\Delta)+
-%w_{a}^\male (1-\alpha^\male_\Delta) w_{aa}^\female \right]}
-%{ 2w_{AA}^\female } \\
-%\chi_{W'A}^{(XY)}&= \frac{1}{2} {\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]}^{-1}
-%\frac{w_{A}^\female }{w_{A}^\female}
-% \frac{\left[  w_{a}^\male (1-\alpha^\male_\Delta) w_{Aa}^\female (1 + \alpha^\female_\Delta) \right]}
-%{ w_{AA}^\female } \frac{R}{2}\\
-%\chi_{W'a}^{(XY)}&= \frac{1}{2} {\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]}^{-1}
-%\frac{w_{a}^\female}{w_{A}^\female}
-% \frac{\left[  w_{A}^\male (1+\alpha^\male_\Delta) w_{Aa}^\female (1-\alpha^\female_\Delta) \right]}
-%{  w_{AA}^\female} \frac{R}{2}.
-%\end{align}
-%\end{subequations}
-%
-%%\noindent
-%%In this case, the zygotic sex ratio ($\zeta$) is given by the difference in haploid selection in males on $a$ (fixed on the Y) and $A$ (fixed on the X) alleles, i.e., there are more males than females if $\zeta = \alpha^\male w_A^\male / [(1-\alpha^\male)w_a^\male + \alpha^\male w_A^\male]<1/2$.
-%$\alpha^\male<1/2$ and/or $w_{a}^\male>w_{A}^\male$.
-%%Populations with haploid selection for $a$ in males have a male biased zygotic sex ratio are thus more permissive to invasion by a neo-W ($\Lambda_{mA}$ and $\Lambda_{ma}$ larger).
-%%%In addition, the spread of neo-W alleles depends on the fitness of female diploids after mating with an X-$A$ or Y-$a$ male gamete, relative to the fitness of females in the population (all have genotype $AA$ and fitness $w_{AA}^\female$ at this equilibrium).
-%%Haploid selection in males has a second effect; the spread rate of neo-W haplotypes is determined by their fitness in diploid females, which depends on their diploid genotype and thus on the male gamete they pair with.
-%%Zygotes carrying dominant neo-W alleles will develop as females regardless of their genotype at the XY locus. 
-%%Therefore, neo-W females result from matings with either X-$A$ or Y-$a$ male gametes. 
-%%The relative proportion of these male gametes is determined by haploid selection in males; mating with a Y-$a$ male gamete is more likely if the $a$ allele is favoured during male gamete production or competition ($\zeta<1/2$).
-%%Thus, neo-W females experience different diploid selection than XX females, and the extent of this difference depends on haploid selection in males.
-%%Furthermore, haploid selection in females can directly select upon neo-W-$A$ or neo-W-$a$ haplotypes. 
-%%A neo-W-$A$ female gamete has the same fitness during haploid competition as resident $A$-bearing female gametes. 
-%%On the other hand, neo-W-$a$ female gametes can be favoured or disfavoured during female haploid competition (favoured if $w_{a}^\female>w_{A}^\female$). 
-%%Meiotic drive in females ($\alpha^\female$) similarly affects the fitness of these neo-W haplotypes, except that it impacts both haplotypes as meiotic drive only occurs in heterozygotes and therefore does not occur in resident XX females (who are always homozygote $AA$).
-%
-%Haploid selection impacts the spread of neo-W haplotypes in three ways (also seen in Table \ref{tab:haplotype_growth}).
-%Firstly, the zygotic sex ratio becomes male biased, $\zeta>1/2$, when the $a$ allele (which is fixed on the Y) is favoured during competition among male gametes or by meiotic drive in males.
-%Specifically, at equilibrium $(B)$, female zygote frequency is $1 - \zeta = w_A^\male (1+\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$ where $2\bar{w}_{H}^\male= \big[w_a^\male (1-\alpha^\male_\Delta) +  w_A^\male (1+\alpha^\male_\Delta) \big]$ has been canceled out in equations \eqref{Binvasion} to leave the term ${\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]}^{-1}$.
-%Male biased sex ratios facilitate the spread of a neo-W because neo-W alleles cause the zygotes that carry them to develop as the rarer, female, sex. 
-%
-%Secondly, haploid selection in females selects on neo-W haplotypes directly.
-%At equilibrium $(B)$, the fitness of female gametes under the ancestral sex-determining system is $w_{A}^\female$ such that the relative fitnesses of neo-W-$A$ and neo-W-$a$ haplotypes during female gametic competition are $w_{A}^\female/w_{A}^\female$ and $w_{a}^\female/w_{A}^\female$ (see terms in equation \ref{Binvasion}).
-%Meiotic drive in females will also change the proportion of gametes that carry the $A$ versus $a$ alleles, which will be produced by heterozygous females in proportions $(1+\alpha_{\Delta}^\female)/2$ and $(1-\alpha_{\Delta}^\female)/2$, respectively.
-%These terms are only associated with heterozygous females, i.e., they are found alongside $w_{Aa}^\female$.
-%
-%Thirdly, haploid selection in males affects the diploid genotypes of females by altering the allele frequencies in the male gametes with which female gametes pair.
-%At equlibrium $(B)$, neo-W female gametes will mate with X-$A$ male gametes with probability $ w_A^\male (1+\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$ and Y-$a$ male gametes with probability $w_a^\male (1-\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$, where the $2\bar{w}_{H}^\male$ terms have been canceled in Eq \eqref{Binvasion} (as mentioned above).
-%Thus, neo-W-$A$ haplotypes are found in $AA$ female diploids with probability $ w_A^\male (1+\alpha^\male_\Delta)/ (2\bar{w}_{H}^\male)$ (e.g., first term in square brackets in the numerator of equation \ref{Binvasion}a) and in $Aa$ female diploids with probability $w_a^\male (1-\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$ (e.g., the second term in square brackets in the numerator of equation \ref{Binvasion}a).
-%
-%%For instance, because an epistatically dominant neo-W always causes its carrier to become female, it creates females who carry either Y-$a$ or X-$A$ genotypes from their father.
-%%Thus, because when there is a polymorphism the X carries some non-zero frequency of $A$, haploid selection in males impacts the diploid genotypes of females (e.g., creating more $Aa$ females when drive in males favours Y-$a$).
-%%How this affects the spread of the neo-W then depends on diploid and haploid selection in females.
-%
-%The other terms in equations \eqref{Binvasion} are more easily interpreted if we assume that there is no haploid selection in either sex, in which case $\Lambda_{W'A}^{(XY)}=(w_{AA}^\female+w_{Aa}^\female)/2 w_{AA}^\female$ and $\Lambda_{W'a}^{(XY)}=(w_{aa}^\female+w_{Aa}^\female)/ 2 w_{AA}^\female$.
-%Neither haplotype can spread under purely sexually-antagonistic selection at equilibrium $(B)$, with directional selection in each sex.
-%Essentially, the X is then already as specialized as possible for the female beneficial allele ($A$ is fixed on the X background), and the neo-W often makes daughters with the Y-$a$ haplotype, increasing the flow of $a$ alleles into females, which reduces the fitness of those females.
-%
-%If selection doesn't uniformly favour $A$ in females, however, neo-W-$A$ haplotypes and/or neo-W-$a$ haplotypes can spread ($\Lambda_{W'A}^{(XY)}>1$ and/or $\Lambda_{W'a}^{(XY)}>1$).
-%%If $\Lambda_{mA}>1$ (requiring $w_{Aa}^\female>w_{AA}^\female$), the implication is that the neo-W can spread alongside the $A$ allele, despite the fact that the neo-W sometimes brings $Y-a$ haplotypes into females, because $a$ is favoured by selection in females despite $A$ being fixed on the X.
-%A neo-W-$A$ haplotype can spread ($\Lambda_{W'A}^{(XY)}>1$) when $w_{Aa}^\female>w_{AA}^\female$, despite the fact that a neo-W brings Y-$a$ haplotypes into females.
-%In this case the $a$ allele is favoured by selection in females despite $A$ being fixed on the X background.
-%For this equilibrium to be stable (i.e.,  to keep $A$ fixed on the X), X-$a$ cannot be overly favoured in females and X-$A$ must be sufficiently favoured in males (for example, by overdominance in males).
-%Specifically, from the stability conditions for equilibrium (B), we must have $w_{Aa}^\female < 2 w_{AA}^\female$ and $w_{Aa}^\male/\big[(w_{aa}^\male+w_{Aa}^\male)/2\big]>w_{Aa}^\female/w_{AA}^\female$.
-%
-%Still considering $w_{Aa}^\female>w_{AA}^\female$, the neo-W can also spread alongside the $a$ allele ($\Lambda_{W'a}^{(XY)}>1$) if $w_{aa}^\female$ is large enough such that $(w_{Aa}^\female+w_{aa}^\female)/2>w_{AA}^\female$.
-%%there is sufficiently strong underdominance in females ($w_{aa}^\female>w_{Aa}^\female$) \textcolor{blue}{[this is describing directional selection, not overdominance - check the conditions for the case we want to talk about]}, such that $(w_{Aa}^\female+w_{aa}^\female)/2>w_{AA}^\female$.
-%This can occur with overdominance or directional selection for $a$ in females (Fig \ref{fig:regionplots}B,C).
-%In this case, $a$ is favoured on the ancestral Y background in males and on the ancestral X background in females (comparing $Aa$ to $AA$ genotypes in females) but $A$ is fixed on the X background due to selection in males.
-%The neo-W-$a$ haplotype can spread because it produces females with higher fitness $Aa$ and $aa$ genotypes. 
-%
-%%When both haplotypes can spread on their own ($\Lambda_{mA}>1$ and $\Lambda_{ma}>1$), the neo-W invades regardless the recombination rate between it and the selected locus, $R$.
-%%When neither haplotype can spread ($\Lambda_{mA}<1$ and $\Lambda_{ma}<1$) the neo-W can never invade.
-%%And when only one haplotype can spread on its own the neo-W invades only when the rate of recombination onto the favourable background is sufficiently larger than the rate of recombination off this background (i.e., equation\ref{eq:lambdasGen} is satisfied).
-%
-%%Haploid selection affects the conclusions outlined above by altering the zygotic sex ratio and exerting direct selection on neo-W haplotypes.
-%%The effect of sex-ratio selection is straightforward and can be seen in Eq \eqref{Binvasion}, where male drive and gamete competition for $a$ (which is fixed on the Y and therefore causes a male bias) increases all four terms.
-%%Direct selection on neo-W haplotypes can also be seen in Eq \eqref{Binvasion} by noticing that increasing female drive in favour of $A$ increases the neo-W-$A$ haplotype growth rate ($\Lambda_{mA}$) while female drive and gamete competition in favour of $a$ increases the neo-W-$a$ haplotype growth rate ($\Lambda_{ma}$).
-%%Gamete competition in females does not impact the spread of neo-W-$A$ haplotypes because they are on the same background as the resident X.
-%%Recombination between the selected locus and the neo-W complicates things slightly, as selective advantages for one neo-W haplotype during the haploid stage in females comes at a cost to the other, and thus recombination off the favoured background becomes more detrimental.
-%
-%%\textcolor{red}{the versions for equil $(A)$ are not terrible but could be improved by cleverly re-writing with the $\phi$ and $\psi$ terms from above, I think...}
-%
-%Similar equations can be derived for equilibrium (A) by substituting the equilibrium frequencies into Table \ref{tab:haplotype_growth}
-%
-%\begin{subequations}\label{Ainvasion}
-%\begin{align}
-%\Lambda_{W'A}^{(XY)}&= \frac{a}{b} \left[w_{AA}^\female w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi +  w_{Aa}^\female (1+\alpha^\female_\Delta) w_a^\male c \right] / (2 w_a^\female) \\
-%\Lambda_{W'a}^{(XY)}&= \frac{a}{b} \left[ w_{Aa}^\female (1-\alpha^\female_\Delta) w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi +  w_{aa}^\female w_a^\male c \right] / (2 w_A^\female) \\
-%\chi_{W'A}^{(XY)}&= \frac{a}{b} \frac{R}{2} \left[   w_{Aa}^\female (1+\alpha^\female_\Delta) w_a^\male c \right] / w_a^\female\\ 
-%\chi_{W'a}^{(XY)}&= \frac{a}{b} \frac{R}{2} \left[ w_{Aa}^\female (1-\alpha^\female_\Delta) w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi \right] / w_A^\female,
-%%\Lambda_{W'A}^{(XY)}&=   {\left[ 2 (1 - \zeta) \right]}^{-1} w_A^{\female} \left[ b w_{AA}^\female + c w_{Aa}^\female \left(1 - \alpha^\female_\Delta \right) \right]/ \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\female}_{D} \right)  \\
-%%\Lambda_{W'a}^{(XY)}&=  \\
-%%\chi_{W'A}^{(XY)}&= \\ 
-%%\chi_{W'a}^{(XY)}&=
-%\end{align}
-%\end{subequations}
-%
-%\noindent
-%where 
-%
-%\begin{subequations}
-%\begin{align}
-%a &= w_a^\female \phi + w_A^\female \psi \\
-%b &= w_{AA}^\female \left[ w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \right] \phi^2 + w_{Aa}^\female \left[ w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) + w_{aa}^\male w_a^\male \right] \psi \phi + w_{aa}^\female \left( w_{aa}^\male w_a^\male \right) \psi^2\\
-%%c &= w_{Aa}^\male (1-\alpha^\male_\Delta) \phi \left[ w_{Aa}^\male (1+\alpha^\male_\Delta) \phi \right] + w_{Aa}^\male\phi \left[ 2w_{AA}^\male + w_{aa}^\male (1+\alpha^\male_\Delta) \right] \psi + w_{aa}^\male \psi \left(2w_{AA}^\male \psi \right) \\
-%c &= w_{Aa}^\male (1-\alpha^\male_\Delta) \phi + 2w_{aa}^\male \psi.
-%\end{align}
-%\end{subequations}
-%
-%%\textcolor{red}{Sally suggests using some $\zeta$ term in the above equations}
-%%\textcolor{blue}{Maybe just reference table 2?}
-%
-%As with equilibrium (B), haploid selection again modifies invasion fitnesses by altering the ancestral sex ratio, $\zeta$ (see Table \ref{tab:haplotype_growth}), and directly selecting upon female gametes, through $w_{i}^\female$.
-%The only difference is that resident XX females are no longer always homozygote $AA$ and males are no longer always heterozygote $Aa$.
-%Thus the effect of haploid selection in males is reduced, as is the difference in fitness between neo-W haplotypes and resident X haplotypes, as both can be on any diploid or haploid background.  
-%
-%The other terms are easier to interpret in the absence of haploid selection.
-%For instance, without haploid selection, the neo-W-$A$ haplotype spreads ($\Lambda_{W'A}^{(XY)}>1$) if and only if
-%
-%\begin{equation}\label{eq:BeqWAspread}
-%2(w_{Aa}^\female-w_{aa}^\female)w_{aa}^\male \psi^2 > (w_{AA}^\female-w_{Aa}^\female)w_{Aa}^\male \phi (\phi-\psi),
-%\end{equation}
-%
-%\noindent  
-%where $\phi-\psi=w_{AA}^\female w_{Aa}^\male-w_{aa}^\female w_{aa}^\male$ and both $\phi$ and $\psi$ are positive when equilibrium (A) is stable. 
-%In contrast to equilibrium (B), a neo-W haplotype can spread under purely sexually-antagonistic selection  ($w_{aa}^\female<w_{Aa}^\female<w_{AA}^\female$ and $w_{AA}^\male<w_{Aa}^\male<w_{aa}^\male$).
-%The neo-W-$A$ can spread as long as it becomes associated with females that bear more $A$ alleles than observed at equilibrium (A), effectively specializing on female fitness. 
-%%In this case, the neo-W-$A$ haplotype can spread, despite producing a lot of $Aa$ daughters by obtaining the $a$ from Y-gametes, when $aa$ females, which the neo-W-$A$ never makes, are strongly selected against.
-%%This can be intuited from the fact that \eqref{eq:BeqWAspread} will be more easily met when $w_{Aa}^\female-w_{aa}^\female\approx w_{Aa}^\female$ and $w_{AA}^\female-w_{Aa}^\female\approx 0$, implying $w_{aa}^\female \approx 0$ and $w_{Aa}^\female\approx w_{AA}^\female$ (although this is complicated by the fact that $w_{aa}^\female$ and $w_{Aa}^\female$ affect $\phi$ and $\psi$ too, the intuition holds).
-%
-%Without haploid selection, the neo-W-$a$ haplotype spreads ($\Lambda_{W'a}^{(XY)}>1$) if and only if
-%
-%\begin{equation}\label{eq:BeqWaspread}
-%(w_{aa}^\female + w_{Aa}^\female-2w_{AA}^\female)w_{Aa}^\male \phi^2 + (w_{aa}^\female-w_{Aa}^\female)(w_{Aa}^\male+2w_{aa}^\male) \phi \psi >0.
-%\end{equation}
-%
-%\noindent
-%This condition cannot be met with purely sexually antagonistic selection (as both terms on the left-hand side would then be negative), but it can be met under other circumstances. 
-%For example, with overdominance in males there is selection for increased $A$ frequencies on the X background in males, which are always paired with Y-$a$ haplotypes.
-%Directional selection for $a$ in females can then maintain a polymorphism at the $\mathbf{A}$ locus on the X background.
-%This scenario selects for a modifier that increases recombination between the sex chromosomes (e.g., blue region of Fig 2d in~\cite{Otto2014}) and facilitates the spread of neo-W-$a$ haplotypes, which create females bearing more $a$ alleles than the ancestral X haplotype does.
-%
-%\subsubsection*{Role of haploid selection with tight linkage between $\mathbf{X}$ and $\mathbf{A}$ loci}
-%
-%Haploid selection generally expands the conditions under which neo-W alleles can spread within ancestral systems that have evolved tight linkage between the sex-determining locus and a selected locus ($r \approx 0$).
-%First, haploid selection can allow a polymorphism to be maintained when it would not under diploid selection alone (e.g., with directional selection in diploids). 
-%In cases of ploidally-antagonistic selection, where there is a balance between alleles favored in the haploid stage and the diploid stage, neo-W alleles - even if unlinked to the selected locus - can spread (\nameref{fig:regionPloidAntag}).
-%Second, even when diploid selection could itself maintain a polymorphism, haploid selection can increase the conditions under which transitions among sex-determining systems are possible.
-%Of particularly importance, when selection is sexually-antagonistic in diploids ($s^\female s^\male <0$ and $0<h^\circ<1$), an unlinked neo-W ($R=1/2$) cannot invade unless there is also haploid selection (see proof in \nameref{file:Mathematica}; Fig \ref{fig:SexAntagTighter} and \nameref{fig:SexAntagTighterMaleDrive}).
-%More generally, haploid selection alters the conditions under which neo-W alleles can spread (compare \nameref{fig:regionMaleDrive}-\nameref{fig:regionFemaleGS} to Fig \ref{fig:regionplots}). 
-%
-%%[SALLY:  I think that is enough, but we could add somewhere??: "Without haploid selection, unlinked neo-W alleles ($R=1/2$) can invade only under certain conditions, requiring either overdominance in males or underdominance in females (see proof in supplementary \textit{Mathematica} file).?
-Note that underdominance in females with directional selection in males can lead to the spread of unlinked neo-W?s, but only from equilB (only $\Lambda_{ma}$ is greater than one in this case).]
-%
-%Male haploid selection in favour of the $a$ allele ($\alpha_{\Delta}^\male<0$, $w_{A}^\male<w_{a}^\male$) generates male-biased sex ratios at equilibria (A) and (B), where Y-$a$ is fixed ($\hat{p}_{Y}^\male=0$).
-%Male-biased sex ratios facilitate the spread of neo-W-$A$ and neo-W-$a$ haplotypes (increasing $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$). 
-%Panels A-C in \nameref{fig:regionMaleDrive} and \ref{fig:regionMaleGS} show that neo-W haplotypes tend to spread for a wider range of parameters when sex ratios are male biased, compared to Fig \ref{fig:regionplots} without haploid selection.
-%By contrast, male haploid selection in favour of the $A$ allele generates female-biased sex ratios and reduces $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$, as demonstrated by panels D-F in \nameref{fig:regionMaleDrive} and \nameref{fig:regionMaleGS}.
-%
-%Female haploid selection generates direct selection on the neo-W-$A$ and neo-W-$a$ haplotypes as they spread in females. 
-%Thus, female haploid selection in favour of the $a$ allele tends to increase $\Lambda_{W'a}^{(XY)}$ and decrease $\Lambda_{W'A}^{(XY)}$, as shown by panels A-C in \nameref{fig:regionFemaleDrive} and \nameref{fig:regionFemaleGS}.
-%Conversely, female haploid selection in favour of the $A$ allele increases $\Lambda_{W'A}^{(XY)}$ and decreases $\Lambda_{W'a}^{(XY)}$, see panels D-F in \nameref{fig:regionFemaleDrive} and \nameref{fig:regionFemaleGS}.
-%
-%Thus, the impact of haploid selection on transitions between sex-determining systems must be considered as two sides of a coin: it can generate sex-ratio biases that promote transitions that equalize the sex ratio, but it can also direct select for transitions that cause sex ratios to become biased.
+}
+\label{fig:freqAll}
+\end{figure}
+%\end{landscape}
 

### 2018-06-02 LaTeX/main_final.tex
revision 2 complete by matt

--- 2018-05-21 LaTeX/main_revised.tex
@@
 
-% Extra symbols added
+% Extra symbols added (male and female)
 \usepackage{stix}
-%Three part table - I think this is allowed
+%Three part table 
 \usepackage[flushleft]{threeparttable}
@@
 %reference equations in appendices
-\usepackage{xr}
-\externaldocument{S1Appendix_revised}
-\externaldocument{S2Appendix_revised}
-\externaldocument{S3Appendix_revised}
+%\usepackage{xr}
+%\externaldocument{S1Appendix_revised}
+%\externaldocument{S2Appendix_revised}
+%\externaldocument{S3Appendix_revised}
 
@@
 % Please keep the abstract below 300 words
-%currently 308 words
+%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section*{Abstract}
+%%%%%%%%%%%%%%%%%%%%%%%%%%
 Sex determination is remarkably dynamic; many taxa display shifts in the location of sex-determining loci or the evolution of entirely new sex-determining systems. 
@@
 Variation at such loci can favour the spread of new sex-determining systems in which the heterogametic sex changes (XY to ZW or ZW to XY) and the new sex-determining region is less closely linked (or even unlinked) to the locus under selection.
-%, which is \textcolor{red}{not expected from previous theory}.
 (2) We consider selection upon haploid genotypes either during gametic competition (e.g., pollen competition) or meiosis (i.e., non-Mendelian segregation), which can cause the zygotic sex ratio to become biased.
@@
 With haploid selection, we find that transitions between male and female heterogamety can evolve where linkage with the sex-determining locus is either strengthened or weakened. 
-%Furthermore, we find that the selective strengths exerted by the sex-ratio and associations with selected alleles are often equivalent. 
 Furthermore, we find that sex-ratio biases may increase or decrease with the spread of new sex chromosomes, which implies that transitions between sex-determining systems cannot be simply predicted by selection to equalise the sex ratio.
 In fact, under many conditions, we find that transitions in sex determination are favoured equally strongly in cases where the sex ratio bias increases or decreases.
-%Furthermore, we find that the selective forces to equalize the sex ratio are equally important to selective forces that generate skewed sex ratios when accounting for the spread of new sex chromosomes.
-%This allows sex-ratio biases to increase or decrease with the spread of new sex chromosomes and implies that transitions between sex-determining systems cannot be simply predicted by selection to equalise the sex ratio.
 Overall, our models predict that sex determination systems should be highly dynamic, particularly when haploid selection is present, consistent with the evolutionary lability of this trait in many taxa.
-%Overall, our models reveal that transitions between sex-determining systems, particularly transitions where the heterogametic sex changes, can be driven by loci in previously unpredicted genomic locations that experience selection during diploid and/or haploid phases.
-%Our results predict conditions under which sex-determining systems are likely to be labile and draw connections with sex-ratio evolution.
 
@@
 % Author Summary not valid for PLOS ONE submissions.   
-%currently 193 words
+%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section*{Author summary}
+%%%%%%%%%%%%%%%%%%%%%%%%%%
 Systems of sex determination are strikingly diverse and labile in many clades. 
@@
 % Use "Eq" instead of "Equation" for equation citations.
+%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section*{Introduction}
-%TRANSITIONS ARE COMMON
+%%%%%%%%%%%%%%%%%%%%%%%%%%
 Animals and angiosperms exhibit extremely diverse sex-determining systems (reviewed in~\cite{Bull:1983vi,Charlesworth:2010it,Beukeboom:2014vb,Bachtrog:2014bx, Pennell2018}). 
-Among species with genetic sex determination (GSD), some taxa have heterogametic males (XY) and homogametic females (XX), including %non-monotreme?
-I think monotremes have XY but tonnes of translocations, giving: X1,X2...X6 Y1
-mammals and most dioecious plants~\cite{Ming:2011iy}; whereas other taxa have homogametic males (ZZ) and heterogametic females (ZW), including Lepidoptera and birds. 
+Among species with genetic sex determination (GSD), some taxa have heterogametic males (XY) and homogametic females (XX), including mammals and most dioecious plants~\cite{Ming:2011iy}; whereas other taxa have homogametic males (ZZ) and heterogametic females (ZW), including Lepidoptera and birds.
 Within several taxa, the chromosome that harbours the master sex-determining locus changes, due either to translocation of the master sex-determining locus or to the evolution of a new master locus.  
 During these transitions, the heterogametic sex can remain the same (hereafter `cis-GSD transitions') as in Salmonids~\cite{Li:2011fm,Yano:2012di}, Diptera~\cite{Vicoso:2015hf}, and \textit{Oryzias}~\cite{Myosho:2012fv}.
-%Presentation at evolution found neo sex chromosome in birds, doesn't seem to be published or bioRxiv yet (consider pers com.), title: A previously unknown neo-sex chromosome mediates plumage divergence and speciation in hybridizing birds Jason Sardell; Elizabeth Cooper; J.
-Albert C.
-Uy.
-I wonder if this is actually a fusion event though?
 Alternatively, species can switch between male and female heterogamety (XY$\leftrightarrow$ZW, hereafter `trans-GSD transitions'), as in snakes~\cite{Gamble2017}, lizards~\cite{Ezaz:2009tk}, eight of 26 teleost fish families~\cite{Mank:2006bt}, true fruit flies (Tephritids,~\cite{Vicoso:2015hf}), amphibians~\cite{Hillis:1990gu}, the angiosperm genus \textit{Silene}~\cite{Slancarova:2013dq}, the angiosperm family \textit{Salicaceae}~\cite{Pucholt2015,Pucholt2017} and Coleoptera and Hemiptera (plate 2~\cite{Beukeboom:2014vb}).
@@
 
-%MAJOR MECHANISMS
-%(1) sex-ratio selection
-%Predominant theories accounting for transitions between GSD systems by selection involve sex-ratio selection or selective differences between the sexes (e.g., sexually antagonistic selection)~\cite{Blaser2012, Beukeboom:2014vb,vanDoorn2014re}.
-%\citet{Bull:1977wt} shows that direct selection on new sex determination loci can allow them to spread and switch between male and female heterogamety. 
 It has been suggested that sex-ratio selection is a particularly dominant force in the evolution of sex determination (e.g., Bull, 1983, p 66-67 ~\cite{Bull:1983vi}; Buekeboom and Perrin, 2014, Chapter 7~\cite{Beukeboom:2014vb}).
@@
 Selection therefore typically favours mutants that increase investment in the rarer sex, including new sex determination systems.
-%Because the sex ratio is directly determined by the sex-determining system, it has been suggested that sex-ratio selection is a particularly dominant force in the evolution of sex determination (e.g., Bull, 1983, p 66-67 ~\cite{Bull:1983vi}; Buekeboom and Perrin, 2014, Chapter 7~\cite{Beukeboom:2014vb}).
-
-%MAJOR MECHANISMS
-%(2) sex-antagonism
+
 The evolution of sex determination is also thought to be strongly influenced by differences in selection between the sexes ~\cite{Blaser2012, Beukeboom:2014vb,vanDoorn2014re}.
 For example, loci experiencing sexual antagonism have been shown to favour the spread of new genetic sex-determining alleles that are closely linked~\cite{vanDoorn:2007eu,vanDoorn:2010hu,Muralidhar2018}.
-%van Doorn and Kirkpatrick~\cite{vanDoorn:2007eu,vanDoorn:2010hu} and Muralidhar and Veller~\cite{Muralidhar2018} have shown that new sex-determining alleles can be favoured if they arise at loci in close linkage with a locus that experiences sexual antagonism.
 Linkage allows a stronger favourable association to build up between a male-beneficial allele and a neo-Y allele, for example. 
 Such associations can favour cis-GSD transitions~\cite{vanDoorn:2007eu}, trans-GSD transitions~\cite{vanDoorn:2010hu}, and new partially-masculinizing or partially-feminizing alleles in a population with ESD~\cite{Muralidhar2018}.
-%However, any sexually-antagonistic loci that are more closely linked to the ancestral sex-determining locus should develop similar, favourable associations and are expected to hinder the spread of a new sex-determining system~\cite{vanDoorn:2007eu,vanDoorn:2010hu}.
 By similar logic, however, existing sexually-antagonistic alleles associated with the current sex-determining locus are expected to hinder the spread of a new sex-determining system~\cite{vanDoorn:2007eu,vanDoorn:2010hu}.
 
-%Tight linkage Model Feature and Result
 One novel feature of the models developed here is that we explicitly consider the maintenance of genetic variation around the ancestral sex-determining locus (e.g., within the non-recombining region of a sex chromosome).
-%during trans-GSD transitions
-%, when considering loci in very tight linkage with the ancestral sex-determining locus (e.g., within the non-recombining region of a sex chromosome), 
-%\textcolor{red}{[vDK2007 does "explicitly" consider this as well (although on pg 15 of their SOM they say they will ignore equilibrium A, as it is stable under a "limited range of biologically relevant parameter combinations"; perhaps haploid selection changes this impression), but only for cis-GSD transitions.
-They find that if equil B is stable the neo-Y never spreads when r=0.
-vDK2010 does not "explicitly" calculate pX and pY, which are required to see if their equation 7 is positive or negative, but nowhere do they seem to say that weaker linkage \textit{can't} evolve given r initially small.]}
-%we explicitly calculate ancestral polymorphisms. 
-%Our analysis reveals that, under various forms of selection, the ancestral-X can carry suboptimal alleles for females and/or the ancestral-Y can carry female-beneficial alleles. 
 Counterintuitively, when linkage is tight between the sex-determining locus and a selected locus, an allele good for females can be at higher frequency on the ancestral-Y than on the ancestral-X under a variety of forms of selection.
@@
 
-%Haploid selection model feature and discussion of why needed
 Most significantly, we include haploid selection (gametic competition or meiotic drive) in models describing cis-GSD, trans-GSD, and GSD to ESD transitions.
@@
 
-%Previous models with haploid selection
 Two previous studies have considered the spread of GSD with sex-limited meiotic drive~\cite{Kozielska:2010vm,Ubeda:2015fx} under a limited number of possible genetic architectures and diploid selective regimes.
@@
 For example, a masculinizing allele spreads in association with an allele that is favoured during male meiosis, causing sex ratios to become male-biased.
-This suggests that the benefits of associating with driving alleles can overwhelm selection to balance the sex ratio. %, at least when new sex-determining alleles are rare. 
+This suggests that the benefits of associating with driving alleles can overwhelm selection to balance the sex ratio.
 However, Kozielska et al. (2010)~\cite{Kozielska:2010vm} considered an ancestral GSD system that is perfectly linked to a meiotic driver and therefore exhibiting an ancestral sex ratio bias. 
@@
 
-%main results
 Here, we analytically find the conditions under which new GSD or ESD systems spread in ancestral GSD systems with any degree of linkage between the loci involved and arbitrary forms of haploid and diploid selection.
@@
 Finally, we show that ESD may not evolve, even if the sex ratio is initially biased by haploid selection, which is not predicted by previous theories for transitions to ESD~\cite{Charnov:1982wg,Bull:1983vi,West:2009we}.
-%Together, our results suggest that neither selection to equalize the sex ratio nor the benefits of associating with haploid selected alleles is an overwhelming force driving transitions between sex-determining systems.
 Together, our results suggest that both selection to equalize the sex ratio and the benefits of associating with haploid selected alleles can drive transitions between sex-determining systems, leading to stronger or weaker sex-linkage and increased or decreased sex ratio bias.
 
-%Here we use mathematical models to find the conditions under which new sex-determining systems spread when individuals experience selection at both diploid and haploid stages, which allows fitness differences between the sexes and sex ratio biases to occur simultaneously
-
-%Haploid selection results
-
-%The sex ratio is directly determined by the sex-determining system, and it has therefore been suggested that sex-ratio selection is a dominant force in the evolution of sex determination (e.g., Bull, 1983, p 66-67 ~\cite{Bull:1983vi}; Buekeboom and Perrin, 2014, Chapter 7~\cite{Beukeboom:2014vb}).
-%`Fisherian' sex-ratio selection favours a 1:1 zygotic sex ratio when assuming that males and females are equally costly to produce~\cite{Fisher:1930wy,Charnov:1982wg}.
-%This follows from the fact that, for an autosomal locus, half of the genetic material is inherited from a male and half from a female~\cite{West:2009we}. 
-%Thus, if the sex ratio is biased, an individual of the rarer sex will, on average, contribute more genetic material to the next generation. 
-%Selection therefore favours mutants that increase investment in the rarer sex.
-
-%The default mode of sex-ratio selection is `Fisherian' sex-ratio selection, which favours equal investment in male and female offspring \citep[i.e., a 1:1 zygotic sex ratio when assuming that males and females are equally costly to produce,][]{Fisher:1930wy,Charnov:1982wg}.
-%Given that the sex-determining system can directly affect the sex ratio, we might expect Fisherian sex-ratio selection to influence the spread of new sex-determining systems. 
-%In the case of sex-chromosome evolution, Kozielska et al.
-(2010)~\cite{Kozielska:2010vm} consider systems in which the ancestral sex chromosomes experience meiotic drive (e.g., where driving X or Y chromosomes are inherited disproportionately often), which causes sex ratios to become biased~\cite{Hamilton:1967ts}.
-%They find that masculinizing or feminizing mutations that arise at a new, unlinked locus (i.e., neo-Y or neo-W chromosomes) can then spread, which restore an even sex ratio. 
-%However, starting from ESD, Ubeda et al.
-(2015)~\cite{Ubeda:2015fx} have numerically shown that sex-specific meiotic drive can allow masculinizing and feminizing mutations to spread (i.e., ESD $\rightarrow$ GSD) despite causing a sex-ratio bias.
-
-%HOLES IN CURRENT THEORY
-%(1) haploid selection; it exists in many spp
-%While both opposing selection in the diploid sexes and sex-ratio selection surely influence the evolution of new sex-determining factors, so too might selection in the haploid phase.
-
-%HOLES IN CURRENT THEORY
-%(2) haploid selection; it can complicate outcomes for SD transitions
-%There are various ways by which haploid selection could influence transitions between sex-determining systems. 
-%If we assume that haploid selection at any particular locus predominantly occurs in one sex (e.g., meiotic drive during spermatogenesis), then such loci experience a form of sex-specific selection. 
-%In this respect, we might expect that haploid selection would affect transitions between sex-determining systems in a similar manner to sex-specific diploid selection (as explored in~\cite{vanDoorn:2007eu,vanDoorn:2010hu}).
-%That is, new masculinizing mutations (neo-Y alleles) could be favoured via associations with alleles that are beneficial in the male haploid stage (e.g., \cite{Ubeda:2015fx}). 
-%Kozielska et al.
-(2010)~\cite{Kozielska:2010vm} have shown this to be theoretically possible for the special case of perfect linkage between the new sex-determining locus and a locus that experiences meiotic drive in one sex, under a limited number of forms of diploid selection.
-%Similarly, Ubeda et al.
-(2015)~\cite{Ubeda:2015fx} numerically show that sex-specific meiotic drive can allow masculinizing and feminizing mutations to spread in an ancestrally environmental-sex-determination system, again under a limited number of forms of diploid selection.
-%On the other hand, sex ratios can also become biased by linkage between the sex-determining locus and a locus that harbours genetic variation in haploid fitness, as indeed occurs in the two examples above.
-%There are also several known empirical cases of sex-ratio bias caused by sex-linked meiotic drive alleles (Burt and Trivers, 2006, Chapter 6~\cite{Burt:2006}) or selection among X- and Y-bearing pollen~\cite{Lloyd:1974tz,Conn:1981uw,Stehlik:2005ul,Stehlik:2006to,Field:2012fd,Field:2013cc}.
-%Sex-ratio selection can thus select against the spread of linked sex-determining alleles and favour the invasion of alternative, unlinked sex-determination systems \cite{Kozielska:2010vm,Ubeda:2015fx}.
-%It is not yet clear when new sex-determining alleles are favoured by associations with haploid selected alleles vs.
-sex-ratio bias, especially under a wide range of possible diploid selection regimes (e.g., sex-antagonism, overdominance).
-
-%We consider both selected loci that are loosely linked to the sex-determining region (e.g., on an autosome) and selected loci that are in very tight linkage with the ancestral sex-determining locus (e.g., within the non-recombining sex-determining region).
-%Our main findings are three:
-%(1) transitions between sex-determining systems can decrease or increase sex-ratio bias, and with sufficiently loose linkage between the selected locus and the sex-determining locus, the selective force exerted by sex-ratio selection and favourable associations with haploid-selected alleles are exactly equivalent;
-%(2) ancestrally-tight sex-linkage and haploid selection allow trans-GSD transitions that weaken sex-linkage; and
-%(3) haploid selection removes the need for sex-antagonism, increasing the range of scenarios that select for transitions between sex-determining systems.
-
-%MAIN FINDINGS IN GENERAL TERMS
-%We find that the spread of novel sex-determining systems is influenced by both Fisherian sex-ratio selection and by selection on linked alleles. 
-%We find that sex-ratio biases caused by haploid selection can exert Fisherian sex-ratio selection upon novel sex-determiners but that their spread is also determined by selection on genetically-associated alleles.
-%Indeed, it is only when haploid-selected loci are tightly linked to the ancestral sex-determining region (and so sex-ratio biases are initially large) that we see an asymmetry between selection for XY to ZW transitions and ZW to XY transitions (e.g., because haploid selection in males only causes biased zygotic sex ratios in an ancestrally XY system).
-%Fisherian sex-ratio selection does not always dominate; it is possible for selection on linked alleles to drive turnover between sex-determining systems despite causing increasingly biased sex ratios, and our analytical results elucidate what is required for this to be so.
-%Because sex-determining loci are often found within a region of suppressed recombination, there can be a significant number of tightly linked loci. 
-%We find that loci tightly linked with the sex-determining locus can drive transitions in which the heterogametic sex changes, even when the new sex-determining locus is less closely linked to loci under selection (either including haploid selection or not).
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section*{Model}
-
-%genetic system
+%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 We consider transitions between ancestral and novel sex-determining systems using a three-locus model, each locus having two alleles (Fig \ref{fig:model_outline}).
@@
 To evaluate the evolution of new sex-determining systems, we consider the spread of a novel sex-determining allele ($m$) at the $\mathbf{M}$ locus.
-%We only do invasion analytically though (is this sentence still ok?)
 
@@
 Nevertheless, our supplementary analysis file (\nameref{file:Mathematica}) allows other dominance relationships between loci to be specified (see also \cite{vanDoorn:2007eu} supplementary material for a numerical analysis).
-%See also the supplementary material in \cite{vanDoorn:2007eu} for a numerical analysis that relaxes the assumption of epistatic dominance.
-%We also analyze a model of maternally-controlled environmental sex-determination, where mothers with at least one $m$ allele produce daughters with probability $k$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Model Outline
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \begin{figure}[!h]
 %\centering
-\centerline{\includegraphics[width=0.9\linewidth]{../Plots/Sex_determination_outline.pdf}}
+%\centerline{\includegraphics[width=0.9\linewidth]{../Plots/Sex_determination_outline.pdf}}
 \caption{
@@
 Panel A: Recombination rate parameters between the ancestral-sex-determining locus ($\mathbf{X}$, here assumed to have alleles X and Y), a locus under selection ($\mathbf{A}$, with alleles $A$ and $a$), and a new sex-determining locus ($\mathbf{M}$, with alleles $M$ and $m$).
-%If $r<1/2$, then associations between ancestral sex-determining alleles and selected alleles can be present in new male gametes/gametophytes. 
 Panel B: Haploid selection is often sex-limited, occurring during haploid production or competition in one sex (shown here in males by dashed circles). 
@@
 \end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 In each generation, we census the genotype frequencies in male and female gametes before gametic competition. 
-%Below, it is convenient to follow the ancestral equilibrium frequency of the $A$ allele among female gametes (eggs), $\hat{p}^\female_X$, and among X-bearing, $\hat{p}^\male_X$, and among Y-bearing, $\hat{p}^\male_Y$, male gametes (sperm/pollen).
-%We also track the ancestral fraction of male gametes that are Y-bearing, $\hat{q}_{Y}$, which may deviate from $1/2$ due to meiotic drive in males. 
-%
 After gametic competition, conjugation between male and female gametes occurs at random.
 The resulting zygotes develop as males or females, depending on their genotypes at the $\mathbf{X}$ and $\mathbf{M}$ loci. 
-%(and the $\mathbf{M}$ genotype of their mother in the case of maternal control).
 Diploid males and females then experience viability and/or individual-based fertility selection, with relative fitnesses $w_{AA}^{\circ}$, $w_{Aa}^{\circ}$, and $w_{aa}^{\circ}$. 
-%where $g$ is the diploid genotype at the $\mathbf{A}$ locus ($g \in \{AA, Aa, aa\}$).
 We do not consider fertility selection that depends on the mating partner, e.g., sexual selection with variation in choosiness. 
@@
 Our model is entirely deterministic and hence ignores chance fluctuations in allele frequencies due to genetic drift.
-%During the , the $\mathbf{A}$ locus can experience sex-specific gametic competition, diploid selection, and/or meiotic drive.
 
 \begin{table}[ht]
-%\centering
 \smallskip
@@
 
-The model outlined above describes both ancestral XY and ZW sex-determining systems. %if we relabel the two sexes as being ancestrally `heterogametic' or ancestrally `homogametic'. 
+The model outlined above describes both ancestral XY and ZW sex-determining systems. 
 Without loss of generality, we refer to the ancestrally heterogametic sex as male and the ancestrally homogametic sex as female.
@@
 The evolution of a new sex-determining system requires that a rare mutant allele, $m$, at the novel sex-determining locus, $\mathbf{M}$, increases in frequency when rare. 
-Specifically, $m$ invades when $\lambda_m^{(XY)}>1$, where $\lambda_m^{(XY)}$ is the leading eigenvalue of the system of eight equations describing $m$-bearing gamete frequencies, \ref{eq:recursions}.
-%This is determined by the leading eigenvalue ($\lambda_m^{(XY)}$) of the system of eight equations describing the frequency of eggs and sperm carrying the $m$ allele in the next generation (equations \ref{eq:recursions}).
+Specifically, $m$ invades when $\lambda_m^{(XY)}>1$, where $\lambda_m^{(XY)}$ is the leading eigenvalue of the system of eight equations describing $m$-bearing gamete frequencies, Eqs S1.1. 
 This system simplifies substantially for an epistatically dominant neo-Y ($k=0$) or neo-W ($k=1$), see \nameref{app:inv_cond} for details.
-%We will consider only equilibrium frequencies of alleles, $\hat{p}^\circ_i$, and Y-bearing male gametes, $\hat{q}_{Y}$, when calculating the eigenvalues.
 
@@
 \begin{equation}\label{eq:lambdasGen}
-%\frac{\chi_{mA}}{\Lambda_{mA}-1}+\frac{\chi_{ma}}{\Lambda_{ma}-1}>0.
 \chi_{ma}^{(XY)}/\left(\Lambda_{ma}^{(XY)} - 1\right) + \chi_{mA}^{(XY)}/\left(\Lambda_{mA}^{(XY)} - 1\right) < 1.
@@
 Condition \ref{eq:lambdasGen} may or may not be satisfied for the full range of locations of the new sex-determining locus, including $R=1/2$ (e.g., on an autosome), depending on the nature of selection.
-Interpreting this condition, if we assume that only the $mA$ haplotype would increase in frequency when $R=0$ (i.e., $\Lambda_{ma}^{(XY)}<1<\Lambda_{mA}^{(XY)}$), then the first term on the left-hand side of \eqref{eq:lambdasGen} is negative and invasion requires that growth rate of $mA$ haplotypes ($\Lambda_{mA}^{(XY)}-1>0$) and the rate at which they are produced by recombination ($\chi_{ma}^{(XY)}$) are sufficiently large relative to the rate of decline of $ma$ haplotypes ($1-\Lambda_{ma}^{(XY)}>0$) and the rate at which $m$ and $A$ are dissociated by recombination ($\chi_{mA}^{(XY)}$).
-
-%The leading eigenvalue for a rare neo-Y or neo-W allele, $m\in\{Y',W'\}$, is the largest value of $x$ that solves $x^2+ b x + c = 0$.  %$(\lambda_m^{(i)})^2+ b \lambda_m^{(i)} + c =0$. 
-%The coefficients are $b= - (\Lambda_{mA}^{(XY)} + \Lambda_{ma}^{(XY)})+(\chi_{mA}^{(XY)} + \chi_{ma}^{(XY)})$ and $c = (\Lambda_{mA}^{(XY)} - \chi_{mA}^{(XY)}) (\Lambda_{ma}^{(XY)} - \chi_{ma}^{(XY)}) - \chi_{mA}^{(XY)} \chi_{ma}^{(XY)}$, where $\Lambda_{mi}^{(XY)}>0$ is the multiplicative growth rate (which we will call the ``haplotypic growth rate'') of the neo-sex determination allele $m$ on background $i\in\{A,a\}$ without accounting for loss due to recombination ($R=0$), and $\chi_{mi}^{(XY)}>0$ is the rate at which mutant haplotypes on background $i\in\{A,a\}$ recombine onto the other $\mathbf{A}$ locus background in heterozygotes (proportional to $R$; we call this the ``dissociative force" as it breaks down linkage disequilibrium), see Table \ref{tab:haplotype_growth}.
-%In the ancestral population, it is convenient to follow the frequency of the $A$ allele among female gametes (eggs), $p^\female_X$, and among X-bearing, $p^\male_X$, and among Y-bearing, $p^\male_Y$, male gametes (sperm/pollen).
-%We also track the fraction of male gametes that are Y-bearing, $q$, which may deviate from $1/2$ due to meiotic drive in males. 
-%We will consider only equilibrium frequencies of alleles, $\hat{p}^\circ_i$, and Y-bearing male gametes, $\hat{q}_{Y}$, when calculating the eigenvalues.
-
-%The evolution of a new sex-determining system depends on the growth rate of a rare mutant allele, $m$, at the novel sex-determining locus, $\mathbf{M}$. %, increases in frequency when rare. 
-%This growth rate is determined by the leading eigenvalue ($\lambda_m^{(XY)}$) of the system of eight equations describing the frequency of eggs and sperm carrying the $m$ allele in the next generation (equations \ref{eq:recursions}).
-%, evaluated at the above equilibrium.
-%Thus, the system describing the change in frequency of the $m$ allele consists of eight recursion equations. 
-%This system simplifies substantially for an epistatically dominant neo-Y ($k=0$) or neo-W ($k=1$), see \nameref{app:inv_cond}. 
-%The leading eigenvalue for a rare neo-Y or neo-W allele, $m\in\{Y',W'\}$, is the largest value of $x$ that solves $x^2+ b x + c = 0$, where $b= - (\Lambda_{mA}^{(XY)} + \Lambda_{ma}^{(XY)})+(\chi_{mA}^{(XY)} + \chi_{ma}^{(XY)})$ and $c = (\Lambda_{mA}^{(XY)} - \chi_{mA}^{(XY)}) (\Lambda_{ma}^{(XY)} - \chi_{ma}^{(XY)}) - \chi_{mA}^{(XY)} \chi_{ma}^{(XY)}$.
-%The variable $\Lambda_{mi}^{(XY)}>0$ is the multiplicative growth rate of the neo-sex-determining allele $m$ on background $i\in\{A,a\}$ without accounting for loss due to recombination ($R=0$).
-%We will call  $\Lambda_{mi}^{(XY)}$ the ``haplotypic growth rate''.
-%The variable $\chi_{mi}^{(XY)}>0$ is the rate at which mutant haplotypes on background $i\in\{A,a\}$ recombine onto the other $\mathbf{A}$ locus background in heterozygotes (proportional to $R$).
-%We call $\chi_{mi}^{(XY)}$ the ``dissociative force", as it breaks down linkage disequilibrium.
-%Both variables are listed in Table \ref{tab:haplotype_growth} for neo-Y and neo-W mutants.
+Interpreting this condition, if we assume that only the $mA$ haplotype would increase in frequency when $R=0$ (i.e., $\Lambda_{ma}^{(XY)}<1<\Lambda_{mA}^{(XY)}$), then the first term on the left-hand side of Eq \eqref{eq:lambdasGen} is negative and invasion requires that growth rate of $mA$ haplotypes ($\Lambda_{mA}^{(XY)}-1>0$) and the rate at which they are produced by recombination ($\chi_{ma}^{(XY)}$) are sufficiently large relative to the rate of decline of $ma$ haplotypes ($1-\Lambda_{ma}^{(XY)}>0$) and the rate at which $m$ and $A$ are dissociated by recombination ($\chi_{mA}^{(XY)}$).
 
@@
 \smallskip
-%\caption{Parameters determining invasion (equation \ref{eq:charpoly_neoY}) for neo-Y or neo-W alleles}
 \caption{ {\bf Parameters determining invasion of mutant neo-Y and neo-W alleles into an ancestrally XY system}}
@@
 $\hat{q}_{Y}$ is the frequency of Y-bearing male gametes. 
-%      \item $R$ is the probability of recombination between loci $\mathbf{A}$ and $\mathbf{M}$.
 $\zeta$ is the zygotic sex ratio (fraction male).
@@
 
-%The new sex-determining allele increases in frequency when rare when the largest eigenvalue is greater than one ($\lambda_m^{(XY)}>1$). 
-%If the average change in frequency of the two haplotypes that carry the $m$ allele ($Am$ and $am$) is positive, invasion will always occur, i.e., if $(\Lambda_{mA} + \Lambda_{ma})/2 > 1$ then $\Lambda > 1$.
-%The leading eigenvalue is the largest solution of $f(\lambda_m^{(i)})=(\lambda_m^{(i)})^2+b\lambda_m^{(i)}+c=0$ and the Perron-Frobenius theorem guarantees that it is positive, unique, and real.  
-%Since $f(\Lambda_{mA}^{(i)})$ and $f(\Lambda_{ma}^{(i)})$ are of opposite signs, the leading eigenvalue must fall between these two quantities and is the larger of them when $R = 0$ (see \nameref{file:Mathematica}).
-%If both haplotypic growth rates are greater than one ($\Lambda_{mA}^{(XY)}, \Lambda_{ma}^{(XY)}>1$), then the new sex-determining allele invades regardless of the rate of recombination between the new sex-determining locus and the selected locus ($R$), see \nameref{app:inv_cond} for details.
-%Conversely, if both haplotypic growth rates are less than one ($\Lambda_{mA}^{(XY)}, \Lambda_{ma}^{(XY)}<1$), then invasion can never occur.  
-%Finally, if only one haplotypic growth rate is greater than one, the new sex-determining allele can always invade when arising at a locus that is tightly linked to the selected locus ($R\approx0$).  
-%Furthermore, it can be shown that the leading eigenvalue declines with $R$, and invasion requires that $R$ is sufficiently small such that: 
-%\begin{equation}\label{eq:lambdasGen}
-%\frac{\chi_{mA}}{\Lambda_{mA}-1}+\frac{\chi_{ma}}{\Lambda_{ma}-1}>0.
-%\chi_{ma}^{(XY)}/\left(\Lambda_{ma}^{(XY)} - 1\right) + \chi_{mA}^{(XY)}/\left(\Lambda_{mA}^{(XY)} - 1\right) < 1.
-%\end{equation}
-%\noindent 
-%This condition may or may not be satisfied for the full range of locations of the new sex-determining locus, including $R=1/2$, depending on the nature of selection.  
-%Interpreting this condition, if we assume that only the $mA$ haplotype would increase in frequency when $R=0$ ($\Lambda_{ma}^{(XY)}<1<\Lambda_{mA}^{(XY)}$) then the first term on the left-hand side of \eqref{eq:lambdasGen} is negative and invasion requires that growth rate of $mA$ haplotypes ($\Lambda_{mA}^{(i)}-1>0$) and the rate at which they are produced by recombination ($\chi_{ma}^{(i)}$) are sufficiently large relative to the rate of decline of $ma$ haplotypes ($1-\Lambda_{ma}^{(i)}>0$) and the rate at which $m$ and $A$ are dissociated by recombination ($\chi_{mA}^{(i)}$).
-
 The haplotypic growth rates and dissociative forces are listed in Table \ref{tab:haplotype_growth} for a neo-Y and neo-W invading an ancestrally XY system.
@@
 This is because a dominant neo-Y (neo-W) is always found in males (females), and therefore the frequency of the neo-Y (neo-W), $m$, only changes in males (females), Fig \ref{fig:model_outline}C,D.
-%Beyond the direct effects of selection, there are also indirect effects caused by past selection molding the equilibrium allele frequencies ($\hat{p}^\circ_i$ terms), which generally do depend on selection in both sexes.
 (3) Haploid selection thus plays two roles, generating Fisherian selection to equalize the ancestral sex-ratio (through $\zeta$) and generating selection for the neo-Y/neo-W through associations with haploid selected loci, which can distort the sex ratio.
@@
 Polymorphisms can be maintained by mutation-selection balance or occur transiently during the spread of beneficial alleles. 
-%However, polymorphisms maintained by selection can maintain alleles at intermediate allele frequencies for longer periods. 
 Here, however, we focus on polymorphisms maintained by selection for longer periods. 
-%where the $A$ allele reaches a stable intermediate equilibrium frequency under the ancestral sex-determining system before the new sex-determining allele ($m$) arises. 
 Such polymorphisms can be maintained by heterozygote advantage, sexually-antagonistic selection, ploidally-antagonistic selection, or a combination~\cite{Immler:2012tl}.
@@
 
-%\textcolor{red}{note: vD\&K (2010) use a QLE and therefore point out that their results does not require equilibria maintained by sexually antagonistic selection, only differences in fitness between male and females ($s^\male\neq s^\female$).
-e.g., during a sweep of a positive beneficial mutation, a new SDR can spread because it generates a stronger association with the sex that is favoured the most (e.g., putting the selected allele more often in females and  $s^\male< s^\female$).
-This is only transient, and most of the time during sweeps or mutation-selection balance, $V_A$ is small so the importance is probably small.
-}
-
 \subsection*{Tight linkage with the ancestral sex-determining locus ($r \approx 0$)}
@@
 When there is complete linkage between the ancestral sex-determining locus and the selected locus $\mathbf{A}$ ($r=0$), either the $A$ allele or the $a$ allele must be fixed in gametes containing a Y allele (\nameref{app:eq_stab}).
-% because selection on the Y is effectively haploid an incapably of maintaining a polymorphism in the absence of frequency dependent selection. 
 Because the labelling of alleles is arbitrary, we will assume that the $a$ locus is fixed in gametes with a Y ($p^\male_Y=0$), without loss of generality. 
 If there are two alleles maintained at the $\mathbf{A}$ locus, the $A$ allele can be fixed ($\hat{p}^\female_X=\hat{p}^\male_X=1$) or segregating at an intermediate frequency (0<$\hat{p}^\female_X, \hat{p}^\male_X$<1) in gametes with an X.
-%However, because the X is present in both males and females, there are distinct selection pressures on X's in females and X's in males, which will always be paired with an $A$ allele from the Y.
 
 We find that a neo-Y allele can never invade an ancestral XY system that already has tight linkage with the locus under selection ($\lambda_{Y'}^{(XY)} \leq 1$ when $r=0$; for details see \nameref{file:Mathematica}).
-%When $R=0$, a neo-Y haplotype with the same allele as the ancestral Y is neutral ($\Lambda_{Y'a}^{(XY)}=1$) and does not change in frequency.
-%The other neo-Y haplotype will not spread ($\Lambda_{Y'A}^{(XY)}<1$) given that the initial equilibrium is stable. 
-%Therefore, a neo-Y mutation cannot spread in an ancestral XY system ($\lambda_{Y'}^{(XY)} \leq 1$, regardless of $R$) where selected loci are within or very near the non-recombining region around the sex-determining locus.
 In essence, through tight linkage with the $\mathbf{A}$ locus, the ancestral Y becomes strongly specialized on the allele that has the highest fitness across male haploid and diploid phases. 
@@
 
-Neo-W alleles, on the other hand, can invade an ancestral XY system (the full invasion conditions are given in \nameref{app:inv_cond}; equations \ref{Binvasion} and \ref{Ainvasion}).
+Neo-W alleles, on the other hand, can invade an ancestral XY system (the full invasion conditions are given in \nameref{app:inv_cond}; Eqs S3.1 and S3.2).
 Invasion occurs when neo-W females can have higher fitness than the XX females in the ancestral population.
@@
 \noindent\textit{Conclusion 1:}
-%\textbf{selection on loci within the non-recombining region around the sex-determining locus ($r\approx0$) allows the invasion of less closely linked sex-determining alleles ($r<R\leq1/2$) during a trans-GSD transition} (XY $\leftrightarrow$ ZW).
 \textbf{Selection on loci in or near the non-recombining region around the ancestral sex-determining locus ($r\approx0$) prevents cis-GSD transitions (XY $\leftrightarrow$ XY, ZW $\leftrightarrow$ ZW) but can spur trans-GSD transitions (XY $\leftrightarrow$ ZW).}
-%\textcolor{red}{[Not clear from van Doorn \& Kirkpatrick 2007, 2010]}
 \vspace{0.5cm}
 
-%Essentially, neo-W alleles are able to invade (even with $R>r$) because the ancestral X experiences selection in males. 
-%This can lead to (1) XX females having lower than maximum fitness ($\Lambda_{W'A}^{(XY)}>1$) and/or (2) the Y carrying alleles that are beneficial in females. 
 \noindent 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Both neo-W haplotypes can spread, in the absence of haploid selection, when there is overdominance
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}[!h]
 \centering
-%\centerline{\includegraphics[width=1.25\linewidth]{Region_plot_combined_Mike}}
-\centerline{\includegraphics[width=1.4\linewidth, right]{../Plots/Region_plot_combined.eps}}
+%\centerline{\includegraphics[width=1.4\linewidth, right]{../Plots/Region_plot_combined.eps}}
 \caption{
@@
 The parameter values marked with an asterisk correspond to the fitnesses used in Fig \ref{fig:SexAntagTighter}C. 
-%Where both haplotypic growth rates are greater than one, a neo-W will spread when rare, regardless of linkage with the selected locus (for any $R$). 
 \nameref{fig:positionOverdominance} shows the dynamics arising with the parameters marked with a dagger. 
-%Here, there is no haploid selection $t^\circ = \alpha^\circ_\Delta = 0$.
 }
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Tight linkage allows looser sex-linkage to evolve, even in absence of haploid selection
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}[!h]
 \centering
-\centerline{\includegraphics[width=1.4\linewidth, right]{../Plots/PositionPlot_SexAntagTighter.eps}}
+%\centerline{\includegraphics[width=1.4\linewidth, right]{../Plots/PositionPlot_SexAntagTighter.eps}}
 \caption{
@@
 A very loosely linked neo-W does not spread in this case (blue and green lines overlap and go to 0 in inset). 
-Fitness parameters are: $w_{AA}^\female = 1.05$, $w_{aa}^\male = 1.2$, $w_{aa}^\female = w_{AA}^\male = 0.85$, $w_{Aa}^\circ = 1$.%,  $t^\circ = \alpha^\circ_\Delta = 0$.
-%\textcolor{red}{consider removing panel A, which is repeated in Fig 3.}
-%\textcolor{blue}{probably better to remove from panel 3, eh?}
+Fitness parameters are: $w_{AA}^\female = 1.05$, $w_{aa}^\male = 1.2$, $w_{aa}^\female = w_{AA}^\male = 0.85$, $w_{Aa}^\circ = 1$.
 }
@@
 \end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 Assuming selection is weak relative to recombination, van Doorn and Kirkpatrick~\cite{vanDoorn:2010hu} showed that invasion by a neo-W allele occurs under the same conditions as its fixation in females.
-%`pseudo-fixation' (at pseudo-fixation the neo-W reaches its maximum frequency among eggs, which is usually 1/2, but can deviate from 1/2 when there is haploid selection before censusing). 
 An equivalent analysis is not possible where recombination rates are low. 
@@
 Here we assume that selection is weak ($s^\circ$, $t^\circ$, $\alpha_{\Delta}^\circ$ of order $\epsilon$, where $\epsilon$ is some number much less than one) and thus implicitly assume that all recombination rates ($r$, $R$ and $\rho$) are large relative to selection.
-%, we denote the leading eigenvalues describing the invasion of a neo-Y ($k=0$) and a neo-W ($k=1$) into an ancestrally XY system by $\lambda_{Y',XY}$ and $\lambda_{W',XY}$, respectively. 
 To leading order in selection,
@@
 \noindent
-where $\bar{p}$ is the frequency of $A$, to leading-order (Eq \ref{eq:pAve}), and $S_{A}=(\bar{s}^\male +\alpha_{\Delta}^\male+t^\male) - (\bar{s}^\female+\alpha_{\Delta}^\female+t^\female)$ describes sex differences in selection for the $A$ versus $a$ allele across diploid selection, meiosis, and gametic competition.
+where $\bar{p}$ is the frequency of $A$, to leading-order (Eq S2.3), and $S_{A}=(\bar{s}^\male +\alpha_{\Delta}^\male+t^\male) - (\bar{s}^\female+\alpha_{\Delta}^\female+t^\female)$ describes sex differences in selection for the $A$ versus $a$ allele across diploid selection, meiosis, and gametic competition.
 The diploid selection term, $\bar{s}^\circ=\big{[} \bar{p}s^\circ+(1-\bar{p})h^\circ s^\circ\big{]} -\big{[} \bar{p}h^\circ s^\circ+(1-\bar{p}) \big{]}$, is the difference in fitness between $A$ and $a$ alleles in diploids of sex $\circ \in \{\female,\male\}$.
@@
 
-%The new sex-determining allele, $m$, will spread in an XY system if $\lambda_{m}^{(XY)}>1$. 
 Eq \eqref{eq:lambda_neoY} demonstrates that, under weak selection, a neo-Y allele will invade an XY system ($\lambda_{Y'}^{(XY)}>1$) if and only if it is more closely linked to the selected locus than the ancestral sex-determining locus (i.e., if $R<r$).
-%; note that $\bar{p}(1-\bar{p})S_{A}^2$ is strictly positive as long as $\mathbf{A}$ is polymorphic).
 This echoes our results above where a neo-Y could never invade if $r\approx0$. 
 It is also consistent with the results of \cite{vanDoorn:2007eu}, who considered diploid selection only and also found that cis-GSD transitions can only occur when the new sex-determining locus is more closely linked to a locus under sexually-antagonistic selection.
-%Because tighter linkage between the sex-determining region and a selected locus evolves during these transitions, stronger associations between selected alleles and diploid sexes can build up by selection (e.g., between male-beneficial alleles and the male-determining allele, Y).%, increasing diploid mean fitness (Fig \ref{fig:Combination_MeanFit}).
 
@@
 \noindent
-%Similarly, a neo-W is typically favoured when it is more closely linked to the selected locus than the ancestral sex-determining region is, ($R<r$).
 Similarly, in the absence of haploid selection ($t^\circ=\alpha^\circ_{\Delta}=0$), Eq \eqref{eq:lambda_neoW} indicates that trans-GSD transitions can occur if and only if the new sex-determining locus is more closely linked to a locus under selection, $R<r$, as found by \cite{vanDoorn:2010hu}.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%A neo-W can invade an XY system under a large number of selective regimes
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}[!h]
 \centering
-\includegraphics[width=\linewidth]{../Plots/PositionPlot.eps}
+%\includegraphics[width=\linewidth]{../Plots/PositionPlot.eps}
 \caption{
@@
 In panel A, male drive ($\alpha^\male_{\Delta} = -1/20$, $t^\circ = \alpha^\female_{\Delta} = 0$) opposes selection in diploids (no sex-differences: $s^\circ = 1/10$, $h^\circ = 7/10$).   
-%, in which case the new sex-determining allele can invade regardless of its linkage with the selected locus ($R$).
 In panel B, gametic competition in males ($t^\male = -1/10$, $t^\female = \alpha^\circ_{\Delta} = 0$) opposes selection in diploids (sex-differences: $s^\male = 3/20$, $s^\female = 1/20$, $h^\circ = 7/10$).
@@
 Fig \ref{fig:Combination_Centimorgans} then demonstrates that under these conditions neo-W alleles can spread when they are more loosely \textit{or} more closely linked to the locus that experiences haploid selection, i.e., Conclusions 3B and 3C (c.f., Fig \ref{fig:SexAntagTighter}A for diploid sexually-antagonistic selection alone).
-%When the neo-W is more closely linked to the haploid selected locus its invasion increases (or creates anew) sex-ratio bias (Fig \ref{fig:SexRatioBad}A).
-%Under the same selection scenario (drive in males), a neo-Y would invade an ancestrally ZW system
-% shows that when a neo-W invades that increases linkage with a haploid selected locus, it biases the sex-ratio.
-%, while those that decrease sex-linkage equalize the sex-ratio. 
-%When sex-linkage decreases ($R>r$), neo-W alleles can benefit from Y-associated alleles that have higher fitness in the female diploid phase but then dissociate from these alleles through recombination before any subsequent haploid selection.
-
-%When there is no gametic competition and meiotic drive is in one sex only, an unlinked neo-W can invade as long as the same allele is favoured during diploid selection in males and females ($s^\female s^\male>0$, see Fig \ref{fig:Combination_Centimorgans}A and Fig \ref{fig:SexRatioBad}B).
-%, which is 50\% of the parameter space.
-%When there is no meiotic drive and gametic competition occurs in one sex only, an unlinked neo-W can invade as long as the same allele is favoured in male and female diploid selection and there are sex differences in selection of one type (e.g., $s^\female(s^\male-s^\female)>0$, see Fig \ref{fig:Combination_Centimorgans}B).
-%, which is 25\% of the parameter space.
-%These special cases indicate that neo-W invasion occurs for a relatively large fraction of the parameter space, even if the neo-W uncouples the sex-determining locus from a locus under selection.
 
@@
 Scenario &  Assumptions & neo-W spreads ($\lambda_{W'}^{(XY)}>1$) if \\ [0.5ex] \hline
-%  $r=1/2$, $R<1/2$ & Always \\ [0.5ex] \hline
-%  $r<1/2$, $R=1/2$ &  \\ [0.5ex] \hline
 \noalign{\vskip 1mm}
@@
 For example, if there is meiotic drive in males only ($\alpha^\male_\Delta \neq 0$, $\alpha^\female_\Delta=0$), without gametic competition ($t^\female=t^\male=0$) the zygotic sex ratio is initially biased only when the ancestral sex-determining system is XY (Figs \ref{fig:model_outline}B and \ref{fig:SexRatioBad}A) and not ZW (Figs \ref{fig:model_outline}B and \ref{fig:SexRatioBad}B).
-%If the ancxestral sex-determining system is ZW, the zygotic sex ratio will be 1:1 because diploid sex is determined by the proportion of Z-bearing versus W-bearing eggs and meiosis in females is fair (Fig \ref{fig:Combination_Turnover}D).
 If Fisherian sex-ratio selection were dominant, we would thus expect a difference in the potential for XY to ZW and ZW to XY transitions. 
-%However, to leading order with selection weak relative to recombination, we find that sex-ratio selection favours the spread of a neo-W by an amount equl to the spread of a neo-Y into a ZW system (relabeling XY as the heterogametic sex and reversing the labels of males and females in Table \ref{tab:specialcases})
-However, invasion by a neo-W allele into an XY system and invasion by a neo-Y allele into a ZW system occur under the same conditions ($\lambda_{Y'}^{(XY)} = \lambda_{W'}^{(ZW)}$ and $\lambda_{W'}^{(XY)}=\lambda_{Y'}^{(ZW)}$, at least to order $\epsilon^2$), implying that,% surprisingly,
+However, invasion by a neo-W allele into an XY system and invasion by a neo-Y allele into a ZW system occur under the same conditions ($\lambda_{Y'}^{(XY)} = \lambda_{W'}^{(ZW)}$ and $\lambda_{W'}^{(XY)}=\lambda_{Y'}^{(ZW)}$, at least to order $\epsilon^2$), implying that,
 \vspace{0.5cm}
@@
 \noindent\textit{Conclusion 4:}
-\textbf{When selection is weak relative to recombination, the presence of haploid selection equally favors the spread of new sex determination systems that reduce sex-ratio bias (benefiting from Fisherian sex ratio selection) or that generate a sex-ratio bias (benefiting from associations with selected alleles).
+\textbf{When selection is weak relative to recombination, trans-GSD transitions in the presence of haploid selection are favoured as often and as strongly whether they erase ancestral sex-ratio bias (benefiting from Fisherian sex ratio selection) or generate sex-ratio bias (benefiting from associations with selected alleles).
 }
 \vspace{0.5cm}
-%\noindent\textcolor{red}{\textit{Conclusion 3:}
-%\textbf{when selection is weak relative to recombination, sex-ratio selection is exactly equal in magnitude to the selection imposed by associations with selected alleles. } }
-%%\textcolor{red}{[new result]}
-%\vspace{0.5cm}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%sex-ratio selection is not a good predictor of neo-W invasion into an XY system
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}[!h]
 \centering
-\includegraphics[width=\linewidth]{../Plots/Temporal_SR.eps}
+%\includegraphics[width=\linewidth]{../Plots/Temporal_SR.eps}
 \caption{
@@
 In panel B, male drive in an ancestral ZW system has no effect on the zygotic sex ratio (50:50 at generation 0), yet a neo-Y can invade and replace the ancestral sex-determining system (inset shows the frequency of males carrying a neo-Y).
-%When $R<1/2$, the neo-Y becomes associated with the allele favoured by drive, causing the zygotic sex ratio to become biased, hence the frequency of the neo-Y at pseudo-fixation can be higher than $0.5$ (inset).
 Parameters:  $s^\female =s^\male = 0.2$, $h^\female = h^\male = 0.7$, $t^\female = t^\male = \alpha^\female_\Delta = 0$, $\alpha^\male_\Delta = -0.1$, $r=0.02$.
@@
 \end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%
-%As selection becomes stronger (or linkage becomes tighter), this symmetry between sex-ratio selection and haploid selection is lost, causing differences in the strength of selection favouring the two heterogametic transitions (compare red to black near -25cM and 25 cM in Fig \ref{fig:Combination_Centimorgans}).
-\textcolor{red}{normalise fitness in sexually antagonistic case}
-%
-%Why can new sex-determining regions invade when they are more loosely linked to selected loci ($R>r$)?  
-%Consider first the case where both sex-determining-loci are linked to the selected locus ($r<R<1/2$). 
-%In an ancestral-XY system, haploid selection in males can facilitate the spread of a neo-W because the zygotic sex ratio is ancestrally male biased and the W produces more of the rarer sex (Fig \ref{fig:SexRatioBad}A).
-%A new sex determining region can also, however, benefit from becoming more associated with drive. 
-%For example in an ancestral-ZW system with the same selection regime (haploid selection in males), a neo-Y can spread despite the fact that the zygotic sex is initially even; in this case, the neo-Y spreads because it is often found in males and can, if it carries the driven allele $a$, benefit from haploid selection in males (Fig \ref{fig:SexRatioBad}B).
 
@@
 In particular, we assume individuals carrying allele $m$ develop as females with probability $k\in(0,1)$.
-%\textcolor{red}{In our deterministic model this means the fraction female is exactly $k$, even when $m$ is rare (exploring the effect of the variance induced by ESD would also be interesting).}
 In our deterministic model this means the fraction female in the subpopulation containing $m$ is exactly $k$, even when $m$ is rare (i.e., ESD does not introduce any additional variance in sex determination).
@@
 Such correlations can favour environmental sex-determining systems by allowing each sex to be produced in the environment in which it has highest fitness; in the absence of these correlations previous theory would predict that ESD is favoured when it produces more equal sex ratios than the ancestral system (see reviews by~\cite{Charnov:1982wg,Bull:1983vi,West:2009we}).
-%(e.g., maternal condition, mate quality, age, or host size)
-
-The characteristic polynomial determining the leading eigenvalue (equations \ref{eq:recursions}) does not factor for ESD ($0<k<1$) as it does for a neo-Y ($k=0$) or neo-W ($k=1$) allele. 
+
+The characteristic polynomial determining the leading eigenvalue (Eqs S1.1) does not factor for ESD ($0<k<1$) as it does for a neo-Y ($k=0$) or neo-W ($k=1$) allele. 
 We therefore focus on weak selection here, where the leading eigenvalue is
@@
 This reduces to $\lambda_{Y'}^{(XY)}$ when $k=0$ and $\lambda_{W'}^{(XY)}$ when $k=1$. 
-
-%Under Fisherian sex-ratio selection, autosomal modifiers favour equal investment in male and female offspring, i.e., a 1:1 sex ratio~\cite{Fisher:1930wy,Charnov:1982wg,West:2009we}. 
-%A novel environmental sex-determiner that causes half of its carriers to become female and half to become male ($k=1/2$) will be in males half of the time and in females half of the time (like an autosome).
-%In addition, these novel sex-determination alleles equalize the sex ratio and therefore one might expect them to be favoured by Fisherian sex-ratio selection when the resident sex ratio is biased.
-%However, assuming weak selection, we find that the growth rate of a rare, dominant offspring-controlled neo-ESD allele that produces males or females with equal probability ($k=1/2$) is
 Of particular interest are ESD mutations that cause half of their carriers to develop as females and half as males ($k=1/2$), creating equal sex ratios.
@@
 \lambda_{ESD'}^{(XY)} =1+ \frac{1}{2}\frac{(\lambda_{Y'\rvert R=1/2}^{(XY)}-1) + (\lambda_{W'\rvert R=1/2}^{(XY)}-1)}{2} + O\left(\epsilon^3\right),
-%V_A \frac{r}{1-2r}  \frac{s_{f} \left( s^\male - 3 s^\female\right) }{8 {\left( s_{f} + s_{m} \right)}^2} t_{m}^2.
 \label{eq:lambda_ESD}
@@
 \noindent
-where $\lambda_{Y'\rvert R=1/2}^{(XY)}$ and $\lambda_{W'\rvert R=1/2}^{(XY)}$ represent $\lambda_{Y'}^{(XY)}$ and $\lambda_{W'}^{(XY)}$ when evaluated at $R=1/2$ (Equations \ref{eq:lambda_neoY} and \ref{eq:lambda_neoW}).
+where $\lambda_{Y'\rvert R=1/2}^{(XY)}$ and $\lambda_{W'\rvert R=1/2}^{(XY)}$ represent $\lambda_{Y'}^{(XY)}$ and $\lambda_{W'}^{(XY)}$ when evaluated at $R=1/2$ (Eqs \ref{eq:lambda_neoY} and \ref{eq:lambda_neoW}).
 That is, ESD with $k=1/2$ behaves as if the $\mathbf{M}$ and $\mathbf{A}$ loci were unlinked, regardless of the actual value of $R$.
@@
 That is, with haploid selection, an allele causing environmental-sex-determination can invade an ancestrally-XY system because it generates females that are either rare or have high fitness, in the same manner as a neo-W (likewise, ESD invades a ZW system for the same reasons that a neo-Y can).
-%An important result from Eq \eqref{eq:lambda_ESD} is that ESD can invade if there is haploid selection. 
-%When evaluated at $R=1/2$, $\Lambda_{Y',XY}$ is necessarily less than one, but $\Lambda_{W',XY}$ can be greater than one if there is haploid selection, as discussed above. 
-%Previous studies where ESD is favoured have typically assumed that environmental conditions (e.g., maternal condition, mate quality, age, or host size) can differentially affect the fitness of males versus females such that ESD invades because it allows sex determination to depend on the environment \citep[reviewed in][]{Charnov:1982wg,Bull:1983vi,West:2009we}.
-%Here, ESD mutations can spread because they generate females that are either rare or have high fitness, in the same manner as a neo-W.
 
@@
 Nevertheless, ESD is equally likely to invade both XY (through $\lambda_{W'}^{(XY)}$) and ZW (through $\lambda_{Y'}^{(ZW)}$) systems, equalizing the zygotic sex ratio in the former case but not in the latter.
-%This is again because haploid selection can facilitate the turnover of sex chromosomes either through sex-ratio biases or through associations between the new sex determining region with selected alleles.
-%With weak selection, these two forces are nearly equal in strength. 
 In addition, we note that ESD may not invade, even if the sex ratio is initially biased (e.g., with drive in males only, $r<1/2$, $h^\female=h^\male$, and $s^\female s^\male<0$, then $\lambda_{W'}^{(XY)}<1$, see Table \ref{tab:specialcases}).
@@
 }
-%\textcolor{red}{[new result]}
-
-%\textcolor{red}{
-%Somehow need to add two further conclusions suggested by review 2:
-%\vspace{0.5cm}
-%\\
-%\noindent\textit{Conclusion 6: sex-antagonism and tighter sex linkage not required for transitions.}
-%\vspace{0.5cm}
-%\\
-%\noindent\textit{Conclusion 7: haploid selection makes conditions for transitions permissive.}
-%\vspace{0.5cm}
-%\\
-%\noindent Or are these evident from the first 5 conclusions?
-%}
-
+
+%%%%%%%%%%%%%%%%%
 \section*{Discussion}
+%%%%%%%%%%%%%%%%%
 
@@
 In accordance with the latter mechanism, we find that sex-differences in selection at the haploid stage can favour cis- or trans-GSD transitions that tighten sex-linkage (Conclusion 3A \&3B). 
-%, as exemplified in~\cite{Ubeda:2015fx} for ESD-GSD transitions.
 Contrary to this expectation, however, we find that trans-GSD transitions can be favoured that loosen linkage with the sex-determining locus, either when linkage is initially tight (Conclusions 1 \& 2, Figs \ref{fig:regionplots} \& \ref{fig:SexAntagTighter}) or when there is haploid selection (Conclusion 3C, Figs \ref{fig:Combination_Centimorgans} \& \ref{fig:SexRatioBad}).
@@
 
-%We find that the spread of new sex-determining systems cannot be simply predicted from their effect on the sex ratio. 
 On the one hand, sex-ratio biases caused by haploid selection can facilitate trans-GSD transitions or transitions from genetic to environmental sex determination~\cite{Kozielska:2010vm}. 
@@
 This male bias increases the potential for a neo-W or ESD allele to invade (Table \ref{tab:haplotype_growth}), equalizing the sex ratio (e.g., see Fig \ref{fig:SexRatioBad}B, for related examples see~\cite{Kozielska:2010vm}).
-%We find that sex-ratio biases caused by haploid selection can also affect transitions between sex-determining systems (e.g., see $\zeta$ terms in Table \ref{tab:haplotype_growth}). 
-%However, the neo-W may not equalize the sex ratio (e.g., if the driving allele also drives in females or affects competition among eggs)
 On the other hand, sex-ratio selection can be overwhelmed by additional selective effects, preventing a neo-W or ESD allele from invading, even if it would balance the sex ratio (e.g., when selection also acts in opposite directions in male and female diploids, Table \ref{tab:specialcases}).
-%and equalizing the sex ratio.
 Indeed, transitions between sex-determining systems can generate stronger sex-ratio biases (e.g., Fig \ref{fig:SexRatioBad}A and step 1 in~\cite{Ubeda:2015fx}).
@@
 That is, the sex-ratio bias created by male haploid selection facilitates the spread of a neo-W allele into an XY system to the same degree that male haploid selection drives the spread of a neo-Y into a ZW system with a 1:1 sex ratio (Fig \ref{fig:SexRatioBad}).
-%Thus, haploid selection can favour trans-GSD transitions both via sex-ratio selection and via selection on alleles associated with the new sex-determining allele, and these selective pressures are often predicted to be of equal magnitude.
-
-%Our results indicate that haploid selection could be an important factor driving the evolution of new sex-determining systems. 
+
 Because both Fisherian selection to equalize the sex ratio and the benefits of hitchhiking with driven alleles can facilitate transitions among sex chromosome systems, we predict that haploid selection should increase the lability of sex determination systems.
@@
 
-%HAPLOID SELECTION (genomic location of haploid selected loci and comparative patterns) 
 Linking haploid expression with the evolution of sex-determination, a recent transcriptome analysis in \textit{Rumex} shows that pollen-biased expression (relative to expression in flower buds or leaves) is enhanced among XY-linked genes compared to autosomal genes or compared to hemizygous genes that are only linked to the X
@@
 This suggests that the spread of neo-Y chromosomes in this clade could have been favoured through linkage with haploid selected genes rather than those under sexually antagonistic selection.
-%maybe add a flag here for switching to clade-level expectations:
-
-%In general, we predict that haploid selection increases lability of sex-determining systems, particularly because haploid selection can cause transitions that increase or decrease sex-linkage (Conclusion 2A \& 2B, e.g., the final state of the red line in Fig \ref{fig:SexRatioBad}B is the starting state in Fig \ref{fig:SexRatioBad}A).
+
 Frequent turnovers driven by haploid selection may help to explain the relative rarity of heteromorphic sex chromosomes in plants.
@@
 
-%Limitation 1: DEGENERATE Y
 Our models assume that sex-determining alleles do not experience direct selection except via their associations with sex and selected alleles.
@@
 However, they noted that very rare recombination events around the ancestral sex-determining locus can allow the completion of trans-GSD transitions.  
-%While not explicitly studied, we also predict that Y or W degeneration would prevent fixation of the new sex-determining genes considered here.
 Degeneration around the Y or W could explain why trans-GSD transitions are not observed to be much more common than cis-GSD transitions despite the fact that our models demonstrate that they are favoured under a wider range of conditions, especially with haploid selection.
@@
 
-%Limitation 3: don't consider m alleles with similar k to ancester, no ancestral ESD considered
 In this study, we have only considered new sex-determining alleles of large effect. 
@@
 
-%Limitation 2: TWO ALLELE DRIVE
-%Another simplification that we made is that meiotic drive involves only a single locus with two alleles. 
-%However, many meiotic drive systems involve an interaction with another locus at which alleles may `suppress' the action of meiotic drive \citep[][]{Burt:2006,Lindholm:2016cw}.
-%Thus, the dynamics of meiotic drive alleles can be heavily dependent on the interaction between two loci and the recombination rate between them, which in turn can be affected by sex-linkage if there is reduced recombination between sex chromosomes~\cite{Hurst:1991uh}.
-%Furthermore, in some cases, a driving allele may act by killing any gametes that carry a `target' allele at another locus, in which case there can be fertility effects that alter the equilibrium frequency of a meiotic drive allele~\cite{Holman:2015en}.
-%In polygamous mating systems, the intensity of pollen/sperm competition can depend on the density of males available to donate pollen/sperm, which can itself depend on the sex ratio~\cite{Taylor:2002wu}.
-%In terms of our model, this implies that the strength of gametic competition ($t^\male$) may both determine and be determined by the sex ratio. 
-%How the evolution of new sex-determining mechanisms could be influenced by two-locus meiotic drive and/or by ecological feedbacks under different mating systems remains to be studied.
-
+%%%%%%%%%%%%%%%%%%
 \section*{Conclusion}
+%%%%%%%%%%%%%%%%%%
 
@@
 
+%%%%%%%%%%%%%%%%%%
 \section*{Supporting information}
+%%%%%%%%%%%%%%%%%%
 
@@
 {\bf Supplementary \textit{Mathematica} file.}  This file can be used to re-derive our results and generate figures.
+
+\paragraph*{S2 File.}
+\label{file:MathematicaCDF}
+{\bf Supplementary \textit{Mathematica} file in CDF form.}  This file can be used to re-derive our results and generate figures with a free online viewer (\hyperref[www.wolfram.com/cdf-player/]{www.wolfram.com/cdf-player/}).
+
+\paragraph*{S3 File.}
+\label{file:MathematicaPDF}
+{\bf Supplementary \textit{Mathematica} file in PDF form.}  This file can be used to see how we have derived our results and have generated figures with any PDF viewer.
 
@@
 Equilibria where the $A$ allele is more common among Y-bearing male gametes can also be stable and allow neo-W invasion for these parameters (blue lines).
-%The weak selection approximation holds when all recombination rates are large relative to selection (around 0 in panels A and C), in which case, in the absence of haploid selection, neo-W alleles should spread if and only if they are more tightly linked to the selected locus (positive invasion fitness if and only if the selected locus is in the grey region).
-%However, when recombination rates are small (panels B and D and when the selected locus is near the SDRs in all panels), this weak selection prediction can break down.
 
@@
 Here, we plot the frequency of the neo-W allele among female gametes.
-%; as the neo-W reaches frequency $0.5$, polymorphism at the ancestral XY locus is lost with Y becoming fixed such that sex is determined only be the ZW allele carried by a female gamete. 
 Panels A, C and D show cases where a steady state is reached with the neo-W at a frequency below $0.5$, in which case ancestral-X and Y alleles also both segregate. 
@@
 In contrast, the neo-W is not lost in panel D as it is favoured regardless of whether Y-$A$ or Y-$a$ haplotypes predominate (again, compare blue to black curves in \nameref{fig:positionOverdominance}C and  \nameref{fig:positionOverdominance}D).
-%Fitness parameters are the same as in \nameref{fig:positionOverdominance}; in panels A and B the $a$ allele is favoured in females ($w_{aa}^\female=1.05$, $w_{Aa}^\circ=1$, $w_{AA}^\female=0.85$) while there is overdominance in males ($w_{aa}^\male=w_{AA}^\male=0.75$) and in panels C and D, there is overdominance in both sexes ($w_{aa}^\female=w_{AA}^\female=0.6$, $w_{aa}^\male=0.5$, $w_{AA}^\male=0.7$, $w_{Aa}^\circ=1$).
-%These parameters are marked by a dagger in Fig \ref{fig:regionplots}. 
-%Here, there is no haploid selection $t^\circ = \alpha^\circ_\Delta = 0$.
 
@@
 This figure is equivalent to Fig \ref{fig:regionplots} but with meiotic drive in males.
-%We vary the fitness of male homozygotes relative to heterozygotes ($w_{Aa}^\circ=1$) and only consider stable equilibria at which both $\mathbf{A}$ locus allele are maintained and the $a$ allele is initially fixed on the Y, region outlined.
 In panels A-C, meiotic drive in males favours the $a$ allele ($\alpha_{\Delta}^\male=-0.16$), creating male-biased sex ratios and generally increasing $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$.
 By contrast, $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$ tend to be reduced when meiotic drive in males favours the $A$ allele ($\alpha_{\Delta}^\male=0.16$), panels D-F.
-%We consider three forms of selection in females: directional selection in favour of the $A$ allele (panels A and D, $w_{aa}^\female=0.85$, $w_{AA}^\female=1.05$), direction selection in favour of the $a$ allele (panels B and E, $w_{aa}^\female=1.05$, $w_{AA}^\female=0.85$), and overdominance (panels C and F, $w_{aa}^\female=w_{AA}^\female=0.6$).
 
@@
 This figure is equivalent to Fig \ref{fig:regionplots} but with gametic competition in males.
-%Diploid selection parameters ($w_{ij}^\circ$) are the same as those in \nameref{fig:regionMaleDrive}. 
 The $a$ allele is favoured during male gametic competition in Panels A-C ($w_{a}^\male=1.16$, $w_{A}^\male=1$), which creates male biased sex ratios and increases $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$.
@@
 This figure is equivalent to Fig \ref{fig:regionplots} but with meiotic drive in females.
-%Diploid selection parameters ($w_{ij}^\circ$) are the same as those in \nameref{fig:regionMaleDrive} and \nameref{fig:regionMaleGS}. 
 The $a$ allele is favoured by meiotic drive in females in Panels A-C ($\alpha_{\Delta}^\female=-0.16$), which increases $\Lambda_{W'a}^{(XY)}$ and decreases $\Lambda_{W'A}^{(XY)}$. 
@@
 This figure is equivalent to Fig \ref{fig:regionplots} but with gametic competition in females.
-%Diploid selection parameters ($w_{ij}^\circ$) are the same as those in \nameref{fig:regionMaleDrive}, \nameref{fig:regionMaleGS}, and \nameref{fig:regionFemaleDrive}. 
 The $a$ allele is favoured during female gametic competition in females in Panels A-C ($w_{a}^\female=1.16$, $w_{A}^\female=1$), which increases $\Lambda_{W'a}^{(XY)}$ and decreases $\Lambda_{W'A}^{(XY)}$.
@@
 
+%%%%%%%%%%%%%%%%%%
 \section*{Acknowledgments}
-We thank Georgy Sandler and Stephen Wright for sharing their results with us, and we thank Bret Payseur and three anonymous reviewers for helpful comments on this manuscript. 
+%%%%%%%%%%%%%%%%%%
+We thank Georgy Sandler and Stephen Wright for sharing their results with us and we thank Bret Payseur for helpful comments on a previous version of this manuscript. 
 %This project was supported by the Natural Sciences and Engineering Research Council of Canada (CGS-D 6564 to MMO; RGPIN-2016-03711 to SPO).
@@
 % step-by-step instructions.
-% 
-\bibliography{sex_chromosomes}
-
-%\newpage
-%
-%\setcounter{equation}{0}
-%\renewcommand{\theequation}{S1.\arabic{equation}}
-%
-%\section*{S1 Appendix}
-%
-%\subsection*{Recursion equations}
-%
-%
-%In each generation we census the genotype frequencies in male and female gametes/gametophytes (hereafter, gametes) between meiosis (and any meiotic drive) and gametic competition. 
-%At this stage we denote the frequencies of X- and Y-bearing gametes from males and females $x_{i}^{\circ}$ and $y_{i}^{\circ}$.
-%The superscript $\circ \in \{\male,\female\}$ specifies the sex of the diploid that the gamete came from. 
-%The subscript $i\in\{1,2,3,4\}$ specifies the genotype at the selected locus $\mathbf{A}$ and at the novel sex-determining locus $\mathbf{M}$, where $1=AM$, $2=aM$, $3=Am$, and $4=am$. 
-%The gamete frequencies from each sex sum to one, $\sum_{i}x_{i}^{\circ}+y_{i}^{\circ}=1$. 
-%
-%Competition then occurs among gametes of the same sex (e.g., among eggs and among sperm separately) according to the genotype at the $\mathbf{A}$ locus ($w_{1}^\circ=w_{3}^\circ=w_{A}^\circ$, $w_{2}^\circ=w_{4}^\circ=w_{a}^\circ$, see Table \ref{tab:fitnesstable}).
-%The genotype frequencies after gametic competition are $x_{i}^{\circ,s}= w_{i}^{\circ}x_{i}^{\circ}/\bar{w}_{H}^{\circ}$ and $y_{i}^{\circ,s}= w_{i}^{\circ}y_{i}^{\circ}/\bar{w}_{H}^{\circ}$, where $\bar{w}_{H}^{\circ}=\sum_{i} w_{i}^{\circ}x_{i}^{\circ}+w_{i}^{\circ}y_{i}^{\circ}$ is the mean fitness of male ($\circ=\male$) or female ($\circ=\female$) gametes.
-%
-%Random mating then occurs between gametes to produce diploid zygotes.
-%%To shorten notation we now use index $i$ (and $j$) to denote the alleles at both the $\mathbf{A}$ and $\mathbf{M}$ loci and label $MA=1$, $Ma=2$, $mA=3$, and $ma=4$, such that $i,j\in\{1,2,3,4\}$.
-%The frequencies of XX zygotes are then denoted as $xx_{ij}$, XY zygotes as $xy_{ij}$, and YY zygotes as $yy_{ij}$, where $\mathbf{A}$ and $\mathbf{M}$ locus genotypes are given by $i,j\in\{1,2,3,4\}$, as above.
-%In XY zygotes, the haplotype inherited from an X-bearing gamete is given by $i$ and the haplotype from a Y-bearing gamete is given by $j$. 
-%In XX and YY zygotes, individuals with diploid genotype $ij$ are equivalent to those with diploid genotype $ji$; for simplicity, we use $xx_{ij}$ and $yy_{ij}$ with $i\neq j$ to denote the average of these frequencies, $xx_{ij}=(x_{i}^{\female,s}x_{j}^{\male,s}+x_{j}^{\female,s}x_{i}^{\male,s})/2$ and $yy_{ij}=(y_{i}^{\female,s}y_{j}^{\male,s}+y_{j}^{\female,s}y_{i}^{\male,s})/2$.
-%
-%
-%Denoting the $\mathbf{M}$ locus genotype by $b \in \{MM, Mm, mm\}$ and the $\mathbf{X}$ locus genotype by $c \in \{XX, XY, YY\}$, zygotes develop as females with probability $k_{bc}$. 
-%Therefore, the frequencies of XX females are given by $xx_{ij}^{\female}=k_{bc}xx_{ij}$, XY females are given by $xy_{ij}^{\female}=k_{bc}xy_{ij}$, and YY females are given by $yy_{ij}^{\female}=k_{bc}yy_{ij}$.
-%Similarly, XX male frequencies are $xx_{ij}^{\male}=(1-k_{bc})xx_{ij}$, XY male frequencies are $xy_{ij}^{\male}=(1-k_{bc})xy_{ij}$, and YY males frequencies are $yy_{ij}^{\male}=(1-k_{bc})yy_{ij}$.
-%This notation allows both the ancestral and novel sex-determining regions to determine zygotic sex according to an XY system, a ZW system, or an environmental sex-determining system. 
-%In addition, we can consider any epistatic dominance relationship between the two sex-determining loci. 
-%Here, we assume that the ancestral sex-determining system ($\mathbf{X}$ locus) is XY ($k_{MMXX}=1$ and $k_{MMXY}=k_{MMYY}=0$) or ZW ($k_{MMZZ}=0$ and $k_{MMZW}=k_{MMWW}=1$) and epistatically recessive to a dominant novel sex-determining locus, $\mathbf{M}$ ($k_{Mmc}=k_{mmc}=k$).
-%
-%
-%Selection among diploids then occurs according to the diploid genotype at the $\mathbf{A}$ locus, $l \in \{AA, Aa, aa\}$, for an individual of type $ij$ (see Table \ref{tab:fitnesstable}). 
-%The diploid frequencies after selection in sex $\circ$ are given by $xx_{ij}^{\circ,s}=w_{l}^{\circ} xx_{ij}/\bar{w}^{\circ}_{D}$, $xy_{ij}^{\circ,s}=w_{l}^{\circ} xy_{ij}/\bar{w}^{\circ}_{D}$, and $yy_{ij}^{\circ,s}=w_{l}^{\circ} yy_{ij}/\bar{w}^{\circ}_{D}$, where $\bar{w}^{\circ}_{D}= \sum_{i=1}^{4}\sum_{j=1}^{4}w_{l}^{\circ}xx_{ij}+w_{l}^{\circ}xy_{ij}+w_{l}^{\circ}yy_{ij}$ is the mean fitness of diploids of sex $\circ$.
-%
-%Finally, these diploids undergo meiosis to produce the next generation of gametes. 
-%Recombination and sex-specific meiotic drive occur during meiosis.
-%%We can also assume that recombination is sex specific and/or affected by the M locus - but generally we don't so I just describe $R=R_{f}=R, r_{MM,d}=r_{Mm,d}=r_{mm,d}=r, \chi_{m}=\chi_{f}=\chi$.
-%Here, we allow any relative locations for the $\mathbf{X}$, $\mathbf{A}$, and $\mathbf{M}$ loci by using three parameters to describe the recombination rates between them. 
-%$R$ is the recombination rate between the $\mathbf{A}$ and $\mathbf{M}$ loci, $\rho$ is the recombination rate between the $\mathbf{M}$ and $\mathbf{X}$ loci, and $r$ is the recombination rate between the $\mathbf{A}$ and $\mathbf{X}$ loci (Fig \ref{fig:model_outline}).
-%\nameref{tab:chisubstitutions} shows replacements that can be made for each possible ordering of the loci assuming that there is no cross-over interference.
-%During meiosis in sex $\circ$, meiotic drive occurs such that, in $Aa$ heterozygotes, a fraction $\alpha^{\circ}$ of gametes produced carry the $A$ allele and $(1-\alpha^\circ)$ carry the $a$ allele.
-%
-%Among gametes from sex $\circ$, the frequencies of haplotypes (before gametic competition) in the next generation are given by
-%
-%\begingroup
-%\allowdisplaybreaks
-%\begin{subequations}
-%\begin{align}
-%%
-%\begin{split}
-%x_{1}^{{\circ}'}=&xx_{11}^{\circ,s}+xx_{13}^{\circ,s}/2+(xx_{12}^{\circ,s}+xx_{14}^{\circ,s})\alpha^\circ\\
-%&-R(xx_{14}^{\circ,s}-xx_{23}^{\circ,s}) \alpha^\circ\\
-%&+(xy_{11}^{\circ,s}+xy_{13}^{\circ,s})/2+(xy_{12}^{\circ,s}+xy_{14}^{\circ,s})\alpha^\circ\\
-%&- r(xy_{12}^{\circ,s}-xy_{21}^{\circ,s})\alpha^\circ - \rho(xy_{13}^{\circ,s}-xy_{31}^{\circ,s})/2\\
-%&+\big{[}-(R+r+\rho)xy_{14}^{\circ,s} +(R+\rho-r)xy_{41}^{\circ,s}\\
-%&+(R+r-\rho) xy_{23}^{\circ,s}+(R+\rho-r)xy_{32}^{\circ,s}\big{]}\alpha^\circ/2
-%\end{split}
-%\\
-%%
-%\begin{split}
-%x_{2}^{{\circ}'}=&xx_{22}^{\circ,s}+xx_{24}^{\circ,s}/2+(xx_{12}^{\circ,s}+xx_{23}^{\circ,s})\alpha^\circ\\
-%&-R(xx_{23}^{\circ,s}-xx_{14}^{\circ,s}) \alpha^\circ\\
-%&(xy_{22}^{\circ,s}+xy_{24}^{\circ,s})/2+(xy_{21}^{\circ,s}+xy_{23}^{\circ,s})(1-\alpha^\circ)\\
-%&- r(xy_{21}^{\circ,s}-xy_{12}^{\circ,s})(1-\alpha^\circ) - \rho(xy_{24}^{\circ,s}-xy_{42}^{\circ,s})/2\\
-%&+\big{[}-(R+r+\rho)xy_{23}^{\circ,s}+(R+\rho-r)xy_{32}^{\circ,s}\\
-%&+(R+r-\rho) xy_{14}^{\circ,s}+(R+\rho-r)xy_{41}^{\circ,s}\big{]}(1-\alpha^\circ)/2
-%\end{split}
-%\\
-%%
-%\begin{split}
-%x_{3}^{{\circ}'}=&xx_{33}^{\circ,s}+xx_{13}^{\circ,s}/2+(xx_{23}^{\circ,s}+xx_{34}^{\circ,s})\alpha^\circ\\
-%&-R(xx_{23}^{\circ,s}-xx_{14}^{\circ,s}) \alpha^\circ\\
-%&(xy_{33}^{\circ,s}+xy_{31}^{\circ,s})/2+(xy_{32}^{\circ,s}+xy_{34}^{\circ,s})\alpha^\circ\\
-%&- r(xy_{34}^{\circ,s}-xy_{43}^{\circ,s}) \alpha^\circ - \rho(xy_{31}^{\circ,s}-xy_{13}^{\circ,s})/2\\
-%&+\big{[}-(R+r+\rho)xy_{32}^{\circ,s} +(R+\rho-r)xy_{23}^{\circ,s}\\
-%&+(R+r-\rho) xy_{41}^{\circ,s}+(R+\rho-r)xy_{14}^{\circ,s}\big{]} \alpha^\circ/2
-%\end{split}
-%\\
-%%
-%\begin{split}
-%x_{4}^{{\circ}'}=&xx_{44}^{\circ,s}+xx_{34}^{\circ,s}/2+(xx_{14}^{\circ,s}+xx_{24}^{\circ,s})\alpha^\circ\\
-%&-R(xx_{14}^{\circ,s}-xx_{23}^{\circ,s}) \alpha^\circ\\
-%&(xy_{44}^{\circ,s}+xy_{42}^{\circ,s})/2+(xy_{41}^{\circ,s}+xy_{43}^{\circ,s})(1-\alpha^\circ)\\
-%&- r(xy_{43}^{\circ,s}-xy_{34}^{\circ,s})(1-\alpha^\circ) - \rho(xy_{42}^{\circ,s}-xy_{24}^{\circ,s})/2\\
-%&+\big{[}-(R+r+\rho)xy_{41}^{\circ,s}+(R+\rho-r)xy_{14}^{\circ,s}\\
-%&+(R+r-\rho) xy_{32}^{\circ,s}+(R+\rho-r)xy_{23}^{\circ,s}\big{]}(1-\alpha^\circ)/2
-%\end{split}
-%\\
-%\begin{split}
-%y_{1}^{{\circ}'}=&yy_{11}^{\circ,s}+yy_{13}^{\circ,s}/2+(yy_{12}^{\circ,s}+yy_{14}^{\circ,s})\alpha^\circ\\
-%&-R(yy_{14}^{\circ,s}-yy_{23}^{\circ,s}) \alpha^\circ\\
-%&(xy_{11}^{\circ,s}+xy_{31}^{\circ,s})/2+(xy_{21}^{\circ,s}+xy_{41}^{\circ,s})\alpha^\circ\\
-%&- r(xy_{21}^{\circ,s}-xy_{12}^{\circ,s})\alpha^\circ - \rho(xy_{31}^{\circ,s}-xy_{13}^{\circ,s})/2\\
-%&+\big{[} - (R+r+\rho)xy_{41}^{\circ,s} + (R+\rho-r)xy_{14}^{\circ,s}\\
-%& + (R+r-\rho)xy_{32}^{\circ,s} + (R+\rho-r) xy_{23}^{\circ,s}\big{]}\alpha^\circ/2
-%\end{split}
-%\\
-%%
-%\begin{split}
-%y_{2}^{{\circ}'}=&yy_{22}^{\circ,s}+yy_{24}^{\circ,s}/2+(yy_{12}^{\circ,s}+yy_{23}^{\circ,s})\alpha^\circ\\
-%&-R(yy_{23}^{\circ,s}-yy_{14}^{\circ,s}) \alpha^\circ\\
-%&(xy_{22}^{\circ,s}+xy_{42}^{\circ,s})/2+(xy_{12}^{\circ,s}+xy_{32}^{\circ,s})(1-\alpha^\circ)\\
-%&- r(xy_{12}^{\circ,s}-xy_{21}^{\circ,s})(1-\alpha^\circ) - \rho(xy_{42}^{\circ,s}-xy_{24}^{\circ,s})/2\\
-%&+\big{[}-(R+r+\rho)xy_{32}^{\circ,s} +(R+\rho-r) xy_{23}^{\circ,s}\\
-%&+(R+r-\rho)xy_{41}^{\circ,s}+(R+\rho-r)xy_{14}^{\circ,s}\big{]}(1-\alpha^\circ)/2
-%\end{split}
-%\\
-%%
-%\begin{split}
-%y_{3}^{{\circ}'}=&yy_{33}^{\circ,s}+yy_{13}^{\circ,s}/2+(yy_{23}^{\circ,s}+yy_{34}^{\circ,s})\alpha^\circ\\
-%&-R(yy_{23}^{\circ,s}-yy_{14}^{\circ,s}) \alpha^\circ\\
-%&(xy_{33}^{\circ,s}+xy_{13}^{\circ,s})/2+(xy_{23}^{\circ,s}+xy_{43}^{\circ,s})\alpha^\circ\\
-%&- r(xy_{43}^{\circ,s}-xy_{34}^{\circ,s})\alpha^\circ - \rho(xy_{13}^{\circ,s}-xy_{31}^{\circ,s})/2\\
-%&+\big{[}-(R+r+\rho)xy_{23}^{\circ,s} +(R+\rho-r)xy_{32}^{\circ,s}\\
-%&+(R+r-\rho) xy_{14}^{\circ,s} + (R+\rho-r) xy_{41}^{\circ,s}\big{]}\alpha^\circ/2
-%\end{split}
-%\\
-%%
-%\begin{split}
-%y_{4}^{{\circ}'}=&yy_{44}^{\circ,s}+yy_{34}^{\circ,s}/2+(yy_{14}^{\circ,s}+yy_{24}^{\circ,s})\alpha^\circ\\
-%&-R(yy_{14}^{\circ,s}-yy_{23}^{\circ,s}) \alpha^\circ\\
-%&(xy_{44}^{\circ,s}+xy_{24}^{\circ,s})/2+(xy_{14}^{\circ,s}+xy_{34}^{\circ,s})(1-\alpha^\circ)\\
-%&- r(xy_{34}^{\circ,s}-xy_{43}^{\circ,s})(1-\alpha^\circ) - \rho(xy_{24}^{\circ,s}-xy_{42}^{\circ,s})/2\\
-%&+\big{[}-(R+r+\rho) xy_{14}^{\circ,s} + (R+\rho-r)xy_{41}^{\circ,s}\\
-%&+(R+r-\rho) xy_{23}^{\circ,s} + (R+\rho-r) xy_{32}^{\circ,s}\big{]}(1-\alpha^\circ)/2.
-%\end{split}
-%\end{align}
-%\label{eq:recursions}
-%\end{subequations}
-%
-%\endgroup
-%
-%\noindent
-%The full system is therefore described by 16 recurrence equations (three diallelic loci in two sexes, $2^3 \times 2 = 16$). 
-%However, not all diploid types are produced under certain sex-determining systems. 
-%For example, with the $M$ allele fixed and an ancestral XY sex-determining system, there are XX females and XY males ($x_{3}^\circ=x_{4}^\circ=y_{3}^\male=y_{4}^\male=y_{i}^\female=0,\;\forall\; i$).
-%%($xx_{11}^{\male}=xx_{12}^{\male}=xx_{22}^\male=xy_{11}^{\female}=xy_{12}^{\female}=xy_{21}^{\female}=xy_{22}^\female=yy_{11}^{\female}=yy_{12}^{\female}=yy_{22}^\female=0$). 
-%In this case, the system only involves six recursion equations, %because there is only one $\mathbf{M}$ locus allele and no Y-bearing female gametes. 
-%which we assume below to calculate the equilibria.
-
-%\newpage
-
-%\setcounter{equation}{0}
-%\renewcommand{\theequation}{S2.\arabic{equation}}
-%
-%\section*{S2 Appendix}
-%
-%\subsection*{Resident equilibria and stability}
-%
-%In the resident population (allele $M$ fixed), we follow the frequency of $A$ in X-bearing female gametes, $p^\female_X$, and X-bearing male gametes, $p^\male_X$, and Y-bearing male gametes, $p^\male_Y$.
-%We also track the total frequency of Y among male gametes, $q$, which may deviate from $1/2$ due to meiotic drive in males. 
-%These four variables determine the frequencies of the six resident gamete types, which sum to one in each sex: $x_{1}^{\female}=\hat{p}_X^\female$, $x_{2}^{\female}=1-\hat{p}_X^\female$, $x_{1}^{\male}=(1-q)\hat{p}_X^\male$, $x_{2}^{\male}=(1-q)(1-\hat{p}_X^\male)$, $y_{1}^{\male}=q \hat{p}_Y^\male$, and $y_{2}^{\male}=q(1-\hat{p}_Y^\male)$.
-%Mean fitnesses in the resident population are given in \nameref{tab:meanfitnesses}.
-%
-%Various forms of selection can maintain a polymorphism at the $\mathbf{A}$ locus, including sexually antagonistic selection, overdominance, conflicts between diploid selection and selection upon haploid genotypes (ploidally-antagonsitic selection,~\cite{Immler:2012tl}), or a combination of these selective regimes (see below).
-%
-%In particular special cases, e.g., no sex-differences in selection or meiotic drive ($s^\male=s^\female$, $h^\male=h^\female$, and $\alpha^\male=\alpha^\female=1/2$), the equilibrium allele frequency and stability can be calculated analytically without assuming anything about the relative strengths of selection and recombination.
-%However, here, we focus on two regimes (tight linkage between $\mathbf{A}$ and $\mathbf{X}$ and weak selection) in order to make fewer assumptions about fitnesses. 
-%
-%\subsubsection*{Tight linkage between $\mathbf{X}$ and $\mathbf{A}$ loci}
-%
-%We first calculate the equilibria in the ancestral population when the recombination rate between the $\mathbf{X}$ and $\mathbf{A}$ loci is small ($r$ of order $\epsilon$). 
-%Selection at the $\mathbf{A}$ locus will not affect evolution at the novel sex-determining locus, $\mathbf{M}$, if one allele is fixed on all backgrounds. 
-%We therefore focus on the five equilibria that maintain both $A$ and $a$ alleles, four of which are given to leading order by:
-%
-%\begin{subequations}\label{eq:tightequil}
-%\begin{align}
-%(A)\ \ \ &\hat{p}_{Y}^{\male}=0,
-%\ \hat{q}_{Y}=\frac{1}{2}\left(1 - \alpha_\Delta^\male \frac{ w_{Aa}^{\male} \phi}{w_{Aa}^{\male} \phi+ w_{aa}^{\male} \psi}\right),\\
-%&\hat{p}_{X}^{\female}=\frac{w_{a}^{\female} \phi}{w_{a}^{\female} \phi+ w_{A}^{\female} \psi},
-%\ \hat{p}_{X}^{\male}=\frac{(1+\alpha_\Delta^\male)w_{Aa}^{\male} \phi}{(1+\alpha_\Delta^\male)w_{Aa}^{\male} \phi +w_{aa}^{\male} \psi} \nonumber \\
-%(A')\ \ \ &\hat{p}_{Y}^{\male}=1,
-%\ \hat{q}_{Y}=\frac{1}{2}\left(1 + \alpha_\Delta^\male \frac{w_{Aa}^{\male} \phi'}{w_{Aa}^{\male} \phi' + w_{AA}^{\male} \psi'}\right),\\
-%&\hat{p}_{X}^{\female}=1-\frac{w_{A}^{\female} \phi'}{w_{A}^{\female} \phi'+ w_{a}^{\female} \psi'},
-%\ \hat{p}_{X}^{\male}=1-\frac{(1-\alpha_\Delta^\male)w_{Aa}^{\male} \phi'}{(1-\alpha_\Delta^\male)w_{Aa}^{\male} \phi'+w_{AA}^{\male} \psi'} \nonumber \\
-%(B)\ \ \ &\hat{p}_{Y}^{\male}=0,\ \hat{p}_{X}^{\female}=1,\ \hat{p}_{X}^{\male}=1, \ \hat{q}_{Y}=(1 -\alpha^\male_\Delta)/2\\
-%(B')\ \ \ &\hat{p}_{Y}^{\male}=1,\ \hat{p}_{X}^{\female}=0,\ \hat{p}_{X}^{\male}=0, \ \hat{q}_{Y}=(1+\alpha^\male_\Delta)/2
-%\end{align}
-%\end{subequations}
-%\begin{equation*}
-%\begin{split}
-%\phi=&(1+\alpha^\female_\Delta) w_{A}^{\female} w_{Aa}^{\female} \left[ w_{a}^{\male} w_{aa}^{\male} + (1+\alpha_\Delta^\male) w_{A}^{\male} w_{Aa}^{\male} \right]/2 - w_{a}^{\male} w_{a}^{\female} w_{aa}^{\male} w_{aa}^{\female} \\
-%\psi=&(1-\alpha^\female_\Delta) w_{a}^{\female} w_{Aa}^{\female} \left[ w_{a}^{\male} w_{aa}^{\male} + (1+\alpha_\Delta^\male) w_{A}^{\male} w_{Aa}^{\male}\right]/2 - (1+\alpha_\Delta^\male) w_{A}^{\male} w_{A}^{\female} w_{Aa}^{\male} w_{AA}^{\female}\\
-%\phi'=&(1-\alpha^\female_\Delta) w_{a}^{\female} w_{Aa}^{\female} \left[ w_{A}^{\male} w_{AA}^{\male} + (1-\alpha_\Delta^\male) w_{a}^{\male} w_{Aa}^{\male} \right]/2 - w_{A}^{\male} w_{A}^{\female} w_{AA}^{\male} w_{AA}^{\female}\\
-%\psi'=&(1+\alpha^\female_\Delta) w_{A}^{\female} w_{Aa}^{\female} \left[ w_{A}^{\male} w_{AA}^{\male} + (1-\alpha_\Delta^\male) w_{a}^{\male} w_{Aa}^{\male} \right]/2 - (1-\alpha_\Delta^\male) w_{a}^{\male} w_{a}^{\female} w_{Aa}^{\male} w_{aa}^{\female}.
-%\end{split}
-%\end{equation*}
-%
-%\noindent
-%A fifth equilibrium $(C)$ also exists where $A$ is present at an intermediate frequency on the Y background ($0<\hat{p}_{Y}^{\male}<1$). 
-%However, equilibrium $(C)$ is never locally stable when $r \approx 0$ and is therefore not considered further.
-%Thus, the Y background can either be fixed for the $a$ allele (equilibria ($A$) and ($B$)) or the $A$ allele (equilibria ($A'$) and ($B'$)).
-%The X background can then either be polymorphic (equilibria ($A$) and ($A'$)) or fixed for the alternative allele (equilibria ($B$) and ($B'$)).
-%Since equilibria $(A)$ and $(B)$ are equivalent to equilibria $(A')$ and $(B')$ with the labelling of $A$ and $a$ alleles interchanged, we discuss only equilibria $(A)$ and $(B)$, in which the Y background is fixed for the $a$ allele.
-%If there is no haploid selection ($\alpha^{\circ}_\Delta=0$, $w_{A}^{\circ}=w_{a}^{\circ}=1$), these equilibria are equivalent to those found by~\cite{Lloyd1977} and~\cite{Otto2014}.
-%
-%We next calculate when equilibria $(A)$ and $(B)$ are locally stable for $r=0$. 
-%According to the `small parameter theory'~\cite{Karlin:1972ab,Karlin:1972dq}, these stability properties are unaffected by small amounts of recombination between the sex-determining locus and the $\mathbf{A}$ locus, although equilibrium frequencies may be slightly altered.
-%For the $a$ allele to be stably fixed on the Y background we need $\bar{w}_{Ya}^{\male} > \bar{w}_{YA}^{\male}$ where $\bar{w}_{Ya}^{\male} = w_{a}^{\male} \big[\hat{p}_X^\female(1-\alpha^\male_\Delta) w_{A}^{\female} w_{Aa}^{\male} + (1-\hat{p}_X^\female)w_{a}^{\female} w_{aa}^{\male} \big]$ and $\bar{w}_{YA}^{\male} = w_{A}^{\male} \big[ \hat{p}_X^\female w_{A}^{\female} w_{AA}^{\male} + (1-\hat{p}_X^\female)(1+\alpha^\male_\Delta) w_{a}^{\female} w_{Aa}^{\male} \big]$.
-%That is, Y-$a$ haplotypes must have higher fitness than Y-$A$ haplotypes.  
-%Substituting in $\hat{p}_X^\female$ from Eq \eqref{eq:tightequil}, fixation of the $a$ allele on the Y background requires that $\gamma_{i}>0$ where $\gamma_{(A)}=w_{a}^{\male} \big[ (1-\alpha^\male_\Delta) w_{Aa}^{\male} \phi + w_{aa}^{\male} \psi \big]-w_{A}^{\male} \big[ w_{AA}^{\male} \phi + (1 + \alpha^{\male}_\Delta)w_{Aa}^{\male} \psi \big]$ for equilibrium $(A)$ and $\gamma_{(B)}=(1-\alpha^{\male}_\Delta)w_{a}^{\male}w_{Aa}^{\male}-w_{A}^{\male}w_{AA}^{\male}$ for equilibrium $(B)$.
-%Stability of a polymorphism on the X background (equilibrium $(A)$) further requires that $\phi >0$ and $\psi >0$. 
-%Fixation of the $a$ allele on the X background (equilibrium $(B)$) can be stable only if equilibrium $(A)$ is not, as it requires $\psi<0$.
-%and $2w_{A}^{\female}w_{AA}^{\female}>(1-\alpha_\Delta^{\female})w_{a}^{\female}w_{Aa}^{\female}$ or just $4w_{A}^{\female}w_{AA}^{\female}<(1-\alpha_\Delta^{\female})w_{a}^{\female}w_{Aa}^{\female}$ (which also prevents $\psi>0$).
-%
-%%\textcolor{red}{check last condition and the stability condition below are correct}
-%%\textcolor{blue}{The last condition looks good to me, although in your Turnover-norec-MFS.nb you look at YA fixed, so you have to flip everything (so I made Turnover-norec-MFS-MMO.nb to do this).
-%%The one issue I can find here is that you can also prevent $\Lambda>1$ when the slope and intercept of the quadratic at $\Lambda=1$ are negative (you only looked at both being positive).
-In this case we need $4w_{A}^{\female}w_{AA}^{\female}<(1-\alpha_\Delta^{\female})w_{a}^{\female}w_{Aa}^{\female}$, which also prevents $\psi>0$.
-%%I've added this in.
-%%It could also be the case that the slope and intercept are the same sign but the roots are imaginary - but this is never the case here.
-%%Stability condition below looks good to me (from matt version of turnoverSOM-MIKE.nb).}
-%
-%\subsubsection*{Selection weak relative to recombination}
-%
-%Here, we assume that selection is weak relative to recombination ($s^\circ$, $t^\circ$, $\alpha_{\Delta}^\circ$ of order $\epsilon$). 
-%The maintenance of a polymorphism at the $\mathbf{A}$ locus then requires that
-%
-%\begin{equation}
-%\begin{split}
-%0&< - \left[(1-h^\female)s^\female +(1-h^\male) s^\male + t^\female +t^\male + \alpha_{\Delta}^\female+\alpha_{\Delta}^\male\right]\\
-%%
-%\text{and }\quad 0&<h^\female s^\female +h^\male s^\male + t^\female +t^\male + \alpha_{\Delta}^\female+\alpha_{\Delta}^\male.
-%\end{split}
-%\end{equation}
-%
-%\noindent
-%which indicates that a polymorphism can be maintained by various selective regimes. 
-%
-%Given that a polymorphism is maintained at the $\mathbf{A}$ locus by weak selection, the frequencies of $A$ in each type of gamete are the same ($\hat{p}^\female_X=\hat{p}^\male_X=\hat{p}^\male_Y=\bar{p}$) and given, to leading order, by
-%
-%\begin{equation}
-%\bar{p}=\frac{h^\female s^\female + h^\male s^\male +t^\female+t^\male+\alpha_{\Delta}^\female+\alpha_{\Delta}^\male}
-%{(2h^\female-1)s^\female+(2h^\male-1)s^\male}
-%+O(\epsilon)
-%.
-%\label{eq:pAve}
-%\end{equation}
-%
-%\noindent
-%Differences in frequency between gamete types are of $O(\epsilon)$:
-%
-%\begin{equation}
-%\begin{split}
-%\hat{p}^\male_X-\hat{p}^\female_X&=\bar{p}(1-\bar{p})\big{(}D^\male - D^\female +\alpha_{\Delta}^\male-\alpha_{\Delta}^\female \big{)}
-%+O(\epsilon^2)\\
-%%
-%\hat{p}^\male_Y-\hat{p}^\female_X&=\bar{p}(1-\bar{p})\left[D^\male - D^\female+\alpha_{\Delta}^\male-\alpha_{\Delta}^\female+(1-2r)(t^\male-t^\female)\right]/2r
-%+O(\epsilon^2)\\
-%%
-%\hat{p}^\male_Y-\hat{p}^\male_X&=\bar{p}(1-\bar{p})\left(D^\male - D^\female+\alpha_{\Delta}^\male-\alpha_{\Delta}^\female+t^\male-t^\female\right)(1-2r)/2r
-%+O(\epsilon^2),
-%\end{split}
-%\label{eq:freq_diffs}
-%\end{equation}
-%
-%\noindent
-%where $\bar{p}(1-\bar{p})=\bar{p}(1-\bar{p})$ is the variance in the frequency of $A$ and $D^\circ=\big{[} \bar{p}s^\circ+(1-\bar{p})h^\circ s^\circ\big{]} -\big{[} \bar{p}h^\circ s^\circ+(1-\bar{p}) \big{]}$ corresponds to the difference in fitness between $A$ and $a$ alleles in diploids of sex $\circ \in \{\female,\male\}$.
-%The frequency of Y-bearing male gametes depends upon the difference in the frequency of the $A$ allele between X- and Y-bearing male gametes and the strength of meiotic drive in favour of the $A$ allele in males, $q=1/2+\alpha_{\Delta}^\male(\hat{p}^\male_Y-\hat{p}^\male_X)/2+O(\epsilon^3)$.
-%Without gametic competition or drive ($\alpha_{\Delta}^\circ=t^\circ=0$) our results reduce to those of~\cite{vanDoorn:2007eu}.
-
-%\newpage
-
-%\setcounter{equation}{0}
-%\renewcommand{\theequation}{S3.\arabic{equation}}
-%
-%\section*{S3 Appendix}
-%
-%\subsection*{Invasion conditions}
-%
-%A rare neo-Y or neo-W allele, $m$, will spread in an XY sex-determining system when the leading eigenvalue, $\lambda_m^{(XY)}$, of the Jacobian matrix derived from the eight mutant recursion equations (given by \ref{eq:recursions}c,d,g,h), evaluated at the ancestral equilibrium, is greater than one.
-%However, because a neo-Y (neo-W) is always in males (females) and is epistatically dominant to the ancestral sex-determining locus, the characteristic polynomial factors into two quadratics times $(\lambda_m^{(XY)})^4$.
-%One quadratic governs the change in the frequency of the new sex determination factor associated with the $A$ and $a$ allele frequencies, summing across backgrounds at the old sex-determining locus (i.e., summing haplotypes bearing the original X and Y alleles).
-%%It is the largest root of this quadratic that determines the spread of the new $m$ allele (see details in \nameref{file:Mathematica}).  
-%The second quadratic describes the dynamics of the difference in the $m$-$A$ and $m$-$a$ haplotypes between X and Y backgrounds.  
-%Asymptotically, this difference is constrained to grow at a rate equal to or less than the sum while the $m$ allele is rare, because the frequencies can never become negative. 
-%We therefore focus on the leading eigenvalue, $\lambda_m^{(XY)}$, which is the largest root of the first quadratic $f(x) = x^2+ b x + c = 0$, as described in the text (details in \nameref{file:Mathematica}).
-%
-%When $R=0$ the two roots are $\Lambda_{mA}^{(XY)}$ and $\Lambda_{ma}^{(XY)}$, and the leading eigenvalue is the larger of the two.
-%When $R>0$ then $f(\Lambda_{mA}^{(XY)})$ and $f(\Lambda_{ma}^{(XY)})$ are of opposite signs, and the leading eigenvalue must fall between these two quantities (details in \nameref{file:Mathematica}).
-%(the Perron-Frobenius theorem guarantees that the largest eigenvalue is positive, unique, and real).
-%Thus, $\lambda_m^{(XY)}>1$ if both $\Lambda_{mA}^{(XY)}>1$ and $\Lambda_{ma}^{(XY)}>1$; similarly, $\lambda_m^{(XY)}<1$ if both $\Lambda_{mA}^{(XY)}<1$ and $\Lambda_{ma}^{(XY)}<1$.
-%If only one haplotypic growth rate is greater than one ($\Lambda_{ma}^{(XY)}<1<\Lambda_{mA}^{(XY)}$ or $\Lambda_{mA}^{(XY)}<1<\Lambda_{ma}^{(XY)}$), then $\lambda_m^{(XY)}$ is greater than one when condition \eqref{eq:lambdasGen} is met.
-%Thus, the invasion of a new sex-determining allele is determined by the haplotypic growth rates ($\Lambda_{mj}^{(XY)}$ terms), which do not account for loss due to recombination, and the rates at which recombination between the $\mathbf{M}$ and $\mathbf{A}$ loci breaks apart these haplotypes ($\chi_{mj}^{(XY)}$).
-%For tight linkage between the ancestral sex-determining locus ($\mathbf{X}$) and the selected locus ($\mathbf{A}$) we can calculate these terms explicitly (see below).
-%For weak selection we approximate the leading eigenvalue with a Taylor series. 
-%The leading eigenvalue for any $k$ is given up to order $\epsilon^2$ by Eq \eqref{eq:lambda_ESD_k}.
-%
-%\subsubsection*{Tight linkage between $\mathbf{A}$ and $\mathbf{X}$ ($r \approx 0$)}
-%
-%Here, we explore the conditions under which a neo-W invades an XY system assuming that the $\mathbf{A}$ locus is initially in tight linkage with the ancestral sex-determining locus ($r \approx 0$). 
-%We disregard neo-Y mutations, which never spread given that the ancestral population is at a stable equilibrium (see \nameref{file:Mathematica} for proof). 
-%
-%Starting with the simpler $(B)$ equilibrium, the terms that determine the leading eigenvalue are
-%
-%\begin{subequations}\label{Binvasion}
-%\begin{align}
-%\Lambda_{W'A}^{(XY)}&= {\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]}^{-1}
-%\frac{w_{A}^\female }{w_{A}^\female}
-%\frac{\left[ w_{A}^\male (1+\alpha^\male_\Delta) w_{AA}^\female + 
-%w_{a}^\male (1-\alpha^\male_\Delta) w_{Aa}^\female (1+\alpha^\female_\Delta) \right]}
-%{ 2w_{AA}^\female } \\
-%\Lambda_{W'a}^{(XY)}&= {\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]}^{-1}
-%\frac{w_{a}^\female}{w_{A}^\female}
-%\frac{\left[  w_{A}^\male (1+\alpha^\male_\Delta) w_{Aa}^\female (1-\alpha^\female_\Delta)+
-%w_{a}^\male (1-\alpha^\male_\Delta) w_{aa}^\female \right]}
-%{ 2w_{AA}^\female } \\
-%\chi_{W'A}^{(XY)}&= \frac{1}{2} {\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]}^{-1}
-%\frac{w_{A}^\female }{w_{A}^\female}
-% \frac{\left[  w_{a}^\male (1-\alpha^\male_\Delta) w_{Aa}^\female (1 + \alpha^\female_\Delta) \right]}
-%{ w_{AA}^\female } \frac{R}{2}\\
-%\chi_{W'a}^{(XY)}&= \frac{1}{2} {\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]}^{-1}
-%\frac{w_{a}^\female}{w_{A}^\female}
-% \frac{\left[  w_{A}^\male (1+\alpha^\male_\Delta) w_{Aa}^\female (1-\alpha^\female_\Delta) \right]}
-%{  w_{AA}^\female} \frac{R}{2}.
-%\end{align}
-%\end{subequations}
-%
-%%\noindent
-%%In this case, the zygotic sex ratio ($\zeta$) is given by the difference in haploid selection in males on $a$ (fixed on the Y) and $A$ (fixed on the X) alleles, i.e., there are more males than females if $\zeta = \alpha^\male w_A^\male / [(1-\alpha^\male)w_a^\male + \alpha^\male w_A^\male]<1/2$.
-%$\alpha^\male<1/2$ and/or $w_{a}^\male>w_{A}^\male$.
-%%Populations with haploid selection for $a$ in males have a male biased zygotic sex ratio are thus more permissive to invasion by a neo-W ($\Lambda_{mA}$ and $\Lambda_{ma}$ larger).
-%%%In addition, the spread of neo-W alleles depends on the fitness of female diploids after mating with an X-$A$ or Y-$a$ male gamete, relative to the fitness of females in the population (all have genotype $AA$ and fitness $w_{AA}^\female$ at this equilibrium).
-%%Haploid selection in males has a second effect; the spread rate of neo-W haplotypes is determined by their fitness in diploid females, which depends on their diploid genotype and thus on the male gamete they pair with.
-%%Zygotes carrying dominant neo-W alleles will develop as females regardless of their genotype at the XY locus. 
-%%Therefore, neo-W females result from matings with either X-$A$ or Y-$a$ male gametes. 
-%%The relative proportion of these male gametes is determined by haploid selection in males; mating with a Y-$a$ male gamete is more likely if the $a$ allele is favoured during male gamete production or competition ($\zeta<1/2$).
-%%Thus, neo-W females experience different diploid selection than XX females, and the extent of this difference depends on haploid selection in males.
-%%Furthermore, haploid selection in females can directly select upon neo-W-$A$ or neo-W-$a$ haplotypes. 
-%%A neo-W-$A$ female gamete has the same fitness during haploid competition as resident $A$-bearing female gametes. 
-%%On the other hand, neo-W-$a$ female gametes can be favoured or disfavoured during female haploid competition (favoured if $w_{a}^\female>w_{A}^\female$). 
-%%Meiotic drive in females ($\alpha^\female$) similarly affects the fitness of these neo-W haplotypes, except that it impacts both haplotypes as meiotic drive only occurs in heterozygotes and therefore does not occur in resident XX females (who are always homozygote $AA$).
-%
-%Haploid selection impacts the spread of neo-W haplotypes in three ways (also seen in Table \ref{tab:haplotype_growth}).
-%Firstly, the zygotic sex ratio becomes male biased, $\zeta>1/2$, when the $a$ allele (which is fixed on the Y) is favoured during competition among male gametes or by meiotic drive in males.
-%Specifically, at equilibrium $(B)$, female zygote frequency is $1 - \zeta = w_A^\male (1+\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$ where $2\bar{w}_{H}^\male= \big[w_a^\male (1-\alpha^\male_\Delta) +  w_A^\male (1+\alpha^\male_\Delta) \big]$ has been canceled out in equations \eqref{Binvasion} to leave the term ${\left[w_{A}^\male (1+\alpha^\male_\Delta) \right]}^{-1}$.
-%Male biased sex ratios facilitate the spread of a neo-W because neo-W alleles cause the zygotes that carry them to develop as the rarer, female, sex. 
-%
-%Secondly, haploid selection in females selects on neo-W haplotypes directly.
-%At equilibrium $(B)$, the fitness of female gametes under the ancestral sex-determining system is $w_{A}^\female$ such that the relative fitnesses of neo-W-$A$ and neo-W-$a$ haplotypes during female gametic competition are $w_{A}^\female/w_{A}^\female$ and $w_{a}^\female/w_{A}^\female$ (see terms in equation \ref{Binvasion}).
-%Meiotic drive in females will also change the proportion of gametes that carry the $A$ versus $a$ alleles, which will be produced by heterozygous females in proportions $(1+\alpha_{\Delta}^\female)/2$ and $(1-\alpha_{\Delta}^\female)/2$, respectively.
-%These terms are only associated with heterozygous females, i.e., they are found alongside $w_{Aa}^\female$.
-%
-%Thirdly, haploid selection in males affects the diploid genotypes of females by altering the allele frequencies in the male gametes with which female gametes pair.
-%At equlibrium $(B)$, neo-W female gametes will mate with X-$A$ male gametes with probability $ w_A^\male (1+\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$ and Y-$a$ male gametes with probability $w_a^\male (1-\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$, where the $2\bar{w}_{H}^\male$ terms have been canceled in Eq \eqref{Binvasion} (as mentioned above).
-%Thus, neo-W-$A$ haplotypes are found in $AA$ female diploids with probability $ w_A^\male (1+\alpha^\male_\Delta)/ (2\bar{w}_{H}^\male)$ (e.g., first term in square brackets in the numerator of equation \ref{Binvasion}a) and in $Aa$ female diploids with probability $w_a^\male (1-\alpha^\male_\Delta) / (2\bar{w}_{H}^\male)$ (e.g., the second term in square brackets in the numerator of equation \ref{Binvasion}a).
-%
-%%For instance, because an epistatically dominant neo-W always causes its carrier to become female, it creates females who carry either Y-$a$ or X-$A$ genotypes from their father.
-%%Thus, because when there is a polymorphism the X carries some non-zero frequency of $A$, haploid selection in males impacts the diploid genotypes of females (e.g., creating more $Aa$ females when drive in males favours Y-$a$).
-%%How this affects the spread of the neo-W then depends on diploid and haploid selection in females.
-%
-%The other terms in equations \eqref{Binvasion} are more easily interpreted if we assume that there is no haploid selection in either sex, in which case $\Lambda_{W'A}^{(XY)}=(w_{AA}^\female+w_{Aa}^\female)/2 w_{AA}^\female$ and $\Lambda_{W'a}^{(XY)}=(w_{aa}^\female+w_{Aa}^\female)/ 2 w_{AA}^\female$.
-%Neither haplotype can spread under purely sexually-antagonistic selection at equilibrium $(B)$, with directional selection in each sex.
-%Essentially, the X is then already as specialized as possible for the female beneficial allele ($A$ is fixed on the X background), and the neo-W often makes daughters with the Y-$a$ haplotype, increasing the flow of $a$ alleles into females, which reduces the fitness of those females.
-%
-%If selection doesn't uniformly favour $A$ in females, however, neo-W-$A$ haplotypes and/or neo-W-$a$ haplotypes can spread ($\Lambda_{W'A}^{(XY)}>1$ and/or $\Lambda_{W'a}^{(XY)}>1$).
-%%If $\Lambda_{mA}>1$ (requiring $w_{Aa}^\female>w_{AA}^\female$), the implication is that the neo-W can spread alongside the $A$ allele, despite the fact that the neo-W sometimes brings $Y-a$ haplotypes into females, because $a$ is favoured by selection in females despite $A$ being fixed on the X.
-%A neo-W-$A$ haplotype can spread ($\Lambda_{W'A}^{(XY)}>1$) when $w_{Aa}^\female>w_{AA}^\female$, despite the fact that a neo-W brings Y-$a$ haplotypes into females.
-%In this case the $a$ allele is favoured by selection in females despite $A$ being fixed on the X background.
-%For this equilibrium to be stable (i.e.,  to keep $A$ fixed on the X), X-$a$ cannot be overly favoured in females and X-$A$ must be sufficiently favoured in males (for example, by overdominance in males).
-%Specifically, from the stability conditions for equilibrium (B), we must have $w_{Aa}^\female < 2 w_{AA}^\female$ and $w_{Aa}^\male/\big[(w_{aa}^\male+w_{Aa}^\male)/2\big]>w_{Aa}^\female/w_{AA}^\female$.
-%
-%Still considering $w_{Aa}^\female>w_{AA}^\female$, the neo-W can also spread alongside the $a$ allele ($\Lambda_{W'a}^{(XY)}>1$) if $w_{aa}^\female$ is large enough such that $(w_{Aa}^\female+w_{aa}^\female)/2>w_{AA}^\female$.
-%%there is sufficiently strong underdominance in females ($w_{aa}^\female>w_{Aa}^\female$) \textcolor{blue}{[this is describing directional selection, not overdominance - check the conditions for the case we want to talk about]}, such that $(w_{Aa}^\female+w_{aa}^\female)/2>w_{AA}^\female$.
-%This can occur with overdominance or directional selection for $a$ in females (Fig \ref{fig:regionplots}B,C).
-%In this case, $a$ is favoured on the ancestral Y background in males and on the ancestral X background in females (comparing $Aa$ to $AA$ genotypes in females) but $A$ is fixed on the X background due to selection in males.
-%The neo-W-$a$ haplotype can spread because it produces females with higher fitness $Aa$ and $aa$ genotypes. 
-%
-%%When both haplotypes can spread on their own ($\Lambda_{mA}>1$ and $\Lambda_{ma}>1$), the neo-W invades regardless the recombination rate between it and the selected locus, $R$.
-%%When neither haplotype can spread ($\Lambda_{mA}<1$ and $\Lambda_{ma}<1$) the neo-W can never invade.
-%%And when only one haplotype can spread on its own the neo-W invades only when the rate of recombination onto the favourable background is sufficiently larger than the rate of recombination off this background (i.e., equation\ref{eq:lambdasGen} is satisfied).
-%
-%%Haploid selection affects the conclusions outlined above by altering the zygotic sex ratio and exerting direct selection on neo-W haplotypes.
-%%The effect of sex-ratio selection is straightforward and can be seen in Eq \eqref{Binvasion}, where male drive and gamete competition for $a$ (which is fixed on the Y and therefore causes a male bias) increases all four terms.
-%%Direct selection on neo-W haplotypes can also be seen in Eq \eqref{Binvasion} by noticing that increasing female drive in favour of $A$ increases the neo-W-$A$ haplotype growth rate ($\Lambda_{mA}$) while female drive and gamete competition in favour of $a$ increases the neo-W-$a$ haplotype growth rate ($\Lambda_{ma}$).
-%%Gamete competition in females does not impact the spread of neo-W-$A$ haplotypes because they are on the same background as the resident X.
-%%Recombination between the selected locus and the neo-W complicates things slightly, as selective advantages for one neo-W haplotype during the haploid stage in females comes at a cost to the other, and thus recombination off the favoured background becomes more detrimental.
-%
-%%\textcolor{red}{the versions for equil $(A)$ are not terrible but could be improved by cleverly re-writing with the $\phi$ and $\psi$ terms from above, I think...}
-%
-%Similar equations can be derived for equilibrium (A) by substituting the equilibrium frequencies into Table \ref{tab:haplotype_growth}
-%
-%\begin{subequations}\label{Ainvasion}
-%\begin{align}
-%\Lambda_{W'A}^{(XY)}&= \frac{a}{b} \left[w_{AA}^\female w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi +  w_{Aa}^\female (1+\alpha^\female_\Delta) w_a^\male c \right] / (2 w_a^\female) \\
-%\Lambda_{W'a}^{(XY)}&= \frac{a}{b} \left[ w_{Aa}^\female (1-\alpha^\female_\Delta) w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi +  w_{aa}^\female w_a^\male c \right] / (2 w_A^\female) \\
-%\chi_{W'A}^{(XY)}&= \frac{a}{b} \frac{R}{2} \left[   w_{Aa}^\female (1+\alpha^\female_\Delta) w_a^\male c \right] / w_a^\female\\ 
-%\chi_{W'a}^{(XY)}&= \frac{a}{b} \frac{R}{2} \left[ w_{Aa}^\female (1-\alpha^\female_\Delta) w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \phi \right] / w_A^\female,
-%%\Lambda_{W'A}^{(XY)}&=   {\left[ 2 (1 - \zeta) \right]}^{-1} w_A^{\female} \left[ b w_{AA}^\female + c w_{Aa}^\female \left(1 - \alpha^\female_\Delta \right) \right]/ \left(\bar{w}_H^\female \bar{w}_H^\male \bar{w}^{\female}_{D} \right)  \\
-%%\Lambda_{W'a}^{(XY)}&=  \\
-%%\chi_{W'A}^{(XY)}&= \\ 
-%%\chi_{W'a}^{(XY)}&=
-%\end{align}
-%\end{subequations}
-%
-%\noindent
-%where 
-%
-%\begin{subequations}
-%\begin{align}
-%a &= w_a^\female \phi + w_A^\female \psi \\
-%b &= w_{AA}^\female \left[ w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) \right] \phi^2 + w_{Aa}^\female \left[ w_{Aa}^\male w_A^\male (1+\alpha^\male_\Delta) + w_{aa}^\male w_a^\male \right] \psi \phi + w_{aa}^\female \left( w_{aa}^\male w_a^\male \right) \psi^2\\
-%%c &= w_{Aa}^\male (1-\alpha^\male_\Delta) \phi \left[ w_{Aa}^\male (1+\alpha^\male_\Delta) \phi \right] + w_{Aa}^\male\phi \left[ 2w_{AA}^\male + w_{aa}^\male (1+\alpha^\male_\Delta) \right] \psi + w_{aa}^\male \psi \left(2w_{AA}^\male \psi \right) \\
-%c &= w_{Aa}^\male (1-\alpha^\male_\Delta) \phi + 2w_{aa}^\male \psi.
-%\end{align}
-%\end{subequations}
-%
-%%\textcolor{red}{Sally suggests using some $\zeta$ term in the above equations}
-%%\textcolor{blue}{Maybe just reference table 2?}
-%
-%As with equilibrium (B), haploid selection again modifies invasion fitnesses by altering the ancestral sex ratio, $\zeta$ (see Table \ref{tab:haplotype_growth}), and directly selecting upon female gametes, through $w_{i}^\female$.
-%The only difference is that resident XX females are no longer always homozygote $AA$ and males are no longer always heterozygote $Aa$.
-%Thus the effect of haploid selection in males is reduced, as is the difference in fitness between neo-W haplotypes and resident X haplotypes, as both can be on any diploid or haploid background.  
-%
-%The other terms are easier to interpret in the absence of haploid selection.
-%For instance, without haploid selection, the neo-W-$A$ haplotype spreads ($\Lambda_{W'A}^{(XY)}>1$) if and only if
-%
-%\begin{equation}\label{eq:BeqWAspread}
-%2(w_{Aa}^\female-w_{aa}^\female)w_{aa}^\male \psi^2 > (w_{AA}^\female-w_{Aa}^\female)w_{Aa}^\male \phi (\phi-\psi),
-%\end{equation}
-%
-%\noindent  
-%where $\phi-\psi=w_{AA}^\female w_{Aa}^\male-w_{aa}^\female w_{aa}^\male$ and both $\phi$ and $\psi$ are positive when equilibrium (A) is stable. 
-%In contrast to equilibrium (B), a neo-W haplotype can spread under purely sexually-antagonistic selection  ($w_{aa}^\female<w_{Aa}^\female<w_{AA}^\female$ and $w_{AA}^\male<w_{Aa}^\male<w_{aa}^\male$).
-%The neo-W-$A$ can spread as long as it becomes associated with females that bear more $A$ alleles than observed at equilibrium (A), effectively specializing on female fitness. 
-%%In this case, the neo-W-$A$ haplotype can spread, despite producing a lot of $Aa$ daughters by obtaining the $a$ from Y-gametes, when $aa$ females, which the neo-W-$A$ never makes, are strongly selected against.
-%%This can be intuited from the fact that \eqref{eq:BeqWAspread} will be more easily met when $w_{Aa}^\female-w_{aa}^\female\approx w_{Aa}^\female$ and $w_{AA}^\female-w_{Aa}^\female\approx 0$, implying $w_{aa}^\female \approx 0$ and $w_{Aa}^\female\approx w_{AA}^\female$ (although this is complicated by the fact that $w_{aa}^\female$ and $w_{Aa}^\female$ affect $\phi$ and $\psi$ too, the intuition holds).
-%
-%Without haploid selection, the neo-W-$a$ haplotype spreads ($\Lambda_{W'a}^{(XY)}>1$) if and only if
-%
-%\begin{equation}\label{eq:BeqWaspread}
-%(w_{aa}^\female + w_{Aa}^\female-2w_{AA}^\female)w_{Aa}^\male \phi^2 + (w_{aa}^\female-w_{Aa}^\female)(w_{Aa}^\male+2w_{aa}^\male) \phi \psi >0.
-%\end{equation}
-%
-%\noindent
-%This condition cannot be met with purely sexually antagonistic selection (as both terms on the left-hand side would then be negative), but it can be met under other circumstances. 
-%For example, with overdominance in males there is selection for increased $A$ frequencies on the X background in males, which are always paired with Y-$a$ haplotypes.
-%Directional selection for $a$ in females can then maintain a polymorphism at the $\mathbf{A}$ locus on the X background.
-%This scenario selects for a modifier that increases recombination between the sex chromosomes (e.g., blue region of Fig 2d in~\cite{Otto2014}) and facilitates the spread of neo-W-$a$ haplotypes, which create females bearing more $a$ alleles than the ancestral X haplotype does.
-%
-%\subsubsection*{Role of haploid selection with tight linkage between $\mathbf{X}$ and $\mathbf{A}$ loci}
-%
-%Haploid selection generally expands the conditions under which neo-W alleles can spread within ancestral systems that have evolved tight linkage between the sex-determining locus and a selected locus ($r \approx 0$).
-%First, haploid selection can allow a polymorphism to be maintained when it would not under diploid selection alone (e.g., with directional selection in diploids). 
-%In cases of ploidally-antagonistic selection, where there is a balance between alleles favored in the haploid stage and the diploid stage, neo-W alleles - even if unlinked to the selected locus - can spread (\nameref{fig:regionPloidAntag}).
-%Second, even when diploid selection could itself maintain a polymorphism, haploid selection can increase the conditions under which transitions among sex-determining systems are possible.
-%Of particularly importance, when selection is sexually-antagonistic in diploids ($s^\female s^\male <0$ and $0<h^\circ<1$), an unlinked neo-W ($R=1/2$) cannot invade unless there is also haploid selection (see proof in \nameref{file:Mathematica}; Fig \ref{fig:SexAntagTighter} and \nameref{fig:SexAntagTighterMaleDrive}).
-%More generally, haploid selection alters the conditions under which neo-W alleles can spread (compare \nameref{fig:regionMaleDrive}-\nameref{fig:regionFemaleGS} to Fig \ref{fig:regionplots}). 
-%
-%%[SALLY:  I think that is enough, but we could add somewhere??: "Without haploid selection, unlinked neo-W alleles ($R=1/2$) can invade only under certain conditions, requiring either overdominance in males or underdominance in females (see proof in supplementary \textit{Mathematica} file).?
-Note that underdominance in females with directional selection in males can lead to the spread of unlinked neo-W?s, but only from equilB (only $\Lambda_{ma}$ is greater than one in this case).]
-%
-%Male haploid selection in favour of the $a$ allele ($\alpha_{\Delta}^\male<0$, $w_{A}^\male<w_{a}^\male$) generates male-biased sex ratios at equilibria (A) and (B), where Y-$a$ is fixed ($\hat{p}_{Y}^\male=0$).
-%Male-biased sex ratios facilitate the spread of neo-W-$A$ and neo-W-$a$ haplotypes (increasing $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$). 
-%Panels A-C in \nameref{fig:regionMaleDrive} and \ref{fig:regionMaleGS} show that neo-W haplotypes tend to spread for a wider range of parameters when sex ratios are male biased, compared to Fig \ref{fig:regionplots} without haploid selection.
-%By contrast, male haploid selection in favour of the $A$ allele generates female-biased sex ratios and reduces $\Lambda_{W'A}^{(XY)}$ and $\Lambda_{W'a}^{(XY)}$, as demonstrated by panels D-F in \nameref{fig:regionMaleDrive} and \nameref{fig:regionMaleGS}.
-%
-%Female haploid selection generates direct selection on the neo-W-$A$ and neo-W-$a$ haplotypes as they spread in females. 
-%Thus, female haploid selection in favour of the $a$ allele tends to increase $\Lambda_{W'a}^{(XY)}$ and decrease $\Lambda_{W'A}^{(XY)}$, as shown by panels A-C in \nameref{fig:regionFemaleDrive} and \nameref{fig:regionFemaleGS}.
-%Conversely, female haploid selection in favour of the $A$ allele increases $\Lambda_{W'A}^{(XY)}$ and decreases $\Lambda_{W'a}^{(XY)}$, see panels D-F in \nameref{fig:regionFemaleDrive} and \nameref{fig:regionFemaleGS}.
-%
-%Thus, the impact of haploid selection on transitions between sex-determining systems must be considered as two sides of a coin: it can generate sex-ratio biases that promote transitions that equalize the sex ratio, but it can also direct select for transitions that cause sex ratios to become biased.
+
+\begin{thebibliography}{100}
+
+\bibitem{Bull:1983vi}
+Bull JJ.
+\newblock {Evolution of sex determining mechanisms.}
+\newblock Menlo Park, CA: The Benjamin Cummings Publishing Company; 1983.
+
+\bibitem{Charlesworth:2010it}
+Charlesworth D, Mank JE.
+\newblock {The birds and the bees and the flowers and the trees: lessons from
+  genetic mapping of sex determination in plants and animals}.
+\newblock Genetics. 2010;186(1):9--31.
+
+\bibitem{Beukeboom:2014vb}
+Beukeboom LW, Perrin N.
+\newblock {The evolution of sex determination}.
+\newblock Oxford, UK: Oxford University Press; 2014.
+
+\bibitem{Bachtrog:2014bx}
+Bachtrog D, Mank JE, Peichel CL, Kirkpatrick M, Otto SP, Ashman TL, et~al.
+\newblock {Sex determination: why so many ways of doing it?}
+\newblock PLoS Biology. 2014;12(7):e1001899.
+
+\bibitem{Pennell2018}
+Pennell MW, Mank JE, Peichel CL.
+\newblock Transitions in sex determination and sex chromosomes across
+  vertebrate species.
+\newblock Molecular Ecology. 2018;Early Online.
+\newblock doi:{10.1111/mec.14540}.
+
+\bibitem{Ming:2011iy}
+Ming R, Bendahmane A, Renner SS.
+\newblock {Sex chromosomes in land plants}.
+\newblock Annual Review of Plant Biology. 2011;62(1):485--514.
+
+\bibitem{Li:2011fm}
+Li J, Phillips RB, Harwood AS, Koop BF, Davidson WS.
+\newblock {Identification of the sex chromosomes of brown trout (\textit{Salmo
+  trutta}) and their comparison with the corresponding chromosomes in Atlantic
+  salmon (\textit{Salmo salar}) and rainbow trout (\textit{Oncorhynchus
+  mykiss})}.
+\newblock Cytogenetic and Genome Research. 2011;133(1):25--33.
+
+\bibitem{Yano:2012di}
+Yano A, Nicol B, Jouanno E, Quillet E, Fostier A, Guyomard R, et~al.
+\newblock {The sexually dimorphic on the Y-chromosome gene (sdY) is a conserved
+  male-specific Y-chromosome sequence in many salmonids}.
+\newblock Evolutionary Applications. 2012;6(3):486--496.
+
+\bibitem{Vicoso:2015hf}
+Vicoso B, Bachtrog D.
+\newblock {Numerous transitions of sex chromosomes in Diptera.}
+\newblock PLoS Biology. 2015;13(4):e1002078.
+
+\bibitem{Myosho:2012fv}
+Myosho T, Otake H, Masuyama H, Matsuda M, Kuroki Y, Fujiyama A, et~al.
+\newblock {Tracing the emergence of a novel sex-determining gene in medaka,
+  \textit{Oryzias luzonensis}}.
+\newblock Genetics. 2012;191(1):163--170.
+
+\bibitem{Gamble2017}
+Gamble T, Castoe TA, Nielse SV, Banks JL, Card DC, Schield DR, et~al.
+\newblock {The discovery of XY sex chromosomes in a \textit{Boa} and
+  \textit{Python}}.
+\newblock Current Biology. 2017;27:2148--2152.
+
+\bibitem{Ezaz:2009tk}
+Ezaz T, Sarre SD, O'Meally D.
+\newblock {Sex chromosome evolution in lizards: independent origins and rapid
+  transitions}.
+\newblock Cytogenetic and Genome Research. 2009;127:249--260.
+
+\bibitem{Mank:2006bt}
+Mank JE, Promislow DEL, Avise JC.
+\newblock {Evolution of alternative sex-determining mechanisms in teleost
+  fishes}.
+\newblock Biological Journal of the Linnean Society. 2006;87(1):83--93.
+
+\bibitem{Hillis:1990gu}
+Hillis DM, Green DM.
+\newblock {Evolutionary changes of heterogametic sex in the phylogenetic
+  history of amphibians}.
+\newblock Journal of Evolutionary Biology. 1990;3(1):49--64.
+
+\bibitem{Slancarova:2013dq}
+Slancarova V, Zdanska J, Janousek B, Talianova M, Zschach C, Zluvova J, et~al.
+\newblock {Evolution of sex determination systems with heterogametic males and
+  females in \emph{Silene}}.
+\newblock Evolution. 2013;67(12):3669--3677.
+
+\bibitem{Pucholt2015}
+Pucholt P, R{\"o}nnberg-W{\"a}stljung AC, Berlin S.
+\newblock {Single locus sex determination and female heterogamety in the baskey
+  willow (\textit{Salix viminalis} L.)}.
+\newblock Heredity. 2015;114:575--583.
+
+\bibitem{Pucholt2017}
+Pucholt P, Wright A, Conze LL, Mank JE, Berlin S.
+\newblock {Recent sex chromosome divergence despite ancient dioecy in the
+  willow \textit{Salix viminalis}}.
+\newblock Molecular Biology and Evolution. 2017;34:1991--2001.
+
+\bibitem{Macdonald1978}
+McDonald IC, Evenson P, Nickel CA, Johnson OA.
+\newblock {House fly genetics: isolation of a female determining factor on
+  chromosome 4}.
+\newblock Annals of the Entomological Society of America. 1978;71:692--694.
+
+\bibitem{Thompson1971}
+Thompson PE.
+\newblock {Male and female heterogamety in population of \textit{Chironomus
+  tentans} (Diptera: Chironomidae)}.
+\newblock The Canadian Entomologist. 1971;103:369--372.
+
+\bibitem{Ogata:2007jm}
+Ogata M, Hasegawa Y, Ohtani H, Mineyama M, Miura I.
+\newblock {The ZZ/ZW sex-determining mechanism originated twice and
+  independently during evolution of the frog, \textit{Rana rugosa}}.
+\newblock Heredity. 2007;100(1):92--99.
+
+\bibitem{Ser:2010iq}
+Ser JR, Roberts RB, Kocher TD.
+\newblock {Multiple interacting loci control sex determination in lake Malawi
+  cichlid fish.}
+\newblock Evolution. 2010;64(2):486--501.
+
+\bibitem{Lee2004}
+Lee BY, Hulata G, Kocher TD.
+\newblock {Two unlinked loci controlling the sex of blue tilapia
+  (\textit{Oreochromis aureus})}.
+\newblock Heredity. 2004;92:543--549.
+
+\bibitem{Vandeputte2007}
+Vandeputte M, Dupont-Nivet M, Chavanne H, Chatain B.
+\newblock {A polygenic hypothesis for sex determination in the European sea
+  bass \textit{Dicentrarchus labrax}}.
+\newblock Genetics. 2007;176:1049--1057.
+
+\bibitem{Liew2012}
+Liew WC, Bartfai R, Lim Z, Sreeninvasan R, Siegfried KR, Orban L.
+\newblock {Polygenic sex determination system in Zebrafish}.
+\newblock PLoS One. 2012;4:e34397.
+
+\bibitem{Wilson2014}
+Wilson CA, High SK, McCluskey BM, Amores A, Yan Y, Titus TA, et~al.
+\newblock {Wild sex in zebrafish: loss of the natural sex determinant in
+  domesticated strains}.
+\newblock Genetics. 2014;198(3):1291--1308.
+
+\bibitem{Conover:1987in}
+Conover DO, Heins SW.
+\newblock {Adaptive variation in environmental and genetic sex determination in
+  a fish}.
+\newblock Nature. 1987;326(6112):496--498.
+
+\bibitem{Pokorna:2009ui}
+Pokorn{\'a} M, Kratochv{\'i}l L.
+\newblock {Phylogeny of sex-determining mechanisms in squamate reptiles: are
+  sex chromosomes an evolutionary trap?}
+\newblock Zoological Journal of the Linnean Society. 2009;156:168--183.
+
+\bibitem{Pen:2010kk}
+Pen I, Uller T, Feldmeyer B, Harts A, While GM, Wapstra E.
+\newblock {Climate-driven population divergence in sex-determining systems}.
+\newblock Nature. 2010;468(7322):436--438.
+
+\bibitem{Holleley:2015hc}
+Holleley CE, O'Meally D, Sarre SD, Marshall~Graves JA, Ezaz T, Matsubara K,
+  et~al.
+\newblock {Sex reversal triggers the rapid transition from genetic to
+  temperature-dependent sex}.
+\newblock Nature. 2015;523(7558):79--82.
+
+\bibitem{Fisher:1930wy}
+Fisher R.
+\newblock {The genetical theory of natural selection}.
+\newblock London: Clarendon Press; 1930.
+
+\bibitem{Charnov:1982wg}
+Charnov EL.
+\newblock {The theory of sex allocation.}
+\newblock Princeton, NJ: Princeton University Press; 1982.
+
+\bibitem{West:2009we}
+West S.
+\newblock {Sex allocation}.
+\newblock Princeton, NJ: Princeton University Press; 2009.
+
+\bibitem{Blaser2012}
+Blaser O, Grossen C, Neuenschwander S, Perrin N.
+\newblock {Sex-chromosome turnovers induced by deleterious mutation load}.
+\newblock Evolution. 2012;67:635--645.
+
+\bibitem{vanDoorn2014re}
+van Doorn GS.
+\newblock {Patterns and mechanisms of evolutionary tranistions between genetic
+  sex-determining systems}.
+\newblock Cold Spring Harbour Perspectives in Biology. 2014;6:a017681.
+
+\bibitem{vanDoorn:2007eu}
+van Doorn GS, Kirkpatrick M.
+\newblock {Turnover of sex chromosomes induced by sexual conflict.}
+\newblock Nature. 2007;449(7164):909--912.
+
+\bibitem{vanDoorn:2010hu}
+van Doorn GS, Kirkpatrick M.
+\newblock {Transitions between male and female heterogamety caused by
+  sex-antagonistic selection}.
+\newblock Genetics. 2010;186(2):629--645.
+
+\bibitem{Muralidhar2018}
+Muralidhar P, Veller C.
+\newblock {Sexual antagonism and the instability of environmental sex
+  determination}.
+\newblock Nature Ecology and Evolution. 2018;2:343–351.
+
+\bibitem{Mulcahy:1996ha}
+Mulcahy DL, Sari-Gorla M, Mulcahy GB.
+\newblock {Pollen selection - past, present and future}.
+\newblock Sexual Plant Reproduction. 1996;9(6):353--356.
+
+\bibitem{JOSEPH:2004haa}
+Joseph S, Kirkpatrick M.
+\newblock {Haploid selection in animals}.
+\newblock Trends in Ecology {\&} Evolution. 2004;19(11):592--597.
+
+\bibitem{Ubeda:2005gw}
+{\'U}beda F, Haig D.
+\newblock {On the evolutionary stability of Mendelian segregation.}
+\newblock Genetics. 2005;170(3):1345--1357.
+
+\bibitem{Lindholm:2016cw}
+Lindholm AK, Dyer KA, Firman RC, Fishman L, Forstmeier W, Holman L, et~al.
+\newblock {The ecology and evolutionary dynamics of meiotic drive.}
+\newblock Trends in Ecology {\&} Evolution. 2016;31(4):315--326.
+
+\bibitem{Kozielska:2010vm}
+Kozielska M, Weissing FJ, Beukeboom LW, Pen I.
+\newblock {Segregation distortion and the evolution of sex-determining
+  mechanisms}.
+\newblock Heredity. 2010;104:100--112.
+
+\bibitem{Ubeda:2015fx}
+{\'U}beda F, Patten MM, Wild G.
+\newblock {On the origin of sex chromosomes from meiotic drive.}
+\newblock Proceedings of the Royal Society B: Biological Sciences.
+  2015;282(1798):20141932.
+
+\bibitem{Kallman1968}
+Kallman K.
+\newblock {Evidence for the existence of transformer genes for sex in the
+  telost \textit{Xiphphorus maculatus}}.
+\newblock Genetics. 1968;60:811--828.
+
+\bibitem{Dubendorfer2002}
+Dubendorfer A, Hediger M, Burghardt G, Bopp D.
+\newblock \textit{Musca domestica}, a window on the evolution of sex-determining
+  mechanisms in insects.
+\newblock International Journal of Developmental Biology. 2002;46(1):75--79.
+
+\bibitem{Roco2015}
+Roco AS, Olmstead AW, Degitz SJ, Amano T, Zimmerman LB, Bullejos M.
+\newblock {Coexistence of Y, W, and Z sex chromosomes in \textit{Xenopus
+  tropicalis}}.
+\newblock Proceedings of the National Academy of Sciences.
+  2015;112(34):E4752--E4761.
+
+\bibitem{Holman:2015en}
+Holman L, Price TAR, Wedell N, Kokko H.
+\newblock {Coevolutionary dynamics of polyandry and sex-linked meiotic drive}.
+\newblock Evolution. 2015;69(3):709--720.
+
+\bibitem{Immler:2012tl}
+Immler S, Arnqvist G, Otto SP.
+\newblock {Ploidally antagonistic selection maintains stable genetic
+  polymorphism}.
+\newblock Evolution. 2012;66(1):55--65.
+
+\bibitem{Lloyd1977}
+Lloyd DG, Webb C.
+\newblock {Secondary sex characters in plants}.
+\newblock Botanical Review. 1977;43:177--216.
+
+\bibitem{Otto2014}
+Otto SP.
+\newblock {Selective maintenance of recombination between the sex chromosomes}.
+\newblock Journal of Evolutionary Biology. 2014;27:1431--1442.
+
+\bibitem{Lalanne2004}
+Lalanne E, Michaelidis C, Moore JM, Gagliano W, Johnson A, Patel R, et~al.
+\newblock {Analysis of transposon insertion mutants highlights the diversity of
+  mechanisms underlying male progamic development in \textit{Arabidopsis}}.
+\newblock Genetics. 2004;167:1975--1986.
+
+\bibitem{Fishman2005}
+Fishman L, Willis JH.
+\newblock {A novel meiotic drive locus almost completely distorts segregation
+  in \textit{Mimulus} (monkeyflower) hybrids}.
+\newblock Genetics. 2005;169:347--353.
+
+\bibitem{Leppala2008}
+Lepp{\"a}l{\"a} J, Bechsgaard JS, Schierup MH, Savolainen O.
+\newblock {Transmission ratio distortion in \textit{Arabidopsis lyrata}:
+  effects of population divergence and the S-locus}.
+\newblock Heredity. 2008;100:71--78.
+
+\bibitem{Leppala2013}
+Lepp{\"a}l{\"a} J, Bokma F, Savolainen O.
+\newblock {Investigating incipient speciation in \textit{Arabidopsis lyrata}
+  from patterns of transmission ratio distortion}.
+\newblock Genetics. 2013;194:697--708.
+
+\bibitem{Didion2015}
+Didion JP, Morgan AP, Clayschulte AMF, Mcmullon RC, Yadgary L, Petkov PM,
+  et~al.
+\newblock {A multi-megabase copy number gain causes maternal transmission ratio
+  distortion on mouse chromosome 2}.
+\newblock PLoS Genetics. 2015;11:e1004850.
+
+\bibitem{Didion2016}
+Didion JP, Morgan AP, Yadgary L, Bell TA, McMullan RC, Ortiz~de Solorzano L,
+  et~al.
+\newblock {R2d2 drives selfish genetic sweeps in the house mouse}.
+\newblock Molecular Biology and Evolution. 2016;33:1381--1395.
+
+\bibitem{Jaenike:2001vb}
+Jaenike J.
+\newblock {Sex chromosome meiotic drive}.
+\newblock Annual Review of Ecology and Systematics. 2001;32:25--49.
+
+\bibitem{Burt:2006}
+Burt A, Trivers R.
+\newblock {Genes in conflict: the biology of selfish genetic elements}.
+\newblock Cambridge, MA: Belknap Press; 2006.
+
+\bibitem{Lloyd:1974tz}
+Lloyd DG.
+\newblock {Female-predominant sex ratios in angiosperms}.
+\newblock Heredity. 1974;32(1):35--44.
+
+\bibitem{Conn:1981uw}
+Conn JS, Blum U.
+\newblock {Sex ratio of \emph{Rumex hastatulus}: the effect of environmental
+  factors and certation}.
+\newblock Evolution. 1981;35(6):1108--1116.
+
+\bibitem{Stehlik:2005ul}
+Stehlik I, Barrett S.
+\newblock {Mechanisms governing sex-ratio variation in dioecious \emph{Rumex
+  nivalis}}.
+\newblock Evolution. 2005;59(4):814--825.
+
+\bibitem{Stehlik:2006to}
+Stehlik I, Barrett SCH.
+\newblock {Pollination intensity influences sex ratios in dioecious \textit{Rumex
+  nivalis}, a wind-pollinated plant.}
+\newblock Evolution. 2006;60(6):1207--1214.
+
+\bibitem{Field:2012fd}
+Field DL, Pickup M, Barrett SCH.
+\newblock {The influence of pollination intensity on fertilization success,
+  progeny sex ratio, and fitness in a wind-pollinated, dioecious plant}.
+\newblock International Journal of Plant Sciences. 2012;173(2):184--191.
+
+\bibitem{Field:2013cc}
+Field DL, Pickup M, Barrett SCH.
+\newblock {Comparative analyses of sex-ratio variation in dioecious flowering
+  plants.}
+\newblock Evolution. 2013;67(3):661--672.
+
+\bibitem{Zheng:2001fi}
+Zheng Y, Deng X, Martin-DeLeon PA.
+\newblock {Lack of sharing of Spam1 (Ph-20) among mouse spermatids and
+  transmission ratio distortion}.
+\newblock Biology of Reproduction. 2001;64(6):1730--1738.
+
+\bibitem{Vibranovski:2010et}
+Vibranovski MD, Chalopin DS, Lopes HF, Long M, Karr TL.
+\newblock {Direct evidence for postmeiotic transcription during
+  \emph{Drosophila melanogaster} spermatogenesis}.
+\newblock Genetics. 2010;186(1):431--433.
+
+\bibitem{Immler:2014im}
+Immler S, Hotzy C, Alavioon G, Petersson E, Arnqvist G.
+\newblock {Sperm variation within a single ejaculate affects offspring
+  development in Atlantic salmon}.
+\newblock Biology Letters. 2014;10(2):20131040.
+
+\bibitem{Alavioon2017}
+Alavioon G, Hotzy C, Nakhro K, Rudolf S, Scofield DG, Zajitschek S, et~al.
+\newblock {Haploid selection within a single ejaculate increases offspring
+  fitness}.
+\newblock Proceedings of the National Academy of Sciences. 2017;114:8053--8058.
+
+\bibitem{Immler2018}
+Immler S, Otto SP.
+\newblock The evolutionary consequences of selection at the haploid gametic
+  stage.
+\newblock The American Naturalist. In
+  Press;doi:{https://dx.doi.org/10.1086/698483}.
+
+\bibitem{Tau2007}
+Tau Y, Araripe L, Kingan SB, Ke Y, Xiao H, Hartl DL.
+\newblock {A sex-ratio meiotic drive system in \textit{Drosophila simulans}.
+  II: an X-linked distorter}.
+\newblock PLoS Biology. 2007;5(11):e293.
+\newblock doi:{10.1371/journal.pbio.0050293}.
+
+\bibitem{Cocquet2012}
+Cocquet J, Ellis PJI, Mahadevaiah SK, Affara NA, Vaiman D, Burgoyne PS.
+\newblock {A genetic basis for a postmeiotic X versus Y chromosome intragenomic
+  conflict in the mouse}.
+\newblock PLoS Genetics. 2012;8(9):e1002900.
+\newblock doi:{10.1371/journal.pgen.1002900}.
+
+\bibitem{Helleu2016}
+Helleu Q, G{\'e}rard PR, Dubruille R, Ogereau D, Prud{\textquoteright}homme B,
+  Loppin B, et~al.
+\newblock Rapid evolution of a Y-chromosome heterochromatin protein underlies
+  sex chromosome meiotic drive.
+\newblock Proceedings of the National Academy of Sciences.
+  2016;113(15):4110--4115.
+\newblock doi:{10.1073/pnas.1519332113}.
+
+\bibitem{Bachtrog2018}
+Bachtrog D, Ellison C, Leonard C, Landeen E, Gibilisco L, Phadnis N.
+\newblock Rampant cryptic sex chromosome drive in \textit{Drosophila}.
+\newblock bioRxiv. 2018;doi:{10.1101/324368}.
+
+\bibitem{Borg:2009jpa}
+Borg M, Brownfield L, Twell D.
+\newblock {Male gametophyte development: a molecular perspective}.
+\newblock Journal of Experimental Botany. 2009;60(5):1465--1478.
+
+\bibitem{Arunkumar:2013iq}
+Arunkumar R, Josephs EB, Williamson RJ, Wright SI.
+\newblock {Pollen-specific, but not sperm-specific, genes show stronger
+  purifying selection and higher rates of positive selection than sporophytic
+  genes in \emph{Capsella grandiflora}}.
+\newblock Molecular Biology and Evolution. 2013;30(11):2475--2486.
+
+\bibitem{Gossmann:2014dua}
+Gossmann TI, Schmid MW, Grossniklaus U, Schmid KJ.
+\newblock {Selection-driven evolution of sex-biased genes is consistent with
+  sexual selection in \emph{Arabidopsis thaliana}}.
+\newblock Molecular biology and evolution. 2014;31(3):574--583.
+
+\bibitem{Hormaza:1996cv}
+Hormaza JI, Herrero M.
+\newblock {Male gametophytic selection as a plant breeding tool}.
+\newblock Scientia horticulturae. 1996;65(4):321--333.
+
+\bibitem{Ravikumar:2003uo}
+Ravikumar RL, Patil BS, Salimath PM.
+\newblock {Drought tolerance in sorghum by pollen selection using osmotic
+  stress}.
+\newblock Euphytica. 2003;133:371--376.
+
+\bibitem{Hedhly:2004iv}
+Hedhly A, Hormaza JI, Herrero M.
+\newblock {Effect of temperature on pollen tube kinetics and dynamics in sweet
+  cherry, \emph{Prunus avium} (Rosaceae).}
+\newblock American journal of botany. 2004;91(4):558--564.
+
+\bibitem{Clarke:2004ir}
+Clarke HJ, Khan TN, Siddique KHM.
+\newblock {Pollen selection for chilling tolerance at hybridisation leads to
+  improved chickpea cultivars}.
+\newblock Euphytica. 2004;139(1):65--74.
+
+\bibitem{Sandler264382}
+Sandler G, Beaudry FEG, Barrett SCH, Wright SI.
+\newblock The effects of haploid selection on Y chromosome evolution in a
+  dioecious plant.
+\newblock bioRxiv. 2018;doi:{10.1101/264382}.
+
+\bibitem{Kafer2017}
+K{\"a}fer J, Marais GAB, Pannell J.
+\newblock {On the rarity of dioecy in flowering plants}.
+\newblock Molecular Ecology. 2017;26:1225--1241.
+
+\bibitem{Goldberg2017}
+Goldberg EE, Otto SP, Vamosi JC, Mayrose I, Sabath N, Ming R.
+\newblock {Macroevolutionary synthesis of flowering plant sexual systems}.
+\newblock Evolution. 2017;71:898--912.
+
+\bibitem{Charlesworth1978}
+Charlesworth B, Charlesworth D.
+\newblock A model for the evolution of dioecy and gynodioecy.
+\newblock The American Naturalist. 1978;112(988):975--997.
+
+\bibitem{Lindholm:2002dw}
+Lindholm A, Breden F.
+\newblock {Sex chromosomes and sexual selection in poeciliid fishes}.
+\newblock The American Naturalist. 2002;160(S6):S214--24.
+
+\bibitem{Tripathi:2009cw}
+Tripathi N, Hoffmann M, Willing EM, Lanz C, Weigel D, Dreyer C.
+\newblock {Genetic linkage map of the guppy, \textit{Poecilia reticulata}, and
+  quantitative trait loci analysis of male size and colour variation.}
+\newblock Proceedings of the Royal Society B: Biological Sciences.
+  2009;276(1665):2195--2208.
+
+\bibitem{Roberts2009}
+Roberts RB, Ser JR, Kocher TD.
+\newblock Sexual conflict resolved by invasion of a novel xex determiner in
+  Lake Malawi cichlid fishes.
+\newblock Science. 2009;326(5955):998--1001.
+
+\bibitem{Kallman1965}
+Kallman K.
+\newblock {Genetics and geography of sex determination in the poeciliid fish,
+  \textit{Xiphphorus maculatus}}.
+\newblock Zoologica. 1965;50(13):151--190.
+
+\bibitem{Volff2001}
+Volff JN, Schartl M.
+\newblock {Variability of genetic sex determination in poeciliid fishes}.
+\newblock Genetica. 2001;111(1):101--110.
+
+\bibitem{Schultheis2006}
+Schulteis C, Zhou Q, Froschauer A, Nanda I, Selz Y, Schmidt C, et~al.
+\newblock {Molecular analysis of the sex-determining region of the platyfish
+  \textit{Xiphophorus maculatus}}.
+\newblock Zebrafish. 2006;3(3):299--309.
+
+\bibitem{Fredga1994}
+Fredga K.
+\newblock Bizarre mammalian sex-determining mechanisms.
+\newblock In: Short RV, Balaban E, editors. The differences between the sexes.
+  Cambridge, USA: Cambridge University Press; 1994. p. 419--432.
+
+\bibitem{Bianchi2002}
+Bianchi NO.
+\newblock {\textit{Akodon} sex reversed females: the never ending story}.
+\newblock Cytogenetic and Genome Research. 2002;96:60--65.
+
+\bibitem{Sanchez2010}
+S{\'a}nchez A, Marchal JA, Romero-Fern{\'a}ndez I, Pinna-Senn E, Ortiz MI,
+  Bella JL, et~al.
+\newblock {No differences in the \textit{Sry} gene between males and XY females
+  in \textit{Akodon} (Rodentia, Cricetidae)}.
+\newblock Sexual Development. 2010;4:155--161.
+
+\bibitem{Hoekstra2001}
+Hoekstra HE, Hoekstra JM.
+\newblock {An unusual sex-determination system in South American field mice
+  (genus \textit{Akodon}): the role of mutation, selection, and meiotic drive
+  in maintaining XY females}.
+\newblock Evolution. 2001;55(1):190--197.
+
+\bibitem{Veyrunes2010}
+Veyrunes F, Chevret P, Catalan J, Castiglia R, Watson J, Dobigny G, et~al.
+\newblock {A novel sex determination system in a close relative of the house
+  mouse}.
+\newblock Proceedings of the Royal Society B: Biological Sciences.
+  2010;277(1684):1049--1056.
+
+\bibitem{Saunders2014}
+Saunders PA, Perez J, Rahmoun M, Ronce O, Crochet PA, Veyrunes F.
+\newblock {XY females do better than the XX in the African pygmy mouse,
+  \textit{Mus minutoides}}.
+\newblock Evolution. 2014;68(7):2119--2127.
+
+\bibitem{Saunders2016}
+Saunders PA, Franco T, Sottas C, Maurice T, Guila G, Veyrunes F.
+\newblock {XY females do better than the XX in the African pygmy mouse,
+  \textit{Mus minutoides}}.
+\newblock Scientific Reports. 2016;6:22881e.
+
+\bibitem{Veyrunes2017}
+Veyrunes F, Perez J.
+\newblock {X inactivation in a mammal species with three sex chromosomes}.
+\newblock Chromosoma. 2017;127(2):261--267.
+
+\bibitem{Rice:1996ke}
+Rice WR.
+\newblock {Evolution of the Y sex chromosome in animals}.
+\newblock BioScience. 1996;46(5):331--343.
+
+\bibitem{Charlesworth:2000cc}
+Charlesworth B, Charlesworth D.
+\newblock {The degeneration of Y chromosomes.}
+\newblock Philosophical Transactions of the Royal Society B: Biological
+  sciences. 2000;355(1403):1563--1572.
+
+\bibitem{Bachtrog:2006ed}
+Bachtrog D.
+\newblock {A dynamic view of sex chromosome evolution.}
+\newblock Current opinion in genetics {\&} development. 2006;16(6):578--585.
+
+\bibitem{Marais:2008hm}
+Marais GAB, Nicolas M, Bergero R, Chambrier P, Kejnovsky E, Mon{\'e}ger F,
+  et~al.
+\newblock {Evidence for degeneration of the Y chromosome in the dioecious plant
+  \emph{Silene latifolia}}.
+\newblock Current Biology. 2008;18(7):545--549.
+
+\bibitem{Veller2017}
+Veller C, Muralidhar P, Constable GWA, Nowak MA.
+\newblock Drift-induced selection between male and female heterogamety.
+\newblock Genetics. 2017;207(2):711--727.
+
+\end{thebibliography}
 

### 2018-06-03 LaTeX/Turnover_bioRXiv_final.tex
biorxiv revised with final submission

--- 2018-06-02 LaTeX/Turnover_bioRXiv_revision.tex
@@
 \noindent\textit{Conclusion 4:}
-\textbf{When selection is weak relative to recombination, the presence of haploid selection equally favors the spread of new sex determination systems that reduce sex-ratio bias (benefiting from Fisherian sex ratio selection) or that generate a sex-ratio bias (benefiting from associations with selected alleles).
+\textbf{When selection is weak relative to recombination, trans-GSD transitions in the presence of haploid selection are favoured as often and as strongly whether they erase ancestral sex-ratio bias (benefiting from Fisherian sex ratio selection) or generate sex-ratio bias (benefiting from associations with selected alleles).
 }
@@
 \label{file:Mathematica}
-{\bf Supplementary \textit{Mathematica} file.}  This file can be used to re-derive our results and generate figures. Please contact authors for access.
+{\bf Supplementary \textit{Mathematica} file.}  This file can be used to re-derive our results and generate figures. Please contact authors for access (or for a PDF version).
 
